### 2020-06-02 appendix/major.tex
Initial Overleaf Import

\section{Properties of majorization}
\label{app:major}

\subsection{Equivalent conditions for majorization}

\begin{theorem}
Given $\bmx, \bmy, \bmd \in \mathbb{R}^n$, such that the components of $\bmd$ are positive, the following statements are equivalent:
 \begin{enumerate}
	\item[(TM1)] $\bmx \prec_{\bmd} \bmy$;
	\item[(TM2)] $\Gamma_{\bmd}({\bmx}) \prec \Gamma_{\bmd}({\bmy})$;
	\item[(TM3)]\label{en:tm3} $\sum\limits_{i=1}^n \abs{x_i - t d_i} \leq \sum\limits_{i=1}^n \abs{y_i - t d_i}$ for all $t \in \mathbb{R}$;
	\item[(TM4)] $\sum\limits_{i=1}^n (x_i - t d_i)^+ \leq \sum\limits_{i=1}^n (y_i - t d_i)^+$ for all $t \in \mathbb{R}$ and $\sum\limits_{i=1}^n x_i = \sum\limits_{i=1}^n y_i$;
	\item[(TM5)] $\forall k, L_{\bmx|\bmd}(k) \leq L_{\bmy|\bmd}(k)$ and $L_{\bmx|\bmd}(k=n) = L_{\bmy|\bmd}(k=n)$.
 \end{enumerate}
\end{theorem}
\begin{proof}
    \begin{enumerate}
        \item[1$\leftrightarrow2$]
        Suppose now there exists a stochastic $S$ such that $\bmx = S\bmy$ with $\bmd = S\bmd$ and let $B = \Gamma_{\bmd} \circ S \circ \Gamma_{\bmd}^{-1}$.
        $B$ is a $D$-dimensional bistochastic matrix, since composition of stochastic matrices is stochastic and $(\Gamma_{\bmd} \circ S \circ \Gamma_{\bmd}^{-1}) (\frac{1}{D}\bm{1}) = (\Gamma_{\bmd} \circ S) (\bm{d}) = \Gamma_{\bmd}(\bm{d}) = \frac{1}{D}\bm{1}$. Then, $B$ maps $\Gamma_{\bmd}({\bmy})$ to $\Gamma_{\bmd}({\bmx})$.
        Conversely, given $B$, let $S = \Gamma_{\bmd}^{-1} \circ B \circ \Gamma_{\bmd}$.
        Similarly, $S$ is the stochastic matrix that preserves $\bmd$ and maps $\bmy$ to $\bmx$.
        \item[$2\leftrightarrow3$]\hspace{-5pt}, $2\leftrightarrow4$, $2\leftrightarrow5$ These three statement are equivalent to \nick{blah} respectively for the embedded vectors $\Gamma_{\bmd}({\bmx}), \Gamma_{\bmd}({\bmy})$.
        This is clear by rewriting
        \begin{align}
            \sum\limits_{i=1}^n \abs{x_i - t d_i} &= \sum\limits_{i=1}^n d_i \abs{\frac{x_i}{d_i} - t} = \sum\limits_{i=1}^D \abs{\Gamma_{\bmd}(\bmx)_i - t}, \\
            \sum\limits_{i=1}^n (x_i - t d_i)^+ &= \sum\limits_{i=1}^D (\Gamma_{\bmd}(\bmx)_i - t)^+, \\
            L_{\bmx|\bmd}(k) &= L_{\Gamma_{\bmd}(\bmx)}(k'), \\
            \text{with}\ k&=1,\dots,n\ \text{and}\ k'=1,\dots,D \nonumber
        \end{align} 
        and similarly for the right hand side.
    \end{enumerate}
\end{proof}

\subsection{Mana properties}
Mana monotonicity can be directly seen due to statement~\ref{en:tm3} in~\cref{thm:dmajor} for $t=0$.
Furthermore, mana is additive due to the multiplicative property~\ref{en:w4} of~\cref{thm:wstate}.

### 2020-06-02 appendix/wigner.tex
Initial Overleaf Import

\section{Properties of the Wigner distribution}
\label{app:wigner}

Here we present important properties of the Wigner distribution that are used throughout the paper.

\begin{proposition}\label{thm:wstate}
    The Wigner distribution of a state $\rho$ is
    \begin{enumerate}%[label=\enlabel{W}{\arabic*}]
        \item\label{en:w1} Real valued: $\W{\rho} \in \mathbb{R}^{d^2}$;
        \item\label{en:w2} Normalised: $\sum_{\bmz \in \pd} \W[\bmz]{\rho}=1$;
        \item\label{en:w3} Bounded: $\abs{\W[\bmx]{\rho}} \leq \frac{1}{d}$.
        \item\label{en:w4} Additive under mixing:

        $\W[\bmx]{\sum_i p_i \rho_i} = \sum\limits_i p_i \W[\bmx]{\rho_i}$;
        \item\label{en:w5} Multiplicative under tensor products:

        $\W[\bmx_A \oplus \bmx_B]{\rho_A \otimes \rho_B} = \W[\bmx_A]{\rho_A}\W[\bmx_B]{\rho_B}$.
	\end{enumerate}
\end{proposition}

\begin{proposition}
    \label{thm:wchannel}
    The Wigner distribution of a $\cptp$ operation $\E: \cal{B}(\hd[d_A]) \mapsto \cal{B}(\hd[d_B])$ is:
    \begin{enumerate}
        \item\label{en:wo1} Real-valued: $\W[\bmy|\bmx]{\E} \in \mathbb{R}$;
        \item\label{en:wo2} Normalised: $\sum_{\bmz \in \pd[d_B]} \W[\bmz|\bmx]{\E} = 1$ for any $\bmx \in \pd[d_A]$;
        \item\label{en:wo3} Bounded: $\abs{\W[\bmy|\bmx]{\E}} \leq \frac{d_A}{d_B}$;
	    \item\label{en:wo4} \nick{Transitive}: $\W[\bmy]{\E(\rho)} = \sum_{\bmz \in \pd[d_A]} \W[\bmy|\bmz]{\E} \W[\bmz]{\rho}$ for any $\bmy \in \pd[d_B]$.
    \end{enumerate}
\end{proposition}
If $d_A = d_B$, and in particular if operation $\E$ maps a Hilbert space onto itself, then the stochasticity condition $\abs{\W[\bmy|\bmx]{\E}} \leq 1$ is satisfied.

### 2020-06-02 magic_paper.tex
Initial Overleaf Import

\input{preamble/magic_preamble}

\begin{document}

\input{sections/abstract}
\input{sections/title}
\maketitle

\input{sections/introduction}
\newpage
\input{sections/magic/magic}
\input{sections/magic/phasespace}
\input{sections/major/major}
\newpage
\input{sections/distill/distill}
\input{sections/conclusion}

\bibliography{bib/magic_bib}
\bibliographystyle{bib/apsrev4-2}

\appendix
\input{appendix/wigner}
\input{appendix/major}

\end{document}

### 2020-06-02 sections/abstract.tex
Initial Overleaf Import

\begin{abstract}
Magic states are essential for achieving universality in fault-tolerant schemes.
Magic resource theories attempt to quantify magic via monotones and thus describe the manipulation of magic states.
Here we introduce the concept of majorization fragments as a more generalised projection of such theories in discrete odd dimensions which allows for more powerful results than what monotones can provide.
Fragments naturally link the symmetries of a gate sequence with conditions on the convertibility between states.
We demonstrate the power of fragments by providing exact conditions for the convertibility of single-copy qutrit magic states as well as stricter distillation bounds than the established mana monotone in any odd dimension.
\end{abstract}

### 2020-06-02 sections/distill/distill.tex
Initial Overleaf Import

\section{Distillation bounds}
\label{sec:distill}

Consider a general magic state distillation process,
\begin{equation}\label{eq:distprocess}
    \rho^{\otimes k} \xrightarrow{\E \in \O} \tau,
\end{equation}
where $n$ noisy copies of magic state $\rho$ are converted to a single-copy magic state $\tau$.
Identifying a symmetry of the distillation process responsible for leaving a state $\sigma$ invariant is equivalent with restricting the process to the $\sigma$-fragment $\O_\sigma$.

Mana is monotonic and additive in all $\sigma$-fragments as seen in~\cref{app:major}, so it provides a bound for distillation processes
\begin{equation}
    \mana{\rho} \geq \frac{1}{k} \mana{\tau}.
\end{equation}.

A new bound can be obtained in any $\sigma$-fragment by comparing the Lorenz curves of the initial and target states,
\begin{equation}\label{eq:majbound}
    L_k(\rho^{\otimes k} | \sigma) \geq L_k (\tau | \sigma),\ k=1,\dots,d^2,
\end{equation}
If the Lorenz curve of the initial state is below the target curve at any point, the process is not possible.
In general, the Wigner components of a $k$-copy state $\rho^{\otimes k}$ are calculated, along with their multiplicities, by expanding the terms in the multinomial expansion $\left( \sum_{\bm{z} \in \cal{P}_d} W_\rho(\bm{z}) \right)^n$.
This follows from the multiplicativity of the Wigner distribution.

The Strange state $\ketbra{\rm{S}}$ depicted in~\cref{fig:strange} is the simplest to analyse, since it only has two distinct components $\{ -\frac{1}{3}, \frac{1}{6} \}$, the latter with a multiplicity of 8.
Calculating the binomial expansion for the components of $\ket{S}\bra{S}^{\otimes k}$ gives $\{(-1)^j 2^{j-k} 3^{-k}\}_{0 \leq j \leq k}$ with multiplicity $8^{k-j} \binom{k}{j}$ for the $j$-th term.
This allows analytical calculation of all Lorenz curve points, hence the maximum of the $k$-copy state is
\begin{equation}\label{eq:Skmax}
    \max_k{L_k \left( \ketbra{S}^{\otimes k} \bigm| \sigma \right)} = 1 + \left(\frac{4}{3}\right)^k \sum\limits_{j: 1 \leq 2j+1 \leq k} 4^{-(2j+1)} \binom{k}{2j+1}.
\end{equation}

Consider the noisy Strange state,
\begin{equation}
    \rho_{\rm{S}}(\epsilon) = (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \sigma,
\end{equation}
in the $\sigma$-fragment $\O_\sigma$.
At noise level $\epsilon \leq \frac{3}{4}$, the Wigner distribution $\W{\rho_{\rm{S}}(\epsilon)}$ contains negativities and the state can be purified so as to obtain a single-copy state with sufficiently low $\epsilon$.
In~\cref{fig:distill}, we examine the purifying process 
\begin{equation}\label{eq:purify}
    \rho_{\rm{S}}^{\otimes k}(\epsilon_{\rm{th}}) \xrightarrow{\E \in \O_\sigma} \rho_{\rm{S}}(0.05),\ \sigma = (1-p)\ketbra{0} + p \frac{1}{3}\id
\end{equation}
with $\epsilon_{\rm{th}}$ being the noise level threshold that does not prohibit the process for given number of copies $k$ and $\sigma$-fragment, parametrised by $p$ as a mixture of the zero and the maximally mixed states.
\begin{figure}
    \centering
    \includegraphics[scale=0.5]{sections/distill/ratios.pdf}
    \caption{Plot of the noise level threshold ratios between mana and Lorenz curve for the Strange state purifying process in~\cref{eq:purify}.
    The ratios are calculated for different numbers of initial state copies and different $\sigma$-fragments parametrised by $p$ such that $\sigma = (1-p)\ketbra{0} + p \frac{1}{3}\id$.
    Lorenz curve comparison consistently gives stricter bounds as proven in~\cref{thm:bounds}.
    }
    \label{fig:distill}
\end{figure}

Thresholds provided by Lorenz curve comparison are always much stricter than mana thresholds \nick{threshold/bound? need to define the notion of a bound precisely}.
In fact, it is clear than this is the case in any general distillation process.
\begin{theorem}\label{thm:bounds}
    Consider the distillation process in~\cref{eq:distprocess}.
    In any $\sigma$-fragment, $\W{\sigma}$-majorization provides a stricter bound than mana.
\end{theorem}
\begin{proof}
    The maximum of the Lorenz curve of a state $\rho$ can be expressed monotonically in terms of mana, independently of the $\sigma$-fragment,
    \begin{equation}
        \max_k{L_k(\rho | \sigma)} = 1 + \sum_{\bmz: \W[\bmz]{\rho}<0} \abs{\W[\bmz]{\rho}} = \frac{1}{2} \left( 1 + e^\mana{\rho} \right).
    \end{equation}
    Therefore, the majorization condition stated in~\cref{eq:majbound} implies that $\mana{\rho^{\otimes k}} \geq \mana{\tau}$.
\end{proof}

### 2020-06-02 sections/introduction.tex
Initial Overleaf Import

\section{Introduction}
\label{sec:intro}

\begin{enumerate}
    \item Fault-tolerance~\cite{cit:raussendorf, cit:gross2, cit:markov, cit:gross, cit:nest, cit:nest2, cit:vidal, cit:fujii, cit:gottesman}
    \item Magic~\cite{cit:veitch, cit:veitch2, cit:wang, cit:wang2, cit:howard, cit:campbell, cit:gross3, cit:gross4}
    \item Bringing in majorization~\cite{cit:cwiklinski, cit:lostaglio2, cit:lostaglio, cit:gour, cit:janzing, cit:brandao2, cit:gour2, cit:marshall, cit:nielsen}
    \item Section breakdown
\end{enumerate}

### 2020-06-02 sections/magic/magic.tex
Initial Overleaf Import

\section{Magic Resource Theories}
\label{sec:magic}

\subsection{Introduction}

Magic states are necessary for achieving universal quantum computation within fault-tolerant schemes.
Identifying magic as a resource for quantum universality has led to several theories which try to provide a framework for its quantification and manipulation \nick{CITE}.
The main question that such a theory attempts to answer is:
\begin{center}
    \emph{Given two magic states $\rho$ and $\rho'$ is there a free operation that can convert $\rho$ to $\rho'$?}
\end{center}
Magic monotones are often used \nick{CITE} to partially address this question, although such approaches do not exploit much of the structure of the theory.
Therefore, we introduce a generalised notion of a measure, the \emph{fragment}, applicable in general resource theories and in particular in all theories of magic we consider. \nick{expand}

We are interested in all resource theories of magic $\R = (\F, \O)$ that obey two assumptions:
\begin{enumerate}[I]
    \item Free operations send free states into free states, $\E: \F \mapsto \F$, for all $\E \in \O$;
    \item Resource theory $\R$ is a completely free state preserving theory, in the sense that for any $d$-dimensional ancilla system and all free operations $\E$, $(\id_d \otimes \E ) \sigma \in \F$ whenever $\sigma \in \F$.
\end{enumerate}
The first assumption simply states that resources cannot be generated for free and is a minimal requirement for a resource theory. 
An immediate consequence is that if statistical mixing is included in $\O$, then the resource theory is convex.
Convex resource theories have attracted a lot of attention recently \nick{CITE} and include the magic theories discussed in~\cref{sec:prev}.
The second assumption implies that resources cannot be generated even when ancillas are allowed \nick{example of T state generation on Bell state by Campbell}.

The main result of this paper is that any magic theory $\R$ satisfying the above assumptions can be recast as a subtheory of stochasticity.
This reformulation grants additional power to the theory as the structure of stochastic process can be exploited to add insight to the main questions of theories as stated above. \nick{expand}

\subsection{Previous work}\label{sec:prev}

The stabilizer theory \nick{CITE} is the first theory to introduce the idea of magic and it is discussed in sufficient detail for our purposes in~\cref{sec:so}. 
It comprises of the so-called ``stabilizer'' states ($\stab$) and operations ($\so$), while non-stabilizer (resource) states are called magic.
The stabilizer operations can be expressed in terms of a Stinespring dilation as 
\begin{equation}
    \E(\rho) = \tr_E [U(\rho \otimes \sigma_E)U^\dagger],
\end{equation} 
for an ancilla stabilizer state $\sigma_E$. 
The motivation of the theory stems from the fact that stabilizer operations are experimentally straightforward to implement and they can be used to detect and correct errors on the stabilizer states due to their construction \nick{CITE}.
The Gottesman-Knill theorem however indicates that stabilizer operations need to be supplemented with magic states in order to achieve universality, justifying the term ``magic''.

Generalisations of the stabilizer theory appear in the literature intending to include broader classes of operations \nick{CITE}.
The class of stabilizer preserving operations ($\spo$) is defined as the set of $\cptp$ maps that send stabilizer states into stabilizer states~\cite{cit:ahmadi}.
An important subclass of $\spo$ is the set of completely stabilizer preserving operations ($\cspo$), which intuitively cannot induce ``non-stabilizerness'' even when applied to only part of a quantum state, i.e. operations $\E$ such that $(\id_d \otimes \E ) \sigma \in \stab$ for all positive dimensions $d$ whenever $\sigma \in \stab$.

Even though non-stabilizerness is a necessary resource for universality, it has been proven insufficient for magic state distillation~\cite{cit:bravyi, cit:campbell}.
In fact, all states with non-negative Wigner distributions have been proven to be efficiently classically simulable in~\cite{cit:mari}, a result that serves as a generalization of the Gottesman-Knill theorem.
The Wigner distribution of a state in odd prime dimensions is discussed rigorously in~\cref{sec:wigner} and arises as the unique quasi-probability representation of quantum theory that identifies non-contextuality exactly with the states that are efficiently classically simulable~\cite{cit:howard2, cit:veitch2}.
In this framework, the stabilizer states are the only pure states represented with non-negative distributions~\cite{cit:gross3}. 
However, there exist mixed states with non-negative Wigner distributions that are not mixtures of stabilizer states~\cite{cit:gross}.
Therefore, stabilizer-preserving theories have been extended to a theory that preserves state ``Wigner positivity''~\cite{cit:wang}, formally defined in~\cref{sec:wigner} for odd prime dimensions.
Informally, it can be considered as the maximal theory of magic $\R_{\rm{max}} = (\F_{\rm{max}}, \O_{\rm{max}})$, where free states have non-negative Wigner distributions and free operations completely preserve this property.

### 2020-06-02 sections/magic/phasespace.tex
Initial Overleaf Import

\section{Phase Space formalism}
\label{sec:ps}

\subsection{Stabilizer Theory}\label{sec:so}

Let $\{\ket{k}\}_{k \in \zd}$ be the standard computational basis for an arbitrary fault-tolerant scheme, defined over the finite field $\zd = \{ 0, 1, \dots,d-1 \}$, with $d$ an odd prime. 
Since the field has character $d$, addition and multiplication on the field are always considered modulo $d$.
The Hilbert space of any system associated with this scheme is $\hd \coloneqq \spanv{\ket{k}: k \in \zd}$.

The generalised Pauli matrices $X, Z$ can be defined by their respective roles as shift and phase operators,
\begin{align}
    X \ket{k} &= \ket{k + 1} \label{eq:xpauli}\\
	Z \ket{k} &= \omega^k \ket{k}, \label{eq:zpauli}
\end{align}
where $\omega \coloneqq e^{2\pi i/d}$ is the $d$-th root of unity.

The Hilbert space $\hd$ is associated with a phase space $\pd \coloneqq \zd \times \zd$, where every point $\bmx \coloneqq (x_0, x_1)$ corresponds to a displacement operator, defined as
\begin{equation}\label{eq:ddef}
    D_{\bmx} \coloneqq \tau^{x_0 x_1} X^{x_0} Z^{x_1},\ \bmx  \in \pd.
\end{equation}
The phase factor $\tau \coloneqq -\omega^{1/2}$ ensures unitarity.
For a system with composite Hilbert space, $\hd = \hd[d_A] \otimes \hd[d_B]$, the displacement operators are defined as
\begin{equation}\label{eq:composited}
    D_{\bmx_A \oplus \bmx_B} \coloneqq D_{\bmx_A} \otimes D_{\bmx_B},
\end{equation}
where $\bmx_A \oplus \bmx_B \coloneqq (x_{A0}, x_{B0}, x_{A1}, x_{B1}) \in \pd[d_A] \times \pd[d_B]$.

The displacement operators, form a group under matrix multiplication modulo phases,
\begin{equation}\label{eq:gp}
    \gp \coloneqq \{ \tau^k D_{\bmz}: k \in \zd, \bmz \in \pd\}.
\end{equation}
The Clifford unitaries $\cd$ can then be defined as the normaliser of this group, \nick{Reformulate for copies of qudits: $\gp,\ \cd \rightarrow \gp^n,\ \cd^n$. $C-SUM$s live in $\cd^2$}
\begin{equation}
    \cd \coloneqq \{ U \in {\rm{SU}}(d): U\gp U^\dagger = \gp \}.
\end{equation}
The pure stabilizer states are then the orbit of the Clifford unitaries over a computational basis state,
\begin{equation}\label{eq:stab}
    \stab_{{\rm{pure}}} \coloneqq \{ U\ketbra{0}{0}U^\dagger: U \in \cd \}.
\end{equation}

The free states of the stabilizer theory are mixtures of pure stabilizers, 
\begin{equation}
    \stab = \conv\ \stab_{{\rm{pure}}}.
\end{equation}
The free operations of the stabilizer theory is the set of stabilizer operations $\so$ defined as any composition of:
\begin{enumerate}
    \item Preparation in computational basis;
    \item Random Clifford unitaries $\rcu$, i.e. operations $\E$ such that 
    \begin{equation}
        \E(\rho) = \sum_i p_i U_i \rho U_i^\dagger,\ U_i \in \cd;
\end{equation}
    \item Measurement in computational basis.
\end{enumerate}

\subsection{Wigner Distribution}\label{sec:wigner}

We can define the phase-point operators,
\begin{align}
	A_{\bmx} \coloneqq \frac{1}{d} \sum_{\bmz \in \pd} \omega^{\bmx \wedge \bmz} D_{\bmz},\ \bmx \in \pd. \label{eq:ax}
\end{align}
\nick{$\wedge$ has not be defined} They form an orthogonal Hermitian operator basis.
Therefore, any quantum state $\rho \in \cal{B}(\hd)$ can be expressed as a linear combination of the phase-point operators,
\begin{equation}
    \rho = \sum_{\bmz \in \pd} \W[\bmz]{\rho} A_{\bmz},
\end{equation}
where the coefficient vector $\W{\rho}$ is the Wigner distribution of state $\rho$,
\begin{equation}\label{eq:wstate}
    \W[\bmx]{\rho} \coloneqq \frac{1}{d}\tr[A_{\bmx} \rho].
\end{equation}
It is in fact a bounded $d^2$-dimensional quasi-probability distribution over $\pd$ as shown in~\cref{app:wigner}.

The Wigner distributions of different types of qutrit states are illustrated in~\cref{fig:wstate_examples}.
\begin{figure}%
    \centering
    \subfigure[][]{%
    \label{fig:maxmix}%
    \includegraphics[height=2cm]{sections/magic/maxmixed.pdf}
    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
    }\hspace{8pt}%
    \subfigure[][]{%
    \label{fig:zero}%
    \includegraphics[height=2cm]{sections/magic/zerostate.pdf}
    %\caption{Zero state $\ketbra{0}{0}$}%
    }\\
    \subfigure[][]{%
    \label{fig:bound}%
    \includegraphics[height=2cm]{sections/magic/boundstate.pdf}
    %\caption{Bound state}%
    }\hspace{8pt}%
    \subfigure[][]{%
    \label{fig:strange}%
    \includegraphics[height=2cm]{sections/magic/strangestate.pdf}
    %\caption{Strange state $\ketbra{S}{S}$}%
    }
    \caption{Wigner distributions for qutrit states of varying magic. 
    \subref{fig:maxmix} Maximally mixed state $\frac{1}{3}\id$; \subref{fig:zero} Stabilizer zero state $\ketbra{0}{0}$; \subref{fig:bound} A non-stabilizer Wigner-positive state; \subref{fig:strange} Magic strange state $\ket{{\rm{S}}} = \frac{1}{\sqrt{2}}(\ket{1} - \ket{2})$.
    \nick{Explain what a magic / bound magic state is in intro}
    }%
    \label{fig:wstate_examples}
\end{figure}

We can exploit the channel-state duality and use the normalised Choi-Jamio\l{}kowski state 
\begin{equation}\label{eq:cj}
    \frac{1}{d_A}\J_\E \coloneqq \frac{1}{d_A}(\id \otimes \E) \sum_{i,j} \ket{ii}\bra{jj}
\end{equation}
to extend the definition of the Wigner distribution to quantum $\cptp$ operations $\E: \cal{B}(\hd[d_A]) \mapsto \cal{B}(\hd[d_B])$, 
\begin{align}\label{eq:woperation}
    \W[\bmy|\bmx]{\E} 
    &\coloneqq d_A^2 \W[\bm{\bar x} \oplus \bmy]{\frac{1}{d_A}\J_\E} \\
    &= \frac{1}{d_B} \tr_B[A_{\bmy} \E(A_{\bmx})],
\end{align}
where $\bm{\bar x} \coloneqq (x_0, -x_1)$.

The particular form of~\cref{eq:woperation} was chosen so that Wigner distributions of operations act as transition matrices for Wigner distribution of states, $\W{\E(\rho)} = \W{\E}\W{\rho}$.
In particular, $\cptp$ operations that map a Hilbert space to itself and have non-negative Wigner distributions correspond to stochastic matrices.
All these properties are shown in~\cref{app:wigner}

The single-qudit Hadamard gate $H$ and phase gate $S$ generate the $d$-dimensional Clifford group $\cd$. \nick{CITE}
Their Wigner distributions are given by permutation matrices,
\begin{align}
    H &\coloneqq \frac{1}{\sqrt{d}}\sum_{j,k} \omega^{jk} \ketbra{j}{k}, \W[\bmy|\bmx]{H} = \delta_{y_0, -x_1}\delta_{y_1, x_0};\label{eq:H}\\
    S &\coloneqq \sum_k \tau^{k(k+1)} \ketbra{k}{k}, \W[\bmy|\bmx]{S} = \delta_{y_0, x_0}\delta_{y_1, x_0 + x_1 + 2^{-1}}.\label{eq:S}
\end{align}

Equipped with the definitions of the Wigner distribution, we can formally define the Wigner positivity theory $\R_{\rm{max}}$ in odd prime dimensions.
The free states are all states with non-negative Wigner distributions 
\begin{equation}
    \F_{\rm{max}} \coloneqq \{ \rho: \W[\bmz]{\rho} \geq 0 \text{ for all } \bmz \in \pd\}
\end{equation}
The free operations should send the set of free states $\F_{\rm{max}}$ into itself and completely preserve the non-negativity of the states, in the sense that $\E \in \O_{\rm{max}}$ iff $(\id_d \otimes \E ) \sigma \in \stab$ for all odd prime dimensions $d$ whenever $\sigma \in \F_{\rm{max}}$.

It is shown by Wang \textit{et al.}~\cite{cit:wang} that $\O_{\rm{max}}$ coincides with the set of operations $\E$ with a non-negative Wigner distributions, 
\begin{equation}
    \O_{\rm{max}} = \{ \E: \W[\bmy|\bmx]{\E} \geq 0 \text{ for all } \bmx, \bmy \in \pd\}.
\end{equation}

### 2020-06-02 sections/major/major.tex
Initial Overleaf Import

\section{Stochastic structure of magic theories}
\label{sec:struc}

\subsection{Fragments}\label{sec:frag}

Magic is commonly quantified via monotones \nick{CITE}. 
A monotone is a projection from the $d$-dimensional set of density states of the theory to the real line. 
It is monotonically decreasing under free operations, reflecting the no resource generating property of free operations and thus respecting the pre-order $\prec$ of the theory.
A popular magic monotone is the \emph{mana} of a state \nick{CITE}, defined as
\begin{equation}
    \mana{\rho} \coloneqq \log{\left(\sum\limits_{\bmz \in \pd} \abs{\W[\bmz]{\rho}}\right)}.
\end{equation}
However, a single monotone does not provide information on whether two states are incomparable in the theory.
Motivated by this restrictive nature of the monotone, we introduce the idea of a \emph{fragment} as a less restrictive way of comparing the resource of states in an arbitrary theory $\R = (\F, \O)$. \nick{explain exactly why fragments $>$ monotones}
Let $\R' = (\F', \O')$ be a subtheory of $\R$ so that $\F' \subseteq \F$ and $\O' \subseteq \O$. 
Then, we define a fragment as follows.
\begin{definition}\label{def:fragment}
    Let a resource theory $\R = (\F, \O)$ have pre-order $\prec_{\R}$ and operational composition rule $\circ_{\R}$. 
    We call a resource fragment of $\R$ any theory $\R' = (\F', \O')$ with pre-order $\prec_{\R'}$ and operational composition rule $\circ_{\R'}$, if there exists a surjective projection $\Pi \equiv (\Pis, \Pio): \R \mapsto \R'$ that satisfies the following two conditions.
    \begin{enumerate}
        \item $\Pis: \F \mapsto \F'$ and $\Pis(\rho_1) \prec_{\R'} \Pis(\rho_2)$ whenever $\rho_1 \prec_{\R} \rho_2$ for any states $\rho_1, \rho_2 \in \F$;
        \item $\Pio: \O \mapsto \O'$ and $\Pio(\E_1) \circ_{\R'} \Pio(\E_2) = \Pio(\E_1 \circ_{\R} \E_2)$ for any free operations $\E_1, \E_2 \in \O$. 
    \end{enumerate}
\end{definition}
The subtheory $\R'$ is essentially the image of the surjection $\Pi$.
The point of constructing a resource fragment with such a surjective map would be to achieve a more convenient set of free states or operations, or importantly a more convenient pre-order.

\begin{figure}
    \centering
    \includegraphics[height=3cm]{sections/major/fragments.pdf}
    \caption{Fragments \nick{Split into subfigures}
    }
    \label{fig:fragments}
\end{figure}

Any monotone is a trivial example of a resource fragment in the sense of the following~\cref{thm:monofrag}.
\begin{proposition}\label{thm:monofrag}
	Any monotone $\cal{M}$ of a resource theory $\R$ is a resource projection that maps the set of free states to $0$ and the pre-order $\prec_\R$ to a total order.
\end{proposition}
\begin{proof}
	Trivial.
\end{proof}
Mapping free states to real numbers and free operations to simple addition, the two conditions in the definition are equivalent to monotonicity and additivity respectively.
The ``free state'' for real numbers is 0 and all free states of the resource theory are mapped onto it.

The most general magic theory, the theory of Wigner negativity \nick{or positivity?}, can be expressed as $\R = (\F, \O)$ with
\begin{align}
    \F &= \{ \rho: \W[\bmz]{\rho} \geq 0\}\ \text{and} \\
    \O &= \{ \E: \W[\bmy|\bmx]{\E} \geq 0\}
\end{align}
for all points $\bmx, \bmy, \bmz \in \pd$.
Therefore, any free state $\sigma$ corresponds to a $d^2$-dimensional probability distribution $\W{\sigma}$ and any free operation $\E: \cal{B}(\hd) \mapsto \cal{B}(\hd)$ corresponds to a $d^2 \times d^2$ stochastic matrix (or conditional probability distribution) $\W{\E}$.
Note that these mappings are one-to-one due to the orthogonality of the phase-point operators as an operator basis.

Our goal is to give insight into magic state transformations.
We first break up the theory into fragments that allow for the incorporation of $\bmd$-majorization in its framework.
\begin{definition}\label{def:sigmafrag}
    A subtheory $\R'$ of the Wigner negativity theory $\R = (\F, \O)$ is called a \emph{$\sigma$-fragment} iff $\R' = (\F, \O_\sigma)$, where the free operations are restricted to the ones that preserve $\sigma$,
    \begin{equation}
        \O_\sigma \coloneqq \{ \E \in \O: \E(\sigma) = \sigma \}.
    \end{equation}
\end{definition}

State $\sigma$ is thus a fixed point of all operations in $\O_\sigma$ and we provide the following theorem which characterises the $\sigma$-fragments as well as how they make up the whole set of free operations. \nick{move below}

\subsection{Majorization}\label{sec:major}

Majorization is a fundamental tool that has recently found many applications in quantum information theory \nick{CITE}.
It describes the \nick{disorder / non-uniformity} of vectors via stochastic transformations that are possible between them.

In order to discuss such stochastic transformations, we first denote by $\stoch$ the set of $(d \times d)$ stochastic matrices that preserve vector $\bmg$.
Specifically, any $S \in \stoch$ satisfies:
\begin{enumerate}
    \item $S_{ij} \geq 0$ for all $i, j \in \zd$;
    \item $\sum\limits_{j=1}^n S_{ij} = 1$ for all $i \in \zd$;
    \item $S\bmg = \bmg$.
\end{enumerate}
It forms a group under matrix multiplication because it contains the identity and $S^{-1} \in \stoch$ for any $S \in \stoch$.

We can motivate majorization very well for our purposes via its application on quantum thermodynamics in the absence of coherence.
At any given temperature $\beta$, the thermal state $\gamma_\beta$ is intuitively the most ordered state. 
Thermal operations are defined as operations that cannot extract energy from the Gibbs state, $\E(\gamma_\beta) = \gamma_\beta$.
Convertibility between states via thermal operations is equivalent to a stochasticity condition on the energy level populations of the states \nick{CITE}.
Roughly, the statement is that there exists a thermal operation $\E$ such that $\tau = \E(\rho)$ if and only if there exists a a matrix $S \in \stoch[\bmg]$ such that $\bm{q} = S\bm{p}$, where $\bm{q}, \bm{p}$ and $\bmg$ and the energy level population vectors of $\tau, \rho, \gamma_\beta$ respectively. \nick{expand or remove}

We can define majorization based on this definition.
\begin{definition}\label{def:dmajor}
    Given $\bmx, \bmy, \bmg \in \reals^d$, such that the components of $\bmg$ are positive, $\bmy$ is said to $\bmg$-majorize $\bmx$, iff there exists a matrix $S \in \stoch$ such that $\bmx = S\bmy$.

    We denote this partial order by $\bmx \prec_{\bmg} \bmy$.
\end{definition}
If $\bmg = \frac{1}{d}\bm{1}$, the $d$-dimensional uniform distribution, then $\stoch$ is the set of bistochastic matrices and we retrieve the familiar notion of majorization in entanglement theory. \nick{CITE}

A visual representation of $\bmg$-majorization is provided by the Lorenz curve of a vector $\bmz \in \reals^d$.
Let the vector $\bmz^\downarrow$ denote $\bmz$, but with its components arranged in non-increasing order.
\begin{definition}
    Let $\bmz \in \reals^n$.
    Let $\bmg \in \reals^d$ be a vector with positive components, $\pi$ a permutation mapping $(z_i/g_i) \mapsto (z_i/g_i)^\downarrow$ for all $i=1,\dots,d$ and $D = \sum_{i=1}^d g_i$.
    The Lorenz curve $L(\bmz|\bmg)$ of vector $\bmz$ is the piecewise linear curve obtained by joining the points 
\begin{equation}\label{eq:lorenz}
    \left\{ L_k(\bmz|\bmg) \coloneqq \left( \frac{1}{D}\sum_{i=1}^k g_{\pi(i)}, \sum_{i=1}^k z_{\pi(i)} \right) \in \mathbb{R}^2: k = 1,\dots,d \right\}.
\end{equation}
\end{definition}
\emph{Remark 1.} The origin $L_0(\bmz|\bmg) \coloneqq (0,0)$ is usually included in the curve.

\emph{Remark 2.} The first components of $L_k(\bmz|\bmg)$ are rescaled by $D$ so that comparison of curves with unequal dimensions is possible.
In fact, the Lorenz curves $L(\bmz|\bmg)$ and $L(\bmz \otimes \bmg|\bmg \otimes \bmg)$, where $\otimes$ denotes the Kronecker product, are identical.

\emph{Remark 3.} Lorenz curves are always concave.

\emph{Remark 4.} If $L_d(\bmz|\bmg) = 1$ and for all $k$, $L_k(\bmz|\bmg) \leq 1$, then $\bmz$ is a probability distribution.
Lorenz curves of quasi-probability distributions in principle reach above 1.

An example of comparison between different Lorenz curves is illustrated in~\cref{fig:lctoy}.
\begin{figure}
    \centering
    \includegraphics[height=5cm]{sections/major/lctoy.pdf}
    \caption{Example of different Lorenz curves for quasi-probability vectors under $\bmg$-majorization.
    Vectors $\bmy$ and $\bmg$ are simply probability distributions.
    The curve corresponding to vector $\bmg$ is always the straight line connecting $(0,0)$ and $(1,1)$, so that any other Lorenz curve lies above it, for example $\bmx \prec_{\bmg} \bmg$.
    Curves $L_k(\bmx|\bmg)$ and $L_k(\bmy|\bmg)$ intersect, so neither $\bmx \prec_{\bmg} \bmy$ nor $\bmy \prec_{\bmg} \bmx$.
    }
    \label{fig:lctoy}
\end{figure}

We now present the important majorization result needed in our analysis of magic.
\begin{theorem}\label{thm:dmajor}
Given $\bmx, \bmy, \bmg \in \reals^d$, such that the components of $\bmg$ are positive, the following statements are equivalent:
 \begin{enumerate}%[label=\enlabel{TM}{\arabic*}]
	\item\label{en:tm1} $\bmx \prec_{\bmg} \bmy$;
	\item\label{en:tm5} $L_k(\bmx|\bmg) \leq L_k(\bmy|\bmg)$ for all $k=1,2,\dots, d-1$ and $L_d(\bmx|\bmg) = L_d(\bmy|\bmg)$.
 \end{enumerate}
\end{theorem}
A restatement of the theorem including more equivalent conditions, along with a proof is provided in the \nick{appendix}.

\subsection{Magic fragments}\label{sec:magfrag}

\begin{theorem}\label{thm:frag}
    In the resource theory of Wigner negativity $\R = (\O, \F)$, the following statements hold:
    \begin{enumerate}
        \item The $\sigma$-fragment $\O_\sigma$ is equal to the set of all $\cptp$ operations with stochastic Wigner distributions that leave $\W{\sigma}$ invariant. \nick{Assuming maximal resource theory}
        \item Every free operation leaves at least one free state invariant such that $\O = \bigcup\limits_{\sigma \in \F} \O_\sigma$.
        \item If a free operation leaves two states invariant, then it also leaves every mixture of them invariant, $\O_{\sigma} \cap \O_{\sigma'} \subseteq \O_{p\sigma + (1-p)\sigma'}$ for all $p \in [0,1]$.
    \end{enumerate}
\end{theorem}
\begin{proof}
    \begin{enumerate}
    \item Let $\O_\sigma' \coloneqq \{ \E \in \cptp: \W{\E} \in \stochw \}$ be the described set of operations.

    Suppose $\E$ is in $\O_\sigma$, then $\E \in \cptp$ and $\W{\E} \in \stochw$ due to property~\ref{en:wo4} of~\cref{thm:wchannel}, hence $\O_\sigma \subseteq \O_\sigma'$.

    Conversely, suppose $\E \in \cptp$ with $\W{\E} \in \stochw$. 
    Then, $\W[\bmy|\bmx]{\E} \geq 0$ for all $\bmx, \bmy$, hence $\E \in \O$.
    Furthermore, $\W{\E} \W{\sigma} = \W{\sigma}$ implies $\E(\sigma) = \sigma$ using~\cref{eq:woperation} defined for any $\cptp$ operation $\E$.
    Hence, $\O_\sigma' \subseteq \O_\sigma$.

    \item Suppose $\E$ is in $\O_\sigma$, then it is also in $\O$, hence $\bigcup\limits_{\sigma \in \F} \O_\sigma \subseteq \O$.

    Conversely, suppose $\E$ is in $\O$. 
    The free states are mapped one-to-one to a subset $\cal{S}$ of the $(d^2 - 1)$-dimensional probability simplex.
    $\cal{S}$ is convex, since any combination of free states is also free and the Wigner distribution is linear.
    Therefore, $\cal{S}$ is convex and compact as a convex subset of the bounded compact probability simplex.
    Then, $\W{\E}{}$ is a stochastic, thus continuous, mapping from $\cal{S}$ to itself and Brouwer's fixed point theorem \nick{CITE} implies that there exists a probability distribution $g_{\bmz}, \bmz \in \pd$ that is preserved by $\W{\E}{}$.
    This corresponds one-to-one to a state $\sigma \coloneqq \sum_{\bmz \in \pd} g_{\bmz} A_{\bmz}$ and so $\O \subseteq \bigcup\limits_{\sigma \in \F} \O_\sigma$.

    \item Let $\E \in \O_{\sigma} \cap \O_{\sigma'}$.
    Then $\E \in \cptp$ and corresponds to stochastic Wigner distribution $\W{\E}$ such that $\W{\E} \W{\sigma} = \W{\sigma}$ and $\W{\E} \W{\sigma'} = \W{\sigma'}$.
    Then, $\W{\E} \W{p\sigma + (1-p)\sigma'} = \W{p\sigma + (1-p)\sigma'}$ for any $p \in [0,1]$ due to the additive property~\ref{en:w4} of the Wigner distribution, implying that state $p\sigma + (1-p)\sigma'$ is also left invariant by $\E$.
    \end{enumerate}
\end{proof}

The structure of the $\sigma$-fragment $(\F, \O_\sigma)$ for any $d$-dimensional $\sigma$ in $\F$ admits the pre-order of $\bmg$-majorization with $\bmg = \W{\sigma}$, a $d^2$-dimensional probability vector. 
If any component of $\W{\sigma}$ is zero, then we can always add some $\epsilon$ amount of unital noise by mixing $\sigma$ with the maximally mixed state $\frac{1}{d}\id$. 
This ensures that all components are strictly positive and $\bmd$-majorization can be used.

\begin{proposition}
    A state conversion $\rho \xrightarrow{\E \in \O} \tau$ is possible only if there exists a free state $\sigma$ such that for \nick{an infinitesimal $\epsilon$}, $\W{\tau} \prec_{\W{\sigma'}} \W{\rho}$, where $\sigma' = (1-\epsilon)\sigma + \epsilon \frac{1}{d}\id$.
\end{proposition}

\emph{Remark 1.} Note that free states $\F$ map onto a \emph{strict subset} of the set of probability distributions.
As a counterexample, consider the 9-dimensional probability distribution with non-zero components $\left(\frac{1}{2}, \frac{1}{4}, \frac{1}{4} \right)$. 
It does not correspond to any qutrit Wigner distribution because the component with value $\frac{1}{2}$ does not satisfy the boundedness condition~\ref{en:w3} of~\cref{thm:wstate}.

\emph{Remark 2.} Similarly, any $\O_\sigma$ may be mapped onto a \emph{strict subset} of the set $\stochw$ of stochastic matrices that preserve $\W{\sigma}{}$.

As an example, consider the permutation matrix
\begin{equation}
    \Pi_X = \begin{psmallmatrix}
        0 & 1 & 0 & 0 & 0 \\
        0 & 0 & 0 & 0 & 1 \\
        0 & 0 & 0 & 1 & 0 \\
        1 & 0 & 0 & 0 & 0 \\
        0 & 0 & 1 & 0 & 0
    \end{psmallmatrix} \otimes \begin{psmallmatrix}
        0 & 0 & 1 & 0 & 0 \\
        0 & 0 & 0 & 0 & 1 \\
        0 & 0 & 0 & 1 & 0 \\
        1 & 0 & 0 & 0 & 0 \\
        0 & 1 & 0 & 0 & 0    
    \end{psmallmatrix} \in \stochw,\ d=5.
\end{equation}
It preserves the uniform distribution $\W{\frac{1}{5}\id}{}$, but it does not correspond to any completely positive operation and therefore to any $\E \in \O$, due to~\cref{thm:frag}.

\emph{Remark 3.} No $\sigma$-fragment is empty.
In fact, an example of a stabilizer operation $\E \in \so \cap \O_\sigma$, for any $\sigma$-fragment, is the completely depolarising \nick{replacement} map
\begin{align}
    \E(\rho) &= \sigma \tr[\rho],\ \text{with} \\
    \W[\bmy|\bmx]{\E} &= \W[\bmy]{\sigma} \tr[\rho],
\end{align}
which can be thought as a sequence of tracing out state $\rho$ and preparing the stabilizer $\sigma$.

The zoo of all the operation classes is summarised in ~\cref{fig:zoo}.
Completely positive-Wigner-preserving operations ($\cpwp$) form the largest operation class in the literature.
Therefore, $\sigma$-fragments cover this theory of magic exactly and any magic subtheory is contained within this cover.
For example, the stabilizer-preserving ($\spo$)~\cite{cit:ahmadi} and completely stabilizer-preserving ($\cspo$)~\cite{cit:seddon} operation subclasses follow the hierarchy $\so \subset \cspo \subset \spo \subset \cpwp$ and therefore are described by our $\sigma$-fragments.

\begin{figure}
    \centering
        \includegraphics[scale=0.5]{sections/major/operations.pdf}
    \caption{Zoo of allowed operations for magic resource theories.
    Established theories involve operations within the yellow regions, following the hierarchy $\so \subset \cspo \subset \spo \subset \cpwp$.
    We introduce fragments $\O_\sigma \subset \stochw,\ \sigma \in \F$ that cover $\cpwp$ with each one extending to a set of stochastic maps that allows for $\bmd$-majorization to be used.
    \nick{fragments are the intersections of blue and orange, not the whole bubble - technically $\stochw$ should be replaced by its operational pre-image.}
    }
    \label{fig:zoo}
\end{figure}

### 2020-06-03 sections/major/major.tex
added couple of comments / minor changes + fixed operations fig

@@
 Then, we define a fragment as follows.
-\begin{definition}\label{def:fragment}
+\begin{definition}[\textbf{Resource projection}]\label{def:fragment}
     Let a resource theory $\R = (\F, \O)$ have pre-order $\prec_{\R}$ and operational composition rule $\circ_{\R}$. 
@@
     \end{enumerate}
+    We call $\Pi$ a resource projection.
 \end{definition}
@@
 We first break up the theory into fragments that allow for the incorporation of $\bmd$-majorization in its framework.
-\begin{definition}\label{def:sigmafrag}
+\begin{definition}[\textbf{$\boldsymbol\sigma$-fragment}]\label{def:sigmafrag}
     A subtheory $\R'$ of the Wigner negativity theory $\R = (\F, \O)$ is called a \emph{$\sigma$-fragment} iff $\R' = (\F, \O_\sigma)$, where the free operations are restricted to the ones that preserve $\sigma$,
@@
     $\cal{S}$ is convex, since any combination of free states is also free and the Wigner distribution is linear.
-    Therefore, $\cal{S}$ is convex and compact as a convex subset of the bounded compact probability simplex.
+    Therefore, $\cal{S}$ is convex and compact as a convex subset of the bounded compact probability simplex. \nick{Need to prove that $\cal{S}$ is closed.}
     Then, $\W{\E}{}$ is a stochastic, thus continuous, mapping from $\cal{S}$ to itself and Brouwer's fixed point theorem \nick{CITE} implies that there exists a probability distribution $g_{\bmz}, \bmz \in \pd$ that is preserved by $\W{\E}{}$.

### 2020-06-04 sections/major/major.tex
Proof of 'monotone is a fragment'

@@
 A monotone is a projection from the $d$-dimensional set of density states of the theory to the real line. 
-It is monotonically decreasing under free operations, reflecting the no resource generating property of free operations and thus respecting the pre-order $\prec$ of the theory.
+It is monotonically decreasing under free operations, 
+\begin{equation}\label{eq:monotonicity}
+    \cal{M}(\rho_1) \leq \cal{M}(\rho_2)\ \text{if}\ \rho_1 \prec_{\R} \rho_2,
+\end{equation}
+reflecting the no resource generating property of free operations and thus respecting the pre-order $\prec$ of the theory.
 A popular magic monotone is the \emph{mana} of a state \nick{CITE}, defined as
@@
 \begin{proof}
-	Trivial.
+	Consider a monotone $\cal{M}$ in the context of a general resource theory $\R = (\F, \O)$.
+	Let $\R' = (\F', \O')$, where $\F' \equiv \mathbb{R}_{\geq 0}$ is the set of non-negative real numbers and $\O'$ is the set of non-increasing real functions mapping $\mathbb{R}_{\geq 0}$ to $\mathbb{R}_{\geq 0}$.
+	Naturally, we also set $\prec_{\R'}$ as the usual total order $\leq$ and $\circ_{\R'}$ as the usual function composition.
+
+	The defining property of a monotone, given in~\cref{eq:monotonicity} ensures condition 1 of~\cref{def:fragment}.
+
+	We can then project any $\E \in \O$ onto a function $f \in \O'$, so that $f$ maps $\cal{M}(\rho)$ onto $\cal{M}(\E(\rho))$ for all states $\rho$.
+
+	\nick{expand}
 \end{proof}
@@
 \begin{proposition}
-    A state conversion $\rho \xrightarrow{\E \in \O} \tau$ is possible only if there exists a free state $\sigma$ such that for \nick{an infinitesimal $\epsilon$}, $\W{\tau} \prec_{\W{\sigma'}} \W{\rho}$, where $\sigma' = (1-\epsilon)\sigma + \epsilon \frac{1}{d}\id$.
+    Let $\R = (\O, \F)$ be a theory of magic.
+    If the state conversion $\rho \xrightarrow{\O} \tau$ is possible, then there exists a full-rank free state $\sigma \in \F$ such that $\W{\tau} \prec_{\W{\sigma}} \W{\rho}$.
 \end{proposition}
+\begin{proof}
+    Suppose there exists $\E \in \O$ such that $\E(\rho) = \tau$.
+    The free operation belongs to a $\sigma$-fragment, $\E \in \O_\sigma$, for some $\sigma \in \F$.
+    Then, $\W{\E}\W{\rho} = \W{\tau}$ with $\W{\E} \in \stochw$, or, equivalently, $\W{\tau} \prec_{\W{\sigma}} \W{\rho}$.
+\end{proof}
+\nick{This proposition needs modification. What about $\E(\rho) = \ketbra{0}$?}
 
@@
 
-\begin{figure}
+\begin{figure}[b]
     \centering
-        \includegraphics[scale=0.5]{sections/major/operations.pdf}
+        \includegraphics[scale=0.45]{sections/major/operations.pdf}
     \caption{Zoo of allowed operations for magic resource theories.

### 2020-06-08 sections/magic/magic.tex
Reshuffling section IV

@@
 \end{center}
-Magic monotones are often used \nick{CITE} to partially address this question, although such approaches do not exploit much of the structure of the theory.
-Therefore, we introduce a generalised notion of a measure, the \emph{fragment}, applicable in general resource theories and in particular in all theories of magic we consider. \nick{expand}
 
-We are interested in all resource theories of magic $\R = (\F, \O)$ that obey two assumptions:
+We are interested in all resource theories of magic $\R = (\F, \O)$ in which free operations cannot generate any amount of resource. 
+The structure of such theory is described by a pre-order, often called partial order \nick{CITE}, $\prec_{\R}$ between states.
+We write $\rho' \prec_{\R} \rho$ iff there exists $\E \in \O$ such that $\E(\rho) = \rho'$.
+Naturally, states may be incomparable under the given theory, meaning that there exists no free operation that converts one to the other.
+
+Formally, the no resource generation condition on the theories translates into two assumptions:
 \begin{enumerate}[I]
@@
 
-The main result of this paper is that any magic theory $\R$ satisfying the above assumptions can be recast as a subtheory of stochasticity.
-This reformulation grants additional power to the theory as the structure of stochastic process can be exploited to add insight to the main questions of theories as stated above. \nick{expand}
+Monotones are often used \nick{CITE} to address the question of state convertibility, although such approaches are usually generic.
+A monotone of any general resource theory is a projection of the theory onto the non-negative real numbers, collapsing the pre-order of the theory to the total order defined on the real line.
+This is the \nick{most naive} non-trivial projection under which the images of incomparable states can be compared.
+Our first contribution is the introduction of a generalised notion of \emph{resource projection} which maps a general resource theory onto a subtheory which in principle still retains a partial structure.
+Applying this notion on existing magic theories highlights the hidden stochasticity that governs magic state conversions.
+We show that a magic theory can be subdivided into \emph{fragments} \nick{expand}
 
@@
 Therefore, stabilizer-preserving theories have been extended to a theory that preserves state ``Wigner positivity''~\cite{cit:wang}, formally defined in~\cref{sec:wigner} for odd prime dimensions.
-Informally, it can be considered as the maximal theory of magic $\R_{\rm{max}} = (\F_{\rm{max}}, \O_{\rm{max}})$, where free states have non-negative Wigner distributions and free operations completely preserve this property.
+Informally, it can be considered as the maximal theory of magic $\Rmax = (\Fmax, \Omax)$, where free states have non-negative Wigner distributions and free operations completely preserve this property.

### 2020-06-08 sections/magic/phasespace.tex
Reshuffling section IV

@@
 \end{equation}
-It is in fact a bounded $d^2$-dimensional quasi-probability distribution over $\pd$ as shown in~\cref{app:wigner}.
+It is in fact a real, bounded, $d^2$-dimensional quasi-probability distribution over $\pd$ as shown in~\cref{app:wigner}.
 
@@
 
-The particular form of~\cref{eq:woperation} was chosen so that Wigner distributions of operations act as transition matrices for Wigner distribution of states, $\W{\E(\rho)} = \W{\E}\W{\rho}$.
-In particular, $\cptp$ operations that map a Hilbert space to itself and have non-negative Wigner distributions correspond to stochastic matrices.
-All these properties are shown in~\cref{app:wigner}
+The specific form of~\cref{eq:woperation} is chosen so that Wigner distributions of operations act as transition matrices for Wigner distributions of states, $\W{\E(\rho)} = \W{\E}\W{\rho}$.
+In particular, $\cptp$ operations that map between density operators of equal dimensions and have non-negative Wigner distributions correspond to stochastic matrices, as shown in~\cref{app:wigner}
 
@@
 \end{align}
-
-Equipped with the definitions of the Wigner distribution, we can formally define the Wigner positivity theory $\R_{\rm{max}}$ in odd prime dimensions.
-The free states are all states with non-negative Wigner distributions 
-\begin{equation}
-    \F_{\rm{max}} \coloneqq \{ \rho: \W[\bmz]{\rho} \geq 0 \text{ for all } \bmz \in \pd\}
-\end{equation}
-The free operations should send the set of free states $\F_{\rm{max}}$ into itself and completely preserve the non-negativity of the states, in the sense that $\E \in \O_{\rm{max}}$ iff $(\id_d \otimes \E ) \sigma \in \stab$ for all odd prime dimensions $d$ whenever $\sigma \in \F_{\rm{max}}$.
-
-It is shown by Wang \textit{et al.}~\cite{cit:wang} that $\O_{\rm{max}}$ coincides with the set of operations $\E$ with a non-negative Wigner distributions, 
-\begin{equation}
-    \O_{\rm{max}} = \{ \E: \W[\bmy|\bmx]{\E} \geq 0 \text{ for all } \bmx, \bmy \in \pd\}.
-\end{equation}

### 2020-06-08 sections/major/major.tex
Reshuffling section IV

@@
 
-\subsection{Fragments}\label{sec:frag}
+\subsection{Magic fragments}\label{sec:magfrag}
 
+Equipped with the definitions of the Wigner distribution in odd prime dimensions, we can formally recast the maximal magic theory $\Rmax$ into a stochasticity setting.
+The free states correspond to proper probability distributions 
+\begin{equation}
+    \Fmax \coloneqq \{ \rho: \W[\bmz]{\rho} \geq 0 \text{ for all } \bmz \in \pd\}
+\end{equation}
+
+The free operations should send the set of free states $\Fmax$ into itself and completely preserve the non-negativity of the states, in the sense that $\E \in \Omax$ iff $(\id_d \otimes \E ) \sigma \in \stab$ for all odd prime dimensions $d$ whenever $\sigma \in \Fmax$.
+It is shown by Wang \textit{et al.}~\cite{cit:wang} that $\Omax$ coincides with the set of operations $\E$ that correspond to stochastic Wigner distributions, 
+\begin{equation}
+    \Omax = \{ \E: \W[\bmy|\bmx]{\E} \geq 0 \text{ for all } \bmx, \bmy \in \pd\}.
+\end{equation}
+
+Any magic theory $\R = (\F, \O)$ is a subtheory of $\Rmax$ as explained in~\cref{sec:intro}, and as such it falls under this new stochasticity setting. \nick{expand}
+
+\begin{definition}[\textbf{$\boldsymbol\sigma$-fragment}]\label{def:sigmafrag}
+    A subtheory $\R'$ of the Wigner negativity theory $\R = (\F, \O)$ is called a \emph{$\sigma$-fragment} iff $\R' = (\F, \O_\sigma)$, where the free operations are restricted to the ones that preserve $\sigma$,
+    \begin{equation}
+        \O_\sigma \coloneqq \{ \E \in \O: \E(\sigma) = \sigma \}.
+    \end{equation}
+\end{definition}
+
+State $\sigma$ is thus a fixed point of all operations in $\O_\sigma$. 
+This is an observation arising from the stochastic nature of free operations. 
+We now show that every free operation has a fixed point, so that the theory $\R$ can be entirely subdivided into $\sigma$-fragments.
+
+\begin{theorem}
+    Let $\R = (\F, \O)$ be a theory of magic.
+    Every free operation leaves at least one free state invariant such that $\O = \bigcup\limits_{\sigma \in \F} \O_\sigma$.
+\end{theorem}
+\begin{proof}
+    Suppose $\E$ is in $\O_\sigma$, then it is also in $\O$, hence $\bigcup\limits_{\sigma \in \F} \O_\sigma \subseteq \O$.
+
+    Conversely, suppose $\E$ is in $\O$. 
+    The free states are mapped one-to-one to a subset $\cal{S}$ of the $(d^2 - 1)$-dimensional probability simplex.
+    $\cal{S}$ is convex, since any combination of free states is also free and the Wigner distribution is linear.
+    Therefore, $\cal{S}$ is convex and compact as a convex subset of the bounded compact probability simplex. \nick{Need to prove that $\cal{S}$ is closed.}
+    Then, $\W{\E}{}$ is a stochastic, thus continuous, mapping from $\cal{S}$ to itself and Brouwer's fixed point theorem \nick{CITE} implies that there exists a probability distribution $g_{\bmz}, \bmz \in \pd$ that is preserved by $\W{\E}{}$.
+    This corresponds one-to-one to a state $\sigma \coloneqq \sum_{\bmz \in \pd} g_{\bmz} A_{\bmz}$ and so $\O \subseteq \bigcup\limits_{\sigma \in \F} \O_\sigma$.
+\end{proof}
+
+The subdivision of magic theories into $\sigma$-fragments is powerful because the pre-order $\prec_{\R'}$ of every $\sigma$-fragment is described by well-behaved majorization tools, as we establish in~\cref{sec:major}.
+\nick{expand}
+
+\subsection{Majorization}\label{sec:major}
+
+Majorization is a powerful tool that has recently found many applications in quantum information theory \nick{CITE}.
+It can describes the \nick{disorder / non-uniformity} of distributions that undergo stochastic transformations.
+
+To formally state majorization results, we first denote by $\stoch$ the set of $(d \times d)$ stochastic matrices that preserve the probability vector $\bmd$.
+\nick{Should we introduce notation directly in the magic setting?}
+Specifically, for any $S \in \stoch$, all matrix elements are non-negative, all rows sum to $1$ and $S\bmd = \bmd$.
+\iffalse
+\begin{enumerate}
+    \item $S_{ij} \geq 0$ for all $i, j \in \zd$;
+    \item $\sum\limits_{j=1}^n S_{ij} = 1$ for all $i \in \zd$;
+    \item $S\bmd = \bmd$.
+\end{enumerate}
+\fi
+The set $\stoch$ forms a group under matrix multiplication for all $\bmd$ with positive components.
+
+Majorization finds an important application on quantum thermodynamics in the absence of coherence.
+The use of majorization in this setting provides useful intuition for our purposes.
+At any given temperature $\beta$, the thermal state $\gamma_\beta$ is thermodynamically the most ordered state. 
+Thermal operations are defined as operations that cannot extract energy from the Gibbs state, $\E(\gamma_\beta) = \gamma_\beta$.
+Convertibility between states via thermal operations is equivalent to a stochasticity condition on the energy level populations of the states \nick{CITE}.
+Roughly, the statement is that there exists a thermal operation $\E$ such that $\tau = \E(\rho)$ if and only if there exists a a matrix $S \in \stoch$ such that $\bm{q} = S\bm{p}$, where $\bm{q}, \bm{p}$ and $\bmd$ and the energy level population vectors of $\tau, \rho, \gamma_\beta$ respectively.
+
+Drawing intuition from this setting, we can define majorization as follows.
+\begin{definition}[\textbf{$\boldsymbol\bmd$-majorization}]\label{def:dmajor}
+    Given $\bmx, \bmy, \bmd \in \reals^d$, such that the components of $\bmd$ are positive, $\bmy$ is said to $\bmd$-majorize $\bmx$, iff there exists a matrix $S \in \stoch$ such that $\bmx = S\bmy$.
+\end{definition}
+We denote this pre-order by $\bmx \prec_{\bmd} \bmy$.
+If $\bmd = \frac{1}{d}\bm{1}$, the $d$-dimensional uniform distribution, then $\stoch$ is the set of doubly stochastic matrices and we retrieve the familiar notion of majorization in entanglement theory.
+\nick{CITE}
+
+\nick{We need to address the non-full-rankness of states.\\
+For example, the operation $\E(\rho) = \ketbra{0}$ corresponds to no $\sigma$-fragment because components of $\W{\sigma}$ are zero.\\
+In such a case we can always add some $\epsilon$ amount of unital noise by mixing $\sigma$ with the maximally mixed state $\frac{1}{d}\id$. 
+This ensures that all components are strictly positive and $\bmd$-majorization can be used.
+There are non-full-rank states with no zeros in W.}
+
+The pre-order $\prec_{\R'}$ of the $\sigma$-fragment $\R' = (\F, \O_\sigma)$ between $d$-dimensional states corresponds to the majorization pre-order $\prec_{\W{\sigma}}$ between their $d^2$-dimensional Wigner distributions.
+
+\begin{theorem}
+    Let $\R = (\O, \F)$ be a theory of magic.
+    Suppose the state conversion $\rho \xrightarrow{\E \in \O} \tau$ is possible. 
+    Then, there exists a full-rank free state $\sigma \in \F$ such that  $\W{\tau} \prec_{\W{\sigma}} \W{\rho}$.
+\end{theorem}
+\begin{proof}
+    Suppose there exists $\E \in \O$ such that $\E(\rho) = \tau$.
+    The free operation belongs to a $\sigma$-fragment, $\E \in \O_\sigma$, for some $\sigma \in \F$.
+    Then, $\W{\E}\W{\rho} = \W{\tau}$ with $\W{\E} \in \stochw$, or, equivalently, $\W{\tau} \prec_{\W{\sigma}} \W{\rho}$.
+\end{proof}
+
+A visual representation of $\bmd$-majorization is provided by Lorenz curves.
+Let the vector $\bmz^\downarrow$ denote a component permutation of vector $\bmz \in \reals^d$, so that its components are arranged in non-increasing order.
+\begin{definition}[\textbf{Lorenz curve}]
+    Let $\bmz \in \reals^d$.
+    Let $\bmd \in \reals^d$ be a vector with positive components, $\pi$ a permutation mapping $(z_i/d_i) \mapsto (z_i/d_i)^\downarrow$ for all $i=1,\dots,d$ and $D = \sum_{i=1}^d d_i$.
+    The Lorenz curve $L(\bmz|\bmd)$ of vector $\bmz$ is the piecewise linear curve obtained by joining the points $\{ (x_k, L_k(\bmz|\bmd)) \}_{k=1,\dots,d}$, where
+    \begin{equation}\label{eq:lorenz}
+        (x_k, L_k(\bmz|\bmd)) \coloneqq \left( \frac{1}{D}\sum_{i=1}^k d_{\pi(i)}, \sum_{i=1}^k z_{\pi(i)} \right) \in \mathbb{R}^2.
+    \end{equation}
+\end{definition}
+\emph{Remark 1.} The origin $(x_0, L_0(\bmz|\bmd)) \coloneqq (0,0)$ is usually included in the curve.
+
+\emph{Remark 2.} Components $x_k$ are rescaled by $D$ so that comparison of curves with unequal dimensions is possible.
+In fact, the Lorenz curves $L(\bmz|\bmd)$ and $L(\bmz \otimes \bmd|\bmd \otimes \bmd)$, where $\otimes$ denotes the Kronecker product, are identical.
+
+\emph{Remark 3.} Lorenz curves are always concave.
+
+\emph{Remark 4.} If $L_d(\bmz|\bmd) = 1$ and for all $k$, $L_k(\bmz|\bmd) \leq 1$, then $\bmz$ is a probability distribution.
+Lorenz curves of quasi-probability distributions in principle reach above 1.
+
+A vector $\bmy$ $\bmd$-majorizes another vector $\bmx$  if and only if Lorenz curve $L(\bmy|\bmd)$ lies above Lorenz curve $L(\bmx|\bmd)$.
+\begin{theorem}\label{thm:dmajor}
+    Let $\bmx, \bmy, \bmd \in \reals^d$, such that the components of $\bmd$ are positive. 
+    Then, $\bmx \prec_{\bmd} \bmy$ if and only if $L_k(\bmx|\bmd) \leq L_k(\bmy|\bmd)$ for all $k=1,2,\dots, d-1$ and $L_d(\bmx|\bmd) = L_d(\bmy|\bmd)$.
+\end{theorem}
+A restatement of the theorem including more equivalent conditions, along with a proof is provided in the \nick{appendix}.
+
+An example of comparison between different Lorenz curves is illustrated in~\cref{fig:lctoy}.
+\begin{figure}
+    \centering
+    \includegraphics[height=5cm]{sections/major/lctoy.pdf}
+    \caption{Example of different Lorenz curves for quasi-probability vectors under $\bmd$-majorization.
+    Vectors $\bmy$ and $\bmd$ are simply probability distributions.
+    The curve corresponding to vector $\bmd$ is always the line segment connecting $(0,0)$ and $(1,1)$, so that any other Lorenz curve lies above it, for example $\bmx \prec_{\bmd} \bmd$.
+    Curves $L_k(\bmx|\bmd)$ and $L_k(\bmy|\bmd)$ intersect, so neither $\bmx \prec_{\bmd} \bmy$ nor $\bmy \prec_{\bmd} \bmx$.
+    \nick{Recast in terms of magic}
+    }
+    \label{fig:lctoy}
+\end{figure}
+
+\subsection{General resource fragments}\label{sec:frag}
+
+Subdividing magic into $\sigma$-fragments
 Magic is commonly quantified via monotones \nick{CITE}. 
@@
 \nick{explain exactly why fragments $>$ monotones}
-Let $\R' = (\F', \O')$ be a subtheory of $\R$ so that $\F' \subseteq \F$ and $\O' \subseteq \O$. 
-Then, we define a fragment as follows.
-\begin{definition}[\textbf{Resource projection}]\label{def:fragment}
-    Let a resource theory $\R = (\F, \O)$ have pre-order $\prec_{\R}$ and operational composition rule $\circ_{\R}$. 
-    We call a resource fragment of $\R$ any theory $\R' = (\F', \O')$ with pre-order $\prec_{\R'}$ and operational composition rule $\circ_{\R'}$, if there exists a surjective projection $\Pi \equiv (\Pis, \Pio): \R \mapsto \R'$ that satisfies the following two conditions.
-    \begin{enumerate}
-        \item $\Pis: \F \mapsto \F'$ and $\Pis(\rho_1) \prec_{\R'} \Pis(\rho_2)$ whenever $\rho_1 \prec_{\R} \rho_2$ for any states $\rho_1, \rho_2 \in \F$;
-        \item $\Pio: \O \mapsto \O'$ and $\Pio(\E_1) \circ_{\R'} \Pio(\E_2) = \Pio(\E_1 \circ_{\R} \E_2)$ for any free operations $\E_1, \E_2 \in \O$. 
-    \end{enumerate}
-    We call $\Pi$ a resource projection.
-\end{definition}
-The subtheory $\R'$ is essentially the image of the surjection $\Pi$.
-The point of constructing a resource fragment with such a surjective map would be to achieve a more convenient set of free states or operations, or importantly a more convenient pre-order.
 
@@
 
-Any monotone is a trivial example of a resource fragment in the sense of the following~\cref{thm:monofrag}.
+Let $\R' = (\F', \O')$ be a subtheory of $\R$ so that $\F' \subseteq \F$ and $\O' \subseteq \O$. 
+Then, we define a fragment as follows.
+\begin{definition}[\textbf{Resource projection}]\label{def:fragment}
+    Let a resource theory $\R = (\F, \O)$ have pre-order $\prec_{\R}$ and operational composition rule $\circ_{\R}$. 
+    We call a resource fragment of $\R$ any theory $\R' = (\F', \O')$ with pre-order $\prec_{\R'}$ and operational composition rule $\circ_{\R'}$, if there exists a surjective projection $\Pi \equiv (\Pis, \Pio): \R \mapsto \R'$ that satisfies the following two conditions.
+    \begin{enumerate}
+        \item $\Pis: \F \mapsto \F'$ \nick{actually it maps all states, not just the free ones} and $\rho_1 \prec_{\R} \rho_2$ whenever $\Pis(\rho_1) \prec_{\R'} \Pis(\rho_2)$ for any states $\rho_1, \rho_2$;
+        \item $\Pio: \O \mapsto \O'$ and $\Pio(\E_1) \circ_{\R'} \Pio(\E_2) = \Pio(\E_1 \circ_{\R} \E_2)$ for any free operations $\E_1, \E_2 \in \O$. 
+    \end{enumerate}
+    We call $\Pi$ a resource projection.
+\end{definition}
+Fragment $\R'$ is the image of the projection $\Pi$.
+Considering a resource projection is particularly useful when the structure of the fragment is more tractable.
+
+\begin{proposition}
+    Let $\R = (\F, \O)$ be a theory of magic.
+    Every $\sigma$-fragment $(\F, \O_\sigma)$ is a resource fragment of $\R$.
+\end{proposition}
+\begin{proof}
+    Let the state projection be the identity projection $\Pis:\F\mapsto\F$.
+
+    Consider the operation projection $\Pio:\O \mapsto \O_\sigma$, defined as
+    \begin{equation}
+    \Pio(\E) =
+    \begin{cases}
+        \E,\ &\sigma \in \O, \\
+        1_{\rm{C}},\ &\sigma \notin \O.
+    \end{cases}
+    \end{equation}
+    The ordered pair $(\Pis, \Pio)$ acts as the desired projection.
+\end{proof}
+
+\begin{proposition}
+    Every theory of magic $\R = (\F, \O)$ is a fragment of the maximal theory $\Rmax$.
+\end{proposition}
+\begin{proof}
+    Consider the state projection $\Pis:\Fmax \mapsto \F$, defined as
+    \begin{equation}
+    \Pis(\sigma) =
+    \begin{cases}
+        \sigma,\ &\sigma \in \F, \\
+        \frac{1}{d}\id,\ &\sigma \notin \F.
+    \end{cases}
+    \end{equation}
+    \nick{Perhaps $\Pis = $ identity}
+    Let $1_{\rm{C}}$ denote the identity channel.
+    Consider the operation projection $\Pio:\Omax \mapsto \O$, defined as
+    \begin{equation}
+    \Pio(\E) =
+    \begin{cases}
+        \E,\ &\sigma \in \O, \\
+        1_{\rm{C}},\ &\sigma \notin \O.
+    \end{cases}
+    \end{equation}
+    The orderd pair $(\Pis, \Pio)$ acts as the desired projection.
+\end{proof}
+
+Monotones reduce the structure of the theory into a real number ordering, therefore a monotone is the simplest tractable projection as formally stated in~\cref{thm:monofrag}.
 \begin{proposition}\label{thm:monofrag}
-	Any monotone $\cal{M}$ of a resource theory $\R$ is a resource projection that maps the set of free states to $0$ and the pre-order $\prec_\R$ to a total order.
+	Let $\cal{M}$ be a monotone defined in the context of a resource theory $\R$. 
+	Then $\cal{M}$ is a resource projection that  reduces the pre-order $\prec_\R$ to a total order.
 \end{proposition}
@@
 	Consider a monotone $\cal{M}$ in the context of a general resource theory $\R = (\F, \O)$.
-	Let $\R' = (\F', \O')$, where $\F' \equiv \mathbb{R}_{\geq 0}$ is the set of non-negative real numbers and $\O'$ is the set of non-increasing real functions mapping $\mathbb{R}_{\geq 0}$ to $\mathbb{R}_{\geq 0}$.
-	Naturally, we also set $\prec_{\R'}$ as the usual total order $\leq$ and $\circ_{\R'}$ as the usual function composition.
+	Let $\R' = (\F', \O')$, where $\F' \equiv \{0\}$ is the set of non-negative real numbers and $\O'$ is the set of non-increasing real functions mapping $\mathbb{R}_{\geq 0}$ to $\mathbb{R}_{\geq 0}$. 
+	Naturally, we also set $\prec_{\R'}$ as the usual total order $\leq$ and $\circ_{\R'}$ as the composition of real functions.
 
@@
 \end{proof}
-Mapping free states to real numbers and free operations to simple addition, the two conditions in the definition are equivalent to monotonicity and additivity respectively.
-The ``free state'' for real numbers is 0 and all free states of the resource theory are mapped onto it.
 
-The most general magic theory, the theory of Wigner negativity \nick{or positivity?}, can be expressed as $\R = (\F, \O)$ with
-\begin{align}
-    \F &= \{ \rho: \W[\bmz]{\rho} \geq 0\}\ \text{and} \\
-    \O &= \{ \E: \W[\bmy|\bmx]{\E} \geq 0\}
-\end{align}
-for all points $\bmx, \bmy, \bmz \in \pd$.
-Therefore, any free state $\sigma$ corresponds to a $d^2$-dimensional probability distribution $\W{\sigma}$ and any free operation $\E: \cal{B}(\hd) \mapsto \cal{B}(\hd)$ corresponds to a $d^2 \times d^2$ stochastic matrix (or conditional probability distribution) $\W{\E}$.
-Note that these mappings are one-to-one due to the orthogonality of the phase-point operators as an operator basis.
+\subsection{Set theoretic properties of magic fragments}\label{sec:propmagfrag}
 
-Our goal is to give insight into magic state transformations.
-We first break up the theory into fragments that allow for the incorporation of $\bmd$-majorization in its framework.
-\begin{definition}[\textbf{$\boldsymbol\sigma$-fragment}]\label{def:sigmafrag}
-    A subtheory $\R'$ of the Wigner negativity theory $\R = (\F, \O)$ is called a \emph{$\sigma$-fragment} iff $\R' = (\F, \O_\sigma)$, where the free operations are restricted to the ones that preserve $\sigma$,
+\nick{May move statements around the section or in an appendix.}
+
+\begin{theorem}\label{thm:frag}
+    Let $\R = (\O, \F)$ be a magic theory. 
+    The following statements hold:
+    \begin{enumerate}
+        \item No $\sigma$-fragment is empty.
+        \item If a free operation leaves two states invariant, then it also leaves their mixtures invariant, 
         \begin{equation}
-        \O_\sigma \coloneqq \{ \E \in \O: \E(\sigma) = \sigma \}.
+            \O_{\sigma} \cap \O_{\sigma'} \subseteq \O_{p\sigma + (1-p)\sigma'}\ \text{for all}\ p \in [0,1].
         \end{equation}
-\end{definition}
-
-State $\sigma$ is thus a fixed point of all operations in $\O_\sigma$ and we provide the following theorem which characterises the $\sigma$-fragments as well as how they make up the whole set of free operations.
-\nick{move below}
-
-\subsection{Majorization}\label{sec:major}
-
-Majorization is a fundamental tool that has recently found many applications in quantum information theory \nick{CITE}.
-It describes the \nick{disorder / non-uniformity} of vectors via stochastic transformations that are possible between them.
-
-In order to discuss such stochastic transformations, we first denote by $\stoch$ the set of $(d \times d)$ stochastic matrices that preserve vector $\bmg$.
-Specifically, any $S \in \stoch$ satisfies:
-\begin{enumerate}
-    \item $S_{ij} \geq 0$ for all $i, j \in \zd$;
-    \item $\sum\limits_{j=1}^n S_{ij} = 1$ for all $i \in \zd$;
-    \item $S\bmg = \bmg$.
-\end{enumerate}
-It forms a group under matrix multiplication because it contains the identity and $S^{-1} \in \stoch$ for any $S \in \stoch$.
-
-We can motivate majorization very well for our purposes via its application on quantum thermodynamics in the absence of coherence.
-At any given temperature $\beta$, the thermal state $\gamma_\beta$ is intuitively the most ordered state. 
-Thermal operations are defined as operations that cannot extract energy from the Gibbs state, $\E(\gamma_\beta) = \gamma_\beta$.
-Convertibility between states via thermal operations is equivalent to a stochasticity condition on the energy level populations of the states \nick{CITE}.
-Roughly, the statement is that there exists a thermal operation $\E$ such that $\tau = \E(\rho)$ if and only if there exists a a matrix $S \in \stoch[\bmg]$ such that $\bm{q} = S\bm{p}$, where $\bm{q}, \bm{p}$ and $\bmg$ and the energy level population vectors of $\tau, \rho, \gamma_\beta$ respectively.
-\nick{expand or remove}
-
-We can define majorization based on this definition.
-\begin{definition}\label{def:dmajor}
-    Given $\bmx, \bmy, \bmg \in \reals^d$, such that the components of $\bmg$ are positive, $\bmy$ is said to $\bmg$-majorize $\bmx$, iff there exists a matrix $S \in \stoch$ such that $\bmx = S\bmy$.
-
-    We denote this partial order by $\bmx \prec_{\bmg} \bmy$.
-\end{definition}
-If $\bmg = \frac{1}{d}\bm{1}$, the $d$-dimensional uniform distribution, then $\stoch$ is the set of bistochastic matrices and we retrieve the familiar notion of majorization in entanglement theory.
-\nick{CITE}
-
-A visual representation of $\bmg$-majorization is provided by the Lorenz curve of a vector $\bmz \in \reals^d$.
-Let the vector $\bmz^\downarrow$ denote $\bmz$, but with its components arranged in non-increasing order.
-\begin{definition}
-    Let $\bmz \in \reals^n$.
-    Let $\bmg \in \reals^d$ be a vector with positive components, $\pi$ a permutation mapping $(z_i/g_i) \mapsto (z_i/g_i)^\downarrow$ for all $i=1,\dots,d$ and $D = \sum_{i=1}^d g_i$.
-    The Lorenz curve $L(\bmz|\bmg)$ of vector $\bmz$ is the piecewise linear curve obtained by joining the points 
-\begin{equation}\label{eq:lorenz}
-    \left\{ L_k(\bmz|\bmg) \coloneqq \left( \frac{1}{D}\sum_{i=1}^k g_{\pi(i)}, \sum_{i=1}^k z_{\pi(i)} \right) \in \mathbb{R}^2: k = 1,\dots,d \right\}.
-\end{equation}
-\end{definition}
-\emph{Remark 1.} The origin $L_0(\bmz|\bmg) \coloneqq (0,0)$ is usually included in the curve.
-
-\emph{Remark 2.} The first components of $L_k(\bmz|\bmg)$ are rescaled by $D$ so that comparison of curves with unequal dimensions is possible.
-In fact, the Lorenz curves $L(\bmz|\bmg)$ and $L(\bmz \otimes \bmg|\bmg \otimes \bmg)$, where $\otimes$ denotes the Kronecker product, are identical.
-
-\emph{Remark 3.} Lorenz curves are always concave.
-
-\emph{Remark 4.} If $L_d(\bmz|\bmg) = 1$ and for all $k$, $L_k(\bmz|\bmg) \leq 1$, then $\bmz$ is a probability distribution.
-Lorenz curves of quasi-probability distributions in principle reach above 1.
-
-An example of comparison between different Lorenz curves is illustrated in~\cref{fig:lctoy}.
-\begin{figure}
-    \centering
-    \includegraphics[height=5cm]{sections/major/lctoy.pdf}
-    \caption{Example of different Lorenz curves for quasi-probability vectors under $\bmg$-majorization.
-    Vectors $\bmy$ and $\bmg$ are simply probability distributions.
-    The curve corresponding to vector $\bmg$ is always the straight line connecting $(0,0)$ and $(1,1)$, so that any other Lorenz curve lies above it, for example $\bmx \prec_{\bmg} \bmg$.
-    Curves $L_k(\bmx|\bmg)$ and $L_k(\bmy|\bmg)$ intersect, so neither $\bmx \prec_{\bmg} \bmy$ nor $\bmy \prec_{\bmg} \bmx$.
-    }
-    \label{fig:lctoy}
-\end{figure}
-
-We now present the important majorization result needed in our analysis of magic.
-\begin{theorem}\label{thm:dmajor}
-Given $\bmx, \bmy, \bmg \in \reals^d$, such that the components of $\bmg$ are positive, the following statements are equivalent:
- \begin{enumerate}%[label=\enlabel{TM}{\arabic*}]
-	\item\label{en:tm1} $\bmx \prec_{\bmg} \bmy$;
-	\item\label{en:tm5} $L_k(\bmx|\bmg) \leq L_k(\bmy|\bmg)$ for all $k=1,2,\dots, d-1$ and $L_d(\bmx|\bmg) = L_d(\bmy|\bmg)$.
+        \item Let $\E$ be a $\cptp$ operation with Wigner distribution $\W{\E}$.
+        For $\R = \Rmax$ $\E \in \O_\sigma$ iff $\W{\E} \in \stochw$.
     \end{enumerate}
 \end{theorem}
-A restatement of the theorem including more equivalent conditions, along with a proof is provided in the \nick{appendix}.
+\begin{proof}$ $\\
 
-\subsection{Magic fragments}\label{sec:magfrag}
+    \begin{enumerate}
+    \item Consider the completely depolarising \nick{replacement} map
+    \begin{align}
+        \E(\rho) &= \sigma \tr[\rho],\ \text{with} \\
+        \W[\bmy|\bmx]{\E} &= \W[\bmy]{\sigma} \tr[\rho],
+    \end{align}
+    where $\sigma \in \F$. 
+    Then, $\E \in \O_\sigma$.
+    It can be thought as a sequence of tracing out state $\rho$ and preparing the free state $\sigma$.
 
-\begin{theorem}\label{thm:frag}
-    In the resource theory of Wigner negativity $\R = (\O, \F)$, the following statements hold:
-    \begin{enumerate}
-        \item The $\sigma$-fragment $\O_\sigma$ is equal to the set of all $\cptp$ operations with stochastic Wigner distributions that leave $\W{\sigma}$ invariant.
-\nick{Assuming maximal resource theory}
-        \item Every free operation leaves at least one free state invariant such that $\O = \bigcup\limits_{\sigma \in \F} \O_\sigma$.
-        \item If a free operation leaves two states invariant, then it also leaves every mixture of them invariant, $\O_{\sigma} \cap \O_{\sigma'} \subseteq \O_{p\sigma + (1-p)\sigma'}$ for all $p \in [0,1]$.
-    \end{enumerate}
-\end{theorem}
-\begin{proof}
-    \begin{enumerate}
+    \item Let $\E \in \O_{\sigma} \cap \O_{\sigma'}$.
+    Then $\E \in \cptp$ and corresponds to stochastic Wigner distribution $\W{\E}$ such that $\W{\E} \W{\sigma} = \W{\sigma}$ and $\W{\E} \W{\sigma'} = \W{\sigma'}$.
+    Then, $\W{\E} \W{p\sigma + (1-p)\sigma'} = \W{p\sigma + (1-p)\sigma'}$ for any $p \in [0,1]$ due to the additive property~\ref{en:w4} of the Wigner distribution, implying that state $p\sigma + (1-p)\sigma'$ is also left invariant by $\E$.
+
     \item Let $\O_\sigma' \coloneqq \{ \E \in \cptp: \W{\E} \in \stochw \}$ be the described set of operations.
@@
     Hence, $\O_\sigma' \subseteq \O_\sigma$.
-
-    \item Suppose $\E$ is in $\O_\sigma$, then it is also in $\O$, hence $\bigcup\limits_{\sigma \in \F} \O_\sigma \subseteq \O$.
-
-    Conversely, suppose $\E$ is in $\O$. 
-    The free states are mapped one-to-one to a subset $\cal{S}$ of the $(d^2 - 1)$-dimensional probability simplex.
-    $\cal{S}$ is convex, since any combination of free states is also free and the Wigner distribution is linear.
-    Therefore, $\cal{S}$ is convex and compact as a convex subset of the bounded compact probability simplex. \nick{Need to prove that $\cal{S}$ is closed.}
-    Then, $\W{\E}{}$ is a stochastic, thus continuous, mapping from $\cal{S}$ to itself and Brouwer's fixed point theorem \nick{CITE} implies that there exists a probability distribution $g_{\bmz}, \bmz \in \pd$ that is preserved by $\W{\E}{}$.
-    This corresponds one-to-one to a state $\sigma \coloneqq \sum_{\bmz \in \pd} g_{\bmz} A_{\bmz}$ and so $\O \subseteq \bigcup\limits_{\sigma \in \F} \O_\sigma$.
-
-    \item Let $\E \in \O_{\sigma} \cap \O_{\sigma'}$.
-    Then $\E \in \cptp$ and corresponds to stochastic Wigner distribution $\W{\E}$ such that $\W{\E} \W{\sigma} = \W{\sigma}$ and $\W{\E} \W{\sigma'} = \W{\sigma'}$.
-    Then, $\W{\E} \W{p\sigma + (1-p)\sigma'} = \W{p\sigma + (1-p)\sigma'}$ for any $p \in [0,1]$ due to the additive property~\ref{en:w4} of the Wigner distribution, implying that state $p\sigma + (1-p)\sigma'$ is also left invariant by $\E$.
     \end{enumerate}
@@
 
-The structure of the $\sigma$-fragment $(\F, \O_\sigma)$ for any $d$-dimensional $\sigma$ in $\F$ admits the pre-order of $\bmg$-majorization with $\bmg = \W{\sigma}$, a $d^2$-dimensional probability vector.
-If any component of $\W{\sigma}$ is zero, then we can always add some $\epsilon$ amount of unital noise by mixing $\sigma$ with the maximally mixed state $\frac{1}{d}\id$. 
-This ensures that all components are strictly positive and $\bmd$-majorization can be used.
+Any free state $\sigma \in \cal{B}(\hd)$ corresponds to a $d^2$-dimensional probability distribution $\W{\sigma}$ and any free operation $\E: \cal{B}(\hd) \mapsto \cal{B}(\hd)$ corresponds to a $d^2 \times d^2$ stochastic matrix (or conditional probability distribution) $\W{\E}$.
+Note that these mappings are one-to-one due to the orthogonality of the phase-point operators as an operator basis.
 
-\begin{proposition}
-    Let $\R = (\O, \F)$ be a theory of magic.
-    If the state conversion $\rho \xrightarrow{\O} \tau$ is possible, then there exists a full-rank free state $\sigma \in \F$ such that $\W{\tau} \prec_{\W{\sigma}} \W{\rho}$.
-\end{proposition}
-\begin{proof}
-    Suppose there exists $\E \in \O$ such that $\E(\rho) = \tau$.
-    The free operation belongs to a $\sigma$-fragment, $\E \in \O_\sigma$, for some $\sigma \in \F$.
-    Then, $\W{\E}\W{\rho} = \W{\tau}$ with $\W{\E} \in \stochw$, or, equivalently, $\W{\tau} \prec_{\W{\sigma}} \W{\rho}$.
-\end{proof}
-\nick{This proposition needs modification. What about $\E(\rho) = \ketbra{0}$?}
+\emph{Remark 1.} Note that free states $\F$ are mapped onto a \emph{strict subset} of the set of probability distributions.
+As a counterexample, the sharp $d^2$-dimensional probability distribution $(1, 0, \dots, 0)$ does not correspond to any qudit Wigner distribution because of the boundedness condition~\ref{en:w3} in~\cref{thm:wstate}.
 
-\emph{Remark 1.} Note that free states $\F$ map onto a \emph{strict subset} of the set of probability distributions.
-As a counterexample, consider the 9-dimensional probability distribution with non-zero components $\left(\frac{1}{2}, \frac{1}{4}, \frac{1}{4} \right)$. 
-It does not correspond to any qutrit Wigner distribution because the component with value $\frac{1}{2}$ does not satisfy the boundedness condition~\ref{en:w3} of~\cref{thm:wstate}.
-
-\emph{Remark 2.} Similarly, any $\O_\sigma$ may be mapped onto a \emph{strict subset} of the set $\stochw$ of stochastic matrices that preserve $\W{\sigma}{}$.
+\emph{Remark 2.} Similarly, not all stochastic matrices correspond to $\cpos$ operations.
 
@@
 
-\emph{Remark 3.} No $\sigma$-fragment is empty.
-In fact, an example of a stabilizer operation $\E \in \so \cap \O_\sigma$, for any $\sigma$-fragment, is the completely depolarising \nick{replacement} map
-\begin{align}
-    \E(\rho) &= \sigma \tr[\rho],\ \text{with} \\
-    \W[\bmy|\bmx]{\E} &= \W[\bmy]{\sigma} \tr[\rho],
-\end{align}
-which can be thought as a sequence of tracing out state $\rho$ and preparing the stabilizer $\sigma$.
-
 The zoo of all the operation classes is summarised in ~\cref{fig:zoo}.

### 2020-06-09 sections/frag/frag.tex
Reshuffled stochasticity and fragments sections

\section{General resource fragments}
\label{sec:frag}

State convertibility within a given resource theory is often a hard question to address due to the intricate structure of the theory.
In general, the structure of a theory $\R$ is described by a pre-order $\prec_\R$ \nick{expand / move to intro}.
Subdividing magic theories into $\sigma$-fragments \nick{helps}.
\subsection{Monotones}\label{sec:mono}

Resource theories are commonly equipped with monotones which quantify the resource\nick{CITE}. 
\begin{definition}[\textbf{Resource monotone}]\label{def:mono}
    Let $\R = (\F, \O)$ be a general resource theory.
    A monotone $\M$ is a projection from the set of all states of the theory to the real line, satisfying two conditions:
    \begin{enumerate}
        \item All free states are mapped onto 0, $\M(\sigma) = 0,\ \sigma \in \F$;
        \item $\M$ is monotonically decreasing under free operations, $\M(\rho_1) \leq \M(\rho_2)$ if $\rho_1 \prec_{\R} \rho_2$.
    \end{enumerate}
\end{definition}
The first condition reflects the property that all free states can be converted into each other, hence they need to be mapped onto the same number, by convention 0.
The second condition reflects the no resource generating property of free operations, thus monotones respect the pre-order $\prec_\R$ of the theory.
Furthermore, if a monotone satisfies the additivity condition,
\begin{equation}
    \M(\rho_1 \otimes \rho_2) = \M(\rho_1) + \M(\rho_2),
\end{equation}
it is of practical importance for resource distillation, which we discuss in~\cref{sec:distill} within the context of magic.

A very commonly used magic monotone is the \emph{mana} of a state \nick{CITE}, defined as
\begin{equation}
    \mana{\rho} \coloneqq \log{\left(\sum\limits_{\bmz \in \pd} \abs{\W[\bmz]{\rho}}\right)}.
\end{equation}
It is a monotone, additive function of the $\ell_1$-norm of negativity~\nick{CITE}.

\subsection{Fragments}

Monotones reduce the structure of the resource theory $\R$ into a real number ordering.
Therefore, two states, even if incomparable in $\R$, are always mapped onto ordered real numbers.
This is a generic approach that ensures a form of state comparison and resource quantification.
However, motivated by $\sigma$-fragments in magic theories, it is clear that we can often reduce the theory by a less \nick{information-collapsing} projection into a subtheory $\R'$ which has a tractable pre-order $\R'$, as sketched in~\cref{fig:fragments}.
\begin{figure}
    \centering
    \includegraphics[height=3cm]{sections/major/fragments.pdf}
    \caption{Fragments \nick{Split into subfigures}
    }
    \label{fig:fragments}
\end{figure}
We define such a resource projection for general resource theories as follows.
\begin{definition}[\textbf{Resource projection}]\label{def:fragment}
    Let a resource theory $\R = (\F, \O)$ have pre-order $\prec_{\R}$ and operational composition rule $\circ_{\R}$. 
    Any subtheory $\R' = (\F', \O')$ with pre-order $\prec_{\R'}$ and operational composition rule $\circ_{\R'}$ is called a resource fragment iff there exists a surjective projection $\Pi \equiv (\Pis, \Pio): \R \mapsto \R'$ that satisfies the following two conditions.
    \begin{enumerate}
        \item $\Pis: \cal{B}(\cal{H}) \mapsto \cal{B}(\cal{H})$ and $\rho_1 \prec_{\R} \rho_2$ whenever $\Pis(\rho_1) \prec_{\R'} \Pis(\rho_2)$ for all states $\rho_1, \rho_2$;
        \item $\Pio: \O \mapsto \O'$ and $\Pio(\E_1) \circ_{\R'} \Pio(\E_2) = \Pio(\E_1 \circ_{\R} \E_2)$ for all free operations $\E_1, \E_2 \in \O$. 
    \end{enumerate}
    We call $\Pi$ a resource projection.
\end{definition}
Fragment $\R'$ is the image of the projection $\Pi$.
Considering a resource projection is particularly useful when the structure of the fragment is more tractable.

A monotone is the simplest tractable projection as formally stated in~\cref{thm:monofrag}.
\begin{proposition}\label{thm:monofrag}
	Let $\M$ be a resource monotone of a resource theory $\R$. 
	Then $\M$ is a resource projection that reduces the pre-order $\prec_\R$ to a total order.
\end{proposition}
\begin{proof}
	Consider a monotone $\M$ in the context of a general resource theory $\R = (\F, \O)$.
	Let $\R' = (\F', \O')$, where $\F' \equiv \{0\}$ and $\O'$ is the set of non-increasing real functions mapping the set of non-negative real numbers $\mathbb{R}_{\geq 0}$ to itself. 
	We also set $\prec_{\R'}$ as the usual total order $\leq$ and $\circ_{\R'}$ as the composition of real functions.

	Let $\Pis = \M$.
	The defining properties of a monotone, given in~\cref{def:mono}, ensure condition 1 of~\cref{def:fragment}.

	Let $\Pio$ project any $\E \in \O$ onto a function $f \in \O$ which maps $\M(\rho)$ onto $\M(\E(\rho))$ for all states $\rho$.

	The ordered pair $(\Pis, \Pio)$ is the resource projection which corresponds to monotone $\M$.
\end{proof}

We now justify the name $\sigma$-fragment for the subdivision of a magic theory $\R = (\F, \O)$, by establishing a resource projection which reduces $\R$ into any subtheory $(\F, \O_\sigma)$.
\begin{proposition}
    Let $\R = (\F, \O)$ be a theory of magic.
    Every $\sigma$-fragment $(\F, \O_\sigma)$ is a resource fragment of $\R$.
\end{proposition}
\begin{proof}
    Let the state projection be the identity projection $\Pis:\F\mapsto\F$.

    Consider the operation projection $\Pio:\O \mapsto \O_\sigma$, defined as
    \begin{equation}
    \Pio(\E) =
    \begin{cases}
        \E,\ &\sigma \in \O, \\
        1_{\rm{C}},\ &\sigma \notin \O.
    \end{cases}
    \end{equation}
    The ordered pair $(\Pis, \Pio)$ acts as the desired projection.
\end{proof}

An important example of a fragment appears in quantum thermodynamics. 
Consider a projection $\Pi$, such that $\Pis$ dephases all states in the energy eigenbasis, while $\Pio$ maps all free operations to themselves.
Then $\Pi$ describes the theory in the absence of coherences and the new pre-order is simply thermo-majorization, which in fact is fully solvable in the form of entropic conditions~\cite{cit:gour}. \nick{expand/rephrase}

Existing magic theories can be thought of as fragments of $\Rmax$.
\begin{proposition}
    Every theory of magic $\R$ is a fragment of the maximal theory $\Rmax$.
\end{proposition}
\begin{proof}
    Consider the state projection $\Pis:\Fmax \mapsto \F$, defined as
    \begin{equation}
    \Pis(\sigma) =
    \begin{cases}
        \sigma,\ &\sigma \in \F, \\
        \frac{1}{d}\id,\ &\sigma \notin \F.
    \end{cases}
    \end{equation}
    \nick{Perhaps $\Pis = $ identity}
    Let $1_{\rm{C}}$ denote the identity channel.
    Consider the operation projection $\Pio:\Omax \mapsto \O$, defined as
    \begin{equation}
    \Pio(\E) =
    \begin{cases}
        \E,\ &\sigma \in \O, \\
        1_{\rm{C}},\ &\sigma \notin \O.
    \end{cases}
    \end{equation}
    The orderd pair $(\Pis, \Pio)$ acts as the desired projection.
\end{proof}

### 2020-06-09 sections/major/major.tex
Reshuffled stochasticity and fragments sections

@@
 
+Let $\R = (\F, \O)$ be a general resource theory.
+We call $\R' = (\F', \O')$ a \emph{subtheory} of $\R$ iff $\F' \subseteq \F$ and $\O' \subseteq \O$. 
 Any magic theory $\R = (\F, \O)$ is a subtheory of $\Rmax$ as explained in~\cref{sec:intro}, and as such it falls under this new stochasticity setting. \nick{expand}
@@
 \begin{definition}[\textbf{$\boldsymbol\sigma$-fragment}]\label{def:sigmafrag}
-    A subtheory $\R'$ of the Wigner negativity theory $\R = (\F, \O)$ is called a \emph{$\sigma$-fragment} iff $\R' = (\F, \O_\sigma)$, where the free operations are restricted to the ones that preserve $\sigma$,
+    A subtheory $\R'$ of a magic theory $\R = (\F, \O)$ is called a \emph{$\sigma$-fragment} of $\R$ iff $\R' = (\F, \O_\sigma)$, where the free operations are restricted to the ones that leave $\sigma$ invariant,
     \begin{equation}
@@
 \end{proof}
+Therefore, identifying an invariance in the setup helps in determining whether a state conversion $\rho \xrightarrow{\E \in \O} \tau$ is possible. 
+If state $\sigma$ is left invariant by an operational sequence, then the total operation $\E$ that converts $\rho$ to $\tau$ lies in $\O_\sigma$. \nick{expand}
+
+The zoo of all magic operation classes is summarised in ~\cref{fig:zoo}.
+Completely positive-Wigner-preserving operations~\cite{cit:wang} form the operation class $\Omax$.
+Therefore, $\sigma$-fragments cover this theory of magic exactly and any magic subtheory is contained within this cover.
+In particular, the stabilizer operations $\so$ are contained within $\Omax$.
+\begin{figure}[t]
+    \centering
+        \includegraphics[scale=0.47
+        ]{sections/major/operations.pdf}
+    \caption{Zoo of allowed operations for magic resource theories.
+    Established theories involve operations within the yellow regions, following the hierarchy $\so \subset \cspo \subset \spo \subset \Omax$.
+    We introduce fragments $\O_\sigma,\ \sigma \in \F$ that cover $\Omax$ with each one extending to a set of stochastic maps that allows for $\bmd$-majorization to be used.
+    }
+    \label{fig:zoo}
+\end{figure}
 
@@
 
-\subsection{General resource fragments}\label{sec:frag}
-
-Subdividing magic into $\sigma$-fragments
-Magic is commonly quantified via monotones \nick{CITE}. 
-A monotone is a projection from the $d$-dimensional set of density states of the theory to the real line. 
-It is monotonically decreasing under free operations, 
-\begin{equation}\label{eq:monotonicity}
-    \cal{M}(\rho_1) \leq \cal{M}(\rho_2)\ \text{if}\ \rho_1 \prec_{\R} \rho_2,
-\end{equation}
-reflecting the no resource generating property of free operations and thus respecting the pre-order $\prec$ of the theory.
-A popular magic monotone is the \emph{mana} of a state \nick{CITE}, defined as
-\begin{equation}
-    \mana{\rho} \coloneqq \log{\left(\sum\limits_{\bmz \in \pd} \abs{\W[\bmz]{\rho}}\right)}.
-\end{equation}
-However, a single monotone does not provide information on whether two states are incomparable in the theory.
-Motivated by this restrictive nature of the monotone, we introduce the idea of a \emph{fragment} as a less restrictive way of comparing the resource of states in an arbitrary theory $\R = (\F, \O)$.
-\nick{explain exactly why fragments $>$ monotones}
-
-\begin{figure}
-    \centering
-    \includegraphics[height=3cm]{sections/major/fragments.pdf}
-    \caption{Fragments \nick{Split into subfigures}
-    }
-    \label{fig:fragments}
-\end{figure}
-
-Let $\R' = (\F', \O')$ be a subtheory of $\R$ so that $\F' \subseteq \F$ and $\O' \subseteq \O$. 
-Then, we define a fragment as follows.
-\begin{definition}[\textbf{Resource projection}]\label{def:fragment}
-    Let a resource theory $\R = (\F, \O)$ have pre-order $\prec_{\R}$ and operational composition rule $\circ_{\R}$. 
-    We call a resource fragment of $\R$ any theory $\R' = (\F', \O')$ with pre-order $\prec_{\R'}$ and operational composition rule $\circ_{\R'}$, if there exists a surjective projection $\Pi \equiv (\Pis, \Pio): \R \mapsto \R'$ that satisfies the following two conditions.
-    \begin{enumerate}
-        \item $\Pis: \F \mapsto \F'$ \nick{actually it maps all states, not just the free ones} and $\rho_1 \prec_{\R} \rho_2$ whenever $\Pis(\rho_1) \prec_{\R'} \Pis(\rho_2)$ for any states $\rho_1, \rho_2$;
-        \item $\Pio: \O \mapsto \O'$ and $\Pio(\E_1) \circ_{\R'} \Pio(\E_2) = \Pio(\E_1 \circ_{\R} \E_2)$ for any free operations $\E_1, \E_2 \in \O$. 
-    \end{enumerate}
-    We call $\Pi$ a resource projection.
-\end{definition}
-Fragment $\R'$ is the image of the projection $\Pi$.
-Considering a resource projection is particularly useful when the structure of the fragment is more tractable.
-
-\begin{proposition}
-    Let $\R = (\F, \O)$ be a theory of magic.
-    Every $\sigma$-fragment $(\F, \O_\sigma)$ is a resource fragment of $\R$.
-\end{proposition}
-\begin{proof}
-    Let the state projection be the identity projection $\Pis:\F\mapsto\F$.
-
-    Consider the operation projection $\Pio:\O \mapsto \O_\sigma$, defined as
-    \begin{equation}
-    \Pio(\E) =
-    \begin{cases}
-        \E,\ &\sigma \in \O, \\
-        1_{\rm{C}},\ &\sigma \notin \O.
-    \end{cases}
-    \end{equation}
-    The ordered pair $(\Pis, \Pio)$ acts as the desired projection.
-\end{proof}
-
-\begin{proposition}
-    Every theory of magic $\R = (\F, \O)$ is a fragment of the maximal theory $\Rmax$.
-\end{proposition}
-\begin{proof}
-    Consider the state projection $\Pis:\Fmax \mapsto \F$, defined as
-    \begin{equation}
-    \Pis(\sigma) =
-    \begin{cases}
-        \sigma,\ &\sigma \in \F, \\
-        \frac{1}{d}\id,\ &\sigma \notin \F.
-    \end{cases}
-    \end{equation}
-    \nick{Perhaps $\Pis = $ identity}
-    Let $1_{\rm{C}}$ denote the identity channel.
-    Consider the operation projection $\Pio:\Omax \mapsto \O$, defined as
-    \begin{equation}
-    \Pio(\E) =
-    \begin{cases}
-        \E,\ &\sigma \in \O, \\
-        1_{\rm{C}},\ &\sigma \notin \O.
-    \end{cases}
-    \end{equation}
-    The orderd pair $(\Pis, \Pio)$ acts as the desired projection.
-\end{proof}
-
-Monotones reduce the structure of the theory into a real number ordering, therefore a monotone is the simplest tractable projection as formally stated in~\cref{thm:monofrag}.
-\begin{proposition}\label{thm:monofrag}
-	Let $\cal{M}$ be a monotone defined in the context of a resource theory $\R$. 
-	Then $\cal{M}$ is a resource projection that  reduces the pre-order $\prec_\R$ to a total order.
-\end{proposition}
-\begin{proof}
-	Consider a monotone $\cal{M}$ in the context of a general resource theory $\R = (\F, \O)$.
-	Let $\R' = (\F', \O')$, where $\F' \equiv \{0\}$ is the set of non-negative real numbers and $\O'$ is the set of non-increasing real functions mapping $\mathbb{R}_{\geq 0}$ to $\mathbb{R}_{\geq 0}$. 
-	Naturally, we also set $\prec_{\R'}$ as the usual total order $\leq$ and $\circ_{\R'}$ as the composition of real functions.
-
-	The defining property of a monotone, given in~\cref{eq:monotonicity} ensures condition 1 of~\cref{def:fragment}.
-
-	We can then project any $\E \in \O$ onto a function $f \in \O'$, so that $f$ maps $\cal{M}(\rho)$ onto $\cal{M}(\E(\rho))$ for all states $\rho$.
-
-	\nick{expand}
-\end{proof}
-
 \subsection{Set theoretic properties of magic fragments}\label{sec:propmagfrag}
@@
 It preserves the uniform distribution $\W{\frac{1}{5}\id}{}$, but it does not correspond to any completely positive operation and therefore to any $\E \in \O$, due to~\cref{thm:frag}.
-
-The zoo of all the operation classes is summarised in ~\cref{fig:zoo}.
-Completely positive-Wigner-preserving operations ($\cpwp$) form the largest operation class in the literature.
-Therefore, $\sigma$-fragments cover this theory of magic exactly and any magic subtheory is contained within this cover.
-For example, the stabilizer-preserving ($\spo$)~\cite{cit:ahmadi} and completely stabilizer-preserving ($\cspo$)~\cite{cit:seddon} operation subclasses follow the hierarchy $\so \subset \cspo \subset \spo \subset \cpwp$ and therefore are described by our $\sigma$-fragments.
-
-\begin{figure}[b]
-    \centering
-        \includegraphics[scale=0.45]{sections/major/operations.pdf}
-    \caption{Zoo of allowed operations for magic resource theories.
-    Established theories involve operations within the yellow regions, following the hierarchy $\so \subset \cspo \subset \spo \subset \cpwp$.
-    We introduce fragments $\O_\sigma \subset \stochw,\ \sigma \in \F$ that cover $\cpwp$ with each one extending to a set of stochastic maps that allows for $\bmd$-majorization to be used.
-    \nick{fragments are the intersections of blue and orange, not the whole bubble - technically $\stochw$ should be replaced by its operational pre-image.}
-    }
-    \label{fig:zoo}
-\end{figure}

### 2020-06-09 sections/frag/frag.tex
Updated resource projection definition

@@
         \item All free states are mapped onto 0, $\M(\sigma) = 0,\ \sigma \in \F$;
-        \item $\M$ is monotonically decreasing under free operations, $\M(\rho_1) \leq \M(\rho_2)$ if $\rho_1 \prec_{\R} \rho_2$.
+        \item $\M$ is monotonically decreasing under free operations, $\M(\rho_1) \leq \M(\rho_2)$ whenever $\rho_1 \prec_{\R} \rho_2$.
     \end{enumerate}
@@
 However, motivated by $\sigma$-fragments in magic theories, it is clear that we can often reduce the theory by a less \nick{information-collapsing} projection into a subtheory $\R'$ which has a tractable pre-order $\R'$, as sketched in~\cref{fig:fragments}.
-\begin{figure}
+\begin{figure}[t]
     \centering
@@
     \begin{enumerate}
-        \item $\Pis: \cal{B}(\cal{H}) \mapsto \cal{B}(\cal{H})$ and $\rho_1 \prec_{\R} \rho_2$ whenever $\Pis(\rho_1) \prec_{\R'} \Pis(\rho_2)$ for all states $\rho_1, \rho_2$;
+        \item $\Pis: \cal{B}(\cal{H}) \mapsto \cal{B}(\cal{H})$ and $\Pis(\rho_2) \nprec_{\R'} \Pis(\rho_1)$ whenever $\rho_1 \prec_{\R} \rho_2$;
         \item $\Pio: \O \mapsto \O'$ and $\Pio(\E_1) \circ_{\R'} \Pio(\E_2) = \Pio(\E_1 \circ_{\R} \E_2)$ for all free operations $\E_1, \E_2 \in \O$.
@@
 Fragment $\R'$ is the image of the projection $\Pi$.
-Considering a resource projection is particularly useful when the structure of the fragment is more tractable.
+Considering a resource projection is particularly useful when the pre-order of the fragment is tractable.
+Note the subtle difference of condition 1 in~\cref{def:fragment} and condition 2 in~\cref{def:mono}, which is due to fragments generally retaining a pre-order, while monotones impose a total order.
 
-A monotone is the simplest tractable projection as formally stated in~\cref{thm:monofrag}.
+A monotone is the projection with the simplest tractable order as formally stated in~\cref{thm:monofrag}.
 \begin{proposition}\label{thm:monofrag}

### 2020-06-10 sections/frag/frag.tex
Noticed inaccuracies in the definition of resource projection + subsequent theorems.

@@
     \begin{enumerate}
-        \item $\Pis: \cal{B}(\cal{H}) \mapsto \cal{B}(\cal{H})$ and $\Pis(\rho_2) \nprec_{\R'} \Pis(\rho_1)$ whenever $\rho_1 \prec_{\R} \rho_2$;
+        \item $\Pis: \D \mapsto \D$ and $\Pis(\rho_2) \nprec_{\R'} \Pis(\rho_1)$ whenever $\rho_1 \prec_{\R} \rho_2$;
         \item $\Pio: \O \mapsto \O'$ and $\Pio(\E_1) \circ_{\R'} \Pio(\E_2) = \Pio(\E_1 \circ_{\R} \E_2)$ for all free operations $\E_1, \E_2 \in \O$.
@@
 	Let $\Pis = \M$.
-	The defining properties of a monotone, given in~\cref{def:mono}, ensure condition 1 of~\cref{def:fragment}.
+	The defining properties of a monotone, given in~\cref{def:mono}, ensure condition 1 of~\cref{def:fragment}. \nick{expand}
 
@@
 \begin{proof}
-    Let the state projection be the identity projection $\Pis:\F\mapsto\F$.
+    Let the state projection be the identity projection $\Pis:\D\mapsto\D$.
 
@@
     \end{equation}
+    \nick{$\Pio$ should be different, this here is not right.
+If we need to project every $\E \in \O$, we may need a different condition on $\Pio$ than $\Pio(\E_1) \circ_{\R'} \Pio(\E_2) = \Pio(\E_1 \circ_{\R} \E_2)$.}
     The ordered pair $(\Pis, \Pio)$ acts as the desired projection.
@@
 \begin{proof}
-    Consider the state projection $\Pis:\Fmax \mapsto \F$, defined as
-    \begin{equation}
-    \Pis(\sigma) =
-    \begin{cases}
-        \sigma,\ &\sigma \in \F, \\
-        \frac{1}{d}\id,\ &\sigma \notin \F.
-    \end{cases}
-    \end{equation}
-    \nick{Perhaps $\Pis = $ identity}
-    Let $1_{\rm{C}}$ denote the identity channel.
-    Consider the operation projection $\Pio:\Omax \mapsto \O$, defined as
-    \begin{equation}
-    \Pio(\E) =
-    \begin{cases}
-        \E,\ &\sigma \in \O, \\
-        1_{\rm{C}},\ &\sigma \notin \O.
-    \end{cases}
-    \end{equation}
-    The orderd pair $(\Pis, \Pio)$ acts as the desired projection.
+    \nick{We need a state projection that establishes that some free states are not free any more $+$ an operations projection.}
 \end{proof}

### 2020-06-10 sections/magic/magic.tex
Noticed inaccuracies in the definition of resource projection + subsequent theorems.

@@
 We are interested in all resource theories of magic $\R = (\F, \O)$ in which free operations cannot generate any amount of resource. 
-The structure of such theory is described by a pre-order, often called partial order \nick{CITE}, $\prec_{\R}$ between states.
+Further denote by $\D$ the set of states considered under the theory, that is the union of free and resource states.
+The structure of such theory is described by a partial order \nick{CITE}, hereinafter called a \emph{pre-order}, $\prec_{\R}$ between states.
 We write $\rho' \prec_{\R} \rho$ iff there exists $\E \in \O$ such that $\E(\rho) = \rho'$.
 Naturally, states may be incomparable under the given theory, meaning that there exists no free operation that converts one to the other.
+We further call $\R' = (\F', \O')$ a \emph{subtheory} of $\R$ iff $\F' \subseteq \F$ and $\O' \subseteq \O$. 
+The above notation will be used for general resource theories as well.
 

### 2020-06-10 sections/major/major.tex
Updated resource projection definition
Noticed inaccuracies in the definition of resource projection + subsequent theorems.

@@
 
-Let $\R = (\F, \O)$ be a general resource theory.
-We call $\R' = (\F', \O')$ a \emph{subtheory} of $\R$ iff $\F' \subseteq \F$ and $\O' \subseteq \O$. 
-Any magic theory $\R = (\F, \O)$ is a subtheory of $\Rmax$ as explained in~\cref{sec:intro}, and as such it falls under this new stochasticity setting. \nick{expand}
-
+Any magic theory $\R = (\F, \O)$ is a subtheory of $\Rmax$ as explained in~\cref{sec:intro}, and as such it falls under this new stochasticity setting. 
+This observation gives rise to the idea of subdividing magic theories into ``chunks'' identified by the invariance of a particular state under stochastic processes. \nick{explain better}
 \begin{definition}[\textbf{$\boldsymbol\sigma$-fragment}]\label{def:sigmafrag}
@@
 State $\sigma$ is thus a fixed point of all operations in $\O_\sigma$. 
-This is an observation arising from the stochastic nature of free operations. 
 We now show that every free operation has a fixed point, so that the theory $\R$ can be entirely subdivided into $\sigma$-fragments.
@@
 \begin{theorem}
-    Let $\R = (\O, \F)$ be a theory of magic.
-    Suppose the state conversion $\rho \xrightarrow{\E \in \O} \tau$ is possible. 
+    Let $\R = (\F, \O)$ be a theory of magic.
+    Suppose the state conversion $\rho \xrightarrow{\E \in \O} \tau$ is possible, $\tau \prec_\R \rho$.
     Then, there exists a full-rank free state $\sigma \in \F$ such that  $\W{\tau} \prec_{\W{\sigma}} \W{\rho}$.
@@
     The curve corresponding to vector $\bmd$ is always the line segment connecting $(0,0)$ and $(1,1)$, so that any other Lorenz curve lies above it, for example $\bmx \prec_{\bmd} \bmd$.
-    Curves $L_k(\bmx|\bmd)$ and $L_k(\bmy|\bmd)$ intersect, so neither $\bmx \prec_{\bmd} \bmy$ nor $\bmy \prec_{\bmd} \bmx$.
+    Curves $L_k(\bmx|\bmd)$ and $L_k(\bmy|\bmd)$ intersect, so $\bmx \nprec_{\bmd} \bmy$ as well as $\bmy \nprec_{\bmd} \bmx$.
     \nick{Recast in terms of magic}
@@
 
-\emph{Remark 2.} Similarly, not all stochastic matrices correspond to $\cpos$ operations.
+\emph{Remark 2.} Similarly, not all stochastic matrices correspond to completely positive operations.
 
@@
 \end{equation}
-It preserves the uniform distribution $\W{\frac{1}{5}\id}{}$, but it does not correspond to any completely positive operation and therefore to any $\E \in \O$, due to~\cref{thm:frag}.
+It preserves the uniform distribution $\W{\frac{1}{5}\id}{}$, but it does not correspond to any $\cpos$ operation, hence any $\E \in \O$ due to~\cref{thm:frag}.

### 2020-06-11 appendix.tex
Restructured document

--- 2020-06-02 appendix/major.tex
@@
 Furthermore, mana is additive due to the multiplicative property~\ref{en:w4} of~\cref{thm:wstate}.
+
+%%%
+
+\section{Properties of the Wigner distribution}
+\label{app:wigner}
+
+Here we present important properties of the Wigner distribution that are used throughout the paper.
+
+\begin{proposition}\label{thm:wstate}
+    The Wigner distribution of a state $\rho$ is
+    \begin{enumerate}%[label=\enlabel{W}{\arabic*}]
+        \item\label{en:w1} Real valued: $\W{\rho} \in \mathbb{R}^{d^2}$;
+        \item\label{en:w2} Normalised: $\sum_{\bmz \in \pd} \W[\bmz]{\rho}=1$;
+        \item\label{en:w3} Bounded: $\abs{\W[\bmx]{\rho}} \leq \frac{1}{d}$.
+        \item\label{en:w4} Additive under mixing:
+
+        $\W[\bmx]{\sum_i p_i \rho_i} = \sum\limits_i p_i \W[\bmx]{\rho_i}$;
+        \item\label{en:w5} Multiplicative under tensor products:
+
+        $\W[\bmx_A \oplus \bmx_B]{\rho_A \otimes \rho_B} = \W[\bmx_A]{\rho_A}\W[\bmx_B]{\rho_B}$.
+	\end{enumerate}
+\end{proposition}
+A distribution satisfying the first three properties does not necessarily correspond to a positive semi-definite state.
+
+\begin{proposition}
+    \label{thm:wchannel}
+    The Wigner distribution of a $\cptp$ operation $\E: \cal{B}(\hd[d_A]) \mapsto \cal{B}(\hd[d_B])$ is:
+    \begin{enumerate}
+        \item\label{en:wo1} Real-valued: $\W[\bmy|\bmx]{\E} \in \mathbb{R}$;
+        \item\label{en:wo2} Normalised: $\sum_{\bmz \in \pd[d_B]} \W[\bmz|\bmx]{\E} = 1$ for any $\bmx \in \pd[d_A]$;
+        \item\label{en:wo3} Bounded: $\abs{\W[\bmy|\bmx]{\E}} \leq \frac{d_A}{d_B}$;
+	    \item\label{en:wo4} \nick{Transitive}: $\W[\bmy]{\E(\rho)} = \sum_{\bmz \in \pd[d_A]} \W[\bmy|\bmz]{\E} \W[\bmz]{\rho}$ for any $\bmy \in \pd[d_B]$.
+    \end{enumerate}
+\end{proposition}
+If $d_A = d_B$, and in particular if operation $\E$ maps a Hilbert space onto itself, then the stochasticity condition $\abs{\W[\bmy|\bmx]{\E}} \leq 1$ is satisfied.

### 2020-06-11 magic_paper.tex
Reshuffled stochasticity and fragments sections
Restructured document

@@
-\input{preamble/magic_preamble}
+\documentclass[pra,
+aps,
+twocolumn,
+superscriptaddress,
+groupedaddress,
+nofootinbib,
+reprint
+]{revtex4-1}
+
+\input{preamble}
 
@@
 
-\input{sections/abstract}
-\input{sections/title}
+\begin{abstract}
+Magic states are essential for achieving universality in fault-tolerant schemes.
+Magic resource theories attempt to quantify magic via monotones and thus describe the manipulation of magic states.
+Here we introduce the concept of majorization fragments as a more generalised projection of such theories in discrete odd dimensions which allows for more powerful results than what monotones can provide.
+Fragments naturally link the symmetries of a gate sequence with conditions on the convertibility between states.
+We demonstrate the power of fragments by providing exact conditions for the convertibility of single-copy qutrit magic states as well as stricter distillation bounds than the established mana monotone in any odd dimension.
+\end{abstract}
+
+\input{title}
 \maketitle
 
-\input{sections/introduction}
-\newpage
-\input{sections/magic/magic}
-\input{sections/magic/phasespace}
-\input{sections/major/major}
-\newpage
-\input{sections/distill/distill}
-\input{sections/conclusion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\bibliography{bib/magic_bib}
-\bibliographystyle{bib/apsrev4-2}
+\section{Introduction}
+\label{sec:intro}
+
+\begin{enumerate}
+    \item Fault-tolerance~\cite{cit:raussendorf, cit:gross2, cit:markov, cit:gross, cit:nest, cit:nest2, cit:vidal, cit:fujii, cit:gottesman}
+    \item Magic~\cite{cit:veitch, cit:veitch2, cit:wang, cit:wang2, cit:howard, cit:campbell, cit:gross3, cit:gross4}
+    \item Bringing in majorization~\cite{cit:cwiklinski, cit:lostaglio2, cit:lostaglio, cit:gour, cit:janzing, cit:brandao2, cit:gour2, cit:marshall, cit:nielsen}
+    \item Section breakdown
+\end{enumerate}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Magic Resource Theories}
+\label{sec:magic}
+
+\subsection{Introduction}
+
+Magic states are necessary for achieving universal quantum computation within fault-tolerant schemes.
+Identifying magic as a resource for quantum universality has led to several theories which try to provide a framework for its quantification and manipulation \nick{CITE}.
+The main question that such a theory attempts to answer is:
+\begin{center}
+    \emph{Given two magic states $\rho$ and $\rho'$ is there a free operation that can convert $\rho$ to $\rho'$?}
+\end{center}
+
+We are interested in all resource theories of magic $\R = (\F, \O)$ in which free operations cannot generate any amount of resource. 
+Further denote by $\D$ the set of states considered under the theory, that is the union of free and resource states.
+The structure of such theory is described by a partial order \nick{CITE}, hereinafter called a \emph{pre-order}, $\prec_{\R}$ between states.
+We write $\rho' \prec_{\R} \rho$ iff there exists $\E \in \O$ such that $\E(\rho) = \rho'$.
+Naturally, states may be incomparable under the given theory, meaning that there exists no free operation that converts one to the other.
+We further call $\R' = (\F', \O')$ a \emph{subtheory} of $\R$ iff $\F' \subseteq \F$ and $\O' \subseteq \O$. 
+The above notation will be used for general resource theories as well.
+
+Formally, the no resource generation condition on the theories translates into two assumptions:
+\begin{enumerate}[I]
+    \item Free operations send free states into free states, $\E: \F \mapsto \F$, for all $\E \in \O$;
+    \item Resource theory $\R$ is a completely free state preserving theory, in the sense that for any $d$-dimensional ancilla system and all free operations $\E$, $(\id_d \otimes \E ) \sigma \in \F$ whenever $\sigma \in \F$.
+\end{enumerate}
+The first assumption simply states that resources cannot be generated for free and is a minimal requirement for a resource theory. 
+An immediate consequence is that if statistical mixing is included in $\O$, then the resource theory is convex.
+Convex resource theories have attracted a lot of attention recently \nick{CITE} and include the magic theories discussed in~\cref{sec:prev}.
+The second assumption implies that resources cannot be generated even when ancillas are allowed \nick{example of T state generation on Bell state by Campbell}.
+
+Monotones are often used \nick{CITE} to address the question of state convertibility, although such approaches are usually generic.
+A monotone of any general resource theory is a projection of the theory onto the non-negative real numbers, collapsing the pre-order of the theory to the total order defined on the real line.
+This is the \nick{most naive} non-trivial projection under which the images of incomparable states can be compared.
+Our first contribution is the introduction of a generalised notion of \emph{resource projection} which maps a general resource theory onto a subtheory which in principle still retains a partial structure.
+Applying this notion on existing magic theories highlights the hidden stochasticity that governs magic state conversions.
+We show that a magic theory can be subdivided into \emph{fragments} \nick{expand}
+
+\subsection{Previous work}\label{sec:prev}
+
+The stabilizer theory \nick{CITE} is the first theory to introduce the idea of magic and it is discussed in sufficient detail for our purposes in~\cref{sec:so}. 
+It comprises of the so-called ``stabilizer'' states ($\stab$) and operations ($\so$), while non-stabilizer (resource) states are called magic.
+The stabilizer operations can be expressed in terms of a Stinespring dilation as 
+\begin{equation}
+    \E(\rho) = \tr_E [U(\rho \otimes \sigma_E)U^\dagger],
+\end{equation} 
+for an ancilla stabilizer state $\sigma_E$. 
+The motivation of the theory stems from the fact that stabilizer operations are experimentally straightforward to implement and they can be used to detect and correct errors on the stabilizer states due to their construction \nick{CITE}.
+The Gottesman-Knill theorem however indicates that stabilizer operations need to be supplemented with magic states in order to achieve universality, justifying the term ``magic''.
+
+Generalisations of the stabilizer theory appear in the literature intending to include broader classes of operations \nick{CITE}.
+The class of stabilizer preserving operations ($\spo$) is defined as the set of $\cptp$ maps that send stabilizer states into stabilizer states~\cite{cit:ahmadi}.
+An important subclass of $\spo$ is the set of completely stabilizer preserving operations ($\cspo$), which intuitively cannot induce ``non-stabilizerness'' even when applied to only part of a quantum state, i.e.
+operations $\E$ such that $(\id_d \otimes \E ) \sigma \in \stab$ for all positive dimensions $d$ whenever $\sigma \in \stab$.
+
+Even though non-stabilizerness is a necessary resource for universality, it has been proven insufficient for magic state distillation~\cite{cit:bravyi, cit:campbell}.
+In fact, all states with non-negative Wigner distributions have been proven to be efficiently classically simulable in~\cite{cit:mari}, a result that serves as a generalization of the Gottesman-Knill theorem.
+The Wigner distribution of a state in odd prime dimensions is discussed rigorously in~\cref{sec:wigner} and arises as the unique quasi-probability representation of quantum theory that identifies non-contextuality exactly with the states that are efficiently classically simulable~\cite{cit:howard2, cit:veitch2}.
+In this framework, the stabilizer states are the only pure states represented with non-negative distributions~\cite{cit:gross3}. 
+However, there exist mixed states with non-negative Wigner distributions that are not mixtures of stabilizer states~\cite{cit:gross}.
+Therefore, stabilizer-preserving theories have been extended to a theory that preserves state ``Wigner positivity''~\cite{cit:wang}, formally defined in~\cref{sec:wigner} for odd prime dimensions.
+Informally, it can be considered as the maximal theory of magic $\Rmax = (\Fmax, \Omax)$, where free states have non-negative Wigner distributions and free operations completely preserve this property.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Phase Space formalism}
+\label{sec:ps}
+
+\subsection{Stabilizer Theory}\label{sec:so}
+
+Let $\{\ket{k}\}_{k \in \zd}$ be the standard computational basis for an arbitrary fault-tolerant scheme, defined over the finite field $\zd = \{ 0, 1, \dots,d-1 \}$, with $d$ an odd prime. 
+Since the field has character $d$, addition and multiplication on the field are always considered modulo $d$.
+The Hilbert space of any system associated with this scheme is $\hd \coloneqq \spanv{\ket{k}: k \in \zd}$.
+
+The generalised Pauli matrices $X, Z$ can be defined by their respective roles as shift and phase operators,
+\begin{align}
+    X \ket{k} &= \ket{k + 1} \label{eq:xpauli}\\
+	Z \ket{k} &= \omega^k \ket{k}, \label{eq:zpauli}
+\end{align}
+where $\omega \coloneqq e^{2\pi i/d}$ is the $d$-th root of unity.
+
+The Hilbert space $\hd$ is associated with a phase space $\pd \coloneqq \zd \times \zd$, where every point $\bmx \coloneqq (x_0, x_1)$ corresponds to a displacement operator, defined as
+\begin{equation}\label{eq:ddef}
+    D_{\bmx} \coloneqq \tau^{x_0 x_1} X^{x_0} Z^{x_1},\ \bmx  \in \pd.
+\end{equation}
+The phase factor $\tau \coloneqq -\omega^{1/2}$ ensures unitarity.
+For a system with composite Hilbert space, $\hd = \hd[d_A] \otimes \hd[d_B]$, the displacement operators are defined as
+\begin{equation}\label{eq:composited}
+    D_{\bmx_A \oplus \bmx_B} \coloneqq D_{\bmx_A} \otimes D_{\bmx_B},
+\end{equation}
+where $\bmx_A \oplus \bmx_B \coloneqq (x_{A0}, x_{B0}, x_{A1}, x_{B1}) \in \pd[d_A] \times \pd[d_B]$.
+
+The displacement operators, form a group under matrix multiplication modulo phases,
+\begin{equation}\label{eq:gp}
+    \gp \coloneqq \{ \tau^k D_{\bmz}: k \in \zd, \bmz \in \pd\}.
+\end{equation}
+The Clifford unitaries $\cd$ can then be defined as the normaliser of this group, \nick{Reformulate for copies of qudits: $\gp,\ \cd \rightarrow \gp^n,\ \cd^n$. $C-SUM$s live in $\cd^2$}
+\begin{equation}
+    \cd \coloneqq \{ U \in {\rm{SU}}(d): U\gp U^\dagger = \gp \}.
+\end{equation}
+The pure stabilizer states are then the orbit of the Clifford unitaries over a computational basis state,
+\begin{equation}\label{eq:stab}
+    \stab_{{\rm{pure}}} \coloneqq \{ U\ketbra{0}{0}U^\dagger: U \in \cd \}.
+\end{equation}
+
+The free states of the stabilizer theory are mixtures of pure stabilizers, 
+\begin{equation}
+    \stab = \conv\ \stab_{{\rm{pure}}}.
+\end{equation}
+The free operations of the stabilizer theory is the set of stabilizer operations $\so$ defined as any composition of:
+\begin{enumerate}
+    \item Preparation in computational basis;
+    \item Random Clifford unitaries $\rcu$, i.e. operations $\E$ such that 
+    \begin{equation}
+        \E(\rho) = \sum_i p_i U_i \rho U_i^\dagger,\ U_i \in \cd;
+\end{equation}
+    \item Measurement in computational basis.
+\end{enumerate}
+
+\subsection{Wigner Distribution}\label{sec:wigner}
+
+We can define the phase-point operators,
+\begin{align}
+	A_{\bmx} \coloneqq \frac{1}{d} \sum_{\bmz \in \pd} \omega^{\bmx \wedge \bmz} D_{\bmz},\ \bmx \in \pd. \label{eq:ax}
+\end{align}
+\nick{$\wedge$ has not be defined} They form an orthogonal Hermitian operator basis.
+Therefore, any quantum state $\rho \in \cal{B}(\hd)$ can be expressed as a linear combination of the phase-point operators,
+\begin{equation}
+    \rho = \sum_{\bmz \in \pd} \W[\bmz]{\rho} A_{\bmz},
+\end{equation}
+where the coefficient vector $\W{\rho}$ is the Wigner distribution of state $\rho$,
+\begin{equation}\label{eq:wstate}
+    \W[\bmx]{\rho} \coloneqq \frac{1}{d}\tr[A_{\bmx} \rho].
+\end{equation}
+It is in fact a real, bounded, $d^2$-dimensional quasi-probability distribution over $\pd$ as shown in~\cref{app:wigner}.
+
+The Wigner distributions of different types of qutrit states are illustrated in~\cref{fig:wstate_examples}.
+\begin{figure}%
+    \centering
+    \subfigure[][]{%
+    \label{fig:maxmix}%
+    \includegraphics[height=2cm]{figs/maxmixed.pdf}
+    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
+    }\hspace{8pt}%
+    \subfigure[][]{%
+    \label{fig:zero}%
+    \includegraphics[height=2cm]{figs/zerostate.pdf}
+    %\caption{Zero state $\ketbra{0}{0}$}%
+    }\\
+    \subfigure[][]{%
+    \label{fig:bound}%
+    \includegraphics[height=2cm]{figs/boundstate.pdf}
+    %\caption{Bound state}%
+    }\hspace{8pt}%
+    \subfigure[][]{%
+    \label{fig:strange}%
+    \includegraphics[height=2cm]{figs/strangestate.pdf}
+    %\caption{Strange state $\ketbra{S}{S}$}%
+    }
+    \caption{Wigner distributions for qutrit states of varying magic. 
+    \subref{fig:maxmix} Maximally mixed state $\frac{1}{3}\id$; \subref{fig:zero} Stabilizer zero state $\ketbra{0}{0}$; \subref{fig:bound} A non-stabilizer Wigner-positive state; \subref{fig:strange} Magic strange state $\ket{{\rm{S}}} = \frac{1}{\sqrt{2}}(\ket{1} - \ket{2})$.
+    \nick{Explain what a magic / bound magic state is in intro}
+    }%
+    \label{fig:wstate_examples}
+\end{figure}
+
+We can exploit the channel-state duality and use the normalised Choi-Jamio\l{}kowski state 
+\begin{equation}\label{eq:cj}
+    \frac{1}{d_A}\J_\E \coloneqq \frac{1}{d_A}(\id \otimes \E) \sum_{i,j} \ket{ii}\bra{jj}
+\end{equation}
+to extend the definition of the Wigner distribution to quantum $\cptp$ operations $\E: \cal{B}(\hd[d_A]) \mapsto \cal{B}(\hd[d_B])$, 
+\begin{align}\label{eq:woperation}
+    \W[\bmy|\bmx]{\E} 
+    &\coloneqq d_A^2 \W[\bm{\bar x} \oplus \bmy]{\frac{1}{d_A}\J_\E} \\
+    &= \frac{1}{d_B} \tr_B[A_{\bmy} \E(A_{\bmx})],
+\end{align}
+where $\bm{\bar x} \coloneqq (x_0, -x_1)$.
+
+The specific form of~\cref{eq:woperation} is chosen so that Wigner distributions of operations act as transition matrices for Wigner distributions of states, $\W{\E(\rho)} = \W{\E}\W{\rho}$.
+In particular, $\cptp$ operations that map between density operators of equal dimensions and have non-negative Wigner distributions correspond to stochastic matrices, as shown in~\cref{app:wigner}
+
+The single-qudit Hadamard gate $H$ and phase gate $S$ generate the $d$-dimensional Clifford group $\cd$. \nick{CITE}
+Their Wigner distributions are given by permutation matrices,
+\begin{align}
+    H &\coloneqq \frac{1}{\sqrt{d}}\sum_{j,k} \omega^{jk} \ketbra{j}{k}, \W[\bmy|\bmx]{H} = \delta_{y_0, -x_1}\delta_{y_1, x_0};\label{eq:H}\\
+    S &\coloneqq \sum_k \tau^{k(k+1)} \ketbra{k}{k}, \W[\bmy|\bmx]{S} = \delta_{y_0, x_0}\delta_{y_1, x_0 + x_1 + 2^{-1}}.\label{eq:S}
+\end{align}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Stochastic structure of magic theories}
+\label{sec:struc}
+
+\subsection{Magic fragments}\label{sec:magfrag}
+
+Equipped with the definitions of the Wigner distribution in odd prime dimensions, we can formally recast the maximal magic theory $\Rmax$ into a stochasticity setting.
+The free states correspond to proper probability distributions 
+\begin{equation}
+    \Fmax \coloneqq \{ \rho: \W[\bmz]{\rho} \geq 0 \text{ for all } \bmz \in \pd\}
+\end{equation}
+
+The free operations should send the set of free states $\Fmax$ into itself and completely preserve the non-negativity of the states, in the sense that $\E \in \Omax$ iff $(\id_d \otimes \E ) \sigma \in \stab$ for all odd prime dimensions $d$ whenever $\sigma \in \Fmax$.
+It is shown by Wang \textit{et al.}~\cite{cit:wang} that $\Omax$ coincides with the set of operations $\E$ that correspond to stochastic Wigner distributions, 
+\begin{equation}
+    \Omax = \{ \E: \W[\bmy|\bmx]{\E} \geq 0 \text{ for all } \bmx, \bmy \in \pd\}.
+\end{equation}
+
+Any magic theory $\R = (\F, \O)$ is a subtheory of $\Rmax$ as explained in~\cref{sec:intro}, and as such it falls under this new stochasticity setting. 
+This observation gives rise to the idea of subdividing magic theories into ``chunks'' identified by the invariance of a particular state under stochastic processes. \nick{explain better}
+\begin{definition}[\textbf{$\boldsymbol\sigma$-fragment}]\label{def:sigmafrag}
+    A subtheory $\R'$ of a magic theory $\R = (\F, \O)$ is called a \emph{$\sigma$-fragment} of $\R$ iff $\R' = (\F, \O_\sigma)$, where the free operations are restricted to the ones that leave $\sigma$ invariant,
+    \begin{equation}
+        \O_\sigma \coloneqq \{ \E \in \O: \E(\sigma) = \sigma \}.
+    \end{equation}
+\end{definition}
+
+State $\sigma$ is thus a fixed point of all operations in $\O_\sigma$. 
+We now show that every free operation has a fixed point, so that the theory $\R$ can be entirely subdivided into $\sigma$-fragments.
+
+\begin{theorem}
+    Let $\R = (\F, \O)$ be a theory of magic.
+    Every free operation leaves at least one free state invariant such that $\O = \bigcup\limits_{\sigma \in \F} \O_\sigma$.
+\end{theorem}
+\begin{proof}
+    Suppose $\E$ is in $\O_\sigma$, then it is also in $\O$, hence $\bigcup\limits_{\sigma \in \F} \O_\sigma \subseteq \O$.
+
+    Conversely, suppose $\E$ is in $\O$. 
+    The free states are mapped one-to-one to a subset $\cal{S}$ of the $(d^2 - 1)$-dimensional probability simplex.
+    $\cal{S}$ is convex, since any combination of free states is also free and the Wigner distribution is linear.
+    Therefore, $\cal{S}$ is convex and compact as a convex subset of the bounded compact probability simplex. \nick{Need to prove that $\cal{S}$ is closed.}
+    Then, $\W{\E}{}$ is a stochastic, thus continuous, mapping from $\cal{S}$ to itself and Brouwer's fixed point theorem \nick{CITE} implies that there exists a probability distribution $g_{\bmz}, \bmz \in \pd$ that is preserved by $\W{\E}{}$.
+    This corresponds one-to-one to a state $\sigma \coloneqq \sum_{\bmz \in \pd} g_{\bmz} A_{\bmz}$ and so $\O \subseteq \bigcup\limits_{\sigma \in \F} \O_\sigma$.
+\end{proof}
+Therefore, identifying an invariance in the setup helps in determining whether a state conversion $\rho \xrightarrow{\E \in \O} \tau$ is possible. 
+If state $\sigma$ is left invariant by an operational sequence, then the total operation $\E$ that converts $\rho$ to $\tau$ lies in $\O_\sigma$. \nick{expand}
+
+The zoo of all magic operation classes is summarised in ~\cref{fig:zoo}.
+Completely positive-Wigner-preserving operations~\cite{cit:wang} form the operation class $\Omax$.
+Therefore, $\sigma$-fragments cover this theory of magic exactly and any magic subtheory is contained within this cover.
+In particular, the stabilizer operations $\so$ are contained within $\Omax$.
+\begin{figure}[t]
+    \centering
+        \includegraphics[scale=0.47
+        ]{figs/operations.pdf}
+    \caption{Zoo of allowed operations for magic resource theories.
+    Established theories involve operations within the yellow regions, following the hierarchy $\so \subset \cspo \subset \spo \subset \Omax$.
+    We introduce fragments $\O_\sigma,\ \sigma \in \F$ that cover $\Omax$ with each one extending to a set of stochastic maps that allows for $\bmd$-majorization to be used.
+    }
+    \label{fig:zoo}
+\end{figure}
+
+The subdivision of magic theories into $\sigma$-fragments is powerful because the pre-order $\prec_{\R'}$ of every $\sigma$-fragment is described by well-behaved majorization tools, as we establish in~\cref{sec:major}.
+\nick{expand}
+
+\subsection{Majorization}\label{sec:major}
+
+Majorization is a powerful tool that has recently found many applications in quantum information theory \nick{CITE}.
+It can describes the \nick{disorder / non-uniformity} of distributions that undergo stochastic transformations.
+
+To formally state majorization results, we first denote by $\stoch$ the set of $(d \times d)$ stochastic matrices that preserve the probability vector $\bmd$.
+\nick{Should we introduce notation directly in the magic setting?}
+Specifically, for any $S \in \stoch$, all matrix elements are non-negative, all rows sum to $1$ and $S\bmd = \bmd$.
+\iffalse
+\begin{enumerate}
+    \item $S_{ij} \geq 0$ for all $i, j \in \zd$;
+    \item $\sum\limits_{j=1}^n S_{ij} = 1$ for all $i \in \zd$;
+    \item $S\bmd = \bmd$.
+\end{enumerate}
+\fi
+The set $\stoch$ forms a group under matrix multiplication for all $\bmd$ with positive components.
+
+Majorization finds an important application on quantum thermodynamics in the absence of coherence.
+The use of majorization in this setting provides useful intuition for our purposes.
+At any given temperature $\beta$, the thermal state $\gamma_\beta$ is thermodynamically the most ordered state. 
+Thermal operations are defined as operations that cannot extract energy from the Gibbs state, $\E(\gamma_\beta) = \gamma_\beta$.
+Convertibility between states via thermal operations is equivalent to a stochasticity condition on the energy level populations of the states \nick{CITE}.
+Roughly, the statement is that there exists a thermal operation $\E$ such that $\tau = \E(\rho)$ if and only if there exists a a matrix $S \in \stoch$ such that $\bm{q} = S\bm{p}$, where $\bm{q}, \bm{p}$ and $\bmd$ and the energy level population vectors of $\tau, \rho, \gamma_\beta$ respectively.
+
+Drawing intuition from this setting, we can define majorization as follows.
+\begin{definition}[\textbf{$\boldsymbol\bmd$-majorization}]\label{def:dmajor}
+    Given $\bmx, \bmy, \bmd \in \reals^d$, such that the components of $\bmd$ are positive, $\bmy$ is said to $\bmd$-majorize $\bmx$, iff there exists a matrix $S \in \stoch$ such that $\bmx = S\bmy$.
+\end{definition}
+We denote this pre-order by $\bmx \prec_{\bmd} \bmy$.
+If $\bmd = \frac{1}{d}\bm{1}$, the $d$-dimensional uniform distribution, then $\stoch$ is the set of doubly stochastic matrices and we retrieve the familiar notion of majorization in entanglement theory.
+\nick{CITE}
+
+\nick{We need to address the non-full-rankness of states.\\
+For example, the operation $\E(\rho) = \ketbra{0}$ corresponds to no $\sigma$-fragment because components of $\W{\sigma}$ are zero.\\
+In such a case we can always add some $\epsilon$ amount of unital noise by mixing $\sigma$ with the maximally mixed state $\frac{1}{d}\id$. 
+This ensures that all components are strictly positive and $\bmd$-majorization can be used.
+There are non-full-rank states with no zeros in W.}
+
+The pre-order $\prec_{\R'}$ of the $\sigma$-fragment $\R' = (\F, \O_\sigma)$ between $d$-dimensional states corresponds to the majorization pre-order $\prec_{\W{\sigma}}$ between their $d^2$-dimensional Wigner distributions.
+
+\begin{theorem}
+    Let $\R = (\F, \O)$ be a theory of magic.
+    Suppose the state conversion $\rho \xrightarrow{\E \in \O} \tau$ is possible, $\tau \prec_\R \rho$.
+    Then, there exists a full-rank free state $\sigma \in \F$ such that  $\W{\tau} \prec_{\W{\sigma}} \W{\rho}$.
+\end{theorem}
+\begin{proof}
+    Suppose there exists $\E \in \O$ such that $\E(\rho) = \tau$.
+    The free operation belongs to a $\sigma$-fragment, $\E \in \O_\sigma$, for some $\sigma \in \F$.
+    Then, $\W{\E}\W{\rho} = \W{\tau}$ with $\W{\E} \in \stochw$, or, equivalently, $\W{\tau} \prec_{\W{\sigma}} \W{\rho}$.
+\end{proof}
+
+A visual representation of $\bmd$-majorization is provided by Lorenz curves.
+Let the vector $\bmz^\downarrow$ denote a component permutation of vector $\bmz \in \reals^d$, so that its components are arranged in non-increasing order.
+\begin{definition}[\textbf{Lorenz curve}]
+    Let $\bmz \in \reals^d$.
+    Let $\bmd \in \reals^d$ be a vector with positive components, $\pi$ a permutation mapping $(z_i/d_i) \mapsto (z_i/d_i)^\downarrow$ for all $i=1,\dots,d$ and $D = \sum_{i=1}^d d_i$.
+    The Lorenz curve $L(\bmz|\bmd)$ of vector $\bmz$ is the piecewise linear curve obtained by joining the points $\{ (x_k, L_k(\bmz|\bmd)) \}_{k=1,\dots,d}$, where
+    \begin{equation}\label{eq:lorenz}
+        (x_k, L_k(\bmz|\bmd)) \coloneqq \left( \frac{1}{D}\sum_{i=1}^k d_{\pi(i)}, \sum_{i=1}^k z_{\pi(i)} \right) \in \mathbb{R}^2.
+    \end{equation}
+\end{definition}
+\emph{Remark 1.} The origin $(x_0, L_0(\bmz|\bmd)) \coloneqq (0,0)$ is usually included in the curve.
+
+\emph{Remark 2.} Components $x_k$ are rescaled by $D$ so that comparison of curves with unequal dimensions is possible.
+In fact, the Lorenz curves $L(\bmz|\bmd)$ and $L(\bmz \otimes \bmd|\bmd \otimes \bmd)$, where $\otimes$ denotes the Kronecker product, are identical.
+
+\emph{Remark 3.} Lorenz curves are always concave.
+
+\emph{Remark 4.} If $L_d(\bmz|\bmd) = 1$ and for all $k$, $L_k(\bmz|\bmd) \leq 1$, then $\bmz$ is a probability distribution.
+Lorenz curves of quasi-probability distributions in principle reach above 1.
+
+A vector $\bmy$ $\bmd$-majorizes another vector $\bmx$  if and only if Lorenz curve $L(\bmy|\bmd)$ lies above Lorenz curve $L(\bmx|\bmd)$.
+\begin{theorem}\label{thm:dmajor}
+    Let $\bmx, \bmy, \bmd \in \reals^d$, such that the components of $\bmd$ are positive. 
+    Then, $\bmx \prec_{\bmd} \bmy$ if and only if $L_k(\bmx|\bmd) \leq L_k(\bmy|\bmd)$ for all $k=1,2,\dots, d-1$ and $L_d(\bmx|\bmd) = L_d(\bmy|\bmd)$.
+\end{theorem}
+A restatement of the theorem including more equivalent conditions, along with a proof is provided in the \nick{appendix}.
+
+An example of comparison between different Lorenz curves is illustrated in~\cref{fig:lctoy}.
+\begin{figure}
+    \centering
+    \includegraphics[height=5cm]{figs/lctoy.pdf}
+    \caption{Example of different Lorenz curves for quasi-probability vectors under $\bmd$-majorization.
+    Vectors $\bmy$ and $\bmd$ are simply probability distributions.
+    The curve corresponding to vector $\bmd$ is always the line segment connecting $(0,0)$ and $(1,1)$, so that any other Lorenz curve lies above it, for example $\bmx \prec_{\bmd} \bmd$.
+    Curves $L_k(\bmx|\bmd)$ and $L_k(\bmy|\bmd)$ intersect, so $\bmx \nprec_{\bmd} \bmy$ as well as $\bmy \nprec_{\bmd} \bmx$.
+    \nick{Recast in terms of magic}
+    }
+    \label{fig:lctoy}
+\end{figure}
+
+\subsection{Set theoretic properties of magic fragments}\label{sec:propmagfrag}
+
+\nick{May move statements around the section or in an appendix.}
+
+\begin{theorem}\label{thm:frag}
+    Let $\R = (\O, \F)$ be a magic theory. 
+    The following statements hold:
+    \begin{enumerate}
+        \item No $\sigma$-fragment is empty.
+        \item If a free operation leaves two states invariant, then it also leaves their mixtures invariant, 
+        \begin{equation}
+            \O_{\sigma} \cap \O_{\sigma'} \subseteq \O_{p\sigma + (1-p)\sigma'}\ \text{for all}\ p \in [0,1].
+        \end{equation}
+        \item Let $\E$ be a $\cptp$ operation with Wigner distribution $\W{\E}$.
+        For $\R = \Rmax$ $\E \in \O_\sigma$ iff $\W{\E} \in \stochw$.
+    \end{enumerate}
+\end{theorem}
+\begin{proof}$ $\\
+
+    \begin{enumerate}
+    \item Consider the completely depolarising \nick{replacement} map
+    \begin{align}
+        \E(\rho) &= \sigma \tr[\rho],\ \text{with} \\
+        \W[\bmy|\bmx]{\E} &= \W[\bmy]{\sigma} \tr[\rho],
+    \end{align}
+    where $\sigma \in \F$. 
+    Then, $\E \in \O_\sigma$.
+    It can be thought as a sequence of tracing out state $\rho$ and preparing the free state $\sigma$.
+
+    \item Let $\E \in \O_{\sigma} \cap \O_{\sigma'}$.
+    Then $\E \in \cptp$ and corresponds to stochastic Wigner distribution $\W{\E}$ such that $\W{\E} \W{\sigma} = \W{\sigma}$ and $\W{\E} \W{\sigma'} = \W{\sigma'}$.
+    Then, $\W{\E} \W{p\sigma + (1-p)\sigma'} = \W{p\sigma + (1-p)\sigma'}$ for any $p \in [0,1]$ due to the additive property~\ref{en:w4} of the Wigner distribution, implying that state $p\sigma + (1-p)\sigma'$ is also left invariant by $\E$.
+
+    \item Let $\O_\sigma' \coloneqq \{ \E \in \cptp: \W{\E} \in \stochw \}$ be the described set of operations.
+
+    Suppose $\E$ is in $\O_\sigma$, then $\E \in \cptp$ and $\W{\E} \in \stochw$ due to property~\ref{en:wo4} of~\cref{thm:wchannel}, hence $\O_\sigma \subseteq \O_\sigma'$.
+
+    Conversely, suppose $\E \in \cptp$ with $\W{\E} \in \stochw$. 
+    Then, $\W[\bmy|\bmx]{\E} \geq 0$ for all $\bmx, \bmy$, hence $\E \in \O$.
+    Furthermore, $\W{\E} \W{\sigma} = \W{\sigma}$ implies $\E(\sigma) = \sigma$ using~\cref{eq:woperation} defined for any $\cptp$ operation $\E$.
+    Hence, $\O_\sigma' \subseteq \O_\sigma$.
+    \end{enumerate}
+\end{proof}
+
+Any free state $\sigma \in \cal{B}(\hd)$ corresponds to a $d^2$-dimensional probability distribution $\W{\sigma}$ and any free operation $\E: \cal{B}(\hd) \mapsto \cal{B}(\hd)$ corresponds to a $d^2 \times d^2$ stochastic matrix (or conditional probability distribution) $\W{\E}$.
+Note that these mappings are one-to-one due to the orthogonality of the phase-point operators as an operator basis.
+
+\emph{Remark 1.} Note that free states $\F$ are mapped onto a \emph{strict subset} of the set of probability distributions.
+As a counterexample, the sharp $d^2$-dimensional probability distribution $(1, 0, \dots, 0)$ does not correspond to any qudit Wigner distribution because of the boundedness condition~\ref{en:w3} in~\cref{thm:wstate}.
+
+\emph{Remark 2.} Similarly, not all stochastic matrices correspond to completely positive operations.
+
+As an example, consider the permutation matrix
+\begin{equation}
+    \Pi_X = \begin{psmallmatrix}
+        0 & 1 & 0 & 0 & 0 \\
+        0 & 0 & 0 & 0 & 1 \\
+        0 & 0 & 0 & 1 & 0 \\
+        1 & 0 & 0 & 0 & 0 \\
+        0 & 0 & 1 & 0 & 0
+    \end{psmallmatrix} \otimes \begin{psmallmatrix}
+        0 & 0 & 1 & 0 & 0 \\
+        0 & 0 & 0 & 0 & 1 \\
+        0 & 0 & 0 & 1 & 0 \\
+        1 & 0 & 0 & 0 & 0 \\
+        0 & 1 & 0 & 0 & 0    
+    \end{psmallmatrix} \in \stochw,\ d=5.
+\end{equation}
+It preserves the uniform distribution $\W{\frac{1}{5}\id}{}$, but it does not correspond to any $\cpos$ operation, hence any $\E \in \O$ due to~\cref{thm:frag}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{General resource fragments}
+\label{sec:frag}
+
+State convertibility within a given resource theory is often a hard question to address due to the intricate structure of the theory.
+In general, the structure of a theory $\R$ is described by a pre-order $\prec_\R$ \nick{expand / move to intro}.
+Subdividing magic theories into $\sigma$-fragments \nick{helps}.
+\subsection{Monotones}\label{sec:mono}
+
+Resource theories are commonly equipped with monotones which quantify the resource\nick{CITE}. 
+\begin{definition}[\textbf{Resource monotone}]\label{def:mono}
+    Let $\R = (\F, \O)$ be a general resource theory.
+    A monotone $\M$ is a projection from the set of all states of the theory to the real line, satisfying two conditions:
+    \begin{enumerate}
+        \item All free states are mapped onto 0, $\M(\sigma) = 0,\ \sigma \in \F$;
+        \item $\M$ is monotonically decreasing under free operations, $\M(\rho_1) \leq \M(\rho_2)$ whenever $\rho_1 \prec_{\R} \rho_2$.
+    \end{enumerate}
+\end{definition}
+The first condition reflects the property that all free states can be converted into each other, hence they need to be mapped onto the same number, by convention 0.
+The second condition reflects the no resource generating property of free operations, thus monotones respect the pre-order $\prec_\R$ of the theory.
+Furthermore, if a monotone satisfies the additivity condition,
+\begin{equation}
+    \M(\rho_1 \otimes \rho_2) = \M(\rho_1) + \M(\rho_2),
+\end{equation}
+it is of practical importance for resource distillation, which we discuss in~\cref{sec:distill} within the context of magic.
+
+A very commonly used magic monotone is the \emph{mana} of a state \nick{CITE}, defined as
+\begin{equation}
+    \mana{\rho} \coloneqq \log{\left(\sum\limits_{\bmz \in \pd} \abs{\W[\bmz]{\rho}}\right)}.
+\end{equation}
+It is a monotone, additive function of the $\ell_1$-norm of negativity~\nick{CITE}.
+
+\subsection{Fragments}
+
+Monotones reduce the structure of the resource theory $\R$ into a real number ordering.
+Therefore, two states, even if incomparable in $\R$, are always mapped onto ordered real numbers.
+This is a generic approach that ensures a form of state comparison and resource quantification.
+However, motivated by $\sigma$-fragments in magic theories, it is clear that we can often reduce the theory by a less \nick{information-collapsing} projection into a subtheory $\R'$ which has a tractable pre-order $\R'$, as sketched in~\cref{fig:fragments}.
+\begin{figure}[t]
+    \centering
+    \includegraphics[height=3cm]{figs/fragments.pdf}
+    \caption{Fragments \nick{Split into subfigures}
+    }
+    \label{fig:fragments}
+\end{figure}
+We define such a resource projection for general resource theories as follows.
+\begin{definition}[\textbf{Resource projection}]\label{def:fragment}
+    Let a resource theory $\R = (\F, \O)$ have pre-order $\prec_{\R}$ and operational composition rule $\circ_{\R}$. 
+    Any subtheory $\R' = (\F', \O')$ with pre-order $\prec_{\R'}$ and operational composition rule $\circ_{\R'}$ is called a resource fragment iff there exists a surjective projection $\Pi \equiv (\Pis, \Pio): \R \mapsto \R'$ that satisfies the following two conditions.
+    \begin{enumerate}
+        \item $\Pis: \D \mapsto \D$ and $\Pis(\rho_2) \nprec_{\R'} \Pis(\rho_1)$ whenever $\rho_1 \prec_{\R} \rho_2$;
+        \item $\Pio: \O \mapsto \O'$ and $\Pio(\E_1) \circ_{\R'} \Pio(\E_2) = \Pio(\E_1 \circ_{\R} \E_2)$ for all free operations $\E_1, \E_2 \in \O$.
+    \end{enumerate}
+    We call $\Pi$ a resource projection.
+\end{definition}
+Fragment $\R'$ is the image of the projection $\Pi$.
+Considering a resource projection is particularly useful when the pre-order of the fragment is tractable.
+Note the subtle difference of condition 1 in~\cref{def:fragment} and condition 2 in~\cref{def:mono}, which is due to fragments generally retaining a pre-order, while monotones impose a total order.
+
+A monotone is the projection with the simplest tractable order as formally stated in~\cref{thm:monofrag}.
+\begin{proposition}\label{thm:monofrag}
+	Let $\M$ be a resource monotone of a resource theory $\R$. 
+	Then $\M$ is a resource projection that reduces the pre-order $\prec_\R$ to a total order.
+\end{proposition}
+\begin{proof}
+	Consider a monotone $\M$ in the context of a general resource theory $\R = (\F, \O)$.
+	Let $\R' = (\F', \O')$, where $\F' \equiv \{0\}$ and $\O'$ is the set of non-increasing real functions mapping the set of non-negative real numbers $\mathbb{R}_{\geq 0}$ to itself. 
+	We also set $\prec_{\R'}$ as the usual total order $\leq$ and $\circ_{\R'}$ as the composition of real functions.
+
+	Let $\Pis = \M$.
+	The defining properties of a monotone, given in~\cref{def:mono}, ensure condition 1 of~\cref{def:fragment}. \nick{expand}
+
+	Let $\Pio$ project any $\E \in \O$ onto a function $f \in \O$ which maps $\M(\rho)$ onto $\M(\E(\rho))$ for all states $\rho$.
+
+	The ordered pair $(\Pis, \Pio)$ is the resource projection which corresponds to monotone $\M$.
+\end{proof}
+
+We now justify the name $\sigma$-fragment for the subdivision of a magic theory $\R = (\F, \O)$, by establishing a resource projection which reduces $\R$ into any subtheory $(\F, \O_\sigma)$.
+\begin{proposition}
+    Let $\R = (\F, \O)$ be a theory of magic.
+    Every $\sigma$-fragment $(\F, \O_\sigma)$ is a resource fragment of $\R$.
+\end{proposition}
+\begin{proof}
+    Let the state projection be the identity projection $\Pis:\D\mapsto\D$.
+
+    Consider the operation projection $\Pio:\O \mapsto \O_\sigma$, defined as
+    \begin{equation}
+    \Pio(\E) =
+    \begin{cases}
+        \E,\ &\sigma \in \O, \\
+        1_{\rm{C}},\ &\sigma \notin \O.
+    \end{cases}
+    \end{equation}
+    \nick{$\Pio$ should be different, this here is not right.
+If we need to project every $\E \in \O$, we may need a different condition on $\Pio$ than $\Pio(\E_1) \circ_{\R'} \Pio(\E_2) = \Pio(\E_1 \circ_{\R} \E_2)$.}
+    The ordered pair $(\Pis, \Pio)$ acts as the desired projection.
+\end{proof}
+
+An important example of a fragment appears in quantum thermodynamics. 
+Consider a projection $\Pi$, such that $\Pis$ dephases all states in the energy eigenbasis, while $\Pio$ maps all free operations to themselves.
+Then $\Pi$ describes the theory in the absence of coherences and the new pre-order is simply thermo-majorization, which in fact is fully solvable in the form of entropic conditions~\cite{cit:gour}.
+\nick{expand/rephrase}
+
+Existing magic theories can be thought of as fragments of $\Rmax$.
+\begin{proposition}
+    Every theory of magic $\R$ is a fragment of the maximal theory $\Rmax$.
+\end{proposition}
+\begin{proof}
+    \nick{We need a state projection that establishes that some free states are not free any more $+$ an operations projection.}
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Distillation bounds}
+\label{sec:distill}
+
+Consider a general magic state distillation process,
+\begin{equation}\label{eq:distprocess}
+    \rho^{\otimes k} \xrightarrow{\E \in \O} \tau,
+\end{equation}
+where $n$ noisy copies of magic state $\rho$ are converted to a single-copy magic state $\tau$.
+Identifying a symmetry of the distillation process responsible for leaving a state $\sigma$ invariant is equivalent with restricting the process to the $\sigma$-fragment $\O_\sigma$.
+
+Mana is monotonic and additive in all $\sigma$-fragments as seen in~\cref{app:major}, so it provides a bound for distillation processes
+\begin{equation}
+    \mana{\rho} \geq \frac{1}{k} \mana{\tau}.
+\end{equation}.
+
+A new bound can be obtained in any $\sigma$-fragment by comparing the Lorenz curves of the initial and target states,
+\begin{equation}\label{eq:majbound}
+    L_k(\rho^{\otimes k} | \sigma) \geq L_k (\tau | \sigma),\ k=1,\dots,d^2,
+\end{equation}
+If the Lorenz curve of the initial state is below the target curve at any point, the process is not possible.
+In general, the Wigner components of a $k$-copy state $\rho^{\otimes k}$ are calculated, along with their multiplicities, by expanding the terms in the multinomial expansion $\left( \sum_{\bm{z} \in \cal{P}_d} W_\rho(\bm{z}) \right)^n$.
+This follows from the multiplicativity of the Wigner distribution.
+
+The Strange state $\ketbra{\rm{S}}$ depicted in~\cref{fig:strange} is the simplest to analyse, since it only has two distinct components $\{ -\frac{1}{3}, \frac{1}{6} \}$, the latter with a multiplicity of 8.
+Calculating the binomial expansion for the components of $\ket{S}\bra{S}^{\otimes k}$ gives $\{(-1)^j 2^{j-k} 3^{-k}\}_{0 \leq j \leq k}$ with multiplicity $8^{k-j} \binom{k}{j}$ for the $j$-th term.
+This allows analytical calculation of all Lorenz curve points, hence the maximum of the $k$-copy state is
+\begin{equation}\label{eq:Skmax}
+    \max_k{L_k \left( \ketbra{S}^{\otimes k} \bigm| \sigma \right)} = 1 + \left(\frac{4}{3}\right)^k \sum\limits_{j: 1 \leq 2j+1 \leq k} 4^{-(2j+1)} \binom{k}{2j+1}.
+\end{equation}
+
+Consider the noisy Strange state,
+\begin{equation}
+    \rho_{\rm{S}}(\epsilon) = (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \sigma,
+\end{equation}
+in the $\sigma$-fragment $\O_\sigma$.
+At noise level $\epsilon \leq \frac{3}{4}$, the Wigner distribution $\W{\rho_{\rm{S}}(\epsilon)}$ contains negativities and the state can be purified so as to obtain a single-copy state with sufficiently low $\epsilon$.
+In~\cref{fig:distill}, we examine the purifying process 
+\begin{equation}\label{eq:purify}
+    \rho_{\rm{S}}^{\otimes k}(\epsilon_{\rm{th}}) \xrightarrow{\E \in \O_\sigma} \rho_{\rm{S}}(0.05),\ \sigma = (1-p)\ketbra{0} + p \frac{1}{3}\id
+\end{equation}
+with $\epsilon_{\rm{th}}$ being the noise level threshold that does not prohibit the process for given number of copies $k$ and $\sigma$-fragment, parametrised by $p$ as a mixture of the zero and the maximally mixed states.
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.5]{figs/ratios.pdf}
+    \caption{Plot of the noise level threshold ratios between mana and Lorenz curve for the Strange state purifying process in~\cref{eq:purify}.
+    The ratios are calculated for different numbers of initial state copies and different $\sigma$-fragments parametrised by $p$ such that $\sigma = (1-p)\ketbra{0} + p \frac{1}{3}\id$.
+    Lorenz curve comparison consistently gives stricter bounds as proven in~\cref{thm:bounds}.
+    \nick{Highlight physics/invariance}
+    }
+    \label{fig:distill}
+\end{figure}
+
+Thresholds provided by Lorenz curve comparison are always much stricter than mana thresholds \nick{threshold/bound? need to define the notion of a bound precisely}.
+In fact, it is clear than this is the case in any general distillation process.
+\begin{theorem}\label{thm:bounds}
+    Consider the distillation process in~\cref{eq:distprocess}.
+    In any $\sigma$-fragment, $\W{\sigma}$-majorization provides a stricter bound than mana.
+\end{theorem}
+\begin{proof}
+    The maximum of the Lorenz curve of a state $\rho$ can be expressed monotonically in terms of mana, independently of the $\sigma$-fragment,
+    \begin{equation}
+        \max_k{L_k(\rho | \sigma)} = 1 + \sum_{\bmz: \W[\bmz]{\rho}<0} \abs{\W[\bmz]{\rho}} = \frac{1}{2} \left( 1 + e^\mana{\rho} \right).
+    \end{equation}
+    Therefore, the majorization condition stated in~\cref{eq:majbound} implies that $\mana{\rho^{\otimes k}} \geq \mana{\tau}$.
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Conclusion}
+\label{sec:conc}
+
+\begin{enumerate}
+    \item Introduced fragments
+    \item Identify symmetries of the setup
+    \item Combined single-shot thermodynamics with magic 
+    \item Can we solve other cases exactly? (apart from single qutrit)
+\end{enumerate}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\bibliography{bib}
+%\bibliographystyle{apsrev4-2}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \appendix
-\input{appendix/wigner}
-\input{appendix/major}
+\input{appendix}
 

### 2020-06-12 magic_paper.tex
Various bits on fragments edited. Notion of covariant and contravariant projections introduced.

@@
 Any magic theory $\R = (\F, \O)$ is a subtheory of $\Rmax$ as explained in~\cref{sec:intro}, and as such it falls under this new stochasticity setting.
-This observation gives rise to the idea of subdividing magic theories into ``chunks'' identified by the invariance of a particular state under stochastic processes. \nick{explain better}
+For technical simplicity in what follows we assume that $\F$ is a closed set, and note that $\F_{\mbox{\tiny max}}$ is itself a closed set, since it is specified by a finite set of linear constraints of the form $\tr [ L\rho] \ge 0$ with $L \in \mathcal{B}(\mathcal{H})$.
+
+Given this context we now define the following key notion, that is central to our analysis.
 \begin{definition}[\textbf{$\boldsymbol\sigma$-fragment}]\label{def:sigmafrag}
-    A subtheory $\R'$ of a magic theory $\R = (\F, \O)$ is called a \emph{$\sigma$-fragment} of $\R$ iff $\R' = (\F, \O_\sigma)$, where the free operations are restricted to the ones that leave $\sigma$ invariant,
+   Given a resource theory of magic $\R = (\F, \O)$, the \emph{$\sigma$-fragment of $\R$} is the resource theory $\R_\sigma = (\F, \O_\sigma)$, where the free operations are restricted to the ones that leave $\sigma$ invariant, namely
     \begin{equation}
@@
 
-State $\sigma$ is thus a fixed point of all operations in $\O_\sigma$. 
-We now show that every free operation has a fixed point, so that the theory $\R$ can be entirely subdivided into $\sigma$-fragments.
+With this basic notion defined, we now show that any resource theory of magic can be faithfully subdivided into $\sigma$-fragments, in such a way that any problem of interconversion in the parent magic theory $\R$ can be analysed across the different fragments.
 
@@
     Let $\R = (\F, \O)$ be a theory of magic.
-    Every free operation leaves at least one free state invariant such that $\O = \bigcup\limits_{\sigma \in \F} \O_\sigma$.
+    Every operation in $\O$ leaves at least one free state invariant,
+  \begin{equation}
+\O = \bigcup\limits_{\sigma \in \F} \O_\sigma, 
+\end{equation}
+and therefore $\rho\longrightarrow \tau$ in $\R$ if and only if $\rho\longrightarrow \tau$ in a $\sigma$--fragment of $\R$.
 \end{theorem}
 \begin{proof}
-    Suppose $\E$ is in $\O_\sigma$, then it is also in $\O$, hence $\bigcup\limits_{\sigma \in \F} \O_\sigma \subseteq \O$.
-
-    Conversely, suppose $\E$ is in $\O$. 
-    The free states are mapped one-to-one to a subset $\cal{S}$ of the $(d^2 - 1)$-dimensional probability simplex.
+    Suppose $\E$ is in $\O_\sigma$, then it is also in $\O$, hence $\bigcup\limits_{\sigma \in \F} \O_\sigma \subseteq \O$. Conversely, suppose $\E$ is in $\O$. 
+    The free states are a closed set that is mapped one-to-one to a closed subset $\cal{S}$ of the $(d^2 - 1)$-dimensional probability simplex.
     $\cal{S}$ is convex, since any combination of free states is also free and the Wigner distribution is linear.
-    Therefore, $\cal{S}$ is convex and compact as a convex subset of the bounded compact probability simplex. \nick{Need to prove that $\cal{S}$ is closed.}
-    Then, $\W{\E}{}$ is a stochastic, thus continuous, mapping from $\cal{S}$ to itself and Brouwer's fixed point theorem \nick{CITE} implies that there exists a probability distribution $g_{\bmz}, \bmz \in \pd$ that is preserved by $\W{\E}{}$.
-    This corresponds one-to-one to a state $\sigma \coloneqq \sum_{\bmz \in \pd} g_{\bmz} A_{\bmz}$ and so $\O \subseteq \bigcup\limits_{\sigma \in \F} \O_\sigma$.
+    Therefore, $\cal{S}$ is convex and compact as a convex subset of the bounded compact probability simplex.
+    Then, $\W{\E}{}$ is a stochastic, continuous, mapping from $\cal{S}$ to itself and so Brouwer's fixed point theorem \nick{CITE} implies that there exists a probability distribution $g_{\bmz}$ for some $ \bmz \in \pd$ that is a fixed point of $\W{\E}{}$.
+    This corresponds to an operator $\sigma \coloneqq \sum_{\bmz \in \pd} g_{\bmz} A_{\bmz}$  which is a state in $\F$.
+Therefore $\E \in \O_\sigma$, and so $\O = \bigcup\limits_{\sigma \in \F} \O_\sigma$.
+The state interconversion result follows immediately.
 \end{proof}
-Therefore, identifying an invariance in the setup helps in determining whether a state conversion $\rho \xrightarrow{\E \in \O} \tau$ is possible. 
-If state $\sigma$ is left invariant by an operational sequence, then the total operation $\E$ that converts $\rho$ to $\tau$ lies in $\O_\sigma$. \nick{expand}
 
@@
         ]{figs/operations.pdf}
-    \caption{Zoo of allowed operations for magic resource theories.
+    \caption{\textbf{Decomposition of a magic theory $\R$ intro $\sigma$--fragments.} 
     Established theories involve operations within the yellow regions, following the hierarchy $\so \subset \cspo \subset \spo \subset \Omax$.
@@
 
-\subsection{Majorization}\label{sec:major}
+\subsection{Majorization in the $\sigma$--fragments}\label{sec:major}
 
@@
 Lorenz curves of quasi-probability distributions in principle reach above 1.
+\ddd{[It is usually better to convert the Lorenz curve into a \emph{function} $L_{\bmz|\bmd}(x)$ defined on $[0,1]$.
+Then the majorization simply becomes the functional inequality $L_{\bmz|\bmd}(x) \ge L _{\bmy|\bmd}(x)$ for all $x$.]}
 
-A vector $\bmy$ $\bmd$-majorizes another vector $\bmx$  if and only if Lorenz curve $L(\bmy|\bmd)$ lies above Lorenz curve $L(\bmx|\bmd)$.
+A vector $\bmy$ is said to \emph{$\bmd$--majorize} another vector $\bmx$  if and only if the Lorenz curve $L(\bmy|\bmd)$ lies above Lorenz curve $L(\bmx|\bmd)$.
 \begin{theorem}\label{thm:dmajor}
@@
 
-\nick{May move statements around the section or in an appendix.}
+\nick{May move statements around the section or in an appendix.} \ddd{[Yes, the following theorem, while useful, isn't so interesting.]}
 
@@
     It can be thought as a sequence of tracing out state $\rho$ and preparing the free state $\sigma$.
+\ddd{[There is no reason this map is in $\O$.
+Better to use the identity map, which we can assume is always available.]}
 
@@
 
-\section{General resource fragments}
+\section{Extension to general quantum resource theories}
 \label{sec:frag}
+
+\ddd{In the previous section we introduced the notion of $\sigma$--fragments for any resource theory of magic.
+In this section we pause to generalise this concept to an arbitrary resource theory and explain precisely how it connects with resource monotones.
+The busy reader more focussed on magic may skip this section.}
 
@@
 \begin{definition}[\textbf{Resource monotone}]\label{def:mono}
-    Let $\R = (\F, \O)$ be a general resource theory.
-    A monotone $\M$ is a projection from the set of all states of the theory to the real line, satisfying two conditions:
+    Let $\R = (\F, \O)$ be a resource theory.
+    A resource monotone $\M$ is a projection from the set of all states of the theory to the real line, satisfying two conditions:
     \begin{enumerate}
-        \item All free states are mapped onto 0, $\M(\sigma) = 0,\ \sigma \in \F$;
+        \item All free states are mapped onto 0, $\M(\sigma) = 0,\ \sigma \in \F$; \ddd{[This is not a requirement!]}
         \item $\M$ is monotonically decreasing under free operations, $\M(\rho_1) \leq \M(\rho_2)$ whenever $\rho_1 \prec_{\R} \rho_2$.
@@
 
-Monotones reduce the structure of the resource theory $\R$ into a real number ordering.
+Monotones reduce the structure of the resource theory $\R$ into a \emph{total} order on the real numbers.
 Therefore, two states, even if incomparable in $\R$, are always mapped onto ordered real numbers.
@@
 \end{definition}
+
+\ddd{[I think the following might be the right way to understand things, using the notion of ``covariant'' and ``contravariant''.]}
+
+\ddd{\begin{definition}[Covariant Projection] Let $\R = (\F, \O)$ be a resource theory with pre-order $\prec$.
+Then a \emph{covariant resource projection} of $\R$ to a resource theory $\R'$ with pre-order $\prec'$, is a pair of mappings $\Pi_s, \Pi_o$, where $\Pi_s$ maps quantum states in $\R$ to quantum states in $\R'$, and $\Pi_o$ maps free operations in $\R$ into free operations in $\R'$.
+Moreover, these obey
+\begin{enumerate}
+        \item $\rho_1 \prec \rho_2$  implies that $\Pis(\rho_2) \prec' \Pis(\rho_1)$.
+        \item  $\Pio(\E_1) \circ \Pio(\E_2) = \Pio(\E_1 \circ \E_2)$ for all free operations $\E_1, \E_2 \in \O$.
+    \end{enumerate}
+\end{definition}
+In a similar manner we can define the following distinct notion of a resource projection.
+\begin{definition}[Contravariant Projection] Let $\R = (\F, \O)$ be a resource theory with pre-order $\prec$.
+Then a \emph{contravariant resource projection} of $\R$ to a resource theory $\R'$ with pre-order $\prec'$, is a pair of mappings $\Pi_s, \Pi_o$, where $\Pi_s$ maps quantum states in $\R$ to quantum states in $\R'$, and $\Pi_o$ maps free operations in $\R$ into free operations in $\R'$.
+Moreover, these obey
+\begin{enumerate}
+        \item $\Pis(\rho_1) \prec' \Pis(\rho_2)$ implies that $\rho_1 \prec \rho_2$ .
+        \item  $\Pio(\E_1) \circ \Pio(\E_2) = \Pio(\E_1 \circ \E_2)$ for all free operations $\E_1, \E_2 \in \O$.
+    \end{enumerate}
+\end{definition}
+The use of covariant and contravariant here refers to direction of implication between the two pre-orders\footnote{ Also note that strictly these are not projections in the sense of $\Pi^2 = \Pi$, but are instead morphisms.
+Here our use of the term projection is motivated by the idea that one one generally loses information about $\R$ under the mapping.}.
+It is now clear that any resource monotone is a covariant projection, while the $\sigma$--fragments are contravariant projections of the magic theory.
+}
+
 Fragment $\R'$ is the image of the projection $\Pi$.
@@
 
+\ddd{[If you agree with the covariant-contravariant definitions above then you can update the following results using the new terminology.]}
 A monotone is the projection with the simplest tractable order as formally stated in~\cref{thm:monofrag}.
@@
 
+\begin{example}Let $\R = (\F,\O)$ be a resource theory, and let $\D \in \O$ be any free operation.
+Then we can define the following contravariant projection $\Pi_s( \rho) := \D(\rho)$ for all states $\rho$, and $\Pi_o (\E) = \E$.
+\ddd{[Explain why contravariant]}.
+As a simple example, we can consider the thermal operations resource theory of thermodynamics, and take $\D$ to be the dephasing map that kills off coherences between energy eigenspaces.
+Then the resource projection $\R'$ induced by $\D$ is fully described by the thermo-majorization pre-order on distributions over energies.
+\end{example}
+
 We now justify the name $\sigma$-fragment for the subdivision of a magic theory $\R = (\F, \O)$, by establishing a resource projection which reduces $\R$ into any subtheory $(\F, \O_\sigma)$.
@@
     Let $\R = (\F, \O)$ be a theory of magic.
-    Every $\sigma$-fragment $(\F, \O_\sigma)$ is a resource fragment of $\R$.
+    Every $\sigma$-fragment $(\F, \O_\sigma)$ \ddd{defines a contravariant projection} of $\R$.
 \end{proposition}
@@
 
+\ddd{[Is there a way to view Nielsen's theorem as describing a projection of the full mixed state LOCC entanglement theory?
+Is really not essential but might be nice to include.
+Send $\rho_{AB} $ to the most entangled pure state in its eigendecomposition?]}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     \end{equation}
-    Therefore, the majorization condition stated in~\cref{eq:majbound} implies that $\mana{\rho^{\otimes k}} \geq \mana{\tau}$.
+    Therefore, the majorization condition stated in~\cref{eq:majbound} implies that $\mana{\rho^{\otimes k}} \geq \mana{\tau}$. \ddd{[This is a bit too short]}
 \end{proof}

### 2020-06-16 appendix.tex
Cleaning up fragments section, wrote comment on Theorem 4

@@
+\section{Properties of the Wigner distribution}
+\label{app:wigner}
+
+Here we present important properties of the Wigner distribution that are used throughout the paper.
+
+\begin{proposition}\label{thm:wstate}
+    The Wigner distribution of a state $\rho$ is
+    \begin{enumerate}
+        \item\label{en:w1} Real valued: $\W{\rho} \in \mathbb{R}^{d^2}$;
+        \item\label{en:w2} Normalised: $\sum_{\bmz \in \pd} \W[\bmz]{\rho}=1$;
+        \item\label{en:w3} Bounded: $\abs{\W[\bmx]{\rho}} \leq \frac{1}{d}$.
+        \item\label{en:w4} Additive under mixing:
+
+        $\W[\bmx]{\sum_i p_i \rho_i} = \sum\limits_i p_i \W[\bmx]{\rho_i}$;
+        \item\label{en:w5} Multiplicative under tensor products:
+
+        $\W[\bmx_A \oplus \bmx_B]{\rho_A \otimes \rho_B} = \W[\bmx_A]{\rho_A}\W[\bmx_B]{\rho_B}$.
+	\end{enumerate}
+\end{proposition}
+A distribution satisfying the first three properties does not necessarily correspond to a positive semi-definite state.
+
+\begin{proposition}
+    \label{thm:wchannel}
+    The Wigner distribution of a $\cptp$ operation $\E: \cal{B}(\hd[d_A]) \mapsto \cal{B}(\hd[d_B])$ is:
+    \begin{enumerate}
+        \item\label{en:wo1} Real-valued: $\W[\bmy|\bmx]{\E} \in \mathbb{R}$;
+        \item\label{en:wo2} Normalised: $\sum_{\bmz \in \pd[d_B]} \W[\bmz|\bmx]{\E} = 1$ for any $\bmx \in \pd[d_A]$;
+        \item\label{en:wo3} Bounded: $\abs{\W[\bmy|\bmx]{\E}} \leq \frac{d_A}{d_B}$;
+	    \item\label{en:wo4} \nick{Transitive}: $\W[\bmy]{\E(\rho)} = \sum_{\bmz \in \pd[d_A]} \W[\bmy|\bmz]{\E} \W[\bmz]{\rho}$ for any $\bmy \in \pd[d_B]$.
+    \end{enumerate}
+\end{proposition}
+If $d_A = d_B$, and in particular if operation $\E$ maps a Hilbert space onto itself, then the stochasticity condition $\abs{\W[\bmy|\bmx]{\E}} \leq 1$ is satisfied.
+
+%%%
+
 \section{Properties of majorization}
@@
 Given $\bmx, \bmy, \bmd \in \mathbb{R}^n$, such that the components of $\bmd$ are positive, the following statements are equivalent:
- \begin{enumerate}
-	\item[(TM1)] $\bmx \prec_{\bmd} \bmy$;
-	\item[(TM2)] $\Gamma_{\bmd}({\bmx}) \prec \Gamma_{\bmd}({\bmy})$;
-	\item[(TM3)]\label{en:tm3} $\sum\limits_{i=1}^n \abs{x_i - t d_i} \leq \sum\limits_{i=1}^n \abs{y_i - t d_i}$ for all $t \in \mathbb{R}$;
-	\item[(TM4)] $\sum\limits_{i=1}^n (x_i - t d_i)^+ \leq \sum\limits_{i=1}^n (y_i - t d_i)^+$ for all $t \in \mathbb{R}$ and $\sum\limits_{i=1}^n x_i = \sum\limits_{i=1}^n y_i$;
-	\item[(TM5)] $\forall k, L_{\bmx|\bmd}(k) \leq L_{\bmy|\bmd}(k)$ and $L_{\bmx|\bmd}(k=n) = L_{\bmy|\bmd}(k=n)$.
+ \begin{enumerate}%[\rm{(TM1)}]
+	\item $\bmx \prec_{\bmd} \bmy$;
+	\item $\Gamma_{\bmd}({\bmx}) \prec \Gamma_{\bmd}({\bmy})$;
+	\item\label{en:tm3} $\sum\limits_{i=1}^n \abs{x_i - t d_i} \leq \sum\limits_{i=1}^n \abs{y_i - t d_i}$ for all $t \in \mathbb{R}$;
+	\item $\sum\limits_{i=1}^n (x_i - t d_i)^+ \leq \sum\limits_{i=1}^n (y_i - t d_i)^+$ for all $t \in \mathbb{R}$ and $\sum\limits_{i=1}^n x_i = \sum\limits_{i=1}^n y_i$;
+	\item $\forall k, L_{\bmx|\bmd}(k) \leq L_{\bmy|\bmd}(k)$ and $L_{\bmx|\bmd}(k=n) = L_{\bmy|\bmd}(k=n)$.
  \end{enumerate}
@@
 
-\section{Properties of the Wigner distribution}
-\label{app:wigner}
+\section{Properties of $\sigma$-fragments}
+\label{app:frag}
 
-Here we present important properties of the Wigner distribution that are used throughout the paper.
+\begin{theorem}\label{thm:frag}
+    Let $\R = (\O, \F)$ be a magic theory. 
+    The following statements hold:
+    \begin{enumerate}
+        \item No $\sigma$-fragment is empty.
+        \item If a free operation leaves two states invariant, then it also leaves their mixtures invariant, 
+        \begin{equation}
+            \O_{\sigma} \cap \O_{\sigma'} \subseteq \O_{p\sigma + (1-p)\sigma'}\ \text{for all}\ p \in [0,1].
+        \end{equation}
+        \item Let $\E$ be a $\cptp$ operation with Wigner distribution $\W{\E}$.
+        For $\R = \Rmax$ $\E \in \O_\sigma$ iff $\W{\E} \in \stochw$.
+    \end{enumerate}
+\end{theorem}
+\begin{proof}$ $\\
 
-\begin{proposition}\label{thm:wstate}
-    The Wigner distribution of a state $\rho$ is
-    \begin{enumerate}%[label=\enlabel{W}{\arabic*}]
-        \item\label{en:w1} Real valued: $\W{\rho} \in \mathbb{R}^{d^2}$;
-        \item\label{en:w2} Normalised: $\sum_{\bmz \in \pd} \W[\bmz]{\rho}=1$;
-        \item\label{en:w3} Bounded: $\abs{\W[\bmx]{\rho}} \leq \frac{1}{d}$.
-        \item\label{en:w4} Additive under mixing:
+    \begin{enumerate}
+    \item The identity channel $1_{\rm{C}}: \D \mapsto \D$ belongs to every $\sigma$-fragment, as $1_{\rm{C}} \in \O$ and $1_{\rm{C}}\sigma = \sigma$ for all $\sigma \in \F$.
 
-        $\W[\bmx]{\sum_i p_i \rho_i} = \sum\limits_i p_i \W[\bmx]{\rho_i}$;
-        \item\label{en:w5} Multiplicative under tensor products:
+    \item Let $\E \in \O_{\sigma} \cap \O_{\sigma'}$.
+    Then $\E \in \cptp$ and corresponds to stochastic Wigner distribution $\W{\E}$ such that $\W{\E} \W{\sigma} = \W{\sigma}$ and $\W{\E} \W{\sigma'} = \W{\sigma'}$.
+    Then, $\W{\E} \W{p\sigma + (1-p)\sigma'} = \W{p\sigma + (1-p)\sigma'}$ for any $p \in [0,1]$ due to the additive property~\ref{en:w4} of the Wigner distribution, implying that state $p\sigma + (1-p)\sigma'$ is also left invariant by $\E$.
 
-        $\W[\bmx_A \oplus \bmx_B]{\rho_A \otimes \rho_B} = \W[\bmx_A]{\rho_A}\W[\bmx_B]{\rho_B}$.
+    \item Let $\O_\sigma' \coloneqq \{ \E \in \cptp: \W{\E} \in \stochw \}$ be the described set of operations.
+
+    Suppose $\E$ is in $\O_\sigma$, then $\E \in \cptp$ and $\W{\E} \in \stochw$ due to property~\ref{en:wo4} of~\cref{thm:wchannel}, hence $\O_\sigma \subseteq \O_\sigma'$.
+
+    Conversely, suppose $\E \in \cptp$ with $\W{\E} \in \stochw$. 
+    Then, $\W[\bmy|\bmx]{\E} \geq 0$ for all $\bmx, \bmy$, hence $\E \in \O$.
+    Furthermore, $\W{\E} \W{\sigma} = \W{\sigma}$ implies $\E(\sigma) = \sigma$ using~\cref{eq:woperation} defined for any $\cptp$ operation $\E$.
+    Hence, $\O_\sigma' \subseteq \O_\sigma$.
     \end{enumerate}
-\end{proposition}
-A distribution satisfying the first three properties does not necessarily correspond to a positive semi-definite state.
+\end{proof}
 
-\begin{proposition}
-    \label{thm:wchannel}
-    The Wigner distribution of a $\cptp$ operation $\E: \cal{B}(\hd[d_A]) \mapsto \cal{B}(\hd[d_B])$ is:
-    \begin{enumerate}
-        \item\label{en:wo1} Real-valued: $\W[\bmy|\bmx]{\E} \in \mathbb{R}$;
-        \item\label{en:wo2} Normalised: $\sum_{\bmz \in \pd[d_B]} \W[\bmz|\bmx]{\E} = 1$ for any $\bmx \in \pd[d_A]$;
-        \item\label{en:wo3} Bounded: $\abs{\W[\bmy|\bmx]{\E}} \leq \frac{d_A}{d_B}$;
-	    \item\label{en:wo4} \nick{Transitive}: $\W[\bmy]{\E(\rho)} = \sum_{\bmz \in \pd[d_A]} \W[\bmy|\bmz]{\E} \W[\bmz]{\rho}$ for any $\bmy \in \pd[d_B]$.
-    \end{enumerate}
-\end{proposition}
-If $d_A = d_B$, and in particular if operation $\E$ maps a Hilbert space onto itself, then the stochasticity condition $\abs{\W[\bmy|\bmx]{\E}} \leq 1$ is satisfied.
+Any free state $\sigma \in \cal{B}(\hd)$ corresponds to a $d^2$-dimensional probability distribution $\W{\sigma}$ and any free operation $\E: \cal{B}(\hd) \mapsto \cal{B}(\hd)$ corresponds to a $d^2 \times d^2$ stochastic matrix (or conditional probability distribution) $\W{\E}$.
+Note that these mappings are one-to-one due to the orthogonality of the phase-point operators as an operator basis.
+
+\emph{Remark 1.} Note that free states $\F$ are mapped onto a \emph{strict subset} of the set of probability distributions.
+As a counterexample, the sharp $d^2$-dimensional probability distribution $(1, 0, \dots, 0)$ does not correspond to any qudit Wigner distribution because of the boundedness condition~\ref{en:w3} in~\cref{thm:wstate}.
+
+\emph{Remark 2.} Similarly, not all stochastic matrices correspond to completely positive operations.
+
+As an example, consider the permutation matrix
+\begin{equation}
+    \Pi_X = \begin{psmallmatrix}
+        0 & 1 & 0 & 0 & 0 \\
+        0 & 0 & 0 & 0 & 1 \\
+        0 & 0 & 0 & 1 & 0 \\
+        1 & 0 & 0 & 0 & 0 \\
+        0 & 0 & 1 & 0 & 0
+    \end{psmallmatrix} \otimes \begin{psmallmatrix}
+        0 & 0 & 1 & 0 & 0 \\
+        0 & 0 & 0 & 0 & 1 \\
+        0 & 0 & 0 & 1 & 0 \\
+        1 & 0 & 0 & 0 & 0 \\
+        0 & 1 & 0 & 0 & 0    
+    \end{psmallmatrix} \in \stochw,\ d=5.
+\end{equation}
+It preserves the uniform distribution $\W{\frac{1}{5}\id}{}$, but it does not correspond to any $\cpos$ operation, hence any $\E \in \O$ due to~\cref{thm:frag}.

### 2020-06-16 magic_paper.tex
Cleaning up fragments section, wrote comment on Theorem 4

@@
 \begin{definition}[\textbf{$\boldsymbol\sigma$-fragment}]\label{def:sigmafrag}
-   Given a resource theory of magic $\R = (\F, \O)$, the \emph{$\sigma$-fragment of $\R$} is the resource theory $\R_\sigma = (\F, \O_\sigma)$, where the free operations are restricted to the ones that leave $\sigma$ invariant, namely
+   Given a resource theory of magic $\R = (\F, \O)$, the \emph{$\sigma$--fragment of $\R$} is the resource theory $\R_\sigma = (\F, \O_\sigma)$, where the free operations are restricted to the ones that leave $\sigma$ invariant, namely
     \begin{equation}
@@
 
-With this basic notion defined, we now show that any resource theory of magic can be faithfully subdivided into $\sigma$-fragments, in such a way that any problem of interconversion in the parent magic theory $\R$ can be analysed across the different fragments.
+With this basic notion defined, we now show that any resource theory of magic can be faithfully subdivided into $\sigma$--fragments, in such a way that any problem of interconversion in the parent magic theory $\R$ can be analysed across the different fragments.
 
@@
   \begin{equation}
-\O = \bigcup\limits_{\sigma \in \F} \O_\sigma, 
+\O = \bigcup\limits_{\sigma \in \F} \O_\sigma.
 \end{equation}
-and therefore $\rho\longrightarrow \tau$ in $\R$ if and only if $\rho\longrightarrow \tau$ in a $\sigma$--fragment of $\R$.
+Therefore, $\rho\longrightarrow \tau$ in $\R$ if and only if $\rho\longrightarrow \tau$ in a $\sigma$--fragment of $\R$.
 \end{theorem}
@@
 Completely positive-Wigner-preserving operations~\cite{cit:wang} form the operation class $\Omax$.
-Therefore, $\sigma$-fragments cover this theory of magic exactly and any magic subtheory is contained within this cover.
+Therefore, $\sigma$--fragments cover this theory of magic exactly and any magic subtheory is contained within this cover.
 In particular, the stabilizer operations $\so$ are contained within $\Omax$.
@@
 
-The subdivision of magic theories into $\sigma$-fragments is powerful because the pre-order $\prec_{\R'}$ of every $\sigma$-fragment is described by well-behaved majorization tools, as we establish in~\cref{sec:major}.
+The subdivision of magic theories into $\sigma$--fragments is powerful because the pre-order $\prec_{\R'}$ of every $\sigma$--fragment is described by well-behaved majorization tools, as we establish in~\cref{sec:major}.
 \nick{expand}
@@
 
-\nick{We need to address the non-full-rankness of states.\\
-For example, the operation $\E(\rho) = \ketbra{0}$ corresponds to no $\sigma$-fragment because components of $\W{\sigma}$ are zero.\\
-In such a case we can always add some $\epsilon$ amount of unital noise by mixing $\sigma$ with the maximally mixed state $\frac{1}{d}\id$. 
-This ensures that all components are strictly positive and $\bmd$-majorization can be used.
-There are non-full-rank states with no zeros in W.}
-
-The pre-order $\prec_{\R'}$ of the $\sigma$-fragment $\R' = (\F, \O_\sigma)$ between $d$-dimensional states corresponds to the majorization pre-order $\prec_{\W{\sigma}}$ between their $d^2$-dimensional Wigner distributions.
+The pre-order $\prec_{\R'}$ of the $\sigma$--fragment $\R' = (\F, \O_\sigma)$ between $d$-dimensional states corresponds to the majorization pre-order $\prec_{\W{\sigma}}$ between their $d^2$-dimensional Wigner distributions.
 
@@
     Then, there exists a full-rank free state $\sigma \in \F$ such that  $\W{\tau} \prec_{\W{\sigma}} \W{\rho}$.
+
+\nick{We need to address zeros in the Wigner distribution (I think full-rank states do not have any zeros - there certainly exist non-full-rank states with no zeros).
+
+For example, the replacement operation $\E(\rho) = \ketbra{0}$ is free in $\Rmax$ with $\E \in \O_{\ketbra{0}}$, BUT $W{\ketbra{0}}$-majorization is not defined because $W{\ketbra{0}}$ contains zeros.
+
+In such a case we can always add some $\epsilon$ amount of noise by mixing $\sigma$ with a free full-rank state, e.g.
+a thermal state $\gamma_\beta$, to get $\sigma' = (1-\epsilon)\sigma + \epsilon\gamma_\beta$.
+This ensures that all Wigner components of $\sigma'$ are strictly positive and $\W{\sigma'}$-majorization can be used BUT $\E$ is NOT in $\O_{\sigma'}$ now for any $\epsilon > 0$.
+
+This could be solved if every operation preserves some thermal state.
+Otherwise, simply stating in this theorem that ``there exists a full-rank free state $\sigma \in \F$ such that  $\W{\tau} \prec_{\W{\sigma}} \W{\rho}$'' is not accurate and needs reformulation to include the error $\epsilon$.
+}
 \end{theorem}
@@
     Suppose there exists $\E \in \O$ such that $\E(\rho) = \tau$.
-    The free operation belongs to a $\sigma$-fragment, $\E \in \O_\sigma$, for some $\sigma \in \F$.
-    Then, $\W{\E}\W{\rho} = \W{\tau}$ with $\W{\E} \in \stochw$, or, equivalently, $\W{\tau} \prec_{\W{\sigma}} \W{\rho}$.
+    The free operation belongs to a $\sigma$--fragment, $\E \in \O_\sigma$, for some $\sigma \in \F$ so that $\W{\E}\W{\rho} = \W{\tau}$ with $\W{\E} \in \stochw$.
+
+    If all components of $\W{\sigma}$ are positive, we directly have $\W{\tau} \prec_{\W{\sigma}} \W{\rho}$.
+
+    If $\W{\sigma}$ contains some zero components, we can construct the full-rank state $\sigma' = (1-\epsilon)\sigma + \epsilon\gamma_\beta$ by mixing an arbitrarily small amout $\epsilon>0$ of some thermal state $\gamma_\beta$ \nick{can replace with maximally mixed state}, so that all components of $\W{\sigma'}$ are positive.
+\nick{but $\W{\tau} \prec_{\W{\sigma'}} \W{\rho}$ is NOT true now}
 \end{proof}
@@
 
-\subsection{Set theoretic properties of magic fragments}\label{sec:propmagfrag}
-
-\nick{May move statements around the section or in an appendix.} \ddd{[Yes, the following theorem, while useful, isn't so interesting.]}
-
-\begin{theorem}\label{thm:frag}
-    Let $\R = (\O, \F)$ be a magic theory. 
-    The following statements hold:
-    \begin{enumerate}
-        \item No $\sigma$-fragment is empty.
-        \item If a free operation leaves two states invariant, then it also leaves their mixtures invariant, 
-        \begin{equation}
-            \O_{\sigma} \cap \O_{\sigma'} \subseteq \O_{p\sigma + (1-p)\sigma'}\ \text{for all}\ p \in [0,1].
-        \end{equation}
-        \item Let $\E$ be a $\cptp$ operation with Wigner distribution $\W{\E}$.
-        For $\R = \Rmax$ $\E \in \O_\sigma$ iff $\W{\E} \in \stochw$.
-    \end{enumerate}
-\end{theorem}
-\begin{proof}$ $\\
-
-    \begin{enumerate}
-    \item Consider the completely depolarising \nick{replacement} map
-    \begin{align}
-        \E(\rho) &= \sigma \tr[\rho],\ \text{with} \\
-        \W[\bmy|\bmx]{\E} &= \W[\bmy]{\sigma} \tr[\rho],
-    \end{align}
-    where $\sigma \in \F$. 
-    Then, $\E \in \O_\sigma$.
-    It can be thought as a sequence of tracing out state $\rho$ and preparing the free state $\sigma$.
-\ddd{[There is no reason this map is in $\O$.
-Better to use the identity map, which we can assume is always available.]}
-
-    \item Let $\E \in \O_{\sigma} \cap \O_{\sigma'}$.
-    Then $\E \in \cptp$ and corresponds to stochastic Wigner distribution $\W{\E}$ such that $\W{\E} \W{\sigma} = \W{\sigma}$ and $\W{\E} \W{\sigma'} = \W{\sigma'}$.
-    Then, $\W{\E} \W{p\sigma + (1-p)\sigma'} = \W{p\sigma + (1-p)\sigma'}$ for any $p \in [0,1]$ due to the additive property~\ref{en:w4} of the Wigner distribution, implying that state $p\sigma + (1-p)\sigma'$ is also left invariant by $\E$.
-
-    \item Let $\O_\sigma' \coloneqq \{ \E \in \cptp: \W{\E} \in \stochw \}$ be the described set of operations.
-
-    Suppose $\E$ is in $\O_\sigma$, then $\E \in \cptp$ and $\W{\E} \in \stochw$ due to property~\ref{en:wo4} of~\cref{thm:wchannel}, hence $\O_\sigma \subseteq \O_\sigma'$.
-
-    Conversely, suppose $\E \in \cptp$ with $\W{\E} \in \stochw$. 
-    Then, $\W[\bmy|\bmx]{\E} \geq 0$ for all $\bmx, \bmy$, hence $\E \in \O$.
-    Furthermore, $\W{\E} \W{\sigma} = \W{\sigma}$ implies $\E(\sigma) = \sigma$ using~\cref{eq:woperation} defined for any $\cptp$ operation $\E$.
-    Hence, $\O_\sigma' \subseteq \O_\sigma$.
-    \end{enumerate}
-\end{proof}
-
-Any free state $\sigma \in \cal{B}(\hd)$ corresponds to a $d^2$-dimensional probability distribution $\W{\sigma}$ and any free operation $\E: \cal{B}(\hd) \mapsto \cal{B}(\hd)$ corresponds to a $d^2 \times d^2$ stochastic matrix (or conditional probability distribution) $\W{\E}$.
-Note that these mappings are one-to-one due to the orthogonality of the phase-point operators as an operator basis.
-
-\emph{Remark 1.} Note that free states $\F$ are mapped onto a \emph{strict subset} of the set of probability distributions.
-As a counterexample, the sharp $d^2$-dimensional probability distribution $(1, 0, \dots, 0)$ does not correspond to any qudit Wigner distribution because of the boundedness condition~\ref{en:w3} in~\cref{thm:wstate}.
-
-\emph{Remark 2.} Similarly, not all stochastic matrices correspond to completely positive operations.
-
-As an example, consider the permutation matrix
-\begin{equation}
-    \Pi_X = \begin{psmallmatrix}
-        0 & 1 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 1 \\
-        0 & 0 & 0 & 1 & 0 \\
-        1 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 1 & 0 & 0
-    \end{psmallmatrix} \otimes \begin{psmallmatrix}
-        0 & 0 & 1 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 1 \\
-        0 & 0 & 0 & 1 & 0 \\
-        1 & 0 & 0 & 0 & 0 \\
-        0 & 1 & 0 & 0 & 0    
-    \end{psmallmatrix} \in \stochw,\ d=5.
-\end{equation}
-It preserves the uniform distribution $\W{\frac{1}{5}\id}{}$, but it does not correspond to any $\cpos$ operation, hence any $\E \in \O$ due to~\cref{thm:frag}.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\ddd{In the previous section we introduced the notion of $\sigma$--fragments for any resource theory of magic.
+In the previous section we introduced the notion of $\sigma$--fragments for any resource theory of magic.
 In this section we pause to generalise this concept to an arbitrary resource theory and explain precisely how it connects with resource monotones.
-The busy reader more focussed on magic may skip this section.}
+The busy reader more focussed on magic may skip this section.
 
@@
 In general, the structure of a theory $\R$ is described by a pre-order $\prec_\R$ \nick{expand / move to intro}.
-Subdividing magic theories into $\sigma$-fragments \nick{helps}.
+Subdividing magic theories into $\sigma$--fragments \nick{helps}.
 \subsection{Monotones}\label{sec:mono}
@@
     Let $\R = (\F, \O)$ be a resource theory.
-    A resource monotone $\M$ is a projection from the set of all states of the theory to the real line, satisfying two conditions:
-    \begin{enumerate}
-        \item All free states are mapped onto 0, $\M(\sigma) = 0,\ \sigma \in \F$; \ddd{[This is not a requirement!]}
-        \item $\M$ is monotonically decreasing under free operations, $\M(\rho_1) \leq \M(\rho_2)$ whenever $\rho_1 \prec_{\R} \rho_2$.
-    \end{enumerate}
+    A resource monotone $\M$ is a projection from the set of quantum states of the theory onto the real line, so that $\M$ is monotonically decreasing under free operations,
+    \begin{equation}
+        \M(\rho_1) \leq \M(\rho_2)\ \text{whenever}\ \rho_1 \prec_{\R} \rho_2.
+    \end{equation}
 \end{definition}
-The first condition reflects the property that all free states can be converted into each other, hence they need to be mapped onto the same number, by convention 0.
-The second condition reflects the no resource generating property of free operations, thus monotones respect the pre-order $\prec_\R$ of the theory.
+The monotonicity condition reflects the no resource generating property of free operations, so that monotones respect the pre-order $\prec_\R$ of the theory.
 Furthermore, if a monotone satisfies the additivity condition,
@@
 
+Monotones reduce the structure of the resource theory $\R$ to a \emph{total} order on the real numbers.
+Therefore, two states, even if incomparable in $\R$, are always mapped onto ordered real numbers.
+We now generalise this idea to any projection of the theory that ensures a form of comparison between states.
+\begin{definition}[\textbf{Covariant projection}]\label{def:covproj}
+Let $\R = (\F, \O)$ be a resource theory with pre-order $\prec_\R$. 
+Then a \emph{covariant resource projection} of $\R$ into a resource theory $\R'$ with pre-order $\prec_{\R'}$, is a pair of mappings $(\Pi_s, \Pi_o)$, where $\Pi_s$ maps quantum states in $\R$ into quantum states in $\R'$, and $\Pi_o$ maps free operations in $\R$ into free operations in $\R'$.
+Moreover, these obey
+	\begin{enumerate}
+        \item $\Pis(\rho_2) \prec_{\R'} \Pis(\rho_1)$ whenever $\rho_1 \prec_\R \rho_2$;
+        \item $\Pio(\E) = \Pio(\E_1) \circ \Pio(\E_2)$ whenever $\E = \E_1 \circ \E_2$.
+    \end{enumerate}
+We call $\R'$ a \emph{covariant fragment} of $\R$.
+\end{definition}
+
+Resource monotones can now be clearly seen as covariant projections of resource theories.
+\begin{proposition}\label{thm:monoproj}
+	Let $\M$ be a resource monotone of a resource theory $\R$. 
+	Then $\M$ is a covariant projection that reduces the pre-order $\prec_\R$ to a total order.
+\end{proposition}
+\begin{proof}
+	Consider a monotone $\M$ in the context of a general resource theory $\R = (\F, \O)$.
+	The defining property of a monotone, stated in~\cref{def:mono} ensures order preservation under state projection $\Pis$.	
+	Let $\Pio$ project any $\E \in \O$ onto a real non-increasing function $f$ mapping $\M(\rho)$ to $\M(\E(\rho))$ for all states $\rho$.
+	Then, the composition of functions is preserved under operation projection $\Pio$.	
+	The ordered pair $(\Pis, \Pio)$ is the covariant resource projection which corresponds to monotone $\M$.
+\end{proof}
+
+On the other hand, $\sigma$--fragments are an example of reducing the structure of a magic theory $\R$ to a subtheory with a tractable pre-order.
+States which are incomparable in $\R$ remain incomparable, but transformations between comparable states may no longer be possible.
+We generalise the idea of reducing the structure of a theory into a simpler one, by introducing two types of resource projections.
+\begin{definition}[\textbf{Contravariant projection}]\label{def:contraproj}
+	Let $\R = (\F, \O)$ be a resource theory with pre-order $\prec_\R$. 
+Then a \emph{contravariant resource projection} of $\R$ onto a resource theory $\R'$ with pre-order $\prec_{\R'}$, is a pair of mappings $(\Pi_s, \Pi_o)$, where $\Pi_s$ maps quantum states in $\R$ onto quantum states in $\R'$, and $\Pi_o$ maps free operations in $\R$ onto free operations in $\R'$.
+Moreover, these obey
+	\begin{enumerate}
+        \item $\rho_1 \prec_\R \rho_2$ whenever $\Pis(\rho_1) \prec_{\R'} \Pis(\rho_2)$;
+        \item $\E = \E_1 \circ \E_2$ whenever $\Pio(\E) = \Pio(\E_1) \circ \Pio(\E_2)$.
+    \end{enumerate}
+We call $\R'$ a \emph{contravariant fragment} of $\R$.
+\end{definition}
+The use of covariant and contravariant in~\cref{def:covproj,def:contraproj} refers to the direction of implication between the two pre-orders and operation compositions\footnote{Note that strictly these are not projections in the sense of $\Pi^2 = \Pi$, but are instead morphisms.
+Here our use of the term projection is motivated by the idea that one one generally loses information about $\R$ under the mapping.}.
+
+\begin{proposition}\label{thm:sigmaproj}
+    Let $\R = (\F, \O)$ be a theory of magic.
+    Every $\sigma$--fragment $(\F, \O_\sigma)$ is a contravariant fragment of $\R$.
+\end{proposition}
+\begin{proof}
+    Let the state projection $\Pis$ map all states onto themselves, so order preservation is trivially satisfied.    
+    Consider the operation projection $\Pio:\O \mapsto \O_\sigma$, defined as
+    \begin{equation}
+    \Pio(\E) =
+    \begin{cases}
+        \E,\ &\E \in \O_\sigma, \\
+        1_{\rm{C}},\ &\E \notin \O_\sigma.
+    \end{cases}
+    \end{equation}
+    Since for any $\E_1, \E_2 \in \O_\sigma,$ it is also true that $\E_1 \circ \E_2 \in \O_\sigma$, operational composition is contravariantly preserved.
+\end{proof}
+
+\begin{proposition}
+	Let $\R = (\F,\O)$ be a resource theory, and let $\D \in \O$ be a free operation, which is reversible by $\D_{\rm{rev}} \in \O$, so that $\D_{\rm{rev}} \circ \D = 1_{\rm{C}}$.
+
+	Then, we can define a contravariant projection of $\R$, by acting with $\D$ on all states.
+\end{proposition}
+\begin{proof}
+	We show that the theory $\R' = (\F', \O)$, with $\F' = \{\D(\rho):\rho \in \F \}$, is a contravariant fragment of $\R$.
+	Let $\Pis$ map every state $\rho$ to $\D(\rho)$.
+	Then, $\D(\rho_1) \prec \D(\rho_2)$ implies that there exists $\E \in \O$ such that $\rho_1 = (\D_{\rm{rev}} \circ \E \circ \D) (\rho_2)$, so the state order is preserved contravariantly.
+
+	Finally, let $\Pio$ map every free operation to itself, so that composition of operations is trivially preserved.
+
+\nick{If $\D$ is a recovery map, so that $\D \circ \D_{\rm{rev}} = 1_{\rm{C}}$, then this is a covariant projection instead.
+
+If $\D$ is not reversible, this mapping is in general NOT contravariant (consider the replacement map $\D(\rho) = \frac{1}{d}\id$ for a strange state and stabilizer state - surely there is such a counterexample in thermodynamics theory if we consider a highly coherent state and one with the same energy population but no coherences.}
+\end{proof}
+
+Important examples of resource fragments appear in several established resource theories.
+\nick{Need to check if the thermodynamics example works, include magic theories as fragments of $\Rmax$, include Nielsen's bipartite entanglement.}
+
+\newpage
+
+\subsection{Fragments - OLD}
+
+\nick{OLD VERSION}
+
 Monotones reduce the structure of the resource theory $\R$ into a \emph{total} order on the real numbers.
 Therefore, two states, even if incomparable in $\R$, are always mapped onto ordered real numbers.
-This is a generic approach that ensures a form of state comparison and resource quantification.
-However, motivated by $\sigma$-fragments in magic theories, it is clear that we can often reduce the theory by a less \nick{information-collapsing} projection into a subtheory $\R'$ which has a tractable pre-order $\R'$, as sketched in~\cref{fig:fragments}.
+This is a generic approach that ensures a form of comparison between states and resource quantification.
+However, motivated by $\sigma$--fragments in magic theories, it is clear that we can often reduce the theory by a less \nick{information-collapsing} projection into a subtheory $\R'$ which has a tractable pre-order $\R'$, as sketched in~\cref{fig:fragments}.
 \begin{figure}[t]
@@
 \ddd{[I think the following might be the right way to understand things, using the notion of ``covariant'' and ``contravariant''.]}
-
-\ddd{\begin{definition}[Covariant Projection] Let $\R = (\F, \O)$ be a resource theory with pre-order $\prec$.
-Then a \emph{covariant resource projection} of $\R$ to a resource theory $\R'$ with pre-order $\prec'$, is a pair of mappings $\Pi_s, \Pi_o$, where $\Pi_s$ maps quantum states in $\R$ to quantum states in $\R'$, and $\Pi_o$ maps free operations in $\R$ into free operations in $\R'$.
-Moreover, these obey
-\begin{enumerate}
-        \item $\rho_1 \prec \rho_2$  implies that $\Pis(\rho_2) \prec' \Pis(\rho_1)$.
-        \item  $\Pio(\E_1) \circ \Pio(\E_2) = \Pio(\E_1 \circ \E_2)$ for all free operations $\E_1, \E_2 \in \O$.
-    \end{enumerate}
-\end{definition}
-In a similar manner we can define the following distinct notion of a resource projection.
-\begin{definition}[Contravariant Projection] Let $\R = (\F, \O)$ be a resource theory with pre-order $\prec$.
-Then a \emph{contravariant resource projection} of $\R$ to a resource theory $\R'$ with pre-order $\prec'$, is a pair of mappings $\Pi_s, \Pi_o$, where $\Pi_s$ maps quantum states in $\R$ to quantum states in $\R'$, and $\Pi_o$ maps free operations in $\R$ into free operations in $\R'$.
-Moreover, these obey
-\begin{enumerate}
-        \item $\Pis(\rho_1) \prec' \Pis(\rho_2)$ implies that $\rho_1 \prec \rho_2$ .
-        \item  $\Pio(\E_1) \circ \Pio(\E_2) = \Pio(\E_1 \circ \E_2)$ for all free operations $\E_1, \E_2 \in \O$.
-    \end{enumerate}
-\end{definition}
-The use of covariant and contravariant here refers to direction of implication between the two pre-orders\footnote{ Also note that strictly these are not projections in the sense of $\Pi^2 = \Pi$, but are instead morphisms.
-Here our use of the term projection is motivated by the idea that one one generally loses information about $\R$ under the mapping.}.
-It is now clear that any resource monotone is a covariant projection, while the $\sigma$--fragments are contravariant projections of the magic theory.
-}
 
@@
 
-\begin{example}Let $\R = (\F,\O)$ be a resource theory, and let $\D \in \O$ be any free operation.
-Then we can define the following contravariant projection $\Pi_s( \rho) := \D(\rho)$ for all states $\rho$, and $\Pi_o (\E) = \E$.
-\ddd{[Explain why contravariant]}.
+\begin{example}.
 As a simple example, we can consider the thermal operations resource theory of thermodynamics, and take $\D$ to be the dephasing map that kills off coherences between energy eigenspaces.
@@
 
-We now justify the name $\sigma$-fragment for the subdivision of a magic theory $\R = (\F, \O)$, by establishing a resource projection which reduces $\R$ into any subtheory $(\F, \O_\sigma)$.
+We now justify the name $\sigma$--fragment for the subdivision of a magic theory $\R = (\F, \O)$, by establishing a resource projection which reduces $\R$ into any subtheory $(\F, \O_\sigma)$.
 \begin{proposition}
     Let $\R = (\F, \O)$ be a theory of magic.
-    Every $\sigma$-fragment $(\F, \O_\sigma)$ \ddd{defines a contravariant projection} of $\R$.
+    Every $\sigma$--fragment $(\F, \O_\sigma)$ \ddd{defines a contravariant projection} of $\R$.
 \end{proposition}
@@
 where $n$ noisy copies of magic state $\rho$ are converted to a single-copy magic state $\tau$.
-Identifying a symmetry of the distillation process responsible for leaving a state $\sigma$ invariant is equivalent with restricting the process to the $\sigma$-fragment $\O_\sigma$.
+Identifying a symmetry of the distillation process responsible for leaving a state $\sigma$ invariant is equivalent with restricting the process to the $\sigma$--fragment $\O_\sigma$.
 
-Mana is monotonic and additive in all $\sigma$-fragments as seen in~\cref{app:major}, so it provides a bound for distillation processes
+Mana is monotonic and additive in all $\sigma$--fragments as seen in~\cref{app:major}, so it provides a bound for distillation processes
 \begin{equation}
@@
 
-A new bound can be obtained in any $\sigma$-fragment by comparing the Lorenz curves of the initial and target states,
+A new bound can be obtained in any $\sigma$--fragment by comparing the Lorenz curves of the initial and target states,
 \begin{equation}\label{eq:majbound}
@@
 \end{equation}
-in the $\sigma$-fragment $\O_\sigma$.
+in the $\sigma$--fragment $\O_\sigma$.
 At noise level $\epsilon \leq \frac{3}{4}$, the Wigner distribution $\W{\rho_{\rm{S}}(\epsilon)}$ contains negativities and the state can be purified so as to obtain a single-copy state with sufficiently low $\epsilon$.
@@
 \end{equation}
-with $\epsilon_{\rm{th}}$ being the noise level threshold that does not prohibit the process for given number of copies $k$ and $\sigma$-fragment, parametrised by $p$ as a mixture of the zero and the maximally mixed states.
+with $\epsilon_{\rm{th}}$ being the noise level threshold that does not prohibit the process for given number of copies $k$ and $\sigma$--fragment, parametrised by $p$ as a mixture of the zero and the maximally mixed states.
 \begin{figure}
@@
     \caption{Plot of the noise level threshold ratios between mana and Lorenz curve for the Strange state purifying process in~\cref{eq:purify}.
-    The ratios are calculated for different numbers of initial state copies and different $\sigma$-fragments parametrised by $p$ such that $\sigma = (1-p)\ketbra{0} + p \frac{1}{3}\id$.
+    The ratios are calculated for different numbers of initial state copies and different $\sigma$--fragments parametrised by $p$ such that $\sigma = (1-p)\ketbra{0} + p \frac{1}{3}\id$.
     Lorenz curve comparison consistently gives stricter bounds as proven in~\cref{thm:bounds}.
@@
     Consider the distillation process in~\cref{eq:distprocess}.
-    In any $\sigma$-fragment, $\W{\sigma}$-majorization provides a stricter bound than mana.
+    In any $\sigma$--fragment, $\W{\sigma}$-majorization provides a stricter bound than mana.
 \end{theorem}
 \begin{proof}
-    The maximum of the Lorenz curve of a state $\rho$ can be expressed monotonically in terms of mana, independently of the $\sigma$-fragment,
+    The maximum of the Lorenz curve of a state $\rho$ can be expressed monotonically in terms of mana, independently of the $\sigma$--fragment,
     \begin{equation}

### 2020-06-17 magic_paper.tex
Composition condition for resource projection definitions needs more discussion

@@
 Therefore, two states, even if incomparable in $\R$, are always mapped onto ordered real numbers.
-We now generalise this idea to any projection of the theory that ensures a form of comparison between states.
+We now generalise this idea of a theory projection that preserves comparability between states.
 \begin{definition}[\textbf{Covariant projection}]\label{def:covproj}
@@
 	Consider a monotone $\M$ in the context of a general resource theory $\R = (\F, \O)$.
-	The defining property of a monotone, stated in~\cref{def:mono} ensures order preservation under state projection $\Pis$.	
-	Let $\Pio$ project any $\E \in \O$ onto a real non-increasing function $f$ mapping $\M(\rho)$ to $\M(\E(\rho))$ for all states $\rho$.
-	Then, the composition of functions is preserved under operation projection $\Pio$.	
+	The defining property of a monotone, seen in~\cref{def:mono} ensures order preservation under state projection $\Pis = \M$, where the pre-order $\prec_{\R'}$ is simply the total order $\leq$ of real numbers.
+
+	Let $\Pio$ project any $\E \in \O$ onto a real non-increasing function $f$ defined by mapping $\M(\rho)$ to $\M(\E(\rho))$ for every state $\rho$.
+	Then, composition of free opearations implies composition of their function projections. \nick{expand?}
+
 	The ordered pair $(\Pis, \Pio)$ is the covariant resource projection which corresponds to monotone $\M$.
@@
 On the other hand, $\sigma$--fragments are an example of reducing the structure of a magic theory $\R$ to a subtheory with a tractable pre-order.
-States which are incomparable in $\R$ remain incomparable, but transformations between comparable states may no longer be possible.
-We generalise the idea of reducing the structure of a theory into a simpler one, by introducing two types of resource projections.
+States which are incomparable in $\R$ remain incomparable, but conversions between states which are comparable in $\R$ may no longer be possible.
 \begin{definition}[\textbf{Contravariant projection}]\label{def:contraproj}
@@
 \end{definition}
+Note that a contravariant projection is always a surjective mapping for both states and operations, so that the conditions in~\cref{def:contraproj} make sense.
 The use of covariant and contravariant in~\cref{def:covproj,def:contraproj} refers to the direction of implication between the two pre-orders and operation compositions\footnote{Note that strictly these are not projections in the sense of $\Pi^2 = \Pi$, but are instead morphisms.
@@
 
-\begin{proposition}\label{thm:sigmaproj}
-    Let $\R = (\F, \O)$ be a theory of magic.
-    Every $\sigma$--fragment $(\F, \O_\sigma)$ is a contravariant fragment of $\R$.
+\begin{proposition}\label{thm:subproj}
+    Let $\R = (\F, \O)$ be a general resource theory. 
+    Then, any subtheory $\R' = (\F, \O')$ of $\R$, where $\O' \subseteq \O$, is a contravariant fragment of $\R$.    
 \end{proposition}
 \begin{proof}
-    Let the state projection $\Pis$ map all states onto themselves, so order preservation is trivially satisfied.    
-    Consider the operation projection $\Pio:\O \mapsto \O_\sigma$, defined as
+    We will establish a contravariant projection $(\Pis, \Pio)$ from $\R$ to $\R'$.
+    Let the state projection $\Pis$ map all states onto themselves and suppose that $\rho_1 \prec_{\R'} \rho_2$. 
+    Then, there exists $\E \in \O' \subseteq \O$ such that $\rho_1 = \E(\rho_2)$, therefore $\rho_1 \prec_{\R} \rho_2$ as well.
+
+    Consider the operation projection $\Pio:\O \mapsto \O'$, defined as
     \begin{equation}
@@
     \begin{cases}
-        \E,\ &\E \in \O_\sigma, \\
-        1_{\rm{C}},\ &\E \notin \O_\sigma.
+        \E,\ &\E \in \O', \\
+        1_{\rm{C}},\ &\E \notin \O',
     \end{cases}
     \end{equation}    
-    Since for any $\E_1, \E_2 \in \O_\sigma,$ it is also true that $\E_1 \circ \E_2 \in \O_\sigma$, operational composition is contravariantly preserved.
+    This projection ensures that operational composition is contravariantly preserved.
+    For any $\E_1, \E_2 \in \O'$, then $\E =\E_1 \circ \E_2 \in \O_\sigma$ as well, so $\E = \Pio(\E) = \Pio(\E_1) \circ \Pio(\E_2) = \E_1 \circ \E_2$.
+    If $\E_1 \notin \O'$ or $\E_2 \notin \O'$, then $\Pio(\E) \neq \Pio(\E_1) \circ \Pio(\E_2)$.
+
+    \nick{This does not hold in the case of all $\E, \E_1, \E_2 \notin \O'$. We need to update the composition condition in~\cref{def:contraproj}}
 \end{proof}
+As an immediate corollary of~\cref{thm:subproj}, a $\sigma$--fragment of any magic theory $\R$ is a contravariant fragment of $\R$.
 
 \begin{proposition}
-	Let $\R = (\F,\O)$ be a resource theory, and let $\D \in \O$ be a free operation, which is reversible by $\D_{\rm{rev}} \in \O$, so that $\D_{\rm{rev}} \circ \D = 1_{\rm{C}}$.
+	Let $\R = (\F,\O)$ be a resource theory, and let $\D \in \O$ be a free operation, which is reversible by $\D_{\rm{rev}} \in \O$, so that $\D_{\rm{rev}} \circ \D = \idc$.
 
-	Then, we can define a contravariant projection of $\R$, by acting with $\D$ on all states.
+	Then, we can define a contravariant projection of $\R$, by acting on all quantum states with $\D$.
 \end{proposition}
@@
 	We show that the theory $\R' = (\F', \O)$, with $\F' = \{\D(\rho):\rho \in \F \}$, is a contravariant fragment of $\R$.
-	Let $\Pis$ map every state $\rho$ to $\D(\rho)$.
-	Then, $\D(\rho_1) \prec \D(\rho_2)$ implies that there exists $\E \in \O$ such that $\rho_1 = (\D_{\rm{rev}} \circ \E \circ \D) (\rho_2)$, so the state order is preserved contravariantly.
+
+	Let $\Pis$ map every state $\rho$ to $\D(\rho)$ and suppose $\D(\rho_1) \prec \D(\rho_2)$. 
+	Then, there exists $\E \in \O$ such that $\rho_1 = (\D_{\rm{rev}} \circ \E \circ \D) (\rho_2)$, so $\rho_1 \prec \rho_2$.
 
@@
 
-\nick{If $\D$ is a recovery map, so that $\D \circ \D_{\rm{rev}} = 1_{\rm{C}}$, then this is a covariant projection instead.
+\nick{If $\D$ is a recovery map, so that $\D \circ \D_{\rm{rev}} = \idc$, then this is a covariant projection instead.
 
@@
         \E,\ &\sigma \in \O, \\
-        1_{\rm{C}},\ &\sigma \notin \O.
+        \idc,\ &\sigma \notin \O.
     \end{cases}

### 2020-06-18 magic_paper.tex
More blue comments to be addressed. Statements and proofs of abstract projections sharpened. Mana and Majorization subsection created.

@@
 \begin{equation}\label{eq:cj}
-    \frac{1}{d_A}\J_\E \coloneqq \frac{1}{d_A}(\id \otimes \E) \sum_{i,j} \ket{ii}\bra{jj}
+    \frac{1}{d_A}\J(\E) \coloneqq \frac{1}{d_A}(\id \otimes \E) \sum_{i,j} \ket{ii}\bra{jj}
 \end{equation}
@@
     \W[\bmy|\bmx]{\E} 
-    &\coloneqq d_A^2 \W[\bm{\bar x} \oplus \bmy]{\frac{1}{d_A}\J_\E} \\
+    &\coloneqq d_A^2 \W[\bm{\bar x} \oplus \bmy]{\frac{1}{d_A}\J(\E)} \\
     &= \frac{1}{d_B} \tr_B[A_{\bmy} \E(A_{\bmx})],
@@
     \caption{\textbf{Decomposition of a magic theory $\R$ intro $\sigma$--fragments.} 
-    Established theories involve operations within the yellow regions, following the hierarchy $\so \subset \cspo \subset \spo \subset \Omax$.
+    Examples of magic theories (SO: Stabilizer Operations, CSPO: Completely Positive Stabilizer Preserving Operations, SPO: Stabilizer Preserving Operations) involve operations within the yellow regions, following the hierarchy $\so \subset \cspo \subset \spo \subset \Omax$.
     We introduce fragments $\O_\sigma,\ \sigma \in \F$ that cover $\Omax$ with each one extending to a set of stochastic maps that allows for $\bmd$-majorization to be used.
+\ddd{[I think introducing the CSPO and SPO is overly complex here - best to keep things simple and clear.
+I'd delete them and only explain the terms used in the actual figure.]}
     }
@@
 The use of majorization in this setting provides useful intuition for our purposes.
-At any given temperature $\beta$, the thermal state $\gamma_\beta$ is thermodynamically the most ordered state. 
+At any given temperature $\beta$, the thermal state $\gamma_\beta$ is thermodynamically the most disordered state. 
 Thermal operations are defined as operations that cannot extract energy from the Gibbs state, $\E(\gamma_\beta) = \gamma_\beta$.
@@
 The pre-order $\prec_{\R'}$ of the $\sigma$--fragment $\R' = (\F, \O_\sigma)$ between $d$-dimensional states corresponds to the majorization pre-order $\prec_{\W{\sigma}}$ between their $d^2$-dimensional Wigner distributions.
+For simplicity we shall shorten this notation and use $\prec_\sigma$, as there is little risk of confusion.
+\ddd{[update any occurrences]}
 
@@
     Let $\R = (\F, \O)$ be a theory of magic.
-    Suppose the state conversion $\rho \xrightarrow{\E \in \O} \tau$ is possible, $\tau \prec_\R \rho$.
-    Then, there exists a full-rank free state $\sigma \in \F$ such that  $\W{\tau} \prec_{\W{\sigma}} \W{\rho}$.
+    Suppose the state conversion $\rho \xrightarrow{\E \in \O} \tau$ is possible.
+    Then, there exists a full-rank free state $\sigma \in \F$ such that  $\W{\tau} \prec_\sigma \W{\rho}$.
 
@@
 Resource monotones can now be clearly seen as covariant projections of resource theories.
-\begin{proposition}\label{thm:monoproj}
-	Let $\M$ be a resource monotone of a resource theory $\R$. 
-	Then $\M$ is a covariant projection that reduces the pre-order $\prec_\R$ to a total order.
+\begin{proposition}[Totally ordered covariant theories]\label{thm:monoproj}
+	Any $\M$ resource monotone of a resource theory $\R$ is a covariant projection for which $\prec_{\R'}$ is a total order, and conversely any such covariant project corresponds to a resource monotone $\M$.
 \end{proposition}
@@
 	Consider a monotone $\M$ in the context of a general resource theory $\R = (\F, \O)$.
-	The defining property of a monotone, seen in~\cref{def:mono} ensures order preservation under state projection $\Pis = \M$, where the pre-order $\prec_{\R'}$ is simply the total order $\leq$ of real numbers.
+	The defining property of a monotone, seen in~\cref{def:mono} ensures order preservation under state projection $\Pis = \M$, where the pre-order $\prec_{\R'}$ is simply the total order $\leq$ on $\mathbb{R}$.
+For the quantum operations, we simply choose $\Pio(\E) = 1_\times$, namely the `multiplication by 1' operation on real numbers.
+The definition of a resource monotone then automatically implies covariance.
+Conversely given any covariant projection of $\R$ we may map the totally ordered set of elements $\Pis(\rho)$ via an injective function $f$ into $\mathbb{R}$ for which $\M(\rho):=f(\Pi_s(\rho))$ provides a numerical value for each $\rho$ that obeys the required conditions for a resource monotone.
 
-	Let $\Pio$ project any $\E \in \O$ onto a real non-increasing function $f$ defined by mapping $\M(\rho)$ to $\M(\E(\rho))$ for every state $\rho$.
-	Then, composition of free opearations implies composition of their function projections. \nick{expand?}
-
-	The ordered pair $(\Pis, \Pio)$ is the covariant resource projection which corresponds to monotone $\M$.
 \end{proof}
@@
 \begin{proposition}\label{thm:subproj}
-    Let $\R = (\F, \O)$ be a general resource theory. 
-    Then, any subtheory $\R' = (\F, \O')$ of $\R$, where $\O' \subseteq \O$, is a contravariant fragment of $\R$.    
+    Let $\R = (\F, \O)$ be a resource theory, and let $\O' \subseteq \O$ be a non-empty subset of the free operations that is closed under composition, and moreover $\O'$ is the largest such subset, in the sense that for any $\E_1 \not \in \O'$ and any $\E_2 \in \O'$ we have that both $\E_1 \circ \E_2$ and $\E_2 \circ \E_1$ are not in $\O'$.
+Then $\R' = (\F, \O')$ of $\R$ defines a contravariant fragment of $\R$.
 \end{proposition}
 \begin{proof}
-    We will establish a contravariant projection $(\Pis, \Pio)$ from $\R$ to $\R'$.
-    Let the state projection $\Pis$ map all states onto themselves and suppose that $\rho_1 \prec_{\R'} \rho_2$. 
-    Then, there exists $\E \in \O' \subseteq \O$ such that $\rho_1 = \E(\rho_2)$, therefore $\rho_1 \prec_{\R} \rho_2$ as well.
+    We first define $\Pis (\rho) = \rho$ for all $\rho$.
+It is clear that since $\O'$ is a subset of $\O$ any operation in $\O'$ will map the set of free states into itself.
+Moreover the identity channel $id$ is necessarily in $\O'$, due to the maximality assumption.
+For $\Pio$ we let $\Pis(\E) = \E$ if $\E \in \O'$ and otherwise $\Pis(\E) =id$.
+Now consider $\Pio (\E_1 \circ \E_2)$.
+Either the triple $\{\E_1, \E_2, \E_1\circ \E_2\}$ are all in $\O'$ or they are all outside of $\O'$.
+For the former case $\Pio(\E_1 \circ \E_2) = \E_1 \circ \E_2 = \Pio(\E_1) \circ \Pio(\E_2)$, while for the latter $\Pio(\E_1 \circ \E_2) = id = \Pio(\E_1) \circ \Pio(\E_2)$, which proves that compositions are respected under the map.
+Finally, $\rho \prec_{R'} \sigma$ implies there exists $\E \in \O' \subseteq \O$ such that $ \E(\rho) = \sigma$, and since $\E \in \O$ this implies $\rho \prec _{\R} \sigma$, as required, which completes the proof.
 
-    Consider the operation projection $\Pio:\O \mapsto \O'$, defined as
-    \begin{equation}
-    \Pio(\E) =
-    \begin{cases}
-        \E,\ &\E \in \O', \\
-        1_{\rm{C}},\ &\E \notin \O',
-    \end{cases}
-    \end{equation}    
-    This projection ensures that operational composition is contravariantly preserved.
-    For any $\E_1, \E_2 \in \O'$, then $\E =\E_1 \circ \E_2 \in \O_\sigma$ as well, so $\E = \Pio(\E) = \Pio(\E_1) \circ \Pio(\E_2) = \E_1 \circ \E_2$.
-    If $\E_1 \notin \O'$ or $\E_2 \notin \O'$, then $\Pio(\E) \neq \Pio(\E_1) \circ \Pio(\E_2)$.
-
-    \nick{This does not hold in the case of all $\E, \E_1, \E_2 \notin \O'$. We need to update the composition condition in~\cref{def:contraproj}}
 \end{proof}
+\ddd{[The key method in proof-analysis is to first make any assumptions you want in order to get the result that you want...then you can later go back and see what assumptions can be weakened or dropped.]}
 As an immediate corollary of~\cref{thm:subproj}, a $\sigma$--fragment of any magic theory $\R$ is a contravariant fragment of $\R$.
@@
 \newpage
-
-\subsection{Fragments - OLD}
-
-\nick{OLD VERSION}
-
-Monotones reduce the structure of the resource theory $\R$ into a \emph{total} order on the real numbers.
-Therefore, two states, even if incomparable in $\R$, are always mapped onto ordered real numbers.
-This is a generic approach that ensures a form of comparison between states and resource quantification.
-However, motivated by $\sigma$--fragments in magic theories, it is clear that we can often reduce the theory by a less \nick{information-collapsing} projection into a subtheory $\R'$ which has a tractable pre-order $\R'$, as sketched in~\cref{fig:fragments}.
-\begin{figure}[t]
-    \centering
-    \includegraphics[height=3cm]{figs/fragments.pdf}
-    \caption{Fragments \nick{Split into subfigures}
-    }
-    \label{fig:fragments}
-\end{figure}
-We define such a resource projection for general resource theories as follows.
-\begin{definition}[\textbf{Resource projection}]\label{def:fragment}
-    Let a resource theory $\R = (\F, \O)$ have pre-order $\prec_{\R}$ and operational composition rule $\circ_{\R}$. 
-    Any subtheory $\R' = (\F', \O')$ with pre-order $\prec_{\R'}$ and operational composition rule $\circ_{\R'}$ is called a resource fragment iff there exists a surjective projection $\Pi \equiv (\Pis, \Pio): \R \mapsto \R'$ that satisfies the following two conditions.
-    \begin{enumerate}
-        \item $\Pis: \D \mapsto \D$ and $\Pis(\rho_2) \nprec_{\R'} \Pis(\rho_1)$ whenever $\rho_1 \prec_{\R} \rho_2$;
-        \item $\Pio: \O \mapsto \O'$ and $\Pio(\E_1) \circ_{\R'} \Pio(\E_2) = \Pio(\E_1 \circ_{\R} \E_2)$ for all free operations $\E_1, \E_2 \in \O$.
-    \end{enumerate}
-    We call $\Pi$ a resource projection.
-\end{definition}
-
-\ddd{[I think the following might be the right way to understand things, using the notion of ``covariant'' and ``contravariant''.]}
-
-Fragment $\R'$ is the image of the projection $\Pi$.
-Considering a resource projection is particularly useful when the pre-order of the fragment is tractable.
-Note the subtle difference of condition 1 in~\cref{def:fragment} and condition 2 in~\cref{def:mono}, which is due to fragments generally retaining a pre-order, while monotones impose a total order.
-
-\ddd{[If you agree with the covariant-contravariant definitions above then you can update the following results using the new terminology.]}
-A monotone is the projection with the simplest tractable order as formally stated in~\cref{thm:monofrag}.
-\begin{proposition}\label{thm:monofrag}
-	Let $\M$ be a resource monotone of a resource theory $\R$. 
-	Then $\M$ is a resource projection that reduces the pre-order $\prec_\R$ to a total order.
-\end{proposition}
-\begin{proof}
-	Consider a monotone $\M$ in the context of a general resource theory $\R = (\F, \O)$.
-	Let $\R' = (\F', \O')$, where $\F' \equiv \{0\}$ and $\O'$ is the set of non-increasing real functions mapping the set of non-negative real numbers $\mathbb{R}_{\geq 0}$ to itself. 
-	We also set $\prec_{\R'}$ as the usual total order $\leq$ and $\circ_{\R'}$ as the composition of real functions.
-
-	Let $\Pis = \M$.
-	The defining properties of a monotone, given in~\cref{def:mono}, ensure condition 1 of~\cref{def:fragment}. \nick{expand}
-
-	Let $\Pio$ project any $\E \in \O$ onto a function $f \in \O$ which maps $\M(\rho)$ onto $\M(\E(\rho))$ for all states $\rho$.
-
-	The ordered pair $(\Pis, \Pio)$ is the resource projection which corresponds to monotone $\M$.
-\end{proof}
-
-\begin{example}.
+%
+%\subsection{Fragments - OLD}
+%
+%\nick{OLD VERSION}
+%
+%Monotones reduce the structure of the resource theory $\R$ into a \emph{total} order on the real numbers.
+%Therefore, two states, even if incomparable in $\R$, are always mapped onto ordered real numbers.
+%This is a generic approach that ensures a form of comparison between states and resource quantification.
+%However, motivated by $\sigma$--fragments in magic theories, it is clear that we can often reduce the theory by a less \nick{information-collapsing} projection into a subtheory $\R'$ which has a tractable pre-order $\R'$, as sketched in~\cref{fig:fragments}.
+%\begin{figure}[t]
+%    \centering
+%    \includegraphics[height=3cm]{figs/fragments.pdf}
+%    \caption{Fragments \nick{Split into subfigures}
+%    }
+%    \label{fig:fragments}
+%\end{figure}
+%We define such a resource projection for general resource theories as follows.
+%\begin{definition}[\textbf{Resource projection}]\label{def:fragment}
+%    Let a resource theory $\R = (\F, \O)$ have pre-order $\prec_{\R}$ and operational composition rule $\circ_{\R}$. 
+%    Any subtheory $\R' = (\F', \O')$ with pre-order $\prec_{\R'}$ and operational composition rule $\circ_{\R'}$ is called a resource fragment iff there exists a surjective projection $\Pi \equiv (\Pis, \Pio): \R \mapsto \R'$ that satisfies the following two conditions.
+%    \begin{enumerate}
+%        \item $\Pis: \D \mapsto \D$ and $\Pis(\rho_2) \nprec_{\R'} \Pis(\rho_1)$ whenever $\rho_1 \prec_{\R} \rho_2$;
+%        \item $\Pio: \O \mapsto \O'$ and $\Pio(\E_1) \circ_{\R'} \Pio(\E_2) = \Pio(\E_1 \circ_{\R} \E_2)$ for all free operations $\E_1, \E_2 \in \O$.
+%    \end{enumerate}
+%    We call $\Pi$ a resource projection.
+%\end{definition}
+%
+%\ddd{[I think the following might be the right way to understand things, using the notion of ``covariant'' and ``contravariant''.]}
+%
+%Fragment $\R'$ is the image of the projection $\Pi$.
+%Considering a resource projection is particularly useful when the pre-order of the fragment is tractable.
+%Note the subtle difference of condition 1 in~\cref{def:fragment} and condition 2 in~\cref{def:mono}, which is due to fragments generally retaining a pre-order, while monotones impose a total order.
+%
+%\ddd{[If you agree with the covariant-contravariant definitions above then you can update the following results using the new terminology.]}
+%A monotone is the projection with the simplest tractable order as formally stated in~\cref{thm:monofrag}.
+%\begin{proposition}\label{thm:monofrag}
+%	Let $\M$ be a resource monotone of a resource theory $\R$. 
+%	Then $\M$ is a resource projection that reduces the pre-order $\prec_\R$ to a total order.
+%\end{proposition}
+%\begin{proof}
+%	Consider a monotone $\M$ in the context of a general resource theory $\R = (\F, \O)$.
+%	Let $\R' = (\F', \O')$, where $\F' \equiv \{0\}$ and $\O'$ is the set of non-increasing real functions mapping the set of non-negative real numbers $\mathbb{R}_{\geq 0}$ to itself. 
+%	We also set $\prec_{\R'}$ as the usual total order $\leq$ and $\circ_{\R'}$ as the composition of real functions.
+%	
+%	Let $\Pis = \M$.
+%	The defining properties of a monotone, given in~\cref{def:mono}, ensure condition 1 of~\cref{def:fragment}. \nick{expand}
+%	
+%	Let $\Pio$ project any $\E \in \O$ onto a function $f \in \O$ which maps $\M(\rho)$ onto $\M(\E(\rho))$ for all states $\rho$.
+%	
+%	The ordered pair $(\Pis, \Pio)$ is the resource projection which corresponds to monotone $\M$.
+%\end{proof}
+%
+%\begin{example}.
 As a simple example, we can consider the thermal operations resource theory of thermodynamics, and take $\D$ to be the dephasing map that kills off coherences between energy eigenspaces.
 Then the resource projection $\R'$ induced by $\D$ is fully described by the thermo-majorization pre-order on distributions over energies.
-\end{example}
-
-We now justify the name $\sigma$--fragment for the subdivision of a magic theory $\R = (\F, \O)$, by establishing a resource projection which reduces $\R$ into any subtheory $(\F, \O_\sigma)$.
-\begin{proposition}
-    Let $\R = (\F, \O)$ be a theory of magic.
-    Every $\sigma$--fragment $(\F, \O_\sigma)$ \ddd{defines a contravariant projection} of $\R$.
-\end{proposition}
-\begin{proof}
-    Let the state projection be the identity projection $\Pis:\D\mapsto\D$.
-
-    Consider the operation projection $\Pio:\O \mapsto \O_\sigma$, defined as
-    \begin{equation}
-    \Pio(\E) =
-    \begin{cases}
-        \E,\ &\sigma \in \O, \\
-        \idc,\ &\sigma \notin \O.
-    \end{cases}
-    \end{equation}
-    \nick{$\Pio$ should be different, this here is not right.
+%\end{example}
+%
+%We now justify the name $\sigma$--fragment for the subdivision of a magic theory $\R = (\F, \O)$, by establishing a resource projection which reduces $\R$ into any subtheory $(\F, \O_\sigma)$.
+%\begin{proposition}
+%    Let $\R = (\F, \O)$ be a theory of magic.
+%    Every $\sigma$--fragment $(\F, \O_\sigma)$ \ddd{defines a contravariant projection} of $\R$.
+%\end{proposition}
+%\begin{proof}
+%    Let the state projection be the identity projection $\Pis:\D\mapsto\D$.
+%    
+%    Consider the operation projection $\Pio:\O \mapsto \O_\sigma$, defined as
+%    \begin{equation}
+%    \Pio(\E) =
+%    \begin{cases}
+%        \E,\ &\sigma \in \O, \\
+%        \idc,\ &\sigma \notin \O.
+%    \end{cases}
+%    \end{equation}
+%    \nick{$\Pio$ should be different, this here is not right.
 If we need to project every $\E \in \O$, we may need a different condition on $\Pio$ than $\Pio(\E_1) \circ_{\R'} \Pio(\E_2) = \Pio(\E_1 \circ_{\R} \E_2)$.}
-    The ordered pair $(\Pis, \Pio)$ acts as the desired projection.
-\end{proof}
-
-An important example of a fragment appears in quantum thermodynamics. 
-Consider a projection $\Pi$, such that $\Pis$ dephases all states in the energy eigenbasis, while $\Pio$ maps all free operations to themselves.
-Then $\Pi$ describes the theory in the absence of coherences and the new pre-order is simply thermo-majorization, which in fact is fully solvable in the form of entropic conditions~\cite{cit:gour}.
+%    The ordered pair $(\Pis, \Pio)$ acts as the desired projection.
+%\end{proof}
+%
+%An important example of a fragment appears in quantum thermodynamics. 
+%Consider a projection $\Pi$, such that $\Pis$ dephases all states in the energy eigenbasis, while $\Pio$ maps all free operations to themselves.
+%Then $\Pi$ describes the theory in the absence of coherences and the new pre-order is simply thermo-majorization, which in fact is fully solvable in the form of entropic conditions~\cite{cit:gour}.
 \nick{expand/rephrase}
-
-Existing magic theories can be thought of as fragments of $\Rmax$.
-\begin{proposition}
-    Every theory of magic $\R$ is a fragment of the maximal theory $\Rmax$.
-\end{proposition}
-\begin{proof}
-    \nick{We need a state projection that establishes that some free states are not free any more $+$ an operations projection.}
-\end{proof}
-
-\ddd{[Is there a way to view Nielsen's theorem as describing a projection of the full mixed state LOCC entanglement theory?
+%
+%Existing magic theories can be thought of as fragments of $\Rmax$.
+%\begin{proposition}
+%    Every theory of magic $\R$ is a fragment of the maximal theory $\Rmax$.
+%\end{proposition}
+%\begin{proof}
+%    \nick{We need a state projection that establishes that some free states are not free any more $+$ an operations projection.}
+%\end{proof}
+%
+%\ddd{[Is there a way to view Nielsen's theorem as describing a projection of the full mixed state LOCC entanglement theory?
 Is really not essential but might be nice to include.
 Send $\rho_{AB} $ to the most entangled pure state in its eigendecomposition?]}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-Mana is monotonic and additive in all $\sigma$--fragments as seen in~\cref{app:major}, so it provides a bound for distillation processes
+\subsection{Mana and Majorization}
+We now discuss majorization features common to all fragments, before specialising to particular $\sigma$--fragments and how analysis in them preceeds.
+Mana is the basic resource monotone for magic.
+Here we show that its basic properties are actually special cases of more general majorization features.
+More precisely its properties can be viewed as majorization-based, and independent of the particular $\sigma$--fragment one works in.
+
+As discussed above, we know that every magic interconversion problem can be analysed across all $\sigma$--fragments and moreover the pre-order in each fragment is exactly specified by $d$--majorization.We now note the following equivalent formulations of $d$--majorization.
+\begin{theorem}
+Given $\bmx, \bmy, \bmd \in \mathbb{R}^n$, such that the components of $\bmd$ are positive, the following statements are equivalent:
+ \begin{enumerate}%[\rm{(TM1)}]
+	\item $\bmx \prec_{\bmd} \bmy$;
+	\item $\Gamma_{\bmd}({\bmx}) \prec \Gamma_{\bmd}({\bmy})$;
+	\item\label{en:tm3} $\sum\limits_{i=1}^n \abs{x_i - t d_i} \leq \sum\limits_{i=1}^n \abs{y_i - t d_i}$ for all $t \in \mathbb{R}$;
+	\item $\sum\limits_{i=1}^n (x_i - t d_i)^+ \leq \sum\limits_{i=1}^n (y_i - t d_i)^+$ for all $t \in \mathbb{R}$ and $\sum\limits_{i=1}^n x_i = \sum\limits_{i=1}^n y_i$;
+	\item $\forall k, L_{\bmx|\bmd}(k) \leq L_{\bmy|\bmd}(k)$ and $L_{\bmx|\bmd}(k=n) = L_{\bmy|\bmd}(k=n)$.
+ \end{enumerate}
+\end{theorem}
+However, statement 3 implies that if we take $t=0$ then we see that this becomes that $\mbox{mana}(\rho) \ge \mbox{mana}(\sigma)$. \ddd{[expand/tidy this]}
+
+\ddd{[I didn't follow your mana is additive argument]}
+so it provides a bound for distillation processes
 \begin{equation}

### 2020-06-18 magic_paper.tex
Some small additional things improved. Blended majorization and Wigner functions a bit more. More needed.

@@
 
-\subsection{Majorization in the $\sigma$--fragments}\label{sec:major}
+\subsection{Majorization of quasi-probabilities in the $\sigma$--fragments}\label{sec:major}
 
@@
 A restatement of the theorem including more equivalent conditions, along with a proof is provided in the \nick{appendix}.
+
+\subsection{Lorenz curves for magic states in a $\sigma$--fragment}
+With this it is straightforward to construct Lorenz curves for Wigner distributions in any $\sigma$--fragment.
+For any $\sigma$ being a full rank free state we have that $W_\sigma(\bmx) $ is a strictly positive full-rank probability distribution, and so one can define a corresponding notion of $d$--majorization on \emph{quasi}--distributions.We write $L_{\rho|\sigma}(x)$ for the Lorenz curve of $W_\rho(\bmx)$ with respect to $W_\sigma(\bmx)$.
+
+We now see that $0\le L_{\rho |\sigma}(x) \le 1$ for all $x$ if and only if $\rho$ is a positive Wigner state.
+Moreover, the area of the function $L_{\rho|\sigma}$ above the line $y=1$ is a resource monotone in this fragment.
+\ddd{[expand on this -- relate to mana?]}
 
@@
 Important examples of resource fragments appear in several established resource theories.
-\nick{Need to check if the thermodynamics example works, include magic theories as fragments of $\Rmax$, include Nielsen's bipartite entanglement.}
+\nick{Need to check if the thermodynamics example works, include magic theories as fragments of $\Rmax$, include Nielsen's bipartite entanglement.} \ddd{[Don't worry about these things now -- let's get the computations section improved]}
 
@@
 
-\subsection{Mana and Majorization}
+\subsection{Magic, Mana and Majorization}
 We now discuss majorization features common to all fragments, before specialising to particular $\sigma$--fragments and how analysis in them preceeds.
@@
 \end{equation}
+\ddd{[We can probably put upper and lower bounds on this value fairly readily.
+E.g.
+using known sum rules.
+Also -- bad choice of variable $k$, using it as index and also copy number.
+I think $L_{\rho|\sigma}$ is a neater formulation, since you then package things into a single object -- a function.]}
 

### 2020-06-18 magic_paper.tex
Left technical comments in red. Need to generalise discussion of distillation process to general state conversations and fix proof of theorem 13, then add subsections on different fragments

--- 2020-06-18 magic_paper.tex
@@
     }
-    \caption{Wigner distributions for qutrit states of varying magic. 
+    \caption{\textbf{Qutrit Wigner distributions of varying magic.} 
     \subref{fig:maxmix} Maximally mixed state $\frac{1}{3}\id$; \subref{fig:zero} Stabilizer zero state $\ketbra{0}{0}$; \subref{fig:bound} A non-stabilizer Wigner-positive state; \subref{fig:strange} Magic strange state $\ket{{\rm{S}}} = \frac{1}{\sqrt{2}}(\ket{1} - \ket{2})$.
@@
 For technical simplicity in what follows we assume that $\F$ is a closed set, and note that $\F_{\mbox{\tiny max}}$ is itself a closed set, since it is specified by a finite set of linear constraints of the form $\tr [ L\rho] \ge 0$ with $L \in \mathcal{B}(\mathcal{H})$.
+\nick{Unfortunately, this is not enough. 
+There are positive Wigner ditributions which correspond to invalid states i.e. they are NOT positive semi-definite.
+Therefore, there are ``holes'' in the set specified by these linear constraints.
+We need a stricter argument.}
 
@@
 \end{equation}
-Therefore, $\rho\longrightarrow \tau$ in $\R$ if and only if $\rho\longrightarrow \tau$ in a $\sigma$--fragment of $\R$.
+Therefore, $\rho \longrightarrow \tau$ in $\R$ if and only if $\rho \longrightarrow \tau$ in a $\sigma$--fragment of $\R$.
 \end{theorem}
 \begin{proof}
-    Suppose $\E$ is in $\O_\sigma$, then it is also in $\O$, hence $\bigcup\limits_{\sigma \in \F} \O_\sigma \subseteq \O$. Conversely, suppose $\E$ is in $\O$. 
+    Suppose $\E$ is in a $\sigma$--fragment $\O_\sigma$.
+    Then it is also in $\O$, hence $\bigcup\limits_{\sigma \in \F} \O_\sigma \subseteq \O$.
+
+    Conversely, suppose $\E$ is in $\O$. 
     The free states are a closed set that is mapped one-to-one to a closed subset $\cal{S}$ of the $(d^2 - 1)$-dimensional probability simplex.
     $\cal{S}$ is convex, since any combination of free states is also free and the Wigner distribution is linear.
-    Therefore, $\cal{S}$ is convex and compact as a convex subset of the bounded compact probability simplex.
-    Then, $\W{\E}{}$ is a stochastic, continuous, mapping from $\cal{S}$ to itself and so Brouwer's fixed point theorem \nick{CITE} implies that there exists a probability distribution $g_{\bmz}$ for some $ \bmz \in \pd$ that is a fixed point of $\W{\E}{}$.
-    This corresponds to an operator $\sigma \coloneqq \sum_{\bmz \in \pd} g_{\bmz} A_{\bmz}$  which is a state in $\F$.
+    Therefore, $\cal{S}$ is convex and compact as a closed convex subset of the bounded compact probability simplex.
+
+    We can now view $\W{\E}$ as a stochastic, continuous mapping from $\cal{S}$ to itself, thus Brouwer's fixed point theorem \nick{CITE} implies that there exists a probability distribution $d_{\bmz}$ for some $ \bmz \in \pd$ that is a fixed point of $\W{\E}$.
+    This corresponds to a free state $\sigma \coloneqq \sum_{\bmz \in \pd} d_{\bmz} A_{\bmz} \in \F$. 
     Therefore $\E \in \O_\sigma$, and so $\O = \bigcup\limits_{\sigma \in \F} \O_\sigma$.
+
     The state interconversion result follows immediately.
@@
     \caption{\textbf{Decomposition of a magic theory $\R$ intro $\sigma$--fragments.} 
-    Examples of magic theories (SO: Stabilizer Operations, CSPO: Completely Positive Stabilizer Preserving Operations, SPO: Stabilizer Preserving Operations) involve operations within the yellow regions, following the hierarchy $\so \subset \cspo \subset \spo \subset \Omax$.
-    We introduce fragments $\O_\sigma,\ \sigma \in \F$ that cover $\Omax$ with each one extending to a set of stochastic maps that allows for $\bmd$-majorization to be used.
-\ddd{[I think introducing the CSPO and SPO is overly complex here - best to keep things simple and clear.
-I'd delete them and only explain the terms used in the actual figure.]}
+    Examples of magic theories ($\so$: Stabilizer operations, $\Omax$: Completely positive-Wigner-preserving operations) involve operations within the yellow regions, with all other established magic theories between these two.
+    We introduce $\sigma$--fragments $\O_\sigma$ defined for all free states $\sigma$ that cover $\Omax$ with each one extendible to a set of stochastic maps outside the $\cptp$ operations.
+    Within each $\sigma$--fragment $\bmd$-majorization can be used allowing for an \nick{in-depth approach} towards the study of magic state interconversion.
     }
@@
 
-The subdivision of magic theories into $\sigma$--fragments is powerful because the pre-order $\prec_{\R'}$ of every $\sigma$--fragment is described by well-behaved majorization tools, as we establish in~\cref{sec:major}.
-\nick{expand}
+The subdivision of magic theories into $\sigma$--fragments is powerful because the pre-order $\prec_{\R_\sigma}$ of every $\sigma$--fragment is described by well-behaved majorization tools, as we establish in~\cref{sec:major}.
 
@@
 
-Majorization is a powerful tool that has recently found many applications in quantum information theory \nick{CITE}.
+Majorization is a collection of powerful tools that has recently found many applications in quantum information theory \nick{CITE}.
 It can describes the \nick{disorder / non-uniformity} of distributions that undergo stochastic transformations.
@@
 
-The pre-order $\prec_{\R'}$ of the $\sigma$--fragment $\R' = (\F, \O_\sigma)$ between $d$-dimensional states corresponds to the majorization pre-order $\prec_{\W{\sigma}}$ between their $d^2$-dimensional Wigner distributions.
-For simplicity we shall shorten this notation and use $\prec_\sigma$, as there is little risk of confusion.
-\ddd{[update any occurrences]}
+The pre-order $\prec_{\R_\sigma}$ of the $\sigma$--fragment $\R_\sigma = (\F, \O_\sigma)$ between $d$-dimensional states corresponds to the majorization pre-order $\prec_{\W{\sigma}}$ between their $d^2$-dimensional Wigner distributions.
+For simplicity we shall merge this notation into $\prec_\sigma$, as there is little risk of confusion.
 
 \begin{theorem}
-    Let $\R = (\F, \O)$ be a theory of magic.
-    Suppose the state conversion $\rho \xrightarrow{\E \in \O} \tau$ is possible.
+    Let $\R = (\F, \O)$ be a theory of magic and suppose the state conversion $\rho \longrightarrow \tau$ is possible.
     Then, there exists a full-rank free state $\sigma \in \F$ such that  $\W{\tau} \prec_\sigma \W{\rho}$.
@@
 Let the vector $\bmz^\downarrow$ denote a component permutation of vector $\bmz \in \reals^d$, so that its components are arranged in non-increasing order.
-\begin{definition}[\textbf{Lorenz curve}]
+\begin{definition}[\textbf{Lorenz curve}]\label{def:lc}
     Let $\bmz \in \reals^d$.
@@
 Lorenz curves of quasi-probability distributions in principle reach above 1.
-\ddd{[It is usually better to convert the Lorenz curve into a \emph{function} $L_{\bmz|\bmd}(x)$ defined on $[0,1]$.
-Then the majorization simply becomes the functional inequality $L_{\bmz|\bmd}(x) \ge L _{\bmy|\bmd}(x)$ for all $x$.]}
+
+\emph{Remark 5.} We can recast the Lorenz curve into the \emph{function} $L_{\bmz|\bmd}(x)$ defined on $[0,1]$.
 
@@
 \end{theorem}
-A restatement of the theorem including more equivalent conditions, along with a proof is provided in the \nick{appendix}.
+A restatement of the theorem including more equivalent conditions, along with a proof is provided in~\cref{app:major}.
 
-An example of comparison between different Lorenz curves is illustrated in~\cref{fig:lctoy}.
+An example of comparison between different Lorenz curves is illustrated in~\cref{fig:lctoy}. \nick{expand}
 \begin{figure}
@@
 State convertibility within a given resource theory is often a hard question to address due to the intricate structure of the theory.
-In general, the structure of a theory $\R$ is described by a pre-order $\prec_\R$ \nick{expand / move to intro}.
-Subdividing magic theories into $\sigma$--fragments \nick{helps}.
+In general, the structure of a theory $\R$ is described by a pre-order $\prec_\R$ and usually resource monotones are employed to reduce this structure into a simple real number ordering\nick{CITE}.
+The subdivisions of magic theories into $\sigma$--fragments suggests a new approach towards investigating state convertibility which retains more structure of the origin theory than a measure can.
+
 \subsection{Monotones}\label{sec:mono}
 
-Resource theories are commonly equipped with monotones which quantify the resource\nick{CITE}. 
+We highlight the defining property of a monotone for the discussion that follows.
 \begin{definition}[\textbf{Resource monotone}]\label{def:mono}
@@
 The monotonicity condition reflects the no resource generating property of free operations, so that monotones respect the pre-order $\prec_\R$ of the theory.
-Furthermore, if a monotone satisfies the additivity condition,
+Furthermore, a monotone may also satisfy the additivity condition,
 \begin{equation}
-    \M(\rho_1 \otimes \rho_2) = \M(\rho_1) + \M(\rho_2),
+    \M(\rho_1 \otimes \rho_2) = \M(\rho_1) + \M(\rho_2).
 \end{equation}
-it is of practical importance for resource distillation, which we discuss in~\cref{sec:distill} within the context of magic.
+This optional condition is of practical importance for resource distillation, which we discuss in~\cref{sec:distill} within the context of magic.
 
-A very commonly used magic monotone is the \emph{mana} of a state \nick{CITE}, defined as
+The most fundamental and commonly used magic monotone is the \emph{mana} of a state \nick{CITE}, defined as
 \begin{equation}
@@
 \end{equation}
-It is a monotone, additive function of the $\ell_1$-norm of negativity~\nick{CITE}.
+It is a monotone function of the $\ell_1$-norm of state negativity~\nick{CITE} that satisfies the additivity condition.
 
@@
 Let $\R = (\F, \O)$ be a resource theory with pre-order $\prec_\R$. 
-Then a \emph{covariant resource projection} of $\R$ into a resource theory $\R'$ with pre-order $\prec_{\R'}$, is a pair of mappings $(\Pi_s, \Pi_o)$, where $\Pi_s$ maps quantum states in $\R$ into quantum states in $\R'$, and $\Pi_o$ maps free operations in $\R$ into free operations in $\R'$.
+Then a \emph{covariant resource projection} of $\R$ to a resource theory $\R'$ with pre-order $\prec_{\R'}$, is a pair of mappings $(\Pi_s, \Pi_o)$, where $\Pi_s$ maps quantum states in $\R$ to quantum states in $\R'$, and $\Pi_o$ maps free operations in $\R$ to free operations in $\R'$.
 Moreover, these obey
 	\begin{enumerate}
-        \item $\Pis(\rho_2) \prec_{\R'} \Pis(\rho_1)$ whenever $\rho_1 \prec_\R \rho_2$;
+        \item $\Pis(\rho_1) \prec_{\R'} \Pis(\rho_2)$ whenever $\rho_1 \prec_\R \rho_2$;
         \item $\Pio(\E) = \Pio(\E_1) \circ \Pio(\E_2)$ whenever $\E = \E_1 \circ \E_2$.
@@
 
-Resource monotones can now be clearly seen as covariant projections of resource theories.
-\begin{proposition}[Totally ordered covariant theories]\label{thm:monoproj}
-	Any $\M$ resource monotone of a resource theory $\R$ is a covariant projection for which $\prec_{\R'}$ is a total order, and conversely any such covariant project corresponds to a resource monotone $\M$.
+Resource monotones can now be clearly seen as a special case of covariant resource projections.
+\begin{proposition}[\textbf{Totally ordered covariant theories}]\label{thm:monoproj}
+	Any resource monotone $\M$ of a resource theory $\R$ is a covariant projection for which $\prec_{\R'}$ is a total order. 
+	Conversely, any such covariant projection corresponds to a resource monotone $\M$. 
 \end{proposition}
@@
 	Consider a monotone $\M$ in the context of a general resource theory $\R = (\F, \O)$.
-	The defining property of a monotone, seen in~\cref{def:mono} ensures order preservation under state projection $\Pis = \M$, where the pre-order $\prec_{\R'}$ is simply the total order $\leq$ on $\mathbb{R}$.
-For the quantum operations, we simply choose $\Pio(\E) = 1_\times$, namely the `multiplication by 1' operation on real numbers.
+	State order is covariantly preserved due to the defining property of a monotone, seen in~\cref{def:mono}, where the pre-order $\prec_{\R'}$ is simply the total order $\leq$ on $\mathbb{R}$.
+
+	Operational composition is covariantly preserved when we simply choose $\Pio(\E) = 1_\times$, namely the `multiplication by 1' operation on real numbers. 
 	The definition of a resource monotone then automatically implies covariance.
-Conversely given any covariant projection of $\R$ we may map the totally ordered set of elements $\Pis(\rho)$ via an injective function $f$ into $\mathbb{R}$ for which $\M(\rho):=f(\Pi_s(\rho))$ provides a numerical value for each $\rho$ that obeys the required conditions for a resource monotone.
+
+	Conversely, given any covariant projection of $\R$ for which $\prec_{\R'}$ is a total order, we may map the totally ordered set of elements $\Pis(\rho)$ via an injective, non-decreasing function $f$ into $\mathbb{R}$.
+	Then, $\M(\rho):=f(\Pi_s(\rho))$ provides a numerical value for each $\rho$ that obeys the defining monotone condition.
 
@@
 
-On the other hand, $\sigma$--fragments are an example of reducing the structure of a magic theory $\R$ to a subtheory with a tractable pre-order.
-States which are incomparable in $\R$ remain incomparable, but conversions between states which are comparable in $\R$ may no longer be possible.
+We can also view $\sigma$--fragments as an example of reducing the structure of a magic theory $\R$ to a subtheory with a tractable pre-order.
+However, states which are incomparable in $\R$ remain incomparable and conversions between states which are comparable in $\R$ may no longer be possible.
 \begin{definition}[\textbf{Contravariant projection}]\label{def:contraproj}
@@
 \end{proof}
-\ddd{[The key method in proof-analysis is to first make any assumptions you want in order to get the result that you want...then you can later go back and see what assumptions can be weakened or dropped.]}
+\nick{The above proposition is not relevant to $\sigma$-fragments where ``for any $\E_1 \not \in \O_\sigma$ and any $\E_2 \in \O_\sigma$'' we sometimes have $\E_1 \circ \E_2 \in \O_\sigma$ as well as $\E_2 \circ \E_1 \in \O_\sigma$ and sometimes $\E_1 \circ \E_2 \notin \O_\sigma$ as well as $\E_2 \circ \E_1 \notin \O_\sigma$}
 As an immediate corollary of~\cref{thm:subproj}, a $\sigma$--fragment of any magic theory $\R$ is a contravariant fragment of $\R$.
@@
 
-\section{Distillation bounds}
+\section{Magic state interconversion and Lorenz curves}
 \label{sec:distill}
 
-Consider a general magic state distillation process,
+Any quantum circuit aiming at a given magic state conversion $\rho \longrightarrow \tau$ possesses certain symmetries according to~\cref{thm:frag} that allow us to study the conversion within only certain $\sigma$-fragments.
+As a simple example, the dephasing channel
+\begin{equation}
+	\Delta(\rho) = \sum_{k \in \zd} \ketbra{k}{k}\rho\ketbra{k}{k}
+\end{equation}
+removes coherent phases in the computational basis and therefore only leaves invariant mixtures of computational basis states.
+If the circuit simply consists of such dephasing channels, the whole analysis could be restricted in the $\sigma$--fragments for pure computational basis states $\sigma$.
+
+Lorenz curves provide a very efficient method of numerically checking if a certain state conversion is impossible within a $\sigma$--fragment by exploiting the equivalence with $d$--majorization stated in~\cref{thm:dmajor}.
+Such methods are often more conclusive than magic monotones as we discuss in section~\cref{sec:scmana}.
+
+\subsection{Mana and Majorization}\label{sec:scmana}
+We now discuss majorization features common to all fragments, before specialising to particular $\sigma$--fragments and how analysis in them proceeds. 
+Mana is the fundamental resource monotone for magic. 
+Here we show that its properties are in fact special cases of more general majorization features. 
+More precisely, its properties can be viewed as majorization-based, and independent of the particular $\sigma$--fragment one works in.
+
+As discussed above, we know that every magic interconversion problem can be analysed across all $\sigma$--fragments that reflect symmetries of the circuit and moreover the pre-order in each such fragment is exactly specified by $d$--majorization.
+
+Consider a general magic state distillation process, \nick{Generalise discussion to any state conversion?}
 \begin{equation}\label{eq:distprocess}
-    \rho^{\otimes k} \xrightarrow{\E \in \O} \tau,
+    \rho^{\otimes k} \longrightarrow \tau,
 \end{equation}
-where $n$ noisy copies of magic state $\rho$ are converted to a single-copy magic state $\tau$.
-Identifying a symmetry of the distillation process responsible for leaving a state $\sigma$ invariant is equivalent with restricting the process to the $\sigma$--fragment $\O_\sigma$.
+where $k$ noisy copies of magic state $\rho$ are converted to a single-copy magic state $\tau$.
 
-\subsection{Mana and Majorization}
-We now discuss majorization features common to all fragments, before specialising to particular $\sigma$--fragments and how analysis in them preceeds.
-Mana is the basic resource monotone for magic.
-Here we show that its basic properties are actually special cases of more general majorization features.
-More precisely its properties can be viewed as majorization-based, and independent of the particular $\sigma$--fragment one works in.
-
-As discussed above, we know that every magic interconversion problem can be analysed across all $\sigma$--fragments and moreover the pre-order in each fragment is exactly specified by $d$--majorization.We now note the following equivalent formulations of $d$--majorization.
-\begin{theorem}
-Given $\bmx, \bmy, \bmd \in \mathbb{R}^n$, such that the components of $\bmd$ are positive, the following statements are equivalent:
- \begin{enumerate}%[\rm{(TM1)}]
-	\item $\bmx \prec_{\bmd} \bmy$;
-	\item $\Gamma_{\bmd}({\bmx}) \prec \Gamma_{\bmd}({\bmy})$;
-	\item\label{en:tm3} $\sum\limits_{i=1}^n \abs{x_i - t d_i} \leq \sum\limits_{i=1}^n \abs{y_i - t d_i}$ for all $t \in \mathbb{R}$;
-	\item $\sum\limits_{i=1}^n (x_i - t d_i)^+ \leq \sum\limits_{i=1}^n (y_i - t d_i)^+$ for all $t \in \mathbb{R}$ and $\sum\limits_{i=1}^n x_i = \sum\limits_{i=1}^n y_i$;
-	\item $\forall k, L_{\bmx|\bmd}(k) \leq L_{\bmy|\bmd}(k)$ and $L_{\bmx|\bmd}(k=n) = L_{\bmy|\bmd}(k=n)$.
- \end{enumerate}
-\end{theorem}
-However, statement 3 implies that if we take $t=0$ then we see that this becomes that $\mbox{mana}(\rho) \ge \mbox{mana}(\sigma)$. \ddd{[expand/tidy this]}
-
-\ddd{[I didn't follow your mana is additive argument]}
-so it provides a bound for distillation processes
+It is shown in~\cref{app:major} that mana is an additive monotone in every $\sigma$--fragment under $d$--majorization, so it provides a bound for the process,
 \begin{equation}
     \mana{\rho} \geq \frac{1}{k} \mana{\tau}.
-\end{equation}.
+\end{equation}
 
-A new bound can be obtained in any $\sigma$--fragment by comparing the Lorenz curves of the initial and target states,
+A new bound can be obtained in every $\sigma$--fragment by comparing the Lorenz curves of the initial and target states,
 \begin{equation}\label{eq:majbound}
@@
     \includegraphics[scale=0.5]{figs/ratios.pdf}
-    \caption{Plot of the noise level threshold ratios between mana and Lorenz curve for the Strange state purifying process in~\cref{eq:purify}.
+    \caption{\textbf{Noise threshold ratios.} Mana and Lorenz curve ratios for the Strange state purifying process in~\cref{eq:purify}.
     The ratios are calculated for different numbers of initial state copies and different $\sigma$--fragments parametrised by $p$ such that $\sigma = (1-p)\ketbra{0} + p \frac{1}{3}\id$.
     Lorenz curve comparison consistently gives stricter bounds as proven in~\cref{thm:bounds}.
-    \nick{Highlight physics/invariance}
+    \nick{Consider set of pure stabilizer states instead of $(1-p)\ketbra{0} + p \frac{1}{3}\id$ perhaps}
     }
@@
 \begin{proof}
-    The maximum of the Lorenz curve of a state $\rho$ can be expressed monotonically in terms of mana, independently of the $\sigma$--fragment,
+    The maximum of the Lorenz curve of a state $\rho$ is independent of the $\sigma$--fragment
+
+    The Lorenz curve maximum can then be expressed monotonically in terms of mana,
     \begin{equation}

### 2020-06-19 magic_paper.tex

@@
 
-An example of comparison between different Lorenz curves is illustrated in~\cref{fig:lctoy}. \nick{expand}
+\subsection{Lorenz curves for magic states in a $\sigma$--fragment}
+With this it is straightforward to construct Lorenz curves for Wigner distributions in any $\sigma$--fragment.
+For any $\sigma$ being a full rank free state we have that $W_\sigma(\bmx) $ is a strictly positive full-rank probability distribution, and so one can define a corresponding notion of $d$--majorization on \emph{quasi}--distributions.We write $L_{\rho|\sigma}(x)$ for the Lorenz curve of $W_\rho(\bmx)$ with respect to $W_\sigma(\bmx)$.
+
+We now see that $0\le L_{\rho |\sigma}(x) \le 1$ for all $x$ if and only if $\rho$ is a positive Wigner state.
+Moreover, the area of the function $L_{\rho|\sigma}$ above the line $y=1$ is a resource monotone in this fragment.
+\ddd{[expand on this -- relate to mana?]}
+
+An example of comparison between different Lorenz curves is illustrated in~\cref{fig:lctoy}.
+
 \begin{figure}
@@
 
+\subsection{Magic, Mana and Majorization}
+We now discuss majorization features common to all fragments, before specialising to particular $\sigma$--fragments and how analysis in them preceeds.
+Mana is the basic resource monotone for magic.
+Here we show that its basic properties are actually special cases of more general majorization features.
+More precisely its properties can be viewed as majorization-based, and independent of the particular $\sigma$--fragment one works in.
+
 Lorenz curves provide a very efficient method of numerically checking if a certain state conversion is impossible within a $\sigma$--fragment by exploiting the equivalence with $d$--majorization stated in~\cref{thm:dmajor}.

### 2020-06-19 magic_paper.tex
Comment on maximal subset of operations, replying to Nick.

@@
 \end{proof}
-\nick{The above proposition is not relevant to $\sigma$-fragments where ``for any $\E_1 \not \in \O_\sigma$ and any $\E_2 \in \O_\sigma$'' we sometimes have $\E_1 \circ \E_2 \in \O_\sigma$ as well as $\E_2 \circ \E_1 \in \O_\sigma$ and sometimes $\E_1 \circ \E_2 \notin \O_\sigma$ as well as $\E_2 \circ \E_1 \notin \O_\sigma$}
+\nick{The above proposition is not relevant to $\sigma$-fragments where ``for any $\E_1 \not \in \O_\sigma$ and any $\E_2 \in \O_\sigma$'' we sometimes have $\E_1 \circ \E_2 \in \O_\sigma$ as well as $\E_2 \circ \E_1 \in \O_\sigma$ and sometimes $\E_1 \circ \E_2 \notin \O_\sigma$ as well as $\E_2 \circ \E_1 \notin \O_\sigma$} \ddd{[Is this true?
+Act the combination of channels on $\sigma$.
+If it is a fixed point of only one of the channels then the composition cannot have it as a fixed point...thus the combination is in $\O_\sigma$ if and only if each of the channels is in $\O_\sigma$...right?]}
 As an immediate corollary of~\cref{thm:subproj}, a $\sigma$--fragment of any magic theory $\R$ is a contravariant fragment of $\R$.

### 2020-06-19 magic_paper.tex

--- 2020-06-19 magic_paper.tex
@@
 Moreover, the area of the function $L_{\rho|\sigma}$ above the line $y=1$ is a resource monotone in this fragment.
-\ddd{[expand on this -- relate to mana?]}
+\ddd{[expand on this -- relate to mana?]} \nick{the area depends on several positive Wigner components and cannot be written as a function of mana annoyingly - can make plot similar to 4.1 in my thesis}
 
 An example of comparison between different Lorenz curves is illustrated in~\cref{fig:lctoy}.
-
 \begin{figure}
@@
 	Consider a monotone $\M$ in the context of a general resource theory $\R = (\F, \O)$.
-	State order is covariantly preserved due to the defining property of a monotone, seen in~\cref{def:mono}, where the pre-order $\prec_{\R'}$ is simply the total order $\leq$ on $\mathbb{R}$.
+	State order is covariantly preserved due to the defining property of a monotone, stated in~\cref{def:mono}, where the pre-order $\prec_{\R'}$ is simply the total order $\leq$ on $\mathbb{R}$.
 
@@
 	Conversely, given any covariant projection of $\R$ for which $\prec_{\R'}$ is a total order, we may map the totally ordered set of elements $\Pis(\rho)$ via an injective, non-decreasing function $f$ into $\mathbb{R}$.
-	Then, $\M(\rho):=f(\Pi_s(\rho))$ provides a numerical value for each $\rho$ that obeys the defining monotone condition.
+	Then, $\M(\rho):=f(\Pi_s(\rho))$ provides a numerical value for each $\rho$ that obeys the definition of a monotone.
 
@@
 
-\subsection{Magic, Mana and Majorization}
-We now discuss majorization features common to all fragments, before specialising to particular $\sigma$--fragments and how analysis in them preceeds.
-Mana is the basic resource monotone for magic.
-Here we show that its basic properties are actually special cases of more general majorization features.
-More precisely its properties can be viewed as majorization-based, and independent of the particular $\sigma$--fragment one works in.
-
 Lorenz curves provide a very efficient method of numerically checking if a certain state conversion is impossible within a $\sigma$--fragment by exploiting the equivalence with $d$--majorization stated in~\cref{thm:dmajor}.
@@
 
-\subsection{Mana and Majorization}\label{sec:scmana}
+\subsection{Mana and majorization in magic theories}\label{sec:scmana}
 We now discuss majorization features common to all fragments, before specialising to particular $\sigma$--fragments and how analysis in them proceeds. 

### 2020-06-20 magic_paper.tex
Expanded on Lorenz curve section, added proposition 7 on continuity and Lemma 8 on the lorenz curve maximum

@@
 The pre-order $\prec_{\R_\sigma}$ of the $\sigma$--fragment $\R_\sigma = (\F, \O_\sigma)$ between $d$-dimensional states corresponds to the majorization pre-order $\prec_{\W{\sigma}}$ between their $d^2$-dimensional Wigner distributions.
-For simplicity we shall merge this notation into $\prec_\sigma$, as there is little risk of confusion.
+For simplicity we shall merge the notation into $\prec_\sigma$, as there is little risk of confusion.
 
-\begin{theorem}
-    Let $\R = (\F, \O)$ be a theory of magic and suppose the state conversion $\rho \longrightarrow \tau$ is possible.
-    Then, there exists a full-rank free state $\sigma \in \F$ such that  $\W{\tau} \prec_\sigma \W{\rho}$.
-
-\nick{We need to address zeros in the Wigner distribution (I think full-rank states do not have any zeros - there certainly exist non-full-rank states with no zeros).
-
-For example, the replacement operation $\E(\rho) = \ketbra{0}$ is free in $\Rmax$ with $\E \in \O_{\ketbra{0}}$, BUT $W{\ketbra{0}}$-majorization is not defined because $W{\ketbra{0}}$ contains zeros.
-
-In such a case we can always add some $\epsilon$ amount of noise by mixing $\sigma$ with a free full-rank state, e.g.
-a thermal state $\gamma_\beta$, to get $\sigma' = (1-\epsilon)\sigma + \epsilon\gamma_\beta$.
-This ensures that all Wigner components of $\sigma'$ are strictly positive and $\W{\sigma'}$-majorization can be used BUT $\E$ is NOT in $\O_{\sigma'}$ now for any $\epsilon > 0$.
-
-This could be solved if every operation preserves some thermal state.
-Otherwise, simply stating in this theorem that ``there exists a full-rank free state $\sigma \in \F$ such that  $\W{\tau} \prec_{\W{\sigma}} \W{\rho}$'' is not accurate and needs reformulation to include the error $\epsilon$.
-}
+\begin{theorem}\label{thm:sigmamajor}
+    Let $\R = (\F, \O)$ be a theory of magic and suppose the state conversion $\rho \longrightarrow \tau$ is possible within a $\sigma$--fragment for some full-rank free state $\sigma$.
+    Then, $\W{\tau} \prec_\sigma \W{\rho}$.
 \end{theorem}
 \begin{proof}
-    Suppose there exists $\E \in \O$ such that $\E(\rho) = \tau$.
-    The free operation belongs to a $\sigma$--fragment, $\E \in \O_\sigma$, for some $\sigma \in \F$ so that $\W{\E}\W{\rho} = \W{\tau}$ with $\W{\E} \in \stochw$.
+    Suppose there exists $\E \in \O_\sigma$ such that $\E(\rho) = \tau$.
+    Therefore, the Wigner distribution of this free operation satisfies $\W{\E} \in \stochw$ and $\W{\E}\W{\rho} = \W{\tau}$.
 
-    If all components of $\W{\sigma}$ are positive, we directly have $\W{\tau} \prec_{\W{\sigma}} \W{\rho}$.
-
-    If $\W{\sigma}$ contains some zero components, we can construct the full-rank state $\sigma' = (1-\epsilon)\sigma + \epsilon\gamma_\beta$ by mixing an arbitrarily small amout $\epsilon>0$ of some thermal state $\gamma_\beta$ \nick{can replace with maximally mixed state}, so that all components of $\W{\sigma'}$ are positive.
-\nick{but $\W{\tau} \prec_{\W{\sigma'}} \W{\rho}$ is NOT true now}
+    Since $\sigma$ is full-rank and free, its Wigner distribution is strictly positive in all components, so it directly follows from~\cref{def:dmajor} that $\W{\tau} \prec_{\sigma} \W{\rho}$.
 \end{proof}
 
-A visual representation of $\bmd$-majorization is provided by Lorenz curves.
+A numerically efficient reformulation of $\bmd$-majorization is provided by Lorenz curves.
 Let the vector $\bmz^\downarrow$ denote a component permutation of vector $\bmz \in \reals^d$, so that its components are arranged in non-increasing order.
@@
     Let $\bmz \in \reals^d$.
-    Let $\bmd \in \reals^d$ be a vector with positive components, $\pi$ a permutation mapping $(z_i/d_i) \mapsto (z_i/d_i)^\downarrow$ for all $i=1,\dots,d$ and $D = \sum_{i=1}^d d_i$.
-    The Lorenz curve $L(\bmz|\bmd)$ of vector $\bmz$ is the piecewise linear curve obtained by joining the points $\{ (x_k, L_k(\bmz|\bmd)) \}_{k=1,\dots,d}$, where
+    Let $\bmd \in \reals^d$ be a vector with positive components, $\pi$ a permutation mapping $(z_i/d_i) \mapsto (z_\pi(i)/d_\pi(i)) \coloneqq (z_i/d_i)^\downarrow$ for all $i=1,\dots,d$ and $D = \sum_{i=1}^d d_i$.
+
+    Consider the piecewise linear curve obtained by joining the points $\{(0,0)\} \cup \{ (x_k, \lc{\bmz}{\bmd}(k)) \}_{k=1,\dots,d}$,where
     \begin{equation}\label{eq:lorenz}
-        (x_k, L_k(\bmz|\bmd)) \coloneqq \left( \frac{1}{D}\sum_{i=1}^k d_{\pi(i)}, \sum_{i=1}^k z_{\pi(i)} \right) \in \mathbb{R}^2.
+        (x_k, \lc{\bmz}{\bmd}(k)) \coloneqq \left( \frac{1}{D}\sum_{i=1}^k d_{\pi(i)}, \sum_{i=1}^k z_{\pi(i)} \right) \in \mathbb{R}^2.
     \end{equation}
+    The Lorenz curve of vector $\bmz$ with respect to $\bmd$ is then $\lc{\bmz}{\bmd}(x)$ for all $x \in [0,1]$.
 \end{definition}
-\emph{Remark 1.} The origin $(x_0, L_0(\bmz|\bmd)) \coloneqq (0,0)$ is usually included in the curve.
+Components $x_k$ are rescaled by $D$ so that comparison of curves with unequal dimensions is possible.
+In fact, one can see that the Lorenz curves $\lc{\bmz}{\bmd}$ and $\lc{\bmz \otimes \bmd}{\bmd \otimes \bmd}$, where $\otimes$ denotes the Kronecker product, are identical.
+Furthermore, a Lorenz curve $\lc{\bmz}{\bmd}(x)$ is always concave in $x$, since it consists of $d$ line segments each with slope $D(\frac{z_i}{d_i})^\downarrow$ for $i=1,\dots,d$ which is non-increasing by construction.
 
-\emph{Remark 2.} Components $x_k$ are rescaled by $D$ so that comparison of curves with unequal dimensions is possible.
-In fact, the Lorenz curves $L(\bmz|\bmd)$ and $L(\bmz \otimes \bmd|\bmd \otimes \bmd)$, where $\otimes$ denotes the Kronecker product, are identical.
-
-\emph{Remark 3.} Lorenz curves are always concave.
-
-\emph{Remark 4.} If $L_d(\bmz|\bmd) = 1$ and for all $k$, $L_k(\bmz|\bmd) \leq 1$, then $\bmz$ is a probability distribution.
-Lorenz curves of quasi-probability distributions in principle reach above 1.
-
-\emph{Remark 5.} We can recast the Lorenz curve into the \emph{function} $L_{\bmz|\bmd}(x)$ defined on $[0,1]$.
-
-A vector $\bmy$ is said to \emph{$\bmd$--majorize} another vector $\bmx$  if and only if the Lorenz curve $L(\bmy|\bmd)$ lies above Lorenz curve $L(\bmx|\bmd)$.
+A vector $\bmy$ \emph{$\bmd$--majorizes} another vector $\bmx$ if and only if the Lorenz curve $\lc{\bmy}{\bmd}$ lies above Lorenz curve $\lc{\bmx}{\bmd}$, thus reducing $\bmd$--majorization into a finite set of inequalities.
 \begin{theorem}\label{thm:dmajor}
     Let $\bmx, \bmy, \bmd \in \reals^d$, such that the components of $\bmd$ are positive. 
-    Then, $\bmx \prec_{\bmd} \bmy$ if and only if $L_k(\bmx|\bmd) \leq L_k(\bmy|\bmd)$ for all $k=1,2,\dots, d-1$ and $L_d(\bmx|\bmd) = L_d(\bmy|\bmd)$.
+    Then, $\bmx \prec_{\bmd} \bmy$ if and only if $\lc{\bmx}{\bmd}(x) \leq \lc{\bmy}{\bmd}(x)$ for all $x \in [0,1]$ with strict equality at $x=1$.
 \end{theorem}
-A restatement of the theorem including more equivalent conditions, along with a proof is provided in~\cref{app:major}.
-
-\subsection{Lorenz curves for magic states in a $\sigma$--fragment}
-With this it is straightforward to construct Lorenz curves for Wigner distributions in any $\sigma$--fragment.
-For any $\sigma$ being a full rank free state we have that $W_\sigma(\bmx) $ is a strictly positive full-rank probability distribution, and so one can define a corresponding notion of $d$--majorization on \emph{quasi}--distributions.We write $L_{\rho|\sigma}(x)$ for the Lorenz curve of $W_\rho(\bmx)$ with respect to $W_\sigma(\bmx)$.
-
-We now see that $0\le L_{\rho |\sigma}(x) \le 1$ for all $x$ if and only if $\rho$ is a positive Wigner state.
-Moreover, the area of the function $L_{\rho|\sigma}$ above the line $y=1$ is a resource monotone in this fragment.
-\ddd{[expand on this -- relate to mana?]} \nick{the area depends on several positive Wigner components and cannot be written as a function of mana annoyingly - can make plot similar to 4.1 in my thesis}
-
-An example of comparison between different Lorenz curves is illustrated in~\cref{fig:lctoy}.
+A restatement of the theorem including more equivalent conditions and a proof are provided in~\cref{app:major}.
+An example of comparison between different Lorenz curves is illustrated in~\cref{fig:lctoy}.\nick{move around}
 \begin{figure}
@@
 \end{figure}
+
+\subsection{Lorenz curves for magic states in a $\sigma$--fragment}
+It is now straightforward to construct Lorenz curves for Wigner distributions in any $\sigma$--fragment.
+As we have seen in~\cref{thm:sigmamajor}, for any full-rank free state $\sigma$ we have that $\W{\sigma}$ is a strictly positive full-rank probability distribution, and so one can define a corresponding notion of $d$--majorization on \emph{quasi}--distributions.
+We write $\lc{\rho}{\sigma}(x)$ for the Lorenz curve of $\W{\rho}$ with respect to $\W{\sigma}$.
+
+We now establish important properties of Lorenz curves that are independent of the $\sigma$--fragment they are define in.
+\begin{proposition}\label{thm:lccont}
+	The Lorenz curve $\lc{\rho}{\sigma}$ of a state $\rho$ with respect to state $\sigma$ is uniformly continuous in $\sigma$.
+\end{proposition}
+The proof of this important result in \nick{the appendix}.
+The consequence of this statement is that infinitesimal changes in state $\sigma$ only result in infinitesimal shifts of the $\sigma$--fragment.
+Therefore, Lorenz curves and majorization analysis in general \nick{behave nicely in the presence of / are robust under} imperfections in the experimental implementation of quantum operations.
+In particular, any $\sigma_0$--fragment defined by a non full-rank state $\sigma_0$ can be approximated by a $\sigma$--fragment defined by a full-rank $\sigma$ which is arbitrarily close to $\sigma_0$, such that $\sigma = (1-\epsilon)\sigma_0 + \epsilon\frac{1}{d}\id$, for some small $\epsilon > 0$.
+Such $\sigma_0$--fragments may include important stabilizer operations such that the replacement channel defined as $\E(\rho) = \sigma_0$ for all states $\rho$.
+Normalisation of the Wigner distribution \nick{REF} ensures that for all quantum states $\rho$, $\lc{\rho}{\sigma}(x) \geq 0$ and $\lc{\rho}{\sigma}(1) = 1$.
+As a consequence, checking whether a state conversion $\rho \longrightarrow \tau$ is possible as per~\cref{thm:dmajor}, reduces to the condition $\lc{\rho}{\sigma}(x) \leq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$.
+
+It can further be seen that the maximum of $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment and directly related to the state sum-negativity $\sn{\rho}$ \nick{CITE}, defined as the sum of the negative components in $\W{\rho}$.
+\begin{lemma}\label{lem:lcmax}
+	Given a quantum state $\rho$, the maximum of its Lorenz curve $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment in which it is defined and equal to $1+\sn{\rho}$.
+\end{lemma}
+\begin{proof}
+	\nick{Proof}
+\end{proof}
+
+Therefore, it is clear that $0 \leq \lc{\rho}{\sigma}(x) \leq 1$ for all $x \in [0,1]$ if and only if $\rho$ is a positive Wigner state.
+The maximum of the Lorenz curve corresponds to the well established monotone of sum-negativity $\rm{sn}$ further discussed in \nick{expand}
+Moreover, the area of the function $L_{\rho|\sigma}$ above the line $y=1$ is also a resource monotone in this fragment.
+\ddd{[expand - relate to mana?]} \nick{the area depends on several positive Wigner components and cannot be written as a function of mana annoyingly - can make plot similar to 4.1 in my thesis}
 
@@
 \end{equation}
-It is a monotone function of the $\ell_1$-norm of state negativity~\nick{CITE} that satisfies the additivity condition.
+It is a monotone function of the $\ell_1$-norm of the Wigner distribution that satisfies the additivity condition.
 
@@
 \end{proof}
-\nick{The above proposition is not relevant to $\sigma$-fragments where ``for any $\E_1 \not \in \O_\sigma$ and any $\E_2 \in \O_\sigma$'' we sometimes have $\E_1 \circ \E_2 \in \O_\sigma$ as well as $\E_2 \circ \E_1 \in \O_\sigma$ and sometimes $\E_1 \circ \E_2 \notin \O_\sigma$ as well as $\E_2 \circ \E_1 \notin \O_\sigma$}
+\ddd{[Is this true?
+Act the combination of channels on $\sigma$.
+If it is a fixed point of only one of the channels then the composition cannot have it as a fixed point...thus the combination is in $\O_\sigma$ if and only if each of the channels is in $\O_\sigma$...right?]}\nick{Suppose $\E_2$ is the replacement channel $\E_2(\rho) = \sigma$.
+This is a stabilizer operation.
+Then $\E_2 \circ \E_1 \in \O_\sigma$ even if $\E_1 \notin \O_\sigma$.
+Now suppose $\E$ is a Hadamard unitary, then $id = \E \circ \E_{reverse}$ but $id \in \O_{\ketbra{0}}$ while $\E, \E_{reverse} \notin \O_{\ketbra{0}}$.}
 As an immediate corollary of~\cref{thm:subproj}, a $\sigma$--fragment of any magic theory $\R$ is a contravariant fragment of $\R$.
@@
 \newpage
-%
-%\subsection{Fragments - OLD}
-%
-%\nick{OLD VERSION}
-%
-%Monotones reduce the structure of the resource theory $\R$ into a \emph{total} order on the real numbers.
-%Therefore, two states, even if incomparable in $\R$, are always mapped onto ordered real numbers.
-%This is a generic approach that ensures a form of comparison between states and resource quantification.
-%However, motivated by $\sigma$--fragments in magic theories, it is clear that we can often reduce the theory by a less \nick{information-collapsing} projection into a subtheory $\R'$ which has a tractable pre-order $\R'$, as sketched in~\cref{fig:fragments}.
-%\begin{figure}[t]
-%    \centering
-%    \includegraphics[height=3cm]{figs/fragments.pdf}
-%    \caption{Fragments \nick{Split into subfigures}
-%    }
-%    \label{fig:fragments}
-%\end{figure}
-%We define such a resource projection for general resource theories as follows.
-%\begin{definition}[\textbf{Resource projection}]\label{def:fragment}
-%    Let a resource theory $\R = (\F, \O)$ have pre-order $\prec_{\R}$ and operational composition rule $\circ_{\R}$. 
-%    Any subtheory $\R' = (\F', \O')$ with pre-order $\prec_{\R'}$ and operational composition rule $\circ_{\R'}$ is called a resource fragment iff there exists a surjective projection $\Pi \equiv (\Pis, \Pio): \R \mapsto \R'$ that satisfies the following two conditions.
-%    \begin{enumerate}
-%        \item $\Pis: \D \mapsto \D$ and $\Pis(\rho_2) \nprec_{\R'} \Pis(\rho_1)$ whenever $\rho_1 \prec_{\R} \rho_2$;
-%        \item $\Pio: \O \mapsto \O'$ and $\Pio(\E_1) \circ_{\R'} \Pio(\E_2) = \Pio(\E_1 \circ_{\R} \E_2)$ for all free operations $\E_1, \E_2 \in \O$.
-%    \end{enumerate}
-%    We call $\Pi$ a resource projection.
-%\end{definition}
-%
-%\ddd{[I think the following might be the right way to understand things, using the notion of ``covariant'' and ``contravariant''.]}
-%
-%Fragment $\R'$ is the image of the projection $\Pi$.
-%Considering a resource projection is particularly useful when the pre-order of the fragment is tractable.
-%Note the subtle difference of condition 1 in~\cref{def:fragment} and condition 2 in~\cref{def:mono}, which is due to fragments generally retaining a pre-order, while monotones impose a total order.
-%
-%\ddd{[If you agree with the covariant-contravariant definitions above then you can update the following results using the new terminology.]}
-%A monotone is the projection with the simplest tractable order as formally stated in~\cref{thm:monofrag}.
-%\begin{proposition}\label{thm:monofrag}
-%	Let $\M$ be a resource monotone of a resource theory $\R$. 
-%	Then $\M$ is a resource projection that reduces the pre-order $\prec_\R$ to a total order.
-%\end{proposition}
-%\begin{proof}
-%	Consider a monotone $\M$ in the context of a general resource theory $\R = (\F, \O)$.
-%	Let $\R' = (\F', \O')$, where $\F' \equiv \{0\}$ and $\O'$ is the set of non-increasing real functions mapping the set of non-negative real numbers $\mathbb{R}_{\geq 0}$ to itself. 
-%	We also set $\prec_{\R'}$ as the usual total order $\leq$ and $\circ_{\R'}$ as the composition of real functions.
-%	
-%	Let $\Pis = \M$.
-%	The defining properties of a monotone, given in~\cref{def:mono}, ensure condition 1 of~\cref{def:fragment}. \nick{expand}
-%	
-%	Let $\Pio$ project any $\E \in \O$ onto a function $f \in \O$ which maps $\M(\rho)$ onto $\M(\E(\rho))$ for all states $\rho$.
-%	
-%	The ordered pair $(\Pis, \Pio)$ is the resource projection which corresponds to monotone $\M$.
-%\end{proof}
-%
-%\begin{example}.
-As a simple example, we can consider the thermal operations resource theory of thermodynamics, and take $\D$ to be the dephasing map that kills off coherences between energy eigenspaces.
-Then the resource projection $\R'$ induced by $\D$ is fully described by the thermo-majorization pre-order on distributions over energies.
-%\end{example}
-%
-%We now justify the name $\sigma$--fragment for the subdivision of a magic theory $\R = (\F, \O)$, by establishing a resource projection which reduces $\R$ into any subtheory $(\F, \O_\sigma)$.
-%\begin{proposition}
-%    Let $\R = (\F, \O)$ be a theory of magic.
-%    Every $\sigma$--fragment $(\F, \O_\sigma)$ \ddd{defines a contravariant projection} of $\R$.
-%\end{proposition}
-%\begin{proof}
-%    Let the state projection be the identity projection $\Pis:\D\mapsto\D$.
-%    
-%    Consider the operation projection $\Pio:\O \mapsto \O_\sigma$, defined as
-%    \begin{equation}
-%    \Pio(\E) =
-%    \begin{cases}
-%        \E,\ &\sigma \in \O, \\
-%        \idc,\ &\sigma \notin \O.
-%    \end{cases}
-%    \end{equation}
-%    \nick{$\Pio$ should be different, this here is not right.
-If we need to project every $\E \in \O$, we may need a different condition on $\Pio$ than $\Pio(\E_1) \circ_{\R'} \Pio(\E_2) = \Pio(\E_1 \circ_{\R} \E_2)$.}
-%    The ordered pair $(\Pis, \Pio)$ acts as the desired projection.
-%\end{proof}
-%
-%An important example of a fragment appears in quantum thermodynamics. 
-%Consider a projection $\Pi$, such that $\Pis$ dephases all states in the energy eigenbasis, while $\Pio$ maps all free operations to themselves.
-%Then $\Pi$ describes the theory in the absence of coherences and the new pre-order is simply thermo-majorization, which in fact is fully solvable in the form of entropic conditions~\cite{cit:gour}.
-\nick{expand/rephrase}
-%
-%Existing magic theories can be thought of as fragments of $\Rmax$.
-%\begin{proposition}
-%    Every theory of magic $\R$ is a fragment of the maximal theory $\Rmax$.
-%\end{proposition}
-%\begin{proof}
-%    \nick{We need a state projection that establishes that some free states are not free any more $+$ an operations projection.}
-%\end{proof}
-%
-%\ddd{[Is there a way to view Nielsen's theorem as describing a projection of the full mixed state LOCC entanglement theory?
-Is really not essential but might be nice to include.
-Send $\rho_{AB} $ to the most entangled pure state in its eigendecomposition?]}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{equation}
-removes coherent phases in the computational basis and therefore only leaves invariant mixtures of computational basis states.
-If the circuit simply consists of such dephasing channels, the whole analysis could be restricted in the $\sigma$--fragments for pure computational basis states $\sigma$.
+removes coherent phases in the computational basis and therefore leaves exactly all mixtures of computational basis states invariant.
+If the circuit simply consists of such dephasing channels, the whole analysis can be restricted in the $\sigma$--fragments for pure computational basis states $\sigma$ \nick{as seen in a theorem in the appendix}.
 
-Lorenz curves provide a very efficient method of numerically checking if a certain state conversion is impossible within a $\sigma$--fragment by exploiting the equivalence with $d$--majorization stated in~\cref{thm:dmajor}.
+Lorenz curves provide an efficient method of numerically checking if a certain state conversion is impossible within a $\sigma$--fragment by exploiting the equivalence with $d$--majorization stated in~\cref{thm:dmajor}.
 Such methods are often more conclusive than magic monotones as we discuss in section~\cref{sec:scmana}.
@@
 \begin{equation}\label{eq:majbound}
-    L_k(\rho^{\otimes k} | \sigma) \geq L_k (\tau | \sigma),\ k=1,\dots,d^2,
+    L_k(\rho^{\otimes k} | \sigma) \geq L_k (\tau | \sigma),\ k=1,\dots,d^2.
 \end{equation}
@@
 
-The Strange state $\ketbra{\rm{S}}$ depicted in~\cref{fig:strange} is the simplest to analyse, since it only has two distinct components $\{ -\frac{1}{3}, \frac{1}{6} \}$, the latter with a multiplicity of 8.
+As an example, consider a qutrit distillation process involving the Strange state $\ketbra{\rm{S}}$ depicted in~\cref{fig:strange}. 
+It is the simplest non-trivial case to analyse, since the Strange state only has two distinct components $\left\{ -\frac{1}{3}, \frac{1}{6} \right\}$ with multiplicities $1$ and $8$ respectively.
 Calculating the binomial expansion for the components of $\ket{S}\bra{S}^{\otimes k}$ gives $\{(-1)^j 2^{j-k} 3^{-k}\}_{0 \leq j \leq k}$ with multiplicity $8^{k-j} \binom{k}{j}$ for the $j$-th term.
@@
 \begin{equation}\label{eq:Skmax}
-    \max_k{L_k \left( \ketbra{S}^{\otimes k} \bigm| \sigma \right)} = 1 + \left(\frac{4}{3}\right)^k \sum\limits_{j: 1 \leq 2j+1 \leq k} 4^{-(2j+1)} \binom{k}{2j+1}.
+    \max_j{L_j \left( \ketbra{S}^{\otimes k} \bigm| \sigma \right)} = 1 + \left(\frac{4}{3}\right)^k \sum\limits_{j: 1 \leq 2j+1 \leq k} 4^{-(2j+1)} \binom{k}{2j+1}.
 \end{equation}
@@
 in the $\sigma$--fragment $\O_\sigma$.
-At noise level $\epsilon \leq \frac{3}{4}$, the Wigner distribution $\W{\rho_{\rm{S}}(\epsilon)}$ contains negativities and the state can be purified so as to obtain a single-copy state with sufficiently low $\epsilon$.
+At any noise level $\epsilon \leq \frac{3}{4}$, the Wigner distribution $\W{\rho_{\rm{S}}(\epsilon)}$ contains negativities and the state can be purified so as to obtain a single-copy state with sufficiently low $\epsilon$.
 In~\cref{fig:distill}, we examine the purifying process 
@@
 with $\epsilon_{\rm{th}}$ being the noise level threshold that does not prohibit the process for given number of copies $k$ and $\sigma$--fragment, parametrised by $p$ as a mixture of the zero and the maximally mixed states.
+Thresholds provided by Lorenz curve comparison are always much stricter than mana thresholds \nick{threshold/bound? need to define the notion of a bound precisely}.
 \begin{figure}
@@
 
-Thresholds provided by Lorenz curve comparison are always much stricter than mana thresholds \nick{threshold/bound? need to define the notion of a bound precisely}.
-In fact, it is clear than this is the case in any general distillation process.
+In fact, we can more generally claim that mana bounds are always weaker than bounds provided by Lorenz curve comparison for any magic state interconversion.
 \begin{theorem}\label{thm:bounds}
-    Consider the distillation process in~\cref{eq:distprocess}.
-    In any $\sigma$--fragment, $\W{\sigma}$-majorization provides a stricter bound than mana.
+    Given a magic state conversion $\rho \longrightarrow \tau$, $\W{\sigma}$--majorization provides a stricter bound than mana in any $\sigma$--fragment.
 \end{theorem}
 \begin{proof}
-    The maximum of the Lorenz curve of a state $\rho$ is independent of the $\sigma$--fragment
-
-    The Lorenz curve maximum can then be expressed monotonically in terms of mana,
+    The maximum of the Lorenz curve of a state $\rho$ is independent of the $\sigma$--fragment due to~\cref{lem:lcmax}, and can be expressed monotonically in terms of mana,
     \begin{equation}
@@
     \end{equation}
-    Therefore, the majorization condition stated in~\cref{eq:majbound} implies that $\mana{\rho^{\otimes k}} \geq \mana{\tau}$. \ddd{[This is a bit too short]}
+    Therefore, the $\W{\sigma}$--majorization condition
+    \begin{equation}
+    	L_k(\rho | \sigma) \geq L_k (\tau | \sigma),\ k=1,\dots,d^2
+    \end{equation}
+    implies the mana condition $\mana{\rho} \geq \mana{\tau}$.
+
+    \ddd{[This is a bit too short]}\nick{I have added~\cref{lem:lcmax}}
 \end{proof}

### 2020-06-20 appendix.tex
Expanded on Lorenz curve section, added proposition 7 on continuity and Lemma 8 on the lorenz curve maximum
Added area monotone, began next subsections in computational section

@@
 \subsection{Mana properties}
-Mana monotonicity can be directly seen due to statement~\ref{en:tm3} in~\cref{thm:dmajor} for $t=0$.
+Mana monotonicity in any $\sigma$--fragment can be directly seen due to statement~\ref{en:tm3} in~\cref{thm:dmajor} for $t=0$.
 Furthermore, mana is additive due to the multiplicative property~\ref{en:w4} of~\cref{thm:wstate}.
@@
 It preserves the uniform distribution $\W{\frac{1}{5}\id}{}$, but it does not correspond to any $\cpos$ operation, hence any $\E \in \O$ due to~\cref{thm:frag}.
+
+\section{Area monotone}
+\label{app:areamono}
+
+Let $L_{>1}$ be the set of points on the Lorenz curve $\lc{\rho}{\sigma}(k)$ that lie above $1$ of state $\rho$ in the $\sigma$--fragment. 
+If $\rho$ is a free state, $L_{>1}$ is empty and $\A_\sigma(\rho) = 0$. 
+Otherwise, $\A_\sigma(\rho) > 0$ and it can be calculated exactly using the trapezium rule or the shoelace formula. 
+Let $k$ be the index of the first point $\left(x_k, \lc{\rho}{\sigma}(k)\right)$ lying above $1$. 
+Then $L_\rho(k)$ crosses $1$ at
+\begin{equation}
+	x_{\rm{int}} = x_k - \frac{x_k - x_{k-1}}{\lc{\rho}{\sigma}(k) - \lc{\rho}{\sigma}(k-1)}\lc{\rho}{\sigma}(k),\vspace{10pt}
+\end{equation}
+as well as at $\left(x_d, \lc{\rho}{\sigma}(d)\right) = (1,1)$
+
+Now we can define
+\begin{equation}
+L_{>1}^+ = \{ (x_i, y_i) \}_{0 \leq i \leq n}
+\end{equation}
+such that it contains the initial point of intersection $(x_0, y_0) \equiv (x_{n+1}, y_{n+1}) \coloneqq (x_{\rm{int}}, 1)$, all points $(x_i, y_i)$, labelled by $i=1,\dots,n-1$ that lie above $y=1$ contained in $L_{>1}$ and finally the second point of intersection $(x_n, y_n) = (1,1)$.
+Then, 
+\begin{equation}
+	\A_\sigma(\rho) = \frac{1}{2} \sum\limits_{i=0}^n (x_{i+1} y_i - x_i y_{i+1}).
+\end{equation}
+
+\begin{figure}%
+    \centering
+    \subfigure[][]{%
+    \label{fig:test1}%
+    \includegraphics[height=3cm]{figs/negmasking_rho_strange_lc.pdf}
+    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
+    }\hspace{8pt}%
+    \subfigure[][]{%
+    \label{fig:test2}%
+    \includegraphics[height=3cm]{figs/negmasking_rho_strange_meas.pdf}
+    %\caption{Zero state $\ketbra{0}{0}$}%
+    }
+    \caption{\subref{fig:test1} Lorenz curve of $p\ketbra{\rm{S}} + (1-p) \frac{1}{d}\id$ for $p$ given in the legend.\subref{fig:test2} Different measures for the states on the left. \\
+    \nick{can replace~\cref{fig:lctoy} with a more informative version of this figure}
+    }%
+    \label{fig:test}
+\end{figure}

### 2020-06-20 magic_paper.tex
Added area monotone, began next subsections in computational section

@@
 \end{definition}
+\nick{The discrete formulation is more useful in the whole discussion that follows, but the functional formulation is a little more elegant - what to choose?}
 Components $x_k$ are rescaled by $D$ so that comparison of curves with unequal dimensions is possible.
@@
     Curves $L_k(\bmx|\bmd)$ and $L_k(\bmy|\bmd)$ intersect, so $\bmx \nprec_{\bmd} \bmy$ as well as $\bmy \nprec_{\bmd} \bmx$.
-    \nick{Recast in terms of magic}
+    \nick{Recast in terms of magic - replace with~\cref{fig:test}?}
     }
@@
 
-We now establish important properties of Lorenz curves that are independent of the $\sigma$--fragment they are define in.
+We now establish important properties of Lorenz curves that are independent of the $\sigma$--fragment they are defined in.
 \begin{proposition}\label{thm:lccont}
-	The Lorenz curve $\lc{\rho}{\sigma}$ of a state $\rho$ with respect to state $\sigma$ is uniformly continuous in $\sigma$.
+	The Lorenz curve $\lc{\rho}{\sigma}(x)$ of a state $\rho$ with respect to state $\sigma$ is uniformly continuous in $\sigma$. 
+	\nick{In the sense that if $\sigma$ and $\sigma'$ are $\delta$-close with respect to a state norm, then the curves $\lc{\rho}{\sigma}(x)$ and $\lc{\rho}{\sigma'}(x)$ are $\epsilon$-close at all $x \in [0,1]$.
+	I think this clears up the narrative quite a bit? - Should we keep and prove this result?}
 \end{proposition}
-The proof of this important result in \nick{the appendix}.
+The proof of this important result is in \nick{the appendix}.
 The consequence of this statement is that infinitesimal changes in state $\sigma$ only result in infinitesimal shifts of the $\sigma$--fragment.
@@
 Such $\sigma_0$--fragments may include important stabilizer operations such that the replacement channel defined as $\E(\rho) = \sigma_0$ for all states $\rho$.
+
 Normalisation of the Wigner distribution \nick{REF} ensures that for all quantum states $\rho$, $\lc{\rho}{\sigma}(x) \geq 0$ and $\lc{\rho}{\sigma}(1) = 1$.
@@
 Therefore, it is clear that $0 \leq \lc{\rho}{\sigma}(x) \leq 1$ for all $x \in [0,1]$ if and only if $\rho$ is a positive Wigner state.
-The maximum of the Lorenz curve corresponds to the well established monotone of sum-negativity $\rm{sn}$ further discussed in \nick{expand}
-Moreover, the area of the function $L_{\rho|\sigma}$ above the line $y=1$ is also a resource monotone in this fragment.
-\ddd{[expand - relate to mana?]} \nick{the area depends on several positive Wigner components and cannot be written as a function of mana annoyingly - can make plot similar to 4.1 in my thesis}
+The maximum of the Lorenz curve corresponds to the well established monotone of sum-negativity ($\rm{sn}$) further discussed in \nick{expand - move subsection on monotones (\cref{sec:mono}) in intro}.
+Moreover, the area $\A_\sigma(\rho)$ of the function $L_{\rho|\sigma}$ above the line $y=1$ is also a resource monotone in the $\sigma$--fragment. 
+This is clear because for any state conversion $\rho \longrightarrow \tau$ for some $\E \in \O_\sigma$, the Lorenz curve $L_{\tau|\sigma}$ is lower than $L_{\rho|\sigma}$, hence $\A_\sigma(\E(\rho)) \leq \A_\sigma(\rho)$.
+The exact form of the monotone is given in~\cref{app:areamono}
+
+\ddd{[relate to mana?]} \nick{the area depends on several positive Wigner components and cannot be written as a function of mana annoyingly - should we include the area?
+Have a look at~\cref{app:areamono}}
 
@@
 
+\subsection{Magic in thermal fragments}
+
+\nick{$\rcu$ and Noisy channels preserve $\frac{1}{d}\id$}
+
+\nick{Can extend to general thermal states}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-06-21 magic_paper.tex
Response to points. Also potential closed form for S-state sum provided - check if correct.

@@
 Any magic theory $\R = (\F, \O)$ is a subtheory of $\Rmax$ as explained in~\cref{sec:intro}, and as such it falls under this new stochasticity setting.
-For technical simplicity in what follows we assume that $\F$ is a closed set, and note that $\F_{\mbox{\tiny max}}$ is itself a closed set, since it is specified by a finite set of linear constraints of the form $\tr [ L\rho] \ge 0$ with $L \in \mathcal{B}(\mathcal{H})$.
-\nick{Unfortunately, this is not enough. 
-There are positive Wigner ditributions which correspond to invalid states i.e. they are NOT positive semi-definite.
-Therefore, there are ``holes'' in the set specified by these linear constraints.
-We need a stricter argument.}
+For technical simplicity in what follows we assume that $\F$ is a closed set, and note that $\F_{\mbox{\tiny max}}$ is itself a closed set, since it is specified by a finite set of linear constraints of the form $\tr [ L\rho] \ge 0$ with $L \in \mathcal{B}(\mathcal{H})$ \ddd{ intersected with the closed set of density operators $\{\rho: \rho \ge 0, \tr[\rho]=1\}$.
+[I think this fixes your concern, no?
+I think this ``must" give a closed set.]}
 
@@
 \end{definition}
-\nick{The discrete formulation is more useful in the whole discussion that follows, but the functional formulation is a little more elegant - what to choose?}
+\nick{The discrete formulation is more useful in the whole discussion that follows, but the functional formulation is a little more elegant - what to choose?} \ddd{[Obviously for computing things the discrete version is best, but we want to keep the narrative clear for the unfamiliar reader.
+We can put the fine-print details in the appendix, but use the more elegant function expressions in the main text, of course explaining the link in simple terms.
+]}
 Components $x_k$ are rescaled by $D$ so that comparison of curves with unequal dimensions is possible.
@@
 	\nick{In the sense that if $\sigma$ and $\sigma'$ are $\delta$-close with respect to a state norm, then the curves $\lc{\rho}{\sigma}(x)$ and $\lc{\rho}{\sigma'}(x)$ are $\epsilon$-close at all $x \in [0,1]$.
-	I think this clears up the narrative quite a bit? - Should we keep and prove this result?}
+	I think this clears up the narrative quite a bit? - Should we keep and prove this result?} \ddd{[Is a nice result...hmm let's wait and see. It might distract from the main message.]}
 \end{proposition}
@@
 \end{proof}
-\ddd{[Is this true?
-Act the combination of channels on $\sigma$.
-If it is a fixed point of only one of the channels then the composition cannot have it as a fixed point...thus the combination is in $\O_\sigma$ if and only if each of the channels is in $\O_\sigma$...right?]}\nick{Suppose $\E_2$ is the replacement channel $\E_2(\rho) = \sigma$.
+\nick{Suppose $\E_2$ is the replacement channel $\E_2(\rho) = \sigma$.
 This is a stabilizer operation.
 Then $\E_2 \circ \E_1 \in \O_\sigma$ even if $\E_1 \notin \O_\sigma$.
-Now suppose $\E$ is a Hadamard unitary, then $id = \E \circ \E_{reverse}$ but $id \in \O_{\ketbra{0}}$ while $\E, \E_{reverse} \notin \O_{\ketbra{0}}$.}
+Now suppose $\E$ is a Hadamard unitary, then $id = \E \circ \E_{reverse}$ but $id \in \O_{\ketbra{0}}$ while $\E, \E_{reverse} \notin \O_{\ketbra{0}}$.} \ddd{[Ah ok, agreed.
+This is fine for now.
+Let's not spend ages trying to generalise this so as to include the majorization fragments.
+It's just good to explore the possibilities a bit, to illustrate the non-trivial aspects.]}
 As an immediate corollary of~\cref{thm:subproj}, a $\sigma$--fragment of any magic theory $\R$ is a contravariant fragment of $\R$.
@@
 
-If $\D$ is not reversible, this mapping is in general NOT contravariant (consider the replacement map $\D(\rho) = \frac{1}{d}\id$ for a strange state and stabilizer state - surely there is such a counterexample in thermodynamics theory if we consider a highly coherent state and one with the same energy population but no coherences.}
+If $\D$ is not reversible, this mapping is in general NOT contravariant (consider the replacement map $\D(\rho) = \frac{1}{d}\id$ for a strange state and stabilizer state - surely there is such a counterexample in thermodynamics theory if we consider a highly coherent state and one with the same energy population but no coherences.} \ddd{[Ok.
+Again, let's not spend time worrying about this now.
+It's clear there is various fine-print to these cases...but they're not essential to our work so let's put this on hold.]}
 \end{proof}
@@
 \end{equation}
-\ddd{[We can probably put upper and lower bounds on this value fairly readily.
-E.g.
-using known sum rules.
-Also -- bad choice of variable $k$, using it as index and also copy number.
-I think $L_{\rho|\sigma}$ is a neater formulation, since you then package things into a single object -- a function.]}
+\ddd{[Why doesn't the following give the sum in closed form:]}
+Let
+\begin{equation}
+S(a) :=(1+a)^k= \sum_{n=1}^k a^n \binom{k}{n},
+\end{equation}
+then we have
+\begin{align}
+S(a) - S(-a) &= (1+a)^k - (1-a)^k \nonumber \\
+&= 2\sum_{n=1, n \mbox{ odd}}^k a^n \binom{k}{n}.
+\end{align}
+Thus
+\begin{equation}
+\sum_{n=1, n \mbox{ odd}}^k a^n \binom{k}{n} = \frac{1}{2} \left [  (1+a)^k - (1-a)^k \right ].
+\end{equation}
+Putting in $a = 1/4$ gives
+\begin{equation}
+\sum_{n=1, n \mbox{ odd}}^k \frac{1}{4^n} \binom{k}{n} = \frac{1}{2} \left [  (5/4)^k - (3/4)^k \right ].
+\end{equation}
+If true, then we'd have
+\begin{equation}
+ \max_x L_{S|\sigma}(x) = \frac{1}{2} \left (1 + \left(\frac{5}{3}\right)^k \right ).
+\end{equation}
+\ddd{[Am I missing something here?]}
 
@@
 
-    \ddd{[This is a bit too short]}\nick{I have added~\cref{lem:lcmax}}
+    \ddd{[This is a bit too short]}\nick{I have added~\cref{lem:lcmax}}\ddd{[Lemma 8 should sit next to this. :)]}
 \end{proof}

### 2020-06-21 magic_paper.tex
Mainly worked on Lemma 8 and section VI

--- 2020-06-20 magic_paper.tex
@@
 Any magic theory $\R = (\F, \O)$ is a subtheory of $\Rmax$ as explained in~\cref{sec:intro}, and as such it falls under this new stochasticity setting. 
-For technical simplicity in what follows we assume that $\F$ is a closed set, and note that $\F_{\mbox{\tiny max}}$ is itself a closed set, since it is specified by a finite set of linear constraints of the form $\tr [ L\rho] \ge 0$ with $L \in \mathcal{B}(\mathcal{H})$.
-\nick{Unfortunately, this is not enough. 
-There are positive Wigner ditributions which correspond to invalid states i.e. they are NOT positive semi-definite.
-Therefore, there are ``holes'' in the set specified by these linear constraints.
-We need a stricter argument.}
+For technical simplicity in what follows we assume that $\F$ is a closed set, and note that $\F_{\rm{ max}}$ is itself a closed set, since it is specified by a finite set of linear constraints of the form $\tr[ L\rho] \geq 0$ with $L \in \cal{B}(\cal{H})$, ensuring that the state is positive as well as Wigner-positive.
 
@@
     \caption{\textbf{Decomposition of a magic theory $\R$ intro $\sigma$--fragments.} 
-    Examples of magic theories ($\so$: Stabilizer operations, $\Omax$: Completely positive-Wigner-preserving operations) involve operations within the yellow regions, with all other established magic theories between these two.
+    Examples of magic theories ($\so$: Stabilizer operations, $\Omax$: Completely positive-Wigner-preserving operations, $\rcu$: Random Clifford Unitaries -- subclass of $\so$) involve operations within the yellow regions, with all other established magic theories between these two.
     We introduce $\sigma$--fragments $\O_\sigma$ defined for all free states $\sigma$ that cover $\Omax$ with each one extendible to a set of stochastic maps outside the $\cptp$ operations.
@@
 A numerically efficient reformulation of $\bmd$-majorization is provided by Lorenz curves.
-Let the vector $\bmz^\downarrow$ denote a component permutation of vector $\bmz \in \reals^d$, so that its components are arranged in non-increasing order.
+Let the vector $\bmu^\downarrow$ denote the vector $\bmu \in \reals^d$ with its components arranged in non-increasing order.
 \begin{definition}[\textbf{Lorenz curve}]\label{def:lc}
-    Let $\bmz \in \reals^d$.
-    Let $\bmd \in \reals^d$ be a vector with positive components, $\pi$ a permutation mapping $(z_i/d_i) \mapsto (z_\pi(i)/d_\pi(i)) \coloneqq (z_i/d_i)^\downarrow$ for all $i=1,\dots,d$ and $D = \sum_{i=1}^d d_i$.
+    Let $\bmz, \bmd \in \reals^d$, where the components of $\bmd$ are positive with $D = \sum_{i=1}^d d_i$ and denote by $\bmu \coloneqq (z_1/d_1, \dots, z_d/d_d)^T$ the vector of ratios between the corresponding components of $\bmz$ and $\bmd$.
 
-    Consider the piecewise linear curve obtained by joining the points $\{(0,0)\} \cup \{ (x_k, \lc{\bmz}{\bmd}(k)) \}_{k=1,\dots,d}$,where
+    Finally, denote by $\pi: \zd \mapsto \zd$ the permutation that sorts $\bmu$, $(\bmu^\downarrow)_i = u_{\pi(i)}$ for all $i=1,\dots,d$.
+
+    Consider the piecewise linear curve obtained by joining the points $\{(0,0)\} \cup \{ (x_k, \lc{\bmz}{\bmd}(k)) \}_{k=1,\dots,d}$, where
     \begin{equation}\label{eq:lorenz}
@@
     \end{equation}
-    The Lorenz curve of vector $\bmz$ with respect to $\bmd$ is then $\lc{\bmz}{\bmd}(x)$ for all $x \in [0,1]$.
+    The \emph{Lorenz curve} of vector $\bmz$ with respect to $\bmd$ is then $\lc{\bmz}{\bmd}(x)$ for all $x \in [0,1]$
+
+    Expressed explicitly,
+    \begin{equation}
+		\lc{\rho}{\sigma}(x) = (\bmu^\downarrow)_i x + \lc{\rho}{\sigma}(i) - (\bmu^\downarrow)_i x_i,\ x \in (x_{i-1}, x_i],
+	\end{equation}
+	for all $i=1,\dots,d$ with $x_0 \coloneqq 0$.
 \end{definition}
@@
 Components $x_k$ are rescaled by $D$ so that comparison of curves with unequal dimensions is possible.
-In fact, one can see that the Lorenz curves $\lc{\bmz}{\bmd}$ and $\lc{\bmz \otimes \bmd}{\bmd \otimes \bmd}$, where $\otimes$ denotes the Kronecker product, are identical.
-Furthermore, a Lorenz curve $\lc{\bmz}{\bmd}(x)$ is always concave in $x$, since it consists of $d$ line segments each with slope $D(\frac{z_i}{d_i})^\downarrow$ for $i=1,\dots,d$ which is non-increasing by construction.
+In fact, the Lorenz curves $\lc{\bmz}{\bmd}$ and $\lc{\bmz \otimes \bmd}{\bmd \otimes \bmd}$, where $\otimes$ denotes the Kronecker product, are identical.
+Furthermore, a Lorenz curve $\lc{\bmz}{\bmd}(x)$ is always concave in $x$, since it consists of $d$ line segments each with slope $(\bmu^\downarrow)_i$ for $i=1,\dots,d$ which is non-increasing by definition.
 
@@
 Such $\sigma_0$--fragments may include important stabilizer operations such that the replacement channel defined as $\E(\rho) = \sigma_0$ for all states $\rho$.
+For simplicity, we restrict analysis to $\sigma$-fragments, where $\sigma$ is full-rank.
 
@@
 \begin{proof}
-	\nick{Proof}
+	Borrowing the notation of~\cref{def:lc}, the derivative of the Lorenz curve $\lc{\rho}{\sigma}$ is
+	\begin{equation}
+		\frac{\rm{d}}{\rm{d}x} \lc{\rho}{\sigma}(x) = (\bmu^\downarrow)_i,\ x \in (x_{i-1}, x_i],
+	\end{equation}
+	for all $i=1,\dots,d^2$.
+
+	Note that all components of $\W{\sigma}$ are positive, so $(\bmu^\downarrow)_i \geq 0$ if and only if $(\W{\rho})_i \geq 0$ for any $i=1,\dots,d^2$.
+
+	Suppose all components of $\W{\rho}$ are non-negative.
+	Then, $\sn{\rho}=0$ and the global maximum of the Lorenz curve is dictated by the normalisation of $\W{\rho}$ so we trivially have
+	\begin{equation}
+		\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} = 1 = 1 + \sn{\rho}.
+	\end{equation}
+
+	Suppose that $\W{\rho}$ has at least one negative component.
+	Let $k$ be the index of the smallest non-negative component of $\bmu^\downarrow$.
+	Then the maximum of the Lorenz curve $\lc{\rho}{\sigma}$ occurs at $x_k$, just before its slope becomes negative. 
+	The $x$-coordinate $x_k$ is different for different $\sigma$--fragments but the value of the maximum is the same and is given by
+	\begin{align}
+		&\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)}
+		= \lc{\rho}{\sigma}(x_k)
+		= \sum\limits_{i=1}^k (\W{\rho})_{\pi(i)} \\
+		&= \sum\limits_{\bmx: \W[\bmx]{\rho} \geq 0} \W[\bmx]{\rho}
+		= 1 + \sum\limits_{\bmx: \W[\bmx]{\rho} < 0} \abs{\W[\bmx]{\rho}} \\
+		&= 1 + \sn{\rho}.
+	\end{align}
+
 \end{proof}
 
-Therefore, it is clear that $0 \leq \lc{\rho}{\sigma}(x) \leq 1$ for all $x \in [0,1]$ if and only if $\rho$ is a positive Wigner state.
+We stress that $0 \leq \lc{\rho}{\sigma}(x) \leq 1$ for all $x \in [0,1]$ if and only if $\rho$ is a positive Wigner state.
 The maximum of the Lorenz curve corresponds to the well established monotone of sum-negativity ($\rm{sn}$) further discussed in \nick{expand - move subsection on monotones (\cref{sec:mono}) in intro}.
@@
 As a simple example, the dephasing channel
-\begin{equation}
+\begin{equation}\label{eq:dephase}
 	\Delta(\rho) = \sum_{k \in \zd} \ketbra{k}{k}\rho\ketbra{k}{k}
@@
 removes coherent phases in the computational basis and therefore leaves exactly all mixtures of computational basis states invariant.
-If the circuit simply consists of such dephasing channels, the whole analysis can be restricted in the $\sigma$--fragments for pure computational basis states $\sigma$ \nick{as seen in a theorem in the appendix}.
+A model circuit consisting only of such dephasing channels can be fully analysed in the $\sigma$--fragments for the pure computational basis states $\sigma$ \nick{as seen in a theorem in the appendix}.
 
@@
 
-Consider a general magic state distillation process, \nick{Generalise discussion to any state conversion?}
+Consider a general magic state interconversion in $\O_\sigma$, $\rho \xrightarrow{\E \in \O_\sigma} \tau$.
+It is shown in~\cref{app:major} that mana is an additive monotone in every $\sigma$--fragment under $d$--majorization, so it provides a necessary condition for the process to be possible,
+\begin{equation}\label{eq:manabound}
+    \mana{\rho} \geq \mana{\tau}. %{\rm{C}}_{\rm{mana}}(\rho, \tau, \sigma):\ 
+\end{equation}
+A new bound can be obtained in the $\sigma$--fragment by comparing the Lorenz curves of the initial and target states,
+\begin{equation}\label{eq:majbound}
+    \lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x),\ x\in [0,1].
+\end{equation}
+If condition ${\rm{C}}_{\rm{maj}}$ is not satisfied, then the Lorenz curve of initial state $\rho$ is below the curve of target $\tau$ at some point $x$ and the conversion is not possible.
+
+In fact, our current setting makes it apparent that the mana condition is always weaker than the majorization condition for all magic state interconversions.
+\begin{theorem}\label{thm:bounds}
+    Given a magic state conversion $\rho \longrightarrow \tau$, the majorization condition is stronger than the mana condition in all $\sigma$--fragments.
+\end{theorem}
+\begin{proof}
+    The maximum of the Lorenz curve of a state $\rho$ is independent of the $\sigma$--fragment due to~\cref{lem:lcmax}, and can be expressed as an increasing function of mana,
+    \begin{equation}
+        \max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} = 1 + \sn{\rho} = \frac{1}{2} \left( 1 + e^\mana{\rho} \right).
+    \end{equation}
+    Therefore, the $\W{\sigma}$--majorization bound
+    \begin{equation}
+    	\lc{\rho}{\sigma}(x) \geq \lc{\rho}{\sigma}(x),\ x\in[0,1]
+    \end{equation}
+    implies the order $\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} \geq \max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)}$ which is equivalent to the mana bound $\mana{\rho} \geq \mana{\tau}$.
+
+    \ddd{[This is a bit too short]}\nick{I have added~\cref{lem:lcmax}}
+\end{proof}
+
+Of practical importance are magic state distillation (MSD) processes of the form
 \begin{equation}\label{eq:distprocess}
-    \rho^{\otimes k} \longrightarrow \tau,
+    \rho^{\otimes k} \xrightarrow{\E \in \O_\sigma} \tau,
 \end{equation}
-where $k$ noisy copies of magic state $\rho$ are converted to a single-copy magic state $\tau$.
+where $k$ copies of a noisy magic state $\rho$ are converted into a target single-copy state $\tau$. \nick{expand?}
 
-It is shown in~\cref{app:major} that mana is an additive monotone in every $\sigma$--fragment under $d$--majorization, so it provides a bound for the process,
-\begin{equation}
-    \mana{\rho} \geq \frac{1}{k} \mana{\tau}.
-\end{equation}
-
-A new bound can be obtained in every $\sigma$--fragment by comparing the Lorenz curves of the initial and target states,
-\begin{equation}\label{eq:majbound}
-    L_k(\rho^{\otimes k} | \sigma) \geq L_k (\tau | \sigma),\ k=1,\dots,d^2.
-\end{equation}
-If the Lorenz curve of the initial state is below the target curve at any point, the process is not possible.
-In general, the Wigner components of a $k$-copy state $\rho^{\otimes k}$ are calculated, along with their multiplicities, by expanding the terms in the multinomial expansion $\left( \sum_{\bm{z} \in \cal{P}_d} W_\rho(\bm{z}) \right)^n$.
+In general, the Wigner components of a $k$-copy state $\rho^{\otimes k}$ can be calculated, along with their multiplicities, from $W_\rho$ by expanding the terms in the multinomial expansion $\left( \sum_{\bm{z} \in \cal{P}_d} W_\rho(\bm{z}) \right)^n$.
 This follows from the multiplicativity of the Wigner distribution.
@@
 \begin{equation}\label{eq:Skmax}
-    \max_j{L_j \left( \ketbra{S}^{\otimes k} \bigm| \sigma \right)} = 1 + \left(\frac{4}{3}\right)^k \sum\limits_{j: 1 \leq 2j+1 \leq k} 4^{-(2j+1)} \binom{k}{2j+1}.
+    \max_{x\in [0,1]}{\lc{\ketbra{S}^{\otimes k}} {\sigma}}(x) = 1 + \left(\frac{4}{3}\right)^k \sum\limits_{j=0}^{\floor{\frac{k-1}{2}}} 4^{-(2j+1)} \binom{k}{2j+1}.
 \end{equation}
-\ddd{[We can probably put upper and lower bounds on this value fairly readily.
-E.g.
-using known sum rules.
-Also -- bad choice of variable $k$, using it as index and also copy number.
-I think $L_{\rho|\sigma}$ is a neater formulation, since you then package things into a single object -- a function.]}
+\ddd{[We can probably put upper and lower bounds on this value fairly readily. E.g. using known sum rules.]}
 
@@
 \end{equation}
-in the $\sigma$--fragment $\O_\sigma$.
-At any noise level $\epsilon \leq \frac{3}{4}$, the Wigner distribution $\W{\rho_{\rm{S}}(\epsilon)}$ contains negativities and the state can be purified so as to obtain a single-copy state with sufficiently low $\epsilon$.
+in $\O_\sigma$.
+At noise levels $\epsilon \geq \frac{3}{4}$, the state is sufficiently noisy so as the Wigner distribution $\W{\rho_{\rm{S}}(\epsilon)}$ no longer contains negativities. 
+At any $\epsilon \leq \frac{3}{4}$, we can investigate the distillation process resulting in a single-copy state with sufficiently low target $\epsilon_{\tau}$,
+\begin{equation}\label{eq:sdist}
+	\rho_{\rm{S}}(\epsilon)^{\otimes k} \xrightarrow{\E \in \O_\sigma} \rho_{\rm{S}}(\epsilon_{\tau})
+\end{equation}
+
+The more noisy the initial state is, the more copies needed to reach the target, therefore it makes sense to define a noise level threshold
+\begin{equation}\label{eq:ethresh}
+	\epsilon_{\rm{th}}(k, \epsilon_\tau, \sigma) \coloneqq \sup{\{\epsilon:\ \lc{\rho_{\rm{S}}(\epsilon)^{\otimes k}}{\sigma} \geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})}{\sigma}\}},
+\end{equation}
+so that the MSD process~(\ref{eq:sdist}) is impossible for all $\epsilon > \epsilon_{\rm{th}}(k, \epsilon_\tau, \sigma)$
+
+\nick{Condition in~\cref{eq:ethresh} is informally written. Can also define 
+\begin{equation}\label{eq:ethresh}
+	k_{\rm{th}}(\epsilon, \epsilon_\tau, \sigma) \coloneqq \min{\{k:\ k \in \mathbb{N}, \lc{\rho_{\rm{S}}(\epsilon)^{\otimes k}}{\sigma} \geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})}{\sigma}\}}.
+\end{equation}}
+We now examine the MSD process~(\ref{eq:sdist}) in greater detail for some important $\sigma$--fragments.
+
+\subsection{Magic in unital fragments}\label{sec:thermal}
+
+Magic state distillation circuits in principle consist of bulk sequences of random Clifford unitaries ($\rcu$)\nick{CITE}, depicted in~\cref{fig:zoo}.
+Operations in $\rcu$ can be expressed as
+\begin{equation}
+    \E(\rho) = \sum_i p_i U_i \rho U_i^\dagger,\ U_i \in \cd.
+\end{equation}
+Depending on the symmetries of such operations, a sequence of them may belong in various $\sigma$--fragments and the majorization condition~(\ref{eq:majbound}) needs to be checked in all these $\sigma$-fragments that reflect the symmetries of the operation sequence.
+However, they always belong to the \emph{unital fragment} $\O_{\frac{1}{d}\id}$
+
+If one incorporates noisy channels in the circuit, for example dephasing channels as in~\cref{eq:dephase} in various bases, symmetries are reduced.
+Dephasing channels and general bit-flip error channels are examples of the many error-inducing channels that respect the unital symmetry. \nick{expand}
+
+\nick{Replace the following with discussion of MSD process in the unital fragment for various numbers of copies $k$ vs mana}
+
 In~\cref{fig:distill}, we examine the purifying process 
@@
 with $\epsilon_{\rm{th}}$ being the noise level threshold that does not prohibit the process for given number of copies $k$ and $\sigma$--fragment, parametrised by $p$ as a mixture of the zero and the maximally mixed states.
-Thresholds provided by Lorenz curve comparison are always much stricter than mana thresholds \nick{threshold/bound? need to define the notion of a bound precisely}.
+Thresholds provided by Lorenz curve comparison are always much stricter than mana thresholds.
 \begin{figure}
@@
 
-In fact, we can more generally claim that mana bounds are always weaker than bounds provided by Lorenz curve comparison for any magic state interconversion.
-\begin{theorem}\label{thm:bounds}
-    Given a magic state conversion $\rho \longrightarrow \tau$, $\W{\sigma}$--majorization provides a stricter bound than mana in any $\sigma$--fragment.
-\end{theorem}
-\begin{proof}
-    The maximum of the Lorenz curve of a state $\rho$ is independent of the $\sigma$--fragment due to~\cref{lem:lcmax}, and can be expressed monotonically in terms of mana,
+\subsection{Magic in thermal fragments}\label{sec:thermal}
+
+Consider a system driven by Hamiltonian $H$ and a circuit consisting of thermal operations.
+The computational basis now coincides with the energy eigenbasis of Hamiltonian $H$.
+We denote the thermal state $\gamma_\beta = \frac{e^{-\beta H}}{\Z_\beta}$, where $\Z_\beta = \tr[e^{-\beta H}]$.\nick{expand}
+
+Thermal operations coincide with fragment $\O_{\gamma_\beta}$ \nick{expand}
+The Wigner distribution of thermal state $\gamma_\beta$ always consists of strictly positive components,
 \begin{equation}
-        \max_k{L_k(\rho | \sigma)} = 1 + \sum_{\bmz: \W[\bmz]{\rho}<0} \abs{\W[\bmz]{\rho}} = \frac{1}{2} \left( 1 + e^\mana{\rho} \right).
+	\W[\bmx]{\gamma_\beta} = \frac{e^{-\beta \epsilon_{x_0}}}{d\Z_\beta}\ \text{for all}\ \bmx \in \pd,
 \end{equation}
-    Therefore, the $\W{\sigma}$--majorization condition
-    \begin{equation}
-    	L_k(\rho | \sigma) \geq L_k (\tau | \sigma),\ k=1,\dots,d^2
-    \end{equation}
-    implies the mana condition $\mana{\rho} \geq \mana{\tau}$.
+so pre-order $\prec_{\gamma_\beta}$ is well defined.
 
-    \ddd{[This is a bit too short]}\nick{I have added~\cref{lem:lcmax}}
-\end{proof}
-
-\subsection{Magic in thermal fragments}
-
-\nick{$\rcu$ and Noisy channels preserve $\frac{1}{d}\id$}
-
-\nick{Can extend to general thermal states}
+We generalise the analysis of~\cref{sec:unital} \nick{expand}.
+\nick{Include figure with noise threshold level $\epsilon_{\rm{th}}$ in $y$-axis and temperature $\beta$ in $x$-axis. for various numbers of copies $k$.}
 

### 2020-06-21 magic_paper.tex

@@
 Any magic theory $\R = (\F, \O)$ is a subtheory of $\Rmax$ as explained in~\cref{sec:intro}, and as such it falls under this new stochasticity setting. 
-For technical simplicity in what follows we assume that $\F$ is a closed set, and note that $\F_{\rm{ max}}$ is itself a closed set, since it is specified by a finite set of linear constraints of the form $\tr[ L\rho] \geq 0$ with $L \in \cal{B}(\cal{H})$, ensuring that the state is positive as well as Wigner-positive.
+For technical simplicity in what follows we assume that $\F$ is a closed set, and note that $\F_{\rm{ max}}$ is itself a closed set, since it is specified by a finite set of linear constraints of the form $\tr[ L\rho] \geq 0$ with operators $L \in \cal{B}(\cal{H})$ ensuring that the state is positive and Wigner-positive.
 
@@
 \end{definition}
-\nick{The discrete formulation is more useful in the whole discussion that follows, but the functional formulation is a little more elegant - what to choose?}
+\nick{Move the complicated last equation to appendix?}
 Components $x_k$ are rescaled by $D$ so that comparison of curves with unequal dimensions is possible.
@@
 As a consequence, checking whether a state conversion $\rho \longrightarrow \tau$ is possible as per~\cref{thm:dmajor}, reduces to the condition $\lc{\rho}{\sigma}(x) \leq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$.
+We stress that $0 \leq \lc{\rho}{\sigma}(x) \leq 1$ for all $x \in [0,1]$ if and only if $\rho$ is a positive Wigner state.
 
-It can further be seen that the maximum of $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment and directly related to the state sum-negativity $\sn{\rho}$ \nick{CITE}, defined as the sum of the negative components in $\W{\rho}$.
-\begin{lemma}\label{lem:lcmax}
-	Given a quantum state $\rho$, the maximum of its Lorenz curve $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment in which it is defined and equal to $1+\sn{\rho}$.
-\end{lemma}
-\begin{proof}
-	Borrowing the notation of~\cref{def:lc}, the derivative of the Lorenz curve $\lc{\rho}{\sigma}$ is
-	\begin{equation}
-		\frac{\rm{d}}{\rm{d}x} \lc{\rho}{\sigma}(x) = (\bmu^\downarrow)_i,\ x \in (x_{i-1}, x_i],
-	\end{equation}
-	for all $i=1,\dots,d^2$.
-
-	Note that all components of $\W{\sigma}$ are positive, so $(\bmu^\downarrow)_i \geq 0$ if and only if $(\W{\rho})_i \geq 0$ for any $i=1,\dots,d^2$.
-
-	Suppose all components of $\W{\rho}$ are non-negative.
-	Then, $\sn{\rho}=0$ and the global maximum of the Lorenz curve is dictated by the normalisation of $\W{\rho}$ so we trivially have
-	\begin{equation}
-		\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} = 1 = 1 + \sn{\rho}.
-	\end{equation}
-
-	Suppose that $\W{\rho}$ has at least one negative component.
-	Let $k$ be the index of the smallest non-negative component of $\bmu^\downarrow$.
-	Then the maximum of the Lorenz curve $\lc{\rho}{\sigma}$ occurs at $x_k$, just before its slope becomes negative. 
-	The $x$-coordinate $x_k$ is different for different $\sigma$--fragments but the value of the maximum is the same and is given by
-	\begin{align}
-		&\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)}
-		= \lc{\rho}{\sigma}(x_k)
-		= \sum\limits_{i=1}^k (\W{\rho})_{\pi(i)} \\
-		&= \sum\limits_{\bmx: \W[\bmx]{\rho} \geq 0} \W[\bmx]{\rho}
-		= 1 + \sum\limits_{\bmx: \W[\bmx]{\rho} < 0} \abs{\W[\bmx]{\rho}} \\
-		&= 1 + \sn{\rho}.
-	\end{align}
-
-\end{proof}
-
-We stress that $0 \leq \lc{\rho}{\sigma}(x) \leq 1$ for all $x \in [0,1]$ if and only if $\rho$ is a positive Wigner state.
-The maximum of the Lorenz curve corresponds to the well established monotone of sum-negativity ($\rm{sn}$) further discussed in \nick{expand - move subsection on monotones (\cref{sec:mono}) in intro}.
-Moreover, the area $\A_\sigma(\rho)$ of the function $L_{\rho|\sigma}$ above the line $y=1$ is also a resource monotone in the $\sigma$--fragment. 
+The area $\A_\sigma(\rho)$ between the curve $L_{\rho|\sigma}$ and the line $y=1$ is a resource monotone in the $\sigma$--fragment. 
 This is clear because for any state conversion $\rho \longrightarrow \tau$ for some $\E \in \O_\sigma$, the Lorenz curve $L_{\tau|\sigma}$ is lower than $L_{\rho|\sigma}$, hence $\A_\sigma(\E(\rho)) \leq \A_\sigma(\rho)$.
@@
 It is a monotone function of the $\ell_1$-norm of the Wigner distribution that satisfies the additivity condition.
+In particular, mana can be re-expressed as $\mana{\rho} = \log{(2\sn{\rho}+1)}$, where the sum-negativity ($\rm{sn}$) \nick{CITE} is the sum of the negative components in $\W{\rho}$,
+\begin{equation}
+	\sn{\rho} = \sum\limits_{\bmx: \W[\bmx]{\rho} < 0} \abs{\W[\bmx]{\rho}}.
+\end{equation}
 
@@
 \end{equation}
-If condition ${\rm{C}}_{\rm{maj}}$ is not satisfied, then the Lorenz curve of initial state $\rho$ is below the curve of target $\tau$ at some point $x$ and the conversion is not possible.
+If one of these consitions is not satisfied, then the Lorenz curve of initial state $\rho$ is below the curve of target $\tau$ at some point $x$ and the conversion is not possible.
 
 In fact, our current setting makes it apparent that the mana condition is always weaker than the majorization condition for all magic state interconversions.
+
+We first show that the maximum of $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment and directly related to the state sum-negativity $\sn{\rho}$ discussed in~\cref{sec:mono}
+\begin{lemma}\label{lem:lcmax}
+	Given a quantum state $\rho$, the maximum of its Lorenz curve $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment in which it is defined and equal to $1+\sn{\rho}$.
+\end{lemma}
+\begin{proof}
+	Borrowing the notation of~\cref{def:lc}, the derivative of the Lorenz curve $\lc{\rho}{\sigma}$ is
+	\begin{equation}
+		\frac{\rm{d}}{\rm{d}x} \lc{\rho}{\sigma}(x) = (\bmu^\downarrow)_i,\ x \in (x_{i-1}, x_i],
+	\end{equation}
+	for all $i=1,\dots,d^2$.
+
+	Note that all components of $\W{\sigma}$ are positive, so $(\bmu^\downarrow)_i \geq 0$ if and only if $(\W{\rho})_i \geq 0$ for any $i=1,\dots,d^2$.
+
+	Suppose all components of $\W{\rho}$ are non-negative.
+	Then, $\sn{\rho}=0$ and the global maximum of the Lorenz curve is dictated by the normalisation of $\W{\rho}$ so we trivially have
+	\begin{equation}
+		\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} = 1 = 1 + \sn{\rho}.
+	\end{equation}
+
+	Suppose that $\W{\rho}$ has at least one negative component.
+	Let $k$ be the index of the smallest non-negative component of $\bmu^\downarrow$.
+	Then the maximum of the Lorenz curve $\lc{\rho}{\sigma}$ occurs at $x_k$, just before its slope becomes negative. 
+	The $x$-coordinate $x_k$ is different for different $\sigma$--fragments but the value of the maximum is the same and is given by
+	\begin{align}
+		&\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)}
+		= \lc{\rho}{\sigma}(x_k)
+		= \sum\limits_{i=1}^k (\W{\rho})_{\pi(i)} \\
+		&= \sum\limits_{\bmx: \W[\bmx]{\rho} \geq 0} \W[\bmx]{\rho}
+		= 1 + \sn{\rho}.
+	\end{align}
+
+\end{proof}
+\nick{Perhaps create Lorenz curve appendix and put the proof there as well as how functional form and discretised form of Lorenz curves relate}
+We can therefore view mana as one of the features of the Lorenz curve, its maximum.
 \begin{theorem}\label{thm:bounds}
@@
     implies the order $\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} \geq \max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)}$ which is equivalent to the mana bound $\mana{\rho} \geq \mana{\tau}$.
-
-    \ddd{[This is a bit too short]}\nick{I have added~\cref{lem:lcmax}}
 \end{proof}
@@
 \begin{equation}\label{eq:Skmax}
-    \max_{x\in [0,1]}{\lc{\ketbra{S}^{\otimes k}} {\sigma}}(x) = 1 + \left(\frac{4}{3}\right)^k \sum\limits_{j=0}^{\floor{\frac{k-1}{2}}} 4^{-(2j+1)} \binom{k}{2j+1}.
+    \max_{x\in [0,1]}{\lc{\ketbra{S}^{\otimes k}} {\sigma}}(x) = \frac{1}{2}\left (1 + \left(\frac{5}{3}\right)^k \right).
 \end{equation}
-\ddd{[We can probably put upper and lower bounds on this value fairly readily. E.g. using known sum rules.]}
+%1 + \left(\frac{4}{3}\right)^k \sum\limits_{j=0}^{\floor{\frac{k-1}{2}}} 4^{-(2j+1)} \binom{k}{2j+1}
+%\sum_{n=1, n \mbox{ odd}}^k a^n \binom{k}{n} = \frac{1}{2} \left [  (1+a)^k - (1-a)^k \right ]
 
@@
 
-\subsection{Magic in unital fragments}\label{sec:thermal}
+\subsection{Magic in unital fragments}\label{sec:unital}
 

### 2020-06-23 magic_paper.tex
some restructiing. Also given suggested simpler account of the peak in Lorenz curve.

@@
 
+\ddd{[Things we must emphasize:
+\begin{enumerate}
+\item We can tackle more `physicsy' questions like: how much magic can be distilled via free operations with some given fixed-point structure? E.g. 
+\item This allows a diagnostic on the kind of operations needed to do good distillation. I.e. what fixed point structure should they have?
+\item We go beyond magic monotones and replace a monotone with a $\sigma$-fragment.
+\item We can get both upper and lower bounds on magic distillation.
+\end{enumerate}•
+}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{theorem}\label{thm:sigmamajor}
-    Let $\R = (\F, \O)$ be a theory of magic and suppose the state conversion $\rho \longrightarrow \tau$ is possible within a $\sigma$--fragment for some full-rank free state $\sigma$.
-    Then, $\W{\tau} \prec_\sigma \W{\rho}$.
+    Let $\R = (\F, \O)$ be a theory of magic. Then $\rho \longrightarrow \tau$ is possible then  $\W{\tau} \prec_\sigma \W{\rho}$ within a $\sigma$--fragment.
 \end{theorem}
-\begin{proof}
-    Suppose there exists $\E \in \O_\sigma$ such that $\E(\rho) = \tau$.
+\begin{proof}Suppose we can convert $\rho$ into $\tau$ in the magic theory.
+Thus there is some $\O_\sigma$ and some $\E \in \O_\sigma$ such that $\E(\rho) = \tau$, and $\E(\sigma)=\sigma$.
 Therefore, the Wigner distribution of this free operation satisfies $\W{\E} \in \stochw$ and $\W{\E}\W{\rho} = \W{\tau}$.
-
 Since $\sigma$ is full-rank and free, its Wigner distribution is strictly positive in all components, so it directly follows from~\cref{def:dmajor} that $\W{\tau} \prec_{\sigma} \W{\rho}$.
 \end{proof}
+This result can be understood as an extension of the idea of a magic monotone, where we replace $\M(\tau) \le \M(\rho)$ with $W_\tau \prec_\sigma W_\rho$.
+However the majorization constraints can be used to place upper bounds on magic state distillation in a way that allows one to incorporate the physics of the allowed operations -- this enables us to bound how much magic can be distilled via quantum operations that, for example, preserve the equilibrium state of the system, or via operations that are symmetric about the $Z$-axis of the Bloch sphere.
 
+This approach can also provide \emph{lower bounds} on distillation, however now more structure about the specific free operations must be included.
+This is more involved and we discuss this later in the paper.
+
+\subsection{Majorization computations in a $\sigma$--fragment}
 A numerically efficient reformulation of $\bmd$-majorization is provided by Lorenz curves.
@@
 \end{definition}
-\nick{Move the complicated last equation to appendix?}
+\nick{Move the complicated last equation to appendix?} \ddd{[Yes. Just describe in words, is simpler. the reader with being able to understand how to construct a piecewise linear function.]}
 Components $x_k$ are rescaled by $D$ so that comparison of curves with unequal dimensions is possible.
@@
 
-\subsection{Lorenz curves for magic states in a $\sigma$--fragment}
 It is now straightforward to construct Lorenz curves for Wigner distributions in any $\sigma$--fragment.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Magic state interconversion and Lorenz curves}
+\label{sec:distill}
+
+Any quantum circuit aiming at a given magic state conversion $\rho \longrightarrow \tau$ possesses certain symmetries according to~\cref{thm:frag} that allow us to study the conversion within only certain $\sigma$-fragments.
+As a simple example, the dephasing channel
+\begin{equation}\label{eq:dephase}
+	\Delta(\rho) = \sum_{k \in \zd} \ketbra{k}{k}\rho\ketbra{k}{k}
+\end{equation}
+removes coherent phases in the computational basis and therefore leaves exactly all mixtures of computational basis states invariant.
+A model circuit consisting only of such dephasing channels can be fully analysed in the $\sigma$--fragments for the pure computational basis states $\sigma$ \nick{as seen in a theorem in the appendix}.
+
+Lorenz curves provide an efficient method of numerically checking if a certain state conversion is impossible within a $\sigma$--fragment by exploiting the equivalence with $d$--majorization stated in~\cref{thm:dmajor}.
+Such methods are often more conclusive than magic monotones as we discuss in section~\cref{sec:scmana}.
+
+\subsection{Mana and majorization in magic theories}\label{sec:scmana}
+We now discuss majorization features common to all fragments, before specialising to particular $\sigma$--fragments and how analysis in them proceeds. 
+Mana is the fundamental resource monotone for magic. 
+Here we show that its properties are in fact special cases of more general majorization features. 
+More precisely, its properties can be viewed as majorization-based, and independent of the particular $\sigma$--fragment one works in.
+
+As discussed above, we know that every magic interconversion problem can be analysed across all $\sigma$--fragments that reflect symmetries of the circuit and moreover the pre-order in each such fragment is exactly specified by $d$--majorization.
+
+Consider a general magic state interconversion in $\O_\sigma$, $\rho \xrightarrow{\E \in \O_\sigma} \tau$.
+It is shown in~\cref{app:major} that mana is an additive monotone in every $\sigma$--fragment under $d$--majorization, so it provides a necessary condition for the process to be possible,
+\begin{equation}\label{eq:manabound}
+    \mana{\rho} \geq \mana{\tau}. %{\rm{C}}_{\rm{mana}}(\rho, \tau, \sigma):\ 
+\end{equation}
+A new bound can be obtained in the $\sigma$--fragment by comparing the Lorenz curves of the initial and target states,
+\begin{equation}\label{eq:majbound}
+    \lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x),\ x\in [0,1].
+\end{equation}
+If one of these consitions is not satisfied, then the Lorenz curve of initial state $\rho$ is below the curve of target $\tau$ at some point $x$ and the conversion is not possible.
+
+In fact, our current setting makes it apparent that the mana condition is always weaker than the majorization condition for all magic state interconversions.
+
+We first show that the maximum of $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment and directly related to the state sum-negativity $\sn{\rho}$ discussed in~\cref{sec:mono}
+\begin{lemma}\label{lem:lcmax}
+	Given a quantum state $\rho$, the maximum of its Lorenz curve $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment in which it is defined and equal to $1+\sn{\rho}$.
+\end{lemma}
+\begin{proof}
+	Borrowing the notation of~\cref{def:lc}, the derivative of the Lorenz curve $\lc{\rho}{\sigma}$ is
+	\begin{equation}
+		\frac{\rm{d}}{\rm{d}x} \lc{\rho}{\sigma}(x) = (\bmu^\downarrow)_i,\ x \in (x_{i-1}, x_i],
+	\end{equation}
+\ddd{[The function is not differentiable at the key points involved. The maximum is obtained when you sum all the non-negative components.]}
+
+	Note that all components of $\W{\sigma}$ are positive, so $(\bmu^\downarrow)_i \geq 0$ if and only if $(\W{\rho})_i \geq 0$ for any $i=1,\dots,d^2$.
+
+	Suppose all components of $\W{\rho}$ are non-negative.
+	Then, $\sn{\rho}=0$ and the global maximum of the Lorenz curve is dictated by the normalisation of $\W{\rho}$ so we trivially have
+	\begin{equation}
+		\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} = 1 = 1 + \sn{\rho}.
+	\end{equation}
+
+	Suppose that $\W{\rho}$ has at least one negative component.
+	Let $k$ be the index of the smallest non-negative component of $\bmu^\downarrow$.
+	Then the maximum of the Lorenz curve $\lc{\rho}{\sigma}$ occurs at $x_k$, just before its slope becomes negative. 
+	The $x$-coordinate $x_k$ is different for different $\sigma$--fragments but the value of the maximum is the same and is given by
+	\begin{align}
+		&\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)}
+		= \lc{\rho}{\sigma}(x_k)
+		= \sum\limits_{i=1}^k (\W{\rho})_{\pi(i)} \\
+		&= \sum\limits_{\bmx: \W[\bmx]{\rho} \geq 0} \W[\bmx]{\rho}
+		= 1 + \sn{\rho}.
+	\end{align}
+
+\end{proof}
+\nick{Perhaps create Lorenz curve appendix and put the proof there as well as how functional form and discretised form of Lorenz curves relate}
+\ddd{[This I think is a simpler approach:]}
+The Lorenz curve of $L_{\bmx |\bmd}(x)$ is defined by piecewise linear sections sequentially linking the points $\{ (a_k,b_k)\}$ where $a_k = \sum_{i=1}^k x_i$, $ b_k = \sum_{i=1}^k d_i$ and we order the components such that $\tilde{x}_i:=x_i / d_i$ form a non-increasing sequence in $i$.
+
+Now let $k_\star$ be the index of the smallest non-negative number in $(\tilde{x}_i)$, and define 
+\begin{align}
+a_\star &:= \sum_{i=1}^{k_\star} x_i\\
+b_\star &:= \sum_{i=1}^{k_\star} d_i.
+\end{align}
+It is then clear that $L_{\rho|\sigma}(x)$ attains a maximum value of $a_\star \ge 1$ at the point $x = d_\star$.
+
+Note that since $\bmd \ge \mathbf{0}$, for $i > k_\star$ we have that $x_i \le 0$, independent of the particular $\bmd$ we use.
+Therefore the value of $a_\star$ is independent of the particular fragment, with only the location of the maximum ($x=b_\star$) varying from fragment to fragment.
+\ddd{[This method is tidier.]}
+
+We can therefore view mana as one of the features of the Lorenz curve, its maximum.
+\begin{theorem}\label{thm:bounds}
+    Given a magic state conversion $\rho \longrightarrow \tau$, the majorization condition is stronger than the mana condition in all $\sigma$--fragments.
+\end{theorem}
+\begin{proof}
+    The maximum of the Lorenz curve of a state $\rho$ is independent of the $\sigma$--fragment due to~\cref{lem:lcmax}, and can be expressed as an increasing function of mana,
+    \begin{equation}
+        \max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} = 1 + \sn{\rho} = \frac{1}{2} \left( 1 + e^\mana{\rho} \right).
+    \end{equation}
+    Therefore, the $\W{\sigma}$--majorization bound
+    \begin{equation}
+    	\lc{\rho}{\sigma}(x) \geq \lc{\rho}{\sigma}(x),\ x\in[0,1]
+    \end{equation}
+    implies the order $\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} \geq \max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)}$ which is equivalent to the mana bound $\mana{\rho} \geq \mana{\tau}$.
+\end{proof}
+
+Of practical importance are magic state distillation (MSD) processes of the form
+\begin{equation}\label{eq:distprocess}
+    \rho^{\otimes k} \xrightarrow{\E \in \O_\sigma} \tau,
+\end{equation}
+where $k$ copies of a noisy magic state $\rho$ are converted into a target single-copy state $\tau$. \nick{expand?}
+
+In general, the Wigner components of a $k$-copy state $\rho^{\otimes k}$ can be calculated, along with their multiplicities, from $W_\rho$ by expanding the terms in the multinomial expansion $\left( \sum_{\bm{z} \in \cal{P}_d} W_\rho(\bm{z}) \right)^n$.
+This follows from the multiplicativity of the Wigner distribution.
+
+As an example, consider a qutrit distillation process involving the Strange state $\ketbra{\rm{S}}$ depicted in~\cref{fig:strange}. 
+It is the simplest non-trivial case to analyse, since the Strange state only has two distinct components $\left\{ -\frac{1}{3}, \frac{1}{6} \right\}$ with multiplicities $1$ and $8$ respectively.
+Calculating the binomial expansion for the components of $\ket{S}\bra{S}^{\otimes k}$ gives $\{(-1)^j 2^{j-k} 3^{-k}\}_{0 \leq j \leq k}$ with multiplicity $8^{k-j} \binom{k}{j}$ for the $j$-th term.
+This allows analytical calculation of all Lorenz curve points, and for the $k$-copy state we have that
+\begin{equation}\label{eq:Skmax}
+    \max_x{\lc{\ketbra{S}^{\otimes k}} {\sigma}}(x) = \frac{1}{2}\left (1 + \left(\frac{5}{3}\right)^k \right),
+\end{equation}
+independent of the particular $\sigma$--fragment. \ddd{[We should also give for what value of $x$ this maximum occurs.]} 
+%1 + \left(\frac{4}{3}\right)^k \sum\limits_{j=0}^{\floor{\frac{k-1}{2}}} 4^{-(2j+1)} \binom{k}{2j+1}
+%\sum_{n=1, n \mbox{ odd}}^k a^n \binom{k}{n} = \frac{1}{2} \left [  (1+a)^k - (1-a)^k \right ]
+
+\subsection{Distilling out magic in a fragment}
+Consider, as an example, the problem of purifying out magic from a noisy state of the form
+\begin{equation}
+    \rho_{\rm{S}}(\epsilon) = (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \sigma,
+\end{equation}
+in $\O_\sigma$.
+At noise levels $\epsilon \geq \frac{3}{4}$, the state is sufficiently noisy so as the Wigner distribution $\W{\rho_{\rm{S}}(\epsilon)}$ no longer contains negativities. 
+At any $\epsilon \leq \frac{3}{4}$, we can investigate the distillation process resulting in a single-copy state with sufficiently low target $\epsilon_{\tau}$,
+\begin{equation}\label{eq:sdist}
+	\rho_{\rm{S}}(\epsilon)^{\otimes k} \xrightarrow{\E \in \O_\sigma} \rho_{\rm{S}}(\epsilon_{\tau})
+\end{equation}
+
+The more noisy the initial state is, the more copies needed to reach the target, therefore it makes sense to define a noise level threshold
+\begin{equation}\label{eq:ethresh}
+	\epsilon_{\rm{th}}(k, \epsilon_\tau, \sigma) \coloneqq \sup{\{\epsilon:\ \lc{\rho_{\rm{S}}(\epsilon)^{\otimes k}}{\sigma} \geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})}{\sigma}\}},
+\end{equation}
+so that the MSD process~(\ref{eq:sdist}) is impossible for all $\epsilon > \epsilon_{\rm{th}}(k, \epsilon_\tau, \sigma)$
+
+\nick{Condition in~\cref{eq:ethresh} is informally written. Can also define 
+\begin{equation}\label{eq:ethresh}
+	k_{\rm{th}}(\epsilon, \epsilon_\tau, \sigma) \coloneqq \min{\{k:\ k \in \mathbb{N}, \lc{\rho_{\rm{S}}(\epsilon)^{\otimes k}}{\sigma} \geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})}{\sigma}\}}.
+\end{equation}}
+We now examine the MSD process~(\ref{eq:sdist}) in greater detail for some important $\sigma$--fragments.
+
+\subsection{Magic in unital fragments}\label{sec:unital}
+
+Magic state distillation circuits in principle consist of bulk sequences of random Clifford unitaries ($\rcu$)\nick{CITE}, depicted in~\cref{fig:zoo}.
+Operations in $\rcu$ can be expressed as
+\begin{equation}
+    \E(\rho) = \sum_i p_i U_i \rho U_i^\dagger,\ U_i \in \cd.
+\end{equation}
+Depending on the symmetries of such operations, a sequence of them may belong in various $\sigma$--fragments and the majorization condition~(\ref{eq:majbound}) needs to be checked in all these $\sigma$-fragments that reflect the symmetries of the operation sequence.
+However, they always belong to the \emph{unital fragment} $\O_{\frac{1}{d}\id}$
+
+If one incorporates noisy channels in the circuit, for example dephasing channels as in~\cref{eq:dephase} in various bases, symmetries are reduced.
+Dephasing channels and general bit-flip error channels are examples of the many error-inducing channels that respect the unital symmetry. \nick{expand}
+
+\nick{Replace the following with discussion of MSD process in the unital fragment for various numbers of copies $k$ vs mana}
+
+In~\cref{fig:distill}, we examine the purifying process 
+\begin{equation}\label{eq:purify}
+    \rho_{\rm{S}}^{\otimes k}(\epsilon_{\rm{th}}) \xrightarrow{\E \in \O_\sigma} \rho_{\rm{S}}(0.05),\ \sigma = (1-p)\ketbra{0} + p \frac{1}{3}\id
+\end{equation}
+with $\epsilon_{\rm{th}}$ being the noise level threshold that does not prohibit the process for given number of copies $k$ and $\sigma$--fragment, parametrised by $p$ as a mixture of the zero and the maximally mixed states.
+Thresholds provided by Lorenz curve comparison are always much stricter than mana thresholds.
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.5]{figs/ratios.pdf}
+    \caption{\textbf{Noise threshold ratios.} Mana and Lorenz curve ratios for the Strange state purifying process in~\cref{eq:purify}.
+    The ratios are calculated for different numbers of initial state copies and different $\sigma$--fragments parametrised by $p$ such that $\sigma = (1-p)\ketbra{0} + p \frac{1}{3}\id$.
+    Lorenz curve comparison consistently gives stricter bounds as proven in~\cref{thm:bounds}.
+    \nick{Consider set of pure stabilizer states instead of $(1-p)\ketbra{0} + p \frac{1}{3}\id$ perhaps}
+    }
+    \label{fig:distill}
+\end{figure}
+
+\subsection{Magic in thermal fragments}\label{sec:thermal}
+
+Consider a system driven by Hamiltonian $H$ and a circuit consisting of thermal operations.
+The computational basis now coincides with the energy eigenbasis of Hamiltonian $H$.
+We denote the thermal state $\gamma_\beta = \frac{e^{-\beta H}}{\Z_\beta}$, where $\Z_\beta = \tr[e^{-\beta H}]$.\nick{expand}
+
+Thermal operations coincide with fragment $\O_{\gamma_\beta}$ \nick{expand}
+The Wigner distribution of thermal state $\gamma_\beta$ always consists of strictly positive components,
+\begin{equation}
+	\W[\bmx]{\gamma_\beta} = \frac{e^{-\beta \epsilon_{x_0}}}{d\Z_\beta}\ \text{for all}\ \bmx \in \pd,
+\end{equation}
+so pre-order $\prec_{\gamma_\beta}$ is well defined.
+
+We generalise the analysis of~\cref{sec:unital} \nick{expand}.
+\nick{Include figure with noise threshold level $\epsilon_{\rm{th}}$ in $y$-axis and temperature $\beta$ in $x$-axis. for various numbers of copies $k$.}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Magic state interconversion and Lorenz curves}
-\label{sec:distill}
-
-Any quantum circuit aiming at a given magic state conversion $\rho \longrightarrow \tau$ possesses certain symmetries according to~\cref{thm:frag} that allow us to study the conversion within only certain $\sigma$-fragments.
-As a simple example, the dephasing channel
-\begin{equation}\label{eq:dephase}
-	\Delta(\rho) = \sum_{k \in \zd} \ketbra{k}{k}\rho\ketbra{k}{k}
-\end{equation}
-removes coherent phases in the computational basis and therefore leaves exactly all mixtures of computational basis states invariant.
-A model circuit consisting only of such dephasing channels can be fully analysed in the $\sigma$--fragments for the pure computational basis states $\sigma$ \nick{as seen in a theorem in the appendix}.
-
-Lorenz curves provide an efficient method of numerically checking if a certain state conversion is impossible within a $\sigma$--fragment by exploiting the equivalence with $d$--majorization stated in~\cref{thm:dmajor}.
-Such methods are often more conclusive than magic monotones as we discuss in section~\cref{sec:scmana}.
-
-\subsection{Mana and majorization in magic theories}\label{sec:scmana}
-We now discuss majorization features common to all fragments, before specialising to particular $\sigma$--fragments and how analysis in them proceeds. 
-Mana is the fundamental resource monotone for magic. 
-Here we show that its properties are in fact special cases of more general majorization features. 
-More precisely, its properties can be viewed as majorization-based, and independent of the particular $\sigma$--fragment one works in.
-
-As discussed above, we know that every magic interconversion problem can be analysed across all $\sigma$--fragments that reflect symmetries of the circuit and moreover the pre-order in each such fragment is exactly specified by $d$--majorization.
-
-Consider a general magic state interconversion in $\O_\sigma$, $\rho \xrightarrow{\E \in \O_\sigma} \tau$.
-It is shown in~\cref{app:major} that mana is an additive monotone in every $\sigma$--fragment under $d$--majorization, so it provides a necessary condition for the process to be possible,
-\begin{equation}\label{eq:manabound}
-    \mana{\rho} \geq \mana{\tau}. %{\rm{C}}_{\rm{mana}}(\rho, \tau, \sigma):\ 
-\end{equation}
-A new bound can be obtained in the $\sigma$--fragment by comparing the Lorenz curves of the initial and target states,
-\begin{equation}\label{eq:majbound}
-    \lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x),\ x\in [0,1].
-\end{equation}
-If one of these consitions is not satisfied, then the Lorenz curve of initial state $\rho$ is below the curve of target $\tau$ at some point $x$ and the conversion is not possible.
-
-In fact, our current setting makes it apparent that the mana condition is always weaker than the majorization condition for all magic state interconversions.
-
-We first show that the maximum of $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment and directly related to the state sum-negativity $\sn{\rho}$ discussed in~\cref{sec:mono}
-\begin{lemma}\label{lem:lcmax}
-	Given a quantum state $\rho$, the maximum of its Lorenz curve $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment in which it is defined and equal to $1+\sn{\rho}$.
-\end{lemma}
-\begin{proof}
-	Borrowing the notation of~\cref{def:lc}, the derivative of the Lorenz curve $\lc{\rho}{\sigma}$ is
-	\begin{equation}
-		\frac{\rm{d}}{\rm{d}x} \lc{\rho}{\sigma}(x) = (\bmu^\downarrow)_i,\ x \in (x_{i-1}, x_i],
-	\end{equation}
-	for all $i=1,\dots,d^2$.
-
-	Note that all components of $\W{\sigma}$ are positive, so $(\bmu^\downarrow)_i \geq 0$ if and only if $(\W{\rho})_i \geq 0$ for any $i=1,\dots,d^2$.
-
-	Suppose all components of $\W{\rho}$ are non-negative.
-	Then, $\sn{\rho}=0$ and the global maximum of the Lorenz curve is dictated by the normalisation of $\W{\rho}$ so we trivially have
-	\begin{equation}
-		\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} = 1 = 1 + \sn{\rho}.
-	\end{equation}
-
-	Suppose that $\W{\rho}$ has at least one negative component.
-	Let $k$ be the index of the smallest non-negative component of $\bmu^\downarrow$.
-	Then the maximum of the Lorenz curve $\lc{\rho}{\sigma}$ occurs at $x_k$, just before its slope becomes negative. 
-	The $x$-coordinate $x_k$ is different for different $\sigma$--fragments but the value of the maximum is the same and is given by
-	\begin{align}
-		&\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)}
-		= \lc{\rho}{\sigma}(x_k)
-		= \sum\limits_{i=1}^k (\W{\rho})_{\pi(i)} \\
-		&= \sum\limits_{\bmx: \W[\bmx]{\rho} \geq 0} \W[\bmx]{\rho}
-		= 1 + \sn{\rho}.
-	\end{align}
-
-\end{proof}
-\nick{Perhaps create Lorenz curve appendix and put the proof there as well as how functional form and discretised form of Lorenz curves relate}
-We can therefore view mana as one of the features of the Lorenz curve, its maximum.
-\begin{theorem}\label{thm:bounds}
-    Given a magic state conversion $\rho \longrightarrow \tau$, the majorization condition is stronger than the mana condition in all $\sigma$--fragments.
-\end{theorem}
-\begin{proof}
-    The maximum of the Lorenz curve of a state $\rho$ is independent of the $\sigma$--fragment due to~\cref{lem:lcmax}, and can be expressed as an increasing function of mana,
-    \begin{equation}
-        \max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} = 1 + \sn{\rho} = \frac{1}{2} \left( 1 + e^\mana{\rho} \right).
-    \end{equation}
-    Therefore, the $\W{\sigma}$--majorization bound
-    \begin{equation}
-    	\lc{\rho}{\sigma}(x) \geq \lc{\rho}{\sigma}(x),\ x\in[0,1]
-    \end{equation}
-    implies the order $\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} \geq \max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)}$ which is equivalent to the mana bound $\mana{\rho} \geq \mana{\tau}$.
-\end{proof}
-
-Of practical importance are magic state distillation (MSD) processes of the form
-\begin{equation}\label{eq:distprocess}
-    \rho^{\otimes k} \xrightarrow{\E \in \O_\sigma} \tau,
-\end{equation}
-where $k$ copies of a noisy magic state $\rho$ are converted into a target single-copy state $\tau$. \nick{expand?}
-
-In general, the Wigner components of a $k$-copy state $\rho^{\otimes k}$ can be calculated, along with their multiplicities, from $W_\rho$ by expanding the terms in the multinomial expansion $\left( \sum_{\bm{z} \in \cal{P}_d} W_\rho(\bm{z}) \right)^n$.
-This follows from the multiplicativity of the Wigner distribution.
-
-As an example, consider a qutrit distillation process involving the Strange state $\ketbra{\rm{S}}$ depicted in~\cref{fig:strange}. 
-It is the simplest non-trivial case to analyse, since the Strange state only has two distinct components $\left\{ -\frac{1}{3}, \frac{1}{6} \right\}$ with multiplicities $1$ and $8$ respectively.
-Calculating the binomial expansion for the components of $\ket{S}\bra{S}^{\otimes k}$ gives $\{(-1)^j 2^{j-k} 3^{-k}\}_{0 \leq j \leq k}$ with multiplicity $8^{k-j} \binom{k}{j}$ for the $j$-th term.
-This allows analytical calculation of all Lorenz curve points, hence the maximum of the $k$-copy state is
-\begin{equation}\label{eq:Skmax}
-    \max_{x\in [0,1]}{\lc{\ketbra{S}^{\otimes k}} {\sigma}}(x) = \frac{1}{2}\left (1 + \left(\frac{5}{3}\right)^k \right).
-\end{equation}
-%1 + \left(\frac{4}{3}\right)^k \sum\limits_{j=0}^{\floor{\frac{k-1}{2}}} 4^{-(2j+1)} \binom{k}{2j+1}
-%\sum_{n=1, n \mbox{ odd}}^k a^n \binom{k}{n} = \frac{1}{2} \left [  (1+a)^k - (1-a)^k \right ]
-
-Consider the noisy Strange state,
-\begin{equation}
-    \rho_{\rm{S}}(\epsilon) = (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \sigma,
-\end{equation}
-in $\O_\sigma$.
-At noise levels $\epsilon \geq \frac{3}{4}$, the state is sufficiently noisy so as the Wigner distribution $\W{\rho_{\rm{S}}(\epsilon)}$ no longer contains negativities. 
-At any $\epsilon \leq \frac{3}{4}$, we can investigate the distillation process resulting in a single-copy state with sufficiently low target $\epsilon_{\tau}$,
-\begin{equation}\label{eq:sdist}
-	\rho_{\rm{S}}(\epsilon)^{\otimes k} \xrightarrow{\E \in \O_\sigma} \rho_{\rm{S}}(\epsilon_{\tau})
-\end{equation}
-
-The more noisy the initial state is, the more copies needed to reach the target, therefore it makes sense to define a noise level threshold
-\begin{equation}\label{eq:ethresh}
-	\epsilon_{\rm{th}}(k, \epsilon_\tau, \sigma) \coloneqq \sup{\{\epsilon:\ \lc{\rho_{\rm{S}}(\epsilon)^{\otimes k}}{\sigma} \geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})}{\sigma}\}},
-\end{equation}
-so that the MSD process~(\ref{eq:sdist}) is impossible for all $\epsilon > \epsilon_{\rm{th}}(k, \epsilon_\tau, \sigma)$
-
-\nick{Condition in~\cref{eq:ethresh} is informally written. Can also define 
-\begin{equation}\label{eq:ethresh}
-	k_{\rm{th}}(\epsilon, \epsilon_\tau, \sigma) \coloneqq \min{\{k:\ k \in \mathbb{N}, \lc{\rho_{\rm{S}}(\epsilon)^{\otimes k}}{\sigma} \geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})}{\sigma}\}}.
-\end{equation}}
-We now examine the MSD process~(\ref{eq:sdist}) in greater detail for some important $\sigma$--fragments.
-
-\subsection{Magic in unital fragments}\label{sec:unital}
-
-Magic state distillation circuits in principle consist of bulk sequences of random Clifford unitaries ($\rcu$)\nick{CITE}, depicted in~\cref{fig:zoo}.
-Operations in $\rcu$ can be expressed as
-\begin{equation}
-    \E(\rho) = \sum_i p_i U_i \rho U_i^\dagger,\ U_i \in \cd.
-\end{equation}
-Depending on the symmetries of such operations, a sequence of them may belong in various $\sigma$--fragments and the majorization condition~(\ref{eq:majbound}) needs to be checked in all these $\sigma$-fragments that reflect the symmetries of the operation sequence.
-However, they always belong to the \emph{unital fragment} $\O_{\frac{1}{d}\id}$
-
-If one incorporates noisy channels in the circuit, for example dephasing channels as in~\cref{eq:dephase} in various bases, symmetries are reduced.
-Dephasing channels and general bit-flip error channels are examples of the many error-inducing channels that respect the unital symmetry. \nick{expand}
-
-\nick{Replace the following with discussion of MSD process in the unital fragment for various numbers of copies $k$ vs mana}
-
-In~\cref{fig:distill}, we examine the purifying process 
-\begin{equation}\label{eq:purify}
-    \rho_{\rm{S}}^{\otimes k}(\epsilon_{\rm{th}}) \xrightarrow{\E \in \O_\sigma} \rho_{\rm{S}}(0.05),\ \sigma = (1-p)\ketbra{0} + p \frac{1}{3}\id
-\end{equation}
-with $\epsilon_{\rm{th}}$ being the noise level threshold that does not prohibit the process for given number of copies $k$ and $\sigma$--fragment, parametrised by $p$ as a mixture of the zero and the maximally mixed states.
-Thresholds provided by Lorenz curve comparison are always much stricter than mana thresholds.
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.5]{figs/ratios.pdf}
-    \caption{\textbf{Noise threshold ratios.} Mana and Lorenz curve ratios for the Strange state purifying process in~\cref{eq:purify}.
-    The ratios are calculated for different numbers of initial state copies and different $\sigma$--fragments parametrised by $p$ such that $\sigma = (1-p)\ketbra{0} + p \frac{1}{3}\id$.
-    Lorenz curve comparison consistently gives stricter bounds as proven in~\cref{thm:bounds}.
-    \nick{Consider set of pure stabilizer states instead of $(1-p)\ketbra{0} + p \frac{1}{3}\id$ perhaps}
-    }
-    \label{fig:distill}
-\end{figure}
-
-\subsection{Magic in thermal fragments}\label{sec:thermal}
-
-Consider a system driven by Hamiltonian $H$ and a circuit consisting of thermal operations.
-The computational basis now coincides with the energy eigenbasis of Hamiltonian $H$.
-We denote the thermal state $\gamma_\beta = \frac{e^{-\beta H}}{\Z_\beta}$, where $\Z_\beta = \tr[e^{-\beta H}]$.\nick{expand}
-
-Thermal operations coincide with fragment $\O_{\gamma_\beta}$ \nick{expand}
-The Wigner distribution of thermal state $\gamma_\beta$ always consists of strictly positive components,
-\begin{equation}
-	\W[\bmx]{\gamma_\beta} = \frac{e^{-\beta \epsilon_{x_0}}}{d\Z_\beta}\ \text{for all}\ \bmx \in \pd,
-\end{equation}
-so pre-order $\prec_{\gamma_\beta}$ is well defined.
-
-We generalise the analysis of~\cref{sec:unital} \nick{expand}.
-\nick{Include figure with noise threshold level $\epsilon_{\rm{th}}$ in $y$-axis and temperature $\beta$ in $x$-axis. for various numbers of copies $k$.}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-06-23 magic_paper.tex
minor changes

--- 2020-06-21 magic_paper.tex
@@
 It is a monotone function of the $\ell_1$-norm of the Wigner distribution that satisfies the additivity condition.
-In particular, mana can be re-expressed as $\mana{\rho} = \log{(2\sn{\rho}+1)}$, where the sum-negativity ($\rm{sn}$) \nick{CITE} is the sum of the negative components in $\W{\rho}$,
+In particular, mana can be re-expressed as $\mana{\rho} = \log{(2\hspace{2pt}\sn{\rho}+1)}$, where the sum-negativity ($\rm{sn}$) \nick{CITE} is the sum of the negative components in $\W{\rho}$,
 \begin{equation}

### 2020-06-23 appendix.tex

@@
 
+Any $\bmd$-majorization problem can be rephrased as a majorization problem in a higher dimensional space due to the embedding map.
+\begin{definition}
+    The embedding map $\Gamma_{\bmd}:\mathbb{R}^n \mapsto \mathbb{R}^D, D = \sum\limits_{i=1}^n d_i$ is the function
+    \begin{equation}
+        \Gamma_{\bmd}(\bmz) = \bigoplus_{i=1}^n z_i\  \frac{1}{d_i}\bm{1},
+    \end{equation}
+    where $\bm{1}/d_i$ is the $d_i$-dimensional uniform distribution.
+    The left inverse $\Gamma_{\bmd}^{-1}: \mathbb{R}^D \mapsto \mathbb{R}^n$ is defined to sum up the elements in each block of $\Gamma_{\bmd}(\bmz)$, so that
+    \begin{equation}
+        \Gamma_{\bmd}^{-1}(\oplus_{i=1}^n z_i \bm{1}/d_i) = \bmz.
+    \end{equation}
+    This is not a right inverse, because $\Gamma_{\bmd}$ is not surjective.
+\end{definition}
+The direct sum simply amounts to listing the uniform distributions one after the other.
+The embedding map maps the Gibbs distribution to the uniform distribution, $\Gamma_{\bmd}(\bmd) = \bm{1}/D$.
+Then, a non-increasing ordering $\Gamma_{\bmd}(\bmz)^\downarrow$ in the new space, corresponds to the so-called ``$\beta$-ordering'' of the original vector denoted by the permutation $\pi$ mapping $(z_i/d_i) \mapsto (z_i/d_i)^\downarrow$ for all $i=1,\dots,n$.
+Intuitively, $\beta$-ordering tends to simply non-increasing ordering as $\beta$ tends to 0.
+This ordering naturally leads to a generalised notion of the Lorenz curve.
+
 \begin{theorem}
@@
 \end{proof}
+
+The Lorenz curve can be explicitly expressed as
+    \begin{equation}
+		\lc{\rho}{\sigma}(x) = (\bmu^\downarrow)_i x + \lc{\rho}{\sigma}(i) - (\bmu^\downarrow)_i x_i,\ x \in (x_{i-1}, x_i],
+	\end{equation}
+	for all $i=1,\dots,d$ with $x_0 \coloneqq 0$.
 

### 2020-06-23 magic_paper.tex

--- 2020-06-23 magic_paper.tex
@@
 
-\ddd{[Things we must emphasize:
+\ddd{Things we must emphasize:
 \begin{enumerate}
@@
 \item We can get both upper and lower bounds on magic distillation.
-\end{enumerate}•
+\end{enumerate}
 }
@@
 
-\subsection{Majorization of quasi-probabilities in the $\sigma$--fragments}\label{sec:major}
+\subsection{Majorization of quasi-probabilities in $\sigma$--fragments}\label{sec:major}
 
@@
     Let $\R = (\F, \O)$ be a theory of magic. Then $\rho \longrightarrow \tau$ is possible then  $\W{\tau} \prec_\sigma \W{\rho}$ within a $\sigma$--fragment.
+    \nick{I understand that dropping the full-rank assumption on $\sigma$ makes the statement a lot stronger, but also incorrect e.g.
+in the case of the replacement channel $\E(\rho) = \ketbra{0}$, since $d$-majorization in $\O_{\ketbra{0}}$ is not well-defined.}
 \end{theorem}
-\begin{proof}Suppose we can convert $\rho$ into $\tau$ in the magic theory.
+\begin{proof}
+Suppose we can convert $\rho$ into $\tau$ in the magic theory. 
 Thus there is some $\O_\sigma$ and some $\E \in \O_\sigma$ such that $\E(\rho) = \tau$, and $\E(\sigma)=\sigma$. 
@@
 \end{proof}
-This result can be understood as an extension of the idea of a magic monotone, where we replace $\M(\tau) \le \M(\rho)$ with $W_\tau \prec_\sigma W_\rho$.
+This result can be understood as an extension of the idea of a magic monotone, where we replace $\M(\tau) \leq \M(\rho)$ with $\W{\tau} \prec_\sigma \W{\rho}$. 
 However the majorization constraints can be used to place upper bounds on magic state distillation in a way that allows one to incorporate the physics of the allowed operations -- this enables us to bound how much magic can be distilled via quantum operations that, for example, preserve the equilibrium state of the system, or via operations that are symmetric about the $Z$-axis of the Bloch sphere.
@@
 This approach can also provide \emph{lower bounds} on distillation, however now more structure about the specific free operations must be included. 
-This is more involved and we discuss this later in the paper.
+\nick{This is more involved and we discuss this later in the paper.
+Also mention relative majorization somewhere}
 
-\subsection{Majorization computations in a $\sigma$--fragment}
+\subsection{Majorization computations in $\sigma$--fragments}
 A numerically efficient reformulation of $\bmd$-majorization is provided by Lorenz curves.
@@
 \begin{definition}[\textbf{Lorenz curve}]\label{def:lc}
-    Let $\bmz, \bmd \in \reals^d$, where the components of $\bmd$ are positive with $D = \sum_{i=1}^d d_i$ and denote by $\bmu \coloneqq (z_1/d_1, \dots, z_d/d_d)^T$ the vector of ratios between the corresponding components of $\bmz$ and $\bmd$.
+    Let $\bmz, \bmd \in \reals^d$, where the components of $\bmd$ are positive with $D = \sum_{i=1}^d d_i$ and denote by $\tilde{\bmz} \coloneqq (z_1/d_1, \dots, z_d/d_d)^T$ the vector of ratios between the corresponding components of $\bmz$ and $\bmd$.
 
-    Finally, denote by $\pi: \zd \mapsto \zd$ the permutation that sorts $\bmu$, $(\bmu^\downarrow)_i = u_{\pi(i)}$ for all $i=1,\dots,d$.
+    Finally, denote by $\pi: \zd \mapsto \zd$ the permutation that sorts $\tilde{\bmz}$, $(\tilde{\bmz}^\downarrow)_i = z_{\pi(i)}$ for all $i=1,\dots,d$.
 
@@
     \end{equation}
-    The \emph{Lorenz curve} of vector $\bmz$ with respect to $\bmd$ is then $\lc{\bmz}{\bmd}(x)$ for all $x \in [0,1]$
-
-    Expressed explicitly,
-    \begin{equation}
-		\lc{\rho}{\sigma}(x) = (\bmu^\downarrow)_i x + \lc{\rho}{\sigma}(i) - (\bmu^\downarrow)_i x_i,\ x \in (x_{i-1}, x_i],
-	\end{equation}
-	for all $i=1,\dots,d$ with $x_0 \coloneqq 0$.
+    We define the set of points on this curve, $\lc{\bmz}{\bmd}(x),\ x \in [0,1]$, as the \emph{Lorenz curve} of vector $\bmz$ with respect to $\bmd$.
 \end{definition}
-\nick{Move the complicated last equation to appendix?} \ddd{[Yes. Just describe in words, is simpler. the reader with being able to understand how to construct a piecewise linear function.]}
 Components $x_k$ are rescaled by $D$ so that comparison of curves with unequal dimensions is possible.
 In fact, the Lorenz curves $\lc{\bmz}{\bmd}$ and $\lc{\bmz \otimes \bmd}{\bmd \otimes \bmd}$, where $\otimes$ denotes the Kronecker product, are identical.
-Furthermore, a Lorenz curve $\lc{\bmz}{\bmd}(x)$ is always concave in $x$, since it consists of $d$ line segments each with slope $(\bmu^\downarrow)_i$ for $i=1,\dots,d$ which is non-increasing by definition.
+Furthermore, a Lorenz curve $\lc{\bmz}{\bmd}(x)$ is always concave in $x$, since it consists of $d$ line segments each with slope $(\tilde{\bmz}^\downarrow)_i$ for $i=1,\dots,d$ which is non-increasing by definition.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{proof}
-	Borrowing the notation of~\cref{def:lc}, the derivative of the Lorenz curve $\lc{\rho}{\sigma}$ is
+	Borrowing notation from~\cref{def:lc}, let $k_\star$ be the index of the smallest non-negative component $\tilde{\bmz}_{\pi(i)}$ of $\tilde{\bmz}^\downarrow$.
+	It is clear by the construction of the Lorenz curve described in~\cref{def:lc} that the maximum is achieved at
 	\begin{equation}
-		\frac{\rm{d}}{\rm{d}x} \lc{\rho}{\sigma}(x) = (\bmu^\downarrow)_i,\ x \in (x_{i-1}, x_i],
+		x_{k_\star} \coloneqq \sum_{i=1}^{k_\star} (\W{\sigma})_{\pi(i)},
 	\end{equation}
-\ddd{[The function is not differentiable at the key points involved. The maximum is obtained when you sum all the non-negative components.]}
-
+	and takes the value
 	Note that all components of $\W{\sigma}$ are positive, so $(\bmu^\downarrow)_i \geq 0$ if and only if $(\W{\rho})_i \geq 0$ for any $i=1,\dots,d^2$.
@@
 \subsection{Distilling out magic in a fragment}
+\nick{why this new subsection?}
 Consider, as an example, the problem of purifying out magic from a noisy state of the form

### 2020-06-25 magic_paper.tex
Added fragment figures

@@
     \caption{\textbf{Qutrit Wigner distributions of varying magic.} 
-    \subref{fig:maxmix} Maximally mixed state $\frac{1}{3}\id$; \subref{fig:zero} Stabilizer zero state $\ketbra{0}{0}$; \subref{fig:bound} A non-stabilizer Wigner-positive state; \subref{fig:strange} Magic strange state $\ket{{\rm{S}}} = \frac{1}{\sqrt{2}}(\ket{1} - \ket{2})$.
+    \subref{fig:maxmix} Maximally mixed state $\frac{1}{3}\id$; \subref{fig:zero} Stabilizer zero state $\ketbra{0}{0}$; \subref{fig:bound} A non-stabilizer Wigner-positive state; \subref{fig:strange} Magic strange state $\ket{{\rm{S}}} = \frac{1}{\sqrt{2}}(\ket{1} - \ket{2})$ \nick{CITE}.
     \nick{Explain what a magic / bound magic state is in intro}
@@
 A restatement of the theorem including more equivalent conditions and a proof are provided in~\cref{app:major}.
-An example of comparison between different Lorenz curves is illustrated in~\cref{fig:lctoy}.\nick{move around}
+An example of comparison between different Lorenz curves is illustrated in~\cref{fig:lctoy}.
 \begin{figure}
@@
 \begin{proof}
-	Borrowing notation from~\cref{def:lc}, let $k_\star$ be the index of the smallest non-negative component $\tilde{\bmz}_{\pi(i)}$ of $\tilde{\bmz}^\downarrow$.
-	It is clear by the construction of the Lorenz curve described in~\cref{def:lc} that the maximum is achieved at
+	For notational simplicity, denote $(\W{\rho})_i = \W[\bmx]{\rho},\ i = 1,\dots, d^2$ and similarly for $\W{\sigma}$.
+	We choose the index mapping so that the vector of component ratios, 
 	\begin{equation}
-		x_{k_\star} \coloneqq \sum_{i=1}^{k_\star} (\W{\sigma})_{\pi(i)},
+		\tilde{\bm{w}} \coloneqq \left(\frac{(\W{\rho})_1}{(\W{\sigma})_1}, \dots, \frac{(\W{\rho})_{d^2}}{(\W{\sigma})_{d^2}} \right)^T,
 	\end{equation}
-	and takes the value
-	Note that all components of $\W{\sigma}$ are positive, so $(\bmu^\downarrow)_i \geq 0$ if and only if $(\W{\rho})_i \geq 0$ for any $i=1,\dots,d^2$.
+	is sorted in the sense that $\tilde{\bm{w}} = \tilde{\bm{w}}^\downarrow$.
+	Note that all components of $\W{\sigma}$ are positive, so $(\tilde{\bm{w}})_i \geq 0$ if and only if $(\W{\rho})_i \geq 0$ for any $i=1,\dots,d^2$.
 
-	Suppose all components of $\W{\rho}$ are non-negative.
-	Then, $\sn{\rho}=0$ and the global maximum of the Lorenz curve is dictated by the normalisation of $\W{\rho}$ so we trivially have
+	Let $k_\star$ be the index of the smallest non-negative component of $\tilde{\bm{w}}^\downarrow$.
+	Then, $(\W{\rho})_i < 0$ if and only if $i > k_\star$, so the maximum of Lorenz curve $\lc{\rho}{\sigma}(x)$ takes the value 
 	\begin{equation}
-		\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} = 1 = 1 + \sn{\rho}.
+		\lc{\rho}{\sigma}(x_{k_\star}) = \sum_{i=1}^{k_\star} (\W{\rho})_i,
+	\end{equation}
+	and is achieved at
+	\begin{equation}\label{eq:maxloc}
+		x_{k_\star} \coloneqq \sum_{i=1}^{k_\star} (\W{\sigma})_i.
 	\end{equation}
 
-	Suppose that $\W{\rho}$ has at least one negative component.
-	Let $k$ be the index of the smallest non-negative component of $\bmu^\downarrow$.
-	Then the maximum of the Lorenz curve $\lc{\rho}{\sigma}$ occurs at $x_k$, just before its slope becomes negative. 
-	The $x$-coordinate $x_k$ is different for different $\sigma$--fragments but the value of the maximum is the same and is given by
-	\begin{align}
-		&\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)}
-		= \lc{\rho}{\sigma}(x_k)
-		= \sum\limits_{i=1}^k (\W{\rho})_{\pi(i)} \\
-		&= \sum\limits_{\bmx: \W[\bmx]{\rho} \geq 0} \W[\bmx]{\rho}
+	The location of the maximum ($x=x_{k_\star}$) varies from fragment to fragment, but its value is independent of $\sigma$,
+	\begin{equation}
+		\lc{\rho}{\sigma}(x_{k_\star})
+		= \sum\limits_{\bmx: \W[\bmx]{\rho} \geq 0} \W[\bmx]{\rho}
 		= 1 + \sn{\rho}.
-	\end{align}
+	\end{equation}
 
 \end{proof}
-\nick{Perhaps create Lorenz curve appendix and put the proof there as well as how functional form and discretised form of Lorenz curves relate}
-\ddd{[This I think is a simpler approach:]}
-The Lorenz curve of $L_{\bmx |\bmd}(x)$ is defined by piecewise linear sections sequentially linking the points $\{ (a_k,b_k)\}$ where $a_k = \sum_{i=1}^k x_i$, $ b_k = \sum_{i=1}^k d_i$ and we order the components such that $\tilde{x}_i:=x_i / d_i$ form a non-increasing sequence in $i$.
-
-Now let $k_\star$ be the index of the smallest non-negative number in $(\tilde{x}_i)$, and define 
-\begin{align}
-a_\star &:= \sum_{i=1}^{k_\star} x_i\\
-b_\star &:= \sum_{i=1}^{k_\star} d_i.
-\end{align}
-It is then clear that $L_{\rho|\sigma}(x)$ attains a maximum value of $a_\star \ge 1$ at the point $x = d_\star$.
-
-Note that since $\bmd \ge \mathbf{0}$, for $i > k_\star$ we have that $x_i \le 0$, independent of the particular $\bmd$ we use.
-Therefore the value of $a_\star$ is independent of the particular fragment, with only the location of the maximum ($x=b_\star$) varying from fragment to fragment.
-\ddd{[This method is tidier.]}
 
@@
 
-As an example, consider a qutrit distillation process involving the Strange state $\ketbra{\rm{S}}$ depicted in~\cref{fig:strange}. 
-It is the simplest non-trivial case to analyse, since the Strange state only has two distinct components $\left\{ -\frac{1}{3}, \frac{1}{6} \right\}$ with multiplicities $1$ and $8$ respectively.
+As an example, consider the qutrit Strange state $\ketbra{\rm{S}}$ depicted in~\cref{fig:strange}. 
+It is the simplest non-trivial case to analyse because the Strange state only has two distinct components $\left\{ -\frac{1}{3}, \frac{1}{6} \right\}$ with multiplicities $1$ and $8$ respectively.
 Calculating the binomial expansion for the components of $\ket{S}\bra{S}^{\otimes k}$ gives $\{(-1)^j 2^{j-k} 3^{-k}\}_{0 \leq j \leq k}$ with multiplicity $8^{k-j} \binom{k}{j}$ for the $j$-th term.
@@
 \end{equation}
-independent of the particular $\sigma$--fragment. \ddd{[We should also give for what value of $x$ this maximum occurs.]} 
+independent of the particular $\sigma$--fragment.
+\ddd{[We should also give for what value of $x$ this maximum occurs.]} \nick{It will have the form of~\cref{eq:maxloc} and probably cannot be simplified more other than finding $k_\star$ exactly.}
 %1 + \left(\frac{4}{3}\right)^k \sum\limits_{j=0}^{\floor{\frac{k-1}{2}}} 4^{-(2j+1)} \binom{k}{2j+1}
@@
 
-\subsection{Distilling out magic in a fragment}
-\nick{why this new subsection?}
-Consider, as an example, the problem of purifying out magic from a noisy state of the form
+Consider the problem of purifying out magic from a noisy Strange state,
 \begin{equation}
@@
 \end{equation}}
-We now examine the MSD process~(\ref{eq:sdist}) in greater detail for some important $\sigma$--fragments.
+We now examine the MSD process~(\ref{eq:sdist}) in specific $\sigma$--fragments.
 
@@
 If one incorporates noisy channels in the circuit, for example dephasing channels as in~\cref{eq:dephase} in various bases, symmetries are reduced.
-Dephasing channels and general bit-flip error channels are examples of the many error-inducing channels that respect the unital symmetry. \nick{expand}
+Dephasing and bit-flip error channels are examples of the many error-inducing channels that respect the unital symmetry. \nick{expand}
 
-\nick{Replace the following with discussion of MSD process in the unital fragment for various numbers of copies $k$ vs mana}
-
-In~\cref{fig:distill}, we examine the purifying process 
-\begin{equation}\label{eq:purify}
-    \rho_{\rm{S}}^{\otimes k}(\epsilon_{\rm{th}}) \xrightarrow{\E \in \O_\sigma} \rho_{\rm{S}}(0.05),\ \sigma = (1-p)\ketbra{0} + p \frac{1}{3}\id
-\end{equation}
-with $\epsilon_{\rm{th}}$ being the noise level threshold that does not prohibit the process for given number of copies $k$ and $\sigma$--fragment, parametrised by $p$ as a mixture of the zero and the maximally mixed states.
+In~\cref{fig:unital_distill}, we examine the purifying process of~\cref{eq:sdist} with $\epsilon_\tau = 0.05$ which describes all circuits that respect the unital symmetry.
 Thresholds provided by Lorenz curve comparison are always much stricter than mana thresholds.
+\nick{Explain asymptotic behaviour?}
 \begin{figure}
     \centering
-    \includegraphics[scale=0.5]{figs/ratios.pdf}
-    \caption{\textbf{Noise threshold ratios.} Mana and Lorenz curve ratios for the Strange state purifying process in~\cref{eq:purify}.
-    The ratios are calculated for different numbers of initial state copies and different $\sigma$--fragments parametrised by $p$ such that $\sigma = (1-p)\ketbra{0} + p \frac{1}{3}\id$.
+    \includegraphics[scale=0.5]{figs/unital_distill.pdf}
+    \caption{\textbf{Noise thresholds in unital fragment.} Mana and Lorenz curve noise thresholds for the Strange state purification process in~\cref{eq:sdist} with $\epsilon_\tau = 0.05$.
     Lorenz curve comparison consistently gives stricter bounds as proven in~\cref{thm:bounds}.
-    \nick{Consider set of pure stabilizer states instead of $(1-p)\ketbra{0} + p \frac{1}{3}\id$ perhaps}
+    The line $\epsilon = \frac{3}{4}$ indicates the threshold noise beyond which the Strange state no longer contains negativities.
     }
-    \label{fig:distill}
+    \label{fig:unital_distill}
 \end{figure}
@@
 Consider a system driven by Hamiltonian $H$ and a circuit consisting of thermal operations.
-The computational basis now coincides with the energy eigenbasis of Hamiltonian $H$.
-We denote the thermal state $\gamma_\beta = \frac{e^{-\beta H}}{\Z_\beta}$, where $\Z_\beta = \tr[e^{-\beta H}]$.\nick{expand}
+The computational basis now coincides with the Hamiltonian eigenbasis.
+We denote the thermal state at temperature $\beta^{-1}$ by $\gamma_\beta = \frac{e^{-\beta H}}{\Z_\beta}$, where $\Z_\beta = \tr[e^{-\beta H}]$.\nick{expand}
 
-Thermal operations coincide with fragment $\O_{\gamma_\beta}$ \nick{expand}
-The Wigner distribution of thermal state $\gamma_\beta$ always consists of strictly positive components,
+Thermal operations coincide with fragment $\O_{\gamma_\beta}$ \nick{expand}.
+The Wigner distribution of any thermal state $\gamma_\beta$ always consists of strictly positive components,
 \begin{equation}
@@
 
-We generalise the analysis of~\cref{sec:unital} \nick{expand}.
-\nick{Include figure with noise threshold level $\epsilon_{\rm{th}}$ in $y$-axis and temperature $\beta$ in $x$-axis. for various numbers of copies $k$.}
+We generalise the analysis of unital fragments into any circuit with thermalisation noise parametrised by the temperature $\beta^{-1}$.
+In~\cref{fig:thermal_distill}, we examine the majorization bound for the same purification process of~\cref{eq:sdist} with $\epsilon_\tau = 0.05$.
+The curves plotted suggest that there exists a fragment $\O_{\gamma_{\beta_{\rm{max}}}}$ which allows for a highest noise threshold at any given number of copies of the initial state.
+Adding more copies results in a lower optimal temperature $\beta^{-1}$.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[scale=0.5]{figs/thermal_distill.pdf}
+    \caption{\textbf{Noise thresholds in thermal fragments.} Lorenz curve ratios for the Strange state purifying process in~\cref{eq:sdist} with $\epsilon_\tau = 0.05$.
+    The peaks of each curve indicate the optimal temperature $\beta_{\rm{max}}$ that allows for the highest noise threshold at every given number of initial state copies $k$.
+    The line $\epsilon = \frac{3}{4}$ indicates the threshold noise beyond which the Strange state no longer contains negativities.
+    }
+    \label{fig:thermal_distill}
+\end{figure}
 
@@
 \end{definition}
-Note that a contravariant projection is always a surjective mapping for both states and operations, so that the conditions in~\cref{def:contraproj} make sense.
 The use of covariant and contravariant in~\cref{def:covproj,def:contraproj} refers to the direction of implication between the two pre-orders and operation compositions\footnote{Note that strictly these are not projections in the sense of $\Pi^2 = \Pi$, but are instead morphisms.
 Here our use of the term projection is motivated by the idea that one one generally loses information about $\R$ under the mapping.}.
+
+\nick{Perhaps scrap definition of contravariant projection and define contravariant fragment as a subtheory $\R'$ where there exists a (injective) covariant projection from $\R'$ to parent theory $\R$.
+That would make every subtheory $\R' = (\F', \O')$ a contravariant fragment if $\O'$ is closed under composition, this includes $\sigma$--fragments.}
 

### 2020-06-26 magic_paper.tex
Comments added. Very rough trial title given. Section on Symplectic Majorization started.

@@
 \begin{enumerate}
+\item Perhaps a nice lead-in question: ``What happens if we view stabilizer states as thermodynamic equilibrium states and magic as a form of free energy?''
 \item We can tackle more `physicsy' questions like: how much magic can be distilled via free operations with some given fixed-point structure? E.g. 
@@
 
-We can therefore view mana as one of the features of the Lorenz curve, its maximum.
+We can therefore view mana as just one of the features of the Lorenz curve, namely its maximum value. This implies the following result.
 \begin{theorem}\label{thm:bounds}
-    Given a magic state conversion $\rho \longrightarrow \tau$, the majorization condition is stronger than the mana condition in all $\sigma$--fragments.
+    Given a magic state conversion $\rho \longrightarrow \tau$, the majorization condition is stronger than the mana condition in every $\sigma$--fragment.
 \end{theorem}
@@
 independent of the particular $\sigma$--fragment.
-\ddd{[We should also give for what value of $x$ this maximum occurs.]} \nick{It will have the form of~\cref{eq:maxloc} and probably cannot be simplified more other than finding $k_\star$ exactly.}
+\ddd{[We should also give for what value of $x$ this maximum occurs.]} \nick{It will have the form of~\cref{eq:maxloc} and probably cannot be simplified more other than finding $k_\star$ exactly.}\ddd{[Finding $k_\star$ is perfect.
+We'll always have the complexity of the free state distribution to deal with.
+For the unital fragment and thermal fragment this will be computable though.]}
 %1 + \left(\frac{4}{3}\right)^k \sum\limits_{j=0}^{\floor{\frac{k-1}{2}}} 4^{-(2j+1)} \binom{k}{2j+1}
@@
 
+\section{Lower bounds in $\sigma$-fragments}
+\ddd{[Am throwing down some rough material, to be polished later.]}
+
+In order to obtain lower bounds one must now make precise what the free operations actually are in the  theory, beyond the condition of preserving Wigner-positivity.
+
+We first consider the unital fragment, and consider the transformations possible using Clifford unitaries, and convex mixtures of Clifford unitaries.
+We denote the Clifford group as $\C$, and given some quantum state $\rho$ the accessible states in the unital fragment are given by $\E(\rho) = \sum_{g \in \C} p(g) U(g) \rho U(g)^\dagger$.
+
+\subsection{Symplectic majorization of magic state Wigner distributions.}
+We now exploit the the group structure, which leads to a more general notation majorization that has been extensively studied in the classical context, but to our knowledge has not yet been used in quantum information theory.
+
+\begin{definition} Given a group $G$ that acts on a vector space $V$, we say that $\bmx$ \emph{$G$-majorises} $\bmy$ precisely when $\y \in H(\x)$, where $H(\x)$ is the convex hull of $\{g \x : g \in G\}$.
+We denote this as $\y \prec_G \x$.
+\end{definition}
+
+Now any quantum state $\rho$ has a Wigner distribution $W_\rho(\x)$. Given a Clifford unitary $\U \in \C$ we have that its representation in the Heisenberg-Weyl frame is given by
+\begin{equation}
+W_{\U(\rho)} (\x) = [\mbox{\ddd{fill in}}].
+\end{equation}
+
+This group action corresponds to the action of the affine symplectic group on the discrete phase space $\P_d$.
+To proceed we can study the discrete translational action, and the symplectic action separately.
+
+\subsection{Cyclic majorization conditions.}
+We can consider for $G$, the cyclic group of order $N$, which is described by $G= \< g | g^N = e\>$.
+in Terms of the Wigner distributions, this arises for the discrete lattice translations arising from displacement operators.
+
+A set of necessary and sufficient conditions for cyclic majorization has been obtained and is given as follows. \ddd{[I'll fill this out soon.]}
+\subsection{Symplectic majorization for qutrit magic}
+The qutrit system provides a good illustration of the techniques.
+In this case the symplectic group $SL(2,\mathbb{Z}_3)$ is isomorphic (up to $\pm \I$) the symmetry group of the tetrahedron, which in turn is isomorphic to $S_4$, the permutation group on 4 symbols.
+Therefore we expect in this case that symplectic majorization on $\P_3$ corresponds to a restricted form of majorization.
+
+\subsection{Fundamental Regions of a group $G$}
+\ddd{[This is theory for the appendices, and also to help flesh out the theory of $G$ majorization. It looks a bit technical, but the core idea is simple enough once you get it.]}
+Given a group $G$ that acts on a vector space $V$, we now have the following concept.
+\begin{definition} A \emph{fundamental region} $F$ of $G$ in $V$ is any open set $F$ such that $F \cap gF = \varnothing$ for $g \ne e$ and moreover 
+\begin{equation}
+V = \bigcup_{g} \overline{g F}.
+\end{equation}
+\end{definition}
+Here, the overline denotes the closure of a set.
+Loosely speaking, we can view $F$ as obtained by quotienting the vector space $V$ via the group action.
+We then have the following key theorem, which is proved in [CITE].
+\begin{theorem} If $G$ has a fundamental region $F$ that is unique, modulo actions of the group $F\rightarrow gF$, then $\bar{F}$ is a closed, convex cone and for any $\x, \y \in \bar{F}$ we have
+\begin{equation}
+\y \prec_G \x \Leftrightarrow \mathbf{a}\cdot \y \le \mathbf{a} \cdot \x, \mbox{ for all } \mathbf{a} \in \bar{F}.
+\end{equation}
+\end{theorem}
+If the cone $\bar{F}$ is finitely generated, namely 
+\begin{equation}
+\bar{F} = \mbox{cone}( \mathbf{c}_1, \dots, \mathbf{c}_N),
+\end{equation}
+for some finite set of vectors, then the majorization condition reduces to checking a \emph{finite} set of inequalities, namely checking $\mathbf{c}_k \cdot \y \le \mathbf{c}_k \cdot \x$ for $k=1, \dots , N$.
+
+Note now that any group action $G$ on a vector space $V$ always has a fundamental region. Consider any $\x \in V$ such that $g \x \ne \x$ unless $g =e$. For this we define
+\begin{equation}
+K = \{ \mathbf{a} \in V : \sup_g \left [ (g\mathbf{a})\cdot \x \right ] = \mathbf{a} \cdot \x \},
+\end{equation}
+then $F = K_{\mbox{\tiny int}}$ is a fundamental region of $G$ in $V$, where $ K_{\mbox{\tiny int}}$ is the interior of the set $K$.
+In simple terms, this fundamental region corresponds to the set of vectors that are `close' to $\x$, in the sense that any non-trivial group action $\mathbf{a} \rightarrow g \mathbf{a}$ on them moves them away from $\x$ with respect the inner product.
+See [CITE] for a proof of this statement.
+
+\subsection{Computing the fundamental region $F$ for the qutrit}
+Firstly, note that we actually have that $SL(2, \mathbb{Z}_3)$ is represented by $U(g)$ on $\P_3$, and so we should use that notation for precision.
+
+Since the symplectic group for $d=3$ is a reflection group, it turns out that this guarantees that an essentially unique fundamental region exists, and so we can reduce to a \emph{finite} set of majorization conditions (I think 5 in this case).
+Note that the $K$ defined above is always a closed, convex cone.
+This means it should be `easy' to determine the fundamental region.
+Reflection groups are Coexter groups, and I believe this set $K$ is essentially a Weyl chamber in that language.
+Anyhow, let's not get distracted by abstraction.
+
+The concrete recipe going forward:
+\begin{enumerate}
+\item Pick your favorite $\x \in P_3$ that is \emph{not} stabilized by $g\ne e$. I.e. a vector that moves under all non-trivial group actions.
+\item For each $g_k$ look for the extremal cases of $\y$ such that have constant inner product with $\x$. This corresponds to 
+\begin{equation}
+\left [ (U(g_k) -\I) \y \right ] \cdot \x = 0 \mbox{ for }k=1, \dots ,24.
+\end{equation}
+Or equivalently,
+\begin{equation}
+\y \cdot A^T\x = 0,
+\end{equation}
+where $A := U(g_k) -\I$.
+\item Write down the matrix equation for each $g_k$.
+\item Each of these conditions defines a hyperplane $H_k$ in $\P_3$ corresponding to the boundary of $K$.
+\item We possibly don't need to range over all 24 group elements....but am not sure on this.
+\item From this, we should be able to extract a generating set of vectors.
+\end{enumerate}
+
+\subsection{Symplectic majorization for $d =5$ and beyond.}
+For the case $d=5$ we also have a particularly simple group structure, where now the symplectic group $SL(2, \mathbb{Z}_5)$ is isomorphic to the symmetry group of the icosahedron.
+This is another reflection group and therefore we can again obtain the finite set of majorization conditions to describe it.
+Here the order of the group is $60$ and so we probably shouldn't make Nick compute this by hand.
+\newpage
 \section{Extension to general quantum resource theories}

### 2020-06-27 magic_paper.tex
Toy example of G-majorization added to illustrate how the algorithm works explicitly.

@@
 
+\subsection{Toy example to see how the algorithm works}
+Okay, let's see how it works in a simple case.
+Let's consider the case of $V= \mathbb{R}^2$ and $G=S_2=\<g|g^2=e\>$ with the group action $g.(x,y) = (y,x)$ that swaps the components of the vector.
+We should get standard majorization out of this $G$--majorization.
+
+First we find an $\x$ that transforms non-trivially under non-trivial group actions. The vector $\x=(1,0)$ does this. To construct a fundamental region we now look at the equation 
+\begin{equation}
+[g.(x,y) - (x,y)] \cdot (1,0) = 0
+\end{equation}
+and solve for $x,y$. This becomes,
+\begin{equation}
+(y-x, x-y)\cdot(1,0)=0,
+\end{equation}
+which implies the hyperplane (line!) $y=x$ is the \emph{boundary} of the fundamental region. Since we decided to start with $(1,0)$ we can take the region to the right of this line, and so:
+\begin{equation}
+F = \{(x,y) : x>y \}
+\end{equation}
+where we note that we use the strict inequality to get the interior. The region $\bar{F}$ is a half-space, but this is actually a cone, and can be written as
+\begin{equation}
+F= \mbox{cone}( (1,1),(-1,-1), (5,0)).
+\end{equation}
+The first two vectors give the boundary, and we just need one other vector inside $F$ to generate it fully, chosen arbitrarily to be $(5,0)$.
+This last one is needed since $(1,1)$ and $(-1,-1)$ are linearly dependent!
+Therefore
+\begin{align}
+\mathbf{c}_1 &= (1,1) \nonumber \\
+\mathbf{c}_2 &= (-1,-1) \nonumber \\
+\mathbf{c}_3 &= (5,0).
+\end{align}
+The $S_2$--majorization ordering is then given by
+\begin{equation}
+\y \prec \x \Leftrightarrow \mathbf{c}_k \cdot \y \le  \mathbf{c}_k \cdot \x,
+\end{equation}
+for $k=1,2,3$ whenever $\x,\y \in F$.
+Note that is gives the ordering for all vectors in the space, since any general vector can be transformed into $F$ via a group action, since $F$ is a fundamental region.
+Indeed mapping an $\x$ into $F$ is simply $\x \rightarrow \x^\downarrow$, the sorting maneuver!
+The generating vectors $(1,1)$ and $(-1,-1)$ imply that both 
+\begin{equation}
+y_1 + y_2 \le x_1 +x_2,
+\end{equation}
+and
+\begin{equation}
+y_1 + y_2 \ge x_1 +x_2,
+\end{equation}
+which becomes the majorization condition
+\begin{equation}
+y_1+y_2 = x_1 + x_2.
+\end{equation}
+Easy! The final condition from $\mathbf{c}_3=(1,0)$ is then the condition that
+\begin{equation}
+5y_1 \le 5x_1 \Rightarrow y_1 \le x_1,
+\end{equation}
+which is the final majorization condition.
+Thus we have shown how the familiar majorization structure corresponds to the theory of $G$--majorization, and the cone ordering structure that comes from fundamental regions.
+
 \subsection{Symplectic majorization for $d =5$ and beyond.}

### 2020-06-28 magic_paper.tex
Two more G-majorization examples added to understand how it works better. New title given that seems more eye-catching and interesting.

@@
 
-\input{title}
+\preprint{APS/123-QED}
+
+\title{Thermodynamic fragments in magic state theories}
+
+\author{Nikolaos Koukoulekidis}
+	\affiliation{Department of Physics, Imperial College London, London SW7 2AZ, UK}
+	\email{nk2314@imperial.ac.uk}
+\author{David Jennings}
+	\affiliation{School of Physics and Astronomy, University of Leeds, Leeds, LS2 9JT, UK}
+	\affiliation{Department of Physics, Imperial College London, London SW7 2AZ, UK}
+
+\date{\today}
 \maketitle
@@
 
+\subsection{Another toy example -- non-standard majorization this time}
+Okay, let's look at another option for $V=\mathbb{R}^2$.
+Now consider the group $G=\mathbb{Z}_2 \times \mathbb{Z}_2$ that can be represented as $G=\<g_1,g_2 | g^1=e, g_2 = e, g_1g_2 = g_2g_1\>$, and acts on vectors as $g_1.(x,y) = (-x,y), g_2.(x,y)=(x,-y)$.
+In other words the group just flips vectors about X/Y axes.
+
+A vector that moves under the non-trivial group actions is $(1,1)$, so we use this one and solve for $[g.(x,y) - (x,y)] \cdot (1,1) = 0$. We have for $g = g_1$ the equation
+\begin{equation}
+[(-x,y) - (x,y)]\cdot (1,1) = 0,
+\end{equation}
+which implies the line $x=0$.
+
+For $g=g_2$ we have
+\begin{equation}
+[(x,-y) - (x,y)]\cdot (1,1) = 0,
+\end{equation}
+which implies the line $y=0$.
+
+For $g=g_1g_2$ we have
+\begin{equation}
+[(-x,-y) - (x,y)]\cdot (1,1) = 0,
+\end{equation}
+which implies the line $x+y=0$. The open region bounded by these three conditions is the set
+\begin{equation}
+F := \{ (x,y) : x>0, y>0\}.
+\end{equation}
+So the positive quadrant of $\mathbb{R}^2$ is a fundamental region for $G$, which makes sense since via sign flips we can map this onto the whole plane, once we close the set.
+This is again a convex cone and $\bar{F} = \mbox{cone}((1,0), (0,1))$.
+Thus given any two vectors $\x,\y$ we first act with $G$ to flip their signs so that their components are all positive, $\x \rightarrow \x^\star\ge \mathbf{0}$, then $\y \prec_G \x$ if and only if $y_1 \le x_1$ and $y_2 \le x_2$.
+This implies that
+\begin{equation}
+\y \prec_G \x \Leftrightarrow \y^\star \le \x^\star. 
+\end{equation}
+So the $G=\mathbb{Z}_2 \times \mathbb{Z}_2$ majorization gives the component-wise ordering on vectors once you sort them. It is clear that this extends to any $G=\mathbb{Z}_2^{\times n}$.
+\subsection{A more complex example $S_3$ on $\mathbb{R}^3$.}
+So the symmetric group $S_n$ always gives majorization.
+But the symmetric group has $|S_n| = n!$ elements to it, which is super-exponentially big in $n$.
+We clearly don't have to check $n!$ equations, since the majorization conditions involve just $n+1$ inequalities, and so it must be that the basic generating conditions of the group suffice to determine the fundamental region of $G$.
+
+Let's look at $V = \mathbb{R}^3$ and $G=S_3$ acting on $\x = (x_i)$ as $g.\x = (x_{g^{-1}}(i))$.
+A vector that transforms non-trivially under all non-trivial actions is $(2,1,0)$.
+Let's look at the transpositions, and the boundary planes they give first.
+
+For $g= (1\,\,2)$ we have the equation
+\begin{equation}
+[(y,x,z) - (x,y,z)] \cdot (2,1,0) = 0,
+\end{equation}
+which implies the plane $2(y-x)+ x-y = 0$, namely,
+\begin{equation}
+H_1 = \{(x,y,z) : y=x\}.
+\end{equation}
+The other choices of transpositions work the same and give the planes
+\begin{align}
+H_2 &= \{(x,y,z) : y=z\} \\
+H_3 &= \{(x,y,z) : x=z\}.
+\end{align}
+Note that their intersection gives the line $\{(x,y,z) : x=y=z\}$, which is the line of uniform vectors at the bottom of the majorization pre-order.
+
+What information do the $3$-cycles give? Okay, let's now look at $g=( 1 \,\, 2 \,\, 3)$. The core equation for this becomes
+\begin{equation}
+[(z,x,y) - (x,y,z)] \cdot (2,1,0) = 0,
+\end{equation}
+and so gives
+\begin{align}
+2(z-x) + (x-y) &= 0 \nonumber \\
+\Rightarrow x+y &=2z. 
+\end{align}
+Namely the plane
+\begin{equation}
+H_4 = \{(x,y,z) :  x+y =2z\}.
+\end{equation}The remaining $3$--cycle $(3\,\,2\,\,1)$ gives
+\begin{align}
+H_5 &= \{(x,y,z) : y+z = 2x\}.
+\end{align}
+Note that $|S_3| = 6$, but the identity element $g=e$ gives no constraint, and so there are exactly $5$ bounding planes.
+Note also that the line $\{ (t,t,t)\} $ is again the intersection of all the planes.
+
+These 5 planes bound a cone containing $(2,1,0)$, namely the fundamental region $F$. What's a good algorithm to obtain a generating set of vectors for this cone?
+
+Firstly, since the line $\{(t,t,t)\}$ being the intersection of all the planes, is definitely on the boundary of $F$, this means we must have $\mathbf{c}_1 = (1,1,1)$ and $\mathbf{c}_2 = (-1,-1,-1)$ in our generating set.
+Perhaps a good algorithm is to compute intersections, obtain generating vectors for these intersections of the hyperplanes, $H_{ij}$ and then let $K_i$ and $K_j$ be the half-spaces in which $(2,1,0)$ resides.
+Now the intersection of two cones, is itself a cone so we can just keep intersecting the half-space/cones.
+Thus, we compute
+\begin{align}
+H_{12} &:= H_1 \cap H_2 \\
+&=\{ (t,t,t) : t\in \mathbb{R}\}=:L.
+\end{align}
+Similarly, $H_{13} = H_{23}= L$. What about the other intersections? Well $H_{14} = H_{15}=L$. In fact all intersections are the same! 
+\begin{equation}
+H_{ij} = H_i \cap H_j = L \mbox{ for all } i,j.
+\end{equation}
+The fundamental region is given by the intersection of $K_1$ and $K_2$, or any other two half-spaces.
+This is generated by $\mathbf{c}_1$ and $\mathbf{c}_2$ above, and any two independent vectors in the intersection of these half-spaces.
+We can choose
+\begin{align}
+\mathbf{c}_3 &= (1,1,0) \\
+\mathbf{c}_4 &= (1,0,0),
+\end{align}
+note that $\mathbf{c}_3 \in H_1$ and $\mathbf{c}_4 \in H_2$, while $\mathbf{c}_3 \in K_2$ and $\mathbf{c}_4 \in K_1$ and so this works correctly. We thus have
+\begin{equation}
+\bar{F} = \mbox{cone}(\mathbf{c}_1 ,\mathbf{c}_2 ,\mathbf{c}_3 ,\mathbf{c}_4 ).
+\end{equation}
+The first two inequalities give the condition that
+\begin{equation}
+x_1+x_2+x_3 = y_1+y_2+y_3,
+\end{equation}
+while the remaining two conditions give the inequalities
+\begin{align}
+y_1 &\le x_1 \\
+y_1+y_2 &\le x_1 +x_2.
+\end{align}
+This is the standard majorization relation.
+Geometrically, the cone $\bar{F}$ is actually a funny one to visualise: it consists of a half-line radiating out from $(0,0,0)$ to $(-1, -1, -1)$, together with the triangular ``infinite pyramid'' generated by positive combinations of $(1,1,1), (1,1,0), (1,0,0)$.
+But we can also take positive linear combinations of $(-1,-1,-1)$ and e.g.
+$(1,1,0)$ and so it is still a bit tricky to visualise.
 \subsection{Symplectic majorization for $d =5$ and beyond.}

### 2020-07-07 magic_paper.tex
Added content in Fragments section. Calculations seem hard, the trick doesnt work, but stabilizer fragments look kinda interesting

@@
 \begin{equation}\label{eq:distprocess}
-    \rho^{\otimes k} \xrightarrow{\E \in \O_\sigma} \tau,
-\end{equation}
-where $k$ copies of a noisy magic state $\rho$ are converted into a target single-copy state $\tau$. \nick{expand?}
-
-In general, the Wigner components of a $k$-copy state $\rho^{\otimes k}$ can be calculated, along with their multiplicities, from $W_\rho$ by expanding the terms in the multinomial expansion $\left( \sum_{\bm{z} \in \cal{P}_d} W_\rho(\bm{z}) \right)^n$.
+    \rho^{\otimes n} \xrightarrow{\E \in \O_\sigma} \tau,
+\end{equation}
+where $n$ copies of a noisy magic state $\rho$ are converted into a target single-copy state $\tau$. \nick{expand?}
+
+In general, the Wigner components of a $n$-copy state $\rho^{\otimes n}$ can be calculated directly from $W_\rho$, along with their multiplicities, by expanding the terms in the multinomial expansion $\left( \sum_{\bm{z} \in \cal{P}_d} W_\rho(\bm{z}) \right)^n$.
+\nick{is this clear?}
 This follows from the multiplicativity of the Wigner distribution.
@@
 As an example, consider the qutrit Strange state $\ketbra{\rm{S}}$ depicted in~\cref{fig:strange}. 
-It is the simplest non-trivial case to analyse because the Strange state only has two distinct components $\left\{ -\frac{1}{3}, \frac{1}{6} \right\}$ with multiplicities $1$ and $8$ respectively.
-Calculating the binomial expansion for the components of $\ket{S}\bra{S}^{\otimes k}$ gives $\{(-1)^j 2^{j-k} 3^{-k}\}_{0 \leq j \leq k}$ with multiplicity $8^{k-j} \binom{k}{j}$ for the $j$-th term.
-This allows analytical calculation of all Lorenz curve points, and for the $k$-copy state we have that
+It is the simplest non-trivial case to analyse because its Wigner distribution consists of two distinct components.
+Calculating the components of $\ket{S}\bra{S}^{\otimes n}$ allows for analytical calculation of the maximum of the $n$-copy state,
 \begin{equation}\label{eq:Skmax}
-    \max_x{\lc{\ketbra{S}^{\otimes k}} {\sigma}}(x) = \frac{1}{2}\left (1 + \left(\frac{5}{3}\right)^k \right),
-\end{equation}
-independent of the particular $\sigma$--fragment.
-\ddd{[We should also give for what value of $x$ this maximum occurs.]} \nick{It will have the form of~\cref{eq:maxloc} and probably cannot be simplified more other than finding $k_\star$ exactly.}\ddd{[Finding $k_\star$ is perfect.
-We'll always have the complexity of the free state distribution to deal with.
-For the unital fragment and thermal fragment this will be computable though.]}
-%1 + \left(\frac{4}{3}\right)^k \sum\limits_{j=0}^{\floor{\frac{k-1}{2}}} 4^{-(2j+1)} \binom{k}{2j+1}
-%\sum_{n=1, n \mbox{ odd}}^k a^n \binom{k}{n} = \frac{1}{2} \left [  (1+a)^k - (1-a)^k \right ]
+    \max_x{\lc{\ketbra{S}^{\otimes n}} {\sigma}}(x) = \frac{1}{2}\left (1 + \left(\frac{5}{3}\right)^n \right).
+\end{equation}
+Its location $x_{k_\star}$ depends on the $\sigma$--fragment and is given by~\cref{eq:maxloc} with $k_\star = \frac{1}{2}(7^n + 9^n)$.
+%1 + \left(\frac{4}{3}\right)^n \sum\limits_{j=0}^{\floor{\frac{n-1}{2}}} 4^{-(2j+1)} \binom{n}{2j+1}
+%\sum_{i=j, j: odd}^n a^j \binom{n}{j} = \frac{1}{2} [ (1+a)^n - (1-a)^n ]
+%$\{(-1)^j 2^{j-n} 3^{-n}\}_{0 \leq j \leq n}$ with multiplicity $8^{n-j} \binom{n}{j}$ for the $j$-th term
 
@@
 \begin{equation}\label{eq:sdist}
-	\rho_{\rm{S}}(\epsilon)^{\otimes k} \xrightarrow{\E \in \O_\sigma} \rho_{\rm{S}}(\epsilon_{\tau})
+	\rho_{\rm{S}}(\epsilon)^{\otimes n} \xrightarrow{\E \in \O_\sigma} \rho_{\rm{S}}(\epsilon_{\tau})
 \end{equation}
@@
 \begin{equation}\label{eq:ethresh}
-	\epsilon_{\rm{th}}(k, \epsilon_\tau, \sigma) \coloneqq \sup{\{\epsilon:\ \lc{\rho_{\rm{S}}(\epsilon)^{\otimes k}}{\sigma} \geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})}{\sigma}\}},
-\end{equation}
-so that the MSD process~(\ref{eq:sdist}) is impossible for all $\epsilon > \epsilon_{\rm{th}}(k, \epsilon_\tau, \sigma)$
+	\epsilon_{\rm{th}}(n, \epsilon_\tau, \sigma) \coloneqq \sup{\{\epsilon:\ \lc{\rho_{\rm{S}}(\epsilon)^{\otimes n}}{\sigma} \geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})}{\sigma}\}},
+\end{equation}
+so that the MSD process~(\ref{eq:sdist}) is impossible for all $\epsilon > \epsilon_{\rm{th}}(n, \epsilon_\tau, \sigma)$
 
@@
 \begin{equation}\label{eq:ethresh}
-	k_{\rm{th}}(\epsilon, \epsilon_\tau, \sigma) \coloneqq \min{\{k:\ k \in \mathbb{N}, \lc{\rho_{\rm{S}}(\epsilon)^{\otimes k}}{\sigma} \geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})}{\sigma}\}}.
+	n_{\rm{th}}(\epsilon, \epsilon_\tau, \sigma) \coloneqq \min{\{n:\ n \in \mathbb{N}, \lc{\rho_{\rm{S}}(\epsilon)^{\otimes n}}{\sigma} \geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})}{\sigma}\}}.
 \end{equation}}
@@
 Depending on the symmetries of such operations, a sequence of them may belong in various $\sigma$--fragments and the majorization condition~(\ref{eq:majbound}) needs to be checked in all these $\sigma$-fragments that reflect the symmetries of the operation sequence.
-However, they always belong to the \emph{unital fragment} $\O_{\frac{1}{d}\id}$
+However, they always belong to the \emph{unital fragment} $\O_{\frac{1}{d}\id}$.
 
@@
 Dephasing and bit-flip error channels are examples of the many error-inducing channels that respect the unital symmetry. \nick{expand}
+
+Lorenz curve analysis simplifies significantly in the unital fragment \nick{or so I thought initially}, because the invariant Wigner distribution is the uniform distribution depicted in~\cref{fig:maxmix}.
+Therefore, $\W[\bmu]{(\frac{1}{d}\id)^{\otimes n}} = \frac{1}{d^{2n}}$ for all $\bmu \in \pd[d^n]$ and the Lorenz curve ordering only depends on $\rho$ \nick{rephrase}
+The Lorenz curve $\lc{\ketbra{\rm{S}}^{\otimes n}}{\frac{1}{d}\id}$ consists of $n+1$ line segments, with $n$ endpoints, or ``elbows'', between $(0,0)$ and $(1,1)$. 
+The $k_\star$-th endpoint is the maximum in~\cref{eq:Skmax} occuring at 
+\begin{equation}
+	x_{k_\star} = \frac{1}{2}\left(1 + \left( \frac{7}{9} \right)^n \right).
+\end{equation}
+
+All $n$ elbows, depicted in the diagram of~\cref{fig:lccalc}, are given by the following sums, $\left( x_k, \lc{\ketbra{\rm{S}^{\otimes n}}}{\frac{1}{d}\id}(k) \right) =$
+\begin{equation}\label{eq:leftelb}
+	\left( \frac{1}{9^n} \sum\limits_{j=0}^{k-1} 8^{2j} \binom{n}{2j}, \frac{1}{3^n} \sum\limits_{j=0}^{k-1} 4^{2j} \binom{n}{2j} \right)
+\end{equation}
+for all elbows left of the maximum, $k = 1, \dots, k_\star = \floor{\frac{n}{2}}+1$ and $\left( x_k, \lc{\ketbra{\rm{S}^{\otimes n}}}{\frac{1}{d}\id}(k) \right) = (x_{k_\star}, L(k_\star)) + $
+\begin{equation}\label{eq:rightelb}
+	\left( \left(\frac{8}{9}\right)^n \sum\limits_{j=0}^{k'-1} 8^{-(2j+1)} \binom{n}{2j+1}, \left(\frac{4}{3}\right)^n \sum\limits_{j=0}^{k'-1} 4^{-(2j+1)} \binom{n}{2j+1} \right),
+\end{equation}
+for all elbows right of the maximum, $k' = k_\star, \dots, n$.
+
+\begin{figure}%
+    \centering
+    \subfigure[][]{%
+    \label{fig:lcs_maxmix}%
+    \includegraphics[height=3cm]{figs/lcs_maxmix.pdf}
+    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
+    }\hspace{1pt}%
+    \subfigure[][]{%
+    \label{fig:lcs_thermal}%
+    \includegraphics[height=3cm]{figs/lcs_thermal.pdf}
+    %\caption{Zero state $\ketbra{0}{0}$}%
+    }\\
+    \subfigure[][]{%
+    \label{fig:lcs_zero}%
+    \includegraphics[height=3cm]{figs/lcs_zero.pdf}
+    %\caption{Bound state}%
+    }\hspace{1pt}%
+    \subfigure[][]{%
+    \label{fig:lcs_one}%
+    \includegraphics[height=3cm]{figs/lcs_one.pdf}
+    %\caption{Strange state $\ketbra{S}{S}$}%
+    }
+    \caption{\textbf{Lorenz curves of Strange state copies.} Lorenz curves of $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ for $n=1,2,3,4$.
+    Solid lines represent pure Strange states ($\epsilon = 0$); dashed lines represent noisy Strange states ($\epsilon = 0.1$).
+    \subref{fig:lcs_maxmix} Unital fragment; \subref{fig:lcs_thermal} Thermal fragment with $H = (0,1,2)$ and $\beta = 0.5$; \subref{fig:lcs_zero} Fragment $\O_{\ketbra{0}{0}}$ (corresponds to red curve in~\cref{fig:stab_distill}); \subref{fig:lcs_one} Fragment $\O_{\ketbra{1}{1}}$ (corresponds to blue curve in~\cref{fig:stab_distill}).
+    }%
+    \label{fig:wstate_examples}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.5]{figs/lccalcdiagram.pdf}
+    \caption{\textbf{Anatomy of Strange state Lorenz curve}
+    There are $n$ ``elbows'' in this Lorenz curve of an $n$-copy Strange state.
+    Labels $k, k'$ indicate elbows left and right of the maximum respectively.
+    Their coordinates are given in~\cref{eq:leftelb,eq:rightelb}.
+    }
+    \label{fig:lccalc}
+\end{figure}
+
+We plot the Lorenz curves of pure and noisy Strange state $n$-copy states for $n$ up to $4$ in~\cref{fig:lcs}.
+For $n=1$, the Lorenz curve is simply additive, 
+\begin{equation}
+\lc{(1-\epsilon)\rho + \epsilon\sigma}{\sigma} = (1-\epsilon)\lc{\rho}{\sigma} + \epsilon\lc{\sigma}{\sigma},
+\end{equation}
+for any $\sigma, \rho$, but for $n\geq 2$, calculations become more complicated.
 
@@
 
-\begin{figure}[t]
+\begin{figure}
     \centering
     \includegraphics[scale=0.5]{figs/thermal_distill.pdf}
-    \caption{\textbf{Noise thresholds in thermal fragments.} Lorenz curve ratios for the Strange state purifying process in~\cref{eq:sdist} with $\epsilon_\tau = 0.05$.
+    \caption{\textbf{Threshold dependence on temperature in thermal fragments.} Lorenz curve ratios for the Strange state purifying process in~\cref{eq:sdist} with $\epsilon_\tau = 0.05$.
     The peaks of each curve indicate the optimal temperature $\beta_{\rm{max}}$ that allows for the highest noise threshold at every given number of initial state copies $k$.
@@
 \end{figure}
+
+\newpage
+
+\subsection{Magic in pure stabilizer fragments}\label{sec:magstab}
+
+There exist $d(d+1)$ pure stabilizer states for a $d$-dimensional system, all of which correspond to a uniform distribion over an affine line in the phase space \nick{CITE}.
+As an example, the distribution of the qutrit zero state $\ketbra{0}$ is illustrated in~\cref{fig:zero}.
+Any pure stabilizer state $\sigma$ is a rank--$1$ state and contains $d^2 - d$ zeros in its Wigner distribution, so we approximate it by the full--rank state $\sigma' = (1-\epsilon)\sigma + \epsilon \frac{1}{d}\id$ for some infinitesimal $\epsilon > 0$.
+
+We explore the distillation process of~\cref{eq:sdist} in these modified fragments $\O_\sigma'$ in~\cref{fig:stab_distill}.
+We repeat the plot for distillation of Norrell states in~\cref{fig:stab_distill_norrell}.
+
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.5]{figs/stab_distill.pdf}
+    \caption{\textbf{Strange state distillation thresholds in stabilizer fragments.} Lorenz curve thresholds for the Strange state purifying process in~\cref{eq:sdist} with $\epsilon_\tau = 0.05$.
+    All $12$ stabilizer fragments produce two distinct trends: ($k=0$ - red curve) the stabilizer states that have non-zero value at the origin of the phase space lie low and ($k=1,2$ - blue curve) the stabilizer states that have a zero value at the origin of the phase space lie high.
+    This is specific to the Strange state.
+    For high enough copies, these Lorenz curves surpass the unital noise threshold $\epsilon_{\rm{th}} = \frac{3}{4}$.
+    }
+    \label{fig:stab_distill}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.5]{figs/stab_distill_norrell.pdf}
+    \caption{\textbf{Norrell state distillation thresholds in stabilizer fragments.} Lorenz curve thresholds for the Strange state purifying process in~\cref{eq:sdist} with $\epsilon_\tau = 0.05$.
+    For high enough copies, certain Lorenz curves surpass the unital noise threshold $\epsilon_{\rm{th}} = \frac{3}{4}$.
+    }
+    \label{fig:stab_distill_norrell}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2020-07-13 magic_paper.tex
Minimum copies plot

@@
 
-All $n$ elbows, depicted in the diagram of~\cref{fig:lccalc}, are given by the following sums, $\left( x_k, \lc{\ketbra{\rm{S}^{\otimes n}}}{\frac{1}{d}\id}(k) \right) =$
+All $n$ elbows, depicted in the diagram of~\cref{fig:lccalc}, are given by the following sums, $\left( x_k, \lc{\ketbra{\rm{S}}^{\otimes n}}{\frac{1}{d}\id}(k) \right) =$
 \begin{equation}\label{eq:leftelb}
@@
 \end{equation}
-for all elbows left of the maximum, $k = 1, \dots, k_\star = \floor{\frac{n}{2}}+1$ and $\left( x_k, \lc{\ketbra{\rm{S}^{\otimes n}}}{\frac{1}{d}\id}(k) \right) = (x_{k_\star}, L(k_\star)) + $
+for all elbows left of the maximum, $k = 1, \dots, k_\star = \floor{\frac{n}{2}}+1$ and $\left( x_k, \lc{\ketbra{\rm{S}}^{\otimes n}}{\frac{1}{d}\id}(k) \right) = (x_{k_\star}, L(k_\star)) + $
 \begin{equation}\label{eq:rightelb}
-	\left( \left(\frac{8}{9}\right)^n \sum\limits_{j=0}^{k'-1} 8^{-(2j+1)} \binom{n}{2j+1}, \left(\frac{4}{3}\right)^n \sum\limits_{j=0}^{k'-1} 4^{-(2j+1)} \binom{n}{2j+1} \right),
-\end{equation}
-for all elbows right of the maximum, $k' = k_\star, \dots, n$.
+	\left( \left(\frac{8}{9}\right)^n \sum\limits_{j=0}^{k' - k_\star - 1} 8^{-(2j+1)} \binom{n}{2j+1}, \left(\frac{4}{3}\right)^n \sum\limits_{j=0}^{k' - k_\star - 1} 4^{-(2j+1)} \binom{n}{2j+1} \right),
+\end{equation}
+for all elbows right of the maximum, $k' = k_\star + 1, \dots, n$.
 
@@
     }%
-    \label{fig:wstate_examples}
+    \label{fig:lcs}
 \end{figure}
@@
     \label{fig:unital_distill}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.5]{figs/unital_distill_copies.pdf}
+    \caption{\textbf{Copies required for Strange state distillation.} Mana and Lorenz curve copy thresholds for the Strange state purification process in~\cref{eq:sdist} with $\epsilon_\tau = 0.05$.
+    Lorenz curve comparison consistently provides higher low bounds on the number of noisy Strange state copies required.
+    }
+    \label{fig:unital_distill_copies}
 \end{figure}

### 2020-07-14 magic_paper.tex
Added algorithm for cyclic majorization.

@@
 
-A set of necessary and sufficient conditions for cyclic majorization has been obtained and is given as follows. \ddd{[I'll fill this out soon.]}
+A set of necessary and sufficient conditions for cyclic majorization has been obtained and is given as follows.
+Suppose $\x, \y$ are two real vectors in $\mathbb{R}^n$.
+Let $\Delta$ be the elementary shift operator, defined by
+\begin{equation}
+\Delta \x = \Delta (x_1, x_2, \dots, x_n) := (x_n, x_1, x_2, \dots, x_{n-1}),
+\end{equation}
+and from this it is clear that $\Delta$ generates a representation of the abelian group $(\mathbb{Z}_n,+)$.
+We now say that $\x$ \emph{cyclically majorizes} $\y$, written $\x \succ_C \y$, if and only if 
+\begin{equation}
+\y = \sum_{k=0}^{n-1} p_k \Delta^k \x,
+\end{equation}
+for some probability distribution $p=(p_k)$. This means that $\y$ lies in the convex hull of the orbit of $\x$ under cyclic shifts. Thus, we may write this condition as $\y = L(\p) \x$, where
+\begin{equation}
+L(\p) :=  \sum_{k=0}^{n-1} p_k \Delta^k,
+\end{equation}
+is a linear operator, as a function of an unknown distribution $\p$. We now have the following key identity for linear operators of this form:
+\begin{equation}
+L(\p)\x = QL(\x) \p,
+\end{equation}
+where $Q$ is a permutation matrix sending $e_0:=(1,0,0,\dots ,0)$ to itself, and otherwise sending $e_k$ to $e_{n-1-k}$, where $e_k=  (0,0,\dots, 0,1,0,\dots, 0)$ is the $k$'th basis vector.
+We thus have
+\begin{align}
+\x \succ_C \y &\Leftrightarrow \y = L(\p) \x \mbox{ for some dist. } \p. \nonumber \\
+&\Leftrightarrow \y = QL(\x) \p \mbox{ for some dist. } \p. \nonumber \\
+&\Leftrightarrow [QL(\x)]^{-1}\y = \p \mbox{ for some dist. } \p. \nonumber \\
+&\Leftrightarrow [QL(\x)]^{-1}\y = \p  \ge \mathbf{0} \mbox{ and normalized}.
+\end{align}
+This implies that to check whether $\x \succ_C \y$ it suffices to compute the components of the left-hand side and ensure non-negativity (I suspect it is normalised if $\x$ and $\y$ are normalised).
+
+Note though that by using Fourier analysis we can simplify this in terms of computational demands to checking if the vector
+\begin{equation}
+\p = C(\x') Q\y,
+\end{equation}
+has non-negative components, where
+\begin{equation}
+\x' := n\F_n [\F_n\x]^{-1},
+\end{equation}
+with $\F_n$ being the discrete Fourier transform, and the bracket term $[\F_n \x]^{-1}$ denotes the vector obtained by inverting the components of $\F \x$ individually.
+So the recipe for cyclic majorization is:
+\begin{enumerate}
+\item Given inputs $\x$ and $\y$.
+\item Compute the vector $\x'$ via two Fourier transforms and $n$ inversions.
+\item Compute the circulant matrix $C(\x')$.
+\item Compute $\C(\x')Q \y$ and check if all components are non-negative.
+\end{enumerate}•
+
 \subsection{Symplectic majorization for qutrit magic}

### 2020-07-15 magic_paper.tex
Added subsection Lorenz curves calculations temporarily, where I include all important results on our ncopy strange state lorenz curve calculations in the unital fragment

--- 2020-07-13 magic_paper.tex
@@
 
-Lorenz curve analysis simplifies significantly in the unital fragment \nick{or so I thought initially}, because the invariant Wigner distribution is the uniform distribution depicted in~\cref{fig:maxmix}.
-Therefore, $\W[\bmu]{(\frac{1}{d}\id)^{\otimes n}} = \frac{1}{d^{2n}}$ for all $\bmu \in \pd[d^n]$ and the Lorenz curve ordering only depends on $\rho$ \nick{rephrase}
-The Lorenz curve $\lc{\ketbra{\rm{S}}^{\otimes n}}{\frac{1}{d}\id}$ consists of $n+1$ line segments, with $n$ endpoints, or ``elbows'', between $(0,0)$ and $(1,1)$. 
-The $k_\star$-th endpoint is the maximum in~\cref{eq:Skmax} occuring at 
-\begin{equation}
-	x_{k_\star} = \frac{1}{2}\left(1 + \left( \frac{7}{9} \right)^n \right).
-\end{equation}
-
-All $n$ elbows, depicted in the diagram of~\cref{fig:lccalc}, are given by the following sums, $\left( x_k, \lc{\ketbra{\rm{S}}^{\otimes n}}{\frac{1}{d}\id}(k) \right) =$
-\begin{equation}\label{eq:leftelb}
-	\left( \frac{1}{9^n} \sum\limits_{j=0}^{k-1} 8^{2j} \binom{n}{2j}, \frac{1}{3^n} \sum\limits_{j=0}^{k-1} 4^{2j} \binom{n}{2j} \right)
-\end{equation}
-for all elbows left of the maximum, $k = 1, \dots, k_\star = \floor{\frac{n}{2}}+1$ and $\left( x_k, \lc{\ketbra{\rm{S}}^{\otimes n}}{\frac{1}{d}\id}(k) \right) = (x_{k_\star}, L(k_\star)) + $
-\begin{equation}\label{eq:rightelb}
-	\left( \left(\frac{8}{9}\right)^n \sum\limits_{j=0}^{k' - k_\star - 1} 8^{-(2j+1)} \binom{n}{2j+1}, \left(\frac{4}{3}\right)^n \sum\limits_{j=0}^{k' - k_\star - 1} 4^{-(2j+1)} \binom{n}{2j+1} \right),
-\end{equation}
-for all elbows right of the maximum, $k' = k_\star + 1, \dots, n$.
+We plot the Lorenz curves of pure and noisy Strange state $n$-copy states for $n$ up to $4$ in~\cref{fig:lcs}.
+For $n=1$, the Lorenz curve is simply additive, 
+\begin{equation}
+\lc{(1-\epsilon)\rho + \epsilon\sigma}{\sigma} = (1-\epsilon)\lc{\rho}{\sigma} + \epsilon\lc{\sigma}{\sigma},
+\end{equation}
+for any $\sigma, \rho$, but for $n\geq 2$, calculations become more complicated.
 
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.5]{figs/lccalcdiagram.pdf}
-    \caption{\textbf{Anatomy of Strange state Lorenz curve}
-    There are $n$ ``elbows'' in this Lorenz curve of an $n$-copy Strange state.
-    Labels $k, k'$ indicate elbows left and right of the maximum respectively.
-    Their coordinates are given in~\cref{eq:leftelb,eq:rightelb}.
-    }
-    \label{fig:lccalc}
-\end{figure}
-
-We plot the Lorenz curves of pure and noisy Strange state $n$-copy states for $n$ up to $4$ in~\cref{fig:lcs}.
-For $n=1$, the Lorenz curve is simply additive, 
-\begin{equation}
-\lc{(1-\epsilon)\rho + \epsilon\sigma}{\sigma} = (1-\epsilon)\lc{\rho}{\sigma} + \epsilon\lc{\sigma}{\sigma},
-\end{equation}
-for any $\sigma, \rho$, but for $n\geq 2$, calculations become more complicated.
-
 In~\cref{fig:unital_distill}, we examine the purifying process of~\cref{eq:sdist} with $\epsilon_\tau = 0.05$ which describes all circuits that respect the unital symmetry.
@@
 \end{figure}
+
+\newpage
+
+\subsection{Lorenz curves calculations}
+
+Lorenz curve analysis simplifies significantly in the unital fragment \nick{or so I thought initially}, because the invariant Wigner distribution is the uniform distribution depicted in~\cref{fig:maxmix}.
+Therefore, $\W[\bmu]{(\frac{1}{d}\id)^{\otimes n}} = \frac{1}{d^{2n}}$ for all $\bmu \in \pd[d^n]$ and the ordering of the points on the Lorenz curve only depends on the ordering of the Wigner components of $\rho$.
+The Lorenz curve $\lc{\ketbra{\rm{S}}^{\otimes n}}{\frac{1}{d}\id}$ consists of $n+1$ line segments, with $n$ endpoints, or ``elbows'', between $(0,0)$ and $(1,1)$. 
+The $k_\star$-th endpoint is the maximum in~\cref{eq:Skmax} occuring at 
+\begin{equation}
+	x_{k_\star} = \frac{1}{2}\left(1 + \left( \frac{7}{9} \right)^n \right).
+\end{equation}
+
+We now investigate the location of all $n$ elbows, depicted in the diagram of~\cref{fig:lccalc}.
+
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.5]{figs/lccalcdiagram.pdf}
+    \caption{\textbf{Anatomy of Strange state Lorenz curve}
+    There are $n$ ``elbows'' in this Lorenz curve of an $n$-copy Strange state.
+    Labels $k, k'$ indicate elbows left and right of the maximum respectively.
+    Their coordinates are given in~\cref{eq:leftelb,eq:rightelb}.
+    }
+    \label{fig:lccalc}
+\end{figure}
+
+Let $\bar n = 2\floor{\frac{n}{2}}$ be equal to $n$ if $n$ is even and $n-1$ if $n$ is odd.
+Then, the positive components of the $n$-copy Strange state Wigner distribution $\W{\ketbra{\rm{S}}}$ are, in decreasing order, $6^{-n} 2^{\bar n} 2^{-j},\ j=0, 2, \dots, \bar n$ with respective multiplicites $8^{n-\bar n} 8^j \binom{n}{\bar n - j}$.
+The negative components are, in decreasing order $-6^{-n} 2^j,\ j=1,3, \dots, n$ with respective multiplicities $8^n 8^{-j} \binom{n}{j}$.
+
+Denote by $\Phi(m; n, p)$ the cumulative binomial distribution,
+\begin{equation}
+	\Phi(m; n, p) \coloneqq \sum\limits_{j=0}^m \binom{n}{j} p^j (1-p)^{n-j}.
+\end{equation}
+Let $\Phi_+(m; n, p)$ denote the same sum but only considering the even indices, $j = 0, 2, \dots, m$ and similarly let $\Phi_-(m; n, p)$ denote the same sum but only considering the odd indices, $j = 1, 3, \dots, m$.
+
+Assume $n$ is even, so that $\bar n = n$.
+Then we can express any elbow on the $n$-copy Strange state Lorenz curve as
+\begin{align}
+	L_+(m; n) &= \left(\frac{5}{3}\right)^n \Phi_+\left(m;n,\frac{4}{5}\right) \label{eq:leftelb}\\
+	L_-(m; n) &= L_\star - \left(\frac{5}{3}\right)^n \Phi_-\left(m;n,\frac{1}{5}\right), \label{eq:rightelb}
+\end{align}
+where $L_\star = L_+(n; n)$ is the maximum of the curve and $L_+, L_-$ indicate points on the left, right of the curve respectively for some index $m$.
+
+The locations of the elbows are at
+\begin{align}
+	x_+(m; n) &= \Phi_+\left(m;n,\frac{8}{9}\right) \\
+	x_-(m; n) &= x_\star + \Phi_-\left(m;n,\frac{1}{9}\right),
+\end{align}
+where $x_\star = x_+(n; n)$ is the location of the maximum.
+
+\newpage
 

### 2020-07-15 magic_paper.tex
Comment on bounds

@@
 Let $\Phi_+(m; n, p)$ denote the same sum but only considering the even indices, $j = 0, 2, \dots, m$ and similarly let $\Phi_-(m; n, p)$ denote the same sum but only considering the odd indices, $j = 1, 3, \dots, m$.
+Then,
+\begin{align}	
+	\Phi_+ + \Phi_- &= \Phi \\
+	\Phi_+ - \Phi_- &= \Phi^c \coloneqq \sum\limits_{j=0}^m \binom{n}{j} (-p)^j (1-p)^{n-j}.
+\end{align}
+
+\nick{$\Phi$ is bounded by the two exponentials in Wikipedia ONLY for $m\leq np$ so these bounds do not hold for $m>np$.
+
+$\Phi^c$ is NOT bounded above by setting $m=n$ (which yields $(1 - 2p)^n$) and NOT bounded below by 0 - both due to the existence of negative terms in the sum.
+It does appear however to be strictly within the open interval $(-1, 1)$.}
 
@@
 \begin{align}
-	L_+(m; n) &= \left(\frac{5}{3}\right)^n \Phi_+\left(m;n,\frac{4}{5}\right) \label{eq:leftelb}\\
+	L_+(m; n) &= \left(\frac{5}{3}\right)^n \Phi_+\left(m;n,\frac{4}{5}\right), \label{eq:leftelb}\\
 	L_-(m; n) &= L_\star - \left(\frac{5}{3}\right)^n \Phi_-\left(m;n,\frac{1}{5}\right), \label{eq:rightelb}
@@
 \begin{align}
-	x_+(m; n) &= \Phi_+\left(m;n,\frac{8}{9}\right) \\
+	x_+(m; n) &= \Phi_+\left(m;n,\frac{8}{9}\right), \\
 	x_-(m; n) &= x_\star + \Phi_-\left(m;n,\frac{1}{9}\right),

### 2020-07-16 magic_paper.tex
connected kth elbow to function

@@
 
-Let $\bar n = 2\floor{\frac{n}{2}}$ be equal to $n$ if $n$ is even and $n-1$ if $n$ is odd.
+Let $\overline{n} = 2\floor{\frac{n}{2}}$ be equal to $n$ if $n$ is even and $n-1$ if $n$ is odd.
 Then, the positive components of the $n$-copy Strange state Wigner distribution $\W{\ketbra{\rm{S}}}$ are, in decreasing order, $6^{-n} 2^{\bar n} 2^{-j},\ j=0, 2, \dots, \bar n$ with respective multiplicites $8^{n-\bar n} 8^j \binom{n}{\bar n - j}$.
@@
 Denote by $\Phi(m; n, p)$ the cumulative binomial distribution,
-\begin{equation}
-	\Phi(m; n, p) \coloneqq \sum\limits_{j=0}^m \binom{n}{j} p^j (1-p)^{n-j}.
-\end{equation}
-Let $\Phi_+(m; n, p)$ denote the same sum but only considering the even indices, $j = 0, 2, \dots, m$ and similarly let $\Phi_-(m; n, p)$ denote the same sum but only considering the odd indices, $j = 1, 3, \dots, m$.
-Then,
-\begin{align}	
-	\Phi_+ + \Phi_- &= \Phi \\
-	\Phi_+ - \Phi_- &= \Phi^c \coloneqq \sum\limits_{j=0}^m \binom{n}{j} (-p)^j (1-p)^{n-j}.
+\begin{align}
+	\Phi(m; n, p) &\coloneqq \sum\limits_{j=0}^m \binom{n}{j} p^j (1-p)^{n-j}, \\
+	\Phi^c(m; n, p) &\coloneqq \sum\limits_{j=0}^m \binom{n}{j} (-p)^j (1-p)^{n-j}.
+\end{align}
+Note that $\Phi(m; n, p)^c$ differs only by a factor of $(-1)^j$.
+Let $\Phi_+(m; n, p)$ and $\Phi_-(m; n, p)$ denote the partial sums of even and odd indices respectively,
+\begin{align}	
+	\Phi_+(m; n, p) &= \frac{1}{2} \left( \Phi(m; n, p) + \Phi^c(m; n, p) \right), \\
+	\Phi_-(m; n, p) &= \frac{1}{2} \left( \Phi(m; n, p) - \Phi^c(m; n, p) \right).
 \end{align}
@@
 \end{align}
-where $L_\star = L_+(n; n)$ is the maximum of the curve and $L_+, L_-$ indicate points on the left, right of the curve respectively for some index $m$.
+where $L_\star = L_+(n; n)$ is the maximum of the curve and $L_+, L_-$ respectively indicate the elbows on the left, right of the maximum for some index $m$.
 
@@
 where $x_\star = x_+(n; n)$ is the location of the maximum.
+
+Clearly by definition, 
+\begin{align}
+	\Phi_+(2m+1;n,p) &= \Phi_+(2m;n,p), \\
+	\Phi_-(2m;n,p) &= \Phi_-(2m-1;n,p),
+\end{align}
+so we define the piece-wise functions
+\begin{equation}
+	L(m;n) =
+	\begin{cases}
+	L_+(m; n)&,\ m\text{: even}, \\
+	L_-(m; n)&,\ m\text{: odd}
+	\end{cases}
+\end{equation}
+and
+\begin{equation}
+	x(m;n) =
+	\begin{cases}
+	x_+(m; n)&,\ m\text{: even}, \\
+	x_-(m; n)&,\ m\text{: odd}
+	\end{cases}
+\end{equation}
+Finally, the $k$-th elbow is located at
+\begin{equation}
+	\left(x_k, \lc{\ketbra{\rm{S}}^{\otimes n}}{\frac{1}{d}\id}(k) \right) = \left( x(2k;n), L(2k;n) \right),
+\end{equation}
+where $2k$ is considered$\mod{(n+1)}$.
 

### 2020-07-17 magic_paper.tex
Added two figures that illustrate the phi distributions

@@
 
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.5]{figs/Phi.pdf}
+    \caption{Distributions $\Phi(m;n,p)$ (blue) and $\Phi^c(m;n,p)$ (orange) for $n=20$ and $p=\frac{4}{5}$.
+    The green curve is the upper bound on $\Phi$, valid for all $m \leq np = 8$.
+    }
+    \label{fig:Phi}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.5]{figs/Phi_ratio.pdf}
+    \caption{Distributions $\Phi_+(m;n,p)$ (blue) and $\Phi_-(m;n,p)$ (orange) for $n=20$ and $p=\frac{4}{5}$.
+    The green curve is the ratio of the two
+    }
+    \label{fig:Phi_ratio}
+\end{figure}
+
 \newpage

### 2020-07-20 magic_paper.tex
Added analysis

@@
 Note that $\Phi(m; n, p)^c$ differs only by a factor of $(-1)^j$.
+It is clear that for any $n,p$ and $m \leq n$
+\begin{align}
+	&\Phi(m; n, p) + \Phi(n-m; n, 1-p) = 1, \label{eq:reversef}\\
+	&\Phi^c(m; n, p) \leq \Phi(m; n, p),
+\end{align}
+where equality in the second line holds iff $m=0$.
+
 Let $\Phi_+(m; n, p)$ and $\Phi_-(m; n, p)$ denote the partial sums of even and odd indices respectively,
@@
 
-\nick{$\Phi$ is bounded by the two exponentials in Wikipedia ONLY for $m\leq np$ so these bounds do not hold for $m>np$.
-
-$\Phi^c$ is NOT bounded above by setting $m=n$ (which yields $(1 - 2p)^n$) and NOT bounded below by 0 - both due to the existence of negative terms in the sum.
-It does appear however to be strictly within the open interval $(-1, 1)$.}
-
 Assume $n$ is even, so that $\bar n = n$.
@@
 	\begin{cases}
-	L_+(m; n)&,\ m\text{: even}, \\
-	L_-(m; n)&,\ m\text{: odd}
+	L_+(m; n),&\ m\text{: even}, \\
+	L_-(m; n),&\ m\text{: odd}
 	\end{cases}
@@
 	\begin{cases}
-	x_+(m; n)&,\ m\text{: even}, \\
-	x_-(m; n)&,\ m\text{: odd}
+	x_+(m; n),&\ m\text{: even}, \\
+	x_-(m; n),&\ m\text{: odd}
 	\end{cases}
 \end{equation}
-Finally, the $k$-th elbow is located at
-\begin{equation}
-	\left(x_k, \lc{\ketbra{\rm{S}}^{\otimes n}}{\frac{1}{d}\id}(k) \right) = \left( x(2k;n), L(2k;n) \right),
-\end{equation}
-where $2k$ is considered$\mod{(n+1)}$.
+Finally, the $m$-th elbow is located at
+\begin{equation}
+	\left(x_m, \lc{\ketbra{\rm{S}}^{\otimes n}}{\frac{1}{d}\id}(m) \right) = \left( x(2m;n), L(2m;n) \right),
+\end{equation}
+where $2m$ is considered \hspace{-7pt}$\mod{(n+1)}$.
+
+We now want to bound these points for any index $m$, so as to investigate the asymptotic behaviour of the Lorenz curve.
+We define the upper bound
+\begin{equation}
+	U(m;n,p) \coloneqq 
+	\begin{cases}
+	e^{-nS\left(\frac{m}{n}||p \right)} \label{eq:ubd},&\ m \leq np, \\
+	1,&\ m>np.
+	\end{cases}
+\end{equation}
+\nick{we need to replace 1 with an exponential decay}
+where 
+\begin{equation}
+	S(\alpha||\beta) \coloneqq \alpha \log{\frac{\alpha}{\beta}} + (1-\alpha) \log{\frac{1-\alpha}{1-\beta}},
+\end{equation}
+is the classical relative entropy.
+
+There are two useful lower bounds for $\Phi(m;n,p)$, which we define as
+\begin{equation}
+	L(m;n,p) \coloneqq \max{\left\{ c(m;n) U(m;n,p), \\ 1 - U(n-m;n,1-p) \right\}} \label{eq:lbd},
+\end{equation}
+where
+\begin{equation}
+	c(m;n) = \left[8m\left(1-\frac{m}{n}\right)\right]^{-1/2}.
+\end{equation}
+Generally, the first expression within the $\max$ function is useful iff $m \leq np$, while the second expression is due to~\cref{eq:reversef} and thususeful iff $m \geq np$.
+So we choose $L(m;n,p$ to be the maximum of the two at any $m$.
+Figure~\cref{fig:Phi} demonstrates the upper and lower bounds for $\Phi(m;n,\frac{4}{5}$.
 
@@
     \includegraphics[scale=0.5]{figs/Phi.pdf}
-    \caption{Distributions $\Phi(m;n,p)$ (blue) and $\Phi^c(m;n,p)$ (orange) for $n=20$ and $p=\frac{4}{5}$.
-    The green curve is the upper bound on $\Phi$, valid for all $m \leq np = 8$.
+    \caption{Distributions $\Phi(m;n,p)$ (blue) and $\Phi^c(m;n,p)$ (orange) for $n=30$ and $p=\frac{4}{5}$.
+    The upper and lower bounds on $\Phi$ are also presented. 
+    The upper bound is given by~\cref{eq:ubd} and the lower bound by~\cref{eq:lbd}.
     }
     \label{fig:Phi}
+\end{figure}
+
+We see in~\cref{fig:phicmax} that distribution $\Phi^c(m;n,p)$ is also bounded by a constant number $\epsilon$, $0<\epsilon<1$ for all $m$.
+The bound $\epsilon$ tends to decrease as $n$ increases, so that $\abs{\Phi^c(m;n,p)} \leq \frac{1}{10}$ for $n\geq 30$.
+
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.5]{figs/Phic_max.pdf}
+    \caption{Maximum of the absolute value of $\Phi^c(m;n,p)$ over all $m$ for given $n$.
+    Here, we plot for all even $n$, $2\leq n\leq 30$.
+    The maximum is decreasing in $n$ and falls below $\frac{1}{10}$ for $n=30$.
+    \nick{we want to extract exponential bound from this graph instead of constant bound}.
+    }
+    \label{fig:phicmax}
 \end{figure}
@@
     \label{fig:Phi_ratio}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.5]{figs/Phi_nexp.pdf}
+    \caption{Distributions $\Phi_+(m;n,p)/ U(m;n,p)$ (blue) and $U(m;n,p) \Phi_-(m;n,p)$ (orange) for $n=30$ and $p=\frac{4}{5}$.
+    We multiply the bound in~\cref{eq:ubd} to extract the exponential behaviour of the two distributions.
+    Here, $np = 24$, so for $m\geq 24$, $U(m;n,p) = 1$.
+    }
+    \label{fig:phinexp}
 \end{figure}

### 2020-07-21 magic_paper.tex
bounds on Phi

@@
 \begin{align}
-	\Phi(m; n, p) &\coloneqq \sum\limits_{j=0}^m \binom{n}{j} p^j (1-p)^{n-j}, \\
-	\Phi^c(m; n, p) &\coloneqq \sum\limits_{j=0}^m \binom{n}{j} (-p)^j (1-p)^{n-j}.
+	\Phi(m; n, p) &\coloneqq \sum\limits_{j=0}^m \binom{n}{j} p^j (1-p)^{n-j}, \label{eq:phi}\\
+	\Phi^c(m; n, p) &\coloneqq \sum\limits_{j=0}^m \binom{n}{j} (-p)^j (1-p)^{n-j}. \label{eq:phic}
 \end{align}
@@
 
-We now want to bound these points for any index $m$, so as to investigate the asymptotic behaviour of the Lorenz curve.
-We define the upper bound
-\begin{equation}
-	U(m;n,p) \coloneqq 
+We now want to bound these points for any index $m$, so as to investigate the asymptotic behaviour of the Lorenz curves.
+We first define a useful function
+\begin{equation}
+	c(m;n) = 
 	\begin{cases}
-	e^{-nS\left(\frac{m}{n}||p \right)} \label{eq:ubd},&\ m \leq np, \\
-	1,&\ m>np.
+		0,&\ m=0, \\
+		\left[8m\left(1-\frac{m}{n}\right)\right]^{-1/2},&\ 0<m<n, \\
+		1,&\ m=n,
 	\end{cases}
 \end{equation}
-\nick{we need to replace 1 with an exponential decay}
+as well as the classical relative entropy,
+\begin{equation}
+	S(\alpha||\beta) \coloneqq \alpha \log{\frac{\alpha}{\beta}} + (1-\alpha) \log{\frac{1-\alpha}{1-\beta}}.
+\end{equation}
+
+We now define two functions that we use to bound $\Phi(m;n,p)$,
+\begin{align}
+	U(m;n,p) &\coloneqq	e^{-nS\left(\frac{m}{n}||p \right)} \label{eq:ubd}, \\
+	L(m;n,p) &\coloneqq c(m;n)e^{-nS\left(\frac{m}{n}||p \right)} \label{eq:lbd}.
+\end{align}
+
+\begin{lemma}\label{lem:ulbd}
+	The cumulative distribution $\Phi(m;n,p)$ defined in~\cref{eq:phic} is exponentially bounded for all $m: 0\leq m \leq n$,
+	\begin{equation}
+		B_L(m;n,p) \leq \Phi(m;n,p) \leq B_U(m;n,p),\ m\leq np
+	\end{equation}
 	where
 	\begin{equation}
-	S(\alpha||\beta) \coloneqq \alpha \log{\frac{\alpha}{\beta}} + (1-\alpha) \log{\frac{1-\alpha}{1-\beta}},
-\end{equation}
-is the classical relative entropy.
-
-There are two useful lower bounds for $\Phi(m;n,p)$, which we define as
-\begin{equation}
-	L(m;n,p) \coloneqq \max{\left\{ c(m;n) U(m;n,p), \\ 1 - U(n-m;n,1-p) \right\}} \label{eq:lbd},
-\end{equation}
-where
-\begin{equation}
-	c(m;n) = \left[8m\left(1-\frac{m}{n}\right)\right]^{-1/2}.
-\end{equation}
-Generally, the first expression within the $\max$ function is useful iff $m \leq np$, while the second expression is due to~\cref{eq:reversef} and thususeful iff $m \geq np$.
-So we choose $L(m;n,p$ to be the maximum of the two at any $m$.
-Figure~\cref{fig:Phi} demonstrates the upper and lower bounds for $\Phi(m;n,\frac{4}{5}$.
-
-\begin{figure}
+		B_L(m;n,p) = \\
+		\begin{cases}
+			L(m;n,p),&\ m \leq np, \\
+			1 - U(n-m;n,1-p),&\ m > np,
+		\end{cases}
+	\end{equation}
+	and
+	\begin{equation}
+		B_U(m;n,p) =
+		\begin{cases}
+			U(m;n,p),&\ m \leq np, \\
+			1 - L(n-m;n,1-p),&\ m > np.
+		\end{cases}
+	\end{equation}
+\end{lemma}
+
+The bounds are demonstrated in~\cref{fig:phi} for the interesting cases of $\Phi\left(m;n,\frac{1}{5}\right),\Phi\left(m;n,\frac{4}{5}\right)$.
+
+\begin{figure}%
     \centering
-    \includegraphics[scale=0.5]{figs/Phi.pdf}
-    \caption{Distributions $\Phi(m;n,p)$ (blue) and $\Phi^c(m;n,p)$ (orange) for $n=30$ and $p=\frac{4}{5}$.
-    The upper and lower bounds on $\Phi$ are also presented. 
-    The upper bound is given by~\cref{eq:ubd} and the lower bound by~\cref{eq:lbd}.
-    }
-    \label{fig:Phi}
+    \subfigure[][]{%
+    \label{fig:phi1}%
+    \includegraphics[height=5cm]{figs/Phi.pdf}
+    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
+    }\\%
+    \subfigure[][]{%
+    \label{fig:phi4}%
+    \includegraphics[height=5cm]{figs/Phi2.pdf}
+    %\caption{Zero state $\ketbra{0}{0}$}%
+    }
+    \caption{Distributions $\Phi(m;n,p)$ (black) and $\Phi^c(m;n,p)$ (red) for $n=30$ and probability: 
+    \subref{fig:phi1} $p=\frac{4}{5}$; \subref{fig:phi4} $p=\frac{1}{5}$.
+    The upper and lower bounds on $\Phi(m;n,p)$ as stated in~\cref{lem:ulbd} are also presented. 
+    }%
+    \label{fig:phi}
 \end{figure}
@@
     \includegraphics[scale=0.5]{figs/Phi_nexp.pdf}
-    \caption{Distributions $\Phi_+(m;n,p)/ U(m;n,p)$ (blue) and $U(m;n,p) \Phi_-(m;n,p)$ (orange) for $n=30$ and $p=\frac{4}{5}$.
-    We multiply the bound in~\cref{eq:ubd} to extract the exponential behaviour of the two distributions.
+    \caption{Distributions $\Phi_+(m;n,p)/U(m;n,p)$ (blue) and $\Phi_-(m;n,p)/U(m;n,p)$ (orange) for $n=30$ and $p=\frac{4}{5}$.
+    We divide by the bound in~\cref{eq:ubd} to extract the exponential behaviour of the two distributions.
     Here, $np = 24$, so for $m\geq 24$, $U(m;n,p) = 1$.

### 2020-07-21 magic_paper.tex
Started noisy subsection

@@
 
+\subsubsection{Lorenz curve ordering and maximum}
+
 Lorenz curve analysis simplifies significantly in the unital fragment \nick{or so I thought initially}, because the invariant Wigner distribution is the uniform distribution depicted in~\cref{fig:maxmix}.
@@
 
+\subsubsection{Lorenz curve in terms of a binomial cumulative distribution}
+
 Denote by $\Phi(m; n, p)$ the cumulative binomial distribution,
@@
 Finally, the $m$-th elbow is located at
-\begin{equation}
+\begin{equation}\label{eq:slc}
 	\left(x_m, \lc{\ketbra{\rm{S}}^{\otimes n}}{\frac{1}{d}\id}(m) \right) = \left( x(2m;n), L(2m;n) \right),
@@
 where $2m$ is considered \hspace{-7pt}$\mod{(n+1)}$.
+
+\subsubsection{Bounds on cumulative distribution}
 
@@
 \end{figure}
+
+\subsubsection{Noisy Strange states}
+
+Strange states of the form 
+\begin{equation}
+    \rho_{\rm{S}}(\epsilon) = (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \frac{1}{d}\id,
+\end{equation}
+contain two discrete Wigner components, so $n$-copy states $\rho_{\rm{S}}^{\otimes n}(\epsilon)$ contain $n+1$ discrete components~\cref{tab:swc} as in the noiseless case.
+\begin{table}[h]                           
+ \centering
+ \begin{tabular}{|c|c|}
+ \hline
+ $m_j$ & $8^{n-j}\binom{n}{j}$ \\ [0.5ex] 
+ \hline\hline
+ $w_j$ & $\left(\frac{1}{6} - \frac{1}{18}\epsilon \right)^{n-j}\left(-\frac{1}{3} + \frac{4}{9}\epsilon \right)^{j}$ \\
+ \hline
+\end{tabular}
+ \caption{Wigner components of $\rho_{\rm{S}}^{\otimes n}(\epsilon)$}
+ \label{tab:swc}
+\end{table}
+
+Clearly, there are negative Wigner components iff $0\leq \epsilon < \frac{3}{4}$.
+At the limiting case of non-negative Wigner components $\epsilon = \frac{3}{4}$, the Lorenz curve is simply given by three points,
+\begin{equation}
+\left\{(0,0), \left(\left(\frac{8}{9}\right)^n, 1\right), (1,1) \right\}
+\end{equation}
+and exponentially tends to a step-function.
+The case of $\epsilon = 0$ is given at~\cref{eq:slc} and the noisy cases with $0 < \epsilon < \frac{3}{4}$ follow a similar analysis.
 

### 2020-09-28 magic_paper.tex
Basic bounds on phi plus, phi minus

@@
 \author{Nikolaos Koukoulekidis}
+	\email{nk2314@imperial.ac.uk}
 	\affiliation{Department of Physics, Imperial College London, London SW7 2AZ, UK}
-	\email{nk2314@imperial.ac.uk}
 \author{David Jennings}
@@
     \caption{\textbf{Decomposition of a magic theory $\R$ intro $\sigma$--fragments.} 
-    Examples of magic theories ($\so$: Stabilizer operations, $\Omax$: Completely positive-Wigner-preserving operations, $\rcu$: Random Clifford Unitaries -- subclass of $\so$) involve operations within the yellow regions, with all other established magic theories between these two.
-    We introduce $\sigma$--fragments $\O_\sigma$ defined for all free states $\sigma$ that cover $\Omax$ with each one extendible to a set of stochastic maps outside the $\cptp$ operations.
-    Within each $\sigma$--fragment $\bmd$-majorization can be used allowing for an \nick{in-depth approach} towards the study of magic state interconversion.
+	Examples of magic theories ($\so$: Stabilizer operations, $\Omax$: Completely positive-Wigner-preserving operations, $\rcu$: Random Clifford Unitaries -- subclass of $\so$) involve operations denoted by the two yellow regions, with every other established magic theory  between them.
+    We introduce $\sigma$--fragments $\O_\sigma$ defined for all free states $\sigma$ that cover $\Omax$. 
+    Each $\O_\sigma$ is extensible to a set of stochastic maps outside the $\cptp$ operations.
+    Within each $\sigma$--fragment $\bmd$-majorization can be used allowing for an intricate, but tractable approach towards the study of magic state interconversion.
     }
@@
 \begin{theorem}\label{thm:sigmamajor}
-    Let $\R = (\F, \O)$ be a theory of magic. Then $\rho \longrightarrow \tau$ is possible then  $\W{\tau} \prec_\sigma \W{\rho}$ within a $\sigma$--fragment.
+    Let $\R = (\F, \O)$ be a theory of magic. Then $\rho \longrightarrow \tau$ is possible iff  $\W{\tau} \prec_\sigma \W{\rho}$ within a $\sigma$--fragment.
     \nick{I understand that dropping the full-rank assumption on $\sigma$ makes the statement a lot stronger, but also incorrect e.g.
@@
 
+\subsection{Strange state Lorenz curves in the unital fragment}
+
+In this section we analytically investigate the behaviour of the Lorenz curve of an $n$-copy Strange state in the unital fragment, 
+\begin{equation}\label{eq:lcsu}
+	\lc{\rho_{\rm{S}}(\epsilon)^{\otimes n}} {\frac{1}{d}\id}(x).
+\end{equation}
+An analytic handle on this type of Lorenz curves, which we call ``standard'' Lorenz curves, elevates Strange states to ``standard candles'' in the context of magic state distillation \nick{expand}.
+We first present some relevant theory on error bounds of general binary codes and then show how it can be used to approximate the Lorenz curves of~\cref{eq:lcsu}.
+
+\subsubsection{Binomial distributions and error bounds}
+In this section, for any non-negative reals $a,b$ with $b\geq a$, we will denote the set of integers $n$ such that $a\leq n \leq b$ as $[a,b]$ for convenience.
+
+Consider an experiment consisting of $n$ trials of throwing a $p$-coin, that is a coin with probability $p$ of landing on one side and $1-p$ of landing on the other.
+That could be a string of $n$ bits with bit-flip error probability $p$.
+
+The experiment is described by binomial statistics and we define the ``left'' and ``right'' tails of the cumulative binomial distribution,
+\begin{align}
+	\Phi_\ell(m; n, p) &\coloneqq \sum\limits_{j=0}^m \binom{n}{j} p^j (1-p)^{n-j}, \label{eq:phi}\\
+	\Phi_r(m; n, p) &\coloneqq \sum\limits_{j=m}^n \binom{n}{j} p^j (1-p)^{n-j}, \label{eq:phir}
+\end{align}
+where $m\in [0,n]$.
+
+They are related by the symmetry between the left tail of a $p$-coin distribution and the right tail of a $(1-p)$-coin distribution,
+\begin{equation}\label{eq:phil2phir}
+	\Phi_\ell(m; n, p) = \Phi_r(n-m; n, 1-p),\ m\in [0,n],
+\end{equation}
+as well as the normalisation condition,
+\begin{equation}
+	\Phi_\ell(m; n, p) + \Phi_r(m+1; n, p) = 1,\ m\in [0,n-1].
+\end{equation}
+
+Equivalently, we get
+\begin{align}
+	\Phi_\ell(m; n, p) + \Phi_\ell(n-m-1; n, 1-p) &= 1,\ m\in [0,n-1], \label{eq:reversephi}\\
+	\Phi_r(m; n, p) + \Phi_r(n-m+1; n, 1-p) &= 1,\ m\in [1,n]. \label{eq:reversephir}
+\end{align}
+
+The classical entropy of a $p$-coin is
+\begin{equation}\label{eq:ent}
+	S(p) \coloneqq -p\log{p} -(1-p)\log{(1-p)},
+\end{equation}
+which is symmetric, $S(p) = S(1-p)$.
+%Let $c(m; n) \coloneqq [m(1-m/n)]^{-1/2},\ m\in [1, n-1]$.
+A useful result is the entropic bound on a combination~\cite{cit:ash}.
+\begin{lemma}\label{lem:comb_bounds}
+	For all $m\in [1,n-1]$,
+	\begin{align}
+		&\left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{nS\left(\frac{m}{n}\right)} \leq \binom{n}{m} \leq \\
+		&\left[ 2\pi m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{nS\left(\frac{m}{n}\right)}.
+	\end{align}
+\end{lemma}
+\begin{proof}
+	For $m = 1,2, n-1, n-2$ check by direct calculation.	
+	For all other cases, use Stirling's approximation.
+\end{proof}
+
+Bounds on the tails of a cumulative binomial distribution can be expressed in terms of the classical relative entropy between a $p$-coin and a $q$-coin,
+\begin{equation}\label{eq:ent_rel}
+	\ent{p}{q} \coloneqq p \log{\frac{p}{q}} + (1-p) \log{\frac{1-p}{1-q}}.
+\end{equation}
+This entropy satisfies the identity
+\begin{equation}
+	\ent{p}{q} = \ent{1-p}{1-q}.
+\end{equation}
+We can now derive entropic bounds on binomial cumulative distributions~\cite{cit:ash}.
+\begin{lemma}\label{lem:phir_bounds}
+	Given fixed $n>0$ and $p$, $\Phi_r$ satisfies the following bounds:
+	\begin{align*}
+		\begin{split}
+		&\text{1. } \Phi_r(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ents},\ m\in [1,n-1] \\
+		&\text{2. } \Phi_r(m; n, p) \leq 2^{-n\ents},\ m\in [np,n] \\
+		&\text{3. } \Phi_r(m; n, p) \leq 1 - \left[ 8(m-1)\left(1-\frac{m-1}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m-1}{n}}{p}}, \\
+		&\hspace{14pt} m\in [2,n]
+		\end{split}
+		\\
+		&\text{4. } \Phi_r(m; n, p) \geq 1 - 2^{-n\ent{\frac{m-1}{n}}{p}},\ m\in [2,np+1]
+	\end{align*}
+
+	The asymptotic behaviour of $\Phi_r$ is determined by the relative entropy, 
+	\begin{equation}
+		\lim_{n\rightarrow\infty}{-\frac{1}{n}\log{\Phi_r(m; n, p)} = \ent{\frac{m}{n}}{p}},\ m\in [np,n]
+	\end{equation}
+\end{lemma}
+\begin{proof}
+	For bound (1), note that
+	\begin{align*}
+		\Phi_r(m; n, p) &= \sum\limits_{j=m}^n \binom{n}{j} p^j (1-p)^{n-j} \\
+						   &\geq \binom{n}{m} p^{m} (1-p)^{n-m} \\
+						   &\geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{nS\left(\frac{m}{n}\right)} p^{m} (1-p)^{n-m} \\
+						   &= \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ents}.
+	\end{align*}
+	The first inequality follows from the positivity of the terms in the series, the second from~\cref{lem:comb_bounds} and the equality from the entropy definitions in~\cref{eq:ent,eq:ent_rel}
+
+	For bound (2), consider a binomial random variable $X = \sum_{i=1}^N$, where $X_i$ takes the values 1, 0 with probabilities $p$ and $1-p$ respectively.
+	Then we have
+	\begin{align*}
+		\Phi_r(m; n, p) &= P(X \geq m) = P\left(2^{rX} \geq 2^{rm}\right) \\
+						   &\leq 2^{-rm} E\left(2^{rX}\right) = 2^{-rm + n\log{(1-p+pe^r)}} \\
+						   &\leq 2^{-n\ents}.
+	\end{align*}
+	The first inequality holds for any discrete random variable $X$ with $r \geq 0$, while the second inequality involves maximisation of the exponent which occurs at $e^r = \frac{m(1-p)}{(n-m)p}$ (a non-negative $r$ exists if $np \leq m$).
+
+	Bound 3 follows from bound 1 and~\cref{eq:reversephir}. Bound 4 follows from bound x2 and~\cref{eq:reversephir}.
+
+	The asymptotic limit is a direct consequence of the squeeze theorem.
+\end{proof}
+
+\begin{lemma}\label{lem:phil_bounds}
+	Given fixed $n>0$ and $p$, $\Phi_\ell$ satisfies the following bounds:
+	\begin{align*}
+		\begin{split}
+		&\text{1. } \Phi_\ell(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ents},\ m\in [1,n-1] \\
+		&\text{2. } \Phi_\ell(m; n, p) \leq 2^{-n\ents},\ m\in [0,np] \\
+		&\text{3. } \Phi_\ell(m; n, p) \leq 1 - \left[ 8(m+1)\left(1-\frac{m+1}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m+1}{n}}{p}}, \\
+		&\hspace{14pt} m\in [0,n-2]
+		\end{split}
+		\\
+		&\text{4. } \Phi_\ell(m; n, p) \geq 1 - 2^{-n\ent{\frac{m+1}{n}}{p}},\ m\in [np+1,n-2]
+	\end{align*}
+
+	The asymptotic behaviour of $\Phi_\ell$ is determined by the relative entropy,
+	\begin{equation}
+		\lim_{n\rightarrow\infty}{-\frac{1}{n}\log{\Phi_r(m; n, p)} = \ent{\frac{m}{n}}{p}},\ m\in [0,np]
+	\end{equation}
+\end{lemma}
+\begin{proof}
+	This lemma is a direct consequence of~\cref{lem:phir_bounds} and~\cref{eq:phil2phir}.
+\end{proof}
+
+We now define the alternating counterpart of the left tail distribution,
+\begin{equation}\label{eq:phialt}
+	\Phi_\ell^{\rm{alt}}(m; n, p) \coloneqq \sum\limits_{j=0}^m \binom{n}{j} (-p)^j (1-p)^{n-j},
+\end{equation}
+where $m\in [0,n]$.
+$\Phi_\ell^{\rm{alt}}$ is \emph{not} the cumulative distribution of any random variable.
+It is upper bounded by $\Phi_\ell$,
+\begin{equation}\label{eq:alt_bound}
+	\abs{\Phi_\ell^{\rm{alt}}(m; n, p)} \leq \Phi(m; n, p),\ m\in [0,n]
+\end{equation}
+with equality iff $m=0$.
+
+We further define the two balanced combinations of $\Phi_\ell, \Phi_\ell^{\rm{alt}}$ for all $m\in [0,n]$,
+\begin{align}	
+	\Phi_+(m; n, p) &\coloneqq \frac{1}{2} \left( \Phi_\ell(m; n, p) + \Phi_\ell^{\rm{alt}}(m; n, p) \right), \\
+	\Phi_-(m; n, p) &\coloneqq \frac{1}{2} \left( \Phi_\ell(m; n, p) - \Phi_\ell^{\rm{alt}}(m; n, p) \right), \\
+	\Phi(m; n, p) &\coloneqq \label{eq:phi}
+	\begin{cases}
+		\Phi_+(m; n, p),\ \text{for even }m\in[0,n] \\
+		\Phi_-(m; n, p),\ \text{for odd }m\in[0,n].
+	\end{cases}
+\end{align}
+\begin{lemma}\label{lem:phi_bounds}
+	Given fixed $n>0$ and $p$, $\Phi$ satisfies the following bounds:
+	\begin{align*}
+		\begin{split}
+		&\text{1. } \Phi(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ents},\ m\in [1,n-1] \\
+		&\text{2. } \Phi(m; n, p) \leq 2^{-n\ents},\ m\in [0,np] \\
+		&\text{3. } \Phi(m; n, p) \leq 1 - \left[ 8(m+1)\left(1-\frac{m+1}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m+1}{n}}{p}}, \\
+		&\hspace{14pt} m\in [0,n-2]
+		\end{split}
+		\\
+		&\text{4. } \nick{!!!}
+	\end{align*}
+\end{lemma}
+\begin{proof}
+	Bound 1 follows directly from~\cref{lem:comb_bounds}.
+
+	Bounds 2,3 follow from bounds 2,3 in~\cref{lem:phil_bounds} combined with~\cref{eq:phi,eq:alt_bound}.
+\end{proof}
+
+\subsubsection{Standard Lorenz curves in terms of binomial distributions}
+The coordinates of the standard Lorenz curve can be directly expressed in terms of $\Phi_+, \Phi_-$, for all $m$, some fixed $p$ and number of copies $n$.
+
+\null\newpage
+\null\newpage
+
 \subsection{Lorenz curves calculations}

### 2020-09-29 magic_paper.tex
Plot of bounds

@@
 		\end{split}
-		\\
-		&\text{4. } \nick{!!!}
 	\end{align*}
@@
 \end{proof}
+\begin{lemma}\label{lem:phi_strictbounds}
+	Given fixed $n>0$ and $p$, $\Phi_+, \Phi_-$ satisfy the following bounds:
+	\begin{align*}
+		\begin{split}
+		&\text{1. } \Phi_+(2m; n, p) \geq \sum_{0\leq j \leq m}\left[ 8(2j)\left(1-\frac{2j}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{2j}{n}}{p}}, \\
+		&\hspace{14pt} m\in [1,\left\lceil\frac{n}{2}\right\rceil] \\
+		&\text{2. } \Phi_+(2m; n, p) \leq \sum_{0\leq j \leq m}\left[ 2\pi(2j)\left(1-\frac{2j}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{2j}{n}}{p}}, \\
+		&\hspace{14pt} m\in [1,\left\lceil\frac{n}{2}\right\rceil] \\
+		&\text{3. } \Phi_-(2m+1; n, p) \geq \sum_{0\leq j \leq m}\left[ 8(2j)\left(1-\frac{2j}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{2j}{n}}{p}}, \\
+		&\hspace{14pt} m\in [1,\left\lceil\frac{n-1}{2}\right\rceil] \\
+		&\text{4. } \Phi_-(2m+1; n, p) \leq \sum_{0\leq j \leq m}\left[ 2\pi(2j)\left(1-\frac{2j}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{2j}{n}}{p}}, \\
+		&\hspace{14pt} m\in [1,\left\lceil\frac{n-1}{2}\right\rceil] \\
+		\end{split}
+	\end{align*}
+\end{lemma}
+\begin{proof}
+	The bounds are direct consequences of~\cref{lem:comb_bounds}.
+\end{proof}
+
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.5]{figs/phi_bounds.pdf}
+    \caption{\textbf{Cumulative binomial distribution bounds}
+    Distributions $\Phi_\ell, \Phi_+$ are plotted for $n=100$ and $p=1/9$.
+    The first three bounds are given in~\cref{lem:phil_bounds,lem:phi_bounds} and are valid for both $\Phi_\ell$ and $\Phi_+$.
+    The fourth bound is given in~\cref{lem:phil_bounds} and is only valid for $\Phi_\ell$.
+    The fifth and sixth bounds are quite strict and given in~\cref{lem:phi_strictbounds} for $\Phi_+$.
+    }
+    \label{fig:lccalc}
+\end{figure}
 

### 2020-10-08 magic_paper.tex
refining

@@
 \subsubsection{Binomial distributions and error bounds}
-In this section, for any non-negative reals $a,b$ with $b\geq a$, we will denote the set of integers $n$ such that $a\leq n \leq b$ as $[a,b]$ for convenience.
+\textbf{Notational convention:} For any non-negative reals $a,b$ with $b\geq a$, we will denote the set of integers $n$ such that $a\leq n \leq b$ as $[a,b]$ for convenience.\\
 
@@
 
-The experiment is described by binomial statistics and we define the ``left'' and ``right'' tails of the cumulative binomial distribution,
+The experiment is described by binomial statistics and we define the left tail of the cumulative binomial distribution,
+\begin{equation}\label{eq:phil}
+	\Phi_\ell(m; n, p) \coloneqq \sum\limits_{j=0}^m \binom{n}{j} p^j (1-p)^{n-j},
+\end{equation}
+where $m\in [0,n]$.
+
+The symmetry between the left tail of a $p$-coin distribution and the right tail of a $(1-p)$-coin distribution dictates that
+\begin{align}\label{eq:phi_reverse}
+	\Phi_\ell(m; n, p) + \Phi_\ell(n-m-1; n, 1-p) &= 1,\ m\in [0,n-1],
+\end{align}
+
+The classical entropy of a $p$-coin is
+\begin{equation}\label{eq:ent}
+	S(p) \coloneqq -p\log{p} -(1-p)\log{(1-p)},
+\end{equation}
+which is symmetric, $S(p) = S(1-p)$.
+%Let $c(m; n) \coloneqq [m(1-m/n)]^{-1/2},\ m\in [1, n-1]$.
+A useful result is the entropic bound on a combination~\cite{cit:ash}.
+\begin{lemma}\label{lem:comb_bounds}
+	For all $m\in [1,n-1]$,
+	\begin{align}
+		&\left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{nS\left(\frac{m}{n}\right)} \leq \binom{n}{m} \leq \\
+		&\left[ 2\pi m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{nS\left(\frac{m}{n}\right)}.
+	\end{align}
+\end{lemma}
+\begin{proof}
+	For $m = 1,2, n-1, n-2$ check by direct calculation.	
+	For all other cases, use Stirling's approximation.
+\end{proof}
+
+Bounds on the tails of a cumulative binomial distribution can be expressed in terms of the classical relative entropy between a $p$-coin and a $q$-coin,
+\begin{equation}\label{eq:ent_rel}
+	\ent{p}{q} \coloneqq p \log{\frac{p}{q}} + (1-p) \log{\frac{1-p}{1-q}}.
+\end{equation}
+This entropy satisfies the identity
+\begin{equation}
+	\ent{p}{q} = \ent{1-p}{1-q}.
+\end{equation}
+
+We can now derive entropic bounds on binomial cumulative distributions~\cite{cit:ash}.
+\begin{lemma}\label{lem:phil_bounds}
+	Given fixed $n>0$ and $p$, $\Phi_\ell$ satisfies the following bounds:
+	\begin{align*}
+		\begin{split}
+		&\text{1. } \Phi_\ell(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ents},\ m\in [1,n-1] \\
+		&\text{2. } \Phi_\ell(m; n, p) \leq 2^{-n\ents},\ m\in [0,np] \\
+		&\text{3. } \Phi_\ell(m; n, p) \leq 1 - \left[ 8(m+1)\left(1-\frac{m+1}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m+1}{n}}{p}}, \\
+		&\hspace{14pt} m\in [0,n-2]
+		\end{split}
+		\\
+		&\text{4. } \Phi_\ell(m; n, p) \geq 1 - 2^{-n\ent{\frac{m+1}{n}}{p}},\ m\in [np+1,n-2]
+	\end{align*}
+\end{lemma}
+
+We now define the partial sums
+\begin{align}	
+	\Phi_+(m; n, p) &\coloneqq \sum\limits_{j=0}^{m/2} \binom{n}{2j} p^{2j} (1-p)^{n-2j}, \nonumber\\ 
+	&m\in[0,n]\ \text{and m even}, \label{eq:fp} \\
+	\Phi_-(m; n, p) &\coloneqq \sum\limits_{j=1}^{(m-1)/2} \binom{n}{2j+1} p^{2j+1} (1-p)^{n-(2j+1)}, \nonumber\\ 
+	&m\in[0,n]\ \text{and m odd}. \label{eq:fn2}
+\end{align}
+Index $m$ only takes even (odd) values when labelling $\Phi_+$ ($\Phi_-$) and therefore we can use $\Phi_{\pm}$ to compactify statements that hold for both sums.
+In particular, we derive ``loose'' and ``strict'' bounds on $\Phi_{\pm}$.
+\begin{lemma}\label{lem:bounds_loose}
+	Given fixed $n>0$ and $p$, $\Phi$ satisfies the following bounds:
+	\begin{align*}
+		\begin{split}
+		&\text{1. } \Phi_{\pm}(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ents},\ m\in [1,n-1] \\
+		&\text{2. } \Phi_{\pm}(m; n, p) \leq 2^{-n\ents},\ m\in [0,np] \\
+		&\text{3. } \Phi_{\pm}(m; n, p) \leq 1 - \left[ 8(m+1)\left(1-\frac{m+1}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m+1}{n}}{p}}, \\
+		&\hspace{14pt} m\in [0,n-2]
+		\end{split}
+	\end{align*}
+\end{lemma}
+\begin{proof}
+	!!!
+\end{proof}
+\begin{lemma}\label{lem:bounds_strict}
+	Given fixed $n>0$ and $p$, $\Phi_+, \Phi_-$ satisfy the following bounds:
+	\begin{align*}
+		\begin{split}
+		&\text{1. } \Phi_+(m; n, p) \geq \sum\limits_{j=0}^{m/2}\left[ 8(2j)\left(1-\frac{2j}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{2j}{n}}{p}}, \\
+		&\hspace{14pt} \text{for all even } m\in [2,n] \\
+		&\text{2. } \Phi_+(m; n, p) \leq \sum\limits_{j=0}^{m/2}\left[ 2\pi(2j)\left(1-\frac{2j}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{2j}{n}}{p}}, \\
+		&\hspace{14pt} \text{for all even } m\in [2,n] \\
+		&\text{3. } \Phi_-(m; n, p) \geq \sum\limits_{j=1}^{(m-1)/2}\left[ 8(2j+1)\left(1-\frac{2j+1}{n}\right) \right]^{-\frac{1}{2}} \times \\
+		&\hspace{14pt} \times 2^{-n\ent{\frac{2j+1}{n}}{p}},\ \text{for all odd } m\in [1,n] \\
+		&\text{4. } \Phi_-(m; n, p) \leq \sum\limits_{j=1}^{(m-1)/2}\left[ 2\pi(2j+1)\left(1-\frac{2j+1}{n}\right) \right]^{-\frac{1}{2}} \times \\
+		&\hspace{14pt} \times 2^{-n\ent{\frac{2j+1}{n}}{p}},\ \text{for all odd } m\in [1,n]
+		\end{split}
+	\end{align*}
+\end{lemma}
+\begin{proof}
+	!!!
+\end{proof}
+
+\null\newpage
+\null\newpage
+
+The experiment is described by binomial statistics and we define the left and ``right'' tails of the cumulative binomial distribution,
 \begin{align}
@@
 
-	Bound 3 follows from bound 1 and~\cref{eq:reversephir}. Bound 4 follows from bound x2 and~\cref{eq:reversephir}.
+	Bound 3 follows from bound 1 and~\cref{eq:reversephir}. Bound 4 follows from bound 2 and~\cref{eq:reversephir}.
 
@@
 It is upper bounded by $\Phi_\ell$,
-\begin{equation}\label{eq:alt_bound}
-	\abs{\Phi_\ell^{\rm{alt}}(m; n, p)} \leq \Phi(m; n, p),\ m\in [0,n]
+\begin{equation}\label{eq:phialt_bound}
+	\abs{\Phi_\ell^{\rm{alt}}(m; n, p)} \leq \Phi_\ell(m; n, p),\ m\in [0,n]
 \end{equation}

### 2020-10-15 magic_paper.tex
Added complete expressions for noisy n-copy Strange state Lorenz curves in Unital fragment. Added plot highlightind the difficulty in using binomial bounds on the Lorenz curves

@@
 \begin{equation}\label{eq:sdist}
-	\rho_{\rm{S}}(\epsilon)^{\otimes n} \xrightarrow{\E \in \O_\sigma} \rho_{\rm{S}}(\epsilon_{\tau})
+	\noisysn \xrightarrow{\E \in \O_\sigma} \rho_{\rm{S}}(\epsilon_{\tau})
 \end{equation}
@@
 \begin{equation}\label{eq:ethresh}
-	\epsilon_{\rm{th}}(n, \epsilon_\tau, \sigma) \coloneqq \sup{\{\epsilon:\ \lc{\rho_{\rm{S}}(\epsilon)^{\otimes n}}{\sigma} \geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})}{\sigma}\}},
+	\epsilon_{\rm{th}}(n, \epsilon_\tau, \sigma) \coloneqq \sup{\{\epsilon:\ \lc{\noisysn}{\sigma} \geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})}{\sigma}\}},
 \end{equation}
@@
 \begin{equation}\label{eq:ethresh}
-	n_{\rm{th}}(\epsilon, \epsilon_\tau, \sigma) \coloneqq \min{\{n:\ n \in \mathbb{N}, \lc{\rho_{\rm{S}}(\epsilon)^{\otimes n}}{\sigma} \geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})}{\sigma}\}}.
+	n_{\rm{th}}(\epsilon, \epsilon_\tau, \sigma) \coloneqq \min{\{n:\ n \in \mathbb{N}, \lc{\noisysn}{\sigma} \geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})}{\sigma}\}}.
 \end{equation}}
@@
     }
-    \caption{\textbf{Lorenz curves of Strange state copies.} Lorenz curves of $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ for $n=1,2,3,4$.
+    \caption{\textbf{Lorenz curves of Strange state copies.} Lorenz curves of $\noisysn$ for $n=1,2,3,4$.
     Solid lines represent pure Strange states ($\epsilon = 0$); dashed lines represent noisy Strange states ($\epsilon = 0.1$).
@@
 \begin{equation}\label{eq:lcsu}
-	\lc{\rho_{\rm{S}}(\epsilon)^{\otimes n}} {\frac{1}{d}\id}(x).
+	\lc{\noisysn}{\frac{1}{d}\id}(x).
 \end{equation}
@@
 \subsubsection{Binomial distributions and error bounds}
-\textbf{Notational convention:} For any non-negative reals $a,b$ with $b\geq a$, we will denote the set of integers $n$ such that $a\leq n \leq b$ as $[a,b]$ for convenience.\\
+\textbf{Notational convention:} For any non-negative reals $a,b$ with $b\geq a$, we will denote the set of integers $n$ such that $a\leq n \leq b$ as $[a,b]$.\\
 
@@
 \end{lemma}
+\begin{proof}
+	\nick{cite proof}
+\end{proof}
 
@@
 	\Phi_+(m; n, p) &\coloneqq \sum\limits_{j=0}^{m/2} \binom{n}{2j} p^{2j} (1-p)^{n-2j}, \nonumber\\ 
-	&m\in[0,n]\ \text{and m even}, \label{eq:fp} \\
+	&m\in[0,n]\ \text{and }m\text{ even}, \label{eq:fp} \\
 	\Phi_-(m; n, p) &\coloneqq \sum\limits_{j=1}^{(m-1)/2} \binom{n}{2j+1} p^{2j+1} (1-p)^{n-(2j+1)}, \nonumber\\ 
-	&m\in[0,n]\ \text{and m odd}. \label{eq:fn2}
-\end{align}
-Index $m$ only takes even (odd) values when labelling $\Phi_+$ ($\Phi_-$) and therefore we can use $\Phi_{\pm}$ to compactify statements that hold for both sums.
+	&m\in[0,n]\ \text{and }m\text{ odd}. \label{eq:fn2}
+\end{align}
+Index $m$ only takes even (odd) values when labelling $\Phi_+$ ($\Phi_-$) and therefore we can use $\Phi_{\pm}$ to compactify statements that hold for both $\Phi_+, \Phi_-$.
 In particular, we derive ``loose'' and ``strict'' bounds on $\Phi_{\pm}$.
@@
 \begin{proof}
-	!!!
+	\nick{paste proof}
 \end{proof}
@@
 \begin{proof}
-	!!!
+	\nick{paste proof}
 \end{proof}
+
+\subsubsection{Standard Lorenz curves in terms of binomial distributions}
+\textbf{Note:} We assume that the number of copies $n$ is even throughout.
+
+The Lorenz curve $\lc{\noisysn}{\frac{1}{d}\id}$ consists of $n+1$ line segments, connecting at $n$ points, called \emph{elbows}, between the endpoints $(0,0)$ and $(1,1)$, as illustrated in~\cref{fig:lcsu_elbows}.
+\begin{figure}[b]
+    \centering
+    \includegraphics[scale=0.5]{figs/lccalcdiagram.pdf}
+    \caption{\textbf{Anatomy of Strange state Lorenz curve}
+    There are $n$ ``elbows'' in this Lorenz curve of an $n$-copy Strange state.
+    Labels $k, k'$ indicate two elbows for the $n=4$ case.
+    Their coordinates are given in~\cref{eq:lcsu_elbows}.
+    }
+    \label{fig:lcsu_elbows}
+\end{figure}
+We denote the Lorenz curve maximum as the $k_\star$-th point.
+It occurs at 
+\begin{align}\label{eq:lcsu_max}
+	x_{k_\star} &= \frac{1}{2}\left(1 + \left( \frac{7}{9} \right)^n \right), \\
+	L_{k_\star} &\equiv \lc{\noisysn}{\frac{1}{d}\id}(x_{k_\star}) = \frac{1}{2}\left (1 + \left(\frac{15-8\epsilon}{9}\right)^n \right),
+\end{align}
+with $k_\star = n/2$.
+The coordinates of the standard Lorenz curve for a gien number of copies $n$ and noise level $\epsilon$ can be directly expressed in terms of $\Phi_+, \Phi_-$, for all $m$, $n$ the number of copies and some fixed $p \equiv p(\epsilon)$.
+
+The Wigner distribution of the qutrit maximally mixed state $\id/3$ is the uniform distribution $\bm{1}/9$.
+The Wigner distribution of the 1-copy noisy Strange state $\rho_{\rm{S}}(\epsilon)$ in the unital fragment is a permutation of 8 positive components ($w_+$) and 1 negative ($w_-$) with
+\begin{align}
+	w_+ &= \frac{1}{6} - \frac{1}{18}\epsilon \\
+	w_- &= -\frac{1}{3} + \frac{4}{9}\epsilon.
+\end{align}
+They are depicted in~\cref{fig:noisys}.
+\begin{figure}[t]
+    \centering
+    \includegraphics[scale=0.7]{figs/noisys.pdf}
+    \caption{\textbf{Wigner components of the noisy Strange state.} 
+    In the interval $0 \leq \epsilon < 3/7$, the negative component is larger than the positive components.
+    At $\epsilon = 3/7$ the Wigner distribution is $(-\frac{1}{7},\frac{1}{7},\dots,\frac{1}{7})$.
+    In the interval $3/7 < \epsilon < 3/4$, the positive components are larger than the negative component.
+    In the interval $3/4 \leq \epsilon \leq 1$, there is no negativity.
+    }
+    \label{fig:noisys}
+\end{figure}
+The $n+1$ distinct Wigner components ($w_j$) of $\noisysn$ along with their multiplicities ($c_j$) are given in~\cref{tab:lcsu_w}.
+\begin{table}[t]                           
+ \centering
+ \begin{tabular}{c|c|c|c}
+ $\epsilon$ & $j$ & $\left[0, \frac{n}{2}\right]$ & $\left[\frac{n}{2} + 1, n \right]$ \\ [0.5ex] 
+ \hline
+  & $w_{j}$ & $w_+^{2j}w_-^{n-2j}$ & $w_+^{n-2j}w_-^{2j}$  \\
+  $0\leq \epsilon < \frac{3}{7}$ & & & \\
+  & $c_{j}$ & $8^{2j}\binom{n}{2j}$ & $8^{n-2j}\binom{n}{2j}$ \\
+ \hline
+  & $w_{j}$ & $w_+^{n-2j}w_-^{2j}$ & $w_+^{2j}w_-^{n-2j}$  \\
+  $\frac{3}{7} \leq \epsilon < \frac{3}{4} $ & & & \\
+  & $c_{j}$ & $8^{n-2j}\binom{n}{2j}$ & $8^{2j}\binom{n}{2j}$
+\end{tabular}
+ \caption{Wigner components of $\rho_{\rm{S}}^{\otimes n}(\epsilon)$. The multiplication $2j$ is modulo $(n+1)$.}
+ \label{tab:lcsu_w}
+\end{table}
+
+To get the Lorenz curve, we need to sum up the Wigner components in decreasing order and the order depends on the noise level $\epsilon$, so we define probabilities associated with the $x$-coordinate ($p_x$) and the vertical coordinate ($p_L$) of the Lorenz curve accordingly,
+\begin{equation}
+	(p_x, p_L) \equiv \big( p_x(\epsilon), p_L(\epsilon) \big) = 
+	\begin{cases}
+		\left( \frac{8}{9}, \frac{12-4\epsilon}{15-8\epsilon} \right),\ & 0\leq \epsilon < \frac{3}{7} \\
+		\left( \frac{1}{9}, \frac{3-4\epsilon}{15-8\epsilon} \right),\ & \frac{3}{7}\leq \epsilon < \frac{3}{4} \\
+	\end{cases}	
+\end{equation}
+
+We are now in a position to express Lorenz curve coordinates in terms of phi distributions,
+\begin{equation}
+	x_k(n, \epsilon) = 
+	\begin{cases}
+		\Phi_+(k;n,p_x),\\
+		\hspace{20pt} k\in[0,n]\ \text{and }k\text{ even}, \\
+		x_{k_\star} + \Phi_-(k;n,1-p_x),\\
+		\hspace{20pt} k\in[0,n]\ \text{and }k\text{ odd}, \\
+	\end{cases}	
+\end{equation}
+and
+\begin{equation}
+	L_k(n, \epsilon) = 
+	\begin{cases}
+		\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+(k;n,p_L),\\
+		\hspace{20pt} k\in[0,n]\ \text{and }k\text{ even}, \\
+		L_{k_\star} + \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-(k;n,1-p_L),\\
+		\hspace{20pt} k\in[0,n]\ \text{and }k\text{ odd}. \\
+	\end{cases}	
+\end{equation}
+
+Finally, the $m$-th elbow is located at
+\begin{equation}\label{eq:lcsu_elbows}
+	\left(x_m, \lc{\noisysn}{\frac{1}{d}\id}(x_m) \right) = \Big( x_{2m}(n, \epsilon), L_{2m}(n, \epsilon) \Big),
+\end{equation}
+where $2m$ is considered \hspace{-7pt}$\mod{(n+1)}$.
+
+We can therefore use~\cref{lem:bounds_loose,lem:bounds_strict} to bound the standard Lorenz curves.
+\begin{figure}[b]
+    \centering
+    \includegraphics[scale=0.5]{figs/lc_bounds.pdf}
+    \caption{\textbf{Lorenz curves and bounding curves.} 
+    The figure explores the distillation process of a 10-copy $0.25$-noisy Strange state to a 4-copy $0.05$-noisy Strange state in the unital fragment.
+    Clearly, by looking at the Lorenz curves, the distillation process is possible.
+    However the bounding curves, derived in~\cref{lem:bounds_strict}, intersect at the end, suggesting that the process is not necessarily possible.
+    }
+    \label{fig:lc_bounds}
+\end{figure}
 

### 2020-10-20 magic_paper.tex
Added Lemma (page 11) on necessary lorenz curves comparisons"

@@
 	x_{k_\star} &= \frac{1}{2}\left(1 + \left( \frac{7}{9} \right)^n \right), \\
-	L_{k_\star} &\equiv \lc{\noisysn}{\frac{1}{d}\id}(x_{k_\star}) = \frac{1}{2}\left (1 + \left(\frac{15-8\epsilon}{9}\right)^n \right),
+	L_{k_\star} &\equiv \lc{\noisysn}{\frac{1}{d}\id}(x_{k_\star}) = \frac{1}{2}\left (1 + \left(\frac{5}{3}-\frac{8}{9}\epsilon\right)^n \right),
 \end{align}
@@
 		\hspace{20pt} k\in[0,n]\ \text{and }k\text{ even}, \\
-		L_{k_\star} + \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-(k;n,1-p_L),\\
+		L_{k_\star} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-(k;n,1-p_L),\\
 		\hspace{20pt} k\in[0,n]\ \text{and }k\text{ odd}. \\
@@
     \centering
-    \includegraphics[scale=0.5]{figs/lc_bounds.pdf}
+    \includegraphics[scale=0.4]{figs/lc_bounds.pdf}
     \caption{\textbf{Lorenz curves and bounding curves.} 
@@
 \end{figure}
+
+\subsubsection{Lorenz curve comparison}
+According to~\cref{thm:dmajor}, a necessary condition for $\rho \xrightarrow{\E \in \O_\sigma} \tau$ is that $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$.
+We can reduce this condition to a finite set of inequalities, defined at the elbows of $\lc{\tau}{\sigma}(x)$.
+\begin{theorem}\label{thm:elbows}
+	Let $\rho, \tau$ be two quantum states with Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in the $\sigma$-fragment.
+	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff the elbows of $\lc{\tau}{\sigma}(x)$ lie vertically below $\lc{\rho}{\sigma}(x)$.
+\end{theorem}
+\begin{proof}
+	Let $n$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ and $T \coloneqq \{x_0, x_1, \dots, x_n, x_{n+1} \}$ be the set of the elbows' $x$-coordinates including $x_0 = 0$ and $x_{n+1} = 1$.
+
+	$\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ implies $\lc{\rho}{\sigma}(x_k) \geq \lc{\tau}{\sigma}(x_k)$ for all $x_k \in T$ trivially.
+
+	Conversely, assume that $\lc{\rho}{\sigma}(x_k) \geq \lc{\tau}{\sigma}(x_k)$ for all $x_k \in T$.
+	Pick two consecutive $x$-coordinates $x_i, x_{i+1}$ and consider the line segment $\ell_\tau(x)$ connecting points $(x_i, \lc{\tau}{\sigma}(x_i))$ and $(x_{i+1}, \lc{\tau}{\sigma}(x_{i+1}))$ as well as the line segment $\ell_\rho(x)$ connecting points $(x_i, \lc{\rho}{\sigma}(x_i))$ and $(x_{i+1}, \lc{\rho}{\sigma}(x_{i+1}))$.
+	This is illustrated in~\cref{fig:elbows_proof}.
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.6]{figs/elbows_proof.pdf}
+    \caption{\textbf{Illustration of~\cref{thm:elbows}}.
+    }
+    \label{fig:elbows_proof}
+\end{figure}
+
+	Due to concavity of $\lc{\rho}{\sigma}$, it is clear that for all $x \in [x_i, x_{i+1}]$, we have $\lc{\rho}{\sigma}(x) \geq \ell_\rho(x) \geq \ell_\tau(x) = \lc{\tau}{\sigma}(x)$.
+	This argument can be made in all intervals $[x_i, x_{i+1}]$ with $i=0,\dots,n$, so the proof is complete.
+\end{proof}
+
+Consider now the magic state conversion,
+\begin{equation}\label{eq:su_conversion}
+	\noisysn \xrightarrow{\E \in \O_{\id/d}} \rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}.
+\end{equation}
+The Lorenz curve comparison of these states gives rise to $k$ independent necessary constraints
+\begin{align}
+\lc{\noisysn}{\frac{1}{d}\id}(x_1) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x_1), \nonumber\\
+\lc{\noisysn}{\frac{1}{d}\id}(x_2) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x_2), \nonumber\\
+&\vdotswithin{=} \nonumber\\
+\lc{\noisysn}{\frac{1}{d}\id}(x_k) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x_k), \nonumber
+\end{align}
+where $x_1, x_2, \dots, x_k$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}$.
 

### 2020-10-21 magic_paper.tex
Added discussion on Lorenz curve comparison for state conversion

@@
 \subsubsection{Lorenz curve comparison}
+Consider the magic state conversion,
+\begin{equation}\label{eq:su_conversion}
+	\noisysn \xrightarrow{\E \in \O_{\id/d}} \rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}.
+\end{equation}
+Pointwise comparison of the initial and final state Lorenz curves is non-trivial, since the elbows of the curves do not align veritically.
+The initial state Lorenz curve consists of
+\begin{equation}
+	\sum_{j=0}^{n} c_j = 9^n
+\end{equation}
+\nick{technically $(9^n+1)$ because 0 is artificially added in the end} points with $x$-coordinates incrementing by $\frac{1}{9^n}$ which we denote as the set 
+\begin{equation}
+X \coloneqq \left\{ \sum_{i=0}^{k} \frac{i}{9^n} \right\}_{0 < k \leq 9^n}.
+\end{equation}
+
+The final state Lorenz curve consists of $9^k (< 9^n)$ points and, in order to make a pointwise comparison, we rewrite it as
+\begin{equation}
+\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k} \otimes \left( \frac{1}{d}\id\right)^{\otimes(n-k)},
+\end{equation}
+with transformed Wigner components $w_j^\prime = d^{-2(n-k)}w_j$ and multiplicities $c_j^\prime = d^{2(n-k)}c_j$, where $w_j, c_j$ are given in~\cref{tab:lcsu_w} for $j=0,\dots,k$.
+The Lorenz curve of the final state remains the same, but now it consists of $9^n$ points with the same $x$-coordinates as the initial state.
+Therefore, we can compare the curves pointwise with $9^n$ inequalities of the form
+\begin{equation}\label{eq:lc_pointwise}
+\lc{\noisysn}{\frac{1}{d}\id}(x) \geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x)
+\end{equation}
+for all $x \in X$.
+
 According to~\cref{thm:dmajor}, a necessary condition for $\rho \xrightarrow{\E \in \O_\sigma} \tau$ is that $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$.
-We can reduce this condition to a finite set of inequalities, defined at the elbows of $\lc{\tau}{\sigma}(x)$.
+We can reduce the inequalities in~\cref{eq:lc_pointwise} significantly with the following result.
 \begin{theorem}\label{thm:elbows}
@@
 
-Consider now the magic state conversion,
-\begin{equation}\label{eq:su_conversion}
-	\noisysn \xrightarrow{\E \in \O_{\id/d}} \rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}.
-\end{equation}
-The Lorenz curve comparison of these states gives rise to $k$ independent necessary constraints
+Returning to~\ref{eq:su_conversion}, the $k$ independent necessary constraints are
 \begin{align}
@@
 \end{align}
-where $x_1, x_2, \dots, x_k$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}$.
+where $x_1, x_2, \dots, x_k \in X$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}$.
 

### 2020-10-22 magic_paper.tex
Comments on adding in free states and getting corresponding Lorenz curves.

@@
 \end{equation}
-Pointwise comparison of the initial and final state Lorenz curves is non-trivial, since the elbows of the curves do not align veritically.
+Pointwise comparison of the initial and final state Lorenz curves is non-trivial, since the elbows of the curves do not align vertically.
 The initial state Lorenz curve consists of
@@
 \end{equation}
-
-The final state Lorenz curve consists of $9^k (< 9^n)$ points and, in order to make a pointwise comparison, we rewrite it as
+\ddd{[DJ: This sum can be evaluated: $\sum_{i=0}^k = \frac{1}{2}k(k+1)$. Always aim to tidy and simplify! Half of research is presenting the facts simply and clearly.]}
+
+The final state Lorenz curve consists of $9^k (< 9^n)$ points and, \ddd{however since we work in the unital fragment the maximally mixed state$\frac{1}{d} \I$ is a free state and so we are free to add in arbitrary many copies to the final state.
+This addition does not change the total Lorenz curve of the state, but merely increases the resolution on the $x$ axis.
+We thus want to compute the Lorenz curve of the state}
 \begin{equation}
@@
 \end{equation}
-with transformed Wigner components $w_j^\prime = d^{-2(n-k)}w_j$ and multiplicities $c_j^\prime = d^{2(n-k)}c_j$, where $w_j, c_j$ are given in~\cref{tab:lcsu_w} for $j=0,\dots,k$.
-The Lorenz curve of the final state remains the same, but now it consists of $9^n$ points with the same $x$-coordinates as the initial state.
+with transformed Wigner components 
+\begin{equation}
+w_j^\prime = \frac{1}{d^{2(n-k)}}w_j,
+\end{equation}
+and multiplicities $c_j^\prime = d^{2(n-k)}c_j$, where $w_j, c_j$ are given in~\cref{tab:lcsu_w} for $j=0,\dots,k$.
+\ddd{[DJ: You've been too sloppy and rushed here.
+Give the explicit definition of $w'_j$.
+You've hit a problem almost certainly because you are not handling this technical bit carefully and explicitly - it is crucial, so really unpack it slowly!]}
+The Lorenz curve of the final state remains the same, but now it consists of $9^n$ points with the same $x$-coordinates as the initial state \ddd{[DJ: I don't think this is true.
+You should step through the computation of the Lorenz curve more carefully and see why]}.
 Therefore, we can compare the curves pointwise with $9^n$ inequalities of the form

### 2020-10-27 magic_paper.tex
I explain the ineqaulities with an example, giving concrete formulas for calculating both sides of the inequality, still determining index j seems necessary but not analytically possible

@@
 We are now in a position to express Lorenz curve coordinates in terms of phi distributions,
-\begin{equation}
+\begin{equation}\label{x_coord_elb}
 	x_k(n, \epsilon) = 
@@
 and
-\begin{equation}
+\begin{equation}\label{lc_coord_elb}
 	L_k(n, \epsilon) = 
@@
 \begin{equation}
-	\sum_{j=0}^{n} c_j = 9^n
-\end{equation}
-\nick{technically $(9^n+1)$ because 0 is artificially added in the end} points with $x$-coordinates incrementing by $\frac{1}{9^n}$ which we denote as the set 
-\begin{equation}
-X \coloneqq \left\{ \sum_{i=0}^{k} \frac{i}{9^n} \right\}_{0 < k \leq 9^n}.
-\end{equation}
-\ddd{[DJ: This sum can be evaluated: $\sum_{i=0}^k = \frac{1}{2}k(k+1)$. Always aim to tidy and simplify! Half of research is presenting the facts simply and clearly.]}
-
-The final state Lorenz curve consists of $9^k (< 9^n)$ points and, \ddd{however since we work in the unital fragment the maximally mixed state$\frac{1}{d} \I$ is a free state and so we are free to add in arbitrary many copies to the final state.
-This addition does not change the total Lorenz curve of the state, but merely increases the resolution on the $x$ axis.
-We thus want to compute the Lorenz curve of the state}
+	1 + \sum_{j=0}^{n} c_j = d^{2n} + 1
+\end{equation}
+points with $x$-coordinates incrementing by $\frac{1}{9^n}$ which we denote as the set 
+\begin{equation}
+X \coloneqq \left\{ \frac{k}{d^{2n}} \right\}_{0 \leq k \leq d^{2n}}.
+\end{equation}
+
+The final state Lorenz curve consists of $9^k (< 9^n)$ points, however, since we work in the unital fragment, the maximally mixed state $\frac{1}{d}\id$ is free, so can add in arbitrary many copies to the final state.
+This addition does not change the total Lorenz curve of the state, but merely increases the resolution on the $x$-axis. 
+We thus want to compute the Lorenz curve of the state
 \begin{equation}
@@
 You've hit a problem almost certainly because you are not handling this technical bit carefully and explicitly - it is crucial, so really unpack it slowly!]}
-The Lorenz curve of the final state remains the same, but now it consists of $9^n$ points with the same $x$-coordinates as the initial state \ddd{[DJ: I don't think this is true.
+
+Let's look at an example in~\cref{fig:lc_compare}.
+The Lorenz curve of the final state $\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes 2}$ remains the same when we rewrite the state as $\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes 2} \otimes (\tfrac{1}{3} \id)^{\otimes 2}$, but now it consists of $9^4$ points with the same $x$-coordinates as the initial state.
+\ddd{[DJ: I don't think this is true.
 You should step through the computation of the Lorenz curve more carefully and see why]}.
-Therefore, we can compare the curves pointwise with $9^n$ inequalities of the form
+The line segment between elbows $x_0 = 0$ and $x_1 = 1/9^2$ consists only of its endpoints for state $\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes 2}$.
+However, for state $\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes 2} \otimes \left( \tfrac{1}{3} \id\right)^{\otimes 2}$ it consists of $82$ points with coordinates $(k/9^4, kw_0)$ for $k=0,\dots,9^2$.
+The same reasoning applies on all three line segments comprising the Lorenz curve.
+\begin{figure}[t]
+    \centering
+    \includegraphics[scale=0.6]{figs/lc_compare.pdf}
+    \caption{\textbf{Example of Lorenz curve comparison.} 
+    The upper Lorenz curve (blue -- $n=4$ and $\epsilon = 0.20$) is always higher than the lower Lorenz curve (red -- $k=2$ and $\epsilon_\tau = 0.05$).
+    }
+    \label{fig:lc_compare}
+\end{figure}
+Therefore, we can compare the curves pointwise with $9^n + 1$ inequalities of the form
 \begin{equation}\label{eq:lc_pointwise}
@@
 	Let $\rho, \tau$ be two quantum states with Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in the $\sigma$-fragment.
-	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff the elbows of $\lc{\tau}{\sigma}(x)$ lie vertically below $\lc{\rho}{\sigma}(x)$.
+
+	Let $k$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ and $T \coloneqq \{x_0, x_1, \dots, x_k, x_{k+1} \}$ be the $x$-coordinates of the elbows with $x_0 = 0$ and $x_{k+1} = 1$.
+
+	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_j) \geq \lc{\tau}{\sigma}(x_j)$ for all $j =1,\dots,k$.
 \end{theorem}
 \begin{proof}	
-	Let $n$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ and $T \coloneqq \{x_0, x_1, \dots, x_n, x_{n+1} \}$ be the set of the elbows' $x$-coordinates including $x_0 = 0$ and $x_{n+1} = 1$.
-
-	$\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ implies $\lc{\rho}{\sigma}(x_k) \geq \lc{\tau}{\sigma}(x_k)$ for all $x_k \in T$ trivially.
-
-	Conversely, assume that $\lc{\rho}{\sigma}(x_k) \geq \lc{\tau}{\sigma}(x_k)$ for all $x_k \in T$.
+	$\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ trivially implies $\lc{\rho}{\sigma}(x_k) \geq \lc{\tau}{\sigma}(x_k)$ for all $k =0,\dots,n+1$.
+
+	Conversely, assume that $\lc{\rho}{\sigma}(x_j) \geq \lc{\tau}{\sigma}(x_j)$ for all $j =1,\dots,k$.
+	First, note that $\lc{\rho}{\sigma}(x_0) = \lc{\tau}{\sigma}(x_0) = 0$ and $\lc{\rho}{\sigma}(x_{k+1}) = \lc{\tau}{\sigma}(x_{k+1}) = 1$.
+
 	Pick two consecutive $x$-coordinates $x_i, x_{i+1}$ and consider the line segment $\ell_\tau(x)$ connecting points $(x_i, \lc{\tau}{\sigma}(x_i))$ and $(x_{i+1}, \lc{\tau}{\sigma}(x_{i+1}))$ as well as the line segment $\ell_\rho(x)$ connecting points $(x_i, \lc{\rho}{\sigma}(x_i))$ and $(x_{i+1}, \lc{\rho}{\sigma}(x_{i+1}))$.
@@
 	Due to concavity of $\lc{\rho}{\sigma}$, it is clear that for all $x \in [x_i, x_{i+1}]$, we have $\lc{\rho}{\sigma}(x) \geq \ell_\rho(x) \geq \ell_\tau(x) = \lc{\tau}{\sigma}(x)$.
-	This argument can be made in all intervals $[x_i, x_{i+1}]$ with $i=0,\dots,n$, so the proof is complete.
+	This argument can be made in all intervals $[x_i, x_{i+1}]$ with $i=0,\dots,k$, so the proof is complete.
 \end{proof}
@@
 \end{align}
-where $x_1, x_2, \dots, x_k \in X$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}$.
+where $x_1, x_2, \dots, x_k \in T \subset X$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).
+
+The RHSs can be calculated directly by~\cref{lc_coord_elb}, but the LHSs do not correspond to elbows.
+To calculate $\lc{\noisysn}{\frac{1}{d}\id}(x_j)$ for $j=1,\dots,k$, we first need to identify the elbow of the curve just before $x_j$.
+Let $R \coloneqq \{x^{(\rho)}_0, x^{(\rho)}_1, \dots, x^{(\rho)}_n, x^{(\rho)}_{n+1}\} \subset X$ be the elbows of $\lc{\noisysn}{\frac{1}{d}\id}(x)$.
+Then, the elbow index just before $x_j$ is
+\begin{equation}
+	J = \max{\{i: x^{(\rho)}_i \leq x_j \}}.
+\end{equation}
+The slope from the $J$-th elbow to point $(x_j, \lc{\noisysn}{\frac{1}{d}\id}(x_j)$ is given by the $(J+1)$-th Wigner component, so that the LHS can be calculated as 
+\begin{equation}\label{calc_lhs}
+	L_J + d^{2n}(x_j - x_J)w_{J+1}.
+\end{equation}
+This is illustrated in~\cref{fig:lc_compare}, where we check the constarint at $x_2 = 0.8025$.
+Using~\cref{lc_coord_elb}, we find that $\lc{\rho_{\rm{S}}(\epsilon_\tau)^{\otimes 2}}{\frac{1}{d}\id}(x_2) = 1.8158$, while expression~\cref{calc_lhs} gives $\lc{\rho_{\rm{S}}(\epsilon)^{\otimes 4}}{\frac{1}{d}\id}(x_2) = 2.235$.
 

### 2020-11-03 magic_paper.tex
minor changes

@@
 Give the explicit definition of $w'_j$.
-You've hit a problem almost certainly because you are not handling this technical bit carefully and explicitly - it is crucial, so really unpack it slowly!]}
+You've hit a problem almost certainly because you are not handling this technical bit carefully and explicitly - it is crucial, so really unpack it slowly!]} \nick{I don't think it gets more explicit, you just split the line segments uniformly into $d^{2(n-k)}$ segments of length equal to $1/d^{2(n-k)}$ of the total length.}
 
@@
 The Lorenz curve of the final state $\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes 2}$ remains the same when we rewrite the state as $\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes 2} \otimes (\tfrac{1}{3} \id)^{\otimes 2}$, but now it consists of $9^4$ points with the same $x$-coordinates as the initial state.
-\ddd{[DJ: I don't think this is true.
-You should step through the computation of the Lorenz curve more carefully and see why]}.
 The line segment between elbows $x_0 = 0$ and $x_1 = 1/9^2$ consists only of its endpoints for state $\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes 2}$.
@@
 To calculate $\lc{\noisysn}{\frac{1}{d}\id}(x_j)$ for $j=1,\dots,k$, we first need to identify the elbow of the curve just before $x_j$.
-Let $R \coloneqq \{x^{(\rho)}_0, x^{(\rho)}_1, \dots, x^{(\rho)}_n, x^{(\rho)}_{n+1}\} \subset X$ be the elbows of $\lc{\noisysn}{\frac{1}{d}\id}(x)$.
+Let $R \coloneqq \{y_0, y_1, \dots, y_n, y_{n+1}\} \subset X$ be the elbows of $\lc{\noisysn}{\frac{1}{d}\id}(x)$.
 Then, the elbow index just before $x_j$ is
 \begin{equation}
-	J = \max{\{i: x^{(\rho)}_i \leq x_j \}}.
+	J = \max{\{i: y_i \leq x_j \}}.
 \end{equation}

### 2020-11-03 magic_paper.tex
minor changes

@@
     \caption{\textbf{Example of Lorenz curve comparison.} 
-    The upper Lorenz curve (blue -- $n=4$ and $\epsilon = 0.20$) is always higher than the lower Lorenz curve (red -- $k=2$ and $\epsilon_\tau = 0.05$).
+    The upper Lorenz curve (blue / $n=4$ and $\epsilon = 0.20$) is always higher than the lower Lorenz curve (red / $k=2$ and $\epsilon_\tau = 0.05$).
     }
@@
 \end{equation}
-This is illustrated in~\cref{fig:lc_compare}, where we check the constarint at $x_2 = 0.8025$.
+This is illustrated in~\cref{fig:lc_compare}, where we check the constraint at $x_2 = 0.8025$.
 Using~\cref{lc_coord_elb}, we find that $\lc{\rho_{\rm{S}}(\epsilon_\tau)^{\otimes 2}}{\frac{1}{d}\id}(x_2) = 1.8158$, while expression~\cref{calc_lhs} gives $\lc{\rho_{\rm{S}}(\epsilon)^{\otimes 4}}{\frac{1}{d}\id}(x_2) = 2.235$.

### 2020-11-13 magic_paper.tex
Cleaned up Lorenz curve section, added new notation

@@
 \subsubsection{Standard Lorenz curves in terms of binomial distributions}
-\textbf{Note:} We assume that the number of copies $n$ is even throughout.
-
-The Lorenz curve $\lc{\noisysn}{\frac{1}{d}\id}$ consists of $n+1$ line segments, connecting at $n$ points, called \emph{elbows}, between the endpoints $(0,0)$ and $(1,1)$, as illustrated in~\cref{fig:lcsu_elbows}.
-\begin{figure}[b]
-    \centering
-    \includegraphics[scale=0.5]{figs/lccalcdiagram.pdf}
-    \caption{\textbf{Anatomy of Strange state Lorenz curve}
-    There are $n$ ``elbows'' in this Lorenz curve of an $n$-copy Strange state.
-    Labels $k, k'$ indicate two elbows for the $n=4$ case.
-    Their coordinates are given in~\cref{eq:lcsu_elbows}.
-    }
-    \label{fig:lcsu_elbows}
-\end{figure}
-We denote the Lorenz curve maximum as the $k_\star$-th point.
-It occurs at 
-\begin{align}\label{eq:lcsu_max}
-	x_{k_\star} &= \frac{1}{2}\left(1 + \left( \frac{7}{9} \right)^n \right), \\
-	L_{k_\star} &\equiv \lc{\noisysn}{\frac{1}{d}\id}(x_{k_\star}) = \frac{1}{2}\left (1 + \left(\frac{5}{3}-\frac{8}{9}\epsilon\right)^n \right),
-\end{align}
-with $k_\star = n/2$.
-The coordinates of the standard Lorenz curve for a gien number of copies $n$ and noise level $\epsilon$ can be directly expressed in terms of $\Phi_+, \Phi_-$, for all $m$, $n$ the number of copies and some fixed $p \equiv p(\epsilon)$.
 
@@
 The $n+1$ distinct Wigner components ($w_j$) of $\noisysn$ along with their multiplicities ($c_j$) are given in~\cref{tab:lcsu_w}.
-\begin{table}[t]                           
+\begin{table}[b]                           
  \centering
@@
 We are now in a position to express Lorenz curve coordinates in terms of phi distributions,
-\begin{equation}\label{x_coord_elb}
+\begin{equation}\label{eq:x_coord_elb}
 	x_k(n, \epsilon) = 
@@
 and
-\begin{equation}\label{lc_coord_elb}
+\begin{equation}\label{eq:lc_coord_elb}
 	L_k(n, \epsilon) = 
@@
 
-\subsubsection{Lorenz curve comparison}
-Consider the magic state conversion,
+\subsubsection{Pointwise Lorenz curve comparison}
+
+In this subsection, we obtain explicit coordinates for all points on the Lorenz curve.
+
+Consider the $\epsilon$-noisy, $n$-copy Strange state
+\begin{equation}
+    \noisysn = \left( (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \frac{1}{3}\id \right)^{\otimes n},
+\end{equation}
+with Wigner distribution
+\begin{equation}
+	\begin{split}
+		\W{\noisysn} &= \left( \overbrace{\frac{1}{6} - \frac{1}{18}\epsilon, \dots, \frac{1}{6} - \frac{1}{18}\epsilon}^8, \overbrace{-\frac{1}{3} + \frac{4}{9}\epsilon}^1 \right)^{\otimes n} \\
+		&= \rm{W}^+_{\noisysn} + \rm{W}^-_{\noisysn},
+	\end{split}
+\end{equation}
+where we split non-negative and negative components into $\rm{W}^+_{\noisysn}$ and $\rm{W}^-_{\noisysn}$.
+
+As a simple example, we split the Wigner distribution of state $\rho_{\rm{S}}(0)^{\otimes 2}$,
+\begin{equation*}
+	\begin{split}
+    &\rm{W}^+_{\rho_{\rm{S}}(0)^{\otimes 2}} = \left( \overbrace{\left( -\frac{1}{3} \right)^2}^1, \overbrace{\left( \frac{1}{6} \right)^2, \dots, \left( \frac{1}{6} \right)^2}^{64} \right) \text{ and } \\
+    &\rm{W}^-_{\rho_{\rm{S}}(0)^{\otimes 2}} = \left( \overbrace{ -\frac{1}{3} \cdot \frac{1}{6}, \dots, -\frac{1}{3} \cdot \frac{1}{6}}^{16} \right)
+    \end{split}
+\end{equation*}
+
+For now, we restrict to the non-negative Wigner components $\rm{W}^+_{\noisysn}$ [i.e. the ``LHS of the Lorenz curve''] and we drop superscript $+$ for clarity.
+Assume: 
+\begin{itemize}
+    \item $n$ is even [ensures Lorenz curve coordinates can be expressed in terms of $\Phi_{\pm}$ distributions];
+    \item $0 \leq \epsilon \leq \frac{3}{7}$ [ensures closed-form expressions for Lorenz curve coordinates];
+\end{itemize}
+There are $\frac{n}{2}+1$ distinct non-negative components in the Wigner distribution $\W{\noisysn}$.\\
+
+We can rewrite the non-negative part of the Wigner distribution $\W{\noisysn}$ in a compact form, by simply listing the distinct Wigner components $w(k; n, \epsilon)$ along with their multiplicities $m(k; n)$:
+\begin{align}
+    &{\W{\noisysn}} = \\ 
+    &\big\{\left( m_k, w_k \right)\big\}_{k=0,\dots,n/2} = \nonumber\\ 
+    &\big\{\left( m(k; n), w(k; n, \epsilon) \right)\big\}_{k=0,\dots,n/2} = \nonumber\\
+    &\left\{ \left( 8^{n-2k}\binom{n}{2k}, \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2k}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{n-2k} \right) \right\}_{k=0,\dots,n/2}. \nonumber
+\end{align}
+
+The expressions for the Lorenz curve elbows in the unital fragment are then known:
+\begin{align}
+    &{\rm{L}_{\noisysn}} = \\
+    &\big\{\left( x_k, L_k \right)\big\}_{k=0,\dots,n/2} = \nonumber\\
+    &\big\{\left( x(k; n), L(k; n, \epsilon) \right)\big\}_{k=0,\dots,n/2} = \nonumber\\
+    &\left\{ \left( \frac{1}{9^n}\sum\limits_{j=0}^k m_j, \sum\limits_{j=0}^k m_j w_j \right) \right\}_{k=0,\dots,n/2} = \nonumber\\
+    &\left\{ \left( \Phi_+\left(2k;n,\frac{8}{9}\right), \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+\left(2k;n,4\frac{3-\epsilon}{15-8\epsilon}\right) \right) \right\}_{k=0,\dots,n/2}.
+\nonumber
+\end{align}
+We include the origin in the Lorenz curve as it does not arise from the above expressions, denoting it by $(x_{-1}, L_{-1}) \coloneqq (0,0)$.
+
+We can get explicit expressions for all $\frac{1}{2}(7^n + 9^n)$ points of the Lorenz curve, using a two-index parameterisation:
+\begin{align}
+    x_{k,\alpha} &= \left( 1-\frac{\alpha}{m_k} \right) x_{k-1} + \frac{\alpha}{m_k} x_k \label{eq:x}\\
+    L_{k,\alpha} &= \left( 1-\frac{\alpha}{m_k} \right) L_{k-1} + \frac{\alpha}{m_k} L_k \label{eq:l}\\
+    &\text{for } k=0,\dots,\frac{n}{2} \text{ and } \alpha = 1,\dots,m_k. \nonumber
+\end{align}
+
+As a simple example, we plot the Lorenz curve of state $\rho_{\rm{S}}(0)^{\otimes 2}$,
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.6]{figs/lcpoints.pdf}
+    \caption{\textbf{All points on the Lorenz curve are uniformly distributed.}
+    \cref{eq:x,eq:l}) capture the coordinates of all points up to the maximum.
+    }
+    \label{fig:lc}
+\end{figure}
+
+Consider now the state 
+\begin{equation}
+    \rho(m, \epsilon, s) = \rho_{\rm{S}}(\epsilon)^{\otimes m} \otimes \left( \frac{1}{3}\id \right)^{\otimes s}.
+\end{equation}
+
+Tensoring with the maximally mixed state keeps the Lorenz curve unchanged, but increases the resolution of (the uniformly distributed) points.
+The new point coordinates are given by:
+\begin{align}
+    x_{k,\alpha, \beta} &= \left( 1-p_{k,\alpha, \beta}\right) x_{k-1} + p_{k,\alpha, \beta} x_k \\
+    L_{k,\alpha, \beta} &= \left( 1-p_{k,\alpha, \beta} \right) L_{k-1} + p_{k,\alpha, \beta} L_k, \\
+    &\text{where } p(k, \alpha, \beta) = \frac{(\alpha-1)9^s + \beta}{9^s m_k} \\
+    &\text{for } k=0,\dots,\frac{n}{2},\ \alpha = 1,\dots,m_k \text{ and } \beta = 1,\dots,9^s. \nonumber
+\end{align}
+
+We can unify the indices, by introducing a single index
+\begin{equation}
+    i(k,\alpha,\beta) \coloneqq \beta + \left[ (\alpha-1) + \sum_{j=0}^{k-1} 8^{m-2j}\binom{m}{2j} \right]9^s,
+\end{equation}
+so that $i=1,2,\dots, \frac{1}{2}(7^{m+s} + 9^{m+s})$.
+The $\frac{m}{2}$ elbows correspond to $\beta=0,\ \alpha=1$.
+This index function is bijective.
+
+\section*{Strange state Lorenz curve comparison in the unital fragment}
+
+Consider the Strange state purification process in the unital fragment,
 \begin{equation}\label{eq:su_conversion}
-	\noisysn \xrightarrow{\E \in \O_{\id/d}} \rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}.
-\end{equation}
-Pointwise comparison of the initial and final state Lorenz curves is non-trivial, since the elbows of the curves do not align vertically.
-The initial state Lorenz curve consists of
-\begin{equation}
-	1 + \sum_{j=0}^{n} c_j = d^{2n} + 1
-\end{equation}
-points with $x$-coordinates incrementing by $\frac{1}{9^n}$ which we denote as the set 
-\begin{equation}
-X \coloneqq \left\{ \frac{k}{d^{2n}} \right\}_{0 \leq k \leq d^{2n}}.
-\end{equation}
-
-The final state Lorenz curve consists of $9^k (< 9^n)$ points, however, since we work in the unital fragment, the maximally mixed state $\frac{1}{d}\id$ is free, so can add in arbitrary many copies to the final state.
-This addition does not change the total Lorenz curve of the state, but merely increases the resolution on the $x$-axis. 
-We thus want to compute the Lorenz curve of the state
-\begin{equation}
-\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k} \otimes \left( \frac{1}{d}\id\right)^{\otimes(n-k)},
-\end{equation}
-with transformed Wigner components 
-\begin{equation}
-w_j^\prime = \frac{1}{d^{2(n-k)}}w_j,
-\end{equation}
-and multiplicities $c_j^\prime = d^{2(n-k)}c_j$, where $w_j, c_j$ are given in~\cref{tab:lcsu_w} for $j=0,\dots,k$. 
-\ddd{[DJ: You've been too sloppy and rushed here.
-Give the explicit definition of $w'_j$.
-You've hit a problem almost certainly because you are not handling this technical bit carefully and explicitly - it is crucial, so really unpack it slowly!]} \nick{I don't think it gets more explicit, you just split the line segments uniformly into $d^{2(n-k)}$ segments of length equal to $1/d^{2(n-k)}$ of the total length.}
-
-Let's look at an example in~\cref{fig:lc_compare}.
-The Lorenz curve of the final state $\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes 2}$ remains the same when we rewrite the state as $\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes 2} \otimes (\tfrac{1}{3} \id)^{\otimes 2}$, but now it consists of $9^4$ points with the same $x$-coordinates as the initial state.
-The line segment between elbows $x_0 = 0$ and $x_1 = 1/9^2$ consists only of its endpoints for state $\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes 2}$.
-However, for state $\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes 2} \otimes \left( \tfrac{1}{3} \id\right)^{\otimes 2}$ it consists of $82$ points with coordinates $(k/9^4, kw_0)$ for $k=0,\dots,9^2$.
-The same reasoning applies on all three line segments comprising the Lorenz curve.
-\begin{figure}[t]
-    \centering
-    \includegraphics[scale=0.6]{figs/lc_compare.pdf}
-    \caption{\textbf{Example of Lorenz curve comparison.} 
-    The upper Lorenz curve (blue / $n=4$ and $\epsilon = 0.20$) is always higher than the lower Lorenz curve (red / $k=2$ and $\epsilon_\tau = 0.05$).
-    }
-    \label{fig:lc_compare}
-\end{figure}
-Therefore, we can compare the curves pointwise with $9^n + 1$ inequalities of the form
-\begin{equation}\label{eq:lc_pointwise}
-\lc{\noisysn}{\frac{1}{d}\id}(x) \geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x)
-\end{equation}
-for all $x \in X$.
-
-According to~\cref{thm:dmajor}, a necessary condition for $\rho \xrightarrow{\E \in \O_\sigma} \tau$ is that $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$.
-We can reduce the inequalities in~\cref{eq:lc_pointwise} significantly with the following result.
+    \noisysn \xrightarrow{\mathcal{O}_{\id/d}} \rho_{\rm{S}}(m, \epsilon', s).
+\end{equation}
+In order to get Lorenz curve constraints on this state conversion, we need to match up the indices for the two states.
+We use non-primed indices for the initial state and primed indices for the target state,
+\begin{align}
+    i(k, \alpha) &= (\alpha-1) + \sum_{j=0}^{k-1} 8^{n-2j}\binom{n}{2j}, \\
+    i'(k',\alpha',\beta') &= \beta' + \left[ (\alpha'-1) + \sum_{j'=0}^{k'-1} 8^{m-2j'}\binom{m}{2j'} \right]9^s,
+\end{align}
+
+The question is: \emph{Given a triplet $(k', \alpha', \beta')$, what is the tuple $(k, \alpha)$ such that $i(k, \alpha) = i'(k',\alpha',\beta')$?}
+
+\newpage
+
 \begin{theorem}\label{thm:elbows}
@@
 
-Returning to~\ref{eq:su_conversion}, the $k$ independent necessary constraints are
-\begin{align}
-\lc{\noisysn}{\frac{1}{d}\id}(x_1) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x_1), \nonumber\\
-\lc{\noisysn}{\frac{1}{d}\id}(x_2) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x_2), \nonumber\\
+Returning to~\cref{eq:su_conversion}, the $k$ independent necessary constraints are
+\begin{align}
+\lc{\noisysn}{\frac{1}{d}\id}(x_{1,0,0}) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x_{1,0,0}), \nonumber\\
+\lc{\noisysn}{\frac{1}{d}\id}(x_{2,0,0}) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x_{2,0,0}), \nonumber\\
 &\vdotswithin{=} \nonumber\\
-\lc{\noisysn}{\frac{1}{d}\id}(x_k) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x_k), \nonumber
-\end{align}
-where $x_1, x_2, \dots, x_k \in T \subset X$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).
-
-The RHSs can be calculated directly by~\cref{lc_coord_elb}, but the LHSs do not correspond to elbows.
-To calculate $\lc{\noisysn}{\frac{1}{d}\id}(x_j)$ for $j=1,\dots,k$, we first need to identify the elbow of the curve just before $x_j$.
-Let $R \coloneqq \{y_0, y_1, \dots, y_n, y_{n+1}\} \subset X$ be the elbows of $\lc{\noisysn}{\frac{1}{d}\id}(x)$.
-Then, the elbow index just before $x_j$ is
-\begin{equation}
-	J = \max{\{i: y_i \leq x_j \}}.
-\end{equation}
-The slope from the $J$-th elbow to point $(x_j, \lc{\noisysn}{\frac{1}{d}\id}(x_j)$ is given by the $(J+1)$-th Wigner component, so that the LHS can be calculated as 
-\begin{equation}\label{calc_lhs}
-	L_J + d^{2n}(x_j - x_J)w_{J+1}.
-\end{equation}
-This is illustrated in~\cref{fig:lc_compare}, where we check the constraint at $x_2 = 0.8025$.
-Using~\cref{lc_coord_elb}, we find that $\lc{\rho_{\rm{S}}(\epsilon_\tau)^{\otimes 2}}{\frac{1}{d}\id}(x_2) = 1.8158$, while expression~\cref{calc_lhs} gives $\lc{\rho_{\rm{S}}(\epsilon)^{\otimes 4}}{\frac{1}{d}\id}(x_2) = 2.235$.
-
-\null\newpage
-\null\newpage
-
-The experiment is described by binomial statistics and we define the left and ``right'' tails of the cumulative binomial distribution,
-\begin{align}
-	\Phi_\ell(m; n, p) &\coloneqq \sum\limits_{j=0}^m \binom{n}{j} p^j (1-p)^{n-j}, \label{eq:phi}\\
-	\Phi_r(m; n, p) &\coloneqq \sum\limits_{j=m}^n \binom{n}{j} p^j (1-p)^{n-j}, \label{eq:phir}
-\end{align}
-where $m\in [0,n]$.
-
-They are related by the symmetry between the left tail of a $p$-coin distribution and the right tail of a $(1-p)$-coin distribution,
-\begin{equation}\label{eq:phil2phir}
-	\Phi_\ell(m; n, p) = \Phi_r(n-m; n, 1-p),\ m\in [0,n],
-\end{equation}
-as well as the normalisation condition,
-\begin{equation}
-	\Phi_\ell(m; n, p) + \Phi_r(m+1; n, p) = 1,\ m\in [0,n-1].
-\end{equation}
-
-Equivalently, we get
-\begin{align}
-	\Phi_\ell(m; n, p) + \Phi_\ell(n-m-1; n, 1-p) &= 1,\ m\in [0,n-1], \label{eq:reversephi}\\
-	\Phi_r(m; n, p) + \Phi_r(n-m+1; n, 1-p) &= 1,\ m\in [1,n]. \label{eq:reversephir}
-\end{align}
-
-The classical entropy of a $p$-coin is
-\begin{equation}\label{eq:ent}
-	S(p) \coloneqq -p\log{p} -(1-p)\log{(1-p)},
-\end{equation}
-which is symmetric, $S(p) = S(1-p)$.
-%Let $c(m; n) \coloneqq [m(1-m/n)]^{-1/2},\ m\in [1, n-1]$.
-A useful result is the entropic bound on a combination~\cite{cit:ash}.
-\begin{lemma}\label{lem:comb_bounds}
-	For all $m\in [1,n-1]$,
-	\begin{align}
-		&\left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{nS\left(\frac{m}{n}\right)} \leq \binom{n}{m} \leq \\
-		&\left[ 2\pi m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{nS\left(\frac{m}{n}\right)}.
-	\end{align}
-\end{lemma}
-\begin{proof}
-	For $m = 1,2, n-1, n-2$ check by direct calculation.	
-	For all other cases, use Stirling's approximation.
-\end{proof}
-
-Bounds on the tails of a cumulative binomial distribution can be expressed in terms of the classical relative entropy between a $p$-coin and a $q$-coin,
-\begin{equation}\label{eq:ent_rel}
-	\ent{p}{q} \coloneqq p \log{\frac{p}{q}} + (1-p) \log{\frac{1-p}{1-q}}.
-\end{equation}
-This entropy satisfies the identity
-\begin{equation}
-	\ent{p}{q} = \ent{1-p}{1-q}.
-\end{equation}
-We can now derive entropic bounds on binomial cumulative distributions~\cite{cit:ash}.
-\begin{lemma}\label{lem:phir_bounds}
-	Given fixed $n>0$ and $p$, $\Phi_r$ satisfies the following bounds:
-	\begin{align*}
-		\begin{split}
-		&\text{1. } \Phi_r(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ents},\ m\in [1,n-1] \\
-		&\text{2. } \Phi_r(m; n, p) \leq 2^{-n\ents},\ m\in [np,n] \\
-		&\text{3. } \Phi_r(m; n, p) \leq 1 - \left[ 8(m-1)\left(1-\frac{m-1}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m-1}{n}}{p}}, \\
-		&\hspace{14pt} m\in [2,n]
-		\end{split}
-		\\
-		&\text{4. } \Phi_r(m; n, p) \geq 1 - 2^{-n\ent{\frac{m-1}{n}}{p}},\ m\in [2,np+1]
-	\end{align*}
-
-	The asymptotic behaviour of $\Phi_r$ is determined by the relative entropy, 
-	\begin{equation}
-		\lim_{n\rightarrow\infty}{-\frac{1}{n}\log{\Phi_r(m; n, p)} = \ent{\frac{m}{n}}{p}},\ m\in [np,n]
-	\end{equation}
-\end{lemma}
-\begin{proof}
-	For bound (1), note that
-	\begin{align*}
-		\Phi_r(m; n, p) &= \sum\limits_{j=m}^n \binom{n}{j} p^j (1-p)^{n-j} \\
-						   &\geq \binom{n}{m} p^{m} (1-p)^{n-m} \\
-						   &\geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{nS\left(\frac{m}{n}\right)} p^{m} (1-p)^{n-m} \\
-						   &= \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ents}.
-	\end{align*}
-	The first inequality follows from the positivity of the terms in the series, the second from~\cref{lem:comb_bounds} and the equality from the entropy definitions in~\cref{eq:ent,eq:ent_rel}
-
-	For bound (2), consider a binomial random variable $X = \sum_{i=1}^N$, where $X_i$ takes the values 1, 0 with probabilities $p$ and $1-p$ respectively.
-	Then we have
-	\begin{align*}
-		\Phi_r(m; n, p) &= P(X \geq m) = P\left(2^{rX} \geq 2^{rm}\right) \\
-						   &\leq 2^{-rm} E\left(2^{rX}\right) = 2^{-rm + n\log{(1-p+pe^r)}} \\
-						   &\leq 2^{-n\ents}.
-	\end{align*}
-	The first inequality holds for any discrete random variable $X$ with $r \geq 0$, while the second inequality involves maximisation of the exponent which occurs at $e^r = \frac{m(1-p)}{(n-m)p}$ (a non-negative $r$ exists if $np \leq m$).
-
-	Bound 3 follows from bound 1 and~\cref{eq:reversephir}. Bound 4 follows from bound 2 and~\cref{eq:reversephir}.
-
-	The asymptotic limit is a direct consequence of the squeeze theorem.
-\end{proof}
-
-\begin{lemma}\label{lem:phil_bounds}
-	Given fixed $n>0$ and $p$, $\Phi_\ell$ satisfies the following bounds:
-	\begin{align*}
-		\begin{split}
-		&\text{1. } \Phi_\ell(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ents},\ m\in [1,n-1] \\
-		&\text{2. } \Phi_\ell(m; n, p) \leq 2^{-n\ents},\ m\in [0,np] \\
-		&\text{3. } \Phi_\ell(m; n, p) \leq 1 - \left[ 8(m+1)\left(1-\frac{m+1}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m+1}{n}}{p}}, \\
-		&\hspace{14pt} m\in [0,n-2]
-		\end{split}
-		\\
-		&\text{4. } \Phi_\ell(m; n, p) \geq 1 - 2^{-n\ent{\frac{m+1}{n}}{p}},\ m\in [np+1,n-2]
-	\end{align*}
-
-	The asymptotic behaviour of $\Phi_\ell$ is determined by the relative entropy,
-	\begin{equation}
-		\lim_{n\rightarrow\infty}{-\frac{1}{n}\log{\Phi_r(m; n, p)} = \ent{\frac{m}{n}}{p}},\ m\in [0,np]
-	\end{equation}
-\end{lemma}
-\begin{proof}
-	This lemma is a direct consequence of~\cref{lem:phir_bounds} and~\cref{eq:phil2phir}.
-\end{proof}
-
-We now define the alternating counterpart of the left tail distribution,
-\begin{equation}\label{eq:phialt}
-	\Phi_\ell^{\rm{alt}}(m; n, p) \coloneqq \sum\limits_{j=0}^m \binom{n}{j} (-p)^j (1-p)^{n-j},
-\end{equation}
-where $m\in [0,n]$.
-$\Phi_\ell^{\rm{alt}}$ is \emph{not} the cumulative distribution of any random variable.
-It is upper bounded by $\Phi_\ell$,
-\begin{equation}\label{eq:phialt_bound}
-	\abs{\Phi_\ell^{\rm{alt}}(m; n, p)} \leq \Phi_\ell(m; n, p),\ m\in [0,n]
-\end{equation}
-with equality iff $m=0$.
-
-We further define the two balanced combinations of $\Phi_\ell, \Phi_\ell^{\rm{alt}}$ for all $m\in [0,n]$,
-\begin{align}	
-	\Phi_+(m; n, p) &\coloneqq \frac{1}{2} \left( \Phi_\ell(m; n, p) + \Phi_\ell^{\rm{alt}}(m; n, p) \right), \\
-	\Phi_-(m; n, p) &\coloneqq \frac{1}{2} \left( \Phi_\ell(m; n, p) - \Phi_\ell^{\rm{alt}}(m; n, p) \right), \\
-	\Phi(m; n, p) &\coloneqq \label{eq:phi}
-	\begin{cases}
-		\Phi_+(m; n, p),\ \text{for even }m\in[0,n] \\
-		\Phi_-(m; n, p),\ \text{for odd }m\in[0,n].
-	\end{cases}
-\end{align}
-\begin{lemma}\label{lem:phi_bounds}
-	Given fixed $n>0$ and $p$, $\Phi$ satisfies the following bounds:
-	\begin{align*}
-		\begin{split}
-		&\text{1. } \Phi(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ents},\ m\in [1,n-1] \\
-		&\text{2. } \Phi(m; n, p) \leq 2^{-n\ents},\ m\in [0,np] \\
-		&\text{3. } \Phi(m; n, p) \leq 1 - \left[ 8(m+1)\left(1-\frac{m+1}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m+1}{n}}{p}}, \\
-		&\hspace{14pt} m\in [0,n-2]
-		\end{split}
-	\end{align*}
-\end{lemma}
-\begin{proof}
-	Bound 1 follows directly from~\cref{lem:comb_bounds}.
-
-	Bounds 2,3 follow from bounds 2,3 in~\cref{lem:phil_bounds} combined with~\cref{eq:phi,eq:alt_bound}.
-\end{proof}
-\begin{lemma}\label{lem:phi_strictbounds}
-	Given fixed $n>0$ and $p$, $\Phi_+, \Phi_-$ satisfy the following bounds:
-	\begin{align*}
-		\begin{split}
-		&\text{1. } \Phi_+(2m; n, p) \geq \sum_{0\leq j \leq m}\left[ 8(2j)\left(1-\frac{2j}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{2j}{n}}{p}}, \\
-		&\hspace{14pt} m\in [1,\left\lceil\frac{n}{2}\right\rceil] \\
-		&\text{2. } \Phi_+(2m; n, p) \leq \sum_{0\leq j \leq m}\left[ 2\pi(2j)\left(1-\frac{2j}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{2j}{n}}{p}}, \\
-		&\hspace{14pt} m\in [1,\left\lceil\frac{n}{2}\right\rceil] \\
-		&\text{3. } \Phi_-(2m+1; n, p) \geq \sum_{0\leq j \leq m}\left[ 8(2j)\left(1-\frac{2j}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{2j}{n}}{p}}, \\
-		&\hspace{14pt} m\in [1,\left\lceil\frac{n-1}{2}\right\rceil] \\
-		&\text{4. } \Phi_-(2m+1; n, p) \leq \sum_{0\leq j \leq m}\left[ 2\pi(2j)\left(1-\frac{2j}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{2j}{n}}{p}}, \\
-		&\hspace{14pt} m\in [1,\left\lceil\frac{n-1}{2}\right\rceil] \\
-		\end{split}
-	\end{align*}
-\end{lemma}
-\begin{proof}
-	The bounds are direct consequences of~\cref{lem:comb_bounds}.
-\end{proof}
-
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.5]{figs/phi_bounds.pdf}
-    \caption{\textbf{Cumulative binomial distribution bounds}
-    Distributions $\Phi_\ell, \Phi_+$ are plotted for $n=100$ and $p=1/9$.
-    The first three bounds are given in~\cref{lem:phil_bounds,lem:phi_bounds} and are valid for both $\Phi_\ell$ and $\Phi_+$.
-    The fourth bound is given in~\cref{lem:phil_bounds} and is only valid for $\Phi_\ell$.
-    The fifth and sixth bounds are quite strict and given in~\cref{lem:phi_strictbounds} for $\Phi_+$.
-    }
-    \label{fig:lccalc}
-\end{figure}
-
-\subsubsection{Standard Lorenz curves in terms of binomial distributions}
-The coordinates of the standard Lorenz curve can be directly expressed in terms of $\Phi_+, \Phi_-$, for all $m$, some fixed $p$ and number of copies $n$.
-
-\null\newpage
-\null\newpage
-
-\subsection{Lorenz curves calculations}
-
-\subsubsection{Lorenz curve ordering and maximum}
-
-Lorenz curve analysis simplifies significantly in the unital fragment \nick{or so I thought initially}, because the invariant Wigner distribution is the uniform distribution depicted in~\cref{fig:maxmix}.
-Therefore, $\W[\bmu]{(\frac{1}{d}\id)^{\otimes n}} = \frac{1}{d^{2n}}$ for all $\bmu \in \pd[d^n]$ and the ordering of the points on the Lorenz curve only depends on the ordering of the Wigner components of $\rho$.
-The Lorenz curve $\lc{\ketbra{\rm{S}}^{\otimes n}}{\frac{1}{d}\id}$ consists of $n+1$ line segments, with $n$ endpoints, or ``elbows'', between $(0,0)$ and $(1,1)$. 
-The $k_\star$-th endpoint is the maximum in~\cref{eq:Skmax} occuring at 
-\begin{equation}
-	x_{k_\star} = \frac{1}{2}\left(1 + \left( \frac{7}{9} \right)^n \right).
-\end{equation}
-
-We now investigate the location of all $n$ elbows, depicted in the diagram of~\cref{fig:lccalc}.
-
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.5]{figs/lccalcdiagram.pdf}
-    \caption{\textbf{Anatomy of Strange state Lorenz curve}
-    There are $n$ ``elbows'' in this Lorenz curve of an $n$-copy Strange state.
-    Labels $k, k'$ indicate elbows left and right of the maximum respectively.
-    Their coordinates are given in~\cref{eq:leftelb,eq:rightelb}.
-    }
-    \label{fig:lccalc}
-\end{figure}
-
-Let $\overline{n} = 2\floor{\frac{n}{2}}$ be equal to $n$ if $n$ is even and $n-1$ if $n$ is odd.
-Then, the positive components of the $n$-copy Strange state Wigner distribution $\W{\ketbra{\rm{S}}}$ are, in decreasing order, $6^{-n} 2^{\bar n} 2^{-j},\ j=0, 2, \dots, \bar n$ with respective multiplicites $8^{n-\bar n} 8^j \binom{n}{\bar n - j}$.
-The negative components are, in decreasing order $-6^{-n} 2^j,\ j=1,3, \dots, n$ with respective multiplicities $8^n 8^{-j} \binom{n}{j}$.
-
-\subsubsection{Lorenz curve in terms of a binomial cumulative distribution}
-
-Denote by $\Phi(m; n, p)$ the cumulative binomial distribution,
-\begin{align}
-	\Phi(m; n, p) &\coloneqq \sum\limits_{j=0}^m \binom{n}{j} p^j (1-p)^{n-j}, \label{eq:phi}\\
-	\Phi^c(m; n, p) &\coloneqq \sum\limits_{j=0}^m \binom{n}{j} (-p)^j (1-p)^{n-j}. \label{eq:phic}
-\end{align}
-Note that $\Phi(m; n, p)^c$ differs only by a factor of $(-1)^j$.
-It is clear that for any $n,p$ and $m \leq n$
-\begin{align}
-	&\Phi(m; n, p) + \Phi(n-m; n, 1-p) = 1, \label{eq:reversef}\\
-	&\Phi^c(m; n, p) \leq \Phi(m; n, p),
-\end{align}
-where equality in the second line holds iff $m=0$.
-
-Let $\Phi_+(m; n, p)$ and $\Phi_-(m; n, p)$ denote the partial sums of even and odd indices respectively,
-\begin{align}	
-	\Phi_+(m; n, p) &= \frac{1}{2} \left( \Phi(m; n, p) + \Phi^c(m; n, p) \right), \\
-	\Phi_-(m; n, p) &= \frac{1}{2} \left( \Phi(m; n, p) - \Phi^c(m; n, p) \right).
-\end{align}
-
-Assume $n$ is even, so that $\bar n = n$.
-Then we can express any elbow on the $n$-copy Strange state Lorenz curve as
-\begin{align}
-	L_+(m; n) &= \left(\frac{5}{3}\right)^n \Phi_+\left(m;n,\frac{4}{5}\right), \label{eq:leftelb}\\
-	L_-(m; n) &= L_\star - \left(\frac{5}{3}\right)^n \Phi_-\left(m;n,\frac{1}{5}\right), \label{eq:rightelb}
-\end{align}
-where $L_\star = L_+(n; n)$ is the maximum of the curve and $L_+, L_-$ respectively indicate the elbows on the left, right of the maximum for some index $m$.
-
-The locations of the elbows are at
-\begin{align}
-	x_+(m; n) &= \Phi_+\left(m;n,\frac{8}{9}\right), \\
-	x_-(m; n) &= x_\star + \Phi_-\left(m;n,\frac{1}{9}\right),
-\end{align}
-where $x_\star = x_+(n; n)$ is the location of the maximum.
-
-Clearly by definition, 
-\begin{align}
-	\Phi_+(2m+1;n,p) &= \Phi_+(2m;n,p), \\
-	\Phi_-(2m;n,p) &= \Phi_-(2m-1;n,p),
-\end{align}
-so we define the piece-wise functions
-\begin{equation}
-	L(m;n) =
-	\begin{cases}
-	L_+(m; n),&\ m\text{: even}, \\
-	L_-(m; n),&\ m\text{: odd}
-	\end{cases}
-\end{equation}
-and
-\begin{equation}
-	x(m;n) =
-	\begin{cases}
-	x_+(m; n),&\ m\text{: even}, \\
-	x_-(m; n),&\ m\text{: odd}
-	\end{cases}
-\end{equation}
-Finally, the $m$-th elbow is located at
-\begin{equation}\label{eq:slc}
-	\left(x_m, \lc{\ketbra{\rm{S}}^{\otimes n}}{\frac{1}{d}\id}(m) \right) = \left( x(2m;n), L(2m;n) \right),
-\end{equation}
-where $2m$ is considered \hspace{-7pt}$\mod{(n+1)}$.
-
-\subsubsection{Bounds on cumulative distribution}
-
-We now want to bound these points for any index $m$, so as to investigate the asymptotic behaviour of the Lorenz curves.
-We first define a useful function
-\begin{equation}
-	c(m;n) = 
-	\begin{cases}
-		0,&\ m=0, \\
-		\left[8m\left(1-\frac{m}{n}\right)\right]^{-1/2},&\ 0<m<n, \\
-		1,&\ m=n,
-	\end{cases}
-\end{equation}
-as well as the classical relative entropy,
-\begin{equation}
-	S(\alpha||\beta) \coloneqq \alpha \log{\frac{\alpha}{\beta}} + (1-\alpha) \log{\frac{1-\alpha}{1-\beta}}.
-\end{equation}
-
-We now define two functions that we use to bound $\Phi(m;n,p)$,
-\begin{align}
-	U(m;n,p) &\coloneqq	e^{-nS\left(\frac{m}{n}||p \right)} \label{eq:ubd}, \\
-	L(m;n,p) &\coloneqq c(m;n)e^{-nS\left(\frac{m}{n}||p \right)} \label{eq:lbd}.
-\end{align}
-
-\begin{lemma}\label{lem:ulbd}
-	The cumulative distribution $\Phi(m;n,p)$ defined in~\cref{eq:phic} is exponentially bounded for all $m: 0\leq m \leq n$,
-	\begin{equation}
-		B_L(m;n,p) \leq \Phi(m;n,p) \leq B_U(m;n,p),\ m\leq np
-	\end{equation}
-	where
-	\begin{equation}
-		B_L(m;n,p) = \\
-		\begin{cases}
-			L(m;n,p),&\ m \leq np, \\
-			1 - U(n-m;n,1-p),&\ m > np,
-		\end{cases}
-	\end{equation}
-	and
-	\begin{equation}
-		B_U(m;n,p) =
-		\begin{cases}
-			U(m;n,p),&\ m \leq np, \\
-			1 - L(n-m;n,1-p),&\ m > np.
-		\end{cases}
-	\end{equation}
-\end{lemma}
-
-The bounds are demonstrated in~\cref{fig:phi} for the interesting cases of $\Phi\left(m;n,\frac{1}{5}\right),\Phi\left(m;n,\frac{4}{5}\right)$.
-
-\begin{figure}%
-    \centering
-    \subfigure[][]{%
-    \label{fig:phi1}%
-    \includegraphics[height=5cm]{figs/Phi.pdf}
-    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
-    }\\%
-    \subfigure[][]{%
-    \label{fig:phi4}%
-    \includegraphics[height=5cm]{figs/Phi2.pdf}
-    %\caption{Zero state $\ketbra{0}{0}$}%
-    }
-    \caption{Distributions $\Phi(m;n,p)$ (black) and $\Phi^c(m;n,p)$ (red) for $n=30$ and probability: 
-    \subref{fig:phi1} $p=\frac{4}{5}$; \subref{fig:phi4} $p=\frac{1}{5}$.
-    The upper and lower bounds on $\Phi(m;n,p)$ as stated in~\cref{lem:ulbd} are also presented. 
-    }%
-    \label{fig:phi}
-\end{figure}
-
-We see in~\cref{fig:phicmax} that distribution $\Phi^c(m;n,p)$ is also bounded by a constant number $\epsilon$, $0<\epsilon<1$ for all $m$.
-The bound $\epsilon$ tends to decrease as $n$ increases, so that $\abs{\Phi^c(m;n,p)} \leq \frac{1}{10}$ for $n\geq 30$.
-
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.5]{figs/Phic_max.pdf}
-    \caption{Maximum of the absolute value of $\Phi^c(m;n,p)$ over all $m$ for given $n$.
-    Here, we plot for all even $n$, $2\leq n\leq 30$.
-    The maximum is decreasing in $n$ and falls below $\frac{1}{10}$ for $n=30$.
-    \nick{we want to extract exponential bound from this graph instead of constant bound}.
-    }
-    \label{fig:phicmax}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.5]{figs/Phi_ratio.pdf}
-    \caption{Distributions $\Phi_+(m;n,p)$ (blue) and $\Phi_-(m;n,p)$ (orange) for $n=20$ and $p=\frac{4}{5}$.
-    The green curve is the ratio of the two
-    }
-    \label{fig:Phi_ratio}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.5]{figs/Phi_nexp.pdf}
-    \caption{Distributions $\Phi_+(m;n,p)/U(m;n,p)$ (blue) and $\Phi_-(m;n,p)/U(m;n,p)$ (orange) for $n=30$ and $p=\frac{4}{5}$.
-    We divide by the bound in~\cref{eq:ubd} to extract the exponential behaviour of the two distributions.
-    Here, $np = 24$, so for $m\geq 24$, $U(m;n,p) = 1$.
-    }
-    \label{fig:phinexp}
-\end{figure}
-
-\subsubsection{Noisy Strange states}
-
-Strange states of the form 
-\begin{equation}
-    \rho_{\rm{S}}(\epsilon) = (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \frac{1}{d}\id,
-\end{equation}
-contain two discrete Wigner components, so $n$-copy states $\rho_{\rm{S}}^{\otimes n}(\epsilon)$ contain $n+1$ discrete components~\cref{tab:swc} as in the noiseless case.
-\begin{table}[h]                           
- \centering
- \begin{tabular}{|c|c|}
- \hline
- $m_j$ & $8^{n-j}\binom{n}{j}$ \\ [0.5ex] 
- \hline\hline
- $w_j$ & $\left(\frac{1}{6} - \frac{1}{18}\epsilon \right)^{n-j}\left(-\frac{1}{3} + \frac{4}{9}\epsilon \right)^{j}$ \\
- \hline
-\end{tabular}
- \caption{Wigner components of $\rho_{\rm{S}}^{\otimes n}(\epsilon)$}
- \label{tab:swc}
-\end{table}
-
-Clearly, there are negative Wigner components iff $0\leq \epsilon < \frac{3}{4}$.
-At the limiting case of non-negative Wigner components $\epsilon = \frac{3}{4}$, the Lorenz curve is simply given by three points,
-\begin{equation}
-\left\{(0,0), \left(\left(\frac{8}{9}\right)^n, 1\right), (1,1) \right\}
-\end{equation}
-and exponentially tends to a step-function.
-The case of $\epsilon = 0$ is given at~\cref{eq:slc} and the noisy cases with $0 < \epsilon < \frac{3}{4}$ follow a similar analysis.
-
-\newpage
+\lc{\noisysn}{\frac{1}{d}\id}(x_{m,0,0}) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x_{m,0,0}), \nonumber
+\end{align}
+where $x_{1,0,0}, x_{2,0,0}, \dots, x_{m,0,0} \in T \subset X$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).
 

### 2020-11-19 magic_paper.tex
Indices cleanup

@@
     &\big\{\left( m(k; n), w(k; n, \epsilon) \right)\big\}_{k=0,\dots,n/2} = \nonumber\\
-    &\left\{ \left( 8^{n-2k}\binom{n}{2k}, \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2k}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{n-2k} \right) \right\}_{k=0,\dots,n/2}. \nonumber
+    &\left\{ \left( 8^{2k}\binom{n}{2k}, \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2k}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{n-2k} \right) \right\}_{k=0,\dots,n/2}. \nonumber
 \end{align}
@@
 \begin{equation}
-    \rho(m, \epsilon, s) = \rho_{\rm{S}}(\epsilon)^{\otimes m} \otimes \left( \frac{1}{3}\id \right)^{\otimes s}.
+    \rho(r, \epsilon, s) = \rho_{\rm{S}}(\epsilon)^{\otimes r} \otimes \left( \frac{1}{3}\id \right)^{\otimes s}.
 \end{equation}
@@
     &\text{where } p(k, \alpha, \beta) = \frac{(\alpha-1)9^s + \beta}{9^s m_k} \\
-    &\text{for } k=0,\dots,\frac{n}{2},\ \alpha = 1,\dots,m_k \text{ and } \beta = 1,\dots,9^s. \nonumber
+    &\text{for } k=0,\dots,\frac{r}{2},\ \alpha = 1,\dots,m_k \text{ and } \beta = 1,\dots,9^s. \nonumber
 \end{align}
@@
 \begin{equation}
-    i(k,\alpha,\beta) \coloneqq \beta + \left[ (\alpha-1) + \sum_{j=0}^{k-1} 8^{m-2j}\binom{m}{2j} \right]9^s,
-\end{equation}
-so that $i=1,2,\dots, \frac{1}{2}(7^{m+s} + 9^{m+s})$.
-The $\frac{m}{2}$ elbows correspond to $\beta=0,\ \alpha=1$.
+    i(k,\alpha,\beta) \coloneqq \beta + \left[ (\alpha-1) + \sum_{j=0}^{k-1} 8^{2j}\binom{r}{2j} \right]9^s,
+\end{equation}
+so that $i=1,2,\dots, \frac{1}{2}9^s(7^{r} + 9^{r})$.
+The $\frac{r}{2}$ elbows correspond to 
+\begin{equation}
+	i(k, \alpha, \beta) = i(\kappa, m_{\kappa}, 9^s) \equiv \sum_{j=0}^{\kappa} m_j,\ \kappa = 0,\dots,\frac{r}{2}.
+\end{equation}
 This index function is bijective.
@@
 \begin{equation}\label{eq:su_conversion}
-    \noisysn \xrightarrow{\mathcal{O}_{\id/d}} \rho_{\rm{S}}(m, \epsilon', s).
+    \noisysn \xrightarrow{\mathcal{O}_{\id/d}} \rho_{\rm{S}}(r, \epsilon', s),\ n = r + s.
 \end{equation}
@@
 \begin{align}
-    i(k, \alpha) &= (\alpha-1) + \sum_{j=0}^{k-1} 8^{n-2j}\binom{n}{2j}, \\
-    i'(k',\alpha',\beta') &= \beta' + \left[ (\alpha'-1) + \sum_{j'=0}^{k'-1} 8^{m-2j'}\binom{m}{2j'} \right]9^s,
-\end{align}
-
-The question is: \emph{Given a triplet $(k', \alpha', \beta')$, what is the tuple $(k, \alpha)$ such that $i(k, \alpha) = i'(k',\alpha',\beta')$?}
+    i(k, \alpha) &= 1 + (\alpha-1) + \sum_{j=0}^{k-1} 8^{2j}\binom{n}{2j}, \\
+    i'(k',\alpha',\beta') &= \beta' + \left[ (\alpha'-1) + \sum_{j'=0}^{k'-1} 8^{2j'}\binom{r}{2j'} \right]9^s,
+\end{align}
+for $i,i' = 1,2,\dots, \frac{1}{2}(7^{n} + 9^{n})$.
+
+We need $x_{i(k, \alpha)} = x_{i'(k', \alpha', \beta')}$, so the question is: \emph{Given a triplet $(k', \alpha', \beta')$, what is the tuple $(k, \alpha)$ such that $i(k, \alpha) = i'(k',\alpha',\beta')$?}
+
+In other words, we choose a fixed $i'(k',\alpha',\beta')$ and we are searching for $i(k, \alpha)$ such that 
+\begin{equation}
+	i(k, \alpha) \equiv \alpha + \sum_{j=0}^{k-1} 8^{2j}\binom{n}{2j} = i'(k',\alpha',\beta').
+\end{equation}
+
+As an example, consider the process 
+\begin{equation}
+\rho_{\rm{S}}(\epsilon)^{\otimes 4} \xrightarrow{\mathcal{O}_{\id/d}} \rho_{\rm{S}}(\epsilon')^{\otimes 2} \otimes \left( \frac{1}{3}\id \right)^{\otimes 2}.
+\end{equation}
+We want to check which Lorenz curve is higher at the first two elbows of the target state, i.e. we want to verify or reject the inequalities
+\begin{align}
+	L_{i(k_0, \alpha_0)} &\geq L_{i'(0, 1, 81)}, \\
+	L_{i(k_1, \alpha_1)} &\geq L_{i'(1, 64, 81)},
+\end{align}
+where the first two multiplicities of the target state are $1$ and $64$.
+The challenge is to find $k_0, \alpha_0$ such that $i(k_0, \alpha_0) = i'(0,1,81)$ and $k_1, \alpha_1$ such that $i(k_1, \alpha_1) = i'(1,64,81)$
 
@@
 
-	Let $k$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ and $T \coloneqq \{x_0, x_1, \dots, x_k, x_{k+1} \}$ be the $x$-coordinates of the elbows with $x_0 = 0$ and $x_{k+1} = 1$.
-
-	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_j) \geq \lc{\tau}{\sigma}(x_j)$ for all $j =1,\dots,k$.
+	Let $r$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ and $T \coloneqq \{x_0, x_1, \dots, x_r, x_{r+1} \}$ be the $x$-coordinates of the elbows with $x_0 = 0$ and $x_{r+1} = 1$.
+
+	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_j) \geq \lc{\tau}{\sigma}(x_j)$ for all $j =1,\dots,r$.
 \end{theorem}
 \begin{proof}	
-	$\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ trivially implies $\lc{\rho}{\sigma}(x_k) \geq \lc{\tau}{\sigma}(x_k)$ for all $k =0,\dots,n+1$.
-
-	Conversely, assume that $\lc{\rho}{\sigma}(x_j) \geq \lc{\tau}{\sigma}(x_j)$ for all $j =1,\dots,k$.
-	First, note that $\lc{\rho}{\sigma}(x_0) = \lc{\tau}{\sigma}(x_0) = 0$ and $\lc{\rho}{\sigma}(x_{k+1}) = \lc{\tau}{\sigma}(x_{k+1}) = 1$.
+	$\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ trivially implies $\lc{\rho}{\sigma}(x_j) \geq \lc{\tau}{\sigma}(x_j)$ for all $j =1,\dots,r$.
+
+	Conversely, assume that $\lc{\rho}{\sigma}(x_j) \geq \lc{\tau}{\sigma}(x_j)$ for all $j =1,\dots,r$.
+	First, note that $\lc{\rho}{\sigma}(x_0) = \lc{\tau}{\sigma}(x_0) = 0$ and $\lc{\rho}{\sigma}(x_{r+1}) = \lc{\tau}{\sigma}(x_{r+1}) = 1$.
 
@@
 	Due to concavity of $\lc{\rho}{\sigma}$, it is clear that for all $x \in [x_i, x_{i+1}]$, we have $\lc{\rho}{\sigma}(x) \geq \ell_\rho(x) \geq \ell_\tau(x) = \lc{\tau}{\sigma}(x)$.
-	This argument can be made in all intervals $[x_i, x_{i+1}]$ with $i=0,\dots,k$, so the proof is complete.
+	This argument can be made in all intervals $[x_i, x_{i+1}]$ with $i=0,\dots,r$, so the proof is complete.
 \end{proof}
 
-Returning to~\cref{eq:su_conversion}, the $k$ independent necessary constraints are
-\begin{align}
-\lc{\noisysn}{\frac{1}{d}\id}(x_{1,0,0}) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x_{1,0,0}), \nonumber\\
-\lc{\noisysn}{\frac{1}{d}\id}(x_{2,0,0}) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x_{2,0,0}), \nonumber\\
+Returning to~\cref{eq:su_conversion}, the $r$ independent necessary constraints are
+\begin{align}
+\lc{\noisysn}{\frac{1}{d}\id}\left(x_{(0, m'_{0}, 9^{s})}\right) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}\left(x_{(0, m'_{0}, 9^{s})}\right), \nonumber\\
+\lc{\noisysn}{\frac{1}{d}\id}\left(x_{(1, m'_{1}, 9^{s})}\right) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}\left(x_{(1, m'_{1}, 9^{s})}\right), \nonumber\\
 &\vdotswithin{=} \nonumber\\
-\lc{\noisysn}{\frac{1}{d}\id}(x_{m,0,0}) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x_{m,0,0}), \nonumber
-\end{align}
-where $x_{1,0,0}, x_{2,0,0}, \dots, x_{m,0,0} \in T \subset X$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).
+\lc{\noisysn}{\frac{1}{d}\id}\left(x_{(r, m'_{r}, 9^{s})}\right) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}\left(x_{(r, m'_{r}, 9^{s})}\right), \nonumber
+\end{align}
+where $x_{(0, m'_{0}, 9^{s'})}, x_{(1, m'_{1}, 9^{s'})}, \dots, x_{(r, m'_{r}, 9^{s'})} \in T \subset X$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes r}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).
+
+\null\newpage
+\null\newpage
 

### 2020-11-20 magic_paper.tex
Distillation bound example

@@
 \begin{align}
-    x_{k,\alpha, \beta} &= \left( 1-p_{k,\alpha, \beta}\right) x_{k-1} + p_{k,\alpha, \beta} x_k \\
-    L_{k,\alpha, \beta} &= \left( 1-p_{k,\alpha, \beta} \right) L_{k-1} + p_{k,\alpha, \beta} L_k, \\
+    x_{k,\alpha, \beta} &= \left( 1-p_{k,\alpha, \beta}\right) x_{k-1} + p_{k,\alpha, \beta} x_k \label{eq:lcsu_xcoord}\\
+    L_{k,\alpha, \beta} &= \left( 1-p_{k,\alpha, \beta} \right) L_{k-1} + p_{k,\alpha, \beta} L_k, \label{eq:lcsu_lcoord}\\
     &\text{where } p(k, \alpha, \beta) = \frac{(\alpha-1)9^s + \beta}{9^s m_k} \\
@@
 \end{equation}
-This index function is bijective.
+This index function is bijective, i.e.
+\begin{equation}
+	(k, \alpha, \beta) = (k', \alpha', \beta') \Leftrightarrow i(k, \alpha, \beta) = i(k', \alpha', \beta').
+\end{equation}
 
@@
 \end{equation}
-In order to get Lorenz curve constraints on this state conversion, we need to match up the indices for the two states.
+In order to get Lorenz curve constraints on this state conversion, we need a method to match up indices between the two curves.
 We use non-primed indices for the initial state and primed indices for the target state,
 \begin{align}
-    i(k, \alpha) &= 1 + (\alpha-1) + \sum_{j=0}^{k-1} 8^{2j}\binom{n}{2j}, \\
+    i(k, \alpha, \beta=1) &= 1 + (\alpha-1) + \sum_{j=0}^{k-1} 8^{2j}\binom{n}{2j}, \\
     i'(k',\alpha',\beta') &= \beta' + \left[ (\alpha'-1) + \sum_{j'=0}^{k'-1} 8^{2j'}\binom{r}{2j'} \right]9^s,
@@
 
-We need $x_{i(k, \alpha)} = x_{i'(k', \alpha', \beta')}$, so the question is: \emph{Given a triplet $(k', \alpha', \beta')$, what is the tuple $(k, \alpha)$ such that $i(k, \alpha) = i'(k',\alpha',\beta')$?}
+For pointwise comparison of the two curves, we require $x_{i(k, \alpha)} = x_{i'(k', \alpha', \beta')}$, so the question is: \emph{Given a triplet $(k', \alpha', \beta')$, what is the tuple $(k, \alpha)$ such that $i(k, \alpha) = i'(k',\alpha',\beta')$?}
 
@@
 \begin{equation}
-	i(k, \alpha) \equiv \alpha + \sum_{j=0}^{k-1} 8^{2j}\binom{n}{2j} = i'(k',\alpha',\beta').
-\end{equation}
-
-As an example, consider the process 
+	i(k, \alpha) = \alpha + \sum_{j=0}^{k-1} 8^{2j}\binom{n}{2j} \overset{!}{=} i'(k',\alpha',\beta').
+\end{equation}
+
+As a basic example, consider the process 
 \begin{equation}
@@
 \end{equation}
-We want to check which Lorenz curve is higher at the first two elbows of the target state, i.e. we want to verify or reject the inequalities
-\begin{align}
-	L_{i(k_0, \alpha_0)} &\geq L_{i'(0, 1, 81)}, \\
-	L_{i(k_1, \alpha_1)} &\geq L_{i'(1, 64, 81)},
-\end{align}
-where the first two multiplicities of the target state are $1$ and $64$.
-The challenge is to find $k_0, \alpha_0$ such that $i(k_0, \alpha_0) = i'(0,1,81)$ and $k_1, \alpha_1$ such that $i(k_1, \alpha_1) = i'(1,64,81)$
+We want to check which Lorenz curve is higher at the first elbows of the target state, i.e. we want to verify or reject the first inequality below:
+\begin{equation}
+	L_{i(k, \alpha)} \geq L'_{i'(0, 1, 81)}
+\end{equation}
+where the first multiplicity of the target state is $m_0 = 1$.
+The multiplicities of the initial state are $(1, 384, 4096)$
+Note that the second elbow of the target state (its maximum) lies on the RHS of the initial state curve's maximum, hence our expressions do not work on the coordinates of the initial state curve at that point \nick{yet}.
+
+The challenge is to find $k, \alpha$ such that $i(k, \alpha) = i'(0,1,81)$.
+\nick{By trial and error}, we find that $(k, \alpha) = (1, 80)$.
+Now we can use~\cref{eq:lcsu_lcoord} to directly calculate
+\begin{align*}
+	L'_{i'(0,1,81)} &= L'_0 = \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^2 \Phi_+\left(0;2,4\frac{3-\epsilon}{15-8\epsilon}\right), \\
+	L_{i(1, 80)} &= \left(1-\frac{80}{384} \right) L_0 + \frac{80}{384} L_1 \\
+	\begin{split}
+	&= \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^4 \bigg[ \frac{19}{24} \Phi_+\left(0;4,4\frac{3-\epsilon}{15-8\epsilon}\right) \\ 
+	&\qquad + \frac{5}{24}\Phi_+\left(2;4,4\frac{3-\epsilon}{15-8\epsilon}\right) \bigg],
+	\end{split}
+\end{align*}
+and then compare them.
 
@@
 \begin{align}
-\lc{\noisysn}{\frac{1}{d}\id}\left(x_{(0, m'_{0}, 9^{s})}\right) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}\left(x_{(0, m'_{0}, 9^{s})}\right), \nonumber\\
-\lc{\noisysn}{\frac{1}{d}\id}\left(x_{(1, m'_{1}, 9^{s})}\right) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}\left(x_{(1, m'_{1}, 9^{s})}\right), \nonumber\\
+\lc{\noisysn}{\frac{1}{d}\id}\left(x_{i'(0, m'_{0}, 9^{s})}\right) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}\left(x_{i'(0, m'_{0}, 9^{s})}\right), \nonumber\\
+\lc{\noisysn}{\frac{1}{d}\id}\left(x_{i'(1, m'_{1}, 9^{s})}\right) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}\left(x_{i'(1, m'_{1}, 9^{s})}\right), \nonumber\\
 &\vdotswithin{=} \nonumber\\
-\lc{\noisysn}{\frac{1}{d}\id}\left(x_{(r, m'_{r}, 9^{s})}\right) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}\left(x_{(r, m'_{r}, 9^{s})}\right), \nonumber
-\end{align}
-where $x_{(0, m'_{0}, 9^{s'})}, x_{(1, m'_{1}, 9^{s'})}, \dots, x_{(r, m'_{r}, 9^{s'})} \in T \subset X$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes r}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).
+\lc{\noisysn}{\frac{1}{d}\id}\left(x_{i'(r, m'_{r}, 9^{s})}\right) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}\left(x_{i'(r, m'_{r}, 9^{s})}\right), \nonumber
+\end{align}
+where $x_{i'(0, m'_{0}, 9^{s'})}, x_{i'(1, m'_{1}, 9^{s'})}, \dots, x_{i'(r, m'_{r}, 9^{s'})} \in T$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon')^{\otimes r}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).
 

### 2020-11-25 appendix.tex
tidying up

@@
 
+\begin{figure}[t]%
+    \centering
+    \subfigure[][]{%
+    \label{fig:test1}%
+    \includegraphics[height=3cm]{figs/negmasking_rho_strange_lc.pdf}
+    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
+    }\hspace{8pt}%
+    \subfigure[][]{%
+    \label{fig:test2}%
+    \includegraphics[height=3cm]{figs/negmasking_rho_strange_meas.pdf}
+    %\caption{Zero state $\ketbra{0}{0}$}%
+    }
+    \caption{\subref{fig:test1} Lorenz curve of $p\ketbra{\rm{S}} + (1-p) \frac{1}{d}\id$ for $p$ given in the legend.\subref{fig:test2} Different measures for the states on the left. \\
+    \nick{can replace~\cref{fig:lctoy} with a more informative version of this figure}
+    }%
+    \label{fig:test}
+\end{figure}
+
 Let $L_{>1}$ be the set of points on the Lorenz curve $\lc{\rho}{\sigma}(k)$ that lie above $1$ of state $\rho$ in the $\sigma$--fragment. 
@@
 
-\begin{figure}%
+\section{Technical derivations for standard Lorenz curves}
+\label{app:lcsu_technical}
+
+\subsubsection{Binomial distributions and error bounds}
+Consider an experiment consisting of $n$ trials of throwing a $p$-coin, that is a coin with probability $p$ of landing on one side and $1-p$ of landing on the other.
+This scenario describes the construction of an $n$-copy Strange state Wigner distribution from a single-copy as presented in~\cref{sec:lcsu}.
+The experiment is described by binomial statistics and we write down the sum over an even number of successful trials $\Phi_+$ (over an odd number of successful trials $\Phi_-$),
+\begin{align}	
+	\Phi_+(m; n, p) &\coloneqq \sum\limits_{j=0}^{m/2} \binom{n}{2j} p^{2j} (1-p)^{n-2j}, \nonumber\\ 
+	&\text{for even integers } m\in[0,n], \label{eq:fp} \\
+	\Phi_-(m; n, p) &\coloneqq \sum\limits_{j=1}^{(m-1)/2} \binom{n}{2j+1} p^{2j+1} (1-p)^{n-(2j+1)}, \nonumber\\ 
+	&\text{for odd integers } m\in[0,n]. \label{eq:fn2}
+\end{align}
+Note that index $m$ only takes even (odd) values when labelling $\Phi_+$ ($\Phi_-$).
+$\Phi_+$ describes the elbow coordinates on the LHS of the curve maximum, including the maximum, while $\Phi_-$.
+
+We define the classical relative entropy between a $p$-coin and a $q$-coin as
+\begin{equation}\label{eq:ent_rel}
+	\ent{p}{q} \coloneqq p \log{\frac{p}{q}} + (1-p) \log{\frac{1-p}{1-q}}.
+\end{equation}
+It satisfies the identity $\ent{p}{q} = \ent{1-p}{1-q}$.
+
+The classical entropy of a $p$-coin is
+\begin{equation}\label{eq:ent}
+	S(p) \coloneqq -p\log{p} -(1-p)\log{(1-p)},
+\end{equation}
+which is symmetric, $S(p) = S(1-p)$.
+%Let $c(m; n) \coloneqq [m(1-m/n)]^{-1/2},\ m\in [1, n-1]$.
+A useful result is the entropic bound on a combination~\cite{cit:ash}.
+\begin{lemma}\label{lem:comb_bounds}
+	For all $m\in [1,n-1]$,
+	\begin{align}
+		&\left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{nS\left(\frac{m}{n}\right)} \leq \binom{n}{m} \leq \\
+		&\left[ 2\pi m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{nS\left(\frac{m}{n}\right)}.
+	\end{align}
+\end{lemma}
+\begin{proof}
+	For $m = 1,2, n-1, n-2$ check by direct calculation.	
+	For all other cases, use Stirling's approximation.
+\end{proof}
+
+Bounds on the tails of a cumulative binomial distribution can be expressed in
+
+and therefore we can use $\Phi_{\pm}$ to compactify statements that hold for both $\Phi_+, \Phi_-$.
+
+\iffalse
+The experiment is described by binomial statistics and we define the left tail of the cumulative binomial distribution,
+\begin{equation}\label{eq:phil}
+	\Phi_\ell(m; n, p) \coloneqq \sum\limits_{j=0}^m \binom{n}{j} p^j (1-p)^{n-j},
+\end{equation}
+where $m\in [0,n]$.
+
+The symmetry between the left tail of a $p$-coin distribution and the right tail of a $(1-p)$-coin distribution dictates that
+\begin{align}\label{eq:phi_reverse}
+	\Phi_\ell(m; n, p) + \Phi_\ell(n-m-1; n, 1-p) &= 1,\ m\in [0,n-1],
+\end{align}
+Entropic bounds on $\Phi_\ell$~\cite{cit:ash}.
+\begin{lemma}\label{lem:phil_bounds}
+	Given fixed $n>0$ and $p$, $\Phi_\ell$ satisfies the following bounds:
+	\begin{align*}
+		\begin{split}
+		&\text{1. } \Phi_\ell(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ents},\ m\in [1,n-1] \\
+		&\text{2. } \Phi_\ell(m; n, p) \leq 2^{-n\ents},\ m\in [0,np] \\
+		&\text{3. } \Phi_\ell(m; n, p) \leq 1 - \left[ 8(m+1)\left(1-\frac{m+1}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m+1}{n}}{p}}, \\
+		&\hspace{14pt} m\in [0,n-2]
+		\end{split}
+		\\
+		&\text{4. } \Phi_\ell(m; n, p) \geq 1 - 2^{-n\ent{\frac{m+1}{n}}{p}},\ m\in [np+1,n-2]
+	\end{align*}
+\end{lemma}
+\begin{proof}
+	\nick{cite proof}
+\end{proof}
+
+In particular, we derive ``loose'' and ``strict'' bounds on $\Phi_{\pm}$.
+\begin{lemma}\label{lem:bounds_loose}
+	Given fixed $n>0$ and $p$, $\Phi$ satisfies the following bounds:
+	\begin{align*}
+		\begin{split}
+		&\text{1. } \Phi_{\pm}(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ents},\ m\in [1,n-1] \\
+		&\text{2. } \Phi_{\pm}(m; n, p) \leq 2^{-n\ents},\ m\in [0,np] \\
+		&\text{3. } \Phi_{\pm}(m; n, p) \leq 1 - \left[ 8(m+1)\left(1-\frac{m+1}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m+1}{n}}{p}}, \\
+		&\hspace{14pt} m\in [0,n-2]
+		\end{split}
+	\end{align*}
+\end{lemma}
+\begin{proof}
+	\nick{paste proof}
+\end{proof}
+\begin{lemma}\label{lem:bounds_strict}
+	Given fixed $n>0$ and $p$, $\Phi_+, \Phi_-$ satisfy the following bounds:
+	\begin{align*}
+		\begin{split}
+		&\text{1. } \Phi_+(m; n, p) \geq \sum\limits_{j=0}^{m/2}\left[ 8(2j)\left(1-\frac{2j}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{2j}{n}}{p}}, \\
+		&\hspace{14pt} \text{for all even } m\in [2,n] \\
+		&\text{2. } \Phi_+(m; n, p) \leq \sum\limits_{j=0}^{m/2}\left[ 2\pi(2j)\left(1-\frac{2j}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{2j}{n}}{p}}, \\
+		&\hspace{14pt} \text{for all even } m\in [2,n] \\
+		&\text{3. } \Phi_-(m; n, p) \geq \sum\limits_{j=1}^{(m-1)/2}\left[ 8(2j+1)\left(1-\frac{2j+1}{n}\right) \right]^{-\frac{1}{2}} \times \\
+		&\hspace{14pt} \times 2^{-n\ent{\frac{2j+1}{n}}{p}},\ \text{for all odd } m\in [1,n] \\
+		&\text{4. } \Phi_-(m; n, p) \leq \sum\limits_{j=1}^{(m-1)/2}\left[ 2\pi(2j+1)\left(1-\frac{2j+1}{n}\right) \right]^{-\frac{1}{2}} \times \\
+		&\hspace{14pt} \times 2^{-n\ent{\frac{2j+1}{n}}{p}},\ \text{for all odd } m\in [1,n]
+		\end{split}
+	\end{align*}
+\end{lemma}
+\begin{proof}
+	\nick{paste proof}
+\end{proof}
+\fi
+
+They are depicted in~\cref{fig:noisys}.
+\begin{figure}[t]
     \centering
-    \subfigure[][]{%
-    \label{fig:test1}%
-    \includegraphics[height=3cm]{figs/negmasking_rho_strange_lc.pdf}
-    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
-    }\hspace{8pt}%
-    \subfigure[][]{%
-    \label{fig:test2}%
-    \includegraphics[height=3cm]{figs/negmasking_rho_strange_meas.pdf}
-    %\caption{Zero state $\ketbra{0}{0}$}%
+    \includegraphics[scale=0.7]{figs/noisys.pdf}
+    \caption{\textbf{Wigner components of the noisy Strange state.} 
+    In the interval $0 \leq \epsilon < 3/7$, the negative component is larger than the positive components.
+    At $\epsilon = 3/7$ the Wigner distribution is $(-\frac{1}{7},\frac{1}{7},\dots,\frac{1}{7})$.
+    In the interval $3/7 < \epsilon < 3/4$, the positive components are larger than the negative component.
+    In the interval $3/4 \leq \epsilon \leq 1$, there is no negativity.
     }
-    \caption{\subref{fig:test1} Lorenz curve of $p\ketbra{\rm{S}} + (1-p) \frac{1}{d}\id$ for $p$ given in the legend.\subref{fig:test2} Different measures for the states on the left. \\
-    \nick{can replace~\cref{fig:lctoy} with a more informative version of this figure}
-    }%
-    \label{fig:test}
+    \label{fig:noisys}
 \end{figure}
+The $n+1$ distinct Wigner components ($w_j$) of $\noisysn$ along with their multiplicities ($m_j$) are given in~\cref{tab:lcsu_w}.
+\begin{table}[b]                           
+ \centering
+ \begin{tabular}{c|c|c|c}
+ $\epsilon$ & $j$ & $\left[0, \frac{n}{2}\right]$ & $\left[\frac{n}{2} + 1, n \right]$ \\ [0.5ex] 
+ \hline
+  & $w_{j}$ & $w_+^{2j}w_-^{n-2j}$ & $w_+^{n-2j}w_-^{2j}$  \\
+  $0\leq \epsilon < \frac{3}{7}$ & & & \\
+  & $m_{j}$ & $8^{2j}\binom{n}{2j}$ & $8^{n-2j}\binom{n}{2j}$ \\
+ \hline
+  & $w_{j}$ & $w_+^{n-2j}w_-^{2j}$ & $w_+^{2j}w_-^{n-2j}$  \\
+  $\frac{3}{7} \leq \epsilon < \frac{3}{4} $ & & & \\
+  & $m_{j}$ & $8^{n-2j}\binom{n}{2j}$ & $8^{2j}\binom{n}{2j}$
+\end{tabular}
+ \caption{Wigner components of $\noisysn$. The multiplication $2j$ is modulo $(n+1)$.}
+ \label{tab:lcsu_w}
+\end{table}
+
+To get the Lorenz curve, we need to sum up the Wigner components in decreasing order and the order depends on the noise level $\epsilon$, so we define probabilities associated with the $x$-coordinate ($p_x$) and the vertical coordinate ($p_L$) of the Lorenz curve accordingly,
+\begin{equation}
+	(p_x, p_L) \equiv \big( p_x(\epsilon), p_L(\epsilon) \big) = 
+	\begin{cases}
+		\left( \frac{8}{9}, \frac{12-4\epsilon}{15-8\epsilon} \right),\ & 0\leq \epsilon < \frac{3}{7} \\
+		\left( \frac{1}{9}, \frac{3-4\epsilon}{15-8\epsilon} \right),\ & \frac{3}{7}\leq \epsilon < \frac{3}{4} \\
+	\end{cases}	
+\end{equation}
+
+We are now in a position to express Lorenz curve coordinates in terms of phi distributions,
+\begin{equation}\label{eq:x_coord_elb}
+	x_k(n, \epsilon) = 
+	\begin{cases}
+		\Phi_+(k;n,p_x),\\
+		\hspace{20pt} k\in[0,n]\ \text{and }k\text{ even}, \\
+		x_{k_\star} + \Phi_-(k;n,1-p_x),\\
+		\hspace{20pt} k\in[0,n]\ \text{and }k\text{ odd}, \\
+	\end{cases}	
+\end{equation}
+and
+\begin{equation}\label{eq:lc_coord_elb}
+	L_k(n, \epsilon) = 
+	\begin{cases}
+		\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+(k;n,p_L),\\
+		\hspace{20pt} k\in[0,n]\ \text{and }k\text{ even}, \\
+		L_{k_\star} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-(k;n,1-p_L),\\
+		\hspace{20pt} k\in[0,n]\ \text{and }k\text{ odd}. \\
+	\end{cases}	
+\end{equation}
+
+Finally, the $m$-th elbow is located at
+\begin{equation}\label{eq:lcsu_elbows}
+	\left(x_m, \lc{\noisysn}{\frac{1}{d}\id}(x_m) \right) = \Big( x_{2m}(n, \epsilon), L_{2m}(n, \epsilon) \Big),
+\end{equation}
+where $2m$ is considered \hspace{-7pt}$\mod{(n+1)}$.
+
+We can therefore use~\cref{lem:bounds_loose,lem:bounds_strict} to bound the standard Lorenz curves.
+\begin{figure}[b]
+    \centering
+    \includegraphics[scale=0.4]{figs/lc_bounds.pdf}
+    \caption{\textbf{Lorenz curves and bounding curves.} 
+    The figure explores the distillation process of a 10-copy $0.25$-noisy Strange state to a 4-copy $0.05$-noisy Strange state in the unital fragment.
+    Clearly, by looking at the Lorenz curves, the distillation process is possible.
+    However the bounding curves, derived in~\cref{lem:bounds_strict}, intersect at the end, suggesting that the process is not necessarily possible.
+    }
+    \label{fig:lc_bounds}
+\end{figure}
+
+Assume: 
+\begin{itemize}
+    \item $n$ is even [ensures Lorenz curve coordinates can be expressed in terms of $\Phi_{\pm}$ distributions];
+    \item $0 \leq \epsilon \leq \frac{3}{7}$ [ensures closed-form expressions for Lorenz curve coordinates];
+\end{itemize}
+There are $\frac{n}{2}+1$ distinct non-negative components in the Wigner distribution $\W{\noisysn}$.\\
+
+We can rewrite the non-negative part of the Wigner distribution $\W{\noisysn}$ in a compact form, by simply listing the distinct Wigner components $w(k; n, \epsilon)$ along with their multiplicities $m(k; n)$:
+\begin{align}
+    &{\W{\noisysn}} = \\ 
+    &\big\{\left( m_k, w_k \right)\big\}_{k=0,\dots,n/2} = \nonumber\\ 
+    &\big\{\left( m(k; n), w(k; n, \epsilon) \right)\big\}_{k=0,\dots,n/2} = \nonumber\\
+    &\left\{ \left( 8^{2k}\binom{n}{2k}, \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2k}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{n-2k} \right) \right\}_{k=0,\dots,n/2}. \nonumber
+\end{align}
+
+The expressions for the Lorenz curve elbows in the unital fragment are then known:
+\begin{align}
+    &{\rm{L}_{\noisysn}} = \\
+    &\big\{\left( x_k, L_k \right)\big\}_{k=0,\dots,n/2} = \nonumber\\
+    &\big\{\left( x(k; n), L(k; n, \epsilon) \right)\big\}_{k=0,\dots,n/2} = \nonumber\\
+    &\left\{ \left( \frac{1}{9^n}\sum\limits_{j=0}^k m_j, \sum\limits_{j=0}^k m_j w_j \right) \right\}_{k=0,\dots,n/2} = \nonumber\\
+    &\left\{ \left( \Phi_+\left(2k;n,\frac{8}{9}\right), \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+\left(2k;n,4\frac{3-\epsilon}{15-8\epsilon}\right) \right) \right\}_{k=0,\dots,n/2}.
+\nonumber
+\end{align}
+We include the origin in the Lorenz curve as it does not arise from the above expressions, denoting it by $(x_{-1}, L_{-1}) \coloneqq (0,0)$.
+
+We can get explicit expressions for all $\frac{1}{2}(7^n + 9^n)$ points of the Lorenz curve, using a two-index parameterisation:
+\begin{align}
+    x_{k,\alpha} &= \left( 1-\frac{\alpha}{m_k} \right) x_{k-1} + \frac{\alpha}{m_k} x_k \label{eq:x}\\
+    L_{k,\alpha} &= \left( 1-\frac{\alpha}{m_k} \right) L_{k-1} + \frac{\alpha}{m_k} L_k \label{eq:l}\\
+    &\text{for } k=0,\dots,\frac{n}{2} \text{ and } \alpha = 1,\dots,m_k. \nonumber
+\end{align}
+
+As a simple example, we plot the Lorenz curve of state $\noisys(0)\too{2}$,
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.6]{figs/lcpoints.pdf}
+    \caption{\textbf{All points on the Lorenz curve are uniformly distributed.}
+    \cref{eq:x,eq:l}) capture the coordinates of all points up to the maximum.
+    }
+    \label{fig:lc}
+\end{figure}
+
+Consider now the state 
+\begin{equation}
+    \noisys(r, \epsilon, s) = \noisys(\epsilon)\too{r} \otimes \left( \frac{1}{3}\id \right)\too{s}.
+\end{equation}
+
+Tensoring with the maximally mixed state keeps the Lorenz curve unchanged, but increases the resolution of (the uniformly distributed) points.
+The new point coordinates are given by:
+\begin{align}
+    x_{k,\alpha, \beta} &= \left( 1-p_{k,\alpha, \beta}\right) x_{k-1} + p_{k,\alpha, \beta} x_k \label{eq:lcsu_xcoord}\\
+    L_{k,\alpha, \beta} &= \left( 1-p_{k,\alpha, \beta} \right) L_{k-1} + p_{k,\alpha, \beta} L_k, \label{eq:lcsu_lcoord}\\
+    &\text{where } p(k, \alpha, \beta) = \frac{(\alpha-1)9^s + \beta}{9^s m_k} \\
+    &\text{for } k=0,\dots,\frac{r}{2},\ \alpha = 1,\dots,m_k \text{ and } \beta = 1,\dots,9^s. \nonumber
+\end{align}
+
+We can unify the indices, by introducing a single index
+\begin{equation}
+    i(k,\alpha,\beta) \coloneqq \beta + \left[ (\alpha-1) + \sum_{j=0}^{k-1} 8^{2j}\binom{r}{2j} \right]9^s,
+\end{equation}
+so that $i=1,2,\dots, \frac{1}{2}9^s(7^{r} + 9^{r})$.
+The $\frac{r}{2}$ elbows correspond to 
+\begin{equation}
+	i(k, \alpha, \beta) = i(\kappa, m_{\kappa}, 9^s) \equiv \sum_{j=0}^{\kappa} m_j,\ \kappa = 0,\dots,\frac{r}{2}.
+\end{equation}
+This index function is bijective, i.e.
+\begin{equation}
+	(k, \alpha, \beta) = (k', \alpha', \beta') \Leftrightarrow i(k, \alpha, \beta) = i(k', \alpha', \beta').
+\end{equation}

### 2020-11-25 magic_paper.tex
tidying up

@@
 Monotones are often used \nick{CITE} to address the question of state convertibility, although such approaches are usually generic.
+We highlight the defining property of a monotone here, as it is useful in several sections that follow.
+\begin{definition}[\textbf{Resource monotone}]\label{def:mono}
+    Let $\R = (\F, \O)$ be a resource theory.
+    A resource monotone $\M$ is a projection from the set of quantum states of the theory onto the real line, so that $\M$ is monotonically decreasing under free operations,
+    \begin{equation}
+        \M(\rho_1) \leq \M(\rho_2)\ \text{whenever}\ \rho_1 \prec_{\R} \rho_2.
+    \end{equation}
+\end{definition}
+The monotonicity condition reflects the no resource generating property of free operations, so that monotones respect the pre-order $\prec_\R$ of the theory.
 A monotone of any general resource theory is a projection of the theory onto the non-negative real numbers, collapsing the pre-order of the theory to the total order defined on the real line.
-This is the \nick{most naive} non-trivial projection under which the images of incomparable states can be compared.
-Our first contribution is the introduction of a generalised notion of \emph{resource projection} which maps a general resource theory onto a subtheory which in principle still retains a partial structure.
+Our contribution is the introduction of a generalised notion of \emph{resource projection} which maps a general resource theory onto a subtheory which in principle still retains a partial structure (as opposed to the real line).
 Applying this notion on existing magic theories highlights the hidden stochasticity that governs magic state conversions.
@@
     \subref{fig:maxmix} Maximally mixed state $\frac{1}{3}\id$; \subref{fig:zero} Stabilizer zero state $\ketbra{0}{0}$; \subref{fig:bound} A non-stabilizer Wigner-positive state; \subref{fig:strange} Magic strange state $\ket{{\rm{S}}} = \frac{1}{\sqrt{2}}(\ket{1} - \ket{2})$ \nick{CITE}.
-    \nick{Explain what a magic / bound magic state is in intro}
+    \nick{Explain what a magic state is in intro}
     }%
@@
 \begin{theorem}\label{thm:sigmamajor}
-    Let $\R = (\F, \O)$ be a theory of magic. Then $\rho \longrightarrow \tau$ is possible iff  $\W{\tau} \prec_\sigma \W{\rho}$ within a $\sigma$--fragment.
-    \nick{I understand that dropping the full-rank assumption on $\sigma$ makes the statement a lot stronger, but also incorrect e.g.
-in the case of the replacement channel $\E(\rho) = \ketbra{0}$, since $d$-majorization in $\O_{\ketbra{0}}$ is not well-defined.}
+    Let $\R = (\F, \O)$ be a theory of magic. Then $\rho \longrightarrow \tau$ is possible \nick{only if}  $\W{\tau} \prec_\sigma \W{\rho}$ within a $\sigma$--fragment.
 \end{theorem}
@@
 Therefore, the Wigner distribution of this free operation satisfies $\W{\E} \in \stochw$ and $\W{\E}\W{\rho} = \W{\tau}$. 
-Since $\sigma$ is full-rank and free, its Wigner distribution is strictly positive in all components, so it directly follows from~\cref{def:dmajor} that $\W{\tau} \prec_{\sigma} \W{\rho}$.
+Since $\sigma$ is \nick{full-rank} and free, its Wigner distribution is strictly positive in all components, so it directly follows from~\cref{def:dmajor} that $\W{\tau} \prec_{\sigma} \W{\rho}$.
 \end{proof}
@@
 Furthermore, a Lorenz curve $\lc{\bmz}{\bmd}(x)$ is always concave in $x$, since it consists of $d$ line segments each with slope $(\tilde{\bmz}^\downarrow)_i$ for $i=1,\dots,d$ which is non-increasing by definition.
+Finally, points on the interior of the Lorenz curve connecting line segments of different slopes are called \emph{elbows}.
 
@@
 
-\section{Magic state interconversion and Lorenz curves}
+\section{Magic state interconversion and Lorenz curve comparison}
 \label{sec:distill}
@@
 
-\subsection{Mana and majorization in magic theories}\label{sec:scmana}
+\subsection{Majorization in magic theories}\label{sec:scmana}
 We now discuss majorization features common to all fragments, before specialising to particular $\sigma$--fragments and how analysis in them proceeds.
-Mana is the fundamental resource monotone for magic. 
-Here we show that its properties are in fact special cases of more general majorization features. 
-More precisely, its properties can be viewed as majorization-based, and independent of the particular $\sigma$--fragment one works in.
 
@@
 
-Consider a general magic state interconversion in $\O_\sigma$, $\rho \xrightarrow{\E \in \O_\sigma} \tau$.
-It is shown in~\cref{app:major} that mana is an additive monotone in every $\sigma$--fragment under $d$--majorization, so it provides a necessary condition for the process to be possible,
-\begin{equation}\label{eq:manabound}
-    \mana{\rho} \geq \mana{\tau}. %{\rm{C}}_{\rm{mana}}(\rho, \tau, \sigma):\ 
-\end{equation}
-A new bound can be obtained in the $\sigma$--fragment by comparing the Lorenz curves of the initial and target states,
+Consider a general magic state interconversion in $\O_\sigma$, 
+\begin{equation}
+	\rho \xrightarrow{\E \in \O_\sigma} \tau.
+\end{equation}
+
+Magic theories utilise monotone bounds of the form
+\begin{equation}\label{eq:majbound}
+    \M(\rho) \geq \M(\tau),
+\end{equation}
+to determine whether the interconversion is allowed.
+Monotone bounds hold independently of $\sigma$--fragments, therefore they provide no understanding with regard to the type of operations that allow the interconversion.
+
+New bounds can be obtained in the $\sigma$--fragment by pointwise Lorenz curve comparison of the initial and target states,
 \begin{equation}\label{eq:majbound}
@@
 \end{equation}
-If one of these consitions is not satisfied, then the Lorenz curve of initial state $\rho$ is below the curve of target $\tau$ at some point $x$ and the conversion is not possible.
-
-In fact, our current setting makes it apparent that the mana condition is always weaker than the majorization condition for all magic state interconversions.
-
-We first show that the maximum of $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment and directly related to the state sum-negativity $\sn{\rho}$ discussed in~\cref{sec:mono}
+This inequality is parametrised by $x$ and if it is not satisfied at any point $x$, then the Lorenz curves intersect and the conversion is impossible.
+
+We can reduce the number of independent constraints stemming from this inequality down to the number of elbows of the target state.
+\begin{theorem}\label{thm:elbows}
+	Let $\rho, \tau$ be two quantum states with Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in the $\sigma$-fragment.
+
+	Let $r$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ and $E \coloneqq \{x_1, \dots, x_\kk\}$ be their locations.
+
+	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_j) \geq \lc{\tau}{\sigma}(x_j)$ for all $j =1,\dots,\kk$.
+\end{theorem}
+\begin{proof}	
+	$\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ trivially implies $\lc{\rho}{\sigma}(x_j) \geq \lc{\tau}{\sigma}(x_j)$ for all $j =1,\dots,\kk$.
+
+	Conversely, assume that $\lc{\rho}{\sigma}(x_j) \geq \lc{\tau}{\sigma}(x_j)$ for all $j =1,\dots,r$.
+	First, let $x_0 = 0$ and $x_{\kk+1} = 1$, so that $\lc{\rho}{\sigma}(x_0) = \lc{\tau}{\sigma}(x_0) = 0$ and $\lc{\rho}{\sigma}(x_{\kk+1}) = \lc{\tau}{\sigma}(x_{\kk+1}) = 1$.
+	Hence, we can extend the set of elbows $E$ to $E' = E \cup \{x_0, x_{\kk+1}\}$.
+
+	Pick two consecutive locations $x_i, x_{i+1}$ in $E'$ and consider the line segment $\ell_\tau(x)$ connecting points $(x_i, \lc{\tau}{\sigma}(x_i))$ and $(x_{i+1}, \lc{\tau}{\sigma}(x_{i+1}))$ as well as the line segment $\ell_\rho(x)$ connecting points $(x_i, \lc{\rho}{\sigma}(x_i))$ and $(x_{i+1}, \lc{\rho}{\sigma}(x_{i+1}))$.
+	This is illustrated in~\cref{fig:elbows_proof}.
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.6]{figs/elbows_proof.pdf}
+    \caption{\textbf{Illustration of~\cref{thm:elbows}}.
+    }
+    \label{fig:elbows_proof}
+\end{figure}
+
+	Due to concavity of $\lc{\rho}{\sigma}$, it is clear that for all $x \in [x_i, x_{i+1}]$, we have $\lc{\rho}{\sigma}(x) \geq \ell_\rho(x) \geq \ell_\tau(x) = \lc{\tau}{\sigma}(x)$.
+	This argument can be made in all intervals $[x_i, x_{i+1}]$ with $i=0,\dots,\kk$, so the proof is complete.
+\end{proof}
+This theorem is of practical importance in checking Lorenz curve bounds, and it is used in the discussion of standard Lorenz curves in~\cref{sec:lcsu}.
+
+\nick{We can skip mana and just discuss sum-negativity}
+
+One of the most fundamental and commonly used magic monotones is the \emph{mana} of a state \nick{CITE}, defined as
+\begin{equation}
+    \mana{\rho} \coloneqq \log{(2\sn{\rho}+1)},
+\end{equation}
+where the \emph{sum-negativity} ($\rm{sn}$) \nick{CITE} is the sum of the negative components in $\W{\rho}$,
+\begin{equation}
+    \sn{\rho} \coloneqq \sum\limits_{\bmx: \W[\bmx]{\rho} < 0} \abs{\W[\bmx]{\rho}}.
+\end{equation}
+Mana is an additive\footnote{It satisfies the condition $\mana{\rho_1 \otimes \rho_2} = \mana{\rho_1} + \mana{\rho_2}$ which is practical is distillation settings.} magic monotone, so it provides a necessary condition for magic state interconvertibility.
+
+Here, we show that its properties can be viewed as majorization-based, and independent of the particular $\sigma$--fragment one works in.
+In fact, our current setting makes it apparent that the mana provides a weaker condition than majorization for all magic state interconversions.
+
+We first show that the Lorenz curve maximum of state $\rho$ is independent of the $\sigma$--fragment and directly related to its sum-negativity.
 \begin{lemma}\label{lem:lcmax}
@@
 
-	Let $k_\star$ be the index of the smallest non-negative component of $\tilde{\bm{w}}^\downarrow$.
-	Then, $(\W{\rho})_i < 0$ if and only if $i > k_\star$, so the maximum of Lorenz curve $\lc{\rho}{\sigma}(x)$ takes the value 
-	\begin{equation}
-		\lc{\rho}{\sigma}(x_{k_\star}) = \sum_{i=1}^{k_\star} (\W{\rho})_i,
+	Let $\jj_\star$ be the index of the smallest non-negative component of $\tilde{\bm{w}}^\downarrow$.
+	Then, $(\W{\rho})_i < 0$ if and only if $i > \jj_\star$, so the maximum of Lorenz curve $\lc{\rho}{\sigma}(x)$ takes the value 
+	\begin{equation}
+		\lc{\rho}{\sigma}(x_{\jj_\star}) = \sum_{i=1}^{\jj_\star} (\W{\rho})_i,
 	\end{equation}
@@
 	\begin{equation}\label{eq:maxloc}
-		x_{k_\star} \coloneqq \sum_{i=1}^{k_\star} (\W{\sigma})_i.
+		x_{\jj_\star} \coloneqq \sum_{i=1}^{\jj_\star} (\W{\sigma})_i.
 	\end{equation}
@@
 
-We can therefore view mana as just one of the features of the Lorenz curve, namely its maximum value. This implies the following result.
+We can therefore view mana as just one feature of the Lorenz curve, namely its maximum value. 
+This implies the following result.
 \begin{theorem}\label{thm:bounds}
@@
     \end{equation}
-    Therefore, the $\W{\sigma}$--majorization bound
+    Therefore, the majorization bound
     \begin{equation}
@@
 
-Of practical importance are magic state distillation (MSD) processes of the form
-\begin{equation}\label{eq:distprocess}
-    \rho^{\otimes n} \xrightarrow{\E \in \O_\sigma} \tau,
-\end{equation}
-where $n$ copies of a noisy magic state $\rho$ are converted into a target single-copy state $\tau$. \nick{expand?}
-
-In general, the Wigner components of a $n$-copy state $\rho^{\otimes n}$ can be calculated directly from $W_\rho$, along with their multiplicities, by expanding the terms in the multinomial expansion $\left( \sum_{\bm{z} \in \cal{P}_d} W_\rho(\bm{z}) \right)^n$.
-\nick{is this clear?}
-This follows from the multiplicativity of the Wigner distribution.
-
-As an example, consider the qutrit Strange state $\ketbra{\rm{S}}$ depicted in~\cref{fig:strange}. 
-It is the simplest non-trivial case to analyse because its Wigner distribution consists of two distinct components.
-Calculating the components of $\ket{S}\bra{S}^{\otimes n}$ allows for analytical calculation of the maximum of the $n$-copy state,
-\begin{equation}\label{eq:Skmax}
-    \max_x{\lc{\ketbra{S}^{\otimes n}} {\sigma}}(x) = \frac{1}{2}\left (1 + \left(\frac{5}{3}\right)^n \right).
-\end{equation}
-Its location $x_{k_\star}$ depends on the $\sigma$--fragment and is given by~\cref{eq:maxloc} with $k_\star = \frac{1}{2}(7^n + 9^n)$.
-%1 + \left(\frac{4}{3}\right)^n \sum\limits_{j=0}^{\floor{\frac{n-1}{2}}} 4^{-(2j+1)} \binom{n}{2j+1}
-%\sum_{i=j, j: odd}^n a^j \binom{n}{j} = \frac{1}{2} [ (1+a)^n - (1-a)^n ]
-%$\{(-1)^j 2^{j-n} 3^{-n}\}_{0 \leq j \leq n}$ with multiplicity $8^{n-j} \binom{n}{j}$ for the $j$-th term
-
-Consider the problem of purifying out magic from a noisy Strange state,
-\begin{equation}
-    \rho_{\rm{S}}(\epsilon) = (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \sigma,
-\end{equation}
-in $\O_\sigma$.
-At noise levels $\epsilon \geq \frac{3}{4}$, the state is sufficiently noisy so as the Wigner distribution $\W{\rho_{\rm{S}}(\epsilon)}$ no longer contains negativities. 
-At any $\epsilon \leq \frac{3}{4}$, we can investigate the distillation process resulting in a single-copy state with sufficiently low target $\epsilon_{\tau}$,
-\begin{equation}\label{eq:sdist}
-	\noisysn \xrightarrow{\E \in \O_\sigma} \rho_{\rm{S}}(\epsilon_{\tau})
-\end{equation}
-
-The more noisy the initial state is, the more copies needed to reach the target, therefore it makes sense to define a noise level threshold 
+Denote an $n$-copy, $\epsilon$-noisy magic state $\rho$ in the $\sigma$--fragment by
+\begin{equation}\label{eq:dist}
+    \rho(\epsilon)\too{\nn} = \left[ (1 - \epsilon) \rho + \epsilon \sigma \right]\too{\nn},
+\end{equation}
+and consider the general magic state distillation (MSD) / purification process
+\begin{equation}
+		\rho(\epsilon)\too{\nn} \xrightarrow{\E \in \O_\sigma} \rho(\epsilon')\too{\kk},
+\end{equation}
+where it is converted into a $\kk$-copy, $\epsilon'$-noisy state, such that the number of copies has decreased ($\kk < \nn$), but the state is less noisy ($\epsilon' < \epsilon$).
+
+The more noisy the initial state is, the more copies needed to reach the target. 
+We make this idea precise by defining the \emph{noise level threshold} as
 \begin{equation}\label{eq:ethresh}
-	\epsilon_{\rm{th}}(n, \epsilon_\tau, \sigma) \coloneqq \sup{\{\epsilon:\ \lc{\noisysn}{\sigma} \geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})}{\sigma}\}},
-\end{equation}
-so that the MSD process~(\ref{eq:sdist}) is impossible for all $\epsilon > \epsilon_{\rm{th}}(n, \epsilon_\tau, \sigma)$
-
-\nick{Condition in~\cref{eq:ethresh} is informally written. Can also define 
+	\begin{split}
+	\epsilon_{\rm{th}}(\nn, \kk, \epsilon', \sigma) \coloneqq &\sup{\{\epsilon:\ \lc{\rho(\epsilon)\too{\nn}}{\sigma}}(x) \geq \\
+	&{\lc{\rho(\epsilon')\too{\kk}}{\sigma}(x),\ x\in[0,1]\}}.
+	\end{split}
+\end{equation}
+The MSD process~(\ref{eq:dist}) is impossible for all $\epsilon > \epsilon_{\rm{th}}(\nn, \kk, \epsilon', \sigma)$.
+
+\nick{Can also define a distillation bound
 \begin{equation}\label{eq:ethresh}
-	n_{\rm{th}}(\epsilon, \epsilon_\tau, \sigma) \coloneqq \min{\{n:\ n \in \mathbb{N}, \lc{\noisysn}{\sigma} \geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})}{\sigma}\}}.
+	\nn_{\rm{th}}(\epsilon, \epsilon', \sigma) \coloneqq \min{\{\nn:\ \nn \in \mathbb{N}, \lc{\noisysn}{\sigma} \geq \lc{\noisys(\epsilon')}{\sigma}\}}.
 \end{equation}}
-We now examine the MSD process~(\ref{eq:sdist}) in specific $\sigma$--fragments.
-
-\subsection{Magic in unital fragments}\label{sec:unital}
-
-Magic state distillation circuits in principle consist of bulk sequences of random Clifford unitaries ($\rcu$)\nick{CITE}, depicted in~\cref{fig:zoo}.
-Operations in $\rcu$ can be expressed as
-\begin{equation}
-    \E(\rho) = \sum_i p_i U_i \rho U_i^\dagger,\ U_i \in \cd.
-\end{equation}
-Depending on the symmetries of such operations, a sequence of them may belong in various $\sigma$--fragments and the majorization condition~(\ref{eq:majbound}) needs to be checked in all these $\sigma$-fragments that reflect the symmetries of the operation sequence.
-However, they always belong to the \emph{unital fragment} $\O_{\frac{1}{d}\id}$.
-
-If one incorporates noisy channels in the circuit, for example dephasing channels as in~\cref{eq:dephase} in various bases, symmetries are reduced.
-Dephasing and bit-flip error channels are examples of the many error-inducing channels that respect the unital symmetry. \nick{expand}
-
-We plot the Lorenz curves of pure and noisy Strange state $n$-copy states for $n$ up to $4$ in~\cref{fig:lcs}.
-For $n=1$, the Lorenz curve is simply additive, 
+
+In general, the Wigner components of an $n$-copy state $\rho\too{n}$ can be calculated directly from $\W{\rho}$ by convolution of the distribution with itself,
+\begin{equation}
+	\W{\rho\too{\NN}} = \rm{W}_{\rho}\too{\NN},
+\end{equation}
+where $\otimes$ can be interpreted as the usual Kroenecker product in the last expression.
+Furthermore, single-copy Lorenz curves are simply additive in noise, 
 \begin{equation}
@@
 \end{equation}
-for any $\sigma, \rho$, but for $n\geq 2$, calculations become more complicated.
-
+for any $\sigma, \rho$.
+This is not true for higher number of copies.
+
+An important example is the purificiation process~\cref{eq:dist} of the qutrit Strange state $\ketbra{\rm{S}}$,
+\begin{equation}
+    \noisys(\epsilon) = (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \sigma,
+\end{equation}
+in $\O_\sigma$, where $\ket{\rm{S}}$ is defined in~\cref{fig:strange}. 
+For $\epsilon=0$, this state is a qutrit of maximal sum-negativity \nick{CITE} and therefore acts as the ideal distiallation target, analogous to a Bell state in bipartite entangelement theory.
+
+In~\cref{fig:lcs}, we illustrate the Lorenz curves of pure and noisy $n$-copy Strange states for $n$ up to $4$ in different $\sigma$-fragments.
 \begin{figure}%
@@
 
-In~\cref{fig:unital_distill}, we examine the purifying process of~\cref{eq:sdist} with $\epsilon_\tau = 0.05$ which describes all circuits that respect the unital symmetry.
-Thresholds provided by Lorenz curve comparison are always much stricter than mana thresholds.
-\nick{Explain asymptotic behaviour?}
-\begin{figure}
+In the following sections, we address the question of state interconversions in various $\sigma$--fragments, including concrete examples of the Strange state distillation process. \nick{adapt}
+
+\subsection{Magic in the unital fragment}\label{sec:unital}
+
+Magic state distillation circuits in principle consist of bulk sequences of random Clifford unitaries ($\rcu$)\nick{CITE}, depicted in~\cref{fig:zoo}.
+Operations in $\rcu$ can be expressed as
+\begin{equation}
+    \E(\rho) = \sum_i p_i U_i \rho U_i^\dagger,\ U_i \in \cd.
+\end{equation}
+Depending on the symmetries of such operations, a sequence of them may belong in various $\sigma$--fragments and the majorization condition~(\ref{eq:majbound}) needs to be checked in all these $\sigma$-fragments that reflect the symmetries of the operation sequence.
+However, they always belong to the \emph{unital fragment} $\O_{\frac{1}{d}\id}$.
+
+If one incorporates noisy channels in the circuit, for example dephasing channels as in~\cref{eq:dephase} in various bases, symmetries are reduced.
+Dephasing and bit-flip error channels are examples of the many error-inducing channels that respect the unital symmetry. \nick{expand}
+\begin{figure}[b]
     \centering
     \includegraphics[scale=0.5]{figs/unital_distill.pdf}
-    \caption{\textbf{Noise thresholds in unital fragment.} Mana and Lorenz curve noise thresholds for the Strange state purification process in~\cref{eq:sdist} with $\epsilon_\tau = 0.05$.
+    \caption{\textbf{Noise thresholds in unital fragment.} Mana and Lorenz curve noise thresholds for the Strange state purification process in~\cref{eq:sdist} with $\epsilon' = 0.05$.
     Lorenz curve comparison consistently gives stricter bounds as proven in~\cref{thm:bounds}.
@@
 
+\iffalse
+% Copies plot
 \begin{figure}
@@
 \end{figure}
-
-\newpage
-
-\subsection{Strange state Lorenz curves in the unital fragment}
-
-In this section we analytically investigate the behaviour of the Lorenz curve of an $n$-copy Strange state in the unital fragment, 
+\fi
+
+In~\cref{fig:unital_distill}, we examine the Strange state distillation process of~\cref{eq:dist} with $\epsilon' = 0.05$ which describes all circuits that respect the unital symmetry.
+Thresholds provided by Lorenz curve comparison are always much stricter than mana thresholds.
+\nick{Explain asymptotic behaviour?}
+
+\nick{We devote a section on Strange state Lorenz curve analysis in the unital fragment}
+
+\null\newpage
+
+\subsection{Strange state interconversions in the unital fragment}\label{sec:lcsu}
+
+In this section we analytically investigate the behaviour of the Lorenz curve of an $n$-copy Strange state in the unital fragment ($\sigma = \id/3$), 
 \begin{equation}\label{eq:lcsu}
-	\lc{\noisysn}{\frac{1}{d}\id}(x).
-\end{equation}
-An analytic handle on this type of Lorenz curves, which we call ``standard'' Lorenz curves, elevates Strange states to ``standard candles'' in the context of magic state distillation \nick{expand}.
-We first present some relevant theory on error bounds of general binary codes and then show how it can be used to approximate the Lorenz curves of~\cref{eq:lcsu}.
-
-\subsubsection{Binomial distributions and error bounds}
-\textbf{Notational convention:} For any non-negative reals $a,b$ with $b\geq a$, we will denote the set of integers $n$ such that $a\leq n \leq b$ as $[a,b]$.\\
-
-Consider an experiment consisting of $n$ trials of throwing a $p$-coin, that is a coin with probability $p$ of landing on one side and $1-p$ of landing on the other.
-That could be a string of $n$ bits with bit-flip error probability $p$.
-
-The experiment is described by binomial statistics and we define the left tail of the cumulative binomial distribution,
-\begin{equation}\label{eq:phil}
-	\Phi_\ell(m; n, p) \coloneqq \sum\limits_{j=0}^m \binom{n}{j} p^j (1-p)^{n-j},
-\end{equation}
-where $m\in [0,n]$.
-
-The symmetry between the left tail of a $p$-coin distribution and the right tail of a $(1-p)$-coin distribution dictates that
-\begin{align}\label{eq:phi_reverse}
-	\Phi_\ell(m; n, p) + \Phi_\ell(n-m-1; n, 1-p) &= 1,\ m\in [0,n-1],
-\end{align}
-
-The classical entropy of a $p$-coin is
-\begin{equation}\label{eq:ent}
-	S(p) \coloneqq -p\log{p} -(1-p)\log{(1-p)},
-\end{equation}
-which is symmetric, $S(p) = S(1-p)$.
-%Let $c(m; n) \coloneqq [m(1-m/n)]^{-1/2},\ m\in [1, n-1]$.
-A useful result is the entropic bound on a combination~\cite{cit:ash}.
-\begin{lemma}\label{lem:comb_bounds}
-	For all $m\in [1,n-1]$,
-	\begin{align}
-		&\left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{nS\left(\frac{m}{n}\right)} \leq \binom{n}{m} \leq \\
-		&\left[ 2\pi m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{nS\left(\frac{m}{n}\right)}.
-	\end{align}
-\end{lemma}
-\begin{proof}
-	For $m = 1,2, n-1, n-2$ check by direct calculation.	
-	For all other cases, use Stirling's approximation.
-\end{proof}
-
-Bounds on the tails of a cumulative binomial distribution can be expressed in terms of the classical relative entropy between a $p$-coin and a $q$-coin,
-\begin{equation}\label{eq:ent_rel}
-	\ent{p}{q} \coloneqq p \log{\frac{p}{q}} + (1-p) \log{\frac{1-p}{1-q}}.
-\end{equation}
-This entropy satisfies the identity
-\begin{equation}
-	\ent{p}{q} = \ent{1-p}{1-q}.
-\end{equation}
-
-We can now derive entropic bounds on binomial cumulative distributions~\cite{cit:ash}.
-\begin{lemma}\label{lem:phil_bounds}
-	Given fixed $n>0$ and $p$, $\Phi_\ell$ satisfies the following bounds:
-	\begin{align*}
-		\begin{split}
-		&\text{1. } \Phi_\ell(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ents},\ m\in [1,n-1] \\
-		&\text{2. } \Phi_\ell(m; n, p) \leq 2^{-n\ents},\ m\in [0,np] \\
-		&\text{3. } \Phi_\ell(m; n, p) \leq 1 - \left[ 8(m+1)\left(1-\frac{m+1}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m+1}{n}}{p}}, \\
-		&\hspace{14pt} m\in [0,n-2]
-		\end{split}
-		\\
-		&\text{4. } \Phi_\ell(m; n, p) \geq 1 - 2^{-n\ent{\frac{m+1}{n}}{p}},\ m\in [np+1,n-2]
-	\end{align*}
-\end{lemma}
-\begin{proof}
-	\nick{cite proof}
-\end{proof}
-
-We now define the partial sums
-\begin{align}	
-	\Phi_+(m; n, p) &\coloneqq \sum\limits_{j=0}^{m/2} \binom{n}{2j} p^{2j} (1-p)^{n-2j}, \nonumber\\ 
-	&m\in[0,n]\ \text{and }m\text{ even}, \label{eq:fp} \\
-	\Phi_-(m; n, p) &\coloneqq \sum\limits_{j=1}^{(m-1)/2} \binom{n}{2j+1} p^{2j+1} (1-p)^{n-(2j+1)}, \nonumber\\ 
-	&m\in[0,n]\ \text{and }m\text{ odd}. \label{eq:fn2}
-\end{align}
-Index $m$ only takes even (odd) values when labelling $\Phi_+$ ($\Phi_-$) and therefore we can use $\Phi_{\pm}$ to compactify statements that hold for both $\Phi_+, \Phi_-$.
-In particular, we derive ``loose'' and ``strict'' bounds on $\Phi_{\pm}$.
-\begin{lemma}\label{lem:bounds_loose}
-	Given fixed $n>0$ and $p$, $\Phi$ satisfies the following bounds:
-	\begin{align*}
-		\begin{split}
-		&\text{1. } \Phi_{\pm}(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ents},\ m\in [1,n-1] \\
-		&\text{2. } \Phi_{\pm}(m; n, p) \leq 2^{-n\ents},\ m\in [0,np] \\
-		&\text{3. } \Phi_{\pm}(m; n, p) \leq 1 - \left[ 8(m+1)\left(1-\frac{m+1}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m+1}{n}}{p}}, \\
-		&\hspace{14pt} m\in [0,n-2]
-		\end{split}
-	\end{align*}
-\end{lemma}
-\begin{proof}
-	\nick{paste proof}
-\end{proof}
-\begin{lemma}\label{lem:bounds_strict}
-	Given fixed $n>0$ and $p$, $\Phi_+, \Phi_-$ satisfy the following bounds:
-	\begin{align*}
-		\begin{split}
-		&\text{1. } \Phi_+(m; n, p) \geq \sum\limits_{j=0}^{m/2}\left[ 8(2j)\left(1-\frac{2j}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{2j}{n}}{p}}, \\
-		&\hspace{14pt} \text{for all even } m\in [2,n] \\
-		&\text{2. } \Phi_+(m; n, p) \leq \sum\limits_{j=0}^{m/2}\left[ 2\pi(2j)\left(1-\frac{2j}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{2j}{n}}{p}}, \\
-		&\hspace{14pt} \text{for all even } m\in [2,n] \\
-		&\text{3. } \Phi_-(m; n, p) \geq \sum\limits_{j=1}^{(m-1)/2}\left[ 8(2j+1)\left(1-\frac{2j+1}{n}\right) \right]^{-\frac{1}{2}} \times \\
-		&\hspace{14pt} \times 2^{-n\ent{\frac{2j+1}{n}}{p}},\ \text{for all odd } m\in [1,n] \\
-		&\text{4. } \Phi_-(m; n, p) \leq \sum\limits_{j=1}^{(m-1)/2}\left[ 2\pi(2j+1)\left(1-\frac{2j+1}{n}\right) \right]^{-\frac{1}{2}} \times \\
-		&\hspace{14pt} \times 2^{-n\ent{\frac{2j+1}{n}}{p}},\ \text{for all odd } m\in [1,n]
-		\end{split}
-	\end{align*}
-\end{lemma}
-\begin{proof}
-	\nick{paste proof}
-\end{proof}
-
-\subsubsection{Standard Lorenz curves in terms of binomial distributions}
-
-The Wigner distribution of the qutrit maximally mixed state $\id/3$ is the uniform distribution $\bm{1}/9$.
-The Wigner distribution of the 1-copy noisy Strange state $\rho_{\rm{S}}(\epsilon)$ in the unital fragment is a permutation of 8 positive components ($w_+$) and 1 negative ($w_-$) with
-\begin{align}
-	w_+ &= \frac{1}{6} - \frac{1}{18}\epsilon \\
-	w_- &= -\frac{1}{3} + \frac{4}{9}\epsilon.
-\end{align}
-They are depicted in~\cref{fig:noisys}.
-\begin{figure}[t]
-    \centering
-    \includegraphics[scale=0.7]{figs/noisys.pdf}
-    \caption{\textbf{Wigner components of the noisy Strange state.} 
-    In the interval $0 \leq \epsilon < 3/7$, the negative component is larger than the positive components.
-    At $\epsilon = 3/7$ the Wigner distribution is $(-\frac{1}{7},\frac{1}{7},\dots,\frac{1}{7})$.
-    In the interval $3/7 < \epsilon < 3/4$, the positive components are larger than the negative component.
-    In the interval $3/4 \leq \epsilon \leq 1$, there is no negativity.
-    }
-    \label{fig:noisys}
-\end{figure}
-The $n+1$ distinct Wigner components ($w_j$) of $\noisysn$ along with their multiplicities ($c_j$) are given in~\cref{tab:lcsu_w}.
-\begin{table}[b]                           
- \centering
- \begin{tabular}{c|c|c|c}
- $\epsilon$ & $j$ & $\left[0, \frac{n}{2}\right]$ & $\left[\frac{n}{2} + 1, n \right]$ \\ [0.5ex] 
- \hline
-  & $w_{j}$ & $w_+^{2j}w_-^{n-2j}$ & $w_+^{n-2j}w_-^{2j}$  \\
-  $0\leq \epsilon < \frac{3}{7}$ & & & \\
-  & $c_{j}$ & $8^{2j}\binom{n}{2j}$ & $8^{n-2j}\binom{n}{2j}$ \\
- \hline
-  & $w_{j}$ & $w_+^{n-2j}w_-^{2j}$ & $w_+^{2j}w_-^{n-2j}$  \\
-  $\frac{3}{7} \leq \epsilon < \frac{3}{4} $ & & & \\
-  & $c_{j}$ & $8^{n-2j}\binom{n}{2j}$ & $8^{2j}\binom{n}{2j}$
-\end{tabular}
- \caption{Wigner components of $\rho_{\rm{S}}^{\otimes n}(\epsilon)$. The multiplication $2j$ is modulo $(n+1)$.}
- \label{tab:lcsu_w}
-\end{table}
-
-To get the Lorenz curve, we need to sum up the Wigner components in decreasing order and the order depends on the noise level $\epsilon$, so we define probabilities associated with the $x$-coordinate ($p_x$) and the vertical coordinate ($p_L$) of the Lorenz curve accordingly,
-\begin{equation}
-	(p_x, p_L) \equiv \big( p_x(\epsilon), p_L(\epsilon) \big) = 
-	\begin{cases}
-		\left( \frac{8}{9}, \frac{12-4\epsilon}{15-8\epsilon} \right),\ & 0\leq \epsilon < \frac{3}{7} \\
-		\left( \frac{1}{9}, \frac{3-4\epsilon}{15-8\epsilon} \right),\ & \frac{3}{7}\leq \epsilon < \frac{3}{4} \\
-	\end{cases}	
-\end{equation}
-
-We are now in a position to express Lorenz curve coordinates in terms of phi distributions,
-\begin{equation}\label{eq:x_coord_elb}
-	x_k(n, \epsilon) = 
-	\begin{cases}
-		\Phi_+(k;n,p_x),\\
-		\hspace{20pt} k\in[0,n]\ \text{and }k\text{ even}, \\
-		x_{k_\star} + \Phi_-(k;n,1-p_x),\\
-		\hspace{20pt} k\in[0,n]\ \text{and }k\text{ odd}, \\
-	\end{cases}	
-\end{equation}
-and
-\begin{equation}\label{eq:lc_coord_elb}
-	L_k(n, \epsilon) = 
-	\begin{cases}
-		\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+(k;n,p_L),\\
-		\hspace{20pt} k\in[0,n]\ \text{and }k\text{ even}, \\
-		L_{k_\star} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-(k;n,1-p_L),\\
-		\hspace{20pt} k\in[0,n]\ \text{and }k\text{ odd}. \\
-	\end{cases}	
-\end{equation}
-
-Finally, the $m$-th elbow is located at
-\begin{equation}\label{eq:lcsu_elbows}
-	\left(x_m, \lc{\noisysn}{\frac{1}{d}\id}(x_m) \right) = \Big( x_{2m}(n, \epsilon), L_{2m}(n, \epsilon) \Big),
-\end{equation}
-where $2m$ is considered \hspace{-7pt}$\mod{(n+1)}$.
-
-We can therefore use~\cref{lem:bounds_loose,lem:bounds_strict} to bound the standard Lorenz curves.
-\begin{figure}[b]
-    \centering
-    \includegraphics[scale=0.4]{figs/lc_bounds.pdf}
-    \caption{\textbf{Lorenz curves and bounding curves.} 
-    The figure explores the distillation process of a 10-copy $0.25$-noisy Strange state to a 4-copy $0.05$-noisy Strange state in the unital fragment.
-    Clearly, by looking at the Lorenz curves, the distillation process is possible.
-    However the bounding curves, derived in~\cref{lem:bounds_strict}, intersect at the end, suggesting that the process is not necessarily possible.
-    }
-    \label{fig:lc_bounds}
-\end{figure}
-
-\subsubsection{Pointwise Lorenz curve comparison}
-
-In this subsection, we obtain explicit coordinates for all points on the Lorenz curve.
-
-Consider the $\epsilon$-noisy, $n$-copy Strange state
-\begin{equation}
-    \noisysn = \left( (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \frac{1}{3}\id \right)^{\otimes n},
-\end{equation}
-with Wigner distribution
-\begin{equation}
-	\begin{split}
-		\W{\noisysn} &= \left( \overbrace{\frac{1}{6} - \frac{1}{18}\epsilon, \dots, \frac{1}{6} - \frac{1}{18}\epsilon}^8, \overbrace{-\frac{1}{3} + \frac{4}{9}\epsilon}^1 \right)^{\otimes n} \\
-		&= \rm{W}^+_{\noisysn} + \rm{W}^-_{\noisysn},
-	\end{split}
-\end{equation}
-where we split non-negative and negative components into $\rm{W}^+_{\noisysn}$ and $\rm{W}^-_{\noisysn}$.
-
-As a simple example, we split the Wigner distribution of state $\rho_{\rm{S}}(0)^{\otimes 2}$,
+	\lc{\noisysn}{\frac{1}{d}\id}(x),\ x\in[0,1].
+\end{equation}
+We recognise Lorenz curve of this type as ``standard candles'' in the context of magic state distillation and call them the \emph{standard Lorenz curves} \nick{expand}.
+
+The aim is to study the MSD process,
+\begin{equation}\label{eq:sudist}
+	\noisysn \xrightarrow{\E \in \O_{\id/3}} \noisys(\epsilon')\too{\kk},
+\end{equation}
+in the regime where $0 \leq \epsilon \leq \tfrac{3}{4}$.
+For $\tfrac{3}{4} \leq \epsilon < 1$, the noisy Strange state $\noisys(\epsilon)$ contains no Wigner negativities in the unital fragment as seen in~\cref{eq:wsu}.
+
+\subsubsection{Coordinate expressions for standard Lorenz curves}
+The Wigner distribution of the $\NN$-copy qutrit maximally mixed state $\left(\id/3\right)\too{\NN}$ is the uniform distribution 
+\begin{equation}\label{eq:wu}
+	\W{\left(\id/3\right)\too{\NN}} = \left( \overbrace{\frac{1}{9^\NN}, \dots, \frac{1}{9^\NN}}^{9^\NN} \right).
+\end{equation}
+The Wigner distribution of the 1-copy $\epsilon$-noisy Strange state $\noisys(\epsilon)$ in the unital fragment is a permutation of 
+\begin{equation}\label{eq:wsu}
+	\W{\noisys(\epsilon)} = \left( \overbrace{\frac{1}{6} - \frac{1}{18}\epsilon, \dots, \frac{1}{6} - \frac{1}{18}\epsilon}^8, \overbrace{-\frac{1}{3} + \frac{4}{9}\epsilon}^1 \right)
+\end{equation}
+The Wigner distribution of the $\NN$-copy $\epsilon$-noisy Strange state $\noisysN$ in the unital fragment is the $n$-th convolution $\W{\noisysN} = \rm{W}_{\noisys(\epsilon)}\too{N}$.
+
+For example, the Wigner distribution of state $\noisys(0)\too{2}$ is
 \begin{equation*}
-	\begin{split}
-    &\rm{W}^+_{\rho_{\rm{S}}(0)^{\otimes 2}} = \left( \overbrace{\left( -\frac{1}{3} \right)^2}^1, \overbrace{\left( \frac{1}{6} \right)^2, \dots, \left( \frac{1}{6} \right)^2}^{64} \right) \text{ and } \\
-    &\rm{W}^-_{\rho_{\rm{S}}(0)^{\otimes 2}} = \left( \overbrace{ -\frac{1}{3} \cdot \frac{1}{6}, \dots, -\frac{1}{3} \cdot \frac{1}{6}}^{16} \right)
-    \end{split}
+	\rm{W}_{\noisys(0)\too{2}} = \left( \overbrace{\left( -\frac{1}{3} \right)^2}^1, \overbrace{\left( \frac{1}{6} \right)^2, \dots, \left( \frac{1}{6} \right)^2}^{64}, \overbrace{ -\frac{1}{3} \cdot \frac{1}{6}, \dots, -\frac{1}{3} \cdot \frac{1}{6}}^{16} \right)
 \end{equation*}
 
-For now, we restrict to the non-negative Wigner components $\rm{W}^+_{\noisysn}$ [i.e. the ``LHS of the Lorenz curve''] and we drop superscript $+$ for clarity.
-Assume: 
-\begin{itemize}
-    \item $n$ is even [ensures Lorenz curve coordinates can be expressed in terms of $\Phi_{\pm}$ distributions];
-    \item $0 \leq \epsilon \leq \frac{3}{7}$ [ensures closed-form expressions for Lorenz curve coordinates];
-\end{itemize}
-There are $\frac{n}{2}+1$ distinct non-negative components in the Wigner distribution $\W{\noisysn}$.\\
-
-We can rewrite the non-negative part of the Wigner distribution $\W{\noisysn}$ in a compact form, by simply listing the distinct Wigner components $w(k; n, \epsilon)$ along with their multiplicities $m(k; n)$:
-\begin{align}
-    &{\W{\noisysn}} = \\ 
-    &\big\{\left( m_k, w_k \right)\big\}_{k=0,\dots,n/2} = \nonumber\\ 
-    &\big\{\left( m(k; n), w(k; n, \epsilon) \right)\big\}_{k=0,\dots,n/2} = \nonumber\\
-    &\left\{ \left( 8^{2k}\binom{n}{2k}, \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2k}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{n-2k} \right) \right\}_{k=0,\dots,n/2}. \nonumber
-\end{align}
-
-The expressions for the Lorenz curve elbows in the unital fragment are then known:
-\begin{align}
-    &{\rm{L}_{\noisysn}} = \\
-    &\big\{\left( x_k, L_k \right)\big\}_{k=0,\dots,n/2} = \nonumber\\
-    &\big\{\left( x(k; n), L(k; n, \epsilon) \right)\big\}_{k=0,\dots,n/2} = \nonumber\\
-    &\left\{ \left( \frac{1}{9^n}\sum\limits_{j=0}^k m_j, \sum\limits_{j=0}^k m_j w_j \right) \right\}_{k=0,\dots,n/2} = \nonumber\\
-    &\left\{ \left( \Phi_+\left(2k;n,\frac{8}{9}\right), \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+\left(2k;n,4\frac{3-\epsilon}{15-8\epsilon}\right) \right) \right\}_{k=0,\dots,n/2}.
-\nonumber
-\end{align}
-We include the origin in the Lorenz curve as it does not arise from the above expressions, denoting it by $(x_{-1}, L_{-1}) \coloneqq (0,0)$.
-
-We can get explicit expressions for all $\frac{1}{2}(7^n + 9^n)$ points of the Lorenz curve, using a two-index parameterisation:
-\begin{align}
-    x_{k,\alpha} &= \left( 1-\frac{\alpha}{m_k} \right) x_{k-1} + \frac{\alpha}{m_k} x_k \label{eq:x}\\
-    L_{k,\alpha} &= \left( 1-\frac{\alpha}{m_k} \right) L_{k-1} + \frac{\alpha}{m_k} L_k \label{eq:l}\\
-    &\text{for } k=0,\dots,\frac{n}{2} \text{ and } \alpha = 1,\dots,m_k. \nonumber
-\end{align}
-
-As a simple example, we plot the Lorenz curve of state $\rho_{\rm{S}}(0)^{\otimes 2}$,
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.6]{figs/lcpoints.pdf}
-    \caption{\textbf{All points on the Lorenz curve are uniformly distributed.}
-    \cref{eq:x,eq:l}) capture the coordinates of all points up to the maximum.
-    }
-    \label{fig:lc}
-\end{figure}
-
-Consider now the state 
-\begin{equation}
-    \rho(r, \epsilon, s) = \rho_{\rm{S}}(\epsilon)^{\otimes r} \otimes \left( \frac{1}{3}\id \right)^{\otimes s}.
-\end{equation}
-
-Tensoring with the maximally mixed state keeps the Lorenz curve unchanged, but increases the resolution of (the uniformly distributed) points.
-The new point coordinates are given by:
-\begin{align}
-    x_{k,\alpha, \beta} &= \left( 1-p_{k,\alpha, \beta}\right) x_{k-1} + p_{k,\alpha, \beta} x_k \label{eq:lcsu_xcoord}\\
-    L_{k,\alpha, \beta} &= \left( 1-p_{k,\alpha, \beta} \right) L_{k-1} + p_{k,\alpha, \beta} L_k, \label{eq:lcsu_lcoord}\\
-    &\text{where } p(k, \alpha, \beta) = \frac{(\alpha-1)9^s + \beta}{9^s m_k} \\
-    &\text{for } k=0,\dots,\frac{r}{2},\ \alpha = 1,\dots,m_k \text{ and } \beta = 1,\dots,9^s. \nonumber
-\end{align}
-
-We can unify the indices, by introducing a single index
-\begin{equation}
-    i(k,\alpha,\beta) \coloneqq \beta + \left[ (\alpha-1) + \sum_{j=0}^{k-1} 8^{2j}\binom{r}{2j} \right]9^s,
-\end{equation}
-so that $i=1,2,\dots, \frac{1}{2}9^s(7^{r} + 9^{r})$.
-The $\frac{r}{2}$ elbows correspond to 
-\begin{equation}
-	i(k, \alpha, \beta) = i(\kappa, m_{\kappa}, 9^s) \equiv \sum_{j=0}^{\kappa} m_j,\ \kappa = 0,\dots,\frac{r}{2}.
-\end{equation}
-This index function is bijective, i.e.
-\begin{equation}
-	(k, \alpha, \beta) = (k', \alpha', \beta') \Leftrightarrow i(k, \alpha, \beta) = i(k', \alpha', \beta').
-\end{equation}
-
-\section*{Strange state Lorenz curve comparison in the unital fragment}
+In~\cref{app:lcsu_technical}, we derive explicit expressions for the coordinates of standard Lorenz curves, which we present here.
+
+\nick{noisy maximum}
+Calculating the components of $\ket{S}\bra{S}\too{n}$ allows for analytical calculation of the maximum of the $n$-copy state,
+\begin{equation}\label{eq:Skmax}
+    \max_x{\lc{\ketbra{S}\too{n}} {\sigma}}(x) = \frac{1}{2}\left (1 + \left(\frac{5}{3}\right)^n \right).
+\end{equation}
+Its location $x_{k_\star}$ depends on the $\sigma$--fragment and is given by~\cref{eq:maxloc} with $k_\star = \frac{1}{2}(7^n + 9^n)$.
+%1 + \left(\frac{4}{3}\right)^n \sum\limits_{j=0}^{\floor{\frac{n-1}{2}}} 4^{-(2j+1)} \binom{n}{2j+1}
+%\sum_{i=j, j: odd}^n a^j \binom{n}{j} = \frac{1}{2} [ (1+a)^n - (1-a)^n ]
+%$\{(-1)^j 2^{j-n} 3^{-n}\}_{0 \leq j \leq n}$ with multiplicity $8^{n-j} \binom{n}{j}$ for the $j$-th term
+
+\subsubsection{Standard Lorenz curve comparison}
 
@@
 \begin{equation}
-\rho_{\rm{S}}(\epsilon)^{\otimes 4} \xrightarrow{\mathcal{O}_{\id/d}} \rho_{\rm{S}}(\epsilon')^{\otimes 2} \otimes \left( \frac{1}{3}\id \right)^{\otimes 2}.
+\rho_{\rm{S}}(\epsilon)\too{4} \xrightarrow{\mathcal{O}_{\id/d}} \rho_{\rm{S}}(\epsilon')\too{2} \otimes \left( \frac{1}{3}\id \right)\too{2}.
 \end{equation}
@@
 
-\newpage
-
-\begin{theorem}\label{thm:elbows}
-	Let $\rho, \tau$ be two quantum states with Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in the $\sigma$-fragment.
-
-	Let $r$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ and $T \coloneqq \{x_0, x_1, \dots, x_r, x_{r+1} \}$ be the $x$-coordinates of the elbows with $x_0 = 0$ and $x_{r+1} = 1$.
-
-	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_j) \geq \lc{\tau}{\sigma}(x_j)$ for all $j =1,\dots,r$.
-\end{theorem}
-\begin{proof}	
-	$\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ trivially implies $\lc{\rho}{\sigma}(x_j) \geq \lc{\tau}{\sigma}(x_j)$ for all $j =1,\dots,r$.
-
-	Conversely, assume that $\lc{\rho}{\sigma}(x_j) \geq \lc{\tau}{\sigma}(x_j)$ for all $j =1,\dots,r$.
-	First, note that $\lc{\rho}{\sigma}(x_0) = \lc{\tau}{\sigma}(x_0) = 0$ and $\lc{\rho}{\sigma}(x_{r+1}) = \lc{\tau}{\sigma}(x_{r+1}) = 1$.
-
-	Pick two consecutive $x$-coordinates $x_i, x_{i+1}$ and consider the line segment $\ell_\tau(x)$ connecting points $(x_i, \lc{\tau}{\sigma}(x_i))$ and $(x_{i+1}, \lc{\tau}{\sigma}(x_{i+1}))$ as well as the line segment $\ell_\rho(x)$ connecting points $(x_i, \lc{\rho}{\sigma}(x_i))$ and $(x_{i+1}, \lc{\rho}{\sigma}(x_{i+1}))$.
-	This is illustrated in~\cref{fig:elbows_proof}.
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.6]{figs/elbows_proof.pdf}
-    \caption{\textbf{Illustration of~\cref{thm:elbows}}.
-    }
-    \label{fig:elbows_proof}
-\end{figure}
-
-	Due to concavity of $\lc{\rho}{\sigma}$, it is clear that for all $x \in [x_i, x_{i+1}]$, we have $\lc{\rho}{\sigma}(x) \geq \ell_\rho(x) \geq \ell_\tau(x) = \lc{\tau}{\sigma}(x)$.
-	This argument can be made in all intervals $[x_i, x_{i+1}]$ with $i=0,\dots,r$, so the proof is complete.
-\end{proof}
-
-Returning to~\cref{eq:su_conversion}, the $r$ independent necessary constraints are
+\nick{Returning to~\cref{eq:su_conversion}, and }using~\cref{thm:elbows}, the $r$ independent necessary constraints are
 \begin{align}
-\lc{\noisysn}{\frac{1}{d}\id}\left(x_{i'(0, m'_{0}, 9^{s})}\right) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}\left(x_{i'(0, m'_{0}, 9^{s})}\right), \nonumber\\
-\lc{\noisysn}{\frac{1}{d}\id}\left(x_{i'(1, m'_{1}, 9^{s})}\right) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}\left(x_{i'(1, m'_{1}, 9^{s})}\right), \nonumber\\
+\lc{\noisysn}{\frac{1}{d}\id}\left(x_{i'(0, m'_{0}, 9^{s})}\right) &\geq \lc{\rho_{\rm{S}}(\epsilon')\too{k}}{\frac{1}{d}\id}\left(x_{i'(0, m'_{0}, 9^{s})}\right), \nonumber\\
+\lc{\noisysn}{\frac{1}{d}\id}\left(x_{i'(1, m'_{1}, 9^{s})}\right) &\geq \lc{\rho_{\rm{S}}(\epsilon')\too{k}}{\frac{1}{d}\id}\left(x_{i'(1, m'_{1}, 9^{s})}\right), \nonumber\\
 &\vdotswithin{=} \nonumber\\
-\lc{\noisysn}{\frac{1}{d}\id}\left(x_{i'(r, m'_{r}, 9^{s})}\right) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}\left(x_{i'(r, m'_{r}, 9^{s})}\right), \nonumber
+\lc{\noisysn}{\frac{1}{d}\id}\left(x_{i'(r, m'_{r}, 9^{s})}\right) &\geq \lc{\rho_{\rm{S}}(\epsilon')\too{k}}{\frac{1}{d}\id}\left(x_{i'(r, m'_{r}, 9^{s})}\right), \nonumber
 \end{align}
-where $x_{i'(0, m'_{0}, 9^{s'})}, x_{i'(1, m'_{1}, 9^{s'})}, \dots, x_{i'(r, m'_{r}, 9^{s'})} \in T$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon')^{\otimes r}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).
+where $x_{i'(0, m'_{0}, 9^{s'})}, x_{i'(1, m'_{1}, 9^{s'})}, \dots, x_{i'(r, m'_{r}, 9^{s'})} \in T$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon')\too{r}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).
 
@@
 We generalise the analysis of unital fragments into any circuit with thermalisation noise parametrised by the temperature $\beta^{-1}$.
-In~\cref{fig:thermal_distill}, we examine the majorization bound for the same purification process of~\cref{eq:sdist} with $\epsilon_\tau = 0.05$.
+In~\cref{fig:thermal_distill}, we examine the majorization bound for the same purification process of~\cref{eq:sdist} with $\epsilon' = 0.05$.
 The curves plotted suggest that there exists a fragment $\O_{\gamma_{\beta_{\rm{max}}}}$ which allows for a highest noise threshold at any given number of copies of the initial state.
@@
 
-\begin{figure}
+\begin{figure}[b]
     \centering
     \includegraphics[scale=0.5]{figs/thermal_distill.pdf}
-    \caption{\textbf{Threshold dependence on temperature in thermal fragments.} Lorenz curve ratios for the Strange state purifying process in~\cref{eq:sdist} with $\epsilon_\tau = 0.05$.
+    \caption{\textbf{Threshold dependence on temperature in thermal fragments.} Lorenz curve ratios for the Strange state purifying process in~\cref{eq:sdist} with $\epsilon' = 0.05$.
     The peaks of each curve indicate the optimal temperature $\beta_{\rm{max}}$ that allows for the highest noise threshold at every given number of initial state copies $k$.
@@
 
-\begin{figure}
+\begin{figure}[b]
     \centering
     \includegraphics[scale=0.5]{figs/stab_distill.pdf}
-    \caption{\textbf{Strange state distillation thresholds in stabilizer fragments.} Lorenz curve thresholds for the Strange state purifying process in~\cref{eq:sdist} with $\epsilon_\tau = 0.05$.
+    \caption{\textbf{Strange state distillation thresholds in stabilizer fragments.} Lorenz curve thresholds for the Strange state purifying process in~\cref{eq:sdist} with $\epsilon' = 0.05$.
     All $12$ stabilizer fragments produce two distinct trends: ($k=0$ - red curve) the stabilizer states that have non-zero value at the origin of the phase space lie low and ($k=1,2$ - blue curve) the stabilizer states that have a zero value at the origin of the phase space lie high.
@@
     \includegraphics[scale=0.5]{figs/stab_distill_norrell.pdf}
-    \caption{\textbf{Norrell state distillation thresholds in stabilizer fragments.} Lorenz curve thresholds for the Strange state purifying process in~\cref{eq:sdist} with $\epsilon_\tau = 0.05$.
+    \caption{\textbf{Norrell state distillation thresholds in stabilizer fragments.} Lorenz curve thresholds for the Strange state purifying process in~\cref{eq:sdist} with $\epsilon' = 0.05$.
     For high enough copies, certain Lorenz curves surpass the unital noise threshold $\epsilon_{\rm{th}} = \frac{3}{4}$.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+\null\newpage
 \section{Lower bounds in $\sigma$-fragments}
@@
 The busy reader more focussed on magic may skip this section.
+\nick{restate}
 
@@
 The subdivisions of magic theories into $\sigma$--fragments suggests a new approach towards investigating state convertibility which retains more structure of the origin theory than a measure can.
-
-\subsection{Monotones}\label{sec:mono}
-
-We highlight the defining property of a monotone for the discussion that follows.
-\begin{definition}[\textbf{Resource monotone}]\label{def:mono}
-    Let $\R = (\F, \O)$ be a resource theory.
-    A resource monotone $\M$ is a projection from the set of quantum states of the theory onto the real line, so that $\M$ is monotonically decreasing under free operations,
-    \begin{equation}
-        \M(\rho_1) \leq \M(\rho_2)\ \text{whenever}\ \rho_1 \prec_{\R} \rho_2.
-    \end{equation}
-\end{definition}
-The monotonicity condition reflects the no resource generating property of free operations, so that monotones respect the pre-order $\prec_\R$ of the theory.
-Furthermore, a monotone may also satisfy the additivity condition,
-\begin{equation}
-    \M(\rho_1 \otimes \rho_2) = \M(\rho_1) + \M(\rho_2).
-\end{equation}
-This optional condition is of practical importance for resource distillation, which we discuss in~\cref{sec:distill} within the context of magic.
-
-The most fundamental and commonly used magic monotone is the \emph{mana} of a state \nick{CITE}, defined as
-\begin{equation}
-    \mana{\rho} \coloneqq \log{\left(\sum\limits_{\bmz \in \pd} \abs{\W[\bmz]{\rho}}\right)}.
-\end{equation}
-It is a monotone function of the $\ell_1$-norm of the Wigner distribution that satisfies the additivity condition.
-In particular, mana can be re-expressed as $\mana{\rho} = \log{(2\sn{\rho}+1)}$, where the sum-negativity ($\rm{sn}$) \nick{CITE} is the sum of the negative components in $\W{\rho}$,
-\begin{equation}
-	\sn{\rho} = \sum\limits_{\bmx: \W[\bmx]{\rho} < 0} \abs{\W[\bmx]{\rho}}.
-\end{equation}
-
-\subsection{Fragments}
 

### 2020-11-28 appendix.tex
Added standard Lorenz curve expressions for all cases. Tidied up Strange state section and appendix

--- 2020-06-23 appendix.tex
@@
 
-\section{Area monotone}
-\label{app:areamono}
+\section{Lorenz curve properties}
+\label{app:lc_properties}
+
+\subsection{Area monotone}\label{app:areamono}
+
+\begin{figure}[t]%
+    \centering
+    \subfigure[][]{%
+    \label{fig:test1}%
+    \includegraphics[height=3cm]{figs/negmasking_rho_strange_lc.pdf}
+    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
+    }\hspace{8pt}%
+    \subfigure[][]{%
+    \label{fig:test2}%
+    \includegraphics[height=3cm]{figs/negmasking_rho_strange_meas.pdf}
+    %\caption{Zero state $\ketbra{0}{0}$}%
+    }
+    \caption{\subref{fig:test1} Lorenz curve of $p\ketbra{\rm{S}} + (1-p) \frac{1}{d}\id$ for $p$ given in the legend.\subref{fig:test2} Different measures for the states on the left. \\
+    \nick{can replace~\cref{fig:lctoy} with a more informative version of this figure}
+    }%
+    \label{fig:test}
+\end{figure}
 
@@
 
-\begin{figure}%
+\section{Technical derivations for standard Lorenz curves}
+\label{app:lcsu_technical}
+
+\subsection{Binomial distributions and error bounds}\label{app:phi}
+Consider an experiment consisting of $n$ trials of throwing a $p$-coin, that is a coin with probability $p$ of landing on one side and $1-p$ of landing on the other.
+This scenario describes the construction of an $n$-copy Strange state Wigner distribution from a single-copy as presented in~\cref{sec:lcsu}.
+The experiment is described by binomial statistics and we write down the sum over an even number of successful trials $\Phi_+$ (over an odd number of successful trials $\Phi_-$),
+\begin{align}	
+	\Phi_+(\mmf; \nnf, p) &\coloneqq \sum\limits_{\dummy=0}^{\mmf/2} \binom{\nnf}{2\dummy} p^{2\dummy} (1-p)^{\nnf-2\dummy}, \nonumber\\ 
+	&\text{for even integers } \mmf\in[0,\nnf], \label{eq:fp_app} \\
+	\Phi_-(\mmf; \nnf, p) &\coloneqq \sum\limits_{\dummy=1}^{(\mmf-1)/2} \binom{\nnf}{2\dummy+1} p^{2\dummy+1} (1-p)^{\nnf-(2\dummy+1)}, \nonumber\\ 
+	&\text{for odd integers } \mmf\in[1,\nnf]. \label{eq:fn_app}
+\end{align}
+Note that index $\mmf$ only takes even (odd) values when labelling $\Phi_+$ ($\Phi_-$).
+In~\cref{app:lcsu_coord_elb}, we will use $\Phi_+$ and $\Phi_-$ to express the elbow coordinates of standard Lorenz curves.
+
+We define the classical entropy of a $p$-coin as well as the classical relative entropy between a $p$-coin and a $q$-coin,
+\begin{align}
+	S(p) &\coloneqq -p\log{p} -(1-p)\log{(1-p)}, \label{eq:ent}\\
+	\ent{p}{q} &\coloneqq p \log{\frac{p}{q}} + (1-p) \log{\frac{1-p}{1-q}}. \label{eq:ent_rel}
+\end{align}
+They are symmetric in the sense that $S(p) = S(1-p)$ and $\ent{p}{q} = \ent{1-p}{1-q}$.
+
+A useful result is the entropic bound on a combination~\cite{cit:ash}.
+\begin{lemma}\label{lem:comb_bounds}
+	For all $\mmf\in [1,\nnf-1]$,
+	\begin{align}
+		&\left[ 8\mmf\left(1-\frac{\mmf}{\nnf}\right) \right]^{-\frac{1}{2}} 2^{\nnf S\left(\frac{\mmf}{\nnf}\right)} \leq \binom{\nnf}{\mmf} \leq \\
+		&\left[ 2\pi \mmf\left(1-\frac{\mmf}{\nnf}\right) \right]^{-\frac{1}{2}} 2^{\nnf S\left(\frac{\mmf}{\nnf}\right)}.
+	\end{align}
+\end{lemma}
+\begin{proof}
+	For $\mmf = 1,2, \nnf-1, \nnf-2$ check by direct calculation.	
+	For all other cases, use Stirling's approximation. 
+	\nick{CITE}
+\end{proof}
+With the help of this lemma, we directly arrive at 
+\begin{theorem}\label{thm:bounds_strict}
+	Given fixed $n>0$ and $p$, $\Phi_+, \Phi_-$ satisfy the following bounds:
+	\begin{align*}
+		\begin{split}
+		&\text{1. } \Phi_+(\mmf; \nnf, p) \geq \sum\limits_{\dummy=0}^{\mmf/2}\left[ 16\dummy\left(1-\frac{2\dummy}{\nnf}\right) \right]^{-\frac{1}{2}} 2^{-\nnf\ent{\frac{2\dummy}{\nnf}}{p}}, \\
+		&\hspace{14pt} \text{for all even } \mmf\in [2,\nnf] \\
+		&\text{2. } \Phi_+(\mmf; \nnf, p) \leq \sum\limits_{\dummy=0}^{\mmf/2}\left[ 4\pi\dummy\left(1-\frac{2\dummy}{\nnf}\right) \right]^{-\frac{1}{2}} 2^{-\nnf\ent{\frac{2\dummy}{\nnf}}{p}}, \\
+		&\hspace{14pt} \text{for all even } \mmf\in [2,\nnf] \\
+		&\text{3. } \Phi_-(\mmf; \nnf, p) \geq \sum\limits_{\dummy=1}^{(\mmf-1)/2}\left[ 16(\dummy+1)\left(1-\frac{2\dummy+1}{\nnf}\right) \right]^{-\frac{1}{2}} \times \\
+		&\hspace{14pt} \times 2^{-\nnf\ent{\frac{2\dummy+1}{\nnf}}{p}},\ \text{for all odd }\mmf\in [1,\nnf] \\
+		&\text{4. } \Phi_-(\mmf; \nnf, p) \leq \sum\limits_{\dummy=1}^{(\mmf-1)/2}\left[ 4\pi(\dummy+1)\left(1-\frac{2\dummy+1}{\nnf}\right) \right]^{-\frac{1}{2}} \times \\
+		&\hspace{14pt} \times 2^{-\nnf\ent{\frac{2\dummy+1}{\nnf}}{p}},\ \text{for all odd } \mmf\in [1,\nnf]
+		\end{split}
+	\end{align*}
+\end{theorem}
+\begin{proof}
+	All four statements follow from application of~\cref{lem:comb_bounds} on the combinatorial coefficient and the defintion of relative entropy given in~\cref{eq:ent_rel}
+\end{proof}
+
+\iffalse % LOOSE BOUNDS & PLOT - START
+The experiment is described by binomial statistics and we define the left tail of the cumulative binomial distribution,
+\begin{equation}\label{eq:phil}
+	\Phi_\ell(m; n, p) \coloneqq \sum\limits_{j=0}^m \binom{n}{j} p^j (1-p)^{n-j},
+\end{equation}
+where $m\in [0,n]$.
+
+The symmetry between the left tail of a $p$-coin distribution and the right tail of a $(1-p)$-coin distribution dictates that
+\begin{align}\label{eq:phi_reverse}
+	\Phi_\ell(m; n, p) + \Phi_\ell(n-m-1; n, 1-p) &= 1,\ m\in [0,n-1],
+\end{align}
+Entropic bounds on $\Phi_\ell$~\cite{cit:ash}.
+\begin{lemma}\label{lem:phil_bounds}
+	Given fixed $n>0$ and $p$, $\Phi_\ell$ satisfies the following bounds:
+	\begin{align*}
+		\begin{split}
+		&\text{1. } \Phi_\ell(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ents},\ m\in [1,n-1] \\
+		&\text{2. } \Phi_\ell(m; n, p) \leq 2^{-n\ents},\ m\in [0,np] \\
+		&\text{3. } \Phi_\ell(m; n, p) \leq 1 - \left[ 8(m+1)\left(1-\frac{m+1}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m+1}{n}}{p}}, \\
+		&\hspace{14pt} m\in [0,n-2]
+		\end{split}
+		\\
+		&\text{4. } \Phi_\ell(m; n, p) \geq 1 - 2^{-n\ent{\frac{m+1}{n}}{p}},\ m\in [np+1,n-2]
+	\end{align*}
+\end{lemma}
+\begin{proof}
+	\nick{cite proof}
+\end{proof}
+Loose bounds follow
+\begin{lemma}\label{lem:bounds_loose}
+	Given fixed $n>0$ and $p$, $\Phi$ satisfies the following bounds:
+	\begin{align*}
+		\begin{split}
+		&\text{1. } \Phi_{\pm}(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ents},\ m\in [1,n-1] \\
+		&\text{2. } \Phi_{\pm}(m; n, p) \leq 2^{-n\ents},\ m\in [0,np] \\
+		&\text{3. } \Phi_{\pm}(m; n, p) \leq 1 - \left[ 8(m+1)\left(1-\frac{m+1}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m+1}{n}}{p}}, \\
+		&\hspace{14pt} m\in [0,n-2]
+		\end{split}
+	\end{align*}
+\end{lemma}
+\begin{proof}
+	\nick{paste proof}
+\end{proof}
+
+We can therefore use~\cref{lem:bounds_loose,lem:bounds_strict} to bound the standard Lorenz curves.
+\begin{figure}[b]
     \centering
-    \subfigure[][]{%
-    \label{fig:test1}%
-    \includegraphics[height=3cm]{figs/negmasking_rho_strange_lc.pdf}
-    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
-    }\hspace{8pt}%
-    \subfigure[][]{%
-    \label{fig:test2}%
-    \includegraphics[height=3cm]{figs/negmasking_rho_strange_meas.pdf}
-    %\caption{Zero state $\ketbra{0}{0}$}%
+    \includegraphics[scale=0.4]{figs/lc_bounds.pdf}
+    \caption{\textbf{Lorenz curves and bounding curves.} 
+    The figure explores the distillation process of a 10-copy $0.25$-noisy Strange state to a 4-copy $0.05$-noisy Strange state in the unital fragment.
+    Clearly, by looking at the Lorenz curves, the distillation process is possible.
+    However the bounding curves, derived in~\cref{lem:bounds_strict}, intersect at the end, suggesting that the process is not necessarily possible.
     }
-    \caption{\subref{fig:test1} Lorenz curve of $p\ketbra{\rm{S}} + (1-p) \frac{1}{d}\id$ for $p$ given in the legend.\subref{fig:test2} Different measures for the states on the left. \\
-    \nick{can replace~\cref{fig:lctoy} with a more informative version of this figure}
-    }%
-    \label{fig:test}
+    \label{fig:lc_bounds}
 \end{figure}
+\fi % LOOSE BOUNDS & PLOT - END
+
+\subsection{Standard Lorenz curve elbow coordinates}\label{app:lcsu_coord_elb}
+The Wigner distribution of the $\NN$-copy qutrit maximally mixed state $\left(\id/3\right)\too{\NN}$ is the uniform distribution 
+\begin{equation}\label{eq:wu}
+	\W{\left(\id/3\right)\too{\NN}} = \Bigg( \overbrace{\frac{1}{9^\NN}, \dots, \frac{1}{9^\NN}}^{9^\NN} \Bigg).
+\end{equation}
+The Wigner distribution of the 1-copy $\epsilon$-noisy Strange state $\noisys(\epsilon)$ in the unital fragment is a permutation of 
+\begin{equation}\label{eq:wsu}
+	\W{\noisys(\epsilon)} = \Bigg( \overbrace{\frac{1}{6} - \frac{1}{18}\epsilon, \dots, \frac{1}{6} - \frac{1}{18}\epsilon}^8, \overbrace{-\frac{1}{3} + \frac{4}{9}\epsilon}^1 \Bigg)
+\end{equation}
+The two distinct components are plotted~\cref{fig:noisys} as a function of noise. 
+It is clear that in the unital fragment the Strange state contains Wigner negativities in the regime $0 \leq \epsilon \leq \tfrac{3}{4}$.
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.7]{figs/noisys.pdf}
+    \caption{\textbf{Wigner components of the noisy Strange state.} 
+    In the interval $0 \leq \epsilon < 3/7$, the negative component is larger than the positive components.
+    At $\epsilon = 3/7$ the Wigner distribution is $(-\frac{1}{7},\frac{1}{7},\dots,\frac{1}{7})$.
+    In the interval $3/7 < \epsilon < 3/4$, the positive components are larger than the negative component.
+    In the interval $3/4 \leq \epsilon \leq 1$, there is no negativity.
+    }
+    \label{fig:noisys}
+\end{figure}
+
+The Wigner distribution of the $\NN$-copy $\epsilon$-noisy Strange state $\noisysN$ in the unital fragment is given by the convolution $\W{\noisysN} = \rm{W}_{\noisys(\epsilon)}\too{\NN}$.
+In general, $\noisysN$ contains $\NN + 1$ distinct components, labelled $0,\dots, \NN$.
+We present the distinct Wigner components of $\noisysN$ along with their multiplicites in~\cref{tab:lcsu}.
+Note that LHS (RHS) refers to elbow coordinates $\ii$ on the left of and including (right of) the maximum, precisely
+\begin{align}
+&\text{LHS: } 0 \leq \ii \leq \frac{\lfloor \NN \rfloor}{2}; \\
+&\text{RHS: } \frac{\lfloor \NN \rfloor}{2}+1 \leq \ii \leq \NN.
+\end{align}
+\begin{table}[h]
+  \def\arraystretch{1.5}
+  \centering
+  \begin{tabular}{c|c|c|r|r}
+    \multicolumn{3}{c|}{Case} & \multicolumn{1}{c}{$\mlt_{\ii}(\NN, \epsilon)$} & \multicolumn{1}{|c}{$w_{\ii}(\NN, \epsilon)$} \\[0.5ex]\hline
+    \multirow{4}{*}{\raisebox{-4ex}{\rotatebox[origin=c]{90}{$0\leq \epsilon < \frac{3}{7}$}}} & \hspace{0.8ex}\multirow{2}{*}{\raisebox{-1ex}{\rotatebox[origin=c]{90}{$\NN$ even}}}\hspace{0.8ex} & LHS & $8^{2\ii}\binom{\NN}{2\ii}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{\NN-2\ii}$ \\
+    & & RHS & $8^{\NN-2\ii}\binom{\NN}{2\ii}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{\NN-2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2\ii}$ \\ \cline{2-5}
+    & \multirow{2}{*}{\raisebox{-2ex}{\rotatebox[origin=c]{90}{$\NN$ odd}}} & LHS & $8^{2\ii+1}\binom{\NN}{2\ii+1}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2\ii+1}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{\NN-2\ii-1}$ \\
+    & & RHS & $8^{\NN-2\ii-1}\binom{\NN}{2\ii+1}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{\NN-2\ii-1}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2\ii+1}$ \\ \hline
+    \multirow{4}{*}{\raisebox{-4ex}{\rotatebox[origin=c]{90}{$\frac{3}{7}\leq \epsilon < \frac{3}{4}$}}} & \multirow{2}{*}{\raisebox{-1ex}{\rotatebox[origin=c]{90}{$\NN$ even}}} & LHS & $8^{\NN-2\ii}\binom{\NN}{2\ii}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{\NN-2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2\ii}$ \\
+    & & RHS & $8^{2\ii}\binom{\NN}{2\ii}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{\NN-2\ii}$ \\ \cline{2-5}
+    & \multirow{2}{*}{\raisebox{-2ex}{\rotatebox[origin=c]{90}{$\NN$ odd}}} & LHS & $8^{\NN-2\ii}\binom{\NN}{2\ii}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{\NN-2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2\ii}$ \\
+    & & RHS & $8^{2\ii}\binom{\NN}{2\ii}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{\NN-2\ii}$ \\ \hline
+  \end{tabular}
+  \caption{Wigner components $w_{\ii}(\NN, \epsilon)$ of $\noisysN$ along with their multiplicities $\mlt_{\ii}(\NN, \epsilon)$ in decreasing order in $\ii,\ 0 \leq \ii \leq \NN$.
+  The order changes depending on the noise level $\epsilon$, the parity of the number of copies $\NN$ and the parity of the components (LHS vs RHS).
+  Multiplication $2\ii$ is considered modulo $(\NN+1)$.}
+  \label{tab:lcsu}
+\end{table}
+
+For example, the distribution of state $\noisys(0)\too{2}$ is
+\begin{equation*}
+	\begin{split}
+	\rm{W}_{\noisys(0)\too{2}} = \Bigg( &\overbrace{\left( -\frac{1}{3} \right)^2}^1, \overbrace{\left( \frac{1}{6} \right)^2, \dots, \left( \frac{1}{6} \right)^2}^{64}, \\
+	&\overbrace{ -\frac{1}{3} \cdot \frac{1}{6}, \dots, -\frac{1}{3} \cdot \frac{1}{6}}^{16} \Bigg)
+	\end{split}
+\end{equation*}
+
+Every standard Lorenz curve contains $\NN$ elbows, labelled by 
+\begin{equation*}
+\{(x_{\ii}, L_{\ii})\}_{\ii=-1,0,\dots,\NN}\ ,
+\end{equation*}
+where the boundary points $(x_{-1}, L_{-1}) = (0,0)$ and $(x_{\NN}, L_{\NN}) = (1,1)$ are also included.
+The maximum is the $(\lfloor \NN \rfloor/2)$-th elbow and its coordinates are calculated by collecting all the positive Wigner components,
+\begin{align}
+	x_{\lfloor \NN \rfloor/2} &= \frac{1}{2}\left(1 + \left(\frac{7}{9}\right)^\NN\right), \\
+	L_{\lfloor \NN \rfloor/2} &= \frac{1}{2}\left (1 + \left(\frac{15 - 8\epsilon}{9}\right)^\NN \right).
+\end{align}
+%\sum_{j: even}^n a^j \binom{n}{j} = \frac{1}{2} [ (1+a)^n + (1-a)^n ]
+
+Expressions for all the elbow coordinates follow from summing up the Wigner components in decreasing order and we present the elbow coordinates for standard Lorenz curves in~\cref{tab:lcsu_coord_elb_app}.
+\begin{table}[h]
+  \def\arraystretch{1.5}
+  \centering
+  \begin{tabular}{c|c|c|r|r}
+    \multicolumn{3}{c|}{Case} & \multicolumn{1}{c}{$x_{\ii}$} & \multicolumn{1}{|c}{$L_{\ii}$} \\[0.5ex]\hline
+    \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$0\leq \epsilon < \frac{3}{7}$}}} & \hspace{0.8ex}\multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$\NN$ even}}}\hspace{0.8ex} & LHS & $\Phi_+\left(2\ii;\NN,\frac{8}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_+\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\
+    & & RHS & $x_{\NN/2} + \Phi_-\left(2\ii;\NN,\frac{1}{9}\right)$ & $L_{\NN/2} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_-\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
+    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$\NN$ odd}}} & LHS & $\Phi_-\left(2\ii;\NN,\frac{8}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_-\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\
+    & & RHS & $x_{\NN/2} + \Phi_-\left(2\ii;\NN,\frac{1}{9}\right)$ & $L_{\NN/2} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_-\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
+    \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$\frac{3}{7}\leq \epsilon < \frac{3}{4}$}}} & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$\NN$ even}}} & LHS & $\Phi_+\left(2\ii;\NN,\frac{1}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_+\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\
+    & & RHS & $x_{\NN/2} + \Phi_-\left(2\ii;\NN,\frac{8}{9}\right)$ & $L_{\NN/2} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_-\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
+    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$\NN$ odd}}} & LHS & $\Phi_+\left(2\ii;\NN,\frac{1}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_+\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\
+    & & RHS & $x_{\NN/2} + \Phi_+\left(2\ii;\NN,\frac{8}{9}\right)$ & $L_{\NN/2} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_+\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
+  \end{tabular}
+  \caption{Standard Lorenz curves elbow coordinates.
+  The expresion depends on the noise level $\epsilon$, the parity of the number of copies $\NN$ and the location of the elbow relative to the maximum (LHS vs RHS).
+  Multiplication $2\ii$ is considered modulo $(\NN+1)$.
+  Note that the Lorenz curve boundary points are $(x_{-1}, L_{-1}) \coloneqq (0,0)$ and $(x_{\NN}, L_{\NN}) = (1,1)$.
+  }
+  \label{tab:lcsu_coord_elb_app}
+\end{table}
+
+\subsection{Standard Lorenz curve coordinates}\label{app:lcsu_coord}
+We can get explicit expressions for all $9^{\NN}$ points of the standard Lorenz curve $\lc{\noisysN}{\id/3}$, in terms of the elbow coordinates:
+\begin{align}
+    x_{\ii\jj} &= \left( 1-\frac{\jj}{\mlt_{\ii}} \right) x_{\ii-1} + \frac{\jj}{\mlt_{\ii}} x_{\ii}, \label{eq:x}\\
+    L_{\ii\jj} &= \left( 1-\frac{\jj}{\mlt_{\ii}} \right) L_{\ii-1} + \frac{\jj}{\mlt_{\ii}} L_{\ii} \label{eq:l}
+\end{align}
+for $\jj = 1,\dots,\mlt_{\ii}$ and $\ii=0,\dots,\NN$, where multiplicities $\mlt_\ii = \mlt_\ii(\NN, \epsilon)$ are given in~\cref{tab:lcsu}.
+
+For visualisation purposes, we plot the Lorenz curve of state $\noisys(0)\too{2}$.
+\begin{figure}[t]
+    \centering
+    \includegraphics[scale=0.6]{figs/lcpoints.pdf}
+    \caption{\textbf{All points on the Lorenz curve are uniformly distributed.}
+    \cref{eq:x,eq:l}) capture the coordinates of all points up to the maximum.
+    }
+    \label{fig:lc}
+\end{figure}
+
+Consider the state 
+\begin{equation*}
+    \noisys(\epsilon)\too{\tt} \otimes \left( \frac{1}{3}\id \right)\too{\mm},
+\end{equation*} %\noisys(\tt, \epsilon, \mm) \coloneqq 
+with $\tt + \mm = \NN$.
+
+Tensoring with the maximally mixed state keeps the Lorenz curve unchanged, but increases the resolution of (the uniformly distributed) points.
+The new point coordinates are given by:
+\begin{align}
+    &x_{\ii\jj\kk} = \left( 1-p_{\ii\jj\kk}\right) x_{\ii-1} + p_{\ii\jj\kk} x_{\ii} \label{eq:lcsu_xcoord}\\
+    &L_{\ii\jj\kk} = \left( 1-p_{\ii\jj\kk} \right) L_{\ii-1} + p_{\ii\jj\kk} L_{\ii}, \label{eq:lcsu_lcoord}\\
+    &\text{where } p_{\ii\jj\kk} = \frac{\kk + (\jj-1)9^{\mm}}{9^{\mm} \mlt_{\ii}} \nonumber\\
+    &\text{for } \ii=0,\dots,\tt,\ \jj = 1,\dots,\mlt_{\ii}(\tt, \epsilon') \text{ and } \kk = 1,\dots,9^{\mm}. \nonumber
+\end{align}
+
+We can unify the indices, by introducing a single index
+\begin{equation}
+    \II(\ii,\jj,\kk) \coloneqq \kk + \left[ (\jj-1) + \sum_{\dummy=0}^{\ii-1} \mlt_{\dummy}(\tt, \epsilon') \right]9^{\mm},
+\end{equation}
+so that $\II=1,2,\dots, 9^{\NN}$.
+The elbow coordinates correspond to 
+\begin{equation}
+	\II(\ii, \mlt_{\ii}(\tt, \epsilon'), 9^{\mm}) = \sum_{\dummy=0}^{\ii} \mlt_{\dummy}(\tt, \epsilon'),\ \ii= 0,\dots,\tt.
+\end{equation}
+The index function $\II$ is bijective, i.e.
+\begin{equation}
+	(\ii,\jj,\kk) = (\ii',\jj',\kk') \Leftrightarrow \II(\ii,\jj,\kk) = \II(\ii',\jj',\kk').
+\end{equation}
+
+\subsection{Strange state MSD in the unital fragment}\label{app:lc_compare}
+Consider the Strange state MSD process in the unital fragment,
+\begin{equation}\label{eq:su_conversion}
+    \noisysn \xrightarrow{\mathcal{O}_{\id/3}} \noisys(\tt, \epsilon', \mm),\ \nn = \tt + \mm.
+\end{equation}
+We denote initial state indices without a prime and target state indices with a prime,
+\begin{align}
+    \II(\ii,\jj,\kk=1) &= \jj + \sum_{\dummy=0}^{\ii-1} \mlt_{\dummy}(\nn, \epsilon), \\
+    \II'(\ii',\jj',\kk') &= \kk' + \left[ (\jj'-1) + \sum_{\dummy=0}^{\ii'-1} \mlt_{\dummy}(\tt, \epsilon') \right]9^{\mm}.
+\end{align}
+
+Pointwise Lorenz curve comparison requires $x_{\II} = x_{\II'}$, so the question is: 
+\begin{center}
+\emph{Given a triplet $(\ii',\jj',\kk')$, what is the tuple $(\ii,\jj)$ such that $\II(\ii,\jj) = \II'(\ii',\jj',\kk')$?}
+\end{center}
+
+As a basic example, consider the process 
+\begin{equation}
+\rho_{\rm{S}}(\epsilon)\too{4} \xrightarrow{\mathcal{O}_{\id/d}} \rho_{\rm{S}}(\epsilon')\too{2} \otimes \left( \frac{1}{3}\id \right)\too{2}.
+\end{equation}
+We want to check which Lorenz curve is higher at the first elbows of the target state, i.e. we want to verify or reject the first inequality below:
+\begin{equation}
+	L_{\II(\ii,\jj)} \geq L'_{\II'(0, 1, 81)}
+\end{equation}
+where the first multiplicity of the target state is $m_0 = 1$.
+The multiplicities of the initial state are $(1, 384, 4096)$.
+
+The challenge is to find $\ii,\jj$ such that $i(\ii,\jj) = i'(0,1,81)$.
+\nick{By trial and error}, we find that $(\ii,\jj) = (1, 80)$.
+Now we can use~\cref{eq:lcsu_lcoord} to directly calculate
+\begin{align*}
+	L'_{i'(0,1,81)} &= L'_0 = \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^2 \Phi_+\left(0;2,4\frac{3-\epsilon}{15-8\epsilon}\right), \\
+	L_{i(1, 80)} &= \left(1-\frac{80}{384} \right) L_0 + \frac{80}{384} L_1 \\
+	\begin{split}
+	&= \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^4 \bigg[ \frac{19}{24} \Phi_+\left(0;4,4\frac{3-\epsilon}{15-8\epsilon}\right) \\ 
+	&\qquad + \frac{5}{24}\Phi_+\left(2;4,4\frac{3-\epsilon}{15-8\epsilon}\right) \bigg],
+	\end{split}
+\end{align*}
+and then compare them.
+
+\subsection{Lorenz curve independent constraints}\label{app:lc_constraints}
+
+\begin{theorem}
+	Let $\rho, \tau$ be two quantum states with Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in the $\sigma$-fragment.
+
+	Let $\tt$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ and $E \coloneqq \{x_1, \dots, x_\tt\}$ be their locations.
+
+	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_{\ii}) \geq \lc{\tau}{\sigma}(x_{\ii})$ for all $\ii =1,\dots,\tt$.
+\end{theorem}
+\begin{proof}	
+	$\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ trivially implies $\lc{\rho}{\sigma}(x_{\ii}) \geq \lc{\tau}{\sigma}(x_{\ii})$ for all $\ii = 1,\dots,\tt$.
+
+	Conversely, assume that $\lc{\rho}{\sigma}(x_{\ii}) \geq \lc{\tau}{\sigma}(x_{\ii})$ for all $\ii = 1,\dots,r$.
+	First, let $x_0 = 0$ and $x_{\tt+1} = 1$, so that $\lc{\rho}{\sigma}(x_0) = \lc{\tau}{\sigma}(x_0) = 0$ and $\lc{\rho}{\sigma}(x_{\tt+1}) = \lc{\tau}{\sigma}(x_{\tt+1}) = 1$.
+	Hence, we can extend the set of elbows $E$ to $E' = E \cup \{x_0, x_{\tt+1}\}$.
+
+	Pick two consecutive locations $x_{\ii}, x_{\ii+1}$ in $E'$ and consider the line segment $\ell_\tau(x)$ connecting points $(x_{\ii}, \lc{\tau}{\sigma}(x_{\ii}))$ and $(x_{\ii+1}, \lc{\tau}{\sigma}(x_{\ii+1}))$ as well as the line segment $\ell_\rho(x)$ connecting points $(x_{\ii}, \lc{\rho}{\sigma}(x_{\ii}))$ and $(x_{\ii+1}, \lc{\rho}{\sigma}(x_{\ii+1}))$.
+	This is illustrated in~\cref{fig:elbows_proof}.
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.6]{figs/elbows_proof.pdf}
+    \caption{\textbf{Illustration of~\cref{thm:elbows}}.
+    }
+    \label{fig:elbows_proof}
+\end{figure}
+
+	Due to concavity of $\lc{\rho}{\sigma}$, it is clear that for all $x \in [x_{\ii}, x_{\ii+1}]$, we have $\lc{\rho}{\sigma}(x) \geq \ell_\rho(x) \geq \ell_\tau(x) = \lc{\tau}{\sigma}(x)$.
+	This argument can be made in all intervals $[x_{\ii}, x_{\ii+1}]$ with $\ii=0,\dots,\tt$, so the proof is complete.
+\end{proof}
+This theorem is of practical importance in calculating the necessary distillation constraints derived via majorization.

### 2020-11-28 magic_paper.tex
Added standard Lorenz curve expressions for all cases. Tidied up Strange state section and appendix

@@
 This inequality is parametrised by $x$ and if it is not satisfied at any point $x$, then the Lorenz curves intersect and the conversion is impossible.
-
-We can reduce the number of independent constraints stemming from this inequality down to the number of elbows of the target state.
+We can refine the independent constraints stemming from this inequality and consider it at only the locations of the target state elbows.
 \begin{theorem}\label{thm:elbows}
@@
 
-	Let $r$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ and $E \coloneqq \{x_1, \dots, x_\kk\}$ be their locations.
-
-	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_j) \geq \lc{\tau}{\sigma}(x_j)$ for all $j =1,\dots,\kk$.
+	Let $\tt$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ and $E \coloneqq \{x_1, \dots, x_\tt\}$ be their locations.
+
+	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_{\ii}) \geq \lc{\tau}{\sigma}(x_{\ii})$ for all $\ii =1,\dots,\tt$.
 \end{theorem}
-\begin{proof}	
-	$\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ trivially implies $\lc{\rho}{\sigma}(x_j) \geq \lc{\tau}{\sigma}(x_j)$ for all $j =1,\dots,\kk$.
-
-	Conversely, assume that $\lc{\rho}{\sigma}(x_j) \geq \lc{\tau}{\sigma}(x_j)$ for all $j =1,\dots,r$.
-	First, let $x_0 = 0$ and $x_{\kk+1} = 1$, so that $\lc{\rho}{\sigma}(x_0) = \lc{\tau}{\sigma}(x_0) = 0$ and $\lc{\rho}{\sigma}(x_{\kk+1}) = \lc{\tau}{\sigma}(x_{\kk+1}) = 1$.
-	Hence, we can extend the set of elbows $E$ to $E' = E \cup \{x_0, x_{\kk+1}\}$.
-
-	Pick two consecutive locations $x_i, x_{i+1}$ in $E'$ and consider the line segment $\ell_\tau(x)$ connecting points $(x_i, \lc{\tau}{\sigma}(x_i))$ and $(x_{i+1}, \lc{\tau}{\sigma}(x_{i+1}))$ as well as the line segment $\ell_\rho(x)$ connecting points $(x_i, \lc{\rho}{\sigma}(x_i))$ and $(x_{i+1}, \lc{\rho}{\sigma}(x_{i+1}))$.
-	This is illustrated in~\cref{fig:elbows_proof}.
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.6]{figs/elbows_proof.pdf}
-    \caption{\textbf{Illustration of~\cref{thm:elbows}}.
-    }
-    \label{fig:elbows_proof}
-\end{figure}
-
-	Due to concavity of $\lc{\rho}{\sigma}$, it is clear that for all $x \in [x_i, x_{i+1}]$, we have $\lc{\rho}{\sigma}(x) \geq \ell_\rho(x) \geq \ell_\tau(x) = \lc{\tau}{\sigma}(x)$.
-	This argument can be made in all intervals $[x_i, x_{i+1}]$ with $i=0,\dots,\kk$, so the proof is complete.
-\end{proof}
-This theorem is of practical importance in checking Lorenz curve bounds, and it is used in the discussion of standard Lorenz curves in~\cref{sec:lcsu}.
+A proof is provided in~\cref{app:lc_constraints}.
 
@@
 
-	Let $\jj_\star$ be the index of the smallest non-negative component of $\tilde{\bm{w}}^\downarrow$.
-	Then, $(\W{\rho})_i < 0$ if and only if $i > \jj_\star$, so the maximum of Lorenz curve $\lc{\rho}{\sigma}(x)$ takes the value 
-	\begin{equation}
-		\lc{\rho}{\sigma}(x_{\jj_\star}) = \sum_{i=1}^{\jj_\star} (\W{\rho})_i,
+	Let $\ii_\star$ be the index of the smallest non-negative component of $\tilde{\bm{w}}^\downarrow$.
+	Then, $(\W{\rho})_i < 0$ if and only if $i > \ii_\star$, so the maximum of Lorenz curve $\lc{\rho}{\sigma}(x)$ takes the value 
+	\begin{equation}
+		\lc{\rho}{\sigma}(x_{\ii_\star}) = \sum_{i=1}^{\ii_\star} (\W{\rho})_i,
 	\end{equation}
@@
 	\begin{equation}\label{eq:maxloc}
-		x_{\jj_\star} \coloneqq \sum_{i=1}^{\jj_\star} (\W{\sigma})_i.
-	\end{equation}
-
-	The location of the maximum ($x=x_{k_\star}$) varies from fragment to fragment, but its value is independent of $\sigma$,
-	\begin{equation}
-		\lc{\rho}{\sigma}(x_{k_\star})
+		x_{\ii_\star} \coloneqq \sum_{i=1}^{\ii_\star} (\W{\sigma})_i.
+	\end{equation}
+
+	The location of the maximum ($x=x_{\ii_\star}$) varies from fragment to fragment, but its value is independent of $\sigma$,
+	\begin{equation}
+		\lc{\rho}{\sigma}(x_{\ii_\star})
 		= \sum\limits_{\bmx: \W[\bmx]{\rho} \geq 0} \W[\bmx]{\rho}
@@
     \begin{equation}
-    	\lc{\rho}{\sigma}(x) \geq \lc{\rho}{\sigma}(x),\ x\in[0,1]
-    \end{equation}
-    implies the order $\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} \geq \max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)}$ which is equivalent to the mana bound $\mana{\rho} \geq \mana{\tau}$.
+    	\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x),\ x\in[0,1]
+    \end{equation}
+    implies the order $\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} \geq \max_{x\in[0,1]}{\lc{\tau}{\sigma}(x)}$, equivalent to the mana condition $\mana{\rho} \geq \mana{\tau}$.
 \end{proof}
@@
 \begin{equation}
-		\rho(\epsilon)\too{\nn} \xrightarrow{\E \in \O_\sigma} \rho(\epsilon')\too{\kk},
-\end{equation}
-where it is converted into a $\kk$-copy, $\epsilon'$-noisy state, such that the number of copies has decreased ($\kk < \nn$), but the state is less noisy ($\epsilon' < \epsilon$).
+		\rho(\epsilon)\too{\nn} \xrightarrow{\E \in \O_\sigma} \rho(\epsilon')\too{\tt},
+\end{equation}
+where it is converted into a $\tt$-copy, $\epsilon'$-noisy state, such that the number of copies has decreased ($\tt < \nn$), but the state is less noisy ($\epsilon' < \epsilon$).
 
@@
 	\begin{split}
-	\epsilon_{\rm{th}}(\nn, \kk, \epsilon', \sigma) \coloneqq &\sup{\{\epsilon:\ \lc{\rho(\epsilon)\too{\nn}}{\sigma}}(x) \geq \\
-	&{\lc{\rho(\epsilon')\too{\kk}}{\sigma}(x),\ x\in[0,1]\}}.
+	\epsilon_{\rm{th}}(\nn, \tt, \epsilon', \sigma) \coloneqq &\sup{\{\epsilon:\ \lc{\rho(\epsilon)\too{\nn}}{\sigma}}(x) \geq \\
+	&{\lc{\rho(\epsilon')\too{\tt}}{\sigma}(x),\ x\in[0,1]\}}.
 	\end{split}
 \end{equation}
-The MSD process~(\ref{eq:dist}) is impossible for all $\epsilon > \epsilon_{\rm{th}}(\nn, \kk, \epsilon', \sigma)$.
+The MSD process~(\ref{eq:dist}) is impossible for all $\epsilon > \epsilon_{\rm{th}}(\nn, \tt, \epsilon', \sigma)$.
 
@@
 \begin{equation}\label{eq:ethresh}
-	\nn_{\rm{th}}(\epsilon, \epsilon', \sigma) \coloneqq \min{\{\nn:\ \nn \in \mathbb{N}, \lc{\noisysn}{\sigma} \geq \lc{\noisys(\epsilon')}{\sigma}\}}.
+	\nn_{\rm{th}}(\epsilon, \epsilon', \sigma) \coloneqq \min{\{\nn: \lc{\noisysn}{\sigma} \geq \lc{\noisys(\epsilon')}{\sigma}\}}.
 \end{equation}}
 
-In general, the Wigner components of an $n$-copy state $\rho\too{n}$ can be calculated directly from $\W{\rho}$ by convolution of the distribution with itself,
+In general, the Wigner components of an $\NN$-copy state $\rho\too{\NN}$ can be calculated directly from $\W{\rho}$ by convolution of the distribution with itself,
 \begin{equation}
@@
     }
-    \caption{\textbf{Lorenz curves of Strange state copies.} Lorenz curves of $\noisysn$ for $n=1,2,3,4$.
+    \caption{\textbf{Lorenz curves of Strange state copies.} Lorenz curves of $\noisysn$ for $\nn=1,2,3,4$.
     Solid lines represent pure Strange states ($\epsilon = 0$); dashed lines represent noisy Strange states ($\epsilon = 0.1$).
     \subref{fig:lcs_maxmix} Unital fragment; \subref{fig:lcs_thermal} Thermal fragment with $H = (0,1,2)$ and $\beta = 0.5$; \subref{fig:lcs_zero} Fragment $\O_{\ketbra{0}{0}}$ (corresponds to red curve in~\cref{fig:stab_distill}); \subref{fig:lcs_one} Fragment $\O_{\ketbra{1}{1}}$ (corresponds to blue curve in~\cref{fig:stab_distill}).
+    The elbows of a curve are the non-differentiable points that form ``angles'' between consecutive line segments.
     }%
@@
 \subsection{Magic in the unital fragment}\label{sec:unital}
-
-Magic state distillation circuits in principle consist of bulk sequences of random Clifford unitaries ($\rcu$)\nick{CITE}, depicted in~\cref{fig:zoo}.
+The unital fragment encompasses the circuits which preserve the maximally mixed state ($\id/d$) and so it includes many important families of circuits.
+
+MSD circuits in principle consist of bulk sequences of random Clifford unitaries ($\rcu$)\nick{CITE}, depicted in~\cref{fig:zoo}.
 Operations in $\rcu$ can be expressed as
@@
 \end{equation}
-Depending on the symmetries of such operations, a sequence of them may belong in various $\sigma$--fragments and the majorization condition~(\ref{eq:majbound}) needs to be checked in all these $\sigma$-fragments that reflect the symmetries of the operation sequence.
-However, they always belong to the \emph{unital fragment} $\O_{\frac{1}{d}\id}$.
-
-If one incorporates noisy channels in the circuit, for example dephasing channels as in~\cref{eq:dephase} in various bases, symmetries are reduced.
+Depending on the symmetries of such operations, a Clifford sequence may belong in other $\sigma$--fragments as well.
+In this case, the majorization condition~(\ref{eq:majbound}) needs to be checked in all the $\sigma$-fragments that reflect the symmetries of the operation sequence.
+
+In general, noisy circuits are well-described by the unital fragment.
+To see this, consider incorporating noisy channels in the circuit, for example dephasing channels as in~\cref{eq:dephase} defined in different bases.
+This process destroys the circuit symmetries, except for the invariance of the maximally mixed state.
 Dephasing and bit-flip error channels are examples of the many error-inducing channels that respect the unital symmetry. \nick{expand}
-\begin{figure}[b]
+
+In~\cref{fig:unital_distill}, we examine the Strange state distillation process of~\cref{eq:dist} with $\epsilon' = 0.05$ which describes all circuits that respect the unital symmetry.
+Thresholds provided by Lorenz curve comparison are always much stricter than mana thresholds.
+\nick{Explain asymptotic behaviour?}
+\begin{figure}[h]
     \centering
     \includegraphics[scale=0.5]{figs/unital_distill.pdf}
-    \caption{\textbf{Noise thresholds in unital fragment.} Mana and Lorenz curve noise thresholds for the Strange state purification process in~\cref{eq:sdist} with $\epsilon' = 0.05$.
+    \caption{\textbf{Noise thresholds in unital fragment.} Mana and Lorenz curve noise thresholds for the Strange state purification process in~\cref{eq:dist} with $\epsilon' = 0.05$.
     Lorenz curve comparison consistently gives stricter bounds as proven in~\cref{thm:bounds}.
     The line $\epsilon = \frac{3}{4}$ indicates the threshold noise beyond which the Strange state no longer contains negativities. 
+    \nick{Redo figure}
     }
@@
 
-In~\cref{fig:unital_distill}, we examine the Strange state distillation process of~\cref{eq:dist} with $\epsilon' = 0.05$ which describes all circuits that respect the unital symmetry.
-Thresholds provided by Lorenz curve comparison are always much stricter than mana thresholds.
-\nick{Explain asymptotic behaviour?}
-
-\nick{We devote a section on Strange state Lorenz curve analysis in the unital fragment}
-
 \null\newpage
 
-\subsection{Strange state interconversions in the unital fragment}\label{sec:lcsu}
-
-In this section we analytically investigate the behaviour of the Lorenz curve of an $n$-copy Strange state in the unital fragment ($\sigma = \id/3$), 
+\subsubsection*{Strange state distillation in the unital fragment}\label{sec:lcsu}
+
+In this section we study the MSD process,
+\begin{equation}\label{eq:sudist}
+	\noisysn \xrightarrow{\E \in \O_{\id/3}} \noisys(\epsilon')\too{\tt} \otimes \left( \frac{1}{3}\id \right)\too{\mm},\ \nn = \tt + \mm,
+\end{equation}
+where we have uniformised the number of qutrits on both sides of the process.
+
+In~\cref{app:lcsu_technical}, we define explicit expressions for the Lorenz curve of the $n$-copy, $\epsilon$-noisy Strange state in the unital fragment, 
 \begin{equation}\label{eq:lcsu}
-	\lc{\noisysn}{\frac{1}{d}\id}(x),\ x\in[0,1].
-\end{equation}
-We recognise Lorenz curve of this type as ``standard candles'' in the context of magic state distillation and call them the \emph{standard Lorenz curves} \nick{expand}.
-
-The aim is to study the MSD process,
-\begin{equation}\label{eq:sudist}
-	\noisysn \xrightarrow{\E \in \O_{\id/3}} \noisys(\epsilon')\too{\kk},
-\end{equation}
-in the regime where $0 \leq \epsilon \leq \tfrac{3}{4}$.
-For $\tfrac{3}{4} \leq \epsilon < 1$, the noisy Strange state $\noisys(\epsilon)$ contains no Wigner negativities in the unital fragment as seen in~\cref{eq:wsu}.
-
-\subsubsection{Coordinate expressions for standard Lorenz curves}
-The Wigner distribution of the $\NN$-copy qutrit maximally mixed state $\left(\id/3\right)\too{\NN}$ is the uniform distribution 
-\begin{equation}\label{eq:wu}
-	\W{\left(\id/3\right)\too{\NN}} = \left( \overbrace{\frac{1}{9^\NN}, \dots, \frac{1}{9^\NN}}^{9^\NN} \right).
-\end{equation}
-The Wigner distribution of the 1-copy $\epsilon$-noisy Strange state $\noisys(\epsilon)$ in the unital fragment is a permutation of 
-\begin{equation}\label{eq:wsu}
-	\W{\noisys(\epsilon)} = \left( \overbrace{\frac{1}{6} - \frac{1}{18}\epsilon, \dots, \frac{1}{6} - \frac{1}{18}\epsilon}^8, \overbrace{-\frac{1}{3} + \frac{4}{9}\epsilon}^1 \right)
-\end{equation}
-The Wigner distribution of the $\NN$-copy $\epsilon$-noisy Strange state $\noisysN$ in the unital fragment is the $n$-th convolution $\W{\noisysN} = \rm{W}_{\noisys(\epsilon)}\too{N}$.
-
-For example, the Wigner distribution of state $\noisys(0)\too{2}$ is
-\begin{equation*}
-	\rm{W}_{\noisys(0)\too{2}} = \left( \overbrace{\left( -\frac{1}{3} \right)^2}^1, \overbrace{\left( \frac{1}{6} \right)^2, \dots, \left( \frac{1}{6} \right)^2}^{64}, \overbrace{ -\frac{1}{3} \cdot \frac{1}{6}, \dots, -\frac{1}{3} \cdot \frac{1}{6}}^{16} \right)
-\end{equation*}
-
-In~\cref{app:lcsu_technical}, we derive explicit expressions for the coordinates of standard Lorenz curves, which we present here.
-
-\nick{noisy maximum}
-Calculating the components of $\ket{S}\bra{S}\too{n}$ allows for analytical calculation of the maximum of the $n$-copy state,
-\begin{equation}\label{eq:Skmax}
-    \max_x{\lc{\ketbra{S}\too{n}} {\sigma}}(x) = \frac{1}{2}\left (1 + \left(\frac{5}{3}\right)^n \right).
-\end{equation}
-Its location $x_{k_\star}$ depends on the $\sigma$--fragment and is given by~\cref{eq:maxloc} with $k_\star = \frac{1}{2}(7^n + 9^n)$.
-%1 + \left(\frac{4}{3}\right)^n \sum\limits_{j=0}^{\floor{\frac{n-1}{2}}} 4^{-(2j+1)} \binom{n}{2j+1}
-%\sum_{i=j, j: odd}^n a^j \binom{n}{j} = \frac{1}{2} [ (1+a)^n - (1-a)^n ]
-%$\{(-1)^j 2^{j-n} 3^{-n}\}_{0 \leq j \leq n}$ with multiplicity $8^{n-j} \binom{n}{j}$ for the $j$-th term
-
-\subsubsection{Standard Lorenz curve comparison}
-
-Consider the Strange state purification process in the unital fragment,
-\begin{equation}\label{eq:su_conversion}
-    \noisysn \xrightarrow{\mathcal{O}_{\id/d}} \rho_{\rm{S}}(r, \epsilon', s),\ n = r + s.
-\end{equation}
-In order to get Lorenz curve constraints on this state conversion, we need a method to match up indices between the two curves.
-We use non-primed indices for the initial state and primed indices for the target state,
-\begin{align}
-    i(k, \alpha, \beta=1) &= 1 + (\alpha-1) + \sum_{j=0}^{k-1} 8^{2j}\binom{n}{2j}, \\
-    i'(k',\alpha',\beta') &= \beta' + \left[ (\alpha'-1) + \sum_{j'=0}^{k'-1} 8^{2j'}\binom{r}{2j'} \right]9^s,
-\end{align}
-for $i,i' = 1,2,\dots, \frac{1}{2}(7^{n} + 9^{n})$.
-
-For pointwise comparison of the two curves, we require $x_{i(k, \alpha)} = x_{i'(k', \alpha', \beta')}$, so the question is: \emph{Given a triplet $(k', \alpha', \beta')$, what is the tuple $(k, \alpha)$ such that $i(k, \alpha) = i'(k',\alpha',\beta')$?}
-
-In other words, we choose a fixed $i'(k',\alpha',\beta')$ and we are searching for $i(k, \alpha)$ such that 
-\begin{equation}
-	i(k, \alpha) = \alpha + \sum_{j=0}^{k-1} 8^{2j}\binom{n}{2j} \overset{!}{=} i'(k',\alpha',\beta').
-\end{equation}
-
-As a basic example, consider the process 
-\begin{equation}
-\rho_{\rm{S}}(\epsilon)\too{4} \xrightarrow{\mathcal{O}_{\id/d}} \rho_{\rm{S}}(\epsilon')\too{2} \otimes \left( \frac{1}{3}\id \right)\too{2}.
-\end{equation}
-We want to check which Lorenz curve is higher at the first elbows of the target state, i.e. we want to verify or reject the first inequality below:
-\begin{equation}
-	L_{i(k, \alpha)} \geq L'_{i'(0, 1, 81)}
-\end{equation}
-where the first multiplicity of the target state is $m_0 = 1$.
-The multiplicities of the initial state are $(1, 384, 4096)$
-Note that the second elbow of the target state (its maximum) lies on the RHS of the initial state curve's maximum, hence our expressions do not work on the coordinates of the initial state curve at that point \nick{yet}.
-
-The challenge is to find $k, \alpha$ such that $i(k, \alpha) = i'(0,1,81)$.
-\nick{By trial and error}, we find that $(k, \alpha) = (1, 80)$.
-Now we can use~\cref{eq:lcsu_lcoord} to directly calculate
-\begin{align*}
-	L'_{i'(0,1,81)} &= L'_0 = \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^2 \Phi_+\left(0;2,4\frac{3-\epsilon}{15-8\epsilon}\right), \\
-	L_{i(1, 80)} &= \left(1-\frac{80}{384} \right) L_0 + \frac{80}{384} L_1 \\
-	\begin{split}
-	&= \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^4 \bigg[ \frac{19}{24} \Phi_+\left(0;4,4\frac{3-\epsilon}{15-8\epsilon}\right) \\ 
-	&\qquad + \frac{5}{24}\Phi_+\left(2;4,4\frac{3-\epsilon}{15-8\epsilon}\right) \bigg],
-	\end{split}
-\end{align*}
-and then compare them.
-
-\nick{Returning to~\cref{eq:su_conversion}, and }using~\cref{thm:elbows}, the $r$ independent necessary constraints are
+	\lc{\noisys(\epsilon')\too{\tt} \otimes \left( \frac{1}{3}\id \right)\too{\mm}}{\frac{1}{d}\id}(x),\ x\in[0,1].
+\end{equation}
+We call Lorenz curves of this type \emph{standard Lorenz curves}. \nick{expand (non-uniformity)}
+
+It is clear in~\cref{fig:lcs} that Lorenz curves are fully defined by the coordinates of their elbows.
+For standard Lorenz curves, elbow coordinates are defined in terms of the two functions,
+\begin{align}	
+	\Phi_+(\mmf; \nnf, p) &\coloneqq \sum\limits_{\dummy=0}^{\mmf/2} \binom{\nnf}{2\dummy} p^{2\dummy} (1-p)^{\nnf-2\dummy}, \nonumber\\ 
+	&\text{for even integers } \mmf\in[0,\nnf], \label{eq:fp} \\
+	\Phi_-(\mmf; \nnf, p) &\coloneqq \sum\limits_{\dummy=1}^{(\mmf-1)/2} \binom{\nnf}{2\dummy+1} p^{2\dummy+1} (1-p)^{\nnf-(2\dummy+1)}, \nonumber\\ 
+	&\text{for odd integers } \mmf\in[1,\nnf]. \label{eq:fn}
+\end{align}
+Note that index $\mmf$ only takes even (odd) values when labelling $\Phi_+$ ($\Phi_-$).
+The exact expresions depend on the noise level $\epsilon$, the parity of the number of copies $\NN$ and whether the location of the elbow relative to the curve maximum (LHS vs RHS).
+All cases are presented in~\cref{tab:lcsu_coord_elb}.
+\begin{table}[h]
+  \def\arraystretch{1.5}
+  \centering
+  \begin{tabular}{c|c|c|r|r}
+    \multicolumn{3}{c|}{Case} & \multicolumn{1}{c}{$x_{\ii}$} & \multicolumn{1}{|c}{$L_{\ii}$} \\[0.5ex]\hline
+    \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$0\leq \epsilon < \frac{3}{7}$}}} & \hspace{0.8ex}\multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$\NN$ even}}}\hspace{0.8ex} & LHS & $\Phi_+\left(2\ii;\NN,\frac{8}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_+\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\
+    & & RHS & $x_{\NN/2} + \Phi_-\left(2\ii;\NN,\frac{1}{9}\right)$ & $L_{\NN/2} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_-\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
+    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$\NN$ odd}}} & LHS & $\Phi_-\left(2\ii;\NN,\frac{8}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_-\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\
+    & & RHS & $x_{\NN/2} + \Phi_-\left(2\ii;\NN,\frac{1}{9}\right)$ & $L_{\NN/2} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_-\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
+    \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$\frac{3}{7}\leq \epsilon < \frac{3}{4}$}}} & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$\NN$ even}}} & LHS & $\Phi_+\left(2\ii;\NN,\frac{1}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_+\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\
+    & & RHS & $x_{\NN/2} + \Phi_-\left(2\ii;\NN,\frac{8}{9}\right)$ & $L_{\NN/2} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_-\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
+    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$\NN$ odd}}} & LHS & $\Phi_+\left(2\ii;\NN,\frac{1}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_+\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\
+    & & RHS & $x_{\NN/2} + \Phi_+\left(2\ii;\NN,\frac{8}{9}\right)$ & $L_{\NN/2} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_+\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
+  \end{tabular}
+  \caption{Standard Lorenz curves elbow coordinates.
+  Multiplication $2\ii$ is considered modulo $(\NN+1)$.
+  Note that the Lorenz curve boundary points are $(x_{-1}, L_{-1}) \coloneqq (0,0)$ and $(x_{\NN}, L_{\NN}) = (1,1)$.
+  }
+  \label{tab:lcsu_coord_elb}
+\end{table}
+
+The coordinates of any point on the standard Lorenz curve is given by
+
+\begin{equation}
+    \II(\ii,\jj,\kk) \coloneqq \kk + \left[ (\jj-1) + \sum_{\dummy=0}^{\ii-1} 8^{2\dummy}\binom{\tt}{2\dummy} \right]9^{\mm},
+\end{equation}
+
+\begin{align}
+    \II(\ii,\jj,\kk=1) &= \jj + \sum_{\dummy=0}^{\ii-1} 8^{2\dummy}\binom{\nn}{2\dummy}, \\
+    \II'(\ii',\jj',\kk') &= \kk' + \left[ (\jj'-1) + \sum_{\dummy=0}^{\ii'-1} 8^{2\dummy}\binom{\tt}{2\dummy} \right]9^{\mm}.
+\end{align}
+
+In particular, it can used in the discussion of standard Lorenz curves to set the necessary constraints,
 \begin{align}
@@
 
-\begin{figure}[b]
+\begin{figure}[h]
     \centering
@@
 
-\begin{figure}
+\begin{figure}[h]
     \centering

### 2020-11-30 appendix.tex
added main text on LC

@@
 	\Phi_-(\mmf; \nnf, p) &\coloneqq \sum\limits_{\dummy=1}^{(\mmf-1)/2} \binom{\nnf}{2\dummy+1} p^{2\dummy+1} (1-p)^{\nnf-(2\dummy+1)}, \nonumber\\ 
-	&\text{for odd integers } \mmf\in[1,\nnf]. \label{eq:fn_app}
+	&\text{for odd integers } \mmf\in[0,\nnf]. \label{eq:fn_app}
 \end{align}
@@
 \begin{lemma}\label{lem:comb_bounds}
-	For all $\mmf\in [1,\nnf-1]$,
+	For all $\dummy\in [1,\nnf-1]$,
 	\begin{align}
-		&\left[ 8\mmf\left(1-\frac{\mmf}{\nnf}\right) \right]^{-\frac{1}{2}} 2^{\nnf S\left(\frac{\mmf}{\nnf}\right)} \leq \binom{\nnf}{\mmf} \leq \\
-		&\left[ 2\pi \mmf\left(1-\frac{\mmf}{\nnf}\right) \right]^{-\frac{1}{2}} 2^{\nnf S\left(\frac{\mmf}{\nnf}\right)}.
+		&\left[ 8\dummy\left(1-\frac{\dummy}{\nnf}\right) \right]^{-\frac{1}{2}} 2^{\nnf S\left(\frac{\dummy}{\nnf}\right)} \leq \binom{\nnf}{\dummy} \leq \\
+		&\left[ 2\pi \dummy\left(1-\frac{\dummy}{\nnf}\right) \right]^{-\frac{1}{2}} 2^{\nnf S\left(\frac{\dummy}{\nnf}\right)}.
 	\end{align}
@@
 \begin{proof}
-	For $\mmf = 1,2, \nnf-1, \nnf-2$ check by direct calculation.	
+	For $\dummy = 1,2, \nnf-1, \nnf-2$ check by direct calculation.	
 	For all other cases, use Stirling's approximation. 
@@
 This theorem is of practical importance in calculating the necessary distillation constraints derived via majorization.
+
+In particular, it can be used in the discussion of standard Lorenz curves to set the necessary constraints,
+\begin{align}
+L\left(x_{i'(0, \mlt'_{0}, 9^{\mm})}\right) &\geq L\left(x_{i'(0, m'_{0}, 9^{\mm})}\right), \nonumber\\
+L\left(x_{i'(1, \mlt'_{1}, 9^{\mm})}\right) &\geq L\left(x_{i'(1, m'_{1}, 9^{\mm})}\right), \nonumber\\
+&\vdotswithin{=} \nonumber\\
+L\left(x_{i'(\tt, \mlt'_{r}, 9^{\mm})}\right) &\geq L\left(x_{i'(\tt, m'_{\tt}, 9^{\mm})}\right), \nonumber
+\end{align}
+where $x_{i'(0, \mlt'_{0}, 9^{\mm'})}, x_{i'(1, \mlt'_{1}, 9^{\mm'})}, \dots, x_{i'(\tt, \mlt'_{\tt}, 9^{\mm'})} \in T$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon')\too{\tt}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).

### 2020-11-30 magic_paper.tex
added main text on LC

@@
 A proof is provided in~\cref{app:lc_constraints}.
+Any of the $t$ inequalities in the theorem provides a valid contraint leading to some upper distillation bound, and the more one cosiders, the stricter the bound is.
 
@@
 
-In~\cref{app:lcsu_technical}, we define explicit expressions for the Lorenz curve of the $n$-copy, $\epsilon$-noisy Strange state in the unital fragment, 
+In~\cref{app:lcsu_technical}, we define explicit expressions for the Lorenz curve of the $\NN$-copy, $\epsilon$-noisy Strange state in the unital fragment, 
 \begin{equation}\label{eq:lcsu}
@@
 
-It is clear in~\cref{fig:lcs} that Lorenz curves are fully defined by the coordinates of their elbows.
-For standard Lorenz curves, elbow coordinates are defined in terms of the two functions,
+Lorenz curves are fully defined by the coordinates of their elbows which is clear in~\cref{fig:lcs} for the Strange state in particular.
+The exact expressions for the elbow coordinates of a standard Lorenz curve can take $2^3 = 8$ different forms, depending on whether the noise level $\epsilon$ is low/high, the parity of the number of copies $\NN$ is even/odd and the location of the elbow relative to the maximum is on the left hand side (LHS -- includes maximum) / right hand side (RHS).
+They are given in full detail in~\cref{app:lcsu_coord_elb}.
+
+Here we focus on the part of the process described by the LHS of the Lorenz curves, in low noise regimes ($0 \leq \epsilon < 3/7$) with even numbers of initial and target copies.
+In this case, the elbow expressions of the standard Lorenz curve in~\cref{eq:lcsu} are given by
 \begin{align}
-	\Phi_+(\mmf; \nnf, p) &\coloneqq \sum\limits_{\dummy=0}^{\mmf/2} \binom{\nnf}{2\dummy} p^{2\dummy} (1-p)^{\nnf-2\dummy}, \nonumber\\ 
-	&\text{for even integers } \mmf\in[0,\nnf], \label{eq:fp} \\
-	\Phi_-(\mmf; \nnf, p) &\coloneqq \sum\limits_{\dummy=1}^{(\mmf-1)/2} \binom{\nnf}{2\dummy+1} p^{2\dummy+1} (1-p)^{\nnf-(2\dummy+1)}, \nonumber\\ 
-	&\text{for odd integers } \mmf\in[1,\nnf]. \label{eq:fn}
-\end{align}
-Note that index $\mmf$ only takes even (odd) values when labelling $\Phi_+$ ($\Phi_-$).
-The exact expresions depend on the noise level $\epsilon$, the parity of the number of copies $\NN$ and whether the location of the elbow relative to the curve maximum (LHS vs RHS).
-All cases are presented in~\cref{tab:lcsu_coord_elb}.
-\begin{table}[h]
-  \def\arraystretch{1.5}
-  \centering
-  \begin{tabular}{c|c|c|r|r}
-    \multicolumn{3}{c|}{Case} & \multicolumn{1}{c}{$x_{\ii}$} & \multicolumn{1}{|c}{$L_{\ii}$} \\[0.5ex]\hline
-    \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$0\leq \epsilon < \frac{3}{7}$}}} & \hspace{0.8ex}\multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$\NN$ even}}}\hspace{0.8ex} & LHS & $\Phi_+\left(2\ii;\NN,\frac{8}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_+\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\
-    & & RHS & $x_{\NN/2} + \Phi_-\left(2\ii;\NN,\frac{1}{9}\right)$ & $L_{\NN/2} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_-\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
-    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$\NN$ odd}}} & LHS & $\Phi_-\left(2\ii;\NN,\frac{8}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_-\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\
-    & & RHS & $x_{\NN/2} + \Phi_-\left(2\ii;\NN,\frac{1}{9}\right)$ & $L_{\NN/2} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_-\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
-    \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$\frac{3}{7}\leq \epsilon < \frac{3}{4}$}}} & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$\NN$ even}}} & LHS & $\Phi_+\left(2\ii;\NN,\frac{1}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_+\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\
-    & & RHS & $x_{\NN/2} + \Phi_-\left(2\ii;\NN,\frac{8}{9}\right)$ & $L_{\NN/2} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_-\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
-    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$\NN$ odd}}} & LHS & $\Phi_+\left(2\ii;\NN,\frac{1}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_+\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\
-    & & RHS & $x_{\NN/2} + \Phi_+\left(2\ii;\NN,\frac{8}{9}\right)$ & $L_{\NN/2} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_+\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
-  \end{tabular}
-  \caption{Standard Lorenz curves elbow coordinates.
-  Multiplication $2\ii$ is considered modulo $(\NN+1)$.
-  Note that the Lorenz curve boundary points are $(x_{-1}, L_{-1}) \coloneqq (0,0)$ and $(x_{\NN}, L_{\NN}) = (1,1)$.
-  }
-  \label{tab:lcsu_coord_elb}
-\end{table}
-
-The coordinates of any point on the standard Lorenz curve is given by
-
-\begin{equation}
-    \II(\ii,\jj,\kk) \coloneqq \kk + \left[ (\jj-1) + \sum_{\dummy=0}^{\ii-1} 8^{2\dummy}\binom{\tt}{2\dummy} \right]9^{\mm},
-\end{equation}
-
+	x_i &= \Phi_+\left(2\ii;\NN,\frac{8}{9}\right), \\
+	L_i &= \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_+\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right),
+\end{align}
+for $i=0,\dots,\frac{\NN}{2}$, where
+\begin{equation}
+	\Phi_+(\mmf; \nnf, p) \coloneqq \sum\limits_{\dummy=0}^{\mmf/2} \binom{\nnf}{2\dummy} p^{2\dummy} (1-p)^{\nnf-2\dummy}.
+\end{equation}
+Conventionally, we set $(x_{-1}, L_{-1}) = (0,0)$.
+
+The coordinates of any point on the Lorenz curve LHS can be expressed as convex sums of the neighbouring elbows,
 \begin{align}
-    \II(\ii,\jj,\kk=1) &= \jj + \sum_{\dummy=0}^{\ii-1} 8^{2\dummy}\binom{\nn}{2\dummy}, \\
-    \II'(\ii',\jj',\kk') &= \kk' + \left[ (\jj'-1) + \sum_{\dummy=0}^{\ii'-1} 8^{2\dummy}\binom{\tt}{2\dummy} \right]9^{\mm}.
-\end{align}
-
-In particular, it can used in the discussion of standard Lorenz curves to set the necessary constraints,
-\begin{align}
-\lc{\noisysn}{\frac{1}{d}\id}\left(x_{i'(0, m'_{0}, 9^{s})}\right) &\geq \lc{\rho_{\rm{S}}(\epsilon')\too{k}}{\frac{1}{d}\id}\left(x_{i'(0, m'_{0}, 9^{s})}\right), \nonumber\\
-\lc{\noisysn}{\frac{1}{d}\id}\left(x_{i'(1, m'_{1}, 9^{s})}\right) &\geq \lc{\rho_{\rm{S}}(\epsilon')\too{k}}{\frac{1}{d}\id}\left(x_{i'(1, m'_{1}, 9^{s})}\right), \nonumber\\
-&\vdotswithin{=} \nonumber\\
-\lc{\noisysn}{\frac{1}{d}\id}\left(x_{i'(r, m'_{r}, 9^{s})}\right) &\geq \lc{\rho_{\rm{S}}(\epsilon')\too{k}}{\frac{1}{d}\id}\left(x_{i'(r, m'_{r}, 9^{s})}\right), \nonumber
-\end{align}
-where $x_{i'(0, m'_{0}, 9^{s'})}, x_{i'(1, m'_{1}, 9^{s'})}, \dots, x_{i'(r, m'_{r}, 9^{s'})} \in T$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon')\too{r}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).
+    x_{\ii\jj\kk} &= \left( 1-p_{\ii\jj\kk}\right) x_{\ii-1} + p_{\ii\jj\kk} x_{\ii} \label{eq:lcsu_xcoord}\\
+    L_{\ii\jj\kk} &= \left( 1-p_{\ii\jj\kk} \right) L_{\ii-1} + p_{\ii\jj\kk} L_{\ii}, \label{eq:lcsu_lcoord}
+\end{align}
+where we use a three-index parametrisation for the coordinates, with $\ii$ determined by the count of the elbow that follows, $\jj$ by the number of Strange state copies and $\kk$ by the number of tensored maximally mixed state copies.
+Therefore, for the initial state $\noisysn$ we have
+\begin{equation}
+	p_{\ii\jj\kk} = \frac{\jj}{8^{2\ii}\binom{\nn}{2\ii}},
+\end{equation}
+with $\ii=0,\dots,\nn,\ \jj(\ii) = 1,\dots,8^{2\ii}\binom{\nn}{2\ii}$ and $\kk = 1$.
+For the target state $\noisys(\epsilon')\too{\tt} \otimes \left( \frac{1}{3}\id \right)\too{\mm}$,
+\begin{equation}
+	p_{\ii\jj\kk} = \frac{\kk + (\jj-1)9^{\mm}}{9^{\mm} 8^{2\ii}\binom{\tt}{2\ii}}
+\end{equation}
+with $\ii=0,\dots,\tt,\ \jj(\ii) = 1,\dots,8^{2\ii}\binom{\tt}{2\ii}$ and $\kk = 1,\dots,9^{\mm}$.
 

### 2020-11-30 appendix.tex
LC stuff

@@
 
+According to~\cref{thm:elbows} which is proved in~\cref{app:lc_constraints}, for standard Lorenz curves, we need to match indices at the target state elbows, so the requirement on the indices is finding a tuple $(\ii, \jj)$, such that for a given $\ii' = 0,\dots,\tt$,
+\begin{equation}
+	\jj + \sum_{\dummy=0}^{\ii-1} \mlt_{\dummy}(\nn, \epsilon) = \sum_{\dummy=0}^{\ii'} \mlt_{\dummy}(\tt, \epsilon').
+\end{equation}
+
 As a basic example, consider the process 
 \begin{equation}
-\rho_{\rm{S}}(\epsilon)\too{4} \xrightarrow{\mathcal{O}_{\id/d}} \rho_{\rm{S}}(\epsilon')\too{2} \otimes \left( \frac{1}{3}\id \right)\too{2}.
+\rho_{\rm{S}}(\epsilon)\too{4} \xrightarrow{\mathcal{O}_{\id/3}} \rho_{\rm{S}}(\epsilon')\too{2} \otimes \left( \frac{1}{3}\id \right)\too{2}.
 \end{equation}
@@
 \begin{align}
-L\left(x_{i'(0, \mlt'_{0}, 9^{\mm})}\right) &\geq L\left(x_{i'(0, m'_{0}, 9^{\mm})}\right), \nonumber\\
-L\left(x_{i'(1, \mlt'_{1}, 9^{\mm})}\right) &\geq L\left(x_{i'(1, m'_{1}, 9^{\mm})}\right), \nonumber\\
+L\left(x_{\II'(0, \mlt'_{0}, 9^{\mm})}\right) &\geq L\left(x_{\II'(0, m'_{0}, 9^{\mm})}\right), \nonumber\\
+L\left(x_{\II'(1, \mlt'_{1}, 9^{\mm})}\right) &\geq L\left(x_{\II'(1, m'_{1}, 9^{\mm})}\right), \nonumber\\
 &\vdotswithin{=} \nonumber\\
-L\left(x_{i'(\tt, \mlt'_{r}, 9^{\mm})}\right) &\geq L\left(x_{i'(\tt, m'_{\tt}, 9^{\mm})}\right), \nonumber
+L\left(x_{\II'(\tt, \mlt'_{r}, 9^{\mm})}\right) &\geq L\left(x_{\II'(\tt, m'_{\tt}, 9^{\mm})}\right), \nonumber
 \end{align}
-where $x_{i'(0, \mlt'_{0}, 9^{\mm'})}, x_{i'(1, \mlt'_{1}, 9^{\mm'})}, \dots, x_{i'(\tt, \mlt'_{\tt}, 9^{\mm'})} \in T$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon')\too{\tt}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).
+where $x_{\II'(0, \mlt'_{0}, 9^{\mm'})}, x_{\II'(1, \mlt'_{1}, 9^{\mm'})}, \dots, x_{\II'(\tt, \mlt'_{\tt}, 9^{\mm'})} \in T$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon')\too{\tt}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).

### 2020-11-30 magic_paper.tex
LC stuff

@@
 \begin{equation}
-	\Phi_+(\mmf; \nnf, p) \coloneqq \sum\limits_{\dummy=0}^{\mmf/2} \binom{\nnf}{2\dummy} p^{2\dummy} (1-p)^{\nnf-2\dummy}.
+	\Phi_+(2\mmf; \nnf, p) \coloneqq \sum\limits_{\dummy=0}^{\mmf} \binom{\nnf}{2\dummy} p^{2\dummy} (1-p)^{\nnf-2\dummy}.
 \end{equation}
@@
 \end{equation}
-with $\ii=0,\dots,\nn,\ \jj(\ii) = 1,\dots,8^{2\ii}\binom{\nn}{2\ii}$ and $\kk = 1$.
+with $\ii=0,\dots,\frac{\nn}{2},\ \jj(\ii) = 1,\dots,8^{2\ii}\binom{\nn}{2\ii}$ and $\kk = 1$.
 For the target state $\noisys(\epsilon')\too{\tt} \otimes \left( \frac{1}{3}\id \right)\too{\mm}$,
 \begin{equation}
-	p_{\ii\jj\kk} = \frac{\kk + (\jj-1)9^{\mm}}{9^{\mm} 8^{2\ii}\binom{\tt}{2\ii}}
-\end{equation}
-with $\ii=0,\dots,\tt,\ \jj(\ii) = 1,\dots,8^{2\ii}\binom{\tt}{2\ii}$ and $\kk = 1,\dots,9^{\mm}$.
+	p_{\ii'\jj'\kk'} = \frac{\kk' + (\jj'-1)9^{\mm}}{9^{\mm} 8^{2\ii'}\binom{\tt}{2\ii'}}
+\end{equation}
+with $\ii'=0,\dots,\frac{\tt}{2},\ \jj'(\ii') = 1,\dots,8^{2\ii'}\binom{\tt}{2\ii'}$ and $\kk' = 1,\dots,9^{\mm}$.
+
+Pointwise Lorenz curve comparison requires $x_{\ii\jj\kk} = x_{\ii'\jj'\kk'}$, so we need ot match up the indices appropriately in order to compare $L_{\ii\jj\kk}$ and $L_{\ii'\jj'\kk'}$.
+In~\cref{app:lc_compare}, we show that the requirement on the indices is finding a tuple $(\ii, \jj(\ii))$, such that for a given $\ii' = 0,\dots,\frac{\tt}{2}$,
+\begin{equation}
+	\jj + \sum_{\dummy=0}^{\ii-1} 8^{2\dummy}\binom{\nn}{2\dummy} = \sum_{\dummy=0}^{\ii'} 8^{2\dummy}\binom{\tt}{2\dummy}.
+\end{equation}
 

### 2020-12-01 appendix.tex
Tidying up of main text. Theory added yielding compact bounds on Phi+. Needs checking.

--- 2020-11-30 appendix.tex
@@
 where $x_{i'(0, \mlt'_{0}, 9^{\mm'})}, x_{i'(1, \mlt'_{1}, 9^{\mm'})}, \dots, x_{i'(\tt, \mlt'_{\tt}, 9^{\mm'})} \in T$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon')\too{\tt}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).
+
+\section{Theory on bounding the core functions}
+The core function is $\Phi_+$ which is an even power cumulative function.
+We have good asymptotic bounds on the behaviour of the standard cumulative function $\Phi$, and the difference between these two functions is essentially given by the function
+\begin{equation}
+S(a,r,n) := \sum_{k=0}^r \binom{n}{k} (-a)^k.
+\end{equation}
+If we define the cumulative distribution function as
+\begin{equation} 
+\Phi(a,r,n) := \sum_{k=0}^r \binom{n}{k} a^k,
+\end{equation}
+then we have the simple relation
+\begin{equation}
+\Phi_+(a,r,n) = \frac{1}{2}( \Phi(a,r,n)  + S(a,r,n)).
+\end{equation}
+We would like some theory that estimates the value of this function for different parameter regimes.
+We can consider the function $f(x) = (1+x)^n$ and note that the function $S(a,r,n)$ is the $r$'th partial sum of this expansion at the point $x=-a$.
+
+The truncated Taylor series tells us (e.g. see Wolfram MathWorld) that
+\begin{equation}
+f(x) = f(x_0) + (x-x_0) f'(x_0) + \dots \frac{(x-x_0)^r}{r!}f^{(r)}(x_0) + R_r(x)
+\end{equation}
+with a remainder term
+\begin{align}
+R_r (x)&= \int_{x_0}^x dt f^{(r+1)}(t) \frac{(x-t)^r}{r!} \\
+&= \frac{(x-x_0)^{r+1}}{(r+1)!} f^{(r+1)}(x_*),
+\end{align}
+where in the second expression $x_* \in [x_0,x]$ is an implicit point that comes from the Mean Value Theorem.
+
+Applying this to the function $f(x) = (1+x)^n$ with $x_0=0$ gives
+\begin{equation}
+(1+x)^n = \sum_{k=0}^r \binom{n}{k} x^k + R_r.
+\end{equation}
+Evaluating at $x=-a$ then gives us
+\begin{equation}
+S(a,r,n) = (1-a)^n - R_r(-a),
+\end{equation}
+where the key remainder term is given by
+\begin{align}
+R_r(-a) &= \int_0^{-a} dt f^{(r+1)}(t) \frac{(-a-t)^r}{r!} \\
+&= \frac{(-a)^{r+1}}{(r+1)!} f^{(r+1)}(x_*).
+\end{align}
+We can also compute the derivative $f^{(r+1)}(x)$ explicitly, and get
+\begin{equation}
+f^{(r+1)}(x) = \frac{n!}{(n-r-1)!}(1+x)^{n-r-1}.
+\end{equation}
+Therefore, we have that
+\begin{align}
+R_r(-a) &= \frac{(-1)^r n!}{r!(n-r-1)!}\int_0^{-a} dt(1+t)^{n-r-1} (a+t)^r \\
+&= \frac{(-a)^{r+1}}{r!} \binom{n}{r+1}(1+x_*)^{n-r-1},
+\end{align}
+where in the latter expression $x_* \in [-a,0]$.
+Also note that the first integral expression can be estimated via either Cauchy-Schwarz or the Hoelder inequality.
+Therefore, we can either work with an explicit form with an unknown (but bounded) parameter $x_*$, or we can use the integral form and provide concrete estimates on it value.
+
+A very simple estimate, based on $x_*$ lying in the interval $[-a,0]$ gives
+\begin{equation}
+\frac{(-a)^{r+1}}{r!} \binom{n}{r+1} (1-a_*)^{n-r-1}\le R_r(-a) \le  \frac{(-a)^{r+1}}{r!} \binom{n}{r+1}.
+\end{equation}
+
+This in turn leads to the following bounds on $\Phi_+(a,r,n)$:
+\begin{align}
+\hspace{-2cm}2\Phi_+(a,r,n) &\le \Phi(a,r,n)+ (1-a)^n - \frac{(-a)^{r+1}}{r!} \binom{n}{r+1} (1-a)^{n-r-1} \nonumber \\
+2\Phi_+(a,r,n) & \ge\Phi(a,r,n)+ (1-a)^n - \frac{(-a)^{r+1}}{r!} \binom{n}{r+1} .
+\end{align}
+Details need checking to see if I dropped any constants/signs. Are these bounds good in practice? Asymptotically?

### 2020-12-01 magic_paper.tex
Tidying up of main text. Theory added yielding compact bounds on Phi+. Needs checking.

--- 2020-11-30 magic_paper.tex
@@
 
-\subsubsection*{Strange state distillation in the unital fragment}\label{sec:lcsu}
-
-In this section we study the MSD process,
+\subsection{Strange state distillation in the unital fragment}\label{sec:lcsu}
+
+We would now like to study the constraints coming soley from majorization in the unital fragment.
+We consider the problem of purifying $n$ copies of a noisy strange state $\rho(\epsilon)^{\otimes n}$ into a smaller number of $t$ copies of a less noisy strange state $\rho(\epsilon')^{\otimes t}$, with $\epsilon' \le \epsilon$.
+Since the state $\frac{1}{3} \I$ is  free state in this fragment the interconversion problem is unaffected if we tensor in copies of this maximally mixed state.
+This turns out to simply the Lorenz curve analysis, and so we focus on the process,
 \begin{equation}\label{eq:sudist}
-	\noisysn \xrightarrow{\E \in \O_{\id/3}} \noisys(\epsilon')\too{\tt} \otimes \left( \frac{1}{3}\id \right)\too{\mm},\ \nn = \tt + \mm,
-\end{equation}
-where we have uniformised the number of qutrits on both sides of the process.
+	\rho_S(\epsilon)^{\otimes 2n} \longrightarrow\sigma(\epsilon', n, t):=  \rho_S(\epsilon')^{\otimes 2t} \otimes \left( \frac{1}{3}\id \right)^{\otimes2n-2t}.
+\end{equation}
+Since the state on left-hand side of this of the form $\sigma(\epsilon, n, 0)$ it suffices to construct the Lorenz curve $L_\sigma(x)$ for the generic noisy strange state $\sigma(\epsilon, n ,t)$.
+For simplicity we assume that $\epsilon \le 3/7$, which is the threshold below which negativity is present in the state.
+
+The state $\sigma(\epsilon, n, t)$ has the following Wigner quasi-distribution takes on values $w_k$, with associated multiplicities $m_k$ where
+\begin{align}
+w_k &=  \\
+m_k &=
+\end{align}
+From this, it is readily seen that $L_\sigma(x)$ has elbows to the left-hand side of its peak located at points $x=x_i$ where
+\begin{equation}
+x_i = \Phi_+ (i, n , \frac{8}{9}),
+\end{equation}
+with $ i = 0,1, \dots , n$ and where $\Phi_+(i,n,p)$ is an even-power cumulant distribution function given by
+\begin{equation}
+\Phi_+( i, n,p) := \sum_{k=0}^{i} \binom{2n}{2k} p ^{2k} (1-p)^{2n-2k}.
+\end{equation}
+The value of the Lorenz curve at an elbow is given by
+\begin{equation}
+L_\sigma(x_i) \equiv L_i =  \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^{2n} \Phi_+\left(i;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right),
+\end{equation}
+and we define $(x_{-1}, L_{-1}) = (0,0)$.
 
@@
 \begin{equation}\label{eq:lcsu}
-	\lc{\noisys(\epsilon')\too{\tt} \otimes \left( \frac{1}{3}\id \right)\too{\mm}}{\frac{1}{d}\id}(x),\ x\in[0,1].
-\end{equation}
-We call Lorenz curves of this type \emph{standard Lorenz curves}. \nick{expand (non-uniformity)}
+	\lc{\noisys(\epsilon')\too {\tt} \otimes \left( \frac{1}{3}\id \right)\too{\mm}}{\frac{1}{d}\id}(x),\ x\in[0,1].
+\end{equation}
 
@@
 They are given in full detail in~\cref{app:lcsu_coord_elb}.
-
-Here we focus on the part of the process described by the LHS of the Lorenz curves, in low noise regimes ($0 \leq \epsilon < 3/7$) with even numbers of initial and target copies.
-In this case, the elbow expressions of the standard Lorenz curve in~\cref{eq:lcsu} are given by
-\begin{align}
-	x_i &= \Phi_+\left(2\ii;\NN,\frac{8}{9}\right), \\
-	L_i &= \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_+\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right),
-\end{align}
-for $i=0,\dots,\frac{\NN}{2}$, where
-\begin{equation}
-	\Phi_+(\mmf; \nnf, p) \coloneqq \sum\limits_{\dummy=0}^{\mmf/2} \binom{\nnf}{2\dummy} p^{2\dummy} (1-p)^{\nnf-2\dummy}.
-\end{equation}
-Conventionally, we set $(x_{-1}, L_{-1}) = (0,0)$.
 

### 2020-12-03 appendix.tex

--- 2020-11-30 appendix.tex
@@
 \begin{align}
-&\text{LHS: } 0 \leq \ii \leq \frac{\lfloor \NN \rfloor}{2}; \\
-&\text{RHS: } \frac{\lfloor \NN \rfloor}{2}+1 \leq \ii \leq \NN.
+&\text{LHS: } 0 \leq \ii \leq \left\lfloor \frac{\NN}{2} \right\rfloor ; \\
+&\text{RHS: } \left\lfloor \frac{\NN}{2} \right\rfloor +1 \leq \ii \leq \NN.
 \end{align}
@@
     \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$0\leq \epsilon < \frac{3}{7}$}}} & \hspace{0.8ex}\multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$\NN$ even}}}\hspace{0.8ex} & LHS & $\Phi_+\left(2\ii;\NN,\frac{8}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_+\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\
-    & & RHS & $x_{\NN/2} + \Phi_-\left(2\ii;\NN,\frac{1}{9}\right)$ & $L_{\NN/2} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_-\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
+    & & RHS & $x_{\lfloor \NN/2 \rfloor} + \Phi_-\left(2\ii;\NN,\frac{1}{9}\right)$ & $L_{\lfloor \NN/2 \rfloor} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_-\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
     & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$\NN$ odd}}} & LHS & $\Phi_-\left(2\ii;\NN,\frac{8}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_-\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\
-    & & RHS & $x_{\NN/2} + \Phi_-\left(2\ii;\NN,\frac{1}{9}\right)$ & $L_{\NN/2} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_-\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
+    & & RHS & $x_{\lfloor \NN/2 \rfloor} + \Phi_-\left(2\ii;\NN,\frac{1}{9}\right)$ & $L_{\lfloor \NN/2 \rfloor} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_-\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
     \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$\frac{3}{7}\leq \epsilon < \frac{3}{4}$}}} & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$\NN$ even}}} & LHS & $\Phi_+\left(2\ii;\NN,\frac{1}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_+\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\
-    & & RHS & $x_{\NN/2} + \Phi_-\left(2\ii;\NN,\frac{8}{9}\right)$ & $L_{\NN/2} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_-\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
+    & & RHS & $x_{\lfloor \NN/2 \rfloor} + \Phi_-\left(2\ii;\NN,\frac{8}{9}\right)$ & $L_{\lfloor \NN/2 \rfloor} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_-\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
     & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$\NN$ odd}}} & LHS & $\Phi_+\left(2\ii;\NN,\frac{1}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_+\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\
-    & & RHS & $x_{\NN/2} + \Phi_+\left(2\ii;\NN,\frac{8}{9}\right)$ & $L_{\NN/2} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_+\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
+    & & RHS & $x_{\lfloor \NN/2 \rfloor} + \Phi_+\left(2\ii;\NN,\frac{8}{9}\right)$ & $L_{\lfloor \NN/2 \rfloor} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_+\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
   \end{tabular}
@@
 \begin{equation*}
-    \noisys(\epsilon)\too{\tt} \otimes \left( \frac{1}{3}\id \right)\too{\mm},
-\end{equation*} %\noisys(\tt, \epsilon, \mm) \coloneqq 
-with $\tt + \mm = \NN$.
+\noisys(\tt, \epsilon, \nn-\tt) \coloneqq \noisys(\epsilon)\too{\tt} \otimes \left( \frac{1}{3}\id \right)\too{(\nn-\tt)},
+\end{equation*}
 
@@
     &L_{\ii\jj\kk} = \left( 1-p_{\ii\jj\kk} \right) L_{\ii-1} + p_{\ii\jj\kk} L_{\ii}, \label{eq:lcsu_lcoord}\\
-    &\text{where } p_{\ii\jj\kk} = \frac{\kk + (\jj-1)9^{\mm}}{9^{\mm} \mlt_{\ii}} \nonumber\\
-    &\text{for } \ii=0,\dots,\tt,\ \jj = 1,\dots,\mlt_{\ii}(\tt, \epsilon') \text{ and } \kk = 1,\dots,9^{\mm}. \nonumber
+    &\text{where } p_{\ii\jj\kk} = \frac{\kk + (\jj-1)9^{\nn-\tt}}{9^{\nn-\tt} \mlt_{\ii}} \nonumber\\
+    &\text{for } \ii=0,\dots,\tt,\ \jj = 1,\dots,\mlt_{\ii}(\tt, \epsilon') \text{ and } \kk = 1,\dots,9^{\nn-\tt}. \nonumber
 \end{align}
@@
 \begin{equation}
-    \II(\ii,\jj,\kk) \coloneqq \kk + \left[ (\jj-1) + \sum_{\dummy=0}^{\ii-1} \mlt_{\dummy}(\tt, \epsilon') \right]9^{\mm},
+    \II(\ii,\jj,\kk) \coloneqq \kk + \left[ (\jj-1) + \sum_{\dummy=0}^{\ii-1} \mlt_{\dummy}(\tt, \epsilon') \right]9^{\nn-\tt},
 \end{equation}
@@
 \begin{equation}
-	\II(\ii, \mlt_{\ii}(\tt, \epsilon'), 9^{\mm}) = \sum_{\dummy=0}^{\ii} \mlt_{\dummy}(\tt, \epsilon'),\ \ii= 0,\dots,\tt.
+	\II(\ii, \mlt_{\ii}(\tt, \epsilon'), 9^{\nn-\tt}) = \sum_{\dummy=0}^{\ii} \mlt_{\dummy}(\tt, \epsilon'),\ \ii= 0,\dots,\tt.
 \end{equation}
@@
 \begin{equation}\label{eq:su_conversion}
-    \noisysn \xrightarrow{\mathcal{O}_{\id/3}} \noisys(\tt, \epsilon', \mm),\ \nn = \tt + \mm.
+    \noisys(\tt, \epsilon, 0) \xrightarrow{\mathcal{O}_{\id/3}} \noisys(\tt, \epsilon', \nn-\tt).
 \end{equation}
@@
     \II(\ii,\jj,\kk=1) &= \jj + \sum_{\dummy=0}^{\ii-1} \mlt_{\dummy}(\nn, \epsilon), \\
-    \II'(\ii',\jj',\kk') &= \kk' + \left[ (\jj'-1) + \sum_{\dummy=0}^{\ii'-1} \mlt_{\dummy}(\tt, \epsilon') \right]9^{\mm}.
+    \II'(\ii',\jj',\kk') &= \kk' + \left[ (\jj'-1) + \sum_{\dummy=0}^{\ii'-1} \mlt_{\dummy}(\tt, \epsilon') \right]9^{\nn-\tt}.
 \end{align}
@@
 \begin{align}
-L\left(x_{\II'(0, \mlt'_{0}, 9^{\mm})}\right) &\geq L\left(x_{\II'(0, m'_{0}, 9^{\mm})}\right), \nonumber\\
-L\left(x_{\II'(1, \mlt'_{1}, 9^{\mm})}\right) &\geq L\left(x_{\II'(1, m'_{1}, 9^{\mm})}\right), \nonumber\\
+L\left(x_{\II'(0, \mlt'_{0}, 9^{\nn-\tt})}\right) &\geq L\left(x_{\II'(0, m'_{0}, 9^{\nn-\tt})}\right), \nonumber\\
+L\left(x_{\II'(1, \mlt'_{1}, 9^{\nn-\tt})}\right) &\geq L\left(x_{\II'(1, m'_{1}, 9^{\nn-\tt})}\right), \nonumber\\
 &\vdotswithin{=} \nonumber\\
-L\left(x_{\II'(\tt, \mlt'_{r}, 9^{\mm})}\right) &\geq L\left(x_{\II'(\tt, m'_{\tt}, 9^{\mm})}\right), \nonumber
+L\left(x_{\II'(\tt, \mlt'_{r}, 9^{\nn-\tt})}\right) &\geq L\left(x_{\II'(\tt, m'_{\tt}, 9^{\nn-\tt})}\right), \nonumber
 \end{align}
-where $x_{\II'(0, \mlt'_{0}, 9^{\mm'})}, x_{\II'(1, \mlt'_{1}, 9^{\mm'})}, \dots, x_{\II'(\tt, \mlt'_{\tt}, 9^{\mm'})} \in T$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon')\too{\tt}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).
+where $x_{\II'(0, \mlt'_{0}, 9^{\nn - \tt})}, x_{\II'(1, \mlt'_{1}, 9^{\nn - \tt})}, \dots, x_{\II'(\tt, \mlt'_{\tt}, 9^{\nn - \tt})} \in T$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon')\too{\tt}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).
+
+\section{Theory on bounding the core functions}
+The core functions are $\Phi_{\pm}$ which is an even power cumulative function. 
+We can rewrite it as
+\begin{equation}
+\Phi_{\pm}(m; n, a) = \frac{1}{2}( \Phi(m; n, a) \pm (1+a)^{-n} S(m; n, a) ),
+\end{equation}
+where we have substituted $a = p/(1-p)$. 
+$\Phi$ is the standard cumulative function 
+\begin{equation}
+	\Phi(m; n, a) = (1+a)^{-n} \sum_{k=0}^m \binom{n}{k} a^k,
+\end{equation}
+and the remainder term is
+\begin{equation}
+S(m; n, a) \coloneqq \sum_{k=0}^m \binom{n}{k} (-a)^k.
+\end{equation}
+We have good asymptotic bounds on the behaviour of $\Phi$~\cite{cit:ash},
+\begin{lemma}\label{lem:phil_bounds}
+	Given fixed $n>0$ and $p$, $\Phi_\ell$ satisfies the following bounds:
+	\begin{align*}
+		\begin{split}
+		&\text{1. } \Phi(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ents},\ m\in [1,n-1] \\
+		&\text{2. } \Phi(m; n, p) \leq 2^{-n\ents},\ m\in [0,np] \\
+		&\text{3. } \Phi(m; n, p) \leq 1 - \left[ 8(m+1)\left(1-\frac{m+1}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m+1}{n}}{p}}, \\
+		&\hspace{14pt} m\in [0,n-2]
+		\end{split}
+		\\
+		&\text{4. } \Phi(m; n, p) \geq 1 - 2^{-n\ent{\frac{m+1}{n}}{p}},\ m\in [np+1,n-2]
+	\end{align*}
+\end{lemma}
+
+We would like some theory that estimates the value of $S(m; n, a)$ for different parameter regimes. 
+We can consider the function $f(x) = (1+x)^n$ and note that $S(m; n, a)$ is the $m$'th partial sum of this expansion at the point $x=-a$.
+
+The truncated Maclaurin series of a general function $f(x)$ is
+\begin{equation}
+	f(x) = f(0) + x f'(0) + \dots \frac{x^m}{m!}f^{(m)}(0) + R_m(x)
+\end{equation}
+with a remainder term
+\begin{align}
+	R_m (x)&= \int_{0}^x dt f^{(m+1)}(t) \frac{(x-t)^r}{r!} \\
+	&= \frac{x^{m+1}}{(m+1)!} f^{(m+1)}(x_*),
+\end{align}
+where in the second expression, $x_*$ is an implicit point that lies between $0$ and $x$ that comes from the Mean Value Theorem.
+
+Applying this to the function $f(x) = (1+x)^n$ gives
+\begin{equation}
+	(1+x)^n = \sum_{k=0}^m \binom{n}{k} x^k + R_m.
+\end{equation}
+Evaluating at $x=-a$ gives
+\begin{equation}
+	S(m; n, a) = (1-a)^n - R_m(-a),
+\end{equation}
+where the key remainder term is given by
+\begin{align}
+	R_m(-a) &= \int_0^{-a} dt f^{(m+1)}(t) \frac{(-a-t)^m}{m!} \\
+&= \frac{(-a)^{m+1}}{(m+1)!} f^{(m+1)}(x_*).
+\end{align}
+We can also compute the derivative $f^{(m+1)}(x)$ explicitly,
+\begin{equation}
+	f^{(m+1)}(x) = (m+1)!\binom{n}{m+1}(1+x)^{n-m-1}.
+\end{equation}
+Therefore, we have that
+\begin{align}
+	R_m(-a) &= (-1)^{m+1}(m+1)\binom{n}{m+1}\int_{-a}^0 dt (1+t)^{n-m-1}(a+t)^m \\
+&= \binom{n}{m+1}(-a)^{m+1}(1+x_*)^{n-m-1},
+\end{align}
+where in the latter expression $x_* \in [-a,0]$. 
+Note that the first integral expression can be estimated via the Cauchy-Schwarz or the Hoelder inequality. 
+Therefore, we can either work with an explicit form with an unknown (but bounded) parameter $x_*$, or we can use the integral form and provide concrete estimates on it value.
+
+A very simple estimate, based on $x_*$ lying in the interval $[-a,0]$ gives
+\begin{equation}
+\binom{n}{m+1}(-a)^{m+1}(1-a)^{n-m-1} \leq R_m(-a) \le  \binom{n}{m+1}(-a)^{m+1}.
+\end{equation}
+
+This in turn leads to the following bounds on $\Phi_+(a,r,n)$:
+\begin{align}
+\hspace{-2cm}2\Phi_+(a,r,n) &\le \Phi(a,r,n)+ (1-a)^n - \frac{(-a)^{r+1}}{r!} \binom{n}{r+1} (1-a)^{n-r-1} \nonumber \\
+2\Phi_+(a,r,n) & \ge\Phi(a,r,n)+ (1-a)^n - \frac{(-a)^{r+1}}{r!} \binom{n}{r+1} .
+\end{align}
+Details need checking to see if I dropped any constants/signs. Are these bounds good in practice? Asymptotically?

### 2020-12-03 magic_paper.tex

--- 2020-11-30 magic_paper.tex
@@
 
-\subsubsection*{Strange state distillation in the unital fragment}\label{sec:lcsu}
-
-In this section we study the MSD process,
+\subsection{Strange state distillation in the unital fragment}\label{sec:lcsu}
+
+We would now like to study the constraints coming solely from majorization in the unital fragment. 
+We consider the problem of purifying $\NN$ copies of a noisy strange state $\noisysN$ into a smaller number of $\tt$ copies of a less noisy strange state $\rho(\epsilon')\too{\tt}$, with $\epsilon' \le \epsilon$ and $\tt \leq \nn$.
+Since the state $\frac{1}{3} \I$ is free in this fragment, the interconversion problem is unaffected if we tensor in copies of it. 
+This turns out to simplify the Lorenz curve analysis, and so we focus on the process,
 \begin{equation}\label{eq:sudist}
-	\noisysn \xrightarrow{\E \in \O_{\id/3}} \noisys(\epsilon')\too{\tt} \otimes \left( \frac{1}{3}\id \right)\too{\mm},\ \nn = \tt + \mm,
-\end{equation}
-where we have uniformised the number of qutrits on both sides of the process.
-
-In~\cref{app:lcsu_technical}, we define explicit expressions for the Lorenz curve of the $\NN$-copy, $\epsilon$-noisy Strange state in the unital fragment, 
-\begin{equation}\label{eq:lcsu}
-	\lc{\noisys(\epsilon')\too{\tt} \otimes \left( \frac{1}{3}\id \right)\too{\mm}}{\frac{1}{d}\id}(x),\ x\in[0,1].
-\end{equation}
-We call Lorenz curves of this type \emph{standard Lorenz curves}. \nick{expand (non-uniformity)}
-
-Lorenz curves are fully defined by the coordinates of their elbows which is clear in~\cref{fig:lcs} for the Strange state in particular.
-The exact expressions for the elbow coordinates of a standard Lorenz curve can take $2^3 = 8$ different forms, depending on whether the noise level $\epsilon$ is low/high, the parity of the number of copies $\NN$ is even/odd and the location of the elbow relative to the maximum is on the left hand side (LHS -- includes maximum) / right hand side (RHS).
-They are given in full detail in~\cref{app:lcsu_coord_elb}.
-
-Here we focus on the part of the process described by the LHS of the Lorenz curves, in low noise regimes ($0 \leq \epsilon < 3/7$) with even numbers of initial and target copies.
-In this case, the elbow expressions of the standard Lorenz curve in~\cref{eq:lcsu} are given by
+	\noisys\too{2\nn} \longrightarrow \noisys(\tt, \epsilon', \nn) \coloneqq  \noisys(\epsilon')\too{2\tt} \otimes \left( \frac{1}{3}\id \right)\too{2(n-t)},
+\end{equation}
+where all copies are even.
+Since the initial state can be written in the form $\noisys(2\nn, \epsilon, 0)$, it suffices to construct the Lorenz curve $\lc{\rho}{\id/3}(x)$ for the generic noisy strange state $\noisys(\nn, \epsilon ,\tt)$.
+The exact expressions for the coordinates of this Lorenz curve can take $2^3 = 8$ different forms, depending on whether the noise level $\epsilon$ is lower/higher than $3/7$, the parity of the number of copies $\NN$ is even/odd and the location relative to the curve peak is on the left hand side (LHS -- including the maximum) / right hand side (RHS).
+They are given in full detail in~\cref{app:lcsu_technical}.
+
+Here we focus on the case of LHS points on Lorenz curves of even copies and noise levels $\epsilon \leq 3/7$.
+The state $\rho(2\nn, \epsilon ,2\tt)$ has a Wigner distribution that takes on values $w_\ii$, with associated multiplicities $\mlt_\ii$, where
 \begin{align}
-	x_i &= \Phi_+\left(2\ii;\NN,\frac{8}{9}\right), \\
-	L_i &= \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_+\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right),
-\end{align}
-for $i=0,\dots,\frac{\NN}{2}$, where
-\begin{equation}
-	\Phi_+(\mmf; \nnf, p) \coloneqq \sum\limits_{\dummy=0}^{\mmf/2} \binom{\nnf}{2\dummy} p^{2\dummy} (1-p)^{\nnf-2\dummy}.
-\end{equation}
-Conventionally, we set $(x_{-1}, L_{-1}) = (0,0)$.
+w_\ii &= \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2(\nn-\ii)} \\
+m_\ii &= 8^{2\ii}\binom{2\nn}{2\ii}
+\end{align}
+From this, it is readily seen that $L_\sigma(x)$ has elbows on the LHS of its peak located at points $x=x_\ii$, where
+\begin{equation}
+x_\ii = \Phi_+ (\ii, \nn , \frac{8}{9}),
+\end{equation}
+with $\ii = 0,1, \dots , n$ and where $\Phi_+(i,n,p)$ is an even-power cumulant distribution function given by
+\begin{equation}
+\Phi_+(\ii, \nn, p) \coloneqq \sum_{\dummy=0}^{\ii} \binom{2\nn}{2\dummy} p ^{2\ii} (1-p)^{2(\nn-\ii)}.
+\end{equation}
+The value of the Lorenz curve at an elbow is given by
+\begin{equation}
+\lc{\rho}{\id/3}(x_{\ii}) \equiv L_{\ii} =  \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^{2\nn} \Phi_+\left(i;\nn,\frac{12-4\epsilon}{15-8\epsilon}\right),
+\end{equation}
+and we define $(x_{-1}, L_{-1}) = (0,0)$.
 
@@
 \end{align}
-where we use a three-index parametrisation for the coordinates, with $\ii$ determined by the count of the elbow that follows, $\jj$ by the number of Strange state copies and $\kk$ by the number of tensored maximally mixed state copies.
-Therefore, for the initial state $\noisysn$ we have
-\begin{equation}
-	p_{\ii\jj\kk} = \frac{\jj}{8^{2\ii}\binom{\nn}{2\ii}},
-\end{equation}
-with $\ii=0,\dots,\nn,\ \jj(\ii) = 1,\dots,8^{2\ii}\binom{\nn}{2\ii}$ and $\kk = 1$.
-For the target state $\noisys(\epsilon')\too{\tt} \otimes \left( \frac{1}{3}\id \right)\too{\mm}$,
-\begin{equation}
-	p_{\ii\jj\kk} = \frac{\kk + (\jj-1)9^{\mm}}{9^{\mm} 8^{2\ii}\binom{\tt}{2\ii}}
-\end{equation}
-with $\ii=0,\dots,\tt,\ \jj(\ii) = 1,\dots,8^{2\ii}\binom{\tt}{2\ii}$ and $\kk = 1,\dots,9^{\mm}$.
+where we use a three-index parametrisation for the coordinates, with $\ii$ the index of the elbow that follows, $\jj = 1,\dots,\mlt_\ii$ and $\kk=1,\dots,9^{2(\nn-\tt)}$.
+Therefore, for the initial state $\noisys\too{2\nn}$ we have
+\begin{equation}
+	p_{\ii\jj\kk} = \frac{\jj}{8^{2\ii}\binom{2\nn}{2\ii}},
+\end{equation}
+with $\ii=0,\dots,\nn,\ \jj(\ii) = 1,\dots,8^{2\ii}\binom{2\nn}{2\ii}$ and $\kk = 1$.
+For the target state $\noisys(\epsilon')\too{2\tt} \otimes \left( \frac{1}{3}\id \right)\too{2(\nn-\tt)}$,
+\begin{equation}
+	p_{\ii'\jj'\kk'} = \frac{\kk' + (\jj'-1)9^{2(\nn-\tt)}}{9^{2(\nn-\tt)} 8^{2\ii'}\binom{2\tt}{2\ii'}}
+\end{equation}
+with $\ii'=0,\dots,\tt,\ \jj'(\ii') = 1,\dots,8^{2\ii'}\binom{\tt}{2\ii'}$ and $\kk' = 1,\dots,9^{2(\nn-\tt)}$.
 

### 2020-12-04 magic_paper.tex
Added distillation bound in the main text

@@
 We would now like to study the constraints coming solely from majorization in the unital fragment. 
-We consider the problem of purifying $\NN$ copies of a noisy strange state $\noisysN$ into a smaller number of $\tt$ copies of a less noisy strange state $\rho(\epsilon')\too{\tt}$, with $\epsilon' \le \epsilon$ and $\tt \leq \nn$.
-Since the state $\frac{1}{3} \I$ is free in this fragment, the interconversion problem is unaffected if we tensor in copies of it. 
+We consider the problem of purifying $\nn$ copies of a noisy strange state $\noisysn$ into a smaller number of copies $\tt$ of a less noisy strange state $\noisys(\epsilon')\too{\tt}$, with $\epsilon' \le \epsilon$ and $\tt \leq \nn$.
+Since the state $\frac{1}{3} \id$ is free, the interconversion problem is unaffected if we tensor in copies of it. 
 This turns out to simplify the Lorenz curve analysis, and so we focus on the process,
 \begin{equation}\label{eq:sudist}
-	\noisys\too{2\nn} \longrightarrow \noisys(\tt, \epsilon', \nn) \coloneqq  \noisys(\epsilon')\too{2\tt} \otimes \left( \frac{1}{3}\id \right)\too{2(n-t)},
-\end{equation}
-where all copies are even.
-Since the initial state can be written in the form $\noisys(2\nn, \epsilon, 0)$, it suffices to construct the Lorenz curve $\lc{\rho}{\id/3}(x)$ for the generic noisy strange state $\noisys(\nn, \epsilon ,\tt)$.
-The exact expressions for the coordinates of this Lorenz curve can take $2^3 = 8$ different forms, depending on whether the noise level $\epsilon$ is lower/higher than $3/7$, the parity of the number of copies $\NN$ is even/odd and the location relative to the curve peak is on the left hand side (LHS -- including the maximum) / right hand side (RHS).
-They are given in full detail in~\cref{app:lcsu_technical}.
-
-Here we focus on the case of LHS points on Lorenz curves of even copies and noise levels $\epsilon \leq 3/7$.
-The state $\rho(2\nn, \epsilon ,2\tt)$ has a Wigner distribution that takes on values $w_\ii$, with associated multiplicities $\mlt_\ii$, where
-\begin{align}
-w_\ii &= \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2(\nn-\ii)} \\
-m_\ii &= 8^{2\ii}\binom{2\nn}{2\ii}
-\end{align}
-From this, it is readily seen that $L_\sigma(x)$ has elbows on the LHS of its peak located at points $x=x_\ii$, where
-\begin{equation}
-x_\ii = \Phi_+ (\ii, \nn , \frac{8}{9}),
+	\noisys\too{\nn} \longrightarrow \noisys(\tt, \epsilon', \nn - \nn') \coloneqq  \noisys(\epsilon')\too{\tt} \otimes \left( \frac{1}{3}\id \right)\too{(\nn-\tt)},
+\end{equation}
+where all copies $\nn, \tt, \nn - \tt$ are even.
+Since the initial state can be written in the form $\noisys(\nn, \epsilon, 0)$, it suffices to construct the Lorenz curve $\lc{\noisys}{\id/3}(x)$ for the generic noisy strange state $\noisys(\nn, \epsilon ,\tt)$.
+This curve is defined at $9^\nn$ points between $0$ and $1$.
+The exact expressions for the coordinates of these points can take $2^3 = 8$ different forms, depending on whether the noise level $\epsilon$ is low/high (relative to $\frac{3}{7}$), the parity of the number of copies $\nn$ is even/odd and the location relative to the curve peak is on the left hand side (LHS -- including the maximum) / right hand side (RHS).
+The full details are provided in~\cref{app:lcsu_technical}.
+
+Here we focus on the case of Lorenz curves of even copies $\nn, \tt$ and low noise levels ($\epsilon \leq 3/7$).
+The part of the curve on the LHS of its peak is constructed by the positive components of the state Wigner distribution that take values $w_\ii$, with associated multiplicities $\mlt_\ii$,
+\begin{align}
+	w_\ii &= \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{\nn-2\ii}, \\
+	m_\ii &= 8^{2\ii}\binom{\nn}{2\ii},
+\end{align}
+where $i=0,\dots,\frac{n}{2}$.
+From this, it is readily seen that $\lc{\rho}{\id/3}(x)$ has elbows on the LHS of its peak located at points $x=x_\ii$, where
+\begin{equation}
+	x_\ii = \Phi_+ \left( 2\ii, \nn , \frac{8}{9} \right),
 \end{equation}
@@
 \begin{equation}
-\Phi_+(\ii, \nn, p) \coloneqq \sum_{\dummy=0}^{\ii} \binom{2\nn}{2\dummy} p ^{2\ii} (1-p)^{2(\nn-\ii)}.
+	\Phi_+(2\ii, \nn, p) \coloneqq \sum_{\dummy=0}^{\ii} \binom{\nn}{2\dummy} p ^{2\dummy} (1-p)^{\nn-2\dummy}.
 \end{equation}
@@
 \begin{equation}
-\lc{\rho}{\id/3}(x_{\ii}) \equiv L_{\ii} =  \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^{2\nn} \Phi_+\left(i;\nn,\frac{12-4\epsilon}{15-8\epsilon}\right),
+	\lc{\rho}{\id/3}(x_{\ii}) \equiv L_{\ii} =  \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^{\nn} \Phi_+\left(2i;\nn,\frac{12-4\epsilon}{15-8\epsilon}\right),
 \end{equation}
@@
 
+\iffalse
 The coordinates of any point on the Lorenz curve LHS can be expressed as convex sums of the neighbouring elbows,
@@
 \begin{equation}
-	p_{\ii'\jj'\kk'} = \frac{\kk' + (\jj'-1)9^{2(\nn-\tt)}}{9^{2(\nn-\tt)} 8^{2\ii'}\binom{2\tt}{2\ii'}}
+	p'_{\ii'\jj'\kk'} = \frac{\kk' + (\jj'-1)9^{2(\nn-\tt)}}{9^{2(\nn-\tt)} 8^{2\ii'}\binom{2\tt}{2\ii'}}
 \end{equation}
 with $\ii'=0,\dots,\tt,\ \jj'(\ii') = 1,\dots,8^{2\ii'}\binom{\tt}{2\ii'}$ and $\kk' = 1,\dots,9^{2(\nn-\tt)}$.
+\fi
+
+Lorenz curve comparison provides $9^\nn$ necessary constraints for the process~\cref{eq:sudist}.
+\cref{thm:elbows} shows that they can be reduced to $\tt$ independent constraints.
+However, in principle we can pick any location $x_\star$ at which the Lorenz curves are defined and we then get a necessary distillation constraint, 
+\begin{equation}
+	\lc{\noisys(\nn, \epsilon, 0)}{\frac{\id}{3}}(x_\star) \geq \lc{\noisys(\tt, \epsilon', \nn-\tt)}{\frac{\id}{3}}(x_\star).
+\end{equation}
+
+We choose $x_\star = x_0 = \Phi_+(0, \nn, \frac{8}{9}) = \frac{1}{9^{\nn}}$, the location of the first elbow of the initial state $\noisys(\nn, \epsilon, 0)$.
+The initial state Lorenz curve coordinate at this location is
+\begin{equation}
+	L_\star = L_0 = \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^{\nn} \Phi_+\left(0;\nn,\frac{12-4\epsilon}{15-8\epsilon}\right) = \left(\frac{3-4\epsilon}{9}\right)^\nn
+\end{equation}
+
+The first elbow of the target state is located at $x'_0 = \frac{1}{9^{\tt}} < x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$, we can always interpolate between the origin and the first target state elbow, so that
+\begin{equation}
+	L'_\star = \frac{x_\star}{x'_0}L_0 = \frac{1}{9^{\nn-\tt}}\Phi_+\left(0;\tt,\frac{12-4\epsilon}{15-8\epsilon}\right) = \frac{(3-4\epsilon)^{\tt}}{9^{\nn}}.
+\end{equation}
+The process in~\cref{eq:sudist} is therefore possible if $L_\star \geq L'_\star$ or equivalently,
+\begin{align}
+	\frac{\nn}{\tt} &\geq \frac{\ln{(3-4\epsilon')}}{\ln{(3-4\epsilon)}}, \\
+	\epsilon &\leq \frac{3}{4} - \frac{1}{4}(3-4\epsilon')^{\frac{\tt}{\nn}}.
+\end{align}
+As an example, the process with $(\nn, \tt) = (12, 4)$ and $\epsilon' = 0.05$ yields $\epsilon \leq 0.398$.
+Numerical comparison of the curves with varying $\epsilon$ suggests that we require $\epsilon \leq 0.373$ for the process to be possible.
+\nick{All numerical examples I have tested, for various different cases, are quite close}
 

### 2020-12-04 magic_paper.tex
Corrected typos

@@
 
-The first elbow of the target state is located at $x'_0 = \frac{1}{9^{\tt}} < x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$, we can always interpolate between the origin and the first target state elbow, so that
-\begin{equation}
-	L'_\star = \frac{x_\star}{x'_0}L_0 = \frac{1}{9^{\nn-\tt}}\Phi_+\left(0;\tt,\frac{12-4\epsilon}{15-8\epsilon}\right) = \frac{(3-4\epsilon)^{\tt}}{9^{\nn}}.
+The first elbow of the target state is located at $x'_0 = \frac{1}{9^{\tt}} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can always interpolate between the origin and the first target state elbow,
+\begin{equation}
+	\begin{split}
+	L'_\star &= \frac{x_\star}{x'_0}L'_0 = \frac{1}{9^{\nn-\tt}}\left( \frac{5}{3} - \frac{8}{9}\epsilon'\ \right)^{\tt}\Phi_+\left(0;\tt,\frac{12-4\epsilon'}{15-8\epsilon'}\right) \\
+	&= \frac{(3-4\epsilon')^{\tt}}{9^{\nn}}.
+	\end{split}
 \end{equation}

### 2020-12-07 magic_paper.tex
Minor edits. Questions/tasks posed at end of unital fragment section.

@@
 
-\subsection{Magic in the unital fragment}\label{sec:unital}
+\section{Magic in the unital fragment}\label{sec:unital}
 The unital fragment encompasses the circuits which preserve the maximally mixed state ($\id/d$) and so it includes many important families of circuits.
@@
 
-\subsection{Strange state distillation in the unital fragment}\label{sec:lcsu}
+\subsection{Distillation rate bounds for the unital fragment}\label{sec:lcsu}
 
@@
 Since the state $\frac{1}{3} \id$ is free, the interconversion problem is unaffected if we tensor in copies of it.
+More precisely the associated Lorenz curve in invariant under tensoring in arbitrary many copies of this free state.
 This turns out to simplify the Lorenz curve analysis, and so we focus on the process,
@@
 This curve is defined at $9^\nn$ points between $0$ and $1$.
-The exact expressions for the coordinates of these points can take $2^3 = 8$ different forms, depending on whether the noise level $\epsilon$ is low/high (relative to $\frac{3}{7}$), the parity of the number of copies $\nn$ is even/odd and the location relative to the curve peak is on the left hand side (LHS -- including the maximum) / right hand side (RHS).
+The exact expressions for the coordinates of these points can take $8$ different forms, depending on whether the noise level $\epsilon$ is greater than or less than $\frac{3}{7}$, the parity of the number of copies $\nn$ is even/odd and the location relative to the curve peak is on the left hand side (LHS -- including the maximum) / right hand side (RHS).
 The full details are provided in~\cref{app:lcsu_technical}.
@@
 \end{equation}
+We provide technical details on the function $\Phi_+$ in the appendices.
+
 The value of the Lorenz curve at an elbow is given by
@@
 \cref{thm:elbows} shows that they can be reduced to $\tt$ independent constraints.
-However, in principle we can pick any location $x_\star$ at which the Lorenz curves are defined and we then get a necessary distillation constraint, 
+However, in principle we can pick any location $x_\star \in [0,1]$ at which the Lorenz curves are defined and we then get a necessary distillation constraint, 
 \begin{equation}
@@
 
-The first elbow of the target state is located at $x'_0 = \frac{1}{9^{\tt}} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can always interpolate between the origin and the first target state elbow,
+The first elbow of the target state is located at $x'_0 = \frac{1}{9^{\tt}} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the first target state elbow,
 \begin{equation}
@@
 \end{equation}
-The process in~\cref{eq:sudist} is therefore possible if $L_\star \geq L'_\star$ or equivalently,
-\begin{align}
-	\frac{\nn}{\tt} &\geq \frac{\ln{(3-4\epsilon')}}{\ln{(3-4\epsilon)}}, \\
+The process in~\cref{eq:sudist} is therefore possible only if $L_\star \geq L'_\star$ or equivalently,
+\begin{align}
+	\frac{n'}{n} &\leq \frac{\ln{(3-4\epsilon)}}{\ln{(3-4\epsilon')}}, \\
 	\epsilon &\leq \frac{3}{4} - \frac{1}{4}(3-4\epsilon')^{\frac{\tt}{\nn}}.
@@
 
+Moreover, for the problem of distilling pure magic states where $\epsilon'=0$ we obtain an upper bound on the unital fragment distillation rate $R=n/n'$ given by
+\begin{equation}
+R \le \frac{\ln (3-4 \epsilon)}{\ln 3},
+\end{equation}
+which holds for all finite $n$. In comparison, the bound from mana gives $ R \le $ \ddd{[GIVE VALUE]}.
+
+\ddd{[This is good, and the bound coming from the first elbow seems very easy to obtain. Going forward:
+\begin{enumerate}
+\item Does the ``last elbow'' give the same bound? Is it as simple?
+\item Numerically is this about as good as it gets from majorization?
+\item How does this rate compare with existing literature?
+\end{enumerate}
+If this bound is better than existing literature then great.
+I suspect not though.
+However, remember the core message of our work is that we're ``incorporating physical restrictions'' into the magic analysis.
+Given this, one thing that would round the paper off could be if we re-played the ``first elbow'' bound for some non-trivial temperature.
+Meaning: choose a ``nice'' Hamiltonian and compute the first elbow constraint via the thermo-majorization distortion of the Wigner components.
+This would then give us something clearly new -- namely a bound with temperature dependence!
+People would find this interesting since nothing like it exists yet.}
 \null\newpage

### 2020-12-14 magic_paper.tex
minor typos
Added mana bound. Started discussion on thermal fragment

@@
 
-\section{Magic in the unital fragment}\label{sec:unital}
+\section{Magic in unital and thermal fragments}\label{sec:unital}
 The unital fragment encompasses the circuits which preserve the maximally mixed state ($\id/d$) and so it includes many important families of circuits.
@@
 
-\subsection{Distillation rate bounds for the unital fragment}\label{sec:lcsu}
+\subsection{Distillation rate bounds in the unital fragment}\label{sec:lcsu}
 
@@
 \begin{equation}
-	x_\ii = \Phi_+ \left( 2\ii, \nn , \frac{8}{9} \right),
+	x_\ii = \Phi_+ \left( 2\ii; \nn , \frac{8}{9} \right),
 \end{equation}
@@
 \begin{equation}
-	\Phi_+(2\ii, \nn, p) \coloneqq \sum_{\dummy=0}^{\ii} \binom{\nn}{2\dummy} p ^{2\dummy} (1-p)^{\nn-2\dummy}.
+	\Phi_+(2\ii; \nn, p) \coloneqq \sum_{\dummy=0}^{\ii} \binom{\nn}{2\dummy} p ^{2\dummy} (1-p)^{\nn-2\dummy}.
 \end{equation}
@@
 \begin{align}
-	\frac{n'}{n} &\leq \frac{\ln{(3-4\epsilon)}}{\ln{(3-4\epsilon')}}, \\
+	\frac{n}{n'} &\geq \frac{\ln{(3-4\epsilon')}}{\ln{(3-4\epsilon)}}, \text{ or}\\
 	\epsilon &\leq \frac{3}{4} - \frac{1}{4}(3-4\epsilon')^{\frac{\tt}{\nn}}.
@@
 Numerical comparison of the curves with varying $\epsilon$ suggests that we require $\epsilon \leq 0.373$ for the process to be possible.
-\nick{All numerical examples I have tested, for various different cases, are quite close}
-
-Moreover, for the problem of distilling pure magic states where $\epsilon'=0$ we obtain an upper bound on the unital fragment distillation rate $R=n/n'$ given by
-\begin{equation}
-R \le \frac{\ln (3-4 \epsilon)}{\ln 3},
-\end{equation}
-which holds for all finite $n$. In comparison, the bound from mana gives $ R \le $ \ddd{[GIVE VALUE]}.
+
+Moreover, for the problem of distilling pure magic states where $\epsilon'=0$ we obtain a \nick{lower} bound on the unital fragment distillation rate $R=n/n'$ given by
+\begin{equation}
+R \geq \frac{\ln (3-4 \epsilon)}{\ln 3},
+\end{equation}
+which holds for all finite $n$. 
+In comparison, the bound from mana gives 
+\begin{equation}
+	R_{\rm{mana}} \geq \frac{\ln \left(\frac{5}{3} - \frac{8}{9}\epsilon \right)}{\ln \frac{5}{3}},
+\end{equation}
+a threshold which is lower/looser than the one provided by majorization for all $\epsilon > 0$.
 
@@
 People would find this interesting since nothing like it exists yet.}
-\null\newpage
-\null\newpage
 
@@
 so pre-order $\prec_{\gamma_\beta}$ is well defined.
+
+For a qutrit, let the energy spectrum be $E_0 \geq E_1 \geq E_2$. 
+Then, we can explicitly write the thermal Wigner distribution as
+\begin{equation}
+	\W{\gamma_\beta} = \frac{1}{3\Z_\beta} \big( \overbrace{e^{-\beta E_0}}^3, \overbrace{e^{-\beta E_1}}^3, \overbrace{e^{-\beta E_2}}^3 \big),
+\end{equation}
+which is sorted in decreasing order.
+We choose the Strange state where the negativity is in the first component of its Wigner distribution
+\begin{equation}\label{eq:wsu}
+	\W{\noisys(\epsilon)} = \Bigg( \overbrace{-\frac{1}{3} + \frac{4}{9}\epsilon}^1, \overbrace{\frac{1}{6} - \frac{1}{18}\epsilon}^8\Bigg),
+\end{equation}
+
+However, higher copies are not sorted, for example
+\begin{equation}
+	\begin{split}
+	\W{\gamma_\beta\too{2}} = \frac{1}{9\Z_\beta^2} \Bigg( &\overbrace{\overbrace{e^{-\beta 2E_0}}^3, \overbrace{e^{-\beta (E_0 + E_1)}}^3, \overbrace{e^{-\beta (E_0 + E_2)}}^3}^3, \\
+	 &\overbrace{\overbrace{e^{-\beta (E_1 + E_0)}}^3, \overbrace{e^{-\beta 2E_1}}^3, \overbrace{e^{-\beta (E_1 + E_2)}}^3}^3, \\
+	 &\overbrace{\overbrace{e^{-\beta (E_2 + E_0)}}^3, \overbrace{e^{-\beta (E_2 + E_1)}}^3, \overbrace{e^{-\beta 2E_2}}^3}^3 \Bigg).
+	\end{split}
+\end{equation}
+For the Strange state we have
+\begin{equation}
+	\begin{split}
+	\W{\noisys(\epsilon)\too{2}} = \Bigg( &\overbrace{\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^2}^1, \overbrace{ \left( -\frac{1}{3} + \frac{4}{9}\epsilon \right) \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)}^{8}, \\
+	&\overbrace{\overbrace{ \left( -\frac{1}{3} + \frac{4}{9}\epsilon \right) \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)}^1, \overbrace{\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^2}^8}^8,  \Bigg).
+	\end{split}
+\end{equation}
+\nick{We need to sort the distributions $\W{\gamma_\beta\too{2}}, \W{\noisys(\epsilon)\too{2}}$, so that the vector
+\begin{equation}
+	\tilde{\bm{w}} \coloneqq \left(\frac{(\W{\noisys(\epsilon)\too{2}})_1}{(\W{\sigma})_1}, \dots, \frac{(\W{\rho})_{81}}{(\W{\sigma})_{81}} \right)^T,
+\end{equation}
+is in decreasing order, i.e. $\tilde{\bm{w}} = \tilde{\bm{w}}^\downarrow$.
+Then, we need to generalise for any number of copies $n$}
+
+\null\newpage
+\null\newpage
 
@@
 \end{figure}
-
-\newpage
 

### 2020-12-16 magic_paper.tex
Question on mana bound. Things to be expanded on for the thermal fragment analysis.

@@
 
-Moreover, for the problem of distilling pure magic states where $\epsilon'=0$ we obtain a \nick{lower} bound on the unital fragment distillation rate $R=n/n'$ given by
-\begin{equation}
-R \geq \frac{\ln (3-4 \epsilon)}{\ln 3},
+Moreover, for the problem of distilling pure magic states where $\epsilon'=0$ we obtain a upper bound on the unital fragment distillation rate $R=n'/n$ given by
+\begin{equation}
+R \leq \frac{\ln 3}{\ln (3-4 \epsilon)},
 \end{equation}
@@
 \begin{equation}
-	R_{\rm{mana}} \geq \frac{\ln \left(\frac{5}{3} - \frac{8}{9}\epsilon \right)}{\ln \frac{5}{3}},
-\end{equation}
-a threshold which is lower/looser than the one provided by majorization for all $\epsilon > 0$.
-
-\ddd{[This is good, and the bound coming from the first elbow seems very easy to obtain. Going forward:
+	R_{\rm{mana}} \leq \frac{\ln \frac{5}{3}}{\ln \left(\frac{5}{3} - \frac{8}{9}\epsilon \right)},
+\end{equation}
+a threshold which is looser than the one provided by majorization for all $\epsilon > 0$.
+For example, for $\epsilon = 0.4$ we obtain $R\le 3.27 $ while the mana bound gives $R_{\rm{mana}} \le 1.89$.
+\ddd{[Am I making some mistake here??
+Mana does better according to these numbers?
+Does it only do better for a region of $\epsilon$ values?
+Perhaps plot the functions together.]}
+
+\ddd{[Going forward:
 \begin{enumerate}
@@
 Thermal operations coincide with fragment $\O_{\gamma_\beta}$ \nick{expand}.
+\ddd{[Completely vital.
+What Hamiltonian are you choosing?
+Note you can choose it to make life easy for yourself.
+E.g.
+$H=Z$ for example.]}
 The Wigner distribution of any thermal state $\gamma_\beta$ always consists of strictly positive components,
@@
 \end{equation}
-so pre-order $\prec_{\gamma_\beta}$ is well defined.
+so pre-order $\prec_{\gamma_\beta}$ is well defined. \ddd{[Not clear where this equation comes from.]}
 
@@
 \end{equation}
-For the Strange state we have
+\ddd{[Definitely impressed by this Latexing...but perhaps just give the multiplicities and spectrum values. I.e. ``(blah) with multiplicity (blah) and ...'']} For the Strange state we have
 \begin{equation}

### 2020-12-17 magic_paper.tex
Replied to comments

@@
 \begin{equation}
-R \leq \frac{\ln 3}{\ln (3-4 \epsilon)},
+R \leq \frac{\ln (3-4 \epsilon)}{\ln 3},
 \end{equation}
@@
 \begin{equation}
-	R_{\rm{mana}} \leq \frac{\ln \frac{5}{3}}{\ln \left(\frac{5}{3} - \frac{8}{9}\epsilon \right)},
-\end{equation}
-a threshold which is looser than the one provided by majorization for all $\epsilon > 0$.
-For example, for $\epsilon = 0.4$ we obtain $R\le 3.27 $ while the mana bound gives $R_{\rm{mana}} \le 1.89$.
-\ddd{[Am I making some mistake here??
-Mana does better according to these numbers?
-Does it only do better for a region of $\epsilon$ values?
-Perhaps plot the functions together.]}
+	R_{\rm{mana}} \leq \frac{\ln \left(\frac{5}{3} - \frac{8}{9}\epsilon \right)}{\ln \frac{5}{3}},
+\end{equation}
+a threshold which is looser than the one provided by majorization for all $\epsilon > 0$ as illustrated in~\cref{fig:distill_bounds}.
+For example, for $\epsilon = 0.4$ we obtain $R\le 0.31 $ while the mana bound gives $R_{\rm{mana}} \le 0.53$.
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.5]{figs/distill_bounds.pdf}
+    \caption{\textbf{Distillation rate in unital fragment.} Distillation rates obtained by mana and majorization are plotted for $\epsilon' = 0$, up to noise levels $\epsilon_{\rm{max}} = \frac{3}{7}$.
+    Majorization consistently provides stricter rates as proven in~\cref{thm:bounds}.
+    }
+    \label{fig:distill_bounds}
+\end{figure}
 
@@
 E.g.
-$H=Z$ for example.]}
-The Wigner distribution of any thermal state $\gamma_\beta$ always consists of strictly positive components,
+$H=Z$ for example.]}\nick{$X, Z$ are not Hermitian.
+Currently a general Hamiltonian with spectrum $(\epsilon_0,\epsilon_1,\epsilon_2)$.}
+The Wigner distribution of any thermal state $\gamma_\beta$ is calculated directly by the definition in~\cref{eq:wstate},
 \begin{equation}
@@
 \end{equation}
-so pre-order $\prec_{\gamma_\beta}$ is well defined. \ddd{[Not clear where this equation comes from.]}
+and always consists of strictly positive components, so pre-order $\prec_{\gamma_\beta}$ is well defined.
 
@@
 \end{equation}
-\ddd{[Definitely impressed by this Latexing...but perhaps just give the multiplicities and spectrum values. I.e. ``(blah) with multiplicity (blah) and ...'']} For the Strange state we have
+\ddd{[Definitely impressed by this Latexing...but perhaps just give the multiplicities and spectrum values.
+I.e.
+``(blah) with multiplicity (blah) and ...'']} \nick{So the problem is that the exact position of each component matters, e.g.
+thermal state component $e^{-\beta 2E_0}$ corresponds to a positive Strange state component in one position and a negative Strange state component in another.}
+For the Strange state we have
 \begin{equation}

### 2021-01-12 magic_paper.tex
Thermal Wigner for H=(1,0,0)

@@
 
+Take the simplest scenario, where Hamiltonian $H$ has spectrum $(1,0,0)$.
+Then, $\Z_\beta = 2 + e^{-\beta}$ and the 1-copy Wigner distributions are depicted in~\cref{tab:thermal_w}.
+\begin{table}[h]
+  \def\arraystretch{1.5}
+  \centering
+  \begin{tabular}{c|c|c|c}
+    $\bmx = (x_0, x_1)$ & $W_{\noisys}(\bmx)$ & $W_{\gamma_\beta}(\bmx)$ & $W_{\noisys}(\bmx)/W_{\gamma_\beta}(\bmx)$ \\
+    \hline
+    $(0,0)$ & $-\frac{1}{3}$ & $\frac{1}{3(1+2e^\beta)}$ & $-\frac{1}{1+2e^\beta}$ \\
+    \hline
+    \makecell{$(0,1)$ \\ $(0,2)$} & $\frac{1}{6}$ & $\frac{1}{3(1+2e^\beta)}$ & $\frac{1}{2(1+2e^\beta)}$ \\
+    \hline
+    \makecell{$(1,0)$ \\ $\vdots$ \\ $(2,2)$} & $\frac{1}{6}$ & $\frac{1}{3(2+e^{-\beta})}$ & $\frac{1}{2(2+e^{-\beta})}$
+  \end{tabular}
+  \caption{Wigner components $W_{\gamma_\beta}(\bmx)$, $W_{\noisys}(\bmx)$ and their ratio $W_{\noisys}(\bmx)/W_{\gamma_\beta}(\bmx)$.
+  The order of the ratio depends on temperature $\beta$ with a threshold value of $\beta_{\rm{thr}} \approx 0.48$.}
+  \label{tab:thermal_w}
+\end{table}
+To construct the Lorenz curves, we need to sort the ratio $W_{\noisys}(\bmx)/W_{\gamma_\beta}(\bmx)$, but sorting depends on temperature $\beta$.
+
+\newpage
+
 For a qutrit, let the energy spectrum be $E_0 \geq E_1 \geq E_2$. 

### 2021-01-12 magic_paper.tex
simplified/corrected expressions

--- 2020-12-17 magic_paper.tex
@@
 The computational basis now coincides with the Hamiltonian eigenbasis.
-We denote the thermal state at temperature $\beta^{-1}$ by $\gamma_\beta = \frac{e^{-\beta H}}{\Z_\beta}$, where $\Z_\beta = \tr[e^{-\beta H}]$.\nick{expand}
-
+We denote the thermal state at temperature $\beta^{-1}$ by $\gamma_\beta = \frac{e^{-\beta H}}{\Z_\beta}$, where $\Z_\beta = \tr[e^{-\beta H}]$.
 Thermal operations coincide with fragment $\O_{\gamma_\beta}$ \nick{expand}.
-\ddd{[Completely vital.
-What Hamiltonian are you choosing?
-Note you can choose it to make life easy for yourself.
-E.g.
-$H=Z$ for example.]}\nick{$X, Z$ are not Hermitian.
-Currently a general Hamiltonian with spectrum $(\epsilon_0,\epsilon_1,\epsilon_2)$.}
-The Wigner distribution of any thermal state $\gamma_\beta$ is calculated directly by the definition in~\cref{eq:wstate},
-\begin{equation}
-	\W[\bmx]{\gamma_\beta} = \frac{e^{-\beta \epsilon_{x_0}}}{d\Z_\beta}\ \text{for all}\ \bmx \in \pd,
-\end{equation}
-and always consists of strictly positive components, so pre-order $\prec_{\gamma_\beta}$ is well defined.
+
+Consider a general qutrit Hamiltonian $H$ with spectrum $(E_0, E_1, E_2)$.
+The Wigner distribution of any qutrit thermal state $\gamma_\beta$ is calculated directly by the definition in~\cref{eq:wstate},
+\begin{equation}
+	\W[\bmx]{\gamma_\beta} = \frac{e^{-\beta E_{x_0}}}{d\Z_\beta}\ \text{for all}\ \bmx \in \pd,
+\end{equation}
+and always consists of strictly positive components, therefore the pre-order $\prec_{\gamma_\beta}$ is well defined.
+
+Consider the simple scenario, where $H$ has the spectrum $(1,0,0)$.
+Then, $\Z_\beta = 2 + e^{-\beta}$ and the 1-copy Wigner distributions are depicted in~\cref{tab:thermal_w}.
+\begin{table}[h]
+  \def\arraystretch{2}
+  \centering
+  \begin{tabular}{c|c|c|c}
+    $\bmx = (x_0, x_1)$ & $W_{\noisys}(\bmx)$ & $W_{\gamma_\beta}(\bmx)$ & $W_{\noisys}(\bmx)/W_{\gamma_\beta}(\bmx)$ \\
+    \hline
+    \makecell{$(0,0)$ \\ \vdots \\ $(0,2)$} & $\displaystyle \frac{1}{6} - \frac{1}{18}\epsilon$ & $\displaystyle \frac{1}{3(1+2e^\beta)}$ & $\displaystyle \left(\frac{1}{2}-\frac{1}{6}\epsilon \right)(1+2e^\beta)$ \\
+    \hline
+    \makecell{$(1,0)$ \\ $\vdots$ \\ $(2,1)$} & $\displaystyle \frac{1}{6} - \frac{1}{18}\epsilon$ & $\displaystyle \frac{1}{3(2+e^{ -\beta})}$ & $\displaystyle \left(\frac{1}{2}-\frac{1}{6}\epsilon \right)(2+e^{-\beta})$ \\
+    \hline
+    $(2,2)$ & $\displaystyle -\frac{1}{3} + \frac{4}{9}\epsilon$ & $\displaystyle \frac{1}{3(2+e^{-\beta})}$ & $\displaystyle \left(-1 + \frac{4}{3}\epsilon \right)(2+e^{-\beta})$ \\
+    \hline
+  \end{tabular}
+  \caption{Wigner components $W_{\gamma_\beta}(\bmx)$, $W_{\noisys}(\bmx)$ and their ratio $W_{\noisys}(\bmx)/W_{\gamma_\beta}(\bmx)$ listed in order of decreasing ratio (holds for all $\beta$).}
+  \label{tab:thermal_w}
+\end{table}
+To construct the Lorenz curves, we simply take the cumulative sum of the Wigner components in order of increasing ratio.
+
+\newpage
 

### 2021-01-13 magic_paper.tex
added calculations on a first bound, looks very loose though, not complete

@@
 The first elbow of the target state is located at $x'_0 = \frac{1}{9^{\tt}} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the first target state elbow,
-\begin{equation}
+\begin{equation}\label{eq:constraint_deriv}
 	\begin{split}
@@
 
-Consider a general qutrit Hamiltonian $H$ with spectrum $(E_0, E_1, E_2)$.
+Consider a general qutrit Hamiltonian 
+\begin{equation}
+	H = E_0 \ketbra{0} + E_1 \ketbra{1} + E_2 \ketbra{2},
+\end{equation}
+where the eigenbasis coincides with the computation basis of the Pauli Z operator.
 The Wigner distribution of any qutrit thermal state $\gamma_\beta$ is calculated directly by the definition in~\cref{eq:wstate},
@@
 
-Consider the simple scenario, where $H$ has the spectrum $(1,0,0)$.
+Consider the simple scenario, where $H$ has the spectrum 
+\begin{equation}
+	(E_0, E_1, E_2) = (1,0,0).
+\end{equation}
 Then, $\Z_\beta = 2 + e^{-\beta}$ and the 1-copy Wigner distributions are depicted in~\cref{tab:thermal_w}.
@@
   \begin{tabular}{c|c|c|c}
-    $\bmx = (x_0, x_1)$ & $W_{\noisys}(\bmx)$ & $W_{\gamma_\beta}(\bmx)$ & $W_{\noisys}(\bmx)/W_{\gamma_\beta}(\bmx)$ \\
+    $\bmx = (x_0, x_1)$ & $W_{\noisys}(\bmx)$ & $W_{\gamma_\beta}(\bmx)$ & $W_{\noisys(\epsilon)}(\bmx)/W_{\gamma_\beta}(\bmx)$ \\
     \hline
@@
   \end{tabular}
-  \caption{Wigner components $W_{\gamma_\beta}(\bmx)$, $W_{\noisys}(\bmx)$ and their ratio $W_{\noisys}(\bmx)/W_{\gamma_\beta}(\bmx)$ listed in order of decreasing ratio (holds for all $\beta$).}
+  \caption{Wigner components $W_{\gamma_\beta}(\bmx)$, $W_{\noisys}(\bmx)$ and the associated slope $W_{\noisys}(\bmx)/W_{\gamma_\beta}(\bmx)$ listed in order of decreasing slope (holds for all $\beta$).}
   \label{tab:thermal_w}
 \end{table}
-To construct the Lorenz curves, we simply take the cumulative sum of the Wigner components in order of increasing ratio.
+
+To construct the 1-copy Lorenz curve $\lc{\noisys(\epsilon)}{\gamma_\beta}$, we simply take the cumulative sum of the Wigner components in order of decreasing slope $W_{\noisys}(\bmx)/W_{\gamma_\beta}(\bmx)$.
+The first elbow of the 1-copy Lorenz curve is
+\begin{equation}
+	(x_0, L_0) = \left( \frac{1}{1+2e^\beta}, \frac{1}{2} - \frac{1}{6}\epsilon \right).
+\end{equation}
+
+In order to construct the 2-copy Lorenz curve, we first obtain the 2-copy Wigner distribution as a convolution of the 1-copy Wigner distribution (between two identical systems A and B) and then take again the cumulative sum of the Wigner components in order of decreasing slope $W_{\noisys\too{2}}(\bmx_A \oplus \bmx_B)/W_{\gamma_\beta\too{2}}(\bmx_A \oplus \bmx_B)$.
+This order, hence the first elbow depends on the temperature,
+\begin{equation}
+	(x_0, L_0) = 
+	\begin{cases}
+		\left( \frac{1}{9(2+e^{-\beta})^2}, \left(\frac{1}{3} - \frac{4}{9}\epsilon \right)^2 \right),\ &\beta \leq \ln{\left(8-\frac{18}{3-\epsilon}\right)}, \\
+		\left( \frac{1}{(1+2e^\beta)^2}, \left(\frac{1}{2} - \frac{1}{6}\epsilon \right)^2 \right),\ &\beta \geq \ln{\left(8-\frac{18}{3-\epsilon}\right)}.
+	\end{cases}
+\end{equation}
+
+\nick{Unfortunately, performing the same calculation as in~\cref{eq:constraint_deriv} for $\beta \leq \ln{\left(8-\frac{18}{3-\epsilon}\right)}$, yields a very loose bound.
+The first elbow is not a good indicator in this case, points closer to the peak intersect first.}
 

### 2021-01-14 magic_paper.tex
added deets

@@
 
-Consider a system driven by Hamiltonian $H$ and a circuit consisting of thermal operations.
-The computational basis now coincides with the Hamiltonian eigenbasis.
-We denote the thermal state at temperature $\beta^{-1}$ by $\gamma_\beta = \frac{e^{-\beta H}}{\Z_\beta}$, where $\Z_\beta = \tr[e^{-\beta H}]$.
-Thermal operations coincide with fragment $\O_{\gamma_\beta}$ \nick{expand}.
-
-Consider a general qutrit Hamiltonian 
+Consider a system with Hamiltonian $H$ and in contact with a thermal bath of temperature $\beta^{-1}$.
+We denote the thermal state at that temperature by $\gamma \equiv \gamma_\beta = \frac{e^{-\beta H}}{\Z_\beta}$, where $\Z \equiv \Z_\beta = \tr[e^{-\beta H}]$.
+As long as the thermal state is free, it is associated with a set of free, thermal operations and the dynamics of the system can be described within the fragment $\O_{\gamma}$.
+
+We want to focus on qutrit interconversions and extract a temperature-dependent distillation bound.
+To this end, consider the qutrit Hamiltonian
 \begin{equation}
@@
 \end{equation}
-where the eigenbasis coincides with the computation basis of the Pauli Z operator.
-The Wigner distribution of any qutrit thermal state $\gamma_\beta$ is calculated directly by the definition in~\cref{eq:wstate},
-\begin{equation}
-	\W[\bmx]{\gamma_\beta} = \frac{e^{-\beta E_{x_0}}}{d\Z_\beta}\ \text{for all}\ \bmx \in \pd,
-\end{equation}
-and always consists of strictly positive components, therefore the pre-order $\prec_{\gamma_\beta}$ is well defined.
-
-Consider the simple scenario, where $H$ has the spectrum 
+where the eigenbasis coincides with the computational ($Z$) basis.
+The thermal state associated with this Hamiltonian is
+\begin{align}
+	\gamma &= \frac{e^{-\beta H}}{\Z} = \frac{e^{-\beta \sum\limits_{k=0}^2 E_k \ketbra{k}}}{\Z} \\
+	&= \frac{e^{-\beta E_0}}{\Z}\ketbra{0} + \frac{e^{-\beta E_1}}{\Z}\ketbra{1} + \frac{e^{-\beta E_2}}{\Z}\ketbra{2},
+\end{align}
+where $\Z = e^{-\beta E_0} + e^{-\beta E_1} + e^{-\beta E_2}$.
+
+The Wigner distribution of state $\gamma$ can be seen as the ensemble average of the distributions of the computational basis states,
+\begin{align}
+	\W[\bmx]{\gamma} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z}\W[\bmx]{\ketbra{k}} \\
+	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z} \delta_{x_0, k} = \frac{e^{-\beta E_{x_0}}}{d\Z},
+\end{align}
+for all $\bmx \in \pd$. 
+All Wigner components are strictly positive, therefore the pre-order $\prec_{\gamma_\beta}$ is well defined.
+
+Consider the simple energy spectrum 
 \begin{equation}
@@
 \end{equation}
-Then, $\Z_\beta = 2 + e^{-\beta}$ and the 1-copy Wigner distributions are depicted in~\cref{tab:thermal_w}.
+Then, $Z = 2 + e^{-\beta}$.
+Furthermore, for clarity, let $\chi \coloneqq \frac{1}{6}-\frac{1}{18}\epsilon$ be the positive and $-\psi \coloneqq -\frac{1}{3} + \frac{4}{9}\epsilon$ the negative Wigner components of $\noisys(\epsilon)$.
+The 1-copy Wigner distributions in this scenario are depicted in~\cref{tab:thermal_w}.
 \begin{table}[h]
@@
   \begin{tabular}{c|c|c|c}
-    $\bmx = (x_0, x_1)$ & $W_{\noisys}(\bmx)$ & $W_{\gamma_\beta}(\bmx)$ & $W_{\noisys(\epsilon)}(\bmx)/W_{\gamma_\beta}(\bmx)$ \\
+    $\bmx = (x_0, x_1)$ & $W_{\noisys}(\bmx)$ & $W_{\gamma}(\bmx)$ & $\tilde{\bmw}$ \\
     \hline
-    \makecell{$(0,0)$ \\ \vdots \\ $(0,2)$} & $\displaystyle \frac{1}{6} - \frac{1}{18}\epsilon$ & $\displaystyle \frac{1}{3(1+2e^\beta)}$ & $\displaystyle \left(\frac{1}{2}-\frac{1}{6}\epsilon \right)(1+2e^\beta)$ \\
+    \makecell{$(0,0)$ \\ \vdots \\ $(0,2)$} & $\displaystyle \chi$ & $\displaystyle \frac{e^{-\beta}}{3Z}$ & $\displaystyle 3Z \chi e^{\beta}$ \\
     \hline
-    \makecell{$(1,0)$ \\ $\vdots$ \\ $(2,1)$} & $\displaystyle \frac{1}{6} - \frac{1}{18}\epsilon$ & $\displaystyle \frac{1}{3(2+e^{ -\beta})}$ & $\displaystyle \left(\frac{1}{2}-\frac{1}{6}\epsilon \right)(2+e^{-\beta})$ \\
+    \makecell{$(1,0)$ \\ $\vdots$ \\ $(2,1)$} & $\displaystyle \chi$ & $\displaystyle \frac{1}{3Z}$ & $\displaystyle 3Z \chi$ \\
     \hline
-    $(2,2)$ & $\displaystyle -\frac{1}{3} + \frac{4}{9}\epsilon$ & $\displaystyle \frac{1}{3(2+e^{-\beta})}$ & $\displaystyle \left(-1 + \frac{4}{3}\epsilon \right)(2+e^{-\beta})$ \\
+    $(2,2)$ & $\displaystyle -\psi$ & $\displaystyle \frac{1}{3Z}$ & $\displaystyle 3Z (-\psi)$ \\
     \hline
   \end{tabular}
-  \caption{Wigner components $W_{\gamma_\beta}(\bmx)$, $W_{\noisys}(\bmx)$ and the associated slope $W_{\noisys}(\bmx)/W_{\gamma_\beta}(\bmx)$ listed in order of decreasing slope (holds for all $\beta$).}
+  \caption{Wigner components $W_{\gamma}(\bmx)$, $W_{\noisys}(\bmx)$ and the associated slope $\tilde{\bmw}$ listed in order of decreasing slope (holds for all temperatures $\beta^{-1}$).}
   \label{tab:thermal_w}
@@
 
-To construct the 1-copy Lorenz curve $\lc{\noisys(\epsilon)}{\gamma_\beta}$, we simply take the cumulative sum of the Wigner components in order of decreasing slope $W_{\noisys}(\bmx)/W_{\gamma_\beta}(\bmx)$.
+To construct the 1-copy Lorenz curve $\lc{\noisys(\epsilon)}{\gamma_\beta}$, we simply add up the Wigner components in order of decreasing slope $\tilde{\bmw} \coloneqq W_{\noisys}(\bmx)/W_{\gamma_\beta}(\bmx)$.
 The first elbow of the 1-copy Lorenz curve is
 \begin{equation}
-	(x_0, L_0) = \left( \frac{1}{1+2e^\beta}, \frac{1}{2} - \frac{1}{6}\epsilon \right).
-\end{equation}
+	(x_0, L_0) = \left( \frac{e^{-\beta}}{Z}, 3\chi \right).
+\end{equation}
+
+Notice that the slope of the $n$-copy Lorenz curve can be expressed as a self-convolution of the 1-copy Lorenz curve slope $n$ times,
+\begin{equation}
+	\tilde{\bmw\too{n}} = \frac{W_{\noisys\too{n}}(\bmx)}{W_{\gamma\too{n}}(\bmx)} = \left( \frac{W_{\noisys}(\bmx)}{W_{\gamma}(\bmx)} \right)\too{n} = \tilde{\bmw}\too{n}.
+\end{equation}
+
+According to~\cref{def:lc}, to construct the $n$-copy Lorenz curve, we need to sort $\tilde{\bmw\too{n}}$ in decreasing order and take the cumulative sum of the corresponding components $W_{\noisys\too{n}}(\bmx)$ and $W_{\gamma\too{n}}(\bmx)$.
 

### 2021-01-18 magic_paper.tex
Outline for thermal n-copy lorenz curve generating functions, need to understand maximum

@@
 Consider a system with Hamiltonian $H$ and in contact with a thermal bath of temperature $\beta^{-1}$.
-We denote the thermal state at that temperature by $\gamma \equiv \gamma_\beta = \frac{e^{-\beta H}}{\Z_\beta}$, where $\Z \equiv \Z_\beta = \tr[e^{-\beta H}]$.
+We denote the thermal state at that temperature by $\gamma \equiv \gamma_\beta = \frac{e^{-\beta H}}{E_\beta}$, where $E \equiv E_\beta = \tr[e^{-\beta H}]$.
 As long as the thermal state is free, it is associated with a set of free, thermal operations and the dynamics of the system can be described within the fragment $\O_{\gamma}$.
@@
 \end{equation}
-where the eigenbasis coincides with the computational ($Z$) basis.
+where the eigenbasis coincides with the computational basis.
 The thermal state associated with this Hamiltonian is
 \begin{align}
-	\gamma &= \frac{e^{-\beta H}}{\Z} = \frac{e^{-\beta \sum\limits_{k=0}^2 E_k \ketbra{k}}}{\Z} \\
-	&= \frac{e^{-\beta E_0}}{\Z}\ketbra{0} + \frac{e^{-\beta E_1}}{\Z}\ketbra{1} + \frac{e^{-\beta E_2}}{\Z}\ketbra{2},
-\end{align}
-where $\Z = e^{-\beta E_0} + e^{-\beta E_1} + e^{-\beta E_2}$.
+	\gamma &= \frac{e^{-\beta H}}{E} = \frac{e^{-\beta \sum\limits_{k=0}^2 E_k \ketbra{k}}}{E} \\
+	&= \frac{e^{-\beta E_0}}{E}\ketbra{0} + \frac{e^{-\beta E_1}}{E}\ketbra{1} + \frac{e^{-\beta E_2}}{E}\ketbra{2},
+\end{align}
+where $E = e^{-\beta E_0} + e^{-\beta E_1} + e^{-\beta E_2}$.
 
@@
 \begin{align}
-	\W[\bmx]{\gamma} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z}\W[\bmx]{\ketbra{k}} \\
-	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z} \delta_{x_0, k} = \frac{e^{-\beta E_{x_0}}}{d\Z},
+	\W[\bmx]{\gamma} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{E}\W[\bmx]{\ketbra{k}} \\
+	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{E} \delta_{x_0, k} = \frac{e^{-\beta E_{x_0}}}{dE},
 \end{align}
@@
 Then, $Z = 2 + e^{-\beta}$.
-Furthermore, for clarity, let $\chi \coloneqq \frac{1}{6}-\frac{1}{18}\epsilon$ be the positive and $-\psi \coloneqq -\frac{1}{3} + \frac{4}{9}\epsilon$ the negative Wigner components of $\noisys(\epsilon)$.
+Furthermore, for clarity, let $\chi \coloneqq \frac{1}{6}-\frac{1}{18}\epsilon$ be the positive and $-\nu \coloneqq -\frac{1}{3} + \frac{4}{9}\epsilon$ the negative Wigner components of $\noisys(\epsilon)$.
 The 1-copy Wigner distributions in this scenario are depicted in~\cref{tab:thermal_w}.
@@
     \hline
-    $(2,2)$ & $\displaystyle -\psi$ & $\displaystyle \frac{1}{3Z}$ & $\displaystyle 3Z (-\psi)$ \\
+    $(2,2)$ & $\displaystyle -\nu$ & $\displaystyle \frac{1}{3Z}$ & $\displaystyle 3Z (-\nu)$ \\
     \hline
@@
 \begin{equation}
-	\tilde{\bmw\too{n}} = \frac{W_{\noisys\too{n}}(\bmx)}{W_{\gamma\too{n}}(\bmx)} = \left( \frac{W_{\noisys}(\bmx)}{W_{\gamma}(\bmx)} \right)\too{n} = \tilde{\bmw}\too{n}.
-\end{equation}
-
-According to~\cref{def:lc}, to construct the $n$-copy Lorenz curve, we need to sort $\tilde{\bmw\too{n}}$ in decreasing order and take the cumulative sum of the corresponding components $W_{\noisys\too{n}}(\bmx)$ and $W_{\gamma\too{n}}(\bmx)$.
+	\widetilde{\bmw\too{n}} = \frac{W_{\noisys\too{n}}(\bmx)}{W_{\gamma\too{n}}(\bmx)} = \left( \frac{W_{\noisys}(\bmx)}{W_{\gamma}(\bmx)} \right)\too{n} = \widetilde{\bmw}\too{n}.
+\end{equation}
+
+According to~\cref{def:lc}, to construct the $n$-copy Lorenz curve, we need to sort $\widetilde{\bmw\too{n}}$ in decreasing order and take the cumulative sum of the corresponding components $W_{\noisys\too{n}}(\bmx)$ and $W_{\gamma\too{n}}(\bmx)$.
+
+We can therefore construst a trinomial generating function that returns the values and the multiplicities of the distinct Wigner components for a general $n$-copy $\epsilon$-noisy Strange state in a $\gamma_\beta$-fragment.
+\begin{equation}
+	\tilde{w}(X,Y) \coloneqq (3Z)^n (-\nu + 5\chi X + 3\chi e^\beta Y)^n
+\end{equation}
+There are $\frac{(n+1)(n+2)}{2}$ distinct $X^i Y^j$ terms ($i,j = 0,\dots,n$ with $i+j \leq n$) with the coefficients of these terms representing the multiplicities and values of the different ratios.
+
+We can inductively show that the ``start of the Lorenz curve'' corresponds to $\nu^n$ for even $n$ and $\nu^(n-1) \chi e^\beta$ for 
+\begin{equation}
+	\beta \leq \ln{\left(8-\frac{18}{3-\epsilon}\right)}
+\end{equation}
+\nick{Not good enough to restrict to the start of the curve (show why)}
+
+\nick{coordinate generating functions}
 
@@
 \begin{equation}
-	\W{\gamma_\beta} = \frac{1}{3\Z_\beta} \big( \overbrace{e^{-\beta E_0}}^3, \overbrace{e^{-\beta E_1}}^3, \overbrace{e^{-\beta E_2}}^3 \big),
+	\W{\gamma_\beta} = \frac{1}{3E_\beta} \big( \overbrace{e^{-\beta E_0}}^3, \overbrace{e^{-\beta E_1}}^3, \overbrace{e^{-\beta E_2}}^3 \big),
 \end{equation}
@@
 	\begin{split}
-	\W{\gamma_\beta\too{2}} = \frac{1}{9\Z_\beta^2} \Bigg( &\overbrace{\overbrace{e^{-\beta 2E_0}}^3, \overbrace{e^{-\beta (E_0 + E_1)}}^3, \overbrace{e^{-\beta (E_0 + E_2)}}^3}^3, \\
+	\W{\gamma_\beta\too{2}} = \frac{1}{9E_\beta^2} \Bigg( &\overbrace{\overbrace{e^{-\beta 2E_0}}^3, \overbrace{e^{-\beta (E_0 + E_1)}}^3, \overbrace{e^{-\beta (E_0 + E_2)}}^3}^3, \\
 	 &\overbrace{\overbrace{e^{-\beta (E_1 + E_0)}}^3, \overbrace{e^{-\beta 2E_1}}^3, \overbrace{e^{-\beta (E_1 + E_2)}}^3}^3, \\

### 2021-01-20 magic_paper.tex
added first elbow coordinates for n-copy. Will add more details tomorrow. Need to teak first elbow condition

@@
   \end{tabular}
-  \caption{Wigner components $W_{\gamma}(\bmx)$, $W_{\noisys}(\bmx)$ and the associated slope $\tilde{\bmw}$ listed in order of decreasing slope (holds for all temperatures $\beta^{-1}$).}
+  \caption{Wigner components $W_{\gamma}(\bmx)$, $W_{\noisys}(\bmx)$ and the associated slope $\widetilde{\bmw}$ listed in order of decreasing slope (holds for all temperatures $\beta^{-1}$).}
   \label{tab:thermal_w}
@@
 
-To construct the 1-copy Lorenz curve $\lc{\noisys(\epsilon)}{\gamma_\beta}$, we simply add up the Wigner components in order of decreasing slope $\tilde{\bmw} \coloneqq W_{\noisys}(\bmx)/W_{\gamma_\beta}(\bmx)$.
+To construct the 1-copy Lorenz curve $\lc{\noisys(\epsilon)}{\gamma_\beta}$, we simply add up the Wigner components in order of decreasing slope $\widetilde{\bmw} \coloneqq W_{\noisys}(\bmx)/W_{\gamma_\beta}(\bmx)$.
 The first elbow of the 1-copy Lorenz curve is
@@
 
+As illustrated in~\cref{tab:thermal_w}, the phase space can be split into three regions, based on the different values of the slope $\widetilde{\bmw}$.
+As more copies ($n>1$) are considered, the system is described by higher dimensional phase spaces which contains more regions of different slope.
 Notice that the slope of the $n$-copy Lorenz curve can be expressed as a self-convolution of the 1-copy Lorenz curve slope $n$ times,
 \begin{equation}
-	\widetilde{\bmw\too{n}} = \frac{W_{\noisys\too{n}}(\bmx)}{W_{\gamma\too{n}}(\bmx)} = \left( \frac{W_{\noisys}(\bmx)}{W_{\gamma}(\bmx)} \right)\too{n} = \widetilde{\bmw}\too{n}.
-\end{equation}
-
-According to~\cref{def:lc}, to construct the $n$-copy Lorenz curve, we need to sort $\widetilde{\bmw\too{n}}$ in decreasing order and take the cumulative sum of the corresponding components $W_{\noisys\too{n}}(\bmx)$ and $W_{\gamma\too{n}}(\bmx)$.
-
-We can therefore construst a trinomial generating function that returns the values and the multiplicities of the distinct Wigner components for a general $n$-copy $\epsilon$-noisy Strange state in a $\gamma_\beta$-fragment.
-\begin{equation}
-	\tilde{w}(X,Y) \coloneqq (3Z)^n (-\nu + 5\chi X + 3\chi e^\beta Y)^n
-\end{equation}
-There are $\frac{(n+1)(n+2)}{2}$ distinct $X^i Y^j$ terms ($i,j = 0,\dots,n$ with $i+j \leq n$) with the coefficients of these terms representing the multiplicities and values of the different ratios.
-
-We can inductively show that the ``start of the Lorenz curve'' corresponds to $\nu^n$ for even $n$ and $\nu^(n-1) \chi e^\beta$ for 
-\begin{equation}
+	\widetilde{\bmw\too{n}} = \frac{\W{\noisys\too{n}}[\bmx]}{\W{\gamma\too{n}}[\bmx]} = \left( \frac{\W{\noisys}[\bmx]}{\W{\gamma}[\bmx]} \right)\too{n} = \widetilde{\bmw}\too{n}.
+\end{equation}
+Therefore, the regions of different slope in an $n$-copy phase space are generated by the 1-copy phase space regions.
+The process is outlined below.
+
+According to~\cref{def:lc}, to construct the $n$-copy Lorenz curve, we need to evaluate the components of $\widetilde{\bmw\too{n}}$, sort them in decreasing order and take the cumulative sum of the corresponding components $\W{\noisys\too{n}}[\bmx]$ and $\W{\gamma\too{n}}[\bmx]$.
+
+To evaluate the distinct components and multiplicities of $\widetilde{\bmw\too{n}}, \W{\noisys\too{n}}[\bmx], \W{\gamma\too{n}}[\bmx]$, we can construct trinomial generating functions.
+In particular, for a general $n$-copy $\epsilon$-noisy Strange state in a $\gamma_\beta$-fragment, we can use~\cref{tab:thermal_w} to construct the following generating functions,
+\begin{align}
+	&G(X,Y; \noisys) \coloneqq (-\nu + 5\chi X + 3\chi Y)^n \nonumber\\
+	&= \sum\limits_{\substack{i,j = 0,\dots,n \\ i+j \leq n}} m_{ij} \big[(-\nu)^{n-i-j} \chi^{i+j} \big] X^i Y^j, \\
+	&G(X,Y; \gamma) \coloneqq \left( \frac{1}{3Z} + 5\frac{1}{3Z} X + 3 \frac{e^{-\beta}}{3Z} Y \right)^n \nonumber\\
+	&= (3Z)^{-n} \sum\limits_{\substack{i,j = 0,\dots,n \\ i+j \leq n}} m_{ij} e^{-j\beta} X^i Y^j, \\
+	&G(X,Y; \widetilde{\bmw}) \coloneqq \Big( 3Z(-\nu) + 5(3Z\chi) X + 3(3Z\chi) e^\beta Y \Big)^n \nonumber\\
+	&= (3Z)^n \sum\limits_{\substack{i,j = 0,\dots,n \\ i+j \leq n}} m_{ij} \big[(-\nu)^{n-i-j} \chi^{i+j} e^{j\beta} \big] X^i Y^j,
+\end{align}
+where the $(i,j)$-th term multiplicity $m_{ij}$ is given by
+\begin{equation}
+	m_{ij} \coloneqq \frac{n!}{i!j!(n-i-j)!} 5^i 3^j.
+\end{equation}
+There are $\frac{(n+1)(n+2)}{2}$ distinct $X^i Y^j$ terms. 
+Each term $X^i Y^j$ represents a phase space region with different slope. 
+Consider the generating function $G(X,Y;\widetilde{\bmw})$ for the slope. 
+The coefficient in front of the term is a product of the multiplicity $m_{ij}$ and the value of the slope in the region, $(-\nu)^{n-i-j} \chi^{i+j} e^{j\beta}$.
+To find the value of the Wigner components $\W{\noisys\too{n}}(\bmx), \W{\gamma\too{n}}(\bmx)$ in this phase space region, we simply read the coefficients of the term $X^i Y^j$ in functions $G(X,Y; \noisys), G(X,Y; \gamma)$ respectively.
+
+For example, the 2-copy case gives
+\begin{equation}
+	\begin{split}
+	&G(\widetilde{\bmw\too{2}}; X,Y) = 9Z^2 \Big( 1(\nu^2) + 10(-\nu \chi)X + 6(-\nu \chi e^\beta) Y + \\
+	&30 (\chi^2 e^\beta) XY + 25(\chi^2)X^2 + 9(\chi^2 e^{2\beta})Y^2 \Big).
+	\end{split}
+\end{equation}
+The expression contains six different terms corresponding to the different phase space regions.
+Each term (e.g.
+$X$) has a coefficient that consists of the multiplicity, i.e.
+the number of phase space points contained in the corresponding region, (e.g.
+$10$) and the value of the slope at the points of the region (e.g.
+$9Z^2(-\nu \chi)$).
+
+We want to calculate the coordinates of the first elbow of the $n$-copy Lorenz curve $\lc{\noisys(\epsilon)}{\gamma_\beta}$.
+To do this, we first need to find the highest slope value, i.e. find
+\begin{equation}
+	\widetilde{\bmw}_{\rm{max}} = \max{\{ (-\nu)^{n-i-j} \chi^{i+j} e^{j\beta} \}_{i,j}}.
+\end{equation}
+For even $n$,
+\begin{equation}
+	\widetilde{\bmw}_{\rm{max}} = \max{\{ \nu^n, \chi^n e^{n\beta} \}}.
+\end{equation}
+The final optimisation depends on the temperature regime, we work in.
+Specifically, $\widetilde{\bmw}_{\rm{max}} =  \nu^n$ for
+\begin{equation}\label{eq:temp_regime}
 	\beta \leq \ln{\left(8-\frac{18}{3-\epsilon}\right)}
 \end{equation}
-\nick{Not good enough to restrict to the start of the curve (show why)}
-
-\nick{coordinate generating functions}
-
-In order to construct the 2-copy Lorenz curve, we first obtain the 2-copy Wigner distribution as a convolution of the 1-copy Wigner distribution (between two identical systems A and B) and then take again the cumulative sum of the Wigner components in order of decreasing slope $W_{\noisys\too{2}}(\bmx_A \oplus \bmx_B)/W_{\gamma_\beta\too{2}}(\bmx_A \oplus \bmx_B)$.
-This order, hence the first elbow depends on the temperature,
-\begin{equation}
-	(x_0, L_0) = 
-	\begin{cases}
-		\left( \frac{1}{9(2+e^{-\beta})^2}, \left(\frac{1}{3} - \frac{4}{9}\epsilon \right)^2 \right),\ &\beta \leq \ln{\left(8-\frac{18}{3-\epsilon}\right)}, \\
-		\left( \frac{1}{(1+2e^\beta)^2}, \left(\frac{1}{2} - \frac{1}{6}\epsilon \right)^2 \right),\ &\beta \geq \ln{\left(8-\frac{18}{3-\epsilon}\right)}.
-	\end{cases}
-\end{equation}
-
-\nick{Unfortunately, performing the same calculation as in~\cref{eq:constraint_deriv} for $\beta \leq \ln{\left(8-\frac{18}{3-\epsilon}\right)}$, yields a very loose bound.
-The first elbow is not a good indicator in this case, points closer to the peak intersect first.}
-
-\newpage
-
-For a qutrit, let the energy spectrum be $E_0 \geq E_1 \geq E_2$. 
-Then, we can explicitly write the thermal Wigner distribution as
-\begin{equation}
-	\W{\gamma_\beta} = \frac{1}{3E_\beta} \big( \overbrace{e^{-\beta E_0}}^3, \overbrace{e^{-\beta E_1}}^3, \overbrace{e^{-\beta E_2}}^3 \big),
-\end{equation}
-which is sorted in decreasing order.
-We choose the Strange state where the negativity is in the first component of its Wigner distribution
-\begin{equation}\label{eq:wsu}
-	\W{\noisys(\epsilon)} = \Bigg( \overbrace{-\frac{1}{3} + \frac{4}{9}\epsilon}^1, \overbrace{\frac{1}{6} - \frac{1}{18}\epsilon}^8\Bigg),
-\end{equation}
-
-However, higher copies are not sorted, for example
-\begin{equation}
-	\begin{split}
-	\W{\gamma_\beta\too{2}} = \frac{1}{9E_\beta^2} \Bigg( &\overbrace{\overbrace{e^{-\beta 2E_0}}^3, \overbrace{e^{-\beta (E_0 + E_1)}}^3, \overbrace{e^{-\beta (E_0 + E_2)}}^3}^3, \\
-	 &\overbrace{\overbrace{e^{-\beta (E_1 + E_0)}}^3, \overbrace{e^{-\beta 2E_1}}^3, \overbrace{e^{-\beta (E_1 + E_2)}}^3}^3, \\
-	 &\overbrace{\overbrace{e^{-\beta (E_2 + E_0)}}^3, \overbrace{e^{-\beta (E_2 + E_1)}}^3, \overbrace{e^{-\beta 2E_2}}^3}^3 \Bigg).
-	\end{split}
-\end{equation}
-\ddd{[Definitely impressed by this Latexing...but perhaps just give the multiplicities and spectrum values.
-I.e.
-``(blah) with multiplicity (blah) and ...'']} \nick{So the problem is that the exact position of each component matters, e.g.
-thermal state component $e^{-\beta 2E_0}$ corresponds to a positive Strange state component in one position and a negative Strange state component in another.}
-For the Strange state we have
-\begin{equation}
-	\begin{split}
-	\W{\noisys(\epsilon)\too{2}} = \Bigg( &\overbrace{\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^2}^1, \overbrace{ \left( -\frac{1}{3} + \frac{4}{9}\epsilon \right) \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)}^{8}, \\
-	&\overbrace{\overbrace{ \left( -\frac{1}{3} + \frac{4}{9}\epsilon \right) \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)}^1, \overbrace{\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^2}^8}^8,  \Bigg).
-	\end{split}
-\end{equation}
-\nick{We need to sort the distributions $\W{\gamma_\beta\too{2}}, \W{\noisys(\epsilon)\too{2}}$, so that the vector
-\begin{equation}
-	\tilde{\bm{w}} \coloneqq \left(\frac{(\W{\noisys(\epsilon)\too{2}})_1}{(\W{\sigma})_1}, \dots, \frac{(\W{\rho})_{81}}{(\W{\sigma})_{81}} \right)^T,
-\end{equation}
-is in decreasing order, i.e. $\tilde{\bm{w}} = \tilde{\bm{w}}^\downarrow$.
-Then, we need to generalise for any number of copies $n$}
+This value of slope corresponds to term $X^0Y^0 = 1$, so the Lorenz curve coordinates are
+\begin{equation}
+	(x_0, L_0) = \Big( (3Z)^{-n}, \nu^n \Big).
+\end{equation}
+
+\nick{Not good enough. For curves to intersect must have such high noise that condition~\cref{eq:temp_regime} does not hold anymore. Need to tweak.}
 

### 2021-01-21 magic_paper.tex
Full n-copy first elbow coordinates. Need to expand on the first elbow constraint

@@
 \begin{equation}
-	\widetilde{\bmw\too{n}} = \frac{\W{\noisys\too{n}}[\bmx]}{\W{\gamma\too{n}}[\bmx]} = \left( \frac{\W{\noisys}[\bmx]}{\W{\gamma}[\bmx]} \right)\too{n} = \widetilde{\bmw}\too{n}.
+	\widetilde{\bmw\too{n}} = \frac{\W{\noisys\too{n}}(\bmx)}{\W{\gamma\too{n}}(\bmx)} = \left( \frac{\W{\noisys}(\bmx)}{\W{\gamma}(\bmx)} \right)\too{n} = \widetilde{\bmw}\too{n}.
 \end{equation}
@@
 
-According to~\cref{def:lc}, to construct the $n$-copy Lorenz curve, we need to evaluate the components of $\widetilde{\bmw\too{n}}$, sort them in decreasing order and take the cumulative sum of the corresponding components $\W{\noisys\too{n}}[\bmx]$ and $\W{\gamma\too{n}}[\bmx]$.
-
-To evaluate the distinct components and multiplicities of $\widetilde{\bmw\too{n}}, \W{\noisys\too{n}}[\bmx], \W{\gamma\too{n}}[\bmx]$, we can construct trinomial generating functions.
+According to~\cref{def:lc}, to construct the $n$-copy Lorenz curve, we need to evaluate the components of $\widetilde{\bmw\too{n}}$, sort them in decreasing order and take the cumulative sum of the corresponding components $\W{\noisys\too{n}}(\bmx)$ and $\W{\gamma\too{n}}(\bmx)$.
+
+To evaluate the distinct components and multiplicities of $\widetilde{\bmw\too{n}}, \W{\noisys\too{n}}(\bmx), \W{\gamma\too{n}}(\bmx)$, we can construct trinomial generating functions.
 In particular, for a general $n$-copy $\epsilon$-noisy Strange state in a $\gamma_\beta$-fragment, we can use~\cref{tab:thermal_w} to construct the following generating functions,
@@
 
-We want to calculate the coordinates of the first elbow of the $n$-copy Lorenz curve $\lc{\noisys(\epsilon)}{\gamma_\beta}$.
-To do this, we first need to find the highest slope value, i.e. find
-\begin{equation}
-	\widetilde{\bmw}_{\rm{max}} = \max{\{ (-\nu)^{n-i-j} \chi^{i+j} e^{j\beta} \}_{i,j}}.
-\end{equation}
-For even $n$,
-\begin{equation}
-	\widetilde{\bmw}_{\rm{max}} = \max{\{ \nu^n, \chi^n e^{n\beta} \}}.
-\end{equation}
-The final optimisation depends on the temperature regime, we work in.
-Specifically, $\widetilde{\bmw}_{\rm{max}} =  \nu^n$ for
+In order to calculate the coordinates of the first elbow of the $n$-copy Lorenz curve $\lc{\noisys(\epsilon)}{\gamma_\beta}$, we need to find the highest slope value,
+\begin{equation}
+	\widetilde{\bmw}_{\rm{max}} = \max{\{ (-\nu)^{n-i-j} \chi^{i+j} e^{j\beta} \}_{i,j}},
+\end{equation}
+where we have ignored the positive prefactor $(3Z)^n$.
+We can narrow down the maximisation, by noticing that we always have $\chi e^\beta \geq \chi$, so the maximum is achieved for $i=0$ and we can maximise over $\{ (-\nu)^{n-j} \chi^{j} e^{j\beta} \}$.
+Then, notice that either $\nu \geq \chi e^{\beta}$ or $\nu < \chi e^{\beta}$, so, for even $n$, the maximum can only be achieved for $j\in\{0,n\}$ and
+\begin{equation}
+	\widetilde{\bmw}_{\rm{max}} = 
+	\begin{cases}
+		\nu^n, &\nu \geq \chi e^{\beta}, \\
+		\chi^n e^{n\beta}, &\nu < \chi e^{\beta}.
+	\end{cases}
+\end{equation}
+By expanding $\nu, \chi$, this expression can be equivalently recast in terms of a temperature regime,
 \begin{equation}\label{eq:temp_regime}
-	\beta \leq \ln{\left(8-\frac{18}{3-\epsilon}\right)}
-\end{equation}
-This value of slope corresponds to term $X^0Y^0 = 1$, so the Lorenz curve coordinates are
-\begin{equation}
-	(x_0, L_0) = \Big( (3Z)^{-n}, \nu^n \Big).
-\end{equation}
+	\widetilde{\bmw}_{\rm{max}} = 
+	\begin{cases}
+		\nu^n, &\beta \leq \ln{\left(8-\frac{18}{3-\epsilon}\right)}, \\
+		\chi^n e^{n\beta}, &\beta > \ln{\left(8-\frac{18}{3-\epsilon}\right)}.
+	\end{cases}
+\end{equation}
+The values of the slope correspond to terms $X^0Y^0 = 1$ and $X^0Y^n = Y^n$ respectively, so the Lorenz curve coordinates are
+\begin{equation}
+	(x_0, L_0) = 
+	\begin{cases}
+		\Big( (3Z)^{-n}, \nu^n \Big), &\beta \leq \ln{\left(8-\frac{18}{3-\epsilon}\right)}, \\
+		\Big( \frac{e^{-n\beta}}{Z^n}, 3^n\chi^n \Big), &\beta > \ln{\left(8-\frac{18}{3-\epsilon}\right)}.
+	\end{cases}
+\end{equation}
+
+Note that as $\beta$ tends to $0$, we get the first elbow coordinates that we found for the unital fragment, $(9^{-n}, \nu^n)$.
 

### 2021-01-21 magic_paper.tex
Added analysis on temperature-dependent bounds, they look good, they are a continuous extension of unital bounds

@@
 
-Moreover, for the problem of distilling pure magic states where $\epsilon'=0$ we obtain a upper bound on the unital fragment distillation rate $R=n'/n$ given by
+Moreover, for the problem of distilling pure magic states where $\epsilon'=0$ we obtain an upper bound on the unital fragment distillation rate $R=n'/n$ given by
 \begin{equation}
@@
 Note that as $\beta$ tends to $0$, we get the first elbow coordinates that we found for the unital fragment, $(9^{-n}, \nu^n)$.
-
-\nick{Not good enough. For curves to intersect must have such high noise that condition~\cref{eq:temp_regime} does not hold anymore. Need to tweak.}
+We can also invert the temperature constraint into a noise constraint for the state,
+\begin{equation}\label{eq:tempregime}
+	\beta \leq \ln{\left(8-\frac{18}{3-\epsilon}\right)} \Leftrightarrow \epsilon \leq 3 - \frac{18}{8-e^{\beta}}.
+\end{equation}
+
+Consider the Strange state distillation process
+\begin{equation}\label{eq:stdist}
+	\noisys\too{\nn} \longrightarrow \noisys(\tt, \epsilon', \nn - \nn') \coloneqq  \noisys(\epsilon')\too{\tt} \otimes \left( \frac{1}{3}\id \right)\too{(\nn-\tt)},
+\end{equation}
+in the thermal fragment $\O_{\gamma_\beta}$.
+We are now in a position to extract a distillation bound that takes the temperature $\beta$ into account in an analogous method as the one used for the unital fragment distillation bound.
+
+We choose the temperature regime in~\cref{eq:tempregime} and we pick the location $x_\star = x_0 = (3Z)^{-\nn} = (3(2+e^{-\beta}))^{-\nn}$ of the first elbow of the initial state $\noisys(\nn, \epsilon, 0)$ and write down the necessary distillation constraint,
+\begin{equation}
+	\lc{\noisys(\nn, \epsilon, 0)}{\gamma_\beta}(x_\star) \geq \lc{\noisys(\tt, \epsilon', \nn-\tt)}{\gamma_\beta}(x_\star).
+\end{equation}
+
+The initial state Lorenz curve coordinate at this location is $L_\star = L_0 = (1/3 - 4\epsilon/9)^{\nn}$.
+
+The first elbow of the target state is located at $x'_0 = (3Z)^{-\tt} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the first target state elbow,
+\begin{equation}\label{eq:constraint_deriv_temp}
+	L'_\star = \frac{x_\star}{x'_0}L'_0 = (3(2+e^{-\beta}))^{\tt-\nn} \left( \frac{1}{3} - \frac{4}{9} \epsilon' \right)^{\tt}.
+\end{equation}
+The process in~\cref{eq:stdist} is therefore possible only if $L_\star \geq L'_\star$ or equivalently,
+\begin{align}
+	\frac{n}{n'} \geq \frac{\ln{\Big[ (1-\frac{4}{3}\epsilon')(2+e^{-\beta}) \Big]}}{\ln{\Big[ (1-\frac{4}{3}\epsilon)(2+e^{-\beta}) \Big]}},
+\end{align}
+with $\tt \leq \nn$ and $\epsilon' \leq \epsilon \leq 3 - 18/\big(8-e^{\beta}\big)$.
+
+Moreover, for the problem of distilling pure magic states where $\epsilon'=0$ we obtain an upper bound on the unital fragment distillation rate $R=n'/n$ given by
+\begin{equation}
+	R \leq R(\beta) \coloneqq \frac{\ln{\Big[ (1-\frac{4}{3}\epsilon)(2+e^{-\beta}) \Big]}}{\ln{(2+e^{-\beta})}},
+\end{equation}
+which holds for all finite $n$. 
+We compare $R(\beta)$ with the mana bound $R_{\rm{mana}}$ for different values of $\beta$ in~\cref{fig:distill_bounds_temp}.
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.5]{figs/distill_bounds_temp.pdf}
+    \caption{\textbf{Distillation rate in thermal fragments.} Distillation rates obtained by mana and majorization are plotted for $\epsilon' = 0$, up to noise levels $\epsilon_{\rm{max}} = 8-\frac{18}{3-e^{\beta}}$.
+    As $\beta$ increases, the range of noise levels that our bound is valid in decreases and the distillation bound becomes stricter.
+    }
+    \label{fig:distill_bounds_temp}
+\end{figure}
 

### 2021-01-25 magic_paper.tex
Added general hamiltonian case. indeed bound can be written in terms of partition function

@@
 Consider a system with Hamiltonian $H$ and in contact with a thermal bath of temperature $\beta^{-1}$.
-We denote the thermal state at that temperature by $\gamma \equiv \gamma_\beta = \frac{e^{-\beta H}}{E_\beta}$, where $E \equiv E_\beta = \tr[e^{-\beta H}]$.
+We denote the thermal state at that temperature by $\gamma \equiv \gamma_\beta = \frac{e^{-\beta H}}{Z_\beta}$, where $Z \equiv Z_\beta = \tr[e^{-\beta H}]$.
 As long as the thermal state is free, it is associated with a set of free, thermal operations and the dynamics of the system can be described within the fragment $\O_{\gamma}$.
@@
 \begin{align}
-	\gamma &= \frac{e^{-\beta H}}{E} = \frac{e^{-\beta \sum\limits_{k=0}^2 E_k \ketbra{k}}}{E} \\
-	&= \frac{e^{-\beta E_0}}{E}\ketbra{0} + \frac{e^{-\beta E_1}}{E}\ketbra{1} + \frac{e^{-\beta E_2}}{E}\ketbra{2},
-\end{align}
-where $E = e^{-\beta E_0} + e^{-\beta E_1} + e^{-\beta E_2}$.
+	\gamma &= \frac{e^{-\beta H}}{Z} = \frac{e^{-\beta \sum\limits_{k=0}^2 E_k \ketbra{k}}}{Z} \\
+	&= \frac{e^{-\beta E_0}}{Z}\ketbra{0} + \frac{e^{-\beta E_1}}{Z}\ketbra{1} + \frac{e^{-\beta E_2}}{Z}\ketbra{2},
+\end{align}
+where $Z = e^{-\beta E_0} + e^{-\beta E_1} + e^{-\beta E_2}$.
 
@@
 \begin{align}
-	\W[\bmx]{\gamma} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{E}\W[\bmx]{\ketbra{k}} \\
-	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{E} \delta_{x_0, k} = \frac{e^{-\beta E_{x_0}}}{dE},
+	\W[\bmx]{\gamma} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{Z}\W[\bmx]{\ketbra{k}} \\
+	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{Z} \delta_{x_0, k} = \frac{e^{-\beta E_{x_0}}}{dZ},
 \end{align}
@@
 
+\subsubsection{General case}
+
+Let's return to the general qutrit Hamiltonian
+\begin{equation}\label{eq:h_thermal_general}
+	H = E_0 \ketbra{0} + E_1 \ketbra{1} + E_2 \ketbra{2},
+\end{equation}
+defined on the computational basis.
+For the moment, we do not need to define an order between the energy eigenvalues.
+The thermal state is
+\begin{equation}
+	\gamma = \frac{e^{-\beta E_0}}{Z}\ketbra{0} + \frac{e^{-\beta E_1}}{Z}\ketbra{1} + \frac{e^{-\beta E_2}}{Z}\ketbra{2},
+\end{equation}
+where $\Z = e^{-\beta E_0} + e^{-\beta E_1} + e^{-\beta E_2}$.
+
+We choose the Strange state where the negative component lies at phase space point $(2,2)$, i.e. it aligns with a thermal Wigner component associated with energy $E_2$.
+However, the analysis that follows is general in the sense that choosing a different Strange state permutation is equivalent to changing the order between energy eigenvalues.
+
+There are now 4 phase space different regions for the 1-copy case, listed in~\cref{tab:thermal_w_general}.
+\begin{table}[h]
+  \def\arraystretch{2}
+  \centering
+  \begin{tabular}{c|c|c|c}
+    $\bmx = (x_0, x_1)$ & $W_{\noisys}(\bmx)$ & $W_{\gamma}(\bmx)$ & $\tilde{\bmw}$ \\
+    \hline
+    \makecell{$(0,0)$ \\ \vdots \\ $(0,2)$} & $\displaystyle \chi$ & $\displaystyle \frac{e^{-\beta E_0}}{3\Z}$ & $\displaystyle 3\Z e^{\beta E_0} \chi$ \\
+    \hline
+    \makecell{$(1,0)$ \\ \vdots \\ $(1,2)$} & $\displaystyle \chi$ & $\displaystyle \frac{e^{-\beta E_1}}{3\Z}$ & $\displaystyle 3\Z e^{\beta E_1} \chi$ \\
+    \hline
+    \makecell{$(2,0)$ \\ $(2,1)$} & $\displaystyle \chi$ & $\displaystyle \frac{e^{-\beta E_2}}{3\Z}$ & $\displaystyle 3\Z e^{\beta E_2} \chi$ \\
+    \hline
+    $(2,2)$ & $\displaystyle -\nu$ & $\displaystyle \frac{e^{-\beta E_2}}{3\Z}$ & $\displaystyle 3\Z e^{\beta E_2} (-\nu)$ \\
+    \hline
+  \end{tabular}
+  \caption{Wigner components $W_{\gamma}(\bmx)$, $W_{\noisys}(\bmx)$ and the associated slope $\widetilde{\bmw}$ for Hamiltonian $H$ in~\cref{eq:h_thermal_general}. 
+  Ordering depends on the energy ordering.}
+  \label{tab:thermal_w_general}
+\end{table}
+
+The generating functions are
+\begin{widetext}
+\begin{align}
+	&G(X,Y; \noisys) \coloneqq (-\nu + 3\chi X + 3\chi Y + 2\chi Z)^n \nonumber\\
+	&= \sum\limits_{\substack{i,j,k = 0,\dots,n \\ i+j+k \leq n}} m_{ijk} \big[(-\nu)^{n-i-j-k} \chi^{i+j+k} \big] X^i Y^j Z^k, \\
+	&G(X,Y; \gamma) \coloneqq \left( \frac{e^{\beta E_2}}{3\Z} + 3\frac{e^{\beta E_0}}{3\Z} X + 3\frac{e^{\beta E_1}}{3\Z} Y + 2\frac{e^{\beta E_2}}{3\Z} Z \right)^n \nonumber\\
+	&= (3\Z)^{-n}\sum\limits_{\substack{i,j,k = 0,\dots,n \\ i+j+k \leq n}} m_{ijk} e^{-\beta [ i E_0 + j E_2 + (n-i-j) E_3 ]} X^i Y^j Z^k, \\
+	&G(X,Y; \widetilde{\bmw}) \coloneqq \Big( 3\Z e^{\beta E_2}(-\nu) + 3(3\Z e^{\beta E_0}\chi) X + 3(3\Z e^{\beta E_1}\chi + 2(3\Z e^{\beta E_2}\chi) e^\beta Z \Big)^n \nonumber\\
+	&= (3\Z)^n \sum\limits_{\substack{i,j,k = 0,\dots,n \\ i+j+k \leq n}} m_{ijk} \big[(-\nu)^{n-i-j-k} \chi^{i+j+k} e^{\beta [(n-i-j)E_2 + iE_0 + jE_1]} \big] X^i Y^j Z^k,
+\end{align}
+\end{widetext}
+where the $(i,j,k)$-th term multiplicity $m_{ij}$ is given by
+\begin{equation}
+	m_{ijk} \coloneqq \frac{n!}{i!j!k!(n-i-j-k)!} 3^i 3^j 2^k.
+\end{equation}
+
+In order to find the first elbow coordinates, we need to find the maximum value of the term
+\begin{equation}
+	\tilde{w} \coloneqq (-\nu)^{n-i-j-k} \chi^{i+j+k} e^{\beta [(n-i-j)E_2 + iE_0 + jE_1]}
+\end{equation}
+over all $i,j,k = 0,\dots,n$ with the constraint $i+j+k \leq n$.
+This optimisation depends on the ordering of the energy eigenvalues.
+We restrict to even $n$ now.
+Specifically, there are two scenarios:
+\begin{itemize}
+	\item The eigenvalue ($E_2$) corresponding to the subspace of the negative Strange Wigner component is largest.
+	In this case, $\tilde{w}$ attains its maximum value $\nu^n e^{n\beta E_2}$ for $i=j=k=0$.
+	\item The eigenvalue ($E_2$) corresponding to the subspace of the negative Strange Wigner component is not largest.
+	In this case, (wlog assume $E_0$ is largest)
+	\begin{equation}
+	  \tilde{w} =
+     \begin{cases}
+		\nu^n, &\beta E_0 \leq \ln{\left(8-\frac{18}{3-\epsilon}\right)}, \\
+		\chi^n e^{n\beta E_0}, &\beta E_0 > \ln{\left(8-\frac{18}{3-\epsilon}\right)}.
+	  \end{cases}
+	\end{equation}
+	The first case corresponds to $i=j=k=0$, and the second case to $i=n,j=k=0$.
+\end{itemize}
+In both scenarios, for small enough $\beta$, the first elbow is given by the term with $i=j=k=0$.
+The coordinates are
+\begin{equation}
+	(x_0, L_0) = ((3\Z)^n, \nu^n)
+\end{equation}
+and therefore the first elbow constraint $L_\star \geq L'_\star$ gives
+\begin{align}
+	\frac{n}{n'} \geq \frac{\ln{\Big[ (1-\frac{4}{3}\epsilon')\Z_\beta \Big]}}{\ln{\Big[ (1-\frac{4}{3}\epsilon)\Z_\beta \Big]}},
+\end{align}
+with $\tt \leq \nn$ and $\epsilon' \leq \epsilon$. 
+Moreover, if $E_2$ is not largest, we have the additional constarint $\epsilon \leq 3 - 18/\big(8-e^{\beta}\big)$.
+This agrees with the previous scenario where the energy spectrum was $(1,0,0)$.
+
 \null\newpage

### 2021-01-27 magic_paper.tex
tidying up thermal section

@@
 
+Consider a qutrit system with maximally Wigner-negative magic state $\ket{\rm{S}} = \frac{1}{\sqrt{2}}(\ket{0} - \omega^2 \ket{1})$.
+It can be written in density operator form as
+\begin{align}
+	\ketbra{\rm{S}} = \sum_{\bmx \neq (2,2)} \frac{1}{6} A_{\bmx} - \frac{1}{3} A_{(2,2)},
+\end{align}
+where $\bmx$ ranges in the $3$-dimensional phase space $\pd[3]$.
+This is a permutation of the pure Strange state visualised in~\cref{fig:strange}.
+We allow for isotropic (uniform) noise, so that the system state is a convex sum of the pure Strange state and the maximally mixed state,
+\begin{equation}
+	\noisys(\epsilon) \coloneqq (1-\epsilon)\ketbra{\rm{S}} + \epsilon \frac{1}{3}\id,
+\end{equation}
+where we choose to restrict the noise level, $0 \leq \epsilon \leq \frac{3}{7}$, so that the Wigner distribution of the state always contains a negative component which is greater than the 8 positive components of the state.
+
+In particular, the Wigner distribution of the state can be written as 
+\begin{equation}
+	\W[\bmx]{\noisys(\epsilon)} = (1-\epsilon)\W[\bmx]{\ketbra{\rm{S}}} + \epsilon\W[\bmx]{\frac{1}{3}\id},
+\end{equation}
+so we get positive components
+\begin{equation}
+	w_+(\epsilon) = \frac{1}{6} -\frac{1}{18}\epsilon
+\end{equation}
+at the 8 phase space points $\bmx \in \pd[3] \setminus \{(2,2)\}$ and a negative component
+\begin{equation}
+	- w_-(\epsilon) = - \left( \frac{1}{3} -\frac{4}{9}\epsilon \right)
+\end{equation}
+at point $\bmx = (2,2)$.
+
+We are interested in studying Strange state distillation in general thermal fragments $\O_{\gamma_\beta}$ where the thermal state is
+\begin{equation}
+	\gamma_\beta \coloneqq \frac{e^{-\beta H}}{\Z_\beta},
+\end{equation}
+with partition function $\Z_\beta = \tr \big[e^{-\beta H} \big]$, defined in terms of some Hamiltonian $H$ and temperature $\beta^{-1}$.
+
+To this end, consider the general qutrit Hamiltonian
+\begin{equation}
+	H = E_0 \ketbra{0} + E_1 \ketbra{1} + E_2 \ketbra{2},
+\end{equation}
+where the energy eigenbasis coincides with the computational basis.
+We have that energy eigenvalues $E_i \geq 0$, but impose no order between them.
+
+The thermal state associated with this Hamiltonian is
+\begin{align}
+	\gamma_\beta &= \frac{e^{-\beta H}}{\Z_\beta} = \frac{e^{-\beta \sum\limits_{k=0}^2 E_k \ketbra{k}}}{\Z_\beta} \\
+	&= \frac{e^{-\beta E_0}}{\Z_\beta}\ketbra{0} + \frac{e^{-\beta E_1}}{\Z_\beta}\ketbra{1} + \frac{e^{-\beta E_2}}{\Z_\beta}\ketbra{2},
+\end{align}
+where $\Z_\beta = e^{-\beta E_0} + e^{-\beta E_1} + e^{-\beta E_2}$.
+
+The Wigner distribution of state $\gamma_\beta$ can be seen as the ensemble average of the distributions of the computational basis states,
+\begin{align}
+	\W[\bmx]{\gamma_\beta} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z_\beta}\W[\bmx]{\ketbra{k}} \\
+	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z_\beta} \delta_{x_0, k} = \frac{e^{-\beta E_{x_0}}}{3\Z_\beta},
+\end{align}
+for all $\bmx \in \pd[3]$. 
+All Wigner components are strictly positive, therefore the pre-order $\prec_{\gamma_\beta}$ is well defined.
+
+We are now in a position to consider the Strange state distillation process
+\begin{equation}\label{eq:msd_thermal}
+		\noisys(\epsilon)\too{\nn} \xrightarrow{\E \in \O_{\gamma_\beta}} \noisys(\epsilon')\too{\tt} \otimes \gamma_\beta\too{\nn-\tt},
+\end{equation}
+where we are allowed to tensor in copies of the thermal state $\gamma_\beta$, since it is free in fragment $\O_{\gamma_\beta}$.
+
+Our aim is to obtain a distillation bound for~\cref{eq:msd_thermal} which depends on variables $\nn, \tt, \epsilon, \epsilon'$ as well as $\beta$.
+In the analysis that follows, we drop obvious variable dependencies for clarity.
+
+Consider a general $\epsilon$-noisy Strange state $\noisys$ in a thermal fragment $\O_{\gamma}$.
+We can construct the Gibbs-rescaled distribution 
+\begin{equation}
+	\widetilde{\rm{W}}(\bmx) \coloneqq \frac{\W[\bmx]{\noisys}}{\W[\bmx]{\gamma}},
+\end{equation}
+which naturally splits the phase space $\pd[3]$ into four regions of different ``slopes'', i.e. values of the Gibbs-rescaled distribution, as illustrated in~\cref{fig:pd_split_thermal}.
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.5]{figs/pd_split_thermal.pdf}
+    \caption{\textbf{Qutrit phase space regions with different Gibbs-rescaled values.}
+    }
+    \label{fig:pd_split_thermal}
+\end{figure}
+
+An $n$-copy system is described over a phase space given by the $n$-times Cartesian product $\pd[3]^{\times n}$) which contains more regions of different slope.
+In particular, it contains exactly the regions $X^i Y^j Z^k$, where $i,j,k = 0,\dots,n$ and $i+j+k \leq n$. 
+For example, region $XY$ consists of all points expressed as the direct sum $\bmx \oplus \bmy$, where $\bmx \in X$ and $\bmy \in Y$.
+
+The $n$-copy Gibbs-rescaled distribution can be written as a self-convolution,
+\begin{equation}
+	\widetilde{\rm{W}}(\bmx) = \frac{\W{\noisys\too{n}}(\bmx)}{\W{\gamma\too{n}}(\bmx)} = \left( \frac{\W{\noisys}(\bmx)}{\W{\gamma}(\bmx)} \right)\too{n} = \widetilde{\bmw}\too{n}.
+\end{equation}
+Therefore, the regions of different slope in an $n$-copy phase space are generated by the 1-copy phase space regions.
+
+\subsection{OLD Magic in thermal fragments}
+
 Consider a system with Hamiltonian $H$ and in contact with a thermal bath of temperature $\beta^{-1}$.

### 2021-01-28 magic_paper.tex
tiidying up thermal 2

@@
 \begin{equation}\label{eq:dist}
-    \rho(\epsilon)\too{\nn} = \left[ (1 - \epsilon) \rho + \epsilon \sigma \right]\too{\nn},
+    \rho(\epsilon)\too{n} = \left[ (1 - \epsilon) \rho + \epsilon \sigma \right]\too{n},
 \end{equation}
@@
 \begin{equation}
-		\rho(\epsilon)\too{\nn} \xrightarrow{\E \in \O_\sigma} \rho(\epsilon')\too{\tt},
-\end{equation}
-where it is converted into a $\tt$-copy, $\epsilon'$-noisy state, such that the number of copies has decreased ($\tt < \nn$), but the state is less noisy ($\epsilon' < \epsilon$).
+		\rho(\epsilon)\too{n} \xrightarrow{\E \in \O_\sigma} \rho(\epsilon')\too{\tt},
+\end{equation}
+where it is converted into a $\tt$-copy, $\epsilon'$-noisy state, such that the number of copies has decreased ($\tt < n$), but the state is less noisy ($\epsilon' < \epsilon$).
 
@@
 	\begin{split}
-	\epsilon_{\rm{th}}(\nn, \tt, \epsilon', \sigma) \coloneqq &\sup{\{\epsilon:\ \lc{\rho(\epsilon)\too{\nn}}{\sigma}}(x) \geq \\
+	\epsilon_{\rm{th}}(n, \tt, \epsilon', \sigma) \coloneqq &\sup{\{\epsilon:\ \lc{\rho(\epsilon)\too{n}}{\sigma}}(x) \geq \\
 	&{\lc{\rho(\epsilon')\too{\tt}}{\sigma}(x),\ x\in[0,1]\}}.
@@
 \end{equation}
-The MSD process~(\ref{eq:dist}) is impossible for all $\epsilon > \epsilon_{\rm{th}}(\nn, \tt, \epsilon', \sigma)$.
+The MSD process~(\ref{eq:dist}) is impossible for all $\epsilon > \epsilon_{\rm{th}}(n, \tt, \epsilon', \sigma)$.
 
@@
 \begin{equation}\label{eq:ethresh}
-	\nn_{\rm{th}}(\epsilon, \epsilon', \sigma) \coloneqq \min{\{\nn: \lc{\noisysn}{\sigma} \geq \lc{\noisys(\epsilon')}{\sigma}\}}.
+	n_{\rm{th}}(\epsilon, \epsilon', \sigma) \coloneqq \min{\{n: \lc{\noisysn}{\sigma} \geq \lc{\noisys(\epsilon')}{\sigma}\}}.
 \end{equation}}
@@
     }
-    \caption{\textbf{Lorenz curves of Strange state copies.} Lorenz curves of $\noisysn$ for $\nn=1,2,3,4$.
+    \caption{\textbf{Lorenz curves of Strange state copies.} Lorenz curves of $\noisysn$ for $n=1,2,3,4$.
     Solid lines represent pure Strange states ($\epsilon = 0$); dashed lines represent noisy Strange states ($\epsilon = 0.1$).
@@
 We would now like to study the constraints coming solely from majorization in the unital fragment. 
-We consider the problem of purifying $\nn$ copies of a noisy strange state $\noisysn$ into a smaller number of copies $\tt$ of a less noisy strange state $\noisys(\epsilon')\too{\tt}$, with $\epsilon' \le \epsilon$ and $\tt \leq \nn$.
+We consider the problem of purifying $n$ copies of a noisy strange state $\noisysn$ into a smaller number of copies $\tt$ of a less noisy strange state $\noisys(\epsilon')\too{\tt}$, with $\epsilon' \le \epsilon$ and $\tt \leq n$.
 Since the state $\frac{1}{3} \id$ is free, the interconversion problem is unaffected if we tensor in copies of it.
@@
 \begin{equation}\label{eq:sudist}
-	\noisys\too{\nn} \longrightarrow \noisys(\tt, \epsilon', \nn - \nn') \coloneqq  \noisys(\epsilon')\too{\tt} \otimes \left( \frac{1}{3}\id \right)\too{(\nn-\tt)},
-\end{equation}
-where all copies $\nn, \tt, \nn - \tt$ are even.
-Since the initial state can be written in the form $\noisys(\nn, \epsilon, 0)$, it suffices to construct the Lorenz curve $\lc{\noisys}{\id/3}(x)$ for the generic noisy strange state $\noisys(\nn, \epsilon ,\tt)$.
-This curve is defined at $9^\nn$ points between $0$ and $1$.
-The exact expressions for the coordinates of these points can take $8$ different forms, depending on whether the noise level $\epsilon$ is greater than or less than $\frac{3}{7}$, the parity of the number of copies $\nn$ is even/odd and the location relative to the curve peak is on the left hand side (LHS -- including the maximum) / right hand side (RHS).
+	\noisys\too{n} \longrightarrow \noisys(\tt, \epsilon', n - n') \coloneqq  \noisys(\epsilon')\too{\tt} \otimes \left( \frac{1}{3}\id \right)\too{(n-\tt)},
+\end{equation}
+where all copies $n, \tt, n - \tt$ are even.
+Since the initial state can be written in the form $\noisys(n, \epsilon, 0)$, it suffices to construct the Lorenz curve $\lc{\noisys}{\id/3}(x)$ for the generic noisy strange state $\noisys(n, \epsilon ,\tt)$.
+This curve is defined at $9^n$ points between $0$ and $1$.
+The exact expressions for the coordinates of these points can take $8$ different forms, depending on whether the noise level $\epsilon$ is greater than or less than $\frac{3}{7}$, the parity of the number of copies $n$ is even/odd and the location relative to the curve peak is on the left hand side (LHS -- including the maximum) / right hand side (RHS).
 The full details are provided in~\cref{app:lcsu_technical}.
 
-Here we focus on the case of Lorenz curves of even copies $\nn, \tt$ and low noise levels ($\epsilon \leq 3/7$).
+Here we focus on the case of Lorenz curves of even copies $n, \tt$ and low noise levels ($\epsilon \leq 3/7$).
 The part of the curve on the LHS of its peak is constructed by the positive components of the state Wigner distribution that take values $w_\ii$, with associated multiplicities $\mlt_\ii$,
 \begin{align}
-	w_\ii &= \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{\nn-2\ii}, \\
-	m_\ii &= 8^{2\ii}\binom{\nn}{2\ii},
+	w_\ii &= \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{n-2\ii}, \\
+	m_\ii &= 8^{2\ii}\binom{n}{2\ii},
 \end{align}
@@
 \begin{equation}
-	x_\ii = \Phi_+ \left( 2\ii; \nn , \frac{8}{9} \right),
+	x_\ii = \Phi_+ \left( 2\ii; n , \frac{8}{9} \right),
 \end{equation}
@@
 \begin{equation}
-	\Phi_+(2\ii; \nn, p) \coloneqq \sum_{\dummy=0}^{\ii} \binom{\nn}{2\dummy} p ^{2\dummy} (1-p)^{\nn-2\dummy}.
+	\Phi_+(2\ii; n, p) \coloneqq \sum_{\dummy=0}^{\ii} \binom{n}{2\dummy} p ^{2\dummy} (1-p)^{n-2\dummy}.
 \end{equation}
@@
 \begin{equation}
-	\lc{\rho}{\id/3}(x_{\ii}) \equiv L_{\ii} =  \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^{\nn} \Phi_+\left(2i;\nn,\frac{12-4\epsilon}{15-8\epsilon}\right),
+	\lc{\rho}{\id/3}(x_{\ii}) \equiv L_{\ii} =  \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^{n} \Phi_+\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right),
 \end{equation}
@@
 \end{align}
-where we use a three-index parametrisation for the coordinates, with $\ii$ the index of the elbow that follows, $\jj = 1,\dots,\mlt_\ii$ and $\kk=1,\dots,9^{2(\nn-\tt)}$.
-Therefore, for the initial state $\noisys\too{2\nn}$ we have
-\begin{equation}
-	p_{\ii\jj\kk} = \frac{\jj}{8^{2\ii}\binom{2\nn}{2\ii}},
-\end{equation}
-with $\ii=0,\dots,\nn,\ \jj(\ii) = 1,\dots,8^{2\ii}\binom{2\nn}{2\ii}$ and $\kk = 1$.
-For the target state $\noisys(\epsilon')\too{2\tt} \otimes \left( \frac{1}{3}\id \right)\too{2(\nn-\tt)}$,
-\begin{equation}
-	p'_{\ii'\jj'\kk'} = \frac{\kk' + (\jj'-1)9^{2(\nn-\tt)}}{9^{2(\nn-\tt)} 8^{2\ii'}\binom{2\tt}{2\ii'}}
-\end{equation}
-with $\ii'=0,\dots,\tt,\ \jj'(\ii') = 1,\dots,8^{2\ii'}\binom{\tt}{2\ii'}$ and $\kk' = 1,\dots,9^{2(\nn-\tt)}$.
+where we use a three-index parametrisation for the coordinates, with $\ii$ the index of the elbow that follows, $\jj = 1,\dots,\mlt_\ii$ and $\kk=1,\dots,9^{2(n-\tt)}$.
+Therefore, for the initial state $\noisys\too{2n}$ we have
+\begin{equation}
+	p_{\ii\jj\kk} = \frac{\jj}{8^{2\ii}\binom{2n}{2\ii}},
+\end{equation}
+with $\ii=0,\dots,n,\ \jj(\ii) = 1,\dots,8^{2\ii}\binom{2n}{2\ii}$ and $\kk = 1$.
+For the target state $\noisys(\epsilon')\too{2\tt} \otimes \left( \frac{1}{3}\id \right)\too{2(n-\tt)}$,
+\begin{equation}
+	p'_{\ii'\jj'\kk'} = \frac{\kk' + (\jj'-1)9^{2(n-\tt)}}{9^{2(n-\tt)} 8^{2\ii'}\binom{2\tt}{2\ii'}}
+\end{equation}
+with $\ii'=0,\dots,\tt,\ \jj'(\ii') = 1,\dots,8^{2\ii'}\binom{\tt}{2\ii'}$ and $\kk' = 1,\dots,9^{2(n-\tt)}$.
 \fi
 
-Lorenz curve comparison provides $9^\nn$ necessary constraints for the process~\cref{eq:sudist}.
+Lorenz curve comparison provides $9^n$ necessary constraints for the process~\cref{eq:sudist}.
 \cref{thm:elbows} shows that they can be reduced to $\tt$ independent constraints.
@@
 \begin{equation}
-	\lc{\noisys(\nn, \epsilon, 0)}{\frac{\id}{3}}(x_\star) \geq \lc{\noisys(\tt, \epsilon', \nn-\tt)}{\frac{\id}{3}}(x_\star).
-\end{equation}
-
-We choose $x_\star = x_0 = \Phi_+(0, \nn, \frac{8}{9}) = \frac{1}{9^{\nn}}$, the location of the first elbow of the initial state $\noisys(\nn, \epsilon, 0)$.
+	\lc{\noisys(n, \epsilon, 0)}{\frac{\id}{3}}(x_\star) \geq \lc{\noisys(\tt, \epsilon', n-\tt)}{\frac{\id}{3}}(x_\star).
+\end{equation}
+
+We choose $x_\star = x_0 = \Phi_+(0, n, \frac{8}{9}) = \frac{1}{9^{n}}$, the location of the first elbow of the initial state $\noisys(n, \epsilon, 0)$.
 The initial state Lorenz curve coordinate at this location is
 \begin{equation}
-	L_\star = L_0 = \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^{\nn} \Phi_+\left(0;\nn,\frac{12-4\epsilon}{15-8\epsilon}\right) = \left(\frac{3-4\epsilon}{9}\right)^\nn
+	L_\star = L_0 = \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^{n} \Phi_+\left(0;n,\frac{12-4\epsilon}{15-8\epsilon}\right) = \left(\frac{3-4\epsilon}{9}\right)^n
 \end{equation}
@@
 	\begin{split}
-	L'_\star &= \frac{x_\star}{x'_0}L'_0 = \frac{1}{9^{\nn-\tt}}\left( \frac{5}{3} - \frac{8}{9}\epsilon'\ \right)^{\tt}\Phi_+\left(0;\tt,\frac{12-4\epsilon'}{15-8\epsilon'}\right) \\
-	&= \frac{(3-4\epsilon')^{\tt}}{9^{\nn}}.
+	L'_\star &= \frac{x_\star}{x'_0}L'_0 = \frac{1}{9^{n-\tt}}\left( \frac{5}{3} - \frac{8}{9}\epsilon'\ \right)^{\tt}\Phi_+\left(0;\tt,\frac{12-4\epsilon'}{15-8\epsilon'}\right) \\
+	&= \frac{(3-4\epsilon')^{\tt}}{9^{n}}.
 	\end{split}
@@
 	\frac{n}{n'} &\geq \frac{\ln{(3-4\epsilon')}}{\ln{(3-4\epsilon)}}, \text{ or}\\
-	\epsilon &\leq \frac{3}{4} - \frac{1}{4}(3-4\epsilon')^{\frac{\tt}{\nn}}.
-\end{align}
-As an example, the process with $(\nn, \tt) = (12, 4)$ and $\epsilon' = 0.05$ yields $\epsilon \leq 0.398$.
+	\epsilon &\leq \frac{3}{4} - \frac{1}{4}(3-4\epsilon')^{\frac{\tt}{n}}.
+\end{align}
+As an example, the process with $(n, \tt) = (12, 4)$ and $\epsilon' = 0.05$ yields $\epsilon \leq 0.398$.
 Numerical comparison of the curves with varying $\epsilon$ suggests that we require $\epsilon \leq 0.373$ for the process to be possible.
@@
 \begin{equation}
-	w_+(\epsilon) = \frac{1}{6} -\frac{1}{18}\epsilon
+	\wp(\epsilon) = \frac{1}{6} -\frac{1}{18}\epsilon
 \end{equation}
@@
 \begin{equation}
-	- w_-(\epsilon) = - \left( \frac{1}{3} -\frac{4}{9}\epsilon \right)
+	- \wn(\epsilon) = - \left( \frac{1}{3} -\frac{4}{9}\epsilon \right)
 \end{equation}
@@
 \begin{equation}\label{eq:msd_thermal}
-		\noisys(\epsilon)\too{\nn} \xrightarrow{\E \in \O_{\gamma_\beta}} \noisys(\epsilon')\too{\tt} \otimes \gamma_\beta\too{\nn-\tt},
+		\noisys(\epsilon)\too{n} \xrightarrow{\E \in \O_{\gamma_\beta}} \noisys(\epsilon')\too{\tt} \otimes \gamma_\beta\too{(n-\tt)},
 \end{equation}
@@
 
-Our aim is to obtain a distillation bound for~\cref{eq:msd_thermal} which depends on variables $\nn, \tt, \epsilon, \epsilon'$ as well as $\beta$.
+Our aim is to obtain a distillation bound for~\cref{eq:msd_thermal} which depends on variables $n, \tt, \epsilon, \epsilon'$ as well as $\beta$.
 In the analysis that follows, we drop obvious variable dependencies for clarity.
@@
 \begin{equation}
-	\widetilde{\rm{W}}(\bmx) \coloneqq \frac{\W[\bmx]{\noisys}}{\W[\bmx]{\gamma}},
-\end{equation}
-which naturally splits the phase space $\pd[3]$ into four regions of different ``slopes'', i.e. values of the Gibbs-rescaled distribution, as illustrated in~\cref{fig:pd_split_thermal}.
+	\widetilde{\rm{W}}_{\noisys|\gamma}(\bmx) = \widetilde{\rm{W}}_1(\bmx) \coloneqq \frac{\W[\bmx]{\noisys}}{\W[\bmx]{\gamma}},
+\end{equation}
+which naturally splits the phase space $\pd[3]$ into four regions where the ``slope'', i.e. the value of the Gibbs-rescaled distribution, is different.
 \begin{figure}[h]
@@
     \caption{\textbf{Qutrit phase space regions with different Gibbs-rescaled values.}
+    The slope is positive in regions $X,Y,Z$, but attains a different value in each region and the slope is negative in region $1$.
+    The distribution values and multiplicites (i.e. the numpber of phase space points contained in the region) can be read off as the term coefficients in~\cref{eq:g1}.
     }
@@
 \end{figure}
-
-An $n$-copy system is described over a phase space given by the $n$-times Cartesian product $\pd[3]^{\times n}$) which contains more regions of different slope.
-In particular, it contains exactly the regions $X^i Y^j Z^k$, where $i,j,k = 0,\dots,n$ and $i+j+k \leq n$. 
-For example, region $XY$ consists of all points expressed as the direct sum $\bmx \oplus \bmy$, where $\bmx \in X$ and $\bmy \in Y$.
-
-The $n$-copy Gibbs-rescaled distribution can be written as a self-convolution,
-\begin{equation}
-	\widetilde{\rm{W}}(\bmx) = \frac{\W{\noisys\too{n}}(\bmx)}{\W{\gamma\too{n}}(\bmx)} = \left( \frac{\W{\noisys}(\bmx)}{\W{\gamma}(\bmx)} \right)\too{n} = \widetilde{\bmw}\too{n}.
-\end{equation}
-Therefore, the regions of different slope in an $n$-copy phase space are generated by the 1-copy phase space regions.
+In each region, we want to keep track of the corresponding values and multiplicities of Wigner distributions $\W{\noisys}, \W{\gamma}$ and Gibbs-rescaled distribution $\widetilde{\rm{W}}_1$. 
+To this end, we label the four regions using variables $1,X,Y,Z$ as illustrated in~\cref{fig:pd_split_thermal}, and we write down the expressions:
+\begin{align}\label{eq:g1}
+	G_1(\noisys) &\coloneqq -\wn + 3\wp X + 3\wp Y + 2\wp Z \\
+	\begin{split}
+	G_1(\gamma) &\coloneqq (3\Z)^{-1} \big( e^{-\beta E_2} + 3e^{-\beta E_0} X \\
+	&\hspace{49pt} + 3e^{-\beta E_1} Y + 2e^{-\beta E_2} Z \big) 
+	\end{split}
+	\\
+	\begin{split}
+	G_1(\noisys|\gamma) &\coloneqq (3\Z) \big( -\wn e^{\beta E_2} + 3\wp e^{\beta E_0} X \\
+	&\hspace{41pt} + 3\wp e^{\beta E_1} Y + 2\wp e^{\beta E_2} Z \big)
+	\end{split}
+\end{align}
+The coefficient of each term reads as the multiplicity times the value of the desired distribution in the corresponding region.
+
+An $n$-copy system is described over a phase space given by the $n$-times Cartesian product $\pd[3]^{\times n}$ which generates new regions of different slope.
+In particular, it comprises exactly the regions $X^i Y^j Z^k$, where $i,j,k = 0,\dots,n$ and 
+\begin{equation}
+	\alpha \coloneqq i+j+k \leq n.
+\end{equation} 
+For example, region $YZ$ consists of all points expressed as the direct sum $\bmy \oplus \bmz$, where $\bmy \in Y$ and $\bmz \in Z$.
+\nick{abuse of notation: I use X,Y,Z as sets and as variables that represent those sets}
+
+The $n$-copy Wigner distributions, and therefore the $n$-copy Gibbs-rescaled distribution can be written as self-convolutions,
+\begin{align}
+	\W{\noisys\too{n}}(\bmx) &= \W{\noisys}(\bmx)\too{n} \\
+	\W{\gamma\too{n}}(\bmx) &= \W{\gamma}(\bmx)\too{n} \\
+	\begin{split}
+	\widetilde{\rm{W}}_{\noisys\too{n}|\gamma\too{n}}(\bmx) &= \widetilde{\rm{W}}_n(\bmx) = \frac{\W{\noisys\too{n}}(\bmx)}{\W{\gamma\too{n}}(\bmx)} \\
+	&= \left( \frac{\W{\noisys}(\bmx)}{\W{\gamma}(\bmx)} \right)\too{n} = \left( \widetilde{\rm{W}}_1(\bmx)\right) \too{n}.
+	\end{split}
+\end{align}
+Therefore, the values and multiplicites of the $n$-copy distributions are generated directly as a multinomial expansion of the $1$-copy expressions in~\cref{eq:g1}.
+\begin{align}\label{eq:gn}
+	&G_n(\noisys) \coloneqq G_1(\noisys)^n = \\
+	&\sum\limits_{\substack{i,j,k = 0,\dots,n \\ \alpha \leq n}}\hspace{-10pt} m_{ijk} \big[(-\wn)^{n-\alpha} \wp^{\alpha} \big] X^i Y^j Z^k, \nonumber
+	\\[10pt]
+	&G_n(\gamma) \coloneqq G_1(\gamma)^n = \\
+	&(3\Z)^{-n}\hspace{-10pt} \sum\limits_{\substack{i,j,k = 0,\dots,n \\ \alpha \leq n}}\hspace{-10pt} m_{ijk} \Big[ e^{-\beta ( i E_0 + j E_1 + k E_2 )} e^{-\beta (n-\alpha)E_2} \Big] X^i Y^j Z^k, \nonumber
+	\\[10pt]
+	&G_n(\noisys|\gamma) \coloneqq G_1(\noisys|\gamma)^n = \\
+	&(3\Z)^{n}\hspace{-10pt} \sum\limits_{\substack{i,j,k = 0,\dots,n \\ \alpha \leq n}}\hspace{-10pt} m_{ijk} \Big[ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_2} \times \nonumber\\[-15pt]
+	&\hspace{80pt} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big] X^i Y^j Z^k, \nonumber
+\end{align}
+where the $(i,j,k)$-th term multiplicity $m_{ijk}$ (i.e. the number of phase space points contained in region $X^i Y^j Z^k$) is given by
+\begin{equation}
+	m_{ijk} \coloneqq \frac{n!}{i!j!k!(n-\alpha)!} 3^i 3^j 2^k.
+\end{equation}
+
+In order to construct the Lorenz curve of a Strange state in a thermal fragment we need to sort the components of $\widetilde{W}_n$ in decreasing order.
+In particular, to find the coordinates of the first elbow $(x_0, L_0)$, we need to evaluate the greatest component,
+\begin{equation}\label{eq:max_slope}
+	\widetilde{W}_{\rm{max}} \coloneqq \max\limits_{i,j,k}{\Big\{ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_2} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}}
+\end{equation}
+Notice that for $0 \leq \epsilon \leq \frac{3}{7}$, we have $\wn \geq \wp$.
+Assume that $n$ is even (the analysis is similar for odd $n$). 
+We then need the sum $\alpha = i+j+k$ to be even, so that the expression remains positive.
+
+Given a value for the sum $\alpha$, the term $\wn^{n-\alpha} \wp^{\alpha} e^{-\beta (n-\alpha)E_2}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
+Hence, we have
+\begin{align}
+	\widetilde{W}_{\rm{max}} &= \max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_2} e^{\beta \alpha E_{\rm{max}}} \Big\}} \\
+	&= \max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \wn^n e^{\beta n E_2} \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_2)} \right)^{\alpha} \Big\}}
+\end{align}
+The last expression is clearly maximised for $\alpha = 0$ ($\alpha = n$) when the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_2)} \leq 1$ ($>1$).
+Therefore, we have
+\begin{equation}
+\widetilde{W}_{\rm{max}} =
+	\begin{cases}
+		\wn^n e^{n\beta E_2},\ &\beta \leq \frac{1}{E_{\rm{max}} - E_2}\ln{\left( 8-\frac{18}{3-\epsilon} \right)} \\
+		\wp^n e^{n\beta E_{\rm{max}}},\ &\beta > \frac{1}{E_{\rm{max}} - E_2}\ln{\left( 8-\frac{18}{3-\epsilon} \right)}
+	\end{cases}
+\end{equation}
 
@@
 \begin{equation}\label{eq:stdist}
-	\noisys\too{\nn} \longrightarrow \noisys(\tt, \epsilon', \nn - \nn') \coloneqq  \noisys(\epsilon')\too{\tt} \otimes \left( \frac{1}{3}\id \right)\too{(\nn-\tt)},
+	\noisys\too{n} \longrightarrow \noisys(\tt, \epsilon', n - n') \coloneqq  \noisys(\epsilon')\too{\tt} \otimes \left( \frac{1}{3}\id \right)\too{(n-\tt)},
 \end{equation}
@@
 
-We choose the temperature regime in~\cref{eq:tempregime} and we pick the location $x_\star = x_0 = (3Z)^{-\nn} = (3(2+e^{-\beta}))^{-\nn}$ of the first elbow of the initial state $\noisys(\nn, \epsilon, 0)$ and write down the necessary distillation constraint,
-\begin{equation}
-	\lc{\noisys(\nn, \epsilon, 0)}{\gamma_\beta}(x_\star) \geq \lc{\noisys(\tt, \epsilon', \nn-\tt)}{\gamma_\beta}(x_\star).
-\end{equation}
-
-The initial state Lorenz curve coordinate at this location is $L_\star = L_0 = (1/3 - 4\epsilon/9)^{\nn}$.
+We choose the temperature regime in~\cref{eq:tempregime} and we pick the location $x_\star = x_0 = (3Z)^{-n} = (3(2+e^{-\beta}))^{-n}$ of the first elbow of the initial state $\noisys(n, \epsilon, 0)$ and write down the necessary distillation constraint,
+\begin{equation}
+	\lc{\noisys(n, \epsilon, 0)}{\gamma_\beta}(x_\star) \geq \lc{\noisys(\tt, \epsilon', n-\tt)}{\gamma_\beta}(x_\star).
+\end{equation}
+
+The initial state Lorenz curve coordinate at this location is $L_\star = L_0 = (1/3 - 4\epsilon/9)^{n}$.
 
@@
 \begin{equation}\label{eq:constraint_deriv_temp}
-	L'_\star = \frac{x_\star}{x'_0}L'_0 = (3(2+e^{-\beta}))^{\tt-\nn} \left( \frac{1}{3} - \frac{4}{9} \epsilon' \right)^{\tt}.
+	L'_\star = \frac{x_\star}{x'_0}L'_0 = (3(2+e^{-\beta}))^{\tt-n} \left( \frac{1}{3} - \frac{4}{9} \epsilon' \right)^{\tt}.
 \end{equation}
@@
 \end{align}
-with $\tt \leq \nn$ and $\epsilon' \leq \epsilon \leq 3 - 18/\big(8-e^{\beta}\big)$.
+with $\tt \leq n$ and $\epsilon' \leq \epsilon \leq 3 - 18/\big(8-e^{\beta}\big)$.
 
@@
 \end{align}
-with $\tt \leq \nn$ and $\epsilon' \leq \epsilon$. 
+with $\tt \leq n$ and $\epsilon' \leq \epsilon$. 
 Moreover, if $E_2$ is not largest, we have the additional constarint $\epsilon \leq 3 - 18/\big(8-e^{\beta}\big)$.

### 2021-02-02 magic_paper.tex
added low and high temperature limits separately

@@
 The use of majorization in this setting provides useful intuition for our purposes.
-At any given temperature $\beta$, the thermal state $\gamma_\beta$ is thermodynamically the most disordered state. 
+At any given temperature $\beta^{-1}$, the thermal state $\gamma_\beta$ is thermodynamically the most disordered state. 
 Thermal operations are defined as operations that cannot extract energy from the Gibbs state, $\E(\gamma_\beta) = \gamma_\beta$.
@@
 
-Consider a qutrit system with maximally Wigner-negative magic state $\ket{\rm{S}} = \frac{1}{\sqrt{2}}(\ket{0} - \omega^2 \ket{1})$.
+Consider a qutrit system with maximally Wigner-negative magic state $\ket{{\rm{S}}} = \frac{1}{\sqrt{2}}(\ket{1} - \ket{2})$.
 It can be written in density operator form as
 \begin{align}
-	\ketbra{\rm{S}} = \sum_{\bmx \neq (2,2)} \frac{1}{6} A_{\bmx} - \frac{1}{3} A_{(2,2)},
+	\ketbra{\rm{S}} = -\frac{1}{3} A_{\bmo} + \sum_{\bmx \neq \bmo} \frac{1}{6} A_{\bmx},
 \end{align}
 where $\bmx$ ranges in the $3$-dimensional phase space $\pd[3]$.
-This is a permutation of the pure Strange state visualised in~\cref{fig:strange}.
+This is the pure Strange state visualised in~\cref{fig:strange}.
 We allow for isotropic (uniform) noise, so that the system state is a convex sum of the pure Strange state and the maximally mixed state,
@@
 \end{equation}
-where we choose to restrict the noise level, $0 \leq \epsilon \leq \frac{3}{7}$, so that the Wigner distribution of the state always contains a negative component which is greater than the 8 positive components of the state.
+where we choose to restrict the noise level, $0 \leq \epsilon \leq \frac{3}{7}$, so that the Wigner distribution of the state always contains a negative component which is greater than the remaining 8 positive components.
 
@@
 \end{equation}
-at the 8 phase space points $\bmx \in \pd[3] \setminus \{(2,2)\}$ and a negative component
+at the 8 phase space points $\bmx \in \pd[3] \setminus \{\bmo\}$ and a negative component
 \begin{equation}
@@
 \end{equation}
-at point $\bmx = (2,2)$.
+at the origin $\bmx = \bmo$.
 
@@
 We have that energy eigenvalues $E_i \geq 0$, but impose no order between them.
+We denote the highest energy eigenvalue as
+\begin{equation}
+	E_{\rm{max}} \coloneqq \max{\{E_0, E_1, E_2\}}.
+\end{equation}
 
@@
     \caption{\textbf{Qutrit phase space regions with different Gibbs-rescaled values.}
-    The slope is positive in regions $X,Y,Z$, but attains a different value in each region and the slope is negative in region $1$.
-    The distribution values and multiplicites (i.e. the numpber of phase space points contained in the region) can be read off as the term coefficients in~\cref{eq:g1}.
+    The slope is positive in regions $X,Y,Z$ and negative in region $1$.
+    It attains a unique value in each region.
+    The values and multiplicites can be read off as the term coefficients in~\cref{eq:g1}.
     }
@@
 \end{figure}
-In each region, we want to keep track of the corresponding values and multiplicities of Wigner distributions $\W{\noisys}, \W{\gamma}$ and Gibbs-rescaled distribution $\widetilde{\rm{W}}_1$. 
+In each region, we want to keep track of the number of phase space points it contains (i.e.
+the multiplicity) and the corresponding values of the Wigner distributions $\W{\noisys}, \W{\gamma}$ and the Gibbs-rescaled distribution $\widetilde{\rm{W}}_1$.
 To this end, we label the four regions using variables $1,X,Y,Z$ as illustrated in~\cref{fig:pd_split_thermal}, and we write down the expressions:
 \begin{align}\label{eq:g1}
-	G_1(\noisys) &\coloneqq -\wn + 3\wp X + 3\wp Y + 2\wp Z \\
+	G_1(\noisys) &\coloneqq -\wn + 2\wp X + 3\wp Y + 3\wp Z \\
 	\begin{split}
-	G_1(\gamma) &\coloneqq (3\Z)^{-1} \big( e^{-\beta E_2} + 3e^{-\beta E_0} X \\
-	&\hspace{49pt} + 3e^{-\beta E_1} Y + 2e^{-\beta E_2} Z \big) 
+	G_1(\gamma) &\coloneqq (3\Z)^{-1} \big( e^{-\beta E_0} + 2e^{-\beta E_0} X \\
+	&\hspace{49pt} + 3e^{-\beta E_1} Y + 3e^{-\beta E_2} Z \big) 
 	\end{split}
@@
 	\begin{split}
-	G_1(\noisys|\gamma) &\coloneqq (3\Z) \big( -\wn e^{\beta E_2} + 3\wp e^{\beta E_0} X \\
-	&\hspace{41pt} + 3\wp e^{\beta E_1} Y + 2\wp e^{\beta E_2} Z \big)
+	G_1(\noisys|\gamma) &\coloneqq (3\Z) \big( -\wn e^{\beta E_0} + 2\wp e^{\beta E_0} X \\
+	&\hspace{41pt} + 3\wp e^{\beta E_1} Y + 3\wp e^{\beta E_2} Z \big)
 	\end{split}
@@
 The coefficient of each term reads as the multiplicity times the value of the desired distribution in the corresponding region.
+Note that the negative Strange state Wigner component pairs with energy eigenvalue $E_0$ in region $1$.
 
@@
 \end{equation}
-For example, region $YZ$ consists of all points expressed as the direct sum $\bmy \oplus \bmz$, where $\bmy \in Y$ and $\bmz \in Z$.
+For example, region $YZ$ consists of all points expressed as the direct sum $\bmy \oplus \bmz$ or $\bmz \oplus \bmy$, where $\bmy \in Y$ and $\bmz \in Z$.
+Note that there is no difference between e.g. regions $YZ$ and $ZY$, since multiplication of slopes is commutative. 
 \nick{abuse of notation: I use X,Y,Z as sets and as variables that represent those sets}
 
-The $n$-copy Wigner distributions, and therefore the $n$-copy Gibbs-rescaled distribution can be written as self-convolutions,
-\begin{align}
-	\W{\noisys\too{n}}(\bmx) &= \W{\noisys}(\bmx)\too{n} \\
-	\W{\gamma\too{n}}(\bmx) &= \W{\gamma}(\bmx)\too{n} \\
-	\begin{split}
-	\widetilde{\rm{W}}_{\noisys\too{n}|\gamma\too{n}}(\bmx) &= \widetilde{\rm{W}}_n(\bmx) = \frac{\W{\noisys\too{n}}(\bmx)}{\W{\gamma\too{n}}(\bmx)} \\
-	&= \left( \frac{\W{\noisys}(\bmx)}{\W{\gamma}(\bmx)} \right)\too{n} = \left( \widetilde{\rm{W}}_1(\bmx)\right) \too{n}.
-	\end{split}
+The $n$-copy Wigner distributions $\W{\noisys\too{n}}, \W{\gamma\too{n}}$, and consequently the $n$-copy Gibbs-rescaled distribution $\widetilde{\rm{W}}_n = \widetilde{\rm{W}}_{\noisys\too{n}|\gamma\too{n}}$ can be written as self-convolutions,
+\begin{align}
+	\W{\noisys\too{n}}(\bmx_1 \oplus \dots \oplus \bmx_n) &= \W{\noisys}(\bmx_1)\dots\W{\noisys}(\bmx_n) \nonumber\\
+	&= \W{\noisys}(\bmx)\too{n} \\[10pt]
+	\W{\gamma\too{n}}(\bmx_1 \oplus \dots \oplus \bmx_n) &= \W{\gamma}(\bmx_1)\dots\W{\gamma}(\bmx_n) \nonumber\\
+	&= \W{\gamma}(\bmx)\too{n} \\[10pt]
+	\widetilde{\rm{W}}_n(\bmx_1 \oplus \dots \oplus \bmx_n) &= \frac{\W{\noisys\too{n}}(\bmx_1 \oplus \dots \oplus \bmx_n)}{\W{\gamma\too{n}}(\bmx_1 \oplus \dots \oplus \bmx_n)} \\
+	= \frac{\W{\noisys}(\bmx_1)\dots\W{\noisys}(\bmx_n)}{\W{\gamma}(\bmx_1)\dots\W{\gamma}(\bmx_n)} &= \left( \frac{\W{\noisys}(\bmx)}{\W{\gamma}(\bmx)} \right)\too{n} \nonumber\\
+	&= \left( \widetilde{\rm{W}}_1(\bmx)\right) \too{n}. \nonumber
 \end{align}
@@
 	&G_n(\gamma) \coloneqq G_1(\gamma)^n = \\
-	&(3\Z)^{-n}\hspace{-10pt} \sum\limits_{\substack{i,j,k = 0,\dots,n \\ \alpha \leq n}}\hspace{-10pt} m_{ijk} \Big[ e^{-\beta ( i E_0 + j E_1 + k E_2 )} e^{-\beta (n-\alpha)E_2} \Big] X^i Y^j Z^k, \nonumber
+	&(3\Z)^{-n}\hspace{-10pt} \sum\limits_{\substack{i,j,k = 0,\dots,n \\ \alpha \leq n}}\hspace{-10pt} m_{ijk} \Big[ e^{-\beta ( i E_0 + j E_1 + k E_2 )} e^{-\beta (n-\alpha)E_0} \Big] X^i Y^j Z^k, \nonumber
 	\\[10pt]
 	&G_n(\noisys|\gamma) \coloneqq G_1(\noisys|\gamma)^n = \\
-	&(3\Z)^{n}\hspace{-10pt} \sum\limits_{\substack{i,j,k = 0,\dots,n \\ \alpha \leq n}}\hspace{-10pt} m_{ijk} \Big[ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_2} \times \nonumber\\[-15pt]
+	&(3\Z)^{n}\hspace{-10pt} \sum\limits_{\substack{i,j,k = 0,\dots,n \\ \alpha \leq n}}\hspace{-10pt} m_{ijk} \Big[ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} \times \nonumber\\[-15pt]
 	&\hspace{80pt} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big] X^i Y^j Z^k, \nonumber
@@
 \begin{equation}
-	m_{ijk} \coloneqq \frac{n!}{i!j!k!(n-\alpha)!} 3^i 3^j 2^k.
+	m_{ijk} \coloneqq \frac{n!}{i!j!k!(n-\alpha)!} 2^i 3^j 3^k.
 \end{equation}
@@
 \begin{equation}\label{eq:max_slope}
-	\widetilde{W}_{\rm{max}} \coloneqq \max\limits_{i,j,k}{\Big\{ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_2} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}}
+	\widetilde{W}_{\rm{max}} \coloneqq \max\limits_{i,j,k}{\Big\{ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}}
 \end{equation}
@@
 
-Given a value for the sum $\alpha$, the term $\wn^{n-\alpha} \wp^{\alpha} e^{-\beta (n-\alpha)E_2}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
+Given an even value $\alpha$ for the sum, the term $\wn^{n-\alpha} \wp^{\alpha} e^{-\beta (n-\alpha)E_0}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
 Hence, we have
 \begin{align}
-	\widetilde{W}_{\rm{max}} &= \max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_2} e^{\beta \alpha E_{\rm{max}}} \Big\}} \\
-	&= \max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \wn^n e^{\beta n E_2} \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_2)} \right)^{\alpha} \Big\}}
-\end{align}
-The last expression is clearly maximised for $\alpha = 0$ ($\alpha = n$) when the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_2)} \leq 1$ ($>1$).
-Therefore, we have
+	\widetilde{W}_{\rm{max}} &= \max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta \alpha E_{\rm{max}}} \Big\}} \\
+	&= \max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \wn^n e^{n\beta E_0} \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}
+\end{align}
+The last expression is clearly maximised for $\alpha = 0$ ($\alpha = n$) when the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than or equal to $1$ (greater than $1$).
+We want to rewrite the expression as a noise level $\epsilon$ constraint with respect to temperature $\beta^{-1}$, where the noise threshold is
+\begin{equation}
+	\epsilon_{\rm{th}} \coloneqq 3 - \dfrac{18}{8-e^{(E_{\rm{max}} - E_0)\beta}}.
+	%\beta \leq \frac{1}{E_{\rm{max}} - E_0}\ln{\left( 8-\frac{18}{3-\epsilon} \right)}
+\end{equation}
+The noise threshold $\epsilon_{\rm{th}}$ is an increasing function of temperature $\beta^{-1}$.
+We have
 \begin{equation}
@@
 	\begin{cases}
-		\wn^n e^{n\beta E_2},\ &\beta \leq \frac{1}{E_{\rm{max}} - E_2}\ln{\left( 8-\frac{18}{3-\epsilon} \right)} \\
-		\wp^n e^{n\beta E_{\rm{max}}},\ &\beta > \frac{1}{E_{\rm{max}} - E_2}\ln{\left( 8-\frac{18}{3-\epsilon} \right)}
+		\wn^n e^{n\beta E_0}, &\epsilon \leq \epsilon_{\rm{th}}, 	\\
+		\wp^n e^{n\beta E_{\rm{max}}}, &\epsilon > \epsilon_{\rm{th}}.
 	\end{cases}
@@
 
+For low noise levels $\epsilon \leq \epsilon_{\rm{th}}$, we get $\widetilde{W}_{\rm{max}} = \wn^n e^{n\beta E_0}$ occuring in the region labelled by $(i,j,k) = (0,0,0)$.
+This scenario includes the unital fragment, defined at the limit $\beta \rightarrow 0$, because for $\beta = 0$, we have $\epsilon_{\rm{th}} = 3/7$, so $\epsilon \leq \epsilon_{\rm{th}}$ always holds.
+
+In the low noise level scenario, the multiplicity is $m_{000} = 1$ and the first elbow coordinates can be read off the $X^0Y^0Z^0$ term in generating functions $G_n(\noisys), G_n(\gamma)$,
+\begin{equation}
+	(x_0, L_0) = ((3\Z)^{-n}, \wn^n)
+\end{equation}
+and the necessary distillation constraint defined at the location $x_\star = x_0$ of the initial state's first elbow is
+\begin{equation}\label{eq:first_elbow_constraint}
+	\lc{\noisys(\epsilon)\too{n}}{\gamma_\beta}(x_\star) \geq \lc{\noisys(\epsilon')\too{\tt}}{\gamma_\beta}(x_\star).
+\end{equation}
+
+The first elbow of the target state is located at $x'_0 = (3Z)^{-\tt} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the target state's first elbow,
+\begin{equation}\label{eq:constraint_deriv_temp}
+	L'_\star = \frac{x_\star}{x'_0}L'_0 = (3\Z_\beta)^{\tt-n} \left( \frac{1}{3} - \frac{4}{9} \epsilon' \right)^{\tt}.
+\end{equation}
+The process in~\cref{eq:stdist} is therefore possible only if $L_\star \geq L'_\star$ or equivalently,
+\begin{align}
+	\frac{n}{n'} \geq \frac{\ln{\Big[ \big( 1-\frac{4}{3}\epsilon' \big)\Z_\beta \Big]}}{\ln{\Big[ \big( 1-\frac{4}{3}\epsilon \big)\Z_\beta \Big]}} = \frac{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} - \beta F_\beta}{\ln{\big( 1-\frac{4}{3}\epsilon \big)} - \beta F_\beta},
+\end{align}
+with $\tt \leq n$ and $\epsilon' \leq \epsilon \leq \epsilon_{\rm{th}}$. 
+The free energy of thermal state $\gamma_\beta$ is denoted by
+\begin{equation}
+	F_\beta \coloneqq \tr[\gamma_\beta H] - \beta^{-1} \tr[\gamma_\beta \log{\gamma_\beta}].
+\end{equation}
+
+Our approach also allows for analysis at the limit of low temperature, $\beta \rightarrow \infty$.
+In fact, for any
+\begin{equation}
+	\beta \geq \beta_{\rm{th}} \coloneqq \frac{1}{E_{\rm{max}} - E_0} \ln2,
+\end{equation}
+we always have $\epsilon_{\rm{th}} \leq 0$, so $\epsilon \geq \epsilon_{\rm{th}}$.
+Note that if $E_{\rm{max}} = E_0$, the bound is infinite, simply meaning that $\epsilon = \epsilon_{\rm{th}}$ at the limit $\beta = \infty$.
+In the low temperature scenario, we get $\widetilde{W}_{\rm{max}} = \wn^p e^{n\beta E_{\rm{max}}}$ occuring in a region labelled by 
+\begin{equation}
+	(i,j,k) = 
+	\begin{cases}
+	(n,0,0), &E_{\rm{max}} = E_0, \\
+	(0,n,0), &E_{\rm{max}} = E_1, \\
+	(0,0,n), &E_{\rm{max}} = E_2.
+	\end{cases}
+\end{equation}
+The bound expression does not depend on which energy is the highest so, without loss of generality, assume that $E_{\rm{max}} = E_0$.
+Then, the multiplicity is $m_{n00} = 2^n$ and the first elbow coordinates can be read off the $X^nY^0Z^0$ term in generating functions $G_n(\noisys), G_n(\gamma)$,
+\begin{equation}
+	(x_0, L_0) = \left( \left(\frac{2}{3}\frac{e^{-\beta E_0}}{\Z_\beta}\right)^n, (2u)^n \right)
+\end{equation}
+and the distillation constraint is defined at the location $x_\star = x_0$ of the initial state's first elbow as in~\cref{eq:first_elbow_constraint}.
+
+The first elbow of the target state is located at $x'_0 = (2e^{-\beta E_0} / (2\Z_\beta))^{\tt} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the target state's first elbow,
+\begin{equation}\label{eq:constraint_deriv_lowtemp}
+	L'_\star = \frac{x_\star}{x'_0}L'_0 = 2^n \left(\frac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n-\tt} \left( \frac{1}{6} - \frac{1}{18}\epsilon' \right)^{\tt}.
+\end{equation}
+Therefore, in the low temperature scenario $\beta \geq \beta_{\rm{th}}$, the distillation process in~\cref{eq:stdist} is possible only if $L_\star \geq L'_\star$ or equivalently,
+\begin{align}
+	\frac{n}{n'} &\geq \frac{\ln{\Big[ \big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)\Z_\beta e^{\beta E_{\rm{max}}} \Big]}}{\ln{\Big[ \big( \frac{1}{2}-\frac{1}{6}\epsilon \big)\Z_\beta e^{\beta E_{\rm{max}}} \Big]}} \nonumber\\
+	&= \frac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} - \beta F_\beta + \beta E_{\rm{max}}}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} - \beta F_\beta + \beta E_{\rm{max}}},
+\end{align}
+with $\tt \leq n$ and $\epsilon' \leq \epsilon$.
+
+\null\newpage
+\null\newpage
+
 \subsection{OLD Magic in thermal fragments}
+
+For $\beta = 0$, $\epsilon_{\rm{th}} = 3/7$, so $\epsilon \leq \epsilon_{\rm{th}}$ always.
+In this case, $\widetilde{W}_{\rm{max}} = \wn^n e^{n\beta E_0}$ occuring in the region labelled by $(i,j,k) = (0,0,0)$.
+
+For 	
+\begin{equation}
+	\beta \geq \beta_{\rm{th}} \coloneqq \frac{1}{E_{\rm{max}} - E_0} \ln2,
+\end{equation}
+$\epsilon_{\rm{th}} \leq 0$, so $\epsilon \geq \epsilon_{\rm{th}}$ always.
+
+For $0 < \beta < \beta_{\rm{th}}$, the order between energy eigenvalues matters.
+\begin{itemize}
+\item If $E_{\rm{max}} = E_0$, only the first case is valid, since the noise constraint becomes $\epsilon \leq 3/7$.
+In this case, $\widetilde{W}_{\rm{max}} = \wn^n e^{n\beta E_0}$ occuring in the region labelled by $(i,j,k) = (0,0,0)$.
+\item If $E_{\rm{max}} = E_1$, then for low noise levels $\epsilon \leq \epsilon_{\rm{th}}$, $\widetilde{W}_{\rm{max}}  = \wn^n e^{n\beta E_0}$ occuring in the region labelled by $(i,j,k) = (0,0,0)$ and for high noise levels $\epsilon > \epsilon_{\rm{th}}$, $\widetilde{W}_{\rm{max}}  = \wp^n e^{n\beta E_1}$ occuring in the region labelled by $(i,j,k) = (0,n,0)$.
+\item If $E_{\rm{max}} = E_2$, then for low noise levels $\epsilon \leq \epsilon_{\rm{th}}$, $\widetilde{W}_{\rm{max}}  = \wn^n e^{n\beta E_0}$ occuring in the region labelled by $(i,j,k) = (0,0,0)$ and for high noise levels $\epsilon > \epsilon_{\rm{th}}$, $\widetilde{W}_{\rm{max}}  = \wp^n e^{n\beta E_2}$ occuring in the region labelled by $(i,j,k) = (0,0,n)$.
+\end{itemize}
 
@@
 in the thermal fragment $\O_{\gamma_\beta}$.
-We are now in a position to extract a distillation bound that takes the temperature $\beta$ into account in an analogous method as the one used for the unital fragment distillation bound.
+We are now in a position to extract a distillation bound that takes the temperature $\beta^{-1}$ into account in an analogous method as the one used for the unital fragment distillation bound.
 
@@
     \caption{\textbf{Threshold dependence on temperature in thermal fragments.} Lorenz curve ratios for the Strange state purifying process in~\cref{eq:sdist} with $\epsilon' = 0.05$.
-    The peaks of each curve indicate the optimal temperature $\beta_{\rm{max}}$ that allows for the highest noise threshold at every given number of initial state copies $k$.
+    The peaks of each curve indicate the optimal temperature $\beta_{\rm{max}}^{-1}$ that allows for the highest noise threshold at every given number of initial state copies $k$.
     The line $\epsilon = \frac{3}{4}$ indicates the threshold noise beyond which the Strange state no longer contains negativities.

### 2021-02-02 magic_paper.tex
Added rates and figures of rates for key noise, temperature regimes. Low temperature looks pretty horrible

@@
 \end{equation}
-The process in~\cref{eq:stdist} is therefore possible only if $L_\star \geq L'_\star$ or equivalently,
+The process in~\cref{eq:msd_thermal} is therefore possible only if $L_\star \geq L'_\star$ or equivalently,
 \begin{align}
@@
 \end{equation}
+
+Moreover, we can obtain an upper bound on thermal fragment distillation rate $R=n'/n$ for pure target Strange states ($\epsilon' = 0$) given by
+\begin{equation}
+	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\big( 1-\frac{4}{3}\epsilon \big)}}{\beta F_\beta},
+\end{equation}
+which holds for all finite $n$ with $\tt \leq n$ and $\epsilon' \leq \epsilon \leq \epsilon_{\rm{th}}$. 
+We compare $R(\beta)$ for different values of $\beta$ with the mana bound $R_{\rm{mana}}$ in~\cref{fig:distill_bounds_temp}.
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.5]{figs/distill_bounds_temp.pdf}
+    \caption{\textbf{Distillation rate with low noise in thermal fragments.} Distillation rates obtained by majorization $R(\beta)$ for low noise levels $\epsilon \leq \epsilon_{\rm{th}}$ are plotted for different temperatures $\beta^{-1}$ such that $0 \leq \beta \leq \beta_{\rm{th}}$.
+    The mana distillation rate $R_{\rm{mana}}$ is given for comparison.
+    As $\beta$ increases, the range of noise levels for which $R(\beta)$ is valid decreases and the distillation bound becomes stricter.
+    }
+    \label{fig:distill_bounds_temp}
+\end{figure}
 
@@
 \end{equation}
-Therefore, in the low temperature scenario $\beta \geq \beta_{\rm{th}}$, the distillation process in~\cref{eq:stdist} is possible only if $L_\star \geq L'_\star$ or equivalently,
+Therefore, in the low temperature scenario $\beta \geq \beta_{\rm{th}}$, the distillation process in~\cref{eq:msd_thermal} is possible only if $L_\star \geq L'_\star$ or equivalently,
 \begin{align}
 	\frac{n}{n'} &\geq \frac{\ln{\Big[ \big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)\Z_\beta e^{\beta E_{\rm{max}}} \Big]}}{\ln{\Big[ \big( \frac{1}{2}-\frac{1}{6}\epsilon \big)\Z_\beta e^{\beta E_{\rm{max}}} \Big]}} \nonumber\\
-	&= \frac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} - \beta F_\beta + \beta E_{\rm{max}}}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} - \beta F_\beta + \beta E_{\rm{max}}},
+	&= \frac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F_\beta)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F_\beta)},
 \end{align}
 with $\tt \leq n$ and $\epsilon' \leq \epsilon$.
+
+We can obtain an upper bound on thermal fragment distillation rate $R=n'/n$ for pure target Strange states ($\epsilon' = 0$) in this regime as well. 
+It is given by
+\begin{equation}
+	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\big(\frac{3}{3-\epsilon} \big)}}{-\ln{2} + \beta (E_{\rm{max}} - F_\beta)},
+\end{equation}
+which holds for all finite $n$ with $\tt \leq n$ and $\epsilon' \leq \epsilon$. 
+We compare $R(\beta)$ for different values of $\beta$ with the mana bound $R_{\rm{mana}}$ in~\cref{fig:distill_bounds_lowtemp}.
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.5]{figs/distill_bounds_lowtemp.pdf}
+    \caption{\textbf{Distillation rate for low temperatures in thermal fragments.} Distillation rates obtained by majorization $R(\beta)$ in the temperature regime $\beta \geq \beta_{\rm{th}}$ are plotted for different temperatures $\beta^{-1}$.
+    The mana distillation rate $R_{\rm{mana}}$ is given for comparison.
+    \nick{Terrible bound for low temperatures. I'll check for possible calculation errors.}
+    }
+    \label{fig:distill_bounds_lowtemp}
+\end{figure}
 

### 2021-02-08 magic_paper.tex
minor additions
restructured coordinate analysis to be more legible, added red note on important fine print, but checked the rest numerically and have corrected minor errors

@@
 \begin{equation}
-    \mana{\rho} \coloneqq \log{(2\sn{\rho}+1)},
+    \mana{\rho} \coloneqq \ln{(2\sn{\rho}+1)},
 \end{equation}
@@
 \end{align}
-The last expression is clearly maximised for $\alpha = 0$ ($\alpha = n$) when the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than or equal to $1$ (greater than $1$).
+The last expression is maximised for $\alpha = 0$ ($\alpha = n$) when the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than or equal to $1$ (greater than $1$).
 We want to rewrite the expression as a noise level $\epsilon$ constraint with respect to temperature $\beta^{-1}$, where the noise threshold is
@@
 \end{equation}
-The noise threshold $\epsilon_{\rm{th}}$ is an increasing function of temperature $\beta^{-1}$.
+The noise threshold $\epsilon_{\rm{th}}$ is a decreasing function of $\beta$.
+It achieves its maximum value $3/7$ for $(E_{\rm{max}} - E_0)\beta = 0$, and its minimum value $0$ for
+\begin{equation}
+	\beta_{\rm{th}} \coloneqq \frac{1}{E_{\rm{max}} - E_0} \ln2.
+\end{equation}
 We have
@@
 	\begin{cases}
-		\wn^n e^{n\beta E_0}, &\epsilon \leq \epsilon_{\rm{th}}, 	\\
-		\wp^n e^{n\beta E_{\rm{max}}}, &\epsilon > \epsilon_{\rm{th}}.
+		\wn^n e^{n\beta E_0}, &\epsilon \leq \epsilon_{\rm{th}},\ \hspace{30pt}\rm{(C1)}	\\
+		\wp^n e^{n\beta E_{\rm{max}}}, &\epsilon > \epsilon_{\rm{th}}.\ \hspace{32pt}\rm{(C2)} 
 	\end{cases}
 \end{equation}
-
-For low noise levels $\epsilon \leq \epsilon_{\rm{th}}$, we get $\widetilde{W}_{\rm{max}} = \wn^n e^{n\beta E_0}$ occuring in the region labelled by $(i,j,k) = (0,0,0)$.
-This scenario includes the unital fragment, defined at the limit $\beta \rightarrow 0$, because for $\beta = 0$, we have $\epsilon_{\rm{th}} = 3/7$, so $\epsilon \leq \epsilon_{\rm{th}}$ always holds.
-
-In the low noise level scenario, the multiplicity is $m_{000} = 1$ and the first elbow coordinates can be read off the $X^0Y^0Z^0$ term in generating functions $G_n(\noisys), G_n(\gamma)$,
-\begin{equation}
-	(x_0, L_0) = ((3\Z)^{-n}, \wn^n)
-\end{equation}
-and the necessary distillation constraint defined at the location $x_\star = x_0$ of the initial state's first elbow is
+Case 1 $\rm{(C1)}$ corresponds to the region labelled by $(i,j,k) = (0,0,0)$.
+Case 2 $\rm{(C2)}$ corresponds to the region labelled by 
+\begin{equation}
+	(i,j,k) = 
+	\begin{cases}
+	(0,n,0), &\text{if } E_{\rm{max}} = E_1, \\
+	(0,0,n), &\text{if } E_{\rm{max}} = E_2.
+	\end{cases}
+\end{equation}
+Note that if $E_{\rm{max}} = E_0$, we get $\epsilon_{\rm{th}} = 3/7$ and $\rm{(C1)}$ holds for all $\epsilon$ and $\beta$.
+Assuming $E_{\rm{max}} > E_0$, we get the cases:
+\begin{itemize}
+	\item $\beta = 0$. Then, $\epsilon_{\rm{th}} = 3/7$ and $\rm{(C1)}$ holds for all noise levels $\epsilon$.
+	This is the unital fragment.
+	\item $0 < \beta < \beta_{\rm{th}}$. Then, $0 < \epsilon_{\rm{th}} < 3/7$ and $\rm{(C1)}$ holds for $\epsilon \leq \epsilon_{\rm{th}}$, while $\rm{(C2)}$ holds for $\epsilon \geq \epsilon_{\rm{th}}$.
+	\item $\beta \geq \beta_{\rm{th}}$. Then, $ \epsilon_{\rm{th}} \leq 0$ and $\rm{(C2)}$ holds for all $\epsilon$.
+\end{itemize}
+
+Whenever the set of physical parameters falls under $\rm{(C1)}$, the multiplicity is $m_{000} = 1$ and the first elbow coordinates can be read off the $X^0Y^0Z^0$ term in generating functions $G_n(\noisys), G_n(\gamma)$.
+If it falls under $\rm{(C2)}$, then $E_{\rm{max}} = E_1$ ($E_{\rm{max}} = E_2$), the multiplicity is $m_{0n0} = 3^n$ ($m_{00n} = 3^n$) and the first elbow coordinates can be read off the $X^0Y^nZ^0$ ($X^0Y^0Z^n$) term in generating functions $G_n(\noisys), G_n(\gamma)$,
+\begin{equation}
+	(x_0, L_0) =
+	\begin{cases}
+		\left( \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^n, \wn^n \right), &\rm{(C1)}	\vspace{10pt}\\
+		\left( \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^n, (3u)^n \right). &\rm{(C2)} 
+	\end{cases}
+\end{equation}
+
+Considering the distillation process in~\cref{eq:msd_thermal}, the Lorenz curves of the initial and target states may each be described by either $\rm{(C1)}$ or $\rm{(C2)}$.
+In any case, a necessary distillation constraint can be defined at the location $x_\star = x_0$ of the initial state's first elbow and be expressed as
 \begin{equation}\label{eq:first_elbow_constraint}
@@
 
+Let's focus on the case where both Lorenz curves are described by $\rm{(C1)}$.
+This case includes the unital fragment.
+
 The first elbow of the target state is located at $x'_0 = (3Z)^{-\tt} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the target state's first elbow,
 \begin{equation}\label{eq:constraint_deriv_temp}
-	L'_\star = \frac{x_\star}{x'_0}L'_0 = (3\Z_\beta)^{\tt-n} \left( \frac{1}{3} - \frac{4}{9} \epsilon' \right)^{\tt}.
-\end{equation}
-The process in~\cref{eq:msd_thermal} is therefore possible only if $L_\star \geq L'_\star$ or equivalently,
-\begin{align}
-	\frac{n}{n'} \geq \frac{\ln{\Big[ \big( 1-\frac{4}{3}\epsilon' \big)\Z_\beta \Big]}}{\ln{\Big[ \big( 1-\frac{4}{3}\epsilon \big)\Z_\beta \Big]}} = \frac{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} - \beta F_\beta}{\ln{\big( 1-\frac{4}{3}\epsilon \big)} - \beta F_\beta},
+	L'_\star = \frac{x_\star}{x'_0}L'_0 = \left(\frac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n-\tt} \left( \frac{1}{3} - \frac{4}{9} \epsilon' \right)^{\tt}.
+\end{equation}
+The constraint in~\cref{eq:first_elbow_constraint} therefore holds only if
+\begin{align}
+	\frac{n}{n'} &\geq \frac{\ln{\Big[ \big( 1-\frac{4}{3}\epsilon' \big)\Z_\beta  e^{\beta E_0} \Big]}}{\ln{\Big[ \big( 1-\frac{4}{3}\epsilon \big)\Z_\beta e^{\beta E_0} \Big]}} \\
+	&= \frac{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} - \beta (F_\beta - E_0)}{\ln{\big( 1-\frac{4}{3}\epsilon \big)} - \beta (F_\beta - E_0)},
 \end{align}
@@
 \begin{equation}
-	F_\beta \coloneqq \tr[\gamma_\beta H] - \beta^{-1} \tr[\gamma_\beta \log{\gamma_\beta}].
+	F_\beta \coloneqq \tr[\gamma_\beta H] + \beta^{-1} \tr[\gamma_\beta \ln{\gamma_\beta}] = -\beta^{-1} \ln{\Z_\beta}.
 \end{equation}
@@
 \begin{equation}
-	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\big( 1-\frac{4}{3}\epsilon \big)}}{\beta F_\beta},
+	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\left( \frac{1}{1 - \frac{4}{3}\epsilon} \right)}}{\beta (E_0 - F_\beta)},
 \end{equation}
 which holds for all finite $n$ with $\tt \leq n$ and $\epsilon' \leq \epsilon \leq \epsilon_{\rm{th}}$.
+\nick{In fact, it holds for $0 \leq \epsilon \leq \epsilon_*$, where $\epsilon_\star$ is the noise level (lower than $\epsilon_{\rm{th}}$) at which the state conversion turns from $\rm{(C1)} \rightarrow \rm{(C1)}$ to $\rm{(C1)} \rightarrow \rm{(C2)}$.
+Need to adjust~\cref{fig:distill_bounds_temp} accordingly}
+At the limit of high temperature, $\beta \rightarrow 0$, we get $\beta F_\beta \rightarrow -\ln{3}$, and we retrieve the unital fragment bound,
+\begin{equation}
+	R(\beta) \xrightarrow{\beta \rightarrow 0} \frac{\ln{(3-4\epsilon)}}{\ln{3}}.
+\end{equation}
 We compare $R(\beta)$ for different values of $\beta$ with the mana bound $R_{\rm{mana}}$ in~\cref{fig:distill_bounds_temp}.
@@
     The mana distillation rate $R_{\rm{mana}}$ is given for comparison.
+    The Hamiltonian spectrum is simple harmonic, $(E_0, E_1, E_2) = (0,1,2)$.
     As $\beta$ increases, the range of noise levels for which $R(\beta)$ is valid decreases and the distillation bound becomes stricter.
@@
 
-Our approach also allows for analysis at the limit of low temperature, $\beta \rightarrow \infty$.
-In fact, for any
-\begin{equation}
-	\beta \geq \beta_{\rm{th}} \coloneqq \frac{1}{E_{\rm{max}} - E_0} \ln2,
-\end{equation}
-we always have $\epsilon_{\rm{th}} \leq 0$, so $\epsilon \geq \epsilon_{\rm{th}}$.
-Note that if $E_{\rm{max}} = E_0$, the bound is infinite, simply meaning that $\epsilon = \epsilon_{\rm{th}}$ at the limit $\beta = \infty$.
-In the low temperature scenario, we get $\widetilde{W}_{\rm{max}} = \wn^p e^{n\beta E_{\rm{max}}}$ occuring in a region labelled by 
-\begin{equation}
-	(i,j,k) = 
-	\begin{cases}
-	(n,0,0), &E_{\rm{max}} = E_0, \\
-	(0,n,0), &E_{\rm{max}} = E_1, \\
-	(0,0,n), &E_{\rm{max}} = E_2.
-	\end{cases}
-\end{equation}
-The bound expression does not depend on which energy is the highest so, without loss of generality, assume that $E_{\rm{max}} = E_0$.
-Then, the multiplicity is $m_{n00} = 2^n$ and the first elbow coordinates can be read off the $X^nY^0Z^0$ term in generating functions $G_n(\noisys), G_n(\gamma)$,
-\begin{equation}
-	(x_0, L_0) = \left( \left(\frac{2}{3}\frac{e^{-\beta E_0}}{\Z_\beta}\right)^n, (2u)^n \right)
-\end{equation}
-and the distillation constraint is defined at the location $x_\star = x_0$ of the initial state's first elbow as in~\cref{eq:first_elbow_constraint}.
-
-The first elbow of the target state is located at $x'_0 = (2e^{-\beta E_0} / (2\Z_\beta))^{\tt} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the target state's first elbow,
+Our approach also allows for analysis at the limit of low temperature, $\beta \rightarrow \infty$, which is a limit case of $\rm{(C2)}$ with $\beta \geq \beta_{\rm{th}}$.
+
+We consider 
+\begin{equation}
+	x_\star = x_0 = (e^{-\beta E_{\rm{max}}} / \Z_\beta)^{n}.
+\end{equation}
+The first elbow of the target state is located at $x'_0 = (e^{-\beta E_{\rm{max}}} / \Z_\beta)^{\tt} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the target state's first elbow,
 \begin{equation}\label{eq:constraint_deriv_lowtemp}
-	L'_\star = \frac{x_\star}{x'_0}L'_0 = 2^n \left(\frac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n-\tt} \left( \frac{1}{6} - \frac{1}{18}\epsilon' \right)^{\tt}.
-\end{equation}
-Therefore, in the low temperature scenario $\beta \geq \beta_{\rm{th}}$, the distillation process in~\cref{eq:msd_thermal} is possible only if $L_\star \geq L'_\star$ or equivalently,
+	L'_\star = \frac{x_\star}{x'_0}L'_0 = \left(\frac{e^{-\beta E_2}}{\Z_\beta}\right)^{n-\tt} \left( \frac{1}{2} - \frac{1}{6}\epsilon' \right)^{\tt}.
+\end{equation}
+Therefore, in the low temperature scenario $\beta \geq \beta_{\rm{th}}$, the constraint in~\cref{eq:first_elbow_constraint} holds only if
 \begin{align}
@@
 \begin{equation}
-	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\big(\frac{3}{3-\epsilon} \big)}}{-\ln{2} + \beta (E_{\rm{max}} - F_\beta)},
+	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\left(\frac{1}{1-\frac{1}{3}\epsilon} \right)}}{-\ln{2} + \beta (E_{\rm{max}} - F_\beta)},
 \end{equation}
 which holds for all finite $n$ with $\tt \leq n$ and $\epsilon' \leq \epsilon$.
+At the zero temperature limit, $F_\beta$ tends to zero, so $R(\beta) \xrightarrow{\beta \rightarrow \infty} 1$.
 We compare $R(\beta)$ for different values of $\beta$ with the mana bound $R_{\rm{mana}}$ in~\cref{fig:distill_bounds_lowtemp}.
@@
     The mana distillation rate $R_{\rm{mana}}$ is given for comparison.
-    \nick{Terrible bound for low temperatures. I'll check for possible calculation errors.}
+    The Hamiltonian spectrum is simple harmonic, $(E_0, E_1, E_2) = (0,1,2)$.
+    \nick{Not-so-good bound for low temperatures, other elbows perform a lot better numerically.}
     }

### 2021-02-12 magic_paper.tex
Added lemma that proves explicit expressions for n-copy wigner, it uses multinomial theorem, but no need for explicit reference outside the proof

@@
 
+\subsubsection{Component-multiplicity pairs}
+
+\nick{Probably will move this subsection to the earlier section where we discuss phase spaces in general}
+
+In general, a $1$-copy $d$-dimensional state is defined exactly by its $d^2$ Wigner distribution $W$. 
+The distribution $W$ can always be described by a set of $D \leq d^2$ component-multiplicity pairs denoted by $\{(w_i, m_i)\}_{i=1,\dots,D}$.
+\begin{definition}
+	Consider a $d^2$-dimensional distribution $W$ and a positive integer $D$. 
+	We call the set of order pairs $\{(w_i, m_i)\}_{i=1,\dots,D}$ a \emph{complete set of component-multiplicity pairs}, if $W$ contains $m_i$ components $w_i$ and $\sum_{i=0}^D m_i = d^2$.
+\end{definition}
+Therefore, such a set that describes a distribution $W$ contains in its description each component of $W$ exactly once.
+As an example, two complete sets of pairs for the Strange state are $\{( -1/3, 1), ( 1/6, 8)\}$ and $\{(-1/3, 1), (1/6, 2), (1/6, 3), (1/6, 3)\}$.
+
+Consider two states $\rho_A, \rho_B$ with Wigner distributions $\W{\rho_A}, \W{\rho_B}$ described respectively by complete sets of component-multiplicity pairs 
+\begin{equation}
+	\{(w_i, m_i)\}_{i=1,\dots,D_A} \text{ and } \{(w_j', m_j')\}_{j=0,\dots,D_B}.
+\end{equation}
+The multiplicative property of the Wigner distribution over a composite phase space $\pd[d_A] \times \pd[d_B]$,
+\begin{equation}
+	\W[\bmx_A \oplus \bmx_B]{\rho_A \otimes \rho_B} = \W[\bmx_A]{\rho_A}\W[\bmx_B]{\rho_B},
+\end{equation}
+implies that the distribution $\W{\rho_A \otimes \rho_B}$ is $d_A^2 d_B^2$-dimensional and contains components of the form $w_i w_j'$. 
+Therefore, the set $\{(w_i w_j', m_i m_j')\}$ with $i=1,\dots,D_A$ and $j=1,\dots,D_B$ is a complete set of component-multiplicity pairs for the distribution of the composite system $\W{\rho_A \otimes \rho_B}$.
+This is true because all components are of the form $w_i w_j'$ and 
+\begin{equation*}
+	\sum_{i=1}^{D_A}\sum_{j=1}^{D_B} m_i m_j' = \sum_{i=1}^{D_A} m_i \sum_{j=1}^{D_B} m_j' = d_A^2 d_B^2.
+\end{equation*}
+
+Given a state $\rho$ and a complete set of component-multiplicity pairs describing its Wigner distribution $\W{\rho}$, we now provide a method of computing the components (and multiplicities) of the $n$-copy distribution $\W{\rho}\too{n}$.
+\begin{lemma}\label{lem:ncopycomponents}
+	Let $W$ be a $d$-dimensional distribution defined by a complete set of component-multiplicity pairs $\{(w_i, m_i)\}_{i=1,\dots,D}$ with $D \leq d$ and consider the distribution $W\too{n}$ obtained by taking the Kronecker product $W \otimes \dots \otimes W$ between $n$ copies of $W$.
+
+	Denote by $C_D^n \coloneqq \{\bmk\}$ the set of all vectors $\bmk \coloneqq (k_1, \dots, k_D)$ with non-negative integer components that sum to $n$, i.e.
+	\begin{equation*}
+	0 \leq k_1, \dots, k_D \leq n \text{ and } k_1 + \dots + k_D = n.
+	\end{equation*}
+
+	Then, $W\too{n}$ admits a complete set of component-multiplicity pairs $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$, where
+\begin{align}
+	M_{\bmk} &= \frac{n!}{k_1!\dots k_D!} \prod\limits_{i=1}^D {m_i}^{k_i}, \label{eq:M}\\
+	W_{\bmk} &= \prod\limits_{i=1}^D {w_i}^{k_i}. \label{eq:W}
+\end{align}
+\end{lemma}
+\begin{proof}
+	We proceed by induction.
+
+	Assume $n = 1$.
+	Let $\bmk_i \coloneqq (0,\dots,0,1,0,\dots,0)$ be a vector with its $i$-th component equal to 1 and 0's elsewhere.
+	The set $C_D^1$ consists of all vectors of this form, i.e. 
+\begin{equation*}
+	C_D^1 = \{ \bmk_i \}_{i=1,\dots,D}
+\end{equation*}
+	It is also true by direct calculation that
+\begin{equation*}
+	\left( W_{\bmk_i}, M_{\bmk_i} \right) = (w_i, m_i).
+\end{equation*}
+Therefore, $\{ (W_{\bmk}, M_{\bmk}) \}_{\bmk \in C_D^1}$ is a complete set of component-multiplicity pairs for $W$.
+
+	Assume that $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$ as given in~\cref{eq:M,eq:W} is a complete set of component-multiplicity pairs for the $n$-copy distribution $W\too{n}$.
+	By construction, the distribution $W\too{(n+1)} = W\too{n} \otimes W$ is multiplicative, so it admits the complete set of component multiplicity pairs
+\begin{equation}
+	\{(W_{\bmk} w_i, M_{\bmk} m_i)\},\ \bmk \in C_D^n \text{ and } i=1,\dots,D.
+\end{equation}
+
+	Consider the component sum of the distribution $W\too{(n+1)}$,
+\begin{align*}
+	&\sum_{\bmk \in C_D^n}\sum_{i=1}^D M_{\bmk} m_i W_{\bmk} w_i = \sum_{\bmk \in C_D^n} M_{\bmk}W_{\bmk} \sum_{i=1}^D m_i w_i =\\
+	&\sum_{\bmk \in C_D^n} \frac{n!}{k_1!\dots k_D!} \prod\limits_{i=1}^D {m_i}^{k_i}{w_i}^{k_i} \sum_{i=1}^D m_i w_i =\\
+	&\left( \sum_{i=1}^D m_i w_i \right)^n \left( \sum_{i=1}^D m_i w_i \right) = \left( \sum_{i=1}^D m_i w_i \right)^{n+1} =\\
+	&\sum_{\bmq \in C_D^{n+1}} M_{\bmq}W_{\bmq},
+\end{align*}
+where in the last expression, vectors $\bmq = (q_1, \dots, q_D)$ have non-negative integer components that sum to $(n+1)$ and 
+\begin{align*}
+	M_{\bmq} &= \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i},\\
+	W_{\bmq} &= \prod\limits_{i=1}^D {w_i}^{q_i}.
+\end{align*}
+We have used the multinomial theorem to proceed between lines 2-3 and lines 3-4 of the derivation.
+
+We have achieved a regrouping of the distribution components.
+Every component $W_{\bmq}$ is of the form $W_{\bmk} w_i$ with $q_i = k_i + 1$ and $q_j = k_j$ for $j\neq i$ and 
+\begin{align*}
+	\sum_{\bmq \in C_D^{n+1}}  \hspace{-6pt} M_{\bmq} =  \hspace{-10pt} \sum_{\bmq \in C_D^{n+1}} \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i} = 
+	\left( \sum_{i=1}^D m_i \right)^{n+1} \hspace{-10pt} = d^{n+1},
+\end{align*}
+which is the dimension of $W\too{(n+1)}$.
+
+Therefore, $\{ (W_{\bmq}, M_{\bmq}) \}_{\bmq \in C_D^{n+1}}$ is a complete set of component-multiplicity pairs for $W\too{n}$, completing the proof.
+\end{proof}
+
+\subsubsection{Distillation bounds}
+
 We are now in a position to consider the Strange state distillation process
@@
 \begin{equation}
-	\widetilde{\rm{W}}_{\noisys|\gamma}(\bmx) = \widetilde{\rm{W}}_1(\bmx) \coloneqq \frac{\W[\bmx]{\noisys}}{\W[\bmx]{\gamma}},
-\end{equation}
+	\widetilde{\rm{W}}_{\noisys|\gamma}(\bmx) \coloneqq \frac{\W[\bmx]{\noisys}}{\W[\bmx]{\gamma}},
+\end{equation}
+Notice that the Gibbs-rescaled distribution is multiplicative in general,
+\begin{align}
+	&\widetilde{\rm{W}}_{\rho_A \otimes \rho_B | \gamma_A \otimes \gamma_B}(\bmx_A \oplus \bmx_B) = \frac{\W[\bmx_A \oplus \bmx_B]{\rho_A \otimes \rho_B}}{\W[\bmx_A \oplus \bmx_B]{\gamma_A \otimes \gamma_B}} = \nonumber \\
+	&\frac{\W[\bmx_A]{\rho_A}\W[\bmx_B]{\rho_B}}{\W[\bmx_A]{\gamma_A}\W[\bmx_B]{\gamma_B}} = \widetilde{\rm{W}}_{\rho_A | \gamma_A}(\bmx_A)\widetilde{\rm{W}}_{\rho_B  | \gamma_B}(\bmx_B).
+\end{align}
+
+We construct complete sets of component-multiplicity pairs and based on the distinct components of the Gibbs-rescaled distribution,
+\begin{align}
+	S(\noisys) &\coloneqq \{ (-\wn, 1), (\wp, 2), (\wp, 3), (\wp, 3) \} \\
+	S(\gamma) &\coloneqq \Big\{ \left( \frac{e^{-\beta E_0}}{3\Z}, 1 \right), \left( \frac{e^{-\beta E_0}}{3\Z}, 2 \right), \nonumber\\
+	&\hspace{23pt} \left( \frac{e^{-\beta E_1}}{3\Z}, 3 \right), \left( \frac{e^{-\beta E_2}}{3\Z}, 3 \right) \Big\} \\
+	S(\noisys | \gamma) &\coloneqq \{ (-\wn 3\Z e^{\beta E_0}, 1), (\wp 3\Z e^{\beta E_0}, 2), \nonumber\\
+	&\hspace{21pt} (\wp 3\Z e^{\beta E_1}, 3), (\wp 3\Z e^{\beta E_2}, 3) \}
+\end{align}
+
+There are four distinct component-multiplicity pairs for the Gibbs-rescaled distribution, so in order to use~\cref{lem:ncopycomponents} to find the components of the $n$-copy distributions, we first define an index vector
+\begin{equation}
+	\bmq \coloneqq (n-\alpha,i,j,k),
+\end{equation}
+where $i,j,k$ are non-negative integers that satisfy 
+\begin{equation*}
+	i+j+k \eqqcolon \alpha \leq n.
+\end{equation*}
+The $n$-copy
+
+\begin{align}\label{eq:gn}
+	&G_n(\noisys) \coloneqq G_1(\noisys)^n = \\
+	&\sum\limits_{\substack{i,j,k = 0,\dots,n \\ \alpha \leq n}}\hspace{-10pt} m_{ijk} \big[(-\wn)^{n-\alpha} \wp^{\alpha} \big] X^i Y^j Z^k, \nonumber
+	\\[10pt]
+	&G_n(\gamma) \coloneqq G_1(\gamma)^n = \\
+	&(3\Z)^{-n}\hspace{-10pt} \sum\limits_{\substack{i,j,k = 0,\dots,n \\ \alpha \leq n}}\hspace{-10pt} m_{ijk} \Big[ e^{-\beta ( i E_0 + j E_1 + k E_2 )} e^{-\beta (n-\alpha)E_0} \Big] X^i Y^j Z^k, \nonumber
+	\\[10pt]
+	&G_n(\noisys|\gamma) \coloneqq G_1(\noisys|\gamma)^n = \\
+	&(3\Z)^{n}\hspace{-10pt} \sum\limits_{\substack{i,j,k = 0,\dots,n \\ \alpha \leq n}}\hspace{-10pt} m_{ijk} \Big[ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} \times \nonumber\\[-15pt]
+	&\hspace{80pt} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big] X^i Y^j Z^k, \nonumber
+\end{align}
+where the $(i,j,k)$-th term multiplicity $m_{ijk}$ (i.e. the number of phase space points contained in region $X^i Y^j Z^k$) is given by
+\begin{equation}
+	m_{ijk} \coloneqq \frac{n!}{i!j!k!(n-\alpha)!} 2^i 3^j 3^k.
+\end{equation}
+
+In order to construct the Lorenz curve of a Strange state in a thermal fragment we need to sort the components of $\widetilde{W}_n$ in decreasing order.
+In particular, to find the coordinates of the first elbow $(x_0, L_0)$, we need to evaluate the greatest component,
+\begin{equation}\label{eq:max_slope}
+	\widetilde{W}_{\rm{max}} \coloneqq \max\limits_{i,j,k}{\Big\{ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}},
+\end{equation}
+where $0 \leq i,j,k \leq n$ and $i+j+k \eqqcolon \alpha \leq n$.
+Notice that for $0 \leq \epsilon \leq 3/7$, we have $\wn \geq \wp$.
+Assume that $n$ is even. 
+We then need the sum $\alpha = i+j+k$ to be even, so that the expression remains positive.
+
+Given an even value $\alpha$ for the sum, the term $\wn^{n-\alpha} \wp^{\alpha} e^{-\beta (n-\alpha)E_0}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
+Hence, we have
+\begin{align}
+	\widetilde{W}_{\rm{max}} &= \max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta \alpha E_{\rm{max}}} \Big\}} \\
+	&= \max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \wn^n e^{n\beta E_0} \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}
+\end{align}
+The last expression is maximised for $\alpha = 0$ ($\alpha = n$) when the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than $1$ (greater than $1$).
+The threshold value of $1$ is achieved when the noise level $\epsilon$ is equal to
+\begin{equation}
+	\epsilon_{\rm{th}} \coloneqq 3 - \dfrac{18}{8-e^{(E_{\rm{max}} - E_0)\beta}}.
+	%\beta \leq \frac{1}{E_{\rm{max}} - E_0}\ln{\left( 8-\frac{18}{3-\epsilon} \right)}
+\end{equation}
+The noise level threshold $\epsilon_{\rm{th}}$ is a decreasing function of $\beta$.
+It achieves its maximum value $3/7$ for $(E_{\rm{max}} - E_0)\beta = 0$, and a value equal to $0$ for
+\begin{equation}
+	\beta_{\rm{th}} \coloneqq \frac{1}{E_{\rm{max}} - E_0} \ln2.
+\end{equation}
+For $\beta > \beta_{\rm{th}}$, $\epsilon_{\rm{th}}$ is negative, meaning that the noise level $\epsilon$ will always be higher than the threshold.
+We highlight that the threshold becomes $0$ when the difference between the maximum energy level and the level associated with the state negativity is equal to the energy extracted from a single particle Szilard's engine,
+\begin{equation}
+	E_{\rm{max}} - E_0 = \beta_{\rm{th}}^{-1} \ln2.
+\end{equation}
+
+The maximum slope finally is
+\begin{equation}
+\widetilde{W}_{\rm{max}} =
+	\begin{cases}
+		\wn^n e^{n\beta E_0}, &\epsilon \leq \epsilon_{\rm{th}},\ \hspace{30pt}\rm{(C1)}	\\
+		\wp^n e^{n\beta E_{\rm{max}}}, &\epsilon > \epsilon_{\rm{th}}.\ \hspace{32pt}\rm{(C2)} 
+	\end{cases}
+\end{equation}
+Case 1 $\rm{(C1)}$ corresponds to the region labelled by $(i,j,k) = (0,0,0)$.
+Case 2 $\rm{(C2)}$ corresponds to the region labelled by 
+\begin{equation}
+	(i,j,k) = 
+	\begin{cases}
+	(0,n,0), &\text{if } E_{\rm{max}} = E_1, \\
+	(0,0,n), &\text{if } E_{\rm{max}} = E_2.
+	\end{cases}
+\end{equation}
+Note that if $E_{\rm{max}} = E_0$, we get $\epsilon_{\rm{th}} = 3/7$ and $\rm{(C1)}$ holds for all $\epsilon$ and $\beta$.
+Assuming $E_{\rm{max}} > E_0$, we get the cases:
+\begin{itemize}
+	\item $\beta = 0$. Then, $\epsilon_{\rm{th}} = 3/7$ and $\rm{(C1)}$ holds for all noise levels $\epsilon$.
+	This is the unital fragment.
+	\item $0 < \beta < \beta_{\rm{th}}$. Then, $0 < \epsilon_{\rm{th}} < 3/7$ and $\rm{(C1)}$ holds for $\epsilon \leq \epsilon_{\rm{th}}$, while $\rm{(C2)}$ holds for $\epsilon \geq \epsilon_{\rm{th}}$.
+	\item $\beta \geq \beta_{\rm{th}}$. Then, $ \epsilon_{\rm{th}} \leq 0$ and $\rm{(C2)}$ holds for all $\epsilon$.
+\end{itemize}
+
+Whenever the set of physical parameters falls under $\rm{(C1)}$, the multiplicity is $m_{000} = 1$ and the first elbow coordinates can be read off the $X^0Y^0Z^0$ term in generating functions $G_n(\noisys), G_n(\gamma)$.
+If it falls under $\rm{(C2)}$, then $E_{\rm{max}} = E_1$ ($E_{\rm{max}} = E_2$), the multiplicity is $m_{0n0} = 3^n$ ($m_{00n} = 3^n$) and the first elbow coordinates can be read off the $X^0Y^nZ^0$ ($X^0Y^0Z^n$) term in generating functions $G_n(\noisys), G_n(\gamma)$,
+\begin{equation}
+	(x_0, L_0) =
+	\begin{cases}
+		\left( \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^n, \wn^n \right), &\rm{(C1)}	\vspace{10pt}\\
+		\left( \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^n, (3u)^n \right). &\rm{(C2)} 
+	\end{cases}
+\end{equation}
+
+Considering the distillation process in~\cref{eq:msd_thermal}, the Lorenz curves of the initial and target states may each be described by either $\rm{(C1)}$ or $\rm{(C2)}$.
+In any case, a necessary distillation constraint can be defined at the location $x_\star = x_0$ of the initial state's first elbow and be expressed as
+\begin{equation}\label{eq:first_elbow_constraint}
+	\lc{\noisys(\epsilon)\too{n}}{\gamma_\beta}(x_\star) \geq \lc{\noisys(\epsilon')\too{\tt}}{\gamma_\beta}(x_\star).
+\end{equation}
+
+Let's focus on the case where both Lorenz curves are described by $\rm{(C1)}$.
+This case includes the unital fragment.
+
+The first elbow of the target state is located at $x'_0 = (3Z)^{-\tt} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the target state's first elbow,
+\begin{equation}\label{eq:constraint_deriv_temp}
+	L'_\star = \frac{x_\star}{x'_0}L'_0 = \left(\frac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n-\tt} \left( \frac{1}{3} - \frac{4}{9} \epsilon' \right)^{\tt}.
+\end{equation}
+The constraint in~\cref{eq:first_elbow_constraint} therefore holds only if
+\begin{align}
+	\frac{n}{n'} &\geq \frac{\ln{\Big[ \big( 1-\frac{4}{3}\epsilon' \big)\Z_\beta  e^{\beta E_0} \Big]}}{\ln{\Big[ \big( 1-\frac{4}{3}\epsilon \big)\Z_\beta e^{\beta E_0} \Big]}} \\
+	&= \frac{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} - \beta (F_\beta - E_0)}{\ln{\big( 1-\frac{4}{3}\epsilon \big)} - \beta (F_\beta - E_0)},
+\end{align}
+with $\tt \leq n$ and $\epsilon' \leq \epsilon \leq \epsilon_{\rm{th}}$. 
+The free energy of thermal state $\gamma_\beta$ is denoted by
+\begin{equation}
+	F_\beta \coloneqq \tr[\gamma_\beta H] + \beta^{-1} \tr[\gamma_\beta \ln{\gamma_\beta}] = -\beta^{-1} \ln{\Z_\beta}.
+\end{equation}
+
+Moreover, we can obtain an upper bound on thermal fragment distillation rate $R=n'/n$ for pure target Strange states ($\epsilon' = 0$) given by
+\begin{equation}
+	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\left( \frac{1}{1 - \frac{4}{3}\epsilon} \right)}}{\beta (E_0 - F_\beta)},
+\end{equation}
+which holds for all finite $n$ with $\tt \leq n$ and $\epsilon' \leq \epsilon \leq \epsilon_{\rm{th}}$.
+\nick{In fact, it holds for $0 \leq \epsilon \leq \epsilon_*$, where $\epsilon_\star$ is the noise level (lower than $\epsilon_{\rm{th}}$) at which the state conversion turns from $\rm{(C1)} \rightarrow \rm{(C1)}$ to $\rm{(C2)} \rightarrow \rm{(C1)}$.
+Need to adjust~\cref{fig:distill_bounds_temp} accordingly}
+At the limit of high temperature, $\beta \rightarrow 0$, we get $\beta F_\beta \rightarrow -\ln{3}$, and we retrieve the unital fragment bound,
+\begin{equation}
+	R(\beta) \xrightarrow{\beta \rightarrow 0} \frac{\ln{(3-4\epsilon)}}{\ln{3}}.
+\end{equation}
+We compare $R(\beta)$ for different values of $\beta$ with the mana bound $R_{\rm{mana}}$ in~\cref{fig:distill_bounds_temp}.
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.5]{figs/distill_bounds_temp.pdf}
+    \caption{\textbf{Distillation rate with low noise in thermal fragments.} Distillation rates obtained by majorization $R(\beta)$ for low noise levels $\epsilon \leq \epsilon_{\rm{th}}$ are plotted for different temperatures $\beta^{-1}$ such that $0 \leq \beta \leq \beta_{\rm{th}}$.
+    The mana distillation rate $R_{\rm{mana}}$ is given for comparison.
+    The Hamiltonian spectrum is simple harmonic, $(E_0, E_1, E_2) = (0,1,2)$.
+    As $\beta$ increases, the range of noise levels for which $R(\beta)$ is valid decreases and the distillation bound becomes stricter.
+    }
+    \label{fig:distill_bounds_temp}
+\end{figure}
+
+Our approach also allows for analysis at the limit of low temperature, $\beta \rightarrow \infty$, which is a limit case of $\rm{(C2)}$ with $\beta \geq \beta_{\rm{th}}$.
+
+We consider 
+\begin{equation}
+	x_\star = x_0 = (e^{-\beta E_{\rm{max}}} / \Z_\beta)^{n}.
+\end{equation}
+The first elbow of the target state is located at $x'_0 = (e^{-\beta E_{\rm{max}}} / \Z_\beta)^{\tt} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the target state's first elbow,
+\begin{equation}\label{eq:constraint_deriv_lowtemp}
+	L'_\star = \frac{x_\star}{x'_0}L'_0 = \left(\frac{e^{-\beta E_2}}{\Z_\beta}\right)^{n-\tt} \left( \frac{1}{2} - \frac{1}{6}\epsilon' \right)^{\tt}.
+\end{equation}
+Therefore, in the low temperature scenario $\beta \geq \beta_{\rm{th}}$, the constraint in~\cref{eq:first_elbow_constraint} holds only if
+\begin{align}
+	\frac{n}{n'} &\geq \frac{\ln{\Big[ \big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)\Z_\beta e^{\beta E_{\rm{max}}} \Big]}}{\ln{\Big[ \big( \frac{1}{2}-\frac{1}{6}\epsilon \big)\Z_\beta e^{\beta E_{\rm{max}}} \Big]}} \nonumber\\
+	&= \frac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F_\beta)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F_\beta)},
+\end{align}
+with $\tt \leq n$ and $\epsilon' \leq \epsilon$.
+
+We can obtain an upper bound on thermal fragment distillation rate $R=n'/n$ for pure target Strange states ($\epsilon' = 0$) in this regime as well. 
+It is given by
+\begin{equation}
+	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\left(\frac{1}{1-\frac{1}{3}\epsilon} \right)}}{-\ln{2} + \beta (E_{\rm{max}} - F_\beta)},
+\end{equation}
+which holds for all finite $n$ with $\tt \leq n$ and $\epsilon' \leq \epsilon$.
+At the zero temperature limit, $F_\beta$ tends to zero, so $R(\beta) \xrightarrow{\beta \rightarrow \infty} 1$.
+We compare $R(\beta)$ for different values of $\beta$ with the mana bound $R_{\rm{mana}}$ in~\cref{fig:distill_bounds_lowtemp}.
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.5]{figs/distill_bounds_lowtemp.pdf}
+    \caption{\textbf{Distillation rate for low temperatures in thermal fragments.} Distillation rates obtained by majorization $R(\beta)$ in the temperature regime $\beta \geq \beta_{\rm{th}}$ are plotted for different temperatures $\beta^{-1}$.
+    The mana distillation rate $R_{\rm{mana}}$ is given for comparison.
+    The Hamiltonian spectrum is simple harmonic, $(E_0, E_1, E_2) = (0,1,2)$.
+    \nick{Not-so-good bound for low temperatures, other elbows perform a lot better numerically.}
+    }
+    \label{fig:distill_bounds_lowtemp}
+\end{figure}
+
+\null\newpage
+\null\newpage
+
+\subsection{OLD Magic in thermal fragments}
+
 which naturally splits the phase space $\pd[3]$ into four regions where the ``slope'', i.e. the value of the Gibbs-rescaled distribution, is different.
@@
 
-An $n$-copy system is described over a phase space given by the $n$-times Cartesian product $\pd[3]^{\times n}$ which generates new regions of different slope.
-In particular, it comprises exactly the regions $X^i Y^j Z^k$, where $i,j,k = 0,\dots,n$ and 
-\begin{equation}
-	\alpha \coloneqq i+j+k \leq n.
-\end{equation}
-For example, region $YZ$ consists of all points expressed as the direct sum $\bmy \oplus \bmz$ or $\bmz \oplus \bmy$, where $\bmy \in Y$ and $\bmz \in Z$.
-Note that there is no difference between e.g. regions $YZ$ and $ZY$, since multiplication of slopes is commutative. 
-\nick{abuse of notation: I use X,Y,Z as sets and as variables that represent those sets}
-
-The $n$-copy Wigner distributions $\W{\noisys\too{n}}, \W{\gamma\too{n}}$, and consequently the $n$-copy Gibbs-rescaled distribution $\widetilde{\rm{W}}_n = \widetilde{\rm{W}}_{\noisys\too{n}|\gamma\too{n}}$ can be written as self-convolutions,
-\begin{align}
-	\W{\noisys\too{n}}(\bmx_1 \oplus \dots \oplus \bmx_n) &= \W{\noisys}(\bmx_1)\dots\W{\noisys}(\bmx_n) \nonumber\\
-	&= \W{\noisys}(\bmx)\too{n} \\[10pt]
-	\W{\gamma\too{n}}(\bmx_1 \oplus \dots \oplus \bmx_n) &= \W{\gamma}(\bmx_1)\dots\W{\gamma}(\bmx_n) \nonumber\\
-	&= \W{\gamma}(\bmx)\too{n} \\[10pt]
-	\widetilde{\rm{W}}_n(\bmx_1 \oplus \dots \oplus \bmx_n) &= \frac{\W{\noisys\too{n}}(\bmx_1 \oplus \dots \oplus \bmx_n)}{\W{\gamma\too{n}}(\bmx_1 \oplus \dots \oplus \bmx_n)} \\
-	= \frac{\W{\noisys}(\bmx_1)\dots\W{\noisys}(\bmx_n)}{\W{\gamma}(\bmx_1)\dots\W{\gamma}(\bmx_n)} &= \left( \frac{\W{\noisys}(\bmx)}{\W{\gamma}(\bmx)} \right)\too{n} \nonumber\\
-	&= \left( \widetilde{\rm{W}}_1(\bmx)\right) \too{n}. \nonumber
-\end{align}
-Therefore, the values and multiplicites of the $n$-copy distributions are generated directly as a multinomial expansion of the $1$-copy expressions in~\cref{eq:g1}.
-\begin{align}\label{eq:gn}
-	&G_n(\noisys) \coloneqq G_1(\noisys)^n = \\
-	&\sum\limits_{\substack{i,j,k = 0,\dots,n \\ \alpha \leq n}}\hspace{-10pt} m_{ijk} \big[(-\wn)^{n-\alpha} \wp^{\alpha} \big] X^i Y^j Z^k, \nonumber
-	\\[10pt]
-	&G_n(\gamma) \coloneqq G_1(\gamma)^n = \\
-	&(3\Z)^{-n}\hspace{-10pt} \sum\limits_{\substack{i,j,k = 0,\dots,n \\ \alpha \leq n}}\hspace{-10pt} m_{ijk} \Big[ e^{-\beta ( i E_0 + j E_1 + k E_2 )} e^{-\beta (n-\alpha)E_0} \Big] X^i Y^j Z^k, \nonumber
-	\\[10pt]
-	&G_n(\noisys|\gamma) \coloneqq G_1(\noisys|\gamma)^n = \\
-	&(3\Z)^{n}\hspace{-10pt} \sum\limits_{\substack{i,j,k = 0,\dots,n \\ \alpha \leq n}}\hspace{-10pt} m_{ijk} \Big[ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} \times \nonumber\\[-15pt]
-	&\hspace{80pt} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big] X^i Y^j Z^k, \nonumber
-\end{align}
-where the $(i,j,k)$-th term multiplicity $m_{ijk}$ (i.e. the number of phase space points contained in region $X^i Y^j Z^k$) is given by
-\begin{equation}
-	m_{ijk} \coloneqq \frac{n!}{i!j!k!(n-\alpha)!} 2^i 3^j 3^k.
-\end{equation}
-
-In order to construct the Lorenz curve of a Strange state in a thermal fragment we need to sort the components of $\widetilde{W}_n$ in decreasing order.
-In particular, to find the coordinates of the first elbow $(x_0, L_0)$, we need to evaluate the greatest component,
-\begin{equation}\label{eq:max_slope}
-	\widetilde{W}_{\rm{max}} \coloneqq \max\limits_{i,j,k}{\Big\{ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}}
-\end{equation}
-Notice that for $0 \leq \epsilon \leq \frac{3}{7}$, we have $\wn \geq \wp$.
-Assume that $n$ is even (the analysis is similar for odd $n$). 
-We then need the sum $\alpha = i+j+k$ to be even, so that the expression remains positive.
-
-Given an even value $\alpha$ for the sum, the term $\wn^{n-\alpha} \wp^{\alpha} e^{-\beta (n-\alpha)E_0}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
-Hence, we have
-\begin{align}
-	\widetilde{W}_{\rm{max}} &= \max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta \alpha E_{\rm{max}}} \Big\}} \\
-	&= \max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \wn^n e^{n\beta E_0} \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}
-\end{align}
-The last expression is maximised for $\alpha = 0$ ($\alpha = n$) when the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than or equal to $1$ (greater than $1$).
-We want to rewrite the expression as a noise level $\epsilon$ constraint with respect to temperature $\beta^{-1}$, where the noise threshold is
-\begin{equation}
-	\epsilon_{\rm{th}} \coloneqq 3 - \dfrac{18}{8-e^{(E_{\rm{max}} - E_0)\beta}}.
-	%\beta \leq \frac{1}{E_{\rm{max}} - E_0}\ln{\left( 8-\frac{18}{3-\epsilon} \right)}
-\end{equation}
-The noise threshold $\epsilon_{\rm{th}}$ is a decreasing function of $\beta$.
-It achieves its maximum value $3/7$ for $(E_{\rm{max}} - E_0)\beta = 0$, and its minimum value $0$ for
-\begin{equation}
-	\beta_{\rm{th}} \coloneqq \frac{1}{E_{\rm{max}} - E_0} \ln2.
-\end{equation}
-We have
-\begin{equation}
-\widetilde{W}_{\rm{max}} =
-	\begin{cases}
-		\wn^n e^{n\beta E_0}, &\epsilon \leq \epsilon_{\rm{th}},\ \hspace{30pt}\rm{(C1)}	\\
-		\wp^n e^{n\beta E_{\rm{max}}}, &\epsilon > \epsilon_{\rm{th}}.\ \hspace{32pt}\rm{(C2)} 
-	\end{cases}
-\end{equation}
-Case 1 $\rm{(C1)}$ corresponds to the region labelled by $(i,j,k) = (0,0,0)$.
-Case 2 $\rm{(C2)}$ corresponds to the region labelled by 
-\begin{equation}
-	(i,j,k) = 
-	\begin{cases}
-	(0,n,0), &\text{if } E_{\rm{max}} = E_1, \\
-	(0,0,n), &\text{if } E_{\rm{max}} = E_2.
-	\end{cases}
-\end{equation}
-Note that if $E_{\rm{max}} = E_0$, we get $\epsilon_{\rm{th}} = 3/7$ and $\rm{(C1)}$ holds for all $\epsilon$ and $\beta$.
-Assuming $E_{\rm{max}} > E_0$, we get the cases:
-\begin{itemize}
-	\item $\beta = 0$. Then, $\epsilon_{\rm{th}} = 3/7$ and $\rm{(C1)}$ holds for all noise levels $\epsilon$.
-	This is the unital fragment.
-	\item $0 < \beta < \beta_{\rm{th}}$. Then, $0 < \epsilon_{\rm{th}} < 3/7$ and $\rm{(C1)}$ holds for $\epsilon \leq \epsilon_{\rm{th}}$, while $\rm{(C2)}$ holds for $\epsilon \geq \epsilon_{\rm{th}}$.
-	\item $\beta \geq \beta_{\rm{th}}$. Then, $ \epsilon_{\rm{th}} \leq 0$ and $\rm{(C2)}$ holds for all $\epsilon$.
-\end{itemize}
-
-Whenever the set of physical parameters falls under $\rm{(C1)}$, the multiplicity is $m_{000} = 1$ and the first elbow coordinates can be read off the $X^0Y^0Z^0$ term in generating functions $G_n(\noisys), G_n(\gamma)$.
-If it falls under $\rm{(C2)}$, then $E_{\rm{max}} = E_1$ ($E_{\rm{max}} = E_2$), the multiplicity is $m_{0n0} = 3^n$ ($m_{00n} = 3^n$) and the first elbow coordinates can be read off the $X^0Y^nZ^0$ ($X^0Y^0Z^n$) term in generating functions $G_n(\noisys), G_n(\gamma)$,
-\begin{equation}
-	(x_0, L_0) =
-	\begin{cases}
-		\left( \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^n, \wn^n \right), &\rm{(C1)}	\vspace{10pt}\\
-		\left( \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^n, (3u)^n \right). &\rm{(C2)} 
-	\end{cases}
-\end{equation}
-
-Considering the distillation process in~\cref{eq:msd_thermal}, the Lorenz curves of the initial and target states may each be described by either $\rm{(C1)}$ or $\rm{(C2)}$.
-In any case, a necessary distillation constraint can be defined at the location $x_\star = x_0$ of the initial state's first elbow and be expressed as
-\begin{equation}\label{eq:first_elbow_constraint}
-	\lc{\noisys(\epsilon)\too{n}}{\gamma_\beta}(x_\star) \geq \lc{\noisys(\epsilon')\too{\tt}}{\gamma_\beta}(x_\star).
-\end{equation}
-
-Let's focus on the case where both Lorenz curves are described by $\rm{(C1)}$.
-This case includes the unital fragment.
-
-The first elbow of the target state is located at $x'_0 = (3Z)^{-\tt} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the target state's first elbow,
-\begin{equation}\label{eq:constraint_deriv_temp}
-	L'_\star = \frac{x_\star}{x'_0}L'_0 = \left(\frac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n-\tt} \left( \frac{1}{3} - \frac{4}{9} \epsilon' \right)^{\tt}.
-\end{equation}
-The constraint in~\cref{eq:first_elbow_constraint} therefore holds only if
-\begin{align}
-	\frac{n}{n'} &\geq \frac{\ln{\Big[ \big( 1-\frac{4}{3}\epsilon' \big)\Z_\beta  e^{\beta E_0} \Big]}}{\ln{\Big[ \big( 1-\frac{4}{3}\epsilon \big)\Z_\beta e^{\beta E_0} \Big]}} \\
-	&= \frac{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} - \beta (F_\beta - E_0)}{\ln{\big( 1-\frac{4}{3}\epsilon \big)} - \beta (F_\beta - E_0)},
-\end{align}
-with $\tt \leq n$ and $\epsilon' \leq \epsilon \leq \epsilon_{\rm{th}}$. 
-The free energy of thermal state $\gamma_\beta$ is denoted by
-\begin{equation}
-	F_\beta \coloneqq \tr[\gamma_\beta H] + \beta^{-1} \tr[\gamma_\beta \ln{\gamma_\beta}] = -\beta^{-1} \ln{\Z_\beta}.
-\end{equation}
-
-Moreover, we can obtain an upper bound on thermal fragment distillation rate $R=n'/n$ for pure target Strange states ($\epsilon' = 0$) given by
-\begin{equation}
-	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\left( \frac{1}{1 - \frac{4}{3}\epsilon} \right)}}{\beta (E_0 - F_\beta)},
-\end{equation}
-which holds for all finite $n$ with $\tt \leq n$ and $\epsilon' \leq \epsilon \leq \epsilon_{\rm{th}}$.
-\nick{In fact, it holds for $0 \leq \epsilon \leq \epsilon_*$, where $\epsilon_\star$ is the noise level (lower than $\epsilon_{\rm{th}}$) at which the state conversion turns from $\rm{(C1)} \rightarrow \rm{(C1)}$ to $\rm{(C1)} \rightarrow \rm{(C2)}$.
-Need to adjust~\cref{fig:distill_bounds_temp} accordingly}
-At the limit of high temperature, $\beta \rightarrow 0$, we get $\beta F_\beta \rightarrow -\ln{3}$, and we retrieve the unital fragment bound,
-\begin{equation}
-	R(\beta) \xrightarrow{\beta \rightarrow 0} \frac{\ln{(3-4\epsilon)}}{\ln{3}}.
-\end{equation}
-We compare $R(\beta)$ for different values of $\beta$ with the mana bound $R_{\rm{mana}}$ in~\cref{fig:distill_bounds_temp}.
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.5]{figs/distill_bounds_temp.pdf}
-    \caption{\textbf{Distillation rate with low noise in thermal fragments.} Distillation rates obtained by majorization $R(\beta)$ for low noise levels $\epsilon \leq \epsilon_{\rm{th}}$ are plotted for different temperatures $\beta^{-1}$ such that $0 \leq \beta \leq \beta_{\rm{th}}$.
-    The mana distillation rate $R_{\rm{mana}}$ is given for comparison.
-    The Hamiltonian spectrum is simple harmonic, $(E_0, E_1, E_2) = (0,1,2)$.
-    As $\beta$ increases, the range of noise levels for which $R(\beta)$ is valid decreases and the distillation bound becomes stricter.
-    }
-    \label{fig:distill_bounds_temp}
-\end{figure}
-
-Our approach also allows for analysis at the limit of low temperature, $\beta \rightarrow \infty$, which is a limit case of $\rm{(C2)}$ with $\beta \geq \beta_{\rm{th}}$.
-
-We consider 
-\begin{equation}
-	x_\star = x_0 = (e^{-\beta E_{\rm{max}}} / \Z_\beta)^{n}.
-\end{equation}
-The first elbow of the target state is located at $x'_0 = (e^{-\beta E_{\rm{max}}} / \Z_\beta)^{\tt} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the target state's first elbow,
-\begin{equation}\label{eq:constraint_deriv_lowtemp}
-	L'_\star = \frac{x_\star}{x'_0}L'_0 = \left(\frac{e^{-\beta E_2}}{\Z_\beta}\right)^{n-\tt} \left( \frac{1}{2} - \frac{1}{6}\epsilon' \right)^{\tt}.
-\end{equation}
-Therefore, in the low temperature scenario $\beta \geq \beta_{\rm{th}}$, the constraint in~\cref{eq:first_elbow_constraint} holds only if
-\begin{align}
-	\frac{n}{n'} &\geq \frac{\ln{\Big[ \big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)\Z_\beta e^{\beta E_{\rm{max}}} \Big]}}{\ln{\Big[ \big( \frac{1}{2}-\frac{1}{6}\epsilon \big)\Z_\beta e^{\beta E_{\rm{max}}} \Big]}} \nonumber\\
-	&= \frac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F_\beta)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F_\beta)},
-\end{align}
-with $\tt \leq n$ and $\epsilon' \leq \epsilon$.
-
-We can obtain an upper bound on thermal fragment distillation rate $R=n'/n$ for pure target Strange states ($\epsilon' = 0$) in this regime as well. 
-It is given by
-\begin{equation}
-	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\left(\frac{1}{1-\frac{1}{3}\epsilon} \right)}}{-\ln{2} + \beta (E_{\rm{max}} - F_\beta)},
-\end{equation}
-which holds for all finite $n$ with $\tt \leq n$ and $\epsilon' \leq \epsilon$.
-At the zero temperature limit, $F_\beta$ tends to zero, so $R(\beta) \xrightarrow{\beta \rightarrow \infty} 1$.
-We compare $R(\beta)$ for different values of $\beta$ with the mana bound $R_{\rm{mana}}$ in~\cref{fig:distill_bounds_lowtemp}.
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.5]{figs/distill_bounds_lowtemp.pdf}
-    \caption{\textbf{Distillation rate for low temperatures in thermal fragments.} Distillation rates obtained by majorization $R(\beta)$ in the temperature regime $\beta \geq \beta_{\rm{th}}$ are plotted for different temperatures $\beta^{-1}$.
-    The mana distillation rate $R_{\rm{mana}}$ is given for comparison.
-    The Hamiltonian spectrum is simple harmonic, $(E_0, E_1, E_2) = (0,1,2)$.
-    \nick{Not-so-good bound for low temperatures, other elbows perform a lot better numerically.}
-    }
-    \label{fig:distill_bounds_lowtemp}
-\end{figure}
-
-\null\newpage
-\null\newpage
-
-\subsection{OLD Magic in thermal fragments}
-
 For $\beta = 0$, $\epsilon_{\rm{th}} = 3/7$, so $\epsilon \leq \epsilon_{\rm{th}}$ always.

### 2021-02-14 magic_paper.tex
wigner phase space to vector correspondence done?

@@
 In general, a $1$-copy $d$-dimensional state is defined exactly by its $d^2$ Wigner distribution $W$. 
-The distribution $W$ can always be described by a set of $D \leq d^2$ component-multiplicity pairs denoted by $\{(w_i, m_i)\}_{i=1,\dots,D}$.
+The distribution $W$ can always be described by a Wigner-component vector $\bmw = (w_i)_{i=1,\dots,D}$ and a multiplicity vector $\bmm = (m_i)_{i=1,\dots,D}$, where $D \leq d^2$ and they form component-multiplicity pairs denoted by $\{(w_i, m_i)\}_{i=1,\dots,D}$.
 \begin{definition}
@@
 
-We construct complete sets of component-multiplicity pairs and based on the distinct components of the Gibbs-rescaled distribution,
-\begin{align}
-	S(\noisys) &\coloneqq \{ (-\wn, 1), (\wp, 2), (\wp, 3), (\wp, 3) \} \\
-	S(\gamma) &\coloneqq \Big\{ \left( \frac{e^{-\beta E_0}}{3\Z}, 1 \right), \left( \frac{e^{-\beta E_0}}{3\Z}, 2 \right), \nonumber\\
-	&\hspace{23pt} \left( \frac{e^{-\beta E_1}}{3\Z}, 3 \right), \left( \frac{e^{-\beta E_2}}{3\Z}, 3 \right) \Big\} \\
-	S(\noisys | \gamma) &\coloneqq \{ (-\wn 3\Z e^{\beta E_0}, 1), (\wp 3\Z e^{\beta E_0}, 2), \nonumber\\
-	&\hspace{21pt} (\wp 3\Z e^{\beta E_1}, 3), (\wp 3\Z e^{\beta E_2}, 3) \}
-\end{align}
-
-There are four distinct component-multiplicity pairs for the Gibbs-rescaled distribution, so in order to use~\cref{lem:ncopycomponents} to find the components of the $n$-copy distributions, we first define an index vector
+We construct component and multiplicity vectors based on the distinct components of the Gibbs-rescaled distribution,
+\begin{align}
+	\bmm &\coloneqq (1,2,3,3) \\
+	\bmw(\noisys) &\coloneqq (-\wn, \wp, \wp, \wp) \\
+	\bmw(\gamma) &\coloneqq \frac{1}{3\Z} \left( e^{-\beta E_0}, e^{-\beta E_0}, e^{-\beta E_1}, e^{-\beta E_2} \right) \\
+	\bmw(\noisys | \gamma) &\coloneqq 3\Z \left( -\wn e^{\beta E_0}, \wp e^{\beta E_0}, \wp e^{\beta E_1}, \wp e^{\beta E_2} \right) \label{eq:bmw_rescaled}
+\end{align}
+
+There are four distinct values of the Gibbs-rescaled distribution on the phase space, with the negative Strange component $-\wn$ corresponding to energy $E_0$ as illustrated in the phase space split in~\cref{fig:pd_split_thermal}.
+The Wigner-component vectors $\bmw(\noisys), \bmw(\gamma)$ are then constructed so as to match the four phase space regions.
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.5]{figs/pd_split_thermal.pdf}
+    \caption{\textbf{Qutrit phase space regions with different Gibbs-rescaled values.}
+    The slope is negative in region $1$ and positive in regions $X,Y,Z$.
+    It attains a unique value in each region, given by~\cref{eq:bmw_rescaled} respectively.
+    }
+    \label{fig:pd_split_thermal}
+\end{figure}
+
+For notational convenience, we define the index vector
 \begin{equation}
@@
 \end{equation}
-where $i,j,k$ are non-negative integers that satisfy 
+where $i,j,k$ are non-negative integers and
 \begin{equation*}
-	i+j+k \eqqcolon \alpha \leq n.
+	\alpha \coloneqq i+j+k \leq n.
 \end{equation*}
-The $n$-copy
-
-\begin{align}\label{eq:gn}
-	&G_n(\noisys) \coloneqq G_1(\noisys)^n = \\
-	&\sum\limits_{\substack{i,j,k = 0,\dots,n \\ \alpha \leq n}}\hspace{-10pt} m_{ijk} \big[(-\wn)^{n-\alpha} \wp^{\alpha} \big] X^i Y^j Z^k, \nonumber
-	\\[10pt]
-	&G_n(\gamma) \coloneqq G_1(\gamma)^n = \\
-	&(3\Z)^{-n}\hspace{-10pt} \sum\limits_{\substack{i,j,k = 0,\dots,n \\ \alpha \leq n}}\hspace{-10pt} m_{ijk} \Big[ e^{-\beta ( i E_0 + j E_1 + k E_2 )} e^{-\beta (n-\alpha)E_0} \Big] X^i Y^j Z^k, \nonumber
-	\\[10pt]
-	&G_n(\noisys|\gamma) \coloneqq G_1(\noisys|\gamma)^n = \\
-	&(3\Z)^{n}\hspace{-10pt} \sum\limits_{\substack{i,j,k = 0,\dots,n \\ \alpha \leq n}}\hspace{-10pt} m_{ijk} \Big[ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} \times \nonumber\\[-15pt]
-	&\hspace{80pt} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big] X^i Y^j Z^k, \nonumber
-\end{align}
-where the $(i,j,k)$-th term multiplicity $m_{ijk}$ (i.e. the number of phase space points contained in region $X^i Y^j Z^k$) is given by
-\begin{equation}
-	m_{ijk} \coloneqq \frac{n!}{i!j!k!(n-\alpha)!} 2^i 3^j 3^k.
-\end{equation}
-
-In order to construct the Lorenz curve of a Strange state in a thermal fragment we need to sort the components of $\widetilde{W}_n$ in decreasing order.
+The Wigner components of the $n$-copy distributions are now readily provided by~\cref{lem:ncopycomponents}.
+Firstly, the $n$-copy multiplicity is given according to~\cref{eq:M} by
+\begin{equation}
+	m_{ijk} \coloneqq M_{\bmq} = \frac{n!}{i!j!k!(n-\alpha)!} 2^i 3^j 3^k.
+\end{equation}
+The distribution values that correspond to the same index $\bmq$ are given according to~\cref{eq:W} by
+\begin{align}
+	w(\noisys)_{ijk} &= (-\wn)^{n-\alpha} \wp^{\alpha} \\
+	w(\gamma)_{ijk} &= (3\Z)^{-n} e^{-\beta (n-\alpha)E_0} e^{-\beta ( i E_0 + j E_1 + k E_2 )} \\
+	w(\noisys | \gamma)_{ijk} &= (3\Z)^{n} (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )}
+\end{align}
+
+In order to construct the $n$-copy Lorenz curve of a Strange state in a thermal fragment we need to sort the components of the $n$-copy Gibbs-rescaled distribution, $w(\noisys | \gamma)_{ijk}$ in decreasing order.
 In particular, to find the coordinates of the first elbow $(x_0, L_0)$, we need to evaluate the greatest component,
-\begin{equation}\label{eq:max_slope}
-	\widetilde{W}_{\rm{max}} \coloneqq \max\limits_{i,j,k}{\Big\{ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}},
-\end{equation}
-where $0 \leq i,j,k \leq n$ and $i+j+k \eqqcolon \alpha \leq n$.
+\begin{align}
+	&\bmw(\noisys | \gamma)_{\rm{max}} \coloneqq \label{eq:max_slope}\\
+	&(3\Z)^{n} \max\limits_{i,j,k}\Big\{ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \nonumber
+\end{align}
+where $0 \leq i,j,k \leq n$ and $\alpha \coloneqq i+j+k \leq n$.
 Notice that for $0 \leq \epsilon \leq 3/7$, we have $\wn \geq \wp$.

### 2021-02-14 magic_paper.tex
Added complete analysis on thermal fragments, only left with fixing plots a bit

@@
 \begin{align}
-	\widetilde{W}_{\rm{max}} &= \max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta \alpha E_{\rm{max}}} \Big\}} \\
-	&= \max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \wn^n e^{n\beta E_0} \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}
+	&\bmw(\noisys | \gamma)_{\rm{max}} = \nonumber\\
+	&\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta \alpha E_{\rm{max}}} \Big\}} = \nonumber\\
+	&\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \wn^n e^{n\beta E_0} \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}
 \end{align}
@@
 \begin{equation}
-\widetilde{W}_{\rm{max}} =
+\bmw(\noisys | \gamma)_{\rm{max}} =
 	\begin{cases}
@@
 
-Whenever the set of physical parameters falls under $\rm{(C1)}$, the multiplicity is $m_{000} = 1$ and the first elbow coordinates can be read off the $X^0Y^0Z^0$ term in generating functions $G_n(\noisys), G_n(\gamma)$.
-If it falls under $\rm{(C2)}$, then $E_{\rm{max}} = E_1$ ($E_{\rm{max}} = E_2$), the multiplicity is $m_{0n0} = 3^n$ ($m_{00n} = 3^n$) and the first elbow coordinates can be read off the $X^0Y^nZ^0$ ($X^0Y^0Z^n$) term in generating functions $G_n(\noisys), G_n(\gamma)$,
-\begin{equation}
+In $\rm{(C1)}$, the multiplicity is $m_{000} = 1$ and the corresponding Wigner components are $\bmw(\noisys)_{000}, \bmw(\gamma)_{000}$.
+In $\rm{(C2)}$, we have $E_{\rm{max}} = E_1$ ($E_{\rm{max}} = E_2$), the multiplicity is $m_{0n0} = 3^n$ ($m_{00n} = 3^n$) and the corresponding Wigner components are $\bmw(\noisys)_{0n0}, \bmw(\gamma)_{0n0}$ ($\bmw(\noisys)_{00n}, \bmw(\gamma)_{00n}$).
+The first elbow coordinate expression can finally be expressed as
+\begin{equation}\label{eq:first_elb_coords}
 	(x_0, L_0) =
@@
 
-Considering the distillation process in~\cref{eq:msd_thermal}, the Lorenz curves of the initial and target states may each be described by either $\rm{(C1)}$ or $\rm{(C2)}$.
-In any case, a necessary distillation constraint can be defined at the location $x_\star = x_0$ of the initial state's first elbow and be expressed as
+Consider the distillation process in~\cref{eq:msd_thermal},
+\begin{equation*}
+		\noisys(\epsilon)\too{n} \xrightarrow{\E \in \O_{\gamma_\beta}} \noisys(\epsilon')\too{\tt} \otimes \gamma_\beta\too{(n-\tt)},
+\end{equation*}
+with $n > n'$ and $\epsilon > epsilon'$.
+A necessary distillation constraint can be defined at the location $x_\star = x_0$ of the initial state's first elbow, expressed as
 \begin{equation}\label{eq:first_elbow_constraint}
@@
 
-Let's focus on the case where both Lorenz curves are described by $\rm{(C1)}$.
-This case includes the unital fragment.
-
-The first elbow of the target state is located at $x'_0 = (3Z)^{-\tt} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the target state's first elbow,
+The Lorenz curves of the initial and target states may each be described by either $\rm{(C1)}$ or $\rm{(C2)}$, depending on the physical parameters $\epsilon, \epsilon', \beta$.
+Specifically, we can get three scenarios:
+\begin{enumerate}
+	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} = E_0$ OR $E_{\rm{max}} > E_0$, $\beta < \beta_{\rm{th}}$ and $\epsilon' < \epsilon  \leq \epsilon_{\rm{th}}$.
+	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} > E_0$, $\beta < \beta_{\rm{th}}$ and $\epsilon' \leq \epsilon_{\rm{th}} < \epsilon$.
+	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $E_{\rm{max}} > E_0$, $\beta \geq \beta_{\rm{th}}$.
+\end{enumerate}
+Note that $\rm{(C1)} \rightarrow \rm{(C2)}$ is impossible because it would imply $\epsilon \leq \epsilon_{\rm{th}} \leq \epsilon' < \epsilon$, a contradiction.
+
+In all three scenarios, it is simple to check that the first elbow of the initial state is always located closer to $0$ compared to the first elbow of the target state, $x_0 \leq x_0'$:
+\begin{enumerate}
+	\item $\rm{(C1)} \rightarrow \rm{(C1)}$. 
+	It is always true that $e^{-\beta E_0} / \Z_\beta \leq 1$, so
+	\begin{align*}
+		x_0 &= \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^n = \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n-\tt} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{\tt} \\
+		&< \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{\tt} = x_0'		
+	\end{align*}
+	\item $\rm{(C2)} \rightarrow \rm{(C1)}$.
+	It is always true that
+	\begin{align*}
+		&\Z_\beta^{n-\tt} > (e^{-\beta E_{\rm{max}}})^{n-\tt} = e^{-\beta (n-\tt) E_{\rm{max}}}, \text{ so} \\
+		x_0 &= \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^n = \dfrac{e^{-\beta(n E_{\rm{max}} - \tt E_0)}}{\Z_\beta^{n-\tt}} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{\tt} \\
+		&< \dfrac{e^{-\beta(n E_{\rm{max}} - \tt E_0)}}{e^{-\beta (n-\tt) E_{\rm{max}}}} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{\tt} \\
+		&= e^{-\beta \tt (E_{\rm{max}} - E_0)} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{\tt} \\
+		&< \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{\tt} = x_0'.
+	\end{align*}
+	\item $\rm{(C2)} \rightarrow \rm{(C2)}$.
+	It is always true that $e^{-\beta E_{\rm{max}}} / \Z_\beta \leq 1$, so
+	\begin{align*}
+		x_0 &= \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^n = \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^{n-\tt} \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^{\tt} \\
+		&\leq \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^{\tt} = x_0'	
+	\end{align*}
+\end{enumerate}
+We can thus find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$ by interpolating between the origin and the target state's first elbow, 
 \begin{equation}\label{eq:constraint_deriv_temp}
-	L'_\star = \frac{x_\star}{x'_0}L'_0 = \left(\frac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n-\tt} \left( \frac{1}{3} - \frac{4}{9} \epsilon' \right)^{\tt}.
-\end{equation}
-The constraint in~\cref{eq:first_elbow_constraint} therefore holds only if
-\begin{align}
-	\frac{n}{n'} &\geq \frac{\ln{\Big[ \big( 1-\frac{4}{3}\epsilon' \big)\Z_\beta  e^{\beta E_0} \Big]}}{\ln{\Big[ \big( 1-\frac{4}{3}\epsilon \big)\Z_\beta e^{\beta E_0} \Big]}} \\
-	&= \frac{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} - \beta (F_\beta - E_0)}{\ln{\big( 1-\frac{4}{3}\epsilon \big)} - \beta (F_\beta - E_0)},
-\end{align}
-with $\tt \leq n$ and $\epsilon' \leq \epsilon \leq \epsilon_{\rm{th}}$. 
-The free energy of thermal state $\gamma_\beta$ is denoted by
+	L'_\star = \frac{x_\star}{x'_0}L'_0.
+\end{equation}
+We need $L_0 \geq L_\star'$. Therefore, restricting to the first elbow, the necessary distillation condition in~\cref{eq:first_elbow_constraint} simply becomes
+\begin{equation}\label{eq:first_elb_bound}
+	\frac{L_0}{x_0} \geq \frac{L_0'}{x_0'}.
+\end{equation}
+Involving more elbows gives stricter, but more convoluted necessary distillation constraints.
+
+We now compute distillation bounds based on the first elbow constraint in the three possible scenarios.
+We express them in terms of the free energy of thermal state $\gamma_\beta$ denoted by
 \begin{equation}
@@
 \end{equation}
-
-Moreover, we can obtain an upper bound on thermal fragment distillation rate $R=n'/n$ for pure target Strange states ($\epsilon' = 0$) given by
+Substituting coordinates from~\cref{eq:first_elb_coords} appropriately in~\cref{eq:first_elb_bound}, we get the following necessary conditions:
+\begin{enumerate}
+	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} = E_0$ OR $E_{\rm{max}} > E_0$, $\beta < \beta_{\rm{th}}$ and $\epsilon' < \epsilon  \leq \epsilon_{\rm{th}}$.
+
+\begin{align}
+	\frac{n}{n'} &\geq \frac{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F_\beta)}{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_0 - F_\beta)}, \text{ or} \\
+	\epsilon &\leq \frac{3}{4} - \frac{3}{4} \left( 1 - \frac{4}{3}\epsilon' \right)^{\frac{\tt}{n}} \left( \frac{e^{-\beta E_0}}{\Z_\beta} \right)^{1 - \frac{\tt}{n}}	
+\end{align}
+This leads to an upper bound for the distillation rate $R=n'/n$ of pure Strange states ($\epsilon' = 0$),
 \begin{equation}
@@
 \end{equation}
-which holds for all finite $n$ with $\tt \leq n$ and $\epsilon' \leq \epsilon \leq \epsilon_{\rm{th}}$.
-\nick{In fact, it holds for $0 \leq \epsilon \leq \epsilon_*$, where $\epsilon_\star$ is the noise level (lower than $\epsilon_{\rm{th}}$) at which the state conversion turns from $\rm{(C1)} \rightarrow \rm{(C1)}$ to $\rm{(C2)} \rightarrow \rm{(C1)}$.
-Need to adjust~\cref{fig:distill_bounds_temp} accordingly}
-At the limit of high temperature, $\beta \rightarrow 0$, we get $\beta F_\beta \rightarrow -\ln{3}$, and we retrieve the unital fragment bound,
+
+	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} > E_0$, $\beta < \beta_{\rm{th}}$ and $\epsilon' \leq \epsilon_{\rm{th}} < \epsilon$.
+
+\begin{align}
+	\frac{n}{n'} &\geq \frac{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F_\beta)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F_\beta)}, \text{ or} \\
+	\epsilon &\leq 3 - 6 \left( 1 - \frac{4}{3}\epsilon' \right)^{\frac{\tt}{n}} \frac{e^{-\beta E_{\rm{max}}} e^{\frac{\tt}{n}\beta E_0}}{\Z_\beta^{1-\frac{\tt}{n}}}	
+\end{align}
+This leads to an upper bound for the distillation rate $R=n'/n$ of pure Strange states ($\epsilon' = 0$),
+\begin{equation}
+	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\left(\frac{1}{1-\frac{1}{3}\epsilon} \right)} + (E_{\rm{max}} - E_0)(\beta_{\rm{th}} - \beta)}{\beta (E_0 - F_\beta)},
+\end{equation}
+
+	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $E_{\rm{max}} > E_0$, $\beta \geq \beta_{\rm{th}}$.
+
+\begin{align}
+	\frac{n}{n'} &\geq \frac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F_\beta)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F_\beta)}, \text{ or} \\
+	\epsilon &\leq 3 - 6 \left( \frac{1}{2} - \frac{1}{6}\epsilon' \right)^{\frac{\tt}{n}} \left( \frac{e^{-\beta E_{\rm{max}}}}{\Z_\beta} \right)^{1 - \frac{\tt}{n}}	
+\end{align}
+This leads to an upper bound for the distillation rate $R=n'/n$ of pure Strange states ($\epsilon' = 0$),
+\begin{equation}
+	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\left(\frac{1}{1-\frac{1}{3}\epsilon} \right)}}{-\ln{2} + \beta (E_{\rm{max}} - F_\beta)},
+\end{equation}
+\end{enumerate}
+
+Consider pure Strange state distillation at high temperatures, $\beta \leq \beta_{\rm{th}}$.
+Depending on the noise level of the initial state, we have either a $\rm{(C1)} \rightarrow \rm{(C1)}$ or a $\rm{(C2)} \rightarrow \rm{(C1)}$ scenario.
+
+We compare $R(\beta)$ for different temperatures with the mana bound $R_{\rm{mana}}$ in~\cref{fig:distill_bounds_temp}.
+At every $\beta > 0$, the rates indicate a transition at $\epsilon_{\rm{th}}$.
+As $\beta$ increases, the rate becomes stricter.
+At the high temperature limit, $\beta \rightarrow 0$, we get $\beta F_\beta \rightarrow -\ln{3}$, and we retrieve the unital fragment bound,
 \begin{equation}
@@
 \end{equation}
-We compare $R(\beta)$ for different values of $\beta$ with the mana bound $R_{\rm{mana}}$ in~\cref{fig:distill_bounds_temp}.
+
 \begin{figure}[h]
@@
     As $\beta$ increases, the range of noise levels for which $R(\beta)$ is valid decreases and the distillation bound becomes stricter.
+\nick{it holds for $0 \leq \epsilon \leq \epsilon_*$, where $\epsilon_\star$ is the noise level ($ \leq \epsilon_{\rm{th}}$) at which the state conversion turns from $\rm{(C1)} \rightarrow \rm{(C1)}$ to $\rm{(C2)} \rightarrow \rm{(C1)}$.
+Need to adjust~\cref{fig:distill_bounds_temp} accordingly}
     }
@@
 
-Our approach also allows for analysis at the limit of low temperature, $\beta \rightarrow \infty$, which is a limit case of $\rm{(C2)}$ with $\beta \geq \beta_{\rm{th}}$.
-
-We consider 
-\begin{equation}
-	x_\star = x_0 = (e^{-\beta E_{\rm{max}}} / \Z_\beta)^{n}.
-\end{equation}
-The first elbow of the target state is located at $x'_0 = (e^{-\beta E_{\rm{max}}} / \Z_\beta)^{\tt} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the target state's first elbow,
-\begin{equation}\label{eq:constraint_deriv_lowtemp}
-	L'_\star = \frac{x_\star}{x'_0}L'_0 = \left(\frac{e^{-\beta E_2}}{\Z_\beta}\right)^{n-\tt} \left( \frac{1}{2} - \frac{1}{6}\epsilon' \right)^{\tt}.
-\end{equation}
-Therefore, in the low temperature scenario $\beta \geq \beta_{\rm{th}}$, the constraint in~\cref{eq:first_elbow_constraint} holds only if
-\begin{align}
-	\frac{n}{n'} &\geq \frac{\ln{\Big[ \big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)\Z_\beta e^{\beta E_{\rm{max}}} \Big]}}{\ln{\Big[ \big( \frac{1}{2}-\frac{1}{6}\epsilon \big)\Z_\beta e^{\beta E_{\rm{max}}} \Big]}} \nonumber\\
-	&= \frac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F_\beta)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F_\beta)},
-\end{align}
-with $\tt \leq n$ and $\epsilon' \leq \epsilon$.
-
-We can obtain an upper bound on thermal fragment distillation rate $R=n'/n$ for pure target Strange states ($\epsilon' = 0$) in this regime as well. 
-It is given by
-\begin{equation}
-	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\left(\frac{1}{1-\frac{1}{3}\epsilon} \right)}}{-\ln{2} + \beta (E_{\rm{max}} - F_\beta)},
-\end{equation}
-which holds for all finite $n$ with $\tt \leq n$ and $\epsilon' \leq \epsilon$.
+Consider pure Strange state distillation at low temperatures, $\beta \rightarrow \infty$.
+Independently of the noise level of the initial state, we have a $\rm{(C2)} \rightarrow \rm{(C2)}$ scenario.
+
+We compare $R(\beta)$ for different temperatures with the mana bound $R_{\rm{mana}}$ in~\cref{fig:distill_bounds_lowtemp}.
+As $\beta$ decreases, the rate becomes stricter.
 At the zero temperature limit, $F_\beta$ tends to zero, so $R(\beta) \xrightarrow{\beta \rightarrow \infty} 1$.
-We compare $R(\beta)$ for different values of $\beta$ with the mana bound $R_{\rm{mana}}$ in~\cref{fig:distill_bounds_lowtemp}.
+
 \begin{figure}[h]

### 2021-02-15 magic_paper.tex
Latex broken trying to do basic editing. Very annoying.

@@
 	\begin{split}
-	\epsilon_{\rm{th}}(n, \tt, \epsilon', \sigma) \coloneqq &\sup{\{\epsilon:\ \lc{\rho(\epsilon)\too{n}}{\sigma}}(x) \geq \\
+	\epsilon_{\star}(n, \tt, \epsilon', \sigma) \coloneqq &\sup{\{\epsilon:\ \lc{\rho(\epsilon)\too{n}}{\sigma}}(x) \geq \\
 	&{\lc{\rho(\epsilon')\too{\tt}}{\sigma}(x),\ x\in[0,1]\}}.
@@
 \end{equation}
-The MSD process~(\ref{eq:dist}) is impossible for all $\epsilon > \epsilon_{\rm{th}}(n, \tt, \epsilon', \sigma)$.
+The MSD process~(\ref{eq:dist}) is impossible for all $\epsilon > \epsilon_{\star}(n, \tt, \epsilon', \sigma)$.
 
@@
 \begin{equation}\label{eq:ethresh}
-	n_{\rm{th}}(\epsilon, \epsilon', \sigma) \coloneqq \min{\{n: \lc{\noisysn}{\sigma} \geq \lc{\noisys(\epsilon')}{\sigma}\}}.
+	n_{\star}(\epsilon, \epsilon', \sigma) \coloneqq \min{\{n: \lc{\noisysn}{\sigma} \geq \lc{\noisys(\epsilon')}{\sigma}\}}.
 \end{equation}}
@@
 \begin{equation}
-	\wp(\epsilon) = \frac{1}{6} -\frac{1}{18}\epsilon
+	u(\epsilon) = \frac{1}{6} -\frac{1}{18}\epsilon
 \end{equation}
@@
 \begin{equation}
-	- \wn(\epsilon) = - \left( \frac{1}{3} -\frac{4}{9}\epsilon \right)
+	- v(\epsilon) = - \left( \frac{1}{3} -\frac{4}{9}\epsilon \right)
 \end{equation}
@@
 
+\ddd{Note the following is relevant: you might have $W_{\bmq} = W_{\bmq'}$ for two different $\bmq$, $\bmq'$.
+This would make a difference to our calculations for the first elbow.
+Check this doesn't occur.
+(If it does, our analysis is still correct, but it simply could be improved).}
+
 \subsubsection{Distillation bounds}
@@
 	\bmm &\coloneqq (1,2,3,3) \\
-	\bmw(\noisys) &\coloneqq (-\wn, \wp, \wp, \wp) \\
+	\bmw(\noisys) &\coloneqq (-v, u, u, u) \\
 	\bmw(\gamma) &\coloneqq \frac{1}{3\Z} \left( e^{-\beta E_0}, e^{-\beta E_0}, e^{-\beta E_1}, e^{-\beta E_2} \right) \\
-	\bmw(\noisys | \gamma) &\coloneqq 3\Z \left( -\wn e^{\beta E_0}, \wp e^{\beta E_0}, \wp e^{\beta E_1}, \wp e^{\beta E_2} \right) \label{eq:bmw_rescaled}
-\end{align}
-
-There are four distinct values of the Gibbs-rescaled distribution on the phase space, with the negative Strange component $-\wn$ corresponding to energy $E_0$ as illustrated in the phase space split in~\cref{fig:pd_split_thermal}.
+	\bmw(\noisys | \gamma) &\coloneqq 3\Z \left( -v e^{\beta E_0}, u e^{\beta E_0}, u e^{\beta E_1}, u e^{\beta E_2} \right) \label{eq:bmw_rescaled}
+\end{align}
+
+There are four distinct values of the Gibbs-rescaled distribution on the phase space, with the negative Strange component $-v$ corresponding to energy $E_0$ as illustrated in the phase space split in~\cref{fig:pd_split_thermal}.
 The Wigner-component vectors $\bmw(\noisys), \bmw(\gamma)$ are then constructed so as to match the four phase space regions.
@@
 \begin{align}
-	w(\noisys)_{ijk} &= (-\wn)^{n-\alpha} \wp^{\alpha} \\
+	w(\noisys)_{ijk} &= (-v)^{n-\alpha} u^{\alpha} \\
 	w(\gamma)_{ijk} &= (3\Z)^{-n} e^{-\beta (n-\alpha)E_0} e^{-\beta ( i E_0 + j E_1 + k E_2 )} \\
-	w(\noisys | \gamma)_{ijk} &= (3\Z)^{n} (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )}
+	w(\noisys | \gamma)_{ijk} &= (3\Z)^{n} (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )}
 \end{align}
@@
 	&\bmw(\noisys | \gamma)_{\rm{max}} \coloneqq \label{eq:max_slope}\\
-	&(3\Z)^{n} \max\limits_{i,j,k}\Big\{ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \nonumber
+	&(3\Z)^{n} \max\limits_{i,j,k}\Big\{ (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \nonumber
 \end{align}
 where $0 \leq i,j,k \leq n$ and $\alpha \coloneqq i+j+k \leq n$.
-Notice that for $0 \leq \epsilon \leq 3/7$, we have $\wn \geq \wp$.
-Assume that $n$ is even. 
-We then need the sum $\alpha = i+j+k$ to be even, so that the expression remains positive.
-
-Given an even value $\alpha$ for the sum, the term $\wn^{n-\alpha} \wp^{\alpha} e^{-\beta (n-\alpha)E_0}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
-Hence, we have
-\begin{align}
-	&\bmw(\noisys | \gamma)_{\rm{max}} = \nonumber\\
-	&\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta \alpha E_{\rm{max}}} \Big\}} = \nonumber\\
-	&\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \wn^n e^{n\beta E_0} \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}
-\end{align}
-The last expression is maximised for $\alpha = 0$ ($\alpha = n$) when the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than $1$ (greater than $1$).
-The threshold value of $1$ is achieved when the noise level $\epsilon$ is equal to
-\begin{equation}
-	\epsilon_{\rm{th}} \coloneqq 3 - \dfrac{18}{8-e^{(E_{\rm{max}} - E_0)\beta}}.
-	%\beta \leq \frac{1}{E_{\rm{max}} - E_0}\ln{\left( 8-\frac{18}{3-\epsilon} \right)}
-\end{equation}
-The noise level threshold $\epsilon_{\rm{th}}$ is a decreasing function of $\beta$.
-It achieves its maximum value $3/7$ for $(E_{\rm{max}} - E_0)\beta = 0$, and a value equal to $0$ for
-\begin{equation}
-	\beta_{\rm{th}} \coloneqq \frac{1}{E_{\rm{max}} - E_0} \ln2.
-\end{equation}
-For $\beta > \beta_{\rm{th}}$, $\epsilon_{\rm{th}}$ is negative, meaning that the noise level $\epsilon$ will always be higher than the threshold.
-We highlight that the threshold becomes $0$ when the difference between the maximum energy level and the level associated with the state negativity is equal to the energy extracted from a single particle Szilard's engine,
-\begin{equation}
-	E_{\rm{max}} - E_0 = \beta_{\rm{th}}^{-1} \ln2.
-\end{equation}
-
-The maximum slope finally is
-\begin{equation}
-\bmw(\noisys | \gamma)_{\rm{max}} =
-	\begin{cases}
-		\wn^n e^{n\beta E_0}, &\epsilon \leq \epsilon_{\rm{th}},\ \hspace{30pt}\rm{(C1)}	\\
-		\wp^n e^{n\beta E_{\rm{max}}}, &\epsilon > \epsilon_{\rm{th}}.\ \hspace{32pt}\rm{(C2)} 
-	\end{cases}
-\end{equation}
-Case 1 $\rm{(C1)}$ corresponds to the region labelled by $(i,j,k) = (0,0,0)$.
-Case 2 $\rm{(C2)}$ corresponds to the region labelled by 
-\begin{equation}
-	(i,j,k) = 
-	\begin{cases}
-	(0,n,0), &\text{if } E_{\rm{max}} = E_1, \\
-	(0,0,n), &\text{if } E_{\rm{max}} = E_2.
-	\end{cases}
-\end{equation}
-Note that if $E_{\rm{max}} = E_0$, we get $\epsilon_{\rm{th}} = 3/7$ and $\rm{(C1)}$ holds for all $\epsilon$ and $\beta$.
-Assuming $E_{\rm{max}} > E_0$, we get the cases:
-\begin{itemize}
-	\item $\beta = 0$. Then, $\epsilon_{\rm{th}} = 3/7$ and $\rm{(C1)}$ holds for all noise levels $\epsilon$.
-	This is the unital fragment.
-	\item $0 < \beta < \beta_{\rm{th}}$. Then, $0 < \epsilon_{\rm{th}} < 3/7$ and $\rm{(C1)}$ holds for $\epsilon \leq \epsilon_{\rm{th}}$, while $\rm{(C2)}$ holds for $\epsilon \geq \epsilon_{\rm{th}}$.
-	\item $\beta \geq \beta_{\rm{th}}$. Then, $ \epsilon_{\rm{th}} \leq 0$ and $\rm{(C2)}$ holds for all $\epsilon$.
-\end{itemize}
+Notice that for $0 \leq \epsilon \leq 3/7$, we have $v \geq u$. We assume that $n$ is even, ans so we then need the sum $\alpha = i+j+k$ to be even, so that the expression is positive.
+
+%Given an even value $\alpha$ for the sum, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_0}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
+%Hence, we have \ddd{Why did the $\Z$ term disappear?}
+%\begin{align}
+%	\bmw(\noisys | \gamma)_{\rm{max}}
+%&=\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ v^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta \alpha E_{\rm{max}}} \Big\}}  \nonumber\\
+%	&= v^n e^{n\beta E_0}\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}
+%\end{align}
+%If the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than $1$ then the maximum occurs at $\alpha=0$, and otherwise the maximum occurs at $\alpha = n$.
+%The threshold value of $1$ is achieved for this term when the noise level $\epsilon$ is equal to
+%\begin{equation}
+%	\epsilon_{\star}(\beta) := 3 - \dfrac{18}{8-e^{(E_{\rm{max}} - E_0)\beta}}.
+%	%\beta \leq \frac{1}{E_{\rm{max}} - E_0}\ln{\left( 8-\frac{18}{3-\epsilon} \right)}
+%\end{equation}
+%For the case $E_{\rm{max}} = E_0$ this threshold is constant in temperature and given by Since $ E_{\rm max} - E_0 \ge 0$ the threshold $\epsilon_{\star}$ is a decreasing function of $\beta$, and it achieves its maximum value $3/7$ for $(E_{\rm{max}} - E_0)\beta = 0$, and a value equal to $0$ for
+%\begin{equation}
+%	\beta_{\star} \coloneqq \frac{1}{E_{\rm{max}} - E_0} \ln2.
+%\end{equation}
+%For $\beta > \beta_{\star}$, $\epsilon_{\star}$ is negative, meaning that the noise level $\epsilon$ will always be higher than the threshold.
+%We highlight that the threshold becomes $0$ when the difference between the maximum energy level and the level associated with the state negativity is equal to the energy extracted from a single particle Szilard's engine,
+%\begin{equation}
+%	E_{\rm{max}} - E_0 = kT_{\star} \ln2.
+%\end{equation}
+%
+%The maximum slope \ddd{``maximum slope??''} finally is
+%\begin{equation}
+%\bmw(\noisys | \gamma)_{\rm{max}} =
+%	\begin{cases}
+%		v^n e^{n\beta E_0}, &\epsilon \leq \epsilon_{\star},\ \hspace{30pt}\rm{(C1)}	\\
+%		u^n e^{n\beta E_{\rm{max}}}, &\epsilon > \epsilon_{\star}.\ \hspace{32pt}\rm{(C2)} 
+%	\end{cases}
+%\end{equation}
+%Case $\rm{(C1)}$ corresponds to $(i,j,k) = (0,0,0)$, while case $\rm{(C2)}$ corresponds to the  the conditions 
+%\begin{equation}
+%	(i,j,k) = 
+%	\begin{cases}
+%	(0,n,0), &\text{if } E_{\rm{max}} = E_1, \\
+%	(0,0,n), &\text{if } E_{\rm{max}} = E_2.
+%	\end{cases}
+%\end{equation}
+%Note that if $E_{\rm{max}} = E_0$, we get $\epsilon_{\star} = 3/7$ and $\rm{(C1)}$ holds for all $\epsilon$ and $\beta$.
+%Assuming $E_{\rm{max}} > E_0$, we get the cases:
+%\begin{itemize}
+%	\item $\beta = 0$. Then, $\epsilon_{\star} = 3/7$ and $\rm{(C1)}$ holds for all noise levels $\epsilon$.
+%	This is the unital fragment.
+%	\item $0 < \beta < \beta_{\star}$. Then, $0 < \epsilon_{\star} < 3/7$ and $\rm{(C1)}$ holds for $\epsilon \leq \epsilon_{\star}$, while $\rm{(C2)}$ holds for $\epsilon \geq \epsilon_{\star}$.
+%	\item $\beta \geq \beta_{\star}$. Then, $ \epsilon_{\star} \leq 0$ and $\rm{(C2)}$ holds for all $\epsilon$.
+%\end{itemize}
 
@@
 	\begin{cases}
-		\left( \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^n, \wn^n \right), &\rm{(C1)}	\vspace{10pt}\\
+		\left( \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^n, v^n \right), &\rm{(C1)}	\vspace{10pt}\\
 		\left( \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^n, (3u)^n \right). &\rm{(C2)} 
@@
 \end{equation*}
-with $n > n'$ and $\epsilon > epsilon'$.
+with $n > n'$ and $\epsilon > \epsilon'$.
 A necessary distillation constraint can be defined at the location $x_\star = x_0$ of the initial state's first elbow, expressed as
@@
 \begin{enumerate}
-	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} = E_0$ OR $E_{\rm{max}} > E_0$, $\beta < \beta_{\rm{th}}$ and $\epsilon' < \epsilon  \leq \epsilon_{\rm{th}}$.
-	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} > E_0$, $\beta < \beta_{\rm{th}}$ and $\epsilon' \leq \epsilon_{\rm{th}} < \epsilon$.
-	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $E_{\rm{max}} > E_0$, $\beta \geq \beta_{\rm{th}}$.
+	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} = E_0$ OR $E_{\rm{max}} > E_0$, $\beta < \beta_{\star}$ and $\epsilon' < \epsilon  \leq \epsilon_{\star}$.
+	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} > E_0$, $\beta < \beta_{\star}$ and $\epsilon' \leq \epsilon_{\star} < \epsilon$.
+	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $E_{\rm{max}} > E_0$, $\beta \geq \beta_{\star}$.
 \end{enumerate}
-Note that $\rm{(C1)} \rightarrow \rm{(C2)}$ is impossible because it would imply $\epsilon \leq \epsilon_{\rm{th}} \leq \epsilon' < \epsilon$, a contradiction.
+Note that $\rm{(C1)} \rightarrow \rm{(C2)}$ is impossible because it would imply $\epsilon \leq \epsilon_{\star} \leq \epsilon' < \epsilon$, a contradiction.
 
@@
 \begin{enumerate}
-	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} = E_0$ OR $E_{\rm{max}} > E_0$, $\beta < \beta_{\rm{th}}$ and $\epsilon' < \epsilon  \leq \epsilon_{\rm{th}}$.
+	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} = E_0$ OR $E_{\rm{max}} > E_0$, $\beta < \beta_{\star}$ and $\epsilon' < \epsilon  \leq \epsilon_{\star}$.
 
@@
 
-	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} > E_0$, $\beta < \beta_{\rm{th}}$ and $\epsilon' \leq \epsilon_{\rm{th}} < \epsilon$.
+	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} > E_0$, $\beta < \beta_{\star}$ and $\epsilon' \leq \epsilon_{\star} < \epsilon$.
 
@@
 \begin{equation}
-	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\left(\frac{1}{1-\frac{1}{3}\epsilon} \right)} + (E_{\rm{max}} - E_0)(\beta_{\rm{th}} - \beta)}{\beta (E_0 - F_\beta)},
-\end{equation}
-
-	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $E_{\rm{max}} > E_0$, $\beta \geq \beta_{\rm{th}}$.
+	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\left(\frac{1}{1-\frac{1}{3}\epsilon} \right)} + (E_{\rm{max}} - E_0)(\beta_{\star} - \beta)}{\beta (E_0 - F_\beta)},
+\end{equation}
+
+	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $E_{\rm{max}} > E_0$, $\beta \geq \beta_{\star}$.
 
@@
 
-Consider pure Strange state distillation at high temperatures, $\beta \leq \beta_{\rm{th}}$.
+Consider pure Strange state distillation at high temperatures, $\beta \leq \beta_{\star}$.
 Depending on the noise level of the initial state, we have either a $\rm{(C1)} \rightarrow \rm{(C1)}$ or a $\rm{(C2)} \rightarrow \rm{(C1)}$ scenario.
@@
 We compare $R(\beta)$ for different temperatures with the mana bound $R_{\rm{mana}}$ in~\cref{fig:distill_bounds_temp}.
-At every $\beta > 0$, the rates indicate a transition at $\epsilon_{\rm{th}}$.
+At every $\beta > 0$, the rates indicate a transition at $\epsilon_{\star}$.
 As $\beta$ increases, the rate becomes stricter.
@@
     \includegraphics[scale=0.5]{figs/distill_bounds_temp.pdf}
-    \caption{\textbf{Distillation rate with low noise in thermal fragments.} Distillation rates obtained by majorization $R(\beta)$ for low noise levels $\epsilon \leq \epsilon_{\rm{th}}$ are plotted for different temperatures $\beta^{-1}$ such that $0 \leq \beta \leq \beta_{\rm{th}}$.
+    \caption{\textbf{Distillation rate with low noise in thermal fragments.} Distillation rates obtained by majorization $R(\beta)$ for low noise levels $\epsilon \leq \epsilon_{\star}$ are plotted for different temperatures $\beta^{-1}$ such that $0 \leq \beta \leq \beta_{\star}$.
     The mana distillation rate $R_{\rm{mana}}$ is given for comparison.
@@
     As $\beta$ increases, the range of noise levels for which $R(\beta)$ is valid decreases and the distillation bound becomes stricter.
-\nick{it holds for $0 \leq \epsilon \leq \epsilon_*$, where $\epsilon_\star$ is the noise level ($ \leq \epsilon_{\rm{th}}$) at which the state conversion turns from $\rm{(C1)} \rightarrow \rm{(C1)}$ to $\rm{(C2)} \rightarrow \rm{(C1)}$.
+\nick{it holds for $0 \leq \epsilon \leq \epsilon_*$, where $\epsilon_\star$ is the noise level ($ \leq \epsilon_{\star}$) at which the state conversion turns from $\rm{(C1)} \rightarrow \rm{(C1)}$ to $\rm{(C2)} \rightarrow \rm{(C1)}$.
 Need to adjust~\cref{fig:distill_bounds_temp} accordingly}
@@
     \includegraphics[scale=0.5]{figs/distill_bounds_lowtemp.pdf}
-    \caption{\textbf{Distillation rate for low temperatures in thermal fragments.} Distillation rates obtained by majorization $R(\beta)$ in the temperature regime $\beta \geq \beta_{\rm{th}}$ are plotted for different temperatures $\beta^{-1}$.
+    \caption{\textbf{Distillation rate for low temperatures in thermal fragments.} Distillation rates obtained by majorization $R(\beta)$ in the temperature regime $\beta \geq \beta_{\star}$ are plotted for different temperatures $\beta^{-1}$.
     The mana distillation rate $R_{\rm{mana}}$ is given for comparison.
@@
 \begin{align}\label{eq:g1}
-	G_1(\noisys) &\coloneqq -\wn + 2\wp X + 3\wp Y + 3\wp Z \\
+	G_1(\noisys) &\coloneqq -v + 2u X + 3u Y + 3u Z \\
 	\begin{split}
@@
 	\begin{split}
-	G_1(\noisys|\gamma) &\coloneqq (3\Z) \big( -\wn e^{\beta E_0} + 2\wp e^{\beta E_0} X \\
-	&\hspace{41pt} + 3\wp e^{\beta E_1} Y + 3\wp e^{\beta E_2} Z \big)
+	G_1(\noisys|\gamma) &\coloneqq (3\Z) \big( -v e^{\beta E_0} + 2u e^{\beta E_0} X \\
+	&\hspace{41pt} + 3u e^{\beta E_1} Y + 3u e^{\beta E_2} Z \big)
 	\end{split}
@@
 
-For $\beta = 0$, $\epsilon_{\rm{th}} = 3/7$, so $\epsilon \leq \epsilon_{\rm{th}}$ always.
-In this case, $\widetilde{W}_{\rm{max}} = \wn^n e^{n\beta E_0}$ occuring in the region labelled by $(i,j,k) = (0,0,0)$.
+For $\beta = 0$, $\epsilon_{\star} = 3/7$, so $\epsilon \leq \epsilon_{\star}$ always.
+In this case, $\widetilde{W}_{\rm{max}} = v^n e^{n\beta E_0}$ occuring in the region labelled by $(i,j,k) = (0,0,0)$.
 
@@
 \begin{equation}
-	\beta \geq \beta_{\rm{th}} \coloneqq \frac{1}{E_{\rm{max}} - E_0} \ln2,
-\end{equation}
-$\epsilon_{\rm{th}} \leq 0$, so $\epsilon \geq \epsilon_{\rm{th}}$ always.
-
-For $0 < \beta < \beta_{\rm{th}}$, the order between energy eigenvalues matters.
+	\beta \geq \beta_{\star} \coloneqq \frac{1}{E_{\rm{max}} - E_0} \ln2,
+\end{equation}
+$\epsilon_{\star} \leq 0$, so $\epsilon \geq \epsilon_{\star}$ always.
+
+For $0 < \beta < \beta_{\star}$, the order between energy eigenvalues matters.
 \begin{itemize}
 \item If $E_{\rm{max}} = E_0$, only the first case is valid, since the noise constraint becomes $\epsilon \leq 3/7$.
-In this case, $\widetilde{W}_{\rm{max}} = \wn^n e^{n\beta E_0}$ occuring in the region labelled by $(i,j,k) = (0,0,0)$.
-\item If $E_{\rm{max}} = E_1$, then for low noise levels $\epsilon \leq \epsilon_{\rm{th}}$, $\widetilde{W}_{\rm{max}}  = \wn^n e^{n\beta E_0}$ occuring in the region labelled by $(i,j,k) = (0,0,0)$ and for high noise levels $\epsilon > \epsilon_{\rm{th}}$, $\widetilde{W}_{\rm{max}}  = \wp^n e^{n\beta E_1}$ occuring in the region labelled by $(i,j,k) = (0,n,0)$.
-\item If $E_{\rm{max}} = E_2$, then for low noise levels $\epsilon \leq \epsilon_{\rm{th}}$, $\widetilde{W}_{\rm{max}}  = \wn^n e^{n\beta E_0}$ occuring in the region labelled by $(i,j,k) = (0,0,0)$ and for high noise levels $\epsilon > \epsilon_{\rm{th}}$, $\widetilde{W}_{\rm{max}}  = \wp^n e^{n\beta E_2}$ occuring in the region labelled by $(i,j,k) = (0,0,n)$.
+In this case, $\widetilde{W}_{\rm{max}} = v^n e^{n\beta E_0}$ occuring in the region labelled by $(i,j,k) = (0,0,0)$.
+\item If $E_{\rm{max}} = E_1$, then for low noise levels $\epsilon \leq \epsilon_{\star}$, $\widetilde{W}_{\rm{max}}  = v^n e^{n\beta E_0}$ occuring in the region labelled by $(i,j,k) = (0,0,0)$ and for high noise levels $\epsilon > \epsilon_{\star}$, $\widetilde{W}_{\rm{max}}  = u^n e^{n\beta E_1}$ occuring in the region labelled by $(i,j,k) = (0,n,0)$.
+\item If $E_{\rm{max}} = E_2$, then for low noise levels $\epsilon \leq \epsilon_{\star}$, $\widetilde{W}_{\rm{max}}  = v^n e^{n\beta E_0}$ occuring in the region labelled by $(i,j,k) = (0,0,0)$ and for high noise levels $\epsilon > \epsilon_{\star}$, $\widetilde{W}_{\rm{max}}  = u^n e^{n\beta E_2}$ occuring in the region labelled by $(i,j,k) = (0,0,n)$.
 \end{itemize}
@@
     This is specific to the Strange state.
-    For high enough copies, these Lorenz curves surpass the unital noise threshold $\epsilon_{\rm{th}} = \frac{3}{4}$.
+    For high enough copies, these Lorenz curves surpass the unital noise threshold $\epsilon_{\star} = \frac{3}{4}$.
     }
@@
     \caption{\textbf{Norrell state distillation thresholds in stabilizer fragments.} Lorenz curve thresholds for the Strange state purifying process in~\cref{eq:sdist} with $\epsilon' = 0.05$.
-    For high enough copies, certain Lorenz curves surpass the unital noise threshold $\epsilon_{\rm{th}} = \frac{3}{4}$.
+    For high enough copies, certain Lorenz curves surpass the unital noise threshold $\epsilon_{\star} = \frac{3}{4}$.
     }

### 2021-02-15 magic_paper.tex
First attampt at fixing code

@@
 
-	Let $\tt$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ and $E \coloneqq \{x_1, \dots, x_\tt\}$ be their locations.
-
-	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_{\ii}) \geq \lc{\tau}{\sigma}(x_{\ii})$ for all $\ii =1,\dots,\tt$.
+	Let $n'$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ and $E \coloneqq \{x_1, \dots, x_n'\}$ be their locations.
+
+	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_{\ii}) \geq \lc{\tau}{\sigma}(x_{\ii})$ for all $\ii =1,\dots,n'$.
 \end{theorem}
@@
 \begin{equation}\label{eq:dist}
-    \rho(\epsilon)\too{n} = \left[ (1 - \epsilon) \rho + \epsilon \sigma \right]\too{n},
+    \rho(\epsilon)^{\otimes n} = \left[ (1 - \epsilon) \rho + \epsilon \sigma \right]^{\otimes n},
 \end{equation}
@@
 \begin{equation}
-		\rho(\epsilon)\too{n} \xrightarrow{\E \in \O_\sigma} \rho(\epsilon')\too{\tt},
-\end{equation}
-where it is converted into a $\tt$-copy, $\epsilon'$-noisy state, such that the number of copies has decreased ($\tt < n$), but the state is less noisy ($\epsilon' < \epsilon$).
+		\rho(\epsilon)^{\otimes n} \xrightarrow{\E \in \O_\sigma} \rho(\epsilon')^{\otimes n'},
+\end{equation}
+where it is converted into a $n'$-copy, $\epsilon'$-noisy state, such that the number of copies has decreased ($n' < n$), but the state is less noisy ($\epsilon' < \epsilon$).
 
@@
 	\begin{split}
-	\epsilon_{\star}(n, \tt, \epsilon', \sigma) \coloneqq &\sup{\{\epsilon:\ \lc{\rho(\epsilon)\too{n}}{\sigma}}(x) \geq \\
-	&{\lc{\rho(\epsilon')\too{\tt}}{\sigma}(x),\ x\in[0,1]\}}.
+	\epsilon_{\star}(n, n', \epsilon', \sigma) \coloneqq &\sup{\{\epsilon:\ \lc{\rho(\epsilon)^{\otimes n}}{\sigma}}(x) \geq \\
+	&{\lc{\rho(\epsilon')^{\otimes n'}}{\sigma}(x),\ x\in[0,1]\}}.
 	\end{split}
 \end{equation}
-The MSD process~(\ref{eq:dist}) is impossible for all $\epsilon > \epsilon_{\star}(n, \tt, \epsilon', \sigma)$.
+The MSD process~(\ref{eq:dist}) is impossible for all $\epsilon > \epsilon_{\star}(n, n', \epsilon', \sigma)$.
 
@@
 
-In general, the Wigner components of an $\NN$-copy state $\rho\too{\NN}$ can be calculated directly from $\W{\rho}$ by convolution of the distribution with itself,
-\begin{equation}
-	\W{\rho\too{\NN}} = \rm{W}_{\rho}\too{\NN},
+In general, the Wigner components of an $\NN$-copy state $\rho^{\otimes \NN}$ can be calculated directly from $\W{\rho}$ by convolution of the distribution with itself,
+\begin{equation}
+	\W{\rho^{\otimes \NN}} = \rm{W}_{\rho}^{\otimes \NN},
 \end{equation}
@@
 We would now like to study the constraints coming solely from majorization in the unital fragment. 
-We consider the problem of purifying $n$ copies of a noisy strange state $\noisysn$ into a smaller number of copies $\tt$ of a less noisy strange state $\noisys(\epsilon')\too{\tt}$, with $\epsilon' \le \epsilon$ and $\tt \leq n$.
+We consider the problem of purifying $n$ copies of a noisy strange state $\noisysn$ into a smaller number of copies $n'$ of a less noisy strange state $\noisys(\epsilon')^{\otimes n'}$, with $\epsilon' \le \epsilon$ and $n' \leq n$.
 Since the state $\frac{1}{3} \id$ is free, the interconversion problem is unaffected if we tensor in copies of it.
@@
 \begin{equation}\label{eq:sudist}
-	\noisys\too{n} \longrightarrow \noisys(\tt, \epsilon', n - n') \coloneqq  \noisys(\epsilon')\too{\tt} \otimes \left( \frac{1}{3}\id \right)\too{(n-\tt)},
-\end{equation}
-where all copies $n, \tt, n - \tt$ are even.
-Since the initial state can be written in the form $\noisys(n, \epsilon, 0)$, it suffices to construct the Lorenz curve $\lc{\noisys}{\id/3}(x)$ for the generic noisy strange state $\noisys(n, \epsilon ,\tt)$.
+	\noisys^{\otimes n} \longrightarrow \noisys(n', \epsilon', n - n') \coloneqq  \noisys(\epsilon')^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n-n')},
+\end{equation}
+where all copies $n, n', n - n'$ are even.
+Since the initial state can be written in the form $\noisys(n, \epsilon, 0)$, it suffices to construct the Lorenz curve $\lc{\noisys}{\id/3}(x)$ for the generic noisy strange state $\noisys(n, \epsilon ,n')$.
 This curve is defined at $9^n$ points between $0$ and $1$.
@@
 
-Here we focus on the case of Lorenz curves of even copies $n, \tt$ and low noise levels ($\epsilon \leq 3/7$).
+Here we focus on the case of Lorenz curves of even copies $n, n'$ and low noise levels ($\epsilon \leq 3/7$).
 The part of the curve on the LHS of its peak is constructed by the positive components of the state Wigner distribution that take values $w_\ii$, with associated multiplicities $\mlt_\ii$,
@@
 \end{align}
-where we use a three-index parametrisation for the coordinates, with $\ii$ the index of the elbow that follows, $\jj = 1,\dots,\mlt_\ii$ and $\kk=1,\dots,9^{2(n-\tt)}$.
-Therefore, for the initial state $\noisys\too{2n}$ we have
+where we use a three-index parametrisation for the coordinates, with $\ii$ the index of the elbow that follows, $\jj = 1,\dots,\mlt_\ii$ and $\kk=1,\dots,9^{2(n-n')}$.
+Therefore, for the initial state $\noisys^{\otimes 2n}$ we have
 \begin{equation}
@@
 with $\ii=0,\dots,n,\ \jj(\ii) = 1,\dots,8^{2\ii}\binom{2n}{2\ii}$ and $\kk = 1$.
-For the target state $\noisys(\epsilon')\too{2\tt} \otimes \left( \frac{1}{3}\id \right)\too{2(n-\tt)}$,
-\begin{equation}
-	p'_{\ii'\jj'\kk'} = \frac{\kk' + (\jj'-1)9^{2(n-\tt)}}{9^{2(n-\tt)} 8^{2\ii'}\binom{2\tt}{2\ii'}}
-\end{equation}
-with $\ii'=0,\dots,\tt,\ \jj'(\ii') = 1,\dots,8^{2\ii'}\binom{\tt}{2\ii'}$ and $\kk' = 1,\dots,9^{2(n-\tt)}$.
+For the target state $\noisys(\epsilon')^{\otimes 2n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes 2(n-n')}$,
+\begin{equation}
+	p'_{\ii'\jj'\kk'} = \frac{\kk' + (\jj'-1)9^{2(n-n')}}{9^{2(n-n')} 8^{2\ii'}\binom{2n'}{2\ii'}}
+\end{equation}
+with $\ii'=0,\dots,n',\ \jj'(\ii') = 1,\dots,8^{2\ii'}\binom{n'}{2\ii'}$ and $\kk' = 1,\dots,9^{2(n-n')}$.
 \fi
@@
 Lorenz curve comparison provides $9^n$ necessary constraints for the process~\cref{eq:sudist}.
-\cref{thm:elbows} shows that they can be reduced to $\tt$ independent constraints.
+\cref{thm:elbows} shows that they can be reduced to $n'$ independent constraints.
 However, in principle we can pick any location $x_\star \in [0,1]$ at which the Lorenz curves are defined and we then get a necessary distillation constraint, 
 \begin{equation}
-	\lc{\noisys(n, \epsilon, 0)}{\frac{\id}{3}}(x_\star) \geq \lc{\noisys(\tt, \epsilon', n-\tt)}{\frac{\id}{3}}(x_\star).
+	\lc{\noisys(n, \epsilon, 0)}{\frac{\id}{3}}(x_\star) \geq \lc{\noisys(n', \epsilon', n-n')}{\frac{\id}{3}}(x_\star).
 \end{equation}
@@
 
-The first elbow of the target state is located at $x'_0 = \frac{1}{9^{\tt}} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the first target state elbow,
+The first elbow of the target state is located at $x'_0 = \frac{1}{9^{n'}} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the first target state elbow,
 \begin{equation}\label{eq:constraint_deriv}
 	\begin{split}
-	L'_\star &= \frac{x_\star}{x'_0}L'_0 = \frac{1}{9^{n-\tt}}\left( \frac{5}{3} - \frac{8}{9}\epsilon'\ \right)^{\tt}\Phi_+\left(0;\tt,\frac{12-4\epsilon'}{15-8\epsilon'}\right) \\
-	&= \frac{(3-4\epsilon')^{\tt}}{9^{n}}.
+	L'_\star &= \frac{x_\star}{x'_0}L'_0 = \frac{1}{9^{n-n'}}\left( \frac{5}{3} - \frac{8}{9}\epsilon'\ \right)^{n'}\Phi_+\left(0;n',\frac{12-4\epsilon'}{15-8\epsilon'}\right) \\
+	&= \frac{(3-4\epsilon')^{n'}}{9^{n}}.
 	\end{split}
@@
 	\frac{n}{n'} &\geq \frac{\ln{(3-4\epsilon')}}{\ln{(3-4\epsilon)}}, \text{ or}\\
-	\epsilon &\leq \frac{3}{4} - \frac{1}{4}(3-4\epsilon')^{\frac{\tt}{n}}.
-\end{align}
-As an example, the process with $(n, \tt) = (12, 4)$ and $\epsilon' = 0.05$ yields $\epsilon \leq 0.398$.
+	\epsilon &\leq \frac{3}{4} - \frac{1}{4}(3-4\epsilon')^{\frac{n'}{n}}.
+\end{align}
+As an example, the process with $(n, n') = (12, 4)$ and $\epsilon' = 0.05$ yields $\epsilon \leq 0.398$.
 Numerical comparison of the curves with varying $\epsilon$ suggests that we require $\epsilon \leq 0.373$ for the process to be possible.
@@
 
-Given a state $\rho$ and a complete set of component-multiplicity pairs describing its Wigner distribution $\W{\rho}$, we now provide a method of computing the components (and multiplicities) of the $n$-copy distribution $\W{\rho}\too{n}$.
+Given a state $\rho$ and a complete set of component-multiplicity pairs describing its Wigner distribution $\W{\rho}$, we now provide a method of computing the components (and multiplicities) of the $n$-copy distribution $\W{\rho}^{\otimes n}$.
 \begin{lemma}\label{lem:ncopycomponents}
-	Let $W$ be a $d$-dimensional distribution defined by a complete set of component-multiplicity pairs $\{(w_i, m_i)\}_{i=1,\dots,D}$ with $D \leq d$ and consider the distribution $W\too{n}$ obtained by taking the Kronecker product $W \otimes \dots \otimes W$ between $n$ copies of $W$.
+	Let $W$ be a $d$-dimensional distribution defined by a complete set of component-multiplicity pairs $\{(w_i, m_i)\}_{i=1,\dots,D}$ with $D \leq d$ and consider the distribution $W^{\otimes n}$ obtained by taking the Kronecker product $W \otimes \dots \otimes W$ between $n$ copies of $W$.
 
@@
 
-	Then, $W\too{n}$ admits a complete set of component-multiplicity pairs $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$, where
+	Then, $W^{\otimes n}$ admits a complete set of component-multiplicity pairs $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$, where
 \begin{align}
@@
 
-	Assume that $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$ as given in~\cref{eq:M,eq:W} is a complete set of component-multiplicity pairs for the $n$-copy distribution $W\too{n}$.
-	By construction, the distribution $W\too{(n+1)} = W\too{n} \otimes W$ is multiplicative, so it admits the complete set of component multiplicity pairs
+	Assume that $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$ as given in~\cref{eq:M,eq:W} is a complete set of component-multiplicity pairs for the $n$-copy distribution $W^{\otimes n}$.
+	By construction, the distribution $W^{\otimes (n+1)} = W^{\otimes n} \otimes W$ is multiplicative, so it admits the complete set of component multiplicity pairs
 \begin{equation}
@@
 
-	Consider the component sum of the distribution $W\too{(n+1)}$,
+	Consider the component sum of the distribution $W^{\otimes (n+1)}$,
 \begin{align*}
@@
 \end{align*}
-which is the dimension of $W\too{(n+1)}$.
-
-Therefore, $\{ (W_{\bmq}, M_{\bmq}) \}_{\bmq \in C_D^{n+1}}$ is a complete set of component-multiplicity pairs for $W\too{n}$, completing the proof.
+which is the dimension of $W^{\otimes (n+1)}$.
+
+Therefore, $\{ (W_{\bmq}, M_{\bmq}) \}_{\bmq \in C_D^{n+1}}$ is a complete set of component-multiplicity pairs for $W^{\otimes n}$, completing the proof.
 \end{proof}
@@
 (If it does, our analysis is still correct, but it simply could be improved).}
+\nick{This is in general true, will check if in our case it makes a difference}
 
@@
 \begin{equation}\label{eq:msd_thermal}
-		\noisys(\epsilon)\too{n} \xrightarrow{\E \in \O_{\gamma_\beta}} \noisys(\epsilon')\too{\tt} \otimes \gamma_\beta\too{(n-\tt)},
+		\noisys(\epsilon)^{\otimes n} \xrightarrow{\E \in \O_{\gamma_\beta}} \noisys(\epsilon')^{\otimes n'} \otimes \gamma_\beta^{\otimes (n-n')},
 \end{equation}
@@
 
-Our aim is to obtain a distillation bound for~\cref{eq:msd_thermal} which depends on variables $n, \tt, \epsilon, \epsilon'$ as well as $\beta$.
+Our aim is to obtain a distillation bound for~\cref{eq:msd_thermal} which depends on variables $n, n', \epsilon, \epsilon'$ as well as $\beta$.
 In the analysis that follows, we drop obvious variable dependencies for clarity.
@@
 where $0 \leq i,j,k \leq n$ and $\alpha \coloneqq i+j+k \leq n$.
-Notice that for $0 \leq \epsilon \leq 3/7$, we have $v \geq u$. We assume that $n$ is even, ans so we then need the sum $\alpha = i+j+k$ to be even, so that the expression is positive.
-
-%Given an even value $\alpha$ for the sum, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_0}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
-%Hence, we have \ddd{Why did the $\Z$ term disappear?}
-%\begin{align}
-%	\bmw(\noisys | \gamma)_{\rm{max}}
-%&=\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ v^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta \alpha E_{\rm{max}}} \Big\}}  \nonumber\\
-%	&= v^n e^{n\beta E_0}\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}
-%\end{align}
-%If the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than $1$ then the maximum occurs at $\alpha=0$, and otherwise the maximum occurs at $\alpha = n$.
-%The threshold value of $1$ is achieved for this term when the noise level $\epsilon$ is equal to
-%\begin{equation}
-%	\epsilon_{\star}(\beta) := 3 - \dfrac{18}{8-e^{(E_{\rm{max}} - E_0)\beta}}.
-%	%\beta \leq \frac{1}{E_{\rm{max}} - E_0}\ln{\left( 8-\frac{18}{3-\epsilon} \right)}
-%\end{equation}
-%For the case $E_{\rm{max}} = E_0$ this threshold is constant in temperature and given by Since $ E_{\rm max} - E_0 \ge 0$ the threshold $\epsilon_{\star}$ is a decreasing function of $\beta$, and it achieves its maximum value $3/7$ for $(E_{\rm{max}} - E_0)\beta = 0$, and a value equal to $0$ for
-%\begin{equation}
-%	\beta_{\star} \coloneqq \frac{1}{E_{\rm{max}} - E_0} \ln2.
-%\end{equation}
-%For $\beta > \beta_{\star}$, $\epsilon_{\star}$ is negative, meaning that the noise level $\epsilon$ will always be higher than the threshold.
-%We highlight that the threshold becomes $0$ when the difference between the maximum energy level and the level associated with the state negativity is equal to the energy extracted from a single particle Szilard's engine,
-%\begin{equation}
-%	E_{\rm{max}} - E_0 = kT_{\star} \ln2.
-%\end{equation}
-%
-%The maximum slope \ddd{``maximum slope??''} finally is
-%\begin{equation}
-%\bmw(\noisys | \gamma)_{\rm{max}} =
-%	\begin{cases}
-%		v^n e^{n\beta E_0}, &\epsilon \leq \epsilon_{\star},\ \hspace{30pt}\rm{(C1)}	\\
-%		u^n e^{n\beta E_{\rm{max}}}, &\epsilon > \epsilon_{\star}.\ \hspace{32pt}\rm{(C2)} 
-%	\end{cases}
-%\end{equation}
-%Case $\rm{(C1)}$ corresponds to $(i,j,k) = (0,0,0)$, while case $\rm{(C2)}$ corresponds to the  the conditions 
-%\begin{equation}
-%	(i,j,k) = 
-%	\begin{cases}
-%	(0,n,0), &\text{if } E_{\rm{max}} = E_1, \\
-%	(0,0,n), &\text{if } E_{\rm{max}} = E_2.
-%	\end{cases}
-%\end{equation}
-%Note that if $E_{\rm{max}} = E_0$, we get $\epsilon_{\star} = 3/7$ and $\rm{(C1)}$ holds for all $\epsilon$ and $\beta$.
-%Assuming $E_{\rm{max}} > E_0$, we get the cases:
-%\begin{itemize}
-%	\item $\beta = 0$. Then, $\epsilon_{\star} = 3/7$ and $\rm{(C1)}$ holds for all noise levels $\epsilon$.
-%	This is the unital fragment.
-%	\item $0 < \beta < \beta_{\star}$. Then, $0 < \epsilon_{\star} < 3/7$ and $\rm{(C1)}$ holds for $\epsilon \leq \epsilon_{\star}$, while $\rm{(C2)}$ holds for $\epsilon \geq \epsilon_{\star}$.
-%	\item $\beta \geq \beta_{\star}$. Then, $ \epsilon_{\star} \leq 0$ and $\rm{(C2)}$ holds for all $\epsilon$.
-%\end{itemize}
+Notice that for $0 \leq \epsilon \leq 3/7$, we have $v \geq u$. 
+We assume that $n$ is even, so we then need the sum $\alpha = i+j+k$ to be even, so that the expression is positive.
+
+Given an even value $\alpha$ for the sum, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_0}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
+Hence, we have
+\begin{align}
+	&\bmw(\noisys | \gamma)_{\rm{max}} = \nonumber\\
+	&(3\Z)^{n} \max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ v^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta \alpha E_{\rm{max}}} \Big\}} =  \nonumber\\
+	&(3\Z)^{n} v^n e^{n\beta E_0}\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}
+\end{align}
+If the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than $1$ then the maximum occurs at $\alpha=0$, and otherwise the maximum occurs at $\alpha = n$.
+The threshold value of $1$ is achieved for this term when the noise level $\epsilon$ is equal to
+\begin{equation}
+	\epsilon_{\star}(\beta) := 3 - \dfrac{18}{8-e^{(E_{\rm{max}} - E_0)\beta}}.
+	%\beta \leq \frac{1}{E_{\rm{max}} - E_0}\ln{\left( 8-\frac{18}{3-\epsilon} \right)}
+\end{equation}
+For the case $E_{\rm{max}} = E_0$ this threshold is constant in temperature and given by Since $ E_{\rm max} - E_0 \ge 0$ the threshold $\epsilon_{\star}$ is a decreasing function of $\beta$, and it achieves its maximum value $3/7$ for $(E_{\rm{max}} - E_0)\beta = 0$, and a value equal to $0$ for
+\begin{equation}
+	\beta_{\star} \coloneqq \frac{1}{E_{\rm{max}} - E_0} \ln2.
+\end{equation}
+For $\beta > \beta_{\star}$, $\epsilon_{\star}$ is negative, meaning that the noise level $\epsilon$ will always be higher than the threshold.
+We highlight that the threshold becomes $0$ when the difference between the maximum energy level and the level associated with the state negativity is equal to the energy extracted from a single particle Szilard's engine,
+\begin{equation}
+	E_{\rm{max}} - E_0 = kT_{\star} \ln2.
+\end{equation}
+
+The maximum value of the Gibbs-rescaled distribution finally is
+\begin{equation}
+\bmw(\noisys | \gamma)_{\rm{max}} =
+	\begin{cases}
+		(3\Z)^{n} v^n e^{n\beta E_0}, &\epsilon \leq \epsilon_{\star},\ \hspace{30pt}\rm{(C1)}	\\
+		(3\Z)^{n} u^n e^{n\beta E_{\rm{max}}}, &\epsilon > \epsilon_{\star}.\ \hspace{32pt}\rm{(C2)} 
+	\end{cases}
+\end{equation}
+Case $\rm{(C1)}$ corresponds to $(i,j,k) = (0,0,0)$, while case $\rm{(C2)}$ corresponds to the  the conditions 
+\begin{equation}
+	(i,j,k) = 
+	\begin{cases}
+	(0,n,0), &\text{if } E_{\rm{max}} = E_1, \\
+	(0,0,n), &\text{if } E_{\rm{max}} = E_2.
+	\end{cases}
+\end{equation}
+Note that if $E_{\rm{max}} = E_0$, we get $\epsilon_{\star} = 3/7$ and $\rm{(C1)}$ holds for all $\epsilon$ and $\beta$.
+Assuming $E_{\rm{max}} > E_0$, we get the cases:
+\begin{itemize}
+	\item $\beta = 0$. Then, $\epsilon_{\star} = 3/7$ and $\rm{(C1)}$ holds for all noise levels $\epsilon$.
+	This is the unital fragment.
+	\item $0 < \beta < \beta_{\star}$. Then, $0 < \epsilon_{\star} < 3/7$ and $\rm{(C1)}$ holds for $\epsilon \leq \epsilon_{\star}$, while $\rm{(C2)}$ holds for $\epsilon \geq \epsilon_{\star}$.
+	\item $\beta \geq \beta_{\star}$. Then, $ \epsilon_{\star} \leq 0$ and $\rm{(C2)}$ holds for all $\epsilon$.
+\end{itemize}
 
@@
 \begin{equation*}
-		\noisys(\epsilon)\too{n} \xrightarrow{\E \in \O_{\gamma_\beta}} \noisys(\epsilon')\too{\tt} \otimes \gamma_\beta\too{(n-\tt)},
+		\noisys(\epsilon)^{\otimes n} \xrightarrow{\E \in \O_{\gamma_\beta}} \noisys(\epsilon')^{\otimes n'} \otimes \gamma_\beta^{\otimes (n-n')},
 \end{equation*}
@@
 \begin{equation}\label{eq:first_elbow_constraint}
-	\lc{\noisys(\epsilon)\too{n}}{\gamma_\beta}(x_\star) \geq \lc{\noisys(\epsilon')\too{\tt}}{\gamma_\beta}(x_\star).
+	\lc{\noisys(\epsilon)^{\otimes n}}{\gamma_\beta}(x_\star) \geq \lc{\noisys(\epsilon')^{\otimes n'}}{\gamma_\beta}(x_\star).
 \end{equation}
@@
 	\begin{align*}
-		x_0 &= \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^n = \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n-\tt} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{\tt} \\
-		&< \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{\tt} = x_0'		
+		x_0 &= \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^n = \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n-n'} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} \\
+		&< \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} = x_0'		
 	\end{align*}
@@
 	\begin{align*}
-		&\Z_\beta^{n-\tt} > (e^{-\beta E_{\rm{max}}})^{n-\tt} = e^{-\beta (n-\tt) E_{\rm{max}}}, \text{ so} \\
-		x_0 &= \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^n = \dfrac{e^{-\beta(n E_{\rm{max}} - \tt E_0)}}{\Z_\beta^{n-\tt}} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{\tt} \\
-		&< \dfrac{e^{-\beta(n E_{\rm{max}} - \tt E_0)}}{e^{-\beta (n-\tt) E_{\rm{max}}}} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{\tt} \\
-		&= e^{-\beta \tt (E_{\rm{max}} - E_0)} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{\tt} \\
-		&< \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{\tt} = x_0'.
+		&\Z_\beta^{n-n'} > (e^{-\beta E_{\rm{max}}})^{n-n'} = e^{-\beta (n-n') E_{\rm{max}}}, \text{ so} \\
+		x_0 &= \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^n = \dfrac{e^{-\beta(n E_{\rm{max}} - n' E_0)}}{\Z_\beta^{n-n'}} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} \\
+		&< \dfrac{e^{-\beta(n E_{\rm{max}} - n' E_0)}}{e^{-\beta (n-n') E_{\rm{max}}}} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} \\
+		&= e^{-\beta n' (E_{\rm{max}} - E_0)} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} \\
+		&< \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} = x_0'.
 	\end{align*}
@@
 	\begin{align*}
-		x_0 &= \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^n = \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^{n-\tt} \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^{\tt} \\
-		&\leq \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^{\tt} = x_0'	
+		x_0 &= \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^n = \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^{n-n'} \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^{n'} \\
+		&\leq \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^{n'} = x_0'	
 	\end{align*}
@@
 	\frac{n}{n'} &\geq \frac{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F_\beta)}{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_0 - F_\beta)}, \text{ or} \\
-	\epsilon &\leq \frac{3}{4} - \frac{3}{4} \left( 1 - \frac{4}{3}\epsilon' \right)^{\frac{\tt}{n}} \left( \frac{e^{-\beta E_0}}{\Z_\beta} \right)^{1 - \frac{\tt}{n}}	
+	\epsilon &\leq \frac{3}{4} - \frac{3}{4} \left( 1 - \frac{4}{3}\epsilon' \right)^{\frac{n'}{n}} \left( \frac{e^{-\beta E_0}}{\Z_\beta} \right)^{1 - \frac{n'}{n}}	
 \end{align}
@@
 	\frac{n}{n'} &\geq \frac{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F_\beta)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F_\beta)}, \text{ or} \\
-	\epsilon &\leq 3 - 6 \left( 1 - \frac{4}{3}\epsilon' \right)^{\frac{\tt}{n}} \frac{e^{-\beta E_{\rm{max}}} e^{\frac{\tt}{n}\beta E_0}}{\Z_\beta^{1-\frac{\tt}{n}}}	
+	\epsilon &\leq 3 - 6 \left( 1 - \frac{4}{3}\epsilon' \right)^{\frac{n'}{n}} \frac{e^{-\beta E_{\rm{max}}} e^{\frac{n'}{n}\beta E_0}}{\Z_\beta^{1-\frac{n'}{n}}}	
 \end{align}
@@
 	\frac{n}{n'} &\geq \frac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F_\beta)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F_\beta)}, \text{ or} \\
-	\epsilon &\leq 3 - 6 \left( \frac{1}{2} - \frac{1}{6}\epsilon' \right)^{\frac{\tt}{n}} \left( \frac{e^{-\beta E_{\rm{max}}}}{\Z_\beta} \right)^{1 - \frac{\tt}{n}}	
+	\epsilon &\leq 3 - 6 \left( \frac{1}{2} - \frac{1}{6}\epsilon' \right)^{\frac{n'}{n}} \left( \frac{e^{-\beta E_{\rm{max}}}}{\Z_\beta} \right)^{1 - \frac{n'}{n}}	
 \end{align}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \null\newpage
@@
 
-\subsection{OLD Magic in thermal fragments}
-
-which naturally splits the phase space $\pd[3]$ into four regions where the ``slope'', i.e. the value of the Gibbs-rescaled distribution, is different.
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.5]{figs/pd_split_thermal.pdf}
-    \caption{\textbf{Qutrit phase space regions with different Gibbs-rescaled values.}
-    The slope is positive in regions $X,Y,Z$ and negative in region $1$.
-    It attains a unique value in each region.
-    The values and multiplicites can be read off as the term coefficients in~\cref{eq:g1}.
-    }
-    \label{fig:pd_split_thermal}
-\end{figure}
-In each region, we want to keep track of the number of phase space points it contains (i.e.
-the multiplicity) and the corresponding values of the Wigner distributions $\W{\noisys}, \W{\gamma}$ and the Gibbs-rescaled distribution $\widetilde{\rm{W}}_1$.
-To this end, we label the four regions using variables $1,X,Y,Z$ as illustrated in~\cref{fig:pd_split_thermal}, and we write down the expressions:
-\begin{align}\label{eq:g1}
-	G_1(\noisys) &\coloneqq -v + 2u X + 3u Y + 3u Z \\
-	\begin{split}
-	G_1(\gamma) &\coloneqq (3\Z)^{-1} \big( e^{-\beta E_0} + 2e^{-\beta E_0} X \\
-	&\hspace{49pt} + 3e^{-\beta E_1} Y + 3e^{-\beta E_2} Z \big) 
-	\end{split}
-	\\
-	\begin{split}
-	G_1(\noisys|\gamma) &\coloneqq (3\Z) \big( -v e^{\beta E_0} + 2u e^{\beta E_0} X \\
-	&\hspace{41pt} + 3u e^{\beta E_1} Y + 3u e^{\beta E_2} Z \big)
-	\end{split}
-\end{align}
-The coefficient of each term reads as the multiplicity times the value of the desired distribution in the corresponding region.
-Note that the negative Strange state Wigner component pairs with energy eigenvalue $E_0$ in region $1$.
-
-For $\beta = 0$, $\epsilon_{\star} = 3/7$, so $\epsilon \leq \epsilon_{\star}$ always.
-In this case, $\widetilde{W}_{\rm{max}} = v^n e^{n\beta E_0}$ occuring in the region labelled by $(i,j,k) = (0,0,0)$.
-
-For 	
-\begin{equation}
-	\beta \geq \beta_{\star} \coloneqq \frac{1}{E_{\rm{max}} - E_0} \ln2,
-\end{equation}
-$\epsilon_{\star} \leq 0$, so $\epsilon \geq \epsilon_{\star}$ always.
-
-For $0 < \beta < \beta_{\star}$, the order between energy eigenvalues matters.
-\begin{itemize}
-\item If $E_{\rm{max}} = E_0$, only the first case is valid, since the noise constraint becomes $\epsilon \leq 3/7$.
-In this case, $\widetilde{W}_{\rm{max}} = v^n e^{n\beta E_0}$ occuring in the region labelled by $(i,j,k) = (0,0,0)$.
-\item If $E_{\rm{max}} = E_1$, then for low noise levels $\epsilon \leq \epsilon_{\star}$, $\widetilde{W}_{\rm{max}}  = v^n e^{n\beta E_0}$ occuring in the region labelled by $(i,j,k) = (0,0,0)$ and for high noise levels $\epsilon > \epsilon_{\star}$, $\widetilde{W}_{\rm{max}}  = u^n e^{n\beta E_1}$ occuring in the region labelled by $(i,j,k) = (0,n,0)$.
-\item If $E_{\rm{max}} = E_2$, then for low noise levels $\epsilon \leq \epsilon_{\star}$, $\widetilde{W}_{\rm{max}}  = v^n e^{n\beta E_0}$ occuring in the region labelled by $(i,j,k) = (0,0,0)$ and for high noise levels $\epsilon > \epsilon_{\star}$, $\widetilde{W}_{\rm{max}}  = u^n e^{n\beta E_2}$ occuring in the region labelled by $(i,j,k) = (0,0,n)$.
-\end{itemize}
-
-Consider a system with Hamiltonian $H$ and in contact with a thermal bath of temperature $\beta^{-1}$.
-We denote the thermal state at that temperature by $\gamma \equiv \gamma_\beta = \frac{e^{-\beta H}}{Z_\beta}$, where $Z \equiv Z_\beta = \tr[e^{-\beta H}]$.
-As long as the thermal state is free, it is associated with a set of free, thermal operations and the dynamics of the system can be described within the fragment $\O_{\gamma}$.
-
-We want to focus on qutrit interconversions and extract a temperature-dependent distillation bound.
-To this end, consider the qutrit Hamiltonian
-\begin{equation}
-	H = E_0 \ketbra{0} + E_1 \ketbra{1} + E_2 \ketbra{2},
-\end{equation}
-where the eigenbasis coincides with the computational basis.
-The thermal state associated with this Hamiltonian is
-\begin{align}
-	\gamma &= \frac{e^{-\beta H}}{Z} = \frac{e^{-\beta \sum\limits_{k=0}^2 E_k \ketbra{k}}}{Z} \\
-	&= \frac{e^{-\beta E_0}}{Z}\ketbra{0} + \frac{e^{-\beta E_1}}{Z}\ketbra{1} + \frac{e^{-\beta E_2}}{Z}\ketbra{2},
-\end{align}
-where $Z = e^{-\beta E_0} + e^{-\beta E_1} + e^{-\beta E_2}$.
-
-The Wigner distribution of state $\gamma$ can be seen as the ensemble average of the distributions of the computational basis states,
-\begin{align}
-	\W[\bmx]{\gamma} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{Z}\W[\bmx]{\ketbra{k}} \\
-	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{Z} \delta_{x_0, k} = \frac{e^{-\beta E_{x_0}}}{dZ},
-\end{align}
-for all $\bmx \in \pd$. 
-All Wigner components are strictly positive, therefore the pre-order $\prec_{\gamma_\beta}$ is well defined.
-
-Consider the simple energy spectrum 
-\begin{equation}
-	(E_0, E_1, E_2) = (1,0,0).
-\end{equation}
-Then, $Z = 2 + e^{-\beta}$.
-Furthermore, for clarity, let $\chi \coloneqq \frac{1}{6}-\frac{1}{18}\epsilon$ be the positive and $-\nu \coloneqq -\frac{1}{3} + \frac{4}{9}\epsilon$ the negative Wigner components of $\noisys(\epsilon)$.
-The 1-copy Wigner distributions in this scenario are depicted in~\cref{tab:thermal_w}.
-\begin{table}[h]
-  \def\arraystretch{2}
-  \centering
-  \begin{tabular}{c|c|c|c}
-    $\bmx = (x_0, x_1)$ & $W_{\noisys}(\bmx)$ & $W_{\gamma}(\bmx)$ & $\tilde{\bmw}$ \\
-    \hline
-    \makecell{$(0,0)$ \\ \vdots \\ $(0,2)$} & $\displaystyle \chi$ & $\displaystyle \frac{e^{-\beta}}{3Z}$ & $\displaystyle 3Z \chi e^{\beta}$ \\
-    \hline
-    \makecell{$(1,0)$ \\ $\vdots$ \\ $(2,1)$} & $\displaystyle \chi$ & $\displaystyle \frac{1}{3Z}$ & $\displaystyle 3Z \chi$ \\
-    \hline
-    $(2,2)$ & $\displaystyle -\nu$ & $\displaystyle \frac{1}{3Z}$ & $\displaystyle 3Z (-\nu)$ \\
-    \hline
-  \end{tabular}
-  \caption{Wigner components $W_{\gamma}(\bmx)$, $W_{\noisys}(\bmx)$ and the associated slope $\widetilde{\bmw}$ listed in order of decreasing slope (holds for all temperatures $\beta^{-1}$).}
-  \label{tab:thermal_w}
-\end{table}
-
-To construct the 1-copy Lorenz curve $\lc{\noisys(\epsilon)}{\gamma_\beta}$, we simply add up the Wigner components in order of decreasing slope $\widetilde{\bmw} \coloneqq W_{\noisys}(\bmx)/W_{\gamma_\beta}(\bmx)$.
-The first elbow of the 1-copy Lorenz curve is
-\begin{equation}
-	(x_0, L_0) = \left( \frac{e^{-\beta}}{Z}, 3\chi \right).
-\end{equation}
-
-As illustrated in~\cref{tab:thermal_w}, the phase space can be split into three regions, based on the different values of the slope $\widetilde{\bmw}$.
-As more copies ($n>1$) are considered, the system is described by higher dimensional phase spaces which contains more regions of different slope.
-Notice that the slope of the $n$-copy Lorenz curve can be expressed as a self-convolution of the 1-copy Lorenz curve slope $n$ times,
-\begin{equation}
-	\widetilde{\bmw\too{n}} = \frac{\W{\noisys\too{n}}(\bmx)}{\W{\gamma\too{n}}(\bmx)} = \left( \frac{\W{\noisys}(\bmx)}{\W{\gamma}(\bmx)} \right)\too{n} = \widetilde{\bmw}\too{n}.
-\end{equation}
-Therefore, the regions of different slope in an $n$-copy phase space are generated by the 1-copy phase space regions.
-The process is outlined below.
-
-According to~\cref{def:lc}, to construct the $n$-copy Lorenz curve, we need to evaluate the components of $\widetilde{\bmw\too{n}}$, sort them in decreasing order and take the cumulative sum of the corresponding components $\W{\noisys\too{n}}(\bmx)$ and $\W{\gamma\too{n}}(\bmx)$.
-
-To evaluate the distinct components and multiplicities of $\widetilde{\bmw\too{n}}, \W{\noisys\too{n}}(\bmx), \W{\gamma\too{n}}(\bmx)$, we can construct trinomial generating functions.
-In particular, for a general $n$-copy $\epsilon$-noisy Strange state in a $\gamma_\beta$-fragment, we can use~\cref{tab:thermal_w} to construct the following generating functions,
-\begin{align}
-	&G(X,Y; \noisys) \coloneqq (-\nu + 5\chi X + 3\chi Y)^n \nonumber\\
-	&= \sum\limits_{\substack{i,j = 0,\dots,n \\ i+j \leq n}} m_{ij} \big[(-\nu)^{n-i-j} \chi^{i+j} \big] X^i Y^j, \\
-	&G(X,Y; \gamma) \coloneqq \left( \frac{1}{3Z} + 5\frac{1}{3Z} X + 3 \frac{e^{-\beta}}{3Z} Y \right)^n \nonumber\\
-	&= (3Z)^{-n} \sum\limits_{\substack{i,j = 0,\dots,n \\ i+j \leq n}} m_{ij} e^{-j\beta} X^i Y^j, \\
-	&G(X,Y; \widetilde{\bmw}) \coloneqq \Big( 3Z(-\nu) + 5(3Z\chi) X + 3(3Z\chi) e^\beta Y \Big)^n \nonumber\\
-	&= (3Z)^n \sum\limits_{\substack{i,j = 0,\dots,n \\ i+j \leq n}} m_{ij} \big[(-\nu)^{n-i-j} \chi^{i+j} e^{j\beta} \big] X^i Y^j,
-\end{align}
-where the $(i,j)$-th term multiplicity $m_{ij}$ is given by
-\begin{equation}
-	m_{ij} \coloneqq \frac{n!}{i!j!(n-i-j)!} 5^i 3^j.
-\end{equation}
-There are $\frac{(n+1)(n+2)}{2}$ distinct $X^i Y^j$ terms. 
-Each term $X^i Y^j$ represents a phase space region with different slope. 
-Consider the generating function $G(X,Y;\widetilde{\bmw})$ for the slope. 
-The coefficient in front of the term is a product of the multiplicity $m_{ij}$ and the value of the slope in the region, $(-\nu)^{n-i-j} \chi^{i+j} e^{j\beta}$.
-To find the value of the Wigner components $\W{\noisys\too{n}}(\bmx), \W{\gamma\too{n}}(\bmx)$ in this phase space region, we simply read the coefficients of the term $X^i Y^j$ in functions $G(X,Y; \noisys), G(X,Y; \gamma)$ respectively.
-
-For example, the 2-copy case gives
-\begin{equation}
-	\begin{split}
-	&G(\widetilde{\bmw\too{2}}; X,Y) = 9Z^2 \Big( 1(\nu^2) + 10(-\nu \chi)X + 6(-\nu \chi e^\beta) Y + \\
-	&30 (\chi^2 e^\beta) XY + 25(\chi^2)X^2 + 9(\chi^2 e^{2\beta})Y^2 \Big).
-	\end{split}
-\end{equation}
-The expression contains six different terms corresponding to the different phase space regions.
-Each term (e.g.
-$X$) has a coefficient that consists of the multiplicity, i.e.
-the number of phase space points contained in the corresponding region, (e.g.
-$10$) and the value of the slope at the points of the region (e.g.
-$9Z^2(-\nu \chi)$).
-
-In order to calculate the coordinates of the first elbow of the $n$-copy Lorenz curve $\lc{\noisys(\epsilon)}{\gamma_\beta}$, we need to find the highest slope value,
-\begin{equation}
-	\widetilde{\bmw}_{\rm{max}} = \max{\{ (-\nu)^{n-i-j} \chi^{i+j} e^{j\beta} \}_{i,j}},
-\end{equation}
-where we have ignored the positive prefactor $(3Z)^n$.
-We can narrow down the maximisation, by noticing that we always have $\chi e^\beta \geq \chi$, so the maximum is achieved for $i=0$ and we can maximise over $\{ (-\nu)^{n-j} \chi^{j} e^{j\beta} \}$.
-Then, notice that either $\nu \geq \chi e^{\beta}$ or $\nu < \chi e^{\beta}$, so, for even $n$, the maximum can only be achieved for $j\in\{0,n\}$ and
-\begin{equation}
-	\widetilde{\bmw}_{\rm{max}} = 
-	\begin{cases}
-		\nu^n, &\nu \geq \chi e^{\beta}, \\
-		\chi^n e^{n\beta}, &\nu < \chi e^{\beta}.
-	\end{cases}
-\end{equation}
-By expanding $\nu, \chi$, this expression can be equivalently recast in terms of a temperature regime,
-\begin{equation}\label{eq:temp_regime}
-	\widetilde{\bmw}_{\rm{max}} = 
-	\begin{cases}
-		\nu^n, &\beta \leq \ln{\left(8-\frac{18}{3-\epsilon}\right)}, \\
-		\chi^n e^{n\beta}, &\beta > \ln{\left(8-\frac{18}{3-\epsilon}\right)}.
-	\end{cases}
-\end{equation}
-The values of the slope correspond to terms $X^0Y^0 = 1$ and $X^0Y^n = Y^n$ respectively, so the Lorenz curve coordinates are
-\begin{equation}
-	(x_0, L_0) = 
-	\begin{cases}
-		\Big( (3Z)^{-n}, \nu^n \Big), &\beta \leq \ln{\left(8-\frac{18}{3-\epsilon}\right)}, \\
-		\Big( \frac{e^{-n\beta}}{Z^n}, 3^n\chi^n \Big), &\beta > \ln{\left(8-\frac{18}{3-\epsilon}\right)}.
-	\end{cases}
-\end{equation}
-
-Note that as $\beta$ tends to $0$, we get the first elbow coordinates that we found for the unital fragment, $(9^{-n}, \nu^n)$.
-We can also invert the temperature constraint into a noise constraint for the state,
-\begin{equation}\label{eq:tempregime}
-	\beta \leq \ln{\left(8-\frac{18}{3-\epsilon}\right)} \Leftrightarrow \epsilon \leq 3 - \frac{18}{8-e^{\beta}}.
-\end{equation}
-
-Consider the Strange state distillation process
-\begin{equation}\label{eq:stdist}
-	\noisys\too{n} \longrightarrow \noisys(\tt, \epsilon', n - n') \coloneqq  \noisys(\epsilon')\too{\tt} \otimes \left( \frac{1}{3}\id \right)\too{(n-\tt)},
-\end{equation}
-in the thermal fragment $\O_{\gamma_\beta}$.
-We are now in a position to extract a distillation bound that takes the temperature $\beta^{-1}$ into account in an analogous method as the one used for the unital fragment distillation bound.
-
-We choose the temperature regime in~\cref{eq:tempregime} and we pick the location $x_\star = x_0 = (3Z)^{-n} = (3(2+e^{-\beta}))^{-n}$ of the first elbow of the initial state $\noisys(n, \epsilon, 0)$ and write down the necessary distillation constraint,
-\begin{equation}
-	\lc{\noisys(n, \epsilon, 0)}{\gamma_\beta}(x_\star) \geq \lc{\noisys(\tt, \epsilon', n-\tt)}{\gamma_\beta}(x_\star).
-\end{equation}
-
-The initial state Lorenz curve coordinate at this location is $L_\star = L_0 = (1/3 - 4\epsilon/9)^{n}$.
-
-The first elbow of the target state is located at $x'_0 = (3Z)^{-\tt} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the first target state elbow,
-\begin{equation}\label{eq:constraint_deriv_temp}
-	L'_\star = \frac{x_\star}{x'_0}L'_0 = (3(2+e^{-\beta}))^{\tt-n} \left( \frac{1}{3} - \frac{4}{9} \epsilon' \right)^{\tt}.
-\end{equation}
-The process in~\cref{eq:stdist} is therefore possible only if $L_\star \geq L'_\star$ or equivalently,
-\begin{align}
-	\frac{n}{n'} \geq \frac{\ln{\Big[ (1-\frac{4}{3}\epsilon')(2+e^{-\beta}) \Big]}}{\ln{\Big[ (1-\frac{4}{3}\epsilon)(2+e^{-\beta}) \Big]}},
-\end{align}
-with $\tt \leq n$ and $\epsilon' \leq \epsilon \leq 3 - 18/\big(8-e^{\beta}\big)$.
-
-Moreover, for the problem of distilling pure magic states where $\epsilon'=0$ we obtain an upper bound on the unital fragment distillation rate $R=n'/n$ given by
-\begin{equation}
-	R \leq R(\beta) \coloneqq \frac{\ln{\Big[ (1-\frac{4}{3}\epsilon)(2+e^{-\beta}) \Big]}}{\ln{(2+e^{-\beta})}},
-\end{equation}
-which holds for all finite $n$. 
-We compare $R(\beta)$ with the mana bound $R_{\rm{mana}}$ for different values of $\beta$ in~\cref{fig:distill_bounds_temp}.
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.5]{figs/distill_bounds_temp.pdf}
-    \caption{\textbf{Distillation rate in thermal fragments.} Distillation rates obtained by mana and majorization are plotted for $\epsilon' = 0$, up to noise levels $\epsilon_{\rm{max}} = 8-\frac{18}{3-e^{\beta}}$.
-    As $\beta$ increases, the range of noise levels that our bound is valid in decreases and the distillation bound becomes stricter.
-    }
-    \label{fig:distill_bounds_temp}
-\end{figure}
-
-\subsubsection{General case}
-
-Let's return to the general qutrit Hamiltonian
-\begin{equation}\label{eq:h_thermal_general}
-	H = E_0 \ketbra{0} + E_1 \ketbra{1} + E_2 \ketbra{2},
-\end{equation}
-defined on the computational basis.
-For the moment, we do not need to define an order between the energy eigenvalues.
-The thermal state is
-\begin{equation}
-	\gamma = \frac{e^{-\beta E_0}}{Z}\ketbra{0} + \frac{e^{-\beta E_1}}{Z}\ketbra{1} + \frac{e^{-\beta E_2}}{Z}\ketbra{2},
-\end{equation}
-where $\Z = e^{-\beta E_0} + e^{-\beta E_1} + e^{-\beta E_2}$.
-
-We choose the Strange state where the negative component lies at phase space point $(2,2)$, i.e. it aligns with a thermal Wigner component associated with energy $E_2$.
-However, the analysis that follows is general in the sense that choosing a different Strange state permutation is equivalent to changing the order between energy eigenvalues.
-
-There are now 4 phase space different regions for the 1-copy case, listed in~\cref{tab:thermal_w_general}.
-\begin{table}[h]
-  \def\arraystretch{2}
-  \centering
-  \begin{tabular}{c|c|c|c}
-    $\bmx = (x_0, x_1)$ & $W_{\noisys}(\bmx)$ & $W_{\gamma}(\bmx)$ & $\tilde{\bmw}$ \\
-    \hline
-    \makecell{$(0,0)$ \\ \vdots \\ $(0,2)$} & $\displaystyle \chi$ & $\displaystyle \frac{e^{-\beta E_0}}{3\Z}$ & $\displaystyle 3\Z e^{\beta E_0} \chi$ \\
-    \hline
-    \makecell{$(1,0)$ \\ \vdots \\ $(1,2)$} & $\displaystyle \chi$ & $\displaystyle \frac{e^{-\beta E_1}}{3\Z}$ & $\displaystyle 3\Z e^{\beta E_1} \chi$ \\
-    \hline
-    \makecell{$(2,0)$ \\ $(2,1)$} & $\displaystyle \chi$ & $\displaystyle \frac{e^{-\beta E_2}}{3\Z}$ & $\displaystyle 3\Z e^{\beta E_2} \chi$ \\
-    \hline
-    $(2,2)$ & $\displaystyle -\nu$ & $\displaystyle \frac{e^{-\beta E_2}}{3\Z}$ & $\displaystyle 3\Z e^{\beta E_2} (-\nu)$ \\
-    \hline
-  \end{tabular}
-  \caption{Wigner components $W_{\gamma}(\bmx)$, $W_{\noisys}(\bmx)$ and the associated slope $\widetilde{\bmw}$ for Hamiltonian $H$ in~\cref{eq:h_thermal_general}. 
-  Ordering depends on the energy ordering.}
-  \label{tab:thermal_w_general}
-\end{table}
-
-The generating functions are
-\begin{widetext}
-\begin{align}
-	&G(X,Y; \noisys) \coloneqq (-\nu + 3\chi X + 3\chi Y + 2\chi Z)^n \nonumber\\
-	&= \sum\limits_{\substack{i,j,k = 0,\dots,n \\ i+j+k \leq n}} m_{ijk} \big[(-\nu)^{n-i-j-k} \chi^{i+j+k} \big] X^i Y^j Z^k, \\
-	&G(X,Y; \gamma) \coloneqq \left( \frac{e^{\beta E_2}}{3\Z} + 3\frac{e^{\beta E_0}}{3\Z} X + 3\frac{e^{\beta E_1}}{3\Z} Y + 2\frac{e^{\beta E_2}}{3\Z} Z \right)^n \nonumber\\
-	&= (3\Z)^{-n}\sum\limits_{\substack{i,j,k = 0,\dots,n \\ i+j+k \leq n}} m_{ijk} e^{-\beta [ i E_0 + j E_2 + (n-i-j) E_3 ]} X^i Y^j Z^k, \\
-	&G(X,Y; \widetilde{\bmw}) \coloneqq \Big( 3\Z e^{\beta E_2}(-\nu) + 3(3\Z e^{\beta E_0}\chi) X + 3(3\Z e^{\beta E_1}\chi + 2(3\Z e^{\beta E_2}\chi) e^\beta Z \Big)^n \nonumber\\
-	&= (3\Z)^n \sum\limits_{\substack{i,j,k = 0,\dots,n \\ i+j+k \leq n}} m_{ijk} \big[(-\nu)^{n-i-j-k} \chi^{i+j+k} e^{\beta [(n-i-j)E_2 + iE_0 + jE_1]} \big] X^i Y^j Z^k,
-\end{align}
-\end{widetext}
-where the $(i,j,k)$-th term multiplicity $m_{ij}$ is given by
-\begin{equation}
-	m_{ijk} \coloneqq \frac{n!}{i!j!k!(n-i-j-k)!} 3^i 3^j 2^k.
-\end{equation}
-
-In order to find the first elbow coordinates, we need to find the maximum value of the term
-\begin{equation}
-	\tilde{w} \coloneqq (-\nu)^{n-i-j-k} \chi^{i+j+k} e^{\beta [(n-i-j)E_2 + iE_0 + jE_1]}
-\end{equation}
-over all $i,j,k = 0,\dots,n$ with the constraint $i+j+k \leq n$.
-This optimisation depends on the ordering of the energy eigenvalues.
-We restrict to even $n$ now.
-Specifically, there are two scenarios:
-\begin{itemize}
-	\item The eigenvalue ($E_2$) corresponding to the subspace of the negative Strange Wigner component is largest.
-	In this case, $\tilde{w}$ attains its maximum value $\nu^n e^{n\beta E_2}$ for $i=j=k=0$.
-	\item The eigenvalue ($E_2$) corresponding to the subspace of the negative Strange Wigner component is not largest.
-	In this case, (wlog assume $E_0$ is largest)
-	\begin{equation}
-	  \tilde{w} =
-     \begin{cases}
-		\nu^n, &\beta E_0 \leq \ln{\left(8-\frac{18}{3-\epsilon}\right)}, \\
-		\chi^n e^{n\beta E_0}, &\beta E_0 > \ln{\left(8-\frac{18}{3-\epsilon}\right)}.
-	  \end{cases}
-	\end{equation}
-	The first case corresponds to $i=j=k=0$, and the second case to $i=n,j=k=0$.
-\end{itemize}
-In both scenarios, for small enough $\beta$, the first elbow is given by the term with $i=j=k=0$.
-The coordinates are
-\begin{equation}
-	(x_0, L_0) = ((3\Z)^n, \nu^n)
-\end{equation}
-and therefore the first elbow constraint $L_\star \geq L'_\star$ gives
-\begin{align}
-	\frac{n}{n'} \geq \frac{\ln{\Big[ (1-\frac{4}{3}\epsilon')\Z_\beta \Big]}}{\ln{\Big[ (1-\frac{4}{3}\epsilon)\Z_\beta \Big]}},
-\end{align}
-with $\tt \leq n$ and $\epsilon' \leq \epsilon$. 
-Moreover, if $E_2$ is not largest, we have the additional constarint $\epsilon \leq 3 - 18/\big(8-e^{\beta}\big)$.
-This agrees with the previous scenario where the energy spectrum was $(1,0,0)$.
-
-\null\newpage
-\null\newpage
+\subsection{Random plots}
 
@@
 \end{figure}
-
-\subsection{Magic in pure stabilizer fragments}\label{sec:magstab}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\null\newpage
 \null\newpage

### 2021-02-15 appendix.tex
Full n-copy first elbow coordinates. Need to expand on the first elbow constraint
More code simplifications

@@
 \begin{align}	
-	\Phi_+(\mmf; \nnf, p) &\coloneqq \sum\limits_{\dummy=0}^{\mmf/2} \binom{\nnf}{2\dummy} p^{2\dummy} (1-p)^{\nnf-2\dummy}, \nonumber\\ 
-	&\text{for even integers } \mmf\in[0,\nnf], \label{eq:fp_app} \\
-	\Phi_-(\mmf; \nnf, p) &\coloneqq \sum\limits_{\dummy=1}^{(\mmf-1)/2} \binom{\nnf}{2\dummy+1} p^{2\dummy+1} (1-p)^{\nnf-(2\dummy+1)}, \nonumber\\ 
-	&\text{for odd integers } \mmf\in[0,\nnf]. \label{eq:fn_app}
+	\Phi_+(af; nf, p) &\coloneqq \sum\limits_{\ell=0}^{af/2} \binom{nf}{2\ell} p^{2\ell} (1-p)^{nf-2\ell}, \nonumber\\ 
+	&\text{for even integers } af\in[0,nf], \label{eq:fp_app} \\
+	\Phi_-(af; nf, p) &\coloneqq \sum\limits_{\ell=1}^{(af-1)/2} \binom{nf}{2\ell+1} p^{2\ell+1} (1-p)^{nf-(2\ell+1)}, \nonumber\\ 
+	&\text{for odd integers } af\in[0,nf]. \label{eq:fn_app}
 \end{align}
-Note that index $\mmf$ only takes even (odd) values when labelling $\Phi_+$ ($\Phi_-$).
+Note that index $af$ only takes even (odd) values when labelling $\Phi_+$ ($\Phi_-$).
 In~\cref{app:lcsu_coord_elb}, we will use $\Phi_+$ and $\Phi_-$ to express the elbow coordinates of standard Lorenz curves.
@@
 \begin{lemma}\label{lem:comb_bounds}
-	For all $\dummy\in [1,\nnf-1]$,
+	For all $\ell\in [1,nf-1]$,
 	\begin{align}
-		&\left[ 8\dummy\left(1-\frac{\dummy}{\nnf}\right) \right]^{-\frac{1}{2}} 2^{\nnf S\left(\frac{\dummy}{\nnf}\right)} \leq \binom{\nnf}{\dummy} \leq \\
-		&\left[ 2\pi \dummy\left(1-\frac{\dummy}{\nnf}\right) \right]^{-\frac{1}{2}} 2^{\nnf S\left(\frac{\dummy}{\nnf}\right)}.
+		&\left[ 8\ell\left(1-\frac{\ell}{nf}\right) \right]^{-\frac{1}{2}} 2^{nf S\left(\frac{\ell}{nf}\right)} \leq \binom{nf}{\ell} \leq \\
+		&\left[ 2\pi \ell\left(1-\frac{\ell}{nf}\right) \right]^{-\frac{1}{2}} 2^{nf S\left(\frac{\ell}{nf}\right)}.
 	\end{align}
@@
 \begin{proof}
-	For $\dummy = 1,2, \nnf-1, \nnf-2$ check by direct calculation.	
+	For $\ell = 1,2, nf-1, nf-2$ check by direct calculation.	
 	For all other cases, use Stirling's approximation. 
@@
 		\begin{split}
-		&\text{1. } \Phi_+(\mmf; \nnf, p) \geq \sum\limits_{\dummy=0}^{\mmf/2}\left[ 16\dummy\left(1-\frac{2\dummy}{\nnf}\right) \right]^{-\frac{1}{2}} 2^{-\nnf\ent{\frac{2\dummy}{\nnf}}{p}}, \\
-		&\hspace{14pt} \text{for all even } \mmf\in [2,\nnf] \\
-		&\text{2. } \Phi_+(\mmf; \nnf, p) \leq \sum\limits_{\dummy=0}^{\mmf/2}\left[ 4\pi\dummy\left(1-\frac{2\dummy}{\nnf}\right) \right]^{-\frac{1}{2}} 2^{-\nnf\ent{\frac{2\dummy}{\nnf}}{p}}, \\
-		&\hspace{14pt} \text{for all even } \mmf\in [2,\nnf] \\
-		&\text{3. } \Phi_-(\mmf; \nnf, p) \geq \sum\limits_{\dummy=1}^{(\mmf-1)/2}\left[ 16(\dummy+1)\left(1-\frac{2\dummy+1}{\nnf}\right) \right]^{-\frac{1}{2}} \times \\
-		&\hspace{14pt} \times 2^{-\nnf\ent{\frac{2\dummy+1}{\nnf}}{p}},\ \text{for all odd }\mmf\in [1,\nnf] \\
-		&\text{4. } \Phi_-(\mmf; \nnf, p) \leq \sum\limits_{\dummy=1}^{(\mmf-1)/2}\left[ 4\pi(\dummy+1)\left(1-\frac{2\dummy+1}{\nnf}\right) \right]^{-\frac{1}{2}} \times \\
-		&\hspace{14pt} \times 2^{-\nnf\ent{\frac{2\dummy+1}{\nnf}}{p}},\ \text{for all odd } \mmf\in [1,\nnf]
+		&\text{1. } \Phi_+(af; nf, p) \geq \sum\limits_{\ell=0}^{af/2}\left[ 16\ell\left(1-\frac{2\ell}{nf}\right) \right]^{-\frac{1}{2}} 2^{-nf\ent{\frac{2\ell}{nf}}{p}}, \\
+		&\hspace{14pt} \text{for all even } af\in [2,nf] \\
+		&\text{2. } \Phi_+(af; nf, p) \leq \sum\limits_{\ell=0}^{af/2}\left[ 4\pi\ell\left(1-\frac{2\ell}{nf}\right) \right]^{-\frac{1}{2}} 2^{-nf\ent{\frac{2\ell}{nf}}{p}}, \\
+		&\hspace{14pt} \text{for all even } af\in [2,nf] \\
+		&\text{3. } \Phi_-(af; nf, p) \geq \sum\limits_{\ell=1}^{(af-1)/2}\left[ 16(\ell+1)\left(1-\frac{2\ell+1}{nf}\right) \right]^{-\frac{1}{2}} \times \\
+		&\hspace{14pt} \times 2^{-nf\ent{\frac{2\ell+1}{nf}}{p}},\ \text{for all odd }af\in [1,nf] \\
+		&\text{4. } \Phi_-(af; nf, p) \leq \sum\limits_{\ell=1}^{(af-1)/2}\left[ 4\pi(\ell+1)\left(1-\frac{2\ell+1}{nf}\right) \right]^{-\frac{1}{2}} \times \\
+		&\hspace{14pt} \times 2^{-nf\ent{\frac{2\ell+1}{nf}}{p}},\ \text{for all odd } af\in [1,nf]
 		\end{split}
@@
 \subsection{Standard Lorenz curve elbow coordinates}\label{app:lcsu_coord_elb}
-The Wigner distribution of the $\NN$-copy qutrit maximally mixed state $\left(\id/3\right)\too{\NN}$ is the uniform distribution 
+The Wigner distribution of the $n$-copy qutrit maximally mixed state $\left(\id/3\right)^{\otimes n}$ is the uniform distribution 
 \begin{equation}\label{eq:wu}
-	\W{\left(\id/3\right)\too{\NN}} = \Bigg( \overbrace{\frac{1}{9^\NN}, \dots, \frac{1}{9^\NN}}^{9^\NN} \Bigg).
+	\W{\left(\id/3\right)^{\otimes n}} = \Bigg( \overbrace{\frac{1}{9^n}, \dots, \frac{1}{9^n}}^{9^n} \Bigg).
 \end{equation}
-The Wigner distribution of the 1-copy $\epsilon$-noisy Strange state $\noisys(\epsilon)$ in the unital fragment is a permutation of 
+The Wigner distribution of the 1-copy $\epsilon$-noisy Strange state $\rho_{\rm{S}}(\epsilon)$ in the unital fragment is a permutation of 
 \begin{equation}\label{eq:wsu}
-	\W{\noisys(\epsilon)} = \Bigg( \overbrace{\frac{1}{6} - \frac{1}{18}\epsilon, \dots, \frac{1}{6} - \frac{1}{18}\epsilon}^8, \overbrace{-\frac{1}{3} + \frac{4}{9}\epsilon}^1 \Bigg)
+	\W{\rho_{\rm{S}}(\epsilon)} = \Bigg( \overbrace{\frac{1}{6} - \frac{1}{18}\epsilon, \dots, \frac{1}{6} - \frac{1}{18}\epsilon}^8, \overbrace{-\frac{1}{3} + \frac{4}{9}\epsilon}^1 \Bigg)
 \end{equation}
@@
 
-The Wigner distribution of the $\NN$-copy $\epsilon$-noisy Strange state $\noisysN$ in the unital fragment is given by the convolution $\W{\noisysN} = \rm{W}_{\noisys(\epsilon)}\too{\NN}$.
-In general, $\noisysN$ contains $\NN + 1$ distinct components, labelled $0,\dots, \NN$.
-We present the distinct Wigner components of $\noisysN$ along with their multiplicites in~\cref{tab:lcsu}.
-Note that LHS (RHS) refers to elbow coordinates $\ii$ on the left of and including (right of) the maximum, precisely
+The Wigner distribution of the $n$-copy $\epsilon$-noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ in the unital fragment is given by the convolution $\W{\rho_{\rm{S}}(\epsilon)^{\otimes n}} = \rm{W}_{\rho_{\rm{S}}(\epsilon)}^{\otimes n}$.
+In general, $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ contains $n + 1$ distinct components, labelled $0,\dots, n$.
+We present the distinct Wigner components of $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ along with their multiplicites in~\cref{tab:lcsu}.
+Note that LHS (RHS) refers to elbow coordinates $i$ on the left of and including (right of) the maximum, precisely
 \begin{align}
-&\text{LHS: } 0 \leq \ii \leq \left\lfloor \frac{\NN}{2} \right\rfloor ; \\
-&\text{RHS: } \left\lfloor \frac{\NN}{2} \right\rfloor +1 \leq \ii \leq \NN.
+&\text{LHS: } 0 \leq i \leq \left\lfloor \frac{n}{2} \right\rfloor ; \\
+&\text{RHS: } \left\lfloor \frac{n}{2} \right\rfloor +1 \leq i \leq n.
 \end{align}
@@
   \begin{tabular}{c|c|c|r|r}
-    \multicolumn{3}{c|}{Case} & \multicolumn{1}{c}{$\mlt_{\ii}(\NN, \epsilon)$} & \multicolumn{1}{|c}{$w_{\ii}(\NN, \epsilon)$} \\[0.5ex]\hline
-    \multirow{4}{*}{\raisebox{-4ex}{\rotatebox[origin=c]{90}{$0\leq \epsilon < \frac{3}{7}$}}} & \hspace{0.8ex}\multirow{2}{*}{\raisebox{-1ex}{\rotatebox[origin=c]{90}{$\NN$ even}}}\hspace{0.8ex} & LHS & $8^{2\ii}\binom{\NN}{2\ii}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{\NN-2\ii}$ \\
-    & & RHS & $8^{\NN-2\ii}\binom{\NN}{2\ii}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{\NN-2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2\ii}$ \\ \cline{2-5}
-    & \multirow{2}{*}{\raisebox{-2ex}{\rotatebox[origin=c]{90}{$\NN$ odd}}} & LHS & $8^{2\ii+1}\binom{\NN}{2\ii+1}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2\ii+1}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{\NN-2\ii-1}$ \\
-    & & RHS & $8^{\NN-2\ii-1}\binom{\NN}{2\ii+1}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{\NN-2\ii-1}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2\ii+1}$ \\ \hline
-    \multirow{4}{*}{\raisebox{-4ex}{\rotatebox[origin=c]{90}{$\frac{3}{7}\leq \epsilon < \frac{3}{4}$}}} & \multirow{2}{*}{\raisebox{-1ex}{\rotatebox[origin=c]{90}{$\NN$ even}}} & LHS & $8^{\NN-2\ii}\binom{\NN}{2\ii}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{\NN-2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2\ii}$ \\
-    & & RHS & $8^{2\ii}\binom{\NN}{2\ii}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{\NN-2\ii}$ \\ \cline{2-5}
-    & \multirow{2}{*}{\raisebox{-2ex}{\rotatebox[origin=c]{90}{$\NN$ odd}}} & LHS & $8^{\NN-2\ii}\binom{\NN}{2\ii}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{\NN-2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2\ii}$ \\
-    & & RHS & $8^{2\ii}\binom{\NN}{2\ii}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{\NN-2\ii}$ \\ \hline
+    \multicolumn{3}{c|}{Case} & \multicolumn{1}{c}{$m_{i}(n, \epsilon)$} & \multicolumn{1}{|c}{$w_{i}(n, \epsilon)$} \\[0.5ex]\hline
+    \multirow{4}{*}{\raisebox{-4ex}{\rotatebox[origin=c]{90}{$0\leq \epsilon < \frac{3}{7}$}}} & \hspace{0.8ex}\multirow{2}{*}{\raisebox{-1ex}{\rotatebox[origin=c]{90}{$n$ even}}}\hspace{0.8ex} & LHS & $8^{2i}\binom{n}{2i}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2i}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{n-2i}$ \\
+    & & RHS & $8^{n-2i}\binom{n}{2i}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{n-2i}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2i}$ \\ \cline{2-5}
+    & \multirow{2}{*}{\raisebox{-2ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $8^{2i+1}\binom{n}{2i+1}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2i+1}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{n-2i-1}$ \\
+    & & RHS & $8^{n-2i-1}\binom{n}{2i+1}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{n-2i-1}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2i+1}$ \\ \hline
+    \multirow{4}{*}{\raisebox{-4ex}{\rotatebox[origin=c]{90}{$\frac{3}{7}\leq \epsilon < \frac{3}{4}$}}} & \multirow{2}{*}{\raisebox{-1ex}{\rotatebox[origin=c]{90}{$n$ even}}} & LHS & $8^{n-2i}\binom{n}{2i}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{n-2i}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2i}$ \\
+    & & RHS & $8^{2i}\binom{n}{2i}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2i}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{n-2i}$ \\ \cline{2-5}
+    & \multirow{2}{*}{\raisebox{-2ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $8^{n-2i}\binom{n}{2i}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{n-2i}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2i}$ \\
+    & & RHS & $8^{2i}\binom{n}{2i}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2i}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{n-2i}$ \\ \hline
   \end{tabular}
-  \caption{Wigner components $w_{\ii}(\NN, \epsilon)$ of $\noisysN$ along with their multiplicities $\mlt_{\ii}(\NN, \epsilon)$ in decreasing order in $\ii,\ 0 \leq \ii \leq \NN$.
-  The order changes depending on the noise level $\epsilon$, the parity of the number of copies $\NN$ and the parity of the components (LHS vs RHS).
-  Multiplication $2\ii$ is considered modulo $(\NN+1)$.}
+  \caption{Wigner components $w_{i}(n, \epsilon)$ of $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ along with their multiplicities $m_{i}(n, \epsilon)$ in decreasing order in $i,\ 0 \leq i \leq n$.
+  The order changes depending on the noise level $\epsilon$, the parity of the number of copies $n$ and the parity of the components (LHS vs RHS).
+  Multiplication $2i$ is considered modulo $(n+1)$.}
   \label{tab:lcsu}
@@
 
-For example, the distribution of state $\noisys(0)\too{2}$ is
+For example, the distribution of state $\rho_{\rm{S}}(0)^{\otimes 2}$ is
 \begin{equation*}
 	\begin{split}
-	\rm{W}_{\noisys(0)\too{2}} = \Bigg( &\overbrace{\left( -\frac{1}{3} \right)^2}^1, \overbrace{\left( \frac{1}{6} \right)^2, \dots, \left( \frac{1}{6} \right)^2}^{64}, \\
+	\rm{W}_{\rho_{\rm{S}}(0)^{\otimes 2}} = \Bigg( &\overbrace{\left( -\frac{1}{3} \right)^2}^1, \overbrace{\left( \frac{1}{6} \right)^2, \dots, \left( \frac{1}{6} \right)^2}^{64}, \\
 	&\overbrace{ -\frac{1}{3} \cdot \frac{1}{6}, \dots, -\frac{1}{3} \cdot \frac{1}{6}}^{16} \Bigg)
@@
 
-Every standard Lorenz curve contains $\NN$ elbows, labelled by 
+Every standard Lorenz curve contains $n$ elbows, labelled by 
 \begin{equation*}
-\{(x_{\ii}, L_{\ii})\}_{\ii=-1,0,\dots,\NN}\ ,
+\{(x_{i}, L_{i})\}_{i=-1,0,\dots,n}\ ,
 \end{equation*}
-where the boundary points $(x_{-1}, L_{-1}) = (0,0)$ and $(x_{\NN}, L_{\NN}) = (1,1)$ are also included.
-The maximum is the $(\lfloor \NN \rfloor/2)$-th elbow and its coordinates are calculated by collecting all the positive Wigner components,
+where the boundary points $(x_{-1}, L_{-1}) = (0,0)$ and $(x_{n}, L_{n}) = (1,1)$ are also included.
+The maximum is the $(\lfloor n/2 \rfloor)$-th elbow and its coordinates are calculated by collecting all the positive Wigner components,
 \begin{align}
-	x_{\lfloor \NN \rfloor/2} &= \frac{1}{2}\left(1 + \left(\frac{7}{9}\right)^\NN\right), \\
-	L_{\lfloor \NN \rfloor/2} &= \frac{1}{2}\left (1 + \left(\frac{15 - 8\epsilon}{9}\right)^\NN \right).
+	x_{\lfloor n/2 \rfloor} &= \frac{1}{2}\left(1 + \left(\frac{7}{9}\right)^n\right), \\
+	L_{\lfloor n/2 \rfloor} &= \frac{1}{2}\left (1 + \left(\frac{15 - 8\epsilon}{9}\right)^n \right).
 \end{align}
@@
   \begin{tabular}{c|c|c|r|r}
-    \multicolumn{3}{c|}{Case} & \multicolumn{1}{c}{$x_{\ii}$} & \multicolumn{1}{|c}{$L_{\ii}$} \\[0.5ex]\hline
-    \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$0\leq \epsilon < \frac{3}{7}$}}} & \hspace{0.8ex}\multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$\NN$ even}}}\hspace{0.8ex} & LHS & $\Phi_+\left(2\ii;\NN,\frac{8}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_+\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\
-    & & RHS & $x_{\lfloor \NN/2 \rfloor} + \Phi_-\left(2\ii;\NN,\frac{1}{9}\right)$ & $L_{\lfloor \NN/2 \rfloor} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_-\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
-    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$\NN$ odd}}} & LHS & $\Phi_-\left(2\ii;\NN,\frac{8}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_-\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\
-    & & RHS & $x_{\lfloor \NN/2 \rfloor} + \Phi_-\left(2\ii;\NN,\frac{1}{9}\right)$ & $L_{\lfloor \NN/2 \rfloor} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_-\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
-    \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$\frac{3}{7}\leq \epsilon < \frac{3}{4}$}}} & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$\NN$ even}}} & LHS & $\Phi_+\left(2\ii;\NN,\frac{1}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_+\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\
-    & & RHS & $x_{\lfloor \NN/2 \rfloor} + \Phi_-\left(2\ii;\NN,\frac{8}{9}\right)$ & $L_{\lfloor \NN/2 \rfloor} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_-\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
-    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$\NN$ odd}}} & LHS & $\Phi_+\left(2\ii;\NN,\frac{1}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_+\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\
-    & & RHS & $x_{\lfloor \NN/2 \rfloor} + \Phi_+\left(2\ii;\NN,\frac{8}{9}\right)$ & $L_{\lfloor \NN/2 \rfloor} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_+\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
+    \multicolumn{3}{c|}{Case} & \multicolumn{1}{c}{$x_{i}$} & \multicolumn{1}{|c}{$L_{i}$} \\[0.5ex]\hline
+    \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$0\leq \epsilon < \frac{3}{7}$}}} & \hspace{0.8ex}\multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ even}}}\hspace{0.8ex} & LHS & $\Phi_+\left(2i;n,\frac{8}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\
+    & & RHS & $x_{\lfloor n/2 \rfloor} + \Phi_-\left(2i;n,\frac{1}{9}\right)$ & $L_{\lfloor n/2 \rfloor} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-\left(2i;n,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
+    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $\Phi_-\left(2i;n,\frac{8}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_-\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\
+    & & RHS & $x_{\lfloor n/2 \rfloor} + \Phi_-\left(2i;n,\frac{1}{9}\right)$ & $L_{\lfloor n/2 \rfloor} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-\left(2i;n,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
+    \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$\frac{3}{7}\leq \epsilon < \frac{3}{4}$}}} & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ even}}} & LHS & $\Phi_+\left(2i;n,\frac{1}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+\left(2i;n,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\
+    & & RHS & $x_{\lfloor n/2 \rfloor} + \Phi_-\left(2i;n,\frac{8}{9}\right)$ & $L_{\lfloor n/2 \rfloor} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
+    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $\Phi_+\left(2i;n,\frac{1}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+\left(2i;n,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\
+    & & RHS & $x_{\lfloor n/2 \rfloor} + \Phi_+\left(2i;n,\frac{8}{9}\right)$ & $L_{\lfloor n/2 \rfloor} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_+\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
   \end{tabular}
   \caption{Standard Lorenz curves elbow coordinates.
-  The expresion depends on the noise level $\epsilon$, the parity of the number of copies $\NN$ and the location of the elbow relative to the maximum (LHS vs RHS).
-  Multiplication $2\ii$ is considered modulo $(\NN+1)$.
-  Note that the Lorenz curve boundary points are $(x_{-1}, L_{-1}) \coloneqq (0,0)$ and $(x_{\NN}, L_{\NN}) = (1,1)$.
+  The expresion depends on the noise level $\epsilon$, the parity of the number of copies $n$ and the location of the elbow relative to the maximum (LHS vs RHS).
+  Multiplication $2i$ is considered modulo $(n+1)$.
+  Note that the Lorenz curve boundary points are $(x_{-1}, L_{-1}) \coloneqq (0,0)$ and $(x_{n}, L_{n}) = (1,1)$.
   }
@@
 \subsection{Standard Lorenz curve coordinates}\label{app:lcsu_coord}
-We can get explicit expressions for all $9^{\NN}$ points of the standard Lorenz curve $\lc{\noisysN}{\id/3}$, in terms of the elbow coordinates:
+We can get explicit expressions for all $9^{n}$ points of the standard Lorenz curve $\lc{\rho_{\rm{S}}(\epsilon)^{\otimes n}}{\id/3}$, in terms of the elbow coordinates:
 \begin{align}
-    x_{\ii\jj} &= \left( 1-\frac{\jj}{\mlt_{\ii}} \right) x_{\ii-1} + \frac{\jj}{\mlt_{\ii}} x_{\ii}, \label{eq:x}\\
-    L_{\ii\jj} &= \left( 1-\frac{\jj}{\mlt_{\ii}} \right) L_{\ii-1} + \frac{\jj}{\mlt_{\ii}} L_{\ii} \label{eq:l}
+    x_{ij} &= \left( 1-\frac{j}{m_{i}} \right) x_{i-1} + \frac{j}{m_{i}} x_{i}, \label{eq:x}\\
+    L_{ij} &= \left( 1-\frac{j}{m_{i}} \right) L_{i-1} + \frac{j}{m_{i}} L_{i} \label{eq:l}
 \end{align}
-for $\jj = 1,\dots,\mlt_{\ii}$ and $\ii=0,\dots,\NN$, where multiplicities $\mlt_\ii = \mlt_\ii(\NN, \epsilon)$ are given in~\cref{tab:lcsu}.
+for $j = 1,\dots,m_{i}$ and $i=0,\dots,n$, where multiplicities $m_i = m_i(n, \epsilon)$ are given in~\cref{tab:lcsu}.
 
-For visualisation purposes, we plot the Lorenz curve of state $\noisys(0)\too{2}$.
+For visualisation purposes, we plot the Lorenz curve of state $\rho_{\rm{S}}(0)^{\otimes 2}$.
 \begin{figure}[t]
@@
 \begin{equation*}
-\noisys(\tt, \epsilon, \nn-\tt) \coloneqq \noisys(\epsilon)\too{\tt} \otimes \left( \frac{1}{3}\id \right)\too{(\nn-\tt)},
+\rho_{\rm{S}}(n', \epsilon, n-n') \coloneqq \rho_{\rm{S}}(\epsilon)^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n-n')},
 \end{equation*}
@@
 \begin{align}
-    &x_{\ii\jj\kk} = \left( 1-p_{\ii\jj\kk}\right) x_{\ii-1} + p_{\ii\jj\kk} x_{\ii} \label{eq:lcsu_xcoord}\\
-    &L_{\ii\jj\kk} = \left( 1-p_{\ii\jj\kk} \right) L_{\ii-1} + p_{\ii\jj\kk} L_{\ii}, \label{eq:lcsu_lcoord}\\
-    &\text{where } p_{\ii\jj\kk} = \frac{\kk + (\jj-1)9^{\nn-\tt}}{9^{\nn-\tt} \mlt_{\ii}} \nonumber\\
-    &\text{for } \ii=0,\dots,\tt,\ \jj = 1,\dots,\mlt_{\ii}(\tt, \epsilon') \text{ and } \kk = 1,\dots,9^{\nn-\tt}. \nonumber
+    &x_{ijk} = \left( 1-p_{ijk}\right) x_{i-1} + p_{ijk} x_{i} \label{eq:lcsu_xcoord}\\
+    &L_{ijk} = \left( 1-p_{ijk} \right) L_{i-1} + p_{ijk} L_{i}, \label{eq:lcsu_lcoord}\\
+    &\text{where } p_{ijk} = \frac{k + (j-1)9^{n-n'}}{9^{n-n'} m_{i}} \nonumber\\
+    &\text{for } i=0,\dots,n',\ j = 1,\dots,m_{i}(n', \epsilon') \text{ and } k = 1,\dots,9^{n-n'}. \nonumber
 \end{align}
@@
 \begin{equation}
-    \II(\ii,\jj,\kk) \coloneqq \kk + \left[ (\jj-1) + \sum_{\dummy=0}^{\ii-1} \mlt_{\dummy}(\tt, \epsilon') \right]9^{\nn-\tt},
+    I(i,j,k) \coloneqq k + \left[ (j-1) + \sum_{\ell=0}^{i-1} m_{\ell}(n', \epsilon') \right]9^{n-n'},
 \end{equation}
-so that $\II=1,2,\dots, 9^{\NN}$.
+so that $I=1,2,\dots, 9^{n}$.
 The elbow coordinates correspond to 
 \begin{equation}
-	\II(\ii, \mlt_{\ii}(\tt, \epsilon'), 9^{\nn-\tt}) = \sum_{\dummy=0}^{\ii} \mlt_{\dummy}(\tt, \epsilon'),\ \ii= 0,\dots,\tt.
+	I(i, m_{i}(n', \epsilon'), 9^{n-n'}) = \sum_{\ell=0}^{i} m_{\ell}(n', \epsilon'),\ i= 0,\dots,n'.
 \end{equation}
-The index function $\II$ is bijective, i.e.
+The index function $I$ is bijective, i.e.
 \begin{equation}
-	(\ii,\jj,\kk) = (\ii',\jj',\kk') \Leftrightarrow \II(\ii,\jj,\kk) = \II(\ii',\jj',\kk').
+	(i,j,k) = (i',j',k') \Leftrightarrow I(i,j,k) = I(i',j',k').
 \end{equation}
@@
 \begin{equation}\label{eq:su_conversion}
-    \noisys(\tt, \epsilon, 0) \xrightarrow{\mathcal{O}_{\id/3}} \noisys(\tt, \epsilon', \nn-\tt).
+    \rho_{\rm{S}}(n', \epsilon, 0) \xrightarrow{\mathcal{O}_{\id/3}} \rho_{\rm{S}}(n', \epsilon', n-n').
 \end{equation}
@@
 \begin{align}
-    \II(\ii,\jj,\kk=1) &= \jj + \sum_{\dummy=0}^{\ii-1} \mlt_{\dummy}(\nn, \epsilon), \\
-    \II'(\ii',\jj',\kk') &= \kk' + \left[ (\jj'-1) + \sum_{\dummy=0}^{\ii'-1} \mlt_{\dummy}(\tt, \epsilon') \right]9^{\nn-\tt}.
+    I(i,j,k=1) &= j + \sum_{\ell=0}^{i-1} m_{\ell}(n, \epsilon), \\
+    I'(i',j',k') &= k' + \left[ (j'-1) + \sum_{\ell=0}^{i'-1} m_{\ell}(n', \epsilon') \right]9^{n-n'}.
 \end{align}
 
-Pointwise Lorenz curve comparison requires $x_{\II} = x_{\II'}$, so the question is: 
+Pointwise Lorenz curve comparison requires $x_{I} = x_{I'}$, so the question is: 
 \begin{center}
-\emph{Given a triplet $(\ii',\jj',\kk')$, what is the tuple $(\ii,\jj)$ such that $\II(\ii,\jj) = \II'(\ii',\jj',\kk')$?}
+\emph{Given a triplet $(i',j',k')$, what is the tuple $(i,j)$ such that $I(i,j) = I'(i',j',k')$?}
 \end{center}
 
-According to~\cref{thm:elbows} which is proved in~\cref{app:lc_constraints}, for standard Lorenz curves, we need to match indices at the target state elbows, so the requirement on the indices is finding a tuple $(\ii, \jj)$, such that for a given $\ii' = 0,\dots,\tt$,
+According to~\cref{thm:elbows} which is proved in~\cref{app:lc_constraints}, for standard Lorenz curves, we need to match indices at the target state elbows, so the requirement on the indices is finding a tuple $(i, j)$, such that for a given $i' = 0,\dots,n'$,
 \begin{equation}
-	\jj + \sum_{\dummy=0}^{\ii-1} \mlt_{\dummy}(\nn, \epsilon) = \sum_{\dummy=0}^{\ii'} \mlt_{\dummy}(\tt, \epsilon').
+	j + \sum_{\ell=0}^{i-1} m_{\ell}(n, \epsilon) = \sum_{\ell=0}^{i'} m_{\ell}(n', \epsilon').
 \end{equation}
@@
 \begin{equation}
-\rho_{\rm{S}}(\epsilon)\too{4} \xrightarrow{\mathcal{O}_{\id/3}} \rho_{\rm{S}}(\epsilon')\too{2} \otimes \left( \frac{1}{3}\id \right)\too{2}.
+\rho_{\rm{S}}(\epsilon)^{\otimes 4} \xrightarrow{\mathcal{O}_{\id/3}} \rho_{\rm{S}}(\epsilon')^{\otimes 2} \otimes \left( \frac{1}{3}\id \right)^{\otimes 2}.
 \end{equation}
@@
 \begin{equation}
-	L_{\II(\ii,\jj)} \geq L'_{\II'(0, 1, 81)}
+	L_{I(i,j)} \geq L'_{I'(0, 1, 81)}
 \end{equation}
@@
 
-The challenge is to find $\ii,\jj$ such that $i(\ii,\jj) = i'(0,1,81)$.
-\nick{By trial and error}, we find that $(\ii,\jj) = (1, 80)$.
+The challenge is to find $i,j$ such that $i(i,j) = i'(0,1,81)$.
+\nick{By trial and error}, we find that $(i,j) = (1, 80)$.
 Now we can use~\cref{eq:lcsu_lcoord} to directly calculate
@@
 
-	Let $\tt$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ and $E \coloneqq \{x_1, \dots, x_\tt\}$ be their locations.
+	Let $n'$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ and $E \coloneqq \{x_1, \dots, x_n'\}$ be their locations.
 
-	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_{\ii}) \geq \lc{\tau}{\sigma}(x_{\ii})$ for all $\ii =1,\dots,\tt$.
+	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\tau}{\sigma}(x_{i})$ for all $i =1,\dots,n'$.
 \end{theorem}
 \begin{proof}	
-	$\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ trivially implies $\lc{\rho}{\sigma}(x_{\ii}) \geq \lc{\tau}{\sigma}(x_{\ii})$ for all $\ii = 1,\dots,\tt$.
+	$\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ trivially implies $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\tau}{\sigma}(x_{i})$ for all $i = 1,\dots,n'$.
 
-	Conversely, assume that $\lc{\rho}{\sigma}(x_{\ii}) \geq \lc{\tau}{\sigma}(x_{\ii})$ for all $\ii = 1,\dots,r$.
-	First, let $x_0 = 0$ and $x_{\tt+1} = 1$, so that $\lc{\rho}{\sigma}(x_0) = \lc{\tau}{\sigma}(x_0) = 0$ and $\lc{\rho}{\sigma}(x_{\tt+1}) = \lc{\tau}{\sigma}(x_{\tt+1}) = 1$.
-	Hence, we can extend the set of elbows $E$ to $E' = E \cup \{x_0, x_{\tt+1}\}$.
+	Conversely, assume that $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\tau}{\sigma}(x_{i})$ for all $i = 1,\dots,r$.
+	First, let $x_0 = 0$ and $x_{n'+1} = 1$, so that $\lc{\rho}{\sigma}(x_0) = \lc{\tau}{\sigma}(x_0) = 0$ and $\lc{\rho}{\sigma}(x_{n'+1}) = \lc{\tau}{\sigma}(x_{n'+1}) = 1$.
+	Hence, we can extend the set of elbows $E$ to $E' = E \cup \{x_0, x_{n'+1}\}$.
 
-	Pick two consecutive locations $x_{\ii}, x_{\ii+1}$ in $E'$ and consider the line segment $\ell_\tau(x)$ connecting points $(x_{\ii}, \lc{\tau}{\sigma}(x_{\ii}))$ and $(x_{\ii+1}, \lc{\tau}{\sigma}(x_{\ii+1}))$ as well as the line segment $\ell_\rho(x)$ connecting points $(x_{\ii}, \lc{\rho}{\sigma}(x_{\ii}))$ and $(x_{\ii+1}, \lc{\rho}{\sigma}(x_{\ii+1}))$.
+	Pick two consecutive locations $x_{i}, x_{i+1}$ in $E'$ and consider the line segment $\ell_\tau(x)$ connecting points $(x_{i}, \lc{\tau}{\sigma}(x_{i}))$ and $(x_{i+1}, \lc{\tau}{\sigma}(x_{i+1}))$ as well as the line segment $\ell_\rho(x)$ connecting points $(x_{i}, \lc{\rho}{\sigma}(x_{i}))$ and $(x_{i+1}, \lc{\rho}{\sigma}(x_{i+1}))$.
 	This is illustrated in~\cref{fig:elbows_proof}.
@@
 
-	Due to concavity of $\lc{\rho}{\sigma}$, it is clear that for all $x \in [x_{\ii}, x_{\ii+1}]$, we have $\lc{\rho}{\sigma}(x) \geq \ell_\rho(x) \geq \ell_\tau(x) = \lc{\tau}{\sigma}(x)$.
-	This argument can be made in all intervals $[x_{\ii}, x_{\ii+1}]$ with $\ii=0,\dots,\tt$, so the proof is complete.
+	Due to concavity of $\lc{\rho}{\sigma}$, it is clear that for all $x \in [x_{i}, x_{i+1}]$, we have $\lc{\rho}{\sigma}(x) \geq \ell_\rho(x) \geq \ell_\tau(x) = \lc{\tau}{\sigma}(x)$.
+	This argument can be made in all intervals $[x_{i}, x_{i+1}]$ with $i=0,\dots,n'$, so the proof is complete.
 \end{proof}
@@
 \begin{align}
-L\left(x_{\II'(0, \mlt'_{0}, 9^{\nn-\tt})}\right) &\geq L\left(x_{\II'(0, m'_{0}, 9^{\nn-\tt})}\right), \nonumber\\
-L\left(x_{\II'(1, \mlt'_{1}, 9^{\nn-\tt})}\right) &\geq L\left(x_{\II'(1, m'_{1}, 9^{\nn-\tt})}\right), \nonumber\\
+L\left(x_{I'(0, m'_{0}, 9^{n-n'})}\right) &\geq L\left(x_{I'(0, m'_{0}, 9^{n-n'})}\right), \nonumber\\
+L\left(x_{I'(1, m'_{1}, 9^{n-n'})}\right) &\geq L\left(x_{I'(1, m'_{1}, 9^{n-n'})}\right), \nonumber\\
 &\vdotswithin{=} \nonumber\\
-L\left(x_{\II'(\tt, \mlt'_{r}, 9^{\nn-\tt})}\right) &\geq L\left(x_{\II'(\tt, m'_{\tt}, 9^{\nn-\tt})}\right), \nonumber
+L\left(x_{I'(n', m'_{r}, 9^{n-n'})}\right) &\geq L\left(x_{I'(n', m'_{n'}, 9^{n-n'})}\right), \nonumber
 \end{align}
-where $x_{\II'(0, \mlt'_{0}, 9^{\nn - \tt})}, x_{\II'(1, \mlt'_{1}, 9^{\nn - \tt})}, \dots, x_{\II'(\tt, \mlt'_{\tt}, 9^{\nn - \tt})} \in T$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon')\too{\tt}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).
+where $x_{I'(0, m'_{0}, 9^{n - n'})}, x_{I'(1, m'_{1}, 9^{n - n'})}, \dots, x_{I'(n', m'_{n'}, 9^{n - n'})} \in T$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon')^{\otimes n'}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).
 

### 2021-02-15 magic_paper.tex
More code simplifications

@@
 
-	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_{\ii}) \geq \lc{\tau}{\sigma}(x_{\ii})$ for all $\ii =1,\dots,n'$.
+	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\tau}{\sigma}(x_{i})$ for all $i =1,\dots,n'$.
 \end{theorem}
@@
 
-	Let $\ii_\star$ be the index of the smallest non-negative component of $\tilde{\bm{w}}^\downarrow$.
-	Then, $(\W{\rho})_i < 0$ if and only if $i > \ii_\star$, so the maximum of Lorenz curve $\lc{\rho}{\sigma}(x)$ takes the value 
-	\begin{equation}
-		\lc{\rho}{\sigma}(x_{\ii_\star}) = \sum_{i=1}^{\ii_\star} (\W{\rho})_i,
+	Let $i_\star$ be the index of the smallest non-negative component of $\tilde{\bm{w}}^\downarrow$.
+	Then, $(\W{\rho})_i < 0$ if and only if $i > i_\star$, so the maximum of Lorenz curve $\lc{\rho}{\sigma}(x)$ takes the value 
+	\begin{equation}
+		\lc{\rho}{\sigma}(x_{i_\star}) = \sum_{i=1}^{i_\star} (\W{\rho})_i,
 	\end{equation}
@@
 	\begin{equation}\label{eq:maxloc}
-		x_{\ii_\star} \coloneqq \sum_{i=1}^{\ii_\star} (\W{\sigma})_i.
-	\end{equation}
-
-	The location of the maximum ($x=x_{\ii_\star}$) varies from fragment to fragment, but its value is independent of $\sigma$,
-	\begin{equation}
-		\lc{\rho}{\sigma}(x_{\ii_\star})
+		x_{i_\star} \coloneqq \sum_{i=1}^{i_\star} (\W{\sigma})_i.
+	\end{equation}
+
+	The location of the maximum ($x=x_{i_\star}$) varies from fragment to fragment, but its value is independent of $\sigma$,
+	\begin{equation}
+		\lc{\rho}{\sigma}(x_{i_\star})
 		= \sum\limits_{\bmx: \W[\bmx]{\rho} \geq 0} \W[\bmx]{\rho}
@@
 \begin{equation}\label{eq:ethresh}
-	n_{\star}(\epsilon, \epsilon', \sigma) \coloneqq \min{\{n: \lc{\noisysn}{\sigma} \geq \lc{\noisys(\epsilon')}{\sigma}\}}.
-\end{equation}}
-
-In general, the Wigner components of an $\NN$-copy state $\rho^{\otimes \NN}$ can be calculated directly from $\W{\rho}$ by convolution of the distribution with itself,
-\begin{equation}
-	\W{\rho^{\otimes \NN}} = \rm{W}_{\rho}^{\otimes \NN},
+	n_{\star}(\epsilon, \epsilon', \sigma) \coloneqq \min{\{n: \lc{\rho_{\rm{S}}n}{\sigma} \geq \lc{\rho_{\rm{S}}(\epsilon')}{\sigma}\}}.
+\end{equation}
+}
+
+In general, the Wigner components of an $n$-copy state $\rho^{\otimes n}$ can be calculated directly from $\W{\rho}$ by convolution of the distribution with itself,
+\begin{equation}
+	\W{\rho^{\otimes n}} = \rm{W}_{\rho}^{\otimes n},
 \end{equation}
@@
 \begin{equation}
-    \noisys(\epsilon) = (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \sigma,
+    \rho_{\rm{S}}(\epsilon) = (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \sigma,
 \end{equation}
@@
     }
-    \caption{\textbf{Lorenz curves of Strange state copies.} Lorenz curves of $\noisysn$ for $n=1,2,3,4$.
+    \caption{\textbf{Lorenz curves of Strange state copies.} Lorenz curves of $\rho_{\rm{S}}n$ for $n=1,2,3,4$.
     Solid lines represent pure Strange states ($\epsilon = 0$); dashed lines represent noisy Strange states ($\epsilon = 0.1$).
@@
 We would now like to study the constraints coming solely from majorization in the unital fragment. 
-We consider the problem of purifying $n$ copies of a noisy strange state $\noisysn$ into a smaller number of copies $n'$ of a less noisy strange state $\noisys(\epsilon')^{\otimes n'}$, with $\epsilon' \le \epsilon$ and $n' \leq n$.
+We consider the problem of purifying $n$ copies of a noisy strange state $\rho_{\rm{S}}n$ into a smaller number of copies $n'$ of a less noisy strange state $\rho_{\rm{S}}(\epsilon')^{\otimes n'}$, with $\epsilon' \le \epsilon$ and $n' \leq n$.
 Since the state $\frac{1}{3} \id$ is free, the interconversion problem is unaffected if we tensor in copies of it.
@@
 \begin{equation}\label{eq:sudist}
-	\noisys^{\otimes n} \longrightarrow \noisys(n', \epsilon', n - n') \coloneqq  \noisys(\epsilon')^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n-n')},
+	\rho_{\rm{S}}^{\otimes n} \longrightarrow \rho_{\rm{S}}(n', \epsilon', n - n') \coloneqq  \rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n-n')},
 \end{equation}
 where all copies $n, n', n - n'$ are even.
-Since the initial state can be written in the form $\noisys(n, \epsilon, 0)$, it suffices to construct the Lorenz curve $\lc{\noisys}{\id/3}(x)$ for the generic noisy strange state $\noisys(n, \epsilon ,n')$.
+Since the initial state can be written in the form $\rho_{\rm{S}}(n, \epsilon, 0)$, it suffices to construct the Lorenz curve $\lc{\rho_{\rm{S}}}{\id/3}(x)$ for the generic noisy strange state $\rho_{\rm{S}}(n, \epsilon ,n')$.
 This curve is defined at $9^n$ points between $0$ and $1$.
@@
 Here we focus on the case of Lorenz curves of even copies $n, n'$ and low noise levels ($\epsilon \leq 3/7$).
-The part of the curve on the LHS of its peak is constructed by the positive components of the state Wigner distribution that take values $w_\ii$, with associated multiplicities $\mlt_\ii$,
-\begin{align}
-	w_\ii &= \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{n-2\ii}, \\
-	m_\ii &= 8^{2\ii}\binom{n}{2\ii},
+The part of the curve on the LHS of its peak is constructed by the positive components of the state Wigner distribution that take values $w_i$, with associated multiplicities $m_i$,
+\begin{align}
+	w_i &= \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2i}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{n-2i}, \\
+	m_i &= 8^{2i}\binom{n}{2i},
 \end{align}
 where $i=0,\dots,\frac{n}{2}$.
-From this, it is readily seen that $\lc{\rho}{\id/3}(x)$ has elbows on the LHS of its peak located at points $x=x_\ii$, where
-\begin{equation}
-	x_\ii = \Phi_+ \left( 2\ii; n , \frac{8}{9} \right),
-\end{equation}
-with $\ii = 0,1, \dots , n$ and where $\Phi_+(i,n,p)$ is an even-power cumulant distribution function given by
-\begin{equation}
-	\Phi_+(2\ii; n, p) \coloneqq \sum_{\dummy=0}^{\ii} \binom{n}{2\dummy} p ^{2\dummy} (1-p)^{n-2\dummy}.
+From this, it is readily seen that $\lc{\rho}{\id/3}(x)$ has elbows on the LHS of its peak located at points $x=x_i$, where
+\begin{equation}
+	x_i = \Phi_+ \left( 2i; n , \frac{8}{9} \right),
+\end{equation}
+with $i = 0,1, \dots , n$ and where $\Phi_+(i,n,p)$ is an even-power cumulant distribution function given by
+\begin{equation}
+	\Phi_+(2i; n, p) \coloneqq \sum_{\ell=0}^{i} \binom{n}{2\ell} p ^{2\ell} (1-p)^{n-2\ell}.
 \end{equation}
@@
 \begin{equation}
-	\lc{\rho}{\id/3}(x_{\ii}) \equiv L_{\ii} =  \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^{n} \Phi_+\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right),
+	\lc{\rho}{\id/3}(x_{i}) \equiv L_{i} =  \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^{n} \Phi_+\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right),
 \end{equation}
@@
 \begin{align}
-    x_{\ii\jj\kk} &= \left( 1-p_{\ii\jj\kk}\right) x_{\ii-1} + p_{\ii\jj\kk} x_{\ii} \label{eq:lcsu_xcoord}\\
-    L_{\ii\jj\kk} &= \left( 1-p_{\ii\jj\kk} \right) L_{\ii-1} + p_{\ii\jj\kk} L_{\ii}, \label{eq:lcsu_lcoord}
-\end{align}
-where we use a three-index parametrisation for the coordinates, with $\ii$ the index of the elbow that follows, $\jj = 1,\dots,\mlt_\ii$ and $\kk=1,\dots,9^{2(n-n')}$.
-Therefore, for the initial state $\noisys^{\otimes 2n}$ we have
-\begin{equation}
-	p_{\ii\jj\kk} = \frac{\jj}{8^{2\ii}\binom{2n}{2\ii}},
-\end{equation}
-with $\ii=0,\dots,n,\ \jj(\ii) = 1,\dots,8^{2\ii}\binom{2n}{2\ii}$ and $\kk = 1$.
-For the target state $\noisys(\epsilon')^{\otimes 2n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes 2(n-n')}$,
-\begin{equation}
-	p'_{\ii'\jj'\kk'} = \frac{\kk' + (\jj'-1)9^{2(n-n')}}{9^{2(n-n')} 8^{2\ii'}\binom{2n'}{2\ii'}}
-\end{equation}
-with $\ii'=0,\dots,n',\ \jj'(\ii') = 1,\dots,8^{2\ii'}\binom{n'}{2\ii'}$ and $\kk' = 1,\dots,9^{2(n-n')}$.
+    x_{ijk} &= \left( 1-p_{ijk}\right) x_{i-1} + p_{ijk} x_{i} \label{eq:lcsu_xcoord}\\
+    L_{ijk} &= \left( 1-p_{ijk} \right) L_{i-1} + p_{ijk} L_{i}, \label{eq:lcsu_lcoord}
+\end{align}
+where we use a three-index parametrisation for the coordinates, with $i$ the index of the elbow that follows, $j = 1,\dots,m_i$ and $k=1,\dots,9^{2(n-n')}$.
+Therefore, for the initial state $\rho_{\rm{S}}^{\otimes 2n}$ we have
+\begin{equation}
+	p_{ijk} = \frac{j}{8^{2i}\binom{2n}{2i}},
+\end{equation}
+with $i=0,\dots,n,\ j(i) = 1,\dots,8^{2i}\binom{2n}{2i}$ and $k = 1$.
+For the target state $\rho_{\rm{S}}(\epsilon')^{\otimes 2n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes 2(n-n')}$,
+\begin{equation}
+	p'_{i'j'k'} = \frac{k' + (j'-1)9^{2(n-n')}}{9^{2(n-n')} 8^{2i'}\binom{2n'}{2i'}}
+\end{equation}
+with $i'=0,\dots,n',\ j'(i') = 1,\dots,8^{2i'}\binom{n'}{2i'}$ and $k' = 1,\dots,9^{2(n-n')}$.
 \fi
@@
 \begin{equation}
-	\lc{\noisys(n, \epsilon, 0)}{\frac{\id}{3}}(x_\star) \geq \lc{\noisys(n', \epsilon', n-n')}{\frac{\id}{3}}(x_\star).
-\end{equation}
-
-We choose $x_\star = x_0 = \Phi_+(0, n, \frac{8}{9}) = \frac{1}{9^{n}}$, the location of the first elbow of the initial state $\noisys(n, \epsilon, 0)$.
+	\lc{\rho_{\rm{S}}(n, \epsilon, 0)}{\frac{\id}{3}}(x_\star) \geq \lc{\rho_{\rm{S}}(n', \epsilon', n-n')}{\frac{\id}{3}}(x_\star).
+\end{equation}
+
+We choose $x_\star = x_0 = \Phi_+(0, n, \frac{8}{9}) = \frac{1}{9^{n}}$, the location of the first elbow of the initial state $\rho_{\rm{S}}(n, \epsilon, 0)$.
 The initial state Lorenz curve coordinate at this location is
@@
 \begin{equation}
-	\noisys(\epsilon) \coloneqq (1-\epsilon)\ketbra{\rm{S}} + \epsilon \frac{1}{3}\id,
+	\rho_{\rm{S}}(\epsilon) \coloneqq (1-\epsilon)\ketbra{\rm{S}} + \epsilon \frac{1}{3}\id,
 \end{equation}
@@
 \begin{equation}
-	\W[\bmx]{\noisys(\epsilon)} = (1-\epsilon)\W[\bmx]{\ketbra{\rm{S}}} + \epsilon\W[\bmx]{\frac{1}{3}\id},
+	\W[\bmx]{\rho_{\rm{S}}(\epsilon)} = (1-\epsilon)\W[\bmx]{\ketbra{\rm{S}}} + \epsilon\W[\bmx]{\frac{1}{3}\id},
 \end{equation}
@@
 \begin{equation}\label{eq:msd_thermal}
-		\noisys(\epsilon)^{\otimes n} \xrightarrow{\E \in \O_{\gamma_\beta}} \noisys(\epsilon')^{\otimes n'} \otimes \gamma_\beta^{\otimes (n-n')},
+		\rho_{\rm{S}}(\epsilon)^{\otimes n} \xrightarrow{\E \in \O_{\gamma_\beta}} \rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \gamma_\beta^{\otimes (n-n')},
 \end{equation}
@@
 
-Consider a general $\epsilon$-noisy Strange state $\noisys$ in a thermal fragment $\O_{\gamma}$.
+Consider a general $\epsilon$-noisy Strange state $\rho_{\rm{S}}$ in a thermal fragment $\O_{\gamma}$.
 We can construct the Gibbs-rescaled distribution 
 \begin{equation}
-	\widetilde{\rm{W}}_{\noisys|\gamma}(\bmx) \coloneqq \frac{\W[\bmx]{\noisys}}{\W[\bmx]{\gamma}},
+	\widetilde{\rm{W}}_{\rho_{\rm{S}}|\gamma}(\bmx) \coloneqq \frac{\W[\bmx]{\rho_{\rm{S}}}}{\W[\bmx]{\gamma}},
 \end{equation}
@@
 	\bmm &\coloneqq (1,2,3,3) \\
-	\bmw(\noisys) &\coloneqq (-v, u, u, u) \\
+	\bmw(\rho_{\rm{S}}) &\coloneqq (-v, u, u, u) \\
 	\bmw(\gamma) &\coloneqq \frac{1}{3\Z} \left( e^{-\beta E_0}, e^{-\beta E_0}, e^{-\beta E_1}, e^{-\beta E_2} \right) \\
-	\bmw(\noisys | \gamma) &\coloneqq 3\Z \left( -v e^{\beta E_0}, u e^{\beta E_0}, u e^{\beta E_1}, u e^{\beta E_2} \right) \label{eq:bmw_rescaled}
+	\bmw(\rho_{\rm{S}} | \gamma) &\coloneqq 3\Z \left( -v e^{\beta E_0}, u e^{\beta E_0}, u e^{\beta E_1}, u e^{\beta E_2} \right) \label{eq:bmw_rescaled}
 \end{align}
@@
 There are four distinct values of the Gibbs-rescaled distribution on the phase space, with the negative Strange component $-v$ corresponding to energy $E_0$ as illustrated in the phase space split in~\cref{fig:pd_split_thermal}.
-The Wigner-component vectors $\bmw(\noisys), \bmw(\gamma)$ are then constructed so as to match the four phase space regions.
+The Wigner-component vectors $\bmw(\rho_{\rm{S}}), \bmw(\gamma)$ are then constructed so as to match the four phase space regions.
 \begin{figure}[h]
@@
 \begin{align}
-	w(\noisys)_{ijk} &= (-v)^{n-\alpha} u^{\alpha} \\
+	w(\rho_{\rm{S}})_{ijk} &= (-v)^{n-\alpha} u^{\alpha} \\
 	w(\gamma)_{ijk} &= (3\Z)^{-n} e^{-\beta (n-\alpha)E_0} e^{-\beta ( i E_0 + j E_1 + k E_2 )} \\
-	w(\noisys | \gamma)_{ijk} &= (3\Z)^{n} (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )}
-\end{align}
-
-In order to construct the $n$-copy Lorenz curve of a Strange state in a thermal fragment we need to sort the components of the $n$-copy Gibbs-rescaled distribution, $w(\noisys | \gamma)_{ijk}$ in decreasing order.
+	w(\rho_{\rm{S}} | \gamma)_{ijk} &= (3\Z)^{n} (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )}
+\end{align}
+
+In order to construct the $n$-copy Lorenz curve of a Strange state in a thermal fragment we need to sort the components of the $n$-copy Gibbs-rescaled distribution, $w(\rho_{\rm{S}} | \gamma)_{ijk}$ in decreasing order.
 In particular, to find the coordinates of the first elbow $(x_0, L_0)$, we need to evaluate the greatest component,
 \begin{align}
-	&\bmw(\noisys | \gamma)_{\rm{max}} \coloneqq \label{eq:max_slope}\\
+	&\bmw(\rho_{\rm{S}} | \gamma)_{\rm{max}} \coloneqq \label{eq:max_slope}\\
 	&(3\Z)^{n} \max\limits_{i,j,k}\Big\{ (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \nonumber
@@
 \begin{align}
-	&\bmw(\noisys | \gamma)_{\rm{max}} = \nonumber\\
+	&\bmw(\rho_{\rm{S}} | \gamma)_{\rm{max}} = \nonumber\\
 	&(3\Z)^{n} \max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ v^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta \alpha E_{\rm{max}}} \Big\}} =  \nonumber\\
@@
 \begin{equation}
-\bmw(\noisys | \gamma)_{\rm{max}} =
+\bmw(\rho_{\rm{S}} | \gamma)_{\rm{max}} =
 	\begin{cases}
@@
 
-In $\rm{(C1)}$, the multiplicity is $m_{000} = 1$ and the corresponding Wigner components are $\bmw(\noisys)_{000}, \bmw(\gamma)_{000}$.
-In $\rm{(C2)}$, we have $E_{\rm{max}} = E_1$ ($E_{\rm{max}} = E_2$), the multiplicity is $m_{0n0} = 3^n$ ($m_{00n} = 3^n$) and the corresponding Wigner components are $\bmw(\noisys)_{0n0}, \bmw(\gamma)_{0n0}$ ($\bmw(\noisys)_{00n}, \bmw(\gamma)_{00n}$).
+In $\rm{(C1)}$, the multiplicity is $m_{000} = 1$ and the corresponding Wigner components are $\bmw(\rho_{\rm{S}})_{000}, \bmw(\gamma)_{000}$.
+In $\rm{(C2)}$, we have $E_{\rm{max}} = E_1$ ($E_{\rm{max}} = E_2$), the multiplicity is $m_{0n0} = 3^n$ ($m_{00n} = 3^n$) and the corresponding Wigner components are $\bmw(\rho_{\rm{S}})_{0n0}, \bmw(\gamma)_{0n0}$ ($\bmw(\rho_{\rm{S}})_{00n}, \bmw(\gamma)_{00n}$).
 The first elbow coordinate expression can finally be expressed as
@@
 \begin{equation*}
-		\noisys(\epsilon)^{\otimes n} \xrightarrow{\E \in \O_{\gamma_\beta}} \noisys(\epsilon')^{\otimes n'} \otimes \gamma_\beta^{\otimes (n-n')},
+		\rho_{\rm{S}}(\epsilon)^{\otimes n} \xrightarrow{\E \in \O_{\gamma_\beta}} \rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \gamma_\beta^{\otimes (n-n')},
 \end{equation*}
@@
 \begin{equation}\label{eq:first_elbow_constraint}
-	\lc{\noisys(\epsilon)^{\otimes n}}{\gamma_\beta}(x_\star) \geq \lc{\noisys(\epsilon')^{\otimes n'}}{\gamma_\beta}(x_\star).
+	\lc{\rho_{\rm{S}}(\epsilon)^{\otimes n}}{\gamma_\beta}(x_\star) \geq \lc{\rho_{\rm{S}}(\epsilon')^{\otimes n'}}{\gamma_\beta}(x_\star).
 \end{equation}

### 2021-02-15 magic_paper.tex
Tidied analysis. Started statement of general theorem for stabilizer fragments. Questions raised at few points of analysis.

@@
 \item How does this rate compare with existing literature?
-\end{enumerate}
-If this bound is better than existing literature then great.
-I suspect not though.
-However, remember the core message of our work is that we're ``incorporating physical restrictions'' into the magic analysis.
-Given this, one thing that would round the paper off could be if we re-played the ``first elbow'' bound for some non-trivial temperature.
-Meaning: choose a ``nice'' Hamiltonian and compute the first elbow constraint via the thermo-majorization distortion of the Wigner components.
-This would then give us something clearly new -- namely a bound with temperature dependence!
-People would find this interesting since nothing like it exists yet.}
-
-\subsection{Magic in thermal fragments}\label{sec:thermal}
+\end{enumerate}}
+
+\newpage
+\section{Magic bounds in arbitrary stabilizer fragments}\label{sec:thermal}
+
+We now generalise the approach taken in the previous section and consider bounds on magic distillation for an arbitrary stabilizer fragment, $\R_\sigma$ where $\sigma$ is any quantum state $\sigma \in \rm{STAB}$.
+In other words we consider those bounds on distillation that apply when the free operations have $\sigma$ as a fixed point.
+
+These bounds can be interpreted in two different ways: on one hand they can be viewed as a family of upper bounds parameterized by a stabilizer state $\sigma$, on the other we can associate $\sigma$ to actual hardware limitations or to biased noise models in which it is an equilibrium state of some kind.
+Without loss of generality we can always write $\sigma = \frac{1}{\Z} e^{-\beta H}$ for some $\beta \ge 0$ and Hamiltonian $H$ (either effective or actual)\footnote{Technicalities arise for the case where $\sigma$ is not full rank, but this can be still described via $ \beta \rightarrow 0$ limiting process.}.
+
+Given this context, we can now state the following result, which is dependent on the free energy $F_\beta$ of a Gibbs state $\sigma$ where $ \beta F_\beta =  \beta\tr[H \sigma] - S(\sigma)$.
+We also fix the noisy Strange state to be of the form
+\begin{equation}
+	\rho_{\rm{S}}(\epsilon) \coloneqq (1-\epsilon)\ketbra{\rm{S}} + \epsilon \frac{1}{3}\id,
+\end{equation}
+but more general states can be handled in exactly the same manner.
+\begin{theorem}Let $\sigma$ be a qutrit stabilizer state, given by $\sigma = \frac{1}{\Z} e^{-\beta H}$ with $H$ having eigenvalues $E_0 \le E_1 \le E_2$, and where $\beta$ is an (effective) inverse temperature for the state.
+Then any distillation rate $R$ in the $\sigma$-fragment is bounded as follows.
+If \ddd{[Conditions]}
+\begin{equation}
+	R \leq 1 + \frac{\ln{\left( 1 - \frac{4}{3}\epsilon \right)}}{\beta (E_0 - F_\beta)},
+\end{equation}
+Or if \ddd{[I need to insert conditions]}
+\begin{equation}
+	R \le 1 + \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)} + (E_2 - E_0)(\beta_{\star} - \beta)}{\beta (E_0 - F_\beta)},
+\end{equation}
+Or finally if \ddd{[I need to insert conditions]}
+\begin{equation}
+	R \leq  1+ \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)}}{-\ln{2} + \beta (E_2 - F_\beta)},
+\end{equation}
+where
+\begin{equation}
+	\epsilon_{\star}(\beta) := 3 - \dfrac{18}{8-e^{(E_2 - E_0)\beta}}.
+\end{equation}
+is a threshold error rate.
+\end{theorem}
 
@@
 If the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than $1$ then the maximum occurs at $\alpha=0$, and otherwise the maximum occurs at $\alpha = n$.
-The threshold value of $1$ is achieved for this term when the noise level $\epsilon$ is equal to
+To determine this transition we set
+\begin{equation}
+\frac{u(\epsilon)}{v(\epsilon)} e^{\beta (E_{\rm{max}} - E_0)} =1,
+\end{equation}
+and solve for $\epsilon$ as a function of $\beta$. We denote the value value of $\epsilon$ for which this occurs $\epsilon_{\star}$ and find that it is equal to
 \begin{equation}
 	\epsilon_{\star}(\beta) := 3 - \dfrac{18}{8-e^{(E_{\rm{max}} - E_0)\beta}}.
-	%\beta \leq \frac{1}{E_{\rm{max}} - E_0}\ln{\left( 8-\frac{18}{3-\epsilon} \right)}
-\end{equation}
-For the case $E_{\rm{max}} = E_0$ this threshold is constant in temperature and given by Since $ E_{\rm max} - E_0 \ge 0$ the threshold $\epsilon_{\star}$ is a decreasing function of $\beta$, and it achieves its maximum value $3/7$ for $(E_{\rm{max}} - E_0)\beta = 0$, and a value equal to $0$ for
+\end{equation}
+For the case $E_{\rm{max}} = E_0$, namely the negative component overlaps the highest energy state distribution, this threshold is constant in temperature and given by $\epsilon_{\star} = 3/7$.
+
+Otherwise, we have that the negative component does not overlap with the highest energy state and so $ E_{\rm max} - E_0 > 0$.
+For this regime the threshold $\epsilon_{\star} (\beta)$ is a decreasing function of $\beta$, and it achieves its maximum value $3/7$ for $\beta = 0$, namely on the unital fragment.
+It also attains a value $0$ for
 \begin{equation}
@@
 For $\beta > \beta_{\star}$, $\epsilon_{\star}$ is negative, meaning that the noise level $\epsilon$ will always be higher than the threshold.
-We highlight that the threshold becomes $0$ when the difference between the maximum energy level and the level associated with the state negativity is equal to the energy extracted from a single particle Szilard's engine,
+\ddd{For $\beta \rightarrow \infty$ surely $\epsilon_{\star} \rightarrow 3$, and so it goes negative, but then goes positive again?
+I.e.
+there's another temperature region to consider.
+What am I missing here?}
+
+We note that the threshold becomes $0$ when the difference between the maximum energy level and the level associated with the state negativity is equal to the energy extracted from a single particle Szilard's engine,
 \begin{equation}
@@
 
-We now compute distillation bounds based on the first elbow constraint in the three possible scenarios.
+We now compute distillation bounds based on the first elbow constraint in the three possible scenarios. \ddd{[Does anything special happen if we have degeneracies in energy? ]}
 We express them in terms of the free energy of thermal state $\gamma_\beta$ denoted by

### 2021-02-16 magic_paper.tex
Replied to all comments, added scatter plot of Rate, made corrections to existing text. Next, I can try to plot the same scatter plot but for full majorization, or minus R_mana

@@
 Then any distillation rate $R$ in the $\sigma$-fragment is bounded as follows.
-If \ddd{[Conditions]}
+If $\beta \leq \beta_{\star}$ and $\epsilon' < \epsilon  \leq \epsilon_{\star}$,
 \begin{equation}
@@
 \end{equation}
-Or if \ddd{[I need to insert conditions]}
-\begin{equation}
-	R \le 1 + \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)} + (E_2 - E_0)(\beta_{\star} - \beta)}{\beta (E_0 - F_\beta)},
-\end{equation}
-Or finally if \ddd{[I need to insert conditions]}
+Or if $\beta \leq \beta_{\star}$ and $\epsilon' \leq \epsilon_{\star} < \epsilon$
+\begin{equation}
+	R \le 1 + \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)} - (E_2 - E_0)(\beta_{\star} - \beta)}{\beta (E_0 - F_\beta)},
+\end{equation}
+Or finally if $\beta > \beta_{\star}$
 \begin{equation}
@@
 \begin{equation}
-	\epsilon_{\star}(\beta) := 3 - \dfrac{18}{8-e^{(E_2 - E_0)\beta}}.
+	\beta_\star \coloneqq \frac{1}{E_2 - E_0} \ln{2}
+\end{equation}
+is a threshold temperature and for $\beta \leq \beta_\star$,
+\begin{equation}
+	\epsilon_{\star}(\beta) \coloneqq 3 - \dfrac{18}{8-e^{(E_2 - E_0)\beta}}.
 \end{equation}
@@
 (If it does, our analysis is still correct, but it simply could be improved).}
-\nick{This is in general true, will check if in our case it makes a difference}
+\nick{It can occur accidentally, but it doesn't make a difference for first elbow analysis, as we ``bring the top Lorenz curve down till its first elbow touches the bottom Lorenz curve''.
+Basically, Lorenz curves have fewer elbows, but because the first elbow constraint boils down to a ratio comparison~\cref{eq:first_elb_bound} it doesn't change the analysis.}
 
@@
     \caption{\textbf{Qutrit phase space regions with different Gibbs-rescaled values.}
-    The slope is negative in region $1$ and positive in regions $X,Y,Z$.
-    It attains a unique value in each region, given by~\cref{eq:bmw_rescaled} respectively.
+    The Gibbs-rescaled distribution attains a unique value in each region $1,X,Y,Z$, given by~\cref{eq:bmw_rescaled} respectively.
     }
@@
 \begin{equation}
-\frac{u(\epsilon)}{v(\epsilon)} e^{\beta (E_{\rm{max}} - E_0)} =1,
-\end{equation}
-and solve for $\epsilon$ as a function of $\beta$. We denote the value value of $\epsilon$ for which this occurs $\epsilon_{\star}$ and find that it is equal to
+	\frac{u(\epsilon)}{v(\epsilon)} e^{\beta (E_{\rm{max}} - E_0)} = 1.
+\end{equation}
+This can be rewritten as
+\begin{equation}\label{eq:noise_transition}
+	\frac{3-\epsilon}{6-8\epsilon} e^{\beta (E_{\rm{max}} - E_0)} = 1.
+\end{equation}
+The function $(3-\epsilon) / (6-8\epsilon)$ is increasing in $\epsilon$, achieving its minimum value $1/2$ at $\epsilon = 0$ and its maximum value $1$ at $\epsilon = 3/7$.
+We want to find in which cases there exists a threshold noise level $\epsilon_\star$ at which the transition in~\cref{eq:noise_transition} occurs.
+
+For the case $E_{\rm{max}} = E_0$, namely when the negative component overlaps the highest energy state distribution, this threshold is constant in temperature and given by $\epsilon_{\star} = 3/7$.
+
+There is a threshold temperature value $\beta_\star$ given by
+\begin{equation}
+	\beta_{\star} \coloneqq \frac{1}{E_{\rm{max}} - E_0} \ln2.
+\end{equation}
+Below the threshold temperature, $0 \leq \beta \leq \beta_\star$, the transition is well defined and the threshold noise level at which it occurs is given by
 \begin{equation}
@@
 \end{equation}
-For the case $E_{\rm{max}} = E_0$, namely the negative component overlaps the highest energy state distribution, this threshold is constant in temperature and given by $\epsilon_{\star} = 3/7$.
-
-Otherwise, we have that the negative component does not overlap with the highest energy state and so $ E_{\rm max} - E_0 > 0$.
-For this regime the threshold $\epsilon_{\star} (\beta)$ is a decreasing function of $\beta$, and it achieves its maximum value $3/7$ for $\beta = 0$, namely on the unital fragment.
-It also attains a value $0$ for
-\begin{equation}
-	\beta_{\star} \coloneqq \frac{1}{E_{\rm{max}} - E_0} \ln2.
-\end{equation}
-For $\beta > \beta_{\star}$, $\epsilon_{\star}$ is negative, meaning that the noise level $\epsilon$ will always be higher than the threshold.
-\ddd{For $\beta \rightarrow \infty$ surely $\epsilon_{\star} \rightarrow 3$, and so it goes negative, but then goes positive again?
-I.e.
-there's another temperature region to consider.
-What am I missing here?}
-
-We note that the threshold becomes $0$ when the difference between the maximum energy level and the level associated with the state negativity is equal to the energy extracted from a single particle Szilard's engine,
+This encompasses the case $E_{\rm{max}} = E_0$.
+
+We note that the threshold noise level $\epsilon_\star$ becomes $0$ when $\beta = \beta_\star$, namely the difference between the maximum energy level and the level associated with the state negativity is equal to the energy extracted from a single particle Szilard's engine,
 \begin{equation}
@@
 \end{equation}
+
+For $\beta > \beta_\star$, we have
+\begin{equation*}
+	\frac{3-\epsilon}{6-8\epsilon} e^{\beta (E_{\rm{max}} - E_0)} > \frac{3-\epsilon}{6-8\epsilon} 2 \geq \frac{1}{2}2 = 1,
+\end{equation*}
+so there is no transition and the threshold noise level remains $\epsilon_\star = 0$.
 
@@
 	This is the unital fragment.
-	\item $0 < \beta < \beta_{\star}$. Then, $0 < \epsilon_{\star} < 3/7$ and $\rm{(C1)}$ holds for $\epsilon \leq \epsilon_{\star}$, while $\rm{(C2)}$ holds for $\epsilon \geq \epsilon_{\star}$.
-	\item $\beta \geq \beta_{\star}$. Then, $ \epsilon_{\star} \leq 0$ and $\rm{(C2)}$ holds for all $\epsilon$.
+	\item $0 < \beta \leq \beta_{\star}$. Then, $0 \leq \epsilon_{\star} < 3/7$ and $\rm{(C1)}$ holds for $\epsilon \leq \epsilon_{\star}$, while $\rm{(C2)}$ holds for $\epsilon \geq \epsilon_{\star}$.
+	\item $\beta > \beta_{\star}$. Then, $ \epsilon_{\star} = 0$ and $\rm{(C2)}$ holds for all $\epsilon$.
 \end{itemize}
@@
 \end{enumerate}
-Note that $\rm{(C1)} \rightarrow \rm{(C2)}$ is impossible because it would imply $\epsilon \leq \epsilon_{\star} \leq \epsilon' < \epsilon$, a contradiction.
+Note that $\rm{(C1)} \rightarrow \rm{(C2)}$ is impossible because it would imply $\beta < \beta_{\star}$ and $\epsilon \leq \epsilon_{\star} \leq \epsilon' < \epsilon$, a contradiction.
 
@@
 We now compute distillation bounds based on the first elbow constraint in the three possible scenarios. \ddd{[Does anything special happen if we have degeneracies in energy? ]}
+\nick{If we have degeneracies, basically the Gibbs-rescaled distribution in~\cref{eq:bmw_rescaled} has some equal components, so Lorenz curves have fewer elbows, but because the first elbow constraint boils down to a ratio comparison~\cref{eq:first_elb_bound} it doesn't change the analysis}
 We express them in terms of the free energy of thermal state $\gamma_\beta$ denoted by
@@
 \begin{equation}
-	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\left( \frac{1}{1 - \frac{4}{3}\epsilon} \right)}}{\beta (E_0 - F_\beta)},
+	R \leq R(\epsilon, \beta) \coloneqq 1 - \frac{\ln{\left( \frac{1}{1 - \frac{4}{3}\epsilon} \right)}}{\beta (E_0 - F_\beta)},
 \end{equation}
@@
 \end{enumerate}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.5]{figs/noise_threshold.pdf}
+    \caption{\textbf{Noise threshold $\epsilon_\star$ and rate $R(\beta, \epsilon_\star)$ versus $\beta$.}
+    At $\beta = 0$ and threshold noise level $\epsilon = \epsilon_\star = 3/7$, the rate is $R(0, \epsilon_\star) = \frac{\ln{(9/7)}}{\ln{3}} \approx 0.23$.
+    }
+    \label{fig:noise_threshold}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.5]{figs/rate_contour.png}
+    \caption{\textbf{Rate $R(\beta, \epsilon)$ versus $\beta$ and $\epsilon$.}
+    The vertical dashed line indicates the temperature threshold $\beta_\star$ and the diagonal dashed curve indicates the noise threshold $\epsilon_\star$ at every $\beta \leq \beta_\star$.
+    }
+    \label{fig:rate_contour}
+\end{figure}
 
@@
     As $\beta$ increases, the range of noise levels for which $R(\beta)$ is valid decreases and the distillation bound becomes stricter.
-\nick{it holds for $0 \leq \epsilon \leq \epsilon_*$, where $\epsilon_\star$ is the noise level ($ \leq \epsilon_{\star}$) at which the state conversion turns from $\rm{(C1)} \rightarrow \rm{(C1)}$ to $\rm{(C2)} \rightarrow \rm{(C1)}$.
-Need to adjust~\cref{fig:distill_bounds_temp} accordingly}
     }

### 2021-02-17 magic_paper.tex
Phase space formalism, \bmx = (x, p) or (x0, x1) ? Define everything immediately in n-copy case or 1-copy case and then n-copy case or 1-copy case only?

@@
 
-Let $\{\ket{k}\}_{k \in \zd}$ be the standard computational basis for an arbitrary fault-tolerant scheme, defined over the finite field $\zd = \{ 0, 1, \dots,d-1 \}$, with $d$ an odd prime. 
+Let $\{\ket{k}\}_{k \in \mathbb{Z}_d}$ be the standard computational basis for an arbitrary fault-tolerant scheme, defined over the finite field $\mathbb{Z}_d = \{ 0, 1, \dots,d-1 \}$, with $d$ an odd prime.
 Since the field has character $d$, addition and multiplication on the field are always considered modulo $d$.
-The Hilbert space of any system associated with this scheme is $\hd \coloneqq \spanv{\ket{k}: k \in \zd}$.
+The Hilbert space of any system associated with this scheme is $\hd \coloneqq \spanv{\ket{k}: k \in \mathbb{Z}_d}$.
 
@@
 
-The Hilbert space $\hd$ is associated with a phase space $\pd \coloneqq \zd \times \zd$, where every point $\bmx \coloneqq (x_0, x_1)$ corresponds to a displacement operator, defined as
+The Hilbert space $\hd$ is associated with a phase space $\cal{P}_d \coloneqq \mathbb{Z}_d \times \mathbb{Z}_d$, where every point $\bmx \coloneqq (x, p)$ corresponds to a displacement operator, defined as
 \begin{equation}\label{eq:ddef}
-    D_{\bmx} \coloneqq \tau^{x_0 x_1} X^{x_0} Z^{x_1},\ \bmx  \in \pd.
+    D_{\bmx} \coloneqq \tau^{x p} X^{x} Z^{p},\ (x, p) \in \cal{P}_d.
 \end{equation}
 The phase factor $\tau \coloneqq -\omega^{1/2}$ ensures unitarity.
-For a system with composite Hilbert space, $\hd = \hd[d_A] \otimes \hd[d_B]$, the displacement operators are defined as
+For a composite system with Hilbert space, $\hd = \hd[d_1] \otimes \dots \otimes \hd[d_n]$, the displacement operators are defined as
 \begin{equation}\label{eq:composited}
-    D_{\bmx_A \oplus \bmx_B} \coloneqq D_{\bmx_A} \otimes D_{\bmx_B},
-\end{equation}
-where $\bmx_A \oplus \bmx_B \coloneqq (x_{A0}, x_{B0}, x_{A1}, x_{B1}) \in \pd[d_A] \times \pd[d_B]$.
-
-The displacement operators, form a group under matrix multiplication modulo phases,
+    D_{\bmx} \coloneqq D_{(x_1, p_1)} \otimes \dots \otimes D_{(x_n, p_n)},
+\end{equation}
+where 
+\begin{align}
+	\bmx \coloneqq (x_1, x_2, \dots, x_n, p_1, \dots, p_n) \in \cal{P}_{d_1} \times \dots \times \cal{P}_{d_n}.
+\end{align}
+
+The displacement operators form the Heisenberg-Weyl group \nick{CITE} under matrix multiplication modulo phases,
 \begin{equation}\label{eq:gp}
-    \gp \coloneqq \{ \tau^k D_{\bmz}: k \in \zd, \bmz \in \pd\}.
-\end{equation}
-The Clifford unitaries $\cd$ can then be defined as the normaliser of this group, \nick{Reformulate for copies of qudits: $\gp,\ \cd \rightarrow \gp^n,\ \cd^n$. $C-SUM$s live in $\cd^2$}
-\begin{equation}
-    \cd \coloneqq \{ U \in {\rm{SU}}(d): U\gp U^\dagger = \gp \}.
-\end{equation}
-The pure stabilizer states are then the orbit of the Clifford unitaries over a computational basis state,
+    {\rm{GP}}_d^n \coloneqq \{ \tau^k D_{\bmx}: k \in \mathbb{Z}_d, \bmx \in \cal{P}_d^n\}.
+\end{equation}
+The Clifford operations can be defined as the set of unitaries that normalise the Heisenberg-Weyl group,
+\begin{equation}
+    \cal{C}_d^n \coloneqq \{ U: U {\rm{GP}}_d^n U^\dagger = {\rm{GP}}_d^n \}.
+\end{equation}
+The pure stabilizer states can then defined as the orbit of the Clifford operations over a computational basis state,
 \begin{equation}\label{eq:stab}
-    \stab_{{\rm{pure}}} \coloneqq \{ U\ketbra{0}{0}U^\dagger: U \in \cd \}.
-\end{equation}
-
-The free states of the stabilizer theory are mixtures of pure stabilizers, 
+    \stab_{{\rm{pure}}} \coloneqq \{ U\ketbra{0}{0}U^\dagger: U \in \cal{C}_d^n\}.
+\end{equation}
+
+The stabilizer theory forms a magic resource theory $\R = (\stab, \so)$, where the free states are mixtures of pure stabilizers,
 \begin{equation}
@@
 \end{equation}
-The free operations of the stabilizer theory is the set of stabilizer operations $\so$ defined as any composition of:
+and the free operations ($\so$) are defined as compositions of:
 \begin{enumerate}
     \item Preparation in computational basis;
-    \item Random Clifford unitaries $\rcu$, i.e. operations $\E$ such that 
-    \begin{equation}
-        \E(\rho) = \sum_i p_i U_i \rho U_i^\dagger,\ U_i \in \cd;
+    \item Random Clifford unitaries ($\rcu$), i.e. operations $\E$ such that 
+    \begin{equation}
+        \E(\rho) = \sum_i p_i U_i \rho U_i^\dagger,\ U_i \in \cal{C}_d^n;
 \end{equation}
@@
 
-We can define the phase-point operators,
-\begin{align}
-	A_{\bmx} \coloneqq \frac{1}{d} \sum_{\bmz \in \pd} \omega^{\bmx \wedge \bmz} D_{\bmz},\ \bmx \in \pd. \label{eq:ax}
-\end{align}
-\nick{$\wedge$ has not be defined} They form an orthogonal Hermitian operator basis.
-Therefore, any quantum state $\rho \in \cal{B}(\hd)$ can be expressed as a linear combination of the phase-point operators,
-\begin{equation}
-    \rho = \sum_{\bmz \in \pd} \W[\bmz]{\rho} A_{\bmz},
+We define the phase-point operators at every phase space point $\bmx \in \cal{P}_d$,
+\begin{align}
+	A_{\bmx} \coloneqq \frac{1}{d} \sum_{\bmz \in \cal{P}_d} \omega^{\eta(\bmx, \bmz)} D_{\bmz}, \label{eq:ax}
+\end{align}
+where $\eta(\bmx, \bmz)$ is the standard symplectic form,
+\begin{equation}
+	\eta(\bmx, \bmz) \coloneqq \bmz^T \begin{pmatrix}
+		0  & 1 \\ %\mathbbm{O}_n  & \id_n \\
+		-1 & 0 \\ %-\id_n & \mathbbm{O}_n \\
+	\end{pmatrix} \bmx.
+\end{equation}
+
+The phase-point operators form an orthogonal Hermitian operator basis as shown in~\cref{app:wigner}.
+Therefore, any quantum state $\rho \in \cal{B}(\hd)$ can be expressed as a linear combination of them,
+\begin{equation}
+    \rho = \sum_{\bmz \in \cal{P}_d} \W[\bmz]{\rho} A_{\bmz},
 \end{equation}
@@
 \end{equation}
-It is in fact a real, bounded, $d^2$-dimensional quasi-probability distribution over $\pd$ as shown in~\cref{app:wigner}.
-
-The Wigner distributions of different types of qutrit states are illustrated in~\cref{fig:wstate_examples}.
+
+The state Wigner distribution is in fact a real, bounded, $d^2$-dimensional quasi-probability distribution over $\cal{P}_d$ as shown in~\cref{app:wigner}.
+
+In~\cref{fig:wstate_examples}, we visualise the Wigner distributions of different types of qutrit states.
 \begin{figure}%
@@
     \subref{fig:maxmix} Maximally mixed state $\frac{1}{3}\id$; \subref{fig:zero} Stabilizer zero state $\ketbra{0}{0}$; \subref{fig:bound} A non-stabilizer Wigner-positive state; \subref{fig:strange} Magic strange state $\ket{{\rm{S}}} = \frac{1}{\sqrt{2}}(\ket{1} - \ket{2})$ \nick{CITE}.
-    \nick{Explain what a magic state is in intro}
     }%
@@
 \end{align}
-where $\bm{\bar x} \coloneqq (x_0, -x_1)$.
+where $\bm{\bar x} \coloneqq (x, -p)$.
 
@@
 
-The single-qudit Hadamard gate $H$ and phase gate $S$ generate the $d$-dimensional Clifford group $\cd$. \nick{CITE}
+The single-qudit Hadamard gate $H$ and phase gate $S$ generate the $d$-dimensional Clifford group $\cal{C}_d$. \nick{CITE}
 Their Wigner distributions are given by permutation matrices,
@@
 \begin{equation}
-    \Fmax \coloneqq \{ \rho: \W[\bmz]{\rho} \geq 0 \text{ for all } \bmz \in \pd\}
+    \Fmax \coloneqq \{ \rho: \W[\bmz]{\rho} \geq 0 \text{ for all } \bmz \in \cal{P}_d\}
 \end{equation}
@@
 \begin{equation}
-    \Omax = \{ \E: \W[\bmy|\bmx]{\E} \geq 0 \text{ for all } \bmx, \bmy \in \pd\}.
+    \Omax = \{ \E: \W[\bmy|\bmx]{\E} \geq 0 \text{ for all } \bmx, \bmy \in \cal{P}_d\}.
 \end{equation}
@@
 
-    We can now view $\W{\E}$ as a stochastic, continuous mapping from $\cal{S}$ to itself, thus Brouwer's fixed point theorem \nick{CITE} implies that there exists a probability distribution $d_{\bmz}$ for some $ \bmz \in \pd$ that is a fixed point of $\W{\E}$.
-    This corresponds to a free state $\sigma \coloneqq \sum_{\bmz \in \pd} d_{\bmz} A_{\bmz} \in \F$. 
+    We can now view $\W{\E}$ as a stochastic, continuous mapping from $\cal{S}$ to itself, thus Brouwer's fixed point theorem \nick{CITE} implies that there exists a probability distribution $d_{\bmz}$ for some $ \bmz \in \cal{P}_d$ that is a fixed point of $\W{\E}$.
+    This corresponds to a free state $\sigma \coloneqq \sum_{\bmz \in \cal{P}_d} d_{\bmz} A_{\bmz} \in \F$. 
     Therefore $\E \in \O_\sigma$, and so $\O = \bigcup\limits_{\sigma \in \F} \O_\sigma$.
@@
 \begin{enumerate}
-    \item $S_{ij} \geq 0$ for all $i, j \in \zd$;
-    \item $\sum\limits_{j=1}^n S_{ij} = 1$ for all $i \in \zd$;
+    \item $S_{ij} \geq 0$ for all $i, j \in \mathbb{Z}_d$;
+    \item $\sum\limits_{j=1}^n S_{ij} = 1$ for all $i \in \mathbb{Z}_d$;
     \item $S\bmd = \bmd$.
@@
 
-    Finally, denote by $\pi: \zd \mapsto \zd$ the permutation that sorts $\tilde{\bmz}$, $(\tilde{\bmz}^\downarrow)_i = z_{\pi(i)}$ for all $i=1,\dots,d$.
+    Finally, denote by $\pi: \mathbb{Z}_d \mapsto \mathbb{Z}_d$ the permutation that sorts $\tilde{\bmz}$, $(\tilde{\bmz}^\downarrow)_i = z_{\pi(i)}$ for all $i=1,\dots,d$.
 
@@
 \begin{equation}\label{eq:dephase}
-	\Delta(\rho) = \sum_{k \in \zd} \ketbra{k}{k}\rho\ketbra{k}{k}
+	\Delta(\rho) = \sum_{k \in \mathbb{Z}_d} \ketbra{k}{k}\rho\ketbra{k}{k}
 \end{equation}
@@
 \begin{equation}
-    \E(\rho) = \sum_i p_i U_i \rho U_i^\dagger,\ U_i \in \cd.
+    \E(\rho) = \sum_i p_i U_i \rho U_i^\dagger,\ U_i \in \cal{C}_d.
 \end{equation}
@@
 \end{align}
-where $\bmx$ ranges in the $3$-dimensional phase space $\pd[3]$.
+where $\bmx$ ranges in the $3$-dimensional phase space $\cal{P}_d[3]$.
 This is the pure Strange state visualised in~\cref{fig:strange}.
@@
 \end{equation}
-at the 8 phase space points $\bmx \in \pd[3] \setminus \{\bmo\}$ and a negative component
+at the 8 phase space points $\bmx \in \cal{P}_d[3] \setminus \{\bmo\}$ and a negative component
 \begin{equation}
@@
 \end{align}
-for all $\bmx \in \pd[3]$. 
+for all $\bmx \in \cal{P}_d[3]$. 
 All Wigner components are strictly positive, therefore the pre-order $\prec_{\gamma_\beta}$ is well defined.
@@
 \end{equation}
-The multiplicative property of the Wigner distribution over a composite phase space $\pd[d_A] \times \pd[d_B]$,
+The multiplicative property of the Wigner distribution over a composite phase space $\cal{P}_d[d_A] \times \cal{P}_d[d_B]$,
 \begin{equation}

### 2021-02-18 magic_paper.tex
Checked Sec.III and IV. Comments left where I am unsure about what to write

@@
 \subsection{Stabilizer Theory}\label{sec:so}
+
+\nick{Should I define things in (a) 1-copy case only (b) $n$-copy case only (c) 1-copy case, then $n$-copy case ?}
 
@@
 The free operations should send the set of free states $\Fmax$ into itself and completely preserve the non-negativity of the states, in the sense that $\E \in \Omax$ iff $(\id_d \otimes \E ) \sigma \in \stab$ for all odd prime dimensions $d$ whenever $\sigma \in \Fmax$.
-It is shown by Wang \textit{et al.}~\cite{cit:wang} that $\Omax$ coincides with the set of operations $\E$ that correspond to stochastic Wigner distributions, 
+It is shown by Wang \textit{et al.}~\cite{cit:wang} that $\Omax$ coincides with the set of operations $\E$ with stochastic Wigner distributions, 
 \begin{equation}
@@
 
-Any magic theory $\R = (\F, \O)$ is a subtheory of $\Rmax$ as explained in~\cref{sec:intro}, and as such it falls under this new stochasticity setting. 
+Any magic theory $\R = (\F, \O)$ that has been proposed is a subtheory of $\Rmax$ in the sense that $\F \subseteq \Fmax$ and $\O \subseteq \Omax$, and as such it falls under this new stochasticity setting.
 For technical simplicity in what follows we assume that $\F$ is a closed set, and note that $\F_{\rm{ max}}$ is itself a closed set, since it is specified by a finite set of linear constraints of the form $\tr[ L\rho] \geq 0$ with operators $L \in \cal{B}(\cal{H})$ ensuring that the state is positive and Wigner-positive.
@@
 \begin{definition}[\textbf{$\boldsymbol\sigma$-fragment}]\label{def:sigmafrag}
-   Given a resource theory of magic $\R = (\F, \O)$, the \emph{$\sigma$--fragment of $\R$} is the resource theory $\R_\sigma = (\F, \O_\sigma)$, where the free operations are restricted to the ones that leave $\sigma$ invariant, namely
+   Given a resource theory of magic $\R = (\F, \O)$, the \emph{$\sigma$--fragment of $\R$} is the resource theory $\R_\sigma = (\F_\sigma, \O_\sigma)$, where $\F_\sigma = \{\sigma\}$ and the free operations are restricted to the ones that leave $\sigma$ invariant,
     \begin{equation}
@@
 
-With this basic notion defined, we now show that any resource theory of magic can be faithfully subdivided into $\sigma$--fragments, in such a way that any problem of interconversion in the parent magic theory $\R$ can be analysed across the different fragments.
+Note that $\F = \bigcup_{\sigma \in \F} \F_\sigma$ trivially.
+With this basic notion defined, we now show that this union holds for free operations as well and therefore that any resource theory of magic can be faithfully subdivided into $\sigma$--fragments, in such a way that any problem of interconversion in the parent magic theory $\R$ can be analysed across the different fragments.
 
@@
 \end{proof}
-
-The zoo of all magic operation classes is summarised in ~\cref{fig:zoo}.
-Completely positive-Wigner-preserving operations~\cite{cit:wang} form the operation class $\Omax$.
-Therefore, $\sigma$--fragments cover this theory of magic exactly and any magic subtheory is contained within this cover.
-In particular, the stabilizer operations $\so$ are contained within $\Omax$.
 \begin{figure}[t]
@@
 
+The zoo of all magic operation classes is summarised in ~\cref{fig:zoo}.
+Completely positive-Wigner-preserving operations~\cite{cit:wang} form the maximal operation class $\Omax$.
+This theory of magic is thus covered by $\sigma$--fragments exactly and every other magic theory is contained within this cover.
+In particular, the stabilizer operations $\so$ are contained within $\Omax$.
+
 The subdivision of magic theories into $\sigma$--fragments is powerful because the pre-order $\prec_{\R_\sigma}$ of every $\sigma$--fragment is described by well-behaved majorization tools, as we establish in~\cref{sec:major}.
@@
 Majorization is a collection of powerful tools that has recently found many applications in quantum information theory \nick{CITE}.
-It can describes the \nick{disorder / non-uniformity} of distributions that undergo stochastic transformations.
+It describes the \nick{disorder / non-uniformity} of distributions that undergo stochastic transformations.
 
 To formally state majorization results, we first denote by $\stoch$ the set of $(d \times d)$ stochastic matrices that preserve the probability vector $\bmd$.
-\nick{Should we introduce notation directly in the magic setting?}
 Specifically, for any $S \in \stoch$, all matrix elements are non-negative, all rows sum to $1$ and $S\bmd = \bmd$.
@@
 
-Majorization finds an important application on quantum thermodynamics in the absence of coherence.
-The use of majorization in this setting provides useful intuition for our purposes.
+Majorization exactly describes quantum thermodynamics in the absence of coherence.
+The use of majorization in this setting provides vital intuition for our purposes.
 At any given temperature $\beta^{-1}$, the thermal state $\gamma_\beta$ is thermodynamically the most disordered state. 
@@
 Convertibility between states via thermal operations is equivalent to a stochasticity condition on the energy level populations of the states \nick{CITE}.
-Roughly, the statement is that there exists a thermal operation $\E$ such that $\tau = \E(\rho)$ if and only if there exists a a matrix $S \in \stoch$ such that $\bm{q} = S\bm{p}$, where $\bm{q}, \bm{p}$ and $\bmd$ and the energy level population vectors of $\tau, \rho, \gamma_\beta$ respectively.
-
-Drawing intuition from this setting, we can define majorization as follows.
+Informally, there exists a thermal operation $\E$ such that $\tau = \E(\rho)$ if and only if there exists a matrix $S \in \stoch$ such that $\bm{q} = S\bm{p}$, where $\bm{q}, \bm{p}$ and $\bmd$ and the energy level population vectors of $\tau, \rho, \gamma_\beta$ respectively.
+
+Based on this setting, we define majorization as follows.
 \begin{definition}[\textbf{$\boldsymbol\bmd$-majorization}]\label{def:dmajor}
@@
 We denote this pre-order by $\bmx \prec_{\bmd} \bmy$.
-If $\bmd = \frac{1}{d}\bm{1}$, the $d$-dimensional uniform distribution, then $\stoch$ is the set of doubly stochastic matrices and we retrieve the familiar notion of majorization in entanglement theory.
+If $\bmd = \frac{1}{d}\bm{1}$, the $d$-dimensional uniform distribution, then $\stoch$ is the set of doubly stochastic matrices and we retrieve the familiar notion of majorization from entanglement theory.
 \nick{CITE}
 
-The pre-order $\prec_{\R_\sigma}$ of the $\sigma$--fragment $\R_\sigma = (\F, \O_\sigma)$ between $d$-dimensional states corresponds to the majorization pre-order $\prec_{\W{\sigma}}$ between their $d^2$-dimensional Wigner distributions.
+In any magic theory, we can pick a certain free state, for example a stabilizer and view it as the analog of some thermal state $\gamma_\beta$.
+Without loss of generality we can always write $\sigma = \frac{1}{\Z} e^{-\beta H}$ for some $\beta \ge 0$ and Hamiltonian $H$ (either effective or actual)\footnote{Technicalities arise for the case where $\sigma$ is not full rank, but this can be still described via $ \beta \rightarrow 0$ limiting process.}.
+It then defines a set of free operations $\O_\sigma$ analogous to the thermal operations that preserve $\gamma_\beta$ the pre-order $\prec_{\R_\sigma}$ between these operations follows the rules of $\bmd$-majorization.
+
+In particular, the pre-order $\prec_{\R_\sigma}$ of the $\sigma$--fragment $\R_\sigma = (\F, \O_\sigma)$ between $d$-dimensional states corresponds to the majorization pre-order $\prec_{\W{\sigma}}$ between their $d^2$-dimensional Wigner distributions.
 For simplicity we shall merge the notation into $\prec_\sigma$, as there is little risk of confusion.
@@
 This result can be understood as an extension of the idea of a magic monotone, where we replace $\M(\tau) \leq \M(\rho)$ with $\W{\tau} \prec_\sigma \W{\rho}$. 
-However the majorization constraints can be used to place upper bounds on magic state distillation in a way that allows one to incorporate the physics of the allowed operations -- this enables us to bound how much magic can be distilled via quantum operations that, for example, preserve the equilibrium state of the system, or via operations that are symmetric about the $Z$-axis of the Bloch sphere.
+The physical difference between the two expressions is that the majorization ordering occurs in a specific $\sigma$-fragment.
+Therefore, majorization constraints can be used to place upper bounds on magic state distillation in a way that allows one to incorporate the physics of the allowed operations -- specifically, it enables us to bound how much magic can be distilled via quantum operations that, for example, preserve the equilibrium state of the system, or via operations that are symmetric about the $Z$-axis of the Bloch sphere.
 
 This approach can also provide \emph{lower bounds} on distillation, however now more structure about the specific free operations must be included. 
-\nick{This is more involved and we discuss this later in the paper.
-Also mention relative majorization somewhere}
+\nick{This is more involved and we discuss this later in the paper.}
+
+\nick{Also mention relative majorization somewhere}
 
 \subsection{Majorization computations in $\sigma$--fragments}
-A numerically efficient reformulation of $\bmd$-majorization is provided by Lorenz curves.
+The pre-order imposed by $\bmd$-majorization admits a numerically efficient reformulation in terms of Lorenz curves.
 Let the vector $\bmu^\downarrow$ denote the vector $\bmu \in \reals^d$ with its components arranged in non-increasing order.
@@
     \begin{equation}\label{eq:lorenz}
-        (x_k, \lc{\bmz}{\bmd}(k)) \coloneqq \left( \frac{1}{D}\sum_{i=1}^k d_{\pi(i)}, \sum_{i=1}^k z_{\pi(i)} \right) \in \mathbb{R}^2.
+        (x_k, \lc{\bmz}{\bmd}(k)) \coloneqq \left( \frac{1}{D}\sum_{i=1}^k d_{\pi(i)}, \sum_{i=1}^k z_{\pi(i)} \right).
     \end{equation}
@@
 Furthermore, a Lorenz curve $\lc{\bmz}{\bmd}(x)$ is always concave in $x$, since it consists of $d$ line segments each with slope $(\tilde{\bmz}^\downarrow)_i$ for $i=1,\dots,d$ which is non-increasing by definition.
-Finally, points on the interior of the Lorenz curve connecting line segments of different slopes are called \emph{elbows}.
-
-A vector $\bmy$ \emph{$\bmd$--majorizes} another vector $\bmx$ if and only if the Lorenz curve $\lc{\bmy}{\bmd}$ lies above Lorenz curve $\lc{\bmx}{\bmd}$, thus reducing $\bmd$--majorization into a finite set of inequalities.
+Finally, the points on the interior of the Lorenz curve connecting line segments of different slopes are called \emph{elbows}.
+
+A vector $\bmy$ is said to \emph{$\bmd$--majorize} another vector $\bmx$ if and only if the Lorenz curve $\lc{\bmy}{\bmd}$ lies above Lorenz curve $\lc{\bmx}{\bmd}$, thus reducing $\bmd$--majorization into a finite set of inequalities.
 \begin{theorem}\label{thm:dmajor}

### 2021-02-22 appendix.tex
Phase space formalism, \bmx = (x, p) or (x0, x1) ? Define everything immediately in n-copy case or 1-copy case and then n-copy case or 1-copy case only?
Abstract changed. Re-ordered material on notation etc. Sharpened stabilizer fragment result+details.

@@
         \item\label{en:w1} Real valued: $\W{\rho} \in \mathbb{R}^{d^2}$;
-        \item\label{en:w2} Normalised: $\sum_{\bmz \in \pd} \W[\bmz]{\rho}=1$;
+        \item\label{en:w2} Normalised: $\sum_{\bmz \in \cal{P}_d} \W[\bmz]{\rho}=1$;
         \item\label{en:w3} Bounded: $\abs{\W[\bmx]{\rho}} \leq \frac{1}{d}$.
@@
         \item\label{en:wo1} Real-valued: $\W[\bmy|\bmx]{\E} \in \mathbb{R}$;
-        \item\label{en:wo2} Normalised: $\sum_{\bmz \in \pd[d_B]} \W[\bmz|\bmx]{\E} = 1$ for any $\bmx \in \pd[d_A]$;
+        \item\label{en:wo2} Normalised: $\sum_{\bmz \in \cal{P}_{d_B}} \W[\bmz|\bmx]{\E} = 1$ for any $\bmx \in \cal{P}_{d_A}$;
         \item\label{en:wo3} Bounded: $\abs{\W[\bmy|\bmx]{\E}} \leq \frac{d_A}{d_B}$;
-	    \item\label{en:wo4} \nick{Transitive}: $\W[\bmy]{\E(\rho)} = \sum_{\bmz \in \pd[d_A]} \W[\bmy|\bmz]{\E} \W[\bmz]{\rho}$ for any $\bmy \in \pd[d_B]$.
+	    \item\label{en:wo4} \nick{Transitive}: $\W[\bmy]{\E(\rho)} = \sum_{\bmz \in \cal{P}_{d_A}]} \W[\bmy|\bmz]{\E} \W[\bmz]{\rho}$ for any $\bmy \in \cal{P}_{d_B}$.
     \end{enumerate}
@@
 
+\subsection{Component-multiplicity pairs}
+
+In general, a $1$-copy $d$-dimensional state is defined exactly by its $d^2$ Wigner distribution $W$. 
+The distribution $W$ can always be described by a Wigner-component vector $\bmw = (w_i)_{i=1,\dots,D}$ and a multiplicity vector $\bmm = (m_i)_{i=1,\dots,D}$, where $D \leq d^2$ and they form component-multiplicity pairs denoted by $\{(w_i, m_i)\}_{i=1,\dots,D}$.
+\begin{definition}
+	Consider a $d^2$-dimensional distribution $W$ and a positive integer $D$. 
+	We call the set of order pairs $\{(w_i, m_i)\}_{i=1,\dots,D}$ a \emph{complete set of component-multiplicity pairs}, if $W$ contains $m_i$ components $w_i$ and $\sum_{i=0}^D m_i = d^2$.
+\end{definition}
+Therefore, such a set that describes a distribution $W$ contains in its description each component of $W$ exactly once.
+As an example, two complete sets of pairs for the Strange state are $\{( -1/3, 1), ( 1/6, 8)\}$ and $\{(-1/3, 1), (1/6, 2), (1/6, 3), (1/6, 3)\}$.
+
+Consider two states $\rho_A, \rho_B$ with Wigner distributions $\W{\rho_A}, \W{\rho_B}$ described respectively by complete sets of component-multiplicity pairs 
+\begin{equation}
+	\{(w_i, m_i)\}_{i=1,\dots,D_A} \text{ and } \{(w_j', m_j')\}_{j=0,\dots,D_B}.
+\end{equation}
+The multiplicative property of the Wigner distribution over a composite phase space $\cal{P}_d[d_A] \times \cal{P}_d[d_B]$,
+\begin{equation}
+	\W[\bmx_A \oplus \bmx_B]{\rho_A \otimes \rho_B} = \W[\bmx_A]{\rho_A}\W[\bmx_B]{\rho_B},
+\end{equation}
+implies that the distribution $\W{\rho_A \otimes \rho_B}$ is $d_A^2 d_B^2$-dimensional and contains components of the form $w_i w_j'$. 
+Therefore, the set $\{(w_i w_j', m_i m_j')\}$ with $i=1,\dots,D_A$ and $j=1,\dots,D_B$ is a complete set of component-multiplicity pairs for the distribution of the composite system $\W{\rho_A \otimes \rho_B}$.
+This is true because all components are of the form $w_i w_j'$ and 
+\begin{equation*}
+	\sum_{i=1}^{D_A}\sum_{j=1}^{D_B} m_i m_j' = \sum_{i=1}^{D_A} m_i \sum_{j=1}^{D_B} m_j' = d_A^2 d_B^2.
+\end{equation*}
+
+Given a state $\rho$ and a complete set of component-multiplicity pairs describing its Wigner distribution $\W{\rho}$, we now provide a method of computing the components (and multiplicities) of the $n$-copy distribution $\W{\rho}^{\otimes n}$.
+\begin{lemma}\label{lem:ncopycomponents}
+	Let $W$ be a $d$-dimensional distribution defined by a complete set of component-multiplicity pairs $\{(w_i, m_i)\}_{i=1,\dots,D}$ with $D \leq d$ and consider the distribution $W^{\otimes n}$ obtained by taking the Kronecker product $W \otimes \dots \otimes W$ between $n$ copies of $W$.
+
+	Denote by $C_D^n \coloneqq \{\bmk\}$ the set of all vectors $\bmk \coloneqq (k_1, \dots, k_D)$ with non-negative integer components that sum to $n$, i.e.
+	\begin{equation*}
+	0 \leq k_1, \dots, k_D \leq n \text{ and } k_1 + \dots + k_D = n.
+	\end{equation*}
+
+	Then, $W^{\otimes n}$ admits a complete set of component-multiplicity pairs $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$, where
+\begin{align}
+	M_{\bmk} &= \frac{n!}{k_1!\dots k_D!} \prod\limits_{i=1}^D {m_i}^{k_i}, \label{eq:M}\\
+	W_{\bmk} &= \prod\limits_{i=1}^D {w_i}^{k_i}. \label{eq:W}
+\end{align}
+\end{lemma}
+\begin{proof}
+	We proceed by induction.
+
+	Assume $n = 1$.
+	Let $\bmk_i \coloneqq (0,\dots,0,1,0,\dots,0)$ be a vector with its $i$-th component equal to 1 and 0's elsewhere.
+	The set $C_D^1$ consists of all vectors of this form, i.e. 
+\begin{equation*}
+	C_D^1 = \{ \bmk_i \}_{i=1,\dots,D}
+\end{equation*}
+	It is also true by direct calculation that
+\begin{equation*}
+	\left( W_{\bmk_i}, M_{\bmk_i} \right) = (w_i, m_i).
+\end{equation*}
+Therefore, $\{ (W_{\bmk}, M_{\bmk}) \}_{\bmk \in C_D^1}$ is a complete set of component-multiplicity pairs for $W$.
+
+	Assume that $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$ as given in~\cref{eq:M,eq:W} is a complete set of component-multiplicity pairs for the $n$-copy distribution $W^{\otimes n}$.
+	By construction, the distribution $W^{\otimes (n+1)} = W^{\otimes n} \otimes W$ is multiplicative, so it admits the complete set of component multiplicity pairs
+\begin{equation}
+	\{(W_{\bmk} w_i, M_{\bmk} m_i)\},\ \bmk \in C_D^n \text{ and } i=1,\dots,D.
+\end{equation}
+
+	Consider the component sum of the distribution $W^{\otimes (n+1)}$,
+\begin{align*}
+	&\sum_{\bmk \in C_D^n}\sum_{i=1}^D M_{\bmk} m_i W_{\bmk} w_i = \sum_{\bmk \in C_D^n} M_{\bmk}W_{\bmk} \sum_{i=1}^D m_i w_i =\\
+	&\sum_{\bmk \in C_D^n} \frac{n!}{k_1!\dots k_D!} \prod\limits_{i=1}^D {m_i}^{k_i}{w_i}^{k_i} \sum_{i=1}^D m_i w_i =\\
+	&\left( \sum_{i=1}^D m_i w_i \right)^n \left( \sum_{i=1}^D m_i w_i \right) = \left( \sum_{i=1}^D m_i w_i \right)^{n+1} =\\
+	&\sum_{\bmq \in C_D^{n+1}} M_{\bmq}W_{\bmq},
+\end{align*}
+where in the last expression, vectors $\bmq = (q_1, \dots, q_D)$ have non-negative integer components that sum to $(n+1)$ and 
+\begin{align*}
+	M_{\bmq} &= \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i},\\
+	W_{\bmq} &= \prod\limits_{i=1}^D {w_i}^{q_i}.
+\end{align*}
+We have used the multinomial theorem to proceed between lines 2-3 and lines 3-4 of the derivation.
+
+We have achieved a regrouping of the distribution components.
+Every component $W_{\bmq}$ is of the form $W_{\bmk} w_i$ with $q_i = k_i + 1$ and $q_j = k_j$ for $j\neq i$ and 
+\begin{align*}
+	\sum_{\bmq \in C_D^{n+1}}  \hspace{-6pt} M_{\bmq} =  \hspace{-10pt} \sum_{\bmq \in C_D^{n+1}} \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i} = 
+	\left( \sum_{i=1}^D m_i \right)^{n+1} \hspace{-10pt} = d^{n+1},
+\end{align*}
+which is the dimension of $W^{\otimes (n+1)}$.
+
+Therefore, $\{ (W_{\bmq}, M_{\bmq}) \}_{\bmq \in C_D^{n+1}}$ is a complete set of component-multiplicity pairs for $W^{\otimes n}$, completing the proof.
+\end{proof}
+
+\ddd{Note the following is relevant: you might have $W_{\bmq} = W_{\bmq'}$ for two different $\bmq$, $\bmq'$.
+This would make a difference to our calculations for the first elbow.
+Check this doesn't occur.
+(If it does, our analysis is still correct, but it simply could be improved).}
+\nick{It can occur accidentally, but it doesn't make a difference for first elbow analysis, as we ``bring the top Lorenz curve down till its first elbow touches the bottom Lorenz curve''.
+Basically, Lorenz curves have fewer elbows, but because the first elbow constraint boils down to a ratio comparison~\cref{eq:first_elb_bound} it doesn't change the analysis.}
 \subsection{Lorenz curve independent constraints}\label{app:lc_constraints}

### 2021-02-22 magic_paper.tex
Abstract changed. Re-ordered material on notation etc. Sharpened stabilizer fragment result+details.

@@
 \begin{abstract}
-Magic states are essential for achieving universality in fault-tolerant schemes.
-Magic resource theories attempt to quantify magic via monotones and thus describe the manipulation of magic states.
-Here we introduce the concept of majorization fragments as a more generalised projection of such theories in discrete odd dimensions which allows for more powerful results than what monotones can provide.
-Fragments naturally link the symmetries of a gate sequence with conditions on the convertibility between states.
-We demonstrate the power of fragments by providing exact conditions for the convertibility of single-copy qutrit magic states as well as stricter distillation bounds than the established mana monotone in any odd dimension.
+\ddd{[To be sharpened]} Magic states are key ingredients in schemes to realise universal fault-tolerant quantum computation.
+Theories of magic states attempt to quantify this computational element via monotones and determine how these states may be efficiently transformed into useful forms.
+Here we introduce the concept of `fragments', which generalise the concept of magic monotones and has a natural thermodynamic structure based on majorization.
+From this perspective magic can be viewed as a form of free energy within each fragment and is constrained by relative majorization relations but now on quasi-probability distributions.
+Notably this approach allows us to incorporate actual physical constraints, for example noise models with particular bias or temperature-dependent features, and study how these constrain general magic distillation protocols.
+In this context we present general temperature-dependent bounds on distillation rates that any theory of magic must respect.
+Significantly, this analysis also presents a thermodynamic context which cannot be analysed via traditional methods based on thermodynamic entropies, due to the presence of negativity, and raises novel questions in the context of statistical mechanics.
 \end{abstract}
@@
 
-\title{Thermodynamic fragments in magic state theories}
+\title{Thermodynamic fragments for magic states in quantum computation}
 
@@
 
-The stabilizer theory \nick{CITE} is the first theory to introduce the idea of magic and it is discussed in sufficient detail for our purposes in~\cref{sec:so}. 
-It comprises of the so-called ``stabilizer'' states ($\stab$) and operations ($\so$), while non-stabilizer (resource) states are called magic.
+\ddd{[Section needs a lot of fixing]}
+
+The stabilizer theory of magic comprises of the so-called ``stabilizer'' states ($\stab$) and operations ($\so$), while non-stabilizer (resource) states are called magic.
 The stabilizer operations can be expressed in terms of a Stinespring dilation as 
@@
 
-\ddd{Things we must emphasize:
+\ddd{Things we MUST emphasize:
 \begin{enumerate}
 \item Perhaps a nice lead-in question: ``What happens if we view stabilizer states as thermodynamic equilibrium states and magic as a form of free energy?''
-\item We can tackle more `physicsy' questions like: how much magic can be distilled via free operations with some given fixed-point structure? E.g. 
+\item We have found a scenario in which it is impossible to describe a thermodynamic structure using any entropic approach!
+\item We can tackle more `physicsy' questions like: how much magic can be distilled via available operations with some given fixed-point structure? 
 \item This allows a diagnostic on the kind of operations needed to do good distillation. I.e. what fixed point structure should they have?
-\item We go beyond magic monotones and replace a monotone with a $\sigma$-fragment.
+\item We go beyond the concept of monotones and replace a monotone with a $\sigma$-fragment.
 \item We can get both upper and lower bounds on magic distillation.
@@
 
+\newpage
 \section{Phase Space formalism}
@@
 
-\nick{Should I define things in (a) 1-copy case only (b) $n$-copy case only (c) 1-copy case, then $n$-copy case ?}
-
-Let $\{\ket{k}\}_{k \in \mathbb{Z}_d}$ be the standard computational basis for an arbitrary fault-tolerant scheme, defined over the finite field $\mathbb{Z}_d = \{ 0, 1, \dots,d-1 \}$, with $d$ an odd prime.
+Let $\{\ket{k}\}_{k \in \mathbb{Z}_d}$ be the standard computational basis, defined over $\mathbb{Z}_d = \{ 0, 1, \dots,d-1 \}$, with $d$ an odd prime. 
 Since the field has character $d$, addition and multiplication on the field are always considered modulo $d$.
@@
 \end{align}
-where $\omega \coloneqq e^{2\pi i/d}$ is the $d$-th root of unity.
-
+where $\omega \coloneqq e^{2\pi i/d}$ is the $d$-th root of unity and addition is modulo $d$.
 The Hilbert space $\hd$ is associated with a phase space $\cal{P}_d \coloneqq \mathbb{Z}_d \times \mathbb{Z}_d$, where every point $\bmx \coloneqq (x, p)$ corresponds to a displacement operator, defined as
@@
 \begin{align}
-	\bmx \coloneqq (x_1, x_2, \dots, x_n, p_1, \dots, p_n) \in \cal{P}_{d_1} \times \dots \times \cal{P}_{d_n}.
-\end{align}
+	\bmx \coloneqq (x_1, x_2, \dots, x_n, p_1, \dots, p_n) \in \cal{P}_{d_1} \times \dots \times \cal{P}_{d_n},
+\end{align}
+denotes the phase space point for an $n$--copy system.
 
@@
 \begin{equation}\label{eq:gp}
-    {\rm{GP}}_d^n \coloneqq \{ \tau^k D_{\bmx}: k \in \mathbb{Z}_d, \bmx \in \cal{P}_d^n\}.
-\end{equation}
-The Clifford operations can be defined as the set of unitaries that normalise the Heisenberg-Weyl group,
-\begin{equation}
-    \cal{C}_d^n \coloneqq \{ U: U {\rm{GP}}_d^n U^\dagger = {\rm{GP}}_d^n \}.
-\end{equation}
-The pure stabilizer states can then defined as the orbit of the Clifford operations over a computational basis state,
-\begin{equation}\label{eq:stab}
-    \stab_{{\rm{pure}}} \coloneqq \{ U\ketbra{0}{0}U^\dagger: U \in \cal{C}_d^n\}.
-\end{equation}
-
-The stabilizer theory forms a magic resource theory $\R = (\stab, \so)$, where the free states are mixtures of pure stabilizers,
-\begin{equation}
-    \stab = \conv\ \stab_{{\rm{pure}}}.
-\end{equation}
-and the free operations ($\so$) are defined as compositions of:
-\begin{enumerate}
-    \item Preparation in computational basis;
-    \item Random Clifford unitaries ($\rcu$), i.e. operations $\E$ such that 
-    \begin{equation}
-        \E(\rho) = \sum_i p_i U_i \rho U_i^\dagger,\ U_i \in \cal{C}_d^n;
-\end{equation}
-    \item Measurement in computational basis.
-\end{enumerate}
-
-\subsection{Wigner Distribution}\label{sec:wigner}
+    {\rm{HW}}_d^n \coloneqq \{ \tau^k D_{\bmx}: k \in \mathbb{Z}_d, \bmx \in \cal{P}_d^n\}.
+\end{equation}
+The Clifford operations $ \cal{C}_d^n $ are then defined as the set of unitaries that normalise the Heisenberg-Weyl group.
+We may define the pure stabilizer states as those states obtained by acting on $|0\>$ with Clifford unitaries.
+Finally, we define $\stab$ as the convex hull of all pure stabilizer states, namely all probabilistic mixtures of states of the form $U|0\>\<0|U^\dagger$ where $U$ is some Clifford unitary.
+The stabilizer theory forms a magic resource theory $\R = (\stab, \so)$
+and the free operations are stabilizer operations ($\so$), defined as compositions of preparation of computational basis states, Clifford unitaries, measurement in the computational basis, and the ability to discard subsystems.
+
+\subsection{Wigner representations for quantum states and quantum channels}\label{sec:wigner}
 
@@
 \end{align}
-where $\eta(\bmx, \bmz)$ is the standard symplectic form,
+where $\eta(\bmx, \bmz)$ is the standard symplectic form, given explicitly by
 \begin{equation}
 	\eta(\bmx, \bmz) \coloneqq \bmz^T \begin{pmatrix}
-		0  & 1 \\ %\mathbbm{O}_n  & \id_n \\
-		-1 & 0 \\ %-\id_n & \mathbbm{O}_n \\
+		0  & \I \\ %\mathbbm{O}_n  & \id_n \\
+		-\I & 0 \\ %-\id_n & \mathbbm{O}_n \\
 	\end{pmatrix} \bmx.
@@
 
-The state Wigner distribution is in fact a real, bounded, $d^2$-dimensional quasi-probability distribution over $\cal{P}_d$ as shown in~\cref{app:wigner}.
-
-In~\cref{fig:wstate_examples}, we visualise the Wigner distributions of different types of qutrit states.
+For any quantum state $\rho$, the Wigner distribution $W_\rho(\bmx)$ is readily seen to be a $d^2$-dimensional quasi-probability distribution over $\cal{P}_d$ (see~\cref{app:wigner} for details).
+In~\cref{fig:wstate_examples}, we show Wigner distributions of different types of qutrit states.
 \begin{figure}%
@@
 
-We can exploit the channel-state duality and use the normalised Choi-Jamio\l{}kowski state 
+We also have Wigner representations for general quantum channels. We may exploit the channel-state duality and use the normalised Choi-Jamio\l{}kowski state 
 \begin{equation}\label{eq:cj}
-    \frac{1}{d_A}\J(\E) \coloneqq \frac{1}{d_A}(\id \otimes \E) \sum_{i,j} \ket{ii}\bra{jj}
-\end{equation}
-to extend the definition of the Wigner distribution to quantum $\cptp$ operations $\E: \cal{B}(\hd[d_A]) \mapsto \cal{B}(\hd[d_B])$, 
+  \J(\E) \coloneqq \frac{1}{d_A}(\id \otimes \E) \sum_{i,j} \ket{ii}\bra{jj}
+\end{equation}
+to extend the definition of the Wigner distribution to a quantum channel $\E: \B(\H_A) \rightarrow \B(\H_B)$, via the expression
 \begin{align}\label{eq:woperation}
     \W[\bmy|\bmx]{\E} 
-    &\coloneqq d_A^2 \W[\bm{\bar x} \oplus \bmy]{\frac{1}{d_A}\J(\E)} \\
+    &\coloneqq d_A^2 \W[\bm{\bar x} \oplus \bmy]{\J(\E)} \\
     &= \frac{1}{d_B} \tr_B[A_{\bmy} \E(A_{\bmx})],
@@
     \centering
-        \includegraphics[scale=0.47
+        \includegraphics[scale=0.3
         ]{figs/operations.pdf}
@@
 \begin{theorem}\label{thm:sigmamajor}
-    Let $\R = (\F, \O)$ be a theory of magic. Then $\rho \longrightarrow \tau$ is possible \nick{only if}  $\W{\tau} \prec_\sigma \W{\rho}$ within a $\sigma$--fragment.
+    Let $\R = (\F, \O)$ be a theory of magic. If $\rho \longrightarrow \tau$  in $\R$ then  $\W{\tau} \prec_\sigma \W{\rho}$ within at least one $\sigma$--fragment.
 \end{theorem}
@@
 \begin{lemma}\label{lem:lcmax}
-	Given a quantum state $\rho$, the maximum of its Lorenz curve $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment in which it is defined and equal to $1+\sn{\rho}$.
+	Given a quantum state $\rho$, the maximum of its Lorenz curve $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment and is equal to $1+\sn{\rho}$.
 \end{lemma}
@@
 but more general states can be handled in exactly the same manner.
+In the following result we consider the bounds on distilling out pure states $|S\>\<S|$, with $\epsilon'=0$, but these bounds are easily generalised to purification bounds with $\epsilon' \ne 0$.
+Finally, we assume that $\epsilon \le 3/7$, so that the noisy magic state has non-zero negativity.
 \begin{theorem}Let $\sigma$ be a qutrit stabilizer state, given by $\sigma = \frac{1}{\Z} e^{-\beta H}$ with $H$ having eigenvalues $E_0 \le E_1 \le E_2$, and where $\beta$ is an (effective) inverse temperature for the state.
-Then any distillation rate $R$ in the $\sigma$-fragment is bounded as follows.
-If $\beta \leq \beta_{\star}$ and $\epsilon' < \epsilon  \leq \epsilon_{\star}$,
-\begin{equation}
-	R \leq 1 + \frac{\ln{\left( 1 - \frac{4}{3}\epsilon \right)}}{\beta (E_0 - F_\beta)},
-\end{equation}
-Or if $\beta \leq \beta_{\star}$ and $\epsilon' \leq \epsilon_{\star} < \epsilon$
-\begin{equation}
-	R \le 1 + \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)} - (E_2 - E_0)(\beta_{\star} - \beta)}{\beta (E_0 - F_\beta)},
-\end{equation}
-Or finally if $\beta > \beta_{\star}$
-\begin{equation}
-	R \leq  1+ \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)}}{-\ln{2} + \beta (E_2 - F_\beta)},
-\end{equation}
-where
+We define
 \begin{equation}
@@
 \end{equation}
-is a threshold temperature and for $\beta \leq \beta_\star$,
+and for $\beta \leq \beta_\star$ define
 \begin{equation}
@@
 \end{equation}
-is a threshold error rate.
+a threshold error rate. Then any distillation rate $R(\epsilon, \beta)$ in the $\sigma$-fragment of a magic theory is bounded as follows:
+
+If $\beta \leq \beta_{\star}$ and $\epsilon  \leq \epsilon_{\star}$,
+\begin{equation}
+	R(\epsilon,\beta) \leq 1 + \frac{\ln{\left( 1 - \frac{4}{3}\epsilon \right)}}{\beta (E_0 - F_\beta)}.
+\end{equation}
+If $\beta \leq \beta_{\star}$ and $\epsilon_{\star} < \epsilon$ then
+\begin{equation}
+	R(\epsilon, \beta) \le 1 + \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)} - (E_2 - E_0)(\beta_{\star} - \beta)}{\beta (E_0 - F_\beta)},
+\end{equation}
+Otherwise if $\beta > \beta_{\star}$
+\begin{equation}
+	R(\epsilon, \beta) \leq  1+ \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)}}{-\ln{2} + \beta (E_2 - F_\beta)}.
+\end{equation}
 \end{theorem}
+A few comments can be given on this result.
+Firstly, the specific numerical factors in $\epsilon_\star$ are a result of our choice of magic state.
+Secondly, these bounds can almost certainly be improved through a finer analysis of the Lorenz curve.
+The existing bounds follow by considering the dominant terms in the rescaled Wigner distribution and do not, for example, take into account the Lorenz curve's peak structure.
+Finally, it is striking that we obtain a Landauer-like condition with a characteristic temperature $kT_\star \ln 2 = E_2 - E_0$, where $kT_\star = \beta_\star^{-1}$.
+It is unclear whether this points to a generic feature that can be directly related to fundamental thermodynamic relations, such as the erasure cost of a single bit being $kT \ln 2$.
+Given that we work with qutrits this seems surprising, but does deserve further study.
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[scale=0.5]{figs/rate_contour.png}
+    \caption{\textbf{Bounds on magic distillation rates $R(\beta, \epsilon)$ within stabilizer fragments.}
+    The vertical dashed line is the `Landauer-like' temperature threshold $\beta_\star$ and the diagonal dashed curve corresponds to the noise threshold $\epsilon_\star (\beta)$ at every $\beta \leq \beta_\star$.
+The unital fragment corresponds to the $\beta =0 $ line.
+    }
+    \label{fig:rate_contour}
+\end{figure}
 
@@
 
-\subsubsection{Component-multiplicity pairs}
-
-\nick{Probably will move this subsection to the earlier section where we discuss phase spaces in general}
-
-In general, a $1$-copy $d$-dimensional state is defined exactly by its $d^2$ Wigner distribution $W$. 
-The distribution $W$ can always be described by a Wigner-component vector $\bmw = (w_i)_{i=1,\dots,D}$ and a multiplicity vector $\bmm = (m_i)_{i=1,\dots,D}$, where $D \leq d^2$ and they form component-multiplicity pairs denoted by $\{(w_i, m_i)\}_{i=1,\dots,D}$.
-\begin{definition}
-	Consider a $d^2$-dimensional distribution $W$ and a positive integer $D$. 
-	We call the set of order pairs $\{(w_i, m_i)\}_{i=1,\dots,D}$ a \emph{complete set of component-multiplicity pairs}, if $W$ contains $m_i$ components $w_i$ and $\sum_{i=0}^D m_i = d^2$.
-\end{definition}
-Therefore, such a set that describes a distribution $W$ contains in its description each component of $W$ exactly once.
-As an example, two complete sets of pairs for the Strange state are $\{( -1/3, 1), ( 1/6, 8)\}$ and $\{(-1/3, 1), (1/6, 2), (1/6, 3), (1/6, 3)\}$.
-
-Consider two states $\rho_A, \rho_B$ with Wigner distributions $\W{\rho_A}, \W{\rho_B}$ described respectively by complete sets of component-multiplicity pairs 
-\begin{equation}
-	\{(w_i, m_i)\}_{i=1,\dots,D_A} \text{ and } \{(w_j', m_j')\}_{j=0,\dots,D_B}.
-\end{equation}
-The multiplicative property of the Wigner distribution over a composite phase space $\cal{P}_d[d_A] \times \cal{P}_d[d_B]$,
-\begin{equation}
-	\W[\bmx_A \oplus \bmx_B]{\rho_A \otimes \rho_B} = \W[\bmx_A]{\rho_A}\W[\bmx_B]{\rho_B},
-\end{equation}
-implies that the distribution $\W{\rho_A \otimes \rho_B}$ is $d_A^2 d_B^2$-dimensional and contains components of the form $w_i w_j'$. 
-Therefore, the set $\{(w_i w_j', m_i m_j')\}$ with $i=1,\dots,D_A$ and $j=1,\dots,D_B$ is a complete set of component-multiplicity pairs for the distribution of the composite system $\W{\rho_A \otimes \rho_B}$.
-This is true because all components are of the form $w_i w_j'$ and 
-\begin{equation*}
-	\sum_{i=1}^{D_A}\sum_{j=1}^{D_B} m_i m_j' = \sum_{i=1}^{D_A} m_i \sum_{j=1}^{D_B} m_j' = d_A^2 d_B^2.
-\end{equation*}
-
-Given a state $\rho$ and a complete set of component-multiplicity pairs describing its Wigner distribution $\W{\rho}$, we now provide a method of computing the components (and multiplicities) of the $n$-copy distribution $\W{\rho}^{\otimes n}$.
-\begin{lemma}\label{lem:ncopycomponents}
-	Let $W$ be a $d$-dimensional distribution defined by a complete set of component-multiplicity pairs $\{(w_i, m_i)\}_{i=1,\dots,D}$ with $D \leq d$ and consider the distribution $W^{\otimes n}$ obtained by taking the Kronecker product $W \otimes \dots \otimes W$ between $n$ copies of $W$.
-
-	Denote by $C_D^n \coloneqq \{\bmk\}$ the set of all vectors $\bmk \coloneqq (k_1, \dots, k_D)$ with non-negative integer components that sum to $n$, i.e.
-	\begin{equation*}
-	0 \leq k_1, \dots, k_D \leq n \text{ and } k_1 + \dots + k_D = n.
-	\end{equation*}
-
-	Then, $W^{\otimes n}$ admits a complete set of component-multiplicity pairs $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$, where
-\begin{align}
-	M_{\bmk} &= \frac{n!}{k_1!\dots k_D!} \prod\limits_{i=1}^D {m_i}^{k_i}, \label{eq:M}\\
-	W_{\bmk} &= \prod\limits_{i=1}^D {w_i}^{k_i}. \label{eq:W}
-\end{align}
-\end{lemma}
-\begin{proof}
-	We proceed by induction.
-
-	Assume $n = 1$.
-	Let $\bmk_i \coloneqq (0,\dots,0,1,0,\dots,0)$ be a vector with its $i$-th component equal to 1 and 0's elsewhere.
-	The set $C_D^1$ consists of all vectors of this form, i.e. 
-\begin{equation*}
-	C_D^1 = \{ \bmk_i \}_{i=1,\dots,D}
-\end{equation*}
-	It is also true by direct calculation that
-\begin{equation*}
-	\left( W_{\bmk_i}, M_{\bmk_i} \right) = (w_i, m_i).
-\end{equation*}
-Therefore, $\{ (W_{\bmk}, M_{\bmk}) \}_{\bmk \in C_D^1}$ is a complete set of component-multiplicity pairs for $W$.
-
-	Assume that $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$ as given in~\cref{eq:M,eq:W} is a complete set of component-multiplicity pairs for the $n$-copy distribution $W^{\otimes n}$.
-	By construction, the distribution $W^{\otimes (n+1)} = W^{\otimes n} \otimes W$ is multiplicative, so it admits the complete set of component multiplicity pairs
-\begin{equation}
-	\{(W_{\bmk} w_i, M_{\bmk} m_i)\},\ \bmk \in C_D^n \text{ and } i=1,\dots,D.
-\end{equation}
-
-	Consider the component sum of the distribution $W^{\otimes (n+1)}$,
-\begin{align*}
-	&\sum_{\bmk \in C_D^n}\sum_{i=1}^D M_{\bmk} m_i W_{\bmk} w_i = \sum_{\bmk \in C_D^n} M_{\bmk}W_{\bmk} \sum_{i=1}^D m_i w_i =\\
-	&\sum_{\bmk \in C_D^n} \frac{n!}{k_1!\dots k_D!} \prod\limits_{i=1}^D {m_i}^{k_i}{w_i}^{k_i} \sum_{i=1}^D m_i w_i =\\
-	&\left( \sum_{i=1}^D m_i w_i \right)^n \left( \sum_{i=1}^D m_i w_i \right) = \left( \sum_{i=1}^D m_i w_i \right)^{n+1} =\\
-	&\sum_{\bmq \in C_D^{n+1}} M_{\bmq}W_{\bmq},
-\end{align*}
-where in the last expression, vectors $\bmq = (q_1, \dots, q_D)$ have non-negative integer components that sum to $(n+1)$ and 
-\begin{align*}
-	M_{\bmq} &= \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i},\\
-	W_{\bmq} &= \prod\limits_{i=1}^D {w_i}^{q_i}.
-\end{align*}
-We have used the multinomial theorem to proceed between lines 2-3 and lines 3-4 of the derivation.
-
-We have achieved a regrouping of the distribution components.
-Every component $W_{\bmq}$ is of the form $W_{\bmk} w_i$ with $q_i = k_i + 1$ and $q_j = k_j$ for $j\neq i$ and 
-\begin{align*}
-	\sum_{\bmq \in C_D^{n+1}}  \hspace{-6pt} M_{\bmq} =  \hspace{-10pt} \sum_{\bmq \in C_D^{n+1}} \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i} = 
-	\left( \sum_{i=1}^D m_i \right)^{n+1} \hspace{-10pt} = d^{n+1},
-\end{align*}
-which is the dimension of $W^{\otimes (n+1)}$.
-
-Therefore, $\{ (W_{\bmq}, M_{\bmq}) \}_{\bmq \in C_D^{n+1}}$ is a complete set of component-multiplicity pairs for $W^{\otimes n}$, completing the proof.
-\end{proof}
-
-\ddd{Note the following is relevant: you might have $W_{\bmq} = W_{\bmq'}$ for two different $\bmq$, $\bmq'$.
-This would make a difference to our calculations for the first elbow.
-Check this doesn't occur.
-(If it does, our analysis is still correct, but it simply could be improved).}
-\nick{It can occur accidentally, but it doesn't make a difference for first elbow analysis, as we ``bring the top Lorenz curve down till its first elbow touches the bottom Lorenz curve''.
-Basically, Lorenz curves have fewer elbows, but because the first elbow constraint boils down to a ratio comparison~\cref{eq:first_elb_bound} it doesn't change the analysis.}
-
 \subsubsection{Distillation bounds}
+
+Let $\sigma = \frac{1}{\Z} e^{-\beta H}$ be a stabilizer state, which is given in its eigen-decomposition as 
+\begin{equation}
+\sigma = \frac{1}{\Z} ( e^{-\beta E_0} |\varphi_0\>\< \varphi_0| + e^{-\beta E_1} |\varphi_1\>\< \varphi_1| + e^{-\beta E_2} |\varphi_2\>\< \varphi_2| ),
+\end{equation}
+where $\{|\varphi_k\>\}$ are pure, orthonormal stabilizer states.
+Therefore the exist a Clifford operation that takes $|\varphi_k\> \rightarrow |k\>$, with the effect of permuting the negative component of $\rho_S(\epsilon)$ in the discrete phase space.
 
@@
 
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.5]{figs/rate_contour.png}
-    \caption{\textbf{Rate $R(\beta, \epsilon)$ versus $\beta$ and $\epsilon$.}
-    The vertical dashed line indicates the temperature threshold $\beta_\star$ and the diagonal dashed curve indicates the noise threshold $\epsilon_\star$ at every $\beta \leq \beta_\star$.
-    }
-    \label{fig:rate_contour}
-\end{figure}
-
 Consider pure Strange state distillation at high temperatures, $\beta \leq \beta_{\star}$.

### 2021-02-24 magic_paper.tex
A bit stuck. Not sure how to edit stuff

@@
 Therefore, stabilizer-preserving theories have been extended to a theory that preserves state ``Wigner positivity''~\cite{cit:wang}, formally defined in~\cref{sec:wigner} for odd prime dimensions.
-Informally, it can be considered as the maximal theory of magic $\Rmax = (\Fmax, \Omax)$, where free states have non-negative Wigner distributions and free operations completely preserve this property.
+Informally, it can be considered as the maximal theory of magic $\Rmax = (\Fmax, \Omax)$, where free states have non-negative Wigner distributions and free operations completely preserve this property.\\
 
@@
 where 
-\begin{align}
-	\bmx \coloneqq (x_1, x_2, \dots, x_n, p_1, \dots, p_n) \in \cal{P}_{d_1} \times \dots \times \cal{P}_{d_n},
-\end{align}
+\begin{align*}
+	\bmx \coloneqq (x_1, p_1, x_2, p_2, \dots, x_n, p_n) \in \cal{P}_{d_1} \times \dots \times \cal{P}_{d_n},
+\end{align*}
 denotes the phase space point for an $n$--copy system.
@@
 	\eta(\bmx, \bmz) \coloneqq \bmz^T \begin{pmatrix}
-		0  & \I \\ %\mathbbm{O}_n  & \id_n \\
-		-\I & 0 \\ %-\id_n & \mathbbm{O}_n \\
+		0  & \id \\ %\mathbbm{O}_n  & \id_n \\
+		-\id & 0 \\ %-\id_n & \mathbbm{O}_n \\
 	\end{pmatrix} \bmx.
@@
     \caption{\textbf{Qutrit Wigner distributions of varying magic.} 
-    \subref{fig:maxmix} Maximally mixed state $\frac{1}{3}\id$; \subref{fig:zero} Stabilizer zero state $\ketbra{0}{0}$; \subref{fig:bound} A non-stabilizer Wigner-positive state; \subref{fig:strange} Magic strange state $\ket{{\rm{S}}} = \frac{1}{\sqrt{2}}(\ket{1} - \ket{2})$ \nick{CITE}.
+    \subref{fig:maxmix} Maximally mixed state $\frac{1}{3}\id$; \subref{fig:zero} Stabilizer zero state $\ketbra{0}{0}$; \subref{fig:bound} A non-stabilizer Wigner-positive state; \subref{fig:strange} Magic Strange state $\ket{{\rm{S}}} = \frac{1}{\sqrt{2}}(\ket{1} - \ket{2})$, coined in~\cite{cit:veitch2}.
     }%
@@
 
-The single-qudit Hadamard gate $H$ and phase gate $S$ generate the $d$-dimensional Clifford group $\cal{C}_d$. \nick{CITE}
+The single-qudit Hadamard gate $H$ and phase gate $S$ generate the $d$-dimensional Clifford group $\cal{C}_d$~\cite{cit:gottesman1998}.
 Their Wigner distributions are given by permutation matrices,
@@
 \end{align}
+\nick{Remove above paragraph?}
 
@@
 \begin{equation}
-    \Fmax \coloneqq \{ \rho: \W[\bmz]{\rho} \geq 0 \text{ for all } \bmz \in \cal{P}_d\}
+    \Fmax \coloneqq \{ \rho: \W[\bmx]{\rho} \geq 0 \text{ for all } \bmx \in \cal{P}_d\}
 \end{equation}
@@
 
-Any magic theory $\R = (\F, \O)$ that has been proposed is a subtheory of $\Rmax$ in the sense that $\F \subseteq \Fmax$ and $\O \subseteq \Omax$, and as such it falls under this new stochasticity setting.
+Every established magic theory $\R = (\F, \O)$ is a subtheory of $\Rmax$ in the sense that $\F \subseteq \Fmax$ and $\O \subseteq \Omax$, and as such it falls under this new stochasticity setting. 
 For technical simplicity in what follows we assume that $\F$ is a closed set, and note that $\F_{\rm{ max}}$ is itself a closed set, since it is specified by a finite set of linear constraints of the form $\tr[ L\rho] \geq 0$ with operators $L \in \cal{B}(\cal{H})$ ensuring that the state is positive and Wigner-positive.
@@
 In any magic theory, we can pick a certain free state, for example a stabilizer and view it as the analog of some thermal state $\gamma_\beta$.
-Without loss of generality we can always write $\sigma = \frac{1}{\Z} e^{-\beta H}$ for some $\beta \ge 0$ and Hamiltonian $H$ (either effective or actual)\footnote{Technicalities arise for the case where $\sigma$ is not full rank, but this can be still described via $ \beta \rightarrow 0$ limiting process.}.
+Without loss of generality we can always write a state $\sigma$ as a thermal state, $\sigma = \gamma_\beta \coloneqq \frac{1}{\Z} e^{-\beta H}$ for some $\beta \ge 0$ and Hamiltonian $H$ (either effective or actual)\footnote{Technicalities arise for the case where $\sigma$ is not full rank, but this can be still described via $ \beta \rightarrow 0$ limiting process.}.
 It then defines a set of free operations $\O_\sigma$ analogous to the thermal operations that preserve $\gamma_\beta$ the pre-order $\prec_{\R_\sigma}$ between these operations follows the rules of $\bmd$-majorization.
@@
 removes coherent phases in the computational basis and therefore leaves exactly all mixtures of computational basis states invariant.
-A model circuit consisting only of such dephasing channels can be fully analysed in the $\sigma$--fragments for the pure computational basis states $\sigma$ \nick{as seen in a theorem in the appendix}.
+A model circuit consisting only of such dephasing channels can be fully analysed in the $\sigma$--fragments for the pure computational basis states $\sigma$.
 
@@
 
-\section{Magic in unital and thermal fragments}\label{sec:unital}
+\section{Magic in the unital fragment}\label{sec:unital}
 The unital fragment encompasses the circuits which preserve the maximally mixed state ($\id/d$) and so it includes many important families of circuits.
@@
 In the following result we consider the bounds on distilling out pure states $|S\>\<S|$, with $\epsilon'=0$, but these bounds are easily generalised to purification bounds with $\epsilon' \ne 0$.
-Finally, we assume that $\epsilon \le 3/7$, so that the noisy magic state has non-zero negativity.
+Finally, we assume that $\epsilon \le 3/7$, so that the noisy magic state has \nick{a dominant negative component}.
 \begin{theorem}Let $\sigma$ be a qutrit stabilizer state, given by $\sigma = \frac{1}{\Z} e^{-\beta H}$ with $H$ having eigenvalues $E_0 \le E_1 \le E_2$, and where $\beta$ is an (effective) inverse temperature for the state.
@@
 \end{equation}
-If $\beta \leq \beta_{\star}$ and $\epsilon_{\star} < \epsilon$ then
+If $\beta \leq \beta_{\star}$ and $\epsilon_{\star} < \epsilon$, then
 \begin{equation}
@@
 \end{equation}
-Otherwise if $\beta > \beta_{\star}$
+Otherwise if $\beta > \beta_{\star}$,
 \begin{equation}
@@
     \includegraphics[scale=0.5]{figs/rate_contour.png}
-    \caption{\textbf{Bounds on magic distillation rates $R(\beta, \epsilon)$ within stabilizer fragments.}
+    \caption{\textbf{Bounds on magic distillation rates $R(\epsilon, \beta)$ within stabilizer fragments.}
     The vertical dashed line is the `Landauer-like' temperature threshold $\beta_\star$ and the diagonal dashed curve corresponds to the noise threshold $\epsilon_\star (\beta)$ at every $\beta \leq \beta_\star$.
@@
 \end{align}
-where $\bmx$ ranges in the $3$-dimensional phase space $\cal{P}_d[3]$.
+where $\bmx$ ranges in the $3$-dimensional phase space $\cal{P}_d$.
 This is the pure Strange state visualised in~\cref{fig:strange}.
@@
 
-In the previous section we introduced the notion of $\sigma$--fragments for any resource theory of magic.
+So far we have introduced the notion of $\sigma$--fragments for any resource theory of magic. 
 In this section we pause to generalise this concept to an arbitrary resource theory and explain precisely how it connects with resource monotones. 
 The busy reader more focussed on magic may skip this section.
-\nick{restate}
 
 State convertibility within a given resource theory is often a hard question to address due to the intricate structure of the theory.
-In general, the structure of a theory $\R$ is described by a pre-order $\prec_\R$ and usually resource monotones are employed to reduce this structure into a simple real number ordering\nick{CITE}.
-The subdivisions of magic theories into $\sigma$--fragments suggests a new approach towards investigating state convertibility which retains more structure of the origin theory than a measure can.
+In general, the structure of a theory $\R$ is described by a pre-order $\prec_\R$ and usually resource monotones are employed to reduce this structure into a simple real number ordering \nick{CITE}.
+The subdivisions of magic theories into $\sigma$--fragments suggests a new approach towards investigating state convertibility which retains more structure of the originaltheory than a measure can.
 

### 2021-02-24 appendix.tex
Tidied up before the mana section

@@
 
-\subsection{Mana properties}
-Mana monotonicity in any $\sigma$--fragment can be directly seen due to statement~\ref{en:tm3} in~\cref{thm:dmajor} for $t=0$.
-Furthermore, mana is additive due to the multiplicative property~\ref{en:w4} of~\cref{thm:wstate}.
+\begin{proposition}\label{thm:lccont}
+	The Lorenz curve $\lc{\rho}{\sigma}(x)$ of a state $\rho$ with respect to state $\sigma$ is uniformly continuous in $\sigma$.
+\end{proposition}
+\begin{proof}
+	If $\sigma$ and $\sigma'$ are $\delta$-close with respect to a state norm, then the curves $\lc{\rho}{\sigma}(x)$ and $\lc{\rho}{\sigma'}(x)$ are $\epsilon$-close at all $x \in [0,1]$.
+\end{proof}
 
@@
 
-\begin{theorem}\label{thm:frag}
+\begin{theorem}\label{thm:frag_app}
     Let $\R = (\O, \F)$ be a magic theory. 
@@
 \label{app:lc_properties}
+
+Single-copy Lorenz curves are simply additive in noise, 
+\begin{equation}
+\lc{(1-\epsilon)\rho + \epsilon\sigma}{\sigma} = (1-\epsilon)\lc{\rho}{\sigma} + \epsilon\lc{\sigma}{\sigma},
+\end{equation}
+for any $\sigma, \rho$.
+This is not true for higher number of copies.
 
@@
 \begin{lemma}\label{lem:comb_bounds}
-	For all $\ell\in [1,nf-1]$,
+	For all $\ell\in [1,np-1]$,
 	\begin{align}
-		&\left[ 8\ell\left(1-\frac{\ell}{nf}\right) \right]^{-\frac{1}{2}} 2^{nf S\left(\frac{\ell}{nf}\right)} \leq \binom{nf}{\ell} \leq \\
-		&\left[ 2\pi \ell\left(1-\frac{\ell}{nf}\right) \right]^{-\frac{1}{2}} 2^{nf S\left(\frac{\ell}{nf}\right)}.
+		&\left[ 8\ell\left(1-\frac{\ell}{np}\right) \right]^{-\frac{1}{2}} 2^{n S\left(\frac{\ell}{np}\right)} \leq \binom{np}{\ell} \leq \\
+		&\left[ 2\pi \ell\left(1-\frac{\ell}{np}\right) \right]^{-\frac{1}{2}} 2^{n S\left(\frac{\ell}{np}\right)}.
 	\end{align}
@@
 \begin{proof}
-	For $\ell = 1,2, nf-1, nf-2$ check by direct calculation.	
+	For $\ell = 1,2, np-1, np-2$ check by direct calculation.	
 	For all other cases, use Stirling's approximation. 
@@
 		\begin{split}
-		&\text{1. } \Phi_+(af; nf, p) \geq \sum\limits_{\ell=0}^{af/2}\left[ 16\ell\left(1-\frac{2\ell}{nf}\right) \right]^{-\frac{1}{2}} 2^{-nf\ent{\frac{2\ell}{nf}}{p}}, \\
-		&\hspace{14pt} \text{for all even } af\in [2,nf] \\
-		&\text{2. } \Phi_+(af; nf, p) \leq \sum\limits_{\ell=0}^{af/2}\left[ 4\pi\ell\left(1-\frac{2\ell}{nf}\right) \right]^{-\frac{1}{2}} 2^{-nf\ent{\frac{2\ell}{nf}}{p}}, \\
-		&\hspace{14pt} \text{for all even } af\in [2,nf] \\
-		&\text{3. } \Phi_-(af; nf, p) \geq \sum\limits_{\ell=1}^{(af-1)/2}\left[ 16(\ell+1)\left(1-\frac{2\ell+1}{nf}\right) \right]^{-\frac{1}{2}} \times \\
-		&\hspace{14pt} \times 2^{-nf\ent{\frac{2\ell+1}{nf}}{p}},\ \text{for all odd }af\in [1,nf] \\
-		&\text{4. } \Phi_-(af; nf, p) \leq \sum\limits_{\ell=1}^{(af-1)/2}\left[ 4\pi(\ell+1)\left(1-\frac{2\ell+1}{nf}\right) \right]^{-\frac{1}{2}} \times \\
-		&\hspace{14pt} \times 2^{-nf\ent{\frac{2\ell+1}{nf}}{p}},\ \text{for all odd } af\in [1,nf]
+		&\text{1. } \Phi_+(a; n, p) \geq \sum\limits_{\ell=0}^{np/2}\left[ 16\ell\left(1-\frac{2\ell}{np}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{2\ell}{nf}}{p}}, \\
+		&\hspace{14pt} \text{for all even } a\in [2,np] \\
+		&\text{2. } \Phi_+(a; n, p) \leq \sum\limits_{\ell=0}^{np/2}\left[ 4\pi\ell\left(1-\frac{2\ell}{nf}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{2\ell}{np}}{p}}, \\
+		&\hspace{14pt} \text{for all even } a\in [2,np] \\
+		&\text{3. } \Phi_-(a; n, p) \geq \sum\limits_{\ell=1}^{(np-1)/2}\left[ 16(\ell+1)\left(1-\frac{2\ell+1}{np}\right) \right]^{-\frac{1}{2}} \times \\
+		&\hspace{14pt} \times 2^{-n\ent{\frac{2\ell+1}{np}}{p}},\ \text{for all odd }a\in [1,np] \\
+		&\text{4. } \Phi_-(a; n, p) \leq \sum\limits_{\ell=1}^{(np-1)/2}\left[ 4\pi(\ell+1)\left(1-\frac{2\ell+1}{nf}\right) \right]^{-\frac{1}{2}} \times \\
+		&\hspace{14pt} \times 2^{-n\ent{\frac{2\ell+1}{np}}{p}},\ \text{for all odd } a\in [1,np]
 		\end{split}
@@
 
-\ddd{Note the following is relevant: you might have $W_{\bmq} = W_{\bmq'}$ for two different $\bmq$, $\bmq'$.
-This would make a difference to our calculations for the first elbow.
-Check this doesn't occur.
-(If it does, our analysis is still correct, but it simply could be improved).}
-\nick{It can occur accidentally, but it doesn't make a difference for first elbow analysis, as we ``bring the top Lorenz curve down till its first elbow touches the bottom Lorenz curve''.
-Basically, Lorenz curves have fewer elbows, but because the first elbow constraint boils down to a ratio comparison~\cref{eq:first_elb_bound} it doesn't change the analysis.}
 \subsection{Lorenz curve independent constraints}\label{app:lc_constraints}
 
-\begin{theorem}
-	Let $\rho, \tau$ be two quantum states with Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in the $\sigma$-fragment.
+\begin{theorem}\label{thm:elbows}
+	Let $\rho, \tau$ be two quantum states with Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in the $\sigma$--fragment.
 
-	Let $n'$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ and $E \coloneqq \{x_1, \dots, x_n'\}$ be their locations.
+	Let $t$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ at locations $x_1, \dots, x_t$.
 
-	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\tau}{\sigma}(x_{i})$ for all $i =1,\dots,n'$.
+	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\tau}{\sigma}(x_{i})$ for all $i =1,\dots,t$.
 \end{theorem}

### 2021-02-24 magic_paper.tex
Tidied up before the mana section

@@
 
-\section{Introduction}
-\label{sec:intro}
+\section{Introduction and background}
+\label{sec:intro_prev}
 
@@
     \item Bringing in majorization~\cite{cit:cwiklinski, cit:lostaglio2, cit:lostaglio, cit:gour, cit:janzing, cit:brandao2, cit:gour2, cit:marshall, cit:nielsen}
-    \item Section breakdown
 \end{enumerate}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Magic Resource Theories}
-\label{sec:magic}
-
 \subsection{Introduction}
+\label{sec:intro}
 
@@
 
-\subsection{Previous work}\label{sec:prev}
+\subsection{Previous work}
+\label{sec:prev}
 
@@
 \item This allows a diagnostic on the kind of operations needed to do good distillation. I.e. what fixed point structure should they have?
-\item We go beyond the concept of monotones and replace a monotone with a $\sigma$-fragment.
+\item We go beyond the concept of monotones and replace a monotone with a $\sigma$--fragment.
 \item We can get both upper and lower bounds on magic distillation.
@@
 \newpage
-\section{Phase Space formalism}
+\section{Preliminaries and definitions}
 \label{sec:ps}
@@
 where $\omega \coloneqq e^{2\pi i/d}$ is the $d$-th root of unity and addition is modulo $d$.
-The Hilbert space $\hd$ is associated with a phase space $\cal{P}_d \coloneqq \mathbb{Z}_d \times \mathbb{Z}_d$, where every point $\bmx \coloneqq (x, p)$ corresponds to a displacement operator, defined as
+The Hilbert space $\hd$ is associated with a phase space $\cal{P}_d = \mathbb{Z}_d \times \mathbb{Z}_d$, where every point $\bmx \coloneqq (x, p)$ corresponds to a displacement operator, defined as
 \begin{equation}\label{eq:ddef}
@@
 The phase factor $\tau \coloneqq -\omega^{1/2}$ ensures unitarity.
-For a composite system with Hilbert space, $\hd = \hd[d_1] \otimes \dots \otimes \hd[d_n]$, the displacement operators are defined as
+For a composite system with product dimension $d = d_1 \dots d_n$ and Hilbert space, $\hd = \hd[d_1] \otimes \dots \otimes \hd[d_n]$, the displacement operators are defined as
 \begin{equation}\label{eq:composited}
@@
 \begin{align*}
-	\bmx \coloneqq (x_1, p_1, x_2, p_2, \dots, x_n, p_n) \in \cal{P}_{d_1} \times \dots \times \cal{P}_{d_n},
+	\bmx \coloneqq (x_1, p_1, x_2, p_2, \dots, x_n, p_n) \in \cal{P}_{d_1} \times \dots \times \cal{P}_{d_n} \eqqcolon  \cal{P}_d,
 \end{align*}
@@
 
-\subsection{Wigner representations for quantum states and quantum channels}\label{sec:wigner}
+\subsection{Wigner representations for quantum states and quantum operations}\label{sec:wigner}
 
@@
 
-The single-qudit Hadamard gate $H$ and phase gate $S$ generate the $d$-dimensional Clifford group $\cal{C}_d$~\cite{cit:gottesman1998}.
-Their Wigner distributions are given by permutation matrices,
-\begin{align}
-    H &\coloneqq \frac{1}{\sqrt{d}}\sum_{j,k} \omega^{jk} \ketbra{j}{k}, \W[\bmy|\bmx]{H} = \delta_{y_0, -x_1}\delta_{y_1, x_0};\label{eq:H}\\
-    S &\coloneqq \sum_k \tau^{k(k+1)} \ketbra{k}{k}, \W[\bmy|\bmx]{S} = \delta_{y_0, x_0}\delta_{y_1, x_0 + x_1 + 2^{-1}}.\label{eq:S}
-\end{align}
-\nick{Remove above paragraph?}
+\subsection{Magic monotones}
+\label{sec:mono}
+
+We highlight the defining property of a monotone, as it is useful in later discussion.
+\begin{definition}[\textbf{Resource monotone}]\label{def:mono}
+    Let $\R = (\F, \O)$ be a resource theory.
+    A resource monotone $\M$ is a projection from the set of quantum states of the theory onto the real line, so that $\M$ is monotonically decreasing under free operations,
+    \begin{equation}
+        \M(\rho_1) \leq \M(\rho_2)\ \text{whenever}\ \rho_1 \prec_{\R} \rho_2.
+    \end{equation}
+\end{definition}
+
+\nick{We can skip mana and just discuss sum-negativity}
+One of the most fundamental and commonly used magic monotones is the \emph{mana} of a state~\cite{cit:veitch2}, defined as
+\begin{equation}
+    \mana{\rho} \coloneqq \ln{(2\hspace{1pt}\sn{\rho}+1)},
+\end{equation}
+where the \emph{sum-negativity} ($\rm{sn}$)~\cite{cit:veitch2} is the sum of the negative components in $\W{\rho}$,
+\begin{equation}
+    \sn{\rho} \coloneqq \sum\limits_{\bmx: \W[\bmx]{\rho} < 0} \abs{\W[\bmx]{\rho}}.
+\end{equation}
+Mana is an additive\footnote{It satisfies the condition $\mana{\rho_1 \otimes \rho_2} = \mana{\rho_1} + \mana{\rho_2}$ which is practical in distillation settings.} magic monotone, so it provides an analytical necessary condition for many-copy magic state interconvertibility.
+
+\subsection{Majorization}
+\label{sec:major}
+
+Majorization is a collection of powerful tools that has recently found many applications in quantum information theory \nick{CITE}.
+It describes the \nick{disorder / non-uniformity} of distributions that undergo stochastic transformations.
+
+To formally state majorization results, we first denote by $\stoch$ the set of $(d \times d)$ stochastic matrices that preserve the probability vector $\bmd$.
+Specifically, for any $S \in \stoch$, all matrix elements are non-negative, all rows sum to $1$ and $S\bmd = \bmd$.
+\iffalse
+\begin{enumerate}
+    \item $S_{ij} \geq 0$ for all $i, j \in \mathbb{Z}_d$;
+    \item $\sum\limits_{j=1}^n S_{ij} = 1$ for all $i \in \mathbb{Z}_d$;
+    \item $S\bmd = \bmd$.
+\end{enumerate}
+\fi
+The set $\stoch$ forms a group under matrix multiplication for all $\bmd$ with positive components.
+
+Majorization exactly describes quantum thermodynamics in the absence of coherence.
+The use of majorization in this setting provides vital intuition for our purposes.
+At any given temperature $\beta^{-1}$, the thermal state $\gamma_\beta$ is thermodynamically the most disordered state. 
+Thermal operations are defined as operations that cannot extract energy from the Gibbs state, $\E(\gamma_\beta) = \gamma_\beta$.
+Convertibility between states via thermal operations is equivalent to a stochasticity condition on the energy level populations of the states \nick{CITE}.
+Informally, there exists a thermal operation $\E$ such that $\tau = \E(\rho)$ if and only if there exists a matrix $S \in \stoch$ such that $\bm{q} = S\bm{p}$, where $\bm{q}, \bm{p}$ and $\bmd$ and the energy level population vectors of $\tau, \rho, \gamma_\beta$ respectively.
+
+Based on this setting, we define majorization as follows.
+\begin{definition}[\textbf{$\boldsymbol\bmd$-majorization}]\label{def:dmajor}
+    Given $\bmx, \bmy, \bmd \in \reals^d$, such that the components of $\bmd$ are positive, $\bmy$ is said to $\bmd$-majorize $\bmx$, iff there exists a matrix $S \in \stoch$ such that $\bmx = S\bmy$.
+\end{definition}
+We denote this pre-order by $\bmx \prec_{\bmd} \bmy$.
+If $\bmd = \frac{1}{d}\bm{1}$, the $d$-dimensional uniform distribution, then $\stoch$ is the set of doubly stochastic matrices and we retrieve the familiar notion of majorization from entanglement theory.
+\nick{CITE}
+
+The pre-order imposed by $\bmd$-majorization admits a numerically efficient reformulation in terms of Lorenz curves.
+Let the vector $\bmu^\downarrow$ denote the vector $\bmu \in \reals^d$ with its components arranged in non-increasing order.
+\begin{definition}[\textbf{Lorenz curve}]\label{def:lc}
+    Let $\bmz, \bmd \in \reals^d$, where the components of $\bmd$ are positive with $D = \sum_{i=1}^d d_i$ and denote by $\tilde{\bmz} \coloneqq (z_1/d_1, \dots, z_d/d_d)^T$ the vector of ratios between the corresponding components of $\bmz$ and $\bmd$.
+
+    Finally, denote by $\pi: \mathbb{Z}_d \mapsto \mathbb{Z}_d$ the permutation that sorts $\tilde{\bmz}$, $(\tilde{\bmz}^\downarrow)_i = z_{\pi(i)}$ for all $i=1,\dots,d$.
+
+    Consider the piecewise linear curve obtained by joining the points $\{(0,0)\} \cup \{ (x_k, \lc{\bmz}{\bmd}(k)) \}_{k=1,\dots,d}$, where
+    \begin{equation}\label{eq:lorenz}
+        (x_k, \lc{\bmz}{\bmd}(k)) \coloneqq \left( \frac{1}{D}\sum_{i=1}^k d_{\pi(i)}, \sum_{i=1}^k z_{\pi(i)} \right).
+    \end{equation}
+    We define the set of points on this curve, $\lc{\bmz}{\bmd}(x),\ x \in [0,1]$, as the \emph{Lorenz curve} of vector $\bmz$ with respect to $\bmd$.
+\end{definition}
+Components $x_k$ are rescaled by $D$ so that comparison of curves with unequal dimensions is possible.
+In fact, the Lorenz curves $\lc{\bmz}{\bmd}$ and $\lc{\bmz \otimes \bmd}{\bmd \otimes \bmd}$, where $\otimes$ denotes the Kronecker product, are identical.
+Furthermore, a Lorenz curve $\lc{\bmz}{\bmd}(x)$ is always concave in $x$, since it consists of $d$ line segments each with slope $(\tilde{\bmz}^\downarrow)_i$ for $i=1,\dots,d$ which is non-increasing by definition.
+Finally, the points on the interior of the Lorenz curve connecting line segments of different slopes are called \emph{elbows}.
+
+A vector $\bmy$ is said to \emph{$\bmd$--majorize} another vector $\bmx$ if and only if the Lorenz curve $\lc{\bmy}{\bmd}$ lies above Lorenz curve $\lc{\bmx}{\bmd}$, thus reducing $\bmd$--majorization into a finite set of inequalities.
+\begin{theorem}\label{thm:dmajor}
+    Let $\bmx, \bmy, \bmd \in \reals^d$, such that the components of $\bmd$ are positive. 
+    Then, $\bmx \prec_{\bmd} \bmy$ if and only if $\lc{\bmx}{\bmd}(x) \leq \lc{\bmy}{\bmd}(x)$ for all $x \in [0,1]$ with strict equality at $x=1$.
+\end{theorem}
+A restatement of the theorem including more equivalent conditions and a proof are provided in~\cref{app:major}.
 
@@
 
-\begin{theorem}
+\begin{theorem}\label{thm:frag}
     Let $\R = (\F, \O)$ be a theory of magic.
@@
 
-The subdivision of magic theories into $\sigma$--fragments is powerful because the pre-order $\prec_{\R_\sigma}$ of every $\sigma$--fragment is described by well-behaved majorization tools, as we establish in~\cref{sec:major}.
-
-\subsection{Majorization of quasi-probabilities in $\sigma$--fragments}\label{sec:major}
-
-Majorization is a collection of powerful tools that has recently found many applications in quantum information theory \nick{CITE}.
-It describes the \nick{disorder / non-uniformity} of distributions that undergo stochastic transformations.
-
-To formally state majorization results, we first denote by $\stoch$ the set of $(d \times d)$ stochastic matrices that preserve the probability vector $\bmd$.
-Specifically, for any $S \in \stoch$, all matrix elements are non-negative, all rows sum to $1$ and $S\bmd = \bmd$.
-\iffalse
-\begin{enumerate}
-    \item $S_{ij} \geq 0$ for all $i, j \in \mathbb{Z}_d$;
-    \item $\sum\limits_{j=1}^n S_{ij} = 1$ for all $i \in \mathbb{Z}_d$;
-    \item $S\bmd = \bmd$.
-\end{enumerate}
-\fi
-The set $\stoch$ forms a group under matrix multiplication for all $\bmd$ with positive components.
-
-Majorization exactly describes quantum thermodynamics in the absence of coherence.
-The use of majorization in this setting provides vital intuition for our purposes.
-At any given temperature $\beta^{-1}$, the thermal state $\gamma_\beta$ is thermodynamically the most disordered state. 
-Thermal operations are defined as operations that cannot extract energy from the Gibbs state, $\E(\gamma_\beta) = \gamma_\beta$.
-Convertibility between states via thermal operations is equivalent to a stochasticity condition on the energy level populations of the states \nick{CITE}.
-Informally, there exists a thermal operation $\E$ such that $\tau = \E(\rho)$ if and only if there exists a matrix $S \in \stoch$ such that $\bm{q} = S\bm{p}$, where $\bm{q}, \bm{p}$ and $\bmd$ and the energy level population vectors of $\tau, \rho, \gamma_\beta$ respectively.
-
-Based on this setting, we define majorization as follows.
-\begin{definition}[\textbf{$\boldsymbol\bmd$-majorization}]\label{def:dmajor}
-    Given $\bmx, \bmy, \bmd \in \reals^d$, such that the components of $\bmd$ are positive, $\bmy$ is said to $\bmd$-majorize $\bmx$, iff there exists a matrix $S \in \stoch$ such that $\bmx = S\bmy$.
-\end{definition}
-We denote this pre-order by $\bmx \prec_{\bmd} \bmy$.
-If $\bmd = \frac{1}{d}\bm{1}$, the $d$-dimensional uniform distribution, then $\stoch$ is the set of doubly stochastic matrices and we retrieve the familiar notion of majorization from entanglement theory.
-\nick{CITE}
-
-In any magic theory, we can pick a certain free state, for example a stabilizer and view it as the analog of some thermal state $\gamma_\beta$.
-Without loss of generality we can always write a state $\sigma$ as a thermal state, $\sigma = \gamma_\beta \coloneqq \frac{1}{\Z} e^{-\beta H}$ for some $\beta \ge 0$ and Hamiltonian $H$ (either effective or actual)\footnote{Technicalities arise for the case where $\sigma$ is not full rank, but this can be still described via $ \beta \rightarrow 0$ limiting process.}.
-It then defines a set of free operations $\O_\sigma$ analogous to the thermal operations that preserve $\gamma_\beta$ the pre-order $\prec_{\R_\sigma}$ between these operations follows the rules of $\bmd$-majorization.
-
+Every  quantum circuit aiming at a given magic state conversion $\rho \longrightarrow \tau$ possesses certain symmetries according to~\cref{thm:frag} that allow us to study the conversion within only certain $\sigma$--fragments that reflect these symmetries.
+As a simple example, the dephasing channel
+\begin{equation}\label{eq:dephase}
+	\Delta(\rho) = \sum_{k \in \mathbb{Z}_d} \ketbra{k}{k}\rho\ketbra{k}{k}
+\end{equation}
+removes coherent phases in the computational basis and therefore leaves exactly all mixtures of computational basis states invariant.
+A noise channel consisting only of such dephasing operations can be fully analysed in the $\sigma$--fragments for the pure computational basis states $\sigma$.
+\nick{Have proven in appendix that we need to consider \emph{only} the pure stabilizer fragments - not mixed ones}
+
+The subdivision of magic theories into $\sigma$--fragments is also powerful because the pre-order $\prec_{\R_\sigma}$ of every $\sigma$--fragment is described by well-behaved majorization tools, as we establish in the rest of this section.
+
+\subsection{Majorization of quasi-probabilities in $\sigma$--fragments}\label{sec:major_frag}
+
+We can approach any magic theory through a thermodynamic lens, and in doing so we are provided with valuable insights on the structure of the theory. 
+Firstly, any free state, for example a stabilizer state, can be viewed as a thermal state $\gamma_\beta$.
+Without loss of generality we can always write a quantum state $\sigma$ as a thermal state, $\sigma = \gamma_\beta \coloneqq \frac{1}{\Z_\beta} e^{-\beta H}$ for some $\beta \geq 0$ and Hamiltonian $H$ (either effective or actual)\footnote{Technicalities arise for the case where $\sigma$ is not full rank, but this can be still described via $ \beta \rightarrow 0$ limiting process.}.
+We can also view the set of free operations $\O_\sigma$ as a counterpart of thermal operations, in the sense that any operation $\E$ in $\O_\sigma$ preserves state $\sigma$.
+
+It is then apparent that the pre-order $\prec_{\R_\sigma}$ between the operations in the $\sigma$--fragment follows the rules of $\bmd$-majorization as outlined in~\cref{sec:major}.
 In particular, the pre-order $\prec_{\R_\sigma}$ of the $\sigma$--fragment $\R_\sigma = (\F, \O_\sigma)$ between $d$-dimensional states corresponds to the majorization pre-order $\prec_{\W{\sigma}}$ between their $d^2$-dimensional Wigner distributions.
 For simplicity we shall merge the notation into $\prec_\sigma$, as there is little risk of confusion.
+
+Note that the Wigner components of an $n$-copy state $\rho^{\otimes n}$ can be calculated directly from $\W{\rho}$ by convolution of the distribution with itself,
+\begin{equation}
+	\W{\rho^{\otimes n}} = \rm{W}_{\rho}^{\otimes n},
+\end{equation}
+where $\otimes$ can be interpreted as the usual Kroenecker product in the last expression.
+
+Furthermore, we restrict our analysis to $\sigma$--fragments, where $\sigma$ is full-rank.
+This is justified as majorization is continuous between fragments, in the sense that the pre-orders $\prec_\sigma$ and $\prec_{\sigma'}$ are equivalent for states $\sigma$ and $\sigma'$ which are $\epsilon$-close.
+\nick{CHECK}
+Therefore, majorization analysis is robust under imperfections in the experimental implementation of quantum operations.
+
+In particular, any $\sigma$--fragment, with $\sigma$ not full-rank, can be approximated by the $\sigma'$--fragment defined as a mixture of $\sigma$ with uniform noise, $\sigma' = (1-\epsilon)\sigma + \epsilon\frac{1}{d}\id$, for some infinitesimal $\epsilon > 0$, so that $\sigma'$ is full-rank and arbitrarily close to $\sigma$.
+There exist many $\sigma$--fragments with $\sigma$ not full-rank, such as when $\sigma$ is a pure stabilizer, e.g. the zero state as depicted in~\cref{fig:zero}. 
+Operations in such fragments include important stabilizer operations like the replacement channel defined as $\E(\rho) = \sigma$ for all states $\rho$.
 
@@
 Therefore, the Wigner distribution of this free operation satisfies $\W{\E} \in \stochw$ and $\W{\E}\W{\rho} = \W{\tau}$. 
-Since $\sigma$ is \nick{full-rank} and free, its Wigner distribution is strictly positive in all components, so it directly follows from~\cref{def:dmajor} that $\W{\tau} \prec_{\sigma} \W{\rho}$.
+Since $\sigma$ is full-rank and free, its Wigner distribution is strictly positive in all components, so it directly follows from~\cref{def:dmajor} that $\W{\tau} \prec_{\sigma} \W{\rho}$.
+
+\nick{The theorem statement and proof currently assume that $\sigma$ is full-rank}
 \end{proof}
-This result can be understood as an extension of the idea of a magic monotone, where we replace $\M(\tau) \leq \M(\rho)$ with $\W{\tau} \prec_\sigma \W{\rho}$. 
-The physical difference between the two expressions is that the majorization ordering occurs in a specific $\sigma$-fragment.
+
+The result of~\cref{thm:sigmamajor} can be understood as an extension of the idea of a magic monotone, where we replace $\M(\tau) \leq \M(\rho)$ with $\W{\tau} \prec_\sigma \W{\rho}$. 
+The physical difference between the two expressions is that the majorization ordering occurs in a specific $\sigma$--fragment.
 Therefore, majorization constraints can be used to place upper bounds on magic state distillation in a way that allows one to incorporate the physics of the allowed operations -- specifically, it enables us to bound how much magic can be distilled via quantum operations that, for example, preserve the equilibrium state of the system, or via operations that are symmetric about the $Z$-axis of the Bloch sphere.
+We discuss distillation upper bounds in~\nick{REF}
 
 This approach can also provide \emph{lower bounds} on distillation, however now more structure about the specific free operations must be included. 
-\nick{This is more involved and we discuss this later in the paper.}
-
-\nick{Also mention relative majorization somewhere}
+We discuss distillation lower bounds in~\nick{REF}
+
+\nick{Mention relative majorization as a possibility}
 
 \subsection{Majorization computations in $\sigma$--fragments}
-The pre-order imposed by $\bmd$-majorization admits a numerically efficient reformulation in terms of Lorenz curves.
-Let the vector $\bmu^\downarrow$ denote the vector $\bmu \in \reals^d$ with its components arranged in non-increasing order.
-\begin{definition}[\textbf{Lorenz curve}]\label{def:lc}
-    Let $\bmz, \bmd \in \reals^d$, where the components of $\bmd$ are positive with $D = \sum_{i=1}^d d_i$ and denote by $\tilde{\bmz} \coloneqq (z_1/d_1, \dots, z_d/d_d)^T$ the vector of ratios between the corresponding components of $\bmz$ and $\bmd$.
-
-    Finally, denote by $\pi: \mathbb{Z}_d \mapsto \mathbb{Z}_d$ the permutation that sorts $\tilde{\bmz}$, $(\tilde{\bmz}^\downarrow)_i = z_{\pi(i)}$ for all $i=1,\dots,d$.
-
-    Consider the piecewise linear curve obtained by joining the points $\{(0,0)\} \cup \{ (x_k, \lc{\bmz}{\bmd}(k)) \}_{k=1,\dots,d}$, where
-    \begin{equation}\label{eq:lorenz}
-        (x_k, \lc{\bmz}{\bmd}(k)) \coloneqq \left( \frac{1}{D}\sum_{i=1}^k d_{\pi(i)}, \sum_{i=1}^k z_{\pi(i)} \right).
-    \end{equation}
-    We define the set of points on this curve, $\lc{\bmz}{\bmd}(x),\ x \in [0,1]$, as the \emph{Lorenz curve} of vector $\bmz$ with respect to $\bmd$.
-\end{definition}
-Components $x_k$ are rescaled by $D$ so that comparison of curves with unequal dimensions is possible.
-In fact, the Lorenz curves $\lc{\bmz}{\bmd}$ and $\lc{\bmz \otimes \bmd}{\bmd \otimes \bmd}$, where $\otimes$ denotes the Kronecker product, are identical.
-Furthermore, a Lorenz curve $\lc{\bmz}{\bmd}(x)$ is always concave in $x$, since it consists of $d$ line segments each with slope $(\tilde{\bmz}^\downarrow)_i$ for $i=1,\dots,d$ which is non-increasing by definition.
-Finally, the points on the interior of the Lorenz curve connecting line segments of different slopes are called \emph{elbows}.
-
-A vector $\bmy$ is said to \emph{$\bmd$--majorize} another vector $\bmx$ if and only if the Lorenz curve $\lc{\bmy}{\bmd}$ lies above Lorenz curve $\lc{\bmx}{\bmd}$, thus reducing $\bmd$--majorization into a finite set of inequalities.
-\begin{theorem}\label{thm:dmajor}
-    Let $\bmx, \bmy, \bmd \in \reals^d$, such that the components of $\bmd$ are positive. 
-    Then, $\bmx \prec_{\bmd} \bmy$ if and only if $\lc{\bmx}{\bmd}(x) \leq \lc{\bmy}{\bmd}(x)$ for all $x \in [0,1]$ with strict equality at $x=1$.
-\end{theorem}
-A restatement of the theorem including more equivalent conditions and a proof are provided in~\cref{app:major}.
+
+It is straightforward to construct Lorenz curves for Wigner distributions in any $\sigma$--fragment.
+As we have seen in~\cref{thm:sigmamajor}, for any full-rank free state $\sigma$ we have that $\W{\sigma}$ is a strictly positive full-rank probability distribution, and so one can define a corresponding notion of $d$--majorization on \emph{quasi}--distributions.
+We write $\lc{\rho}{\sigma}(x)$ for the Lorenz curve of $\W{\rho}$ with respect to $\W{\sigma}$.
+
 An example of comparison between different Lorenz curves is illustrated in~\cref{fig:lctoy}.
+The curves in the figure are constructed in the \emph{unital fragment}, i.e. the $\sigma$--fragment defined by the maximally mixed state $\sigma = \frac{1}{d}\id$.
+In~\cref{fig:lcs}, we illustrate the Lorenz curves of pure and noisy $n$-copy Strange states for $n$ up to $4$ in different $\sigma$--fragments.
 \begin{figure}
@@
     Curves $L_k(\bmx|\bmd)$ and $L_k(\bmy|\bmd)$ intersect, so $\bmx \nprec_{\bmd} \bmy$ as well as $\bmy \nprec_{\bmd} \bmx$.
-    \nick{Recast in terms of magic - replace with~\cref{fig:test}?}
+    \nick{RECAST}
     }
@@
 \end{figure}
-
-It is now straightforward to construct Lorenz curves for Wigner distributions in any $\sigma$--fragment.
-As we have seen in~\cref{thm:sigmamajor}, for any full-rank free state $\sigma$ we have that $\W{\sigma}$ is a strictly positive full-rank probability distribution, and so one can define a corresponding notion of $d$--majorization on \emph{quasi}--distributions.
-We write $\lc{\rho}{\sigma}(x)$ for the Lorenz curve of $\W{\rho}$ with respect to $\W{\sigma}$.
-
-We now establish important properties of Lorenz curves that are independent of the $\sigma$--fragment they are defined in.
-\begin{proposition}\label{thm:lccont}
-	The Lorenz curve $\lc{\rho}{\sigma}(x)$ of a state $\rho$ with respect to state $\sigma$ is uniformly continuous in $\sigma$. 
-	\nick{In the sense that if $\sigma$ and $\sigma'$ are $\delta$-close with respect to a state norm, then the curves $\lc{\rho}{\sigma}(x)$ and $\lc{\rho}{\sigma'}(x)$ are $\epsilon$-close at all $x \in [0,1]$.
-	I think this clears up the narrative quite a bit? - Should we keep and prove this result?} \ddd{[Is a nice result...hmm let's wait and see. It might distract from the main message.]}
-\end{proposition}
-The proof of this important result is in \nick{the appendix}.
-The consequence of this statement is that infinitesimal changes in state $\sigma$ only result in infinitesimal shifts of the $\sigma$--fragment.
-Therefore, Lorenz curves and majorization analysis in general \nick{behave nicely in the presence of / are robust under} imperfections in the experimental implementation of quantum operations.
-In particular, any $\sigma_0$--fragment defined by a non full-rank state $\sigma_0$ can be approximated by a $\sigma$--fragment defined by a full-rank $\sigma$ which is arbitrarily close to $\sigma_0$, such that $\sigma = (1-\epsilon)\sigma_0 + \epsilon\frac{1}{d}\id$, for some small $\epsilon > 0$.
-Such $\sigma_0$--fragments may include important stabilizer operations such that the replacement channel defined as $\E(\rho) = \sigma_0$ for all states $\rho$.
-For simplicity, we restrict analysis to $\sigma$-fragments, where $\sigma$ is full-rank.
-
-Normalisation of the Wigner distribution \nick{REF} ensures that for all quantum states $\rho$, $\lc{\rho}{\sigma}(x) \geq 0$ and $\lc{\rho}{\sigma}(1) = 1$.
-As a consequence, checking whether a state conversion $\rho \longrightarrow \tau$ is possible as per~\cref{thm:dmajor}, reduces to the condition $\lc{\rho}{\sigma}(x) \leq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$.
-We stress that $0 \leq \lc{\rho}{\sigma}(x) \leq 1$ for all $x \in [0,1]$ if and only if $\rho$ is a positive Wigner state.
-
-The area $\A_\sigma(\rho)$ between the curve $L_{\rho|\sigma}$ and the line $y=1$ is a resource monotone in the $\sigma$--fragment. 
-This is clear because for any state conversion $\rho \longrightarrow \tau$ for some $\E \in \O_\sigma$, the Lorenz curve $L_{\tau|\sigma}$ is lower than $L_{\rho|\sigma}$, hence $\A_\sigma(\E(\rho)) \leq \A_\sigma(\rho)$.
-The exact form of the monotone is given in~\cref{app:areamono}
-
-\ddd{[relate to mana?]} \nick{the area depends on several positive Wigner components and cannot be written as a function of mana annoyingly - should we include the area?
-Have a look at~\cref{app:areamono}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Magic state interconversion and Lorenz curve comparison}
-\label{sec:distill}
-
-Any quantum circuit aiming at a given magic state conversion $\rho \longrightarrow \tau$ possesses certain symmetries according to~\cref{thm:frag} that allow us to study the conversion within only certain $\sigma$-fragments.
-As a simple example, the dephasing channel
-\begin{equation}\label{eq:dephase}
-	\Delta(\rho) = \sum_{k \in \mathbb{Z}_d} \ketbra{k}{k}\rho\ketbra{k}{k}
-\end{equation}
-removes coherent phases in the computational basis and therefore leaves exactly all mixtures of computational basis states invariant.
-A model circuit consisting only of such dephasing channels can be fully analysed in the $\sigma$--fragments for the pure computational basis states $\sigma$.
-
-Lorenz curves provide an efficient method of numerically checking if a certain state conversion is impossible within a $\sigma$--fragment by exploiting the equivalence with $d$--majorization stated in~\cref{thm:dmajor}.
-Such methods are often more conclusive than magic monotones as we discuss in section~\cref{sec:scmana}.
-
-\subsection{Majorization in magic theories}\label{sec:scmana}
-We now discuss majorization features common to all fragments, before specialising to particular $\sigma$--fragments and how analysis in them proceeds.
-
-As discussed above, we know that every magic interconversion problem can be analysed across all $\sigma$--fragments that reflect symmetries of the circuit and moreover the pre-order in each such fragment is exactly specified by $d$--majorization.
-
-Consider a general magic state interconversion in $\O_\sigma$, 
-\begin{equation}
-	\rho \xrightarrow{\E \in \O_\sigma} \tau.
-\end{equation}
-
-Magic theories utilise monotone bounds of the form
-\begin{equation}\label{eq:majbound}
-    \M(\rho) \geq \M(\tau),
-\end{equation}
-to determine whether the interconversion is allowed.
-Monotone bounds hold independently of $\sigma$--fragments, therefore they provide no understanding with regard to the type of operations that allow the interconversion.
-
-New bounds can be obtained in the $\sigma$--fragment by pointwise Lorenz curve comparison of the initial and target states,
-\begin{equation}\label{eq:majbound}
-    \lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x),\ x\in [0,1].
-\end{equation}
-This inequality is parametrised by $x$ and if it is not satisfied at any point $x$, then the Lorenz curves intersect and the conversion is impossible.
-We can refine the independent constraints stemming from this inequality and consider it at only the locations of the target state elbows.
-\begin{theorem}\label{thm:elbows}
-	Let $\rho, \tau$ be two quantum states with Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in the $\sigma$-fragment.
-
-	Let $n'$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ and $E \coloneqq \{x_1, \dots, x_n'\}$ be their locations.
-
-	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\tau}{\sigma}(x_{i})$ for all $i =1,\dots,n'$.
-\end{theorem}
-A proof is provided in~\cref{app:lc_constraints}.
-Any of the $t$ inequalities in the theorem provides a valid contraint leading to some upper distillation bound, and the more one cosiders, the stricter the bound is.
-
-\nick{We can skip mana and just discuss sum-negativity}
-
-One of the most fundamental and commonly used magic monotones is the \emph{mana} of a state \nick{CITE}, defined as
-\begin{equation}
-    \mana{\rho} \coloneqq \ln{(2\sn{\rho}+1)},
-\end{equation}
-where the \emph{sum-negativity} ($\rm{sn}$) \nick{CITE} is the sum of the negative components in $\W{\rho}$,
-\begin{equation}
-    \sn{\rho} \coloneqq \sum\limits_{\bmx: \W[\bmx]{\rho} < 0} \abs{\W[\bmx]{\rho}}.
-\end{equation}
-Mana is an additive\footnote{It satisfies the condition $\mana{\rho_1 \otimes \rho_2} = \mana{\rho_1} + \mana{\rho_2}$ which is practical is distillation settings.} magic monotone, so it provides a necessary condition for magic state interconvertibility.
-
-Here, we show that its properties can be viewed as majorization-based, and independent of the particular $\sigma$--fragment one works in.
-In fact, our current setting makes it apparent that the mana provides a weaker condition than majorization for all magic state interconversions.
-
-We first show that the Lorenz curve maximum of state $\rho$ is independent of the $\sigma$--fragment and directly related to its sum-negativity.
-\begin{lemma}\label{lem:lcmax}
-	Given a quantum state $\rho$, the maximum of its Lorenz curve $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment and is equal to $1+\sn{\rho}$.
-\end{lemma}
-\begin{proof}
-	For notational simplicity, denote $(\W{\rho})_i = \W[\bmx]{\rho},\ i = 1,\dots, d^2$ and similarly for $\W{\sigma}$.
-	We choose the index mapping so that the vector of component ratios, 
-	\begin{equation}
-		\tilde{\bm{w}} \coloneqq \left(\frac{(\W{\rho})_1}{(\W{\sigma})_1}, \dots, \frac{(\W{\rho})_{d^2}}{(\W{\sigma})_{d^2}} \right)^T,
-	\end{equation}
-	is sorted in the sense that $\tilde{\bm{w}} = \tilde{\bm{w}}^\downarrow$.
-	Note that all components of $\W{\sigma}$ are positive, so $(\tilde{\bm{w}})_i \geq 0$ if and only if $(\W{\rho})_i \geq 0$ for any $i=1,\dots,d^2$.
-
-	Let $i_\star$ be the index of the smallest non-negative component of $\tilde{\bm{w}}^\downarrow$.
-	Then, $(\W{\rho})_i < 0$ if and only if $i > i_\star$, so the maximum of Lorenz curve $\lc{\rho}{\sigma}(x)$ takes the value 
-	\begin{equation}
-		\lc{\rho}{\sigma}(x_{i_\star}) = \sum_{i=1}^{i_\star} (\W{\rho})_i,
-	\end{equation}
-	and is achieved at
-	\begin{equation}\label{eq:maxloc}
-		x_{i_\star} \coloneqq \sum_{i=1}^{i_\star} (\W{\sigma})_i.
-	\end{equation}
-
-	The location of the maximum ($x=x_{i_\star}$) varies from fragment to fragment, but its value is independent of $\sigma$,
-	\begin{equation}
-		\lc{\rho}{\sigma}(x_{i_\star})
-		= \sum\limits_{\bmx: \W[\bmx]{\rho} \geq 0} \W[\bmx]{\rho}
-		= 1 + \sn{\rho}.
-	\end{equation}
-
-\end{proof}
-
-We can therefore view mana as just one feature of the Lorenz curve, namely its maximum value. 
-This implies the following result.
-\begin{theorem}\label{thm:bounds}
-    Given a magic state conversion $\rho \longrightarrow \tau$, the majorization condition is stronger than the mana condition in every $\sigma$--fragment.
-\end{theorem}
-\begin{proof}
-    The maximum of the Lorenz curve of a state $\rho$ is independent of the $\sigma$--fragment due to~\cref{lem:lcmax}, and can be expressed as an increasing function of mana,
-    \begin{equation}
-        \max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} = 1 + \sn{\rho} = \frac{1}{2} \left( 1 + e^\mana{\rho} \right).
-    \end{equation}
-    Therefore, the majorization bound
-    \begin{equation}
-    	\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x),\ x\in[0,1]
-    \end{equation}
-    implies the order $\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} \geq \max_{x\in[0,1]}{\lc{\tau}{\sigma}(x)}$, equivalent to the mana condition $\mana{\rho} \geq \mana{\tau}$.
-\end{proof}
-
-Denote an $n$-copy, $\epsilon$-noisy magic state $\rho$ in the $\sigma$--fragment by
-\begin{equation}\label{eq:dist}
-    \rho(\epsilon)^{\otimes n} = \left[ (1 - \epsilon) \rho + \epsilon \sigma \right]^{\otimes n},
-\end{equation}
-and consider the general magic state distillation (MSD) / purification process
-\begin{equation}
-		\rho(\epsilon)^{\otimes n} \xrightarrow{\E \in \O_\sigma} \rho(\epsilon')^{\otimes n'},
-\end{equation}
-where it is converted into a $n'$-copy, $\epsilon'$-noisy state, such that the number of copies has decreased ($n' < n$), but the state is less noisy ($\epsilon' < \epsilon$).
-
-The more noisy the initial state is, the more copies needed to reach the target. 
-We make this idea precise by defining the \emph{noise level threshold} as
-\begin{equation}\label{eq:ethresh}
-	\begin{split}
-	\epsilon_{\star}(n, n', \epsilon', \sigma) \coloneqq &\sup{\{\epsilon:\ \lc{\rho(\epsilon)^{\otimes n}}{\sigma}}(x) \geq \\
-	&{\lc{\rho(\epsilon')^{\otimes n'}}{\sigma}(x),\ x\in[0,1]\}}.
-	\end{split}
-\end{equation}
-The MSD process~(\ref{eq:dist}) is impossible for all $\epsilon > \epsilon_{\star}(n, n', \epsilon', \sigma)$.
-
-\nick{Can also define a distillation bound
-\begin{equation}\label{eq:ethresh}
-	n_{\star}(\epsilon, \epsilon', \sigma) \coloneqq \min{\{n: \lc{\rho_{\rm{S}}n}{\sigma} \geq \lc{\rho_{\rm{S}}(\epsilon')}{\sigma}\}}.
-\end{equation}
-}
-
-In general, the Wigner components of an $n$-copy state $\rho^{\otimes n}$ can be calculated directly from $\W{\rho}$ by convolution of the distribution with itself,
-\begin{equation}
-	\W{\rho^{\otimes n}} = \rm{W}_{\rho}^{\otimes n},
-\end{equation}
-where $\otimes$ can be interpreted as the usual Kroenecker product in the last expression.
-Furthermore, single-copy Lorenz curves are simply additive in noise, 
-\begin{equation}
-\lc{(1-\epsilon)\rho + \epsilon\sigma}{\sigma} = (1-\epsilon)\lc{\rho}{\sigma} + \epsilon\lc{\sigma}{\sigma},
-\end{equation}
-for any $\sigma, \rho$.
-This is not true for higher number of copies.
-
-An important example is the purificiation process~\cref{eq:dist} of the qutrit Strange state $\ketbra{\rm{S}}$,
-\begin{equation}
-    \rho_{\rm{S}}(\epsilon) = (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \sigma,
-\end{equation}
-in $\O_\sigma$, where $\ket{\rm{S}}$ is defined in~\cref{fig:strange}. 
-For $\epsilon=0$, this state is a qutrit of maximal sum-negativity \nick{CITE} and therefore acts as the ideal distiallation target, analogous to a Bell state in bipartite entangelement theory.
-
-In~\cref{fig:lcs}, we illustrate the Lorenz curves of pure and noisy $n$-copy Strange states for $n$ up to $4$ in different $\sigma$-fragments.
 \begin{figure}%
@@
     Solid lines represent pure Strange states ($\epsilon = 0$); dashed lines represent noisy Strange states ($\epsilon = 0.1$).
-    \subref{fig:lcs_maxmix} Unital fragment; \subref{fig:lcs_thermal} Thermal fragment with $H = (0,1,2)$ and $\beta = 0.5$; \subref{fig:lcs_zero} Fragment $\O_{\ketbra{0}{0}}$ (corresponds to red curve in~\cref{fig:stab_distill}); \subref{fig:lcs_one} Fragment $\O_{\ketbra{1}{1}}$ (corresponds to blue curve in~\cref{fig:stab_distill}).
-    The elbows of a curve are the non-differentiable points that form ``angles'' between consecutive line segments.
+    \subref{fig:lcs_maxmix} Unital fragment; \subref{fig:lcs_thermal} Thermal fragment with $H = (0,1,2)$ and $\beta = 0.5$; \subref{fig:lcs_zero} Fragment $\O_{\ketbra{0}{0}}$; \subref{fig:lcs_one} Fragment $\O_{\ketbra{1}{1}}$.
+    \nick{change / move / remove ?}
     }%
@@
 
-In the following sections, we address the question of state interconversions in various $\sigma$--fragments, including concrete examples of the Strange state distillation process. \nick{adapt}
+We now establish important properties of Lorenz curves that are independent of the $\sigma$--fragment they are defined in.
+
+Normalisation of the Wigner distribution \nick{REF} ensures that for all quantum states $\rho$, $\lc{\rho}{\sigma}(x) \geq 0$ and $\lc{\rho}{\sigma}(1) = 1$.
+We stress that $0 \leq \lc{\rho}{\sigma}(x) \leq 1$ for all $x \in [0,1]$ if and only if $\rho$ is a positive Wigner state.
+As a consequence, checking whether a magic state conversion of the form
+\begin{equation}
+	\rho \xrightarrow{\E \in \O_\sigma} \tau
+\end{equation} 
+is possible, reduces to the set of constraints
+\begin{equation}\label{eq:majbound}
+    \lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x),\ x\in [0,1],
+\end{equation}
+due to~\cref{thm:sigmamajor,thm:dmajor}.
+
+We can refine the number of independent constraints stemming from this inequality. 
+In fact, there are only as many independent constraints as there are elbows in the Lorenz curve of the target state as shown in~\cref{app:lc_constraints}.
+However, in principle any one inequality defined at some location $x$ provides a valid constraint leading to some upper distillation bound, and the more locations one considers, the stricter the bound is.
+
+The area $\A_\sigma(\rho)$ between the curve $L_{\rho|\sigma}$ and the line $y=1$ is a resource monotone in the $\sigma$--fragment. 
+This is clear because for any state conversion $\rho \longrightarrow \tau$ for some $\E \in \O_\sigma$, the Lorenz curve $L_{\tau|\sigma}$ is lower than $L_{\rho|\sigma}$, hence $\A_\sigma(\E(\rho)) \leq \A_\sigma(\rho)$.
+The exact form of the monotone is given in~\cref{app:areamono}
+\nick{should we include the area? Have a look at~\cref{app:areamono}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Mana as a feature of majorization}
+
+We now show that the magic monotone of mana, and equivalently the sum-negativity of a quantum state, can be viewed as majorization-based, and independent of the particular $\sigma$--fragment one works in.
+In fact, our current setting makes it apparent that mana provides a weaker condition than majorization for all magic state interconversions.
+
+We first show that the Lorenz curve maximum of state $\rho$ is independent of the $\sigma$--fragment and directly related to its sum-negativity.
+\begin{lemma}\label{lem:lcmax}
+	Given a quantum state $\rho$, the maximum of its Lorenz curve $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment and is equal to $1+\sn{\rho}$.
+\end{lemma}
+\begin{proof}
+	For notational simplicity, denote $(\W{\rho})_i = \W[\bmx]{\rho},\ i = 1,\dots, d^2$ and similarly for $\W{\sigma}$.
+	We choose the index mapping so that the vector of component ratios, 
+	\begin{equation}
+		\tilde{\bm{w}} \coloneqq \left(\frac{(\W{\rho})_1}{(\W{\sigma})_1}, \dots, \frac{(\W{\rho})_{d^2}}{(\W{\sigma})_{d^2}} \right)^T,
+	\end{equation}
+	is sorted in the sense that $\tilde{\bm{w}} = \tilde{\bm{w}}^\downarrow$.
+	Note that all components of $\W{\sigma}$ are positive, so $(\tilde{\bm{w}})_i \geq 0$ if and only if $(\W{\rho})_i \geq 0$ for any $i=1,\dots,d^2$.
+
+	Let $i_\star$ be the index of the smallest non-negative component of $\tilde{\bm{w}}^\downarrow$.
+	Then, $(\W{\rho})_i < 0$ if and only if $i > i_\star$, so the maximum of Lorenz curve $\lc{\rho}{\sigma}(x)$ takes the value 
+	\begin{equation}
+		\lc{\rho}{\sigma}(x_{i_\star}) = \sum_{i=1}^{i_\star} (\W{\rho})_i,
+	\end{equation}
+	and is achieved at
+	\begin{equation}\label{eq:maxloc}
+		x_{i_\star} \coloneqq \sum_{i=1}^{i_\star} (\W{\sigma})_i.
+	\end{equation}
+
+	The location of the maximum ($x=x_{i_\star}$) varies from fragment to fragment, but its value is independent of $\sigma$,
+	\begin{equation}
+		\lc{\rho}{\sigma}(x_{i_\star})
+		= \sum\limits_{\bmx: \W[\bmx]{\rho} \geq 0} \W[\bmx]{\rho}
+		= 1 + \sn{\rho}.
+	\end{equation}
+
+\end{proof}
+
+We can therefore view mana as just one feature of the Lorenz curve, namely its maximum value. 
+Conversely, the maximum of the Lorenz curve acts as a valid magic monotone.
+This implies the following result.
+\begin{theorem}\label{thm:bounds}
+    Given a magic state conversion $\rho \longrightarrow \tau$, the majorization condition is stronger than the mana condition in every $\sigma$--fragment.
+\end{theorem}
+\begin{proof}
+    The maximum of the Lorenz curve of a state $\rho$ is independent of the $\sigma$--fragment due to~\cref{lem:lcmax}, and can be expressed as an increasing function of mana,
+    \begin{equation}
+        \max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} = 1 + \sn{\rho} = \frac{1}{2} \left( 1 + e^\mana{\rho} \right).
+    \end{equation}
+    Therefore, the majorization bound
+    \begin{equation}
+    	\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x),\ x\in[0,1]
+    \end{equation}
+    implies the order $\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} \geq \max_{x\in[0,1]}{\lc{\tau}{\sigma}(x)}$, equivalent to the mana condition $\mana{\rho} \geq \mana{\tau}$.
+\end{proof}
 
@@
 Depending on the symmetries of such operations, a Clifford sequence may belong in other $\sigma$--fragments as well.
-In this case, the majorization condition~(\ref{eq:majbound}) needs to be checked in all the $\sigma$-fragments that reflect the symmetries of the operation sequence.
+In this case, the majorization condition~(\ref{eq:majbound}) needs to be checked in all the $\sigma$--fragments that reflect the symmetries of the operation sequence.
 
@@
 We would now like to study the constraints coming solely from majorization in the unital fragment. 
-We consider the problem of purifying $n$ copies of a noisy strange state $\rho_{\rm{S}}n$ into a smaller number of copies $n'$ of a less noisy strange state $\rho_{\rm{S}}(\epsilon')^{\otimes n'}$, with $\epsilon' \le \epsilon$ and $n' \leq n$.
+Define the $\epsilon$-noisy Strange state $\ketbra{\rm{S}}$,
+\begin{equation}
+    \rho_{\rm{S}}(\epsilon) = (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \sigma,
+\end{equation}
+in $\O_\sigma$, where $\ket{\rm{S}}$ is defined in~\cref{fig:strange}. 
+For $\epsilon=0$, this state is a qutrit of maximal sum-negativity \nick{CITE} and therefore acts as the ideal distiallation target, analogous to a Bell state in bipartite entangelement theory.
+
+We consider the problem of purifying $n$ copies of a noisy Strange state $\rho_{\rm{S}}n$ into a smaller number of copies $n'$ of a less noisy strange state $\rho_{\rm{S}}(\epsilon')^{\otimes n'}$, with $\epsilon' \le \epsilon$ and $n' \leq n$.
 Since the state $\frac{1}{3} \id$ is free, the interconversion problem is unaffected if we tensor in copies of it.
@@
 \end{equation}
-a threshold error rate. Then any distillation rate $R(\epsilon, \beta)$ in the $\sigma$-fragment of a magic theory is bounded as follows:
+a threshold error rate. Then any distillation rate $R(\epsilon, \beta)$ in the $\sigma$--fragment of a magic theory is bounded as follows:
 
@@
 
+Consider pure Strange state distillation at high temperatures, $\beta \leq \beta_{\star}$.
+Depending on the noise level of the initial state, we have either a $\rm{(C1)} \rightarrow \rm{(C1)}$ or a $\rm{(C2)} \rightarrow \rm{(C1)}$ scenario.
+
+At every $\beta > 0$, the rates indicate a transition at $\epsilon_{\star}$.
+As $\beta$ increases, the rate becomes stricter.
+At the high temperature limit, $\beta \rightarrow 0$, we get $\beta F_\beta \rightarrow -\ln{3}$, and we retrieve the unital fragment bound,
+\begin{equation}
+	R(\beta) \xrightarrow{\beta \rightarrow 0} \frac{\ln{(3-4\epsilon)}}{\ln{3}}.
+\end{equation}
+
+Consider pure Strange state distillation at low temperatures, $\beta \rightarrow \infty$.
+Independently of the noise level of the initial state, we have a $\rm{(C2)} \rightarrow \rm{(C2)}$ scenario.
+
+As $\beta$ increases, the rate becomes looser.
+At the zero temperature limit, $F_\beta$ tends to zero, so $R(\epsilon, \beta) \xrightarrow{\beta \rightarrow \infty} 1$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\null\newpage
+
+\section{Random info}
+
+\nick{Move stuff around or remove.}\vspace{-10pt}
+
 \begin{figure}[h]
@@
 \end{figure}
-
-Consider pure Strange state distillation at high temperatures, $\beta \leq \beta_{\star}$.
-Depending on the noise level of the initial state, we have either a $\rm{(C1)} \rightarrow \rm{(C1)}$ or a $\rm{(C2)} \rightarrow \rm{(C1)}$ scenario.
-
-We compare $R(\beta)$ for different temperatures with the mana bound $R_{\rm{mana}}$ in~\cref{fig:distill_bounds_temp}.
-At every $\beta > 0$, the rates indicate a transition at $\epsilon_{\star}$.
-As $\beta$ increases, the rate becomes stricter.
-At the high temperature limit, $\beta \rightarrow 0$, we get $\beta F_\beta \rightarrow -\ln{3}$, and we retrieve the unital fragment bound,
-\begin{equation}
-	R(\beta) \xrightarrow{\beta \rightarrow 0} \frac{\ln{(3-4\epsilon)}}{\ln{3}}.
-\end{equation}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.5]{figs/distill_bounds_temp.pdf}
-    \caption{\textbf{Distillation rate with low noise in thermal fragments.} Distillation rates obtained by majorization $R(\beta)$ for low noise levels $\epsilon \leq \epsilon_{\star}$ are plotted for different temperatures $\beta^{-1}$ such that $0 \leq \beta \leq \beta_{\star}$.
-    The mana distillation rate $R_{\rm{mana}}$ is given for comparison.
-    The Hamiltonian spectrum is simple harmonic, $(E_0, E_1, E_2) = (0,1,2)$.
-    As $\beta$ increases, the range of noise levels for which $R(\beta)$ is valid decreases and the distillation bound becomes stricter.
-    }
-    \label{fig:distill_bounds_temp}
-\end{figure}
-
-Consider pure Strange state distillation at low temperatures, $\beta \rightarrow \infty$.
-Independently of the noise level of the initial state, we have a $\rm{(C2)} \rightarrow \rm{(C2)}$ scenario.
-
-We compare $R(\beta)$ for different temperatures with the mana bound $R_{\rm{mana}}$ in~\cref{fig:distill_bounds_lowtemp}.
-As $\beta$ decreases, the rate becomes stricter.
-At the zero temperature limit, $F_\beta$ tends to zero, so $R(\beta) \xrightarrow{\beta \rightarrow \infty} 1$.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.5]{figs/distill_bounds_lowtemp.pdf}
-    \caption{\textbf{Distillation rate for low temperatures in thermal fragments.} Distillation rates obtained by majorization $R(\beta)$ in the temperature regime $\beta \geq \beta_{\star}$ are plotted for different temperatures $\beta^{-1}$.
-    The mana distillation rate $R_{\rm{mana}}$ is given for comparison.
-    The Hamiltonian spectrum is simple harmonic, $(E_0, E_1, E_2) = (0,1,2)$.
-    \nick{Not-so-good bound for low temperatures, other elbows perform a lot better numerically.}
-    }
-    \label{fig:distill_bounds_lowtemp}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\null\newpage
-\null\newpage
-
-\subsection{Random plots}
 
@@
 
-There exist $d(d+1)$ pure stabilizer states for a $d$-dimensional system, all of which correspond to a uniform distribion over an affine line in the phase space \nick{CITE}.
+There exist $d(d+1)$ pure stabilizer states for a $d$-dimensional system, all of which correspond to a uniform distribution over an affine line in the phase space \nick{CITE}.
 As an example, the distribution of the qutrit zero state $\ketbra{0}$ is illustrated in~\cref{fig:zero}.
-Any pure stabilizer state $\sigma$ is a rank--$1$ state and contains $d^2 - d$ zeros in its Wigner distribution, so we approximate it by the full--rank state $\sigma' = (1-\epsilon)\sigma + \epsilon \frac{1}{d}\id$ for some infinitesimal $\epsilon > 0$.
-
-We explore the distillation process of~\cref{eq:sdist} in these modified fragments $\O_\sigma'$ in~\cref{fig:stab_distill}.
-We repeat the plot for distillation of Norrell states in~\cref{fig:stab_distill_norrell}.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.5]{figs/stab_distill.pdf}
-    \caption{\textbf{Strange state distillation thresholds in stabilizer fragments.} Lorenz curve thresholds for the Strange state purifying process in~\cref{eq:sdist} with $\epsilon' = 0.05$.
-    All $12$ stabilizer fragments produce two distinct trends: ($k=0$ - red curve) the stabilizer states that have non-zero value at the origin of the phase space lie low and ($k=1,2$ - blue curve) the stabilizer states that have a zero value at the origin of the phase space lie high.
-    This is specific to the Strange state.
-    For high enough copies, these Lorenz curves surpass the unital noise threshold $\epsilon_{\star} = \frac{3}{4}$.
-    }
-    \label{fig:stab_distill}
-\end{figure}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.5]{figs/stab_distill_norrell.pdf}
-    \caption{\textbf{Norrell state distillation thresholds in stabilizer fragments.} Lorenz curve thresholds for the Strange state purifying process in~\cref{eq:sdist} with $\epsilon' = 0.05$.
-    For high enough copies, certain Lorenz curves surpass the unital noise threshold $\epsilon_{\star} = \frac{3}{4}$.
-    }
-    \label{fig:stab_distill_norrell}
-\end{figure}
+Any pure stabilizer state $\sigma$ is a rank--$1$ state and contains $d^2 - d$ zeros in its Wigner distribution, so we approximate it by the full--rank state $\sigma' = (1-\epsilon)\sigma + \epsilon \frac{1}{d}\id$ for some $\epsilon > 0$.
 
@@
 \null\newpage
-\null\newpage
-\section{Lower bounds in $\sigma$-fragments}
+\section{Lower bounds in $\sigma$--fragments}
 \ddd{[Am throwing down some rough material, to be polished later.]}

### 2021-02-25 magic_paper.tex
More tidying before the unital section

@@
 Monotones are often used \nick{CITE} to address the question of state convertibility, although such approaches are usually generic.
-We highlight the defining property of a monotone here, as it is useful in several sections that follow.
-\begin{definition}[\textbf{Resource monotone}]\label{def:mono}
-    Let $\R = (\F, \O)$ be a resource theory.
-    A resource monotone $\M$ is a projection from the set of quantum states of the theory onto the real line, so that $\M$ is monotonically decreasing under free operations,
-    \begin{equation}
-        \M(\rho_1) \leq \M(\rho_2)\ \text{whenever}\ \rho_1 \prec_{\R} \rho_2.
-    \end{equation}
-\end{definition}
+
 The monotonicity condition reflects the no resource generating property of free operations, so that monotones respect the pre-order $\prec_\R$ of the theory.
@@
 \begin{definition}[\textbf{Lorenz curve}]\label{def:lc}
-    Let $\bmz, \bmd \in \reals^d$, where the components of $\bmd$ are positive with $D = \sum_{i=1}^d d_i$ and denote by $\tilde{\bmz} \coloneqq (z_1/d_1, \dots, z_d/d_d)^T$ the vector of ratios between the corresponding components of $\bmz$ and $\bmd$.
-
-    Finally, denote by $\pi: \mathbb{Z}_d \mapsto \mathbb{Z}_d$ the permutation that sorts $\tilde{\bmz}$, $(\tilde{\bmz}^\downarrow)_i = z_{\pi(i)}$ for all $i=1,\dots,d$.
+    Let $\bmw, \bmd \in \reals^d$, where the components of $\bmd$ are positive with $D = \sum_{i=1}^d d_i$ and denote by $\widetilde{\bmw} \coloneqq (w_1/d_1, \dots, w_d/\nick{d_d})^T$ the vector of ratios between the corresponding components of $\bmw$ and $\bmd$.
+
+    Finally, denote by $\pi: \mathbb{Z}_d \mapsto \mathbb{Z}_d$ the permutation that sorts $\widetilde{\bmw}$, $(\widetilde{\bmw}^\downarrow)_i = w_{\pi(i)}$ for all $i=1,\dots,d$.
 
@@
     \begin{equation}\label{eq:lorenz}
-        (x_k, \lc{\bmz}{\bmd}(k)) \coloneqq \left( \frac{1}{D}\sum_{i=1}^k d_{\pi(i)}, \sum_{i=1}^k z_{\pi(i)} \right).
-    \end{equation}
-    We define the set of points on this curve, $\lc{\bmz}{\bmd}(x),\ x \in [0,1]$, as the \emph{Lorenz curve} of vector $\bmz$ with respect to $\bmd$.
+        (x_k, \lc{\bmw}{\bmd}(k)) \coloneqq \left( \frac{1}{D}\sum_{i=1}^k d_{\pi(i)}, \sum_{i=1}^k w_{\pi(i)} \right).
+    \end{equation}
+    We define the set of points on this curve, $\lc{\bmw}{\bmd}(x),\ x \in [0,1]$, as the \emph{Lorenz curve} of vector $\bmw$ with respect to $\bmd$.
 \end{definition}
 Components $x_k$ are rescaled by $D$ so that comparison of curves with unequal dimensions is possible.
-In fact, the Lorenz curves $\lc{\bmz}{\bmd}$ and $\lc{\bmz \otimes \bmd}{\bmd \otimes \bmd}$, where $\otimes$ denotes the Kronecker product, are identical.
-Furthermore, a Lorenz curve $\lc{\bmz}{\bmd}(x)$ is always concave in $x$, since it consists of $d$ line segments each with slope $(\tilde{\bmz}^\downarrow)_i$ for $i=1,\dots,d$ which is non-increasing by definition.
+In fact, the Lorenz curves $\lc{\bmw}{\bmd}$ and $\lc{\bmw \otimes \bmd}{\bmd \otimes \bmd}$, where $\otimes$ denotes the Kronecker product, are identical.
+Furthermore, a Lorenz curve $\lc{\bmw}{\bmd}(x)$ is always concave in $x$, since it consists of $d$ line segments each with slope $(\widetilde{\bmw}^\downarrow)_i$ for $i=1,\dots,d$ which is non-increasing by definition.
 Finally, the points on the interior of the Lorenz curve connecting line segments of different slopes are called \emph{elbows}.
@@
 \begin{equation}
-	\W{\rho^{\otimes n}} = \rm{W}_{\rho}^{\otimes n},
-\end{equation}
-where $\otimes$ can be interpreted as the usual Kroenecker product in the last expression.
+	\W{\rho^{\otimes n}} = \W{\rho}^{\otimes n},
+\end{equation}
+where $\otimes$ can be interpreted as the usual Kronecker product in the last expression.
+We may use the vector notation $\bmw(\rho) = (w(\rho)_i)_{i=1,\dots,d^2}$ for the Wigner distribution, in which case we can express the Kronecker product as
+\begin{equation}
+	\W{\rho} \otimes \W{\rho} = (w(\rho)_i w(\rho)_j)_{i,j=1,\dots,d^2}.
+\end{equation}
+The correspondence between the phase space and pure vector representations of the Wigner distribuition is discussed more in~\cref{app:cmpairs}.
 
@@
 
-\subsection{Majorization computations in $\sigma$--fragments}
+\subsection{Lorenz curves of quasi-probabilities in $\sigma$--fragments}
 
@@
 We write $\lc{\rho}{\sigma}(x)$ for the Lorenz curve of $\W{\rho}$ with respect to $\W{\sigma}$.
-
-An example of comparison between different Lorenz curves is illustrated in~\cref{fig:lctoy}.
-The curves in the figure are constructed in the \emph{unital fragment}, i.e. the $\sigma$--fragment defined by the maximally mixed state $\sigma = \frac{1}{d}\id$.
-In~\cref{fig:lcs}, we illustrate the Lorenz curves of pure and noisy $n$-copy Strange states for $n$ up to $4$ in different $\sigma$--fragments.
+The vector of ratios $\widetilde{\bmw}(\rho|\sigma)$ used to construct the curve and defined as
+\begin{equation}
+	\widetilde{w}(\rho|\sigma)_i \coloneqq \frac{w(\rho)_i}{w(\sigma)_i},
+\end{equation}
+is called the Gibbs-rescaled distribution of $\rho$ with respect to $\sigma$.
+
+An example of comparison between different Lorenz curves is provided in~\cref{fig:lctoy}.
+The curves in the figure are constructed in the \emph{unital fragment}, i.e.
+the $\sigma$--fragment defined by the maximally mixed state $\sigma = \frac{1}{d}\id$ whose Wigner distribution is the uniform probability distribution.
 \begin{figure}
@@
     \includegraphics[height=5cm]{figs/lctoy.pdf}
-    \caption{Example of different Lorenz curves for quasi-probability vectors under $\bmd$-majorization.
-    Vectors $\bmy$ and $\bmd$ are simply probability distributions.
-    The curve corresponding to vector $\bmd$ is always the line segment connecting $(0,0)$ and $(1,1)$, so that any other Lorenz curve lies above it, for example $\bmx \prec_{\bmd} \bmd$.
-    Curves $L_k(\bmx|\bmd)$ and $L_k(\bmy|\bmd)$ intersect, so $\bmx \nprec_{\bmd} \bmy$ as well as $\bmy \nprec_{\bmd} \bmx$.
-    \nick{RECAST}
+    \caption{\textbf{Quasi-probability Lorenz curve comparison}.
+    The Lorenz curves are constructed by the Wigner distributions illustrated in~\cref{fig:wstate_examples} in the unital fragment $\O_{\id/d}$ for $d=3$.
+    The maximally mixed state curve is simply the line connecting $(0,0)$ and $(1,1)$.
+    There is no operation in $\O_{\id/d}$ that can convert $\ket{\rm{S}}$ to $\ket{0}$, as their Lorenz curves intersect.
     }
@@
 \end{figure}
+
+Normalisation of the Wigner distribution \nick{REF} ensures that for all quantum states $\rho$, $\lc{\rho}{\sigma}(x) \geq 0$ and $\lc{\rho}{\sigma}(1) = 1$.
+We stress that $0 \leq \lc{\rho}{\sigma}(x) \leq 1$ for all $x \in [0,1]$ if and only if $\rho$ is a positive Wigner state.
+As a consequence, checking whether a magic state conversion of the form
+\begin{equation}\label{eq:sigma_conv}
+	\rho \xrightarrow{\E \in \O_\sigma} \tau
+\end{equation} 
+is not possible, reduces to the set of constraints
+\begin{equation}\label{eq:majbound}
+    \lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x),\ x\in [0,1],
+\end{equation}
+due to~\cref{thm:sigmamajor,thm:dmajor}.
+
+We can refine the number of independent constraints stemming from this inequality. 
+In fact, there are only as many independent constraints as there are elbows in the Lorenz curve of the target state as shown in~\cref{app:lc_constraints}.
+However, in principle any one inequality defined at some location $x$ provides a valid constraint leading to some upper distillation bound, and the more locations one considers, the stricter the bound is.
+
+The area $\A_\sigma(\rho)$ between the curve $L_{\rho|\sigma}$ and the line $y=1$ is a resource monotone in the $\sigma$--fragment. 
+This is clear because for any state conversion like~\cref{eq:sigma_conv}, the Lorenz curve $L_{\tau|\sigma}$ is lower than $L_{\rho|\sigma}$, hence $\A_\sigma(\E(\rho)) \leq \A_\sigma(\rho)$.
+The exact form of the monotone is given in~\cref{app:areamono}
+\nick{should we include the area? Have a look at~\cref{app:areamono}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Mana as a feature of majorization}
+
+We now show that the magic monotone of mana, and equivalently the sum-negativity of a quantum state, can be viewed as majorization-based, and independent of the particular $\sigma$--fragment one works in.
+In fact, our current setting makes it apparent that mana provides a weaker condition than majorization for all magic state interconversions.
+
+We first show that the Lorenz curve maximum of state $\rho$ is independent of the $\sigma$--fragment and directly related to its sum-negativity.
+\begin{lemma}\label{lem:lcmax}
+	Given a quantum state $\rho$, the maximum of its Lorenz curve $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment and is equal to $1+\sn{\rho}$.
+\end{lemma}
+\begin{proof}
+	We may use the vector notation of the Wigner distributions $\bmw(\rho)$ and $\bmw(\sigma)$.
+	We choose the component indexing so that the Gibbs-rescaled distribution 
+	\begin{equation}
+		\widetilde{\bm{w}}(\rho|\sigma) \coloneqq \left(\frac{w(\rho)_1}{w(\sigma)_1}, \dots, \frac{w(\rho)_{d^2}}{w(\sigma)_{d^2}} \right)^T,
+	\end{equation}
+	is sorted, $\widetilde{\bm{w}} = \widetilde{\bm{w}}^\downarrow$.
+	Note that all components of $\bmw(\sigma)$ are positive, so $\widetilde{w}_i \geq 0$ if and only if $w(\rho)_i \geq 0$ for any $i=1,\dots,d^2$.
+
+	Let $i_\star$ be the index of the smallest non-negative component of $\widetilde{\bm{w}}^\downarrow$.
+	Then, $w(\rho)_i < 0$ if and only if $i > i_\star$, so the maximum of Lorenz curve $\lc{\rho}{\sigma}(x)$ takes the value 
+	\begin{equation}
+		\lc{\rho}{\sigma}(x_{i_\star}) = \sum_{i=1}^{i_\star} w(\rho)_i,
+	\end{equation}
+	and is achieved at
+	\begin{equation}\label{eq:maxloc}
+		x_{i_\star} \coloneqq \sum_{i=1}^{i_\star} w(\sigma)_i.
+	\end{equation}
+
+	The location of the maximum ($x=x_{i_\star}$) varies from fragment to fragment, but its value is independent of $\sigma$,
+	\begin{equation}
+		\lc{\rho}{\sigma}(x_{i_\star})
+		= \sum\limits_{\bmx: \W[\bmx]{\rho} \geq 0} \W[\bmx]{\rho}
+		= 1 + \sn{\rho}.
+	\end{equation}
+
+\end{proof}
+
+We can therefore view mana as just one feature of the Lorenz curve, namely its maximum value. 
+Conversely, it is now clear that the maximum of the Lorenz curve acts as a valid magic monotone.
+This implies the following result.
+\begin{theorem}\label{thm:bounds}
+    Given a magic state conversion $\rho \longrightarrow \tau$, the majorization condition is stronger than the mana condition in every $\sigma$--fragment.
+\end{theorem}
+\begin{proof}
+    The maximum of the Lorenz curve of a state $\rho$ is independent of the $\sigma$--fragment due to~\cref{lem:lcmax}, and can be expressed as an increasing function of mana,
+    \begin{equation}
+        \max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} = 1 + \sn{\rho} = \frac{1}{2} \left( 1 + e^\mana{\rho} \right).
+    \end{equation}
+    Therefore, the majorization bound
+    \begin{equation}
+    	\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x),\ x\in[0,1]
+    \end{equation}
+    implies the order $\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} \geq \max_{x\in[0,1]}{\lc{\tau}{\sigma}(x)}$, equivalent to the mana condition $\mana{\rho} \geq \mana{\tau}$.
+\end{proof}
+
+In the sections~\cref{sec:unital,sec:stab}, we study majorization constraints on magic distillation arising in different fragments. 
+For this reason, we define the $n$-copy, $\epsilon$-noisy Strange state,
+\begin{equation}
+    \rho_{\rm{S}}(\epsilon)^{\otimes n} \coloneqq \left[ (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \frac{1}{3}\id \right]^{\otimes n},
+\end{equation}
+in $\O_\sigma$, where $\ket{\rm{S}}$ is defined in~\cref{fig:strange} and the induced noise is uniform. 
+For $\epsilon=0$, this state is a qutrit of maximal sum-negativity / mana~\cite{cit:veitch2} and therefore acts as the ideal distiallation target, analogous to a Bell state in bipartite entangelement theory.
+
+In~\cref{fig:lcs}, we illustrate the Lorenz curves of pure and noisy $n$-copy Strange states for $n$ up to $4$ in different $\sigma$--fragments.
+As shown in~\cref{lem:lcmax}, the curve peaks equal $1 + \sn{\rho_{\rm{S}}(\epsilon)^{\otimes n}}$ independently of the $\sigma$--fragment.
 \begin{figure}%
@@
     }
-    \caption{\textbf{Lorenz curves of Strange state copies.} Lorenz curves of $\rho_{\rm{S}}n$ for $n=1,2,3,4$.
+    \caption{\textbf{Lorenz curves of $n$-copy Strange states.} Lorenz curves of $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ for $n=1,2,3,4$.
     Solid lines represent pure Strange states ($\epsilon = 0$); dashed lines represent noisy Strange states ($\epsilon = 0.1$).
@@
 
-We now establish important properties of Lorenz curves that are independent of the $\sigma$--fragment they are defined in.
-
-Normalisation of the Wigner distribution \nick{REF} ensures that for all quantum states $\rho$, $\lc{\rho}{\sigma}(x) \geq 0$ and $\lc{\rho}{\sigma}(1) = 1$.
-We stress that $0 \leq \lc{\rho}{\sigma}(x) \leq 1$ for all $x \in [0,1]$ if and only if $\rho$ is a positive Wigner state.
-As a consequence, checking whether a magic state conversion of the form
-\begin{equation}
-	\rho \xrightarrow{\E \in \O_\sigma} \tau
-\end{equation} 
-is possible, reduces to the set of constraints
-\begin{equation}\label{eq:majbound}
-    \lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x),\ x\in [0,1],
-\end{equation}
-due to~\cref{thm:sigmamajor,thm:dmajor}.
-
-We can refine the number of independent constraints stemming from this inequality. 
-In fact, there are only as many independent constraints as there are elbows in the Lorenz curve of the target state as shown in~\cref{app:lc_constraints}.
-However, in principle any one inequality defined at some location $x$ provides a valid constraint leading to some upper distillation bound, and the more locations one considers, the stricter the bound is.
-
-The area $\A_\sigma(\rho)$ between the curve $L_{\rho|\sigma}$ and the line $y=1$ is a resource monotone in the $\sigma$--fragment. 
-This is clear because for any state conversion $\rho \longrightarrow \tau$ for some $\E \in \O_\sigma$, the Lorenz curve $L_{\tau|\sigma}$ is lower than $L_{\rho|\sigma}$, hence $\A_\sigma(\E(\rho)) \leq \A_\sigma(\rho)$.
-The exact form of the monotone is given in~\cref{app:areamono}
-\nick{should we include the area? Have a look at~\cref{app:areamono}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Mana as a feature of majorization}
-
-We now show that the magic monotone of mana, and equivalently the sum-negativity of a quantum state, can be viewed as majorization-based, and independent of the particular $\sigma$--fragment one works in.
-In fact, our current setting makes it apparent that mana provides a weaker condition than majorization for all magic state interconversions.
-
-We first show that the Lorenz curve maximum of state $\rho$ is independent of the $\sigma$--fragment and directly related to its sum-negativity.
-\begin{lemma}\label{lem:lcmax}
-	Given a quantum state $\rho$, the maximum of its Lorenz curve $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment and is equal to $1+\sn{\rho}$.
-\end{lemma}
-\begin{proof}
-	For notational simplicity, denote $(\W{\rho})_i = \W[\bmx]{\rho},\ i = 1,\dots, d^2$ and similarly for $\W{\sigma}$.
-	We choose the index mapping so that the vector of component ratios, 
-	\begin{equation}
-		\tilde{\bm{w}} \coloneqq \left(\frac{(\W{\rho})_1}{(\W{\sigma})_1}, \dots, \frac{(\W{\rho})_{d^2}}{(\W{\sigma})_{d^2}} \right)^T,
-	\end{equation}
-	is sorted in the sense that $\tilde{\bm{w}} = \tilde{\bm{w}}^\downarrow$.
-	Note that all components of $\W{\sigma}$ are positive, so $(\tilde{\bm{w}})_i \geq 0$ if and only if $(\W{\rho})_i \geq 0$ for any $i=1,\dots,d^2$.
-
-	Let $i_\star$ be the index of the smallest non-negative component of $\tilde{\bm{w}}^\downarrow$.
-	Then, $(\W{\rho})_i < 0$ if and only if $i > i_\star$, so the maximum of Lorenz curve $\lc{\rho}{\sigma}(x)$ takes the value 
-	\begin{equation}
-		\lc{\rho}{\sigma}(x_{i_\star}) = \sum_{i=1}^{i_\star} (\W{\rho})_i,
-	\end{equation}
-	and is achieved at
-	\begin{equation}\label{eq:maxloc}
-		x_{i_\star} \coloneqq \sum_{i=1}^{i_\star} (\W{\sigma})_i.
-	\end{equation}
-
-	The location of the maximum ($x=x_{i_\star}$) varies from fragment to fragment, but its value is independent of $\sigma$,
-	\begin{equation}
-		\lc{\rho}{\sigma}(x_{i_\star})
-		= \sum\limits_{\bmx: \W[\bmx]{\rho} \geq 0} \W[\bmx]{\rho}
-		= 1 + \sn{\rho}.
-	\end{equation}
-
-\end{proof}
-
-We can therefore view mana as just one feature of the Lorenz curve, namely its maximum value. 
-Conversely, the maximum of the Lorenz curve acts as a valid magic monotone.
-This implies the following result.
-\begin{theorem}\label{thm:bounds}
-    Given a magic state conversion $\rho \longrightarrow \tau$, the majorization condition is stronger than the mana condition in every $\sigma$--fragment.
-\end{theorem}
-\begin{proof}
-    The maximum of the Lorenz curve of a state $\rho$ is independent of the $\sigma$--fragment due to~\cref{lem:lcmax}, and can be expressed as an increasing function of mana,
-    \begin{equation}
-        \max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} = 1 + \sn{\rho} = \frac{1}{2} \left( 1 + e^\mana{\rho} \right).
-    \end{equation}
-    Therefore, the majorization bound
-    \begin{equation}
-    	\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x),\ x\in[0,1]
-    \end{equation}
-    implies the order $\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} \geq \max_{x\in[0,1]}{\lc{\tau}{\sigma}(x)}$, equivalent to the mana condition $\mana{\rho} \geq \mana{\tau}$.
-\end{proof}
-
-\section{Magic in the unital fragment}\label{sec:unital}
+\null\newpage
+\null\newpage
+
+\section{Magic in the unital fragment}
+\label{sec:unital}
+
 The unital fragment encompasses the circuits which preserve the maximally mixed state ($\id/d$) and so it includes many important families of circuits.
@@
 Depending on the symmetries of such operations, a Clifford sequence may belong in other $\sigma$--fragments as well.
-In this case, the majorization condition~(\ref{eq:majbound}) needs to be checked in all the $\sigma$--fragments that reflect the symmetries of the operation sequence.
+In such a case, the majorization condition~(\ref{eq:majbound}) needs to be checked in the $\sigma$--fragments that reflect all symmetries of the operation sequence.
 
@@
 
-In~\cref{fig:unital_distill}, we examine the Strange state distillation process of~\cref{eq:dist} with $\epsilon' = 0.05$ which describes all circuits that respect the unital symmetry.
-Thresholds provided by Lorenz curve comparison are always much stricter than mana thresholds.
-\nick{Explain asymptotic behaviour?}
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.5]{figs/unital_distill.pdf}
-    \caption{\textbf{Noise thresholds in unital fragment.} Mana and Lorenz curve noise thresholds for the Strange state purification process in~\cref{eq:dist} with $\epsilon' = 0.05$.
-    Lorenz curve comparison consistently gives stricter bounds as proven in~\cref{thm:bounds}.
-    The line $\epsilon = \frac{3}{4}$ indicates the threshold noise beyond which the Strange state no longer contains negativities. 
-    \nick{Redo figure}
-    }
-    \label{fig:unital_distill}
-\end{figure}
-
-\iffalse
-% Copies plot
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.5]{figs/unital_distill_copies.pdf}
-    \caption{\textbf{Copies required for Strange state distillation.} Mana and Lorenz curve copy thresholds for the Strange state purification process in~\cref{eq:sdist} with $\epsilon_\tau = 0.05$.
-    Lorenz curve comparison consistently provides higher low bounds on the number of noisy Strange state copies required.
-    }
-    \label{fig:unital_distill_copies}
-\end{figure}
-\fi
-
-\null\newpage
-
 \subsection{Distillation rate bounds in the unital fragment}\label{sec:lcsu}
 
-We would now like to study the constraints coming solely from majorization in the unital fragment. 
-Define the $\epsilon$-noisy Strange state $\ketbra{\rm{S}}$,
-\begin{equation}
-    \rho_{\rm{S}}(\epsilon) = (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \sigma,
-\end{equation}
-in $\O_\sigma$, where $\ket{\rm{S}}$ is defined in~\cref{fig:strange}. 
-For $\epsilon=0$, this state is a qutrit of maximal sum-negativity \nick{CITE} and therefore acts as the ideal distiallation target, analogous to a Bell state in bipartite entangelement theory.
-
-We consider the problem of purifying $n$ copies of a noisy Strange state $\rho_{\rm{S}}n$ into a smaller number of copies $n'$ of a less noisy strange state $\rho_{\rm{S}}(\epsilon')^{\otimes n'}$, with $\epsilon' \le \epsilon$ and $n' \leq n$.
-Since the state $\frac{1}{3} \id$ is free, the interconversion problem is unaffected if we tensor in copies of it.
-More precisely the associated Lorenz curve in invariant under tensoring in arbitrary many copies of this free state.
-This turns out to simplify the Lorenz curve analysis, and so we focus on the process,
+We consider the problem of purifying $n$ copies of a noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ into a smaller number of copies $n'$ of a less noisy strange state $\rho_{\rm{S}}(\epsilon')^{\otimes n'}$, with $\epsilon' \leq \epsilon$ and $n' \leq n$,
 \begin{equation}\label{eq:sudist}
-	\rho_{\rm{S}}^{\otimes n} \longrightarrow \rho_{\rm{S}}(n', \epsilon', n - n') \coloneqq  \rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n-n')},
+	\rho_{\rm{S}}^{\otimes n} \longrightarrow \rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n-n')},
 \end{equation}
 where all copies $n, n', n - n'$ are even.
+Since the state $\frac{1}{3} \id$ is free, tensoring in copies of it does not affect the distillation process.
+
 Since the initial state can be written in the form $\rho_{\rm{S}}(n, \epsilon, 0)$, it suffices to construct the Lorenz curve $\lc{\rho_{\rm{S}}}{\id/3}(x)$ for the generic noisy strange state $\rho_{\rm{S}}(n, \epsilon ,n')$.
@@
 \newpage
-\section{Magic bounds in arbitrary stabilizer fragments}\label{sec:thermal}
+\section{Magic bounds in arbitrary stabilizer fragments}
+\label{sec:stab}
 

### 2021-02-25 magic_paper.tex
More tidying

@@
 In particular, any $\sigma$--fragment, with $\sigma$ not full-rank, can be approximated by the $\sigma'$--fragment defined as a mixture of $\sigma$ with uniform noise, $\sigma' = (1-\epsilon)\sigma + \epsilon\frac{1}{d}\id$, for some infinitesimal $\epsilon > 0$, so that $\sigma'$ is full-rank and arbitrarily close to $\sigma$.
-There exist many $\sigma$--fragments with $\sigma$ not full-rank, such as when $\sigma$ is a pure stabilizer, e.g. the zero state as depicted in~\cref{fig:zero}. 
-Operations in such fragments include important stabilizer operations like the replacement channel defined as $\E(\rho) = \sigma$ for all states $\rho$.
+Important examples include pure stabilzer states which are rank-$1$ states e.g. the zero state depicted in~\cref{fig:zero}. 
+Operations in such fragments include important stabilizer operations like the replacement channel, $\E(\rho) = \sigma$ for all states $\rho$.
 
@@
 This is clear because for any state conversion like~\cref{eq:sigma_conv}, the Lorenz curve $L_{\tau|\sigma}$ is lower than $L_{\rho|\sigma}$, hence $\A_\sigma(\E(\rho)) \leq \A_\sigma(\rho)$.
-The exact form of the monotone is given in~\cref{app:areamono}
+The exact form of the monotone is given in~\cref{app:areamono}.
 \nick{should we include the area? Have a look at~\cref{app:areamono}}
@@
 \section{Mana as a feature of majorization}
+
+\nick{Should this be a section on its own or a subsection of the previous section?}
 
@@
 For this reason, we define the $n$-copy, $\epsilon$-noisy Strange state,
-\begin{equation}
+\begin{equation}\label{eq:noisysn}
     \rho_{\rm{S}}(\epsilon)^{\otimes n} \coloneqq \left[ (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \frac{1}{3}\id \right]^{\otimes n},
@@
 
-In~\cref{fig:lcs}, we illustrate the Lorenz curves of pure and noisy $n$-copy Strange states for $n$ up to $4$ in different $\sigma$--fragments.
+In~\cref{fig:lcs}, we illustrate the Lorenz curves $\lc{\rho_{\rm{S}}}{\sigma}$\footnote{We drop parameters $\epsilon$ and $n$ for clarity} of pure and noisy $n$-copy Strange states for $n$ up to $4$ in different $\sigma$--fragments.
 As shown in~\cref{lem:lcmax}, the curve peaks equal $1 + \sn{\rho_{\rm{S}}(\epsilon)^{\otimes n}}$ independently of the $\sigma$--fragment.
@@
 This process destroys the circuit symmetries, except for the invariance of the maximally mixed state.
-Dephasing and bit-flip error channels are examples of the many error-inducing channels that respect the unital symmetry. \nick{expand}
+Dephasing and bit-flip error channels are examples of the many error-inducing channels that respect the unital symmetry. \nick{Expand on significance of unital fragment}
 
@@
 
-We consider the problem of purifying $n$ copies of a noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ into a smaller number of copies $n'$ of a less noisy strange state $\rho_{\rm{S}}(\epsilon')^{\otimes n'}$, with $\epsilon' \leq \epsilon$ and $n' \leq n$,
+We consider the problem of purifying $n$ copies of a noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ as given in~\cref{eq:noisysn} into a smaller number of copies $n'$ of a less noisy strange state $\rho_{\rm{S}}(\epsilon')^{\otimes n'}$, with $\epsilon' < \epsilon$ and $n' \leq n$,
 \begin{equation}\label{eq:sudist}
-	\rho_{\rm{S}}^{\otimes n} \longrightarrow \rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n-n')},
+	\rho_{\rm{S}}(\epsilon)^{\otimes n} \longrightarrow \rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n-n')},
 \end{equation}
 where all copies $n, n', n - n'$ are even.
-Since the state $\frac{1}{3} \id$ is free, tensoring in copies of it does not affect the distillation process.
-
-Since the initial state can be written in the form $\rho_{\rm{S}}(n, \epsilon, 0)$, it suffices to construct the Lorenz curve $\lc{\rho_{\rm{S}}}{\id/3}(x)$ for the generic noisy strange state $\rho_{\rm{S}}(n, \epsilon ,n')$.
-This curve is defined at $9^n$ points between $0$ and $1$.
-The exact expressions for the coordinates of these points can take $8$ different forms, depending on whether the noise level $\epsilon$ is greater than or less than $\frac{3}{7}$, the parity of the number of copies $n$ is even/odd and the location relative to the curve peak is on the left hand side (LHS -- including the maximum) / right hand side (RHS).
-The full details are provided in~\cref{app:lcsu_technical}.
-
-Here we focus on the case of Lorenz curves of even copies $n, n'$ and low noise levels ($\epsilon \leq 3/7$).
+Since the state $\id / 3$ is free, tensoring in copies of it does not affect the distillation process.
+
+The Lorenz curve $\lc{\rho_{\rm{S}}}{\id/3}$, for some general noise parameter $\epsilon$ and number of copies $n$, is defined at $9^n$ points between $0$ and $1$.
+The exact expressions for the coordinates of these points can take $8$ different forms, depending on whether the noise level $\epsilon$ is greater or less than $\frac{3}{7}$, the parity of the number of copies $n$ is even or odd and the location relative to the curve peak is on the left hand side (LHS -- including the curve peak) or right hand side (RHS) of the curve peak.
+The full details for the Lorenz curve construction are provided in~\cref{app:lcsu_technical}.
+
+\nick{In the following, should we talk about the coordinates of all elbows and then say that we are gonna use only the first elbow, or should we leave full-elbow analysis for the appendix and only talk about first elbow here?}
+
+Here we focus on the case of Lorenz curves with even copies $n, n'$ and low noise levels ($\epsilon' < \epsilon \leq 3/7$).
 The part of the curve on the LHS of its peak is constructed by the positive components of the state Wigner distribution that take values $w_i$, with associated multiplicities $m_i$,
@@
 where $i=0,\dots,\frac{n}{2}$.
-From this, it is readily seen that $\lc{\rho}{\id/3}(x)$ has elbows on the LHS of its peak located at points $x=x_i$, where
+It is readily seen that $\lc{\rho_{\rm{S}}}{\id/3}(x)$ has elbows on the LHS of its peak located at points $x=x_i$, where
 \begin{equation}
@@
 
-We now generalise the approach taken in the previous section and consider bounds on magic distillation for an arbitrary stabilizer fragment, $\R_\sigma$ where $\sigma$ is any quantum state $\sigma \in \rm{STAB}$.
-In other words we consider those bounds on distillation that apply when the free operations have $\sigma$ as a fixed point.
+We now generalise the approach taken in the previous section and consider bounds on magic distillation for an arbitrary stabilizer fragment, $\R_\sigma$ where $\sigma$ is any quantum state $\sigma \in \stab$.
+In other words, we consider those bounds on distillation that apply when the free operations have $\sigma$ as a fixed point.
 
 These bounds can be interpreted in two different ways: on one hand they can be viewed as a family of upper bounds parameterized by a stabilizer state $\sigma$, on the other we can associate $\sigma$ to actual hardware limitations or to biased noise models in which it is an equilibrium state of some kind.
-Without loss of generality we can always write $\sigma = \frac{1}{\Z} e^{-\beta H}$ for some $\beta \ge 0$ and Hamiltonian $H$ (either effective or actual)\footnote{Technicalities arise for the case where $\sigma$ is not full rank, but this can be still described via $ \beta \rightarrow 0$ limiting process.}.
-
-Given this context, we can now state the following result, which is dependent on the free energy $F_\beta$ of a Gibbs state $\sigma$ where $ \beta F_\beta =  \beta\tr[H \sigma] - S(\sigma)$.
-We also fix the noisy Strange state to be of the form
-\begin{equation}
-	\rho_{\rm{S}}(\epsilon) \coloneqq (1-\epsilon)\ketbra{\rm{S}} + \epsilon \frac{1}{3}\id,
-\end{equation}
-but more general states can be handled in exactly the same manner.
-In the following result we consider the bounds on distilling out pure states $|S\>\<S|$, with $\epsilon'=0$, but these bounds are easily generalised to purification bounds with $\epsilon' \ne 0$.
-Finally, we assume that $\epsilon \le 3/7$, so that the noisy magic state has \nick{a dominant negative component}.
-\begin{theorem}Let $\sigma$ be a qutrit stabilizer state, given by $\sigma = \frac{1}{\Z} e^{-\beta H}$ with $H$ having eigenvalues $E_0 \le E_1 \le E_2$, and where $\beta$ is an (effective) inverse temperature for the state.
+Without loss of generality, we can always write a stabiler state $\sigma$ as a Gibbs state $\sigma = \frac{1}{\Z_\beta} e^{-\beta H}$ for some $\beta \geq 0$ and Hamiltonian $H$ as discussed in~\cref{sec:major_frag}.
+
+We focus on the distillation process
+\begin{equation}\label{eq:sudist}
+	\rho_{\rm{S}}(\epsilon)^{\otimes n} \longrightarrow \rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \gamma_\beta^{\otimes (n-n')},
+\end{equation}
+where the noisy Strange state is given in~\cref{eq:noisysn}, but more general states can be handled in exactly the same manner.
+Notice that tensoring in copies of $\gamma_\beta$ does not affect the process, since the state is free.
+In the following result, all copies $n, n', n - n'$ are even with $n > n'$, and $\epsilon'=0$, but the bounds are easily generalised to odd numbers of copies and $\epsilon'$ such that $0 < \epsilon' < \epsilon$.
+Finally, we assume a \nick{generous} range of initial noise levels, $\epsilon \leq 3/7$, so that the largest Wigner component of the 1-copy noisy magic state is negative.
+
+\nick{Specify: How general can the states get? What about not full-rank states? Should we include the case of odd $n$ or non-zero $\epsilon'$ in the appendix? What about $\epsilon>0$?}
+
+Given this context, we now provide the following result, which depends on the free energy $F_\beta$ of state $\sigma$,
+\begin{equation}
+	F_\beta \coloneqq \tr[H \sigma] - \beta^{-1}S(\sigma) = -\beta^{-1}\log{\Z_\beta},
+\end{equation}
+where the von Neumann entropy is $S(\sigma) \coloneqq -\tr[\sigma\log{\sigma}]$.
+
+\begin{theorem}\label{thm:stab_bounds}
+	Let $\sigma$ be a qutrit stabilizer state, given by $\sigma = \frac{1}{\Z} e^{-\beta H}$ with $H$ having eigenvalues $E_0 \le E_1 \le E_2$, and where $\beta$ is an (effective) inverse temperature for the state.
 We define
@@
 
+\begin{proof}
+	Here we provide a sketch of the proof with all the details included in \nick{the appendix}.
+
+\nick{Rest of section needs tidying}
+
 Consider a qutrit system with maximally Wigner-negative magic state $\ket{{\rm{S}}} = \frac{1}{\sqrt{2}}(\ket{1} - \ket{2})$.
@@
 All Wigner components are strictly positive, therefore the pre-order $\prec_{\gamma_\beta}$ is well defined.
-
-\subsubsection{Distillation bounds}
 
@@
 
+\end{proof}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-There exist $d(d+1)$ pure stabilizer states for a $d$-dimensional system, all of which correspond to a uniform distribution over an affine line in the phase space \nick{CITE}.
-As an example, the distribution of the qutrit zero state $\ketbra{0}$ is illustrated in~\cref{fig:zero}.
-Any pure stabilizer state $\sigma$ is a rank--$1$ state and contains $d^2 - d$ zeros in its Wigner distribution, so we approximate it by the full--rank state $\sigma' = (1-\epsilon)\sigma + \epsilon \frac{1}{d}\id$ for some $\epsilon > 0$.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\null\newpage
 \section{Lower bounds in $\sigma$--fragments}

### 2021-02-25 appendix.tex
More tidying before the unital section
Start of stabilizer section & first appendices, I am unsure of how structure unital section

@@
-\section{Properties of the Wigner distribution}
+\section{Properties of Wigner distributions}
 \label{app:wigner}
@@
 \begin{proposition}\label{thm:wstate}
-    The Wigner distribution of a state $\rho$ is
+  The Wigner distribution of a state $\rho \in \cal{B}(\cal{H}_d)$ is
   \begin{enumerate}
-        \item\label{en:w1} Real valued: $\W{\rho} \in \mathbb{R}^{d^2}$;
-        \item\label{en:w2} Normalised: $\sum_{\bmz \in \cal{P}_d} \W[\bmz]{\rho}=1$;
-        \item\label{en:w3} Bounded: $\abs{\W[\bmx]{\rho}} \leq \frac{1}{d}$.
-        \item\label{en:w4} Additive under mixing:
-
+    \item[(i)]\label{en:w1} Real valued: $\W{\rho} \in \mathbb{R}^{d^2}$;
+    \item[(ii)]\label{en:w2} Normalised: $\sum_{\bmz \in \cal{P}_d} \W[\bmz]{\rho}=1$;
+    \item[(iii)]\label{en:w3} Bounded: $\abs{\W[\bmx]{\rho}} \leq \frac{1}{d}$.
+    \item[(iv)]\label{en:w4} Additive under mixing: \vspace{2pt}\\
     $\W[\bmx]{\sum_i p_i \rho_i} = \sum\limits_i p_i \W[\bmx]{\rho_i}$;
-        \item\label{en:w5} Multiplicative under tensor products:
-
+    \item[(v)]\label{en:w5} Multiplicative under tensor products: \vspace{2pt}\\
     $\W[\bmx_A \oplus \bmx_B]{\rho_A \otimes \rho_B} = \W[\bmx_A]{\rho_A}\W[\bmx_B]{\rho_B}$.
@@
 \end{proposition}
-A distribution satisfying the first three properties does not necessarily correspond to a positive semi-definite state.
+Not all distributions satisfying these properties correspond to positive semi-definite states.
+\begin{proof}
+	\nick{Proof?}
+\end{proof}
 
@@
     \label{thm:wchannel}
-    The Wigner distribution of a $\cptp$ operation $\E: \cal{B}(\hd[d_A]) \mapsto \cal{B}(\hd[d_B])$ is:
+    The Wigner distribution of a $\cptp$ operation $\E: \cal{B}(\cal{H}_{d_A}) \mapsto \cal{B}(\cal{H}_{d_B})$ is
     \begin{enumerate}
-        \item\label{en:wo1} Real-valued: $\W[\bmy|\bmx]{\E} \in \mathbb{R}$;
-        \item\label{en:wo2} Normalised: $\sum_{\bmz \in \cal{P}_{d_B}} \W[\bmz|\bmx]{\E} = 1$ for any $\bmx \in \cal{P}_{d_A}$;
+        \item\label{en:wo1} Real-valued: $\W{\E} \in \mathbb{R}^{d^2} \times \mathbb{R}^{d^2}$;
+        \item\label{en:wo2} Normalised: $\sum_{\bmz \in \cal{P}_{d_B}} \W[\bmz|\bmx]{\E} = 1$ \\ 
+        for any $\bmx \in \cal{P}_{d_A}$;
         \item\label{en:wo3} Bounded: $\abs{\W[\bmy|\bmx]{\E}} \leq \frac{d_A}{d_B}$;
-	    \item\label{en:wo4} \nick{Transitive}: $\W[\bmy]{\E(\rho)} = \sum_{\bmz \in \cal{P}_{d_A}]} \W[\bmy|\bmz]{\E} \W[\bmz]{\rho}$ for any $\bmy \in \cal{P}_{d_B}$.
+	    \item\label{en:wo4} Transitive: $\W[\bmy]{\E(\rho)} = \sum_{\bmz \in \cal{P}_{d_A}} \W[\bmy|\bmz]{\E} \W[\bmz]{\rho}$ for any $\bmy \in \cal{P}_{d_B}$.
     \end{enumerate}
@@
 If $d_A = d_B$, and in particular if operation $\E$ maps a Hilbert space onto itself, then the stochasticity condition $\abs{\W[\bmy|\bmx]{\E}} \leq 1$ is satisfied.
+\begin{proof}
+	\nick{Proof?}
+\end{proof}
+A $(d \times d)$ matrix $S$ is in $\stoch$, if
+\begin{enumerate}
+    \item $S_{ij} \geq 0$ for all $i, j \in \mathbb{Z}_d$;
+    \item $\sum\limits_{j=1}^n S_{ij} = 1$ for all $i \in \mathbb{Z}_d$;
+    \item $S\bmd = \bmd$.
+\end{enumerate}
 
@@
 
-\subsection{Equivalent conditions for majorization}
+\subsection{Simple--majorization equivalence conditions}
 
-Any $\bmd$-majorization problem can be rephrased as a majorization problem in a higher dimensional space due to the embedding map.
+In the unital fragment, namely the limit of infinite temperature, $\beta = 0$, the free state is the maximally mixed state $\frac{1}{d}\id$ with uniform Wigner distribution $\frac{1}{d}\bm{1}  = (\frac{1}{d},\dots,\frac{1}{d})$.
+This fragment is governed by simple majorization and we first prove strong equivalences for this type of majorization.
+\begin{theorem}\label{thm:major}
+Given $\bmx, \bmy \in \mathbb{R}^n$ the following statements are equivalent:
+ \begin{enumerate}
+	\item\label{en:m1} $\bmx \prec \bmy$;
+	\item\label{en:m2} $\bmx = B \bmy$ for bistochastic $B$;
+	\item\label{en:m3} $\sum\limits_{i=1}^n \abs{x_i - t} \leq \sum\limits_{i=1}^n \abs{y_i - t}$ for all $t \in \mathbb{R}$;
+	\item\label{en:m4} $\sum\limits_{i=1}^n (x_i - t)^+ \leq \sum\limits_{i=1}^n (y_i - t)^+$ for all $t \in \mathbb{R}$ and $\sum\limits_{i=1}^n x_i = \sum\limits_{i=1}^n y_i$, where $(x)^+ = \max{\{x, 0\}}$;
+	\item\label{en:m5} $L_{\bmx}(k) \leq L_{\bmy}(k)$ for $k=1,\dots,n-1$	and $L_{\bmx}(n) = L_{\bmy}(n)$.
+ \end{enumerate}
+\end{theorem}
+\begin{proof}
+	\nick{Proof?}
+\end{proof}
+
+\subsection{Embedding map}
+
+Any $\bmd$-majorization problem can be rephrased as a simple majorization problem in a higher dimensional space via the embedding map.
 \begin{definition}
@@
   \begin{equation}
-        \Gamma_{\bmd}(\bmz) = \bigoplus_{i=1}^n z_i\  \frac{1}{d_i}\bm{1},
+    \Gamma_{\bmd}(\bmw) = \bigoplus_{i=1}^n w_i\  \frac{1}{d_i}\bm{1},
   \end{equation}
 where $\bm{1}/d_i$ is the $d_i$-dimensional uniform distribution.
-    The left inverse $\Gamma_{\bmd}^{-1}: \mathbb{R}^D \mapsto \mathbb{R}^n$ is defined to sum up the elements in each block of $\Gamma_{\bmd}(\bmz)$, so that
+The left inverse $\Gamma_{\bmd}^{-1}: \mathbb{R}^D \mapsto \mathbb{R}^n$ is defined to sum up the elements in each block of $\Gamma_{\bmd}(\bmw)$, so that
   \begin{equation}
-        \Gamma_{\bmd}^{-1}(\oplus_{i=1}^n z_i \bm{1}/d_i) = \bmz.
+     \Gamma_{\bmd}^{-1}(\oplus_{i=1}^n w_i \bm{1}/d_i) = \bmw.
   \end{equation}
@@
 The embedding map maps the Gibbs distribution to the uniform distribution, $\Gamma_{\bmd}(\bmd) = \bm{1}/D$.
-Then, a non-increasing ordering $\Gamma_{\bmd}(\bmz)^\downarrow$ in the new space, corresponds to the so-called ``$\beta$-ordering'' of the original vector denoted by the permutation $\pi$ mapping $(z_i/d_i) \mapsto (z_i/d_i)^\downarrow$ for all $i=1,\dots,n$.
-Intuitively, $\beta$-ordering tends to simply non-increasing ordering as $\beta$ tends to 0.
-This ordering naturally leads to a generalised notion of the Lorenz curve.
+Then, a non-increasing ordering $\Gamma_{\bmd}(\bmz)^\downarrow$ in the new space, corresponds to the so-called ``$\beta$-ordering'' of the original vector denoted by the permutation $\pi$ in~\cref{def:lc}, mapping $(w_i/d_i) \mapsto (w_i/d_i)^\downarrow$ for all $i=1,\dots,n$.
+
+\subsection{\textit{d}-majorization equivalence conditions}
 
@@
 Given $\bmx, \bmy, \bmd \in \mathbb{R}^n$, such that the components of $\bmd$ are positive, the following statements are equivalent:
- \begin{enumerate}%[\rm{(TM1)}]
+  \begin{enumerate}
     \item $\bmx \prec_{\bmd} \bmy$;
@@
     \item $\sum\limits_{i=1}^n (x_i - t d_i)^+ \leq \sum\limits_{i=1}^n (y_i - t d_i)^+$ for all $t \in \mathbb{R}$ and $\sum\limits_{i=1}^n x_i = \sum\limits_{i=1}^n y_i$;
-	\item $\forall k, L_{\bmx|\bmd}(k) \leq L_{\bmy|\bmd}(k)$ and $L_{\bmx|\bmd}(k=n) = L_{\bmy|\bmd}(k=n)$.
+    \item $L_{\bmx|\bmd}(k) \leq L_{\bmy|\bmd}(k)$ for $k=1,\dots,n-1$	and $L_{\bmx|\bmd}(n) = L_{\bmy|\bmd}(n)$.
   \end{enumerate}
@@
 \begin{proof}
+  \nick{Proof?}
+\end{proof}
+\iffalse
     \begin{enumerate}
@@
     \end{enumerate}
-\end{proof}
-
-The Lorenz curve can be explicitly expressed as
-    \begin{equation}
-		\lc{\rho}{\sigma}(x) = (\bmu^\downarrow)_i x + \lc{\rho}{\sigma}(i) - (\bmu^\downarrow)_i x_i,\ x \in (x_{i-1}, x_i],
-	\end{equation}
-	for all $i=1,\dots,d$ with $x_0 \coloneqq 0$.
-
-\begin{proposition}\label{thm:lccont}
-	The Lorenz curve $\lc{\rho}{\sigma}(x)$ of a state $\rho$ with respect to state $\sigma$ is uniformly continuous in $\sigma$.
-\end{proposition}
-\begin{proof}
-	If $\sigma$ and $\sigma'$ are $\delta$-close with respect to a state norm, then the curves $\lc{\rho}{\sigma}(x)$ and $\lc{\rho}{\sigma'}(x)$ are $\epsilon$-close at all $x \in [0,1]$.
-\end{proof}
+\fi
 
@@
 
-\section{Properties of $\sigma$-fragments}
+\section{Properties of $\sigma$--fragments}
 \label{app:frag}
 
+\nick{this section hasn't been refereced in various parts of the main text}
+
 \begin{theorem}\label{thm:frag_app}
-    Let $\R = (\O, \F)$ be a magic theory. 
+    Let $\R_\sigma = (\O_\sigma, \F_\sigma)$ be a $\sigma$--fragment of magic theory $\R = (\O, \F)$. 
     The following statements hold:
     \begin{enumerate}
-        \item No $\sigma$-fragment is empty.
+        \item No $\sigma$--fragment is empty.
         \item If a free operation leaves two states invariant, then it also leaves their mixtures invariant, 
-        \begin{equation}
+        \begin{equation*}
             \O_{\sigma} \cap \O_{\sigma'} \subseteq \O_{p\sigma + (1-p)\sigma'}\ \text{for all}\ p \in [0,1].
-        \end{equation}
+        \end{equation*}
         \item Let $\E$ be a $\cptp$ operation with Wigner distribution $\W{\E}$.
-        For $\R = \Rmax$ $\E \in \O_\sigma$ iff $\W{\E} \in \stochw$.
+        For $\R = \Rmax$, $\E \in \O_\sigma$ iff $\W{\E} \in \stochw$. \nick{I don't like this one}
     \end{enumerate}
@@
     \begin{enumerate}
-    \item The identity channel $1_{\rm{C}}: \D \mapsto \D$ belongs to every $\sigma$-fragment, as $1_{\rm{C}} \in \O$ and $1_{\rm{C}}\sigma = \sigma$ for all $\sigma \in \F$.
+    \item The identity channel $1_{\rm{C}}: \D \mapsto \D$ belongs to every $\sigma$--fragment, as $1_{\rm{C}} \in \O$ and $1_{\rm{C}}\sigma = \sigma$ for all $\sigma \in \F$.
 
@@
 
-Any free state $\sigma \in \cal{B}(\hd)$ corresponds to a $d^2$-dimensional probability distribution $\W{\sigma}$ and any free operation $\E: \cal{B}(\hd) \mapsto \cal{B}(\hd)$ corresponds to a $d^2 \times d^2$ stochastic matrix (or conditional probability distribution) $\W{\E}$.
+Any free state $\sigma \in \F$ corresponds to a $d^2$-dimensional probability distribution $\W{\sigma}$ and any free operation $\E \in \O$ corresponds to a $d^2 \times d^2$ stochastic matrix (or conditional probability distribution) $\W{\E}$.
 Note that these mappings are one-to-one due to the orthogonality of the phase-point operators as an operator basis.
 
-\emph{Remark 1.} Note that free states $\F$ are mapped onto a \emph{strict subset} of the set of probability distributions.
-As a counterexample, the sharp $d^2$-dimensional probability distribution $(1, 0, \dots, 0)$ does not correspond to any qudit Wigner distribution because of the boundedness condition~\ref{en:w3} in~\cref{thm:wstate}.
+Note further that free states $\F$ are mapped onto a \emph{strict subset} of the set of probability distributions.
+As a counterexample, the sharp $d^2$-dimensional probability distribution $(1, 0, \dots, 0)$ does not correspond to any qudit Wigner distribution because of the boundedness condition in~\cref{thm:wstate}.
 
-\emph{Remark 2.} Similarly, not all stochastic matrices correspond to completely positive operations.
-
+Similarly, not all stochastic matrices correspond to completely positive operations.
 As an example, consider the permutation matrix
@@
 \end{equation}
-It preserves the uniform distribution $\W{\frac{1}{5}\id}{}$, but it does not correspond to any $\cpos$ operation, hence any $\E \in \O$ due to~\cref{thm:frag}.
+It preserves the uniform distribution $\W{\frac{1}{5}\id}$, but it does not correspond to any positive operation.
 
-\section{Lorenz curve properties}
+\section{Properties of Lorenz curves}
 \label{app:lc_properties}
 
-Single-copy Lorenz curves are simply additive in noise, 
+\nick{Prove statements underneath~\cref{def:lc}?}
+
+\subsection{Basic properties}
+
+Furthermore, single-copy Lorenz curves are simply additive in noise, 
 \begin{equation}
@@
 
+\subsection{$\sigma$--fragment continuity}
+
+\begin{proposition}\label{thm:lccont}
+	The Lorenz curve $\lc{\rho}{\sigma}(x)$ of a state $\rho$ with respect to state $\sigma$ is uniformly continuous in $\sigma$.
+\end{proposition}
+\begin{proof}
+	\nick{Idea:} If $\sigma$ and $\sigma'$ are $\delta$-close with respect to a state norm, then the curves $\lc{\rho}{\sigma}(x)$ and $\lc{\rho}{\sigma'}(x)$ are $\epsilon$-close at all $x \in [0,1]$.
+\end{proof}
+
 \subsection{Area monotone}\label{app:areamono}
 
-\begin{figure}[t]%
+\nick{I don't believe in the area monotone - should we keep?}
+
+\begin{figure}[h]%
     \centering
@@
 \subsection{Component-multiplicity pairs}
+\label{app:cmpairs}
 

### 2021-02-25 magic_paper.tex
Start of stabilizer section & first appendices, I am unsure of how structure unital section

@@
 Since the field has character $d$, addition and multiplication on the field are always considered modulo $d$.
-The Hilbert space of any system associated with this scheme is $\hd \coloneqq \spanv{\ket{k}: k \in \mathbb{Z}_d}$.
+The Hilbert space of any system associated with this scheme is $\cal{H}_d \coloneqq \spanv{\ket{k}: k \in \mathbb{Z}_d}$.
 
@@
 where $\omega \coloneqq e^{2\pi i/d}$ is the $d$-th root of unity and addition is modulo $d$.
-The Hilbert space $\hd$ is associated with a phase space $\cal{P}_d = \mathbb{Z}_d \times \mathbb{Z}_d$, where every point $\bmx \coloneqq (x, p)$ corresponds to a displacement operator, defined as
+The Hilbert space $\cal{H}_d$ is associated with a phase space $\cal{P}_d = \mathbb{Z}_d \times \mathbb{Z}_d$, where every point $\bmx \coloneqq (x, p)$ corresponds to a displacement operator, defined as
 \begin{equation}\label{eq:ddef}
@@
 The phase factor $\tau \coloneqq -\omega^{1/2}$ ensures unitarity.
-For a composite system with product dimension $d = d_1 \dots d_n$ and Hilbert space, $\hd = \hd[d_1] \otimes \dots \otimes \hd[d_n]$, the displacement operators are defined as
+For a composite system with product dimension $d = d_1 \dots d_n$ and Hilbert space, $\cal{H}_d = \cal{H}_{d_1}] \otimes \dots \otimes \cal{H}_{d_n}]$, the displacement operators are defined as
 \begin{equation}\label{eq:composited}
@@
 The phase-point operators form an orthogonal Hermitian operator basis as shown in~\cref{app:wigner}.
-Therefore, any quantum state $\rho \in \cal{B}(\hd)$ can be expressed as a linear combination of them,
+Therefore, any quantum state $\rho \in \cal{B}(\cal{H}_d)$ can be expressed as a linear combination of them,
 \begin{equation}
@@
 Specifically, for any $S \in \stoch$, all matrix elements are non-negative, all rows sum to $1$ and $S\bmd = \bmd$.
-\iffalse
-\begin{enumerate}
-    \item $S_{ij} \geq 0$ for all $i, j \in \mathbb{Z}_d$;
-    \item $\sum\limits_{j=1}^n S_{ij} = 1$ for all $i \in \mathbb{Z}_d$;
-    \item $S\bmd = \bmd$.
-\end{enumerate}
-\fi
 The set $\stoch$ forms a group under matrix multiplication for all $\bmd$ with positive components.
 
-Majorization exactly describes quantum thermodynamics in the absence of coherence.
+Majorization describes quantum thermodynamics exactly in the absence of quantum coherence.
 The use of majorization in this setting provides vital intuition for our purposes.
@@
 Informally, there exists a thermal operation $\E$ such that $\tau = \E(\rho)$ if and only if there exists a matrix $S \in \stoch$ such that $\bm{q} = S\bm{p}$, where $\bm{q}, \bm{p}$ and $\bmd$ and the energy level population vectors of $\tau, \rho, \gamma_\beta$ respectively.
+Formal statements of the above can be found \nick{in the appendix}.
 
@@
 
-    Consider the piecewise linear curve obtained by joining the points $\{(0,0)\} \cup \{ (x_k, \lc{\bmz}{\bmd}(k)) \}_{k=1,\dots,d}$, where
+    Consider the piecewise linear curve obtained by joining the points $\{(0,0)\} \cup \{ (x_k, \lc{\bmw}{\bmd}(k)) \}_{k=1,\dots,d}$, where
     \begin{equation}\label{eq:lorenz}
@@
 We focus on the distillation process
-\begin{equation}\label{eq:sudist}
+\begin{equation}\label{eq:stdist}
 	\rho_{\rm{S}}(\epsilon)^{\otimes n} \longrightarrow \rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \gamma_\beta^{\otimes (n-n')},

### 2021-03-07 magic_paper.tex
Started discussion on rate comparison

@@
 We write $\lc{\rho}{\sigma}(x)$ for the Lorenz curve of $\W{\rho}$ with respect to $\W{\sigma}$.
-The vector of ratios $\widetilde{\bmw}(\rho|\sigma)$ used to construct the curve and defined as
+The vector of ratios $\widetilde{\bmw}(\rho|\sigma)$ used to construct the curve is defined as
 \begin{equation}
@@
 in $\O_\sigma$, where $\ket{\rm{S}}$ is defined in~\cref{fig:strange} and the induced noise is uniform.
+
 For $\epsilon=0$, this state is a qutrit of maximal sum-negativity / mana~\cite{cit:veitch2} and therefore acts as the ideal distiallation target, analogous to a Bell state in bipartite entangelement theory.
+The Strange state is exceptionally symmetric under Clifford transformations and as a result there exists a \emph{twirling} protocol, discussed in detail in~\cite{cit:prakash,cit:prakash2}, allowing for the conversion of any noisy magic state to the form of~\cref{eq:noisysn} via Cliffords.
 
@@
 These bounds can be interpreted in two different ways: on one hand they can be viewed as a family of upper bounds parameterized by a stabilizer state $\sigma$, on the other we can associate $\sigma$ to actual hardware limitations or to biased noise models in which it is an equilibrium state of some kind.
-Without loss of generality, we can always write a stabiler state $\sigma$ as a Gibbs state $\sigma = \frac{1}{\Z_\beta} e^{-\beta H}$ for some $\beta \geq 0$ and Hamiltonian $H$ as discussed in~\cref{sec:major_frag}.
+Without loss of generality, we can always write a stabiler state $\sigma$ as a Gibbs state $\sigma = \gamma_\beta \coloneqq \frac{1}{\Z_\beta} e^{-\beta H}$ for some $\beta \geq 0$ and Hamiltonian $H$ as discussed in~\cref{sec:major_frag}.
 
@@
 where the noisy Strange state is given in~\cref{eq:noisysn}, but more general states can be handled in exactly the same manner.
+We also highlight that any magic state can be written in terms of a noisy Strange state.
 Notice that tensoring in copies of $\gamma_\beta$ does not affect the process, since the state is free.
@@
 
-\nick{Specify: How general can the states get? What about not full-rank states? Should we include the case of odd $n$ or non-zero $\epsilon'$ in the appendix? What about $\epsilon>0$?}
+\nick{Specify: How general can the states get? What about not full-rank states? Should we include the case of odd $n$ or non-zero $\epsilon'$ in the appendix? What about $\epsilon>3/7$?}
 
@@
 
+\section{Comparison with existing distillation rates}
+\label{sec:comparison}
+
+We have derived a \emph{distillation bound} $R(\epsilon, \epsilon', \beta)$ for the process
+\begin{equation}\label{eq:stdist}
+	\rho_{\rm{S}}(\epsilon)^{\otimes n} \longrightarrow \rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \gamma_\beta^{\otimes (n-n')},
+\end{equation}
+with even $n, n'$ and $0 \leq \epsilon' < \epsilon \leq 3/7$, where the $n$-copy, $\epsilon$-noisy Strange state is
+\begin{equation}\label{eq:test}
+    \rho_{\rm{S}}(\epsilon)^{\otimes n} \coloneqq \left[ (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \frac{1}{3}\id \right]^{\otimes n}.
+\end{equation}
+
+The bound informs us that any distillation protocol in the $\gamma_\beta$-fragment with an $\epsilon$-noisy input and $\epsilon'$-noisy output has a \emph{distillation rate} 
+\begin{equation}
+	\frac{n'}{n} \leq R(\epsilon, \epsilon', \beta).
+\end{equation}
+
+We can rephrase this result, saying that any distillation protocol in the $\gamma_\beta$-fragment with an $n$-copy input and $n'$-copy, $\epsilon'$-noisy desired output, must have input noise level 
+\begin{equation}
+	\epsilon \leq  E\left(\frac{n'}{n}, \epsilon', \beta \right)
+\end{equation}
+for some error bound $E$ related to $R$.
+
+An $n$-copy state $\rho^n$ has \emph{error rate} $\epsilon$ iff $\rho$ has an overlap of at least $1-\epsilon$ with magic state $\ket{\rm{S}}$,
+\begin{equation}
+	\bra{\rm{S}}\rho\ket{\rm{S}} \geq 1-\epsilon.
+\end{equation}
+The $\epsilon$-noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ has error rate $\frac{2}{3}\epsilon$.
+A general state of $n$ qutrits with error rate $\epsilon$ can be converted to the form $\rho_{\rm{S}}(\epsilon_0)^{\otimes n}$ for some noise level $\epsilon_0$ not necessarily equal to $\epsilon$.
+
+Given an $[[n,n',d]]$ error correcting code, a distillation protocol that achieves the process in~\cref{eq:test} requires
+\begin{align}
+	\epsilon' &\sim O((n\epsilon)^d) \\
+	\frac{n}{n'} &\sim O(\log^\gamma{1/\epsilon'}),\ \gamma = \log_d{\left(\frac{n}{n'}\right)}
+\end{align}
+
+In~\cite{Bravyi2012,Hastings2018}, the asymptotic rate $O(\log^\gamma{1/\epsilon'})$ is called the \emph{distillation cost}.
+\nick{These inequalities seem to be the other way around.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-03-08 magic_paper.tex
Added thoughts on how to incorporate our results in current literature

@@
 \begin{align}
-	\epsilon' &\sim O((n\epsilon)^d) \\
-	\frac{n}{n'} &\sim O(\log^\gamma{1/\epsilon'}),\ \gamma = \log_d{\left(\frac{n}{n'}\right)}
-\end{align}
-
-In~\cite{Bravyi2012,Hastings2018}, the asymptotic rate $O(\log^\gamma{1/\epsilon'})$ is called the \emph{distillation cost}.
-\nick{These inequalities seem to be the other way around.}
+	\epsilon' &\sim O\left((n\epsilon)^d\right) \\
+	\frac{n}{n'} &\sim O(\log^\gamma{(1/\epsilon')}),\ \gamma = \log_d{\left(\frac{n}{n'}\right)}
+\end{align}
+
+In~\cite{Bravyi2012,Hastings2018}, the asymptotic rate $O(\log^\gamma{(1/\epsilon')})$ is called the \emph{distillation cost}.
+
+There are many distillation protocols in the literature, e.g.~\cite{Bravyi2012,Hastings2018}, that involve a specific value of $\gamma$.
+They should all satisfy
+\begin{equation}\label{eq:rate_cost}
+	\frac{1}{R(\epsilon, \epsilon', \beta)} \leq \frac{n}{n'} \sim O(\log^\gamma{(1/\epsilon')}).
+\end{equation}
+Therefore, given process parameters $n, n', \epsilon, \epsilon'$, we can scan through the stabilizer states to find a range of $\beta$ for which inequality~\cref{eq:rate_cost} is valid.
+In principle, the higher the value of parameter $\gamma$, the lower the output error rate $\epsilon'$ can be while~\cref{eq:rate_cost} is still true.
+In~\cite{Hastings2018} \nick{CITE MORE}, they report a value of $\gamma = 0.6779\dots$, while in~\cite{Krishna2019}, they report a scaling $\gamma = O(1/\log{d})$ with respect to the system's odd prime dimension $d$.
+The latter tends to 0 asymptotically.
+
+Furthermore, in~\cite{cit:bravyi,cit:prakash}, two different distillation protocols are proposed with output error rate scalings of the form 
+\begin{equation}
+	\epsilon' \propto (\alpha \epsilon)^{n^\xi},
+\end{equation}
+where $\alpha$ is some constant, $\xi = 1/\log_3{15} \approx 0.4$ in~\cite{cit:bravyi} for qubit codes and $\xi = 1/\log_3{19008} \approx 0.1$ for qutrit codes.
+They also report a certain input threshold error rate $\epsilon_\star$ above which distillation is not possible.
+A first requirement is that $\epsilon_\star \leq E(n'/n, \epsilon', \beta)$, but we can also again find a range of $\beta$ for which the inequality
+\begin{equation}
+	\epsilon \leq E\left(\frac{n'}{n}, \epsilon'(\epsilon), \beta \right)
+\end{equation}
+holds, given some distillation rate $n'/n$ and input error rate $\epsilon$.
 

### 2021-03-12 magic_paper.tex
Added comparisons with prakash

@@
 
-In particular, any $\sigma$--fragment, with $\sigma$ not full-rank, can be approximated by the $\sigma'$--fragment defined as a mixture of $\sigma$ with uniform noise, $\sigma' = (1-\epsilon)\sigma + \epsilon\frac{1}{d}\id$, for some infinitesimal $\epsilon > 0$, so that $\sigma'$ is full-rank and arbitrarily close to $\sigma$.
+In particular, any $\sigma$--fragment, with $\sigma$ not full-rank, can be approximated by the $\sigma'$--fragment defined as a mixture of $\sigma$ with depolarising noise, $\sigma' = (1-\epsilon)\sigma + \epsilon\frac{1}{d}\id$, for some infinitesimal $\epsilon > 0$, so that $\sigma'$ is full-rank and arbitrarily close to $\sigma$.
 Important examples include pure stabilzer states which are rank-$1$ states e.g. the zero state depicted in~\cref{fig:zero}. 
@@
 \end{equation}
-in $\O_\sigma$, where $\ket{\rm{S}}$ is defined in~\cref{fig:strange} and the induced noise is uniform.
+in $\O_\sigma$, where $\ket{\rm{S}}$ is coined in~\cref{fig:strange} and we induce uniform depolarising noise.
 
@@
 In the following result, all copies $n, n', n - n'$ are even with $n > n'$, and $\epsilon'=0$, but the bounds are easily generalised to odd numbers of copies and $\epsilon'$ such that $0 < \epsilon' < \epsilon$.
-Finally, we assume a \nick{generous} range of initial noise levels, $\epsilon \leq 3/7$, so that the largest Wigner component of the 1-copy noisy magic state is negative.
+Finally, we assume a range of initial noise levels, $\epsilon \leq 3/7$  \nick{higher than all threshold values CITE}, so that the largest Wigner component of the 1-copy noisy magic state is negative.
 
@@
 This is the pure Strange state visualised in~\cref{fig:strange}.
-We allow for isotropic (uniform) noise, so that the system state is a convex sum of the pure Strange state and the maximally mixed state,
+We allow for depolarising noise, so that the system state is a convex sum of the pure Strange state and the maximally mixed state,
 \begin{equation}
@@
 		&= e^{-\beta n' (E_{\rm{max}} - E_0)} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} \\
-		&< \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} = x_0'.
+		&\leq \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} = x_0'.
 	\end{align*}
@@
 
-We can rephrase this result, saying that any distillation protocol in the $\gamma_\beta$-fragment with an $n$-copy input and $n'$-copy, $\epsilon'$-noisy desired output, must have input noise level 
-\begin{equation}
-	\epsilon \leq  E\left(\frac{n'}{n}, \epsilon', \beta \right)
-\end{equation}
-for some error bound $E$ related to $R$.
-
-An $n$-copy state $\rho^n$ has \emph{error rate} $\epsilon$ iff $\rho$ has an overlap of at least $1-\epsilon$ with magic state $\ket{\rm{S}}$,
-\begin{equation}
-	\bra{\rm{S}}\rho\ket{\rm{S}} \geq 1-\epsilon.
-\end{equation}
-The $\epsilon$-noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ has error rate $\frac{2}{3}\epsilon$.
-A general state of $n$ qutrits with error rate $\epsilon$ can be converted to the form $\rho_{\rm{S}}(\epsilon_0)^{\otimes n}$ for some noise level $\epsilon_0$ not necessarily equal to $\epsilon$.
-
-Given an $[[n,n',d]]$ error correcting code, a distillation protocol that achieves the process in~\cref{eq:test} requires
-\begin{align}
-	\epsilon' &\sim O\left((n\epsilon)^d\right) \\
-	\frac{n}{n'} &\sim O(\log^\gamma{(1/\epsilon')}),\ \gamma = \log_d{\left(\frac{n}{n'}\right)}
-\end{align}
-
-In~\cite{Bravyi2012,Hastings2018}, the asymptotic rate $O(\log^\gamma{(1/\epsilon')})$ is called the \emph{distillation cost}.
-
-There are many distillation protocols in the literature, e.g.~\cite{Bravyi2012,Hastings2018}, that involve a specific value of $\gamma$.
+We apply our results on the ternary Golay code distillation protocol suggested in~\cite{cit:prakash}.
+In this protocol, a single Strange state is distilled with noise level
+\begin{equation}
+	\epsilon'(n, \epsilon) \approx \frac{1}{\alpha}(\alpha\epsilon)^{n^\xi},
+\end{equation}
+where $\alpha \approx 1.75$ and $\xi \approx 0.112$ are constants specific to the protocol.
+This can be rewritten in terms of the protocol distillation rate,
+\begin{equation}
+	R_{\rm{Golay}}(\epsilon, \epsilon') = \frac{1}{n} \approx \left( \frac{\log{(\alpha \epsilon)}}{\log{(\alpha \epsilon')}} \right)^{\frac{1}{\xi}}
+\end{equation}
+
+We compare the distillation rate of the protocol with our distillation bound, 
+\begin{equation}
+	R_{\rm{Golay}}(\epsilon, \epsilon') \leq R(\epsilon, \epsilon', \beta)
+\end{equation} 
+in figure~\cref{fig:prakash_compare}
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.5]{figs/prakash_compare.png}
+    \caption{\textbf{Comparison with ternary Golay distillation rate.}
+    Our bound is not violated but gets close to saturated for some noise levels.
+    The thick diagonal line indicates where $\epsilon' = \epsilon$.
+    }
+    \label{fig:prakash_compare}
+\end{figure}
+
+We can also rewrite the expression as 
+\begin{equation}
+	\epsilon_{\rm{Golay}}(\epsilon', n) \approx \frac{1}{\alpha}(\alpha\epsilon')^{n^{-\xi}},
+\end{equation}
+and compare with the numerically optimal error bounds provided by majorization as shown in~\cref{fig:prakash_compare_errors}
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.5]{figs/prakash_compare_errors.png}
+    \caption{\textbf{Comparison with ternary Golay output error rate.}
+    Our bound is not violated but achieves a maximum saturation of $\epsilon_\star - \epsilon_{\rm{Golay}} = 0.147$.
+    }
+    \label{fig:prakash_compare_errors}
+\end{figure}
+
+\iffalse
+An $n$-copy state $\rho^n$ has \emph{error rate} $\delta$ iff $\rho$ has an overlap of at least $1-\delta$ with magic state $\ket{\rm{S}}$,
+\begin{equation}
+	\bra{\rm{S}}\rho\ket{\rm{S}} \geq 1-\delta.
+\end{equation}
+The $\epsilon$-noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ has error rate $\delta = \frac{2}{3}\epsilon$.
+A general state of $n$ qutrits with error rate $\delta$ can be converted to the form $\rho_{\rm{S}}(\epsilon_0)^{\otimes n}$ for some noise level $\epsilon$ not necessarily equal to $\delta$.
+
+Given an $[[m,k,d]]$ error correcting code, a distillation protocol that achieves the process in~\cref{eq:test} requires that the following bound holds,
+\begin{align}
+	\frac{n}{n'} = O(\log^\gamma{(1/\epsilon')}),\ \gamma = \log_d{\left(\frac{m}{k}\right)}
+\end{align}
+
+In~\cite{Bravyi2012,Hastings2018}, the asymptotic rate $O(\log^\gamma{(1/\epsilon')})$ is called the \emph{distillation cost}, and in~\cite{cit:bravyi,Krishna2019} the parameter $\gamma$ is called the \emph{overhead}.
+
+There are many distillation protocols in the literature, e.g.~\cite{Bravyi2012,Hastings2018}, that involve a specific value of $\gamma$ and convert a specific number of copies $n$ of input states to $n'=1$ output state \nick{what about $\epsilon$?}.
 They should all satisfy
 \begin{equation}\label{eq:rate_cost}
-	\frac{1}{R(\epsilon, \epsilon', \beta)} \leq \frac{n}{n'} \sim O(\log^\gamma{(1/\epsilon')}).
+	\frac{1}{R(\epsilon, \epsilon', \beta)} \leq \frac{n}{n'} = O(\log^\gamma{(1/\epsilon')}).
 \end{equation}
@@
 
+We can rephrase this result, saying that any distillation protocol in the $\gamma_\beta$-fragment with an $n$-copy input and $n'$-copy, $\epsilon'$-noisy desired output, must have input noise level 
+\begin{equation}
+	\epsilon \leq  E\left(\frac{n'}{n}, \epsilon', \beta \right)
+\end{equation}
+for some error bound $E$ related to $R$.
+
 Furthermore, in~\cite{cit:bravyi,cit:prakash}, two different distillation protocols are proposed with output error rate scalings of the form 
@@
 A first requirement is that $\epsilon_\star \leq E(n'/n, \epsilon', \beta)$, but we can also again find a range of $\beta$ for which the inequality
-\begin{equation}
-	\epsilon \leq E\left(\frac{n'}{n}, \epsilon'(\epsilon), \beta \right)
-\end{equation}
+\begin{align}
+	\epsilon &\leq E\left(\frac{n'}{n}, \epsilon'(\epsilon), \beta \right) \\
+	\epsilon' &\sim O\left((n\epsilon)^d\right)
+\end{align}
 holds, given some distillation rate $n'/n$ and input error rate $\epsilon$.
+\fi
 

### 2021-03-16 magic_paper.tex
Summary of possible comparisons added

@@
 
+A recent distillation bound was introduced in~\cite{Seddon2020}, where they show that for the deterministic conversion of $n$ copies of a qubit state $\rho$ to a target pure magic state $\ket{\psi}$, the following bound on the distillation rate holds,
+\begin{equation}\label{eq:seddon}
+	\frac{n'}{n} \leq \frac{\log{\Lambda^+(\rho)}}{\log{F(\psi)^{-1}}},
+\end{equation}
+where $\Lambda^+(\rho)$ is the generalised robustness of state $\rho$, calculable via a costly SDP and $F(\psi)$ denotes the stabilizer fidelity of state $\ket{\psi}$.
+They demonstrate the performance of their bound by considering the purification process of the qubit magic state $\ket{H}$, with their figure replicated in~\cref{fig:seddon}. 
+For high initial noise level ($\epsilon = 0.25$), their bound dictates that $R = 1/150$, which is pretty good.
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.3]{figs/seddon.png}
+    \caption{\textbf{Comparison of Seddon \textit{et al.}'s bound~\cite{Seddon2020} in~\cref{eq:seddon} with a generic resource bound in~\cite{Fang2020}.}
+    The process they consider is purifying $n$ copies of $(1-\epsilon)\ketbra{H} + \epsilon/3 \id$ to $n'$ copies of $(1-\epsilon')\ketbra{H} + \epsilon'/3 \id$.
+    Their bound (red and blue) is pretty good compared with the generic (violet) bound.
+    Not sure why it looks like their bound gives $n\rightarrow 25$ as $1-\epsilon \rightarrow 1$.
+    }
+    \label{fig:seddon}
+\end{figure}
+
+Similar concrete rates have been studied for qudits in two occasions:
+First, the mana bound, which we have demonstrated in~\cref{fig:distill_bounds}.
+Secondly, Wang \textit{et al.}'s max-thauma bound~\cite{Wang2020}, which as far as I can tell, is less tight than mana (?).
+It is defined via an SDP, but we can use its properties (super-additivity and zero at free states) to readily get a bound on noisy Strange states,
+\begin{equation}
+	\theta_{\rm{max}}(\rho_{\rm{S}}(\epsilon)) \geq (1-\epsilon) \ketbra{\rm{S}} + \epsilon \frac{1}{3}\id = (1-\epsilon) \theta_{\rm{max}}(\rho_{\rm{S}}(0)).
+\end{equation}
+Their bound simply states that any deterministic single-copy distillation process $\rho^{\otimes n} \longrightarrow \tau$ requires an initial number of copies $n \geq \theta_{\rm{max}}(\rho) / \theta_{\rm{max}}(\tau)$.
+Therefore, the rate of our pure Strange state distillation process~\cref{eq:sudist} can only get as tight as
+\begin{equation}
+	R = 1/n = \frac{\theta_{\rm{max}}(\rho_{\rm{S}}(\epsilon))}{\theta_{\rm{max}}(\rho_{\rm{S}}(0))} \leq 1-\epsilon,
+\end{equation}
+which is less tight than mana as could be readily observed if plotted in~\cref{fig:distill_bounds}.
+
 \iffalse

### 2021-03-19 appendix.tex
added notes

@@
 
-\section{Properties of $\sigma$--fragments}
+\section{Technical properties of $\sigma$--fragments}
 \label{app:frag}
@@
 
-\section{Technical derivations for standard Lorenz curves}
+\subsection{Lorenz curve independent constraints}\label{app:lc_constraints}
+
+\begin{theorem}\label{thm:elbows}
+	Let $\rho, \tau$ be two quantum states with Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in the $\sigma$--fragment.
+
+	Let $t$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ at locations $x_1, \dots, x_t$.
+
+	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\tau}{\sigma}(x_{i})$ for all $i =1,\dots,t$.
+\end{theorem}
+\begin{proof}	
+	$\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ trivially implies $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\tau}{\sigma}(x_{i})$ for all $i = 1,\dots,n'$.
+
+	Conversely, assume that $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\tau}{\sigma}(x_{i})$ for all $i = 1,\dots,r$.
+	First, let $x_0 = 0$ and $x_{n'+1} = 1$, so that $\lc{\rho}{\sigma}(x_0) = \lc{\tau}{\sigma}(x_0) = 0$ and $\lc{\rho}{\sigma}(x_{n'+1}) = \lc{\tau}{\sigma}(x_{n'+1}) = 1$.
+	Hence, we can extend the set of elbows $E$ to $E' = E \cup \{x_0, x_{n'+1}\}$.
+
+	Pick two consecutive locations $x_{i}, x_{i+1}$ in $E'$ and consider the line segment $\ell_\tau(x)$ connecting points $(x_{i}, \lc{\tau}{\sigma}(x_{i}))$ and $(x_{i+1}, \lc{\tau}{\sigma}(x_{i+1}))$ as well as the line segment $\ell_\rho(x)$ connecting points $(x_{i}, \lc{\rho}{\sigma}(x_{i}))$ and $(x_{i+1}, \lc{\rho}{\sigma}(x_{i+1}))$.
+	This is illustrated in~\cref{fig:elbows_proof}.
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.6]{figs/elbows_proof.pdf}
+    \caption{\textbf{Illustration of~\cref{thm:elbows}}.
+    }
+    \label{fig:elbows_proof}
+\end{figure}
+
+	Due to concavity of $\lc{\rho}{\sigma}$, it is clear that for all $x \in [x_{i}, x_{i+1}]$, we have $\lc{\rho}{\sigma}(x) \geq \ell_\rho(x) \geq \ell_\tau(x) = \lc{\tau}{\sigma}(x)$.
+	This argument can be made in all intervals $[x_{i}, x_{i+1}]$ with $i=0,\dots,n'$, so the proof is complete.
+\end{proof}
+This theorem is of practical importance in calculating the necessary distillation constraints derived via majorization.
+
+In particular, it can be used in the discussion of standard Lorenz curves to set the necessary constraints,
+\begin{align}
+L\left(x_{I'(0, m'_{0}, 9^{n-n'})}\right) &\geq L\left(x_{I'(0, m'_{0}, 9^{n-n'})}\right), \nonumber\\
+L\left(x_{I'(1, m'_{1}, 9^{n-n'})}\right) &\geq L\left(x_{I'(1, m'_{1}, 9^{n-n'})}\right), \nonumber\\
+&\vdotswithin{=} \nonumber\\
+L\left(x_{I'(n', m'_{r}, 9^{n-n'})}\right) &\geq L\left(x_{I'(n', m'_{n'}, 9^{n-n'})}\right), \nonumber
+\end{align}
+where $x_{I'(0, m'_{0}, 9^{n - n'})}, x_{I'(1, m'_{1}, 9^{n - n'})}, \dots, x_{I'(n', m'_{n'}, 9^{n - n'})} \in T$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon')^{\otimes n'}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).
+
+\section{Technical derivation for Lorenz curves in unital fragment}
 \label{app:lcsu_technical}
@@
 \end{proof}
-
-\subsection{Lorenz curve independent constraints}\label{app:lc_constraints}
-
-\begin{theorem}\label{thm:elbows}
-	Let $\rho, \tau$ be two quantum states with Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in the $\sigma$--fragment.
-
-	Let $t$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ at locations $x_1, \dots, x_t$.
-
-	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\tau}{\sigma}(x_{i})$ for all $i =1,\dots,t$.
-\end{theorem}
-\begin{proof}	
-	$\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ trivially implies $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\tau}{\sigma}(x_{i})$ for all $i = 1,\dots,n'$.
-
-	Conversely, assume that $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\tau}{\sigma}(x_{i})$ for all $i = 1,\dots,r$.
-	First, let $x_0 = 0$ and $x_{n'+1} = 1$, so that $\lc{\rho}{\sigma}(x_0) = \lc{\tau}{\sigma}(x_0) = 0$ and $\lc{\rho}{\sigma}(x_{n'+1}) = \lc{\tau}{\sigma}(x_{n'+1}) = 1$.
-	Hence, we can extend the set of elbows $E$ to $E' = E \cup \{x_0, x_{n'+1}\}$.
-
-	Pick two consecutive locations $x_{i}, x_{i+1}$ in $E'$ and consider the line segment $\ell_\tau(x)$ connecting points $(x_{i}, \lc{\tau}{\sigma}(x_{i}))$ and $(x_{i+1}, \lc{\tau}{\sigma}(x_{i+1}))$ as well as the line segment $\ell_\rho(x)$ connecting points $(x_{i}, \lc{\rho}{\sigma}(x_{i}))$ and $(x_{i+1}, \lc{\rho}{\sigma}(x_{i+1}))$.
-	This is illustrated in~\cref{fig:elbows_proof}.
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.6]{figs/elbows_proof.pdf}
-    \caption{\textbf{Illustration of~\cref{thm:elbows}}.
-    }
-    \label{fig:elbows_proof}
-\end{figure}
-
-	Due to concavity of $\lc{\rho}{\sigma}$, it is clear that for all $x \in [x_{i}, x_{i+1}]$, we have $\lc{\rho}{\sigma}(x) \geq \ell_\rho(x) \geq \ell_\tau(x) = \lc{\tau}{\sigma}(x)$.
-	This argument can be made in all intervals $[x_{i}, x_{i+1}]$ with $i=0,\dots,n'$, so the proof is complete.
-\end{proof}
-This theorem is of practical importance in calculating the necessary distillation constraints derived via majorization.
-
-In particular, it can be used in the discussion of standard Lorenz curves to set the necessary constraints,
-\begin{align}
-L\left(x_{I'(0, m'_{0}, 9^{n-n'})}\right) &\geq L\left(x_{I'(0, m'_{0}, 9^{n-n'})}\right), \nonumber\\
-L\left(x_{I'(1, m'_{1}, 9^{n-n'})}\right) &\geq L\left(x_{I'(1, m'_{1}, 9^{n-n'})}\right), \nonumber\\
-&\vdotswithin{=} \nonumber\\
-L\left(x_{I'(n', m'_{r}, 9^{n-n'})}\right) &\geq L\left(x_{I'(n', m'_{n'}, 9^{n-n'})}\right), \nonumber
-\end{align}
-where $x_{I'(0, m'_{0}, 9^{n - n'})}, x_{I'(1, m'_{1}, 9^{n - n'})}, \dots, x_{I'(n', m'_{n'}, 9^{n - n'})} \in T$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon')^{\otimes n'}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).
-
-\section{Theory on bounding the core functions}
-The core functions are $\Phi_{\pm}$ which is an even power cumulative function. 
-We can rewrite it as
-\begin{equation}
-\Phi_{\pm}(m; n, a) = \frac{1}{2}( \Phi(m; n, a) \pm (1+a)^{-n} S(m; n, a) ),
-\end{equation}
-where we have substituted $a = p/(1-p)$. 
-$\Phi$ is the standard cumulative function 
-\begin{equation}
-	\Phi(m; n, a) = (1+a)^{-n} \sum_{k=0}^m \binom{n}{k} a^k,
-\end{equation}
-and the remainder term is
-\begin{equation}
-S(m; n, a) \coloneqq \sum_{k=0}^m \binom{n}{k} (-a)^k.
-\end{equation}
-We have good asymptotic bounds on the behaviour of $\Phi$~\cite{cit:ash},
-\begin{lemma}\label{lem:phil_bounds}
-	Given fixed $n>0$ and $p$, $\Phi_\ell$ satisfies the following bounds:
-	\begin{align*}
-		\begin{split}
-		&\text{1. } \Phi(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ents},\ m\in [1,n-1] \\
-		&\text{2. } \Phi(m; n, p) \leq 2^{-n\ents},\ m\in [0,np] \\
-		&\text{3. } \Phi(m; n, p) \leq 1 - \left[ 8(m+1)\left(1-\frac{m+1}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m+1}{n}}{p}}, \\
-		&\hspace{14pt} m\in [0,n-2]
-		\end{split}
-		\\
-		&\text{4. } \Phi(m; n, p) \geq 1 - 2^{-n\ent{\frac{m+1}{n}}{p}},\ m\in [np+1,n-2]
-	\end{align*}
-\end{lemma}
-
-We would like some theory that estimates the value of $S(m; n, a)$ for different parameter regimes. 
-We can consider the function $f(x) = (1+x)^n$ and note that $S(m; n, a)$ is the $m$'th partial sum of this expansion at the point $x=-a$.
-
-The truncated Maclaurin series of a general function $f(x)$ is
-\begin{equation}
-	f(x) = f(0) + x f'(0) + \dots \frac{x^m}{m!}f^{(m)}(0) + R_m(x)
-\end{equation}
-with a remainder term
-\begin{align}
-	R_m (x)&= \int_{0}^x dt f^{(m+1)}(t) \frac{(x-t)^r}{r!} \\
-	&= \frac{x^{m+1}}{(m+1)!} f^{(m+1)}(x_*),
-\end{align}
-where in the second expression, $x_*$ is an implicit point that lies between $0$ and $x$ that comes from the Mean Value Theorem.
-
-Applying this to the function $f(x) = (1+x)^n$ gives
-\begin{equation}
-	(1+x)^n = \sum_{k=0}^m \binom{n}{k} x^k + R_m.
-\end{equation}
-Evaluating at $x=-a$ gives
-\begin{equation}
-	S(m; n, a) = (1-a)^n - R_m(-a),
-\end{equation}
-where the key remainder term is given by
-\begin{align}
-	R_m(-a) &= \int_0^{-a} dt f^{(m+1)}(t) \frac{(-a-t)^m}{m!} \\
-&= \frac{(-a)^{m+1}}{(m+1)!} f^{(m+1)}(x_*).
-\end{align}
-We can also compute the derivative $f^{(m+1)}(x)$ explicitly,
-\begin{equation}
-	f^{(m+1)}(x) = (m+1)!\binom{n}{m+1}(1+x)^{n-m-1}.
-\end{equation}
-Therefore, we have that
-\begin{align}
-	R_m(-a) &= (-1)^{m+1}(m+1)\binom{n}{m+1}\int_{-a}^0 dt (1+t)^{n-m-1}(a+t)^m \\
-&= \binom{n}{m+1}(-a)^{m+1}(1+x_*)^{n-m-1},
-\end{align}
-where in the latter expression $x_* \in [-a,0]$. 
-Note that the first integral expression can be estimated via the Cauchy-Schwarz or the Hoelder inequality. 
-Therefore, we can either work with an explicit form with an unknown (but bounded) parameter $x_*$, or we can use the integral form and provide concrete estimates on it value.
-
-A very simple estimate, based on $x_*$ lying in the interval $[-a,0]$ gives
-\begin{equation}
-\binom{n}{m+1}(-a)^{m+1}(1-a)^{n-m-1} \leq R_m(-a) \le  \binom{n}{m+1}(-a)^{m+1}.
-\end{equation}
-
-This in turn leads to the following bounds on $\Phi_+(a,r,n)$:
-\begin{align}
-\hspace{-2cm}2\Phi_+(a,r,n) &\le \Phi(a,r,n)+ (1-a)^n - \frac{(-a)^{r+1}}{r!} \binom{n}{r+1} (1-a)^{n-r-1} \nonumber \\
-2\Phi_+(a,r,n) & \ge\Phi(a,r,n)+ (1-a)^n - \frac{(-a)^{r+1}}{r!} \binom{n}{r+1} .
-\end{align}
-Details need checking to see if I dropped any constants/signs. Are these bounds good in practice? Asymptotically?

### 2021-03-19 magic_paper.tex
added notes

@@
 Theories of magic states attempt to quantify this computational element via monotones and determine how these states may be efficiently transformed into useful forms.
-Here we introduce the concept of `fragments', which generalise the concept of magic monotones and has a natural thermodynamic structure based on majorization.
-From this perspective magic can be viewed as a form of free energy within each fragment and is constrained by relative majorization relations but now on quasi-probability distributions.
+Here we introduce the concept of `fragments', which generalise the concept of magic monotones and has a natural thermodynamic structure based on majorisation.
+From this perspective magic can be viewed as a form of free energy within each fragment and is constrained by relative majorisation relations but now on quasi-probability distributions.
 Notably this approach allows us to incorporate actual physical constraints, for example noise models with particular bias or temperature-dependent features, and study how these constrain general magic distillation protocols.
@@
     \item Magic~\cite{cit:veitch, cit:veitch2, cit:wang, cit:wang2, cit:howard, cit:campbell, cit:gross3, cit:gross4}
-    \item Bringing in majorization~\cite{cit:cwiklinski, cit:lostaglio2, cit:lostaglio, cit:gour, cit:janzing, cit:brandao2, cit:gour2, cit:marshall, cit:nielsen}
+    \item Bringing in majorisation~\cite{cit:cwiklinski, cit:lostaglio2, cit:lostaglio, cit:gour, cit:janzing, cit:brandao2, cit:gour2, cit:marshall, cit:nielsen}
 \end{enumerate}
@@
 
-The stabilizer theory of magic comprises of the so-called ``stabilizer'' states ($\stab$) and operations ($\so$), while non-stabilizer (resource) states are called magic.
-The stabilizer operations can be expressed in terms of a Stinespring dilation as 
+The stabiliser theory of magic comprises of the so-called ``stabiliser'' states ($\stab$) and operations ($\so$), while non-stabiliser (resource) states are called magic.
+The stabiliser operations can be expressed in terms of a Stinespring dilation as 
 \begin{equation}
@@
 \end{equation} 
-for an ancilla stabilizer state $\sigma_E$. 
-The motivation of the theory stems from the fact that stabilizer operations are experimentally straightforward to implement and they can be used to detect and correct errors on the stabilizer states due to their construction \nick{CITE}.
-The Gottesman-Knill theorem however indicates that stabilizer operations need to be supplemented with magic states in order to achieve universality, justifying the term ``magic''.
-
-Generalisations of the stabilizer theory appear in the literature intending to include broader classes of operations \nick{CITE}.
-The class of stabilizer preserving operations ($\spo$) is defined as the set of $\cptp$ maps that send stabilizer states into stabilizer states~\cite{cit:ahmadi}.
-An important subclass of $\spo$ is the set of completely stabilizer preserving operations ($\cspo$), which intuitively cannot induce ``non-stabilizerness'' even when applied to only part of a quantum state, i.e.
+for an ancilla stabiliser state $\sigma_E$. 
+The motivation of the theory stems from the fact that stabiliser operations are experimentally straightforward to implement and they can be used to detect and correct errors on the stabiliser states due to their construction \nick{CITE}.
+The Gottesman-Knill theorem however indicates that stabiliser operations need to be supplemented with magic states in order to achieve universality, justifying the term ``magic''.
+
+Generalisations of the stabiliser theory appear in the literature intending to include broader classes of operations \nick{CITE}.
+The class of stabiliser preserving operations ($\spo$) is defined as the set of $\cptp$ maps that send stabiliser states into stabiliser states~\cite{cit:ahmadi}.
+An important subclass of $\spo$ is the set of completely stabiliser preserving operations ($\cspo$), which intuitively cannot induce ``non-stabiliserness'' even when applied to only part of a quantum state, i.e.
 operations $\E$ such that $(\id_d \otimes \E ) \sigma \in \stab$ for all positive dimensions $d$ whenever $\sigma \in \stab$.
 
-Even though non-stabilizerness is a necessary resource for universality, it has been proven insufficient for magic state distillation~\cite{cit:bravyi, cit:campbell}.
+Even though non-stabiliserness is a necessary resource for universality, it has been proven insufficient for magic state distillation~\cite{cit:bravyi, cit:campbell}.
 In fact, all states with non-negative Wigner distributions have been proven to be efficiently classically simulable in~\cite{cit:mari}, a result that serves as a generalization of the Gottesman-Knill theorem.
 The Wigner distribution of a state in odd prime dimensions is discussed rigorously in~\cref{sec:wigner} and arises as the unique quasi-probability representation of quantum theory that identifies non-contextuality exactly with the states that are efficiently classically simulable~\cite{cit:howard2, cit:veitch2}.
-In this framework, the stabilizer states are the only pure states represented with non-negative distributions~\cite{cit:gross3}. 
-However, there exist mixed states with non-negative Wigner distributions that are not mixtures of stabilizer states~\cite{cit:gross}.
-Therefore, stabilizer-preserving theories have been extended to a theory that preserves state ``Wigner positivity''~\cite{cit:wang}, formally defined in~\cref{sec:wigner} for odd prime dimensions.
+In this framework, the stabiliser states are the only pure states represented with non-negative distributions~\cite{cit:gross3}. 
+However, there exist mixed states with non-negative Wigner distributions that are not mixtures of stabiliser states~\cite{cit:gross}.
+Therefore, stabiliser-preserving theories have been extended to a theory that preserves state ``Wigner positivity''~\cite{cit:wang}, formally defined in~\cref{sec:wigner} for odd prime dimensions.
 Informally, it can be considered as the maximal theory of magic $\Rmax = (\Fmax, \Omax)$, where free states have non-negative Wigner distributions and free operations completely preserve this property.\\
@@
 \begin{enumerate}
-\item Perhaps a nice lead-in question: ``What happens if we view stabilizer states as thermodynamic equilibrium states and magic as a form of free energy?''
+\item Perhaps a nice lead-in question: ``What happens if we view stabiliser states as thermodynamic equilibrium states and magic as a form of free energy?''
 \item We have found a scenario in which it is impossible to describe a thermodynamic structure using any entropic approach!
@@
 The phase factor $\tau \coloneqq -\omega^{1/2}$ ensures unitarity.
-For a composite system with product dimension $d = d_1 \dots d_n$ and Hilbert space, $\cal{H}_d = \cal{H}_{d_1}] \otimes \dots \otimes \cal{H}_{d_n}]$, the displacement operators are defined as
+For a composite system with product dimension $d = d_1 \dots d_n$ and Hilbert space, $\cal{H}_d = \cal{H}_{d_1} \otimes \dots \otimes \cal{H}_{d_n}$, the displacement operators are defined as
 \begin{equation}\label{eq:composited}
@@
 The Clifford operations $ \cal{C}_d^n $ are then defined as the set of unitaries that normalise the Heisenberg-Weyl group.
-We may define the pure stabilizer states as those states obtained by acting on $|0\>$ with Clifford unitaries.
-Finally, we define $\stab$ as the convex hull of all pure stabilizer states, namely all probabilistic mixtures of states of the form $U|0\>\<0|U^\dagger$ where $U$ is some Clifford unitary.
-The stabilizer theory forms a magic resource theory $\R = (\stab, \so)$
-and the free operations are stabilizer operations ($\so$), defined as compositions of preparation of computational basis states, Clifford unitaries, measurement in the computational basis, and the ability to discard subsystems.
+We may define the pure stabiliser states as those states obtained by acting on $|0\>$ with Clifford unitaries.
+Finally, we define $\stab$ as the convex hull of all pure stabiliser states, namely all probabilistic mixtures of states of the form $U|0\>\<0|U^\dagger$ where $U$ is some Clifford unitary.
+The stabiliser theory forms a magic resource theory $\R = (\stab, \so)$
+and the free operations are stabiliser operations ($\so$), defined as compositions of preparation of computational basis states, Clifford unitaries, measurement in the computational basis, and the ability to discard subsystems.
 
@@
 		-\id & 0 \\ %-\id_n & \mathbbm{O}_n \\
-	\end{pmatrix} \bmx.
-\end{equation}
+	\end{pmatrix} \bmx,
+\end{equation}
+where $0, \id$ denote the $n\times n$ zero and identity matrices.
 
@@
     \caption{\textbf{Qutrit Wigner distributions of varying magic.} 
-    \subref{fig:maxmix} Maximally mixed state $\frac{1}{3}\id$; \subref{fig:zero} Stabilizer zero state $\ketbra{0}{0}$; \subref{fig:bound} A non-stabilizer Wigner-positive state; \subref{fig:strange} Magic Strange state $\ket{{\rm{S}}} = \frac{1}{\sqrt{2}}(\ket{1} - \ket{2})$, coined in~\cite{cit:veitch2}.
+    \subref{fig:maxmix} Maximally mixed state $\frac{1}{3}\id$; \subref{fig:zero} Stabilizer zero state $\ketbra{0}{0}$; \subref{fig:bound} A non-stabiliser Wigner-positive state; \subref{fig:strange} Magic Strange state $\ket{{\rm{S}}} = \frac{1}{\sqrt{2}}(\ket{1} - \ket{2})$, coined in~\cite{cit:veitch2}.
     }%
@@
 \end{equation}
-Mana is an additive\footnote{It satisfies the condition $\mana{\rho_1 \otimes \rho_2} = \mana{\rho_1} + \mana{\rho_2}$ which is practical in distillation settings.} magic monotone, so it provides an analytical necessary condition for many-copy magic state interconvertibility.
-
-\subsection{Majorization}
+Mana is an additive\footnote{It satisfies the condition $\mana{\rho_1 \otimes \rho_2} = \mana{\rho_1} + \mana{\rho_2}$ which is practical in distillation settings.} magic monotone, so it provides an analytical, necessary condition for many-copy magic state interconvertibility.
+
+\subsection{Majorisation}
 \label{sec:major}
 
-Majorization is a collection of powerful tools that has recently found many applications in quantum information theory \nick{CITE}.
+Majorisation is a collection of powerful tools that has recently found many applications in quantum information theory \nick{CITE}.
 It describes the \nick{disorder / non-uniformity} of distributions that undergo stochastic transformations.
 
-To formally state majorization results, we first denote by $\stoch$ the set of $(d \times d)$ stochastic matrices that preserve the probability vector $\bmd$.
+To formally state majorisation results, we first denote by $\stoch$ the set of $(d \times d)$ stochastic matrices that preserve the probability vector $\bmd$.
 Specifically, for any $S \in \stoch$, all matrix elements are non-negative, all rows sum to $1$ and $S\bmd = \bmd$.
@@
 
-Majorization describes quantum thermodynamics exactly in the absence of quantum coherence.
-The use of majorization in this setting provides vital intuition for our purposes.
+Majorisation describes quantum thermodynamics exactly in the absence of quantum coherence.
+The use of majorisation in this setting provides vital intuition for our purposes.
 At any given temperature $\beta^{-1}$, the thermal state $\gamma_\beta$ is thermodynamically the most disordered state. 
@@
 
-Based on this setting, we define majorization as follows.
-\begin{definition}[\textbf{$\boldsymbol\bmd$-majorization}]\label{def:dmajor}
-    Given $\bmx, \bmy, \bmd \in \reals^d$, such that the components of $\bmd$ are positive, $\bmy$ is said to $\bmd$-majorize $\bmx$, iff there exists a matrix $S \in \stoch$ such that $\bmx = S\bmy$.
+Based on this setting, we define majorisation as follows.
+\begin{definition}[\textbf{$\boldsymbol\bmd$-majorisation}]\label{def:dmajor}
+    Given $\bmx, \bmy, \bmd \in \reals^d$, such that the components of $\bmd$ are positive, $\bmy$ is said to $\bmd$-majorise $\bmx$, iff there exists a matrix $S \in \stoch$ such that $\bmx = S\bmy$.
 \end{definition}
 We denote this pre-order by $\bmx \prec_{\bmd} \bmy$.
-If $\bmd = \frac{1}{d}\bm{1}$, the $d$-dimensional uniform distribution, then $\stoch$ is the set of doubly stochastic matrices and we retrieve the familiar notion of majorization from entanglement theory.
+If $\bmd = \frac{1}{d}\bm{1}$, the $d$-dimensional uniform distribution, then $\stoch$ is the set of doubly stochastic matrices and we retrieve the familiar notion of majorisation from entanglement theory.
 \nick{CITE}
 
-The pre-order imposed by $\bmd$-majorization admits a numerically efficient reformulation in terms of Lorenz curves.
+The pre-order imposed by $\bmd$-majorisation admits a numerically efficient reformulation in terms of Lorenz curves.
 Let the vector $\bmu^\downarrow$ denote the vector $\bmu \in \reals^d$ with its components arranged in non-increasing order.
@@
 
-A vector $\bmy$ is said to \emph{$\bmd$--majorize} another vector $\bmx$ if and only if the Lorenz curve $\lc{\bmy}{\bmd}$ lies above Lorenz curve $\lc{\bmx}{\bmd}$, thus reducing $\bmd$--majorization into a finite set of inequalities.
+A vector $\bmy$ is said to \emph{$\bmd$--majorise} another vector $\bmx$ if and only if the Lorenz curve $\lc{\bmy}{\bmd}$ lies above Lorenz curve $\lc{\bmx}{\bmd}$, thus reducing $\bmd$--majorisation into a finite set of inequalities.
 \begin{theorem}\label{thm:dmajor}
@@
     Each $\O_\sigma$ is extensible to a set of stochastic maps outside the $\cptp$ operations.
-    Within each $\sigma$--fragment $\bmd$-majorization can be used allowing for an intricate, but tractable approach towards the study of magic state interconversion.
+    Within each $\sigma$--fragment $\bmd$-majorisation can be used allowing for an intricate, but tractable approach towards the study of magic state interconversion.
     }
@@
 This theory of magic is thus covered by $\sigma$--fragments exactly and every other magic theory is contained within this cover.
-In particular, the stabilizer operations $\so$ are contained within $\Omax$.
+In particular, the stabiliser operations $\so$ are contained within $\Omax$.
 
@@
 A noise channel consisting only of such dephasing operations can be fully analysed in the $\sigma$--fragments for the pure computational basis states $\sigma$.
-\nick{Have proven in appendix that we need to consider \emph{only} the pure stabilizer fragments - not mixed ones}
-
-The subdivision of magic theories into $\sigma$--fragments is also powerful because the pre-order $\prec_{\R_\sigma}$ of every $\sigma$--fragment is described by well-behaved majorization tools, as we establish in the rest of this section.
-
-\subsection{Majorization of quasi-probabilities in $\sigma$--fragments}\label{sec:major_frag}
+\nick{Have proven in appendix that we need to consider \emph{only} the pure stabiliser fragments - not mixed ones}
+
+The subdivision of magic theories into $\sigma$--fragments is also powerful because the pre-order $\prec_{\R_\sigma}$ of every $\sigma$--fragment is described by well-behaved majorisation tools, as we establish in the rest of this section.
+
+\subsection{Majorisation of quasi-probabilities in $\sigma$--fragments}\label{sec:major_frag}
 
 We can approach any magic theory through a thermodynamic lens, and in doing so we are provided with valuable insights on the structure of the theory. 
-Firstly, any free state, for example a stabilizer state, can be viewed as a thermal state $\gamma_\beta$.
+Firstly, any free state, for example a stabiliser state, can be viewed as a thermal state $\gamma_\beta$.
 Without loss of generality we can always write a quantum state $\sigma$ as a thermal state, $\sigma = \gamma_\beta \coloneqq \frac{1}{\Z_\beta} e^{-\beta H}$ for some $\beta \geq 0$ and Hamiltonian $H$ (either effective or actual)\footnote{Technicalities arise for the case where $\sigma$ is not full rank, but this can be still described via $ \beta \rightarrow 0$ limiting process.}.
@@
 
-It is then apparent that the pre-order $\prec_{\R_\sigma}$ between the operations in the $\sigma$--fragment follows the rules of $\bmd$-majorization as outlined in~\cref{sec:major}.
-In particular, the pre-order $\prec_{\R_\sigma}$ of the $\sigma$--fragment $\R_\sigma = (\F, \O_\sigma)$ between $d$-dimensional states corresponds to the majorization pre-order $\prec_{\W{\sigma}}$ between their $d^2$-dimensional Wigner distributions.
+It is then apparent that the pre-order $\prec_{\R_\sigma}$ between the operations in the $\sigma$--fragment follows the rules of $\bmd$-majorisation as outlined in~\cref{sec:major}.
+In particular, the pre-order $\prec_{\R_\sigma}$ of the $\sigma$--fragment $\R_\sigma = (\F, \O_\sigma)$ between $d$-dimensional states corresponds to the majorisation pre-order $\prec_{\W{\sigma}}$ between their $d^2$-dimensional Wigner distributions.
 For simplicity we shall merge the notation into $\prec_\sigma$, as there is little risk of confusion.
@@
 Furthermore, we restrict our analysis to $\sigma$--fragments, where $\sigma$ is full-rank.
-This is justified as majorization is continuous between fragments, in the sense that the pre-orders $\prec_\sigma$ and $\prec_{\sigma'}$ are equivalent for states $\sigma$ and $\sigma'$ which are $\epsilon$-close.
+This is justified as majorisation is continuous between fragments, in the sense that the pre-orders $\prec_\sigma$ and $\prec_{\sigma'}$ are equivalent for states $\sigma$ and $\sigma'$ which are $\epsilon$-close.
 \nick{CHECK}
-Therefore, majorization analysis is robust under imperfections in the experimental implementation of quantum operations.
-
-In particular, any $\sigma$--fragment, with $\sigma$ not full-rank, can be approximated by the $\sigma'$--fragment defined as a mixture of $\sigma$ with depolarising noise, $\sigma' = (1-\epsilon)\sigma + \epsilon\frac{1}{d}\id$, for some infinitesimal $\epsilon > 0$, so that $\sigma'$ is full-rank and arbitrarily close to $\sigma$.
-Important examples include pure stabilzer states which are rank-$1$ states e.g. the zero state depicted in~\cref{fig:zero}. 
-Operations in such fragments include important stabilizer operations like the replacement channel, $\E(\rho) = \sigma$ for all states $\rho$.
+Therefore, majorisation analysis is robust under imperfections in the experimental implementation of quantum operations.
+
+In particular, we can always use common noise effects to approximate any $\sigma$--fragment where $\sigma$ is not full-rank by the $\sigma'$--fragment where $\sigma'$ is a noisy approximation of $\sigma$.
+For example, inducing depolarising noise, we can write $\sigma' = (1-\epsilon)\sigma + \epsilon\frac{1}{d}\id$, for some infinitesimal $\epsilon > 0$, so that $\sigma'$ is full-rank and arbitrarily close to $\sigma$.
+Important examples of such $\sigma$--fragments include pure stabiliser states which are rank-$1$, e.g. the zero state depicted in~\cref{fig:zero}. 
+Operations in such fragments include important stabiliser operations like the replacement channel, $\E(\rho) = \sigma$ for all states $\rho$.
 
@@
 Since $\sigma$ is full-rank and free, its Wigner distribution is strictly positive in all components, so it directly follows from~\cref{def:dmajor} that $\W{\tau} \prec_{\sigma} \W{\rho}$.
-
-\nick{The theorem statement and proof currently assume that $\sigma$ is full-rank}
 \end{proof}
@@
 The result of~\cref{thm:sigmamajor} can be understood as an extension of the idea of a magic monotone, where we replace $\M(\tau) \leq \M(\rho)$ with $\W{\tau} \prec_\sigma \W{\rho}$. 
-The physical difference between the two expressions is that the majorization ordering occurs in a specific $\sigma$--fragment.
-Therefore, majorization constraints can be used to place upper bounds on magic state distillation in a way that allows one to incorporate the physics of the allowed operations -- specifically, it enables us to bound how much magic can be distilled via quantum operations that, for example, preserve the equilibrium state of the system, or via operations that are symmetric about the $Z$-axis of the Bloch sphere.
-We discuss distillation upper bounds in~\nick{REF}
+The physical difference between the two expressions is that the majorisation ordering occurs in a specific $\sigma$--fragment.
+Therefore, majorisation constraints can be used to place upper bounds on magic state distillation in a way that allows one to incorporate the physics of the allowed operations -- specifically, it enables us to bound how much magic can be distilled via quantum operations that, for example, preserve the equilibrium state of the system, or via operations that are symmetric about the $Z$-axis of the Bloch sphere.
+We discuss distillation upper bounds in detail in~\cref{sec:unital,sec:stab}
 
 This approach can also provide \emph{lower bounds} on distillation, however now more structure about the specific free operations must be included. 
-We discuss distillation lower bounds in~\nick{REF}
-
-\nick{Mention relative majorization as a possibility}
+We briefly discuss distillation lower bounds in~\nick{REF}.
+
+\nick{Mention relative majorisation as a possibility}
 
@@
 It is straightforward to construct Lorenz curves for Wigner distributions in any $\sigma$--fragment.
-As we have seen in~\cref{thm:sigmamajor}, for any full-rank free state $\sigma$ we have that $\W{\sigma}$ is a strictly positive full-rank probability distribution, and so one can define a corresponding notion of $d$--majorization on \emph{quasi}--distributions.
+As we have seen in~\cref{thm:sigmamajor}, for any full-rank free state $\sigma$ we have that $\W{\sigma}$ is a strictly positive full-rank probability distribution, and so one can define a corresponding notion of $d$--majorisation on \emph{quasi}--distributions.
 We write $\lc{\rho}{\sigma}(x)$ for the Lorenz curve of $\W{\rho}$ with respect to $\W{\sigma}$.
-The vector of ratios $\widetilde{\bmw}(\rho|\sigma)$ used to construct the curve is defined as
+The vector of ratios $\widetilde{\bmw}(\rho|\sigma)$ used to construct the curve is
 \begin{equation}
@@
 \end{equation}
-is called the Gibbs-rescaled distribution of $\rho$ with respect to $\sigma$.
+and is called the \emph{Gibbs-rescaled} distribution of $\rho$ with respect to $\sigma$.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Mana as a feature of majorization}
-
-\nick{Should this be a section on its own or a subsection of the previous section?}
-
-We now show that the magic monotone of mana, and equivalently the sum-negativity of a quantum state, can be viewed as majorization-based, and independent of the particular $\sigma$--fragment one works in.
-In fact, our current setting makes it apparent that mana provides a weaker condition than majorization for all magic state interconversions.
+We can now show that the magic monotone of mana, and equivalently the sum-negativity of a quantum state, can be viewed as a feature of majorisation, and independent of the particular $\sigma$--fragment one works in.
+In fact, our current setting makes it apparent that mana provides a weaker condition than majorisation for all magic state interconversions.
 
@@
 \begin{theorem}\label{thm:bounds}
-    Given a magic state conversion $\rho \longrightarrow \tau$, the majorization condition is stronger than the mana condition in every $\sigma$--fragment.
+    Given a magic state conversion $\rho \longrightarrow \tau$, the majorisation condition is stronger than the mana condition in every $\sigma$--fragment.
 \end{theorem}
@@
     \end{equation}
-    Therefore, the majorization bound
+    Therefore, the majorisation bound
     \begin{equation}
@@
     \end{equation}
-    implies the order $\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} \geq \max_{x\in[0,1]}{\lc{\tau}{\sigma}(x)}$, equivalent to the mana condition $\mana{\rho} \geq \mana{\tau}$.
+    implies the order $\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} \geq \max_{x\in[0,1]}{\lc{\tau}{\sigma}(x)}$, hence the mana condition $\mana{\rho} \geq \mana{\tau}$.
 \end{proof}
 
-In the sections~\cref{sec:unital,sec:stab}, we study majorization constraints on magic distillation arising in different fragments. 
+In sections~\cref{sec:unital,sec:stab}, we study majorisation constraints on magic distillation arising in different fragments. 
 For this reason, we define the $n$-copy, $\epsilon$-noisy Strange state,
@@
 \end{equation}
-in $\O_\sigma$, where $\ket{\rm{S}}$ is coined in~\cref{fig:strange} and we induce uniform depolarising noise.
-
-For $\epsilon=0$, this state is a qutrit of maximal sum-negativity / mana~\cite{cit:veitch2} and therefore acts as the ideal distiallation target, analogous to a Bell state in bipartite entangelement theory.
+in $\O_\sigma$, where the pure magic state $\ket{\rm{S}}$ is induced with depolarising noise. 
+Its Wigner distribution is visualised in~\cref{fig:strange}.
+
+At $\epsilon=0$, the Strange state is a qutrit magic state of maximal sum-negativity / mana~\cite{cit:veitch2} and therefore acts as an ideal distillation target, analogous to a Bell state in bipartite entanglement theory.
 The Strange state is exceptionally symmetric under Clifford transformations and as a result there exists a \emph{twirling} protocol, discussed in detail in~\cite{cit:prakash,cit:prakash2}, allowing for the conversion of any noisy magic state to the form of~\cref{eq:noisysn} via Cliffords.
 
-In~\cref{fig:lcs}, we illustrate the Lorenz curves $\lc{\rho_{\rm{S}}}{\sigma}$\footnote{We drop parameters $\epsilon$ and $n$ for clarity} of pure and noisy $n$-copy Strange states for $n$ up to $4$ in different $\sigma$--fragments.
-As shown in~\cref{lem:lcmax}, the curve peaks equal $1 + \sn{\rho_{\rm{S}}(\epsilon)^{\otimes n}}$ independently of the $\sigma$--fragment.
-\begin{figure}%
+In~\cref{fig:lcs}, we illustrate the Lorenz curve $\lc{\rho_{\rm{S}}}{\sigma}$\footnote{Hereinafter, we may drop parameters $\epsilon$ and $n$ for clarity} of pure and noisy $n$-copy Strange states in some thermal $\sigma$--fragment.
+Due to~\cref{lem:lcmax}, it is clear that the curves peak at $1 + \sn{\rho_{\rm{S}}(\epsilon)^{\otimes n}}$.
+\begin{figure}
     \centering
-    \subfigure[][]{%
-    \label{fig:lcs_maxmix}%
-    \includegraphics[height=3cm]{figs/lcs_maxmix.pdf}
-    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
-    }\hspace{1pt}%
-    \subfigure[][]{%
-    \label{fig:lcs_thermal}%
-    \includegraphics[height=3cm]{figs/lcs_thermal.pdf}
-    %\caption{Zero state $\ketbra{0}{0}$}%
-    }\\
-    \subfigure[][]{%
-    \label{fig:lcs_zero}%
-    \includegraphics[height=3cm]{figs/lcs_zero.pdf}
-    %\caption{Bound state}%
-    }\hspace{1pt}%
-    \subfigure[][]{%
-    \label{fig:lcs_one}%
-    \includegraphics[height=3cm]{figs/lcs_one.pdf}
-    %\caption{Strange state $\ketbra{S}{S}$}%
+    \includegraphics[height=5cm]{figs/lc_strange.pdf}
+    \caption{\textbf{Strange state Lorenz curves.} Lorenz curves of $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ for $n=1,2,3,4$ in the $\sigma$--fragment where $\sigma = e^{-\beta H}/\Z_{\beta}$, with Hamiltonian spectrum $(0,1,2)$ over the computational basis and $\beta = 0.5$.
+    Solid lines represent pure Strange states ($\epsilon = 0$); dashed lines represent noisy Strange states ($\epsilon = 0.1$).
     }
-    \caption{\textbf{Lorenz curves of $n$-copy Strange states.} Lorenz curves of $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ for $n=1,2,3,4$.
-    Solid lines represent pure Strange states ($\epsilon = 0$); dashed lines represent noisy Strange states ($\epsilon = 0.1$).
-    \subref{fig:lcs_maxmix} Unital fragment; \subref{fig:lcs_thermal} Thermal fragment with $H = (0,1,2)$ and $\beta = 0.5$; \subref{fig:lcs_zero} Fragment $\O_{\ketbra{0}{0}}$; \subref{fig:lcs_one} Fragment $\O_{\ketbra{1}{1}}$.
-    \nick{change / move / remove ?}
-    }%
     \label{fig:lcs}
@@
 
-\null\newpage
-\null\newpage
-
 \section{Magic in the unital fragment}
@@
 Depending on the symmetries of such operations, a Clifford sequence may belong in other $\sigma$--fragments as well.
-In such a case, the majorization condition~(\ref{eq:majbound}) needs to be checked in the $\sigma$--fragments that reflect all symmetries of the operation sequence.
+In such a case, the majorisation condition~(\ref{eq:majbound}) needs to be checked in the $\sigma$--fragments that reflect all symmetries of the operation sequence.
 
@@
 
-\subsection{Distillation rate bounds in the unital fragment}\label{sec:lcsu}
-
-We consider the problem of purifying $n$ copies of a noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ as given in~\cref{eq:noisysn} into a smaller number of copies $n'$ of a less noisy strange state $\rho_{\rm{S}}(\epsilon')^{\otimes n'}$, with $\epsilon' < \epsilon$ and $n' \leq n$,
+We now consider the task of purifying $n$ copies of a noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ as given in~\cref{eq:noisysn} into a smaller number of copies $n'$ of a less noisy strange state $\rho_{\rm{S}}(\epsilon')^{\otimes n'}$, with $\epsilon' < \epsilon$ and $n' \leq n$,
 \begin{equation}\label{eq:sudist}
@@
 The Lorenz curve $\lc{\rho_{\rm{S}}}{\id/3}$, for some general noise parameter $\epsilon$ and number of copies $n$, is defined at $9^n$ points between $0$ and $1$.
-The exact expressions for the coordinates of these points can take $8$ different forms, depending on whether the noise level $\epsilon$ is greater or less than $\frac{3}{7}$, the parity of the number of copies $n$ is even or odd and the location relative to the curve peak is on the left hand side (LHS -- including the curve peak) or right hand side (RHS) of the curve peak.
-The full details for the Lorenz curve construction are provided in~\cref{app:lcsu_technical}.
+The exact expressions for the coordinates of these points can take $8$ different forms, depending on whether the noise level \nick{noise level / error rate} $\epsilon$ is greater or less than $\frac{3}{7}$, the parity of the number of copies $n$ is even or odd and the location relative to the curve peak is on the left hand side (LHS -- including the curve peak) or right hand side (RHS) of the curve peak.
+The full details for the construction of all Lorenz curve forms are provided in~\cref{app:lcsu_technical}.
 
@@
 \begin{equation}
-R \leq \frac{\ln (3-4 \epsilon)}{\ln 3},
+R \leq 1 + \frac{\ln (1 - \frac{4}{3} \epsilon)}{\ln 3},
 \end{equation}
@@
 \begin{equation}
-	R_{\rm{mana}} \leq \frac{\ln \left(\frac{5}{3} - \frac{8}{9}\epsilon \right)}{\ln \frac{5}{3}},
-\end{equation}
-a threshold which is looser than the one provided by majorization for all $\epsilon > 0$ as illustrated in~\cref{fig:distill_bounds}.
+	R_{\rm{mana}} \leq 1 + \frac{\ln \left(1 - \frac{8}{15}\epsilon \right)}{\ln \frac{5}{3}},
+\end{equation}
+a threshold which is looser than the one provided by majorisation for all $\epsilon > 0$ as illustrated in~\cref{fig:distill_bounds}.
 For example, for $\epsilon = 0.4$ we obtain $R\le 0.31 $ while the mana bound gives $R_{\rm{mana}} \le 0.53$.
-\begin{figure}[h]
+\begin{figure}[t]
     \centering
     \includegraphics[scale=0.5]{figs/distill_bounds.pdf}
-    \caption{\textbf{Distillation rate in unital fragment.} Distillation rates obtained by mana and majorization are plotted for $\epsilon' = 0$, up to noise levels $\epsilon_{\rm{max}} = \frac{3}{7}$.
-    Majorization consistently provides stricter rates as proven in~\cref{thm:bounds}.
+    \caption{\textbf{Distillation rate in unital fragment.} Distillation rates obtained by mana and majorisation are plotted for $\epsilon' = 0$, up to noise levels $\epsilon_{\rm{max}} = \frac{3}{7}$.
+    Majorisation consistently provides stricter rates as proven in~\cref{thm:bounds}. \nick{add thauma?}
     }
@@
 
-\ddd{[Going forward:
-\begin{enumerate}
-\item Does the ``last elbow'' give the same bound? Is it as simple?
-\item Numerically is this about as good as it gets from majorization?
-\item How does this rate compare with existing literature?
-\end{enumerate}}
-
-\newpage
-\section{Magic bounds in arbitrary stabilizer fragments}
+\section{Magic bounds in arbitrary stabiliser fragments}
 \label{sec:stab}
 
-We now generalise the approach taken in the previous section and consider bounds on magic distillation for an arbitrary stabilizer fragment, $\R_\sigma$ where $\sigma$ is any quantum state $\sigma \in \stab$.
+We now generalise the approach taken in the previous section and consider bounds on magic distillation for an arbitrary stabiliser fragment, $\R_\sigma$ where $\sigma$ is any quantum state $\sigma \in \stab$.
 In other words, we consider those bounds on distillation that apply when the free operations have $\sigma$ as a fixed point.
 
-These bounds can be interpreted in two different ways: on one hand they can be viewed as a family of upper bounds parameterized by a stabilizer state $\sigma$, on the other we can associate $\sigma$ to actual hardware limitations or to biased noise models in which it is an equilibrium state of some kind.
-Without loss of generality, we can always write a stabiler state $\sigma$ as a Gibbs state $\sigma = \gamma_\beta \coloneqq \frac{1}{\Z_\beta} e^{-\beta H}$ for some $\beta \geq 0$ and Hamiltonian $H$ as discussed in~\cref{sec:major_frag}.
+These bounds can be interpreted in two different ways: on one hand they can be viewed as a family of upper bounds parameterized by a stabiliser state $\sigma$, on the other we can associate $\sigma$ to actual hardware limitations or to biased noise models in which it is an equilibrium state of some kind.
+Without loss of generality, we can always write a stabiliser state $\sigma$ as a Gibbs state $\sigma = \gamma_\beta \coloneqq \frac{1}{\Z_\beta} e^{-\beta H}$ for some $\beta \geq 0$ and Hamiltonian $H$ as discussed in~\cref{sec:major_frag}.
 
@@
 \begin{equation}\label{eq:stdist}
-	\rho_{\rm{S}}(\epsilon)^{\otimes n} \longrightarrow \rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \gamma_\beta^{\otimes (n-n')},
-\end{equation}
-where the noisy Strange state is given in~\cref{eq:noisysn}, but more general states can be handled in exactly the same manner.
-We also highlight that any magic state can be written in terms of a noisy Strange state.
+	\rho_{\rm{S}}(\epsilon)^{\otimes n} \longrightarrow \rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \sigma^{\otimes (n-n')},
+\end{equation}
+where the noisy Strange state is given in~\cref{eq:noisysn} and we highlight again that any magic state can be transformed to this form via Clifford operations.
 Notice that tensoring in copies of $\gamma_\beta$ does not affect the process, since the state is free.
 In the following result, all copies $n, n', n - n'$ are even with $n > n'$, and $\epsilon'=0$, but the bounds are easily generalised to odd numbers of copies and $\epsilon'$ such that $0 < \epsilon' < \epsilon$.
-Finally, we assume a range of initial noise levels, $\epsilon \leq 3/7$  \nick{higher than all threshold values CITE}, so that the largest Wigner component of the 1-copy noisy magic state is negative.
-
-\nick{Specify: How general can the states get? What about not full-rank states? Should we include the case of odd $n$ or non-zero $\epsilon'$ in the appendix? What about $\epsilon>3/7$?}
+Finally, we assume a range of initial noise levels, $\epsilon \leq 3/7$  \nick{higher than all threshold values in literature CITE}, so that the largest Wigner component of the 1-copy noisy magic state is negative.
 
@@
 \begin{theorem}\label{thm:stab_bounds}
-	Let $\sigma$ be a qutrit stabilizer state, given by $\sigma = \frac{1}{\Z} e^{-\beta H}$ with $H$ having eigenvalues $E_0 \le E_1 \le E_2$, and where $\beta$ is an (effective) inverse temperature for the state.
+	Let $\sigma$ be a qutrit stabiliser state, given by $\sigma = \frac{1}{\Z} e^{-\beta H}$ with $H$ having eigenvalues $E_0 \le E_1 \le E_2$, and where $\beta$ is an (effective) inverse temperature for the state.
 We define
@@
 \end{equation}
-and for $\beta \leq \beta_\star$ define
+and for $\beta \leq \beta_\star$, we define a threshold error rate
 \begin{equation}
@@
 \end{equation}
-a threshold error rate. Then any distillation rate $R(\epsilon, \beta)$ in the $\sigma$--fragment of a magic theory is bounded as follows:
-
+Then any distillation rate $R(\epsilon, \beta)$ in the $\sigma$--fragment of a magic theory is bounded as follows:\\
 If $\beta \leq \beta_{\star}$ and $\epsilon  \leq \epsilon_{\star}$,
@@
 \begin{equation}
-	R(\epsilon, \beta) \le 1 + \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)} - (E_2 - E_0)(\beta_{\star} - \beta)}{\beta (E_0 - F_\beta)},
+	R(\epsilon, \beta) \le 1 + \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)} - (E_2 - E_0)(\beta_{\star} - \beta)}{\beta (E_0 - F_\beta)}.
 \end{equation}
@@
 Firstly, the specific numerical factors in $\epsilon_\star$ are a result of our choice of magic state. 
-Secondly, these bounds can almost certainly be improved through a finer analysis of the Lorenz curve. 
+Secondly, these bounds are derived based on analysis of only a part of the Lorenz curves and can be improved via a finer analysis. 
+This is apparent by simple numerical calculations on the entirety of the curves.
 The existing bounds follow by considering the dominant terms in the rescaled Wigner distribution and do not, for example, take into account the Lorenz curve's peak structure. 
@@
     \centering
-    \includegraphics[scale=0.5]{figs/rate_contour.png}
-    \caption{\textbf{Bounds on magic distillation rates $R(\epsilon, \beta)$ within stabilizer fragments.}
+    \includegraphics[scale=0.55]{figs/rate_scatter.pdf}
+    \caption{\textbf{Bounds on magic distillation rates $R(\epsilon, \beta)$ within stabiliser fragments.}
     The vertical dashed line is the `Landauer-like' temperature threshold $\beta_\star$ and the diagonal dashed curve corresponds to the noise threshold $\epsilon_\star (\beta)$ at every $\beta \leq \beta_\star$.
@@
 \begin{proof}
-	Here we provide a sketch of the proof with all the details included in \nick{the appendix}.
-
-\nick{Rest of section needs tidying}
-
-Consider a qutrit system with maximally Wigner-negative magic state $\ket{{\rm{S}}} = \frac{1}{\sqrt{2}}(\ket{1} - \ket{2})$.
-It can be written in density operator form as
-\begin{align}
-	\ketbra{\rm{S}} = -\frac{1}{3} A_{\bmo} + \sum_{\bmx \neq \bmo} \frac{1}{6} A_{\bmx},
-\end{align}
-where $\bmx$ ranges in the $3$-dimensional phase space $\cal{P}_d$.
-This is the pure Strange state visualised in~\cref{fig:strange}.
-We allow for depolarising noise, so that the system state is a convex sum of the pure Strange state and the maximally mixed state,
-\begin{equation}
-	\rho_{\rm{S}}(\epsilon) \coloneqq (1-\epsilon)\ketbra{\rm{S}} + \epsilon \frac{1}{3}\id,
-\end{equation}
-where we choose to restrict the noise level, $0 \leq \epsilon \leq \frac{3}{7}$, so that the Wigner distribution of the state always contains a negative component which is greater than the remaining 8 positive components.
-
-In particular, the Wigner distribution of the state can be written as 
+	We provide an outline of the proof here, with all technical details included in \nick{the appendix}.\\
+
+The Wigner distribution of $\epsilon$-noisy Strange state can be written as 
 \begin{equation}
@@
 
-Let $\sigma = \frac{1}{\Z} e^{-\beta H}$ be a stabilizer state, which is given in its eigen-decomposition as 
+Let $\sigma = \frac{1}{\Z} e^{-\beta H}$ be a stabiliser state, which is given in its eigen-decomposition as 
 \begin{equation}
@@
 \end{equation}
-where $\{|\varphi_k\>\}$ are pure, orthonormal stabilizer states.
+where $\{|\varphi_k\>\}$ are pure, orthonormal stabiliser states.
 Therefore the exist a Clifford operation that takes $|\varphi_k\> \rightarrow |k\>$, with the effect of permuting the negative component of $\rho_S(\epsilon)$ in the discrete phase space.
@@
 
+\null\newpage
 \section{Comparison with existing distillation rates}
@@
 \end{equation}
-and compare with the numerically optimal error bounds provided by majorization as shown in~\cref{fig:prakash_compare_errors}
+and compare with the numerically optimal error bounds provided by majorisation as shown in~\cref{fig:prakash_compare_errors}
 \begin{figure}[h]
@@
 \end{equation}
-where $\Lambda^+(\rho)$ is the generalised robustness of state $\rho$, calculable via a costly SDP and $F(\psi)$ denotes the stabilizer fidelity of state $\ket{\psi}$.
+where $\Lambda^+(\rho)$ is the generalised robustness of state $\rho$, calculable via a costly SDP and $F(\psi)$ denotes the stabiliser fidelity of state $\ket{\psi}$.
 They demonstrate the performance of their bound by considering the purification process of the qubit magic state $\ket{H}$, with their figure replicated in~\cref{fig:seddon}. 
@@
 \end{equation}
-Their bound simply states that any deterministic single-copy distillation process $\rho^{\otimes n} \longrightarrow \tau$ requires an initial number of copies $n \geq \theta_{\rm{max}}(\rho) / \theta_{\rm{max}}(\tau)$.
+Their bound simply states that any deterministic single-copy distillation process $\rho^{\otimes n} \longrightarrow \tau$ requires an initial number of copies $n \geq \theta_{\rm{max}}(\tau) / \theta_{\rm{max}}(\rho)$.
 Therefore, the rate of our pure Strange state distillation process~\cref{eq:sudist} can only get as tight as
@@
 
-\iffalse
-An $n$-copy state $\rho^n$ has \emph{error rate} $\delta$ iff $\rho$ has an overlap of at least $1-\delta$ with magic state $\ket{\rm{S}}$,
-\begin{equation}
-	\bra{\rm{S}}\rho\ket{\rm{S}} \geq 1-\delta.
-\end{equation}
-The $\epsilon$-noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ has error rate $\delta = \frac{2}{3}\epsilon$.
-A general state of $n$ qutrits with error rate $\delta$ can be converted to the form $\rho_{\rm{S}}(\epsilon_0)^{\otimes n}$ for some noise level $\epsilon$ not necessarily equal to $\delta$.
-
-Given an $[[m,k,d]]$ error correcting code, a distillation protocol that achieves the process in~\cref{eq:test} requires that the following bound holds,
-\begin{align}
-	\frac{n}{n'} = O(\log^\gamma{(1/\epsilon')}),\ \gamma = \log_d{\left(\frac{m}{k}\right)}
-\end{align}
-
-In~\cite{Bravyi2012,Hastings2018}, the asymptotic rate $O(\log^\gamma{(1/\epsilon')})$ is called the \emph{distillation cost}, and in~\cite{cit:bravyi,Krishna2019} the parameter $\gamma$ is called the \emph{overhead}.
-
-There are many distillation protocols in the literature, e.g.~\cite{Bravyi2012,Hastings2018}, that involve a specific value of $\gamma$ and convert a specific number of copies $n$ of input states to $n'=1$ output state \nick{what about $\epsilon$?}.
-They should all satisfy
-\begin{equation}\label{eq:rate_cost}
-	\frac{1}{R(\epsilon, \epsilon', \beta)} \leq \frac{n}{n'} = O(\log^\gamma{(1/\epsilon')}).
-\end{equation}
-Therefore, given process parameters $n, n', \epsilon, \epsilon'$, we can scan through the stabilizer states to find a range of $\beta$ for which inequality~\cref{eq:rate_cost} is valid.
-In principle, the higher the value of parameter $\gamma$, the lower the output error rate $\epsilon'$ can be while~\cref{eq:rate_cost} is still true.
-In~\cite{Hastings2018} \nick{CITE MORE}, they report a value of $\gamma = 0.6779\dots$, while in~\cite{Krishna2019}, they report a scaling $\gamma = O(1/\log{d})$ with respect to the system's odd prime dimension $d$.
-The latter tends to 0 asymptotically.
-
-We can rephrase this result, saying that any distillation protocol in the $\gamma_\beta$-fragment with an $n$-copy input and $n'$-copy, $\epsilon'$-noisy desired output, must have input noise level 
-\begin{equation}
-	\epsilon \leq  E\left(\frac{n'}{n}, \epsilon', \beta \right)
-\end{equation}
-for some error bound $E$ related to $R$.
-
-Furthermore, in~\cite{cit:bravyi,cit:prakash}, two different distillation protocols are proposed with output error rate scalings of the form 
-\begin{equation}
-	\epsilon' \propto (\alpha \epsilon)^{n^\xi},
-\end{equation}
-where $\alpha$ is some constant, $\xi = 1/\log_3{15} \approx 0.4$ in~\cite{cit:bravyi} for qubit codes and $\xi = 1/\log_3{19008} \approx 0.1$ for qutrit codes.
-They also report a certain input threshold error rate $\epsilon_\star$ above which distillation is not possible.
-A first requirement is that $\epsilon_\star \leq E(n'/n, \epsilon', \beta)$, but we can also again find a range of $\beta$ for which the inequality
-\begin{align}
-	\epsilon &\leq E\left(\frac{n'}{n}, \epsilon'(\epsilon), \beta \right) \\
-	\epsilon' &\sim O\left((n\epsilon)^d\right)
-\end{align}
-holds, given some distillation rate $n'/n$ and input error rate $\epsilon$.
-\fi
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\null\newpage
-
-\section{Random info}
-
-\nick{Move stuff around or remove.}\vspace{-10pt}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.5]{figs/noise_threshold.pdf}
-    \caption{\textbf{Noise threshold $\epsilon_\star$ and rate $R(\beta, \epsilon_\star)$ versus $\beta$.}
-    At $\beta = 0$ and threshold noise level $\epsilon = \epsilon_\star = 3/7$, the rate is $R(0, \epsilon_\star) = \frac{\ln{(9/7)}}{\ln{3}} \approx 0.23$.
-    }
-    \label{fig:noise_threshold}
-\end{figure}
-
-We generalise the analysis of unital fragments into any circuit with thermalisation noise parametrised by the temperature $\beta^{-1}$.
-In~\cref{fig:thermal_distill}, we examine the majorization bound for the same purification process of~\cref{eq:sdist} with $\epsilon' = 0.05$.
-The curves plotted suggest that there exists a fragment $\O_{\gamma_{\beta_{\rm{max}}}}$ which allows for a highest noise threshold at any given number of copies of the initial state.
-Adding more copies results in a lower optimal temperature $\beta^{-1}$.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.5]{figs/thermal_distill.pdf}
-    \caption{\textbf{Threshold dependence on temperature in thermal fragments.} Lorenz curve ratios for the Strange state purifying process in~\cref{eq:sdist} with $\epsilon' = 0.05$.
-    The peaks of each curve indicate the optimal temperature $\beta_{\rm{max}}^{-1}$ that allows for the highest noise threshold at every given number of initial state copies $k$.
-    The line $\epsilon = \frac{3}{4}$ indicates the threshold noise beyond which the Strange state no longer contains negativities.
-    }
-    \label{fig:thermal_distill}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Lower bounds in $\sigma$--fragments}
-\ddd{[Am throwing down some rough material, to be polished later.]}
-
-In order to obtain lower bounds one must now make precise what the free operations actually are in the  theory, beyond the condition of preserving Wigner-positivity.
-
-We first consider the unital fragment, and consider the transformations possible using Clifford unitaries, and convex mixtures of Clifford unitaries.
-We denote the Clifford group as $\C$, and given some quantum state $\rho$ the accessible states in the unital fragment are given by $\E(\rho) = \sum_{g \in \C} p(g) U(g) \rho U(g)^\dagger$.
-
-\subsection{Symplectic majorization of magic state Wigner distributions.}
-We now exploit the the group structure, which leads to a more general notation majorization that has been extensively studied in the classical context, but to our knowledge has not yet been used in quantum information theory.
-
-\begin{definition} Given a group $G$ that acts on a vector space $V$, we say that $\bmx$ \emph{$G$-majorises} $\bmy$ precisely when $\y \in H(\x)$, where $H(\x)$ is the convex hull of $\{g \x : g \in G\}$.
-We denote this as $\y \prec_G \x$.
-\end{definition}
-
-Now any quantum state $\rho$ has a Wigner distribution $W_\rho(\x)$. Given a Clifford unitary $\U \in \C$ we have that its representation in the Heisenberg-Weyl frame is given by
-\begin{equation}
-W_{\U(\rho)} (\x) = [\mbox{\ddd{fill in}}].
-\end{equation}
-
-This group action corresponds to the action of the affine symplectic group on the discrete phase space $\P_d$.
-To proceed we can study the discrete translational action, and the symplectic action separately.
-
-\subsection{Cyclic majorization conditions.}
-We can consider for $G$, the cyclic group of order $N$, which is described by $G= \< g | g^N = e\>$.
-in Terms of the Wigner distributions, this arises for the discrete lattice translations arising from displacement operators.
-
-A set of necessary and sufficient conditions for cyclic majorization has been obtained and is given as follows.
-Suppose $\x, \y$ are two real vectors in $\mathbb{R}^n$.
-Let $\Delta$ be the elementary shift operator, defined by
-\begin{equation}
-\Delta \x = \Delta (x_1, x_2, \dots, x_n) := (x_n, x_1, x_2, \dots, x_{n-1}),
-\end{equation}
-and from this it is clear that $\Delta$ generates a representation of the abelian group $(\mathbb{Z}_n,+)$.
-We now say that $\x$ \emph{cyclically majorizes} $\y$, written $\x \succ_C \y$, if and only if 
-\begin{equation}
-\y = \sum_{k=0}^{n-1} p_k \Delta^k \x,
-\end{equation}
-for some probability distribution $p=(p_k)$. This means that $\y$ lies in the convex hull of the orbit of $\x$ under cyclic shifts. Thus, we may write this condition as $\y = L(\p) \x$, where
-\begin{equation}
-L(\p) :=  \sum_{k=0}^{n-1} p_k \Delta^k,
-\end{equation}
-is a linear operator, as a function of an unknown distribution $\p$. We now have the following key identity for linear operators of this form:
-\begin{equation}
-L(\p)\x = QL(\x) \p,
-\end{equation}
-where $Q$ is a permutation matrix sending $e_0:=(1,0,0,\dots ,0)$ to itself, and otherwise sending $e_k$ to $e_{n-1-k}$, where $e_k=  (0,0,\dots, 0,1,0,\dots, 0)$ is the $k$'th basis vector.
-We thus have
-\begin{align}
-\x \succ_C \y &\Leftrightarrow \y = L(\p) \x \mbox{ for some dist. } \p. \nonumber \\
-&\Leftrightarrow \y = QL(\x) \p \mbox{ for some dist. } \p. \nonumber \\
-&\Leftrightarrow [QL(\x)]^{-1}\y = \p \mbox{ for some dist. } \p. \nonumber \\
-&\Leftrightarrow [QL(\x)]^{-1}\y = \p  \ge \mathbf{0} \mbox{ and normalized}.
-\end{align}
-This implies that to check whether $\x \succ_C \y$ it suffices to compute the components of the left-hand side and ensure non-negativity (I suspect it is normalised if $\x$ and $\y$ are normalised).
-
-Note though that by using Fourier analysis we can simplify this in terms of computational demands to checking if the vector
-\begin{equation}
-\p = C(\x') Q\y,
-\end{equation}
-has non-negative components, where
-\begin{equation}
-\x' := n\F_n [\F_n\x]^{-1},
-\end{equation}
-with $\F_n$ being the discrete Fourier transform, and the bracket term $[\F_n \x]^{-1}$ denotes the vector obtained by inverting the components of $\F \x$ individually.
-So the recipe for cyclic majorization is:
+\ddd{[Going forward:
 \begin{enumerate}
-\item Given inputs $\x$ and $\y$.
-\item Compute the vector $\x'$ via two Fourier transforms and $n$ inversions.
-\item Compute the circulant matrix $C(\x')$.
-\item Compute $\C(\x')Q \y$ and check if all components are non-negative.
-\end{enumerate}•
-
-\subsection{Symplectic majorization for qutrit magic}
-The qutrit system provides a good illustration of the techniques.
-In this case the symplectic group $SL(2,\mathbb{Z}_3)$ is isomorphic (up to $\pm \I$) the symmetry group of the tetrahedron, which in turn is isomorphic to $S_4$, the permutation group on 4 symbols.
-Therefore we expect in this case that symplectic majorization on $\P_3$ corresponds to a restricted form of majorization.
-
-\subsection{Fundamental Regions of a group $G$}
-\ddd{[This is theory for the appendices, and also to help flesh out the theory of $G$ majorization. It looks a bit technical, but the core idea is simple enough once you get it.]}
-Given a group $G$ that acts on a vector space $V$, we now have the following concept.
-\begin{definition} A \emph{fundamental region} $F$ of $G$ in $V$ is any open set $F$ such that $F \cap gF = \varnothing$ for $g \ne e$ and moreover 
-\begin{equation}
-V = \bigcup_{g} \overline{g F}.
-\end{equation}
-\end{definition}
-Here, the overline denotes the closure of a set.
-Loosely speaking, we can view $F$ as obtained by quotienting the vector space $V$ via the group action.
-We then have the following key theorem, which is proved in [CITE].
-\begin{theorem} If $G$ has a fundamental region $F$ that is unique, modulo actions of the group $F\rightarrow gF$, then $\bar{F}$ is a closed, convex cone and for any $\x, \y \in \bar{F}$ we have
-\begin{equation}
-\y \prec_G \x \Leftrightarrow \mathbf{a}\cdot \y \le \mathbf{a} \cdot \x, \mbox{ for all } \mathbf{a} \in \bar{F}.
-\end{equation}
-\end{theorem}
-If the cone $\bar{F}$ is finitely generated, namely 
-\begin{equation}
-\bar{F} = \mbox{cone}( \mathbf{c}_1, \dots, \mathbf{c}_N),
-\end{equation}
-for some finite set of vectors, then the majorization condition reduces to checking a \emph{finite} set of inequalities, namely checking $\mathbf{c}_k \cdot \y \le \mathbf{c}_k \cdot \x$ for $k=1, \dots , N$.
-
-Note now that any group action $G$ on a vector space $V$ always has a fundamental region. Consider any $\x \in V$ such that $g \x \ne \x$ unless $g =e$. For this we define
-\begin{equation}
-K = \{ \mathbf{a} \in V : \sup_g \left [ (g\mathbf{a})\cdot \x \right ] = \mathbf{a} \cdot \x \},
-\end{equation}
-then $F = K_{\mbox{\tiny int}}$ is a fundamental region of $G$ in $V$, where $ K_{\mbox{\tiny int}}$ is the interior of the set $K$.
-In simple terms, this fundamental region corresponds to the set of vectors that are `close' to $\x$, in the sense that any non-trivial group action $\mathbf{a} \rightarrow g \mathbf{a}$ on them moves them away from $\x$ with respect the inner product.
-See [CITE] for a proof of this statement.
-
-\subsection{Computing the fundamental region $F$ for the qutrit}
-Firstly, note that we actually have that $SL(2, \mathbb{Z}_3)$ is represented by $U(g)$ on $\P_3$, and so we should use that notation for precision.
-
-Since the symplectic group for $d=3$ is a reflection group, it turns out that this guarantees that an essentially unique fundamental region exists, and so we can reduce to a \emph{finite} set of majorization conditions (I think 5 in this case).
-Note that the $K$ defined above is always a closed, convex cone.
-This means it should be `easy' to determine the fundamental region.
-Reflection groups are Coexter groups, and I believe this set $K$ is essentially a Weyl chamber in that language.
-Anyhow, let's not get distracted by abstraction.
-
-The concrete recipe going forward:
-\begin{enumerate}
-\item Pick your favorite $\x \in P_3$ that is \emph{not} stabilized by $g\ne e$. I.e. a vector that moves under all non-trivial group actions.
-\item For each $g_k$ look for the extremal cases of $\y$ such that have constant inner product with $\x$. This corresponds to 
-\begin{equation}
-\left [ (U(g_k) -\I) \y \right ] \cdot \x = 0 \mbox{ for }k=1, \dots ,24.
-\end{equation}
-Or equivalently,
-\begin{equation}
-\y \cdot A^T\x = 0,
-\end{equation}
-where $A := U(g_k) -\I$.
-\item Write down the matrix equation for each $g_k$.
-\item Each of these conditions defines a hyperplane $H_k$ in $\P_3$ corresponding to the boundary of $K$.
-\item We possibly don't need to range over all 24 group elements....but am not sure on this.
-\item From this, we should be able to extract a generating set of vectors.
-\end{enumerate}
-
-\subsection{Toy example to see how the algorithm works}
-Okay, let's see how it works in a simple case.
-Let's consider the case of $V= \mathbb{R}^2$ and $G=S_2=\<g|g^2=e\>$ with the group action $g.(x,y) = (y,x)$ that swaps the components of the vector.
-We should get standard majorization out of this $G$--majorization.
-
-First we find an $\x$ that transforms non-trivially under non-trivial group actions. The vector $\x=(1,0)$ does this. To construct a fundamental region we now look at the equation 
-\begin{equation}
-[g.(x,y) - (x,y)] \cdot (1,0) = 0
-\end{equation}
-and solve for $x,y$. This becomes,
-\begin{equation}
-(y-x, x-y)\cdot(1,0)=0,
-\end{equation}
-which implies the hyperplane (line!) $y=x$ is the \emph{boundary} of the fundamental region. Since we decided to start with $(1,0)$ we can take the region to the right of this line, and so:
-\begin{equation}
-F = \{(x,y) : x>y \}
-\end{equation}
-where we note that we use the strict inequality to get the interior. The region $\bar{F}$ is a half-space, but this is actually a cone, and can be written as
-\begin{equation}
-F= \mbox{cone}( (1,1),(-1,-1), (5,0)).
-\end{equation}
-The first two vectors give the boundary, and we just need one other vector inside $F$ to generate it fully, chosen arbitrarily to be $(5,0)$.
-This last one is needed since $(1,1)$ and $(-1,-1)$ are linearly dependent!
-Therefore
-\begin{align}
-\mathbf{c}_1 &= (1,1) \nonumber \\
-\mathbf{c}_2 &= (-1,-1) \nonumber \\
-\mathbf{c}_3 &= (5,0).
-\end{align}
-The $S_2$--majorization ordering is then given by
-\begin{equation}
-\y \prec \x \Leftrightarrow \mathbf{c}_k \cdot \y \le  \mathbf{c}_k \cdot \x,
-\end{equation}
-for $k=1,2,3$ whenever $\x,\y \in F$.
-Note that is gives the ordering for all vectors in the space, since any general vector can be transformed into $F$ via a group action, since $F$ is a fundamental region.
-Indeed mapping an $\x$ into $F$ is simply $\x \rightarrow \x^\downarrow$, the sorting maneuver!
-The generating vectors $(1,1)$ and $(-1,-1)$ imply that both 
-\begin{equation}
-y_1 + y_2 \le x_1 +x_2,
-\end{equation}
-and
-\begin{equation}
-y_1 + y_2 \ge x_1 +x_2,
-\end{equation}
-which becomes the majorization condition
-\begin{equation}
-y_1+y_2 = x_1 + x_2.
-\end{equation}
-Easy! The final condition from $\mathbf{c}_3=(1,0)$ is then the condition that
-\begin{equation}
-5y_1 \le 5x_1 \Rightarrow y_1 \le x_1,
-\end{equation}
-which is the final majorization condition.
-Thus we have shown how the familiar majorization structure corresponds to the theory of $G$--majorization, and the cone ordering structure that comes from fundamental regions.
-
-\subsection{Another toy example -- non-standard majorization this time}
-Okay, let's look at another option for $V=\mathbb{R}^2$.
-Now consider the group $G=\mathbb{Z}_2 \times \mathbb{Z}_2$ that can be represented as $G=\<g_1,g_2 | g^1=e, g_2 = e, g_1g_2 = g_2g_1\>$, and acts on vectors as $g_1.(x,y) = (-x,y), g_2.(x,y)=(x,-y)$.
-In other words the group just flips vectors about X/Y axes.
-
-A vector that moves under the non-trivial group actions is $(1,1)$, so we use this one and solve for $[g.(x,y) - (x,y)] \cdot (1,1) = 0$. We have for $g = g_1$ the equation
-\begin{equation}
-[(-x,y) - (x,y)]\cdot (1,1) = 0,
-\end{equation}
-which implies the line $x=0$.
-
-For $g=g_2$ we have
-\begin{equation}
-[(x,-y) - (x,y)]\cdot (1,1) = 0,
-\end{equation}
-which implies the line $y=0$.
-
-For $g=g_1g_2$ we have
-\begin{equation}
-[(-x,-y) - (x,y)]\cdot (1,1) = 0,
-\end{equation}
-which implies the line $x+y=0$. The open region bounded by these three conditions is the set
-\begin{equation}
-F := \{ (x,y) : x>0, y>0\}.
-\end{equation}
-So the positive quadrant of $\mathbb{R}^2$ is a fundamental region for $G$, which makes sense since via sign flips we can map this onto the whole plane, once we close the set.
-This is again a convex cone and $\bar{F} = \mbox{cone}((1,0), (0,1))$.
-Thus given any two vectors $\x,\y$ we first act with $G$ to flip their signs so that their components are all positive, $\x \rightarrow \x^\star\ge \mathbf{0}$, then $\y \prec_G \x$ if and only if $y_1 \le x_1$ and $y_2 \le x_2$.
-This implies that
-\begin{equation}
-\y \prec_G \x \Leftrightarrow \y^\star \le \x^\star. 
-\end{equation}
-So the $G=\mathbb{Z}_2 \times \mathbb{Z}_2$ majorization gives the component-wise ordering on vectors once you sort them. It is clear that this extends to any $G=\mathbb{Z}_2^{\times n}$.
-\subsection{A more complex example $S_3$ on $\mathbb{R}^3$.}
-So the symmetric group $S_n$ always gives majorization.
-But the symmetric group has $|S_n| = n!$ elements to it, which is super-exponentially big in $n$.
-We clearly don't have to check $n!$ equations, since the majorization conditions involve just $n+1$ inequalities, and so it must be that the basic generating conditions of the group suffice to determine the fundamental region of $G$.
-
-Let's look at $V = \mathbb{R}^3$ and $G=S_3$ acting on $\x = (x_i)$ as $g.\x = (x_{g^{-1}}(i))$.
-A vector that transforms non-trivially under all non-trivial actions is $(2,1,0)$.
-Let's look at the transpositions, and the boundary planes they give first.
-
-For $g= (1\,\,2)$ we have the equation
-\begin{equation}
-[(y,x,z) - (x,y,z)] \cdot (2,1,0) = 0,
-\end{equation}
-which implies the plane $2(y-x)+ x-y = 0$, namely,
-\begin{equation}
-H_1 = \{(x,y,z) : y=x\}.
-\end{equation}
-The other choices of transpositions work the same and give the planes
-\begin{align}
-H_2 &= \{(x,y,z) : y=z\} \\
-H_3 &= \{(x,y,z) : x=z\}.
-\end{align}
-Note that their intersection gives the line $\{(x,y,z) : x=y=z\}$, which is the line of uniform vectors at the bottom of the majorization pre-order.
-
-What information do the $3$-cycles give? Okay, let's now look at $g=( 1 \,\, 2 \,\, 3)$. The core equation for this becomes
-\begin{equation}
-[(z,x,y) - (x,y,z)] \cdot (2,1,0) = 0,
-\end{equation}
-and so gives
-\begin{align}
-2(z-x) + (x-y) &= 0 \nonumber \\
-\Rightarrow x+y &=2z. 
-\end{align}
-Namely the plane
-\begin{equation}
-H_4 = \{(x,y,z) :  x+y =2z\}.
-\end{equation}The remaining $3$--cycle $(3\,\,2\,\,1)$ gives
-\begin{align}
-H_5 &= \{(x,y,z) : y+z = 2x\}.
-\end{align}
-Note that $|S_3| = 6$, but the identity element $g=e$ gives no constraint, and so there are exactly $5$ bounding planes.
-Note also that the line $\{ (t,t,t)\} $ is again the intersection of all the planes.
-
-These 5 planes bound a cone containing $(2,1,0)$, namely the fundamental region $F$. What's a good algorithm to obtain a generating set of vectors for this cone?
-
-Firstly, since the line $\{(t,t,t)\}$ being the intersection of all the planes, is definitely on the boundary of $F$, this means we must have $\mathbf{c}_1 = (1,1,1)$ and $\mathbf{c}_2 = (-1,-1,-1)$ in our generating set.
-Perhaps a good algorithm is to compute intersections, obtain generating vectors for these intersections of the hyperplanes, $H_{ij}$ and then let $K_i$ and $K_j$ be the half-spaces in which $(2,1,0)$ resides.
-Now the intersection of two cones, is itself a cone so we can just keep intersecting the half-space/cones.
-Thus, we compute
-\begin{align}
-H_{12} &:= H_1 \cap H_2 \\
-&=\{ (t,t,t) : t\in \mathbb{R}\}=:L.
-\end{align}
-Similarly, $H_{13} = H_{23}= L$. What about the other intersections? Well $H_{14} = H_{15}=L$. In fact all intersections are the same! 
-\begin{equation}
-H_{ij} = H_i \cap H_j = L \mbox{ for all } i,j.
-\end{equation}
-The fundamental region is given by the intersection of $K_1$ and $K_2$, or any other two half-spaces.
-This is generated by $\mathbf{c}_1$ and $\mathbf{c}_2$ above, and any two independent vectors in the intersection of these half-spaces.
-We can choose
-\begin{align}
-\mathbf{c}_3 &= (1,1,0) \\
-\mathbf{c}_4 &= (1,0,0),
-\end{align}
-note that $\mathbf{c}_3 \in H_1$ and $\mathbf{c}_4 \in H_2$, while $\mathbf{c}_3 \in K_2$ and $\mathbf{c}_4 \in K_1$ and so this works correctly. We thus have
-\begin{equation}
-\bar{F} = \mbox{cone}(\mathbf{c}_1 ,\mathbf{c}_2 ,\mathbf{c}_3 ,\mathbf{c}_4 ).
-\end{equation}
-The first two inequalities give the condition that
-\begin{equation}
-x_1+x_2+x_3 = y_1+y_2+y_3,
-\end{equation}
-while the remaining two conditions give the inequalities
-\begin{align}
-y_1 &\le x_1 \\
-y_1+y_2 &\le x_1 +x_2.
-\end{align}
-This is the standard majorization relation.
-Geometrically, the cone $\bar{F}$ is actually a funny one to visualise: it consists of a half-line radiating out from $(0,0,0)$ to $(-1, -1, -1)$, together with the triangular ``infinite pyramid'' generated by positive combinations of $(1,1,1), (1,1,0), (1,0,0)$.
-But we can also take positive linear combinations of $(-1,-1,-1)$ and e.g.
-$(1,1,0)$ and so it is still a bit tricky to visualise.
-\subsection{Symplectic majorization for $d =5$ and beyond.}
-For the case $d=5$ we also have a particularly simple group structure, where now the symplectic group $SL(2, \mathbb{Z}_5)$ is isomorphic to the symmetry group of the icosahedron.
-This is another reflection group and therefore we can again obtain the finite set of majorization conditions to describe it.
-Here the order of the group is $60$ and so we probably shouldn't make Nick compute this by hand.
-\newpage
-\section{Extension to general quantum resource theories}
-\label{sec:frag}
-
-So far we have introduced the notion of $\sigma$--fragments for any resource theory of magic. 
-In this section we pause to generalise this concept to an arbitrary resource theory and explain precisely how it connects with resource monotones. 
-The busy reader more focussed on magic may skip this section.
-
-State convertibility within a given resource theory is often a hard question to address due to the intricate structure of the theory.
-In general, the structure of a theory $\R$ is described by a pre-order $\prec_\R$ and usually resource monotones are employed to reduce this structure into a simple real number ordering \nick{CITE}.
-The subdivisions of magic theories into $\sigma$--fragments suggests a new approach towards investigating state convertibility which retains more structure of the originaltheory than a measure can.
-
-Monotones reduce the structure of the resource theory $\R$ to a \emph{total} order on the real numbers.
-Therefore, two states, even if incomparable in $\R$, are always mapped onto ordered real numbers.
-We now generalise this idea of a theory projection that preserves comparability between states. 
-\begin{definition}[\textbf{Covariant projection}]\label{def:covproj}
-Let $\R = (\F, \O)$ be a resource theory with pre-order $\prec_\R$. 
-Then a \emph{covariant resource projection} of $\R$ to a resource theory $\R'$ with pre-order $\prec_{\R'}$, is a pair of mappings $(\Pi_s, \Pi_o)$, where $\Pi_s$ maps quantum states in $\R$ to quantum states in $\R'$, and $\Pi_o$ maps free operations in $\R$ to free operations in $\R'$.
-Moreover, these obey
-	\begin{enumerate}
-        \item $\Pis(\rho_1) \prec_{\R'} \Pis(\rho_2)$ whenever $\rho_1 \prec_\R \rho_2$;
-        \item $\Pio(\E) = \Pio(\E_1) \circ \Pio(\E_2)$ whenever $\E = \E_1 \circ \E_2$.
-    \end{enumerate}
-We call $\R'$ a \emph{covariant fragment} of $\R$.
-\end{definition}
-
-Resource monotones can now be clearly seen as a special case of covariant resource projections.
-\begin{proposition}[\textbf{Totally ordered covariant theories}]\label{thm:monoproj}
-	Any resource monotone $\M$ of a resource theory $\R$ is a covariant projection for which $\prec_{\R'}$ is a total order. 
-	Conversely, any such covariant projection corresponds to a resource monotone $\M$. 
-\end{proposition}
-\begin{proof}
-	Consider a monotone $\M$ in the context of a general resource theory $\R = (\F, \O)$.
-	State order is covariantly preserved due to the defining property of a monotone, stated in~\cref{def:mono}, where the pre-order $\prec_{\R'}$ is simply the total order $\leq$ on $\mathbb{R}$.
-
-	Operational composition is covariantly preserved when we simply choose $\Pio(\E) = 1_\times$, namely the `multiplication by 1' operation on real numbers. 
-	The definition of a resource monotone then automatically implies covariance.
-
-	Conversely, given any covariant projection of $\R$ for which $\prec_{\R'}$ is a total order, we may map the totally ordered set of elements $\Pis(\rho)$ via an injective, non-decreasing function $f$ into $\mathbb{R}$.
-	Then, $\M(\rho):=f(\Pi_s(\rho))$ provides a numerical value for each $\rho$ that obeys the definition of a monotone.
-
-\end{proof}
-
-We can also view $\sigma$--fragments as an example of reducing the structure of a magic theory $\R$ to a subtheory with a tractable pre-order.
-However, states which are incomparable in $\R$ remain incomparable and conversions between states which are comparable in $\R$ may no longer be possible.
-\begin{definition}[\textbf{Contravariant projection}]\label{def:contraproj}
-	Let $\R = (\F, \O)$ be a resource theory with pre-order $\prec_\R$. 
-Then a \emph{contravariant resource projection} of $\R$ onto a resource theory $\R'$ with pre-order $\prec_{\R'}$, is a pair of mappings $(\Pi_s, \Pi_o)$, where $\Pi_s$ maps quantum states in $\R$ onto quantum states in $\R'$, and $\Pi_o$ maps free operations in $\R$ onto free operations in $\R'$.
-Moreover, these obey
-	\begin{enumerate}
-        \item $\rho_1 \prec_\R \rho_2$ whenever $\Pis(\rho_1) \prec_{\R'} \Pis(\rho_2)$;
-        \item $\E = \E_1 \circ \E_2$ whenever $\Pio(\E) = \Pio(\E_1) \circ \Pio(\E_2)$.
-    \end{enumerate}
-We call $\R'$ a \emph{contravariant fragment} of $\R$.
-\end{definition}
-The use of covariant and contravariant in~\cref{def:covproj,def:contraproj} refers to the direction of implication between the two pre-orders and operation compositions\footnote{Note that strictly these are not projections in the sense of $\Pi^2 = \Pi$, but are instead morphisms.
-Here our use of the term projection is motivated by the idea that one one generally loses information about $\R$ under the mapping.}.
-
-\nick{Perhaps scrap definition of contravariant projection and define contravariant fragment as a subtheory $\R'$ where there exists a (injective) covariant projection from $\R'$ to parent theory $\R$.
-That would make every subtheory $\R' = (\F', \O')$ a contravariant fragment if $\O'$ is closed under composition, this includes $\sigma$--fragments.}
-
-\begin{proposition}\label{thm:subproj}
-    Let $\R = (\F, \O)$ be a resource theory, and let $\O' \subseteq \O$ be a non-empty subset of the free operations that is closed under composition, and moreover $\O'$ is the largest such subset, in the sense that for any $\E_1 \not \in \O'$ and any $\E_2 \in \O'$ we have that both $\E_1 \circ \E_2$ and $\E_2 \circ \E_1$ are not in $\O'$.
-Then $\R' = (\F, \O')$ of $\R$ defines a contravariant fragment of $\R$.
-\end{proposition}
-\begin{proof}
-    We first define $\Pis (\rho) = \rho$ for all $\rho$.
-It is clear that since $\O'$ is a subset of $\O$ any operation in $\O'$ will map the set of free states into itself.
-Moreover the identity channel $id$ is necessarily in $\O'$, due to the maximality assumption.
-For $\Pio$ we let $\Pis(\E) = \E$ if $\E \in \O'$ and otherwise $\Pis(\E) =id$.
-Now consider $\Pio (\E_1 \circ \E_2)$.
-Either the triple $\{\E_1, \E_2, \E_1\circ \E_2\}$ are all in $\O'$ or they are all outside of $\O'$.
-For the former case $\Pio(\E_1 \circ \E_2) = \E_1 \circ \E_2 = \Pio(\E_1) \circ \Pio(\E_2)$, while for the latter $\Pio(\E_1 \circ \E_2) = id = \Pio(\E_1) \circ \Pio(\E_2)$, which proves that compositions are respected under the map.
-Finally, $\rho \prec_{R'} \sigma$ implies there exists $\E \in \O' \subseteq \O$ such that $ \E(\rho) = \sigma$, and since $\E \in \O$ this implies $\rho \prec _{\R} \sigma$, as required, which completes the proof.
-
-\end{proof}
-\nick{Suppose $\E_2$ is the replacement channel $\E_2(\rho) = \sigma$.
-This is a stabilizer operation.
-Then $\E_2 \circ \E_1 \in \O_\sigma$ even if $\E_1 \notin \O_\sigma$.
-Now suppose $\E$ is a Hadamard unitary, then $id = \E \circ \E_{reverse}$ but $id \in \O_{\ketbra{0}}$ while $\E, \E_{reverse} \notin \O_{\ketbra{0}}$.} \ddd{[Ah ok, agreed.
-This is fine for now.
-Let's not spend ages trying to generalise this so as to include the majorization fragments.
-It's just good to explore the possibilities a bit, to illustrate the non-trivial aspects.]}
-As an immediate corollary of~\cref{thm:subproj}, a $\sigma$--fragment of any magic theory $\R$ is a contravariant fragment of $\R$.
-
-\begin{proposition}
-	Let $\R = (\F,\O)$ be a resource theory, and let $\D \in \O$ be a free operation, which is reversible by $\D_{\rm{rev}} \in \O$, so that $\D_{\rm{rev}} \circ \D = \idc$.
-
-	Then, we can define a contravariant projection of $\R$, by acting on all quantum states with $\D$.
-\end{proposition}
-\begin{proof}
-	We show that the theory $\R' = (\F', \O)$, with $\F' = \{\D(\rho):\rho \in \F \}$, is a contravariant fragment of $\R$.
-
-	Let $\Pis$ map every state $\rho$ to $\D(\rho)$ and suppose $\D(\rho_1) \prec \D(\rho_2)$. 
-	Then, there exists $\E \in \O$ such that $\rho_1 = (\D_{\rm{rev}} \circ \E \circ \D) (\rho_2)$, so $\rho_1 \prec \rho_2$.
-
-	Finally, let $\Pio$ map every free operation to itself, so that composition of operations is trivially preserved.
-
-\nick{If $\D$ is a recovery map, so that $\D \circ \D_{\rm{rev}} = \idc$, then this is a covariant projection instead.
-
-If $\D$ is not reversible, this mapping is in general NOT contravariant (consider the replacement map $\D(\rho) = \frac{1}{d}\id$ for a strange state and stabilizer state - surely there is such a counterexample in thermodynamics theory if we consider a highly coherent state and one with the same energy population but no coherences.} \ddd{[Ok.
-Again, let's not spend time worrying about this now.
-It's clear there is various fine-print to these cases...but they're not essential to our work so let's put this on hold.]}
-\end{proof}
-
-Important examples of resource fragments appear in several established resource theories.
-\nick{Need to check if the thermodynamics example works, include magic theories as fragments of $\Rmax$, include Nielsen's bipartite entanglement.} \ddd{[Don't worry about these things now -- let's get the computations section improved]}
-
-\newpage
+\item Does the ``last elbow'' give the same bound? Is it as simple?
+\item Numerically is this about as good as it gets from majorisation?
+\item How does this rate compare with existing literature?
+\end{enumerate}}
 

### 2021-03-19 notes/notes.tex
added notes

\documentclass[pra,
aps,
twocolumn,
superscriptaddress,
groupedaddress,
nofootinbib,
reprint
]{revtex4-1}

\input{preamble}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Lower bounds in $\sigma$--fragments}
\ddd{[Am throwing down some rough material, to be polished later.]}

In order to obtain lower bounds one must now make precise what the free operations actually are in the  theory, beyond the condition of preserving Wigner-positivity.

We first consider the unital fragment, and consider the transformations possible using Clifford unitaries, and convex mixtures of Clifford unitaries. We denote the Clifford group as $\C$, and given some quantum state $\rho$ the accessible states in the unital fragment are given by $\E(\rho) = \sum_{g \in \C} p(g) U(g) \rho U(g)^\dagger$.

\subsection{Symplectic majorisation of magic state Wigner distributions.}
We now exploit the the group structure, which leads to a more general notation majorisation that has been extensively studied in the classical context, but to our knowledge has not yet been used in quantum information theory.

\begin{definition} Given a group $G$ that acts on a vector space $V$, we say that $\bmx$ \emph{$G$-majorises} $\bmy$ precisely when $\y \in H(\x)$, where $H(\x)$ is the convex hull of $\{g \x : g \in G\}$. We denote this as $\y \prec_G \x$.
\end{definition}

Now any quantum state $\rho$ has a Wigner distribution $W_\rho(\x)$. Given a Clifford unitary $\U \in \C$ we have that its representation in the Heisenberg-Weyl frame is given by
\begin{equation}
W_{\U(\rho)} (\x) = [\mbox{\ddd{fill in}}].
\end{equation}

This group action corresponds to the action of the affine symplectic group on the discrete phase space $\P_d$. To proceed we can study the discrete translational action, and the symplectic action separately.

\subsection{Cyclic majorisation conditions.}
We can consider for $G$, the cyclic group of order $N$, which is described by $G= \< g | g^N = e\>$. in Terms of the Wigner distributions, this arises for the discrete lattice translations arising from displacement operators.

A set of necessary and sufficient conditions for cyclic majorisation has been obtained and is given as follows. Suppose $\x, \y$ are two real vectors in $\mathbb{R}^n$. Let $\Delta$ be the elementary shift operator, defined by
\begin{equation}
\Delta \x = \Delta (x_1, x_2, \dots, x_n) := (x_n, x_1, x_2, \dots, x_{n-1}),
\end{equation}
and from this it is clear that $\Delta$ generates a representation of the abelian group $(\mathbb{Z}_n,+)$.
We now say that $\x$ \emph{cyclically majorises} $\y$, written $\x \succ_C \y$, if and only if 
\begin{equation}
\y = \sum_{k=0}^{n-1} p_k \Delta^k \x,
\end{equation}
for some probability distribution $p=(p_k)$. This means that $\y$ lies in the convex hull of the orbit of $\x$ under cyclic shifts. Thus, we may write this condition as $\y = L(\p) \x$, where
\begin{equation}
L(\p) :=  \sum_{k=0}^{n-1} p_k \Delta^k,
\end{equation}
is a linear operator, as a function of an unknown distribution $\p$. We now have the following key identity for linear operators of this form:
\begin{equation}
L(\p)\x = QL(\x) \p,
\end{equation}
where $Q$ is a permutation matrix sending $e_0:=(1,0,0,\dots ,0)$ to itself, and otherwise sending $e_k$ to $e_{n-1-k}$, where $e_k=  (0,0,\dots, 0,1,0,\dots, 0)$ is the $k$'th basis vector. We thus have
\begin{align}
\x \succ_C \y &\Leftrightarrow \y = L(\p) \x \mbox{ for some dist. } \p. \nonumber \\
&\Leftrightarrow \y = QL(\x) \p \mbox{ for some dist. } \p. \nonumber \\
&\Leftrightarrow [QL(\x)]^{-1}\y = \p \mbox{ for some dist. } \p. \nonumber \\
&\Leftrightarrow [QL(\x)]^{-1}\y = \p  \ge \mathbf{0} \mbox{ and normalized}.
\end{align}
This implies that to check whether $\x \succ_C \y$ it suffices to compute the components of the left-hand side and ensure non-negativity (I suspect it is normalised if $\x$ and $\y$ are normalised).

Note though that by using Fourier analysis we can simplify this in terms of computational demands to checking if the vector
\begin{equation}
\p = C(\x') Q\y,
\end{equation}
has non-negative components, where
\begin{equation}
\x' := n\F_n [\F_n\x]^{-1},
\end{equation}
with $\F_n$ being the discrete Fourier transform, and the bracket term $[\F_n \x]^{-1}$ denotes the vector obtained by inverting the components of $\F \x$ individually. So the recipe for cyclic majorisation is:
\begin{enumerate}
\item Given inputs $\x$ and $\y$.
\item Compute the vector $\x'$ via two Fourier transforms and $n$ inversions.
\item Compute the circulant matrix $C(\x')$.
\item Compute $\C(\x')Q \y$ and check if all components are non-negative.
\end{enumerate}•

\subsection{Symplectic majorisation for qutrit magic}
The qutrit system provides a good illustration of the techniques. In this case the symplectic group $SL(2,\mathbb{Z}_3)$ is isomorphic (up to $\pm \I$) the symmetry group of the tetrahedron, which in turn is isomorphic to $S_4$, the permutation group on 4 symbols. Therefore we expect in this case that symplectic majorisation on $\P_3$ corresponds to a restricted form of majorisation.

\subsection{Fundamental Regions of a group $G$}
\ddd{[This is theory for the appendices, and also to help flesh out the theory of $G$ majorisation. It looks a bit technical, but the core idea is simple enough once you get it.]}
Given a group $G$ that acts on a vector space $V$, we now have the following concept.
\begin{definition} A \emph{fundamental region} $F$ of $G$ in $V$ is any open set $F$ such that $F \cap gF = \varnothing$ for $g \ne e$ and moreover 
\begin{equation}
V = \bigcup_{g} \overline{g F}.
\end{equation}
\end{definition}
Here, the overline denotes the closure of a set. Loosely speaking, we can view $F$ as obtained by quotienting the vector space $V$ via the group action. We then have the following key theorem, which is proved in [CITE].
\begin{theorem} If $G$ has a fundamental region $F$ that is unique, modulo actions of the group $F\rightarrow gF$, then $\bar{F}$ is a closed, convex cone and for any $\x, \y \in \bar{F}$ we have
\begin{equation}
\y \prec_G \x \Leftrightarrow \mathbf{a}\cdot \y \le \mathbf{a} \cdot \x, \mbox{ for all } \mathbf{a} \in \bar{F}.
\end{equation}
\end{theorem}
If the cone $\bar{F}$ is finitely generated, namely 
\begin{equation}
\bar{F} = \mbox{cone}( \mathbf{c}_1, \dots, \mathbf{c}_N),
\end{equation}
for some finite set of vectors, then the majorisation condition reduces to checking a \emph{finite} set of inequalities, namely checking $\mathbf{c}_k \cdot \y \le \mathbf{c}_k \cdot \x$ for $k=1, \dots , N$.

Note now that any group action $G$ on a vector space $V$ always has a fundamental region. Consider any $\x \in V$ such that $g \x \ne \x$ unless $g =e$. For this we define
\begin{equation}
K = \{ \mathbf{a} \in V : \sup_g \left [ (g\mathbf{a})\cdot \x \right ] = \mathbf{a} \cdot \x \},
\end{equation}
then $F = K_{\mbox{\tiny int}}$ is a fundamental region of $G$ in $V$, where $ K_{\mbox{\tiny int}}$ is the interior of the set $K$. In simple terms, this fundamental region corresponds to the set of vectors that are `close' to $\x$, in the sense that any non-trivial group action $\mathbf{a} \rightarrow g \mathbf{a}$ on them moves them away from $\x$ with respect the inner product. See [CITE] for a proof of this statement.

\subsection{Computing the fundamental region $F$ for the qutrit}
Firstly, note that we actually have that $SL(2, \mathbb{Z}_3)$ is represented by $U(g)$ on $\P_3$, and so we should use that notation for precision.

Since the symplectic group for $d=3$ is a reflection group, it turns out that this guarantees that an essentially unique fundamental region exists, and so we can reduce to a \emph{finite} set of majorisation conditions (I think 5 in this case). Note that the $K$ defined above is always a closed, convex cone. This means it should be `easy' to determine the fundamental region. Reflection groups are Coexter groups, and I believe this set $K$ is essentially a Weyl chamber in that language. Anyhow, let's not get distracted by abstraction.

The concrete recipe going forward:
\begin{enumerate}
\item Pick your favorite $\x \in P_3$ that is \emph{not} stabilized by $g\ne e$. I.e. a vector that moves under all non-trivial group actions.
\item For each $g_k$ look for the extremal cases of $\y$ such that have constant inner product with $\x$. This corresponds to 
\begin{equation}
\left [ (U(g_k) -\I) \y \right ] \cdot \x = 0 \mbox{ for }k=1, \dots ,24.
\end{equation}
Or equivalently,
\begin{equation}
\y \cdot A^T\x = 0,
\end{equation}
where $A := U(g_k) -\I$.
\item Write down the matrix equation for each $g_k$.
\item Each of these conditions defines a hyperplane $H_k$ in $\P_3$ corresponding to the boundary of $K$.
\item We possibly don't need to range over all 24 group elements....but am not sure on this.
\item From this, we should be able to extract a generating set of vectors.
\end{enumerate}

\subsection{Toy example to see how the algorithm works}
Okay, let's see how it works in a simple case. Let's consider the case of $V= \mathbb{R}^2$ and $G=S_2=\<g|g^2=e\>$ with the group action $g.(x,y) = (y,x)$ that swaps the components of the vector. We should get standard majorisation out of this $G$--majorisation.

First we find an $\x$ that transforms non-trivially under non-trivial group actions. The vector $\x=(1,0)$ does this. To construct a fundamental region we now look at the equation 
\begin{equation}
[g.(x,y) - (x,y)] \cdot (1,0) = 0
\end{equation}
and solve for $x,y$. This becomes,
\begin{equation}
(y-x, x-y)\cdot(1,0)=0,
\end{equation}
which implies the hyperplane (line!) $y=x$ is the \emph{boundary} of the fundamental region. Since we decided to start with $(1,0)$ we can take the region to the right of this line, and so:
\begin{equation}
F = \{(x,y) : x>y \}
\end{equation}
where we note that we use the strict inequality to get the interior. The region $\bar{F}$ is a half-space, but this is actually a cone, and can be written as
\begin{equation}
F= \mbox{cone}( (1,1),(-1,-1), (5,0)).
\end{equation}
The first two vectors give the boundary, and we just need one other vector inside $F$ to generate it fully, chosen arbitrarily to be $(5,0)$. This last one is needed since $(1,1)$ and $(-1,-1)$ are linearly dependent! Therefore
\begin{align}
\mathbf{c}_1 &= (1,1) \nonumber \\
\mathbf{c}_2 &= (-1,-1) \nonumber \\
\mathbf{c}_3 &= (5,0).
\end{align}
The $S_2$--majorisation ordering is then given by
\begin{equation}
\y \prec \x \Leftrightarrow \mathbf{c}_k \cdot \y \le  \mathbf{c}_k \cdot \x,
\end{equation}
for $k=1,2,3$ whenever $\x,\y \in F$. Note that is gives the ordering for all vectors in the space, since any general vector can be transformed into $F$ via a group action, since $F$ is a fundamental region. Indeed mapping an $\x$ into $F$ is simply $\x \rightarrow \x^\downarrow$, the sorting maneuver!
The generating vectors $(1,1)$ and $(-1,-1)$ imply that both 
\begin{equation}
y_1 + y_2 \le x_1 +x_2,
\end{equation}
and
\begin{equation}
y_1 + y_2 \ge x_1 +x_2,
\end{equation}
which becomes the majorisation condition
\begin{equation}
y_1+y_2 = x_1 + x_2.
\end{equation}
Easy! The final condition from $\mathbf{c}_3=(1,0)$ is then the condition that
\begin{equation}
5y_1 \le 5x_1 \Rightarrow y_1 \le x_1,
\end{equation}
which is the final majorisation condition. Thus we have shown how the familiar majorisation structure corresponds to the theory of $G$--majorisation, and the cone ordering structure that comes from fundamental regions.

\subsection{Another toy example -- non-standard majorisation this time}
Okay, let's look at another option for $V=\mathbb{R}^2$. Now consider the group $G=\mathbb{Z}_2 \times \mathbb{Z}_2$ that can be represented as $G=\<g_1,g_2 | g^1=e, g_2 = e, g_1g_2 = g_2g_1\>$, and acts on vectors as $g_1.(x,y) = (-x,y), g_2.(x,y)=(x,-y)$. In other words the group just flips vectors about X/Y axes.

A vector that moves under the non-trivial group actions is $(1,1)$, so we use this one and solve for $[g.(x,y) - (x,y)] \cdot (1,1) = 0$. We have for $g = g_1$ the equation
\begin{equation}
[(-x,y) - (x,y)]\cdot (1,1) = 0,
\end{equation}
which implies the line $x=0$.

For $g=g_2$ we have
\begin{equation}
[(x,-y) - (x,y)]\cdot (1,1) = 0,
\end{equation}
which implies the line $y=0$.

For $g=g_1g_2$ we have
\begin{equation}
[(-x,-y) - (x,y)]\cdot (1,1) = 0,
\end{equation}
which implies the line $x+y=0$. The open region bounded by these three conditions is the set
\begin{equation}
F := \{ (x,y) : x>0, y>0\}.
\end{equation}
So the positive quadrant of $\mathbb{R}^2$ is a fundamental region for $G$, which makes sense since via sign flips we can map this onto the whole plane, once we close the set. This is again a convex cone and $\bar{F} = \mbox{cone}((1,0), (0,1))$. Thus given any two vectors $\x,\y$ we first act with $G$ to flip their signs so that their components are all positive, $\x \rightarrow \x^\star\ge \mathbf{0}$, then $\y \prec_G \x$ if and only if $y_1 \le x_1$ and $y_2 \le x_2$. This implies that 
\begin{equation}
\y \prec_G \x \Leftrightarrow \y^\star \le \x^\star. 
\end{equation}
So the $G=\mathbb{Z}_2 \times \mathbb{Z}_2$ majorisation gives the component-wise ordering on vectors once you sort them. It is clear that this extends to any $G=\mathbb{Z}_2^{\times n}$.
\subsection{A more complex example $S_3$ on $\mathbb{R}^3$.}
So the symmetric group $S_n$ always gives majorisation. But the symmetric group has $|S_n| = n!$ elements to it, which is super-exponentially big in $n$. We clearly don't have to check $n!$ equations, since the majorisation conditions involve just $n+1$ inequalities, and so it must be that the basic generating conditions of the group suffice to determine the fundamental region of $G$.

Let's look at $V = \mathbb{R}^3$ and $G=S_3$ acting on $\x = (x_i)$ as $g.\x = (x_{g^{-1}}(i))$. A vector that transforms non-trivially under all non-trivial actions is $(2,1,0)$. Let's look at the transpositions, and the boundary planes they give first.

For $g= (1\,\,2)$ we have the equation
\begin{equation}
[(y,x,z) - (x,y,z)] \cdot (2,1,0) = 0,
\end{equation}
which implies the plane $2(y-x)+ x-y = 0$, namely,
\begin{equation}
H_1 = \{(x,y,z) : y=x\}.
\end{equation}
The other choices of transpositions work the same and give the planes
\begin{align}
H_2 &= \{(x,y,z) : y=z\} \\
H_3 &= \{(x,y,z) : x=z\}.
\end{align}
Note that their intersection gives the line $\{(x,y,z) : x=y=z\}$, which is the line of uniform vectors at the bottom of the majorisation pre-order.

What information do the $3$-cycles give? Okay, let's now look at $g=( 1 \,\, 2 \,\, 3)$. The core equation for this becomes
\begin{equation}
[(z,x,y) - (x,y,z)] \cdot (2,1,0) = 0,
\end{equation}
and so gives
\begin{align}
2(z-x) + (x-y) &= 0 \nonumber \\
\Rightarrow x+y &=2z. 
\end{align}
Namely the plane
\begin{equation}
H_4 = \{(x,y,z) :  x+y =2z\}.
\end{equation}The remaining $3$--cycle $(3\,\,2\,\,1)$ gives
\begin{align}
H_5 &= \{(x,y,z) : y+z = 2x\}.
\end{align}
Note that $|S_3| = 6$, but the identity element $g=e$ gives no constraint, and so there are exactly $5$ bounding planes. Note also that the line $\{ (t,t,t)\} $ is again the intersection of all the planes.

These 5 planes bound a cone containing $(2,1,0)$, namely the fundamental region $F$. What's a good algorithm to obtain a generating set of vectors for this cone?

Firstly, since the line $\{(t,t,t)\}$ being the intersection of all the planes, is definitely on the boundary of $F$, this means we must have $\mathbf{c}_1 = (1,1,1)$ and $\mathbf{c}_2 = (-1,-1,-1)$ in our generating set. Perhaps a good algorithm is to compute intersections, obtain generating vectors for these intersections of the hyperplanes, $H_{ij}$ and then let $K_i$ and $K_j$ be the half-spaces in which $(2,1,0)$ resides. Now the intersection of two cones, is itself a cone so we can just keep intersecting the half-space/cones. Thus, we compute
\begin{align}
H_{12} &:= H_1 \cap H_2 \\
&=\{ (t,t,t) : t\in \mathbb{R}\}=:L.
\end{align}
Similarly, $H_{13} = H_{23}= L$. What about the other intersections? Well $H_{14} = H_{15}=L$. In fact all intersections are the same! 
\begin{equation}
H_{ij} = H_i \cap H_j = L \mbox{ for all } i,j.
\end{equation}
The fundamental region is given by the intersection of $K_1$ and $K_2$, or any other two half-spaces. This is generated by $\mathbf{c}_1$ and $\mathbf{c}_2$ above, and any two independent vectors in the intersection of these half-spaces. We can choose 
\begin{align}
\mathbf{c}_3 &= (1,1,0) \\
\mathbf{c}_4 &= (1,0,0),
\end{align}
note that $\mathbf{c}_3 \in H_1$ and $\mathbf{c}_4 \in H_2$, while $\mathbf{c}_3 \in K_2$ and $\mathbf{c}_4 \in K_1$ and so this works correctly. We thus have
\begin{equation}
\bar{F} = \mbox{cone}(\mathbf{c}_1 ,\mathbf{c}_2 ,\mathbf{c}_3 ,\mathbf{c}_4 ).
\end{equation}
The first two inequalities give the condition that
\begin{equation}
x_1+x_2+x_3 = y_1+y_2+y_3,
\end{equation}
while the remaining two conditions give the inequalities
\begin{align}
y_1 &\le x_1 \\
y_1+y_2 &\le x_1 +x_2.
\end{align}
This is the standard majorisation relation. Geometrically, the cone $\bar{F}$ is actually a funny one to visualise: it consists of a half-line radiating out from $(0,0,0)$ to $(-1, -1, -1)$, together with the triangular ``infinite pyramid'' generated by positive combinations of $(1,1,1), (1,1,0), (1,0,0)$. But we can also take positive linear combinations of $(-1,-1,-1)$ and e.g. $(1,1,0)$ and so it is still a bit tricky to visualise.
\subsection{Symplectic majorisation for $d =5$ and beyond.}
For the case $d=5$ we also have a particularly simple group structure, where now the symplectic group $SL(2, \mathbb{Z}_5)$ is isomorphic to the symmetry group of the icosahedron. This is another reflection group and therefore we can again obtain the finite set of majorisation conditions to describe it. Here the order of the group is $60$ and so we probably shouldn't make Nick compute this by hand.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Extension to general quantum resource theories}
\label{sec:frag}

So far we have introduced the notion of $\sigma$--fragments for any resource theory of magic. 
In this section we pause to generalise this concept to an arbitrary resource theory and explain precisely how it connects with resource monotones. 
The busy reader more focussed on magic may skip this section.

State convertibility within a given resource theory is often a hard question to address due to the intricate structure of the theory.
In general, the structure of a theory $\R$ is described by a pre-order $\prec_\R$ and usually resource monotones are employed to reduce this structure into a simple real number ordering \nick{CITE}.
The subdivisions of magic theories into $\sigma$--fragments suggests a new approach towards investigating state convertibility which retains more structure of the originaltheory than a measure can.

Monotones reduce the structure of the resource theory $\R$ to a \emph{total} order on the real numbers.
Therefore, two states, even if incomparable in $\R$, are always mapped onto ordered real numbers.
We now generalise this idea of a theory projection that preserves comparability between states. 
\begin{definition}[\textbf{Covariant projection}]\label{def:covproj}
Let $\R = (\F, \O)$ be a resource theory with pre-order $\prec_\R$. 
Then a \emph{covariant resource projection} of $\R$ to a resource theory $\R'$ with pre-order $\prec_{\R'}$, is a pair of mappings $(\Pi_s, \Pi_o)$, where $\Pi_s$ maps quantum states in $\R$ to quantum states in $\R'$, and $\Pi_o$ maps free operations in $\R$ to free operations in $\R'$. 
Moreover, these obey
	\begin{enumerate}
        \item $\Pis(\rho_1) \prec_{\R'} \Pis(\rho_2)$ whenever $\rho_1 \prec_\R \rho_2$;
        \item $\Pio(\E) = \Pio(\E_1) \circ \Pio(\E_2)$ whenever $\E = \E_1 \circ \E_2$.
    \end{enumerate}
We call $\R'$ a \emph{covariant fragment} of $\R$.
\end{definition}

Resource monotones can now be clearly seen as a special case of covariant resource projections.
\begin{proposition}[\textbf{Totally ordered covariant theories}]\label{thm:monoproj}
	Any resource monotone $\M$ of a resource theory $\R$ is a covariant projection for which $\prec_{\R'}$ is a total order. 
	Conversely, any such covariant projection corresponds to a resource monotone $\M$. 
\end{proposition}
\begin{proof}
	Consider a monotone $\M$ in the context of a general resource theory $\R = (\F, \O)$.
	State order is covariantly preserved due to the defining property of a monotone, stated in~\cref{def:mono}, where the pre-order $\prec_{\R'}$ is simply the total order $\leq$ on $\mathbb{R}$.

	Operational composition is covariantly preserved when we simply choose $\Pio(\E) = 1_\times$, namely the `multiplication by 1' operation on real numbers. 
	The definition of a resource monotone then automatically implies covariance.

	Conversely, given any covariant projection of $\R$ for which $\prec_{\R'}$ is a total order, we may map the totally ordered set of elements $\Pis(\rho)$ via an injective, non-decreasing function $f$ into $\mathbb{R}$. 
	Then, $\M(\rho):=f(\Pi_s(\rho))$ provides a numerical value for each $\rho$ that obeys the definition of a monotone.

\end{proof}

We can also view $\sigma$--fragments as an example of reducing the structure of a magic theory $\R$ to a subtheory with a tractable pre-order.
However, states which are incomparable in $\R$ remain incomparable and conversions between states which are comparable in $\R$ may no longer be possible.
\begin{definition}[\textbf{Contravariant projection}]\label{def:contraproj}
	Let $\R = (\F, \O)$ be a resource theory with pre-order $\prec_\R$. 
Then a \emph{contravariant resource projection} of $\R$ onto a resource theory $\R'$ with pre-order $\prec_{\R'}$, is a pair of mappings $(\Pi_s, \Pi_o)$, where $\Pi_s$ maps quantum states in $\R$ onto quantum states in $\R'$, and $\Pi_o$ maps free operations in $\R$ onto free operations in $\R'$. 
Moreover, these obey
	\begin{enumerate}
        \item $\rho_1 \prec_\R \rho_2$ whenever $\Pis(\rho_1) \prec_{\R'} \Pis(\rho_2)$;
        \item $\E = \E_1 \circ \E_2$ whenever $\Pio(\E) = \Pio(\E_1) \circ \Pio(\E_2)$.
    \end{enumerate}
We call $\R'$ a \emph{contravariant fragment} of $\R$.
\end{definition}
The use of covariant and contravariant in~\cref{def:covproj,def:contraproj} refers to the direction of implication between the two pre-orders and operation compositions\footnote{Note that strictly these are not projections in the sense of $\Pi^2 = \Pi$, but are instead morphisms. 
Here our use of the term projection is motivated by the idea that one one generally loses information about $\R$ under the mapping.}.

\nick{Perhaps scrap definition of contravariant projection and define contravariant fragment as a subtheory $\R'$ where there exists a (injective) covariant projection from $\R'$ to parent theory $\R$. That would make every subtheory $\R' = (\F', \O')$ a contravariant fragment if $\O'$ is closed under composition, this includes $\sigma$--fragments.}

\begin{proposition}\label{thm:subproj}
    Let $\R = (\F, \O)$ be a resource theory, and let $\O' \subseteq \O$ be a non-empty subset of the free operations that is closed under composition, and moreover $\O'$ is the largest such subset, in the sense that for any $\E_1 \not \in \O'$ and any $\E_2 \in \O'$ we have that both $\E_1 \circ \E_2$ and $\E_2 \circ \E_1$ are not in $\O'$. Then $\R' = (\F, \O')$ of $\R$ defines a contravariant fragment of $\R$.    
\end{proposition}
\begin{proof}
    We first define $\Pis (\rho) = \rho$ for all $\rho$. It is clear that since $\O'$ is a subset of $\O$ any operation in $\O'$ will map the set of free states into itself. Moreover the identity channel $id$ is necessarily in $\O'$, due to the maximality assumption. For $\Pio$ we let $\Pis(\E) = \E$ if $\E \in \O'$ and otherwise $\Pis(\E) =id$. Now consider $\Pio (\E_1 \circ \E_2)$. Either the triple $\{\E_1, \E_2, \E_1\circ \E_2\}$ are all in $\O'$ or they are all outside of $\O'$. For the former case $\Pio(\E_1 \circ \E_2) = \E_1 \circ \E_2 = \Pio(\E_1) \circ \Pio(\E_2)$, while for the latter $\Pio(\E_1 \circ \E_2) = id = \Pio(\E_1) \circ \Pio(\E_2)$, which proves that compositions are respected under the map. Finally, $\rho \prec_{R'} \sigma$ implies there exists $\E \in \O' \subseteq \O$ such that $ \E(\rho) = \sigma$, and since $\E \in \O$ this implies $\rho \prec _{\R} \sigma$, as required, which completes the proof.

\end{proof}
\nick{Suppose $\E_2$ is the replacement channel $\E_2(\rho) = \sigma$. This is a stabiliser operation. Then $\E_2 \circ \E_1 \in \O_\sigma$ even if $\E_1 \notin \O_\sigma$. Now suppose $\E$ is a Hadamard unitary, then $id = \E \circ \E_{reverse}$ but $id \in \O_{\ketbra{0}}$ while $\E, \E_{reverse} \notin \O_{\ketbra{0}}$.} \ddd{[Ah ok, agreed. This is fine for now. Let's not spend ages trying to generalise this so as to include the majorisation fragments. It's just good to explore the possibilities a bit, to illustrate the non-trivial aspects.]}
As an immediate corollary of~\cref{thm:subproj}, a $\sigma$--fragment of any magic theory $\R$ is a contravariant fragment of $\R$.

\begin{proposition}
	Let $\R = (\F,\O)$ be a resource theory, and let $\D \in \O$ be a free operation, which is reversible by $\D_{\rm{rev}} \in \O$, so that $\D_{\rm{rev}} \circ \D = \idc$.

	Then, we can define a contravariant projection of $\R$, by acting on all quantum states with $\D$.
\end{proposition}
\begin{proof}
	We show that the theory $\R' = (\F', \O)$, with $\F' = \{\D(\rho):\rho \in \F \}$, is a contravariant fragment of $\R$.

	Let $\Pis$ map every state $\rho$ to $\D(\rho)$ and suppose $\D(\rho_1) \prec \D(\rho_2)$. 
	Then, there exists $\E \in \O$ such that $\rho_1 = (\D_{\rm{rev}} \circ \E \circ \D) (\rho_2)$, so $\rho_1 \prec \rho_2$.

	Finally, let $\Pio$ map every free operation to itself, so that composition of operations is trivially preserved.

\nick{If $\D$ is a recovery map, so that $\D \circ \D_{\rm{rev}} = \idc$, then this is a covariant projection instead.

If $\D$ is not reversible, this mapping is in general NOT contravariant (consider the replacement map $\D(\rho) = \frac{1}{d}\id$ for a strange state and stabiliser state - surely there is such a counterexample in thermodynamics theory if we consider a highly coherent state and one with the same energy population but no coherences.} \ddd{[Ok. Again, let's not spend time worrying about this now. It's clear there is various fine-print to these cases...but they're not essential to our work so let's put this on hold.]}
\end{proof}

Important examples of resource fragments appear in several established resource theories. \nick{Need to check if the thermodynamics example works, include magic theories as fragments of $\Rmax$, include Nielsen's bipartite entanglement.} \ddd{[Don't worry about these things now -- let's get the computations section improved]}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Bound comparison}
An $n$-copy state $\rho^n$ has \emph{error rate} $\delta$ iff $\rho$ has an overlap of at least $1-\delta$ with magic state $\ket{\rm{S}}$,
\begin{equation}
	\bra{\rm{S}}\rho\ket{\rm{S}} \geq 1-\delta.
\end{equation}
The $\epsilon$-noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ has error rate $\delta = \frac{2}{3}\epsilon$.
A general state of $n$ qutrits with error rate $\delta$ can be converted to the form $\rho_{\rm{S}}(\epsilon_0)^{\otimes n}$ for some noise level $\epsilon$ not necessarily equal to $\delta$.

Given an $[[m,k,d]]$ error correcting code, a distillation protocol that achieves the process in~\cref{eq:test} requires that the following bound holds,
\begin{align}
	\frac{n}{n'} = O(\log^\gamma{(1/\epsilon')}),\ \gamma = \log_d{\left(\frac{m}{k}\right)}
\end{align}

In~\cite{Bravyi2012,Hastings2018}, the asymptotic rate $O(\log^\gamma{(1/\epsilon')})$ is called the \emph{distillation cost}, and in~\cite{cit:bravyi,Krishna2019} the parameter $\gamma$ is called the \emph{overhead}.

There are many distillation protocols in the literature, e.g.~\cite{Bravyi2012,Hastings2018}, that involve a specific value of $\gamma$ and convert a specific number of copies $n$ of input states to $n'=1$ output state \nick{what about $\epsilon$?}.
They should all satisfy
\begin{equation}\label{eq:rate_cost}
	\frac{1}{R(\epsilon, \epsilon', \beta)} \leq \frac{n}{n'} = O(\log^\gamma{(1/\epsilon')}).
\end{equation}
Therefore, given process parameters $n, n', \epsilon, \epsilon'$, we can scan through the stabiliser states to find a range of $\beta$ for which inequality~\cref{eq:rate_cost} is valid.
In principle, the higher the value of parameter $\gamma$, the lower the output error rate $\epsilon'$ can be while~\cref{eq:rate_cost} is still true.
In~\cite{Hastings2018} \nick{CITE MORE}, they report a value of $\gamma = 0.6779\dots$, while in~\cite{Krishna2019}, they report a scaling $\gamma = O(1/\log{d})$ with respect to the system's odd prime dimension $d$.
The latter tends to 0 asymptotically.

We can rephrase this result, saying that any distillation protocol in the $\gamma_\beta$-fragment with an $n$-copy input and $n'$-copy, $\epsilon'$-noisy desired output, must have input noise level 
\begin{equation}
	\epsilon \leq  E\left(\frac{n'}{n}, \epsilon', \beta \right)
\end{equation}
for some error bound $E$ related to $R$.

Furthermore, in~\cite{cit:bravyi,cit:prakash}, two different distillation protocols are proposed with output error rate scalings of the form 
\begin{equation}
	\epsilon' \propto (\alpha \epsilon)^{n^\xi},
\end{equation}
where $\alpha$ is some constant, $\xi = 1/\log_3{15} \approx 0.4$ in~\cite{cit:bravyi} for qubit codes and $\xi = 1/\log_3{19008} \approx 0.1$ for qutrit codes.
They also report a certain input threshold error rate $\epsilon_\star$ above which distillation is not possible.
A first requirement is that $\epsilon_\star \leq E(n'/n, \epsilon', \beta)$, but we can also again find a range of $\beta$ for which the inequality
\begin{align}
	\epsilon &\leq E\left(\frac{n'}{n}, \epsilon'(\epsilon), \beta \right) \\
	\epsilon' &\sim O\left((n\epsilon)^d\right)
\end{align}
holds, given some distillation rate $n'/n$ and input error rate $\epsilon$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Random info}
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{figs/noise_threshold.pdf}
    \caption{\textbf{Noise threshold $\epsilon_\star$ and rate $R(\beta, \epsilon_\star)$ versus $\beta$.}
    At $\beta = 0$ and threshold noise level $\epsilon = \epsilon_\star = 3/7$, the rate is $R(0, \epsilon_\star) = \frac{\ln{(9/7)}}{\ln{3}} \approx 0.23$.
    }
    \label{fig:noise_threshold}
\end{figure}

We generalise the analysis of unital fragments into any circuit with thermalisation noise parametrised by the temperature $\beta^{-1}$.
In~\cref{fig:thermal_distill}, we examine the majorisation bound for the same purification process of~\cref{eq:sdist} with $\epsilon' = 0.05$.
The curves plotted suggest that there exists a fragment $\O_{\gamma_{\beta_{\rm{max}}}}$ which allows for a highest noise threshold at any given number of copies of the initial state.
Adding more copies results in a lower optimal temperature $\beta^{-1}$.

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{figs/thermal_distill.pdf}
    \caption{\textbf{Threshold dependence on temperature in thermal fragments.} Lorenz curve ratios for the Strange state purifying process in~\cref{eq:sdist} with $\epsilon' = 0.05$.
    The peaks of each curve indicate the optimal temperature $\beta_{\rm{max}}^{-1}$ that allows for the highest noise threshold at every given number of initial state copies $k$.
    The line $\epsilon = \frac{3}{4}$ indicates the threshold noise beyond which the Strange state no longer contains negativities.
    }
    \label{fig:thermal_distill}
\end{figure}

\end{document}

### 2021-03-21 appendix.tex
restructuring

@@
 
-%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
         0 & 1 & 0 & 0 & 0    
-    \end{psmallmatrix} \in \stochw,\ d=5.
+    \end{psmallmatrix} \in {\rm{S}}_5({\W{\frac{1}{5}\id}}).
 \end{equation}
-It preserves the uniform distribution $\W{\frac{1}{5}\id}$, but it does not correspond to any positive operation.
+It preserves the uniform distribution $\W{\frac{1}{5}\id}$, but it does not correspond to any positive (hence quantum) operation.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-In particular, it can be used in the discussion of standard Lorenz curves to set the necessary constraints,
+\nick{In particular}, it can be used in the discussion of standard Lorenz curves to set the necessary constraints,
 \begin{align}
@@
 where $x_{I'(0, m'_{0}, 9^{n - n'})}, x_{I'(1, m'_{1}, 9^{n - n'})}, \dots, x_{I'(n', m'_{n'}, 9^{n - n'})} \in T$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon')^{\otimes n'}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Technical details of bound derivation in stabiliser fragments}
+\label{app:lcst_technical}
+
 \subsection{Component-multiplicity pairs}

### 2021-03-22 appendix.tex
Tidied up stabilizer bound proof

@@
 \end{equation}
-The multiplicative property of the Wigner distribution over a composite phase space $\cal{P}_d[d_A] \times \cal{P}_d[d_B]$,
+The multiplicative property of the Wigner distribution over a composite phase space $\cal{P}_{d_A} \times \cal{P}_{d_B}$ shown in~\cref{thm:wstate},
 \begin{equation}
@@
 \end{equation*}
+
+Note that the rescaled distribution is also multiplicative,
+\begin{align}
+	&\widetilde{\rm{W}}_{\rho_A \otimes \rho_B | \gamma_A \otimes \gamma_B}(\bmx_A \oplus \bmx_B) = \frac{\W[\bmx_A \oplus \bmx_B]{\rho_A \otimes \rho_B}}{\W[\bmx_A \oplus \bmx_B]{\gamma_A \otimes \gamma_B}} = \nonumber \\
+	&\frac{\W[\bmx_A]{\rho_A}\W[\bmx_B]{\rho_B}}{\W[\bmx_A]{\gamma_A}\W[\bmx_B]{\gamma_B}} = \widetilde{\rm{W}}_{\rho_A | \gamma_A}(\bmx_A)\widetilde{\rm{W}}_{\rho_B  | \gamma_B}(\bmx_B),
+\end{align}
+so result holds for this too \nick{FIX SECTION}.
 
@@
 \end{proof}
+
+\subsection{First elbow location}
+\label{app:first_elb_loc}
+
+Here, we show that the horizontal location of the first elbow is lower for an initial state compared to the target state for a valid distillation process ($n > n'$).
+\begin{enumerate}
+	\item $\rm{(C1)} \rightarrow \rm{(C1)}$. 
+	It is always true that $e^{-\beta E_0} / \Z_\beta \leq 1$, so
+	\begin{align*}
+		x_0 &= \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^n = \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n-n'} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} \\
+		&< \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} = x_0'		
+	\end{align*}
+	\item $\rm{(C2)} \rightarrow \rm{(C1)}$.
+	It is always true that
+	\begin{align*}
+		&\Z_\beta^{n-n'} > (e^{-\beta E_{\rm{max}}})^{n-n'} = e^{-\beta (n-n') E_{\rm{max}}}, \text{ so} \\
+		x_0 &= \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^n = \dfrac{e^{-\beta(n E_{\rm{max}} - n' E_0)}}{\Z_\beta^{n-n'}} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} \\
+		&< \dfrac{e^{-\beta(n E_{\rm{max}} - n' E_0)}}{e^{-\beta (n-n') E_{\rm{max}}}} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} \\
+		&= e^{-\beta n' (E_{\rm{max}} - E_0)} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} \\
+		&\leq \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} = x_0'.
+	\end{align*}
+	\item $\rm{(C2)} \rightarrow \rm{(C2)}$.
+	It is always true that $e^{-\beta E_{\rm{max}}} / \Z_\beta \leq 1$, so
+	\begin{align*}
+		x_0 &= \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^n = \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^{n-n'} \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^{n'} \\
+		&\leq \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^{n'} = x_0'	
+	\end{align*}
+\end{enumerate}

### 2021-03-22 magic_paper.tex
Tidied up stabilizer bound proof

@@
 \end{equation}
-and is called the \emph{Gibbs-rescaled} distribution of $\rho$ with respect to $\sigma$.
+and is called the \emph{rescaled} distribution of $\rho$ with respect to $\sigma$.
 
@@
 	We may use the vector notation of the Wigner distributions $\bmw(\rho)$ and $\bmw(\sigma)$.
-	We choose the component indexing so that the Gibbs-rescaled distribution 
+	We choose the component indexing so that the rescaled distribution 
 	\begin{equation}
@@
 In the following result, all copies $n, n', n - n'$ are even with $n > n'$, and $\epsilon'=0$, but the bounds are easily generalised to odd numbers of copies and $\epsilon'$ such that $0 < \epsilon' < \epsilon$.
-Finally, we assume a range of initial noise levels, $\epsilon \leq 3/7$  \nick{higher than all threshold values in literature CITE}, so that the largest Wigner component of the 1-copy noisy magic state is negative.
-
-Given this context, we now provide the following result, which depends on the free energy $F_\beta$ of state $\sigma$,
+Finally, we assume a range of initial noise levels, $\epsilon \leq 3/7$, so that the largest Wigner component of the 1-copy noisy magic state is negative.
+The numerical value of $3/7$ is higher than corresponding values of relevant existing distillation protocol error thresholds~\cite{cit:bravyi,cit:prakash}.
+
+Given this context, we now provide the following result on bounding the distillation rate $R = R(\epsilon, \epsilon', \beta) \coloneqq \frac{n'}{n}$ of the process in~\cref{eq:stdist}.
+The bounds depend on the free energy $F_\beta$ of state $\sigma$,
 \begin{equation}
@@
 This is apparent by simple numerical calculations on the entirety of the curves.
-The existing bounds follow by considering the dominant terms in the rescaled Wigner distribution and do not, for example, take into account the Lorenz curve's peak structure. 
+Specifically, the existing bounds follow by considering the dominant terms in the rescaled Wigner distribution and do not, for example, take into account the Lorenz curve's peak structure. 
 Finally, it is striking that we obtain a Landauer-like condition with a characteristic temperature $kT_\star \ln 2 = E_2 - E_0$, where $kT_\star = \beta_\star^{-1}$. 
@@
 \begin{proof}
-	We provide an outline of the proof here, with all technical details included in \nick{the appendix}.\\
-
-The Wigner distribution of $\epsilon$-noisy Strange state can be written as 
+	We provide an outline of the proof here, with all technical details included in~\cref{app:lcst_technical}.\\
+
+The Wigner distribution of the $\epsilon$-noisy Strange state can be written as 
 \begin{equation}
@@
 \end{equation}
-at the 8 phase space points $\bmx \in \cal{P}_d[3] \setminus \{\bmo\}$ and a negative component
+at the 8 phase space points $\bmx \in \cal{P}_3 \setminus \{\bmo\}$ and a negative component
 \begin{equation}
@@
 
-We are interested in studying Strange state distillation in general thermal fragments $\O_{\gamma_\beta}$ where the thermal state is
-\begin{equation}
-	\gamma_\beta \coloneqq \frac{e^{-\beta H}}{\Z_\beta},
-\end{equation}
-with partition function $\Z_\beta = \tr \big[e^{-\beta H} \big]$, defined in terms of some Hamiltonian $H$ and temperature $\beta^{-1}$.
-
-To this end, consider the general qutrit Hamiltonian
-\begin{equation}
-	H = E_0 \ketbra{0} + E_1 \ketbra{1} + E_2 \ketbra{2},
-\end{equation}
-where the energy eigenbasis coincides with the computational basis.
-We have that energy eigenvalues $E_i \geq 0$, but impose no order between them.
-We denote the highest energy eigenvalue as
-\begin{equation}
-	E_{\rm{max}} \coloneqq \max{\{E_0, E_1, E_2\}}.
-\end{equation}
-
-The thermal state associated with this Hamiltonian is
-\begin{align}
-	\gamma_\beta &= \frac{e^{-\beta H}}{\Z_\beta} = \frac{e^{-\beta \sum\limits_{k=0}^2 E_k \ketbra{k}}}{\Z_\beta} \\
-	&= \frac{e^{-\beta E_0}}{\Z_\beta}\ketbra{0} + \frac{e^{-\beta E_1}}{\Z_\beta}\ketbra{1} + \frac{e^{-\beta E_2}}{\Z_\beta}\ketbra{2},
-\end{align}
-where $\Z_\beta = e^{-\beta E_0} + e^{-\beta E_1} + e^{-\beta E_2}$.
+Let $\displaystyle \sigma = e^{-\beta H} / \Z_\beta$ be a stabiliser state, where $\beta \geq 0$ and $H = E_0 \ketbra{0} + E_1 \ketbra{1} + E_2 \ketbra{2}$, with $E_k \geq 0$.
+Its eigen-decomposition can be written as 
+\begin{equation}
+	\sigma = \frac{e^{-\beta E_0}}{\Z_\beta} \ketbra{\varphi_0} + \frac{e^{-\beta E_1}}{\Z_\beta} \ketbra{\varphi_1} + \frac{e^{-\beta E_2}}{\Z_\beta} \ketbra{\varphi_2},
+\end{equation}
+where $\{\ket{\varphi_k}\}$ are pure, orthonormal stabiliser states. 
+Therefore, there exists a Clifford operation that maps $\sigma$ to $\gamma_\beta$, where 
+\begin{equation}
+\gamma_\beta = \frac{e^{-\beta E_0}}{\Z_\beta} \ketbra{0} + \frac{e^{-\beta E_1}}{\Z_\beta} \ketbra{1} + \frac{e^{-\beta E_2}}{\Z_\beta} \ketbra{2}.
+\end{equation}
+\nick{Prove this carefully}
+
+This Clifford operation permutes the Hamiltonian eigenvalues on the phase space, so that the negative component of $\rho_S(\epsilon)$ can lie on the same point on the phase space as any of the eigenvalues.
+For this reason, we impose no order between the eigenvalues, but simply choose $E_0$ as the eigenvalue that is associated with the state negativity and denote the highest energy by $E_{\rm{max}} \coloneqq \max{\{E_0, E_1, E_2\}}$.
 
@@
 \end{align}
-for all $\bmx \in \cal{P}_d[3]$. 
-All Wigner components are strictly positive, therefore the pre-order $\prec_{\gamma_\beta}$ is well defined.
-
-Let $\sigma = \frac{1}{\Z} e^{-\beta H}$ be a stabiliser state, which is given in its eigen-decomposition as 
-\begin{equation}
-\sigma = \frac{1}{\Z} ( e^{-\beta E_0} |\varphi_0\>\< \varphi_0| + e^{-\beta E_1} |\varphi_1\>\< \varphi_1| + e^{-\beta E_2} |\varphi_2\>\< \varphi_2| ),
-\end{equation}
-where $\{|\varphi_k\>\}$ are pure, orthonormal stabiliser states.
-Therefore the exist a Clifford operation that takes $|\varphi_k\> \rightarrow |k\>$, with the effect of permuting the negative component of $\rho_S(\epsilon)$ in the discrete phase space.
-
-We are now in a position to consider the Strange state distillation process
-\begin{equation}\label{eq:msd_thermal}
-		\rho_{\rm{S}}(\epsilon)^{\otimes n} \xrightarrow{\E \in \O_{\gamma_\beta}} \rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \gamma_\beta^{\otimes (n-n')},
-\end{equation}
-where we are allowed to tensor in copies of the thermal state $\gamma_\beta$, since it is free in fragment $\O_{\gamma_\beta}$.
-
-Our aim is to obtain a distillation bound for~\cref{eq:msd_thermal} which depends on variables $n, n', \epsilon, \epsilon'$ as well as $\beta$.
+for all $\bmx \in \cal{P}_3$. 
+All Wigner components are strictly positive, therefore the pre-order $\prec_{\gamma_\beta}$ is always well-defined.
+
+Our aim is to obtain a distillation bound for~\cref{eq:stdist} which depends on variables $n, n', \epsilon, \epsilon'$ as well as $\beta$.
 In the analysis that follows, we drop obvious variable dependencies for clarity.
 
-Consider a general $\epsilon$-noisy Strange state $\rho_{\rm{S}}$ in a thermal fragment $\O_{\gamma}$.
-We can construct the Gibbs-rescaled distribution 
-\begin{equation}
-	\widetilde{\rm{W}}_{\rho_{\rm{S}}|\gamma}(\bmx) \coloneqq \frac{\W[\bmx]{\rho_{\rm{S}}}}{\W[\bmx]{\gamma}},
-\end{equation}
-Notice that the Gibbs-rescaled distribution is multiplicative in general,
-\begin{align}
-	&\widetilde{\rm{W}}_{\rho_A \otimes \rho_B | \gamma_A \otimes \gamma_B}(\bmx_A \oplus \bmx_B) = \frac{\W[\bmx_A \oplus \bmx_B]{\rho_A \otimes \rho_B}}{\W[\bmx_A \oplus \bmx_B]{\gamma_A \otimes \gamma_B}} = \nonumber \\
-	&\frac{\W[\bmx_A]{\rho_A}\W[\bmx_B]{\rho_B}}{\W[\bmx_A]{\gamma_A}\W[\bmx_B]{\gamma_B}} = \widetilde{\rm{W}}_{\rho_A | \gamma_A}(\bmx_A)\widetilde{\rm{W}}_{\rho_B  | \gamma_B}(\bmx_B).
-\end{align}
-
-We construct component and multiplicity vectors based on the distinct components of the Gibbs-rescaled distribution,
-\begin{align}
-	\bmm &\coloneqq (1,2,3,3) \\
-	\bmw(\rho_{\rm{S}}) &\coloneqq (-v, u, u, u) \\
-	\bmw(\gamma) &\coloneqq \frac{1}{3\Z} \left( e^{-\beta E_0}, e^{-\beta E_0}, e^{-\beta E_1}, e^{-\beta E_2} \right) \\
-	\bmw(\rho_{\rm{S}} | \gamma) &\coloneqq 3\Z \left( -v e^{\beta E_0}, u e^{\beta E_0}, u e^{\beta E_1}, u e^{\beta E_2} \right) \label{eq:bmw_rescaled}
-\end{align}
-
-There are four distinct values of the Gibbs-rescaled distribution on the phase space, with the negative Strange component $-v$ corresponding to energy $E_0$ as illustrated in the phase space split in~\cref{fig:pd_split_thermal}.
-The Wigner-component vectors $\bmw(\rho_{\rm{S}}), \bmw(\gamma)$ are then constructed so as to match the four phase space regions.
+We construct the Strange state rescaled distribution 
+\begin{equation}
+	\widetilde{\rm{W}}_{\rho_{\rm{S}}|\gamma}(\bmx) \coloneqq \frac{\W[\bmx]{\rho_{\rm{S}}}}{\W[\bmx]{\gamma}}.
+\end{equation}
+There are four distinct values of the rescaled distribution on the phase space, as illustrated in the phase space diagram in~\cref{fig:pd_split_thermal}.
 \begin{figure}[h]
@@
     \includegraphics[scale=0.5]{figs/pd_split_thermal.pdf}
-    \caption{\textbf{Qutrit phase space regions with different Gibbs-rescaled values.}
-    The Gibbs-rescaled distribution attains a unique value in each region $1,X,Y,Z$, given by~\cref{eq:bmw_rescaled} respectively.
+    \caption{\textbf{Qutrit phase space regions with different rescaled values.}
+    The rescaled distribution attains a unique value in each of the four regions, given by $3\Z \times$ the value depicted in the region, according to~\cref{eq:bmw_rescaled}.
     }
@@
 
-For notational convenience, we define the index vector
-\begin{equation}
-	\bmq \coloneqq (n-\alpha,i,j,k),
-\end{equation}
-where $i,j,k$ are non-negative integers and
-\begin{equation*}
-	\alpha \coloneqq i+j+k \leq n.
-\end{equation*}
-The Wigner components of the $n$-copy distributions are now readily provided by~\cref{lem:ncopycomponents}.
-Firstly, the $n$-copy multiplicity is given according to~\cref{eq:M} by
-\begin{equation}
-	m_{ijk} \coloneqq M_{\bmq} = \frac{n!}{i!j!k!(n-\alpha)!} 2^i 3^j 3^k.
-\end{equation}
-The distribution values that correspond to the same index $\bmq$ are given according to~\cref{eq:W} by
-\begin{align}
-	w(\rho_{\rm{S}})_{ijk} &= (-v)^{n-\alpha} u^{\alpha} \\
-	w(\gamma)_{ijk} &= (3\Z)^{-n} e^{-\beta (n-\alpha)E_0} e^{-\beta ( i E_0 + j E_1 + k E_2 )} \\
-	w(\rho_{\rm{S}} | \gamma)_{ijk} &= (3\Z)^{n} (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )}
-\end{align}
-
-In order to construct the $n$-copy Lorenz curve of a Strange state in a thermal fragment we need to sort the components of the $n$-copy Gibbs-rescaled distribution, $w(\rho_{\rm{S}} | \gamma)_{ijk}$ in decreasing order.
-In particular, to find the coordinates of the first elbow $(x_0, L_0)$, we need to evaluate the greatest component,
+The component values and multiplicities of the relevant distributions in the four distinct regions are summarised by the following component and multiplicity vectors,
+\begin{align}
+	\bmm &\coloneqq (1,2,3,3), \\
+	\bmw(\rho_{\rm{S}}) &\coloneqq (-v, u, u, u), \\
+	\bmw(\gamma) &\coloneqq \frac{1}{3\Z} \left( e^{-\beta E_0}, e^{-\beta E_0}, e^{-\beta E_1}, e^{-\beta E_2} \right), \\
+	\bmw(\rho_{\rm{S}} | \gamma) &\coloneqq 3\Z \left( -v e^{\beta E_0}, u e^{\beta E_0}, u e^{\beta E_1}, u e^{\beta E_2} \right). \label{eq:bmw_rescaled}
+\end{align}
+
+Using this notation, the component values and multiplicities of the $n$-copy distributions can be readily provided by~\cref{lem:ncopycomponents} in~\cref{app:cmpairs}.
+They are parametrised by three independent components $i,j,k$, with sum $\alpha \coloneqq i+j+k \leq n$.
+Then, the $n$-copy multiplicity is given by
+\begin{equation}
+	m_{ijk} = \frac{n!}{i!j!k!(n-\alpha)!} 2^i 3^j 3^k,
+\end{equation}
+while the distribution values that correspond to the same index triplet $(i,j,k)$ are given by
+\begin{align}
+	w(\rho_{\rm{S}})_{ijk} &= (-v)^{n-\alpha} u^{\alpha}, \\
+	w(\gamma)_{ijk} &= (3\Z)^{-n} e^{-\beta (n-\alpha)E_0} e^{-\beta ( i E_0 + j E_1 + k E_2 )}, \\
+	w(\rho_{\rm{S}} | \gamma)_{ijk} &= (3\Z)^{n} (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )}.
+\end{align}
+
+In order to construct the $n$-copy Lorenz curve $\lc{\rho_{\rm{S}}^{\otimes n}}{\gamma}$ we need to sort the components of the $n$-copy rescaled distribution, $w(\rho_{\rm{S}} | \gamma)_{ijk}$ in decreasing order.
+In particular, to find the coordinates of the first elbow $(x_0, L_0)$, we need to evaluate the maximum rescaled component,
 \begin{align}
@@
 Notice that for $0 \leq \epsilon \leq 3/7$, we have $v \geq u$. 
-We assume that $n$ is even, so we then need the sum $\alpha = i+j+k$ to be even, so that the expression is positive.
-
-Given an even value $\alpha$ for the sum, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_0}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
+We assume that $n$ is even, so that we need the sum $\alpha = i+j+k$ to be even for the expression to be positive. 
+The following analysis is similar if $n$ is chosen to be odd.
+
+Given an even value for the sum $\alpha$, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_0}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
 Hence, we have
@@
 	&\bmw(\rho_{\rm{S}} | \gamma)_{\rm{max}} = \nonumber\\
-	&(3\Z)^{n} \max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ v^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta \alpha E_{\rm{max}}} \Big\}} =  \nonumber\\
-	&(3\Z)^{n} v^n e^{n\beta E_0}\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}
-\end{align}
-If the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than $1$ then the maximum occurs at $\alpha=0$, and otherwise the maximum occurs at $\alpha = n$.
-To determine this transition we set
-\begin{equation}
-	\frac{u(\epsilon)}{v(\epsilon)} e^{\beta (E_{\rm{max}} - E_0)} = 1.
-\end{equation}
-This can be rewritten as
+	&(3\Z)^{n} v^n e^{n\beta E_0}\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}.
+\end{align}
+If the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than $1$ then the maximum occurs at $\alpha=0$, otherwise the maximum occurs at $\alpha = n$. To determine this transition we set
 \begin{equation}\label{eq:noise_transition}
-	\frac{3-\epsilon}{6-8\epsilon} e^{\beta (E_{\rm{max}} - E_0)} = 1.
-\end{equation}
-The function $(3-\epsilon) / (6-8\epsilon)$ is increasing in $\epsilon$, achieving its minimum value $1/2$ at $\epsilon = 0$ and its maximum value $1$ at $\epsilon = 3/7$.
+	\frac{u(\epsilon)}{v(\epsilon)} e^{\beta (E_{\rm{max}} - E_0)} \coloneqq \frac{3-\epsilon}{6-8\epsilon} e^{\beta (E_{\rm{max}} - E_0)} = 1.
+\end{equation}
 We want to find in which cases there exists a threshold noise level $\epsilon_\star$ at which the transition in~\cref{eq:noise_transition} occurs.
-
-For the case $E_{\rm{max}} = E_0$, namely when the negative component overlaps the highest energy state distribution, this threshold is constant in temperature and given by $\epsilon_{\star} = 3/7$.
-
-There is a threshold temperature value $\beta_\star$ given by
+If $E_{\rm{max}} = E_0$, namely if the state negativity lies in the same phase space region as the highest energy, this threshold is constant in temperature and given by $\epsilon_{\star} = 3/7$. 
+Otherwise, there is a threshold temperature value $\beta_\star$ given by
 \begin{equation}
@@
 \end{equation}
-Below the threshold temperature, $0 \leq \beta \leq \beta_\star$, the transition is well defined and the threshold noise level at which it occurs is given by
+Below the threshold, $0 \leq \beta \leq \beta_\star$, the transition is well defined and the threshold noise level at which it occurs is given by
 \begin{equation}
@@
 This encompasses the case $E_{\rm{max}} = E_0$.
-
-We note that the threshold noise level $\epsilon_\star$ becomes $0$ when $\beta = \beta_\star$, namely the difference between the maximum energy level and the level associated with the state negativity is equal to the energy extracted from a single particle Szilard's engine,
-\begin{equation}
-	E_{\rm{max}} - E_0 = kT_{\star} \ln2.
-\end{equation}
-
 For $\beta > \beta_\star$, we have
@@
 \end{equation*}
-so there is no transition and the threshold noise level remains $\epsilon_\star = 0$.
-
-The maximum value of the Gibbs-rescaled distribution finally is
-\begin{equation}
+so there is no transition and we set $\epsilon_\star = 0$.
+
+The maximum rescaled component can then be expressed as
+\begin{equation*}
 \bmw(\rho_{\rm{S}} | \gamma)_{\rm{max}} =
@@
 	\end{cases}
-\end{equation}
-Case $\rm{(C1)}$ corresponds to $(i,j,k) = (0,0,0)$, while case $\rm{(C2)}$ corresponds to the  the conditions 
+\end{equation*}
+Case $\rm{(C1)}$ corresponds to $(i,j,k) = (0,0,0)$, so the multiplicity is $m_{000} = 1$ and the corresponding Wigner components are $\bmw(\rho_{\rm{S}})_{000}, \bmw(\gamma)_{000}$. 
+Case $\rm{(C2)}$ corresponds to
 \begin{equation}
@@
 \end{equation}
-Note that if $E_{\rm{max}} = E_0$, we get $\epsilon_{\star} = 3/7$ and $\rm{(C1)}$ holds for all $\epsilon$ and $\beta$.
-Assuming $E_{\rm{max}} > E_0$, we get the cases:
-\begin{itemize}
-	\item $\beta = 0$. Then, $\epsilon_{\star} = 3/7$ and $\rm{(C1)}$ holds for all noise levels $\epsilon$.
-	This is the unital fragment.
-	\item $0 < \beta \leq \beta_{\star}$. Then, $0 \leq \epsilon_{\star} < 3/7$ and $\rm{(C1)}$ holds for $\epsilon \leq \epsilon_{\star}$, while $\rm{(C2)}$ holds for $\epsilon \geq \epsilon_{\star}$.
-	\item $\beta > \beta_{\star}$. Then, $ \epsilon_{\star} = 0$ and $\rm{(C2)}$ holds for all $\epsilon$.
-\end{itemize}
-
-In $\rm{(C1)}$, the multiplicity is $m_{000} = 1$ and the corresponding Wigner components are $\bmw(\rho_{\rm{S}})_{000}, \bmw(\gamma)_{000}$.
-In $\rm{(C2)}$, we have $E_{\rm{max}} = E_1$ ($E_{\rm{max}} = E_2$), the multiplicity is $m_{0n0} = 3^n$ ($m_{00n} = 3^n$) and the corresponding Wigner components are $\bmw(\rho_{\rm{S}})_{0n0}, \bmw(\gamma)_{0n0}$ ($\bmw(\rho_{\rm{S}})_{00n}, \bmw(\gamma)_{00n}$).
-The first elbow coordinate expression can finally be expressed as
+and we have $E_{\rm{max}} = E_1$ ($E_{\rm{max}} = E_2$), so the multiplicity is $m_{0n0} = 3^n$ ($m_{00n} = 3^n$) and the corresponding Wigner components are $\bmw(\rho_{\rm{S}})_{0n0}, \bmw(\gamma)_{0n0}$ ($\bmw(\rho_{\rm{S}})_{00n}, \bmw(\gamma)_{00n}$).
+
+The first elbow coordinate can finally be derived as
 \begin{equation}\label{eq:first_elb_coords}
@@
 \end{equation}
-
-Consider the distillation process in~\cref{eq:msd_thermal},
-\begin{equation*}
-		\rho_{\rm{S}}(\epsilon)^{\otimes n} \xrightarrow{\E \in \O_{\gamma_\beta}} \rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \gamma_\beta^{\otimes (n-n')},
-\end{equation*}
-with $n > n'$ and $\epsilon > \epsilon'$.
-A necessary distillation constraint can be defined at the location $x_\star = x_0$ of the initial state's first elbow, expressed as
+\null\\
+
+A necessary distillation constraint for the process in~\cref{eq:stdist} can be defined at the location $x_\star = x_0$ of the initial state's first elbow,
 \begin{equation}\label{eq:first_elbow_constraint}
@@
 The Lorenz curves of the initial and target states may each be described by either $\rm{(C1)}$ or $\rm{(C2)}$, depending on the physical parameters $\epsilon, \epsilon', \beta$.
-Specifically, we can get three scenarios:
+Specifically, we have three scenarios:
 \begin{enumerate}
-	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} = E_0$ OR $E_{\rm{max}} > E_0$, $\beta < \beta_{\star}$ and $\epsilon' < \epsilon  \leq \epsilon_{\star}$.
+	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} = E_0$ or $E_{\rm{max}} > E_0$, $\beta < \beta_{\star}$ and $\epsilon' < \epsilon  \leq \epsilon_{\star}$.
 	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} > E_0$, $\beta < \beta_{\star}$ and $\epsilon' \leq \epsilon_{\star} < \epsilon$.
-	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $E_{\rm{max}} > E_0$, $\beta \geq \beta_{\star}$.
+	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $E_{\rm{max}} > E_0$, $\beta < \beta_{\star}$ and $\epsilon_{\star} \leq \epsilon' < \epsilon$ or $E_{\rm{max}} > E_0$, $\beta \geq \beta_{\star}$.
 \end{enumerate}
@@
 
-In all three scenarios, it is simple to check that the first elbow of the initial state is always located closer to $0$ compared to the first elbow of the target state, $x_0 \leq x_0'$:
+In all three scenarios, it is simple to check that the initial state's first elbow is always located to the left (closer to $0$) of the target state's first elbow, $x_0 \leq x_0'$, as proven in~\cref{app:first_elb_loc}.
+The prime indicates target state coordinates.
+We can thus find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star = x_0$ by interpolating between the origin and the target state's first elbow, 
+\begin{equation}\label{eq:constraint_deriv_temp}
+	L'_\star = \frac{x_\star}{x'_0}L'_0.
+\end{equation}
+Condition~\cref{eq:first_elbow_constraint} reads that we need $L_0 = L_\star \geq L_\star'$.
+Therefore, restricting to the first elbow, the necessary distillation condition in~\cref{eq:first_elbow_constraint} simply becomes
+\begin{equation}\label{eq:first_elb_bound}
+	\frac{L_0}{x_0} \geq \frac{L_0'}{x_0'}.
+\end{equation}
+Involving more elbows gives stricter, but more convoluted necessary distillation constraints.
+
+We are now in a position to compute analytical distillation bounds for the distillation rate $R = R(\epsilon, \epsilon', \beta) \coloneqq n'/n$, based on the first elbow constraint for all three possible scenarios.
+Substituting coordinates from~\cref{eq:first_elb_coords} appropriately in~\cref{eq:first_elb_bound}, we get the following necessary conditions:
 \begin{enumerate}
 	\item $\rm{(C1)} \rightarrow \rm{(C1)}$.
-	It is always true that $e^{-\beta E_0} / \Z_\beta \leq 1$, so
-	\begin{align*}
-		x_0 &= \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^n = \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n-n'} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} \\
-		&< \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} = x_0'		
-	\end{align*}
-	\item $\rm{(C2)} \rightarrow \rm{(C1)}$.
-	It is always true that
-	\begin{align*}
-		&\Z_\beta^{n-n'} > (e^{-\beta E_{\rm{max}}})^{n-n'} = e^{-\beta (n-n') E_{\rm{max}}}, \text{ so} \\
-		x_0 &= \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^n = \dfrac{e^{-\beta(n E_{\rm{max}} - n' E_0)}}{\Z_\beta^{n-n'}} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} \\
-		&< \dfrac{e^{-\beta(n E_{\rm{max}} - n' E_0)}}{e^{-\beta (n-n') E_{\rm{max}}}} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} \\
-		&= e^{-\beta n' (E_{\rm{max}} - E_0)} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} \\
-		&\leq \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} = x_0'.
-	\end{align*}
-	\item $\rm{(C2)} \rightarrow \rm{(C2)}$.
-	It is always true that $e^{-\beta E_{\rm{max}}} / \Z_\beta \leq 1$, so
-	\begin{align*}
-		x_0 &= \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^n = \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^{n-n'} \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^{n'} \\
-		&\leq \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^{n'} = x_0'	
-	\end{align*}
+
+\begin{align}
+	R \leq \frac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_0 - F_\beta)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F_\beta)}.
+\end{align}
+Equivalently, we require
+\begin{align}
+	\epsilon \leq \frac{3}{4} - \frac{3}{4} \left( 1 - \frac{4}{3}\epsilon' \right)^{R} \left( \frac{e^{-\beta E_0}}{\Z_\beta} \right)^{1 - R}	.
+\end{align}
+
+	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} > E_0$, $\beta < \beta_{\star}$ and $\epsilon' \leq \epsilon_{\star} < \epsilon$.
+
+\begin{align}
+	R \leq \frac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F_\beta)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F_\beta)}
+\end{align}
+Equivalently, we require
+\begin{align}
+	\epsilon &\leq 3 - 6 \left( 1 - \frac{4}{3}\epsilon' \right)^{R} \frac{e^{-\beta E_{\rm{max}}} e^{R\beta E_0}}{\Z_\beta^{1-R}}	
+\end{align}
+
+	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $E_{\rm{max}} > E_0$, $\beta \geq \beta_{\star}$.
+
+\begin{align}
+	R \leq \frac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F_\beta)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F_\beta)}
+\end{align}
+Equivalently, we require
+\begin{align}
+	\epsilon &\leq 3 - 6 \left( \frac{1}{2} - \frac{1}{6}\epsilon' \right)^{R} \left( \frac{e^{-\beta E_{\rm{max}}}}{\Z_\beta} \right)^{1 - R}.
+\end{align}
 \end{enumerate}
-We can thus find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$ by interpolating between the origin and the target state's first elbow, 
-\begin{equation}\label{eq:constraint_deriv_temp}
-	L'_\star = \frac{x_\star}{x'_0}L'_0.
-\end{equation}
-We need $L_0 \geq L_\star'$. Therefore, restricting to the first elbow, the necessary distillation condition in~\cref{eq:first_elbow_constraint} simply becomes
-\begin{equation}\label{eq:first_elb_bound}
-	\frac{L_0}{x_0} \geq \frac{L_0'}{x_0'}.
-\end{equation}
-Involving more elbows gives stricter, but more convoluted necessary distillation constraints.
-
-We now compute distillation bounds based on the first elbow constraint in the three possible scenarios. \ddd{[Does anything special happen if we have degeneracies in energy? ]}
-\nick{If we have degeneracies, basically the Gibbs-rescaled distribution in~\cref{eq:bmw_rescaled} has some equal components, so Lorenz curves have fewer elbows, but because the first elbow constraint boils down to a ratio comparison~\cref{eq:first_elb_bound} it doesn't change the analysis}
-We express them in terms of the free energy of thermal state $\gamma_\beta$ denoted by
-\begin{equation}
-	F_\beta \coloneqq \tr[\gamma_\beta H] + \beta^{-1} \tr[\gamma_\beta \ln{\gamma_\beta}] = -\beta^{-1} \ln{\Z_\beta}.
-\end{equation}
-Substituting coordinates from~\cref{eq:first_elb_coords} appropriately in~\cref{eq:first_elb_bound}, we get the following necessary conditions:
-\begin{enumerate}
-	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} = E_0$ OR $E_{\rm{max}} > E_0$, $\beta < \beta_{\star}$ and $\epsilon' < \epsilon  \leq \epsilon_{\star}$.
-
-\begin{align}
-	\frac{n}{n'} &\geq \frac{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F_\beta)}{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_0 - F_\beta)}, \text{ or} \\
-	\epsilon &\leq \frac{3}{4} - \frac{3}{4} \left( 1 - \frac{4}{3}\epsilon' \right)^{\frac{n'}{n}} \left( \frac{e^{-\beta E_0}}{\Z_\beta} \right)^{1 - \frac{n'}{n}}	
-\end{align}
-This leads to an upper bound for the distillation rate $R=n'/n$ of pure Strange states ($\epsilon' = 0$),
-\begin{equation}
-	R \leq R(\epsilon, \beta) \coloneqq 1 - \frac{\ln{\left( \frac{1}{1 - \frac{4}{3}\epsilon} \right)}}{\beta (E_0 - F_\beta)},
-\end{equation}
-
-	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} > E_0$, $\beta < \beta_{\star}$ and $\epsilon' \leq \epsilon_{\star} < \epsilon$.
-
-\begin{align}
-	\frac{n}{n'} &\geq \frac{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F_\beta)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F_\beta)}, \text{ or} \\
-	\epsilon &\leq 3 - 6 \left( 1 - \frac{4}{3}\epsilon' \right)^{\frac{n'}{n}} \frac{e^{-\beta E_{\rm{max}}} e^{\frac{n'}{n}\beta E_0}}{\Z_\beta^{1-\frac{n'}{n}}}	
-\end{align}
-This leads to an upper bound for the distillation rate $R=n'/n$ of pure Strange states ($\epsilon' = 0$),
-\begin{equation}
-	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\left(\frac{1}{1-\frac{1}{3}\epsilon} \right)} + (E_{\rm{max}} - E_0)(\beta_{\star} - \beta)}{\beta (E_0 - F_\beta)},
-\end{equation}
-
-	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $E_{\rm{max}} > E_0$, $\beta \geq \beta_{\star}$.
-
-\begin{align}
-	\frac{n}{n'} &\geq \frac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F_\beta)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F_\beta)}, \text{ or} \\
-	\epsilon &\leq 3 - 6 \left( \frac{1}{2} - \frac{1}{6}\epsilon' \right)^{\frac{n'}{n}} \left( \frac{e^{-\beta E_{\rm{max}}}}{\Z_\beta} \right)^{1 - \frac{n'}{n}}	
-\end{align}
-This leads to an upper bound for the distillation rate $R=n'/n$ of pure Strange states ($\epsilon' = 0$),
-\begin{equation}
-	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\left(\frac{1}{1-\frac{1}{3}\epsilon} \right)}}{-\ln{2} + \beta (E_{\rm{max}} - F_\beta)},
-\end{equation}
-\end{enumerate}
-
-Consider pure Strange state distillation at high temperatures, $\beta \leq \beta_{\star}$.
-Depending on the noise level of the initial state, we have either a $\rm{(C1)} \rightarrow \rm{(C1)}$ or a $\rm{(C2)} \rightarrow \rm{(C1)}$ scenario.
-
-At every $\beta > 0$, the rates indicate a transition at $\epsilon_{\star}$.
-As $\beta$ increases, the rate becomes stricter.
-At the high temperature limit, $\beta \rightarrow 0$, we get $\beta F_\beta \rightarrow -\ln{3}$, and we retrieve the unital fragment bound,
-\begin{equation}
-	R(\beta) \xrightarrow{\beta \rightarrow 0} \frac{\ln{(3-4\epsilon)}}{\ln{3}}.
-\end{equation}
-
-Consider pure Strange state distillation at low temperatures, $\beta \rightarrow \infty$.
-Independently of the noise level of the initial state, we have a $\rm{(C2)} \rightarrow \rm{(C2)}$ scenario.
-
-As $\beta$ increases, the rate becomes looser.
-At the zero temperature limit, $F_\beta$ tends to zero, so $R(\epsilon, \beta) \xrightarrow{\beta \rightarrow \infty} 1$.
+
+Substituting $\epsilon' = 0$ leads to the expressions of the theorem statement.
 

### 2021-03-22 notes/notes.tex
Tidied up stabilizer bound proof

@@
 
+Whether we are dealing with $\rm{(C1)}$ or $\rm{(C2)}$ depends on the physical parameters $\beta$ and $\epsilon$ as follows:
+\begin{itemize}
+	\item $\beta = 0$. Then, $\epsilon_{\star} = 3/7$ and $\rm{(C1)}$ holds for all noise levels $\epsilon$.
+	This is the unital fragment.
+	\item $0 < \beta \leq \beta_{\star}$. Then, $0 \leq \epsilon_{\star} < 3/7$ and $\rm{(C1)}$ holds for $\epsilon \leq \epsilon_{\star}$, while $\rm{(C2)}$ holds for $\epsilon \geq \epsilon_{\star}$.
+	\item $\beta > \beta_{\star}$. Then, $ \epsilon_{\star} = 0$ and $\rm{(C2)}$ holds for all $\epsilon$.
+\end{itemize}
+
 \end{document}

### 2021-03-22 magic_paper.tex
Tidied up unital and stabilizer fragment bound sections

@@
 
-\nick{We can skip mana and just discuss sum-negativity}
 One of the most fundamental and commonly used magic monotones is the \emph{mana} of a state~\cite{cit:veitch2}, defined as
@@
 \end{equation}
-where the \emph{sum-negativity} ($\rm{sn}$)~\cite{cit:veitch2} is the sum of the negative components in $\W{\rho}$,
+where the \emph{sum-negativity}~\cite{cit:veitch2} is the sum of the negative components in $\W{\rho}$,
 \begin{equation}
@@
 The correspondence between the phase space and pure vector representations of the Wigner distribuition is discussed more in~\cref{app:cmpairs}.
+\nick{In the rest of the paper we will be using the two notations interchangeably.}
 
@@
 
-Normalisation of the Wigner distribution \nick{REF} ensures that for all quantum states $\rho$, $\lc{\rho}{\sigma}(x) \geq 0$ and $\lc{\rho}{\sigma}(1) = 1$.
+Normalisation of the Wigner distribution ensures that for all quantum states $\rho$, $\lc{\rho}{\sigma}(x) \geq 0$ and $\lc{\rho}{\sigma}(1) = 1$.
 We stress that $0 \leq \lc{\rho}{\sigma}(x) \leq 1$ for all $x \in [0,1]$ if and only if $\rho$ is a positive Wigner state.
@@
 In fact, there are only as many independent constraints as there are elbows in the Lorenz curve of the target state as shown in~\cref{app:lc_constraints}.
-However, in principle any one inequality defined at some location $x$ provides a valid constraint leading to some upper distillation bound, and the more locations one considers, the stricter the bound is.
-
-The area $\A_\sigma(\rho)$ between the curve $L_{\rho|\sigma}$ and the line $y=1$ is a resource monotone in the $\sigma$--fragment. 
-This is clear because for any state conversion like~\cref{eq:sigma_conv}, the Lorenz curve $L_{\tau|\sigma}$ is lower than $L_{\rho|\sigma}$, hence $\A_\sigma(\E(\rho)) \leq \A_\sigma(\rho)$.
-The exact form of the monotone is given in~\cref{app:areamono}.
-\nick{should we include the area? Have a look at~\cref{app:areamono}}
-
-We can now show that the magic monotone of mana, and equivalently the sum-negativity of a quantum state, can be viewed as a feature of majorisation, and independent of the particular $\sigma$--fragment one works in.
-In fact, our current setting makes it apparent that mana provides a weaker condition than majorisation for all magic state interconversions.
+However, in principle any one location $x$ provides a valid constraint leading to some upper distillation bound, while optimising over the location would provide the strictest bound.
+In particular, we establish the \emph{first elbow constraint} which we use in~\cref{sec:unital,sec:stab} explicitly.
+\begin{lemma}
+	Consider a magic state interconversion as in~\cref{eq:sigma_conv}, where we denote by $(x_0, L_0)$ and $(x'_0, L'_0)$ the first elbow coordinates of the initial and target states respectively.
+	If $x_0 < x'_0$, then it holds that
+\begin{equation}\label{eq:first_elb_bound}
+	\frac{L_0}{x_0} \geq \frac{L_0'}{x_0'}.
+\end{equation}
+\end{lemma}
+\begin{proof}
+	Consider the Lorenz curve constraint at $x = x_0$,
+\begin{equation}
+	\lc{\rho}{\sigma}(x_0) \geq \lc{\tau}{\sigma}(x_0).
+\end{equation}
+Since $x_0 < x'_0$, we can find the target state Lorenz curve coordinate $L'_\star$ at location $x = x_0$ by interpolating between the origin and the target state's first elbow, 
+\begin{equation}\label{eq:constraint_deriv_temp}
+	L'_\star = \frac{x_0}{x'_0}L'_0.
+\end{equation}
+We need $L_0 \geq L_\star'$ and rearranging we get~\cref{eq:constraint_deriv_temp}.
+\end{proof}
+
+We can now turn the attention from the first elbow to the peak of the Lorenz curve to associate it directly with the magic monotone of mana, and equivalently the sum-negativity of a quantum state. 
+This holds independently of the particular $\sigma$--fragment one works in and as a result it becomes apparent that mana provides a weaker condition than majorisation for all magic state interconversions.
 
@@
 Conversely, it is now clear that the maximum of the Lorenz curve acts as a valid magic monotone.
-This implies the following result.
 \begin{theorem}\label{thm:bounds}
@@
 
-In sections~\cref{sec:unital,sec:stab}, we study majorisation constraints on magic distillation arising in different fragments. 
+The area $\A_\sigma(\rho)$ between the curve $L_{\rho|\sigma}$ and the line $y=1$ is a resource monotone in the $\sigma$--fragment. 
+This is clear because for any state conversion like~\cref{eq:sigma_conv}, the Lorenz curve $L_{\tau|\sigma}$ is lower than $L_{\rho|\sigma}$, hence $\A_\sigma(\E(\rho)) \leq \A_\sigma(\rho)$.
+The exact form of the monotone is given in~\cref{app:areamono}.
+\nick{should we include the area? Have a look at~\cref{app:areamono}}
+
+In~\cref{sec:unital,sec:stab}, we study majorisation constraints on magic distillation arising in different fragments. 
 For this reason, we define the $n$-copy, $\epsilon$-noisy Strange state,
@@
 Its Wigner distribution is visualised in~\cref{fig:strange}.
+
+We refer to parameter $\epsilon$ as \emph{noise level} to avoid confusion with the error rate $\delta$, a term commonly used in the literature to denote that the distilled state has a marginal overlap of at least $1-\delta$ with the desired magic state.
+In our case the error rate of the state in~\cref{eq:noisysn} would be $\delta = \frac{2}{3}\epsilon$.
 
@@
 Dephasing and bit-flip error channels are examples of the many error-inducing channels that respect the unital symmetry. \nick{Expand on significance of unital fragment}
-
-We now consider the task of purifying $n$ copies of a noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ as given in~\cref{eq:noisysn} into a smaller number of copies $n'$ of a less noisy strange state $\rho_{\rm{S}}(\epsilon')^{\otimes n'}$, with $\epsilon' < \epsilon$ and $n' \leq n$,
+\null\\
+
+We consider the task of purifying $n$ copies of a noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ as given in~\cref{eq:noisysn} into a smaller number of copies $n'$ of a less noisy strange state $\rho_{\rm{S}}(\epsilon')^{\otimes n'}$, with $\epsilon' < \epsilon$ and $n' \leq n$,
 \begin{equation}\label{eq:sudist}
@@
 Since the state $\id / 3$ is free, tensoring in copies of it does not affect the distillation process.
+The distillation rate $R \coloneqq n'/n$ for this process will in general depend on the noise levels, $R = R(\epsilon, \epsilon')$ and our task is to provide it with an upper bound.
 
 The Lorenz curve $\lc{\rho_{\rm{S}}}{\id/3}$, for some general noise parameter $\epsilon$ and number of copies $n$, is defined at $9^n$ points between $0$ and $1$.
-The exact expressions for the coordinates of these points can take $8$ different forms, depending on whether the noise level \nick{noise level / error rate} $\epsilon$ is greater or less than $\frac{3}{7}$, the parity of the number of copies $n$ is even or odd and the location relative to the curve peak is on the left hand side (LHS -- including the curve peak) or right hand side (RHS) of the curve peak.
+The exact expressions for the coordinates of these points can take $8$ different forms, depending on whether the noise level $\epsilon$ is greater or less than $\frac{3}{7}$, the parity of the number of copies $n$ is even or odd and the location relative to the curve peak is on the left hand side (LHS -- including the curve peak) or right hand side (RHS) of the curve peak.
 The full details for the construction of all Lorenz curve forms are provided in~\cref{app:lcsu_technical}.
 
-\nick{In the following, should we talk about the coordinates of all elbows and then say that we are gonna use only the first elbow, or should we leave full-elbow analysis for the appendix and only talk about first elbow here?}
-
-Here we focus on the case of Lorenz curves with even copies $n, n'$ and low noise levels ($\epsilon' < \epsilon \leq 3/7$).
-The part of the curve on the LHS of its peak is constructed by the positive components of the state Wigner distribution that take values $w_i$, with associated multiplicities $m_i$,
+Here we focus on the comparison of the first elbow (which lies in the LHS part) of Lorenz curves with even copies $n, n'$ and low noise levels ($\epsilon' < \epsilon \leq 3/7$).
+
+The Wigner distribution of the 1-copy, $\epsilon$-noisy Strange state can be written as 
+\begin{equation}
+	\W[\bmx]{\rho_{\rm{S}}(\epsilon)} = (1-\epsilon)\W[\bmx]{\ketbra{\rm{S}}} + \epsilon\W[\bmx]{\frac{1}{3}\id},
+\end{equation}
+so we get positive components
+\begin{equation}
+	u(\epsilon) \coloneqq \frac{1}{6} -\frac{1}{18}\epsilon
+\end{equation}
+at the 8 phase space points $\bmx \in \cal{P}_3 \setminus \{\bmo\}$ and a negative component
+\begin{equation}
+	- v(\epsilon) \coloneqq - \left( \frac{1}{3} -\frac{4}{9}\epsilon \right)
+\end{equation}
+at the origin $\bmx = \bmo$.
+
+For the sake of clarity, we may omit obvious variable dependencies in the following analysis.
+
+The rescaled distribution in the unital fragment simply is 
+\begin{equation}
+	\widetilde{\rm{W}}_{\rho_{\rm{S}}|\frac{1}{3}\id}(\bmx) = \frac{\W[\bmx]{\rho_{\rm{S}}}}{\W[\bmx]{\frac{1}{3}\id}} = d\W[\bmx]{\rho_{\rm{S}}},
+\end{equation}
+so ordering the rescaled distribution is equivalent to ordering $\W{\rho_{\rm{S}}}$.
+
+The component values and multiplicities ($m_i$) in the $n$-copy case are 
 \begin{align}
-	w_i &= \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2i}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{n-2i}, \\
-	m_i &= 8^{2i}\binom{n}{2i},
+	m_i &= 8^{2i}\binom{n}{2i}, \\
+	w(\rho_{\rm{S}})_i &= u^{2i}(-v)^{n-2i}, \\
+	w(\id/3)_i &=  \frac{1}{9^n},
 \end{align}
-where $i=0,\dots,\frac{n}{2}$.
-It is readily seen that $\lc{\rho_{\rm{S}}}{\id/3}(x)$ has elbows on the LHS of its peak located at points $x=x_i$, where
-\begin{equation}
-	x_i = \Phi_+ \left( 2i; n , \frac{8}{9} \right),
-\end{equation}
-with $i = 0,1, \dots , n$ and where $\Phi_+(i,n,p)$ is an even-power cumulant distribution function given by
-\begin{equation}
-	\Phi_+(2i; n, p) \coloneqq \sum_{\ell=0}^{i} \binom{n}{2\ell} p ^{2\ell} (1-p)^{n-2\ell}.
-\end{equation}
-We provide technical details on the function $\Phi_+$ in the appendices.
-
-The value of the Lorenz curve at an elbow is given by
-\begin{equation}
-	\lc{\rho}{\id/3}(x_{i}) \equiv L_{i} =  \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^{n} \Phi_+\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right),
-\end{equation}
-and we define $(x_{-1}, L_{-1}) = (0,0)$.
-
-\iffalse
-The coordinates of any point on the Lorenz curve LHS can be expressed as convex sums of the neighbouring elbows,
-\begin{align}
-    x_{ijk} &= \left( 1-p_{ijk}\right) x_{i-1} + p_{ijk} x_{i} \label{eq:lcsu_xcoord}\\
-    L_{ijk} &= \left( 1-p_{ijk} \right) L_{i-1} + p_{ijk} L_{i}, \label{eq:lcsu_lcoord}
-\end{align}
-where we use a three-index parametrisation for the coordinates, with $i$ the index of the elbow that follows, $j = 1,\dots,m_i$ and $k=1,\dots,9^{2(n-n')}$.
-Therefore, for the initial state $\rho_{\rm{S}}^{\otimes 2n}$ we have
-\begin{equation}
-	p_{ijk} = \frac{j}{8^{2i}\binom{2n}{2i}},
-\end{equation}
-with $i=0,\dots,n,\ j(i) = 1,\dots,8^{2i}\binom{2n}{2i}$ and $k = 1$.
-For the target state $\rho_{\rm{S}}(\epsilon')^{\otimes 2n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes 2(n-n')}$,
-\begin{equation}
-	p'_{i'j'k'} = \frac{k' + (j'-1)9^{2(n-n')}}{9^{2(n-n')} 8^{2i'}\binom{2n'}{2i'}}
-\end{equation}
-with $i'=0,\dots,n',\ j'(i') = 1,\dots,8^{2i'}\binom{n'}{2i'}$ and $k' = 1,\dots,9^{2(n-n')}$.
-\fi
-
-Lorenz curve comparison provides $9^n$ necessary constraints for the process~\cref{eq:sudist}.
-\cref{thm:elbows} shows that they can be reduced to $n'$ independent constraints.
-However, in principle we can pick any location $x_\star \in [0,1]$ at which the Lorenz curves are defined and we then get a necessary distillation constraint, 
-\begin{equation}
-	\lc{\rho_{\rm{S}}(n, \epsilon, 0)}{\frac{\id}{3}}(x_\star) \geq \lc{\rho_{\rm{S}}(n', \epsilon', n-n')}{\frac{\id}{3}}(x_\star).
-\end{equation}
-
-We choose $x_\star = x_0 = \Phi_+(0, n, \frac{8}{9}) = \frac{1}{9^{n}}$, the location of the first elbow of the initial state $\rho_{\rm{S}}(n, \epsilon, 0)$.
-The initial state Lorenz curve coordinate at this location is
-\begin{equation}
-	L_\star = L_0 = \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^{n} \Phi_+\left(0;n,\frac{12-4\epsilon}{15-8\epsilon}\right) = \left(\frac{3-4\epsilon}{9}\right)^n
-\end{equation}
-
-The first elbow of the target state is located at $x'_0 = \frac{1}{9^{n'}} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the first target state elbow,
-\begin{equation}\label{eq:constraint_deriv}
-	\begin{split}
-	L'_\star &= \frac{x_\star}{x'_0}L'_0 = \frac{1}{9^{n-n'}}\left( \frac{5}{3} - \frac{8}{9}\epsilon'\ \right)^{n'}\Phi_+\left(0;n',\frac{12-4\epsilon'}{15-8\epsilon'}\right) \\
-	&= \frac{(3-4\epsilon')^{n'}}{9^{n}}.
-	\end{split}
-\end{equation}
-The process in~\cref{eq:sudist} is therefore possible only if $L_\star \geq L'_\star$ or equivalently,
-\begin{align}
-	\frac{n}{n'} &\geq \frac{\ln{(3-4\epsilon')}}{\ln{(3-4\epsilon)}}, \text{ or}\\
-	\epsilon &\leq \frac{3}{4} - \frac{1}{4}(3-4\epsilon')^{\frac{n'}{n}}.
-\end{align}
-As an example, the process with $(n, n') = (12, 4)$ and $\epsilon' = 0.05$ yields $\epsilon \leq 0.398$.
-Numerical comparison of the curves with varying $\epsilon$ suggests that we require $\epsilon \leq 0.373$ for the process to be possible.
-
-Moreover, for the problem of distilling pure magic states where $\epsilon'=0$ we obtain an upper bound on the unital fragment distillation rate $R=n'/n$ given by
-\begin{equation}
-R \leq 1 + \frac{\ln (1 - \frac{4}{3} \epsilon)}{\ln 3},
-\end{equation}
-which holds for all finite $n$. 
-In comparison, the bound from mana gives 
-\begin{equation}
-	R_{\rm{mana}} \leq 1 + \frac{\ln \left(1 - \frac{8}{15}\epsilon \right)}{\ln \frac{5}{3}},
-\end{equation}
-a threshold which is looser than the one provided by majorisation for all $\epsilon > 0$ as illustrated in~\cref{fig:distill_bounds}.
-For example, for $\epsilon = 0.4$ we obtain $R\le 0.31 $ while the mana bound gives $R_{\rm{mana}} \le 0.53$.
+where index $i$ runs through $0,\dots,\frac{n}{2}$.
+This is derived in~\cref{app:lcsu_coord_elb}.
+
+It is readily seen that the maximum Wigner component is achieved when $i=0$, so the corresponding multiplicity and Wigner component are $m_0 = 1$, $w(\rho_{\rm{S}})_0 = v^n$.
+The first elbow coordinates therefore can be expressed as
+\begin{equation}\label{eq:first_elb_coords}
+	(x_0, L_0) = (m_0\hspace{2pt} w(\id/3)_0,\ m_0\hspace{2pt} w(\rho_{\rm{S}})_0) = \left(\frac{1}{9^n}, v^n \right)
+\end{equation}
+
+The first elbow of the target state is located at $x'_0 = \frac{1}{9^{n'}} > x_0$, so we can use the first elbow condition,
+\begin{equation}\label{eq:first_elb_bound}
+	\frac{L_0}{x_0} \geq \frac{L_0'}{x_0'},
+\end{equation}
+to compute analytical distillation bounds for distillation rate $R = R(\epsilon, \epsilon') \coloneqq n'/n$ in the unital fragment.
+We substitute coordinates from~\cref{eq:first_elb_coords} appropriately in~\cref{eq:first_elb_bound} to get
+\begin{equation}
+	R \leq \frac{\ln{(3-4\epsilon)}}{\ln{(3-4\epsilon')}}.
+\end{equation}
+
+Specifically for the problem of distilling pure magic states ($\epsilon'=0$), we obtain an upper bound in the unital fragment given by
+\begin{equation}
+	R \leq 1 + \frac{\ln (1 - \frac{4}{3} \epsilon)}{\ln 3}.
+\end{equation}
+
+Similar upper bounds on distillation rates for qudits of odd prime dimension include the mana bound~\cite{cit:veitch} and the max--thauma bound~\cite{Wang2020} which is defined via a semi-definite program, but possesses properties that allow for an easy comparison with our bound.
+The mana bound can be directly calculated as
+\begin{equation}
+	R \leq \frac{\mana{\rho_{\rm{S}}}(\epsilon)}{\mana{\rho_{\rm{S}}}(0)} = 1 + \frac{\ln \left(1 - \frac{8}{15}\epsilon \right)}{\ln \frac{5}{3}}.
+\end{equation}
+Using the properties of super-additivity and vanishing at free states of the max--thauma, we obtain
+\begin{equation}
+	\theta_{\rm{max}}(\rho_{\rm{S}}(\epsilon)) \geq (1-\epsilon) \ketbra{\rm{S}} + \epsilon \frac{1}{3}\id = (1-\epsilon) \theta_{\rm{max}}(\rho_{\rm{S}}(0)),
+\end{equation}
+so that for a deterministic single-copy distillation process, an initial number of copies $n \geq \theta_{\rm{max}}(\tau) / \theta_{\rm{max}}(\rho) \geq 1-\epsilon$ is required.
+Therefore, the max--thauma bound for the pure Strange state distillation process can get as tight as
+\begin{equation}
+	R = \frac{1}{n} = \frac{\theta_{\rm{max}}(\rho_{\rm{S}}(\epsilon))}{\theta_{\rm{max}}(\rho_{\rm{S}}(0))} \leq 1-\epsilon.
+\end{equation}
+
+Both the mana and the max--thauma bounds are looser than the majorization bound we derived via the first elbow constraint as illustrated in~\cref{fig:distill_bounds}.
 \begin{figure}[t]
@@
     \includegraphics[scale=0.5]{figs/distill_bounds.pdf}
-    \caption{\textbf{Distillation rate in unital fragment.} Distillation rates obtained by mana and majorisation are plotted for $\epsilon' = 0$, up to noise levels $\epsilon_{\rm{max}} = \frac{3}{7}$.
-    Majorisation consistently provides stricter rates as proven in~\cref{thm:bounds}. \nick{add thauma?}
+    \caption{\textbf{Distillation bounds in the unital fragment.} Distillation bounds obtained by majorisation, mana and the line $1-\epsilon$ (tightest bound of max--thauma) are plotted for $\epsilon' = 0$, up to noise level $\epsilon = \frac{3}{7}$.
+    Majorisation consistently provides stricter rates than mana and max--thauma.
     }
@@
 Given this context, we now provide the following result on bounding the distillation rate $R = R(\epsilon, \epsilon', \beta) \coloneqq \frac{n'}{n}$ of the process in~\cref{eq:stdist}.
+We also write $R(\epsilon, \beta) = R(\epsilon, \epsilon'=0, \beta)$.
 The bounds depend on the free energy $F_\beta$ of state $\sigma$,
@@
 where the von Neumann entropy is $S(\sigma) \coloneqq -\tr[\sigma\log{\sigma}]$.
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[scale=0.55]{figs/rate_scatter.pdf}
+    \caption{\textbf{Bounds on magic distillation rates $R(\epsilon, \beta)$ within stabiliser fragments.}
+    The vertical dashed line is the `Landauer-like' temperature threshold $\beta_\star$ and the diagonal dashed curve corresponds to the noise threshold $\epsilon_\star (\beta)$ at every $\beta \leq \beta_\star$.
+The unital fragment corresponds to the $\beta =0 $ line.
+    }
+    \label{fig:rate_contour}
+\end{figure}
 
@@
 \end{equation}
-and for $\beta \leq \beta_\star$, we define a threshold error rate
+and for $\beta \leq \beta_\star$, we define a threshold noise level
 \begin{equation}
@@
 
-\begin{figure}[t!]
-    \centering
-    \includegraphics[scale=0.55]{figs/rate_scatter.pdf}
-    \caption{\textbf{Bounds on magic distillation rates $R(\epsilon, \beta)$ within stabiliser fragments.}
-    The vertical dashed line is the `Landauer-like' temperature threshold $\beta_\star$ and the diagonal dashed curve corresponds to the noise threshold $\epsilon_\star (\beta)$ at every $\beta \leq \beta_\star$.
-The unital fragment corresponds to the $\beta =0 $ line.
-    }
-    \label{fig:rate_contour}
-\end{figure}
-
 \begin{proof}
-	We provide an outline of the proof here, with all technical details included in~\cref{app:lcst_technical}.\\
-
-The Wigner distribution of the $\epsilon$-noisy Strange state can be written as 
-\begin{equation}
-	\W[\bmx]{\rho_{\rm{S}}(\epsilon)} = (1-\epsilon)\W[\bmx]{\ketbra{\rm{S}}} + \epsilon\W[\bmx]{\frac{1}{3}\id},
-\end{equation}
-so we get positive components
-\begin{equation}
-	u(\epsilon) = \frac{1}{6} -\frac{1}{18}\epsilon
-\end{equation}
-at the 8 phase space points $\bmx \in \cal{P}_3 \setminus \{\bmo\}$ and a negative component
-\begin{equation}
-	- v(\epsilon) = - \left( \frac{1}{3} -\frac{4}{9}\epsilon \right)
-\end{equation}
-at the origin $\bmx = \bmo$.
+	We provide the full proof here, with some technical details pushed to~\cref{app:lcst_technical}.\\
 
@@
 
-This Clifford operation permutes the Hamiltonian eigenvalues on the phase space, so that the negative component of $\rho_S(\epsilon)$ can lie on the same point on the phase space as any of the eigenvalues.
+This Clifford operation permutes the Hamiltonian eigenvalues on the phase space, so that the negative component $-v$ of $\rho_S(\epsilon)$ can lie on the same point on the phase space as any of the eigenvalues.
 For this reason, we impose no order between the eigenvalues, but simply choose $E_0$ as the eigenvalue that is associated with the state negativity and denote the highest energy by $E_{\rm{max}} \coloneqq \max{\{E_0, E_1, E_2\}}$.
@@
 Our aim is to obtain a distillation bound for~\cref{eq:stdist} which depends on variables $n, n', \epsilon, \epsilon'$ as well as $\beta$.
-In the analysis that follows, we drop obvious variable dependencies for clarity.
+In the analysis that follows, we again drop obvious variable dependencies for clarity.
 
@@
 \begin{equation}
-	\widetilde{\rm{W}}_{\rho_{\rm{S}}|\gamma}(\bmx) \coloneqq \frac{\W[\bmx]{\rho_{\rm{S}}}}{\W[\bmx]{\gamma}}.
-\end{equation}
-There are four distinct values of the rescaled distribution on the phase space, as illustrated in the phase space diagram in~\cref{fig:pd_split_thermal}.
+	\widetilde{\rm{W}}_{\rho_{\rm{S}}|\gamma}(\bmx) = \frac{\W[\bmx]{\rho_{\rm{S}}}}{\W[\bmx]{\gamma}},
+\end{equation}
+which attains four distinct values on the phase space, naturally splitting it into four regions as illustrated in the~\cref{fig:pd_split_thermal}.
 \begin{figure}[h]
@@
 
-The first elbow coordinate can finally be derived as
+The first elbow coordinates can finally be derived as
 \begin{equation}\label{eq:first_elb_coords}
@@
 \null\\
-
-A necessary distillation constraint for the process in~\cref{eq:stdist} can be defined at the location $x_\star = x_0$ of the initial state's first elbow,
-\begin{equation}\label{eq:first_elbow_constraint}
-	\lc{\rho_{\rm{S}}(\epsilon)^{\otimes n}}{\gamma_\beta}(x_\star) \geq \lc{\rho_{\rm{S}}(\epsilon')^{\otimes n'}}{\gamma_\beta}(x_\star).
-\end{equation}
 
@@
 
-In all three scenarios, it is simple to check that the initial state's first elbow is always located to the left (closer to $0$) of the target state's first elbow, $x_0 \leq x_0'$, as proven in~\cref{app:first_elb_loc}.
-The prime indicates target state coordinates.
-We can thus find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star = x_0$ by interpolating between the origin and the target state's first elbow, 
-\begin{equation}\label{eq:constraint_deriv_temp}
-	L'_\star = \frac{x_\star}{x'_0}L'_0.
-\end{equation}
-Condition~\cref{eq:first_elbow_constraint} reads that we need $L_0 = L_\star \geq L_\star'$.
-Therefore, restricting to the first elbow, the necessary distillation condition in~\cref{eq:first_elbow_constraint} simply becomes
+In all three scenarios, it is simple to check that the initial state's first elbow is always located to the left (closer to $0$) of the target state's first elbow, $x_0 \leq x_0'$, as proven in~\cref{app:first_elb_loc}, where the prime ($'$) is used to indicate target state coordinates.
+Therefore, we can use the first elbow condition,
 \begin{equation}\label{eq:first_elb_bound}
-	\frac{L_0}{x_0} \geq \frac{L_0'}{x_0'}.
-\end{equation}
+	\frac{L_0}{x_0} \geq \frac{L_0'}{x_0'},
+\end{equation}
+to compute analytical distillation bounds for the distillation rate $R = R(\epsilon, \epsilon', \beta) \coloneqq n'/n$ in all three possible scenarios.
 Involving more elbows gives stricter, but more convoluted necessary distillation constraints.
 
-We are now in a position to compute analytical distillation bounds for the distillation rate $R = R(\epsilon, \epsilon', \beta) \coloneqq n'/n$, based on the first elbow constraint for all three possible scenarios.
-Substituting coordinates from~\cref{eq:first_elb_coords} appropriately in~\cref{eq:first_elb_bound}, we get the following necessary conditions:
-\begin{enumerate}
-	\item $\rm{(C1)} \rightarrow \rm{(C1)}$.
-
-\begin{align}
-	R \leq \frac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_0 - F_\beta)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F_\beta)}.
-\end{align}
-Equivalently, we require
-\begin{align}
-	\epsilon \leq \frac{3}{4} - \frac{3}{4} \left( 1 - \frac{4}{3}\epsilon' \right)^{R} \left( \frac{e^{-\beta E_0}}{\Z_\beta} \right)^{1 - R}	.
-\end{align}
-
-	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} > E_0$, $\beta < \beta_{\star}$ and $\epsilon' \leq \epsilon_{\star} < \epsilon$.
-
-\begin{align}
-	R \leq \frac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F_\beta)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F_\beta)}
-\end{align}
-Equivalently, we require
-\begin{align}
-	\epsilon &\leq 3 - 6 \left( 1 - \frac{4}{3}\epsilon' \right)^{R} \frac{e^{-\beta E_{\rm{max}}} e^{R\beta E_0}}{\Z_\beta^{1-R}}	
-\end{align}
-
-	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $E_{\rm{max}} > E_0$, $\beta \geq \beta_{\star}$.
-
-\begin{align}
-	R \leq \frac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F_\beta)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F_\beta)}
-\end{align}
-Equivalently, we require
-\begin{align}
-	\epsilon &\leq 3 - 6 \left( \frac{1}{2} - \frac{1}{6}\epsilon' \right)^{R} \left( \frac{e^{-\beta E_{\rm{max}}}}{\Z_\beta} \right)^{1 - R}.
-\end{align}
-\end{enumerate}
-
-Substituting $\epsilon' = 0$ leads to the expressions of the theorem statement.
+We substitute coordinates from~\cref{eq:first_elb_coords} appropriately in~\cref{eq:first_elb_bound} to get the following necessary conditions,
+\begin{equation}\label{eq:rate_bounds_proof}
+	R \leq
+	\begin{cases}
+		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_0 - F_\beta)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F_\beta)},\ &\rm{(C1)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
+		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F_\beta)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F_\beta)},\ &\rm{(C2)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
+		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F_\beta)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F_\beta)},\ &\rm{(C2)} \rightarrow \rm{(C2)}.
+	\end{cases}
+\end{equation}
+Equivalently, we require that
+\begin{equation}\label{eq:error_bounds_proof}
+	\epsilon \leq
+	\begin{cases}
+		\frac{3}{4} - \frac{3}{4} \left( 1 - \frac{4}{3}\epsilon' \right)^{R} \left( \dfrac{e^{-\beta E_0}}{\Z_\beta} \right)^{1 - R},\ &\rm{(C1)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
+		3 - 6 \left( 1 - \frac{4}{3}\epsilon' \right)^{R} \dfrac{e^{-\beta E_{\rm{max}}} e^{R\beta E_0}}{\Z_\beta^{1-R}},\ &\rm{(C2)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
+		3 - 6 \left( \frac{1}{2} - \frac{1}{6}\epsilon' \right)^{R} \left( \dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta} \right)^{1 - R},\ &\rm{(C2)} \rightarrow \rm{(C2)}.
+	\end{cases}
+\end{equation}
+
+Substituting $\epsilon' = 0$ in~\cref{eq:rate_bounds_proof} leads to the theorem statement.
 
 \end{proof}
-
-\null\newpage
-\section{Comparison with existing distillation rates}
-\label{sec:comparison}
-
-We have derived a \emph{distillation bound} $R(\epsilon, \epsilon', \beta)$ for the process
-\begin{equation}\label{eq:stdist}
-	\rho_{\rm{S}}(\epsilon)^{\otimes n} \longrightarrow \rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \gamma_\beta^{\otimes (n-n')},
-\end{equation}
-with even $n, n'$ and $0 \leq \epsilon' < \epsilon \leq 3/7$, where the $n$-copy, $\epsilon$-noisy Strange state is
-\begin{equation}\label{eq:test}
-    \rho_{\rm{S}}(\epsilon)^{\otimes n} \coloneqq \left[ (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \frac{1}{3}\id \right]^{\otimes n}.
-\end{equation}
-
-The bound informs us that any distillation protocol in the $\gamma_\beta$-fragment with an $\epsilon$-noisy input and $\epsilon'$-noisy output has a \emph{distillation rate} 
-\begin{equation}
-	\frac{n'}{n} \leq R(\epsilon, \epsilon', \beta).
-\end{equation}
-
-We apply our results on the ternary Golay code distillation protocol suggested in~\cite{cit:prakash}.
-In this protocol, a single Strange state is distilled with noise level
-\begin{equation}
-	\epsilon'(n, \epsilon) \approx \frac{1}{\alpha}(\alpha\epsilon)^{n^\xi},
-\end{equation}
-where $\alpha \approx 1.75$ and $\xi \approx 0.112$ are constants specific to the protocol.
-This can be rewritten in terms of the protocol distillation rate,
-\begin{equation}
-	R_{\rm{Golay}}(\epsilon, \epsilon') = \frac{1}{n} \approx \left( \frac{\log{(\alpha \epsilon)}}{\log{(\alpha \epsilon')}} \right)^{\frac{1}{\xi}}
-\end{equation}
-
-We compare the distillation rate of the protocol with our distillation bound, 
-\begin{equation}
-	R_{\rm{Golay}}(\epsilon, \epsilon') \leq R(\epsilon, \epsilon', \beta)
-\end{equation} 
-in figure~\cref{fig:prakash_compare}
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.5]{figs/prakash_compare.png}
-    \caption{\textbf{Comparison with ternary Golay distillation rate.}
-    Our bound is not violated but gets close to saturated for some noise levels.
-    The thick diagonal line indicates where $\epsilon' = \epsilon$.
-    }
-    \label{fig:prakash_compare}
-\end{figure}
-
-We can also rewrite the expression as 
-\begin{equation}
-	\epsilon_{\rm{Golay}}(\epsilon', n) \approx \frac{1}{\alpha}(\alpha\epsilon')^{n^{-\xi}},
-\end{equation}
-and compare with the numerically optimal error bounds provided by majorisation as shown in~\cref{fig:prakash_compare_errors}
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.5]{figs/prakash_compare_errors.png}
-    \caption{\textbf{Comparison with ternary Golay output error rate.}
-    Our bound is not violated but achieves a maximum saturation of $\epsilon_\star - \epsilon_{\rm{Golay}} = 0.147$.
-    }
-    \label{fig:prakash_compare_errors}
-\end{figure}
-
-A recent distillation bound was introduced in~\cite{Seddon2020}, where they show that for the deterministic conversion of $n$ copies of a qubit state $\rho$ to a target pure magic state $\ket{\psi}$, the following bound on the distillation rate holds,
-\begin{equation}\label{eq:seddon}
-	\frac{n'}{n} \leq \frac{\log{\Lambda^+(\rho)}}{\log{F(\psi)^{-1}}},
-\end{equation}
-where $\Lambda^+(\rho)$ is the generalised robustness of state $\rho$, calculable via a costly SDP and $F(\psi)$ denotes the stabiliser fidelity of state $\ket{\psi}$.
-They demonstrate the performance of their bound by considering the purification process of the qubit magic state $\ket{H}$, with their figure replicated in~\cref{fig:seddon}. 
-For high initial noise level ($\epsilon = 0.25$), their bound dictates that $R = 1/150$, which is pretty good.
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.3]{figs/seddon.png}
-    \caption{\textbf{Comparison of Seddon \textit{et al.}'s bound~\cite{Seddon2020} in~\cref{eq:seddon} with a generic resource bound in~\cite{Fang2020}.}
-    The process they consider is purifying $n$ copies of $(1-\epsilon)\ketbra{H} + \epsilon/3 \id$ to $n'$ copies of $(1-\epsilon')\ketbra{H} + \epsilon'/3 \id$.
-    Their bound (red and blue) is pretty good compared with the generic (violet) bound.
-    Not sure why it looks like their bound gives $n\rightarrow 25$ as $1-\epsilon \rightarrow 1$.
-    }
-    \label{fig:seddon}
-\end{figure}
-
-Similar concrete rates have been studied for qudits in two occasions:
-First, the mana bound, which we have demonstrated in~\cref{fig:distill_bounds}.
-Secondly, Wang \textit{et al.}'s max-thauma bound~\cite{Wang2020}, which as far as I can tell, is less tight than mana (?).
-It is defined via an SDP, but we can use its properties (super-additivity and zero at free states) to readily get a bound on noisy Strange states,
-\begin{equation}
-	\theta_{\rm{max}}(\rho_{\rm{S}}(\epsilon)) \geq (1-\epsilon) \ketbra{\rm{S}} + \epsilon \frac{1}{3}\id = (1-\epsilon) \theta_{\rm{max}}(\rho_{\rm{S}}(0)).
-\end{equation}
-Their bound simply states that any deterministic single-copy distillation process $\rho^{\otimes n} \longrightarrow \tau$ requires an initial number of copies $n \geq \theta_{\rm{max}}(\tau) / \theta_{\rm{max}}(\rho)$.
-Therefore, the rate of our pure Strange state distillation process~\cref{eq:sudist} can only get as tight as
-\begin{equation}
-	R = 1/n = \frac{\theta_{\rm{max}}(\rho_{\rm{S}}(\epsilon))}{\theta_{\rm{max}}(\rho_{\rm{S}}(0))} \leq 1-\epsilon,
-\end{equation}
-which is less tight than mana as could be readily observed if plotted in~\cref{fig:distill_bounds}.
-
-\ddd{[Going forward:
-\begin{enumerate}
-\item Does the ``last elbow'' give the same bound? Is it as simple?
-\item Numerically is this about as good as it gets from majorisation?
-\item How does this rate compare with existing literature?
-\end{enumerate}}
 
@@
 
-\begin{enumerate}
-    \item Introduced fragments
-    \item Identify symmetries of the setup
-    \item Combined single-shot thermodynamics with magic 
-    \item Can we solve other cases exactly? (apart from single qutrit)
-\end{enumerate}
+\nick{Summary}
 

### 2021-03-22 notes/notes.tex
Tidied up unital and stabilizer fragment bound sections

@@
 
+\null\newpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\section{Bound comparison}
+\null\newpage
+\section{Comparison with existing distillation rates}
+\label{sec:comparison}
+
+We have derived a \emph{distillation bound} $R(\epsilon, \epsilon', \beta)$ for the process
+\begin{equation}\label{eq:stdist}
+	\rho_{\rm{S}}(\epsilon)^{\otimes n} \longrightarrow \rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \gamma_\beta^{\otimes (n-n')},
+\end{equation}
+with even $n, n'$ and $0 \leq \epsilon' < \epsilon \leq 3/7$, where the $n$-copy, $\epsilon$-noisy Strange state is
+\begin{equation}\label{eq:test}
+    \rho_{\rm{S}}(\epsilon)^{\otimes n} \coloneqq \left[ (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \frac{1}{3}\id \right]^{\otimes n}.
+\end{equation}
+
+The bound informs us that any distillation protocol in the $\gamma_\beta$-fragment with an $\epsilon$-noisy input and $\epsilon'$-noisy output has a \emph{distillation rate} 
+\begin{equation}
+	\frac{n'}{n} \leq R(\epsilon, \epsilon', \beta).
+\end{equation}
+
+We apply our results on the ternary Golay code distillation protocol suggested in~\cite{cit:prakash}.
+In this protocol, a single Strange state is distilled with noise level
+\begin{equation}
+	\epsilon'(n, \epsilon) \approx \frac{1}{\alpha}(\alpha\epsilon)^{n^\xi},
+\end{equation}
+where $\alpha \approx 1.75$ and $\xi \approx 0.112$ are constants specific to the protocol.
+This can be rewritten in terms of the protocol distillation rate,
+\begin{equation}
+	R_{\rm{Golay}}(\epsilon, \epsilon') = \frac{1}{n} \approx \left( \frac{\log{(\alpha \epsilon)}}{\log{(\alpha \epsilon')}} \right)^{\frac{1}{\xi}}
+\end{equation}
+
+We compare the distillation rate of the protocol with our distillation bound, 
+\begin{equation}
+	R_{\rm{Golay}}(\epsilon, \epsilon') \leq R(\epsilon, \epsilon', \beta)
+\end{equation} 
+in figure~\cref{fig:prakash_compare}
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.5]{figs/prakash_compare.png}
+    \caption{\textbf{Comparison with ternary Golay distillation rate.}
+    Our bound is not violated but gets close to saturated for some noise levels.
+    The thick diagonal line indicates where $\epsilon' = \epsilon$.
+    }
+    \label{fig:prakash_compare}
+\end{figure}
+
+We can also rewrite the expression as 
+\begin{equation}
+	\epsilon_{\rm{Golay}}(\epsilon', n) \approx \frac{1}{\alpha}(\alpha\epsilon')^{n^{-\xi}},
+\end{equation}
+and compare with the numerically optimal error bounds provided by majorisation as shown in~\cref{fig:prakash_compare_errors}
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.5]{figs/prakash_compare_errors.png}
+    \caption{\textbf{Comparison with ternary Golay output error rate.}
+    Our bound is not violated but achieves a maximum saturation of $\epsilon_\star - \epsilon_{\rm{Golay}} = 0.147$.
+    }
+    \label{fig:prakash_compare_errors}
+\end{figure}
+
+A recent distillation bound was introduced in~\cite{Seddon2020}, where they show that for the deterministic conversion of $n$ copies of a qubit state $\rho$ to a target pure magic state $\ket{\psi}$, the following bound on the distillation rate holds,
+\begin{equation}\label{eq:seddon}
+	\frac{n'}{n} \leq \frac{\log{\Lambda^+(\rho)}}{\log{F(\psi)^{-1}}},
+\end{equation}
+where $\Lambda^+(\rho)$ is the generalised robustness of state $\rho$, calculable via a costly SDP and $F(\psi)$ denotes the stabiliser fidelity of state $\ket{\psi}$.
+They demonstrate the performance of their bound by considering the purification process of the qubit magic state $\ket{H}$, with their figure replicated in~\cref{fig:seddon}. 
+For high initial noise level ($\epsilon = 0.25$), their bound dictates that $R = 1/150$, which is pretty good.
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.3]{figs/seddon.png}
+    \caption{\textbf{Comparison of Seddon \textit{et al.}'s bound~\cite{Seddon2020} in~\cref{eq:seddon} with a generic resource bound in~\cite{Fang2020}.}
+    The process they consider is purifying $n$ copies of $(1-\epsilon)\ketbra{H} + \epsilon/3 \id$ to $n'$ copies of $(1-\epsilon')\ketbra{H} + \epsilon'/3 \id$.
+    Their bound (red and blue) is pretty good compared with the generic (violet) bound.
+    Not sure why it looks like their bound gives $n\rightarrow 25$ as $1-\epsilon \rightarrow 1$.
+    }
+    \label{fig:seddon}
+\end{figure}
+
+Similar concrete rates have been studied for qudits in two occasions:
+First, the mana bound, which we have demonstrated in~\cref{fig:distill_bounds}.
+Secondly, Wang \textit{et al.}'s max-thauma bound~\cite{Wang2020}, which as far as I can tell, is less tight than mana (?).
+It is defined via an SDP, but we can use its properties (super-additivity and zero at free states) to readily get a bound on noisy Strange states,
+\begin{equation}
+	\theta_{\rm{max}}(\rho_{\rm{S}}(\epsilon)) \geq (1-\epsilon) \ketbra{\rm{S}} + \epsilon \frac{1}{3}\id = (1-\epsilon) \theta_{\rm{max}}(\rho_{\rm{S}}(0)).
+\end{equation}
+Their bound simply states that any deterministic single-copy distillation process $\rho^{\otimes n} \longrightarrow \tau$ requires an initial number of copies $n \geq \theta_{\rm{max}}(\tau) / \theta_{\rm{max}}(\rho)$.
+Therefore, the rate of our pure Strange state distillation process~\cref{eq:sudist} can only get as tight as
+\begin{equation}
+	R = 1/n = \frac{\theta_{\rm{max}}(\rho_{\rm{S}}(\epsilon))}{\theta_{\rm{max}}(\rho_{\rm{S}}(0))} \leq 1-\epsilon,
+\end{equation}
+which is less tight than mana as could be readily observed if plotted in~\cref{fig:distill_bounds}.
+
+\ddd{[Going forward:
+\begin{enumerate}
+\item Does the ``last elbow'' give the same bound? Is it as simple?
+\item Numerically is this about as good as it gets from majorisation?
+\item How does this rate compare with existing literature?
+\end{enumerate}}
+
 An $n$-copy state $\rho^n$ has \emph{error rate} $\delta$ iff $\rho$ has an overlap of at least $1-\delta$ with magic state $\ket{\rm{S}}$,
@@
 
+Consider pure Strange state distillation at high temperatures, $\beta \leq \beta_{\star}$.
+Depending on the noise level of the initial state, we have either a $\rm{(C1)} \rightarrow \rm{(C1)}$ or a $\rm{(C2)} \rightarrow \rm{(C1)}$ scenario.
+
+At every $\beta > 0$, the rates indicate a transition at $\epsilon_{\star}$.
+As $\beta$ increases, the rate becomes stricter.
+At the high temperature limit, $\beta \rightarrow 0$, we get $\beta F_\beta \rightarrow -\ln{3}$, and we retrieve the unital fragment bound,
+\begin{equation}
+	R(\beta) \xrightarrow{\beta \rightarrow 0} \frac{\ln{(3-4\epsilon)}}{\ln{3}}.
+\end{equation}
+
+Consider pure Strange state distillation at low temperatures, $\beta \rightarrow \infty$.
+Independently of the noise level of the initial state, we have a $\rm{(C2)} \rightarrow \rm{(C2)}$ scenario.
+
+As $\beta$ increases, the rate becomes looser.
+At the zero temperature limit, $F_\beta$ tends to zero, so $R(\epsilon, \beta) \xrightarrow{\beta \rightarrow \infty} 1$.
+
 \end{document}

### 2021-03-24 appendix.tex
Tidied up unital and stabilizer fragment bound sections
Fixed appendices, except for unital fragment appendix. What do we include there / what do we get rid of?

@@
     \item[(iv)]\label{en:w4} Additive under mixing: \vspace{2pt}\\
-    $\W[\bmx]{\sum_i p_i \rho_i} = \sum\limits_i p_i \W[\bmx]{\rho_i}$;
+    $\W[\bmx]{p\rho_1 + (1-p)\rho_2} = p\W[\bmx]{\rho_1} + (1-p)\W[\bmx]{\rho_2}$;
     \item[(v)]\label{en:w5} Multiplicative under tensor products: \vspace{2pt}\\
@@
 \end{proposition}
-Not all distributions satisfying these properties correspond to positive semi-definite states.
 \begin{proof}
-	\nick{Proof?}
+	Proof of all properties can be found in the literature~\cite{cit:veitch,Vourdas_2004,cit:gross3,Wang_2019} except for property (iii) which we prove here.
+
+	Let $\{\lambda_i\}_{i \in \mathbb{Z}_d}$ be the (non-negative) eigenvalues of $\rho$, summing to 1.
+        Let $\{\alpha_{\bmx,i}\}_{i \in \mathbb{Z}_d}$ be the eigenvalues of $A_{\bmx}$.
+For any $\bmx, \alpha_{\bmx,i} \in \{-1, 1\}$, due to the hermiticity and unitarity of the phase-point operators.
+        Then,
+        \begin{equation}
+        \abs{\W{\rho}{\bmx}} = \frac{1}{d}\abs{\tr[A_{\bmx} \rho]} \leq \frac{1}{d} \abs{\sum_i \alpha_{\bmx,i} \lambda_i} \leq \frac{1}{d}\sum_i \lambda_i = \frac{1}{d}.
+        \end{equation}
+        The first inequality follows from Theorem 1 of~\cite{cit:mirsky} for complex matrices, while the second is the triangle inequality.
 \end{proof}
@@
     \begin{enumerate}
-        \item\label{en:wo1} Real-valued: $\W{\E} \in \mathbb{R}^{d^2} \times \mathbb{R}^{d^2}$;
-        \item\label{en:wo2} Normalised: $\sum_{\bmz \in \cal{P}_{d_B}} \W[\bmz|\bmx]{\E} = 1$ \\ 
+        \item[(i)]\label{en:wo1} Real-valued: $\W{\E} \in \mathbb{R}^{d^2} \times \mathbb{R}^{d^2}$;
+        \item[(ii)]\label{en:wo2} Normalised: $\sum_{\bmz \in \cal{P}_{d_B}} \W[\bmz|\bmx]{\E} = 1$ \\ 
         for any $\bmx \in \cal{P}_{d_A}$;
-        \item\label{en:wo3} Bounded: $\abs{\W[\bmy|\bmx]{\E}} \leq \frac{d_A}{d_B}$;
-	    \item\label{en:wo4} Transitive: $\W[\bmy]{\E(\rho)} = \sum_{\bmz \in \cal{P}_{d_A}} \W[\bmy|\bmz]{\E} \W[\bmz]{\rho}$ for any $\bmy \in \cal{P}_{d_B}$.
+        \item[(iii)]\label{en:wo3} Bounded: $\abs{\W[\bmy|\bmx]{\E}} \leq \frac{d_A}{d_B}$;
+	    \item[(iv)]\label{en:wo4} Transitive: $\W[\bmy]{\E(\rho)} = \sum_{\bmz \in \cal{P}_{d_A}} \W[\bmy|\bmz]{\E} \W[\bmz]{\rho}$ for any $\bmy \in \cal{P}_{d_B}$.
     \end{enumerate}
@@
 \begin{proof}
-	\nick{Proof?}
+	Proof of all properties can be found in Wang \textit{et al.}~\cite{Wang_2019} except for property (iii) which is a direct consequence of the definition of $\W{\E}$ and the corresponding property (iii) in~\cref{thm:wstate}.
 \end{proof}
-A $(d \times d)$ matrix $S$ is in $\stoch$, if
-\begin{enumerate}
-    \item $S_{ij} \geq 0$ for all $i, j \in \mathbb{Z}_d$;
-    \item $\sum\limits_{j=1}^n S_{ij} = 1$ for all $i \in \mathbb{Z}_d$;
-    \item $S\bmd = \bmd$.
-\end{enumerate}
 
@@
 This fragment is governed by simple majorization and we first prove strong equivalences for this type of majorization.
-\begin{theorem}\label{thm:major}
+\begin{proposition}\label{prop:major}
 Given $\bmx, \bmy \in \mathbb{R}^n$ the following statements are equivalent:
  \begin{enumerate}
-	\item\label{en:m1} $\bmx \prec \bmy$;
-	\item\label{en:m2} $\bmx = B \bmy$ for bistochastic $B$;
-	\item\label{en:m3} $\sum\limits_{i=1}^n \abs{x_i - t} \leq \sum\limits_{i=1}^n \abs{y_i - t}$ for all $t \in \mathbb{R}$;
-	\item\label{en:m4} $\sum\limits_{i=1}^n (x_i - t)^+ \leq \sum\limits_{i=1}^n (y_i - t)^+$ for all $t \in \mathbb{R}$ and $\sum\limits_{i=1}^n x_i = \sum\limits_{i=1}^n y_i$, where $(x)^+ = \max{\{x, 0\}}$;
-	\item\label{en:m5} $L_{\bmx}(k) \leq L_{\bmy}(k)$ for $k=1,\dots,n-1$	and $L_{\bmx}(n) = L_{\bmy}(n)$.
+	\item[(i)]\label{en:m1} $\bmx \prec \bmy$;
+	\item[(ii)]\label{en:m2} $\bmx = B \bmy$ for bistochastic $B$;
+	\item[(iii)]\label{en:m3} $\sum\limits_{i=1}^n \abs{x_i - t} \leq \sum\limits_{i=1}^n \abs{y_i - t}$ for all $t \in \mathbb{R}$;
+	\item[(iv)]\label{en:m4} $\sum\limits_{i=1}^n (x_i - t)^+ \leq \sum\limits_{i=1}^n (y_i - t)^+$ for all $t \in \mathbb{R}$ and \vspace{5pt}\\ $\sum\limits_{i=1}^n x_i = \sum\limits_{i=1}^n y_i$, where $(x)^+ = \max{\{x, 0\}}$;
+	\item[(v)]\label{en:m5} $L_{\bmx}(k) \leq L_{\bmy}(k)$ for $k=1,\dots,n-1$	and \vspace{5pt}\\ $L_{\bmx}(n) = L_{\bmy}(n)$.
  \end{enumerate}
-\end{theorem}
+\end{proposition}
 \begin{proof}
-	\nick{Proof?}
+	These simple majorisation properties are well-known and proofs can be found in~\cite{cit:marshall,cit:bhatia,cit:nielsen,cit:lostaglio}.
+	The equivalence between (i) and (ii) is the statement of the Hardy, Littlewood and Polya theorem.
 \end{proof}
@@
 
-Any $\bmd$-majorization problem can be rephrased as a simple majorization problem in a higher dimensional space via the embedding map.
+Any $\bmd$--majorization problem can be rephrased as a simple majorization problem in a higher dimensional space via the embedding map.
 \begin{definition}
-  The embedding map $\Gamma_{\bmd}:\mathbb{R}^n \mapsto \mathbb{R}^D, D = \sum\limits_{i=1}^n d_i$ is the function
+  The embedding map $\Gamma_{\bmd}:\mathbb{R}^n \mapsto \mathbb{R}^N, N = \sum\limits_{i=1}^n d_i$ is the function
   \begin{equation}
@@
 where $\bm{1}/d_i$ is the $d_i$-dimensional uniform distribution.
-The left inverse $\Gamma_{\bmd}^{-1}: \mathbb{R}^D \mapsto \mathbb{R}^n$ is defined to sum up the elements in each block of $\Gamma_{\bmd}(\bmw)$, so that
+The left inverse $\Gamma_{\bmd}^{-1}: \mathbb{R}^N \mapsto \mathbb{R}^n$ is defined to sum up the elements in each block of $\Gamma_{\bmd}(\bmw)$, so that
   \begin{equation}
@@
 The direct sum simply amounts to listing the uniform distributions one after the other.
-The embedding map maps the Gibbs distribution to the uniform distribution, $\Gamma_{\bmd}(\bmd) = \bm{1}/D$.
+The embedding map maps the Gibbs distribution to the uniform distribution, $\Gamma_{\bmd}(\bmd) = \bm{1}/N$.
 Then, a non-increasing ordering $\Gamma_{\bmd}(\bmz)^\downarrow$ in the new space, corresponds to the so-called ``$\beta$-ordering'' of the original vector denoted by the permutation $\pi$ in~\cref{def:lc}, mapping $(w_i/d_i) \mapsto (w_i/d_i)^\downarrow$ for all $i=1,\dots,n$.
@@
 
-\begin{theorem}
+We take the opportunity here	 to simply list useful equivalent statements for $\bmd$--majorisation.
+
+\begin{proposition}\label{prop:dmajor}
 Given $\bmx, \bmy, \bmd \in \mathbb{R}^n$, such that the components of $\bmd$ are positive, the following statements are equivalent:
   \begin{enumerate}
-    \item $\bmx \prec_{\bmd} \bmy$;
-    \item $\Gamma_{\bmd}({\bmx}) \prec \Gamma_{\bmd}({\bmy})$;
-    \item\label{en:tm3} $\sum\limits_{i=1}^n \abs{x_i - t d_i} \leq \sum\limits_{i=1}^n \abs{y_i - t d_i}$ for all $t \in \mathbb{R}$;
-    \item $\sum\limits_{i=1}^n (x_i - t d_i)^+ \leq \sum\limits_{i=1}^n (y_i - t d_i)^+$ for all $t \in \mathbb{R}$ and $\sum\limits_{i=1}^n x_i = \sum\limits_{i=1}^n y_i$;
-    \item $L_{\bmx|\bmd}(k) \leq L_{\bmy|\bmd}(k)$ for $k=1,\dots,n-1$	and $L_{\bmx|\bmd}(n) = L_{\bmy|\bmd}(n)$.
+    \item[(i)] $\bmx \prec_{\bmd} \bmy$;
+    \item[(ii)] $\Gamma_{\bmd}({\bmx}) \prec \Gamma_{\bmd}({\bmy})$;
+    \item[(iii)]\label{en:tm3} $\sum\limits_{i=1}^n \abs{x_i - t d_i} \leq \sum\limits_{i=1}^n \abs{y_i - t d_i}$ for all $t \in \mathbb{R}$;
+    \item[(iv)] $\sum\limits_{i=1}^n (x_i - t d_i)^+ \leq \sum\limits_{i=1}^n (y_i - t d_i)^+$ for all $t \in \mathbb{R}$ and \vspace{5pt}\\ $\sum\limits_{i=1}^n x_i = \sum\limits_{i=1}^n y_i$;
+    \item[(v)] $L_{\bmx|\bmd}(k) \leq L_{\bmy|\bmd}(k)$ for $k=1,\dots,n-1$	 and \vspace{5pt}\\ $L_{\bmx|\bmd}(n) = L_{\bmy|\bmd}(n)$.
   \end{enumerate}
-\end{theorem}
-\begin{proof}
-  \nick{Proof?}
-\end{proof}
-\iffalse
+\end{proposition}
+\begin{proof}$ $\vspace{-12pt}\\
 \begin{enumerate}
 	\item[1$\leftrightarrow2$]
-        Suppose now there exists a stochastic $S$ such that $\bmx = S\bmy$ with $\bmd = S\bmd$ and let $B = \Gamma_{\bmd} \circ S \circ \Gamma_{\bmd}^{-1}$.
-        $B$ is a $D$-dimensional bistochastic matrix, since composition of stochastic matrices is stochastic and $(\Gamma_{\bmd} \circ S \circ \Gamma_{\bmd}^{-1}) (\frac{1}{D}\bm{1}) = (\Gamma_{\bmd} \circ S) (\bm{d}) = \Gamma_{\bmd}(\bm{d}) = \frac{1}{D}\bm{1}$.
+	Suppose there exists a $\bmd$--stochastic $S$ such that $\bmx = S\bmy$ and let $B = \Gamma_{\bmd} \circ S \circ \Gamma_{\bmd}^{-1}$.
+$B$ is a $N$-dimensional bistochastic matrix, since composition of stochastic matrices is stochastic and $(\Gamma_{\bmd} \circ S \circ \Gamma_{\bmd}^{-1}) (\frac{1}{N}\bm{1}) = (\Gamma_{\bmd} \circ S) (\bm{d}) = \Gamma_{\bmd}(\bm{d}) = \frac{1}{N}\bm{1}$.
 Then, $B$ maps $\Gamma_{\bmd}({\bmy})$ to $\Gamma_{\bmd}({\bmx})$.
 	Conversely, given $B$, let $S = \Gamma_{\bmd}^{-1} \circ B \circ \Gamma_{\bmd}$.
-        Similarly, $S$ is the stochastic matrix that preserves $\bmd$ and maps $\bmy$ to $\bmx$.
-        \item[$2\leftrightarrow3$]\hspace{-5pt}, $2\leftrightarrow4$, $2\leftrightarrow5$ These three statement are equivalent to \nick{blah} respectively for the embedded vectors $\Gamma_{\bmd}({\bmx}), \Gamma_{\bmd}({\bmy})$.
-        This is clear by rewriting
-        \begin{align}
-            \sum\limits_{i=1}^n \abs{x_i - t d_i} &= \sum\limits_{i=1}^n d_i \abs{\frac{x_i}{d_i} - t} = \sum\limits_{i=1}^D \abs{\Gamma_{\bmd}(\bmx)_i - t}, \\
-            \sum\limits_{i=1}^n (x_i - t d_i)^+ &= \sum\limits_{i=1}^D (\Gamma_{\bmd}(\bmx)_i - t)^+, \\
-            L_{\bmx|\bmd}(k) &= L_{\Gamma_{\bmd}(\bmx)}(k'), \\
-            \text{with}\ k&=1,\dots,n\ \text{and}\ k'=1,\dots,D \nonumber
-        \end{align} 
-        and similarly for the right hand side.
+	Similarly, $S$ is a $\bmd$--stochastic matrix that maps $\bmy$ to $\bmx$.
+	\item[$2\leftrightarrow3$]\hspace{-5pt}, $2\leftrightarrow4$, $2\leftrightarrow5$ These three statements are equivalent to statements (iii), (iv), (v) in~\cref{prop:major} respectively, for the embedded vectors $\Gamma_{\bmd}({\bmx}), \Gamma_{\bmd}({\bmy})$, which becomes apparent by rewriting
+	\begin{align*}
+	&\sum\limits_{i=1}^n \abs{x_i - t d_i} = \sum\limits_{i=1}^n d_i \abs{\frac{x_i}{d_i} - t} = \sum\limits_{i=1}^N \abs{\Gamma_{\bmd}(\bmx)_i - t}, \\
+	&\sum\limits_{i=1}^n (x_i - t d_i)^+ = \sum\limits_{i=1}^N (\Gamma_{\bmd}(\bmx)_i - t)^+, \\
+	&L_{\bmx|\bmd}(k) = L_{\Gamma_{\bmd}(\bmx)}(k'), \text{with}\ k=1,\dots,n\ \\
+	&\text{and}\ k'=1,\dots,N, \nonumber
+	\end{align*} 
+and similarly for the right hand sides of the inequalities.
 \end{enumerate}
-\fi
+\vspace{-19pt}
+\end{proof}
 
@@
 
-\nick{this section hasn't been refereced in various parts of the main text}
+In this section, we provide some useful technical properties of general $\sigma$--fragments.
 
-\begin{theorem}\label{thm:frag_app}
+\begin{proposition}\label{thm:frag_app}
     Let $\R_\sigma = (\O_\sigma, \F_\sigma)$ be a $\sigma$--fragment of magic theory $\R = (\O, \F)$. 
@@
         \begin{equation*}
-            \O_{\sigma} \cap \O_{\sigma'} \subseteq \O_{p\sigma + (1-p)\sigma'}\ \text{for all}\ p \in [0,1].
+            \O_{\sigma} \cap \O_{\sigma'} \subseteq \O_{p\sigma + (1-p)\sigma'}\ \text{for any}\ p \in [0,1].
         \end{equation*}
-        \item Let $\E$ be a $\cptp$ operation with Wigner distribution $\W{\E}$.
-        For $\R = \Rmax$, $\E \in \O_\sigma$ iff $\W{\E} \in \stochw$. \nick{I don't like this one}
     \end{enumerate}
-\end{theorem}
-\begin{proof}$ $\\
+\end{proposition}
+\begin{proof}$ $\vspace{-12pt}\\
 
@@
     Then, $\W{\E} \W{p\sigma + (1-p)\sigma'} = \W{p\sigma + (1-p)\sigma'}$ for any $p \in [0,1]$ due to the additive property~\ref{en:w4} of the Wigner distribution, implying that state $p\sigma + (1-p)\sigma'$ is also left invariant by $\E$.
-
-    \item Let $\O_\sigma' \coloneqq \{ \E \in \cptp: \W{\E} \in \stochw \}$ be the described set of operations.
-
-    Suppose $\E$ is in $\O_\sigma$, then $\E \in \cptp$ and $\W{\E} \in \stochw$ due to property~\ref{en:wo4} of~\cref{thm:wchannel}, hence $\O_\sigma \subseteq \O_\sigma'$.
-
-    Conversely, suppose $\E \in \cptp$ with $\W{\E} \in \stochw$. 
-    Then, $\W[\bmy|\bmx]{\E} \geq 0$ for all $\bmx, \bmy$, hence $\E \in \O$.
-    Furthermore, $\W{\E} \W{\sigma} = \W{\sigma}$ implies $\E(\sigma) = \sigma$ using~\cref{eq:woperation} defined for any $\cptp$ operation $\E$.
-    Hence, $\O_\sigma' \subseteq \O_\sigma$.
 \end{enumerate}
+\vspace{-20pt}
 \end{proof}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Properties of Lorenz curves}
-\label{app:lc_properties}
-
-\nick{Prove statements underneath~\cref{def:lc}?}
-
-\subsection{Basic properties}
-
-Furthermore, single-copy Lorenz curves are simply additive in noise, 
-\begin{equation}
-	\lc{(1-\epsilon)\rho + \epsilon\sigma}{\sigma} = (1-\epsilon)\lc{\rho}{\sigma} + \epsilon\lc{\sigma}{\sigma},
-\end{equation}
-for any $\sigma, \rho$.
-This is not true for higher number of copies.
-
-\subsection{$\sigma$--fragment continuity}
-
-\begin{proposition}\label{thm:lccont}
-	The Lorenz curve $\lc{\rho}{\sigma}(x)$ of a state $\rho$ with respect to state $\sigma$ is uniformly continuous in $\sigma$.
-\end{proposition}
-\begin{proof}
-	\nick{Idea:} If $\sigma$ and $\sigma'$ are $\delta$-close with respect to a state norm, then the curves $\lc{\rho}{\sigma}(x)$ and $\lc{\rho}{\sigma'}(x)$ are $\epsilon$-close at all $x \in [0,1]$.
-\end{proof}
-
-\subsection{Area monotone}\label{app:areamono}
-
-\nick{I don't believe in the area monotone - should we keep?}
-
-\begin{figure}[h]%
-    \centering
-    \subfigure[][]{%
-    \label{fig:test1}%
-    \includegraphics[height=3cm]{figs/negmasking_rho_strange_lc.pdf}
-    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
-    }\hspace{8pt}%
-    \subfigure[][]{%
-    \label{fig:test2}%
-    \includegraphics[height=3cm]{figs/negmasking_rho_strange_meas.pdf}
-    %\caption{Zero state $\ketbra{0}{0}$}%
-    }
-    \caption{\subref{fig:test1} Lorenz curve of $p\ketbra{\rm{S}} + (1-p) \frac{1}{d}\id$ for $p$ given in the legend.\subref{fig:test2} Different measures for the states on the left. \\
-    \nick{can replace~\cref{fig:lctoy} with a more informative version of this figure}
-    }%
-    \label{fig:test}
-\end{figure}
-
-Let $L_{>1}$ be the set of points on the Lorenz curve $\lc{\rho}{\sigma}(k)$ that lie above $1$ of state $\rho$ in the $\sigma$--fragment. 
-If $\rho$ is a free state, $L_{>1}$ is empty and $\A_\sigma(\rho) = 0$. 
-Otherwise, $\A_\sigma(\rho) > 0$ and it can be calculated exactly using the trapezium rule or the shoelace formula. 
-Let $k$ be the index of the first point $\left(x_k, \lc{\rho}{\sigma}(k)\right)$ lying above $1$. 
-Then $L_\rho(k)$ crosses $1$ at
-\begin{equation}
-	x_{\rm{int}} = x_k - \frac{x_k - x_{k-1}}{\lc{\rho}{\sigma}(k) - \lc{\rho}{\sigma}(k-1)}\lc{\rho}{\sigma}(k),\vspace{10pt}
-\end{equation}
-as well as at $\left(x_d, \lc{\rho}{\sigma}(d)\right) = (1,1)$
-
-Now we can define
-\begin{equation}
-L_{>1}^+ = \{ (x_i, y_i) \}_{0 \leq i \leq n}
-\end{equation}
-such that it contains the initial point of intersection $(x_0, y_0) \equiv (x_{n+1}, y_{n+1}) \coloneqq (x_{\rm{int}}, 1)$, all points $(x_i, y_i)$, labelled by $i=1,\dots,n-1$ that lie above $y=1$ contained in $L_{>1}$ and finally the second point of intersection $(x_n, y_n) = (1,1)$.
-Then, 
-\begin{equation}
-	\A_\sigma(\rho) = \frac{1}{2} \sum\limits_{i=0}^n (x_{i+1} y_i - x_i y_{i+1}).
-\end{equation}
-
-\subsection{Lorenz curve independent constraints}\label{app:lc_constraints}
-
-\begin{theorem}\label{thm:elbows}
+We now prove a result referenced in~\cref{sec:lc}.
+\begin{proposition}\label{thm:elbows}
 	Let $\rho, \tau$ be two quantum states with Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in the $\sigma$--fragment.
@@
 	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\tau}{\sigma}(x_{i})$ for all $i =1,\dots,t$.
-\end{theorem}
+\end{proposition}
 \begin{proof}	
@@
 \end{proof}
-This theorem is of practical importance in calculating the necessary distillation constraints derived via majorization.
-
-\nick{In particular}, it can be used in the discussion of standard Lorenz curves to set the necessary constraints,
-\begin{align}
-L\left(x_{I'(0, m'_{0}, 9^{n-n'})}\right) &\geq L\left(x_{I'(0, m'_{0}, 9^{n-n'})}\right), \nonumber\\
-L\left(x_{I'(1, m'_{1}, 9^{n-n'})}\right) &\geq L\left(x_{I'(1, m'_{1}, 9^{n-n'})}\right), \nonumber\\
-&\vdotswithin{=} \nonumber\\
-L\left(x_{I'(n', m'_{r}, 9^{n-n'})}\right) &\geq L\left(x_{I'(n', m'_{n'}, 9^{n-n'})}\right), \nonumber
-\end{align}
-where $x_{I'(0, m'_{0}, 9^{n - n'})}, x_{I'(1, m'_{1}, 9^{n - n'})}, \dots, x_{I'(n', m'_{n'}, 9^{n - n'})} \in T$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon')^{\otimes n'}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).
+This theorem is of practical importance in calculating the necessary distillation constraints derived via majorization in $\sigma$--fragments.
 
@@
 
-\section{Technical derivation for Lorenz curves in unital fragment}
+\section{Lorenz curves in the unital fragment}
 \label{app:lcsu_technical}
@@
 Consider an experiment consisting of $n$ trials of throwing a $p$-coin, that is a coin with probability $p$ of landing on one side and $1-p$ of landing on the other.
-This scenario describes the construction of an $n$-copy Strange state Wigner distribution from a single-copy as presented in~\cref{sec:lcsu}.
-The experiment is described by binomial statistics and we write down the sum over an even number of successful trials $\Phi_+$ (over an odd number of successful trials $\Phi_-$),
+We express the sum over an even number of successful trials $\Phi_+$ and the sum over an odd number of successful trials $\Phi_-$,
 \begin{align}	
-	\Phi_+(af; nf, p) &\coloneqq \sum\limits_{\ell=0}^{af/2} \binom{nf}{2\ell} p^{2\ell} (1-p)^{nf-2\ell}, \nonumber\\ 
-	&\text{for even integers } af\in[0,nf], \label{eq:fp_app} \\
-	\Phi_-(af; nf, p) &\coloneqq \sum\limits_{\ell=1}^{(af-1)/2} \binom{nf}{2\ell+1} p^{2\ell+1} (1-p)^{nf-(2\ell+1)}, \nonumber\\ 
-	&\text{for odd integers } af\in[0,nf]. \label{eq:fn_app}
+	\Phi_+(a; n, p) &\coloneqq \sum\limits_{\ell=0}^{a/2} \binom{n}{2\ell} p^{2\ell} (1-p)^{n-2\ell}, \nonumber\\ 
+	&\text{for even integers } m\in[0,n], \label{eq:fp_app} \\
+	\Phi_-(a; n, p) &\coloneqq \sum\limits_{\ell=1}^{(a-1)/2} \binom{n}{2\ell+1} p^{2\ell+1} (1-p)^{n-(2\ell+1)}, \nonumber\\ 
+	&\text{for odd integers }m\in[0,n]. \label{eq:fn_app}
 \end{align}
-Note that index $af$ only takes even (odd) values when labelling $\Phi_+$ ($\Phi_-$).
-In~\cref{app:lcsu_coord_elb}, we will use $\Phi_+$ and $\Phi_-$ to express the elbow coordinates of standard Lorenz curves.
+Note that index $m$ only takes even (odd) values when labelling $\Phi_+$ ($\Phi_-$).
+In~\cref{app:lcsu_coord_elb}, we will use $\Phi_+$ and $\Phi_-$ to express the elbow coordinates of Lorenz curves in the unital fragment.
 
-We define the classical entropy of a $p$-coin as well as the classical relative entropy between a $p$-coin and a $q$-coin,
+We also define the classical entropy of a $p$-coin as well as the classical relative entropy between a $p$-coin and a $q$-coin,
 \begin{align}
@@
 
-\subsection{Standard Lorenz curve elbow coordinates}\label{app:lcsu_coord_elb}
+\subsection{Strange state Lorenz curve elbow coordinates in the unital fragment}\label{app:lcsu_coord_elb}
 The Wigner distribution of the $n$-copy qutrit maximally mixed state $\left(\id/3\right)^{\otimes n}$ is the uniform distribution 
@@
 \label{app:cmpairs}
-
-In general, a $1$-copy $d$-dimensional state is defined exactly by its $d^2$ Wigner distribution $W$. 
-The distribution $W$ can always be described by a Wigner-component vector $\bmw = (w_i)_{i=1,\dots,D}$ and a multiplicity vector $\bmm = (m_i)_{i=1,\dots,D}$, where $D \leq d^2$ and they form component-multiplicity pairs denoted by $\{(w_i, m_i)\}_{i=1,\dots,D}$.
+In general, a $1$-copy $d$--dimensional state $\rho$ is defined exactly by its $d^2$--dimensional Wigner distribution $\W{\rho}$. 
+The distribution $\W{\rho}$ is usually defined on the phase space, but it can be convenient to define it using pure vector notation. 
+In particular, we introduce a component vector $\bmw(\rho) = (w_i)_{i=1,\dots,D}$ and a multiplicity vector $\bmm(\rho) = (m_i)_{i=1,\dots,D}$, where $D \leq d^2$ which together form a set of component-multiplicity pairs $\{(w_i, m_i)\}_{i=1,\dots,D}$.
 \begin{definition}
-	Consider a $d^2$-dimensional distribution $W$ and a positive integer $D$. 
-	We call the set of order pairs $\{(w_i, m_i)\}_{i=1,\dots,D}$ a \emph{complete set of component-multiplicity pairs}, if $W$ contains $m_i$ components $w_i$ and $\sum_{i=0}^D m_i = d^2$.
+	Consider a distribution $W$ and a positive integer $D \leq {\rm{dim}}\hspace{1pt}W$. 
+	We call the set of ordered pairs $\{(w_i, m_i)\}_{i=1,\dots,D}$ a \emph{complete set of component-multiplicity pairs}, if $W$ contains $m_i$ components $w_i$ and $\sum_{i=0}^D m_i = d^2$.
 \end{definition}
-Therefore, such a set that describes a distribution $W$ contains in its description each component of $W$ exactly once.
+Therefore, such a set describes each component of $\W{\rho}$ exactly once.
 As an example, two complete sets of pairs for the Strange state are $\{( -1/3, 1), ( 1/6, 8)\}$ and $\{(-1/3, 1), (1/6, 2), (1/6, 3), (1/6, 3)\}$.
@@
 \end{align}
-so result holds for this too \nick{FIX SECTION}.
+so a complete set of component-multiplicity pairs can be obtained for this distribution in the same fashion as for usual Wigner distributions.
 
@@
 \begin{lemma}\label{lem:ncopycomponents}
-	Let $W$ be a $d$-dimensional distribution defined by a complete set of component-multiplicity pairs $\{(w_i, m_i)\}_{i=1,\dots,D}$ with $D \leq d$ and consider the distribution $W^{\otimes n}$ obtained by taking the Kronecker product $W \otimes \dots \otimes W$ between $n$ copies of $W$.
+	Let $W$ be a distribution defined by a complete set of component-multiplicity pairs $\{(w_i, m_i)\}_{i=1,\dots,D}$ with $D \leq {\rm{dim}}\hspace{1pt}W$ and consider the distribution $W^{\otimes n}$ obtained by taking the Kronecker product $W \otimes \dots \otimes W$ between $n$ copies of $W$.
 
@@
 	Assume $n = 1$.
-	Let $\bmk_i \coloneqq (0,\dots,0,1,0,\dots,0)$ be a vector with its $i$-th component equal to 1 and 0's elsewhere.
+	Let $\bmk_i$ be the vector with its $i$-th component equal to 1 and 0's elsewhere.
 	The set $C_D^1$ consists of all vectors of this form, i.e. 
@@
 
+Index vector $\bmk$ has $D-1$ independent components and in the proof of our main theorem in~\cref{sec:stab} we have $D=4$, so we simplify the notation by writing the component and multiplicity vectors of the $n$-copy state distributions as $m_{ijk}, w(\rho_{\rm{S}})_{ijk}, w(\gamma)_{ijk}$ and $w(\rho_{\rm{S}}|\gamma)_{ijk}$, where $i,j,k$ are the 3 independent index components.
+
 \subsection{First elbow location}
 \label{app:first_elb_loc}
+Consider a magic state interconversion in a stabilizer $\sigma$--fragment, as in~\cref{eq:stdist}, where we remind that $n \geq n'$ and we denote by $(x_0, L_0)$ and $(x'_0, L'_0)$ the first elbow coordinates of the initial and target states respectively.
 
-Here, we show that the horizontal location of the first elbow is lower for an initial state compared to the target state for a valid distillation process ($n > n'$).
-\begin{enumerate}
-	\item $\rm{(C1)} \rightarrow \rm{(C1)}$. 
-	It is always true that $e^{-\beta E_0} / \Z_\beta \leq 1$, so
+Here, we show that $x_0 \leq x'_0$ for any of the three scenarios outlined in the proof of our main theorem in~\cref{sec:stab}.\\
+
+1. $\rm{(C1)} \rightarrow \rm{(C1)}$.
+We know from statistical physics that $e^{-\beta E_0} / \Z_\beta \leq 1$, so
 	\begin{align*}
@@
 	\end{align*}
-	\item $\rm{(C2)} \rightarrow \rm{(C1)}$.
-	It is always true that
+
+2. $\rm{(C2)} \rightarrow \rm{(C1)}$.
+We now use the slightly altered inequality $e^{-\beta E_{\rm{max}}} / \Z_\beta \leq 1$ to proceed,
 	\begin{align*}
-		&\Z_\beta^{n-n'} > (e^{-\beta E_{\rm{max}}})^{n-n'} = e^{-\beta (n-n') E_{\rm{max}}}, \text{ so} \\
 		x_0 &= \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^n = \dfrac{e^{-\beta(n E_{\rm{max}} - n' E_0)}}{\Z_\beta^{n-n'}} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} \\
-		&< \dfrac{e^{-\beta(n E_{\rm{max}} - n' E_0)}}{e^{-\beta (n-n') E_{\rm{max}}}} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} \\
+		&\leq \dfrac{e^{-\beta(n E_{\rm{max}} - n' E_0)}}{e^{-\beta (n-n') E_{\rm{max}}}} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} \\
 		&= e^{-\beta n' (E_{\rm{max}} - E_0)} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} \\
@@
 	\end{align*}
-	\item $\rm{(C2)} \rightarrow \rm{(C2)}$.
-	It is always true that $e^{-\beta E_{\rm{max}}} / \Z_\beta \leq 1$, so
+
+3. $\rm{(C2)} \rightarrow \rm{(C2)}$.
+Similarly in this scenario,
 	\begin{align*}
@@
 	\end{align*}
-\end{enumerate}

### 2021-03-24 magic_paper.tex
Fixed appendices, except for unital fragment appendix. What do we include there / what do we get rid of?

@@
 \begin{document}
+% - vs -- (n-copy, sigma-fragment etc.)
+% Plot consistency (esp Figs. 3, 4, 5, 6)
+%
+%
+%
 
@@
     \item Fault-tolerance~\cite{cit:raussendorf, cit:gross2, cit:markov, cit:gross, cit:nest, cit:nest2, cit:vidal, cit:fujii, cit:gottesman}
-    \item Magic~\cite{cit:veitch, cit:veitch2, cit:wang, cit:wang2, cit:howard, cit:campbell, cit:gross3, cit:gross4}
+    \item Magic~\cite{cit:veitch, cit:veitch2, Wang_2019, Wang_2018, cit:howard, cit:campbell, cit:gross3, cit:gross4}
     \item Bringing in majorisation~\cite{cit:cwiklinski, cit:lostaglio2, cit:lostaglio, cit:gour, cit:janzing, cit:brandao2, cit:gour2, cit:marshall, cit:nielsen}
@@
 However, there exist mixed states with non-negative Wigner distributions that are not mixtures of stabiliser states~\cite{cit:gross}.
-Therefore, stabiliser-preserving theories have been extended to a theory that preserves state ``Wigner positivity''~\cite{cit:wang}, formally defined in~\cref{sec:wigner} for odd prime dimensions.
+Therefore, stabiliser-preserving theories have been extended to a theory that preserves state ``Wigner positivity''~\cite{Wang_2019}, formally defined in~\cref{sec:wigner} for odd prime dimensions.
 Informally, it can be considered as the maximal theory of magic $\Rmax = (\Fmax, \Omax)$, where free states have non-negative Wigner distributions and free operations completely preserve this property.\\
@@
 Mana is an additive\footnote{It satisfies the condition $\mana{\rho_1 \otimes \rho_2} = \mana{\rho_1} + \mana{\rho_2}$ which is practical in distillation settings.} magic monotone, so it provides an analytical, necessary condition for many-copy magic state interconvertibility.
+The magic monotone of \emph{max--thauma}~\cref{Wang_2018} has also been introduced more recently for qudits of odd prime dimension.
 
@@
 To formally state majorisation results, we first denote by $\stoch$ the set of $(d \times d)$ stochastic matrices that preserve the probability vector $\bmd$.
-Specifically, for any $S \in \stoch$, all matrix elements are non-negative, all rows sum to $1$ and $S\bmd = \bmd$.
-The set $\stoch$ forms a group under matrix multiplication for all $\bmd$ with positive components.
+Specifically, for any \emph{$\bmd$--stochastic matrix} $S \in \stoch$, all matrix elements are non-negative, all rows sum to $1$ and $S\bmd = \bmd$.
+The set $\stoch$ forms a group under matrix multiplication for any $\bmd$ with positive components.
 
@@
 Informally, there exists a thermal operation $\E$ such that $\tau = \E(\rho)$ if and only if there exists a matrix $S \in \stoch$ such that $\bm{q} = S\bm{p}$, where $\bm{q}, \bm{p}$ and $\bmd$ and the energy level population vectors of $\tau, \rho, \gamma_\beta$ respectively.
-Formal statements of the above can be found \nick{in the appendix}.
 
-Based on this setting, we define majorisation as follows.
-\begin{definition}[\textbf{$\boldsymbol\bmd$-majorisation}]\label{def:dmajor}
-    Given $\bmx, \bmy, \bmd \in \reals^d$, such that the components of $\bmd$ are positive, $\bmy$ is said to $\bmd$-majorise $\bmx$, iff there exists a matrix $S \in \stoch$ such that $\bmx = S\bmy$.
+Based on this setting, we define $\bmd$--majorisation as follows.
+\begin{definition}[\textbf{$\boldsymbol\bmd$--majorisation}]\label{def:dmajor}
+    Given $\bmx, \bmy, \bmd \in \reals^d$, such that the components of $\bmd$ are positive, $\bmy$ is said to $\bmd$--majorise $\bmx$, iff there exists a $\bmd$--stochastic matrix $S$ such that $\bmx = S\bmy$.
 \end{definition}
@@
 
-The pre-order imposed by $\bmd$-majorisation admits a numerically efficient reformulation in terms of Lorenz curves.
+The pre-order imposed by $\bmd$--majorisation admits a numerically efficient reformulation in terms of Lorenz curves.
 Let the vector $\bmu^\downarrow$ denote the vector $\bmu \in \reals^d$ with its components arranged in non-increasing order.
 \begin{definition}[\textbf{Lorenz curve}]\label{def:lc}
-    Let $\bmw, \bmd \in \reals^d$, where the components of $\bmd$ are positive with $D = \sum_{i=1}^d d_i$ and denote by $\widetilde{\bmw} \coloneqq (w_1/d_1, \dots, w_d/\nick{d_d})^T$ the vector of ratios between the corresponding components of $\bmw$ and $\bmd$.
+    Let $\bmw, \bmd \in \reals^d$, where the components of $\bmd$ are positive with $D = \sum_{i=1}^d d_i$ and denote by $\widetilde{\bmw} \coloneqq (w_1/d_1, \dots, w_d/\nick{d_d})^T$ the rescaled vector $\bmw$ by $\bmd$.
 
@@
 Components $x_k$ are rescaled by $D$ so that comparison of curves with unequal dimensions is possible.
-In fact, the Lorenz curves $\lc{\bmw}{\bmd}$ and $\lc{\bmw \otimes \bmd}{\bmd \otimes \bmd}$, where $\otimes$ denotes the Kronecker product, are identical.
-Furthermore, a Lorenz curve $\lc{\bmw}{\bmd}(x)$ is always concave in $x$, since it consists of $d$ line segments each with slope $(\widetilde{\bmw}^\downarrow)_i$ for $i=1,\dots,d$ which is non-increasing by definition.
-Finally, the points on the interior of the Lorenz curve connecting line segments of different slopes are called \emph{elbows}.
+In fact, the Lorenz curves $\lc{\bmw}{\bmd}$ and $\lc{\bmw \otimes \bmd}{\bmd \otimes \bmd}$, where $\otimes$ denotes the Kronecker product, coincide.
+Furthermore, a Lorenz curve $\lc{\bmw}{\bmd}(x)$ is always concave in $x$, since it consists of $d$ line segments each with slope $(\widetilde{\bmw}^\downarrow)_i$ for $i=1,\dots,d$ which by definition is a non-increasing sequence.
+Finally, the points on the interior of the Lorenz curve that connect line segments of different slopes are in general non-differentiable and we call them\emph{elbows}.
 
@@
 The free operations should send the set of free states $\Fmax$ into itself and completely preserve the non-negativity of the states, in the sense that $\E \in \Omax$ iff $(\id_d \otimes \E ) \sigma \in \stab$ for all odd prime dimensions $d$ whenever $\sigma \in \Fmax$.
-It is shown by Wang \textit{et al.}~\cite{cit:wang} that $\Omax$ coincides with the set of operations $\E$ with stochastic Wigner distributions, 
+It is shown by Wang \textit{et al.}~\cite{Wang_2019} that $\Omax$ coincides with the set of operations $\E$ with stochastic Wigner distributions, 
 \begin{equation}
@@
     Each $\O_\sigma$ is extensible to a set of stochastic maps outside the $\cptp$ operations.
-    Within each $\sigma$--fragment $\bmd$-majorisation can be used allowing for an intricate, but tractable approach towards the study of magic state interconversion.
+    Within each $\sigma$--fragment $\bmd$--majorisation can be used allowing for tractable approach towards the study of magic state interconversion.
     }
@@
 The zoo of all magic operation classes is summarised in ~\cref{fig:zoo}.
-Completely positive-Wigner-preserving operations~\cite{cit:wang} form the maximal operation class $\Omax$.
+It is clear from the diagram that free operations are in general mapped onto strict subsets of stochastic maps.
+This statement, along with more technical properties of the $\sigma$--fragment are discussed in~\cref{app:frag}.
+Completely positive-Wigner-preserving operations~\cite{Wang_2019} form the maximal operation class $\Omax$.
 This theory of magic is thus covered by $\sigma$--fragments exactly and every other magic theory is contained within this cover.
@@
 removes coherent phases in the computational basis and therefore leaves exactly all mixtures of computational basis states invariant.
-A noise channel consisting only of such dephasing operations can be fully analysed in the $\sigma$--fragments for the pure computational basis states $\sigma$.
-\nick{Have proven in appendix that we need to consider \emph{only} the pure stabiliser fragments - not mixed ones}
+A noise channel consisting only of such dephasing operations can be fully analysed in the $\sigma$--fragments for the pure computational basis states $\sigma$ as proven in~\cref{app:frag}.
 
@@
 
-It is then apparent that the pre-order $\prec_{\R_\sigma}$ between the operations in the $\sigma$--fragment follows the rules of $\bmd$-majorisation as outlined in~\cref{sec:major}.
+It is then apparent that the pre-order $\prec_{\R_\sigma}$ between the operations in the $\sigma$--fragment follows the rules of $\bmd$--majorisation as outlined in~\cref{sec:major}.
 In particular, the pre-order $\prec_{\R_\sigma}$ of the $\sigma$--fragment $\R_\sigma = (\F, \O_\sigma)$ between $d$-dimensional states corresponds to the majorisation pre-order $\prec_{\W{\sigma}}$ between their $d^2$-dimensional Wigner distributions.
@@
 \end{proof}
+The converse is in general not true, since stochastic matrices do not necessarily correspond to valid quantum operations.
 
@@
 \subsection{Lorenz curves of quasi-probabilities in $\sigma$--fragments}
+\label{sec:lc}
 
 It is straightforward to construct Lorenz curves for Wigner distributions in any $\sigma$--fragment.
-As we have seen in~\cref{thm:sigmamajor}, for any full-rank free state $\sigma$ we have that $\W{\sigma}$ is a strictly positive full-rank probability distribution, and so one can define a corresponding notion of $d$--majorisation on \emph{quasi}--distributions.
+As we have seen in~\cref{thm:sigmamajor}, for any full-rank free state $\sigma$ we have that $\W{\sigma}$ is a strictly positive full-rank probability distribution, and so one can define a corresponding notion of $\bmd$--majorisation on \emph{quasi}--distributions.
 We write $\lc{\rho}{\sigma}(x)$ for the Lorenz curve of $\W{\rho}$ with respect to $\W{\sigma}$.
@@
 We can refine the number of independent constraints stemming from this inequality. 
-In fact, there are only as many independent constraints as there are elbows in the Lorenz curve of the target state as shown in~\cref{app:lc_constraints}.
+In fact, there are only as many independent constraints as there are elbows in the Lorenz curve of the target state as shown in~\cref{thm:elbows} in~\cref{app:frag}.
 However, in principle any one location $x$ provides a valid constraint leading to some upper distillation bound, while optimising over the location would provide the strictest bound.
@@
 	If $x_0 < x'_0$, then it holds that
-\begin{equation}\label{eq:first_elb_bound}
+\begin{equation}\label{eq:first_elb_bound1}
 	\frac{L_0}{x_0} \geq \frac{L_0'}{x_0'}.
@@
 Since $x_0 < x'_0$, we can find the target state Lorenz curve coordinate $L'_\star$ at location $x = x_0$ by interpolating between the origin and the target state's first elbow, 
-\begin{equation}\label{eq:constraint_deriv_temp}
+\begin{equation}
 	L'_\star = \frac{x_0}{x'_0}L'_0.
 \end{equation}
-We need $L_0 \geq L_\star'$ and rearranging we get~\cref{eq:constraint_deriv_temp}.
+We need $L_0 \geq L_\star'$ and rearranging we get~\cref{eq:first_elb_bound1}.
 \end{proof}
@@
 
-The area $\A_\sigma(\rho)$ between the curve $L_{\rho|\sigma}$ and the line $y=1$ is a resource monotone in the $\sigma$--fragment. 
+The area $\A_\sigma(\rho)$ between the curve $L_{\rho|\sigma}$ and the line $y=1$ is also a resource monotone in the $\sigma$--fragment. 
 This is clear because for any state conversion like~\cref{eq:sigma_conv}, the Lorenz curve $L_{\tau|\sigma}$ is lower than $L_{\rho|\sigma}$, hence $\A_\sigma(\E(\rho)) \leq \A_\sigma(\rho)$.
-The exact form of the monotone is given in~\cref{app:areamono}.
-\nick{should we include the area? Have a look at~\cref{app:areamono}}
+It cannot be directly expressed in terms of mana, as it depends on positive Wigner components as well.
 
@@
 The first elbow of the target state is located at $x'_0 = \frac{1}{9^{n'}} > x_0$, so we can use the first elbow condition,
-\begin{equation}\label{eq:first_elb_bound}
+\begin{equation}\label{eq:first_elb_bound2}
 	\frac{L_0}{x_0} \geq \frac{L_0'}{x_0'},
@@
 to compute analytical distillation bounds for distillation rate $R = R(\epsilon, \epsilon') \coloneqq n'/n$ in the unital fragment.
-We substitute coordinates from~\cref{eq:first_elb_coords} appropriately in~\cref{eq:first_elb_bound} to get
+We substitute coordinates from~\cref{eq:first_elb_coords} appropriately in~\cref{eq:first_elb_bound2} to get
 \begin{equation}
@@
 \begin{equation}
-	R \leq \frac{\mana{\rho_{\rm{S}}}(\epsilon)}{\mana{\rho_{\rm{S}}}(0)} = 1 + \frac{\ln \left(1 - \frac{8}{15}\epsilon \right)}{\ln \frac{5}{3}}.
+	R \leq \frac{\mana{\rho_{\rm{S}}(\epsilon)}}{\mana{\rho_{\rm{S}}(0)}} = 1 + \frac{\ln \left(1 - \frac{8}{15}\epsilon \right)}{\ln \frac{5}{3}}.
 \end{equation}
-Using the properties of super-additivity and vanishing at free states of the max--thauma, we obtain
-\begin{equation}
-	\theta_{\rm{max}}(\rho_{\rm{S}}(\epsilon)) \geq (1-\epsilon) \ketbra{\rm{S}} + \epsilon \frac{1}{3}\id = (1-\epsilon) \theta_{\rm{max}}(\rho_{\rm{S}}(0)),
-\end{equation}
+Using the max--thaum properties of super-additivity and vanishing at free states, we obtain
+\begin{align}
+	&\theta_{\rm{max}}(\rho_{\rm{S}}(\epsilon)) \geq (1-\epsilon) \theta_{\rm{max}}(\ketbra{\rm{S}}) + \epsilon \theta_{\rm{max}}\left(\frac{1}{3}\id \right) = \nonumber\\
+	&(1-\epsilon) \theta_{\rm{max}}(\rho_{\rm{S}}(0)),
+\end{align}
 so that for a deterministic single-copy distillation process, an initial number of copies $n \geq \theta_{\rm{max}}(\tau) / \theta_{\rm{max}}(\rho) \geq 1-\epsilon$ is required.
@@
     \includegraphics[scale=0.5]{figs/distill_bounds.pdf}
-    \caption{\textbf{Distillation bounds in the unital fragment.} Distillation bounds obtained by majorisation, mana and the line $1-\epsilon$ (tightest bound of max--thauma) are plotted for $\epsilon' = 0$, up to noise level $\epsilon = \frac{3}{7}$.
+    \caption{\textbf{Distillation bounds in the unital fragment.} Distillation bounds obtained by majorisation, mana and the line $1-\epsilon$ (tightest bound of max--thauma) are plotted for $\epsilon' = 0$, up to noise level $\epsilon = 3/7$.
     Majorisation consistently provides stricter rates than mana and max--thauma.
@@
 They are parametrised by three independent components $i,j,k$, with sum $\alpha \coloneqq i+j+k \leq n$.
-Then, the $n$-copy multiplicity is given by
+The $n$-copy multiplicity is given by
 \begin{equation}
@@
 Therefore, we can use the first elbow condition,
-\begin{equation}\label{eq:first_elb_bound}
+\begin{equation}\label{eq:first_elb_bound3}
 	\frac{L_0}{x_0} \geq \frac{L_0'}{x_0'},
@@
 
-We substitute coordinates from~\cref{eq:first_elb_coords} appropriately in~\cref{eq:first_elb_bound} to get the following necessary conditions,
+We substitute coordinates from~\cref{eq:first_elb_coords} appropriately in~\cref{eq:first_elb_bound3} to get the following necessary conditions,
 \begin{equation}\label{eq:rate_bounds_proof}
@@
 
+\section{Lower magic bounds via majorisation}
+\label{sec:lower_bounds}
+
+\nick{Add from notes}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Fragments in general resource theories}
+\label{sec:general_resources}
+
+\nick{Add from notes}
+
+So far we have introduced the notion of $\sigma$--fragments for any resource theory of magic. 
+In this section we briefly generalise this concept to arbitrary resource theories and explain precisely how it connects with resource monotones. 
+The busy reader more focussed on magic may skip this section.
+
+State convertibility within a given resource theory is often a hard question to address due to the intricate structure of the theory.
+In general, the structure of a theory $\R$ is described by a pre-order $\prec_\R$ and usually resource monotones are employed to reduce this structure into a simple real number ordering \nick{CITE}.
+The subdivisions of magic theories into $\sigma$--fragments suggests a new approach towards investigating state convertibility which retains more structure of the originaltheory than a measure can.
+
+Monotones reduce the structure of the resource theory $\R$ to a \emph{total} order on the real numbers.
+Therefore, two states, even if incomparable in $\R$, are always mapped onto ordered real numbers.
+We now generalise this idea of a theory projection that preserves comparability between states. 
+\begin{definition}[\textbf{Covariant projection}]\label{def:covproj}
+Let $\R = (\F, \O)$ be a resource theory with pre-order $\prec_\R$. 
+Then a \emph{covariant resource projection} of $\R$ to a resource theory $\R'$ with pre-order $\prec_{\R'}$, is a pair of mappings $(\Pi_s, \Pi_o)$, where $\Pi_s$ maps quantum states in $\R$ to quantum states in $\R'$, and $\Pi_o$ maps free operations in $\R$ to free operations in $\R'$.
+Moreover, these obey
+	\begin{enumerate}
+        \item $\Pis(\rho_1) \prec_{\R'} \Pis(\rho_2)$ whenever $\rho_1 \prec_\R \rho_2$;
+        \item $\Pio(\E) = \Pio(\E_1) \circ \Pio(\E_2)$ whenever $\E = \E_1 \circ \E_2$.
+    \end{enumerate}
+We call $\R'$ a \emph{covariant fragment} of $\R$.
+\end{definition}
+
+Resource monotones can now be clearly seen as a special case of covariant resource projections.
+\begin{proposition}[\textbf{Totally ordered covariant theories}]\label{thm:monoproj}
+	Any resource monotone $\M$ of a resource theory $\R$ is a covariant projection for which $\prec_{\R'}$ is a total order. 
+	Conversely, any such covariant projection corresponds to a resource monotone $\M$. 
+\end{proposition}
+\begin{proof}
+	Consider a monotone $\M$ in the context of a general resource theory $\R = (\F, \O)$.
+	State order is covariantly preserved due to the defining property of a monotone, stated in~\cref{def:mono}, where the pre-order $\prec_{\R'}$ is simply the total order $\leq$ on $\mathbb{R}$.
+
+	Operational composition is covariantly preserved when we simply choose $\Pio(\E) = 1_\times$, namely the `multiplication by 1' operation on real numbers. 
+	The definition of a resource monotone then automatically implies covariance.
+
+	Conversely, given any covariant projection of $\R$ for which $\prec_{\R'}$ is a total order, we may map the totally ordered set of elements $\Pis(\rho)$ via an injective, non-decreasing function $f$ into $\mathbb{R}$.
+	Then, $\M(\rho):=f(\Pi_s(\rho))$ provides a numerical value for each $\rho$ that obeys the definition of a monotone.
+
+\end{proof}
+
+We can also view $\sigma$--fragments as an example of reducing the structure of a magic theory $\R$ to a subtheory with a tractable pre-order.
+However, states which are incomparable in $\R$ remain incomparable and conversions between states which are comparable in $\R$ may no longer be possible.
+\begin{definition}[\textbf{Contravariant projection}]\label{def:contraproj}
+	Let $\R = (\F, \O)$ be a resource theory with pre-order $\prec_\R$. 
+Then a \emph{contravariant resource projection} of $\R$ onto a resource theory $\R'$ with pre-order $\prec_{\R'}$, is a pair of mappings $(\Pi_s, \Pi_o)$, where $\Pi_s$ maps quantum states in $\R$ onto quantum states in $\R'$, and $\Pi_o$ maps free operations in $\R$ onto free operations in $\R'$.
+Moreover, these obey
+	\begin{enumerate}
+        \item $\rho_1 \prec_\R \rho_2$ whenever $\Pis(\rho_1) \prec_{\R'} \Pis(\rho_2)$;
+        \item $\E = \E_1 \circ \E_2$ whenever $\Pio(\E) = \Pio(\E_1) \circ \Pio(\E_2)$.
+    \end{enumerate}
+We call $\R'$ a \emph{contravariant fragment} of $\R$.
+\end{definition}
+The use of covariant and contravariant in~\cref{def:covproj,def:contraproj} refers to the direction of implication between the two pre-orders and operation compositions\footnote{Note that strictly these are not projections in the sense of $\Pi^2 = \Pi$, but are instead morphisms.
+Here our use of the term projection is motivated by the idea that one one generally loses information about $\R$ under the mapping.}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Conclusion}

### 2021-03-24 notes/notes.tex
Fixed appendices, except for unital fragment appendix. What do we include there / what do we get rid of?

@@
 
+\section{Area monotone}\label{app:areamono}
+
+\nick{I don't believe in the area monotone - should we keep?}
+
+\begin{figure}[h]%
+    \centering
+    \subfigure[][]{%
+    \label{fig:test1}%
+    \includegraphics[height=3cm]{figs/negmasking_rho_strange_lc.pdf}
+    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
+    }\hspace{8pt}%
+    \subfigure[][]{%
+    \label{fig:test2}%
+    \includegraphics[height=3cm]{figs/negmasking_rho_strange_meas.pdf}
+    %\caption{Zero state $\ketbra{0}{0}$}%
+    }
+    \caption{\subref{fig:test1} Lorenz curve of $p\ketbra{\rm{S}} + (1-p) \frac{1}{d}\id$ for $p$ given in the legend.\subref{fig:test2} Different measures for the states on the left. \\
+    \nick{can replace~\cref{fig:lctoy} with a more informative version of this figure}
+    }%
+    \label{fig:test}
+\end{figure}
+
+Let $L_{>1}$ be the set of points on the Lorenz curve $\lc{\rho}{\sigma}(k)$ that lie above $1$ of state $\rho$ in the $\sigma$--fragment. 
+If $\rho$ is a free state, $L_{>1}$ is empty and $\A_\sigma(\rho) = 0$. 
+Otherwise, $\A_\sigma(\rho) > 0$ and it can be calculated exactly using the trapezium rule or the shoelace formula. 
+Let $k$ be the index of the first point $\left(x_k, \lc{\rho}{\sigma}(k)\right)$ lying above $1$. 
+Then $L_\rho(k)$ crosses $1$ at
+\begin{equation}
+	x_{\rm{int}} = x_k - \frac{x_k - x_{k-1}}{\lc{\rho}{\sigma}(k) - \lc{\rho}{\sigma}(k-1)}\lc{\rho}{\sigma}(k),\vspace{10pt}
+\end{equation}
+as well as at $\left(x_d, \lc{\rho}{\sigma}(d)\right) = (1,1)$
+
+Now we can define
+\begin{equation}
+L_{>1}^+ = \{ (x_i, y_i) \}_{0 \leq i \leq n}
+\end{equation}
+such that it contains the initial point of intersection $(x_0, y_0) \equiv (x_{n+1}, y_{n+1}) \coloneqq (x_{\rm{int}}, 1)$, all points $(x_i, y_i)$, labelled by $i=1,\dots,n-1$ that lie above $y=1$ contained in $L_{>1}$ and finally the second point of intersection $(x_n, y_n) = (1,1)$.
+Then, 
+\begin{equation}
+	\A_\sigma(\rho) = \frac{1}{2} \sum\limits_{i=0}^n (x_{i+1} y_i - x_i y_{i+1}).
+\end{equation}
+
+We note that single-copy Lorenz curves are additive in noise, 
+\begin{equation}
+	\lc{(1-\epsilon)\rho + \epsilon\sigma}{\sigma} = (1-\epsilon)\lc{\rho}{\sigma} + \epsilon\lc{\sigma}{\sigma},
+\end{equation}
+for any $\sigma, \rho$.
+This is not true for higher number of copies.
+
+\nick{In particular}, it can be used in the discussion of standard Lorenz curves to set the necessary constraints,
+\begin{align}
+L\left(x_{I'(0, m'_{0}, 9^{n-n'})}\right) &\geq L\left(x_{I'(0, m'_{0}, 9^{n-n'})}\right), \nonumber\\
+L\left(x_{I'(1, m'_{1}, 9^{n-n'})}\right) &\geq L\left(x_{I'(1, m'_{1}, 9^{n-n'})}\right), \nonumber\\
+&\vdotswithin{=} \nonumber\\
+L\left(x_{I'(n', m'_{r}, 9^{n-n'})}\right) &\geq L\left(x_{I'(n', m'_{n'}, 9^{n-n'})}\right), \nonumber
+\end{align}
+where $x_{I'(0, m'_{0}, 9^{n - n'})}, x_{I'(1, m'_{1}, 9^{n - n'})}, \dots, x_{I'(n', m'_{n'}, 9^{n - n'})} \in T$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon')^{\otimes n'}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).
+
+\section{Stabilizer proof details}
+
 Whether we are dealing with $\rm{(C1)}$ or $\rm{(C2)}$ depends on the physical parameters $\beta$ and $\epsilon$ as follows:

### 2021-03-25 appendix.tex
added citations

@@
   \end{equation}
-where $\bm{1}/d_i$ is the $d_i$-dimensional uniform distribution.
+where $\bm{1}/d_i$ is the $d_i$--dimensional uniform distribution.
 The left inverse $\Gamma_{\bmd}^{-1}: \mathbb{R}^N \mapsto \mathbb{R}^n$ is defined to sum up the elements in each block of $\Gamma_{\bmd}(\bmw)$, so that
@@
 	Suppose there exists a $\bmd$--stochastic $S$ such that $\bmx = S\bmy$ and let $B = \Gamma_{\bmd} \circ S \circ \Gamma_{\bmd}^{-1}$.
-$B$ is a $N$-dimensional bistochastic matrix, since composition of stochastic matrices is stochastic and $(\Gamma_{\bmd} \circ S \circ \Gamma_{\bmd}^{-1}) (\frac{1}{N}\bm{1}) = (\Gamma_{\bmd} \circ S) (\bm{d}) = \Gamma_{\bmd}(\bm{d}) = \frac{1}{N}\bm{1}$.
+$B$ is a $N$--dimensional bistochastic matrix, since composition of stochastic matrices is stochastic and $(\Gamma_{\bmd} \circ S \circ \Gamma_{\bmd}^{-1}) (\frac{1}{N}\bm{1}) = (\Gamma_{\bmd} \circ S) (\bm{d}) = \Gamma_{\bmd}(\bm{d}) = \frac{1}{N}\bm{1}$.
 Then, $B$ maps $\Gamma_{\bmd}({\bmy})$ to $\Gamma_{\bmd}({\bmx})$.
@@
 
-Any free state $\sigma \in \F$ corresponds to a $d^2$-dimensional probability distribution $\W{\sigma}$ and any free operation $\E \in \O$ corresponds to a $d^2 \times d^2$ stochastic matrix (or conditional probability distribution) $\W{\E}$.
+Any free state $\sigma \in \F$ corresponds to a $d^2$--dimensional probability distribution $\W{\sigma}$ and any free operation $\E \in \O$ corresponds to a $d^2 \times d^2$ stochastic matrix (or conditional probability distribution) $\W{\E}$.
 Note that these mappings are one-to-one due to the orthogonality of the phase-point operators as an operator basis.
@@
 Note further that free states $\F$ are mapped onto a \emph{strict subset} of the set of probability distributions.
-As a counterexample, the sharp $d^2$-dimensional probability distribution $(1, 0, \dots, 0)$ does not correspond to any qudit Wigner distribution because of the boundedness condition in~\cref{thm:wstate}.
+As a counterexample, the sharp $d^2$--dimensional probability distribution $(1, 0, \dots, 0)$ does not correspond to any qudit Wigner distribution because of the boundedness condition in~\cref{thm:wstate}.
 
@@
 \subsection{Binomial distributions and error bounds}\label{app:phi}
-Consider an experiment consisting of $n$ trials of throwing a $p$-coin, that is a coin with probability $p$ of landing on one side and $1-p$ of landing on the other.
+Consider an experiment consisting of $n$ trials of throwing a $p$--coin, that is a coin with probability $p$ of landing on one side and $1-p$ of landing on the other.
 We express the sum over an even number of successful trials $\Phi_+$ and the sum over an odd number of successful trials $\Phi_-$,
@@
 
-We also define the classical entropy of a $p$-coin as well as the classical relative entropy between a $p$-coin and a $q$-coin,
+We also define the classical entropy of a $p$--coin as well as the classical relative entropy between a $p$--coin and a $q$--coin,
 \begin{align}
@@
 
-The symmetry between the left tail of a $p$-coin distribution and the right tail of a $(1-p)$-coin distribution dictates that
+The symmetry between the left tail of a $p$--coin distribution and the right tail of a $(1-p)$--coin distribution dictates that
 \begin{align}\label{eq:phi_reverse}
@@
     \caption{\textbf{Lorenz curves and bounding curves.} 
-    The figure explores the distillation process of a 10-copy $0.25$-noisy Strange state to a 4-copy $0.05$-noisy Strange state in the unital fragment.
+    The figure explores the distillation process of a 10-copy $0.25$--noisy Strange state to a 4-copy $0.05$--noisy Strange state in the unital fragment.
     Clearly, by looking at the Lorenz curves, the distillation process is possible.
@@
 \subsection{Strange state Lorenz curve elbow coordinates in the unital fragment}\label{app:lcsu_coord_elb}
-The Wigner distribution of the $n$-copy qutrit maximally mixed state $\left(\id/3\right)^{\otimes n}$ is the uniform distribution 
+The Wigner distribution of the $n$--copy qutrit maximally mixed state $\left(\id/3\right)^{\otimes n}$ is the uniform distribution 
 \begin{equation}\label{eq:wu}
@@
 \end{equation}
-The Wigner distribution of the 1-copy $\epsilon$-noisy Strange state $\rho_{\rm{S}}(\epsilon)$ in the unital fragment is a permutation of 
+The Wigner distribution of the 1-copy $\epsilon$--noisy Strange state $\rho_{\rm{S}}(\epsilon)$ in the unital fragment is a permutation of 
 \begin{equation}\label{eq:wsu}
@@
 
-The Wigner distribution of the $n$-copy $\epsilon$-noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ in the unital fragment is given by the convolution $\W{\rho_{\rm{S}}(\epsilon)^{\otimes n}} = \rm{W}_{\rho_{\rm{S}}(\epsilon)}^{\otimes n}$.
+The Wigner distribution of the $n$--copy $\epsilon$--noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ in the unital fragment is given by the convolution $\W{\rho_{\rm{S}}(\epsilon)^{\otimes n}} = \rm{W}_{\rho_{\rm{S}}(\epsilon)}^{\otimes n}$.
 In general, $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ contains $n + 1$ distinct components, labelled $0,\dots, n$.
@@
 \label{app:cmpairs}
-In general, a $1$-copy $d$--dimensional state $\rho$ is defined exactly by its $d^2$--dimensional Wigner distribution $\W{\rho}$. 
+In general, a $1$--copy $d$--dimensional state $\rho$ is defined exactly by its $d^2$--dimensional Wigner distribution $\W{\rho}$. 
 The distribution $\W{\rho}$ is usually defined on the phase space, but it can be convenient to define it using pure vector notation. 
@@
 \end{equation}
-implies that the distribution $\W{\rho_A \otimes \rho_B}$ is $d_A^2 d_B^2$-dimensional and contains components of the form $w_i w_j'$. 
+implies that the distribution $\W{\rho_A \otimes \rho_B}$ is $d_A^2 d_B^2$--dimensional and contains components of the form $w_i w_j'$. 
 Therefore, the set $\{(w_i w_j', m_i m_j')\}$ with $i=1,\dots,D_A$ and $j=1,\dots,D_B$ is a complete set of component-multiplicity pairs for the distribution of the composite system $\W{\rho_A \otimes \rho_B}$.
@@
 
-Given a state $\rho$ and a complete set of component-multiplicity pairs describing its Wigner distribution $\W{\rho}$, we now provide a method of computing the components (and multiplicities) of the $n$-copy distribution $\W{\rho}^{\otimes n}$.
+Given a state $\rho$ and a complete set of component-multiplicity pairs describing its Wigner distribution $\W{\rho}$, we now provide a method of computing the components (and multiplicities) of the $n$--copy distribution $\W{\rho}^{\otimes n}$.
 \begin{lemma}\label{lem:ncopycomponents}
@@
 
-	Assume that $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$ as given in~\cref{eq:M,eq:W} is a complete set of component-multiplicity pairs for the $n$-copy distribution $W^{\otimes n}$.
+	Assume that $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$ as given in~\cref{eq:M,eq:W} is a complete set of component-multiplicity pairs for the $n$--copy distribution $W^{\otimes n}$.
 	By construction, the distribution $W^{\otimes (n+1)} = W^{\otimes n} \otimes W$ is multiplicative, so it admits the complete set of component multiplicity pairs
@@
 
-Index vector $\bmk$ has $D-1$ independent components and in the proof of our main theorem in~\cref{sec:stab} we have $D=4$, so we simplify the notation by writing the component and multiplicity vectors of the $n$-copy state distributions as $m_{ijk}, w(\rho_{\rm{S}})_{ijk}, w(\gamma)_{ijk}$ and $w(\rho_{\rm{S}}|\gamma)_{ijk}$, where $i,j,k$ are the 3 independent index components.
+Index vector $\bmk$ has $D-1$ independent components and in the proof of our main theorem in~\cref{sec:stab} we have $D=4$, so we simplify the notation by writing the component and multiplicity vectors of the $n$--copy state distributions as $m_{ijk}, w(\rho_{\rm{S}})_{ijk}, w(\gamma)_{ijk}$ and $w(\rho_{\rm{S}}|\gamma)_{ijk}$, where $i,j,k$ are the 3 independent index components.
 

### 2021-03-25 magic_paper.tex
added citations

@@
 \begin{document}
-% - vs -- (n-copy, sigma-fragment etc.)
-% Plot consistency (esp Figs. 3, 4, 5, 6)
-%
-%
-%
+% - vs -- (n-copy, sigma--fragment etc.)
+% Distillation rate vs bound
+% Sec: Appendix D
+% Sec: Intro
+% Sec: General resources
+% Sec: Lower bounds
+% Sec: Abstract
+% Plot consistency (esp. figs 3,4,5,6)
+% Spacing
 
@@
 
-\begin{enumerate}
-    \item Fault-tolerance~\cite{cit:raussendorf, cit:gross2, cit:markov, cit:gross, cit:nest, cit:nest2, cit:vidal, cit:fujii, cit:gottesman}
-    \item Magic~\cite{cit:veitch, cit:veitch2, Wang_2019, Wang_2018, cit:howard, cit:campbell, cit:gross3, cit:gross4}
-    \item Bringing in majorisation~\cite{cit:cwiklinski, cit:lostaglio2, cit:lostaglio, cit:gour, cit:janzing, cit:brandao2, cit:gour2, cit:marshall, cit:nielsen}
-\end{enumerate}
-
 \subsection{Introduction}
@@
 
-Magic states are necessary for achieving universal quantum computation within fault-tolerant schemes.
-Identifying magic as a resource for quantum universality has led to several theories which try to provide a framework for its quantification and manipulation \nick{CITE}.
+Magic states are necessary for achieving universal quantum computation within fault-tolerant schemes~\cite{cit:veitch, cit:mari, cit:gottesman, cit:bravyi, cit:knill, Campbell_2011}.
+Identifying magic as a resource for quantum universality has led to several theories which try to provide a framework for its quantification and manipulation \cite{cit:veitch2, cit:howard, Wang_2019, Seddon_2021}.
 The main question that such a theory attempts to answer is:
@@
 Further denote by $\D$ the set of states considered under the theory, that is the union of free and resource states.
-The structure of such theory is described by a partial order \nick{CITE}, hereinafter called a \emph{pre-order}, $\prec_{\R}$ between states.
+The structure of such theory is described by a partial order, hereinafter called a \emph{pre-order}, $\prec_{\R}$ between states.
 We write $\rho' \prec_{\R} \rho$ iff there exists $\E \in \O$ such that $\E(\rho) = \rho'$.
@@
     \item Free operations send free states into free states, $\E: \F \mapsto \F$, for all $\E \in \O$;
-    \item Resource theory $\R$ is a completely free state preserving theory, in the sense that for any $d$-dimensional ancilla system and all free operations $\E$, $(\id_d \otimes \E ) \sigma \in \F$ whenever $\sigma \in \F$.
+    \item Resource theory $\R$ is a completely free state preserving theory, in the sense that for any $d$--dimensional ancilla system and all free operations $\E$, $(\id_d \otimes \E ) \sigma \in \F$ whenever $\sigma \in \F$.
 \end{enumerate}
@@
 An immediate consequence is that if statistical mixing is included in $\O$, then the resource theory is convex.
-Convex resource theories have attracted a lot of attention recently \nick{CITE} and include the magic theories discussed in~\cref{sec:prev}.
-The second assumption implies that resources cannot be generated even when ancillas are allowed \nick{example of T state generation on Bell state by Campbell}.
-
-Monotones are often used \nick{CITE} to address the question of state convertibility, although such approaches are usually generic.
+
+Monotones are often used to address the question of state convertibility, although such approaches are usually generic.
 
@@
 Applying this notion on existing magic theories highlights the hidden stochasticity that governs magic state conversions.
-We show that a magic theory can be subdivided into \emph{fragments} \nick{expand}
+We show that a magic theory can be subdivided into \emph{fragments} \nick{FIX AND EXPAND}
 
@@
 
-\ddd{[Section needs a lot of fixing]}
-
 The stabiliser theory of magic comprises of the so-called ``stabiliser'' states ($\stab$) and operations ($\so$), while non-stabiliser (resource) states are called magic.
@@
 for an ancilla stabiliser state $\sigma_E$. 
-The motivation of the theory stems from the fact that stabiliser operations are experimentally straightforward to implement and they can be used to detect and correct errors on the stabiliser states due to their construction \nick{CITE}.
+The motivation of the theory stems from the fact that stabiliser operations are experimentally straightforward to implement and they can be used to detect and correct errors on the stabiliser states due to their construction \cite{cit:gottesman, cit:gottesman2, cit:gottesman1998}.
 The Gottesman-Knill theorem however indicates that stabiliser operations need to be supplemented with magic states in order to achieve universality, justifying the term ``magic''.
 
-Generalisations of the stabiliser theory appear in the literature intending to include broader classes of operations \nick{CITE}.
+Generalisations of the stabiliser theory appear in the literature intending to include broader classes of operations.
 The class of stabiliser preserving operations ($\spo$) is defined as the set of $\cptp$ maps that send stabiliser states into stabiliser states~\cite{cit:ahmadi}.
-An important subclass of $\spo$ is the set of completely stabiliser preserving operations ($\cspo$), which intuitively cannot induce ``non-stabiliserness'' even when applied to only part of a quantum state, i.e.
+An important subclass of $\spo$ is the set of completely stabiliser preserving operations ($\cspo$)~\cite{cit:seddon}, which intuitively cannot induce ``non-stabiliserness'' even when applied to only part of a quantum state, i.e.
 operations $\E$ such that $(\id_d \otimes \E ) \sigma \in \stab$ for all positive dimensions $d$ whenever $\sigma \in \stab$.
@@
 In fact, all states with non-negative Wigner distributions have been proven to be efficiently classically simulable in~\cite{cit:mari}, a result that serves as a generalization of the Gottesman-Knill theorem.
-The Wigner distribution of a state in odd prime dimensions is discussed rigorously in~\cref{sec:wigner} and arises as the unique quasi-probability representation of quantum theory that identifies non-contextuality exactly with the states that are efficiently classically simulable~\cite{cit:howard2, cit:veitch2}.
+The Wigner distribution of a state in odd prime dimensions, formally defined in~\cref{sec:wigner}, arises as the unique quasi-probability representation of quantum theory that identifies non-contextuality exactly with the states that are efficiently classically simulable~\cite{Delfosse_2017, cit:howard2, cit:veitch2}.
 In this framework, the stabiliser states are the only pure states represented with non-negative distributions~\cite{cit:gross3}. 
 However, there exist mixed states with non-negative Wigner distributions that are not mixtures of stabiliser states~\cite{cit:gross}.
-Therefore, stabiliser-preserving theories have been extended to a theory that preserves state ``Wigner positivity''~\cite{Wang_2019}, formally defined in~\cref{sec:wigner} for odd prime dimensions.
+Therefore, stabiliser-preserving theories have been extended to a theory that preserves state ``Wigner positivity''~\cite{Wang_2019}.
 Informally, it can be considered as the maximal theory of magic $\Rmax = (\Fmax, \Omax)$, where free states have non-negative Wigner distributions and free operations completely preserve this property.\\
@@
 
-The displacement operators form the Heisenberg-Weyl group \nick{CITE} under matrix multiplication modulo phases,
+The displacement operators form the Heisenberg-Weyl group~\cite{Folland_1989, Bengtsson_2006} under matrix multiplication modulo phases,
 \begin{equation}\label{eq:gp}
@@
 
-For any quantum state $\rho$, the Wigner distribution $W_\rho(\bmx)$ is readily seen to be a $d^2$-dimensional quasi-probability distribution over $\cal{P}_d$ (see~\cref{app:wigner} for details).
+For any quantum state $\rho$, the Wigner distribution $W_\rho(\bmx)$ is readily seen to be a $d^2$--dimensional quasi-probability distribution over $\cal{P}_d$ (see~\cref{app:wigner} for details).
 In~\cref{fig:wstate_examples}, we show Wigner distributions of different types of qutrit states.
@@
 Mana is an additive\footnote{It satisfies the condition $\mana{\rho_1 \otimes \rho_2} = \mana{\rho_1} + \mana{\rho_2}$ which is practical in distillation settings.} magic monotone, so it provides an analytical, necessary condition for many-copy magic state interconvertibility.
-The magic monotone of \emph{max--thauma}~\cref{Wang_2018} has also been introduced more recently for qudits of odd prime dimension.
+The magic monotone of \emph{max--thauma}~\cite{Wang_2018} has also been introduced more recently for qudits of odd prime dimension.
 
@@
 
-Majorisation is a collection of powerful tools that has recently found many applications in quantum information theory \nick{CITE}.
+Majorisation~\cite{cit:marshall} is a collection of powerful tools that has recently found many applications in quantum information theory~\cite{Nielsen_1999, cit:cwiklinski, cit:lostaglio2, cit:gour, cit:gour2, Horodecki_2003, Vallejos_2021}.
 It describes the \nick{disorder / non-uniformity} of distributions that undergo stochastic transformations.
@@
 Thermal operations are defined as operations that cannot extract energy from the Gibbs state, $\E(\gamma_\beta) = \gamma_\beta$.
-Convertibility between states via thermal operations is equivalent to a stochasticity condition on the energy level populations of the states \nick{CITE}.
+Convertibility between states via thermal operations is equivalent to a stochasticity condition on the energy level populations of the states~\cite{cit:lostaglio}.
 Informally, there exists a thermal operation $\E$ such that $\tau = \E(\rho)$ if and only if there exists a matrix $S \in \stoch$ such that $\bm{q} = S\bm{p}$, where $\bm{q}, \bm{p}$ and $\bmd$ and the energy level population vectors of $\tau, \rho, \gamma_\beta$ respectively.
@@
 We denote this pre-order by $\bmx \prec_{\bmd} \bmy$.
-If $\bmd = \frac{1}{d}\bm{1}$, the $d$-dimensional uniform distribution, then $\stoch$ is the set of doubly stochastic matrices and we retrieve the familiar notion of majorisation from entanglement theory.
-\nick{CITE}
+If $\bmd = \frac{1}{d}\bm{1}$, the $d$--dimensional uniform distribution, then $\stoch$ is the set of doubly stochastic matrices and we retrieve the familiar notion of majorisation from entanglement theory~\cite{Nielsen_1999}.
 
@@
 Given this context we now define the following key notion, that is central to our analysis.
-\begin{definition}[\textbf{$\boldsymbol\sigma$-fragment}]\label{def:sigmafrag}
+\begin{definition}[\textbf{$\boldsymbol\sigma$--fragment}]\label{def:sigmafrag}
    Given a resource theory of magic $\R = (\F, \O)$, the \emph{$\sigma$--fragment of $\R$} is the resource theory $\R_\sigma = (\F_\sigma, \O_\sigma)$, where $\F_\sigma = \{\sigma\}$ and the free operations are restricted to the ones that leave $\sigma$ invariant,
@@
     Conversely, suppose $\E$ is in $\O$. 
-    The free states are a closed set that is mapped one-to-one to a closed subset $\cal{S}$ of the $(d^2 - 1)$-dimensional probability simplex.
+    The free states are a closed set that is mapped one-to-one to a closed subset $\cal{S}$ of the $(d^2 - 1)$--dimensional probability simplex.
     $\cal{S}$ is convex, since any combination of free states is also free and the Wigner distribution is linear.
@@
 
-    We can now view $\W{\E}$ as a stochastic, continuous mapping from $\cal{S}$ to itself, thus Brouwer's fixed point theorem \nick{CITE} implies that there exists a probability distribution $d_{\bmz}$ for some $ \bmz \in \cal{P}_d$ that is a fixed point of $\W{\E}$.
+    We can now view $\W{\E}$ as a stochastic, continuous mapping from $\cal{S}$ to itself, thus Brouwer's fixed point theorem~\cite{cit:brouwer} implies that there exists a probability distribution $d_{\bmz}$ for some $ \bmz \in \cal{P}_d$ that is a fixed point of $\W{\E}$.
     This corresponds to a free state $\sigma \coloneqq \sum_{\bmz \in \cal{P}_d} d_{\bmz} A_{\bmz} \in \F$. 
@@
     \caption{\textbf{Decomposition of a magic theory $\R$ intro $\sigma$--fragments.} 
-	Examples of magic theories ($\so$: Stabilizer operations, $\Omax$: Completely positive-Wigner-preserving operations, $\rcu$: Random Clifford Unitaries -- subclass of $\so$) involve operations denoted by the two yellow regions, with every other established magic theory  between them.
+	Examples of magic theories ($\so$: Stabilizer operations, $\Omax$: Completely positive-Wigner-preserving operations, $\rcu$: Random Clifford Unitaries -- subclass of $\so$) involve operations denoted by the two yellow regions, with other established magic theories  between them.
     We introduce $\sigma$--fragments $\O_\sigma$ defined for all free states $\sigma$ that cover $\Omax$. 
@@
 It is then apparent that the pre-order $\prec_{\R_\sigma}$ between the operations in the $\sigma$--fragment follows the rules of $\bmd$--majorisation as outlined in~\cref{sec:major}.
-In particular, the pre-order $\prec_{\R_\sigma}$ of the $\sigma$--fragment $\R_\sigma = (\F, \O_\sigma)$ between $d$-dimensional states corresponds to the majorisation pre-order $\prec_{\W{\sigma}}$ between their $d^2$-dimensional Wigner distributions.
+In particular, the pre-order $\prec_{\R_\sigma}$ of the $\sigma$--fragment $\R_\sigma = (\F, \O_\sigma)$ between $d$--dimensional states corresponds to the majorisation pre-order $\prec_{\W{\sigma}}$ between their $d^2$--dimensional Wigner distributions.
 For simplicity we shall merge the notation into $\prec_\sigma$, as there is little risk of confusion.
 
-Note that the Wigner components of an $n$-copy state $\rho^{\otimes n}$ can be calculated directly from $\W{\rho}$ by convolution of the distribution with itself,
+Note that the Wigner components of an $n$--copy state $\rho^{\otimes n}$ can be calculated directly from $\W{\rho}$ by convolution of the distribution with itself,
 \begin{equation}
@@
 \end{equation}
-The correspondence between the phase space and pure vector representations of the Wigner distribuition is discussed more in~\cref{app:cmpairs}.
-\nick{In the rest of the paper we will be using the two notations interchangeably.}
+The correspondence between the phase space and pure vector representations of the Wigner distribution is discussed more in~\cref{app:cmpairs}.
+The vector notation will be useful in the proof of our main result,~\cref{thm:stab_bounds}
 
 Furthermore, we restrict our analysis to $\sigma$--fragments, where $\sigma$ is full-rank.
-This is justified as majorisation is continuous between fragments, in the sense that the pre-orders $\prec_\sigma$ and $\prec_{\sigma'}$ are equivalent for states $\sigma$ and $\sigma'$ which are $\epsilon$-close.
+This is justified as majorisation is continuous between fragments, in the sense that the pre-orders $\prec_\sigma$ and $\prec_{\sigma'}$ are equivalent for states $\sigma$ and $\sigma'$ which are $\epsilon$--close.
 \nick{CHECK}
@@
 This approach can also provide \emph{lower bounds} on distillation, however now more structure about the specific free operations must be included. 
-We briefly discuss distillation lower bounds in~\nick{REF}.
+We briefly discuss distillation lower bounds in~\cref{sec:lower_bounds}.
 
@@
 In~\cref{sec:unital,sec:stab}, we study majorisation constraints on magic distillation arising in different fragments. 
-For this reason, we define the $n$-copy, $\epsilon$-noisy Strange state,
+For this reason, we define the $n$--copy, $\epsilon$--noisy Strange state,
 \begin{equation}\label{eq:noisysn}
@@
 
-In~\cref{fig:lcs}, we illustrate the Lorenz curve $\lc{\rho_{\rm{S}}}{\sigma}$\footnote{Hereinafter, we may drop parameters $\epsilon$ and $n$ for clarity} of pure and noisy $n$-copy Strange states in some thermal $\sigma$--fragment.
+In~\cref{fig:lcs}, we illustrate the Lorenz curve $\lc{\rho_{\rm{S}}}{\sigma}$\footnote{Hereinafter, we may omit obvious variable dependencies like $\epsilon$ and $n$ for clarity} of pure and noisy $n$--copy Strange states in some thermal $\sigma$--fragment.
 Due to~\cref{lem:lcmax}, it is clear that the curves peak at $1 + \sn{\rho_{\rm{S}}(\epsilon)^{\otimes n}}$.
@@
 
-MSD circuits in principle consist of bulk sequences of random Clifford unitaries ($\rcu$)\nick{CITE}, depicted in~\cref{fig:zoo}.
+MSD circuits in principle consist of bulk sequences of random Clifford unitaries ($\rcu$)~\cite{cit:bravyi}, depicted in~\cref{fig:zoo}.
 Operations in $\rcu$ can be expressed as
@@
 
-The Wigner distribution of the 1-copy, $\epsilon$-noisy Strange state can be written as 
+The Wigner distribution of the 1-copy, $\epsilon$--noisy Strange state can be written as 
 \begin{equation}
@@
 
-For the sake of clarity, we may omit obvious variable dependencies in the following analysis.
-
 The rescaled distribution in the unital fragment simply is 
@@
 
-The component values and multiplicities ($m_i$) in the $n$-copy case are 
+The component values and multiplicities ($m_i$) in the $n$--copy case are 
 \begin{align}
@@
 
-Using this notation, the component values and multiplicities of the $n$-copy distributions can be readily provided by~\cref{lem:ncopycomponents} in~\cref{app:cmpairs}.
+Using this notation, the component values and multiplicities of the $n$--copy distributions can be readily provided by~\cref{lem:ncopycomponents} in~\cref{app:cmpairs}.
 They are parametrised by three independent components $i,j,k$, with sum $\alpha \coloneqq i+j+k \leq n$.
-The $n$-copy multiplicity is given by
+The $n$--copy multiplicity is given by
 \begin{equation}
@@
 
-In order to construct the $n$-copy Lorenz curve $\lc{\rho_{\rm{S}}^{\otimes n}}{\gamma}$ we need to sort the components of the $n$-copy rescaled distribution, $w(\rho_{\rm{S}} | \gamma)_{ijk}$ in decreasing order.
+In order to construct the $n$--copy Lorenz curve $\lc{\rho_{\rm{S}}^{\otimes n}}{\gamma}$ we need to sort the components of the $n$--copy rescaled distribution, $w(\rho_{\rm{S}} | \gamma)_{ijk}$ in decreasing order.
 In particular, to find the coordinates of the first elbow $(x_0, L_0)$, we need to evaluate the maximum rescaled component,
@@
 State convertibility within a given resource theory is often a hard question to address due to the intricate structure of the theory.
-In general, the structure of a theory $\R$ is described by a pre-order $\prec_\R$ and usually resource monotones are employed to reduce this structure into a simple real number ordering \nick{CITE}.
+In general, the structure of a theory $\R$ is described by a pre-order $\prec_\R$ and usually resource monotones are employed to reduce this structure into a simple real number ordering.
 The subdivisions of magic theories into $\sigma$--fragments suggests a new approach towards investigating state convertibility which retains more structure of the originaltheory than a measure can.

### 2021-03-25 magic_paper.tex
Initial edits for Sect. II. References needed at various points.

--- 2021-03-22 magic_paper.tex
@@
 \newpage
-\section{Preliminaries and definitions}
+\section{Phase space representations of quantum states}
 \label{sec:ps}
 
-\subsection{Stabilizer Theory}\label{sec:so}
+Central to our construction is the representation of any quantum state or quantum operation on a system of dimension $d$ in terms of quasi-probability representations on a discrete phase space \ddd{[CITE the review on quasi-reps]}.
+This construction is a discrete version of Wigner representations in quantum optics.
 
-Let $\{\ket{k}\}_{k \in \mathbb{Z}_d}$ be the standard computational basis, defined over $\mathbb{Z}_d = \{ 0, 1, \dots,d-1 \}$, with $d$ an odd prime. 
-Since the field has character $d$, addition and multiplication on the field are always considered modulo $d$.
-The Hilbert space of any system associated with this scheme is $\cal{H}_d \coloneqq \spanv{\ket{k}: k \in \mathbb{Z}_d}$.
-
-The generalised Pauli matrices $X, Z$ can be defined by their respective roles as shift and phase operators,
+We consider a $d$--dimensional quantum system with Hilbert space $\H_d$, and let $\{ |0\>, |1\>, \dots , |d-1\>\}$ denote the standard computational basis, defined over $\mathbb{Z}_d = \{ 0, 1, \dots,d-1 \}$.
+On this space, generalised Pauli matrices $X, Z$ can be defined by their respective roles as shift and phase operators, which act on the basis states as follows,
 \begin{align}
     X \ket{k} &= \ket{k + 1} \label{eq:xpauli}\\
-	Z \ket{k} &= \omega^k \ket{k}, \label{eq:zpauli}
+	Z \ket{k} &= \omega^k \ket{k}. \label{eq:zpauli}
 \end{align}
-where $\omega \coloneqq e^{2\pi i/d}$ is the $d$-th root of unity and addition is modulo $d$.
-The Hilbert space $\cal{H}_d$ is associated with a phase space $\cal{P}_d = \mathbb{Z}_d \times \mathbb{Z}_d$, where every point $\bmx \coloneqq (x, p)$ corresponds to a displacement operator, defined as
+Here $\omega \coloneqq e^{2\pi i/d}$ is the $d$-th root of unity and addition is taken modulo $d$.
+From these we can construct a phase space $\cal{P}_d = \mathbb{Z}_d \times \mathbb{Z}_d$ that provides a complete representation of the quantum system.
+Given a point $\bmx \coloneqq (x, p)$ we define a displacement operator,
 \begin{equation}\label{eq:ddef}
-    D_{\bmx} \coloneqq \tau^{x p} X^{x} Z^{p},\ (x, p) \in \cal{P}_d.
+    D_{\bmx} \coloneqq \tau^{x p} X^{x} Z^{p},\ 
 \end{equation}
-The phase factor $\tau \coloneqq -\omega^{1/2}$ ensures unitarity.
-For a composite system with product dimension $d = d_1 \dots d_n$ and Hilbert space, $\cal{H}_d = \cal{H}_{d_1} \otimes \dots \otimes \cal{H}_{d_n}$, the displacement operators are defined as
+where a phase factor $\tau \coloneqq -\omega^{1/2}$ ensures unitarity.
+We assume going forward that $d$ is an odd prime, however the case $d=2$ can be also handled, but with some additional technical caveats \ddd{[CITE]}.
+For a composite system with composite dimension $d = d_1 \dots d_n$ we can decompose the Hilbert space as $\cal{H}_d = \cal{H}_{d_1} \otimes \dots \otimes \cal{H}_{d_n}$, and then define displacement operators as
 \begin{equation}\label{eq:composited}
@@
 \end{equation}
-where 
+where now we have
 \begin{align*}
@@
 \end{align*}
-denotes the phase space point for an $n$--copy system.
+to denote the phase space point for the composite system.
+For simplicity going forward we assume $n$ copies of a $d$--dimensional system $d_1=d_2 = \cdots = d$, and therefore, we have that $\x \in \mathbb{Z}_d^{2n}$.
 
-The displacement operators form the Heisenberg-Weyl group \nick{CITE} under matrix multiplication modulo phases,
+These displacement operators form the Heisenberg-Weyl group \nick{CITE} under matrix multiplication modulo phases,
 \begin{equation}\label{eq:gp}
@@
 \end{equation}
-The Clifford operations $ \cal{C}_d^n $ are then defined as the set of unitaries that normalise the Heisenberg-Weyl group.
+The Clifford operations $ \cal{C}_d^n $ are then defined as the set of unitaries that normalise the Heisenberg-Weyl group \ddd{[CITE]}.
 We may define the pure stabiliser states as those states obtained by acting on $|0\>$ with Clifford unitaries.
 Finally, we define $\stab$ as the convex hull of all pure stabiliser states, namely all probabilistic mixtures of states of the form $U|0\>\<0|U^\dagger$ where $U$ is some Clifford unitary.
-The stabiliser theory forms a magic resource theory $\R = (\stab, \so)$
-and the free operations are stabiliser operations ($\so$), defined as compositions of preparation of computational basis states, Clifford unitaries, measurement in the computational basis, and the ability to discard subsystems.
 
@@
 
-We define the phase-point operators at every phase space point $\bmx \in \cal{P}_d$,
+In order to provide a complete decomposition of arbitrary quantum states and quantum operations we now define a complete basis of hermitian observables that behaves naturally under the action of the Clifford group.
+To every point $\x \in \P_d$ we define the phase-point operator $A_{\x}$ given by
 \begin{align}
@@
 \end{align}
-where $\eta(\bmx, \bmz)$ is the standard symplectic form, given explicitly by
+where $\eta(\bmx, \bmz)$ is the symplectic inner product between any two points $\x,\z \in \P_d$, and is given explicitly by
 \begin{equation}
@@
 
-The phase-point operators form an orthogonal Hermitian operator basis as shown in~\cref{app:wigner}.
+The phase-point operators form an orthogonal (with respect to the Hilbert-Schmidt inner product) operator basis as shown in~\cref{app:wigner}.
 Therefore, any quantum state $\rho \in \cal{B}(\cal{H}_d)$ can be expressed as a linear combination of them,
@@
 For any quantum state $\rho$, the Wigner distribution $W_\rho(\bmx)$ is readily seen to be a $d^2$-dimensional quasi-probability distribution over $\cal{P}_d$ (see~\cref{app:wigner} for details).
+More precisely, $W_\rho(\x)$ is a real-valued function on $\P_d$ with the property that $\sum_{\x} W_\rho(x) = 1$.
 In~\cref{fig:wstate_examples}, we show Wigner distributions of different types of qutrit states.
@@
 
+\subsection{Magic theories for quantum computation}
+\label{sec:mono}
+
+The state-injection model for quantum computation \ddd{[CITE]} is a key avenue to realising a full-scale, fault-tolerant quantum computer.
+Within the approach Clifford unitaries can be done in a robust, fault-tolerant way.
+However, due to the Eastin-Knill theorem \ddd{[CITE]}, it is impossible to have a universal set of transversal gates and so while Clifford unitaries can be realised transversally one must find ways around the Eastin-Knill restriction.
+The state-injection approach supplements the Clifford gates with noisy quantum states, called `magic states', that are outside the set of stabliser states and, when incorporated into Clifford circuits, provides universality.
+The obstacle to this is that the states are invariably noisy and so protocols must be employed so as to purify many copies of the magic states and improve the overall performance of the induced quantum gates.
+A central question is then: given a number $n$ of noisy magic states how many purified magic states can we obtain within the fault-tolerant set of quantum operations?
+
+To address such questions both concrete distillation protocols have been developed, and there has been analysis of bounds of distillation rates within natural theoretical frameworks.
+These frameworks provide theories of magic in which one views magic states as ``resource'' states with respect to a natural class of quantum operations that are consider cheap, or ``free'' \ddd{[CITE Gour resource review]}.
+One very natural class of free operations considered are those obtained from Clifford operations, measurements and the ability to discard quantum systems.
+However there are several other candidate frameworks.
+
+For any theory of magic a natural route to bounding the distillation rates obtainable is through the concept of a \emph{magic monotone}.
+A magic monotone is a real-valued function of any quantum state $\M(\rho)$ that is monotonically non-increasing under the free operations of the magic theory.
+More precisely $\M(\sigma) \le \M(\rho)$ whenever it is possible to convert $\rho$ into $\sigma$ using at least one of the free operations available (e.g.
+Clifford operations).
+
+One of the most fundamental and commonly used magic monotones is the \emph{mana} of a state~\cite{cit:veitch2}, defined as
+\begin{equation}
+    \mana{\rho} \coloneqq \ln{(2\hspace{1pt}\sn{\rho}+1)},
+\end{equation}
+where the \emph{sum-negativity}~\cite{cit:veitch2} is the sum of the negative components in $\W{\rho}$,
+\begin{equation}
+    \sn{\rho} \coloneqq \sum\limits_{\bmx: \W[\bmx]{\rho} < 0} \abs{\W[\bmx]{\rho}}.
+\end{equation}
+Mana is an additive\footnote{It satisfies the condition $\mana{\rho_1 \otimes \rho_2} = \mana{\rho_1} + \mana{\rho_2}$ which is practical in distillation settings.} magic monotone, so it provides an analytical, necessary condition for many-copy magic state interconvertibility.
+
+A range of other monotones have been developed in the literature\ddd{[CITE]}, and each provides a means to upper bound distillation rates within a particular theory of magic.
+In this work we shall consider a broad framework for magic, with conditions that any theory of magic should satisfy.
+However, in contrast to prior works we shall not construct magic monotones, but instead develop a generalisation to resource monotones.
+The approach we take will also allow us to address how distillation rates are constrained by physical properties -- such as a system having biased-noise, some equilibrium structure or operations that manifest invariances, such as axial symmetry around the qubit $Z$-axis.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Stochastic structure of magic theories}
+\label{sec:struc}
+
 We also have Wigner representations for general quantum channels. We may exploit the channel-state duality and use the normalised Choi-Jamio\l{}kowski state 
@@
 In particular, $\cptp$ operations that map between density operators of equal dimensions and have non-negative Wigner distributions correspond to stochastic matrices, as shown in~\cref{app:wigner}
-
-\subsection{Magic monotones}
-\label{sec:mono}
-
-We highlight the defining property of a monotone, as it is useful in later discussion.
-\begin{definition}[\textbf{Resource monotone}]\label{def:mono}
-    Let $\R = (\F, \O)$ be a resource theory.
-    A resource monotone $\M$ is a projection from the set of quantum states of the theory onto the real line, so that $\M$ is monotonically decreasing under free operations,
-    \begin{equation}
-        \M(\rho_1) \leq \M(\rho_2)\ \text{whenever}\ \rho_1 \prec_{\R} \rho_2.
-    \end{equation}
-\end{definition}
-
-One of the most fundamental and commonly used magic monotones is the \emph{mana} of a state~\cite{cit:veitch2}, defined as
-\begin{equation}
-    \mana{\rho} \coloneqq \ln{(2\hspace{1pt}\sn{\rho}+1)},
-\end{equation}
-where the \emph{sum-negativity}~\cite{cit:veitch2} is the sum of the negative components in $\W{\rho}$,
-\begin{equation}
-    \sn{\rho} \coloneqq \sum\limits_{\bmx: \W[\bmx]{\rho} < 0} \abs{\W[\bmx]{\rho}}.
-\end{equation}
-Mana is an additive\footnote{It satisfies the condition $\mana{\rho_1 \otimes \rho_2} = \mana{\rho_1} + \mana{\rho_2}$ which is practical in distillation settings.} magic monotone, so it provides an analytical, necessary condition for many-copy magic state interconvertibility.
-
-\subsection{Majorisation}
-\label{sec:major}
-
-Majorisation is a collection of powerful tools that has recently found many applications in quantum information theory \nick{CITE}.
-It describes the \nick{disorder / non-uniformity} of distributions that undergo stochastic transformations.
-
-To formally state majorisation results, we first denote by $\stoch$ the set of $(d \times d)$ stochastic matrices that preserve the probability vector $\bmd$.
-Specifically, for any $S \in \stoch$, all matrix elements are non-negative, all rows sum to $1$ and $S\bmd = \bmd$.
-The set $\stoch$ forms a group under matrix multiplication for all $\bmd$ with positive components.
-
-Majorisation describes quantum thermodynamics exactly in the absence of quantum coherence.
-The use of majorisation in this setting provides vital intuition for our purposes.
-At any given temperature $\beta^{-1}$, the thermal state $\gamma_\beta$ is thermodynamically the most disordered state. 
-Thermal operations are defined as operations that cannot extract energy from the Gibbs state, $\E(\gamma_\beta) = \gamma_\beta$.
-Convertibility between states via thermal operations is equivalent to a stochasticity condition on the energy level populations of the states \nick{CITE}.
-Informally, there exists a thermal operation $\E$ such that $\tau = \E(\rho)$ if and only if there exists a matrix $S \in \stoch$ such that $\bm{q} = S\bm{p}$, where $\bm{q}, \bm{p}$ and $\bmd$ and the energy level population vectors of $\tau, \rho, \gamma_\beta$ respectively.
-Formal statements of the above can be found \nick{in the appendix}.
-
-Based on this setting, we define majorisation as follows.
-\begin{definition}[\textbf{$\boldsymbol\bmd$-majorisation}]\label{def:dmajor}
-    Given $\bmx, \bmy, \bmd \in \reals^d$, such that the components of $\bmd$ are positive, $\bmy$ is said to $\bmd$-majorise $\bmx$, iff there exists a matrix $S \in \stoch$ such that $\bmx = S\bmy$.
-\end{definition}
-We denote this pre-order by $\bmx \prec_{\bmd} \bmy$.
-If $\bmd = \frac{1}{d}\bm{1}$, the $d$-dimensional uniform distribution, then $\stoch$ is the set of doubly stochastic matrices and we retrieve the familiar notion of majorisation from entanglement theory.
-\nick{CITE}
-
-The pre-order imposed by $\bmd$-majorisation admits a numerically efficient reformulation in terms of Lorenz curves.
-Let the vector $\bmu^\downarrow$ denote the vector $\bmu \in \reals^d$ with its components arranged in non-increasing order.
-\begin{definition}[\textbf{Lorenz curve}]\label{def:lc}
-    Let $\bmw, \bmd \in \reals^d$, where the components of $\bmd$ are positive with $D = \sum_{i=1}^d d_i$ and denote by $\widetilde{\bmw} \coloneqq (w_1/d_1, \dots, w_d/\nick{d_d})^T$ the vector of ratios between the corresponding components of $\bmw$ and $\bmd$.
-
-    Finally, denote by $\pi: \mathbb{Z}_d \mapsto \mathbb{Z}_d$ the permutation that sorts $\widetilde{\bmw}$, $(\widetilde{\bmw}^\downarrow)_i = w_{\pi(i)}$ for all $i=1,\dots,d$.
-
-    Consider the piecewise linear curve obtained by joining the points $\{(0,0)\} \cup \{ (x_k, \lc{\bmw}{\bmd}(k)) \}_{k=1,\dots,d}$, where
-    \begin{equation}\label{eq:lorenz}
-        (x_k, \lc{\bmw}{\bmd}(k)) \coloneqq \left( \frac{1}{D}\sum_{i=1}^k d_{\pi(i)}, \sum_{i=1}^k w_{\pi(i)} \right).
-    \end{equation}
-    We define the set of points on this curve, $\lc{\bmw}{\bmd}(x),\ x \in [0,1]$, as the \emph{Lorenz curve} of vector $\bmw$ with respect to $\bmd$.
-\end{definition}
-Components $x_k$ are rescaled by $D$ so that comparison of curves with unequal dimensions is possible.
-In fact, the Lorenz curves $\lc{\bmw}{\bmd}$ and $\lc{\bmw \otimes \bmd}{\bmd \otimes \bmd}$, where $\otimes$ denotes the Kronecker product, are identical.
-Furthermore, a Lorenz curve $\lc{\bmw}{\bmd}(x)$ is always concave in $x$, since it consists of $d$ line segments each with slope $(\widetilde{\bmw}^\downarrow)_i$ for $i=1,\dots,d$ which is non-increasing by definition.
-Finally, the points on the interior of the Lorenz curve connecting line segments of different slopes are called \emph{elbows}.
-
-A vector $\bmy$ is said to \emph{$\bmd$--majorise} another vector $\bmx$ if and only if the Lorenz curve $\lc{\bmy}{\bmd}$ lies above Lorenz curve $\lc{\bmx}{\bmd}$, thus reducing $\bmd$--majorisation into a finite set of inequalities.
-\begin{theorem}\label{thm:dmajor}
-    Let $\bmx, \bmy, \bmd \in \reals^d$, such that the components of $\bmd$ are positive. 
-    Then, $\bmx \prec_{\bmd} \bmy$ if and only if $\lc{\bmx}{\bmd}(x) \leq \lc{\bmy}{\bmd}(x)$ for all $x \in [0,1]$ with strict equality at $x=1$.
-\end{theorem}
-A restatement of the theorem including more equivalent conditions and a proof are provided in~\cref{app:major}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Stochastic structure of magic theories}
-\label{sec:struc}
-
 \subsection{Magic fragments}\label{sec:magfrag}
@@
 The subdivision of magic theories into $\sigma$--fragments is also powerful because the pre-order $\prec_{\R_\sigma}$ of every $\sigma$--fragment is described by well-behaved majorisation tools, as we establish in the rest of this section.
+
+\subsection{Majorisation}
+\label{sec:major}
+
+Majorisation is a collection of powerful tools that has recently found many applications in quantum information theory \nick{CITE}.
+It describes the \nick{disorder / non-uniformity} of distributions that undergo stochastic transformations.
+
+To formally state majorisation results, we first denote by $\stoch$ the set of $(d \times d)$ stochastic matrices that preserve the probability vector $\bmd$.
+Specifically, for any $S \in \stoch$, all matrix elements are non-negative, all rows sum to $1$ and $S\bmd = \bmd$.
+The set $\stoch$ forms a group under matrix multiplication for all $\bmd$ with positive components.
+
+Majorisation describes quantum thermodynamics exactly in the absence of quantum coherence.
+The use of majorisation in this setting provides vital intuition for our purposes.
+At any given temperature $\beta^{-1}$, the thermal state $\gamma_\beta$ is thermodynamically the most disordered state. 
+Thermal operations are defined as operations that cannot extract energy from the Gibbs state, $\E(\gamma_\beta) = \gamma_\beta$.
+Convertibility between states via thermal operations is equivalent to a stochasticity condition on the energy level populations of the states \nick{CITE}.
+Informally, there exists a thermal operation $\E$ such that $\tau = \E(\rho)$ if and only if there exists a matrix $S \in \stoch$ such that $\bm{q} = S\bm{p}$, where $\bm{q}, \bm{p}$ and $\bmd$ and the energy level population vectors of $\tau, \rho, \gamma_\beta$ respectively.
+Formal statements of the above can be found \nick{in the appendix}.
+
+Based on this setting, we define majorisation as follows.
+\begin{definition}[\textbf{$\boldsymbol\bmd$-majorisation}]\label{def:dmajor}
+    Given $\bmx, \bmy, \bmd \in \reals^d$, such that the components of $\bmd$ are positive, $\bmy$ is said to $\bmd$-majorise $\bmx$, iff there exists a matrix $S \in \stoch$ such that $\bmx = S\bmy$.
+\end{definition}
+We denote this pre-order by $\bmx \prec_{\bmd} \bmy$.
+If $\bmd = \frac{1}{d}\bm{1}$, the $d$-dimensional uniform distribution, then $\stoch$ is the set of doubly stochastic matrices and we retrieve the familiar notion of majorisation from entanglement theory.
+\nick{CITE}
+
+The pre-order imposed by $\bmd$-majorisation admits a numerically efficient reformulation in terms of Lorenz curves.
+Let the vector $\bmu^\downarrow$ denote the vector $\bmu \in \reals^d$ with its components arranged in non-increasing order.
+\begin{definition}[\textbf{Lorenz curve}]\label{def:lc}
+    Let $\bmw, \bmd \in \reals^d$, where the components of $\bmd$ are positive with $D = \sum_{i=1}^d d_i$ and denote by $\widetilde{\bmw} \coloneqq (w_1/d_1, \dots, w_d/\nick{d_d})^T$ the vector of ratios between the corresponding components of $\bmw$ and $\bmd$.
+
+    Finally, denote by $\pi: \mathbb{Z}_d \mapsto \mathbb{Z}_d$ the permutation that sorts $\widetilde{\bmw}$, $(\widetilde{\bmw}^\downarrow)_i = w_{\pi(i)}$ for all $i=1,\dots,d$.
+
+    Consider the piecewise linear curve obtained by joining the points $\{(0,0)\} \cup \{ (x_k, \lc{\bmw}{\bmd}(k)) \}_{k=1,\dots,d}$, where
+    \begin{equation}\label{eq:lorenz}
+        (x_k, \lc{\bmw}{\bmd}(k)) \coloneqq \left( \frac{1}{D}\sum_{i=1}^k d_{\pi(i)}, \sum_{i=1}^k w_{\pi(i)} \right).
+    \end{equation}
+    We define the set of points on this curve, $\lc{\bmw}{\bmd}(x),\ x \in [0,1]$, as the \emph{Lorenz curve} of vector $\bmw$ with respect to $\bmd$.
+\end{definition}
+Components $x_k$ are rescaled by $D$ so that comparison of curves with unequal dimensions is possible.
+In fact, the Lorenz curves $\lc{\bmw}{\bmd}$ and $\lc{\bmw \otimes \bmd}{\bmd \otimes \bmd}$, where $\otimes$ denotes the Kronecker product, are identical.
+Furthermore, a Lorenz curve $\lc{\bmw}{\bmd}(x)$ is always concave in $x$, since it consists of $d$ line segments each with slope $(\widetilde{\bmw}^\downarrow)_i$ for $i=1,\dots,d$ which is non-increasing by definition.
+Finally, the points on the interior of the Lorenz curve connecting line segments of different slopes are called \emph{elbows}.
+
+A vector $\bmy$ is said to \emph{$\bmd$--majorise} another vector $\bmx$ if and only if the Lorenz curve $\lc{\bmy}{\bmd}$ lies above Lorenz curve $\lc{\bmx}{\bmd}$, thus reducing $\bmd$--majorisation into a finite set of inequalities.
+\begin{theorem}\label{thm:dmajor}
+    Let $\bmx, \bmy, \bmd \in \reals^d$, such that the components of $\bmd$ are positive. 
+    Then, $\bmx \prec_{\bmd} \bmy$ if and only if $\lc{\bmx}{\bmd}(x) \leq \lc{\bmy}{\bmd}(x)$ for all $x \in [0,1]$ with strict equality at $x=1$.
+\end{theorem}
+A restatement of the theorem including more equivalent conditions and a proof are provided in~\cref{app:major}.
 
@@
     \includegraphics[height=5cm]{figs/lc_strange.pdf}
-    \caption{\textbf{Strange state Lorenz curves.} Lorenz curves of $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ for $n=1,2,3,4$ in the $\sigma$--fragment where $\sigma = e^{-\beta H}/\Z_{\beta}$, with Hamiltonian spectrum $(0,1,2)$ over the computational basis and $\beta = 0.5$.
-    Solid lines represent pure Strange states ($\epsilon = 0$); dashed lines represent noisy Strange states ($\epsilon = 0.1$).
+    \caption{\textbf{A `heretical' family of Lorenz curves.} Traditionally, Lorenz curves are monotone increasing cumulant functions that reach a maximum value of $1$.
+In contrast, Lorenz curves for magic states break through the value of $L(x)=1$ due to the presence of negativity in the associated quasi-probability distribution.
+The above family of curves correspond to multiple copies of noisy Strange states $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ for $n=1,2,3,4$ within a particular stabilizer fragment.
+Solid lines represent pure Strange states, while dashed lines represent noisy Strange states with depolarising noise $\epsilon = 0.1$.
     }

### 2021-03-25 magic_paper.tex
Resolved clashes in edits.

--- 2021-03-25 magic_paper.tex
@@
 \newpage
-\section{Preliminaries and definitions}
+\section{Phase space representations of quantum states}
 \label{sec:ps}
 
-\subsection{Stabilizer Theory}\label{sec:so}
-
-Let $\{\ket{k}\}_{k \in \mathbb{Z}_d}$ be the standard computational basis, defined over $\mathbb{Z}_d = \{ 0, 1, \dots,d-1 \}$, with $d$ an odd prime. 
-Since the field has character $d$, addition and multiplication on the field are always considered modulo $d$.
-The Hilbert space of any system associated with this scheme is $\cal{H}_d \coloneqq \spanv{\ket{k}: k \in \mathbb{Z}_d}$.
-
-The generalised Pauli matrices $X, Z$ can be defined by their respective roles as shift and phase operators,
+Central to our construction is the representation of any quantum state or quantum operation on a system of dimension $d$ in terms of quasi-probability representations on a discrete phase space \ddd{[CITE the review on quasi-reps]}.
+This construction is a discrete version of Wigner representations in quantum optics.
+
+We consider a $d$--dimensional quantum system with Hilbert space $\H_d$, and let $\{ |0\>, |1\>, \dots , |d-1\>\}$ denote the standard computational basis, defined over $\mathbb{Z}_d = \{ 0, 1, \dots,d-1 \}$.
+On this space, generalised Pauli matrices $X, Z$ can be defined by their respective roles as shift and phase operators, which act on the basis states as follows,
 \begin{align}
     X \ket{k} &= \ket{k + 1} \label{eq:xpauli}\\
-	Z \ket{k} &= \omega^k \ket{k}, \label{eq:zpauli}
+	Z \ket{k} &= \omega^k \ket{k}. \label{eq:zpauli}
 \end{align}
-where $\omega \coloneqq e^{2\pi i/d}$ is the $d$-th root of unity and addition is modulo $d$.
-The Hilbert space $\cal{H}_d$ is associated with a phase space $\cal{P}_d = \mathbb{Z}_d \times \mathbb{Z}_d$, where every point $\bmx \coloneqq (x, p)$ corresponds to a displacement operator, defined as
+Here $\omega \coloneqq e^{2\pi i/d}$ is the $d$-th root of unity and addition is taken modulo $d$.
+From these we can construct a phase space $\cal{P}_d = \mathbb{Z}_d \times \mathbb{Z}_d$ that provides a complete representation of the quantum system.
+Given a point $\bmx \coloneqq (x, p)$ we define a displacement operator,
 \begin{equation}\label{eq:ddef}
-    D_{\bmx} \coloneqq \tau^{x p} X^{x} Z^{p},\ (x, p) \in \cal{P}_d.
-\end{equation}
-The phase factor $\tau \coloneqq -\omega^{1/2}$ ensures unitarity.
-For a composite system with product dimension $d = d_1 \dots d_n$ and Hilbert space, $\cal{H}_d = \cal{H}_{d_1} \otimes \dots \otimes \cal{H}_{d_n}$, the displacement operators are defined as
+    D_{\bmx} \coloneqq \tau^{x p} X^{x} Z^{p},\ 
+\end{equation}
+where a phase factor $\tau \coloneqq -\omega^{1/2}$ ensures unitarity.
+We assume going forward that $d$ is an odd prime, however the case $d=2$ can be also handled, but with some additional technical caveats \ddd{[CITE]}.
+For a composite system with composite dimension $d = d_1 \dots d_n$ we can decompose the Hilbert space as $\cal{H}_d = \cal{H}_{d_1} \otimes \dots \otimes \cal{H}_{d_n}$, and then define displacement operators as
 \begin{equation}\label{eq:composited}
@@
 \end{align*}
-denotes the phase space point for an $n$--copy system.
+to denote the phase space point for the composite system.
+For simplicity going forward we assume $n$ copies of a $d$--dimensional system $d_1=d_2 = \cdots = d$, and therefore, we have that $\x \in \mathbb{Z}_d^{2n}$.
 
@@
 
-For any quantum state $\rho$, the Wigner distribution $W_\rho(\bmx)$ is readily seen to be a $d^2$--dimensional quasi-probability distribution over $\cal{P}_d$ (see~\cref{app:wigner} for details).
+For any quantum state $\rho$, the Wigner distribution $W_\rho(\bmx)$ is readily seen to be a $d^2$-dimensional quasi-probability distribution over $\cal{P}_d$ (see~\cref{app:wigner} for details).
+More precisely, $W_\rho(\x)$ is a real-valued function on $\P_d$ with the property that $\sum_{\x} W_\rho(x) = 1$.
 In~\cref{fig:wstate_examples}, we show Wigner distributions of different types of qutrit states.
+
 \begin{figure}%
@@
 
+\subsection{Magic theories for quantum computation}
+\label{sec:mono}
+
+The state-injection model for quantum computation \ddd{[CITE]} is a key avenue to realising a full-scale, fault-tolerant quantum computer.
+Within the approach Clifford unitaries can be done in a robust, fault-tolerant way.
+However, due to the Eastin-Knill theorem \ddd{[CITE]}, it is impossible to have a universal set of transversal gates and so while Clifford unitaries can be realised transversally one must find ways around the Eastin-Knill restriction.
+The state-injection approach supplements the Clifford gates with noisy quantum states, called `magic states', that are outside the set of stabliser states and, when incorporated into Clifford circuits, provides universality.
+The obstacle to this is that the states are invariably noisy and so protocols must be employed so as to purify many copies of the magic states and improve the overall performance of the induced quantum gates.
+A central question is then: given a number $n$ of noisy magic states how many purified magic states can we obtain within the fault-tolerant set of quantum operations?
+
+To address such questions both concrete distillation protocols have been developed, and there has been analysis of bounds of distillation rates within natural theoretical frameworks.
+These frameworks provide theories of magic in which one views magic states as ``resource'' states with respect to a natural class of quantum operations that are consider cheap, or ``free'' \ddd{[CITE Gour resource review]}.
+One very natural class of free operations considered are those obtained from Clifford operations, measurements and the ability to discard quantum systems.
+However there are several other candidate frameworks.
+
+For any theory of magic a natural route to bounding the distillation rates obtainable is through the concept of a \emph{magic monotone}.
+A magic monotone is a real-valued function of any quantum state $\M(\rho)$ that is monotonically non-increasing under the free operations of the magic theory.
+More precisely $\M(\sigma) \le \M(\rho)$ whenever it is possible to convert $\rho$ into $\sigma$ using at least one of the free operations available (e.g.
+Clifford operations).
+
+One of the most fundamental and commonly used magic monotones is the \emph{mana} of a state~\cite{cit:veitch2}, defined as
+\begin{equation}
+    \mana{\rho} \coloneqq \ln{(2\hspace{1pt}\sn{\rho}+1)},
+\end{equation}
+where the \emph{sum-negativity}~\cite{cit:veitch2} is the sum of the negative components in $\W{\rho}$,
+\begin{equation}
+    \sn{\rho} \coloneqq \sum\limits_{\bmx: \W[\bmx]{\rho} < 0} \abs{\W[\bmx]{\rho}}.
+\end{equation}
+
+Mana is an additive\footnote{It satisfies the condition $\mana{\rho_1 \otimes \rho_2} = \mana{\rho_1} + \mana{\rho_2}$ which is practical in distillation settings.} magic monotone, so it provides an analytical, necessary condition for many-copy magic state interconvertibility.
+
+A range of other monotones have been developed in the literature\cite{Wang_2018} \ddd{[CITE MORE]}, and each provides a means to upper bound distillation rates within a particular theory of magic.
+In this work we shall consider a broad framework for magic, with conditions that any theory of magic should satisfy.
+However, in contrast to prior works we shall not construct magic monotones, but instead develop a generalisation to resource monotones.
+The approach we take will also allow us to address how distillation rates are constrained by physical properties -- such as a system having biased-noise, some equilibrium structure or operations that manifest invariances, such as axial symmetry around the qubit $Z$-axis.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Stochastic structure of magic theories}
+\label{sec:struc}
+
 We also have Wigner representations for general quantum channels. We may exploit the channel-state duality and use the normalised Choi-Jamio\l{}kowski state 
@@
 In particular, $\cptp$ operations that map between density operators of equal dimensions and have non-negative Wigner distributions correspond to stochastic matrices, as shown in~\cref{app:wigner}
-
-\subsection{Magic monotones}
-\label{sec:mono}
-
-We highlight the defining property of a monotone, as it is useful in later discussion.
-\begin{definition}[\textbf{Resource monotone}]\label{def:mono}
-    Let $\R = (\F, \O)$ be a resource theory.
-    A resource monotone $\M$ is a projection from the set of quantum states of the theory onto the real line, so that $\M$ is monotonically decreasing under free operations,
-    \begin{equation}
-        \M(\rho_1) \leq \M(\rho_2)\ \text{whenever}\ \rho_1 \prec_{\R} \rho_2.
-    \end{equation}
-\end{definition}
-
-One of the most fundamental and commonly used magic monotones is the \emph{mana} of a state~\cite{cit:veitch2}, defined as
-\begin{equation}
-    \mana{\rho} \coloneqq \ln{(2\hspace{1pt}\sn{\rho}+1)},
-\end{equation}
-where the \emph{sum-negativity}~\cite{cit:veitch2} is the sum of the negative components in $\W{\rho}$,
-\begin{equation}
-    \sn{\rho} \coloneqq \sum\limits_{\bmx: \W[\bmx]{\rho} < 0} \abs{\W[\bmx]{\rho}}.
-\end{equation}
-Mana is an additive\footnote{It satisfies the condition $\mana{\rho_1 \otimes \rho_2} = \mana{\rho_1} + \mana{\rho_2}$ which is practical in distillation settings.} magic monotone, so it provides an analytical, necessary condition for many-copy magic state interconvertibility.
-The magic monotone of \emph{max--thauma}~\cite{Wang_2018} has also been introduced more recently for qudits of odd prime dimension.
-
-\subsection{Majorisation}
-\label{sec:major}
-
-Majorisation~\cite{cit:marshall} is a collection of powerful tools that has recently found many applications in quantum information theory~\cite{Nielsen_1999, cit:cwiklinski, cit:lostaglio2, cit:gour, cit:gour2, Horodecki_2003, Vallejos_2021}.
-It describes the \nick{disorder / non-uniformity} of distributions that undergo stochastic transformations.
-
-To formally state majorisation results, we first denote by $\stoch$ the set of $(d \times d)$ stochastic matrices that preserve the probability vector $\bmd$.
-Specifically, for any \emph{$\bmd$--stochastic matrix} $S \in \stoch$, all matrix elements are non-negative, all rows sum to $1$ and $S\bmd = \bmd$.
-The set $\stoch$ forms a group under matrix multiplication for any $\bmd$ with positive components.
-
-Majorisation describes quantum thermodynamics exactly in the absence of quantum coherence.
-The use of majorisation in this setting provides vital intuition for our purposes.
-At any given temperature $\beta^{-1}$, the thermal state $\gamma_\beta$ is thermodynamically the most disordered state. 
-Thermal operations are defined as operations that cannot extract energy from the Gibbs state, $\E(\gamma_\beta) = \gamma_\beta$.
-Convertibility between states via thermal operations is equivalent to a stochasticity condition on the energy level populations of the states~\cite{cit:lostaglio}.
-Informally, there exists a thermal operation $\E$ such that $\tau = \E(\rho)$ if and only if there exists a matrix $S \in \stoch$ such that $\bm{q} = S\bm{p}$, where $\bm{q}, \bm{p}$ and $\bmd$ and the energy level population vectors of $\tau, \rho, \gamma_\beta$ respectively.
-
-Based on this setting, we define $\bmd$--majorisation as follows.
-\begin{definition}[\textbf{$\boldsymbol\bmd$--majorisation}]\label{def:dmajor}
-    Given $\bmx, \bmy, \bmd \in \reals^d$, such that the components of $\bmd$ are positive, $\bmy$ is said to $\bmd$--majorise $\bmx$, iff there exists a $\bmd$--stochastic matrix $S$ such that $\bmx = S\bmy$.
-\end{definition}
-We denote this pre-order by $\bmx \prec_{\bmd} \bmy$.
-If $\bmd = \frac{1}{d}\bm{1}$, the $d$--dimensional uniform distribution, then $\stoch$ is the set of doubly stochastic matrices and we retrieve the familiar notion of majorisation from entanglement theory~\cite{Nielsen_1999}.
-
-The pre-order imposed by $\bmd$--majorisation admits a numerically efficient reformulation in terms of Lorenz curves.
-Let the vector $\bmu^\downarrow$ denote the vector $\bmu \in \reals^d$ with its components arranged in non-increasing order.
-\begin{definition}[\textbf{Lorenz curve}]\label{def:lc}
-    Let $\bmw, \bmd \in \reals^d$, where the components of $\bmd$ are positive with $D = \sum_{i=1}^d d_i$ and denote by $\widetilde{\bmw} \coloneqq (w_1/d_1, \dots, w_d/\nick{d_d})^T$ the rescaled vector $\bmw$ by $\bmd$.
-
-    Finally, denote by $\pi: \mathbb{Z}_d \mapsto \mathbb{Z}_d$ the permutation that sorts $\widetilde{\bmw}$, $(\widetilde{\bmw}^\downarrow)_i = w_{\pi(i)}$ for all $i=1,\dots,d$.
-
-    Consider the piecewise linear curve obtained by joining the points $\{(0,0)\} \cup \{ (x_k, \lc{\bmw}{\bmd}(k)) \}_{k=1,\dots,d}$, where
-    \begin{equation}\label{eq:lorenz}
-        (x_k, \lc{\bmw}{\bmd}(k)) \coloneqq \left( \frac{1}{D}\sum_{i=1}^k d_{\pi(i)}, \sum_{i=1}^k w_{\pi(i)} \right).
-    \end{equation}
-    We define the set of points on this curve, $\lc{\bmw}{\bmd}(x),\ x \in [0,1]$, as the \emph{Lorenz curve} of vector $\bmw$ with respect to $\bmd$.
-\end{definition}
-Components $x_k$ are rescaled by $D$ so that comparison of curves with unequal dimensions is possible.
-In fact, the Lorenz curves $\lc{\bmw}{\bmd}$ and $\lc{\bmw \otimes \bmd}{\bmd \otimes \bmd}$, where $\otimes$ denotes the Kronecker product, coincide.
-Furthermore, a Lorenz curve $\lc{\bmw}{\bmd}(x)$ is always concave in $x$, since it consists of $d$ line segments each with slope $(\widetilde{\bmw}^\downarrow)_i$ for $i=1,\dots,d$ which by definition is a non-increasing sequence.
-Finally, the points on the interior of the Lorenz curve that connect line segments of different slopes are in general non-differentiable and we call them\emph{elbows}.
-
-A vector $\bmy$ is said to \emph{$\bmd$--majorise} another vector $\bmx$ if and only if the Lorenz curve $\lc{\bmy}{\bmd}$ lies above Lorenz curve $\lc{\bmx}{\bmd}$, thus reducing $\bmd$--majorisation into a finite set of inequalities.
-\begin{theorem}\label{thm:dmajor}
-    Let $\bmx, \bmy, \bmd \in \reals^d$, such that the components of $\bmd$ are positive. 
-    Then, $\bmx \prec_{\bmd} \bmy$ if and only if $\lc{\bmx}{\bmd}(x) \leq \lc{\bmy}{\bmd}(x)$ for all $x \in [0,1]$ with strict equality at $x=1$.
-\end{theorem}
-A restatement of the theorem including more equivalent conditions and a proof are provided in~\cref{app:major}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Stochastic structure of magic theories}
-\label{sec:struc}
-
 \subsection{Magic fragments}\label{sec:magfrag}
@@
 
+\subsection{Majorisation}
+\label{sec:major}
+
+Majorisation~\cite{cit:marshall} is a collection of powerful tools that has recently found many applications in quantum information theory~\cite{Nielsen_1999, cit:cwiklinski, cit:lostaglio2, cit:gour, cit:gour2, Horodecki_2003, Vallejos_2021}.
+It describes the \nick{disorder / non-uniformity} of distributions that undergo stochastic transformations.
+
+To formally state majorisation results, we first denote by $\stoch$ the set of $(d \times d)$ stochastic matrices that preserve the probability vector $\bmd$.
+Specifically, for any \emph{$\bmd$--stochastic matrix} $S \in \stoch$, all matrix elements are non-negative, all rows sum to $1$ and $S\bmd = \bmd$.
+The set $\stoch$ forms a group under matrix multiplication for any $\bmd$ with positive components.
+
+Majorisation describes quantum thermodynamics exactly in the absence of quantum coherence.
+The use of majorisation in this setting provides vital intuition for our purposes.
+At any given temperature $\beta^{-1}$, the thermal state $\gamma_\beta$ is thermodynamically the most disordered state. 
+Thermal operations are defined as operations that cannot extract energy from the Gibbs state, $\E(\gamma_\beta) = \gamma_\beta$.
+Convertibility between states via thermal operations is equivalent to a stochasticity condition on the energy level populations of the states~\cite{cit:lostaglio}.
+Informally, there exists a thermal operation $\E$ such that $\tau = \E(\rho)$ if and only if there exists a matrix $S \in \stoch$ such that $\bm{q} = S\bm{p}$, where $\bm{q}, \bm{p}$ and $\bmd$ and the energy level population vectors of $\tau, \rho, \gamma_\beta$ respectively.
+
+Based on this setting, we define $\bmd$--majorisation as follows.
+\begin{definition}[\textbf{$\boldsymbol\bmd$--majorisation}]\label{def:dmajor}
+    Given $\bmx, \bmy, \bmd \in \reals^d$, such that the components of $\bmd$ are positive, $\bmy$ is said to $\bmd$--majorise $\bmx$, iff there exists a $\bmd$--stochastic matrix $S$ such that $\bmx = S\bmy$.
+\end{definition}
+We denote this pre-order by $\bmx \prec_{\bmd} \bmy$.
+If $\bmd = \frac{1}{d}\bm{1}$, the $d$--dimensional uniform distribution, then $\stoch$ is the set of doubly stochastic matrices and we retrieve the familiar notion of majorisation from entanglement theory~\cite{Nielsen_1999}.
+
+The pre-order imposed by $\bmd$--majorisation admits a numerically efficient reformulation in terms of Lorenz curves.
+Let the vector $\bmu^\downarrow$ denote the vector $\bmu \in \reals^d$ with its components arranged in non-increasing order.
+\begin{definition}[\textbf{Lorenz curve}]\label{def:lc}
+    Let $\bmw, \bmd \in \reals^d$, where the components of $\bmd$ are positive with $D = \sum_{i=1}^d d_i$ and denote by $\widetilde{\bmw} \coloneqq (w_1/d_1, \dots, w_d/\nick{d_d})^T$ the rescaled vector $\bmw$ by $\bmd$.
+
+    Finally, denote by $\pi: \mathbb{Z}_d \mapsto \mathbb{Z}_d$ the permutation that sorts $\widetilde{\bmw}$, $(\widetilde{\bmw}^\downarrow)_i = w_{\pi(i)}$ for all $i=1,\dots,d$.
+
+    Consider the piecewise linear curve obtained by joining the points $\{(0,0)\} \cup \{ (x_k, \lc{\bmw}{\bmd}(k)) \}_{k=1,\dots,d}$, where
+    \begin{equation}\label{eq:lorenz}
+        (x_k, \lc{\bmw}{\bmd}(k)) \coloneqq \left( \frac{1}{D}\sum_{i=1}^k d_{\pi(i)}, \sum_{i=1}^k w_{\pi(i)} \right).
+    \end{equation}
+    We define the set of points on this curve, $\lc{\bmw}{\bmd}(x),\ x \in [0,1]$, as the \emph{Lorenz curve} of vector $\bmw$ with respect to $\bmd$.
+\end{definition}
+Components $x_k$ are rescaled by $D$ so that comparison of curves with unequal dimensions is possible.
+In fact, the Lorenz curves $\lc{\bmw}{\bmd}$ and $\lc{\bmw \otimes \bmd}{\bmd \otimes \bmd}$, where $\otimes$ denotes the Kronecker product, coincide.
+Furthermore, a Lorenz curve $\lc{\bmw}{\bmd}(x)$ is always concave in $x$, since it consists of $d$ line segments each with slope $(\widetilde{\bmw}^\downarrow)_i$ for $i=1,\dots,d$ which by definition is a non-increasing sequence.
+Finally, the points on the interior of the Lorenz curve that connect line segments of different slopes are in general non-differentiable and we call them\emph{elbows}.
+
+A vector $\bmy$ is said to \emph{$\bmd$--majorise} another vector $\bmx$ if and only if the Lorenz curve $\lc{\bmy}{\bmd}$ lies above Lorenz curve $\lc{\bmx}{\bmd}$, thus reducing $\bmd$--majorisation into a finite set of inequalities.
+\begin{theorem}\label{thm:dmajor}
+    Let $\bmx, \bmy, \bmd \in \reals^d$, such that the components of $\bmd$ are positive. 
+    Then, $\bmx \prec_{\bmd} \bmy$ if and only if $\lc{\bmx}{\bmd}(x) \leq \lc{\bmy}{\bmd}(x)$ for all $x \in [0,1]$ with strict equality at $x=1$.
+\end{theorem}
+A restatement of the theorem including more equivalent conditions and a proof are provided in~\cref{app:major}.
+
 \subsection{Majorisation of quasi-probabilities in $\sigma$--fragments}\label{sec:major_frag}

### 2021-03-25 appendix.tex
tidyup

@@
 \end{proof}
-
-\iffalse % LOOSE BOUNDS & PLOT - START
-The experiment is described by binomial statistics and we define the left tail of the cumulative binomial distribution,
-\begin{equation}\label{eq:phil}
-	\Phi_\ell(m; n, p) \coloneqq \sum\limits_{j=0}^m \binom{n}{j} p^j (1-p)^{n-j},
-\end{equation}
-where $m\in [0,n]$.
-
-The symmetry between the left tail of a $p$--coin distribution and the right tail of a $(1-p)$--coin distribution dictates that
-\begin{align}\label{eq:phi_reverse}
-	\Phi_\ell(m; n, p) + \Phi_\ell(n-m-1; n, 1-p) &= 1,\ m\in [0,n-1],
-\end{align}
-Entropic bounds on $\Phi_\ell$~\cite{cit:ash}.
-\begin{lemma}\label{lem:phil_bounds}
-	Given fixed $n>0$ and $p$, $\Phi_\ell$ satisfies the following bounds:
-	\begin{align*}
-		\begin{split}
-		&\text{1. } \Phi_\ell(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ents},\ m\in [1,n-1] \\
-		&\text{2. } \Phi_\ell(m; n, p) \leq 2^{-n\ents},\ m\in [0,np] \\
-		&\text{3. } \Phi_\ell(m; n, p) \leq 1 - \left[ 8(m+1)\left(1-\frac{m+1}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m+1}{n}}{p}}, \\
-		&\hspace{14pt} m\in [0,n-2]
-		\end{split}
-		\\
-		&\text{4. } \Phi_\ell(m; n, p) \geq 1 - 2^{-n\ent{\frac{m+1}{n}}{p}},\ m\in [np+1,n-2]
-	\end{align*}
-\end{lemma}
-\begin{proof}
-	\nick{cite proof}
-\end{proof}
-Loose bounds follow
-\begin{lemma}\label{lem:bounds_loose}
-	Given fixed $n>0$ and $p$, $\Phi$ satisfies the following bounds:
-	\begin{align*}
-		\begin{split}
-		&\text{1. } \Phi_{\pm}(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ents},\ m\in [1,n-1] \\
-		&\text{2. } \Phi_{\pm}(m; n, p) \leq 2^{-n\ents},\ m\in [0,np] \\
-		&\text{3. } \Phi_{\pm}(m; n, p) \leq 1 - \left[ 8(m+1)\left(1-\frac{m+1}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m+1}{n}}{p}}, \\
-		&\hspace{14pt} m\in [0,n-2]
-		\end{split}
-	\end{align*}
-\end{lemma}
-\begin{proof}
-	\nick{paste proof}
-\end{proof}
-
-We can therefore use~\cref{lem:bounds_loose,lem:bounds_strict} to bound the standard Lorenz curves.
-\begin{figure}[b]
-    \centering
-    \includegraphics[scale=0.4]{figs/lc_bounds.pdf}
-    \caption{\textbf{Lorenz curves and bounding curves.} 
-    The figure explores the distillation process of a 10-copy $0.25$--noisy Strange state to a 4-copy $0.05$--noisy Strange state in the unital fragment.
-    Clearly, by looking at the Lorenz curves, the distillation process is possible.
-    However the bounding curves, derived in~\cref{lem:bounds_strict}, intersect at the end, suggesting that the process is not necessarily possible.
-    }
-    \label{fig:lc_bounds}
-\end{figure}
-\fi % LOOSE BOUNDS & PLOT - END
 

### 2021-03-25 notes/notes.tex
tidyup

@@
 So far we have introduced the notion of $\sigma$--fragments for any resource theory of magic. 
-In this section we pause to generalise this concept to an arbitrary resource theory and explain precisely how it connects with resource monotones. 
+In this section we briefly generalise this concept to arbitrary resource theories and explain precisely how it connects with resource monotones. 
 The busy reader more focussed on magic may skip this section.
@@
 
+\null\newpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Phi bounds}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[scale=0.4]{figs/lc_bounds.pdf}
+    \caption{\textbf{Lorenz curves and bounding curves.} 
+    The figure explores the distillation process of a 10-copy $0.25$--noisy Strange state to a 4-copy $0.05$--noisy Strange state in the unital fragment.
+    Clearly, by looking at the Lorenz curves, the distillation process is possible.
+    However the bounding curves, derived in~\cref{lem:bounds_strict}, intersect at the end, suggesting that the process is not necessarily possible.
+    }
+    \label{fig:lc_bounds}
+\end{figure}
+
+The experiment is described by binomial statistics and we define the left tail of the cumulative binomial distribution,
+\begin{equation}\label{eq:phil}
+	\Phi_\ell(m; n, p) \coloneqq \sum\limits_{j=0}^m \binom{n}{j} p^j (1-p)^{n-j},
+\end{equation}
+where $m\in [0,n]$.
+
+The symmetry between the left tail of a $p$--coin distribution and the right tail of a $(1-p)$--coin distribution dictates that
+\begin{align}\label{eq:phi_reverse}
+	\Phi_\ell(m; n, p) + \Phi_\ell(n-m-1; n, 1-p) &= 1,\ m\in [0,n-1],
+\end{align}
+Entropic bounds on $\Phi_\ell$~\cite{cit:ash}.
+\begin{lemma}\label{lem:phil_bounds}
+	Given fixed $n>0$ and $p$, $\Phi_\ell$ satisfies the following bounds:
+	\begin{align*}
+		\begin{split}
+		&\text{1. } \Phi_\ell(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ents},\ m\in [1,n-1] \\
+		&\text{2. } \Phi_\ell(m; n, p) \leq 2^{-n\ents},\ m\in [0,np] \\
+		&\text{3. } \Phi_\ell(m; n, p) \leq 1 - \left[ 8(m+1)\left(1-\frac{m+1}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m+1}{n}}{p}}, \\
+		&\hspace{14pt} m\in [0,n-2]
+		\end{split}
+		\\
+		&\text{4. } \Phi_\ell(m; n, p) \geq 1 - 2^{-n\ent{\frac{m+1}{n}}{p}},\ m\in [np+1,n-2]
+	\end{align*}
+\end{lemma}
+\begin{proof}
+	\nick{cite proof}
+\end{proof}
+Loose bounds follow
+\begin{lemma}\label{lem:bounds_loose}
+	Given fixed $n>0$ and $p$, $\Phi$ satisfies the following bounds:
+	\begin{align*}
+		\begin{split}
+		&\text{1. } \Phi_{\pm}(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ents},\ m\in [1,n-1] \\
+		&\text{2. } \Phi_{\pm}(m; n, p) \leq 2^{-n\ents},\ m\in [0,np] \\
+		&\text{3. } \Phi_{\pm}(m; n, p) \leq 1 - \left[ 8(m+1)\left(1-\frac{m+1}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m+1}{n}}{p}}, \\
+		&\hspace{14pt} m\in [0,n-2]
+		\end{split}
+	\end{align*}
+\end{lemma}
+\begin{proof}
+	\nick{paste proof}
+\end{proof}
+
+We can therefore use~\cref{lem:bounds_loose,lem:bounds_strict} to bound the standard Lorenz curves.
+
+\null\newpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Area monotone}\label{app:areamono}
@@
 
+\null\newpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Stabilizer proof details}

### 2021-03-26 appendix.tex
Added comments and citations in Sec.II

@@
 
-Here we present important properties of the Wigner distribution that are used throughout the paper.
+Here we present important properties of the phase-point operators and the Wigner distribution that are used throughout the paper.
+
+\begin{proposition}\label{thm:aproperties}
+    For any dimension $d$, the phase-point operators satisfy:
+    \begin{enumerate}
+        \item[(i)]\label{en:a1} Hermiticity and unitarity: $A_{\bmx}^\dagger = A_{\bmx} = A_{\bmx}^{-1}$;
+	    \item[(ii)]\label{en:a2} Closure under transposition: $A_{(x, p)}^T = A_{(x, p)}$;
+	    \item[(iii)]\label{en:a3} Unit trace for odd $d$: $\tr[A_{\bmx}] = 1$;
+	    \item[(iv)]\label{en:a4} Completeness relation: $\sum_{\bmz \in \cal{P}_d} A_{\bmz} = d\id$;
+	    \item[(i)]\label{en:a5} Orthogonality: $\tr[A_{\bmx}^\dagger A_{\bm{x'}}] = d \delta_{\bmx,\bm{x'}}$.
+	\end{enumerate}
+\end{proposition}
+\begin{proof}
+	All properties follow from the definition in~\cref{eq:ax} along with properties of the displacement operator $D_{\bmx}$ and can be found in the literature, e.g.~\cite{cit:veitch,Vourdas_2004,cit:gross3}
+\end{proof}
 
@@
 Let $\{\lambda_i\}_{i \in \mathbb{Z}_d}$ be the (non-negative) eigenvalues of $\rho$, summing to 1.
-        Let $\{\alpha_{\bmx,i}\}_{i \in \mathbb{Z}_d}$ be the eigenvalues of $A_{\bmx}$.
-For any $\bmx, \alpha_{\bmx,i} \in \{-1, 1\}$, due to the hermiticity and unitarity of the phase-point operators.
+Let $\{\alpha_{\bmx,i}\}_{i \in \mathbb{Z}_d}$ be the eigenvalues of $A_{\bmx}$. For any $\bmx, \alpha_{\bmx,i} \in \{-1, 1\}$, due to the hermiticity and unitarity of the phase-point operators. 
 Then,
-        \begin{equation}
-        \abs{\W{\rho}{\bmx}} = \frac{1}{d}\abs{\tr[A_{\bmx} \rho]} \leq \frac{1}{d} \abs{\sum_i \alpha_{\bmx,i} \lambda_i} \leq \frac{1}{d}\sum_i \lambda_i = \frac{1}{d}.
-        \end{equation}
-        The first inequality follows from Theorem 1 of~\cite{cit:mirsky} for complex matrices, while the second is the triangle inequality.
+\begin{align}
+	\abs{\W{\rho}{\bmx}} &= \frac{1}{d}\abs{\tr[A_{\bmx} \rho]} \leq \frac{1}{d} \abs{\sum_i \alpha_{\bmx,i} \lambda_i} \nonumber\\ &\leq \frac{1}{d}\sum_i \lambda_i = \frac{1}{d}.
+\end{align}
+The first inequality follows from Theorem 1 of~\cite{cit:mirsky} for the trace of complex matrices, while the second is the triangle inequality.
 \end{proof}

### 2021-03-26 magic_paper.tex
tidyup
Added comments and citations in Sec.II

@@
 \begin{document}
-% - vs -- (n-copy, sigma--fragment etc.)
 % Distillation rate vs bound
-% Sec: Appendix D
-% Sec: Intro
+% Proofs in App. A
+% Eq. numbering in last line always
+% Sec: App. D
 % Sec: General resources
 % Sec: Lower bounds
+% Sec: Intro
 % Sec: Abstract
-% Plot consistency (esp. figs 3,4,5,6)
-% Spacing
+% Figs consistency (esp. figs 3,4,5,6 and 1,7) + Figure 0 ?
+% Spacing (fig positioning, sections, paragraphs)
 
@@
 
-Central to our construction is the representation of any quantum state or quantum operation on a system of dimension $d$ in terms of quasi-probability representations on a discrete phase space \ddd{[CITE the review on quasi-reps]}.
+Central to our construction is the representation of any quantum state or quantum operation on a system of dimension $d$ in terms of quasi-probability representations on a discrete phase space \ddd{[CITE the review on quasi-reps]}\nick{which one?}.
 This construction is a discrete version of Wigner representations in quantum optics.
 
-We consider a $d$--dimensional quantum system with Hilbert space $\H_d$, and let $\{ |0\>, |1\>, \dots , |d-1\>\}$ denote the standard computational basis, defined over $\mathbb{Z}_d = \{ 0, 1, \dots,d-1 \}$.
-On this space, generalised Pauli matrices $X, Z$ can be defined by their respective roles as shift and phase operators, which act on the basis states as follows,
+Consider a $d$--dimensional quantum system with Hilbert space $\H_d$, and let $\{ |0\>, |1\>, \dots , |d-1\>\}$ denote the standard computational basis, defined over $\mathbb{Z}_d = \{ 0, 1, \dots,d-1 \}$.
+On this space, generalised Pauli matrices $X, Z$ can be defined by their respective roles as shift and phase operators, acting on the basis states as follows,
 \begin{align}
@@
 \end{equation}
-where a phase factor $\tau \coloneqq -\omega^{1/2}$ ensures unitarity.
-We assume going forward that $d$ is an odd prime, however the case $d=2$ can be also handled, but with some additional technical caveats \ddd{[CITE]}.
+where the phase factor $\tau \coloneqq -\omega^{1/2}$ ensures unitarity.
+We assume going forward that $d$ is an odd prime, however the case $d=2$ can also be handled, but with some additional technical caveats~\cite{Appleby_2005}.
 For a composite system with composite dimension $d = d_1 \dots d_n$ we can decompose the Hilbert space as $\cal{H}_d = \cal{H}_{d_1} \otimes \dots \otimes \cal{H}_{d_n}$, and then define displacement operators as
@@
 to denote the phase space point for the composite system. 
-For simplicity going forward we assume $n$ copies of a $d$--dimensional system $d_1=d_2 = \cdots = d$, and therefore, we have that $\x \in \mathbb{Z}_d^{2n}$.
+For simplicity going forward, we assume $n$ copies of a $d$--dimensional system $d_1=d_2 = \cdots = d$, and therefore, we have that $\x \in \mathbb{Z}_d^{2n}$.
 
@@
 \end{equation}
-The Clifford operations $ \cal{C}_d^n $ are then defined as the set of unitaries that normalise the Heisenberg-Weyl group \ddd{[CITE]}.
-We may define the pure stabiliser states as those states obtained by acting on $|0\>$ with Clifford unitaries.
+The Clifford operations $ \cal{C}_d^n $ are then defined as the set of unitaries that normalise the Heisenberg-Weyl group~\cite{Appleby_2005}.
+We may define the pure stabiliser states as those states obtained by acting on $|0\>$ with Clifford unitaries~\cite{cit:gross3}.
 Finally, we define $\stab$ as the convex hull of all pure stabiliser states, namely all probabilistic mixtures of states of the form $U|0\>\<0|U^\dagger$ where $U$ is some Clifford unitary.
@@
 
-In order to provide a complete decomposition of arbitrary quantum states and quantum operations we now define a complete basis of hermitian observables that behaves naturally under the action of the Clifford group.
-To every point $\x \in \P_d$ we define the phase-point operator $A_{\x}$ given by
-\begin{align}
-	A_{\bmx} \coloneqq \frac{1}{d} \sum_{\bmz \in \cal{P}_d} \omega^{\eta(\bmx, \bmz)} D_{\bmz}, \label{eq:ax}
-\end{align}
+In order to provide a complete decomposition of arbitrary quantum states and quantum operations we now define a complete basis of Hermitian observables that behaves naturally under the action of the Clifford group.
+At every point $\x \in \P_d$ we define the phase-point operator
+\begin{equation}\label{eq:ax}
+	A_{\bmx} \coloneqq \frac{1}{d} \sum_{\bmz \in \cal{P}_d} \omega^{\eta(\bmx, \bmz)} D_{\bmz}, 
+\end{equation}
 where $\eta(\bmx, \bmz)$ is the symplectic inner product between any two points $\x,\z \in \P_d$, and is given explicitly by
@@
 
-The phase-point operators form an orthogonal (with respect to the Hilbert-Schmidt inner product) operator basis as shown in~\cref{app:wigner}.
+The phase-point operators form an orthogonal (with respect to the Hilbert-Schmidt inner product) operator basis as discussed in~\cref{app:wigner}.
 Therefore, any quantum state $\rho \in \cal{B}(\cal{H}_d)$ can be expressed as a linear combination of them,
@@
 For any quantum state $\rho$, the Wigner distribution $W_\rho(\bmx)$ is readily seen to be a $d^2$-dimensional quasi-probability distribution over $\cal{P}_d$ (see~\cref{app:wigner} for details).
-More precisely, $W_\rho(\x)$ is a real-valued function on $\P_d$ with the property that $\sum_{\x} W_\rho(x) = 1$.
+More precisely, $W_\rho(\x)$ is a real-valued function on $\P_d$ with the property that $\sum_{\x} W_\rho(\bmx) = 1$.
 In~\cref{fig:wstate_examples}, we show Wigner distributions of different types of qutrit states.
+
+We may also exploit the channel-state duality and use the normalised Choi-Jamio\l{}kowski state 
+\begin{equation}\label{eq:cj}
+  \J(\E) \coloneqq \frac{1}{d_A}(\id \otimes \E) \sum_{i,j} \ket{ii}\bra{jj}
+\end{equation}
+to extend the definition of the Wigner distribution to a quantum channel $\E: \B(\H_A) \rightarrow \B(\H_B)$, via the expression
+\begin{align}\label{eq:woperation}
+    \W[\bmy|\bmx]{\E} 
+    &\coloneqq d_A^2 \W[\bm{\bar x} \oplus \bmy]{\J(\E)} \nonumber\\
+    &= \frac{1}{d_B} \tr_B[A_{\bmy} \E(A_{\bmx})],
+\end{align}
+where $\bm{\bar x} = (x_1, -p_1, \dots, x_n, -p_n)$ is $\bmx$ with momentum coordinates negated.
+
+The specific form of~\cref{eq:woperation} is chosen so that Wigner distributions of channels act as transition matrices for Wigner distributions of states, $\W{\E(\rho)} = \W{\E}\W{\rho}$.
+In particular, $\cptp$ channels that map between density operators of equal dimensions and have non-negative Wigner distributions correspond to stochastic matrices, as shown in~\cref{app:wigner}
 
@@
 
-The state-injection model for quantum computation \ddd{[CITE]} is a key avenue to realising a full-scale, fault-tolerant quantum computer.
-Within the approach Clifford unitaries can be done in a robust, fault-tolerant way.
-However, due to the Eastin-Knill theorem \ddd{[CITE]}, it is impossible to have a universal set of transversal gates and so while Clifford unitaries can be realised transversally one must find ways around the Eastin-Knill restriction.
-The state-injection approach supplements the Clifford gates with noisy quantum states, called `magic states', that are outside the set of stabliser states and, when incorporated into Clifford circuits, provides universality.
-The obstacle to this is that the states are invariably noisy and so protocols must be employed so as to purify many copies of the magic states and improve the overall performance of the induced quantum gates.
+\nick{There are repetitions with text in introduction, this sections looks more introduction-like I think ?}
+
+The state-injection model for quantum computation~\cite{cit:bravyi} is a key avenue to realising a full-scale, fault-tolerant quantum computer.
+Within this approach, Clifford unitaries can be done in a robust, fault-tolerant way.
+However, due to the Eastin-Knill theorem~\cite{Eastin_2009}, it is impossible to have a universal set of transversal gates and so while Clifford unitaries can be realised transversally one must find ways around the Eastin-Knill restriction.
+The state-injection approach supplements the Clifford gates with noisy quantum states, called `magic states', that are outside the set of stabliser states and, when incorporated into Clifford circuits, provide universality.
+The obstacle to this is that the states are invariably noisy and so protocols must be employed to purify many copies of the magic states and improve the overall performance of the induced quantum gates.
 A central question is then: given a number $n$ of noisy magic states how many purified magic states can we obtain within the fault-tolerant set of quantum operations?
@@
 To address such questions both concrete distillation protocols have been developed, and there has been analysis of bounds of distillation rates within natural theoretical frameworks.
-These frameworks provide theories of magic in which one views magic states as ``resource'' states with respect to a natural class of quantum operations that are consider cheap, or ``free'' \ddd{[CITE Gour resource review]}.
+These frameworks provide theories of magic in which one views magic states as ``resource'' states with respect to a natural class of quantum operations that are consider cheap, or ``free''~\cite{Gour_2019}.
 One very natural class of free operations considered are those obtained from Clifford operations, measurements and the ability to discard quantum systems.
@@
 
-A range of other monotones have been developed in the literature\cite{Wang_2018} \ddd{[CITE MORE]}, and each provides a means to upper bound distillation rates within a particular theory of magic.
+A range of other monotones have been developed in the literature\cite{cit:howard, Wang_2020, Seddon_2021} \nick{actually there aren't that many} and each provides a means to upper bound distillation rates within a particular theory of magic.
 In this work we shall consider a broad framework for magic, with conditions that any theory of magic should satisfy.
@@
 
-We also have Wigner representations for general quantum channels. We may exploit the channel-state duality and use the normalised Choi-Jamio\l{}kowski state 
-\begin{equation}\label{eq:cj}
-  \J(\E) \coloneqq \frac{1}{d_A}(\id \otimes \E) \sum_{i,j} \ket{ii}\bra{jj}
-\end{equation}
-to extend the definition of the Wigner distribution to a quantum channel $\E: \B(\H_A) \rightarrow \B(\H_B)$, via the expression
-\begin{align}\label{eq:woperation}
-    \W[\bmy|\bmx]{\E} 
-    &\coloneqq d_A^2 \W[\bm{\bar x} \oplus \bmy]{\J(\E)} \\
-    &= \frac{1}{d_B} \tr_B[A_{\bmy} \E(A_{\bmx})],
-\end{align}
-where $\bm{\bar x} \coloneqq (x, -p)$.
-
-The specific form of~\cref{eq:woperation} is chosen so that Wigner distributions of operations act as transition matrices for Wigner distributions of states, $\W{\E(\rho)} = \W{\E}\W{\rho}$.
-In particular, $\cptp$ operations that map between density operators of equal dimensions and have non-negative Wigner distributions correspond to stochastic matrices, as shown in~\cref{app:wigner}
 \subsection{Magic fragments}\label{sec:magfrag}

### 2021-03-26 magic_paper.tex
small changes

@@
 % Figs consistency (esp. figs 3,4,5,6 and 1,7) + Figure 0 ?
-% Spacing (fig positioning, sections, paragraphs)
+% Spacing (fig positioning, sections, paragraphs, QED symbols)
 
@@
     \caption{\textbf{A `heretical' family of Lorenz curves.} Traditionally, Lorenz curves are monotone increasing cumulant functions that reach a maximum value of $1$.
-In contrast, Lorenz curves for magic states break through the value of $L(x)=1$ due to the presence of negativity in the associated quasi-probability distribution.
+In contrast, Lorenz curves for magic states break through the value of $L(x)=1$ due to the presence of negativity in the associated quasi-probability distributions.
 The above family of curves correspond to multiple copies of noisy Strange states $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ for $n=1,2,3,4$ within a particular stabilizer fragment.
@@
 Given this context, we now provide the following result on bounding the distillation rate $R = R(\epsilon, \epsilon', \beta) \coloneqq \frac{n'}{n}$ of the process in~\cref{eq:stdist}.
+\nick{I think we should denote distillation rates by $R$ and our distillation bound by $R(\epsilon, \epsilon', \beta)$, since the bound is what really depends on $\epsilon, \epsilon', \beta$.}
 We also write $R(\epsilon, \beta) = R(\epsilon, \epsilon'=0, \beta)$.
@@
 \begin{align}
-	\W[\bmx]{\gamma_\beta} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z_\beta}\W[\bmx]{\ketbra{k}} \\
+	\W[\bmx]{\gamma_\beta} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z_\beta}\W[\bmx]{\ketbra{k}} \nonumber\\
 	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z_\beta} \delta_{x_0, k} = \frac{e^{-\beta E_{x_0}}}{3\Z_\beta},
@@
 \begin{align}
-	&\bmw(\rho_{\rm{S}} | \gamma)_{\rm{max}} \coloneqq \label{eq:max_slope}\\
-	&(3\Z)^{n} \max\limits_{i,j,k}\Big\{ (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \nonumber
+	&\bmw(\rho_{\rm{S}} | \gamma)_{\rm{max}} \coloneqq (3\Z)^{n}\times \nonumber\\
+	&\max\limits_{i,j,k}\Big\{ (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \label{eq:max_slope}
 \end{align}
@@
 The maximum rescaled component can then be expressed as
-\begin{equation*}
+\begin{equation}
 \bmw(\rho_{\rm{S}} | \gamma)_{\rm{max}} =
 	\begin{cases}
-		(3\Z)^{n} v^n e^{n\beta E_0}, &\epsilon \leq \epsilon_{\star},\ \hspace{30pt}\rm{(C1)}	\\
-		(3\Z)^{n} u^n e^{n\beta E_{\rm{max}}}, &\epsilon > \epsilon_{\star}.\ \hspace{32pt}\rm{(C2)} 
+		(3\Z)^{n} v^n e^{n\beta E_0}, &\epsilon \leq \epsilon_{\star},\ \hspace{3pt}\rm{(C1)}	\\
+		(3\Z)^{n} u^n e^{n\beta E_{\rm{max}}}, &\epsilon > \epsilon_{\star}.\ \hspace{5pt}\rm{(C2)} 
 	\end{cases}
-\end{equation*}
+\end{equation}
 Case $\rm{(C1)}$ corresponds to $(i,j,k) = (0,0,0)$, so the multiplicity is $m_{000} = 1$ and the corresponding Wigner components are $\bmw(\rho_{\rm{S}})_{000}, \bmw(\gamma)_{000}$. 
@@
 
-State convertibility within a given resource theory is often a hard question to address due to the intricate structure of the theory.
+State convertibility within a given resource theory is often a hard question to address due to intricacies of the theory structure.
 In general, the structure of a theory $\R$ is described by a pre-order $\prec_\R$ and usually resource monotones are employed to reduce this structure into a simple real number ordering.
-The subdivisions of magic theories into $\sigma$--fragments suggests a new approach towards investigating state convertibility which retains more structure of the originaltheory than a measure can.
+The subdivisions of magic theories into $\sigma$--fragments suggests a new approach towards investigating state convertibility which retains more structure of the original theory than a measure can.
 
@@
 	Consider a monotone $\M$ in the context of a general resource theory $\R = (\F, \O)$.
-	State order is covariantly preserved due to the defining property of a monotone, stated in~\cref{def:mono}, where the pre-order $\prec_{\R'}$ is simply the total order $\leq$ on $\mathbb{R}$.
+	State order is covariantly preserved due to the defining property of a monotone, where the pre-order $\prec_{\R'}$ is simply the total order $\leq$ on $\mathbb{R}$.
 

### 2021-03-26 notes/notes.tex
small changes

@@
 The use of covariant and contravariant in~\cref{def:covproj,def:contraproj} refers to the direction of implication between the two pre-orders and operation compositions\footnote{Note that strictly these are not projections in the sense of $\Pi^2 = \Pi$, but are instead morphisms.
-Here our use of the term projection is motivated by the idea that one one generally loses information about $\R$ under the mapping.}.
-
-\nick{Perhaps scrap definition of contravariant projection and define contravariant fragment as a subtheory $\R'$ where there exists a (injective) covariant projection from $\R'$ to parent theory $\R$.
-That would make every subtheory $\R' = (\F', \O')$ a contravariant fragment if $\O'$ is closed under composition, this includes $\sigma$--fragments.}
+Here our use of the term projection is motivated by the idea that one one generally loses information about $\R$ under the mapping.}
 

### 2021-03-27 magic_paper.tex
Edits for Section III begun. Re-structuring of material and emphasis.

@@
 
-Central to our construction is the representation of any quantum state or quantum operation on a system of dimension $d$ in terms of quasi-probability representations on a discrete phase space \ddd{[CITE the review on quasi-reps]}\nick{which one?}.
+Central to our construction is the representation of any quantum state or quantum operation on a system of dimension $d$ in terms of quasi-probability representations on a discrete phase space \ddd{[CITE the review on quasi-reps-- I think Chris Ferrie has one that is good.]}\nick{which one?}.
 This construction is a discrete version of Wigner representations in quantum optics.
@@
 In~\cref{fig:wstate_examples}, we show Wigner distributions of different types of qutrit states.
-
-We may also exploit the channel-state duality and use the normalised Choi-Jamio\l{}kowski state 
-\begin{equation}\label{eq:cj}
-  \J(\E) \coloneqq \frac{1}{d_A}(\id \otimes \E) \sum_{i,j} \ket{ii}\bra{jj}
-\end{equation}
-to extend the definition of the Wigner distribution to a quantum channel $\E: \B(\H_A) \rightarrow \B(\H_B)$, via the expression
-\begin{align}\label{eq:woperation}
-    \W[\bmy|\bmx]{\E} 
-    &\coloneqq d_A^2 \W[\bm{\bar x} \oplus \bmy]{\J(\E)} \nonumber\\
-    &= \frac{1}{d_B} \tr_B[A_{\bmy} \E(A_{\bmx})],
-\end{align}
-where $\bm{\bar x} = (x_1, -p_1, \dots, x_n, -p_n)$ is $\bmx$ with momentum coordinates negated.
-
-The specific form of~\cref{eq:woperation} is chosen so that Wigner distributions of channels act as transition matrices for Wigner distributions of states, $\W{\E(\rho)} = \W{\E}\W{\rho}$.
-In particular, $\cptp$ channels that map between density operators of equal dimensions and have non-negative Wigner distributions correspond to stochastic matrices, as shown in~\cref{app:wigner}
 
@@
 
-\nick{There are repetitions with text in introduction, this sections looks more introduction-like I think ?}
+\nick{There are repetitions with text in introduction, this sections looks more introduction-like I think ?}\ddd{We'll organise things later - better to get key chunks down first.}
 
@@
 
-A range of other monotones have been developed in the literature\cite{cit:howard, Wang_2020, Seddon_2021} \nick{actually there aren't that many} and each provides a means to upper bound distillation rates within a particular theory of magic.
+A range of monotones have been developed in the literature\cite{cit:howard, Wang_2020, Seddon_2021} and each provides a means to upper bound distillation rates within a particular theory of magic.
 In this work we shall consider a broad framework for magic, with conditions that any theory of magic should satisfy.
@@
 
-\section{Stochastic structure of magic theories}
+\subsection{Stochastic structure of magic theories}
 \label{sec:struc}
 
-\subsection{Magic fragments}\label{sec:magfrag}
-
-Equipped with the definitions of the Wigner distribution in odd prime dimensions, we can formally recast the maximal magic theory $\Rmax$ into a stochasticity setting.
-The free states correspond to proper probability distributions 
-\begin{equation}
-    \Fmax \coloneqq \{ \rho: \W[\bmx]{\rho} \geq 0 \text{ for all } \bmx \in \cal{P}_d\}
-\end{equation}
-
-The free operations should send the set of free states $\Fmax$ into itself and completely preserve the non-negativity of the states, in the sense that $\E \in \Omax$ iff $(\id_d \otimes \E ) \sigma \in \stab$ for all odd prime dimensions $d$ whenever $\sigma \in \Fmax$.
-It is shown by Wang \textit{et al.}~\cite{Wang_2019} that $\Omax$ coincides with the set of operations $\E$ with stochastic Wigner distributions, 
-\begin{equation}
-    \Omax = \{ \E: \W[\bmy|\bmx]{\E} \geq 0 \text{ for all } \bmx, \bmy \in \cal{P}_d\}.
-\end{equation}
-
-Every established magic theory $\R = (\F, \O)$ is a subtheory of $\Rmax$ in the sense that $\F \subseteq \Fmax$ and $\O \subseteq \Omax$, and as such it falls under this new stochasticity setting. 
-For technical simplicity in what follows we assume that $\F$ is a closed set, and note that $\F_{\rm{ max}}$ is itself a closed set, since it is specified by a finite set of linear constraints of the form $\tr[ L\rho] \geq 0$ with operators $L \in \cal{B}(\cal{H})$ ensuring that the state is positive and Wigner-positive.
-
-Given this context we now define the following key notion, that is central to our analysis.
+Within the Wigner representation all negatively represented states are magic states, although in general the converse is not true.
+However, it is known that all positively represented states used in Clifford circuits admit an efficient classical description, and therefore it is natural to consider focus on describing those negatively represented magic states.
+The free states in any magic theory therefore lie in the set
+\begin{equation}
+    \Fmax \coloneqq \{ \rho: \W[\bmx]{\rho} \geq 0 \text{ for all } \bmx \in \cal{P}_d\}.
+\end{equation}
+Our focus is on states with negativity, and so the particular choice of free states is not so important for our analysis.
+The remaining component that needs addressing is the set of quantum operations that is considered free, or easy.
+Stabilizer operations are the most natural set of operations as they admit a classically efficient description for uniform quantum circuits.
+However, other choices of operations have been considered in the literature \ddd{[CITE]}.
+Common to these theories is that free $\E$  is such that $id \otimes \E (\rho)$ has a positive Wigner distribution whenever $ \rho$ has a positive Wigner distribution.
+Therefore the condition that $\E$ does not generate Wigner negativity is an essential requirement of any magic theory.
+
+Any quantum channel admits a Wigner representation, in terms of the phase space operators defined earlier.
+If $\E$ is some quantum channel from a quantum system $A$ to a quantum system $B$, and $\J(\E)$ is its associated Choi state then we can define
+\begin{equation}
+W_{\E}(\y |\x) := d_A^2 W_{\J(\E)}(\bar{\x} \oplus \y),
+\end{equation}
+where $\bar{x} =(x_1, -p_1, \dots , x_n, -p_n)$ can be viewed as the time-reversed version of $\x$ in the discrete phase space, where momenta are reflected while coordinates remain unchanged.
+
+With this representation of a quantum channel, we can view $W_{\E}( \y | \x)$ as a transition matrix sending $\x \rightarrow \y$, which is consistent with the representation of quantum states, as
+\begin{equation}
+W_{\E(\rho)} (\y) = \sum_{\x \in \P_d} W_{\E}( \y | \x) W_\rho(\x),
+\end{equation}
+for any $\E$ and $\rho$.
+Now if $\E$ sends any positively represented quantum state to another positively represented quantum state then it can be shown~\cite{Wang_2019} that $W_{\E}(\y |\x)$ must form a stochastic matrix.
+In particular, all Clifford operations correspond to stochastic matrices in this Wigner representation.
+However, it is important to note that not all stochastic maps on the phase space correspond to valid quantum operations.
+In particular, the stochastic maps must respect the symplectic structure of the phase space and so this provides an additional non-trivial constraint.
+
+In what follows we shall therefore assume that we have a magic theory $\R = (\F, \O)$ in which the free states $\F$ form a closed, convex set with each state represented by a positive Wigner function, while the free operations $\O$ are represented by stochastic maps acting on the discrete phase space.
+
+\section{Breaking a magic theory into fragments}
+We wish to consider how physical constraints that may be hardware specific, affect magic distillation rates.
+These are not a priori encoded in the formulation of the magic theory, and constitute additional physical conditions on top of the underlying resource-theoretic accounting.
+For example, there may be non-trivial thermal noise in the physical set-up or the accessible operations, there might be strong bias in the noise present, or we might be limited in how easily certain gates can be realised.
+\ddd{[find roughly related cites for these?]}
+
+While we will not consider very model-specific limitations, we still want to inject in some physical constraints.
+We proceed by considering imposing equilibrium, or fixed-point, restrictions on the actual operations that are accessible to us.
+While such restrictions could be viewed as the existence of some non-trivial thermodynamic constraint, it could equally be viewed as encoding a high noise-bias or difficulty in realising a particular quantum gate.
+We can therefore define the following sub-theory of any magic theory $\R$.
 \begin{definition}[\textbf{$\boldsymbol\sigma$--fragment}]\label{def:sigmafrag}
-   Given a resource theory of magic $\R = (\F, \O)$, the \emph{$\sigma$--fragment of $\R$} is the resource theory $\R_\sigma = (\F_\sigma, \O_\sigma)$, where $\F_\sigma = \{\sigma\}$ and the free operations are restricted to the ones that leave $\sigma$ invariant,
-    \begin{equation}
-        \O_\sigma \coloneqq \{ \E \in \O: \E(\sigma) = \sigma \}.
-    \end{equation}
+   Given a theory of magic $\R = (\F, \O)$, the \emph{$\sigma$--fragment of $\R$} is the sub-theory $\R_\sigma = (\F, \O_\sigma)$, in which the free operations are 
+   \begin{equation}
+        \O_\sigma \coloneqq \{ \E \in \O: \E(\sigma) = \sigma \},
+    \end{equation}
+namely those operations that leave the state $\sigma \in \F$ invariant.
 \end{definition}
-
-Note that $\F = \bigcup_{\sigma \in \F} \F_\sigma$ trivially.
-With this basic notion defined, we now show that this union holds for free operations as well and therefore that any resource theory of magic can be faithfully subdivided into $\sigma$--fragments, in such a way that any problem of interconversion in the parent magic theory $\R$ can be analysed across the different fragments.
-
+This notion provides a simple way to break up any theory into smaller, more manageable parts that are destinguished by additional physical constraints.
+Moreover, the union over all fragments returns the parent theory, and so we are not discarding any information about the theory by breaking it up in this way.
+This can be made precise as follows.
 \begin{theorem}\label{thm:frag}
     Let $\R = (\F, \O)$ be a theory of magic.
-    Every operation in $\O$ leaves at least one free state invariant,
-  \begin{equation}
-\O = \bigcup\limits_{\sigma \in \F} \O_\sigma.
-\end{equation}
-Therefore, $\rho \longrightarrow \tau$ in $\R$ if and only if $\rho \longrightarrow \tau$ in a $\sigma$--fragment of $\R$.
+Then a transformation $\rho \longrightarrow \tau$ is possible in $\R$ if and only if the transformation $\rho \longrightarrow \tau$ is possible in at least one $\sigma$--fragment of $\R$.
 \end{theorem}
+The proof of this is very straightforward.
 \begin{proof}
-    Suppose $\E$ is in a $\sigma$--fragment $\O_\sigma$.
-    Then it is also in $\O$, hence $\bigcup\limits_{\sigma \in \F} \O_\sigma \subseteq \O$.
-
-    Conversely, suppose $\E$ is in $\O$. 
-    The free states are a closed set that is mapped one-to-one to a closed subset $\cal{S}$ of the $(d^2 - 1)$--dimensional probability simplex.
-    $\cal{S}$ is convex, since any combination of free states is also free and the Wigner distribution is linear.
-    Therefore, $\cal{S}$ is convex and compact as a closed convex subset of the bounded compact probability simplex.
-
-    We can now view $\W{\E}$ as a stochastic, continuous mapping from $\cal{S}$ to itself, thus Brouwer's fixed point theorem~\cite{cit:brouwer} implies that there exists a probability distribution $d_{\bmz}$ for some $ \bmz \in \cal{P}_d$ that is a fixed point of $\W{\E}$.
-    This corresponds to a free state $\sigma \coloneqq \sum_{\bmz \in \cal{P}_d} d_{\bmz} A_{\bmz} \in \F$. 
-    Therefore $\E \in \O_\sigma$, and so $\O = \bigcup\limits_{\sigma \in \F} \O_\sigma$.
-
-    The state interconversion result follows immediately.
+    Suppose the interconversion is possible in a $\sigma$--fragment via some $\E \in \O_\sigma$.
+But since $\O_\sigma \subseteq \O$ it is also possible in $\R$.
+Conversely, suppose the transformation is possible in $\R$ via some $\E$ in $\O$.
+The free states $\F$ are a closed, convex set and moreover the image of $\F$ under the map $\E$ is in $\F$.
+By the Brouwer Fixed-Point theorem~\cite{cit:brouwer} this mapping must therefore have a fixed point $\sigma \in \F$.
+Therefore $\E \in \O_\sigma$ and so the interconversion is possible in this fragment.
 \end{proof}
+
+This implies that we can now consider magic distillation rates within a particular $\sigma$--fragment and then see how the bounds on the distillation rates depend on the particular fragment we work within.
+Therefore, this route can potentially shed light on how the physics of a protocol constrain distillation rates above and beyond global constraints from the parent resource theory.
+For example, how does temperature affect distillation bounds?
+Do isotropic maps have better bounds, or does bias towards a pure stabilizer state fixed point provide more freedom?
+
 \begin{figure}[t]
@@
 
-The zoo of all magic operation classes is summarised in ~\cref{fig:zoo}.
-It is clear from the diagram that free operations are in general mapped onto strict subsets of stochastic maps.
-This statement, along with more technical properties of the $\sigma$--fragment are discussed in~\cref{app:frag}.
-Completely positive-Wigner-preserving operations~\cite{Wang_2019} form the maximal operation class $\Omax$.
-This theory of magic is thus covered by $\sigma$--fragments exactly and every other magic theory is contained within this cover.
-In particular, the stabiliser operations $\so$ are contained within $\Omax$.
-
-Every  quantum circuit aiming at a given magic state conversion $\rho \longrightarrow \tau$ possesses certain symmetries according to~\cref{thm:frag} that allow us to study the conversion within only certain $\sigma$--fragments that reflect these symmetries.
-As a simple example, the dephasing channel
-\begin{equation}\label{eq:dephase}
-	\Delta(\rho) = \sum_{k \in \mathbb{Z}_d} \ketbra{k}{k}\rho\ketbra{k}{k}
-\end{equation}
-removes coherent phases in the computational basis and therefore leaves exactly all mixtures of computational basis states invariant.
-A noise channel consisting only of such dephasing operations can be fully analysed in the $\sigma$--fragments for the pure computational basis states $\sigma$ as proven in~\cref{app:frag}.
-
-The subdivision of magic theories into $\sigma$--fragments is also powerful because the pre-order $\prec_{\R_\sigma}$ of every $\sigma$--fragment is described by well-behaved majorisation tools, as we establish in the rest of this section.
-
-\subsection{Majorisation}
+More importantly, by adding in this additional structure to the magic theory, it actually allows us to say more than would be possible at the level of the full parent theory.
+In particular, the interconversion structure in each fragment can be analysed using tools from single-shot thermodynamics and majorization theory as we discuss in the next section.
+
+\subsection{Quantifying disorder without entropies}
 \label{sec:major}
@@
 Majorisation~\cite{cit:marshall} is a collection of powerful tools that has recently found many applications in quantum information theory~\cite{Nielsen_1999, cit:cwiklinski, cit:lostaglio2, cit:gour, cit:gour2, Horodecki_2003, Vallejos_2021}.
-It describes the \nick{disorder / non-uniformity} of distributions that undergo stochastic transformations.
+It describes the disorder of distributions that undergo stochastic transformations.
 
@@
 
-\nick{Mention relative majorisation as a possibility}
-
 \subsection{Lorenz curves of quasi-probabilities in $\sigma$--fragments}
@@
 the $\sigma$--fragment defined by the maximally mixed state $\sigma = \frac{1}{d}\id$ whose Wigner distribution is the uniform probability distribution.
+
 \begin{figure}
     \centering
-    \includegraphics[height=5cm]{figs/lctoy.pdf}
+    \includegraphics[height=4.5cm]{figs/lc_strange.pdf}
+    \caption{\textbf{A `heretical' family of Lorenz curves.} Traditionally, Lorenz curves are monotone increasing cumulant functions that reach a maximum value of $1$.
+In contrast, Lorenz curves for magic states break through the value of $L(x)=1$ due to the presence of negativity in the associated quasi-probability distributions.
+The above family of curves correspond to multiple copies of noisy Strange states $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ for $n=1,2,3,4$ within a particular stabilizer fragment.
+Solid lines represent pure Strange states, while dashed lines represent noisy Strange states with depolarising noise $\epsilon = 0.1$.
+    }
+    \label{fig:lcs}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[height=4.5cm]{figs/lctoy.pdf}
     \caption{\textbf{Quasi-probability Lorenz curve comparison}.
@@
     The maximally mixed state curve is simply the line connecting $(0,0)$ and $(1,1)$.
-    There is no operation in $\O_{\id/d}$ that can convert $\ket{\rm{S}}$ to $\ket{0}$, as their Lorenz curves intersect.
+    There is no operation in $\O_{\id/d}$ that can convert $\ket{\rm{S}}$ to $\ket{0}$, as their Lorenz curves intersect.\ddd{[Is debatable if this figure gives much...is a bit boring.]}
     }
@@
 Due to~\cref{lem:lcmax}, it is clear that the curves peak at $1 + \sn{\rho_{\rm{S}}(\epsilon)^{\otimes n}}$.
-\begin{figure}
-    \centering
-    \includegraphics[height=5cm]{figs/lc_strange.pdf}
-    \caption{\textbf{A `heretical' family of Lorenz curves.} Traditionally, Lorenz curves are monotone increasing cumulant functions that reach a maximum value of $1$.
-In contrast, Lorenz curves for magic states break through the value of $L(x)=1$ due to the presence of negativity in the associated quasi-probability distributions.
-The above family of curves correspond to multiple copies of noisy Strange states $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ for $n=1,2,3,4$ within a particular stabilizer fragment.
-Solid lines represent pure Strange states, while dashed lines represent noisy Strange states with depolarising noise $\epsilon = 0.1$.
-    }
-    \label{fig:lcs}
-\end{figure}
 
@@
 \label{sec:unital}
-
+We shall provide a general analysis across multiple fragments, but before we do that it is useful to illustrate the techniques in the simplest fragment first.
 The unital fragment encompasses the circuits which preserve the maximally mixed state ($\id/d$) and so it includes many important families of circuits.
@@
     \centering
-    \includegraphics[scale=0.5]{figs/distill_bounds.pdf}
+    \includegraphics[scale=0.45]{figs/distill_bounds.pdf}
     \caption{\textbf{Distillation bounds in the unital fragment.} Distillation bounds obtained by majorisation, mana and the line $1-\epsilon$ (tightest bound of max--thauma) are plotted for $\epsilon' = 0$, up to noise level $\epsilon = 3/7$.
@@
     \includegraphics[scale=0.55]{figs/rate_scatter.pdf}
-    \caption{\textbf{Bounds on magic distillation rates $R(\epsilon, \beta)$ within stabiliser fragments.}
+    \caption{\textbf{Bounds on magic distillation rates $R(\epsilon, \beta)$ within arbitrary stabiliser fragments.}
     The vertical dashed line is the `Landauer-like' temperature threshold $\beta_\star$ and the diagonal dashed curve corresponds to the noise threshold $\epsilon_\star (\beta)$ at every $\beta \leq \beta_\star$.
@@
 \begin{theorem}\label{thm:stab_bounds}
-	Let $\sigma$ be a qutrit stabiliser state, given by $\sigma = \frac{1}{\Z} e^{-\beta H}$ with $H$ having eigenvalues $E_0 \le E_1 \le E_2$, and where $\beta$ is an (effective) inverse temperature for the state.
-We define
-\begin{equation}
-	\beta_\star \coloneqq \frac{1}{E_2 - E_0} \ln{2}
-\end{equation}
-and for $\beta \leq \beta_\star$, we define a threshold noise level
+	Let $\sigma$ be any qutrit stabiliser state, and write the state as $\sigma = \frac{1}{\Z} e^{-\beta H}$ with $H$ having eigenvalues $E_0 \le E_1 \le E_2$, and where $\beta$ is an effective inverse temperature for the state.
+We define $\beta_\star = (1/kT_\star)$ through the relation
+\begin{equation}
+	E_2 - E_0 =: kT_\star \ln{2}
+\end{equation}
+and for $\beta \leq \beta_\star$, and define a threshold noise level
 \begin{equation}
@@
 \end{equation}
+In the above expressions $F_\beta$ is the effective free energy of the stabilizer state.
 \end{theorem}
@@
 where $\{\ket{\varphi_k}\}$ are pure, orthonormal stabiliser states.
-Therefore, there exists a Clifford operation that maps $\sigma$ to $\gamma_\beta$, where 
-\begin{equation}
-\gamma_\beta = \frac{e^{-\beta E_0}}{\Z_\beta} \ketbra{0} + \frac{e^{-\beta E_1}}{\Z_\beta} \ketbra{1} + \frac{e^{-\beta E_2}}{\Z_\beta} \ketbra{2}.
-\end{equation}
-\nick{Prove this carefully}
-
-This Clifford operation permutes the Hamiltonian eigenvalues on the phase space, so that the negative component $-v$ of $\rho_S(\epsilon)$ can lie on the same point on the phase space as any of the eigenvalues.
+These pure states can be represented in terms of Generalized Paulis.
+Let $C$ be the unitary transforming each $|\varphi_k\>\<\varphi_k|$ to $|k\>\<k|$.
+Since the Clifford group is the normalizer of the Heisenberg-Weyl group this implies that $C$ must be a Clifford unitary.
+Therefore, $C$ maps $\sigma$ to $\gamma_\beta$, where
+\begin{equation}
+\gamma_\beta = \frac{e^{-\beta E_0}}{\Z_\beta} \ketbra{0} + \frac{e^{-\beta E_1}}{\Z_\beta} \ketbra{1} + \frac{e^{-\beta E_2}}{\Z_\beta} \ketbra{2},
+\end{equation}
+is a stabilizer state, diagonal in the computational basis.
+The Clifford operation permutes the Hamiltonian eigenvalues on the phase space, so that the negative component $-v$ of $\rho_S(\epsilon)$ can lie on the same point on the phase space as any of the eigenvalues.
 For this reason, we impose no order between the eigenvalues, but simply choose $E_0$ as the eigenvalue that is associated with the state negativity and denote the highest energy by $E_{\rm{max}} \coloneqq \max{\{E_0, E_1, E_2\}}$.
@@
     \centering
-    \includegraphics[scale=0.5]{figs/pd_split_thermal.pdf}
+    \includegraphics[scale=0.45]{figs/pd_split_thermal.pdf}
     \caption{\textbf{Qutrit phase space regions with different rescaled values.}

### 2021-03-28 magic_paper.tex
Discussion of fragment as projection of pre-order. Majorization introduced and discussed.

@@
 However, it is known that all positively represented states used in Clifford circuits admit an efficient classical description, and therefore it is natural to consider focus on describing those negatively represented magic states.
-The free states in any magic theory therefore lie in the set
+The free states in any magic theory must therefore lie in the set
 \begin{equation}
@@
 
+We can now show that each magic fragment admits constraints that do not take the form of state monotones. The development of any monotone $\M(\rho)$ for a magic theory $\R$ can be viewed abstractly as
+\begin{equation}
+\M : \mbox{(pre-order of states)} \longrightarrow \mbox{(total order of numerical values).} \nonumber
+\end{equation}
+More precisely, within the theory we order magic states as $\rho_1 \succ \rho_2$ whenever there is an operation $\E \in \O$ such that $\E(\rho_1) = \rho_2$.
+However, in general many states will not be interconvertible in either direction, and so this ordering is a pre-order in the sense that incomparable states exist.
+A magic monotone projects this pre-order of states onto the number line, and so through this lens any two states are directly comparable in terms of the values of $\M(\rho_1)$ and $\M(\rho_2)$.
+Of course, the price is that the monotone provides only a necessary, but not sufficient, condition for the transformation $\rho_1 \rightarrow \rho_2$.
+
+The restriction of a magic theory $\R$ to some fragment $\R_\sigma$ can now be interpreted as a generalisation of the magic monotone construction: instead of mapping the pre-order of states in $\R$ onto the number line, we instead map this pre-order onto \emph{a simpler pre-order of states.} Therefore, we are retaining more of the original parent theory, while working in a scenario that admits greater structure and simplicity.
+We can view this as a mapping $\P_\sigma: \R \rightarrow \R_\sigma$ that restricts to a sub-theory (a $\sigma$--fragment) of the parent theory $\R$.
+Thus,
+\begin{equation}
+\P_\sigma: \mbox{(pre-order)} \longrightarrow \mbox{(simpler pre-order).}
+\end{equation}
+By framing the projection onto a fragment in this light, we can view Theorem \ref{thm:frag} as a statement that the collection $\{\P_\sigma\}$ provides a complete set of generalized monotones for the theory.
+
+The question is now whether the sub-theories can be analysed to provide additional insights into magic distillation protocols.
+We shall do this by working in the Wigner representation of a given $\sigma$--fragment.
+The problem of magic state distillation then becomes that of processing negativity under stochastic maps $W_{\E}( \y |\x)$ that leave a particular quasi-distribution $W_\sigma(\x)$ invariant.
+However $\sigma \in \F$ is is positively represented and so the sub-theory has an invariant classical probability distribution as a fixed point.
+This structure allows us to make use of a range of classical tools, and in particular majorization theory.
+
 Majorisation~\cite{cit:marshall} is a collection of powerful tools that has recently found many applications in quantum information theory~\cite{Nielsen_1999, cit:cwiklinski, cit:lostaglio2, cit:gour, cit:gour2, Horodecki_2003, Vallejos_2021}.
 It describes the disorder of distributions that undergo stochastic transformations.
-
-To formally state majorisation results, we first denote by $\stoch$ the set of $(d \times d)$ stochastic matrices that preserve the probability vector $\bmd$.
-Specifically, for any \emph{$\bmd$--stochastic matrix} $S \in \stoch$, all matrix elements are non-negative, all rows sum to $1$ and $S\bmd = \bmd$.
-The set $\stoch$ forms a group under matrix multiplication for any $\bmd$ with positive components.
-
-Majorisation describes quantum thermodynamics exactly in the absence of quantum coherence.
-The use of majorisation in this setting provides vital intuition for our purposes.
-At any given temperature $\beta^{-1}$, the thermal state $\gamma_\beta$ is thermodynamically the most disordered state. 
-Thermal operations are defined as operations that cannot extract energy from the Gibbs state, $\E(\gamma_\beta) = \gamma_\beta$.
-Convertibility between states via thermal operations is equivalent to a stochasticity condition on the energy level populations of the states~\cite{cit:lostaglio}.
-Informally, there exists a thermal operation $\E$ such that $\tau = \E(\rho)$ if and only if there exists a matrix $S \in \stoch$ such that $\bm{q} = S\bm{p}$, where $\bm{q}, \bm{p}$ and $\bmd$ and the energy level population vectors of $\tau, \rho, \gamma_\beta$ respectively.
-
-Based on this setting, we define $\bmd$--majorisation as follows.
-\begin{definition}[\textbf{$\boldsymbol\bmd$--majorisation}]\label{def:dmajor}
-    Given $\bmx, \bmy, \bmd \in \reals^d$, such that the components of $\bmd$ are positive, $\bmy$ is said to $\bmd$--majorise $\bmx$, iff there exists a $\bmd$--stochastic matrix $S$ such that $\bmx = S\bmy$.
-\end{definition}
-We denote this pre-order by $\bmx \prec_{\bmd} \bmy$.
-If $\bmd = \frac{1}{d}\bm{1}$, the $d$--dimensional uniform distribution, then $\stoch$ is the set of doubly stochastic matrices and we retrieve the familiar notion of majorisation from entanglement theory~\cite{Nielsen_1999}.
-
+In its simplest form it defines a pre-order on probability distributions.
+Given two distributions $\p= (p_1, \dots, p_n)$ and $\q = (q_1, \dots, q_n)$ over $n$ outcomes, we say that $\p$ majorises $\q$, denoted $\p \succ \q$, if there is a bistochastic map $A=(A_{ij})$ such that $A\p = \q$.
+Here, bistochastic means that $\sum_i A_{ij} = \sum_j A_{ij} = 1$.
+A well known result tells us that the condition $ \p \succ \q$ over probability distributions is equivalent to $n-1$ inequalities, and these conditions are easily checked.
+
+However, there is a natural generalisation of this, called \emph{relative majorization} (also known as $d$--majorization, or in the context of thermodynamics, thermo-majorization) that dates back to the 1950s.
+For a fixed probability distribution $\r = (r_1, \dots, r_n)$ we define majorization relative to $\r$ as follows:
+\begin{equation}
+\p \succ_{\r} \q,
+\end{equation}
+if and only if there exists a stochastic map $A$ such that $A\r = \r$ and $A \p = \q$.
+In order words, the relative majorization pre-order coincides with the image of $\p$ under stochastic maps that have $\r$ as a fixed point.
+It is readily checked that the original majorization condition between probability distributions corresponds to the case $\r = (1/n, \dots, 1/n)$.
+The pre-order that results from relative majorization is also easily checked and again corresponds to checking a small number of inequalities.
+
+However, it turns out that relative majorization is equally applicable to \emph{quasi-probability} distributions, and therefore can be applied to the Wigner representation of a given fragment.
+To our knowledge, this application of majorization to quasi-distributions in  physics has not been considered previously.
+The caveat here is that relative majorization ranges over all stochastic maps with a given fixed point, while in the case of the Wigner representation there is an additional restriction that the symplectic structure is respected.
+This implies that any relative majorization conditions provide necessary, but not sufficient, conditions on magic state interconversions in the fragment.
+However, this observation raises a question that to our knowledge has not been previously considered in the classical statistical mechanics literature: what are the conditions for symplectic majorization of classical statistical mechanics?
+We shall return to this question later on when we discuss how our approach could be used to construct concrete lower-bounds on distillation rates.
+
+\subsection{The relative majorization conditions on magic interconversion within a fragment}
 The pre-order imposed by $\bmd$--majorisation admits a numerically efficient reformulation in terms of Lorenz curves.

### 2021-03-28 magic_paper.tex
Clean-up / Comments in Sec.III

--- 2021-03-27 magic_paper.tex
@@
 
-Central to our construction is the representation of any quantum state or quantum operation on a system of dimension $d$ in terms of quasi-probability representations on a discrete phase space \ddd{[CITE the review on quasi-reps-- I think Chris Ferrie has one that is good.]}\nick{which one?}.
+Central to our construction is the representation of any quantum state or quantum operation on a system of dimension $d$ in terms of quasi-probability representations on a discrete phase space~\cite{Ferrie_2008}.
 This construction is a discrete version of Wigner representations in quantum optics.
@@
 
-\nick{There are repetitions with text in introduction, this sections looks more introduction-like I think ?}\ddd{We'll organise things later - better to get key chunks down first.}
-
 The state-injection model for quantum computation~\cite{cit:bravyi} is a key avenue to realising a full-scale, fault-tolerant quantum computer.
@@
 
-A range of monotones have been developed in the literature\cite{cit:howard, Wang_2020, Seddon_2021} and each provides a means to upper bound distillation rates within a particular theory of magic.
+A range of monotones have been developed in the literature~\cite{cit:howard, Wang_2020, Seddon_2021} \nick{Actually I think they are not that many for qudits: Mana, Robustness, Wang's entropic measures} and each provides a means to upper bound distillation rates within a particular theory of magic.
 In this work we shall consider a broad framework for magic, with conditions that any theory of magic should satisfy.
@@
 Stabilizer operations are the most natural set of operations as they admit a classically efficient description for uniform quantum circuits.
-However, other choices of operations have been considered in the literature \ddd{[CITE]}.
-Common to these theories is that free $\E$  is such that $id \otimes \E (\rho)$ has a positive Wigner distribution whenever $ \rho$ has a positive Wigner distribution.
-Therefore the condition that $\E$ does not generate Wigner negativity is an essential requirement of any magic theory.
+However, other choices of operations have been considered in the literature~\cite{cit:ahmadi, cit:seddon, Wang_2019}.
+Common to these theories is that free $\E$  is such that $(\id \otimes \E) (\rho)$ has a positive Wigner distribution whenever $ \rho$ has a positive Wigner distribution.
+\nick{This is not true for stabilizer-preserving operations~\cite{cit:ahmadi}, since ``completely'' stabilizer-preserving operations~\cite{cit:seddon} is a strict subset} Therefore, the condition that $\E$ does not generate Wigner negativity is an essential requirement of any magic theory.
 
@@
 In what follows we shall therefore assume that we have a magic theory $\R = (\F, \O)$ in which the free states $\F$ form a closed, convex set with each state represented by a positive Wigner function, while the free operations $\O$ are represented by stochastic maps acting on the discrete phase space.
+\nick{Should we justify closedness, i.e.
+we require state positivity and Wigner-positivity both of which are closed linear constraints.
+I think we don't require convexity, we just need boundedness which trivially holds for quantum states}
 
@@
 These are not a priori encoded in the formulation of the magic theory, and constitute additional physical conditions on top of the underlying resource-theoretic accounting.
-For example, there may be non-trivial thermal noise in the physical set-up or the accessible operations, there might be strong bias in the noise present, or we might be limited in how easily certain gates can be realised.
-\ddd{[find roughly related cites for these?]}
-
-While we will not consider very model-specific limitations, we still want to inject in some physical constraints.
+For example, there may be non-trivial thermal noise in the physical set-up or the accessible operations, there might be strong bias in the noise present, or we might be limited in how easily certain gates can be realised.~\cite{Litinski_2019, Babbush_2018, Fowler_2019, Li_2015}.
+\nick{good enough?
+- struggled to find better refs}
+
+Our formulation will not consider model-specific limitations, but will still inject broad physical constraints.
 We proceed by considering imposing equilibrium, or fixed-point, restrictions on the actual operations that are accessible to us.
-While such restrictions could be viewed as the existence of some non-trivial thermodynamic constraint, it could equally be viewed as encoding a high noise-bias or difficulty in realising a particular quantum gate.
+While such restrictions could be viewed as the existence of some non-trivial thermodynamic constraint, they could equally be viewed as encoding a high noise-bias or difficulty in realising a particular quantum gate.
 We can therefore define the following sub-theory of any magic theory $\R$.
@@
 This notion provides a simple way to break up any theory into smaller, more manageable parts that are destinguished by additional physical constraints.
-Moreover, the union over all fragments returns the parent theory, and so we are not discarding any information about the theory by breaking it up in this way.
-This can be made precise as follows.
+Moreover, the union over all fragments returns the parent theory, so we are not discarding any information by breaking up the theory in this way.
+We make this statement precise as follows.
 \begin{theorem}\label{thm:frag}
@@
 \end{theorem}
-The proof of this is very straightforward.
+The proof of this is straightforward.
 \begin{proof}
@@
 
-This implies that we can now consider magic distillation rates within a particular $\sigma$--fragment and then see how the bounds on the distillation rates depend on the particular fragment we work within.
+We can now consider magic distillation rates within a particular $\sigma$--fragment and then see how the bounds on the distillation rates depend on the particular fragment we work within.
 Therefore, this route can potentially shed light on how the physics of a protocol constrain distillation rates above and beyond global constraints from the parent resource theory.
@@
 Do isotropic maps have better bounds, or does bias towards a pure stabilizer state fixed point provide more freedom?
+\nick{We probably want to provide clear answers to these later on}
 
@@
 
-More importantly, by adding in this additional structure to the magic theory, it actually allows us to say more than would be possible at the level of the full parent theory.
+More importantly, by introducing this additional structure to a magic theory, it actually allows for deeper analysis than would be possible at the level of the full parent theory.
 In particular, the interconversion structure in each fragment can be analysed using tools from single-shot thermodynamics and majorization theory as we discuss in the next section.
@@
 This process destroys the circuit symmetries, except for the invariance of the maximally mixed state.
-Dephasing and bit-flip error channels are examples of the many error-inducing channels that respect the unital symmetry. \nick{Expand on significance of unital fragment}
+Dephasing and bit-flip error channels are examples of the many error-inducing channels that respect the unital symmetry.
+\nick{Expand on significance of unital fragment / Include example of depolarising channel earlier as demonstration of our ``pinpointing harware limitations''-approach}
 \null\\

### 2021-03-29 magic_paper.tex
Section on Lorenz curves for quasi-probs. More to follow today.

@@
 
-A range of monotones have been developed in the literature~\cite{cit:howard, Wang_2020, Seddon_2021} \nick{Actually I think they are not that many for qudits: Mana, Robustness, Wang's entropic measures} and each provides a means to upper bound distillation rates within a particular theory of magic.
+A range of monotones have been developed in the literature~\cite{cit:howard, Wang_2020, Seddon_2021} \nick{Actually I think they are not that many for qudits: Mana, Robustness, Wang's entropic measures}\ddd{[Then we kick ass, and give exponentially many new ones.]} and each provides a means to upper bound distillation rates within a particular theory of magic.
 In this work we shall consider a broad framework for magic, with conditions that any theory of magic should satisfy.
@@
 we require state positivity and Wigner-positivity both of which are closed linear constraints.
-I think we don't require convexity, we just need boundedness which trivially holds for quantum states}
+I think we don't require convexity, we just need boundedness which trivially holds for quantum states}\ddd{[Fine print.
+No issue.]}
 
@@
 For example, there may be non-trivial thermal noise in the physical set-up or the accessible operations, there might be strong bias in the noise present, or we might be limited in how easily certain gates can be realised.~\cite{Litinski_2019, Babbush_2018, Fowler_2019, Li_2015}.
-\nick{good enough?
-- struggled to find better refs}
 
@@
 \begin{equation}
-\M : \mbox{(pre-order of states)} \longrightarrow \mbox{(total order of numerical values).} \nonumber
+\M : \mbox{(pre-order of states)} \mapsto \mbox{(total order of numerical values).} \nonumber
 \end{equation}
@@
 
-\subsection{The relative majorization conditions on magic interconversion within a fragment}
-The pre-order imposed by $\bmd$--majorisation admits a numerically efficient reformulation in terms of Lorenz curves.
-Let the vector $\bmu^\downarrow$ denote the vector $\bmu \in \reals^d$ with its components arranged in non-increasing order.
-\begin{definition}[\textbf{Lorenz curve}]\label{def:lc}
-    Let $\bmw, \bmd \in \reals^d$, where the components of $\bmd$ are positive with $D = \sum_{i=1}^d d_i$ and denote by $\widetilde{\bmw} \coloneqq (w_1/d_1, \dots, w_d/\nick{d_d})^T$ the rescaled vector $\bmw$ by $\bmd$.
-
-    Finally, denote by $\pi: \mathbb{Z}_d \mapsto \mathbb{Z}_d$ the permutation that sorts $\widetilde{\bmw}$, $(\widetilde{\bmw}^\downarrow)_i = w_{\pi(i)}$ for all $i=1,\dots,d$.
-
-    Consider the piecewise linear curve obtained by joining the points $\{(0,0)\} \cup \{ (x_k, \lc{\bmw}{\bmd}(k)) \}_{k=1,\dots,d}$, where
+\subsection{Quasi-probability majorization and non-monotonic Lorenz curves}
+
+We now turn to the application of majorization to describing magic in different fragments.
+The simplest way to express the conditions for interconversion is through Lorenz curves, which we now describe.
+
+Given a vector $\x$ we define $\x^\downarrow$ to be the re-arrangement of the components of $\x$ into decreasing order.
+Now, given two $n$--component vectors $\w$ and $\r$ we define the \emph{Lorenz curve} of $\w$ relative to $\r$, denoted $L_{\w|\r}(x)$, as the piece-wise linear function that passes through $(0,0)$ and the $n$ points
 \begin{equation}\label{eq:lorenz}
-        (x_k, \lc{\bmw}{\bmd}(k)) \coloneqq \left( \frac{1}{D}\sum_{i=1}^k d_{\pi(i)}, \sum_{i=1}^k w_{\pi(i)} \right).
-    \end{equation}
-    We define the set of points on this curve, $\lc{\bmw}{\bmd}(x),\ x \in [0,1]$, as the \emph{Lorenz curve} of vector $\bmw$ with respect to $\bmd$.
-\end{definition}
-Components $x_k$ are rescaled by $D$ so that comparison of curves with unequal dimensions is possible.
-In fact, the Lorenz curves $\lc{\bmw}{\bmd}$ and $\lc{\bmw \otimes \bmd}{\bmd \otimes \bmd}$, where $\otimes$ denotes the Kronecker product, coincide.
-Furthermore, a Lorenz curve $\lc{\bmw}{\bmd}(x)$ is always concave in $x$, since it consists of $d$ line segments each with slope $(\widetilde{\bmw}^\downarrow)_i$ for $i=1,\dots,d$ which by definition is a non-increasing sequence.
-Finally, the points on the interior of the Lorenz curve that connect line segments of different slopes are in general non-differentiable and we call them\emph{elbows}.
-
-A vector $\bmy$ is said to \emph{$\bmd$--majorise} another vector $\bmx$ if and only if the Lorenz curve $\lc{\bmy}{\bmd}$ lies above Lorenz curve $\lc{\bmx}{\bmd}$, thus reducing $\bmd$--majorisation into a finite set of inequalities.
-\begin{theorem}\label{thm:dmajor}
-    Let $\bmx, \bmy, \bmd \in \reals^d$, such that the components of $\bmd$ are positive. 
-    Then, $\bmx \prec_{\bmd} \bmy$ if and only if $\lc{\bmx}{\bmd}(x) \leq \lc{\bmy}{\bmd}(x)$ for all $x \in [0,1]$ with strict equality at $x=1$.
-\end{theorem}
-A restatement of the theorem including more equivalent conditions and a proof are provided in~\cref{app:major}.
-
-\subsection{Majorisation of quasi-probabilities in $\sigma$--fragments}\label{sec:major_frag}
+        (x_k,L_{\w|\r}(x_k)) =\left( \frac{1}{R}\sum_{i=1}^k r_{\pi(i)}, \sum_{i=1}^k w_{\pi(i)} \right),
+\end{equation}
+where $R:= \sum_{i=1}^n r_i$, and $\pi$ is the permutation on $n$ objects that sends $\tilde{\w}$ to $\tilde{\w}^{\downarrow}$, where $\tilde{w}_i := w_i/r_i$ is the vector of component-wise ratios of $\w$ and $\r$.
+The form of this requires that $\r$ has no zero components, which we shall assume without loss of generality as in any physical situation the rank of a quantum state is not an operationally meaningful quantity.
+
+If $\w$ and $\r$ are both probability distributions then the Lorenz curve is defined on the interval $[0,1]$, and rises monotonically until it reaches the value $1$ at $x=1$.
+The value $L_{\w|\r}(x) = 1$ is a global upper bound to the function, only attained at the end-point $x=1$.
+However, if $\w$ is a \emph{quasi-probability} distribution with negative values, and $\r$ a regular probability distribution things are different.
+Now the Lorenz curve is no longer monotone increasing, but is a concave function that breaks through the $L_{\w|\r}(x) = 1$ barrier at an interior point and attains some non-trivial maximum $L_\star$ above the value $1$, before decreasing monotonically to $L_{\w|\r}(x)= 1$ at the end-point $x=1$.
+See Figure \ref{fig:lcs} for examples of non-monotonic Lorenz curves for quasi-distributions.
+For quasi-distributions within quantum theory, the breaking of this barrier is associated with the degree of non-classicality.
+Since majorization provides a measure of order/disorder this is consistent with the intuition that negativity, for example within the context of entanglement theory or quantum computing, can provide a greater form of order than is possible within classical theory.
+
+\begin{figure}
+    \centering
+    \includegraphics[height=4.5cm]{figs/lc_strange.pdf}
+    \caption{\textbf{A `heretical' family of Lorenz curves.} Traditionally, Lorenz curves for distributions are monotone increasing cumulant functions that reach a maximum value of $1$.
+In contrast, Lorenz curves for magic states break through the value of $L(x)=1$ due to the presence of negativity in the associated quasi-probability distributions.
+The above family of curves correspond to multiple copies of noisy Strange states $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ for $n=1,2,3,4$ within a particular stabilizer fragment.
+Solid lines represent pure Strange states, while dashed lines represent noisy Strange states with depolarising noise $\epsilon = 0.1$.
+    }
+    \label{fig:lcs}
+\end{figure}
+
+Given the definition of Lorenz curves, the condition for relative majorization can now be compactly phrased.
+We have that $\w_1 \succ_{\r} \w_2$ if and only if $L_{\w_1 | \r} (x) \ge L_{\w_2 | \r}(x)$ for all $x \in [0,1]$.
+In other words, the Lorenz curve of $\w_1$ relative to $\r$ is never below the Lorenz curve of $\w_2$ relative to $\r$.
+Phrased more abstractly, the relative majorization pre-order corresponds to the standard ordering of concave, piece-wise linear functions passing through $(0,0)$ and $(1,1)$.
+Another neat geometric formulation of relative majorization exists that simply states that the $L_1$-norm angle between $\w_1$ and $\r$ is greater than or equal to the $L_1$-norm angle between $\w_2$ and $\r$ (see \ddd{[CITE]} for details).
+
+\subsection{Majorisation of negative Wigner distributions within $\sigma$--fragments}\label{sec:major_frag}
 
@@
 the $\sigma$--fragment defined by the maximally mixed state $\sigma = \frac{1}{d}\id$ whose Wigner distribution is the uniform probability distribution.
-
-\begin{figure}
-    \centering
-    \includegraphics[height=4.5cm]{figs/lc_strange.pdf}
-    \caption{\textbf{A `heretical' family of Lorenz curves.} Traditionally, Lorenz curves are monotone increasing cumulant functions that reach a maximum value of $1$.
-In contrast, Lorenz curves for magic states break through the value of $L(x)=1$ due to the presence of negativity in the associated quasi-probability distributions.
-The above family of curves correspond to multiple copies of noisy Strange states $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ for $n=1,2,3,4$ within a particular stabilizer fragment.
-Solid lines represent pure Strange states, while dashed lines represent noisy Strange states with depolarising noise $\epsilon = 0.1$.
-    }
-    \label{fig:lcs}
-\end{figure}
 

### 2021-03-29 magic_paper.tex
Rough version of Section III finalised. Still needs polish though.

@@
 
-We can approach any magic theory through a thermodynamic lens, and in doing so we are provided with valuable insights on the structure of the theory. 
-Firstly, any free state, for example a stabiliser state, can be viewed as a thermal state $\gamma_\beta$.
-Without loss of generality we can always write a quantum state $\sigma$ as a thermal state, $\sigma = \gamma_\beta \coloneqq \frac{1}{\Z_\beta} e^{-\beta H}$ for some $\beta \geq 0$ and Hamiltonian $H$ (either effective or actual)\footnote{Technicalities arise for the case where $\sigma$ is not full rank, but this can be still described via $ \beta \rightarrow 0$ limiting process.}.
-We can also view the set of free operations $\O_\sigma$ as a counterpart of thermal operations, in the sense that any operation $\E$ in $\O_\sigma$ preserves state $\sigma$.
-
-It is then apparent that the pre-order $\prec_{\R_\sigma}$ between the operations in the $\sigma$--fragment follows the rules of $\bmd$--majorisation as outlined in~\cref{sec:major}.
-In particular, the pre-order $\prec_{\R_\sigma}$ of the $\sigma$--fragment $\R_\sigma = (\F, \O_\sigma)$ between $d$--dimensional states corresponds to the majorisation pre-order $\prec_{\W{\sigma}}$ between their $d^2$--dimensional Wigner distributions.
-For simplicity we shall merge the notation into $\prec_\sigma$, as there is little risk of confusion.
-
-Note that the Wigner components of an $n$--copy state $\rho^{\otimes n}$ can be calculated directly from $\W{\rho}$ by convolution of the distribution with itself,
-\begin{equation}
-	\W{\rho^{\otimes n}} = \W{\rho}^{\otimes n},
-\end{equation}
-where $\otimes$ can be interpreted as the usual Kronecker product in the last expression.
-We may use the vector notation $\bmw(\rho) = (w(\rho)_i)_{i=1,\dots,d^2}$ for the Wigner distribution, in which case we can express the Kronecker product as
-\begin{equation}
-	\W{\rho} \otimes \W{\rho} = (w(\rho)_i w(\rho)_j)_{i,j=1,\dots,d^2}.
-\end{equation}
-The correspondence between the phase space and pure vector representations of the Wigner distribution is discussed more in~\cref{app:cmpairs}.
-The vector notation will be useful in the proof of our main result,~\cref{thm:stab_bounds}
-
-Furthermore, we restrict our analysis to $\sigma$--fragments, where $\sigma$ is full-rank.
-This is justified as majorisation is continuous between fragments, in the sense that the pre-orders $\prec_\sigma$ and $\prec_{\sigma'}$ are equivalent for states $\sigma$ and $\sigma'$ which are $\epsilon$--close.
+Having described how majorization relative to a fiducial distribution can be computed, we now turn to its application within a particular fragment of a magic theory $\R= (\F, \O)$.
+
+If we consider some $\sigma \in \F$, and its corresponding fragment $\R_\sigma$, then we are typically interested in the ability to transform many copies of some magic state $\rho$ into more pure forms of magic.
+The state $\rho$ is assumed to have negativity in the Wigner representation, and so $W_\rho(\x) < 0$ for some regions of $\x \in \P_d$.
+We again note that we restrict to odd-dimensional quantum systems, for simplicity.
+In contrast the state $\sigma$ will have a Wigner distribution $W_\sigma(\x)$ that forms a genuine probability distribution.
+On the technical assumption that $\sigma$ is full rank, then we also have that $W_\sigma(\x)$ is non-negative on the discrete phase space $\P_d$.
+Any non-full rank states can be handled as a limiting case in which we mix in a small fraction $\epsilon (\I/d)$ to the quantum state $\sigma$, and later take $\epsilon$ tending to zero.
+
+As discussed already, the free operations within the magic theory $\R$ are represented by stochastic maps, and within $\R_\sigma$ by stochastic maps that leave $W_\sigma(\x)$ invariant.
+Therefore a necessary condition for magic state transformations $\rho_1 \rightarrow \rho_2$ within $\R_\sigma$ will be that
+\begin{equation}
+W_{\rho_1} \succ_{W_{\sigma}} W_{\rho_2},
+\end{equation}
+or put another way, relative to $W_\sigma$ the quasi-distribution $W_{\rho_1}$ is more ordered than the quasi-distribution $W_{\rho_2}$.
+
+This in turn can be expressed in terms of Lorenz curves. To simplify notation we denote by $L_{\rho | \sigma}(x)$ the Lorenz curve $L_{W_{\rho} | W_{\sigma}} (x)$. We therefore have that
+\begin{equation}
+\rho_1 \rightarrow \rho_2 \mbox{ within }\R_\sigma \mbox{ implies that } L_{\rho_1 |\sigma} (x) \ge L_{\rho_2 |\sigma} (x),
+\end{equation}
+for all $x \in [0,1]$.
+Therefore, the constraint in terms of the Lorenz curves for the magic states can be used to impose upper bounds on magic distillation rates.
+Note however, that this is not a single numerical constraint, but is a \emph{family} of constraints.
+Indeed for $n$ copies of a $d$ dimensional system the number of terms in $W_{\rho}$ is $d^{2n}$ and so the Lorenz curve condition corresponds to \emph{exponentially} many constraints.
+
+%We can approach any magic theory through a thermodynamic lens, and in doing so we are provided with valuable insights on the structure of the theory. 
+%Firstly, any free state, for example a stabiliser state, can be viewed as a thermal state $\gamma_\beta$.
+%Without loss of generality we can always write a quantum state $\sigma$ as a thermal state, $\sigma = \gamma_\beta \coloneqq \frac{1}{\Z_\beta} e^{-\beta H}$ for some $\beta \geq 0$ and Hamiltonian $H$ (either effective or actual)\footnote{Technicalities arise for the case where $\sigma$ is not full rank, but this can be still described via $ \beta \rightarrow 0$ limiting process.}.
+%We can also view the set of free operations $\O_\sigma$ as a counterpart of thermal operations, in the sense that any operation $\E$ in $\O_\sigma$ preserves state $\sigma$. 
+%
+%It is then apparent that the pre-order $\prec_{\R_\sigma}$ between the operations in the $\sigma$--fragment follows the rules of $\bmd$--majorisation as outlined in~\cref{sec:major}.
+%In particular, the pre-order $\prec_{\R_\sigma}$ of the $\sigma$--fragment $\R_\sigma = (\F, \O_\sigma)$ between $d$--dimensional states corresponds to the majorisation pre-order $\prec_{\W{\sigma}}$ between their $d^2$--dimensional Wigner distributions.
+%For simplicity we shall merge the notation into $\prec_\sigma$, as there is little risk of confusion.
+%
+%Note that the Wigner components of an $n$--copy state $\rho^{\otimes n}$ can be calculated directly from $\W{\rho}$ by convolution of the distribution with itself,
+%\begin{equation}
+%	\W{\rho^{\otimes n}} = \W{\rho}^{\otimes n},
+%\end{equation}
+%where $\otimes$ can be interpreted as the usual Kronecker product in the last expression.
+%We may use the vector notation $\bmw(\rho) = (w(\rho)_i)_{i=1,\dots,d^2}$ for the Wigner distribution, in which case we can express the Kronecker product as
+%\begin{equation}
+%	\W{\rho} \otimes \W{\rho} = (w(\rho)_i w(\rho)_j)_{i,j=1,\dots,d^2}.
+%\end{equation}
+%The correspondence between the phase space and pure vector representations of the Wigner distribution is discussed more in~\cref{app:cmpairs}.
+%The vector notation will be useful in the proof of our main result,~\cref{thm:stab_bounds}
+%
+%Furthermore, we restrict our analysis to $\sigma$--fragments, where $\sigma$ is full-rank.
+%This is justified as majorisation is continuous between fragments, in the sense that the pre-orders $\prec_\sigma$ and $\prec_{\sigma'}$ are equivalent for states $\sigma$ and $\sigma'$ which are $\epsilon$--close.
 \nick{CHECK}
-Therefore, majorisation analysis is robust under imperfections in the experimental implementation of quantum operations.
-
-In particular, we can always use common noise effects to approximate any $\sigma$--fragment where $\sigma$ is not full-rank by the $\sigma'$--fragment where $\sigma'$ is a noisy approximation of $\sigma$.
-For example, inducing depolarising noise, we can write $\sigma' = (1-\epsilon)\sigma + \epsilon\frac{1}{d}\id$, for some infinitesimal $\epsilon > 0$, so that $\sigma'$ is full-rank and arbitrarily close to $\sigma$.
-Important examples of such $\sigma$--fragments include pure stabiliser states which are rank-$1$, e.g. the zero state depicted in~\cref{fig:zero}. 
-Operations in such fragments include important stabiliser operations like the replacement channel, $\E(\rho) = \sigma$ for all states $\rho$.
-
-\begin{theorem}\label{thm:sigmamajor}
-    Let $\R = (\F, \O)$ be a theory of magic. If $\rho \longrightarrow \tau$  in $\R$ then  $\W{\tau} \prec_\sigma \W{\rho}$ within at least one $\sigma$--fragment.
-\end{theorem}
-\begin{proof}
-Suppose we can convert $\rho$ into $\tau$ in the magic theory. 
-Thus there is some $\O_\sigma$ and some $\E \in \O_\sigma$ such that $\E(\rho) = \tau$, and $\E(\sigma)=\sigma$. 
-Therefore, the Wigner distribution of this free operation satisfies $\W{\E} \in \stochw$ and $\W{\E}\W{\rho} = \W{\tau}$. 
-Since $\sigma$ is full-rank and free, its Wigner distribution is strictly positive in all components, so it directly follows from~\cref{def:dmajor} that $\W{\tau} \prec_{\sigma} \W{\rho}$.
-\end{proof}
-The converse is in general not true, since stochastic matrices do not necessarily correspond to valid quantum operations.
-
-The result of~\cref{thm:sigmamajor} can be understood as an extension of the idea of a magic monotone, where we replace $\M(\tau) \leq \M(\rho)$ with $\W{\tau} \prec_\sigma \W{\rho}$. 
-The physical difference between the two expressions is that the majorisation ordering occurs in a specific $\sigma$--fragment.
-Therefore, majorisation constraints can be used to place upper bounds on magic state distillation in a way that allows one to incorporate the physics of the allowed operations -- specifically, it enables us to bound how much magic can be distilled via quantum operations that, for example, preserve the equilibrium state of the system, or via operations that are symmetric about the $Z$-axis of the Bloch sphere.
-We discuss distillation upper bounds in detail in~\cref{sec:unital,sec:stab}
-
-This approach can also provide \emph{lower bounds} on distillation, however now more structure about the specific free operations must be included. 
-We briefly discuss distillation lower bounds in~\cref{sec:lower_bounds}.
-
-\subsection{Lorenz curves of quasi-probabilities in $\sigma$--fragments}
+%Therefore, majorisation analysis is robust under imperfections in the experimental implementation of quantum operations.
+%
+%In particular, we can always use common noise effects to approximate any $\sigma$--fragment where $\sigma$ is not full-rank by the $\sigma'$--fragment where $\sigma'$ is a noisy approximation of $\sigma$.
+%For example, inducing depolarising noise, we can write $\sigma' = (1-\epsilon)\sigma + \epsilon\frac{1}{d}\id$, for some infinitesimal $\epsilon > 0$, so that $\sigma'$ is full-rank and arbitrarily close to $\sigma$.
+%Important examples of such $\sigma$--fragments include pure stabiliser states which are rank-$1$, e.g. the zero state depicted in~\cref{fig:zero}. 
+%Operations in such fragments include important stabiliser operations like the replacement channel, $\E(\rho) = \sigma$ for all states $\rho$.
+%
+%\begin{theorem}\label{thm:sigmamajor}
+%    Let $\R = (\F, \O)$ be a theory of magic. If $\rho \longrightarrow \tau$  in $\R$ then  $\W{\tau} \prec_\sigma \W{\rho}$ within at least one $\sigma$--fragment.
+%\end{theorem}
+%\begin{proof}
+%Suppose we can convert $\rho$ into $\tau$ in the magic theory. 
+%Thus there is some $\O_\sigma$ and some $\E \in \O_\sigma$ such that $\E(\rho) = \tau$, and $\E(\sigma)=\sigma$. 
+%Therefore, the Wigner distribution of this free operation satisfies $\W{\E} \in \stochw$ and $\W{\E}\W{\rho} = \W{\tau}$. 
+%Since $\sigma$ is full-rank and free, its Wigner distribution is strictly positive in all components, so it directly follows from~\cref{def:dmajor} that $\W{\tau} \prec_{\sigma} \W{\rho}$.
+%\end{proof}
+%The converse is in general not true, since stochastic matrices do not necessarily correspond to valid quantum operations.
+%
+%The result of~\cref{thm:sigmamajor} can be understood as an extension of the idea of a magic monotone, where we replace $\M(\tau) \leq \M(\rho)$ with $\W{\tau} \prec_\sigma \W{\rho}$. 
+%The physical difference between the two expressions is that the majorisation ordering occurs in a specific $\sigma$--fragment.
+%Therefore, majorisation constraints can be used to place upper bounds on magic state distillation in a way that allows one to incorporate the physics of the allowed operations -- specifically, it enables us to bound how much magic can be distilled via quantum operations that, for example, preserve the equilibrium state of the system, or via operations that are symmetric about the $Z$-axis of the Bloch sphere.
+%We discuss distillation upper bounds in detail in~\cref{sec:unital,sec:stab}
+
+\subsection{Basic monotones for magic states in a particular fragment}
 \label{sec:lc}
-
-It is straightforward to construct Lorenz curves for Wigner distributions in any $\sigma$--fragment.
-As we have seen in~\cref{thm:sigmamajor}, for any full-rank free state $\sigma$ we have that $\W{\sigma}$ is a strictly positive full-rank probability distribution, and so one can define a corresponding notion of $\bmd$--majorisation on \emph{quasi}--distributions.
-We write $\lc{\rho}{\sigma}(x)$ for the Lorenz curve of $\W{\rho}$ with respect to $\W{\sigma}$.
-The vector of ratios $\widetilde{\bmw}(\rho|\sigma)$ used to construct the curve is
-\begin{equation}
-	\widetilde{w}(\rho|\sigma)_i \coloneqq \frac{w(\rho)_i}{w(\sigma)_i},
-\end{equation}
-and is called the \emph{rescaled} distribution of $\rho$ with respect to $\sigma$.
-
-An example of comparison between different Lorenz curves is provided in~\cref{fig:lctoy}.
-The curves in the figure are constructed in the \emph{unital fragment}, i.e.
-the $\sigma$--fragment defined by the maximally mixed state $\sigma = \frac{1}{d}\id$ whose Wigner distribution is the uniform probability distribution.
 
@@
 
-Normalisation of the Wigner distribution ensures that for all quantum states $\rho$, $\lc{\rho}{\sigma}(x) \geq 0$ and $\lc{\rho}{\sigma}(1) = 1$.
-We stress that $0 \leq \lc{\rho}{\sigma}(x) \leq 1$ for all $x \in [0,1]$ if and only if $\rho$ is a positive Wigner state.
-As a consequence, checking whether a magic state conversion of the form
-\begin{equation}\label{eq:sigma_conv}
-	\rho \xrightarrow{\E \in \O_\sigma} \tau
-\end{equation} 
-is not possible, reduces to the set of constraints
-\begin{equation}\label{eq:majbound}
-    \lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x),\ x\in [0,1],
-\end{equation}
-due to~\cref{thm:sigmamajor,thm:dmajor}.
-
-We can refine the number of independent constraints stemming from this inequality. 
-In fact, there are only as many independent constraints as there are elbows in the Lorenz curve of the target state as shown in~\cref{thm:elbows} in~\cref{app:frag}.
-However, in principle any one location $x$ provides a valid constraint leading to some upper distillation bound, while optimising over the location would provide the strictest bound.
-In particular, we establish the \emph{first elbow constraint} which we use in~\cref{sec:unital,sec:stab} explicitly.
-\begin{lemma}
-	Consider a magic state interconversion as in~\cref{eq:sigma_conv}, where we denote by $(x_0, L_0)$ and $(x'_0, L'_0)$ the first elbow coordinates of the initial and target states respectively.
-	If $x_0 < x'_0$, then it holds that
-\begin{equation}\label{eq:first_elb_bound1}
-	\frac{L_0}{x_0} \geq \frac{L_0'}{x_0'}.
-\end{equation}
+In this section we give some generic aspects of Lorenz curves for magic states. In particular these allow us to interpret previous magic monotones in a new light.
+
+If we have a magic state $\rho$ that has negativity in its Wigner representation, then as discussed, its Lorenz curve over-shoots $1$ and reaches a non-trivial maximum $L_\star$ that depends on the particular state.
+It is easy to establish the following result.
+\begin{lemma}\label{lem:lcmax}
+	Given a magic state $\rho$, the maximum $L_\star$ of its Lorenz curve $\lc{\rho}{\sigma}(x)$ is independent of the $\sigma$--fragment and is equal to $1+\sn{\rho}$, where $\rm{sn}(\rho)$ is the sum negativity of $\rho$.
+Thus, the majorization constraint is stronger than mana in any fragment.
 \end{lemma}
 \begin{proof}
-	Consider the Lorenz curve constraint at $x = x_0$,
-\begin{equation}
-	\lc{\rho}{\sigma}(x_0) \geq \lc{\tau}{\sigma}(x_0).
-\end{equation}
-Since $x_0 < x'_0$, we can find the target state Lorenz curve coordinate $L'_\star$ at location $x = x_0$ by interpolating between the origin and the target state's first elbow, 
-\begin{equation}
-	L'_\star = \frac{x_0}{x'_0}L'_0.
-\end{equation}
-We need $L_0 \geq L_\star'$ and rearranging we get~\cref{eq:first_elb_bound1}.
-\end{proof}
-
-We can now turn the attention from the first elbow to the peak of the Lorenz curve to associate it directly with the magic monotone of mana, and equivalently the sum-negativity of a quantum state. 
-This holds independently of the particular $\sigma$--fragment one works in and as a result it becomes apparent that mana provides a weaker condition than majorisation for all magic state interconversions.
-
-We first show that the Lorenz curve maximum of state $\rho$ is independent of the $\sigma$--fragment and directly related to its sum-negativity.
-\begin{lemma}\label{lem:lcmax}
-	Given a quantum state $\rho$, the maximum of its Lorenz curve $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment and is equal to $1+\sn{\rho}$.
-\end{lemma}
-\begin{proof}
-	We may use the vector notation of the Wigner distributions $\bmw(\rho)$ and $\bmw(\sigma)$.
+	We denote the Wigner distributions of the states compactly as vectors $\bmw(\rho) \equiv W_\rho(x)$ and $\bmw(\sigma) \equiv W_\sigma(x)$.
 	We choose the component indexing so that the rescaled distribution 
@@
 	The location of the maximum ($x=x_{i_\star}$) varies from fragment to fragment, but its value is independent of $\sigma$,
-	\begin{equation}
-		\lc{\rho}{\sigma}(x_{i_\star})
-		= \sum\limits_{\bmx: \W[\bmx]{\rho} \geq 0} \W[\bmx]{\rho}
-		= 1 + \sn{\rho}.
-	\end{equation}
-
+	\begin{align}
+	L_\star &:=	\lc{\rho}{\sigma}(x_{i_\star}) 
+		= \sum\limits_{\bmx: \W[\bmx]{\rho} \geq 0} \W[\bmx]{\rho} \nonumber \\
+		&= 1 + \sn{\rho}.
+	\end{align}
+
+Since the magic monotone mana is given by $\rm{mana}(\rho) := \log \rm{sn}(\rho)$ we see that mana corresponds precisely to peak of the Lorenz curve $L_{\rho|\sigma}(x)$.
+Therefore mana as one condition from $d^n$ constraints, and so majorization is strictly stronger a constraint in any fragment.
 \end{proof}
-
-We can therefore view mana as just one feature of the Lorenz curve, namely its maximum value. 
-Conversely, it is now clear that the maximum of the Lorenz curve acts as a valid magic monotone.
-\begin{theorem}\label{thm:bounds}
-    Given a magic state conversion $\rho \longrightarrow \tau$, the majorisation condition is stronger than the mana condition in every $\sigma$--fragment.
-\end{theorem}
+From this Lorenz curve perspective it is easy to construct other monotones. For example, within a given fragment the area above $L=1$ is another magic monotone, as we now show.
+\begin{lemma} Let $\A_\sigma(\rho)$ be the area of the region $\{(x,y) : (x, L_{\rho | \sigma}(x)) \ge 1\}$. Then $\A_\sigma(\rho)$ is a magic monotone for $\R_\sigma$.
+\end{lemma}
 \begin{proof}
-    The maximum of the Lorenz curve of a state $\rho$ is independent of the $\sigma$--fragment due to~\cref{lem:lcmax}, and can be expressed as an increasing function of mana,
-    \begin{equation}
-        \max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} = 1 + \sn{\rho} = \frac{1}{2} \left( 1 + e^\mana{\rho} \right).
-    \end{equation}
-    Therefore, the majorisation bound
-    \begin{equation}
-    	\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x),\ x\in[0,1]
-    \end{equation}
-    implies the order $\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} \geq \max_{x\in[0,1]}{\lc{\tau}{\sigma}(x)}$, hence the mana condition $\mana{\rho} \geq \mana{\tau}$.
+Consider the transformation $\rho_1 \rightarrow \rho_2$ within $\R_\sigma$.
+We have that $L_{\rho_1|\sigma}(x)$ is never below the curve $L_{\rho_2|\sigma}(x)$, and therefore the region above $L=1$ for $\rho_2$ is a subset the corresponding region for $\rho_1$.
+Thus, $\A_\sigma(\rho_1) \geq \A_\sigma(\rho_2)$, and so is a magic monotone.
 \end{proof}
-
-The area $\A_\sigma(\rho)$ between the curve $L_{\rho|\sigma}$ and the line $y=1$ is also a resource monotone in the $\sigma$--fragment. 
-This is clear because for any state conversion like~\cref{eq:sigma_conv}, the Lorenz curve $L_{\tau|\sigma}$ is lower than $L_{\rho|\sigma}$, hence $\A_\sigma(\E(\rho)) \leq \A_\sigma(\rho)$.
-It cannot be directly expressed in terms of mana, as it depends on positive Wigner components as well.
+In contrast, however, this monotone is \emph{specific to the fragment}, and its value will vary as we change $\sigma$.
+Therefore its monotonicity is also including the physics of the fragment.
+I.e.
+it provides a means to analyse magic distillation only under free operations that leave $\sigma$ invariant.
+
+There are as many independent constraints as there are elbows in the Lorenz curve of the target state as shown in~\cref{thm:elbows} in~\cref{app:frag}.
+However, in principle any one location $x$ provides a valid constraint leading to some upper distillation bound, while optimising over the location would provide the strictest bound.
+%
+%For example, the first elbow of the Lorenz curve yields the following condition.
+%\begin{lemma}
+%	Consider a magic state interconversion as in~\cref{eq:sigma_conv}, where we denote by $(x_0, L_0)$ and $(x'_0, L'_0)$ the first elbow coordinates of the initial and target states respectively.
+%	If $x_0 < x'_0$, then it holds that
+%\begin{equation}\label{eq:first_elb_bound1}
+%	\frac{L_0}{x_0} \geq \frac{L_0'}{x_0'}.
+%\end{equation}
+%\end{lemma}
+%\begin{proof}
+%	Consider the Lorenz curve constraint at $x = x_0$,
+%\begin{equation}
+%	\lc{\rho}{\sigma}(x_0) \geq \lc{\tau}{\sigma}(x_0).
+%\end{equation}
+%Since $x_0 < x'_0$, we can find the target state Lorenz curve coordinate $L'_\star$ at location $x = x_0$ by interpolating between the origin and the target state's first elbow, 
+%\begin{equation}
+%	L'_\star = \frac{x_0}{x'_0}L'_0.
+%\end{equation}
+%We need $L_0 \geq L_\star'$ and rearranging we get~\cref{eq:first_elb_bound1}.
+%\end{proof}
+
+\section{Magic in the unital fragment}
 
@@
 
-\section{Magic in the unital fragment}
 \label{sec:unital}

### 2021-03-30 magic_paper.tex
added last elbow bound discussion

--- 2021-03-28 magic_paper.tex
@@
 \end{align}
-If the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than $1$ then the maximum occurs at $\alpha=0$, otherwise the maximum occurs at $\alpha = n$. To determine this transition we set
+If the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than $1$ then the maximum occurs at $\alpha=0$, otherwise it occurs at $\alpha = n$. 
+To determine this transition we set
 \begin{equation}\label{eq:noise_transition}
@@
 \end{proof}
+
+\nick{LAST ELBOW BOUND}
+
+To find the coordinates of the \textbf{last} elbow $(x_E, L_E)$, where $E$ is the number of elbows, we need to evaluate the minimum rescaled component,
+\begin{align}
+	&\bmw(\rho_{\rm{S}} | \gamma)_{\rm{min}} \coloneqq (3\Z)^{n}\times \nonumber\\
+	&\min\limits_{i,j,k}\Big\{ (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \label{eq:min_slope}
+\end{align}
+where $0 \leq i,j,k \leq n$ and $\alpha \coloneqq i+j+k \leq n$.
+Notice that for $0 \leq \epsilon \leq 3/7$, we have $v \geq u$. 
+We need the sum $\alpha = i+j+k$ to be odd for the expression to be negative.
+
+Given an odd value for the sum $\alpha$, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_0}$ is fixed (and negative), so the expression is minimised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
+Hence, we have
+\begin{align}
+	&\bmw(\rho_{\rm{S}} | \gamma)_{\rm{min}} = \nonumber\\
+	&-(3\Z)^{n} v^n e^{n\beta E_0}\max\limits_{\substack{\alpha = 1,3, \\ \dots,n-1}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}.
+\end{align}
+If the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than $1$ then the minimum occurs at $\alpha=1$, otherwise it occurs at $\alpha = n-1$.
+
+The minimum rescaled component can then be expressed as
+\begin{equation}
+\bmw(\rho_{\rm{S}} | \gamma)_{\rm{min}} =
+	\begin{cases}
+		-(3\Z)^{n} v^{n-1} u e^{\beta [(n-1)E_0 + E_{\rm{max}}]}, &\epsilon \leq \epsilon_{\star},\ \hspace{3pt}\rm{(C1)}	\\
+		-(3\Z)^{n} v u^{n-1} e^{\beta [E_0 + (n-1)E_{\rm{max}}]}, &\epsilon > \epsilon_{\star}.\ \hspace{5pt}\rm{(C2)} 
+	\end{cases}
+\end{equation}
+Case $\rm{(C1)}$ can correspond to $(i,j,k) = (1,0,0)$ if $E_{\rm{max}} = E_0$, when the multiplicity is $m_{100} = 2n$ and the corresponding Wigner components are $\bmw(\rho_{\rm{S}})_{100}, \bmw(\gamma)_{100}$ or it can correspond to $(i,j,k) = (0,1,0)$ ($(i,j,k) = (0,0,1)$), if $E_{\rm{max}} = E_1$ ($E_{\rm{max}} = E_2$), when the multiplicity is $m_{010} = 3n$ ($m_{001} = 3n$) and the corresponding Wigner components are $\bmw(\rho_{\rm{S}})_{010}, \bmw(\gamma)_{010}$ ($\bmw(\rho_{\rm{S}})_{001}, \bmw(\gamma)_{001}$).
+Case $\rm{(C2)}$ corresponds to $(i,j,k) = (0,n-1,0)$ ($(i,j,k) = (0,0,n-1)$)
+if we have $E_{\rm{max}} = E_1$ ($E_{\rm{max}} = E_2$), when the multiplicity is $m_{0,n-1,0} = 3^{n-1}n$ ($m_{0,0,n-1} = 3^{n-1}n$) and the corresponding Wigner components are $\bmw(\rho_{\rm{S}})_{0,n-1,0}, \bmw(\gamma)_{0,n-1,0}$ ($\bmw(\rho_{\rm{S}})_{0,0,n-1}, \bmw(\gamma)_{0,0,n-1}$).
+
+The last elbow coordinates can finally be derived by sutracting the appropriate rescaled component from 1,
+\begin{equation}\label{eq:first_elb_coords}
+	(x_E, L_E) =
+	\begin{cases}
+		&\left( 1-\dfrac{2n}{(3\Z_\beta)^n}e^{-\beta [(n-1)E_0 + E_{\rm{max}}]},\ 1 + 2n v^{n-1} u \right), \vspace{5pt}\\
+		&\hspace{5pt} \text{if } E_{\rm{max}} = E_0, \hspace{51pt}\rm{(C1a)} \vspace{10pt}\\
+		&\left( 1-\dfrac{3n}{(3\Z_\beta)^n}e^{-\beta [(n-1)E_0 + E_{\rm{max}}]},\ 1 + 3n v^{n-1} u \right), \vspace{5pt}\\
+		&\hspace{5pt} \text{if } E_{\rm{max}} > E_0, \epsilon \leq \epsilon_{\star}, \hspace{20pt}\rm{(C1b)} \vspace{10pt}\\
+		&\left( 1-\dfrac{n}{3\Z_\beta^n}e^{-\beta [E_0 + (n-1)E_{\rm{max}}]},\ 1 + 3^{n-1}n v u^{n-1} u \right), \vspace{5pt}\\
+		&\hspace{5pt} \text{if } E_{\rm{max}} > E_0, \epsilon \geq \epsilon_{\star}. \hspace{22pt}\rm{(C2)}
+	\end{cases}
+\end{equation}
+
+Assuming that $E_{\rm{max}} > E_0$ for clarity, we have the same three scenarios as in the case of the first elbow bound:
+\begin{enumerate}
+	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $\beta < \beta_{\star}$ and $\epsilon' < \epsilon  \leq \epsilon_{\star}$.
+	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $\beta < \beta_{\star}$ and $\epsilon' \leq \epsilon_{\star} < \epsilon$.
+	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $\beta < \beta_{\star}$ and $\epsilon_{\star} \leq \epsilon' < \epsilon$ or $\beta \geq \beta_{\star}$.
+\end{enumerate}
+Now the last elbow condition on Lorenz curves can be derived by simple interpolation, giving the condition
+\begin{align}
+	L_E \geq 1 + \frac{1-x_E}{1-x_E'} (L_E' - 1),
+\end{align}
+provided that the last elbow location is closer to 1 for the initial state than the target state, which is always true.
+
+Focussing on the first scenario, the last elbow condition gives
+\begin{equation}
+	R_{\rm{last-elb}} = R_{\rm{first-elb}} + \frac{1}{n} \dfrac{\log{u(\epsilon)v(\epsilon')} - \log{u(\epsilon')v(\epsilon)}}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F_\beta)}.
+\end{equation}
+The numerator $log{u(\epsilon)v(\epsilon')} - \log{u(\epsilon')v(\epsilon)}$ is always positive for $\epsilon > \epsilon'$.
+The denominator (for $\beta < \beta_\star$) can only be negative for $\epsilon' > 0.41$.
+Therefore, the $R_{\rm{first-elb}}$ is almost always stricter than $R_{\rm{last-elb}}$.
 

### 2021-03-30 magic_paper.tex
Small edits to start of unital fragment.

@@
 
-A range of monotones have been developed in the literature~\cite{cit:howard, Wang_2020, Seddon_2021} \nick{Actually I think they are not that many for qudits: Mana, Robustness, Wang's entropic measures}\ddd{[Then we kick ass, and give exponentially many new ones.]} and each provides a means to upper bound distillation rates within a particular theory of magic.
+A range of monotones have been developed in the literature~\cite{cit:howard, Wang_2020, Seddon_2021} and each provides a means to upper bound distillation rates within a particular theory of magic.
 In this work we shall consider a broad framework for magic, with conditions that any theory of magic should satisfy.
@@
 \end{proof}
-In contrast, however, this monotone is \emph{specific to the fragment}, and its value will vary as we change $\sigma$.
+In contrast to mana, however, this area monotone is \emph{specific to the fragment}, and its value will vary as we change $\sigma$.
 Therefore its monotonicity is also including the physics of the fragment.
@@
 However, in principle any one location $x$ provides a valid constraint leading to some upper distillation bound, while optimising over the location would provide the strictest bound.
-%
-%For example, the first elbow of the Lorenz curve yields the following condition.
-%\begin{lemma}
-%	Consider a magic state interconversion as in~\cref{eq:sigma_conv}, where we denote by $(x_0, L_0)$ and $(x'_0, L'_0)$ the first elbow coordinates of the initial and target states respectively.
-%	If $x_0 < x'_0$, then it holds that
-%\begin{equation}\label{eq:first_elb_bound1}
-%	\frac{L_0}{x_0} \geq \frac{L_0'}{x_0'}.
-%\end{equation}
-%\end{lemma}
-%\begin{proof}
-%	Consider the Lorenz curve constraint at $x = x_0$,
-%\begin{equation}
-%	\lc{\rho}{\sigma}(x_0) \geq \lc{\tau}{\sigma}(x_0).
-%\end{equation}
-%Since $x_0 < x'_0$, we can find the target state Lorenz curve coordinate $L'_\star$ at location $x = x_0$ by interpolating between the origin and the target state's first elbow, 
-%\begin{equation}
-%	L'_\star = \frac{x_0}{x'_0}L'_0.
-%\end{equation}
-%We need $L_0 \geq L_\star'$ and rearranging we get~\cref{eq:first_elb_bound1}.
-%\end{proof}
+However, we ultimately want to make statements about asymptotic distillation rates,
+\begin{equation}
+\rho_1^{\otimes N} \longrightarrow \rho_2^{\otimes R N}
+\end{equation}
+where $\rho_2$ is a more pure form of magic than $\rho_1$ and $R$ is made as large as possible as $N$ tends to infinity.
+We shall next turn to this analysis, and exploit basic features of a magic state in order to obtain non-trivial distillation bounds.
 
@@
 
-In~\cref{sec:unital,sec:stab}, we study majorisation constraints on magic distillation arising in different fragments. 
-For this reason, we define the $n$--copy, $\epsilon$--noisy Strange state,
+In this section we apply majorization to magic state distillation within a simple fragment, namely the unital fragment.
+This corresponds to considering distillation protocols where one is restricted to free operations that are \emph{unital operations}, meaning that $\E(\I/d) = \I/d$.
+This is a particularly nice set of operations, which include for example all Weyl-covariant channels \ddd{[CITE]}.
+To make things concrete we shall consider qutrit magic states ($d=3$).
+This is convenient since this system doesn't have the subtleties of the qubit case, and admits non-trivial structure (e.g.
+Hamiltonians with two different energy gaps) while being sufficiently simple to analyse in detail.
+
+For our distillation protocols we need to choose a canonical pure magic state as a target. For this we shall choose the Strange state $|S\>$ given as
+\begin{equation}
+|S\> := \frac{1}{\sqrt{2}} (|1\> + |2\>),
+\end{equation}
+in the computational basis.
+The reason for this particular choice is that the Wigner distribution is very simple.
+Specifically $W_S(\x)$ has a single negative value of $-1/3$ at $\x =(0,0)$ and the value $1/6$ at all other points.
+We also define the $\epsilon$--noisy Strange state as
 \begin{equation}\label{eq:noisysn}
-    \rho_{\rm{S}}(\epsilon)^{\otimes n} \coloneqq \left[ (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \frac{1}{3}\id \right]^{\otimes n},
-\end{equation}
+    \rho_{\rm{S}}(\epsilon)\coloneqq \left[ (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \frac{1}{3}\id \right],
+\end{equation}
+where $\epsilon$ is the depolarization noise parameter.
 in $\O_\sigma$, where the pure magic state $\ket{\rm{S}}$ is induced with depolarising noise.
+In fact, any magic state $\rho$ can be processed via Clifford operations and put into this canonical form for some $\epsilon \ge 0$.
+
 Its Wigner distribution is visualised in~\cref{fig:strange}.

### 2021-03-31 magic_paper.tex
added last elbow analysis

--- 2021-03-30 magic_paper.tex
@@
 
-Similar upper bounds on distillation rates for qudits of odd prime dimension include the mana bound~\cite{cit:veitch} and the max--thauma bound~\cite{Wang2020} which is defined via a semi-definite program, but possesses properties that allow for an easy comparison with our bound.
+Similar upper bounds on distillation rates for qudits of odd prime dimension include the mana bound~\cite{cit:veitch} and the max--thauma bound~\cite{Wang_2020} which is defined via a semi-definite program, but possesses properties that allow for an easy comparison with our bound.
 The mana bound can be directly calculated as
@@
 
-The last elbow coordinates can finally be derived by sutracting the appropriate rescaled component from 1,
-\begin{equation}\label{eq:first_elb_coords}
-	(x_E, L_E) =
+The last elbow coordinates can finally be derived by sutracting the appropriate rescaled component from 1, $(x_E, L_E) =$
+\begin{equation}\label{eq:last_elb_coords}
 	\begin{cases}
@@
 		&\hspace{5pt} \text{if } E_{\rm{max}} > E_0, \epsilon \leq \epsilon_{\star}, \hspace{20pt}\rm{(C1b)} \vspace{10pt}\\
-		&\left( 1-\dfrac{n}{3\Z_\beta^n}e^{-\beta [E_0 + (n-1)E_{\rm{max}}]},\ 1 + 3^{n-1}n v u^{n-1} u \right), \vspace{5pt}\\
+		&\left( 1-\dfrac{n}{3\Z_\beta^n}e^{-\beta [E_0 + (n-1)E_{\rm{max}}]},\ 1 + 3^{n-1}n v u^{n-1} \right), \vspace{5pt}\\
 		&\hspace{5pt} \text{if } E_{\rm{max}} > E_0, \epsilon \geq \epsilon_{\star}. \hspace{22pt}\rm{(C2)}
@@
 Now the last elbow condition on Lorenz curves can be derived by simple interpolation, giving the condition
-\begin{align}
+\begin{equation}
 	L_E \geq 1 + \frac{1-x_E}{1-x_E'} (L_E' - 1),
-\end{align}
+\end{equation}
 provided that the last elbow location is closer to 1 for the initial state than the target state, which is always true.
 
-Focussing on the first scenario, the last elbow condition gives
-\begin{equation}
-	R_{\rm{last-elb}} = R_{\rm{first-elb}} + \frac{1}{n} \dfrac{\log{u(\epsilon)v(\epsilon')} - \log{u(\epsilon')v(\epsilon)}}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F_\beta)}.
-\end{equation}
-The numerator $log{u(\epsilon)v(\epsilon')} - \log{u(\epsilon')v(\epsilon)}$ is always positive for $\epsilon > \epsilon'$.
-The denominator (for $\beta < \beta_\star$) can only be negative for $\epsilon' > 0.41$.
-Therefore, the $R_{\rm{first-elb}}$ is almost always stricter than $R_{\rm{last-elb}}$.
+The last elbow bound then can be rephrased in terms of the first elbow bound as $R_{\rm{last-elb}} - R_{\rm{first-elb}} = $
+\begin{equation}\label{eq:last_elb_coords}
+	\begin{cases}
+		\dfrac{1}{n} \dfrac{\log{\frac{u(\epsilon)v(\epsilon')}{u(\epsilon')v(\epsilon)}}}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F_\beta)},\ &\rm{(C1)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
+		\dfrac{1}{n} \dfrac{\log{\frac{v(\epsilon)v(\epsilon')}{u(\epsilon)u(\epsilon')}} - 2\beta(E_{\rm{max}} - E_0)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F_\beta)},\ &\rm{(C2)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
+		\dfrac{1}{n} \dfrac{\log{\frac{v(\epsilon')u(\epsilon')}{v(\epsilon')u(\epsilon)}}}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F_\beta)},\ &\rm{(C2)} \rightarrow \rm{(C2)},
+	\end{cases}
+\end{equation}
+
+Note that the last elbow bounds have a dependence on $n$, which interestingly is due to $n$ being even.
+Had we considered \textbf{odd} number of copies $n$, then the first elbow bound would depend on $n$ and the last elbow bound would not.
+
+Determining the sign of the difference between the last and first elbow bounds tells us which bound is better.
+The term $\log{\frac{u(\epsilon)v(\epsilon')}{u(\epsilon')v(\epsilon)}}$ is always positive for $\epsilon > \epsilon'$, therefore the last elbow bound, compared to the first elbow bound, is always \textbf{worse} in the first scenario and always \textbf{better} in the third scenario (remember, this is the yellow-ish right part of~\cref{fig:rate_contour}).
+
+In the second scenario ($\rm{(C2)} \rightarrow \rm{(C1)}$), the expression looks very weird to me, seems like the difference tends to $-\infty$ as $E_{\rm{max}} \rightarrow \infty$.
+I am a bit stuck with this expression and I am not sure it's worth putting more time in it.
 

### 2021-03-31 magic_paper.tex
minor additions
Cleaned up after Sec.II

@@
 % Sec: Abstract
-% Figs consistency (esp. figs 3,4,5,6 and 1,7) + Figure 0 ?
+% Figs consistency (esp. figs 3,4,5 and 1,6) + Figure 0 ?
 % Spacing (fig positioning, sections, paragraphs, QED symbols)
@@
 Central to our construction is the representation of any quantum state or quantum operation on a system of dimension $d$ in terms of quasi-probability representations on a discrete phase space~\cite{Ferrie_2008}.
-This construction is a discrete version of Wigner representations in quantum optics.
+This construction is a discrete version of Wigner representations in quantum optics~\cite{Wigner_1932, Vourdas_2004}.
 
@@
 The Clifford operations $ \cal{C}_d^n $ are then defined as the set of unitaries that normalise the Heisenberg-Weyl group~\cite{Appleby_2005}.
-We may define the pure stabiliser states as those states obtained by acting on $|0\>$ with Clifford unitaries~\cite{cit:gross3}.
-Finally, we define $\stab$ as the convex hull of all pure stabiliser states, namely all probabilistic mixtures of states of the form $U|0\>\<0|U^\dagger$ where $U$ is some Clifford unitary.
+We may define the pure stabiliser states as those states obtained by acting on $|0\>$ with Clifford unitaries~\cite{cit:gross3} and, finally, the full set of stabilizer states as the convex hull of all pure stabilisers, namely all probabilistic mixtures of states of the form $U|0\>\<0|U^\dagger$ where $U$ is Clifford.
 
@@
 
-The phase-point operators form an orthogonal (with respect to the Hilbert-Schmidt inner product) operator basis as discussed in~\cref{app:wigner}.
+The phase-point operators form an orthogonal operator basis with respect to the Hilbert-Schmidt inner product, as discussed in~\cref{app:wigner}.
 Therefore, any quantum state $\rho \in \cal{B}(\cal{H}_d)$ can be expressed as a linear combination of them,
@@
 
-For any quantum state $\rho$, the Wigner distribution $W_\rho(\bmx)$ is readily seen to be a $d^2$-dimensional quasi-probability distribution over $\cal{P}_d$ (see~\cref{app:wigner} for details).
-More precisely, $W_\rho(\x)$ is a real-valued function on $\P_d$ with the property that $\sum_{\x} W_\rho(\bmx) = 1$.
+For any quantum state $\rho$, the Wigner distribution $W_\rho(\bmx)$ is readily seen to be a $d^2$-dimensional quasi-probability distribution over $\cal{P}_d$.
+More precisely, $W_\rho(\x)$ is a bounded real-valued function on $\P_d$ with the normalisation property $\sum_{\x} W_\rho(\bmx) = 1$ (see~\cref{app:wigner} for details).
 In~\cref{fig:wstate_examples}, we show Wigner distributions of different types of qutrit states.
 
-\begin{figure}%
+\begin{figure}[t]
     \centering
@@
 
+Any quantum operation $\E$ can also admit a Wigner representation. If $\E$ maps some quantum system $A$ to a quantum system $B$, and $\J(\E)$ is its associated Choi state then we can define
+\begin{equation}
+W_{\E}(\y |\x) \coloneqq d_A^2 W_{\J(\E)}(\bar{\x} \oplus \y),
+\end{equation}
+where $\bar{x} =(x_1, -p_1, \dots , x_n, -p_n)$ can be viewed as the time-reversed version of $\x$ in the discrete phase space, where momenta are reflected while position coordinates remain unchanged.
+
 \subsection{Magic theories for quantum computation}
@@
 The state-injection model for quantum computation~\cite{cit:bravyi} is a key avenue to realising a full-scale, fault-tolerant quantum computer.
-Within this approach, Clifford unitaries can be done in a robust, fault-tolerant way.
-However, due to the Eastin-Knill theorem~\cite{Eastin_2009}, it is impossible to have a universal set of transversal gates and so while Clifford unitaries can be realised transversally one must find ways around the Eastin-Knill restriction.
-The state-injection approach supplements the Clifford gates with noisy quantum states, called `magic states', that are outside the set of stabliser states and, when incorporated into Clifford circuits, provide universality.
+Within this approach, Clifford unitaries can be implemented in a robust, fault-tolerant way.
+However, due to the Eastin-Knill theorem~\cite{Eastin_2009}, it is impossible to have a universal set of transversal gates, and although Clifford unitaries can be realised transversally, one needs to find ways around the Eastin-Knill restriction.
+The state-injection approach supplements the Clifford unitaries with noisy quantum states, called `magic states', that are outside the set of stabliser states and, when incorporated into Clifford circuits, provide universality.
 The obstacle to this is that the states are invariably noisy and so protocols must be employed to purify many copies of the magic states and improve the overall performance of the induced quantum gates.
@@
 
-To address such questions both concrete distillation protocols have been developed, and there has been analysis of bounds of distillation rates within natural theoretical frameworks.
+To address such questions, concrete distillation protocols have been developed, and there has also been analysis of bounds on distillation rates within natural theoretical frameworks.
 These frameworks provide theories of magic in which one views magic states as ``resource'' states with respect to a natural class of quantum operations that are consider cheap, or ``free''~\cite{Gour_2019}.
 One very natural class of free operations considered are those obtained from Clifford operations, measurements and the ability to discard quantum systems.
-However there are several other candidate frameworks.
-
-For any theory of magic a natural route to bounding the distillation rates obtainable is through the concept of a \emph{magic monotone}.
+However, there are several other candidate frameworks~\cite{cit:ahmadi, cit:seddon, Wang_2019}.
+
+In any theory of magic, a natural route to bounding the distillation rates obtainable is through the concept of a \emph{magic monotone}.
 A magic monotone is a real-valued function of any quantum state $\M(\rho)$ that is monotonically non-increasing under the free operations of the magic theory.
-More precisely $\M(\sigma) \le \M(\rho)$ whenever it is possible to convert $\rho$ into $\sigma$ using at least one of the free operations available (e.g.
+More precisely $\M(\sigma) \le \M(\rho)$ whenever it is possible to convert $\rho$ into $\sigma$ using free operations (e.g.
 Clifford operations).
@@
 A range of monotones have been developed in the literature~\cite{cit:howard, Wang_2020, Seddon_2021} and each provides a means to upper bound distillation rates within a particular theory of magic.
-In this work we shall consider a broad framework for magic, with conditions that any theory of magic should satisfy.
+In this work we shall consider a broad framework for magic, with conditions that any magic theory should satisfy.
 However, in contrast to prior works we shall not construct magic monotones, but instead develop a generalisation to resource monotones.
-The approach we take will also allow us to address how distillation rates are constrained by physical properties -- such as a system having biased-noise, some equilibrium structure or operations that manifest invariances, such as axial symmetry around the qubit $Z$-axis.
+The approach we take will also allow us to address how distillation rates are constrained by physical properties -- such as a system having biased noise, some equilibrium structure or operations that manifest invariances, such as axial symmetry around the qubit $Z$-axis.
 
@@
 
-Within the Wigner representation all negatively represented states are magic states, although in general the converse is not true.
-However, it is known that all positively represented states used in Clifford circuits admit an efficient classical description, and therefore it is natural to consider focus on describing those negatively represented magic states.
+Within the Wigner representation, all negatively represented states are magic states, although in general the converse is not true~\cite{cit:campbell}.
+However, it is known that all positively represented states used in Clifford circuits admit an efficient classical description, so it is natural to focus on the negatively represented magic states.
 The free states in any magic theory must therefore lie in the set
@@
 \end{equation}
-Our focus is on states with negativity, and so the particular choice of free states is not so important for our analysis.
-The remaining component that needs addressing is the set of quantum operations that is considered free, or easy.
-Stabilizer operations are the most natural set of operations as they admit a classically efficient description for uniform quantum circuits.
-However, other choices of operations have been considered in the literature~\cite{cit:ahmadi, cit:seddon, Wang_2019}.
-Common to these theories is that free $\E$  is such that $(\id \otimes \E) (\rho)$ has a positive Wigner distribution whenever $ \rho$ has a positive Wigner distribution.
-\nick{This is not true for stabilizer-preserving operations~\cite{cit:ahmadi}, since ``completely'' stabilizer-preserving operations~\cite{cit:seddon} is a strict subset} Therefore, the condition that $\E$ does not generate Wigner negativity is an essential requirement of any magic theory.
-
-Any quantum channel admits a Wigner representation, in terms of the phase space operators defined earlier.
-If $\E$ is some quantum channel from a quantum system $A$ to a quantum system $B$, and $\J(\E)$ is its associated Choi state then we can define
-\begin{equation}
-W_{\E}(\y |\x) := d_A^2 W_{\J(\E)}(\bar{\x} \oplus \y),
-\end{equation}
-where $\bar{x} =(x_1, -p_1, \dots , x_n, -p_n)$ can be viewed as the time-reversed version of $\x$ in the discrete phase space, where momenta are reflected while coordinates remain unchanged.
-
-With this representation of a quantum channel, we can view $W_{\E}( \y | \x)$ as a transition matrix sending $\x \rightarrow \y$, which is consistent with the representation of quantum states, as
+Our focus is on states with negativity, so the particular choice of free states is not critical for our analysis.
+The remaining component that defines any magic theory is the set of allowed (free) quantum operations, i.e.
+the ones that are considered free.
+The assumption we require on free operations is simply that they send any free state to another free state,meaning that $\F$ must be closed, which is a common assumption among all magic theories.
+
+\nick{``the condition that $\E$ does not generate Wigner negativity is an essential requirement of any magic theory'': this is not true for stabilizer-preserving operations (SPOs)~\cite{cit:ahmadi}.
+Note that ``completely'' SPOs~\cite{cit:seddon} are a strict subset.
+However, SPOs are a subset of Wang's CPWP operations~\cite{Wang_2019} so our results hold for SPOs too.}
+
+We can view the Wigner representation $W_{\E}( \y | \x)$ of a quantum channel $\E$ as a transition matrix mapping points $\x \rightarrow \y$, which is consistent with the representation of quantum states, as
 \begin{equation}
@@
 for any $\E$ and $\rho$.
-Now if $\E$ sends any positively represented quantum state to another positively represented quantum state then it can be shown~\cite{Wang_2019} that $W_{\E}(\y |\x)$ must form a stochastic matrix.
+Now if $\E$ sends all positively represented quantum state to other positively represented quantum states then it can be shown~\cite{Wang_2019} that $W_{\E}(\y |\x)$ must form a stochastic matrix.
 In particular, all Clifford operations correspond to stochastic matrices in this Wigner representation.
 However, it is important to note that not all stochastic maps on the phase space correspond to valid quantum operations.
-In particular, the stochastic maps must respect the symplectic structure of the phase space and so this provides an additional non-trivial constraint.
-
-In what follows we shall therefore assume that we have a magic theory $\R = (\F, \O)$ in which the free states $\F$ form a closed, convex set with each state represented by a positive Wigner function, while the free operations $\O$ are represented by stochastic maps acting on the discrete phase space.
-\nick{Should we justify closedness, i.e.
-we require state positivity and Wigner-positivity both of which are closed linear constraints.
-I think we don't require convexity, we just need boundedness which trivially holds for quantum states}\ddd{[Fine print.
-No issue.]}
+In particular, the stochastic maps must respect the symplectic structure of the phase space, which is an additional non-trivial constraint.
+
+In what follows we shall therefore assume that we have a magic theory $\R = (\F, \O)$ in which the free states $\F$ form a closed set with each state represented by a non-negative Wigner function, while the free operations $\O$ are represented by stochastic maps acting on the discrete phase space.
 
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[height=4.5cm]{figs/lctoy.pdf}
-    \caption{\textbf{Quasi-probability Lorenz curve comparison}.
-    The Lorenz curves are constructed by the Wigner distributions illustrated in~\cref{fig:wstate_examples} in the unital fragment $\O_{\id/d}$ for $d=3$.
-    The maximally mixed state curve is simply the line connecting $(0,0)$ and $(1,1)$.
-    There is no operation in $\O_{\id/d}$ that can convert $\ket{\rm{S}}$ to $\ket{0}$, as their Lorenz curves intersect.\ddd{[Is debatable if this figure gives much...is a bit boring.]}
-    }
-    \label{fig:lctoy}
-\end{figure}
-
 In this section we give some generic aspects of Lorenz curves for magic states. In particular these allow us to interpret previous magic monotones in a new light.
@@
 \begin{equation}\label{eq:noisysn}
-    \rho_{\rm{S}}(\epsilon)\coloneqq \left[ (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \frac{1}{3}\id \right],
+    \rho_{\rm{S}}(\epsilon)\coloneqq (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \frac{1}{3}\id,
 \end{equation}
@@
 Had we considered \textbf{odd} number of copies $n$, then the first elbow bound would depend on $n$ and the last elbow bound would not.
+This, along with the unital fragment analysis, makes me think that calculating the bounds again for odd $n$ or $\epsilon > 3/7$ would reveal nice symmetries of the analysis, but it's probably not worth the time, so including last elbow analysis properly feels incomplete.
 

### 2021-04-01 appendix.tex
Cleaned up Sec.III

@@
 
+\subsection{First and last elbow conditions}
+
+Here we prove the majorization constraints that arise by considering the first and last elbow of the initial stata only.
+\begin{proposition}\label{prop:first_elb}
+	Consider a magic state interconversion as in~\cref{eq:stdist}, where we denote by $(x_0, L_0)$ and $(x'_0, L'_0)$ the first elbow coordinates of the initial and target states respectively.
+	If $x_0 < x'_0$, then it holds that
+\begin{equation}\label{eq:first_elb_bound1}
+	\frac{L_0}{x_0} \geq \frac{L_0'}{x_0'}.
+\end{equation}
+\end{proposition}
+\begin{proof}
+	Consider the Lorenz curve constraint at $x = x_0$,
+\begin{equation}
+	\lc{\rho}{\sigma}(x_0) \geq \lc{\tau}{\sigma}(x_0).
+\end{equation}
+Since $x_0 < x'_0$, we can find the target state Lorenz curve coordinate $L'_\star$ at location $x = x_0$ by interpolating between the origin and the target state's first elbow, 
+\begin{equation}
+	L'_\star = \frac{x_0}{x'_0}L'_0.
+\end{equation}
+We need $L_0 \geq L_\star'$ and rearranging we get~\cref{eq:first_elb_bound1}.
+\end{proof}
+
+\begin{proposition}\label{prop:last_elb}
+	Consider a magic state interconversion as in~\cref{eq:stdist}, where we denote by $(x_E, L_E)$ and $(x'_E, L'_E)$ the last elbow coordinates of the initial and target states respectively.
+	If $x_E > x'_E$, then it holds that
+\begin{equation}\label{eq:last_elb_bound1}
+	L_E \geq 1 + \frac{1-x_E}{1-x_E'} (L_E' - 1).
+\end{equation}
+\end{proposition}
+\begin{proof}
+	Consider the Lorenz curve constraint at $x = x_E$,
+\begin{equation}
+	\lc{\rho}{\sigma}(x_E) \geq \lc{\tau}{\sigma}(x_E).
+\end{equation}
+Since $x_E > x'_E$, we can find the target state Lorenz curve coordinate $L'_\star$ at location $x = x_E$ by interpolating between the the end-point $(1,1)$ and the target state's last elbow, 
+\begin{equation}
+	L'_\star = -\frac{L_E' - 1}{1 - x_E'}x_E + \frac{L_E' - x_E'}{1 - x_E'}.
+\end{equation}
+We need $L_E \geq L_\star'$ and rearranging we get~\cref{eq:last_elb_bound1}.
+\end{proof}
+
 \subsection{Component-multiplicity pairs}

### 2021-04-01 magic_paper.tex
Cleaned up Sec.III

@@
 the ones that are considered free.
-The assumption we require on free operations is simply that they send any free state to another free state,meaning that $\F$ must be closed, which is a common assumption among all magic theories.
-
-\nick{``the condition that $\E$ does not generate Wigner negativity is an essential requirement of any magic theory'': this is not true for stabilizer-preserving operations (SPOs)~\cite{cit:ahmadi}.
+The assumption we require on free operations is simply that they send any free state to another free state, meaning that a resource state cannot be created freely, a common assumption among all magic theories.
+
+\nick{``the condition that $\id \otimes \E$ does not generate Wigner negativity is an essential requirement of any magic theory'': this is not true for stabilizer-preserving operations (SPOs)~\cite{cit:ahmadi}.
 Note that ``completely'' SPOs~\cite{cit:seddon} are a strict subset.
@@
 Our formulation will not consider model-specific limitations, but will still inject broad physical constraints.
-We proceed by considering imposing equilibrium, or fixed-point, restrictions on the actual operations that are accessible to us.
+We proceed by considering fixed-point, or ``equilibrium'', restrictions on the actual operations that are accessible to us.
 While such restrictions could be viewed as the existence of some non-trivial thermodynamic constraint, they could equally be viewed as encoding a high noise-bias or difficulty in realising a particular quantum gate.
@@
 Conversely, suppose the transformation is possible in $\R$ via some $\E$ in $\O$.
-The free states $\F$ are a closed, convex set and moreover the image of $\F$ under the map $\E$ is in $\F$.
+The free states $\F$ are a closed, bounded set and moreover the image of $\F$ under the map $\E$ is in $\F$.
 By the Brouwer Fixed-Point theorem~\cite{cit:brouwer} this mapping must therefore have a fixed point $\sigma \in \F$.
@@
 
-We can now consider magic distillation rates within a particular $\sigma$--fragment and then see how the bounds on the distillation rates depend on the particular fragment we work within.
+We can now consider magic distillation rates within $\sigma$--fragments and then see how the bounds on the distillation rates depend on the choice of the fragment we work within.
 Therefore, this route can potentially shed light on how the physics of a protocol constrain distillation rates above and beyond global constraints from the parent resource theory.
 For example, how does temperature affect distillation bounds?
-Do isotropic maps have better bounds, or does bias towards a pure stabilizer state fixed point provide more freedom?
-\nick{We probably want to provide clear answers to these later on}
+Do isotropic maps have better bounds, or does bias towards some pure stabilizer state provide more freedom?
+\nick{remember to re-address these questions after deriving our bounds later on}
 
@@
     \caption{\textbf{Decomposition of a magic theory $\R$ intro $\sigma$--fragments.} 
-	Examples of magic theories ($\so$: Stabilizer operations, $\Omax$: Completely positive-Wigner-preserving operations, $\rcu$: Random Clifford Unitaries -- subclass of $\so$) involve operations denoted by the two yellow regions, with other established magic theories  between them.
+	Examples of magic theories ($\so$: Stabilizer operations, $\Omax$: Completely positive-Wigner-preserving operations, $\rcu$: Random Clifford Unitaries -- subclass of $\so$) are labelled, with other established magic theories also contained within the yellow regions.
     We introduce $\sigma$--fragments $\O_\sigma$ defined for all free states $\sigma$ that cover $\Omax$. 
     Each $\O_\sigma$ is extensible to a set of stochastic maps outside the $\cptp$ operations.
-    Within each $\sigma$--fragment $\bmd$--majorisation can be used allowing for tractable approach towards the study of magic state interconversion.
+    Within each $\sigma$--fragment, $\bmd$--majorisation can be used allowing for a tractable approach towards the study of magic state interconversions.
     }
@@
 
-We can now show that each magic fragment admits constraints that do not take the form of state monotones. The development of any monotone $\M(\rho)$ for a magic theory $\R$ can be viewed abstractly as
-\begin{equation}
-\M : \mbox{(pre-order of states)} \mapsto \mbox{(total order of numerical values).} \nonumber
+We can now show that each magic fragment admits constraints that do not take the form of state monotones. 
+The development of any monotone $\M(\rho)$ for a magic theory $\R$ can be viewed abstractly as
+\begin{equation}
+\M : \mbox{(pre-order of states)} \mapsto \mbox{(total order of numbers).} \nonumber
 \end{equation}
@@
 However, in general many states will not be interconvertible in either direction, and so this ordering is a pre-order in the sense that incomparable states exist.
-A magic monotone projects this pre-order of states onto the number line, and so through this lens any two states are directly comparable in terms of the values of $\M(\rho_1)$ and $\M(\rho_2)$.
+A magic monotone projects this pre-order of states onto the real number line, and, through this lens, any two states are directly comparable in terms of their mapped values $\M(\rho_1)$, $\M(\rho_2)$.
 Of course, the price is that the monotone provides only a necessary, but not sufficient, condition for the transformation $\rho_1 \rightarrow \rho_2$.
 
-The restriction of a magic theory $\R$ to some fragment $\R_\sigma$ can now be interpreted as a generalisation of the magic monotone construction: instead of mapping the pre-order of states in $\R$ onto the number line, we instead map this pre-order onto \emph{a simpler pre-order of states.} Therefore, we are retaining more of the original parent theory, while working in a scenario that admits greater structure and simplicity.
+The restriction of a magic theory $\R$ to some fragment $\R_\sigma$ can now be interpreted as a generalisation of the magic monotone construction: instead of mapping the pre-order of states in $\R$ onto the number line, we instead map this pre-order onto \emph{a simpler pre-order of states}.
+Therefore, we are retaining more of the original parent theory, while working in a scenario that admits greater structure and simplicity.
 We can view this as a mapping $\P_\sigma: \R \rightarrow \R_\sigma$ that restricts to a sub-theory (a $\sigma$--fragment) of the parent theory $\R$.
@@
 \end{equation}
-By framing the projection onto a fragment in this light, we can view Theorem \ref{thm:frag} as a statement that the collection $\{\P_\sigma\}$ provides a complete set of generalized monotones for the theory.
+By framing the projection onto a fragment in this light, we can view Theorem \ref{thm:frag} as a statement that the collection $\{\P_\sigma\}_{\sigma \in \F}$ provides a complete set of generalized monotones for the theory.
 
 The question is now whether the sub-theories can be analysed to provide additional insights into magic distillation protocols.
-We shall do this by working in the Wigner representation of a given $\sigma$--fragment.
+We shall provide an answer by working in the Wigner representation of a given $\sigma$--fragment.
 The problem of magic state distillation then becomes that of processing negativity under stochastic maps $W_{\E}( \y |\x)$ that leave a particular quasi-distribution $W_\sigma(\x)$ invariant.
-However $\sigma \in \F$ is is positively represented and so the sub-theory has an invariant classical probability distribution as a fixed point.
+However, $\sigma \in \F$ is positively represented, so the sub-theory has an invariant classical probability distribution as a fixed point.
 This structure allows us to make use of a range of classical tools, and in particular majorization theory.
@@
 In its simplest form it defines a pre-order on probability distributions.
-Given two distributions $\p= (p_1, \dots, p_n)$ and $\q = (q_1, \dots, q_n)$ over $n$ outcomes, we say that $\p$ majorises $\q$, denoted $\p \succ \q$, if there is a bistochastic map $A=(A_{ij})$ such that $A\p = \q$.
-Here, bistochastic means that $\sum_i A_{ij} = \sum_j A_{ij} = 1$.
-A well known result tells us that the condition $ \p \succ \q$ over probability distributions is equivalent to $n-1$ inequalities, and these conditions are easily checked.
-
-However, there is a natural generalisation of this, called \emph{relative majorization} (also known as $d$--majorization, or in the context of thermodynamics, thermo-majorization) that dates back to the 1950s.
-For a fixed probability distribution $\r = (r_1, \dots, r_n)$ we define majorization relative to $\r$ as follows:
+Given two distributions $\p= (p_1, \dots, p_n)$ and $\q = (q_1, \dots, q_n)$ over $n$ outcomes, we say that $\p$ majorises $\q$, denoted $\p \succ \q$, if there exists a bistochastic map $A = (A_{ij})$ such that $A\p = \q$, where bistochastic means that $A_{ij} \geq 0$ and $\sum_i A_{ij} = \sum_j A_{ij} = 1$.
+A well-known result~\cite{cit:marshall} tells us that the condition $ \p \succ \q$ over probability distributions is equivalent to $n-1$ inequalities, which can be easily checked.
+
+There is a natural generalisation, which we call \emph{relative majorization} (also known as $d$--majorization~\cite{Veinott_1971}, or in the context of thermodynamics, thermo-majorization)\footnote{The term ``relative majorization'' is often used~\cite{Ruch_1976} to describe a further generalisation of $\bmd$-majorization, but here we use it as equivalent.}.
+For a fixed probability distribution $\r = (r_1, \dots, r_n)$ with positive components, we define majorization relative to $\r$ as follows:
 \begin{equation}
@@
 
-However, it turns out that relative majorization is equally applicable to \emph{quasi-probability} distributions, and therefore can be applied to the Wigner representation of a given fragment.
+It turns out that relative majorization is equally applicable to \emph{quasi-probability} distributions, and therefore can be applied to the Wigner representation of a given fragment.
 To our knowledge, this application of majorization to quasi-distributions in  physics has not been considered previously.
-The caveat here is that relative majorization ranges over all stochastic maps with a given fixed point, while in the case of the Wigner representation there is an additional restriction that the symplectic structure is respected.
-This implies that any relative majorization conditions provide necessary, but not sufficient, conditions on magic state interconversions in the fragment.
-However, this observation raises a question that to our knowledge has not been previously considered in the classical statistical mechanics literature: what are the conditions for symplectic majorization of classical statistical mechanics?
-We shall return to this question later on when we discuss how our approach could be used to construct concrete lower-bounds on distillation rates.
+The caveat here is that relative majorization ranges over all stochastic maps with a given fixed point, while in the case of the Wigner representation there is an additional restriction that the phase space structure is respected.
+Therefore, any relative majorization constraint can provide necessary, but not sufficient conditions on magic state interconversions in the fragment.
+This observation raises a question that to our knowledge has not been previously considered in the classical statistical mechanics literature: what are the conditions for symplectic majorization of classical statistical mechanics?
+We shall return to this question later on when we discuss how our approach could be used to construct concrete lower-bounds on distillation rates in~\cref{sec:lower_bounds}.
 
@@
 \end{equation}
-where $R:= \sum_{i=1}^n r_i$, and $\pi$ is the permutation on $n$ objects that sends $\tilde{\w}$ to $\tilde{\w}^{\downarrow}$, where $\tilde{w}_i := w_i/r_i$ is the vector of component-wise ratios of $\w$ and $\r$.
+where $R:= \sum_{i=1}^n r_i$, and $\pi$ is the permutation on $n$ objects that sends $\widetilde{\w}$ to $\widetilde{\w}^{\downarrow}$, where $\widetilde{w}_i := w_i/r_i$ is the vector of component-wise ratios of $\w$ and $\r$.
 The form of this requires that $\r$ has no zero components, which we shall assume without loss of generality as in any physical situation the rank of a quantum state is not an operationally meaningful quantity.
@@
 If $\w$ and $\r$ are both probability distributions then the Lorenz curve is defined on the interval $[0,1]$, and rises monotonically until it reaches the value $1$ at $x=1$.
-The value $L_{\w|\r}(x) = 1$ is a global upper bound to the function, only attained at the end-point $x=1$.
+The value $L_{\w|\r}(x) = 1$ is a global maximum, attained at the end-point $x=1$.
 However, if $\w$ is a \emph{quasi-probability} distribution with negative values, and $\r$ a regular probability distribution things are different.
@@
 See Figure \ref{fig:lcs} for examples of non-monotonic Lorenz curves for quasi-distributions.
-For quasi-distributions within quantum theory, the breaking of this barrier is associated with the degree of non-classicality.
+The non-differentiable points on the curve occur at the locations where $\widetilde{\bmw}$ changes value and are called \emph{elbows}.
+Within quantum theory, the breaking of this barrier is associated with the degree of non-classicality.
 Since majorization provides a measure of order/disorder this is consistent with the intuition that negativity, for example within the context of entanglement theory or quantum computing, can provide a greater form of order than is possible within classical theory.
@@
 In contrast, Lorenz curves for magic states break through the value of $L(x)=1$ due to the presence of negativity in the associated quasi-probability distributions.
-The above family of curves correspond to multiple copies of noisy Strange states $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ for $n=1,2,3,4$ within a particular stabilizer fragment.
-Solid lines represent pure Strange states, while dashed lines represent noisy Strange states with depolarising noise $\epsilon = 0.1$.
+The above family of curves correspond to multiple copies of noisy Strange states $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ (\cref{eq:noisysn}) for $n=1,2,3,4$ within a particular stabilizer fragment.
+Solid lines represent pure Strange states, while dashed lines represent noisy Strange states with depolarising noise ($\epsilon = 0.1$).
     }
@@
 
-Given the definition of Lorenz curves, the condition for relative majorization can now be compactly phrased.
-We have that $\w_1 \succ_{\r} \w_2$ if and only if $L_{\w_1 | \r} (x) \ge L_{\w_2 | \r}(x)$ for all $x \in [0,1]$.
+Given the definition of Lorenz curves, the condition for relative majorization can now be phrased compactly.
+We have that $\w_1 \succ_{\r} \w_2$ if and only if $L_{\w_1 | \r} (x) \ge L_{\w_2 | \r}(x)$ for all $x \in [0,1]$ (technical discussion and proof can be found in~\cref{app:major}.
 In other words, the Lorenz curve of $\w_1$ relative to $\r$ is never below the Lorenz curve of $\w_2$ relative to $\r$.
 Phrased more abstractly, the relative majorization pre-order corresponds to the standard ordering of concave, piece-wise linear functions passing through $(0,0)$ and $(1,1)$.
-Another neat geometric formulation of relative majorization exists that simply states that the $L_1$-norm angle between $\w_1$ and $\r$ is greater than or equal to the $L_1$-norm angle between $\w_2$ and $\r$ (see \ddd{[CITE]} for details).
+We note that another neat geometric formulation of relative majorization exists, stating that the $L_1$-norm angle between $\w_1$ and $\r$ is greater than or equal to the $L_1$-norm angle between $\w_2$ and $\r$ (see \ddd{[CITE]}\nick{haven't seen this before} for details).
 
@@
 If we consider some $\sigma \in \F$, and its corresponding fragment $\R_\sigma$, then we are typically interested in the ability to transform many copies of some magic state $\rho$ into more pure forms of magic.
-The state $\rho$ is assumed to have negativity in the Wigner representation, and so $W_\rho(\x) < 0$ for some regions of $\x \in \P_d$.
+The state $\rho$ is assumed to have negativity in the Wigner representation, so $W_\rho(\x) < 0$ for some regions of $\x \in \P_d$.
 We again note that we restrict to odd-dimensional quantum systems, for simplicity.
-In contrast the state $\sigma$ will have a Wigner distribution $W_\sigma(\x)$ that forms a genuine probability distribution.
-On the technical assumption that $\sigma$ is full rank, then we also have that $W_\sigma(\x)$ is non-negative on the discrete phase space $\P_d$.
-Any non-full rank states can be handled as a limiting case in which we mix in a small fraction $\epsilon (\I/d)$ to the quantum state $\sigma$, and later take $\epsilon$ tending to zero.
+In contrast, the state $\sigma$ will have a Wigner distribution $W_\sigma(\x)$ that forms a genuine probability distribution.
+On the technical assumption that $\sigma$ is full rank, we also have that $W_\sigma(\x) > 0$ for all $\x \in \P_d$.
+Any non-full rank states $\sigma$ can be handled as a limiting case in which we inject an infinitesimal fraction of depolarising noise $\epsilon (\id/d)$.
 
 As discussed already, the free operations within the magic theory $\R$ are represented by stochastic maps, and within $\R_\sigma$ by stochastic maps that leave $W_\sigma(\x)$ invariant.
-Therefore a necessary condition for magic state transformations $\rho_1 \rightarrow \rho_2$ within $\R_\sigma$ will be that
+Therefore, a necessary condition for magic state transformations $\rho_1 \rightarrow \rho_2$ within $\R_\sigma$ will be that
 \begin{equation}
@@
 \begin{equation}
-\rho_1 \rightarrow \rho_2 \mbox{ within }\R_\sigma \mbox{ implies that } L_{\rho_1 |\sigma} (x) \ge L_{\rho_2 |\sigma} (x),
+\rho_1 \rightarrow \rho_2 \mbox{ within }\R_\sigma \mbox{ implies } L_{\rho_1 |\sigma} (x) \ge L_{\rho_2 |\sigma} (x),
 \end{equation}
 for all $x \in [0,1]$.
-Therefore, the constraint in terms of the Lorenz curves for the magic states can be used to impose upper bounds on magic distillation rates.
-Note however, that this is not a single numerical constraint, but is a \emph{family} of constraints.
-Indeed for $n$ copies of a $d$ dimensional system the number of terms in $W_{\rho}$ is $d^{2n}$ and so the Lorenz curve condition corresponds to \emph{exponentially} many constraints.
-
-%We can approach any magic theory through a thermodynamic lens, and in doing so we are provided with valuable insights on the structure of the theory. 
-%Firstly, any free state, for example a stabiliser state, can be viewed as a thermal state $\gamma_\beta$.
-%Without loss of generality we can always write a quantum state $\sigma$ as a thermal state, $\sigma = \gamma_\beta \coloneqq \frac{1}{\Z_\beta} e^{-\beta H}$ for some $\beta \geq 0$ and Hamiltonian $H$ (either effective or actual)\footnote{Technicalities arise for the case where $\sigma$ is not full rank, but this can be still described via $ \beta \rightarrow 0$ limiting process.}.
-%We can also view the set of free operations $\O_\sigma$ as a counterpart of thermal operations, in the sense that any operation $\E$ in $\O_\sigma$ preserves state $\sigma$. 
-%
-%It is then apparent that the pre-order $\prec_{\R_\sigma}$ between the operations in the $\sigma$--fragment follows the rules of $\bmd$--majorisation as outlined in~\cref{sec:major}.
-%In particular, the pre-order $\prec_{\R_\sigma}$ of the $\sigma$--fragment $\R_\sigma = (\F, \O_\sigma)$ between $d$--dimensional states corresponds to the majorisation pre-order $\prec_{\W{\sigma}}$ between their $d^2$--dimensional Wigner distributions.
-%For simplicity we shall merge the notation into $\prec_\sigma$, as there is little risk of confusion.
-%
-%Note that the Wigner components of an $n$--copy state $\rho^{\otimes n}$ can be calculated directly from $\W{\rho}$ by convolution of the distribution with itself,
-%\begin{equation}
-%	\W{\rho^{\otimes n}} = \W{\rho}^{\otimes n},
-%\end{equation}
-%where $\otimes$ can be interpreted as the usual Kronecker product in the last expression.
-%We may use the vector notation $\bmw(\rho) = (w(\rho)_i)_{i=1,\dots,d^2}$ for the Wigner distribution, in which case we can express the Kronecker product as
-%\begin{equation}
-%	\W{\rho} \otimes \W{\rho} = (w(\rho)_i w(\rho)_j)_{i,j=1,\dots,d^2}.
-%\end{equation}
-%The correspondence between the phase space and pure vector representations of the Wigner distribution is discussed more in~\cref{app:cmpairs}.
-%The vector notation will be useful in the proof of our main result,~\cref{thm:stab_bounds}
-%
-%Furthermore, we restrict our analysis to $\sigma$--fragments, where $\sigma$ is full-rank.
-%This is justified as majorisation is continuous between fragments, in the sense that the pre-orders $\prec_\sigma$ and $\prec_{\sigma'}$ are equivalent for states $\sigma$ and $\sigma'$ which are $\epsilon$--close.
-\nick{CHECK}
-%Therefore, majorisation analysis is robust under imperfections in the experimental implementation of quantum operations.
-%
-%In particular, we can always use common noise effects to approximate any $\sigma$--fragment where $\sigma$ is not full-rank by the $\sigma'$--fragment where $\sigma'$ is a noisy approximation of $\sigma$.
-%For example, inducing depolarising noise, we can write $\sigma' = (1-\epsilon)\sigma + \epsilon\frac{1}{d}\id$, for some infinitesimal $\epsilon > 0$, so that $\sigma'$ is full-rank and arbitrarily close to $\sigma$.
-%Important examples of such $\sigma$--fragments include pure stabiliser states which are rank-$1$, e.g. the zero state depicted in~\cref{fig:zero}. 
-%Operations in such fragments include important stabiliser operations like the replacement channel, $\E(\rho) = \sigma$ for all states $\rho$.
-%
-%\begin{theorem}\label{thm:sigmamajor}
-%    Let $\R = (\F, \O)$ be a theory of magic. If $\rho \longrightarrow \tau$  in $\R$ then  $\W{\tau} \prec_\sigma \W{\rho}$ within at least one $\sigma$--fragment.
-%\end{theorem}
-%\begin{proof}
-%Suppose we can convert $\rho$ into $\tau$ in the magic theory. 
-%Thus there is some $\O_\sigma$ and some $\E \in \O_\sigma$ such that $\E(\rho) = \tau$, and $\E(\sigma)=\sigma$. 
-%Therefore, the Wigner distribution of this free operation satisfies $\W{\E} \in \stochw$ and $\W{\E}\W{\rho} = \W{\tau}$. 
-%Since $\sigma$ is full-rank and free, its Wigner distribution is strictly positive in all components, so it directly follows from~\cref{def:dmajor} that $\W{\tau} \prec_{\sigma} \W{\rho}$.
-%\end{proof}
-%The converse is in general not true, since stochastic matrices do not necessarily correspond to valid quantum operations.
-%
-%The result of~\cref{thm:sigmamajor} can be understood as an extension of the idea of a magic monotone, where we replace $\M(\tau) \leq \M(\rho)$ with $\W{\tau} \prec_\sigma \W{\rho}$. 
-%The physical difference between the two expressions is that the majorisation ordering occurs in a specific $\sigma$--fragment.
-%Therefore, majorisation constraints can be used to place upper bounds on magic state distillation in a way that allows one to incorporate the physics of the allowed operations -- specifically, it enables us to bound how much magic can be distilled via quantum operations that, for example, preserve the equilibrium state of the system, or via operations that are symmetric about the $Z$-axis of the Bloch sphere.
-%We discuss distillation upper bounds in detail in~\cref{sec:unital,sec:stab}
+Therefore, the magic state Lorenz curve condition can be used to impose upper bounds on magic distillation rates.
+Note, however, that unlike any monotone, this is not a single numerical constraint, but a \emph{family} of constraints.
+Indeed, for $n$ copies of a $d$--dimensional system the number of terms in $W_{\rho}$ is $d^{2n}$, so the Lorenz curve condition corresponds to \emph{exponentially} many constraints, of which there are as many independent constraints as there are elbows in the Lorenz curve of the target state as shown in~\cref{thm:elbows} in~\cref{app:frag}.
+In principle, any one location $x$ provides a valid constraint leading to some upper distillation bound and optimising over the location provides the strictest bound.
 
@@
 \begin{lemma}\label{lem:lcmax}
-	Given a magic state $\rho$, the maximum $L_\star$ of its Lorenz curve $\lc{\rho}{\sigma}(x)$ is independent of the $\sigma$--fragment and is equal to $1+\sn{\rho}$, where $\rm{sn}(\rho)$ is the sum negativity of $\rho$.
+	Given a magic state $\rho$, the maximum $L_\star$ of its Lorenz curve $\lc{\rho}{\sigma}(x)$ is independent of the $\sigma$--fragment and equal to $1+\sn{\rho}$, where $\rm{sn}(\rho)$ is the sum negativity of $\rho$.
 Thus, the majorization constraint is stronger than mana in any fragment.
@@
 
-	The location of the maximum ($x=x_{i_\star}$) varies from fragment to fragment, but its value is independent of $\sigma$,
+	The location of the maximum ($x=x_{i_\star}$) varies from fragment to fragment \nick{try to calculate for thermal fragments}, but its value is independent of $\sigma$,
 	\begin{align}
@@
 
-Since the magic monotone mana is given by $\rm{mana}(\rho) := \log \rm{sn}(\rho)$ we see that mana corresponds precisely to peak of the Lorenz curve $L_{\rho|\sigma}(x)$.
-Therefore mana as one condition from $d^n$ constraints, and so majorization is strictly stronger a constraint in any fragment.
+Since the magic monotone mana is a monotonic function of sum-negativity, $\rm{mana}(\rho) \coloneqq \ln{(2\hspace{1pt}\sn{\rho}+1)}$, we see that mana corresponds precisely to the peak of the Lorenz curve $L_{\rho|\sigma}(x)$.
+Therefore, mana is one of $d^{2n}$ constraints, so majorization is strictly a stronger constraint in any fragment.
 \end{proof}
-From this Lorenz curve perspective it is easy to construct other monotones. For example, within a given fragment the area above $L=1$ is another magic monotone, as we now show.
+Using the Lorenz curve perspective, it is simple to construct other monotones. For example, within a given fragment, the area above $L=1$ is another magic monotone.
 \begin{lemma} Let $\A_\sigma(\rho)$ be the area of the region $\{(x,y) : (x, L_{\rho | \sigma}(x)) \ge 1\}$. Then $\A_\sigma(\rho)$ is a magic monotone for $\R_\sigma$.
@@
 Consider the transformation $\rho_1 \rightarrow \rho_2$ within $\R_\sigma$.
-We have that $L_{\rho_1|\sigma}(x)$ is never below the curve $L_{\rho_2|\sigma}(x)$, and therefore the region above $L=1$ for $\rho_2$ is a subset the corresponding region for $\rho_1$.
-Thus, $\A_\sigma(\rho_1) \geq \A_\sigma(\rho_2)$, and so is a magic monotone.
+We have that $L_{\rho_1|\sigma}(x)$ is never below the curve $L_{\rho_2|\sigma}(x)$, and therefore the region above $L=1$ for $\rho_2$ is a subset of the corresponding region for $\rho_1$.
+Thus, $\A_\sigma(\rho_1) \geq \A_\sigma(\rho_2)$, so $\A_\sigma$ is a magic monotone in $\R_\sigma$.
 \end{proof}
-In contrast to mana, however, this area monotone is \emph{specific to the fragment}, and its value will vary as we change $\sigma$.
-Therefore its monotonicity is also including the physics of the fragment.
-I.e.
-it provides a means to analyse magic distillation only under free operations that leave $\sigma$ invariant.
-
-There are as many independent constraints as there are elbows in the Lorenz curve of the target state as shown in~\cref{thm:elbows} in~\cref{app:frag}.
-However, in principle any one location $x$ provides a valid constraint leading to some upper distillation bound, while optimising over the location would provide the strictest bound.
-However, we ultimately want to make statements about asymptotic distillation rates,
+In contrast to mana, the area monotone is \emph{specific to the fragment}, and its value will vary as we change $\sigma$.
+Therefore its monotonicity is also including the physics of the fragment and provides a means to analyse magic distillation only under free operations that leave $\sigma$ invariant.
+
+We ultimately want to make statements about asymptotic distillation rates $R$,
 \begin{equation}
@@
 \end{equation}
-where $\rho_2$ is a more pure form of magic than $\rho_1$ and $R$ is made as large as possible as $N$ tends to infinity.
+where $\rho_2$ is a purer magic state than $\rho_1$ and $R$ is made as large as possible as $N$ tends to infinity.
 We shall next turn to this analysis, and exploit basic features of a magic state in order to obtain non-trivial distillation bounds.
@@
 In general, noisy circuits are well-described by the unital fragment.
-To see this, consider incorporating noisy channels in the circuit, for example dephasing channels as in~\cref{eq:dephase} defined in different bases.
-This process destroys the circuit symmetries, except for the invariance of the maximally mixed state.
-Dephasing and bit-flip error channels are examples of the many error-inducing channels that respect the unital symmetry.
-\nick{Expand on significance of unital fragment / Include example of depolarising channel earlier as demonstration of our ``pinpointing harware limitations''-approach}
-\null\\
+To see this, consider incorporating noisy channels in the circuit, for example dephasing channels like
+\begin{equation}\label{eq:dephase}
+	\Delta(\rho) = \sum_{k \in \mathbb{Z}_d} \ketbra{\phi_k}\rho\ketbra{\phi_k}
+\end{equation}
+in various bases $\ket{\phi_k}$.
+A circuit consisting of such dephasing channels can be fully analysed in the $\sigma$--fragments of the pure basis states $\sigma = \ketbra{\phi_k}$ (see proof in~\cref{app:frag}).
+Incorporating many such channels in different bases destroys the circuit symmetries, except for the invariance of the maximally mixed state.
 

### 2021-04-05 magic_paper.tex
Section IV, unital fragment tidied.

@@
 
-There is a natural generalisation, which we call \emph{relative majorization} (also known as $d$--majorization~\cite{Veinott_1971}, or in the context of thermodynamics, thermo-majorization)\footnote{The term ``relative majorization'' is often used~\cite{Ruch_1976} to describe a further generalisation of $\bmd$-majorization, but here we use it as equivalent.}.
+There is a natural generalisation, which we call \emph{relative majorization} (also known as $d$--majorization~\cite{Veinott_1971}, or in the context of thermodynamics, thermo-majorization)\footnote{The general form of relative majorization is defined as $(\p,\r) \succ (\q, \r')$ iff there is a stochastic map $A$ such that $A\p = \q$ and $A\r = \r'$.}.
 For a fixed probability distribution $\r = (r_1, \dots, r_n)$ with positive components, we define majorization relative to $\r$ as follows:
@@
 Phrased more abstractly, the relative majorization pre-order corresponds to the standard ordering of concave, piece-wise linear functions passing through $(0,0)$ and $(1,1)$.
-We note that another neat geometric formulation of relative majorization exists, stating that the $L_1$-norm angle between $\w_1$ and $\r$ is greater than or equal to the $L_1$-norm angle between $\w_2$ and $\r$ (see \ddd{[CITE]}\nick{haven't seen this before} for details).
+We note that another neat geometric formulation of relative majorization exists, stating that the $L_1$-norm angle between $\w_1$ and $\r$ is greater than or equal to the $L_1$-norm angle between $\w_2$ and $\r$ (see \ddd{[CITE]}\nick{haven't seen this before}\ddd{[`Orthogonality and Disjointness in Spaces of Measures'', by Paul Busch.]} for details).
 
@@
 where $\epsilon$ is the depolarization noise parameter.
-in $\O_\sigma$, where the pure magic state $\ket{\rm{S}}$ is induced with depolarising noise.
-In fact, any magic state $\rho$ can be processed via Clifford operations and put into this canonical form for some $\epsilon \ge 0$.
-
-Its Wigner distribution is visualised in~\cref{fig:strange}.
-
-We refer to parameter $\epsilon$ as \emph{noise level} to avoid confusion with the error rate $\delta$, a term commonly used in the literature to denote that the distilled state has a marginal overlap of at least $1-\delta$ with the desired magic state.
-In our case the error rate of the state in~\cref{eq:noisysn} would be $\delta = \frac{2}{3}\epsilon$.
-
-At $\epsilon=0$, the Strange state is a qutrit magic state of maximal sum-negativity / mana~\cite{cit:veitch2} and therefore acts as an ideal distillation target, analogous to a Bell state in bipartite entanglement theory.
-The Strange state is exceptionally symmetric under Clifford transformations and as a result there exists a \emph{twirling} protocol, discussed in detail in~\cite{cit:prakash,cit:prakash2}, allowing for the conversion of any noisy magic state to the form of~\cref{eq:noisysn} via Cliffords.
-
-In~\cref{fig:lcs}, we illustrate the Lorenz curve $\lc{\rho_{\rm{S}}}{\sigma}$\footnote{Hereinafter, we may omit obvious variable dependencies like $\epsilon$ and $n$ for clarity} of pure and noisy $n$--copy Strange states in some thermal $\sigma$--fragment.
-Due to~\cref{lem:lcmax}, it is clear that the curves peak at $1 + \sn{\rho_{\rm{S}}(\epsilon)^{\otimes n}}$.
-
-\label{sec:unital}
-We shall provide a general analysis across multiple fragments, but before we do that it is useful to illustrate the techniques in the simplest fragment first.
-The unital fragment encompasses the circuits which preserve the maximally mixed state ($\id/d$) and so it includes many important families of circuits.
-
-MSD circuits in principle consist of bulk sequences of random Clifford unitaries ($\rcu$)~\cite{cit:bravyi}, depicted in~\cref{fig:zoo}.
-Operations in $\rcu$ can be expressed as
-\begin{equation}
-    \E(\rho) = \sum_i p_i U_i \rho U_i^\dagger,\ U_i \in \cal{C}_d.
-\end{equation}
-Depending on the symmetries of such operations, a Clifford sequence may belong in other $\sigma$--fragments as well.
-In such a case, the majorisation condition~(\ref{eq:majbound}) needs to be checked in the $\sigma$--fragments that reflect all symmetries of the operation sequence.
-
-In general, noisy circuits are well-described by the unital fragment.
-To see this, consider incorporating noisy channels in the circuit, for example dephasing channels like
-\begin{equation}\label{eq:dephase}
-	\Delta(\rho) = \sum_{k \in \mathbb{Z}_d} \ketbra{\phi_k}\rho\ketbra{\phi_k}
-\end{equation}
-in various bases $\ket{\phi_k}$.
-A circuit consisting of such dephasing channels can be fully analysed in the $\sigma$--fragments of the pure basis states $\sigma = \ketbra{\phi_k}$ (see proof in~\cref{app:frag}).
-Incorporating many such channels in different bases destroys the circuit symmetries, except for the invariance of the maximally mixed state.
-
-We consider the task of purifying $n$ copies of a noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ as given in~\cref{eq:noisysn} into a smaller number of copies $n'$ of a less noisy strange state $\rho_{\rm{S}}(\epsilon')^{\otimes n'}$, with $\epsilon' < \epsilon$ and $n' \leq n$,
+Moreover, any magic state $\rho$ can be processed via Clifford operations~\cite{cit:prakash,cit:prakash2} and put into this canonical form for some $\epsilon \ge 0$.
+
+We now consider the task of purifying $n$ copies of a noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ as given in~\cref{eq:noisysn} into a smaller number of copies $n'$ of a less noisy strange state $\rho_{\rm{S}}(\epsilon')^{\otimes n'}$, with $\epsilon' < \epsilon$ and $n' \leq n$.
+It turns out that our majorization relations are simplest to express when the number of systems remains constant.
+To do this is simply tensor in $n'-n$ auxiliary free states, which do not affect the distillation analysis.
+Since we work in the unital fragment it makes sense to choose these free states to be the maximally mixed state, since the Lorenz curves are unaffected.
+More generally, it is easy to show that
+\begin{equation}
+L_{\rho |\sigma} (x) = L_{\rho\otimes \sigma |\sigma}(x),
+\end{equation}
+for any full-rank $\sigma \in \F$. Therefore, we can consider the transformation
 \begin{equation}\label{eq:sudist}
@@
 \end{equation}
-where all copies $n, n', n - n'$ are even.
-Since the state $\id / 3$ is free, tensoring in copies of it does not affect the distillation process.
-The distillation rate $R \coloneqq n'/n$ for this process will in general depend on the noise levels, $R = R(\epsilon, \epsilon')$ and our task is to provide it with an upper bound.
-
-The Lorenz curve $\lc{\rho_{\rm{S}}}{\id/3}$, for some general noise parameter $\epsilon$ and number of copies $n$, is defined at $9^n$ points between $0$ and $1$.
-The exact expressions for the coordinates of these points can take $8$ different forms, depending on whether the noise level $\epsilon$ is greater or less than $\frac{3}{7}$, the parity of the number of copies $n$ is even or odd and the location relative to the curve peak is on the left hand side (LHS -- including the curve peak) or right hand side (RHS) of the curve peak.
-The full details for the construction of all Lorenz curve forms are provided in~\cref{app:lcsu_technical}.
-
-Here we focus on the comparison of the first elbow (which lies in the LHS part) of Lorenz curves with even copies $n, n'$ and low noise levels ($\epsilon' < \epsilon \leq 3/7$).
-
-The Wigner distribution of the 1-copy, $\epsilon$--noisy Strange state can be written as 
-\begin{equation}
-	\W[\bmx]{\rho_{\rm{S}}(\epsilon)} = (1-\epsilon)\W[\bmx]{\ketbra{\rm{S}}} + \epsilon\W[\bmx]{\frac{1}{3}\id},
-\end{equation}
-so we get positive components
+and compare the Lorenz curves for both the input and output states to bound $R(\epsilon, \epsilon') \coloneqq n'/n$, the rate of this interconversion within the fragment.
+
+The Wigner distribution of the single-copy, $\epsilon$--noisy Strange state  is given by
+\begin{equation}
+	\W[\bmx]{\rho_{\rm{S}}(\epsilon)} = (1-\epsilon)\W[\bmx]{\ketbra{\rm{S}}} + \epsilon\W[\bmx]{\frac{1}{3}\id}.
+\end{equation}
+Since the Wigner distribution $W_{\I/3}(x)$ is the uniform probability distribution over the phase space, we get that $W_{\rho_S(\epsilon) } (\x)$ has positive components
 \begin{equation}
@@
 \end{equation}
-at the 8 phase space points $\bmx \in \cal{P}_3 \setminus \{\bmo\}$ and a negative component
+at the 8 phase space points $\x  \ne (0,0)$ and a single negative component
 \begin{equation}
@@
 \end{equation}
-at the origin $\bmx = \bmo$.
-
-The rescaled distribution in the unital fragment simply is 
-\begin{equation}
-	\widetilde{\rm{W}}_{\rho_{\rm{S}}|\frac{1}{3}\id}(\bmx) = \frac{\W[\bmx]{\rho_{\rm{S}}}}{\W[\bmx]{\frac{1}{3}\id}} = d\W[\bmx]{\rho_{\rm{S}}},
-\end{equation}
-so ordering the rescaled distribution is equivalent to ordering $\W{\rho_{\rm{S}}}$.
-
-The component values and multiplicities ($m_i$) in the $n$--copy case are 
+located at the origin $\bmx = \bmo$. We assume that $\epsilon < 3/4$ to ensure the presence of negativity in the Wigner distribution.
+
+To use relative majorization on such distributions we must rescale relative to the free state, however the rescaled distribution in the unital fragment is simply
+\begin{equation}
+	\widetilde{\rm{W}}_{\rho_{\rm{S}}|\frac{1}{3}\id}(\bmx) = \frac{\W[\bmx]{\rho_{\rm{S}}}}{\W[\bmx]{\frac{1}{3}\id}} = 9\W[\bmx]{\rho_{\rm{S}}},
+\end{equation}
+so the probleme of ordering the rescaled distribution is equivalent to ordering $\W{\rho_{\rm{S}}}$.
+The Wigner distribution of $n$ copies of the state is obtained by the $n$-fold product of the single copy distribution, and the Lorenz curve $L_{\rho|\sigma}(x)$ for $\rho = \rho_S(\epsilon)^{\otimes n}$ and $\sigma = (\I/3)^{\otimes n}$ is readily computed for any $n$ and $\epsilon$, and the full details are provided in~\cref{app:lcsu_technical}.
+The non-trivial element that arises for quasi-distributions is that the product of negative components generates a positive number, and therefore the ordering of the components of $W_{\rho |\sigma}(x)$ depends on whether $-v(\epsilon)$ appears to an even or odd power.
+
+The component values $w_i$ and associated multiplicities ($m_i$) in the $n$--copy case are 
 \begin{align}
 	m_i &= 8^{2i}\binom{n}{2i}, \\
-	w(\rho_{\rm{S}})_i &= u^{2i}(-v)^{n-2i}, \\
-	w(\id/3)_i &=  \frac{1}{9^n},
+	w_i &= u^{2i}(-v)^{n-2i},
 \end{align}
-where index $i$ runs through $0,\dots,\frac{n}{2}$.
-This is derived in~\cref{app:lcsu_coord_elb}.
-
-It is readily seen that the maximum Wigner component is achieved when $i=0$, so the corresponding multiplicity and Wigner component are $m_0 = 1$, $w(\rho_{\rm{S}})_0 = v^n$.
-The first elbow coordinates therefore can be expressed as
-\begin{equation}\label{eq:first_elb_coords}
-	(x_0, L_0) = (m_0\hspace{2pt} w(\id/3)_0,\ m_0\hspace{2pt} w(\rho_{\rm{S}})_0) = \left(\frac{1}{9^n}, v^n \right)
-\end{equation}
-
-The first elbow of the target state is located at $x'_0 = \frac{1}{9^{n'}} > x_0$, so we can use the first elbow condition,
-\begin{equation}\label{eq:first_elb_bound2}
-	\frac{L_0}{x_0} \geq \frac{L_0'}{x_0'},
-\end{equation}
-to compute analytical distillation bounds for distillation rate $R = R(\epsilon, \epsilon') \coloneqq n'/n$ in the unital fragment.
-We substitute coordinates from~\cref{eq:first_elb_coords} appropriately in~\cref{eq:first_elb_bound2} to get
-\begin{equation}
-	R \leq \frac{\ln{(3-4\epsilon)}}{\ln{(3-4\epsilon')}}.
-\end{equation}
-
-Specifically for the problem of distilling pure magic states ($\epsilon'=0$), we obtain an upper bound in the unital fragment given by
+where index $i$ runs through $0,\dots,\frac{n}{2}$, and we assume for simplicity that $n$ is even.
+The details are provided in~\cref{app:lcsu_coord_elb}.
+\ddd{[This looks like there's a typo.
+If $n$ is even then so too is $n-2i$ but then we don't get any negative values in $w_i$.
+Needs fixing.]}
+
+The largest Wigner component of $v^n$ occurs when $i=0$ and is unique. The Lorenz curve $L_{\rho|\sigma}(x)$ rises monotonically and reaches a maximum value
+\begin{equation}
+ L_\star:=L_{\rho |\sigma} (x_\star) = \sum_{i = 0}^{n/2} m_{2i} w_{2i} > 1,
+\end{equation}
+which occurs at $x=x_\star$ given by
+\begin{equation}
+x_\star = \mbox{[Fill in tidily]}.
+\end{equation}
+
+It is possible to derive bounds from the peak region of the Lorenz curves for $\rho_S(\epsilon)^{\otimes n}$ and $\rho_S(\epsilon')^{\otimes n'}$ and then impose the constraint that one never dips below the other, however it turns out that a simple constraint can be obtained by considering the first elbow of the Lorenz curves.
+This is particularly simple for $\epsilon' < \epsilon \leq 3/7$.
+\ddd{[Why??]}
+The first elbow coordinates for $\rho_S(\epsilon)^{\otimes n}$ are given by $(1/9^n, v(\epsilon)^n)$, while for $\rho_S(\epsilon')^{\otimes n'}$ the first elbow occurs at $(1/9^{n'}, v(\epsilon')^{n'})$.
+
+Finally, by requiring that the output state Lorenz curve is never above the input state Lorenz curve for the first elbow, we get
+\begin{equation}
+	R(\epsilon, \epsilon') \leq \frac{\ln{(3-4\epsilon)}}{\ln{(3-4\epsilon')}}.
+\end{equation}
+
+Specifically for the limiting case of distilling pure magic states ($\epsilon'=0$), we obtain an upper bound in the unital fragment given by
 \begin{equation}
@@
 \end{equation}
-Using the max--thaum properties of super-additivity and vanishing at free states, we obtain
+Using the max--thauma properties of super-additivity and vanishing at free states, we obtain
 \begin{align}
@@
 Both the mana and the max--thauma bounds are looser than the majorization bound we derived via the first elbow constraint as illustrated in~\cref{fig:distill_bounds}.
+However, beyond this comparison with these global bounds it is important to emphasize that the above majorization bound gives constraints on any distillation protocol that is \emph{unital}, and therefore allows for a finer analysis of magic protocols than global bounds would allow.
+
+While unital channels are quite natural, we might wonder if we obtain radically different distillation bounds if we allow biases into our protocols, or use protocols that are invariant under some residual symmetry.
+In the next section we provide relative majorization bounds in arbitrary stabilizer fragments, and in particular we shall parameterize these bounds from a thermodynamic perspective.
+Specifically, we can interpret the stabilizer state $\sigma$, defining the fragment, as a thermodynamic equilibrium state at some effective temperature and with some effective Hamiltonian.
 \begin{figure}[t]
@@
     \caption{\textbf{Distillation bounds in the unital fragment.} Distillation bounds obtained by majorisation, mana and the line $1-\epsilon$ (tightest bound of max--thauma) are plotted for $\epsilon' = 0$, up to noise level $\epsilon = 3/7$.
-    Majorisation consistently provides stricter rates than mana and max--thauma.
+    Majorisation provides stricter rates than the global mana and max--thauma bounds.
     }

### 2021-04-07 magic_paper.tex
Very basic text on lower bounds added.

@@
 
-These bounds can be interpreted in two different ways: on one hand they can be viewed as a family of upper bounds parameterized by a stabiliser state $\sigma$, on the other we can associate $\sigma$ to actual hardware limitations or to biased noise models in which it is an equilibrium state of some kind.
+These bounds can be interpreted in two different ways: 
+\begin{enumerate}
+\item As family of upper bounds parameterized by an abstract stabiliser state $\sigma$.
+\item That the state $\sigma$ corresponds to actual hardware limitations or to biased noise model in which $\sigma$ is an equilibrium state of some kind. 
+\end{enumerate}
 Without loss of generality, we can always write a stabiliser state $\sigma$ as a Gibbs state $\sigma = \gamma_\beta \coloneqq \frac{1}{\Z_\beta} e^{-\beta H}$ for some $\beta \geq 0$ and Hamiltonian $H$ as discussed in~\cref{sec:major_frag}.
+Our analysis depends on the free energy $F(\beta)$ of the state $\sigma$,
+\begin{equation}
+	F(\beta) \coloneqq \tr[H \sigma] - \beta^{-1}S(\sigma) = -\beta^{-1}\log{\Z_\beta},
+\end{equation}
+where the von Neumann entropy is $S(\sigma) \coloneqq -\tr[\sigma\log{\sigma}]$.
+Again, under interpretation (1) above this is simply an abstract entropic measure of the stabilizer state, while under interpretation (2) it corresponds to the thermodynamic free energy of the equilibrium state.
 
@@
 \end{equation}
-where the noisy Strange state is given in~\cref{eq:noisysn} and we highlight again that any magic state can be transformed to this form via Clifford operations.
-Notice that tensoring in copies of $\gamma_\beta$ does not affect the process, since the state is free.
-In the following result, all copies $n, n', n - n'$ are even with $n > n'$, and $\epsilon'=0$, but the bounds are easily generalised to odd numbers of copies and $\epsilon'$ such that $0 < \epsilon' < \epsilon$.
-Finally, we assume a range of initial noise levels, $\epsilon \leq 3/7$, so that the largest Wigner component of the 1-copy noisy magic state is negative.
-The numerical value of $3/7$ is higher than corresponding values of relevant existing distillation protocol error thresholds~\cite{cit:bravyi,cit:prakash}.
+and as before tensoring in copies of $\sigma$ does not affect the Lorenz curves of the magic states in the fragment.
 
@@
 We also write $R(\epsilon, \beta) = R(\epsilon, \epsilon'=0, \beta)$.
-The bounds depend on the free energy $F_\beta$ of state $\sigma$,
-\begin{equation}
-	F_\beta \coloneqq \tr[H \sigma] - \beta^{-1}S(\sigma) = -\beta^{-1}\log{\Z_\beta},
-\end{equation}
-where the von Neumann entropy is $S(\sigma) \coloneqq -\tr[\sigma\log{\sigma}]$.
 
@@
 \begin{equation}
-	R(\epsilon,\beta) \leq 1 + \frac{\ln{\left( 1 - \frac{4}{3}\epsilon \right)}}{\beta (E_0 - F_\beta)}.
+	R(\epsilon,\beta) \leq 1 + \frac{\ln{\left( 1 - \frac{4}{3}\epsilon \right)}}{\beta (E_0 - F(\beta))}.
 \end{equation}
@@
 \begin{equation}
-	R(\epsilon, \beta) \le 1 + \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)} - (E_2 - E_0)(\beta_{\star} - \beta)}{\beta (E_0 - F_\beta)}.
+	R(\epsilon, \beta) \le 1 + \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)} - (E_2 - E_0)(\beta_{\star} - \beta)}{\beta (E_0 - F(\beta))}.
 \end{equation}
@@
 \begin{equation}
-	R(\epsilon, \beta) \leq  1+ \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)}}{-\ln{2} + \beta (E_2 - F_\beta)}.
-\end{equation}
-In the above expressions $F_\beta$ is the effective free energy of the stabilizer state.
+	R(\epsilon, \beta) \leq  1+ \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)}}{-\ln{2} + \beta (E_2 - F(\beta))}.
+\end{equation}
+In the above expressions $F(\beta)$ is the effective free energy of the stabilizer state.
 \end{theorem}
@@
 where $\{\ket{\varphi_k}\}$ are pure, orthonormal stabiliser states.
-These pure states can be represented in terms of Generalized Paulis.
+These pure states can be represented in terms of generalized Paulis.
 Let $C$ be the unitary transforming each $|\varphi_k\>\<\varphi_k|$ to $|k\>\<k|$.
@@
 	\begin{cases}
-		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_0 - F_\beta)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F_\beta)},\ &\rm{(C1)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
-		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F_\beta)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F_\beta)},\ &\rm{(C2)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
-		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F_\beta)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F_\beta)},\ &\rm{(C2)} \rightarrow \rm{(C2)}.
+		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_0 - F(\beta))}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F(\beta))},\ &\rm{(C1)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
+		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F(\beta))}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
+		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F(\beta))}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C2)}.
 	\end{cases}
@@
 	\begin{cases}
-		\dfrac{1}{n} \dfrac{\log{\frac{u(\epsilon)v(\epsilon')}{u(\epsilon')v(\epsilon)}}}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F_\beta)},\ &\rm{(C1)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
-		\dfrac{1}{n} \dfrac{\log{\frac{v(\epsilon)v(\epsilon')}{u(\epsilon)u(\epsilon')}} - 2\beta(E_{\rm{max}} - E_0)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F_\beta)},\ &\rm{(C2)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
-		\dfrac{1}{n} \dfrac{\log{\frac{v(\epsilon')u(\epsilon')}{v(\epsilon')u(\epsilon)}}}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F_\beta)},\ &\rm{(C2)} \rightarrow \rm{(C2)},
+		\dfrac{1}{n} \dfrac{\log{\frac{u(\epsilon)v(\epsilon')}{u(\epsilon')v(\epsilon)}}}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F(\beta))},\ &\rm{(C1)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
+		\dfrac{1}{n} \dfrac{\log{\frac{v(\epsilon)v(\epsilon')}{u(\epsilon)u(\epsilon')}} - 2\beta(E_{\rm{max}} - E_0)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
+		\dfrac{1}{n} \dfrac{\log{\frac{v(\epsilon')u(\epsilon')}{v(\epsilon')u(\epsilon)}}}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C2)},
 	\end{cases}
@@
 
-\section{Lower magic bounds via majorisation}
+\subsection{Lower magic bounds via majorisation}
 \label{sec:lower_bounds}
 
-\nick{Add from notes}
+\ddd{[Initial text. To be edited.]}
+We have described how relative majorization can be used to establish upper bounds on magic distillation protocols that take into account additional physics of the system.
+Given this, one might wonder if this approach could also provide \emph{lower bounds} for distillation protocols.
+Now, in contrast to the upper bounds, it is necessary to include the symplectic constraints on the phase space into the majorization relations.
+
+  For example, the Clifford group action on a quantum system corresponds to the action of the affine symplectic group on the discrete phase space.
+Therefore, any convex mixture of Clifford unitaries will correpond to a convex mixture of these group actions.
+From the Hardy-Littlewood theorem, we know that traditional majorization is obtained from convex mixtures of arbitrary permutations.
+However this has been generalised to convex mixtures of elements of a group $G$ that acts on vectors.
+This $G$--majorization has been studied in the classical literature and a range of results are known about it.
+For example, if $G$ is a finite reflection group then the $G$--majorization pre-order is described by a finite list of conditions, just as happens for the full majorization ordering.
+One route is therefore to consider reflection sub-groups of the affine symplectic group, for which the majorization relation reduces to a finite set of conditions.
+This would therefore provide concrete lower bounds on distillation rates.
+
+  The topic of $G$--majorization has been extensively studied, but to our knowledge there hasn't been work on relative $G$--majorization.
+This would correspond to transformations that are \emph{not} unital, but still respect the symplectic structure.
+Physically, this regime would correspond to a form of thermo-majorization obtained from looking at the action of the Clifford group at a micro-canonical level, and then reducing to a small subsystem.
+While this seems like a painful thing to consider, there is motivation for this beyond the aim of constructing lower bounds for magic protocols: in the case of statistical mechanics on a phase space this is precisely the situation, albeit in the continuum limit.
+Statistical mechanics of actual systems obey Hamiltonian dynamics and so automatically respect a symplectic form.
+Therefore the pre-order of statistical mechanical states with respect to phase space dynamics preserving a Gibbs state must correspond to a symplectic thermo-majorization condition.
+Of course, technical features arise in the continuum limit when considering distributions on an unbounded phase space, but this could be remedied by either considering a compact phase space (e.g.
+for a particle on a ring) or by first studying the discrete case.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Fragments in general resource theories}
-\label{sec:general_resources}
-
-\nick{Add from notes}
-
-So far we have introduced the notion of $\sigma$--fragments for any resource theory of magic. 
-In this section we briefly generalise this concept to arbitrary resource theories and explain precisely how it connects with resource monotones. 
-The busy reader more focussed on magic may skip this section.
-
-State convertibility within a given resource theory is often a hard question to address due to intricacies of the theory structure.
-In general, the structure of a theory $\R$ is described by a pre-order $\prec_\R$ and usually resource monotones are employed to reduce this structure into a simple real number ordering.
-The subdivisions of magic theories into $\sigma$--fragments suggests a new approach towards investigating state convertibility which retains more structure of the original theory than a measure can.
-
-Monotones reduce the structure of the resource theory $\R$ to a \emph{total} order on the real numbers.
-Therefore, two states, even if incomparable in $\R$, are always mapped onto ordered real numbers.
-We now generalise this idea of a theory projection that preserves comparability between states. 
-\begin{definition}[\textbf{Covariant projection}]\label{def:covproj}
-Let $\R = (\F, \O)$ be a resource theory with pre-order $\prec_\R$. 
-Then a \emph{covariant resource projection} of $\R$ to a resource theory $\R'$ with pre-order $\prec_{\R'}$, is a pair of mappings $(\Pi_s, \Pi_o)$, where $\Pi_s$ maps quantum states in $\R$ to quantum states in $\R'$, and $\Pi_o$ maps free operations in $\R$ to free operations in $\R'$.
-Moreover, these obey
-	\begin{enumerate}
-        \item $\Pis(\rho_1) \prec_{\R'} \Pis(\rho_2)$ whenever $\rho_1 \prec_\R \rho_2$;
-        \item $\Pio(\E) = \Pio(\E_1) \circ \Pio(\E_2)$ whenever $\E = \E_1 \circ \E_2$.
-    \end{enumerate}
-We call $\R'$ a \emph{covariant fragment} of $\R$.
-\end{definition}
-
-Resource monotones can now be clearly seen as a special case of covariant resource projections.
-\begin{proposition}[\textbf{Totally ordered covariant theories}]\label{thm:monoproj}
-	Any resource monotone $\M$ of a resource theory $\R$ is a covariant projection for which $\prec_{\R'}$ is a total order. 
-	Conversely, any such covariant projection corresponds to a resource monotone $\M$. 
-\end{proposition}
-\begin{proof}
-	Consider a monotone $\M$ in the context of a general resource theory $\R = (\F, \O)$.
-	State order is covariantly preserved due to the defining property of a monotone, where the pre-order $\prec_{\R'}$ is simply the total order $\leq$ on $\mathbb{R}$.
-
-	Operational composition is covariantly preserved when we simply choose $\Pio(\E) = 1_\times$, namely the `multiplication by 1' operation on real numbers. 
-	The definition of a resource monotone then automatically implies covariance.
-
-	Conversely, given any covariant projection of $\R$ for which $\prec_{\R'}$ is a total order, we may map the totally ordered set of elements $\Pis(\rho)$ via an injective, non-decreasing function $f$ into $\mathbb{R}$.
-	Then, $\M(\rho):=f(\Pi_s(\rho))$ provides a numerical value for each $\rho$ that obeys the definition of a monotone.
-
-\end{proof}
-
-We can also view $\sigma$--fragments as an example of reducing the structure of a magic theory $\R$ to a subtheory with a tractable pre-order.
-However, states which are incomparable in $\R$ remain incomparable and conversions between states which are comparable in $\R$ may no longer be possible.
-\begin{definition}[\textbf{Contravariant projection}]\label{def:contraproj}
-	Let $\R = (\F, \O)$ be a resource theory with pre-order $\prec_\R$. 
-Then a \emph{contravariant resource projection} of $\R$ onto a resource theory $\R'$ with pre-order $\prec_{\R'}$, is a pair of mappings $(\Pi_s, \Pi_o)$, where $\Pi_s$ maps quantum states in $\R$ onto quantum states in $\R'$, and $\Pi_o$ maps free operations in $\R$ onto free operations in $\R'$.
-Moreover, these obey
-	\begin{enumerate}
-        \item $\rho_1 \prec_\R \rho_2$ whenever $\Pis(\rho_1) \prec_{\R'} \Pis(\rho_2)$;
-        \item $\E = \E_1 \circ \E_2$ whenever $\Pio(\E) = \Pio(\E_1) \circ \Pio(\E_2)$.
-    \end{enumerate}
-We call $\R'$ a \emph{contravariant fragment} of $\R$.
-\end{definition}
-The use of covariant and contravariant in~\cref{def:covproj,def:contraproj} refers to the direction of implication between the two pre-orders and operation compositions\footnote{Note that strictly these are not projections in the sense of $\Pi^2 = \Pi$, but are instead morphisms.
-Here our use of the term projection is motivated by the idea that one one generally loses information about $\R$ under the mapping.}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%\section{Fragments in general resource theories}
+%\label{sec:general_resources}
+%
+%\nick{Add from notes}
+%
+%So far we have introduced the notion of $\sigma$--fragments for any resource theory of magic. 
+%In this section we briefly generalise this concept to arbitrary resource theories and explain precisely how it connects with resource monotones. 
+%The busy reader more focussed on magic may skip this section.
+%
+%State convertibility within a given resource theory is often a hard question to address due to intricacies of the theory structure.
+%In general, the structure of a theory $\R$ is described by a pre-order $\prec_\R$ and usually resource monotones are employed to reduce this structure into a simple real number ordering.
+%The subdivisions of magic theories into $\sigma$--fragments suggests a new approach towards investigating state convertibility which retains more structure of the original theory than a measure can.
+%
+%Monotones reduce the structure of the resource theory $\R$ to a \emph{total} order on the real numbers.
+%Therefore, two states, even if incomparable in $\R$, are always mapped onto ordered real numbers.
+%We now generalise this idea of a theory projection that preserves comparability between states. 
+%\begin{definition}[\textbf{Covariant projection}]\label{def:covproj}
+%Let $\R = (\F, \O)$ be a resource theory with pre-order $\prec_\R$. 
+%Then a \emph{covariant resource projection} of $\R$ to a resource theory $\R'$ with pre-order $\prec_{\R'}$, is a pair of mappings $(\Pi_s, \Pi_o)$, where $\Pi_s$ maps quantum states in $\R$ to quantum states in $\R'$, and $\Pi_o$ maps free operations in $\R$ to free operations in $\R'$.
+%Moreover, these obey
+%	\begin{enumerate}
+%        \item $\Pis(\rho_1) \prec_{\R'} \Pis(\rho_2)$ whenever $\rho_1 \prec_\R \rho_2$;
+%        \item $\Pio(\E) = \Pio(\E_1) \circ \Pio(\E_2)$ whenever $\E = \E_1 \circ \E_2$.
+%    \end{enumerate}
+%We call $\R'$ a \emph{covariant fragment} of $\R$.
+%\end{definition}
+%
+%Resource monotones can now be clearly seen as a special case of covariant resource projections.
+%\begin{proposition}[\textbf{Totally ordered covariant theories}]\label{thm:monoproj}
+%	Any resource monotone $\M$ of a resource theory $\R$ is a covariant projection for which $\prec_{\R'}$ is a total order. 
+%	Conversely, any such covariant projection corresponds to a resource monotone $\M$. 
+%\end{proposition}
+%\begin{proof}
+%	Consider a monotone $\M$ in the context of a general resource theory $\R = (\F, \O)$.
+%	State order is covariantly preserved due to the defining property of a monotone, where the pre-order $\prec_{\R'}$ is simply the total order $\leq$ on $\mathbb{R}$. 
+%	
+%	Operational composition is covariantly preserved when we simply choose $\Pio(\E) = 1_\times$, namely the `multiplication by 1' operation on real numbers. 
+%	The definition of a resource monotone then automatically implies covariance.
+%	
+%	Conversely, given any covariant projection of $\R$ for which $\prec_{\R'}$ is a total order, we may map the totally ordered set of elements $\Pis(\rho)$ via an injective, non-decreasing function $f$ into $\mathbb{R}$.
+%	Then, $\M(\rho):=f(\Pi_s(\rho))$ provides a numerical value for each $\rho$ that obeys the definition of a monotone.
+%	
+%\end{proof}
+%
+%We can also view $\sigma$--fragments as an example of reducing the structure of a magic theory $\R$ to a subtheory with a tractable pre-order.
+%However, states which are incomparable in $\R$ remain incomparable and conversions between states which are comparable in $\R$ may no longer be possible.
+%\begin{definition}[\textbf{Contravariant projection}]\label{def:contraproj}
+%	Let $\R = (\F, \O)$ be a resource theory with pre-order $\prec_\R$. 
+%Then a \emph{contravariant resource projection} of $\R$ onto a resource theory $\R'$ with pre-order $\prec_{\R'}$, is a pair of mappings $(\Pi_s, \Pi_o)$, where $\Pi_s$ maps quantum states in $\R$ onto quantum states in $\R'$, and $\Pi_o$ maps free operations in $\R$ onto free operations in $\R'$.
+%Moreover, these obey
+%	\begin{enumerate}
+%        \item $\rho_1 \prec_\R \rho_2$ whenever $\Pis(\rho_1) \prec_{\R'} \Pis(\rho_2)$;
+%        \item $\E = \E_1 \circ \E_2$ whenever $\Pio(\E) = \Pio(\E_1) \circ \Pio(\E_2)$.
+%    \end{enumerate}
+%We call $\R'$ a \emph{contravariant fragment} of $\R$.
+%\end{definition}
+%The use of covariant and contravariant in~\cref{def:covproj,def:contraproj} refers to the direction of implication between the two pre-orders and operation compositions\footnote{Note that strictly these are not projections in the sense of $\Pi^2 = \Pi$, but are instead morphisms.
+%Here our use of the term projection is motivated by the idea that one one generally loses information about $\R$ under the mapping.}.
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2021-04-09 magic_paper.tex
minor changes

--- 2021-04-05 magic_paper.tex
@@
 % Proofs in App. A
-% Eq. numbering in last line always
 % Sec: App. D
@@
 % Figs consistency (esp. figs 3,4,5 and 1,6) + Figure 0 ?
+% Eq. numbering in last line always
+% British vs US english
 % Spacing (fig positioning, sections, paragraphs, QED symbols)
@@
 
-There is a natural generalisation, which we call \emph{relative majorization} (also known as $d$--majorization~\cite{Veinott_1971}, or in the context of thermodynamics, thermo-majorization)\footnote{The general form of relative majorization is defined as $(\p,\r) \succ (\q, \r')$ iff there is a stochastic map $A$ such that $A\p = \q$ and $A\r = \r'$.}.
+There is a natural generalisation, which we call \emph{relative majorization} (also known as $\bmd$--majorization~\cite{Veinott_1971}, or in the context of thermodynamics, thermo-majorization)\footnote{The general form of relative majorization is defined as $(\p,\r) \succ (\q, \r')$ iff there is a stochastic map $A$ such that $A\r = \r'$ and $A\p = \q$.
+We retrieve $\bmd$--majorization when $\r = \r'$.}.
 For a fixed probability distribution $\r = (r_1, \dots, r_n)$ with positive components, we define majorization relative to $\r$ as follows:
@@
 Phrased more abstractly, the relative majorization pre-order corresponds to the standard ordering of concave, piece-wise linear functions passing through $(0,0)$ and $(1,1)$.
-We note that another neat geometric formulation of relative majorization exists, stating that the $L_1$-norm angle between $\w_1$ and $\r$ is greater than or equal to the $L_1$-norm angle between $\w_2$ and $\r$ (see \ddd{[CITE]}\nick{haven't seen this before}\ddd{[`Orthogonality and Disjointness in Spaces of Measures'', by Paul Busch.]} for details).
+We note that another neat geometric formulation of relative majorization exists, stating that the $L_1$-norm angle between $\w_1$ and $\r$ is greater than or equal to the $L_1$-norm angle between $\w_2$ and $\r$ (see~\cite{Busch_1998} for details).
 
@@
 
-In this section we apply majorization to magic state distillation within a simple fragment, namely the unital fragment.
-This corresponds to considering distillation protocols where one is restricted to free operations that are \emph{unital operations}, meaning that $\E(\I/d) = \I/d$.
+In this section, we apply majorization to magic state distillation within a simple fragment, namely the unital fragment.
+This encompasses distillation protocols where one is restricted to \emph{unital operations}, meaning that $\E(\I/d) = \I/d$ for all free $\E$.
 This is a particularly nice set of operations, which include for example all Weyl-covariant channels \ddd{[CITE]}.
 To make things concrete we shall consider qutrit magic states ($d=3$).
-This is convenient since this system doesn't have the subtleties of the qubit case, and admits non-trivial structure (e.g.
-Hamiltonians with two different energy gaps) while being sufficiently simple to analyse in detail.
+This is convenient since qutrit systems don't have the subtleties of the qubit case, and admit non-trivial structure (e.g.
+Hamiltonians with two different energy gaps), while being sufficiently simple to analyse in detail.
 

### 2021-04-12 magic_paper.tex
Cleaned up Sec.IV

@@
 namely those operations that leave the state $\sigma \in \F$ invariant.
+\nick{We discussed that the only free state in $\R_\sigma$ is $\sigma$}
 \end{definition}
@@
 The form of this requires that $\r$ has no zero components, which we shall assume without loss of generality as in any physical situation the rank of a quantum state is not an operationally meaningful quantity.
+We also stress that the curve contains non-differentiable points at locations where $\widetilde{\bmw}$ changes value, which we call \emph{elbows}.
 
@@
 See Figure \ref{fig:lcs} for examples of non-monotonic Lorenz curves for quasi-distributions.
-The non-differentiable points on the curve occur at the locations where $\widetilde{\bmw}$ changes value and are called \emph{elbows}.
 Within quantum theory, the breaking of this barrier is associated with the degree of non-classicality.
@@
 Note, however, that unlike any monotone, this is not a single numerical constraint, but a \emph{family} of constraints.
-Indeed, for $n$ copies of a $d$--dimensional system the number of terms in $W_{\rho}$ is $d^{2n}$, so the Lorenz curve condition corresponds to \emph{exponentially} many constraints, of which there are as many independent constraints as there are elbows in the Lorenz curve of the target state as shown in~\cref{thm:elbows} in~\cref{app:frag}.
+Indeed, for $n$ copies of a $d$--dimensional system the number of terms in $W_{\rho}$ is $d^{2n}$, so the Lorenz curve condition corresponds to \emph{exponentially} many constraints, of which there are as many independent constraints as there are elbows in the Lorenz curve of the target state, which is proved in~\cref{thm:elbows} in~\cref{app:frag}.
 In principle, any one location $x$ provides a valid constraint leading to some upper distillation bound and optimising over the location provides the strictest bound.
@@
 This encompasses distillation protocols where one is restricted to \emph{unital operations}, meaning that $\E(\I/d) = \I/d$ for all free $\E$.
-This is a particularly nice set of operations, which include for example all Weyl-covariant channels \ddd{[CITE]}.
-To make things concrete we shall consider qutrit magic states ($d=3$).
-This is convenient since qutrit systems don't have the subtleties of the qubit case, and admit non-trivial structure (e.g.
-Hamiltonians with two different energy gaps), while being sufficiently simple to analyse in detail.
+This is a particularly powerful set of operations, which for example include all Weyl-covariant channels~\cite{cit:gross3}.
+To make things concrete, we shall consider qutrit magic states ($d=3$) as qutrit systems don't exhibit the subtleties and peculirities of qubit systems, while they admit non-trivial structure (e.g.
+Hamiltonians with two different energy gaps) and still are sufficiently simple to analyse in detail.
 
@@
 in the computational basis.
-The reason for this particular choice is that the Wigner distribution is very simple.
-Specifically $W_S(\x)$ has a single negative value of $-1/3$ at $\x =(0,0)$ and the value $1/6$ at all other points.
-We also define the $\epsilon$--noisy Strange state as
+This qutrit magic state is exceptionally symmetric and simple which benefits our analysis.
+Its distribution $W_S(\x)$ has a single negative value of $-1/3$ at $\x =(0,0)$ and the positive value $1/6$ at all other points.
+We can define the $\epsilon$--noisy Strange state as
 \begin{equation}\label{eq:noisysn}
@@
 where $\epsilon$ is the depolarization noise parameter.
-Moreover, any magic state $\rho$ can be processed via Clifford operations~\cite{cit:prakash,cit:prakash2} and put into this canonical form for some $\epsilon \ge 0$.
-
-We now consider the task of purifying $n$ copies of a noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ as given in~\cref{eq:noisysn} into a smaller number of copies $n'$ of a less noisy strange state $\rho_{\rm{S}}(\epsilon')^{\otimes n'}$, with $\epsilon' < \epsilon$ and $n' \leq n$.
-It turns out that our majorization relations are simplest to express when the number of systems remains constant.
-To do this is simply tensor in $n'-n$ auxiliary free states, which do not affect the distillation analysis.
-Since we work in the unital fragment it makes sense to choose these free states to be the maximally mixed state, since the Lorenz curves are unaffected.
-More generally, it is easy to show that
-\begin{equation}
-L_{\rho |\sigma} (x) = L_{\rho\otimes \sigma |\sigma}(x),
-\end{equation}
-for any full-rank $\sigma \in \F$. Therefore, we can consider the transformation
+Moreover, utilising the symmetries of the Strange state allow for any magic state $\rho$ to be processed via Clifford operations~\cite{cit:prakash,cit:prakash2} and put into this canonical form for some $\epsilon \ge 0$.
+
+The Wigner distribution of the single-copy, $\epsilon$--noisy Strange state  is given by
+\begin{equation}
+	\W[\bmx]{\rho_{\rm{S}}(\epsilon)} = (1-\epsilon)\W[\bmx]{\ketbra{\rm{S}}} + \epsilon\W[\bmx]{\frac{1}{3}\id}.
+\end{equation}
+Since the Wigner distribution $W_{\I/3}(x)$ is the uniform probability distribution over the phase space, we get that $W_{\rho_S(\epsilon) } (\x)$ has a single negative component
+\begin{equation}
+	- v(\epsilon) \coloneqq - \left( \frac{1}{3} -\frac{4}{9}\epsilon \right)
+\end{equation} 
+located at the origin $\bmx = \bmo$ and positive components
+\begin{equation}
+	u(\epsilon) \coloneqq \frac{1}{6} -\frac{1}{18}\epsilon
+\end{equation}
+at the 8 phase space points $\x \ne (0,0)$. We assume that $\epsilon < 3/4$ to ensure the presence of negativity in the Wigner distribution.
+
+We now consider the task of purifying $n$ copies of a noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ as given in~\cref{eq:noisysn} into a smaller number of copies $n'$ of a less noisy Strange state $\rho_{\rm{S}}(\epsilon')^{\otimes n'}$, with $\epsilon' < \epsilon$ and $n' \leq n$.
+Since we work in the unital fragment, the only free state is the maximally mixed state, and we choose to tensor in $n'-n$ auxiliary copies of it to the output.
+This highlights that we are working in the unital fragment, while it does not affect neither the distillation process nor our analysis, since the Lorenz curves remain unaffected.
+More generally, it is easy to see that
+\begin{equation}
+	L_{\rho |\sigma} (x) = L_{\rho \otimes \sigma |\sigma}(x),
+\end{equation}
+for any full-rank $\sigma \in \F$. Therefore, we consider the transformation
 \begin{equation}\label{eq:sudist}
@@
 \end{equation}
-and compare the Lorenz curves for both the input and output states to bound $R(\epsilon, \epsilon') \coloneqq n'/n$, the rate of this interconversion within the fragment.
-
-The Wigner distribution of the single-copy, $\epsilon$--noisy Strange state  is given by
-\begin{equation}
-	\W[\bmx]{\rho_{\rm{S}}(\epsilon)} = (1-\epsilon)\W[\bmx]{\ketbra{\rm{S}}} + \epsilon\W[\bmx]{\frac{1}{3}\id}.
-\end{equation}
-Since the Wigner distribution $W_{\I/3}(x)$ is the uniform probability distribution over the phase space, we get that $W_{\rho_S(\epsilon) } (\x)$ has positive components
-\begin{equation}
-	u(\epsilon) \coloneqq \frac{1}{6} -\frac{1}{18}\epsilon
-\end{equation}
-at the 8 phase space points $\x  \ne (0,0)$ and a single negative component
-\begin{equation}
-	- v(\epsilon) \coloneqq - \left( \frac{1}{3} -\frac{4}{9}\epsilon \right)
-\end{equation}
-located at the origin $\bmx = \bmo$. We assume that $\epsilon < 3/4$ to ensure the presence of negativity in the Wigner distribution.
+and compare the Lorenz curves for the input and output states to bound $R(\epsilon, \epsilon') \coloneqq n'/n$, the rate of this interconversion within the fragment.
 
@@
 \end{equation}
-so the probleme of ordering the rescaled distribution is equivalent to ordering $\W{\rho_{\rm{S}}}$.
+so the problem of ordering the rescaled distribution, which is required for the evaluation of the Lorenz curves, is equivalent to ordering $\W{\rho_{\rm{S}}}$.
 The Wigner distribution of $n$ copies of the state is obtained by the $n$-fold product of the single copy distribution, and the Lorenz curve $L_{\rho|\sigma}(x)$ for $\rho = \rho_S(\epsilon)^{\otimes n}$ and $\sigma = (\I/3)^{\otimes n}$ is readily computed for any $n$ and $\epsilon$, and the full details are provided in~\cref{app:lcsu_technical}.
-The non-trivial element that arises for quasi-distributions is that the product of negative components generates a positive number, and therefore the ordering of the components of $W_{\rho |\sigma}(x)$ depends on whether $-v(\epsilon)$ appears to an even or odd power.
+We highlight that the non-trivial element that arises for quasi-distributions is that the product of negative components can generate a positive $n$-fold component, so the ordering of the components of $W_{\rho |\sigma}(x)$ depends on whether $-v(\epsilon)$ appears to an even or odd power in the expression below.
 
@@
 \begin{align}
-	m_i &= 8^{2i}\binom{n}{2i}, \\
-	w_i &= u^{2i}(-v)^{n-2i},
-\end{align}
-where index $i$ runs through $0,\dots,\frac{n}{2}$, and we assume for simplicity that $n$ is even.
-The details are provided in~\cref{app:lcsu_coord_elb}.
-\ddd{[This looks like there's a typo.
-If $n$ is even then so too is $n-2i$ but then we don't get any negative values in $w_i$.
-Needs fixing.]}
-
-The largest Wigner component of $v^n$ occurs when $i=0$ and is unique. The Lorenz curve $L_{\rho|\sigma}(x)$ rises monotonically and reaches a maximum value
-\begin{equation}
- L_\star:=L_{\rho |\sigma} (x_\star) = \sum_{i = 0}^{n/2} m_{2i} w_{2i} > 1,
-\end{equation}
+	m_i &= 8^{i}\binom{n}{i}, \\
+	w_i &= u^{i}(-v)^{n-i},
+\end{align}
+where index $i$ runs through $0, \dots, n$, and we assume for simplicity of exposition that $n$ is even and the noise level is not high, $\epsilon \leq 3/7$, so that $v \geq u$.
+The details of this scenario, along with the other possible scenarios that occur depending on the parity of the number of copies and the noise level, are provided in~\cref{app:lcsu_coord_elb}.
+
+The Lorenz curve $L_{\rho|\sigma}(x)$ rises monotonically and reaches a maximum value
+\begin{align}\label{eq:lcsu_max}
+	L_\star &\coloneqq L_{\rho |\sigma} (x_\star) = \sum_{i = 0}^{n/2} m_{2i} w_{2i} \nonumber\\
+	&= \frac{1}{2} + \frac{1}{2}\left(\frac{15 - 8\epsilon}{9}\right)^n > 1,
+\end{align}
 which occurs at $x=x_\star$ given by
 \begin{equation}
-x_\star = \mbox{[Fill in tidily]}.
-\end{equation}
-
-It is possible to derive bounds from the peak region of the Lorenz curves for $\rho_S(\epsilon)^{\otimes n}$ and $\rho_S(\epsilon')^{\otimes n'}$ and then impose the constraint that one never dips below the other, however it turns out that a simple constraint can be obtained by considering the first elbow of the Lorenz curves.
-This is particularly simple for $\epsilon' < \epsilon \leq 3/7$.
-\ddd{[Why??]}
-The first elbow coordinates for $\rho_S(\epsilon)^{\otimes n}$ are given by $(1/9^n, v(\epsilon)^n)$, while for $\rho_S(\epsilon')^{\otimes n'}$ the first elbow occurs at $(1/9^{n'}, v(\epsilon')^{n'})$.
-
-Finally, by requiring that the output state Lorenz curve is never above the input state Lorenz curve for the first elbow, we get
+	x_\star = \frac{1}{2} + \frac{1}{2}\left(\frac{7}{9}\right)^n.
+\end{equation}
+
+It is possible to derive distillation bounds from any location of the Lorenz curve, including the region around the peak, by imposing the constraint that the Lorenz curve of the input state never dips below the curve of the output.
+However, it turns out that a simple and sufficiently non-trivial constraint can be obtained by considering the first elbow of the Lorenz curves. 
+The largest Wigner component of occurs for $i=0$ and is unique, so the first elbow coordinates for $\rho_S(\epsilon)^{\otimes n}$ are given by $(1/9^n, v(\epsilon)^n)$, while for $\rho_S(\epsilon')^{\otimes n'}$ the first elbow occurs at $(1/9^{n'}, v(\epsilon')^{n'})$.
+
+The first elbow constraint involves a simple interpolation, done in~\cref{app:elb_constraints}, in order to find the coordinates of the point which is vertically aligned with the first elbow of the input state, leading to the constraint
 \begin{equation}
@@
 Both the mana and the max--thauma bounds are looser than the majorization bound we derived via the first elbow constraint as illustrated in~\cref{fig:distill_bounds}.
-However, beyond this comparison with these global bounds it is important to emphasize that the above majorization bound gives constraints on any distillation protocol that is \emph{unital}, and therefore allows for a finer analysis of magic protocols than global bounds would allow.
-
-While unital channels are quite natural, we might wonder if we obtain radically different distillation bounds if we allow biases into our protocols, or use protocols that are invariant under some residual symmetry.
+However, beyond this comparison with these global bounds it is important to emphasize that the above majorization bound gives constraints on any distillation protocol that is \emph{unital}, and therefore allows for a finer analysis of magic distillation protocols than global bounds would allow.
+\nick{this is a bit repetitive and vague, can you clarify?}
+
+While unital channels are quite natural, we might wonder how different distillation bounds can be if we allow biases into our protocols, or use protocols that are invariant under some residual symmetry.
 In the next section we provide relative majorization bounds in arbitrary stabilizer fragments, and in particular we shall parameterize these bounds from a thermodynamic perspective.
-Specifically, we can interpret the stabilizer state $\sigma$, defining the fragment, as a thermodynamic equilibrium state at some effective temperature and with some effective Hamiltonian.
+Specifically, we can interpret the stabilizer state $\sigma$, which defines the fragment, as a thermodynamic equilibrium state at some effective temperature and with some effective Hamiltonian.
 \begin{figure}[t]

### 2021-04-12 appendix.tex
Cleaned up Sec.IV
More tidying of stabilizer fragment statement+proof

@@
 \subsection{First and last elbow conditions}
-
+\label{app:elb_constraints}
 Here we prove the majorization constraints that arise by considering the first and last elbow of the initial stata only.
@@
 	\end{align*}
+
+\nick{LAST ELBOW BOUND}
+
+To find the coordinates of the \textbf{last} elbow $(x_E, L_E)$, where $E$ is the number of elbows, we need to evaluate the minimum rescaled component,
+\begin{align}
+	&\bmw(\rho_{\rm{S}} | \sigma)_{\rm{min}} \coloneqq (3\Z)^{n}\times \nonumber\\
+	&\min\limits_{i,j,k}\Big\{ (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \label{eq:min_slope}
+\end{align}
+where $0 \leq i,j,k \leq n$ and $\alpha \coloneqq i+j+k \leq n$.
+Notice that for $0 \leq \epsilon \leq 3/7$, we have $v \geq u$. 
+We need the sum $\alpha = i+j+k$ to be odd for the expression to be negative.
+
+Given an odd value for the sum $\alpha$, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_0}$ is fixed (and negative), so the expression is minimised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
+Hence, we have
+\begin{align}
+	&\bmw(\rho_{\rm{S}} | \sigma)_{\rm{min}} = \nonumber\\
+	&-(3\Z)^{n} v^n e^{n\beta E_0}\max\limits_{\substack{\alpha = 1,3, \\ \dots,n-1}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}.
+\end{align}
+If the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than $1$ then the minimum occurs at $\alpha=1$, otherwise it occurs at $\alpha = n-1$.
+
+The minimum rescaled component can then be expressed as
+\begin{equation}
+\bmw(\rho_{\rm{S}} | \sigma)_{\rm{min}} =
+	\begin{cases}
+		-(3\Z)^{n} v^{n-1} u e^{\beta [(n-1)E_0 + E_{\rm{max}}]}, &\epsilon \leq \epsilon_{\star},\ \hspace{3pt}\rm{(C1)}	\\
+		-(3\Z)^{n} v u^{n-1} e^{\beta [E_0 + (n-1)E_{\rm{max}}]}, &\epsilon > \epsilon_{\star}.\ \hspace{5pt}\rm{(C2)} 
+	\end{cases}
+\end{equation}
+Case $\rm{(C1)}$ can correspond to $(i,j,k) = (1,0,0)$ if $E_{\rm{max}} = E_0$, when the multiplicity is $m_{100} = 2n$ and the corresponding Wigner components are $\bmw(\rho_{\rm{S}})_{100}, \bmw(\sigma)_{100}$ or it can correspond to $(i,j,k) = (0,1,0)$ ($(i,j,k) = (0,0,1)$), if $E_{\rm{max}} = E_1$ ($E_{\rm{max}} = E_2$), when the multiplicity is $m_{010} = 3n$ ($m_{001} = 3n$) and the corresponding Wigner components are $\bmw(\rho_{\rm{S}})_{010}, \bmw(\sigma)_{010}$ ($\bmw(\rho_{\rm{S}})_{001}, \bmw(\sigma)_{001}$).
+Case $\rm{(C2)}$ corresponds to $(i,j,k) = (0,n-1,0)$ ($(i,j,k) = (0,0,n-1)$)
+if we have $E_{\rm{max}} = E_1$ ($E_{\rm{max}} = E_2$), when the multiplicity is $m_{0,n-1,0} = 3^{n-1}n$ ($m_{0,0,n-1} = 3^{n-1}n$) and the corresponding Wigner components are $\bmw(\rho_{\rm{S}})_{0,n-1,0}, \bmw(\sigma)_{0,n-1,0}$ ($\bmw(\rho_{\rm{S}})_{0,0,n-1}, \bmw(\sigma)_{0,0,n-1}$).
+
+The last elbow coordinates can finally be derived by sutracting the appropriate rescaled component from 1, $(x_E, L_E) =$
+\begin{equation}\label{eq:last_elb_coords}
+	\begin{cases}
+		&\left( 1-\dfrac{2n}{(3\Z_\beta)^n}e^{-\beta [(n-1)E_0 + E_{\rm{max}}]},\ 1 + 2n v^{n-1} u \right), \vspace{5pt}\\
+		&\hspace{5pt} \text{if } E_{\rm{max}} = E_0, \hspace{51pt}\rm{(C1a)} \vspace{10pt}\\
+		&\left( 1-\dfrac{3n}{(3\Z_\beta)^n}e^{-\beta [(n-1)E_0 + E_{\rm{max}}]},\ 1 + 3n v^{n-1} u \right), \vspace{5pt}\\
+		&\hspace{5pt} \text{if } E_{\rm{max}} > E_0, \epsilon \leq \epsilon_{\star}, \hspace{20pt}\rm{(C1b)} \vspace{10pt}\\
+		&\left( 1-\dfrac{n}{3\Z_\beta^n}e^{-\beta [E_0 + (n-1)E_{\rm{max}}]},\ 1 + 3^{n-1}n v u^{n-1} \right), \vspace{5pt}\\
+		&\hspace{5pt} \text{if } E_{\rm{max}} > E_0, \epsilon \geq \epsilon_{\star}. \hspace{22pt}\rm{(C2)}
+	\end{cases}
+\end{equation}
+
+Assuming that $E_{\rm{max}} > E_0$ for clarity, we have the same three scenarios as in the case of the first elbow bound:
+\begin{enumerate}
+	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $\beta < \beta_{\star}$ and $\epsilon' < \epsilon  \leq \epsilon_{\star}$.
+	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $\beta < \beta_{\star}$ and $\epsilon' \leq \epsilon_{\star} < \epsilon$.
+	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $\beta < \beta_{\star}$ and $\epsilon_{\star} \leq \epsilon' < \epsilon$ or $\beta \geq \beta_{\star}$.
+\end{enumerate}
+Now the last elbow condition on Lorenz curves can be derived by simple interpolation, giving the condition
+\begin{equation}
+	L_E \geq 1 + \frac{1-x_E}{1-x_E'} (L_E' - 1),
+\end{equation}
+provided that the last elbow location is closer to 1 for the initial state than the target state, which is always true.
+
+The last elbow bound then can be rephrased in terms of the first elbow bound as $R_{\rm{last-elb}} - R_{\rm{first-elb}} = $
+\begin{equation}\label{eq:last_elb_coords}
+	\begin{cases}
+		\dfrac{1}{n} \dfrac{\log{\frac{u(\epsilon)v(\epsilon')}{u(\epsilon')v(\epsilon)}}}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F(\beta))},\ &\rm{(C1)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
+		\dfrac{1}{n} \dfrac{\log{\frac{v(\epsilon)v(\epsilon')}{u(\epsilon)u(\epsilon')}} - 2\beta(E_{\rm{max}} - E_0)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
+		\dfrac{1}{n} \dfrac{\log{\frac{v(\epsilon')u(\epsilon')}{v(\epsilon')u(\epsilon)}}}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C2)},
+	\end{cases}
+\end{equation}
+
+Note that the last elbow bounds have a dependence on $n$, which interestingly is due to $n$ being even.
+Had we considered \textbf{odd} number of copies $n$, then the first elbow bound would depend on $n$ and the last elbow bound would not.
+This, along with the unital fragment analysis, makes me think that calculating the bounds again for odd $n$ or $\epsilon > 3/7$ would reveal nice symmetries of the analysis, but it's probably not worth the time, so including last elbow analysis properly feels incomplete.
+
+Determining the sign of the difference between the last and first elbow bounds tells us which bound is better.
+The term $\log{\frac{u(\epsilon)v(\epsilon')}{u(\epsilon')v(\epsilon)}}$ is always positive for $\epsilon > \epsilon'$, therefore the last elbow bound, compared to the first elbow bound, is always \textbf{worse} in the first scenario and always \textbf{better} in the third scenario (remember, this is the yellow-ish right part of~\cref{fig:rate_contour}).
+
+In the second scenario ($\rm{(C2)} \rightarrow \rm{(C1)}$), the expression looks very weird to me, seems like the difference tends to $-\infty$ as $E_{\rm{max}} \rightarrow \infty$.
+I am a bit stuck with this expression and I am not sure it's worth putting more time in it.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-04-12 appendix.tex
minor changes

--- 2021-04-01 appendix.tex
@@
 \end{align}
-The first inequality follows from Theorem 1 of~\cite{cit:mirsky} for the trace of complex matrices, while the second is the triangle inequality.
+The first inequality follows from Theorem 1 of~\cite{cit:mirsky} for the trace of complex matrices, while the second is the Cauchy-Schwarz inequality.
 \end{proof}
@@
 \begin{proof}
-	Proof of all properties can be found in Wang \textit{et al.}~\cite{Wang_2019} except for property (iii) which is a direct consequence of the definition of $\W{\E}$ and the corresponding property (iii) in~\cref{thm:wstate}.
+	Proof of all properties are provided by Wang \textit{et al.}~\cite{Wang_2019} except for property (iii) which is a direct consequence of the definition of $\W{\E}$ and the corresponding property (iii) in~\cref{thm:wstate}.
 \end{proof}

### 2021-04-12 magic_paper.tex

@@
 \item As family of upper bounds parameterized by an abstract stabiliser state $\sigma$.
-\item That the state $\sigma$ corresponds to actual hardware limitations or to biased noise model in which $\sigma$ is an equilibrium state of some kind. 
+\item The state $\sigma$ corresponds to actual hardware limitations or to biased noise model in which $\sigma$ is an equilibrium state of some kind. 
 \end{enumerate}
-Without loss of generality, we can always write a stabiliser state $\sigma$ as a Gibbs state $\sigma = \gamma_\beta \coloneqq \frac{1}{\Z_\beta} e^{-\beta H}$ for some $\beta \geq 0$ and Hamiltonian $H$ as discussed in~\cref{sec:major_frag}.
-Our analysis depends on the free energy $F(\beta)$ of the state $\sigma$,
-\begin{equation}
-	F(\beta) \coloneqq \tr[H \sigma] - \beta^{-1}S(\sigma) = -\beta^{-1}\log{\Z_\beta},
-\end{equation}
-where the von Neumann entropy is $S(\sigma) \coloneqq -\tr[\sigma\log{\sigma}]$.
-Again, under interpretation (1) above this is simply an abstract entropic measure of the stabilizer state, while under interpretation (2) it corresponds to the thermodynamic free energy of the equilibrium state.
+Without loss of generality, we can always write a full-rank stabiliser state $\sigma$ in the form $\sigma =  \frac{1}{\Z_\beta} e^{-\beta H}$ for some $\beta \geq 0$ and effective Hamiltonian $H$.
+Our results will also depend on the free energy $F(\beta)$ of the state $\sigma$, which is defined by
+\begin{equation}
+	F(\beta) \coloneqq \tr[H \sigma] - \beta^{-1}S(\sigma) = -\beta^{-1}\log{\Z_\beta}.
+\end{equation}
+Here $S(\sigma)$ is the von Neumann entropy $S(\sigma) \coloneqq -\tr[\sigma\log{\sigma}]$.
+Again, under interpretation (1) above this is an abstract entropic measure of the stabilizer state, while under interpretation (2) it corresponds to the thermodynamic free energy of the equilibrium state.
 
@@
 Given this context, we now provide the following result on bounding the distillation rate $R = R(\epsilon, \epsilon', \beta) \coloneqq \frac{n'}{n}$ of the process in~\cref{eq:stdist}.
-\nick{I think we should denote distillation rates by $R$ and our distillation bound by $R(\epsilon, \epsilon', \beta)$, since the bound is what really depends on $\epsilon, \epsilon', \beta$.}
-We also write $R(\epsilon, \beta) = R(\epsilon, \epsilon'=0, \beta)$.
+We shall write $R(\epsilon, \beta) = R(\epsilon, \epsilon'=0, \beta)$ for the limiting case of distilling a pure magic state.
 
@@
     \centering
-    \includegraphics[scale=0.55]{figs/rate_scatter.pdf}
-    \caption{\textbf{Bounds on magic distillation rates $R(\epsilon, \beta)$ within arbitrary stabiliser fragments.}
+    \includegraphics[scale=0.4]{figs/rate_scatter.pdf}
+    \caption{\textbf{Magic distillation bounds within arbitrary stabiliser fragments.}
+  Shown is a contour plot of  $R(\epsilon, \beta)$ where $\beta$ is an effective inverse temperature and $\epsilon$ is the depolarisation error for the magic state.
+The relevant data from the spectrum of the qutrit operator $H$ enters in via $\epsilon_\star(\beta)$ and $\beta_\star$.
 The vertical dashed line is the `Landauer-like' temperature threshold $\beta_\star$ and the diagonal dashed curve corresponds to the noise threshold $\epsilon_\star (\beta)$ at every $\beta \leq \beta_\star$.
@@
 \begin{theorem}\label{thm:stab_bounds}
-	Let $\sigma$ be any qutrit stabiliser state, and write the state as $\sigma = \frac{1}{\Z} e^{-\beta H}$ with $H$ having eigenvalues $E_0 \le E_1 \le E_2$, and where $\beta$ is an effective inverse temperature for the state.
+	Given any theory of magic $\R = (\F, \O)$.
+Let $\sigma$ be any qutrit stabiliser state, and write the state as $\sigma = \frac{1}{\Z} e^{-\beta H}$ with $H$ having eigenvalues $E_0, E_1, E_2$, and where $\beta$ is an effective inverse temperature for the state.
 We define $\beta_\star = (1/kT_\star)$ through the relation
 \begin{equation}
-	E_2 - E_0 =: kT_\star \ln{2}
-\end{equation}
-and for $\beta \leq \beta_\star$, and define a threshold noise level
-\begin{equation}
-	\epsilon_{\star}(\beta) \coloneqq 3 - \dfrac{18}{8-e^{(E_2 - E_0)\beta}}.
+	E_{\rm max} - E_s =: kT_\star \ln 2,
+\end{equation}
+where $E_{\rm max} = \max\{E_k\}$ and $E_s$ is the eigenvalue of the eigenstate that overlaps the negative component of $\rho_S(\epsilon)$.  For $\beta \leq \beta_\star$ define a threshold noise level
+\begin{equation}
+	\epsilon_{\star}(\beta) \coloneqq 3 - \dfrac{18}{8-e^{(E_{\rm max} - E_s)\beta}}.
 \end{equation}
@@
 \begin{equation}
-	R(\epsilon,\beta) \leq 1 + \frac{\ln{\left( 1 - \frac{4}{3}\epsilon \right)}}{\beta (E_0 - F(\beta))}.
+	R(\epsilon,\beta) \leq 1 + \frac{\ln{\left( 1 - \frac{4}{3}\epsilon \right)}}{\beta (E_s - F(\beta))}.
 \end{equation}
@@
 \begin{equation}
-	R(\epsilon, \beta) \le 1 + \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)} - (E_2 - E_0)(\beta_{\star} - \beta)}{\beta (E_0 - F(\beta))}.
+	R(\epsilon, \beta) \le 1 + \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)} - (E_{\rm max} - E_s)(\beta_{\star} - \beta)}{\beta (E_s - F(\beta))}.
 \end{equation}
@@
 \begin{equation}
-	R(\epsilon, \beta) \leq  1+ \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)}}{-\ln{2} + \beta (E_2 - F(\beta))}.
+	R(\epsilon, \beta) \leq  1+ \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)}}{-\ln{2} + \beta (E_{\rm max} - F(\beta))}.
 \end{equation}
@@
 Specifically, the existing bounds follow by considering the dominant terms in the rescaled Wigner distribution and do not, for example, take into account the Lorenz curve's peak structure. 
-Finally, it is striking that we obtain a Landauer-like condition with a characteristic temperature $kT_\star \ln 2 = E_2 - E_0$, where $kT_\star = \beta_\star^{-1}$. 
+Finally, it is notable that we obtain a Landauer-like condition with a characteristic temperature $kT_\star \ln 2 = E_{\rm max} - E_s$, where $kT_\star = \beta_\star^{-1}$. 
 It is unclear whether this points to a generic feature that can be directly related to fundamental thermodynamic relations, such as the erasure cost of a single bit being $kT \ln 2$. 
@@
 
-Let $\displaystyle \sigma = e^{-\beta H} / \Z_\beta$ be a stabiliser state, where $\beta \geq 0$ and $H = E_0 \ketbra{0} + E_1 \ketbra{1} + E_2 \ketbra{2}$, with $E_k \geq 0$.
-Its eigen-decomposition can be written as 
+Let $\displaystyle \sigma = e^{-\beta H} / \Z_\beta$ be a stabiliser state, where $\beta \geq 0$ and $H = E_0 \ketbra{\varphi_0} + E_1 \ketbra{\varphi_1} + E_2 \ketbra{\varphi_2}$ is an eigendecomposition of $H$, where we have $E_0 \le E_1 \le E_2$.
+The stabilizer state $\sigma$ can now be written as 
 \begin{equation}
@@
 \end{equation}
-where $\{\ket{\varphi_k}\}$ are pure, orthonormal stabiliser states.
-These pure states can be represented in terms of generalized Paulis.
+where $\{\ket{\varphi_k}\<\varphi_k|\}$ are pure, orthonormal stabiliser states, which can be represented in terms of generalized Paulis.
 Let $C$ be the unitary transforming each $|\varphi_k\>\<\varphi_k|$ to $|k\>\<k|$.
-Since the Clifford group is the normalizer of the Heisenberg-Weyl group this implies that $C$ must be a Clifford unitary.
-Therefore, $C$ maps $\sigma$ to $\gamma_\beta$, where
-\begin{equation}
-\gamma_\beta = \frac{e^{-\beta E_0}}{\Z_\beta} \ketbra{0} + \frac{e^{-\beta E_1}}{\Z_\beta} \ketbra{1} + \frac{e^{-\beta E_2}}{\Z_\beta} \ketbra{2},
-\end{equation}
-is a stabilizer state, diagonal in the computational basis.
-The Clifford operation permutes the Hamiltonian eigenvalues on the phase space, so that the negative component $-v$ of $\rho_S(\epsilon)$ can lie on the same point on the phase space as any of the eigenvalues.
-For this reason, we impose no order between the eigenvalues, but simply choose $E_0$ as the eigenvalue that is associated with the state negativity and denote the highest energy by $E_{\rm{max}} \coloneqq \max{\{E_0, E_1, E_2\}}$.
-
-The Wigner distribution of state $\gamma_\beta$ can be seen as the ensemble average of the distributions of the computational basis states,
+Since the Clifford group is the normalizer of the Heisenberg-Weyl group this implies that $C$ is a Clifford unitary.
+Therefore, $C$ maps $\sigma$ to another stabilizer state that is diagonal in the computational basis, and we can therefore assume without loss of generality that $\sigma$ is diagonal in $\{|0\>,|1\>, |2\>\}$.
+However, this choice means that the location of the negative Wigner component $-v(\epsilon)$ of the strange state will be transformed on the discrete phase space.
+We denote by $E_s$ the eigenvalue of $H$ where the associated eigenvector has Wigner distribution overlapping the negative component of the magic state $C\rho_S(\epsilon)C^\dagger$.
+
+The Wigner distribution of state $\sigma$ is then given by
 \begin{align}
-	\W[\bmx]{\gamma_\beta} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z_\beta}\W[\bmx]{\ketbra{k}} \nonumber\\
+	\W[\bmx]{\sigma} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z_\beta}W_{\ketbra{k}}(x_0,x_1) \nonumber\\
 	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z_\beta} \delta_{x_0, k} = \frac{e^{-\beta E_{x_0}}}{3\Z_\beta},
 \end{align}
-for all $\bmx \in \cal{P}_3$. 
-All Wigner components are strictly positive, therefore the pre-order $\prec_{\gamma_\beta}$ is always well-defined.
-
-Our aim is to obtain a distillation bound for~\cref{eq:stdist} which depends on variables $n, n', \epsilon, \epsilon'$ as well as $\beta$.
-In the analysis that follows, we again drop obvious variable dependencies for clarity.
-
-We construct the Strange state rescaled distribution 
-\begin{equation}
-	\widetilde{\rm{W}}_{\rho_{\rm{S}}|\gamma}(\bmx) = \frac{\W[\bmx]{\rho_{\rm{S}}}}{\W[\bmx]{\gamma}},
+where $x_0$ is the first component of $\x$, labeling one of the three vertical lines in the phase space.
+Since we have restricted to full-rank states, all Wigner components are strictly positive, and so the pre-order $\prec_{\sigma}$ is well-defined.
+States that are not full-rank can be addressed as a limiting case of the above.
+
+The Strange state rescaled distribution for a magic state $\rho_S(\epsilon)$ is now given by 
+\begin{equation}
+	\widetilde{\rm{W}}_{\rho_{\rm{S}}|\sigma}(\bmx) = \frac{\W[\bmx]{\rho_{\rm{S}}}}{\W[\bmx]{\sigma}},
 \end{equation}
@@
     \caption{\textbf{Qutrit phase space regions with different rescaled values.}
-    The rescaled distribution attains a unique value in each of the four regions, given by $3\Z \times$ the value depicted in the region, according to~\cref{eq:bmw_rescaled}.
+    The rescaled distribution attains a unique value in each of the four regions is proportional to the value depicted in the region, according to~\cref{eq:bmw_rescaled}.
     }
@@
 \begin{align}
+	\bmw(\rho_{\rm{S}}) &\coloneqq (-v, u, u, u), \\
 		\bmm &\coloneqq (1,2,3,3), \\
-	\bmw(\rho_{\rm{S}}) &\coloneqq (-v, u, u, u), \\
-	\bmw(\gamma) &\coloneqq \frac{1}{3\Z} \left( e^{-\beta E_0}, e^{-\beta E_0}, e^{-\beta E_1}, e^{-\beta E_2} \right), \\
-	\bmw(\rho_{\rm{S}} | \gamma) &\coloneqq 3\Z \left( -v e^{\beta E_0}, u e^{\beta E_0}, u e^{\beta E_1}, u e^{\beta E_2} \right). \label{eq:bmw_rescaled}
+	\bmw(\sigma) &\coloneqq \frac{1}{3\Z} \left( e^{-\beta E_0}, e^{-\beta E_0}, e^{-\beta E_1}, e^{-\beta E_2} \right), \\
+	\bmw(\rho_{\rm{S}} | \sigma) &\coloneqq 3\Z \left( -v e^{\beta E_0}, u e^{\beta E_0}, u e^{\beta E_1}, u e^{\beta E_2} \right). \label{eq:bmw_rescaled}
 \end{align}
 
-Using this notation, the component values and multiplicities of the $n$--copy distributions can be readily provided by~\cref{lem:ncopycomponents} in~\cref{app:cmpairs}.
-They are parametrised by three independent components $i,j,k$, with sum $\alpha \coloneqq i+j+k \leq n$.
+Using this notation, the values and multiplicities of the $n$--copy distribution $\bmw(\rho^{\otimes n}_S |\sigma^{\otimes n})$ are computed in~\cref{lem:ncopycomponents} in~\cref{app:cmpairs}.
+The values are denoted by $w_{ijk}$ and with associated multiplicity $m_{ijk}$.
+The indices $i,j,k$ obey the constraint $\alpha \coloneqq i+j+k \leq n$.
 The $n$--copy multiplicity is given by
@@
 \end{equation}
-while the distribution values that correspond to the same index triplet $(i,j,k)$ are given by
+while the distribution values are given by
 \begin{align}
-	w(\rho_{\rm{S}})_{ijk} &= (-v)^{n-\alpha} u^{\alpha}, \\
-	w(\gamma)_{ijk} &= (3\Z)^{-n} e^{-\beta (n-\alpha)E_0} e^{-\beta ( i E_0 + j E_1 + k E_2 )}, \\
-	w(\rho_{\rm{S}} | \gamma)_{ijk} &= (3\Z)^{n} (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )}.
+	w(\rho_{\rm{S}} | \sigma)_{ijk} &= (3\Z)^{n} (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )}.
 \end{align}
 
-In order to construct the $n$--copy Lorenz curve $\lc{\rho_{\rm{S}}^{\otimes n}}{\gamma}$ we need to sort the components of the $n$--copy rescaled distribution, $w(\rho_{\rm{S}} | \gamma)_{ijk}$ in decreasing order.
-In particular, to find the coordinates of the first elbow $(x_0, L_0)$, we need to evaluate the maximum rescaled component,
+In order to construct the $n$--copy Lorenz curve $\lc{\rho_{\rm{S}}^{\otimes n}}{\sigma}$ we need to order the components of the distribution, $w(\rho_{\rm{S}} | \sigma)_{ijk}$ in decreasing order.
+In particular, to find the coordinates of the first elbow $(x_0, L_0)$, we need to evaluate the maximum component,
 \begin{align}
-	&\bmw(\rho_{\rm{S}} | \gamma)_{\rm{max}} \coloneqq (3\Z)^{n}\times \nonumber\\
-	&\max\limits_{i,j,k}\Big\{ (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \label{eq:max_slope}
+	&\bmw(\rho_{\rm{S}} | \sigma)_{\rm{max}} \coloneqq (3\Z)^{n}\times \nonumber\\
+	&\max\limits_{i,j,k}\Big\{ (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \label{eq:max_slope}
 \end{align}
@@
 Notice that for $0 \leq \epsilon \leq 3/7$, we have $v \geq u$. 
-We assume that $n$ is even, so that we need the sum $\alpha = i+j+k$ to be even for the expression to be positive. 
-The following analysis is similar if $n$ is chosen to be odd.
-
-Given an even value for the sum $\alpha$, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_0}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
+We can also assume that $n$ is even, so that we need the sum $\alpha = i+j+k$ to be even for the expression to be positive.
+
+Given an even value for $\alpha$, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_s}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
 Hence, we have
 \begin{align}
-	&\bmw(\rho_{\rm{S}} | \gamma)_{\rm{max}} = \nonumber\\
-	&(3\Z)^{n} v^n e^{n\beta E_0}\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}.
+	&\bmw(\rho_{\rm{S}} | \sigma)_{\rm{max}} = \nonumber\\
+	&(3\Z)^{n} v^n e^{n\beta E_s}\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}.
 \end{align}
-If the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than $1$ then the maximum occurs at $\alpha=0$, otherwise it occurs at $\alpha = n$. 
+If the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_s)}$ is less than $1$ then the maximum occurs at $\alpha=0$, otherwise it occurs at $\alpha = n$. 
 To determine this transition we set
 \begin{equation}\label{eq:noise_transition}
-	\frac{u(\epsilon)}{v(\epsilon)} e^{\beta (E_{\rm{max}} - E_0)} \coloneqq \frac{3-\epsilon}{6-8\epsilon} e^{\beta (E_{\rm{max}} - E_0)} = 1.
+	\frac{u(\epsilon)}{v(\epsilon)} e^{\beta (E_{\rm{max}} - E_s)} \coloneqq \frac{3-\epsilon}{6-8\epsilon} e^{\beta (E_{\rm{max}} - E_s)} = 1.
 \end{equation}
@@
 \begin{equation}
-	\beta_{\star} \coloneqq \frac{1}{E_{\rm{max}} - E_0} \ln2.
+	\beta_{\star} \coloneqq \frac{1}{E_{\rm{max}} - E_s} \ln2.
 \end{equation}
@@
 \begin{equation}
-	\epsilon_{\star}(\beta) := 3 - \dfrac{18}{8-e^{(E_{\rm{max}} - E_0)\beta}}.
+	\epsilon_{\star}(\beta) := 3 - \dfrac{18}{8-e^{(E_{\rm{max}} - E_s)\beta}}.
 \end{equation}
@@
 \begin{equation*}
-	\frac{3-\epsilon}{6-8\epsilon} e^{\beta (E_{\rm{max}} - E_0)} > \frac{3-\epsilon}{6-8\epsilon} 2 \geq \frac{1}{2}2 = 1,
+	\frac{3-\epsilon}{6-8\epsilon} e^{\beta (E_{\rm{max}} - E_s)} > \frac{3-\epsilon}{6-8\epsilon} 2 \geq \frac{1}{2}2 = 1,
 \end{equation*}
@@
 
-The maximum rescaled component can then be expressed as
-\begin{equation}
-\bmw(\rho_{\rm{S}} | \gamma)_{\rm{max}} =
+The maximum component can then be expressed as
+\begin{equation}
+\bmw(\rho_{\rm{S}} | \sigma)_{\rm{max}} =
 	\begin{cases}
-		(3\Z)^{n} v^n e^{n\beta E_0}, &\epsilon \leq \epsilon_{\star},\ \hspace{3pt}\rm{(C1)}	\\
+		(3\Z)^{n} v^n e^{n\beta E_s}, &\epsilon \leq \epsilon_{\star},\ \hspace{3pt}\rm{(C1)}	\\
 		(3\Z)^{n} u^n e^{n\beta E_{\rm{max}}}, &\epsilon > \epsilon_{\star}.\ \hspace{5pt}\rm{(C2)} 
@@
 \end{equation}
-Case $\rm{(C1)}$ corresponds to $(i,j,k) = (0,0,0)$, so the multiplicity is $m_{000} = 1$ and the corresponding Wigner components are $\bmw(\rho_{\rm{S}})_{000}, \bmw(\gamma)_{000}$. 
+Case $\rm{(C1)}$ corresponds to $(i,j,k) = (0,0,0)$, so the multiplicity is $m_{000} = 1$, while
 Case $\rm{(C2)}$ corresponds to
@@
 \end{equation}
-and we have $E_{\rm{max}} = E_1$ ($E_{\rm{max}} = E_2$), so the multiplicity is $m_{0n0} = 3^n$ ($m_{00n} = 3^n$) and the corresponding Wigner components are $\bmw(\rho_{\rm{S}})_{0n0}, \bmw(\gamma)_{0n0}$ ($\bmw(\rho_{\rm{S}})_{00n}, \bmw(\gamma)_{00n}$).
-
-The first elbow coordinates can finally be derived as
+and we have $E_{\rm{max}} \ne E_s$, so the multiplicity in each case is $3^n$.
+
+The coordinates of the first elbow are now given by
 \begin{equation}\label{eq:first_elb_coords}
@@
 	\begin{cases}
-		\left( \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^n, v^n \right), &\rm{(C1)}	\vspace{10pt}\\
-		\left( \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^n, (3u)^n \right). &\rm{(C2)} 
+		\left(\frac{1}{3^n} e^{-n\beta (E_s - F(\beta))}, v^n \right), &\rm{(C1)}	\vspace{10pt}\\
+		\left( e^{-n\beta (E_{\rm{max}}-F(\beta))}, (3u)^n \right). &\rm{(C2)} 
 	\end{cases}
 \end{equation}
-\null\\
-
 The Lorenz curves of the initial and target states may each be described by either $\rm{(C1)}$ or $\rm{(C2)}$, depending on the physical parameters $\epsilon, \epsilon', \beta$.
-Specifically, we have three scenarios:
+Specifically, we have three scenarios of relevance to magic distillation:
 \begin{enumerate}
-	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} = E_0$ or $E_{\rm{max}} > E_0$, $\beta < \beta_{\star}$ and $\epsilon' < \epsilon  \leq \epsilon_{\star}$.
-	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} > E_0$, $\beta < \beta_{\star}$ and $\epsilon' \leq \epsilon_{\star} < \epsilon$.
-	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $E_{\rm{max}} > E_0$, $\beta < \beta_{\star}$ and $\epsilon_{\star} \leq \epsilon' < \epsilon$ or $E_{\rm{max}} > E_0$, $\beta \geq \beta_{\star}$.
+	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} = E_s$ or $E_{\rm{max}} > E_s$, $\beta < \beta_{\star}$ and $\epsilon' < \epsilon  \leq \epsilon_{\star}$.
+	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} > E_s$, $\beta < \beta_{\star}$ and $\epsilon' \leq \epsilon_{\star} < \epsilon$.
+	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $E_{\rm{max}} > E_s$, $\beta < \beta_{\star}$ and $\epsilon_{\star} \leq \epsilon' < \epsilon$ or $E_{\rm{max}} > E_s$, $\beta \geq \beta_{\star}$.
 \end{enumerate}
-Note that $\rm{(C1)} \rightarrow \rm{(C2)}$ is impossible because it would imply $\beta < \beta_{\star}$ and $\epsilon \leq \epsilon_{\star} \leq \epsilon' < \epsilon$, a contradiction.
-
-In all three scenarios, it is simple to check that the initial state's first elbow is always located to the left (closer to $0$) of the target state's first elbow, $x_0 \leq x_0'$, as proven in~\cref{app:first_elb_loc}, where the prime ($'$) is used to indicate target state coordinates.
-Therefore, we can use the first elbow condition,
-\begin{equation}\label{eq:first_elb_bound3}
-	\frac{L_0}{x_0} \geq \frac{L_0'}{x_0'},
-\end{equation}
-to compute analytical distillation bounds for the distillation rate $R = R(\epsilon, \epsilon', \beta) \coloneqq n'/n$ in all three possible scenarios.
-Involving more elbows gives stricter, but more convoluted necessary distillation constraints.
-
-We substitute coordinates from~\cref{eq:first_elb_coords} appropriately in~\cref{eq:first_elb_bound3} to get the following necessary conditions,
+The fourth case $\rm{(C1)} \rightarrow \rm{(C2)}$ is not considered as it would correspond to $\epsilon' > \epsilon$ \ddd{[True?]}, which means that the output magic state is noisier than the input state.
+
+In each of the three scenarios, it is simple to check that the initial state's first elbow has $x_0$ coordinate closer to $0$) than that of the output state: $x_0 \leq x_0'$, see~\cref{app:first_elb_loc} for details.
+Therefore we obtain distillation bounds directly by comparing $L_0$ and $L_0'$.
+We we do so we obtain the following distillation bounds,
 \begin{equation}\label{eq:rate_bounds_proof}
@@
 	\begin{cases}
-		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_0 - F(\beta))}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F(\beta))},\ &\rm{(C1)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
-		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F(\beta))}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
+		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F(\beta))}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_s - F(\beta))},\ &\rm{(C1)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
+		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F(\beta))}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_s - F(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
 		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F(\beta))}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C2)}.
@@
 \end{equation}
-Equivalently, we require that
-\begin{equation}\label{eq:error_bounds_proof}
-	\epsilon \leq
-	\begin{cases}
-		\frac{3}{4} - \frac{3}{4} \left( 1 - \frac{4}{3}\epsilon' \right)^{R} \left( \dfrac{e^{-\beta E_0}}{\Z_\beta} \right)^{1 - R},\ &\rm{(C1)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
-		3 - 6 \left( 1 - \frac{4}{3}\epsilon' \right)^{R} \dfrac{e^{-\beta E_{\rm{max}}} e^{R\beta E_0}}{\Z_\beta^{1-R}},\ &\rm{(C2)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
-		3 - 6 \left( \frac{1}{2} - \frac{1}{6}\epsilon' \right)^{R} \left( \dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta} \right)^{1 - R},\ &\rm{(C2)} \rightarrow \rm{(C2)}.
-	\end{cases}
-\end{equation}
-
-Substituting $\epsilon' = 0$ in~\cref{eq:rate_bounds_proof} leads to the theorem statement.
+Substituting $\epsilon' = 0$ into these expressions leads to the stated distillation bounds.
 
 \end{proof}
-
-\nick{LAST ELBOW BOUND}
-
-To find the coordinates of the \textbf{last} elbow $(x_E, L_E)$, where $E$ is the number of elbows, we need to evaluate the minimum rescaled component,
-\begin{align}
-	&\bmw(\rho_{\rm{S}} | \gamma)_{\rm{min}} \coloneqq (3\Z)^{n}\times \nonumber\\
-	&\min\limits_{i,j,k}\Big\{ (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \label{eq:min_slope}
-\end{align}
-where $0 \leq i,j,k \leq n$ and $\alpha \coloneqq i+j+k \leq n$.
-Notice that for $0 \leq \epsilon \leq 3/7$, we have $v \geq u$. 
-We need the sum $\alpha = i+j+k$ to be odd for the expression to be negative.
-
-Given an odd value for the sum $\alpha$, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_0}$ is fixed (and negative), so the expression is minimised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
-Hence, we have
-\begin{align}
-	&\bmw(\rho_{\rm{S}} | \gamma)_{\rm{min}} = \nonumber\\
-	&-(3\Z)^{n} v^n e^{n\beta E_0}\max\limits_{\substack{\alpha = 1,3, \\ \dots,n-1}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}.
-\end{align}
-If the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than $1$ then the minimum occurs at $\alpha=1$, otherwise it occurs at $\alpha = n-1$.
-
-The minimum rescaled component can then be expressed as
-\begin{equation}
-\bmw(\rho_{\rm{S}} | \gamma)_{\rm{min}} =
-	\begin{cases}
-		-(3\Z)^{n} v^{n-1} u e^{\beta [(n-1)E_0 + E_{\rm{max}}]}, &\epsilon \leq \epsilon_{\star},\ \hspace{3pt}\rm{(C1)}	\\
-		-(3\Z)^{n} v u^{n-1} e^{\beta [E_0 + (n-1)E_{\rm{max}}]}, &\epsilon > \epsilon_{\star}.\ \hspace{5pt}\rm{(C2)} 
-	\end{cases}
-\end{equation}
-Case $\rm{(C1)}$ can correspond to $(i,j,k) = (1,0,0)$ if $E_{\rm{max}} = E_0$, when the multiplicity is $m_{100} = 2n$ and the corresponding Wigner components are $\bmw(\rho_{\rm{S}})_{100}, \bmw(\gamma)_{100}$ or it can correspond to $(i,j,k) = (0,1,0)$ ($(i,j,k) = (0,0,1)$), if $E_{\rm{max}} = E_1$ ($E_{\rm{max}} = E_2$), when the multiplicity is $m_{010} = 3n$ ($m_{001} = 3n$) and the corresponding Wigner components are $\bmw(\rho_{\rm{S}})_{010}, \bmw(\gamma)_{010}$ ($\bmw(\rho_{\rm{S}})_{001}, \bmw(\gamma)_{001}$).
-Case $\rm{(C2)}$ corresponds to $(i,j,k) = (0,n-1,0)$ ($(i,j,k) = (0,0,n-1)$)
-if we have $E_{\rm{max}} = E_1$ ($E_{\rm{max}} = E_2$), when the multiplicity is $m_{0,n-1,0} = 3^{n-1}n$ ($m_{0,0,n-1} = 3^{n-1}n$) and the corresponding Wigner components are $\bmw(\rho_{\rm{S}})_{0,n-1,0}, \bmw(\gamma)_{0,n-1,0}$ ($\bmw(\rho_{\rm{S}})_{0,0,n-1}, \bmw(\gamma)_{0,0,n-1}$).
-
-The last elbow coordinates can finally be derived by sutracting the appropriate rescaled component from 1, $(x_E, L_E) =$
-\begin{equation}\label{eq:last_elb_coords}
-	\begin{cases}
-		&\left( 1-\dfrac{2n}{(3\Z_\beta)^n}e^{-\beta [(n-1)E_0 + E_{\rm{max}}]},\ 1 + 2n v^{n-1} u \right), \vspace{5pt}\\
-		&\hspace{5pt} \text{if } E_{\rm{max}} = E_0, \hspace{51pt}\rm{(C1a)} \vspace{10pt}\\
-		&\left( 1-\dfrac{3n}{(3\Z_\beta)^n}e^{-\beta [(n-1)E_0 + E_{\rm{max}}]},\ 1 + 3n v^{n-1} u \right), \vspace{5pt}\\
-		&\hspace{5pt} \text{if } E_{\rm{max}} > E_0, \epsilon \leq \epsilon_{\star}, \hspace{20pt}\rm{(C1b)} \vspace{10pt}\\
-		&\left( 1-\dfrac{n}{3\Z_\beta^n}e^{-\beta [E_0 + (n-1)E_{\rm{max}}]},\ 1 + 3^{n-1}n v u^{n-1} \right), \vspace{5pt}\\
-		&\hspace{5pt} \text{if } E_{\rm{max}} > E_0, \epsilon \geq \epsilon_{\star}. \hspace{22pt}\rm{(C2)}
-	\end{cases}
-\end{equation}
-
-Assuming that $E_{\rm{max}} > E_0$ for clarity, we have the same three scenarios as in the case of the first elbow bound:
-\begin{enumerate}
-	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $\beta < \beta_{\star}$ and $\epsilon' < \epsilon  \leq \epsilon_{\star}$.
-	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $\beta < \beta_{\star}$ and $\epsilon' \leq \epsilon_{\star} < \epsilon$.
-	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $\beta < \beta_{\star}$ and $\epsilon_{\star} \leq \epsilon' < \epsilon$ or $\beta \geq \beta_{\star}$.
-\end{enumerate}
-Now the last elbow condition on Lorenz curves can be derived by simple interpolation, giving the condition
-\begin{equation}
-	L_E \geq 1 + \frac{1-x_E}{1-x_E'} (L_E' - 1),
-\end{equation}
-provided that the last elbow location is closer to 1 for the initial state than the target state, which is always true.
-
-The last elbow bound then can be rephrased in terms of the first elbow bound as $R_{\rm{last-elb}} - R_{\rm{first-elb}} = $
-\begin{equation}\label{eq:last_elb_coords}
-	\begin{cases}
-		\dfrac{1}{n} \dfrac{\log{\frac{u(\epsilon)v(\epsilon')}{u(\epsilon')v(\epsilon)}}}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F(\beta))},\ &\rm{(C1)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
-		\dfrac{1}{n} \dfrac{\log{\frac{v(\epsilon)v(\epsilon')}{u(\epsilon)u(\epsilon')}} - 2\beta(E_{\rm{max}} - E_0)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
-		\dfrac{1}{n} \dfrac{\log{\frac{v(\epsilon')u(\epsilon')}{v(\epsilon')u(\epsilon)}}}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C2)},
-	\end{cases}
-\end{equation}
-
-Note that the last elbow bounds have a dependence on $n$, which interestingly is due to $n$ being even.
-Had we considered \textbf{odd} number of copies $n$, then the first elbow bound would depend on $n$ and the last elbow bound would not.
-This, along with the unital fragment analysis, makes me think that calculating the bounds again for odd $n$ or $\epsilon > 3/7$ would reveal nice symmetries of the analysis, but it's probably not worth the time, so including last elbow analysis properly feels incomplete.
-
-Determining the sign of the difference between the last and first elbow bounds tells us which bound is better.
-The term $\log{\frac{u(\epsilon)v(\epsilon')}{u(\epsilon')v(\epsilon)}}$ is always positive for $\epsilon > \epsilon'$, therefore the last elbow bound, compared to the first elbow bound, is always \textbf{worse} in the first scenario and always \textbf{better} in the third scenario (remember, this is the yellow-ish right part of~\cref{fig:rate_contour}).
-
-In the second scenario ($\rm{(C2)} \rightarrow \rm{(C1)}$), the expression looks very weird to me, seems like the difference tends to $-\infty$ as $E_{\rm{max}} \rightarrow \infty$.
-I am a bit stuck with this expression and I am not sure it's worth putting more time in it.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2021-04-12 magic_paper.tex
Cleaned up Sec.V. What to do with last elbow? How to clean up lower bounds subsection?

@@
 
-We now generalise the approach taken in the previous section and consider bounds on magic distillation for an arbitrary stabiliser fragment, $\R_\sigma$ where $\sigma$ is any quantum state $\sigma \in \stab$.
+We now generalise the approach taken in the previous section and consider bounds on magic distillation for an arbitrary stabiliser fragment $\R_\sigma$, where $\sigma$ is any quantum state $\sigma \in \stab$.
 In other words, we consider those bounds on distillation that apply when the free operations have $\sigma$ as a fixed point.
@@
 \begin{enumerate}
-\item As family of upper bounds parameterized by an abstract stabiliser state $\sigma$.
-\item The state $\sigma$ corresponds to actual hardware limitations or to biased noise model in which $\sigma$ is an equilibrium state of some kind. 
+\item As a family of upper bounds parameterised by an abstract stabiliser state $\sigma$.
+\item The state $\sigma$ can also reflect actual hardware limitations or some kind of biased noise model in which $\sigma$ is an equilibrium state.
 \end{enumerate}
 Without loss of generality, we can always write a full-rank stabiliser state $\sigma$ in the form $\sigma =  \frac{1}{\Z_\beta} e^{-\beta H}$ for some $\beta \geq 0$ and effective Hamiltonian $H$.
-Our results will also depend on the free energy $F(\beta)$ of the state $\sigma$, which is defined by
+Our results will also depend on the free energy $F(\beta)$ of the state $\sigma$, expressed as
 \begin{equation}
@@
 Here $S(\sigma)$ is the von Neumann entropy $S(\sigma) \coloneqq -\tr[\sigma\log{\sigma}]$.
-Again, under interpretation (1) above this is an abstract entropic measure of the stabilizer state, while under interpretation (2) it corresponds to the thermodynamic free energy of the equilibrium state.
+Again, under interpretation (1) above, this is an abstract entropic measure of the stabilizer state, while, under interpretation (2), it corresponds to the thermodynamic free energy of the equilibrium state.
 
@@
 \end{equation}
-and as before tensoring in copies of $\sigma$ does not affect the Lorenz curves of the magic states in the fragment.
+where, as before, tensoring in copies of $\sigma$ does not affect the Lorenz curves of the magic states in the fragment.
 
@@
 \begin{theorem}\label{thm:stab_bounds}
-	Given any theory of magic $\R = (\F, \O)$.
-Let $\sigma$ be any qutrit stabiliser state, and write the state as $\sigma = \frac{1}{\Z} e^{-\beta H}$ with $H$ having eigenvalues $E_0, E_1, E_2$, and where $\beta$ is an effective inverse temperature for the state.
-We define $\beta_\star = (1/kT_\star)$ through the relation
+	Given a theory of magic $\R = (\F, \O)$, let $\sigma$ be any qutrit stabiliser state, and write the state as $\sigma = \frac{1}{\Z} e^{-\beta H}$, where $H$ has eigenvalues $E_0, E_1, E_2$, and $\beta$ is an effective inverse temperature for the state.
+We define $\beta_\star = 1/kT_\star$ through the relation
 \begin{equation}
-	E_{\rm max} - E_s =: kT_\star \ln 2,
+	E_{\rm max} - E_s \eqqcolon kT_\star \ln 2,
 \end{equation}
-where $E_{\rm max} = \max\{E_k\}$ and $E_s$ is the eigenvalue of the eigenstate that overlaps the negative component of $\rho_S(\epsilon)$.  For $\beta \leq \beta_\star$ define a threshold noise level
+where $E_{\rm max} = \max\{E_0, E_1, E_2\}$ and $E_s$ is the eigenvalue of the eigenstate that overlaps the negative component of $\rho_S(\epsilon)$.
+\nick{is the ``overlap'' statement precise enough?} For $\beta \leq \beta_\star$, we define a threshold noise level
 \begin{equation}
@@
 \end{equation}
-Then any distillation rate $R(\epsilon, \beta)$ in the $\sigma$--fragment of a magic theory is bounded as follows:\\
+Then, any distillation rate $R(\epsilon, \beta)$ in the $\sigma$--fragment of a magic theory is bounded as follows:\\
 If $\beta \leq \beta_{\star}$ and $\epsilon  \leq \epsilon_{\star}$,
@@
 
-Let $\displaystyle \sigma = e^{-\beta H} / \Z_\beta$ be a stabiliser state, where $\beta \geq 0$ and $H = E_0 \ketbra{\varphi_0} + E_1 \ketbra{\varphi_1} + E_2 \ketbra{\varphi_2}$ is an eigendecomposition of $H$, where we have $E_0 \le E_1 \le E_2$.
+Let $\displaystyle \sigma = e^{-\beta H} / \Z_\beta$ be a stabiliser state, where $\beta \geq 0$ and $H = E_0 \ketbra{\varphi_0} + E_1 \ketbra{\varphi_1} + E_2 \ketbra{\varphi_2}$ is an eigendecomposition of $H$.
 The stabilizer state $\sigma$ can now be written as 
@@
 \begin{align}
-	\W[\bmx]{\sigma} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z_\beta}W_{\ketbra{k}}(x_0,x_1) \nonumber\\
-	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z_\beta} \delta_{x_0, k} = \frac{e^{-\beta E_{x_0}}}{3\Z_\beta},
+	\W[\bmx]{\sigma} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z_\beta}W_{\ketbra{k}}(x, p) \nonumber\\
+	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z_\beta} \delta_{x, k} = \frac{e^{-\beta E_{x}}}{3\Z_\beta},
 \end{align}
-where $x_0$ is the first component of $\x$, labeling one of the three vertical lines in the phase space.
+where $x$ labels one of the three vertical lines in the phase space.
 Since we have restricted to full-rank states, all Wigner components are strictly positive, and so the pre-order $\prec_{\sigma}$ is well-defined.
@@
 Using this notation, the values and multiplicities of the $n$--copy distribution $\bmw(\rho^{\otimes n}_S |\sigma^{\otimes n})$ are computed in~\cref{lem:ncopycomponents} in~\cref{app:cmpairs}.
-The values are denoted by $w_{ijk}$ and with associated multiplicity $m_{ijk}$.
-The indices $i,j,k$ obey the constraint $\alpha \coloneqq i+j+k \leq n$.
+The values are denoted by $w(\rho_{\rm{S}} | \sigma)_{ijk}$ with associated multiplicity $m_{ijk}$.
+The indices $i,j,k$ are non-negative integers and obey the constraint $\alpha \coloneqq i+j+k \leq n$.
 The $n$--copy multiplicity is given by
@@
 while the distribution values are given by
+\begin{align}\label{eq:ncopy_w_rescaled}
+	w(\rho_{\rm{S}} | \sigma)_{ijk} &= (3\Z)^{n} (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )},
+\end{align}
+where we have also computed the unscaled components
 \begin{align}
-	w(\rho_{\rm{S}} | \sigma)_{ijk} &= (3\Z)^{n} (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )}.
+	w(\rho_{\rm{S}})_{ijk} &= (-v)^{n-\alpha} u^{\alpha}, \label{eq:ncopy_wrho}\\
+	w(\sigma)_{ijk} &= (3\Z)^{-n} e^{-\beta (n-\alpha)E_s} e^{-\beta ( i E_0 + j E_1 + k E_2 )}. \label{eq:ncopy_wsigma}
 \end{align}
@@
 \begin{align}
-	&\bmw(\rho_{\rm{S}} | \sigma)_{\rm{max}} \coloneqq (3\Z)^{n}\times \nonumber\\
+	&w(\rho_{\rm{S}} | \sigma)_{\rm{max}} \coloneqq (3\Z)^{n}\times \nonumber\\
 	&\max\limits_{i,j,k}\Big\{ (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \label{eq:max_slope}
@@
 \begin{align}
-	&\bmw(\rho_{\rm{S}} | \sigma)_{\rm{max}} = \nonumber\\
+	&w(\rho_{\rm{S}} | \sigma)_{\rm{max}} = \nonumber\\
 	&(3\Z)^{n} v^n e^{n\beta E_s}\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}.
@@
 \begin{equation}
-\bmw(\rho_{\rm{S}} | \sigma)_{\rm{max}} =
+w(\rho_{\rm{S}} | \sigma)_{\rm{max}} =
 	\begin{cases}
@@
 	(0,n,0), &\text{if } E_{\rm{max}} = E_1, \\
-	(0,0,n), &\text{if } E_{\rm{max}} = E_2.
+	(0,0,n), &\text{if } E_{\rm{max}} = E_2,
 	\end{cases}
 \end{equation}
-and we have $E_{\rm{max}} \ne E_s$, so the multiplicity in each case is $3^n$.
+so the multiplicity in each case is $3^n$.
 
-The coordinates of the first elbow are now given by
+Using the appropriate indices in~\cref{eq:ncopy_wrho,eq:ncopy_wsigma}, the first elbow coordinates can now be expressed as
 \begin{equation}\label{eq:first_elb_coords}
@@
 \end{enumerate}
-The fourth case $\rm{(C1)} \rightarrow \rm{(C2)}$ is not considered as it would correspond to $\epsilon' > \epsilon$ \ddd{[True?]}, which means that the output magic state is noisier than the input state.
+The fourth case $\rm{(C1)} \rightarrow \rm{(C2)}$ is not considered as it would correspond to $\epsilon \leq \epsilon_\star < \epsilon$, which would imply that the output magic state is noisier than the input state.
 
-In each of the three scenarios, it is simple to check that the initial state's first elbow has $x_0$ coordinate closer to $0$) than that of the output state: $x_0 \leq x_0'$, see~\cref{app:first_elb_loc} for details.
-Therefore we obtain distillation bounds directly by comparing $L_0$ and $L_0'$.
-We we do so we obtain the following distillation bounds,
+In each of the three scenarios, it is simple to check that the initial state's first elbow has $x_0$ coordinate closer to $0$ compared to the output state, $x_0 \leq x_0'$ (see~\cref{app:first_elb_loc} for details).
+Therefore, we can use the first elbow constraint, as described in~\cref{app:elb_constraints}, leading to the following distillation bounds,
 \begin{equation}\label{eq:rate_bounds_proof}

### 2021-04-13 magic_paper.tex
Fixing elements of stablizer proof.

@@
 This is a particularly powerful set of operations, which for example include all Weyl-covariant channels~\cite{cit:gross3}.
-To make things concrete, we shall consider qutrit magic states ($d=3$) as qutrit systems don't exhibit the subtleties and peculirities of qubit systems, while they admit non-trivial structure (e.g.
+To make things concrete, we shall consider qutrit magic states ($d=3$) as the Wigner representation is simpler than $d=2$, while they admit non-trivial structure (e.g.
 Hamiltonians with two different energy gaps) and still are sufficiently simple to analyse in detail.
@@
 \item As a family of upper bounds parameterised by an abstract stabiliser state $\sigma$.
-\item The state $\sigma$ can also reflect actual hardware limitations or some kind of biased noise model in which $\sigma$ is an equilibrium state.
+\item The invariant state $\sigma$ reflects actual hardware limitations, a biased noise model, or a statement of the ambient thermal environment for the system.
 \end{enumerate}
+In what follows we shall be agnostic about which of the two apply.
 Without loss of generality, we can always write a full-rank stabiliser state $\sigma$ in the form $\sigma =  \frac{1}{\Z_\beta} e^{-\beta H}$ for some $\beta \geq 0$ and effective Hamiltonian $H$.
@@
 Here $S(\sigma)$ is the von Neumann entropy $S(\sigma) \coloneqq -\tr[\sigma\log{\sigma}]$.
-Again, under interpretation (1) above, this is an abstract entropic measure of the stabilizer state, while, under interpretation (2), it corresponds to the thermodynamic free energy of the equilibrium state.
+Note that under interpretation (1) above, this is an abstract entropic measure of the stabilizer state, while, under interpretation (2), it corresponds to the actual thermodynamic free energy of the equilibrium state.
 
@@
 \end{equation}
-where $E_{\rm max} = \max\{E_0, E_1, E_2\}$ and $E_s$ is the eigenvalue of the eigenstate that overlaps the negative component of $\rho_S(\epsilon)$.
-\nick{is the ``overlap'' statement precise enough?} For $\beta \leq \beta_\star$, we define a threshold noise level
+where $E_{\rm max} = \max\{E_0, E_1, E_2\}$ and $E_s$ is the eigenvalue of the eigenstate that overlaps the negative component of $\rho_S(\epsilon)$ in the Wigner representation.
+For $\beta \leq \beta_\star$, we define a threshold noise level
 \begin{equation}
@@
 where $\{\ket{\varphi_k}\<\varphi_k|\}$ are pure, orthonormal stabiliser states, which can be represented in terms of generalized Paulis.
-Let $C$ be the unitary transforming each $|\varphi_k\>\<\varphi_k|$ to $|k\>\<k|$.
+To make our analysis simpler we perform a change of basis that does not affect the Wigner negativity of the problem.
+We let $C$ be the unitary transforming each $|\varphi_k\>\<\varphi_k|$ to $|k\>\<k|$.
 Since the Clifford group is the normalizer of the Heisenberg-Weyl group this implies that $C$ is a Clifford unitary.
@@
 We denote by $E_s$ the eigenvalue of $H$ where the associated eigenvector has Wigner distribution overlapping the negative component of the magic state $C\rho_S(\epsilon)C^\dagger$.
+This is unique, since the eigenstates form an orthonormal basis.
 
@@
 	\W[\bmx]{\sigma} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z_\beta}W_{\ketbra{k}}(x, p) \nonumber\\
-	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z_\beta} \delta_{x, k} = \frac{e^{-\beta E_{x}}}{3\Z_\beta},
+	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z_\beta} \delta_{x, k} = \frac{e^{-\beta E_x}}{3\Z_\beta},
 \end{align}
@@
 \begin{equation}
-	\widetilde{\rm{W}}_{\rho_{\rm{S}}|\sigma}(\bmx) = \frac{\W[\bmx]{\rho_{\rm{S}}}}{\W[\bmx]{\sigma}},
+	\widetilde{\rm{W}}_{\rho_{\rm{S}}|\sigma}(\bmx) = \frac{\W[\bmx]{\rho_S}}{\W[\bmx]{\sigma}},
 \end{equation}
@@
     \includegraphics[scale=0.45]{figs/pd_split_thermal.pdf}
-    \caption{\textbf{Qutrit phase space regions with different rescaled values.}
-    The rescaled distribution attains a unique value in each of the four regions is proportional to the value depicted in the region, according to~\cref{eq:bmw_rescaled}.
+    \caption{\textbf{Qutrit phase space regions for $W_{\rho | \sigma}(\x)$.}
+    Here the negative component of the magic state overlaps the Wigner distribution of $|0\>$.
+The rescaled distribution attains a single value in each of the four regions that is proportional to the value depicted in the region, see~\cref{eq:bmw_rescaled}.
     }
@@
 
-In order to construct the $n$--copy Lorenz curve $\lc{\rho_{\rm{S}}^{\otimes n}}{\sigma}$ we need to order the components of the distribution, $w(\rho_{\rm{S}} | \sigma)_{ijk}$ in decreasing order.
+In order to construct the $n$--copy Lorenz curve $\lc{\rho_{\rm{S}}^{\otimes n}}{\sigma^{\otimes n}}$ we need to order the components of the distribution, $w(\rho_{\rm{S}} | \sigma)_{ijk}$ in decreasing order.
 In particular, to find the coordinates of the first elbow $(x_0, L_0)$, we need to evaluate the maximum component,
@@
 where $0 \leq i,j,k \leq n$ and $\alpha \coloneqq i+j+k \leq n$.
-Notice that for $0 \leq \epsilon \leq 3/7$, we have $v \geq u$. 
-We can also assume that $n$ is even, so that we need the sum $\alpha = i+j+k$ to be even for the expression to be positive.
+However, for $0 \leq \epsilon \leq 3/7$, we have $v \geq u$, and so since we assume that $n$ is even we need that the sum $\alpha = i+j+k$ to be even for the expression to be positive.
 
@@
 	&w(\rho_{\rm{S}} | \sigma)_{\rm{max}} = \nonumber\\
-	&(3\Z)^{n} v^n e^{n\beta E_s}\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}.
+	&(3\Z)^{n} v^n e^{n\beta E_s}\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_s)} \right)^{\alpha} \Big\}}.
 \end{align}
-If the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_s)}$ is less than $1$ then the maximum occurs at $\alpha=0$, otherwise it occurs at $\alpha = n$. 
-To determine this transition we set
+If the expression $\frac{u(\epsilon)}{v(\epsilon)} e^{\beta (E_{\rm{max}} - E_s)}$ is less than $1$ then the maximum occurs at $\alpha=0$, otherwise it occurs at $\alpha = n$.
+For a fixed stabilizer state $\sigma$ this transition is determined by the value of the depolarising noise parameter $\epsilon$ of the noisy magic state.
+This transition occurs at $\epsilon = \epsilon_\star$ where
 \begin{equation}\label{eq:noise_transition}
-	\frac{u(\epsilon)}{v(\epsilon)} e^{\beta (E_{\rm{max}} - E_s)} \coloneqq \frac{3-\epsilon}{6-8\epsilon} e^{\beta (E_{\rm{max}} - E_s)} = 1.
+	\frac{u(\epsilon_\star)}{v(\epsilon_\star)} e^{\beta (E_{\rm{max}} - E_s)} = \frac{3-\epsilon_\star}{6-8\epsilon_\star} e^{\beta (E_{\rm{max}} - E_s)} = 1.
 \end{equation}
-We want to find in which cases there exists a threshold noise level $\epsilon_\star$ at which the transition in~\cref{eq:noise_transition} occurs.
-If $E_{\rm{max}} = E_0$, namely if the state negativity lies in the same phase space region as the highest energy, this threshold is constant in temperature and given by $\epsilon_{\star} = 3/7$. 
-Otherwise, there is a threshold temperature value $\beta_\star$ given by
+If $E_{\rm{max}} = E_s$, namely if the state negativity lies in the same phase space region as the highest energy, this threshold is constant in temperature and given by $\epsilon_{\star} = 3/7$.
+However, the condition that $\epsilon_\star \ge 0$ also implies a constraint on the effective temperature of the stabilizer state.
+Specifically, there is a threshold temperature value $\beta_\star$ given by
 \begin{equation}
-	\beta_{\star} \coloneqq \frac{1}{E_{\rm{max}} - E_s} \ln2.
+	\beta_{\star} \coloneqq \frac{1}{E_{\rm{max}} - E_s} \ln2,
 \end{equation}
-Below the threshold, $0 \leq \beta \leq \beta_\star$, the transition is well defined and the threshold noise level at which it occurs is given by
+such that for the regime $0 \leq \beta \leq \beta_\star$ a transition noise level $\epsilon_\star$ exists, and for $\beta > \beta_\star$ no such transition exists.
+The transition value for the noise is given by
 \begin{equation}
@@
 \end{equation}
-This encompasses the case $E_{\rm{max}} = E_0$.
-For $\beta > \beta_\star$, we have
+The quantity $w(\rho_{\rm{S}} | \sigma)_{\rm{max}}$ is now given by
 \begin{equation*}
-	\frac{3-\epsilon}{6-8\epsilon} e^{\beta (E_{\rm{max}} - E_s)} > \frac{3-\epsilon}{6-8\epsilon} 2 \geq \frac{1}{2}2 = 1,
-\end{equation*}
-so there is no transition and we set $\epsilon_\star = 0$.
-
-The maximum component can then be expressed as
-\begin{equation}
 w(\rho_{\rm{S}} | \sigma)_{\rm{max}} =
 	\begin{cases}
-		(3\Z)^{n} v^n e^{n\beta E_s}, &\epsilon \leq \epsilon_{\star},\ \hspace{3pt}\rm{(C1)}	\\
-		(3\Z)^{n} u^n e^{n\beta E_{\rm{max}}}, &\epsilon > \epsilon_{\star}.\ \hspace{5pt}\rm{(C2)} 
+		(3\Z)^{n} v^n e^{n\beta E_s}, &\mbox{if }\epsilon \leq \epsilon_{\star},\ \hspace{3pt}\rm{(C1)}	\\
+		(3\Z)^{n} u^n e^{n\beta E_{\rm{max}}}, &\mbox{if }\epsilon > \epsilon_{\star}.\ \hspace{5pt}\rm{(C2)} 
 	\end{cases}
-\end{equation}
+\end{equation*}
 Case $\rm{(C1)}$ corresponds to $(i,j,k) = (0,0,0)$, so the multiplicity is $m_{000} = 1$, while
@@
 
-Using the appropriate indices in~\cref{eq:ncopy_wrho,eq:ncopy_wsigma}, the first elbow coordinates can now be expressed as
+Using that $F(\beta) = -\beta^{-1} \log \Z$, the first elbow coordinates in the two cases are now given by
 \begin{equation}\label{eq:first_elb_coords}
@@
 \end{equation}
-The Lorenz curves of the initial and target states may each be described by either $\rm{(C1)}$ or $\rm{(C2)}$, depending on the physical parameters $\epsilon, \epsilon', \beta$.
+\ddd{[Are the factors of 3 correct in the previous equation?]} To obtain the distillation bounds from majorization we can now compute the above terms for both the input and output states.
+Depending on the noise parameters $\epsilon, \epsilon'$ for the initial and target states the Lorenz curve data may fall into either case $\rm{(C1)}$ or case $\rm{(C2)}$.
 Specifically, we have three scenarios of relevance to magic distillation:
@@
 \end{enumerate}
-The fourth case $\rm{(C1)} \rightarrow \rm{(C2)}$ is not considered as it would correspond to $\epsilon \leq \epsilon_\star < \epsilon$, which would imply that the output magic state is noisier than the input state.
+The fourth case $\rm{(C1)} \rightarrow \rm{(C2)}$ is not considered as it would correspond to $\epsilon \leq \epsilon_\star < \epsilon'$, which would imply that the output magic state is noisier than the input state.
 

### 2021-04-13 magic_paper.tex
Introduction started. Initial trial line put down.

@@
 
-\title{Thermodynamic fragments for magic states in quantum computation}
+\title{Thermodynamic structures for magic states in quantum computation}
 
@@
 
+\ddd{[Still work in progress. Gotta fix narrative line first.]}
+
+The state-injection model for quantum computation~\cite{cit:bravyi} is a central approach to realising a full-scale, fault-tolerant quantum computer.
+Within this scheme, Clifford unitaries can be implemented in a robust, fault-tolerant way.
+However, due to the Eastin-Knill theorem~\cite{Eastin_2009}, it is impossible to have a universal set of transversal gates, and although Clifford unitaries can be realised transversally, one needs to find ways around the Eastin-Knill restriction.
+The state-injection approach supplements the Clifford unitaries with noisy quantum states, called `magic states', that are outside the set of stabliser states and, when incorporated into Clifford circuits, provide universality.
+The obstacle to this is that the states are invariably noisy and so protocols must be employed to purify many copies of the magic states and improve the overall performance of the induced quantum gates.
+A central question is then: given a number $n$ of noisy magic states how many purified magic states can we obtain within the fault-tolerant set of quantum operations?
+
+To address such questions, concrete distillation protocols have been developed, and there has also been analysis of bounds on distillation rates within natural theoretical frameworks.
+These frameworks provide theories of magic in which one views magic states as ``resource'' states with respect to a natural class of quantum operations that are consider cheap, or ``free''~\cite{Gour_2019}.
+One very natural class of free operations considered are those obtained from Clifford operations, measurements and the ability to discard quantum systems.
+However, there are several other candidate frameworks~\cite{cit:ahmadi, cit:seddon, Wang_2019}.
+
 Magic states are necessary for achieving universal quantum computation within fault-tolerant schemes~\cite{cit:veitch, cit:mari, cit:gottesman, cit:bravyi, cit:knill, Campbell_2011}.
@@
 \begin{center}
-    \emph{Given two magic states $\rho$ and $\rho'$ is there a free operation that can convert $\rho$ to $\rho'$?}
+    \emph{How do physical constraints, such as hardware limitations, noise bias or thermodynamics, restrict magic distillation protocols?}
 \end{center}
 
-We are interested in all resource theories of magic $\R = (\F, \O)$ in which free operations cannot generate any amount of resource. 
-Further denote by $\D$ the set of states considered under the theory, that is the union of free and resource states.
-The structure of such theory is described by a partial order, hereinafter called a \emph{pre-order}, $\prec_{\R}$ between states.
-We write $\rho' \prec_{\R} \rho$ iff there exists $\E \in \O$ such that $\E(\rho) = \rho'$.
-Naturally, states may be incomparable under the given theory, meaning that there exists no free operation that converts one to the other.
-We further call $\R' = (\F', \O')$ a \emph{subtheory} of $\R$ iff $\F' \subseteq \F$ and $\O' \subseteq \O$. 
-The above notation will be used for general resource theories as well.
+Such constraints make stabilizer states inequivalent, and can give rise to stabilizer states that are invariant under the constraints.
+In this work we shall approach this question using tools from statistical mechanics and thermodynamics.
+In particular we shall view \emph{magic as a form of free energy}, relative to the set of stabilizer states.
+This perspective takes the convex set of stabilizer states as a manifold of ``equilibrium'' states.
+However, while a free energy difference exists between two thermodynamic equilibrium states at temperatures $T_1$ and $T_2$, here we focus in on the degree to which the magic state lies off the set of stabilizer states, and therefore magic is more accurately viewed as a form of non-equilibrium free energy that is strictly non-classical.
 
-Formally, the no resource generation condition on the theories translates into two assumptions:
-\begin{enumerate}[I]
-    \item Free operations send free states into free states, $\E: \F \mapsto \F$, for all $\E \in \O$;
-    \item Resource theory $\R$ is a completely free state preserving theory, in the sense that for any $d$--dimensional ancilla system and all free operations $\E$, $(\id_d \otimes \E ) \sigma \in \F$ whenever $\sigma \in \F$.
-\end{enumerate}
-The first assumption simply states that resources cannot be generated for free and is a minimal requirement for a resource theory. 
-An immediate consequence is that if statistical mixing is included in $\O$, then the resource theory is convex.
+Our approach is through the discrete Wigner representation of quantum states, in which all states and operations can be described on a discrete phase space.
+Crucially we focus on magic states with negativity in their Wigner function, which is known to be a necessary condition for universality in the state-injection model.
+However following a thermodynamic perspective in this context raises a novel problem, namely it is impossible to define entropies for quasi-distributions.
+To circumvent this obstacle we make use of a more fundamental tool in thermodynamics -- majorization theory.
 
-Monotones are often used to address the question of state convertibility, although such approaches are usually generic.
+This construction also provides distillation bounds without relying on magic monotones -- instead of projecting the pre-order of magic states onto the real line (which is a monotone) we instead cover the pre-order of states with a collection of simpler `fragments', which admit analysis through the lens of majorization.
+The choice of fragment breaks the equivalence of all stabilizer states in the theory and can be used to consider adding physical constraints on the form of protocols accessible.
 
-The monotonicity condition reflects the no resource generating property of free operations, so that monotones respect the pre-order $\prec_\R$ of the theory.
-A monotone of any general resource theory is a projection of the theory onto the non-negative real numbers, collapsing the pre-order of the theory to the total order defined on the real line.
-Our contribution is the introduction of a generalised notion of \emph{resource projection} which maps a general resource theory onto a subtheory which in principle still retains a partial structure (as opposed to the real line).
-Applying this notion on existing magic theories highlights the hidden stochasticity that governs magic state conversions.
-We show that a magic theory can be subdivided into \emph{fragments} \nick{FIX AND EXPAND}
+We provide a range of upper bounds, which reveal that the thermodynamic structure in the presence of negativity is surprisingly non-trivial and displays a range of features that do not appear in classical statistical mechanics.
+We also discuss how this approach could be used to construct explicit lower bounds on distillation.
+This in turn raises non-trivial questions that are also of interest in statistical mechanics.
+More precisely: what are the conditions for majorization that respects the symplectic structure of phase space?
 
-\subsection{Previous work}
-\label{sec:prev}
-
-The stabiliser theory of magic comprises of the so-called ``stabiliser'' states ($\stab$) and operations ($\so$), while non-stabiliser (resource) states are called magic.
-The stabiliser operations can be expressed in terms of a Stinespring dilation as 
-\begin{equation}
-    \E(\rho) = \tr_E [U(\rho \otimes \sigma_E)U^\dagger],
-\end{equation} 
-for an ancilla stabiliser state $\sigma_E$. 
-The motivation of the theory stems from the fact that stabiliser operations are experimentally straightforward to implement and they can be used to detect and correct errors on the stabiliser states due to their construction \cite{cit:gottesman, cit:gottesman2, cit:gottesman1998}.
-The Gottesman-Knill theorem however indicates that stabiliser operations need to be supplemented with magic states in order to achieve universality, justifying the term ``magic''.
-
-Generalisations of the stabiliser theory appear in the literature intending to include broader classes of operations.
-The class of stabiliser preserving operations ($\spo$) is defined as the set of $\cptp$ maps that send stabiliser states into stabiliser states~\cite{cit:ahmadi}.
-An important subclass of $\spo$ is the set of completely stabiliser preserving operations ($\cspo$)~\cite{cit:seddon}, which intuitively cannot induce ``non-stabiliserness'' even when applied to only part of a quantum state, i.e.
-operations $\E$ such that $(\id_d \otimes \E ) \sigma \in \stab$ for all positive dimensions $d$ whenever $\sigma \in \stab$.
-
+\subsection{Prior text that might be useful}
 Even though non-stabiliserness is a necessary resource for universality, it has been proven insufficient for magic state distillation~\cite{cit:bravyi, cit:campbell}.
@@
 However, there exist mixed states with non-negative Wigner distributions that are not mixtures of stabiliser states~\cite{cit:gross}.
-Therefore, stabiliser-preserving theories have been extended to a theory that preserves state ``Wigner positivity''~\cite{Wang_2019}.
-Informally, it can be considered as the maximal theory of magic $\Rmax = (\Fmax, \Omax)$, where free states have non-negative Wigner distributions and free operations completely preserve this property.\\
 
-\ddd{Things we MUST emphasize:
-\begin{enumerate}
-\item Perhaps a nice lead-in question: ``What happens if we view stabiliser states as thermodynamic equilibrium states and magic as a form of free energy?''
-\item We have found a scenario in which it is impossible to describe a thermodynamic structure using any entropic approach!
-\item We can tackle more `physicsy' questions like: how much magic can be distilled via available operations with some given fixed-point structure? 
-\item This allows a diagnostic on the kind of operations needed to do good distillation. I.e. what fixed point structure should they have?
-\item We go beyond the concept of monotones and replace a monotone with a $\sigma$--fragment.
-\item We can get both upper and lower bounds on magic distillation.
-\end{enumerate}
-}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\newpage
 \section{Phase space representations of quantum states}
@@
 
-\section{Conclusion}
-\label{sec:conc}
+\section{Outlook}
 
-\nick{Summary}
+In this work we have looked at magic through the lens of thermodynamics. Specifically, we find that it can be viewed as a strictly non-classical form of non-equilibrium free energy.
 

### 2021-04-14 magic_paper.tex
minor corrections in sec.V, a bit of info in intro

@@
 In this work we shall approach this question using tools from statistical mechanics and thermodynamics.
-In particular we shall view \emph{magic as a form of free energy}, relative to the set of stabilizer states.
+In particular, we shall view \emph{magic as a form of free energy}, relative to the set of stabilizer states.
 This perspective takes the convex set of stabilizer states as a manifold of ``equilibrium'' states.
@@
 
-Our approach is through the discrete Wigner representation of quantum states, in which all states and operations can be described on a discrete phase space.
-Crucially we focus on magic states with negativity in their Wigner function, which is known to be a necessary condition for universality in the state-injection model.
-However following a thermodynamic perspective in this context raises a novel problem, namely it is impossible to define entropies for quasi-distributions.
-To circumvent this obstacle we make use of a more fundamental tool in thermodynamics -- majorization theory.
+Our approach relies on the discrete Wigner representation of quantum states, in which all states and operations can be described on a discrete phase space.
+Crucially, we focus on magic states with negativity in their Wigner function, which is known to be a necessary condition for universality in the state-injection model.
+However, following a thermodynamic perspective in this context raises a novel problem, namely it is impossible to define entropies for quasi-distributions.
+We circumvent this obstacle by making use of a more fundamental tool in thermodynamics -- majorization theory.
 
-This construction also provides distillation bounds without relying on magic monotones -- instead of projecting the pre-order of magic states onto the real line (which is a monotone) we instead cover the pre-order of states with a collection of simpler `fragments', which admit analysis through the lens of majorization.
-The choice of fragment breaks the equivalence of all stabilizer states in the theory and can be used to consider adding physical constraints on the form of protocols accessible.
+Our construction also provides distillation bounds without relying on magic monotones -- instead of projecting the pre-order of magic states onto the real line (which is a monotone) we instead cover the pre-order of states with a collection of simpler `fragments', which admit analysis through the lens of majorization.
+The choice of fragment breaks the equivalence of all stabilizer states in the theory and can be used to consider adding physical constraints in the form of accessible protocols.
+\nick{We need to give some concrete example here, we keep repeating this ``advantage'' abstractly}
 
@@
 Even though non-stabiliserness is a necessary resource for universality, it has been proven insufficient for magic state distillation~\cite{cit:bravyi, cit:campbell}.
-In fact, all states with non-negative Wigner distributions have been proven to be efficiently classically simulable in~\cite{cit:mari}, a result that serves as a generalization of the Gottesman-Knill theorem.
-The Wigner distribution of a state in odd prime dimensions, formally defined in~\cref{sec:wigner}, arises as the unique quasi-probability representation of quantum theory that identifies non-contextuality exactly with the states that are efficiently classically simulable~\cite{Delfosse_2017, cit:howard2, cit:veitch2}.
+In fact, all states with non-negative Wigner distributions have been proven to be efficiently classically simulable~\cite{cit:mari}, a result that serves as a generalization of the Gottesman-Knill theorem.
+The Wigner distribution of a state in odd prime dimensions arises as the unique quasi-probability representation of quantum theory that identifies non-contextuality exactly with the states that are efficiently classically simulable~\cite{Delfosse_2017, cit:howard2, cit:veitch2}.
 In this framework, the stabiliser states are the only pure states represented with non-negative distributions~\cite{cit:gross3}. 
 However, there exist mixed states with non-negative Wigner distributions that are not mixtures of stabiliser states~\cite{cit:gross}.
+
+The paper is structured as follows.
+In~\cref{sec:ps}, we formally define the Wigner representation of quantum states and outline its relevant properties.
+In~\cref{sec:frag}, we introduce majorisation and apply it on general magic theories.
+We go on to prove magic distillation bounds which account for abstract thermodynamic considerations in~\cref{sec:unital,sec:stab} and conclude in~\cref{sec:outlook}.
 
@@
     \subfigure[][]{%
-    \label{fig:strange}%
-    \includegraphics[height=2cm]{figs/strangestate.pdf}
+    \label{fig:Strange}%
+    \includegraphics[height=2cm]{figs/Strangestate.pdf}
     %\caption{Strange state $\ketbra{S}{S}$}%
@@
     \caption{\textbf{Qutrit Wigner distributions of varying magic.} 
-    \subref{fig:maxmix} Maximally mixed state $\frac{1}{3}\id$; \subref{fig:zero} Stabilizer zero state $\ketbra{0}{0}$; \subref{fig:bound} A non-stabiliser Wigner-positive state; \subref{fig:strange} Magic Strange state $\ket{{\rm{S}}} = \frac{1}{\sqrt{2}}(\ket{1} - \ket{2})$, coined in~\cite{cit:veitch2}.
+    \subref{fig:maxmix} Maximally mixed state $\frac{1}{3}\id$; \subref{fig:zero} Stabilizer zero state $\ketbra{0}{0}$; \subref{fig:bound} A non-stabiliser Wigner-positive state; \subref{fig:Strange} Magic Strange state $\ket{{\rm{S}}} = \frac{1}{\sqrt{2}}(\ket{1} - \ket{2})$, coined in~\cite{cit:veitch2}.
     }%
@@
 \section{Breaking a magic theory into fragments}
+\label{sec:frag}
+
 We wish to consider how physical constraints that may be hardware specific, affect magic distillation rates.
@@
 \subsection{Quasi-probability majorization and non-monotonic Lorenz curves}
+\label{sec:lc}
 
@@
     \centering
-    \includegraphics[height=4.5cm]{figs/lc_strange.pdf}
+    \includegraphics[height=4.5cm]{figs/lc_Strange.pdf}
     \caption{\textbf{A `heretical' family of Lorenz curves.} Traditionally, Lorenz curves for distributions are monotone increasing cumulant functions that reach a maximum value of $1$.
@@
 
-\subsection{Majorisation of negative Wigner distributions within $\sigma$--fragments}\label{sec:major_frag}
+\subsection{Majorisation of negative Wigner distributions within $\sigma$--fragments}
+\label{sec:major_frag}
 
@@
 \subsection{Basic monotones for magic states in a particular fragment}
-\label{sec:lc}
+\label{sec:monotones_frag}
 
@@
 \section{Magic in the unital fragment}
+\label{sec:unital}
 
@@
 This is a particularly powerful set of operations, which for example include all Weyl-covariant channels~\cite{cit:gross3}.
-To make things concrete, we shall consider qutrit magic states ($d=3$) as the Wigner representation is simpler than $d=2$, while they admit non-trivial structure (e.g.
+To make things concrete, we shall consider qutrit magic states ($d=3$) as the Wigner representation is simpler compared to qubits ($d=2$), while they admit non-trivial structure (e.g.
 Hamiltonians with two different energy gaps) and still are sufficiently simple to analyse in detail.
@@
 \item As a family of upper bounds parameterised by an abstract stabiliser state $\sigma$.
-\item The invariant state $\sigma$ reflects actual hardware limitations, a biased noise model, or a statement of the ambient thermal environment for the system.
+\item As a consequence of the actual hardware limitations, noise bias or ambient thermal environment reflected by the invariant state $\sigma$ for the system.
 \end{enumerate}
-In what follows we shall be agnostic about which of the two apply.
+In what follows we shall be agnostic on the interpretation.
 Without loss of generality, we can always write a full-rank stabiliser state $\sigma$ in the form $\sigma =  \frac{1}{\Z_\beta} e^{-\beta H}$ for some $\beta \geq 0$ and effective Hamiltonian $H$.
@@
     \caption{\textbf{Magic distillation bounds within arbitrary stabiliser fragments.}
-  Shown is a contour plot of  $R(\epsilon, \beta)$ where $\beta$ is an effective inverse temperature and $\epsilon$ is the depolarisation error for the magic state.
+  Shown is a contour plot of  $R(\epsilon, \beta)$ where $\beta$ is an effective inverse temperature and $\epsilon$ is the depolarising noise of the magic state.
 The relevant data from the spectrum of the qutrit operator $H$ enters in via $\epsilon_\star(\beta)$ and $\beta_\star$.
@@
 We let $C$ be the unitary transforming each $|\varphi_k\>\<\varphi_k|$ to $|k\>\<k|$.
-Since the Clifford group is the normalizer of the Heisenberg-Weyl group this implies that $C$ is a Clifford unitary.
-Therefore, $C$ maps $\sigma$ to another stabilizer state that is diagonal in the computational basis, and we can therefore assume without loss of generality that $\sigma$ is diagonal in $\{|0\>,|1\>, |2\>\}$.
-However, this choice means that the location of the negative Wigner component $-v(\epsilon)$ of the strange state will be transformed on the discrete phase space.
+Since the Clifford group is the normalizer of the Heisenberg-Weyl group, $C$ is a Clifford unitary.
+Therefore, $C$ maps $\sigma$ to another stabilizer state that is diagonal in the computational basis, and we can assume without loss of generality that $\sigma$ is diagonal in $\{|0\>,|1\>, |2\>\}$.
+However, this choice means that the location of the negative Wigner component $-v(\epsilon)$ of the Strange state will be permuted on the discrete phase space.
 We denote by $E_s$ the eigenvalue of $H$ where the associated eigenvector has Wigner distribution overlapping the negative component of the magic state $C\rho_S(\epsilon)C^\dagger$.
@@
 \begin{equation}
-	\widetilde{\rm{W}}_{\rho_{\rm{S}}|\sigma}(\bmx) = \frac{\W[\bmx]{\rho_S}}{\W[\bmx]{\sigma}},
+	\widetilde{\rm{W}}_{\rho_{\rm{S}}|\sigma}(\bmx) = \frac{\W[\bmx]{\rho_{\rm{S}}}}{\W[\bmx]{\sigma}},
 \end{equation}
@@
     \includegraphics[scale=0.45]{figs/pd_split_thermal.pdf}
-    \caption{\textbf{Qutrit phase space regions for $W_{\rho | \sigma}(\x)$.}
-    Here the negative component of the magic state overlaps the Wigner distribution of $|0\>$.
-The rescaled distribution attains a single value in each of the four regions that is proportional to the value depicted in the region, see~\cref{eq:bmw_rescaled}.
+    \caption{\textbf{Qutrit phase space regions for $W_{\rho_{\rm{S}} | \sigma}(\x)$.}
+    Here, the negative component of the magic state overlaps the Wigner distribution of $|0\>$.
+The rescaled distribution attains a single value in each of the four regions, proportional to the value depicted in the region, see~\cref{eq:bmw_rescaled}.
     }
@@
 
-In order to construct the $n$--copy Lorenz curve $\lc{\rho_{\rm{S}}^{\otimes n}}{\sigma^{\otimes n}}$ we need to order the components of the distribution, $w(\rho_{\rm{S}} | \sigma)_{ijk}$ in decreasing order.
+In order to construct the $n$--copy Lorenz curve $\lc{\rho_{\rm{S}}^{\otimes n}}{\sigma}$ we need to order the components of the distribution, $w(\rho_{\rm{S}} | \sigma)_{ijk}$ in decreasing order.
 In particular, to find the coordinates of the first elbow $(x_0, L_0)$, we need to evaluate the maximum component,
@@
 where $0 \leq i,j,k \leq n$ and $\alpha \coloneqq i+j+k \leq n$.
-However, for $0 \leq \epsilon \leq 3/7$, we have $v \geq u$, and so since we assume that $n$ is even we need that the sum $\alpha = i+j+k$ to be even for the expression to be positive.
+For $0 \leq \epsilon \leq 3/7$, we have $v \geq u$. Since we assume that $n$ is even, we need the sum $\alpha = i+j+k$ to be even too, so that the expression is positive.
 
@@
 If the expression $\frac{u(\epsilon)}{v(\epsilon)} e^{\beta (E_{\rm{max}} - E_s)}$ is less than $1$ then the maximum occurs at $\alpha=0$, otherwise it occurs at $\alpha = n$.
-For a fixed stabilizer state $\sigma$ this transition is determined by the value of the depolarising noise parameter $\epsilon$ of the noisy magic state.
-This transition occurs at $\epsilon = \epsilon_\star$ where
+For a fixed stabilizer state $\sigma$, this transition is determined by the value of the depolarising noise parameter $\epsilon$ of the noisy magic state.
+The transition occurs at $\epsilon = \epsilon_\star$ where
 \begin{equation}\label{eq:noise_transition}
@@
 \end{equation}
-so the multiplicity in each case is $3^n$.
+so the multiplicity in both cases is $3^n$.
 
@@
 \end{equation}
-\ddd{[Are the factors of 3 correct in the previous equation?]} To obtain the distillation bounds from majorization we can now compute the above terms for both the input and output states.
+To obtain the distillation bounds from majorization we can now compute the above terms for both the input and output states.
 Depending on the noise parameters $\epsilon, \epsilon'$ for the initial and target states the Lorenz curve data may fall into either case $\rm{(C1)}$ or case $\rm{(C2)}$.
@@
 \end{enumerate}
-The fourth case $\rm{(C1)} \rightarrow \rm{(C2)}$ is not considered as it would correspond to $\epsilon \leq \epsilon_\star < \epsilon'$, which would imply that the output magic state is noisier than the input state.
+The scenario $\rm{(C1)} \rightarrow \rm{(C2)}$ is not considered as it would correspond to $\epsilon \leq \epsilon_\star < \epsilon'$, which would imply that the output magic state is noisier than the input state.
 
@@
 \section{Outlook}
+\label{sec:outlook}
 

### 2021-04-15 appendix.tex
Corrections and tidying in appendices, left two red comments in sections that need deletion/restructuring

@@
 	\item[(iv)]\label{en:m4} $\sum\limits_{i=1}^n (x_i - t)^+ \leq \sum\limits_{i=1}^n (y_i - t)^+$ for all $t \in \mathbb{R}$ and \vspace{5pt}\\ $\sum\limits_{i=1}^n x_i = \sum\limits_{i=1}^n y_i$, where $(x)^+ = \max{\{x, 0\}}$;
-	\item[(v)]\label{en:m5} $L_{\bmx}(k) \leq L_{\bmy}(k)$ for $k=1,\dots,n-1$	and \vspace{5pt}\\ $L_{\bmx}(n) = L_{\bmy}(n)$.
+	\item[(v)]\label{en:m5} $L_{\bmx}(t) \leq L_{\bmy}(t)$ for $t\in [0,1)$	and \vspace{5pt}\\ $L_{\bmx}(1) = L_{\bmy}(1)$, where $L_{\bmz}(t) = L_{\bmz|\frac{1}{d}\bm{1}}(t)$.
  \end{enumerate}
 \end{proposition}
-\begin{proof}
-	These simple majorisation properties are well-known and proofs can be found in~\cite{cit:marshall,cit:bhatia,cit:nielsen,cit:lostaglio}.
-	The equivalence between (i) and (ii) is the statement of the Hardy, Littlewood and Polya theorem.
-\end{proof}
+	The equivalence between (i) and (ii) is the statement of the Hardy, Littlewood and Polya theorem and is taken as our definition of majorisation in the main text.
+
+	The rest of the properties are well-known and proofs can be found in~\cite{cit:marshall,cit:bhatia,cit:nielsen,cit:lostaglio}.
 
@@
 The embedding map maps the Gibbs distribution to the uniform distribution, $\Gamma_{\bmd}(\bmd) = \bm{1}/N$.
-Then, a non-increasing ordering $\Gamma_{\bmd}(\bmz)^\downarrow$ in the new space, corresponds to the so-called ``$\beta$-ordering'' of the original vector denoted by the permutation $\pi$ in~\cref{def:lc}, mapping $(w_i/d_i) \mapsto (w_i/d_i)^\downarrow$ for all $i=1,\dots,n$.
+Then, a non-increasing ordering $\Gamma_{\bmd}(\bmz)^\downarrow$ in the new space, corresponds to the so-called ``$\beta$-ordering'' of the original vector denoted by the permutation $\pi$ in~\cref{eq:lc}, mapping $(w_i/d_i) \mapsto (w_i/d_i)^\downarrow$ for all $i=1,\dots,n$.
 
@@
     \item[(iv)] $\sum\limits_{i=1}^n (x_i - t d_i)^+ \leq \sum\limits_{i=1}^n (y_i - t d_i)^+$ for all $t \in \mathbb{R}$ and \vspace{5pt}\\ $\sum\limits_{i=1}^n x_i = \sum\limits_{i=1}^n y_i$;
-    \item[(v)] $L_{\bmx|\bmd}(k) \leq L_{\bmy|\bmd}(k)$ for $k=1,\dots,n-1$	 and \vspace{5pt}\\ $L_{\bmx|\bmd}(n) = L_{\bmy|\bmd}(n)$.
+    \item[(v)] $L_{\bmx|\bmd}(t) \leq L_{\bmy|\bmd}(t)$ for $t\in [0,1)$ and \vspace{5pt}\\ $L_{\bmx|\bmd}(1) = L_{\bmy|\bmd}(1)$.
   \end{enumerate}
@@
 	\item[1$\leftrightarrow2$]
-	Suppose there exists a $\bmd$--stochastic $S$ such that $\bmx = S\bmy$ and let $B = \Gamma_{\bmd} \circ S \circ \Gamma_{\bmd}^{-1}$.
-$B$ is a $N$--dimensional bistochastic matrix, since composition of stochastic matrices is stochastic and $(\Gamma_{\bmd} \circ S \circ \Gamma_{\bmd}^{-1}) (\frac{1}{N}\bm{1}) = (\Gamma_{\bmd} \circ S) (\bm{d}) = \Gamma_{\bmd}(\bm{d}) = \frac{1}{N}\bm{1}$.
+	Suppose there exists a $\bmd$--stochastic $A$ such that $\bmx = A\bmy$ and let $B = \Gamma_{\bmd} \circ A \circ \Gamma_{\bmd}^{-1}$.
+$B$ is a $N$--dimensional bistochastic matrix, since composition of stochastic matrices is stochastic and $(\Gamma_{\bmd} \circ A \circ \Gamma_{\bmd}^{-1})\big(\frac{1}{N}\bm{1}\big) = (\Gamma_{\bmd} \circ A) (\bm{d}) = \Gamma_{\bmd}(\bm{d}) = \frac{1}{N}\bm{1}$.
 Then, $B$ maps $\Gamma_{\bmd}({\bmy})$ to $\Gamma_{\bmd}({\bmx})$.
-	Conversely, given $B$, let $S = \Gamma_{\bmd}^{-1} \circ B \circ \Gamma_{\bmd}$.
-	Similarly, $S$ is a $\bmd$--stochastic matrix that maps $\bmy$ to $\bmx$.
-	\item[$2\leftrightarrow3$]\hspace{-5pt}, $2\leftrightarrow4$, $2\leftrightarrow5$ These three statements are equivalent to statements (iii), (iv), (v) in~\cref{prop:major} respectively, for the embedded vectors $\Gamma_{\bmd}({\bmx}), \Gamma_{\bmd}({\bmy})$, which becomes apparent by rewriting
+
+	Conversely, given $B$, let $A = \Gamma_{\bmd}^{-1} \circ B \circ \Gamma_{\bmd}$.
+	Similarly, $A$ is a $\bmd$--stochastic matrix that maps $\bmy$ to $\bmx$.
+	\item[$2\leftrightarrow3$] These \hspace{1pt} three \hspace{1pt} statements \hspace{1pt} are \hspace{1pt} equivalent \hspace{1pt} to \hspace{1pt} state-
+	\item[$2\leftrightarrow4$] \vspace{-7pt} ments (iii), (iv), (v) \hspace{1pt} in~\cref{prop:major} respectively, 
+	\item[$2\leftrightarrow5$] \vspace{-7pt} for the embedded vectors $\Gamma_{\bmd}({\bmx}), \Gamma_{\bmd}({\bmy})$, which becomes apparent by rewriting
 	\begin{align*}
-	&\sum\limits_{i=1}^n \abs{x_i - t d_i} = \sum\limits_{i=1}^n d_i \abs{\frac{x_i}{d_i} - t} = \sum\limits_{i=1}^N \abs{\Gamma_{\bmd}(\bmx)_i - t}, \\
-	&\sum\limits_{i=1}^n (x_i - t d_i)^+ = \sum\limits_{i=1}^N (\Gamma_{\bmd}(\bmx)_i - t)^+, \\
-	&L_{\bmx|\bmd}(k) = L_{\Gamma_{\bmd}(\bmx)}(k'), \text{with}\ k=1,\dots,n\ \\
-	&\text{and}\ k'=1,\dots,N, \nonumber
+	&\hspace{15pt} \sum\limits_{i=1}^n \abs{x_i - t d_i} = \sum\limits_{i=1}^n d_i \abs{\frac{x_i}{d_i} - t} = \sum\limits_{i=1}^N \abs{\Gamma_{\bmd}(\bmx)_i - t}, \\[3pt]
+	&\hspace{15pt} \sum\limits_{i=1}^n (x_i - t d_i)^+ = \sum\limits_{i=1}^N (\Gamma_{\bmd}(\bmx)_i - t)^+ \text{ and} \\[6pt]
+	&\hspace{15pt} L_{\bmx|\bmd}(t) = L_{\Gamma_{\bmd}(\bmx)}(t),
 	\end{align*} 
@@
 \begin{enumerate}
-    \item The identity channel $1_{\rm{C}}: \D \mapsto \D$ belongs to every $\sigma$--fragment, as $1_{\rm{C}} \in \O$ and $1_{\rm{C}}\sigma = \sigma$ for all $\sigma \in \F$.
+    \item The identity channel $1_{\rm{C}}$ belongs to every $\sigma$--fragment, as $1_{\rm{C}} \in \O$ and $1_{\rm{C}}\sigma = \sigma$ for all $\sigma \in \F$.
 
@@
 
-We now prove a result referenced in~\cref{sec:lc}.
+We now prove a result on the independence of the Lorenz curve constraints.
 \begin{proposition}\label{thm:elbows}
@@
 \end{proof}
-This theorem is of practical importance in calculating the necessary distillation constraints derived via majorization in $\sigma$--fragments.
+This theorem is of practical importance in reducing the necessary distillation constraints derived via majorization in $\sigma$--fragments.
 
@@
 Consider an experiment consisting of $n$ trials of throwing a $p$--coin, that is a coin with probability $p$ of landing on one side and $1-p$ of landing on the other.
-We express the sum over an even number of successful trials $\Phi_+$ and the sum over an odd number of successful trials $\Phi_-$,
+We express the sums over an even number $m$ of successful trials $\Phi_+$ and an odd number $m$ of successful trials $\Phi_-$,
 \begin{align}	
-	\Phi_+(a; n, p) &\coloneqq \sum\limits_{\ell=0}^{a/2} \binom{n}{2\ell} p^{2\ell} (1-p)^{n-2\ell}, \nonumber\\ 
+	\Phi_+(m; n, p) &\coloneqq \sum\limits_{\ell=0}^{m/2} \binom{n}{2\ell} p^{2\ell} (1-p)^{n-2\ell}, \nonumber\\ 
 	&\text{for even integers } m\in[0,n], \label{eq:fp_app} \\
-	\Phi_-(a; n, p) &\coloneqq \sum\limits_{\ell=1}^{(a-1)/2} \binom{n}{2\ell+1} p^{2\ell+1} (1-p)^{n-(2\ell+1)}, \nonumber\\ 
+	\Phi_-(m; n, p) &\coloneqq \sum\limits_{\ell=1}^{(m-1)/2} \binom{n}{2\ell+1} p^{2\ell+1} (1-p)^{n-(2\ell+1)}, \nonumber\\ 
 	&\text{for odd integers }m\in[0,n]. \label{eq:fn_app}
@@
 Note that index $m$ only takes even (odd) values when labelling $\Phi_+$ ($\Phi_-$).
-In~\cref{app:lcsu_coord_elb}, we will use $\Phi_+$ and $\Phi_-$ to express the elbow coordinates of Lorenz curves in the unital fragment.
+In~\cref{app:lcsu_coord}, we will use $\Phi_+$ and $\Phi_-$ to express the elbow coordinates of Lorenz curves in the unital fragment.
 
-We also define the classical entropy of a $p$--coin as well as the classical relative entropy between a $p$--coin and a $q$--coin,
+We also define the classical entropy of a $p$--coin and the classical relative entropy between a $p$--coin and a $q$--coin,
 \begin{align}
@@
 \begin{lemma}\label{lem:comb_bounds}
-	For all $\ell\in [1,np-1]$,
+	For all $\ell\in [1,n-1]$,
 	\begin{align}
-		&\left[ 8\ell\left(1-\frac{\ell}{np}\right) \right]^{-\frac{1}{2}} 2^{n S\left(\frac{\ell}{np}\right)} \leq \binom{np}{\ell} \leq \\
-		&\left[ 2\pi \ell\left(1-\frac{\ell}{np}\right) \right]^{-\frac{1}{2}} 2^{n S\left(\frac{\ell}{np}\right)}.
+		&\left[ 8\ell\left(1-\frac{\ell}{n}\right) \right]^{-\frac{1}{2}} 2^{n S\left(\frac{\ell}{n}\right)} \leq \binom{n}{\ell} \leq \\
+		&\left[ 2\pi \ell\left(1-\frac{\ell}{n}\right) \right]^{-\frac{1}{2}} 2^{n S\left(\frac{\ell}{n}\right)}.
 	\end{align}
 \end{lemma}
-\begin{proof}
-	For $\ell = 1,2, np-1, np-2$ check by direct calculation.	
-	For all other cases, use Stirling's approximation. 
-	\nick{CITE}
-\end{proof}
+The proof provided in~\cite{cit:ash} proceedx with direct calculation for the edge cases $\ell = 1,2, n-1, n-2$ and use Stirling's approximation for the remaining cases.
+
 With the help of this lemma, we directly arrive at 
 \begin{theorem}\label{thm:bounds_strict}
-	Given fixed $n>0$ and $p$, $\Phi_+, \Phi_-$ satisfy the following bounds:
+	Given fixed positive integer $n$ and probability $p$, $\Phi_+, \Phi_-$ satisfy the following bounds:
 	\begin{align*}
 		\begin{split}
-		&\text{1. } \Phi_+(a; n, p) \geq \sum\limits_{\ell=0}^{np/2}\left[ 16\ell\left(1-\frac{2\ell}{np}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{2\ell}{nf}}{p}}, \\
-		&\hspace{14pt} \text{for all even } a\in [2,np] \\
-		&\text{2. } \Phi_+(a; n, p) \leq \sum\limits_{\ell=0}^{np/2}\left[ 4\pi\ell\left(1-\frac{2\ell}{nf}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{2\ell}{np}}{p}}, \\
-		&\hspace{14pt} \text{for all even } a\in [2,np] \\
-		&\text{3. } \Phi_-(a; n, p) \geq \sum\limits_{\ell=1}^{(np-1)/2}\left[ 16(\ell+1)\left(1-\frac{2\ell+1}{np}\right) \right]^{-\frac{1}{2}} \times \\
-		&\hspace{14pt} \times 2^{-n\ent{\frac{2\ell+1}{np}}{p}},\ \text{for all odd }a\in [1,np] \\
-		&\text{4. } \Phi_-(a; n, p) \leq \sum\limits_{\ell=1}^{(np-1)/2}\left[ 4\pi(\ell+1)\left(1-\frac{2\ell+1}{nf}\right) \right]^{-\frac{1}{2}} \times \\
-		&\hspace{14pt} \times 2^{-n\ent{\frac{2\ell+1}{np}}{p}},\ \text{for all odd } a\in [1,np]
+		&\text{1. } \Phi_+(m; n, p) \geq \sum\limits_{\ell=0}^{m/2}\left[ 16\ell\left(1-\frac{2\ell}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{2\ell}{n}}{p}}, \\
+		&\hspace{14pt} \text{for all even } m\in [2,n] \\
+		&\text{2. } \Phi_+(m; n, p) \leq \sum\limits_{\ell=0}^{m/2}\left[ 4\pi\ell\left(1-\frac{2\ell}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{2\ell}{n}}{p}}, \\
+		&\hspace{14pt} \text{for all even } a\in [2,n] \\
+		&\text{3. } \Phi_-(m; n, p) \geq \sum\limits_{\ell=1}^{(m-1)/2}\left[ 16(\ell+1)\left(1-\frac{2\ell+1}{n}\right) \right]^{-\frac{1}{2}} \times \\
+		&\hspace{14pt} \times 2^{-n\ent{\frac{2\ell+1}{n}}{p}},\ \text{for all odd }a\in [1,n] \\
+		&\text{4. } \Phi_-(m; n, p) \leq \sum\limits_{\ell=1}^{(m-1)/2}\left[ 4\pi(\ell+1)\left(1-\frac{2\ell+1}{n}\right) \right]^{-\frac{1}{2}} \times \\
+		&\hspace{14pt} \times 2^{-n\ent{\frac{2\ell+1}{n}}{p}},\ \text{for all odd } a\in [1,n]
 		\end{split}
@@
 
-\subsection{Strange state Lorenz curve elbow coordinates in the unital fragment}\label{app:lcsu_coord_elb}
-The Wigner distribution of the $n$--copy qutrit maximally mixed state $\left(\id/3\right)^{\otimes n}$ is the uniform distribution 
-\begin{equation}\label{eq:wu}
-	\W{\left(\id/3\right)^{\otimes n}} = \Bigg( \overbrace{\frac{1}{9^n}, \dots, \frac{1}{9^n}}^{9^n} \Bigg).
+\subsection{Lorenz curve coordinates in the unital fragment}\label{app:lcsu_coord}
+The Wigner distribution of the $n$--copy qutrit maximally mixed state $\left(\id/3\right)^{\otimes n}$ is the uniform probability distribution over the phase space, consisting of $9^n$ components equal to $9^{-n}$.
+The Wigner distribution of the 1-copy $\epsilon$--noisy Strange state $\rho_{\rm{S}}(\epsilon)$ in the unital fragment consists of some permutation of a single negative component
+\begin{equation}
+	- v(\epsilon) \coloneqq - \left( \frac{1}{3} -\frac{4}{9}\epsilon \right),
 \end{equation} 
-The Wigner distribution of the 1-copy $\epsilon$--noisy Strange state $\rho_{\rm{S}}(\epsilon)$ in the unital fragment is a permutation of 
-\begin{equation}\label{eq:wsu}
-	\W{\rho_{\rm{S}}(\epsilon)} = \Bigg( \overbrace{\frac{1}{6} - \frac{1}{18}\epsilon, \dots, \frac{1}{6} - \frac{1}{18}\epsilon}^8, \overbrace{-\frac{1}{3} + \frac{4}{9}\epsilon}^1 \Bigg)
+and $8$ positive components
+\begin{equation}
+	u(\epsilon) \coloneqq \frac{1}{6} -\frac{1}{18}\epsilon.
 \end{equation}
-The two distinct components are plotted~\cref{fig:noisys} as a function of noise. 
-It is clear that in the unital fragment the Strange state contains Wigner negativities in the regime $0 \leq \epsilon \leq \tfrac{3}{4}$.
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.7]{figs/noisys.pdf}
-    \caption{\textbf{Wigner components of the noisy Strange state.} 
-    In the interval $0 \leq \epsilon < 3/7$, the negative component is larger than the positive components.
-    At $\epsilon = 3/7$ the Wigner distribution is $(-\frac{1}{7},\frac{1}{7},\dots,\frac{1}{7})$.
-    In the interval $3/7 < \epsilon < 3/4$, the positive components are larger than the negative component.
-    In the interval $3/4 \leq \epsilon \leq 1$, there is no negativity.
-    }
-    \label{fig:noisys}
-\end{figure}
+where in the unital fragment we need the condition $0 \leq \epsilon < 3/4$, so that the state contains some Wigner negativity ($-v < 0$).
+It is also clear that $v \geq u$ in the interval $0 \leq \epsilon \leq 3/7$, while $u > v$ in the interval $3/7 < \epsilon < 3/4$.
 
-The Wigner distribution of the $n$--copy $\epsilon$--noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ in the unital fragment is given by the convolution $\W{\rho_{\rm{S}}(\epsilon)^{\otimes n}} = \rm{W}_{\rho_{\rm{S}}(\epsilon)}^{\otimes n}$.
+The Wigner distribution of the $n$--copy $\epsilon$--noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ in the unital fragment is given by the convolution $\W{\rho_{\rm{S}}(\epsilon)^{\otimes n}} = W_{\rho_{\rm{S}}(\epsilon)}^{\otimes n}$.
 In general, $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ contains $n + 1$ distinct components, labelled $0,\dots, n$.
 We present the distinct Wigner components of $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ along with their multiplicites in~\cref{tab:lcsu}.
-Note that LHS (RHS) refers to elbow coordinates $i$ on the left of and including (right of) the maximum, precisely
+Note that LHS (RHS) refers to elbow coordinates $i$ on the left of and including (right of) the Lorenz curve maximum, stated precisely as
 \begin{align}
-&\text{LHS: } 0 \leq i \leq \left\lfloor \frac{n}{2} \right\rfloor ; \\
+&\text{LHS: } 0 \leq i \leq \left\lfloor \frac{n}{2} \right\rfloor \text{ and} \\
 &\text{RHS: } \left\lfloor \frac{n}{2} \right\rfloor +1 \leq i \leq n.
@@
   \end{tabular}
-  \caption{Wigner components $w_{i}(n, \epsilon)$ of $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ along with their multiplicities $m_{i}(n, \epsilon)$ in decreasing order in $i,\ 0 \leq i \leq n$.
-  The order changes depending on the noise level $\epsilon$, the parity of the number of copies $n$ and the parity of the components (LHS vs RHS).
+  \caption{Wigner components $w_{i}(n, \epsilon)$ of $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ along with their multiplicities $m_{i}(n, \epsilon)$, with $0 \leq i \leq n$.
+  The expressions change depending on the noise level $\epsilon$, the parity of the number of copies $n$ and whether the index $i$ is lower or higher than the index of the Lorenz curve maximum (LHS vs RHS).
   Multiplication $2i$ is considered modulo $(n+1)$.}
@@
 
-For example, the distribution of state $\rho_{\rm{S}}(0)^{\otimes 2}$ is
+Every Lorenz curve in the unital fragment contains $n$ elbows, which, along with the boundary points $(x_{-1}, L_{-1}) = (0,0)$ and $(x_{n}, L_{n}) = (1,1)$, are labelled by 
 \begin{equation*}
-	\begin{split}
-	\rm{W}_{\rho_{\rm{S}}(0)^{\otimes 2}} = \Bigg( &\overbrace{\left( -\frac{1}{3} \right)^2}^1, \overbrace{\left( \frac{1}{6} \right)^2, \dots, \left( \frac{1}{6} \right)^2}^{64}, \\
-	&\overbrace{ -\frac{1}{3} \cdot \frac{1}{6}, \dots, -\frac{1}{3} \cdot \frac{1}{6}}^{16} \Bigg)
-	\end{split}
+\{(x_{i}, L_{i})\}_{i=-1,0,\dots,n}.
 \end{equation*}
-
-Every standard Lorenz curve contains $n$ elbows, labelled by 
-\begin{equation*}
-\{(x_{i}, L_{i})\}_{i=-1,0,\dots,n}\ ,
-\end{equation*}
-where the boundary points $(x_{-1}, L_{-1}) = (0,0)$ and $(x_{n}, L_{n}) = (1,1)$ are also included.
-The maximum is the $(\lfloor n/2 \rfloor)$-th elbow and its coordinates are calculated by collecting all the positive Wigner components,
+The maximum is the $\lfloor n/2 \rfloor$-th elbow and its coordinates are calculated by collecting all the positive Wigner components,
 \begin{align}
@@
 
-Expressions for all the elbow coordinates follow from summing up the Wigner components in decreasing order and we present the elbow coordinates for standard Lorenz curves in~\cref{tab:lcsu_coord_elb_app}.
+Expressions for all the elbow coordinates follow from summing up the Wigner components in decreasing order.
+In~\cref{tab:lcsu_coord_elb_app}, we present the elbow coordinates of the $n$-copy, $\epsilon$--noisy Strange state Lorenz curve in the unital fragment for any combination of parameters $n, \epsilon$.
 \begin{table}[h]
@@
   \begin{tabular}{c|c|c|r|r}
-    \multicolumn{3}{c|}{Case} & \multicolumn{1}{c}{$x_{i}$} & \multicolumn{1}{|c}{$L_{i}$} \\[0.5ex]\hline
+\multicolumn{3}{c|}{\multirow{2}{*}{Case}} & \multicolumn{1}{c|}{$x_{i}$} & \multicolumn{1}{c}{$L_{i}$} \\
+    \multicolumn{3}{c|}{} & \multicolumn{1}{c|}{$x_{i} - x_{\lfloor n/2 \rfloor}$} & \multicolumn{1}{c}{$L_{i} - L_{\lfloor n/2 \rfloor}$} \\[0.5ex]\hline 
     \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$0\leq \epsilon < \frac{3}{7}$}}} & \hspace{0.8ex}\multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ even}}}\hspace{0.8ex} & LHS & $\Phi_+\left(2i;n,\frac{8}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\
-    & & RHS & $x_{\lfloor n/2 \rfloor} + \Phi_-\left(2i;n,\frac{1}{9}\right)$ & $L_{\lfloor n/2 \rfloor} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-\left(2i;n,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
+    & & RHS & $\Phi_-\left(2i;n,\frac{1}{9}\right)$ & $- \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-\left(2i;n,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
     & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $\Phi_-\left(2i;n,\frac{8}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_-\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\
-    & & RHS & $x_{\lfloor n/2 \rfloor} + \Phi_-\left(2i;n,\frac{1}{9}\right)$ & $L_{\lfloor n/2 \rfloor} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-\left(2i;n,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
+    & & RHS & $\Phi_-\left(2i;n,\frac{1}{9}\right)$ & $- \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-\left(2i;n,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
     \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$\frac{3}{7}\leq \epsilon < \frac{3}{4}$}}} & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ even}}} & LHS & $\Phi_+\left(2i;n,\frac{1}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+\left(2i;n,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\
-    & & RHS & $x_{\lfloor n/2 \rfloor} + \Phi_-\left(2i;n,\frac{8}{9}\right)$ & $L_{\lfloor n/2 \rfloor} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
+    & & RHS & $\Phi_-\left(2i;n,\frac{8}{9}\right)$ & $- \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
     & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $\Phi_+\left(2i;n,\frac{1}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+\left(2i;n,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\
-    & & RHS & $x_{\lfloor n/2 \rfloor} + \Phi_+\left(2i;n,\frac{8}{9}\right)$ & $L_{\lfloor n/2 \rfloor} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_+\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
+    & & RHS & $\Phi_+\left(2i;n,\frac{8}{9}\right)$ & $- \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_+\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
   \end{tabular}
-  \caption{Standard Lorenz curves elbow coordinates.
-  The expresion depends on the noise level $\epsilon$, the parity of the number of copies $n$ and the location of the elbow relative to the maximum (LHS vs RHS).
+  \caption{Lorenz curve elbow coordinates in the unital fragment.
+  The coordinate expressions depend on the noise level $\epsilon$, the parity of the number of copies $n$ and the location of the elbow relative to the maximum (LHS vs RHS).
   Multiplication $2i$ is considered modulo $(n+1)$.
-  Note that the Lorenz curve boundary points are $(x_{-1}, L_{-1}) \coloneqq (0,0)$ and $(x_{n}, L_{n}) = (1,1)$.
+  For completeness, note that $(x_{-1}, L_{-1}) \coloneqq (0,0)$ is not included in the coordinate expressions.
   }
@@
 
-\subsection{Standard Lorenz curve coordinates}\label{app:lcsu_coord}
-We can get explicit expressions for all $9^{n}$ points of the standard Lorenz curve $\lc{\rho_{\rm{S}}(\epsilon)^{\otimes n}}{\id/3}$, in terms of the elbow coordinates:
+We can get explicit expressions for all $9^{n}$ points of the Lorenz curve $\lc{\rho_{\rm{S}}(\epsilon)^{\otimes n}}{(\id/3)^{\otimes n}}$, in terms of the elbow coordinates:
 \begin{align}
@@
 
-For visualisation purposes, we plot the Lorenz curve of state $\rho_{\rm{S}}(0)^{\otimes 2}$.
-\begin{figure}[t]
-    \centering
-    \includegraphics[scale=0.6]{figs/lcpoints.pdf}
-    \caption{\textbf{All points on the Lorenz curve are uniformly distributed.}
-    \cref{eq:x,eq:l}) capture the coordinates of all points up to the maximum.
-    }
-    \label{fig:lc}
-\end{figure}
-
 Consider the state 
 \begin{equation*}
-\rho_{\rm{S}}(n', \epsilon, n-n') \coloneqq \rho_{\rm{S}}(\epsilon)^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n-n')},
+\rho_{\rm{S}}(\epsilon)^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n-n')},
 \end{equation*}
-
-Tensoring with the maximally mixed state keeps the Lorenz curve unchanged, but increases the resolution of (the uniformly distributed) points.
+where tensoring with the maximally mixed state keeps the Lorenz curve unchanged, but increases the resolution of (the uniformly distributed) points.
 The new point coordinates are given by:
@@
 \subsection{Strange state MSD in the unital fragment}\label{app:lc_compare}
+\nick{DELETE SECTION (?)}
+
 Consider the Strange state MSD process in the unital fragment,
@@
 
-\section{Technical details of bound derivation in stabiliser fragments}
+\section{Technical details of the derivation of distillation bounds}
 \label{app:lcst_technical}
@@
 \label{app:elb_constraints}
-Here we prove the majorization constraints that arise by considering the first and last elbow of the initial stata only.
+Here we prove the majorization constraints that arise by only considering the first or the last elbow of the initial state.
 \begin{proposition}\label{prop:first_elb}
-	Consider a magic state interconversion as in~\cref{eq:stdist}, where we denote by $(x_0, L_0)$ and $(x'_0, L'_0)$ the first elbow coordinates of the initial and target states respectively.
-	If $x_0 < x'_0$, then it holds that
+	Consider a magic state process as in~\cref{eq:stdist}, where we denote by $(x_0, L_0)$ and $(x'_0, L'_0)$ the first elbow coordinates of the initial and target states respectively, where $x_0 < x'_0$.
+	The process is possible only if
 \begin{equation}\label{eq:first_elb_bound1}
@@
 \end{equation}
-We need $L_0 \geq L_\star'$ and rearranging we get~\cref{eq:first_elb_bound1}.
+The process is possible only if $L_0 \geq L_\star'$ and rearranging we get~\cref{eq:first_elb_bound1}.
 \end{proof}
@@
 \begin{proposition}\label{prop:last_elb}
-	Consider a magic state interconversion as in~\cref{eq:stdist}, where we denote by $(x_E, L_E)$ and $(x'_E, L'_E)$ the last elbow coordinates of the initial and target states respectively.
-	If $x_E > x'_E$, then it holds that
+	Consider a magic state interconversion as in~\cref{eq:stdist}, where we denote by $(x_E, L_E)$ and $(x'_E, L'_E)$ the last elbow coordinates of the initial and target states respectively, where $x_E > x'_E$.
+	The process is possible only if
 \begin{equation}\label{eq:last_elb_bound1}
@@
 \end{equation}
-We need $L_E \geq L_\star'$ and rearranging we get~\cref{eq:last_elb_bound1}.
+The process is possible only if $L_E \geq L_\star'$ and rearranging we get~\cref{eq:last_elb_bound1}.
 \end{proof}
@@
 \label{app:cmpairs}
-In general, a $1$--copy $d$--dimensional state $\rho$ is defined exactly by its $d^2$--dimensional Wigner distribution $\W{\rho}$. 
+In general, a $1$--copy $d$--dimensional state $\rho$ is described exactly by its $d^2$--dimensional Wigner distribution $\W{\rho}$. 
 The distribution $\W{\rho}$ is usually defined on the phase space, but it can be convenient to define it using pure vector notation. 
@@
 As an example, two complete sets of pairs for the Strange state are $\{( -1/3, 1), ( 1/6, 8)\}$ and $\{(-1/3, 1), (1/6, 2), (1/6, 3), (1/6, 3)\}$.
+The latter corresponds to the phase space split in~\cref{fig:pd_split}
 
@@
 \begin{lemma}\label{lem:ncopycomponents}
-	Let $W$ be a distribution defined by a complete set of component-multiplicity pairs $\{(w_i, m_i)\}_{i=1,\dots,D}$ with $D \leq {\rm{dim}}\hspace{1pt}W$ and consider the distribution $W^{\otimes n}$ obtained by taking the Kronecker product $W \otimes \dots \otimes W$ between $n$ copies of $W$.
+	Let $W$ be a distribution defined by a complete set of component-multiplicity pairs $\{(w_i, m_i)\}_{i=1,\dots,D}$ with $D \leq {\rm{dim}}\hspace{1pt}W$ and consider the distribution $W^{\otimes n}$ obtained by taking the $n$-fold (Kronecker) product $W \otimes \dots \otimes W$ between $n$ copies of $W$.
 
@@
 
-Index vector $\bmk$ has $D-1$ independent components and in the proof of our main theorem in~\cref{sec:stab} we have $D=4$, so we simplify the notation by writing the component and multiplicity vectors of the $n$--copy state distributions as $m_{ijk}, w(\rho_{\rm{S}})_{ijk}, w(\gamma)_{ijk}$ and $w(\rho_{\rm{S}}|\gamma)_{ijk}$, where $i,j,k$ are the 3 independent index components.
+Index vector $\bmk$ has $D-1$ independent components and in the proof of our main theorem in~\cref{sec:stab} we have $D=4$, so we simplify the notation by writing the component and multiplicity vectors of the $n$--copy state distributions as $m_{ijk}, w(\rho_{\rm{S}})_{ijk}, w(\sigma)_{ijk}$ and $w(\rho_{\rm{S}}|\sigma)_{ijk}$, where $i,j,k$ are the 3 independent index components.
 
@@
 
-1. $\rm{(C1)} \rightarrow \rm{(C1)}$.
+$\rm{(C1)} \rightarrow \rm{(C1)}$.
 We know from statistical physics that $e^{-\beta E_0} / \Z_\beta \leq 1$, so
@@
 
-2. $\rm{(C2)} \rightarrow \rm{(C1)}$.
+$\rm{(C2)} \rightarrow \rm{(C1)}$.
 We now use the slightly altered inequality $e^{-\beta E_{\rm{max}}} / \Z_\beta \leq 1$ to proceed,
@@
 
-3. $\rm{(C2)} \rightarrow \rm{(C2)}$.
+$\rm{(C2)} \rightarrow \rm{(C2)}$.
 Similarly in this scenario,
@@
 
-\nick{LAST ELBOW BOUND}
+\subsection{Deriving distillation bounds from the last elbow}
+\label{sec:last_elb}
+
+\nick{RESTRUCTURE}
 

### 2021-04-15 magic_paper.tex
Corrections and tidying in appendices, left two red comments in sections that need deletion/restructuring

@@
 \begin{document}
-% Distillation rate vs bound
-% Proofs in App. A
+% Write bounds as 1 + ln{}/{} or 1 - (-ln{})/{} ?
 % Sec: App. D
@@
 % Sec: Lower bounds
-% Sec: Intro
-% Sec: Abstract
+
+% Find more (all) refs
 % Figs consistency (esp. figs 3,4,5 and 1,6) + Figure 0 ?
+
 % Eq. numbering in last line always
-% British vs US english
+% UK vs US english
 % Spacing (fig positioning, sections, paragraphs, QED symbols)
@@
 Magic states are necessary for achieving universal quantum computation within fault-tolerant schemes~\cite{cit:veitch, cit:mari, cit:gottesman, cit:bravyi, cit:knill, Campbell_2011}.
-Identifying magic as a resource for quantum universality has led to several theories which try to provide a framework for its quantification and manipulation \cite{cit:veitch2, cit:howard, Wang_2019, Seddon_2021}.
+Identifying magic as a resource for quantum universality has led to several theories which try to provide a framework for its quantification and manipulation \cite{cit:veitch2, cit:howard, Wang_2019, Seddon_2021, Okay_2021}.
 The main question that such a theory attempts to answer is:
@@
 Now, given two $n$--component vectors $\w$ and $\r$ we define the \emph{Lorenz curve} of $\w$ relative to $\r$, denoted $L_{\w|\r}(x)$, as the piece-wise linear function that passes through $(0,0)$ and the $n$ points
-\begin{equation}\label{eq:lorenz}
+\begin{equation}
+\label{eq:lc}
         (x_k,L_{\w|\r}(x_k)) =\left( \frac{1}{R}\sum_{i=1}^k r_{\pi(i)}, \sum_{i=1}^k w_{\pi(i)} \right),
@@
 If we have a magic state $\rho$ that has negativity in its Wigner representation, then as discussed, its Lorenz curve over-shoots $1$ and reaches a non-trivial maximum $L_\star$ that depends on the particular state.
-It is easy to establish the following result.
+In fact, we can establish the following general result.
 \begin{lemma}\label{lem:lcmax}
@@
 We now consider the task of purifying $n$ copies of a noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ as given in~\cref{eq:noisysn} into a smaller number of copies $n'$ of a less noisy Strange state $\rho_{\rm{S}}(\epsilon')^{\otimes n'}$, with $\epsilon' < \epsilon$ and $n' \leq n$.
-Since we work in the unital fragment, the only free state is the maximally mixed state, and we choose to tensor in $n'-n$ auxiliary copies of it to the output.
-This highlights that we are working in the unital fragment, while it does not affect neither the distillation process nor our analysis, since the Lorenz curves remain unaffected.
+Since we work in the unital fragment, the maximally mixed state is free and we choose to tensor in $n'-n$ auxiliary copies of it to the output, highlighting that we are working in the unital fragment.
+This affects neither the distillation process nor our analysis, since the Lorenz curves remain unaffected.
 More generally, it is easy to see that
 \begin{equation}
-	L_{\rho |\sigma} (x) = L_{\rho \otimes \sigma |\sigma}(x),
+	L_{\rho |\sigma} (x) = L_{\rho \otimes \sigma |\sigma \otimes \sigma}(x),
 \end{equation}
@@
 The Wigner distribution of $n$ copies of the state is obtained by the $n$-fold product of the single copy distribution, and the Lorenz curve $L_{\rho|\sigma}(x)$ for $\rho = \rho_S(\epsilon)^{\otimes n}$ and $\sigma = (\I/3)^{\otimes n}$ is readily computed for any $n$ and $\epsilon$, and the full details are provided in~\cref{app:lcsu_technical}.
-We highlight that the non-trivial element that arises for quasi-distributions is that the product of negative components can generate a positive $n$-fold component, so the ordering of the components of $W_{\rho |\sigma}(x)$ depends on whether $-v(\epsilon)$ appears to an even or odd power in the expression below.
+We highlight that the non-trivial element that arises for quasi-distributions is that the product of negative components can generate a positive $n$-fold component, so the ordering of the components of $W_{\rho |\sigma}(x)$ depends on whether $-v(\epsilon)$ appears to an even or odd power in the expression of~\cref{eq:wigu}.
 
@@
 	m_i &= 8^{i}\binom{n}{i}, \\
-	w_i &= u^{i}(-v)^{n-i},
+	w_i &= u^{i}(-v)^{n-i}, \label{eq:wigu}
 \end{align}
 where index $i$ runs through $0, \dots, n$, and we assume for simplicity of exposition that $n$ is even and the noise level is not high, $\epsilon \leq 3/7$, so that $v \geq u$.
-The details of this scenario, along with the other possible scenarios that occur depending on the parity of the number of copies and the noise level, are provided in~\cref{app:lcsu_coord_elb}.
+The details of this scenario, along with the other possible cases that occur depending on the noise level and the parity of the number of copies, are provided in~\cref{app:lcsu_technical}.
 
@@
 However, it turns out that a simple and sufficiently non-trivial constraint can be obtained by considering the first elbow of the Lorenz curves. 
-The largest Wigner component of occurs for $i=0$ and is unique, so the first elbow coordinates for $\rho_S(\epsilon)^{\otimes n}$ are given by $(1/9^n, v(\epsilon)^n)$, while for $\rho_S(\epsilon')^{\otimes n'}$ the first elbow occurs at $(1/9^{n'}, v(\epsilon')^{n'})$.
+The largest Wigner component occurs for $i=0$ and is unique, so the first elbow coordinates for $\rho_S(\epsilon)^{\otimes n}$ are given by $(1/9^n, v(\epsilon)^n)$, while for $\rho_S(\epsilon')^{\otimes n'}$ by $(1/9^{n'}, v(\epsilon')^{n'})$.
 
-The first elbow constraint involves a simple interpolation, done in~\cref{app:elb_constraints}, in order to find the coordinates of the point which is vertically aligned with the first elbow of the input state, leading to the constraint
+The first elbow constraint involves a simple interpolation, done in~\cref{app:elb_constraints}, in order to find the coordinates of the output Lorenz curve point which is vertically aligned with the first elbow of the input Lorenz curve.
+Comparing these two points leads to the bound
 \begin{equation}
@@
 \end{equation}
-
-Specifically for the limiting case of distilling pure magic states ($\epsilon'=0$), we obtain an upper bound in the unital fragment given by
+For the limiting case of distilling pure magic states ($\epsilon'=0$), we obtain an upper bound in the unital fragment given by
 \begin{equation}
@@
 \end{equation}
-which attains four distinct values on the phase space, naturally splitting it into four regions as illustrated in the~\cref{fig:pd_split_thermal}.
+which attains four distinct values on the phase space, naturally splitting it into four regions as illustrated in the~\cref{fig:pd_split}.
 \begin{figure}[h]
@@
     }
-    \label{fig:pd_split_thermal}
+    \label{fig:pd_split}
 \end{figure}

### 2021-04-15 magic_paper.tex
Intro almost done. Needs references added.

@@
 
-\title{Thermodynamic structures for magic states in quantum computation}
+\title{Thermodynamic constraints for magic states in quantum computation}
 
@@
 
-\section{Introduction and background}
-\label{sec:intro_prev}
-
-\subsection{Introduction}
+\section{Introduction}
 \label{sec:intro}
 
-\ddd{[Still work in progress. Gotta fix narrative line first.]}
+The past few years have seen rapid progress towards the goal of a fault-tolerant quantum computer\ddd{[CITE]}.
+However many challenges remain and there is increasing need for theory to take into account physical limitations of the hardware involved.
+The surface code~\cite{cit:bravyi}\ddd{[CITE MORE]} is a leading framework for fault-tolerance with very high error thresholds.
+model for quantum computation is a central approach to realising a full-scale, fault-tolerant quantum computer.
+Within this scheme, Clifford unitaries can be implemented in a robust, fault-tolerant way.
+However, due to the Eastin-Knill theorem~\cite{Eastin_2009}, we also know that it is impossible to have a universal set of transversal gates, and although Clifford unitaries can be realised transversally\ddd{[CSS code for this]}, one needs to find ways around the Eastin-Knill restriction.
+This can be achieved by injecting in quantum states, called magic states, which promote the Clifford group to universal quantum computing.
+However, the obstacle to this is that these states are invariably noisy and so protocols involving stabilizer operations must be employed to purify many copies of the magic states and improve the overall performance of the induced quantum gates.
+A central question is then the overhead on purifying many copies of a magic state into less noisy forms.
 
-The state-injection model for quantum computation~\cite{cit:bravyi} is a central approach to realising a full-scale, fault-tolerant quantum computer.
-Within this scheme, Clifford unitaries can be implemented in a robust, fault-tolerant way.
-However, due to the Eastin-Knill theorem~\cite{Eastin_2009}, it is impossible to have a universal set of transversal gates, and although Clifford unitaries can be realised transversally, one needs to find ways around the Eastin-Knill restriction.
-The state-injection approach supplements the Clifford unitaries with noisy quantum states, called `magic states', that are outside the set of stabliser states and, when incorporated into Clifford circuits, provide universality.
-The obstacle to this is that the states are invariably noisy and so protocols must be employed to purify many copies of the magic states and improve the overall performance of the induced quantum gates.
-A central question is then: given a number $n$ of noisy magic states how many purified magic states can we obtain within the fault-tolerant set of quantum operations?
+To address such questions, concrete distillation protocols have been developed, such as the Bravyi-Haah protocol that provides a quadratic reduction in noise per cycle.
+Such distillation rates have been improved in more recent works \ddd{[CITE]}.
+There is also analysis of magic protocols from the perspective of magic monotones, which provide upper bounds on distillation rates and find application in the analysis of gate synthesis \ddd{[CITE Earl+Mark paper, plus other synthesis paper(s)]}.
+These frameworks for magic view magic states as resource states with respect to a natural class of quantum operations that are consider cheap, or free, such as stabilizer operations~\cite{Gour_2019, cit:ahmadi, cit:seddon, Wang_2019}.
 
-To address such questions, concrete distillation protocols have been developed, and there has also been analysis of bounds on distillation rates within natural theoretical frameworks.
-These frameworks provide theories of magic in which one views magic states as ``resource'' states with respect to a natural class of quantum operations that are consider cheap, or ``free''~\cite{Gour_2019}.
-One very natural class of free operations considered are those obtained from Clifford operations, measurements and the ability to discard quantum systems.
-However, there are several other candidate frameworks~\cite{cit:ahmadi, cit:seddon, Wang_2019}.
+Recent work towards fault-tolerance has begun to bridge the gap between abstract theory and experiment.
+Extensive work has been done on error mitigation \ddd{[cite]}, and the incorporation of hardware physics into the theoretical modes.
+For example, the XZZX code\ddd{[cite]} is a variant of the surface code that incorporates noise bias explicitly and has been shown to attain the hashing bound of random codes.
 
-Magic states are necessary for achieving universal quantum computation within fault-tolerant schemes~\cite{cit:veitch, cit:mari, cit:gottesman, cit:bravyi, cit:knill, Campbell_2011}.
-Identifying magic as a resource for quantum universality has led to several theories which try to provide a framework for its quantification and manipulation \cite{cit:veitch2, cit:howard, Wang_2019, Seddon_2021, Okay_2021}.
-The main question that such a theory attempts to answer is:
-\begin{center}
-    \emph{How do physical constraints, such as hardware limitations, noise bias or thermodynamics, restrict magic distillation protocols?}
-\end{center}
+In this work we develop a framework to analyse magic state distillation protocols where explicit physical constraints are manifest.
+These physical constraints are encoded in the allowed fixed-point structure of the protocol, for example a minimal temperature attainable in the device, noise-biases or fixed-point structure associated with restricted gate-sets.
+The approach we take is most closely aligned with resource theories of magic, however our approach differs in two ways.
+Firstly, we obtain distillation upper bounds without the use of monotones, and secondly our distillation bounds are functions of the physical constraints and so not directly comparable to global magic monotones.
 
-Such constraints make stabilizer states inequivalent, and can give rise to stabilizer states that are invariant under the constraints.
-In this work we shall approach this question using tools from statistical mechanics and thermodynamics.
+We approach this problem using tools from statistical mechanics and recent work from the overlap of thermodynamics and quantum information theory\ddd{[cite]}.
 In particular, we shall view \emph{magic as a form of free energy}, relative to the set of stabilizer states.
-This perspective takes the convex set of stabilizer states as a manifold of ``equilibrium'' states.
-However, while a free energy difference exists between two thermodynamic equilibrium states at temperatures $T_1$ and $T_2$, here we focus in on the degree to which the magic state lies off the set of stabilizer states, and therefore magic is more accurately viewed as a form of non-equilibrium free energy that is strictly non-classical.
+This perspective takes the convex set of stabilizer states as the set of ``equilibrium'' states, and magic corresponds to a form of non-equilibrium free energy that is strictly non-classical.
 
-Our approach relies on the discrete Wigner representation of quantum states, in which all states and operations can be described on a discrete phase space.
-Crucially, we focus on magic states with negativity in their Wigner function, which is known to be a necessary condition for universality in the state-injection model.
-However, following a thermodynamic perspective in this context raises a novel problem, namely it is impossible to define entropies for quasi-distributions.
-We circumvent this obstacle by making use of a more fundamental tool in thermodynamics -- majorization theory.
+Our analysis relies on the discrete Wigner representation of quantum states, in which all states and operations can be described on a discrete phase space \ddd{[cite]}.
+Crucially, we focus on magic states with negativity in their Wigner representation, which is known to be a necessary condition for universality in the state-injection model.
+Interestingly, taking a thermodynamic perspective in this context raises a problem, namely it is impossible to define entropies for quasi-distributions.
+We circumvent this obstacle by making use of a more fundamental tool in thermodynamics -- majorization theory \ddd{[cite]}.
+To our knowledge majorization of quasi-distributions has not been considered in quantum physics before, and therefore our analysis is of broader interest to the study of non-classicality in quantum systems.
 
-Our construction also provides distillation bounds without relying on magic monotones -- instead of projecting the pre-order of magic states onto the real line (which is a monotone) we instead cover the pre-order of states with a collection of simpler `fragments', which admit analysis through the lens of majorization.
-The choice of fragment breaks the equivalence of all stabilizer states in the theory and can be used to consider adding physical constraints in the form of accessible protocols.
+Our construction provides distillation bounds without relying on magic monotones.
+Instead of projecting the pre-order of magic states onto the real line (which is what a monotone involves) we instead cover the pre-order of states with a collection of simpler `fragment' pre-orders that admit analysis in terms of majorization.
+It is this choice of fragment that breaks the equivalence of all stabilizer states in the theory and can be used to consider adding physical constraints in the form of accessible protocols.
 \nick{We need to give some concrete example here, we keep repeating this ``advantage'' abstractly}
 
-We provide a range of upper bounds, which reveal that the thermodynamic structure in the presence of negativity is surprisingly non-trivial and displays a range of features that do not appear in classical statistical mechanics.
-We also discuss how this approach could be used to construct explicit lower bounds on distillation.
-This in turn raises non-trivial questions that are also of interest in statistical mechanics.
-More precisely: what are the conditions for majorization that respects the symplectic structure of phase space?
+Through this approach we obtain a range of upper bounds for magic distillation rates.
+We provide explicit bounds for magic protocols that generate unital channels, as well as bounds that depend on the temperature and Hamiltonian of the system.
+We find that the thermodynamics in the presence of negativity is surprisingly non-trivial and displays a range of features that do not appear in classical statistical mechanics.
 
-\subsection{Prior text that might be useful}
-Even though non-stabiliserness is a necessary resource for universality, it has been proven insufficient for magic state distillation~\cite{cit:bravyi, cit:campbell}.
-In fact, all states with non-negative Wigner distributions have been proven to be efficiently classically simulable~\cite{cit:mari}, a result that serves as a generalization of the Gottesman-Knill theorem.
-The Wigner distribution of a state in odd prime dimensions arises as the unique quasi-probability representation of quantum theory that identifies non-contextuality exactly with the states that are efficiently classically simulable~\cite{Delfosse_2017, cit:howard2, cit:veitch2}.
-In this framework, the stabiliser states are the only pure states represented with non-negative distributions~\cite{cit:gross3}. 
-However, there exist mixed states with non-negative Wigner distributions that are not mixtures of stabiliser states~\cite{cit:gross}.
-
-The paper is structured as follows.
-In~\cref{sec:ps}, we formally define the Wigner representation of quantum states and outline its relevant properties.
-In~\cref{sec:frag}, we introduce majorisation and apply it on general magic theories.
-We go on to prove magic distillation bounds which account for abstract thermodynamic considerations in~\cref{sec:unital,sec:stab} and conclude in~\cref{sec:outlook}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Finally, we discuss how our approach could be improved, and also used to construct explicit lower bounds on distillation that take into account physical structure.
+Our work also raises non-trivial questions that are also of interest in statistical mechanics.
+Specifically: what are the majorization conditions that respect the symplectic structure of phase space?
 
@@
 
-The state-injection model for quantum computation~\cite{cit:bravyi} is a key avenue to realising a full-scale, fault-tolerant quantum computer.
-Within this approach, Clifford unitaries can be implemented in a robust, fault-tolerant way.
-However, due to the Eastin-Knill theorem~\cite{Eastin_2009}, it is impossible to have a universal set of transversal gates, and although Clifford unitaries can be realised transversally, one needs to find ways around the Eastin-Knill restriction.
-The state-injection approach supplements the Clifford unitaries with noisy quantum states, called `magic states', that are outside the set of stabliser states and, when incorporated into Clifford circuits, provide universality.
-The obstacle to this is that the states are invariably noisy and so protocols must be employed to purify many copies of the magic states and improve the overall performance of the induced quantum gates.
-A central question is then: given a number $n$ of noisy magic states how many purified magic states can we obtain within the fault-tolerant set of quantum operations?
-
-To address such questions, concrete distillation protocols have been developed, and there has also been analysis of bounds on distillation rates within natural theoretical frameworks.
-These frameworks provide theories of magic in which one views magic states as ``resource'' states with respect to a natural class of quantum operations that are consider cheap, or ``free''~\cite{Gour_2019}.
+A number of frameworks exist that provide theories of magic in which one views magic states as ``resource'' states with respect to a natural class of quantum operations that are consider cheap, or ``free''~\cite{Gour_2019}.
 One very natural class of free operations considered are those obtained from Clifford operations, measurements and the ability to discard quantum systems.
-However, there are several other candidate frameworks~\cite{cit:ahmadi, cit:seddon, Wang_2019}.
+However, there are other candidates~\cite{cit:ahmadi, cit:seddon, Wang_2019}.
 
@@
 
-One of the most fundamental and commonly used magic monotones is the \emph{mana} of a state~\cite{cit:veitch2}, defined as
+One of the most prominent magic monotones is the \emph{mana} of a state~\cite{cit:veitch2}, defined as
 \begin{equation}
@@
 A range of monotones have been developed in the literature~\cite{cit:howard, Wang_2020, Seddon_2021} and each provides a means to upper bound distillation rates within a particular theory of magic.
-In this work we shall consider a broad framework for magic, with conditions that any magic theory should satisfy.
-However, in contrast to prior works we shall not construct magic monotones, but instead develop a generalisation to resource monotones.
-The approach we take will also allow us to address how distillation rates are constrained by physical properties -- such as a system having biased noise, some equilibrium structure or operations that manifest invariances, such as axial symmetry around the qubit $Z$-axis.
+In this work we shall develop bounds that apply to essentially any reasonable magic theory.
+The central idea is to apply majorization theory to the quasi-probability distributions of magic states.
+In the next section we explain how these majorization constraints relate to the free operations allowed in a theory of magic.
 
@@
 
-	The location of the maximum ($x=x_{i_\star}$) varies from fragment to fragment \nick{try to calculate for thermal fragments}, but its value is independent of $\sigma$,
+	The location of the maximum ($x=x_{i_\star}$) varies from fragment to fragment, but its value is independent of $\sigma$,
 	\begin{align}

### 2021-04-15 magic_paper.tex
Small lemma on sum-negativity added.

@@
 
-In this section we give some generic aspects of Lorenz curves for magic states. In particular these allow us to interpret previous magic monotones in a new light.
+In this section we give some generic aspects of Lorenz curves for magic states.
+In particular these allow us to interpret previous magic monotones in a new light.
+The first result provides a extremely simple way to see that the sum-negativity of a magic state is a monotone.
 
+\begin{lemma} Relative majorization in any fragment implies the monotonicity of sum-negativity $sn(\rho) := \frac{1}{2} (\sum_{\x} |W_\rho(\x) | - 1)$ of a magic state $\rho$. 
+\end{lemma}
+\begin{proof}
+ We make use of a variant form of relative majorization \ddd{[cite]}, which says that $\p \succ_{\r} \q$ if and only if
+	\begin{equation}
+\sum_k | p_k - t r_k | \ge \sum_k |q_k - t r_k|,
+\end{equation}
+for all $t\in \mathbb{R}$.
+If we choose $t=0$ then we get the single condition that $\sum_k |p_k| \ge |\sum_k |q_k|$, independent of the choice of $\r$.
+Applying this to the Wigner quasi-distribution of a quantum state immediately gives the result.
+\end{proof}
 If we have a magic state $\rho$ that has negativity in its Wigner representation, then as discussed, its Lorenz curve over-shoots $1$ and reaches a non-trivial maximum $L_\star$ that depends on the particular state.
-In fact, we can establish the following general result.
+The relation with sum-negativity and mana is provided by the following result.
 \begin{lemma}\label{lem:lcmax}
-	Given a magic state $\rho$, the maximum $L_\star$ of its Lorenz curve $\lc{\rho}{\sigma}(x)$ is independent of the $\sigma$--fragment and equal to $1+\sn{\rho}$, where $\rm{sn}(\rho)$ is the sum negativity of $\rho$.
-Thus, the majorization constraint is stronger than mana in any fragment.
+	Given a magic state $\rho$, the maximum $L_\star$ of its Lorenz curve $\lc{\rho}{\sigma}(x)$ is independent of the $\sigma$--fragment and equal to $1+\sn{\rho}$.
+Moreover, the majorization constraint is stronger than mana in every fragment.
 \end{lemma}

### 2021-04-16 magic_paper.tex
New subsection added. Needs copy-paste of prior eqns but with primes added.

@@
 
-\title{Thermodynamic constraints for magic states in quantum computation}
+\title{General thermodynamic constraints on magic states for quantum computation}
 
@@
 
-\section{Magic bounds in arbitrary stabiliser fragments}
+\section{Magic bounds in arbitrary stabiliser fragments and energetic costs of distillation}
 \label{sec:stab}
@@
 \end{proof}
+We note that the above bounds are not optimal, and since we only use part of the Lorenz curve they can be improved upon.
+However, we find numerically that they do better than, for example, the constraint coming from the peak of the curve.
+Similar bounds can be obtained from the decreasing part of the Lorenz curve, but they do not shed any more light on distillation bounds.
 
+\subsection{Distillation bounds and energy dependencies}
+The previous section was focussed on an individual fragment, and while this does shed light on how physical constraints may, or may not, constrain protocols it is a bit indirect.
+However it is possible to adapt these bounds and put them in a more natural light.
+
+For this we now drop the condition that $\sigma$ is left invariant under the distillation protocol, and assume it transforms to some $\sigma'$.
+This output state must be some other stabilizer state and so has a positive Wigner function also.
+The strategy is then to use how any protocol transforms $\sigma$ to act as a measure of physical features, such as energy, of the protocol.
+Therefore we are interested in the conditions under which $(\rho, \sigma) \rightarrow (\rho', \sigma')$.
+For this we can use the full definition of relative majorization on the associated Wigner functions, and obtain distillation bounds from
+\begin{equation}
+(W_\rho(\x), W_\sigma(\x) ) \succ (W_{\rho'}(\x), W_{\sigma'}(\x) ).
+\end{equation}
+The condition for this that $L_{\rho |\sigma } (x) \ge L_{\rho'|\sigma'} (x)$, and so exactly the same analysis applies as in the previous case, but now with the Gibbs-recaling parameters for the output state being different from the input state \ddd{[cite recent Renes paper]}.
+
+If the physical system has Hamiltonian $H$, and experimentally it can be cooled down to some reference temperature $T$ then we can consider the reference equilibrium state $\sigma = e^{-\beta H}/\Z$, and estimate the energetic and entropic of protocols in terms of how they transform $\sigma$ to some other $\sigma'$.
+For example, if $\sigma'$ is close to the ground state of the system then we know that a great deal of entropy is dumped by the process.
+This allows us to parameterise our distillation bounds in more convenient terms.
+
+The state $\sigma'$ will in general not be an equilibrium state, or have any temperature associated to it.
+However we can still associate thermodynamic variables to it as follows: we consider what changes in Hamiltonian are required in order for the output state $\sigma'$ to still be an equilibrium state at the reference temperature $T$.
+Therefore $H\rightarrow H'$ such that $\sigma' = e^{-\beta H'}/\Z'$ and so the Lorenz curve of the output state $\rho'$ relative to $\sigma'$ will be expressible in terms of the free energy $F'(\beta) = -\beta^{-1} \log \Z'$ and the spectrum of the Hamiltonian $H'$.
+We find that \ddd{[Details?
+Expect that we now get free energy differences $\Delta F := F' - F$ appearing.]}
 \subsection{Lower magic bounds via majorisation}

### 2021-04-16 appendix.tex
Added loads of references

@@
 
+% TO SWAP d --> r, REPLACE ALL \bmd, \bm{d}, d_i WITH \r
+
 \subsection{Simple--majorization equivalence conditions}
 
-In the unital fragment, namely the limit of infinite temperature, $\beta = 0$, the free state is the maximally mixed state $\frac{1}{d}\id$ with uniform Wigner distribution $\frac{1}{d}\bm{1}  = (\frac{1}{d},\dots,\frac{1}{d})$.
+In the unital fragment, namely the limit of infinite temperature, $\beta = 0$, the free state is the maximally mixed state $\frac{1}{n}\id$ with uniform Wigner distribution $\frac{1}{n}\bm{1}  = (\frac{1}{n},\dots,\frac{1}{n})$.
 This fragment is governed by simple majorization and we first prove strong equivalences for this type of majorization.
@@
 	\item[(iv)]\label{en:m4} $\sum\limits_{i=1}^n (x_i - t)^+ \leq \sum\limits_{i=1}^n (y_i - t)^+$ for all $t \in \mathbb{R}$ and \vspace{5pt}\\ $\sum\limits_{i=1}^n x_i = \sum\limits_{i=1}^n y_i$, where $(x)^+ = \max{\{x, 0\}}$;
-	\item[(v)]\label{en:m5} $L_{\bmx}(t) \leq L_{\bmy}(t)$ for $t\in [0,1)$	and \vspace{5pt}\\ $L_{\bmx}(1) = L_{\bmy}(1)$, where $L_{\bmz}(t) = L_{\bmz|\frac{1}{d}\bm{1}}(t)$.
+	\item[(v)]\label{en:m5} $L_{\bmx}(t) \leq L_{\bmy}(t)$ for $t\in [0,1)$	and \vspace{5pt}\\ $L_{\bmx}(1) = L_{\bmy}(1)$, where $L_{\bmz}(t) = L_{\bmz|\frac{1}{n}\bm{1}}(t)$.
  \end{enumerate}
@@
 
-Any $\bmd$--majorization problem can be rephrased as a simple majorization problem in a higher dimensional space via the embedding map.
+Any $\r$--majorization problem can be rephrased as a simple majorization problem in a higher dimensional space via the embedding map.
 \begin{definition}
-  The embedding map $\Gamma_{\bmd}:\mathbb{R}^n \mapsto \mathbb{R}^N, N = \sum\limits_{i=1}^n d_i$ is the function
+  The embedding map $\Gamma_{\r}:\mathbb{R}^n \mapsto \mathbb{R}^N, N = \sum\limits_{i=1}^n r_i$ is the function
   \begin{equation}
-    \Gamma_{\bmd}(\bmw) = \bigoplus_{i=1}^n w_i\  \frac{1}{d_i}\bm{1},
+    \Gamma_{\r}(\bmw) = \bigoplus_{i=1}^n w_i\  \frac{1}{r_i}\bm{1},
   \end{equation}
-where $\bm{1}/d_i$ is the $d_i$--dimensional uniform distribution.
-The left inverse $\Gamma_{\bmd}^{-1}: \mathbb{R}^N \mapsto \mathbb{R}^n$ is defined to sum up the elements in each block of $\Gamma_{\bmd}(\bmw)$, so that
+where $\bm{1}/r_i$ is the $r_i$--dimensional uniform distribution.
+The left inverse $\Gamma_{\r}^{-1}: \mathbb{R}^N \mapsto \mathbb{R}^n$ is defined to sum up the elements in each block of $\Gamma_{\r}(\bmw)$, so that
   \begin{equation}
-     \Gamma_{\bmd}^{-1}(\oplus_{i=1}^n w_i \bm{1}/d_i) = \bmw.
+     \Gamma_{\r}^{-1}(\oplus_{i=1}^n w_i \bm{1}/r_i) = \bmw.
   \end{equation}
-  This is not a right inverse, because $\Gamma_{\bmd}$ is not surjective.
+  This is not a right inverse, because $\Gamma_{\r}$ is not surjective.
 \end{definition}
 The direct sum simply amounts to listing the uniform distributions one after the other.
-The embedding map maps the Gibbs distribution to the uniform distribution, $\Gamma_{\bmd}(\bmd) = \bm{1}/N$.
-Then, a non-increasing ordering $\Gamma_{\bmd}(\bmz)^\downarrow$ in the new space, corresponds to the so-called ``$\beta$-ordering'' of the original vector denoted by the permutation $\pi$ in~\cref{eq:lc}, mapping $(w_i/d_i) \mapsto (w_i/d_i)^\downarrow$ for all $i=1,\dots,n$.
+The embedding map maps the Gibbs distribution to the uniform distribution, $\Gamma_{\r}(\r) = \bm{1}/N$.
+Then, a non-increasing ordering $\Gamma_{\r}(\bmz)^\downarrow$ in the new space, corresponds to the so-called ``$\beta$-ordering'' of the original vector denoted by the permutation $\pi$ in~\cref{eq:lc}, mapping $(w_i/r_i) \mapsto (w_i/r_i)^\downarrow$ for all $i=1,\dots,n$.
 
-\subsection{\textit{d}-majorization equivalence conditions}
+\subsection{\textit{r}-majorization equivalence conditions}
 
-We take the opportunity here	 to simply list useful equivalent statements for $\bmd$--majorisation.
+We take the opportunity here	 to simply list useful equivalent statements for $\r$--majorisation.
 
-\begin{proposition}\label{prop:dmajor}
-Given $\bmx, \bmy, \bmd \in \mathbb{R}^n$, such that the components of $\bmd$ are positive, the following statements are equivalent:
+\begin{proposition}\label{prop:rmajor}
+Given $\bmx, \bmy, \r \in \mathbb{R}^n$, such that the components of $\r$ are positive, the following statements are equivalent:
   \begin{enumerate}
-    \item[(i)] $\bmx \prec_{\bmd} \bmy$;
-    \item[(ii)] $\Gamma_{\bmd}({\bmx}) \prec \Gamma_{\bmd}({\bmy})$;
-    \item[(iii)]\label{en:tm3} $\sum\limits_{i=1}^n \abs{x_i - t d_i} \leq \sum\limits_{i=1}^n \abs{y_i - t d_i}$ for all $t \in \mathbb{R}$;
-    \item[(iv)] $\sum\limits_{i=1}^n (x_i - t d_i)^+ \leq \sum\limits_{i=1}^n (y_i - t d_i)^+$ for all $t \in \mathbb{R}$ and \vspace{5pt}\\ $\sum\limits_{i=1}^n x_i = \sum\limits_{i=1}^n y_i$;
-    \item[(v)] $L_{\bmx|\bmd}(t) \leq L_{\bmy|\bmd}(t)$ for $t\in [0,1)$ and \vspace{5pt}\\ $L_{\bmx|\bmd}(1) = L_{\bmy|\bmd}(1)$.
+    \item[(i)] $\bmx \prec_{\r} \bmy$;
+    \item[(ii)] $\Gamma_{\r}({\bmx}) \prec \Gamma_{\r}({\bmy})$;
+    \item[(iii)]\label{en:tm3} $\sum\limits_{i=1}^n \abs{x_i - t r_i} \leq \sum\limits_{i=1}^n \abs{y_i - t r_i}$ for all $t \in \mathbb{R}$;
+    \item[(iv)] $\sum\limits_{i=1}^n (x_i - t r_i)^+ \leq \sum\limits_{i=1}^n (y_i - t r_i)^+$ for all $t \in \mathbb{R}$ and \vspace{5pt}\\ $\sum\limits_{i=1}^n x_i = \sum\limits_{i=1}^n y_i$;
+    \item[(v)] $L_{\bmx|\r}(t) \leq L_{\bmy|\r}(t)$ for $t\in [0,1)$ and \vspace{5pt}\\ $L_{\bmx|\r}(1) = L_{\bmy|\r}(1)$.
   \end{enumerate}
@@
 	\item[1$\leftrightarrow2$]
-	Suppose there exists a $\bmd$--stochastic $A$ such that $\bmx = A\bmy$ and let $B = \Gamma_{\bmd} \circ A \circ \Gamma_{\bmd}^{-1}$.
-$B$ is a $N$--dimensional bistochastic matrix, since composition of stochastic matrices is stochastic and $(\Gamma_{\bmd} \circ A \circ \Gamma_{\bmd}^{-1})\big(\frac{1}{N}\bm{1}\big) = (\Gamma_{\bmd} \circ A) (\bm{d}) = \Gamma_{\bmd}(\bm{d}) = \frac{1}{N}\bm{1}$.
-Then, $B$ maps $\Gamma_{\bmd}({\bmy})$ to $\Gamma_{\bmd}({\bmx})$.
+	Suppose there exists a $\r$--stochastic $A$ such that $\bmx = A\bmy$ and let $B = \Gamma_{\r} \circ A \circ \Gamma_{\r}^{-1}$.
+$B$ is a $N$--dimensional bistochastic matrix, since composition of stochastic matrices is stochastic and $(\Gamma_{\r} \circ A \circ \Gamma_{\r}^{-1})\big(\frac{1}{N}\bm{1}\big) = (\Gamma_{\r} \circ A) (\r) = \Gamma_{\r}(\r) = \frac{1}{N}\bm{1}$.
+Then, $B$ maps $\Gamma_{\r}({\bmy})$ to $\Gamma_{\r}({\bmx})$.
 
-	Conversely, given $B$, let $A = \Gamma_{\bmd}^{-1} \circ B \circ \Gamma_{\bmd}$.
-	Similarly, $A$ is a $\bmd$--stochastic matrix that maps $\bmy$ to $\bmx$.
+	Conversely, given $B$, let $A = \Gamma_{\r}^{-1} \circ B \circ \Gamma_{\r}$.
+	Similarly, $A$ is a $\r$--stochastic matrix that maps $\bmy$ to $\bmx$.
 	\item[$2\leftrightarrow3$] These \hspace{1pt} three \hspace{1pt} statements \hspace{1pt} are \hspace{1pt} equivalent \hspace{1pt} to \hspace{1pt} state-
 	\item[$2\leftrightarrow4$] \vspace{-7pt} ments (iii), (iv), (v) \hspace{1pt} in~\cref{prop:major} respectively, 
-	\item[$2\leftrightarrow5$] \vspace{-7pt} for the embedded vectors $\Gamma_{\bmd}({\bmx}), \Gamma_{\bmd}({\bmy})$, which becomes apparent by rewriting
+	\item[$2\leftrightarrow5$] \vspace{-7pt} for the embedded vectors $\Gamma_{\r}({\bmx}), \Gamma_{\r}({\bmy})$, which becomes apparent by rewriting
 	\begin{align*}
-	&\hspace{15pt} \sum\limits_{i=1}^n \abs{x_i - t d_i} = \sum\limits_{i=1}^n d_i \abs{\frac{x_i}{d_i} - t} = \sum\limits_{i=1}^N \abs{\Gamma_{\bmd}(\bmx)_i - t}, \\[3pt]
-	&\hspace{15pt} \sum\limits_{i=1}^n (x_i - t d_i)^+ = \sum\limits_{i=1}^N (\Gamma_{\bmd}(\bmx)_i - t)^+ \text{ and} \\[6pt]
-	&\hspace{15pt} L_{\bmx|\bmd}(t) = L_{\Gamma_{\bmd}(\bmx)}(t),
+	&\hspace{15pt} \sum\limits_{i=1}^n \abs{x_i - t r_i} = \sum\limits_{i=1}^n r_i \abs{\frac{x_i}{r_i} - t} = \sum\limits_{i=1}^N \abs{\Gamma_{\r}(\bmx)_i - t}, \\[3pt]
+	&\hspace{15pt} \sum\limits_{i=1}^n (x_i - t r_i)^+ = \sum\limits_{i=1}^N (\Gamma_{\r}(\bmx)_i - t)^+ \text{ and} \\[6pt]
+	&\hspace{15pt} L_{\bmx|\r}(t) = L_{\Gamma_{\r}(\bmx)}(t),
 	\end{align*} 
@@
   Multiplication $2i$ is considered modulo $(n+1)$.
-  For completeness, note that $(x_{-1}, L_{-1}) \coloneqq (0,0)$ is not included in the coordinate expressions.
+  For completeness, note that $(x_{-1}, L_{-1}) \coloneqq (0,0)$ is not included in the table.
   }

### 2021-04-16 magic_paper.tex
Added loads of references

--- 2021-04-15 magic_paper.tex
@@
 % Write bounds as 1 + ln{}/{} or 1 - (-ln{})/{} ?
-% Sec: App. D
 % Sec: General resources
 % Sec: Lower bounds
+% App: D clean-up + d--> r ?
 
-% Find more (all) refs
 % Figs consistency (esp. figs 3,4,5 and 1,6) + Figure 0 ?
@@
 
-The past few years have seen rapid progress towards the goal of a fault-tolerant quantum computer\ddd{[CITE]}.
-However many challenges remain and there is increasing need for theory to take into account physical limitations of the hardware involved.
-The surface code~\cite{cit:bravyi}\ddd{[CITE MORE]} is a leading framework for fault-tolerance with very high error thresholds.
-model for quantum computation is a central approach to realising a full-scale, fault-tolerant quantum computer.
+The past few years have seen rapid progress towards the goal of a fault-tolerant quantum computer~\cite{Fowler_2012, Herrera_2010, Nickerson_2014, Nikahd_2017, chao_2018, lin_pieceable_2020, Lin_2020, Bourassa_2021}.
+However, many challenges remain and there is increasing need for theory to take into account physical limitations of the hardware involved.
+The surface code~\cite{Bravyi_1998, Freedman_2001, Dennis_2002, Raussendorf_2007} is a leading framework for fault-tolerance with very high error thresholds.
 Within this scheme, Clifford unitaries can be implemented in a robust, fault-tolerant way.
-However, due to the Eastin-Knill theorem~\cite{Eastin_2009}, we also know that it is impossible to have a universal set of transversal gates, and although Clifford unitaries can be realised transversally\ddd{[CSS code for this]}, one needs to find ways around the Eastin-Knill restriction.
-This can be achieved by injecting in quantum states, called magic states, which promote the Clifford group to universal quantum computing.
-However, the obstacle to this is that these states are invariably noisy and so protocols involving stabilizer operations must be employed to purify many copies of the magic states and improve the overall performance of the induced quantum gates.
-A central question is then the overhead on purifying many copies of a magic state into less noisy forms.
+However, due to the Eastin-Knill theorem~\cite{Eastin_2009}, we also know that it is impossible to have a universal set of transversal gates, and although Clifford unitaries can be realised transversally~\cite{Calderbank_1996, Steane_1996}, one needs to find ways around the Eastin-Knill restriction.
+This can be achieved by injecting in quantum states, called magic states, which promote the Clifford group to universal quantum computing~\cite{cit:bravyi}.
+The obstacle to this is that these states are invariably noisy and so protocols involving stabilizer operations must be employed to purify many copies of the magic states and improve the overall performance of the induced quantum gates.
+A central question then arises about the overhead on purifying many copies of a magic state into less noisy forms.
 
-To address such questions, concrete distillation protocols have been developed, such as the Bravyi-Haah protocol that provides a quadratic reduction in noise per cycle.
-Such distillation rates have been improved in more recent works \ddd{[CITE]}.
-There is also analysis of magic protocols from the perspective of magic monotones, which provide upper bounds on distillation rates and find application in the analysis of gate synthesis \ddd{[CITE Earl+Mark paper, plus other synthesis paper(s)]}.
-These frameworks for magic view magic states as resource states with respect to a natural class of quantum operations that are consider cheap, or free, such as stabilizer operations~\cite{Gour_2019, cit:ahmadi, cit:seddon, Wang_2019}.
+To address this, concrete distillation protocols have been developed, such as the Bravyi-Haah protocol that provides a quadratic reduction in noise per cycle~\cite{Bravyi2012}.
+Such distillation rates have been improved in more recent works~\cite{Hastings2018, Litinski_2019, Krishna2019, cit:prakash}.
+There is also analysis of magic protocols from the perspective of magic monotones, which provide upper bounds on distillation rates and find application in the analysis of gate synthesis~\cite{Campbell_2017, Howard_2017, Prakash_2018}.
+These frameworks for magic view magic states as resource states with respect to a natural class of quantum operations that are considered cheap, or free, such as stabilizer operations~\cite{Gour_2019, cit:ahmadi, cit:seddon, Wang_2019}.
 
 Recent work towards fault-tolerance has begun to bridge the gap between abstract theory and experiment.
-Extensive work has been done on error mitigation \ddd{[cite]}, and the incorporation of hardware physics into the theoretical modes.
-For example, the XZZX code\ddd{[cite]} is a variant of the surface code that incorporates noise bias explicitly and has been shown to attain the hashing bound of random codes.
+Extensive work has been done on error mitigation~\cite{Li_2017, Temme_2017, Endo_2018, McClean_2017}, and the incorporation of hardware physics into the theoretical modes~\cite{Kandala_2019, Colless_2018, song2018quantum, Bravyi_2021}.
+For example, the XZZX code~\cite{bonilla_ataides_xzzx_2021} is a variant of the surface code that incorporates noise bias explicitly and has been shown to attain the hashing bound of random codes~\cite{Bennett_1996}.
 
-In this work we develop a framework to analyse magic state distillation protocols where explicit physical constraints are manifest.
-These physical constraints are encoded in the allowed fixed-point structure of the protocol, for example a minimal temperature attainable in the device, noise-biases or fixed-point structure associated with restricted gate-sets.
-The approach we take is most closely aligned with resource theories of magic, however our approach differs in two ways.
-Firstly, we obtain distillation upper bounds without the use of monotones, and secondly our distillation bounds are functions of the physical constraints and so not directly comparable to global magic monotones.
+In this work, we develop a framework to analyse magic state distillation protocols where explicit physical constraints are manifest.
+These physical constraints are encoded in the allowed fixed-point structure of the protocol, for example a minimal temperature attainable in the device, noise-biases or fixed-point structure associated with restricted gate-sets (see e.g.~\cite{Aliferis_2008, Stephens_2013, Li_2015, Babbush_2018, Tuckett_2019, Guillaud_2019, Fowler_2019}).
+The approach we take is most closely aligned with resource theories of magic, although it differs in two ways.
+Firstly, we obtain distillation upper bounds without the use of monotones, and secondly our distillation bounds are functions of the physical constraints, thus not directly comparable to global magic monotones.
 
-We approach this problem using tools from statistical mechanics and recent work from the overlap of thermodynamics and quantum information theory\ddd{[cite]}.
+We approach this problem using tools from statistical mechanics and recent work from the overlap of thermodynamics and quantum information theory~\cite{cit:gour, cit:gour2}\nick{You had a specific review in mind I think, which one?} .
 In particular, we shall view \emph{magic as a form of free energy}, relative to the set of stabilizer states.
@@
 
-Our analysis relies on the discrete Wigner representation of quantum states, in which all states and operations can be described on a discrete phase space \ddd{[cite]}.
-Crucially, we focus on magic states with negativity in their Wigner representation, which is known to be a necessary condition for universality in the state-injection model.
+Our analysis relies on the discrete Wigner representation of quantum states, in which all states and operations can be described on a discrete phase space~\cite{Ferrie_2008, Okay_2021}.
+Crucially, we focus on magic states with negativity in their Wigner representation, which is known to be a necessary condition for universality in the state-injection model~\cite{cit:veitch, cit:mari, cit:gottesman, cit:knill, Campbell_2011}.
 Interestingly, taking a thermodynamic perspective in this context raises a problem, namely it is impossible to define entropies for quasi-distributions.
@@
 It is this choice of fragment that breaks the equivalence of all stabilizer states in the theory and can be used to consider adding physical constraints in the form of accessible protocols.
-\nick{We need to give some concrete example here, we keep repeating this ``advantage'' abstractly}
 
@@
 We find that the thermodynamics in the presence of negativity is surprisingly non-trivial and displays a range of features that do not appear in classical statistical mechanics.
-
-Finally, we discuss how our approach could be improved, and also used to construct explicit lower bounds on distillation that take into account physical structure.
-Our work also raises non-trivial questions that are also of interest in statistical mechanics.
-Specifically: what are the majorization conditions that respect the symplectic structure of phase space?
+Finally, we discuss how our approach could be improved and how it can be exploited to construct explicit lower bounds on distillation that take into account physical structure.
 
@@
 
-A number of frameworks exist that provide theories of magic in which one views magic states as ``resource'' states with respect to a natural class of quantum operations that are consider cheap, or ``free''~\cite{Gour_2019}.
-One very natural class of free operations considered are those obtained from Clifford operations, measurements and the ability to discard quantum systems.
-However, there are other candidates~\cite{cit:ahmadi, cit:seddon, Wang_2019}.
+A number of magic theories exist, with the central approach of viewing magic states as ``resource'' states with respect to a natural class of quantum operations that are considered free~\cite{Gour_2019}.
+One very natural class of free operations are those obtained from Clifford operations, measurements and the ability to discard quantum systems.
+However, there are also other noteworthy candidates~\cite{cit:ahmadi, cit:seddon, Wang_2019}.
 
@@
 The central idea is to apply majorization theory to the quasi-probability distributions of magic states.
-In the next section we explain how these majorization constraints relate to the free operations allowed in a theory of magic.
+In the next section, we explain how these majorization constraints relate to the free operations allowed in a theory of magic.
 
@@
 These are not a priori encoded in the formulation of the magic theory, and constitute additional physical conditions on top of the underlying resource-theoretic accounting.
-For example, there may be non-trivial thermal noise in the physical set-up or the accessible operations, there might be strong bias in the noise present, or we might be limited in how easily certain gates can be realised.~\cite{Litinski_2019, Babbush_2018, Fowler_2019, Li_2015}.
+For example, there may be non-trivial thermal noise in the physical set-up or the accessible operations, there might be strong bias in the noise present, or we might be limited in how easily certain gates can be realised.~\cite{Aliferis_2008, Stephens_2013, Li_2015, Babbush_2018, Tuckett_2019, Guillaud_2019, Fowler_2019}.
+\nick{repeats intro}
 
@@
     Each $\O_\sigma$ is extensible to a set of stochastic maps outside the $\cptp$ operations.
-    Within each $\sigma$--fragment, $\bmd$--majorisation can be used allowing for a tractable approach towards the study of magic state interconversions.
+    Within each $\sigma$--fragment, relative majorisation can be used allowing for a tractable approach towards the study of magic state interconversions.
     }
@@
 Note, however, that unlike any monotone, this is not a single numerical constraint, but a \emph{family} of constraints.
-Indeed, for $n$ copies of a $d$--dimensional system the number of terms in $W_{\rho}$ is $d^{2n}$, so the Lorenz curve condition corresponds to \emph{exponentially} many constraints, of which there are as many independent constraints as there are elbows in the Lorenz curve of the target state, which is proved in~\cref{thm:elbows} in~\cref{app:frag}.
+Indeed, for $n$ copies of a $d$--dimensional system the number of terms in $W_{\rho}$ is $d^{2n}$, so the Lorenz curve condition corresponds to \emph{exponentially} many constraints, of which there are as many independent constraints as there are elbows in the Lorenz curve of the output state, which is proved in~\cref{thm:elbows} in~\cref{app:frag}.
 In principle, any one location $x$ provides a valid constraint leading to some upper distillation bound and optimising over the location provides the strictest bound.
@@
 
-In this section we give some generic aspects of Lorenz curves for magic states. In particular these allow us to interpret previous magic monotones in a new light.
+In this section we give some generic aspects of Lorenz curves for magic states.
+In particular these allow us to interpret previous magic monotones in a new light.
+The f,irst result provides an extremely simple way to see that the sum-negativity of a magic state is a monotone.
+
+\begin{lemma} Relative majorization in any fragment implies the monotonicity of sum-negativity. 
+\end{lemma}
+\begin{proof}
+	The sum-negativity of a magic state $\rho$ can be written as $sn(\rho) := \frac{1}{2} (\sum_{\x} |W_\rho(\x) | - 1)$.
+We make use of a variant form of relative majorization, (see~\cref{prop:rmajor} in~\cref{app:major}), stating that $\p \succ_{\r} \q$ if and only if
+	\begin{equation}
+\sum_k | p_k - t r_k | \ge \sum_k |q_k - t r_k|,
+\end{equation}
+for all $t\in \mathbb{R}$.
+Choosing $t=0$ we get the single condition that $\sum_k |p_k| \ge |\sum_k |q_k|$, independent of the choice of $\r$.
+Applying this to the Wigner quasi-distributions of two quantum states immediately gives the result.
+\end{proof}
+As a corollary, this result applies to mana too, since mana is an increasing function of sum-negativity.
 
 If we have a magic state $\rho$ that has negativity in its Wigner representation, then as discussed, its Lorenz curve over-shoots $1$ and reaches a non-trivial maximum $L_\star$ that depends on the particular state.
-In fact, we can establish the following general result.
+There is an exact relation between the peak and sum-negativity or mana, which is provided by the following result.
 \begin{lemma}\label{lem:lcmax}
-	Given a magic state $\rho$, the maximum $L_\star$ of its Lorenz curve $\lc{\rho}{\sigma}(x)$ is independent of the $\sigma$--fragment and equal to $1+\sn{\rho}$, where $\rm{sn}(\rho)$ is the sum negativity of $\rho$.
-Thus, the majorization constraint is stronger than mana in any fragment.
+	Given a magic state $\rho$, the maximum $L_\star$ of its Lorenz curve $\lc{\rho}{\sigma}(x)$ is independent of the $\sigma$--fragment and equal to $1+\sn{\rho}$.
+Moreover, the majorization constraint is stronger than mana in every fragment.
 \end{lemma}
@@
 	\begin{equation}
-		\widetilde{\bm{w}}(\rho|\sigma) \coloneqq \left(\frac{w(\rho)_1}{w(\sigma)_1}, \dots, \frac{w(\rho)_{d^2}}{w(\sigma)_{d^2}} \right)^T,
+		\widetilde{\bmw}(\rho|\sigma) \coloneqq \left(\frac{w(\rho)_1}{w(\sigma)_1}, \dots, \frac{w(\rho)_{d^2}}{w(\sigma)_{d^2}} \right)^T,
 	\end{equation}
-	is sorted, $\widetilde{\bm{w}} = \widetilde{\bm{w}}^\downarrow$.
+	is sorted, $\widetilde{\bmw} = \widetilde{\bmw}^\downarrow$.
 	Note that all components of $\bmw(\sigma)$ are positive, so $\widetilde{w}_i \geq 0$ if and only if $w(\rho)_i \geq 0$ for any $i=1,\dots,d^2$.
 
-	Let $i_\star$ be the index of the smallest non-negative component of $\widetilde{\bm{w}}^\downarrow$.
+	Let $i_\star$ be the index of the smallest non-negative component of $\widetilde{\bmw}^\downarrow$.
 	Then, $w(\rho)_i < 0$ if and only if $i > i_\star$, so the maximum of Lorenz curve $\lc{\rho}{\sigma}(x)$ takes the value 
@@
 \item As a family of upper bounds parameterised by an abstract stabiliser state $\sigma$.
-\item As a consequence of the actual hardware limitations, noise bias or ambient thermal environment reflected by the invariant state $\sigma$ for the system.
+\item As a constraint arising from the actual hardware limitations, noise bias or ambient thermal environment and reflected by the invariant state $\sigma$ for the system.
 \end{enumerate}
@@
 To obtain the distillation bounds from majorization we can now compute the above terms for both the input and output states.
-Depending on the noise parameters $\epsilon, \epsilon'$ for the initial and target states the Lorenz curve data may fall into either case $\rm{(C1)}$ or case $\rm{(C2)}$.
+Depending on the noise parameters $\epsilon, \epsilon'$ for the input and output states the Lorenz curve data may fall into either case $\rm{(C1)}$ or case $\rm{(C2)}$.
 Specifically, we have three scenarios of relevance to magic distillation:
@@
 
-In each of the three scenarios, it is simple to check that the initial state's first elbow has $x_0$ coordinate closer to $0$ compared to the output state, $x_0 \leq x_0'$ (see~\cref{app:first_elb_loc} for details).
+In each of the three scenarios, it is simple to check that the input state's first elbow has $x_0$ coordinate closer to $0$ compared to the output state, $x_0 \leq x_0'$ (see~\cref{app:first_elb_loc} for details).
 Therefore, we can use the first elbow constraint, as described in~\cref{app:elb_constraints}, leading to the following distillation bounds,
@@
 
+Our work also raises a fundamental question that is also of interest in statistical mechanics. Specifically: what are the majorization conditions that respect the symplectic structure of phase space?
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-04-17 magic_paper.tex
Better title. New material showing applicability of Lorenz curve condition to general quasi-distributions

@@
 
-\title{General thermodynamic constraints on magic states for quantum computation}
+\title{General constraints on magic state protocols from statistical mechanics}
 
@@
 
-Given the definition of Lorenz curves, the condition for relative majorization can now be phrased compactly.
-We have that $\w_1 \succ_{\r} \w_2$ if and only if $L_{\w_1 | \r} (x) \ge L_{\w_2 | \r}(x)$ for all $x \in [0,1]$ (technical discussion and proof can be found in~\cref{app:major}.
+\ddd{[I'll tidy this up more tomorrow and extend notation to full relative majorization.]}
+However, the eagle-eyed reader will point out that relative majorization is usually considered for probability distributions, and so we verify
+ that the same conditions apply to quasi-probability distributions.
+This can be done from first principles, but a simple way is to reduce to the problem of genuine distributions by `masking' the negativity in $\w$ using the reference distribution $\r$.
+
+More precisely, if the components of $\r$ are never zero, then there always exists an $\epsilon >0$ such that $\w_\epsilon := \epsilon \w + (1-\epsilon) \r$ is a genuine probability distribution.
+We can see that $(\w , \r) \succ (\w', \r')$ if and only if $(\w_\epsilon , \r) \succ (\w_\epsilon', \r')$, where we choose $\epsilon$ so that both $\w_\epsilon$ and $\w_\epsilon'$ are probability distributions.
+This equivalence holds because there exists a stochastic map $A$ such that $A \w = \w'$ and $A \r = \r'$ if and only if $A[\epsilon \w + (1-\epsilon) \r] = \epsilon \w' + (1-\epsilon) \r'$ and $ A\r = \r'$.
+Now it is shown in \ddd{[cite ``The mixing distance'', E Ruch, R Schranner, TH Seligman]} relative majorization between pairs of distributions occurs if and only if the associated Lorenz curves never cross.
+Therefore we need only establish that this carries over to Lorenz curves for quasi-distributions.
+
+In the appendices we show that 
+\begin{equation}
+L_{a \w + b \r | \r} (x) = a L_{\w|\r} (x) + bL _{\r|\r}(x),
+\end{equation}
+for all $a >0$ and any $b \in \mathbb{R}$. We now have that
+\begin{equation}
+(\w, \r) \succ (\w', \r') \mbox{ if and only if } (\w_\epsilon , \r) \succ (\w_\epsilon', \r'),
+\end{equation}
+and also $(\w_\epsilon , \r) \succ (\w_\epsilon', \r')$ if and only if $L_{\w_\epsilon |\r} (x) \ge L_{\w'_\epsilon |\r'} (x)$ for all $x$.
+However, using the above linearity property of the Lorenz curves we have that
+\begin{align}
+L_{\w_\epsilon |\r} (x) &\ge L_{\w'_\epsilon |\r'} (x) \nonumber \\ 
+&\mbox{ if and only if }& \nonumber \\
+\epsilon L_{\w |\r} (x) + (1-\epsilon) L_{\r|\r}(x) &\ge \epsilon L_{\w' |\r'} (x) + (1-\epsilon) L_{\r'|\r'}(x).
+\end{align}
+However $L_{\r|\r}(x)$ is simply the function $f(x)=x$ for any $\r$ and so the $(1-\epsilon)$ terms cancel on both sides and we get the required relative majorization conditions for the quasi-distributions in terms of their Lorenz curves.
+
+We therefore have that $\w_1 \succ_{\r} \w_2$ if and only if $L_{\w_1 | \r} (x) \ge L_{\w_2 | \r}(x)$ for all $x \in [0,1]$ (technical discussion and proof can be found in~\cref{app:major}.
 In other words, the Lorenz curve of $\w_1$ relative to $\r$ is never below the Lorenz curve of $\w_2$ relative to $\r$.

### 2021-04-17 appendix.tex
Added sigma -> sigma\prime calulation. Surprisingly simpler than I thought, even led to some cleaning up in the first - and last - elbow condition in the stabilizer proof and appendices

@@
 \begin{align}
-	\abs{\W{\rho}{\bmx}} &= \frac{1}{d}\abs{\tr[A_{\bmx} \rho]} \leq \frac{1}{d} \abs{\sum_i \alpha_{\bmx,i} \lambda_i} \nonumber\\ &\leq \frac{1}{d}\sum_i \lambda_i = \frac{1}{d}.
+	\abs{W_{\rho}(\bmx)} &= \frac{1}{d}\abs{\tr[A_{\bmx} \rho]} \leq \frac{1}{d} \abs{\sum_i \alpha_{\bmx,i} \lambda_i} \nonumber\\ &\leq \frac{1}{d}\sum_i \lambda_i = \frac{1}{d}.
 \end{align}
@@
 
-In this section, we provide some useful technical properties of general $\sigma$--fragments.
+In this section, we discuss some technical aspects of general $\sigma$--fragments.
 
@@
 \begin{equation*}
-\rho_{\rm{S}}(\epsilon)^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n-n')},
+\rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n-n')},
 \end{equation*}
@@
 
-\subsection{Strange state MSD in the unital fragment}\label{app:lc_compare}
-\nick{DELETE SECTION (?)}
-
-Consider the Strange state MSD process in the unital fragment,
-\begin{equation}\label{eq:su_conversion}
-    \rho_{\rm{S}}(n', \epsilon, 0) \xrightarrow{\mathcal{O}_{\id/3}} \rho_{\rm{S}}(n', \epsilon', n-n').
-\end{equation}
-We denote initial state indices without a prime and target state indices with a prime,
-\begin{align}
-    I(i,j,k=1) &= j + \sum_{\ell=0}^{i-1} m_{\ell}(n, \epsilon), \\
-    I'(i',j',k') &= k' + \left[ (j'-1) + \sum_{\ell=0}^{i'-1} m_{\ell}(n', \epsilon') \right]9^{n-n'}.
-\end{align}
-
-Pointwise Lorenz curve comparison requires $x_{I} = x_{I'}$, so the question is: 
-\begin{center}
-\emph{Given a triplet $(i',j',k')$, what is the tuple $(i,j)$ such that $I(i,j) = I'(i',j',k')$?}
-\end{center}
-
-According to~\cref{thm:elbows} which is proved in~\cref{app:lc_constraints}, for standard Lorenz curves, we need to match indices at the target state elbows, so the requirement on the indices is finding a tuple $(i, j)$, such that for a given $i' = 0,\dots,n'$,
-\begin{equation}
-	j + \sum_{\ell=0}^{i-1} m_{\ell}(n, \epsilon) = \sum_{\ell=0}^{i'} m_{\ell}(n', \epsilon').
-\end{equation}
-
-As a basic example, consider the process 
-\begin{equation}
-\rho_{\rm{S}}(\epsilon)^{\otimes 4} \xrightarrow{\mathcal{O}_{\id/3}} \rho_{\rm{S}}(\epsilon')^{\otimes 2} \otimes \left( \frac{1}{3}\id \right)^{\otimes 2}.
-\end{equation}
-We want to check which Lorenz curve is higher at the first elbows of the target state, i.e. we want to verify or reject the first inequality below:
-\begin{equation}
-	L_{I(i,j)} \geq L'_{I'(0, 1, 81)}
-\end{equation}
-where the first multiplicity of the target state is $m_0 = 1$.
-The multiplicities of the initial state are $(1, 384, 4096)$.
-
-The challenge is to find $i,j$ such that $i(i,j) = i'(0,1,81)$.
-\nick{By trial and error}, we find that $(i,j) = (1, 80)$.
-Now we can use~\cref{eq:lcsu_lcoord} to directly calculate
-\begin{align*}
-	L'_{i'(0,1,81)} &= L'_0 = \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^2 \Phi_+\left(0;2,4\frac{3-\epsilon}{15-8\epsilon}\right), \\
-	L_{i(1, 80)} &= \left(1-\frac{80}{384} \right) L_0 + \frac{80}{384} L_1 \\
-	\begin{split}
-	&= \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^4 \bigg[ \frac{19}{24} \Phi_+\left(0;4,4\frac{3-\epsilon}{15-8\epsilon}\right) \\ 
-	&\qquad + \frac{5}{24}\Phi_+\left(2;4,4\frac{3-\epsilon}{15-8\epsilon}\right) \bigg],
-	\end{split}
-\end{align*}
-and then compare them.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\subsection{First and last elbow conditions}
+\subsection{First and last elbow constraints}
 \label{app:elb_constraints}
-Here we prove the majorization constraints that arise by only considering the first or the last elbow of the initial state.
+Here we prove the majorization constraints that arise by only considering the first elbow (on the ascending part of the curves) or the last elbow (on the descending part of the curves) that occurs in any of the two curves.
 \begin{proposition}\label{prop:first_elb}
-	Consider a magic state process as in~\cref{eq:stdist}, where we denote by $(x_0, L_0)$ and $(x'_0, L'_0)$ the first elbow coordinates of the initial and target states respectively, where $x_0 < x'_0$.
+	Consider a magic state process as in~\cref{eq:stdist}, where we denote by $(x_0, L_0)$ and $(x'_0, L'_0)$ the first elbow coordinates of the input and output magic states respectively. 
 	The process is possible only if
@@
 \end{equation}
-Since $x_0 < x'_0$, we can find the target state Lorenz curve coordinate $L'_\star$ at location $x = x_0$ by interpolating between the origin and the target state's first elbow, 
+First assume that $x_0 < x'_0$. 
+We can find the output state Lorenz curve coordinate $L'_\star$ at location $x = x_0$ by interpolating between the origin and the output state's first elbow, 
 \begin{equation}
@@
 \end{equation}
-The process is possible only if $L_0 \geq L_\star'$ and rearranging we get~\cref{eq:first_elb_bound1}.
+The process is then possible only if $L_0 \geq L_\star'$ which is a rearrangement of~\cref{eq:first_elb_bound1}.
+
+If instead, $x_0 \geq x'_0$, we would need to find the input state Lorenz curve coordinate $L_\star$ at location $x = x'_0$ by interpolating between the origin and the input state's first elbow, 
+\begin{equation}
+	L_\star = \frac{x'_0}{x_0}L_0.
+\end{equation}
+The process is then possible only if $L_\star \geq L'_0$ which is again a rearrangement of~\cref{eq:first_elb_bound1}.
 \end{proof}
@@
 \begin{proposition}\label{prop:last_elb}
-	Consider a magic state interconversion as in~\cref{eq:stdist}, where we denote by $(x_E, L_E)$ and $(x'_E, L'_E)$ the last elbow coordinates of the initial and target states respectively, where $x_E > x'_E$.
+	Consider a magic state process as in~\cref{eq:stdist}, where we denote by $(x_E, L_E)$ and $(x'_E, L'_E)$ the last elbow coordinates of the input and output magic states respectively.
 	The process is possible only if
 \begin{equation}\label{eq:last_elb_bound1}
-	L_E \geq 1 + \frac{1-x_E}{1-x_E'} (L_E' - 1).
+	\frac{L_E - 1}{1-x_E} \geq \frac{L'_E - 1}{1-x_E'}.
 \end{equation}
@@
 \end{equation}
-Since $x_E > x'_E$, we can find the target state Lorenz curve coordinate $L'_\star$ at location $x = x_E$ by interpolating between the the end-point $(1,1)$ and the target state's last elbow, 
+First assume that $x_E > x'_E$. 
+We can find the output state Lorenz curve coordinate $L'_\star$ at location $x = x_E$ by interpolating between the end-point $(1,1)$ and the output state's last elbow, 
 \begin{equation}
-	L'_\star = -\frac{L_E' - 1}{1 - x_E'}x_E + \frac{L_E' - x_E'}{1 - x_E'}.
+	L'_\star = 1 + \frac{1-x_E}{1-x'_E} (L'_E - 1)
 \end{equation}
-The process is possible only if $L_E \geq L_\star'$ and rearranging we get~\cref{eq:last_elb_bound1}.
+The process is then possible only if $L_E \geq L_\star'$ which is a rearrangement of~\cref{eq:last_elb_bound1}.
+
+If instead, $x_E \leq x'_E$, we would need to find the input state Lorenz curve coordinate $L_\star$ at location $x = x'_E$ by interpolating between the end-point $(1,1)$ and the input state's last elbow,
+\begin{equation}
+	L_\star = 1 + \frac{1-x'_E}{1-x_E} (L_E - 1).
+\end{equation}
+The process is then possible only if $L_\star \geq L'_E$ which is again a rearrangement of~\cref{eq:last_elb_bound1}.
 \end{proof}
@@
 
-\subsection{First elbow location}
-\label{app:first_elb_loc}
-Consider a magic state interconversion in a stabilizer $\sigma$--fragment, as in~\cref{eq:stdist}, where we remind that $n \geq n'$ and we denote by $(x_0, L_0)$ and $(x'_0, L'_0)$ the first elbow coordinates of the initial and target states respectively.
-
-Here, we show that $x_0 \leq x'_0$ for any of the three scenarios outlined in the proof of our main theorem in~\cref{sec:stab}.\\
-
-$\rm{(C1)} \rightarrow \rm{(C1)}$.
-We know from statistical physics that $e^{-\beta E_0} / \Z_\beta \leq 1$, so
-	\begin{align*}
-		x_0 &= \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^n = \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n-n'} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} \\
-		&< \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} = x_0'		
-	\end{align*}
-
-$\rm{(C2)} \rightarrow \rm{(C1)}$.
-We now use the slightly altered inequality $e^{-\beta E_{\rm{max}}} / \Z_\beta \leq 1$ to proceed,
-	\begin{align*}
-		x_0 &= \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^n = \dfrac{e^{-\beta(n E_{\rm{max}} - n' E_0)}}{\Z_\beta^{n-n'}} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} \\
-		&\leq \dfrac{e^{-\beta(n E_{\rm{max}} - n' E_0)}}{e^{-\beta (n-n') E_{\rm{max}}}} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} \\
-		&= e^{-\beta n' (E_{\rm{max}} - E_0)} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} \\
-		&\leq \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} = x_0'.
-	\end{align*}
-
-$\rm{(C2)} \rightarrow \rm{(C2)}$.
-Similarly in this scenario,
-	\begin{align*}
-		x_0 &= \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^n = \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^{n-n'} \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^{n'} \\
-		&\leq \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^{n'} = x_0'	
-	\end{align*}
-
 \subsection{Deriving distillation bounds from the last elbow}
@@
 \end{enumerate}
-Now the last elbow condition on Lorenz curves can be derived by simple interpolation, giving the condition
-\begin{equation}
-	L_E \geq 1 + \frac{1-x_E}{1-x_E'} (L_E' - 1),
-\end{equation}
-provided that the last elbow location is closer to 1 for the initial state than the target state, which is always true.
-
-The last elbow bound then can be rephrased in terms of the first elbow bound as $R_{\rm{last-elb}} - R_{\rm{first-elb}} = $
+Now using last elbow constraint, derived in~\cref{app:elb_constraints}, we can calculate new distillation bounds.
+The last elbow bounds can be rephrased in terms of the first elbow bound, leading to $R_{\rm{last-elb}} - R_{\rm{first-elb}} = $
 \begin{equation}\label{eq:last_elb_coords}

### 2021-04-17 magic_paper.tex
Added sigma -> sigma\prime calulation. Surprisingly simpler than I thought, even led to some cleaning up in the first - and last - elbow condition in the stabilizer proof and appendices

--- 2021-04-16 magic_paper.tex
@@
 
-\title{Thermodynamic constraints for magic states in quantum computation}
+\title{General thermodynamic constraints on magic state conversions for quantum computation}
 
@@
 
-The first elbow constraint involves a simple interpolation, done in~\cref{app:elb_constraints}, in order to find the coordinates of the output Lorenz curve point which is vertically aligned with the first elbow of the input Lorenz curve.
+The first elbow constraint involves a simple interpolation, done in~\cref{app:elb_constraints}, in order to find the coordinates of both Lorenz curve points at the location where the first elbow occurs.
 Comparing these two points leads to the bound
@@
 so that for a deterministic single-copy distillation process, an initial number of copies $n \geq \theta_{\rm{max}}(\tau) / \theta_{\rm{max}}(\rho) \geq 1-\epsilon$ is required.
-Therefore, the max--thauma bound for the pure Strange state distillation process can get as tight as
+Therefore, the max--thauma bound for the pure Strange state distillation process can get as tight as \nick{CALCULATING THAUMA EXACTLY AT THE MOMENT}
 \begin{equation}
@@
 \begin{equation}
-	\epsilon_{\star}(\beta) := 3 - \dfrac{18}{8-e^{(E_{\rm{max}} - E_s)\beta}}.
+	\epsilon_{\star}(\beta) := 3 - \dfrac{18}{8-2^{\beta/\beta_\star}}.
 \end{equation}
@@
 
-In each of the three scenarios, it is simple to check that the input state's first elbow has $x_0$ coordinate closer to $0$ compared to the output state, $x_0 \leq x_0'$ (see~\cref{app:first_elb_loc} for details).
-Therefore, we can use the first elbow constraint, as described in~\cref{app:elb_constraints}, leading to the following distillation bounds,
+In each of the three scenarios, we simply use the first elbow constraint, as described in~\cref{app:elb_constraints}, which leads to the following distillation bounds,
 \begin{equation}\label{eq:rate_bounds_proof}
@@
 \end{proof}
+
+We find numerically that the bounds derived above from the ascending part of the curve generally perform better than when considering the region around the Lorenz curve peak.
+Similar bounds can be obtained from the decreasing part of the Lorenz curve, but they do not shed any more light on distillation.
+Numerically ranging through the entire curve will improve our bounds incrementally, to an extent that depends on the intricate Lorenz curve structure.
+
+\subsection{Distillation bounds and energy dependencies}
+The previous section was focussed on an individual fragment, and while this does shed light on how physical constraints may, or may not, constrain protocols it is a bit indirect.
+However it is possible to adapt these bounds and put them in a more natural light.
+
+For this, we now drop the condition that $\sigma$ is left invariant under the distillation protocol, and assume it transforms to some $\sigma'$.
+This output state must be some other stabilizer state and so has a positive Wigner function also.
+The strategy is then to use how any protocol transforms $\sigma$ to act as a measure of physical features, such as energy, of the protocol.
+Therefore, we are interested in the conditions under which $(\rho, \sigma) \rightarrow (\rho', \sigma')$.
+For this we can use the full definition of relative majorization on the associated Wigner functions, and obtain distillation bounds from
+\begin{equation}
+(W_\rho(\x), W_\sigma(\x) ) \succ (W_{\rho'}(\x), W_{\sigma'}(\x) ).
+\end{equation}
+The condition for this is $L_{\rho |\sigma } (x) \ge L_{\rho'|\sigma'} (x)$, and so exactly the same analysis applies as in the previous case, but now with the Gibbs-recaling parameters for the output state being different from the ones for the input state~\cite{Renes_2016}.
+
+If the physical system has Hamiltonian $H$, and can be experimentally cooled down to some reference temperature $T$ then we can consider the reference equilibrium state $\sigma = e^{-\beta H}/\Z$, and estimate the energetic and entropic costs of any distillation protocol in terms of how the protocol transforms $\sigma$ to some other equilibrium state $\sigma'$.
+For example, if $\sigma'$ is close to the ground state \nick{fun fact: ground states correspond to $\beta \rightarrow \infty$ which makes both Lorenz curves look very rectangular - should we include this as an insight?} of the system, we then know that a great deal of entropy is dumped by the process.
+This allows us to parameterise our distillation bounds in a more insightful way.
+
+We consider an arbitrary change in the Hamiltonian driving the system, $H\rightarrow H'$ such that $\sigma' = e^{-\beta H'}/\Z'$, so the energetic parameters contributing to the Lorenz curve of the output state $\rho'$ relative to $\sigma'$ will change.
+Specifically, the first elbow coordinates of the output Lorenz curve can now be expressed as
+\begin{equation}\label{eq:transformed_first_elb_coords}
+	(x'_0, L'_0) =
+	\begin{cases}
+		\left(\frac{1}{3^{n'}} e^{-n\beta (E'_s - F'(\beta))}, v(\epsilon')^{n'} \right), &\hspace{-7pt} \rm{(C1')}	\vspace{10pt}\\
+		\left( e^{-n'\beta (E'_{\rm{max}}\hspace{-2.5pt}-F'(\beta))}, (3u(\epsilon'))^{n'} \right), &\hspace{-7pt} \rm{(C2')}
+	\end{cases}
+\end{equation}
+where now Case $\rm{(C1')}$ applies when $\epsilon' \leq \epsilon'_\star(\beta'_\star)$ (which encompasses the case $E'_s = E'_{\rm{max}}$) and Case $\rm{(C2')}$ applies when $\epsilon' > \epsilon'_\star(\beta'_\star)$ (which encompasses the case $\beta \geq \beta'_\star$).
+It is therefore now possible to get the scenario $\rm{(C1)} \rightarrow \rm{(C2')}$ if the two Hamiltonians $H,H'$ are sufficiently different.
+
+Using the first elbow constraint again leads to the following distillation bounds,
+\begin{equation}\label{eq:rate_bounds_proof}
+	R \leq
+	\begin{cases}
+		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F(\beta))}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F'(\beta))},\ &\rm{(C1)} \rightarrow \rm{(C1')}, \vspace{10pt}\\
+		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F(\beta))}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F'(\beta))},\ &\rm{(C1)} \rightarrow \rm{(C2')}, \vspace{10pt}\\
+		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F(\beta))}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F'(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C1')}, \vspace{10pt}\\
+		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F(\beta))}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F'(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C2')}.
+	\end{cases}
+\end{equation}
 

### 2021-04-17 notes/notes.tex
Added sigma -> sigma\prime calulation. Surprisingly simpler than I thought, even led to some cleaning up in the first - and last - elbow condition in the stabilizer proof and appendices

@@
 
+\subsection{Strange state MSD in the unital fragment}\label{app:lc_compare}
+
+Consider the Strange state MSD process in the unital fragment,
+\begin{equation}\label{eq:su_conversion}
+    \rho_{\rm{S}}(n', \epsilon, 0) \xrightarrow{\mathcal{O}_{\id/3}} \rho_{\rm{S}}(n', \epsilon', n-n').
+\end{equation}
+We denote input state indices without a prime and target state indices with a prime,
+\begin{align}
+    I(i,j,k=1) &= j + \sum_{\ell=0}^{i-1} m_{\ell}(n, \epsilon), \\
+    I'(i',j',k') &= k' + \left[ (j'-1) + \sum_{\ell=0}^{i'-1} m_{\ell}(n', \epsilon') \right]9^{n-n'}.
+\end{align}
+
+Pointwise Lorenz curve comparison requires $x_{I} = x_{I'}$, so the question is: 
+\begin{center}
+\emph{Given a triplet $(i',j',k')$, what is the tuple $(i,j)$ such that $I(i,j) = I'(i',j',k')$?}
+\end{center}
+
+According to~\cref{thm:elbows} which is proved in~\cref{app:lc_constraints}, for standard Lorenz curves, we need to match indices at the target state elbows, so the requirement on the indices is finding a tuple $(i, j)$, such that for a given $i' = 0,\dots,n'$,
+\begin{equation}
+	j + \sum_{\ell=0}^{i-1} m_{\ell}(n, \epsilon) = \sum_{\ell=0}^{i'} m_{\ell}(n', \epsilon').
+\end{equation}
+
+As a basic example, consider the process 
+\begin{equation}
+\rho_{\rm{S}}(\epsilon)^{\otimes 4} \xrightarrow{\mathcal{O}_{\id/3}} \rho_{\rm{S}}(\epsilon')^{\otimes 2} \otimes \left( \frac{1}{3}\id \right)^{\otimes 2}.
+\end{equation}
+We want to check which Lorenz curve is higher at the first elbows of the target state, i.e. we want to verify or reject the first inequality below:
+\begin{equation}
+	L_{I(i,j)} \geq L'_{I'(0, 1, 81)}
+\end{equation}
+where the first multiplicity of the target state is $m_0 = 1$.
+The multiplicities of the initial state are $(1, 384, 4096)$.
+
+The challenge is to find $i,j$ such that $i(i,j) = i'(0,1,81)$.
+\nick{By trial and error}, we find that $(i,j) = (1, 80)$.
+Now we can use~\cref{eq:lcsu_lcoord} to directly calculate
+\begin{align*}
+	L'_{i'(0,1,81)} &= L'_0 = \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^2 \Phi_+\left(0;2,4\frac{3-\epsilon}{15-8\epsilon}\right), \\
+	L_{i(1, 80)} &= \left(1-\frac{80}{384} \right) L_0 + \frac{80}{384} L_1 \\
+	\begin{split}
+	&= \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^4 \bigg[ \frac{19}{24} \Phi_+\left(0;4,4\frac{3-\epsilon}{15-8\epsilon}\right) \\ 
+	&\qquad + \frac{5}{24}\Phi_+\left(2;4,4\frac{3-\epsilon}{15-8\epsilon}\right) \bigg],
+	\end{split}
+\end{align*}
+and then compare them.
+
 \null\newpage
@@
 
+\subsection{First elbow location}
+\label{app:first_elb_loc}
+Consider a magic state interconversion in a stabilizer $\sigma$--fragment, as in~\cref{eq:stdist}, where we remind that $n \geq n'$ and we denote by $(x_0, L_0)$ and $(x'_0, L'_0)$ the first elbow coordinates of the initial and target states respectively.
+
+Here, we show that $x_0 \leq x'_0$ for any of the three scenarios outlined in the proof of our main theorem in~\cref{sec:stab}.\\
+
+$\rm{(C1)} \rightarrow \rm{(C1)}$.
+We know from statistical physics that $e^{-\beta E_0} / \Z_\beta \leq 1$, so
+	\begin{align*}
+		x_0 &= \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^n = \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n-n'} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} \\
+		&< \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} = x_0'		
+	\end{align*}
+
+$\rm{(C2)} \rightarrow \rm{(C1)}$.
+We now use the slightly altered inequality $e^{-\beta E_{\rm{max}}} / \Z_\beta \leq 1$ to proceed,
+	\begin{align*}
+		x_0 &= \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^n = \dfrac{e^{-\beta(n E_{\rm{max}} - n' E_0)}}{\Z_\beta^{n-n'}} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} \\
+		&\leq \dfrac{e^{-\beta(n E_{\rm{max}} - n' E_0)}}{e^{-\beta (n-n') E_{\rm{max}}}} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} \\
+		&= e^{-\beta n' (E_{\rm{max}} - E_0)} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} \\
+		&\leq \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n'} = x_0'.
+	\end{align*}
+
+$\rm{(C2)} \rightarrow \rm{(C2)}$.
+Similarly in this scenario,
+	\begin{align*}
+		x_0 &= \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^n = \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^{n-n'} \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^{n'} \\
+		&\leq \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^{n'} = x_0'	
+	\end{align*}
+
 \end{document}

### 2021-04-17 magic_paper.tex

@@
 
-\title{General thermodynamic constraints on magic state conversions for quantum computation}
+\title{General constraints on magic distillation protocols from statistical mechanics}
 

### 2021-04-18 appendix.tex
Blending of new perspective. Bits need checking for logical/detail gaps.

@@
 	\item[(i)]\label{en:m1} $\bmx \prec \bmy$;
+\end{theorem}
 	\item[(ii)]\label{en:m2} $\bmx = B \bmy$ for bistochastic $B$;
@@
 
+\begin{lemma} Let $\p$ be a quasi-probability distribution and let $\r$ be a probability distribution with strictly non-zero components.
+Let $a > 0$ and $b \in \mathbb{R}$ then $L_{a\p + b \r | \r} (x) = a L_{\p |\r}(x) + b x$.
+\end{lemma}\label{lemma:Lorenz_linearity}
+\begin{proof} The Lorenz curve of $a\p + b \r$ relative to $\r$ passes through $(0,0)$ and the points $(\sum_{i=1}^k{r_\pi(i)}, \sum_{i=1}^k(a \p + b \r)_{\pi(i)})$ where $\pi$ is the permutation that puts $(a p_i/r_i + b)$ in non-increasing order.
+However since $a > 0$, this is the same permutation that puts  $(p_i/r_i)$ in non-increasing order.
+We thus have
+\begin{equation}
+(\sum_{i=1}^kr_{\pi(i)}, \sum_{i=1}^k(a \p + b \r)_{\pi(i)}) = (\sum_{i=1}^k r_{\pi(i)},a \sum_{i=1}^k  p_{\pi(i)} + b\sum_{i=1}^k r_{\pi(i)}) \nonumber,
+\end{equation}
+therefore the value of the Lorenz function at each potential elbow point $x_k = \sum_{i=1} ^kr_{\pi(i)}$ is given by
+\begin{equation}
+L_{a \p +b \r|\r} (x_k) = a L_{\p|\r} (x_k) + b x_k,
+\end{equation}
+and so from linearity, we have in general $L_{a\p  + b\r|\r} (x) = a L_{\p |\r}(x) + b x$ for any intermediate $x$.
+\end{proof}
 \subsection{Embedding map}

### 2021-04-18 magic_paper.tex
Blending of new perspective. Bits need checking for logical/detail gaps.

@@
 
+\ddd{[Notation needs smoothing to accommodate new points of emphasis]}
 We now turn to the application of majorization to describing magic in different fragments.
@@
 
-\ddd{[I'll tidy this up more tomorrow and extend notation to full relative majorization.]}
-However, the eagle-eyed reader will point out that relative majorization is usually considered for probability distributions, and so we verify
- that the same conditions apply to quasi-probability distributions.
-This can be done from first principles, but a simple way is to reduce to the problem of genuine distributions by `masking' the negativity in $\w$ using the reference distribution $\r$.
+However, relative majorization is usually considered for probability distributions, and so we must verify that the same Lorenz curve conditions apply to quasi-probability distributions.
+This can be done from first principles, but a simpler way is see that this holds is to reduce to the problem of genuine distributions by first `masking' the negativity in the quasi-probability distribution $\w$ using the reference distribution $\r$ and then applying the conditions for relative majorization.
 
@@
 We can see that $(\w , \r) \succ (\w', \r')$ if and only if $(\w_\epsilon , \r) \succ (\w_\epsilon', \r')$, where we choose $\epsilon$ so that both $\w_\epsilon$ and $\w_\epsilon'$ are probability distributions.
-This equivalence holds because there exists a stochastic map $A$ such that $A \w = \w'$ and $A \r = \r'$ if and only if $A[\epsilon \w + (1-\epsilon) \r] = \epsilon \w' + (1-\epsilon) \r'$ and $ A\r = \r'$.
+This equivalence holds because there exists a stochastic map $A$ such that $A \w = \w'$ and $A \r = \r'$ if and only if
+\begin{equation}
+A[\epsilon \w + (1-\epsilon) \r] = \epsilon \w' + (1-\epsilon) \r'\mbox{ and } A\r = \r'.
+\end{equation}
 Now it is shown in \ddd{[cite ``The mixing distance'', E Ruch, R Schranner, TH Seligman]} relative majorization between pairs of distributions occurs if and only if the associated Lorenz curves never cross.
-Therefore we need only establish that this carries over to Lorenz curves for quasi-distributions.
-
-In the appendices we show that 
-\begin{equation}
-L_{a \w + b \r | \r} (x) = a L_{\w|\r} (x) + bL _{\r|\r}(x),
+Therefore we can express this condition in terms of the Lorenz curves of the quasi-probability distributions $\w$ and $\w'$ relative to $\r$ and $\r'$ respectively.
+
+As shown in Appendix \ref{lemma:Lorenz_linearity}, the Lorenz curve for any quasi-probability distribution obeys the following linearity condition
+\begin{equation}
+L_{a \w + b \r | \r} (x) = a L_{\w|\r} (x) + bx,
 \end{equation}
@@
 &\mbox{ if and only if }& \nonumber \\
-\epsilon L_{\w |\r} (x) + (1-\epsilon) L_{\r|\r}(x) &\ge \epsilon L_{\w' |\r'} (x) + (1-\epsilon) L_{\r'|\r'}(x).
-\end{align}
-However $L_{\r|\r}(x)$ is simply the function $f(x)=x$ for any $\r$ and so the $(1-\epsilon)$ terms cancel on both sides and we get the required relative majorization conditions for the quasi-distributions in terms of their Lorenz curves.
+\epsilon L_{\w |\r} (x) + (1-\epsilon) x &\ge \epsilon L_{\w' |\r'} (x) + (1-\epsilon) x.
+\end{align}
+The $(1-\epsilon)$ terms cancel on both sides and we get the required relative majorization conditions for the quasi-distributions in terms of their Lorenz curves.
 
@@
 
-\section{Magic bounds in arbitrary stabiliser fragments and energetic costs of distillation}
+\section{Free energy dependent bounds for magic state distillation protocols}
 \label{sec:stab}
-
-We now generalise the approach taken in the previous section and consider bounds on magic distillation for an arbitrary stabiliser fragment $\R_\sigma$, where $\sigma$ is any quantum state $\sigma \in \stab$.
-In other words, we consider those bounds on distillation that apply when the free operations have $\sigma$ as a fixed point.
-
-These bounds can be interpreted in two different ways: 
-\begin{enumerate}
-\item As a family of upper bounds parameterised by an abstract stabiliser state $\sigma$.
-\item As a constraint arising from the actual hardware limitations, noise bias or ambient thermal environment and reflected by the invariant state $\sigma$ for the system.
-\end{enumerate}
-In what follows we shall be agnostic on the interpretation.
+\ddd{[Various smoothings needed to blend with new emphasis]}
+%
+%We now generalise the approach taken in the previous section and consider bounds on magic distillation for an arbitrary stabiliser fragment $\R_\sigma$, where $\sigma$ is any quantum state $\sigma \in \stab$.
+%In other words, we consider those bounds on distillation that apply when the free operations have $\sigma$ as a fixed point.
+%
+%These bounds can be interpreted in two different ways: 
+%\begin{enumerate}
+%\item As a family of upper bounds parameterised by an abstract stabiliser state $\sigma$.
+%\item As a constraint arising from the actual hardware limitations, noise bias or ambient thermal environment and reflected by the invariant state $\sigma$ for the system.
+%\end{enumerate}
+%In what follows we shall be agnostic on the interpretation.
+
 Without loss of generality, we can always write a full-rank stabiliser state $\sigma$ in the form $\sigma =  \frac{1}{\Z_\beta} e^{-\beta H}$ for some $\beta \geq 0$ and effective Hamiltonian $H$.
-Our results will also depend on the free energy $F(\beta)$ of the state $\sigma$, expressed as
-\begin{equation}
-	F(\beta) \coloneqq \tr[H \sigma] - \beta^{-1}S(\sigma) = -\beta^{-1}\log{\Z_\beta}.
+Our results will also depend on the free energy $F$ of the state $\sigma$, expressed as
+\begin{equation}
+	F \coloneqq \tr[H \sigma] - \beta^{-1}S(\sigma) = -\beta^{-1}\log{\Z_\beta}.
 \end{equation}
@@
 Note that under interpretation (1) above, this is an abstract entropic measure of the stabilizer state, while, under interpretation (2), it corresponds to the actual thermodynamic free energy of the equilibrium state.
-
-We focus on the distillation process
-\begin{equation}\label{eq:stdist}
-	\rho_{\rm{S}}(\epsilon)^{\otimes n} \longrightarrow \rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \sigma^{\otimes (n-n')},
-\end{equation}
-where, as before, tensoring in copies of $\sigma$ does not affect the Lorenz curves of the magic states in the fragment.
+%
+%We focus on the distillation process
+%\begin{equation}\label{eq:stdist}
+%	\rho_{\rm{S}}(\epsilon)^{\otimes n} \longrightarrow \rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \sigma^{\otimes (n-n')},
+%\end{equation}
+%where, as before, tensoring in copies of $\sigma$ does not affect the Lorenz curves of the magic states in the fragment.
 
@@
 \end{figure}
-
-\begin{theorem}\label{thm:stab_bounds}
-	Given a theory of magic $\R = (\F, \O)$, let $\sigma$ be any qutrit stabiliser state, and write the state as $\sigma = \frac{1}{\Z} e^{-\beta H}$, where $H$ has eigenvalues $E_0, E_1, E_2$, and $\beta$ is an effective inverse temperature for the state.
-We define $\beta_\star = 1/kT_\star$ through the relation
+%
+%\begin{theorem}\label{thm:stab_bounds}
+%	Given a theory of magic $\R = (\F, \O)$, let $\sigma$ be any qutrit stabiliser state, and write the state as $\sigma = \frac{1}{\Z} e^{-\beta H}$, where $H$ has eigenvalues $E_0, E_1, E_2$, and $\beta$ is an effective inverse temperature for the state.
+%We define $\beta_\star = 1/kT_\star$ through the relation
+%\begin{equation}
+%	E_{\rm max} - E_s \eqqcolon kT_\star \ln 2,
+%\end{equation}
+%where $E_{\rm max} = \max\{E_0, E_1, E_2\}$ and $E_s$ is the eigenvalue of the eigenstate that overlaps the negative component of $\rho_S(\epsilon)$ in the Wigner representation.
+For $\beta \leq \beta_\star$, we define a threshold noise level
+%\begin{equation}
+%	\epsilon_{\star}(\beta) \coloneqq 3 - \dfrac{18}{8-e^{(E_{\rm max} - E_s)\beta}}.
+%\end{equation}
+%Then, any distillation rate $R(\epsilon, \beta)$ in the $\sigma$--fragment of a magic theory is bounded as follows:\\
+%If $\beta \leq \beta_{\star}$ and $\epsilon  \leq \epsilon_{\star}$,
+%\begin{equation}
+%	R(\epsilon,\beta) \leq 1 + \frac{\ln{\left( 1 - \frac{4}{3}\epsilon \right)}}{\beta (E_s - F)}.
+%\end{equation}
+%If $\beta \leq \beta_{\star}$ and $\epsilon_{\star} < \epsilon$, then
+%\begin{equation}
+%	R(\epsilon, \beta) \le 1 + \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)} - (E_{\rm max} - E_s)(\beta_{\star} - \beta)}{\beta (E_s - F)}.
+%\end{equation}
+%Otherwise if $\beta > \beta_{\star}$,
+%\begin{equation}
+%	R(\epsilon, \beta) \leq  1+ \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)}}{-\ln{2} + \beta (E_{\rm max} - F)}.
+%\end{equation}
+%In the above expressions $F$ is the effective free energy of the stabilizer state.
+%\end{theorem}
+
+\ddd{[Put assumptions here. Needs more polish+checking.]} We now consider a magic distillation protocol on multiple identical qutrits sending 
+\begin{equation}
+\rho_S(\epsilon)^{\otimes n} \longrightarrow \rho_S(\epsilon')^{\otimes Rn}
+\end{equation}•
+with $n \rightarrow \infty$. Let each qutrit have a Hamiltonian $H$ with energies $E_0, E_1, E_2$. Let $T =(k\beta)^{-1}$ be any characteristic temperature for the physical system.
+
+We can now provide distillation bounds that depend on energetic and entropic aspects of the protocol.
+However, this is done relative to a reference temperature that can be chosen freely.
+The measures associated with this protocol are then determined by how it would disturb this reference equilibrium state $\sigma$ to some different state $\sigma'$.
+More precisely, the reference equilibrium state of the $n$ qutrits is given by
+\begin{equation}
+\sigma^{\otimes n} = \left ( \frac{e^{-\beta H}}{\Z} \right )  ^{\otimes n}.
+\end{equation}
+Since we are concerned with magic distillation we may assume that the reference state $\sigma$ is not a magic state, and so has non-negative Wigner distribution.
+Instead we shall assume that it is a full-rank stabilizer state for the qutrit.
+A given magic protocol on the $n$ qutrits will correspond to a quantum channel $\E$ acting on $\rho_S(\epsilon)^{\otimes n}$.
+Our analysis associates to this protocol energy/entropy measures by considering how $\E$ transforms this reference equilibrium state.
+For simplicity we assume that the action of $\E$ on $\sigma^{\otimes n}$ is also such that correlations can be neglected in the $n\rightarrow \infty$ limit, and so $\E(\sigma^{\otimes n}) = (\sigma')^{\otimes n}$ for some state $\sigma'$.
+This assumption simplifies the application of majorization, however we note that work has also been done on the case of where correlations build up and one only looks at the marginal state on an individual subsystem \ddd{[need to cite here]} and so a more detailed analysis can also be performed.
+
+\begin{theorem}\label{thm:free-energy}
+	Consider a magic distillation protocol on $n \gg 1$ identical qutrits under the assumptions just stated. Let $T =(k\beta)^{-1}$ be any characteristic temperature for the physical system.
+
+\noindent Define $\beta_\star = 1/kT_\star$ through the relation
 \begin{equation}
@@
 \end{equation}
-Then, any distillation rate $R(\epsilon, \beta)$ in the $\sigma$--fragment of a magic theory is bounded as follows:\\
-If $\beta \leq \beta_{\star}$ and $\epsilon  \leq \epsilon_{\star}$,
-\begin{equation}
-	R(\epsilon,\beta) \leq 1 + \frac{\ln{\left( 1 - \frac{4}{3}\epsilon \right)}}{\beta (E_s - F(\beta))}.
-\end{equation}
-If $\beta \leq \beta_{\star}$ and $\epsilon_{\star} < \epsilon$, then
-\begin{equation}
-	R(\epsilon, \beta) \le 1 + \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)} - (E_{\rm max} - E_s)(\beta_{\star} - \beta)}{\beta (E_s - F(\beta))}.
-\end{equation}
-Otherwise if $\beta > \beta_{\star}$,
-\begin{equation}
-	R(\epsilon, \beta) \leq  1+ \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)}}{-\ln{2} + \beta (E_{\rm max} - F(\beta))}.
-\end{equation}
-In the above expressions $F(\beta)$ is the effective free energy of the stabilizer state.
+Then the distillation rate $R$ of the protocol is bounded as follows:
+\begin{equation}\label{eq:rate_bounds_proof}
+	R \leq
+	\begin{cases}
+		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F')},\ &\rm{(C1)} \rightarrow \rm{(C1')}, \vspace{10pt}\\
+		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F')},\ &\rm{(C1)} \rightarrow \rm{(C2')}, \vspace{10pt}\\
+		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F')},\ &\rm{(C2)} \rightarrow \rm{(C1')}, \vspace{10pt}\\
+		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F')},\ &\rm{(C2)} \rightarrow \rm{(C2')}.
+	\end{cases}
+\end{equation}
+In the above expressions $F$ is the free energy of the state $\sigma:=e^{-\beta H}/\Z$, $F'$ is the free energy of the single qutrit state $\sigma' =e^{-\beta H'}/\Z'$ defined via the action of the protocol on the reference equilibrium state.
+\ddd{[Need strategy to incorporate conditions in simple, clear way.]}
 \end{theorem}
-A few comments can be given on this result. 
+ The state $\sigma'$ is generally a non-equilibrium state for the system, however one can still associate a free energy value to the output by considering subsequently changing the Hamiltonian $H \rightarrow H'$ such that equilibrium is restored at the reference temperature $T$.
+For example, suppose that $H=H'$ then this implies the protocol would leave the equilibrium state unchanged and so corresponds to a Gibbs-preserving map \ddd{[cite Philippe]}.
+In the more general case $\Delta F := F' - F \ne 0$ and we have a free energy difference between the initial and final times, with respect to the relevant Hamiltonians.
+This is similar to the free energy differences that occur in fluctuation relations, where the final state of the system can be arbitrarily far from equilibrium, yet a free energy term for the final system still arises.
+
 Firstly, the specific numerical factors in $\epsilon_\star$ are a result of our choice of magic state. 
@@
 Specifically, the existing bounds follow by considering the dominant terms in the rescaled Wigner distribution and do not, for example, take into account the Lorenz curve's peak structure.
-Finally, it is notable that we obtain a Landauer-like condition with a characteristic temperature $kT_\star \ln 2 = E_{\rm max} - E_s$, where $kT_\star = \beta_\star^{-1}$. 
-It is unclear whether this points to a generic feature that can be directly related to fundamental thermodynamic relations, such as the erasure cost of a single bit being $kT \ln 2$. 
-Given that we work with qutrits this seems surprising, but does deserve further study.
 
@@
 
-Using that $F(\beta) = -\beta^{-1} \log \Z$, the first elbow coordinates in the two cases are now given by
+Using that $F = -\beta^{-1} \log \Z$, the first elbow coordinates in the two cases are now given by
 \begin{equation}\label{eq:first_elb_coords}
@@
 	\begin{cases}
-		\left(\frac{1}{3^n} e^{-n\beta (E_s - F(\beta))}, v^n \right), &\rm{(C1)}	\vspace{10pt}\\
-		\left( e^{-n\beta (E_{\rm{max}}-F(\beta))}, (3u)^n \right). &\rm{(C2)} 
+		\left(\frac{1}{3^n} e^{-n\beta (E_s - F)}, v^n \right), &\rm{(C1)}	\vspace{10pt}\\
+		\left( e^{-n\beta (E_{\rm{max}}-F)}, (3u)^n \right). &\rm{(C2)} 
 	\end{cases}
@@
 	\begin{cases}
-		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F(\beta))}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_s - F(\beta))},\ &\rm{(C1)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
-		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F(\beta))}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_s - F(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
-		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F(\beta))}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C2)}.
+		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_s - F)},\ &\rm{(C1)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
+		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_s - F)},\ &\rm{(C2)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
+		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F)},\ &\rm{(C2)} \rightarrow \rm{(C2)}.
 	\end{cases}
@@
 	\begin{cases}
-		\left(\frac{1}{3^{n'}} e^{-n\beta (E'_s - F'(\beta))}, v(\epsilon')^{n'} \right), &\hspace{-7pt} \rm{(C1')}	\vspace{10pt}\\
-		\left( e^{-n'\beta (E'_{\rm{max}}\hspace{-2.5pt}-F'(\beta))}, (3u(\epsilon'))^{n'} \right), &\hspace{-7pt} \rm{(C2')}
+		\left(\frac{1}{3^{n'}} e^{-n\beta (E'_s - F')}, v(\epsilon')^{n'} \right), &\hspace{-7pt} \rm{(C1')}	\vspace{10pt}\\
+		\left( e^{-n'\beta (E'_{\rm{max}}\hspace{-2.5pt}-F')}, (3u(\epsilon'))^{n'} \right), &\hspace{-7pt} \rm{(C2')}
 	\end{cases}
@@
 	\begin{cases}
-		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F(\beta))}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F'(\beta))},\ &\rm{(C1)} \rightarrow \rm{(C1')}, \vspace{10pt}\\
-		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F(\beta))}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F'(\beta))},\ &\rm{(C1)} \rightarrow \rm{(C2')}, \vspace{10pt}\\
-		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F(\beta))}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F'(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C1')}, \vspace{10pt}\\
-		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F(\beta))}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F'(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C2')}.
+		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F')},\ &\rm{(C1)} \rightarrow \rm{(C1')}, \vspace{10pt}\\
+		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F')},\ &\rm{(C1)} \rightarrow \rm{(C2')}, \vspace{10pt}\\
+		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F')},\ &\rm{(C2)} \rightarrow \rm{(C1')}, \vspace{10pt}\\
+		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F')},\ &\rm{(C2)} \rightarrow \rm{(C2')}.
 	\end{cases}

### 2021-04-19 appendix.tex
made the changes discussed, havent calculated thauma yet

@@
 	\item[(i)]\label{en:m1} $\bmx \prec \bmy$;
-\end{theorem}
 	\item[(ii)]\label{en:m2} $\bmx = B \bmy$ for bistochastic $B$;
@@
     \item[(ii)] $\Gamma_{\r}({\bmx}) \prec \Gamma_{\r}({\bmy})$;
-    \item[(iii)]\label{en:tm3} $\sum\limits_{i=1}^n \abs{x_i - t r_i} \leq \sum\limits_{i=1}^n \abs{y_i - t r_i}$ for all $t \in \mathbb{R}$;
-    \item[(iv)] $\sum\limits_{i=1}^n (x_i - t r_i)^+ \leq \sum\limits_{i=1}^n (y_i - t r_i)^+$ for all $t \in \mathbb{R}$ and \vspace{5pt}\\ $\sum\limits_{i=1}^n x_i = \sum\limits_{i=1}^n y_i$;
+    \item[(iii)]\label{en:tm3} $\sum\limits_{i=1}^n \abs{x_i - r_i t} \leq \sum\limits_{i=1}^n \abs{y_i - r_i t}$ for all $t \in \mathbb{R}$;
+    \item[(iv)] $\sum\limits_{i=1}^n (x_i - r_i t)^+ \leq \sum\limits_{i=1}^n (y_i - r_i t)^+$ for all $t \in \mathbb{R}$ and \vspace{5pt}\\ $\sum\limits_{i=1}^n x_i = \sum\limits_{i=1}^n y_i$;
     \item[(v)] $L_{\bmx|\r}(t) \leq L_{\bmy|\r}(t)$ for $t\in [0,1)$ and \vspace{5pt}\\ $L_{\bmx|\r}(1) = L_{\bmy|\r}(1)$.
@@
 	\begin{align*}
-	&\hspace{15pt} \sum\limits_{i=1}^n \abs{x_i - t r_i} = \sum\limits_{i=1}^n r_i \abs{\frac{x_i}{r_i} - t} = \sum\limits_{i=1}^N \abs{\Gamma_{\r}(\bmx)_i - t}, \\[3pt]
-	&\hspace{15pt} \sum\limits_{i=1}^n (x_i - t r_i)^+ = \sum\limits_{i=1}^N (\Gamma_{\r}(\bmx)_i - t)^+ \text{ and} \\[6pt]
+	&\hspace{15pt} \sum\limits_{i=1}^n \abs{x_i - r_i t} = \sum\limits_{i=1}^n r_i \abs{\frac{x_i}{r_i} - t} = \sum\limits_{i=1}^N \abs{\Gamma_{\r}(\bmx)_i - t}, \\[3pt]
+	&\hspace{15pt} \sum\limits_{i=1}^n (x_i - r_i t)^+ = \sum\limits_{i=1}^N (\Gamma_{\r}(\bmx)_i - t)^+ \text{ and} \\[6pt]
 	&\hspace{15pt} L_{\bmx|\r}(t) = L_{\Gamma_{\r}(\bmx)}(t),

### 2021-04-19 magic_paper.tex
made the changes discussed, havent calculated thauma yet

@@
 
-\nick{``the condition that $\id \otimes \E$ does not generate Wigner negativity is an essential requirement of any magic theory'': this is not true for stabilizer-preserving operations (SPOs)~\cite{cit:ahmadi}.
-Note that ``completely'' SPOs~\cite{cit:seddon} are a strict subset.
-However, SPOs are a subset of Wang's CPWP operations~\cite{Wang_2019} so our results hold for SPOs too.}
-
 We can view the Wigner representation $W_{\E}( \y | \x)$ of a quantum channel $\E$ as a transition matrix mapping points $\x \rightarrow \y$, which is consistent with the representation of quantum states, as
@@
 namely those operations that leave the state $\sigma \in \F$ invariant.
-\nick{We discussed that the only free state in $\R_\sigma$ is $\sigma$}
 \end{definition}
-This notion provides a simple way to break up any theory into smaller, more manageable parts that are destinguished by additional physical constraints.
+This notion provides a simple way to break up any theory into smaller, more manageable parts that are destinguished by additional physical constraints, illustrated in~\cref{fig:zoo}.
 Moreover, the union over all fragments returns the parent theory, so we are not discarding any information by breaking up the theory in this way.
@@
 \end{theorem}
-The proof of this is straightforward.
 \begin{proof}
+	The proof is straightforward.
    Suppose the interconversion is possible in a $\sigma$--fragment via some $\E \in \O_\sigma$.
@@
 \end{proof}
-
-We can now consider magic distillation rates within $\sigma$--fragments and then see how the bounds on the distillation rates depend on the choice of the fragment we work within.
-Therefore, this route can potentially shed light on how the physics of a protocol constrain distillation rates above and beyond global constraints from the parent resource theory.
-For example, how does temperature affect distillation bounds?
-Do isotropic maps have better bounds, or does bias towards some pure stabilizer state provide more freedom?
-\nick{remember to re-address these questions after deriving our bounds later on}
 
@@
 
-More importantly, by introducing this additional structure to a magic theory, it actually allows for deeper analysis than would be possible at the level of the full parent theory.
+It is now possible to consider magic distillation rates within $\sigma$--fragments and then see how the bounds on the distillation rates depend on the choice of the fragment we work within.
+Therefore, this route can potentially shed light on how the physics of a protocol constrain distillation rates above and beyond global constraints from the parent resource theory.
+For example, how does temperature affect distillation bounds?
+Do isotropic maps have better bounds, or does bias towards some pure stabilizer state provide more freedom?
+\nick{re-write based on new relative majorisation approach}
+
+By introducing this additional structure to a magic theory, we allow for deeper analysis than would be possible at the level of the full parent theory.
 In particular, the interconversion structure in each fragment can be analysed using tools from single-shot thermodynamics and majorization theory as we discuss in the next section.
@@
 More precisely, within the theory we order magic states as $\rho_1 \succ \rho_2$ whenever there is an operation $\E \in \O$ such that $\E(\rho_1) = \rho_2$.
-However, in general many states will not be interconvertible in either direction, and so this ordering is a pre-order in the sense that incomparable states exist.
+In general many states will not be interconvertible in both directions, so this ordering is a pre-order in the sense that incomparable states exist.
 A magic monotone projects this pre-order of states onto the real number line, and, through this lens, any two states are directly comparable in terms of their mapped values $\M(\rho_1)$, $\M(\rho_2)$.
@@
 The question is now whether the sub-theories can be analysed to provide additional insights into magic distillation protocols.
-We shall provide an answer by working in the Wigner representation of a given $\sigma$--fragment.
+An answer can be provided by working in the Wigner representation of a given $\sigma$--fragment.
 The problem of magic state distillation then becomes that of processing negativity under stochastic maps $W_{\E}( \y |\x)$ that leave a particular quasi-distribution $W_\sigma(\x)$ invariant.
@@
 Given two distributions $\p= (p_1, \dots, p_n)$ and $\q = (q_1, \dots, q_n)$ over $n$ outcomes, we say that $\p$ majorises $\q$, denoted $\p \succ \q$, if there exists a bistochastic map $A = (A_{ij})$ such that $A\p = \q$, where bistochastic means that $A_{ij} \geq 0$ and $\sum_i A_{ij} = \sum_j A_{ij} = 1$.
-A well-known result~\cite{cit:marshall} tells us that the condition $ \p \succ \q$ over probability distributions is equivalent to $n-1$ inequalities, which can be easily checked.
-
-There is a natural generalisation, which we call \emph{relative majorization} (also known as $\bmd$--majorization~\cite{Veinott_1971}, or in the context of thermodynamics, thermo-majorization)\footnote{The general form of relative majorization is defined as $(\p,\r) \succ (\q, \r')$ iff there is a stochastic map $A$ such that $A\r = \r'$ and $A\p = \q$.
-We retrieve $\bmd$--majorization when $\r = \r'$.}.
-For a fixed probability distribution $\r = (r_1, \dots, r_n)$ with positive components, we define majorization relative to $\r$ as follows:
-\begin{equation}
-\p \succ_{\r} \q,
-\end{equation}
-if and only if there exists a stochastic map $A$ such that $A\r = \r$ and $A \p = \q$.
+A well-known result~\cite{cit:marshall} tells us that the condition $ \p \succ \q$ over probability distributions is equivalent to $n-1$ inequalities, which can be checked efficiently.
+
+There is a natural generalisation, which is called $\bmd$--majorization~\cite{Veinott_1971}, or in the context of thermodynamics, thermo-majorization.
+For a fixed probability distribution $\r = (r_1, \dots, r_n)$ with positive components, we define majorization relative to $\r$ as $\p \succ_{\r} \q$, if and only if there exists a stochastic map $A$ such that $A\r = \r$ and $A \p = \q$.
 In order words, the relative majorization pre-order coincides with the image of $\p$ under stochastic maps that have $\r$ as a fixed point.
@@
 
-It turns out that relative majorization is equally applicable to \emph{quasi-probability} distributions, and therefore can be applied to the Wigner representation of a given fragment.
-To our knowledge, this application of majorization to quasi-distributions in  physics has not been considered previously.
-The caveat here is that relative majorization ranges over all stochastic maps with a given fixed point, while in the case of the Wigner representation there is an additional restriction that the phase space structure is respected.
-Therefore, any relative majorization constraint can provide necessary, but not sufficient conditions on magic state interconversions in the fragment.
+We can further loosen the condition that vector $\r$ is kept fixed to get \emph{relative majorization}, defined as an ordering between pairs of vectors so that 
+\begin{equation}
+	(\p,\r) \succ (\q, \r')
+\end{equation}
+iff there is a stochastic map $A$ such that $A\r = \r'$ and $A\p = \q$. We retrieve $\bmd$--majorization when $\r = \r'$.
+
+It turns out that relative majorization is equally applicable to \emph{quasi-probability} distributions, and therefore can be applied to the Wigner representation of magic across fragments.
+We justify the applicability and power of relative majorization in the next section.
+
+At this point we note that, to our knowledge, this application of majorization to quasi-distributions in  physics has not been considered previously.
+The caveat here is that relative majorization ranges over stochastic maps that obey a fixed transformation ($A\r = \r'$), while in the case of the Wigner representation there is an additional restriction that the symplectic structure of the phase space is respected.
+Therefore, any majorization constraint can provide necessary, but not sufficient conditions on magic state interconversions in the fragment.
 This observation raises a question that to our knowledge has not been previously considered in the classical statistical mechanics literature: what are the conditions for symplectic majorization of classical statistical mechanics?
-We shall return to this question later on when we discuss how our approach could be used to construct concrete lower-bounds on distillation rates in~\cref{sec:lower_bounds}.
+We shall \nick{return} to this question later on when we discuss how our approach could be used to construct concrete lower-bounds on distillation rates in~\cref{sec:lower_bounds}.
 
@@
 The form of this requires that $\r$ has no zero components, which we shall assume without loss of generality as in any physical situation the rank of a quantum state is not an operationally meaningful quantity.
-We also stress that the curve contains non-differentiable points at locations where $\widetilde{\bmw}$ changes value, which we call \emph{elbows}.
+We also observe that the curve contains non-differentiable points, called \emph{elbows} at locations where $\widetilde{\bmw}$ changes value.
 
@@
 \end{equation}
-Now it is shown in \ddd{[cite ``The mixing distance'', E Ruch, R Schranner, TH Seligman]} relative majorization between pairs of distributions occurs if and only if the associated Lorenz curves never cross.
+Now it is shown in~\cite{ruch_mixing_1978} relative majorization between pairs of distributions occurs if and only if the associated Lorenz curves never cross.
 Therefore we can express this condition in terms of the Lorenz curves of the quasi-probability distributions $\w$ and $\w'$ relative to $\r$ and $\r'$ respectively.
@@
 	\begin{equation}
-\sum_k | p_k - t r_k | \ge \sum_k |q_k - t r_k|,
+\sum_k | p_k - r_k t | \geq \sum_k | q_k - r_k t |,
 \end{equation}
@@
 Here $S(\sigma)$ is the von Neumann entropy $S(\sigma) \coloneqq -\tr[\sigma\log{\sigma}]$.
-Note that under interpretation (1) above, this is an abstract entropic measure of the stabilizer state, while, under interpretation (2), it corresponds to the actual thermodynamic free energy of the equilibrium state.
+\nick{Note that under interpretation (1) above, this is an abstract entropic measure of the stabilizer state, while, under interpretation (2), it corresponds to the actual thermodynamic free energy of the equilibrium state.}
 %
@@
 
-Given this context, we now provide the following result on bounding the distillation rate $R = R(\epsilon, \epsilon', \beta) \coloneqq \frac{n'}{n}$ of the process in~\cref{eq:stdist}.
+Given this context, we now provide the following result on bounding the distillation rate $R = R(\epsilon, \epsilon', \beta) \coloneqq \frac{n'}{n}$ of the process in\nick{~\cref{eq:stdist}}.
 We shall write $R(\epsilon, \beta) = R(\epsilon, \epsilon'=0, \beta)$ for the limiting case of distilling a pure magic state.
@@
 \rho_S(\epsilon)^{\otimes n} \longrightarrow \rho_S(\epsilon')^{\otimes Rn}
-\end{equation}•
+\end{equation}
 with $n \rightarrow \infty$. Let each qutrit have a Hamiltonian $H$ with energies $E_0, E_1, E_2$. Let $T =(k\beta)^{-1}$ be any characteristic temperature for the physical system. 
+We define $\beta_\star = 1/kT_\star$ through the relation
+\begin{equation}
+	E_{\rm max} - E_s \eqqcolon kT_\star \ln 2,
+\end{equation}
+where $E_{\rm max} = \max\{E_0, E_1, E_2\}$ and $E_s$ is the eigenvalue of the eigenstate that overlaps the negative component of $\rho_S(\epsilon)$ in the Wigner representation.
+We define a threshold noise level,
+\begin{equation}
+	\epsilon_{\star}(\beta) \coloneqq 
+	\begin{cases}
+		3 - \dfrac{18}{8-2^{\beta/\beta_\star}}, &\text{ for } \beta \leq \beta_\star \\
+		0, &\text{ for } \beta > \beta_\star.
+	\end{cases}
+\end{equation}
 
@@
 
+Finally, we can paramterise the state $\sigma'$ by defining a fiducial Hamiltonian $H'$, so that $\sigma' = e^{-\beta H'} / \Z$, while we denote all quantities relevant to this output state $\sigma'$ by priming them, leading to $E'_{\rm{max}}, E'_s, \beta'_\star$ and $\epsilon'_\star$.
+
 \begin{theorem}\label{thm:free-energy}
-	Consider a magic distillation protocol on $n \gg 1$ identical qutrits under the assumptions just stated. Let $T =(k\beta)^{-1}$ be any characteristic temperature for the physical system.
-
-\noindent Define $\beta_\star = 1/kT_\star$ through the relation
-\begin{equation}
-	E_{\rm max} - E_s \eqqcolon kT_\star \ln 2,
-\end{equation}
-where $E_{\rm max} = \max\{E_0, E_1, E_2\}$ and $E_s$ is the eigenvalue of the eigenstate that overlaps the negative component of $\rho_S(\epsilon)$ in the Wigner representation.
-For $\beta \leq \beta_\star$, we define a threshold noise level
-\begin{equation}
-	\epsilon_{\star}(\beta) \coloneqq 3 - \dfrac{18}{8-e^{(E_{\rm max} - E_s)\beta}}.
-\end{equation}
+	Consider a magic distillation protocol on $n \gg 1$ identical qutrits under the assumptions just stated.
+
 Then the distillation rate $R$ of the protocol is bounded as follows:
@@
 	\begin{cases}
-		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F')},\ &\rm{(C1)} \rightarrow \rm{(C1')}, \vspace{10pt}\\
-		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F')},\ &\rm{(C1)} \rightarrow \rm{(C2')}, \vspace{10pt}\\
-		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F')},\ &\rm{(C2)} \rightarrow \rm{(C1')}, \vspace{10pt}\\
-		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F')},\ &\rm{(C2)} \rightarrow \rm{(C2')}.
+		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F')},\ &\epsilon \leq \epsilon_\star, \epsilon' \leq \epsilon'_\star, \vspace{10pt}\\
+		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F')},\ &\epsilon \leq \epsilon_\star, \epsilon' > \epsilon'_\star, \vspace{10pt}\\
+		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F')},\ &\epsilon > \epsilon_\star, \epsilon' \leq \epsilon'_\star, \vspace{10pt}\\
+		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F')},\ &\epsilon > \epsilon_\star, \epsilon' > \epsilon'_\star.
 	\end{cases}
 \end{equation}
-In the above expressions $F$ is the free energy of the state $\sigma:=e^{-\beta H}/\Z$, $F'$ is the free energy of the single qutrit state $\sigma' =e^{-\beta H'}/\Z'$ defined via the action of the protocol on the reference equilibrium state.
+In the above expressions $F$ is the free energy of the state $\sigma \coloneqq e^{-\beta H}/\Z$ and $F'$ is the free energy of the single qutrit state $\sigma' = e^{-\beta H'}/\Z'$ defined via the action of the protocol on the reference equilibrium state.
 \ddd{[Need strategy to incorporate conditions in simple, clear way.]}
@@
 \end{equation}
-such that for the regime $0 \leq \beta \leq \beta_\star$ a transition noise level $\epsilon_\star$ exists, and for $\beta > \beta_\star$ no such transition exists.
-The transition value for the noise is given by
-\begin{equation}
-	\epsilon_{\star}(\beta) := 3 - \dfrac{18}{8-2^{\beta/\beta_\star}}.
+such that for the regime $0 \leq \beta \leq \beta_\star$ a transition noise level $\epsilon_\star$ exists, and for $\beta > \beta_\star$ no such transition exists, so we choose $\epsilon_\star = 0$. 
+Therefore, the transition value for the noise is given by
+\begin{equation}
+	\epsilon_{\star}(\beta) \coloneqq 
+	\begin{cases}
+		3 - \dfrac{18}{8-2^{\beta/\beta_\star}}, &\text{ for } \beta \leq \beta_\star \\
+		0, &\text{ for } \beta > \beta_\star.
+	\end{cases}
 \end{equation}
@@
 	\begin{cases}
-		(3\Z)^{n} v^n e^{n\beta E_s}, &\mbox{if }\epsilon \leq \epsilon_{\star},\ \hspace{3pt}\rm{(C1)}	\\
+		(3\Z)^{n} v^n e^{n\beta E_s}, &\mbox{if }\epsilon \leq \epsilon_{\star},\ \hspace{3pt}\rm{(C1)}\\
 		(3\Z)^{n} u^n e^{n\beta E_{\rm{max}}}, &\mbox{if }\epsilon > \epsilon_{\star}.\ \hspace{5pt}\rm{(C2)} 
@@
 	\begin{cases}
-		\left(\frac{1}{3^n} e^{-n\beta (E_s - F)}, v^n \right), &\rm{(C1)}	\vspace{10pt}\\
-		\left( e^{-n\beta (E_{\rm{max}}-F)}, (3u)^n \right). &\rm{(C2)} 
+		\left(\frac{1}{3^n} e^{-n\beta (E_s - F)}, v^n \right), &\epsilon \leq \epsilon_\star \vspace{10pt}\\
+		\left( e^{-n\beta (E_{\rm{max}}-F)}, (3u)^n \right). &\epsilon > \epsilon_\star
 	\end{cases}
 \end{equation}
-To obtain the distillation bounds from majorization we can now compute the above terms for both the input and output states.
-Depending on the noise parameters $\epsilon, \epsilon'$ for the input and output states the Lorenz curve data may fall into either case $\rm{(C1)}$ or case $\rm{(C2)}$.
-Specifically, we have three scenarios of relevance to magic distillation:
-\begin{enumerate}
-	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} = E_s$ or $E_{\rm{max}} > E_s$, $\beta < \beta_{\star}$ and $\epsilon' < \epsilon  \leq \epsilon_{\star}$.
-	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} > E_s$, $\beta < \beta_{\star}$ and $\epsilon' \leq \epsilon_{\star} < \epsilon$.
-	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $E_{\rm{max}} > E_s$, $\beta < \beta_{\star}$ and $\epsilon_{\star} \leq \epsilon' < \epsilon$ or $E_{\rm{max}} > E_s$, $\beta \geq \beta_{\star}$.
-\end{enumerate}
-The scenario $\rm{(C1)} \rightarrow \rm{(C2)}$ is not considered as it would correspond to $\epsilon \leq \epsilon_\star < \epsilon'$, which would imply that the output magic state is noisier than the input state.
-
-In each of the three scenarios, we simply use the first elbow constraint, as described in~\cref{app:elb_constraints}, which leads to the following distillation bounds,
-\begin{equation}\label{eq:rate_bounds_proof}
-	R \leq
+Similarly, considering the output magic state with respect to state $\sigma'$, the image of equilibrium state $\sigma$ under the magic protocol, we get output Lorenz curve coordinates,
+\begin{equation}\label{eq:transformed_first_elb_coords}
+	(x'_0, L'_0) =
 	\begin{cases}
-		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_s - F)},\ &\rm{(C1)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
-		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_s - F)},\ &\rm{(C2)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
-		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F)},\ &\rm{(C2)} \rightarrow \rm{(C2)}.
+		\left(\frac{1}{3^{n'}} e^{-n\beta (E'_s - F')}, v(\epsilon')^{n'} \right), &\epsilon' \leq \epsilon'_\star \vspace{10pt}\\
+		\left( e^{-n'\beta (E'_{\rm{max}}\hspace{-2.5pt}-F')}, (3u(\epsilon'))^{n'} \right), &\epsilon' > \epsilon'_\star
 	\end{cases}
 \end{equation}
-Substituting $\epsilon' = 0$ into these expressions leads to the stated distillation bounds.
+There are four combinations of coordinates, depending on the noise parameters $\epsilon, \epsilon'$ for the input and output states.
+In each of these combinations, we simply use the first elbow constraint, as described in~\cref{app:elb_constraints}, which leads to the bounds in the statement of the theorem.
+%\begin{enumerate}
+%	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} = E_s$ or $E_{\rm{max}} > E_s$, $\beta < \beta_{\star}$ and $\epsilon' < \epsilon  \leq \epsilon_{\star}$.
+%	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} > E_s$, $\beta < \beta_{\star}$ and $\epsilon' \leq \epsilon_{\star} < \epsilon$.
+%	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $E_{\rm{max}} > E_s$, $\beta < \beta_{\star}$ and $\epsilon_{\star} \leq \epsilon' < \epsilon$ or $E_{\rm{max}} > E_s$, $\beta \geq \beta_{\star}$.
+%\end{enumerate}
+%The scenario $\rm{(C1)} \rightarrow \rm{(C2)}$ is not considered as it would correspond to $\epsilon \leq \epsilon_\star < \epsilon'$, which would imply that the output magic state is noisier than the input state.
+%Substituting $\epsilon' = 0$ into these expressions leads to the stated distillation bounds.
 
@@
 This allows us to parameterise our distillation bounds in a more insightful way.
-
-We consider an arbitrary change in the Hamiltonian driving the system, $H\rightarrow H'$ such that $\sigma' = e^{-\beta H'}/\Z'$, so the energetic parameters contributing to the Lorenz curve of the output state $\rho'$ relative to $\sigma'$ will change.
-Specifically, the first elbow coordinates of the output Lorenz curve can now be expressed as
-\begin{equation}\label{eq:transformed_first_elb_coords}
-	(x'_0, L'_0) =
-	\begin{cases}
-		\left(\frac{1}{3^{n'}} e^{-n\beta (E'_s - F')}, v(\epsilon')^{n'} \right), &\hspace{-7pt} \rm{(C1')}	\vspace{10pt}\\
-		\left( e^{-n'\beta (E'_{\rm{max}}\hspace{-2.5pt}-F')}, (3u(\epsilon'))^{n'} \right), &\hspace{-7pt} \rm{(C2')}
-	\end{cases}
-\end{equation}
-where now Case $\rm{(C1')}$ applies when $\epsilon' \leq \epsilon'_\star(\beta'_\star)$ (which encompasses the case $E'_s = E'_{\rm{max}}$) and Case $\rm{(C2')}$ applies when $\epsilon' > \epsilon'_\star(\beta'_\star)$ (which encompasses the case $\beta \geq \beta'_\star$).
-It is therefore now possible to get the scenario $\rm{(C1)} \rightarrow \rm{(C2')}$ if the two Hamiltonians $H,H'$ are sufficiently different.
-
-Using the first elbow constraint again leads to the following distillation bounds,
-\begin{equation}\label{eq:rate_bounds_proof}
-	R \leq
-	\begin{cases}
-		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F')},\ &\rm{(C1)} \rightarrow \rm{(C1')}, \vspace{10pt}\\
-		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F')},\ &\rm{(C1)} \rightarrow \rm{(C2')}, \vspace{10pt}\\
-		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F')},\ &\rm{(C2)} \rightarrow \rm{(C1')}, \vspace{10pt}\\
-		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F')},\ &\rm{(C2)} \rightarrow \rm{(C2')}.
-	\end{cases}
-\end{equation}
 

### 2021-04-20 appendix.tex
a few more changes

@@
 \end{lemma}\label{lemma:Lorenz_linearity}
-\begin{proof} The Lorenz curve of $a\p + b \r$ relative to $\r$ passes through $(0,0)$ and the points $(\sum_{i=1}^k{r_\pi(i)}, \sum_{i=1}^k(a \p + b \r)_{\pi(i)})$ where $\pi$ is the permutation that puts $(a p_i/r_i + b)$ in non-increasing order.
-However since $a > 0$, this is the same permutation that puts  $(p_i/r_i)$ in non-increasing order.
+\begin{proof} The Lorenz curve of $a\p + b \r$ relative to $\r$ passes through $(0,0)$ and the points $(\sum_{i=1}^k{r_{\pi(i)}}, \sum_{i=1}^k(a \p + b \r)_{\pi(i)})$ where $\pi$ is the permutation that puts $(a p_i/r_i + b)$ in non-increasing order.
+Since $a > 0$, the permutation $\pi$ puts  $(p_i/r_i)$ in non-increasing order too.
 We thus have
-\begin{equation}
-(\sum_{i=1}^kr_{\pi(i)}, \sum_{i=1}^k(a \p + b \r)_{\pi(i)}) = (\sum_{i=1}^k r_{\pi(i)},a \sum_{i=1}^k  p_{\pi(i)} + b\sum_{i=1}^k r_{\pi(i)}) \nonumber,
-\end{equation}
+\begin{align*}
+&\left( \sum_{i=1}^kr_{\pi(i)}, \sum_{i=1}^k(a \p + b \r)_{\pi(i)} \right) = \\ 
+&\left( \sum_{i=1}^k r_{\pi(i)},a \sum_{i=1}^k  p_{\pi(i)} + b\sum_{i=1}^k r_{\pi(i)} \right) \nonumber,
+\end{align*}
 therefore the value of the Lorenz function at each potential elbow point $x_k = \sum_{i=1} ^kr_{\pi(i)}$ is given by
-\begin{equation}
-L_{a \p +b \r|\r} (x_k) = a L_{\p|\r} (x_k) + b x_k,
-\end{equation}
-and so from linearity, we have in general $L_{a\p  + b\r|\r} (x) = a L_{\p |\r}(x) + b x$ for any intermediate $x$.
+\begin{align}
+&L_{a \p +b \r|\r} (x_k) = a L_{\p|\r} (x_k) + b L_{\r|\r}(x_k) = \nonumber\\
+&a L_{\p|\r} (x_k) + b x_k,
+\end{align}
+so we have $L_{a\p  + b\r|\r} (x) = a L_{\p |\r}(x) + b x$ for any $x \in [0,1]$ due to linearity.
 \end{proof}

### 2021-04-20 magic_paper.tex
a few more changes

@@
         ]{figs/operations.pdf}
-    \caption{\textbf{Decomposition of a magic theory $\R$ intro $\sigma$--fragments.} 
+    \caption{\textbf{Decomposition of a magic theory $\R$ into $\sigma$--fragments.} 
 	Examples of magic theories ($\so$: Stabilizer operations, $\Omax$: Completely positive-Wigner-preserving operations, $\rcu$: Random Clifford Unitaries -- subclass of $\so$) are labelled, with other established magic theories also contained within the yellow regions.
@@
 At this point we note that, to our knowledge, this application of majorization to quasi-distributions in  physics has not been considered previously.
-The caveat here is that relative majorization ranges over stochastic maps that obey a fixed transformation ($A\r = \r'$), while in the case of the Wigner representation there is an additional restriction that the symplectic structure of the phase space is respected.
-Therefore, any majorization constraint can provide necessary, but not sufficient conditions on magic state interconversions in the fragment.
+The caveat here is that relative majorization ranges over stochastic maps that obey a fixed transformation ($A\r = \r'$), while in the case of the Wigner representation there is a stronger restriction that the symplectic structure of the phase space is respected.
+Therefore, any majorization constraint can provide necessary, but not sufficient conditions on magic state interconversions.
 This observation raises a question that to our knowledge has not been previously considered in the classical statistical mechanics literature: what are the conditions for symplectic majorization of classical statistical mechanics?

### 2021-04-20 magic_paper.tex
Free energy bound physics sharpened. Still needs smoothing. Bit clunky.

@@
 \label{sec:stab}
-\ddd{[Various smoothings needed to blend with new emphasis]}
-%
-%We now generalise the approach taken in the previous section and consider bounds on magic distillation for an arbitrary stabiliser fragment $\R_\sigma$, where $\sigma$ is any quantum state $\sigma \in \stab$.
-%In other words, we consider those bounds on distillation that apply when the free operations have $\sigma$ as a fixed point.
-%
-%These bounds can be interpreted in two different ways: 
+
+We now consider a magic distillation protocol on multiple identical qudits in a noisy magic state $\rho(\epsilon)$, with noise parameter $\epsilon$, sending 
+\begin{equation}
+\rho(\epsilon)^{\otimes n} \longrightarrow \E(\rho(\epsilon)^{\otimes n}) =\rho(\epsilon')^{\otimes m}
+\end{equation}
+with $n \gg 1$, $\epsilon' <\epsilon$ and $\E$ denoting the quantum channel induced by the protocol.
+We can now provide distillation bounds that depend on energetic and entropic aspects of the protocol.
+We do this relative to a reference temperature that can be chosen freely.
+The key ideas is that the physical measures associated with this protocol are determined by how $\E$ would disturb this reference equilibrium state $\tau$ to some different state $\tau'$, if the protocol had been applied to this reference state instead of the $n$-copy magic state.
+
+More precisely, we assume each qudit has Hamiltonian $H$ and we choose some temperature $T = (k\beta)^{-1}$ where $k$ is Boltzmann's constant and $\beta$ the inverse temperature.
+The reference equilibrium state of the $n$ qudits is given by
+\begin{equation}
+\tau^{\otimes n} = \left ( \frac{e^{-\beta H}}{\Z} \right )  ^{\otimes n}.
+\end{equation}
+Since we are concerned with magic distillation we may assume that the reference state $\tau$ is not a magic state, and so has non-negative Wigner distribution, and we shall assume that it is a full-rank stabilizer state for the qudit.
+
+A given magic protocol on the $n$ qudits will correspond to a quantum channel $\E$.
+Our analysis associates to this protocol energy/entropy measures by considering how $\E$ transforms this reference equilibrium state.
+We first note that we can assume without loss of generality that $U_\pi\E(X) U_\pi^\dagger = \E(X)$ for any permutation $U_\pi$ of the $m$ output subsystems.
+The reason for this is that the protocol on the noisy magic state outputs the state $\rho(\epsilon')^{\otimes m}$, which is invariant under permutations, and so we can therefore always symmetrise by performing a group average over the permutation group for the output systems without changing the performance of the distillation protocol on $\rho(\epsilon)^{\otimes n}$.
+Thus, we can assume that $\E$ always outputs a symmetric state in general.
+
+This means in particular that $\E(\tau^{\otimes n}) = \tau'$ is a symmetric state on $m$ subsystems, and so by the quantum de Finetti theorem \ddd{[cite]} we have that
+\begin{equation}
+\tau'  = \int d\mu(x) \sigma_x^{\otimes m},
+\end{equation}
+where $d\mu(x)$ is a probability measure over a set $\{\sigma_x\}$ of single qudit states.
+
+To simplify our analysis we now make the following assumption.
+We assume that in the asymptotic/thermodynamic limit $n,m \rightarrow \infty$ that correlations generated in $\sigma$ are negligible.
+This implies that $d\mu(x)$ is peaked on a particular state $\sigma$, and so $\tau' = \sigma^{\otimes m}$.
+Physically, this is a natural scenario -- for example in traditional thermodynamics it states that the output system is well-described by intrinsic variables that are encoded in $\sigma$.
+Here this assumption allows us to associate a free energy per qudit for the output state, which would be more complex if correlations are present.
+
+The case of correlations between output subsystems can also be considered, but would lead to a more complex analysis within our majorization analysis of Wigner distributions.
+In this direction we highlight recent work in majorization in which stochastic independence and correlations are analysed.
+In particular it has been shown that stochastic independence (no correlations) of independent distributions can be viewed as a resource in an extension of catalytic majorization, and leads to a single-shot operational interpretation of the Shannon entropy.
+
+The action of the protocol on the reference states therefore transforms $\tau \rightarrow \sigma$.
+It turns out our distillation bounds depend on the free energy of the input and output states.
+For a state $\tau = e^{-\beta H}/\Z$ the associated free energy $F$ is given by
+\begin{equation}
+	F \coloneqq \tr[H \tau] - \beta^{-1}S(\tau) = -\beta^{-1}\log{\Z}.
+\end{equation}
+The output state $\sigma$ is generally a non-equilibrium state for the system.
+However, the distillation bound takes a particularly simple form if we associate a similar free energy value to the output state.
+We do this by considering the change in Hamiltonian $H \rightarrow H'$ such that equilibrium is restored at the reference temperature $T$.
+This implies that
+\begin{equation}
+\sigma = \frac{e^{-\beta H'}}{\Z'},
+\end{equation}
+which has free energy $F' = -\beta^{-1} \log \Z'$.
+Therefore the action of $\E$ sending $\tau$ to $\sigma$ is viewed in terms of $\Delta H := H'-H$, which is the Hamiltonian change that would be needed to adiabatically restore equilibrium at temperature $T$.
+
+ Given this account of the physical ingredients of a distillation protocol we now state the following result for the case of qutrits.
+\begin{theorem}\label{thm:free-energy}
+	Consider a magic distillation protocol on $n \gg 1$ qutrits transforming noisy Strange state $\rho_S(\epsilon)^{\otimes n} \rightarrow \rho_S(\epsilon')^{\otimes m}$, under the assumptions just stated.
+
+Let each qutrit have a Hamiltonian $H$ with energies $E_0, E_1, E_2$. Let $T =(k\beta)^{-1}$ be any characteristic temperature for the physical system in the state $\tau$, with free energy $F$. 
+We define $\beta_\star = 1/kT_\star$ through the relation
+\begin{equation}
+	E_{\rm max} - E_s \eqqcolon kT_\star \ln 2,
+\end{equation}
+where $E_{\rm max} = \max\{E_0, E_1, E_2\}$ and $E_s$ is the eigenvalue of the eigenstate that overlaps the negative component of $\rho_S(\epsilon)$ in the Wigner representation.
+We define a threshold noise level,
+\begin{equation}
+	\epsilon_{\star}(\beta) \coloneqq 
+	\begin{cases}
+		3 - \dfrac{18}{8-2^{\beta/\beta_\star}}, &\text{ for } \beta \leq \beta_\star \\
+		0, &\text{ for } \beta > \beta_\star.
+	\end{cases}
+\end{equation}
+Then the distillation rate $R = m/n$ of the magic protocol is bounded as follows:
+\begin{equation}\label{eq:rate_bounds_proof}
+	R \leq
+	\begin{cases}
+		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F')},\ &\epsilon \leq \epsilon_\star, \epsilon' \leq \epsilon'_\star, \vspace{10pt}\\
+		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F')},\ &\epsilon \leq \epsilon_\star, \epsilon' > \epsilon'_\star, \vspace{10pt}\\
+		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F')},\ &\epsilon > \epsilon_\star, \epsilon' \leq \epsilon'_\star, \vspace{10pt}\\
+		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F')},\ &\epsilon > \epsilon_\star, \epsilon' > \epsilon'_\star.
+	\end{cases}
+\end{equation}
+Where $F'$ is the free energy of the single qutrit output state $\sigma = e^{-\beta H'}/\Z'$ of the protocol applied to $\tau$. 
+\end{theorem}
+
+  For example, suppose that $H=H'$ then this implies the protocol would leave the equilibrium state unchanged and so corresponds to a Gibbs-preserving map \ddd{[cite Philippe]}.
+In the more general case $\Delta F := F' - F \ne 0$ and we have a free energy difference between the initial and final times, with respect to the relevant Hamiltonians.
+This is similar to the free energy differences that occur in fluctuation relations, where the final state of the system can be arbitrarily far from equilibrium, yet a free energy term for the final system still arises.
+Firstly, the specific numerical factors in $\epsilon_\star$ are a result of our choice of magic state. 
+Secondly, these bounds are derived based on analysis of only a part of the Lorenz curves and can be improved via a finer analysis. 
+This is apparent by simple numerical calculations on the entirety of the curves.
+Specifically, the existing bounds follow by considering the dominant terms in the rescaled Wigner distribution and do not, for example, take into account the Lorenz curve's peak structure.
+
+\begin{proof}
+	We provide the full proof here, with some technical details pushed to~\cref{app:lcst_technical}.\\
+
+Let $\displaystyle \sigma = e^{-\beta H} / \Z_\beta$ be a stabiliser state, where $\beta \geq 0$ and $H = E_0 \ketbra{\varphi_0} + E_1 \ketbra{\varphi_1} + E_2 \ketbra{\varphi_2}$ is an eigendecomposition of $H$.
+The stabilizer state $\sigma$ can now be written as 
+\begin{equation}
+	\sigma = \frac{e^{-\beta E_0}}{\Z_\beta} \ketbra{\varphi_0} + \frac{e^{-\beta E_1}}{\Z_\beta} \ketbra{\varphi_1} + \frac{e^{-\beta E_2}}{\Z_\beta} \ketbra{\varphi_2},
+\end{equation}
+where $\{\ket{\varphi_k}\<\varphi_k|\}$ are pure, orthonormal stabiliser states, which can be represented in terms of generalized Paulis.
+To make our analysis simpler we perform a change of basis that does not affect the Wigner negativity of the problem.
+We let $C$ be the unitary transforming each $|\varphi_k\>\<\varphi_k|$ to $|k\>\<k|$.
+Since the Clifford group is the normalizer of the Heisenberg-Weyl group, $C$ is a Clifford unitary.
+Therefore, $C$ maps $\sigma$ to another stabilizer state that is diagonal in the computational basis, and we can assume without loss of generality that $\sigma$ is diagonal in $\{|0\>,|1\>, |2\>\}$.
+However, this choice means that the location of the negative Wigner component $-v(\epsilon)$ of the Strange state will be permuted on the discrete phase space.
+We denote by $E_s$ the eigenvalue of $H$ where the associated eigenvector has Wigner distribution overlapping the negative component of the magic state $C\rho_S(\epsilon)C^\dagger$.
+This is unique, since the eigenstates form an orthonormal basis.
+
+The Wigner distribution of state $\sigma$ is then given by
+\begin{align}
+	\W[\bmx]{\sigma} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z_\beta}W_{\ketbra{k}}(x, p) \nonumber\\
+	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z_\beta} \delta_{x, k} = \frac{e^{-\beta E_x}}{3\Z_\beta},
+\end{align}
+where $x$ labels one of the three vertical lines in the phase space.
+Since we have restricted to full-rank states, all Wigner components are strictly positive, and so the pre-order $\prec_{\sigma}$ is well-defined.
+States that are not full-rank can be addressed as a limiting case of the above.
+
+The Strange state rescaled distribution for a magic state $\rho_S(\epsilon)$ is now given by 
+\begin{equation}
+	\widetilde{\rm{W}}_{\rho_{\rm{S}}|\sigma}(\bmx) = \frac{\W[\bmx]{\rho_{\rm{S}}}}{\W[\bmx]{\sigma}},
+\end{equation}
+which attains four distinct values on the phase space, naturally splitting it into four regions as illustrated in the~\cref{fig:pd_split}.
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.45]{figs/pd_split_thermal.pdf}
+    \caption{\textbf{Qutrit phase space regions for $W_{\rho_{\rm{S}} | \sigma}(\x)$.}
+    Here, the negative component of the magic state overlaps the Wigner distribution of $|0\>$.
+The rescaled distribution attains a single value in each of the four regions, proportional to the value depicted in the region, see~\cref{eq:bmw_rescaled}.
+    }
+    \label{fig:pd_split}
+\end{figure}
+
+The component values and multiplicities of the relevant distributions in the four distinct regions are summarised by the following component and multiplicity vectors,
+\begin{align}
+	\bmw(\rho_{\rm{S}}) &\coloneqq (-v, u, u, u), \\
+		\bmm &\coloneqq (1,2,3,3), \\
+	\bmw(\sigma) &\coloneqq \frac{1}{3\Z} \left( e^{-\beta E_0}, e^{-\beta E_0}, e^{-\beta E_1}, e^{-\beta E_2} \right), \\
+	\bmw(\rho_{\rm{S}} | \sigma) &\coloneqq 3\Z \left( -v e^{\beta E_0}, u e^{\beta E_0}, u e^{\beta E_1}, u e^{\beta E_2} \right). \label{eq:bmw_rescaled}
+\end{align}
+
+Using this notation, the values and multiplicities of the $n$--copy distribution $\bmw(\rho^{\otimes n}_S |\sigma^{\otimes n})$ are computed in~\cref{lem:ncopycomponents} in~\cref{app:cmpairs}.
+The values are denoted by $w(\rho_{\rm{S}} | \sigma)_{ijk}$ with associated multiplicity $m_{ijk}$.
+The indices $i,j,k$ are non-negative integers and obey the constraint $\alpha \coloneqq i+j+k \leq n$.
+The $n$--copy multiplicity is given by
+\begin{equation}
+	m_{ijk} = \frac{n!}{i!j!k!(n-\alpha)!} 2^i 3^j 3^k,
+\end{equation}
+while the distribution values are given by
+\begin{align}\label{eq:ncopy_w_rescaled}
+	w(\rho_{\rm{S}} | \sigma)_{ijk} &= (3\Z)^{n} (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )},
+\end{align}
+where we have also computed the unscaled components
+\begin{align}
+	w(\rho_{\rm{S}})_{ijk} &= (-v)^{n-\alpha} u^{\alpha}, \label{eq:ncopy_wrho}\\
+	w(\sigma)_{ijk} &= (3\Z)^{-n} e^{-\beta (n-\alpha)E_s} e^{-\beta ( i E_0 + j E_1 + k E_2 )}. \label{eq:ncopy_wsigma}
+\end{align}
+
+In order to construct the $n$--copy Lorenz curve $\lc{\rho_{\rm{S}}^{\otimes n}}{\sigma^{\otimes n}}$ we need to order the components of the distribution, $w(\rho_{\rm{S}} | \sigma)_{ijk}$ in decreasing order.
+In particular, to find the coordinates of the first elbow $(x_0, L_0)$, we need to evaluate the maximum component,
+\begin{align}
+	&w(\rho_{\rm{S}} | \sigma)_{\rm{max}} \coloneqq (3\Z)^{n}\times \nonumber\\
+	&\max\limits_{i,j,k}\Big\{ (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \label{eq:max_slope}
+\end{align}
+where $0 \leq i,j,k \leq n$ and $\alpha \coloneqq i+j+k \leq n$.
+For $0 \leq \epsilon \leq 3/7$, we have $v \geq u$. Since we assume that $n$ is even, we need the sum $\alpha = i+j+k$ to be even too, so that the expression is positive.
+
+Given an even value for $\alpha$, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_s}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
+Hence, we have
+\begin{align}
+	&w(\rho_{\rm{S}} | \sigma)_{\rm{max}} = \nonumber\\
+	&(3\Z)^{n} v^n e^{n\beta E_s}\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_s)} \right)^{\alpha} \Big\}}.
+\end{align}
+If the expression $\frac{u(\epsilon)}{v(\epsilon)} e^{\beta (E_{\rm{max}} - E_s)}$ is less than $1$ then the maximum occurs at $\alpha=0$, otherwise it occurs at $\alpha = n$.
+For a fixed stabilizer state $\sigma$, this transition is determined by the value of the depolarising noise parameter $\epsilon$ of the noisy magic state.
+The transition occurs at $\epsilon = \epsilon_\star$ where
+\begin{equation}\label{eq:noise_transition}
+	\frac{u(\epsilon_\star)}{v(\epsilon_\star)} e^{\beta (E_{\rm{max}} - E_s)} = \frac{3-\epsilon_\star}{6-8\epsilon_\star} e^{\beta (E_{\rm{max}} - E_s)} = 1.
+\end{equation}
+If $E_{\rm{max}} = E_s$, namely if the state negativity lies in the same phase space region as the highest energy, this threshold is constant in temperature and given by $\epsilon_{\star} = 3/7$.
+However, the condition that $\epsilon_\star \ge 0$ also implies a constraint on the effective temperature of the stabilizer state.
+Specifically, there is a threshold temperature value $\beta_\star$ given by
+\begin{equation}
+	\beta_{\star} \coloneqq \frac{1}{E_{\rm{max}} - E_s} \ln2,
+\end{equation}
+such that for the regime $0 \leq \beta \leq \beta_\star$ a transition noise level $\epsilon_\star$ exists, and for $\beta > \beta_\star$ no such transition exists, so we choose $\epsilon_\star = 0$. 
+Therefore, the transition value for the noise is given by
+\begin{equation}
+	\epsilon_{\star}(\beta) \coloneqq 
+	\begin{cases}
+		3 - \dfrac{18}{8-2^{\beta/\beta_\star}}, &\text{ for } \beta \leq \beta_\star \\
+		0, &\text{ for } \beta > \beta_\star.
+	\end{cases}
+\end{equation}
+The quantity $w(\rho_{\rm{S}} | \sigma)_{\rm{max}}$ is now given by
+\begin{equation*}
+w(\rho_{\rm{S}} | \sigma)_{\rm{max}} =
+	\begin{cases}
+		(3\Z)^{n} v^n e^{n\beta E_s}, &\mbox{if }\epsilon \leq \epsilon_{\star},\ \hspace{3pt}\rm{(C1)}\\
+		(3\Z)^{n} u^n e^{n\beta E_{\rm{max}}}, &\mbox{if }\epsilon > \epsilon_{\star}.\ \hspace{5pt}\rm{(C2)} 
+	\end{cases}
+\end{equation*}
+Case $\rm{(C1)}$ corresponds to $(i,j,k) = (0,0,0)$, so the multiplicity is $m_{000} = 1$, while
+Case $\rm{(C2)}$ corresponds to
+\begin{equation}
+	(i,j,k) = 
+	\begin{cases}
+	(0,n,0), &\text{if } E_{\rm{max}} = E_1, \\
+	(0,0,n), &\text{if } E_{\rm{max}} = E_2,
+	\end{cases}
+\end{equation}
+so the multiplicity in both cases is $3^n$.
+
+Using that $F = -\beta^{-1} \log \Z$, the first elbow coordinates in the two cases are now given by
+\begin{equation}\label{eq:first_elb_coords}
+	(x_0, L_0) =
+	\begin{cases}
+		\left(\frac{1}{3^n} e^{-n\beta (E_s - F)}, v^n \right), &\epsilon \leq \epsilon_\star \vspace{10pt}\\
+		\left( e^{-n\beta (E_{\rm{max}}-F)}, (3u)^n \right). &\epsilon > \epsilon_\star
+	\end{cases}
+\end{equation}
+Similarly, considering the output magic state with respect to state $\sigma'$, the image of equilibrium state $\sigma$ under the magic protocol, we get output Lorenz curve coordinates,
+\begin{equation}\label{eq:transformed_first_elb_coords}
+	(x'_0, L'_0) =
+	\begin{cases}
+		\left(\frac{1}{3^{n'}} e^{-n\beta (E'_s - F')}, v(\epsilon')^{n'} \right), &\epsilon' \leq \epsilon'_\star \vspace{10pt}\\
+		\left( e^{-n'\beta (E'_{\rm{max}}\hspace{-2.5pt}-F')}, (3u(\epsilon'))^{n'} \right), &\epsilon' > \epsilon'_\star
+	\end{cases}
+\end{equation}
+There are four combinations of coordinates, depending on the noise parameters $\epsilon, \epsilon'$ for the input and output states.
+In each of these combinations, we simply use the first elbow constraint, as described in~\cref{app:elb_constraints}, which leads to the bounds in the statement of the theorem.
 %\begin{enumerate}
-%\item As a family of upper bounds parameterised by an abstract stabiliser state $\sigma$.
-%\item As a constraint arising from the actual hardware limitations, noise bias or ambient thermal environment and reflected by the invariant state $\sigma$ for the system.
+%	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} = E_s$ or $E_{\rm{max}} > E_s$, $\beta < \beta_{\star}$ and $\epsilon' < \epsilon  \leq \epsilon_{\star}$.
+%	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} > E_s$, $\beta < \beta_{\star}$ and $\epsilon' \leq \epsilon_{\star} < \epsilon$.
+%	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $E_{\rm{max}} > E_s$, $\beta < \beta_{\star}$ and $\epsilon_{\star} \leq \epsilon' < \epsilon$ or $E_{\rm{max}} > E_s$, $\beta \geq \beta_{\star}$.
 %\end{enumerate}
-%In what follows we shall be agnostic on the interpretation.
-
-Without loss of generality, we can always write a full-rank stabiliser state $\sigma$ in the form $\sigma =  \frac{1}{\Z_\beta} e^{-\beta H}$ for some $\beta \geq 0$ and effective Hamiltonian $H$.
-Our results will also depend on the free energy $F$ of the state $\sigma$, expressed as
-\begin{equation}
-	F \coloneqq \tr[H \sigma] - \beta^{-1}S(\sigma) = -\beta^{-1}\log{\Z_\beta}.
-\end{equation}
-Here $S(\sigma)$ is the von Neumann entropy $S(\sigma) \coloneqq -\tr[\sigma\log{\sigma}]$.
-\nick{Note that under interpretation (1) above, this is an abstract entropic measure of the stabilizer state, while, under interpretation (2), it corresponds to the actual thermodynamic free energy of the equilibrium state.}
-%
-%We focus on the distillation process
-%\begin{equation}\label{eq:stdist}
-%	\rho_{\rm{S}}(\epsilon)^{\otimes n} \longrightarrow \rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \sigma^{\otimes (n-n')},
-%\end{equation}
-%where, as before, tensoring in copies of $\sigma$ does not affect the Lorenz curves of the magic states in the fragment.
-
-Given this context, we now provide the following result on bounding the distillation rate $R = R(\epsilon, \epsilon', \beta) \coloneqq \frac{n'}{n}$ of the process in\nick{~\cref{eq:stdist}}.
-We shall write $R(\epsilon, \beta) = R(\epsilon, \epsilon'=0, \beta)$ for the limiting case of distilling a pure magic state.
+%The scenario $\rm{(C1)} \rightarrow \rm{(C2)}$ is not considered as it would correspond to $\epsilon \leq \epsilon_\star < \epsilon'$, which would imply that the output magic state is noisier than the input state.
+%Substituting $\epsilon' = 0$ into these expressions leads to the stated distillation bounds.
+
+\end{proof}
+
+We find numerically that the bounds derived above from the ascending part of the curve generally perform better than when considering the region around the Lorenz curve peak.
+Similar bounds can be obtained from the decreasing part of the Lorenz curve, but they do not shed any more light on distillation.
+Numerically ranging through the entire curve will improve our bounds incrementally, to an extent that depends on the intricate Lorenz curve structure.
+
+\subsection{Distillation bounds and energy dependencies}
+The previous section was focussed on an individual fragment, and while this does shed light on how physical constraints may, or may not, constrain protocols it is a bit indirect.
+However it is possible to adapt these bounds and put them in a more natural light.
+
+For this, we now drop the condition that $\sigma$ is left invariant under the distillation protocol, and assume it transforms to some $\sigma'$.
+This output state must be some other stabilizer state and so has a positive Wigner function also.
+The strategy is then to use how any protocol transforms $\sigma$ to act as a measure of physical features, such as energy, of the protocol.
+Therefore, we are interested in the conditions under which $(\rho, \sigma) \rightarrow (\rho', \sigma')$.
+For this we can use the full definition of relative majorization on the associated Wigner functions, and obtain distillation bounds from
+\begin{equation}
+(W_\rho(\x), W_\sigma(\x) ) \succ (W_{\rho'}(\x), W_{\sigma'}(\x) ).
+\end{equation}
+The condition for this is $L_{\rho |\sigma } (x) \ge L_{\rho'|\sigma'} (x)$, and so exactly the same analysis applies as in the previous case, but now with the Gibbs-recaling parameters for the output state being different from the ones for the input state~\cite{Renes_2016}.
+
+If the physical system has Hamiltonian $H$, and can be experimentally cooled down to some reference temperature $T$ then we can consider the reference equilibrium state $\sigma = e^{-\beta H}/\Z$, and estimate the energetic and entropic costs of any distillation protocol in terms of how the protocol transforms $\sigma$ to some other equilibrium state $\sigma'$.
+For example, if $\sigma'$ is close to the ground state \nick{fun fact: ground states correspond to $\beta \rightarrow \infty$ which makes both Lorenz curves look very rectangular - should we include this as an insight?} of the system, we then know that a great deal of entropy is dumped by the process.
+This allows us to parameterise our distillation bounds in a more insightful way.
 
@@
 \end{figure}
-%
-%\begin{theorem}\label{thm:stab_bounds}
-%	Given a theory of magic $\R = (\F, \O)$, let $\sigma$ be any qutrit stabiliser state, and write the state as $\sigma = \frac{1}{\Z} e^{-\beta H}$, where $H$ has eigenvalues $E_0, E_1, E_2$, and $\beta$ is an effective inverse temperature for the state.
-%We define $\beta_\star = 1/kT_\star$ through the relation
-%\begin{equation}
-%	E_{\rm max} - E_s \eqqcolon kT_\star \ln 2,
-%\end{equation}
-%where $E_{\rm max} = \max\{E_0, E_1, E_2\}$ and $E_s$ is the eigenvalue of the eigenstate that overlaps the negative component of $\rho_S(\epsilon)$ in the Wigner representation.
-For $\beta \leq \beta_\star$, we define a threshold noise level
-%\begin{equation}
-%	\epsilon_{\star}(\beta) \coloneqq 3 - \dfrac{18}{8-e^{(E_{\rm max} - E_s)\beta}}.
-%\end{equation}
-%Then, any distillation rate $R(\epsilon, \beta)$ in the $\sigma$--fragment of a magic theory is bounded as follows:\\
-%If $\beta \leq \beta_{\star}$ and $\epsilon  \leq \epsilon_{\star}$,
-%\begin{equation}
-%	R(\epsilon,\beta) \leq 1 + \frac{\ln{\left( 1 - \frac{4}{3}\epsilon \right)}}{\beta (E_s - F)}.
-%\end{equation}
-%If $\beta \leq \beta_{\star}$ and $\epsilon_{\star} < \epsilon$, then
-%\begin{equation}
-%	R(\epsilon, \beta) \le 1 + \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)} - (E_{\rm max} - E_s)(\beta_{\star} - \beta)}{\beta (E_s - F)}.
-%\end{equation}
-%Otherwise if $\beta > \beta_{\star}$,
-%\begin{equation}
-%	R(\epsilon, \beta) \leq  1+ \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)}}{-\ln{2} + \beta (E_{\rm max} - F)}.
-%\end{equation}
-%In the above expressions $F$ is the effective free energy of the stabilizer state.
-%\end{theorem}
-
-\ddd{[Put assumptions here. Needs more polish+checking.]} We now consider a magic distillation protocol on multiple identical qutrits sending 
-\begin{equation}
-\rho_S(\epsilon)^{\otimes n} \longrightarrow \rho_S(\epsilon')^{\otimes Rn}
-\end{equation}
-with $n \rightarrow \infty$. Let each qutrit have a Hamiltonian $H$ with energies $E_0, E_1, E_2$. Let $T =(k\beta)^{-1}$ be any characteristic temperature for the physical system. 
-We define $\beta_\star = 1/kT_\star$ through the relation
-\begin{equation}
-	E_{\rm max} - E_s \eqqcolon kT_\star \ln 2,
-\end{equation}
-where $E_{\rm max} = \max\{E_0, E_1, E_2\}$ and $E_s$ is the eigenvalue of the eigenstate that overlaps the negative component of $\rho_S(\epsilon)$ in the Wigner representation.
-We define a threshold noise level,
-\begin{equation}
-	\epsilon_{\star}(\beta) \coloneqq 
-	\begin{cases}
-		3 - \dfrac{18}{8-2^{\beta/\beta_\star}}, &\text{ for } \beta \leq \beta_\star \\
-		0, &\text{ for } \beta > \beta_\star.
-	\end{cases}
-\end{equation}
-
-We can now provide distillation bounds that depend on energetic and entropic aspects of the protocol.
-However, this is done relative to a reference temperature that can be chosen freely.
-The measures associated with this protocol are then determined by how it would disturb this reference equilibrium state $\sigma$ to some different state $\sigma'$.
-More precisely, the reference equilibrium state of the $n$ qutrits is given by
-\begin{equation}
-\sigma^{\otimes n} = \left ( \frac{e^{-\beta H}}{\Z} \right )  ^{\otimes n}.
-\end{equation}
-Since we are concerned with magic distillation we may assume that the reference state $\sigma$ is not a magic state, and so has non-negative Wigner distribution.
-Instead we shall assume that it is a full-rank stabilizer state for the qutrit.
-A given magic protocol on the $n$ qutrits will correspond to a quantum channel $\E$ acting on $\rho_S(\epsilon)^{\otimes n}$.
-Our analysis associates to this protocol energy/entropy measures by considering how $\E$ transforms this reference equilibrium state.
-For simplicity we assume that the action of $\E$ on $\sigma^{\otimes n}$ is also such that correlations can be neglected in the $n\rightarrow \infty$ limit, and so $\E(\sigma^{\otimes n}) = (\sigma')^{\otimes n}$ for some state $\sigma'$.
-This assumption simplifies the application of majorization, however we note that work has also been done on the case of where correlations build up and one only looks at the marginal state on an individual subsystem \ddd{[need to cite here]} and so a more detailed analysis can also be performed.
-
-Finally, we can paramterise the state $\sigma'$ by defining a fiducial Hamiltonian $H'$, so that $\sigma' = e^{-\beta H'} / \Z$, while we denote all quantities relevant to this output state $\sigma'$ by priming them, leading to $E'_{\rm{max}}, E'_s, \beta'_\star$ and $\epsilon'_\star$.
-
-\begin{theorem}\label{thm:free-energy}
-	Consider a magic distillation protocol on $n \gg 1$ identical qutrits under the assumptions just stated.
-
-Then the distillation rate $R$ of the protocol is bounded as follows:
-\begin{equation}\label{eq:rate_bounds_proof}
-	R \leq
-	\begin{cases}
-		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F')},\ &\epsilon \leq \epsilon_\star, \epsilon' \leq \epsilon'_\star, \vspace{10pt}\\
-		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F')},\ &\epsilon \leq \epsilon_\star, \epsilon' > \epsilon'_\star, \vspace{10pt}\\
-		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F')},\ &\epsilon > \epsilon_\star, \epsilon' \leq \epsilon'_\star, \vspace{10pt}\\
-		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F')},\ &\epsilon > \epsilon_\star, \epsilon' > \epsilon'_\star.
-	\end{cases}
-\end{equation}
-In the above expressions $F$ is the free energy of the state $\sigma \coloneqq e^{-\beta H}/\Z$ and $F'$ is the free energy of the single qutrit state $\sigma' = e^{-\beta H'}/\Z'$ defined via the action of the protocol on the reference equilibrium state.
-\ddd{[Need strategy to incorporate conditions in simple, clear way.]}
-\end{theorem}
- The state $\sigma'$ is generally a non-equilibrium state for the system, however one can still associate a free energy value to the output by considering subsequently changing the Hamiltonian $H \rightarrow H'$ such that equilibrium is restored at the reference temperature $T$.
-For example, suppose that $H=H'$ then this implies the protocol would leave the equilibrium state unchanged and so corresponds to a Gibbs-preserving map \ddd{[cite Philippe]}.
-In the more general case $\Delta F := F' - F \ne 0$ and we have a free energy difference between the initial and final times, with respect to the relevant Hamiltonians.
-This is similar to the free energy differences that occur in fluctuation relations, where the final state of the system can be arbitrarily far from equilibrium, yet a free energy term for the final system still arises.
-
-Firstly, the specific numerical factors in $\epsilon_\star$ are a result of our choice of magic state. 
-Secondly, these bounds are derived based on analysis of only a part of the Lorenz curves and can be improved via a finer analysis. 
-This is apparent by simple numerical calculations on the entirety of the curves.
-Specifically, the existing bounds follow by considering the dominant terms in the rescaled Wigner distribution and do not, for example, take into account the Lorenz curve's peak structure.
-
-\begin{proof}
-	We provide the full proof here, with some technical details pushed to~\cref{app:lcst_technical}.\\
-
-Let $\displaystyle \sigma = e^{-\beta H} / \Z_\beta$ be a stabiliser state, where $\beta \geq 0$ and $H = E_0 \ketbra{\varphi_0} + E_1 \ketbra{\varphi_1} + E_2 \ketbra{\varphi_2}$ is an eigendecomposition of $H$.
-The stabilizer state $\sigma$ can now be written as 
-\begin{equation}
-	\sigma = \frac{e^{-\beta E_0}}{\Z_\beta} \ketbra{\varphi_0} + \frac{e^{-\beta E_1}}{\Z_\beta} \ketbra{\varphi_1} + \frac{e^{-\beta E_2}}{\Z_\beta} \ketbra{\varphi_2},
-\end{equation}
-where $\{\ket{\varphi_k}\<\varphi_k|\}$ are pure, orthonormal stabiliser states, which can be represented in terms of generalized Paulis.
-To make our analysis simpler we perform a change of basis that does not affect the Wigner negativity of the problem.
-We let $C$ be the unitary transforming each $|\varphi_k\>\<\varphi_k|$ to $|k\>\<k|$.
-Since the Clifford group is the normalizer of the Heisenberg-Weyl group, $C$ is a Clifford unitary.
-Therefore, $C$ maps $\sigma$ to another stabilizer state that is diagonal in the computational basis, and we can assume without loss of generality that $\sigma$ is diagonal in $\{|0\>,|1\>, |2\>\}$.
-However, this choice means that the location of the negative Wigner component $-v(\epsilon)$ of the Strange state will be permuted on the discrete phase space.
-We denote by $E_s$ the eigenvalue of $H$ where the associated eigenvector has Wigner distribution overlapping the negative component of the magic state $C\rho_S(\epsilon)C^\dagger$.
-This is unique, since the eigenstates form an orthonormal basis.
-
-The Wigner distribution of state $\sigma$ is then given by
-\begin{align}
-	\W[\bmx]{\sigma} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z_\beta}W_{\ketbra{k}}(x, p) \nonumber\\
-	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z_\beta} \delta_{x, k} = \frac{e^{-\beta E_x}}{3\Z_\beta},
-\end{align}
-where $x$ labels one of the three vertical lines in the phase space.
-Since we have restricted to full-rank states, all Wigner components are strictly positive, and so the pre-order $\prec_{\sigma}$ is well-defined.
-States that are not full-rank can be addressed as a limiting case of the above.
-
-The Strange state rescaled distribution for a magic state $\rho_S(\epsilon)$ is now given by 
-\begin{equation}
-	\widetilde{\rm{W}}_{\rho_{\rm{S}}|\sigma}(\bmx) = \frac{\W[\bmx]{\rho_{\rm{S}}}}{\W[\bmx]{\sigma}},
-\end{equation}
-which attains four distinct values on the phase space, naturally splitting it into four regions as illustrated in the~\cref{fig:pd_split}.
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.45]{figs/pd_split_thermal.pdf}
-    \caption{\textbf{Qutrit phase space regions for $W_{\rho_{\rm{S}} | \sigma}(\x)$.}
-    Here, the negative component of the magic state overlaps the Wigner distribution of $|0\>$.
-The rescaled distribution attains a single value in each of the four regions, proportional to the value depicted in the region, see~\cref{eq:bmw_rescaled}.
-    }
-    \label{fig:pd_split}
-\end{figure}
-
-The component values and multiplicities of the relevant distributions in the four distinct regions are summarised by the following component and multiplicity vectors,
-\begin{align}
-	\bmw(\rho_{\rm{S}}) &\coloneqq (-v, u, u, u), \\
-		\bmm &\coloneqq (1,2,3,3), \\
-	\bmw(\sigma) &\coloneqq \frac{1}{3\Z} \left( e^{-\beta E_0}, e^{-\beta E_0}, e^{-\beta E_1}, e^{-\beta E_2} \right), \\
-	\bmw(\rho_{\rm{S}} | \sigma) &\coloneqq 3\Z \left( -v e^{\beta E_0}, u e^{\beta E_0}, u e^{\beta E_1}, u e^{\beta E_2} \right). \label{eq:bmw_rescaled}
-\end{align}
-
-Using this notation, the values and multiplicities of the $n$--copy distribution $\bmw(\rho^{\otimes n}_S |\sigma^{\otimes n})$ are computed in~\cref{lem:ncopycomponents} in~\cref{app:cmpairs}.
-The values are denoted by $w(\rho_{\rm{S}} | \sigma)_{ijk}$ with associated multiplicity $m_{ijk}$.
-The indices $i,j,k$ are non-negative integers and obey the constraint $\alpha \coloneqq i+j+k \leq n$.
-The $n$--copy multiplicity is given by
-\begin{equation}
-	m_{ijk} = \frac{n!}{i!j!k!(n-\alpha)!} 2^i 3^j 3^k,
-\end{equation}
-while the distribution values are given by
-\begin{align}\label{eq:ncopy_w_rescaled}
-	w(\rho_{\rm{S}} | \sigma)_{ijk} &= (3\Z)^{n} (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )},
-\end{align}
-where we have also computed the unscaled components
-\begin{align}
-	w(\rho_{\rm{S}})_{ijk} &= (-v)^{n-\alpha} u^{\alpha}, \label{eq:ncopy_wrho}\\
-	w(\sigma)_{ijk} &= (3\Z)^{-n} e^{-\beta (n-\alpha)E_s} e^{-\beta ( i E_0 + j E_1 + k E_2 )}. \label{eq:ncopy_wsigma}
-\end{align}
-
-In order to construct the $n$--copy Lorenz curve $\lc{\rho_{\rm{S}}^{\otimes n}}{\sigma^{\otimes n}}$ we need to order the components of the distribution, $w(\rho_{\rm{S}} | \sigma)_{ijk}$ in decreasing order.
-In particular, to find the coordinates of the first elbow $(x_0, L_0)$, we need to evaluate the maximum component,
-\begin{align}
-	&w(\rho_{\rm{S}} | \sigma)_{\rm{max}} \coloneqq (3\Z)^{n}\times \nonumber\\
-	&\max\limits_{i,j,k}\Big\{ (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \label{eq:max_slope}
-\end{align}
-where $0 \leq i,j,k \leq n$ and $\alpha \coloneqq i+j+k \leq n$.
-For $0 \leq \epsilon \leq 3/7$, we have $v \geq u$. Since we assume that $n$ is even, we need the sum $\alpha = i+j+k$ to be even too, so that the expression is positive.
-
-Given an even value for $\alpha$, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_s}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
-Hence, we have
-\begin{align}
-	&w(\rho_{\rm{S}} | \sigma)_{\rm{max}} = \nonumber\\
-	&(3\Z)^{n} v^n e^{n\beta E_s}\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_s)} \right)^{\alpha} \Big\}}.
-\end{align}
-If the expression $\frac{u(\epsilon)}{v(\epsilon)} e^{\beta (E_{\rm{max}} - E_s)}$ is less than $1$ then the maximum occurs at $\alpha=0$, otherwise it occurs at $\alpha = n$.
-For a fixed stabilizer state $\sigma$, this transition is determined by the value of the depolarising noise parameter $\epsilon$ of the noisy magic state.
-The transition occurs at $\epsilon = \epsilon_\star$ where
-\begin{equation}\label{eq:noise_transition}
-	\frac{u(\epsilon_\star)}{v(\epsilon_\star)} e^{\beta (E_{\rm{max}} - E_s)} = \frac{3-\epsilon_\star}{6-8\epsilon_\star} e^{\beta (E_{\rm{max}} - E_s)} = 1.
-\end{equation}
-If $E_{\rm{max}} = E_s$, namely if the state negativity lies in the same phase space region as the highest energy, this threshold is constant in temperature and given by $\epsilon_{\star} = 3/7$.
-However, the condition that $\epsilon_\star \ge 0$ also implies a constraint on the effective temperature of the stabilizer state.
-Specifically, there is a threshold temperature value $\beta_\star$ given by
-\begin{equation}
-	\beta_{\star} \coloneqq \frac{1}{E_{\rm{max}} - E_s} \ln2,
-\end{equation}
-such that for the regime $0 \leq \beta \leq \beta_\star$ a transition noise level $\epsilon_\star$ exists, and for $\beta > \beta_\star$ no such transition exists, so we choose $\epsilon_\star = 0$. 
-Therefore, the transition value for the noise is given by
-\begin{equation}
-	\epsilon_{\star}(\beta) \coloneqq 
-	\begin{cases}
-		3 - \dfrac{18}{8-2^{\beta/\beta_\star}}, &\text{ for } \beta \leq \beta_\star \\
-		0, &\text{ for } \beta > \beta_\star.
-	\end{cases}
-\end{equation}
-The quantity $w(\rho_{\rm{S}} | \sigma)_{\rm{max}}$ is now given by
-\begin{equation*}
-w(\rho_{\rm{S}} | \sigma)_{\rm{max}} =
-	\begin{cases}
-		(3\Z)^{n} v^n e^{n\beta E_s}, &\mbox{if }\epsilon \leq \epsilon_{\star},\ \hspace{3pt}\rm{(C1)}\\
-		(3\Z)^{n} u^n e^{n\beta E_{\rm{max}}}, &\mbox{if }\epsilon > \epsilon_{\star}.\ \hspace{5pt}\rm{(C2)} 
-	\end{cases}
-\end{equation*}
-Case $\rm{(C1)}$ corresponds to $(i,j,k) = (0,0,0)$, so the multiplicity is $m_{000} = 1$, while
-Case $\rm{(C2)}$ corresponds to
-\begin{equation}
-	(i,j,k) = 
-	\begin{cases}
-	(0,n,0), &\text{if } E_{\rm{max}} = E_1, \\
-	(0,0,n), &\text{if } E_{\rm{max}} = E_2,
-	\end{cases}
-\end{equation}
-so the multiplicity in both cases is $3^n$.
-
-Using that $F = -\beta^{-1} \log \Z$, the first elbow coordinates in the two cases are now given by
-\begin{equation}\label{eq:first_elb_coords}
-	(x_0, L_0) =
-	\begin{cases}
-		\left(\frac{1}{3^n} e^{-n\beta (E_s - F)}, v^n \right), &\epsilon \leq \epsilon_\star \vspace{10pt}\\
-		\left( e^{-n\beta (E_{\rm{max}}-F)}, (3u)^n \right). &\epsilon > \epsilon_\star
-	\end{cases}
-\end{equation}
-Similarly, considering the output magic state with respect to state $\sigma'$, the image of equilibrium state $\sigma$ under the magic protocol, we get output Lorenz curve coordinates,
-\begin{equation}\label{eq:transformed_first_elb_coords}
-	(x'_0, L'_0) =
-	\begin{cases}
-		\left(\frac{1}{3^{n'}} e^{-n\beta (E'_s - F')}, v(\epsilon')^{n'} \right), &\epsilon' \leq \epsilon'_\star \vspace{10pt}\\
-		\left( e^{-n'\beta (E'_{\rm{max}}\hspace{-2.5pt}-F')}, (3u(\epsilon'))^{n'} \right), &\epsilon' > \epsilon'_\star
-	\end{cases}
-\end{equation}
-There are four combinations of coordinates, depending on the noise parameters $\epsilon, \epsilon'$ for the input and output states.
-In each of these combinations, we simply use the first elbow constraint, as described in~\cref{app:elb_constraints}, which leads to the bounds in the statement of the theorem.
-%\begin{enumerate}
-%	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} = E_s$ or $E_{\rm{max}} > E_s$, $\beta < \beta_{\star}$ and $\epsilon' < \epsilon  \leq \epsilon_{\star}$.
-%	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} > E_s$, $\beta < \beta_{\star}$ and $\epsilon' \leq \epsilon_{\star} < \epsilon$.
-%	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $E_{\rm{max}} > E_s$, $\beta < \beta_{\star}$ and $\epsilon_{\star} \leq \epsilon' < \epsilon$ or $E_{\rm{max}} > E_s$, $\beta \geq \beta_{\star}$.
-%\end{enumerate}
-%The scenario $\rm{(C1)} \rightarrow \rm{(C2)}$ is not considered as it would correspond to $\epsilon \leq \epsilon_\star < \epsilon'$, which would imply that the output magic state is noisier than the input state.
-%Substituting $\epsilon' = 0$ into these expressions leads to the stated distillation bounds.
-
-\end{proof}
-
-We find numerically that the bounds derived above from the ascending part of the curve generally perform better than when considering the region around the Lorenz curve peak.
-Similar bounds can be obtained from the decreasing part of the Lorenz curve, but they do not shed any more light on distillation.
-Numerically ranging through the entire curve will improve our bounds incrementally, to an extent that depends on the intricate Lorenz curve structure.
-
-\subsection{Distillation bounds and energy dependencies}
-The previous section was focussed on an individual fragment, and while this does shed light on how physical constraints may, or may not, constrain protocols it is a bit indirect.
-However it is possible to adapt these bounds and put them in a more natural light.
-
-For this, we now drop the condition that $\sigma$ is left invariant under the distillation protocol, and assume it transforms to some $\sigma'$.
-This output state must be some other stabilizer state and so has a positive Wigner function also.
-The strategy is then to use how any protocol transforms $\sigma$ to act as a measure of physical features, such as energy, of the protocol.
-Therefore, we are interested in the conditions under which $(\rho, \sigma) \rightarrow (\rho', \sigma')$.
-For this we can use the full definition of relative majorization on the associated Wigner functions, and obtain distillation bounds from
-\begin{equation}
-(W_\rho(\x), W_\sigma(\x) ) \succ (W_{\rho'}(\x), W_{\sigma'}(\x) ).
-\end{equation}
-The condition for this is $L_{\rho |\sigma } (x) \ge L_{\rho'|\sigma'} (x)$, and so exactly the same analysis applies as in the previous case, but now with the Gibbs-recaling parameters for the output state being different from the ones for the input state~\cite{Renes_2016}.
-
-If the physical system has Hamiltonian $H$, and can be experimentally cooled down to some reference temperature $T$ then we can consider the reference equilibrium state $\sigma = e^{-\beta H}/\Z$, and estimate the energetic and entropic costs of any distillation protocol in terms of how the protocol transforms $\sigma$ to some other equilibrium state $\sigma'$.
-For example, if $\sigma'$ is close to the ground state \nick{fun fact: ground states correspond to $\beta \rightarrow \infty$ which makes both Lorenz curves look very rectangular - should we include this as an insight?} of the system, we then know that a great deal of entropy is dumped by the process.
-This allows us to parameterise our distillation bounds in a more insightful way.
 

### 2021-04-20 appendix.tex
Restructuring of material. Bit on fragments compressed more. Some proofs pushed to appendices.

@@
 
+\subsection{Comments on monotones and fragements}
+The development of any monotone $\M(\rho)$ for a magic theory $\R$ can be viewed abstractly as
+\begin{equation}
+\M : \mbox{(pre-order of states)} \mapsto \mbox{(total order of numbers).} \nonumber
+\end{equation}
+More precisely, within the theory we order magic states as $\rho_1 \succ \rho_2$ whenever there is an operation $\E \in \O$ such that $\E(\rho_1) = \rho_2$.
+In general many states will not be interconvertible in both directions, so this ordering is a pre-order in the sense that incomparable states exist.
+A magic monotone projects this pre-order of states onto the real number line, and, through this lens, any two states are directly comparable in terms of their mapped values $\M(\rho_1)$, $\M(\rho_2)$.
+Of course, the price is that the monotone provides only a necessary, but not sufficient, condition for the transformation $\rho_1 \rightarrow \rho_2$.
+
+The restriction of a magic theory $\R$ to some fragment $\R_\sigma$ can now be interpreted as a generalisation of the magic monotone construction: instead of mapping the pre-order of states in $\R$ onto the number line, we instead map this pre-order onto \emph{a simpler pre-order of states}.
+Therefore, we are retaining more of the original parent theory, while working in a scenario that admits greater structure and simplicity.
+We can view this as a mapping $\P_\sigma: \R \rightarrow \R_\sigma$ that restricts to a sub-theory (a $\sigma$--fragment) of the parent theory $\R$.
+Thus,
+\begin{equation}
+\P_\sigma: \mbox{(pre-order)} \longrightarrow \mbox{(simpler pre-order).}
+\end{equation}
+By framing the projection onto a fragment in this light, we can view Theorem \ref{thm:frag} as a statement that the collection $\{\P_\sigma\}_{\sigma \in \F}$ provides a complete set of generalized monotones for the theory.
 \subsection{Simple--majorization equivalence conditions}
@@
 \end{proof}
+
+\begin{lemma}\label{lem:lcmax}
+	Given a magic state $\rho$, the maximum $L_\star$ of its Lorenz curve $\lc{\rho}{\sigma}(x)$ is independent of the $\sigma$--fragment and equal to $1+\sn{\rho}$.
+Moreover, the majorization constraint is stronger than mana in every fragment.
+\end{lemma}
+\begin{proof}
+	We denote the Wigner distributions of the states compactly as vectors $\bmw(\rho) \equiv W_\rho(x)$ and $\bmw(\sigma) \equiv W_\sigma(x)$.
+	We choose the component indexing so that the rescaled distribution 
+	\begin{equation}
+		\widetilde{\bmw}(\rho|\sigma) \coloneqq \left(\frac{w(\rho)_1}{w(\sigma)_1}, \dots, \frac{w(\rho)_{d^2}}{w(\sigma)_{d^2}} \right)^T,
+	\end{equation}
+	is sorted, $\widetilde{\bmw} = \widetilde{\bmw}^\downarrow$.
+	Note that all components of $\bmw(\sigma)$ are positive, so $\widetilde{w}_i \geq 0$ if and only if $w(\rho)_i \geq 0$ for any $i=1,\dots,d^2$.
+
+	Let $i_\star$ be the index of the smallest non-negative component of $\widetilde{\bmw}^\downarrow$.
+	Then, $w(\rho)_i < 0$ if and only if $i > i_\star$, so the maximum of Lorenz curve $\lc{\rho}{\sigma}(x)$ takes the value 
+	\begin{equation}
+		\lc{\rho}{\sigma}(x_{i_\star}) = \sum_{i=1}^{i_\star} w(\rho)_i,
+	\end{equation}
+	and is achieved at
+	\begin{equation}\label{eq:maxloc}
+		x_{i_\star} \coloneqq \sum_{i=1}^{i_\star} w(\sigma)_i.
+	\end{equation}
+
+	The location of the maximum ($x=x_{i_\star}$) varies from fragment to fragment, but its value is independent of $\sigma$,
+	\begin{align}
+	L_\star &:=	\lc{\rho}{\sigma}(x_{i_\star}) 
+		= \sum\limits_{\bmx: \W[\bmx]{\rho} \geq 0} \W[\bmx]{\rho} \nonumber \\
+		&= 1 + \sn{\rho}.
+	\end{align}
+
+Since the magic monotone mana is a monotonic function of sum-negativity, $\rm{mana}(\rho) \coloneqq \ln{(2\hspace{1pt}\sn{\rho}+1)}$, we see that mana corresponds precisely to the peak of the Lorenz curve $L_{\rho|\sigma}(x)$.
+Therefore, mana is one of $d^{2n}$ constraints, so majorization is strictly a stronger constraint in any fragment.
+\end{proof}
+
 \subsection{Embedding map}

### 2021-04-20 magic_paper.tex
Restructuring of material. Bit on fragments compressed more. Some proofs pushed to appendices.

@@
 
-\subsection{Stochastic structure of magic theories}
+\subsection{Stochastic structure of magic protocols}
 \label{sec:struc}
@@
 
-\section{Breaking a magic theory into fragments}
+\section{Magic distillation bounds from majorization theory}
 \label{sec:frag}
@@
 We can now show that each magic fragment admits constraints that do not take the form of state monotones.
-The development of any monotone $\M(\rho)$ for a magic theory $\R$ can be viewed abstractly as
-\begin{equation}
-\M : \mbox{(pre-order of states)} \mapsto \mbox{(total order of numbers).} \nonumber
-\end{equation}
-More precisely, within the theory we order magic states as $\rho_1 \succ \rho_2$ whenever there is an operation $\E \in \O$ such that $\E(\rho_1) = \rho_2$.
-In general many states will not be interconvertible in both directions, so this ordering is a pre-order in the sense that incomparable states exist.
-A magic monotone projects this pre-order of states onto the real number line, and, through this lens, any two states are directly comparable in terms of their mapped values $\M(\rho_1)$, $\M(\rho_2)$.
-Of course, the price is that the monotone provides only a necessary, but not sufficient, condition for the transformation $\rho_1 \rightarrow \rho_2$.
-
-The restriction of a magic theory $\R$ to some fragment $\R_\sigma$ can now be interpreted as a generalisation of the magic monotone construction: instead of mapping the pre-order of states in $\R$ onto the number line, we instead map this pre-order onto \emph{a simpler pre-order of states}.
-Therefore, we are retaining more of the original parent theory, while working in a scenario that admits greater structure and simplicity.
-We can view this as a mapping $\P_\sigma: \R \rightarrow \R_\sigma$ that restricts to a sub-theory (a $\sigma$--fragment) of the parent theory $\R$.
-Thus,
-\begin{equation}
-\P_\sigma: \mbox{(pre-order)} \longrightarrow \mbox{(simpler pre-order).}
-\end{equation}
-By framing the projection onto a fragment in this light, we can view Theorem \ref{thm:frag} as a statement that the collection $\{\P_\sigma\}_{\sigma \in \F}$ provides a complete set of generalized monotones for the theory.
 
@@
 
-There is a natural generalisation, which is called $\bmd$--majorization~\cite{Veinott_1971}, or in the context of thermodynamics, thermo-majorization.
+There is a natural generalisation, which is called $\bmd$--majorization~\cite{Veinott_1971}, or in the context of thermodynamics, thermo-majorization \ddd{[cite]}.
 For a fixed probability distribution $\r = (r_1, \dots, r_n)$ with positive components, we define majorization relative to $\r$ as $\p \succ_{\r} \q$, if and only if there exists a stochastic map $A$ such that $A\r = \r$ and $A \p = \q$.
@@
 
-We can further loosen the condition that vector $\r$ is kept fixed to get \emph{relative majorization}, defined as an ordering between pairs of vectors so that 
+We can further generalise this to \emph{relative majorization}\ddd{[cite]}, defined as an ordering between pairs of vectors so that 
 \begin{equation}
@@
 It turns out that relative majorization is equally applicable to \emph{quasi-probability} distributions, and therefore can be applied to the Wigner representation of magic across fragments.
-We justify the applicability and power of relative majorization in the next section.
-
-At this point we note that, to our knowledge, this application of majorization to quasi-distributions in  physics has not been considered previously.
-The caveat here is that relative majorization ranges over stochastic maps that obey a fixed transformation ($A\r = \r'$), while in the case of the Wigner representation there is a stronger restriction that the symplectic structure of the phase space is respected.
-Therefore, any majorization constraint can provide necessary, but not sufficient conditions on magic state interconversions.
-This observation raises a question that to our knowledge has not been previously considered in the classical statistical mechanics literature: what are the conditions for symplectic majorization of classical statistical mechanics?
-We shall \nick{return} to this question later on when we discuss how our approach could be used to construct concrete lower-bounds on distillation rates in~\cref{sec:lower_bounds}.
+We go into more detail on this in the next section.
 
@@
 
-\ddd{[Notation needs smoothing to accommodate new points of emphasis]}
-We now turn to the application of majorization to describing magic in different fragments.
-The simplest way to express the conditions for interconversion is through Lorenz curves, which we now describe.
-
-Given a vector $\x$ we define $\x^\downarrow$ to be the re-arrangement of the components of $\x$ into decreasing order.
+We wish to apply majorization to describing magic in different fragments at the level of the associated Wigner distributions.
+However, these are in general quasi-probability distributions and so it is important to detail how majorization is computed for these cases and what differences quasi-distributions bring over genuine probability distributions.
+
+Central to the analysis is the notion of a Lorenz curve of a vector $\w \in \mathbb{R}^n$ relative to some other vector $\r \in \mathbb{R}^n$.
+Given a vector $\w$ we define $\w^\downarrow$ to be the re-arrangement of the components of $\w$ into decreasing order.
 Now, given two $n$--component vectors $\w$ and $\r$ we define the \emph{Lorenz curve} of $\w$ relative to $\r$, denoted $L_{\w|\r}(x)$, as the piece-wise linear function that passes through $(0,0)$ and the $n$ points
@@
 The value $L_{\w|\r}(x) = 1$ is a global maximum, attained at the end-point $x=1$.
+Moreover, if $\w, \w', \r, \r'$ are all valid probability distributions with neither of $\r,\r'$ having negative components then it has been shownin~\cite{ruch_mixing_1978} that
+\begin{equation}
+(\w, \r) \succ (\w', \r') \mbox{ if and only if } L_{\w |\r}(x) \ge L_{\w' |\r'}(x).
+\end{equation}
+This provides a simple way of computing whether relative majorization holds between pairs of probability distributions.
+
 However, if $\w$ is a \emph{quasi-probability} distribution with negative values, and $\r$ a regular probability distribution things are different.
@@
 \end{equation}
-Now it is shown in~\cite{ruch_mixing_1978} relative majorization between pairs of distributions occurs if and only if the associated Lorenz curves never cross.
+As mentioned, relative majorization between pairs of distributions occurs if and only if the associated Lorenz curves never cross.
 Therefore we can express this condition in terms of the Lorenz curves of the quasi-probability distributions $\w$ and $\w'$ relative to $\r$ and $\r'$ respectively.
@@
 
-We therefore have that $\w_1 \succ_{\r} \w_2$ if and only if $L_{\w_1 | \r} (x) \ge L_{\w_2 | \r}(x)$ for all $x \in [0,1]$ (technical discussion and proof can be found in~\cref{app:major}.
-In other words, the Lorenz curve of $\w_1$ relative to $\r$ is never below the Lorenz curve of $\w_2$ relative to $\r$.
-Phrased more abstractly, the relative majorization pre-order corresponds to the standard ordering of concave, piece-wise linear functions passing through $(0,0)$ and $(1,1)$.
-We note that another neat geometric formulation of relative majorization exists, stating that the $L_1$-norm angle between $\w_1$ and $\r$ is greater than or equal to the $L_1$-norm angle between $\w_2$ and $\r$ (see~\cite{Busch_1998} for details).
+We therefore have that $(\w, \r) \succ (\w', \r')$ if and only if $L_{\w | \r} (x) \ge L_{\w' | \r'}(x)$ for all $x \in [0,1]$ equally applies for the case of $\w,\w'$ being quasi-distributions.
+
+In the next section we discuss the application of majorization to Wigner representations of magic, where the quasi-distribution $W_\rho(x)$ of a magic state can be analysed relative to any Wigner positive free state $W_\sigma(x)$.
+To our knowledge, the application of majorization to quasi-distributions in  physics has not been considered previously.
+The caveat here is that relative majorization ranges over stochastic maps that obey a transformation ($A\r = \r'$), while in the case of the Wigner representation there is a stronger restriction that the symplectic structure of the phase space is respected.
+Therefore, any majorization constraint can provide necessary, but not sufficient conditions on magic state interconversions.
+This observation raises a question that to our knowledge has not been previously considered in the classical statistical mechanics literature: what are the conditions for symplectic majorization of classical statistical mechanics?
+We shall \nick{return} to this question later on when we discuss how our approach could be used to construct concrete lower-bounds on distillation rates in~\cref{sec:lower_bounds}.
 
@@
 \end{lemma}
-\begin{proof}
-	We denote the Wigner distributions of the states compactly as vectors $\bmw(\rho) \equiv W_\rho(x)$ and $\bmw(\sigma) \equiv W_\sigma(x)$.
-	We choose the component indexing so that the rescaled distribution 
-	\begin{equation}
-		\widetilde{\bmw}(\rho|\sigma) \coloneqq \left(\frac{w(\rho)_1}{w(\sigma)_1}, \dots, \frac{w(\rho)_{d^2}}{w(\sigma)_{d^2}} \right)^T,
-	\end{equation}
-	is sorted, $\widetilde{\bmw} = \widetilde{\bmw}^\downarrow$.
-	Note that all components of $\bmw(\sigma)$ are positive, so $\widetilde{w}_i \geq 0$ if and only if $w(\rho)_i \geq 0$ for any $i=1,\dots,d^2$.
-
-	Let $i_\star$ be the index of the smallest non-negative component of $\widetilde{\bmw}^\downarrow$.
-	Then, $w(\rho)_i < 0$ if and only if $i > i_\star$, so the maximum of Lorenz curve $\lc{\rho}{\sigma}(x)$ takes the value 
-	\begin{equation}
-		\lc{\rho}{\sigma}(x_{i_\star}) = \sum_{i=1}^{i_\star} w(\rho)_i,
-	\end{equation}
-	and is achieved at
-	\begin{equation}\label{eq:maxloc}
-		x_{i_\star} \coloneqq \sum_{i=1}^{i_\star} w(\sigma)_i.
-	\end{equation}
-
-	The location of the maximum ($x=x_{i_\star}$) varies from fragment to fragment, but its value is independent of $\sigma$,
-	\begin{align}
-	L_\star &:=	\lc{\rho}{\sigma}(x_{i_\star}) 
-		= \sum\limits_{\bmx: \W[\bmx]{\rho} \geq 0} \W[\bmx]{\rho} \nonumber \\
-		&= 1 + \sn{\rho}.
-	\end{align}
-
-Since the magic monotone mana is a monotonic function of sum-negativity, $\rm{mana}(\rho) \coloneqq \ln{(2\hspace{1pt}\sn{\rho}+1)}$, we see that mana corresponds precisely to the peak of the Lorenz curve $L_{\rho|\sigma}(x)$.
-Therefore, mana is one of $d^{2n}$ constraints, so majorization is strictly a stronger constraint in any fragment.
-\end{proof}
-Using the Lorenz curve perspective, it is simple to construct other monotones. For example, within a given fragment, the area above $L=1$ is another magic monotone.
+The proof of this is given in Appendix \ref{lem:lcmax}.
+Using the Lorenz curve perspective, it is simple to construct other monotones.
+For example, within a given fragment, the area above $L=1$ is another magic monotone.
 \begin{lemma} Let $\A_\sigma(\rho)$ be the area of the region $\{(x,y) : (x, L_{\rho | \sigma}(x)) \ge 1\}$. Then $\A_\sigma(\rho)$ is a magic monotone for $\R_\sigma$.
@@
 
-\section{Magic in the unital fragment}
+\subsection{Magic bounds for unital protocols}
 \label{sec:unital}
@@
 
-To use relative majorization on such distributions we must rescale relative to the free state, however the rescaled distribution in the unital fragment is simply
-\begin{equation}
-	\widetilde{\rm{W}}_{\rho_{\rm{S}}|\frac{1}{3}\id}(\bmx) = \frac{\W[\bmx]{\rho_{\rm{S}}}}{\W[\bmx]{\frac{1}{3}\id}} = 9\W[\bmx]{\rho_{\rm{S}}},
-\end{equation}
-so the problem of ordering the rescaled distribution, which is required for the evaluation of the Lorenz curves, is equivalent to ordering $\W{\rho_{\rm{S}}}$.
 The Wigner distribution of $n$ copies of the state is obtained by the $n$-fold product of the single copy distribution, and the Lorenz curve $L_{\rho|\sigma}(x)$ for $\rho = \rho_S(\epsilon)^{\otimes n}$ and $\sigma = (\I/3)^{\otimes n}$ is readily computed for any $n$ and $\epsilon$, and the full details are provided in~\cref{app:lcsu_technical}.
@@
 Both the mana and the max--thauma bounds are looser than the majorization bound we derived via the first elbow constraint as illustrated in~\cref{fig:distill_bounds}.
-However, beyond this comparison with these global bounds it is important to emphasize that the above majorization bound gives constraints on any distillation protocol that is \emph{unital}, and therefore allows for a finer analysis of magic distillation protocols than global bounds would allow.
-\nick{this is a bit repetitive and vague, can you clarify?}
-
-While unital channels are quite natural, we might wonder how different distillation bounds can be if we allow biases into our protocols, or use protocols that are invariant under some residual symmetry.
+
 In the next section we provide relative majorization bounds in arbitrary stabilizer fragments, and in particular we shall parameterize these bounds from a thermodynamic perspective.
@@
 \begin{theorem}\label{thm:free-energy}
-	Consider a magic distillation protocol on $n \gg 1$ qutrits transforming noisy Strange state $\rho_S(\epsilon)^{\otimes n} \rightarrow \rho_S(\epsilon')^{\otimes m}$, under the assumptions just stated.
-
-Let each qutrit have a Hamiltonian $H$ with energies $E_0, E_1, E_2$. Let $T =(k\beta)^{-1}$ be any characteristic temperature for the physical system in the state $\tau$, with free energy $F$. 
-We define $\beta_\star = 1/kT_\star$ through the relation
+	Consider a magic distillation protocol transforming noisy Strange state $\rho_S(\epsilon)^{\otimes n} \longrightarrow \E(\rho_S(\epsilon)^{\otimes n})=\rho_S(\epsilon')^{\otimes m}$ with $n, m \gg 1$.
+
+Let each qutrit have a Hamiltonian $H$ with energies $E_0, E_1, E_2$, and define $E_{\rm max} = \max\{E_0, E_1, E_2\}$ and $E_s$ the eigenvalue of the eigenstate that overlaps the negative component of $\rho_S(\epsilon)$ in the Wigner representation.
+Let $T =(k\beta)^{-1}$ be any characteristic temperature for the physical system in the state $\tau^{\otimes n}= (e^{-\beta H}/\Z)^{\otimes n}$, with free energy $F$.
+Assume that for $n,m \gg 1$ the channel $\E$ generates negligible correlations on $\tau^{\otimes n}$, and so $\E(\tau^{\otimes n}) = \sigma^{\otimes m}$ for some state $\sigma$.
+
+Define $\beta_\star = 1/kT_\star$ through the relation
 \begin{equation}
@@
 \end{equation}
-where $E_{\rm max} = \max\{E_0, E_1, E_2\}$ and $E_s$ is the eigenvalue of the eigenstate that overlaps the negative component of $\rho_S(\epsilon)$ in the Wigner representation.
-We define a threshold noise level,
+and define a threshold noise,
 \begin{equation}
@@
 \end{equation}
-Then the distillation rate $R = m/n$ of the magic protocol is bounded as follows:
+Then the distillation rate $R = m/n$ of the magic protocol is bounded as:
 \begin{equation}\label{eq:rate_bounds_proof}
@@
 \end{equation}
-Where $F'$ is the free energy of the single qutrit output state $\sigma = e^{-\beta H'}/\Z'$ of the protocol applied to $\tau$. 
+Where $F'$ is the free energy of the state $\sigma = e^{-\beta H'}/\Z'$ and other primed quantities are defined in the same way as the corresponding unprimed quantities. 
 \end{theorem}
@@
 
+The above bounds mainly demonstrate how one can use relative majorization of quasi-distributions to incorporate additional information into distillation bounds.
+However to unpack the results more it is useful to consider the case in which $H=H'$, and look at $\epsilon' \rightarrow 0$.
+For this we obtain Figure \ref{contour-bounds} which gives a contour plot of $R$ as a function of inverse temperature $\beta$ and depolarising noise level $\epsilon$ for the initial noisy magic state.
+\begin{figure}[t!]\label{contour-bounds}
+    \centering
+    \includegraphics[scale=0.4]{figs/rate_scatter.pdf}
+    \caption{\textbf{Temperature-dependent bounds for magic distillation.}
+  Shown is a contour plot of  $R(\epsilon, \beta)$ where $\beta$ is an inverse temperature and $\epsilon$ is the depolarising noise of the magic state.
+The relevant data from the spectrum of the qutrit operator $H$ enters in via $\epsilon_\star(\beta)$ and $\beta_\star$.
+The vertical dashed line is the `Landauer-like' temperature threshold $\beta_\star$ and the diagonal dashed curve corresponds to the noise threshold $\epsilon_\star (\beta)$ for $\beta \leq \beta_\star$.
+The $\beta =0 $ line corresponds to the regime in which the magic protocol gives a unital channel.
+    }
+    \label{fig:rate_contour}
+\end{figure}
 \begin{proof}
@@
 \end{proof}
-
-We find numerically that the bounds derived above from the ascending part of the curve generally perform better than when considering the region around the Lorenz curve peak.
-Similar bounds can be obtained from the decreasing part of the Lorenz curve, but they do not shed any more light on distillation.
-Numerically ranging through the entire curve will improve our bounds incrementally, to an extent that depends on the intricate Lorenz curve structure.
-
-\subsection{Distillation bounds and energy dependencies}
-The previous section was focussed on an individual fragment, and while this does shed light on how physical constraints may, or may not, constrain protocols it is a bit indirect.
-However it is possible to adapt these bounds and put them in a more natural light.
-
-For this, we now drop the condition that $\sigma$ is left invariant under the distillation protocol, and assume it transforms to some $\sigma'$.
-This output state must be some other stabilizer state and so has a positive Wigner function also.
-The strategy is then to use how any protocol transforms $\sigma$ to act as a measure of physical features, such as energy, of the protocol.
-Therefore, we are interested in the conditions under which $(\rho, \sigma) \rightarrow (\rho', \sigma')$.
-For this we can use the full definition of relative majorization on the associated Wigner functions, and obtain distillation bounds from
-\begin{equation}
-(W_\rho(\x), W_\sigma(\x) ) \succ (W_{\rho'}(\x), W_{\sigma'}(\x) ).
-\end{equation}
-The condition for this is $L_{\rho |\sigma } (x) \ge L_{\rho'|\sigma'} (x)$, and so exactly the same analysis applies as in the previous case, but now with the Gibbs-recaling parameters for the output state being different from the ones for the input state~\cite{Renes_2016}.
-
-If the physical system has Hamiltonian $H$, and can be experimentally cooled down to some reference temperature $T$ then we can consider the reference equilibrium state $\sigma = e^{-\beta H}/\Z$, and estimate the energetic and entropic costs of any distillation protocol in terms of how the protocol transforms $\sigma$ to some other equilibrium state $\sigma'$.
-For example, if $\sigma'$ is close to the ground state \nick{fun fact: ground states correspond to $\beta \rightarrow \infty$ which makes both Lorenz curves look very rectangular - should we include this as an insight?} of the system, we then know that a great deal of entropy is dumped by the process.
-This allows us to parameterise our distillation bounds in a more insightful way.
-
-\begin{figure}[t!]
-    \centering
-    \includegraphics[scale=0.4]{figs/rate_scatter.pdf}
-    \caption{\textbf{Magic distillation bounds within arbitrary stabiliser fragments.}
-  Shown is a contour plot of  $R(\epsilon, \beta)$ where $\beta$ is an effective inverse temperature and $\epsilon$ is the depolarising noise of the magic state.
-The relevant data from the spectrum of the qutrit operator $H$ enters in via $\epsilon_\star(\beta)$ and $\beta_\star$.
-The vertical dashed line is the `Landauer-like' temperature threshold $\beta_\star$ and the diagonal dashed curve corresponds to the noise threshold $\epsilon_\star (\beta)$ at every $\beta \leq \beta_\star$.
-The unital fragment corresponds to the $\beta =0 $ line.
-    }
-    \label{fig:rate_contour}
-\end{figure}
 

### 2021-04-21 magic_paper.tex
small corrections plus references

@@
 Interestingly, taking a thermodynamic perspective in this context raises a problem, namely it is impossible to define entropies for quasi-distributions.
-We circumvent this obstacle by making use of a more fundamental tool in thermodynamics -- majorization theory \ddd{[cite]}.
+We circumvent this obstacle by making use of a more fundamental tool in thermodynamics -- majorization theory~\cite{cit:marshall, Veinott_1971, Ruch_1976}.
 To our knowledge majorization of quasi-distributions has not been considered in quantum physics before, and therefore our analysis is of broader interest to the study of non-classicality in quantum systems.
@@
 
-Majorisation~\cite{cit:marshall} is a collection of powerful tools that has recently found many applications in quantum information theory~\cite{Nielsen_1999, cit:cwiklinski, cit:lostaglio2, cit:gour, cit:gour2, Horodecki_2003, Vallejos_2021}.
+Majorisation is a collection of powerful tools that has recently found many applications in quantum information theory~\cite{Nielsen_1999, cit:cwiklinski, cit:lostaglio2, cit:gour, cit:gour2, Horodecki_2003, Vallejos_2021}.
 It describes the disorder of distributions that undergo stochastic transformations.
@@
 
-There is a natural generalisation, which is called $\bmd$--majorization~\cite{Veinott_1971}, or in the context of thermodynamics, thermo-majorization \ddd{[cite]}.
+There is a natural generalisation, which is called $\bmd$--majorization~\cite{Veinott_1971}, or in the context of thermodynamics, thermo-majorization~\cite{cit:horodecki2013}.
 For a fixed probability distribution $\r = (r_1, \dots, r_n)$ with positive components, we define majorization relative to $\r$ as $\p \succ_{\r} \q$, if and only if there exists a stochastic map $A$ such that $A\r = \r$ and $A \p = \q$.
-In order words, the relative majorization pre-order coincides with the image of $\p$ under stochastic maps that have $\r$ as a fixed point.
+In order words, this majorization pre-order coincides with the image of $\p$ under stochastic maps that have $\r$ as a fixed point.
 It is readily checked that the original majorization condition between probability distributions corresponds to the case $\r = (1/n, \dots, 1/n)$.
@@
 
-We can further generalise this to \emph{relative majorization}\ddd{[cite]}, defined as an ordering between pairs of vectors so that 
+We can further generalise this to \emph{relative majorization}~\cite{Ruch_1976, ruch_mixing_1978, Renes_2016, Buscemi_2017}, defined as an ordering between pairs of vectors so that 
 \begin{equation}
@@
 Given a vector $\w$ we define $\w^\downarrow$ to be the re-arrangement of the components of $\w$ into decreasing order.
-Now, given two $n$--component vectors $\w$ and $\r$ we define the \emph{Lorenz curve} of $\w$ relative to $\r$, denoted $L_{\w|\r}(x)$, as the piece-wise linear function that passes through $(0,0)$ and the $n$ points
+Given two $n$--component vectors $\w$ and $\r$, we first define $\widetilde{\w}$, where $\widetilde{w}_i := w_i/r_i$, as the vector of component-wise ratios between $\w$ and $\r$.
+We can now define the \emph{Lorenz curve} of $\w$ relative to $\r$, denoted $L_{\w|\r}(x)$, as the piece-wise linear function that passes through $(0,0)$ and the $n$ points
 \begin{equation}
@@
 \end{equation}
-where $R:= \sum_{i=1}^n r_i$, and $\pi$ is the permutation on $n$ objects that sends $\widetilde{\w}$ to $\widetilde{\w}^{\downarrow}$, where $\widetilde{w}_i := w_i/r_i$ is the vector of component-wise ratios of $\w$ and $\r$.
+where $R:= \sum_{i=1}^n r_i$ and $\pi$ is the permutation on $n$ objects mapping $\widetilde{\w}$ to $\widetilde{\w}^{\downarrow}$.
 The form of this requires that $\r$ has no zero components, which we shall assume without loss of generality as in any physical situation the rank of a quantum state is not an operationally meaningful quantity.
@@
 The value $L_{\w|\r}(x) = 1$ is a global maximum, attained at the end-point $x=1$.
-Moreover, if $\w, \w', \r, \r'$ are all valid probability distributions with neither of $\r,\r'$ having negative components then it has been shownin~\cite{ruch_mixing_1978} that
+Moreover, if $\w, \w', \r, \r'$ are all valid probability distributions with neither of $\r,\r'$ having negative components then it has been shown in~\cite{ruch_mixing_1978} that
 \begin{equation}
@@
 
-However, relative majorization is usually considered for probability distributions, and so we must verify that the same Lorenz curve conditions apply to quasi-probability distributions.
+However, relative majorization is usually considered for probability distributions, so we need to verify that the same Lorenz curve conditions apply to quasi-probability distributions before proceeding with our analysis.
 This can be done from first principles, but a simpler way is see that this holds is to reduce to the problem of genuine distributions by first `masking' the negativity in the quasi-probability distribution $\w$ using the reference distribution $\r$ and then applying the conditions for relative majorization.
 
-More precisely, if the components of $\r$ are never zero, then there always exists an $\epsilon >0$ such that $\w_\epsilon := \epsilon \w + (1-\epsilon) \r$ is a genuine probability distribution.
+More precisely, since the components of $\r$ are strictly positive, there always exists an $\epsilon >0$ such that $\w_\epsilon := \epsilon \w + (1-\epsilon) \r$ is a genuine probability distribution.
 We can see that $(\w , \r) \succ (\w', \r')$ if and only if $(\w_\epsilon , \r) \succ (\w_\epsilon', \r')$, where we choose $\epsilon$ so that both $\w_\epsilon$ and $\w_\epsilon'$ are probability distributions.
@@
 As mentioned, relative majorization between pairs of distributions occurs if and only if the associated Lorenz curves never cross.
-Therefore we can express this condition in terms of the Lorenz curves of the quasi-probability distributions $\w$ and $\w'$ relative to $\r$ and $\r'$ respectively.
+Therefore, we can express this condition in terms of the Lorenz curves of the quasi-probability distributions $\w$ and $\w'$ relative to $\r$ and $\r'$ respectively.
 
@@
 \end{equation}
-or put another way, relative to $W_\sigma$ the quasi-distribution $W_{\rho_1}$ is more ordered than the quasi-distribution $W_{\rho_2}$.
+or put another way, that the quasi-distribution $W_{\rho_1}$ is more ordered than the quasi-distribution $W_{\rho_2}$ relative to $W_\sigma$.
 
-This in turn can be expressed in terms of Lorenz curves. To simplify notation we denote by $L_{\rho | \sigma}(x)$ the Lorenz curve $L_{W_{\rho} | W_{\sigma}} (x)$. We therefore have that
+This in turn can be expressed in terms of Lorenz curves. To simplify notation, we denote by $L_{\rho | \sigma}(x)$ the Lorenz curve $L_{W_{\rho} | W_{\sigma}} (x)$. We therefore have that
 \begin{equation}
@@
 Note, however, that unlike any monotone, this is not a single numerical constraint, but a \emph{family} of constraints.
-Indeed, for $n$ copies of a $d$--dimensional system the number of terms in $W_{\rho}$ is $d^{2n}$, so the Lorenz curve condition corresponds to \emph{exponentially} many constraints, of which there are as many independent constraints as there are elbows in the Lorenz curve of the output state, which is proved in~\cref{thm:elbows} in~\cref{app:frag}.
-In principle, any one location $x$ provides a valid constraint leading to some upper distillation bound and optimising over the location provides the strictest bound.
+Indeed, for $n$ copies of a $d$--dimensional system the number of terms in $W_{\rho}$ is $d^{2n}$, so the Lorenz curve condition corresponds to exponentially many constraints, of which though there are at most as many independent constraints as there are elbows in the Lorenz curve of the output state, as proved in~\cref{thm:elbows} in~\cref{app:frag}.
+In principle, any one location $x$ provides some valid constraint leading to an upper distillation bound, while optimising over the location provides the strictest majorisation bound.
 
@@
 
-In this section we give some generic aspects of Lorenz curves for magic states.
-In particular these allow us to interpret previous magic monotones in a new light.
-The f,irst result provides an extremely simple way to see that the sum-negativity of a magic state is a monotone.
+In this section, we give some generic aspects of Lorenz curves for magic states.
+In particular, these allow us to interpret previous magic monotones in a new light.
+The first result provides an extremely simple way to see that the sum-negativity of a magic state is a monotone.
 
@@
 
-If we have a magic state $\rho$ that has negativity in its Wigner representation, then as discussed, its Lorenz curve over-shoots $1$ and reaches a non-trivial maximum $L_\star$ that depends on the particular state.
-There is an exact relation between the peak and sum-negativity or mana, which is provided by the following result.
+If we have a magic state $\rho$ that has negativity in its Wigner representation, then, as discussed, its Lorenz curve over-shoots $1$ and reaches a non-trivial maximum $L_\star$ that depends on the particular state.
+There is an exact relation between $L_\star$ and sum-negativity or mana, which is provided by the following result.
 \begin{lemma}\label{lem:lcmax}
@@
 For example, within a given fragment, the area above $L=1$ is another magic monotone.
-\begin{lemma} Let $\A_\sigma(\rho)$ be the area of the region $\{(x,y) : (x, L_{\rho | \sigma}(x)) \ge 1\}$. Then $\A_\sigma(\rho)$ is a magic monotone for $\R_\sigma$.
+\begin{lemma}
+Given a magic state $\rho$ and a free state $\sigma$, let $\A_\sigma(\rho)$ be the area of the region $\{(x, y): 1 \leq y \leq L_{\rho | \sigma}(x)\}$.
+Then $\A_\sigma(\rho)$ is a magic monotone for $\R_\sigma$.
 \end{lemma}
@@
 \begin{equation}
-\rho_1^{\otimes N} \longrightarrow \rho_2^{\otimes R N}
+\rho_1^{\otimes n} \longrightarrow \rho_2^{\otimes R n}
 \end{equation}
-where $\rho_2$ is a purer magic state than $\rho_1$ and $R$ is made as large as possible as $N$ tends to infinity.
+where $\rho_2$ is a purer magic state than $\rho_1$ and $R$ is made as large as possible as $n$ tends to infinity.
 We shall next turn to this analysis, and exploit basic features of a magic state in order to obtain non-trivial distillation bounds.
@@
 
-This means in particular that $\E(\tau^{\otimes n}) = \tau'$ is a symmetric state on $m$ subsystems, and so by the quantum de Finetti theorem \ddd{[cite]} we have that
+This means in particular that $\E(\tau^{\otimes n}) = \tau'$ is a symmetric state on $m$ subsystems, and so by the quantum de Finetti theorem~\cite{christandl_2007} we have that
 \begin{equation}
@@
 
-  For example, suppose that $H=H'$ then this implies the protocol would leave the equilibrium state unchanged and so corresponds to a Gibbs-preserving map \ddd{[cite Philippe]}.
+  For example, suppose that $H=H'$ then this implies the protocol would leave the equilibrium state unchanged and so corresponds to a Gibbs-preserving map~\cite{faist_2015}.
 In the more general case $\Delta F := F' - F \ne 0$ and we have a free energy difference between the initial and final times, with respect to the relevant Hamiltonians.

### 2021-04-21 magic_paper.tex
Expansion of proof. Gaps in proof filled. Still stuff to be done on it.

@@
 This observation raises a question that to our knowledge has not been previously considered in the classical statistical mechanics literature: what are the conditions for symplectic majorization of classical statistical mechanics?
-We shall \nick{return} to this question later on when we discuss how our approach could be used to construct concrete lower-bounds on distillation rates in~\cref{sec:lower_bounds}.
+We shall return to this question later on when we discuss how our approach could be used to construct concrete lower-bounds on distillation rates in~\cref{sec:lower_bounds}.
 
@@
 \end{equation}
-Using the max--thauma properties of super-additivity and vanishing at free states, we obtain
-\begin{align}
-	&\theta_{\rm{max}}(\rho_{\rm{S}}(\epsilon)) \geq (1-\epsilon) \theta_{\rm{max}}(\ketbra{\rm{S}}) + \epsilon \theta_{\rm{max}}\left(\frac{1}{3}\id \right) = \nonumber\\
-	&(1-\epsilon) \theta_{\rm{max}}(\rho_{\rm{S}}(0)),
-\end{align}
-so that for a deterministic single-copy distillation process, an initial number of copies $n \geq \theta_{\rm{max}}(\tau) / \theta_{\rm{max}}(\rho) \geq 1-\epsilon$ is required.
-Therefore, the max--thauma bound for the pure Strange state distillation process can get as tight as \nick{CALCULATING THAUMA EXACTLY AT THE MOMENT}
-\begin{equation}
-	R = \frac{1}{n} = \frac{\theta_{\rm{max}}(\rho_{\rm{S}}(\epsilon))}{\theta_{\rm{max}}(\rho_{\rm{S}}(0))} \leq 1-\epsilon.
-\end{equation}
 
@@
 Our analysis associates to this protocol energy/entropy measures by considering how $\E$ transforms this reference equilibrium state.
-We first note that we can assume without loss of generality that $U_\pi\E(X) U_\pi^\dagger = \E(X)$ for any permutation $U_\pi$ of the $m$ output subsystems.
+We first note that we can assume without loss of generality that $U_\pi\E(X) U_\pi^\dagger = \E(X)$ for all $X$ and any permutation $U_\pi$ of the $m$ output subsystems.
 The reason for this is that the protocol on the noisy magic state outputs the state $\rho(\epsilon')^{\otimes m}$, which is invariant under permutations, and so we can therefore always symmetrise by performing a group average over the permutation group for the output systems without changing the performance of the distillation protocol on $\rho(\epsilon)^{\otimes n}$.
@@
 
-Let each qutrit have a Hamiltonian $H$ with energies $E_0, E_1, E_2$, and define $E_{\rm max} = \max\{E_0, E_1, E_2\}$ and $E_s$ the eigenvalue of the eigenstate that overlaps the negative component of $\rho_S(\epsilon)$ in the Wigner representation.
+Let each qutrit have a Hamiltonian $H$ with stabilizer eigenstates having energies $E_0, E_1, E_2$, and define $E_{\rm max} = \max\{E_0, E_1, E_2\}$ and $E_s$ the eigenvalue of the eigenstate that overlaps the negative component of $\rho_S(\epsilon)$ in the Wigner representation.
 Let $T =(k\beta)^{-1}$ be any characteristic temperature for the physical system in the state $\tau^{\otimes n}= (e^{-\beta H}/\Z)^{\otimes n}$, with free energy $F$.
@@
 \begin{proof}
-	We provide the full proof here, with some technical details pushed to~\cref{app:lcst_technical}.\\
+To establish the distillation bounds we consider the distillation protocol that gives
+\begin{equation}
+\E( \rho_S(\epsilon)^{\otimes n}) = \rho_S(\epsilon')^{\otimes m},
+\end{equation}
+for the magic state. We also consider how the protocol transforms the reference equilibrium state as
+\begin{equation}
+\E( \tau^{\otimes n}) = \sigma^{\otimes m}.
+\end{equation}
+Since $\tau$ and $\sigma$ are assumed to be full rank stabilizer states they have a strictly positive Wigner distribution, while in contrast the input and output magic states will have quasi-probability distributions for their Wigner functions.
+For any such protocol we therefore have that
+\begin{equation}
+(W_{\rho_n} (x), W_{\tau_n}(x) ) \succ  (W_{\rho'_m} (x), W_{\sigma_m}(x) ),
+\end{equation}
+where for simplicity we write $\rho_n := \rho_S(\epsilon)^{\otimes n}$, $\rho'_m:= \rho_S(\epsilon')^{\otimes m}$ and similarly for $\tau_n$ and $\sigma_m$. This therefore implies that
+\begin{equation}
+L_{\rho_n |\tau_n}(x) \ge L_{\rho'_m |\sigma_m}(x) \mbox{ for all } x.
+\end{equation}
+We must therefore compute the Lorenz curve data for $\rho_n$ relative to $\tau_n$, and compare with the Lorenz curve of the output state $\rho_m'$ relative to $\sigma_m$.
 
-Let $\displaystyle \sigma = e^{-\beta H} / \Z_\beta$ be a stabiliser state, where $\beta \geq 0$ and $H = E_0 \ketbra{\varphi_0} + E_1 \ketbra{\varphi_1} + E_2 \ketbra{\varphi_2}$ is an eigendecomposition of $H$.
-The stabilizer state $\sigma$ can now be written as 
+We define $W_{\rho | \tau}(\x) := W_\rho(\x)/W_\tau(\x)$, which is always well-defined since $\tau$ is full-rank. Now we have that
 \begin{equation}
-	\sigma = \frac{e^{-\beta E_0}}{\Z_\beta} \ketbra{\varphi_0} + \frac{e^{-\beta E_1}}{\Z_\beta} \ketbra{\varphi_1} + \frac{e^{-\beta E_2}}{\Z_\beta} \ketbra{\varphi_2},
+W_{\rho_1\otimes \rho_2 | \tau_1 \otimes \tau_2} (\x_1 \oplus \x_2) = W_{\rho_1 | \tau_1}(\x_1)W_{\rho_2 | \tau_2}(\x_2),
 \end{equation}
-where $\{\ket{\varphi_k}\<\varphi_k|\}$ are pure, orthonormal stabiliser states, which can be represented in terms of generalized Paulis.
+and also,
+\begin{equation}
+W_{\rho_1\otimes \rho_2} (\x_1 \oplus \x_2) = W_{\rho_1}(\x_1)W_{\rho_2}(\x_2),
+\end{equation}
+for any states $\rho_1, \rho_2$ and any full-rank stabilizer states $\tau_1, \tau_2$. \ddd{[Notation clashing here. Frame result outside as its own lemma -- we gotta check everything.]}
+Therefore we have that
+\begin{align}
+W_{\rho_n |\tau_n} (\x) &= \prod_{i=1}^n W_{\rho|\tau}(\x_i)\\
+W_{\rho_n } (\x) &= \prod_{i=1}^n W_\rho(\x_i)
+\end{align}
+where $\x = \oplus_{i=1}^n \x_i$ is the phase space point for the full system in terms of those of the individual subsystems.
+
+The points defining the Lorenz curve $L_{\rho_n |\tau_n}(x)$ are obtained from first sorting the components of $W_{\rho_n |\tau_n}(\x)$ in non-increasing order and then computing the partial sums of $W_{\rho_n |\tau_n}(\pi(\x))$ where $\pi$ is the permutation that realises the sorting.
+Therefore we first look at the values of $W_{\rho|\tau}(\x_i)$ for the single-copy case.
+
+The equilibrium state at inverse temperature $\beta$ on a single qutrit is given by $\tau = e^{-\beta H} / \Z$.
+Moreover we have that $\tau$ is a full-rank stabilizer state, where $\beta \geq 0$ and $H = E_0 \ketbra{\varphi_0} + E_1 \ketbra{\varphi_1} + E_2 \ketbra{\varphi_2}$ is an eigendecomposition of $H$.
+The state $\tau$ can now be written as 
+\begin{equation}
+	\tau = \frac{e^{-\beta E_0}}{\Z} \ketbra{\varphi_0} + \frac{e^{-\beta E_1}}{\Z} \ketbra{\varphi_1} + \frac{e^{-\beta E_2}}{\Z} \ketbra{\varphi_2},
+\end{equation}
+where the eigenstates $\{\ket{\varphi_k}\<\varphi_k|\}$ are pure, orthonormal stabiliser states, which can be represented in terms of generalized Paulis.
 To make our analysis simpler we perform a change of basis that does not affect the Wigner negativity of the problem.
@@
 Since the Clifford group is the normalizer of the Heisenberg-Weyl group, $C$ is a Clifford unitary.
-Therefore, $C$ maps $\sigma$ to another stabilizer state that is diagonal in the computational basis, and we can assume without loss of generality that $\sigma$ is diagonal in $\{|0\>,|1\>, |2\>\}$.
+Therefore, $C$ maps $\tau$ to another stabilizer state that is diagonal in the computational basis, and we can assume without loss of generality that $\tau$ is diagonal in $\{|0\>,|1\>, |2\>\}$.
 However, this choice means that the location of the negative Wigner component $-v(\epsilon)$ of the Strange state will be permuted on the discrete phase space.
@@
 
-The Wigner distribution of state $\sigma$ is then given by
+The Wigner distribution of state $\tau$ is then given by
 \begin{align}
-	\W[\bmx]{\sigma} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z_\beta}W_{\ketbra{k}}(x, p) \nonumber\\
-	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z_\beta} \delta_{x, k} = \frac{e^{-\beta E_x}}{3\Z_\beta},
+	\W[\bmx]{\tau} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z}W_{\ketbra{k}}(x, p) \nonumber\\
+	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z} \delta_{x, k} = \frac{e^{-\beta E_x}}{3\Z},
 \end{align}
 where $x$ labels one of the three vertical lines in the phase space.
-Since we have restricted to full-rank states, all Wigner components are strictly positive, and so the pre-order $\prec_{\sigma}$ is well-defined.
-States that are not full-rank can be addressed as a limiting case of the above.
-
-The Strange state rescaled distribution for a magic state $\rho_S(\epsilon)$ is now given by 
-\begin{equation}
-	\widetilde{\rm{W}}_{\rho_{\rm{S}}|\sigma}(\bmx) = \frac{\W[\bmx]{\rho_{\rm{S}}}}{\W[\bmx]{\sigma}},
-\end{equation}
-which attains four distinct values on the phase space, naturally splitting it into four regions as illustrated in the~\cref{fig:pd_split}.
+The rescaled Wigner distribution $W_{\rho|\tau}(\x)$ is then easily computed.
+It has $9$ components in two, however several of these come with multiplicities.
+In total there are four distinct values on the phase space, as illustrated in the~\cref{fig:pd_split}.
 \begin{figure}[h]
@@
     \includegraphics[scale=0.45]{figs/pd_split_thermal.pdf}
-    \caption{\textbf{Qutrit phase space regions for $W_{\rho_{\rm{S}} | \sigma}(\x)$.}
+    \caption{\textbf{Qutrit phase space regions for $W_{\rho | \tau}(\x)$.}
     Here, the negative component of the magic state overlaps the Wigner distribution of $|0\>$.
@@
 
-The component values and multiplicities of the relevant distributions in the four distinct regions are summarised by the following component and multiplicity vectors,
+We now denote by $\w(\rho), \w(\rho|\tau)$ the unique values occurring in $W_\rho(\x), W_{\rho|\tau}(\x)$ respectively and $\mathbf{m}$ the vector of associated multiplicities of each value in $W_\rho(\x)$.
+The component values and multiplicities of the relevant distributions in the four distinct regions are given by
 \begin{align}
-	\bmw(\rho_{\rm{S}}) &\coloneqq (-v, u, u, u), \\
+	\w(\rho) &\coloneqq (-v, u, u, u), \\
 		\bmm &\coloneqq (1,2,3,3), \\
-	\bmw(\sigma) &\coloneqq \frac{1}{3\Z} \left( e^{-\beta E_0}, e^{-\beta E_0}, e^{-\beta E_1}, e^{-\beta E_2} \right), \\
-	\bmw(\rho_{\rm{S}} | \sigma) &\coloneqq 3\Z \left( -v e^{\beta E_0}, u e^{\beta E_0}, u e^{\beta E_1}, u e^{\beta E_2} \right). \label{eq:bmw_rescaled}
+	\bmw(\tau) &\coloneqq \frac{1}{3\Z} \left( e^{-\beta E_0}, e^{-\beta E_0}, e^{-\beta E_1}, e^{-\beta E_2} \right), \\
+	\bmw(\rho_{\rm{S}} | \tau) &\coloneqq 3\Z \left( -v e^{\beta E_0}, u e^{\beta E_0}, u e^{\beta E_1}, u e^{\beta E_2} \right). \label{eq:bmw_rescaled}
 \end{align}
 
-Using this notation, the values and multiplicities of the $n$--copy distribution $\bmw(\rho^{\otimes n}_S |\sigma^{\otimes n})$ are computed in~\cref{lem:ncopycomponents} in~\cref{app:cmpairs}.
-The values are denoted by $w(\rho_{\rm{S}} | \sigma)_{ijk}$ with associated multiplicity $m_{ijk}$.
-The indices $i,j,k$ are non-negative integers and obey the constraint $\alpha \coloneqq i+j+k \leq n$.
-The $n$--copy multiplicity is given by
+Using this notation, the values and multiplicities of the $n$--copy distribution $\bmw(\rho_n |\tau_n)$ are computed in~\cref{lem:ncopycomponents} in~\cref{app:cmpairs}. The values are given by 
+\begin{align}\label{eq:ncopy_w_rescaled}
+	[\w(\rho_n | \tau_n)]_{ijk} &= (3\Z)^{n} (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )},
+\end{align}
+where the indices $i,j,k$ are non-negative integers that obey the constraint $\alpha \coloneqq i+j+k \leq n$.
+The multiplicity of this above value is $m_{ijk}$ with
 \begin{equation}
-	m_{ijk} = \frac{n!}{i!j!k!(n-\alpha)!} 2^i 3^j 3^k,
+	m_{ijk} = \frac{n!}{i!j!k!(n-\alpha)!} 2^i 3^j 3^k.
 \end{equation}
-while the distribution values are given by
-\begin{align}\label{eq:ncopy_w_rescaled}
-	w(\rho_{\rm{S}} | \sigma)_{ijk} &= (3\Z)^{n} (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )},
-\end{align}
-where we have also computed the unscaled components
+The associated components of $\w(\rho_n)$ are given by
 \begin{align}
-	w(\rho_{\rm{S}})_{ijk} &= (-v)^{n-\alpha} u^{\alpha}, \label{eq:ncopy_wrho}\\
-	w(\sigma)_{ijk} &= (3\Z)^{-n} e^{-\beta (n-\alpha)E_s} e^{-\beta ( i E_0 + j E_1 + k E_2 )}. \label{eq:ncopy_wsigma}
+	[\w(\rho_n)]_{ijk} &= (-v)^{n-\alpha} u^{\alpha}, \label{eq:ncopy_wrho}\\
+	[\w(\tau)]_{ijk} &= (3\Z)^{-n} e^{-\beta (n-\alpha)E_s} e^{-\beta ( i E_0 + j E_1 + k E_2 )}. \label{eq:ncopy_wsigma}
 \end{align}
 
-In order to construct the $n$--copy Lorenz curve $\lc{\rho_{\rm{S}}^{\otimes n}}{\sigma^{\otimes n}}$ we need to order the components of the distribution, $w(\rho_{\rm{S}} | \sigma)_{ijk}$ in decreasing order.
-In particular, to find the coordinates of the first elbow $(x_0, L_0)$, we need to evaluate the maximum component,
+In order to construct the $n$--copy Lorenz curve $L_{\rho_n|\tau_n}(x)$ we need to order the components of the distribution, $w(\rho_{\rm{S}} | \tau)_{ijk}$ in decreasing order, and identify the sequence of indices that give us $W_{\rho_n}(\pi(\x))$.
+
+Generally this is complex, but to obtain distillation bounds we may determin the location of the first elbow $(x_0, L_0)$ of $L_{\rho_n|\tau_n}(\x)$. To do so we compute the largest component 
+\begin{equation}
+w_{\rm max} := \max_{i,j,k} [\w(\rho_n | \tau_n)]_{ijk},
+\end{equation}
+and determine the indices at which this occurs.
+Putting in the values we obtain
 \begin{align}
-	&w(\rho_{\rm{S}} | \sigma)_{\rm{max}} \coloneqq (3\Z)^{n}\times \nonumber\\
-	&\max\limits_{i,j,k}\Big\{ (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \label{eq:max_slope}
+	\hspace{-1cm}(3\Z)^{-n}w_{\rm max}= \max\limits_{i,j,k}\Big\{ (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \label{eq:max_slope}
 \end{align}
 where $0 \leq i,j,k \leq n$ and $\alpha \coloneqq i+j+k \leq n$.
-For $0 \leq \epsilon \leq 3/7$, we have $v \geq u$. Since we assume that $n$ is even, we need the sum $\alpha = i+j+k$ to be even too, so that the expression is positive.
+Now for $0 \leq \epsilon \leq 3/7$, we have $v \geq u$. Since we assume that $n$ is even, we need the sum $\alpha = i+j+k$ to be even too, so that the expression is positive.
 
@@
 \begin{align}
-	&w(\rho_{\rm{S}} | \sigma)_{\rm{max}} = \nonumber\\
+	&w_{\rm max} = \nonumber\\
 	&(3\Z)^{n} v^n e^{n\beta E_s}\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_s)} \right)^{\alpha} \Big\}}.
@@
 If the expression $\frac{u(\epsilon)}{v(\epsilon)} e^{\beta (E_{\rm{max}} - E_s)}$ is less than $1$ then the maximum occurs at $\alpha=0$, otherwise it occurs at $\alpha = n$.
-For a fixed stabilizer state $\sigma$, this transition is determined by the value of the depolarising noise parameter $\epsilon$ of the noisy magic state.
+For a fixed state $\tau$, this transition is determined by the value of the depolarising noise parameter $\epsilon$ of the noisy magic state.
 The transition occurs at $\epsilon = \epsilon_\star$ where
@@
 \begin{equation*}
-w(\rho_{\rm{S}} | \sigma)_{\rm{max}} =
+w_{\rm max} =
 	\begin{cases}
@@
 \end{equation}
+
+\ddd{[Hmmm this needs an additional assumption on the output state to re-run the same analysis. Very annoying.]}
 Similarly, considering the output magic state with respect to state $\sigma'$, the image of equilibrium state $\sigma$ under the magic protocol, we get output Lorenz curve coordinates,
@@
 
-\subsection{Lower magic bounds via majorisation}
+\section{Outlook and open questions}
 \label{sec:lower_bounds}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%\section{Fragments in general resource theories}
-%\label{sec:general_resources}
-%
-%\nick{Add from notes}
-%
-%So far we have introduced the notion of $\sigma$--fragments for any resource theory of magic. 
-%In this section we briefly generalise this concept to arbitrary resource theories and explain precisely how it connects with resource monotones. 
-%The busy reader more focussed on magic may skip this section.
-%
-%State convertibility within a given resource theory is often a hard question to address due to intricacies of the theory structure.
-%In general, the structure of a theory $\R$ is described by a pre-order $\prec_\R$ and usually resource monotones are employed to reduce this structure into a simple real number ordering.
-%The subdivisions of magic theories into $\sigma$--fragments suggests a new approach towards investigating state convertibility which retains more structure of the original theory than a measure can.
-%
-%Monotones reduce the structure of the resource theory $\R$ to a \emph{total} order on the real numbers.
-%Therefore, two states, even if incomparable in $\R$, are always mapped onto ordered real numbers.
-%We now generalise this idea of a theory projection that preserves comparability between states. 
-%\begin{definition}[\textbf{Covariant projection}]\label{def:covproj}
-%Let $\R = (\F, \O)$ be a resource theory with pre-order $\prec_\R$. 
-%Then a \emph{covariant resource projection} of $\R$ to a resource theory $\R'$ with pre-order $\prec_{\R'}$, is a pair of mappings $(\Pi_s, \Pi_o)$, where $\Pi_s$ maps quantum states in $\R$ to quantum states in $\R'$, and $\Pi_o$ maps free operations in $\R$ to free operations in $\R'$.
-%Moreover, these obey
-%	\begin{enumerate}
-%        \item $\Pis(\rho_1) \prec_{\R'} \Pis(\rho_2)$ whenever $\rho_1 \prec_\R \rho_2$;
-%        \item $\Pio(\E) = \Pio(\E_1) \circ \Pio(\E_2)$ whenever $\E = \E_1 \circ \E_2$.
-%    \end{enumerate}
-%We call $\R'$ a \emph{covariant fragment} of $\R$.
-%\end{definition}
-%
-%Resource monotones can now be clearly seen as a special case of covariant resource projections.
-%\begin{proposition}[\textbf{Totally ordered covariant theories}]\label{thm:monoproj}
-%	Any resource monotone $\M$ of a resource theory $\R$ is a covariant projection for which $\prec_{\R'}$ is a total order. 
-%	Conversely, any such covariant projection corresponds to a resource monotone $\M$. 
-%\end{proposition}
-%\begin{proof}
-%	Consider a monotone $\M$ in the context of a general resource theory $\R = (\F, \O)$.
-%	State order is covariantly preserved due to the defining property of a monotone, where the pre-order $\prec_{\R'}$ is simply the total order $\leq$ on $\mathbb{R}$. 
-%	
-%	Operational composition is covariantly preserved when we simply choose $\Pio(\E) = 1_\times$, namely the `multiplication by 1' operation on real numbers. 
-%	The definition of a resource monotone then automatically implies covariance.
-%	
-%	Conversely, given any covariant projection of $\R$ for which $\prec_{\R'}$ is a total order, we may map the totally ordered set of elements $\Pis(\rho)$ via an injective, non-decreasing function $f$ into $\mathbb{R}$.
-%	Then, $\M(\rho):=f(\Pi_s(\rho))$ provides a numerical value for each $\rho$ that obeys the definition of a monotone.
-%	
-%\end{proof}
-%
-%We can also view $\sigma$--fragments as an example of reducing the structure of a magic theory $\R$ to a subtheory with a tractable pre-order.
-%However, states which are incomparable in $\R$ remain incomparable and conversions between states which are comparable in $\R$ may no longer be possible.
-%\begin{definition}[\textbf{Contravariant projection}]\label{def:contraproj}
-%	Let $\R = (\F, \O)$ be a resource theory with pre-order $\prec_\R$. 
-%Then a \emph{contravariant resource projection} of $\R$ onto a resource theory $\R'$ with pre-order $\prec_{\R'}$, is a pair of mappings $(\Pi_s, \Pi_o)$, where $\Pi_s$ maps quantum states in $\R$ onto quantum states in $\R'$, and $\Pi_o$ maps free operations in $\R$ onto free operations in $\R'$.
-%Moreover, these obey
-%	\begin{enumerate}
-%        \item $\rho_1 \prec_\R \rho_2$ whenever $\Pis(\rho_1) \prec_{\R'} \Pis(\rho_2)$;
-%        \item $\E = \E_1 \circ \E_2$ whenever $\Pio(\E) = \Pio(\E_1) \circ \Pio(\E_2)$.
-%    \end{enumerate}
-%We call $\R'$ a \emph{contravariant fragment} of $\R$.
-%\end{definition}
-%The use of covariant and contravariant in~\cref{def:covproj,def:contraproj} refers to the direction of implication between the two pre-orders and operation compositions\footnote{Note that strictly these are not projections in the sense of $\Pi^2 = \Pi$, but are instead morphisms.
-%Here our use of the term projection is motivated by the idea that one one generally loses information about $\R$ under the mapping.}.
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Outlook}
-\label{sec:outlook}
-
 In this work we have looked at magic through the lens of thermodynamics. Specifically, we find that it can be viewed as a strictly non-classical form of non-equilibrium free energy.

### 2021-04-21 magic_paper.tex
Removed errors, started discussion on max-thauma, need to include numerical majorisation bounds and perhaps other magic state conversions

--- 2021-04-21 magic_paper.tex
@@
 
-Similar upper bounds on distillation rates for qudits of odd prime dimension include the mana bound~\cite{cit:veitch} and the max--thauma bound~\cite{Wang_2020} which is defined via a semi-definite program, but possesses properties that allow for an easy comparison with our bound.
+Similar upper bounds on distillation rates for qudits of odd prime dimension include the mana bound~\cite{cit:veitch} and the max--thauma bound~\cite{Wang_2020} which can be defined as
+\begin{equation}
+	\theta_{\rm{max}}(\rho) \coloneqq \log_2{\min{\{2\hspace{1pt}\sn{V}+1 : V \geq \rho\}}}
+\end{equation}
+and can be calculated numerically via a semi-definite program.
+
 The mana bound can be directly calculated as
@@
 \end{equation}
-Using the max--thauma properties of super-additivity and vanishing at free states, we obtain
-\begin{align}
-	&\theta_{\rm{max}}(\rho_{\rm{S}}(\epsilon)) \geq (1-\epsilon) \theta_{\rm{max}}(\ketbra{\rm{S}}) + \epsilon \theta_{\rm{max}}\left(\frac{1}{3}\id \right) = \nonumber\\
-	&(1-\epsilon) \theta_{\rm{max}}(\rho_{\rm{S}}(0)),
-\end{align}
-so that for a deterministic single-copy distillation process, an initial number of copies $n \geq \theta_{\rm{max}}(\tau) / \theta_{\rm{max}}(\rho) \geq 1-\epsilon$ is required.
-Therefore, the max--thauma bound for the pure Strange state distillation process can get as tight as \nick{CALCULATING THAUMA EXACTLY AT THE MOMENT}
-\begin{equation}
-	R = \frac{1}{n} = \frac{\theta_{\rm{max}}(\rho_{\rm{S}}(\epsilon))}{\theta_{\rm{max}}(\rho_{\rm{S}}(0))} \leq 1-\epsilon.
-\end{equation}
-
-Both the mana and the max--thauma bounds are looser than the majorization bound we derived via the first elbow constraint as illustrated in~\cref{fig:distill_bounds}.
-
-In the next section we provide relative majorization bounds in arbitrary stabilizer fragments, and in particular we shall parameterize these bounds from a thermodynamic perspective.
-Specifically, we can interpret the stabilizer state $\sigma$, which defines the fragment, as a thermodynamic equilibrium state at some effective temperature and with some effective Hamiltonian.
+For the noisy Strange state, the max-thauma bound coincides with the mana bound, and are both looser than the majorization bound we derived via the first elbow constraint as illustrated in~\cref{fig:distill_bounds}.
 \begin{figure}[t]
@@
 \end{figure}
+
+I include in~\cref{fig:test} the purification of Norrell states and the purification of $T$ states.\nick{Need to include numerical majorization curves to compare, extend noise range.}
+
+\begin{figure}[h]
+    \centering
+    \subfigure[][]{%
+    \label{fig:norrell}%
+    \includegraphics[height=3cm]{figs/compare_norrell.pdf}
+    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
+    }\hspace{8pt}%
+    \subfigure[][]{%
+    \label{fig:tstate}%
+    \includegraphics[height=3cm]{figs/compare_tstate.pdf}}
+    \caption{\textbf{Bound comparison} 
+    \subref{fig:norrell} Norrell state purification; \subref{fig:tstate} $T$ state purification;
+    }%
+    \label{fig:test}
+\end{figure}
+
+In the next section we provide relative majorization bounds in arbitrary stabilizer fragments, and in particular we shall parameterize these bounds from a thermodynamic perspective.
+Specifically, we can interpret the stabilizer state $\sigma$, which defines the fragment, as a thermodynamic equilibrium state at some effective temperature and with some effective Hamiltonian.
 

### 2021-04-21 magic_paper.tex

--- 2021-04-21 magic_paper.tex
@@
 \end{equation}
-
-Both the mana and the max--thauma bounds are looser than the majorization bound we derived via the first elbow constraint as illustrated in~\cref{fig:distill_bounds}.
-
-In the next section we provide relative majorization bounds in arbitrary stabilizer fragments, and in particular we shall parameterize these bounds from a thermodynamic perspective.
-Specifically, we can interpret the stabilizer state $\sigma$, which defines the fragment, as a thermodynamic equilibrium state at some effective temperature and with some effective Hamiltonian.
+For the noisy Strange state, the max-thauma bound coincides with the mana bound, and are both looser than the majorization bound we derived via the first elbow constraint as illustrated in~\cref{fig:distill_bounds}.
 \begin{figure}[t]

### 2021-04-21 magic_paper.tex
minor adjustment

@@
 \end{equation}
-For the noisy Strange state, the max-thauma bound coincides with the mana bound, and are both looser than the majorization bound we derived via the first elbow constraint as illustrated in~\cref{fig:distill_bounds}.
+For the noisy Strange state, the max--thauma bound coincides with the mana bound, and are both looser than the majorization bound we derived via the first elbow constraint as illustrated in~\cref{fig:distill_bounds}.
 \begin{figure}[t]
@@
     \includegraphics[scale=0.45]{figs/distill_bounds.pdf}
-    \caption{\textbf{Distillation bounds in the unital fragment.} Distillation bounds obtained by majorisation, mana and the line $1-\epsilon$ (tightest bound of max--thauma) are plotted for $\epsilon' = 0$, up to noise level $\epsilon = 3/7$.
+    \caption{\textbf{Distillation bounds in the unital fragment.} Distillation bounds obtained by the first elbow majorisation constraint, mana and max--thauma are plotted for $\epsilon' = 0$, up to noise level $\epsilon = 3/7$.
     Majorisation provides stricter rates than the global mana and max--thauma bounds.
@@
 
-I include in~\cref{fig:test} the purification of Norrell states and the purification of $T$ states.\nick{Need to include numerical majorization curves to compare, extend noise range.}
+I include in~\cref{fig:test} the mana and max--thauma bounds for the purification of (a) Norrell states and (b) $T$ states.
+\nick{Need to include numerical majorization curves to compare, extend noise range.}
 

### 2021-04-22 magic_paper.tex
Added core diagram in intro. How do we embellish it?

@@
 Finally, we discuss how our approach could be improved and how it can be exploited to construct explicit lower bounds on distillation that take into account physical structure.
+
+\begin{figure}[t]
+    \centering
+        \includegraphics[scale=0.4]{figs/protocol_diagram.pdf}
+    \caption{\textbf{Action of a magic protocol} 
+	A magic protocol aims to turn $n$ copies of some magic state $\rho_1$ to $m$ copies of some other state $\rho_2$.
+	Constraints on the efficiency of the protocol can be imposed by considering its action on an equilibrium state $\tau$.
+	\nick{How do we improve the illustration?}
+    }
+    \label{fig:zoo}
+\end{figure}
 
@@
     \centering
-        \includegraphics[scale=0.3
-        ]{figs/operations.pdf}
+        \includegraphics[scale=0.3]{figs/operations.pdf}
     \caption{\textbf{Decomposition of a magic theory $\R$ into $\sigma$--fragments.} 

### 2021-04-25 magic_paper.tex
probably scrap further state conversion comparisons with thauma max?

@@
 \end{equation}
-and can be calculated numerically via a semi-definite program.
+and can be calculated numerically via a semi-definite program\footnote{Provided as supplemental material with~\cite{Wang_2020}}.
 
@@
 I include in~\cref{fig:test} the mana and max--thauma bounds for the purification of (a) Norrell states and (b) $T$ states.
-\nick{Need to include numerical majorization curves to compare, extend noise range.}
+\nick{Delete this probably?}
 
@@
     \caption{\textbf{Bound comparison} 
-    \subref{fig:norrell} Norrell state purification; \subref{fig:tstate} $T$ state purification;
+    \subref{fig:norrell} Norrell state purification; \subref{fig:tstate} $T$ state purification; \nick{Delete this probably?}
     }%

### 2021-04-25 magic_paper.tex
Subsection analysis added that extends results beyond stabilizer Hamiltonians. Looks pretty general now.

--- 2021-04-22 magic_paper.tex
@@
 In each of these combinations, we simply use the first elbow constraint, as described in~\cref{app:elb_constraints}, which leads to the bounds in the statement of the theorem.
-%\begin{enumerate}
-%	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} = E_s$ or $E_{\rm{max}} > E_s$, $\beta < \beta_{\star}$ and $\epsilon' < \epsilon  \leq \epsilon_{\star}$.
-%	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} > E_s$, $\beta < \beta_{\star}$ and $\epsilon' \leq \epsilon_{\star} < \epsilon$.
-%	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $E_{\rm{max}} > E_s$, $\beta < \beta_{\star}$ and $\epsilon_{\star} \leq \epsilon' < \epsilon$ or $E_{\rm{max}} > E_s$, $\beta \geq \beta_{\star}$.
-%\end{enumerate}
-%The scenario $\rm{(C1)} \rightarrow \rm{(C2)}$ is not considered as it would correspond to $\epsilon \leq \epsilon_\star < \epsilon'$, which would imply that the output magic state is noisier than the input state.
-%Substituting $\epsilon' = 0$ into these expressions leads to the stated distillation bounds.
-
 \end{proof}
+
+\ddd{\subsection{Improving our abilities to include arbitrary output stabilizer states.}
+The existing analysis works fine when the state $\tau'$ has stabilizer eigendecomposition (i.e.
+it's orthonormal basis is along the stabilizer directions...e.g.
+along $|0\>\<0|, |1\>\<1|$ in the Bloch sphere for a qubit).
+However it can lie inside the stabilizer polytope but not have such an eigenbasis.
+Therefore we'd like to include this fully general possibility.}
+
+To do this we just need to analyse how the properties of the output state relate to the magnitudes of its Wigner components.
+Here let $\tau$ be a single full-rank stabilizer qutrit state -- we are really interested in the output state $\tau'$ but let's ignore primes for now....they just clutter expressions unnecessarily.
+For simplicity denote the Wigner components of the magic state as
+\begin{equation}
+\w = (-v, u,u,u,u,u,u,u,u),
+\end{equation}
+and we index from $i=0$ to $i=7$, so that e.g. $w_0 = -v$ and $w_i = u$ for $i \ne 0$. Let $\t$ denote the Wigner distribution for $\tau$, so that
+\begin{equation}
+\t = (t_0, t_1,t_2, t_3, t_4,t_5,t_6,t_7),
+\end{equation}
+and we assume that $t_i >0$ for all $i$.
+We also note that using Clifford unitaries we can always choose to shift either the smallest entry of $\t$ or the largest entry of $\t$ to the $i=0$ slot.
+We might need to exploit this in a moment.
+
+The rescaled distribution is then $\tilde{\w}:= (w_i/t_i)$, and we define $v_0 := v/t_0$ and $u_i := u/t_i$ for $i\ne 0$.
+We now need to consider the $n$--copy version of this, denoted $\tilde{\w}^{\otimes n}$, and determine how the largest component arises.
+A general component of $\tilde{\w}^{\otimes n}$ is given by,
+\begin{equation}
+\tilde{w}_{n,\alpha, i_1, \dots, i_8} = (-v_0)^{i_0} u_1^{i_1} u_2^{i_2} \cdots u_8^{i_8},
+\end{equation}
+with the assumption that firstly $n$ is always even, and the indices obeying the following conditions:
+\begin{align}
+0 &\le i_j \le n \mbox{ for each }j=0,1,\dots ,8 \nonumber \\
+i_0+ i_1 &+ i_2 + \dots i_8 =n.
+\end{align}
+Now the largest entry must be positive, and so we require that $\alpha$ is an even number, and so we consider
+\begin{equation}
+\tilde{w}_{n,i_0, i_1, \dots, i_8} = v_0^{i_0} u_1^{i_1} u_2^{i_2} \cdots u_8^{i_8},
+\end{equation}
+over the above integers with $i_0 \in \{0,2,4, \dots, n\}$.
+Let $a = \max \{v_0, u_1, \dots ,u_8\}$, then clearly the maximum value attained ($\tilde{w}_{\rm max}:= \max_{i_0,i_1,\dots , i_8}(\tilde{w}_{n,i_0, i_1, \dots, i_8})$ ) is given by
+\begin{equation}
+\tilde{w}_{\rm max} = a^n.
+\end{equation}
+If the numbers $\{v_0, u_1, u_2, \dots, u_8\}$ are distinct then this maximum value occurs at a unique $i_k=n$ for some $k \in \{0, 1, \dots, 8\}$. Let's consider this case first.
+
+\textbf{(No multiplicities)} We expect this is the generic case, but I think it always provides a sufficient condition even if multiplicities exist.
+We can assume that noise level is below $3/7$ and so we have that $v >u$, so the $0$ component in $\w$, and so also $\w^{\otimes n}$, is the largest.
+But this needs rescaling by $\t$.
+
+We now make use of the freedom to do a Clifford unitary transformation that sends the smallest entry in $\t$ to the $0$ component.
+Note that in doing so we must also account for this Clifford unitary on the output magic state too!
+To get around this we can simply say that we consider $\rho_S(\epsilon )^{\otimes n} \rightarrow \rho_S(\epsilon')^{\otimes m}$ modulo local Clifford unitaries on the output system.
+This changes the rules of the game to suit our needs.
+Instead of distilling out the precise noisy Strange state, we allow the protocol to have arbitrary post-processing on the individual qutrits via reversible Cliffords.
+I.e.~the magic content is the same in each case, but when we consider the problem of how $\tau \rightarrow \tau'$ this can be used to our advantage to simplify our analysis.
+Need to reflect on this variant and how it affects the content of our result.
+
+So given the ability to assume that the smallest entry of $\t$ is the $t_0$ component this means that for noise levels below $3/7$ the largest component of $\tilde{w}_{n,i_0, i_1, \dots, i_8}$ occurs at $(i_0,i_1, \dots, i_8) = (n,0,0,\dots ,0)$.
+We therefore have, for the no-multiplicity case, that the first elbow occurs at the point $(t_0^n, v^n)$.
+This will lead to a bound expression in terms of $\epsilon$ for the output state, together with whatever value $t_0$ takes on.
+\ddd{[give expression]}.
+While this is fine, we need to link $t_0$ to the physics of the state $\tau = e^{-\beta H}/\Z$.
+Well, just from the definition we have that
+\begin{equation}
+t_0 = \frac{1}{d\Z}\tr [ A_{0,0} e^{-\beta H}],
+\end{equation}
+where, of course, $d=3$. So in $t_0^n$ we immediately get a term $\Z^{-n} = e^{-nF}$, which is nice and general. Using the expansion of the thermal state into its energy eigenstates we obtain
+\begin{align}
+t_0^n &= \left ( \frac{1}{d\Z}\tr [ A_{0,0} e^{-\beta H}] \right )^n \nonumber \\
+&= \frac{e^{-nF}}{3^n} ( \tr [ A_{0,0} \sum_k e^{-\beta E_k} |\varphi_k\>\<\varphi_k|])^n\nonumber \\
+&= \frac{e^{-nF}}{3^n} ( \sum_k \alpha_k e^{-\beta E_k})^n,
+\end{align}
+where we define
+\begin{equation}
+\alpha_k := \<\varphi_k |A_{0,0} |\varphi_k\>, \mbox{ for }k=0,1,2.
+\end{equation}
+However $A_{0,0} = \sum_{r\in \mathbb{Z}_3} | -r\>\<r|$ and so
+\begin{equation}
+\alpha_k := \sum_{r \in \mathbb{Z}_3} \<\varphi_k |-r\> \<r |\varphi_k\>.
+\end{equation}
+This just encodes how the energy eigenbasis of the Hamiltonian $H$ relates to the \emph{stabilizer} basis.
+Anyhow, the nice thing is that we always get the Free energy term emerging in the $t_0^n$ and so we can include this into the distillation bound, with the $\alpha_k$ terms simply handling the messy issue of how the two important bases relate.
+We can package the messy details into some definition in some way.
+E.g.
+the form of the sum involving $\alpha_k$ looks a bit like a partition function, so we can define something like
+\begin{equation}
+\zeta :=  \sum_k \alpha_k e^{-\beta E_k},
+\end{equation}
+so that
+\begin{equation}
+t_0^n = \frac{e^{-nF}}{3^n}\zeta^n,
+\end{equation}
+which is tidy....and we could also then define $\phi$ as a kind of free energy term via $\zeta =: e^{-\beta \phi}$. This then simplifies things to
+\begin{equation}
+t_0^n =  \frac{e^{-n(F+\phi)}}{3^n},
+\end{equation}
+where $F$ corresponds to the physical free energy of $\tau$ while $\phi$ is some weird term that captures the degree to which the energy basis differs from the stabilizer basis.
+\ddd{[Details need tidying/checking and we need the final bounds to be computed.]}
+
+\textbf{(Multiplicity case)} I don't think we really need to delve into this.
+Firstly no multiplicities will be generic.
+Secondly, if multiplicities appear this simply means the above Lorenz curve point is not an elbow but instead as point on the first line segment.
+Imposing the conditions for this point is \emph{also a necessary condition} and therefore suffices to get a bound.
 

### 2021-04-26 magic_paper.tex
Typo corrected. Missing \beta terms
added numerical bounds and discussion

@@
 For the noisy Strange state, the max--thauma bound coincides with the mana bound, and are both looser than the majorization bound we derived via the first elbow constraint as illustrated in~\cref{fig:distill_bounds}.
+Numerical, ``optimal'', bounds $R_{\rm{opt}}$ obtained by considering the entirety of the Lorenz curves have been included in the plot as well, highlighting that the first elbow constraint does not capture the full capabilities of majorization.
+Notably, and in contrast with the first elbow, mana and max--thauma bounds, $R_{\rm{opt}}$ depends on the copies $m,n$, in the sense that it doesn't bound their ratio $m/n$, but it is specific to the process.
 \begin{figure}[t]
@@
     Majorisation provides stricter rates than the global mana and max--thauma bounds.
+    Numerical bounds $R_{\rm{opt}}$ obtained by full Lorenz curve comparison for some processes with even number of copies up to 30 are also plotted illustrating that the first elbow constraint can be improved.
     }
     \label{fig:distill_bounds}
-\end{figure}
-
-I include in~\cref{fig:test} the mana and max--thauma bounds for the purification of (a) Norrell states and (b) $T$ states.
-\nick{Delete this probably?}
-
-\begin{figure}[h]
-    \centering
-    \subfigure[][]{%
-    \label{fig:norrell}%
-    \includegraphics[height=3cm]{figs/compare_norrell.pdf}
-    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
-    }\hspace{8pt}%
-    \subfigure[][]{%
-    \label{fig:tstate}%
-    \includegraphics[height=3cm]{figs/compare_tstate.pdf}}
-    \caption{\textbf{Bound comparison} 
-    \subref{fig:norrell} Norrell state purification; \subref{fig:tstate} $T$ state purification; \nick{Delete this probably?}
-    }%
-    \label{fig:test}
 \end{figure}
@@
 \end{equation}
-where, of course, $d=3$. So in $t_0^n$ we immediately get a term $\Z^{-n} = e^{-nF}$, which is nice and general. Using the expansion of the thermal state into its energy eigenstates we obtain
+where, of course, $d=3$. So in $t_0^n$ we immediately get a term $\Z^{-n} = e^{-n\beta F}$, which is nice and general. Using the expansion of the thermal state into its energy eigenstates we obtain
 \begin{align}
 t_0^n &= \left ( \frac{1}{d\Z}\tr [ A_{0,0} e^{-\beta H}] \right )^n \nonumber \\
-&= \frac{e^{-nF}}{3^n} ( \tr [ A_{0,0} \sum_k e^{-\beta E_k} |\varphi_k\>\<\varphi_k|])^n\nonumber \\
-&= \frac{e^{-nF}}{3^n} ( \sum_k \alpha_k e^{-\beta E_k})^n,
+&= \frac{e^{-n\beta F}}{3^n} ( \tr [ A_{0,0} \sum_k e^{-\beta E_k} |\varphi_k\>\<\varphi_k|])^n\nonumber \\
+&= \frac{e^{-n \beta F}}{3^n} ( \sum_k \alpha_k e^{-\beta E_k})^n,
 \end{align}
@@
 \begin{equation}
-t_0^n = \frac{e^{-nF}}{3^n}\zeta^n,
+t_0^n = \frac{e^{-n\beta F}}{3^n}\zeta^n,
 \end{equation}
@@
 \begin{equation}
-t_0^n =  \frac{e^{-n(F+\phi)}}{3^n},
+t_0^n =  \frac{e^{-n \beta (F+\phi)}}{3^n},
 \end{equation}

### 2021-04-26 magic_paper.tex
Fixed figures, added comments before newest section to return to later

@@
     \centering
-    \includegraphics[height=4.5cm]{figs/lc_Strange.pdf}
+    \includegraphics[scale=0.35]{figs/lc_strange.pdf}
     \caption{\textbf{A `heretical' family of Lorenz curves.} Traditionally, Lorenz curves for distributions are monotone increasing cumulant functions that reach a maximum value of $1$.
 In contrast, Lorenz curves for magic states break through the value of $L(x)=1$ due to the presence of negativity in the associated quasi-probability distributions.
-The above family of curves correspond to multiple copies of noisy Strange states $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ (\cref{eq:noisysn}) for $n=1,2,3,4$ within a particular stabilizer fragment.
+The above family of curves correspond to multiple copies of noisy Strange states $\rho:=\rho_{\rm{S}}(\epsilon)^{\otimes n}$ (\cref{eq:noisysn}) for $n=2,4,6$ within a particular stabilizer fragment ($\sigma = \id/3$).
 Solid lines represent pure Strange states, while dashed lines represent noisy Strange states with depolarising noise ($\epsilon = 0.1$).
@@
 Numerical, ``optimal'', bounds $R_{\rm{opt}}$ obtained by considering the entirety of the Lorenz curves have been included in the plot as well, highlighting that the first elbow constraint does not capture the full capabilities of majorization.
-Notably, and in contrast with the first elbow, mana and max--thauma bounds, $R_{\rm{opt}}$ depends on the copies $m,n$, in the sense that it doesn't bound their ratio $m/n$, but it is specific to the process.
+Notably, in contrast to the other bounds, $R_{\rm{opt}}$ depends explicitly on the copies $m,n$, rather than their ratio $m/n$, so it is specific to the process.
+An interesting question arises regarding the value of $R_{\rm{opt}}$ as $n,m \rightarrow \infty$, while $m/n$ remains constant.
 \begin{figure}[t]
@@
     Majorisation provides stricter rates than the global mana and max--thauma bounds.
-    Numerical bounds $R_{\rm{opt}}$ obtained by full Lorenz curve comparison for some processes with even number of copies up to 30 are also plotted illustrating that the first elbow constraint can be improved.
+    Numerical bounds $R_{\rm{opt}}$ obtained by full Lorenz curve comparison for some Strange state purification processes with even number of copies $m,n \leq 30$ highlight that the first elbow constraint can be improved.
     }
@@
 We do this relative to a reference temperature that can be chosen freely.
-The key ideas is that the physical measures associated with this protocol are determined by how $\E$ would disturb this reference equilibrium state $\tau$ to some different state $\tau'$, if the protocol had been applied to this reference state instead of the $n$-copy magic state.
+The key idea is that the physical measures associated with this protocol are determined by how $\E$ would disturb a reference equilibrium state $\tau$ to some different state $\tau'$, if the protocol had been applied to this reference state instead of the $n$-copy magic state.
 
@@
 \end{equation}
-Since we are concerned with magic distillation we may assume that the reference state $\tau$ is not a magic state, and so has non-negative Wigner distribution, and we shall assume that it is a full-rank stabilizer state for the qudit.
+Since we are concerned with magic distillation we may assume that the reference state $\tau$ is not a magic state, so it has a non-negative Wigner distribution, and we shall further assume that it is a full-rank stabilizer state for the qudit.
 
@@
 We first note that we can assume without loss of generality that $U_\pi\E(X) U_\pi^\dagger = \E(X)$ for all $X$ and any permutation $U_\pi$ of the $m$ output subsystems.
-The reason for this is that the protocol on the noisy magic state outputs the state $\rho(\epsilon')^{\otimes m}$, which is invariant under permutations, and so we can therefore always symmetrise by performing a group average over the permutation group for the output systems without changing the performance of the distillation protocol on $\rho(\epsilon)^{\otimes n}$.
+This is justified because the protocol on the input magic state results in state $\rho(\epsilon')^{\otimes m}$, which is invariant under permutations.
+Therefore, we are always allowed to symmetrise the output $\E(X)$ by performing a group average over the permutation group for the output systems without changing the performance of the distillation protocol on $\rho(\epsilon)^{\otimes n}$.
 Thus, we can assume that $\E$ always outputs a symmetric state in general.
 
-This means in particular that $\E(\tau^{\otimes n}) = \tau'$ is a symmetric state on $m$ subsystems, and so by the quantum de Finetti theorem~\cite{christandl_2007} we have that
+This means in particular that $\E(\tau^{\otimes n}) = \tau'$ is a symmetric state on $m$ subsystems, so by the quantum de Finetti theorem~\cite{christandl_2007} we have that
 \begin{equation}
@@
 This implies that $d\mu(x)$ is peaked on a particular state $\sigma$, and so $\tau' = \sigma^{\otimes m}$.
-Physically, this is a natural scenario -- for example in traditional thermodynamics it states that the output system is well-described by intrinsic variables that are encoded in $\sigma$.
-Here this assumption allows us to associate a free energy per qudit for the output state, which would be more complex if correlations are present.
-
-The case of correlations between output subsystems can also be considered, but would lead to a more complex analysis within our majorization analysis of Wigner distributions.
-In this direction we highlight recent work in majorization in which stochastic independence and correlations are analysed.
+Physically, this is a natural scenario -- for example, in the context of traditional thermodynamics, it states that the output system is well-described by intrinsic variables that are encoded in $\sigma$.
+Here, this assumption allows us to associate a free energy per qudit of the output state, which would be more complex if correlations are present.
+
+The case of correlations between output subsystems can also be considered, but would lead to a more complex analysis within our majorization framework of Wigner distributions.
+In this direction, we highlight recent work in majorization in which stochastic independence and correlations are analysed.
 In particular it has been shown that stochastic independence (no correlations) of independent distributions can be viewed as a resource in an extension of catalytic majorization, and leads to a single-shot operational interpretation of the Shannon entropy.
+\nick{CITE}
 
 The action of the protocol on the reference states therefore transforms $\tau \rightarrow \sigma$.
-It turns out our distillation bounds depend on the free energy of the input and output states.
-For a state $\tau = e^{-\beta H}/\Z$ the associated free energy $F$ is given by
+It turns out our distillation bounds depend on the free energy of the input and output states, so for a state $\tau = e^{-\beta H}/\Z$ we express the associated free energy $F$ by
 \begin{equation}
@@
 \begin{theorem}\label{thm:free-energy}
-	Consider a magic distillation protocol transforming noisy Strange state $\rho_S(\epsilon)^{\otimes n} \longrightarrow \E(\rho_S(\epsilon)^{\otimes n})=\rho_S(\epsilon')^{\otimes m}$ with $n, m \gg 1$.
-
-Let each qutrit have a Hamiltonian $H$ with stabilizer eigenstates having energies $E_0, E_1, E_2$, and define $E_{\rm max} = \max\{E_0, E_1, E_2\}$ and $E_s$ the eigenvalue of the eigenstate that overlaps the negative component of $\rho_S(\epsilon)$ in the Wigner representation.
+	Consider a magic distillation protocol transforming noisy Strange state
+	\begin{equation*}
+		\rho_S(\epsilon)^{\otimes n} \longrightarrow \E(\rho_S(\epsilon)^{\otimes n})=\rho_S(\epsilon')^{\otimes m} 
+	\end{equation*}
+	with $n, m \gg 1$.
+
+Let each qutrit have a Hamiltonian $H$ with stabilizer eigenstates and energies $E_0, E_1, E_2$, and define $E_{\rm max} = \max\{E_0, E_1, E_2\}$ and $E_s$ the eigenvalue of the eigenstate that \nick{overlaps} the negative component of $\rho_S(\epsilon)$ in the Wigner representation.
 Let $T =(k\beta)^{-1}$ be any characteristic temperature for the physical system in the state $\tau^{\otimes n}= (e^{-\beta H}/\Z)^{\otimes n}$, with free energy $F$.
@@
 
-Define $\beta_\star = 1/kT_\star$ through the relation
+Define $\beta_\star = (k T_\star)^{-1}$ through the relation
 \begin{equation}
@@
 	\begin{cases}
-		3 - \dfrac{18}{8-2^{\beta/\beta_\star}}, &\text{ for } \beta \leq \beta_\star \\
+		3 - \dfrac{9}{4-2^{\beta/\beta_\star - 1}}, &\text{ for } \beta \leq \beta_\star \\
 		0, &\text{ for } \beta > \beta_\star.
@@
 \end{equation}
-Then the distillation rate $R = m/n$ of the magic protocol is bounded as:
+Then, the distillation rate $R = m/n$ of the magic protocol is bounded as:
 \begin{equation}\label{eq:rate_bounds_proof}
@@
 		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F')},\ &\epsilon > \epsilon_\star, \epsilon' \leq \epsilon'_\star, \vspace{10pt}\\
-		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F')},\ &\epsilon > \epsilon_\star, \epsilon' > \epsilon'_\star.
+		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F')},\ &\epsilon > \epsilon_\star, \epsilon' > \epsilon'_\star,
 	\end{cases}
 \end{equation}
-Where $F'$ is the free energy of the state $\sigma = e^{-\beta H'}/\Z'$ and other primed quantities are defined in the same way as the corresponding unprimed quantities. 
+where $F'$ is the free energy of the state $\sigma = e^{-\beta H'}/\Z'$ and other primed quantities are defined in the same way as the corresponding unprimed quantities. 
 \end{theorem}
 
-  For example, suppose that $H=H'$ then this implies the protocol would leave the equilibrium state unchanged and so corresponds to a Gibbs-preserving map~\cite{faist_2015}.
-In the more general case $\Delta F := F' - F \ne 0$ and we have a free energy difference between the initial and final times, with respect to the relevant Hamiltonians.
+We note, firstly, that the specific numerical factors in $\epsilon_\star$ are a result of our choice of magic state. 
+Secondly, these bounds are derived based on analysis of only a part of the Lorenz curves and can be improved via a finer analysis. 
+This is apparent by simple numerical calculations on the entirety of the curves as seen in~\cref{fig:distill_bounds} for unital operations.
+Specifically, the existing bounds follow by considering the dominant terms in the rescaled Wigner distribution and do not, for example, take into account the Lorenz curve's peak structure.
+
+As a special case of the result, suppose that $H=H'$, implying that the protocol leaves the equilibrium state unchanged, hence it corresponds to a Gibbs-preserving map~\cite{faist_2015}.
+In the more general case, $\Delta F := F' - F \ne 0$ and we have a free energy difference between the initial and final states, with respect to the relevant Hamiltonians.
 This is similar to the free energy differences that occur in fluctuation relations, where the final state of the system can be arbitrarily far from equilibrium, yet a free energy term for the final system still arises.
-Firstly, the specific numerical factors in $\epsilon_\star$ are a result of our choice of magic state. 
-Secondly, these bounds are derived based on analysis of only a part of the Lorenz curves and can be improved via a finer analysis. 
-This is apparent by simple numerical calculations on the entirety of the curves.
-Specifically, the existing bounds follow by considering the dominant terms in the rescaled Wigner distribution and do not, for example, take into account the Lorenz curve's peak structure.
 
@@
 However to unpack the results more it is useful to consider the case in which $H=H'$, and look at $\epsilon' \rightarrow 0$.
-For this we obtain Figure \ref{contour-bounds} which gives a contour plot of $R$ as a function of inverse temperature $\beta$ and depolarising noise level $\epsilon$ for the initial noisy magic state.
-\begin{figure}[t!]\label{contour-bounds}
+For this we obtain~\cref{fig:rate_contour} which gives a contour plot of $R$ as a function of inverse temperature $\beta$ and depolarising noise level $\epsilon$ for the initial noisy magic state.
+\begin{figure}[t!]
     \centering
-    \includegraphics[scale=0.4]{figs/rate_scatter.pdf}
+    \includegraphics[scale=0.45]{figs/rate_scatter.pdf}
     \caption{\textbf{Temperature-dependent bounds for magic distillation.}
-  Shown is a contour plot of  $R(\epsilon, \beta)$ where $\beta$ is an inverse temperature and $\epsilon$ is the depolarising noise of the magic state.
+  Shown is a contour plot of  $R(\epsilon, \beta)$ for $H=H'$, where $\beta$ is an inverse temperature and $\epsilon$ is the depolarising noise of the magic state.
 The relevant data from the spectrum of the qutrit operator $H$ enters in via $\epsilon_\star(\beta)$ and $\beta_\star$.
@@
 \end{equation}
-for the magic state. We also consider how the protocol transforms the reference equilibrium state as
+for the magic state. We then consider how the protocol transforms the reference equilibrium state as
 \begin{equation}
@@
 \end{equation}
-Since $\tau$ and $\sigma$ are assumed to be full rank stabilizer states they have a strictly positive Wigner distribution, while in contrast the input and output magic states will have quasi-probability distributions for their Wigner functions.
+Since $\tau$ and $\sigma$ are assumed to be full rank stabilizer states they have a strictly positive Wigner distribution, while, in contrast, the input and output magic states will generally have quasi-probability distributions for their Wigner functions.
 For any such protocol we therefore have that
@@
 \end{equation}
-where for simplicity we write $\rho_n := \rho_S(\epsilon)^{\otimes n}$, $\rho'_m:= \rho_S(\epsilon')^{\otimes m}$ and similarly for $\tau_n$ and $\sigma_m$. This therefore implies that
+where for simplicity we write $\rho_n := \rho_S(\epsilon)^{\otimes n}$, $\rho'_m:= \rho_S(\epsilon')^{\otimes m}$ and $\tau_n:=\tau^{\otimes m}$ and $\sigma_m:=\sigma^{\otimes m}$. We then have that
 \begin{equation}
@@
 
-We define $W_{\rho | \tau}(\x) := W_\rho(\x)/W_\tau(\x)$, which is always well-defined since $\tau$ is full-rank. Now we have that
+We define $W_{\rho | \tau}(\x) := W_\rho(\x)/W_\tau(\x)$, which is always well-defined since $\tau$ is full-rank. Now we show in~\cref{app:wigner} that
 \begin{equation}
@@
 \end{equation}
-for any states $\rho_1, \rho_2$ and any full-rank stabilizer states $\tau_1, \tau_2$. \ddd{[Notation clashing here. Frame result outside as its own lemma -- we gotta check everything.]}
+for any states $\rho_1, \rho_2$ and any full-rank stabilizer states $\tau_1, \tau_2$.
+\ddd{[Notation clashing here.
+Frame result outside as its own lemma -- we gotta check everything.]} \nick{Will frame in~\cref{app:wigner} and fix notation in the next commit}
 Therefore we have that
@@
 The points defining the Lorenz curve $L_{\rho_n |\tau_n}(x)$ are obtained from first sorting the components of $W_{\rho_n |\tau_n}(\x)$ in non-increasing order and then computing the partial sums of $W_{\rho_n |\tau_n}(\pi(\x))$ where $\pi$ is the permutation that realises the sorting.
-Therefore we first look at the values of $W_{\rho|\tau}(\x_i)$ for the single-copy case.
+Therefore, we first look at the values of $W_{\rho|\tau}(\x_i)$ for the single-copy case.
 
@@
 where the eigenstates $\{\ket{\varphi_k}\<\varphi_k|\}$ are pure, orthonormal stabiliser states, which can be represented in terms of generalized Paulis.
-To make our analysis simpler we perform a change of basis that does not affect the Wigner negativity of the problem.
+To make our analysis simpler, we perform a change of basis that does not affect the Wigner negativity of the problem.
 We let $C$ be the unitary transforming each $|\varphi_k\>\<\varphi_k|$ to $|k\>\<k|$.
@@
 The rescaled Wigner distribution $W_{\rho|\tau}(\x)$ is then easily computed.
-It has $9$ components in two, however several of these come with multiplicities.
-In total there are four distinct values on the phase space, as illustrated in the~\cref{fig:pd_split}.
+It has $9$ components, but several of these come with multiplicities.
+In total, there are four distinct values on the phase space, as illustrated in~\cref{fig:pd_split}.
 \begin{figure}[h]
@@
 
-We now denote by $\w(\rho), \w(\rho|\tau)$ the unique values occurring in $W_\rho(\x), W_{\rho|\tau}(\x)$ respectively and $\mathbf{m}$ the vector of associated multiplicities of each value in $W_\rho(\x)$.
+We now denote by $\w(\rho), \w(\rho|\tau)$ the unique values occurring in $W_\rho(\x), W_{\rho|\tau}(\x)$ respectively and $\bmm$ the vector of associated multiplicities of each value in $W_\rho(\x)$.
 The component values and multiplicities of the relevant distributions in the four distinct regions are given by
@@
 
-Generally this is complex, but to obtain distillation bounds we may determin the location of the first elbow $(x_0, L_0)$ of $L_{\rho_n|\tau_n}(\x)$. To do so we compute the largest component 
+Generally this is complex, but in order to obtain distillation bounds it is sufficient to determine the location of the first elbow $(x_0, L_0)$ of $L_{\rho_n|\tau_n}(\x)$.
+To do so, we compute the largest component
 \begin{equation}
@@
 \begin{align}
-	\hspace{-1cm}(3\Z)^{-n}w_{\rm max}= \max\limits_{i,j,k}\Big\{ (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \label{eq:max_slope}
+	&(3\Z)^{-n}w_{\rm max} = \nonumber\\
+	&\max\limits_{i,j,k}\Big\{ (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \label{eq:max_slope}
 \end{align}
@@
 
-\ddd{[Hmmm this needs an additional assumption on the output state to re-run the same analysis. Very annoying.]}
+\ddd{[Hmmm this needs an additional assumption on the output state to re-run the same analysis.
+Very annoying.]}\nick{What additional assumption beyond that the output state can be written as a Gibbs state for some $H'$?}
 Similarly, considering the output magic state with respect to state $\sigma'$, the image of equilibrium state $\sigma$ under the magic protocol, we get output Lorenz curve coordinates,

### 2021-04-28 appendix.tex
Added assumptions, statement of new theorem, altered first elbow condition to match assumptions. Next: Add proof, push technical details to appendix

@@
 \label{app:elb_constraints}
-Here we prove the majorization constraints that arise by only considering the first elbow (on the ascending part of the curves) or the last elbow (on the descending part of the curves) that occurs in any of the two curves.
+Here we prove two simple majorization constraints, one arising by considering only the ascending part of the Lorenz curves between the origin $(0,0)$ and the first elbow and the other by considering only the descending part of the curves between the last elbow and the endpoint $(1,1)$.
 \begin{proposition}\label{prop:first_elb}
-	Consider a magic state process as in~\cref{eq:stdist}, where we denote by $(x_0, L_0)$ and $(x'_0, L'_0)$ the first elbow coordinates of the input and output magic states respectively. 
-	The process is possible only if
+	Consider a magic state process $\rho \longrightarrow \tau$ with input and output Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in $\R_\sigma$ and denote by $X_0, X'_0$ the first elbow locations of the input and output curves respectively.
+
+	Then, given any coordinates $(x_0, L_0)$ and $(x'_0, L'_0)$ on the input and output Lorenz curves, where $x_0 \leq X_0$ and $x'_0 \leq X'_0$, the process is possible in $\R_\sigma$ only if
 \begin{equation}\label{eq:first_elb_bound1}
@@
 \begin{proof}
-	Consider the Lorenz curve constraint at $x = x_0$,
+Since both pairs of coordinates are located between $(0,0)$ and the first elbow of their respective curves, we can derive the bound via a simple interpolation on the line segment connecting the origin and the appropriate first elbow.
+
+First assume that $x_0 < x'_0$ and consider the Lorenz curve constraint at $x = x_0$,
 \begin{equation}
@@
 \end{equation}
-First assume that $x_0 < x'_0$. 
 We can find the output state Lorenz curve coordinate $L'_\star$ at location $x = x_0$ by interpolating between the origin and the output state's first elbow, 
@@
 
-If instead, $x_0 \geq x'_0$, we would need to find the input state Lorenz curve coordinate $L_\star$ at location $x = x'_0$ by interpolating between the origin and the input state's first elbow, 
+If instead, $x_0 \geq x'_0$, consider the Lorenz curve constraint at $x = x'_0$,
+\begin{equation}
+	\lc{\rho}{\sigma}(x'_0) \geq \lc{\tau}{\sigma}(x'_0).
+\end{equation}
+We now need to find the input state Lorenz curve coordinate $L_\star$ at location $x = x'_0$ by interpolating between the origin and the input state's first elbow, 
 \begin{equation}
@@
 \begin{proposition}\label{prop:last_elb}
-	Consider a magic state process as in~\cref{eq:stdist}, where we denote by $(x_E, L_E)$ and $(x'_E, L'_E)$ the last elbow coordinates of the input and output magic states respectively.
-	The process is possible only if
+	Consider a magic state process $\rho \longrightarrow \tau$ with input and output Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in $\R_\sigma$ and denote by $X_E, X'_E$ the last elbow locations of the input and output curves respectively.
+
+	Then, given any coordinates $(x_E, L_E)$ and $(x'_E, L'_E)$ on the input and output Lorenz curves, where $x_E \geq X_E$ and $x'_E \geq X'_E$, the process is possible in $\R_\sigma$ only if
 \begin{equation}\label{eq:last_elb_bound1}
@@
 \begin{proof}
-	Consider the Lorenz curve constraint at $x = x_E$,
+Since both pairs of coordinates are located between the last elbow of their respective curves and $(1,1)$, we can derive the bound via a simple interpolation on the line segment connecting the endpoint and the appropriate last elbow.
+
+First assume that $x_E > x'_E$ and consider the Lorenz curve constraint at $x = x_E$,
 \begin{equation}
@@
 \end{equation} 
-First assume that $x_E > x'_E$. 
-We can find the output state Lorenz curve coordinate $L'_\star$ at location $x = x_E$ by interpolating between the end-point $(1,1)$ and the output state's last elbow, 
+We can find the output state Lorenz curve coordinate $L'_\star$ at location $x = x_E$ by interpolating between the endpoint $(1,1)$ and the output state's last elbow, 
 \begin{equation}
@@
 
-If instead, $x_E \leq x'_E$, we would need to find the input state Lorenz curve coordinate $L_\star$ at location $x = x'_E$ by interpolating between the end-point $(1,1)$ and the input state's last elbow,
+If instead, $x_E \leq x'_E$, consider the Lorenz curve constraint at $x = x'_E$,
+\begin{equation}
+	\lc{\rho}{\sigma}(x'_E) \geq \lc{\tau}{\sigma}(x'_E).
+\end{equation} 
+We now need to find the input state Lorenz curve coordinate $L_\star$ at location $x = x'_E$ by interpolating between the endpoint $(1,1)$ and the input state's last elbow, 
 \begin{equation}

### 2021-04-28 magic_paper.tex
Added assumptions, statement of new theorem, altered first elbow condition to match assumptions. Next: Add proof, push technical details to appendix

@@
 % Write bounds as 1 + ln{}/{} or 1 - (-ln{})/{} ?
-% Sec: General resources
-% Sec: Lower bounds
-% App: D clean-up + d--> r ?
-
-% Figs consistency (esp. figs 3,4,5 and 1,6) + Figure 0 ?
-
+% R: rate vs bound ?
+% Appendices: clean-up (d --> r)
+
+% Figs check(fig.0, move to app, consistency)
 % Eq. numbering in last line always
@@
 Given a vector $\w$ we define $\w^\downarrow$ to be the re-arrangement of the components of $\w$ into decreasing order.
-Given two $n$--component vectors $\w$ and $\r$, we first define $\widetilde{\w}$, where $\widetilde{w}_i := w_i/r_i$, as the vector of component-wise ratios between $\w$ and $\r$.
+Given two $n$--component vectors $\w$ and $\r$, we first define $\widetilde{\w}$, where $\widetilde{w}_i \coloneqq w_i/r_i$, as the vector of component-wise ratios between $\w$ and $\r$.
 We can now define the \emph{Lorenz curve} of $\w$ relative to $\r$, denoted $L_{\w|\r}(x)$, as the piece-wise linear function that passes through $(0,0)$ and the $n$ points
@@
 \end{equation}
-where $R:= \sum_{i=1}^n r_i$ and $\pi$ is the permutation on $n$ objects mapping $\widetilde{\w}$ to $\widetilde{\w}^{\downarrow}$.
+where $R\coloneqq \sum_{i=1}^n r_i$ and $\pi$ is the permutation on $n$ objects mapping $\widetilde{\w}$ to $\widetilde{\w}^{\downarrow}$.
 The form of this requires that $\r$ has no zero components, which we shall assume without loss of generality as in any physical situation the rank of a quantum state is not an operationally meaningful quantity.
@@
 In contrast, Lorenz curves for magic states break through the value of $L(x)=1$ due to the presence of negativity in the associated quasi-probability distributions.
-The above family of curves correspond to multiple copies of noisy Strange states $\rho:=\rho_{\rm{S}}(\epsilon)^{\otimes n}$ (\cref{eq:noisysn}) for $n=2,4,6$ within a particular stabilizer fragment ($\sigma = \id/3$).
+The above family of curves correspond to multiple copies of noisy Strange states $\rho\coloneqq\rho_{\rm{S}}(\epsilon)^{\otimes n}$ (\cref{eq:noisysn}) for $n=2,4,6$ within a particular stabilizer fragment ($\sigma \coloneqq \id/3$).
 Solid lines represent pure Strange states, while dashed lines represent noisy Strange states with depolarising noise ($\epsilon = 0.1$).
@@
 
-More precisely, since the components of $\r$ are strictly positive, there always exists an $\epsilon >0$ such that $\w_\epsilon := \epsilon \w + (1-\epsilon) \r$ is a genuine probability distribution.
+More precisely, since the components of $\r$ are strictly positive, there always exists an $\epsilon >0$ such that $\w_\epsilon \coloneqq \epsilon \w + (1-\epsilon) \r$ is a genuine probability distribution.
 We can see that $(\w , \r) \succ (\w', \r')$ if and only if $(\w_\epsilon , \r) \succ (\w_\epsilon', \r')$, where we choose $\epsilon$ so that both $\w_\epsilon$ and $\w_\epsilon'$ are probability distributions.
@@
 \begin{proof}
-	The sum-negativity of a magic state $\rho$ can be written as $sn(\rho) := \frac{1}{2} (\sum_{\x} |W_\rho(\x) | - 1)$.
+	The sum-negativity of a magic state $\rho$ can be written as $sn(\rho) \coloneqq \frac{1}{2} (\sum_{\x} |W_\rho(\x) | - 1)$.
 We make use of a variant form of relative majorization, (see~\cref{prop:rmajor} in~\cref{app:major}), stating that $\p \succ_{\r} \q$ if and only if
@@
 \begin{equation}
-|S\> := \frac{1}{\sqrt{2}} (|1\> + |2\>),
+|S\> \coloneqq \frac{1}{\sqrt{2}} (|1\> + |2\>),
 \end{equation}
@@
 
+As it is important for the statement of our result, we hasten to note that group averaging of the output system and, indeed, any permutation of the output subsystems can be performed via Clifford unitaries, for example $\rm{SWAP}$ gates, which do not affect the magic output of the protocol, so we consider distillation protocols \emph{modulo Clifford operations}.
+
 This means in particular that $\E(\tau^{\otimes n}) = \tau'$ is a symmetric state on $m$ subsystems, so by the quantum de Finetti theorem~\cite{christandl_2007} we have that
@@
 In particular it has been shown that stochastic independence (no correlations) of independent distributions can be viewed as a resource in an extension of catalytic majorization, and leads to a single-shot operational interpretation of the Shannon entropy.
-\nick{CITE}
-
-The action of the protocol on the reference states therefore transforms $\tau \rightarrow \sigma$.
-It turns out our distillation bounds depend on the free energy of the input and output states, so for a state $\tau = e^{-\beta H}/\Z$ we express the associated free energy $F$ by
+\nick{cite David?}
+
+The action of the protocol on the reference state therefore transforms $\tau^{\otimes n} \rightarrow \E(\tau^{\otimes n}) = \sigma^{\otimes m}$. 
+The output state $\sigma$ is a stabilizer state, provided that $\tau$ is as well and that $\E$ is a free operation, but it is generally a non-equilibrium state for the system.
+However, the distillation bounds that we derive take a particularly simple form if we associate a fiducial Hamiltonian $H'$ to the output state by considering the change $H \rightarrow H'$ such that equilibrium is restored at the reference temperature $T$.
+This allows us to express the state as $\sigma = e^{-\beta H'}/\Z'$.
+
+Our distillation bounds depend on two properties of the Hamiltonians $H, H'$.
+The first property is the free energy of the states at the reference temperature, so for a state $\tau = e^{-\beta H}/\Z$ we express the associated free energy $F$ as
 \begin{equation}
@@
 \end{equation}
-The output state $\sigma$ is generally a non-equilibrium state for the system.
-However, the distillation bound takes a particularly simple form if we associate a similar free energy value to the output state.
-We do this by considering the change in Hamiltonian $H \rightarrow H'$ such that equilibrium is restored at the reference temperature $T$.
-This implies that
-\begin{equation}
-\sigma = \frac{e^{-\beta H'}}{\Z'},
-\end{equation}
-which has free energy $F' = -\beta^{-1} \log \Z'$.
-Therefore the action of $\E$ sending $\tau$ to $\sigma$ is viewed in terms of $\Delta H := H'-H$, which is the Hamiltonian change that would be needed to adiabatically restore equilibrium at temperature $T$.
-
- Given this account of the physical ingredients of a distillation protocol we now state the following result for the case of qutrits.
+The output state $\sigma$ then has free energy $F' = -\beta^{-1} \log \Z'$.
+
+The bounds also depend on the overlaps between the Hamiltonian eigenbases and the computational basis $\{\ket{k}\}$, where $k \in \mathbb{Z}_d$.
+For a reference state $\tau$ with associated Hamiltonian $H$ denote the energy eigenbasis by $\{\ket{\phi_k}\}$ and define the \emph{reference partition function $\zeta$} as
+\begin{equation}
+	\zeta \coloneqq \sum_{k \in \mathbb{Z}_d} \alpha_k e^{-\beta E_k},
+\end{equation}
+where the overlap coefficients are
+\begin{equation}
+	\alpha_k \coloneqq \sum_{\mathbb{Z}_d} \braket{\phi_k}{-r}\braket{r}{\phi_k}.
+\end{equation}
+Coefficients $\alpha_k$ are not necessarily positive, which is the case when the Hamiltonian $H$ does not admit a stabilizer decomposition. 
+However, it is simple to see that $\zeta$ is always positive. \nick{because it is proportional to $W_{\tau}(0,0) > 0$ for full-rank, stabilizer $\tau$ - this argument is a bit cyclic}
+We can then naturally associate to the reference state $\tau$ a new form of free energy which is specific to the protocol, which we call the \emph{reference free energy $\Phi$} and define via
+\begin{equation}
+	\Phi \coloneqq -\beta^{-1} \log \zeta.
+\end{equation}
+For the output reference state $\sigma$ with associated Hamiltonian $H'$, we can denote the energy eigenbasis by $\{\ket{\phi'_k}\}$ and similarly define the reference partition function $\zeta'$ and reference free energy $\Phi'$.
+
+Therefore, the action of $\E$ sending $\tau^{\otimes n}$ to $\sigma^{\otimes m}$ is viewed in terms of $\Delta H \coloneqq H'-H$, which is the Hamiltonian change that would be needed to adiabatically restore equilibrium at temperature $T$.
+Given this account of the physical ingredients of a distillation protocol, we now state the following result for the case of qutrits.
+\begin{theorem}\label{thm:free-energy}
+	Consider a magic distillation protocol that transforms the noisy Strange state
+	\begin{equation*}
+		\rho_S(\epsilon)^{\otimes n} \longrightarrow \E(\rho_S(\epsilon)^{\otimes n})=\rho_S(\epsilon')^{\otimes m} 
+	\end{equation*}
+modulo Clifford operations, with even number of copies $n, m$ and noise levels satisfying $\epsilon' \leq \epsilon \leq 3/7$.
+
+Let $T =(k\beta)^{-1}$ be any characteristic temperature for the physical system and let $H$ be the Hamiltonian of each qutrit subsystem.
+Assume that $n,m \gg 1$, so that the channel $\E$ generates negligible correlations on some product equilibrium state 
+\begin{equation}
+	\tau^{\otimes n} \longrightarrow \E(\tau^{\otimes n}) = \sigma^{\otimes m}
+\end{equation} 
+for some state $\sigma = e^{-\beta H'}/\Z'$.
+
+Then, the distillation rate $R = m/n$ of the magic protocol is bounded as:
+\begin{equation}\label{eq:rate_bounds_proof}
+	R \leq \dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (\Phi - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (\Phi' - F')},
+\end{equation}
+where $F, \Phi$ are the free energy and reference free energy defined for state $\tau$, while $F', \Phi'$ are defined for state $\sigma$.
+\end{theorem}
+\begin{proof}
+	\nick{Start}
+\end{proof}
+
 \begin{theorem}\label{thm:free-energy}
@@
 As a special case of the result, suppose that $H=H'$, implying that the protocol leaves the equilibrium state unchanged, hence it corresponds to a Gibbs-preserving map~\cite{faist_2015}.
-In the more general case, $\Delta F := F' - F \ne 0$ and we have a free energy difference between the initial and final states, with respect to the relevant Hamiltonians.
+In the more general case, $\Delta F \coloneqq F' - F \ne 0$ and we have a free energy difference between the initial and final states, with respect to the relevant Hamiltonians.
 This is similar to the free energy differences that occur in fluctuation relations, where the final state of the system can be arbitrarily far from equilibrium, yet a free energy term for the final system still arises.
@@
 \end{equation}
-where for simplicity we write $\rho_n := \rho_S(\epsilon)^{\otimes n}$, $\rho'_m:= \rho_S(\epsilon')^{\otimes m}$ and $\tau_n:=\tau^{\otimes m}$ and $\sigma_m:=\sigma^{\otimes m}$. We then have that
+where for simplicity we write $\rho_n \coloneqq \rho_S(\epsilon)^{\otimes n}$, $\rho'_m\coloneqq \rho_S(\epsilon')^{\otimes m}$ and $\tau_n\coloneqq\tau^{\otimes m}$ and $\sigma_m\coloneqq\sigma^{\otimes m}$.
+We then have that
 \begin{equation}
@@
 
-We define $W_{\rho | \tau}(\x) := W_\rho(\x)/W_\tau(\x)$, which is always well-defined since $\tau$ is full-rank. Now we show in~\cref{app:wigner} that
+We define $W_{\rho | \tau}(\x) \coloneqq W_\rho(\x)/W_\tau(\x)$, which is always well-defined since $\tau$ is full-rank. Now we show in~\cref{app:wigner} that
 \begin{equation}
@@
 \begin{equation}
-	w_{\rm max} := \max_{i,j,k} [\w(\rho_n | \tau_n)]_{ijk},
+	w_{\rm max} \coloneqq \max_{i,j,k} [\w(\rho_n | \tau_n)]_{ijk},
 \end{equation}
@@
 
-The rescaled distribution is then $\tilde{\w}:= (w_i/t_i)$, and we define $v_0 := v/t_0$ and $u_i := u/t_i$ for $i\ne 0$.
+The rescaled distribution is then $\tilde{\w}\coloneqq (w_i/t_i)$, and we define $v_0 \coloneqq v/t_0$ and $u_i \coloneqq u/t_i$ for $i\ne 0$.
 We now need to consider the $n$--copy version of this, denoted $\tilde{\w}^{\otimes n}$, and determine how the largest component arises.
@@
 over the above integers with $i_0 \in \{0,2,4, \dots, n\}$.
-Let $a = \max \{v_0, u_1, \dots ,u_8\}$, then clearly the maximum value attained ($\tilde{w}_{\rm max}:= \max_{i_0,i_1,\dots , i_8}(\tilde{w}_{n,i_0, i_1, \dots, i_8})$ ) is given by
+Let $a = \max \{v_0, u_1, \dots ,u_8\}$, then clearly the maximum value attained ($\tilde{w}_{\rm max}\coloneqq \max_{i_0,i_1,\dots , i_8}(\tilde{w}_{n,i_0, i_1, \dots, i_8})$ ) is given by
 \begin{equation}
@@
 \begin{equation}
-\alpha_k := \<\varphi_k |A_{0,0} |\varphi_k\>, \mbox{ for }k=0,1,2.
+\alpha_k \coloneqq \<\varphi_k |A_{0,0} |\varphi_k\>, \mbox{ for }k=0,1,2.
 \end{equation}
@@
 \begin{equation}
-\alpha_k := \sum_{r \in \mathbb{Z}_3} \<\varphi_k |-r\> \<r |\varphi_k\>.
+\alpha_k \coloneqq \sum_{r \in \mathbb{Z}_3} \<\varphi_k |-r\> \<r |\varphi_k\>.
 \end{equation}
@@
 \begin{equation}
-\zeta :=  \sum_k \alpha_k e^{-\beta E_k},
+\zeta \coloneqq  \sum_k \alpha_k e^{-\beta E_k},
 \end{equation}
@@
 \end{equation}
-which is tidy....and we could also then define $\phi$ as a kind of free energy term via $\zeta =: e^{-\beta \phi}$. This then simplifies things to
+which is tidy....and we could also then define $\phi$ as a kind of free energy term via $\zeta \eqqcolon e^{-\beta \phi}$. This then simplifies things to
 \begin{equation}

### 2021-04-29 appendix.tex
Added proof with one comment/question on a part I am not sure about. Pushed Davids text to notes.tex. Need to fix text following theorem / describing leaf plot

@@
 
+\subsection{OLD VERSION OF MAIN THEOREM}
+
+\begin{theorem}\label{thm:free-energy}
+	Consider a magic distillation protocol transforming noisy Strange state
+	\begin{equation*}
+		\rho_S(\epsilon)^{\otimes n} \longrightarrow \E(\rho_S(\epsilon)^{\otimes n})=\rho_S(\epsilon')^{\otimes m} 
+	\end{equation*}
+	with $n, m \gg 1$.
+
+Let each qutrit have a Hamiltonian $H$ with stabilizer eigenstates and energies $E_0, E_1, E_2$, and define $E_{\rm max} = \max\{E_0, E_1, E_2\}$ and $E_s$ the eigenvalue of the eigenstate that \nick{overlaps} the negative component of $\rho_S(\epsilon)$ in the Wigner representation.
+Let $T =(k\beta)^{-1}$ be any characteristic temperature for the physical system in the state $\tau^{\otimes n}= (e^{-\beta H}/\Z)^{\otimes n}$, with free energy $F$.
+Assume that for $n,m \gg 1$ the channel $\E$ generates negligible correlations on $\tau^{\otimes n}$, and so $\E(\tau^{\otimes n}) = \sigma^{\otimes m}$ for some state $\sigma$.
+
+Define $\beta_\star = (k T_\star)^{-1}$ through the relation
+\begin{equation}
+	E_{\rm max} - E_s \eqqcolon kT_\star \ln 2,
+\end{equation}
+and define a threshold noise,
+\begin{equation}
+	\epsilon_{\star}(\beta) \coloneqq 
+	\begin{cases}
+		3 - \dfrac{9}{4-2^{\beta/\beta_\star - 1}}, &\text{ for } \beta \leq \beta_\star \\
+		0, &\text{ for } \beta > \beta_\star.
+	\end{cases}
+\end{equation}
+Then, the distillation rate $R = m/n$ of the magic protocol is bounded as:
+\begin{equation}\label{eq:rate_bounds_proof}
+	R \leq
+	\begin{cases}
+		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F')},\ &\epsilon \leq \epsilon_\star, \epsilon' \leq \epsilon'_\star, \vspace{10pt}\\
+		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F')},\ &\epsilon \leq \epsilon_\star, \epsilon' > \epsilon'_\star, \vspace{10pt}\\
+		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F')},\ &\epsilon > \epsilon_\star, \epsilon' \leq \epsilon'_\star, \vspace{10pt}\\
+		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F')},\ &\epsilon > \epsilon_\star, \epsilon' > \epsilon'_\star,
+	\end{cases}
+\end{equation}
+where $F'$ is the free energy of the state $\sigma = e^{-\beta H'}/\Z'$ and other primed quantities are defined in the same way as the corresponding unprimed quantities. 
+\end{theorem}
+We note, firstly, that the specific numerical factors in $\epsilon_\star$ are a result of our choice of magic state. 
+\begin{proof}
+To establish the distillation bounds we consider the distillation protocol that gives
+\begin{equation}
+	\E( \rho_S(\epsilon)^{\otimes n}) = \rho_S(\epsilon')^{\otimes m},
+\end{equation}
+for the magic state. We then consider how the protocol transforms the reference equilibrium state as
+\begin{equation}
+	\E( \tau^{\otimes n}) = \sigma^{\otimes m}.
+\end{equation}
+Since $\tau$ and $\sigma$ are assumed to be full rank stabilizer states they have a strictly positive Wigner distribution, while, in contrast, the input and output magic states will generally have quasi-probability distributions for their Wigner functions.
+For any such protocol we therefore have that
+\begin{equation}
+	(W_{\rho_n} (x), W_{\tau_n}(x) ) \succ  (W_{\rho'_m} (x), W_{\sigma_m}(x) ),
+\end{equation}
+where, for the sake of clarity, we write $\rho_n \coloneqq \rho_S(\epsilon)^{\otimes n}$, $\rho'_m \coloneqq \rho_S(\epsilon')^{\otimes m}$ and $\tau_n \coloneqq \tau^{\otimes m}$, $\sigma_m \coloneqq \sigma^{\otimes m}$.
+We then have that
+\begin{equation}
+	L_{\rho_n |\tau_n}(x) \ge L_{\rho'_m |\sigma_m}(x) \mbox{ for all } x.
+\end{equation}
+We must therefore compute the Lorenz curve data for $\rho_n$ relative to $\tau_n$, and compare with the Lorenz curve of the output state $\rho_m'$ relative to $\sigma_m$.
+
+We define $W_{\rho | \tau}(\x) \coloneqq W_\rho(\x)/W_\tau(\x)$, which is always well-defined since $\tau$ is full-rank. Now we show in~\cref{app:wigner} that
+\begin{equation}
+W_{\rho_1\otimes \rho_2 | \tau_1 \otimes \tau_2} (\x_1 \oplus \x_2) = W_{\rho_1 | \tau_1}(\x_1)W_{\rho_2 | \tau_2}(\x_2),
+\end{equation}
+and also,
+\begin{equation}
+W_{\rho_1\otimes \rho_2} (\x_1 \oplus \x_2) = W_{\rho_1}(\x_1)W_{\rho_2}(\x_2),
+\end{equation}
+for any states $\rho_1, \rho_2$ and any full-rank stabilizer states $\tau_1, \tau_2$.
+\ddd{[Notation clashing here.
+Frame result outside as its own lemma -- we gotta check everything.]} \nick{Will frame in~\cref{app:wigner} and fix notation in the next commit}
+Therefore we have that
+\begin{align}
+W_{\rho_n |\tau_n} (\x) &= \prod_{i=1}^n W_{\rho|\tau}(\x_i)\\
+W_{\rho_n } (\x) &= \prod_{i=1}^n W_\rho(\x_i)
+\end{align}
+where $\x = \oplus_{i=1}^n \x_i$ is the phase space point for the full system in terms of those of the individual subsystems.
+
+The points defining the Lorenz curve $L_{\rho_n |\tau_n}(x)$ are obtained from first sorting the components of $W_{\rho_n |\tau_n}(\x)$ in non-increasing order and then computing the partial sums of $W_{\rho_n |\tau_n}(\pi(\x))$ where $\pi$ is the permutation that realises the sorting.
+Therefore, we first look at the values of $W_{\rho|\tau}(\x_i)$ for the single-copy case.
+
+The equilibrium state at inverse temperature $\beta$ on a single qutrit is given by $\tau = e^{-\beta H} / \Z$.
+Moreover we have that $\tau$ is a full-rank stabilizer state, where $\beta \geq 0$ and $H = E_0 \ketbra{\varphi_0} + E_1 \ketbra{\varphi_1} + E_2 \ketbra{\varphi_2}$ is an eigendecomposition of $H$.
+The state $\tau$ can now be written as 
+\begin{equation}
+	\tau = \frac{e^{-\beta E_0}}{\Z} \ketbra{\varphi_0} + \frac{e^{-\beta E_1}}{\Z} \ketbra{\varphi_1} + \frac{e^{-\beta E_2}}{\Z} \ketbra{\varphi_2},
+\end{equation}
+where the eigenstates $\{\ket{\varphi_k}\<\varphi_k|\}$ are pure, orthonormal stabiliser states, which can be represented in terms of generalized Paulis.
+To make our analysis simpler, we perform a change of basis that does not affect the Wigner negativity of the problem.
+We let $C$ be the unitary transforming each $|\varphi_k\>\<\varphi_k|$ to $|k\>\<k|$.
+Since the Clifford group is the normalizer of the Heisenberg-Weyl group, $C$ is a Clifford unitary.
+Therefore, $C$ maps $\tau$ to another stabilizer state that is diagonal in the computational basis, and we can assume without loss of generality that $\tau$ is diagonal in $\{|0\>,|1\>, |2\>\}$.
+However, this choice means that the location of the negative Wigner component $-v(\epsilon)$ of the Strange state will be permuted on the discrete phase space.
+We denote by $E_s$ the eigenvalue of $H$ where the associated eigenvector has Wigner distribution overlapping the negative component of the magic state $C\rho_S(\epsilon)C^\dagger$.
+This is unique, since the eigenstates form an orthonormal basis.
+
+The Wigner distribution of state $\tau$ is then given by
+\begin{align}
+	\W[\bmx]{\tau} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z}W_{\ketbra{k}}(x, p) \nonumber\\
+	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z} \delta_{x, k} = \frac{e^{-\beta E_x}}{3\Z},
+\end{align}
+where $x$ labels one of the three vertical lines in the phase space.
+The rescaled Wigner distribution $W_{\rho|\tau}(\x)$ is then easily computed.
+It has $9$ components, but several of these come with multiplicities.
+In total, there are four distinct values on the phase space, as illustrated in~\cref{fig:pd_split}.
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.45]{figs/pd_split_thermal.pdf}
+    \caption{\textbf{Qutrit phase space regions for $W_{\rho | \tau}(\x)$.}
+    Here, the negative component of the magic state overlaps the Wigner distribution of $|0\>$.
+The rescaled distribution attains a single value in each of the four regions, proportional to the value depicted in the region, see~\cref{eq:bmw_rescaled}.
+    }
+    \label{fig:pd_split}
+\end{figure}
+
+We now denote by $\w(\rho), \w(\rho|\tau)$ the unique values occurring in $W_\rho(\x), W_{\rho|\tau}(\x)$ respectively and $\bmm$ the vector of associated multiplicities of each value in $W_\rho(\x)$.
+The component values and multiplicities of the relevant distributions in the four distinct regions are given by
+\begin{align}
+	\w(\rho) &\coloneqq (-v, u, u, u), \\
+		\bmm &\coloneqq (1,2,3,3), \\
+	\bmw(\tau) &\coloneqq \frac{1}{3\Z} \left( e^{-\beta E_0}, e^{-\beta E_0}, e^{-\beta E_1}, e^{-\beta E_2} \right), \\
+	\bmw(\rho_{\rm{S}} | \tau) &\coloneqq 3\Z \left( -v e^{\beta E_0}, u e^{\beta E_0}, u e^{\beta E_1}, u e^{\beta E_2} \right). \label{eq:bmw_rescaled}
+\end{align}
+
+Using this notation, the values and multiplicities of the $n$--copy distribution $\bmw(\rho_n |\tau_n)$ are computed in~\cref{lem:ncopycomponents} in~\cref{app:cmpairs}. The values are given by 
+\begin{align}\label{eq:ncopy_w_rescaled}
+	[\w(\rho_n | \tau_n)]_{ijk} &= (3\Z)^{n} (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )},
+\end{align}
+where the indices $i,j,k$ are non-negative integers that obey the constraint $\alpha \coloneqq i+j+k \leq n$.
+The multiplicity of this above value is $m_{ijk}$ with
+\begin{equation}
+	m_{ijk} = \frac{n!}{i!j!k!(n-\alpha)!} 2^i 3^j 3^k.
+\end{equation}
+The associated components of $\w(\rho_n)$ are given by
+\begin{align}
+	[\w(\rho_n)]_{ijk} &= (-v)^{n-\alpha} u^{\alpha}, \label{eq:ncopy_wrho}\\
+	[\w(\tau)]_{ijk} &= (3\Z)^{-n} e^{-\beta (n-\alpha)E_s} e^{-\beta ( i E_0 + j E_1 + k E_2 )}. \label{eq:ncopy_wsigma}
+\end{align}
+
+In order to construct the $n$--copy Lorenz curve $L_{\rho_n|\tau_n}(x)$ we need to order the components of the distribution, $w(\rho_{\rm{S}} | \tau)_{ijk}$ in decreasing order, and identify the sequence of indices that give us $W_{\rho_n}(\pi(\x))$.
+
+Generally this is complex, but in order to obtain distillation bounds it is sufficient to determine the location of the first elbow $(x_0, L_0)$ of $L_{\rho_n|\tau_n}(\x)$.
+To do so, we compute the largest component
+\begin{equation}
+	w_{\rm max} \coloneqq \max_{i,j,k} [\w(\rho_n | \tau_n)]_{ijk},
+\end{equation}
+and determine the indices at which this occurs.
+Putting in the values we obtain
+\begin{align}
+	&(3\Z)^{-n}w_{\rm max} = \nonumber\\
+	&\max\limits_{i,j,k}\Big\{ (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \label{eq:max_slope}
+\end{align}
+where $0 \leq i,j,k \leq n$ and $\alpha \coloneqq i+j+k \leq n$.
+Now for $0 \leq \epsilon \leq 3/7$, we have $v \geq u$. Since we assume that $n$ is even, we need the sum $\alpha = i+j+k$ to be even too, so that the expression is positive.
+
+Given an even value for $\alpha$, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_s}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
+Hence, we have
+\begin{align}
+	&w_{\rm max} = \nonumber\\
+	&(3\Z)^{n} v^n e^{n\beta E_s}\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_s)} \right)^{\alpha} \Big\}}.
+\end{align}
+If the expression $\frac{u(\epsilon)}{v(\epsilon)} e^{\beta (E_{\rm{max}} - E_s)}$ is less than $1$ then the maximum occurs at $\alpha=0$, otherwise it occurs at $\alpha = n$.
+For a fixed state $\tau$, this transition is determined by the value of the depolarising noise parameter $\epsilon$ of the noisy magic state.
+The transition occurs at $\epsilon = \epsilon_\star$ where
+\begin{equation}\label{eq:noise_transition}
+	\frac{u(\epsilon_\star)}{v(\epsilon_\star)} e^{\beta (E_{\rm{max}} - E_s)} = \frac{3-\epsilon_\star}{6-8\epsilon_\star} e^{\beta (E_{\rm{max}} - E_s)} = 1.
+\end{equation}
+If $E_{\rm{max}} = E_s$, namely if the state negativity lies in the same phase space region as the highest energy, this threshold is constant in temperature and given by $\epsilon_{\star} = 3/7$.
+However, the condition that $\epsilon_\star \ge 0$ also implies a constraint on the effective temperature of the stabilizer state.
+Specifically, there is a threshold temperature value $\beta_\star$ given by
+\begin{equation}
+	\beta_{\star} \coloneqq \frac{1}{E_{\rm{max}} - E_s} \ln2,
+\end{equation}
+such that for the regime $0 \leq \beta \leq \beta_\star$ a transition noise level $\epsilon_\star$ exists, and for $\beta > \beta_\star$ no such transition exists, so we choose $\epsilon_\star = 0$. 
+Therefore, the transition value for the noise is given by
+\begin{equation}
+	\epsilon_{\star}(\beta) \coloneqq 
+	\begin{cases}
+		3 - \dfrac{9}{4-2^{\beta/\beta_\star - 1}}, &\text{ for } \beta \leq \beta_\star \\
+		0, &\text{ for } \beta > \beta_\star.
+	\end{cases}
+\end{equation}
+The quantity $w(\rho_{\rm{S}} | \sigma)_{\rm{max}}$ is now given by
+\begin{equation*}
+w_{\rm max} =
+	\begin{cases}
+		(3\Z)^{n} v^n e^{n\beta E_s}, &\mbox{if }\epsilon \leq \epsilon_{\star},\ \hspace{3pt}\rm{(C1)}\\
+		(3\Z)^{n} u^n e^{n\beta E_{\rm{max}}}, &\mbox{if }\epsilon > \epsilon_{\star}.\ \hspace{5pt}\rm{(C2)} 
+	\end{cases}
+\end{equation*}
+Case $\rm{(C1)}$ corresponds to $(i,j,k) = (0,0,0)$, so the multiplicity is $m_{000} = 1$, while
+Case $\rm{(C2)}$ corresponds to
+\begin{equation}
+	(i,j,k) = 
+	\begin{cases}
+	(0,n,0), &\text{if } E_{\rm{max}} = E_1, \\
+	(0,0,n), &\text{if } E_{\rm{max}} = E_2,
+	\end{cases}
+\end{equation}
+so the multiplicity in both cases is $3^n$.
+
+Using that $F = -\beta^{-1} \log \Z$, the first elbow coordinates in the two cases are now given by
+\begin{equation}\label{eq:first_elb_coords}
+	(x_0, L_0) =
+	\begin{cases}
+		\left(\frac{1}{3^n} e^{-n\beta (E_s - F)}, v^n \right), &\epsilon \leq \epsilon_\star \vspace{10pt}\\
+		\left( e^{-n\beta (E_{\rm{max}}-F)}, (3u)^n \right). &\epsilon > \epsilon_\star
+	\end{cases}
+\end{equation}
+
+\ddd{[Hmmm this needs an additional assumption on the output state to re-run the same analysis.
+Very annoying.]}\nick{What additional assumption beyond that the output state can be written as a Gibbs state for some $H'$?}
+Similarly, considering the output magic state with respect to state $\sigma'$, the image of equilibrium state $\sigma$ under the magic protocol, we get output Lorenz curve coordinates,
+\begin{equation}\label{eq:transformed_first_elb_coords}
+	(x'_0, L'_0) =
+	\begin{cases}
+		\left(\frac{1}{3^{n'}} e^{-n\beta (E'_s - F')}, v(\epsilon')^{n'} \right), &\epsilon' \leq \epsilon'_\star \vspace{10pt}\\
+		\left( e^{-n'\beta (E'_{\rm{max}}\hspace{-2.5pt}-F')}, (3u(\epsilon'))^{n'} \right), &\epsilon' > \epsilon'_\star
+	\end{cases}
+\end{equation}
+There are four combinations of coordinates, depending on the noise parameters $\epsilon, \epsilon'$ for the input and output states.
+In each of these combinations, we simply use the first elbow constraint, as described in~\cref{app:elb_constraints}, which leads to the bounds in the statement of the theorem.
+\end{proof}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-04-29 magic_paper.tex
Added proof with one comment/question on a part I am not sure about. Pushed Davids text to notes.tex. Need to fix text following theorem / describing leaf plot

@@
 The Wigner distribution of $n$ copies of the state is obtained by the $n$-fold product of the single copy distribution, and the Lorenz curve $L_{\rho|\sigma}(x)$ for $\rho = \rho_S(\epsilon)^{\otimes n}$ and $\sigma = (\I/3)^{\otimes n}$ is readily computed for any $n$ and $\epsilon$, and the full details are provided in~\cref{app:lcsu_technical}.
-We highlight that the non-trivial element that arises for quasi-distributions is that the product of negative components can generate a positive $n$-fold component, so the ordering of the components of $W_{\rho |\sigma}(x)$ depends on whether $-v(\epsilon)$ appears to an even or odd power in the expression of~\cref{eq:wigu}.
+We highlight that the non-trivial element that arises for quasi-distributions is that the product of negative components can generate a positive $n$-fold component, so the ordering of the components of \emph{rescaled Wigner distribution} $W_{\rho |\sigma}(\bmx) \coloneqq W_{\rho}(\bmx)/W_{\sigma}(\bmx)$ depends on whether $-v(\epsilon)$ appears to an even or odd power in the expression of~\cref{eq:wigu}.
 
@@
 \begin{equation}
-	\alpha_k \coloneqq \sum_{\mathbb{Z}_d} \braket{\phi_k}{-r}\braket{r}{\phi_k}.
+	\alpha_k \coloneqq \sum_{r \in \mathbb{Z}_d} \braket{\phi_k}{-r}\braket{r}{\phi_k}.
 \end{equation}
-Coefficients $\alpha_k$ are not necessarily positive, which is the case when the Hamiltonian $H$ does not admit a stabilizer decomposition. 
+Coefficients $\alpha_k$ can be negative when the Hamiltonian $H$ does not admit a Wigner-positive decomposition. 
 However, it is simple to see that $\zeta$ is always positive. \nick{because it is proportional to $W_{\tau}(0,0) > 0$ for full-rank, stabilizer $\tau$ - this argument is a bit cyclic}
@@
 \begin{proof}	
-	\nick{Start}
+For the sake of clarity, we write $\rho_n \coloneqq \rho_S(\epsilon)^{\otimes n}$, $\rho'_m \coloneqq \rho_S(\epsilon')^{\otimes m}$, $\tau_n \coloneqq \tau^{\otimes m}$ and $\sigma_m \coloneqq \sigma^{\otimes m}$.
+
+To establish the distillation bound we consider the distillation protocol that gives $\E( \rho_n) = \rho_m$ for the magic states. 
+We then consider that the protocol transforms the reference equilibrium state as $\E( \tau_n) = \sigma_m$.
+Since $\tau$ and $\sigma$ are assumed to be full rank stabilizer states, they have a strictly positive Wigner distribution, while, in contrast, the input and output magic states generally have quasi-probability Wigner distributions.
+For any such protocol we therefore have that
+\begin{equation}
+	( W_{\rho_n}(\bmx), W_{\tau_n}(\bmx) ) \succ ( W_{\rho'_m}(\bmx), W_{\sigma_m}(\bmx) ),
+\end{equation}
+or, equivalently, in terms of the relevant Lorenz curves,
+\begin{equation}
+	L_{\rho_n |\tau_n}(x) \ge L_{\rho'_m |\sigma_m}(x) \mbox{ for all } x.
+\end{equation}
+
+We define the rescaled Wigner distribution $W_{\rho | \tau}(\x) \coloneqq W_\rho(\x)/W_\tau(\x)$, which is always well-defined since $\tau$ is full-rank. 
+Due to the multiplicative property of the Wigner distribution, the rescaled distribution is also multiplicative in the sense that
+\begin{equation}
+	W_{\rho \otimes \rho' | \tau \otimes \tau'} (\x_1 \oplus \x_2) = W_{\rho | \tau}(\x_1)W_{\rho' | \tau'}(\x_2),
+\end{equation}
+for any states $\rho, \rho'$ and any full-rank stabilizer states $\tau, \tau'$.
+Therefore we have that
+\begin{align}
+	W_{\rho_n |\tau_n} (\x) &= \prod_{i=1}^n W_{\rho|\tau}(\x_i)\\
+	W_{\rho_n } (\x) &= \prod_{i=1}^n W_\rho(\x_i)
+\end{align}
+where $\x = \oplus_{i=1}^n \x_i \in \mathbb{Z}_3^n$ is the phase space point for the full system in terms of those of the individual subsystems.
+
+The points defining the Lorenz curve $L_{\rho_n |\tau_n}(x)$ are obtained from sorting the components of $W_{\rho_n |\tau_n}(\x)$ in non-increasing order and then computing the partial sums of $W_{\rho_n |\tau_n}(\pi(\x))$ where $\pi$ is the permutation that realises the sorting.
+However, similarly to the unital fragment analysis, we aim to use the constraint that is obtained by considering the line segment connecting the origin to the first elbow of both Lorenz curves.
+The proof of this constraint is provided in~\cref{app:elb_constraints}.
+Therefore, we focus on finding the coordinates of some point on this line segment of the Lorenz curves.
+
+We find the coordinates for the input Lorenz curve, but the exact same analysis can be applied on the output Lorenz curve.
+The Wigner distribution of a single noisy Strange state consists of 1 negative component $W_{\rho}(0,0) = -v(\epsilon)$ and 8 positive components $W_{\rho}(\bmx) = u(\epsilon)$ for $\bmx \neq \bmo$.
+The Wigner distribution of the full-rank, stabilizer equilibrium state $\tau$ is $W_{\tau}(\bmx) > 0$ for all $\bmx \in \mathbb{Z}_3^2$.
+We keep the components completely general.
+
+Assume that the smallest component of the equilibrium state distribution is $W_{\tau}(i,j)$.
+We then make use of the freedom to apply Clifford unitaries in order to perform the  Clifford operation
+\begin{equation}
+	\tau \longrightarrow X^{-i}Z^{-j}\ \tau\ Z^{j}X^{i},
+\end{equation}
+which permutes the smallest component to the origin of the phase space, $W_{\tau}(i,j) \longrightarrow W_{\tau}(0,0)$.
+This operation would inevitably affect the magic distillation protocol, but since we consider the state distillation modulo Clifford operations, we are allowed to perform the reverse Clifford operation keeping the magic distillation process as is.
+\nick{I don't understand this too well, how are we allowed to permute $W_\tau$ while keeping $W_\rho$ intact?}
+
+The rescaled distribution components are in general given by
+\begin{equation}
+	W_{\rho_n|\tau_n} = \left(\frac{-v}{W_{\tau}(0,0)}\right)^{i_{\bmo}} \prod_{\bmx \neq \bmo} \left(\frac{u}{W_{\tau}(\bmx)}\right)^{i_{\bmx}},
+\end{equation}
+where the (integer) indices obey the following conditions:
+\begin{align}
+&0 \leq i_{\bmx} \leq n \mbox{ for all } \bmx \in \mathbb{Z}_3^2, \nonumber \\
+&\sum_{\bmx \in \mathbb{Z}_3^2} i_{\bmx} = n.
+\end{align}
+It is now easy to find the largest rescaled component.
+Firstly, note that $n$ is even, so we require that $i_{\bmo} \in \{0,2,\dots,n\}$ for the component to be positive.
+Then, we have that $v \geq u$ because $\epsilon \leq 3/7$, and we have already ensured that $W_{\tau}(0,0) \leq W_{\tau}(\bmx)$ for all $\bmx \in \mathbb{Z}_3^2$.
+Therefore, the largest rescaled component occurs when $i_{\bmo} = n$ and $i_{\bmx} = 0$ for $\bmx \neq \bmo$ and is equal to $(v/W_{\tau}(0,0))^n$.
+Accordingly, the coordinates of the first Lorenz curve point after the origin are given by
+\begin{equation}
+	(x_0, L_0) = ((W_{\tau}(0,0))^n, v^n)
+\end{equation}
+
+Given a Hamiltonian decomposition,
+\begin{equation}
+	H = \sum_{k \in \mathbb{Z}_3} E_k\ketbra{\phi_k}{\phi_k},
+\end{equation}
+we can re-express the coordinate location, by writing
+\begin{align}
+	W_{\tau}(0,0) &= \frac{1}{3\Z}\tr\left[ A_{0,0}e^{\beta H} \right] \nonumber\\
+	&= \frac{e^{\beta F}}{3} \tr\left[ \sum_{r \in \mathbb{Z}_3} \ketbra{-r}{r}\sum_{k \in \mathbb{Z}_3} e^{\beta E_k}\ketbra{\phi_k}{\phi_k} \right] \\
+	&= \frac{e^{\beta F}}{3} \sum_{r \in \mathbb{Z}_3} \alpha_k e^{\beta E_k}
+	= \frac{e^{\beta F}}{3} \zeta \\
+	&= \frac{e^{\beta (F - \Phi)}}{3},
+\end{align}
+where $\alpha_k, \zeta$ and $\Phi$ are as defined prior to the statement of the theorem.
+Finally, the coordinates can be expressed as
+\begin{equation}
+	(x_0, L_0) = \left( \frac{e^{n\beta (F - \Phi)}}{3^n}, v(\epsilon)^n \right).
+\end{equation}
+In the same manner, we can derive the first point coordinates of the output Lorenz curve as
+\begin{equation}
+	(x'_0, L'_0) = \left( \frac{e^{n\beta (F' - \Phi')}}{3^n}, v(\epsilon')^n \right).
+\end{equation}
+
+If the largest rescaled component of a state is distinct with no multiplicities, then these coordinates correspond to the first elbow of the corresponding Lorenz curve, whereas if it appears multiple times, then the coordinates derived correspond to a point on the interior of the line segment connecting the origin to the first elbow.
+In both cases, the bound derived remains the same, as is clear by its derivation in~\cref{app:elb_constraints}, and it is given by $L_0 / x_0 \geq L'_0 / x'_0$, which can be directly rearranged into the stated bound of the theorem.
+
 \end{proof}
 
-\begin{theorem}\label{thm:free-energy}
-	Consider a magic distillation protocol transforming noisy Strange state
-	\begin{equation*}
-		\rho_S(\epsilon)^{\otimes n} \longrightarrow \E(\rho_S(\epsilon)^{\otimes n})=\rho_S(\epsilon')^{\otimes m} 
-	\end{equation*}
-	with $n, m \gg 1$.
-
-Let each qutrit have a Hamiltonian $H$ with stabilizer eigenstates and energies $E_0, E_1, E_2$, and define $E_{\rm max} = \max\{E_0, E_1, E_2\}$ and $E_s$ the eigenvalue of the eigenstate that \nick{overlaps} the negative component of $\rho_S(\epsilon)$ in the Wigner representation.
-Let $T =(k\beta)^{-1}$ be any characteristic temperature for the physical system in the state $\tau^{\otimes n}= (e^{-\beta H}/\Z)^{\otimes n}$, with free energy $F$.
-Assume that for $n,m \gg 1$ the channel $\E$ generates negligible correlations on $\tau^{\otimes n}$, and so $\E(\tau^{\otimes n}) = \sigma^{\otimes m}$ for some state $\sigma$.
-
-Define $\beta_\star = (k T_\star)^{-1}$ through the relation
-\begin{equation}
-	E_{\rm max} - E_s \eqqcolon kT_\star \ln 2,
-\end{equation}
-and define a threshold noise,
-\begin{equation}
-	\epsilon_{\star}(\beta) \coloneqq 
-	\begin{cases}
-		3 - \dfrac{9}{4-2^{\beta/\beta_\star - 1}}, &\text{ for } \beta \leq \beta_\star \\
-		0, &\text{ for } \beta > \beta_\star.
-	\end{cases}
-\end{equation}
-Then, the distillation rate $R = m/n$ of the magic protocol is bounded as:
-\begin{equation}\label{eq:rate_bounds_proof}
-	R \leq
-	\begin{cases}
-		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F')},\ &\epsilon \leq \epsilon_\star, \epsilon' \leq \epsilon'_\star, \vspace{10pt}\\
-		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F')},\ &\epsilon \leq \epsilon_\star, \epsilon' > \epsilon'_\star, \vspace{10pt}\\
-		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F')},\ &\epsilon > \epsilon_\star, \epsilon' \leq \epsilon'_\star, \vspace{10pt}\\
-		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F')},\ &\epsilon > \epsilon_\star, \epsilon' > \epsilon'_\star,
-	\end{cases}
-\end{equation}
-where $F'$ is the free energy of the state $\sigma = e^{-\beta H'}/\Z'$ and other primed quantities are defined in the same way as the corresponding unprimed quantities. 
-\end{theorem}
-
-We note, firstly, that the specific numerical factors in $\epsilon_\star$ are a result of our choice of magic state. 
-Secondly, these bounds are derived based on analysis of only a part of the Lorenz curves and can be improved via a finer analysis. 
-This is apparent by simple numerical calculations on the entirety of the curves as seen in~\cref{fig:distill_bounds} for unital operations.
+The bounds derived are based on analysis of only part of the Lorenz curves and can be improved via a finer analysis.
+This is apparent by simple numerical calculations on the entirety of the curves as seen in~\cref{fig:distill_bounds} for the case of unital operations.
 Specifically, the existing bounds follow by considering the dominant terms in the rescaled Wigner distribution and do not, for example, take into account the Lorenz curve's peak structure.
 
-As a special case of the result, suppose that $H=H'$, implying that the protocol leaves the equilibrium state unchanged, hence it corresponds to a Gibbs-preserving map~\cite{faist_2015}.
+\nick{FIX} As a special case of the result, suppose that $H=H'$, implying that the protocol leaves the equilibrium state unchanged, hence it corresponds to a Gibbs-preserving map~\cite{faist_2015}.
 In the more general case, $\Delta F \coloneqq F' - F \ne 0$ and we have a free energy difference between the initial and final states, with respect to the relevant Hamiltonians.
@@
 
-The above bounds mainly demonstrate how one can use relative majorization of quasi-distributions to incorporate additional information into distillation bounds.
+\nick{FIX} The above bounds mainly demonstrate how one can use relative majorization of quasi-distributions to incorporate additional information into distillation bounds.
 However to unpack the results more it is useful to consider the case in which $H=H'$, and look at $\epsilon' \rightarrow 0$.
@@
 \end{figure}
-\begin{proof}
-To establish the distillation bounds we consider the distillation protocol that gives
-\begin{equation}
-	\E( \rho_S(\epsilon)^{\otimes n}) = \rho_S(\epsilon')^{\otimes m},
-\end{equation}
-for the magic state. We then consider how the protocol transforms the reference equilibrium state as
-\begin{equation}
-	\E( \tau^{\otimes n}) = \sigma^{\otimes m}.
-\end{equation}
-Since $\tau$ and $\sigma$ are assumed to be full rank stabilizer states they have a strictly positive Wigner distribution, while, in contrast, the input and output magic states will generally have quasi-probability distributions for their Wigner functions.
-For any such protocol we therefore have that
-\begin{equation}
-	(W_{\rho_n} (x), W_{\tau_n}(x) ) \succ  (W_{\rho'_m} (x), W_{\sigma_m}(x) ),
-\end{equation}
-where for simplicity we write $\rho_n \coloneqq \rho_S(\epsilon)^{\otimes n}$, $\rho'_m\coloneqq \rho_S(\epsilon')^{\otimes m}$ and $\tau_n\coloneqq\tau^{\otimes m}$ and $\sigma_m\coloneqq\sigma^{\otimes m}$.
-We then have that
-\begin{equation}
-	L_{\rho_n |\tau_n}(x) \ge L_{\rho'_m |\sigma_m}(x) \mbox{ for all } x.
-\end{equation}
-We must therefore compute the Lorenz curve data for $\rho_n$ relative to $\tau_n$, and compare with the Lorenz curve of the output state $\rho_m'$ relative to $\sigma_m$.
-
-We define $W_{\rho | \tau}(\x) \coloneqq W_\rho(\x)/W_\tau(\x)$, which is always well-defined since $\tau$ is full-rank. Now we show in~\cref{app:wigner} that
-\begin{equation}
-W_{\rho_1\otimes \rho_2 | \tau_1 \otimes \tau_2} (\x_1 \oplus \x_2) = W_{\rho_1 | \tau_1}(\x_1)W_{\rho_2 | \tau_2}(\x_2),
-\end{equation}
-and also,
-\begin{equation}
-W_{\rho_1\otimes \rho_2} (\x_1 \oplus \x_2) = W_{\rho_1}(\x_1)W_{\rho_2}(\x_2),
-\end{equation}
-for any states $\rho_1, \rho_2$ and any full-rank stabilizer states $\tau_1, \tau_2$.
-\ddd{[Notation clashing here.
-Frame result outside as its own lemma -- we gotta check everything.]} \nick{Will frame in~\cref{app:wigner} and fix notation in the next commit}
-Therefore we have that
-\begin{align}
-W_{\rho_n |\tau_n} (\x) &= \prod_{i=1}^n W_{\rho|\tau}(\x_i)\\
-W_{\rho_n } (\x) &= \prod_{i=1}^n W_\rho(\x_i)
-\end{align}
-where $\x = \oplus_{i=1}^n \x_i$ is the phase space point for the full system in terms of those of the individual subsystems.
-
-The points defining the Lorenz curve $L_{\rho_n |\tau_n}(x)$ are obtained from first sorting the components of $W_{\rho_n |\tau_n}(\x)$ in non-increasing order and then computing the partial sums of $W_{\rho_n |\tau_n}(\pi(\x))$ where $\pi$ is the permutation that realises the sorting.
-Therefore, we first look at the values of $W_{\rho|\tau}(\x_i)$ for the single-copy case.
-
-The equilibrium state at inverse temperature $\beta$ on a single qutrit is given by $\tau = e^{-\beta H} / \Z$.
-Moreover we have that $\tau$ is a full-rank stabilizer state, where $\beta \geq 0$ and $H = E_0 \ketbra{\varphi_0} + E_1 \ketbra{\varphi_1} + E_2 \ketbra{\varphi_2}$ is an eigendecomposition of $H$.
-The state $\tau$ can now be written as 
-\begin{equation}
-	\tau = \frac{e^{-\beta E_0}}{\Z} \ketbra{\varphi_0} + \frac{e^{-\beta E_1}}{\Z} \ketbra{\varphi_1} + \frac{e^{-\beta E_2}}{\Z} \ketbra{\varphi_2},
-\end{equation}
-where the eigenstates $\{\ket{\varphi_k}\<\varphi_k|\}$ are pure, orthonormal stabiliser states, which can be represented in terms of generalized Paulis.
-To make our analysis simpler, we perform a change of basis that does not affect the Wigner negativity of the problem.
-We let $C$ be the unitary transforming each $|\varphi_k\>\<\varphi_k|$ to $|k\>\<k|$.
-Since the Clifford group is the normalizer of the Heisenberg-Weyl group, $C$ is a Clifford unitary.
-Therefore, $C$ maps $\tau$ to another stabilizer state that is diagonal in the computational basis, and we can assume without loss of generality that $\tau$ is diagonal in $\{|0\>,|1\>, |2\>\}$.
-However, this choice means that the location of the negative Wigner component $-v(\epsilon)$ of the Strange state will be permuted on the discrete phase space.
-We denote by $E_s$ the eigenvalue of $H$ where the associated eigenvector has Wigner distribution overlapping the negative component of the magic state $C\rho_S(\epsilon)C^\dagger$.
-This is unique, since the eigenstates form an orthonormal basis.
-
-The Wigner distribution of state $\tau$ is then given by
-\begin{align}
-	\W[\bmx]{\tau} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z}W_{\ketbra{k}}(x, p) \nonumber\\
-	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z} \delta_{x, k} = \frac{e^{-\beta E_x}}{3\Z},
-\end{align}
-where $x$ labels one of the three vertical lines in the phase space.
-The rescaled Wigner distribution $W_{\rho|\tau}(\x)$ is then easily computed.
-It has $9$ components, but several of these come with multiplicities.
-In total, there are four distinct values on the phase space, as illustrated in~\cref{fig:pd_split}.
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.45]{figs/pd_split_thermal.pdf}
-    \caption{\textbf{Qutrit phase space regions for $W_{\rho | \tau}(\x)$.}
-    Here, the negative component of the magic state overlaps the Wigner distribution of $|0\>$.
-The rescaled distribution attains a single value in each of the four regions, proportional to the value depicted in the region, see~\cref{eq:bmw_rescaled}.
-    }
-    \label{fig:pd_split}
-\end{figure}
-
-We now denote by $\w(\rho), \w(\rho|\tau)$ the unique values occurring in $W_\rho(\x), W_{\rho|\tau}(\x)$ respectively and $\bmm$ the vector of associated multiplicities of each value in $W_\rho(\x)$.
-The component values and multiplicities of the relevant distributions in the four distinct regions are given by
-\begin{align}
-	\w(\rho) &\coloneqq (-v, u, u, u), \\
-		\bmm &\coloneqq (1,2,3,3), \\
-	\bmw(\tau) &\coloneqq \frac{1}{3\Z} \left( e^{-\beta E_0}, e^{-\beta E_0}, e^{-\beta E_1}, e^{-\beta E_2} \right), \\
-	\bmw(\rho_{\rm{S}} | \tau) &\coloneqq 3\Z \left( -v e^{\beta E_0}, u e^{\beta E_0}, u e^{\beta E_1}, u e^{\beta E_2} \right). \label{eq:bmw_rescaled}
-\end{align}
-
-Using this notation, the values and multiplicities of the $n$--copy distribution $\bmw(\rho_n |\tau_n)$ are computed in~\cref{lem:ncopycomponents} in~\cref{app:cmpairs}. The values are given by 
-\begin{align}\label{eq:ncopy_w_rescaled}
-	[\w(\rho_n | \tau_n)]_{ijk} &= (3\Z)^{n} (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )},
-\end{align}
-where the indices $i,j,k$ are non-negative integers that obey the constraint $\alpha \coloneqq i+j+k \leq n$.
-The multiplicity of this above value is $m_{ijk}$ with
-\begin{equation}
-	m_{ijk} = \frac{n!}{i!j!k!(n-\alpha)!} 2^i 3^j 3^k.
-\end{equation}
-The associated components of $\w(\rho_n)$ are given by
-\begin{align}
-	[\w(\rho_n)]_{ijk} &= (-v)^{n-\alpha} u^{\alpha}, \label{eq:ncopy_wrho}\\
-	[\w(\tau)]_{ijk} &= (3\Z)^{-n} e^{-\beta (n-\alpha)E_s} e^{-\beta ( i E_0 + j E_1 + k E_2 )}. \label{eq:ncopy_wsigma}
-\end{align}
-
-In order to construct the $n$--copy Lorenz curve $L_{\rho_n|\tau_n}(x)$ we need to order the components of the distribution, $w(\rho_{\rm{S}} | \tau)_{ijk}$ in decreasing order, and identify the sequence of indices that give us $W_{\rho_n}(\pi(\x))$.
-
-Generally this is complex, but in order to obtain distillation bounds it is sufficient to determine the location of the first elbow $(x_0, L_0)$ of $L_{\rho_n|\tau_n}(\x)$.
-To do so, we compute the largest component
-\begin{equation}
-	w_{\rm max} \coloneqq \max_{i,j,k} [\w(\rho_n | \tau_n)]_{ijk},
-\end{equation}
-and determine the indices at which this occurs.
-Putting in the values we obtain
-\begin{align}
-	&(3\Z)^{-n}w_{\rm max} = \nonumber\\
-	&\max\limits_{i,j,k}\Big\{ (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \label{eq:max_slope}
-\end{align}
-where $0 \leq i,j,k \leq n$ and $\alpha \coloneqq i+j+k \leq n$.
-Now for $0 \leq \epsilon \leq 3/7$, we have $v \geq u$. Since we assume that $n$ is even, we need the sum $\alpha = i+j+k$ to be even too, so that the expression is positive.
-
-Given an even value for $\alpha$, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_s}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
-Hence, we have
-\begin{align}
-	&w_{\rm max} = \nonumber\\
-	&(3\Z)^{n} v^n e^{n\beta E_s}\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_s)} \right)^{\alpha} \Big\}}.
-\end{align}
-If the expression $\frac{u(\epsilon)}{v(\epsilon)} e^{\beta (E_{\rm{max}} - E_s)}$ is less than $1$ then the maximum occurs at $\alpha=0$, otherwise it occurs at $\alpha = n$.
-For a fixed state $\tau$, this transition is determined by the value of the depolarising noise parameter $\epsilon$ of the noisy magic state.
-The transition occurs at $\epsilon = \epsilon_\star$ where
-\begin{equation}\label{eq:noise_transition}
-	\frac{u(\epsilon_\star)}{v(\epsilon_\star)} e^{\beta (E_{\rm{max}} - E_s)} = \frac{3-\epsilon_\star}{6-8\epsilon_\star} e^{\beta (E_{\rm{max}} - E_s)} = 1.
-\end{equation}
-If $E_{\rm{max}} = E_s$, namely if the state negativity lies in the same phase space region as the highest energy, this threshold is constant in temperature and given by $\epsilon_{\star} = 3/7$.
-However, the condition that $\epsilon_\star \ge 0$ also implies a constraint on the effective temperature of the stabilizer state.
-Specifically, there is a threshold temperature value $\beta_\star$ given by
-\begin{equation}
-	\beta_{\star} \coloneqq \frac{1}{E_{\rm{max}} - E_s} \ln2,
-\end{equation}
-such that for the regime $0 \leq \beta \leq \beta_\star$ a transition noise level $\epsilon_\star$ exists, and for $\beta > \beta_\star$ no such transition exists, so we choose $\epsilon_\star = 0$. 
-Therefore, the transition value for the noise is given by
-\begin{equation}
-	\epsilon_{\star}(\beta) \coloneqq 
-	\begin{cases}
-		3 - \dfrac{9}{4-2^{\beta/\beta_\star - 1}}, &\text{ for } \beta \leq \beta_\star \\
-		0, &\text{ for } \beta > \beta_\star.
-	\end{cases}
-\end{equation}
-The quantity $w(\rho_{\rm{S}} | \sigma)_{\rm{max}}$ is now given by
-\begin{equation*}
-w_{\rm max} =
-	\begin{cases}
-		(3\Z)^{n} v^n e^{n\beta E_s}, &\mbox{if }\epsilon \leq \epsilon_{\star},\ \hspace{3pt}\rm{(C1)}\\
-		(3\Z)^{n} u^n e^{n\beta E_{\rm{max}}}, &\mbox{if }\epsilon > \epsilon_{\star}.\ \hspace{5pt}\rm{(C2)} 
-	\end{cases}
-\end{equation*}
-Case $\rm{(C1)}$ corresponds to $(i,j,k) = (0,0,0)$, so the multiplicity is $m_{000} = 1$, while
-Case $\rm{(C2)}$ corresponds to
-\begin{equation}
-	(i,j,k) = 
-	\begin{cases}
-	(0,n,0), &\text{if } E_{\rm{max}} = E_1, \\
-	(0,0,n), &\text{if } E_{\rm{max}} = E_2,
-	\end{cases}
-\end{equation}
-so the multiplicity in both cases is $3^n$.
-
-Using that $F = -\beta^{-1} \log \Z$, the first elbow coordinates in the two cases are now given by
-\begin{equation}\label{eq:first_elb_coords}
-	(x_0, L_0) =
-	\begin{cases}
-		\left(\frac{1}{3^n} e^{-n\beta (E_s - F)}, v^n \right), &\epsilon \leq \epsilon_\star \vspace{10pt}\\
-		\left( e^{-n\beta (E_{\rm{max}}-F)}, (3u)^n \right). &\epsilon > \epsilon_\star
-	\end{cases}
-\end{equation}
-
-\ddd{[Hmmm this needs an additional assumption on the output state to re-run the same analysis.
-Very annoying.]}\nick{What additional assumption beyond that the output state can be written as a Gibbs state for some $H'$?}
-Similarly, considering the output magic state with respect to state $\sigma'$, the image of equilibrium state $\sigma$ under the magic protocol, we get output Lorenz curve coordinates,
-\begin{equation}\label{eq:transformed_first_elb_coords}
-	(x'_0, L'_0) =
-	\begin{cases}
-		\left(\frac{1}{3^{n'}} e^{-n\beta (E'_s - F')}, v(\epsilon')^{n'} \right), &\epsilon' \leq \epsilon'_\star \vspace{10pt}\\
-		\left( e^{-n'\beta (E'_{\rm{max}}\hspace{-2.5pt}-F')}, (3u(\epsilon'))^{n'} \right), &\epsilon' > \epsilon'_\star
-	\end{cases}
-\end{equation}
-There are four combinations of coordinates, depending on the noise parameters $\epsilon, \epsilon'$ for the input and output states.
-In each of these combinations, we simply use the first elbow constraint, as described in~\cref{app:elb_constraints}, which leads to the bounds in the statement of the theorem.
-\end{proof}
-
-\ddd{\subsection{Improving our abilities to include arbitrary output stabilizer states.}
-The existing analysis works fine when the state $\tau'$ has stabilizer eigendecomposition (i.e.
-it's orthonormal basis is along the stabilizer directions...e.g.
-along $|0\>\<0|, |1\>\<1|$ in the Bloch sphere for a qubit).
-However it can lie inside the stabilizer polytope but not have such an eigenbasis.
-Therefore we'd like to include this fully general possibility.}
-
-To do this we just need to analyse how the properties of the output state relate to the magnitudes of its Wigner components.
-Here let $\tau$ be a single full-rank stabilizer qutrit state -- we are really interested in the output state $\tau'$ but let's ignore primes for now....they just clutter expressions unnecessarily.
-For simplicity denote the Wigner components of the magic state as
-\begin{equation}
-\w = (-v, u,u,u,u,u,u,u,u),
-\end{equation}
-and we index from $i=0$ to $i=7$, so that e.g. $w_0 = -v$ and $w_i = u$ for $i \ne 0$. Let $\t$ denote the Wigner distribution for $\tau$, so that
-\begin{equation}
-\t = (t_0, t_1,t_2, t_3, t_4,t_5,t_6,t_7),
-\end{equation}
-and we assume that $t_i >0$ for all $i$.
-We also note that using Clifford unitaries we can always choose to shift either the smallest entry of $\t$ or the largest entry of $\t$ to the $i=0$ slot.
-We might need to exploit this in a moment.
-
-The rescaled distribution is then $\tilde{\w}\coloneqq (w_i/t_i)$, and we define $v_0 \coloneqq v/t_0$ and $u_i \coloneqq u/t_i$ for $i\ne 0$.
-We now need to consider the $n$--copy version of this, denoted $\tilde{\w}^{\otimes n}$, and determine how the largest component arises.
-A general component of $\tilde{\w}^{\otimes n}$ is given by,
-\begin{equation}
-\tilde{w}_{n,\alpha, i_1, \dots, i_8} = (-v_0)^{i_0} u_1^{i_1} u_2^{i_2} \cdots u_8^{i_8},
-\end{equation}
-with the assumption that firstly $n$ is always even, and the indices obeying the following conditions:
-\begin{align}
-0 &\le i_j \le n \mbox{ for each }j=0,1,\dots ,8 \nonumber \\
-i_0+ i_1 &+ i_2 + \dots i_8 =n.
-\end{align}
-Now the largest entry must be positive, and so we require that $\alpha$ is an even number, and so we consider
-\begin{equation}
-\tilde{w}_{n,i_0, i_1, \dots, i_8} = v_0^{i_0} u_1^{i_1} u_2^{i_2} \cdots u_8^{i_8},
-\end{equation}
-over the above integers with $i_0 \in \{0,2,4, \dots, n\}$.
-Let $a = \max \{v_0, u_1, \dots ,u_8\}$, then clearly the maximum value attained ($\tilde{w}_{\rm max}\coloneqq \max_{i_0,i_1,\dots , i_8}(\tilde{w}_{n,i_0, i_1, \dots, i_8})$ ) is given by
-\begin{equation}
-\tilde{w}_{\rm max} = a^n.
-\end{equation}
-If the numbers $\{v_0, u_1, u_2, \dots, u_8\}$ are distinct then this maximum value occurs at a unique $i_k=n$ for some $k \in \{0, 1, \dots, 8\}$. Let's consider this case first.
-
-\textbf{(No multiplicities)} We expect this is the generic case, but I think it always provides a sufficient condition even if multiplicities exist.
-We can assume that noise level is below $3/7$ and so we have that $v >u$, so the $0$ component in $\w$, and so also $\w^{\otimes n}$, is the largest.
-But this needs rescaling by $\t$.
-
-We now make use of the freedom to do a Clifford unitary transformation that sends the smallest entry in $\t$ to the $0$ component.
-Note that in doing so we must also account for this Clifford unitary on the output magic state too!
-To get around this we can simply say that we consider $\rho_S(\epsilon )^{\otimes n} \rightarrow \rho_S(\epsilon')^{\otimes m}$ modulo local Clifford unitaries on the output system.
-This changes the rules of the game to suit our needs.
-Instead of distilling out the precise noisy Strange state, we allow the protocol to have arbitrary post-processing on the individual qutrits via reversible Cliffords.
-I.e.~the magic content is the same in each case, but when we consider the problem of how $\tau \rightarrow \tau'$ this can be used to our advantage to simplify our analysis.
-Need to reflect on this variant and how it affects the content of our result.
-
-So given the ability to assume that the smallest entry of $\t$ is the $t_0$ component this means that for noise levels below $3/7$ the largest component of $\tilde{w}_{n,i_0, i_1, \dots, i_8}$ occurs at $(i_0,i_1, \dots, i_8) = (n,0,0,\dots ,0)$.
-We therefore have, for the no-multiplicity case, that the first elbow occurs at the point $(t_0^n, v^n)$.
-This will lead to a bound expression in terms of $\epsilon$ for the output state, together with whatever value $t_0$ takes on.
-\ddd{[give expression]}.
-While this is fine, we need to link $t_0$ to the physics of the state $\tau = e^{-\beta H}/\Z$.
-Well, just from the definition we have that
-\begin{equation}
-t_0 = \frac{1}{d\Z}\tr [ A_{0,0} e^{-\beta H}],
-\end{equation}
-where, of course, $d=3$. So in $t_0^n$ we immediately get a term $\Z^{-n} = e^{-n\beta F}$, which is nice and general. Using the expansion of the thermal state into its energy eigenstates we obtain
-\begin{align}
-t_0^n &= \left ( \frac{1}{d\Z}\tr [ A_{0,0} e^{-\beta H}] \right )^n \nonumber \\
-&= \frac{e^{-n\beta F}}{3^n} ( \tr [ A_{0,0} \sum_k e^{-\beta E_k} |\varphi_k\>\<\varphi_k|])^n\nonumber \\
-&= \frac{e^{-n \beta F}}{3^n} ( \sum_k \alpha_k e^{-\beta E_k})^n,
-\end{align}
-where we define
-\begin{equation}
-\alpha_k \coloneqq \<\varphi_k |A_{0,0} |\varphi_k\>, \mbox{ for }k=0,1,2.
-\end{equation}
-However $A_{0,0} = \sum_{r\in \mathbb{Z}_3} | -r\>\<r|$ and so
-\begin{equation}
-\alpha_k \coloneqq \sum_{r \in \mathbb{Z}_3} \<\varphi_k |-r\> \<r |\varphi_k\>.
-\end{equation}
-This just encodes how the energy eigenbasis of the Hamiltonian $H$ relates to the \emph{stabilizer} basis.
-Anyhow, the nice thing is that we always get the Free energy term emerging in the $t_0^n$ and so we can include this into the distillation bound, with the $\alpha_k$ terms simply handling the messy issue of how the two important bases relate.
-We can package the messy details into some definition in some way.
-E.g.
-the form of the sum involving $\alpha_k$ looks a bit like a partition function, so we can define something like
-\begin{equation}
-\zeta \coloneqq  \sum_k \alpha_k e^{-\beta E_k},
-\end{equation}
-so that
-\begin{equation}
-t_0^n = \frac{e^{-n\beta F}}{3^n}\zeta^n,
-\end{equation}
-which is tidy....and we could also then define $\phi$ as a kind of free energy term via $\zeta \eqqcolon e^{-\beta \phi}$. This then simplifies things to
-\begin{equation}
-t_0^n =  \frac{e^{-n \beta (F+\phi)}}{3^n},
-\end{equation}
-where $F$ corresponds to the physical free energy of $\tau$ while $\phi$ is some weird term that captures the degree to which the energy basis differs from the stabilizer basis.
-\ddd{[Details need tidying/checking and we need the final bounds to be computed.]}
-
-\textbf{(Multiplicity case)} I don't think we really need to delve into this.
-Firstly no multiplicities will be generic.
-Secondly, if multiplicities appear this simply means the above Lorenz curve point is not an elbow but instead as point on the first line segment.
-Imposing the conditions for this point is \emph{also a necessary condition} and therefore suffices to get a bound.
 

### 2021-04-29 notes/notes.tex
Added proof with one comment/question on a part I am not sure about. Pushed Davids text to notes.tex. Need to fix text following theorem / describing leaf plot

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\ddd{\subsection{Improving our abilities to include arbitrary output stabilizer states.}
+The existing analysis works fine when the state $\tau'$ has stabilizer eigendecomposition (i.e.
+it's orthonormal basis is along the stabilizer directions...e.g.
+along $|0\>\<0|, |1\>\<1|$ in the Bloch sphere for a qubit).
+However it can lie inside the stabilizer polytope but not have such an eigenbasis.
+Therefore we'd like to include this fully general possibility.}
+
+To do this we just need to analyse how the properties of the output state relate to the magnitudes of its Wigner components.
+Here let $\tau$ be a single full-rank stabilizer qutrit state -- we are really interested in the output state $\tau'$ but let's ignore primes for now....they just clutter expressions unnecessarily.
+For simplicity denote the Wigner components of the magic state as
+\begin{equation}
+	\w = (-v, u,u,u,u,u,u,u,u),
+\end{equation}
+and we index from $i=0$ to $i=7$, so that e.g. $w_0 = -v$ and $w_i = u$ for $i \ne 0$. Let $\t$ denote the Wigner distribution for $\tau$, so that
+\begin{equation}
+\t = (t_0, t_1,t_2, t_3, t_4,t_5,t_6,t_7),
+\end{equation}
+and we assume that $t_i >0$ for all $i$.
+We also note that using Clifford unitaries we can always choose to shift either the smallest entry of $\t$ or the largest entry of $\t$ to the $i=0$ slot.
+We might need to exploit this in a moment.
+
+The rescaled distribution is then $\tilde{\w}\coloneqq (w_i/t_i)$, and we define $v_0 \coloneqq v/t_0$ and $u_i \coloneqq u/t_i$ for $i\ne 0$.
+We now need to consider the $n$--copy version of this, denoted $\tilde{\w}^{\otimes n}$, and determine how the largest component arises.
+A general component of $\tilde{\w}^{\otimes n}$ is given by,
+\begin{equation}
+\tilde{w}_{n,\alpha, i_1, \dots, i_8} = (-v_0)^{i_0} u_1^{i_1} u_2^{i_2} \cdots u_8^{i_8},
+\end{equation}
+with the assumption that firstly $n$ is always even, and the indices obeying the following conditions:
+\begin{align}
+0 &\le i_j \le n \mbox{ for each }j=0,1,\dots ,8 \nonumber \\
+i_0+ i_1 &+ i_2 + \dots i_8 =n.
+\end{align}
+Now the largest entry must be positive, and so we require that $\alpha$ is an even number, and so we consider
+\begin{equation}
+\tilde{w}_{n,i_0, i_1, \dots, i_8} = v_0^{i_0} u_1^{i_1} u_2^{i_2} \cdots u_8^{i_8},
+\end{equation}
+over the above integers with $i_0 \in \{0,2,4, \dots, n\}$.
+Let $a = \max \{v_0, u_1, \dots ,u_8\}$, then clearly the maximum value attained ($\tilde{w}_{\rm max}\coloneqq \max_{i_0,i_1,\dots , i_8}(\tilde{w}_{n,i_0, i_1, \dots, i_8})$ ) is given by
+\begin{equation}
+\tilde{w}_{\rm max} = a^n.
+\end{equation}
+If the numbers $\{v_0, u_1, u_2, \dots, u_8\}$ are distinct then this maximum value occurs at a unique $i_k=n$ for some $k \in \{0, 1, \dots, 8\}$. Let's consider this case first.
+
+\textbf{(No multiplicities)} We expect this is the generic case, but I think it always provides a sufficient condition even if multiplicities exist.
+We can assume that noise level is below $3/7$ and so we have that $v >u$, so the $0$ component in $\w$, and so also $\w^{\otimes n}$, is the largest.
+But this needs rescaling by $\t$.
+
+We now make use of the freedom to do a Clifford unitary transformation that sends the smallest entry in $\t$ to the $0$ component.
+Note that in doing so we must also account for this Clifford unitary on the output magic state too!
+To get around this we can simply say that we consider $\rho_S(\epsilon )^{\otimes n} \rightarrow \rho_S(\epsilon')^{\otimes m}$ modulo local Clifford unitaries on the output system.
+This changes the rules of the game to suit our needs.
+Instead of distilling out the precise noisy Strange state, we allow the protocol to have arbitrary post-processing on the individual qutrits via reversible Cliffords.
+I.e.~the magic content is the same in each case, but when we consider the problem of how $\tau \rightarrow \tau'$ this can be used to our advantage to simplify our analysis.
+Need to reflect on this variant and how it affects the content of our result.
+
+So given the ability to assume that the smallest entry of $\t$ is the $t_0$ component this means that for noise levels below $3/7$ the largest component of $\tilde{w}_{n,i_0, i_1, \dots, i_8}$ occurs at $(i_0,i_1, \dots, i_8) = (n,0,0,\dots ,0)$.
+We therefore have, for the no-multiplicity case, that the first elbow occurs at the point $(t_0^n, v^n)$.
+This will lead to a bound expression in terms of $\epsilon$ for the output state, together with whatever value $t_0$ takes on.
+\ddd{[give expression]}.
+While this is fine, we need to link $t_0$ to the physics of the state $\tau = e^{-\beta H}/\Z$.
+Well, just from the definition we have that
+\begin{equation}
+t_0 = \frac{1}{d\Z}\tr [ A_{0,0} e^{-\beta H}],
+\end{equation}
+where, of course, $d=3$. So in $t_0^n$ we immediately get a term $\Z^{-n} = e^{-n\beta F}$, which is nice and general. Using the expansion of the thermal state into its energy eigenstates we obtain
+\begin{align}
+t_0^n &= \left ( \frac{1}{d\Z}\tr [ A_{0,0} e^{-\beta H}] \right )^n \nonumber \\
+&= \frac{e^{-n\beta F}}{3^n} ( \tr [ A_{0,0} \sum_k e^{-\beta E_k} |\varphi_k\>\<\varphi_k|])^n\nonumber \\
+&= \frac{e^{-n \beta F}}{3^n} ( \sum_k \alpha_k e^{-\beta E_k})^n,
+\end{align}
+where we define
+\begin{equation}
+\alpha_k \coloneqq \<\varphi_k |A_{0,0} |\varphi_k\>, \mbox{ for }k=0,1,2.
+\end{equation}
+However $A_{0,0} = \sum_{r\in \mathbb{Z}_3} | -r\>\<r|$ and so
+\begin{equation}
+\alpha_k \coloneqq \sum_{r \in \mathbb{Z}_3} \<\varphi_k |-r\> \<r |\varphi_k\>.
+\end{equation}
+This just encodes how the energy eigenbasis of the Hamiltonian $H$ relates to the \emph{stabilizer} basis.
+Anyhow, the nice thing is that we always get the Free energy term emerging in the $t_0^n$ and so we can include this into the distillation bound, with the $\alpha_k$ terms simply handling the messy issue of how the two important bases relate.
+We can package the messy details into some definition in some way.
+E.g.
+the form of the sum involving $\alpha_k$ looks a bit like a partition function, so we can define something like
+\begin{equation}
+\zeta \coloneqq  \sum_k \alpha_k e^{-\beta E_k},
+\end{equation}
+so that
+\begin{equation}
+t_0^n = \frac{e^{-n\beta F}}{3^n}\zeta^n,
+\end{equation}
+which is tidy....and we could also then define $\phi$ as a kind of free energy term via $\zeta \eqqcolon e^{-\beta \phi}$. This then simplifies things to
+\begin{equation}
+t_0^n =  \frac{e^{-n \beta (F+\phi)}}{3^n},
+\end{equation}
+where $F$ corresponds to the physical free energy of $\tau$ while $\phi$ is some weird term that captures the degree to which the energy basis differs from the stabilizer basis.
+\ddd{[Details need tidying/checking and we need the final bounds to be computed.]}
+
+\textbf{(Multiplicity case)} I don't think we really need to delve into this.
+Firstly no multiplicities will be generic.
+Secondly, if multiplicities appear this simply means the above Lorenz curve point is not an elbow but instead as point on the first line segment.
+Imposing the conditions for this point is \emph{also a necessary condition} and therefore suffices to get a bound.
+
 \section{Lower bounds in $\sigma$--fragments}
@@
 		\begin{split}
-		&\text{1. } \Phi_\ell(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ents},\ m\in [1,n-1] \\
-		&\text{2. } \Phi_\ell(m; n, p) \leq 2^{-n\ents},\ m\in [0,np] \\
+		&\text{1. } \Phi_\ell(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n \ent{p}{q}},\ m\in [1,n-1] \\
+		&\text{2. } \Phi_\ell(m; n, p) \leq 2^{-n\ent{p}{q}},\ m\in [0,np] \\
 		&\text{3. } \Phi_\ell(m; n, p) \leq 1 - \left[ 8(m+1)\left(1-\frac{m+1}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m+1}{n}}{p}}, \\
@@
 		\begin{split}
-		&\text{1. } \Phi_{\pm}(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ents},\ m\in [1,n-1] \\
-		&\text{2. } \Phi_{\pm}(m; n, p) \leq 2^{-n\ents},\ m\in [0,np] \\
+		&\text{1. } \Phi_{\pm}(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{p}{q}},\ m\in [1,n-1] \\
+		&\text{2. } \Phi_{\pm}(m; n, p) \leq 2^{-n\ent{p}{q}},\ m\in [0,np] \\
 		&\text{3. } \Phi_{\pm}(m; n, p) \leq 1 - \left[ 8(m+1)\left(1-\frac{m+1}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m+1}{n}}{p}}, \\

### 2021-05-01 magic_paper.tex
Initial changes of theorem statement. Figured out how to have primes and superscripts. More work to come.

@@
 
-This means in particular that $\E(\tau^{\otimes n}) = \tau'$ is a symmetric state on $m$ subsystems, so by the quantum de Finetti theorem~\cite{christandl_2007} we have that
+This means in particular that $\E(\tau^{\otimes n})$ is a symmetric state on $m$ subsystems, so by the quantum de Finetti theorem~\cite{christandl_2007} we have that
 \begin{equation}
-\tau'  = \int d\mu(x) \sigma_x^{\otimes m},
+\E(\tau) \approx \int d\mu(x) \tau_x^{\prime \otimes m},
 \end{equation}
-where $d\mu(x)$ is a probability measure over a set $\{\sigma_x\}$ of single qudit states.
+where $d\mu(x)$ is a probability measure over a set $\{\tau'_x\}$ of single qudit states.
 
@@
 We assume that in the asymptotic/thermodynamic limit $n,m \rightarrow \infty$ that correlations generated in $\sigma$ are negligible.
-This implies that $d\mu(x)$ is peaked on a particular state $\sigma$, and so $\tau' = \sigma^{\otimes m}$.
-Physically, this is a natural scenario -- for example, in the context of traditional thermodynamics, it states that the output system is well-described by intrinsic variables that are encoded in $\sigma$.
+This implies that $d\mu(x)$ is peaked on a particular state $\tau'$, and so $\E(\tau) = \tau^{\prime \otimes m}$.
+Physically, this is a natural scenario -- for example, in the context of traditional thermodynamics, it states that the output system is well-described by intrinsic variables that are encoded in $\tau'$.
 Here, this assumption allows us to associate a free energy per qudit of the output state, which would be more complex if correlations are present.
@@
 
-The action of the protocol on the reference state therefore transforms $\tau^{\otimes n} \rightarrow \E(\tau^{\otimes n}) = \sigma^{\otimes m}$. 
-The output state $\sigma$ is a stabilizer state, provided that $\tau$ is as well and that $\E$ is a free operation, but it is generally a non-equilibrium state for the system.
+The action of the protocol on the reference state therefore transforms $\tau^{\otimes n} \rightarrow \E(\tau^{\otimes n}) = \tau^{\prime \otimes m}$. 
+The output state $\tau'$ is a stabilizer state, provided that $\tau$ is as well and that $\E$ is a free operation, but it is generally a non-equilibrium state for the system.
 However, the distillation bounds that we derive take a particularly simple form if we associate a fiducial Hamiltonian $H'$ to the output state by considering the change $H \rightarrow H'$ such that equilibrium is restored at the reference temperature $T$.
-This allows us to express the state as $\sigma = e^{-\beta H'}/\Z'$.
+This allows us to express the state as $\tau' = e^{-\beta H'}/\Z'$.
 
@@
 The bounds also depend on the overlaps between the Hamiltonian eigenbases and the computational basis $\{\ket{k}\}$, where $k \in \mathbb{Z}_d$.
-For a reference state $\tau$ with associated Hamiltonian $H$ denote the energy eigenbasis by $\{\ket{\phi_k}\}$ and define the \emph{reference partition function $\zeta$} as
+For a reference state $\tau$ with associated Hamiltonian $H$ denote the energy eigenbasis by $\{|\varphi_k\>\}$ and define the \emph{reference partition function $\zeta$} as
 \begin{equation}
@@
 \begin{equation}
-	\alpha_k \coloneqq \sum_{r \in \mathbb{Z}_d} \braket{\phi_k}{-r}\braket{r}{\phi_k}.
+	\alpha_k \coloneqq \sum_{r \in \mathbb{Z}_d} \braket{E_k}{-r}\braket{r}{E_k}.
 \end{equation}
@@
 \begin{theorem}\label{thm:free-energy}
-	Consider a magic distillation protocol that transforms the noisy Strange state
-	\begin{equation*}
-		\rho_S(\epsilon)^{\otimes n} \longrightarrow \E(\rho_S(\epsilon)^{\otimes n})=\rho_S(\epsilon')^{\otimes m} 
-	\end{equation*}
-modulo Clifford operations, with even number of copies $n, m$ and noise levels satisfying $\epsilon' \leq \epsilon \leq 3/7$.
+	Consider a magic distillation protocol that transforms $n$ copies of an $\epsilon$--noisy Strange state into $m$ copies of an $\epsilon'$--noisy Strange state, with depolarisating errors $\epsilon' \leq \epsilon \leq 3/7$.
+Let $T =(k\beta)^{-1}$ be any temperature for the physical system and let $H= \sum_k E_k |E_k\>\<E_k|$ be the Hamiltonian of each qutrit subsystem.
+Assume for $n,m \rightarrow \infty$ that the protocol's channel $\E$ generates negligible correlations on the equilibrium state and so there is a state $\tau'$ such that
+\begin{equation}
+	\tau^{\otimes n} \longrightarrow \E(\tau^{\otimes n}) = \tau^{\prime \otimes m}
+\end{equation} 
+for $n,m \gg 1$. We write the output state as $\tau' = e^{-\beta H'}/\Z'$ for some Hermitian $H'$.
 
-Let $T =(k\beta)^{-1}$ be any characteristic temperature for the physical system and let $H$ be the Hamiltonian of each qutrit subsystem.
-Assume that $n,m \gg 1$, so that the channel $\E$ generates negligible correlations on some product equilibrium state 
+Then there are local Clifford unitaries $C_1,C_2$, such that $\rho_1 := C_1 \rho_S(\epsilon) C_1^\dagger$ and $\rho_2 := C_2 \rho_S(\epsilon') C_2^\dagger$ for which the protocol gives
 \begin{equation}
-	\tau^{\otimes n} \longrightarrow \E(\tau^{\otimes n}) = \sigma^{\otimes m}
+\rho_1^{\otimes n} \longrightarrow \rho_2^{ \otimes m}.
 \end{equation}
-for some state $\sigma = e^{-\beta H'}/\Z'$.
-
-Then, the distillation rate $R = m/n$ of the magic protocol is bounded as:
+Moreover, the the distillation rate $R = m/n$ is bounded as
 \begin{equation}\label{eq:rate_bounds_proof}
@@
 \end{equation}
-where $F, \Phi$ are the free energy and reference free energy defined for state $\tau$, while $F', \Phi'$ are defined for state $\sigma$.
+where $F$ is the free energy of $\tau$,  and 
+\begin{equation}
+\Phi := -\beta^{-1} \log \zeta
+\end{equation}
+and $\zeta$ is given by
+\begin{align}
+\zeta &:= \sum_{k\in \mathbb{Z}_3} \alpha_k e^{-\beta E_k} \nonumber\\
+\alpha_k &:= \sum_{r \in \mathbb{Z}_3} \< E_k |-r\>\<r| E_k\>.
+\end{align}
+The primed variables are defined similarly for the output system.
 \end{theorem}

### 2021-05-01 magic_paper.tex
minor changes

--- 2021-04-29 magic_paper.tex
@@
 The bounds also depend on the overlaps between the Hamiltonian eigenbases and the computational basis $\{\ket{k}\}$, where $k \in \mathbb{Z}_d$.
-For a reference state $\tau$ with associated Hamiltonian $H$ denote the energy eigenbasis by $\{\ket{\phi_k}\}$ and define the \emph{reference partition function $\zeta$} as
+For a reference state $\tau$ with associated Hamiltonian $H$, denote the energy eigenbasis by $\{\ket{\phi_k}\}$ and define the \emph{reference partition function $\zeta$} as
 \begin{equation}
@@
 Coefficients $\alpha_k$ can be negative when the Hamiltonian $H$ does not admit a Wigner-positive decomposition. 
-However, it is simple to see that $\zeta$ is always positive. \nick{because it is proportional to $W_{\tau}(0,0) > 0$ for full-rank, stabilizer $\tau$ - this argument is a bit cyclic}
+However, it is simple to see that $\zeta$ is always positive. \nick{because it is proportional to $W_{\tau}(0,0) > 0$ for full-rank, stabilizer $\tau$}
 We can then naturally associate to the reference state $\tau$ a new form of free energy which is specific to the protocol, which we call the \emph{reference free energy $\Phi$} and define via

### 2021-05-01 magic_paper.tex

--- 2021-05-01 magic_paper.tex
@@
 Coefficients $\alpha_k$ can be negative when the Hamiltonian $H$ does not admit a Wigner-positive decomposition. 
-However, it is simple to see that $\zeta$ is always positive. \nick{because it is proportional to $W_{\tau}(0,0) > 0$ for full-rank, stabilizer $\tau$ - this argument is a bit cyclic}
+However, it is simple to see that $\zeta$ is always positive. \nick{because it is proportional to $W_{\tau}(0,0)$ and $W_{\tau}(0,0) > 0$ for full-rank, stabilizer $\tau$}
 We can then naturally associate to the reference state $\tau$ a new form of free energy which is specific to the protocol, which we call the \emph{reference free energy $\Phi$} and define via
@@
 \begin{theorem}\label{thm:free-energy}
-	Consider a magic distillation protocol that transforms $n$ copies of an $\epsilon$--noisy Strange state into $m$ copies of an $\epsilon'$--noisy Strange state, with depolarisating errors $\epsilon' \leq \epsilon \leq 3/7$.
-Let $T =(k\beta)^{-1}$ be any temperature for the physical system and let $H= \sum_k E_k |E_k\>\<E_k|$ be the Hamiltonian of each qutrit subsystem.
+	Consider a magic distillation protocol that transforms $n$ copies of an $\epsilon$--noisy Strange state into $m$ copies of an $\epsilon'$--noisy Strange state, with depolarising errors $\epsilon' \leq \epsilon \leq 3/7$.
+Let $T =(k\beta)^{-1}$ be any temperature for the physical system and let $H= \sum_{k \in \mathbb{Z}_3} E_k |E_k\>\<E_k|$ be the Hamiltonian of each qutrit subsystem.
 Assume for $n,m \rightarrow \infty$ that the protocol's channel $\E$ generates negligible correlations on the equilibrium state and so there is a state $\tau'$ such that
@@
 \end{equation}
-Moreover, the the distillation rate $R = m/n$ is bounded as
+Moreover, the distillation rate $R = m/n$ is bounded as
 \begin{equation}\label{eq:rate_bounds_proof}
@@
 \end{equation}
-and $\zeta$ is given by
+where $\zeta$ is given by
 \begin{align}
-\zeta &:= \sum_{k\in \mathbb{Z}_3} \alpha_k e^{-\beta E_k} \nonumber\\
+\zeta &:= \sum_{k\in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}, \nonumber\\
 \alpha_k &:= \sum_{r \in \mathbb{Z}_3} \< E_k |-r\>\<r| E_k\>.
@@
 This operation would inevitably affect the magic distillation protocol, but since we consider the state distillation modulo Clifford operations, we are allowed to perform the reverse Clifford operation keeping the magic distillation process as is.
-\nick{I don't understand this too well, how are we allowed to permute $W_\tau$ while keeping $W_\rho$ intact?}
+\nick{statement here is inaccurate}
 
@@
 If the largest rescaled component of a state is distinct with no multiplicities, then these coordinates correspond to the first elbow of the corresponding Lorenz curve, whereas if it appears multiple times, then the coordinates derived correspond to a point on the interior of the line segment connecting the origin to the first elbow.
-In both cases, the bound derived remains the same, as is clear by its derivation in~\cref{app:elb_constraints}, and it is given by $L_0 / x_0 \geq L'_0 / x'_0$, which can be directly rearranged into the stated bound of the theorem.
+In both cases, the distillation bound remains the same, as is clear by its derivation in~\cref{app:elb_constraints}, and it is given by $L_0 / x_0 \geq L'_0 / x'_0$, which can be directly rearranged into the stated bound of the theorem.
 

### 2021-05-03 magic_paper.tex
Details around main theorem basically finalised.

@@
 	A magic protocol aims to turn $n$ copies of some magic state $\rho_1$ to $m$ copies of some other state $\rho_2$.
-	Constraints on the efficiency of the protocol can be imposed by considering its action on an equilibrium state $\tau$.
+	Constraints on the efficiency of the protocol can be imposed by considering its action on an separate probe state $\tau$.
 	\nick{How do we improve the illustration?}
@@
 
-As it is important for the statement of our result, we hasten to note that group averaging of the output system and, indeed, any permutation of the output subsystems can be performed via Clifford unitaries, for example $\rm{SWAP}$ gates, which do not affect the magic output of the protocol, so we consider distillation protocols \emph{modulo Clifford operations}.
-
 This means in particular that $\E(\tau^{\otimes n})$ is a symmetric state on $m$ subsystems, so by the quantum de Finetti theorem~\cite{christandl_2007} we have that
@@
 
-To simplify our analysis we now make the following assumption.
+To simplify our analysis we will make the following assumption.
 We assume that in the asymptotic/thermodynamic limit $n,m \rightarrow \infty$ that correlations generated in $\sigma$ are negligible.
@@
 
-The action of the protocol on the reference state therefore transforms $\tau^{\otimes n} \rightarrow \E(\tau^{\otimes n}) = \tau^{\prime \otimes m}$. 
-The output state $\tau'$ is a stabilizer state, provided that $\tau$ is as well and that $\E$ is a free operation, but it is generally a non-equilibrium state for the system.
-However, the distillation bounds that we derive take a particularly simple form if we associate a fiducial Hamiltonian $H'$ to the output state by considering the change $H \rightarrow H'$ such that equilibrium is restored at the reference temperature $T$.
-This allows us to express the state as $\tau' = e^{-\beta H'}/\Z'$.
+Our analysis will depend on the energetic properties of the probe state $\tau$ and the output state $\tau'$.
+For the state $\tau = e^{-\beta H}/\Z$ we have the Helmholtz free energy $F$ given by
+\begin{equation}
+	F \coloneqq \tr[H \tau] - \beta^{-1}S(\tau) = -\beta^{-1}\log{\Z},
+\end{equation}
+which is obtained from the internal energy via a Legendre transform \ddd{[cite books for $F$ details]}.
 
-Our distillation bounds depend on two properties of the Hamiltonians $H, H'$.
-The first property is the free energy of the states at the reference temperature, so for a state $\tau = e^{-\beta H}/\Z$ we express the associated free energy $F$ as
-\begin{equation}
-	F \coloneqq \tr[H \tau] - \beta^{-1}S(\tau) = -\beta^{-1}\log{\Z}.
-\end{equation}
-The output state $\sigma$ then has free energy $F' = -\beta^{-1} \log \Z'$.
+As mentioned, we can quantify the energetic aspects of a given protocol by considering how it transforms a physical system in state with a clear notion of energy, such as a thermodynamic equilibrium state.
+The protocol transforms this state as $\tau^{\otimes n} \rightarrow \E(\tau^{\otimes n}) = \tau^{\prime \otimes m}$.
+Since the protocol does not, on its own, generate magic the output state $\tau'$ is also a stabilizer state, provided that $\tau$ is as well.
+This is generally a non-equilibrium state for the system.
+However, the distillation bounds that we derive take a particularly simple form if we associate a Hamiltonian $H'$ to the output state by considering the change $H \rightarrow H'$ such that equilibrium is restored at the reference temperature $T$.
+This Hamiltonian is defined by the expression $\tau' = e^{-\beta H'}/\Z'$, and has free energy $F' = -\beta^{-1} \log \Z'$.
 
-The bounds also depend on the overlaps between the Hamiltonian eigenbases and the computational basis $\{\ket{k}\}$, where $k \in \mathbb{Z}_d$.
-For a reference state $\tau$ with associated Hamiltonian $H$ denote the energy eigenbasis by $\{|\varphi_k\>\}$ and define the \emph{reference partition function $\zeta$} as
-\begin{equation}
-	\zeta \coloneqq \sum_{k \in \mathbb{Z}_d} \alpha_k e^{-\beta E_k},
-\end{equation}
-where the overlap coefficients are
-\begin{equation}
-	\alpha_k \coloneqq \sum_{r \in \mathbb{Z}_d} \braket{E_k}{-r}\braket{r}{E_k}.
-\end{equation}
-Coefficients $\alpha_k$ can be negative when the Hamiltonian $H$ does not admit a Wigner-positive decomposition. 
-However, it is simple to see that $\zeta$ is always positive. \nick{because it is proportional to $W_{\tau}(0,0)$ and $W_{\tau}(0,0) > 0$ for full-rank, stabilizer $\tau$}
-We can then naturally associate to the reference state $\tau$ a new form of free energy which is specific to the protocol, which we call the \emph{reference free energy $\Phi$} and define via
-\begin{equation}
-	\Phi \coloneqq -\beta^{-1} \log \zeta.
-\end{equation}
-For the output reference state $\sigma$ with associated Hamiltonian $H'$, we can denote the energy eigenbasis by $\{\ket{\phi'_k}\}$ and similarly define the reference partition function $\zeta'$ and reference free energy $\Phi'$.
+This provides a simple means to specify energetic details of a protocol through how much it would disturb some reference equilibrium state.
+The approach, when combined with relative majorization, also allows us to derive magic distillation bounds that combine both the computational measures $\epsilon,\epsilon'$, with terms that depend on the Hamiltonian of the physical system.
+As discussed in section (blah), from the perspective of majorization the presence of magic can be viewed as a form of non-classical free energy and so it is also of interest to make an explicit link between the amount of magic in a non-equilibrium state $\rho_S(\epsilon)$ and the actual free energy of an equilibrium state $\tau(\beta)$.
 
-Therefore, the action of $\E$ sending $\tau^{\otimes n}$ to $\sigma^{\otimes m}$ is viewed in terms of $\Delta H \coloneqq H'-H$, which is the Hamiltonian change that would be needed to adiabatically restore equilibrium at temperature $T$.
-Given this account of the physical ingredients of a distillation protocol, we now state the following result for the case of qutrits.
+Given this account we now state the following result for the case of $d=3$ qutrits, in which magic distillation protocols are viewed as non-equilibrium processes.
+
 \begin{theorem}\label{thm:free-energy}
-	Consider a magic distillation protocol that transforms $n$ copies of an $\epsilon$--noisy Strange state into $m$ copies of an $\epsilon'$--noisy Strange state, with depolarising errors $\epsilon' \leq \epsilon \leq 3/7$.
-Let $T =(k\beta)^{-1}$ be any temperature for the physical system and let $H= \sum_{k \in \mathbb{Z}_3} E_k |E_k\>\<E_k|$ be the Hamiltonian of each qutrit subsystem.
-Assume for $n,m \rightarrow \infty$ that the protocol's channel $\E$ generates negligible correlations on the equilibrium state and so there is a state $\tau'$ such that
-\begin{equation}
-	\tau^{\otimes n} \longrightarrow \E(\tau^{\otimes n}) = \tau^{\prime \otimes m}
-\end{equation} 
-for $n,m \gg 1$. We write the output state as $\tau' = e^{-\beta H'}/\Z'$ for some Hermitian $H'$.
+	Consider a magic distillation protocol on qutrits that transforms $n$ copies of an $\epsilon$--noisy Strange state into $m$ copies of an $\epsilon'$--noisy Strange state, with depolarising errors $\epsilon' \leq \epsilon \leq 3/7$.
 
-Then there are local Clifford unitaries $C_1,C_2$, such that $\rho_1 := C_1 \rho_S(\epsilon) C_1^\dagger$ and $\rho_2 := C_2 \rho_S(\epsilon') C_2^\dagger$ for which the protocol gives
+	Let $T =(k\beta)^{-1}$ be any temperature for the physical system and let $H= \sum_{k \in \mathbb{Z}_3} E_k |E_k\>\<E_k|$ be the Hamiltonian of each qutrit subsystem in its eigen-decomposition.
+Assume that for $n,m \rightarrow \infty$ the protocol's channel generates negligible correlations on the equilibrium state $\tau$, and so $\tau^{\otimes n} \longrightarrow \tau^{\prime \otimes m}$ for $n,m \gg 1$.
+We write the state $\tau'$ as $\tau' = e^{-\beta H'}/\Z'$ for some Hermitian $H'$.
+
+Given this, there are local Clifford changes of basis $C_1,C_2$, such that $\rho_1 := C_1 \rho_S(\epsilon) C_1^\dagger$ and $\rho_2 := C_2 \rho_S(\epsilon') C_2^\dagger$ for which the protocol gives
 \begin{equation}
@@
 \end{equation}
-Moreover, the distillation rate $R = m/n$ is bounded as
+Moreover, the magic distillation rate $R = m/n$ for the protocol is bounded by the expression
 \begin{equation}\label{eq:rate_bounds_proof}
-	R \leq \dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (\Phi - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (\Phi' - F')},
+	R \leq \dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (\phi - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (\phi' - F')},
 \end{equation}
@@
 \begin{equation}
-\Phi := -\beta^{-1} \log \zeta
+\phi = -\beta^{-1} \log \zeta
 \end{equation}
-where $\zeta$ is given by
+with $\zeta$ given by the equations
 \begin{align}
-\zeta &:= \sum_{k\in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}, \nonumber\\
-\alpha_k &:= \sum_{r \in \mathbb{Z}_3} \< E_k |-r\>\<r| E_k\>.
+\zeta &= \sum_{k\in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}, \nonumber\\
+\alpha_k &= \sum_{r \in \mathbb{Z}_3} \braket{E_k}{-r}\braket{r}{E_k}.
 \end{align}
@@
 \end{theorem}
+The above bound depends on: (a) quantum computational measures $\epsilon, \epsilon'$, (b) thermodynamic quantities $F, F',$  and (c) intermediate terms $\phi, \phi'$.
+The intermediate terms depend on how the energy eigenbasis of the system $\{|E_k\>\}$ relates to the computational stabilizer basis $\{|k\>\}$.
+In particular the energetic term $\phi$ quantifies the degree to which the negativity in the Wigner representation can be ascribed a sharp energetic value for the given Hamiltonian of the system.
+Its form is similar to $F$, and so can informally be viewed as a `magic free energy' term, associated to a `partition function' $\zeta$.
+While the coefficients $\alpha_k$ may be negative for some $k$, the quantity $\phi$ is always well-defined since the function $\zeta$ is proportional to the Wigner component $W_\tau(0,0)$, which is strictly positive.
+
+The sole purpose of the Clifford unitaries $C_1,C_2$ is to simplify the form of the $\alpha_k$ coefficients.
+For example, if $H=Z$ then the energy eigenbasis is equivalent to the computational basis up to a Fourier transform, and so $\phi$ would have a sharp, temperature-independent value $\phi \in \{E_0,E_1,E_2\}$ once we account for the Clifford change in basis.
+
+The above analysis makes simplifying assumptions that could easily be dropped, at the price of more complex expressions.
+For example, we can obtain general expressions without any assumptions on $\epsilon,\epsilon'$ or drop the Clifford change in basis.
+We could also perform similar analysis for general qudits, and different choices of magic states.
+It might also be of interest consider other choices of reference states that may include more appropriate hardware physics, for example for photonic set-ups.
+
+The only non-trivial assumption is the assumption that we can ignore correlations in the thermodynamic limit.
+This is a common situation in thermodynamics, where correlations are often sub-linear in the particle number in the macroscopic limit.
+One could perturb about this scenario, and make use of variational tools such as the Bogoliubov inequality \ddd{[cite]} for approximating the free energy of a system, to obtain bounds in a similar form.
+
+\newpage
 \begin{proof}	
@@
 \begin{equation}
-	H = \sum_{k \in \mathbb{Z}_3} E_k\ketbra{\phi_k}{\phi_k},
+	H = \sum_{k \in \mathbb{Z}_3} E_k\ketbra{E_k}{E_k},
 \end{equation}
@@
 	W_{\tau}(0,0) &= \frac{1}{3\Z}\tr\left[ A_{0,0}e^{\beta H} \right] \nonumber\\
-	&= \frac{e^{\beta F}}{3} \tr\left[ \sum_{r \in \mathbb{Z}_3} \ketbra{-r}{r}\sum_{k \in \mathbb{Z}_3} e^{\beta E_k}\ketbra{\phi_k}{\phi_k} \right] \\
+	&= \frac{e^{\beta F}}{3} \tr\left[ \sum_{r \in \mathbb{Z}_3} \ketbra{-r}{r}\sum_{k \in \mathbb{Z}_3} e^{\beta E_k}\ketbra{E_k}{E_k} \right] \\
 	&= \frac{e^{\beta F}}{3} \sum_{r \in \mathbb{Z}_3} \alpha_k e^{\beta E_k}
 	= \frac{e^{\beta F}}{3} \zeta \\
-	&= \frac{e^{\beta (F - \Phi)}}{3},
+	&= \frac{e^{\beta (F - \phi)}}{3},
 \end{align}
-where $\alpha_k, \zeta$ and $\Phi$ are as defined prior to the statement of the theorem.
+where $\alpha_k, \zeta$ and $\phi$ are as defined prior to the statement of the theorem.
 Finally, the coordinates can be expressed as
 \begin{equation}
-	(x_0, L_0) = \left( \frac{e^{n\beta (F - \Phi)}}{3^n}, v(\epsilon)^n \right).
+	(x_0, L_0) = \left( \frac{e^{n\beta (F - \phi)}}{3^n}, v(\epsilon)^n \right).
 \end{equation}
@@
 \begin{equation}
-	(x'_0, L'_0) = \left( \frac{e^{n\beta (F' - \Phi')}}{3^n}, v(\epsilon')^n \right).
+	(x'_0, L'_0) = \left( \frac{e^{n\beta (F' - \phi')}}{3^n}, v(\epsilon')^n \right).
 \end{equation}

### 2021-05-03 magic_paper.tex
Free energy bound proof pushed to appendices. Bound added from basic channel constraints. To be compared.

@@
 We can therefore define the following sub-theory of any magic theory $\R$.
-\begin{definition}[\textbf{$\boldsymbol\sigma$--fragment}]\label{def:sigmafrag}
+\begin{definition}\label{def:sigmafrag}
    Given a theory of magic $\R = (\F, \O)$, the \emph{$\sigma$--fragment of $\R$} is the sub-theory $\R_\sigma = (\F, \O_\sigma)$, in which the free operations are 
@@
 \end{theorem}
+The proof of this is provided in Appendix \ref{free-energy-bound-proof}, and is a generalization of the analysis for unital protocols.
+
 The above bound depends on: (a) quantum computational measures $\epsilon, \epsilon'$, (b) thermodynamic quantities $F, F',$  and (c) intermediate terms $\phi, \phi'$.
@@
 
-\newpage
-\begin{proof}	
-For the sake of clarity, we write $\rho_n \coloneqq \rho_S(\epsilon)^{\otimes n}$, $\rho'_m \coloneqq \rho_S(\epsilon')^{\otimes m}$, $\tau_n \coloneqq \tau^{\otimes m}$ and $\sigma_m \coloneqq \sigma^{\otimes m}$.
-
-To establish the distillation bound we consider the distillation protocol that gives $\E( \rho_n) = \rho_m$ for the magic states. 
-We then consider that the protocol transforms the reference equilibrium state as $\E( \tau_n) = \sigma_m$.
-Since $\tau$ and $\sigma$ are assumed to be full rank stabilizer states, they have a strictly positive Wigner distribution, while, in contrast, the input and output magic states generally have quasi-probability Wigner distributions.
-For any such protocol we therefore have that
-\begin{equation}
-	( W_{\rho_n}(\bmx), W_{\tau_n}(\bmx) ) \succ ( W_{\rho'_m}(\bmx), W_{\sigma_m}(\bmx) ),
-\end{equation}
-or, equivalently, in terms of the relevant Lorenz curves,
-\begin{equation}
-	L_{\rho_n |\tau_n}(x) \ge L_{\rho'_m |\sigma_m}(x) \mbox{ for all } x.
-\end{equation}
-
-We define the rescaled Wigner distribution $W_{\rho | \tau}(\x) \coloneqq W_\rho(\x)/W_\tau(\x)$, which is always well-defined since $\tau$ is full-rank. 
-Due to the multiplicative property of the Wigner distribution, the rescaled distribution is also multiplicative in the sense that
-\begin{equation}
-	W_{\rho \otimes \rho' | \tau \otimes \tau'} (\x_1 \oplus \x_2) = W_{\rho | \tau}(\x_1)W_{\rho' | \tau'}(\x_2),
-\end{equation}
-for any states $\rho, \rho'$ and any full-rank stabilizer states $\tau, \tau'$.
-Therefore we have that
-\begin{align}
-	W_{\rho_n |\tau_n} (\x) &= \prod_{i=1}^n W_{\rho|\tau}(\x_i)\\
-	W_{\rho_n } (\x) &= \prod_{i=1}^n W_\rho(\x_i)
-\end{align}
-where $\x = \oplus_{i=1}^n \x_i \in \mathbb{Z}_3^n$ is the phase space point for the full system in terms of those of the individual subsystems.
-
-The points defining the Lorenz curve $L_{\rho_n |\tau_n}(x)$ are obtained from sorting the components of $W_{\rho_n |\tau_n}(\x)$ in non-increasing order and then computing the partial sums of $W_{\rho_n |\tau_n}(\pi(\x))$ where $\pi$ is the permutation that realises the sorting.
-However, similarly to the unital fragment analysis, we aim to use the constraint that is obtained by considering the line segment connecting the origin to the first elbow of both Lorenz curves.
-The proof of this constraint is provided in~\cref{app:elb_constraints}.
-Therefore, we focus on finding the coordinates of some point on this line segment of the Lorenz curves.
-
-We find the coordinates for the input Lorenz curve, but the exact same analysis can be applied on the output Lorenz curve.
-The Wigner distribution of a single noisy Strange state consists of 1 negative component $W_{\rho}(0,0) = -v(\epsilon)$ and 8 positive components $W_{\rho}(\bmx) = u(\epsilon)$ for $\bmx \neq \bmo$.
-The Wigner distribution of the full-rank, stabilizer equilibrium state $\tau$ is $W_{\tau}(\bmx) > 0$ for all $\bmx \in \mathbb{Z}_3^2$.
-We keep the components completely general.
-
-Assume that the smallest component of the equilibrium state distribution is $W_{\tau}(i,j)$.
-We then make use of the freedom to apply Clifford unitaries in order to perform the  Clifford operation
-\begin{equation}
-	\tau \longrightarrow X^{-i}Z^{-j}\ \tau\ Z^{j}X^{i},
-\end{equation}
-which permutes the smallest component to the origin of the phase space, $W_{\tau}(i,j) \longrightarrow W_{\tau}(0,0)$.
-This operation would inevitably affect the magic distillation protocol, but since we consider the state distillation modulo Clifford operations, we are allowed to perform the reverse Clifford operation keeping the magic distillation process as is.
-\nick{statement here is inaccurate}
-
-The rescaled distribution components are in general given by
-\begin{equation}
-	W_{\rho_n|\tau_n} = \left(\frac{-v}{W_{\tau}(0,0)}\right)^{i_{\bmo}} \prod_{\bmx \neq \bmo} \left(\frac{u}{W_{\tau}(\bmx)}\right)^{i_{\bmx}},
-\end{equation}
-where the (integer) indices obey the following conditions:
-\begin{align}
-&0 \leq i_{\bmx} \leq n \mbox{ for all } \bmx \in \mathbb{Z}_3^2, \nonumber \\
-&\sum_{\bmx \in \mathbb{Z}_3^2} i_{\bmx} = n.
-\end{align}
-It is now easy to find the largest rescaled component.
-Firstly, note that $n$ is even, so we require that $i_{\bmo} \in \{0,2,\dots,n\}$ for the component to be positive.
-Then, we have that $v \geq u$ because $\epsilon \leq 3/7$, and we have already ensured that $W_{\tau}(0,0) \leq W_{\tau}(\bmx)$ for all $\bmx \in \mathbb{Z}_3^2$.
-Therefore, the largest rescaled component occurs when $i_{\bmo} = n$ and $i_{\bmx} = 0$ for $\bmx \neq \bmo$ and is equal to $(v/W_{\tau}(0,0))^n$.
-Accordingly, the coordinates of the first Lorenz curve point after the origin are given by
-\begin{equation}
-	(x_0, L_0) = ((W_{\tau}(0,0))^n, v^n)
-\end{equation}
-
-Given a Hamiltonian decomposition,
-\begin{equation}
-	H = \sum_{k \in \mathbb{Z}_3} E_k\ketbra{E_k}{E_k},
-\end{equation}
-we can re-express the coordinate location, by writing
-\begin{align}
-	W_{\tau}(0,0) &= \frac{1}{3\Z}\tr\left[ A_{0,0}e^{\beta H} \right] \nonumber\\
-	&= \frac{e^{\beta F}}{3} \tr\left[ \sum_{r \in \mathbb{Z}_3} \ketbra{-r}{r}\sum_{k \in \mathbb{Z}_3} e^{\beta E_k}\ketbra{E_k}{E_k} \right] \\
-	&= \frac{e^{\beta F}}{3} \sum_{r \in \mathbb{Z}_3} \alpha_k e^{\beta E_k}
-	= \frac{e^{\beta F}}{3} \zeta \\
-	&= \frac{e^{\beta (F - \phi)}}{3},
-\end{align}
-where $\alpha_k, \zeta$ and $\phi$ are as defined prior to the statement of the theorem.
-Finally, the coordinates can be expressed as
-\begin{equation}
-	(x_0, L_0) = \left( \frac{e^{n\beta (F - \phi)}}{3^n}, v(\epsilon)^n \right).
-\end{equation}
-In the same manner, we can derive the first point coordinates of the output Lorenz curve as
-\begin{equation}
-	(x'_0, L'_0) = \left( \frac{e^{n\beta (F' - \phi')}}{3^n}, v(\epsilon')^n \right).
-\end{equation}
-
-If the largest rescaled component of a state is distinct with no multiplicities, then these coordinates correspond to the first elbow of the corresponding Lorenz curve, whereas if it appears multiple times, then the coordinates derived correspond to a point on the interior of the line segment connecting the origin to the first elbow.
-In both cases, the distillation bound remains the same, as is clear by its derivation in~\cref{app:elb_constraints}, and it is given by $L_0 / x_0 \geq L'_0 / x'_0$, which can be directly rearranged into the stated bound of the theorem.
-
-\end{proof}
-
+\subsection{Variation of bounds with physical parameters and constraints from complete positivity}
 The bounds derived are based on analysis of only part of the Lorenz curves and can be improved via a finer analysis.
@@
 Specifically, the existing bounds follow by considering the dominant terms in the rescaled Wigner distribution and do not, for example, take into account the Lorenz curve's peak structure.
+
+\ddd{[To be tidied+blended]} We also note that one can obtain another set of general distillation bounds from the monotonicity of discrimination measures under quantum channels.
+For example, the $L_1$ norm is contractive under quantum channels so that
+\begin{equation}
+|| \rho - \sigma||_1 \ge ||\E(\rho) - \E(\sigma)||_1,
+\end{equation}
+for any quantum channel $\E$.
+Therefore, beyond the constraint that the magic protocol corresponds to a stochastic map in the Wigner distribution, we also have constraints coming from complete-positivity and trace-preservation.
+For example, is $D(\rho,\sigma)$ is a contractive measure on pairs of quantum states that is also additive, in the sense that $D(\rho^{\otimes n}, \sigma^{\otimes n}) = n D(\rho, \sigma)$, then it is readily seen that within the context of the above theorem we also have,
+\begin{equation}
+R \le \frac{D(\rho_S(\epsilon),\tau)}{D(\rho_S(\epsilon'), \tau')},
+\end{equation}
+provided the denominator does not vanish.
+In particular we can choose the Renyi-divergences $D_\alpha(\rho ||\tau)$....or more concretely the von Neumann divergence $S(\rho ||\tau) = \tr[ \rho \log \rho - \rho \log \tau]$.
+However, if $\tau$ is taken to be a Gibbs state then $S(\rho ||\tau) = \beta (F[\rho] - F[\tau])$, namely the difference in free energies of the two states.
+Here we define
+\begin{equation}
+F[\rho] := \tr[H \rho] - \beta^{-1} S(\rho).
+\end{equation}
+  Therefore, simply from the fact that the protocol defines a channel, we obtain the bound
+\begin{equation}
+R \le \frac{F[\rho_S(\epsilon)] - F[\tau]}{F[\rho_S(\epsilon')] - F[\tau']},
+\end{equation}
+and so we can compare this with the above bounds \ddd{[Some numerics on this to compare?]}
 
@@
     \centering
-    \includegraphics[scale=0.45]{figs/rate_scatter.pdf}
+    \includegraphics[scale=0.4]{figs/rate_scatter.pdf}
     \caption{\textbf{Temperature-dependent bounds for magic distillation.}

### 2021-05-03 magic_paper.tex
minor changes

--- 2021-05-01 magic_paper.tex
@@
 Let $T =(k\beta)^{-1}$ be any temperature for the physical system and let $H= \sum_{k \in \mathbb{Z}_3} E_k |E_k\>\<E_k|$ be the Hamiltonian of each qutrit subsystem.
-Assume for $n,m \rightarrow \infty$ that the protocol's channel $\E$ generates negligible correlations on the equilibrium state and so there is a state $\tau'$ such that
+
+Assume for $n,m \rightarrow \infty$ that the protocol's channel $\E$ generates negligible correlations on the equilibrium state, so there is a state $\tau'$ such that
 \begin{equation}
@@
 \end{equation} 
-for $n,m \gg 1$. We write the output state as $\tau' = e^{-\beta H'}/\Z'$ for some Hermitian $H'$.
+for $n,m \gg 1$. 
+We write the output state as $\tau' = e^{-\beta H'}/\Z'$ for some Hermitian $H'$.
 

### 2021-05-04 magic_paper.tex
Tidying of Outlook. More tidying to do.

--- 2021-05-03 magic_paper.tex
@@
 
+\newpage
 \section{Free energy dependent bounds for magic state distillation protocols}
@@
 In particular it has been shown that stochastic independence (no correlations) of independent distributions can be viewed as a resource in an extension of catalytic majorization, and leads to a single-shot operational interpretation of the Shannon entropy.
-\nick{cite David?}
+\ddd{[cite: look up papers by Marcus Mueller.
+He has about 3 or 4 on this.
+Also Mark Wilde has a paper on it]}
 
@@
 One could perturb about this scenario, and make use of variational tools such as the Bogoliubov inequality \ddd{[cite]} for approximating the free energy of a system, to obtain bounds in a similar form.
-
-\subsection{Variation of bounds with physical parameters and constraints from complete positivity}
-The bounds derived are based on analysis of only part of the Lorenz curves and can be improved via a finer analysis.
-This is apparent by simple numerical calculations on the entirety of the curves as seen in~\cref{fig:distill_bounds} for the case of unital operations.
-Specifically, the existing bounds follow by considering the dominant terms in the rescaled Wigner distribution and do not, for example, take into account the Lorenz curve's peak structure.
-
-\ddd{[To be tidied+blended]} We also note that one can obtain another set of general distillation bounds from the monotonicity of discrimination measures under quantum channels.
-For example, the $L_1$ norm is contractive under quantum channels so that
-\begin{equation}
-|| \rho - \sigma||_1 \ge ||\E(\rho) - \E(\sigma)||_1,
-\end{equation}
-for any quantum channel $\E$.
-Therefore, beyond the constraint that the magic protocol corresponds to a stochastic map in the Wigner distribution, we also have constraints coming from complete-positivity and trace-preservation.
-For example, is $D(\rho,\sigma)$ is a contractive measure on pairs of quantum states that is also additive, in the sense that $D(\rho^{\otimes n}, \sigma^{\otimes n}) = n D(\rho, \sigma)$, then it is readily seen that within the context of the above theorem we also have,
-\begin{equation}
-R \le \frac{D(\rho_S(\epsilon),\tau)}{D(\rho_S(\epsilon'), \tau')},
-\end{equation}
-provided the denominator does not vanish.
-In particular we can choose the Renyi-divergences $D_\alpha(\rho ||\tau)$....or more concretely the von Neumann divergence $S(\rho ||\tau) = \tr[ \rho \log \rho - \rho \log \tau]$.
-However, if $\tau$ is taken to be a Gibbs state then $S(\rho ||\tau) = \beta (F[\rho] - F[\tau])$, namely the difference in free energies of the two states.
-Here we define
-\begin{equation}
-F[\rho] := \tr[H \rho] - \beta^{-1} S(\rho).
-\end{equation}
-  Therefore, simply from the fact that the protocol defines a channel, we obtain the bound
-\begin{equation}
-R \le \frac{F[\rho_S(\epsilon)] - F[\tau]}{F[\rho_S(\epsilon')] - F[\tau']},
-\end{equation}
-and so we can compare this with the above bounds \ddd{[Some numerics on this to compare?]}
-
-\nick{FIX} As a special case of the result, suppose that $H=H'$, implying that the protocol leaves the equilibrium state unchanged, hence it corresponds to a Gibbs-preserving map~\cite{faist_2015}.
-In the more general case, $\Delta F \coloneqq F' - F \ne 0$ and we have a free energy difference between the initial and final states, with respect to the relevant Hamiltonians.
-This is similar to the free energy differences that occur in fluctuation relations, where the final state of the system can be arbitrarily far from equilibrium, yet a free energy term for the final system still arises.
-
-\nick{FIX} The above bounds mainly demonstrate how one can use relative majorization of quasi-distributions to incorporate additional information into distillation bounds.
-However to unpack the results more it is useful to consider the case in which $H=H'$, and look at $\epsilon' \rightarrow 0$.
-For this we obtain~\cref{fig:rate_contour} which gives a contour plot of $R$ as a function of inverse temperature $\beta$ and depolarising noise level $\epsilon$ for the initial noisy magic state.
 \begin{figure}[t!]
@@
 \end{figure}
+\subsection{Variation of bounds with physical parameters}
+The bounds derived are based on analysis of only part of the Lorenz curves and can be improved via a finer analysis.
+This is apparent by simple numerical calculations on the entirety of the curves as seen in~\cref{fig:distill_bounds} for the case of unital operations.
+Specifically, the existing bounds follow by considering the dominant terms in the rescaled Wigner distribution and do not, for example, take into account the Lorenz curve's peak structure.
+
+\nick{FIX} As a special case of the result, suppose that $H=H'$, implying that the protocol leaves the equilibrium state unchanged, hence it corresponds to a Gibbs-preserving map~\cite{faist_2015}.
+In the more general case, $\Delta F \coloneqq F' - F \ne 0$ and we have a free energy difference between the initial and final states, with respect to the relevant Hamiltonians.
+This is similar to the free energy differences that occur in fluctuation relations, where the final state of the system can be arbitrarily far from equilibrium, yet a free energy term for the final system still arises.
+
+\ddd{[Need some numerics on varying the $F'$ case]}
+\nick{FIX} The above bounds mainly demonstrate how one can use relative majorization of quasi-distributions to incorporate additional information into distillation bounds.
+However to unpack the results more it is useful to consider the case in which $H=H'$, and look at $\epsilon' \rightarrow 0$.
+For this we obtain~\cref{fig:rate_contour} which gives a contour plot of $R$ as a function of inverse temperature $\beta$ and depolarising noise level $\epsilon$ for the initial noisy magic state.
 
@@
 We have described how relative majorization can be used to establish upper bounds on magic distillation protocols that take into account additional physics of the system.
-Given this, one might wonder if this approach could also provide \emph{lower bounds} for distillation protocols.
+Our bounds only exploited the very simplest aspects of the Lorenz curves of the quasi-distributions, and so it would be of interest to sharpen these bounds and exploit more of the structure in the asymptotic limit.
+This raises interesting questions that do no arise for probability distributions, because we no longer have a notion of typicality and the central limit theorem does not apply.
+That said, for special states such as the Strange state the asymptotic behaviour is relatively simple and so one could study this and obtain a better handle on the $n\rightarrow \infty$ behaviour in a way.
+In appendix (\ddd{BLAH} we give some basic relations on this that could be explored further.
+\ddd{[where did the remainder term bounds go?
+People could potentially build on this]}
+
+One might wonder if this approach could also provide \emph{lower bounds} for distillation protocols.
 Now, in contrast to the upper bounds, it is necessary to include the symplectic constraints on the phase space into the majorization relations.
 
-  For example, the Clifford group action on a quantum system corresponds to the action of the affine symplectic group on the discrete phase space.
+  For example, the Clifford group action on a quantum system corresponds to the action of the affine symplectic group \ddd{[cite Gross discrete Hudson paper, and some maths source on symplectic group]} on the discrete phase space.
 Therefore, any convex mixture of Clifford unitaries will correpond to a convex mixture of these group actions.
-From the Hardy-Littlewood theorem, we know that traditional majorization is obtained from convex mixtures of arbitrary permutations.
+From the Hardy-Littlewood theorem \ddd{[cite]}, we know that traditional majorization is obtained from convex mixtures of arbitrary permutations.
 However this has been generalised to convex mixtures of elements of a group $G$ that acts on vectors.
-This $G$--majorization has been studied in the classical literature and a range of results are known about it.
-For example, if $G$ is a finite reflection group then the $G$--majorization pre-order is described by a finite list of conditions, just as happens for the full majorization ordering.
+This $G$--majorization has been studied in the classical literature and a range of results are known about it \ddd{[cite papers]}.
+For example, if $G$ is a finite reflection group then the $G$--majorization pre-order is described by a finite list of conditions\ddd{[cite]}, just as happens for the full majorization ordering.
 One route is therefore to consider reflection sub-groups of the affine symplectic group, for which the majorization relation reduces to a finite set of conditions.
@@
 This would correspond to transformations that are \emph{not} unital, but still respect the symplectic structure.
-Physically, this regime would correspond to a form of thermo-majorization obtained from looking at the action of the Clifford group at a micro-canonical level, and then reducing to a small subsystem.
+Physically, this regime would correspond to a form of thermo-majorization obtained from looking at the action of the Clifford group at a micro-canonical level, and then reducing to a small subsystem \ddd{[cite stat-mech book, cite Matteo review]}.
 While this seems like a painful thing to consider, there is motivation for this beyond the aim of constructing lower bounds for magic protocols: in the case of statistical mechanics on a phase space this is precisely the situation, albeit in the continuum limit.
-Statistical mechanics of actual systems obey Hamiltonian dynamics and so automatically respect a symplectic form.
+Statistical mechanics of actual systems obey Hamiltonian dynamics and so automatically respect a symplectic form \ddd{[cite a stat-mech book]}.
 Therefore the pre-order of statistical mechanical states with respect to phase space dynamics preserving a Gibbs state must correspond to a symplectic thermo-majorization condition.
@@
 for a particle on a ring) or by first studying the discrete case.
+Such scenarios also arise in the Quantum Hall Effect \ddd{[cite]} and so this is another regime in which these techniques might be of use.
 
-In this work we have looked at magic through the lens of thermodynamics. Specifically, we find that it can be viewed as a strictly non-classical form of non-equilibrium free energy.
-
-Our work also raises a fundamental question that is also of interest in statistical mechanics. Specifically: what are the majorization conditions that respect the symplectic structure of phase space?
+Finally, it would be of interest to consider the possibility of applying these techniques to other scenarios in which one wishes to distinguish classical from non-classical behaviour based on quasi-probability representations \ddd{[cite quantum optics reference, cite Ferrie review on quasi-reps]}
 

### 2021-05-04 magic_paper.tex
More tidying. Many blue text points to be done.

@@
 
-We approach this problem using tools from statistical mechanics and recent work from the overlap of thermodynamics and quantum information theory~\cite{cit:gour, cit:gour2}\nick{You had a specific review in mind I think, which one?} .
+We approach this problem using tools from statistical mechanics and recent work from the overlap of thermodynamics and quantum information theory~\cite{cit:gour, cit:gour2}\nick{You had a specific review in mind I think, which one?}.
 In particular, we shall view \emph{magic as a form of free energy}, relative to the set of stabilizer states.

### 2021-05-04 appendix.tex

@@
 
-\begin{theorem}\label{thm:free-energy}
+\begin{theorem}
 	Consider a magic distillation protocol transforming noisy Strange state
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newpage
+\subsection{Free energy dependent magic distillation bounds}\label{free-energy-bound-proof}
+Here we prove theorem \ref{thm:free-energy}, which bounds magic distillation rates in terms of free energies.
+
+\begin{theorem}
+	Consider a magic distillation protocol on qutrits that transforms $n$ copies of an $\epsilon$--noisy Strange state into $m$ copies of an $\epsilon'$--noisy Strange state, with depolarising errors $\epsilon' \leq \epsilon \leq 3/7$.
+
+	Let $T =(k\beta)^{-1}$ be any temperature for the physical system and let $H= \sum_{k \in \mathbb{Z}_3} E_k |E_k\>\<E_k|$ be the Hamiltonian of each qutrit subsystem in its eigen-decomposition.
+Assume that for $n,m \rightarrow \infty$ the protocol's channel generates negligible correlations on the equilibrium state $\tau$, and so $\tau^{\otimes n} \longrightarrow \tau^{\prime \otimes m}$ for $n,m \gg 1$.
+We write the state $\tau'$ as $\tau' = e^{-\beta H'}/\Z'$ for some Hermitian $H'$.
+
+Given this, there are local Clifford changes of basis $C_1,C_2$, such that $\rho_1 := C_1 \rho_S(\epsilon) C_1^\dagger$ and $\rho_2 := C_2 \rho_S(\epsilon') C_2^\dagger$ for which the protocol gives
+\begin{equation}
+\rho_1^{\otimes n} \longrightarrow \rho_2^{ \otimes m}.
+\end{equation}
+Moreover, the magic distillation rate $R = m/n$ for the protocol is bounded by the expression
+\begin{equation}\label{eq:rate_bounds_proof}
+	R \leq \dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (\phi - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (\phi' - F')},
+\end{equation}
+where $F$ is the free energy of $\tau$,  and 
+\begin{equation}
+\phi = -\beta^{-1} \log \zeta
+\end{equation}
+with $\zeta$ given by the equations
+\begin{align}
+\zeta &= \sum_{k\in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}, \nonumber\\
+\alpha_k &= \sum_{r \in \mathbb{Z}_3} \braket{E_k}{-r}\braket{r}{E_k}.
+\end{align}
+The primed variables are defined similarly for the output system.
+\end{theorem}
+
+\begin{proof}	
+For the sake of clarity, we write $\rho_n \coloneqq \rho_S(\epsilon)^{\otimes n}$, $\rho'_m \coloneqq \rho_S(\epsilon')^{\otimes m}$, $\tau_n \coloneqq \tau^{\otimes m}$ and $\sigma_m \coloneqq \sigma^{\otimes m}$.
+
+To establish the distillation bound we consider the distillation protocol that gives $\E( \rho_n) = \rho_m$ for the magic states. 
+We then consider that the protocol transforms the reference equilibrium state as $\E( \tau_n) = \sigma_m$.
+Since $\tau$ and $\sigma$ are assumed to be full rank stabilizer states, they have a strictly positive Wigner distribution, while, in contrast, the input and output magic states generally have quasi-probability Wigner distributions.
+For any such protocol we therefore have that
+\begin{equation}
+	( W_{\rho_n}(\bmx), W_{\tau_n}(\bmx) ) \succ ( W_{\rho'_m}(\bmx), W_{\sigma_m}(\bmx) ),
+\end{equation}
+or, equivalently, in terms of the relevant Lorenz curves,
+\begin{equation}
+	L_{\rho_n |\tau_n}(x) \ge L_{\rho'_m |\sigma_m}(x) \mbox{ for all } x.
+\end{equation}
+
+We define the rescaled Wigner distribution $W_{\rho | \tau}(\x) \coloneqq W_\rho(\x)/W_\tau(\x)$, which is always well-defined since $\tau$ is full-rank. 
+Due to the multiplicative property of the Wigner distribution, the rescaled distribution is also multiplicative in the sense that
+\begin{equation}
+	W_{\rho \otimes \rho' | \tau \otimes \tau'} (\x_1 \oplus \x_2) = W_{\rho | \tau}(\x_1)W_{\rho' | \tau'}(\x_2),
+\end{equation}
+for any states $\rho, \rho'$ and any full-rank stabilizer states $\tau, \tau'$.
+Therefore we have that
+\begin{align}
+	W_{\rho_n |\tau_n} (\x) &= \prod_{i=1}^n W_{\rho|\tau}(\x_i)\\
+	W_{\rho_n } (\x) &= \prod_{i=1}^n W_\rho(\x_i)
+\end{align}
+where $\x = \oplus_{i=1}^n \x_i \in \mathbb{Z}_3^n$ is the phase space point for the full system in terms of those of the individual subsystems.
+
+The points defining the Lorenz curve $L_{\rho_n |\tau_n}(x)$ are obtained from sorting the components of $W_{\rho_n |\tau_n}(\x)$ in non-increasing order and then computing the partial sums of $W_{\rho_n |\tau_n}(\pi(\x))$ where $\pi$ is the permutation that realises the sorting.
+However, similarly to the unital fragment analysis, we aim to use the constraint that is obtained by considering the line segment connecting the origin to the first elbow of both Lorenz curves.
+The proof of this constraint is provided in~\cref{app:elb_constraints}.
+Therefore, we focus on finding the coordinates of some point on this line segment of the Lorenz curves.
+
+We find the coordinates for the input Lorenz curve, but the exact same analysis can be applied on the output Lorenz curve.
+The Wigner distribution of a single noisy Strange state consists of 1 negative component $W_{\rho}(0,0) = -v(\epsilon)$ and 8 positive components $W_{\rho}(\bmx) = u(\epsilon)$ for $\bmx \neq \bmo$.
+The Wigner distribution of the full-rank, stabilizer equilibrium state $\tau$ is $W_{\tau}(\bmx) > 0$ for all $\bmx \in \mathbb{Z}_3^2$.
+We keep the components completely general.
+
+Assume that the smallest component of the equilibrium state distribution is $W_{\tau}(i,j)$.
+We then make use of the freedom to apply Clifford unitaries in order to perform the  Clifford operation
+\begin{equation}
+	\tau \longrightarrow X^{-i}Z^{-j}\ \tau\ Z^{j}X^{i},
+\end{equation}
+which permutes the smallest component to the origin of the phase space, $W_{\tau}(i,j) \longrightarrow W_{\tau}(0,0)$.
+This operation would inevitably affect the magic distillation protocol, but since we consider the state distillation modulo Clifford operations, we are allowed to perform the reverse Clifford operation keeping the magic distillation process as is.
+\nick{statement here is inaccurate}
+
+The rescaled distribution components are in general given by
+\begin{equation}
+	W_{\rho_n|\tau_n} = \left(\frac{-v}{W_{\tau}(0,0)}\right)^{i_{\bmo}} \prod_{\bmx \neq \bmo} \left(\frac{u}{W_{\tau}(\bmx)}\right)^{i_{\bmx}},
+\end{equation}
+where the (integer) indices obey the following conditions:
+\begin{align}
+&0 \leq i_{\bmx} \leq n \mbox{ for all } \bmx \in \mathbb{Z}_3^2, \nonumber \\
+&\sum_{\bmx \in \mathbb{Z}_3^2} i_{\bmx} = n.
+\end{align}
+It is now easy to find the largest rescaled component.
+Firstly, note that $n$ is even, so we require that $i_{\bmo} \in \{0,2,\dots,n\}$ for the component to be positive.
+Then, we have that $v \geq u$ because $\epsilon \leq 3/7$, and we have already ensured that $W_{\tau}(0,0) \leq W_{\tau}(\bmx)$ for all $\bmx \in \mathbb{Z}_3^2$.
+Therefore, the largest rescaled component occurs when $i_{\bmo} = n$ and $i_{\bmx} = 0$ for $\bmx \neq \bmo$ and is equal to $(v/W_{\tau}(0,0))^n$.
+Accordingly, the coordinates of the first Lorenz curve point after the origin are given by
+\begin{equation}
+	(x_0, L_0) = ((W_{\tau}(0,0))^n, v^n)
+\end{equation}
+
+Given a Hamiltonian decomposition,
+\begin{equation}
+	H = \sum_{k \in \mathbb{Z}_3} E_k\ketbra{E_k}{E_k},
+\end{equation}
+we can re-express the coordinate location, by writing
+\begin{align}
+	W_{\tau}(0,0) &= \frac{1}{3\Z}\tr\left[ A_{0,0}e^{\beta H} \right] \nonumber\\
+	&= \frac{e^{\beta F}}{3} \tr\left[ \sum_{r \in \mathbb{Z}_3} \ketbra{-r}{r}\sum_{k \in \mathbb{Z}_3} e^{\beta E_k}\ketbra{E_k}{E_k} \right] \\
+	&= \frac{e^{\beta F}}{3} \sum_{r \in \mathbb{Z}_3} \alpha_k e^{\beta E_k}
+	= \frac{e^{\beta F}}{3} \zeta \\
+	&= \frac{e^{\beta (F - \phi)}}{3},
+\end{align}
+where $\alpha_k, \zeta$ and $\phi$ are as defined prior to the statement of the theorem.
+Finally, the coordinates can be expressed as
+\begin{equation}
+	(x_0, L_0) = \left( \frac{e^{n\beta (F - \phi)}}{3^n}, v(\epsilon)^n \right).
+\end{equation}
+In the same manner, we can derive the first point coordinates of the output Lorenz curve as
+\begin{equation}
+	(x'_0, L'_0) = \left( \frac{e^{n\beta (F' - \phi')}}{3^n}, v(\epsilon')^n \right).
+\end{equation}
+
+If the largest rescaled component of a state is distinct with no multiplicities, then these coordinates correspond to the first elbow of the corresponding Lorenz curve, whereas if it appears multiple times, then the coordinates derived correspond to a point on the interior of the line segment connecting the origin to the first elbow.
+In both cases, the distillation bound remains the same, as is clear by its derivation in~\cref{app:elb_constraints}, and it is given by $L_0 / x_0 \geq L'_0 / x'_0$, which can be directly rearranged into the stated bound of the theorem.
+\end{proof}

### 2021-05-04 magic_paper.tex

--- 2021-05-04 magic_paper.tex
@@
 Our focus is on states with negativity, so the particular choice of free states is not critical for our analysis.
-The remaining component that defines any magic theory is the set of allowed (free) quantum operations, i.e.
+The remaining component that defines any magic theory is the set of allowed quantum operations, i.e.
 the ones that are considered free.
@@
     \includegraphics[scale=0.45]{figs/distill_bounds.pdf}
-    \caption{\textbf{Distillation bounds in the unital fragment.} Distillation bounds obtained by the first elbow majorisation constraint, mana and max--thauma are plotted for $\epsilon' = 0$, up to noise level $\epsilon = 3/7$.
+    \caption{\textbf{Distillation bounds in the unital fragment.} Distillation bounds obtained by the first elbow majorisation constraint $R$, mana $\M$ and max--thauma $\theta_{\rm{max}}$ are plotted for $\epsilon' = 0$, up to noise level $\epsilon = 3/7$.
     Majorisation provides stricter rates than the global mana and max--thauma bounds.
@@
 
-\newpage
 \section{Free energy dependent bounds for magic state distillation protocols}
@@
 In this direction, we highlight recent work in majorization in which stochastic independence and correlations are analysed.
-In particular it has been shown that stochastic independence (no correlations) of independent distributions can be viewed as a resource in an extension of catalytic majorization, and leads to a single-shot operational interpretation of the Shannon entropy.
-\ddd{[cite: look up papers by Marcus Mueller.
-He has about 3 or 4 on this.
-Also Mark Wilde has a paper on it]}
+In particular, it has been shown that stochastic independence (no correlations) of independent distributions can be viewed as a resource in an extension of catalytic majorization, and leads to a single-shot operational interpretation of the Shannon entropy.
+\nick{cite David?}
 
@@
 The approach, when combined with relative majorization, also allows us to derive magic distillation bounds that combine both the computational measures $\epsilon,\epsilon'$, with terms that depend on the Hamiltonian of the physical system.
-As discussed in section (blah), from the perspective of majorization the presence of magic can be viewed as a form of non-classical free energy and so it is also of interest to make an explicit link between the amount of magic in a non-equilibrium state $\rho_S(\epsilon)$ and the actual free energy of an equilibrium state $\tau(\beta)$.
+As discussed in section~\nick{REF}, from the perspective of majorization the presence of magic can be viewed as a form of non-classical free energy and so it is also of interest to make an explicit link between the amount of magic in a non-equilibrium state $\rho_S(\epsilon)$ and the actual free energy of an equilibrium state $\tau(\beta)$.
 
@@
 	Consider a magic distillation protocol on qutrits that transforms $n$ copies of an $\epsilon$--noisy Strange state into $m$ copies of an $\epsilon'$--noisy Strange state, with depolarising errors $\epsilon' \leq \epsilon \leq 3/7$.
+Let $T =(k\beta)^{-1}$ be any temperature for the physical system and let $H= \sum_{k \in \mathbb{Z}_3} E_k |E_k\>\<E_k|$ be the Hamiltonian of each qutrit subsystem.
 
-	Let $T =(k\beta)^{-1}$ be any temperature for the physical system and let $H= \sum_{k \in \mathbb{Z}_3} E_k |E_k\>\<E_k|$ be the Hamiltonian of each qutrit subsystem in its eigen-decomposition.
-Assume that for $n,m \rightarrow \infty$ the protocol's channel generates negligible correlations on the equilibrium state $\tau$, and so $\tau^{\otimes n} \longrightarrow \tau^{\prime \otimes m}$ for $n,m \gg 1$.
-We write the state $\tau'$ as $\tau' = e^{-\beta H'}/\Z'$ for some Hermitian $H'$.
+Assume for $n,m \rightarrow \infty$ that the protocol's channel $\E$ generates negligible correlations on the equilibrium state, so there is a state $\tau'$ such that
+\begin{equation}
+	\tau^{\otimes n} \longrightarrow \E(\tau^{\otimes n}) = \tau^{\prime \otimes m}
+\end{equation} 
+for $n,m \gg 1$. 
+We write the output state as $\tau' = e^{-\beta H'}/\Z'$ for some Hermitian $H'$.
 
@@
 \end{theorem}
-The proof of this is provided in Appendix \ref{free-energy-bound-proof}, and is a generalization of the analysis for unital protocols.
+The proof of this is provided in~\cref{free-energy-bound-proof}, and is a generalization of the analysis for unital protocols.
 
@@
 We could also perform similar analysis for general qudits, and different choices of magic states.
-It might also be of interest consider other choices of reference states that may include more appropriate hardware physics, for example for photonic set-ups.
+It might also be of interest to consider other choices of reference states that may include more appropriate hardware physics, for example for photonic set-ups.
 
@@
 This is a common situation in thermodynamics, where correlations are often sub-linear in the particle number in the macroscopic limit.
-One could perturb about this scenario, and make use of variational tools such as the Bogoliubov inequality \ddd{[cite]} for approximating the free energy of a system, to obtain bounds in a similar form.
+One could perturb about this scenario, and make use of variational tools such as the Bogoliubov inequality~\cite{bogolyubov_1966} for approximating the free energy of a system, to obtain bounds in a similar form.
+
+\subsection{Variation of bounds with physical parameters and constraints from complete positivity}
+The bounds derived are based on analysis of only part of the Lorenz curves and can be improved via a finer analysis.
+This is apparent by simple numerical calculations on the entirety of the curves as seen in~\cref{fig:distill_bounds} for the case of unital operations.
+Specifically, the existing bounds follow by considering the dominant terms in the rescaled Wigner distribution and do not, for example, take into account the Lorenz curve's peak structure.
+
+\ddd{[To be tidied+blended]} We also note that one can obtain another set of general distillation bounds from the monotonicity of discrimination measures under quantum channels.
+For example, the $L_1$ norm is contractive under quantum channels so that
+\begin{equation}
+|| \rho - \sigma||_1 \ge ||\E(\rho) - \E(\sigma)||_1,
+\end{equation}
+for any quantum channel $\E$.
+Therefore, beyond the constraint that the magic protocol corresponds to a stochastic map in the Wigner distribution, we also have constraints coming from complete-positivity and trace-preservation.
+For example, if $D(\rho,\sigma)$ is a contractive measure on pairs of quantum states that is also additive, in the sense that $D(\rho^{\otimes n}, \sigma^{\otimes n}) = n D(\rho, \sigma)$, then it is readily seen that within the context of the above theorem we also have,
+\begin{equation}
+R \le \frac{D(\rho_S(\epsilon),\tau)}{D(\rho_S(\epsilon'), \tau')},
+\end{equation}
+provided the denominator does not vanish.
+In particular we can choose the Renyi-divergences $D_\alpha(\rho ||\tau)$....or more concretely the von Neumann divergence $S(\rho ||\tau) = \tr[ \rho \log \rho - \rho \log \tau]$.
+However, if $\tau$ is taken to be a Gibbs state then $S(\rho ||\tau) = \beta (F[\rho] - F[\tau])$, namely the difference in free energies of the two states.
+Here we define
+\begin{equation}
+F[\rho] := \tr[H \rho] - \beta^{-1} S(\rho).
+\end{equation}
+  Therefore, simply from the fact that the protocol defines a channel, we obtain the bound
+\begin{equation}
+R \le \frac{F[\rho_S(\epsilon)] - F[\tau]}{F[\rho_S(\epsilon')] - F[\tau']},
+\end{equation}
+and so we can compare this with the above bounds \ddd{[Some numerics on this to compare?]}
+
+\nick{FIX} As a special case of the result, suppose that $H=H'$, implying that the protocol leaves the equilibrium state unchanged, hence it corresponds to a Gibbs-preserving map~\cite{faist_2015}.
+In the more general case, $\Delta F \coloneqq F' - F \ne 0$ and we have a free energy difference between the initial and final states, with respect to the relevant Hamiltonians.
+This is similar to the free energy differences that occur in fluctuation relations, where the final state of the system can be arbitrarily far from equilibrium, yet a free energy term for the final system still arises.
+
+\nick{FIX} The above bounds mainly demonstrate how one can use relative majorization of quasi-distributions to incorporate additional information into distillation bounds.
+However to unpack the results more it is useful to consider the case in which $H=H'$, and look at $\epsilon' \rightarrow 0$.
+For this we obtain~\cref{fig:rate_contour} which gives a contour plot of $R$ as a function of inverse temperature $\beta$ and depolarising noise level $\epsilon$ for the initial noisy magic state.
 \begin{figure}[t!]
@@
 \end{figure}
-\subsection{Variation of bounds with physical parameters}
-The bounds derived are based on analysis of only part of the Lorenz curves and can be improved via a finer analysis.
-This is apparent by simple numerical calculations on the entirety of the curves as seen in~\cref{fig:distill_bounds} for the case of unital operations.
-Specifically, the existing bounds follow by considering the dominant terms in the rescaled Wigner distribution and do not, for example, take into account the Lorenz curve's peak structure.
-
-\nick{FIX} As a special case of the result, suppose that $H=H'$, implying that the protocol leaves the equilibrium state unchanged, hence it corresponds to a Gibbs-preserving map~\cite{faist_2015}.
-In the more general case, $\Delta F \coloneqq F' - F \ne 0$ and we have a free energy difference between the initial and final states, with respect to the relevant Hamiltonians.
-This is similar to the free energy differences that occur in fluctuation relations, where the final state of the system can be arbitrarily far from equilibrium, yet a free energy term for the final system still arises.
-
-\ddd{[Need some numerics on varying the $F'$ case]}
-\nick{FIX} The above bounds mainly demonstrate how one can use relative majorization of quasi-distributions to incorporate additional information into distillation bounds.
-However to unpack the results more it is useful to consider the case in which $H=H'$, and look at $\epsilon' \rightarrow 0$.
-For this we obtain~\cref{fig:rate_contour} which gives a contour plot of $R$ as a function of inverse temperature $\beta$ and depolarising noise level $\epsilon$ for the initial noisy magic state.
 
@@
 We have described how relative majorization can be used to establish upper bounds on magic distillation protocols that take into account additional physics of the system.
-Our bounds only exploited the very simplest aspects of the Lorenz curves of the quasi-distributions, and so it would be of interest to sharpen these bounds and exploit more of the structure in the asymptotic limit.
-This raises interesting questions that do no arise for probability distributions, because we no longer have a notion of typicality and the central limit theorem does not apply.
-That said, for special states such as the Strange state the asymptotic behaviour is relatively simple and so one could study this and obtain a better handle on the $n\rightarrow \infty$ behaviour in a way.
-In appendix (\ddd{BLAH} we give some basic relations on this that could be explored further.
-\ddd{[where did the remainder term bounds go?
-People could potentially build on this]}
-
-One might wonder if this approach could also provide \emph{lower bounds} for distillation protocols.
+Given this, one might wonder if this approach could also provide \emph{lower bounds} for distillation protocols.
 Now, in contrast to the upper bounds, it is necessary to include the symplectic constraints on the phase space into the majorization relations.
 
-  For example, the Clifford group action on a quantum system corresponds to the action of the affine symplectic group \ddd{[cite Gross discrete Hudson paper, and some maths source on symplectic group]} on the discrete phase space.
+  For example, the Clifford group action on a quantum system corresponds to the action of the affine symplectic group on the discrete phase space.
 Therefore, any convex mixture of Clifford unitaries will correpond to a convex mixture of these group actions.
-From the Hardy-Littlewood theorem \ddd{[cite]}, we know that traditional majorization is obtained from convex mixtures of arbitrary permutations.
+From the Hardy-Littlewood theorem, we know that traditional majorization is obtained from convex mixtures of arbitrary permutations.
 However this has been generalised to convex mixtures of elements of a group $G$ that acts on vectors.
-This $G$--majorization has been studied in the classical literature and a range of results are known about it \ddd{[cite papers]}.
-For example, if $G$ is a finite reflection group then the $G$--majorization pre-order is described by a finite list of conditions\ddd{[cite]}, just as happens for the full majorization ordering.
+This $G$--majorization has been studied in the classical literature and a range of results are known about it.
+For example, if $G$ is a finite reflection group then the $G$--majorization pre-order is described by a finite list of conditions, just as happens for the full majorization ordering.
 One route is therefore to consider reflection sub-groups of the affine symplectic group, for which the majorization relation reduces to a finite set of conditions.
@@
 This would correspond to transformations that are \emph{not} unital, but still respect the symplectic structure.
-Physically, this regime would correspond to a form of thermo-majorization obtained from looking at the action of the Clifford group at a micro-canonical level, and then reducing to a small subsystem \ddd{[cite stat-mech book, cite Matteo review]}.
+Physically, this regime would correspond to a form of thermo-majorization obtained from looking at the action of the Clifford group at a micro-canonical level, and then reducing to a small subsystem.
 While this seems like a painful thing to consider, there is motivation for this beyond the aim of constructing lower bounds for magic protocols: in the case of statistical mechanics on a phase space this is precisely the situation, albeit in the continuum limit.
-Statistical mechanics of actual systems obey Hamiltonian dynamics and so automatically respect a symplectic form \ddd{[cite a stat-mech book]}.
+Statistical mechanics of actual systems obey Hamiltonian dynamics and so automatically respect a symplectic form.
 Therefore the pre-order of statistical mechanical states with respect to phase space dynamics preserving a Gibbs state must correspond to a symplectic thermo-majorization condition.
@@
 for a particle on a ring) or by first studying the discrete case.
-Such scenarios also arise in the Quantum Hall Effect \ddd{[cite]} and so this is another regime in which these techniques might be of use.
 
-Finally, it would be of interest to consider the possibility of applying these techniques to other scenarios in which one wishes to distinguish classical from non-classical behaviour based on quasi-probability representations \ddd{[cite quantum optics reference, cite Ferrie review on quasi-reps]}
+In this work we have looked at magic through the lens of thermodynamics. Specifically, we find that it can be viewed as a strictly non-classical form of non-equilibrium free energy.
+
+Our work also raises a fundamental question that is also of interest in statistical mechanics. Specifically: what are the majorization conditions that respect the symplectic structure of phase space?
 

### 2021-05-04 appendix.tex

@@
+\newpage
 \section{Properties of Wigner distributions}
@@
 
-Here we present important properties of the phase-point operators and the Wigner distribution that are used throughout the paper.
+Here we present basic properties of the phase-point operators and the Wigner distribution that are used throughout the paper.
 
@@
         \item[(i)]\label{en:a1} Hermiticity and unitarity: $A_{\bmx}^\dagger = A_{\bmx} = A_{\bmx}^{-1}$;
-	    \item[(ii)]\label{en:a2} Closure under transposition: $A_{(x, p)}^T = A_{(x, p)}$;
+	    \item[(ii)]\label{en:a2} Closure under transposition: $A_{(x, p)}^T = A_{(x, p)}$; \ddd{[FIX]}
 	    \item[(iii)]\label{en:a3} Unit trace for odd $d$: $\tr[A_{\bmx}] = 1$;
@@
 
-\subsection{Comments on monotones and fragements}
-The development of any monotone $\M(\rho)$ for a magic theory $\R$ can be viewed abstractly as
-\begin{equation}
-\M : \mbox{(pre-order of states)} \mapsto \mbox{(total order of numbers).} \nonumber
-\end{equation}
-More precisely, within the theory we order magic states as $\rho_1 \succ \rho_2$ whenever there is an operation $\E \in \O$ such that $\E(\rho_1) = \rho_2$.
-In general many states will not be interconvertible in both directions, so this ordering is a pre-order in the sense that incomparable states exist.
-A magic monotone projects this pre-order of states onto the real number line, and, through this lens, any two states are directly comparable in terms of their mapped values $\M(\rho_1)$, $\M(\rho_2)$.
-Of course, the price is that the monotone provides only a necessary, but not sufficient, condition for the transformation $\rho_1 \rightarrow \rho_2$.
-
-The restriction of a magic theory $\R$ to some fragment $\R_\sigma$ can now be interpreted as a generalisation of the magic monotone construction: instead of mapping the pre-order of states in $\R$ onto the number line, we instead map this pre-order onto \emph{a simpler pre-order of states}.
-Therefore, we are retaining more of the original parent theory, while working in a scenario that admits greater structure and simplicity.
-We can view this as a mapping $\P_\sigma: \R \rightarrow \R_\sigma$ that restricts to a sub-theory (a $\sigma$--fragment) of the parent theory $\R$.
-Thus,
-\begin{equation}
-\P_\sigma: \mbox{(pre-order)} \longrightarrow \mbox{(simpler pre-order).}
-\end{equation}
-By framing the projection onto a fragment in this light, we can view Theorem \ref{thm:frag} as a statement that the collection $\{\P_\sigma\}_{\sigma \in \F}$ provides a complete set of generalized monotones for the theory.
-\subsection{Simple--majorization equivalence conditions}
-
-In the unital fragment, namely the limit of infinite temperature, $\beta = 0$, the free state is the maximally mixed state $\frac{1}{n}\id$ with uniform Wigner distribution $\frac{1}{n}\bm{1} = (\frac{1}{n},\dots,\frac{1}{n})$.
-This fragment is governed by simple majorization and we first prove strong equivalences for this type of majorization.
-\begin{proposition}\label{prop:major}
-Given $\bmx, \bmy \in \mathbb{R}^n$ the following statements are equivalent:
+We now give the following equivalent formulations of $d$--majorization.
+
+\begin{proposition}\label{prop:rmajor}
+Given $\bmx, \bmy, \r \in \mathbb{R}^n$, such that the components of $\r$ are positive, the following statements are equivalent:
   \begin{enumerate}
-	\item[(i)]\label{en:m1} $\bmx \prec \bmy$;
-	\item[(ii)]\label{en:m2} $\bmx = B \bmy$ for bistochastic $B$;
-	\item[(iii)]\label{en:m3} $\sum\limits_{i=1}^n \abs{x_i - t} \leq \sum\limits_{i=1}^n \abs{y_i - t}$ for all $t \in \mathbb{R}$;
-	\item[(iv)]\label{en:m4} $\sum\limits_{i=1}^n (x_i - t)^+ \leq \sum\limits_{i=1}^n (y_i - t)^+$ for all $t \in \mathbb{R}$ and \vspace{5pt}\\ $\sum\limits_{i=1}^n x_i = \sum\limits_{i=1}^n y_i$, where $(x)^+ = \max{\{x, 0\}}$;
-	\item[(v)]\label{en:m5} $L_{\bmx}(t) \leq L_{\bmy}(t)$ for $t\in [0,1)$	and \vspace{5pt}\\ $L_{\bmx}(1) = L_{\bmy}(1)$, where $L_{\bmz}(t) = L_{\bmz|\frac{1}{n}\bm{1}}(t)$.
+    \item[(i)] $\bmx \prec_{\r} \bmy$;
+    \item[(ii)] $\Gamma_{\r}({\bmx}) \prec \Gamma_{\r}({\bmy})$;
+    \item[(iii)]\label{en:tm3} $\sum\limits_{i=1}^n \abs{x_i - r_i t} \leq \sum\limits_{i=1}^n \abs{y_i - r_i t}$ for all $t \in \mathbb{R}$;
+    \item[(iv)] $\sum\limits_{i=1}^n (x_i - r_i t)^+ \leq \sum\limits_{i=1}^n (y_i - r_i t)^+$ for all $t \in \mathbb{R}$ and \vspace{5pt}\\ $\sum\limits_{i=1}^n x_i = \sum\limits_{i=1}^n y_i$;
+    \item[(v)] $L_{\bmx|\r}(t) \leq L_{\bmy|\r}(t)$ for $t\in [0,1)$ and \vspace{5pt}\\ $L_{\bmx|\r}(1) = L_{\bmy|\r}(1)$.
   \end{enumerate}
 \end{proposition}
-	The equivalence between (i) and (ii) is the statement of the Hardy, Littlewood and Polya theorem and is taken as our definition of majorisation in the main text.
-
-	The rest of the properties are well-known and proofs can be found in~\cite{cit:marshall,cit:bhatia,cit:nielsen,cit:lostaglio}.
-
+The proofs for these can be found in~\cite{cit:marshall,cit:bhatia,cit:nielsen,cit:lostaglio} and references therein.
+
+The following lemma is used in the text to relate relative majorization of quasi-distributions to their Lorenz curves.
 \begin{lemma} Let $\p$ be a quasi-probability distribution and let $\r$ be a probability distribution with strictly non-zero components.
@@
 Therefore, mana is one of $d^{2n}$ constraints, so majorization is strictly a stronger constraint in any fragment.
-\end{proof}
-
-\subsection{Embedding map}
-
-Any $\r$--majorization problem can be rephrased as a simple majorization problem in a higher dimensional space via the embedding map.
-\begin{definition}
-  The embedding map $\Gamma_{\r}:\mathbb{R}^n \mapsto \mathbb{R}^N, N = \sum\limits_{i=1}^n r_i$ is the function
-  \begin{equation}
-    \Gamma_{\r}(\bmw) = \bigoplus_{i=1}^n w_i\  \frac{1}{r_i}\bm{1},
-  \end{equation}
-where $\bm{1}/r_i$ is the $r_i$--dimensional uniform distribution.
-The left inverse $\Gamma_{\r}^{-1}: \mathbb{R}^N \mapsto \mathbb{R}^n$ is defined to sum up the elements in each block of $\Gamma_{\r}(\bmw)$, so that
-  \begin{equation}
-     \Gamma_{\r}^{-1}(\oplus_{i=1}^n w_i \bm{1}/r_i) = \bmw.
-  \end{equation}
-  This is not a right inverse, because $\Gamma_{\r}$ is not surjective.
-\end{definition}
-The direct sum simply amounts to listing the uniform distributions one after the other.
-The embedding map maps the Gibbs distribution to the uniform distribution, $\Gamma_{\r}(\r) = \bm{1}/N$.
-Then, a non-increasing ordering $\Gamma_{\r}(\bmz)^\downarrow$ in the new space, corresponds to the so-called ``$\beta$-ordering'' of the original vector denoted by the permutation $\pi$ in~\cref{eq:lc}, mapping $(w_i/r_i) \mapsto (w_i/r_i)^\downarrow$ for all $i=1,\dots,n$.
-
-\subsection{\textit{r}-majorization equivalence conditions}
-
-We take the opportunity here	 to simply list useful equivalent statements for $\r$--majorisation.
-
-\begin{proposition}\label{prop:rmajor}
-Given $\bmx, \bmy, \r \in \mathbb{R}^n$, such that the components of $\r$ are positive, the following statements are equivalent:
-  \begin{enumerate}
-    \item[(i)] $\bmx \prec_{\r} \bmy$;
-    \item[(ii)] $\Gamma_{\r}({\bmx}) \prec \Gamma_{\r}({\bmy})$;
-    \item[(iii)]\label{en:tm3} $\sum\limits_{i=1}^n \abs{x_i - r_i t} \leq \sum\limits_{i=1}^n \abs{y_i - r_i t}$ for all $t \in \mathbb{R}$;
-    \item[(iv)] $\sum\limits_{i=1}^n (x_i - r_i t)^+ \leq \sum\limits_{i=1}^n (y_i - r_i t)^+$ for all $t \in \mathbb{R}$ and \vspace{5pt}\\ $\sum\limits_{i=1}^n x_i = \sum\limits_{i=1}^n y_i$;
-    \item[(v)] $L_{\bmx|\r}(t) \leq L_{\bmy|\r}(t)$ for $t\in [0,1)$ and \vspace{5pt}\\ $L_{\bmx|\r}(1) = L_{\bmy|\r}(1)$.
-  \end{enumerate}
-\end{proposition}
-\begin{proof}$ $\vspace{-12pt}\\
-\begin{enumerate}
-	\item[1$\leftrightarrow2$]
-	Suppose there exists a $\r$--stochastic $A$ such that $\bmx = A\bmy$ and let $B = \Gamma_{\r} \circ A \circ \Gamma_{\r}^{-1}$.
-$B$ is a $N$--dimensional bistochastic matrix, since composition of stochastic matrices is stochastic and $(\Gamma_{\r} \circ A \circ \Gamma_{\r}^{-1})\big(\frac{1}{N}\bm{1}\big) = (\Gamma_{\r} \circ A) (\r) = \Gamma_{\r}(\r) = \frac{1}{N}\bm{1}$.
-Then, $B$ maps $\Gamma_{\r}({\bmy})$ to $\Gamma_{\r}({\bmx})$.
-
-	Conversely, given $B$, let $A = \Gamma_{\r}^{-1} \circ B \circ \Gamma_{\r}$.
-	Similarly, $A$ is a $\r$--stochastic matrix that maps $\bmy$ to $\bmx$.
-	\item[$2\leftrightarrow3$] These \hspace{1pt} three \hspace{1pt} statements \hspace{1pt} are \hspace{1pt} equivalent \hspace{1pt} to \hspace{1pt} state-
-	\item[$2\leftrightarrow4$] \vspace{-7pt} ments (iii), (iv), (v) \hspace{1pt} in~\cref{prop:major} respectively, 
-	\item[$2\leftrightarrow5$] \vspace{-7pt} for the embedded vectors $\Gamma_{\r}({\bmx}), \Gamma_{\r}({\bmy})$, which becomes apparent by rewriting
-	\begin{align*}
-	&\hspace{15pt} \sum\limits_{i=1}^n \abs{x_i - r_i t} = \sum\limits_{i=1}^n r_i \abs{\frac{x_i}{r_i} - t} = \sum\limits_{i=1}^N \abs{\Gamma_{\r}(\bmx)_i - t}, \\[3pt]
-	&\hspace{15pt} \sum\limits_{i=1}^n (x_i - r_i t)^+ = \sum\limits_{i=1}^N (\Gamma_{\r}(\bmx)_i - t)^+ \text{ and} \\[6pt]
-	&\hspace{15pt} L_{\bmx|\r}(t) = L_{\Gamma_{\r}(\bmx)}(t),
-	\end{align*} 
-and similarly for the right hand sides of the inequalities.
-\end{enumerate}
-\vspace{-19pt}
 \end{proof}
@@
 
+\ddd{[Remainder bounds via integrals? This might be of use for others, if they wanted to build on this line.]}
 \subsection{Lorenz curve coordinates in the unital fragment}\label{app:lcsu_coord}
@@
 
+\ddd{[Do we need to keep any of the details in this section? If not then delete it entirely.]}
 \begin{theorem}

### 2021-05-04 magic_paper.tex

--- 2021-05-04 magic_paper.tex
@@
 This is a common situation in thermodynamics, where correlations are often sub-linear in the particle number in the macroscopic limit.
-One could perturb about this scenario, and make use of variational tools such as the Bogoliubov inequality \ddd{[cite]} for approximating the free energy of a system, to obtain bounds in a similar form.
+One could perturb about this scenario, and make use of variational tools such as the Bogoliubov inequality~\cite{bogolyubov_1966} for approximating the free energy of a system, to obtain bounds in a similar form.
+
 \begin{figure}[t!]

### 2021-05-04 appendix.tex
some quick fixes

@@
         \item[(i)]\label{en:a1} Hermiticity and unitarity: $A_{\bmx}^\dagger = A_{\bmx} = A_{\bmx}^{-1}$;
-	    \item[(ii)]\label{en:a2} Closure under transposition: $A_{(x, p)}^T = A_{(x, p)}$; \ddd{[FIX]}
+	    \item[(ii)]\label{en:a2} Closure under transposition: $A_{(x, p)}^T = A_{(x, -p)}$;
 	    \item[(iii)]\label{en:a3} Unit trace for odd $d$: $\tr[A_{\bmx}] = 1$;
@@
 \end{theorem}
+\nick{Should we keep this theorem??}
 \begin{proof}
@@
 
-\ddd{[Remainder bounds via integrals? This might be of use for others, if they wanted to build on this line.]}
+\subsection{Theory on bounding the core functions}
+The core functions are $\Phi_{\pm}$ which is an even power cumulative function. 
+We can rewrite it as
+\begin{equation}
+\Phi_{\pm}(m; n, a) = \frac{1}{2}( \Phi(m; n, a) \pm (1+a)^{-n} S(m; n, a) ),
+\end{equation}
+where we have substituted $a = p/(1-p)$. 
+$\Phi$ is the standard cumulative function 
+\begin{equation}
+	\Phi(m; n, a) = (1+a)^{-n} \sum_{k=0}^m \binom{n}{k} a^k,
+\end{equation}
+and the remainder term is
+\begin{equation}
+S(m; n, a) \coloneqq \sum_{k=0}^m \binom{n}{k} (-a)^k.
+\end{equation}
+We have good asymptotic bounds on the behaviour of $\Phi$~\cite{cit:ash},
+\begin{lemma}\label{lem:phil_bounds}
+	Given fixed $n>0$ and $p$, $\Phi_\ell$ satisfies the following bounds:
+	\begin{align*}
+		\begin{split}
+		&\text{1. } \Phi(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m}{n}}{p}},\ m\in [1,n-1] \\
+		&\text{2. } \Phi(m; n, p) \leq 2^{-n\ent{\frac{m}{n}}{p}},\ m\in [0,np] \\
+		&\text{3. } \Phi(m; n, p) \leq 1 - \left[ 8(m+1)\left(1-\frac{m+1}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m+1}{n}}{p}}, \\
+		&\hspace{14pt} m\in [0,n-2]
+		\end{split}
+		\\
+		&\text{4. } \Phi(m; n, p) \geq 1 - 2^{-n\ent{\frac{m+1}{n}}{p}},\ m\in [np+1,n-2]
+	\end{align*}
+\end{lemma}
+\nick{Should we keep this theorem instead?? Bounds on Phi are numerically veeery loose in general, and this theorem provides even looser bounds than the previous one}
+
+We would like some theory that estimates the value of $S(m; n, a)$ for different parameter regimes. 
+We can consider the function $f(x) = (1+x)^n$ and note that $S(m; n, a)$ is the $m$'th partial sum of this expansion at the point $x=-a$.
+
+The truncated Maclaurin series of a general function $f(x)$ is
+\begin{equation}
+	f(x) = f(0) + x f'(0) + \dots \frac{x^m}{m!}f^{(m)}(0) + R_m(x)
+\end{equation}
+with a remainder term
+\begin{align}
+	R_m (x)&= \int_{0}^x dt f^{(m+1)}(t) \frac{(x-t)^r}{r!} \\
+	&= \frac{x^{m+1}}{(m+1)!} f^{(m+1)}(x_*),
+\end{align}
+where in the second expression, $x_*$ is an implicit point that lies between $0$ and $x$ that comes from the Mean Value Theorem.
+
+Applying this to the function $f(x) = (1+x)^n$ gives
+\begin{equation}
+	(1+x)^n = \sum_{k=0}^m \binom{n}{k} x^k + R_m.
+\end{equation}
+Evaluating at $x=-a$ gives
+\begin{equation}
+	S(m; n, a) = (1-a)^n - R_m(-a),
+\end{equation}
+where the key remainder term is given by
+\begin{align}
+	R_m(-a) &= \int_0^{-a} dt f^{(m+1)}(t) \frac{(-a-t)^m}{m!} \\
+&= \frac{(-a)^{m+1}}{(m+1)!} f^{(m+1)}(x_*).
+\end{align}
+We can also compute the derivative $f^{(m+1)}(x)$ explicitly,
+\begin{equation}
+	f^{(m+1)}(x) = (m+1)!\binom{n}{m+1}(1+x)^{n-m-1}.
+\end{equation}
+Therefore, we have that
+\begin{align}
+	R_m(-a) &= (-1)^{m+1}(m+1)\binom{n}{m+1}\int_{-a}^0 dt (1+t)^{n-m-1}(a+t)^m \\
+&= \binom{n}{m+1}(-a)^{m+1}(1+x_*)^{n-m-1},
+\end{align}
+where in the latter expression $x_* \in [-a,0]$. 
+Note that the first integral expression can be estimated via the Cauchy-Schwarz or the Hoelder inequality. 
+Therefore, we can either work with an explicit form with an unknown (but bounded) parameter $x_*$, or we can use the integral form and provide concrete estimates on it value.
+
+A very simple estimate, based on $x_*$ lying in the interval $[-a,0]$ gives
+\begin{equation}
+\binom{n}{m+1}(-a)^{m+1}(1-a)^{n-m-1} \leq R_m(-a) \le  \binom{n}{m+1}(-a)^{m+1}.
+\end{equation}
+
+This in turn leads to the following bounds on $\Phi_+(a,r,n)$:
+\begin{align}
+\hspace{-2cm}2\Phi_+(a,r,n) &\le \Phi(a,r,n)+ (1-a)^n - \frac{(-a)^{r+1}}{r!} \binom{n}{r+1} (1-a)^{n-r-1} \nonumber \\
+2\Phi_+(a,r,n) & \ge\Phi(a,r,n)+ (1-a)^n - \frac{(-a)^{r+1}}{r!} \binom{n}{r+1} .
+\end{align}
+\nick{Fix notation !}
+
 \subsection{Lorenz curve coordinates in the unital fragment}\label{app:lcsu_coord}
@@
 \begin{equation}
-	(i,j,k) = (i',j',k') \Leftrightarrow I(i,j,k) = I(i',j',k').
+	(i,j,k) = (i',j',k') \text{ iff } I(i,j,k) = I(i',j',k').
 \end{equation}

### 2021-05-07 appendix.tex
No numerics yet. Corrected and tidied all appendices and outlook, answered all blue comments

@@
 
-Here we present basic properties of the phase-point operators and the Wigner distribution that are used throughout the paper.
+Here, we present basic properties of the phase-point operators and the Wigner distribution that are used throughout the paper.
 
@@
 \end{proposition}
-\begin{proof}
 All properties follow from the definition in~\cref{eq:ax} along with properties of the displacement operator $D_{\bmx}$ and can be found in the literature, e.g.~\cite{cit:veitch,Vourdas_2004,cit:gross3}
-\end{proof}
 
@@
 
-% TO SWAP d --> r, REPLACE ALL \bmd, \bm{d}, d_i WITH \r
-
 We now give the following equivalent formulations of $d$--majorization.
@@
   \begin{enumerate}
-    \item[(i)] $\bmx \prec_{\r} \bmy$;
-    \item[(ii)] $\Gamma_{\r}({\bmx}) \prec \Gamma_{\r}({\bmy})$;
-    \item[(iii)]\label{en:tm3} $\sum\limits_{i=1}^n \abs{x_i - r_i t} \leq \sum\limits_{i=1}^n \abs{y_i - r_i t}$ for all $t \in \mathbb{R}$;
-    \item[(iv)] $\sum\limits_{i=1}^n (x_i - r_i t)^+ \leq \sum\limits_{i=1}^n (y_i - r_i t)^+$ for all $t \in \mathbb{R}$ and \vspace{5pt}\\ $\sum\limits_{i=1}^n x_i = \sum\limits_{i=1}^n y_i$;
-    \item[(v)] $L_{\bmx|\r}(t) \leq L_{\bmy|\r}(t)$ for $t\in [0,1)$ and \vspace{5pt}\\ $L_{\bmx|\r}(1) = L_{\bmy|\r}(1)$.
+    \item[(i)] $\bmy = A\bmx$ and $\r = A\r$ for a stochastic map $A$;
+    \item[(ii)]\label{en:tm3} $\sum\limits_{i=1}^n \abs{x_i - r_i t} \leq \sum\limits_{i=1}^n \abs{y_i - r_i t}$ for all $t \in \mathbb{R}$;
+    \item[(iii)] $L_{\bmx|\r}(t) \leq L_{\bmy|\r}(t)$ for $t\in [0,1)$ and \vspace{5pt}\\ $L_{\bmx|\r}(1) = L_{\bmy|\r}(1)$.
   \end{enumerate}
@@
 
-The following lemma is used in the text to relate relative majorization of quasi-distributions to their Lorenz curves.
-\begin{lemma} Let $\p$ be a quasi-probability distribution and let $\r$ be a probability distribution with strictly non-zero components.
+The following result is used in the text to relate relative majorization of quasi-distributions to their Lorenz curves.
+\begin{proposition}\label{lemma:Lorenz_linearity}
+	Let $\p$ be a quasi-probability distribution and let $\r$ be a probability distribution with strictly non-zero components.
 Let $a > 0$ and $b \in \mathbb{R}$ then $L_{a\p + b \r | \r} (x) = a L_{\p |\r}(x) + b x$.
-\end{lemma}\label{lemma:Lorenz_linearity}
-\begin{proof} The Lorenz curve of $a\p + b \r$ relative to $\r$ passes through $(0,0)$ and the points $(\sum_{i=1}^k{r_{\pi(i)}}, \sum_{i=1}^k(a \p + b \r)_{\pi(i)})$ where $\pi$ is the permutation that puts $(a p_i/r_i + b)$ in non-increasing order.
+\end{proposition}
+\begin{proof} 
+	The Lorenz curve of $a\p + b \r$ relative to $\r$ passes through $(0,0)$ and the points $(\sum_{i=1}^k{r_{\pi(i)}}, \sum_{i=1}^k(a \p + b \r)_{\pi(i)})$ where $\pi$ is the permutation that puts $(a p_i/r_i + b)$ in non-increasing order.
 Since $a > 0$, the permutation $\pi$ puts  $(p_i/r_i)$ in non-increasing order too.
@@
 
-\begin{lemma}\label{lem:lcmax}
+\begin{theorem*}
 	Given a magic state $\rho$, the maximum $L_\star$ of its Lorenz curve $\lc{\rho}{\sigma}(x)$ is independent of the $\sigma$--fragment and equal to $1+\sn{\rho}$.
 Moreover, the majorization constraint is stronger than mana in every fragment.
-\end{lemma}
+\end{theorem*}
 \begin{proof}
@@
 
+We first prove a result on the independence of the Lorenz curve constraints, stated in~\cref{sec:major_frag}.
+\begin{proposition}\label{thm:elbows}
+	Let $\rho, \tau$ be two quantum states with Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in the $\sigma$--fragment.
+
+	Let $t$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ at locations $x_1, \dots, x_t$.
+
+	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\tau}{\sigma}(x_{i})$ for all $i =1,\dots,t$.
+\end{proposition}
+\begin{proof}	
+	$\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ trivially implies $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\tau}{\sigma}(x_{i})$ for all $i = 1,\dots,n'$.
+
+	Conversely, assume that $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\tau}{\sigma}(x_{i})$ for all $i = 1,\dots,r$.
+	First, let $x_0 = 0$ and $x_{n'+1} = 1$, so that $\lc{\rho}{\sigma}(x_0) = \lc{\tau}{\sigma}(x_0) = 0$ and $\lc{\rho}{\sigma}(x_{n'+1}) = \lc{\tau}{\sigma}(x_{n'+1}) = 1$.
+	Hence, we can extend the set of elbows $E$ to $E' = E \cup \{x_0, x_{n'+1}\}$.
+
+	Pick two consecutive locations $x_{i}, x_{i+1}$ in $E'$ and consider the line segment $\ell_\tau(x)$ connecting points $(x_{i}, \lc{\tau}{\sigma}(x_{i}))$ and $(x_{i+1}, \lc{\tau}{\sigma}(x_{i+1}))$ as well as the line segment $\ell_\rho(x)$ connecting points $(x_{i}, \lc{\rho}{\sigma}(x_{i}))$ and $(x_{i+1}, \lc{\rho}{\sigma}(x_{i+1}))$.
+	This is illustrated in~\cref{fig:elbows_proof}.
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.5]{figs/elbows_proof.pdf}
+    \caption{\textbf{Illustration of~\cref{thm:elbows}}.
+    }
+    \label{fig:elbows_proof}
+\end{figure}
+
+	Due to concavity of $\lc{\rho}{\sigma}$, it is clear that for all $x \in [x_{i}, x_{i+1}]$, we have $\lc{\rho}{\sigma}(x) \geq \ell_\rho(x) \geq \ell_\tau(x) = \lc{\tau}{\sigma}(x)$.
+	This argument can be made in all intervals $[x_{i}, x_{i+1}]$ with $i=0,\dots,n'$, so the proof is complete.
+\end{proof}
+The above theorem can be of practical importance in reducing the necessary distillation constraints derived via majorization in $\sigma$--fragments.
+
 \begin{proposition}\label{thm:frag_app}
-    Let $\R_\sigma = (\O_\sigma, \F_\sigma)$ be a $\sigma$--fragment of magic theory $\R = (\O, \F)$. 
-    The following statements hold:
+    Let $\R = (\F, \O)$ be a magic theory and $\sigma, \sigma' \in \F$. The following statements hold:
     \begin{enumerate}
-        \item No $\sigma$--fragment is empty.
+        \item No $\sigma$--fragment of $\R$ is empty.
         \item If a free operation leaves two states invariant, then it also leaves their mixtures invariant, 
@@
 Note that these mappings are one-to-one due to the orthogonality of the phase-point operators as an operator basis.
-
 Note further that free states $\F$ are mapped onto a \emph{strict subset} of the set of probability distributions.
 As a counterexample, the sharp $d^2$--dimensional probability distribution $(1, 0, \dots, 0)$ does not correspond to any qudit Wigner distribution because of the boundedness condition in~\cref{thm:wstate}.
-
 Similarly, not all stochastic matrices correspond to completely positive operations.
@@
 
-We now prove a result on the independence of the Lorenz curve constraints.
-\begin{proposition}\label{thm:elbows}
-	Let $\rho, \tau$ be two quantum states with Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in the $\sigma$--fragment.
-
-	Let $t$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ at locations $x_1, \dots, x_t$.
-
-	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\tau}{\sigma}(x_{i})$ for all $i =1,\dots,t$.
-\end{proposition}
-\begin{proof}	
-	$\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ trivially implies $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\tau}{\sigma}(x_{i})$ for all $i = 1,\dots,n'$.
-
-	Conversely, assume that $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\tau}{\sigma}(x_{i})$ for all $i = 1,\dots,r$.
-	First, let $x_0 = 0$ and $x_{n'+1} = 1$, so that $\lc{\rho}{\sigma}(x_0) = \lc{\tau}{\sigma}(x_0) = 0$ and $\lc{\rho}{\sigma}(x_{n'+1}) = \lc{\tau}{\sigma}(x_{n'+1}) = 1$.
-	Hence, we can extend the set of elbows $E$ to $E' = E \cup \{x_0, x_{n'+1}\}$.
-
-	Pick two consecutive locations $x_{i}, x_{i+1}$ in $E'$ and consider the line segment $\ell_\tau(x)$ connecting points $(x_{i}, \lc{\tau}{\sigma}(x_{i}))$ and $(x_{i+1}, \lc{\tau}{\sigma}(x_{i+1}))$ as well as the line segment $\ell_\rho(x)$ connecting points $(x_{i}, \lc{\rho}{\sigma}(x_{i}))$ and $(x_{i+1}, \lc{\rho}{\sigma}(x_{i+1}))$.
-	This is illustrated in~\cref{fig:elbows_proof}.
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.6]{figs/elbows_proof.pdf}
-    \caption{\textbf{Illustration of~\cref{thm:elbows}}.
-    }
-    \label{fig:elbows_proof}
-\end{figure}
-
-	Due to concavity of $\lc{\rho}{\sigma}$, it is clear that for all $x \in [x_{i}, x_{i+1}]$, we have $\lc{\rho}{\sigma}(x) \geq \ell_\rho(x) \geq \ell_\tau(x) = \lc{\tau}{\sigma}(x)$.
-	This argument can be made in all intervals $[x_{i}, x_{i+1}]$ with $i=0,\dots,n'$, so the proof is complete.
-\end{proof}
-This theorem is of practical importance in reducing the necessary distillation constraints derived via majorization in $\sigma$--fragments.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{lemma}
-The proof provided in~\cite{cit:ash} proceedx with direct calculation for the edge cases $\ell = 1,2, n-1, n-2$ and use Stirling's approximation for the remaining cases.
-
-With the help of this lemma, we directly arrive at 
-\begin{theorem}\label{thm:bounds_strict}
-	Given fixed positive integer $n$ and probability $p$, $\Phi_+, \Phi_-$ satisfy the following bounds:
+The proof provided in~\cite{cit:ash} proceeds with direct calculation for the edge cases $\ell = 1,2, n-1, n-2$ and use Stirling's approximation for the remaining cases.
+We can use~\cref{lem:comb_bounds} to provide strict upper and lower bounds on the functions $\Phi_+, \Phi_-$.
+
+\subsection{Theory on bounding the core functions}
+\nick{Should we really keep this section? It is standard calculus and the bounds are really loose.}
+Here we present a more manageable method of bounding the core functions $\Phi_{\pm}$, which however results in looser bounds. 
+We can rewrite the functions as
+\begin{equation}
+	\Phi_{\pm}(m; n, a) = \frac{1}{2}(\Phi(m; n, a) \pm (1+a)^{-n} S(m; n, a)),
+\end{equation}
+where we have substituted $a = p/(1-p)$. 
+$\Phi$ is the standard cumulative function
+\begin{equation}
+	\Phi(m; n, a) = (1+a)^{-n} \sum_{k=0}^m \binom{n}{k} a^k,
+\end{equation}
+and the remainder term is
+\begin{equation}
+	S(m; n, a) \coloneqq \sum_{k=0}^m \binom{n}{k} (-a)^k.
+\end{equation}
+We have the following asymptotic bounds on the behaviour of $\Phi$~\cite{cit:ash},
+\begin{lemma}\label{lem:phi_bounds}
+	Given fixed $n>0$ and $p$, $\Phi$ satisfies the following bounds:
 	\begin{align*}
 		\begin{split}
-		&\text{1. } \Phi_+(m; n, p) \geq \sum\limits_{\ell=0}^{m/2}\left[ 16\ell\left(1-\frac{2\ell}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{2\ell}{n}}{p}}, \\
-		&\hspace{14pt} \text{for all even } m\in [2,n] \\
-		&\text{2. } \Phi_+(m; n, p) \leq \sum\limits_{\ell=0}^{m/2}\left[ 4\pi\ell\left(1-\frac{2\ell}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{2\ell}{n}}{p}}, \\
-		&\hspace{14pt} \text{for all even } a\in [2,n] \\
-		&\text{3. } \Phi_-(m; n, p) \geq \sum\limits_{\ell=1}^{(m-1)/2}\left[ 16(\ell+1)\left(1-\frac{2\ell+1}{n}\right) \right]^{-\frac{1}{2}} \times \\
-		&\hspace{14pt} \times 2^{-n\ent{\frac{2\ell+1}{n}}{p}},\ \text{for all odd }a\in [1,n] \\
-		&\text{4. } \Phi_-(m; n, p) \leq \sum\limits_{\ell=1}^{(m-1)/2}\left[ 4\pi(\ell+1)\left(1-\frac{2\ell+1}{n}\right) \right]^{-\frac{1}{2}} \times \\
-		&\hspace{14pt} \times 2^{-n\ent{\frac{2\ell+1}{n}}{p}},\ \text{for all odd } a\in [1,n]
-		\end{split}
-	\end{align*}
-\end{theorem}
-\nick{Should we keep this theorem??}
-\begin{proof}
-	All four statements follow from application of~\cref{lem:comb_bounds} on the combinatorial coefficient and the defintion of relative entropy given in~\cref{eq:ent_rel}
-\end{proof}
-
-\subsection{Theory on bounding the core functions}
-The core functions are $\Phi_{\pm}$ which is an even power cumulative function. 
-We can rewrite it as
-\begin{equation}
-\Phi_{\pm}(m; n, a) = \frac{1}{2}( \Phi(m; n, a) \pm (1+a)^{-n} S(m; n, a) ),
-\end{equation}
-where we have substituted $a = p/(1-p)$. 
-$\Phi$ is the standard cumulative function 
-\begin{equation}
-	\Phi(m; n, a) = (1+a)^{-n} \sum_{k=0}^m \binom{n}{k} a^k,
-\end{equation}
-and the remainder term is
-\begin{equation}
-S(m; n, a) \coloneqq \sum_{k=0}^m \binom{n}{k} (-a)^k.
-\end{equation}
-We have good asymptotic bounds on the behaviour of $\Phi$~\cite{cit:ash},
-\begin{lemma}\label{lem:phil_bounds}
-	Given fixed $n>0$ and $p$, $\Phi_\ell$ satisfies the following bounds:
-	\begin{align*}
-		\begin{split}
-		&\text{1. } \Phi(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m}{n}}{p}},\ m\in [1,n-1] \\
-		&\text{2. } \Phi(m; n, p) \leq 2^{-n\ent{\frac{m}{n}}{p}},\ m\in [0,np] \\
-		&\text{3. } \Phi(m; n, p) \leq 1 - \left[ 8(m+1)\left(1-\frac{m+1}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m+1}{n}}{p}}, \\
-		&\hspace{14pt} m\in [0,n-2]
+		&\text{1. } \Phi(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m}{n}}{p}}, \\
+		&\hspace{14pt} m\in [1,n-1] \\
+		&\text{2. } \Phi(m; n, p) \geq 1 - 2^{-n\ent{\frac{m+1}{n}}{p}},\ m\in [np+1,n-2] \\
+		&\text{3. } \Phi(m; n, p) \leq 1 - \left[ 8(m+1)\left(1-\frac{m+1}{n}\right) \right]^{-\frac{1}{2}}\times \\
+		&\hspace{14pt} 2^{-n\ent{\frac{m+1}{n}}{p}},\ m\in [0,n-2]
 		\end{split}
 		\\
-		&\text{4. } \Phi(m; n, p) \geq 1 - 2^{-n\ent{\frac{m+1}{n}}{p}},\ m\in [np+1,n-2]
+		&\text{4. } \Phi(m; n, p) \leq 2^{-n\ent{\frac{m}{n}}{p}},\ m\in [0,np]
 	\end{align*}
 \end{lemma}
-\nick{Should we keep this theorem instead?? Bounds on Phi are numerically veeery loose in general, and this theorem provides even looser bounds than the previous one}
 
@@
 \begin{align}
-	R_m (x)&= \int_{0}^x dt f^{(m+1)}(t) \frac{(x-t)^r}{r!} \\
+	R_m (x)&= \int_{0}^x dt f^{(m+1)}(t) \frac{(x-t)^m}{m!} \\
 	&= \frac{x^{m+1}}{(m+1)!} f^{(m+1)}(x_*),
@@
 \begin{align}
-	R_m(-a) &= (-1)^{m+1}(m+1)\binom{n}{m+1}\int_{-a}^0 dt (1+t)^{n-m-1}(a+t)^m \\
+	R_m(-a) &= (-1)^{m+1}(m+1)\binom{n}{m+1}\times \nonumber\\
+	&\hspace{12pt} \int_{-a}^0 dt (1+t)^{n-m-1}(a+t)^m \\
 &= \binom{n}{m+1}(-a)^{m+1}(1+x_*)^{n-m-1},
@@
 where in the latter expression $x_* \in [-a,0]$. 
-Note that the first integral expression can be estimated via the Cauchy-Schwarz or the Hoelder inequality. 
+Note that the first integral expression can be estimated via the Cauchy-Schwarz or the H{\"o}lder inequality. 
 Therefore, we can either work with an explicit form with an unknown (but bounded) parameter $x_*$, or we can use the integral form and provide concrete estimates on it value.
@@
 \begin{equation}
-\binom{n}{m+1}(-a)^{m+1}(1-a)^{n-m-1} \leq R_m(-a) \le  \binom{n}{m+1}(-a)^{m+1}.
-\end{equation}
-
-This in turn leads to the following bounds on $\Phi_+(a,r,n)$:
-\begin{align}
-\hspace{-2cm}2\Phi_+(a,r,n) &\le \Phi(a,r,n)+ (1-a)^n - \frac{(-a)^{r+1}}{r!} \binom{n}{r+1} (1-a)^{n-r-1} \nonumber \\
-2\Phi_+(a,r,n) & \ge\Phi(a,r,n)+ (1-a)^n - \frac{(-a)^{r+1}}{r!} \binom{n}{r+1} .
-\end{align}
-\nick{Fix notation !}
+(1-a)^{n-m-1} \leq \frac{R_m(-a)}{\binom{n}{m+1}(-a)^{m+1}} \leq 1,
+\end{equation}
+which in turn leads to the following bounds on $\Phi_+(m; n, a)$:
+\begin{align}
+	\hspace{-2cm}2\Phi_+(m; n, a) \leq\ &\Phi(m; n, a) + (1-a)^n - \frac{(-a)^{m+1}}{m!} \times \nonumber\\
+	 &\binom{n}{m+1} (1-a)^{n-m-1} \text{ and} \\
+	2\Phi_+(m; n, a) \geq\ &\Phi(m; n, a) + (1-a)^n - \frac{(-a)^{m+1}}{m!} \binom{n}{m+1} .
+\end{align}
 
@@
 
-\section{Technical details of the derivation of distillation bounds}
+\section{Technical details for the derivation of distillation bounds from Lorenz curves}
 \label{app:lcst_technical}
@@
 In general, a $1$--copy $d$--dimensional state $\rho$ is described exactly by its $d^2$--dimensional Wigner distribution $\W{\rho}$. 
-The distribution $\W{\rho}$ is usually defined on the phase space, but it can be convenient to define it using pure vector notation. 
+The distribution $\W{\rho}$ is usually defined on the phase space, but it can be convenient to define it using vector notation. 
 In particular, we introduce a component vector $\bmw(\rho) = (w_i)_{i=1,\dots,D}$ and a multiplicity vector $\bmm(\rho) = (m_i)_{i=1,\dots,D}$, where $D \leq d^2$ which together form a set of component-multiplicity pairs $\{(w_i, m_i)\}_{i=1,\dots,D}$.
@@
 
-Index vector $\bmk$ has $D-1$ independent components and in the proof of our main theorem in~\cref{sec:stab} we have $D=4$, so we simplify the notation by writing the component and multiplicity vectors of the $n$--copy state distributions as $m_{ijk}, w(\rho_{\rm{S}})_{ijk}, w(\sigma)_{ijk}$ and $w(\rho_{\rm{S}}|\sigma)_{ijk}$, where $i,j,k$ are the 3 independent index components.
+%Index vector $\bmk$ has $D-1$ independent components and in the proof of our main theorem in~\cref{sec:stab} we have $D=4$, so we simplify the notation by writing the component and multiplicity vectors of the $n$--copy state distributions as $m_{ijk}, w(\rho_{\rm{S}})_{ijk}, w(\sigma)_{ijk}$ and $w(\rho_{\rm{S}}|\sigma)_{ijk}$, where $i,j,k$ are the 3 independent index components.
+
+\subsection{Free energy dependent magic distillation bounds}\label{free-energy-bound-proof}
+\label{app:main_proof}
+Here we prove~\cref{thm:free-energy}, which bounds magic distillation rates in terms of free energies.
+
+\begin{theorem*}
+	Consider a magic distillation protocol on qutrits that transforms $n$ copies of an $\epsilon$--noisy Strange state into $m$ copies of an $\epsilon'$--noisy Strange state, with depolarising errors $\epsilon' \leq \epsilon \leq 3/7$.
+
+	Let $T =(k\beta)^{-1}$ be any temperature for the physical system and let $H= \sum_{k \in \mathbb{Z}_3} E_k |E_k\>\<E_k|$ be the Hamiltonian of each qutrit subsystem in its eigen-decomposition.
+Assume that for $n,m \rightarrow \infty$ the protocol's channel generates negligible correlations on the equilibrium state $\tau$, and so $\tau^{\otimes n} \longrightarrow \tau^{\prime \otimes m}$ for $n,m \gg 1$.
+We write the state $\tau'$ as $\tau' = e^{-\beta H'}/\Z'$ for some Hermitian $H'$.
+
+Given this, there are local Clifford changes of basis $C_1,C_2$, such that $\rho_1 := C_1 \rho_S(\epsilon) C_1^\dagger$ and $\rho_2 := C_2 \rho_S(\epsilon') C_2^\dagger$ for which the protocol gives
+\begin{equation}
+\rho_1^{\otimes n} \longrightarrow \rho_2^{ \otimes m}.
+\end{equation}
+Moreover, the magic distillation rate $R = m/n$ for the protocol is bounded by the expression
+\begin{equation}\label{eq:rate_bounds_proof}
+	R \leq \dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (\phi - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (\phi' - F')},
+\end{equation}
+where $F$ is the free energy of $\tau$,  and 
+\begin{equation}
+	\phi = -\beta^{-1} \log \zeta
+\end{equation}
+with $\zeta$ given by the equations
+\begin{align}
+	\zeta &= \sum_{k\in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}, \nonumber\\
+	\alpha_k &= \sum_{r \in \mathbb{Z}_3} \braket{E_k}{-r}\braket{r}{E_k}.
+\end{align}
+The primed variables are defined similarly for the output system.
+\end{theorem*}
+
+\begin{proof}	
+For the sake of clarity, we write $\rho_n \coloneqq \rho_S(\epsilon)^{\otimes n}$, $\rho'_m \coloneqq \rho_S(\epsilon')^{\otimes m}$, $\tau_n \coloneqq \tau^{\otimes m}$ and $\tau'_m \coloneqq \tau'^{\otimes m}$.
+
+To establish the distillation bound we consider the distillation protocol that gives $\E( \rho_n) = \rho_m$ for the magic states. 
+We then consider that the protocol transforms the reference equilibrium state as $\E( \tau_n) = \tau'_m$.
+Since $\tau$ and $\tau'$ are assumed to be full rank stabilizer states, they have a strictly positive Wigner distribution, while, in contrast, the input and output magic states generally have quasi-probability Wigner distributions.
+For any such protocol we therefore have that
+\begin{equation}
+	( W_{\rho_n}(\bmx), W_{\tau_n}(\bmx) ) \succ ( W_{\rho'_m}(\bmx), W_{\tau'_m}(\bmx) ),
+\end{equation}
+or, equivalently, in terms of the relevant Lorenz curves,
+\begin{equation}
+	L_{\rho_n |\tau_n}(x) \ge L_{\rho'_m |\tau'_m}(x) \mbox{ for all } x.
+\end{equation}
+
+We define the rescaled Wigner distribution $W_{\rho | \tau}(\x) \coloneqq W_\rho(\x)/W_\tau(\x)$, which is always well-defined since $\tau$ is full-rank. 
+Due to the multiplicative property of the Wigner distribution, the rescaled distribution is also multiplicative in the sense that
+\begin{equation}
+	W_{\rho \otimes \rho' | \tau \otimes \tau'} (\x_1 \oplus \x_2) = W_{\rho | \tau}(\x_1)W_{\rho' | \tau'}(\x_2),
+\end{equation}
+for any states $\rho, \rho'$ and any full-rank stabilizer states $\tau, \tau'$.
+Therefore we have that
+\begin{align}
+	W_{\rho_n |\tau_n} (\x) &= \prod_{i=1}^n W_{\rho|\tau}(\x_i)\\
+	W_{\rho_n } (\x) &= \prod_{i=1}^n W_\rho(\x_i)
+\end{align}
+where $\x = \oplus_{i=1}^n \x_i \in \mathbb{Z}_3^n$ is the phase space point for the full system in terms of those of the individual subsystems.
+
+The points defining the Lorenz curve $L_{\rho_n |\tau_n}(x)$ are obtained from sorting the components of $W_{\rho_n |\tau_n}(\x)$ in non-increasing order and then computing the partial sums of $W_{\rho_n |\tau_n}(\pi(\x))$ where $\pi$ is the permutation that realises the sorting.
+However, similarly to the unital fragment analysis, we aim to use the constraint that is obtained by considering the line segment connecting the origin to the first elbow of both Lorenz curves.
+The proof of this constraint is provided in~\cref{app:elb_constraints}.
+Therefore, we focus on finding the coordinates of some point on this line segment of the Lorenz curves.
+
+We find the coordinates for the input Lorenz curve, but the exact same analysis can be applied on the output Lorenz curve.
+The Wigner distribution of a single noisy Strange state consists of 1 negative component $W_{\rho}(0,0) = -v(\epsilon)$ and 8 positive components $W_{\rho}(\bmx) = u(\epsilon)$ for $\bmx \neq \bmo$.
+The Wigner distribution of the full-rank, stabilizer equilibrium state $\tau$ is $W_{\tau}(\bmx) > 0$ for all $\bmx \in \mathbb{Z}_3^2$.
+We keep the components completely general.
+
+Assume that the smallest component of the equilibrium state distribution is $W_{\tau}(i,j)$.
+We then make use of the freedom to apply Clifford unitaries in order to perform the  Clifford operation
+\begin{equation}
+	\tau \longrightarrow X^{-i}Z^{-j}\ \tau\ Z^{j}X^{i},
+\end{equation}
+which permutes the smallest component to the origin of the phase space, $W_{\tau}(i,j) \longrightarrow W_{\tau}(0,0)$.
+This operation would inevitably affect the magic distillation protocol, but since we consider the state distillation modulo Clifford operations, we are allowed to perform the reverse Clifford operation keeping the magic distillation process as is.
+\nick{statement here is inaccurate - incorporate $C_1, C_2$ in the proof.}
+
+The rescaled distribution components are in general given by
+\begin{equation}
+	W_{\rho_n|\tau_n} = \left(\frac{-v}{W_{\tau}(0,0)}\right)^{i_{\bmo}} \prod_{\bmx \neq \bmo} \left(\frac{u}{W_{\tau}(\bmx)}\right)^{i_{\bmx}},
+\end{equation}
+where the (integer) indices obey the following conditions:
+\begin{align}
+&0 \leq i_{\bmx} \leq n \mbox{ for all } \bmx \in \mathbb{Z}_3^2, \nonumber \\
+&\sum_{\bmx \in \mathbb{Z}_3^2} i_{\bmx} = n.
+\end{align}
+It is now easy to find the largest rescaled component.
+Firstly, note that $n$ is even, so we require that $i_{\bmo} \in \{0,2,\dots,n\}$ for the component to be positive.
+Then, we have that $v \geq u$ because $\epsilon \leq 3/7$, and we have already ensured that $W_{\tau}(0,0) \leq W_{\tau}(\bmx)$ for all $\bmx \in \mathbb{Z}_3^2$.
+Therefore, the largest rescaled component occurs when $i_{\bmo} = n$ and $i_{\bmx} = 0$ for $\bmx \neq \bmo$ and is equal to $(v/W_{\tau}(0,0))^n$.
+Accordingly, the coordinates of the first Lorenz curve point after the origin are given by
+\begin{equation}
+	(x_0, L_0) = ((W_{\tau}(0,0))^n, v^n)
+\end{equation}
+
+Given a Hamiltonian decomposition,
+\begin{equation}
+	H = \sum_{k \in \mathbb{Z}_3} E_k\ketbra{E_k}{E_k},
+\end{equation}
+we can re-express the coordinate location, by writing
+\begin{align}
+	W_{\tau}(0,0) &= \frac{1}{3\Z}\tr\left[ A_{0,0}e^{-\beta H} \right] \nonumber\\
+	&= \frac{e^{\beta F}}{3} \tr\left[ \sum_{r \in \mathbb{Z}_3} \ketbra{-r}{r}\sum_{k \in \mathbb{Z}_3} e^{-\beta E_k}\ketbra{E_k}{E_k} \right] \\
+	&= \frac{e^{\beta F}}{3} \sum_{r \in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}
+	= \frac{e^{\beta F}}{3} \zeta \\
+	&= \frac{e^{\beta (F - \phi)}}{3},
+\end{align}
+where $\alpha_k, \zeta$ and $\phi$ are as defined in the statement of the theorem.
+Finally, the coordinates can be expressed as
+\begin{equation}
+	(x_0, L_0) = \left( \frac{e^{n\beta (F - \phi)}}{3^n}, v(\epsilon)^n \right).
+\end{equation}
+In the same manner, we can derive the first point coordinates of the output Lorenz curve as
+\begin{equation}
+	(x'_0, L'_0) = \left( \frac{e^{n\beta (F' - \phi')}}{3^n}, v(\epsilon')^n \right).
+\end{equation}
+
+If the largest rescaled component of a state is distinct with no multiplicities, then these coordinates correspond to the first elbow of the corresponding Lorenz curve, whereas if it appears multiple times, then the coordinates derived correspond to a point on the interior of the line segment connecting the origin to the first elbow.
+In both cases, the distillation bound remains the same, as is clear by its derivation in~\cref{app:elb_constraints}, and it is given by $L_0 / x_0 \geq L'_0 / x'_0$, which can be directly rearranged into the stated bound of the theorem.
+\end{proof}
 
@@
 
-\nick{RESTRUCTURE}
-
-To find the coordinates of the \textbf{last} elbow $(x_E, L_E)$, where $E$ is the number of elbows, we need to evaluate the minimum rescaled component,
-\begin{align}
-	&\bmw(\rho_{\rm{S}} | \sigma)_{\rm{min}} \coloneqq (3\Z)^{n}\times \nonumber\\
-	&\min\limits_{i,j,k}\Big\{ (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \label{eq:min_slope}
-\end{align}
-where $0 \leq i,j,k \leq n$ and $\alpha \coloneqq i+j+k \leq n$.
-Notice that for $0 \leq \epsilon \leq 3/7$, we have $v \geq u$. 
-We need the sum $\alpha = i+j+k$ to be odd for the expression to be negative.
-
-Given an odd value for the sum $\alpha$, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_0}$ is fixed (and negative), so the expression is minimised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
-Hence, we have
-\begin{align}
-	&\bmw(\rho_{\rm{S}} | \sigma)_{\rm{min}} = \nonumber\\
-	&-(3\Z)^{n} v^n e^{n\beta E_0}\max\limits_{\substack{\alpha = 1,3, \\ \dots,n-1}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}.
-\end{align}
-If the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than $1$ then the minimum occurs at $\alpha=1$, otherwise it occurs at $\alpha = n-1$.
-
-The minimum rescaled component can then be expressed as
-\begin{equation}
-\bmw(\rho_{\rm{S}} | \sigma)_{\rm{min}} =
-	\begin{cases}
-		-(3\Z)^{n} v^{n-1} u e^{\beta [(n-1)E_0 + E_{\rm{max}}]}, &\epsilon \leq \epsilon_{\star},\ \hspace{3pt}\rm{(C1)}	\\
-		-(3\Z)^{n} v u^{n-1} e^{\beta [E_0 + (n-1)E_{\rm{max}}]}, &\epsilon > \epsilon_{\star}.\ \hspace{5pt}\rm{(C2)} 
-	\end{cases}
-\end{equation}
-Case $\rm{(C1)}$ can correspond to $(i,j,k) = (1,0,0)$ if $E_{\rm{max}} = E_0$, when the multiplicity is $m_{100} = 2n$ and the corresponding Wigner components are $\bmw(\rho_{\rm{S}})_{100}, \bmw(\sigma)_{100}$ or it can correspond to $(i,j,k) = (0,1,0)$ ($(i,j,k) = (0,0,1)$), if $E_{\rm{max}} = E_1$ ($E_{\rm{max}} = E_2$), when the multiplicity is $m_{010} = 3n$ ($m_{001} = 3n$) and the corresponding Wigner components are $\bmw(\rho_{\rm{S}})_{010}, \bmw(\sigma)_{010}$ ($\bmw(\rho_{\rm{S}})_{001}, \bmw(\sigma)_{001}$).
-Case $\rm{(C2)}$ corresponds to $(i,j,k) = (0,n-1,0)$ ($(i,j,k) = (0,0,n-1)$)
-if we have $E_{\rm{max}} = E_1$ ($E_{\rm{max}} = E_2$), when the multiplicity is $m_{0,n-1,0} = 3^{n-1}n$ ($m_{0,0,n-1} = 3^{n-1}n$) and the corresponding Wigner components are $\bmw(\rho_{\rm{S}})_{0,n-1,0}, \bmw(\sigma)_{0,n-1,0}$ ($\bmw(\rho_{\rm{S}})_{0,0,n-1}, \bmw(\sigma)_{0,0,n-1}$).
-
-The last elbow coordinates can finally be derived by sutracting the appropriate rescaled component from 1, $(x_E, L_E) =$
-\begin{equation}\label{eq:last_elb_coords}
-	\begin{cases}
-		&\left( 1-\dfrac{2n}{(3\Z_\beta)^n}e^{-\beta [(n-1)E_0 + E_{\rm{max}}]},\ 1 + 2n v^{n-1} u \right), \vspace{5pt}\\
-		&\hspace{5pt} \text{if } E_{\rm{max}} = E_0, \hspace{51pt}\rm{(C1a)} \vspace{10pt}\\
-		&\left( 1-\dfrac{3n}{(3\Z_\beta)^n}e^{-\beta [(n-1)E_0 + E_{\rm{max}}]},\ 1 + 3n v^{n-1} u \right), \vspace{5pt}\\
-		&\hspace{5pt} \text{if } E_{\rm{max}} > E_0, \epsilon \leq \epsilon_{\star}, \hspace{20pt}\rm{(C1b)} \vspace{10pt}\\
-		&\left( 1-\dfrac{n}{3\Z_\beta^n}e^{-\beta [E_0 + (n-1)E_{\rm{max}}]},\ 1 + 3^{n-1}n v u^{n-1} \right), \vspace{5pt}\\
-		&\hspace{5pt} \text{if } E_{\rm{max}} > E_0, \epsilon \geq \epsilon_{\star}. \hspace{22pt}\rm{(C2)}
-	\end{cases}
-\end{equation}
-
-Assuming that $E_{\rm{max}} > E_0$ for clarity, we have the same three scenarios as in the case of the first elbow bound:
-\begin{enumerate}
-	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $\beta < \beta_{\star}$ and $\epsilon' < \epsilon  \leq \epsilon_{\star}$.
-	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $\beta < \beta_{\star}$ and $\epsilon' \leq \epsilon_{\star} < \epsilon$.
-	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $\beta < \beta_{\star}$ and $\epsilon_{\star} \leq \epsilon' < \epsilon$ or $\beta \geq \beta_{\star}$.
-\end{enumerate}
-Now using last elbow constraint, derived in~\cref{app:elb_constraints}, we can calculate new distillation bounds.
-The last elbow bounds can be rephrased in terms of the first elbow bound, leading to $R_{\rm{last-elb}} - R_{\rm{first-elb}} = $
-\begin{equation}\label{eq:last_elb_coords}
-	\begin{cases}
-		\dfrac{1}{n} \dfrac{\log{\frac{u(\epsilon)v(\epsilon')}{u(\epsilon')v(\epsilon)}}}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F(\beta))},\ &\rm{(C1)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
-		\dfrac{1}{n} \dfrac{\log{\frac{v(\epsilon)v(\epsilon')}{u(\epsilon)u(\epsilon')}} - 2\beta(E_{\rm{max}} - E_0)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
-		\dfrac{1}{n} \dfrac{\log{\frac{v(\epsilon')u(\epsilon')}{v(\epsilon')u(\epsilon)}}}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C2)},
-	\end{cases}
-\end{equation}
-
-Note that the last elbow bounds have a dependence on $n$, which interestingly is due to $n$ being even.
-Had we considered \textbf{odd} number of copies $n$, then the first elbow bound would depend on $n$ and the last elbow bound would not.
-This, along with the unital fragment analysis, makes me think that calculating the bounds again for odd $n$ or $\epsilon > 3/7$ would reveal nice symmetries of the analysis, but it's probably not worth the time, so including last elbow analysis properly feels incomplete.
-
-Determining the sign of the difference between the last and first elbow bounds tells us which bound is better.
-The term $\log{\frac{u(\epsilon)v(\epsilon')}{u(\epsilon')v(\epsilon)}}$ is always positive for $\epsilon > \epsilon'$, therefore the last elbow bound, compared to the first elbow bound, is always \textbf{worse} in the first scenario and always \textbf{better} in the third scenario (remember, this is the yellow-ish right part of~\cref{fig:rate_contour}).
-
-In the second scenario ($\rm{(C2)} \rightarrow \rm{(C1)}$), the expression looks very weird to me, seems like the difference tends to $-\infty$ as $E_{\rm{max}} \rightarrow \infty$.
-I am a bit stuck with this expression and I am not sure it's worth putting more time in it.
+Using a similar analysis, we can also derive upper bounds from comparison of the last point coordinates of the Lorenz curve, which now corresponds to the smallest rescaled component.
+
+To this end, assume that the largest component of the equilibrium state distribution is $W_{\tau}(i,j)$.
+We now perform the Clifford operation
+\begin{equation}
+	\tau \longrightarrow X^{1-i}Z^{-j}\ \tau\ Z^{j}X^{i-1},
+\end{equation}
+which permutes the largest component such that $W_{\tau}(i,j) \longrightarrow W_{\tau}(1,0)$.
+Since we have that $u \leq v$ because $\epsilon \leq 3/7$, and we have already ensured that $W_{\tau}(1,0) \geq W_{\tau}(\bmx)$ for all $\bmx \in \mathbb{Z}_3^2$.
+Therefore, the largest rescaled component occurs when $i_{(1,0)} = n$ and $i_{\bmx} = 0$ for $\bmx \neq \bmo$ and is equal to $(v/W_{\tau}(1,0))^n$.
+Accordingly, the coordinates of the first Lorenz curve point after the origin are given by $(x_E, L_E) = ((W_{\tau}(1,0))^n, u(\epsilon)^n)$ for the input state and $(x'_E, L'_E) = ((W_{\tau'}(1,0))^m, u(\epsilon')^m)$ for the output state.
+
+We now redefine the quantities $\alpha_k$, so that again $\phi = -\beta^{-1} \log \zeta$, where $\zeta= \sum_{k\in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}$ and $\alpha_k$ now given by
+\begin{align}
+	\alpha_k = \sum_{r \in \mathbb{Z}_3} \braket{E_k}{1-r}\braket{1+r}{E_k}.
+\end{align}
+This allows us to rewrite $W_{\tau}(1,0) = {e^{\beta (F - \phi)}}/{3}$ and by using the last elbow constraint 
+\begin{equation*}
+	\frac{L_E - 1}{1-x_E} \geq \frac{L'_E - 1}{1-x_E'},
+\end{equation*}
+derived in~\cref{app:elb_constraints}, we can get a new bound expression.
+
+We note that it is also possible to perform a different Clifford transformation and get a different location $(W_{\tau}(\bmx))^n$, with $\bmx \neq \bmo$, since components $(W_{\rho}(\bmx))^n = u$ are all the same as long as $\bmx \neq \bmo$.
+The effect of this is to alter the expressions for the quantities $\alpha_k$, but not the resulting bound expression.
+
+\nick{This section on the last elbow bound is a little weak?}
 
@@
 \ddd{[Do we need to keep any of the details in this section? If not then delete it entirely.]}
+\nick{This proof offers: 1.
+the exact derivation of our main contour plot, justifying the quantities $\epsilon_\star$ and $\beta_\star$ 2.
+a method for lifting the ``Clifford change in basis'' assumption - Can be trimmed down to the case where $H=H'$.
+What do you think?}
 \begin{theorem}
@@
 \end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newpage
-\subsection{Free energy dependent magic distillation bounds}\label{free-energy-bound-proof}
-Here we prove theorem \ref{thm:free-energy}, which bounds magic distillation rates in terms of free energies.
-
-\begin{theorem}
-	Consider a magic distillation protocol on qutrits that transforms $n$ copies of an $\epsilon$--noisy Strange state into $m$ copies of an $\epsilon'$--noisy Strange state, with depolarising errors $\epsilon' \leq \epsilon \leq 3/7$.
-
-	Let $T =(k\beta)^{-1}$ be any temperature for the physical system and let $H= \sum_{k \in \mathbb{Z}_3} E_k |E_k\>\<E_k|$ be the Hamiltonian of each qutrit subsystem in its eigen-decomposition.
-Assume that for $n,m \rightarrow \infty$ the protocol's channel generates negligible correlations on the equilibrium state $\tau$, and so $\tau^{\otimes n} \longrightarrow \tau^{\prime \otimes m}$ for $n,m \gg 1$.
-We write the state $\tau'$ as $\tau' = e^{-\beta H'}/\Z'$ for some Hermitian $H'$.
-
-Given this, there are local Clifford changes of basis $C_1,C_2$, such that $\rho_1 := C_1 \rho_S(\epsilon) C_1^\dagger$ and $\rho_2 := C_2 \rho_S(\epsilon') C_2^\dagger$ for which the protocol gives
-\begin{equation}
-\rho_1^{\otimes n} \longrightarrow \rho_2^{ \otimes m}.
-\end{equation}
-Moreover, the magic distillation rate $R = m/n$ for the protocol is bounded by the expression
-\begin{equation}\label{eq:rate_bounds_proof}
-	R \leq \dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (\phi - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (\phi' - F')},
-\end{equation}
-where $F$ is the free energy of $\tau$,  and 
-\begin{equation}
-\phi = -\beta^{-1} \log \zeta
-\end{equation}
-with $\zeta$ given by the equations
-\begin{align}
-\zeta &= \sum_{k\in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}, \nonumber\\
-\alpha_k &= \sum_{r \in \mathbb{Z}_3} \braket{E_k}{-r}\braket{r}{E_k}.
-\end{align}
-The primed variables are defined similarly for the output system.
-\end{theorem}
-
-\begin{proof}	
-For the sake of clarity, we write $\rho_n \coloneqq \rho_S(\epsilon)^{\otimes n}$, $\rho'_m \coloneqq \rho_S(\epsilon')^{\otimes m}$, $\tau_n \coloneqq \tau^{\otimes m}$ and $\sigma_m \coloneqq \sigma^{\otimes m}$.
-
-To establish the distillation bound we consider the distillation protocol that gives $\E( \rho_n) = \rho_m$ for the magic states. 
-We then consider that the protocol transforms the reference equilibrium state as $\E( \tau_n) = \sigma_m$.
-Since $\tau$ and $\sigma$ are assumed to be full rank stabilizer states, they have a strictly positive Wigner distribution, while, in contrast, the input and output magic states generally have quasi-probability Wigner distributions.
-For any such protocol we therefore have that
-\begin{equation}
-	( W_{\rho_n}(\bmx), W_{\tau_n}(\bmx) ) \succ ( W_{\rho'_m}(\bmx), W_{\sigma_m}(\bmx) ),
-\end{equation}
-or, equivalently, in terms of the relevant Lorenz curves,
-\begin{equation}
-	L_{\rho_n |\tau_n}(x) \ge L_{\rho'_m |\sigma_m}(x) \mbox{ for all } x.
-\end{equation}
-
-We define the rescaled Wigner distribution $W_{\rho | \tau}(\x) \coloneqq W_\rho(\x)/W_\tau(\x)$, which is always well-defined since $\tau$ is full-rank. 
-Due to the multiplicative property of the Wigner distribution, the rescaled distribution is also multiplicative in the sense that
-\begin{equation}
-	W_{\rho \otimes \rho' | \tau \otimes \tau'} (\x_1 \oplus \x_2) = W_{\rho | \tau}(\x_1)W_{\rho' | \tau'}(\x_2),
-\end{equation}
-for any states $\rho, \rho'$ and any full-rank stabilizer states $\tau, \tau'$.
-Therefore we have that
-\begin{align}
-	W_{\rho_n |\tau_n} (\x) &= \prod_{i=1}^n W_{\rho|\tau}(\x_i)\\
-	W_{\rho_n } (\x) &= \prod_{i=1}^n W_\rho(\x_i)
-\end{align}
-where $\x = \oplus_{i=1}^n \x_i \in \mathbb{Z}_3^n$ is the phase space point for the full system in terms of those of the individual subsystems.
-
-The points defining the Lorenz curve $L_{\rho_n |\tau_n}(x)$ are obtained from sorting the components of $W_{\rho_n |\tau_n}(\x)$ in non-increasing order and then computing the partial sums of $W_{\rho_n |\tau_n}(\pi(\x))$ where $\pi$ is the permutation that realises the sorting.
-However, similarly to the unital fragment analysis, we aim to use the constraint that is obtained by considering the line segment connecting the origin to the first elbow of both Lorenz curves.
-The proof of this constraint is provided in~\cref{app:elb_constraints}.
-Therefore, we focus on finding the coordinates of some point on this line segment of the Lorenz curves.
-
-We find the coordinates for the input Lorenz curve, but the exact same analysis can be applied on the output Lorenz curve.
-The Wigner distribution of a single noisy Strange state consists of 1 negative component $W_{\rho}(0,0) = -v(\epsilon)$ and 8 positive components $W_{\rho}(\bmx) = u(\epsilon)$ for $\bmx \neq \bmo$.
-The Wigner distribution of the full-rank, stabilizer equilibrium state $\tau$ is $W_{\tau}(\bmx) > 0$ for all $\bmx \in \mathbb{Z}_3^2$.
-We keep the components completely general.
-
-Assume that the smallest component of the equilibrium state distribution is $W_{\tau}(i,j)$.
-We then make use of the freedom to apply Clifford unitaries in order to perform the  Clifford operation
-\begin{equation}
-	\tau \longrightarrow X^{-i}Z^{-j}\ \tau\ Z^{j}X^{i},
-\end{equation}
-which permutes the smallest component to the origin of the phase space, $W_{\tau}(i,j) \longrightarrow W_{\tau}(0,0)$.
-This operation would inevitably affect the magic distillation protocol, but since we consider the state distillation modulo Clifford operations, we are allowed to perform the reverse Clifford operation keeping the magic distillation process as is.
-\nick{statement here is inaccurate}
-
-The rescaled distribution components are in general given by
-\begin{equation}
-	W_{\rho_n|\tau_n} = \left(\frac{-v}{W_{\tau}(0,0)}\right)^{i_{\bmo}} \prod_{\bmx \neq \bmo} \left(\frac{u}{W_{\tau}(\bmx)}\right)^{i_{\bmx}},
-\end{equation}
-where the (integer) indices obey the following conditions:
-\begin{align}
-&0 \leq i_{\bmx} \leq n \mbox{ for all } \bmx \in \mathbb{Z}_3^2, \nonumber \\
-&\sum_{\bmx \in \mathbb{Z}_3^2} i_{\bmx} = n.
-\end{align}
-It is now easy to find the largest rescaled component.
-Firstly, note that $n$ is even, so we require that $i_{\bmo} \in \{0,2,\dots,n\}$ for the component to be positive.
-Then, we have that $v \geq u$ because $\epsilon \leq 3/7$, and we have already ensured that $W_{\tau}(0,0) \leq W_{\tau}(\bmx)$ for all $\bmx \in \mathbb{Z}_3^2$.
-Therefore, the largest rescaled component occurs when $i_{\bmo} = n$ and $i_{\bmx} = 0$ for $\bmx \neq \bmo$ and is equal to $(v/W_{\tau}(0,0))^n$.
-Accordingly, the coordinates of the first Lorenz curve point after the origin are given by
-\begin{equation}
-	(x_0, L_0) = ((W_{\tau}(0,0))^n, v^n)
-\end{equation}
-
-Given a Hamiltonian decomposition,
-\begin{equation}
-	H = \sum_{k \in \mathbb{Z}_3} E_k\ketbra{E_k}{E_k},
-\end{equation}
-we can re-express the coordinate location, by writing
-\begin{align}
-	W_{\tau}(0,0) &= \frac{1}{3\Z}\tr\left[ A_{0,0}e^{\beta H} \right] \nonumber\\
-	&= \frac{e^{\beta F}}{3} \tr\left[ \sum_{r \in \mathbb{Z}_3} \ketbra{-r}{r}\sum_{k \in \mathbb{Z}_3} e^{\beta E_k}\ketbra{E_k}{E_k} \right] \\
-	&= \frac{e^{\beta F}}{3} \sum_{r \in \mathbb{Z}_3} \alpha_k e^{\beta E_k}
-	= \frac{e^{\beta F}}{3} \zeta \\
-	&= \frac{e^{\beta (F - \phi)}}{3},
-\end{align}
-where $\alpha_k, \zeta$ and $\phi$ are as defined prior to the statement of the theorem.
-Finally, the coordinates can be expressed as
-\begin{equation}
-	(x_0, L_0) = \left( \frac{e^{n\beta (F - \phi)}}{3^n}, v(\epsilon)^n \right).
-\end{equation}
-In the same manner, we can derive the first point coordinates of the output Lorenz curve as
-\begin{equation}
-	(x'_0, L'_0) = \left( \frac{e^{n\beta (F' - \phi')}}{3^n}, v(\epsilon')^n \right).
-\end{equation}
-
-If the largest rescaled component of a state is distinct with no multiplicities, then these coordinates correspond to the first elbow of the corresponding Lorenz curve, whereas if it appears multiple times, then the coordinates derived correspond to a point on the interior of the line segment connecting the origin to the first elbow.
-In both cases, the distillation bound remains the same, as is clear by its derivation in~\cref{app:elb_constraints}, and it is given by $L_0 / x_0 \geq L'_0 / x'_0$, which can be directly rearranged into the stated bound of the theorem.
-\end{proof}

### 2021-05-07 magic_paper.tex
some quick fixes
No numerics yet. Corrected and tidied all appendices and outlook, answered all blue comments

@@
 % Write bounds as 1 + ln{}/{} or 1 - (-ln{})/{} ?
+% Labels and Refs (theorems vs lemmas vs propositions)
 % R: rate vs bound ?
-% Appendices: clean-up (d --> r)
+% Appendices: clean-up
+% Figs check(fig.0, move to app, consistency)
 
-% Figs check(fig.0, move to app, consistency)
-% Eq. numbering in last line always
+% Notation consistency
 % UK vs US english
-% Spacing (fig positioning, sections, paragraphs, QED symbols)
+% Spacing (fig positioning, sections, paragraphs, eq. numbering, QED symbols)
 
@@
 
+\nick{re-write based on new relative majorisation approach}
 The past few years have seen rapid progress towards the goal of a fault-tolerant quantum computer~\cite{Fowler_2012, Herrera_2010, Nickerson_2014, Nikahd_2017, chao_2018, lin_pieceable_2020, Lin_2020, Bourassa_2021}.
@@
 In contrast, Lorenz curves for magic states break through the value of $L(x)=1$ due to the presence of negativity in the associated quasi-probability distributions.
-The above family of curves correspond to multiple copies of noisy Strange states $\rho\coloneqq\rho_{\rm{S}}(\epsilon)^{\otimes n}$ (\cref{eq:noisysn}) for $n=2,4,6$ within a particular stabilizer fragment ($\sigma \coloneqq \id/3$).
-Solid lines represent pure Strange states, while dashed lines represent noisy Strange states with depolarising noise ($\epsilon = 0.1$).
+The above family of curves correspond to multiple copies of noisy Strange states $\rho\coloneqq\rho_{\rm{S}}(\epsilon)^{\otimes n}$ (\cref{eq:noisysn}) for $n=2,4,6$ within a particular stabilizer fragment ($\sigma = \id/3$).
+Solid lines represent pure Strange states, while dashed lines represent $\epsilon$-noisy Strange states with depolarising noise $\epsilon = 0.1$.
     }
@@
 Note, however, that unlike any monotone, this is not a single numerical constraint, but a \emph{family} of constraints.
-Indeed, for $n$ copies of a $d$--dimensional system the number of terms in $W_{\rho}$ is $d^{2n}$, so the Lorenz curve condition corresponds to exponentially many constraints, of which though there are at most as many independent constraints as there are elbows in the Lorenz curve of the output state, as proved in~\cref{thm:elbows} in~\cref{app:frag}.
+Indeed, for $n$ copies of a $d$--dimensional system the number of terms in $W_{\rho}$ is $d^{2n}$, so the Lorenz curve condition corresponds to exponentially many constraints, of which though there are at most as many independent constraints as there are elbows in the Lorenz curve of the output state, as proved in~\cref{thm:elbows} of~\cref{app:frag}.
 In principle, any one location $x$ provides some valid constraint leading to an upper distillation bound, while optimising over the location provides the strictest majorisation bound.
@@
 	The sum-negativity of a magic state $\rho$ can be written as $sn(\rho) \coloneqq \frac{1}{2} (\sum_{\x} |W_\rho(\x) | - 1)$.
-We make use of a variant form of relative majorization, (see~\cref{prop:rmajor} in~\cref{app:major}), stating that $\p \succ_{\r} \q$ if and only if
+We make use of a variant form of relative majorization, (see~\cref{app:major}), stating that $\p \succ_{\r} \q$ if and only if
 	\begin{equation}
@@
 There is an exact relation between $L_\star$ and sum-negativity or mana, which is provided by the following result.
-\begin{lemma}\label{lem:lcmax}
+\begin{theorem}\label{lem:lcmax}
 	Given a magic state $\rho$, the maximum $L_\star$ of its Lorenz curve $\lc{\rho}{\sigma}(x)$ is independent of the $\sigma$--fragment and equal to $1+\sn{\rho}$.
 Moreover, the majorization constraint is stronger than mana in every fragment.
-\end{lemma}
-The proof of this is given in Appendix \ref{lem:lcmax}.
+\end{theorem}
+The proof of this is given in~\cref{app:major}.
 Using the Lorenz curve perspective, it is simple to construct other monotones.
@@
 Notably, in contrast to the other bounds, $R_{\rm{opt}}$ depends explicitly on the copies $m,n$, rather than their ratio $m/n$, so it is specific to the process.
-An interesting question arises regarding the value of $R_{\rm{opt}}$ as $n,m \rightarrow \infty$, while $m/n$ remains constant.
+An interesting open question arises regarding the value of $R_{\rm{opt}}$ as $n,m \rightarrow \infty$, while $m/n$ remains constant.
 \begin{figure}[t]
@@
 To simplify our analysis we will make the following assumption.
-We assume that in the asymptotic/thermodynamic limit $n,m \rightarrow \infty$ that correlations generated in $\sigma$ are negligible.
+We assume that in the asymptotic/thermodynamic limit $n,m \rightarrow \infty$ that correlations generated \nick{between states $\tau_x^\prime$} are negligible.
 This implies that $d\mu(x)$ is peaked on a particular state $\tau'$, and so $\E(\tau) = \tau^{\prime \otimes m}$.
@@
 In this direction, we highlight recent work in majorization in which stochastic independence and correlations are analysed.
-In particular it has been shown that stochastic independence (no correlations) of independent distributions can be viewed as a resource in an extension of catalytic majorization, and leads to a single-shot operational interpretation of the Shannon entropy.
-\ddd{[cite: look up papers by Marcus Mueller.
-He has about 3 or 4 on this.
-Also Mark Wilde has a paper on it]}
+In particular, it has been shown that stochastic independence (no correlations) of independent distributions can be viewed as a resource in an extension of catalytic majorization, and leads to a single-shot operational interpretation of the Shannon entropy~\cite{muller_2015, muller_2016, muller_2019}.
 
 Our analysis will depend on the energetic properties of the probe state $\tau$ and the output state $\tau'$.
-For the state $\tau = e^{-\beta H}/\Z$ we have the Helmholtz free energy $F$ given by
+For the state $\tau = e^{-\beta H}/\Z$, the Helmholtz free energy $F$ is given by
 \begin{equation}
@@
 \end{equation}
-which is obtained from the internal energy via a Legendre transform \ddd{[cite books for $F$ details]}.
+which can be obtained from the internal energy via a Legendre transform~\cite{Pathria_1997}.
 
@@
 The intermediate terms depend on how the energy eigenbasis of the system $\{|E_k\>\}$ relates to the computational stabilizer basis $\{|k\>\}$.
-In particular the energetic term $\phi$ quantifies the degree to which the negativity in the Wigner representation can be ascribed a sharp energetic value for the given Hamiltonian of the system.
-Its form is similar to $F$, and so can informally be viewed as a `magic free energy' term, associated to a `partition function' $\zeta$.
-While the coefficients $\alpha_k$ may be negative for some $k$, the quantity $\phi$ is always well-defined since the function $\zeta$ is proportional to the Wigner component $W_\tau(0,0)$, which is strictly positive.
+In particular, the energetic term $\phi$ quantifies the degree to which the negativity in the Wigner representation can be ascribed a sharp energetic value for the given Hamiltonian of the system.
+Its form is similar to $F$, and so can informally be viewed as a `magic free energy' term, associated to a `magic partition function' $\zeta$.
+While the coefficients $\alpha_k$ may be negative for some $k$, the quantity $\phi$ is always well-defined, since the function $\zeta$ is a positive multiple of the stabilizer Wigner component $W_\tau(0,0)$.
 
@@
 
-The above analysis makes simplifying assumptions that could easily be dropped, at the price of more complex expressions.
-For example, we can obtain general expressions without any assumptions on $\epsilon,\epsilon'$ or drop the Clifford change in basis.
+The above bound demonstrates how one can use relative majorization of quasi-distributions to incorporate additional information into distillation bounds.
+The analysis involved makes simplifying assumptions that could easily be dropped, at the price of more complex expressions.
+For example, we can obtain general expressions without any assumptions on $\epsilon, \epsilon'$ or without performing any Clifford change in basis.
 We could also perform similar analysis for general qudits, and different choices of magic states.
@@
 
-The only non-trivial assumption is the assumption that we can ignore correlations in the thermodynamic limit.
+The only assumption that cannot be trivially dropped is the assumption that we can ignore correlations in the thermodynamic limit.
 This is a common situation in thermodynamics, where correlations are often sub-linear in the particle number in the macroscopic limit.
@@
     \caption{\textbf{Temperature-dependent bounds for magic distillation.}
-  Shown is a contour plot of  $R(\epsilon, \beta)$ for $H=H'$, where $\beta$ is an inverse temperature and $\epsilon$ is the depolarising noise of the magic state.
+  Shown is a contour plot of  $R(\epsilon, \beta)$ for $H = H' = \sum_{k \in \mathbb{Z}_3} k \ketbra{k}$ and $\epsilon' = 0$, where $\beta$ is the inverse temperature and $\epsilon$ the depolarising noise of the input magic state.
 The relevant data from the spectrum of the qutrit operator $H$ enters in via $\epsilon_\star(\beta)$ and $\beta_\star$.
-The vertical dashed line is the `Landauer-like' temperature threshold $\beta_\star$ and the diagonal dashed curve corresponds to the noise threshold $\epsilon_\star (\beta)$ for $\beta \leq \beta_\star$.
-The $\beta =0 $ line corresponds to the regime in which the magic protocol gives a unital channel.
+The vertical dashed line is the `Landauer-like' temperature threshold $\beta_\star$ and the diagonal dashed curve corresponds to the noise threshold $\epsilon_\star(\beta)$ for $\beta \leq \beta_\star$.
+\nick{Refer to definitions of starred quantities} The $\beta = 0$ line corresponds to the regime in which the magic protocol corresponds to a unital channel.
     }
@@
 \end{figure}
-\subsection{Variation of bounds with physical parameters}
-The bounds derived are based on analysis of only part of the Lorenz curves and can be improved via a finer analysis.
+
+The bound derived is based on analysis of only part of the Lorenz curves and can be improved via a finer analysis.
 This is apparent by simple numerical calculations on the entirety of the curves as seen in~\cref{fig:distill_bounds} for the case of unital operations.
-Specifically, the existing bounds follow by considering the dominant terms in the rescaled Wigner distribution and do not, for example, take into account the Lorenz curve's peak structure.
+Specifically, the existing bound follows by considering the dominant terms in the rescaled Wigner distribution and do not, for example, take into account the Lorenz curve's peak structure.
 
-\nick{FIX} As a special case of the result, suppose that $H=H'$, implying that the protocol leaves the equilibrium state unchanged, hence it corresponds to a Gibbs-preserving map~\cite{faist_2015}.
+As a special case of the result, suppose that $H=H'$, implying that the protocol leaves the equilibrium state unchanged, hence it corresponds to a Gibbs-preserving map~\cite{faist_2015}.
+We focus on the pure state distillation case, where $\epsilon' \rightarrow 0$, for which we obtain~\cref{fig:rate_contour}, a contour plot of the bound on $R$ as a function of inverse temperature $\beta$ and depolarising noise level $\epsilon$ for the initial noisy magic state.
+
 In the more general case, $\Delta F \coloneqq F' - F \ne 0$ and we have a free energy difference between the initial and final states, with respect to the relevant Hamiltonians.
@@
 \ddd{[Need some numerics on varying the $F'$ case]}
-\nick{FIX} The above bounds mainly demonstrate how one can use relative majorization of quasi-distributions to incorporate additional information into distillation bounds.
-However to unpack the results more it is useful to consider the case in which $H=H'$, and look at $\epsilon' \rightarrow 0$.
-For this we obtain~\cref{fig:rate_contour} which gives a contour plot of $R$ as a function of inverse temperature $\beta$ and depolarising noise level $\epsilon$ for the initial noisy magic state.
 
@@
 We have described how relative majorization can be used to establish upper bounds on magic distillation protocols that take into account additional physics of the system.
-Our bounds only exploited the very simplest aspects of the Lorenz curves of the quasi-distributions, and so it would be of interest to sharpen these bounds and exploit more of the structure in the asymptotic limit.
+Our bounds only exploited the very simplest aspects of the Lorenz curves of the quasi-distributions, so it would be of interest to sharpen these bounds and exploit more of the structure in the asymptotic limit.
 This raises interesting questions that do no arise for probability distributions, because we no longer have a notion of typicality and the central limit theorem does not apply.
-That said, for special states such as the Strange state the asymptotic behaviour is relatively simple and so one could study this and obtain a better handle on the $n\rightarrow \infty$ behaviour in a way.
-In appendix (\ddd{BLAH} we give some basic relations on this that could be explored further.
-\ddd{[where did the remainder term bounds go?
-People could potentially build on this]}
+That said, for special states such as the Strange state the asymptotic behaviour is relatively simple, so one could study this and obtain a better handle on the asymptotic behaviour ($n \rightarrow \infty$).
+An example of such a question was raised regarding the numerical bounds plotted in~\cref{fig:distill_bounds} for the unital fragment.
+In~\cref{app:lcsu_technical} we give some more extensive analysis in the unital fragment that could be explored further, while in~\cref{app:lcst_technical} we also provide some tools which are useful in all fragments.
 
@@
 
-  For example, the Clifford group action on a quantum system corresponds to the action of the affine symplectic group \ddd{[cite Gross discrete Hudson paper, and some maths source on symplectic group]} on the discrete phase space.
+For example, the Clifford group action on a quantum system corresponds to the action of the affine symplectic group~\cite{cit:gross3, cit:bengtsson} on the discrete phase space.
 Therefore, any convex mixture of Clifford unitaries will correpond to a convex mixture of these group actions.
-From the Hardy-Littlewood theorem \ddd{[cite]}, we know that traditional majorization is obtained from convex mixtures of arbitrary permutations.
-However this has been generalised to convex mixtures of elements of a group $G$ that acts on vectors.
-This $G$--majorization has been studied in the classical literature and a range of results are known about it \ddd{[cite papers]}.
-For example, if $G$ is a finite reflection group then the $G$--majorization pre-order is described by a finite list of conditions\ddd{[cite]}, just as happens for the full majorization ordering.
-One route is therefore to consider reflection sub-groups of the affine symplectic group, for which the majorization relation reduces to a finite set of conditions.
-This would therefore provide concrete lower bounds on distillation rates.
+From the Hardy-Littlewood theorem~\cite{hardy_1952}, we know that traditional majorization is obtained from convex mixtures of arbitrary permutations.
+However, this has been generalised to convex mixtures of elements of a group $G$ that acts on vectors.
+This $G$--majorization has been studied in the classical literature and a range of results are known about it~\cite{giovagnoli_1985, steerneman_1990, eaton_1977}.
+For example, if $G$ is a finite reflection group then the $G$--majorization pre-order is described by a finite list of conditions~\cite{giovagnoli_1985}, just as is the case for the relative majorization ordering.
+One route leading to concrete lower bounds on distillation rates is therefore to consider reflection sub-groups of the affine symplectic, or just symplectic, group, for which the majorization relation reduces to a finite set of conditions.
 
@@
 This would correspond to transformations that are \emph{not} unital, but still respect the symplectic structure.
-Physically, this regime would correspond to a form of thermo-majorization obtained from looking at the action of the Clifford group at a micro-canonical level, and then reducing to a small subsystem \ddd{[cite stat-mech book, cite Matteo review]}.
+Physically, this regime would correspond to a form of thermo-majorization obtained from looking at the action of the Clifford group at a micro-canonical level, and then reducing to a small subsystem~\cite{cit:lostaglio, Pathria_1997}.
 While this seems like a painful thing to consider, there is motivation for this beyond the aim of constructing lower bounds for magic protocols: in the case of statistical mechanics on a phase space this is precisely the situation, albeit in the continuum limit.
-Statistical mechanics of actual systems obey Hamiltonian dynamics and so automatically respect a symplectic form \ddd{[cite a stat-mech book]}.
-Therefore the pre-order of statistical mechanical states with respect to phase space dynamics preserving a Gibbs state must correspond to a symplectic thermo-majorization condition.
+Statistical mechanics of actual systems obey Hamiltonian dynamics and so automatically respect a symplectic form~\cite{Pathria_1997}.
+Therefore, the pre-order of statistical mechanical states with respect to phase space dynamics preserving a Gibbs state must correspond to a symplectic thermo-majorization condition.
 Of course, technical features arise in the continuum limit when considering distributions on an unbounded phase space, but this could be remedied by either considering a compact phase space (e.g.
 for a particle on a ring) or by first studying the discrete case.
-Such scenarios also arise in the Quantum Hall Effect \ddd{[cite]} and so this is another regime in which these techniques might be of use.
+Such scenarios also arise in the Quantum Hall Effect~\cite{Klitzing_1980}, which is thus another regime where these techniques might be of use.
 
-Finally, it would be of interest to consider the possibility of applying these techniques to other scenarios in which one wishes to distinguish classical from non-classical behaviour based on quasi-probability representations \ddd{[cite quantum optics reference, cite Ferrie review on quasi-reps]}
+Finally, it would be of interest to consider the possibility of applying these techniques to other scenarios in which one wishes to distinguish classical from non-classical behaviour based on quasi-probability representations~\cite{Ferrie_2008, barnett_1997}
 

### 2021-05-07 notes/notes.tex
some quick fixes
No numerics yet. Corrected and tidied all appendices and outlook, answered all blue comments

@@
 
-\ddd{[Going forward:
-\begin{enumerate}
-\item Does the ``last elbow'' give the same bound? Is it as simple?
-\item Numerically is this about as good as it gets from majorisation?
-\item How does this rate compare with existing literature?
-\end{enumerate}}
-
 An $n$-copy state $\rho^n$ has \emph{error rate} $\delta$ iff $\rho$ has an overlap of at least $1-\delta$ with magic state $\ket{\rm{S}}$,
@@
 
+With the help of this lemma, we directly arrive at 
+\begin{theorem}\label{thm:bounds_strict}
+	Given fixed positive integer $n$ and probability $p$, $\Phi_+, \Phi_-$ satisfy the following bounds:
+	\begin{align*}
+		\begin{split}
+		&\text{1. } \Phi_+(m; n, p) \geq \sum\limits_{\ell=0}^{m/2}\left[ 16\ell\left(1-\frac{2\ell}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{2\ell}{n}}{p}}, \\
+		&\hspace{14pt} \text{for all even } m\in [2,n] \\
+		&\text{2. } \Phi_+(m; n, p) \leq \sum\limits_{\ell=0}^{m/2}\left[ 4\pi\ell\left(1-\frac{2\ell}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{2\ell}{n}}{p}}, \\
+		&\hspace{14pt} \text{for all even } a\in [2,n] \\
+		&\text{3. } \Phi_-(m; n, p) \geq \sum\limits_{\ell=1}^{(m-1)/2}\left[ 16(\ell+1)\left(1-\frac{2\ell+1}{n}\right) \right]^{-\frac{1}{2}} \times \\
+		&\hspace{14pt} \times 2^{-n\ent{\frac{2\ell+1}{n}}{p}},\ \text{for all odd }a\in [1,n] \\
+		&\text{4. } \Phi_-(m; n, p) \leq \sum\limits_{\ell=1}^{(m-1)/2}\left[ 4\pi(\ell+1)\left(1-\frac{2\ell+1}{n}\right) \right]^{-\frac{1}{2}} \times \\
+		&\hspace{14pt} \times 2^{-n\ent{\frac{2\ell+1}{n}}{p}},\ \text{for all odd } a\in [1,n]
+		\end{split}
+	\end{align*}
+\end{theorem}
+\begin{proof}
+	All four statements follow from application of~\cref{lem:comb_bounds} on the combinatorial coefficient and the defintion of relative entropy given in~\cref{eq:ent_rel}
+\end{proof}
+
 \null\newpage
@@
 
+\subsection{Deriving distillation bounds from the last elbow}
+\label{sec:last_elb}
+
+\nick{RESTRUCTURE}
+
+To find the coordinates of the \textbf{last} elbow $(x_E, L_E)$, where $E$ is the number of elbows, we need to evaluate the minimum rescaled component,
+\begin{align}
+	&\bmw(\rho_{\rm{S}} | \sigma)_{\rm{min}} \coloneqq (3\Z)^{n}\times \nonumber\\
+	&\min\limits_{i,j,k}\Big\{ (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \label{eq:min_slope}
+\end{align}
+where $0 \leq i,j,k \leq n$ and $\alpha \coloneqq i+j+k \leq n$.
+Notice that for $0 \leq \epsilon \leq 3/7$, we have $v \geq u$. 
+We need the sum $\alpha = i+j+k$ to be odd for the expression to be negative.
+
+Given an odd value for the sum $\alpha$, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_0}$ is fixed (and negative), so the expression is minimised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
+Hence, we have
+\begin{align}
+	&\bmw(\rho_{\rm{S}} | \sigma)_{\rm{min}} = \nonumber\\
+	&-(3\Z)^{n} v^n e^{n\beta E_0}\max\limits_{\substack{\alpha = 1,3, \\ \dots,n-1}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}.
+\end{align}
+If the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than $1$ then the minimum occurs at $\alpha=1$, otherwise it occurs at $\alpha = n-1$.
+
+The minimum rescaled component can then be expressed as
+\begin{equation}
+\bmw(\rho_{\rm{S}} | \sigma)_{\rm{min}} =
+	\begin{cases}
+		-(3\Z)^{n} v^{n-1} u e^{\beta [(n-1)E_0 + E_{\rm{max}}]}, &\epsilon \leq \epsilon_{\star},\ \hspace{3pt}\rm{(C1)}	\\
+		-(3\Z)^{n} v u^{n-1} e^{\beta [E_0 + (n-1)E_{\rm{max}}]}, &\epsilon > \epsilon_{\star}.\ \hspace{5pt}\rm{(C2)} 
+	\end{cases}
+\end{equation}
+Case $\rm{(C1)}$ can correspond to $(i,j,k) = (1,0,0)$ if $E_{\rm{max}} = E_0$, when the multiplicity is $m_{100} = 2n$ and the corresponding Wigner components are $\bmw(\rho_{\rm{S}})_{100}, \bmw(\sigma)_{100}$ or it can correspond to $(i,j,k) = (0,1,0)$ ($(i,j,k) = (0,0,1)$), if $E_{\rm{max}} = E_1$ ($E_{\rm{max}} = E_2$), when the multiplicity is $m_{010} = 3n$ ($m_{001} = 3n$) and the corresponding Wigner components are $\bmw(\rho_{\rm{S}})_{010}, \bmw(\sigma)_{010}$ ($\bmw(\rho_{\rm{S}})_{001}, \bmw(\sigma)_{001}$).
+Case $\rm{(C2)}$ corresponds to $(i,j,k) = (0,n-1,0)$ ($(i,j,k) = (0,0,n-1)$)
+if we have $E_{\rm{max}} = E_1$ ($E_{\rm{max}} = E_2$), when the multiplicity is $m_{0,n-1,0} = 3^{n-1}n$ ($m_{0,0,n-1} = 3^{n-1}n$) and the corresponding Wigner components are $\bmw(\rho_{\rm{S}})_{0,n-1,0}, \bmw(\sigma)_{0,n-1,0}$ ($\bmw(\rho_{\rm{S}})_{0,0,n-1}, \bmw(\sigma)_{0,0,n-1}$).
+
+The last elbow coordinates can finally be derived by sutracting the appropriate rescaled component from 1, $(x_E, L_E) =$
+\begin{equation}\label{eq:last_elb_coords}
+	\begin{cases}
+		&\left( 1-\dfrac{2n}{(3\Z_\beta)^n}e^{-\beta [(n-1)E_0 + E_{\rm{max}}]},\ 1 + 2n v^{n-1} u \right), \vspace{5pt}\\
+		&\hspace{5pt} \text{if } E_{\rm{max}} = E_0, \hspace{51pt}\rm{(C1a)} \vspace{10pt}\\
+		&\left( 1-\dfrac{3n}{(3\Z_\beta)^n}e^{-\beta [(n-1)E_0 + E_{\rm{max}}]},\ 1 + 3n v^{n-1} u \right), \vspace{5pt}\\
+		&\hspace{5pt} \text{if } E_{\rm{max}} > E_0, \epsilon \leq \epsilon_{\star}, \hspace{20pt}\rm{(C1b)} \vspace{10pt}\\
+		&\left( 1-\dfrac{n}{3\Z_\beta^n}e^{-\beta [E_0 + (n-1)E_{\rm{max}}]},\ 1 + 3^{n-1}n v u^{n-1} \right), \vspace{5pt}\\
+		&\hspace{5pt} \text{if } E_{\rm{max}} > E_0, \epsilon \geq \epsilon_{\star}. \hspace{22pt}\rm{(C2)}
+	\end{cases}
+\end{equation}
+
+Assuming that $E_{\rm{max}} > E_0$ for clarity, we have the same three scenarios as in the case of the first elbow bound:
+\begin{enumerate}
+	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $\beta < \beta_{\star}$ and $\epsilon' < \epsilon  \leq \epsilon_{\star}$.
+	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $\beta < \beta_{\star}$ and $\epsilon' \leq \epsilon_{\star} < \epsilon$.
+	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $\beta < \beta_{\star}$ and $\epsilon_{\star} \leq \epsilon' < \epsilon$ or $\beta \geq \beta_{\star}$.
+\end{enumerate}
+Now using last elbow constraint, derived in~\cref{app:elb_constraints}, we can calculate new distillation bounds.
+The last elbow bounds can be rephrased in terms of the first elbow bound, leading to $R_{\rm{last-elb}} - R_{\rm{first-elb}} = $
+\begin{equation}\label{eq:last_elb_coords}
+	\begin{cases}
+		\dfrac{1}{n} \dfrac{\log{\frac{u(\epsilon)v(\epsilon')}{u(\epsilon')v(\epsilon)}}}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F(\beta))},\ &\rm{(C1)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
+		\dfrac{1}{n} \dfrac{\log{\frac{v(\epsilon)v(\epsilon')}{u(\epsilon)u(\epsilon')}} - 2\beta(E_{\rm{max}} - E_0)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
+		\dfrac{1}{n} \dfrac{\log{\frac{v(\epsilon')u(\epsilon')}{v(\epsilon')u(\epsilon)}}}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C2)},
+	\end{cases}
+\end{equation}
+
+Note that the last elbow bounds have a dependence on $n$, which interestingly is due to $n$ being even.
+Had we considered \textbf{odd} number of copies $n$, then the first elbow bound would depend on $n$ and the last elbow bound would not.
+This, along with the unital fragment analysis, makes me think that calculating the bounds again for odd $n$ or $\epsilon > 3/7$ would reveal nice symmetries of the analysis, but it's probably not worth the time, so including last elbow analysis properly feels incomplete.
+
+Determining the sign of the difference between the last and first elbow bounds tells us which bound is better.
+The term $\log{\frac{u(\epsilon)v(\epsilon')}{u(\epsilon')v(\epsilon)}}$ is always positive for $\epsilon > \epsilon'$, therefore the last elbow bound, compared to the first elbow bound, is always \textbf{worse} in the first scenario and always \textbf{better} in the third scenario (remember, this is the yellow-ish right part of~\cref{fig:rate_contour}).
+
+In the second scenario ($\rm{(C2)} \rightarrow \rm{(C1)}$), the expression looks very weird to me, seems like the difference tends to $-\infty$ as $E_{\rm{max}} \rightarrow \infty$.
+I am a bit stuck with this expression and I am not sure it's worth putting more time in it.
+
 \end{document}

### 2021-05-09 magic_paper.tex
Proof improved. Proper handling of translation issue. Appendices absorbed into main tex file. Other appendix details fixed/tidied. More to do.

@@
 
+\subsection{Free energy measures and sub-linear correlations in the thermodynamic limit}
 To simplify our analysis we will make the following assumption.
-We assume that in the asymptotic/thermodynamic limit $n,m \rightarrow \infty$ that correlations generated \nick{between states $\tau_x^\prime$} are negligible.
+We assume that in the asymptotic/thermodynamic limit $n,m \rightarrow \infty$ that correlations generated between subsystems are negligible.
 This implies that $d\mu(x)$ is peaked on a particular state $\tau'$, and so $\E(\tau) = \tau^{\prime \otimes m}$.
@@
 
-This provides a simple means to specify energetic details of a protocol through how much it would disturb some reference equilibrium state.
-The approach, when combined with relative majorization, also allows us to derive magic distillation bounds that combine both the computational measures $\epsilon,\epsilon'$, with terms that depend on the Hamiltonian of the physical system.
+\subsection{Free energy dependent bounds on magic state distillation protocols}
+The preceding discussion gives a means to specify energetic details of a protocol through how much it would disturb some reference equilibrium state.
+When combined with relative majorization, it also allows us to derive magic distillation bounds that combine both the computational measures $\epsilon,\epsilon'$, with terms that depend on the Hamiltonian of the physical system.
 As discussed in section~\nick{REF}, from the perspective of majorization the presence of magic can be viewed as a form of non-classical free energy and so it is also of interest to make an explicit link between the amount of magic in a non-equilibrium state $\rho_S(\epsilon)$ and the actual free energy of an equilibrium state $\tau(\beta)$.
@@
 	Consider a magic distillation protocol on qutrits that transforms $n$ copies of an $\epsilon$--noisy Strange state into $m$ copies of an $\epsilon'$--noisy Strange state, with depolarising errors $\epsilon' \leq \epsilon \leq 3/7$.
-Let $T =(k\beta)^{-1}$ be any temperature for the physical system and let $H= \sum_{k \in \mathbb{Z}_3} E_k |E_k\>\<E_k|$ be the Hamiltonian of each qutrit subsystem.
-
-Assume for $n,m \rightarrow \infty$ that the protocol's channel $\E$ generates negligible correlations on the equilibrium state, so there is a state $\tau'$ such that
-\begin{equation}
-	\tau^{\otimes n} \longrightarrow \E(\tau^{\otimes n}) = \tau^{\prime \otimes m}
-\end{equation} 
-for $n,m \gg 1$. 
-We write the output state as $\tau' = e^{-\beta H'}/\Z'$ for some Hermitian $H'$.
-
-Given this, there are local Clifford changes of basis $C_1,C_2$, such that $\rho_1 := C_1 \rho_S(\epsilon) C_1^\dagger$ and $\rho_2 := C_2 \rho_S(\epsilon') C_2^\dagger$ for which the protocol gives
-\begin{equation}
-\rho_1^{\otimes n} \longrightarrow \rho_2^{ \otimes m}.
-\end{equation}
-Moreover, the magic distillation rate $R = m/n$ for the protocol is bounded by the expression
+We also allow pre/post-processing by local Clifford unitaries.
+
+	Let $T =(k\beta)^{-1}$ be any finite temperature for the physical system and let $H= \sum_{k \in \mathbb{Z}_3} E_k |E_k\>\<E_k|$ be the Hamiltonian of each qutrit subsystem in its eigen-decomposition.
+Assume that in the thermodynamic limit the protocol applied to $\tau^{\otimes n}$, gives $\tau^{\otimes n} \longrightarrow \tau^{\prime \otimes m}$ for $n,m \gg 1$, and write the state $\tau'$ as $\tau' = e^{-\beta H'}/\Z'$ for some Hermitian $H'$.
+
+Then the magic distillation rate $R = m/n$ for the protocol is bounded by the expression
 \begin{equation}\label{eq:rate_bounds_proof}
@@
 \end{equation}
-with $\zeta$ given by the equations
+with $\zeta$ given by the expressions
 \begin{align}
 	\zeta &= \sum_{k\in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}, \nonumber\\
-\alpha_k &= \sum_{r \in \mathbb{Z}_3} \braket{E_k}{-r}\braket{r}{E_k}.
-\end{align}
-The primed variables are defined similarly for the output system.
+	\alpha_k &= \sum_{r \in \mathbb{Z}_3} \<E_k| A_{\x_\star} |E_k\>,
+\end{align}
+with $\x_\star = \mbox{argmin}[W_\tau( \x )]$. The primed variables are defined similarly for the output system.
 \end{theorem}
@@
 \appendix
-\input{appendix}
+\newpage
+\section{Properties of Wigner distributions}
+\label{app:wigner}
+
+Here, we present basic properties of the phase-point operators and the Wigner distribution that are used throughout the paper.
+
+\begin{proposition}\label{thm:aproperties}
+    For any dimension $d$, the phase-point operators satisfy:
+    \begin{enumerate}
+        \item[(i)]\label{en:a1} Hermiticity and unitarity: $A_{\bmx}^\dagger = A_{\bmx} = A_{\bmx}^{-1}$;
+	    \item[(ii)]\label{en:a2} Closure under transposition: $A_{(x, p)}^T = A_{(x, -p)}$;
+	    \item[(iii)]\label{en:a3} Unit trace for odd $d$: $\tr[A_{\bmx}] = 1$;
+	    \item[(iv)]\label{en:a4} Completeness relation: $\sum_{\bmz \in \cal{P}_d} A_{\bmz} = d\id$;
+	    \item[(i)]\label{en:a5} Orthogonality: $\tr[A_{\bmx}^\dagger A_{\bm{x'}}] = d \delta_{\bmx,\bm{x'}}$.
+	\end{enumerate}
+\end{proposition}
+All properties follow from the definition in~\cref{eq:ax} along with properties of the displacement operator $D_{\bmx}$ and can be found in the literature, e.g.~\cite{cit:veitch,Vourdas_2004,cit:gross3}
+
+\begin{proposition}\label{thm:wstate}
+  The Wigner distribution of a state $\rho \in \cal{B}(\cal{H}_d)$ is
+  \begin{enumerate}
+    \item[(i)]\label{en:w1} Real valued: $\W{\rho} \in \mathbb{R}^{d^2}$;
+    \item[(ii)]\label{en:w2} Normalised: $\sum_{\bmz \in \cal{P}_d} \W[\bmz]{\rho}=1$;
+    \item[(iii)]\label{en:w3} Bounded: $\abs{\W[\bmx]{\rho}} \leq \frac{1}{d}$.
+    \item[(iv)]\label{en:w4} Additive under mixing: \vspace{2pt}\\
+    $\W[\bmx]{p\rho_1 + (1-p)\rho_2} = p\W[\bmx]{\rho_1} + (1-p)\W[\bmx]{\rho_2}$;
+    \item[(v)]\label{en:w5} Multiplicative under tensor products: \vspace{2pt}\\
+    $\W[\bmx_A \oplus \bmx_B]{\rho_A \otimes \rho_B} = \W[\bmx_A]{\rho_A}\W[\bmx_B]{\rho_B}$.
+	\end{enumerate}
+\end{proposition}
+\begin{proof}
+	Proof of all properties can be found in the literature~\cite{cit:veitch,Vourdas_2004,cit:gross3,Wang_2019} except for property (iii) which we prove here.
+
+Let $\{\lambda_i\}_{i \in \mathbb{Z}_d}$ be the (non-negative) eigenvalues of $\rho$, summing to 1.
+Let $\{\alpha_{\bmx,i}\}_{i \in \mathbb{Z}_d}$ be the eigenvalues of $A_{\bmx}$. For any $\bmx, \alpha_{\bmx,i} \in \{-1, 1\}$, due to the hermiticity and unitarity of the phase-point operators. 
+Then,
+\begin{align}
+	\abs{W_{\rho}(\bmx)} &= \frac{1}{d}\abs{\tr[A_{\bmx} \rho]} \leq \frac{1}{d} \abs{\sum_i \alpha_{\bmx,i} \lambda_i} \nonumber\\ &\leq \frac{1}{d}\sum_i \lambda_i = \frac{1}{d}.
+\end{align}
+The first inequality follows from Theorem 1 of~\cite{cit:mirsky} for the trace of complex matrices, while the second is the Cauchy-Schwarz inequality.
+\end{proof}
+
+\begin{proposition}
+    \label{thm:wchannel}
+    The Wigner distribution of a $\cptp$ operation $\E: \cal{B}(\cal{H}_{d_A}) \mapsto \cal{B}(\cal{H}_{d_B})$ is
+    \begin{enumerate}
+        \item[(i)]\label{en:wo1} Real-valued: $\W{\E} \in \mathbb{R}^{d^2} \times \mathbb{R}^{d^2}$;
+        \item[(ii)]\label{en:wo2} Normalised: $\sum_{\bmz \in \cal{P}_{d_B}} \W[\bmz|\bmx]{\E} = 1$ \\ 
+        for any $\bmx \in \cal{P}_{d_A}$;
+        \item[(iii)]\label{en:wo3} Bounded: $\abs{\W[\bmy|\bmx]{\E}} \leq \frac{d_A}{d_B}$;
+	    \item[(iv)]\label{en:wo4} Transitive: $\W[\bmy]{\E(\rho)} = \sum_{\bmz \in \cal{P}_{d_A}} \W[\bmy|\bmz]{\E} \W[\bmz]{\rho}$ for any $\bmy \in \cal{P}_{d_B}$.
+    \end{enumerate}
+\end{proposition}
+If $d_A = d_B$, and in particular if operation $\E$ maps a Hilbert space onto itself, then the stochasticity condition $\abs{\W[\bmy|\bmx]{\E}} \leq 1$ is satisfied.
+\begin{proof}
+	Proof of all properties are provided by Wang \textit{et al.}~\cite{Wang_2019} except for property (iii) which is a direct consequence of the definition of $\W{\E}$ and the corresponding property (iii) in~\cref{thm:wstate}.
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Properties of majorization}
+\label{app:major}
+
+We now give the following equivalent formulations of $d$--majorization.
+
+\begin{proposition}\label{prop:rmajor}
+Given $\bmx, \bmy, \r \in \mathbb{R}^n$, such that the components of $\r$ are positive, the following statements are equivalent:
+  \begin{enumerate}
+    \item[(i)] $\bmy = A\bmx$ and $\r = A\r$ for a stochastic map $A$;
+    \item[(ii)]\label{en:tm3} $\sum\limits_{i=1}^n \abs{x_i - r_i t} \leq \sum\limits_{i=1}^n \abs{y_i - r_i t}$ for all $t \in \mathbb{R}$;
+    \item[(iii)] $L_{\bmx|\r}(t) \leq L_{\bmy|\r}(t)$ for $t\in [0,1)$ and \vspace{5pt}\\ $L_{\bmx|\r}(1) = L_{\bmy|\r}(1)$.
+  \end{enumerate}
+\end{proposition}
+The proofs for these can be found in~\cite{cit:marshall,cit:bhatia,cit:nielsen,cit:lostaglio} and references therein.
+
+The following result is used in the text to relate relative majorization of quasi-distributions to their Lorenz curves.
+\begin{proposition}\label{lemma:Lorenz_linearity}
+	Let $\p$ be a quasi-probability distribution and let $\r$ be a probability distribution with strictly non-zero components.
+Let $a > 0$ and $b \in \mathbb{R}$ then $L_{a\p + b \r | \r} (x) = a L_{\p |\r}(x) + b x$.
+\end{proposition}
+\begin{proof} 
+	The Lorenz curve of $a\p + b \r$ relative to $\r$ passes through $(0,0)$ and the points $(\sum_{i=1}^k{r_{\pi(i)}}, \sum_{i=1}^k(a \p + b \r)_{\pi(i)})$ where $\pi$ is the permutation that puts $(a p_i/r_i + b)$ in non-increasing order.
+Since $a > 0$, the permutation $\pi$ puts  $(p_i/r_i)$ in non-increasing order too.
+We thus have
+\begin{align*}
+&\left( \sum_{i=1}^kr_{\pi(i)}, \sum_{i=1}^k(a \p + b \r)_{\pi(i)} \right) = \\ 
+&\left( \sum_{i=1}^k r_{\pi(i)},a \sum_{i=1}^k  p_{\pi(i)} + b\sum_{i=1}^k r_{\pi(i)} \right) \nonumber,
+\end{align*}
+therefore the value of the Lorenz function at each potential elbow point $x_k = \sum_{i=1} ^kr_{\pi(i)}$ is given by
+\begin{align}
+&L_{a \p +b \r|\r} (x_k) = a L_{\p|\r} (x_k) + b L_{\r|\r}(x_k) = \nonumber\\
+&a L_{\p|\r} (x_k) + b x_k,
+\end{align}
+so we have $L_{a\p  + b\r|\r} (x) = a L_{\p |\r}(x) + b x$ for any $x \in [0,1]$ due to linearity.
+\end{proof}
+
+\begin{theorem*}
+	Given a magic state $\rho$, the maximum $L_\star$ of its Lorenz curve $\lc{\rho}{\sigma}(x)$ is independent of the $\sigma$--fragment and equal to $1+\sn{\rho}$.
+Moreover, the majorization constraint is stronger than mana in every fragment.
+\end{theorem*}
+\begin{proof}
+	We denote the Wigner distributions of the states compactly as vectors $\bmw(\rho) \equiv W_\rho(x)$ and $\bmw(\sigma) \equiv W_\sigma(x)$.
+	We choose the component indexing so that the rescaled distribution 
+	\begin{equation}
+		\widetilde{\bmw}(\rho|\sigma) \coloneqq \left(\frac{w(\rho)_1}{w(\sigma)_1}, \dots, \frac{w(\rho)_{d^2}}{w(\sigma)_{d^2}} \right)^T,
+	\end{equation}
+	is sorted, $\widetilde{\bmw} = \widetilde{\bmw}^\downarrow$.
+	Note that all components of $\bmw(\sigma)$ are positive, so $\widetilde{w}_i \geq 0$ if and only if $w(\rho)_i \geq 0$ for any $i=1,\dots,d^2$.
+
+	Let $i_\star$ be the index of the smallest non-negative component of $\widetilde{\bmw}^\downarrow$.
+	Then, $w(\rho)_i < 0$ if and only if $i > i_\star$, so the maximum of Lorenz curve $\lc{\rho}{\sigma}(x)$ takes the value 
+	\begin{equation}
+		\lc{\rho}{\sigma}(x_{i_\star}) = \sum_{i=1}^{i_\star} w(\rho)_i,
+	\end{equation}
+	and is achieved at
+	\begin{equation}\label{eq:maxloc}
+		x_{i_\star} \coloneqq \sum_{i=1}^{i_\star} w(\sigma)_i.
+	\end{equation}
+
+	The location of the maximum ($x=x_{i_\star}$) varies from fragment to fragment, but its value is independent of $\sigma$,
+	\begin{align}
+	L_\star &:=	\lc{\rho}{\sigma}(x_{i_\star}) 
+		= \sum\limits_{\bmx: \W[\bmx]{\rho} \geq 0} \W[\bmx]{\rho} \nonumber \\
+		&= 1 + \sn{\rho}.
+	\end{align}
+
+Since the magic monotone mana is a monotonic function of sum-negativity, $\rm{mana}(\rho) \coloneqq \ln{(2\hspace{1pt}\sn{\rho}+1)}$, we see that mana corresponds precisely to the peak of the Lorenz curve $L_{\rho|\sigma}(x)$.
+Therefore, mana is one of $d^{2n}$ constraints, so majorization is strictly a stronger constraint in any fragment.
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Technical properties of $\sigma$--fragments}
+\label{app:frag}
+
+In this section, we discuss some technical aspects of general $\sigma$--fragments.
+
+We first prove a result on the independence of the Lorenz curve constraints, stated in~\cref{sec:major_frag}.
+\begin{proposition}\label{thm:elbows}
+	Let $\rho, \tau$ be two quantum states with Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in the $\sigma$--fragment.
+
+	Let $t$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ at locations $x_1, \dots, x_t$.
+
+	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\tau}{\sigma}(x_{i})$ for all $i =1,\dots,t$.
+\end{proposition}
+\begin{proof}	
+	$\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ trivially implies $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\tau}{\sigma}(x_{i})$ for all $i = 1,\dots,n'$.
+
+	Conversely, assume that $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\tau}{\sigma}(x_{i})$ for all $i = 1,\dots,r$.
+	First, let $x_0 = 0$ and $x_{n'+1} = 1$, so that $\lc{\rho}{\sigma}(x_0) = \lc{\tau}{\sigma}(x_0) = 0$ and $\lc{\rho}{\sigma}(x_{n'+1}) = \lc{\tau}{\sigma}(x_{n'+1}) = 1$.
+	Hence, we can extend the set of elbows $E$ to $E' = E \cup \{x_0, x_{n'+1}\}$.
+
+	Pick two consecutive locations $x_{i}, x_{i+1}$ in $E'$ and consider the line segment $\ell_\tau(x)$ connecting points $(x_{i}, \lc{\tau}{\sigma}(x_{i}))$ and $(x_{i+1}, \lc{\tau}{\sigma}(x_{i+1}))$ as well as the line segment $\ell_\rho(x)$ connecting points $(x_{i}, \lc{\rho}{\sigma}(x_{i}))$ and $(x_{i+1}, \lc{\rho}{\sigma}(x_{i+1}))$.
+	This is illustrated in~\cref{fig:elbows_proof}.
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.5]{figs/elbows_proof.pdf}
+    \caption{\textbf{Illustration of~\cref{thm:elbows}}.
+    }
+    \label{fig:elbows_proof}
+\end{figure}
+
+	Due to concavity of $\lc{\rho}{\sigma}$, it is clear that for all $x \in [x_{i}, x_{i+1}]$, we have $\lc{\rho}{\sigma}(x) \geq \ell_\rho(x) \geq \ell_\tau(x) = \lc{\tau}{\sigma}(x)$.
+	This argument can be made in all intervals $[x_{i}, x_{i+1}]$ with $i=0,\dots,n'$, so the proof is complete.
+\end{proof}
+The above theorem can be of practical importance in reducing the necessary distillation constraints derived via majorization in $\sigma$--fragments.
+
+\begin{proposition}\label{thm:frag_app}
+    Let $\R = (\F, \O)$ be a magic theory and $\sigma, \sigma' \in \F$. The following statements hold:
+    \begin{enumerate}
+        \item No $\sigma$--fragment of $\R$ is empty.
+        \item If a free operation leaves two states invariant, then it also leaves their mixtures invariant, 
+        \begin{equation*}
+            \O_{\sigma} \cap \O_{\sigma'} \subseteq \O_{p\sigma + (1-p)\sigma'}\ \text{for any}\ p \in [0,1].
+        \end{equation*}
+    \end{enumerate}
+\end{proposition}
+\begin{proof}$ $\vspace{-12pt}\\
+
+\begin{enumerate}
+    \item The identity channel $1_{\rm{C}}$ belongs to every $\sigma$--fragment, as $1_{\rm{C}} \in \O$ and $1_{\rm{C}}\sigma = \sigma$ for all $\sigma \in \F$.
+
+    \item Let $\E \in \O_{\sigma} \cap \O_{\sigma'}$.
+    Then $\E \in \cptp$ and corresponds to stochastic Wigner distribution $\W{\E}$ such that $\W{\E} \W{\sigma} = \W{\sigma}$ and $\W{\E} \W{\sigma'} = \W{\sigma'}$.
+    Then, $\W{\E} \W{p\sigma + (1-p)\sigma'} = \W{p\sigma + (1-p)\sigma'}$ for any $p \in [0,1]$ due to the additive property~\ref{en:w4} of the Wigner distribution, implying that state $p\sigma + (1-p)\sigma'$ is also left invariant by $\E$.
+\end{enumerate}
+\vspace{-20pt}
+\end{proof}
+
+Any free state $\sigma \in \F$ corresponds to a $d^2$--dimensional probability distribution $\W{\sigma}$ and any free operation $\E \in \O$ corresponds to a $d^2 \times d^2$ stochastic matrix (or conditional probability distribution) $\W{\E}$.
+Note that these mappings are one-to-one due to the orthogonality of the phase-point operators as an operator basis.
+Note further that free states $\F$ are mapped onto a \emph{strict subset} of the set of probability distributions.
+As a counterexample, the sharp $d^2$--dimensional probability distribution $(1, 0, \dots, 0)$ does not correspond to any qudit Wigner distribution because of the boundedness condition in~\cref{thm:wstate}.
+Similarly, not all stochastic matrices correspond to completely positive operations.
+As an example, consider the permutation matrix
+\begin{equation}
+    \Pi_X = \begin{psmallmatrix}
+        0 & 1 & 0 & 0 & 0 \\
+        0 & 0 & 0 & 0 & 1 \\
+        0 & 0 & 0 & 1 & 0 \\
+        1 & 0 & 0 & 0 & 0 \\
+        0 & 0 & 1 & 0 & 0
+    \end{psmallmatrix} \otimes \begin{psmallmatrix}
+        0 & 0 & 1 & 0 & 0 \\
+        0 & 0 & 0 & 0 & 1 \\
+        0 & 0 & 0 & 1 & 0 \\
+        1 & 0 & 0 & 0 & 0 \\
+        0 & 1 & 0 & 0 & 0    
+    \end{psmallmatrix} \in {\rm{S}}_5({\W{\frac{1}{5}\id}}).
+\end{equation}
+It preserves the uniform distribution $\W{\frac{1}{5}\id}$, but it does not correspond to any positive (hence quantum) operation.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Lorenz curves in the unital fragment}
+\label{app:lcsu_technical}
+
+\subsection{Binomial distributions and error bounds}\label{app:phi}
+Consider an experiment consisting of $n$ trials of throwing a $p$--coin, that is a coin with probability $p$ of landing on one side and $1-p$ of landing on the other.
+We express the sums over an even number $m$ of successful trials $\Phi_+$ and an odd number $m$ of successful trials $\Phi_-$,
+\begin{align}	
+	\Phi_+(m; n, p) &\coloneqq \sum\limits_{\ell=0}^{m/2} \binom{n}{2\ell} p^{2\ell} (1-p)^{n-2\ell}, \nonumber\\ 
+	&\text{for even integers } m\in[0,n], \label{eq:fp_app} \\
+	\Phi_-(m; n, p) &\coloneqq \sum\limits_{\ell=1}^{(m-1)/2} \binom{n}{2\ell+1} p^{2\ell+1} (1-p)^{n-(2\ell+1)}, \nonumber\\ 
+	&\text{for odd integers }m\in[0,n]. \label{eq:fn_app}
+\end{align}
+Note that index $m$ only takes even (odd) values when labelling $\Phi_+$ ($\Phi_-$).
+In~\cref{app:lcsu_coord}, we will use $\Phi_+$ and $\Phi_-$ to express the elbow coordinates of Lorenz curves in the unital fragment.
+
+We also define the classical entropy of a $p$--coin and the classical relative entropy between a $p$--coin and a $q$--coin,
+\begin{align}
+	S(p) &\coloneqq -p\log{p} -(1-p)\log{(1-p)}, \label{eq:ent}\\
+	\ent{p}{q} &\coloneqq p \log{\frac{p}{q}} + (1-p) \log{\frac{1-p}{1-q}}. \label{eq:ent_rel}
+\end{align}
+They are symmetric in the sense that $S(p) = S(1-p)$ and $\ent{p}{q} = \ent{1-p}{1-q}$.
+
+A useful result is the entropic bound on a combination~\cite{cit:ash}.
+\begin{lemma}\label{lem:comb_bounds}
+	For all $\ell\in [1,n-1]$,
+	\begin{align}
+		&\left[ 8\ell\left(1-\frac{\ell}{n}\right) \right]^{-\frac{1}{2}} 2^{n S\left(\frac{\ell}{n}\right)} \leq \binom{n}{\ell} \leq \\
+		&\left[ 2\pi \ell\left(1-\frac{\ell}{n}\right) \right]^{-\frac{1}{2}} 2^{n S\left(\frac{\ell}{n}\right)}.
+	\end{align}
+\end{lemma}
+The proof provided in~\cite{cit:ash} proceeds with direct calculation for the edge cases $\ell = 1,2, n-1, n-2$ and use Stirling's approximation for the remaining cases.
+We can use~\cref{lem:comb_bounds} to provide strict upper and lower bounds on the functions $\Phi_+, \Phi_-$.
+
+\subsection{Theory on bounding the core functions}
+\nick{Should we really keep this section? It is standard calculus and the bounds are really loose.}
+Here we present a more manageable method of bounding the core functions $\Phi_{\pm}$, which however results in looser bounds. 
+We can rewrite the functions as
+\begin{equation}
+	\Phi_{\pm}(m; n, a) = \frac{1}{2}(\Phi(m; n, a) \pm (1+a)^{-n} S(m; n, a)),
+\end{equation}
+where we have substituted $a = p/(1-p)$. 
+$\Phi$ is the standard cumulative function
+\begin{equation}
+	\Phi(m; n, a) = (1+a)^{-n} \sum_{k=0}^m \binom{n}{k} a^k,
+\end{equation}
+and the remainder term is
+\begin{equation}
+	S(m; n, a) \coloneqq \sum_{k=0}^m \binom{n}{k} (-a)^k.
+\end{equation}
+We have the following asymptotic bounds on the behaviour of $\Phi$~\cite{cit:ash},
+\begin{lemma}\label{lem:phi_bounds}
+	Given fixed $n>0$ and $p$, $\Phi$ satisfies the following bounds:
+	\begin{align*}
+		\begin{split}
+		&\text{1. } \Phi(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m}{n}}{p}}, \\
+		&\hspace{14pt} m\in [1,n-1] \\
+		&\text{2. } \Phi(m; n, p) \geq 1 - 2^{-n\ent{\frac{m+1}{n}}{p}},\ m\in [np+1,n-2] \\
+		&\text{3. } \Phi(m; n, p) \leq 1 - \left[ 8(m+1)\left(1-\frac{m+1}{n}\right) \right]^{-\frac{1}{2}}\times \\
+		&\hspace{14pt} 2^{-n\ent{\frac{m+1}{n}}{p}},\ m\in [0,n-2]
+		\end{split}
+		\\
+		&\text{4. } \Phi(m; n, p) \leq 2^{-n\ent{\frac{m}{n}}{p}},\ m\in [0,np]
+	\end{align*}
+\end{lemma}
+
+We would like some theory that estimates the value of $S(m; n, a)$ for different parameter regimes. 
+We can consider the function $f(x) = (1+x)^n$ and note that $S(m; n, a)$ is the $m$'th partial sum of this expansion at the point $x=-a$.
+
+The truncated Maclaurin series of a general function $f(x)$ is
+\begin{equation}
+	f(x) = f(0) + x f'(0) + \dots \frac{x^m}{m!}f^{(m)}(0) + R_m(x)
+\end{equation}
+with a remainder term
+\begin{align}
+	R_m (x)&= \int_{0}^x dt f^{(m+1)}(t) \frac{(x-t)^m}{m!} \\
+	&= \frac{x^{m+1}}{(m+1)!} f^{(m+1)}(x_*),
+\end{align}
+where in the second expression, $x_*$ is an implicit point that lies between $0$ and $x$ that comes from the Mean Value Theorem.
+
+Applying this to the function $f(x) = (1+x)^n$ gives
+\begin{equation}
+	(1+x)^n = \sum_{k=0}^m \binom{n}{k} x^k + R_m.
+\end{equation}
+Evaluating at $x=-a$ gives
+\begin{equation}
+	S(m; n, a) = (1-a)^n - R_m(-a),
+\end{equation}
+where the key remainder term is given by
+\begin{align}
+	R_m(-a) &= \int_0^{-a} dt f^{(m+1)}(t) \frac{(-a-t)^m}{m!} \\
+&= \frac{(-a)^{m+1}}{(m+1)!} f^{(m+1)}(x_*).
+\end{align}
+We can also compute the derivative $f^{(m+1)}(x)$ explicitly,
+\begin{equation}
+	f^{(m+1)}(x) = (m+1)!\binom{n}{m+1}(1+x)^{n-m-1}.
+\end{equation}
+Therefore, we have that
+\begin{align}
+	R_m(-a) &= (-1)^{m+1}(m+1)\binom{n}{m+1}\times \nonumber\\
+	&\hspace{12pt} \int_{-a}^0 dt (1+t)^{n-m-1}(a+t)^m \\
+&= \binom{n}{m+1}(-a)^{m+1}(1+x_*)^{n-m-1},
+\end{align}
+where in the latter expression $x_* \in [-a,0]$. 
+Note that the first integral expression can be estimated via the Cauchy-Schwarz or the H{\"o}lder inequality. 
+Therefore, we can either work with an explicit form with an unknown (but bounded) parameter $x_*$, or we can use the integral form and provide concrete estimates on it value.
+
+A very simple estimate, based on $x_*$ lying in the interval $[-a,0]$ gives
+\begin{equation}
+(1-a)^{n-m-1} \leq \frac{R_m(-a)}{\binom{n}{m+1}(-a)^{m+1}} \leq 1,
+\end{equation}
+which in turn leads to the following bounds on $\Phi_+(m; n, a)$:
+\begin{align}
+	\hspace{-2cm}2\Phi_+(m; n, a) \leq\ &\Phi(m; n, a) + (1-a)^n - \frac{(-a)^{m+1}}{m!} \times \nonumber\\
+	 &\binom{n}{m+1} (1-a)^{n-m-1} \text{ and} \\
+	2\Phi_+(m; n, a) \geq\ &\Phi(m; n, a) + (1-a)^n - \frac{(-a)^{m+1}}{m!} \binom{n}{m+1} .
+\end{align}
+
+\subsection{Lorenz curve coordinates in the unital fragment}\label{app:lcsu_coord}
+The Wigner distribution of the $n$--copy qutrit maximally mixed state $\left(\id/3\right)^{\otimes n}$ is the uniform probability distribution over the phase space, consisting of $9^n$ components equal to $9^{-n}$.
+The Wigner distribution of the 1-copy $\epsilon$--noisy Strange state $\rho_{\rm{S}}(\epsilon)$ in the unital fragment consists of some permutation of a single negative component
+\begin{equation}
+	- v(\epsilon) \coloneqq - \left( \frac{1}{3} -\frac{4}{9}\epsilon \right),
+\end{equation} 
+and $8$ positive components
+\begin{equation}
+	u(\epsilon) \coloneqq \frac{1}{6} -\frac{1}{18}\epsilon.
+\end{equation}
+where in the unital fragment we need the condition $0 \leq \epsilon < 3/4$, so that the state contains some Wigner negativity ($-v < 0$).
+It is also clear that $v \geq u$ in the interval $0 \leq \epsilon \leq 3/7$, while $u > v$ in the interval $3/7 < \epsilon < 3/4$.
+
+The Wigner distribution of the $n$--copy $\epsilon$--noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ in the unital fragment is given by the convolution $\W{\rho_{\rm{S}}(\epsilon)^{\otimes n}} = W_{\rho_{\rm{S}}(\epsilon)}^{\otimes n}$.
+In general, $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ contains $n + 1$ distinct components, labelled $0,\dots, n$.
+We present the distinct Wigner components of $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ along with their multiplicites in~\cref{tab:lcsu}.
+Note that LHS (RHS) refers to elbow coordinates $i$ on the left of and including (right of) the Lorenz curve maximum, stated precisely as
+\begin{align}
+&\text{LHS: } 0 \leq i \leq \left\lfloor \frac{n}{2} \right\rfloor \text{ and} \\
+&\text{RHS: } \left\lfloor \frac{n}{2} \right\rfloor +1 \leq i \leq n.
+\end{align}
+\begin{table}[h]
+  \def\arraystretch{1.5}
+  \centering
+  \begin{tabular}{c|c|c|r|r}
+    \multicolumn{3}{c|}{Case} & \multicolumn{1}{c}{$m_{i}(n, \epsilon)$} & \multicolumn{1}{|c}{$w_{i}(n, \epsilon)$} \\[0.5ex]\hline
+    \multirow{4}{*}{\raisebox{-4ex}{\rotatebox[origin=c]{90}{$0\leq \epsilon < \frac{3}{7}$}}} & \hspace{0.8ex}\multirow{2}{*}{\raisebox{-1ex}{\rotatebox[origin=c]{90}{$n$ even}}}\hspace{0.8ex} & LHS & $8^{2i}\binom{n}{2i}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2i}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{n-2i}$ \\
+    & & RHS & $8^{n-2i}\binom{n}{2i}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{n-2i}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2i}$ \\ \cline{2-5}
+    & \multirow{2}{*}{\raisebox{-2ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $8^{2i+1}\binom{n}{2i+1}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2i+1}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{n-2i-1}$ \\
+    & & RHS & $8^{n-2i-1}\binom{n}{2i+1}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{n-2i-1}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2i+1}$ \\ \hline
+    \multirow{4}{*}{\raisebox{-4ex}{\rotatebox[origin=c]{90}{$\frac{3}{7}\leq \epsilon < \frac{3}{4}$}}} & \multirow{2}{*}{\raisebox{-1ex}{\rotatebox[origin=c]{90}{$n$ even}}} & LHS & $8^{n-2i}\binom{n}{2i}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{n-2i}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2i}$ \\
+    & & RHS & $8^{2i}\binom{n}{2i}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2i}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{n-2i}$ \\ \cline{2-5}
+    & \multirow{2}{*}{\raisebox{-2ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $8^{n-2i}\binom{n}{2i}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{n-2i}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2i}$ \\
+    & & RHS & $8^{2i}\binom{n}{2i}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2i}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{n-2i}$ \\ \hline
+  \end{tabular}
+  \caption{Wigner components $w_{i}(n, \epsilon)$ of $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ along with their multiplicities $m_{i}(n, \epsilon)$, with $0 \leq i \leq n$.
+  The expressions change depending on the noise level $\epsilon$, the parity of the number of copies $n$ and whether the index $i$ is lower or higher than the index of the Lorenz curve maximum (LHS vs RHS).
+  Multiplication $2i$ is considered modulo $(n+1)$.}
+  \label{tab:lcsu}
+\end{table}
+
+Every Lorenz curve in the unital fragment contains $n$ elbows, which, along with the boundary points $(x_{-1}, L_{-1}) = (0,0)$ and $(x_{n}, L_{n}) = (1,1)$, are labelled by 
+\begin{equation*}
+\{(x_{i}, L_{i})\}_{i=-1,0,\dots,n}.
+\end{equation*}
+The maximum is the $\lfloor n/2 \rfloor$-th elbow and its coordinates are calculated by collecting all the positive Wigner components,
+\begin{align}
+	x_{\lfloor n/2 \rfloor} &= \frac{1}{2}\left(1 + \left(\frac{7}{9}\right)^n\right), \\
+	L_{\lfloor n/2 \rfloor} &= \frac{1}{2}\left (1 + \left(\frac{15 - 8\epsilon}{9}\right)^n \right).
+\end{align}
+%\sum_{j: even}^n a^j \binom{n}{j} = \frac{1}{2} [ (1+a)^n + (1-a)^n ]
+
+Expressions for all the elbow coordinates follow from summing up the Wigner components in decreasing order.
+In~\cref{tab:lcsu_coord_elb_app}, we present the elbow coordinates of the $n$-copy, $\epsilon$--noisy Strange state Lorenz curve in the unital fragment for any combination of parameters $n, \epsilon$.
+\begin{table}[h]
+  \def\arraystretch{1.5}
+  \centering
+  \begin{tabular}{c|c|c|r|r}
+\multicolumn{3}{c|}{\multirow{2}{*}{Case}} & \multicolumn{1}{c|}{$x_{i}$} & \multicolumn{1}{c}{$L_{i}$} \\
+    \multicolumn{3}{c|}{} & \multicolumn{1}{c|}{$x_{i} - x_{\lfloor n/2 \rfloor}$} & \multicolumn{1}{c}{$L_{i} - L_{\lfloor n/2 \rfloor}$} \\[0.5ex]\hline 
+    \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$0\leq \epsilon < \frac{3}{7}$}}} & \hspace{0.8ex}\multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ even}}}\hspace{0.8ex} & LHS & $\Phi_+\left(2i;n,\frac{8}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\
+    & & RHS & $\Phi_-\left(2i;n,\frac{1}{9}\right)$ & $- \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-\left(2i;n,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
+    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $\Phi_-\left(2i;n,\frac{8}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_-\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\
+    & & RHS & $\Phi_-\left(2i;n,\frac{1}{9}\right)$ & $- \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-\left(2i;n,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
+    \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$\frac{3}{7}\leq \epsilon < \frac{3}{4}$}}} & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ even}}} & LHS & $\Phi_+\left(2i;n,\frac{1}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+\left(2i;n,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\
+    & & RHS & $\Phi_-\left(2i;n,\frac{8}{9}\right)$ & $- \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
+    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $\Phi_+\left(2i;n,\frac{1}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+\left(2i;n,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\
+    & & RHS & $\Phi_+\left(2i;n,\frac{8}{9}\right)$ & $- \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_+\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
+  \end{tabular}
+  \caption{Lorenz curve elbow coordinates in the unital fragment.
+  The coordinate expressions depend on the noise level $\epsilon$, the parity of the number of copies $n$ and the location of the elbow relative to the maximum (LHS vs RHS).
+  Multiplication $2i$ is considered modulo $(n+1)$.
+  For completeness, note that $(x_{-1}, L_{-1}) \coloneqq (0,0)$ is not included in the table.
+  }
+  \label{tab:lcsu_coord_elb_app}
+\end{table}
+
+We can get explicit expressions for all $9^{n}$ points of the Lorenz curve $\lc{\rho_{\rm{S}}(\epsilon)^{\otimes n}}{(\id/3)^{\otimes n}}$, in terms of the elbow coordinates:
+\begin{align}
+    x_{ij} &= \left( 1-\frac{j}{m_{i}} \right) x_{i-1} + \frac{j}{m_{i}} x_{i}, \label{eq:x}\\
+    L_{ij} &= \left( 1-\frac{j}{m_{i}} \right) L_{i-1} + \frac{j}{m_{i}} L_{i} \label{eq:l}
+\end{align}
+for $j = 1,\dots,m_{i}$ and $i=0,\dots,n$, where multiplicities $m_i = m_i(n, \epsilon)$ are given in~\cref{tab:lcsu}.
+
+Consider the state 
+\begin{equation*}
+\rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n-n')},
+\end{equation*}
+where tensoring with the maximally mixed state keeps the Lorenz curve unchanged, but increases the resolution of (the uniformly distributed) points.
+The new point coordinates are given by:
+\begin{align}
+    &x_{ijk} = \left( 1-p_{ijk}\right) x_{i-1} + p_{ijk} x_{i} \label{eq:lcsu_xcoord}\\
+    &L_{ijk} = \left( 1-p_{ijk} \right) L_{i-1} + p_{ijk} L_{i}, \label{eq:lcsu_lcoord}\\
+    &\text{where } p_{ijk} = \frac{k + (j-1)9^{n-n'}}{9^{n-n'} m_{i}} \nonumber\\
+    &\text{for } i=0,\dots,n',\ j = 1,\dots,m_{i}(n', \epsilon') \text{ and } k = 1,\dots,9^{n-n'}. \nonumber
+\end{align}
+
+We can unify the indices, by introducing a single index
+\begin{equation}
+    I(i,j,k) \coloneqq k + \left[ (j-1) + \sum_{\ell=0}^{i-1} m_{\ell}(n', \epsilon') \right]9^{n-n'},
+\end{equation}
+so that $I=1,2,\dots, 9^{n}$.
+The elbow coordinates correspond to 
+\begin{equation}
+	I(i, m_{i}(n', \epsilon'), 9^{n-n'}) = \sum_{\ell=0}^{i} m_{\ell}(n', \epsilon'),\ i= 0,\dots,n'.
+\end{equation}
+The index function $I$ is bijective, i.e.
+\begin{equation}
+	(i,j,k) = (i',j',k') \text{ iff } I(i,j,k) = I(i',j',k').
+\end{equation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Technical details for the derivation of distillation bounds from Lorenz curves}
+\label{app:lcst_technical}
+
+\subsection{First and last elbow constraints}
+\label{app:elb_constraints}
+Here we prove two simple majorization constraints, one arising by considering only the ascending part of the Lorenz curves between the origin $(0,0)$ and the first elbow and the other by considering only the descending part of the curves between the last elbow and the endpoint $(1,1)$.
+\begin{proposition}\label{prop:first_elb}
+	Consider a magic state process $\rho \longrightarrow \tau$ with input and output Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in $\R_\sigma$ and denote by $X_0, X'_0$ the first elbow locations of the input and output curves respectively.
+
+	Then, given any coordinates $(x_0, L_0)$ and $(x'_0, L'_0)$ on the input and output Lorenz curves, where $x_0 \leq X_0$ and $x'_0 \leq X'_0$, the process is possible in $\R_\sigma$ only if
+\begin{equation}\label{eq:first_elb_bound1}
+	\frac{L_0}{x_0} \geq \frac{L_0'}{x_0'}.
+\end{equation}
+\end{proposition}
+\begin{proof}
+Since both pairs of coordinates are located between $(0,0)$ and the first elbow of their respective curves, we can derive the bound via a simple interpolation on the line segment connecting the origin and the appropriate first elbow.
+
+First assume that $x_0 < x'_0$ and consider the Lorenz curve constraint at $x = x_0$,
+\begin{equation}
+	\lc{\rho}{\sigma}(x_0) \geq \lc{\tau}{\sigma}(x_0).
+\end{equation}
+We can find the output state Lorenz curve coordinate $L'_\star$ at location $x = x_0$ by interpolating between the origin and the output state's first elbow, 
+\begin{equation}
+	L'_\star = \frac{x_0}{x'_0}L'_0.
+\end{equation}
+The process is then possible only if $L_0 \geq L_\star'$ which is a rearrangement of~\cref{eq:first_elb_bound1}.
+
+If instead, $x_0 \geq x'_0$, consider the Lorenz curve constraint at $x = x'_0$,
+\begin{equation}
+	\lc{\rho}{\sigma}(x'_0) \geq \lc{\tau}{\sigma}(x'_0).
+\end{equation}
+We now need to find the input state Lorenz curve coordinate $L_\star$ at location $x = x'_0$ by interpolating between the origin and the input state's first elbow, 
+\begin{equation}
+	L_\star = \frac{x'_0}{x_0}L_0.
+\end{equation}
+The process is then possible only if $L_\star \geq L'_0$ which is again a rearrangement of~\cref{eq:first_elb_bound1}.
+\end{proof}
+
+\begin{proposition}\label{prop:last_elb}
+	Consider a magic state process $\rho \longrightarrow \tau$ with input and output Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in $\R_\sigma$ and denote by $X_E, X'_E$ the last elbow locations of the input and output curves respectively.
+
+	Then, given any coordinates $(x_E, L_E)$ and $(x'_E, L'_E)$ on the input and output Lorenz curves, where $x_E \geq X_E$ and $x'_E \geq X'_E$, the process is possible in $\R_\sigma$ only if
+\begin{equation}\label{eq:last_elb_bound1}
+	\frac{L_E - 1}{1-x_E} \geq \frac{L'_E - 1}{1-x_E'}.
+\end{equation}
+\end{proposition}
+\begin{proof}
+Since both pairs of coordinates are located between the last elbow of their respective curves and $(1,1)$, we can derive the bound via a simple interpolation on the line segment connecting the endpoint and the appropriate last elbow.
+
+First assume that $x_E > x'_E$ and consider the Lorenz curve constraint at $x = x_E$,
+\begin{equation}
+	\lc{\rho}{\sigma}(x_E) \geq \lc{\tau}{\sigma}(x_E).
+\end{equation} 
+We can find the output state Lorenz curve coordinate $L'_\star$ at location $x = x_E$ by interpolating between the endpoint $(1,1)$ and the output state's last elbow, 
+\begin{equation}
+	L'_\star = 1 + \frac{1-x_E}{1-x'_E} (L'_E - 1)
+\end{equation}
+The process is then possible only if $L_E \geq L_\star'$ which is a rearrangement of~\cref{eq:last_elb_bound1}.
+
+If instead, $x_E \leq x'_E$, consider the Lorenz curve constraint at $x = x'_E$,
+\begin{equation}
+	\lc{\rho}{\sigma}(x'_E) \geq \lc{\tau}{\sigma}(x'_E).
+\end{equation} 
+We now need to find the input state Lorenz curve coordinate $L_\star$ at location $x = x'_E$ by interpolating between the endpoint $(1,1)$ and the input state's last elbow, 
+\begin{equation}
+	L_\star = 1 + \frac{1-x'_E}{1-x_E} (L_E - 1).
+\end{equation}
+The process is then possible only if $L_\star \geq L'_E$ which is again a rearrangement of~\cref{eq:last_elb_bound1}.
+\end{proof}
+
+\subsection{Component-multiplicity pairs}
+\label{app:cmpairs}
+
+\begin{lemma}Let $\tau_A, \tau_B$ be full rank stabilizer states on systems $A$ and $B$, and let $\rho_A, \rho_B$ be arbitrary states on $A,B$. Then the rescaled quasi-distribution obeys
+\begin{equation}
+W_{\rho_A \otimes \rho_B | \tau_A \otimes \tau_B}(\bmx_A \oplus \bmx_B) =W_{\rho_A | \tau_A}(\x_A) W_{\rho_B | \tau_B}(\x_B)
+\end{equation}
+\end{lemma}
+\begin{proof} This follows from the definitions. 
+\begin{align}
+W_{\rho_A \otimes \rho_B | \tau_A \otimes \tau_B}(\bmx_A \oplus \bmx_B) &= \frac{W_{\rho_A \otimes \rho_B} (\x_A \oplus \x_B)}{W_{\tau_A \otimes \tau_B} (\x_A \oplus \x_B)}\nonumber \\
+ &= \frac{W_{\rho_A } (\x_A )W_{\rho_B } (\x_B )}{W_{\tau_A } (\x_A )W_{\tau_B } (\x_B )}\nonumber \\
+  &= W_{\rho_A | \tau_A}(\x_A) W_{\rho_B | \tau_B}(\x_B)\nonumber,
+\end{align}
+as claimed.
+\end{proof}
+
+In general, a $1$--copy $d$--dimensional state $\rho$ is described exactly by its $d^2$--dimensional Wigner distribution $\W{\rho}$. 
+The distribution $\W{\rho}$ is defined on the phase space, but it can be convenient to re-express this using vector notation. 
+In particular, we introduce a component vector $\bmw(\rho) = (w_i)_{i=1,\dots,D}$ and a multiplicity vector $\bmm(\rho) = (m_i)_{i=1,\dots,D}$, where $D \leq d^2$ which together form a set of component-multiplicity pairs $\{(w_i, m_i)\}_{i=1,\dots,D}$.
+\begin{definition}
+	Consider a distribution $W$ and a positive integer $D \leq {\rm{dim}}\hspace{1pt}W$. 
+	We call the set of ordered pairs $\{(w_i, m_i)\}_{i=1,\dots,D}$ a \emph{complete set of component-multiplicity pairs}, if $W$ contains $m_i$ components $w_i$ and $\sum_{i=0}^D m_i = d^2$.
+\end{definition}
+Therefore, such a set describes each component of $\W{\rho}$ exactly once.
+As an example, two complete sets of pairs for the Strange state are $\{( -1/3, 1), ( 1/6, 8)\}$ and $\{(-1/3, 1), (1/6, 2), (1/6, 3), (1/6, 3)\}$.
+The latter corresponds to the phase space split in~\cref{fig:pd_split}
+
+Consider two states $\rho_A, \rho_B$ with Wigner distributions $\W{\rho_A}, \W{\rho_B}$ described respectively by complete sets of component-multiplicity pairs 
+\begin{equation}
+	\{(w_i, m_i)\}_{i=1,\dots,D_A} \text{ and } \{(w_j', m_j')\}_{j=0,\dots,D_B}.
+\end{equation}
+The multiplicative property of the Wigner distribution over a composite phase space $\cal{P}_{d_A} \times \cal{P}_{d_B}$ shown in~\cref{thm:wstate},
+\begin{equation}
+	\W[\bmx_A \oplus \bmx_B]{\rho_A \otimes \rho_B} = \W[\bmx_A]{\rho_A}\W[\bmx_B]{\rho_B},
+\end{equation}
+implies that the distribution $\W{\rho_A \otimes \rho_B}$ is $d_A^2 d_B^2$--dimensional and contains components of the form $w_i w_j'$. 
+Therefore, the set $\{(w_i w_j', m_i m_j')\}$ with $i=1,\dots,D_A$ and $j=1,\dots,D_B$ is a complete set of component-multiplicity pairs for the distribution of the composite system $\W{\rho_A \otimes \rho_B}$.
+This is true because all components are of the form $w_i w_j'$ and 
+\begin{equation*}
+	\sum_{i=1}^{D_A}\sum_{j=1}^{D_B} m_i m_j' = \sum_{i=1}^{D_A} m_i \sum_{j=1}^{D_B} m_j' = d_A^2 d_B^2.
+\end{equation*}
+
+Note that the rescaled distribution is also multiplicative, so a complete set of component-multiplicity pairs can be obtained for this distribution in the same fashion as for usual Wigner distributions.
+
+Given a state $\rho$ and a complete set of component-multiplicity pairs describing its Wigner distribution $\W{\rho}$, we now provide a method of computing the components (and multiplicities) of the $n$--copy distribution $\W{\rho}^{\otimes n}$.
+\begin{lemma}\label{lem:ncopycomponents}
+	Let $W$ be a distribution defined by a complete set of component-multiplicity pairs $\{(w_i, m_i)\}_{i=1,\dots,D}$ with $D \leq {\rm{dim}}\hspace{1pt}W$ and consider the distribution $W^{\otimes n}$ obtained by taking the $n$-fold (Kronecker) product $W \otimes \dots \otimes W$ between $n$ copies of $W$.
+
+	Denote by $C_D^n \coloneqq \{\bmk\}$ the set of all vectors $\bmk \coloneqq (k_1, \dots, k_D)$ with non-negative integer components that sum to $n$, i.e.
+	\begin{equation*}
+	0 \leq k_1, \dots, k_D \leq n \text{ and } k_1 + \dots + k_D = n.
+	\end{equation*}
+
+	Then, $W^{\otimes n}$ admits a complete set of component-multiplicity pairs $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$, where
+\begin{align}
+	M_{\bmk} &= \frac{n!}{k_1!\dots k_D!} \prod\limits_{i=1}^D {m_i}^{k_i}, \label{eq:M}\\
+	W_{\bmk} &= \prod\limits_{i=1}^D {w_i}^{k_i}. \label{eq:W}
+\end{align}
+\end{lemma}
+\begin{proof}
+	We proceed by induction.
+
+	Assume $n = 1$.
+	Let $\bmk_i$ be the vector with its $i$-th component equal to 1 and 0's elsewhere.
+	The set $C_D^1$ consists of all vectors of this form, i.e. 
+\begin{equation*}
+	C_D^1 = \{ \bmk_i \}_{i=1,\dots,D}
+\end{equation*}
+	It is also true by direct calculation that
+\begin{equation*}
+	\left( W_{\bmk_i}, M_{\bmk_i} \right) = (w_i, m_i).
+\end{equation*}
+Therefore, $\{ (W_{\bmk}, M_{\bmk}) \}_{\bmk \in C_D^1}$ is a complete set of component-multiplicity pairs for $W$.
+
+	Assume that $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$ as given in~\cref{eq:M,eq:W} is a complete set of component-multiplicity pairs for the $n$--copy distribution $W^{\otimes n}$.
+	By construction, the distribution $W^{\otimes (n+1)} = W^{\otimes n} \otimes W$ is multiplicative, so it admits the complete set of component multiplicity pairs
+\begin{equation}
+	\{(W_{\bmk} w_i, M_{\bmk} m_i)\},\ \bmk \in C_D^n \text{ and } i=1,\dots,D.
+\end{equation}
+
+	Consider the component sum of the distribution $W^{\otimes (n+1)}$,
+\begin{align*}
+	&\sum_{\bmk \in C_D^n}\sum_{i=1}^D M_{\bmk} m_i W_{\bmk} w_i = \sum_{\bmk \in C_D^n} M_{\bmk}W_{\bmk} \sum_{i=1}^D m_i w_i =\\
+	&\sum_{\bmk \in C_D^n} \frac{n!}{k_1!\dots k_D!} \prod\limits_{i=1}^D {m_i}^{k_i}{w_i}^{k_i} \sum_{i=1}^D m_i w_i =\\
+	&\left( \sum_{i=1}^D m_i w_i \right)^n \left( \sum_{i=1}^D m_i w_i \right) = \left( \sum_{i=1}^D m_i w_i \right)^{n+1} =\\
+	&\sum_{\bmq \in C_D^{n+1}} M_{\bmq}W_{\bmq},
+\end{align*}
+where in the last expression, vectors $\bmq = (q_1, \dots, q_D)$ have non-negative integer components that sum to $(n+1)$ and 
+\begin{align*}
+	M_{\bmq} &= \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i},\\
+	W_{\bmq} &= \prod\limits_{i=1}^D {w_i}^{q_i}.
+\end{align*}
+We have used the multinomial theorem to proceed between lines 2-3 and lines 3-4 of the derivation.
+
+We have achieved a regrouping of the distribution components.
+Every component $W_{\bmq}$ is of the form $W_{\bmk} w_i$ with $q_i = k_i + 1$ and $q_j = k_j$ for $j\neq i$ and 
+\begin{align*}
+	\sum_{\bmq \in C_D^{n+1}}  \hspace{-6pt} M_{\bmq} =  \hspace{-10pt} \sum_{\bmq \in C_D^{n+1}} \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i} = 
+	\left( \sum_{i=1}^D m_i \right)^{n+1} \hspace{-10pt} = d^{n+1},
+\end{align*}
+which is the dimension of $W^{\otimes (n+1)}$.
+
+Therefore, $\{ (W_{\bmq}, M_{\bmq}) \}_{\bmq \in C_D^{n+1}}$ is a complete set of component-multiplicity pairs for $W^{\otimes n}$, completing the proof.
+\end{proof}
+
+%Index vector $\bmk$ has $D-1$ independent components and in the proof of our main theorem in~\cref{sec:stab} we have $D=4$, so we simplify the notation by writing the component and multiplicity vectors of the $n$--copy state distributions as $m_{ijk}, w(\rho_{\rm{S}})_{ijk}, w(\sigma)_{ijk}$ and $w(\rho_{\rm{S}}|\sigma)_{ijk}$, where $i,j,k$ are the 3 independent index components.
+
+\newpage
+\subsection{Free energy dependent magic distillation bounds}\label{free-energy-bound-proof}
+\label{app:main_proof}
+Here we prove~\cref{thm:free-energy}, which bounds magic distillation rates in terms of free energies.
+
+\begin{theorem}
+	Consider a magic distillation protocol on qutrits that transforms $n$ copies of an $\epsilon$--noisy Strange state into $m$ copies of an $\epsilon'$--noisy Strange state, with depolarising errors $\epsilon' \leq \epsilon \leq 3/7$.
+We also allow pre/post-processing by local Clifford unitaries.
+
+	Let $T =(k\beta)^{-1}$ be any finite temperature for the physical system and let $H= \sum_{k \in \mathbb{Z}_3} E_k |E_k\>\<E_k|$ be the Hamiltonian of each qutrit subsystem in its eigen-decomposition.
+Assume that in the thermodynamic limit the protocol applied to $\tau^{\otimes n}$, gives $\tau^{\otimes n} \longrightarrow \tau^{\prime \otimes m}$ for $n,m \gg 1$, and write the state $\tau'$ as $\tau' = e^{-\beta H'}/\Z'$ for some Hermitian $H'$.
+
+Then the magic distillation rate $R = m/n$ for the protocol is bounded by the expression
+\begin{equation}\label{eq:rate_bounds_proof}
+	R \leq \dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (\phi - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (\phi' - F')},
+\end{equation}
+where $F$ is the free energy of $\tau$,  and 
+\begin{equation}
+	\phi = -\beta^{-1} \log \zeta
+\end{equation}
+with $\zeta$ given by the expressions
+\begin{align}
+	\zeta &= \sum_{k\in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}, \nonumber\\
+	\alpha_k &= \sum_{r \in \mathbb{Z}_3} \<E_k| A_{\x_\star} |E_k\>,
+\end{align}
+with $\x_\star = \mbox{argmin}[W_\tau( \x )]$. The primed variables are defined similarly for the output system.
+\end{theorem}
+
+\begin{proof}	
+For the sake of clarity, we write $\rho_n \coloneqq \rho_S(\epsilon)^{\otimes n}$, $\rho'_m \coloneqq \rho_S(\epsilon')^{\otimes m}$, $\tau_n \coloneqq \tau^{\otimes m}$ and $\tau'_m \coloneqq \tau'^{\otimes m}$.
+We also assume, without loss of generality on the asymptotic distillation rate, that $n$ and $m$ are both even.
+
+To establish the distillation bound we consider the distillation protocol that gives $\E( \rho_n) = \rho'_m$ for the magic states. 
+We then consider that the protocol transforms the reference equilibrium state as $\E( \tau_n) = \tau'_m$.
+Since we have a finite temperature we have that $\tau$ and $\tau'$ are full rank stabilizer states and have a strictly positive Wigner distribution.
+The input and output magic states generally have quasi-probability Wigner distributions.
+For any such protocol we therefore have that
+\begin{equation}
+	( W_{\rho_n}(\bmx), W_{\tau_n}(\bmx) ) \succ ( W_{\rho'_m}(\bmx), W_{\tau'_m}(\bmx) ),
+\end{equation}
+or, equivalently, in terms of the relevant Lorenz curves,
+\begin{equation}
+	L_{\rho_n |\tau_n}(x) \ge L_{\rho'_m |\tau'_m}(x) \mbox{ for all } x \in [0,1].
+\end{equation}
+
+We now consider the rescaled Wigner distribution $W_{\rho | \tau}(\x) \coloneqq W_\rho(\x)/W_\tau(\x)$, which is well-defined since $\tau$ is full-rank. 
+Due to the multiplicative property of the Wigner distribution, the rescaled distribution is also multiplicative in the sense that
+\begin{equation}
+	W_{\rho \otimes \rho' | \tau \otimes \tau'} (\x_1 \oplus \x_2) = W_{\rho | \tau}(\x_1)W_{\rho' | \tau'}(\x_2),
+\end{equation}
+for any states $\rho, \rho'$ and any full-rank stabilizer states $\tau, \tau'$.
+Therefore we have that
+\begin{align}
+	W_{\rho_n |\tau_n} (\x) &= \prod_{i=1}^n W_{\rho|\tau}(\x_i)\\
+	W_{\rho_n } (\x) &= \prod_{i=1}^n W_\rho(\x_i)
+\end{align}
+where $\x = \oplus_{i=1}^n \x_i \in \mathbb{Z}_3^n$ is the phase space point for the full system in terms of those of the individual subsystems.
+
+The points defining the Lorenz curve $L_{\rho_n |\tau_n}(x)$ are obtained from sorting the components of $W_{\rho_n |\tau_n}(\x)$ in non-increasing order and then computing the partial sums of $W_{\rho_n |\tau_n}(\pi(\x))$ where $\pi$ is the permutation that realises the sorting.
+However, similarly to the unital fragment analysis, we use the necessary constraint obtained by considering the line segment connecting the origin to the first elbow of both Lorenz curves.
+
+The Wigner distribution of a single noisy Strange state consists of 1 negative component $W_{\rho}(0,0) = -v(\epsilon)$ and 8 positive components $W_{\rho}(\bmx) = u(\epsilon)$ for $\bmx \neq \bmo$.
+The Wigner distribution of the full-rank, stabilizer equilibrium state $\tau$ is $W_{\tau}(\bmx) > 0$ for all $\bmx \in \mathbb{Z}_3^2$.
+
+Assume that the smallest component of the distribution $W_\tau(\x)$ is at $\x=\x_\star$.
+Since the magic content of the state is unchanged under a Clifford unitary $C$, we can instead consider the state
+\begin{equation}
+\rho_S(\epsilon) \rightarrow C \rho_S(\epsilon) C^\dagger = D_{x_\star} \rho_S(\epsilon) D_{x_\star}^\dagger,
+\end{equation}
+which has its single negative Wigner component $-v(\epsilon)$ at the point $\x_\star$.
+
+The rescaled distribution components for this transformed state are given by
+\begin{equation}
+	W_{\rho_n|\tau_n} = \left(\frac{-v}{W_{\tau}(\x_\star)}\right)^{i_{\x_\star}} \prod_{\bmx \neq \x_\star} \left(\frac{u}{W_{\tau}(\bmx)}\right)^{i_{\bmx}},
+\end{equation}
+where the integer indices obey the following conditions:
+\begin{align}
+&0 \leq i_{\bmx} \leq n \mbox{ for all } \bmx \in \mathbb{Z}_3^2, \nonumber \\
+&\sum_{\bmx \in \mathbb{Z}_3^2} i_{\bmx} = n.
+\end{align}
+We now compute the largest rescaled component.
+Firstly, note that $n$ is even, so we require that $i_{\x_\star} \in \{0,2,\dots,n\}$ for the component to be positive.
+Then, we have that $v \geq u$ because $\epsilon \leq 3/7$, and we have already ensured that $W_{\tau}(\x_\star) \leq W_{\tau}(\bmx)$ for all $\bmx \in \mathbb{Z}_3^2$.
+Therefore, the largest rescaled component occurs when $i_{\x_{\star}} = n$ and $i_{\x} = 0$ for $\x \neq \x_\star$ and is equal to $(v/W_{\tau}(\x_\star))^n$.
+Accordingly, the coordinates of the first Lorenz curve point after the origin are given by
+\begin{equation}
+	(x_0, L_0) = ((W_{\tau}(\x_\star))^n, v^n)
+\end{equation}
+
+Given a Hamiltonian decomposition,
+\begin{equation}
+	H = \sum_{k \in \mathbb{Z}_3} E_k\ketbra{E_k}{E_k},
+\end{equation}
+we can re-express the coordinate location, by writing
+\begin{align}
+	W_{\tau}(\x_\star) &= \frac{1}{3\Z}\tr\left[ A_{\x_\star}e^{-\beta H} \right] \nonumber\\
+	&= \frac{e^{\beta F}}{3} \tr\left[ A_{\x_\star}\sum_{k \in \mathbb{Z}_3} e^{-\beta E_k}\ketbra{E_k}{E_k} \right] \\
+	&= \frac{e^{\beta F}}{3} \sum_{r \in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}
+	= \frac{e^{\beta F}}{3} \zeta \\
+	&= \frac{e^{\beta (F - \phi)}}{3},
+\end{align}
+where we define
+\begin{align}
+\alpha_k := \<E_k |A_{\x_\star} |E_k\> \\
+\zeta :=  \sum_{r \in \mathbb{Z}_3} \alpha_k e^{-\beta E_k},
+\end{align}
+and the `magic free energy' term $\phi := -\beta^{-1} \log \zeta$.
+Therefore, the coordinates can be expressed as
+\begin{equation}
+	(x_0, L_0) = \left( \frac{e^{n\beta (F - \phi)}}{3^n}, v(\epsilon)^n \right).
+\end{equation}
+The output states obey the same conditions and so we can derive the first point coordinates of the output Lorenz curve as
+\begin{equation}
+	(x'_0, L'_0) = \left( \frac{e^{m\beta (F' - \phi')}}{3^m}, v(\epsilon')^m \right).
+\end{equation}
+
+If the largest rescaled component of a state is distinct with no multiplicities, then these coordinates correspond to the first elbow of the corresponding Lorenz curve, whereas if it appears multiple times, then the coordinates derived correspond to a point on the interior of the line segment connecting the origin to the first elbow.
+In both cases, the distillation bound remains the same, as is clear by its derivation in~\cref{app:elb_constraints}, and it is given by $L_0 / x_0 \geq L'_0 / x'_0$, which can be directly rearranged into the stated bound of the theorem \ddd{[Expand this last bit and show it explicitly -- don't skip lines in a proof, even if they seem obvious.]}.
+\end{proof}
+
+The following lemma shows that if the energy eigenbasis is a stabilizer basis then things simplify more. \ddd{[To be checked]}
+\begin{lemma} If the Hamiltonian $H$ in the previous theorem has a stabilizer eigenbasis, then $\phi = E_{k_s} +kT\log 3$ for some $k_s \in \mathbb{Z}_3$.
+\end{lemma}
+\begin{proof}We first expand $\alpha_k$ as
+\begin{equation}
+\alpha_k = \<E_k | D_{\x_\star} A_{\mathbf{0}} D_{\x_\star}^\dagger |E_k\>.
+\end{equation}
+Since $\{|E_k\>\}$ forms an orthonormal basis, then so too does $\{|\psi_k\>:=D_{\x_\star}^\dagger|E_k\>\}$.
+This implies that in the Wigner representation the distributions $\{W_{\psi_k}(\x)\}$ have orthogonal supports and only one of them, $k=k_s$ say, has $\x=\mathbf{0}$ in its support.
+Therefore only the coefficient $\alpha_{k_s}$ is non-zero and so
+\begin{align}
+\phi &= -\beta^{-1}\log (\sum_k \alpha_k e^{-\beta E_k}) \nonumber \\
+&=E_{k_s} -kT \log W_{\psi_{k_s}}(\mathbf{0}) \nonumber \\
+&=E_{k_s} +kT \log 3,
+\end{align}
+where we use that $\psi_{k}$ are pure stabilizer states and so their non-zero Wigner components are $1/3$.
+\end{proof}
+
+\subsection{Deriving distillation bounds from the last elbow}
+\label{sec:last_elb}
+
+Using a similar analysis, we can also derive upper bounds from comparison of the last point coordinates of the Lorenz curve, which now corresponds to the smallest rescaled component.
+
+To this end, assume that the largest component of the equilibrium state distribution is $W_{\tau}(i,j)$.
+We now perform the Clifford operation
+\begin{equation}
+	\tau \longrightarrow X^{1-i}Z^{-j}\ \tau\ Z^{j}X^{i-1},
+\end{equation}
+which permutes the largest component such that $W_{\tau}(i,j) \longrightarrow W_{\tau}(1,0)$.
+Since we have that $u \leq v$ because $\epsilon \leq 3/7$, and we have already ensured that $W_{\tau}(1,0) \geq W_{\tau}(\bmx)$ for all $\bmx \in \mathbb{Z}_3^2$.
+Therefore, the largest rescaled component occurs when $i_{(1,0)} = n$ and $i_{\bmx} = 0$ for $\bmx \neq \bmo$ and is equal to $(v/W_{\tau}(1,0))^n$.
+Accordingly, the coordinates of the first Lorenz curve point after the origin are given by $(x_E, L_E) = ((W_{\tau}(1,0))^n, u(\epsilon)^n)$ for the input state and $(x'_E, L'_E) = ((W_{\tau'}(1,0))^m, u(\epsilon')^m)$ for the output state.
+
+We now redefine the quantities $\alpha_k$, so that again $\phi = -\beta^{-1} \log \zeta$, where $\zeta= \sum_{k\in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}$ and $\alpha_k$ now given by
+\begin{align}
+	\alpha_k = \sum_{r \in \mathbb{Z}_3} \braket{E_k}{1-r}\braket{1+r}{E_k}.
+\end{align}
+This allows us to rewrite $W_{\tau}(1,0) = {e^{\beta (F - \phi)}}/{3}$ and by using the last elbow constraint 
+\begin{equation*}
+	\frac{L_E - 1}{1-x_E} \geq \frac{L'_E - 1}{1-x_E'},
+\end{equation*}
+derived in~\cref{app:elb_constraints}, we can get a new bound expression.
+
+We note that it is also possible to perform a different Clifford transformation and get a different location $(W_{\tau}(\bmx))^n$, with $\bmx \neq \bmo$, since components $(W_{\rho}(\bmx))^n = u$ are all the same as long as $\bmx \neq \bmo$.
+The effect of this is to alter the expressions for the quantities $\alpha_k$, but not the resulting bound expression.
+
+\nick{This section on the last elbow bound is a little weak?}
+
+\subsection{OLD VERSION OF MAIN THEOREM}
+
+\ddd{[Do we need to keep any of the details in this section? If not then delete it entirely.]}
+\nick{This proof offers: 1.
+the exact derivation of our main contour plot, justifying the quantities $\epsilon_\star$ and $\beta_\star$ 2.
+a method for lifting the ``Clifford change in basis'' assumption - Can be trimmed down to the case where $H=H'$.
+What do you think?}
+\begin{theorem}
+	Consider a magic distillation protocol transforming noisy Strange state
+	\begin{equation*}
+		\rho_S(\epsilon)^{\otimes n} \longrightarrow \E(\rho_S(\epsilon)^{\otimes n})=\rho_S(\epsilon')^{\otimes m} 
+	\end{equation*}
+	with $n, m \gg 1$.
+
+Let each qutrit have a Hamiltonian $H$ with stabilizer eigenstates and energies $E_0, E_1, E_2$, and define $E_{\rm max} = \max\{E_0, E_1, E_2\}$ and $E_s$ the eigenvalue of the eigenstate that \nick{overlaps} the negative component of $\rho_S(\epsilon)$ in the Wigner representation.
+Let $T =(k\beta)^{-1}$ be any characteristic temperature for the physical system in the state $\tau^{\otimes n}= (e^{-\beta H}/\Z)^{\otimes n}$, with free energy $F$.
+Assume that for $n,m \gg 1$ the channel $\E$ generates negligible correlations on $\tau^{\otimes n}$, and so $\E(\tau^{\otimes n}) = \sigma^{\otimes m}$ for some state $\sigma$.
+
+Define $\beta_\star = (k T_\star)^{-1}$ through the relation
+\begin{equation}
+	E_{\rm max} - E_s \eqqcolon kT_\star \ln 2,
+\end{equation}
+and define a threshold noise,
+\begin{equation}
+	\epsilon_{\star}(\beta) \coloneqq 
+	\begin{cases}
+		3 - \dfrac{9}{4-2^{\beta/\beta_\star - 1}}, &\text{ for } \beta \leq \beta_\star \\
+		0, &\text{ for } \beta > \beta_\star.
+	\end{cases}
+\end{equation}
+Then, the distillation rate $R = m/n$ of the magic protocol is bounded as:
+\begin{equation}\label{eq:rate_bounds_proof}
+	R \leq
+	\begin{cases}
+		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F')},\ &\epsilon \leq \epsilon_\star, \epsilon' \leq \epsilon'_\star, \vspace{10pt}\\
+		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F')},\ &\epsilon \leq \epsilon_\star, \epsilon' > \epsilon'_\star, \vspace{10pt}\\
+		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F')},\ &\epsilon > \epsilon_\star, \epsilon' \leq \epsilon'_\star, \vspace{10pt}\\
+		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F')},\ &\epsilon > \epsilon_\star, \epsilon' > \epsilon'_\star,
+	\end{cases}
+\end{equation}
+where $F'$ is the free energy of the state $\sigma = e^{-\beta H'}/\Z'$ and other primed quantities are defined in the same way as the corresponding unprimed quantities. 
+\end{theorem}
+We note, firstly, that the specific numerical factors in $\epsilon_\star$ are a result of our choice of magic state. 
+\begin{proof}
+To establish the distillation bounds we consider the distillation protocol that gives
+\begin{equation}
+	\E( \rho_S(\epsilon)^{\otimes n}) = \rho_S(\epsilon')^{\otimes m},
+\end{equation}
+for the magic state. We then consider how the protocol transforms the reference equilibrium state as
+\begin{equation}
+	\E( \tau^{\otimes n}) = \sigma^{\otimes m}.
+\end{equation}
+Since $\tau$ and $\sigma$ are assumed to be full rank stabilizer states they have a strictly positive Wigner distribution, while, in contrast, the input and output magic states will generally have quasi-probability distributions for their Wigner functions.
+For any such protocol we therefore have that
+\begin{equation}
+	(W_{\rho_n} (x), W_{\tau_n}(x) ) \succ  (W_{\rho'_m} (x), W_{\sigma_m}(x) ),
+\end{equation}
+where, for the sake of clarity, we write $\rho_n \coloneqq \rho_S(\epsilon)^{\otimes n}$, $\rho'_m \coloneqq \rho_S(\epsilon')^{\otimes m}$ and $\tau_n \coloneqq \tau^{\otimes m}$, $\sigma_m \coloneqq \sigma^{\otimes m}$.
+We then have that
+\begin{equation}
+	L_{\rho_n |\tau_n}(x) \ge L_{\rho'_m |\sigma_m}(x) \mbox{ for all } x.
+\end{equation}
+We must therefore compute the Lorenz curve data for $\rho_n$ relative to $\tau_n$, and compare with the Lorenz curve of the output state $\rho_m'$ relative to $\sigma_m$.
+
+We define $W_{\rho | \tau}(\x) \coloneqq W_\rho(\x)/W_\tau(\x)$, which is always well-defined since $\tau$ is full-rank. Now we show in~\cref{app:wigner} that
+\begin{equation}
+W_{\rho_1\otimes \rho_2 | \tau_1 \otimes \tau_2} (\x_1 \oplus \x_2) = W_{\rho_1 | \tau_1}(\x_1)W_{\rho_2 | \tau_2}(\x_2),
+\end{equation}
+and also,
+\begin{equation}
+W_{\rho_1\otimes \rho_2} (\x_1 \oplus \x_2) = W_{\rho_1}(\x_1)W_{\rho_2}(\x_2),
+\end{equation}
+for any states $\rho_1, \rho_2$ and any full-rank stabilizer states $\tau_1, \tau_2$.
+\ddd{[Notation clashing here.
+Frame result outside as its own lemma -- we gotta check everything.]} \nick{Will frame in~\cref{app:wigner} and fix notation in the next commit}
+Therefore we have that
+\begin{align}
+W_{\rho_n |\tau_n} (\x) &= \prod_{i=1}^n W_{\rho|\tau}(\x_i)\\
+W_{\rho_n } (\x) &= \prod_{i=1}^n W_\rho(\x_i)
+\end{align}
+where $\x = \oplus_{i=1}^n \x_i$ is the phase space point for the full system in terms of those of the individual subsystems.
+
+The points defining the Lorenz curve $L_{\rho_n |\tau_n}(x)$ are obtained from first sorting the components of $W_{\rho_n |\tau_n}(\x)$ in non-increasing order and then computing the partial sums of $W_{\rho_n |\tau_n}(\pi(\x))$ where $\pi$ is the permutation that realises the sorting.
+Therefore, we first look at the values of $W_{\rho|\tau}(\x_i)$ for the single-copy case.
+
+The equilibrium state at inverse temperature $\beta$ on a single qutrit is given by $\tau = e^{-\beta H} / \Z$.
+Moreover we have that $\tau$ is a full-rank stabilizer state, where $\beta \geq 0$ and $H = E_0 \ketbra{\varphi_0} + E_1 \ketbra{\varphi_1} + E_2 \ketbra{\varphi_2}$ is an eigendecomposition of $H$.
+The state $\tau$ can now be written as 
+\begin{equation}
+	\tau = \frac{e^{-\beta E_0}}{\Z} \ketbra{\varphi_0} + \frac{e^{-\beta E_1}}{\Z} \ketbra{\varphi_1} + \frac{e^{-\beta E_2}}{\Z} \ketbra{\varphi_2},
+\end{equation}
+where the eigenstates $\{\ket{\varphi_k}\<\varphi_k|\}$ are pure, orthonormal stabiliser states, which can be represented in terms of generalized Paulis.
+To make our analysis simpler, we perform a change of basis that does not affect the Wigner negativity of the problem.
+We let $C$ be the unitary transforming each $|\varphi_k\>\<\varphi_k|$ to $|k\>\<k|$.
+Since the Clifford group is the normalizer of the Heisenberg-Weyl group, $C$ is a Clifford unitary.
+Therefore, $C$ maps $\tau$ to another stabilizer state that is diagonal in the computational basis, and we can assume without loss of generality that $\tau$ is diagonal in $\{|0\>,|1\>, |2\>\}$.
+However, this choice means that the location of the negative Wigner component $-v(\epsilon)$ of the Strange state will be permuted on the discrete phase space.
+We denote by $E_s$ the eigenvalue of $H$ where the associated eigenvector has Wigner distribution overlapping the negative component of the magic state $C\rho_S(\epsilon)C^\dagger$.
+This is unique, since the eigenstates form an orthonormal basis.
+
+The Wigner distribution of state $\tau$ is then given by
+\begin{align}
+	\W[\bmx]{\tau} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z}W_{\ketbra{k}}(x, p) \nonumber\\
+	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z} \delta_{x, k} = \frac{e^{-\beta E_x}}{3\Z},
+\end{align}
+where $x$ labels one of the three vertical lines in the phase space.
+The rescaled Wigner distribution $W_{\rho|\tau}(\x)$ is then easily computed.
+It has $9$ components, but several of these come with multiplicities.
+In total, there are four distinct values on the phase space, as illustrated in~\cref{fig:pd_split}.
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.45]{figs/pd_split_thermal.pdf}
+    \caption{\textbf{Qutrit phase space regions for $W_{\rho | \tau}(\x)$.}
+    Here, the negative component of the magic state overlaps the Wigner distribution of $|0\>$.
+The rescaled distribution attains a single value in each of the four regions, proportional to the value depicted in the region, see~\cref{eq:bmw_rescaled}.
+    }
+    \label{fig:pd_split}
+\end{figure}
+
+We now denote by $\w(\rho), \w(\rho|\tau)$ the unique values occurring in $W_\rho(\x), W_{\rho|\tau}(\x)$ respectively and $\bmm$ the vector of associated multiplicities of each value in $W_\rho(\x)$.
+The component values and multiplicities of the relevant distributions in the four distinct regions are given by
+\begin{align}
+	\w(\rho) &\coloneqq (-v, u, u, u), \\
+		\bmm &\coloneqq (1,2,3,3), \\
+	\bmw(\tau) &\coloneqq \frac{1}{3\Z} \left( e^{-\beta E_0}, e^{-\beta E_0}, e^{-\beta E_1}, e^{-\beta E_2} \right), \\
+	\bmw(\rho_{\rm{S}} | \tau) &\coloneqq 3\Z \left( -v e^{\beta E_0}, u e^{\beta E_0}, u e^{\beta E_1}, u e^{\beta E_2} \right). \label{eq:bmw_rescaled}
+\end{align}
+
+Using this notation, the values and multiplicities of the $n$--copy distribution $\bmw(\rho_n |\tau_n)$ are computed in~\cref{lem:ncopycomponents} in~\cref{app:cmpairs}. The values are given by 
+\begin{align}\label{eq:ncopy_w_rescaled}
+	[\w(\rho_n | \tau_n)]_{ijk} &= (3\Z)^{n} (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )},
+\end{align}
+where the indices $i,j,k$ are non-negative integers that obey the constraint $\alpha \coloneqq i+j+k \leq n$.
+The multiplicity of this above value is $m_{ijk}$ with
+\begin{equation}
+	m_{ijk} = \frac{n!}{i!j!k!(n-\alpha)!} 2^i 3^j 3^k.
+\end{equation}
+The associated components of $\w(\rho_n)$ are given by
+\begin{align}
+	[\w(\rho_n)]_{ijk} &= (-v)^{n-\alpha} u^{\alpha}, \label{eq:ncopy_wrho}\\
+	[\w(\tau)]_{ijk} &= (3\Z)^{-n} e^{-\beta (n-\alpha)E_s} e^{-\beta ( i E_0 + j E_1 + k E_2 )}. \label{eq:ncopy_wsigma}
+\end{align}
+
+In order to construct the $n$--copy Lorenz curve $L_{\rho_n|\tau_n}(x)$ we need to order the components of the distribution, $w(\rho_{\rm{S}} | \tau)_{ijk}$ in decreasing order, and identify the sequence of indices that give us $W_{\rho_n}(\pi(\x))$.
+
+Generally this is complex, but in order to obtain distillation bounds it is sufficient to determine the location of the first elbow $(x_0, L_0)$ of $L_{\rho_n|\tau_n}(\x)$.
+To do so, we compute the largest component
+\begin{equation}
+	w_{\rm max} \coloneqq \max_{i,j,k} [\w(\rho_n | \tau_n)]_{ijk},
+\end{equation}
+and determine the indices at which this occurs.
+Putting in the values we obtain
+\begin{align}
+	&(3\Z)^{-n}w_{\rm max} = \nonumber\\
+	&\max\limits_{i,j,k}\Big\{ (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \label{eq:max_slope}
+\end{align}
+where $0 \leq i,j,k \leq n$ and $\alpha \coloneqq i+j+k \leq n$.
+Now for $0 \leq \epsilon \leq 3/7$, we have $v \geq u$. Since we assume that $n$ is even, we need the sum $\alpha = i+j+k$ to be even too, so that the expression is positive.
+
+Given an even value for $\alpha$, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_s}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
+Hence, we have
+\begin{align}
+	&w_{\rm max} = \nonumber\\
+	&(3\Z)^{n} v^n e^{n\beta E_s}\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_s)} \right)^{\alpha} \Big\}}.
+\end{align}
+If the expression $\frac{u(\epsilon)}{v(\epsilon)} e^{\beta (E_{\rm{max}} - E_s)}$ is less than $1$ then the maximum occurs at $\alpha=0$, otherwise it occurs at $\alpha = n$.
+For a fixed state $\tau$, this transition is determined by the value of the depolarising noise parameter $\epsilon$ of the noisy magic state.
+The transition occurs at $\epsilon = \epsilon_\star$ where
+\begin{equation}\label{eq:noise_transition}
+	\frac{u(\epsilon_\star)}{v(\epsilon_\star)} e^{\beta (E_{\rm{max}} - E_s)} = \frac{3-\epsilon_\star}{6-8\epsilon_\star} e^{\beta (E_{\rm{max}} - E_s)} = 1.
+\end{equation}
+If $E_{\rm{max}} = E_s$, namely if the state negativity lies in the same phase space region as the highest energy, this threshold is constant in temperature and given by $\epsilon_{\star} = 3/7$.
+However, the condition that $\epsilon_\star \ge 0$ also implies a constraint on the effective temperature of the stabilizer state.
+Specifically, there is a threshold temperature value $\beta_\star$ given by
+\begin{equation}
+	\beta_{\star} \coloneqq \frac{1}{E_{\rm{max}} - E_s} \ln2,
+\end{equation}
+such that for the regime $0 \leq \beta \leq \beta_\star$ a transition noise level $\epsilon_\star$ exists, and for $\beta > \beta_\star$ no such transition exists, so we choose $\epsilon_\star = 0$. 
+Therefore, the transition value for the noise is given by
+\begin{equation}
+	\epsilon_{\star}(\beta) \coloneqq 
+	\begin{cases}
+		3 - \dfrac{9}{4-2^{\beta/\beta_\star - 1}}, &\text{ for } \beta \leq \beta_\star \\
+		0, &\text{ for } \beta > \beta_\star.
+	\end{cases}
+\end{equation}
+The quantity $w(\rho_{\rm{S}} | \sigma)_{\rm{max}}$ is now given by
+\begin{equation*}
+w_{\rm max} =
+	\begin{cases}
+		(3\Z)^{n} v^n e^{n\beta E_s}, &\mbox{if }\epsilon \leq \epsilon_{\star},\ \hspace{3pt}\rm{(C1)}\\
+		(3\Z)^{n} u^n e^{n\beta E_{\rm{max}}}, &\mbox{if }\epsilon > \epsilon_{\star}.\ \hspace{5pt}\rm{(C2)} 
+	\end{cases}
+\end{equation*}
+Case $\rm{(C1)}$ corresponds to $(i,j,k) = (0,0,0)$, so the multiplicity is $m_{000} = 1$, while
+Case $\rm{(C2)}$ corresponds to
+\begin{equation}
+	(i,j,k) = 
+	\begin{cases}
+	(0,n,0), &\text{if } E_{\rm{max}} = E_1, \\
+	(0,0,n), &\text{if } E_{\rm{max}} = E_2,
+	\end{cases}
+\end{equation}
+so the multiplicity in both cases is $3^n$.
+
+Using that $F = -\beta^{-1} \log \Z$, the first elbow coordinates in the two cases are now given by
+\begin{equation}\label{eq:first_elb_coords}
+	(x_0, L_0) =
+	\begin{cases}
+		\left(\frac{1}{3^n} e^{-n\beta (E_s - F)}, v^n \right), &\epsilon \leq \epsilon_\star \vspace{10pt}\\
+		\left( e^{-n\beta (E_{\rm{max}}-F)}, (3u)^n \right). &\epsilon > \epsilon_\star
+	\end{cases}
+\end{equation}
+
+\ddd{[Hmmm this needs an additional assumption on the output state to re-run the same analysis.
+Very annoying.]}\nick{What additional assumption beyond that the output state can be written as a Gibbs state for some $H'$?}
+Similarly, considering the output magic state with respect to state $\sigma'$, the image of equilibrium state $\sigma$ under the magic protocol, we get output Lorenz curve coordinates,
+\begin{equation}\label{eq:transformed_first_elb_coords}
+	(x'_0, L'_0) =
+	\begin{cases}
+		\left(\frac{1}{3^{n'}} e^{-n\beta (E'_s - F')}, v(\epsilon')^{n'} \right), &\epsilon' \leq \epsilon'_\star \vspace{10pt}\\
+		\left( e^{-n'\beta (E'_{\rm{max}}\hspace{-2.5pt}-F')}, (3u(\epsilon'))^{n'} \right), &\epsilon' > \epsilon'_\star
+	\end{cases}
+\end{equation}
+There are four combinations of coordinates, depending on the noise parameters $\epsilon, \epsilon'$ for the input and output states.
+In each of these combinations, we simply use the first elbow constraint, as described in~\cref{app:elb_constraints}, which leads to the bounds in the statement of the theorem.
+\end{proof}
 

### 2021-05-10 magic_paper.tex
small changes

--- 2021-05-07 magic_paper.tex
@@
 Its form is similar to $F$, and so can informally be viewed as a `magic free energy' term, associated to a `magic partition function' $\zeta$.
-While the coefficients $\alpha_k$ may be negative for some $k$, the quantity $\phi$ is always well-defined, since the function $\zeta$ is a positive multiple of the stabilizer Wigner component $W_\tau(0,0)$.
+The coefficients $\alpha_k$ may be negative for some $k$, when the Hamiltonian eigen-decomposes into non-stabilizer states, but the quantity $\phi$ is always well-defined, since the function $\zeta$ is a positive multiple of the stabilizer Wigner component $W_\tau(0,0)$, as seen in the proof of the theorem.
 

### 2021-05-10 appendix.tex

@@
 
+\newpage
 \subsection{Free energy dependent magic distillation bounds}\label{free-energy-bound-proof}
@@
 
-To establish the distillation bound we consider the distillation protocol that gives $\E( \rho_n) = \rho_m$ for the magic states. 
+To establish the distillation bound we consider the distillation protocol that gives $\E( \rho_n) = \rho'_m$ for the magic states. 
 We then consider that the protocol transforms the reference equilibrium state as $\E( \tau_n) = \tau'_m$.
@@
 However, similarly to the unital fragment analysis, we aim to use the constraint that is obtained by considering the line segment connecting the origin to the first elbow of both Lorenz curves.
-The proof of this constraint is provided in~\cref{app:elb_constraints}.
-Therefore, we focus on finding the coordinates of some point on this line segment of the Lorenz curves.
 
-We find the coordinates for the input Lorenz curve, but the exact same analysis can be applied on the output Lorenz curve.
 The Wigner distribution of a single noisy Strange state consists of 1 negative component $W_{\rho}(0,0) = -v(\epsilon)$ and 8 positive components $W_{\rho}(\bmx) = u(\epsilon)$ for $\bmx \neq \bmo$.
 The Wigner distribution of the full-rank, stabilizer equilibrium state $\tau$ is $W_{\tau}(\bmx) > 0$ for all $\bmx \in \mathbb{Z}_3^2$.
-We keep the components completely general.
 
-Assume that the smallest component of the equilibrium state distribution is $W_{\tau}(i,j)$.
+Assume that the smallest component of the distribution $W_\tau(\x)$ is at $x=\x_\star$.
 We then make use of the freedom to apply Clifford unitaries in order to perform the  Clifford operation

### 2021-05-10 magic_paper.tex
More appendix work done. Statements simplified. Material re-organised.

--- 2021-05-09 magic_paper.tex
@@
 \newpage
-\section{Properties of Wigner distributions}
+\section{Properties of Wigner representations}
 \label{app:wigner}
@@
     \label{thm:wchannel}
-    The Wigner distribution of a $\cptp$ operation $\E: \cal{B}(\cal{H}_{d_A}) \mapsto \cal{B}(\cal{H}_{d_B})$ is
+    The Wigner distribution of a quantum channel $\E: \cal{B}(\cal{H}_{d_A}) \rightarrow \cal{B}(\cal{H}_{d_B})$ is
     \begin{enumerate}
-        \item[(i)]\label{en:wo1} Real-valued: $\W{\E} \in \mathbb{R}^{d^2} \times \mathbb{R}^{d^2}$;
+        \item[(i)]\label{en:wo1} Real-valued: $\W{\E}(\x) \in \mathbb{R}^{d^2} \times \mathbb{R}^{d^2}$;
         \item[(ii)]\label{en:wo2} Normalised: $\sum_{\bmz \in \cal{P}_{d_B}} \W[\bmz|\bmx]{\E} = 1$ \\ 
@@
         \item[(iii)]\label{en:wo3} Bounded: $\abs{\W[\bmy|\bmx]{\E}} \leq \frac{d_A}{d_B}$;
-	    \item[(iv)]\label{en:wo4} Transitive: $\W[\bmy]{\E(\rho)} = \sum_{\bmz \in \cal{P}_{d_A}} \W[\bmy|\bmz]{\E} \W[\bmz]{\rho}$ for any $\bmy \in \cal{P}_{d_B}$.
+	    \item[(iv)]\label{en:wo4} $\W[\bmy]{\E(\rho)} = \sum_{\bmz \in \cal{P}_{d_A}} \W[\bmy|\bmz]{\E} \W[\bmz]{\rho}$ for any $\bmy \in \cal{P}_{d_B}$.
     \end{enumerate}
 \end{proposition}
-If $d_A = d_B$, and in particular if operation $\E$ maps a Hilbert space onto itself, then the stochasticity condition $\abs{\W[\bmy|\bmx]{\E}} \leq 1$ is satisfied.
 \begin{proof}
-	Proof of all properties are provided by Wang \textit{et al.}~\cite{Wang_2019} except for property (iii) which is a direct consequence of the definition of $\W{\E}$ and the corresponding property (iii) in~\cref{thm:wstate}.
+	Proof of all properties are provided in~\cite{Wang_2019} except for property (iii) which is a direct consequence of the definition of $\W{\E}$ and property (iii) in~\cref{thm:wstate}.
 \end{proof}
@@
 \begin{proposition}\label{prop:rmajor}
-Given $\bmx, \bmy, \r \in \mathbb{R}^n$, such that the components of $\r$ are positive, the following statements are equivalent:
+Given probability distributions $\bmx, \bmy, \r , \r'$, such that the components of $\r$ and $\r'$ are positive, the following statements are equivalent:
   \begin{enumerate}
-    \item[(i)] $\bmy = A\bmx$ and $\r = A\r$ for a stochastic map $A$;
-    \item[(ii)]\label{en:tm3} $\sum\limits_{i=1}^n \abs{x_i - r_i t} \leq \sum\limits_{i=1}^n \abs{y_i - r_i t}$ for all $t \in \mathbb{R}$;
-    \item[(iii)] $L_{\bmx|\r}(t) \leq L_{\bmy|\r}(t)$ for $t\in [0,1)$ and \vspace{5pt}\\ $L_{\bmx|\r}(1) = L_{\bmy|\r}(1)$.
+    \item[(i)] $\bmy = A\bmx$ and $\r' = A\r$ for a stochastic map $A$;
+    \item[(ii)]\label{en:tm3} $\sum\limits_{i=1}^n \abs{x_i - r_i t} \leq \sum\limits_{i=1}^n \abs{y_i - r'_i t}$ for all $t \in \mathbb{R}$;
+    \item[(iii)] $L_{\bmx|\r}(t) \leq L_{\bmy|\r'}(t)$ for $t\in [0,1)$ and \vspace{5pt}\\ $L_{\bmx|\r}(1) = L_{\bmy|\r'}(1)$.
   \end{enumerate}
@@
 
+Within the context of the Wigner representation, we define for convenience 
+\begin{equation}
+W_{\rho| \tau} (\x) := \frac{W_\rho (\x) }{ W_\tau(\x)},
+\end{equation}
+which is well-defined if $\tau$ is a full-rank stabilizer state.
 \begin{theorem*}
@@
 \begin{proof}
-	We denote the Wigner distributions of the states compactly as vectors $\bmw(\rho) \equiv W_\rho(x)$ and $\bmw(\sigma) \equiv W_\sigma(x)$.
-	We choose the component indexing so that the rescaled distribution 
-	\begin{equation}
-		\widetilde{\bmw}(\rho|\sigma) \coloneqq \left(\frac{w(\rho)_1}{w(\sigma)_1}, \dots, \frac{w(\rho)_{d^2}}{w(\sigma)_{d^2}} \right)^T,
-	\end{equation}
-	is sorted, $\widetilde{\bmw} = \widetilde{\bmw}^\downarrow$.
+	We denote the Wigner distributions of the states single-component vectors $\w(\rho)=W_\rho(x)$ and $ \w(\sigma)=W_\sigma(x)$. Likewise, we define
+	\begin{equation}
+\w(\rho|\sigma) = \frac{W_\rho (\x)}{W_{\sigma}(\x)}.
+\end{equation}
+	We choose the component indexing so that $\w(\rho|\sigma)^\downarrow = \w(\rho|\sigma)=:\tilde{\w}$ and so the components are sorted in non-increasing order.
+
 Note that all components of $\bmw(\sigma)$ are positive, so $\widetilde{w}_i \geq 0$ if and only if $w(\rho)_i \geq 0$ for any $i=1,\dots,d^2$.
@@
 Therefore, mana is one of $d^{2n}$ constraints, so majorization is strictly a stronger constraint in any fragment.
+\end{proof}
+
+The following lemma shows that the re-scaled Lorenz curves behave in a natural way under tensor products. 
+\begin{lemma}Let $\tau_A, \tau_B$ be full rank stabilizer states on systems $A$ and $B$, and let $\rho_A, \rho_B$ be arbitrary states on $A,B$. Then the rescaled quasi-distribution obeys
+\begin{equation}
+W_{\rho_A \otimes \rho_B | \tau_A \otimes \tau_B}(\bmx_A \oplus \bmx_B) =W_{\rho_A | \tau_A}(\x_A) W_{\rho_B | \tau_B}(\x_B)
+\end{equation}
+\end{lemma}
+\begin{proof} This follows from the definitions. 
+\begin{align}
+W_{\rho_A \otimes \rho_B | \tau_A \otimes \tau_B}(\bmx_A \oplus \bmx_B) &= \frac{W_{\rho_A \otimes \rho_B} (\x_A \oplus \x_B)}{W_{\tau_A \otimes \tau_B} (\x_A \oplus \x_B)}\nonumber \\
+ &= \frac{W_{\rho_A } (\x_A )W_{\rho_B } (\x_B )}{W_{\tau_A } (\x_A )W_{\tau_B } (\x_B )}\nonumber \\
+  &= W_{\rho_A | \tau_A}(\x_A) W_{\rho_B | \tau_B}(\x_B)\nonumber,
+\end{align}
+as claimed.
 \end{proof}
@@
 \end{proof}
-The above theorem can be of practical importance in reducing the necessary distillation constraints derived via majorization in $\sigma$--fragments.
+The above theorem can be used in reducing the necessary distillation constraints derived via majorization in $\sigma$--fragments.
 
@@
 Consider an experiment consisting of $n$ trials of throwing a $p$--coin, that is a coin with probability $p$ of landing on one side and $1-p$ of landing on the other.
-We express the sums over an even number $m$ of successful trials $\Phi_+$ and an odd number $m$ of successful trials $\Phi_-$,
+We express the sums over an even number $m$ of successful trials $\Phi_+$ and an odd number $m$ of successful trials $\Phi_-$, and so these are given by
 \begin{align}	
@@
 \end{align}
-They are symmetric in the sense that $S(p) = S(1-p)$ and $\ent{p}{q} = \ent{1-p}{1-q}$.
+They are symmetric about $p=1/2$, namely $S(p) = S(1-p)$ and $\ent{p}{q} = \ent{1-p}{1-q}$.
 
@@
 \subsection{Theory on bounding the core functions}
-\nick{Should we really keep this section? It is standard calculus and the bounds are really loose.}
+\nick{Should we really keep this section?
+It is standard calculus and the bounds are really loose.} \ddd{[Depends on what you want to do with them - we want people to build on our work, and so providing them some starter-tools is potentially valuable hints.
+Closed, weak bounds can be very useful.]}
 Here we present a more manageable method of bounding the core functions $\Phi_{\pm}$, which however results in looser bounds. 
@@
 \end{equation} 
-and $8$ positive components
+and $8$ positive components each with value
 \begin{equation}
@@
 \end{equation}
-where in the unital fragment we need the condition $0 \leq \epsilon < 3/4$, so that the state contains some Wigner negativity ($-v < 0$).
+
+In the unital fragment we need the condition $0 \leq \epsilon < 3/4$, so that the state contains some Wigner negativity ($-v < 0$).
 It is also clear that $v \geq u$ in the interval $0 \leq \epsilon \leq 3/7$, while $u > v$ in the interval $3/7 < \epsilon < 3/4$.
 
-The Wigner distribution of the $n$--copy $\epsilon$--noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ in the unital fragment is given by the convolution $\W{\rho_{\rm{S}}(\epsilon)^{\otimes n}} = W_{\rho_{\rm{S}}(\epsilon)}^{\otimes n}$.
-In general, $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ contains $n + 1$ distinct components, labelled $0,\dots, n$.
+The Wigner distribution of the $n$--copy $\epsilon$--noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ in the unital fragment is given by $\W{\rho_{\rm{S}}(\epsilon)^{\otimes n}} = W_{\rho_{\rm{S}}(\epsilon)}^{\otimes n}$.
+In general, $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ contains $n + 1$ distinct components, labelled $0,\dots, n$ \ddd{[What does this mean??]}.
+
 We present the distinct Wigner components of $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ along with their multiplicites in~\cref{tab:lcsu}.
-Note that LHS (RHS) refers to elbow coordinates $i$ on the left of and including (right of) the Lorenz curve maximum, stated precisely as
+Note that LHS (RHS) refers to elbow coordinates $i$ on the left (right of) the Lorenz curve maximum, stated precisely as
 \begin{align}
@@
   The expressions change depending on the noise level $\epsilon$, the parity of the number of copies $n$ and whether the index $i$ is lower or higher than the index of the Lorenz curve maximum (LHS vs RHS).
-  Multiplication $2i$ is considered modulo $(n+1)$.}
+  Multiplication $2i$ is considered modulo $(n+1)$.} \ddd{[This whole section is hard to decypher.
+Are these $w_i$ Wigner components?
+Unique Wigner components?
+Elbow values??
+I can't spend ages decyphering this.
+Can you give clear definitions in the text?]}
+
+  \ddd{[Also what does ``Multiplication $2i$ is considered modulo $(n+1)$'' mean???]}
   \label{tab:lcsu}
@@
 \begin{proposition}\label{prop:first_elb}
-	Consider a magic state process $\rho \longrightarrow \tau$ with input and output Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in $\R_\sigma$ and denote by $X_0, X'_0$ the first elbow locations of the input and output curves respectively.
-
-	Then, given any coordinates $(x_0, L_0)$ and $(x'_0, L'_0)$ on the input and output Lorenz curves, where $x_0 \leq X_0$ and $x'_0 \leq X'_0$, the process is possible in $\R_\sigma$ only if
+	Consider a magic state process $\rho \longrightarrow \rho'$ with input and output Lorenz curves $\lc{\rho}{\tau}(x), \lc{\rho'}{\tau}(x)$ in $\R_\tau$ and denote the coordinates of the first elbow of $L_{\rho|\tau}(x)$ by $(X_0, L_0)$ and the coordinates of the first elbow of $L_{\rho' |\tau}(x)$ by $(X'_0, L'_0)$.
+	Then the process is possible in $\R_\tau$ only if
 \begin{equation}\label{eq:first_elb_bound1}
-	\frac{L_0}{x_0} \geq \frac{L_0'}{x_0'}.
-\end{equation}
+	\frac{L_0}{x} \geq \frac{L_0'}{x'}.
+\end{equation}
+for all $x \leq X_0$ and $x' \leq X'_0$.
 \end{proposition}
@@
 
-First assume that $x_0 < x'_0$ and consider the Lorenz curve constraint at $x = x_0$,
-\begin{equation}
-	\lc{\rho}{\sigma}(x_0) \geq \lc{\tau}{\sigma}(x_0).
-\end{equation}
-We can find the output state Lorenz curve coordinate $L'_\star$ at location $x = x_0$ by interpolating between the origin and the output state's first elbow, 
-\begin{equation}
-	L'_\star = \frac{x_0}{x'_0}L'_0.
-\end{equation}
-The process is then possible only if $L_0 \geq L_\star'$ which is a rearrangement of~\cref{eq:first_elb_bound1}.
-
-If instead, $x_0 \geq x'_0$, consider the Lorenz curve constraint at $x = x'_0$,
-\begin{equation}
-	\lc{\rho}{\sigma}(x'_0) \geq \lc{\tau}{\sigma}(x'_0).
+First assume that $x < x'$ and consider the Lorenz curve constraint,
+\begin{equation}
+	\lc{\rho}{\tau}(x) \geq \lc{\rho'}{\tau}(x).
+\end{equation}
+We can find the output state Lorenz curve coordinate $L_{\rho'|\tau}(x)$ by interpolating between the origin and the output state's first elbow, 
+\begin{equation}
+	L_{\rho'|\tau}(x) = \frac{x}{x'}L_0.
+\end{equation}
+\ddd{[Is this correct??
+I'm trying to simplify your notation and proof, but the above doesn't seem obvious.
+Needs fixing -- I've set up simple notation so we should only use this instead of defining all different variables that confuse things.]}The process is then possible only if $L_0 \geq L_\star'$ which is a rearrangement of~\cref{eq:first_elb_bound1}.
+\ddd{[This is not clear/obvious -- can you step through the steps explicitly.]}
+
+If instead, $x \geq x'$, consider the Lorenz curve constraint at $x = x'$,
+\begin{equation}
+	\lc{\rho}{\tau}(x') \geq \lc{\rho'}{\tau}(x').
 \end{equation}
@@
 
-\begin{lemma}Let $\tau_A, \tau_B$ be full rank stabilizer states on systems $A$ and $B$, and let $\rho_A, \rho_B$ be arbitrary states on $A,B$. Then the rescaled quasi-distribution obeys
-\begin{equation}
-W_{\rho_A \otimes \rho_B | \tau_A \otimes \tau_B}(\bmx_A \oplus \bmx_B) =W_{\rho_A | \tau_A}(\x_A) W_{\rho_B | \tau_B}(\x_B)
-\end{equation}
+In general, a $1$--copy $d$--dimensional state $\rho$ is described by its $d^2$--dimensional Wigner distribution $\W{\rho}$. 
+The distribution $\W{\rho}$ is defined on the phase space, but it can be convenient to re-express this using vector notation.
+
+To each Wigner distribution $W_\rho(\x)$ we can define \emph{component-multiplicity} pairs $\{(w_i, m_i)\}$ where the value $w_i$ occurs in the distribution $W_\rho(\x)$ with multiplicity $m_i$.
+
+As an example, for the Strange state with
+\begin{equation}
+W_{\rho_S}(\x) = (-1/3, 1/6,  1/6,  1/6,  1/6,  1/6,  1/6,  1/6,  1/6)
+\end{equation}
+we have the component-multiplicity pairs: $\{( -1/3, 1), ( 1/6, 8)\}$.
+However we might also wish more freedom and not require that the different $w_i$ values are all distinct.
+For example the component-multiplity pairs $\{(-1/3, 1), (1/6, 2), (1/6, 3), (1/6, 3)\}$ also describe $W_{\rho_S}(\x)$.
+
+This representation is more compact when a Wigner distribution has a lot of multiplicities, and allows for simple handling of multiple copies via the following fact.
+\begin{lemma}
+Consider two Wigner distributions $\W{\rho_A}, \W{\rho_B}$ with component-multiplicity pairs 
+\begin{equation}
+	\{(w_i, m_i)\} \text{ and } \{(w_j', m_j')\},
+\end{equation}
+respectively. Then $\{(w_i w_j', m_i m_j')\}$ gives component-multiplicity pairs for $\W{\rho_A \otimes \rho_B}$.
 \end{lemma}
-\begin{proof} This follows from the definitions. 
-\begin{align}
-W_{\rho_A \otimes \rho_B | \tau_A \otimes \tau_B}(\bmx_A \oplus \bmx_B) &= \frac{W_{\rho_A \otimes \rho_B} (\x_A \oplus \x_B)}{W_{\tau_A \otimes \tau_B} (\x_A \oplus \x_B)}\nonumber \\
- &= \frac{W_{\rho_A } (\x_A )W_{\rho_B } (\x_B )}{W_{\tau_A } (\x_A )W_{\tau_B } (\x_B )}\nonumber \\
-  &= W_{\rho_A | \tau_A}(\x_A) W_{\rho_B | \tau_B}(\x_B)\nonumber,
-\end{align}
-as claimed.
-\end{proof}
-
-In general, a $1$--copy $d$--dimensional state $\rho$ is described exactly by its $d^2$--dimensional Wigner distribution $\W{\rho}$. 
-The distribution $\W{\rho}$ is defined on the phase space, but it can be convenient to re-express this using vector notation. 
-In particular, we introduce a component vector $\bmw(\rho) = (w_i)_{i=1,\dots,D}$ and a multiplicity vector $\bmm(\rho) = (m_i)_{i=1,\dots,D}$, where $D \leq d^2$ which together form a set of component-multiplicity pairs $\{(w_i, m_i)\}_{i=1,\dots,D}$.
-\begin{definition}
-	Consider a distribution $W$ and a positive integer $D \leq {\rm{dim}}\hspace{1pt}W$. 
-	We call the set of ordered pairs $\{(w_i, m_i)\}_{i=1,\dots,D}$ a \emph{complete set of component-multiplicity pairs}, if $W$ contains $m_i$ components $w_i$ and $\sum_{i=0}^D m_i = d^2$.
-\end{definition}
-Therefore, such a set describes each component of $\W{\rho}$ exactly once.
-As an example, two complete sets of pairs for the Strange state are $\{( -1/3, 1), ( 1/6, 8)\}$ and $\{(-1/3, 1), (1/6, 2), (1/6, 3), (1/6, 3)\}$.
-The latter corresponds to the phase space split in~\cref{fig:pd_split}
-
-Consider two states $\rho_A, \rho_B$ with Wigner distributions $\W{\rho_A}, \W{\rho_B}$ described respectively by complete sets of component-multiplicity pairs 
-\begin{equation}
-	\{(w_i, m_i)\}_{i=1,\dots,D_A} \text{ and } \{(w_j', m_j')\}_{j=0,\dots,D_B}.
-\end{equation}
-The multiplicative property of the Wigner distribution over a composite phase space $\cal{P}_{d_A} \times \cal{P}_{d_B}$ shown in~\cref{thm:wstate},
-\begin{equation}
-	\W[\bmx_A \oplus \bmx_B]{\rho_A \otimes \rho_B} = \W[\bmx_A]{\rho_A}\W[\bmx_B]{\rho_B},
-\end{equation}
-implies that the distribution $\W{\rho_A \otimes \rho_B}$ is $d_A^2 d_B^2$--dimensional and contains components of the form $w_i w_j'$. 
-Therefore, the set $\{(w_i w_j', m_i m_j')\}$ with $i=1,\dots,D_A$ and $j=1,\dots,D_B$ is a complete set of component-multiplicity pairs for the distribution of the composite system $\W{\rho_A \otimes \rho_B}$.
+
 This is true because all components are of the form $w_i w_j'$ and 
@@
 \end{equation*}
+
+For distillation protocols we are interested in $n$--copies of a single Wigner distribution. For this we have the following, which follows from combinatorics.
+
+\begin{lemma} Suppose $W_\rho(\x)$ has $K$ component-multiplicity pairs $\{(w_i, m_i)\}$.
+Then $W_{\rho^{\otimes n}} (\x)$ has component-multiplicity pairs $\{(w_{\q}, m_{\q})\}$, where $\q$ is a $K$ component vector of non-negative integers that sum to $n$, and
+\begin{align}
+w_{\q} &= \prod_{i=1}^K w_i^{q_i} \\
+m_{\q} &= \binom{n}{q_1,q_2, \dots, q_K} \prod_{i=1}^K m_i^{q_i},
+\end{align}
+where the first term in the expression for $m_{\q}$ is the generalized binomial coefficient.
+\end{lemma}
 
@@
 
-%Index vector $\bmk$ has $D-1$ independent components and in the proof of our main theorem in~\cref{sec:stab} we have $D=4$, so we simplify the notation by writing the component and multiplicity vectors of the $n$--copy state distributions as $m_{ijk}, w(\rho_{\rm{S}})_{ijk}, w(\sigma)_{ijk}$ and $w(\rho_{\rm{S}}|\sigma)_{ijk}$, where $i,j,k$ are the 3 independent index components.
-
 \newpage
@@
 
-The Wigner distribution of a single noisy Strange state consists of 1 negative component $W_{\rho}(0,0) = -v(\epsilon)$ and 8 positive components $W_{\rho}(\bmx) = u(\epsilon)$ for $\bmx \neq \bmo$.
+The Wigner distribution of a single noisy Strange state consists of 1 negative component $W_{\rho}(\mathbf{0}) = -v(\epsilon)$ and 8 positive components $W_{\rho}(\bmx) = u(\epsilon)$ for $\bmx \neq \bmo$.
 The Wigner distribution of the full-rank, stabilizer equilibrium state $\tau$ is $W_{\tau}(\bmx) > 0$ for all $\bmx \in \mathbb{Z}_3^2$.
@@
 
-\subsection{OLD VERSION OF MAIN THEOREM}
-
-\ddd{[Do we need to keep any of the details in this section? If not then delete it entirely.]}
+\subsection{Dropping pre/post-processing of the magic states}
+If we drop the freedom to transform them magic states via Clifford unitaries that depend on the reference states $\tau$ and $\tau'$, then the analysis just presented gets a little more complex, since the largest component in the rescaled distribution depends on a number of factors.
+We illustrate this by the following result.
+
 \nick{This proof offers: 1.
@@
 a method for lifting the ``Clifford change in basis'' assumption - Can be trimmed down to the case where $H=H'$.
-What do you think?}
+What do you think?} \ddd{[Yep, we re-play the previous notation+line but then drop the Clifford unitary freedom and go through the different cases.]}
 \begin{theorem}

### 2021-05-10 magic_paper.tex
some corrections

--- 2021-05-10 magic_paper.tex
@@
 % UK vs US english
-% Spacing (fig positioning, sections, paragraphs, eq. numbering, QED symbols)
+% Spacing (figs, sections, paragraphs, eq. numbering, \noindent, QEDs)
 
@@
 \end{equation}
-with $n \gg 1$, $\epsilon' <\epsilon$ and $\E$ denoting the quantum channel induced by the protocol.
+with $n \gg 1$ \nick{Should we replace $m$ with $R n$ throughout?}, $\epsilon' <\epsilon$ and $\E$ denoting the quantum channel induced by the protocol.
 We can now provide distillation bounds that depend on energetic and entropic aspects of the protocol.
@@
 	Let $T =(k\beta)^{-1}$ be any finite temperature for the physical system and let $H= \sum_{k \in \mathbb{Z}_3} E_k |E_k\>\<E_k|$ be the Hamiltonian of each qutrit subsystem in its eigen-decomposition.
-Assume that in the thermodynamic limit the protocol applied to $\tau^{\otimes n}$, gives $\tau^{\otimes n} \longrightarrow \tau^{\prime \otimes m}$ for $n,m \gg 1$, and write the state $\tau'$ as $\tau' = e^{-\beta H'}/\Z'$ for some Hermitian $H'$.
+Assume that in the thermodynamic limit ($n,m \gg 1$), the protocol applied to the equilibrium state $\tau^{\otimes n} = (e^{-\beta H}/\Z)^{\otimes n}$ maps $\tau^{\otimes n} \longrightarrow \tau^{\prime \otimes m}$, where we express state $\tau'$ as $\tau' = e^{-\beta H'}/\Z'$ for some Hermitian $H'$.
 
@@
 	\zeta &= \sum_{k\in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}, \nonumber\\
-	\alpha_k &= \sum_{r \in \mathbb{Z}_3} \<E_k| A_{\x_\star} |E_k\>,
-\end{align}
-with $\x_\star = \mbox{argmin}[W_\tau( \x )]$. The primed variables are defined similarly for the output system.
+	\alpha_k &= \<E_k| A_{\x_\star} |E_k\>,
+\end{align}
+and $\x_\star = \arg\!\min W_\tau(\x)$. The primed variables are defined similarly for the output system.
 \end{theorem}
-The proof of this is provided in~\cref{free-energy-bound-proof}, and is a generalization of the analysis for unital protocols.
+\noindent The proof of this is provided in~\cref{free-energy-bound-proof}, and is a generalization of the analysis for unital protocols.
 
@@
 The sole purpose of the Clifford unitaries $C_1,C_2$ is to simplify the form of the $\alpha_k$ coefficients.
-For example, if $H=Z$ then the energy eigenbasis is equivalent to the computational basis up to a Fourier transform, and so $\phi$ would have a sharp, temperature-independent value $\phi \in \{E_0,E_1,E_2\}$ once we account for the Clifford change in basis.
+\nick{That's not right, without Clifford processing we would get bounds that depend on $u$ whenever $\x_\star$ corresponds to $u$, as well as $v$ whenever $\x_\star$ corresponds to $v$ as seen in the contour plot - these are different values} For example, if $H=Z$ then the energy eigenbasis is equivalent to the computational basis up to a Fourier transform, and so $\phi$ would have a sharp, temperature-independent value $\phi \in \{E_0,E_1,E_2\}$ once we account for the Clifford change in basis.
 
@@
     \caption{\textbf{Temperature-dependent bounds for magic distillation.}
-  Shown is a contour plot of  $R(\epsilon, \beta)$ for $H = H' = \sum_{k \in \mathbb{Z}_3} k \ketbra{k}$ and $\epsilon' = 0$, where $\beta$ is the inverse temperature and $\epsilon$ the depolarising noise of the input magic state.
+  Shown is a contour plot of the bound on $R(\epsilon, \beta)$ for $H = H' = \sum_{k \in \mathbb{Z}_3} k \ketbra{k}$ and $\epsilon' = 0$, where $\beta$ is the inverse temperature and $\epsilon$ the depolarising noise of the input magic state.
 The relevant data from the spectrum of the qutrit operator $H$ enters in via $\epsilon_\star(\beta)$ and $\beta_\star$.
@@
 \end{align*}
-therefore the value of the Lorenz function at each potential elbow point $x_k = \sum_{i=1} ^kr_{\pi(i)}$ is given by
+so the value of the Lorenz curve at each potential elbow point $x_k = \sum_{i=1} ^kr_{\pi(i)}$ is given by
 \begin{align}
@@
 
-\begin{lemma}Let $\tau_A, \tau_B$ be full rank stabilizer states on systems $A$ and $B$, and let $\rho_A, \rho_B$ be arbitrary states on $A,B$. Then the rescaled quasi-distribution obeys
+\nick{FIX}
+The above analysis also holds for rescaled distributions, as they are also multiplicative.
+\begin{proposition}Let $\tau_A, \tau_B$ be full rank stabilizer states on systems $A$ and $B$, and let $\rho_A, \rho_B$ be arbitrary states on $A,B$. Then the rescaled quasi-distribution obeys
 \begin{equation}
@@
 \end{equation}
-\end{lemma}
-\begin{proof} This follows from the definitions. 
+\end{proposition}
+\begin{proof} This follows from the multiplicative property of the Wigner distribution. 
 \begin{align}
@@
 \begin{lemma}\label{lem:ncopycomponents}
-	Let $W$ be a distribution defined by a complete set of component-multiplicity pairs $\{(w_i, m_i)\}_{i=1,\dots,D}$ with $D \leq {\rm{dim}}\hspace{1pt}W$ and consider the distribution $W^{\otimes n}$ obtained by taking the $n$-fold (Kronecker) product $W \otimes \dots \otimes W$ between $n$ copies of $W$.
+	Let $W$ be a distribution defined by a complete set of component-multiplicity pairs $\{(w_i, m_i)\}_{i=1,\dots,D}$ with $D \leq {\rm{dim}}\hspace{1pt}W$ and consider the distribution $W^{\otimes n}$ obtained by the $n$-fold (Kronecker) product $W \otimes \dots \otimes W$ between $n$ copies of $W$.
 
@@
 	\zeta &= \sum_{k\in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}, \nonumber\\
-	\alpha_k &= \sum_{r \in \mathbb{Z}_3} \<E_k| A_{\x_\star} |E_k\>,
-\end{align}
-with $\x_\star = \mbox{argmin}[W_\tau( \x )]$. The primed variables are defined similarly for the output system.
+	\alpha_k &= \<E_k| A_{\x_\star} |E_k\>,
+\end{align}
+with $\x_\star = \arg\!\min W_\tau(\x)$. The primed variables are defined similarly for the output system.
 \end{theorem}
@@
 \begin{equation}
-\rho_S(\epsilon) \rightarrow C \rho_S(\epsilon) C^\dagger = D_{x_\star} \rho_S(\epsilon) D_{x_\star}^\dagger,
+\rho_S(\epsilon) \rightarrow C \rho_S(\epsilon) C^\dagger = D_{\x_\star} \rho_S(\epsilon) D_{\x_\star}^\dagger,
 \end{equation}
@@
 \alpha_k := \<E_k |A_{\x_\star} |E_k\> \\
-\zeta :=  \sum_{r \in \mathbb{Z}_3} \alpha_k e^{-\beta E_k},
+\zeta :=  \sum_{k \in \mathbb{Z}_3} \alpha_k e^{-\beta E_k},
 \end{align}

### 2021-05-11 magic_paper.tex

--- 2021-05-10 magic_paper.tex
@@
 Its form is similar to $F$, and so can informally be viewed as a `magic free energy' term, associated to a `magic partition function' $\zeta$.
-While the coefficients $\alpha_k$ may be negative for some $k$, the quantity $\phi$ is always well-defined, since the function $\zeta$ is a positive multiple of the stabilizer Wigner component $W_\tau(0,0)$.
+The coefficients $\alpha_k$ may be negative for some $k$, when the Hamiltonian eigen-decomposes into non-stabilizer states, but the quantity $\phi$ is always well-defined, since the function $\zeta$ is a positive multiple of the stabilizer Wigner component $W_\tau(0,0)$, as seen in the proof of the theorem.
 
 The sole purpose of the Clifford unitaries $C_1,C_2$ is to simplify the form of the $\alpha_k$ coefficients.
-For example, if $H=Z$ then the energy eigenbasis is equivalent to the computational basis up to a Fourier transform, and so $\phi$ would have a sharp, temperature-independent value $\phi \in \{E_0,E_1,E_2\}$ once we account for the Clifford change in basis.
+\nick{That's not right, without Clifford processing we would get bounds that depend on $u$ whenever $\x_\star$ corresponds to $u$, as well as $v$ whenever $\x_\star$ corresponds to $v$ as seen in the contour plot - these are different values} For example, if $H=Z$ then the energy eigenbasis is equivalent to the computational basis up to a Fourier transform, and so $\phi$ would have a sharp, temperature-independent value $\phi \in \{E_0,E_1,E_2\}$ once we account for the Clifford change in basis.
 
@@
 \begin{proposition}\label{prop:rmajor}
-Given probability distributions $\bmx, \bmy, \r , \r'$, such that the components of $\r$ and $\r'$ are positive, the following statements are equivalent:
+Given probability distributions $\bmx, \bmy$, $\r , \r'$, such that the components of $\r$ and $\r'$ are positive, the following statements are equivalent:
   \begin{enumerate}
@@
 
-Within the context of the Wigner representation, we define for convenience 
+Within the context of the Wigner representation, we define the re-scaled quasi-distribution
 \begin{equation}
@@
 which is well-defined if $\tau$ is a full-rank stabilizer state.
+
+The following lemma shows that the re-scaled Lorenz curves behave in a natural way under tensor products. 
+\begin{proposition}
+	Let $\tau_A, \tau_B$ be full rank stabilizer states on systems $A$ and $B$, and let $\rho_A, \rho_B$ be arbitrary states on $A,B$. Then the rescaled quasi-distribution obeys
+\begin{equation}
+W_{\rho_A \otimes \rho_B | \tau_A \otimes \tau_B}(\bmx_A \oplus \bmx_B) =W_{\rho_A | \tau_A}(\x_A) W_{\rho_B | \tau_B}(\x_B)
+\end{equation}
+\end{proposition}
+\begin{proof} This follows from the definitions. 
+\begin{align}
+W_{\rho_A \otimes \rho_B | \tau_A \otimes \tau_B}(\bmx_A \oplus \bmx_B) &= \frac{W_{\rho_A \otimes \rho_B} (\x_A \oplus \x_B)}{W_{\tau_A \otimes \tau_B} (\x_A \oplus \x_B)}\nonumber \\
+ &= \frac{W_{\rho_A } (\x_A )W_{\rho_B } (\x_B )}{W_{\tau_A } (\x_A )W_{\tau_B } (\x_B )}\nonumber \\
+  &= W_{\rho_A | \tau_A}(\x_A) W_{\rho_B | \tau_B}(\x_B)\nonumber,
+\end{align}
+as claimed.
+\end{proof}
+
 \begin{theorem*}
@@
 Therefore, mana is one of $d^{2n}$ constraints, so majorization is strictly a stronger constraint in any fragment.
-\end{proof}
-
-The following lemma shows that the re-scaled Lorenz curves behave in a natural way under tensor products. 
-\begin{lemma}Let $\tau_A, \tau_B$ be full rank stabilizer states on systems $A$ and $B$, and let $\rho_A, \rho_B$ be arbitrary states on $A,B$. Then the rescaled quasi-distribution obeys
-\begin{equation}
-W_{\rho_A \otimes \rho_B | \tau_A \otimes \tau_B}(\bmx_A \oplus \bmx_B) =W_{\rho_A | \tau_A}(\x_A) W_{\rho_B | \tau_B}(\x_B)
-\end{equation}
-\end{lemma}
-\begin{proof} This follows from the definitions. 
-\begin{align}
-W_{\rho_A \otimes \rho_B | \tau_A \otimes \tau_B}(\bmx_A \oplus \bmx_B) &= \frac{W_{\rho_A \otimes \rho_B} (\x_A \oplus \x_B)}{W_{\tau_A \otimes \tau_B} (\x_A \oplus \x_B)}\nonumber \\
- &= \frac{W_{\rho_A } (\x_A )W_{\rho_B } (\x_B )}{W_{\tau_A } (\x_A )W_{\tau_B } (\x_B )}\nonumber \\
-  &= W_{\rho_A | \tau_A}(\x_A) W_{\rho_B | \tau_B}(\x_B)\nonumber,
-\end{align}
-as claimed.
 \end{proof}

### 2021-05-11 magic_paper.tex
Added plots on F, phi variation

@@
 
-The above bound demonstrates how one can use relative majorization of quasi-distributions to incorporate additional information into distillation bounds.
-The analysis involved makes simplifying assumptions that could easily be dropped, at the price of more complex expressions.
-For example, we can obtain general expressions without any assumptions on $\epsilon, \epsilon'$ or without performing any Clifford change in basis.
-We could also perform similar analysis for general qudits, and different choices of magic states.
-It might also be of interest to consider other choices of reference states that may include more appropriate hardware physics, for example for photonic set-ups.
-
-The only assumption that cannot be trivially dropped is the assumption that we can ignore correlations in the thermodynamic limit.
-This is a common situation in thermodynamics, where correlations are often sub-linear in the particle number in the macroscopic limit.
-One could perturb about this scenario, and make use of variational tools such as the Bogoliubov inequality~\cite{bogolyubov_1966} for approximating the free energy of a system, to obtain bounds in a similar form.
-
+\iffalse
 \begin{figure}[t!]
@@
 \end{figure}
+\fi
+
+\begin{figure}[t!]
+    \centering
+    \subfigure[][]{%
+    \label{fig:noCliff}%
+    \includegraphics[scale=0.4]{figs/rate_scatter.pdf}}\\
+    \subfigure[][]{%
+    \label{fig:Cliff}%
+    \includegraphics[scale=0.4]{figs/rate_scatter_cliff.pdf}}
+    \caption{\textbf{Temperature-dependent bounds for magic distillation.} \nick{Need to replot with one shared colorbar} Shown are two contour plots of the bound on $R(\epsilon, \beta)$ for $H = H' = \sum_{k \in \mathbb{Z}_3} k \ketbra{k}$ and $\epsilon' = 0$, where $\beta$ is the inverse temperature and $\epsilon$ the depolarising noise of the input magic state.
+The relevant data from the spectrum of the qutrit operator $H$ enters in via $\epsilon_\star(\beta)$ and $\beta_\star$.
+The $\beta = 0$ line corresponds to the regime in which the magic protocol corresponds to a unital channel.
+\subref{fig:noCliff} No additional Clifford processing is performed to obtain this plot.
+The vertical dashed line is the `Landauer-like' temperature threshold $\beta_\star$ and the diagonal dashed curve corresponds to the noise threshold $\epsilon_\star(\beta)$ for $\beta \leq \beta_\star$, as defined in~\cref{app:cliff_processing}.
+ \subref{fig:Cliff} Clifford processing was performed resulting in a smooth bound.}
+    \label{fig:rate_contour}
+\end{figure}
+
+\cref{thm:free-energy} is a demonstration of how one can use relative majorization of quasi-distributions to incorporate additional information into distillation bounds.
+The analysis involved makes simplifying assumptions that could easily be dropped, at the price of more complex expressions.
+For example, we can obtain general expressions without any assumptions on $\epsilon, \epsilon'$ or without performing any Clifford change in basis.
+We could also perform similar analysis for general qudits, and different choices of magic states.
+It might also be of interest to consider other choices of reference states that may include more appropriate hardware physics, for example for photonic set-ups.
+
+The only assumption that cannot be trivially dropped is the assumption that we can ignore correlations in the thermodynamic limit.
+This is a common situation in thermodynamics, where correlations are often sub-linear in the particle number in the macroscopic limit.
+One could perturb about this scenario, and make use of variational tools such as the Bogoliubov inequality~\cite{bogolyubov_1966} for approximating the free energy of a system, to obtain bounds in a similar form.
 
@@
 
+\subsection{\nick{Numerics on varying $F, \phi$}}
+
 In the more general case, $\Delta F \coloneqq F' - F \ne 0$ and we have a free energy difference between the initial and final states, with respect to the relevant Hamiltonians.
@@
 
-\ddd{[Need some numerics on varying the $F'$ case]}
-
+\nick{Below are some interesting findings}
+
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.4]{figs/test/R_vs_E1.pdf}
+    \caption{Here, $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$, $H = \rm{diag}(0,E,10)$ and $H' = \rm{diag}(0,E',10)$.
+    }
+    \label{fig:rvse1}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.4]{figs/test/R_vs_E2.pdf}
+    \caption{Here, $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$, $H = \rm{diag}(0,5,E)$ and $H' = \rm{diag}(0,5,E')$.
+    }
+    \label{fig:rvse2}
+\end{figure}
+
+\begin{figure}[t!]
+    \centering
+    \subfigure[][]{%
+    \label{fig:phip}%
+    \includegraphics[scale=0.4]{figs/test/phi_p.pdf}}\\
+    \subfigure[][]{%
+    \label{fig:Rp}%
+    \includegraphics[scale=0.4]{figs/test/rate_p.pdf}}
+    \caption{Here, $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$, $H = p\ {\rm{diag}}(0,1,2) + (1-p)\ {\rm{Hadamard}}$.
+\subref{fig:noCliff} Plot of $\phi$ vs $p$
+ \subref{fig:Cliff} Plot of $R$ vs $p$}
+    \label{fig:vsp}
+\end{figure}
+
+Performing the standard 3D-rotation matrix 
+\begin{equation}
+\begin{pmatrix}
+\sin{\theta}\cos{\varphi} & \sin{\theta}\sin{\varphi} & \cos{\theta}\\
+\cos{\theta}\cos{\varphi} & \cos{\theta}\sin{\varphi} & -\sin{\theta}\\
+-\sin{\varphi} & \cos{\varphi} & 0
+\end{pmatrix}
+\end{equation}
+on $H$ to get $H'$ leaves $\phi$ unaffected.
+
+\null\newpage
+\null\newpage
 \section{Outlook and open questions}
@@
 \subsection{Dropping pre/post-processing of the magic states}
+\label{app:cliff_processing}
+
 If we drop the freedom to transform them magic states via Clifford unitaries that depend on the reference states $\tau$ and $\tau'$, then the analysis just presented gets a little more complex, since the largest component in the rescaled distribution depends on a number of factors.

### 2021-05-13 magic_paper.tex
Corrections and tidying in appendices. Will work on appendix section on LC in unital fragments next where notation is hard to read

@@
 \begin{document}
-% Write bounds as 1 + ln{}/{} or 1 - (-ln{})/{} ?
-% Labels and Refs (theorems vs lemmas vs propositions)
-% R: rate vs bound ?
-% Appendices: clean-up
+% Labels and Refs (consistency, thm vs lem vs prop)
 % Figs check(fig.0, move to app, consistency)
 
-% Notation consistency
+% Notation consistency (R is rate not bound, ket vs |> etc, \ln{} -> \ln ,)
 % UK vs US english
@@
     }
-    \label{fig:zoo}
+    \label{fig:sketch}
 \end{figure}
@@
 \begin{proposition}\label{thm:wstate}
-  The Wigner distribution of a state $\rho \in \cal{B}(\cal{H}_d)$ is
+  The state Wigner distribution is
   \begin{enumerate}
-    \item[(i)]\label{en:w1} Real valued: $\W{\rho} \in \mathbb{R}^{d^2}$;
+    \item[(i)]\label{en:w1} Real valued: $\W{\rho}(\bmx) \in \mathbb{R}^{d^2}$;
     \item[(ii)]\label{en:w2} Normalised: $\sum_{\bmz \in \cal{P}_d} \W[\bmz]{\rho}=1$;
@@
         \item[(iii)]\label{en:wo3} Bounded: $\abs{\W[\bmy|\bmx]{\E}} \leq \frac{d_A}{d_B}$;
-	    \item[(iv)]\label{en:wo4} $\W[\bmy]{\E(\rho)} = \sum_{\bmz \in \cal{P}_{d_A}} \W[\bmy|\bmz]{\E} \W[\bmz]{\rho}$ for any $\bmy \in \cal{P}_{d_B}$.
+	    \item[(iv)]\label{en:wo4} $\W[\bmy]{\E(\rho)} = \sum\limits_{\bmz \in \cal{P}_{d_{A}}} \W[\bmy|\bmz]{\E} \W[\bmz]{\rho}$ for any $\bmy \in \cal{P}_{d_B}$.
     \end{enumerate}
@@
 
-We now give the following equivalent formulations of $d$--majorization.
+We now give the following equivalent formulations of relative majorization.
 
@@
 \end{proposition}
-The proofs for these can be found in~\cite{cit:marshall,cit:bhatia,cit:nielsen,cit:lostaglio} and references therein.
+The proofs for these can be found in~\cite{cit:marshall,ruch_mixing_1978,Renes_2016,Buscemi_2017} and references therein.
 
@@
 \begin{equation}
-	W_{\rho| \tau} (\x) := \frac{W_\rho (\x) }{ W_\tau(\x)},
+	W_{\rho|\tau}(\x) := \frac{W_\rho (\x) }{ W_\tau(\x)},
 \end{equation}
@@
 \end{proposition}
-\begin{proof} This follows from the definitions. 
+\begin{proof} This follows from the multiplicativity of the Wigner distribution. 
 \begin{align}
@@
 
-\begin{theorem*}
+We now prove the following result, which was stated in~\cref{sec:monotones_frag}.
+
+\begingroup
+\def\thetheorem{\ref{lem:lcmax}}
+\begin{theorem}
 	Given a magic state $\rho$, the maximum $L_\star$ of its Lorenz curve $\lc{\rho}{\sigma}(x)$ is independent of the $\sigma$--fragment and equal to $1+\sn{\rho}$.
 Moreover, the majorization constraint is stronger than mana in every fragment.
-\end{theorem*}
+\end{theorem}
+\addtocounter{theorem}{-1}
+\endgroup
 \begin{proof}
-	We denote the Wigner distributions of the states single-component vectors $\w(\rho)=W_\rho(x)$ and $ \w(\sigma)=W_\sigma(x)$. Likewise, we define
-	\begin{equation}
-\w(\rho|\sigma) = \frac{W_\rho (\x)}{W_{\sigma}(\x)}.
-\end{equation}
+	We denote the Wigner distributions of the states single-component vectors $\w(\rho)=W_\rho(x)$ and $ \w(\sigma)=W_\sigma(x)$. Likewise, we write $\w(\rho|\sigma) = W_{\rho|\tau}(\x)$.
 	We choose the component indexing so that $\w(\rho|\sigma)^\downarrow = \w(\rho|\sigma)=:\tilde{\w}$ and so the components are sorted in non-increasing order.
 
-Note that all components of $\bmw(\sigma)$ are positive, so $\widetilde{w}_i \geq 0$ if and only if $w(\rho)_i \geq 0$ for any $i=1,\dots,d^2$.
+Note that all components of $\bmw(\sigma)$ are positive, so $w(\rho|\sigma)_i \geq 0$ if and only if $w(\rho)_i \geq 0$ for any $i=1,\dots,d^2$.
 
@@
 	L_\star &:=	\lc{\rho}{\sigma}(x_{i_\star}) 
-		= \sum\limits_{\bmx: \W[\bmx]{\rho} \geq 0} \W[\bmx]{\rho} \nonumber \\
+		= \sum\limits_{\bmx: \W[\bmx]{\rho} \geq 0}\hspace{-5pt} \W[\bmx]{\rho} \nonumber \\
 		&= 1 + \sn{\rho}.
@@
 
-\section{Technical properties of $\sigma$--fragments}
+\section{Technical properties of Lorenz curves and $\sigma$--fragments}
 \label{app:frag}
 
-In this section, we discuss some technical aspects of general $\sigma$--fragments.
-
-We first prove a result on the independence of the Lorenz curve constraints, stated in~\cref{sec:major_frag}.
-\begin{proposition}\label{thm:elbows}
-	Let $\rho, \tau$ be two quantum states with Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in the $\sigma$--fragment.
-
-	Let $t$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ at locations $x_1, \dots, x_t$.
-
-	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\tau}{\sigma}(x_{i})$ for all $i =1,\dots,t$.
+\subsection{First elbow constraints}
+\label{app:elb_constraints}
+Here we prove a simple majorization constraint, arising by considering only the ascending part of the Lorenz curves between the origin $(0,0)$ and the first elbow.
+\begin{proposition}\label{prop:first_elb}
+	Consider a magic state process $\rho \longrightarrow \rho'$ with input and output Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\rho'}{\sigma'}(x)$ and denote the coordinates of the first elbow of $L_{\rho|\sigma}(x)$ by $(X_0, L_0)$ and the coordinates of the first elbow of $L_{\rho' |\sigma'}(x)$ by $(X'_0, L'_0)$.
+
+Then, given any coordinates $(x, L)$ and $(x', L')$ of the input and output Lorenz curves respectively, where $0 < x \leq X_0$ and $0 < x' \leq X'_0$, the process is possible only if
+\begin{equation}\label{eq:first_elb_bound1}
+	\frac{L}{x} \geq \frac{L'}{x'}.
+\end{equation}
 \end{proposition}
 \begin{proof}
-	$\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ trivially implies $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\tau}{\sigma}(x_{i})$ for all $i = 1,\dots,n'$.
-
-	Conversely, assume that $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\tau}{\sigma}(x_{i})$ for all $i = 1,\dots,r$.
-	First, let $x_0 = 0$ and $x_{n'+1} = 1$, so that $\lc{\rho}{\sigma}(x_0) = \lc{\tau}{\sigma}(x_0) = 0$ and $\lc{\rho}{\sigma}(x_{n'+1}) = \lc{\tau}{\sigma}(x_{n'+1}) = 1$.
+Since both pairs of coordinates are located between $(0,0)$ and the first elbow of their respective curves, we can derive the bound via a simple interpolation on the line segment connecting the origin and the appropriate pair of coordinates.
+
+First assume that $x < x'$.
+Then, point $(x, L_{\rho'|\sigma'}(x))$ lies on the lines segment connecting $(0,0)$ and $(x', L')$, so by interpolating between points $(0,0)$ and $(x', L')$, we find that
+\begin{equation}
+	L_{\rho'|\sigma'}(x) = \frac{x}{x'}L'.
+\end{equation}
+Considering the Lorenz curve constraint at $x$, the process is possible only if 
+\begin{equation}
+	L = \lc{\rho}{\sigma}(x) \geq \lc{\rho'}{\sigma'}(x) = \frac{x}{x'}L',
+\end{equation}
+which is a rearrangement of~\cref{eq:first_elb_bound1}.
+
+If instead, $x \geq x'$, the point $(x', L_{\rho|\sigma}(x'))$ lies on the lines segment connecting $(0,0)$ and $(x, L)$, so by interpolating between points $(0,0)$ and $(x, L)$, we find that
+\begin{equation}
+	L_{\rho|\sigma}(x') = \frac{x'}{x}L.
+\end{equation}
+Considering the Lorenz curve constraint at $x'$, the process is possible only if 
+\begin{equation}
+	\frac{x'}{x}L = \lc{\rho}{\sigma}(x') \geq \lc{\rho'}{\sigma'}(x) = L',
+\end{equation}
+which is again a rearrangement of~\cref{eq:first_elb_bound1}.
+\end{proof}
+
+\subsection{Component-multiplicity pairs}
+\label{app:cmpairs}
+
+In general, a $1$--copy $d$--dimensional state $\rho$ is described by its $d^2$--dimensional Wigner distribution $\W{\rho}(\bmx)$. 
+The distribution $\W{\rho}(\bmx)$ is defined on the phase space, but it can be convenient to re-express this using vector notation.
+
+To each Wigner distribution $W_\rho(\x)$ we can associate \emph{component-multiplicity} pairs $\{(w_i, m_i)\}$ where the value $w_i$ occurs in the distribution $W_\rho(\x)$ with multiplicity $m_i$.
+
+As an example, for the Strange state with
+\begin{equation}
+W_{\rho_S}(\x) = (-1/3, 1/6,  1/6,  1/6,  1/6,  1/6,  1/6,  1/6,  1/6)
+\end{equation}
+we have the component-multiplicity pairs: $\{( -1/3, 1), ( 1/6, 8)\}$.
+However, we might also wish more freedom and not require that the different $w_i$ values are all distinct.
+For example, the component-multiplity pairs $\{(-1/3, 1), (1/6, 2), (1/6, 3), (1/6, 3)\}$ also describe $W_{\rho_S}(\x)$.
+
+This representation is more compact when a Wigner distribution has a lot of multiplicities, and allows for simple handling of multiple copies via the following fact.
+\begin{lemma}
+Consider two Wigner distributions $\W{\rho_A}, \W{\rho_B}$ with component-multiplicity pairs 
+\begin{equation}
+	\{(w_i, m_i)\} \text{ and } \{(w_j', m_j')\},
+\end{equation}
+respectively. Then, $\{(w_i w_j', m_i m_j')\}$ gives component-multiplicity pairs for $\W{\rho_A \otimes \rho_B}$.
+\end{lemma}
+
+This is true because all components of $\W{\rho_A \otimes \rho_B}$ are of the form $w_i w_j'$ and 
+\begin{equation*}
+	\sum_{i=1}^{D_A}\sum_{j=1}^{D_B} m_i m_j' = \sum_{i=1}^{D_A} m_i \sum_{j=1}^{D_B} m_j' = d_A^2 d_B^2,
+\end{equation*}
+so the set $\{(w_i w_j', m_i m_j')\}$ contains exactly the Wigner components of $\W{\rho_A \otimes \rho_B}$ and no more.
+
+In the case of distillation protocols, we are interested in $n$--copies of a single Wigner distribution. For this, we have the following result, which follows from combinatorics.
+
+\begin{lemma}\label{ncopy_components}
+	Suppose $W_\rho(\x)$ has $D$ component-multiplicity pairs $\{(w_i, m_i)\}$.
+Then, $W_{\rho^{\otimes n}} (\x)$ has component-multiplicity pairs $\{(W_{\q}, M_{\q})\}$, where $\q$ runs through all $K$-component vectors with non-negative integer components that sum to $n$, and
+\begin{align}
+W_{\q} &= \prod_{i=1}^D w_i^{q_i} \label{eq:W}\\
+M_{\q} &= \binom{n}{q_1,q_2, \dots, q_d} \prod_{i=1}^D m_i^{q_i}, \label{eq:M}
+\end{align}
+where the term outside the product in the expression for $M_{\q}$ is the generalized binomial coefficient.
+\end{lemma}
+\begin{proof}
+	Denote by $C_D^n \coloneqq \{\bmk\}$ the set of all vectors $\bmk \coloneqq (k_1, \dots, k_D)$ with non-negative integer components that sum to $n$, i.e.
+	\begin{equation*}
+	0 \leq k_1, \dots, k_D \leq n \text{ and } k_1 + \dots + k_D = n.
+	\end{equation*}
+
+	We proceed by induction.	
+	Assume $n = 1$ and let $\bmk_i$ be the vector with its $i$-th component equal to 1 and 0's elsewhere.
+	The set $C_D^1$ consists of all vectors of this form, i.e. 
+\begin{equation*}
+	C_D^1 = \{ \bmk_i \}_{i=1,\dots,D}
+\end{equation*}
+	It is also true by direct calculation that
+\begin{equation*}
+	\left( W_{\bmk_i}, M_{\bmk_i} \right) = (w_i, m_i).
+\end{equation*}
+Therefore, $\{ (W_{\bmk}, M_{\bmk}) \}_{\bmk \in C_D^1}$ is a complete set of component-multiplicity pairs for $W$.
+
+	Assume that $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$ as given in~\cref{eq:M,eq:W} is a complete set of component-multiplicity pairs for the $n$--copy distribution $W^{\otimes n}$.
+	By construction, the distribution $W^{\otimes (n+1)} = W^{\otimes n} \otimes W$ is multiplicative, so it admits the complete set of component multiplicity pairs
+\begin{equation}
+	\{(W_{\bmk} w_i, M_{\bmk} m_i)\},\ \bmk \in C_D^n \text{ and } i=1,\dots,D.
+\end{equation}
+
+	Consider the component sum of the distribution $W^{\otimes (n+1)}$,
+\begin{align*}
+	&\sum_{\bmk \in C_D^n}\sum_{i=1}^D M_{\bmk} m_i W_{\bmk} w_i = \sum_{\bmk \in C_D^n} M_{\bmk}W_{\bmk} \sum_{i=1}^D m_i w_i =\\
+	&\sum_{\bmk \in C_D^n} \frac{n!}{k_1!\dots k_D!} \prod\limits_{i=1}^D {m_i}^{k_i}{w_i}^{k_i} \sum_{i=1}^D m_i w_i =\\
+	&\left( \sum_{i=1}^D m_i w_i \right)^n \left( \sum_{i=1}^D m_i w_i \right) = \left( \sum_{i=1}^D m_i w_i \right)^{n+1} =\\
+	&\sum_{\bmq \in C_D^{n+1}} M_{\bmq}W_{\bmq},
+\end{align*}
+where in the last expression, vectors $\bmq = (q_1, \dots, q_D)$ have non-negative integer components that sum to $(n+1)$ and 
+\begin{align*}
+	M_{\bmq} &= \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i},\\
+	W_{\bmq} &= \prod\limits_{i=1}^D {w_i}^{q_i}.
+\end{align*}
+We have used the multinomial theorem to proceed between lines 2-3 and lines 3-4 of the derivation.
+
+We have achieved a regrouping of the distribution components.
+Every component $W_{\bmq}$ is of the form $W_{\bmk} w_i$ with $q_i = k_i + 1$ and $q_j = k_j$ for $j\neq i$ and 
+\begin{align*}
+	\sum_{\bmq \in C_D^{n+1}}  \hspace{-6pt} M_{\bmq} =  \hspace{-10pt} \sum_{\bmq \in C_D^{n+1}} \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i} = 
+	\left( \sum_{i=1}^D m_i \right)^{n+1} \hspace{-10pt} = d^{n+1},
+\end{align*}
+which is the dimension of $W^{\otimes (n+1)}$.
+
+Therefore, $\{ (W_{\bmq}, M_{\bmq}) \}_{\bmq \in C_D^{n+1}}$ contains exactly the components of $W^{\otimes n}$ and no more, completing the proof.
+\end{proof}
+
+The rescaled distribution is also multiplicative, so a set of component-multiplicity pairs can be obtained for the $n$-copy rescaled distribution in the same fashion as for usual Wigner distributions.
+
+\subsection{Lorenz curve constraint independence}
+
+We now prove a result on the independence of the Lorenz curve constraints, stated in~\cref{sec:major_frag}.
+\begin{proposition}\label{thm:elbows}
+	Let $\rho, \rho'$ be two quantum states with Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\rho'}{\sigma'}(x)$ in the $\sigma$--fragment.
+
+	Let $t$ be the number of elbows of $\lc{\rho'}{\sigma'}(x)$ at locations $x_1, \dots, x_t$.
+
+	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\rho'}{\sigma'}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\rho'}{\sigma'}(x_{i})$ for all $i =1,\dots,t$.
+\end{proposition}
+\begin{proof}	
+	$\lc{\rho}{\sigma}(x) \geq \lc{\rho'}{\sigma'}(x)$ for all $x \in [0,1]$ trivially implies $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\rho'}{\sigma'}(x_{i})$ for all $i = 1,\dots,n'$.
+
+	Conversely, assume that $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\rho'}{\sigma'}(x_{i})$ for all $i = 1,\dots,r$.
+	First, let $x_0 = 0$ and $x_{n'+1} = 1$, so that $\lc{\rho}{\sigma}(x_0) = \lc{\rho'}{\sigma'}(x_0) = 0$ and $\lc{\rho}{\sigma}(x_{n'+1}) = \lc{\rho'}{\sigma'}(x_{n'+1}) = 1$.
 	Hence, we can extend the set of elbows $E$ to $E' = E \cup \{x_0, x_{n'+1}\}$.
 
-	Pick two consecutive locations $x_{i}, x_{i+1}$ in $E'$ and consider the line segment $\ell_\tau(x)$ connecting points $(x_{i}, \lc{\tau}{\sigma}(x_{i}))$ and $(x_{i+1}, \lc{\tau}{\sigma}(x_{i+1}))$ as well as the line segment $\ell_\rho(x)$ connecting points $(x_{i}, \lc{\rho}{\sigma}(x_{i}))$ and $(x_{i+1}, \lc{\rho}{\sigma}(x_{i+1}))$.
+	Pick two consecutive locations $x_{i}, x_{i+1}$ in $E'$ and consider the line segment $\ell_\rho'(x)$ connecting points $(x_{i}, \lc{\rho'}{\sigma'}(x_{i}))$ and $(x_{i+1}, \lc{\rho'}{\sigma'}(x_{i+1}))$ as well as the line segment $\ell_\rho(x)$ connecting points $(x_{i}, \lc{\rho}{\sigma}(x_{i}))$ and $(x_{i+1}, \lc{\rho}{\sigma}(x_{i+1}))$.
 	This is illustrated in~\cref{fig:elbows_proof}.
@@
 
-	Due to concavity of $\lc{\rho}{\sigma}$, it is clear that for all $x \in [x_{i}, x_{i+1}]$, we have $\lc{\rho}{\sigma}(x) \geq \ell_\rho(x) \geq \ell_\tau(x) = \lc{\tau}{\sigma}(x)$.
+	Due to concavity of $\lc{\rho}{\sigma}$, it is clear that for all $x \in [x_{i}, x_{i+1}]$, we have $\lc{\rho}{\sigma}(x) \geq \ell_\rho(x) \geq \ell_\rho'(x) = \lc{\rho'}{\sigma}(x)$.
 	This argument can be made in all intervals $[x_{i}, x_{i+1}]$ with $i=0,\dots,n'$, so the proof is complete.
@@
 The above theorem can be used in reducing the necessary distillation constraints derived via majorization in $\sigma$--fragments.
+
+\subsection{Technical properties of $\sigma$--fragments}
 
@@
 Consider an experiment consisting of $n$ trials of throwing a $p$--coin, that is a coin with probability $p$ of landing on one side and $1-p$ of landing on the other.
-We express the sums over an even number $m$ of successful trials $\Phi_+$ and an odd number $m$ of successful trials $\Phi_-$, and so these are given by
+We denote the sums over an even number $m$ of successful trials by $\Phi_+(m; n, p)$ and an odd number $m$ of successful trials by $\Phi_-(m; n, p)$, and they are given by
 \begin{align}	
@@
 The proof provided in~\cite{cit:ash} proceeds with direct calculation for the edge cases $\ell = 1,2, n-1, n-2$ and use Stirling's approximation for the remaining cases.
+
 We can use~\cref{lem:comb_bounds} to provide strict upper and lower bounds on the functions $\Phi_+, \Phi_-$.
@@
 \subsection{Theory on bounding the core functions}
-\nick{Should we really keep this section?
-It is standard calculus and the bounds are really loose.} \ddd{[Depends on what you want to do with them - we want people to build on our work, and so providing them some starter-tools is potentially valuable hints.
-Closed, weak bounds can be very useful.]}
 Here we present a more manageable method of bounding the core functions $\Phi_{\pm}$, which however results in looser bounds. 
@@
 	 &\binom{n}{m+1} (1-a)^{n-m-1} \text{ and} \\
-	2\Phi_+(m; n, a) \geq\ &\Phi(m; n, a) + (1-a)^n - \frac{(-a)^{m+1}}{m!} \binom{n}{m+1} .
+	2\Phi_+(m; n, a) \geq\ &\Phi(m; n, a) + (1-a)^n - \frac{(-a)^{m+1}}{m!}  \times \nonumber\\
+	 &\binom{n}{m+1} .
 \end{align}
@@
 
-The Wigner distribution of the $n$--copy $\epsilon$--noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ in the unital fragment is given by $\W{\rho_{\rm{S}}(\epsilon)^{\otimes n}} = W_{\rho_{\rm{S}}(\epsilon)}^{\otimes n}$.
-In general, $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ contains $n + 1$ distinct components, labelled $0,\dots, n$ \ddd{[What does this mean??]}.
+The Wigner distribution of the $n$--copy $\epsilon$--noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ is given by $\W{\rho_{\rm{S}}(\epsilon)^{\otimes n}} = W_{\rho_{\rm{S}}(\epsilon)}^{\otimes n}$ and, in the unital fragment, it corresponds to the set $\{(w_i, m_i)\}_{i=0,\dots,n}$ of component-multiplicity pairs.
 
@@
   \begin{tabular}{c|c|c|r|r}
-    \multicolumn{3}{c|}{Case} & \multicolumn{1}{c}{$m_{i}(n, \epsilon)$} & \multicolumn{1}{|c}{$w_{i}(n, \epsilon)$} \\[0.5ex]\hline
-    \multirow{4}{*}{\raisebox{-4ex}{\rotatebox[origin=c]{90}{$0\leq \epsilon < \frac{3}{7}$}}} & \hspace{0.8ex}\multirow{2}{*}{\raisebox{-1ex}{\rotatebox[origin=c]{90}{$n$ even}}}\hspace{0.8ex} & LHS & $8^{2i}\binom{n}{2i}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2i}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{n-2i}$ \\
-    & & RHS & $8^{n-2i}\binom{n}{2i}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{n-2i}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2i}$ \\ \cline{2-5}
-    & \multirow{2}{*}{\raisebox{-2ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $8^{2i+1}\binom{n}{2i+1}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2i+1}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{n-2i-1}$ \\
+    \multicolumn{3}{c|}{Case} & \multicolumn{1}{c}{$m_{i}$} & \multicolumn{1}{|c}{$w_{i}$} \\[0.5ex]\hline
+    \multirow{4}{*}{\raisebox{-4ex}{\rotatebox[origin=c]{90}{$0\leq \epsilon < \frac{3}{7}$}}} & \hspace{0.8ex}\multirow{2}{*}{\raisebox{-1ex}{\rotatebox[origin=c]{90}{$n$ even}}}\hspace{0.8ex} & LHS & $8^{2i}\binom{n}{2i}$ & $u(\epsilon)^{2i}v(\epsilon)^{n-2i}$ \\
+    & & RHS & $8^{n-2i}\binom{n}{2i}$ & $-u(\epsilon)^{n-2i}v(\epsilon)^{2i}$ \\ \cline{2-5}
+    & \multirow{2}{*}{\raisebox{-2ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $8^{2i+1}\binom{n}{2i+1}$ & $u(\epsilon)^{2i+1}\left( -v(\epsilon) \right)^{n-2i-1}$ \\
     & & RHS & $8^{n-2i-1}\binom{n}{2i+1}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{n-2i-1}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2i+1}$ \\ \hline
@@
 Can you give clear definitions in the text?]}
+\nick{Working on it.
+I agree that in this section, notation is tough.
+$w_i$ are the Wigner components of $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ that come out of~\cref{ncopy_components}.
+They may not be distinct in some rare cases, i.e.
+when $\epsilon=3/7$ or accidentally.}
 
   \ddd{[Also what does ``Multiplication $2i$ is considered modulo $(n+1)$'' mean???]}
+  \nick{It means $2i \pmod{n+1}$, so that e.g. $2n\pmod{n+1}=2n - (n+1) = n-1$}
   \label{tab:lcsu}
@@
 
-\section{Technical details for the derivation of distillation bounds from Lorenz curves}
+\section{Details for the derivation of distillation bounds from Lorenz curves}
 \label{app:lcst_technical}
 
-\subsection{First and last elbow constraints}
-\label{app:elb_constraints}
-Here we prove two simple majorization constraints, one arising by considering only the ascending part of the Lorenz curves between the origin $(0,0)$ and the first elbow and the other by considering only the descending part of the curves between the last elbow and the endpoint $(1,1)$.
-\begin{proposition}\label{prop:first_elb}
-	Consider a magic state process $\rho \longrightarrow \rho'$ with input and output Lorenz curves $\lc{\rho}{\tau}(x), \lc{\rho'}{\tau}(x)$ in $\R_\tau$ and denote the coordinates of the first elbow of $L_{\rho|\tau}(x)$ by $(X_0, L_0)$ and the coordinates of the first elbow of $L_{\rho' |\tau}(x)$ by $(X'_0, L'_0)$.
-	Then the process is possible in $\R_\tau$ only if
-\begin{equation}\label{eq:first_elb_bound1}
-	\frac{L_0}{x} \geq \frac{L_0'}{x'}.
-\end{equation}
-for all $x \leq X_0$ and $x' \leq X'_0$.
-\end{proposition}
-\begin{proof}
-Since both pairs of coordinates are located between $(0,0)$ and the first elbow of their respective curves, we can derive the bound via a simple interpolation on the line segment connecting the origin and the appropriate first elbow.
-
-First assume that $x < x'$ and consider the Lorenz curve constraint,
-\begin{equation}
-	\lc{\rho}{\tau}(x) \geq \lc{\rho'}{\tau}(x).
-\end{equation}
-We can find the output state Lorenz curve coordinate $L_{\rho'|\tau}(x)$ by interpolating between the origin and the output state's first elbow, 
-\begin{equation}
-	L_{\rho'|\tau}(x) = \frac{x}{x'}L_0.
-\end{equation}
-\ddd{[Is this correct??
-I'm trying to simplify your notation and proof, but the above doesn't seem obvious.
-Needs fixing -- I've set up simple notation so we should only use this instead of defining all different variables that confuse things.]}The process is then possible only if $L_0 \geq L_\star'$ which is a rearrangement of~\cref{eq:first_elb_bound1}.
-\ddd{[This is not clear/obvious -- can you step through the steps explicitly.]}
-
-If instead, $x \geq x'$, consider the Lorenz curve constraint at $x = x'$,
-\begin{equation}
-	\lc{\rho}{\tau}(x') \geq \lc{\rho'}{\tau}(x').
-\end{equation}
-We now need to find the input state Lorenz curve coordinate $L_\star$ at location $x = x'_0$ by interpolating between the origin and the input state's first elbow, 
-\begin{equation}
-	L_\star = \frac{x'_0}{x_0}L_0.
-\end{equation}
-The process is then possible only if $L_\star \geq L'_0$ which is again a rearrangement of~\cref{eq:first_elb_bound1}.
-\end{proof}
-
-\begin{proposition}\label{prop:last_elb}
-	Consider a magic state process $\rho \longrightarrow \tau$ with input and output Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in $\R_\sigma$ and denote by $X_E, X'_E$ the last elbow locations of the input and output curves respectively.
-
-	Then, given any coordinates $(x_E, L_E)$ and $(x'_E, L'_E)$ on the input and output Lorenz curves, where $x_E \geq X_E$ and $x'_E \geq X'_E$, the process is possible in $\R_\sigma$ only if
-\begin{equation}\label{eq:last_elb_bound1}
-	\frac{L_E - 1}{1-x_E} \geq \frac{L'_E - 1}{1-x_E'}.
-\end{equation}
-\end{proposition}
-\begin{proof}
-Since both pairs of coordinates are located between the last elbow of their respective curves and $(1,1)$, we can derive the bound via a simple interpolation on the line segment connecting the endpoint and the appropriate last elbow.
-
-First assume that $x_E > x'_E$ and consider the Lorenz curve constraint at $x = x_E$,
-\begin{equation}
-	\lc{\rho}{\sigma}(x_E) \geq \lc{\tau}{\sigma}(x_E).
-\end{equation} 
-We can find the output state Lorenz curve coordinate $L'_\star$ at location $x = x_E$ by interpolating between the endpoint $(1,1)$ and the output state's last elbow, 
-\begin{equation}
-	L'_\star = 1 + \frac{1-x_E}{1-x'_E} (L'_E - 1)
-\end{equation}
-The process is then possible only if $L_E \geq L_\star'$ which is a rearrangement of~\cref{eq:last_elb_bound1}.
-
-If instead, $x_E \leq x'_E$, consider the Lorenz curve constraint at $x = x'_E$,
-\begin{equation}
-	\lc{\rho}{\sigma}(x'_E) \geq \lc{\tau}{\sigma}(x'_E).
-\end{equation} 
-We now need to find the input state Lorenz curve coordinate $L_\star$ at location $x = x'_E$ by interpolating between the endpoint $(1,1)$ and the input state's last elbow, 
-\begin{equation}
-	L_\star = 1 + \frac{1-x'_E}{1-x_E} (L_E - 1).
-\end{equation}
-The process is then possible only if $L_\star \geq L'_E$ which is again a rearrangement of~\cref{eq:last_elb_bound1}.
-\end{proof}
-
-\subsection{Component-multiplicity pairs}
-\label{app:cmpairs}
-
-In general, a $1$--copy $d$--dimensional state $\rho$ is described by its $d^2$--dimensional Wigner distribution $\W{\rho}$. 
-The distribution $\W{\rho}$ is defined on the phase space, but it can be convenient to re-express this using vector notation.
-
-To each Wigner distribution $W_\rho(\x)$ we can define \emph{component-multiplicity} pairs $\{(w_i, m_i)\}$ where the value $w_i$ occurs in the distribution $W_\rho(\x)$ with multiplicity $m_i$.
-
-As an example, for the Strange state with
-\begin{equation}
-W_{\rho_S}(\x) = (-1/3, 1/6,  1/6,  1/6,  1/6,  1/6,  1/6,  1/6,  1/6)
-\end{equation}
-we have the component-multiplicity pairs: $\{( -1/3, 1), ( 1/6, 8)\}$.
-However we might also wish more freedom and not require that the different $w_i$ values are all distinct.
-For example the component-multiplity pairs $\{(-1/3, 1), (1/6, 2), (1/6, 3), (1/6, 3)\}$ also describe $W_{\rho_S}(\x)$.
-
-This representation is more compact when a Wigner distribution has a lot of multiplicities, and allows for simple handling of multiple copies via the following fact.
-\begin{lemma}
-Consider two Wigner distributions $\W{\rho_A}, \W{\rho_B}$ with component-multiplicity pairs 
-\begin{equation}
-	\{(w_i, m_i)\} \text{ and } \{(w_j', m_j')\},
-\end{equation}
-respectively. Then $\{(w_i w_j', m_i m_j')\}$ gives component-multiplicity pairs for $\W{\rho_A \otimes \rho_B}$.
-\end{lemma}
-
-This is true because all components are of the form $w_i w_j'$ and 
-\begin{equation*}
-	\sum_{i=1}^{D_A}\sum_{j=1}^{D_B} m_i m_j' = \sum_{i=1}^{D_A} m_i \sum_{j=1}^{D_B} m_j' = d_A^2 d_B^2.
-\end{equation*}
-
-For distillation protocols we are interested in $n$--copies of a single Wigner distribution. For this we have the following, which follows from combinatorics.
-
-\begin{lemma} Suppose $W_\rho(\x)$ has $K$ component-multiplicity pairs $\{(w_i, m_i)\}$.
-Then $W_{\rho^{\otimes n}} (\x)$ has component-multiplicity pairs $\{(w_{\q}, m_{\q})\}$, where $\q$ is a $K$ component vector of non-negative integers that sum to $n$, and
-\begin{align}
-w_{\q} &= \prod_{i=1}^K w_i^{q_i} \\
-m_{\q} &= \binom{n}{q_1,q_2, \dots, q_K} \prod_{i=1}^K m_i^{q_i},
-\end{align}
-where the first term in the expression for $m_{\q}$ is the generalized binomial coefficient.
-\end{lemma}
-
-Note that the rescaled distribution is also multiplicative, so a complete set of component-multiplicity pairs can be obtained for this distribution in the same fashion as for usual Wigner distributions.
-
-Given a state $\rho$ and a complete set of component-multiplicity pairs describing its Wigner distribution $\W{\rho}$, we now provide a method of computing the components (and multiplicities) of the $n$--copy distribution $\W{\rho}^{\otimes n}$.
-\begin{lemma}\label{lem:ncopycomponents}
-	Let $W$ be a distribution defined by a complete set of component-multiplicity pairs $\{(w_i, m_i)\}_{i=1,\dots,D}$ with $D \leq {\rm{dim}}\hspace{1pt}W$ and consider the distribution $W^{\otimes n}$ obtained by the $n$-fold (Kronecker) product $W \otimes \dots \otimes W$ between $n$ copies of $W$.
-
-	Denote by $C_D^n \coloneqq \{\bmk\}$ the set of all vectors $\bmk \coloneqq (k_1, \dots, k_D)$ with non-negative integer components that sum to $n$, i.e.
-	\begin{equation*}
-	0 \leq k_1, \dots, k_D \leq n \text{ and } k_1 + \dots + k_D = n.
-	\end{equation*}
-
-	Then, $W^{\otimes n}$ admits a complete set of component-multiplicity pairs $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$, where
-\begin{align}
-	M_{\bmk} &= \frac{n!}{k_1!\dots k_D!} \prod\limits_{i=1}^D {m_i}^{k_i}, \label{eq:M}\\
-	W_{\bmk} &= \prod\limits_{i=1}^D {w_i}^{k_i}. \label{eq:W}
-\end{align}
-\end{lemma}
-\begin{proof}
-	We proceed by induction.
-
-	Assume $n = 1$.
-	Let $\bmk_i$ be the vector with its $i$-th component equal to 1 and 0's elsewhere.
-	The set $C_D^1$ consists of all vectors of this form, i.e. 
-\begin{equation*}
-	C_D^1 = \{ \bmk_i \}_{i=1,\dots,D}
-\end{equation*}
-	It is also true by direct calculation that
-\begin{equation*}
-	\left( W_{\bmk_i}, M_{\bmk_i} \right) = (w_i, m_i).
-\end{equation*}
-Therefore, $\{ (W_{\bmk}, M_{\bmk}) \}_{\bmk \in C_D^1}$ is a complete set of component-multiplicity pairs for $W$.
-
-	Assume that $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$ as given in~\cref{eq:M,eq:W} is a complete set of component-multiplicity pairs for the $n$--copy distribution $W^{\otimes n}$.
-	By construction, the distribution $W^{\otimes (n+1)} = W^{\otimes n} \otimes W$ is multiplicative, so it admits the complete set of component multiplicity pairs
-\begin{equation}
-	\{(W_{\bmk} w_i, M_{\bmk} m_i)\},\ \bmk \in C_D^n \text{ and } i=1,\dots,D.
-\end{equation}
-
-	Consider the component sum of the distribution $W^{\otimes (n+1)}$,
-\begin{align*}
-	&\sum_{\bmk \in C_D^n}\sum_{i=1}^D M_{\bmk} m_i W_{\bmk} w_i = \sum_{\bmk \in C_D^n} M_{\bmk}W_{\bmk} \sum_{i=1}^D m_i w_i =\\
-	&\sum_{\bmk \in C_D^n} \frac{n!}{k_1!\dots k_D!} \prod\limits_{i=1}^D {m_i}^{k_i}{w_i}^{k_i} \sum_{i=1}^D m_i w_i =\\
-	&\left( \sum_{i=1}^D m_i w_i \right)^n \left( \sum_{i=1}^D m_i w_i \right) = \left( \sum_{i=1}^D m_i w_i \right)^{n+1} =\\
-	&\sum_{\bmq \in C_D^{n+1}} M_{\bmq}W_{\bmq},
-\end{align*}
-where in the last expression, vectors $\bmq = (q_1, \dots, q_D)$ have non-negative integer components that sum to $(n+1)$ and 
-\begin{align*}
-	M_{\bmq} &= \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i},\\
-	W_{\bmq} &= \prod\limits_{i=1}^D {w_i}^{q_i}.
-\end{align*}
-We have used the multinomial theorem to proceed between lines 2-3 and lines 3-4 of the derivation.
-
-We have achieved a regrouping of the distribution components.
-Every component $W_{\bmq}$ is of the form $W_{\bmk} w_i$ with $q_i = k_i + 1$ and $q_j = k_j$ for $j\neq i$ and 
-\begin{align*}
-	\sum_{\bmq \in C_D^{n+1}}  \hspace{-6pt} M_{\bmq} =  \hspace{-10pt} \sum_{\bmq \in C_D^{n+1}} \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i} = 
-	\left( \sum_{i=1}^D m_i \right)^{n+1} \hspace{-10pt} = d^{n+1},
-\end{align*}
-which is the dimension of $W^{\otimes (n+1)}$.
-
-Therefore, $\{ (W_{\bmq}, M_{\bmq}) \}_{\bmq \in C_D^{n+1}}$ is a complete set of component-multiplicity pairs for $W^{\otimes n}$, completing the proof.
-\end{proof}
-
-\newpage
 \subsection{Free energy dependent magic distillation bounds}\label{free-energy-bound-proof}
@@
 If the largest rescaled component of a state is distinct with no multiplicities, then these coordinates correspond to the first elbow of the corresponding Lorenz curve, whereas if it appears multiple times, then the coordinates derived correspond to a point on the interior of the line segment connecting the origin to the first elbow.
-In both cases, the distillation bound remains the same, as is clear by its derivation in~\cref{app:elb_constraints}, and it is given by $L_0 / x_0 \geq L'_0 / x'_0$, which can be directly rearranged into the stated bound of the theorem \ddd{[Expand this last bit and show it explicitly -- don't skip lines in a proof, even if they seem obvious.]}.
+In both cases, the distillation bound remains the same, as is clear by its derivation in~\cref{app:elb_constraints}, given by $L_0/x_0 \geq L'_0/x'_0$, leading to
+\begin{equation}
+	\left( 3v(\epsilon)e^{-\beta (F - \phi)} \right)^{n} = \frac{L_0}{x_0}
+	\geq \frac{L'_0}{x'_0} = \left( 3v(\epsilon')e^{-\beta (F' - \phi')} \right)^{m}.
+\end{equation}
+Taking the natural logarithm on both sides and rearranging gives the bound
+\begin{equation}
+	\frac{m}{n} \leq \dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (\phi - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (\phi' - F')},
+\end{equation}
+concluding the proof.
 \end{proof}
 
-The following lemma shows that if the energy eigenbasis is a stabilizer basis then things simplify more. \ddd{[To be checked]}
-\begin{lemma} If the Hamiltonian $H$ in the previous theorem has a stabilizer eigenbasis, then $\phi = E_{k_s} +kT\log 3$ for some $k_s \in \mathbb{Z}_3$.
-\end{lemma}
-\begin{proof}We first expand $\alpha_k$ as
-\begin{equation}
-\alpha_k = \<E_k | D_{\x_\star} A_{\mathbf{0}} D_{\x_\star}^\dagger |E_k\>.
-\end{equation}
-Since $\{|E_k\>\}$ forms an orthonormal basis, then so too does $\{|\psi_k\>:=D_{\x_\star}^\dagger|E_k\>\}$.
-This implies that in the Wigner representation the distributions $\{W_{\psi_k}(\x)\}$ have orthogonal supports and only one of them, $k=k_s$ say, has $\x=\mathbf{0}$ in its support.
-Therefore only the coefficient $\alpha_{k_s}$ is non-zero and so
-\begin{align}
-\phi &= -\beta^{-1}\log (\sum_k \alpha_k e^{-\beta E_k}) \nonumber \\
-&=E_{k_s} -kT \log W_{\psi_{k_s}}(\mathbf{0}) \nonumber \\
-&=E_{k_s} +kT \log 3,
-\end{align}
-where we use that $\psi_{k}$ are pure stabilizer states and so their non-zero Wigner components are $1/3$.
+The following result shows that if the energy eigenbasis is a stabilizer basis then things simplify more.
+\begin{proposition} 
+	Let $H$ be a Hamiltonian $H$ with spectrum $\{E_k\}_{k \in \mathbb{Z}_d}$.
+	If $H$ has a stabilizer eigenbasis, then $\phi = E_{k_{\star}}$ for some $k_{\star} \in \mathbb{Z}_d$.
+\end{proposition}
+\begin{proof}
+	We first write $\alpha_k$ as
+\begin{equation}
+	\alpha_k = \<E_k | A_{\bmx_{\star}} |E_k\> = d W_{\ketbra{E_k}}(\bmx_{\star})
+\end{equation}
+Since each $\ketbra{E_k}$ is a stabilizer state, their Wigner distributions have orthogonal supports in the phase space, so only one of them, say $k = k_{\star}$ contains point $\bmx_{\star}$ in its support.
+Additionally, its distribution is uniform on its support, so $W_{\ketbra{E_{k_{\star}}}}(\bmx_{\star}) = 1/d$.
+
+Therefore, only the coefficient $\alpha_{k_{\star}}$ is non-zero and
+\begin{align}
+\phi &= -\beta^{-1}\ln (\sum_k \alpha_k e^{-\beta E_k}) \nonumber \\
+&=E_{k_{\star}} -kT \ln (d W_{\ketbra{E_{k_{\star}}}}(\bmx_{\star})) =E_{k_{\star}}.
+\end{align}
 \end{proof}
-
-\subsection{Deriving distillation bounds from the last elbow}
-\label{sec:last_elb}
-
-Using a similar analysis, we can also derive upper bounds from comparison of the last point coordinates of the Lorenz curve, which now corresponds to the smallest rescaled component.
-
-To this end, assume that the largest component of the equilibrium state distribution is $W_{\tau}(i,j)$.
-We now perform the Clifford operation
-\begin{equation}
-	\tau \longrightarrow X^{1-i}Z^{-j}\ \tau\ Z^{j}X^{i-1},
-\end{equation}
-which permutes the largest component such that $W_{\tau}(i,j) \longrightarrow W_{\tau}(1,0)$.
-Since we have that $u \leq v$ because $\epsilon \leq 3/7$, and we have already ensured that $W_{\tau}(1,0) \geq W_{\tau}(\bmx)$ for all $\bmx \in \mathbb{Z}_3^2$.
-Therefore, the largest rescaled component occurs when $i_{(1,0)} = n$ and $i_{\bmx} = 0$ for $\bmx \neq \bmo$ and is equal to $(v/W_{\tau}(1,0))^n$.
-Accordingly, the coordinates of the first Lorenz curve point after the origin are given by $(x_E, L_E) = ((W_{\tau}(1,0))^n, u(\epsilon)^n)$ for the input state and $(x'_E, L'_E) = ((W_{\tau'}(1,0))^m, u(\epsilon')^m)$ for the output state.
-
-We now redefine the quantities $\alpha_k$, so that again $\phi = -\beta^{-1} \log \zeta$, where $\zeta= \sum_{k\in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}$ and $\alpha_k$ now given by
-\begin{align}
-	\alpha_k = \sum_{r \in \mathbb{Z}_3} \braket{E_k}{1-r}\braket{1+r}{E_k}.
-\end{align}
-This allows us to rewrite $W_{\tau}(1,0) = {e^{\beta (F - \phi)}}/{3}$ and by using the last elbow constraint 
-\begin{equation*}
-	\frac{L_E - 1}{1-x_E} \geq \frac{L'_E - 1}{1-x_E'},
-\end{equation*}
-derived in~\cref{app:elb_constraints}, we can get a new bound expression.
-
-We note that it is also possible to perform a different Clifford transformation and get a different location $(W_{\tau}(\bmx))^n$, with $\bmx \neq \bmo$, since components $(W_{\rho}(\bmx))^n = u$ are all the same as long as $\bmx \neq \bmo$.
-The effect of this is to alter the expressions for the quantities $\alpha_k$, but not the resulting bound expression.
-
-\nick{This section on the last elbow bound is a little weak?}
 
@@
 
+\subsection{Deriving distillation bounds from the last elbow}
+\label{sec:last_elb}
+
+\begin{proposition}\label{prop:last_elb}
+	Consider a magic state process $\rho \longrightarrow \tau$ with input and output Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in $\R_\sigma$ and denote by $X_E, X'_E$ the last elbow locations of the input and output curves respectively.
+
+	Then, given any coordinates $(x_E, L_E)$ and $(x'_E, L'_E)$ on the input and output Lorenz curves, where $x_E \geq X_E$ and $x'_E \geq X'_E$, the process is possible in $\R_\sigma$ only if
+\begin{equation}\label{eq:last_elb_bound1}
+	\frac{L_E - 1}{1-x_E} \geq \frac{L'_E - 1}{1-x_E'}.
+\end{equation}
+\end{proposition}
+\begin{proof}
+Since both pairs of coordinates are located between the last elbow of their respective curves and $(1,1)$, we can derive the bound via a simple interpolation on the line segment connecting the endpoint and the appropriate last elbow.
+
+First assume that $x_E > x'_E$ and consider the Lorenz curve constraint at $x = x_E$,
+\begin{equation}
+	\lc{\rho}{\sigma}(x_E) \geq \lc{\tau}{\sigma}(x_E).
+\end{equation} 
+We can find the output state Lorenz curve coordinate $L'_\star$ at location $x = x_E$ by interpolating between the endpoint $(1,1)$ and the output state's last elbow, 
+\begin{equation}
+	L'_\star = 1 + \frac{1-x_E}{1-x'_E} (L'_E - 1)
+\end{equation}
+The process is then possible only if $L_E \geq L_\star'$ which is a rearrangement of~\cref{eq:last_elb_bound1}.
+
+If instead, $x_E \leq x'_E$, consider the Lorenz curve constraint at $x = x'_E$,
+\begin{equation}
+	\lc{\rho}{\sigma}(x'_E) \geq \lc{\tau}{\sigma}(x'_E).
+\end{equation} 
+We now need to find the input state Lorenz curve coordinate $L_\star$ at location $x = x'_E$ by interpolating between the endpoint $(1,1)$ and the input state's last elbow, 
+\begin{equation}
+	L_\star = 1 + \frac{1-x'_E}{1-x_E} (L_E - 1).
+\end{equation}
+The process is then possible only if $L_\star \geq L'_E$ which is again a rearrangement of~\cref{eq:last_elb_bound1}.
+\end{proof}
+
+Using a similar analysis, we can also derive upper bounds from comparison of the last point coordinates of the Lorenz curve, which now corresponds to the smallest rescaled component.
+
+To this end, assume that the largest component of the equilibrium state distribution is $W_{\tau}(i,j)$.
+We now perform the Clifford operation
+\begin{equation}
+	\tau \longrightarrow X^{1-i}Z^{-j}\ \tau\ Z^{j}X^{i-1},
+\end{equation}
+which permutes the largest component such that $W_{\tau}(i,j) \longrightarrow W_{\tau}(1,0)$.
+Since we have that $u \leq v$ because $\epsilon \leq 3/7$, and we have already ensured that $W_{\tau}(1,0) \geq W_{\tau}(\bmx)$ for all $\bmx \in \mathbb{Z}_3^2$.
+Therefore, the largest rescaled component occurs when $i_{(1,0)} = n$ and $i_{\bmx} = 0$ for $\bmx \neq \bmo$ and is equal to $(v/W_{\tau}(1,0))^n$.
+Accordingly, the coordinates of the first Lorenz curve point after the origin are given by $(x_E, L_E) = ((W_{\tau}(1,0))^n, u(\epsilon)^n)$ for the input state and $(x'_E, L'_E) = ((W_{\tau'}(1,0))^m, u(\epsilon')^m)$ for the output state.
+
+We now redefine the quantities $\alpha_k$, so that again $\phi = -\beta^{-1} \log \zeta$, where $\zeta= \sum_{k\in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}$ and $\alpha_k$ now given by
+\begin{align}
+	\alpha_k = \sum_{r \in \mathbb{Z}_3} \braket{E_k}{1-r}\braket{1+r}{E_k}.
+\end{align}
+This allows us to rewrite $W_{\tau}(1,0) = {e^{\beta (F - \phi)}}/{3}$ and by using the last elbow constraint 
+\begin{equation*}
+	\frac{L_E - 1}{1-x_E} \geq \frac{L'_E - 1}{1-x_E'},
+\end{equation*}
+derived in~\cref{app:elb_constraints}, we can get a new bound expression.
+
+We note that it is also possible to perform a different Clifford transformation and get a different location $(W_{\tau}(\bmx))^n$, with $\bmx \neq \bmo$, since components $(W_{\rho}(\bmx))^n = u$ are all the same as long as $\bmx \neq \bmo$.
+The effect of this is to alter the expressions for the quantities $\alpha_k$, but not the resulting bound expression.
+
+\nick{This section on the last elbow bound is a little weak?}
+
 \end{document}

### 2021-05-13 notes/notes.tex
Corrections and tidying in appendices. Will work on appendix section on LC in unital fragments next where notation is hard to read

@@
 
+Given a state $\rho$ and a complete set of component-multiplicity pairs describing its Wigner distribution $\W{\rho}$, we now provide a method of computing the components (and multiplicities) of the $n$--copy distribution $\W{\rho}^{\otimes n}$.
+\begin{lemma}\label{lem:ncopycomponents}
+	Let $W$ be a distribution defined by a complete set of component-multiplicity pairs $\{(w_i, m_i)\}_{i=1,\dots,D}$ with $D \leq {\rm{dim}}\hspace{1pt}W$ and consider the distribution $W^{\otimes n}$ obtained by the $n$-fold (Kronecker) product $W \otimes \dots \otimes W$ between $n$ copies of $W$.
+
+	Denote by $C_D^n \coloneqq \{\bmk\}$ the set of all vectors $\bmk \coloneqq (k_1, \dots, k_D)$ with non-negative integer components that sum to $n$, i.e.
+	\begin{equation*}
+	0 \leq k_1, \dots, k_D \leq n \text{ and } k_1 + \dots + k_D = n.
+	\end{equation*}
+
+	Then, $W^{\otimes n}$ admits a complete set of component-multiplicity pairs $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$, where
+\begin{align}
+	M_{\bmk} &= \frac{n!}{k_1!\dots k_D!} \prod\limits_{i=1}^D {m_i}^{k_i}, \label{eq:M}\\
+	W_{\bmk} &= \prod\limits_{i=1}^D {w_i}^{k_i}. \label{eq:W}
+\end{align}
+\end{lemma}
+
+Here we prove two simple majorization constraints, one arising by considering only the ascending part of the Lorenz curves between the origin $(0,0)$ and the first elbow and the other by considering only the descending part of the curves between the last elbow and the endpoint $(1,1)$.
+
 \end{document}

### 2021-05-14 magic_paper.tex
Went through all appendices for tidying, left two questions in red

@@
 
-% Notation consistency (R is rate not bound, ket vs |> etc, \ln{} -> \ln ,)
+% Notation consistency (R is rate not bound, ket vs |> etc, \ln{} -> \ln ,??, italics)
 % UK vs US english
@@
 \end{align}
-where index $i$ runs through $0, \dots, n$, and we assume for simplicity of exposition that $n$ is even and the noise level is not high, $\epsilon \leq 3/7$, so that $v \geq u$.
-The details of this scenario, along with the other possible cases that occur depending on the noise level and the parity of the number of copies, are provided in~\cref{app:lcsu_technical}.
+where index $i$ runs through $0, \dots, n$, and we assume for simplicity of exposition that $n$ is even and the depolarising error is not high, $\epsilon \leq 3/7$, so that $v \geq u$.
+The details of this scenario, along with the other possible cases that occur depending on the error and the parity of the number of copies, are provided in~\cref{app:lcsu_technical}.
 
@@
 
-The first elbow constraint involves a simple interpolation, done in~\cref{app:elb_constraints}, in order to find the coordinates of both Lorenz curve points at the location where the first elbow occurs.
+The first elbow constraint involves a simple interpolation, done in~\cref{app:elb_constraint}, in order to find the coordinates of both Lorenz curve points at the location where the first elbow occurs.
 Comparing these two points leads to the bound
@@
     \includegraphics[scale=0.45]{figs/distill_bounds.pdf}
-    \caption{\textbf{Distillation bounds in the unital fragment.} Distillation bounds obtained by the first elbow majorisation constraint $R$, mana $\M$ and max--thauma $\theta_{\rm{max}}$ are plotted for $\epsilon' = 0$, up to noise level $\epsilon = 3/7$.
+    \caption{\textbf{Distillation bounds in the unital fragment.} Distillation bounds obtained by the first elbow majorisation constraint $R$, mana $\M$ and max--thauma $\theta_{\rm{max}}$ are plotted for $\epsilon' = 0$, up to error $\epsilon = 3/7$.
     Majorisation provides stricter rates than the global mana and max--thauma bounds.
@@
 \end{equation}
-with $n \gg 1$ \nick{Should we replace $m$ with $R n$ throughout?}, $\epsilon' <\epsilon$ and $\E$ denoting the quantum channel induced by the protocol.
+with $n \gg 1$ \nick{Should we replace $m$ with $R n$ or $n'$ throughout?}, $\epsilon' <\epsilon$ and $\E$ denoting the quantum channel induced by the protocol.
 We can now provide distillation bounds that depend on energetic and entropic aspects of the protocol.
@@
 \end{theorem}
-\noindent The proof of this is provided in~\cref{free-energy-bound-proof}, and is a generalization of the analysis for unital protocols.
+\noindent The proof of this is provided in~\cref{thm:free-energy-bound-proof}, and is a generalization of the analysis for unital protocols.
 
@@
 As a special case of the result, suppose that $H=H'$, implying that the protocol leaves the equilibrium state unchanged, hence it corresponds to a Gibbs-preserving map~\cite{faist_2015}.
-We focus on the pure state distillation case, where $\epsilon' \rightarrow 0$, for which we obtain~\cref{fig:rate_contour}, a contour plot of the bound on $R$ as a function of inverse temperature $\beta$ and depolarising noise level $\epsilon$ for the initial noisy magic state.
+We focus on the pure state distillation case, where $\epsilon' \rightarrow 0$, for which we obtain~\cref{fig:rate_contour}, a contour plot of the bound on $R$ as a function of inverse temperature $\beta$ and depolarising error $\epsilon$ for the initial noisy magic state.
 
@@
 	We denote the Wigner distributions of the states single-component vectors $\w(\rho)=W_\rho(x)$ and $ \w(\sigma)=W_\sigma(x)$. Likewise, we write $\w(\rho|\sigma) = W_{\rho|\tau}(\x)$.
-	We choose the component indexing so that $\w(\rho|\sigma)^\downarrow = \w(\rho|\sigma)=:\tilde{\w}$ and so the components are sorted in non-increasing order.
+	We choose the component indexing so that $\w(\rho|\sigma)^\downarrow = \w(\rho|\sigma)$ and so the components are sorted in non-increasing order.
 
@@
 
-	Let $i_\star$ be the index of the smallest non-negative component of $\widetilde{\bmw}^\downarrow$.
+	Let $i_\star$ be the index of the smallest non-negative component of $\w(\rho|\sigma)^\downarrow$.
 	Then, $w(\rho)_i < 0$ if and only if $i > i_\star$, so the maximum of Lorenz curve $\lc{\rho}{\sigma}(x)$ takes the value 
@@
 
-\subsection{First elbow constraints}
-\label{app:elb_constraints}
+\subsection{First elbow constraint}
+\label{app:elb_constraint}
 Here we prove a simple majorization constraint, arising by considering only the ascending part of the Lorenz curves between the origin $(0,0)$ and the first elbow.
@@
 First assume that $x < x'$.
-Then, point $(x, L_{\rho'|\sigma'}(x))$ lies on the lines segment connecting $(0,0)$ and $(x', L')$, so by interpolating between points $(0,0)$ and $(x', L')$, we find that
+Then, point $(x, L_{\rho'|\sigma'}(x))$ lies on the lines segment connecting $(0,0)$ and $(x', L')$, so by interpolating between points $(0,0)$ and $(x', L')$ at location $x$, we find that
 \begin{equation}
@@
 
-If instead, $x \geq x'$, the point $(x', L_{\rho|\sigma}(x'))$ lies on the lines segment connecting $(0,0)$ and $(x, L)$, so by interpolating between points $(0,0)$ and $(x, L)$, we find that
+If instead, $x \geq x'$, the point $(x', L_{\rho|\sigma}(x'))$ lies on the lines segment connecting $(0,0)$ and $(x, L)$, so by interpolating between points $(0,0)$ and $(x, L)$ at location $x'$, we find that
 \begin{equation}
@@
 
-As an example, for the Strange state with
+As an example, for the Strange state $\rho_S := \rho_S(\epsilon=0)$ with
 \begin{equation}
@@
 
-\begin{lemma}\label{ncopy_components}
+\begin{lemma}\label{lem:ncopycomponents}
 	Suppose $W_\rho(\x)$ has $D$ component-multiplicity pairs $\{(w_i, m_i)\}$.
@@
 \subsection{Lorenz curve coordinates in the unital fragment}\label{app:lcsu_coord}
+
 The Wigner distribution of the $n$--copy qutrit maximally mixed state $\left(\id/3\right)^{\otimes n}$ is the uniform probability distribution over the phase space, consisting of $9^n$ components equal to $9^{-n}$.
@@
 
-The Wigner distribution of the $n$--copy $\epsilon$--noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ is given by $\W{\rho_{\rm{S}}(\epsilon)^{\otimes n}} = W_{\rho_{\rm{S}}(\epsilon)}^{\otimes n}$ and, in the unital fragment, it corresponds to the set $\{(w_i, m_i)\}_{i=0,\dots,n}$ of component-multiplicity pairs.
-
-We present the distinct Wigner components of $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ along with their multiplicites in~\cref{tab:lcsu}.
-Note that LHS (RHS) refers to elbow coordinates $i$ on the left (right of) the Lorenz curve maximum, stated precisely as
+The Wigner distribution of the $n$--copy $\epsilon$--noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ is given by $\W{\rho_{\rm{S}}(\epsilon)^{\otimes n}} = W_{\rho_{\rm{S}}(\epsilon)}^{\otimes n}$ and, using~\cref{lem:ncopycomponents} in the unital fragment, we can associate it with the set $\{(w_i, m_i)\}_{i=0,\dots,n}$ of component-multiplicity pairs, as presented in~\cref{tab:lcsu} for all different combinations of parameters $n,\epsilon$.
+We split the values of index $i$ into two intervals, defined precisely as
 \begin{align}
@@
 \end{align}
+The labels $\text{LHS}, \text{RHS}$ imply that the components contribute to the left hand side or the right hand side of the maximum (including the maximum) of the Lorenz curve.
+To compactify notation, we also use multiplication modulo $(n+1)$, specifically, for any positive integer $m \leq 2n$:
+\begin{equation}
+	m \hspace{-6pt}\mod{\hspace{-2pt}(n+1)} = 
+	\begin{cases}
+		m,\ &\text{if } 0 \leq m \leq n, \\
+		m - n - 1,\ &\text{if } n < m \leq 2n.
+	\end{cases}
+\end{equation}
 \begin{table}[h]
@@
     \multicolumn{3}{c|}{Case} & \multicolumn{1}{c}{$m_{i}$} & \multicolumn{1}{|c}{$w_{i}$} \\[0.5ex]\hline
-    \multirow{4}{*}{\raisebox{-4ex}{\rotatebox[origin=c]{90}{$0\leq \epsilon < \frac{3}{7}$}}} & \hspace{0.8ex}\multirow{2}{*}{\raisebox{-1ex}{\rotatebox[origin=c]{90}{$n$ even}}}\hspace{0.8ex} & LHS & $8^{2i}\binom{n}{2i}$ & $u(\epsilon)^{2i}v(\epsilon)^{n-2i}$ \\
-    & & RHS & $8^{n-2i}\binom{n}{2i}$ & $-u(\epsilon)^{n-2i}v(\epsilon)^{2i}$ \\ \cline{2-5}
-    & \multirow{2}{*}{\raisebox{-2ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $8^{2i+1}\binom{n}{2i+1}$ & $u(\epsilon)^{2i+1}\left( -v(\epsilon) \right)^{n-2i-1}$ \\
-    & & RHS & $8^{n-2i-1}\binom{n}{2i+1}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{n-2i-1}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2i+1}$ \\ \hline
-    \multirow{4}{*}{\raisebox{-4ex}{\rotatebox[origin=c]{90}{$\frac{3}{7}\leq \epsilon < \frac{3}{4}$}}} & \multirow{2}{*}{\raisebox{-1ex}{\rotatebox[origin=c]{90}{$n$ even}}} & LHS & $8^{n-2i}\binom{n}{2i}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{n-2i}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2i}$ \\
-    & & RHS & $8^{2i}\binom{n}{2i}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2i}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{n-2i}$ \\ \cline{2-5}
-    & \multirow{2}{*}{\raisebox{-2ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $8^{n-2i}\binom{n}{2i}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{n-2i}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2i}$ \\
-    & & RHS & $8^{2i}\binom{n}{2i}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2i}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{n-2i}$ \\ \hline
+    \multirow{4}{*}{\raisebox{-4ex}{\rotatebox[origin=c]{90}{$0\leq \epsilon < \frac{3}{7}$}}} & \hspace{0.8ex}\multirow{2}{*}{\raisebox{-1ex}{\rotatebox[origin=c]{90}{$n$ even}}}\hspace{0.8ex} & LHS & $8^{2i}\binom{n}{2i}$ & $u^{2i}v^{n-2i}$ \\
+    & & RHS & $8^{n-2i}\binom{n}{2i}$ & $-u^{n-2i}v^{2i}$ \\ \cline{2-5}
+    & \multirow{2}{*}{\raisebox{-2ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $8^{2i+1}\binom{n}{2i+1}$ & $u^{2i+1}v^{n-2i-1}$ \\
+    & & RHS & $8^{n-2i-1}\binom{n}{2i+1}$ & $-u^{n-2i-1}v^{2i+1}$ \\ \hline
+    \multirow{4}{*}{\raisebox{-4ex}{\rotatebox[origin=c]{90}{$\frac{3}{7}\leq \epsilon < \frac{3}{4}$}}} & \multirow{2}{*}{\raisebox{-1ex}{\rotatebox[origin=c]{90}{$n$ even}}} & LHS & $8^{n-2i}\binom{n}{2i}$ & $u^{n-2i}v^{2i}$ \\
+    & & RHS & $8^{2i}\binom{n}{2i}$ & $-u^{2i}v^{n-2i}$ \\ \cline{2-5}
+    & \multirow{2}{*}{\raisebox{-2ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $8^{n-2i}\binom{n}{2i}$ & $u^{n-2i}v^{2i}$ \\
+    & & RHS & $8^{2i}\binom{n}{2i}$ & $-u^{2i}v^{n-2i}$ \\ \hline
   \end{tabular}
   \caption{Wigner components $w_{i}(n, \epsilon)$ of $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ along with their multiplicities $m_{i}(n, \epsilon)$, with $0 \leq i \leq n$.
-  The expressions change depending on the noise level $\epsilon$, the parity of the number of copies $n$ and whether the index $i$ is lower or higher than the index of the Lorenz curve maximum (LHS vs RHS).
-  Multiplication $2i$ is considered modulo $(n+1)$.} \ddd{[This whole section is hard to decypher.
-Are these $w_i$ Wigner components?
-Unique Wigner components?
-Elbow values??
-I can't spend ages decyphering this.
-Can you give clear definitions in the text?]}
-\nick{Working on it.
-I agree that in this section, notation is tough.
-$w_i$ are the Wigner components of $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ that come out of~\cref{ncopy_components}.
-They may not be distinct in some rare cases, i.e.
-when $\epsilon=3/7$ or accidentally.}
-
-  \ddd{[Also what does ``Multiplication $2i$ is considered modulo $(n+1)$'' mean???]}
-  \nick{It means $2i \pmod{n+1}$, so that e.g. $2n\pmod{n+1}=2n - (n+1) = n-1$}
+  The expressions change depending on the error $\epsilon$, the parity of the number of copies $n$ and whether the index $i$ is lower or higher than the index of the Lorenz curve maximum (LHS vs RHS).
+  Multiplication $2i$ is considered $\hspace{-6pt}\mod{\hspace{-2pt}(n+1)}$.}
   \label{tab:lcsu}
@@
 
-Every Lorenz curve in the unital fragment contains $n$ elbows, which, along with the boundary points $(x_{-1}, L_{-1}) = (0,0)$ and $(x_{n}, L_{n}) = (1,1)$, are labelled by 
+In the unital fragment, the rescaled distribution is simply proportional to the Strange state distribution,
+\begin{equation}
+	W_{\rho_{\rm{S}}(\epsilon)^{\otimes n}|\left(\id/3\right)^{\otimes n}} = 9^n W_{\rho_{\rm{S}}(\epsilon)^{\otimes n}},
+\end{equation}
+therefore expressions for the Lorenz curve coordinates follow from summing up the Wigner components in decreasing order.
+As a result, every Lorenz curve in the unital fragment contains at most $n$ elbows, which, along with the boundary points $(x_{-1}, L_{-1}) := (0,0)$ and $(x_{n}, L_{n}) := (1,1)$, are labelled by 
 \begin{equation*}
-\{(x_{i}, L_{i})\}_{i=-1,0,\dots,n}.
+\{(x_{i}, L_{i})\}_{i=-1,0,\dots,n},
 \end{equation*}
-The maximum is the $\lfloor n/2 \rfloor$-th elbow and its coordinates are calculated by collecting all the positive Wigner components,
+where the coordinates are
+\begin{equation}
+	(x_{i}, L_{i}) = \left( \frac{1}{9^n}\sum_{\ell=0}^i m_{\ell}, \sum_{\ell=0}^i m_{\ell} w_{\ell} \right).
+\end{equation}
+The Lorenz curve maximum is the $\lfloor n/2 \rfloor$-th elbow and its coordinates are calculated by collecting all the positive Wigner components,
 \begin{align}
@@
 
-Expressions for all the elbow coordinates follow from summing up the Wigner components in decreasing order.
 In~\cref{tab:lcsu_coord_elb_app}, we present the elbow coordinates of the $n$-copy, $\epsilon$--noisy Strange state Lorenz curve in the unital fragment for any combination of parameters $n, \epsilon$.
@@
   \caption{Lorenz curve elbow coordinates in the unital fragment.
-  The coordinate expressions depend on the noise level $\epsilon$, the parity of the number of copies $n$ and the location of the elbow relative to the maximum (LHS vs RHS).
+  The coordinate expressions depend on the error $\epsilon$, the parity of the number of copies $n$ and the location of the elbow relative to the maximum (LHS vs RHS).
   Multiplication $2i$ is considered modulo $(n+1)$.
@@
 
+\nick{ALTERNATIVE TABLE PRESENTATION:}
+In~\cref{tab:lcsu_coord_elb_app_alt}, we present the elbow coordinates of the $n$-copy, $\epsilon$--noisy Strange state Lorenz curve in the unital fragment for any combination of parameters $n, \epsilon$.
+To compactify notation, we define in terms of $n, \epsilon$ an amplitude $A$ and a probability $p$, as follows:
+\begin{align}
+	A &= \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n, \\
+	p &= \frac{12-4\epsilon}{15-8\epsilon}.
+\end{align}
+
+\begin{table}[h]
+  \def\arraystretch{1.5}
+  \centering
+  \begin{tabular}{c|c|c|r|r}
+    \multicolumn{3}{c|}{Case} & \multicolumn{1}{c}{$x_{i}$} & \multicolumn{1}{|c}{$L_{i}$} \\[0.5ex]\hline
+   \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$0\leq \epsilon < \frac{3}{7}$}}} & \hspace{0.8ex}\multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ even}}}\hspace{0.8ex} & LHS & $x_{\lfloor n/2 \rfloor} + \Phi_+\left(2i;n,\frac{8}{9}\right)$ & $L_{\lfloor n/2 \rfloor} + A \Phi_+\left(2i;n,p\right)$ \\
+    & & RHS & $x_{\lfloor n/2 \rfloor} + \Phi_-\left(2i;n,\frac{1}{9}\right)$ & $L_{\lfloor n/2 \rfloor} - A \Phi_-\left(2i;n,1-p\right)$ \\ \cline{2-5}
+    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $x_{\lfloor n/2 \rfloor} + \Phi_-\left(2i;n,\frac{8}{9}\right)$ & $L_{\lfloor n/2 \rfloor} + A \Phi_-\left(2i;n,p\right)$ \\
+    & & RHS & $x_{\lfloor n/2 \rfloor} + \Phi_-\left(2i;n,\frac{1}{9}\right)$ & $L_{\lfloor n/2 \rfloor} - A \Phi_-\left(2i;n,1-p\right)$ \\ \hline
+    \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$\frac{3}{7}\leq \epsilon < \frac{3}{4}$}}} & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ even}}} & LHS & $x_{\lfloor n/2 \rfloor} + \Phi_+\left(2i;n,\frac{1}{9}\right)$ & $L_{\lfloor n/2 \rfloor} + A \Phi_+\left(2i;n,1-p\right)$ \\
+    & & RHS & $x_{\lfloor n/2 \rfloor} + \Phi_-\left(2i;n,\frac{8}{9}\right)$ & $L_{\lfloor n/2 \rfloor} - A \Phi_-\left(2i;n,p\right)$ \\ \cline{2-5}
+    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $x_{\lfloor n/2 \rfloor} + \Phi_+\left(2i;n,\frac{1}{9}\right)$ & $L_{\lfloor n/2 \rfloor} + A \Phi_+\left(2i;n,1-p\right)$ \\
+    & & RHS & $x_{\lfloor n/2 \rfloor} + \Phi_+\left(2i;n,\frac{8}{9}\right)$ & $L_{\lfloor n/2 \rfloor} - A \Phi_+\left(2i;n,p\right)$ \\ \hline
+  \end{tabular}
+  \caption{Lorenz curve elbow coordinates in the unital fragment.
+  The coordinate expressions depend on the error $\epsilon$, the parity of the number of copies $n$ and the location of the elbow relative to the maximum (LHS vs RHS).
+  Multiplication $2i$ is considered modulo $(n+1)$.
+  For completeness, note that $(x_{-1}, L_{-1}) \coloneqq (0,0)$ is not included in the table.
+  }
+  \label{tab:lcsu_coord_elb_app_alt}
+\end{table}
+
+\newpage
 We can get explicit expressions for all $9^{n}$ points of the Lorenz curve $\lc{\rho_{\rm{S}}(\epsilon)^{\otimes n}}{(\id/3)^{\otimes n}}$, in terms of the elbow coordinates:
@@
 \end{align}
-for $j = 1,\dots,m_{i}$ and $i=0,\dots,n$, where multiplicities $m_i = m_i(n, \epsilon)$ are given in~\cref{tab:lcsu}.
-
-Consider the state 
+for $j = 1,\dots,m_{i}$ and $i=0,\dots,n$, where multiplicities $m_i$ are given in~\cref{tab:lcsu}.
+
+One can consider the state 
 \begin{equation*}
@@
 \end{align}
-with $\x_\star = \arg\!\min W_\tau(\x)$. The primed variables are defined similarly for the output system.
+and $\x_\star = \arg\!\min W_\tau(\x)$. The primed variables are defined similarly for the output system.
 \end{theorem}
 
-\begin{proof}	
+\begin{proof}	\label{thm:free-energy-bound-proof}
 For the sake of clarity, we write $\rho_n \coloneqq \rho_S(\epsilon)^{\otimes n}$, $\rho'_m \coloneqq \rho_S(\epsilon')^{\otimes m}$, $\tau_n \coloneqq \tau^{\otimes m}$ and $\tau'_m \coloneqq \tau'^{\otimes m}$.
@@
 If the largest rescaled component of a state is distinct with no multiplicities, then these coordinates correspond to the first elbow of the corresponding Lorenz curve, whereas if it appears multiple times, then the coordinates derived correspond to a point on the interior of the line segment connecting the origin to the first elbow.
-In both cases, the distillation bound remains the same, as is clear by its derivation in~\cref{app:elb_constraints}, given by $L_0/x_0 \geq L'_0/x'_0$, leading to
+In both cases, the distillation bound remains the same, as is clear by its derivation in~\cref{app:elb_constraint}, given by $L_0/x_0 \geq L'_0/x'_0$, leading to
 \begin{equation}
@@
 
-If we drop the freedom to transform them magic states via Clifford unitaries that depend on the reference states $\tau$ and $\tau'$, then the analysis just presented gets a little more complex, since the largest component in the rescaled distribution depends on a number of factors.
+If we drop the freedom to transform the magic states via Clifford unitaries, then the final expression for the bounds change and become a little more complex, since the largest component in the rescaled distribution depends on a number of factors.
 We illustrate this by the following result.
 
-\nick{This proof offers: 1.
-the exact derivation of our main contour plot, justifying the quantities $\epsilon_\star$ and $\beta_\star$ 2.
-a method for lifting the ``Clifford change in basis'' assumption - Can be trimmed down to the case where $H=H'$.
-What do you think?} \ddd{[Yep, we re-play the previous notation+line but then drop the Clifford unitary freedom and go through the different cases.]}
 \begin{theorem}
-	Consider a magic distillation protocol transforming noisy Strange state
+	Consider a magic distillation protocol on qutrits that transforms
 \begin{equation*}
@@
 
-Let each qutrit have a Hamiltonian $H$ with stabilizer eigenstates and energies $E_0, E_1, E_2$, and define $E_{\rm max} = \max\{E_0, E_1, E_2\}$ and $E_s$ the eigenvalue of the eigenstate that \nick{overlaps} the negative component of $\rho_S(\epsilon)$ in the Wigner representation.
-Let $T =(k\beta)^{-1}$ be any characteristic temperature for the physical system in the state $\tau^{\otimes n}= (e^{-\beta H}/\Z)^{\otimes n}$, with free energy $F$.
-Assume that for $n,m \gg 1$ the channel $\E$ generates negligible correlations on $\tau^{\otimes n}$, and so $\E(\tau^{\otimes n}) = \sigma^{\otimes m}$ for some state $\sigma$.
+Let each qutrit have a Hamiltonian $H$ with energies $E_0, E_1, E_2$ and stabilizer eigenstates, and define $E_{\rm max} = \max\{E_0, E_1, E_2\}$ and $E_s$ as the eigenvalue of the Hamiltonian eigenstate the Wigner representation of which overlaps the negative component of $\rho_S(\epsilon)$ in the phase space.
+Let $T =(k\beta)^{-1}$ be any finite temperature and assume that in the thermodynamic limit ($n,m \gg 1$), the protocol applied to the equilibrium state $\tau^{\otimes n} = (e^{-\beta H}/\Z)^{\otimes n}$ maps $\tau^{\otimes n} \longrightarrow \tau^{\prime \otimes m}$, where we express state $\tau'$ as $\tau' = e^{-\beta H'}/\Z'$ for some Hermitian $H'$.
 
@@
 \end{equation}
-and define a threshold noise,
+and define a threshold error,
 \begin{equation}
@@
 \end{equation}
-where $F'$ is the free energy of the state $\sigma = e^{-\beta H'}/\Z'$ and other primed quantities are defined in the same way as the corresponding unprimed quantities. 
+where $F$ is the free energy of state $\tau$ and all primed quantities are similarly defined for the ouptut system.
 \end{theorem}
@@
 \begin{proof}
-To establish the distillation bounds we consider the distillation protocol that gives
-\begin{equation}
-	\E( \rho_S(\epsilon)^{\otimes n}) = \rho_S(\epsilon')^{\otimes m},
-\end{equation}
-for the magic state. We then consider how the protocol transforms the reference equilibrium state as
-\begin{equation}
-	\E( \tau^{\otimes n}) = \sigma^{\otimes m}.
-\end{equation}
-Since $\tau$ and $\sigma$ are assumed to be full rank stabilizer states they have a strictly positive Wigner distribution, while, in contrast, the input and output magic states will generally have quasi-probability distributions for their Wigner functions.
-For any such protocol we therefore have that
-\begin{equation}
-	(W_{\rho_n} (x), W_{\tau_n}(x) ) \succ  (W_{\rho'_m} (x), W_{\sigma_m}(x) ),
-\end{equation}
-where, for the sake of clarity, we write $\rho_n \coloneqq \rho_S(\epsilon)^{\otimes n}$, $\rho'_m \coloneqq \rho_S(\epsilon')^{\otimes m}$ and $\tau_n \coloneqq \tau^{\otimes m}$, $\sigma_m \coloneqq \sigma^{\otimes m}$.
-We then have that
-\begin{equation}
-	L_{\rho_n |\tau_n}(x) \ge L_{\rho'_m |\sigma_m}(x) \mbox{ for all } x.
-\end{equation}
-We must therefore compute the Lorenz curve data for $\rho_n$ relative to $\tau_n$, and compare with the Lorenz curve of the output state $\rho_m'$ relative to $\sigma_m$.
-
-We define $W_{\rho | \tau}(\x) \coloneqq W_\rho(\x)/W_\tau(\x)$, which is always well-defined since $\tau$ is full-rank. Now we show in~\cref{app:wigner} that
-\begin{equation}
-W_{\rho_1\otimes \rho_2 | \tau_1 \otimes \tau_2} (\x_1 \oplus \x_2) = W_{\rho_1 | \tau_1}(\x_1)W_{\rho_2 | \tau_2}(\x_2),
-\end{equation}
-and also,
-\begin{equation}
-W_{\rho_1\otimes \rho_2} (\x_1 \oplus \x_2) = W_{\rho_1}(\x_1)W_{\rho_2}(\x_2),
-\end{equation}
-for any states $\rho_1, \rho_2$ and any full-rank stabilizer states $\tau_1, \tau_2$.
-\ddd{[Notation clashing here.
-Frame result outside as its own lemma -- we gotta check everything.]} \nick{Will frame in~\cref{app:wigner} and fix notation in the next commit}
-Therefore we have that
-\begin{align}
-W_{\rho_n |\tau_n} (\x) &= \prod_{i=1}^n W_{\rho|\tau}(\x_i)\\
-W_{\rho_n } (\x) &= \prod_{i=1}^n W_\rho(\x_i)
-\end{align}
-where $\x = \oplus_{i=1}^n \x_i$ is the phase space point for the full system in terms of those of the individual subsystems.
-
-The points defining the Lorenz curve $L_{\rho_n |\tau_n}(x)$ are obtained from first sorting the components of $W_{\rho_n |\tau_n}(\x)$ in non-increasing order and then computing the partial sums of $W_{\rho_n |\tau_n}(\pi(\x))$ where $\pi$ is the permutation that realises the sorting.
-Therefore, we first look at the values of $W_{\rho|\tau}(\x_i)$ for the single-copy case.
+The proof proceeds in the same manner as in~\cref{thm:free-energy-bound-proof} up to the point where we need to evaluate $W_{\rho_n |\tau_n} (\x)$ and $W_{\rho_n}(\x)$ explicitly.
+Now we do not have the freedom of additional Clifford processing, so we need to exploit the full structure of the equilibrium state.
 
@@
 		\bmm &\coloneqq (1,2,3,3), \\
-	\bmw(\tau) &\coloneqq \frac{1}{3\Z} \left( e^{-\beta E_0}, e^{-\beta E_0}, e^{-\beta E_1}, e^{-\beta E_2} \right), \\
-	\bmw(\rho_{\rm{S}} | \tau) &\coloneqq 3\Z \left( -v e^{\beta E_0}, u e^{\beta E_0}, u e^{\beta E_1}, u e^{\beta E_2} \right). \label{eq:bmw_rescaled}
+	\w(\tau) &\coloneqq \frac{1}{3\Z} \left( e^{-\beta E_0}, e^{-\beta E_0}, e^{-\beta E_1}, e^{-\beta E_2} \right), \\
+	\w(\rho_{\rm{S}} | \tau) &\coloneqq 3\Z \left( -v e^{\beta E_0}, u e^{\beta E_0}, u e^{\beta E_1}, u e^{\beta E_2} \right). \label{eq:bmw_rescaled}
 \end{align}
@@
 \end{equation}
-such that for the regime $0 \leq \beta \leq \beta_\star$ a transition noise level $\epsilon_\star$ exists, and for $\beta > \beta_\star$ no such transition exists, so we choose $\epsilon_\star = 0$. 
+such that for the regime $0 \leq \beta \leq \beta_\star$ a threshold error $\epsilon_\star$ exists, and for $\beta > \beta_\star$ no such transition exists, so we choose $\epsilon_\star = 0$. 
 Therefore, the transition value for the noise is given by
@@
 
-\ddd{[Hmmm this needs an additional assumption on the output state to re-run the same analysis.
-Very annoying.]}\nick{What additional assumption beyond that the output state can be written as a Gibbs state for some $H'$?}
 Similarly, considering the output magic state with respect to state $\sigma'$, the image of equilibrium state $\sigma$ under the magic protocol, we get output Lorenz curve coordinates,
@@
 There are four combinations of coordinates, depending on the noise parameters $\epsilon, \epsilon'$ for the input and output states.
-In each of these combinations, we simply use the first elbow constraint, as described in~\cref{app:elb_constraints}, which leads to the bounds in the statement of the theorem.
+In each of these combinations, we simply use the first elbow constraint, as described in~\cref{app:elb_constraint}, and manipulate the coordinates as in the proof of~\cref{thm:free-energy}, leading to the bounds in the statement of the theorem.
 \end{proof}
@@
 
+We can run a similar analysis, in order to utilise the descending part of the Lorenz curves to extract bounds.
+These bounds do not offer any additional physical insight and are expressed by , but can be tighter in some scenarios.
+Here we derive an equivalent bound to our main theorem using the last elbow constraint, which we prove first.
+
 \begin{proposition}\label{prop:last_elb}
-	Consider a magic state process $\rho \longrightarrow \tau$ with input and output Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in $\R_\sigma$ and denote by $X_E, X'_E$ the last elbow locations of the input and output curves respectively.
-
-	Then, given any coordinates $(x_E, L_E)$ and $(x'_E, L'_E)$ on the input and output Lorenz curves, where $x_E \geq X_E$ and $x'_E \geq X'_E$, the process is possible in $\R_\sigma$ only if
+	Consider a magic state process $\rho \longrightarrow \rho'$ with input and output Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\rho'}{\sigma'}(x)$ and denote the coordinates of the last elbow of $L_{\rho|\sigma}(x)$ by $(X_E, L_E)$ and the coordinates of the first elbow of $L_{\rho' |\sigma'}(x)$ by $(X'_E, L'_E)$.
+
+Then, given any coordinates $(x, L)$ and $(x', L')$ of the input and output Lorenz curves respectively, where $1 > x \geq X_E$ and $1 > x' \geq X'_E$, the process is possible only if
 \begin{equation}\label{eq:last_elb_bound1}
-	\frac{L_E - 1}{1-x_E} \geq \frac{L'_E - 1}{1-x_E'}.
+	\frac{L - 1}{1-x} \geq \frac{L' - 1}{1-x'}.
 \end{equation}
@@
 \begin{proof}
-Since both pairs of coordinates are located between the last elbow of their respective curves and $(1,1)$, we can derive the bound via a simple interpolation on the line segment connecting the endpoint and the appropriate last elbow.
-
-First assume that $x_E > x'_E$ and consider the Lorenz curve constraint at $x = x_E$,
-\begin{equation}
-	\lc{\rho}{\sigma}(x_E) \geq \lc{\tau}{\sigma}(x_E).
-\end{equation} 
-We can find the output state Lorenz curve coordinate $L'_\star$ at location $x = x_E$ by interpolating between the endpoint $(1,1)$ and the output state's last elbow, 
-\begin{equation}
-	L'_\star = 1 + \frac{1-x_E}{1-x'_E} (L'_E - 1)
-\end{equation}
-The process is then possible only if $L_E \geq L_\star'$ which is a rearrangement of~\cref{eq:last_elb_bound1}.
-
-If instead, $x_E \leq x'_E$, consider the Lorenz curve constraint at $x = x'_E$,
-\begin{equation}
-	\lc{\rho}{\sigma}(x'_E) \geq \lc{\tau}{\sigma}(x'_E).
-\end{equation} 
-We now need to find the input state Lorenz curve coordinate $L_\star$ at location $x = x'_E$ by interpolating between the endpoint $(1,1)$ and the input state's last elbow, 
-\begin{equation}
-	L_\star = 1 + \frac{1-x'_E}{1-x_E} (L_E - 1).
-\end{equation}
-The process is then possible only if $L_\star \geq L'_E$ which is again a rearrangement of~\cref{eq:last_elb_bound1}.
+Since both pairs of coordinates are located between the endpoint $(1,1)$ and the last elbow of their respective curves, we can derive the bound via a simple interpolation on the line segment connecting the endpoint and the appropriate pair of coordinates.
+
+First assume that $x > x'$.
+Then, point $(x, L_{\rho'|\sigma'}(x))$ lies on the lines segment connecting $(1,1)$ and $(x', L')$, so by interpolating between points $(1,1)$ and $(x', L')$, we find that
+\begin{equation}
+	L_{\rho'|\sigma'}(x) = 1 + \frac{1-x}{1-x'} (L' - 1).
+\end{equation}
+Considering the Lorenz curve constraint at $x$, the process is possible only if 
+\begin{equation}
+	L = \lc{\rho}{\sigma}(x) \geq \lc{\rho'}{\sigma'}(x) = 1 + \frac{1-x}{1-x'} (L' - 1),
+\end{equation}
+which is a rearrangement of~\cref{eq:last_elb_bound1}.
+
+If instead, $x \leq x'$, the point $(x', L_{\rho|\sigma}(x'))$ lies on the lines segment connecting $(1,1)$ and $(x, L)$, so by interpolating between points $(1,1)$ and $(x, L)$, we find that
+\begin{equation}
+	L_{\rho|\sigma}(x') = 1 + \frac{1-x'}{1-x} (L - 1).
+\end{equation}
+Considering the Lorenz curve constraint at $x'$, the process is possible only if 
+\begin{equation}
+	1 + \frac{1-x'}{1-x} (L - 1) = \lc{\rho}{\sigma}(x') \geq \lc{\rho'}{\sigma'}(x) = L',
+\end{equation}
+which is again a rearrangement of~\cref{eq:last_elb_bound1}.
 \end{proof}
 
-Using a similar analysis, we can also derive upper bounds from comparison of the last point coordinates of the Lorenz curve, which now corresponds to the smallest rescaled component.
-
-To this end, assume that the largest component of the equilibrium state distribution is $W_{\tau}(i,j)$.
-We now perform the Clifford operation
-\begin{equation}
-	\tau \longrightarrow X^{1-i}Z^{-j}\ \tau\ Z^{j}X^{i-1},
-\end{equation}
-which permutes the largest component such that $W_{\tau}(i,j) \longrightarrow W_{\tau}(1,0)$.
-Since we have that $u \leq v$ because $\epsilon \leq 3/7$, and we have already ensured that $W_{\tau}(1,0) \geq W_{\tau}(\bmx)$ for all $\bmx \in \mathbb{Z}_3^2$.
-Therefore, the largest rescaled component occurs when $i_{(1,0)} = n$ and $i_{\bmx} = 0$ for $\bmx \neq \bmo$ and is equal to $(v/W_{\tau}(1,0))^n$.
-Accordingly, the coordinates of the first Lorenz curve point after the origin are given by $(x_E, L_E) = ((W_{\tau}(1,0))^n, u(\epsilon)^n)$ for the input state and $(x'_E, L'_E) = ((W_{\tau'}(1,0))^m, u(\epsilon')^m)$ for the output state.
-
-We now redefine the quantities $\alpha_k$, so that again $\phi = -\beta^{-1} \log \zeta$, where $\zeta= \sum_{k\in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}$ and $\alpha_k$ now given by
-\begin{align}
-	\alpha_k = \sum_{r \in \mathbb{Z}_3} \braket{E_k}{1-r}\braket{1+r}{E_k}.
-\end{align}
-This allows us to rewrite $W_{\tau}(1,0) = {e^{\beta (F - \phi)}}/{3}$ and by using the last elbow constraint 
-\begin{equation*}
-	\frac{L_E - 1}{1-x_E} \geq \frac{L'_E - 1}{1-x_E'},
-\end{equation*}
-derived in~\cref{app:elb_constraints}, we can get a new bound expression.
-
-We note that it is also possible to perform a different Clifford transformation and get a different location $(W_{\tau}(\bmx))^n$, with $\bmx \neq \bmo$, since components $(W_{\rho}(\bmx))^n = u$ are all the same as long as $\bmx \neq \bmo$.
+In order to derive a bound based on the last elbow constraint, we assume that the smallest component of the equilibrium state distribution is $W_{\tau}(\bmx_\star)$ and the second smallest is $W_{\tau}(\bmy_\star)$.
+We now perform a Clifford operation on $\rho_{\rm{S}}$ so that its Wigner component is $-v(\epsilon)$ at $\bmx_\star$ and $u(\epsilon)$ at $\bmy_\star$. \nick{Is this always possible? I think not}
+Since we have that $u \leq v$ because $\epsilon \leq 3/7$, and $W_{\tau}(\bmx_\star) \geq W_{\tau}(\bmy_\star) \geq W_{\tau}(\bmx)$ for all $\bmx \in \mathbb{Z}_3^2$, the largest rescaled component occurs when $i_{\bmx_\star} = n-1$, $i_{\bmy_\star} = 1$ and $i_{\bmx} = 0$ for $\bmx \notin \{\bmx_\star, \bmy_\star\}$ and it is equal to $(-v^{n-1}u/(W_{\tau}(\bmx_\star)^{n-1}W_{\tau}(\bmy_\star))$.
+Accordingly, the coordinates of the last Lorenz curve point before $(1,1)$ are given by
+\begin{equation}
+	(x_E, L_E) = \left( 1-W_{\tau}(\bmx_\star)^{n-1}W_{\tau}(\bmy_\star), 1 + v(\epsilon)^{n-1}u(\epsilon) \right)
+\end{equation}
+for the input state and we express the same coordinates with primed quantities for the output state.
+
+We now define the quantities $\phi_\alpha$ defined in terms of $\alpha_k = \sum_{r \in \mathbb{Z}_3} \<E_k |A_{\bmx_\star} |E_k\>$.
+and $\phi_\lambda$ defined in terms of $\lambda_k = \sum_{r \in \mathbb{Z}_3} \<E_k |A_{\bmy_\star} |E_k\>$.
+This allows us to rewrite $W_{\tau}(\bmx_\star) = {e^{\beta (F - \phi_\alpha)}}/{3}$ and $W_{\tau}(\bmy_\star) = {e^{\beta (F - \phi_\lambda)}}/{3}$.
+
+Using the last elbow constraint derived in~\cref{prop:last_elb}, we can get the new bound expression,
+\begin{equation}
+	\begin{split}
+	R \leq &\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (\phi_\alpha - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (\phi'_\alpha - F')} + \\
+	&\frac{1}{n}\frac{\ln{\frac{u(\epsilon')v(\epsilon)}{u(\epsilon)v(\epsilon')}}+\beta(\phi_\alpha - \phi'_\alpha + \phi'_\lambda - \phi_\lambda)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (\phi'_\alpha - F')}
+	\end{split}
+\end{equation}
+
+We note that it is possible to perform various Clifford transformations and get a different location $(W_{\tau}(\bmx))^n$, with $\bmx \neq \bmo$, since components $W_{\rho}(\bmx) = u(\epsilon)$ are all the same as long as $\bmx \neq \bmo$.
 The effect of this is to alter the expressions for the quantities $\alpha_k$, but not the resulting bound expression.
 
-\nick{This section on the last elbow bound is a little weak?}
-
 \end{document}

### 2021-05-14 magic_paper.tex
some changes
wrap up of findings on phi, F. phi doesnt really tend to infinity

@@
 
-\begin{figure}[t!]
+\begin{figure}
     \centering
-    \subfigure[][]{%
-    \label{fig:phip}%
-    \includegraphics[scale=0.4]{figs/test/phi_p.pdf}}\\
-    \subfigure[][]{%
-    \label{fig:Rp}%
-    \includegraphics[scale=0.4]{figs/test/rate_p.pdf}}
-    \caption{Here, $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$, $H = p\ {\rm{diag}}(0,1,2) + (1-p)\ {\rm{Hadamard}}$.
-\subref{fig:noCliff} Plot of $\phi$ vs $p$
- \subref{fig:Cliff} Plot of $R$ vs $p$}
-    \label{fig:vsp}
+    \includegraphics[scale=0.4]{figs/test/R_vs_H.pdf}
+    \caption{Here, $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$, $H = {\rm{diag}}(0,1,2)$ and $H' = (1-p-q){\rm{diag}}(0,1,2)+p{\rm{diag}}(1,2,0)+q{\rm{diag}}(2,0,1)$.
+    }
+    \label{fig:rvsh}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.4]{figs/test/R_vs_A.pdf}
+    \caption{Here, $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$, $H = A_{\bmo}$ and $H' = (1-p-q)A_{\bmo}+pA_{(1,2)}+q{\rm{diag}}(0,1,2)$.
+    }
+    \label{fig:rvsa}
 \end{figure}
@@
 on $H$ to get $H'$ leaves $\phi$ unaffected.
+I didn't find any interesting case where $\phi \rightarrow \infty$, except of course when there is some $E_k \rightarrow \infty$. 
+I looked through Hamiltonians which are convex combinations of phase-point operators and SHO (diagonal) Hamiltonians.
 
@@
   The coordinate expressions depend on the error $\epsilon$, the parity of the number of copies $n$ and the location of the elbow relative to the maximum (LHS vs RHS).
-  Multiplication $2i$ is considered modulo $(n+1)$.
+  Multiplication $2i$ is considered $\hspace{-6pt}\mod{\hspace{-2pt}(n+1)}$.
   For completeness, note that $(x_{-1}, L_{-1}) \coloneqq (0,0)$ is not included in the table.
@@
 \label{app:main_proof}
-Here we prove~\cref{thm:free-energy}, which bounds magic distillation rates in terms of free energies.
-
+Here we prove our main theorem, which bounds magic distillation rates in terms of free energies.
+
+\begingroup
+\def\thetheorem{\ref{thm:free-energy}}
 \begin{theorem}
@@
 \end{theorem}
+\addtocounter{theorem}{-1}
+\endgroup
 

### 2021-05-17 magic_paper.tex
Smoothing and re-ordering. Few things still to do.

@@
 \nick{re-write based on new relative majorisation approach}
-The past few years have seen rapid progress towards the goal of a fault-tolerant quantum computer~\cite{Fowler_2012, Herrera_2010, Nickerson_2014, Nikahd_2017, chao_2018, lin_pieceable_2020, Lin_2020, Bourassa_2021}.
+The past few years have seen rapid progress towards the goal of a fault-tolerant quantum computer~\cite{Fowler_2012, Herrera_2010, Nickerson_2014, Nikahd_2017, chao_2018, lin_pieceable_2020, Lin_2020, Bourassa_2021} \ddd{[delete the first two from the bibliography - they are ancient and the second is mine, so it looks like bad self-citing]}.
 However, many challenges remain and there is increasing need for theory to take into account physical limitations of the hardware involved.
@@
 
-We approach this problem using tools from statistical mechanics and recent work from the overlap of thermodynamics and quantum information theory~\cite{cit:gour, cit:gour2}\nick{You had a specific review in mind I think, which one?}.
+We approach this problem using tools from statistical mechanics and recent work from the overlap of thermodynamics and quantum information theory~\cite{cit:gour, cit:gour2}\nick{You had a specific review in mind I think, which one?} \ddd{[cite the Danzig paper from the early 2000s cite thermo-majorization Horodecki Oppenheim, cite the ``second laws'' paper by Brandao et al, cite Matteo's review, cite review articles by Goold et al, and Janet Anders]}.
 In particular, we shall view \emph{magic as a form of free energy}, relative to the set of stabilizer states.
@@
         \includegraphics[scale=0.4]{figs/protocol_diagram.pdf}
-    \caption{\textbf{Action of a magic protocol} 
+    \caption{\textbf{Analysing magic protocols relative to a stabilizer reference state.} 
 	A magic protocol aims to turn $n$ copies of some magic state $\rho_1$ to $m$ copies of some other state $\rho_2$.
 	Constraints on the efficiency of the protocol can be imposed by considering its action on an separate probe state $\tau$.
-	\nick{How do we improve the illustration?}
+	\nick{How do we improve the illustration?}\ddd{[I would have two separate box transformations, the top one has $\rho$ fed into $\E$, the bottom one has $\tau$ fed into it.
+Then put the relevant property (e.g.
+$\epsilon$ for $\rho$, and $F$ for $\tau$ next to the states.
+If viable then have $\phi$ somehow linking the top and bottom -- conveying it is a hybrid quantity in some sense.]}
     }
@@
 \end{equation}
-with $n \gg 1$ \nick{Should we replace $m$ with $R n$ or $n'$ throughout?}, $\epsilon' <\epsilon$ and $\E$ denoting the quantum channel induced by the protocol.
+with $n \gg 1$ \nick{Should we replace $m$ with $R n$ or $n'$ throughout?}\ddd{[Nah, $m$ is simpler than $Rn$ -- you gotta resist the urge to complicate expressions, unless it's needed.
+*Bad* habit.]}, $\epsilon' <\epsilon$ and $\E$ denoting the quantum channel induced by the protocol.
 We can now provide distillation bounds that depend on energetic and entropic aspects of the protocol.
@@
 The coefficients $\alpha_k$ may be negative for some $k$, when the Hamiltonian eigen-decomposes into non-stabilizer states, but the quantity $\phi$ is always well-defined, since the function $\zeta$ is a positive multiple of the stabilizer Wigner component $W_\tau(0,0)$, as seen in the proof of the theorem.
-
-The sole purpose of the Clifford unitaries $C_1,C_2$ is to simplify the form of the $\alpha_k$ coefficients.
-\nick{That's not right, without Clifford processing we would get bounds that depend on $u$ whenever $\x_\star$ corresponds to $u$, as well as $v$ whenever $\x_\star$ corresponds to $v$ as seen in the contour plot - these are different values} For example, if $H=Z$ then the energy eigenbasis is equivalent to the computational basis up to a Fourier transform, and so $\phi$ would have a sharp, temperature-independent value $\phi \in \{E_0,E_1,E_2\}$ once we account for the Clifford change in basis.
+In the case that the system's Hamiltonian $H$ has an eigenbasis consisting of stabilizer states then we show in Appendix \ref{sharp-phi} that $\phi$ takes on a sharp, temperature-independent value $\phi \in \{E_0,E_1,E_2\}$.
+
+The primary role of the pre/post-processing by Clifford unitaries is to simplify the form of the bound, and allow it to be expressed in terms of free energy quantities that do not depend on the parameters $\epsilon, \epsilon', \beta$ in a complex form.
 
@@
 
-The only assumption that cannot be trivially dropped is the assumption that we can ignore correlations in the thermodynamic limit.
+The only assumption that is non-trivial is the assumption that we can ignore correlations in the thermodynamic limit.
 This is a common situation in thermodynamics, where correlations are often sub-linear in the particle number in the macroscopic limit.
@@
 
-\null\newpage
-\null\newpage
 \section{Outlook and open questions}
@@
 
-\ddd{[Initial text. To be edited.]}
 We have described how relative majorization can be used to establish upper bounds on magic distillation protocols that take into account additional physics of the system.
@@
 
-Here, we present basic properties of the phase-point operators and the Wigner distribution that are used throughout the paper.
+In this appendix we present basic properties of the phase-point operators and the Wigner distribution that are used throughout the paper.
 
@@
 
-\section{Properties of majorization}
+\section{Properties of relative majorization and Lorenz curves}
 \label{app:major}
 
-We now give the following equivalent formulations of relative majorization.
+The following provides equivalent formulations of relative majorization.
 
@@
 
-We now prove the following result, which was stated in~\cref{sec:monotones_frag}.
+\section{Lorenz curves and $\sigma$--fragments}
+\label{app:frag}
+
+We now prove the following result on the relation between majorization in a particular fragment and mana, which was stated in~\cref{sec:monotones_frag}.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Technical properties of Lorenz curves and $\sigma$--fragments}
-\label{app:frag}
-
-\subsection{First elbow constraint}
-\label{app:elb_constraint}
-Here we prove a simple majorization constraint, arising by considering only the ascending part of the Lorenz curves between the origin $(0,0)$ and the first elbow.
+We now prove a simple majorization constraint, arising by considering only the part of the Lorenz curves between the origin $(0,0)$ and the first elbow.
 \begin{proposition}\label{prop:first_elb}
@@
 
-\subsection{Component-multiplicity pairs}
-\label{app:cmpairs}
-
-In general, a $1$--copy $d$--dimensional state $\rho$ is described by its $d^2$--dimensional Wigner distribution $\W{\rho}(\bmx)$. 
-The distribution $\W{\rho}(\bmx)$ is defined on the phase space, but it can be convenient to re-express this using vector notation.
-
-To each Wigner distribution $W_\rho(\x)$ we can associate \emph{component-multiplicity} pairs $\{(w_i, m_i)\}$ where the value $w_i$ occurs in the distribution $W_\rho(\x)$ with multiplicity $m_i$.
-
-As an example, for the Strange state $\rho_S := \rho_S(\epsilon=0)$ with
-\begin{equation}
-W_{\rho_S}(\x) = (-1/3, 1/6,  1/6,  1/6,  1/6,  1/6,  1/6,  1/6,  1/6)
-\end{equation}
-we have the component-multiplicity pairs: $\{( -1/3, 1), ( 1/6, 8)\}$.
-However, we might also wish more freedom and not require that the different $w_i$ values are all distinct.
-For example, the component-multiplity pairs $\{(-1/3, 1), (1/6, 2), (1/6, 3), (1/6, 3)\}$ also describe $W_{\rho_S}(\x)$.
-
-This representation is more compact when a Wigner distribution has a lot of multiplicities, and allows for simple handling of multiple copies via the following fact.
-\begin{lemma}
-Consider two Wigner distributions $\W{\rho_A}, \W{\rho_B}$ with component-multiplicity pairs 
-\begin{equation}
-	\{(w_i, m_i)\} \text{ and } \{(w_j', m_j')\},
-\end{equation}
-respectively. Then, $\{(w_i w_j', m_i m_j')\}$ gives component-multiplicity pairs for $\W{\rho_A \otimes \rho_B}$.
-\end{lemma}
-
-This is true because all components of $\W{\rho_A \otimes \rho_B}$ are of the form $w_i w_j'$ and 
-\begin{equation*}
-	\sum_{i=1}^{D_A}\sum_{j=1}^{D_B} m_i m_j' = \sum_{i=1}^{D_A} m_i \sum_{j=1}^{D_B} m_j' = d_A^2 d_B^2,
-\end{equation*}
-so the set $\{(w_i w_j', m_i m_j')\}$ contains exactly the Wigner components of $\W{\rho_A \otimes \rho_B}$ and no more.
-
-In the case of distillation protocols, we are interested in $n$--copies of a single Wigner distribution. For this, we have the following result, which follows from combinatorics.
-
-\begin{lemma}\label{lem:ncopycomponents}
-	Suppose $W_\rho(\x)$ has $D$ component-multiplicity pairs $\{(w_i, m_i)\}$.
-Then, $W_{\rho^{\otimes n}} (\x)$ has component-multiplicity pairs $\{(W_{\q}, M_{\q})\}$, where $\q$ runs through all $K$-component vectors with non-negative integer components that sum to $n$, and
-\begin{align}
-W_{\q} &= \prod_{i=1}^D w_i^{q_i} \label{eq:W}\\
-M_{\q} &= \binom{n}{q_1,q_2, \dots, q_d} \prod_{i=1}^D m_i^{q_i}, \label{eq:M}
-\end{align}
-where the term outside the product in the expression for $M_{\q}$ is the generalized binomial coefficient.
-\end{lemma}
-\begin{proof}
-	Denote by $C_D^n \coloneqq \{\bmk\}$ the set of all vectors $\bmk \coloneqq (k_1, \dots, k_D)$ with non-negative integer components that sum to $n$, i.e.
-	\begin{equation*}
-	0 \leq k_1, \dots, k_D \leq n \text{ and } k_1 + \dots + k_D = n.
-	\end{equation*}
-
-	We proceed by induction.	
-	Assume $n = 1$ and let $\bmk_i$ be the vector with its $i$-th component equal to 1 and 0's elsewhere.
-	The set $C_D^1$ consists of all vectors of this form, i.e. 
-\begin{equation*}
-	C_D^1 = \{ \bmk_i \}_{i=1,\dots,D}
-\end{equation*}
-	It is also true by direct calculation that
-\begin{equation*}
-	\left( W_{\bmk_i}, M_{\bmk_i} \right) = (w_i, m_i).
-\end{equation*}
-Therefore, $\{ (W_{\bmk}, M_{\bmk}) \}_{\bmk \in C_D^1}$ is a complete set of component-multiplicity pairs for $W$.
-
-	Assume that $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$ as given in~\cref{eq:M,eq:W} is a complete set of component-multiplicity pairs for the $n$--copy distribution $W^{\otimes n}$.
-	By construction, the distribution $W^{\otimes (n+1)} = W^{\otimes n} \otimes W$ is multiplicative, so it admits the complete set of component multiplicity pairs
-\begin{equation}
-	\{(W_{\bmk} w_i, M_{\bmk} m_i)\},\ \bmk \in C_D^n \text{ and } i=1,\dots,D.
-\end{equation}
-
-	Consider the component sum of the distribution $W^{\otimes (n+1)}$,
-\begin{align*}
-	&\sum_{\bmk \in C_D^n}\sum_{i=1}^D M_{\bmk} m_i W_{\bmk} w_i = \sum_{\bmk \in C_D^n} M_{\bmk}W_{\bmk} \sum_{i=1}^D m_i w_i =\\
-	&\sum_{\bmk \in C_D^n} \frac{n!}{k_1!\dots k_D!} \prod\limits_{i=1}^D {m_i}^{k_i}{w_i}^{k_i} \sum_{i=1}^D m_i w_i =\\
-	&\left( \sum_{i=1}^D m_i w_i \right)^n \left( \sum_{i=1}^D m_i w_i \right) = \left( \sum_{i=1}^D m_i w_i \right)^{n+1} =\\
-	&\sum_{\bmq \in C_D^{n+1}} M_{\bmq}W_{\bmq},
-\end{align*}
-where in the last expression, vectors $\bmq = (q_1, \dots, q_D)$ have non-negative integer components that sum to $(n+1)$ and 
-\begin{align*}
-	M_{\bmq} &= \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i},\\
-	W_{\bmq} &= \prod\limits_{i=1}^D {w_i}^{q_i}.
-\end{align*}
-We have used the multinomial theorem to proceed between lines 2-3 and lines 3-4 of the derivation.
-
-We have achieved a regrouping of the distribution components.
-Every component $W_{\bmq}$ is of the form $W_{\bmk} w_i$ with $q_i = k_i + 1$ and $q_j = k_j$ for $j\neq i$ and 
-\begin{align*}
-	\sum_{\bmq \in C_D^{n+1}}  \hspace{-6pt} M_{\bmq} =  \hspace{-10pt} \sum_{\bmq \in C_D^{n+1}} \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i} = 
-	\left( \sum_{i=1}^D m_i \right)^{n+1} \hspace{-10pt} = d^{n+1},
-\end{align*}
-which is the dimension of $W^{\otimes (n+1)}$.
-
-Therefore, $\{ (W_{\bmq}, M_{\bmq}) \}_{\bmq \in C_D^{n+1}}$ contains exactly the components of $W^{\otimes n}$ and no more, completing the proof.
-\end{proof}
-
-The rescaled distribution is also multiplicative, so a set of component-multiplicity pairs can be obtained for the $n$-copy rescaled distribution in the same fashion as for usual Wigner distributions.
-
-\subsection{Lorenz curve constraint independence}
-
-We now prove a result on the independence of the Lorenz curve constraints, stated in~\cref{sec:major_frag}.
+We now show that the relative majorization condition can be reduced to considering the elbows of the Lorenz curves.
 \begin{proposition}\label{thm:elbows}
@@
 The above theorem can be used in reducing the necessary distillation constraints derived via majorization in $\sigma$--fragments.
-
-\subsection{Technical properties of $\sigma$--fragments}
-
-\begin{proposition}\label{thm:frag_app}
-    Let $\R = (\F, \O)$ be a magic theory and $\sigma, \sigma' \in \F$. The following statements hold:
-    \begin{enumerate}
-        \item No $\sigma$--fragment of $\R$ is empty.
-        \item If a free operation leaves two states invariant, then it also leaves their mixtures invariant, 
-        \begin{equation*}
-            \O_{\sigma} \cap \O_{\sigma'} \subseteq \O_{p\sigma + (1-p)\sigma'}\ \text{for any}\ p \in [0,1].
-        \end{equation*}
-    \end{enumerate}
-\end{proposition}
-\begin{proof}$ $\vspace{-12pt}\\
-
-\begin{enumerate}
-    \item The identity channel $1_{\rm{C}}$ belongs to every $\sigma$--fragment, as $1_{\rm{C}} \in \O$ and $1_{\rm{C}}\sigma = \sigma$ for all $\sigma \in \F$.
-
-    \item Let $\E \in \O_{\sigma} \cap \O_{\sigma'}$.
-    Then $\E \in \cptp$ and corresponds to stochastic Wigner distribution $\W{\E}$ such that $\W{\E} \W{\sigma} = \W{\sigma}$ and $\W{\E} \W{\sigma'} = \W{\sigma'}$.
-    Then, $\W{\E} \W{p\sigma + (1-p)\sigma'} = \W{p\sigma + (1-p)\sigma'}$ for any $p \in [0,1]$ due to the additive property~\ref{en:w4} of the Wigner distribution, implying that state $p\sigma + (1-p)\sigma'$ is also left invariant by $\E$.
-\end{enumerate}
-\vspace{-20pt}
-\end{proof}
 
@@
 
-\section{Lorenz curves in the unital fragment}
+\section{Lorenz curves for unital processes}
 \label{app:lcsu_technical}
@@
 
-\newpage
 We can get explicit expressions for all $9^{n}$ points of the Lorenz curve $\lc{\rho_{\rm{S}}(\epsilon)^{\otimes n}}{(\id/3)^{\otimes n}}$, in terms of the elbow coordinates:
@@
 The following result shows that if the energy eigenbasis is a stabilizer basis then things simplify more.
-\begin{proposition} 
+\begin{proposition} \label{sharp-phi}
 	Let $H$ be a Hamiltonian $H$ with spectrum $\{E_k\}_{k \in \mathbb{Z}_d}$.
@@
 
+\subsection{Component-multiplicity pairs}
+\label{app:cmpairs}
+
+In general, a $1$--copy $d$--dimensional state $\rho$ is described by its $d^2$--dimensional Wigner distribution $\W{\rho}(\bmx)$. 
+The distribution $\W{\rho}(\bmx)$ is defined on the phase space, but it can be convenient to re-express this using vector notation.
+
+To each Wigner distribution $W_\rho(\x)$ we can associate \emph{component-multiplicity} pairs $\{(w_i, m_i)\}$ where the value $w_i$ occurs in the distribution $W_\rho(\x)$ with multiplicity $m_i$.
+
+As an example, for the Strange state $\rho_S := \rho_S(\epsilon=0)$ with
+\begin{equation}
+W_{\rho_S}(\x) = (-1/3, 1/6,  1/6,  1/6,  1/6,  1/6,  1/6,  1/6,  1/6)
+\end{equation}
+we have the component-multiplicity pairs: $\{( -1/3, 1), ( 1/6, 8)\}$.
+However, we might also wish more freedom and not require that the different $w_i$ values are all distinct.
+For example, the component-multiplity pairs $\{(-1/3, 1), (1/6, 2), (1/6, 3), (1/6, 3)\}$ also describe $W_{\rho_S}(\x)$.
+
+This representation is more compact when a Wigner distribution has a lot of multiplicities, and allows for simple handling of multiple copies via the following fact.
+\begin{lemma}
+Consider two Wigner distributions $\W{\rho_A}, \W{\rho_B}$ with component-multiplicity pairs 
+\begin{equation}
+	\{(w_i, m_i)\} \text{ and } \{(w_j', m_j')\},
+\end{equation}
+respectively. Then, $\{(w_i w_j', m_i m_j')\}$ gives component-multiplicity pairs for $\W{\rho_A \otimes \rho_B}$.
+\end{lemma}
+
+This is true because all components of $\W{\rho_A \otimes \rho_B}$ are of the form $w_i w_j'$ and 
+\begin{equation*}
+	\sum_{i=1}^{D_A}\sum_{j=1}^{D_B} m_i m_j' = \sum_{i=1}^{D_A} m_i \sum_{j=1}^{D_B} m_j' = d_A^2 d_B^2,
+\end{equation*}
+so the set $\{(w_i w_j', m_i m_j')\}$ contains exactly the Wigner components of $\W{\rho_A \otimes \rho_B}$ and no more.
+
+In the case of distillation protocols, we are interested in $n$--copies of a single Wigner distribution. For this, we have the following result, which follows from combinatorics.
+
+\begin{lemma}\label{lem:ncopycomponents}
+	Suppose $W_\rho(\x)$ has $D$ component-multiplicity pairs $\{(w_i, m_i)\}$.
+Then, $W_{\rho^{\otimes n}} (\x)$ has component-multiplicity pairs $\{(W_{\q}, M_{\q})\}$, where $\q$ runs through all $K$-component vectors with non-negative integer components that sum to $n$, and
+\begin{align}
+W_{\q} &= \prod_{i=1}^D w_i^{q_i} \label{eq:W}\\
+M_{\q} &= \binom{n}{q_1,q_2, \dots, q_d} \prod_{i=1}^D m_i^{q_i}, \label{eq:M}
+\end{align}
+where the term outside the product in the expression for $M_{\q}$ is the generalized binomial coefficient.
+\end{lemma}
+\begin{proof}
+	Denote by $C_D^n \coloneqq \{\bmk\}$ the set of all vectors $\bmk \coloneqq (k_1, \dots, k_D)$ with non-negative integer components that sum to $n$, i.e.
+	\begin{equation*}
+	0 \leq k_1, \dots, k_D \leq n \text{ and } k_1 + \dots + k_D = n.
+	\end{equation*}
+
+	We proceed by induction.	
+	Assume $n = 1$ and let $\bmk_i$ be the vector with its $i$-th component equal to 1 and 0's elsewhere.
+	The set $C_D^1$ consists of all vectors of this form, i.e. 
+\begin{equation*}
+	C_D^1 = \{ \bmk_i \}_{i=1,\dots,D}
+\end{equation*}
+	It is also true by direct calculation that
+\begin{equation*}
+	\left( W_{\bmk_i}, M_{\bmk_i} \right) = (w_i, m_i).
+\end{equation*}
+Therefore, $\{ (W_{\bmk}, M_{\bmk}) \}_{\bmk \in C_D^1}$ is a complete set of component-multiplicity pairs for $W$.
+
+	Assume that $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$ as given in~\cref{eq:M,eq:W} is a complete set of component-multiplicity pairs for the $n$--copy distribution $W^{\otimes n}$.
+	By construction, the distribution $W^{\otimes (n+1)} = W^{\otimes n} \otimes W$ is multiplicative, so it admits the complete set of component multiplicity pairs
+\begin{equation}
+	\{(W_{\bmk} w_i, M_{\bmk} m_i)\},\ \bmk \in C_D^n \text{ and } i=1,\dots,D.
+\end{equation}
+
+	Consider the component sum of the distribution $W^{\otimes (n+1)}$,
+\begin{align*}
+	&\sum_{\bmk \in C_D^n}\sum_{i=1}^D M_{\bmk} m_i W_{\bmk} w_i = \sum_{\bmk \in C_D^n} M_{\bmk}W_{\bmk} \sum_{i=1}^D m_i w_i =\\
+	&\sum_{\bmk \in C_D^n} \frac{n!}{k_1!\dots k_D!} \prod\limits_{i=1}^D {m_i}^{k_i}{w_i}^{k_i} \sum_{i=1}^D m_i w_i =\\
+	&\left( \sum_{i=1}^D m_i w_i \right)^n \left( \sum_{i=1}^D m_i w_i \right) = \left( \sum_{i=1}^D m_i w_i \right)^{n+1} =\\
+	&\sum_{\bmq \in C_D^{n+1}} M_{\bmq}W_{\bmq},
+\end{align*}
+where in the last expression, vectors $\bmq = (q_1, \dots, q_D)$ have non-negative integer components that sum to $(n+1)$ and 
+\begin{align*}
+	M_{\bmq} &= \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i},\\
+	W_{\bmq} &= \prod\limits_{i=1}^D {w_i}^{q_i}.
+\end{align*}
+We have used the multinomial theorem to proceed between lines 2-3 and lines 3-4 of the derivation.
+
+We have achieved a regrouping of the distribution components.
+Every component $W_{\bmq}$ is of the form $W_{\bmk} w_i$ with $q_i = k_i + 1$ and $q_j = k_j$ for $j\neq i$ and 
+\begin{align*}
+	\sum_{\bmq \in C_D^{n+1}}  \hspace{-6pt} M_{\bmq} =  \hspace{-10pt} \sum_{\bmq \in C_D^{n+1}} \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i} = 
+	\left( \sum_{i=1}^D m_i \right)^{n+1} \hspace{-10pt} = d^{n+1},
+\end{align*}
+which is the dimension of $W^{\otimes (n+1)}$.
+
+Therefore, $\{ (W_{\bmq}, M_{\bmq}) \}_{\bmq \in C_D^{n+1}}$ contains exactly the components of $W^{\otimes n}$ and no more, completing the proof.
+\end{proof}
+
+The rescaled distribution is also multiplicative, so a set of component-multiplicity pairs can be obtained for the $n$-copy rescaled distribution in the same fashion as for usual Wigner distributions.
+
 \end{document}

### 2021-05-17 magic_paper.tex
Responded to blue comments

@@
 \nick{re-write based on new relative majorisation approach}
-The past few years have seen rapid progress towards the goal of a fault-tolerant quantum computer~\cite{Fowler_2012, Herrera_2010, Nickerson_2014, Nikahd_2017, chao_2018, lin_pieceable_2020, Lin_2020, Bourassa_2021} \ddd{[delete the first two from the bibliography - they are ancient and the second is mine, so it looks like bad self-citing]}.
+The past few years have seen rapid progress towards the goal of a fault-tolerant quantum computer~\cite{Nickerson_2014, Nikahd_2017, chao_2018, lin_pieceable_2020, Lin_2020, Bourassa_2021}.
 However, many challenges remain and there is increasing need for theory to take into account physical limitations of the hardware involved.
@@
 
-We approach this problem using tools from statistical mechanics and recent work from the overlap of thermodynamics and quantum information theory~\cite{cit:gour, cit:gour2}\nick{You had a specific review in mind I think, which one?} \ddd{[cite the Danzig paper from the early 2000s cite thermo-majorization Horodecki Oppenheim, cite the ``second laws'' paper by Brandao et al, cite Matteo's review, cite review articles by Goold et al, and Janet Anders]}.
+We approach this problem using tools from statistical mechanics and recent work from the overlap of thermodynamics and quantum information theory~\cite{cit:horodecki2, Brandao_2015, Vinjanampathy_2016, Goold_2016, cit:lostaglio, cit:gour}\nick{Can't find Danzig's paper anywhere}.
 In particular, we shall view \emph{magic as a form of free energy}, relative to the set of stabilizer states.
@@
     \caption{\textbf{Analysing magic protocols relative to a stabilizer reference state.} 
-	A magic protocol aims to turn $n$ copies of some magic state $\rho_1$ to $m$ copies of some other state $\rho_2$.
-	Constraints on the efficiency of the protocol can be imposed by considering its action on an separate probe state $\tau$.
-	\nick{How do we improve the illustration?}\ddd{[I would have two separate box transformations, the top one has $\rho$ fed into $\E$, the bottom one has $\tau$ fed into it.
-Then put the relevant property (e.g.
-$\epsilon$ for $\rho$, and $F$ for $\tau$ next to the states.
-If viable then have $\phi$ somehow linking the top and bottom -- conveying it is a hybrid quantity in some sense.]}
+	A magic protocol aims to turn $n$ copies of some magic state $\rho$ to $m$ copies of some other state $\rho'$.
+	Constraints on the efficiency of the protocol can be imposed by considering its action on a separate probe state $\tau$.
     }
@@
 
-The first elbow constraint involves a simple interpolation, done in~\cref{app:elb_constraint}, in order to find the coordinates of both Lorenz curve points at the location where the first elbow occurs.
+The first elbow constraint involves a simple interpolation, done in~\cref{prop:first_elb}, in order to find the coordinates of both Lorenz curve points at the location where the first elbow occurs. 
 Comparing these two points leads to the bound
@@
 \end{equation}
-with $n \gg 1$ \nick{Should we replace $m$ with $R n$ or $n'$ throughout?}\ddd{[Nah, $m$ is simpler than $Rn$ -- you gotta resist the urge to complicate expressions, unless it's needed.
-*Bad* habit.]}, $\epsilon' <\epsilon$ and $\E$ denoting the quantum channel induced by the protocol.
+with $n \gg 1$, $\epsilon' <\epsilon$ and $\E$ denoting the quantum channel induced by the protocol.
 We can now provide distillation bounds that depend on energetic and entropic aspects of the protocol.
@@
 If the largest rescaled component of a state is distinct with no multiplicities, then these coordinates correspond to the first elbow of the corresponding Lorenz curve, whereas if it appears multiple times, then the coordinates derived correspond to a point on the interior of the line segment connecting the origin to the first elbow.
-In both cases, the distillation bound remains the same, as is clear by its derivation in~\cref{app:elb_constraint}, given by $L_0/x_0 \geq L'_0/x'_0$, leading to
+In both cases, the distillation bound remains the same, as is clear by its derivation in~\cref{prop:first_elb}, given by $L_0/x_0 \geq L'_0/x'_0$, leading to
 \begin{equation}
@@
 \end{proof}
+
+\subsection{Component-multiplicity pairs}
+\label{app:cmpairs}
+
+In general, a $1$--copy $d$--dimensional state $\rho$ is described by its $d^2$--dimensional Wigner distribution $\W{\rho}(\bmx)$. 
+The distribution $\W{\rho}(\bmx)$ is defined on the phase space, but it can be convenient to re-express this using vector notation.
+
+To each Wigner distribution $W_\rho(\x)$ we can associate \emph{component-multiplicity} pairs $\{(w_i, m_i)\}$ where the value $w_i$ occurs in the distribution $W_\rho(\x)$ with multiplicity $m_i$.
+
+As an example, for the Strange state $\rho_S := \rho_S(\epsilon=0)$ with
+\begin{equation}
+W_{\rho_S}(\x) = (-1/3, 1/6,  1/6,  1/6,  1/6,  1/6,  1/6,  1/6,  1/6)
+\end{equation}
+we have the component-multiplicity pairs: $\{( -1/3, 1), ( 1/6, 8)\}$.
+However, we might also wish more freedom and not require that the different $w_i$ values are all distinct.
+For example, the component-multiplity pairs $\{(-1/3, 1), (1/6, 2), (1/6, 3), (1/6, 3)\}$ also describe $W_{\rho_S}(\x)$.
+
+This representation is more compact when a Wigner distribution has a lot of multiplicities, and allows for simple handling of multiple copies via the following fact.
+\begin{lemma}
+Consider two Wigner distributions $\W{\rho_A}, \W{\rho_B}$ with component-multiplicity pairs 
+\begin{equation}
+	\{(w_i, m_i)\} \text{ and } \{(w_j', m_j')\},
+\end{equation}
+respectively. Then, $\{(w_i w_j', m_i m_j')\}$ gives component-multiplicity pairs for $\W{\rho_A \otimes \rho_B}$.
+\end{lemma}
+
+This is true because all components of $\W{\rho_A \otimes \rho_B}$ are of the form $w_i w_j'$ and 
+\begin{equation*}
+	\sum_{i=1}^{D_A}\sum_{j=1}^{D_B} m_i m_j' = \sum_{i=1}^{D_A} m_i \sum_{j=1}^{D_B} m_j' = d_A^2 d_B^2,
+\end{equation*}
+so the set $\{(w_i w_j', m_i m_j')\}$ contains exactly the Wigner components of $\W{\rho_A \otimes \rho_B}$ and no more.
+
+In the case of distillation protocols, we are interested in $n$--copies of a single Wigner distribution. For this, we have the following result, which follows from combinatorics.
+
+\begin{lemma}\label{lem:ncopycomponents}
+	Suppose $W_\rho(\x)$ has $D$ component-multiplicity pairs $\{(w_i, m_i)\}$.
+Then, $W_{\rho^{\otimes n}} (\x)$ has component-multiplicity pairs $\{(W_{\q}, M_{\q})\}$, where $\q$ runs through all $K$-component vectors with non-negative integer components that sum to $n$, and
+\begin{align}
+W_{\q} &= \prod_{i=1}^D w_i^{q_i} \label{eq:W}\\
+M_{\q} &= \binom{n}{q_1,q_2, \dots, q_d} \prod_{i=1}^D m_i^{q_i}, \label{eq:M}
+\end{align}
+where the term outside the product in the expression for $M_{\q}$ is the generalized binomial coefficient.
+\end{lemma}
+\begin{proof}
+	Denote by $C_D^n \coloneqq \{\bmk\}$ the set of all vectors $\bmk \coloneqq (k_1, \dots, k_D)$ with non-negative integer components that sum to $n$, i.e.
+	\begin{equation*}
+	0 \leq k_1, \dots, k_D \leq n \text{ and } k_1 + \dots + k_D = n.
+	\end{equation*}
+
+	We proceed by induction.	
+	Assume $n = 1$ and let $\bmk_i$ be the vector with its $i$-th component equal to 1 and 0's elsewhere.
+	The set $C_D^1$ consists of all vectors of this form, i.e. 
+\begin{equation*}
+	C_D^1 = \{ \bmk_i \}_{i=1,\dots,D}
+\end{equation*}
+	It is also true by direct calculation that
+\begin{equation*}
+	\left( W_{\bmk_i}, M_{\bmk_i} \right) = (w_i, m_i).
+\end{equation*}
+Therefore, $\{ (W_{\bmk}, M_{\bmk}) \}_{\bmk \in C_D^1}$ is a complete set of component-multiplicity pairs for $W$.
+
+	Assume that $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$ as given in~\cref{eq:M,eq:W} is a complete set of component-multiplicity pairs for the $n$--copy distribution $W^{\otimes n}$.
+	By construction, the distribution $W^{\otimes (n+1)} = W^{\otimes n} \otimes W$ is multiplicative, so it admits the complete set of component multiplicity pairs
+\begin{equation}
+	\{(W_{\bmk} w_i, M_{\bmk} m_i)\},\ \bmk \in C_D^n \text{ and } i=1,\dots,D.
+\end{equation}
+
+	Consider the component sum of the distribution $W^{\otimes (n+1)}$,
+\begin{align*}
+	&\sum_{\bmk \in C_D^n}\sum_{i=1}^D M_{\bmk} m_i W_{\bmk} w_i = \sum_{\bmk \in C_D^n} M_{\bmk}W_{\bmk} \sum_{i=1}^D m_i w_i =\\
+	&\sum_{\bmk \in C_D^n} \frac{n!}{k_1!\dots k_D!} \prod\limits_{i=1}^D {m_i}^{k_i}{w_i}^{k_i} \sum_{i=1}^D m_i w_i =\\
+	&\left( \sum_{i=1}^D m_i w_i \right)^n \left( \sum_{i=1}^D m_i w_i \right) = \left( \sum_{i=1}^D m_i w_i \right)^{n+1} =\\
+	&\sum_{\bmq \in C_D^{n+1}} M_{\bmq}W_{\bmq},
+\end{align*}
+where in the last expression, vectors $\bmq = (q_1, \dots, q_D)$ have non-negative integer components that sum to $(n+1)$ and 
+\begin{align*}
+	M_{\bmq} &= \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i},\\
+	W_{\bmq} &= \prod\limits_{i=1}^D {w_i}^{q_i}.
+\end{align*}
+We have used the multinomial theorem to proceed between lines 2-3 and lines 3-4 of the derivation.
+
+We have achieved a regrouping of the distribution components.
+Every component $W_{\bmq}$ is of the form $W_{\bmk} w_i$ with $q_i = k_i + 1$ and $q_j = k_j$ for $j\neq i$ and 
+\begin{align*}
+	\sum_{\bmq \in C_D^{n+1}}  \hspace{-6pt} M_{\bmq} =  \hspace{-10pt} \sum_{\bmq \in C_D^{n+1}} \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i} = 
+	\left( \sum_{i=1}^D m_i \right)^{n+1} \hspace{-10pt} = d^{n+1},
+\end{align*}
+which is the dimension of $W^{\otimes (n+1)}$.
+
+Therefore, $\{ (W_{\bmq}, M_{\bmq}) \}_{\bmq \in C_D^{n+1}}$ contains exactly the components of $W^{\otimes n}$ and no more, completing the proof.
+\end{proof}
+
+The rescaled distribution is also multiplicative, so a set of component-multiplicity pairs can be obtained for the $n$-copy rescaled distribution in the same fashion as for usual Wigner distributions.
 
@@
 There are four combinations of coordinates, depending on the noise parameters $\epsilon, \epsilon'$ for the input and output states.
-In each of these combinations, we simply use the first elbow constraint, as described in~\cref{app:elb_constraint}, and manipulate the coordinates as in the proof of~\cref{thm:free-energy}, leading to the bounds in the statement of the theorem.
+In each of these combinations, we simply use the first elbow constraint, as described in~\cref{prop:first_elb}, and manipulate the coordinates as in the proof of~\cref{thm:free-energy}, leading to the bounds in the statement of the theorem.
 \end{proof}
@@
 
-\subsection{Component-multiplicity pairs}
-\label{app:cmpairs}
-
-In general, a $1$--copy $d$--dimensional state $\rho$ is described by its $d^2$--dimensional Wigner distribution $\W{\rho}(\bmx)$. 
-The distribution $\W{\rho}(\bmx)$ is defined on the phase space, but it can be convenient to re-express this using vector notation.
-
-To each Wigner distribution $W_\rho(\x)$ we can associate \emph{component-multiplicity} pairs $\{(w_i, m_i)\}$ where the value $w_i$ occurs in the distribution $W_\rho(\x)$ with multiplicity $m_i$.
-
-As an example, for the Strange state $\rho_S := \rho_S(\epsilon=0)$ with
-\begin{equation}
-W_{\rho_S}(\x) = (-1/3, 1/6,  1/6,  1/6,  1/6,  1/6,  1/6,  1/6,  1/6)
-\end{equation}
-we have the component-multiplicity pairs: $\{( -1/3, 1), ( 1/6, 8)\}$.
-However, we might also wish more freedom and not require that the different $w_i$ values are all distinct.
-For example, the component-multiplity pairs $\{(-1/3, 1), (1/6, 2), (1/6, 3), (1/6, 3)\}$ also describe $W_{\rho_S}(\x)$.
-
-This representation is more compact when a Wigner distribution has a lot of multiplicities, and allows for simple handling of multiple copies via the following fact.
-\begin{lemma}
-Consider two Wigner distributions $\W{\rho_A}, \W{\rho_B}$ with component-multiplicity pairs 
-\begin{equation}
-	\{(w_i, m_i)\} \text{ and } \{(w_j', m_j')\},
-\end{equation}
-respectively. Then, $\{(w_i w_j', m_i m_j')\}$ gives component-multiplicity pairs for $\W{\rho_A \otimes \rho_B}$.
-\end{lemma}
-
-This is true because all components of $\W{\rho_A \otimes \rho_B}$ are of the form $w_i w_j'$ and 
-\begin{equation*}
-	\sum_{i=1}^{D_A}\sum_{j=1}^{D_B} m_i m_j' = \sum_{i=1}^{D_A} m_i \sum_{j=1}^{D_B} m_j' = d_A^2 d_B^2,
-\end{equation*}
-so the set $\{(w_i w_j', m_i m_j')\}$ contains exactly the Wigner components of $\W{\rho_A \otimes \rho_B}$ and no more.
-
-In the case of distillation protocols, we are interested in $n$--copies of a single Wigner distribution. For this, we have the following result, which follows from combinatorics.
-
-\begin{lemma}\label{lem:ncopycomponents}
-	Suppose $W_\rho(\x)$ has $D$ component-multiplicity pairs $\{(w_i, m_i)\}$.
-Then, $W_{\rho^{\otimes n}} (\x)$ has component-multiplicity pairs $\{(W_{\q}, M_{\q})\}$, where $\q$ runs through all $K$-component vectors with non-negative integer components that sum to $n$, and
-\begin{align}
-W_{\q} &= \prod_{i=1}^D w_i^{q_i} \label{eq:W}\\
-M_{\q} &= \binom{n}{q_1,q_2, \dots, q_d} \prod_{i=1}^D m_i^{q_i}, \label{eq:M}
-\end{align}
-where the term outside the product in the expression for $M_{\q}$ is the generalized binomial coefficient.
-\end{lemma}
-\begin{proof}
-	Denote by $C_D^n \coloneqq \{\bmk\}$ the set of all vectors $\bmk \coloneqq (k_1, \dots, k_D)$ with non-negative integer components that sum to $n$, i.e.
-	\begin{equation*}
-	0 \leq k_1, \dots, k_D \leq n \text{ and } k_1 + \dots + k_D = n.
-	\end{equation*}
-
-	We proceed by induction.	
-	Assume $n = 1$ and let $\bmk_i$ be the vector with its $i$-th component equal to 1 and 0's elsewhere.
-	The set $C_D^1$ consists of all vectors of this form, i.e. 
-\begin{equation*}
-	C_D^1 = \{ \bmk_i \}_{i=1,\dots,D}
-\end{equation*}
-	It is also true by direct calculation that
-\begin{equation*}
-	\left( W_{\bmk_i}, M_{\bmk_i} \right) = (w_i, m_i).
-\end{equation*}
-Therefore, $\{ (W_{\bmk}, M_{\bmk}) \}_{\bmk \in C_D^1}$ is a complete set of component-multiplicity pairs for $W$.
-
-	Assume that $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$ as given in~\cref{eq:M,eq:W} is a complete set of component-multiplicity pairs for the $n$--copy distribution $W^{\otimes n}$.
-	By construction, the distribution $W^{\otimes (n+1)} = W^{\otimes n} \otimes W$ is multiplicative, so it admits the complete set of component multiplicity pairs
-\begin{equation}
-	\{(W_{\bmk} w_i, M_{\bmk} m_i)\},\ \bmk \in C_D^n \text{ and } i=1,\dots,D.
-\end{equation}
-
-	Consider the component sum of the distribution $W^{\otimes (n+1)}$,
-\begin{align*}
-	&\sum_{\bmk \in C_D^n}\sum_{i=1}^D M_{\bmk} m_i W_{\bmk} w_i = \sum_{\bmk \in C_D^n} M_{\bmk}W_{\bmk} \sum_{i=1}^D m_i w_i =\\
-	&\sum_{\bmk \in C_D^n} \frac{n!}{k_1!\dots k_D!} \prod\limits_{i=1}^D {m_i}^{k_i}{w_i}^{k_i} \sum_{i=1}^D m_i w_i =\\
-	&\left( \sum_{i=1}^D m_i w_i \right)^n \left( \sum_{i=1}^D m_i w_i \right) = \left( \sum_{i=1}^D m_i w_i \right)^{n+1} =\\
-	&\sum_{\bmq \in C_D^{n+1}} M_{\bmq}W_{\bmq},
-\end{align*}
-where in the last expression, vectors $\bmq = (q_1, \dots, q_D)$ have non-negative integer components that sum to $(n+1)$ and 
-\begin{align*}
-	M_{\bmq} &= \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i},\\
-	W_{\bmq} &= \prod\limits_{i=1}^D {w_i}^{q_i}.
-\end{align*}
-We have used the multinomial theorem to proceed between lines 2-3 and lines 3-4 of the derivation.
-
-We have achieved a regrouping of the distribution components.
-Every component $W_{\bmq}$ is of the form $W_{\bmk} w_i$ with $q_i = k_i + 1$ and $q_j = k_j$ for $j\neq i$ and 
-\begin{align*}
-	\sum_{\bmq \in C_D^{n+1}}  \hspace{-6pt} M_{\bmq} =  \hspace{-10pt} \sum_{\bmq \in C_D^{n+1}} \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i} = 
-	\left( \sum_{i=1}^D m_i \right)^{n+1} \hspace{-10pt} = d^{n+1},
-\end{align*}
-which is the dimension of $W^{\otimes (n+1)}$.
-
-Therefore, $\{ (W_{\bmq}, M_{\bmq}) \}_{\bmq \in C_D^{n+1}}$ contains exactly the components of $W^{\otimes n}$ and no more, completing the proof.
-\end{proof}
-
-The rescaled distribution is also multiplicative, so a set of component-multiplicity pairs can be obtained for the $n$-copy rescaled distribution in the same fashion as for usual Wigner distributions.
-
 \end{document}

### 2021-05-23 magic_paper.tex
98 percent happy with appendices. Couple of minor things to check/agree on.

@@
 
-We approach this problem using tools from statistical mechanics and recent work from the overlap of thermodynamics and quantum information theory~\cite{cit:horodecki2, Brandao_2015, Vinjanampathy_2016, Goold_2016, cit:lostaglio, cit:gour}\nick{Can't find Danzig's paper anywhere}.
+We approach this problem using tools from statistical mechanics and recent work from the overlap of thermodynamics and quantum information theory~\cite{cit:horodecki2, Brandao_2015, Vinjanampathy_2016, Goold_2016, cit:lostaglio, cit:gour}\nick{Can't find Danzig's paper anywhere}\ddd{[Remembered name incorrectly, is this one: Janzing, Dominik, et al.
+"Thermodynamic cost of reliability and low temperatures: tightening Landauer's principle and the second law." Put this one first in list -- people always miss it, but it is the first.] }.
 In particular, we shall view \emph{magic as a form of free energy}, relative to the set of stabilizer states.
@@
 	Constraints on the efficiency of the protocol can be imposed by considering its action on a separate probe state $\tau$.
-    }
+    } \ddd{[Not the clearest - we can zoom-chat on this.]}
     \label{fig:sketch}
@@
 In particular, the energetic term $\phi$ quantifies the degree to which the negativity in the Wigner representation can be ascribed a sharp energetic value for the given Hamiltonian of the system.
-Its form is similar to $F$, and so can informally be viewed as a `magic free energy' term, associated to a `magic partition function' $\zeta$.
+Its form is similar to $F$, and so can informally be viewed as a `magic free energy' term, associated to what can informally be viewed as a `partition function' $\zeta$.
 The coefficients $\alpha_k$ may be negative for some $k$, when the Hamiltonian eigen-decomposes into non-stabilizer states, but the quantity $\phi$ is always well-defined, since the function $\zeta$ is a positive multiple of the stabilizer Wigner component $W_\tau(0,0)$, as seen in the proof of the theorem.
-In the case that the system's Hamiltonian $H$ has an eigenbasis consisting of stabilizer states then we show in Appendix \ref{sharp-phi} that $\phi$ takes on a sharp, temperature-independent value $\phi \in \{E_0,E_1,E_2\}$.
+In the case that the system's Hamiltonian $H$ has an eigenbasis consisting of stabilizer states then we show in Appendix \ref{sharp-phi} that $\phi$ takes on a sharp, temperature-independent energy value $\phi \in \{E_0,E_1,E_2\}$.
 
@@
 
+\begin{lemma}\label{L-concave} Let $\p$ be a quasi-probability distribution and let $\r$ be a probability distribution with strictly non-zero components.
+Then $L_{\p|\r}(x)$ is a concave function on $[0,1]$.
+\begin{proof}Let $L_{\p|\r}(x)$ attain its maximum at $x=x_\star$.
+Then from the definition, the function is continuous, monotone increasing on $[0,x_\star]$, and monotone decreasing on $[x_\star, 1]$.
+Consider $a,b \in [0,1]$ with $a <b$ and some probability $q \in [0,1]$.
+If $a$ and $b$ both lie in either the interval $[0,x_\star]$ or $[x_\star, 1]$ then concavity follows immediately.
+Otherwise $a$ is in the first interval and $b$ in the second interval.
+If $w=qa + (1-q)b$ lies in the first interval then
+\begin{align}
+qL_{\p|\r}(a) + (1-q)L_{\p|\r}(b) &\le qL_{\p|\r}(a) + (1-q)L_{\p|\r}(x_\star)\nonumber\\
+& \le L_{\p|\r}(w)
+\end{align}
+from monotonicity on the first interval. Otherwise $w$ lies in the second interval and
+\begin{align}
+qL_{\p|\r}(a) + (1-q)L_{\p|\r}(b) &\le qL_{\p|\r}(x_\star) + (1-q)L_{\p|\r}(b)\nonumber\\
+& \le L_{\p|\r}(w)
+\end{align}
+which follows from monotonicity on the second interval. Therefore the Lorenz curve is concave on $[0,1]$.
+\end{proof}
+\end{lemma}
+
 The following result is used in the text to relate relative majorization of quasi-distributions to their Lorenz curves.
@@
 \begin{theorem}
-	Given a magic state $\rho$, the maximum $L_\star$ of its Lorenz curve $\lc{\rho}{\sigma}(x)$ is independent of the $\sigma$--fragment and equal to $1+\sn{\rho}$.
-Moreover, the majorization constraint is stronger than mana in every fragment.
+	Given a magic state $\rho$, the maximum value $L_\star$ attained by the Lorenz curve $\lc{\rho}{\sigma}(x)$ is independent of the $\sigma$--fragment and equal to $1+\sn{\rho}$.
+Moreover, the relative majorization constraint is stronger than mana in every fragment.
 \end{theorem}
@@
 
-Then, given any coordinates $(x, L)$ and $(x', L')$ of the input and output Lorenz curves respectively, where $0 < x \leq X_0$ and $0 < x' \leq X'_0$, the process is possible only if
+Then, given any coordinates $(x, L)$ and $(x', L')$ on the input and output Lorenz curves respectively, where $0 < x \leq X_0$ and $0 < x' \leq X'_0$, the process is possible only if
 \begin{equation}\label{eq:first_elb_bound1}
@@
 \end{proposition}
+\ddd{[I think the following is a more direct/informative proof]}
+\ddd{\begin{proof} If the transformation is possible then $L_{\rho|\sigma}(x) \ge L_{\rho'|\sigma'} (x)$ for all $x$ in $[0,1]$.
+If we restrict to the initial linear region segment of $L_{\rho|\sigma}(x)$ joining $(0,0)$ to $(X_0,L_0)$ then we require this to be above the initial linear segment of $L_{\rho'|\sigma'}(x)$ joining $(0,0)$ to $(X_0', L_0')$.
+Since both these linear segments go through the origin this condition implies that the slope of the initial segment of the input Lorenz curve must be greater than or equal to the slope of the initial segment of the output Lorenz curve.
+This slope constraint is then equivalent to Equation \ref{eq:first_elb_bound1}.
+\end{proof}}
 \begin{proof}
@@
 
-We now show that the relative majorization condition can be reduced to considering the elbows of the Lorenz curves.
+We now show that the relative majorization condition can be reduced to considering the elbows of the output Lorenz curve.
 \begin{proposition}\label{thm:elbows}
-	Let $\rho, \rho'$ be two quantum states with Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\rho'}{\sigma'}(x)$ in the $\sigma$--fragment.
-
-	Let $t$ be the number of elbows of $\lc{\rho'}{\sigma'}(x)$ at locations $x_1, \dots, x_t$.
-
+	Let $\rho, \rho'$ be any two quantum states with Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\rho'}{\sigma'}(x)$, where $\sigma, \sigma'$ are states with positive Wigner distributions.
+Assume that $\lc{\rho'}{\sigma'}(x)$ has $t$ elbows at locations $x_1, \dots, x_t$.
 Then, $\lc{\rho}{\sigma}(x) \geq \lc{\rho'}{\sigma'}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\rho'}{\sigma'}(x_{i})$ for all $i =1,\dots,t$.
@@
 \begin{proof}	
-	$\lc{\rho}{\sigma}(x) \geq \lc{\rho'}{\sigma'}(x)$ for all $x \in [0,1]$ trivially implies $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\rho'}{\sigma'}(x_{i})$ for all $i = 1,\dots,n'$.
+If $\lc{\rho}{\sigma}(x) \geq \lc{\rho'}{\sigma'}(x)$ for all $x \in [0,1]$ then the condition on the elbows trivially follows.
+
+\ddd{Conversely, assume $L_{\rho|\sigma}(x_i) \ge L_{\rho'|\sigma'}(x_i)$ for all $i=1,\dots t$.
+Suppose on the contrary that $L_{\rho|\sigma}(x)$ dips below $L_{\rho'|\sigma'}(x)$ at some point $y$ where $x_i < y < x_{i+1}$ for some $i$.
+Then this implies
+\begin{align}
+L_{\rho|\sigma}(x_i) &\ge L_{\rho'|\sigma'}(x_i) \nonumber \\
+L_{\rho|\sigma}(y) & <L_{\rho'|\sigma'}(y) \nonumber \\
+L_{\rho|\sigma}(x_{i+1}) &\ge L_{\rho'|\sigma'}(x_{i+1}).
+\end{align}
+However since $L_{\rho'|\sigma'}(x)$ is linear between $x_i$ and $x_{i+1}$, the above conditions imply that $L_{\rho|\sigma}(x)$ is not a concave function, which contradicts Lemma \ref{L-concave}.
+Therefore $L_{\rho|\sigma}(x) \ge L_{\rho'|\sigma'}(x)$ for all $x$ in $[0,1]$.
+}
 
@@
 \end{proof}
-The above theorem can be used in reducing the necessary distillation constraints derived via majorization in $\sigma$--fragments.
-
-Any free state $\sigma \in \F$ corresponds to a $d^2$--dimensional probability distribution $\W{\sigma}$ and any free operation $\E \in \O$ corresponds to a $d^2 \times d^2$ stochastic matrix (or conditional probability distribution) $\W{\E}$.
-Note that these mappings are one-to-one due to the orthogonality of the phase-point operators as an operator basis.
-Note further that free states $\F$ are mapped onto a \emph{strict subset} of the set of probability distributions.
-As a counterexample, the sharp $d^2$--dimensional probability distribution $(1, 0, \dots, 0)$ does not correspond to any qudit Wigner distribution because of the boundedness condition in~\cref{thm:wstate}.
-Similarly, not all stochastic matrices correspond to completely positive operations.
-As an example, consider the permutation matrix
-\begin{equation}
-    \Pi_X = \begin{psmallmatrix}
-        0 & 1 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 1 \\
-        0 & 0 & 0 & 1 & 0 \\
-        1 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 1 & 0 & 0
-    \end{psmallmatrix} \otimes \begin{psmallmatrix}
-        0 & 0 & 1 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 1 \\
-        0 & 0 & 0 & 1 & 0 \\
-        1 & 0 & 0 & 0 & 0 \\
-        0 & 1 & 0 & 0 & 0    
-    \end{psmallmatrix} \in {\rm{S}}_5({\W{\frac{1}{5}\id}}).
-\end{equation}
-It preserves the uniform distribution $\W{\frac{1}{5}\id}$, but it does not correspond to any positive (hence quantum) operation.
+The above result simplifies the computation of relative majorization constraints to looking at the elbows of the output Lorenz curve.
 
@@
 \end{align}
-Note that index $m$ only takes even (odd) values when labelling $\Phi_+$ ($\Phi_-$).
 In~\cref{app:lcsu_coord}, we will use $\Phi_+$ and $\Phi_-$ to express the elbow coordinates of Lorenz curves in the unital fragment.
 
-We also define the classical entropy of a $p$--coin and the classical relative entropy between a $p$--coin and a $q$--coin,
+We have the Shannon entropy of a $p$--coin and the Shannon relative entropy for a $p$--coin and a $q$--coin given by the expressions
 \begin{align}
@@
 \end{align}
-They are symmetric about $p=1/2$, namely $S(p) = S(1-p)$ and $\ent{p}{q} = \ent{1-p}{1-q}$.
-
-A useful result is the entropic bound on a combination~\cite{cit:ash}.
+They are symmetric about $p=1/2$, namely $S(p) = S(1-p)$ and $\ent{p}{q} = \ent{1-p}{1-q}$. We also have the entropic bounds
 \begin{lemma}\label{lem:comb_bounds}
@@
 The proof provided in~\cite{cit:ash} proceeds with direct calculation for the edge cases $\ell = 1,2, n-1, n-2$ and use Stirling's approximation for the remaining cases.
-
-We can use~\cref{lem:comb_bounds} to provide strict upper and lower bounds on the functions $\Phi_+, \Phi_-$.
-
-\subsection{Theory on bounding the core functions}
-Here we present a more manageable method of bounding the core functions $\Phi_{\pm}$, which however results in looser bounds. 
-We can rewrite the functions as
+The bounds~\cref{lem:comb_bounds} can be used to derive the following upper and lower bounds on the functions $\Phi_+, \Phi_-$.
+
+We rewrite the functions as
 \begin{equation}
@@
 \end{equation}
-where we have substituted $a = p/(1-p)$. 
-$\Phi$ is the standard cumulative function
+where $a = p/(1-p)$, and $\Phi$ is the standard cumulative function for the binomial distribution
 \begin{equation}
@@
 \end{equation}
-and the remainder term is
+and we define the remainder term
 \begin{equation}
@@
 \end{equation}
-We have the following asymptotic bounds on the behaviour of $\Phi$~\cite{cit:ash},
+The cumulative function $\Phi$ obeys the following bounds, which are proven in~\cite{cit:ash}.
 \begin{lemma}\label{lem:phi_bounds}
@@
 
-We would like some theory that estimates the value of $S(m; n, a)$ for different parameter regimes. 
-We can consider the function $f(x) = (1+x)^n$ and note that $S(m; n, a)$ is the $m$'th partial sum of this expansion at the point $x=-a$.
-
-The truncated Maclaurin series of a general function $f(x)$ is
+We can now put estimates on $S(m; n, a)$, and hence the functions $\Phi_{\pm}$, for different parameter regimes. 
+We can consider the function $f(x) = (1+x)^n$ and note that $S(m; n, a)$ is the $m$'th partial sum of this expansion at the point $x=-a$. The truncated Maclaurin series is given by
 \begin{equation}
@@
 \end{align}
-where in the second expression, $x_*$ is an implicit point that lies between $0$ and $x$ that comes from the Mean Value Theorem.
+where in the second expression, $x_*$ is a point that lies between $0$ and $x$ that comes from the Mean Value Theorem.
 
@@
 \end{equation}
-Evaluating at $x=-a$ gives
+Therefore if we evaluate at $x=-a$ we obtain
 \begin{equation}
@@
 \end{equation}
-where the key remainder term is given by
+where the remainder term is given by
 \begin{align}
@@
 \end{align}
-We can also compute the derivative $f^{(m+1)}(x)$ explicitly,
+We can compute the derivative $f^{(m+1)}(x)$ explicitly,
 \begin{equation}
@@
 where in the latter expression $x_* \in [-a,0]$. 
-Note that the first integral expression can be estimated via the Cauchy-Schwarz or the H{\"o}lder inequality. 
-Therefore, we can either work with an explicit form with an unknown (but bounded) parameter $x_*$, or we can use the integral form and provide concrete estimates on it value.
+The first integral expression can be estimated via the Cauchy-Schwarz or the H{\"o}lder inequality. 
+Therefore, one has an explicit form with an unknown (but bounded) parameter $x_*$, or the integral form.
 
@@
 \end{align}
+Better bounds can be obtained with a finer analysis, and it would be of interest to obtain tighter asymptotic behaviour on $\Phi_{\pm}$ that could in turn be used to improve magic distillation bounds.
+
+\subsection{Component-multiplicity pairs}
+\label{app:cmpairs}
+
+In general, a $1$--copy $d$--dimensional state $\rho$ is described by its $d^2$--dimensional Wigner distribution $\W{\rho}(\bmx)$. 
+The distribution $\W{\rho}(\bmx)$ is defined on the phase space, but it can be convenient to re-express this using vector notation.
+
+To each Wigner distribution $W_\rho(\x)$ we can associate \emph{component-multiplicity} pairs $\{(w_i, m_i)\}$ where the value $w_i$ occurs in the distribution $W_\rho(\x)$ with multiplicity $m_i$.
+
+As an example, for the Strange state $\rho_S := \rho_S(\epsilon=0)$ with
+\begin{equation}
+W_{\rho_S}(\x) = (-1/3, 1/6,  1/6,  1/6,  1/6,  1/6,  1/6,  1/6,  1/6)
+\end{equation}
+we have the component-multiplicity pairs: $\{( -1/3, 1), ( 1/6, 8)\}$.
+However, we might also wish more freedom and not require that the different $w_i$ values are all distinct.
+For example, the component-multiplity pairs $\{(-1/3, 1), (1/6, 2), (1/6, 3), (1/6, 3)\}$ also describe $W_{\rho_S}(\x)$.
+
+This representation is more compact when a Wigner distribution has a lot of multiplicities, and allows for simple handling of multiple copies via the following fact.
+\begin{lemma}
+Consider two Wigner distributions $\W{\rho_A}, \W{\rho_B}$ with component-multiplicity pairs 
+\begin{equation}
+	\{(w_i, m_i)\} \text{ and } \{(w_j', m_j')\},
+\end{equation}
+respectively. Then, $\{(w_i w_j', m_i m_j')\}$ gives component-multiplicity pairs for $\W{\rho_A \otimes \rho_B}$.
+\end{lemma}
+
+This is true because all components of $\W{\rho_A \otimes \rho_B}$ are of the form $w_i w_j'$ and 
+\begin{equation*}
+	\sum_{i=1}^{D_A}\sum_{j=1}^{D_B} m_i m_j' = \sum_{i=1}^{D_A} m_i \sum_{j=1}^{D_B} m_j' = d_A^2 d_B^2,
+\end{equation*}
+so the set $\{(w_i w_j', m_i m_j')\}$ contains exactly the Wigner components of $\W{\rho_A \otimes \rho_B}$ and no more.
+
+In the case of distillation protocols, we are interested in $n$--copies of a single Wigner distribution. For this, we have the following result, which follows from combinatorics.
+
+\begin{lemma}\label{lem:ncopycomponents}
+	Suppose $W_\rho(\x)$ has $D$ component-multiplicity pairs $\{(w_i, m_i)\}$.
+Then, $W_{\rho^{\otimes n}} (\x)$ has component-multiplicity pairs $\{(W_{\q}, M_{\q})\}$, where $\q$ runs through all $K$-component vectors with non-negative integer components that sum to $n$, and
+\begin{align}
+W_{\q} &= \prod_{i=1}^D w_i^{q_i} \label{eq:W}\\
+M_{\q} &= \binom{n}{q_1,q_2, \dots, q_d} \prod_{i=1}^D m_i^{q_i}, \label{eq:M}
+\end{align}
+where the term outside the product in the expression for $M_{\q}$ is the generalized binomial coefficient.
+\end{lemma}
+\begin{proof}
+	Denote by $C_D^n \coloneqq \{\bmk\}$ the set of all vectors $\bmk \coloneqq (k_1, \dots, k_D)$ with non-negative integer components that sum to $n$, i.e.
+	\begin{equation*}
+	0 \leq k_1, \dots, k_D \leq n \text{ and } k_1 + \dots + k_D = n.
+	\end{equation*}
+
+	We proceed by induction.	
+	Assume $n = 1$ and let $\bmk_i$ be the vector with its $i$-th component equal to 1 and 0's elsewhere.
+	The set $C_D^1$ consists of all vectors of this form, i.e. 
+\begin{equation*}
+	C_D^1 = \{ \bmk_i \}_{i=1,\dots,D}
+\end{equation*}
+	It is also true by direct calculation that
+\begin{equation*}
+	\left( W_{\bmk_i}, M_{\bmk_i} \right) = (w_i, m_i).
+\end{equation*}
+Therefore, $\{ (W_{\bmk}, M_{\bmk}) \}_{\bmk \in C_D^1}$ is a complete set of component-multiplicity pairs for $W$.
+
+	Assume that $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$ as given in~\cref{eq:M,eq:W} is a complete set of component-multiplicity pairs for the $n$--copy distribution $W^{\otimes n}$.
+	By construction, the distribution $W^{\otimes (n+1)} = W^{\otimes n} \otimes W$ is multiplicative, so it admits the complete set of component multiplicity pairs
+\begin{equation}
+	\{(W_{\bmk} w_i, M_{\bmk} m_i)\},\ \bmk \in C_D^n \text{ and } i=1,\dots,D.
+\end{equation}
+
+	Consider the component sum of the distribution $W^{\otimes (n+1)}$,
+\begin{align*}
+	&\sum_{\bmk \in C_D^n}\sum_{i=1}^D M_{\bmk} m_i W_{\bmk} w_i = \sum_{\bmk \in C_D^n} M_{\bmk}W_{\bmk} \sum_{i=1}^D m_i w_i =\\
+	&\sum_{\bmk \in C_D^n} \frac{n!}{k_1!\dots k_D!} \prod\limits_{i=1}^D {m_i}^{k_i}{w_i}^{k_i} \sum_{i=1}^D m_i w_i =\\
+	&\left( \sum_{i=1}^D m_i w_i \right)^n \left( \sum_{i=1}^D m_i w_i \right) = \left( \sum_{i=1}^D m_i w_i \right)^{n+1} =\\
+	&\sum_{\bmq \in C_D^{n+1}} M_{\bmq}W_{\bmq},
+\end{align*}
+where in the last expression, vectors $\bmq = (q_1, \dots, q_D)$ have non-negative integer components that sum to $(n+1)$ and 
+\begin{align*}
+	M_{\bmq} &= \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i},\\
+	W_{\bmq} &= \prod\limits_{i=1}^D {w_i}^{q_i}.
+\end{align*}
+We have used the multinomial theorem to proceed between lines 2-3 and lines 3-4 of the derivation.
+
+We have achieved a regrouping of the distribution components.
+Every component $W_{\bmq}$ is of the form $W_{\bmk} w_i$ with $q_i = k_i + 1$ and $q_j = k_j$ for $j\neq i$ and 
+\begin{align*}
+	\sum_{\bmq \in C_D^{n+1}}  \hspace{-6pt} M_{\bmq} =  \hspace{-10pt} \sum_{\bmq \in C_D^{n+1}} \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i} = 
+	\left( \sum_{i=1}^D m_i \right)^{n+1} \hspace{-10pt} = d^{n+1},
+\end{align*}
+which is the dimension of $W^{\otimes (n+1)}$.
+
+Therefore, $\{ (W_{\bmq}, M_{\bmq}) \}_{\bmq \in C_D^{n+1}}$ contains exactly the components of $W^{\otimes n}$, completing the proof.
+\end{proof}
+
+The rescaled distribution is also multiplicative, so a set of component-multiplicity pairs can be obtained for the $n$-copy rescaled distribution in the same fashion as for usual Wigner distributions.
 
@@
 \end{align}
-The labels $\text{LHS}, \text{RHS}$ imply that the components contribute to the left hand side or the right hand side of the maximum (including the maximum) of the Lorenz curve.
-To compactify notation, we also use multiplication modulo $(n+1)$, specifically, for any positive integer $m \leq 2n$:
+The labels $\text{LHS}, \text{RHS}$ denote that the components contribute to the left hand side or the right hand side of the maximum (including the maximum) of the Lorenz curve.
+To simplify notation, we also use multiplication modulo $(n+1)$, specifically, for any positive integer $m \leq 2n$:
 \begin{equation}
@@
 \end{equation}
+\ddd{Where do we use this modulo $(n+1)$? I don't understand where it's appearing.}
 \begin{table}[h]
@@
   Multiplication $2i$ is considered $\hspace{-6pt}\mod{\hspace{-2pt}(n+1)}$.
-  For completeness, note that $(x_{-1}, L_{-1}) \coloneqq (0,0)$ is not included in the table.
+ The point $(x_{-1}, L_{-1}) \coloneqq (0,0)$ is not included in the table.
   }
@@
 \end{table}
-
-\nick{ALTERNATIVE TABLE PRESENTATION:}
 In~\cref{tab:lcsu_coord_elb_app_alt}, we present the elbow coordinates of the $n$-copy, $\epsilon$--noisy Strange state Lorenz curve in the unital fragment for any combination of parameters $n, \epsilon$.
-To compactify notation, we define in terms of $n, \epsilon$ an amplitude $A$ and a probability $p$, as follows:
+To simplify notation, we define in terms of $n, \epsilon$ an exponentially growing term $A$ and a probability $p$, as follows:
 \begin{align}
@@
 \end{align}
-
-We can unify the indices, by introducing a single index
+We can also combine the indices, by introducing a single index
 \begin{equation}
@@
 \end{equation}
-The index function $I$ is bijective, i.e.
+The indexing $I$ is bijective, i.e.
 \begin{equation}
@@
 \end{align}
-where $\x = \oplus_{i=1}^n \x_i \in \mathbb{Z}_3^n$ is the phase space point for the full system in terms of those of the individual subsystems.
+where $\x = \oplus_{i=1}^n \x_i \in \mathbb{Z}_3^{2n}$ is the phase space point for the full system in terms of those of the individual subsystems.
 
 The points defining the Lorenz curve $L_{\rho_n |\tau_n}(x)$ are obtained from sorting the components of $W_{\rho_n |\tau_n}(\x)$ in non-increasing order and then computing the partial sums of $W_{\rho_n |\tau_n}(\pi(\x))$ where $\pi$ is the permutation that realises the sorting.
-However, similarly to the unital fragment analysis, we use the necessary constraint obtained by considering the line segment connecting the origin to the first elbow of both Lorenz curves.
+However, similar to the unital fragment analysis, we use the slope constraint (Proposition \ref{prop:first_elb}) obtained by considering the line segments connecting the origin to the first elbow of both Lorenz curves.
 
@@
 \end{equation}
-we can re-express the coordinate location, by writing
+we now express the coordinates of the first point in terms of free energy quantities. We expand as follows
 \begin{align}
@@
 \end{align}
-and the `magic free energy' term $\phi := -\beta^{-1} \log \zeta$.
+and a `magic free energy' term $\phi := -\beta^{-1} \log \zeta$.
 Therefore, the coordinates can be expressed as
@@
 \end{equation}
-The output states obey the same conditions and so we can derive the first point coordinates of the output Lorenz curve as
+The output states obey the same conditions and so we also have the first point coordinates of the output Lorenz curve given by
 \begin{equation}
@@
 \end{equation}
-concluding the proof.
+which completes the proof.
 \end{proof}
 
-The following result shows that if the energy eigenbasis is a stabilizer basis then things simplify more.
+The following result shows that if the energy eigenbasis is a stabilizer basis then the above bounds simplify further.
 \begin{proposition} \label{sharp-phi}
@@
 
-\subsection{Component-multiplicity pairs}
-\label{app:cmpairs}
-
-In general, a $1$--copy $d$--dimensional state $\rho$ is described by its $d^2$--dimensional Wigner distribution $\W{\rho}(\bmx)$. 
-The distribution $\W{\rho}(\bmx)$ is defined on the phase space, but it can be convenient to re-express this using vector notation.
-
-To each Wigner distribution $W_\rho(\x)$ we can associate \emph{component-multiplicity} pairs $\{(w_i, m_i)\}$ where the value $w_i$ occurs in the distribution $W_\rho(\x)$ with multiplicity $m_i$.
-
-As an example, for the Strange state $\rho_S := \rho_S(\epsilon=0)$ with
-\begin{equation}
-W_{\rho_S}(\x) = (-1/3, 1/6,  1/6,  1/6,  1/6,  1/6,  1/6,  1/6,  1/6)
-\end{equation}
-we have the component-multiplicity pairs: $\{( -1/3, 1), ( 1/6, 8)\}$.
-However, we might also wish more freedom and not require that the different $w_i$ values are all distinct.
-For example, the component-multiplity pairs $\{(-1/3, 1), (1/6, 2), (1/6, 3), (1/6, 3)\}$ also describe $W_{\rho_S}(\x)$.
-
-This representation is more compact when a Wigner distribution has a lot of multiplicities, and allows for simple handling of multiple copies via the following fact.
-\begin{lemma}
-Consider two Wigner distributions $\W{\rho_A}, \W{\rho_B}$ with component-multiplicity pairs 
-\begin{equation}
-	\{(w_i, m_i)\} \text{ and } \{(w_j', m_j')\},
-\end{equation}
-respectively. Then, $\{(w_i w_j', m_i m_j')\}$ gives component-multiplicity pairs for $\W{\rho_A \otimes \rho_B}$.
-\end{lemma}
-
-This is true because all components of $\W{\rho_A \otimes \rho_B}$ are of the form $w_i w_j'$ and 
-\begin{equation*}
-	\sum_{i=1}^{D_A}\sum_{j=1}^{D_B} m_i m_j' = \sum_{i=1}^{D_A} m_i \sum_{j=1}^{D_B} m_j' = d_A^2 d_B^2,
-\end{equation*}
-so the set $\{(w_i w_j', m_i m_j')\}$ contains exactly the Wigner components of $\W{\rho_A \otimes \rho_B}$ and no more.
-
-In the case of distillation protocols, we are interested in $n$--copies of a single Wigner distribution. For this, we have the following result, which follows from combinatorics.
-
-\begin{lemma}\label{lem:ncopycomponents}
-	Suppose $W_\rho(\x)$ has $D$ component-multiplicity pairs $\{(w_i, m_i)\}$.
-Then, $W_{\rho^{\otimes n}} (\x)$ has component-multiplicity pairs $\{(W_{\q}, M_{\q})\}$, where $\q$ runs through all $K$-component vectors with non-negative integer components that sum to $n$, and
-\begin{align}
-W_{\q} &= \prod_{i=1}^D w_i^{q_i} \label{eq:W}\\
-M_{\q} &= \binom{n}{q_1,q_2, \dots, q_d} \prod_{i=1}^D m_i^{q_i}, \label{eq:M}
-\end{align}
-where the term outside the product in the expression for $M_{\q}$ is the generalized binomial coefficient.
-\end{lemma}
-\begin{proof}
-	Denote by $C_D^n \coloneqq \{\bmk\}$ the set of all vectors $\bmk \coloneqq (k_1, \dots, k_D)$ with non-negative integer components that sum to $n$, i.e.
-	\begin{equation*}
-	0 \leq k_1, \dots, k_D \leq n \text{ and } k_1 + \dots + k_D = n.
-	\end{equation*}
-
-	We proceed by induction.	
-	Assume $n = 1$ and let $\bmk_i$ be the vector with its $i$-th component equal to 1 and 0's elsewhere.
-	The set $C_D^1$ consists of all vectors of this form, i.e. 
-\begin{equation*}
-	C_D^1 = \{ \bmk_i \}_{i=1,\dots,D}
-\end{equation*}
-	It is also true by direct calculation that
-\begin{equation*}
-	\left( W_{\bmk_i}, M_{\bmk_i} \right) = (w_i, m_i).
-\end{equation*}
-Therefore, $\{ (W_{\bmk}, M_{\bmk}) \}_{\bmk \in C_D^1}$ is a complete set of component-multiplicity pairs for $W$.
-
-	Assume that $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$ as given in~\cref{eq:M,eq:W} is a complete set of component-multiplicity pairs for the $n$--copy distribution $W^{\otimes n}$.
-	By construction, the distribution $W^{\otimes (n+1)} = W^{\otimes n} \otimes W$ is multiplicative, so it admits the complete set of component multiplicity pairs
-\begin{equation}
-	\{(W_{\bmk} w_i, M_{\bmk} m_i)\},\ \bmk \in C_D^n \text{ and } i=1,\dots,D.
-\end{equation}
-
-	Consider the component sum of the distribution $W^{\otimes (n+1)}$,
-\begin{align*}
-	&\sum_{\bmk \in C_D^n}\sum_{i=1}^D M_{\bmk} m_i W_{\bmk} w_i = \sum_{\bmk \in C_D^n} M_{\bmk}W_{\bmk} \sum_{i=1}^D m_i w_i =\\
-	&\sum_{\bmk \in C_D^n} \frac{n!}{k_1!\dots k_D!} \prod\limits_{i=1}^D {m_i}^{k_i}{w_i}^{k_i} \sum_{i=1}^D m_i w_i =\\
-	&\left( \sum_{i=1}^D m_i w_i \right)^n \left( \sum_{i=1}^D m_i w_i \right) = \left( \sum_{i=1}^D m_i w_i \right)^{n+1} =\\
-	&\sum_{\bmq \in C_D^{n+1}} M_{\bmq}W_{\bmq},
-\end{align*}
-where in the last expression, vectors $\bmq = (q_1, \dots, q_D)$ have non-negative integer components that sum to $(n+1)$ and 
-\begin{align*}
-	M_{\bmq} &= \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i},\\
-	W_{\bmq} &= \prod\limits_{i=1}^D {w_i}^{q_i}.
-\end{align*}
-We have used the multinomial theorem to proceed between lines 2-3 and lines 3-4 of the derivation.
-
-We have achieved a regrouping of the distribution components.
-Every component $W_{\bmq}$ is of the form $W_{\bmk} w_i$ with $q_i = k_i + 1$ and $q_j = k_j$ for $j\neq i$ and 
-\begin{align*}
-	\sum_{\bmq \in C_D^{n+1}}  \hspace{-6pt} M_{\bmq} =  \hspace{-10pt} \sum_{\bmq \in C_D^{n+1}} \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i} = 
-	\left( \sum_{i=1}^D m_i \right)^{n+1} \hspace{-10pt} = d^{n+1},
-\end{align*}
-which is the dimension of $W^{\otimes (n+1)}$.
-
-Therefore, $\{ (W_{\bmq}, M_{\bmq}) \}_{\bmq \in C_D^{n+1}}$ contains exactly the components of $W^{\otimes n}$ and no more, completing the proof.
-\end{proof}
-
-The rescaled distribution is also multiplicative, so a set of component-multiplicity pairs can be obtained for the $n$-copy rescaled distribution in the same fashion as for usual Wigner distributions.
-
 \subsection{Dropping pre/post-processing of the magic states}
@@
 
-Let each qutrit have a Hamiltonian $H$ with energies $E_0, E_1, E_2$ and stabilizer eigenstates, and define $E_{\rm max} = \max\{E_0, E_1, E_2\}$ and $E_s$ as the eigenvalue of the Hamiltonian eigenstate the Wigner representation of which overlaps the negative component of $\rho_S(\epsilon)$ in the phase space.
+Let each qutrit have a Hamiltonian $H$ with energies $E_0, E_1, E_2$ and stabilizer eigenstates, and define $E_{\rm max} = \max\{E_0, E_1, E_2\}$ and $E_s$ as the eigenvalue of the Hamiltonian eigenstate whose Wigner distribution overlaps the negative component of $\rho_S(\epsilon)$ in the phase space.
 Let $T =(k\beta)^{-1}$ be any finite temperature and assume that in the thermodynamic limit ($n,m \gg 1$), the protocol applied to the equilibrium state $\tau^{\otimes n} = (e^{-\beta H}/\Z)^{\otimes n}$ maps $\tau^{\otimes n} \longrightarrow \tau^{\prime \otimes m}$, where we express state $\tau'$ as $\tau' = e^{-\beta H'}/\Z'$ for some Hermitian $H'$.
@@
 \end{theorem}
-We note, firstly, that the specific numerical factors in $\epsilon_\star$ are a result of our choice of magic state. 
 \begin{proof}
-The proof proceeds in the same manner as in~\cref{thm:free-energy-bound-proof} up to the point where we need to evaluate $W_{\rho_n |\tau_n} (\x)$ and $W_{\rho_n}(\x)$ explicitly.
-Now we do not have the freedom of additional Clifford processing, so we need to exploit the full structure of the equilibrium state.
+The proof proceeds in the same manner as in~\cref{thm:free-energy-bound-proof} up to the point where we need to evaluate $W_{\rho_n |\tau_n} (\x)$ and $W_{\rho_n}(\x)$ explicitly, beyond which we do not have the freedom of additional Clifford processing.
 
@@
 where the eigenstates $\{\ket{\varphi_k}\<\varphi_k|\}$ are pure, orthonormal stabiliser states, which can be represented in terms of generalized Paulis.
-To make our analysis simpler, we perform a change of basis that does not affect the Wigner negativity of the problem.
-We let $C$ be the unitary transforming each $|\varphi_k\>\<\varphi_k|$ to $|k\>\<k|$.
+We are free to redefine the computational basis so it coincides with the basis of $H$.
+Abstractly, let $C$ be the unitary transforming each $|\varphi_k\>\<\varphi_k|$ to $|k\>\<k|$.
 Since the Clifford group is the normalizer of the Heisenberg-Weyl group, $C$ is a Clifford unitary.
 Therefore, $C$ maps $\tau$ to another stabilizer state that is diagonal in the computational basis, and we can assume without loss of generality that $\tau$ is diagonal in $\{|0\>,|1\>, |2\>\}$.
-However, this choice means that the location of the negative Wigner component $-v(\epsilon)$ of the Strange state will be permuted on the discrete phase space.
+However, this re-definition of the computational basis means that the location of the negative Wigner component $-v(\epsilon)$ of the Strange state will be permuted on the discrete phase space.
 We denote by $E_s$ the eigenvalue of $H$ where the associated eigenvector has Wigner distribution overlapping the negative component of the magic state $C\rho_S(\epsilon)C^\dagger$.
@@
 where $x$ labels one of the three vertical lines in the phase space.
-The rescaled Wigner distribution $W_{\rho|\tau}(\x)$ is then easily computed.
-It has $9$ components, but several of these come with multiplicities.
+The rescaled Wigner distribution $W_{\rho|\tau}(\x)$ can now be computed.
+It has $9$ components, but these come with multiplicities.
 In total, there are four distinct values on the phase space, as illustrated in~\cref{fig:pd_split}.
@@
 
-We now denote by $\w(\rho), \w(\rho|\tau)$ the unique values occurring in $W_\rho(\x), W_{\rho|\tau}(\x)$ respectively and $\bmm$ the vector of associated multiplicities of each value in $W_\rho(\x)$.
+We denote by $\w(\rho), \w(\rho|\tau)$ the unique values occurring in $W_\rho(\x), W_{\rho|\tau}(\x)$ respectively and $\bmm$ the vector of associated multiplicities of each value in $W_\rho(\x)$.
 The component values and multiplicities of the relevant distributions in the four distinct regions are given by
@@
 
-Generally this is complex, but in order to obtain distillation bounds it is sufficient to determine the location of the first elbow $(x_0, L_0)$ of $L_{\rho_n|\tau_n}(\x)$.
-To do so, we compute the largest component
+However, it again suffices to use only the constraint from the first elbow $(x_0, L_0)$ of $L_{\rho_n|\tau_n}(\x)$. We therefore compute the largest component 
 \begin{equation}
@@
 
+\ddd{[I would prefer to remove this last elbow constraint analysis, and just mention it in the main text.
+If we include it then I need to go through the details to ensure they're correct -- which is very time-consuming at this stage.
+We *can't* put glaringly sloppy/incorrect things into a paper that will be public to the world.
+Happy to remove and just mention in passing?]}
+
 We can run a similar analysis, in order to utilise the descending part of the Lorenz curves to extract bounds.

### 2021-05-24 magic_paper.tex
responded to points. Need to reorganise App. B. Minor comments left in App.B and App.C

@@
 
-We approach this problem using tools from statistical mechanics and recent work from the overlap of thermodynamics and quantum information theory~\cite{cit:horodecki2, Brandao_2015, Vinjanampathy_2016, Goold_2016, cit:lostaglio, cit:gour}\nick{Can't find Danzig's paper anywhere}\ddd{[Remembered name incorrectly, is this one: Janzing, Dominik, et al.
-"Thermodynamic cost of reliability and low temperatures: tightening Landauer's principle and the second law." Put this one first in list -- people always miss it, but it is the first.] }.
+We approach this problem using tools from statistical mechanics and recent work from the overlap of thermodynamics and quantum information theory~\cite{cit:janzing, cit:horodecki2, Brandao_2015, Vinjanampathy_2016, Goold_2016, cit:lostaglio, cit:gour}.
 In particular, we shall view \emph{magic as a form of free energy}, relative to the set of stabilizer states.
@@
 If $a$ and $b$ both lie in either the interval $[0,x_\star]$ or $[x_\star, 1]$ then concavity follows immediately.
-Otherwise $a$ is in the first interval and $b$ in the second interval.
+Otherwise, $a$ is in the first interval and $b$ in the second interval.
 If $w=qa + (1-q)b$ lies in the first interval then
@@
 \end{align}
-from monotonicity on the first interval. Otherwise $w$ lies in the second interval and
+\nick{second inequality isn't clear to me}
+from monotonicity on the first interval. Otherwise, $w$ lies in the second interval and
 \begin{align}
@@
 \end{align}
+\nick{again second inequality isn't clear to me}
 which follows from monotonicity on the second interval. Therefore the Lorenz curve is concave on $[0,1]$.
@@
 
-\section{Lorenz curves and $\sigma$--fragments}
-\label{app:frag}
+%\subsection{Component-multiplicity pairs}
+%\label{app:cmpairs}
+
+In general, a $1$--copy $d$--dimensional state $\rho$ is described by its $d^2$--dimensional Wigner distribution $\W{\rho}(\bmx)$. 
+The distribution $\W{\rho}(\bmx)$ is defined on the phase space, but it can be convenient to re-express this using vector notation.
+
+To each Wigner distribution $W_\rho(\x)$ we can associate \emph{component-multiplicity} pairs $\{(w_i, m_i)\}$ where the value $w_i$ occurs in the distribution $W_\rho(\x)$ with multiplicity $m_i$.
+
+As an example, for the Strange state $\rho_S := \rho_S(\epsilon=0)$ with
+\begin{equation}
+W_{\rho_S}(\x) = (-1/3, 1/6,  1/6,  1/6,  1/6,  1/6,  1/6,  1/6,  1/6)
+\end{equation}
+we have the component-multiplicity pairs: $\{( -1/3, 1), ( 1/6, 8)\}$.
+However, we might also wish more freedom and not require that the different $w_i$ values are all distinct.
+For example, the component-multiplity pairs $\{(-1/3, 1), (1/6, 2), (1/6, 3), (1/6, 3)\}$ also describe $W_{\rho_S}(\x)$.
+
+This representation is more compact when a Wigner distribution has a lot of multiplicities, and allows for simple handling of multiple copies via the following fact.
+\begin{lemma}
+Consider two Wigner distributions $\W{\rho_A}, \W{\rho_B}$ with component-multiplicity pairs 
+\begin{equation}
+	\{(w_i, m_i)\} \text{ and } \{(w_j', m_j')\},
+\end{equation}
+respectively. Then, $\{(w_i w_j', m_i m_j')\}$ gives component-multiplicity pairs for $\W{\rho_A \otimes \rho_B}$.
+\end{lemma}
+
+This is true because all components of $\W{\rho_A \otimes \rho_B}$ are of the form $w_i w_j'$ and 
+\begin{equation*}
+	\sum_{i=1}^{D_A}\sum_{j=1}^{D_B} m_i m_j' = \sum_{i=1}^{D_A} m_i \sum_{j=1}^{D_B} m_j' = d_A^2 d_B^2,
+\end{equation*}
+so the set $\{(w_i w_j', m_i m_j')\}$ contains exactly the Wigner components of $\W{\rho_A \otimes \rho_B}$ and no more.
+
+In the case of distillation protocols, we are interested in $n$--copies of a single Wigner distribution. For this, we have the following result, which follows from combinatorics.
+
+\begin{lemma}\label{lem:ncopycomponents}
+	Suppose $W_\rho(\x)$ has $D$ component-multiplicity pairs $\{(w_i, m_i)\}$.
+Then, $W_{\rho^{\otimes n}} (\x)$ has component-multiplicity pairs $\{(W_{\q}, M_{\q})\}$, where $\q$ runs through all $K$-component vectors with non-negative integer components that sum to $n$, and
+\begin{align}
+W_{\q} &= \prod_{i=1}^D w_i^{q_i} \label{eq:W}\\
+M_{\q} &= \binom{n}{q_1,q_2, \dots, q_d} \prod_{i=1}^D m_i^{q_i}, \label{eq:M}
+\end{align}
+where the term outside the product in the expression for $M_{\q}$ is the generalized binomial coefficient.
+\end{lemma}
+\begin{proof}
+	Denote by $C_D^n \coloneqq \{\bmk\}$ the set of all vectors $\bmk \coloneqq (k_1, \dots, k_D)$ with non-negative integer components that sum to $n$, i.e.
+	\begin{equation*}
+	0 \leq k_1, \dots, k_D \leq n \text{ and } k_1 + \dots + k_D = n.
+	\end{equation*}
+
+	We proceed by induction.	
+	Assume $n = 1$ and let $\bmk_i$ be the vector with its $i$-th component equal to 1 and 0's elsewhere.
+	The set $C_D^1$ consists of all vectors of this form, i.e. 
+\begin{equation*}
+	C_D^1 = \{ \bmk_i \}_{i=1,\dots,D}
+\end{equation*}
+	It is also true by direct calculation that
+\begin{equation*}
+	\left( W_{\bmk_i}, M_{\bmk_i} \right) = (w_i, m_i).
+\end{equation*}
+Therefore, $\{ (W_{\bmk}, M_{\bmk}) \}_{\bmk \in C_D^1}$ is a complete set of component-multiplicity pairs for $W$.
+
+	Assume that $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$ as given in~\cref{eq:M,eq:W} is a complete set of component-multiplicity pairs for the $n$--copy distribution $W^{\otimes n}$.
+	By construction, the distribution $W^{\otimes (n+1)} = W^{\otimes n} \otimes W$ is multiplicative, so it admits the complete set of component multiplicity pairs
+\begin{equation}
+	\{(W_{\bmk} w_i, M_{\bmk} m_i)\},\ \bmk \in C_D^n \text{ and } i=1,\dots,D.
+\end{equation}
+
+	Consider the component sum of the distribution $W^{\otimes (n+1)}$,
+\begin{align*}
+	&\sum_{\bmk \in C_D^n}\sum_{i=1}^D M_{\bmk} m_i W_{\bmk} w_i = \sum_{\bmk \in C_D^n} M_{\bmk}W_{\bmk} \sum_{i=1}^D m_i w_i =\\
+	&\sum_{\bmk \in C_D^n} \frac{n!}{k_1!\dots k_D!} \prod\limits_{i=1}^D {m_i}^{k_i}{w_i}^{k_i} \sum_{i=1}^D m_i w_i =\\
+	&\left( \sum_{i=1}^D m_i w_i \right)^n \left( \sum_{i=1}^D m_i w_i \right) = \left( \sum_{i=1}^D m_i w_i \right)^{n+1} =\\
+	&\sum_{\bmq \in C_D^{n+1}} M_{\bmq}W_{\bmq},
+\end{align*}
+where in the last expression, vectors $\bmq = (q_1, \dots, q_D)$ have non-negative integer components that sum to $(n+1)$ and 
+\begin{align*}
+	M_{\bmq} &= \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i},\\
+	W_{\bmq} &= \prod\limits_{i=1}^D {w_i}^{q_i}.
+\end{align*}
+We have used the multinomial theorem to proceed between lines 2-3 and lines 3-4 of the derivation.
+
+We have achieved a regrouping of the distribution components.
+Every component $W_{\bmq}$ is of the form $W_{\bmk} w_i$ with $q_i = k_i + 1$ and $q_j = k_j$ for $j\neq i$ and 
+\begin{align*}
+	\sum_{\bmq \in C_D^{n+1}}  \hspace{-6pt} M_{\bmq} =  \hspace{-10pt} \sum_{\bmq \in C_D^{n+1}} \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i} = 
+	\left( \sum_{i=1}^D m_i \right)^{n+1} \hspace{-10pt} = d^{n+1},
+\end{align*}
+which is the dimension of $W^{\otimes (n+1)}$.
+
+Therefore, $\{ (W_{\bmq}, M_{\bmq}) \}_{\bmq \in C_D^{n+1}}$ contains exactly the components of $W^{\otimes n}$, completing the proof.
+\end{proof}
+
+The rescaled distribution is also multiplicative, so a set of component-multiplicity pairs can be obtained for the $n$-copy rescaled distribution in the same fashion as for usual Wigner distributions.
 
@@
 \end{proposition}
-\ddd{[I think the following is a more direct/informative proof]}
-\ddd{\begin{proof} If the transformation is possible then $L_{\rho|\sigma}(x) \ge L_{\rho'|\sigma'} (x)$ for all $x$ in $[0,1]$.
-If we restrict to the initial linear region segment of $L_{\rho|\sigma}(x)$ joining $(0,0)$ to $(X_0,L_0)$ then we require this to be above the initial linear segment of $L_{\rho'|\sigma'}(x)$ joining $(0,0)$ to $(X_0', L_0')$.
-Since both these linear segments go through the origin this condition implies that the slope of the initial segment of the input Lorenz curve must be greater than or equal to the slope of the initial segment of the output Lorenz curve.
-This slope constraint is then equivalent to Equation \ref{eq:first_elb_bound1}.
-\end{proof}}
 \begin{proof} 
-Since both pairs of coordinates are located between $(0,0)$ and the first elbow of their respective curves, we can derive the bound via a simple interpolation on the line segment connecting the origin and the appropriate pair of coordinates.
-
-First assume that $x < x'$.
-Then, point $(x, L_{\rho'|\sigma'}(x))$ lies on the lines segment connecting $(0,0)$ and $(x', L')$, so by interpolating between points $(0,0)$ and $(x', L')$ at location $x$, we find that
-\begin{equation}
-	L_{\rho'|\sigma'}(x) = \frac{x}{x'}L'.
-\end{equation}
-Considering the Lorenz curve constraint at $x$, the process is possible only if 
-\begin{equation}
-	L = \lc{\rho}{\sigma}(x) \geq \lc{\rho'}{\sigma'}(x) = \frac{x}{x'}L',
-\end{equation}
-which is a rearrangement of~\cref{eq:first_elb_bound1}.
-
-If instead, $x \geq x'$, the point $(x', L_{\rho|\sigma}(x'))$ lies on the lines segment connecting $(0,0)$ and $(x, L)$, so by interpolating between points $(0,0)$ and $(x, L)$ at location $x'$, we find that
-\begin{equation}
-	L_{\rho|\sigma}(x') = \frac{x'}{x}L.
-\end{equation}
-Considering the Lorenz curve constraint at $x'$, the process is possible only if 
-\begin{equation}
-	\frac{x'}{x}L = \lc{\rho}{\sigma}(x') \geq \lc{\rho'}{\sigma'}(x) = L',
-\end{equation}
-which is again a rearrangement of~\cref{eq:first_elb_bound1}.
-\end{proof}
+	If the transformation is possible, then $L_{\rho|\sigma}(x) \geq L_{\rho'|\sigma'} (x)$ for all $x$ in $[0,1]$. 
+	Restricting to the initial linear segment of $L_{\rho|\sigma}(x)$ joining $(0,0)$ to $(X_0,L_0)$, we then require that it be above the initial linear segment of $L_{\rho'|\sigma'}(x)$ joining $(0,0)$ to $(X_0', L_0')$.
+	Since both these linear segments start at the origin, this condition is equivalent to the slope of the initial segment of the input Lorenz curve being greater than or equal to the slope of the initial segment of the output Lorenz curve.
+	This slope constraint is then equivalent to~\cref{eq:first_elb_bound1}. \end{proof}
 
@@
 \begin{proof}	
-If $\lc{\rho}{\sigma}(x) \geq \lc{\rho'}{\sigma'}(x)$ for all $x \in [0,1]$ then the condition on the elbows trivially follows.
-
-\ddd{Conversely, assume $L_{\rho|\sigma}(x_i) \ge L_{\rho'|\sigma'}(x_i)$ for all $i=1,\dots t$.
-Suppose on the contrary that $L_{\rho|\sigma}(x)$ dips below $L_{\rho'|\sigma'}(x)$ at some point $y$ where $x_i < y < x_{i+1}$ for some $i$.
-Then this implies
+If $\lc{\rho}{\sigma}(x) \geq \lc{\rho'}{\sigma'}(x)$ for all $x \in [0,1]$, then the condition on the elbows follows trivially.
+
+Conversely, assume $L_{\rho|\sigma}(x_i) \geq L_{\rho'|\sigma'}(x_i)$ for all $i=1,\dots t$. 
+Suppose on the contrary that $L_{\rho|\sigma}(x)$ dips below $L_{\rho'|\sigma'}(x)$ at some point $x=y$ where $x_i < y < x_{i+1}$ for some $i$. Then this implies
 \begin{align}
@@
 \end{align}
-However since $L_{\rho'|\sigma'}(x)$ is linear between $x_i$ and $x_{i+1}$, the above conditions imply that $L_{\rho|\sigma}(x)$ is not a concave function, which contradicts Lemma \ref{L-concave}.
-Therefore $L_{\rho|\sigma}(x) \ge L_{\rho'|\sigma'}(x)$ for all $x$ in $[0,1]$.
-}
-
-	Conversely, assume that $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\rho'}{\sigma'}(x_{i})$ for all $i = 1,\dots,r$.
-	First, let $x_0 = 0$ and $x_{n'+1} = 1$, so that $\lc{\rho}{\sigma}(x_0) = \lc{\rho'}{\sigma'}(x_0) = 0$ and $\lc{\rho}{\sigma}(x_{n'+1}) = \lc{\rho'}{\sigma'}(x_{n'+1}) = 1$.
-	Hence, we can extend the set of elbows $E$ to $E' = E \cup \{x_0, x_{n'+1}\}$.
-
-	Pick two consecutive locations $x_{i}, x_{i+1}$ in $E'$ and consider the line segment $\ell_\rho'(x)$ connecting points $(x_{i}, \lc{\rho'}{\sigma'}(x_{i}))$ and $(x_{i+1}, \lc{\rho'}{\sigma'}(x_{i+1}))$ as well as the line segment $\ell_\rho(x)$ connecting points $(x_{i}, \lc{\rho}{\sigma}(x_{i}))$ and $(x_{i+1}, \lc{\rho}{\sigma}(x_{i+1}))$.
-	This is illustrated in~\cref{fig:elbows_proof}.
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.5]{figs/elbows_proof.pdf}
-    \caption{\textbf{Illustration of~\cref{thm:elbows}}.
-    }
-    \label{fig:elbows_proof}
-\end{figure}
-
-	Due to concavity of $\lc{\rho}{\sigma}$, it is clear that for all $x \in [x_{i}, x_{i+1}]$, we have $\lc{\rho}{\sigma}(x) \geq \ell_\rho(x) \geq \ell_\rho'(x) = \lc{\rho'}{\sigma}(x)$.
-	This argument can be made in all intervals $[x_{i}, x_{i+1}]$ with $i=0,\dots,n'$, so the proof is complete.
+However, since $L_{\rho'|\sigma'}(x)$ is linear between $x_i$ and $x_{i+1}$, the above conditions imply that $L_{\rho|\sigma}(x)$ is not concave, which contradicts~\cref{L-concave}. 
+Therefore, $L_{\rho|\sigma}(x) \geq L_{\rho'|\sigma'}(x)$ for all $x$ in $[0,1]$.
 \end{proof}
@@
 
-\subsection{Component-multiplicity pairs}
-\label{app:cmpairs}
-
-In general, a $1$--copy $d$--dimensional state $\rho$ is described by its $d^2$--dimensional Wigner distribution $\W{\rho}(\bmx)$. 
-The distribution $\W{\rho}(\bmx)$ is defined on the phase space, but it can be convenient to re-express this using vector notation.
-
-To each Wigner distribution $W_\rho(\x)$ we can associate \emph{component-multiplicity} pairs $\{(w_i, m_i)\}$ where the value $w_i$ occurs in the distribution $W_\rho(\x)$ with multiplicity $m_i$.
-
-As an example, for the Strange state $\rho_S := \rho_S(\epsilon=0)$ with
-\begin{equation}
-W_{\rho_S}(\x) = (-1/3, 1/6,  1/6,  1/6,  1/6,  1/6,  1/6,  1/6,  1/6)
-\end{equation}
-we have the component-multiplicity pairs: $\{( -1/3, 1), ( 1/6, 8)\}$.
-However, we might also wish more freedom and not require that the different $w_i$ values are all distinct.
-For example, the component-multiplity pairs $\{(-1/3, 1), (1/6, 2), (1/6, 3), (1/6, 3)\}$ also describe $W_{\rho_S}(\x)$.
-
-This representation is more compact when a Wigner distribution has a lot of multiplicities, and allows for simple handling of multiple copies via the following fact.
-\begin{lemma}
-Consider two Wigner distributions $\W{\rho_A}, \W{\rho_B}$ with component-multiplicity pairs 
-\begin{equation}
-	\{(w_i, m_i)\} \text{ and } \{(w_j', m_j')\},
-\end{equation}
-respectively. Then, $\{(w_i w_j', m_i m_j')\}$ gives component-multiplicity pairs for $\W{\rho_A \otimes \rho_B}$.
-\end{lemma}
-
-This is true because all components of $\W{\rho_A \otimes \rho_B}$ are of the form $w_i w_j'$ and 
-\begin{equation*}
-	\sum_{i=1}^{D_A}\sum_{j=1}^{D_B} m_i m_j' = \sum_{i=1}^{D_A} m_i \sum_{j=1}^{D_B} m_j' = d_A^2 d_B^2,
-\end{equation*}
-so the set $\{(w_i w_j', m_i m_j')\}$ contains exactly the Wigner components of $\W{\rho_A \otimes \rho_B}$ and no more.
-
-In the case of distillation protocols, we are interested in $n$--copies of a single Wigner distribution. For this, we have the following result, which follows from combinatorics.
-
-\begin{lemma}\label{lem:ncopycomponents}
-	Suppose $W_\rho(\x)$ has $D$ component-multiplicity pairs $\{(w_i, m_i)\}$.
-Then, $W_{\rho^{\otimes n}} (\x)$ has component-multiplicity pairs $\{(W_{\q}, M_{\q})\}$, where $\q$ runs through all $K$-component vectors with non-negative integer components that sum to $n$, and
-\begin{align}
-W_{\q} &= \prod_{i=1}^D w_i^{q_i} \label{eq:W}\\
-M_{\q} &= \binom{n}{q_1,q_2, \dots, q_d} \prod_{i=1}^D m_i^{q_i}, \label{eq:M}
-\end{align}
-where the term outside the product in the expression for $M_{\q}$ is the generalized binomial coefficient.
-\end{lemma}
-\begin{proof}
-	Denote by $C_D^n \coloneqq \{\bmk\}$ the set of all vectors $\bmk \coloneqq (k_1, \dots, k_D)$ with non-negative integer components that sum to $n$, i.e.
-	\begin{equation*}
-	0 \leq k_1, \dots, k_D \leq n \text{ and } k_1 + \dots + k_D = n.
-	\end{equation*}
-
-	We proceed by induction.	
-	Assume $n = 1$ and let $\bmk_i$ be the vector with its $i$-th component equal to 1 and 0's elsewhere.
-	The set $C_D^1$ consists of all vectors of this form, i.e. 
-\begin{equation*}
-	C_D^1 = \{ \bmk_i \}_{i=1,\dots,D}
-\end{equation*}
-	It is also true by direct calculation that
-\begin{equation*}
-	\left( W_{\bmk_i}, M_{\bmk_i} \right) = (w_i, m_i).
-\end{equation*}
-Therefore, $\{ (W_{\bmk}, M_{\bmk}) \}_{\bmk \in C_D^1}$ is a complete set of component-multiplicity pairs for $W$.
-
-	Assume that $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$ as given in~\cref{eq:M,eq:W} is a complete set of component-multiplicity pairs for the $n$--copy distribution $W^{\otimes n}$.
-	By construction, the distribution $W^{\otimes (n+1)} = W^{\otimes n} \otimes W$ is multiplicative, so it admits the complete set of component multiplicity pairs
-\begin{equation}
-	\{(W_{\bmk} w_i, M_{\bmk} m_i)\},\ \bmk \in C_D^n \text{ and } i=1,\dots,D.
-\end{equation}
-
-	Consider the component sum of the distribution $W^{\otimes (n+1)}$,
-\begin{align*}
-	&\sum_{\bmk \in C_D^n}\sum_{i=1}^D M_{\bmk} m_i W_{\bmk} w_i = \sum_{\bmk \in C_D^n} M_{\bmk}W_{\bmk} \sum_{i=1}^D m_i w_i =\\
-	&\sum_{\bmk \in C_D^n} \frac{n!}{k_1!\dots k_D!} \prod\limits_{i=1}^D {m_i}^{k_i}{w_i}^{k_i} \sum_{i=1}^D m_i w_i =\\
-	&\left( \sum_{i=1}^D m_i w_i \right)^n \left( \sum_{i=1}^D m_i w_i \right) = \left( \sum_{i=1}^D m_i w_i \right)^{n+1} =\\
-	&\sum_{\bmq \in C_D^{n+1}} M_{\bmq}W_{\bmq},
-\end{align*}
-where in the last expression, vectors $\bmq = (q_1, \dots, q_D)$ have non-negative integer components that sum to $(n+1)$ and 
-\begin{align*}
-	M_{\bmq} &= \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i},\\
-	W_{\bmq} &= \prod\limits_{i=1}^D {w_i}^{q_i}.
-\end{align*}
-We have used the multinomial theorem to proceed between lines 2-3 and lines 3-4 of the derivation.
-
-We have achieved a regrouping of the distribution components.
-Every component $W_{\bmq}$ is of the form $W_{\bmk} w_i$ with $q_i = k_i + 1$ and $q_j = k_j$ for $j\neq i$ and 
-\begin{align*}
-	\sum_{\bmq \in C_D^{n+1}}  \hspace{-6pt} M_{\bmq} =  \hspace{-10pt} \sum_{\bmq \in C_D^{n+1}} \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i} = 
-	\left( \sum_{i=1}^D m_i \right)^{n+1} \hspace{-10pt} = d^{n+1},
-\end{align*}
-which is the dimension of $W^{\otimes (n+1)}$.
-
-Therefore, $\{ (W_{\bmq}, M_{\bmq}) \}_{\bmq \in C_D^{n+1}}$ contains exactly the components of $W^{\otimes n}$, completing the proof.
-\end{proof}
-
-The rescaled distribution is also multiplicative, so a set of component-multiplicity pairs can be obtained for the $n$-copy rescaled distribution in the same fashion as for usual Wigner distributions.
-
 \subsection{Lorenz curve coordinates in the unital fragment}\label{app:lcsu_coord}
@@
 \end{equation}
-\ddd{Where do we use this modulo $(n+1)$? I don't understand where it's appearing.}
+\ddd{Where do we use this modulo $(n+1)$? I don't understand where it's appearing.}\nick{In both tables, wherever you see $2i$.}
 \begin{table}[h]
@@
 \end{table}
+
+\nick{The following is an alternative presentation to Table II, we get to choose one of them to keep}
 In~\cref{tab:lcsu_coord_elb_app_alt}, we present the elbow coordinates of the $n$-copy, $\epsilon$--noisy Strange state Lorenz curve in the unital fragment for any combination of parameters $n, \epsilon$.
@@
 
-\subsection{Deriving distillation bounds from the last elbow}
-\label{sec:last_elb}
-
-\ddd{[I would prefer to remove this last elbow constraint analysis, and just mention it in the main text.
-If we include it then I need to go through the details to ensure they're correct -- which is very time-consuming at this stage.
-We *can't* put glaringly sloppy/incorrect things into a paper that will be public to the world.
-Happy to remove and just mention in passing?]}
-
-We can run a similar analysis, in order to utilise the descending part of the Lorenz curves to extract bounds.
-These bounds do not offer any additional physical insight and are expressed by , but can be tighter in some scenarios.
-Here we derive an equivalent bound to our main theorem using the last elbow constraint, which we prove first.
-
-\begin{proposition}\label{prop:last_elb}
-	Consider a magic state process $\rho \longrightarrow \rho'$ with input and output Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\rho'}{\sigma'}(x)$ and denote the coordinates of the last elbow of $L_{\rho|\sigma}(x)$ by $(X_E, L_E)$ and the coordinates of the first elbow of $L_{\rho' |\sigma'}(x)$ by $(X'_E, L'_E)$.
-
-Then, given any coordinates $(x, L)$ and $(x', L')$ of the input and output Lorenz curves respectively, where $1 > x \geq X_E$ and $1 > x' \geq X'_E$, the process is possible only if
-\begin{equation}\label{eq:last_elb_bound1}
-	\frac{L - 1}{1-x} \geq \frac{L' - 1}{1-x'}.
-\end{equation}
-\end{proposition}
-\begin{proof}
-Since both pairs of coordinates are located between the endpoint $(1,1)$ and the last elbow of their respective curves, we can derive the bound via a simple interpolation on the line segment connecting the endpoint and the appropriate pair of coordinates.
-
-First assume that $x > x'$.
-Then, point $(x, L_{\rho'|\sigma'}(x))$ lies on the lines segment connecting $(1,1)$ and $(x', L')$, so by interpolating between points $(1,1)$ and $(x', L')$, we find that
-\begin{equation}
-	L_{\rho'|\sigma'}(x) = 1 + \frac{1-x}{1-x'} (L' - 1).
-\end{equation}
-Considering the Lorenz curve constraint at $x$, the process is possible only if 
-\begin{equation}
-	L = \lc{\rho}{\sigma}(x) \geq \lc{\rho'}{\sigma'}(x) = 1 + \frac{1-x}{1-x'} (L' - 1),
-\end{equation}
-which is a rearrangement of~\cref{eq:last_elb_bound1}.
-
-If instead, $x \leq x'$, the point $(x', L_{\rho|\sigma}(x'))$ lies on the lines segment connecting $(1,1)$ and $(x, L)$, so by interpolating between points $(1,1)$ and $(x, L)$, we find that
-\begin{equation}
-	L_{\rho|\sigma}(x') = 1 + \frac{1-x'}{1-x} (L - 1).
-\end{equation}
-Considering the Lorenz curve constraint at $x'$, the process is possible only if 
-\begin{equation}
-	1 + \frac{1-x'}{1-x} (L - 1) = \lc{\rho}{\sigma}(x') \geq \lc{\rho'}{\sigma'}(x) = L',
-\end{equation}
-which is again a rearrangement of~\cref{eq:last_elb_bound1}.
-\end{proof}
-
-In order to derive a bound based on the last elbow constraint, we assume that the smallest component of the equilibrium state distribution is $W_{\tau}(\bmx_\star)$ and the second smallest is $W_{\tau}(\bmy_\star)$.
-We now perform a Clifford operation on $\rho_{\rm{S}}$ so that its Wigner component is $-v(\epsilon)$ at $\bmx_\star$ and $u(\epsilon)$ at $\bmy_\star$. \nick{Is this always possible? I think not}
-Since we have that $u \leq v$ because $\epsilon \leq 3/7$, and $W_{\tau}(\bmx_\star) \geq W_{\tau}(\bmy_\star) \geq W_{\tau}(\bmx)$ for all $\bmx \in \mathbb{Z}_3^2$, the largest rescaled component occurs when $i_{\bmx_\star} = n-1$, $i_{\bmy_\star} = 1$ and $i_{\bmx} = 0$ for $\bmx \notin \{\bmx_\star, \bmy_\star\}$ and it is equal to $(-v^{n-1}u/(W_{\tau}(\bmx_\star)^{n-1}W_{\tau}(\bmy_\star))$.
-Accordingly, the coordinates of the last Lorenz curve point before $(1,1)$ are given by
-\begin{equation}
-	(x_E, L_E) = \left( 1-W_{\tau}(\bmx_\star)^{n-1}W_{\tau}(\bmy_\star), 1 + v(\epsilon)^{n-1}u(\epsilon) \right)
-\end{equation}
-for the input state and we express the same coordinates with primed quantities for the output state.
-
-We now define the quantities $\phi_\alpha$ defined in terms of $\alpha_k = \sum_{r \in \mathbb{Z}_3} \<E_k |A_{\bmx_\star} |E_k\>$.
-and $\phi_\lambda$ defined in terms of $\lambda_k = \sum_{r \in \mathbb{Z}_3} \<E_k |A_{\bmy_\star} |E_k\>$.
-This allows us to rewrite $W_{\tau}(\bmx_\star) = {e^{\beta (F - \phi_\alpha)}}/{3}$ and $W_{\tau}(\bmy_\star) = {e^{\beta (F - \phi_\lambda)}}/{3}$.
-
-Using the last elbow constraint derived in~\cref{prop:last_elb}, we can get the new bound expression,
-\begin{equation}
-	\begin{split}
-	R \leq &\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (\phi_\alpha - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (\phi'_\alpha - F')} + \\
-	&\frac{1}{n}\frac{\ln{\frac{u(\epsilon')v(\epsilon)}{u(\epsilon)v(\epsilon')}}+\beta(\phi_\alpha - \phi'_\alpha + \phi'_\lambda - \phi_\lambda)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (\phi'_\alpha - F')}
-	\end{split}
-\end{equation}
-
-We note that it is possible to perform various Clifford transformations and get a different location $(W_{\tau}(\bmx))^n$, with $\bmx \neq \bmo$, since components $W_{\rho}(\bmx) = u(\epsilon)$ are all the same as long as $\bmx \neq \bmo$.
-The effect of this is to alter the expressions for the quantities $\alpha_k$, but not the resulting bound expression.
-
 \end{document}

### 2021-05-24 notes/notes.tex
responded to points. Need to reorganise App. B. Minor comments left in App.B and App.C

@@
 
+\subsection{Deriving distillation bounds from the last elbow}
+\label{sec:last_elb}
+
+\ddd{[I would prefer to remove this last elbow constraint analysis, and just mention it in the main text.
+If we include it then I need to go through the details to ensure they're correct -- which is very time-consuming at this stage.
+We *can't* put glaringly sloppy/incorrect things into a paper that will be public to the world.
+Happy to remove and just mention in passing?]}
+
+We can run a similar analysis, in order to utilise the descending part of the Lorenz curves to extract bounds.
+These bounds do not offer any additional physical insight and are expressed by , but can be tighter in some scenarios.
+Here we derive an equivalent bound to our main theorem using the last elbow constraint, which we prove first.
+
+\begin{proposition}\label{prop:last_elb}
+	Consider a magic state process $\rho \longrightarrow \rho'$ with input and output Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\rho'}{\sigma'}(x)$ and denote the coordinates of the last elbow of $L_{\rho|\sigma}(x)$ by $(X_E, L_E)$ and the coordinates of the first elbow of $L_{\rho' |\sigma'}(x)$ by $(X'_E, L'_E)$.
+
+Then, given any coordinates $(x, L)$ and $(x', L')$ of the input and output Lorenz curves respectively, where $1 > x \geq X_E$ and $1 > x' \geq X'_E$, the process is possible only if
+\begin{equation}\label{eq:last_elb_bound1}
+	\frac{L - 1}{1-x} \geq \frac{L' - 1}{1-x'}.
+\end{equation}
+\end{proposition}
+\begin{proof}
+Since both pairs of coordinates are located between the endpoint $(1,1)$ and the last elbow of their respective curves, we can derive the bound via a simple interpolation on the line segment connecting the endpoint and the appropriate pair of coordinates.
+
+First assume that $x > x'$.
+Then, point $(x, L_{\rho'|\sigma'}(x))$ lies on the lines segment connecting $(1,1)$ and $(x', L')$, so by interpolating between points $(1,1)$ and $(x', L')$, we find that
+\begin{equation}
+	L_{\rho'|\sigma'}(x) = 1 + \frac{1-x}{1-x'} (L' - 1).
+\end{equation}
+Considering the Lorenz curve constraint at $x$, the process is possible only if 
+\begin{equation}
+	L = \lc{\rho}{\sigma}(x) \geq \lc{\rho'}{\sigma'}(x) = 1 + \frac{1-x}{1-x'} (L' - 1),
+\end{equation}
+which is a rearrangement of~\cref{eq:last_elb_bound1}.
+
+If instead, $x \leq x'$, the point $(x', L_{\rho|\sigma}(x'))$ lies on the lines segment connecting $(1,1)$ and $(x, L)$, so by interpolating between points $(1,1)$ and $(x, L)$, we find that
+\begin{equation}
+	L_{\rho|\sigma}(x') = 1 + \frac{1-x'}{1-x} (L - 1).
+\end{equation}
+Considering the Lorenz curve constraint at $x'$, the process is possible only if 
+\begin{equation}
+	1 + \frac{1-x'}{1-x} (L - 1) = \lc{\rho}{\sigma}(x') \geq \lc{\rho'}{\sigma'}(x) = L',
+\end{equation}
+which is again a rearrangement of~\cref{eq:last_elb_bound1}.
+\end{proof}
+
+In order to derive a bound based on the last elbow constraint, we assume that the smallest component of the equilibrium state distribution is $W_{\tau}(\bmx_\star)$ and the second smallest is $W_{\tau}(\bmy_\star)$.
+We now perform a Clifford operation on $\rho_{\rm{S}}$ so that its Wigner component is $-v(\epsilon)$ at $\bmx_\star$ and $u(\epsilon)$ at $\bmy_\star$. \nick{Is this always possible? I think not}
+Since we have that $u \leq v$ because $\epsilon \leq 3/7$, and $W_{\tau}(\bmx_\star) \geq W_{\tau}(\bmy_\star) \geq W_{\tau}(\bmx)$ for all $\bmx \in \mathbb{Z}_3^2$, the largest rescaled component occurs when $i_{\bmx_\star} = n-1$, $i_{\bmy_\star} = 1$ and $i_{\bmx} = 0$ for $\bmx \notin \{\bmx_\star, \bmy_\star\}$ and it is equal to $(-v^{n-1}u/(W_{\tau}(\bmx_\star)^{n-1}W_{\tau}(\bmy_\star))$.
+Accordingly, the coordinates of the last Lorenz curve point before $(1,1)$ are given by
+\begin{equation}
+	(x_E, L_E) = \left( 1-W_{\tau}(\bmx_\star)^{n-1}W_{\tau}(\bmy_\star), 1 + v(\epsilon)^{n-1}u(\epsilon) \right)
+\end{equation}
+for the input state and we express the same coordinates with primed quantities for the output state.
+
+We now define the quantities $\phi_\alpha$ defined in terms of $\alpha_k = \sum_{r \in \mathbb{Z}_3} \<E_k |A_{\bmx_\star} |E_k\>$.
+and $\phi_\lambda$ defined in terms of $\lambda_k = \sum_{r \in \mathbb{Z}_3} \<E_k |A_{\bmy_\star} |E_k\>$.
+This allows us to rewrite $W_{\tau}(\bmx_\star) = {e^{\beta (F - \phi_\alpha)}}/{3}$ and $W_{\tau}(\bmy_\star) = {e^{\beta (F - \phi_\lambda)}}/{3}$.
+
+Using the last elbow constraint derived in~\cref{prop:last_elb}, we can get the new bound expression,
+\begin{equation}
+	\begin{split}
+	R \leq &\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (\phi_\alpha - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (\phi'_\alpha - F')} + \\
+	&\frac{1}{n}\frac{\ln{\frac{u(\epsilon')v(\epsilon)}{u(\epsilon)v(\epsilon')}}+\beta(\phi_\alpha - \phi'_\alpha + \phi'_\lambda - \phi_\lambda)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (\phi'_\alpha - F')}
+	\end{split}
+\end{equation}
+
+We note that it is possible to perform various Clifford transformations and get a different location $(W_{\tau}(\bmx))^n$, with $\bmx \neq \bmo$, since components $W_{\rho}(\bmx) = u(\epsilon)$ are all the same as long as $\bmx \neq \bmo$.
+The effect of this is to alter the expressions for the quantities $\alpha_k$, but not the resulting bound expression.
+
+\begin{proof}
+Since both pairs of coordinates are located between $(0,0)$ and the first elbow of their respective curves, we can derive the bound via a simple interpolation on the line segment connecting the origin and the appropriate pair of coordinates.
+
+First assume that $x < x'$.
+Then, point $(x, L_{\rho'|\sigma'}(x))$ lies on the lines segment connecting $(0,0)$ and $(x', L')$, so by interpolating between points $(0,0)$ and $(x', L')$ at location $x$, we find that
+\begin{equation}
+	L_{\rho'|\sigma'}(x) = \frac{x}{x'}L'.
+\end{equation}
+Considering the Lorenz curve constraint at $x$, the process is possible only if 
+\begin{equation}
+	L = \lc{\rho}{\sigma}(x) \geq \lc{\rho'}{\sigma'}(x) = \frac{x}{x'}L',
+\end{equation}
+which is a rearrangement of~\cref{eq:first_elb_bound1}.
+
+If instead, $x \geq x'$, the point $(x', L_{\rho|\sigma}(x'))$ lies on the lines segment connecting $(0,0)$ and $(x, L)$, so by interpolating between points $(0,0)$ and $(x, L)$ at location $x'$, we find that
+\begin{equation}
+	L_{\rho|\sigma}(x') = \frac{x'}{x}L.
+\end{equation}
+Considering the Lorenz curve constraint at $x'$, the process is possible only if 
+\begin{equation}
+	\frac{x'}{x}L = \lc{\rho}{\sigma}(x') \geq \lc{\rho'}{\sigma'}(x) = L',
+\end{equation}
+which is again a rearrangement of~\cref{eq:first_elb_bound1}.
+\end{proof}
+
+	Conversely, assume that $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\rho'}{\sigma'}(x_{i})$ for all $i = 1,\dots,r$.
+	First, let $x_0 = 0$ and $x_{n'+1} = 1$, so that $\lc{\rho}{\sigma}(x_0) = \lc{\rho'}{\sigma'}(x_0) = 0$ and $\lc{\rho}{\sigma}(x_{n'+1}) = \lc{\rho'}{\sigma'}(x_{n'+1}) = 1$.
+	Hence, we can extend the set of elbows $E$ to $E' = E \cup \{x_0, x_{n'+1}\}$.
+
+	Pick two consecutive locations $x_{i}, x_{i+1}$ in $E'$ and consider the line segment $\ell_\rho'(x)$ connecting points $(x_{i}, \lc{\rho'}{\sigma'}(x_{i}))$ and $(x_{i+1}, \lc{\rho'}{\sigma'}(x_{i+1}))$ as well as the line segment $\ell_\rho(x)$ connecting points $(x_{i}, \lc{\rho}{\sigma}(x_{i}))$ and $(x_{i+1}, \lc{\rho}{\sigma}(x_{i+1}))$.
+	This is illustrated in~\cref{fig:elbows_proof}.
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.5]{figs/elbows_proof.pdf}
+    \caption{\textbf{Illustration of~\cref{thm:elbows}}.
+    }
+    \label{fig:elbows_proof}
+\end{figure}
+
+	Due to concavity of $\lc{\rho}{\sigma}$, it is clear that for all $x \in [x_{i}, x_{i+1}]$, we have $\lc{\rho}{\sigma}(x) \geq \ell_\rho(x) \geq \ell_\rho'(x) = \lc{\rho'}{\sigma}(x)$.
+	This argument can be made in all intervals $[x_{i}, x_{i+1}]$ with $i=0,\dots,n'$, so the proof is complete.
+
 \end{document}

### 2021-05-24 magic_paper.tex
Added changes discussed except App.B

@@
 
+\nick{What happens when the bound $=0$ or $1$?}
+Note that it is always true that $L_0/x_0 > 1$ for any Lorenz curve of a state which is not free (this is because the free state Lorenz curve is a straight line connecting $(0,0$ and $(1,1)$ while all other Lorenz curves lie above it.)
+Therefore, in the bound expression
+\begin{equation}\label{eq:rate_bounds_proof}
+	R = \dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (\phi - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (\phi' - F')},
+\end{equation}
+where the denominator is always positive (and we've set equality to saturate the bound), we can rewrite it as
+\begin{equation}
+	\frac{m}{n}\frac{\ln{(L_0/x_0)}}{\ln{(L'_0/x'_0)}} = R.
+\end{equation}
+If $R=0$ it means that $m=0$ (zero output states) or the slope $L_0/x_0$ equals 1 (input state is free).
+If $R=1$, we get a trade-off between copy number and Lorenz curve slopes,
+\begin{equation}
+	\left(\frac{L_0}{x_0}\right)^m = \left(\frac{L'_0}{x'_0}\right)^n.
+\end{equation}
+
 \section{Outlook and open questions}
@@
 \end{lemma}
-
-This is true because all components of $\W{\rho_A \otimes \rho_B}$ are of the form $w_i w_j'$ and 
+\begin{proof}
+	This result is true because all components of $\W{\rho_A \otimes \rho_B}$ are of the form $w_i w_j'$ and 
 \begin{equation*}
-	\sum_{i=1}^{D_A}\sum_{j=1}^{D_B} m_i m_j' = \sum_{i=1}^{D_A} m_i \sum_{j=1}^{D_B} m_j' = d_A^2 d_B^2,
+	\sum_{i}\sum_{j} m_i m_j' = \sum_{i} m_i \sum_{j} m_j' = d_A^2 d_B^2,
 \end{equation*}
-so the set $\{(w_i w_j', m_i m_j')\}$ contains exactly the Wigner components of $\W{\rho_A \otimes \rho_B}$ and no more.
+where $d_A, d_B$ are the dimensions of $\rho_A, \rho_B$ respectively, and
+so the set $\{(w_i w_j', m_i m_j')\}$ contains exactly the Wigner components of $\W{\rho_A \otimes \rho_B}$.
+\end{proof}
 
@@
 \end{align}
-The labels $\text{LHS}, \text{RHS}$ denote that the components contribute to the left hand side or the right hand side of the maximum (including the maximum) of the Lorenz curve.
-To simplify notation, we also use multiplication modulo $(n+1)$, specifically, for any positive integer $m \leq 2n$:
-\begin{equation}
-	m \hspace{-6pt}\mod{\hspace{-2pt}(n+1)} = 
-	\begin{cases}
-		m,\ &\text{if } 0 \leq m \leq n, \\
-		m - n - 1,\ &\text{if } n < m \leq 2n.
-	\end{cases}
-\end{equation}
-\ddd{Where do we use this modulo $(n+1)$? I don't understand where it's appearing.}\nick{In both tables, wherever you see $2i$.}
+The labels $\text{LHS}, \text{RHS}$ denote that the components contribute to the left hand side or the right hand side of the maximum of the Lorenz curve.
+The maximum is included in the $\text{LHS}$.
 \begin{table}[h]
@@
   The expressions change depending on the error $\epsilon$, the parity of the number of copies $n$ and whether the index $i$ is lower or higher than the index of the Lorenz curve maximum (LHS vs RHS).
-  Multiplication $2i$ is considered $\hspace{-6pt}\mod{\hspace{-2pt}(n+1)}$.}
+  The term $2i$ is considered $\hspace{-6pt}\mod{\hspace{-2pt}(n+1)}$, so that $2i\ \hspace{-6pt}\mod{\hspace{-2pt}(n+1)} = 2i - n - 1$ if $i > \left\lfloor n/2 \right\rfloor$.}
   \label{tab:lcsu}
@@
   \begin{tabular}{c|c|c|r|r}
-\multicolumn{3}{c|}{\multirow{2}{*}{Case}} & \multicolumn{1}{c|}{$x_{i}$} & \multicolumn{1}{c}{$L_{i}$} \\
-    \multicolumn{3}{c|}{} & \multicolumn{1}{c|}{$x_{i} - x_{\lfloor n/2 \rfloor}$} & \multicolumn{1}{c}{$L_{i} - L_{\lfloor n/2 \rfloor}$} \\[0.5ex]\hline 
+%\multicolumn{2}{c|}{\multirow{2}{*}{Case}} & \multicolumn{1}{c|}{LHS} & \multicolumn{1}{c|}{$x_{i}$} & \multicolumn{1}{c}{$L_{i}$} \\
+%    \multicolumn{2}{c|}{} & \multicolumn{1}{c|}{RHS} & \multicolumn{1}{c|}{$x_{i} - x_{\lfloor n/2 \rfloor}$} & \multicolumn{1}{c}{$L_{i} - L_{\lfloor n/2 \rfloor}$} \\[0.5ex]
+\hline 
     \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$0\leq \epsilon < \frac{3}{7}$}}} & \hspace{0.8ex}\multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ even}}}\hspace{0.8ex} & LHS & $\Phi_+\left(2i;n,\frac{8}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\
@@
   \caption{Lorenz curve elbow coordinates in the unital fragment. 
+  \nick{For lines labelled as LHS, the expressions correspond to $x_i$ and $L_i$ respectively, while for lines labelled as RHS, the expressions correspond to $x_i - x_{\lfloor n/2 \rfloor}$ and $L_i - L_{\lfloor n/2 \rfloor}$ respectively}.
   The coordinate expressions depend on the error $\epsilon$, the parity of the number of copies $n$ and the location of the elbow relative to the maximum (LHS vs RHS).
-  Multiplication $2i$ is considered $\hspace{-6pt}\mod{\hspace{-2pt}(n+1)}$.
+  The term $2i$ is considered $\hspace{-6pt}\mod{\hspace{-2pt}(n+1)}$, so that $2i\ \hspace{-6pt}\mod{\hspace{-2pt}(n+1)} = 2i - n - 1$ if $i > \left\lfloor n/2 \right\rfloor$.
   The point $(x_{-1}, L_{-1}) \coloneqq (0,0)$ is not included in the table.
@@
   \label{tab:lcsu_coord_elb_app}
-\end{table}
-
-\nick{The following is an alternative presentation to Table II, we get to choose one of them to keep}
-In~\cref{tab:lcsu_coord_elb_app_alt}, we present the elbow coordinates of the $n$-copy, $\epsilon$--noisy Strange state Lorenz curve in the unital fragment for any combination of parameters $n, \epsilon$.
-To simplify notation, we define in terms of $n, \epsilon$ an exponentially growing term $A$ and a probability $p$, as follows:
-\begin{align}
-	A &= \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n, \\
-	p &= \frac{12-4\epsilon}{15-8\epsilon}.
-\end{align}
-
-\begin{table}[h]
-  \def\arraystretch{1.5}
-  \centering
-  \begin{tabular}{c|c|c|r|r}
-    \multicolumn{3}{c|}{Case} & \multicolumn{1}{c}{$x_{i}$} & \multicolumn{1}{|c}{$L_{i}$} \\[0.5ex]\hline
-   \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$0\leq \epsilon < \frac{3}{7}$}}} & \hspace{0.8ex}\multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ even}}}\hspace{0.8ex} & LHS & $x_{\lfloor n/2 \rfloor} + \Phi_+\left(2i;n,\frac{8}{9}\right)$ & $L_{\lfloor n/2 \rfloor} + A \Phi_+\left(2i;n,p\right)$ \\
-    & & RHS & $x_{\lfloor n/2 \rfloor} + \Phi_-\left(2i;n,\frac{1}{9}\right)$ & $L_{\lfloor n/2 \rfloor} - A \Phi_-\left(2i;n,1-p\right)$ \\ \cline{2-5}
-    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $x_{\lfloor n/2 \rfloor} + \Phi_-\left(2i;n,\frac{8}{9}\right)$ & $L_{\lfloor n/2 \rfloor} + A \Phi_-\left(2i;n,p\right)$ \\
-    & & RHS & $x_{\lfloor n/2 \rfloor} + \Phi_-\left(2i;n,\frac{1}{9}\right)$ & $L_{\lfloor n/2 \rfloor} - A \Phi_-\left(2i;n,1-p\right)$ \\ \hline
-    \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$\frac{3}{7}\leq \epsilon < \frac{3}{4}$}}} & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ even}}} & LHS & $x_{\lfloor n/2 \rfloor} + \Phi_+\left(2i;n,\frac{1}{9}\right)$ & $L_{\lfloor n/2 \rfloor} + A \Phi_+\left(2i;n,1-p\right)$ \\
-    & & RHS & $x_{\lfloor n/2 \rfloor} + \Phi_-\left(2i;n,\frac{8}{9}\right)$ & $L_{\lfloor n/2 \rfloor} - A \Phi_-\left(2i;n,p\right)$ \\ \cline{2-5}
-    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $x_{\lfloor n/2 \rfloor} + \Phi_+\left(2i;n,\frac{1}{9}\right)$ & $L_{\lfloor n/2 \rfloor} + A \Phi_+\left(2i;n,1-p\right)$ \\
-    & & RHS & $x_{\lfloor n/2 \rfloor} + \Phi_+\left(2i;n,\frac{8}{9}\right)$ & $L_{\lfloor n/2 \rfloor} - A \Phi_+\left(2i;n,p\right)$ \\ \hline
-  \end{tabular}
-  \caption{Lorenz curve elbow coordinates in the unital fragment.
-  The coordinate expressions depend on the error $\epsilon$, the parity of the number of copies $n$ and the location of the elbow relative to the maximum (LHS vs RHS).
-  Multiplication $2i$ is considered $\hspace{-6pt}\mod{\hspace{-2pt}(n+1)}$.
-  For completeness, note that $(x_{-1}, L_{-1}) \coloneqq (0,0)$ is not included in the table.
-  }
-  \label{tab:lcsu_coord_elb_app_alt}
 \end{table}
@@
 \end{equation}
+\nick{Note that $3v(\epsilon')e^{-\beta (F' - \phi')} > 1$ because $\rho_{\rm{S}}(\epsilon')$ is not a free state, so the initial slope of the its Lorenz curve exceeds $1$.}
 Taking the natural logarithm on both sides and rearranging gives the bound

### 2021-05-25 magic_paper.tex
Appendix full clean-up. Comments in red to be accepted

@@
 	A magic protocol aims to turn $n$ copies of some magic state $\rho$ to $m$ copies of some other state $\rho'$.
-	Constraints on the efficiency of the protocol can be imposed by considering its action on a separate probe state $\tau$.
-    } \ddd{[Not the clearest - we can zoom-chat on this.]}
+	Constraints on the efficiency of the protocol can be imposed by considering its action on a separate probe state $\tau$ which tranforms to $\tau'$ with free energy $F \rightarrow F'$.
+	A ``magic free energy'' $\phi \rightarrow \phi'$ connects the two state conversions under the protocol. \nick{FIX}
+    }
     \label{fig:sketch}
@@
 
+\nick{repeats intro}
 We wish to consider how physical constraints that may be hardware specific, affect magic distillation rates.
@@
 For example, there may be non-trivial thermal noise in the physical set-up or the accessible operations, there might be strong bias in the noise present, or we might be limited in how easily certain gates can be realised.~\cite{Aliferis_2008, Stephens_2013, Li_2015, Babbush_2018, Tuckett_2019, Guillaud_2019, Fowler_2019}.
-\nick{repeats intro}
 
@@
 
+\nick{re-write based on new relative majorisation approach}
 It is now possible to consider magic distillation rates within $\sigma$--fragments and then see how the bounds on the distillation rates depend on the choice of the fragment we work within.
@@
 Do isotropic maps have better bounds, or does bias towards some pure stabilizer state provide more freedom?
-\nick{re-write based on new relative majorisation approach}
 
@@
 
-As shown in Appendix \ref{lemma:Lorenz_linearity}, the Lorenz curve for any quasi-probability distribution obeys the following linearity condition
+As shown in~\cref{lemma:Lorenz_linearity}, the Lorenz curve for any quasi-probability distribution obeys the following linearity condition
 \begin{equation}
@@
 \end{equation}
-for all $a >0$ and any $b \in \mathbb{R}$. We now have that
+for any $a >0$ and $b \in \mathbb{R}$. We now have that
 \begin{equation}
@@
 Note, however, that unlike any monotone, this is not a single numerical constraint, but a \emph{family} of constraints.
-Indeed, for $n$ copies of a $d$--dimensional system the number of terms in $W_{\rho}$ is $d^{2n}$, so the Lorenz curve condition corresponds to exponentially many constraints, of which though there are at most as many independent constraints as there are elbows in the Lorenz curve of the output state, as proved in~\cref{thm:elbows} of~\cref{app:frag}.
+Indeed, for $n$ copies of a $d$--dimensional system the number of terms in $W_{\rho}$ is $d^{2n}$, so the Lorenz curve condition corresponds to exponentially many constraints, of which though there are at most as many independent constraints as there are elbows in the Lorenz curve of the output state, as proved in~\cref{thm:elbows}.
 In principle, any one location $x$ provides some valid constraint leading to an upper distillation bound, while optimising over the location provides the strictest majorisation bound.
@@
 \begin{proposition}\label{prop:rmajor}
-Given probability distributions $\bmx, \bmy$, $\r , \r'$, such that the components of $\r$ and $\r'$ are positive, the following statements are equivalent:
+Given probability distributions $\p, \q$, $\r , \r'$, such that the components of $\r$ and $\r'$ are positive, the following statements are equivalent:
   \begin{enumerate}
-    \item[(i)] $\bmy = A\bmx$ and $\r' = A\r$ for a stochastic map $A$;
-    \item[(ii)]\label{en:tm3} $\sum\limits_{i=1}^n \abs{x_i - r_i t} \leq \sum\limits_{i=1}^n \abs{y_i - r'_i t}$ for all $t \in \mathbb{R}$;
-    \item[(iii)] $L_{\bmx|\r}(t) \leq L_{\bmy|\r'}(t)$ for $t\in [0,1)$ and \vspace{5pt}\\ $L_{\bmx|\r}(1) = L_{\bmy|\r'}(1)$.
+    \item[(i)] $\q = A\p$ and $\r' = A\r$ for a stochastic map $A$;
+    \item[(ii)]\label{en:tm3} $\sum\limits_{i=1}^n \abs{p_i - r_i t} \leq \sum\limits_{i=1}^n \abs{q_i - r'_i t}$ for all $t \in \mathbb{R}$;
+    \item[(iii)] $L_{\p|\r}(t) \leq L_{\q|\r'}(t)$ for $t\in [0,1)$ and \vspace{5pt}\\ $L_{\p|\r}(1) = L_{\q|\r'}(1)$.
   \end{enumerate}
@@
 
+\subsection{Relative majorization for quasi-distributions}
+\label{app:rel_quasi}
+
+We now show that the Lorenz curve is concave in the context of quasi-distributions.
 \begin{lemma}\label{L-concave} Let $\p$ be a quasi-probability distribution and let $\r$ be a probability distribution with strictly non-zero components.
 Then $L_{\p|\r}(x)$ is a concave function on $[0,1]$.
+\nick{
+\begin{proof}
+	The Lorenz curve of $\p$ relative to $\r$ passes through $(0,0)$ and the points $(\sum_{i=1}^k{r_{\pi(i)}}, \sum_{i=1}^k p_{\pi(i)})$ where $\pi$ is the permutation that puts $p_i/r_i$ in non-increasing order.
+	By construction, the slope of the curve attains the values $p_{\pi(i)}/r_{\pi(i)}$ throughout the interval $[0,1]$, which is a non-increasing sequence due to the definition of $\pi$.
+	Therefore, the Lorenz curve is concave.
+\end{proof}
+}
 \begin{proof}Let $L_{\p|\r}(x)$ attain its maximum at $x=x_\star$.
@@
 
-The following result is used in the text to relate relative majorization of quasi-distributions to their Lorenz curves.
+The following result is used in~\cref{sec:lc} to prove that the Lorenz curve condition due to relative majorization is true for quasi-distributions.
 \begin{proposition}\label{lemma:Lorenz_linearity}
 	Let $\p$ be a quasi-probability distribution and let $\r$ be a probability distribution with strictly non-zero components. 
-Let $a > 0$ and $b \in \mathbb{R}$ then $L_{a\p + b \r | \r} (x) = a L_{\p |\r}(x) + b x$.
+	Then, $L_{a\p + b \r | \r} (x) = a L_{\p |\r}(x) + b x$ for any constants $a > 0$ and $b \in \mathbb{R}$.
 \end{proposition}
@@
 The following lemma shows that the re-scaled Lorenz curves behave in a natural way under tensor products. 
-\begin{proposition}
+\begin{proposition}\label{prop:rescaled_multi}
 	Let $\tau_A, \tau_B$ be full rank stabilizer states on systems $A$ and $B$, and let $\rho_A, \rho_B$ be arbitrary states on $A,B$. Then the rescaled quasi-distribution obeys
@@
 \end{proposition}
-\begin{proof} This follows from the multiplicativity of the Wigner distribution. 
+\begin{proof} This follows from the multiplicativity of the Wigner distribution,
 \begin{align}
@@
  &= \frac{W_{\rho_A } (\x_A )W_{\rho_B } (\x_B )}{W_{\tau_A } (\x_A )W_{\tau_B } (\x_B )}\nonumber \\
-  &= W_{\rho_A | \tau_A}(\x_A) W_{\rho_B | \tau_B}(\x_B)\nonumber,
-\end{align}
-as claimed.
+  &= W_{\rho_A | \tau_A}(\x_A) W_{\rho_B | \tau_B}(\x_B). \nonumber
+\end{align}
 \end{proof}
 
-%\subsection{Component-multiplicity pairs}
-%\label{app:cmpairs}
+\subsection{Component-multiplicity pairs}
+\label{app:cmpairs}
 
@@
 The distribution $\W{\rho}(\bmx)$ is defined on the phase space, but it can be convenient to re-express this using vector notation.
+We discuss this in terms of Wigner distributions, but there is nothing to prevent the discussion from applying to rescaled Wigner distributions as well.
 
@@
 \begin{lemma}
-Consider two Wigner distributions $\W{\rho_A}, \W{\rho_B}$ with component-multiplicity pairs 
+Consider two Wigner distributions $\W{\rho_A}(\x_A), \W{\rho_B}(\x_B)$ with component-multiplicity pairs 
 \begin{equation}
@@
 \end{equation}
-respectively. Then, $\{(w_i w_j', m_i m_j')\}$ gives component-multiplicity pairs for $\W{\rho_A \otimes \rho_B}$.
+respectively. Then, $\{(w_i w_j', m_i m_j')\}$ gives component-multiplicity pairs for $\W{\rho_A \otimes \rho_B}(\x_A \oplus \x_B)$.
 \end{lemma}
 \begin{proof}
-	This result is true because all components of $\W{\rho_A \otimes \rho_B}$ are of the form $w_i w_j'$ and 
+	This result is true because all components of $\W{\rho_A \otimes \rho_B}(\x_A \oplus \x_B)$ are of the form $w_i w_j'$ and 
 \begin{equation*}
@@
 where $d_A, d_B$ are the dimensions of $\rho_A, \rho_B$ respectively, and
-so the set $\{(w_i w_j', m_i m_j')\}$ contains exactly the Wigner components of $\W{\rho_A \otimes \rho_B}$.
+so the set $\{(w_i w_j', m_i m_j')\}$ contains exactly the Wigner components of $\W{\rho_A \otimes \rho_B}(\x_A \oplus \x_B)$.
 \end{proof}
-
-In the case of distillation protocols, we are interested in $n$--copies of a single Wigner distribution. For this, we have the following result, which follows from combinatorics.
-
+The above result also applies when we consider re-scaled Wigner distributions, crucially due to the multiplicativity result shown in~\cref{prop:rescaled_multi}.
+
+In the case of distillation protocols, we are interested in copies of distributions. 
+For this, we have the following result, which follows from combinatorics.
 \begin{lemma}\label{lem:ncopycomponents}
-	Suppose $W_\rho(\x)$ has $D$ component-multiplicity pairs $\{(w_i, m_i)\}$.
-Then, $W_{\rho^{\otimes n}} (\x)$ has component-multiplicity pairs $\{(W_{\q}, M_{\q})\}$, where $\q$ runs through all $K$-component vectors with non-negative integer components that sum to $n$, and
+	Suppose $W_\rho(\x)$ has a set of $D$ component-multiplicity pairs $\{(w_i, m_i)\}$.
+Then, $W_{\rho^{\otimes n}} (\x)$ has component-multiplicity pairs $\{(W_{\q}, M_{\q})\}$, with index $\q$ running through all vectors $(q_1, \dots, q_D)$, where $q_1, \dots, q_D$ are non-negative integers that sum to $n$, and
 \begin{align}
 	W_{\q} &= \prod_{i=1}^D w_i^{q_i} \label{eq:W}\\
-M_{\q} &= \binom{n}{q_1,q_2, \dots, q_d} \prod_{i=1}^D m_i^{q_i}, \label{eq:M}
-\end{align}
-where the term outside the product in the expression for $M_{\q}$ is the generalized binomial coefficient.
+	M_{\q} &= \binom{n}{q_1,q_2, \dots, q_d} \prod_{i=1}^D m_i^{q_i}. \label{eq:M}
+\end{align}
+The term outside the product in the expression for $M_{\q}$ is the generalized binomial coefficient,
+\begin{equation}
+	\binom{n}{q_1,q_2, \dots, q_d} := \frac{n!}{q_1!\dots q_D!}.
+\end{equation}
 \end{lemma}
@@
 \end{equation*}
-Therefore, $\{ (W_{\bmk}, M_{\bmk}) \}_{\bmk \in C_D^1}$ is a complete set of component-multiplicity pairs for $W$.
-
-	Assume that $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$ as given in~\cref{eq:M,eq:W} is a complete set of component-multiplicity pairs for the $n$--copy distribution $W^{\otimes n}$.
-	By construction, the distribution $W^{\otimes (n+1)} = W^{\otimes n} \otimes W$ is multiplicative, so it admits the complete set of component multiplicity pairs
+Therefore, $\{ (W_{\bmk}, M_{\bmk}) \}_{\bmk \in C_D^1}$ is a complete set of component-multiplicity pairs for $W_\rho(\x)$.
+
+	Assume that $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$ as given in~\cref{eq:M,eq:W} is a complete set of component-multiplicity pairs for the $n$--copy distribution $W_{\rho^{\otimes n}}(\bmx) = W_{\rho}(\bmx)^{\otimes n}$.
+	By construction, the distribution $W_{\rho}(\bmx)^{\otimes (n+1)} = W_{\rho}(\bmx)^{\otimes n} \otimes W_{\rho}(\bmx)$, so it admits the complete set of component multiplicity pairs
 \begin{equation}
@@
 
-	Consider the component sum of the distribution $W^{\otimes (n+1)}$,
+	Consider the component sum of the distribution $W_{\rho}(\bmx)^{\otimes (n+1)}$,
 \begin{align*}
@@
 	\sum_{\bmq \in C_D^{n+1}}  \hspace{-6pt} M_{\bmq} =  \hspace{-10pt} \sum_{\bmq \in C_D^{n+1}} \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i} = 
-	\left( \sum_{i=1}^D m_i \right)^{n+1} \hspace{-10pt} = d^{n+1},
+	\left( \sum_{i=1}^D m_i \right)^{n+1} \hspace{-10pt} = d^{2(n+1)},
 \end{align*}
-which is the dimension of $W^{\otimes (n+1)}$.
-
-Therefore, $\{ (W_{\bmq}, M_{\bmq}) \}_{\bmq \in C_D^{n+1}}$ contains exactly the components of $W^{\otimes n}$, completing the proof.
+which is the dimension of $W_{\rho}(\bmx)^{\otimes (n+1)}$.
+
+Therefore, $\{ (W_{\bmq}, M_{\bmq}) \}_{\bmq \in C_D^{n+1}}$ contains exactly the components of $W_{\rho}(\bmx)^{\otimes n}$, completing the proof.
 \end{proof}
-
-The rescaled distribution is also multiplicative, so a set of component-multiplicity pairs can be obtained for the $n$-copy rescaled distribution in the same fashion as for usual Wigner distributions.
-
-We now prove the following result on the relation between majorization in a particular fragment and mana, which was stated in~\cref{sec:monotones_frag}.
-
+Once again, the above result applies on re-scaled Wigner distributions as well.
+
+\subsection{Results on Lorenz curve constraints}
+\label{app:lc_constraints}
+
+We first prove the following result on the relation between majorization in a particular fragment and mana, which was stated in~\cref{sec:monotones_frag}.
 \begingroup
@@
 
-We now show that the relative majorization condition can be reduced to considering the elbows of the output Lorenz curve.
+The following result, referenced in~\cref{sec:major_frag}, reduces the Lorenz curve condition on the interval $[0,1]$ to a finite set of independent inequalities and can therefore simplify the computation of relative majorization constraints in practical scenarios.
 \begin{proposition}\label{thm:elbows}
@@
 \end{proof}
-The above result simplifies the computation of relative majorization constraints to looking at the elbows of the output Lorenz curve.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \end{align}
-They are symmetric about $p=1/2$, namely $S(p) = S(1-p)$ and $\ent{p}{q} = \ent{1-p}{1-q}$. We also have the entropic bounds
+They are symmetric about $p=1/2$ and $q=1/2$, namely $S(p) = S(1-p)$ and $\ent{p}{q} = \ent{1-p}{1-q}$. We also have the entropic bounds
 \begin{lemma}\label{lem:comb_bounds}
@@
 \end{lemma}
-The proof provided in~\cite{cit:ash} proceeds with direct calculation for the edge cases $\ell = 1,2, n-1, n-2$ and use Stirling's approximation for the remaining cases.
-The bounds~\cref{lem:comb_bounds} can be used to derive the following upper and lower bounds on the functions $\Phi_+, \Phi_-$.
-
-We rewrite the functions as
+The proof provided in~\cite{cit:ash} proceeds with direct calculation for the edge cases $\ell = 1,2, n-1, n-2$ and use of Stirling's approximation for the remaining cases.
+The bounds in~\cref{lem:comb_bounds} can be directly inserted into the expressions of functions $\Phi_+$ and $\Phi_-$ to derive strict upper and lower bounds.
+
+It is also possible to derive more manageable bounds on $\Phi_+, \Phi_-$.
+To this end, we rewrite the functions as
 \begin{equation}
@@
 
-The Wigner distribution of the $n$--copy $\epsilon$--noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ is given by $\W{\rho_{\rm{S}}(\epsilon)^{\otimes n}} = W_{\rho_{\rm{S}}(\epsilon)}^{\otimes n}$ and, using~\cref{lem:ncopycomponents} in the unital fragment, we can associate it with the set $\{(w_i, m_i)\}_{i=0,\dots,n}$ of component-multiplicity pairs, as presented in~\cref{tab:lcsu} for all different combinations of parameters $n,\epsilon$.
+The Wigner distribution of the $n$--copy $\epsilon$--noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ is given by $\W{\rho_{\rm{S}}(\epsilon)^{\otimes n}} = W_{\rho_{\rm{S}}(\epsilon)}^{\otimes n}$ and, using~\cref{lem:ncopycomponents} in the unital fragment, we can associate it with a set $\{(w_i, m_i)\}_{i=0,\dots,n}$ of component-multiplicity pairs, the elements of which are presented in~\cref{tab:lcsu} for all different combinations of physical parameters $n, \epsilon$.
 We split the values of index $i$ into two intervals, defined precisely as
@@
 \end{align}
-The labels $\text{LHS}, \text{RHS}$ denote that the components contribute to the left hand side or the right hand side of the maximum of the Lorenz curve.
-The maximum is included in the $\text{LHS}$.
+The labels $\text{LHS}, \text{RHS}$ denote that the components contribute to the left hand side or the right hand side of the Lorenz curve maximum.
+The maximum is included in the $\text{LHS}$ interval.
 \begin{table}[h]
@@
   \caption{Wigner components $w_{i}(n, \epsilon)$ of $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ along with their multiplicities $m_{i}(n, \epsilon)$, with $0 \leq i \leq n$.
-  The expressions change depending on the error $\epsilon$, the parity of the number of copies $n$ and whether the index $i$ is lower or higher than the index of the Lorenz curve maximum (LHS vs RHS).
+  The expressions change depending on the error $\epsilon$, the parity of the number of copies $n$ and whether the index $i$ is lower or higher than the index of the Lorenz curve maximum (LHS or RHS).
   The term $2i$ is considered $\hspace{-6pt}\mod{\hspace{-2pt}(n+1)}$, so that $2i\ \hspace{-6pt}\mod{\hspace{-2pt}(n+1)} = 2i - n - 1$ if $i > \left\lfloor n/2 \right\rfloor$.}
@@
 therefore expressions for the Lorenz curve coordinates follow from summing up the Wigner components in decreasing order.
-As a result, every Lorenz curve in the unital fragment contains at most $n$ elbows, which, along with the boundary points $(x_{-1}, L_{-1}) := (0,0)$ and $(x_{n}, L_{n}) := (1,1)$, are labelled by 
+\nick{As a result, every Strange state Lorenz curve in the unital fragment generally contains $n$ elbows.
+In the case of accidental degeneracies among Wigner components, some elbows my be straightened out.}
+Including the boundary points $(x_{-1}, L_{-1}) := (0,0)$ and $(x_{n}, L_{n}) := (1,1)$, we label these elbows as 
 \begin{equation*}
@@
 \end{equation*}
-where the coordinates are
+where the coordinates are given by
 \begin{equation}
@@
 
-In~\cref{tab:lcsu_coord_elb_app}, we present the elbow coordinates of the $n$-copy, $\epsilon$--noisy Strange state Lorenz curve in the unital fragment for any combination of parameters $n, \epsilon$.
+In~\cref{tab:lcsu_coord_elb_app}, we present the elbow coordinates of the $n$-copy, $\epsilon$--noisy Strange state Lorenz curve in the unital fragment for any combination of physical parameters $n, \epsilon$.
 \begin{table}[h]
@@
   \end{tabular}
-  \caption{Lorenz curve elbow coordinates in the unital fragment. 
-  \nick{For lines labelled as LHS, the expressions correspond to $x_i$ and $L_i$ respectively, while for lines labelled as RHS, the expressions correspond to $x_i - x_{\lfloor n/2 \rfloor}$ and $L_i - L_{\lfloor n/2 \rfloor}$ respectively}.
-  The coordinate expressions depend on the error $\epsilon$, the parity of the number of copies $n$ and the location of the elbow relative to the maximum (LHS vs RHS).
+  \caption{Strange state Lorenz curve elbow coordinates in the unital fragment, with $0 \leq i \leq n$. 
+  \nick{Rows labelled as LHS express the coordinates $x_i$ and then $L_i$, while rows labelled as RHS, express the differences $x_i - x_{\lfloor n/2 \rfloor}$ and then $L_i - L_{\lfloor n/2 \rfloor}$}.
+  The coordinate expressions depend on the error $\epsilon$, the parity of the number of copies $n$ and the location of the elbow relative to the maximum (LHS or RHS).
   The term $2i$ is considered $\hspace{-6pt}\mod{\hspace{-2pt}(n+1)}$, so that $2i\ \hspace{-6pt}\mod{\hspace{-2pt}(n+1)} = 2i - n - 1$ if $i > \left\lfloor n/2 \right\rfloor$.
@@
     &\text{where } p_{ijk} = \frac{k + (j-1)9^{n-n'}}{9^{n-n'} m_{i}} \nonumber\\
-    &\text{for } i=0,\dots,n',\ j = 1,\dots,m_{i}(n', \epsilon') \text{ and } k = 1,\dots,9^{n-n'}. \nonumber
+    &\text{for } i=0,\dots,n',\ j = 1,\dots,m_{i}(n', \epsilon'),\ k = 1,\dots,9^{n-n'}. \nonumber
 \end{align}
@@
 \end{equation}
-\nick{Note that $3v(\epsilon')e^{-\beta (F' - \phi')} > 1$ because $\rho_{\rm{S}}(\epsilon')$ is not a free state, so the initial slope of the its Lorenz curve exceeds $1$.}
+\nick{We stress that $3v(\epsilon')e^{-\beta (F' - \phi')} > 1$ always, because $\rho_{\rm{S}}(\epsilon')$ is not a free state, so the initial slope of its Lorenz curve exceeds $1$.}
 Taking the natural logarithm on both sides and rearranging gives the bound
@@
 This is unique, since the eigenstates form an orthonormal basis.
+\nick{Clifford processing?}
 
@@
 
-Using this notation, the values and multiplicities of the $n$--copy distribution $\bmw(\rho_n |\tau_n)$ are computed in~\cref{lem:ncopycomponents} in~\cref{app:cmpairs}. The values are given by 
+Using this notation, the values and multiplicities of the $n$--copy distribution $\bmw(\rho_n |\tau_n)$ are computed in~\cref{lem:ncopycomponents}. The values are given by 
 \begin{align}\label{eq:ncopy_w_rescaled}

### 2021-05-26 magic_paper.tex
small changes

@@
 Using the Lorenz curve perspective, it is simple to construct other monotones.
-For example, within a given fragment, the area above $L=1$ is another magic monotone.
+For example, within a given fragment, the area above the horizontal line $y = 1$ is another magic monotone.
 \begin{lemma}
@@
 \begin{proof}
-	The Lorenz curve of $\p$ relative to $\r$ passes through $(0,0)$ and the points $(\sum_{i=1}^k{r_{\pi(i)}}, \sum_{i=1}^k p_{\pi(i)})$ where $\pi$ is the permutation that puts $p_i/r_i$ in non-increasing order.
-	By construction, the slope of the curve attains the values $p_{\pi(i)}/r_{\pi(i)}$ throughout the interval $[0,1]$, which is a non-increasing sequence due to the definition of $\pi$.
+	The Lorenz curve of $\p$ relative to $\r$ passes through the origin $(r_{\pi(0)}, p_{\pi(0)}) := (0,0)$ and the points $(\sum_{i=1}^k r_{\pi(i)}, \sum_{i=1}^k p_{\pi(i)})$ where $\pi$ is the permutation that puts $p_i/r_i$ in non-increasing order.
+	By construction, the slope of the curve attains the values 
+\begin{equation}
+	\frac{\sum_{i=0}^k p_{\pi(i)} - \sum_{i=0}^{k-1} p_{\pi(i)}}{\sum_{i=0}^k r_{\pi(i)} - \sum_{i=0}^{k-1} r_{\pi(i)}} = \frac{p_{\pi(k)}}{r_{\pi(k)}},\ \text{with } k \geq 1,
+\end{equation}
+throughout the interval $[0,1]$, which is a non-increasing sequence due to the definition of $\pi$.
 	Therefore, the Lorenz curve is concave.
@@
 therefore expressions for the Lorenz curve coordinates follow from summing up the Wigner components in decreasing order.
-\nick{As a result, every Strange state Lorenz curve in the unital fragment generally contains $n$ elbows.
-In the case of accidental degeneracies among Wigner components, some elbows my be straightened out.}
+\nick{As a result, every Strange state Lorenz curve in the unital fragment contains $n$ elbows.
+In the case of accidental degeneracies among Wigner components, some of these elbows may be straightened out.}
 Including the boundary points $(x_{-1}, L_{-1}) := (0,0)$ and $(x_{n}, L_{n}) := (1,1)$, we label these elbows as 
@@
 
-Let each qutrit have a Hamiltonian $H$ with energies $E_0, E_1, E_2$ and stabilizer eigenstates, and define $E_{\rm max} = \max\{E_0, E_1, E_2\}$ and $E_s$ as the eigenvalue of the Hamiltonian eigenstate whose Wigner distribution overlaps the negative component of $\rho_S(\epsilon)$ in the phase space.
+Let each qutrit have a Hamiltonian $H$ with energies $E_0, E_1, E_2$ and stabilizer eigenstates, and define $E_{\rm max} = \max\{E_0, E_1, E_2\}$ and \nick{$E_s$ as the eigenvalue of the Hamiltonian eigenstate whose Wigner distribution overlaps the negative component of $\rho_S(\epsilon)$ in the phase space.}
 Let $T =(k\beta)^{-1}$ be any finite temperature and assume that in the thermodynamic limit ($n,m \gg 1$), the protocol applied to the equilibrium state $\tau^{\otimes n} = (e^{-\beta H}/\Z)^{\otimes n}$ maps $\tau^{\otimes n} \longrightarrow \tau^{\prime \otimes m}$, where we express state $\tau'$ as $\tau' = e^{-\beta H'}/\Z'$ for some Hermitian $H'$.
@@
 
+\nick{Explain why this is not Clifford processing, ensure overlap with negativity is the one suggested}
 The equilibrium state at inverse temperature $\beta$ on a single qutrit is given by $\tau = e^{-\beta H} / \Z$.
@@
 This is unique, since the eigenstates form an orthonormal basis.
-\nick{Clifford processing?}
 

### 2021-05-27 magic_paper.tex
Edits on main part. Smoothing and polishing.

@@
 \label{sec:intro}
-
-\nick{re-write based on new relative majorisation approach}
 The past few years have seen rapid progress towards the goal of a fault-tolerant quantum computer~\cite{Nickerson_2014, Nikahd_2017, chao_2018, lin_pieceable_2020, Lin_2020, Bourassa_2021}.
@@
 
-In this work, we develop a framework to analyse magic state distillation protocols where explicit physical constraints are manifest.
-These physical constraints are encoded in the allowed fixed-point structure of the protocol, for example a minimal temperature attainable in the device, noise-biases or fixed-point structure associated with restricted gate-sets (see e.g.~\cite{Aliferis_2008, Stephens_2013, Li_2015, Babbush_2018, Tuckett_2019, Guillaud_2019, Fowler_2019}).
-The approach we take is most closely aligned with resource theories of magic, although it differs in two ways.
-Firstly, we obtain distillation upper bounds without the use of monotones, and secondly our distillation bounds are functions of the physical constraints, thus not directly comparable to global magic monotones.
-
+In this work, we develop a framework to analyse magic state distillation protocols where explicit physics of the system is incorporated.
+These distillation bounds are obtained by considering how a given magic state protocol would behave if it were instead applied to a \emph{stabilizer} state that is distinguished by the physics of the system -- for example an equilibrium state at a characteristic temperature, or the maximally mixed state.
+The magic distillation bounds can then be expressed in terms of this distinguished degrees of freedom (e.g.
+free energy changes in the case of temperature, or non-unitality in the case of the maximally mixed state).
+Such bounds are therefore of interest in assessing how physical features such as temperature, noise-biases or fixed-point structure associated with restricted gate-sets constrain distillation protocols, and so of relevance to existing work towards fault-tolerant quantum computing~\cite{Aliferis_2008, Stephens_2013, Li_2015, Babbush_2018, Tuckett_2019, Guillaud_2019, Fowler_2019}.
+
+The approach we take is most closely aligned with resource theories of magic, however it differs in a few ways.
+Firstly, we obtain distillation upper bounds without the use of monotones, and secondly our distillation bounds are hardware dependent.
 We approach this problem using tools from statistical mechanics and recent work from the overlap of thermodynamics and quantum information theory~\cite{cit:janzing, cit:horodecki2, Brandao_2015, Vinjanampathy_2016, Goold_2016, cit:lostaglio, cit:gour}.
 In particular, we shall view \emph{magic as a form of free energy}, relative to the set of stabilizer states.
-This perspective takes the convex set of stabilizer states as the set of ``equilibrium'' states, and magic corresponds to a form of non-equilibrium free energy that is strictly non-classical.
+From this perspective the convex set of stabilizer states behaves as the set of ``equilibrium'' states, and magic corresponds to a form of non-equilibrium free energy that is strictly non-classical.
 
@@
 We circumvent this obstacle by making use of a more fundamental tool in thermodynamics -- majorization theory~\cite{cit:marshall, Veinott_1971, Ruch_1976}.
-To our knowledge majorization of quasi-distributions has not been considered in quantum physics before, and therefore our analysis is of broader interest to the study of non-classicality in quantum systems.
-
-Our construction provides distillation bounds without relying on magic monotones.
-Instead of projecting the pre-order of magic states onto the real line (which is what a monotone involves) we instead cover the pre-order of states with a collection of simpler `fragment' pre-orders that admit analysis in terms of majorization.
-It is this choice of fragment that breaks the equivalence of all stabilizer states in the theory and can be used to consider adding physical constraints in the form of accessible protocols.
+To our knowledge majorization of quasi-distributions has not been considered in quantum physics before, and therefore our analysis is also of interest to the study of non-classicality in quantum systems.
 
@@
     \centering
-        \includegraphics[scale=0.4]{figs/protocol_diagram.pdf}
-    \caption{\textbf{Analysing magic protocols relative to a stabilizer reference state.} 
-	A magic protocol aims to turn $n$ copies of some magic state $\rho$ to $m$ copies of some other state $\rho'$.
-	Constraints on the efficiency of the protocol can be imposed by considering its action on a separate probe state $\tau$ which tranforms to $\tau'$ with free energy $F \rightarrow F'$.
-	A ``magic free energy'' $\phi \rightarrow \phi'$ connects the two state conversions under the protocol. \nick{FIX}
-    }
+        \includegraphics[scale=0.3]{figs/protocol_diagram.pdf}
+    \caption{\textbf{Magic distillation protocols \& stabilizer reference states.} 
+	A magic protocol (top figure) converts $n$ copies of some noisy magic state $\rho$ with noise parameter $\epsilon$ to $m$ copies of some less noisy state $\rho'$ with $\epsilon' < \epsilon$.
+The physics of the protocol can be analysed by considering how it would transform some distinguished reference stabilizer state $\tau^{\otimes n}$ (bottom figure).
+For the case where this reference state is a thermal state at some temperature $T$ our magic distillation bounds are functions of $T$, the noise parameters $\epsilon, \epsilon'$, and the free energy the protocol channel $\E$ injects in.
+In addition a quantity $\phi$ links the computational and physical aspects, and corresponds to the degree to which Wigner negativity in $\rho$ can be assigned a sharp energy via the system Hamiltonian.}
     \label{fig:sketch}
@@
 Then $L_{\p|\r}(x)$ is a concave function on $[0,1]$.
-\nick{
+\end{lemma}
+
 \begin{proof}
 	The Lorenz curve of $\p$ relative to $\r$ passes through the origin $(r_{\pi(0)}, p_{\pi(0)}) := (0,0)$ and the points $(\sum_{i=1}^k r_{\pi(i)}, \sum_{i=1}^k p_{\pi(i)})$ where $\pi$ is the permutation that puts $p_i/r_i$ in non-increasing order.
-	By construction, the slope of the curve attains the values 
-\begin{equation}
-	\frac{\sum_{i=0}^k p_{\pi(i)} - \sum_{i=0}^{k-1} p_{\pi(i)}}{\sum_{i=0}^k r_{\pi(i)} - \sum_{i=0}^{k-1} r_{\pi(i)}} = \frac{p_{\pi(k)}}{r_{\pi(k)}},\ \text{with } k \geq 1,
-\end{equation}
-throughout the interval $[0,1]$, which is a non-increasing sequence due to the definition of $\pi$.
-	Therefore, the Lorenz curve is concave.
+	The function is continuous, and the slope of the curve away from the elbows is well-defined and takes the value 
+\begin{equation}
+	\frac{\sum_{i=0}^k p_{\pi(i)} - \sum_{i=0}^{k-1} p_{\pi(i)}}{\sum_{i=0}^k r_{\pi(i)} - \sum_{i=0}^{k-1} r_{\pi(i)}} = \frac{p_{\pi(k)}}{r_{\pi(k)}},
+\end{equation}
+with $k=0,1,2, \dots$ labeling the line-segments of the Lorenz curve in increasing order.
+From the definition of the Lorenz curve, this implies the slope is piecewise constant, non-increasing on $[0,1]$ minus the elbow locations.
+Therefore, the Lorenz curve is a concave function on $[0,1]$.
+\ddd{[Not fully rigorous due to elbows...
+Here is an alternative proof:]}
 \end{proof}
-}
-\begin{proof}Let $L_{\p|\r}(x)$ attain its maximum at $x=x_\star$.
-Then from the definition, the function is continuous, monotone increasing on $[0,x_\star]$, and monotone decreasing on $[x_\star, 1]$.
-Consider $a,b \in [0,1]$ with $a <b$ and some probability $q \in [0,1]$.
-If $a$ and $b$ both lie in either the interval $[0,x_\star]$ or $[x_\star, 1]$ then concavity follows immediately.
-Otherwise, $a$ is in the first interval and $b$ in the second interval.
-If $w=qa + (1-q)b$ lies in the first interval then
-\begin{align}
-qL_{\p|\r}(a) + (1-q)L_{\p|\r}(b) &\le qL_{\p|\r}(a) + (1-q)L_{\p|\r}(x_\star)\nonumber\\
-& \le L_{\p|\r}(w)
-\end{align}
-\nick{second inequality isn't clear to me}
-from monotonicity on the first interval. Otherwise, $w$ lies in the second interval and
-\begin{align}
-qL_{\p|\r}(a) + (1-q)L_{\p|\r}(b) &\le qL_{\p|\r}(x_\star) + (1-q)L_{\p|\r}(b)\nonumber\\
-& \le L_{\p|\r}(w)
-\end{align}
-\nick{again second inequality isn't clear to me}
-which follows from monotonicity on the second interval. Therefore the Lorenz curve is concave on $[0,1]$.
+\begin{proof} Let $f_1(x)$ be equal to $L_{\p|\r}(x)$ on $[0, x_\star]$ and and $0$ otherwise.
+Also let $f_2(x)$ be equal to $L_{\p|\r}(x)$ on $[x_\star,1]$ and and $0$ otherwise.
+By inspection both $f_1$ and $f_2$ are concave functions, and $f_1(x) + f_2 (x) = L_{\p|\r}(x)$ for all $x\in [0,1]$.
+However the sum of two concave functions is also concave and so the result follows.
 \end{proof}
-\end{lemma}
 
@@
 therefore expressions for the Lorenz curve coordinates follow from summing up the Wigner components in decreasing order.
-\nick{As a result, every Strange state Lorenz curve in the unital fragment contains $n$ elbows.
-In the case of accidental degeneracies among Wigner components, some of these elbows may be straightened out.}
+As a result, every Strange state Lorenz curve in the unital fragment contains $n$ elbows. In the case of accidental degeneracies among Wigner components, some of these elbows may be straightened out.
 Including the boundary points $(x_{-1}, L_{-1}) := (0,0)$ and $(x_{n}, L_{n}) := (1,1)$, we label these elbows as 
@@
   \caption{Strange state Lorenz curve elbow coordinates in the unital fragment, with $0 \leq i \leq n$. 
-  \nick{Rows labelled as LHS express the coordinates $x_i$ and then $L_i$, while rows labelled as RHS, express the differences $x_i - x_{\lfloor n/2 \rfloor}$ and then $L_i - L_{\lfloor n/2 \rfloor}$}.
+  For the LHS cases, the $i$ in the first column labels the elbow coordinate $x_i$ and the second column gives $L_i=L(x_i)$.
+For RHS cases, the $i$ in the first column labels $x_i - x_{\lfloor n/2 \rfloor}$ and the second column gives $L_i - L_{\lfloor n/2 \rfloor}$.
   The coordinate expressions depend on the error $\epsilon$, the parity of the number of copies $n$ and the location of the elbow relative to the maximum (LHS or RHS).
@@
 \end{equation}
-\nick{We stress that $3v(\epsilon')e^{-\beta (F' - \phi')} > 1$ always, because $\rho_{\rm{S}}(\epsilon')$ is not a free state, so the initial slope of its Lorenz curve exceeds $1$.}
+We note that $3v(\epsilon')e^{-\beta (F' - \phi')} > 1$ always, as $\rho_{\rm{S}}(\epsilon')$ is not a free state, so the initial slope of its Lorenz curve exceeds $1$.
 Taking the natural logarithm on both sides and rearranging gives the bound

### 2021-05-28 magic_paper.tex
More smoothing of narrative. Deletion of too much explanation. Streamlined. Temp-bound data needs blending next.

@@
 
-Our analysis relies on the discrete Wigner representation of quantum states, in which all states and operations can be described on a discrete phase space~\cite{Ferrie_2008, Okay_2021}.
+Our analysis relies on the discrete Wigner representation of quantum systems, in which all states and operations can be described on a discrete phase space~\cite{Ferrie_2008, Okay_2021}.
 Crucially, we focus on magic states with negativity in their Wigner representation, which is known to be a necessary condition for universality in the state-injection model~\cite{cit:veitch, cit:mari, cit:gottesman, cit:knill, Campbell_2011}.
-Interestingly, taking a thermodynamic perspective in this context raises a problem, namely it is impossible to define entropies for quasi-distributions.
-We circumvent this obstacle by making use of a more fundamental tool in thermodynamics -- majorization theory~\cite{cit:marshall, Veinott_1971, Ruch_1976}.
+Interestingly, taking a statistical mechanical perspective in this context raises a problem, namely it is impossible to define entropies for quasi-distributions.
+We circumvent this obstacle by making use of a more fundamental tool in thermodynamics and information theory -- majorization theory~\cite{cit:marshall, Veinott_1971, Ruch_1976}.
 To our knowledge majorization of quasi-distributions has not been considered in quantum physics before, and therefore our analysis is also of interest to the study of non-classicality in quantum systems.
@@
 We provide explicit bounds for magic protocols that generate unital channels, as well as bounds that depend on the temperature and Hamiltonian of the system.
-We find that the thermodynamics in the presence of negativity is surprisingly non-trivial and displays a range of features that do not appear in classical statistical mechanics.
+We find that the thermodynamic ordering in the presence of negativity is non-trivial and displays a range of features that, unsurprisingly, do not appear in classical statistical mechanics.
 Finally, we discuss how our approach could be improved and how it can be exploited to construct explicit lower bounds on distillation that take into account physical structure.
@@
 
-A number of magic theories exist, with the central approach of viewing magic states as ``resource'' states with respect to a natural class of quantum operations that are considered free~\cite{Gour_2019}.
+A number of magic theories exist, with the central approach of viewing magic states as computational resource states with respect to a natural class of quantum operations that are considered free~\cite{Gour_2019}.
 One very natural class of free operations are those obtained from Clifford operations, measurements and the ability to discard quantum systems.
@@
 
-One of the most prominent magic monotones is the \emph{mana} of a state~\cite{cit:veitch2}, defined as
+One prominent magic monotone is the \emph{mana} of a state~\cite{cit:veitch2}, defined as
 \begin{equation}
@@
 
-Mana is an additive\footnote{It satisfies the condition $\mana{\rho_1 \otimes \rho_2} = \mana{\rho_1} + \mana{\rho_2}$ which is practical in distillation settings.} magic monotone, so it provides an analytical, necessary condition for many-copy magic state interconvertibility.
-
-A range of monotones have been developed in the literature~\cite{cit:howard, Wang_2020, Seddon_2021} and each provides a means to upper bound distillation rates within a particular theory of magic.
+Mana is an additive\footnote{It satisfies the condition $\mana{\rho_1 \otimes \rho_2} = \mana{\rho_1} + \mana{\rho_2}$.} magic monotone, and the fact that it is non-increasing under free operations provides a constraint on magic state interconvertibility.
+
 In this work we shall develop bounds that apply to essentially any reasonable magic theory.
-The central idea is to apply majorization theory to the quasi-probability distributions of magic states.
-In the next section, we explain how these majorization constraints relate to the free operations allowed in a theory of magic.
+The central idea is to apply majorization theory to the quasi-probability distributions that arise for magic states.
+We begin in the next section by explaining how majorization relates to the free operations in a theory of magic.
 
@@
 However, it is known that all positively represented states used in Clifford circuits admit an efficient classical description, so it is natural to focus on the negatively represented magic states.
-The free states in any magic theory must therefore lie in the set
+The free states in any magic theory are assumed to lie in the set
 \begin{equation}
@@
 The remaining component that defines any magic theory is the set of allowed quantum operations, i.e.
-the ones that are considered free.
-The assumption we require on free operations is simply that they send any free state to another free state, meaning that a resource state cannot be created freely, a common assumption among all magic theories.
-
-We can view the Wigner representation $W_{\E}( \y | \x)$ of a quantum channel $\E$ as a transition matrix mapping points $\x \rightarrow \y$, which is consistent with the representation of quantum states, as
+the ones that are considered free within the theory.
+The most basic assumption we require on free operations is that they send any free state to another free state, meaning that a resource state cannot be created freely, a common assumption among all magic theories.
+
+Any magic state protocol will correspond to a quantum channel $\E$, and admits a Wigner representation $W_{\E}( \y | \x)$ that can be viewed as a transition matrix mapping phase space points $\x \rightarrow \y$.
+The representation obeys the relation
 \begin{equation}
@@
 for any $\E$ and $\rho$.
-Now if $\E$ sends all positively represented quantum state to other positively represented quantum states then it can be shown~\cite{Wang_2019} that $W_{\E}(\y |\x)$ must form a stochastic matrix.
+Now if any magic protocol will send free states to free states, and so $\E$ sends all positively represented quantum state to other positively represented quantum states.
+In such cases, it can be shown~\cite{Wang_2019} that $W_{\E}(\y |\x)$ must form a stochastic matrix.
 In particular, all Clifford operations correspond to stochastic matrices in this Wigner representation.
-However, it is important to note that not all stochastic maps on the phase space correspond to valid quantum operations.
-In particular, the stochastic maps must respect the symplectic structure of the phase space, which is an additional non-trivial constraint.
-
-In what follows we shall therefore assume that we have a magic theory $\R = (\F, \O)$ in which the free states $\F$ form a closed set with each state represented by a non-negative Wigner function, while the free operations $\O$ are represented by stochastic maps acting on the discrete phase space.
-
-\section{Magic distillation bounds from majorization theory}
+
+However, it is important to note that this is not one-to-one.
+Not all stochastic maps on the phase space correspond to valid quantum operations.
+The reason is that the stochastic maps must also respect the symplectic structure of the phase space, which is an additional non-trivial constraint.
+
+In what follows we shall assume that we have a magic theory $\R = (\F, \O)$ in which the free states $\F$ form a closed set and are represented by a non-negative Wigner functions, while the free operations $\O$ are stochastic maps in the Wigner representation.
+To aid our analysis of magic in this phase space setting we shall make use of majorization theory, which we describe in the next section.
+
+\subsection{Quantifying disorder without entropies}
+\label{sec:major}
+
+Majorisation is a collection of powerful tools that has recently found many applications in quantum information theory~\cite{Nielsen_1999, cit:cwiklinski, cit:lostaglio2, cit:gour, cit:gour2, Horodecki_2003, Vallejos_2021}.
+It describes the disorder of distributions that undergo stochastic transformations.
+In its simplest form it defines a pre-order on probability distributions.
+Given two distributions $\p= (p_1, \dots, p_n)$ and $\q = (q_1, \dots, q_n)$ over $n$ outcomes, we say that $\p$ majorises $\q$, denoted $\p \succ \q$, if there exists a bistochastic map $A = (A_{ij})$ such that $A\p = \q$, where bistochastic means that $A_{ij} \geq 0$ and $\sum_i A_{ij} = \sum_j A_{ij} = 1$.
+A well-known result~\cite{cit:marshall} tells us that the condition $ \p \succ \q$ over probability distributions is equivalent to $n-1$ inequalities, which can be checked efficiently.
+
+There is a natural generalisation, which is called $\bmd$--majorization~\cite{Veinott_1971}, or in the context of thermodynamics, thermo-majorization~\cite{cit:horodecki2013}.
+For a fixed probability distribution $\r = (r_1, \dots, r_n)$ with positive components, we define majorization relative to $\r$ as $\p \succ_{\r} \q$, if and only if there exists a stochastic map $A$ such that $A\r = \r$ and $A \p = \q$.
+In order words, this majorization pre-order coincides with the image of $\p$ under stochastic maps that have $\r$ as a fixed point.
+It is readily checked that the original majorization condition between probability distributions corresponds to the case $\r = (1/n, \dots, 1/n)$.
+The pre-order that results from relative majorization is also easily checked and again corresponds to checking a small number of inequalities.
+
+In fact, we can further generalise to \emph{relative majorization}~\cite{Ruch_1976, ruch_mixing_1978, Renes_2016, Buscemi_2017}, defined as an ordering between pairs of vectors so that 
+\begin{equation}
+	(\p,\r) \succ (\q, \r')
+\end{equation}
+iff there is a stochastic map $A$ such that $A\r = \r'$ and $A\p = \q$. We retrieve $\bmd$--majorization when $\r = \r'$.
+
+It turns out that relative majorization is equally applicable to \emph{quasi-probability} distributions, and therefore can be applied to the Wigner representation of magic across fragments.
+We go into more detail on this in the next section.
+
+\subsection{Quasi-probability majorization and non-monotonic Lorenz curves}
+\label{sec:lc}
+
+Our analysis applies majorization to magic states at the level of the associated Wigner distributions.
+However, these are in general quasi-probability distributions and so it is important to check how majorization is computed for these cases and what differences quasi-distributions bring over genuine probability distributions.
+
+Central to the analysis is the notion of a Lorenz curve of a vector $\w \in \mathbb{R}^n$ relative to some other vector $\r \in \mathbb{R}^n$.
+Given a vector $\w$ we define $\w^\downarrow$ to be the re-arrangement of the components of $\w$ into decreasing order.
+Given two $n$--component vectors $\w$ and $\r$, we first define $\widetilde{\w}$, where $\widetilde{w}_i \coloneqq w_i/r_i$, as the vector of component-wise ratios between $\w$ and $\r$.
+We can now define the \emph{Lorenz curve} of $\w$ relative to $\r$, denoted $L_{\w|\r}(x)$, as the piece-wise linear function that passes through $(0,0)$ and the $n$ points
+\begin{equation}
+\label{eq:lc}
+        (x_k,L_{\w|\r}(x_k)) =\left( \frac{1}{R}\sum_{i=1}^k r_{\pi(i)}, \sum_{i=1}^k w_{\pi(i)} \right),
+\end{equation}
+where $R\coloneqq \sum_{i=1}^n r_i$ and $\pi$ is the permutation on $n$ objects mapping $\widetilde{\w}$ to $\widetilde{\w}^{\downarrow}$.
+The form of this requires that $\r$ has no zero components, which we shall assume without loss of generality as in any physical situation the rank of a quantum state is not an operationally meaningful quantity.
+
+In the usual case where $\w$ and $\r$ are both probability distributions the Lorenz curve is defined on the interval $[0,1]$, and rises monotonically until it reaches the value $1$ at $x=1$.
+The value $L_{\w|\r}(x) = 1$ is a global maximum.
+Moreover, if $\w, \w', \r, \r'$ are all valid probability distributions with neither of $\r,\r'$ having negative components then it can be shown~\cite{ruch_mixing_1978} that
+\begin{equation}
+(\w, \r) \succ (\w', \r') \mbox{ if and only if } L_{\w |\r}(x) \ge L_{\w' |\r'}(x),
+\end{equation}
+for all $x \in [0,1]$.
+This provides a simple way of computing whether relative majorization holds between pairs of probability distributions.
+
+However, if $\w$ is a \emph{quasi-probability} distribution with negative values, and $\r$ a regular probability distribution things are different.
+Now the Lorenz curve is no longer monotone increasing, but is a concave function that breaks through the $L_{\w|\r}(x) = 1$ barrier at an interior point and attains some non-trivial maximum $L_\star$ above the value $1$, before decreasing monotonically to $L_{\w|\r}(x)= 1$ at the end-point $x=1$.
+See Figure \ref{fig:lcs} for examples of non-monotonic Lorenz curves for quasi-distributions.
+Within quantum theory, the breaking of this barrier is associated with the degree of non-classicality.
+Since majorization provides a measure of order/disorder this is consistent with the intuition that negativity, for example within the context of quantum optics or quantum computing, can provide a greater form of order than is possible within classical theory.
+
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.35]{figs/lc_strange.pdf}
+    \caption{\textbf{A `heretical' family of Lorenz curves.} Traditionally, Lorenz curves for distributions are monotone increasing cumulant functions that reach a maximum value of $1$.
+In contrast, Lorenz curves for magic states break through the value of $L(x)=1$ due to the presence of negativity in the associated quasi-probability distributions.
+The above family of curves correspond to multiple copies of noisy Strange states $\rho\coloneqq\rho_{\rm{S}}(\epsilon)^{\otimes n}$ (\cref{eq:noisysn}) for $n=2,4,6$ within a particular stabilizer fragment ($\sigma = \id/3$).
+Solid lines represent pure Strange states, while dashed lines represent $\epsilon$-noisy Strange states with depolarising noise $\epsilon = 0.1$.
+    }
+    \label{fig:lcs}
+\end{figure}
+
+However, relative majorization is usually considered for probability distributions, so we need to verify that the same Lorenz curve conditions apply to quasi-probability distributions before proceeding with our analysis.
+This can be done from first principles, but a simpler way is see that this holds is to reduce to the problem of genuine distributions by first `masking' the negativity in the quasi-probability distribution $\w$ using the reference distribution $\r$ and then applying the conditions for relative majorization.
+This negativity masking then gives the following result.
+
+\begin{lemma} Let $\w \in \mathbb{R}^n,\w'\in \mathbb{R}^m$ be quasi-distributions, and let $\r \in \mathbb{R}^n, \r' \in \mathbb{R}^m$ be probability distributions with non-zero components.
+Then $(\w, \r) \succ (\w', \r')$ if and only if $L_{\w|\r}(x) \ge L_{\w |\r}(x)$ for all $x \in [0,1]$.
+\end{lemma}
+
+ \begin{proof}
+Since the components of $\r$ are strictly positive, there always exists an $\epsilon >0$ such that $\w_\epsilon \coloneqq \epsilon \w + (1-\epsilon) \r$ is a genuine probability distribution.
+A similar result holds for $\w'$ and $\r'$ and we choose $\epsilon$ sufficiently small so that both $\w_\epsilon$ and $\w_\epsilon'$ are probability distributions.
+We now have that $(\w , \r) \succ (\w', \r')$ if and only if $(\w_\epsilon , \r) \succ (\w_\epsilon', \r')$.
+This equivalence holds because there exists a stochastic map $A$ such that $A \w = \w'$ and $A \r = \r'$ if and only if
+\begin{equation}
+A[\epsilon \w + (1-\epsilon) \r] = \epsilon \w' + (1-\epsilon) \r'\mbox{ and } A\r = \r'.
+\end{equation}
+In terms of a Lorenz curve condition we have that $(\w_\epsilon , \r) \succ (\w_\epsilon', \r')$ if and only if $L_{\w_\epsilon |\r} (x) \ge L_{\w'_\epsilon |\r'} (x)$ for all $x \in [0,1]$. 
+However, as we show in the Appendices (\cref{lemma:Lorenz_linearity}), the Lorenz curve for any quasi-probability distribution obeys the relation
+\begin{equation}
+L_{a \w + b \r | \r} (x) = a L_{\w|\r} (x) + bx,
+\end{equation}
+for any $a >0$ and $b \in \mathbb{R}$. This relation implies that
+\begin{align}
+L_{\w_\epsilon |\r} (x) &\ge L_{\w'_\epsilon |\r'} (x) \nonumber \\ 
+&\mbox{ if and only if }& \nonumber \\
+\epsilon L_{\w |\r} (x) + (1-\epsilon) x &\ge \epsilon L_{\w' |\r'} (x) + (1-\epsilon) x.
+\end{align}
+Finally, the $(1-\epsilon)x$ terms cancel on both sides and we get the required relative majorization conditions that $(\w, \r) \succ (\w', \r')$ if and only if $L_{\w | \r} (x) \ge L_{\w' | \r'}(x)$ for all $x \in [0,1]$, as required.
+\end{proof}
+
+With all the necessary theory in place, we now turn to magic distillation protocols.
+
+\newpage
+\section{Magic distillation bounds from majorization}
 \label{sec:frag}
 
-\nick{repeats intro}
-We wish to consider how physical constraints that may be hardware specific, affect magic distillation rates.
+We can now consider how physical constraints that may be hardware specific, affect magic distillation rates.
 These are not a priori encoded in the formulation of the magic theory, and constitute additional physical conditions on top of the underlying resource-theoretic accounting.
@@
 
-Our formulation will not consider model-specific limitations, but will still inject broad physical constraints.
-We proceed by considering fixed-point, or ``equilibrium'', restrictions on the actual operations that are accessible to us.
-While such restrictions could be viewed as the existence of some non-trivial thermodynamic constraint, they could equally be viewed as encoding a high noise-bias or difficulty in realising a particular quantum gate.
-We can therefore define the following sub-theory of any magic theory $\R$.
+ In Section \ref{sec:stab} we shall focus on the energetic costs of a protocol, that are defined due to the specific Hamiltonian that the system possesses.
+However, before that, in this section we encode physical constraints at a more abstract level in terms of the fixed-point structure of  the actual operations that are accessible to us.
+We show that any magic theory can always be decomposed in terms of `sub-theories' with a particular fixed-point structure.
+This section therefore exploits $\mathbf{d}$--majorization, while in Section \ref{sec:stab} we drop the requirement of fixed-points and instead use the full relative majorization relation.
+
+ We begin by defining the following sub-theory of any magic theory $\R$.
 \begin{definition}\label{def:sigmafrag}
@@
     Let $\R = (\F, \O)$ be a theory of magic.
-Then a transformation $\rho \longrightarrow \tau$ is possible in $\R$ if and only if the transformation $\rho \longrightarrow \tau$ is possible in at least one $\sigma$--fragment of $\R$.
+Then a transformation $\rho \rightarrow \tau$ is possible in $\R$ if and only if the transformation $\rho \rightarrow \tau$ is possible in at least one $\sigma$--fragment of $\R$.
 \end{theorem}
+The proof of this is straightforward.
 \begin{proof}
-	The proof is straightforward.
    Suppose the interconversion is possible in a $\sigma$--fragment via some $\E \in \O_\sigma$.
@@
 \end{figure}
-
-\nick{re-write based on new relative majorisation approach}
 It is now possible to consider magic distillation rates within $\sigma$--fragments and then see how the bounds on the distillation rates depend on the choice of the fragment we work within.
-Therefore, this route can potentially shed light on how the physics of a protocol constrain distillation rates above and beyond global constraints from the parent resource theory.
-For example, how does temperature affect distillation bounds?
-Do isotropic maps have better bounds, or does bias towards some pure stabilizer state provide more freedom?
-
-By introducing this additional structure to a magic theory, we allow for deeper analysis than would be possible at the level of the full parent theory.
-In particular, the interconversion structure in each fragment can be analysed using tools from single-shot thermodynamics and majorization theory as we discuss in the next section.
-
-\subsection{Quantifying disorder without entropies}
-\label{sec:major}
-
-We can now show that each magic fragment admits constraints that do not take the form of state monotones.
-
-The question is now whether the sub-theories can be analysed to provide additional insights into magic distillation protocols.
-An answer can be provided by working in the Wigner representation of a given $\sigma$--fragment.
-The problem of magic state distillation then becomes that of processing negativity under stochastic maps $W_{\E}( \y |\x)$ that leave a particular quasi-distribution $W_\sigma(\x)$ invariant.
-However, $\sigma \in \F$ is positively represented, so the sub-theory has an invariant classical probability distribution as a fixed point.
-This structure allows us to make use of a range of classical tools, and in particular majorization theory.
-
-Majorisation is a collection of powerful tools that has recently found many applications in quantum information theory~\cite{Nielsen_1999, cit:cwiklinski, cit:lostaglio2, cit:gour, cit:gour2, Horodecki_2003, Vallejos_2021}.
-It describes the disorder of distributions that undergo stochastic transformations.
-In its simplest form it defines a pre-order on probability distributions.
-Given two distributions $\p= (p_1, \dots, p_n)$ and $\q = (q_1, \dots, q_n)$ over $n$ outcomes, we say that $\p$ majorises $\q$, denoted $\p \succ \q$, if there exists a bistochastic map $A = (A_{ij})$ such that $A\p = \q$, where bistochastic means that $A_{ij} \geq 0$ and $\sum_i A_{ij} = \sum_j A_{ij} = 1$.
-A well-known result~\cite{cit:marshall} tells us that the condition $ \p \succ \q$ over probability distributions is equivalent to $n-1$ inequalities, which can be checked efficiently.
-
-There is a natural generalisation, which is called $\bmd$--majorization~\cite{Veinott_1971}, or in the context of thermodynamics, thermo-majorization~\cite{cit:horodecki2013}.
-For a fixed probability distribution $\r = (r_1, \dots, r_n)$ with positive components, we define majorization relative to $\r$ as $\p \succ_{\r} \q$, if and only if there exists a stochastic map $A$ such that $A\r = \r$ and $A \p = \q$.
-In order words, this majorization pre-order coincides with the image of $\p$ under stochastic maps that have $\r$ as a fixed point.
-It is readily checked that the original majorization condition between probability distributions corresponds to the case $\r = (1/n, \dots, 1/n)$.
-The pre-order that results from relative majorization is also easily checked and again corresponds to checking a small number of inequalities.
-
-We can further generalise this to \emph{relative majorization}~\cite{Ruch_1976, ruch_mixing_1978, Renes_2016, Buscemi_2017}, defined as an ordering between pairs of vectors so that 
-\begin{equation}
-	(\p,\r) \succ (\q, \r')
-\end{equation}
-iff there is a stochastic map $A$ such that $A\r = \r'$ and $A\p = \q$. We retrieve $\bmd$--majorization when $\r = \r'$.
-
-It turns out that relative majorization is equally applicable to \emph{quasi-probability} distributions, and therefore can be applied to the Wigner representation of magic across fragments.
-We go into more detail on this in the next section.
-
-\subsection{Quasi-probability majorization and non-monotonic Lorenz curves}
-\label{sec:lc}
-
-We wish to apply majorization to describing magic in different fragments at the level of the associated Wigner distributions.
-However, these are in general quasi-probability distributions and so it is important to detail how majorization is computed for these cases and what differences quasi-distributions bring over genuine probability distributions.
-
-Central to the analysis is the notion of a Lorenz curve of a vector $\w \in \mathbb{R}^n$ relative to some other vector $\r \in \mathbb{R}^n$.
-Given a vector $\w$ we define $\w^\downarrow$ to be the re-arrangement of the components of $\w$ into decreasing order.
-Given two $n$--component vectors $\w$ and $\r$, we first define $\widetilde{\w}$, where $\widetilde{w}_i \coloneqq w_i/r_i$, as the vector of component-wise ratios between $\w$ and $\r$.
-We can now define the \emph{Lorenz curve} of $\w$ relative to $\r$, denoted $L_{\w|\r}(x)$, as the piece-wise linear function that passes through $(0,0)$ and the $n$ points
-\begin{equation}
-\label{eq:lc}
-        (x_k,L_{\w|\r}(x_k)) =\left( \frac{1}{R}\sum_{i=1}^k r_{\pi(i)}, \sum_{i=1}^k w_{\pi(i)} \right),
-\end{equation}
-where $R\coloneqq \sum_{i=1}^n r_i$ and $\pi$ is the permutation on $n$ objects mapping $\widetilde{\w}$ to $\widetilde{\w}^{\downarrow}$.
-The form of this requires that $\r$ has no zero components, which we shall assume without loss of generality as in any physical situation the rank of a quantum state is not an operationally meaningful quantity.
-We also observe that the curve contains non-differentiable points, called \emph{elbows} at locations where $\widetilde{\bmw}$ changes value.
-
-If $\w$ and $\r$ are both probability distributions then the Lorenz curve is defined on the interval $[0,1]$, and rises monotonically until it reaches the value $1$ at $x=1$.
-The value $L_{\w|\r}(x) = 1$ is a global maximum, attained at the end-point $x=1$.
-Moreover, if $\w, \w', \r, \r'$ are all valid probability distributions with neither of $\r,\r'$ having negative components then it has been shown in~\cite{ruch_mixing_1978} that
-\begin{equation}
-(\w, \r) \succ (\w', \r') \mbox{ if and only if } L_{\w |\r}(x) \ge L_{\w' |\r'}(x).
-\end{equation}
-This provides a simple way of computing whether relative majorization holds between pairs of probability distributions.
-
-However, if $\w$ is a \emph{quasi-probability} distribution with negative values, and $\r$ a regular probability distribution things are different.
-Now the Lorenz curve is no longer monotone increasing, but is a concave function that breaks through the $L_{\w|\r}(x) = 1$ barrier at an interior point and attains some non-trivial maximum $L_\star$ above the value $1$, before decreasing monotonically to $L_{\w|\r}(x)= 1$ at the end-point $x=1$.
-See Figure \ref{fig:lcs} for examples of non-monotonic Lorenz curves for quasi-distributions.
-Within quantum theory, the breaking of this barrier is associated with the degree of non-classicality.
-Since majorization provides a measure of order/disorder this is consistent with the intuition that negativity, for example within the context of entanglement theory or quantum computing, can provide a greater form of order than is possible within classical theory.
-
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.35]{figs/lc_strange.pdf}
-    \caption{\textbf{A `heretical' family of Lorenz curves.} Traditionally, Lorenz curves for distributions are monotone increasing cumulant functions that reach a maximum value of $1$.
-In contrast, Lorenz curves for magic states break through the value of $L(x)=1$ due to the presence of negativity in the associated quasi-probability distributions.
-The above family of curves correspond to multiple copies of noisy Strange states $\rho\coloneqq\rho_{\rm{S}}(\epsilon)^{\otimes n}$ (\cref{eq:noisysn}) for $n=2,4,6$ within a particular stabilizer fragment ($\sigma = \id/3$).
-Solid lines represent pure Strange states, while dashed lines represent $\epsilon$-noisy Strange states with depolarising noise $\epsilon = 0.1$.
-    }
-    \label{fig:lcs}
-\end{figure}
-
-However, relative majorization is usually considered for probability distributions, so we need to verify that the same Lorenz curve conditions apply to quasi-probability distributions before proceeding with our analysis.
-This can be done from first principles, but a simpler way is see that this holds is to reduce to the problem of genuine distributions by first `masking' the negativity in the quasi-probability distribution $\w$ using the reference distribution $\r$ and then applying the conditions for relative majorization.
-
-More precisely, since the components of $\r$ are strictly positive, there always exists an $\epsilon >0$ such that $\w_\epsilon \coloneqq \epsilon \w + (1-\epsilon) \r$ is a genuine probability distribution.
-We can see that $(\w , \r) \succ (\w', \r')$ if and only if $(\w_\epsilon , \r) \succ (\w_\epsilon', \r')$, where we choose $\epsilon$ so that both $\w_\epsilon$ and $\w_\epsilon'$ are probability distributions.
-This equivalence holds because there exists a stochastic map $A$ such that $A \w = \w'$ and $A \r = \r'$ if and only if
-\begin{equation}
-A[\epsilon \w + (1-\epsilon) \r] = \epsilon \w' + (1-\epsilon) \r'\mbox{ and } A\r = \r'.
-\end{equation}
-As mentioned, relative majorization between pairs of distributions occurs if and only if the associated Lorenz curves never cross.
-Therefore, we can express this condition in terms of the Lorenz curves of the quasi-probability distributions $\w$ and $\w'$ relative to $\r$ and $\r'$ respectively.
-
-As shown in~\cref{lemma:Lorenz_linearity}, the Lorenz curve for any quasi-probability distribution obeys the following linearity condition
-\begin{equation}
-L_{a \w + b \r | \r} (x) = a L_{\w|\r} (x) + bx,
-\end{equation}
-for any $a >0$ and $b \in \mathbb{R}$. We now have that
-\begin{equation}
-(\w, \r) \succ (\w', \r') \mbox{ if and only if } (\w_\epsilon , \r) \succ (\w_\epsilon', \r'),
-\end{equation}
-and also $(\w_\epsilon , \r) \succ (\w_\epsilon', \r')$ if and only if $L_{\w_\epsilon |\r} (x) \ge L_{\w'_\epsilon |\r'} (x)$ for all $x$.
-However, using the above linearity property of the Lorenz curves we have that
-\begin{align}
-L_{\w_\epsilon |\r} (x) &\ge L_{\w'_\epsilon |\r'} (x) \nonumber \\ 
-&\mbox{ if and only if }& \nonumber \\
-\epsilon L_{\w |\r} (x) + (1-\epsilon) x &\ge \epsilon L_{\w' |\r'} (x) + (1-\epsilon) x.
-\end{align}
-The $(1-\epsilon)$ terms cancel on both sides and we get the required relative majorization conditions for the quasi-distributions in terms of their Lorenz curves.
-
-We therefore have that $(\w, \r) \succ (\w', \r')$ if and only if $L_{\w | \r} (x) \ge L_{\w' | \r'}(x)$ for all $x \in [0,1]$ equally applies for the case of $\w,\w'$ being quasi-distributions.
-
-In the next section we discuss the application of majorization to Wigner representations of magic, where the quasi-distribution $W_\rho(x)$ of a magic state can be analysed relative to any Wigner positive free state $W_\sigma(x)$.
-To our knowledge, the application of majorization to quasi-distributions in  physics has not been considered previously.
-The caveat here is that relative majorization ranges over stochastic maps that obey a transformation ($A\r = \r'$), while in the case of the Wigner representation there is a stronger restriction that the symplectic structure of the phase space is respected.
-Therefore, any majorization constraint can provide necessary, but not sufficient conditions on magic state interconversions.
-This observation raises a question that to our knowledge has not been previously considered in the classical statistical mechanics literature: what are the conditions for symplectic majorization of classical statistical mechanics?
-We shall return to this question later on when we discuss how our approach could be used to construct concrete lower-bounds on distillation rates in~\cref{sec:lower_bounds}.
 
@@
 \label{sec:major_frag}
-
-Having described how majorization relative to a fiducial distribution can be computed, we now turn to its application within a particular fragment of a magic theory $\R= (\F, \O)$.
 
@@
 
-\subsection{Magic bounds for unital protocols}
+\subsection{Magic distillation bounds for unital protocols}
 \label{sec:unital}
@@
     \centering
-    \includegraphics[scale=0.45]{figs/distill_bounds.pdf}
+    \includegraphics[scale=0.35]{figs/distill_bounds.pdf}
     \caption{\textbf{Distillation bounds in the unital fragment.} Distillation bounds obtained by the first elbow majorisation constraint $R$, mana $\M$ and max--thauma $\theta_{\rm{max}}$ are plotted for $\epsilon' = 0$, up to error $\epsilon = 3/7$.
@@
 
-In the next section we provide relative majorization bounds in arbitrary stabilizer fragments, and in particular we shall parameterize these bounds from a thermodynamic perspective.
-Specifically, we can interpret the stabilizer state $\sigma$, which defines the fragment, as a thermodynamic equilibrium state at some effective temperature and with some effective Hamiltonian.
+In the next section we leave fragments behind, and instead use the full structure of relative majorization to obtain bounds that incorporate energetic aspects of a magic state protocol.
 
 \newpage
-\section{Free energy dependent bounds for magic state distillation protocols}
+\section{Temperature-dependent bounds for magic state distillation protocols}
 \label{sec:stab}
@@
 
-\subsection{Free energy measures and sub-linear correlations in the thermodynamic limit}
-To simplify our analysis we will make the following assumption.
+\subsection{Free energy and sub-linear correlations in the thermodynamic limit}
+To simplify our analysis we will make the following physical assumption.
 We assume that in the asymptotic/thermodynamic limit $n,m \rightarrow \infty$ that correlations generated between subsystems are negligible.
 This implies that $d\mu(x)$ is peaked on a particular state $\tau'$, and so $\E(\tau) = \tau^{\prime \otimes m}$.
-Physically, this is a natural scenario -- for example, in the context of traditional thermodynamics, it states that the output system is well-described by intrinsic variables that are encoded in $\tau'$.
-Here, this assumption allows us to associate a free energy per qudit of the output state, which would be more complex if correlations are present.
+Physically, this is a natural scenario -- for example, in the context of traditional thermodynamics, it states that the output system is well-described by intrinsic variables that are encoded in $\tau'$, and correlations are sub-linear in $m$.
+This assumption allows us to associate a free energy per qudit of the output state, which would be more complex if non-trivial correlations were present.
 
@@
 Since the protocol does not, on its own, generate magic the output state $\tau'$ is also a stabilizer state, provided that $\tau$ is as well.
-This is generally a non-equilibrium state for the system.
+This is generally a \emph{non-equilibrium} state for the system.
 However, the distillation bounds that we derive take a particularly simple form if we associate a Hamiltonian $H'$ to the output state by considering the change $H \rightarrow H'$ such that equilibrium is restored at the reference temperature $T$.
@@
 
-\subsection{Free energy dependent bounds on magic state distillation protocols}
+\subsection{Temperature-dependent distillation bounds}
 The preceding discussion gives a means to specify energetic details of a protocol through how much it would disturb some reference equilibrium state.
@@
 \end{align}
-and $\x_\star = \arg\!\min W_\tau(\x)$. The primed variables are defined similarly for the output system.
+and $W_\tau(\x)$ attains a minimum at $x=x_\star$. The primed variables are defined similarly for the output system.
 \end{theorem}
@@
 The coefficients $\alpha_k$ may be negative for some $k$, when the Hamiltonian eigen-decomposes into non-stabilizer states, but the quantity $\phi$ is always well-defined, since the function $\zeta$ is a positive multiple of the stabilizer Wigner component $W_\tau(0,0)$, as seen in the proof of the theorem.
+The quantity $\phi$ would diverge if the state $\tau$ acquired zero Wigner components, which only occurs if $\tau$ is on the boundary of the set of Wigner-positive states.
+
 In the case that the system's Hamiltonian $H$ has an eigenbasis consisting of stabilizer states then we show in Appendix \ref{sharp-phi} that $\phi$ takes on a sharp, temperature-independent energy value $\phi \in \{E_0,E_1,E_2\}$.
@@
 Finally, it would be of interest to consider the possibility of applying these techniques to other scenarios in which one wishes to distinguish classical from non-classical behaviour based on quasi-probability representations~\cite{Ferrie_2008, barnett_1997}
+\section{Acknowledgements}
+We thank Earl Campbell for insightful discussions and comments.
+NK is supported by the EPSRC Centre for Doctoral Training in Controlled Quantum Dynamics.
+DJ is supported by the Royal Society and a University Academic Fellowship.
 
@@
 
-We now show that the Lorenz curve is concave in the context of quasi-distributions.
+We now verify that the Lorenz curve is concave in the context of quasi-distributions.
 \begin{lemma}\label{L-concave} Let $\p$ be a quasi-probability distribution and let $\r$ be a probability distribution with strictly non-zero components.
@@
 \end{lemma}
-
-\begin{proof}
-	The Lorenz curve of $\p$ relative to $\r$ passes through the origin $(r_{\pi(0)}, p_{\pi(0)}) := (0,0)$ and the points $(\sum_{i=1}^k r_{\pi(i)}, \sum_{i=1}^k p_{\pi(i)})$ where $\pi$ is the permutation that puts $p_i/r_i$ in non-increasing order.
-	The function is continuous, and the slope of the curve away from the elbows is well-defined and takes the value 
-\begin{equation}
-	\frac{\sum_{i=0}^k p_{\pi(i)} - \sum_{i=0}^{k-1} p_{\pi(i)}}{\sum_{i=0}^k r_{\pi(i)} - \sum_{i=0}^{k-1} r_{\pi(i)}} = \frac{p_{\pi(k)}}{r_{\pi(k)}},
-\end{equation}
-with $k=0,1,2, \dots$ labeling the line-segments of the Lorenz curve in increasing order.
-From the definition of the Lorenz curve, this implies the slope is piecewise constant, non-increasing on $[0,1]$ minus the elbow locations.
-Therefore, the Lorenz curve is a concave function on $[0,1]$.
-\ddd{[Not fully rigorous due to elbows...
-Here is an alternative proof:]}
-\end{proof}
 \begin{proof} Let $f_1(x)$ be equal to $L_{\p|\r}(x)$ on $[0, x_\star]$ and and $0$ otherwise.

### 2021-05-28 magic_paper.tex
typos and punctuation

--- 2021-05-27 magic_paper.tex
@@
 \end{proof}
-\begin{proof} Let $f_1(x)$ be equal to $L_{\p|\r}(x)$ on $[0, x_\star]$ and and $0$ otherwise.
-Also let $f_2(x)$ be equal to $L_{\p|\r}(x)$ on $[x_\star,1]$ and and $0$ otherwise.
-By inspection both $f_1$ and $f_2$ are concave functions, and $f_1(x) + f_2 (x) = L_{\p|\r}(x)$ for all $x\in [0,1]$.
-However the sum of two concave functions is also concave and so the result follows.
+\begin{proof} Let $f_1(x)$ be equal to $L_{\p|\r}(x)$ on $[0, x_\star]$ and $0$ otherwise.
+Also let $f_2(x)$ be equal to $L_{\p|\r}(x)$ on $[x_\star,1]$ and $0$ otherwise.
+By inspection, both $f_1$ and $f_2$ are concave functions, and $f_1(x) + f_2 (x) = L_{\p|\r}(x)$ for all $x\in [0,1]$.
+However, the sum of two concave functions is also concave and so the result follows.
 \end{proof}

### 2021-05-28 magic_paper.tex
punctuation and typos

--- 2021-05-28 magic_paper.tex
@@
 \begin{document}
-% Labels and Refs (consistency, thm vs lem vs prop)
+% Labels and Refs (consistency, cref vs ref, thm vs lem vs prop, ??)
 % Figs check(fig.0, move to app, consistency)
 
-% Notation consistency (R is rate not bound, ket vs |> etc, \ln{} -> \ln ,??, italics)
+% Notation consistency (R is rate not bound, \ln{} -> \ln, italics)
 % UK vs US english
@@
 In this work, we develop a framework to analyse magic state distillation protocols where explicit physics of the system is incorporated.
-These distillation bounds are obtained by considering how a given magic state protocol would behave if it were instead applied to a \emph{stabilizer} state that is distinguished by the physics of the system -- for example an equilibrium state at a characteristic temperature, or the maximally mixed state.
+Distillation bounds are obtained by considering how a given magic state protocol would behave if it were instead applied to a \emph{stabilizer} state that is distinguished by the physics of the system -- for example an equilibrium state at a characteristic temperature, or the maximally mixed state.
 The magic distillation bounds can then be expressed in terms of this distinguished degrees of freedom (e.g.
 free energy changes in the case of temperature, or non-unitality in the case of the maximally mixed state).
-Such bounds are therefore of interest in assessing how physical features such as temperature, noise-biases or fixed-point structure associated with restricted gate-sets constrain distillation protocols, and so of relevance to existing work towards fault-tolerant quantum computing~\cite{Aliferis_2008, Stephens_2013, Li_2015, Babbush_2018, Tuckett_2019, Guillaud_2019, Fowler_2019}.
+Such bounds are therefore of interest in assessing how physical features such as temperature, noise-biases or fixed-point structure associated with restricted gate-sets constrain distillation protocols, and so are of relevance to existing work towards fault-tolerant quantum computing~\cite{Aliferis_2008, Stephens_2013, Li_2015, Babbush_2018, Tuckett_2019, Guillaud_2019, Fowler_2019}.
 
@@
 In particular, we shall view \emph{magic as a form of free energy}, relative to the set of stabilizer states.
-From this perspective the convex set of stabilizer states behaves as the set of ``equilibrium'' states, and magic corresponds to a form of non-equilibrium free energy that is strictly non-classical.
+From this perspective, the convex set of stabilizer states behaves as the set of ``equilibrium'' states, and magic corresponds to a form of non-equilibrium free energy that is strictly non-classical.
 
@@
 to denote the phase space point for the composite system. 
-For simplicity going forward, we assume $n$ copies of a $d$--dimensional system $d_1=d_2 = \cdots = d$, and therefore, we have that $\x \in \mathbb{Z}_d^{2n}$.
+For simplicity going forward, we assume $n$ copies of a $d$--dimensional system $d_1=d_2 = \cdots = d$, and therefore we have that $\x \in \mathbb{Z}_d^{2n}$.
 
@@
     \includegraphics[height=2cm]{figs/maxmixed.pdf}
-    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
     }\hspace{8pt}%
@@
     \includegraphics[height=2cm]{figs/zerostate.pdf}
-    %\caption{Zero state $\ketbra{0}{0}$}%
     }\\
@@
     \includegraphics[height=2cm]{figs/boundstate.pdf}
-    %\caption{Bound state}%
     }\hspace{8pt}%
@@
     \includegraphics[height=2cm]{figs/Strangestate.pdf}
-    %\caption{Strange state $\ketbra{S}{S}$}%
     }
     \caption{\textbf{Qutrit Wigner distributions of varying magic.} 
-    \subref{fig:maxmix} Maximally mixed state $\frac{1}{3}\id$; \subref{fig:zero} Stabilizer zero state $\ketbra{0}{0}$; \subref{fig:bound} A non-stabiliser Wigner-positive state; \subref{fig:Strange} Magic Strange state $\ket{{\rm{S}}} = \frac{1}{\sqrt{2}}(\ket{1} - \ket{2})$, coined in~\cite{cit:veitch2}.
+    \subref{fig:maxmix} Maximally mixed state $\frac{1}{3}\id$; \subref{fig:zero} Stabilizer zero state $|0\>\<0|$; \subref{fig:bound} A non-stabiliser Wigner-positive state; \subref{fig:Strange} Magic Strange state $\ket{{\rm{S}}} = \frac{1}{\sqrt{2}}(\ket{1} - \ket{2})$, coined in~\cite{cit:veitch2}.
     }%
@@
 for any $\E$ and $\rho$.
-Now if any magic protocol will send free states to free states, and so $\E$ sends all positively represented quantum state to other positively represented quantum states.
+Since the magic protocol sends free states to free states, $\E$ sends all positively represented quantum state to other positively represented quantum states.
 In such cases, it can be shown~\cite{Wang_2019} that $W_{\E}(\y |\x)$ must form a stochastic matrix.
@@
 Our analysis applies majorization to magic states at the level of the associated Wigner distributions.
-However, these are in general quasi-probability distributions and so it is important to check how majorization is computed for these cases and what differences quasi-distributions bring over genuine probability distributions.
+However, these are in general quasi-probability distributions, so it is important to check how majorization is computed for these cases and what differences quasi-distributions bring over genuine probability distributions.
 
@@
 Now the Lorenz curve is no longer monotone increasing, but is a concave function that breaks through the $L_{\w|\r}(x) = 1$ barrier at an interior point and attains some non-trivial maximum $L_\star$ above the value $1$, before decreasing monotonically to $L_{\w|\r}(x)= 1$ at the end-point $x=1$.
-See Figure \ref{fig:lcs} for examples of non-monotonic Lorenz curves for quasi-distributions.
+See~\cref{fig:lcs} for examples of non-monotonic Lorenz curves for quasi-distributions.
 Within quantum theory, the breaking of this barrier is associated with the degree of non-classicality.
@@
 The above family of curves correspond to multiple copies of noisy Strange states $\rho\coloneqq\rho_{\rm{S}}(\epsilon)^{\otimes n}$ (\cref{eq:noisysn}) for $n=2,4,6$ within a particular stabilizer fragment ($\sigma = \id/3$).
-Solid lines represent pure Strange states, while dashed lines represent $\epsilon$-noisy Strange states with depolarising noise $\epsilon = 0.1$.
+Solid lines represent pure Strange states, while dashed lines represent $\epsilon$-noisy Strange states with depolarising error $\epsilon = 0.1$.
     }
@@
 
- In Section \ref{sec:stab} we shall focus on the energetic costs of a protocol, that are defined due to the specific Hamiltonian that the system possesses.
+In~\cref{sec:stab} we shall focus on the energetic costs of a protocol, that are defined due to the specific Hamiltonian that the system possesses.
 However, before that, in this section we encode physical constraints at a more abstract level in terms of the fixed-point structure of  the actual operations that are accessible to us.
 We show that any magic theory can always be decomposed in terms of `sub-theories' with a particular fixed-point structure.
-This section therefore exploits $\mathbf{d}$--majorization, while in Section \ref{sec:stab} we drop the requirement of fixed-points and instead use the full relative majorization relation.
+This section therefore exploits $\mathbf{d}$--majorization, while in~\cref{sec:stab} we drop the requirement of fixed-points and instead use the full relative majorization relation.
 
@@
 By the Brouwer Fixed-Point theorem~\cite{cit:brouwer} this mapping must therefore have a fixed point $\sigma \in \F$.
-Therefore $\E \in \O_\sigma$ and so the interconversion is possible in this fragment.
+Therefore, $\E \in \O_\sigma$ and the interconversion is possible in this fragment.
 \end{proof}
@@
 On the technical assumption that $\sigma$ is full rank, we also have that $W_\sigma(\x) > 0$ for all $\x \in \P_d$.
-Any non-full rank states $\sigma$ can be handled as a limiting case in which we inject an infinitesimal fraction of depolarising noise $\epsilon (\id/d)$.
+Any non-full rank states $\sigma$ can be handled as a limiting case in which we inject an infinitesimal fraction of depolarising error $\epsilon (\id/d)$.
 
@@
 In contrast to mana, the area monotone is \emph{specific to the fragment}, and its value will vary as we change $\sigma$.
-Therefore its monotonicity is also including the physics of the fragment and provides a means to analyse magic distillation only under free operations that leave $\sigma$ invariant.
+Therefore, its monotonicity is also including the physics of the fragment and provides a means to analyse magic distillation only under free operations that leave $\sigma$ invariant.
 
@@
 \end{equation}
-where $\epsilon$ is the depolarization noise parameter.
-Moreover, utilising the symmetries of the Strange state allow for any magic state $\rho$ to be processed via Clifford operations~\cite{cit:prakash,cit:prakash2} and put into this canonical form for some $\epsilon \ge 0$.
+where $\epsilon$ is the depolarizing error parameter.
+Moreover, utilising the symmetries of the Strange state allows for any magic state $\rho$ to be processed via Clifford operations~\cite{cit:prakash,cit:prakash2} and put into this canonical form for some $\epsilon \ge 0$.
 
@@
 \begin{equation}
-	\W[\bmx]{\rho_{\rm{S}}(\epsilon)} = (1-\epsilon)\W[\bmx]{\ketbra{\rm{S}}} + \epsilon\W[\bmx]{\frac{1}{3}\id}.
+	\W[\bmx]{\rho_{\rm{S}}(\epsilon)} = (1-\epsilon)\W[\bmx]{\rm{S}\>\<\rm{S}|} + \epsilon\W[\bmx]{\frac{1}{3}\id}.
 \end{equation}
@@
 
-In the next section we leave fragments behind, and instead use the full structure of relative majorization to obtain bounds that incorporate energetic aspects of a magic state protocol.
+In the next section, we loosen the restriction of working in a fixed fragment, and instead use the full structure of relative majorization to obtain bounds that incorporate energetic aspects of a magic state protocol.
 
@@
 We assume that in the asymptotic/thermodynamic limit $n,m \rightarrow \infty$ that correlations generated between subsystems are negligible.
-This implies that $d\mu(x)$ is peaked on a particular state $\tau'$, and so $\E(\tau) = \tau^{\prime \otimes m}$.
+This implies that $d\mu(x)$ is peaked on a particular state $\tau'$, so $\E(\tau) = \tau^{\prime \otimes m}$.
 Physically, this is a natural scenario -- for example, in the context of traditional thermodynamics, it states that the output system is well-described by intrinsic variables that are encoded in $\tau'$, and correlations are sub-linear in $m$.
@@
 When combined with relative majorization, it also allows us to derive magic distillation bounds that combine both the computational measures $\epsilon,\epsilon'$, with terms that depend on the Hamiltonian of the physical system.
-As discussed in section~\nick{REF}, from the perspective of majorization the presence of magic can be viewed as a form of non-classical free energy and so it is also of interest to make an explicit link between the amount of magic in a non-equilibrium state $\rho_S(\epsilon)$ and the actual free energy of an equilibrium state $\tau(\beta)$.
+As discussed in section~\nick{REF}, from the perspective of majorization the presence of magic can be viewed as a form of non-classical free energy, so it is also of interest to make an explicit link between the amount of magic in a non-equilibrium state $\rho_S(\epsilon)$ and the actual free energy of an equilibrium state $\tau(\beta)$.
 
@@
 \end{align}
-and $W_\tau(\x)$ attains a minimum at $x=x_\star$. The primed variables are defined similarly for the output system.
+and $W_\tau(\x)$ attaining a minimum at $\x=\x_\star$. The primed variables are defined similarly for the output system.
 \end{theorem}
@@
 The above bound depends on: (a) quantum computational measures $\epsilon, \epsilon'$, (b) thermodynamic quantities $F, F',$  and (c) intermediate terms $\phi, \phi'$.
-The intermediate terms depend on how the energy eigenbasis of the system $\{|E_k\>\}$ relates to the computational stabilizer basis $\{|k\>\}$.
+The intermediate terms depend on how the energy eigenbasis of the system $\{\ket{E_k}\}$ relates to the computational stabilizer basis $\{\ket{k}\}$.
 In particular, the energetic term $\phi$ quantifies the degree to which the negativity in the Wigner representation can be ascribed a sharp energetic value for the given Hamiltonian of the system.
-Its form is similar to $F$, and so can informally be viewed as a `magic free energy' term, associated to what can informally be viewed as a `partition function' $\zeta$.
+Its form is similar to $F$, and it can informally be viewed as a `magic free energy' term, associated to what can informally be viewed as a `partition function' $\zeta$.
 The coefficients $\alpha_k$ may be negative for some $k$, when the Hamiltonian eigen-decomposes into non-stabilizer states, but the quantity $\phi$ is always well-defined, since the function $\zeta$ is a positive multiple of the stabilizer Wigner component $W_\tau(0,0)$, as seen in the proof of the theorem.
@@
 
-In the case that the system's Hamiltonian $H$ has an eigenbasis consisting of stabilizer states then we show in Appendix \ref{sharp-phi} that $\phi$ takes on a sharp, temperature-independent energy value $\phi \in \{E_0,E_1,E_2\}$.
+In the case that the system's Hamiltonian $H$ has an eigenbasis consisting of stabilizer states then we show in~\cref{app:main_proof} that $\phi$ takes on a sharp, temperature-independent energy value $\phi \in \{E_0,E_1,E_2\}$.
 
@@
     \caption{\textbf{Temperature-dependent bounds for magic distillation.}
-  Shown is a contour plot of the bound on $R(\epsilon, \beta)$ for $H = H' = \sum_{k \in \mathbb{Z}_3} k \ketbra{k}$ and $\epsilon' = 0$, where $\beta$ is the inverse temperature and $\epsilon$ the depolarising noise of the input magic state.
+  Shown is a contour plot of the bound on $R(\epsilon, \beta)$ for $H = H' = \sum_{k \in \mathbb{Z}_3} k |k\>\<k|$ and $\epsilon' = 0$, where $\beta$ is the inverse temperature and $\epsilon$ the depolarising error of the input magic state.
 The relevant data from the spectrum of the qutrit operator $H$ enters in via $\epsilon_\star(\beta)$ and $\beta_\star$.
@@
     \includegraphics[scale=0.4]{figs/rate_scatter_cliff.pdf}}
-    \caption{\textbf{Temperature-dependent bounds for magic distillation.} \nick{Need to replot with one shared colorbar} Shown are two contour plots of the bound on $R(\epsilon, \beta)$ for $H = H' = \sum_{k \in \mathbb{Z}_3} k \ketbra{k}$ and $\epsilon' = 0$, where $\beta$ is the inverse temperature and $\epsilon$ the depolarising noise of the input magic state.
+    \caption{\textbf{Temperature-dependent bounds for magic distillation.} \nick{Need to replot with one shared colorbar} Shown are two contour plots of the bound on $R(\epsilon, \beta)$ for $H = H' = \sum_{k \in \mathbb{Z}_3} k |k\>\<k|$ and $\epsilon' = 0$, where $\beta$ is the inverse temperature and $\epsilon$ the depolarising error of the input magic state.
 The relevant data from the spectrum of the qutrit operator $H$ enters in via $\epsilon_\star(\beta)$ and $\beta_\star$.
@@
 \end{lemma}
-\begin{proof} Let $f_1(x)$ be equal to $L_{\p|\r}(x)$ on $[0, x_\star]$ and and $0$ otherwise.
+\begin{proof} 
+Let $f_1(x)$ be equal to $L_{\p|\r}(x)$ on $[0, x_\star]$ and and $0$ otherwise.
 Also let $f_2(x)$ be equal to $L_{\p|\r}(x)$ on $[x_\star,1]$ and and $0$ otherwise.
@@
 \end{equation}
-Therefore if we evaluate at $x=-a$ we obtain
+Therefore, if we evaluate at $x=-a$ we obtain
 \begin{equation}
@@
 for any states $\rho, \rho'$ and any full-rank stabilizer states $\tau, \tau'$.
-Therefore we have that
+Therefore, we have that
 \begin{align}
@@
 The points defining the Lorenz curve $L_{\rho_n |\tau_n}(x)$ are obtained from sorting the components of $W_{\rho_n |\tau_n}(\x)$ in non-increasing order and then computing the partial sums of $W_{\rho_n |\tau_n}(\pi(\x))$ where $\pi$ is the permutation that realises the sorting.
-However, similar to the unital fragment analysis, we use the slope constraint (Proposition \ref{prop:first_elb}) obtained by considering the line segments connecting the origin to the first elbow of both Lorenz curves.
+However, similar to the unital fragment analysis, we use the slope constraint (\cref{prop:first_elb}) obtained by considering the line segments connecting the origin to the first elbow of both Lorenz curves.
 
@@
 \begin{equation}
-	H = \sum_{k \in \mathbb{Z}_3} E_k\ketbra{E_k}{E_k},
+	H = \sum_{k \in \mathbb{Z}_3} E_k |E_k\>\<E_k|,
 \end{equation}
@@
 	W_{\tau}(\x_\star) &= \frac{1}{3\Z}\tr\left[ A_{\x_\star}e^{-\beta H} \right] \nonumber\\
-	&= \frac{e^{\beta F}}{3} \tr\left[ A_{\x_\star}\sum_{k \in \mathbb{Z}_3} e^{-\beta E_k}\ketbra{E_k}{E_k} \right] \\
+	&= \frac{e^{\beta F}}{3} \tr\left[ A_{\x_\star}\sum_{k \in \mathbb{Z}_3} e^{-\beta E_k} |E_k\>\<E_k| \right] \\
 	&= \frac{e^{\beta F}}{3} \sum_{r \in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}
@@
 \begin{equation}
-	\alpha_k = \<E_k | A_{\bmx_{\star}} |E_k\> = d W_{\ketbra{E_k}}(\bmx_{\star})
-\end{equation}
-Since each $\ketbra{E_k}$ is a stabilizer state, their Wigner distributions have orthogonal supports in the phase space, so only one of them, say $k = k_{\star}$ contains point $\bmx_{\star}$ in its support.
-Additionally, its distribution is uniform on its support, so $W_{\ketbra{E_{k_{\star}}}}(\bmx_{\star}) = 1/d$.
+	\alpha_k = \<E_k | A_{\bmx_{\star}} |E_k\> = d W_{|E_k\>\<E_k|}(\bmx_{\star})
+\end{equation}
+Since each $|E_k\>\<E_k|$ is a stabilizer state, their Wigner distributions have orthogonal supports in the phase space, so only one of them, say $k = k_{\star}$ contains point $\bmx_{\star}$ in its support.
+Additionally, its distribution is uniform on its support, so $W_{|E_{k_\star}\>\<E_{k_\star}|}(\bmx_{\star}) = 1/d$.
 
@@
 \phi &= -\beta^{-1}\ln (\sum_k \alpha_k e^{-\beta E_k}) \nonumber \\
-&=E_{k_{\star}} -kT \ln (d W_{\ketbra{E_{k_{\star}}}}(\bmx_{\star})) =E_{k_{\star}}.
+&=E_{k_{\star}} -kT \ln (d W_{|E_{k_\star}\>\<E_{k_\star}|}(\bmx_{\star})) =E_{k_{\star}}.
 \end{align}
@@
 The equilibrium state at inverse temperature $\beta$ on a single qutrit is given by $\tau = e^{-\beta H} / \Z$.
-Moreover we have that $\tau$ is a full-rank stabilizer state, where $\beta \geq 0$ and $H = E_0 \ketbra{\varphi_0} + E_1 \ketbra{\varphi_1} + E_2 \ketbra{\varphi_2}$ is an eigendecomposition of $H$.
+Moreover we have that $\tau$ is a full-rank stabilizer state, where $\beta \geq 0$ and $H = E_0 |\varphi_0\>\<\varphi_0| + E_1 |\varphi_1\>\<\varphi_1| + E_2 |\varphi_2\>\<\varphi_2|$ is an eigendecomposition of $H$.
 The state $\tau$ can now be written as 
 \begin{equation}
-	\tau = \frac{e^{-\beta E_0}}{\Z} \ketbra{\varphi_0} + \frac{e^{-\beta E_1}}{\Z} \ketbra{\varphi_1} + \frac{e^{-\beta E_2}}{\Z} \ketbra{\varphi_2},
+	\tau = \frac{e^{-\beta E_0}}{\Z} |\varphi_0\>\<\varphi_0| + \frac{e^{-\beta E_1}}{\Z} |\varphi_1\>\<\varphi_1| + \frac{e^{-\beta E_2}}{\Z} |\varphi_2\>\<\varphi_2|,
 \end{equation}
@@
 \begin{align}
-	\W[\bmx]{\tau} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z}W_{\ketbra{k}}(x, p) \nonumber\\
+	\W[\bmx]{\tau} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z}W_{|k\>\<k|}(x, p) \nonumber\\
 	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z} \delta_{x, k} = \frac{e^{-\beta E_x}}{3\Z},
@@
 If the expression $\frac{u(\epsilon)}{v(\epsilon)} e^{\beta (E_{\rm{max}} - E_s)}$ is less than $1$ then the maximum occurs at $\alpha=0$, otherwise it occurs at $\alpha = n$.
-For a fixed state $\tau$, this transition is determined by the value of the depolarising noise parameter $\epsilon$ of the noisy magic state.
+For a fixed state $\tau$, this transition is determined by the value of the depolarising error parameter $\epsilon$ of the noisy magic state.
 The transition occurs at $\epsilon = \epsilon_\star$ where

### 2021-05-29 magic_paper.tex
Fragment section and Temp-bound intro polished. To-do: contour plot bits and Outlook.

--- 2021-05-28 magic_paper.tex
@@
 
- We begin by defining the following sub-theory of any magic theory $\R$.
+ We begin by defining the following kind of sub-theory of any magic theory $\R$.
 \begin{definition}\label{def:sigmafrag}
@@
     \end{equation}
-namely those operations that leave the state $\sigma \in \F$ invariant.
+namely those free operations that leave the distinguished state $\sigma \in \F$ invariant.
 \end{definition}
-This notion provides a simple way to break up any theory into smaller, more manageable parts that are destinguished by additional physical constraints, illustrated in~\cref{fig:zoo}.
+This notion provides a simple way to break up any theory into smaller, more manageable parts.
 Moreover, the union over all fragments returns the parent theory, so we are not discarding any information by breaking up the theory in this way.
@@
 \end{proof}
+One can compare with resource monotones, which are also called resource measures.
+A complete set of measures $\{\M_i\}_i$ is such that $\rho \rightarrow \sigma$ if and only if $\M_i(\rho) \ge \M_i(\sigma)$ for all $i$.
+The above set of sub-theories can therefore be viewed as a complete set of ``co-measures'' for the theory, where the parent resource theory's complex pre-order of states is mapped to a simpler pre-order for a particular fragment.
+In the next section we show that this pre-order for a given fragment can always be approximated by a majorization pre-order, and from this we can compute magic distillation bounds.
 
@@
 \end{figure}
-It is now possible to consider magic distillation rates within $\sigma$--fragments and then see how the bounds on the distillation rates depend on the choice of the fragment we work within.
 
@@
 
-If we consider some $\sigma \in \F$, and its corresponding fragment $\R_\sigma$, then we are typically interested in the ability to transform many copies of some magic state $\rho$ into more pure forms of magic.
+We consider some $\sigma \in \F$, and its corresponding fragment $\R_\sigma$.
+We are interested in the ability to transform many copies of some noisy magic state $\rho$ towards a more pure form of magic.
 The state $\rho$ is assumed to have negativity in the Wigner representation, so $W_\rho(\x) < 0$ for some regions of $\x \in \P_d$.
-We again note that we restrict to odd-dimensional quantum systems, for simplicity.
-In contrast, the state $\sigma$ will have a Wigner distribution $W_\sigma(\x)$ that forms a genuine probability distribution.
-On the technical assumption that $\sigma$ is full rank, we also have that $W_\sigma(\x) > 0$ for all $\x \in \P_d$.
-Any non-full rank states $\sigma$ can be handled as a limiting case in which we inject an infinitesimal fraction of depolarising noise $\epsilon (\id/d)$.
-
-As discussed already, the free operations within the magic theory $\R$ are represented by stochastic maps, and within $\R_\sigma$ by stochastic maps that leave $W_\sigma(\x)$ invariant.
+The state $\sigma$ is assumed to have a Wigner distribution with $W_\sigma(\x) > 0$ for all $\x$ in the phase space\footnote{Any non-full rank state $\sigma$ can be handled as a limiting case in which we first add an infinitesimal fraction of depolarising noise $\epsilon (\id/d)$ and then take $\epsilon \rightarrow 0$ at the end.}.
+
+The free operations within the magic theory $\R$ are represented by stochastic maps, and within $\R_\sigma$ by stochastic maps that leave $W_\sigma(\x)$ invariant.
 Therefore, a necessary condition for magic state transformations $\rho_1 \rightarrow \rho_2$ within $\R_\sigma$ will be that
@@
 or put another way, that the quasi-distribution $W_{\rho_1}$ is more ordered than the quasi-distribution $W_{\rho_2}$ relative to $W_\sigma$.
-
-This in turn can be expressed in terms of Lorenz curves. To simplify notation, we denote by $L_{\rho | \sigma}(x)$ the Lorenz curve $L_{W_{\rho} | W_{\sigma}} (x)$. We therefore have that
+To simplify notation, we denote by $L_{\rho | \sigma}(x)$ the Lorenz curve $L_{W_{\rho} | W_{\sigma}} (x)$, and therefore have that
 \begin{equation}
@@
 \end{equation}
-for all $x \in [0,1]$.
-Therefore, the magic state Lorenz curve condition can be used to impose upper bounds on magic distillation rates.
-Note, however, that unlike any monotone, this is not a single numerical constraint, but a \emph{family} of constraints.
-Indeed, for $n$ copies of a $d$--dimensional system the number of terms in $W_{\rho}$ is $d^{2n}$, so the Lorenz curve condition corresponds to exponentially many constraints, of which though there are at most as many independent constraints as there are elbows in the Lorenz curve of the output state, as proved in~\cref{thm:elbows}.
-In principle, any one location $x$ provides some valid constraint leading to an upper distillation bound, while optimising over the location provides the strictest majorisation bound.
+for all $x \in [0,1]$, which restricts the transformations that are possible.
+
+  Note, however, that this is not a single numerical constraint, but a family of constraints.
+For $n$ copies of a qudit system of dimension $d$ the number of terms in $W_{\rho}$ is $d^{2n}$, so imposing the Lorenz curve condition corresponds to \emph{exponentially} many constraints.
+However,  before computing explicit examples, in the next section we highlight how these majorization constraints relate to other known monotones.
 
@@
 
-In this section, we give some generic aspects of Lorenz curves for magic states.
-In particular, these allow us to interpret previous magic monotones in a new light.
-The first result provides an extremely simple way to see that the sum-negativity of a magic state is a monotone.
+In this section, we state some generic aspects of Lorenz curves for magic states.
+These allow us to interpret previous magic monotones in a new light.
+The first result gives an extremely simple way to see that the sum-negativity of a magic state is a monotone.
 
@@
 \begin{proof}
-	The sum-negativity of a magic state $\rho$ can be written as $sn(\rho) \coloneqq \frac{1}{2} (\sum_{\x} |W_\rho(\x) | - 1)$.
-We make use of a variant form of relative majorization, (see~\cref{app:major}), stating that $\p \succ_{\r} \q$ if and only if
+	The sum-negativity of a magic state $\rho$ can be written as $sn(\rho) =\frac{1}{2} (\sum_{\x} |W_\rho(\x) | - 1)$.
+We make use of the $L_1$-norm form of relative majorization, (see~\cref{app:major}), which states that $\p \succ_{\r} \q$ if and only if
 	\begin{equation}
@@
 \end{proof}
-As a corollary, this result applies to mana too, since mana is an increasing function of sum-negativity.
 
 If we have a magic state $\rho$ that has negativity in its Wigner representation, then, as discussed, its Lorenz curve over-shoots $1$ and reaches a non-trivial maximum $L_\star$ that depends on the particular state.
-There is an exact relation between $L_\star$ and sum-negativity or mana, which is provided by the following result.
+There is an simple relation between $L_\star$ and sum-negativity or mana, which is provided by the following result.
 \begin{theorem}\label{lem:lcmax}
@@
 The proof of this is given in~\cref{app:major}.
-Using the Lorenz curve perspective, it is simple to construct other monotones.
+Using the Lorenz curve perspective, it is also simple to construct new monotones.
 For example, within a given fragment, the area above the horizontal line $y = 1$ is another magic monotone.
@@
 \end{proof}
-In contrast to mana, the area monotone is \emph{specific to the fragment}, and its value will vary as we change $\sigma$.
-Therefore its monotonicity is also including the physics of the fragment and provides a means to analyse magic distillation only under free operations that leave $\sigma$ invariant.
-
-We ultimately want to make statements about asymptotic distillation rates $R$,
-\begin{equation}
-\rho_1^{\otimes n} \longrightarrow \rho_2^{\otimes R n}
-\end{equation}
-where $\rho_2$ is a purer magic state than $\rho_1$ and $R$ is made as large as possible as $n$ tends to infinity.
-We shall next turn to this analysis, and exploit basic features of a magic state in order to obtain non-trivial distillation bounds.
+Note though, in contrast to mana, the area monotone is \emph{specific to the fragment}, and its value will vary as we change $\sigma$.
+Therefore its monotonicity is conditioned on the physics of the fragment and so provides a means to analyse magic distillation only under free operations that leave $\sigma$ invariant.
+One can also define an area monotone in the more general setting of relative majorization, where one drops the fixed point emphasis as in Section \ref{sec:stab}, but we do not explore this here.
 
@@
 
-In this section, we apply majorization to magic state distillation within a simple fragment, namely the unital fragment.
-This encompasses distillation protocols where one is restricted to \emph{unital operations}, meaning that $\E(\I/d) = \I/d$ for all free $\E$.
-This is a particularly powerful set of operations, which for example include all Weyl-covariant channels~\cite{cit:gross3}.
-To make things concrete, we shall consider qutrit magic states ($d=3$) as the Wigner representation is simpler compared to qubits ($d=2$), while they admit non-trivial structure (e.g.
-Hamiltonians with two different energy gaps) and still are sufficiently simple to analyse in detail.
-
-For our distillation protocols we need to choose a canonical pure magic state as a target. For this we shall choose the Strange state $|S\>$ given as
+We now construct magic state distillation bounds within the unital fragment ($\sigma = \I/d$).
+This describes distillation protocols that generate \emph{unital operations}, meaning that $\E(\I/d) = \I/d$, and includes for example all protocols built from Weyl-covariant channels~\cite{cit:gross3}.
+
+Our approach applies to any dimension, but for simplicity we consider qutrit magic states ($d=3$), for which a canonical magic state exists with a particularly simple Wigner distribution.
+This is the Strange state $|S\>$, which is given by
 \begin{equation}
@@
 in the computational basis.
-This qutrit magic state is exceptionally symmetric and simple which benefits our analysis.
 Its distribution $W_S(\x)$ has a single negative value of $-1/3$ at $\x =(0,0)$ and the positive value $1/6$ at all other points.
-We can define the $\epsilon$--noisy Strange state as
+We define the $\epsilon$--noisy Strange state as
 \begin{equation}\label{eq:noisysn}
@@
 where $\epsilon$ is the depolarization noise parameter.
-Moreover, utilising the symmetries of the Strange state allow for any magic state $\rho$ to be processed via Clifford operations~\cite{cit:prakash,cit:prakash2} and put into this canonical form for some $\epsilon \ge 0$.
+One nice feature of this is that any magic state $\rho$ can be processed via Clifford operations~\cite{cit:prakash,cit:prakash2} and put into this canonical form for some $\epsilon \ge 0$.
 
@@
 \begin{equation}
-	\W[\bmx]{\rho_{\rm{S}}(\epsilon)} = (1-\epsilon)\W[\bmx]{\ketbra{\rm{S}}} + \epsilon\W[\bmx]{\frac{1}{3}\id}.
-\end{equation}
-Since the Wigner distribution $W_{\I/3}(x)$ is the uniform probability distribution over the phase space, we get that $W_{\rho_S(\epsilon) } (\x)$ has a single negative component
+	\W[\bmx]{\rho_{\rm{S}}(\epsilon)} = (1-\epsilon)\W[\bmx]{S} + \epsilon\W[\bmx]{\frac{1}{3}\id}.
+\end{equation}
+with a single negative component
 \begin{equation}
@@
 \end{equation}
-at the 8 phase space points $\x \ne (0,0)$. We assume that $\epsilon < 3/4$ to ensure the presence of negativity in the Wigner distribution.
-
-We now consider the task of purifying $n$ copies of a noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ as given in~\cref{eq:noisysn} into a smaller number of copies $n'$ of a less noisy Strange state $\rho_{\rm{S}}(\epsilon')^{\otimes n'}$, with $\epsilon' < \epsilon$ and $n' \leq n$.
-Since we work in the unital fragment, the maximally mixed state is free and we choose to tensor in $n'-n$ auxiliary copies of it to the output, highlighting that we are working in the unital fragment.
-This affects neither the distillation process nor our analysis, since the Lorenz curves remain unaffected.
-More generally, it is easy to see that
+at the 8 phase space points $\x \ne \mathbf{0}$. We assume that $\epsilon < 3/4$ to ensure the presence of negativity in the Wigner distribution.
+
+We now consider purifying $n$ copies of a noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ into a smaller number of copies $n'$ of a less noisy Strange state $\rho_{\rm{S}}(\epsilon')^{\otimes n'}$, with $\epsilon' < \epsilon$ and $n' \leq n$.
+Since we work in the unital fragment, the maximally mixed state is free and we choose to tensor in $n'-n$ auxiliary copies of it to the output.
+This simplifies analysis, and does not affect distillation rates as it is easy to see that
 \begin{equation}
@@
 \end{equation}
-for any full-rank $\sigma \in \F$. Therefore, we consider the transformation
+for any full-rank $\sigma \in \F$. Therefore, we compute the Lorenz curves for the transformation
 \begin{equation}\label{eq:sudist}
@@
 \end{equation}
-and compare the Lorenz curves for the input and output states to bound $R(\epsilon, \epsilon') \coloneqq n'/n$, the rate of this interconversion within the fragment.
-
-The Wigner distribution of $n$ copies of the state is obtained by the $n$-fold product of the single copy distribution, and the Lorenz curve $L_{\rho|\sigma}(x)$ for $\rho = \rho_S(\epsilon)^{\otimes n}$ and $\sigma = (\I/3)^{\otimes n}$ is readily computed for any $n$ and $\epsilon$, and the full details are provided in~\cref{app:lcsu_technical}.
-We highlight that the non-trivial element that arises for quasi-distributions is that the product of negative components can generate a positive $n$-fold component, so the ordering of the components of \emph{rescaled Wigner distribution} $W_{\rho |\sigma}(\bmx) \coloneqq W_{\rho}(\bmx)/W_{\sigma}(\bmx)$ depends on whether $-v(\epsilon)$ appears to an even or odd power in the expression of~\cref{eq:wigu}.
-
-The component values $w_i$ and associated multiplicities ($m_i$) in the $n$--copy case are 
+and use them to bound the distillation rate $R(\epsilon, \epsilon') \coloneqq n'/n$.
+
+Due to negativity, the ordering of the components of rescaled Wigner distribution $W_{\rho_n |\sigma_n}(\bmx) \coloneqq W_{\rho_n}(\bmx)/W_{\sigma_n}(\bmx)$, for $\rho_n = \rho_S(\epsilon)^{\otimes n}, \sigma_n = \sigma^{\otimes n}$, depends on whether $-v(\epsilon)$ appears to an even or odd power in the expression of~\cref{eq:wigu}.
+Treating the Wigner distributions as vectors, the component values $w_i$ and associated multiplicities ($m_i$) in the $n$--copy case are found to be
 \begin{align}
@@
 \end{align}
-where index $i$ runs through $0, \dots, n$, and we assume for simplicity of exposition that $n$ is even and the depolarising error is not high, $\epsilon \leq 3/7$, so that $v \geq u$.
-The details of this scenario, along with the other possible cases that occur depending on the error and the parity of the number of copies, are provided in~\cref{app:lcsu_technical}.
-
-The Lorenz curve $L_{\rho|\sigma}(x)$ rises monotonically and reaches a maximum value
+where index $i$ runs through $0, \dots, n$, and we assume for simplicity that $n$ is even and $\epsilon \leq 3/7$, which implies that $v \geq u$.
+The details of this are provided in~\cref{app:lcsu_technical}.
+
+The Lorenz curve $L_{\rho_n|\sigma_n}(x)$ reaches a maximum value of
 \begin{align}\label{eq:lcsu_max}
@@
 
-It is possible to derive distillation bounds from any location of the Lorenz curve, including the region around the peak, by imposing the constraint that the Lorenz curve of the input state never dips below the curve of the output.
-However, it turns out that a simple and sufficiently non-trivial constraint can be obtained by considering the first elbow of the Lorenz curves. 
-The largest Wigner component occurs for $i=0$ and is unique, so the first elbow coordinates for $\rho_S(\epsilon)^{\otimes n}$ are given by $(1/9^n, v(\epsilon)^n)$, while for $\rho_S(\epsilon')^{\otimes n'}$ by $(1/9^{n'}, v(\epsilon')^{n'})$.
-
-The first elbow constraint involves a simple interpolation, done in~\cref{prop:first_elb}, in order to find the coordinates of both Lorenz curve points at the location where the first elbow occurs. 
-Comparing these two points leads to the bound
+Distillation bounds can be obained from any location of the Lorenz curve, including the region around the peak, by imposing the constraint that the Lorenz curve of the input state never dips below the curve of the output.
+In particular a compact constraint can be obtained by considering the initial slopes of the two Lorenz curves.
+
+The first elbow coordinates for $\rho_S(\epsilon)^{\otimes n}$ are given by $(1/9^n, v(\epsilon)^n)$, while for $\rho_S(\epsilon')^{\otimes n'}$ by $(1/9^{n'}, v(\epsilon')^{n'})$, and by considering the slope of the line segment joining this first elbow to the origin we can use~\cref{prop:first_elb} in the Appendices, to bound $R(\epsilon, \epsilon')$.
+We find that
 \begin{equation}
@@
 \end{equation}
-For the limiting case of distilling pure magic states ($\epsilon'=0$), we obtain an upper bound in the unital fragment given by
+For the limiting case of pure magic states on the output ($\epsilon'=0$), this simplifies to
 \begin{equation}
@@
 \end{equation}
-
-Similar upper bounds on distillation rates for qudits of odd prime dimension include the mana bound~\cite{cit:veitch} and the max--thauma bound~\cite{Wang_2020} which can be defined as
+This can be compared to other known distillation bounds coming from mana and thauma~\cite{Wang_2020}. The mana bound can be directly calculated as
+\begin{equation}
+	R \leq \frac{\mana{\rho_{\rm{S}}(\epsilon)}}{\mana{\rho_{\rm{S}}(0)}} = 1 + \frac{\ln \left(1 - \frac{8}{15}\epsilon \right)}{\ln \frac{5}{3}}.
+\end{equation}
+The recently introduced max--thauma~\cite{Wang_2020} is defined as
 \begin{equation}
@@
 \end{equation}
-and can be calculated numerically via a semi-definite program\footnote{Provided as supplemental material with~\cite{Wang_2020}}.
-
-The mana bound can be directly calculated as
-\begin{equation}
-	R \leq \frac{\mana{\rho_{\rm{S}}(\epsilon)}}{\mana{\rho_{\rm{S}}(0)}} = 1 + \frac{\ln \left(1 - \frac{8}{15}\epsilon \right)}{\ln \frac{5}{3}}.
-\end{equation}
-For the noisy Strange state, the max--thauma bound coincides with the mana bound, and are both looser than the majorization bound we derived via the first elbow constraint as illustrated in~\cref{fig:distill_bounds}.
-Numerical, ``optimal'', bounds $R_{\rm{opt}}$ obtained by considering the entirety of the Lorenz curves have been included in the plot as well, highlighting that the first elbow constraint does not capture the full capabilities of majorization.
-Notably, in contrast to the other bounds, $R_{\rm{opt}}$ depends explicitly on the copies $m,n$, rather than their ratio $m/n$, so it is specific to the process.
-An interesting open question arises regarding the value of $R_{\rm{opt}}$ as $n,m \rightarrow \infty$, while $m/n$ remains constant.
+and can be calculated numerically via a semi-definite program.
+For the noisy Strange state, the max--thauma bound coincides with the mana bound, and we find that they are both looser than the majorization bound we derived via the first elbow constraint as shown in~\cref{fig:distill_bounds}.
+
+This figure includes numerical estimates of the optimal majorization bounds $R_{\rm{opt}}$ obtained by considering the full Lorenz curve, which show that the first elbow constraint can be further improved.
 \begin{figure}[t]
@@
 
-This means in particular that $\E(\tau^{\otimes n})$ is a symmetric state on $m$ subsystems, so by the quantum de Finetti theorem~\cite{christandl_2007} we have that
+This means in particular that $\E(\tau^{\otimes n})$ is a symmetric state on $m$ subsystems, so by the quantum de Finetti theorem~\cite{christandl_2007} we have that for $m \gg 1$
 \begin{equation}
@@
 where $d\mu(x)$ is a probability measure over a set $\{\tau'_x\}$ of single qudit states.
+This makes the setting easier to handle, although we make one more simplifying assumption as explained in the next section.
 
@@
 To simplify our analysis we will make the following physical assumption.
-We assume that in the asymptotic/thermodynamic limit $n,m \rightarrow \infty$ that correlations generated between subsystems are negligible.
-This implies that $d\mu(x)$ is peaked on a particular state $\tau'$, and so $\E(\tau) = \tau^{\prime \otimes m}$.
-Physically, this is a natural scenario -- for example, in the context of traditional thermodynamics, it states that the output system is well-described by intrinsic variables that are encoded in $\tau'$, and correlations are sub-linear in $m$.
-This assumption allows us to associate a free energy per qudit of the output state, which would be more complex if non-trivial correlations were present.
-
-The case of correlations between output subsystems can also be considered, but would lead to a more complex analysis within our majorization framework of Wigner distributions.
+We assume that in the asymptotic/thermodynamic limit $n,m \rightarrow \infty$ that correlations generated on the reference equilibrium state are negligible.
+This implies that $d\mu(x)$ is peaked on a particular state $\tau'$, and $\E(\tau) = \tau^{\prime \otimes m}$.
+Physically, this is a natural scenario -- for example, in the context of traditional thermodynamics, it states that the output system is well-described by intrinsic variables that do not scale in $m$, and correlations are sub-linear in $m$.
+This allows us to compute a free energy per qudit of the output state.
+
+The case of non-trivial correlations in the thermodynamic limit can also be considered, but leads to a more complex analysis within our majorization framework of Wigner distributions.
 In this direction, we highlight recent work in majorization in which stochastic independence and correlations are analysed.
@@
 
-As mentioned, we can quantify the energetic aspects of a given protocol by considering how it transforms a physical system in state with a clear notion of energy, such as a thermodynamic equilibrium state.
-The protocol transforms this state as $\tau^{\otimes n} \rightarrow \E(\tau^{\otimes n}) = \tau^{\prime \otimes m}$.
-Since the protocol does not, on its own, generate magic the output state $\tau'$ is also a stabilizer state, provided that $\tau$ is as well.
-This is generally a \emph{non-equilibrium} state for the system.
-However, the distillation bounds that we derive take a particularly simple form if we associate a Hamiltonian $H'$ to the output state by considering the change $H \rightarrow H'$ such that equilibrium is restored at the reference temperature $T$.
+The protocol transforms the equilibrium as $\tau^{\otimes n} \rightarrow \E(\tau^{\otimes n}) = \tau^{\prime \otimes m}$.
+The protocol does not, on its own, generate magic and so we assume the output state $\tau'$ is also a Wigner-positive state.
+However, this is generally a \emph{non-equilibrium} state for the system.
+Despite this, the distillation bounds that we derive take a particularly simple form if we associate an effective Hamiltonian $H'$ to the output state by considering the change $H \rightarrow H'$ such that equilibrium is restored at the reference temperature $T$.
 This Hamiltonian is defined by the expression $\tau' = e^{-\beta H'}/\Z'$, and has free energy $F' = -\beta^{-1} \log \Z'$.
@@
 \subsection{Temperature-dependent distillation bounds}
-The preceding discussion gives a means to specify energetic details of a protocol through how much it would disturb some reference equilibrium state.
-When combined with relative majorization, it also allows us to derive magic distillation bounds that combine both the computational measures $\epsilon,\epsilon'$, with terms that depend on the Hamiltonian of the physical system.
-As discussed in section~\nick{REF}, from the perspective of majorization the presence of magic can be viewed as a form of non-classical free energy and so it is also of interest to make an explicit link between the amount of magic in a non-equilibrium state $\rho_S(\epsilon)$ and the actual free energy of an equilibrium state $\tau(\beta)$.
-
-Given this account we now state the following result for the case of $d=3$ qutrits, in which magic distillation protocols are viewed as non-equilibrium processes.
+W can specify energetic details of a protocol through how much it would disturb some reference equilibrium state.
+The magic state transformation is then considered relative to the equilibrium transformation, and can be recast (via the Wigner representation) into a relative majorization statement $(\w, \r) \succ (\w', \r')$ where $\w, \w'$ are quasi-distributions corresponding to the magic transformation, while $\r, \r'$ correspond to the transformation of the reference equilibrium state.
+
+This leads to magic distillation bounds that combine computational measures $\epsilon,\epsilon'$, with terms that depend on the Hamiltonian and reference temperature $T$ of the physical system.
+Given this, we now state the following result for the case of $d=3$ qutrits.
 
@@
 	Let $T =(k\beta)^{-1}$ be any finite temperature for the physical system and let $H= \sum_{k \in \mathbb{Z}_3} E_k |E_k\>\<E_k|$ be the Hamiltonian of each qutrit subsystem in its eigen-decomposition.
-Assume that in the thermodynamic limit ($n,m \gg 1$), the protocol applied to the equilibrium state $\tau^{\otimes n} = (e^{-\beta H}/\Z)^{\otimes n}$ maps $\tau^{\otimes n} \longrightarrow \tau^{\prime \otimes m}$, where we express state $\tau'$ as $\tau' = e^{-\beta H'}/\Z'$ for some Hermitian $H'$.
+Assume that in the thermodynamic limit ($n,m \gg 1$), the protocol applied to the equilibrium state $\tau^{\otimes n} = (e^{-\beta H}/\Z)^{\otimes n}$ maps $\tau^{\otimes n} \longrightarrow \tau^{\prime \otimes m}$, where we write $\tau' = e^{-\beta H'}/\Z'$ for some Hermitian $H'$.
 
@@
 \end{theorem}
-\noindent The proof of this is provided in~\cref{thm:free-energy-bound-proof}, and is a generalization of the analysis for unital protocols.
+\noindent The proof of this is provided in~\cref{thm:free-energy-bound-proof}, and follows a similar line as taken for our unital protocol bound.
 
@@
 
+\ddd{[I might add this. Need to check if first bit is true. I think the ``$x_\star=$ minimum of $W$'' makes it true.]}
+\begin{lemma} If $\tau \not \in \F$ then $\phi$ is undefined, and if $\tau$ is on the boundary of $\F$ then $\phi \rightarrow \infty$.
+Moreover, if $H$ has an energy eigenbasis of stabilizer states then $\phi =E_i$ for some $i$, independent of the finite temperature.
+\end{lemma}
 In the case that the system's Hamiltonian $H$ has an eigenbasis consisting of stabilizer states then we show in Appendix \ref{sharp-phi} that $\phi$ takes on a sharp, temperature-independent energy value $\phi \in \{E_0,E_1,E_2\}$.

### 2021-05-30 magic_paper.tex
Almost done with first draft. Link with single-shot entropy added. Looks much neater perspective.

@@
 
-This leads to magic distillation bounds that combine computational measures $\epsilon,\epsilon'$, with terms that depend on the Hamiltonian and reference temperature $T$ of the physical system.
-Given this, we now state the following result for the case of $d=3$ qutrits.
+This leads to the following magic distillation bound that combines computational measures $\epsilon,\epsilon'$, with terms that depend on the Hamiltonian and reference temperature $T$ of the physical system.
+We state the result for the case of qutrits, but a similar analysis is possible for general qudits.
 
@@
 
-Then the magic distillation rate $R = m/n$ for the protocol is bounded by the expression
+Then the asymptotic magic distillation rate $R = m/n$ is bounded as
 \begin{equation}\label{eq:rate_bounds_proof}
@@
 \end{align}
-and $W_\tau(\x)$ attains a minimum at $x=x_\star$. The primed variables are defined similarly for the output system.
+and $W_\tau(\x)$ attains a minimum at $\x=\x_\star$. The primed variables are defined similarly for the output system.
 \end{theorem}
@@
 
-The above bound depends on: (a) quantum computational measures $\epsilon, \epsilon'$, (b) thermodynamic quantities $F, F',$  and (c) intermediate terms $\phi, \phi'$.
-The intermediate terms depend on how the energy eigenbasis of the system $\{|E_k\>\}$ relates to the computational stabilizer basis $\{|k\>\}$.
-In particular, the energetic term $\phi$ quantifies the degree to which the negativity in the Wigner representation can be ascribed a sharp energetic value for the given Hamiltonian of the system.
-Its form is similar to $F$, and so can informally be viewed as a `magic free energy' term, associated to what can informally be viewed as a `partition function' $\zeta$.
-The coefficients $\alpha_k$ may be negative for some $k$, when the Hamiltonian eigen-decomposes into non-stabilizer states, but the quantity $\phi$ is always well-defined, since the function $\zeta$ is a positive multiple of the stabilizer Wigner component $W_\tau(0,0)$, as seen in the proof of the theorem.
-The quantity $\phi$ would diverge if the state $\tau$ acquired zero Wigner components, which only occurs if $\tau$ is on the boundary of the set of Wigner-positive states.
-
-\ddd{[I might add this. Need to check if first bit is true. I think the ``$x_\star=$ minimum of $W$'' makes it true.]}
-\begin{lemma} If $\tau \not \in \F$ then $\phi$ is undefined, and if $\tau$ is on the boundary of $\F$ then $\phi \rightarrow \infty$.
-Moreover, if $H$ has an energy eigenbasis of stabilizer states then $\phi =E_i$ for some $i$, independent of the finite temperature.
-\end{lemma}
-In the case that the system's Hamiltonian $H$ has an eigenbasis consisting of stabilizer states then we show in Appendix \ref{sharp-phi} that $\phi$ takes on a sharp, temperature-independent energy value $\phi \in \{E_0,E_1,E_2\}$.
-
-The primary role of the pre/post-processing by Clifford unitaries is to simplify the form of the bound, and allow it to be expressed in terms of free energy quantities that do not depend on the parameters $\epsilon, \epsilon', \beta$ in a complex form.
+The above bound depends on: 
+\begin{itemize}
+\item Quantum computational measures $\epsilon, \epsilon'$,
+\item Thermodynamic quantities $\beta, F, F',$
+\item Intermediate terms $\phi, \phi'$. 
+\end{itemize}
+The intermediate terms specify how the energy eigenbasis of the system $\{|E_k\>\}$ relates to the computational stabilizer basis $\{|k\>\}$.
+In particular, the term $\phi$ quantifies to what degree a sharp energy value can be ascribed to the negativity in the Wigner representation.
+Its form is similar to $F$, and so $\phi$ can informally be viewed as a `magic free energy' term.
+
+The coefficients $\alpha_k$ may be negative for some $k$, when the Hamiltonian has non-stabilizer eigenstates, but the quantity $\phi$ is always well-defined, since the function $\zeta$ is always positive for $\tau$ in the interior of $\F$.
+The quantity $\phi$ can diverge if the state $\tau$ acquired zero Wigner components, which occurs for $\tau$ on the boundary of the set of Wigner-positive states, and is not defined outside of $\F$.
+Finally, if $H$ has a stabilizer eigenbasis then $\phi = E_i$ for some $i$, independent of the temperature $T$.
+Details of this are provided in Appendix \ref{app:lcst_technical}.
+
+\subsection{Core aspects of the bound}
+Similar to the unital protocol bounds, the above result is based on only part of the Lorenz curves and so can certainly be tightened with further analysis.
+However we note that the analysis makes use of a single-shot entropy $D_\infty (\p ||\r)$ that remains well-defined even for quasi-distributions (see Appendix~\ref{app:lcst_technical}).
+Specifically, the above bounds follow by considering $D_\infty(\rho, \tau) := D_\infty (W_\rho(\x) || W_\tau (\x))$.
+It is therefore of interest to further explore this perspective and determine what components of single-shot information theory could be extended to quasi-distributions.
+
+The primary role of the pre/post-processing by Clifford unitaries in~\cref{thm:free-energy} is to simplify the form of the bound, and allow it to be expressed in terms of the free energy per particle in a way that does not depend on the parameters $\epsilon, \epsilon', \beta$ in a complex form.
+In Appendix \ref{app:lcst_technical}, we give bounds in which one does not include these Clifford changes of basis (see Theorem \ref{thm:no-processing}), and which have a more non-trivial dependency on the parameters.
 
@@
     \includegraphics[scale=0.4]{figs/rate_scatter_cliff.pdf}}
-    \caption{\textbf{Temperature-dependent bounds for magic distillation.} \nick{Need to replot with one shared colorbar} Shown are two contour plots of the bound on $R(\epsilon, \beta)$ for $H = H' = \sum_{k \in \mathbb{Z}_3} k \ketbra{k}$ and $\epsilon' = 0$, where $\beta$ is the inverse temperature and $\epsilon$ the depolarising noise of the input magic state.
-The relevant data from the spectrum of the qutrit operator $H$ enters in via $\epsilon_\star(\beta)$ and $\beta_\star$.
-The $\beta = 0$ line corresponds to the regime in which the magic protocol corresponds to a unital channel.
-\subref{fig:noCliff} No additional Clifford processing is performed to obtain this plot.
-The vertical dashed line is the `Landauer-like' temperature threshold $\beta_\star$ and the diagonal dashed curve corresponds to the noise threshold $\epsilon_\star(\beta)$ for $\beta \leq \beta_\star$, as defined in~\cref{app:cliff_processing}.
- \subref{fig:Cliff} Clifford processing was performed resulting in a smooth bound.}
+    \caption{\textbf{Temperature-dependent bounds for magic distillation.} Shown are two contour plots of the bound on $R(\epsilon, \beta)$ for the case $H = H' = \sum_{k \in \mathbb{Z}_3} k \ketbra{k}$ and $\epsilon' = 0$, where $\beta$ is the inverse temperature and $\epsilon$ is the depolarising noise of the input magic state.
+The top figure \subref{fig:noCliff} does not use any changes of Clifford basis, and the form of the bound depends on both the noise parameter and temperature.
+The curved dashed line is $\epsilon_\star(\beta)$ is given by Equation \ref{eq:threshold} and $\beta_\star = (kT_\star)^{-1}$ is given by $E_2-\phi = kT_\star \ln 2$.
+In the bottom figure \subref{fig:Cliff} Clifford processing is used resulting in a smoother bound. In both figures the $\beta = 0$ line correspond to the unital bounds.} 
     \label{fig:rate_contour}
@@
 
-\cref{thm:free-energy} is a demonstration of how one can use relative majorization of quasi-distributions to incorporate additional information into distillation bounds.
-The analysis involved makes simplifying assumptions that could easily be dropped, at the price of more complex expressions.
-For example, we can obtain general expressions without any assumptions on $\epsilon, \epsilon'$ or without performing any Clifford change in basis.
-We could also perform similar analysis for general qudits, and different choices of magic states.
-It might also be of interest to consider other choices of reference states that may include more appropriate hardware physics, for example for photonic set-ups.
-
-The only assumption that is non-trivial is the assumption that we can ignore correlations in the thermodynamic limit.
-This is a common situation in thermodynamics, where correlations are often sub-linear in the particle number in the macroscopic limit.
-One could perturb about this scenario, and make use of variational tools such as the Bogoliubov inequality~\cite{bogolyubov_1966} for approximating the free energy of a system, to obtain bounds in a similar form.
-
-The bound derived is based on analysis of only part of the Lorenz curves and can be improved via a finer analysis.
-This is apparent by simple numerical calculations on the entirety of the curves as seen in~\cref{fig:distill_bounds} for the case of unital operations.
-Specifically, the existing bound follows by considering the dominant terms in the rescaled Wigner distribution and do not, for example, take into account the Lorenz curve's peak structure.
-
-As a special case of the result, suppose that $H=H'$, implying that the protocol leaves the equilibrium state unchanged, hence it corresponds to a Gibbs-preserving map~\cite{faist_2015}.
-We focus on the pure state distillation case, where $\epsilon' \rightarrow 0$, for which we obtain~\cref{fig:rate_contour}, a contour plot of the bound on $R$ as a function of inverse temperature $\beta$ and depolarising error $\epsilon$ for the initial noisy magic state.
-
-\subsection{\nick{Numerics on varying $F, \phi$}}
-
-In the more general case, $\Delta F \coloneqq F' - F \ne 0$ and we have a free energy difference between the initial and final states, with respect to the relevant Hamiltonians.
-This is similar to the free energy differences that occur in fluctuation relations, where the final state of the system can be arbitrarily far from equilibrium, yet a free energy term for the final system still arises.
-
-\nick{Below are some interesting findings}
+The analysis makes other simplifying assumptions that could easily be dropped, at the price of more complex expressions.
+We could perform similar analysis for general qudits, and different choices of magic states, for example.
+It might also be of interest to consider other choices of reference states $\tau$ that are more appropriate to the hardware physics, for example for photonic set-ups.
+
+The assumption that is more non-trivial is that we neglect correlations in the reference state in the thermodynamic limit.
+However for more general scenarios one could make use of variational tools such as the Bogoliubov inequality~\cite{bogolyubov_1966} for approximating the free energy of a system via product states, to obtain similar bounds.
+
+\subsection{Distillation bound for special cases}
+
+The simplest special case to consider is where the Hamiltonian $H$ is diagonal in the computational basis, and $H=H'$, implying that the protocol leaves the reference equilibrium state unchanged, hence it corresponds to a Gibbs-preserving map~\cite{faist_2015}.
+For the limiting case of $\epsilon' \rightarrow 0$ we obtain~\cref{fig:rate_contour} which is a contour plot of the bound on $R$ as a function of inverse temperature $\beta$ and the depolarising error $\epsilon$ for the noisy input magic states.
+In this figure we show both the bounds with Clifford basis changes and without them.
+
+In the more general case, $\Delta F \coloneqq F' - F \ne 0$ and so the protocol, when applied to the reference state, adds/extracts free energy from the system.
 
@@
 
-Performing the standard 3D-rotation matrix 
-\begin{equation}
-\begin{pmatrix}
-\sin{\theta}\cos{\varphi} & \sin{\theta}\sin{\varphi} & \cos{\theta}\\
-\cos{\theta}\cos{\varphi} & \cos{\theta}\sin{\varphi} & -\sin{\theta}\\
--\sin{\varphi} & \cos{\varphi} & 0
-\end{pmatrix}
-\end{equation}
-on $H$ to get $H'$ leaves $\phi$ unaffected.
-I didn't find any interesting case where $\phi \rightarrow \infty$, except of course when there is some $E_k \rightarrow \infty$. 
-I looked through Hamiltonians which are convex combinations of phase-point operators and SHO (diagonal) Hamiltonians.
-
-\nick{What happens when the bound $=0$ or $1$?}
-Note that it is always true that $L_0/x_0 > 1$ for any Lorenz curve of a state which is not free (this is because the free state Lorenz curve is a straight line connecting $(0,0$ and $(1,1)$ while all other Lorenz curves lie above it.)
-Therefore, in the bound expression
-\begin{equation}\label{eq:rate_bounds_proof}
-	R = \dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (\phi - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (\phi' - F')},
-\end{equation}
-where the denominator is always positive (and we've set equality to saturate the bound), we can rewrite it as
-\begin{equation}
-	\frac{m}{n}\frac{\ln{(L_0/x_0)}}{\ln{(L'_0/x'_0)}} = R.
-\end{equation}
-If $R=0$ it means that $m=0$ (zero output states) or the slope $L_0/x_0$ equals 1 (input state is free).
-If $R=1$, we get a trade-off between copy number and Lorenz curve slopes,
-\begin{equation}
-	\left(\frac{L_0}{x_0}\right)^m = \left(\frac{L'_0}{x'_0}\right)^n.
-\end{equation}
-
 \section{Outlook and open questions}
@@
 We have described how relative majorization can be used to establish upper bounds on magic distillation protocols that take into account additional physics of the system.
-Our bounds only exploited the very simplest aspects of the Lorenz curves of the quasi-distributions, so it would be of interest to sharpen these bounds and exploit more of the structure in the asymptotic limit.
-This raises interesting questions that do no arise for probability distributions, because we no longer have a notion of typicality and the central limit theorem does not apply.
-That said, for special states such as the Strange state the asymptotic behaviour is relatively simple, so one could study this and obtain a better handle on the asymptotic behaviour ($n \rightarrow \infty$).
-An example of such a question was raised regarding the numerical bounds plotted in~\cref{fig:distill_bounds} for the unital fragment.
-In~\cref{app:lcsu_technical} we give some more extensive analysis in the unital fragment that could be explored further, while in~\cref{app:lcst_technical} we also provide some tools which are useful in all fragments.
-
-One might wonder if this approach could also provide \emph{lower bounds} for distillation protocols.
-Now, in contrast to the upper bounds, it is necessary to include the symplectic constraints on the phase space into the majorization relations.
-
-For example, the Clifford group action on a quantum system corresponds to the action of the affine symplectic group~\cite{cit:gross3, cit:bengtsson} on the discrete phase space.
+Our bounds exploited relatively simple aspects of the Lorenz curves of the quasi-distributions, so it would be of interest to sharpen these bounds and obtain a better handle on the Lorenz curve structure in the $n\rightarrow \infty$ limit.
+This raises interesting as we no longer have a notion of typicality and the central limit theorem does not apply.
+That said, for special states such as the Strange state the asymptotic behaviour is relatively simple, so exact asymptotics for this should be possible.
+In~\cref{app:lcsu_technical} and~\cref{app:lcst_technical} we give additional results that may be of use for later work.
+
+We can also ask if this approach could also provide \emph{lower bounds} for distillation protocols.
+In contrast to the upper bounds, it is now essential to include the symplectic constraints on the phase space in the majorization relations.
+The Clifford group action on a quantum system corresponds to the action of the affine symplectic group $G=SL(2,\mathbb{Z}_d) \ltimes \mathbb{Z}_d^2$ on the discrete phase space~\cite{cit:gross3, cit:bengtsson}.
 Therefore, any convex mixture of Clifford unitaries will correpond to a convex mixture of these group actions.
-From the Hardy-Littlewood theorem~\cite{hardy_1952}, we know that traditional majorization is obtained from convex mixtures of arbitrary permutations.
-However, this has been generalised to convex mixtures of elements of a group $G$ that acts on vectors.
+The Hardy-Littlewood theorem~\cite{hardy_1952} tells us that majorization is obtained from convex mixtures of arbitrary permutations, however this has also been generalised to convex mixtures of elements of a general group $G$.
 This $G$--majorization has been studied in the classical literature and a range of results are known about it~\cite{giovagnoli_1985, steerneman_1990, eaton_1977}.
-For example, if $G$ is a finite reflection group then the $G$--majorization pre-order is described by a finite list of conditions~\cite{giovagnoli_1985}, just as is the case for the relative majorization ordering.
-One route leading to concrete lower bounds on distillation rates is therefore to consider reflection sub-groups of the affine symplectic, or just symplectic, group, for which the majorization relation reduces to a finite set of conditions.
-
-The topic of $G$--majorization has been extensively studied, but to our knowledge there hasn't been work on relative $G$--majorization.
+For example, it is known that if $G$ is a finite reflection group then the $G$--majorization pre-order is described by a finite list of conditions~\cite{giovagnoli_1985}, just as is the case for the relative majorization ordering.
+One route leading to concrete lower bounds on distillation rates is therefore to consider reflection sub-groups of $SL(2,\mathbb{Z}_d) \ltimes \mathbb{Z}_2$, or other simple sub-groups, for which the majorization relation reduces to a finite set of conditions.
+
+The topic of $G$--majorization has been extensively studied, but to our knowledge there has not been work on relative $G$--majorization.
 This would correspond to transformations that are \emph{not} unital, but still respect the symplectic structure.
 Physically, this regime would correspond to a form of thermo-majorization obtained from looking at the action of the Clifford group at a micro-canonical level, and then reducing to a small subsystem~\cite{cit:lostaglio, Pathria_1997}.
-While this seems like a painful thing to consider, there is motivation for this beyond the aim of constructing lower bounds for magic protocols: in the case of statistical mechanics on a phase space this is precisely the situation, albeit in the continuum limit.
+While this might seem like a painful thing to consider, there is motivation for this beyond the aim of simply constructing lower bounds for magic protocols: in the case of statistical mechanics on a phase space this is precisely the situation, albeit in the continuum limit.
 Statistical mechanics of actual systems obey Hamiltonian dynamics and so automatically respect a symplectic form~\cite{Pathria_1997}.
@@
 for a particle on a ring) or by first studying the discrete case.
-Such scenarios also arise in the Quantum Hall Effect~\cite{Klitzing_1980}, which is thus another regime where these techniques might be of use.
-
-Finally, it would be of interest to consider the possibility of applying these techniques to other scenarios in which one wishes to distinguish classical from non-classical behaviour based on quasi-probability representations~\cite{Ferrie_2008, barnett_1997}
+Such scenarios also arise in the Quantum Hall Effect~\cite{Klitzing_1980}, which is thus another regime where these techniques could be of use.
+
+Lastly, we note that it would be of interest to consider the possibility of applying the approach taken here to other scenarios in which one wishes to distinguish classical from non-classical behaviour based on quasi-probability representations~\cite{Ferrie_2008, barnett_1997}
 \section{Acknowledgements}
@@
 
-We now verify that the Lorenz curve is concave in the context of quasi-distributions.
+We verify that the Lorenz curve is concave in the context of quasi-distributions.
 \begin{lemma}\label{L-concave} Let $\p$ be a quasi-probability distribution and let $\r$ be a probability distribution with strictly non-zero components.
@@
 \end{lemma}
-\begin{proof} Let $f_1(x)$ be equal to $L_{\p|\r}(x)$ on $[0, x_\star]$ and and $0$ otherwise.
+\begin{proof} Let $x_\star$ be the point where $L_{\p|\r}(x)$ first attains it maximum.
+Therefore on $[0,x_\star]$ the function rises monotonically to $L_{\p|\r}(x_\star)$, via the sum of all positive entries of $\p$, taken in decreasing order.
+Likewise on $[x_\star, 1]$ the function decreases monotonically from its maximum via the partial sums of the negative entries of $\p$ in decreasing order.
+Let $f_1(x)$ be equal to $L_{\p|\r}(x)$ on $[0, x_\star]$ and $0$ otherwise.
 Also let $f_2(x)$ be equal to $L_{\p|\r}(x)$ on $[x_\star,1]$ and and $0$ otherwise.
@@
 	\end{equation}
-	and is achieved at
-	\begin{equation}\label{eq:maxloc}
-		x_{i_\star} \coloneqq \sum_{i=1}^{i_\star} w(\sigma)_i.
-	\end{equation}
-
-	The location of the maximum ($x=x_{i_\star}$) varies from fragment to fragment, but its value is independent of $\sigma$,
+	and is achieved at $x_{i_\star} \coloneqq \sum_{i=1}^{i_\star} w(\sigma)_i$. The location of this maximum varies from fragment to fragment, but its value is independent of $\sigma$,
 	\begin{align}
@@
 
+We note that we may relate our analysis to the classical single-shot entropy $D_\infty (\p ||\r)$ that remains well-defined even in the case of quasi-distributions. We define 
+\begin{equation}
+D_\infty(\rho,\tau) := D_\infty(W_\rho(\x) || W_\tau (\x)) =\log  \max_{\x} \frac{W_\rho(\x)}{W_\tau(\x)}
+\end{equation}
+which is well-defined since both the nominator and denominator in the above expression are strictly positive when $\tau$ is in the interior of $\F$.
+
+In general we have $D_\infty(\rho, \tau) \ge 0$ for all $\tau$ in the interior of $\F$, and moreover $D_\infty(\rho , \tau) > 0$ for any $\rho \not \in \F$.
+We also have that $D_\infty(\tau , \tau) = 0$ and $D_\infty(\rho^{\otimes n}, \tau^{\otimes n}) = n D_\infty(\rho ,\tau)$.
+Finally we have monotonicity of the function,
+\begin{equation}
+D_\infty (\rho , \tau) \ge D_\infty (\E(\rho), \E(\tau))
+\end{equation}
+for any free operation $\E$.
+\ddd{[True?
+Can we say a bit more?]}.
+Note though that $D_\infty (\rho,\tau) = 0$ can also occur for $\rho \ne \tau$.
+It would be of interest to further explore this more abstract perspective.
+
 \subsection{Dropping pre/post-processing of the magic states}
@@
 
-\begin{theorem}
+\begin{theorem}\label{thm:no-processing}
 	Consider a magic distillation protocol on qutrits that transforms
@@
 and define a threshold error,
-\begin{equation}
+\begin{equation}\label{eq:threshold}
 	\epsilon_{\star}(\beta) \coloneqq 

### 2021-05-31 magic_paper.tex

@@
 \begin{document}
-% Labels and Refs (consistency, thm vs lem vs prop)
+% Labels and Refs (consistency, cref vs ref, thm vs lem vs prop, ??)
 % Figs check(fig.0, move to app, consistency)
 
-% Notation consistency (R is rate not bound, ket vs |> etc, \ln{} -> \ln ,??, italics)
+% Notation consistency (R is rate not bound, noise vs error, \ln{} -> \ln, italics)
 % UK vs US english
@@
 The state $\rho$ is assumed to have negativity in the Wigner representation, so $W_\rho(\x) < 0$ for some regions of $\x \in \P_d$.
-The state $\sigma$ is assumed to have a Wigner distribution with $W_\sigma(\x) > 0$ for all $\x$ in the phase space\footnote{Any non-full rank state $\sigma$ can be handled as a limiting case in which we first add an infinitesimal fraction of depolarising noise $\epsilon (\id/d)$ and then take $\epsilon \rightarrow 0$ at the end.}.
+The state $\sigma$ is assumed to have a Wigner distribution with $W_\sigma(\x) > 0$ for all $\x$ in the phase space\footnote{Any non-full rank state $\sigma$ can be handled as a limiting case in which we first add an infinitesimal fraction of depolarising noise $\epsilon (\id/d)$ and then take $\epsilon \rightarrow 0$ in the end.}.
 
@@
 \end{equation}
-where $\epsilon$ is the depolarization noise parameter.
+where $\epsilon$ is the depolarizing error parameter.
 One nice feature of this is that any magic state $\rho$ can be processed via Clifford operations~\cite{cit:prakash,cit:prakash2} and put into this canonical form for some $\epsilon \ge 0$.
@@
 \begin{equation}
-	\W[\bmx]{\rho_{\rm{S}}(\epsilon)} = (1-\epsilon)\W[\bmx]{S} + \epsilon\W[\bmx]{\frac{1}{3}\id}.
+	\W[\bmx]{\rho_{\rm{S}}(\epsilon)} = (1-\epsilon)\W[\bmx]{\rm{S}\>\<\rm{S}|} + \epsilon\W[\bmx]{\frac{1}{3}\id}.
 \end{equation}
@@
 We assume that in the asymptotic/thermodynamic limit $n,m \rightarrow \infty$ that correlations generated on the reference equilibrium state are negligible.
-This implies that $d\mu(x)$ is peaked on a particular state $\tau'$, and $\E(\tau) = \tau^{\prime \otimes m}$.
+This implies that $d\mu(x)$ is peaked on a particular state $\tau'$, and $\E(\tau) = \tau'^{\otimes m}$.
 Physically, this is a natural scenario -- for example, in the context of traditional thermodynamics, it states that the output system is well-described by intrinsic variables that do not scale in $m$, and correlations are sub-linear in $m$.
@@
 \subsection{Temperature-dependent distillation bounds}
-W can specify energetic details of a protocol through how much it would disturb some reference equilibrium state.
-The magic state transformation is then considered relative to the equilibrium transformation, and can be recast (via the Wigner representation) into a relative majorization statement $(\w, \r) \succ (\w', \r')$ where $\w, \w'$ are quasi-distributions corresponding to the magic transformation, while $\r, \r'$ correspond to the transformation of the reference equilibrium state.
+
+W \nick{what is W?} can specify energetic details of a protocol through how much it would disturb some reference equilibrium state.
+The magic state transformation is then considered relative to the equilibrium transformation, and can be recast via the Wigner representation into a relative majorization statement $(\w, \r) \succ (\w', \r')$ where $\w, \w'$ are quasi-distributions corresponding to the magic transformation, while $\r, \r'$ correspond to the transformation of the reference equilibrium state.
 
@@
 \end{align}
-and $W_\tau(\x)$ attains a minimum at $\x=\x_\star$. The primed variables are defined similarly for the output system.
+and $W_\tau(\x)$ attaining a minimum at $\x=\x_\star$. The primed variables are defined similarly for the output system.
 \end{theorem}
@@
 In particular, the term $\phi$ quantifies to what degree a sharp energy value can be ascribed to the negativity in the Wigner representation.
-Its form is similar to $F$, and so $\phi$ can informally be viewed as a `magic free energy' term.
+Its form is similar to $F$, so $\phi$ can informally be viewed as a `magic free energy' term.
 
@@
 \subsection{Core aspects of the bound}
-Similar to the unital protocol bounds, the above result is based on only part of the Lorenz curves and so can certainly be tightened with further analysis.
-However we note that the analysis makes use of a single-shot entropy $D_\infty (\p ||\r)$ that remains well-defined even for quasi-distributions (see Appendix~\ref{app:lcst_technical}).
+Similar to the unital protocol bounds, the above result is based on only part of the Lorenz curves, so it can certainly be tightened with further analysis.
+However, we note that the analysis makes use of a single-shot entropy $D_\infty (\p ||\r)$ that remains well-defined even for quasi-distributions (see Appendix~\ref{app:lcst_technical}).
 Specifically, the above bounds follow by considering $D_\infty(\rho, \tau) := D_\infty (W_\rho(\x) || W_\tau (\x))$.
 It is therefore of interest to further explore this perspective and determine what components of single-shot information theory could be extended to quasi-distributions.
+%>>>>>>> 1b7a66527324b68f2de70862988bb3d8bc759e82
 
@@
 Our bounds exploited relatively simple aspects of the Lorenz curves of the quasi-distributions, so it would be of interest to sharpen these bounds and obtain a better handle on the Lorenz curve structure in the $n\rightarrow \infty$ limit.
-This raises interesting as we no longer have a notion of typicality and the central limit theorem does not apply.
-That said, for special states such as the Strange state the asymptotic behaviour is relatively simple, so exact asymptotics for this should be possible.
+This raises interesting \nick{questions in the context of statistical mechanics} as we no longer have a notion of typicality and the central limit theorem does not apply.
+That said, for special states such as the Strange state, the asymptotic behaviour is relatively simple, so exact asymptotics for this should be possible.
 In~\cref{app:lcsu_technical} and~\cref{app:lcst_technical} we give additional results that may be of use for later work.
@@
 \end{lemma}
-\begin{proof} Let $x_\star$ be the point where $L_{\p|\r}(x)$ first attains it maximum.
-Therefore on $[0,x_\star]$ the function rises monotonically to $L_{\p|\r}(x_\star)$, via the sum of all positive entries of $\p$, taken in decreasing order.
-Likewise on $[x_\star, 1]$ the function decreases monotonically from its maximum via the partial sums of the negative entries of $\p$ in decreasing order.
+\begin{proof} 
+Let $x_\star$ be the point where $L_{\p|\r}(x)$ first attains it maximum.
+Therefore, on $[0,x_\star]$ the function rises monotonically to $L_{\p|\r}(x_\star)$, via the sum of all positive entries of $\p$, taken in decreasing order.
+Likewise on $[x_\star, 1]$, the function decreases monotonically from its maximum via the partial sums of the negative entries of $\p$ in decreasing order.
 Let $f_1(x)$ be equal to $L_{\p|\r}(x)$ on $[0, x_\star]$ and $0$ otherwise.
@@
 By inspection both $f_1$ and $f_2$ are concave functions, and $f_1(x) + f_2 (x) = L_{\p|\r}(x)$ for all $x\in [0,1]$.
-However the sum of two concave functions is also concave and so the result follows.
+However, the sum of two concave functions is also concave and the result follows.
 \end{proof}
@@
 
-In general we have $D_\infty(\rho, \tau) \ge 0$ for all $\tau$ in the interior of $\F$, and moreover $D_\infty(\rho , \tau) > 0$ for any $\rho \not \in \F$.
+In general, we have $D_\infty(\rho, \tau) \ge 0$ for all $\tau$ in the interior of $\F$, and moreover $D_\infty(\rho , \tau) > 0$ for any $\rho \not \in \F$.
 We also have that $D_\infty(\tau , \tau) = 0$ and $D_\infty(\rho^{\otimes n}, \tau^{\otimes n}) = n D_\infty(\rho ,\tau)$.
-Finally we have monotonicity of the function,
+Finally, we have monotonicity of the function,
 \begin{equation}

### 2021-05-31 magic_paper.tex
Added lots of valuable stuff via the single-shot realisation. Calcs to be checked though. Will keep this contained.

--- 2021-05-30 magic_paper.tex
@@
 
-\subsection{Core aspects of the bound}
+\subsection{Technical aspects of the bound}
 Similar to the unital protocol bounds, the above result is based on only part of the Lorenz curves and so can certainly be tightened with further analysis.
-However we note that the analysis makes use of a single-shot entropy $D_\infty (\p ||\r)$ that remains well-defined even for quasi-distributions (see Appendix~\ref{app:lcst_technical}).
-Specifically, the above bounds follow by considering $D_\infty(\rho, \tau) := D_\infty (W_\rho(\x) || W_\tau (\x))$.
-It is therefore of interest to further explore this perspective and determine what components of single-shot information theory could be extended to quasi-distributions.
 
@@
 \end{figure}
+
+\newpage
+\subsection{Single-shot divergences for quasi-distributions}
+As already mentioned, the Wigner distribution is generally a quasi-distribution and so taking the Shannon entropy $H(\p) = -\sum_i p_i \log p_i$ of the Wigner distribution is not possible off of the set $\F$.
+However, does the same obstacle applies to Renyi entropies?
+The $\alpha$--Renyi entropy $H_\alpha(\p)$ is defined as
+\begin{equation}
+H_\alpha(\p) := -\frac{1}{\alpha -1} \log \sum_i p_i^\alpha,
+\end{equation}
+where $\alpha \ge 0$ and $\lim_{\alpha \rightarrow 1} H_\alpha(\p) = H(\p)$.
+It is clear that if we take $\alpha$ to be an even integer then $H_\alpha (W_\rho(\x))$ is always a well-defined function on Wigner quasi-distributions.
+However it still remains to link such expressions to majorization of quasi-distributions.
+
+In this direction we first note that the analysis for the temperature-dependent bound given by Equation (\ref{eq:rate_bounds_proof}) implicitly makes use of the single-shot Renyi divergence $D_\infty (\p ||\r)$, which is given by
+\begin{equation}
+D_\infty (\p ||\r) = \log \max_i \frac{p_i}{r_i}.
+\end{equation}
+This motivates defining the following \emph{Wigner divergence} $D_\infty(\rho, \tau) := D_\infty (W_\rho(\x) || W_\tau (\x))$ on all quantum states.
+In Appendix~\ref{app:lcst_technical}, we show that this divergence has the following natural properties that are derived via relative majorization.
+\begin{theorem} Let $\tau$ be in the interior of $\F$, and define the Wigner divergence $D_\infty(\rho,\tau) := D_\infty(W_\rho(\x) || W_\tau (\x))$.
+Then $D_\infty(\rho, \tau)$ is well-defined for all $\rho$, and the following hold:
+\begin{enumerate}
+\item $D_\infty(\rho, \tau) \ge 0$ for all quantum states $\rho$.
+\item  $D_\infty(\rho , \tau) = 0$ if and only if $\rho =\tau$.
+\item $D_\infty(\rho^{\otimes 2n}, \tau^{\otimes 2n}) = n D_\infty(\rho^{\otimes 2} ,\tau^{\otimes 2})$ for any $n \in \mathbb{N}$.
+\item For any quantum state $\rho$, and any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$, we have $D_\infty (\rho , \tau) \ge D_\infty (\E(\rho), \E(\tau))$.
+\end{enumerate}
+\end{theorem}
+See Appendix~\ref{app:lcst_technical} for the proof of this.
+Moreover, in the appendices we also prove that for unital processes the Renyi entropies $H_{2m}(\w)$ are monotones for any $m \in \mathbb{N}$ and lead the generalized distillation bounds.
+\begin{equation}
+R \le \frac{H_{2m}(\rho)}{H_{2m}(\rho')}.
+\end{equation}
+It is of interest to further explore this perspective and determine what components of single-shot information theory could be extended to quasi-distributions.
 
@@
 Then the magic distillation rate $R = m/n$ for the protocol is bounded by the expression
-\begin{equation}\label{eq:rate_bounds_proof}
+\begin{equation}
 	R \leq \dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (\phi - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (\phi' - F')},
@@
 \end{align}
+
 \end{proof}
@@
 
-In general we have $D_\infty(\rho, \tau) \ge 0$ for all $\tau$ in the interior of $\F$, and moreover $D_\infty(\rho , \tau) > 0$ for any $\rho \not \in \F$.
-We also have that $D_\infty(\tau , \tau) = 0$ and $D_\infty(\rho^{\otimes n}, \tau^{\otimes n}) = n D_\infty(\rho ,\tau)$.
-Finally we have monotonicity of the function,
-\begin{equation}
-D_\infty (\rho , \tau) \ge D_\infty (\E(\rho), \E(\tau))
-\end{equation}
-for any free operation $\E$.
-\ddd{[True?
-Can we say a bit more?]}.
-Note though that $D_\infty (\rho,\tau) = 0$ can also occur for $\rho \ne \tau$.
-It would be of interest to further explore this more abstract perspective.
-
+\begin{theorem} Let $\tau$ be in the interior of $\F$, and define $D_\infty(\rho,\tau) := D_\infty(W_\rho(\x) || W_\tau (\x))$.
+Then $D_\infty(\rho, \tau)$ is well-defined for all $\rho$, and the following hold:
+\begin{enumerate}
+\item $D_\infty(\rho, \tau) \ge 0$ for all quantum states $\rho$.
+\item  $D_\infty(\rho , \tau) = 0$ if and only if $\rho =\tau$.
+\item $D_\infty(\rho^{\otimes 2n}, \tau^{\otimes 2n}) = n D_\infty(\rho^{\otimes 2} ,\tau^{\otimes 2})$ for any $n \in \mathbb{N}$.
+\item For any quantum state $\rho$, and any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$, we have $D_\infty (\rho , \tau) \ge D_\infty (\E(\rho), \E(\tau))$.
+\end{enumerate}
+\end{theorem}
+\begin{proof}Since $\tau$ is in the interior of $\F$ its Wigner function obeys $W_\tau(\x) >0$ for all points $\x$ in the phase space.
+In general $W_\rho(\x)$ is a quasi-distribution, however since $\sum_{\x} W_\rho (\x) = 1$ this implies it must have at least one positive component and so $\max_{\x} \frac{W_\rho(\x)}{W_\tau(\x)}>0$.
+Therefore $D_\infty (\rho,\tau)$ is always well-defined.
+
+1. We have that 
+\begin{equation}
+D_\infty(W_\rho(\x) || W_\tau (\x)) =\log  \max_{\x} \frac{W_\rho(\x)}{W_\tau(\x)},
+\end{equation}
+and therefore $2^{D_\infty(\rho,\tau)}$ equals the slope of the Lorenz curve $L_{\rho|\tau}(x)$ at $x=0$.
+Since $L_{\rho|\tau}(x)$ is a concave function passing through $(0,0)$ and $(1,1)$ this implies that $L_{\rho |\tau}(x) \ge x$ for all $x \in [0,1]$, and in particular its slope at $x=0$ is always greater than or equal to $1$, which implies $D_\infty (\rho,\tau) \ge 0$ for all $\rho$.
+
+2.
+If $D_\infty (\rho,\tau) = 0$ this implies that $\max_{\x} \frac{W_\rho(\x)}{W_\tau(\x)}=1$ and the initial slope of $L_{\rho|\tau}(x)$ is $1$.
+From the concavity of the function this implies that the slope of $L_{\rho|\tau}(x)$ must equal $1$ throughout the interval $[0,1]$ and this, together with the definition of the Lorenz curve, implies that $\frac{W_\rho(\x)}{W_\tau(\x)}=1$ for all $\x$.
+Since the Wigner representation $\rho \mapsto W_\rho(\x)$ is bijective this implies that $\rho = \tau$ only.
+The converse holds by inspection.
+
+3. Given a vector $\w \in \mathbb{R}^N$ in general it is the case that
+\begin{equation}
+\max_k w_k \ne \max_k |w_k|.
+\end{equation}
+However we do have that
+\begin{equation}
+\max_{k_1,k_2} (w_{k_1} w_{k_2}) = \max_k |w_k|^2 = \max_k w_k^2.
+\end{equation}
+If $\w \in \mathbb{R}^N$ with $w_k \ge 0$ for all $k$ then
+\begin{equation}
+\max_{k_1, k_2, \dots, k_n} [ w_{k_1}w_{k_2}\cdots w_{k_n}] = (\max_k w_k)^n,
+\end{equation}
+and therefore for arbitrary $\w \in \mathbb{R}^N$ and $n$, we have
+\begin{align}
+\hspace{-1.8cm}\max_{k_1, k_2, \dots, k_{2n}} [ w_{k_1}w_{k_2}\cdots w_{k_{2n}}] &\le \max_{k_1, k_2, \dots, k_{2n}}[|w_{k_1}w_{k_2}|\cdots |w_{k_{2n-1}} w_{k_{2n}}|] \nonumber \\
+&=(\max_{k_1 ,k_2} |w_{k_1} w_{k_2}| )^n \nonumber \\
+&\le\max_{k_1, k_2, \dots, k_{2n}} [ w_{k_1}w_{k_2}\cdots w_{k_{2n}}]  .
+\end{align}
+and so we have that in general
+\begin{equation}
+\max_{k_1, k_2, \dots, k_{2n}} [ w_{k_1}w_{k_2}\cdots w_{k_{2n}}]  =  (\max_{k_1 ,k_2} [w_{k_1} w_{k_2}] )^n.
+\end{equation}
+If we now let $\w = W_{\rho|\tau}(\x) := W_{\rho}(\x) /W_{\tau}(\x)$ we have
+\begin{equation}
+\max_{\x_1, \x_2, \dots ,\x_{2n}} \prod_{k=1}^{2n} W_{\rho|\tau}(\x_k) = (\max_{\x_1, \x_2} W_{\rho|\tau}(\x_1)W_{\rho|\tau}(\x_2))^n
+\end{equation}
+and therefore taking logarithms we have that $D_\infty (\rho^{\otimes 2n}, \tau^{\otimes 2n}) = n D_\infty(\rho^{\otimes 2} ,\tau^{\otimes 2})$ as required. \ddd{[Check details for any fine print.]}
+
+4.
+The free operation $\E$ in the Wigner representation corresponds to a stochastic map, which sends $W_\tau(\x)$ to $W_{\E(\tau)}(\x)$, which is another strictly positive probability distribution on the phase space, due to $\E(\tau)$ being in the interior of $\F$.
+Moreover, $(W_\rho(\x), W_\tau(\x) ) \succ (W_{\E(\rho)}(\x) , W_{\E(\tau)}(\x))$.
+As shown in the main text this condition holds if and only if $L_{\rho|\tau}(x) \ge L_{\E(\rho)|\E(\tau)}(x)$ for all $x$.
+In particular, this implies the slope at the origin of the input curve is never less than the slope at the origin of the output curve, and hence the result follows.
+\end{proof}
+
+\newpage
+
+\subsection{Schur-Convexity and quasi-distributions}
+We now make use of known results from majorization theory. We first define \emph{Schur-convex functions} on a subset $\D \subseteq \mathbb{R}^N$.
+
+\begin{definition} A continuous, real-valued function $f$ defined on $\D \subseteq \mathbb{R}^N$ is called Schur-convex on the domain $\D$ if $\p \prec \q$ on $\D$ implies that $f(\p) \le f(\q)$.
+A continuous function $f:\D \rightarrow \mathbb{R}$ is called Schur-concave if $(-f)$ is Schur-convex.
+\end{definition}
+We now can consider the set of all quasi-distributions, which form a hyper-plane and are given by
+\begin{equation}
+\D = \{ \w \in \mathbb{R}^N: \sum_i w_i = 1\}.
+\end{equation}
+For functions that are symmetric, namely $f(\p) = f(\Pi \p)$ for any permutation $\Pi$ of the components, it suffices to restrict to the following region,
+\begin{equation}
+\D^\downarrow = \{ \w \in \D : w_1 \ge w_2 \ge \cdots \ge w_N\}.
+\end{equation}
+
+We now have the following theorem [CITE Marshall+Olkin] that provides a characterization of symmetric, Schur-convex functions on quasi-distributions.
+\begin{theorem} Let $f$ be a real-valued continuous function defined on $\D^\downarrow$ that is continuously differentiable on the interior of $\D^\downarrow$.
+Then $f$ is Schur-convex on $\D^\downarrow$ if and only if $\partial_k f(\w)$ is decreasing in $k$ for all $\w \in \D^\downarrow$, namely
+\begin{equation}
+\partial_1 f(\w) \ge \partial_2 f(\w) \ge \cdots \ge \partial_N f(\w),
+\end{equation}
+for all $\w$ in the interior of $\D^\downarrow$.
+\end{theorem}
+
+\ddd{[TO-DO AND TIDY AND CHECK]} Okay great...this looks easy to do, we just need to compute the terms
+\begin{equation}
+-\frac{\partial H_\alpha}{\partial w_k} (w_1, w_2, \dots, w_N),
+\end{equation}
+for Renyi entropies (which are symmetric), and look to see when the above inequality holds. 
+We assume $ \alpha=2m$ is an even integer, so that $H_\alpha (\w)$ is well-defined on quasi-distributions. We then have that
+\begin{align}
+V_k:=-\frac{\partial H_\alpha}{\partial w_k} &= \partial_k \frac{1}{\alpha-1} \log \sum_i w_i^{2m} \\
+&= \frac{1}{(2m-1) \sum_i w_i^{2m}}2mw_k^{2m-1}.
+\end{align}
+We now impose the monotonicity condition $V_1 \ge V_2 \ge V_3 \cdots \ge V_N$. This requires, setting $S= \sum_i w_i^{2m}$ for simplicity, that
+\begin{align}
+ \frac{1}{(2m-1)S}2mw_i^{2m-1}\ge \frac{1}{(2m-1)S}2mw_{i+1}^{2m-1},
+\end{align}
+for each $i=1,2,\dots, N-1$. We assume that $m >0$ and $2m \ne 1$ and so this becomes
+\begin{equation}
+w_i^{2m-1}\ge w_{i+1}^{2m-1}\mbox{ for all } 1 \le i < N.
+\end{equation}
+For $2m >1$ this condition holds whenever $w_i \ge w_{i+1}$, which is true in $\D^\downarrow$.
+Therefore $-H_{2m}(\w)$ is Schur-Convex on quasi-distributions for any integer $m\in \mathbb{N}$.
+This implies it is a monotone function for majorization, namely,
+\begin{equation}
+\w \succ \w' \mbox{ implies } H_{2m} (\w) \le H_{2m} (\w') \mbox{for any } m \in \mathbb{N}.
+\end{equation}
+This therefore should give \emph{additional} distillation bounds in the unital fragment. We'd need to check additivity is okay, but this should be fine. Therefore
+\begin{equation}
+W_{\rho_n}(\x) \succ W_{\rho'_m}(\x) \mbox{ implies } n H_{2m}(\rho) \le m H_{2m}(\rho'). 
+\end{equation}
+(Some sign error here? Should get:)
+\begin{equation}
+R \le \frac{H_{2m}(\rho)}{H_{2m}(\rho')}.
+\end{equation}
+\ddd{[Plan: check all these calculations! Give the generalised unital bound. Then we just conjecture this extends to Renyi-divergences and leave it at this.]}
 \subsection{Dropping pre/post-processing of the magic states}
@@
 Then, the distillation rate $R = m/n$ of the magic protocol is bounded as:
-\begin{equation}\label{eq:rate_bounds_proof}
+\begin{equation}
 	R \leq

### 2021-05-31 magic_paper.tex
Merge details resolved.

--- 2021-05-31 magic_paper.tex
@@
 
-\subsection{Core aspects of the bound}
-Similar to the unital protocol bounds, the above result is based on only part of the Lorenz curves, so it can certainly be tightened with further analysis.
-However, we note that the analysis makes use of a single-shot entropy $D_\infty (\p ||\r)$ that remains well-defined even for quasi-distributions (see Appendix~\ref{app:lcst_technical}).
-Specifically, the above bounds follow by considering $D_\infty(\rho, \tau) := D_\infty (W_\rho(\x) || W_\tau (\x))$.
-It is therefore of interest to further explore this perspective and determine what components of single-shot information theory could be extended to quasi-distributions.
-%>>>>>>> 1b7a66527324b68f2de70862988bb3d8bc759e82
-
+\subsection{Technical aspects of the bound}
+Similar to the unital protocol bounds, the above result is based on only part of the Lorenz curves and so can certainly be tightened with further analysis.
 The primary role of the pre/post-processing by Clifford unitaries in~\cref{thm:free-energy} is to simplify the form of the bound, and allow it to be expressed in terms of the free energy per particle in a way that does not depend on the parameters $\epsilon, \epsilon', \beta$ in a complex form.
@@
 \begin{equation}
-D_\infty(\rho,\tau) := D_\infty(W_\rho(\x) || W_\tau (\x)) =\log  \max_{\x} \frac{W_\rho(\x)}{W_\tau(\x)}
+\hspace{-1cm}D_\infty(\rho,\tau) := D_\infty(W_\rho(\x) || W_\tau (\x)) =\log  \max_{\x} \frac{W_\rho(\x)}{W_\tau(\x)}\nonumber
 \end{equation}
@@
 
-In general, we have $D_\infty(\rho, \tau) \ge 0$ for all $\tau$ in the interior of $\F$, and moreover $D_\infty(\rho , \tau) > 0$ for any $\rho \not \in \F$.
-We also have that $D_\infty(\tau , \tau) = 0$ and $D_\infty(\rho^{\otimes n}, \tau^{\otimes n}) = n D_\infty(\rho ,\tau)$.
-Finally, we have monotonicity of the function,
-\begin{equation}
-D_\infty (\rho , \tau) \ge D_\infty (\E(\rho), \E(\tau))
-\end{equation}
-for any free operation $\E$.
-\ddd{[True?
-Can we say a bit more?]}.
-Note though that $D_\infty (\rho,\tau) = 0$ can also occur for $\rho \ne \tau$.
-It would be of interest to further explore this more abstract perspective.
-
+\begin{theorem} Let $\tau$ be in the interior of $\F$, and define $D_\infty(\rho,\tau) := D_\infty(W_\rho(\x) || W_\tau (\x))$.
+Then $D_\infty(\rho, \tau)$ is well-defined for all $\rho$, and the following hold:
+\begin{enumerate}
+\item $D_\infty(\rho, \tau) \ge 0$ for all quantum states $\rho$.
+\item  $D_\infty(\rho , \tau) = 0$ if and only if $\rho =\tau$.
+\item $D_\infty(\rho^{\otimes 2n}, \tau^{\otimes 2n}) = n D_\infty(\rho^{\otimes 2} ,\tau^{\otimes 2})$ for any $n \in \mathbb{N}$.
+\item For any quantum state $\rho$, and any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$, we have $D_\infty (\rho , \tau) \ge D_\infty (\E(\rho), \E(\tau))$.
+\end{enumerate}
+\end{theorem}
+\begin{proof}Since $\tau$ is in the interior of $\F$ its Wigner function obeys $W_\tau(\x) >0$ for all points $\x$ in the phase space.
+In general $W_\rho(\x)$ is a quasi-distribution, however since $\sum_{\x} W_\rho (\x) = 1$ this implies it must have at least one positive component and so $\max_{\x} \frac{W_\rho(\x)}{W_\tau(\x)}>0$.
+Therefore $D_\infty (\rho,\tau)$ is always well-defined.
+
+1. We have that 
+\begin{equation}
+D_\infty(W_\rho(\x) || W_\tau (\x)) =\log  \max_{\x} \frac{W_\rho(\x)}{W_\tau(\x)},
+\end{equation}
+and therefore $2^{D_\infty(\rho,\tau)}$ equals the slope of the Lorenz curve $L_{\rho|\tau}(x)$ at $x=0$.
+Since $L_{\rho|\tau}(x)$ is a concave function passing through $(0,0)$ and $(1,1)$ this implies that $L_{\rho |\tau}(x) \ge x$ for all $x \in [0,1]$, and in particular its slope at $x=0$ is always greater than or equal to $1$, which implies $D_\infty (\rho,\tau) \ge 0$ for all $\rho$.
+
+2.
+If $D_\infty (\rho,\tau) = 0$ this implies that $\max_{\x} \frac{W_\rho(\x)}{W_\tau(\x)}=1$ and the initial slope of $L_{\rho|\tau}(x)$ is $1$.
+From the concavity of the function this implies that the slope of $L_{\rho|\tau}(x)$ must equal $1$ throughout the interval $[0,1]$ and this, together with the definition of the Lorenz curve, implies that $\frac{W_\rho(\x)}{W_\tau(\x)}=1$ for all $\x$.
+Since the Wigner representation $\rho \mapsto W_\rho(\x)$ is bijective this implies that $\rho = \tau$ only.
+The converse holds by inspection.
+
+3. Given a vector $\w \in \mathbb{R}^N$ in general it is the case that
+\begin{equation}
+\max_k w_k \ne \max_k |w_k|.
+\end{equation}
+However we do have that
+\begin{equation}
+\max_{k_1,k_2} (w_{k_1} w_{k_2}) = \max_k |w_k|^2 = \max_k w_k^2.
+\end{equation}
+If $\w \in \mathbb{R}^N$ with $w_k \ge 0$ for all $k$ then
+\begin{equation}
+\max_{k_1, k_2, \dots, k_n} [ w_{k_1}w_{k_2}\cdots w_{k_n}] = (\max_k w_k)^n,
+\end{equation}
+and therefore for arbitrary $\w \in \mathbb{R}^N$ and $n$, we have
+\begin{align}
+\hspace{-1cm}\max_{k_1, k_2, \dots, k_{2n}} [ w_{k_1}w_{k_2}\cdots w_{k_{2n}}] &\le \max_{k_1, k_2, \dots, k_{2n}}[|w_{k_1}w_{k_2}|\cdots |w_{k_{2n-1}} w_{k_{2n}}|] \nonumber \\
+&=(\max_{k_1 ,k_2} |w_{k_1} w_{k_2}| )^n \nonumber \\
+&\le\max_{k_1, k_2, \dots, k_{2n}} [ w_{k_1}w_{k_2}\cdots w_{k_{2n}}]  .
+\end{align}
+and so we have that in general
+\begin{equation}
+\max_{k_1, k_2, \dots, k_{2n}} [ w_{k_1}w_{k_2}\cdots w_{k_{2n}}]  =  (\max_{k_1 ,k_2} [w_{k_1} w_{k_2}] )^n.
+\end{equation}
+If we now let $\w = W_{\rho|\tau}(\x) := W_{\rho}(\x) /W_{\tau}(\x)$ we have
+\begin{equation}
+\max_{\x_1, \x_2, \dots ,\x_{2n}} \prod_{k=1}^{2n} W_{\rho|\tau}(\x_k) = (\max_{\x_1, \x_2} W_{\rho|\tau}(\x_1)W_{\rho|\tau}(\x_2))^n
+\end{equation}
+and therefore taking logarithms we have that $D_\infty (\rho^{\otimes 2n}, \tau^{\otimes 2n}) = n D_\infty(\rho^{\otimes 2} ,\tau^{\otimes 2})$ as required. \ddd{[Check details for any fine print.]}
+
+4.
+The free operation $\E$ in the Wigner representation corresponds to a stochastic map, which sends $W_\tau(\x)$ to $W_{\E(\tau)}(\x)$, which is another strictly positive probability distribution on the phase space, due to $\E(\tau)$ being in the interior of $\F$.
+Moreover, $(W_\rho(\x), W_\tau(\x) ) \succ (W_{\E(\rho)}(\x) , W_{\E(\tau)}(\x))$.
+As shown in the main text this condition holds if and only if $L_{\rho|\tau}(x) \ge L_{\E(\rho)|\E(\tau)}(x)$ for all $x$.
+In particular, this implies the slope at the origin of the input curve is never less than the slope at the origin of the output curve, and hence the result follows.
+\end{proof}
+
+\newpage
+
+\subsection{Schur-Convexity and quasi-distributions}
+We now make use of known results from majorization theory. We first define \emph{Schur-convex functions} on a subset $\D \subseteq \mathbb{R}^N$.
+
+\begin{definition} A continuous, real-valued function $f$ defined on $\D \subseteq \mathbb{R}^N$ is called Schur-convex on the domain $\D$ if $\p \prec \q$ on $\D$ implies that $f(\p) \le f(\q)$.
+A continuous function $f:\D \rightarrow \mathbb{R}$ is called Schur-concave if $(-f)$ is Schur-convex.
+\end{definition}
+We now can consider the set of all quasi-distributions, which form a hyper-plane and are given by
+\begin{equation}
+\D = \{ \w \in \mathbb{R}^N: \sum_i w_i = 1\}.
+\end{equation}
+For functions that are symmetric, namely $f(\p) = f(\Pi \p)$ for any permutation $\Pi$ of the components, it suffices to restrict to the following region,
+
+\begin{equation}
+\D^\downarrow = \{ \w \in \D : w_1 \ge w_2 \ge \cdots \ge w_N\}.
+\end{equation}
+
+We now have the following theorem [CITE Marshall+Olkin] that provides a characterization of symmetric, Schur-convex functions on quasi-distributions.
+\begin{theorem} Let $f$ be a real-valued continuous function defined on $\D^\downarrow$ that is continuously differentiable on the interior of $\D^\downarrow$.
+Then $f$ is Schur-convex on $\D^\downarrow$ if and only if $\partial_k f(\w)$ is decreasing in $k$ for all $\w \in \D^\downarrow$, namely
+\begin{equation}
+\partial_1 f(\w) \ge \partial_2 f(\w) \ge \cdots \ge \partial_N f(\w),
+\end{equation}
+for all $\w$ in the interior of $\D^\downarrow$.
+\end{theorem}
+
+\ddd{[TO-DO AND TIDY AND CHECK]} Okay great...this looks easy to do, we just need to compute the terms
+\begin{equation}
+-\frac{\partial H_\alpha}{\partial w_k} (w_1, w_2, \dots, w_N),
+\end{equation}
+for Renyi entropies (which are symmetric), and look to see when the above inequality holds. 
+We assume $ \alpha=2m$ is an even integer, so that $H_\alpha (\w)$ is well-defined on quasi-distributions. We then have that
+\begin{align}
+V_k:=-\frac{\partial H_\alpha}{\partial w_k} &= \partial_k \frac{1}{\alpha-1} \log \sum_i w_i^{2m} \\
+&= \frac{1}{(2m-1) \sum_i w_i^{2m}}2mw_k^{2m-1}.
+\end{align}
+We now impose the monotonicity condition $V_1 \ge V_2 \ge V_3 \cdots \ge V_N$. This requires, setting $S= \sum_i w_i^{2m}$ for simplicity, that
+\begin{align}
+ \frac{1}{(2m-1)S}2mw_i^{2m-1}\ge \frac{1}{(2m-1)S}2mw_{i+1}^{2m-1},
+\end{align}
+for each $i=1,2,\dots, N-1$. We assume that $m >0$ and $2m \ne 1$ and so this becomes
+\begin{equation}
+w_i^{2m-1}\ge w_{i+1}^{2m-1}\mbox{ for all } 1 \le i < N.
+\end{equation}
+For $2m >1$ this condition holds whenever $w_i \ge w_{i+1}$, which is true in $\D^\downarrow$.
+Therefore $-H_{2m}(\w)$ is Schur-Convex on quasi-distributions for any integer $m\in \mathbb{N}$.
+This implies it is a monotone function for majorization, namely,
+\begin{equation}
+\w \succ \w' \mbox{ implies } H_{2m} (\w) \le H_{2m} (\w') \mbox{for any } m \in \mathbb{N}.
+\end{equation}
+This therefore should give \emph{additional} distillation bounds in the unital fragment. We'd need to check additivity is okay, but this should be fine. Therefore
+\begin{equation}
+W_{\rho_n}(\x) \succ W_{\rho'_m}(\x) \mbox{ implies } n H_{2m}(\rho) \le m H_{2m}(\rho'). 
+\end{equation}
+(Some sign error here? Should get:)
+\begin{equation}
+R \le \frac{H_{2m}(\rho)}{H_{2m}(\rho')}.
+\end{equation}
+\ddd{[Plan: check all these calculations! Give the generalised unital bound. Then we just conjecture this extends to Renyi-divergences and leave it at this.]}
 \subsection{Dropping pre/post-processing of the magic states}

### 2021-06-01 magic_paper.tex
added refs and lemma on additivity of H. Will continue shortly

@@
 \label{sec:intro}
+
+\nick{Bunch of refs:}~\cite{White_2021, Rethinasamy_2020, Blackwell_1953, Sarkar_2020, Gour_2020}
+
 The past few years have seen rapid progress towards the goal of a fault-tolerant quantum computer~\cite{Nickerson_2014, Nikahd_2017, chao_2018, lin_pieceable_2020, Lin_2020, Bourassa_2021}.
@@
 As already mentioned, the Wigner distribution is generally a quasi-distribution and so taking the Shannon entropy $H(\p) = -\sum_i p_i \log p_i$ of the Wigner distribution is not possible off of the set $\F$.
-However, does the same obstacle applies to Renyi entropies?
+However, does the same obstacle apply to Renyi entropies?
 The $\alpha$--Renyi entropy $H_\alpha(\p)$ is defined as
 \begin{equation}
-H_\alpha(\p) := -\frac{1}{\alpha -1} \log \sum_i p_i^\alpha,
+	H_\alpha(\p) := \frac{1}{1-\alpha} \log \sum_i p_i^\alpha,
 \end{equation}
 where $\alpha \ge 0$ and $\lim_{\alpha \rightarrow 1} H_\alpha(\p) = H(\p)$.
-It is clear that if we take $\alpha$ to be an even integer then $H_\alpha (W_\rho(\x))$ is always a well-defined function on Wigner quasi-distributions.
-However it still remains to link such expressions to majorization of quasi-distributions.
-
-In this direction we first note that the analysis for the temperature-dependent bound given by Equation (\ref{eq:rate_bounds_proof}) implicitly makes use of the single-shot Renyi divergence $D_\infty (\p ||\r)$, which is given by
+It is clear that if we take $\alpha = 2m$ to be an even integer then $H_{2m}(\rho) := H_{2m}(W_\rho(\x))$ is always a well-defined function on Wigner quasi-distributions.
+However, it still remains to link such expressions to majorization of quasi-distributions.
+
+In this direction, we first note that the analysis for the temperature-dependent bound given by Equation (\ref{eq:rate_bounds_proof}) implicitly makes use of the single-shot Renyi divergence $D_\infty (\p ||\r)$, which is given by
 \begin{equation}
@@
 \end{theorem}
-\begin{proof}Since $\tau$ is in the interior of $\F$ its Wigner function obeys $W_\tau(\x) >0$ for all points $\x$ in the phase space.
-In general $W_\rho(\x)$ is a quasi-distribution, however since $\sum_{\x} W_\rho (\x) = 1$ this implies it must have at least one positive component and so $\max_{\x} \frac{W_\rho(\x)}{W_\tau(\x)}>0$.
+\begin{proof}
+	Since $\tau$ is in the interior of $\F$, its Wigner function obeys $W_\tau(\x) >0$ for all points $\x$ in the phase space.
+In general, $W_\rho(\x)$ is a quasi-distribution, however since $\sum_{\x} W_\rho (\x) = 1$ this implies it must have at least one positive component, so $\max_{\x} \frac{W_\rho(\x)}{W_\tau(\x)}>0$.
 Therefore $D_\infty (\rho,\tau)$ is always well-defined.
@@
 \end{equation}
-For functions that are symmetric, namely $f(\p) = f(\Pi \p)$ for any permutation $\Pi$ of the components, it suffices to restrict to the following region,
+For functions that are symmetric, namely $f(\p) = f(\Pi \p)$ for any component permutation $\Pi$, it suffices to restrict to the following region,
 
@@
 
-We now have the following theorem [CITE Marshall+Olkin] that provides a characterization of symmetric, Schur-convex functions on quasi-distributions.
+We now have the following theorem~\cite{cit:marshall} that provides a characterization of symmetric, Schur-convex functions on quasi-distributions.
 \begin{theorem} Let $f$ be a real-valued continuous function defined on $\D^\downarrow$ that is continuously differentiable on the interior of $\D^\downarrow$.
@@
 
+\begin{lemma}[Additivity of $H_{2m}$]\label{H_add}
+	For any states $\rho, \rho'$ and non-negative $m$, we have
+	\begin{equation}
+		H_{2m}(\rho \otimes \rho') = H_{2m}(\rho) + H_{2m}(\rho')
+	\end{equation}
+\end{lemma}
+\begin{proof}
+	This can be seen directly by the multiplicative property of the Wigner distribution,
+	\begin{align*}
+		H_{2m}&(\rho \otimes \rho') = \frac{1}{1-2m}\log \sum_{\bmx,\bmx'} \left[W_{\rho}(\bmx)W_{\rho}(\bmx')\right]^{2m} \\
+		&= \frac{1}{1-2m}\left( \log \sum_{\bmx}W_{\rho}(\bmx)^{2m} + \log \sum_{\bmx'}W_{\rho}(\bmx')^{2m} \right) \\
+		&= H_{2m}(\rho) + H_{2m}(\rho').
+	\end{align*}
+\end{proof}
+\cref{H_add} implies that for any $n$,
+\begin{equation}
+	H_{2m}(\rho_n) := H_{2m}(\rho^{\otimes n}) = n H_{2m}(\rho).
+\end{equation}
+
+Using the above results, we can show that $H_{2m}$ is Schur-concave for all quasi-distributions.
+In particular, for any non-negative integer $m$, we have that
+\begin{equation}
+	W_{\rho_n}(\bmx) \succ W_{\rho'_{n'}}(\bmx) \mbox{ implies } H_{2m}(\rho_n) \leq H_{2m}(\rho'_{n'}).
+\end{equation}
+By additivity of $H_{2m}$, we get $n H_{2m}(\rho) \leq n' H_{2m}(\rho')$, or equivalently,
+\begin{equation}
+	\frac{n'}{n} \geq \frac{H_{2m}(\rho)}{H_{2m}(\rho')}.
+\end{equation}
+
+\nick{Wrong way? I don't think that $m \rightarrow \infty$ leads to our bound}
+
 \ddd{[TO-DO AND TIDY AND CHECK]} Okay great...this looks easy to do, we just need to compute the terms
 \begin{equation}
--\frac{\partial H_\alpha}{\partial w_k} (w_1, w_2, \dots, w_N),
+	\frac{\partial H_\alpha}{\partial w_k} (w_1, w_2, \dots, w_N),
 \end{equation}

### 2021-06-02 magic_paper.tex
Wrote basic proof of bounds, left comment on how to extend. Checked D_\infty

@@
 2.
-If $D_\infty (\rho,\tau) = 0$ this implies that $\max_{\x} \frac{W_\rho(\x)}{W_\tau(\x)}=1$ and the initial slope of $L_{\rho|\tau}(x)$ is $1$.
-From the concavity of the function this implies that the slope of $L_{\rho|\tau}(x)$ must equal $1$ throughout the interval $[0,1]$ and this, together with the definition of the Lorenz curve, implies that $\frac{W_\rho(\x)}{W_\tau(\x)}=1$ for all $\x$.
+$D_\infty (\rho,\tau) = 0$ implies that $\max_{\x} \frac{W_\rho(\x)}{W_\tau(\x)}=1$ and the initial slope of $L_{\rho|\tau}(x)$ is $1$.
+From the concavity of the function this implies that the slope of $L_{\rho|\tau}(x)$ must equal $1$ throughout the interval $[0,1]$ and this, together with the definition of the Lorenz curve, implies that $W_\rho(\x)/W_\tau(\x) = 1$ for all $\x$.
 Since the Wigner representation $\rho \mapsto W_\rho(\x)$ is bijective this implies that $\rho = \tau$ only.
@@
 
-3. Given a vector $\w \in \mathbb{R}^N$ in general it is the case that
-\begin{equation}
-\max_k w_k \ne \max_k |w_k|.
-\end{equation}
-However we do have that
-\begin{equation}
-\max_{k_1,k_2} (w_{k_1} w_{k_2}) = \max_k |w_k|^2 = \max_k w_k^2.
-\end{equation}
-If $\w \in \mathbb{R}^N$ with $w_k \ge 0$ for all $k$ then
-\begin{equation}
-\max_{k_1, k_2, \dots, k_n} [ w_{k_1}w_{k_2}\cdots w_{k_n}] = (\max_k w_k)^n,
-\end{equation}
-and therefore for arbitrary $\w \in \mathbb{R}^N$ and $n$, we have
-\begin{align}
-\hspace{-1cm}\max_{k_1, k_2, \dots, k_{2n}} [ w_{k_1}w_{k_2}\cdots w_{k_{2n}}] &\le \max_{k_1, k_2, \dots, k_{2n}}[|w_{k_1}w_{k_2}|\cdots |w_{k_{2n-1}} w_{k_{2n}}|] \nonumber \\
-&=(\max_{k_1 ,k_2} |w_{k_1} w_{k_2}| )^n \nonumber \\
-&\le\max_{k_1, k_2, \dots, k_{2n}} [ w_{k_1}w_{k_2}\cdots w_{k_{2n}}]  .
-\end{align}
-and so we have that in general
-\begin{equation}
-\max_{k_1, k_2, \dots, k_{2n}} [ w_{k_1}w_{k_2}\cdots w_{k_{2n}}]  =  (\max_{k_1 ,k_2} [w_{k_1} w_{k_2}] )^n.
-\end{equation}
+3. Given a vector $\w \in \mathbb{R}^N$, it is generally the case that $\max_k w_k \ne \max_k |w_k|$. 
+However, we do have that
+\begin{equation}
+	\max_{k_1,k_2} (w_{k_1} w_{k_2}) = \max_{k_1,k_2} |w_{k_1} w_{k_2}|,
+\end{equation}
+and if additionally $w_k \geq 0$ for all $k$, then we also have
+\begin{equation}
+	\max_{k_1, k_2, \dots, k_n} \left( w_{k_1}w_{k_2}\cdots w_{k_n} \right) = (\max_k w_k)^n.
+\end{equation}
+Therefore, for arbitrary $\w \in \mathbb{R}^N$ and $n$, we have
+\begin{align}
+	&\max_{k_1, k_2, \dots, k_{2n}}\left( w_{k_1}w_{k_2}\cdots w_{k_{2n}} \right) = \nonumber\\
+	&\max_{k_1, k_2, \dots, k_{2n}}\left( |w_{k_1}w_{k_2}|\cdots |w_{k_{2n-1}}w_{k_{2n}}| \right) = \nonumber \\
+	&\left( \max_{k_1 ,k_2}\left( w_{k_1} w_{k_2} \right) \right)^n.
+\end{align}
+
 If we now let $\w = W_{\rho|\tau}(\x) := W_{\rho}(\x) /W_{\tau}(\x)$ we have
 \begin{equation}
-\max_{\x_1, \x_2, \dots ,\x_{2n}} \prod_{k=1}^{2n} W_{\rho|\tau}(\x_k) = (\max_{\x_1, \x_2} W_{\rho|\tau}(\x_1)W_{\rho|\tau}(\x_2))^n
-\end{equation}
-and therefore taking logarithms we have that $D_\infty (\rho^{\otimes 2n}, \tau^{\otimes 2n}) = n D_\infty(\rho^{\otimes 2} ,\tau^{\otimes 2})$ as required. \ddd{[Check details for any fine print.]}
+\max_{\x_1, \x_2, \dots ,\x_{2n}} \prod_{k=1}^{2n} W_{\rho|\tau}(\x_k) = \left( \max_{\x_1, \x_2} W_{\rho|\tau}(\x_1)W_{\rho|\tau}(\x_2) \right)^n
+\end{equation}
+and therefore taking logarithms we have that $D_\infty (\rho^{\otimes 2n}, \tau^{\otimes 2n}) = n D_\infty(\rho^{\otimes 2} ,\tau^{\otimes 2})$ as required.
 
@@
 
-Using the above results, we can show that $H_{2m}$ is Schur-concave for all quasi-distributions.
-In particular, for any non-negative integer $m$, we have that
-\begin{equation}
-	W_{\rho_n}(\bmx) \succ W_{\rho'_{n'}}(\bmx) \mbox{ implies } H_{2m}(\rho_n) \leq H_{2m}(\rho'_{n'}).
-\end{equation}
-By additivity of $H_{2m}$, we get $n H_{2m}(\rho) \leq n' H_{2m}(\rho')$, or equivalently,
-\begin{equation}
-	\frac{n'}{n} \geq \frac{H_{2m}(\rho)}{H_{2m}(\rho')}.
-\end{equation}
-
-\nick{Wrong way? I don't think that $m \rightarrow \infty$ leads to our bound}
-
 \ddd{[TO-DO AND TIDY AND CHECK]} Okay great...this looks easy to do, we just need to compute the terms
@@
 \end{equation}
-This therefore should give \emph{additional} distillation bounds in the unital fragment. We'd need to check additivity is okay, but this should be fine. Therefore
-\begin{equation}
-W_{\rho_n}(\x) \succ W_{\rho'_m}(\x) \mbox{ implies } n H_{2m}(\rho) \le m H_{2m}(\rho'). 
-\end{equation}
-(Some sign error here? Should get:)
-\begin{equation}
-R \le \frac{H_{2m}(\rho)}{H_{2m}(\rho')}.
-\end{equation}
+
 \ddd{[Plan: check all these calculations! Give the generalised unital bound. Then we just conjecture this extends to Renyi-divergences and leave it at this.]}
+
+Using the above results, we can derive the following entropic bound on magic state transformations.
+\nick{to be extended (1) from unital processes to general relative majorization, (2) from $\alpha = 2m$ to $\alpha = 2m/(2k+1)$ for integer $m,k \geq 0$, (1) from Strange state to any magic state distillation}
+
+\begin{theorem}
+	Consider the magic distillation process
+	\begin{equation}
+		\rho_{\rm{S}}(\epsilon)^{\otimes n} \rightarrow \rho_{\rm{S}}(\epsilon')^{\otimes n'},
+	\end{equation}
+	in the unital fragment.
+	Define the $\alpha$-Renyi entropy of a state $\rho$ as
+	\begin{equation}
+		H_{\alpha}(\rho) := \frac{1}{1-\alpha} \log \sum_{\bmx} W_{\rho}(\bmx)^\alpha.
+	\end{equation}
+	Then, we have the following family of upper bounds on the distillation rate $R := n'/n$,
+	\begin{equation}
+		R \leq \frac{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho_{\rm{S}}(\epsilon) \right)}{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho_{\rm{S}}(\epsilon') \right)},
+	\end{equation}
+	for $\alpha = 2m,\ m\in\mathbb{N}$.
+\end{theorem}
+\begin{proof}
+	We can regularise the number of output copies in the process by tensoring in $(n-n')$ copies of the (free) maximally mixed state $\id/3$, so that we instead consider the process
+\begin{equation}
+	\rho_{\rm{S}}(\epsilon)^{\otimes n} \rightarrow \rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n - n')}.
+\end{equation}
+The entropy $H_\alpha$ is well-defined on the input and output states for $\alpha = 2m$ and since we have that $W_{\rho_n}(\bmx) \succ_{\id/3} W_{\rho'_{n'}}(\bmx)$, by Schur-concativity of $H_\alpha$ this implies
+\begin{equation}
+	H_\alpha \left( \rho_{\rm{S}}(\epsilon)^{\otimes n} \right) \leq H_\alpha \left( \rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n - n')} \right).
+\end{equation}
+By additivity of $H_\alpha$, we can rewrite the inequality as
+\begin{equation}
+	n H_\alpha \left( \rho_{\rm{S}}(\epsilon) \right) \leq n' H_\alpha \left( \rho_{\rm{S}}(\epsilon') \right) + (n - n') H_\alpha \left( \id/3 \right).
+\end{equation}
+Now, $H_\alpha \left( \id/3 \right)$ is the maximum value of $H_\alpha(\rho)$ for unital processes because every state $\rho$ majorizes $\id/3$, so we can finally re-arrange the inequality to
+\begin{equation}
+	\frac{n'}{n} \leq \frac{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho_{\rm{S}}(\epsilon) \right)}{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho_{\rm{S}}(\epsilon') \right)}.
+\end{equation}
+\end{proof}
+
 \subsection{Dropping pre/post-processing of the magic states}

### 2021-06-02 magic_paper.tex
added form of noisy strange state entropy

@@
 Using the above results, we can derive the following entropic bound on magic state transformations.
-\nick{to be extended (1) from unital processes to general relative majorization, (2) from $\alpha = 2m$ to $\alpha = 2m/(2k+1)$ for integer $m,k \geq 0$, (1) from Strange state to any magic state distillation}
+\nick{to be extended (1) from unital processes to general relative majorization, (2) from $\alpha = 2m$ to $\alpha = 2m/(2k+1)$ for integer $m,k \geq 0$, (3) from Strange state to any magic state distillation}
 
@@
 
+For an $\epsilon$-noisy Strange state, we have
+\begin{equation}
+	H_{\alpha}\left(\rho_{\rm{S}}(\epsilon)\right) = \frac{1}{1-\alpha}\log_2 \left[ 8\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^\alpha + \left(-\frac{1}{3} + \frac{4}{9}\epsilon \right)^\alpha \right]
+\end{equation}
+
+We also have for any quantum state $\rho$ that
+\begin{equation}
+	H_{0}\left(\rho\right) = 2\log_2 3 = H_\alpha \left( \id/3 \right),
+\end{equation}
+for any $\alpha$, so the bound is not well-defined for $H_0$. \nick{this should be true for general relative majorization.}
 \subsection{Dropping pre/post-processing of the magic states}

### 2021-06-03 magic_paper.tex
Extension to relative majorization added. Details need adding+checking

@@
 \begin{equation}
-R \le \frac{H_{2m}(\rho)}{H_{2m}(\rho')}.
+R \le \frac{H_{2m}(\I/d)- H_{2m}(\rho)}{H_{2m}(\I/d)-H_{2m}(\rho')}.
 \end{equation}
@@
 \end{equation}
+\ddd{[TO DO: Set $\epsilon = 0$ and determine region of $\alpha$ such that $H <0$.]}
 
@@
 \end{equation}
-for any $\alpha$, so the bound is not well-defined for $H_0$. \nick{this should be true for general relative majorization.}
+for any $\alpha$, so the bound is not well-defined for $H_0$.
+
+We extend to relative majorization via the following result.
+\begin{lemma}Let $\w\in \mathbb{R}^N, \w'\in \mathbb{R}^{N'}$ be quasi-distributions and $\r\in \mathbb{R}^N, \r'\in \mathbb{R}^{N'}$ probability distributions with positive rational entries given by $r_i = a_i/K$ and $r_i' = a_i'/K$ for integers $a_i,K, a_i'$.
+Then
+\begin{equation}
+(\p, \r) \succ (\p', \r') \mbox{ if and only if } \Gamma_{\mathbf{a}} (\p) \succ \Gamma_{\mathbf{a}'} (\p'),
+\end{equation}
+and where $\Gamma_{\mathbf{a}} :\mathbb{R}^N \rightarrow \mathbb{R}^K$ is the map
+\begin{equation}
+\Gamma_{\mathbf{a}}(\x) := \bigoplus_{i=1}^N x_i \eta_{a_i},
+\end{equation}
+and $\eta_{a_i} = (1/a_i, 1/a_i, \dots, 1/a_i)$ is the uniform distribution on $a_i$ elements.
+\end{lemma}
+\begin{proof}
+ The map $\Gamma_{\mathbf{a}}$ has a well-defined left-inverse $\Gamma^{-1}_{\mathbf{a}}: \mathbb{R}^K \rightarrow \mathbb{R}^N$ with 
+\begin{equation}
+\Gamma^{-1}_{\mathbf{a}}(\y) = ( \sum_{i=1}^{a_1} y_i,  \sum_{i=a_1 +1}^{a_1+a_2} y_i, \cdots ,  \sum_{i=a_1 +\cdots a_{N-1}+1}^{N} y_i),
+\end{equation}
+that obeys $\Gamma^{-1}_{\mathbf{a}} \circ \Gamma_{\mathbf{a}} (\x) = \x$ for all $\x \in \mathbb{R}^N$.
+
+We now claim that a \emph{bistochastic map} $B$ exists that sends $\Gamma_{\mathbf{a}}(\w)$ to $\Gamma_{\mathbf{a}'}(\w')$ if and only if a stochastic map $A$ exists sending $\w$ to $\w'$ and $\r$ to $\r'$.
+
+Suppose there is a stochastic map $A$ such that $A\w=\w'$ and $A\r = \r'$. We define $B := \Gamma_{\mathbf{a}'} \circ A \circ \Gamma_{\mathbf{a}}^{-1}$, and find that
+\begin{align}
+B \Gamma_{\mathbf{a}}(\w) &=\Gamma_{\mathbf{a}'} \circ A \circ \Gamma_{\mathbf{a}}^{-1}\circ\Gamma_{\mathbf{a}}(\w) \nonumber \\
+&=\Gamma_{\mathbf{a}'} (\w').
+\end{align}Moreover since $\Gamma_{\mathbf{a}} (\r) = (1/K, 1/K, \dots, 1/K)=\Gamma_{\mathbf{a}'} (\r') $ we also have that $B$ sends $(1/K, \dots ,1/K)$ to itself.
+\ddd{[To check that it also conserves probability and has non-negative components]}
+
+Conversely, suppose a bistochastic map $B$ exists sending $\Gamma_{\mathbf{a}}(\w)$ to $\Gamma_{\mathbf{a}'}(\w')$.
+Again, define  $A := \Gamma_{\mathbf{a}'}^{-1} \circ B \circ \Gamma_{\mathbf{a}}$, and find that $A$ is stochastic, and obeys $A\w = \w'$ and $A\r=\r'$.
+\ddd{[Spell out conditions for $A$ to be stochastic maybe]}.
+\end{proof}
+We also note that the vectors $\r, \r'$ with rational components is dense in the set of all positive probability distributions, and so we appeal to the fact that experiments have a finite resolution, and ignore technical details to do with the completion to arbitrary real components.
+
+Therefore if we have a Schur-Concave function $f(\x)$ for majorization of quasi-distributions then we can define a monotonic function for relative majorization via composition with $\Gamma_{\mathbf{a}}$ and its inverse.
+This should provide relative majorization monotones from which we can obtain distillation bounds, such as
+\begin{equation}
+R \le \frac{H_\alpha(\tau) - H_\alpha (\rho)}{H_\alpha(\tau') - H_\alpha (\rho')}.
+\end{equation}
+\ddd{[To be checked]}
 \subsection{Dropping pre/post-processing of the magic states}

### 2021-06-03 magic_paper.tex
Typo...issue with entropy to free energy not clear to me right now.
Final comment for the day.

@@
 \begin{equation}
-R \le \frac{H_\alpha(\tau) - H_\alpha (\rho)}{H_\alpha(\tau') - H_\alpha (\rho')}.
-\end{equation}
-\ddd{[To be checked]}
+R \le \frac{F_\alpha(\tau) - F_\alpha (\rho)}{F_\alpha(\tau') - F_\alpha (\rho')}.
+\end{equation}
+\ddd{[To be checked...transition from entropies to free energies less obvious from this route...needs reflection]}
+
+This is probably all we need to show:
+\begin{equation}
+H_\alpha(\Gamma_{\mathbf{a}}(\p)) = D_\alpha(\p ||\r),
+\end{equation}
+where we define the Renyi relative entropy
+\begin{equation}
+D_\alpha (\p || \r) := \frac{1}{\alpha -1} \log \sum_i p_i^\alpha q_i^{1-\alpha}.
+\end{equation}
+This probably follows from the details of how the $\Gamma_{\mathbf{a}}$ relates to $\r$. Needs expanding carefully.
 \subsection{Dropping pre/post-processing of the magic states}

### 2021-06-03 magic_paper.tex
fixed majorization to relative majorization proof

--- 2021-06-02 magic_paper.tex
@@
 
-\subsection{Schur-Convexity and quasi-distributions}
-We now make use of known results from majorization theory. We first define \emph{Schur-convex functions} on a subset $\D \subseteq \mathbb{R}^N$.
+\subsection{Entropic bounds on quasi-distributions}
+
+We first define the classical $\alpha$-Renyi entropy in terms of the Wigner quasi-distribution of any state $\rho$ as
+\begin{equation}
+	H_\alpha(\rho) := \frac{1}{1-\alpha} \log \sum_{\bmx} W_{\rho}(\bmx)^\alpha,
+\end{equation}
+where $\alpha$ can take values of the form $\alpha_1 / \alpha_2$, with even $\alpha_1 \geq 0$ and odd $\alpha_2 > 0$.
+
+We then prove the following result connecting simple majorization to relative majorization.
+\nick{move following lemma to section on relative majorization equivalent conditions}
+\begin{lemma}
+Let $\w\in \mathbb{R}^N, \w'\in \mathbb{R}^{N'}$ be quasi-distributions and $\r\in \mathbb{R}^N, \r'\in \mathbb{R}^{N'}$ probability distributions with positive rational entries given by $r_i = a_i/K$ and $r_i' = a_i'/K$ for positive integers $a_i, a_i'$ and $K = \sum_{i=1}^N a_i = \sum_{i=1}^{N'} a_i'$.
+Then,
+\begin{equation}
+(\w, \r) \succ (\w', \r') \mbox{ if and only if } \Gamma_{\bma} (\w) \succ \Gamma_{\bma'} (\w'),
+\end{equation}
+where the embedding map $\Gamma_{\bma} :\mathbb{R}^N \rightarrow \mathbb{R}^K$ is given by
+\begin{equation}
+	\Gamma_{\bma}(\x) := \bigoplus_{i=1}^N x_i \eta_{b_i},
+\end{equation}
+with $\eta_{a_i} = (1/a_i, 1/a_i, \dots, 1/a_i)$ the uniform distribution on $a_i$ elements.
+\end{lemma}
+\begin{proof}
+	We first note that the map $\Gamma_{\bma}$ is stochastic and has a well-defined left-inverse $\Gamma^{-1}_{\bma'}: \mathbb{R}^K \rightarrow \mathbb{R}^N$ given by
+\begin{equation}
+	\Gamma^{-1}_{\bma}(\w) = \left( \sum_{i=1}^{a_1} w_i,  \sum_{i = a_1 +1}^{a_1 + a_2} \hspace{-5pt} w_i, \dots , \hspace{-15pt} \sum_{i=a_1 + \dots + a_{N-1}+1}^{K} \hspace{-10pt} w_i \right),
+\end{equation}
+that obeys $(\Gamma^{-1}_{\bma} \circ \Gamma_{\bma}) (\x) = \x$ for all $\x \in \mathbb{R}^N$.
+
+The claim is equivalent to the statement that there exists a \emph{bistochastic map} $B$ sending $\Gamma_{\bma}(\w)$ to $\Gamma_{\bma'}(\w')$ if and only if there exists a stochastic map $A$ sending $\w$ to $\w'$ and $\r$ to $\r'$.
+
+Suppose there is a stochastic map $A$ such that $A\w=\w'$ and $A\r = \r'$. 
+We define $B:\mathbb{R}^K \mapsto \mathbb{R}^K$ by $B := \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1}$ so that it is stochastic as a composition of stochastic maps and it preserves the uniform distribution in $\mathbb{R}^A$, since
+\begin{align}
+	&B(1/K, 1/K, \dots, 1/K) = \big( \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1} \big) \big( \Gamma_{\bma'}(\r) \big) = \nonumber\\
+	&\Gamma_{\bma'} (\r') = (1/K, 1/K, \dots, 1/K),
+\end{align}
+therefore $B$ is bistochastic.
+Finally, $B$ maps the embedded distributions as follows,
+\begin{equation}
+	B \Gamma_{\bma}(\w) = \big( \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1} \big) \big( \Gamma_{\bma}(\w) \big) = \Gamma_{\bma'} (\w').
+\end{equation}
+
+Conversely, suppose a bistochastic map $B$ exists sending $\Gamma_{\bma}(\w)$ to $\Gamma_{\bma'}(\w')$.
+Again, define $A: \mathbb{R}^N \mapsto \mathbb{R}^{N'}$ by $A := \Gamma_{\bma'}^{-1} \circ B \circ \Gamma_{\bma}$ so that it is stochastic as a composition of stochastic maps and $A \w = \big( \Gamma_{\bma'}^{-1} \circ B \circ \Gamma_{\bma} \big) \w = \w'$, as well as $A \r = \r'$.
+\end{proof}
+We also note that the vectors $\r, \r'$ with rational components is dense in the set of all positive probability distributions, and so we appeal to the fact that experiments have a finite resolution, and ignore technical details to do with the completion to arbitrary real components.
+
+We now make use of known results from majorization theory. We first define \emph{Schur-convex and Schur-convave functions} on a subset $\D \subseteq \mathbb{R}^N$.
 
@@
 \end{definition}
-We now can consider the set of all quasi-distributions, which form a hyper-plane and are given by
-\begin{equation}
-\D = \{ \w \in \mathbb{R}^N: \sum_i w_i = 1\}.
+We can consider the set of all quasi-distributions, which form a hyper-plane and are given by
+\begin{equation}
+\D = \{ \w \in \mathbb{R}^N: \sum_{i=1}^N w_i = 1\}.
 \end{equation}
 For functions that are symmetric, namely $f(\p) = f(\Pi \p)$ for any component permutation $\Pi$, it suffices to restrict to the following region,
-
 \begin{equation}
@@
 
-We now have the following theorem~\cite{cit:marshall} that provides a characterization of symmetric, Schur-convex functions on quasi-distributions.
-\begin{theorem} Let $f$ be a real-valued continuous function defined on $\D^\downarrow$ that is continuously differentiable on the interior of $\D^\downarrow$.
+We now have the following theorem~\cite{cit:marshall} that provides a characterization of symmetric, Schur-convex and Schur-concave functions on quasi-distributions.
+\begin{lemma} 
+Let $f$ be a real-valued continuous function defined on $\D^\downarrow$ that is continuously differentiable on the interior of $\D^\downarrow$.
 Then $f$ is Schur-convex on $\D^\downarrow$ if and only if $\partial_k f(\w)$ is decreasing in $k$ for all $\w \in \D^\downarrow$, namely
@@
 for all $\w$ in the interior of $\D^\downarrow$.
-\end{theorem}
-
-\begin{lemma}[Additivity of $H_{2m}$]\label{H_add}
-	For any states $\rho, \rho'$ and non-negative $m$, we have
-	\begin{equation}
-		H_{2m}(\rho \otimes \rho') = H_{2m}(\rho) + H_{2m}(\rho')
+\end{lemma}
+
+We can use the above to prove that $H_\alpha$ is Schur-concave for
+
+\begin{lemma}[Additivity of $H_{\alpha}$]\label{H_add}
+	For any $\alpha > 0$ such that $H_{\alpha}$ is well-defined and any states $\rho, \rho'$, we have
+	\begin{equation}
+		H_{\alpha}(\rho \otimes \rho') = H_{\alpha}(\rho) + H_{\alpha}(\rho')
 	\end{equation}
@@
 	\begin{align*}
-		H_{2m}&(\rho \otimes \rho') = \frac{1}{1-2m}\log \sum_{\bmx,\bmx'} \left[W_{\rho}(\bmx)W_{\rho}(\bmx')\right]^{2m} \\
-		&= \frac{1}{1-2m}\left( \log \sum_{\bmx}W_{\rho}(\bmx)^{2m} + \log \sum_{\bmx'}W_{\rho}(\bmx')^{2m} \right) \\
-		&= H_{2m}(\rho) + H_{2m}(\rho').
+		H_{\alpha}&(\rho \otimes \rho') = \frac{1}{1-\alpha}\log \sum_{\bmx,\bmx'} \left[W_{\rho}(\bmx)W_{\rho}(\bmx')\right]^{\alpha} \\
+		&= \frac{1}{1-\alpha}\left( \log \sum_{\bmx}W_{\rho}(\bmx)^{\alpha} + \log \sum_{\bmx'}W_{\rho}(\bmx')^{\alpha} \right) \\
+		&= H_{\alpha}(\rho) + H_{\alpha}(\rho').
 	\end{align*}
@@
 \end{equation}
-for any $\alpha$, so the bound is not well-defined for $H_0$. \nick{this should be true for general relative majorization.}
+for any $\alpha$, so the bound is not well-defined for $H_0$.
+
+Therefore if we have a Schur-Concave function $f(\x)$ for majorization of quasi-distributions then we can define a monotonic function for relative majorization via composition with $\Gamma_{\mathbf{a}}$ and its inverse.
+This should provide relative majorization monotones from which we can obtain distillation bounds, such as
+\begin{equation}
+R \le \frac{F_\alpha(\tau) - F_\alpha (\rho)}{F_\alpha(\tau') - F_\alpha (\rho')}.
+\end{equation}
+\ddd{[To be checked...transition from entropies to free energies less obvious from this route...needs reflection]}
+
+This is probably all we need to show:
+\begin{equation}
+H_\alpha(\Gamma_{\mathbf{a}}(\p)) = D_\alpha(\p ||\r),
+\end{equation}
+where we define the Renyi relative entropy
+\begin{equation}
+D_\alpha (\p || \r) := \frac{1}{\alpha -1} \log \sum_i p_i^\alpha q_i^{1-\alpha}.
+\end{equation}
+This probably follows from the details of how the $\Gamma_{\mathbf{a}}$ relates to $\r$. Needs expanding carefully.
 \subsection{Dropping pre/post-processing of the magic states}

### 2021-06-04 magic_paper.tex
Trying to unpack the Schur-concavity bit

@@
 
-\begin{definition} A continuous, real-valued function $f$ defined on $\D \subseteq \mathbb{R}^N$ is called Schur-convex on the domain $\D$ if $\p \prec \q$ on $\D$ implies that $f(\p) \le f(\q)$.
-A continuous function $f:\D \rightarrow \mathbb{R}$ is called Schur-concave if $(-f)$ is Schur-convex.
+\begin{definition} A continuous, real-valued function $f$ defined on $\\mathcal{Q} \subseteq \mathbb{R}^N$ is called Schur-convex on the domain $\mathcal{Q}$ if $\p \prec \q$ on $\mathcal{Q}$ implies that $f(\p) \le f(\q)$.
+A continuous function $f:\mathcal{Q} \rightarrow \mathbb{R}$ is called Schur-concave if $(-f)$ is Schur-convex.
 \end{definition}
@@
 \begin{equation}
-\D = \{ \w \in \mathbb{R}^N: \sum_{i=1}^N w_i = 1\}.
+\mathcal{Q} = \{ \w \in \mathbb{R}^N: \sum_{i=1}^N w_i = 1\}.
 \end{equation}
@@
 \begin{equation}
-\D^\downarrow = \{ \w \in \D : w_1 \ge w_2 \ge \cdots \ge w_N\}.
+\mathcal{Q}^\downarrow = \{ \w \in \mathcal{Q} : w_1 \ge w_2 \ge \cdots \ge w_N\}.
 \end{equation}
@@
 \begin{lemma} 
-Let $f$ be a real-valued continuous function defined on $\D^\downarrow$ that is continuously differentiable on the interior of $\D^\downarrow$.
-Then $f$ is Schur-convex on $\D^\downarrow$ if and only if $\partial_k f(\w)$ is decreasing in $k$ for all $\w \in \D^\downarrow$, namely
+Let $f$ be a real-valued continuous function defined on $\mathcal{Q}^\downarrow$ that is continuously differentiable on the interior of $\mathcal{Q}^\downarrow$.
+Then $f$ is Schur-convex on $\mathcal{Q}^\downarrow$ if and only if $\partial_k f(\w)$ is decreasing in $k$ for all $\w \in \mathcal{Q}^\downarrow$, namely
 \begin{equation}
@@
 \end{equation}
-for all $\w$ in the interior of $\D^\downarrow$.
+for all $\w$ in the interior of $\mathcal{Q}^\downarrow$.
 \end{lemma}
@@
 
-\ddd{[TO-DO AND TIDY AND CHECK]} Okay great...this looks easy to do, we just need to compute the terms
-\begin{equation}
-	\frac{\partial H_\alpha}{\partial w_k} (w_1, w_2, \dots, w_N),
-\end{equation}
-for Renyi entropies (which are symmetric), and look to see when the above inequality holds. 
-We assume $ \alpha=2m$ is an even integer, so that $H_\alpha (\w)$ is well-defined on quasi-distributions. We then have that
-\begin{align}
-V_k:=-\frac{\partial H_\alpha}{\partial w_k} &= \partial_k \frac{1}{\alpha-1} \log \sum_i w_i^{2m} \\
-&= \frac{1}{(2m-1) \sum_i w_i^{2m}}2mw_k^{2m-1}.
-\end{align}
-We now impose the monotonicity condition $V_1 \ge V_2 \ge V_3 \cdots \ge V_N$. This requires, setting $S= \sum_i w_i^{2m}$ for simplicity, that
-\begin{align}
- \frac{1}{(2m-1)S}2mw_i^{2m-1}\ge \frac{1}{(2m-1)S}2mw_{i+1}^{2m-1},
-\end{align}
-for each $i=1,2,\dots, N-1$. We assume that $m >0$ and $2m \ne 1$ and so this becomes
-\begin{equation}
-w_i^{2m-1}\ge w_{i+1}^{2m-1}\mbox{ for all } 1 \le i < N.
-\end{equation}
+\ddd{[TO-DO AND TIDY AND CHECK]} The extension of the domain of the Renyi entropies to real values means that is it not real-valued for certain values of $\alpha$.
+However we can make $H_\alpha(\w)$ well-defined on the whole of $\mathcal{Q}$ if $\alpha = \frac{a}{b}$ where $b$ is an odd integer, and $a$ is an even integer.
+Depending on the set of quasi-distributions the quantum system supports the restriction of $a$ being even could be lifted, provided that the sum $\sum_i w_i^\alpha >0$, however we do not consider this here, and restrict to the assumption that $a$ is even.
+
+\begin{theorem} The functions $H_\alpha(\w)$ are well-defined on $\mathcal{Q}$ for $\alpha = \frac{a}{b}$ with $a$ an even integer and $b$ an odd integer, and are Schur-concave functions.
+\end{theorem}
+\begin{proof}
+We now make use of the Schur-Ostrowski criterion to determine when $H_\alpha$ is Schur-Convex on $\mathcal{Q}$.
+
+We have that
+\begin{align}
+V_k:=-\frac{\partial H_\alpha}{\partial w_k} &= \partial_k \frac{1}{\alpha-1} \log \sum_i w_i^{\alpha} \\
+&= \frac{1}{(\alpha-1) \sum_i w_i^{\alpha}}\alpha w_k^{\alpha-1}.
+\end{align}
+We now impose the monotonicity condition $V_1 \ge V_2 \ge V_3 \cdots \ge V_N$. This requires, setting $S= \sum_i w_i^\alpha$ for simplicity, that
+\begin{align}
+ \frac{1}{(\alpha-1)S}\alpha w_i^{\alpha-1}\ge \frac{1}{(\alpha-1)S}\alpha w_{i+1}^{\alpha-1},
+\end{align}
+for each $i=1,2,\dots, N-1$. We have that $S >0$, since $a$ is even, and assume that $\alpha >1$ so that
+\begin{equation}
+w_i^{\alpha-1}\ge w_{i+1}^{\alpha-1}\mbox{ for all } 1 \le i < N.
+\end{equation}
+For $\alpha = a/b > 1$ we have $\alpha-1 = (a-b)/b = a'/b >0$ where $a'$ is an even integer and $b$ an odd integer.
+We now assume that $\w \in \mathcal{Q}^\downarrow$ so that $ w_i \ge w_{i+1}$.
+\ddd{[Wait I'm not sure the inequalities work...]}
+
 For $2m >1$ this condition holds whenever $w_i \ge w_{i+1}$, which is true in $\D^\downarrow$.
@@
 \end{equation}
-
+\end{proof}
 \ddd{[Plan: check all these calculations! Give the generalised unital bound. Then we just conjecture this extends to Renyi-divergences and leave it at this.]}

### 2021-06-04 magic_paper.tex
tidied, filled some gaps, rearranged appendix on entropies

--- 2021-06-03 magic_paper.tex
@@
 \begin{equation}
-\hspace{-1cm}D_\infty(\rho,\tau) := D_\infty(W_\rho(\x) || W_\tau (\x)) =\log  \max_{\x} \frac{W_\rho(\x)}{W_\tau(\x)}\nonumber
+	\hspace{-14pt}D_\infty(\rho,\tau) := D_\infty(W_\rho(\x) || W_\tau (\x)) = \log  \max_{\x} \frac{W_\rho(\x)}{W_\tau(\x)},
 \end{equation}
@@
 where $\alpha$ can take values of the form $\alpha_1 / \alpha_2$, with even $\alpha_1 \geq 0$ and odd $\alpha_2 > 0$.
-
-We then prove the following result connecting simple majorization to relative majorization.
-\nick{move following lemma to section on relative majorization equivalent conditions}
-\begin{lemma}
-Let $\w\in \mathbb{R}^N, \w'\in \mathbb{R}^{N'}$ be quasi-distributions and $\r\in \mathbb{R}^N, \r'\in \mathbb{R}^{N'}$ probability distributions with positive rational entries given by $r_i = a_i/K$ and $r_i' = a_i'/K$ for positive integers $a_i, a_i'$ and $K = \sum_{i=1}^N a_i = \sum_{i=1}^{N'} a_i'$.
-Then,
-\begin{equation}
-(\w, \r) \succ (\w', \r') \mbox{ if and only if } \Gamma_{\bma} (\w) \succ \Gamma_{\bma'} (\w'),
-\end{equation}
-where the embedding map $\Gamma_{\bma} :\mathbb{R}^N \rightarrow \mathbb{R}^K$ is given by
-\begin{equation}
-	\Gamma_{\bma}(\x) := \bigoplus_{i=1}^N x_i \eta_{b_i},
-\end{equation}
-with $\eta_{a_i} = (1/a_i, 1/a_i, \dots, 1/a_i)$ the uniform distribution on $a_i$ elements.
-\end{lemma}
-\begin{proof}
-	We first note that the map $\Gamma_{\bma}$ is stochastic and has a well-defined left-inverse $\Gamma^{-1}_{\bma'}: \mathbb{R}^K \rightarrow \mathbb{R}^N$ given by
-\begin{equation}
-	\Gamma^{-1}_{\bma}(\w) = \left( \sum_{i=1}^{a_1} w_i,  \sum_{i = a_1 +1}^{a_1 + a_2} \hspace{-5pt} w_i, \dots , \hspace{-15pt} \sum_{i=a_1 + \dots + a_{N-1}+1}^{K} \hspace{-10pt} w_i \right),
-\end{equation}
-that obeys $(\Gamma^{-1}_{\bma} \circ \Gamma_{\bma}) (\x) = \x$ for all $\x \in \mathbb{R}^N$.
-
-The claim is equivalent to the statement that there exists a \emph{bistochastic map} $B$ sending $\Gamma_{\bma}(\w)$ to $\Gamma_{\bma'}(\w')$ if and only if there exists a stochastic map $A$ sending $\w$ to $\w'$ and $\r$ to $\r'$.
-
-Suppose there is a stochastic map $A$ such that $A\w=\w'$ and $A\r = \r'$. 
-We define $B:\mathbb{R}^K \mapsto \mathbb{R}^K$ by $B := \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1}$ so that it is stochastic as a composition of stochastic maps and it preserves the uniform distribution in $\mathbb{R}^A$, since
-\begin{align}
-	&B(1/K, 1/K, \dots, 1/K) = \big( \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1} \big) \big( \Gamma_{\bma'}(\r) \big) = \nonumber\\
-	&\Gamma_{\bma'} (\r') = (1/K, 1/K, \dots, 1/K),
-\end{align}
-therefore $B$ is bistochastic.
-Finally, $B$ maps the embedded distributions as follows,
-\begin{equation}
-	B \Gamma_{\bma}(\w) = \big( \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1} \big) \big( \Gamma_{\bma}(\w) \big) = \Gamma_{\bma'} (\w').
-\end{equation}
-
-Conversely, suppose a bistochastic map $B$ exists sending $\Gamma_{\bma}(\w)$ to $\Gamma_{\bma'}(\w')$.
-Again, define $A: \mathbb{R}^N \mapsto \mathbb{R}^{N'}$ by $A := \Gamma_{\bma'}^{-1} \circ B \circ \Gamma_{\bma}$ so that it is stochastic as a composition of stochastic maps and $A \w = \big( \Gamma_{\bma'}^{-1} \circ B \circ \Gamma_{\bma} \big) \w = \w'$, as well as $A \r = \r'$.
-\end{proof}
-We also note that the vectors $\r, \r'$ with rational components is dense in the set of all positive probability distributions, and so we appeal to the fact that experiments have a finite resolution, and ignore technical details to do with the completion to arbitrary real components.
-
-We now make use of known results from majorization theory. We first define \emph{Schur-convex and Schur-convave functions} on a subset $\D \subseteq \mathbb{R}^N$.
-
-\begin{definition} A continuous, real-valued function $f$ defined on $\D \subseteq \mathbb{R}^N$ is called Schur-convex on the domain $\D$ if $\p \prec \q$ on $\D$ implies that $f(\p) \le f(\q)$.
-A continuous function $f:\D \rightarrow \mathbb{R}$ is called Schur-concave if $(-f)$ is Schur-convex.
-\end{definition}
-We can consider the set of all quasi-distributions, which form a hyper-plane and are given by
-\begin{equation}
-\D = \{ \w \in \mathbb{R}^N: \sum_{i=1}^N w_i = 1\}.
-\end{equation}
-For functions that are symmetric, namely $f(\p) = f(\Pi \p)$ for any component permutation $\Pi$, it suffices to restrict to the following region,
-\begin{equation}
-\D^\downarrow = \{ \w \in \D : w_1 \ge w_2 \ge \cdots \ge w_N\}.
-\end{equation}
-
-We now have the following theorem~\cite{cit:marshall} that provides a characterization of symmetric, Schur-convex and Schur-concave functions on quasi-distributions.
-\begin{lemma} 
-Let $f$ be a real-valued continuous function defined on $\D^\downarrow$ that is continuously differentiable on the interior of $\D^\downarrow$.
-Then $f$ is Schur-convex on $\D^\downarrow$ if and only if $\partial_k f(\w)$ is decreasing in $k$ for all $\w \in \D^\downarrow$, namely
-\begin{equation}
-\partial_1 f(\w) \ge \partial_2 f(\w) \ge \cdots \ge \partial_N f(\w),
-\end{equation}
-for all $\w$ in the interior of $\D^\downarrow$.
-\end{lemma}
-
-We can use the above to prove that $H_\alpha$ is Schur-concave for
-
-\begin{lemma}[Additivity of $H_{\alpha}$]\label{H_add}
-	For any $\alpha > 0$ such that $H_{\alpha}$ is well-defined and any states $\rho, \rho'$, we have
-	\begin{equation}
-		H_{\alpha}(\rho \otimes \rho') = H_{\alpha}(\rho) + H_{\alpha}(\rho')
-	\end{equation}
+Note that for any quantum state $\rho$, $H_1$ in particular is not well-defined, while for any valid $\alpha$ we have that
+\begin{equation}
+	H_0(\rho) = 2\log_2 d = H_\alpha \left( \id/d \right),
+\end{equation}
+where $d$ is the dimension of $\rho$.
+For $\rho = \rho_{\rm{S}}(\epsilon)$, we get
+\begin{equation}
+	H_{\alpha}\left(\rho_{\rm{S}}(\epsilon)\right) = \frac{1}{1-\alpha}\log_2 \left[ 8\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^\alpha + \left(-\frac{1}{3} + \frac{4}{9}\epsilon \right)^\alpha \right]
+\end{equation}
+\ddd{[TO DO: Set $\epsilon = 0$ and determine region of $\alpha$ such that $H <0$.]}
+
+We can prove additivity of $H_{\alpha}$ on quantum states.
+
+\begin{lemma}\label{H_add}
+	For any quantum states $\rho, \rho'$, we have
+	\begin{equation}
+		H_{\alpha}(\rho \otimes \rho') = H_{\alpha}(\rho) + H_{\alpha}(\rho'),
+	\end{equation}
+	where $\hspace{-1pt}\alpha\hspace{-1pt}$ is such that $\hspace{-1pt}H_\alpha(\sigma)\hspace{-2pt}$ is well-defined for all states $\sigma$.
 \end{lemma}
@@
 \end{proof}
-\cref{H_add} implies that for any $n$,
-\begin{equation}
-	H_{2m}(\rho_n) := H_{2m}(\rho^{\otimes n}) = n H_{2m}(\rho).
-\end{equation}
-
-\ddd{[TO-DO AND TIDY AND CHECK]} Okay great...this looks easy to do, we just need to compute the terms
-\begin{equation}
-	\frac{\partial H_\alpha}{\partial w_k} (w_1, w_2, \dots, w_N),
-\end{equation}
-for Renyi entropies (which are symmetric), and look to see when the above inequality holds. 
-We assume $ \alpha=2m$ is an even integer, so that $H_\alpha (\w)$ is well-defined on quasi-distributions. We then have that
-\begin{align}
-V_k:=-\frac{\partial H_\alpha}{\partial w_k} &= \partial_k \frac{1}{\alpha-1} \log \sum_i w_i^{2m} \\
-&= \frac{1}{(2m-1) \sum_i w_i^{2m}}2mw_k^{2m-1}.
-\end{align}
-We now impose the monotonicity condition $V_1 \ge V_2 \ge V_3 \cdots \ge V_N$. This requires, setting $S= \sum_i w_i^{2m}$ for simplicity, that
-\begin{align}
- \frac{1}{(2m-1)S}2mw_i^{2m-1}\ge \frac{1}{(2m-1)S}2mw_{i+1}^{2m-1},
-\end{align}
-for each $i=1,2,\dots, N-1$. We assume that $m >0$ and $2m \ne 1$ and so this becomes
-\begin{equation}
-w_i^{2m-1}\ge w_{i+1}^{2m-1}\mbox{ for all } 1 \le i < N.
-\end{equation}
-For $2m >1$ this condition holds whenever $w_i \ge w_{i+1}$, which is true in $\D^\downarrow$.
-Therefore $-H_{2m}(\w)$ is Schur-Convex on quasi-distributions for any integer $m\in \mathbb{N}$.
-This implies it is a monotone function for majorization, namely,
-\begin{equation}
-\w \succ \w' \mbox{ implies } H_{2m} (\w) \le H_{2m} (\w') \mbox{for any } m \in \mathbb{N}.
-\end{equation}
-
-\ddd{[Plan: check all these calculations! Give the generalised unital bound. Then we just conjecture this extends to Renyi-divergences and leave it at this.]}
-
-Using the above results, we can derive the following entropic bound on magic state transformations.
-\nick{to be extended (1) from unital processes to general relative majorization, (2) from $\alpha = 2m$ to $\alpha = 2m/(2k+1)$ for integer $m,k \geq 0$, (3) from Strange state to any magic state distillation}
+
+We then prove the following result connecting simple majorization to relative majorization.
+\nick{move following lemma to section on relative majorization equivalent conditions}
+\begin{lemma}
+Let $\w\in \mathbb{R}^N, \w'\in \mathbb{R}^{N'}$ be quasi-distributions and $\r\in \mathbb{R}^N, \r'\in \mathbb{R}^{N'}$ probability distributions with positive rational entries given by $r_i = a_i/K$ and $r_i' = a_i'/K$ for positive integers $a_i, a_i'$ and $K = \sum_{i=1}^N a_i = \sum_{i=1}^{N'} a_i'$.
+Then,
+\begin{equation}
+(\w, \r) \succ (\w', \r') \mbox{ if and only if } \Gamma_{\bma} (\w) \succ \Gamma_{\bma'} (\w'),
+\end{equation}
+where the embedding map $\Gamma_{\bma} :\mathbb{R}^N \rightarrow \mathbb{R}^K$ is given by
+\begin{equation}
+	\Gamma_{\bma}(\x) := \bigoplus_{i=1}^N x_i \eta_{b_i},
+\end{equation}
+with $\eta_{a_i} = (1/a_i, 1/a_i, \dots, 1/a_i)$ the uniform distribution on $a_i$ elements.
+\end{lemma}
+\begin{proof}
+	We first note that the map $\Gamma_{\bma}$ is stochastic and has a well-defined left-inverse $\Gamma^{-1}_{\bma'}: \mathbb{R}^K \rightarrow \mathbb{R}^N$ given by
+\begin{equation}
+	\Gamma^{-1}_{\bma}(\w) = \left( \sum_{i=1}^{a_1} w_i,  \sum_{i = a_1 +1}^{a_1 + a_2} \hspace{-5pt} w_i, \dots , \hspace{-15pt} \sum_{i=a_1 + \dots + a_{N-1}+1}^{K} \hspace{-10pt} w_i \right),
+\end{equation}
+that obeys $(\Gamma^{-1}_{\bma} \circ \Gamma_{\bma}) (\x) = \x$ for all $\x \in \mathbb{R}^N$.
+
+The claim is equivalent to the statement that there exists a \emph{bistochastic map} $B$ sending $\Gamma_{\bma}(\w)$ to $\Gamma_{\bma'}(\w')$ if and only if there exists a stochastic map $A$ sending $\w$ to $\w'$ and $\r$ to $\r'$.
+
+Suppose there is a stochastic map $A$ such that $A\w=\w'$ and $A\r = \r'$. 
+We define $B:\mathbb{R}^K \mapsto \mathbb{R}^K$ by $B := \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1}$ so that it is stochastic as a composition of stochastic maps and it preserves the uniform distribution in $\mathbb{R}^A$, since
+\begin{align}
+	&B(1/K, 1/K, \dots, 1/K) = \big( \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1} \big) \big( \Gamma_{\bma'}(\r) \big) = \nonumber\\
+	&\Gamma_{\bma'} (\r') = (1/K, 1/K, \dots, 1/K),
+\end{align}
+therefore $B$ is bistochastic.
+Finally, $B$ maps the embedded distributions as follows,
+\begin{equation}
+	B \Gamma_{\bma}(\w) = \big( \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1} \big) \big( \Gamma_{\bma}(\w) \big) = \Gamma_{\bma'} (\w').
+\end{equation}
+
+Conversely, suppose a bistochastic map $B$ exists sending $\Gamma_{\bma}(\w)$ to $\Gamma_{\bma'}(\w')$.
+Again, define $A: \mathbb{R}^N \mapsto \mathbb{R}^{N'}$ by $A := \Gamma_{\bma'}^{-1} \circ B \circ \Gamma_{\bma}$ so that it is stochastic as a composition of stochastic maps and $A \w = \big( \Gamma_{\bma'}^{-1} \circ B \circ \Gamma_{\bma} \big) \w = \w'$, as well as $A \r = \r'$.
+\end{proof}
+We note that the vectors $\r, \r'$ with rational components form a dense subset of the positive probability distributions, so we can appeal to the fact that experiments have a finite resolution to ignore technical details regarding the completion to arbitrary real components.
+
+\subsubsection{Unital fragment}
+
+We now make use of known results from majorization theory to establish the Schur-concavity of $H_\alpha$ on Wigner quasi-distributions where $\alpha$ is such that $H_\alpha$ is well-defined. 
+We first define the notion of \emph{Schur-convex and Schur-convave functions} on a subset $\D \subseteq \mathbb{R}^N$.
+
+\begin{definition} A continuous, real-valued function $f$ defined on $\D \subseteq \mathbb{R}^N$ is called Schur-convex on the domain $\D$ if $\p \prec \q$ on $\D$ implies that $f(\p) \le f(\q)$.
+A continuous function $f:\D \rightarrow \mathbb{R}$ is called Schur-concave if $(-f)$ is Schur-convex.
+\end{definition}
+We can consider the set of all quasi-distributions, which form a hyper-plane and are given by
+\begin{equation}
+\D = \{ \w \in \mathbb{R}^N: \sum_{i=1}^N w_i = 1\}.
+\end{equation}
+For functions that are symmetric, namely $f(\p) = f(\Pi \p)$ for any component permutation $\Pi$, it suffices to restrict to the following region,
+\begin{equation}
+\D^\downarrow = \{ \w \in \D : w_1 \ge w_2 \ge \cdots \ge w_N\}.
+\end{equation}
+
+We now have the following theorem~\cite{cit:marshall} that provides a characterization of symmetric, Schur-convex and Schur-concave functions on quasi-distributions.
+\begin{lemma} 
+Let $f$ be a real-valued continuous function defined on $\D^\downarrow$ that is continuously differentiable on the interior of $\D^\downarrow$.
+Then, $f$ is Schur-convex on $\D^\downarrow$ if and only if $\partial_k f(\w)$ is decreasing in $k$ for all $\w \in \D^\downarrow$, namely
+\begin{equation}
+\partial_1 f(\w) \ge \partial_2 f(\w) \ge \cdots \ge \partial_N f(\w),
+\end{equation}
+for all $\w$ in the interior of $\D^\downarrow$.
+\end{lemma}
+
+We can use the above to prove that $H_\alpha$ is Schur-concave on quasi-distributions for particular values of $\alpha$.
 
 \begin{theorem}
-	Consider the magic distillation process
-	\begin{equation}
-		\rho_{\rm{S}}(\epsilon)^{\otimes n} \rightarrow \rho_{\rm{S}}(\epsilon')^{\otimes n'},
-	\end{equation}
-	in the unital fragment.
-	Define the $\alpha$-Renyi entropy of a state $\rho$ as
-	\begin{equation}
-		H_{\alpha}(\rho) := \frac{1}{1-\alpha} \log \sum_{\bmx} W_{\rho}(\bmx)^\alpha.
-	\end{equation}
-	Then, we have the following family of upper bounds on the distillation rate $R := n'/n$,
-	\begin{equation}
-		R \leq \frac{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho_{\rm{S}}(\epsilon) \right)}{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho_{\rm{S}}(\epsilon') \right)},
-	\end{equation}
-	for $\alpha = 2m,\ m\in\mathbb{N}$.
+	Let $\w, \w' \in \mathbb{R}^N$ be quasi-distributions such that $\w \succ \w'$.
+	Then, $H_\alpha(\w) \leq H_\alpha(\w')$, where $\alpha$ is such that $\hspace{-1pt}H_\alpha(\x)\hspace{-2pt}$ is well-defined for all quasi-distributions $\x$.
 \end{theorem}
 \begin{proof}
-	We can regularise the number of output copies in the process by tensoring in $(n-n')$ copies of the (free) maximally mixed state $\id/3$, so that we instead consider the process
-\begin{equation}
-	\rho_{\rm{S}}(\epsilon)^{\otimes n} \rightarrow \rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n - n')}.
-\end{equation}
-The entropy $H_\alpha$ is well-defined on the input and output states for $\alpha = 2m$ and since we have that $W_{\rho_n}(\bmx) \succ_{\id/3} W_{\rho'_{n'}}(\bmx)$, by Schur-concativity of $H_\alpha$ this implies
-\begin{equation}
-	H_\alpha \left( \rho_{\rm{S}}(\epsilon)^{\otimes n} \right) \leq H_\alpha \left( \rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n - n')} \right).
+Given a fixed $\alpha$ for which $H_\alpha(\x)$ is well-defined for all quasi-distributions $\x$, the function $H_\alpha$ is real-valued, smooth on the interior of $\D^\downarrow$ and symmetric on permutation components of $\x$.
+
+Consider the partial derivatives
+\begin{equation}
+	\frac{\partial H_\alpha}{\partial w_i} = \frac{\alpha w_i^{\alpha-1}}{(1-\alpha)\sum_k{w_k^\alpha}} 
+\end{equation}
+Whenever $w_i \geq w_j$, we have that 
+\begin{equation}
+	\frac{w_i^{\alpha-1}}{1-\alpha} \leq \frac{w_j^{\alpha-1}}{1-\alpha},
+\end{equation}
+independently of whether $\alpha < 1$ or $\alpha > 1$, which leads to
+\begin{equation}
+	\frac{\partial H_\alpha}{\partial w_i} \leq \frac{\partial H_\alpha}{\partial w_j}.
+\end{equation}
+Therefore, $H_\alpha$ is Schur-concave and
+\begin{equation}
+	H_\alpha(\w) \leq H_\alpha(\w'),
+\end{equation}
+for any quasi-distributions $\w, \w'$.
+\end{proof}
+
+We can now derive the following entropic bounds on magic state transformations.
+\nick{to be extended (1) from unital processes to general relative majorization, (2) by dropping the condition $\alpha > 1$}
+
+\begin{theorem}
+	Consider a general magic state distillation process $\rho^{\otimes n} \rightarrow \rho'^{\otimes n'}$	in the unital fragment.
+	We have the following family of upper bounds on the distillation rate $R := n'/n$,
+	\begin{equation}
+		R \leq \frac{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho \right)}{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho') \right)},
+	\end{equation}
+	where $\hspace{-1pt}\alpha\hspace{-1pt}$ is such that $\hspace{-1pt}H_\alpha(\sigma)\hspace{-2pt}$ is well-defined for all states $\sigma$.
+\end{theorem}
+\begin{proof}
+	We can regularise the number of output copies in the state distillation by tensoring in $(n-n')$ copies of the (free) maximally mixed state $\id/3$, so that we instead consider the process
+\begin{equation}
+	\rho^{\otimes n} \rightarrow \rho'^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n - n')}.
+\end{equation}
+Since we have that $W_{\rho^{\otimes n}}(\bmx) \succ_{\id/3} W_{\rho'^{\otimes n'}}(\bmx)$, by Schur-concativity of $H_\alpha$ we obtain
+\begin{equation}
+	H_\alpha \left( \rho^{\otimes n} \right) \leq H_\alpha \left( \rho'^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n - n')} \right).
 \end{equation}
@@
 \begin{equation}
-	n H_\alpha \left( \rho_{\rm{S}}(\epsilon) \right) \leq n' H_\alpha \left( \rho_{\rm{S}}(\epsilon') \right) + (n - n') H_\alpha \left( \id/3 \right).
+	n H_\alpha \left( \rho \right) \leq n' H_\alpha \left( \rho' \right) + (n - n') H_\alpha \left( \id/3 \right).
 \end{equation}
@@
 \begin{equation}
-	\frac{n'}{n} \leq \frac{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho_{\rm{S}}(\epsilon) \right)}{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho_{\rm{S}}(\epsilon') \right)}.
-\end{equation}
-\end{proof}
-
-For an $\epsilon$-noisy Strange state, we have
-\begin{equation}
-	H_{\alpha}\left(\rho_{\rm{S}}(\epsilon)\right) = \frac{1}{1-\alpha}\log_2 \left[ 8\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^\alpha + \left(-\frac{1}{3} + \frac{4}{9}\epsilon \right)^\alpha \right]
-\end{equation}
-\ddd{[TO DO: Set $\epsilon = 0$ and determine region of $\alpha$ such that $H <0$.]}
-
-We also have for any quantum state $\rho$ that
-\begin{equation}
-	H_{0}\left(\rho\right) = 2\log_2 3 = H_\alpha \left( \id/3 \right),
-\end{equation}
-for any $\alpha$, so the bound is not well-defined for $H_0$.
+	\frac{n'}{n} \leq \frac{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho \right)}{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho' \right)}.
+\end{equation}
+\end{proof}
+
+\subsubsection{Extention to general relative majorization}
 

### 2021-06-04 magic_paper.tex

@@
 
-\begin{definition} A continuous, real-valued function $f$ defined on $\D \subseteq \mathbb{R}^N$ is called Schur-convex on the domain $\D$ if $\p \prec \q$ on $\D$ implies that $f(\p) \le f(\q)$.
-A continuous function $f:\D \rightarrow \mathbb{R}$ is called Schur-concave if $(-f)$ is Schur-convex.
+\begin{definition} 
+A continuous, real-valued function $f$ defined on $\mathcal{Q} \subseteq \mathbb{R}^N$ is called Schur-convex on the domain $\mathcal{Q}$ if $\p \prec \q$ on $\mathcal{Q}$ implies that $f(\p) \le f(\q)$.
+A continuous function $f:\mathcal{Q} \rightarrow \mathbb{R}$ is called Schur-concave if $(-f)$ is Schur-convex.
 \end{definition}
@@
 \begin{equation}
-\D = \{ \w \in \mathbb{R}^N: \sum_{i=1}^N w_i = 1\}.
+\mathcal{Q} = \left\{ \w \in \mathbb{R}^N: \sum_{i=1}^N w_i = 1 \right\}.
 \end{equation}
@@
 \begin{lemma}
-Let $f$ be a real-valued continuous function defined on $\D^\downarrow$ that is continuously differentiable on the interior of $\D^\downarrow$.
-Then, $f$ is Schur-convex on $\D^\downarrow$ if and only if $\partial_k f(\w)$ is decreasing in $k$ for all $\w \in \D^\downarrow$, namely
+Let $f$ be a real-valued continuous function defined on $\mathcal{Q}^\downarrow$ that is continuously differentiable on the interior of $\mathcal{Q}^\downarrow$. 
+Then, $f$ is Schur-convex on $\mathcal{Q}^\downarrow$ if and only if $\partial_k f(\w)$ is decreasing in $k$ for all $\w \in \mathcal{Q}^\downarrow$, namely
 \begin{equation}
@@
 \begin{proof}
-Given a fixed $\alpha$ for which $H_\alpha(\x)$ is well-defined for all quasi-distributions $\x$, the function $H_\alpha$ is real-valued, smooth on the interior of $\D^\downarrow$ and symmetric on permutation components of $\x$.
+Given a fixed $\alpha$ for which $H_\alpha(\x)$ is well-defined for all quasi-distributions $\x$, the function $H_\alpha$ is real-valued, smooth on the interior of $\mathcal{Q}^\downarrow$ and symmetric on permutation components of $\x$.
 
@@
 \end{equation}
-independently of whether $\alpha < 1$ or $\alpha > 1$, which leads to
+\nick{wrong} independently of whether $\alpha < 1$ or $\alpha > 1$, which leads to
 \begin{equation}
@@
 \subsubsection{Extention to general relative majorization}
+
+\ddd{[TO-DO AND TIDY AND CHECK]} The extension of the domain of the Renyi entropies to real values means that is it not real-valued for certain values of $\alpha$.
+However we can make $H_\alpha(\w)$ well-defined on the whole of $\mathcal{Q}$ if $\alpha = \frac{a}{b}$ where $b$ is an odd integer, and $a$ is an even integer.
+Depending on the set of quasi-distributions the quantum system supports the restriction of $a$ being even could be lifted, provided that the sum $\sum_i w_i^\alpha >0$, however we do not consider this here, and restrict to the assumption that $a$ is even.
+
+\begin{theorem} The functions $H_\alpha(\w)$ are well-defined on $\mathcal{Q}$ for $\alpha = \frac{a}{b}$ with $a$ an even integer and $b$ an odd integer, and are Schur-concave functions.
+\end{theorem}
+\begin{proof}
+We now make use of the Schur-Ostrowski criterion to determine when $H_\alpha$ is Schur-Convex on $\mathcal{Q}$.
+
+We have that
+\begin{align}
+V_k:=-\frac{\partial H_\alpha}{\partial w_k} &= \partial_k \frac{1}{\alpha-1} \log \sum_i w_i^{\alpha} \\
+&= \frac{1}{(\alpha-1) \sum_i w_i^{\alpha}}\alpha w_k^{\alpha-1}.
+\end{align}
+We now impose the monotonicity condition $V_1 \ge V_2 \ge V_3 \cdots \ge V_N$. This requires, setting $S= \sum_i w_i^\alpha$ for simplicity, that
+\begin{align}
+ \frac{1}{(\alpha-1)S}\alpha w_i^{\alpha-1}\ge \frac{1}{(\alpha-1)S}\alpha w_{i+1}^{\alpha-1},
+\end{align}
+for each $i=1,2,\dots, N-1$. We have that $S >0$, since $a$ is even, and assume that $\alpha >1$ so that
+\begin{equation}
+w_i^{\alpha-1}\ge w_{i+1}^{\alpha-1}\mbox{ for all } 1 \le i < N.
+\end{equation}
+For $\alpha = a/b > 1$ we have $\alpha-1 = (a-b)/b = a'/b >0$ where $a'$ is an even integer and $b$ an odd integer.
+We now assume that $\w \in \mathcal{Q}^\downarrow$ so that $ w_i \ge w_{i+1}$.
+\ddd{[Wait I'm not sure the inequalities work...]}
+\end{proof}
 

### 2021-06-04 magic_paper.tex
expanded argument

@@
 \end{equation}
-\ddd{[TO DO: Set $\epsilon = 0$ and determine region of $\alpha$ such that $H <0$.]}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.35]{figs/test/H_vs_eps_a.pdf}
+    \caption{\ddd{[TO DO: Set $\epsilon = 0$ and determine region of $\alpha$ such that $H <0$.]} Here, the exponent is $\alpha = even/odd$ for $1.10 \leq \alpha \leq 1.50$.
+First dashed contour from the right corresponds to $H_\alpha(\rho_{\rm{S}}(0)) = 0$.
+    }
+    \label{fig:lcs}
+\end{figure}
 
@@
 
-\begin{theorem}
+\begin{theorem}\label{thm:HSchur}
 	Let $\w, \w' \in \mathbb{R}^N$ be quasi-distributions such that $\w \succ \w'$.
-	Then, $H_\alpha(\w) \leq H_\alpha(\w')$, where $\alpha$ is such that $\hspace{-1pt}H_\alpha(\x)\hspace{-2pt}$ is well-defined for all quasi-distributions $\x$.
+	Then, $H_\alpha(\w) \leq H_\alpha(\w')$, where $\alpha = \frac{2a}{2b+1}$ for any positive integers $a,b$ with $a > b$.
 \end{theorem}
 \begin{proof}
-Given a fixed $\alpha$ for which $H_\alpha(\x)$ is well-defined for all quasi-distributions $\x$, the function $H_\alpha$ is real-valued, smooth on the interior of $\mathcal{Q}^\downarrow$ and symmetric on permutation components of $\x$.
+We have $\alpha = \frac{2a}{2b+1} \geq \frac{2b+2}{2b+1} > 1$ and $\alpha$ is a rational with even numerator and odd denominator, so $\sum_i x_i^\alpha > 0$ and $H_\alpha(\x)$ is well-defined for all quasi-distributions $\x$.
+
+Given a fixed $\alpha$ for which $H_\alpha(\x)$ is well-defined, the function $H_\alpha$ is real-valued, smooth on the interior of $\mathcal{Q}^\downarrow$ and symmetric on permutation components of $\x$.
 
@@
 \begin{equation}
-	\frac{\partial H_\alpha}{\partial w_i} = \frac{\alpha w_i^{\alpha-1}}{(1-\alpha)\sum_k{w_k^\alpha}} 
-\end{equation}
-Whenever $w_i \geq w_j$, we have that 
-\begin{equation}
-	\frac{w_i^{\alpha-1}}{1-\alpha} \leq \frac{w_j^{\alpha-1}}{1-\alpha},
-\end{equation}
-\nick{wrong} independently of whether $\alpha < 1$ or $\alpha > 1$, which leads to
+	\frac{\partial H_\alpha}{\partial w_i} = \frac{\alpha}{(\alpha-1)\sum_k{w_k^\alpha}}(-w_i^{\alpha-1})
+\end{equation}
+Whenever $w_i \geq w_j$, for $\alpha$ in the given form, we always have that $\alpha - 1$ is positive and of the form odd$/$odd so \nick{expand argument}
+\begin{equation}
+	-w_i^{\alpha-1} \leq -w_j^{\alpha-1},
+\end{equation}
+which leads to
 \begin{equation}
@@
 \end{proof}
+Note that if $\alpha < 1$ or is of the form odd$/$even, the argument of~\cref{thm:HSchur} does not hold.
 
 We can now derive the following entropic bounds on magic state transformations.
-\nick{to be extended (1) from unital processes to general relative majorization, (2) by dropping the condition $\alpha > 1$}
-
 \begin{theorem}
@@
 We now assume that $\w \in \mathcal{Q}^\downarrow$ so that $ w_i \ge w_{i+1}$.
-\ddd{[Wait I'm not sure the inequalities work...]}
+\ddd{[Wait I'm not sure the inequalities work...]} \nick{Look at proof of~\cref{thm:HSchur} and table below}
+
+\begin{table}[h]
+  \def\arraystretch{1.5}
+  \centering
+  \begin{tabular}{c|c|c|c||c|c}
+    $w_i$ & $w_{i+1}$ & $\alpha$ & $\frac{w_i^{\alpha-1}}{\alpha-1} \geq \frac{w_{i+1}^{\alpha-1}}{\alpha-1}$ & $\alpha$ & $\frac{w_i^{\alpha-1}}{\alpha-1} \geq \frac{w_{i+1}^{\alpha-1}}{\alpha-1}$ \\[0.5ex]\hline
+    $2$ & $1.5$  & $3$ & $2 > 1.125$ T & $1/3$ & $-0.94 > -1.14$ T \\
+    $2$ & $-1.5$ & $3$ & $2 > 1.125$ T & $1/3$ & $-0.94 > -1.14$ T \\
+    $2$ & $-2.5$ & $3$ & $2 < 3.125$ F & $1/3$ & $-0.94 < -0.81$ F \\[0.5ex]\hline
+    $2/3$ & $1/3$  & $3$ & $0.22 > 0.06$ T & $1/3$ & $-1.97 > -3.12$ T \\
+    $2/3$ & $-1/3$ & $3$ & $0.22 > 0.06$ T & $1/3$ & $-1.97 > -3.12$ T \\
+    $2/3$ & $-4/3$ & $3$ & $0.22 < 0.89$ F & $1/3$ & $-1.97 < -1.24$ F \\[0.5ex]\hline
+    $2$ & $1.5$  & $4$ & $2.67 > 1.125$ T & $2/3$ & $-2.38 > -2.62$ T \\
+    $2$ & $-1.5$ & $4$ & $2.66 > -1.125$ T & $2/3$ & $-2.38 > 2.62$ F \\
+    $2$ & $-2.5$ & $4$ & $2.66 > 5.21$ T & $2/3$ & $-2.38 > 2.21$ F \\
+    $-2$ & $-2.5$ & $4$ & $-2.66 > -5.21$ T & $2/3$ & $2.38 > 2.21$ T \\[0.5ex]\hline
+    $2/3$ & $1/3$  & $4$ & $0.10 > 0.01$ T & $2/3$ & $-3.43 > -4.33$ T \\
+    $2/3$ & $-1/3$ & $4$ & $0.10 > -0.01$ T & $2/3$ & $-3.43 > 4.33$ F \\
+    $2/3$ & $-4/3$ & $4$ & $0.10 > -0.79$ T & $2/3$ & $-3.43 > 2.73$ F \\
+    $-1/3$ & $-2/3$ & $4$ & $-0.01 > -0.10$ T & $2/3$ & $4.33 > 3.43$ T \\
+    $-1/3$ & $-4/3$ & $4$ & $-0.01 > -0.79$ T & $2/3$ & $4.33 > 2.73$ T
+  \end{tabular}
+  \caption{Exploring in what regimes the Schur-Ostrowski criterion holds.}
+  \label{tab:test}
+\end{table}
+
 \end{proof}

### 2021-06-04 magic_paper.tex
filled gaps, organised material within the new appendix, important to confirm that alpha = even/odd works: see Theorem 28 proof for explanation and numerical table

@@
 \begin{theorem} Let $\tau$ be in the interior of $\F$, and define $D_\infty(\rho,\tau) := D_\infty(W_\rho(\x) || W_\tau (\x))$.
-Then $D_\infty(\rho, \tau)$ is well-defined for all $\rho$, and the following hold:
+Then $D_\infty(\rho, \tau)$ is well-defined for all $\rho$, and the following hold: \nick{can generalise to $D_{\alpha}$ for appropriate $\alpha$}
 \begin{enumerate}
@@
 \end{equation}
-where $\alpha$ can take values of the form $\alpha_1 / \alpha_2$, with even $\alpha_1 \geq 0$ and odd $\alpha_2 > 0$.
-Note that for any quantum state $\rho$, $H_1$ in particular is not well-defined, while for any valid $\alpha$ we have that
+where $\alpha$ can take values of the form $2a / (2b+1)$, for non-negative integers $a,b$ to ensure that the argument of the logarithm is positive.
+Note that for any quantum state $\rho$, $H_1(\rho)$ in particular is not well-defined  \nick{Notation clashes with quantum Renyi entropies}, while for any valid $\alpha$ we have that
 \begin{equation}
@@
     \includegraphics[scale=0.35]{figs/test/H_vs_eps_a.pdf}
-    \caption{\ddd{[TO DO: Set $\epsilon = 0$ and determine region of $\alpha$ such that $H <0$.]} Here, the exponent is $\alpha = even/odd$ for $1.10 \leq \alpha \leq 1.50$.
-First dashed contour from the right corresponds to $H_\alpha(\rho_{\rm{S}}(0)) = 0$.
+    \caption{\ddd{[TO DO: Set $\epsilon = 0$ and determine region of $\alpha$ such that $H <0$.]} Here, the exponent is $\alpha =$ even$/$odd for $1.10 \leq \alpha \leq 1.50$.
+$H_\alpha$ is increasing in $\alpha$ and $\epsilon$ \nick{should be easy to show analytically}.
+First dashed contour from the right corresponds to $H_\alpha(\rho_{\rm{S}}(\epsilon)) = 0$.
+Specifically, $H_\alpha(\rho_{\rm{S}}(0)) = 0$ has a unique solution, which is the \nick{probably irrational - this seems problematic} solution of $3^\alpha - 2^{3-\alpha} = 1$.
     }
@@
 
+\ddd{[TO-DO TIDY AND CHECK]}
 \begin{theorem}\label{thm:HSchur}
-	Let $\w, \w' \in \mathbb{R}^N$ be quasi-distributions such that $\w \succ \w'$.
-	Then, $H_\alpha(\w) \leq H_\alpha(\w')$, where $\alpha = \frac{2a}{2b+1}$ for any positive integers $a,b$ with $a > b$.
+	Let $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$.
+	Then, $H_\alpha$ is Schur-concave, i.e. for quasi-distributions $\w, \w' \in \mathbb{R}^N$, we have $H_\alpha(\w) \leq H_\alpha(\w')$, whenever $\w \succ \w'$.
 \end{theorem}
 \begin{proof}
-We have $\alpha = \frac{2a}{2b+1} \geq \frac{2b+2}{2b+1} > 1$ and $\alpha$ is a rational with even numerator and odd denominator, so $\sum_i x_i^\alpha > 0$ and $H_\alpha(\x)$ is well-defined for all quasi-distributions $\x$.
+We have $\alpha = \frac{2a}{2b+1} \geq \frac{2b}{2b-1} > 1$ and $\alpha$ is a rational with even numerator and odd denominator, so $\sum_i x_i^\alpha > 0$ and $H_\alpha(\x)$ is well-defined for all quasi-distributions $\x$.
 
@@
 \begin{equation}
-	\frac{\partial H_\alpha}{\partial w_i} = \frac{\alpha}{(\alpha-1)\sum_k{w_k^\alpha}}(-w_i^{\alpha-1})
+	\frac{\partial H_\alpha}{\partial w_i} = \frac{\alpha}{(\alpha-1)\sum_k{w_k^\alpha}}(-w_i^{\alpha-1}).
 \end{equation}
@@
 for any quasi-distributions $\w, \w'$.
-\end{proof}
-Note that if $\alpha < 1$ or is of the form odd$/$even, the argument of~\cref{thm:HSchur} does not hold.
-
-We can now derive the following entropic bounds on magic state transformations.
-\begin{theorem}
-	Consider a general magic state distillation process $\rho^{\otimes n} \rightarrow \rho'^{\otimes n'}$	in the unital fragment.
-	We have the following family of upper bounds on the distillation rate $R := n'/n$,
-	\begin{equation}
-		R \leq \frac{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho \right)}{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho') \right)},
-	\end{equation}
-	where $\hspace{-1pt}\alpha\hspace{-1pt}$ is such that $\hspace{-1pt}H_\alpha(\sigma)\hspace{-2pt}$ is well-defined for all states $\sigma$.
-\end{theorem}
-\begin{proof}
-	We can regularise the number of output copies in the state distillation by tensoring in $(n-n')$ copies of the (free) maximally mixed state $\id/3$, so that we instead consider the process
-\begin{equation}
-	\rho^{\otimes n} \rightarrow \rho'^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n - n')}.
-\end{equation}
-Since we have that $W_{\rho^{\otimes n}}(\bmx) \succ_{\id/3} W_{\rho'^{\otimes n'}}(\bmx)$, by Schur-concativity of $H_\alpha$ we obtain
-\begin{equation}
-	H_\alpha \left( \rho^{\otimes n} \right) \leq H_\alpha \left( \rho'^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n - n')} \right).
-\end{equation}
-By additivity of $H_\alpha$, we can rewrite the inequality as
-\begin{equation}
-	n H_\alpha \left( \rho \right) \leq n' H_\alpha \left( \rho' \right) + (n - n') H_\alpha \left( \id/3 \right).
-\end{equation}
-Now, $H_\alpha \left( \id/3 \right)$ is the maximum value of $H_\alpha(\rho)$ for unital processes because every state $\rho$ majorizes $\id/3$, so we can finally re-arrange the inequality to
-\begin{equation}
-	\frac{n'}{n} \leq \frac{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho \right)}{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho' \right)}.
-\end{equation}
-\end{proof}
-
-\subsubsection{Extention to general relative majorization}
-
-\ddd{[TO-DO AND TIDY AND CHECK]} The extension of the domain of the Renyi entropies to real values means that is it not real-valued for certain values of $\alpha$.
-However we can make $H_\alpha(\w)$ well-defined on the whole of $\mathcal{Q}$ if $\alpha = \frac{a}{b}$ where $b$ is an odd integer, and $a$ is an even integer.
-Depending on the set of quasi-distributions the quantum system supports the restriction of $a$ being even could be lifted, provided that the sum $\sum_i w_i^\alpha >0$, however we do not consider this here, and restrict to the assumption that $a$ is even.
-
-\begin{theorem} The functions $H_\alpha(\w)$ are well-defined on $\mathcal{Q}$ for $\alpha = \frac{a}{b}$ with $a$ an even integer and $b$ an odd integer, and are Schur-concave functions.
-\end{theorem}
-\begin{proof}
-We now make use of the Schur-Ostrowski criterion to determine when $H_\alpha$ is Schur-Convex on $\mathcal{Q}$.
-
-We have that
-\begin{align}
-V_k:=-\frac{\partial H_\alpha}{\partial w_k} &= \partial_k \frac{1}{\alpha-1} \log \sum_i w_i^{\alpha} \\
-&= \frac{1}{(\alpha-1) \sum_i w_i^{\alpha}}\alpha w_k^{\alpha-1}.
-\end{align}
-We now impose the monotonicity condition $V_1 \ge V_2 \ge V_3 \cdots \ge V_N$. This requires, setting $S= \sum_i w_i^\alpha$ for simplicity, that
-\begin{align}
- \frac{1}{(\alpha-1)S}\alpha w_i^{\alpha-1}\ge \frac{1}{(\alpha-1)S}\alpha w_{i+1}^{\alpha-1},
-\end{align}
-for each $i=1,2,\dots, N-1$. We have that $S >0$, since $a$ is even, and assume that $\alpha >1$ so that
-\begin{equation}
-w_i^{\alpha-1}\ge w_{i+1}^{\alpha-1}\mbox{ for all } 1 \le i < N.
-\end{equation}
-For $\alpha = a/b > 1$ we have $\alpha-1 = (a-b)/b = a'/b >0$ where $a'$ is an even integer and $b$ an odd integer.
-We now assume that $\w \in \mathcal{Q}^\downarrow$ so that $ w_i \ge w_{i+1}$.
-\ddd{[Wait I'm not sure the inequalities work...]} \nick{Look at proof of~\cref{thm:HSchur} and table below}
 
@@
   \end{tabular}
-  \caption{Exploring in what regimes the Schur-Ostrowski criterion holds.}
+  \caption{\nick{NUMERICS ON SCHUR-OSTROWSKI CONDITION} Seems like $\alpha=$ even$/$odd and $\alpha > 1$ works for any combination of $w_i, w_{i+1}$ with $w_i > w_{i+1}$ and seems also that no other case works.}
   \label{tab:test}
@@
 \end{proof}
+Note that if $\alpha < 1$ or is of the form odd$/$even, the argument of~\cref{thm:HSchur} does not hold.
+However, the set $F := \{2a/(2b+1): a,b \in \mathbb{N} \text{ and } a>b\}$ is dense in the rationals $\mathbb{Q}_{>1}$ (which in turn is dense in $\mathbb{R}_{>1}$) as any rational $c/d$ with $c>d$ can be approximated by a sequence $f_n := c2^n / (d2^n+1)$ with every element $f_n$ in the set $F$.
+\nick{can turn into lemma}
+
+We can now derive the following entropic bounds on magic state transformations.
+\begin{theorem}
+	Consider a general magic state distillation process $\rho^{\otimes n} \rightarrow \rho'^{\otimes n'}$	in the unital fragment.
+	We have the following family of upper bounds on the distillation rate $R := n'/n$,
+	\begin{equation}
+		R \leq \frac{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho \right)}{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho') \right)} = \frac{D_{\alpha}(\rho||\id/3)}{D_{\alpha}(\rho'||\id/3)},
+	\end{equation}
+	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$.
+\end{theorem}
+\begin{proof}
+	For the given form of $\alpha$, $H_\alpha(\sigma)$ is well-defined adn Schur-concave for all quantum states $\sigma$.
+
+	We first regularise the number of output copies in the state distillation by tensoring in $(n-n')$ copies of the (free) maximally mixed state $\id/3$, so that we instead consider the process
+\begin{equation}
+	\rho^{\otimes n} \rightarrow \rho'^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n - n')}.
+\end{equation}
+Since we have that $W_{\rho^{\otimes n}}(\bmx) \succ_{\id/3} W_{\rho'^{\otimes n'}}(\bmx)$, by Schur-concativity of $H_\alpha$ we obtain
+\begin{equation}
+	H_\alpha \left( \rho^{\otimes n} \right) \leq H_\alpha \left( \rho'^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n - n')} \right).
+\end{equation}
+By additivity of $H_\alpha$, we can rewrite the inequality as
+\begin{equation}
+	n H_\alpha \left( \rho \right) \leq n' H_\alpha \left( \rho' \right) + (n - n') H_\alpha \left( \id/3 \right).
+\end{equation}
+Now, $H_\alpha \left( \id/3 \right)$ is the maximum value of $H_\alpha(\rho)$ for unital processes because every state $\rho$ majorizes $\id/3$, so we can finally re-arrange the inequality to
+\begin{equation}
+	\frac{n'}{n} \leq \frac{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho \right)}{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho' \right)}.
+\end{equation}
+\end{proof}
+
+\subsubsection{Extention to general relative majorization}
 
@@
 This probably follows from the details of how the $\Gamma_{\mathbf{a}}$ relates to $\r$. Needs expanding carefully.
+
+\begin{theorem}
+	Consider a general magic state distillation process that converts magic state $\rho^{\otimes n} \longrightarrow \rho'^{\otimes n'}$ as well as equilibrium state $\tau^{\otimes n} \longrightarrow \tau'^{\otimes n'}$, where we assume that $W_{\tau^{\otimes n}}(\bmx) = a_{\bmx}/K$ and $W_{\tau'^{\otimes n'}}(\bmx) = a_{\bmx}/K$ for positive integers $a_{\bmx}, a_{\bmx}'$ and $K = \sum_{\bmx} a_{\bmx} = \sum_{\bmx} a_{\bmx}'$.
+
+	We have the following family of upper bounds on the distillation rate $R := n'/n$,
+	\begin{equation}
+		R \leq \text{\nick{BOUND}},
+	\end{equation}
+	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$.
+\end{theorem}
+\begin{proof}
+	For the sake of clarity, we write $\rho_n \coloneqq \rho_S(\epsilon)^{\otimes n}$, $\rho'_{n'} \coloneqq \rho_S(\epsilon')^{\otimes n'}$, $\tau_n \coloneqq \tau^{\otimes n}$ and $\tau'_{n'} \coloneqq \tau'^{\otimes n'}$.
+
+	We have that $(W_{\rho_n}, W_{\tau_n}) \succ W_{\rho'_{n'}}, W_{\tau'_{n'}})$, or equivalently $\Gamma_{\bma}(W_{\rho_n}) \succ \Gamma_{\bma'}(W_{\rho'_{n'}})$, where
+\begin{align}
+	\Gamma_{\bma}(W_{\rho_n}) &= \bigoplus_{\bmx} W_{\rho_n}(\bmx) \left(\frac{1}{KW_{\tau_n}(\bmo)}, \dots, \frac{1}{KW_{\tau_n}((d,d))} \right)\nonumber\\
+	&= \frac{1}{K}\bigoplus_{\bmx}\bigoplus_{\bmy} \frac{W_{\rho_n}(\bmx)}{W_{\tau_n}(\bmy)},
+\end{align}
+and similarly for $\Gamma_{\bma'}(W_{\rho'_{n'}})$.
+Therefore,
+\begin{equation}
+	H_{\alpha}(\Gamma_{\bma}(W_{\rho_n})) = \frac{1}{1-\alpha} \log_2 \left( \frac{1}{K^\alpha} \sum_{\bmx, \bmy} \frac{W_{\rho_n}(\bmx)^\alpha}{W_{\tau_n}(\bmy)^\alpha} \right),
+\end{equation}
+while
+\begin{equation}
+	D(\rho||\tau) = \frac{1}{\alpha-1} \log_2 \sum_{\bmx,\bmy} \frac{W_{\rho}(\bmx)^\alpha}{W_{\tau}(\bmy)^{\alpha-1}}.
+\end{equation}
+\nick{correct mistakes, bridge gaps}
+\end{proof}
+
 \subsection{Dropping pre/post-processing of the magic states}

### 2021-06-04 magic_paper.tex
expanded on argument why alpha = even/even works

@@
 \end{equation}
-Whenever $w_i \geq w_j$, for $\alpha$ in the given form, we always have that $\alpha - 1$ is positive and of the form odd$/$odd so \nick{expand argument}
+We first note that for $\alpha$ in the given form, it is always true that
+\begin{equation}
+	\frac{\alpha}{(\alpha-1)\sum_k{w_k^\alpha}} > 0.
+\end{equation}
+We then show that for $\alpha$ in the given form, the function $f(w) = -w^{\alpha - 1}$ is non-increasing.
+To this end, we obtain the first derivative
+\begin{equation}
+	f'(w) = -(\alpha - 1) w^{\alpha-2} = -(\alpha - 1)w^{\frac{2a-4b+2}{2b-1}} \leq 0,
+\end{equation}
+because $\alpha > 1$ and
+\begin{equation}
+	w^{\frac{2a-4b+2}{2b-1}} = \left(w^{2a-4b+2}\right)^{\frac{1}{2b-1}} = \left(w^{\frac{1}{2b-1}}\right)^{2(a-2b+1)} \geq 0,
+\end{equation}
+where each expression is well defined because the rational exponent has even numerator and odd denominator.
+\nick{This step is the reason why $\alpha =$ odd$/$odd or $\alpha < 1$ do not work. $\alpha - 2$ may be less than 0, is this a problem?}
+
+Therefore, whenever $w_i \geq w_j$, we have that 
 \begin{equation}

### 2021-06-05 magic_paper.tex
added on explanation of even/odd working, corrected mistakes ontheorem bridging H_a and D_a

@@
 
-% Notation consistency (R is rate not bound, noise vs error, \ln{} -> \ln, italics)
+% Notation consistency (R is rate not bound, noise vs error, \ln{} -> \ln, italics, keep \bmx for vectors?)
 % UK vs US english
@@
 \begin{equation}
-    \mana{\rho} \coloneqq \ln{(2\hspace{1pt}\sn{\rho}+1)},
+    \mana{\rho} \coloneqq \ln (2\hspace{1pt}\sn{\rho}+1),
 \end{equation}
@@
 \begin{equation}
-	R(\epsilon, \epsilon') \leq \frac{\ln{(3-4\epsilon)}}{\ln{(3-4\epsilon')}}.
+	R(\epsilon, \epsilon') \leq \frac{\ln (3-4\epsilon)}{\ln (3-4\epsilon')}.
 \end{equation}
@@
 \begin{equation}\label{eq:rate_bounds_proof}
-	R \leq \dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (\phi - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (\phi' - F')},
+	R \leq \dfrac{\ln \big( 1-\frac{4}{3}\epsilon \big) + \beta (\phi - F)}{\ln \big( 1-\frac{4}{3}\epsilon' \big) + \beta (\phi' - F')},
 \end{equation}
@@
 
-Since the magic monotone mana is a monotonic function of sum-negativity, $\rm{mana}(\rho) \coloneqq \ln{(2\hspace{1pt}\sn{\rho}+1)}$, we see that mana corresponds precisely to the peak of the Lorenz curve $L_{\rho|\sigma}(x)$.
+Since the magic monotone mana is a monotonic function of sum-negativity, $\rm{mana}(\rho) \coloneqq \ln \hspace{1pt}(2\hspace{1pt}\sn{\rho}+1)$, we see that mana corresponds precisely to the peak of the Lorenz curve $L_{\rho|\sigma}(x)$.
 Therefore, mana is one of $d^{2n}$ constraints, so majorization is strictly a stronger constraint in any fragment.
@@
 \begin{equation}
-	\Gamma_{\bma}(\x) := \bigoplus_{i=1}^N x_i \eta_{b_i},
+	\Gamma_{\bma}(\x) := \bigoplus_{i=1}^N x_i \eta_{a_i},
 \end{equation}
@@
 
-Given a fixed $\alpha$ for which $H_\alpha(\x)$ is well-defined, the function $H_\alpha$ is real-valued, smooth on the interior of $\mathcal{Q}^\downarrow$ and symmetric on permutation components of $\x$.
+Given a fixed $\alpha$ for which $H_\alpha(\x)$ is well-defined, the function $H_\alpha$ is real-valued, smooth on the interior of $\mathcal{Q}^\downarrow$ and symmetric on any component permutation of $\x$.
 
@@
 We then show that for $\alpha$ in the given form, the function $f(w) = -w^{\alpha - 1}$ is non-increasing.
-To this end, we obtain the first derivative
+To this end, we first note that, for $\alpha > 1$, $f(w)$ has no discontinuities and we then obtain the first derivative
 \begin{equation}
@@
 \end{equation}
-where each expression is well defined because the rational exponent has even numerator and odd denominator.
-\nick{This step is the reason why $\alpha =$ odd$/$odd or $\alpha < 1$ do not work. $\alpha - 2$ may be less than 0, is this a problem?}
+where each expression is well-defined because the rational exponent has odd denominator.
+
+\nick{This step is the reason why $\alpha =$ odd$/$odd or $\alpha < 1$ do not work.
+
+Example 1: if $\alpha =$ odd$/$odd, then $f(w)$ is not monotonous because the sign of $f'(w)$ would depend on the sign of $w$. 
+In~\cref{tab:test}, this case fails when $w_i > 0 > -w_i > w_{i+1}$.
+
+Example 2: if $\alpha =$ even$/$odd and $\alpha < 1$, then  $f(w)$ is not monotonous across $0$ because and in fact $\lim_{w\rightarrow 0^+} f(w) = -\infty$, while $\lim_{w\rightarrow 0^-} f(w) = +\infty$.
+In~\cref{tab:test}, this case fails when $w_i > 0 > w_{i+1}$.
+}
 
@@
 \end{equation}
-for any quasi-distributions $\w, \w'$.
+for any quasi-distributions $\w, \w'$ that obey $\w \succ \w'$.
 
@@
   \end{tabular}
-  \caption{\nick{NUMERICS ON SCHUR-OSTROWSKI CONDITION} Seems like $\alpha=$ even$/$odd and $\alpha > 1$ works for any combination of $w_i, w_{i+1}$ with $w_i > w_{i+1}$ and seems also that no other case works.}
+  \caption{\nick{NUMERICS ON SCHUR-OSTROWSKI CONDITION} The case $\alpha=$ even$/$odd and $\alpha > 1$ works for any combination of $w_i, w_{i+1}$ with $w_i > w_{i+1}$. 
+  All other cases do not work.}
   \label{tab:test}
@@
 \end{proof}
-Note that if $\alpha < 1$ or is of the form odd$/$even, the argument of~\cref{thm:HSchur} does not hold.
-However, the set $F := \{2a/(2b+1): a,b \in \mathbb{N} \text{ and } a>b\}$ is dense in the rationals $\mathbb{Q}_{>1}$ (which in turn is dense in $\mathbb{R}_{>1}$) as any rational $c/d$ with $c>d$ can be approximated by a sequence $f_n := c2^n / (d2^n+1)$ with every element $f_n$ in the set $F$.
+The set $F := \{2a/(2b-1): a,b \in \mathbb{N} \text{ and } a \geq b\}$ is dense in the rationals $\mathbb{Q}_{>1}$, which in turn are dense in the reals $\mathbb{R}_{>1}$, as any rational $c/d$ with $c>d$ can be approximated by a sequence $f_n := c2^n / (d2^n+1)$ with every element $f_n$ in the set $F$.
 \nick{can turn into lemma}
@@
 	Consider a general magic state distillation process that converts magic state $\rho^{\otimes n} \longrightarrow \rho'^{\otimes n'}$ as well as equilibrium state $\tau^{\otimes n} \longrightarrow \tau'^{\otimes n'}$, where we assume that $W_{\tau^{\otimes n}}(\bmx) = a_{\bmx}/K$ and $W_{\tau'^{\otimes n'}}(\bmx) = a_{\bmx}/K$ for positive integers $a_{\bmx}, a_{\bmx}'$ and $K = \sum_{\bmx} a_{\bmx} = \sum_{\bmx} a_{\bmx}'$.
+\nick{It may be more convenient to consider $W_{\tau}(\bmx') = a_{\bmx'}/K$, so that $K$ ends up raised to the power of $n$}
 
@@
 
-	We have that $(W_{\rho_n}, W_{\tau_n}) \succ W_{\rho'_{n'}}, W_{\tau'_{n'}})$, or equivalently $\Gamma_{\bma}(W_{\rho_n}) \succ \Gamma_{\bma'}(W_{\rho'_{n'}})$, where
-\begin{align}
-	\Gamma_{\bma}(W_{\rho_n}) &= \bigoplus_{\bmx} W_{\rho_n}(\bmx) \left(\frac{1}{KW_{\tau_n}(\bmo)}, \dots, \frac{1}{KW_{\tau_n}((d,d))} \right)\nonumber\\
-	&= \frac{1}{K}\bigoplus_{\bmx}\bigoplus_{\bmy} \frac{W_{\rho_n}(\bmx)}{W_{\tau_n}(\bmy)},
+	We have that 
+\begin{equation}	
+	\Big(W_{\rho_n}(\bmx), W_{\tau_n}(\bmx')\Big) \succ \Big(W_{\rho'_{n'}}(\bmx), W_{\tau'_{n'}}(\bmx')\Big)
+\end{equation}	
+or equivalently $\Gamma_{\bma}(W_{\rho_n}(\bmx)) \succ \Gamma_{\bma'}(W_{\rho'_{n'}}(\bmx))$ for all $\bmx$, where
+\begin{align}
+	\Gamma_{\bma}(W_{\rho_n}) &= \bigoplus_{\bmx} W_{\rho_n}(\bmx) \left(\frac{1}{KW_{\tau_n}(\bmx)}, \dots, \frac{1}{KW_{\tau_n}(\bmx)} \right)\nonumber\\
+	&= \frac{1}{K}\bigoplus_{\bmx} \Big( W_{\rho_n|\tau_n}(\bmx), \dots, W_{\rho_n|\tau_n}(\bmx) \Big)
 \end{align}
@@
 Therefore,
-\begin{equation}
-	H_{\alpha}(\Gamma_{\bma}(W_{\rho_n})) = \frac{1}{1-\alpha} \log_2 \left( \frac{1}{K^\alpha} \sum_{\bmx, \bmy} \frac{W_{\rho_n}(\bmx)^\alpha}{W_{\tau_n}(\bmy)^\alpha} \right),
-\end{equation}
+\begin{align}
+	&H_{\alpha}(\Gamma_{\bma}(W_{\rho_n})) = \frac{1}{1-\alpha} \log_2 \left( \frac{d^{2n}}{K^\alpha} \sum_{\bmx} \big[ W_{\rho_n|\tau_n}(\bmx) \big]^\alpha \right) = \nonumber\\
+	&\frac{1}{1-\alpha} \log_2 \left( \frac{d^{2n}}{K^\alpha} \sum_{\bmx_1, \dots, \bmx_n} \big[ W_{\rho|\tau}(\bmx_1) \dots W_{\rho|\tau}(\bmx_n) \big]^\alpha \right)
+\end{align}
 while
 \begin{equation}
-	D(\rho||\tau) = \frac{1}{\alpha-1} \log_2 \sum_{\bmx,\bmy} \frac{W_{\rho}(\bmx)^\alpha}{W_{\tau}(\bmy)^{\alpha-1}}.
+	D(\rho||\tau) = \frac{1}{\alpha-1} \log_2 \sum_{\bmx} \frac{W_{\rho}(\bmx)^\alpha}{W_{\tau}(\bmx)^{\alpha-1}}.
 \end{equation}

### 2021-06-05 magic_paper.tex
Quick proof that Wigner negativity coincides with Renyi entropy negativity for some \alpha

@@
 
+The following is a nice thing to establish.
+\begin{theorem} A state $\rho$ has Wigner negativity if and only if $H_\alpha (W_\rho (\x)) < 0$ for some $\alpha >1$.
+\end{theorem}
+Let's try to prove this.
+\begin{proof} If $H_\alpha (W_\rho(\x) <0 $ then this implies that $\log \sum_{\x} W_\rho (\x)^\alpha > 1$, however it is known that $H_\alpha$ is always non-negative on probability distributions and therefore $W_\rho(\x)$ must be a strict quasi-distribution with negativity.
+
+Conversely, suppose $\rho$ has negativity in its Wigner representation.
+This implies that $\sum_{\x} |W_\rho (\x)| >1$.
+We now consider $\sum_{\x} W_\rho (\x)^{a/b}$ for $a/b >1$ and $a$ even and $b$ odd.
+We have that
+\begin{align}
+\sum_{\x} W_\rho (\x)^{a/b} &= \sum_{\x} |W_\rho (\x)|^{a/b} \nonumber \\
+&= \sum_{\x} |W_\rho (\x)|^{1+ \epsilon},
+\end{align}
+where $\epsilon = a/b - 1 >0$. By choosing $a$ and $b$ appropriately we can make $\epsilon$ arbitrarily close to $0$ and therefore there exists a sequence $\epsilon_n$ such that
+\begin{equation}
+\sum_{\x} |W_\rho (\x)|^{1+ \epsilon_n} \rightarrow \sum_{\x} |W_\rho (\x)| >1.
+\end{equation}
+Therefore, $H_\alpha (W_\rho (\x)) <0 $ at some point in the sequence, which completes the proof.
+\end{proof}
+Therefore Wigner negativity coincides with negativity in at least one Renyi entropy.
+\ddd{[Looking at this limit it almost feels like the $\alpha \rightarrow 0$ limit is actually giving mana....modulo the technical problem of taking the limit without calculus.
+I will think more about this point.]}
 \subsubsection{Extention to general relative majorization}

### 2021-06-05 magic_paper.tex
added connection between Ha and Da and proof of general bounds

--- 2021-06-05 magic_paper.tex
@@
 \begin{theorem} Let $\tau$ be in the interior of $\F$, and define $D_\infty(\rho,\tau) := D_\infty(W_\rho(\x) || W_\tau (\x))$.
-Then $D_\infty(\rho, \tau)$ is well-defined for all $\rho$, and the following hold: \nick{can generalise to $D_{\alpha}$ for appropriate $\alpha$}
+Then $D_\infty(\rho, \tau)$ is well-defined for all $\rho$, and the following hold:
 \begin{enumerate}
@@
 \item $D_\infty(\rho^{\otimes 2n}, \tau^{\otimes 2n}) = n D_\infty(\rho^{\otimes 2} ,\tau^{\otimes 2})$ for any $n \in \mathbb{N}$.
+\nick{annoying that it doesn't agree with the simpler property of $D_\alpha$ for finite $\alpha$ in~\cref{thm:Da_props}}
 \item For any quantum state $\rho$, and any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$, we have $D_\infty (\rho , \tau) \ge D_\infty (\E(\rho), \E(\tau))$.
@@
 \end{proof}
-
-\newpage
-
-\subsection{Entropic bounds on quasi-distributions}
-
-We first define the classical $\alpha$-Renyi entropy in terms of the Wigner quasi-distribution of any state $\rho$ as
-\begin{equation}
-	H_\alpha(\rho) := \frac{1}{1-\alpha} \log \sum_{\bmx} W_{\rho}(\bmx)^\alpha,
-\end{equation}
-where $\alpha$ can take values of the form $2a / (2b+1)$, for non-negative integers $a,b$ to ensure that the argument of the logarithm is positive.
-Note that for any quantum state $\rho$, $H_1(\rho)$ in particular is not well-defined  \nick{Notation clashes with quantum Renyi entropies}, while for any valid $\alpha$ we have that
-\begin{equation}
-	H_0(\rho) = 2\log_2 d = H_\alpha \left( \id/d \right),
-\end{equation}
-where $d$ is the dimension of $\rho$.
-For $\rho = \rho_{\rm{S}}(\epsilon)$, we get
-\begin{equation}
-	H_{\alpha}\left(\rho_{\rm{S}}(\epsilon)\right) = \frac{1}{1-\alpha}\log_2 \left[ 8\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^\alpha + \left(-\frac{1}{3} + \frac{4}{9}\epsilon \right)^\alpha \right]
-\end{equation}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.35]{figs/test/H_vs_eps_a.pdf}
-    \caption{\ddd{[TO DO: Set $\epsilon = 0$ and determine region of $\alpha$ such that $H <0$.]} Here, the exponent is $\alpha =$ even$/$odd for $1.10 \leq \alpha \leq 1.50$.
-$H_\alpha$ is increasing in $\alpha$ and $\epsilon$ \nick{should be easy to show analytically}.
-First dashed contour from the right corresponds to $H_\alpha(\rho_{\rm{S}}(\epsilon)) = 0$.
-Specifically, $H_\alpha(\rho_{\rm{S}}(0)) = 0$ has a unique solution, which is the \nick{probably irrational - this seems problematic} solution of $3^\alpha - 2^{3-\alpha} = 1$.
-    }
-    \label{fig:lcs}
-\end{figure}
-
-We can prove additivity of $H_{\alpha}$ on quantum states.
-
-\begin{lemma}\label{H_add}
-	For any quantum states $\rho, \rho'$, we have
-	\begin{equation}
-		H_{\alpha}(\rho \otimes \rho') = H_{\alpha}(\rho) + H_{\alpha}(\rho'),
-	\end{equation}
-	where $\hspace{-1pt}\alpha\hspace{-1pt}$ is such that $\hspace{-1pt}H_\alpha(\sigma)\hspace{-2pt}$ is well-defined for all states $\sigma$.
-\end{lemma}
-\begin{proof}
-	This can be seen directly by the multiplicative property of the Wigner distribution,
-	\begin{align*}
-		H_{\alpha}&(\rho \otimes \rho') = \frac{1}{1-\alpha}\log \sum_{\bmx,\bmx'} \left[W_{\rho}(\bmx)W_{\rho}(\bmx')\right]^{\alpha} \\
-		&= \frac{1}{1-\alpha}\left( \log \sum_{\bmx}W_{\rho}(\bmx)^{\alpha} + \log \sum_{\bmx'}W_{\rho}(\bmx')^{\alpha} \right) \\
-		&= H_{\alpha}(\rho) + H_{\alpha}(\rho').
-	\end{align*}
-\end{proof}
-
-We then prove the following result connecting simple majorization to relative majorization.
-\nick{move following lemma to section on relative majorization equivalent conditions}
-\begin{lemma}
-Let $\w\in \mathbb{R}^N, \w'\in \mathbb{R}^{N'}$ be quasi-distributions and $\r\in \mathbb{R}^N, \r'\in \mathbb{R}^{N'}$ probability distributions with positive rational entries given by $r_i = a_i/K$ and $r_i' = a_i'/K$ for positive integers $a_i, a_i'$ and $K = \sum_{i=1}^N a_i = \sum_{i=1}^{N'} a_i'$.
-Then,
-\begin{equation}
-(\w, \r) \succ (\w', \r') \mbox{ if and only if } \Gamma_{\bma} (\w) \succ \Gamma_{\bma'} (\w'),
-\end{equation}
-where the embedding map $\Gamma_{\bma} :\mathbb{R}^N \rightarrow \mathbb{R}^K$ is given by
-\begin{equation}
-	\Gamma_{\bma}(\x) := \bigoplus_{i=1}^N x_i \eta_{a_i},
-\end{equation}
-with $\eta_{a_i} = (1/a_i, 1/a_i, \dots, 1/a_i)$ the uniform distribution on $a_i$ elements.
-\end{lemma}
-\begin{proof}
-	We first note that the map $\Gamma_{\bma}$ is stochastic and has a well-defined left-inverse $\Gamma^{-1}_{\bma'}: \mathbb{R}^K \rightarrow \mathbb{R}^N$ given by
-\begin{equation}
-	\Gamma^{-1}_{\bma}(\w) = \left( \sum_{i=1}^{a_1} w_i,  \sum_{i = a_1 +1}^{a_1 + a_2} \hspace{-5pt} w_i, \dots , \hspace{-15pt} \sum_{i=a_1 + \dots + a_{N-1}+1}^{K} \hspace{-10pt} w_i \right),
-\end{equation}
-that obeys $(\Gamma^{-1}_{\bma} \circ \Gamma_{\bma}) (\x) = \x$ for all $\x \in \mathbb{R}^N$.
-
-The claim is equivalent to the statement that there exists a \emph{bistochastic map} $B$ sending $\Gamma_{\bma}(\w)$ to $\Gamma_{\bma'}(\w')$ if and only if there exists a stochastic map $A$ sending $\w$ to $\w'$ and $\r$ to $\r'$.
-
-Suppose there is a stochastic map $A$ such that $A\w=\w'$ and $A\r = \r'$. 
-We define $B:\mathbb{R}^K \mapsto \mathbb{R}^K$ by $B := \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1}$ so that it is stochastic as a composition of stochastic maps and it preserves the uniform distribution in $\mathbb{R}^A$, since
-\begin{align}
-	&B(1/K, 1/K, \dots, 1/K) = \big( \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1} \big) \big( \Gamma_{\bma'}(\r) \big) = \nonumber\\
-	&\Gamma_{\bma'} (\r') = (1/K, 1/K, \dots, 1/K),
-\end{align}
-therefore $B$ is bistochastic.
-Finally, $B$ maps the embedded distributions as follows,
-\begin{equation}
-	B \Gamma_{\bma}(\w) = \big( \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1} \big) \big( \Gamma_{\bma}(\w) \big) = \Gamma_{\bma'} (\w').
-\end{equation}
-
-Conversely, suppose a bistochastic map $B$ exists sending $\Gamma_{\bma}(\w)$ to $\Gamma_{\bma'}(\w')$.
-Again, define $A: \mathbb{R}^N \mapsto \mathbb{R}^{N'}$ by $A := \Gamma_{\bma'}^{-1} \circ B \circ \Gamma_{\bma}$ so that it is stochastic as a composition of stochastic maps and $A \w = \big( \Gamma_{\bma'}^{-1} \circ B \circ \Gamma_{\bma} \big) \w = \w'$, as well as $A \r = \r'$.
-\end{proof}
-We note that the vectors $\r, \r'$ with rational components form a dense subset of the positive probability distributions, so we can appeal to the fact that experiments have a finite resolution to ignore technical details regarding the completion to arbitrary real components.
-
-\subsubsection{Unital fragment}
-
-We now make use of known results from majorization theory to establish the Schur-concavity of $H_\alpha$ on Wigner quasi-distributions where $\alpha$ is such that $H_\alpha$ is well-defined. 
-We first define the notion of \emph{Schur-convex and Schur-convave functions} on a subset $\D \subseteq \mathbb{R}^N$.
-
-\begin{definition} 
-A continuous, real-valued function $f$ defined on $\mathcal{Q} \subseteq \mathbb{R}^N$ is called Schur-convex on the domain $\mathcal{Q}$ if $\p \prec \q$ on $\mathcal{Q}$ implies that $f(\p) \le f(\q)$.
-A continuous function $f:\mathcal{Q} \rightarrow \mathbb{R}$ is called Schur-concave if $(-f)$ is Schur-convex.
-\end{definition}
-We can consider the set of all quasi-distributions, which form a hyper-plane and are given by
-\begin{equation}
-\mathcal{Q} = \left\{ \w \in \mathbb{R}^N: \sum_{i=1}^N w_i = 1 \right\}.
-\end{equation}
-For functions that are symmetric, namely $f(\p) = f(\Pi \p)$ for any component permutation $\Pi$, it suffices to restrict to the following region,
-\begin{equation}
-\mathcal{Q}^\downarrow = \{ \w \in \mathcal{Q} : w_1 \ge w_2 \ge \cdots \ge w_N\}.
-\end{equation}
-
-We now have the following theorem~\cite{cit:marshall} that provides a characterization of symmetric, Schur-convex and Schur-concave functions on quasi-distributions.
-\begin{lemma}
-Let $f$ be a real-valued continuous function defined on $\mathcal{Q}^\downarrow$ that is continuously differentiable on the interior of $\mathcal{Q}^\downarrow$. 
-Then, $f$ is Schur-convex on $\mathcal{Q}^\downarrow$ if and only if $\partial_k f(\w)$ is decreasing in $k$ for all $\w \in \mathcal{Q}^\downarrow$, namely
-\begin{equation}
-\partial_1 f(\w) \ge \partial_2 f(\w) \ge \cdots \ge \partial_N f(\w),
-\end{equation}
-for all $\w$ in the interior of $\mathcal{Q}^\downarrow$.
-\end{lemma}
-
-We can use the above to prove that $H_\alpha$ is Schur-concave on quasi-distributions for particular values of $\alpha$.
-
-\ddd{[TO-DO TIDY AND CHECK]}
-\begin{theorem}\label{thm:HSchur}
-	Let $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$.
-	Then, $H_\alpha$ is Schur-concave, i.e. for quasi-distributions $\w, \w' \in \mathbb{R}^N$, we have $H_\alpha(\w) \leq H_\alpha(\w')$, whenever $\w \succ \w'$.
-\end{theorem}
-\begin{proof}
-We have $\alpha = \frac{2a}{2b+1} \geq \frac{2b}{2b-1} > 1$ and $\alpha$ is a rational with even numerator and odd denominator, so $\sum_i x_i^\alpha > 0$ and $H_\alpha(\x)$ is well-defined for all quasi-distributions $\x$.
-
-Given a fixed $\alpha$ for which $H_\alpha(\x)$ is well-defined, the function $H_\alpha$ is real-valued, smooth on the interior of $\mathcal{Q}^\downarrow$ and symmetric on any component permutation of $\x$.
-
-Consider the partial derivatives
-\begin{equation}
-	\frac{\partial H_\alpha}{\partial w_i} = \frac{\alpha}{(\alpha-1)\sum_k{w_k^\alpha}}(-w_i^{\alpha-1}).
-\end{equation}
-We first note that for $\alpha$ in the given form, it is always true that
-\begin{equation}
-	\frac{\alpha}{(\alpha-1)\sum_k{w_k^\alpha}} > 0.
-\end{equation}
-We then show that for $\alpha$ in the given form, the function $f(w) = -w^{\alpha - 1}$ is non-increasing.
-To this end, we first note that, for $\alpha > 1$, $f(w)$ has no discontinuities and we then obtain the first derivative
-\begin{equation}
-	f'(w) = -(\alpha - 1) w^{\alpha-2} = -(\alpha - 1)w^{\frac{2a-4b+2}{2b-1}} \leq 0,
-\end{equation}
-because $\alpha > 1$ and
-\begin{equation}
-	w^{\frac{2a-4b+2}{2b-1}} = \left(w^{2a-4b+2}\right)^{\frac{1}{2b-1}} = \left(w^{\frac{1}{2b-1}}\right)^{2(a-2b+1)} \geq 0,
-\end{equation}
-where each expression is well-defined because the rational exponent has odd denominator.
-
-\nick{This step is the reason why $\alpha =$ odd$/$odd or $\alpha < 1$ do not work.
-
-Example 1: if $\alpha =$ odd$/$odd, then $f(w)$ is not monotonous because the sign of $f'(w)$ would depend on the sign of $w$. 
-In~\cref{tab:test}, this case fails when $w_i > 0 > -w_i > w_{i+1}$.
-
-Example 2: if $\alpha =$ even$/$odd and $\alpha < 1$, then  $f(w)$ is not monotonous across $0$ because and in fact $\lim_{w\rightarrow 0^+} f(w) = -\infty$, while $\lim_{w\rightarrow 0^-} f(w) = +\infty$.
-In~\cref{tab:test}, this case fails when $w_i > 0 > w_{i+1}$.
-}
-
-Therefore, whenever $w_i \geq w_j$, we have that 
-\begin{equation}
-	-w_i^{\alpha-1} \leq -w_j^{\alpha-1},
-\end{equation}
-which leads to
-\begin{equation}
-	\frac{\partial H_\alpha}{\partial w_i} \leq \frac{\partial H_\alpha}{\partial w_j}.
-\end{equation}
-Therefore, $H_\alpha$ is Schur-concave and
-\begin{equation}
-	H_\alpha(\w) \leq H_\alpha(\w'),
-\end{equation}
-for any quasi-distributions $\w, \w'$ that obey $\w \succ \w'$.
 
@@
   \caption{\nick{NUMERICS ON SCHUR-OSTROWSKI CONDITION} The case $\alpha=$ even$/$odd and $\alpha > 1$ works for any combination of $w_i, w_{i+1}$ with $w_i > w_{i+1}$. 
-  All other cases do not work.}
+  All other cases do not work.
+  I put it here cause it's clunky}
   \label{tab:test}
@@
 
+\newpage
+
+\subsection{Entropic bounds on quasi-distributions}
+
+We prove the following result connecting simple majorization to relative majorization.
+\nick{move following lemma to section on relative majorization equivalent conditions}
+\begin{lemma}
+Let $\w\in \mathbb{R}^N, \w'\in \mathbb{R}^{N'}$ be quasi-distributions and $\r\in \mathbb{R}^N, \r'\in \mathbb{R}^{N'}$ probability distributions with positive rational entries given by $r_i = a_i/K$ and $r_i' = a_i'/K$ for positive integers $a_i, a_i'$ and $K = \sum_{i=1}^N a_i = \sum_{i=1}^{N'} a_i'$.
+Then,
+\begin{equation}
+(\w, \r) \succ (\w', \r') \mbox{ if and only if } \Gamma_{\bma} (\w) \succ \Gamma_{\bma'} (\w'),
+\end{equation}
+where the embedding map $\Gamma_{\bma} :\mathbb{R}^N \rightarrow \mathbb{R}^K$ is given by
+\begin{equation}
+	\Gamma_{\bma}(\x) := \bigoplus_{i=1}^N x_i \eta_{a_i},
+\end{equation}
+with $\eta_{a_i} = (1/a_i, 1/a_i, \dots, 1/a_i)$ the uniform distribution on $a_i$ elements.
+\end{lemma}
+\begin{proof}
+	We first note that the map $\Gamma_{\bma}$ is stochastic and has a well-defined left-inverse $\Gamma^{-1}_{\bma'}: \mathbb{R}^K \rightarrow \mathbb{R}^N$ given by
+\begin{equation}
+	\Gamma^{-1}_{\bma}(\w) = \left( \sum_{i=1}^{a_1} w_i,  \sum_{i = a_1 +1}^{a_1 + a_2} \hspace{-5pt} w_i, \dots , \hspace{-15pt} \sum_{i=a_1 + \dots + a_{N-1}+1}^{K} \hspace{-10pt} w_i \right),
+\end{equation}
+that obeys $(\Gamma^{-1}_{\bma} \circ \Gamma_{\bma}) (\x) = \x$ for all $\x \in \mathbb{R}^N$.
+
+The claim is equivalent to the statement that there exists a \emph{bistochastic map} $B$ sending $\Gamma_{\bma}(\w)$ to $\Gamma_{\bma'}(\w')$ if and only if there exists a stochastic map $A$ sending $\w$ to $\w'$ and $\r$ to $\r'$.
+
+Suppose there is a stochastic map $A$ such that $A\w=\w'$ and $A\r = \r'$. 
+We define $B:\mathbb{R}^K \mapsto \mathbb{R}^K$ by $B := \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1}$ so that it is stochastic as a composition of stochastic maps and it preserves the uniform distribution in $\mathbb{R}^A$, since
+\begin{align}
+	&B(1/K, 1/K, \dots, 1/K) = \big( \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1} \big) \big( \Gamma_{\bma'}(\r) \big) = \nonumber\\
+	&\Gamma_{\bma'} (\r') = (1/K, 1/K, \dots, 1/K),
+\end{align}
+therefore $B$ is bistochastic.
+Finally, $B$ maps the embedded distributions as follows,
+\begin{equation}
+	B \Gamma_{\bma}(\w) = \big( \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1} \big) \big( \Gamma_{\bma}(\w) \big) = \Gamma_{\bma'} (\w').
+\end{equation}
+
+Conversely, suppose a bistochastic map $B$ exists sending $\Gamma_{\bma}(\w)$ to $\Gamma_{\bma'}(\w')$.
+Again, define $A: \mathbb{R}^N \mapsto \mathbb{R}^{N'}$ by $A := \Gamma_{\bma'}^{-1} \circ B \circ \Gamma_{\bma}$ so that it is stochastic as a composition of stochastic maps and $A \w = \big( \Gamma_{\bma'}^{-1} \circ B \circ \Gamma_{\bma} \big) \w = \w'$, as well as $A \r = \r'$.
+\end{proof}
+We note that the vectors $\r, \r'$ with rational components form a dense subset of the positive probability distributions, so we can appeal to the fact that experiments have a finite resolution to ignore technical details regarding the completion to arbitrary real components.
+
+\subsubsection{Classical $\alpha$-Renyi entropy and divergence for quasi-distributions}
+
+We first define the classical $\alpha$-Renyi entropy in terms of the Wigner quasi-distribution of any state $\rho$ as
+\begin{equation}
+	H_\alpha(\rho) := \frac{1}{1-\alpha} \log \sum_{\bmx} W_{\rho}(\bmx)^\alpha,
+\end{equation}
+where $\alpha$ can take values of the form $2a / (2b+1)$, for non-negative integers $a,b$ to ensure that the argument of the logarithm is positive.
+Note that for any quantum state $\rho$, $H_1(\rho)$ in particular is not well-defined  \nick{Notation clashes with quantum Renyi entropies}, while for any valid $\alpha$ we have that
+\begin{equation}
+	H_0(\rho) = 2\log_2 d = H_\alpha \left( \id/d \right),
+\end{equation}
+where $d$ is the dimension of $\rho$.
+For $\rho = \rho_{\rm{S}}(\epsilon)$, we get
+\begin{equation}
+	H_{\alpha}\left(\rho_{\rm{S}}(\epsilon)\right) = \frac{1}{1-\alpha}\log_2 \left[ 8\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^\alpha + \left(-\frac{1}{3} + \frac{4}{9}\epsilon \right)^\alpha \right]
+\end{equation}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.35]{figs/test/H_vs_eps_a.pdf}
+    \caption{\ddd{[TO DO: Set $\epsilon = 0$ and determine region of $\alpha$ such that $H <0$.]} Here, the exponent is $\alpha =$ even$/$odd for $1.10 \leq \alpha \leq 1.50$.
+$H_\alpha$ is increasing in $\alpha$ and $\epsilon$ \nick{should be easy to show analytically}.
+First dashed contour from the right corresponds to $H_\alpha(\rho_{\rm{S}}(\epsilon)) = 0$.
+Specifically, $H_\alpha(\rho_{\rm{S}}(0)) = 0$ has a unique solution, which is the \nick{probably irrational} solution of $3^\alpha - 2^{3-\alpha} = 1$.
+    }
+    \label{fig:lcs}
+\end{figure}
+
+We can prove additivity of $H_{\alpha}$ on quantum states.
+
+\begin{lemma}\label{H_add}
+	For any quantum states $\rho, \rho'$, we have
+	\begin{equation}
+		H_{\alpha}(\rho \otimes \rho') = H_{\alpha}(\rho) + H_{\alpha}(\rho'),
+	\end{equation}
+	where $\hspace{-1pt}\alpha\hspace{-1pt}$ is such that $\hspace{-1pt}H_\alpha(\sigma)\hspace{-2pt}$ is well-defined for all states $\sigma$.
+\end{lemma}
+\begin{proof}
+	This can be seen directly by the multiplicative property of the Wigner distribution,
+	\begin{align*}
+		H_{\alpha}&(\rho \otimes \rho') = \frac{1}{1-\alpha}\log \sum_{\bmx,\bmx'} \left[W_{\rho}(\bmx)W_{\rho}(\bmx')\right]^{\alpha} \\
+		&= \frac{1}{1-\alpha}\left( \log \sum_{\bmx}W_{\rho}(\bmx)^{\alpha} + \log \sum_{\bmx'}W_{\rho}(\bmx')^{\alpha} \right) \\
+		&= H_{\alpha}(\rho) + H_{\alpha}(\rho').
+	\end{align*}
+\end{proof}
+
+We now make use of known results from majorization theory to establish the Schur-concavity of $H_\alpha$ on Wigner quasi-distributions where $\alpha$ is such that $H_\alpha$ is well-defined. 
+We first define the notion of \emph{Schur-convex and Schur-convave functions} on a subset $\D \subseteq \mathbb{R}^N$.
+
+\begin{definition} 
+A continuous, real-valued function $f$ defined on $\mathcal{Q} \subseteq \mathbb{R}^N$ is called Schur-convex on the domain $\mathcal{Q}$ if $\p \prec \q$ on $\mathcal{Q}$ implies that $f(\p) \le f(\q)$.
+A continuous function $f:\mathcal{Q} \rightarrow \mathbb{R}$ is called Schur-concave if $(-f)$ is Schur-convex.
+\end{definition}
+We can consider the set of all quasi-distributions, which form a hyper-plane and are given by
+\begin{equation}
+\mathcal{Q} = \left\{ \w \in \mathbb{R}^N: \sum_{i=1}^N w_i = 1 \right\}.
+\end{equation}
+For functions that are symmetric, namely $f(\p) = f(\Pi \p)$ for any component permutation $\Pi$, it suffices to restrict to the following region,
+\begin{equation}
+\mathcal{Q}^\downarrow = \{ \w \in \mathcal{Q} : w_1 \ge w_2 \ge \cdots \ge w_N\}.
+\end{equation}
+
+We now have the following theorem~\cite{cit:marshall} that provides a characterization of symmetric, Schur-convex and Schur-concave functions on quasi-distributions.
+\begin{lemma}
+Let $f$ be a real-valued continuous function defined on $\mathcal{Q}^\downarrow$ that is continuously differentiable on the interior of $\mathcal{Q}^\downarrow$. 
+Then, $f$ is Schur-convex on $\mathcal{Q}^\downarrow$ if and only if $\partial_k f(\w)$ is decreasing in $k$ for all $\w \in \mathcal{Q}^\downarrow$, namely
+\begin{equation}
+\partial_1 f(\w) \ge \partial_2 f(\w) \ge \cdots \ge \partial_N f(\w),
+\end{equation}
+for all $\w$ in the interior of $\mathcal{Q}^\downarrow$.
+\end{lemma}
+
+We can use the above to prove that $H_\alpha$ is Schur-concave on quasi-distributions for particular values of $\alpha$.
+
+\begin{theorem}\label{thm:HSchur}
+	Let $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$.
+	Then, $H_\alpha$ is Schur-concave, i.e. for quasi-distributions $\w, \w' \in \mathbb{R}^N$, we have $H_\alpha(\w) \leq H_\alpha(\w')$, whenever $\w \succ \w'$.
+\end{theorem}
+\begin{proof}
+We have $\alpha = \frac{2a}{2b+1} \geq \frac{2b}{2b-1} > 1$ and $\alpha$ is a rational with even numerator and odd denominator, so $\sum_i x_i^\alpha > 0$ and $H_\alpha(\x)$ is well-defined for all quasi-distributions $\x$.
+
+Given a fixed $\alpha$ for which $H_\alpha(\x)$ is well-defined, the function $H_\alpha$ is real-valued, smooth on the interior of $\mathcal{Q}^\downarrow$ and symmetric on any component permutation of $\x$.
+
+Consider the partial derivatives
+\begin{equation}
+	\frac{\partial H_\alpha}{\partial w_i} = \frac{\alpha}{(\alpha-1)\sum_k{w_k^\alpha}}(-w_i^{\alpha-1}).
+\end{equation}
+We first note that for $\alpha$ in the given form, it is always true that
+\begin{equation}
+	\frac{\alpha}{(\alpha-1)\sum_k{w_k^\alpha}} > 0.
+\end{equation}
+We then show that for $\alpha$ in the given form, the function $f(w) = -w^{\alpha - 1}$ is non-increasing.
+To this end, we first note that, for $\alpha > 1$, $f(w)$ has no discontinuities and we then obtain the first derivative
+\begin{equation}
+	f'(w) = -(\alpha - 1) w^{\alpha-2} = -(\alpha - 1)w^{\frac{2a-4b+2}{2b-1}} \leq 0,
+\end{equation}
+because $\alpha > 1$ and
+\begin{equation}
+	w^{\frac{2a-4b+2}{2b-1}} = \left(w^{2a-4b+2}\right)^{\frac{1}{2b-1}} = \left(w^{\frac{1}{2b-1}}\right)^{2(a-2b+1)} \geq 0,
+\end{equation}
+where each expression is well-defined because the rational exponent has odd denominator.
+
+\nick{This step is the reason why $\alpha =$ odd$/$odd or $\alpha < 1$ do not work.
+
+Example 1: if $\alpha =$ odd$/$odd, then $f(w)$ is not monotonous because the sign of $f'(w)$ would depend on the sign of $w$. 
+In~\cref{tab:test}, this case fails when $w_i > 0 > -w_i > w_{i+1}$.
+
+Example 2: if $\alpha =$ even$/$odd and $\alpha < 1$, then  $f(w)$ is not monotonous across $0$ because and in fact $\lim_{w\rightarrow 0^+} f(w) = -\infty$, while $\lim_{w\rightarrow 0^-} f(w) = +\infty$.
+In~\cref{tab:test}, this case fails when $w_i > 0 > w_{i+1}$.
+}
+
+Therefore, whenever $w_i \geq w_j$, we have that 
+\begin{equation}
+	-w_i^{\alpha-1} \leq -w_j^{\alpha-1},
+\end{equation}
+which leads to
+\begin{equation}
+	\frac{\partial H_\alpha}{\partial w_i} \leq \frac{\partial H_\alpha}{\partial w_j}.
+\end{equation}
+Therefore, $H_\alpha$ is Schur-concave and
+\begin{equation}
+	H_\alpha(\w) \leq H_\alpha(\w'),
+\end{equation}
+for any quasi-distributions $\w, \w'$ that obey $\w \succ \w'$.
 \end{proof}
@@
 
-We can now derive the following entropic bounds on magic state transformations.
+Now we define the classical $\alpha$-Renyi divergence in terms of the Wigner quasi-distribution of any magic state $\rho$ and the Wigner probability distribution of any equilibrium state $\tau$ as
+\begin{equation}
+	D_\alpha(\rho || \tau) := \frac{1}{\alpha - 1} \log_2 \sum_{\bmx} W_{\rho}(\bmx)^\alpha W_{\tau}(\bmx)^{1-\alpha},
+\end{equation}
+where $\alpha$ can take values of the form $2a / (2b+1)$, for non-negative integers $a,b$ to ensure that the argument of the logarithm is positive.
+\nick{Notation clashes with quantum Renyi divergence}
+
+We can connect the $\alpha$-Renyi entropy and divergence for quasi-distributions via the following result.
+
+\begin{theorem}\label{thm:H2D}
+	Let $\w\in \mathbb{R}^N$ be a quasi-distribution and $\r \in \mathbb{R}^N$ a probability distribution with positive rational entries given by $r_i = a_i/K$ for positive integers $a_i$ and $K = \sum_{i=1}^N a_i$.
+	Then,
+	\begin{equation}
+		H_\alpha(\Gamma_{\bma}(\w)) = K - D_\alpha(\w ||\r),
+	\end{equation}
+	where $\alpha = 2c / (2d+1)$ for non-negative integers $c,d$ such that $H_\alpha(\x)$ is well-defined for all $\x$.
+\end{theorem}
+\begin{proof}
+	For the given form of $\alpha$ and positive $r_i,\ i=1,\dots,N$, $D_\alpha(\x ||\r)$ is well-defined for all $\x$.
+
+	The expression follows from the definition of $\Gamma_{\bma}$ which gives
+	\begin{equation}
+		\Gamma_{\bma}(\w) = \bigoplus_{i=1}^N w_i (1/a_i, 1/a_i, \dots, 1/a_i).
+	\end{equation}
+	This directly leads to
+	\begin{align}
+		H_\alpha(\Gamma_{\bma}(\w)) &= \frac{1}{1-\alpha} \log_2 \sum_{i=1}^N a_i \left( \frac{w_i}{a_i} \right)^\alpha \nonumber\\
+		&= \frac{1}{1-\alpha} \log_2 \sum_{i=1}^N w_i^{\alpha} a_i^{1-\alpha} \nonumber\\
+		&= \frac{1}{1-\alpha} \log_2 K^{1-\alpha} \sum_{i=1}^N w_i^{\alpha} \nonumber\\
+		&= K + \frac{1}{1-\alpha} \log_2 \sum_{i=1}^N w_i^{\alpha} r_i^{1-\alpha} \nonumber\\
+		&= K - D_\alpha(\w ||\r).
+	\end{align}
+\end{proof}
+
+\begin{theorem}\label{thm:Da_props} 
+	Let $\tau$ be a state in the interior of $\F$ and $\alpha = 2a / (2b+1)$ for non-negative integers $a,b$
+Then, the $\alpha$-Renyi divergence $D_\alpha(\rho, \tau)$ is well-defined for all states $\rho$, and the following hold:
+\begin{enumerate}
+\item $D_\alpha(\rho || \tau) \ge 0$ for all quantum states $\rho$.
+\item  $D_\alpha(\rho || \tau) = 0$ if and only if $\rho =\tau$.
+\item $D_\alpha(\rho^{\otimes n} || \tau^{\otimes n}) = n D_\alpha(\rho, \tau)$ for any $n \in \mathbb{N}$.
+\item $D_\alpha(\rho || \tau) \geq D_\alpha (\E(\rho) || \E(\tau))$ for any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$.
+\end{enumerate}
+\end{theorem}
+\begin{proof}
+	Since $\tau$ is in the interior of $\F$, its Wigner function obeys $W_\tau(\x) >0$ for all points $\x$ in the phase space. 
+In general, $W_\rho(\x)$ is a quasi-distribution, but the given form of $\alpha$ ensures that $W_{\rho}(\bmx)^\alpha \geq 0$. 
+Therefore $D_\alpha (\rho || \tau)$ is always well-defined.
+
+1. \nick{looks true numerically, maybe can use~\cref{thm:H2D}}
+
+2. Assume $D_\alpha (\rho,\tau) = 0$.
+Then,
+\begin{equation}
+	\sum_{\bmx} W_{\tau}(\bmx) \left( \frac{W_\rho(\x)}{W_\tau(\x)} \right)^\alpha = 1,
+\end{equation}
+\nick{so...}.
+The converse holds by inspection.
+
+3. This property follows from the multiplicativity of the WIgner distribution.
+In particular,
+\begin{align}
+	&D_\alpha(\rho^{\otimes n} || \tau^{\otimes n}) &= \frac{1}{\alpha - 1} \log_2 \sum_{\bmx} W_{\rho^{\otimes n}}(\bmx)^\alpha W_{\tau^{\otimes n}}(\bmx)^{1-\alpha} = \nonumber\\
+	&= n D_{\alpha}(\rho || \tau). \nick{complete steps}
+\end{align}
+
+4. \nick{This must hold due to~\cref{thm:H2D}}
+\end{proof}
+
+\subsubsection{General entropic bounds}
+
+We first derive the following entropic bounds on magic state transformations for unital processes.
 \begin{theorem}
@@
 	\begin{equation}
-		R \leq \frac{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho \right)}{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho') \right)} = \frac{D_{\alpha}(\rho||\id/3)}{D_{\alpha}(\rho'||\id/3)},
+		R \leq \frac{D_{\alpha}(\rho||\id/3)}{D_{\alpha}(\rho'||\id/3)},
 	\end{equation}
@@
 \begin{equation}
-	\frac{n'}{n} \leq \frac{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho \right)}{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho' \right)}.
-\end{equation}
-\end{proof}
-
-\subsubsection{Extention to general relative majorization}
-
-Therefore if we have a Schur-Concave function $f(\x)$ for majorization of quasi-distributions then we can define a monotonic function for relative majorization via composition with $\Gamma_{\mathbf{a}}$ and its inverse.
+	\frac{n'}{n} \leq \frac{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho \right)}{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho' \right)} = \frac{D_{\alpha}(\rho||\id/3)}{D_{\alpha}(\rho'||\id/3)}.
+\end{equation}
+\end{proof}
+
+\ddd{Therefore if we have a Schur-Concave function $f(\x)$ for majorization of quasi-distributions then we can define a monotonic function for relative majorization via composition with $\Gamma_{\mathbf{a}}$ and its inverse.
 This should provide relative majorization monotones from which we can obtain distillation bounds, such as
@@
 	R \le \frac{F_\alpha(\tau) - F_\alpha (\rho)}{F_\alpha(\tau') - F_\alpha (\rho')}.
-\end{equation}
-\ddd{[To be checked...transition from entropies to free energies less obvious from this route...needs reflection]}
-
-This is probably all we need to show:
-\begin{equation}
-H_\alpha(\Gamma_{\mathbf{a}}(\p)) = D_\alpha(\p ||\r),
-\end{equation}
-where we define the Renyi relative entropy
-\begin{equation}
-D_\alpha (\p || \r) := \frac{1}{\alpha -1} \log \sum_i p_i^\alpha q_i^{1-\alpha}.
-\end{equation}
-This probably follows from the details of how the $\Gamma_{\mathbf{a}}$ relates to $\r$. Needs expanding carefully.
+\end{equation}}
+\nick{I don't understand where the free energies came from. Are they known to be Schur-concave?}
 
 \begin{theorem}
-	Consider a general magic state distillation process that converts magic state $\rho^{\otimes n} \longrightarrow \rho'^{\otimes n'}$ as well as equilibrium state $\tau^{\otimes n} \longrightarrow \tau'^{\otimes n'}$, where we assume that $W_{\tau^{\otimes n}}(\bmx) = a_{\bmx}/K$ and $W_{\tau'^{\otimes n'}}(\bmx) = a_{\bmx}/K$ for positive integers $a_{\bmx}, a_{\bmx}'$ and $K = \sum_{\bmx} a_{\bmx} = \sum_{\bmx} a_{\bmx}'$.
-\nick{It may be more convenient to consider $W_{\tau}(\bmx') = a_{\bmx'}/K$, so that $K$ ends up raised to the power of $n$}
+	Consider a general magic state distillation process that converts a magic state $\rho^{\otimes n} \longrightarrow \rho'^{\otimes n'}$ as well as an equilibrium state $\tau^{\otimes n} \longrightarrow \tau'^{\otimes n'}$
 
@@
 	\begin{equation}
-		R \leq \text{\nick{BOUND}},
+		R \leq \frac{D_{\alpha}(\rho||\tau)}{D_{\alpha}(\rho'||\tau')},
 	\end{equation}
@@
 \end{equation}	
-or equivalently $\Gamma_{\bma}(W_{\rho_n}(\bmx)) \succ \Gamma_{\bma'}(W_{\rho'_{n'}}(\bmx))$ for all $\bmx$, where
-\begin{align}
-	\Gamma_{\bma}(W_{\rho_n}) &= \bigoplus_{\bmx} W_{\rho_n}(\bmx) \left(\frac{1}{KW_{\tau_n}(\bmx)}, \dots, \frac{1}{KW_{\tau_n}(\bmx)} \right)\nonumber\\
-	&= \frac{1}{K}\bigoplus_{\bmx} \Big( W_{\rho_n|\tau_n}(\bmx), \dots, W_{\rho_n|\tau_n}(\bmx) \Big)
-\end{align}
-and similarly for $\Gamma_{\bma'}(W_{\rho'_{n'}})$.
-Therefore,
-\begin{align}
-	&H_{\alpha}(\Gamma_{\bma}(W_{\rho_n})) = \frac{1}{1-\alpha} \log_2 \left( \frac{d^{2n}}{K^\alpha} \sum_{\bmx} \big[ W_{\rho_n|\tau_n}(\bmx) \big]^\alpha \right) = \nonumber\\
-	&\frac{1}{1-\alpha} \log_2 \left( \frac{d^{2n}}{K^\alpha} \sum_{\bmx_1, \dots, \bmx_n} \big[ W_{\rho|\tau}(\bmx_1) \dots W_{\rho|\tau}(\bmx_n) \big]^\alpha \right)
-\end{align}
-while
-\begin{equation}
-	D(\rho||\tau) = \frac{1}{\alpha-1} \log_2 \sum_{\bmx} \frac{W_{\rho}(\bmx)^\alpha}{W_{\tau}(\bmx)^{\alpha-1}}.
-\end{equation}
-\nick{correct mistakes, bridge gaps}
+or equivalently $\Gamma_{\bma}(W_{\rho_n}(\bmx)) \succ \Gamma_{\bma'}(W_{\rho'_{n'}}(\bmx))$ for all $\bmx$.
+
+For the given form of $\alpha$, $H_{\alpha}$ is Schur-concave due to~\cref{thm:HSchur}, so
+\begin{equation}
+	H_{\alpha}(\Gamma_{\bma}(W_{\rho_n})) \leq H_{\alpha}(\Gamma_{\bma'}(W_{\rho'_{n'}})),
+\end{equation}
+and we can use~\cref{thm:H2D} to rewrite the inequality as
+\begin{equation}
+	K - D_{\alpha}(W_{\rho_n} || W_{\tau_n}) \leq K - D_{\alpha}(W_{\rho'_{n'}} || W_{\tau'_{n'}}),
+\end{equation}.
+Due to~\cref{thm:Da_props}, we can rewrite the inequality as
+\begin{equation}
+	K - nD_{\alpha}(W_{\rho} || W_{\tau_n}) \leq K - n'D_{\alpha}(W_{\rho'} || W_{\tau'_{n'}}),
+\end{equation}
+and then it is clear that we can rearrange it to
+\begin{equation}
+	\frac{n'}{n} \leq \frac{D_{\alpha}(\rho||\tau)}{D_{\alpha}(\rho'||\tau')}.
+\end{equation}
 \end{proof}

### 2021-06-05 magic_paper.tex

@@
 \begin{align}
-	&D_\alpha(\rho^{\otimes n} || \tau^{\otimes n}) &= \frac{1}{\alpha - 1} \log_2 \sum_{\bmx} W_{\rho^{\otimes n}}(\bmx)^\alpha W_{\tau^{\otimes n}}(\bmx)^{1-\alpha} = \nonumber\\
+	&D_\alpha(\rho^{\otimes n} || \tau^{\otimes n}) = \nonumber\\
+	&\frac{1}{\alpha - 1} \log_2 \sum_{\bmx} W_{\rho^{\otimes n}}(\bmx)^\alpha W_{\tau^{\otimes n}}(\bmx)^{1-\alpha} = \nonumber\\
 	&= n D_{\alpha}(\rho || \tau). \nick{complete steps}
@@
 \end{proof}
+
+\ddd{The following is a nice thing to establish.}
+\begin{theorem} A state $\rho$ has Wigner negativity if and only if $H_\alpha (W_\rho (\x)) < 0$ for some $\alpha >1$.
+\end{theorem}
+Let's try to prove this.
+\begin{proof} If $H_\alpha (W_\rho(\x) <0 $ then this implies that $\log \sum_{\x} W_\rho (\x)^\alpha > 1$, however it is known that $H_\alpha$ is always non-negative on probability distributions and therefore $W_\rho(\x)$ must be a strict quasi-distribution with negativity.
+
+Conversely, suppose $\rho$ has negativity in its Wigner representation.
+This implies that $\sum_{\x} |W_\rho (\x)| >1$.
+We now consider $\sum_{\x} W_\rho (\x)^{a/b}$ for $a/b >1$ and $a$ even and $b$ odd.
+We have that
+\begin{align}
+\sum_{\x} W_\rho (\x)^{a/b} &= \sum_{\x} |W_\rho (\x)|^{a/b} \nonumber \\
+&= \sum_{\x} |W_\rho (\x)|^{1+ \epsilon},
+\end{align}
+where $\epsilon = a/b - 1 >0$. By choosing $a$ and $b$ appropriately we can make $\epsilon$ arbitrarily close to $0$ and therefore there exists a sequence $\epsilon_n$ such that
+\begin{equation}
+\sum_{\x} |W_\rho (\x)|^{1+ \epsilon_n} \rightarrow \sum_{\x} |W_\rho (\x)| >1.
+\end{equation}
+Therefore, $H_\alpha (W_\rho (\x)) <0 $ at some point in the sequence, which completes the proof.
+\end{proof}
+Therefore Wigner negativity coincides with negativity in at least one Renyi entropy.
+\ddd{[Looking at this limit it almost feels like the $\alpha \rightarrow 0$ limit is actually giving mana....modulo the technical problem of taking the limit without calculus.
+I will think more about this point.]}
+\subsubsection{Extention to general relative majorization}
+
+Therefore if we have a Schur-Concave function $f(\x)$ for majorization of quasi-distributions then we can define a monotonic function for relative majorization via composition with $\Gamma_{\mathbf{a}}$ and its inverse.
 

### 2021-06-05 magic_paper.tex
minor corrections and comment additions

@@
 		&= \frac{1}{1-\alpha} \log_2 \sum_{i=1}^N w_i^{\alpha} a_i^{1-\alpha} \nonumber\\
-		&= \frac{1}{1-\alpha} \log_2 K^{1-\alpha} \sum_{i=1}^N w_i^{\alpha} \nonumber\\
+		&= \frac{1}{1-\alpha} \log_2 K^{1-\alpha} \sum_{i=1}^N w_i^{\alpha} r_i^{1-\alpha} \nonumber\\
 		&= K + \frac{1}{1-\alpha} \log_2 \sum_{i=1}^N w_i^{\alpha} r_i^{1-\alpha} \nonumber\\
@@
 
-1. \nick{looks true numerically, maybe can use~\cref{thm:H2D}}
+1. We need to prove that
+\begin{equation}
+	\sum_{\bmx} W_{\tau}(\bmx) W_{\rho|\tau}(\x)^\alpha \geq 1.
+\end{equation}
+\nick{How do we do this, while respecting the constraints on $\alpha$?}
 
@@
 \begin{equation}
-	\sum_{\bmx} W_{\tau}(\bmx) \left( \frac{W_\rho(\x)}{W_\tau(\x)} \right)^\alpha = 1,
+	\sum_{\bmx} W_{\tau}(\bmx) W_{\rho|\tau}(\x)^\alpha = 1,
 \end{equation}
@@
 	&\frac{1}{\alpha - 1} \log_2 \sum_{\bmx} W_{\rho^{\otimes n}}(\bmx)^\alpha W_{\tau^{\otimes n}}(\bmx)^{1-\alpha} = \nonumber\\
-	&= n D_{\alpha}(\rho || \tau). \nick{complete steps}
+	&\frac{1}{\alpha - 1} \log_2 \sum_{\bmx} \prod_{i=1}^n W_{\rho}(\bmx_i)^\alpha W_{\tau}(\bmx_i)^{1-\alpha} = \nonumber\\
+	&\frac{1}{\alpha - 1} \log_2 \prod_{i=1}^n \sum_{\bmx_i} W_{\rho}(\bmx_i)^\alpha W_{\tau}(\bmx_i)^{1-\alpha} = \nonumber\\
+	&\sum_{i=1}^n \frac{1}{\alpha - 1} \log_2 \sum_{\bmx'} W_{\rho}(\bmx')^\alpha W_{\tau}(\bmx')^{1-\alpha} = \nonumber\\
+	&= n D_{\alpha}(\rho || \tau).
 \end{align}
@@
 \end{proof}
+\nick{Combining ALL the properties above (and nothing more) leads to the general bound}
 
@@
 \begin{equation}
-	K - nD_{\alpha}(W_{\rho} || W_{\tau_n}) \leq K - n'D_{\alpha}(W_{\rho'} || W_{\tau'_{n'}}),
-\end{equation}
-and then it is clear that we can rearrange it to
+	K - nD_{\alpha}(W_{\rho} || W_{\tau}) \leq K - n'D_{\alpha}(W_{\rho'} || W_{\tau'}),
+\end{equation}
+and rearrange it to reach
 \begin{equation}
@@
 Therefore Wigner negativity coincides with negativity in at least one Renyi entropy.
-\ddd{[Looking at this limit it almost feels like the $\alpha \rightarrow 0$ limit is actually giving mana....modulo the technical problem of taking the limit without calculus.
+\ddd{[Looking at this limit it almost feels like the $\alpha \rightarrow 0^+$ limit is actually giving mana....modulo the technical problem of taking the limit without calculus.
 I will think more about this point.]}
+
 \subsubsection{Extention to general relative majorization}

### 2021-06-05 magic_paper.tex
introduced schur-convexity of D_alpha which facilitates the remaining proofs

@@
 
+\begin{theorem}\label{thm:DSchur}
+	Let $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$. 
+	Then, $D_\alpha$ is Schur-convex, i.e.
+let $\w, \w' \in \mathbb{R}^N$ be quasi-distributions and $\r, \r' \in \mathbb{R}^N$ be probability distributions with positive rational entries given by $r_i = a_i/K$ and $r_i' = a_i'/K$ for positive integers $a_i, a_i'$ and $K = \sum_{i=1}^N a_i = \sum_{i=1}^{N'} a_i'$.
+	Then, we have $D_\alpha(\w || \r) \geq H_\alpha(\w' || \r')$, whenever $(\w, \r) \succ (\w', \r')$.
+\end{theorem}
+\begin{proof}
+	The statement $(\w, \r) \succ (\w', \r')$ is equivalent to $\Gamma_{\bma}(\w) \succ \Gamma_{\bma'}(\w')$.
+	Therefore, due to~\cref{thm:HSchur} we have
+	\begin{equation}
+		H_\alpha(\Gamma_{\bma}(\w)) \leq H_\alpha(\Gamma_{\bma'}(\w'))
+	\end{equation}
+	which due to~\cref{thm:H2D} is equivalent to
+	\begin{equation}
+		D_\alpha(\w ||\r) \geq D_\alpha(\w' ||\r').
+	\end{equation}
+\end{proof}
+
 \begin{theorem}\label{thm:Da_props} 
@@
 
-1. We need to prove that
-\begin{equation}
-	\sum_{\bmx} W_{\tau}(\bmx) W_{\rho|\tau}(\x)^\alpha \geq 1.
-\end{equation}
-\nick{How do we do this, while respecting the constraints on $\alpha$?}
-
-2. Assume $D_\alpha (\rho,\tau) = 0$.
-Then,
-\begin{equation}
-	\sum_{\bmx} W_{\tau}(\bmx) W_{\rho|\tau}(\x)^\alpha = 1,
-\end{equation}
-\nick{so...}.
-The converse holds by inspection.
+1. $D_\alpha$ is Schur-convex and every pair $(\w, \r)$ majorizes $(\r', \r')$, so
+\begin{equation}
+	D_\alpha(\w || \r) \geq D_\alpha(\r' || \r') = \frac{1}{\alpha-1} \log_2 \sum_{i} r_i = 0.
+\end{equation}
+
+2. In the inequality of property 1, equality holds iff $L_{\w|\r}(x) = L_{\r'|\r'}(x) = L_{\r|\r}(x)$ for all $x$ due to~\cref{prop:rmajor} which holds iff $\w = \r$.
 
@@
 
-4. \nick{This must hold due to~\cref{thm:H2D}}
+4. This follows immediately from Schur-convexity of $D_\alpha$.
 \end{proof}

### 2021-06-06 magic_paper.tex
added figures to show how Ha and Da look like for a>1 and a<1. Stuck at showing Ha > Hb wheneve a>b, otherwise I think we have all the results that we need. Need reaarangement and notation fixing.

@@
 \begin{equation}
-	H_\alpha(\rho) := \frac{1}{1-\alpha} \log \sum_{\bmx} W_{\rho}(\bmx)^\alpha,
+	H_\alpha(\rho) := \frac{1}{1-\alpha} \log_2 \sum_{\bmx} W_{\rho}(\bmx)^\alpha,
 \end{equation}
@@
 where $d$ is the dimension of $\rho$.
+Inducing any magic state $\rho$ with depolarising noise, $\rho(\epsilon) = (1-\epsilon)\rho + \epsilon \sigma$ results in $H_{\alpha}\left(\rho(\epsilon)\right) \leq H_\alpha(\rho)$ because there exists a free operation $\E \in \O$ that transforms $\rho(\epsilon) = \E(\rho)$ and $H_\alpha$ is Schur-concave.
+
 For $\rho = \rho_{\rm{S}}(\epsilon)$, we get
@@
     \caption{\ddd{[TO DO: Set $\epsilon = 0$ and determine region of $\alpha$ such that $H <0$.]} Here, the exponent is $\alpha =$ even$/$odd for $1.10 \leq \alpha \leq 1.50$.
-$H_\alpha$ is increasing in $\alpha$ and $\epsilon$ \nick{should be easy to show analytically}.
+$H_\alpha$ is increasing in $\alpha$ and $\epsilon$.
 First dashed contour from the right corresponds to $H_\alpha(\rho_{\rm{S}}(\epsilon)) = 0$.
@@
     }
-    \label{fig:lcs}
+    \label{fig:H}
 \end{figure}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.35]{figs/test/D_vs_eps_a.pdf}
+    \caption{Here, the exponent is $\alpha =$ even$/$odd for $1.10 \leq \alpha \leq 1.50$. $D_\alpha$ is decreasing in $\alpha$ and $\epsilon$ (clear due to~\cref{thm:H2D}).
+    }
+    \label{fig:D}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.35]{figs/test/H_test.pdf}
+    \caption{Here, the exponent is $\alpha =$ even$/$odd for $0.10 \leq \alpha \leq 0.90$.
+$H_\alpha$ is decreasing in $\epsilon$ (not Schur-conocave for $\alpha < 1$) and increasing in $\alpha$ (clear due to~\cref{thm:H2D}).
+    }
+    \label{fig:Htest}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.35]{figs/test/D_test.pdf}
+    \caption{Here, the exponent is $\alpha =$ even$/$odd for $0.10 \leq \alpha \leq 0.90$.
+$D_\alpha$ is increasing in $\epsilon$ (not Schur-convex for $\alpha < 1$) and decreasing in $\alpha$ (clear due to~\cref{thm:H2D}).
+    }
+    \label{fig:Dtest}
+\end{figure}
+
+\begin{lemma}
+	Let $\alpha \geq \beta > 1$ where $\alpha, \beta$ are even$/$odd.
+	Then,
+	\begin{equation}
+		H_\alpha(\x) \geq H_\beta(\x) \text{ and } D_\alpha(\x || \r) \leq D_\beta(\x || \r)
+	\end{equation}
+	for any quasi-distribution $\x \in \mathbb{R}^N$ and probability distribution $\r \in \mathbb{R}^N$.
+\end{lemma}
+\begin{proof}
+	For $\alpha \geq \beta > 1$, we have
+	\begin{equation}
+		0 > \frac{1}{1-\alpha} \geq \frac{1}{1-\beta},
+	\end{equation}
+	and $w_i^\alpha = |w_i|^\alpha \leq |w_i|^\beta = w_i^\beta$.
+
+	\nick{how to proceed?}
+
+	For any $\r$ with positive rational components, we have $D_\alpha(\x || \r) \leq D_\beta(\x || \r)$ due to~\cref{thm:H2D}.
+\end{proof}
 
@@
 \end{proof}
-The set $F := \{2a/(2b-1): a,b \in \mathbb{N} \text{ and } a \geq b\}$ is dense in the rationals $\mathbb{Q}_{>1}$, which in turn are dense in the reals $\mathbb{R}_{>1}$, as any rational $c/d$ with $c>d$ can be approximated by a sequence $f_n := c2^n / (d2^n+1)$ with every element $f_n$ in the set $F$.
+The set $F := \{2a/(2b-1): a,b \in \mathbb{N} \text{ and } a \geq b\}$ is dense in the rationals $\mathbb{Q}_{>1}$, which in turn are dense in the reals $\mathbb{R}_{>1}$, as any rational $c/d$ with $c>d$ can be approximated by a sequence $f_n := c2^n / (d2^n-1)$ with every element $f_n$ in the set $F$.
 \nick{can turn into lemma}
@@
 \begin{theorem}\label{thm:Da_props} 
-	Let $\tau$ be a state in the interior of $\F$ and $\alpha = 2a / (2b+1)$ for non-negative integers $a,b$
+	Let $\tau$ be a state in the interior of $\F$ and $\alpha = 2a / (2b-1)$ for non-negative integers $a,b$ with $a \geq b$.
 Then, the $\alpha$-Renyi divergence $D_\alpha(\rho, \tau)$ is well-defined for all states $\rho$, and the following hold:
@@
 Let's try to prove this.
-\begin{proof} If $H_\alpha (W_\rho(\x) <0 $ then this implies that $\log \sum_{\x} W_\rho (\x)^\alpha > 1$, however it is known that $H_\alpha$ is always non-negative on probability distributions and therefore $W_\rho(\x)$ must be a strict quasi-distribution with negativity.
+\begin{proof} If $H_\alpha (W_\rho(\x)) <0 $ then this implies that $\log \sum_{\x} W_\rho (\x)^\alpha > 1$, and it is known that $H_\alpha$ is always non-negative on probability distributions, so $W_\rho(\x)$ must be a strict quasi-distribution with negativity.
 
@@
 \end{equation}
+\nick{In this step, we also need to show that $H_\alpha$ is increasing in $\alpha$}
 Therefore, $H_\alpha (W_\rho (\x)) <0 $ at some point in the sequence, which completes the proof.
@@
 Therefore Wigner negativity coincides with negativity in at least one Renyi entropy.
-\ddd{[Looking at this limit it almost feels like the $\alpha \rightarrow 0^+$ limit is actually giving mana....modulo the technical problem of taking the limit without calculus.
+\ddd{[Looking at this limit it almost feels like the $\alpha \rightarrow 1$ limit is actually giving mana....modulo the technical problem of taking the limit without calculus.
 I will think more about this point.]}

### 2021-06-06 magic_paper.tex
Restructiing of appendices.

--- 2021-06-05 magic_paper.tex
@@
 
-We note that we may relate our analysis to the classical single-shot entropy $D_\infty (\p ||\r)$ that remains well-defined even in the case of quasi-distributions. We define 
+\subsection{Dropping pre/post-processing of the magic states}
+\label{app:cliff_processing}
+
+If we drop the freedom to transform the magic states via Clifford unitaries, then the final expression for the bounds change and become a little more complex, since the largest component in the rescaled distribution depends on a number of factors.
+We illustrate this by the following result.
+
+\begin{theorem}\label{thm:no-processing}
+	Consider a magic distillation protocol on qutrits that transforms
+\begin{equation*}
+	\rho_S(\epsilon)^{\otimes n} \longrightarrow \E(\rho_S(\epsilon)^{\otimes n})=\rho_S(\epsilon')^{\otimes m} 
+\end{equation*}
+with $n, m \gg 1$.
+
+Let each qutrit have a Hamiltonian $H$ with energies $E_0, E_1, E_2$ and stabilizer eigenstates, and define $E_{\rm max} = \max\{E_0, E_1, E_2\}$ and \nick{$E_s$ as the eigenvalue of the Hamiltonian eigenstate whose Wigner distribution overlaps the negative component of $\rho_S(\epsilon)$ in the phase space.}
+Let $T =(k\beta)^{-1}$ be any finite temperature and assume that in the thermodynamic limit ($n,m \gg 1$), the protocol applied to the equilibrium state $\tau^{\otimes n} = (e^{-\beta H}/\Z)^{\otimes n}$ maps $\tau^{\otimes n} \longrightarrow \tau^{\prime \otimes m}$, where we express state $\tau'$ as $\tau' = e^{-\beta H'}/\Z'$ for some Hermitian $H'$.
+
+Define $\beta_\star = (k T_\star)^{-1}$ through the relation
+\begin{equation}
+	E_{\rm max} - E_s \eqqcolon kT_\star \ln 2,
+\end{equation}
+and define a threshold error,
+\begin{equation}\label{eq:threshold}
+	\epsilon_{\star}(\beta) \coloneqq 
+	\begin{cases}
+		3 - \dfrac{9}{4-2^{\beta/\beta_\star - 1}}, &\text{ for } \beta \leq \beta_\star \\
+		0, &\text{ for } \beta > \beta_\star.
+	\end{cases}
+\end{equation}
+Then, the distillation rate $R = m/n$ of the magic protocol is bounded as:
+\begin{equation}
+	R \leq
+	\begin{cases}
+		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F')},\ &\epsilon \leq \epsilon_\star, \epsilon' \leq \epsilon'_\star, \vspace{10pt}\\
+		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F')},\ &\epsilon \leq \epsilon_\star, \epsilon' > \epsilon'_\star, \vspace{10pt}\\
+		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F')},\ &\epsilon > \epsilon_\star, \epsilon' \leq \epsilon'_\star, \vspace{10pt}\\
+		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F')},\ &\epsilon > \epsilon_\star, \epsilon' > \epsilon'_\star,
+	\end{cases}
+\end{equation}
+where $F$ is the free energy of state $\tau$ and all primed quantities are similarly defined for the ouptut system.
+\end{theorem}
+\begin{proof}
+The proof proceeds in the same manner as in~\cref{thm:free-energy-bound-proof} up to the point where we need to evaluate $W_{\rho_n |\tau_n} (\x)$ and $W_{\rho_n}(\x)$ explicitly, beyond which we do not have the freedom of additional Clifford processing.
+
+\nick{Explain why this is not Clifford processing, ensure overlap with negativity is the one suggested}
+The equilibrium state at inverse temperature $\beta$ on a single qutrit is given by $\tau = e^{-\beta H} / \Z$.
+Moreover we have that $\tau$ is a full-rank stabilizer state, where $\beta \geq 0$ and $H = E_0 |\varphi_0\>\<\varphi_0| + E_1 |\varphi_1\>\<\varphi_1| + E_2 |\varphi_2\>\<\varphi_2|$ is an eigendecomposition of $H$.
+The state $\tau$ can now be written as 
+\begin{equation}
+	\tau = \frac{e^{-\beta E_0}}{\Z} |\varphi_0\>\<\varphi_0| + \frac{e^{-\beta E_1}}{\Z} |\varphi_1\>\<\varphi_1| + \frac{e^{-\beta E_2}}{\Z} |\varphi_2\>\<\varphi_2|,
+\end{equation}
+where the eigenstates $\{\ket{\varphi_k}\<\varphi_k|\}$ are pure, orthonormal stabiliser states, which can be represented in terms of generalized Paulis.
+We are free to redefine the computational basis so it coincides with the basis of $H$.
+Abstractly, let $C$ be the unitary transforming each $|\varphi_k\>\<\varphi_k|$ to $|k\>\<k|$.
+Since the Clifford group is the normalizer of the Heisenberg-Weyl group, $C$ is a Clifford unitary.
+Therefore, $C$ maps $\tau$ to another stabilizer state that is diagonal in the computational basis, and we can assume without loss of generality that $\tau$ is diagonal in $\{|0\>,|1\>, |2\>\}$.
+However, this re-definition of the computational basis means that the location of the negative Wigner component $-v(\epsilon)$ of the Strange state will be permuted on the discrete phase space.
+We denote by $E_s$ the eigenvalue of $H$ where the associated eigenvector has Wigner distribution overlapping the negative component of the magic state $C\rho_S(\epsilon)C^\dagger$.
+This is unique, since the eigenstates form an orthonormal basis.
+
+The Wigner distribution of state $\tau$ is then given by
+\begin{align}
+	\W[\bmx]{\tau} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z}W_{|k\>\<k|}(x, p) \nonumber\\
+	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z} \delta_{x, k} = \frac{e^{-\beta E_x}}{3\Z},
+\end{align}
+where $x$ labels one of the three vertical lines in the phase space.
+The rescaled Wigner distribution $W_{\rho|\tau}(\x)$ can now be computed.
+It has $9$ components, but these come with multiplicities.
+In total, there are four distinct values on the phase space, as illustrated in~\cref{fig:pd_split}.
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.45]{figs/pd_split_thermal.pdf}
+    \caption{\textbf{Qutrit phase space regions for $W_{\rho | \tau}(\x)$.}
+    Here, the negative component of the magic state overlaps the Wigner distribution of $|0\>$.
+The rescaled distribution attains a single value in each of the four regions, proportional to the value depicted in the region, see~\cref{eq:bmw_rescaled}.
+    }
+    \label{fig:pd_split}
+\end{figure}
+
+We denote by $\w(\rho), \w(\rho|\tau)$ the unique values occurring in $W_\rho(\x), W_{\rho|\tau}(\x)$ respectively and $\bmm$ the vector of associated multiplicities of each value in $W_\rho(\x)$.
+The component values and multiplicities of the relevant distributions in the four distinct regions are given by
+\begin{align}
+	\w(\rho) &\coloneqq (-v, u, u, u), \\
+		\bmm &\coloneqq (1,2,3,3), \\
+	\w(\tau) &\coloneqq \frac{1}{3\Z} \left( e^{-\beta E_0}, e^{-\beta E_0}, e^{-\beta E_1}, e^{-\beta E_2} \right), \\
+	\w(\rho_{\rm{S}} | \tau) &\coloneqq 3\Z \left( -v e^{\beta E_0}, u e^{\beta E_0}, u e^{\beta E_1}, u e^{\beta E_2} \right). \label{eq:bmw_rescaled}
+\end{align}
+
+Using this notation, the values and multiplicities of the $n$--copy distribution $\bmw(\rho_n |\tau_n)$ are computed in~\cref{lem:ncopycomponents}. The values are given by 
+\begin{align}\label{eq:ncopy_w_rescaled}
+	[\w(\rho_n | \tau_n)]_{ijk} &= (3\Z)^{n} (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )},
+\end{align}
+where the indices $i,j,k$ are non-negative integers that obey the constraint $\alpha \coloneqq i+j+k \leq n$.
+The multiplicity of this above value is $m_{ijk}$ with
+\begin{equation}
+	m_{ijk} = \frac{n!}{i!j!k!(n-\alpha)!} 2^i 3^j 3^k.
+\end{equation}
+The associated components of $\w(\rho_n)$ are given by
+\begin{align}
+	[\w(\rho_n)]_{ijk} &= (-v)^{n-\alpha} u^{\alpha}, \label{eq:ncopy_wrho}\\
+	[\w(\tau)]_{ijk} &= (3\Z)^{-n} e^{-\beta (n-\alpha)E_s} e^{-\beta ( i E_0 + j E_1 + k E_2 )}. \label{eq:ncopy_wsigma}
+\end{align}
+
+In order to construct the $n$--copy Lorenz curve $L_{\rho_n|\tau_n}(x)$ we need to order the components of the distribution, $w(\rho_{\rm{S}} | \tau)_{ijk}$ in decreasing order, and identify the sequence of indices that give us $W_{\rho_n}(\pi(\x))$.
+
+However, it again suffices to use only the constraint from the first elbow $(x_0, L_0)$ of $L_{\rho_n|\tau_n}(\x)$. We therefore compute the largest component 
+\begin{equation}
+	w_{\rm max} \coloneqq \max_{i,j,k} [\w(\rho_n | \tau_n)]_{ijk},
+\end{equation}
+and determine the indices at which this occurs.
+Putting in the values we obtain
+\begin{align}
+	&(3\Z)^{-n}w_{\rm max} = \nonumber\\
+	&\max\limits_{i,j,k}\Big\{ (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \label{eq:max_slope}
+\end{align}
+where $0 \leq i,j,k \leq n$ and $\alpha \coloneqq i+j+k \leq n$.
+Now for $0 \leq \epsilon \leq 3/7$, we have $v \geq u$. Since we assume that $n$ is even, we need the sum $\alpha = i+j+k$ to be even too, so that the expression is positive.
+
+Given an even value for $\alpha$, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_s}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
+Hence, we have
+\begin{align}
+	&w_{\rm max} = \nonumber\\
+	&(3\Z)^{n} v^n e^{n\beta E_s}\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_s)} \right)^{\alpha} \Big\}}.
+\end{align}
+If the expression $\frac{u(\epsilon)}{v(\epsilon)} e^{\beta (E_{\rm{max}} - E_s)}$ is less than $1$ then the maximum occurs at $\alpha=0$, otherwise it occurs at $\alpha = n$.
+For a fixed state $\tau$, this transition is determined by the value of the depolarising error parameter $\epsilon$ of the noisy magic state.
+The transition occurs at $\epsilon = \epsilon_\star$ where
+\begin{equation}\label{eq:noise_transition}
+	\frac{u(\epsilon_\star)}{v(\epsilon_\star)} e^{\beta (E_{\rm{max}} - E_s)} = \frac{3-\epsilon_\star}{6-8\epsilon_\star} e^{\beta (E_{\rm{max}} - E_s)} = 1.
+\end{equation}
+If $E_{\rm{max}} = E_s$, namely if the state negativity lies in the same phase space region as the highest energy, this threshold is constant in temperature and given by $\epsilon_{\star} = 3/7$.
+However, the condition that $\epsilon_\star \ge 0$ also implies a constraint on the effective temperature of the stabilizer state.
+Specifically, there is a threshold temperature value $\beta_\star$ given by
+\begin{equation}
+	\beta_{\star} \coloneqq \frac{1}{E_{\rm{max}} - E_s} \ln2,
+\end{equation}
+such that for the regime $0 \leq \beta \leq \beta_\star$ a threshold error $\epsilon_\star$ exists, and for $\beta > \beta_\star$ no such transition exists, so we choose $\epsilon_\star = 0$. 
+Therefore, the transition value for the noise is given by
+\begin{equation}
+	\epsilon_{\star}(\beta) \coloneqq 
+	\begin{cases}
+		3 - \dfrac{9}{4-2^{\beta/\beta_\star - 1}}, &\text{ for } \beta \leq \beta_\star \\
+		0, &\text{ for } \beta > \beta_\star.
+	\end{cases}
+\end{equation}
+The quantity $w(\rho_{\rm{S}} | \sigma)_{\rm{max}}$ is now given by
+\begin{equation*}
+w_{\rm max} =
+	\begin{cases}
+		(3\Z)^{n} v^n e^{n\beta E_s}, &\mbox{if }\epsilon \leq \epsilon_{\star},\ \hspace{3pt}\rm{(C1)}\\
+		(3\Z)^{n} u^n e^{n\beta E_{\rm{max}}}, &\mbox{if }\epsilon > \epsilon_{\star}.\ \hspace{5pt}\rm{(C2)} 
+	\end{cases}
+\end{equation*}
+Case $\rm{(C1)}$ corresponds to $(i,j,k) = (0,0,0)$, so the multiplicity is $m_{000} = 1$, while
+Case $\rm{(C2)}$ corresponds to
+\begin{equation}
+	(i,j,k) = 
+	\begin{cases}
+	(0,n,0), &\text{if } E_{\rm{max}} = E_1, \\
+	(0,0,n), &\text{if } E_{\rm{max}} = E_2,
+	\end{cases}
+\end{equation}
+so the multiplicity in both cases is $3^n$.
+
+Using that $F = -\beta^{-1} \log \Z$, the first elbow coordinates in the two cases are now given by
+\begin{equation}\label{eq:first_elb_coords}
+	(x_0, L_0) =
+	\begin{cases}
+		\left(\frac{1}{3^n} e^{-n\beta (E_s - F)}, v^n \right), &\epsilon \leq \epsilon_\star \vspace{10pt}\\
+		\left( e^{-n\beta (E_{\rm{max}}-F)}, (3u)^n \right). &\epsilon > \epsilon_\star
+	\end{cases}
+\end{equation}
+
+Similarly, considering the output magic state with respect to state $\sigma'$, the image of equilibrium state $\sigma$ under the magic protocol, we get output Lorenz curve coordinates,
+\begin{equation}\label{eq:transformed_first_elb_coords}
+	(x'_0, L'_0) =
+	\begin{cases}
+		\left(\frac{1}{3^{n'}} e^{-n\beta (E'_s - F')}, v(\epsilon')^{n'} \right), &\epsilon' \leq \epsilon'_\star \vspace{10pt}\\
+		\left( e^{-n'\beta (E'_{\rm{max}}\hspace{-2.5pt}-F')}, (3u(\epsilon'))^{n'} \right), &\epsilon' > \epsilon'_\star
+	\end{cases}
+\end{equation}
+There are four combinations of coordinates, depending on the noise parameters $\epsilon, \epsilon'$ for the input and output states.
+In each of these combinations, we simply use the first elbow constraint, as described in~\cref{prop:first_elb}, and manipulate the coordinates as in the proof of~\cref{thm:free-energy}, leading to the bounds in the statement of the theorem.
+\end{proof}
+
+\newpage
+\section{Single-shot entropies on quasi-distributions and magic distillation bounds}
+
+We note that we may relate our analysis to the classical single-shot entropies that remain well-defined even in the case of quasi-distributions.
+
+\subsection{Renyi min-divergence from initial slope}
+We first demonstrate that the initial slope analysis on the Wigner quasi-distributions makes use of the min-relative divergence. We define 
 \begin{equation}
@@
 
-\newpage
-
-\subsection{Entropic bounds on quasi-distributions}
-
-We prove the following result connecting simple majorization to relative majorization.
-\nick{move following lemma to section on relative majorization equivalent conditions}
-\begin{lemma}
-Let $\w\in \mathbb{R}^N, \w'\in \mathbb{R}^{N'}$ be quasi-distributions and $\r\in \mathbb{R}^N, \r'\in \mathbb{R}^{N'}$ probability distributions with positive rational entries given by $r_i = a_i/K$ and $r_i' = a_i'/K$ for positive integers $a_i, a_i'$ and $K = \sum_{i=1}^N a_i = \sum_{i=1}^{N'} a_i'$.
-Then,
-\begin{equation}
-(\w, \r) \succ (\w', \r') \mbox{ if and only if } \Gamma_{\bma} (\w) \succ \Gamma_{\bma'} (\w'),
-\end{equation}
-where the embedding map $\Gamma_{\bma} :\mathbb{R}^N \rightarrow \mathbb{R}^K$ is given by
-\begin{equation}
-	\Gamma_{\bma}(\x) := \bigoplus_{i=1}^N x_i \eta_{a_i},
-\end{equation}
-with $\eta_{a_i} = (1/a_i, 1/a_i, \dots, 1/a_i)$ the uniform distribution on $a_i$ elements.
-\end{lemma}
-\begin{proof}
-	We first note that the map $\Gamma_{\bma}$ is stochastic and has a well-defined left-inverse $\Gamma^{-1}_{\bma'}: \mathbb{R}^K \rightarrow \mathbb{R}^N$ given by
-\begin{equation}
-	\Gamma^{-1}_{\bma}(\w) = \left( \sum_{i=1}^{a_1} w_i,  \sum_{i = a_1 +1}^{a_1 + a_2} \hspace{-5pt} w_i, \dots , \hspace{-15pt} \sum_{i=a_1 + \dots + a_{N-1}+1}^{K} \hspace{-10pt} w_i \right),
-\end{equation}
-that obeys $(\Gamma^{-1}_{\bma} \circ \Gamma_{\bma}) (\x) = \x$ for all $\x \in \mathbb{R}^N$.
-
-The claim is equivalent to the statement that there exists a \emph{bistochastic map} $B$ sending $\Gamma_{\bma}(\w)$ to $\Gamma_{\bma'}(\w')$ if and only if there exists a stochastic map $A$ sending $\w$ to $\w'$ and $\r$ to $\r'$.
-
-Suppose there is a stochastic map $A$ such that $A\w=\w'$ and $A\r = \r'$. 
-We define $B:\mathbb{R}^K \mapsto \mathbb{R}^K$ by $B := \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1}$ so that it is stochastic as a composition of stochastic maps and it preserves the uniform distribution in $\mathbb{R}^A$, since
-\begin{align}
-	&B(1/K, 1/K, \dots, 1/K) = \big( \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1} \big) \big( \Gamma_{\bma'}(\r) \big) = \nonumber\\
-	&\Gamma_{\bma'} (\r') = (1/K, 1/K, \dots, 1/K),
-\end{align}
-therefore $B$ is bistochastic.
-Finally, $B$ maps the embedded distributions as follows,
-\begin{equation}
-	B \Gamma_{\bma}(\w) = \big( \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1} \big) \big( \Gamma_{\bma}(\w) \big) = \Gamma_{\bma'} (\w').
-\end{equation}
-
-Conversely, suppose a bistochastic map $B$ exists sending $\Gamma_{\bma}(\w)$ to $\Gamma_{\bma'}(\w')$.
-Again, define $A: \mathbb{R}^N \mapsto \mathbb{R}^{N'}$ by $A := \Gamma_{\bma'}^{-1} \circ B \circ \Gamma_{\bma}$ so that it is stochastic as a composition of stochastic maps and $A \w = \big( \Gamma_{\bma'}^{-1} \circ B \circ \Gamma_{\bma} \big) \w = \w'$, as well as $A \r = \r'$.
-\end{proof}
-We note that the vectors $\r, \r'$ with rational components form a dense subset of the positive probability distributions, so we can appeal to the fact that experiments have a finite resolution to ignore technical details regarding the completion to arbitrary real components.
-
-\subsubsection{Classical $\alpha$-Renyi entropy and divergence for quasi-distributions}
-
-We first define the classical $\alpha$-Renyi entropy in terms of the Wigner quasi-distribution of any state $\rho$ as
-\begin{equation}
-	H_\alpha(\rho) := \frac{1}{1-\alpha} \log \sum_{\bmx} W_{\rho}(\bmx)^\alpha,
+\subsection{Well-defined Renyi entropies on quasi-distributions}
+
+\ddd{[ISSUE WITH NOTATION: We can't clash with the quantum Renyi entropies. I think we have to use $H_\alpha(W_\rho)$ is bulky...but hopefully clear.]}
+
+We define the classical $\alpha$-Renyi entropy in terms of the Wigner quasi-distribution of any state $\rho$ as
+\begin{equation}
+	H_\alpha(W_\rho) := \frac{1}{1-\alpha} \log \sum_{\bmx} W_{\rho}(\bmx)^\alpha,
 \end{equation}
 where $\alpha$ can take values of the form $2a / (2b+1)$, for non-negative integers $a,b$ to ensure that the argument of the logarithm is positive.
-Note that for any quantum state $\rho$, $H_1(\rho)$ in particular is not well-defined  \nick{Notation clashes with quantum Renyi entropies}, while for any valid $\alpha$ we have that
-\begin{equation}
-	H_0(\rho) = 2\log_2 d = H_\alpha \left( \id/d \right),
+Note that for any quantum state $\rho$, $H_1(W_\rho)$ in particular is not well-defined, while for any valid $\alpha$ we have that
+\begin{equation}
+	H_0(W_\rho) = 2\log_2 d = H_\alpha \left( \id/d \right),
 \end{equation}
@@
 
-We can prove additivity of $H_{\alpha}$ on quantum states.
-
-\begin{lemma}\label{H_add}
-	For any quantum states $\rho, \rho'$, we have
-	\begin{equation}
-		H_{\alpha}(\rho \otimes \rho') = H_{\alpha}(\rho) + H_{\alpha}(\rho'),
-	\end{equation}
-	where $\hspace{-1pt}\alpha\hspace{-1pt}$ is such that $\hspace{-1pt}H_\alpha(\sigma)\hspace{-2pt}$ is well-defined for all states $\sigma$.
-\end{lemma}
-\begin{proof}
-	This can be seen directly by the multiplicative property of the Wigner distribution,
-	\begin{align*}
-		H_{\alpha}&(\rho \otimes \rho') = \frac{1}{1-\alpha}\log \sum_{\bmx,\bmx'} \left[W_{\rho}(\bmx)W_{\rho}(\bmx')\right]^{\alpha} \\
-		&= \frac{1}{1-\alpha}\left( \log \sum_{\bmx}W_{\rho}(\bmx)^{\alpha} + \log \sum_{\bmx'}W_{\rho}(\bmx')^{\alpha} \right) \\
-		&= H_{\alpha}(\rho) + H_{\alpha}(\rho').
-	\end{align*}
-\end{proof}
-
 We now make use of known results from majorization theory to establish the Schur-concavity of $H_\alpha$ on Wigner quasi-distributions where $\alpha$ is such that $H_\alpha$ is well-defined. 
@@
 
-We now have the following theorem~\cite{cit:marshall} that provides a characterization of symmetric, Schur-convex and Schur-concave functions on quasi-distributions.
+We now have that the Schur-Ostrowski theorem~\cite{cit:marshall} provides a characterization of symmetric, Schur-convex and Schur-concave functions on quasi-distributions.
 \begin{lemma}
@@
 where $\alpha$ can take values of the form $2a / (2b+1)$, for non-negative integers $a,b$ to ensure that the argument of the logarithm is positive.
-\nick{Notation clashes with quantum Renyi divergence}
+
+We can check additivity of $H_{\alpha}$ also holds on quasi-distributions. 
+\begin{lemma}\label{H_add}
+	For any $\w, \w' \in \mathcal{Q}$, we have
+	\begin{equation}
+		H_{\alpha}(\w\otimes \w') = H_{\alpha}(\w) + H_{\alpha}(\w'),
+	\end{equation}
+	where $\alpha = 2a/(2b-1)$ with integers $a\ge b$.
+\end{lemma}
+\begin{proof}
+	That fact that negativity does not affect additivity can be seen directly as follows
+	\begin{align*}
+		H_{\alpha}(\w \otimes \w') &= \frac{1}{1-\alpha}\log \sum_{i,j'} \left[\w_i \w'_j\right]^{\alpha} \\
+		&= \frac{1}{1-\alpha}\log  \left [ \sum_i\w_i^\alpha \sum_j\w_j^{\prime \alpha} \right ] \\
+				&= \frac{1}{1-\alpha}\log  \left [ \sum_i\w_i^\alpha\right ] + \frac{1}{1-\alpha}\log \left [ \sum_j\w_j^{\prime \alpha} \right ] \\
+		&= H_{\alpha}(\w) + H_{\alpha}(\w').
+	\end{align*}
+\end{proof}
+
+\subsection{Renyi divergences on quasi-distributions}
+We prove the following result connecting majorization to relative majorization.
+\begin{lemma}
+Let $\w\in \mathbb{R}^N, \w'\in \mathbb{R}^{N'}$ be quasi-distributions and $\r\in \mathbb{R}^N, \r'\in \mathbb{R}^{N'}$ probability distributions with positive rational entries given by $r_i = a_i/K$ and $r_i' = a_i'/K$ for positive integers $a_i, a_i'$ and $K = \sum_{i=1}^N a_i = \sum_{i=1}^{N'} a_i'$.
+Then,
+\begin{equation}
+(\w, \r) \succ (\w', \r') \mbox{ if and only if } \Gamma_{\bma} (\w) \succ \Gamma_{\bma'} (\w'),
+\end{equation}
+where the embedding map $\Gamma_{\bma} :\mathbb{R}^N \rightarrow \mathbb{R}^K$ is given by
+\begin{equation}
+	\Gamma_{\bma}(\x) := \bigoplus_{i=1}^N x_i \eta_{a_i},
+\end{equation}
+with $\eta_{a_i} = (1/a_i, 1/a_i, \dots, 1/a_i)$ the uniform distribution on $a_i$ elements.
+\end{lemma}
+\begin{proof}
+	We first note that the map $\Gamma_{\bma}$ is stochastic and has a well-defined left-inverse $\Gamma^{-1}_{\bma'}: \mathbb{R}^K \rightarrow \mathbb{R}^N$ given by
+\begin{equation}
+	\Gamma^{-1}_{\bma}(\w) = \left( \sum_{i=1}^{a_1} w_i,  \sum_{i = a_1 +1}^{a_1 + a_2} \hspace{-5pt} w_i, \dots , \hspace{-15pt} \sum_{i=a_1 + \dots + a_{N-1}+1}^{K} \hspace{-10pt} w_i \right),
+\end{equation}
+that obeys $(\Gamma^{-1}_{\bma} \circ \Gamma_{\bma}) (\x) = \x$ for all $\x \in \mathbb{R}^N$.
+
+The claim is equivalent to the statement that there exists a \emph{bistochastic map} $B$ sending $\Gamma_{\bma}(\w)$ to $\Gamma_{\bma'}(\w')$ if and only if there exists a stochastic map $A$ sending $\w$ to $\w'$ and $\r$ to $\r'$.
+
+Suppose there is a stochastic map $A$ such that $A\w=\w'$ and $A\r = \r'$. 
+We define $B:\mathbb{R}^K \mapsto \mathbb{R}^K$ by $B := \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1}$ so that it is stochastic as a composition of stochastic maps and it preserves the uniform distribution in $\mathbb{R}^A$, since
+\begin{align}
+	&B(1/K, 1/K, \dots, 1/K) = \big( \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1} \big) \big( \Gamma_{\bma'}(\r) \big) = \nonumber\\
+	&\Gamma_{\bma'} (\r') = (1/K, 1/K, \dots, 1/K),
+\end{align}
+therefore $B$ is bistochastic.
+Finally, $B$ maps the embedded distributions as follows,
+\begin{equation}
+	B \Gamma_{\bma}(\w) = \big( \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1} \big) \big( \Gamma_{\bma}(\w) \big) = \Gamma_{\bma'} (\w').
+\end{equation}
+
+Conversely, suppose a bistochastic map $B$ exists sending $\Gamma_{\bma}(\w)$ to $\Gamma_{\bma'}(\w')$.
+Again, define $A: \mathbb{R}^N \mapsto \mathbb{R}^{N'}$ by $A := \Gamma_{\bma'}^{-1} \circ B \circ \Gamma_{\bma}$ so that it is stochastic as a composition of stochastic maps and $A \w = \big( \Gamma_{\bma'}^{-1} \circ B \circ \Gamma_{\bma} \big) \w = \w'$, as well as $A \r = \r'$.
+\end{proof}
+We note that the vectors $\r, \r'$ with rational components form a dense subset of the positive probability distributions, so we can appeal to the fact that experiments have a finite resolution to ignore technical details regarding the completion to arbitrary real components.
 
@@
 
+We now establish monotonicity for Renyi relative divergences.
 \begin{theorem}\label{thm:DSchur}
@@
 
-\ddd{Therefore if we have a Schur-Concave function $f(\x)$ for majorization of quasi-distributions then we can define a monotonic function for relative majorization via composition with $\Gamma_{\mathbf{a}}$ and its inverse.
-This should provide relative majorization monotones from which we can obtain distillation bounds, such as
-\begin{equation}
-	R \le \frac{F_\alpha(\tau) - F_\alpha (\rho)}{F_\alpha(\tau') - F_\alpha (\rho')}.
-\end{equation}}
-\nick{I don't understand where the free energies came from. Are they known to be Schur-concave?}
-
 \begin{theorem}
@@
 	\begin{equation}
-		R \leq \frac{D_{\alpha}(\rho||\tau)}{D_{\alpha}(\rho'||\tau')},
-	\end{equation}
-	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$.
+		R \leq \frac{D_{\alpha}(\rho||\tau)}{D_{\alpha}(\rho'||\tau')} = \frac{F_\alpha(\rho) - F_\alpha( \tau)}{F'_\alpha(\rho') - F'_\alpha( \tau')},
+	\end{equation}
+	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ and $\beta F_\alpha(\rho) := D_\alpha (\rho || \tau) - \log \Z$ is the $\alpha$--free energy. 
 \end{theorem}
@@
 
-\ddd{The following is a nice thing to establish.}
+We now show the following simple equivalence.
 \begin{theorem} A state $\rho$ has Wigner negativity if and only if $H_\alpha (W_\rho (\x)) < 0$ for some $\alpha >1$.
@@
 Let's try to prove this.
-\begin{proof} If $H_\alpha (W_\rho(\x) <0 $ then this implies that $\log \sum_{\x} W_\rho (\x)^\alpha > 1$, however it is known that $H_\alpha$ is always non-negative on probability distributions and therefore $W_\rho(\x)$ must be a strict quasi-distribution with negativity.
+\begin{proof} If we have $H_\alpha (W_\rho(\x)) <0 $ then this implies that $\log \sum_{\x} W_\rho (\x)^\alpha > 1$, however it is known that $H_\alpha$ is always non-negative on probability distributions and therefore $W_\rho(\x)$ must be a strict quasi-distribution with negativity.
 
@@
 \end{align}
-where $\epsilon = a/b - 1 >0$. By choosing $a$ and $b$ appropriately we can make $\epsilon$ arbitrarily close to $0$ and therefore there exists a sequence $\epsilon_n$ such that
+where $\epsilon = a/b - 1 >0$. By choosing $a$ and $b$ appropriately we can make $\epsilon$ arbitrarily close to $0$ and therefore there exists a sequence $\epsilon_n=a_n/b_n$ such that
 \begin{equation}
@@
 \end{proof}
-Therefore Wigner negativity coincides with negativity in at least one Renyi entropy.
-\ddd{[Looking at this limit it almost feels like the $\alpha \rightarrow 0^+$ limit is actually giving mana....modulo the technical problem of taking the limit without calculus.
+Therefore Wigner negativity coincides with negativity of a Renyi entropy.
+
+\ddd{[Looking at this limit it almost feels like the $\alpha \rightarrow 1^+$ limit is actually giving mana....modulo the technical problem of taking the limit without calculus.
 I will think more about this point.]}
 
-\subsubsection{Extention to general relative majorization}
-
-Therefore if we have a Schur-Concave function $f(\x)$ for majorization of quasi-distributions then we can define a monotonic function for relative majorization via composition with $\Gamma_{\mathbf{a}}$ and its inverse.
-
-\subsection{Dropping pre/post-processing of the magic states}
-\label{app:cliff_processing}
-
-If we drop the freedom to transform the magic states via Clifford unitaries, then the final expression for the bounds change and become a little more complex, since the largest component in the rescaled distribution depends on a number of factors.
-We illustrate this by the following result.
-
-\begin{theorem}\label{thm:no-processing}
-	Consider a magic distillation protocol on qutrits that transforms
-\begin{equation*}
-	\rho_S(\epsilon)^{\otimes n} \longrightarrow \E(\rho_S(\epsilon)^{\otimes n})=\rho_S(\epsilon')^{\otimes m} 
-\end{equation*}
-with $n, m \gg 1$.
-
-Let each qutrit have a Hamiltonian $H$ with energies $E_0, E_1, E_2$ and stabilizer eigenstates, and define $E_{\rm max} = \max\{E_0, E_1, E_2\}$ and \nick{$E_s$ as the eigenvalue of the Hamiltonian eigenstate whose Wigner distribution overlaps the negative component of $\rho_S(\epsilon)$ in the phase space.}
-Let $T =(k\beta)^{-1}$ be any finite temperature and assume that in the thermodynamic limit ($n,m \gg 1$), the protocol applied to the equilibrium state $\tau^{\otimes n} = (e^{-\beta H}/\Z)^{\otimes n}$ maps $\tau^{\otimes n} \longrightarrow \tau^{\prime \otimes m}$, where we express state $\tau'$ as $\tau' = e^{-\beta H'}/\Z'$ for some Hermitian $H'$.
-
-Define $\beta_\star = (k T_\star)^{-1}$ through the relation
-\begin{equation}
-	E_{\rm max} - E_s \eqqcolon kT_\star \ln 2,
-\end{equation}
-and define a threshold error,
-\begin{equation}\label{eq:threshold}
-	\epsilon_{\star}(\beta) \coloneqq 
-	\begin{cases}
-		3 - \dfrac{9}{4-2^{\beta/\beta_\star - 1}}, &\text{ for } \beta \leq \beta_\star \\
-		0, &\text{ for } \beta > \beta_\star.
-	\end{cases}
-\end{equation}
-Then, the distillation rate $R = m/n$ of the magic protocol is bounded as:
-\begin{equation}
-	R \leq
-	\begin{cases}
-		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F')},\ &\epsilon \leq \epsilon_\star, \epsilon' \leq \epsilon'_\star, \vspace{10pt}\\
-		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F')},\ &\epsilon \leq \epsilon_\star, \epsilon' > \epsilon'_\star, \vspace{10pt}\\
-		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F')},\ &\epsilon > \epsilon_\star, \epsilon' \leq \epsilon'_\star, \vspace{10pt}\\
-		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F')},\ &\epsilon > \epsilon_\star, \epsilon' > \epsilon'_\star,
-	\end{cases}
-\end{equation}
-where $F$ is the free energy of state $\tau$ and all primed quantities are similarly defined for the ouptut system.
-\end{theorem}
-\begin{proof}
-The proof proceeds in the same manner as in~\cref{thm:free-energy-bound-proof} up to the point where we need to evaluate $W_{\rho_n |\tau_n} (\x)$ and $W_{\rho_n}(\x)$ explicitly, beyond which we do not have the freedom of additional Clifford processing.
-
-\nick{Explain why this is not Clifford processing, ensure overlap with negativity is the one suggested}
-The equilibrium state at inverse temperature $\beta$ on a single qutrit is given by $\tau = e^{-\beta H} / \Z$.
-Moreover we have that $\tau$ is a full-rank stabilizer state, where $\beta \geq 0$ and $H = E_0 |\varphi_0\>\<\varphi_0| + E_1 |\varphi_1\>\<\varphi_1| + E_2 |\varphi_2\>\<\varphi_2|$ is an eigendecomposition of $H$.
-The state $\tau$ can now be written as 
-\begin{equation}
-	\tau = \frac{e^{-\beta E_0}}{\Z} |\varphi_0\>\<\varphi_0| + \frac{e^{-\beta E_1}}{\Z} |\varphi_1\>\<\varphi_1| + \frac{e^{-\beta E_2}}{\Z} |\varphi_2\>\<\varphi_2|,
-\end{equation}
-where the eigenstates $\{\ket{\varphi_k}\<\varphi_k|\}$ are pure, orthonormal stabiliser states, which can be represented in terms of generalized Paulis.
-We are free to redefine the computational basis so it coincides with the basis of $H$.
-Abstractly, let $C$ be the unitary transforming each $|\varphi_k\>\<\varphi_k|$ to $|k\>\<k|$.
-Since the Clifford group is the normalizer of the Heisenberg-Weyl group, $C$ is a Clifford unitary.
-Therefore, $C$ maps $\tau$ to another stabilizer state that is diagonal in the computational basis, and we can assume without loss of generality that $\tau$ is diagonal in $\{|0\>,|1\>, |2\>\}$.
-However, this re-definition of the computational basis means that the location of the negative Wigner component $-v(\epsilon)$ of the Strange state will be permuted on the discrete phase space.
-We denote by $E_s$ the eigenvalue of $H$ where the associated eigenvector has Wigner distribution overlapping the negative component of the magic state $C\rho_S(\epsilon)C^\dagger$.
-This is unique, since the eigenstates form an orthonormal basis.
-
-The Wigner distribution of state $\tau$ is then given by
-\begin{align}
-	\W[\bmx]{\tau} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z}W_{|k\>\<k|}(x, p) \nonumber\\
-	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z} \delta_{x, k} = \frac{e^{-\beta E_x}}{3\Z},
-\end{align}
-where $x$ labels one of the three vertical lines in the phase space.
-The rescaled Wigner distribution $W_{\rho|\tau}(\x)$ can now be computed.
-It has $9$ components, but these come with multiplicities.
-In total, there are four distinct values on the phase space, as illustrated in~\cref{fig:pd_split}.
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.45]{figs/pd_split_thermal.pdf}
-    \caption{\textbf{Qutrit phase space regions for $W_{\rho | \tau}(\x)$.}
-    Here, the negative component of the magic state overlaps the Wigner distribution of $|0\>$.
-The rescaled distribution attains a single value in each of the four regions, proportional to the value depicted in the region, see~\cref{eq:bmw_rescaled}.
-    }
-    \label{fig:pd_split}
-\end{figure}
-
-We denote by $\w(\rho), \w(\rho|\tau)$ the unique values occurring in $W_\rho(\x), W_{\rho|\tau}(\x)$ respectively and $\bmm$ the vector of associated multiplicities of each value in $W_\rho(\x)$.
-The component values and multiplicities of the relevant distributions in the four distinct regions are given by
-\begin{align}
-	\w(\rho) &\coloneqq (-v, u, u, u), \\
-		\bmm &\coloneqq (1,2,3,3), \\
-	\w(\tau) &\coloneqq \frac{1}{3\Z} \left( e^{-\beta E_0}, e^{-\beta E_0}, e^{-\beta E_1}, e^{-\beta E_2} \right), \\
-	\w(\rho_{\rm{S}} | \tau) &\coloneqq 3\Z \left( -v e^{\beta E_0}, u e^{\beta E_0}, u e^{\beta E_1}, u e^{\beta E_2} \right). \label{eq:bmw_rescaled}
-\end{align}
-
-Using this notation, the values and multiplicities of the $n$--copy distribution $\bmw(\rho_n |\tau_n)$ are computed in~\cref{lem:ncopycomponents}. The values are given by 
-\begin{align}\label{eq:ncopy_w_rescaled}
-	[\w(\rho_n | \tau_n)]_{ijk} &= (3\Z)^{n} (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )},
-\end{align}
-where the indices $i,j,k$ are non-negative integers that obey the constraint $\alpha \coloneqq i+j+k \leq n$.
-The multiplicity of this above value is $m_{ijk}$ with
-\begin{equation}
-	m_{ijk} = \frac{n!}{i!j!k!(n-\alpha)!} 2^i 3^j 3^k.
-\end{equation}
-The associated components of $\w(\rho_n)$ are given by
-\begin{align}
-	[\w(\rho_n)]_{ijk} &= (-v)^{n-\alpha} u^{\alpha}, \label{eq:ncopy_wrho}\\
-	[\w(\tau)]_{ijk} &= (3\Z)^{-n} e^{-\beta (n-\alpha)E_s} e^{-\beta ( i E_0 + j E_1 + k E_2 )}. \label{eq:ncopy_wsigma}
-\end{align}
-
-In order to construct the $n$--copy Lorenz curve $L_{\rho_n|\tau_n}(x)$ we need to order the components of the distribution, $w(\rho_{\rm{S}} | \tau)_{ijk}$ in decreasing order, and identify the sequence of indices that give us $W_{\rho_n}(\pi(\x))$.
-
-However, it again suffices to use only the constraint from the first elbow $(x_0, L_0)$ of $L_{\rho_n|\tau_n}(\x)$. We therefore compute the largest component 
-\begin{equation}
-	w_{\rm max} \coloneqq \max_{i,j,k} [\w(\rho_n | \tau_n)]_{ijk},
-\end{equation}
-and determine the indices at which this occurs.
-Putting in the values we obtain
-\begin{align}
-	&(3\Z)^{-n}w_{\rm max} = \nonumber\\
-	&\max\limits_{i,j,k}\Big\{ (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \label{eq:max_slope}
-\end{align}
-where $0 \leq i,j,k \leq n$ and $\alpha \coloneqq i+j+k \leq n$.
-Now for $0 \leq \epsilon \leq 3/7$, we have $v \geq u$. Since we assume that $n$ is even, we need the sum $\alpha = i+j+k$ to be even too, so that the expression is positive.
-
-Given an even value for $\alpha$, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_s}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
-Hence, we have
-\begin{align}
-	&w_{\rm max} = \nonumber\\
-	&(3\Z)^{n} v^n e^{n\beta E_s}\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_s)} \right)^{\alpha} \Big\}}.
-\end{align}
-If the expression $\frac{u(\epsilon)}{v(\epsilon)} e^{\beta (E_{\rm{max}} - E_s)}$ is less than $1$ then the maximum occurs at $\alpha=0$, otherwise it occurs at $\alpha = n$.
-For a fixed state $\tau$, this transition is determined by the value of the depolarising error parameter $\epsilon$ of the noisy magic state.
-The transition occurs at $\epsilon = \epsilon_\star$ where
-\begin{equation}\label{eq:noise_transition}
-	\frac{u(\epsilon_\star)}{v(\epsilon_\star)} e^{\beta (E_{\rm{max}} - E_s)} = \frac{3-\epsilon_\star}{6-8\epsilon_\star} e^{\beta (E_{\rm{max}} - E_s)} = 1.
-\end{equation}
-If $E_{\rm{max}} = E_s$, namely if the state negativity lies in the same phase space region as the highest energy, this threshold is constant in temperature and given by $\epsilon_{\star} = 3/7$.
-However, the condition that $\epsilon_\star \ge 0$ also implies a constraint on the effective temperature of the stabilizer state.
-Specifically, there is a threshold temperature value $\beta_\star$ given by
-\begin{equation}
-	\beta_{\star} \coloneqq \frac{1}{E_{\rm{max}} - E_s} \ln2,
-\end{equation}
-such that for the regime $0 \leq \beta \leq \beta_\star$ a threshold error $\epsilon_\star$ exists, and for $\beta > \beta_\star$ no such transition exists, so we choose $\epsilon_\star = 0$. 
-Therefore, the transition value for the noise is given by
-\begin{equation}
-	\epsilon_{\star}(\beta) \coloneqq 
-	\begin{cases}
-		3 - \dfrac{9}{4-2^{\beta/\beta_\star - 1}}, &\text{ for } \beta \leq \beta_\star \\
-		0, &\text{ for } \beta > \beta_\star.
-	\end{cases}
-\end{equation}
-The quantity $w(\rho_{\rm{S}} | \sigma)_{\rm{max}}$ is now given by
-\begin{equation*}
-w_{\rm max} =
-	\begin{cases}
-		(3\Z)^{n} v^n e^{n\beta E_s}, &\mbox{if }\epsilon \leq \epsilon_{\star},\ \hspace{3pt}\rm{(C1)}\\
-		(3\Z)^{n} u^n e^{n\beta E_{\rm{max}}}, &\mbox{if }\epsilon > \epsilon_{\star}.\ \hspace{5pt}\rm{(C2)} 
-	\end{cases}
-\end{equation*}
-Case $\rm{(C1)}$ corresponds to $(i,j,k) = (0,0,0)$, so the multiplicity is $m_{000} = 1$, while
-Case $\rm{(C2)}$ corresponds to
-\begin{equation}
-	(i,j,k) = 
-	\begin{cases}
-	(0,n,0), &\text{if } E_{\rm{max}} = E_1, \\
-	(0,0,n), &\text{if } E_{\rm{max}} = E_2,
-	\end{cases}
-\end{equation}
-so the multiplicity in both cases is $3^n$.
-
-Using that $F = -\beta^{-1} \log \Z$, the first elbow coordinates in the two cases are now given by
-\begin{equation}\label{eq:first_elb_coords}
-	(x_0, L_0) =
-	\begin{cases}
-		\left(\frac{1}{3^n} e^{-n\beta (E_s - F)}, v^n \right), &\epsilon \leq \epsilon_\star \vspace{10pt}\\
-		\left( e^{-n\beta (E_{\rm{max}}-F)}, (3u)^n \right). &\epsilon > \epsilon_\star
-	\end{cases}
-\end{equation}
-
-Similarly, considering the output magic state with respect to state $\sigma'$, the image of equilibrium state $\sigma$ under the magic protocol, we get output Lorenz curve coordinates,
-\begin{equation}\label{eq:transformed_first_elb_coords}
-	(x'_0, L'_0) =
-	\begin{cases}
-		\left(\frac{1}{3^{n'}} e^{-n\beta (E'_s - F')}, v(\epsilon')^{n'} \right), &\epsilon' \leq \epsilon'_\star \vspace{10pt}\\
-		\left( e^{-n'\beta (E'_{\rm{max}}\hspace{-2.5pt}-F')}, (3u(\epsilon'))^{n'} \right), &\epsilon' > \epsilon'_\star
-	\end{cases}
-\end{equation}
-There are four combinations of coordinates, depending on the noise parameters $\epsilon, \epsilon'$ for the input and output states.
-In each of these combinations, we simply use the first elbow constraint, as described in~\cref{prop:first_elb}, and manipulate the coordinates as in the proof of~\cref{thm:free-energy}, leading to the bounds in the statement of the theorem.
-\end{proof}
-
 \end{document}

### 2021-06-06 magic_paper.tex
Merge choices made.

@@
     }
-    \label{fig:lcs}
+    \label{fig:H}
 \end{figure}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.35]{figs/test/D_vs_eps_a.pdf}
+    \caption{Here, the exponent is $\alpha =$ even$/$odd for $1.10 \leq \alpha \leq 1.50$. $D_\alpha$ is decreasing in $\alpha$ and $\epsilon$ (clear due to~\cref{thm:H2D}).
+    }
+    \label{fig:D}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.35]{figs/test/H_test.pdf}
+    \caption{Here, the exponent is $\alpha =$ even$/$odd for $0.10 \leq \alpha \leq 0.90$.
+$H_\alpha$ is decreasing in $\epsilon$ (not Schur-conocave for $\alpha < 1$) and increasing in $\alpha$ (clear due to~\cref{thm:H2D}).
+    }
+    \label{fig:Htest}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.35]{figs/test/D_test.pdf}
+    \caption{Here, the exponent is $\alpha =$ even$/$odd for $0.10 \leq \alpha \leq 0.90$.
+$D_\alpha$ is increasing in $\epsilon$ (not Schur-convex for $\alpha < 1$) and decreasing in $\alpha$ (clear due to~\cref{thm:H2D}).
+    }
+    \label{fig:Dtest}
+\end{figure}
+
+\begin{lemma}
+	Let $\alpha \geq \beta > 1$ where $\alpha, \beta$ are even$/$odd.
+	Then,
+	\begin{equation}
+		H_\alpha(\x) \geq H_\beta(\x) \text{ and } D_\alpha(\x || \r) \leq D_\beta(\x || \r)
+	\end{equation}
+	for any quasi-distribution $\x \in \mathbb{R}^N$ and probability distribution $\r \in \mathbb{R}^N$.
+\end{lemma}
+\begin{proof}
+	For $\alpha \geq \beta > 1$, we have
+	\begin{equation}
+		0 > \frac{1}{1-\alpha} \geq \frac{1}{1-\beta},
+	\end{equation}
+	and $w_i^\alpha = |w_i|^\alpha \leq |w_i|^\beta = w_i^\beta$.
+
+	\nick{how to proceed?}
+
+	For any $\r$ with positive rational components, we have $D_\alpha(\x || \r) \leq D_\beta(\x || \r)$ due to~\cref{thm:H2D}.
+\end{proof}
+
+We can prove additivity of $H_{\alpha}$ on quantum states.
+
+\begin{lemma}\label{H_add}
+	For any quantum states $\rho, \rho'$, we have
+	\begin{equation}
+		H_{\alpha}(\rho \otimes \rho') = H_{\alpha}(\rho) + H_{\alpha}(\rho'),
+	\end{equation}
+	where $\hspace{-1pt}\alpha\hspace{-1pt}$ is such that $\hspace{-1pt}H_\alpha(\sigma)\hspace{-2pt}$ is well-defined for all states $\sigma$.
+\end{lemma}
+\begin{proof}
+	This can be seen directly by the multiplicative property of the Wigner distribution,
+	\begin{align*}
+		H_{\alpha}&(\rho \otimes \rho') = \frac{1}{1-\alpha}\log \sum_{\bmx,\bmx'} \left[W_{\rho}(\bmx)W_{\rho}(\bmx')\right]^{\alpha} \\
+		&= \frac{1}{1-\alpha}\left( \log \sum_{\bmx}W_{\rho}(\bmx)^{\alpha} + \log \sum_{\bmx'}W_{\rho}(\bmx')^{\alpha} \right) \\
+		&= H_{\alpha}(\rho) + H_{\alpha}(\rho').
+	\end{align*}
+\end{proof}
 
@@
 Let's try to prove this.
+
 \begin{proof} If we have $H_\alpha (W_\rho(\x)) <0 $ then this implies that $\log \sum_{\x} W_\rho (\x)^\alpha > 1$, however it is known that $H_\alpha$ is always non-negative on probability distributions and therefore $W_\rho(\x)$ must be a strict quasi-distribution with negativity.
@@
 \end{equation}
+\nick{In this step, we also need to show that $H_\alpha$ is increasing in $\alpha$}
 Therefore, $H_\alpha (W_\rho (\x)) <0 $ at some point in the sequence, which completes the proof.
 \end{proof}
+
 Therefore Wigner negativity coincides with negativity of a Renyi entropy.
@@
 \end{document}
+
+\end{document}

### 2021-06-06 magic_paper.tex
Additional appendix edits.

@@
 \end{proof}
-\nick{Combining ALL the properties above (and nothing more) leads to the general bound}
 
@@
 
-\begin{proof} If we have $H_\alpha (W_\rho(\x)) <0 $ then this implies that $\log \sum_{\x} W_\rho (\x)^\alpha > 1$, however it is known that $H_\alpha$ is always non-negative on probability distributions and therefore $W_\rho(\x)$ must be a strict quasi-distribution with negativity.
+\begin{proof} If we have $H_\alpha (W_\rho(\x)) <0 $ for $\alpha >1$ then this implies that $\log \sum_{\x} W_\rho (\x)^\alpha > 1$, however it is known that $H_\alpha$ is always non-negative on probability distributions and therefore $W_\rho(\x)$ must be a strict quasi-distribution with negativity.
 
@@
 \end{align}
-where $\epsilon = a/b - 1 >0$. By choosing $a$ and $b$ appropriately we can make $\epsilon$ arbitrarily close to $0$ and therefore there exists a sequence $\epsilon_n=a_n/b_n$ such that
+where $\epsilon = a/b - 1 >0$.
+By choosing $a$ and $b$ appropriately we can make $\epsilon$ arbitrarily close to $0$.
+More precisely, there exists a sequence $\epsilon_n=a_n/b_n$ with valid integer pairs $a_n, b_n$ such that
 \begin{equation}
@@
 \end{equation}
-\nick{In this step, we also need to show that $H_\alpha$ is increasing in $\alpha$}
-Therefore, $H_\alpha (W_\rho (\x)) <0 $ at some point in the sequence, which completes the proof.
+Since $\frac{1}{1-\alpha}= -\frac{b_n}{a_n} <0$ for any $n$ it follows that $H_\alpha (W_\rho (\x)) = \frac{1}{1-\alpha} \log \sum_{\x} W_\rho (\x)^\alpha  <0 $ at some point in the sequence, which completes the proof.
 \end{proof}

### 2021-06-06 magic_paper.tex
Section on entropies of quasi-dists added to main text. Needs details+refs added.

@@
 
-W \nick{what is W?} can specify energetic details of a protocol through how much it would disturb some reference equilibrium state.
+We can specify energetic details of a protocol through how much it would disturb some reference equilibrium state.
 The magic state transformation is then considered relative to the equilibrium transformation, and can be recast via the Wigner representation into a relative majorization statement $(\w, \r) \succ (\w', \r')$ where $\w, \w'$ are quasi-distributions corresponding to the magic transformation, while $\r, \r'$ correspond to the transformation of the reference equilibrium state.
@@
 \newpage
-\subsection{Single-shot divergences for quasi-distributions}
-As already mentioned, the Wigner distribution is generally a quasi-distribution and so taking the Shannon entropy $H(\p) = -\sum_i p_i \log p_i$ of the Wigner distribution is not possible off of the set $\F$.
-However, does the same obstacle apply to Renyi entropies?
-The $\alpha$--Renyi entropy $H_\alpha(\p)$ is defined as
-\begin{equation}
-	H_\alpha(\p) := \frac{1}{1-\alpha} \log \sum_i p_i^\alpha,
-\end{equation}
-where $\alpha \ge 0$ and $\lim_{\alpha \rightarrow 1} H_\alpha(\p) = H(\p)$.
-It is clear that if we take $\alpha = 2m$ to be an even integer then $H_{2m}(\rho) := H_{2m}(W_\rho(\x))$ is always a well-defined function on Wigner quasi-distributions.
-However, it still remains to link such expressions to majorization of quasi-distributions.
-
-In this direction, we first note that the analysis for the temperature-dependent bound given by Equation (\ref{eq:rate_bounds_proof}) implicitly makes use of the single-shot Renyi divergence $D_\infty (\p ||\r)$, which is given by
+\section{Well-defined \& monotonic  entropies for quasi-distributions}
+We have considered Wigner distributions of magic states within a statistical mechanical setting in which it is was argued that magic should be viewed as a non-classical form of free energy.
+This identification with free energy was done at the level of majorization with respect to stochasticity corresponding to stabilizer operations.
+In this context non-equilibrium states with substantial free energy have Lorenz curves that deviate noticeably from the line $y=x$.
+We also found that when considered in a distillation protocol, magic could be linked to thermodynamic free energies in a non-trivial way.
+We can therefore ask: is it possible to make a more direct link between magic and free energy or entropy?
+
+One obstacle to linking with macroscopic, equilibrium free energy is that the Wigner distribution is generally a quasi-distribution and so the entropy $H(\w) = -\sum_i w_i \log w_i$ of the Wigner distribution is not defined off of the set $\F$, let alone being a physically meaningful quantity.
+
+However in this direction, we first note that the analysis for the temperature-dependent bound given by Equation (\ref{eq:rate_bounds_proof}) implicitly makes use of the single-shot Renyi divergence $D_\infty (\p ||\r)$, which is given by
 \begin{equation}
@@
 \end{equation}
+This does remain well-defined on quasi-distributions, and from the majorization relation also has a clear physical meaning.
 This motivates defining the following \emph{Wigner divergence} $D_\infty(\rho, \tau) := D_\infty (W_\rho(\x) || W_\tau (\x))$ on all quantum states.
@@
 See Appendix~\ref{app:lcst_technical} for the proof of this.
-Moreover, in the appendices we also prove that for unital processes the Renyi entropies $H_{2m}(\w)$ are monotones for any $m \in \mathbb{N}$ and lead the generalized distillation bounds.
-\begin{equation}
-R \le \frac{H_{2m}(\I/d)- H_{2m}(\rho)}{H_{2m}(\I/d)-H_{2m}(\rho')}.
-\end{equation}
-It is of interest to further explore this perspective and determine what components of single-shot information theory could be extended to quasi-distributions.
-
+
+We can now go further, and show that a range of entropies remain both well-defined and meaningful in this setting. The $\alpha$--Renyi entropy $H_\alpha(\p)$ is defined as
+\begin{equation}
+	H_\alpha(\p) := \frac{1}{1-\alpha} \log \sum_i p_i^\alpha.
+\end{equation}
+To extend to quasi-distributions we must ensure the following: (a) the entropy is well-defined on quasi-distributions, and (b) obeys monotonicity under stabilizer/free operations.
+In the Appendices we show the following.
+\begin{theorem} If $\alpha = \frac{2a}{2b-1}$ for integers $a,b \in \mathbb{N}$ and $a\ge b$ then $H_\alpha(\w)$ is well-defined on the set of quasi-distributions $\w$, and moreover if $\w \succ \w'$ for two quasi-distributions $\w, \w'$ then $H_\alpha (\w) \le H_\alpha(\w')$.
+\end{theorem}
+This therefore provides a meaningful extension of entropies to quasi-distributions.
+Moreover we can prove the following result, which establishes the equivalence between Wigner negativity and the existence of negative Renyi entropy.
+\begin{theorem} A quantum state $\rho$ has Wigner negativity if and only if $H_\alpha(W_\rho) <0$ for some $\alpha =  \frac{2a}{2b-1}$, with integers $a \ge b$.
+\end{theorem}
+Therefore, the statistical mechanical description of stabilizer operations provides a setting in which negative entropy is fully meaningful, and quantifies the fact that magic states are `more ordered' than a perfectly sharp, deterministic classical state $\w = (1,0, \dots , 0)$ with zero entropy.
+We note that prior work has shown that negative conditional entropy \ddd{[CITE: ``The thermodynamic meaning of
+negative entropy'']} arises in the context of quantum correlations, however this is unrelated to the present negative entropy.
+
+The $\alpha \rightarrow 1$ limit of the Renyi entropy is not well-defined, however the Renyi entropy description shows that this diverges to $-\infty$ due to the Lorenz curve $L_\rho(x)$ no longer being bounded by $1$.
+Alternatively, we can write the divergence as $-\epsilon \log \sum_{\x} |W_\rho (\x)|^{1+\epsilon}$ with $\epsilon \rightarrow 0^+$, which leads to a second new description of mana: \emph{it is the rate of divergence of the Renyi-entropy} as we approach the asymptotic Shannon entropy $H(\w)$.
+We also note the recent observation \ddd{[CITE Renyi Entropy and Free Energy by John C.
+Baez]}that in standard statistical mechanics that $H_\alpha(\p)$ can be related to the ``$q$--derivative'' of free energy.
+Therefore, we might speculate if the presence of magic in Clifford circuits admits a rigorous interpretation in terms of a phase transition signalled by a first-order divergence in the Wigner free energy.
+However since variation in $\alpha$ is no longer smooth ($\alpha$ is restricted to a dense set of rational values) technical obstacles exist and we do not pursue this speculative line here, but just note that other works exist in which computational transitions are considered in relation to phase transitions [Need to cite].
+
+However, every entropy is best understand as a relative entropy and so we now state the extension to Renyi divergences. \ddd{[Add statements of monotonicity under free ops]}
+
+We can now apply this to obtain new magic bounds. \ddd{[Add]}
 \section{Outlook and open questions}
@@
 Our bounds exploited relatively simple aspects of the Lorenz curves of the quasi-distributions, so it would be of interest to sharpen these bounds and obtain a better handle on the Lorenz curve structure in the $n\rightarrow \infty$ limit.
-This raises interesting \nick{questions in the context of statistical mechanics} as we no longer have a notion of typicality and the central limit theorem does not apply.
+This raises interesting questions in the context of statistical mechanics as we no longer have a notion of typicality and the central limit theorem does not apply.
 That said, for special states such as the Strange state, the asymptotic behaviour is relatively simple, so exact asymptotics for this should be possible.
@@
 
-3. This property follows from the multiplicativity of the WIgner distribution.
+3. This property follows from the multiplicativity of the Wigner distribution.
 In particular,
@@
 \end{theorem}
-Let's try to prove this.
-
+The proof of this is as follows.
 \begin{proof} If we have $H_\alpha (W_\rho(\x)) <0 $ for $\alpha >1$ then this implies that $\log \sum_{\x} W_\rho (\x)^\alpha > 1$, however it is known that $H_\alpha$ is always non-negative on probability distributions and therefore $W_\rho(\x)$ must be a strict quasi-distribution with negativity.
@@
 
-\ddd{[Looking at this limit it almost feels like the $\alpha \rightarrow 1^+$ limit is actually giving mana....modulo the technical problem of taking the limit without calculus.
-I will think more about this point.]}
-
 \end{document}

### 2021-06-06 magic_paper.tex
Minor typos. Done for day.

@@
 The $\alpha \rightarrow 1$ limit of the Renyi entropy is not well-defined, however the Renyi entropy description shows that this diverges to $-\infty$ due to the Lorenz curve $L_\rho(x)$ no longer being bounded by $1$.
-Alternatively, we can write the divergence as $-\epsilon \log \sum_{\x} |W_\rho (\x)|^{1+\epsilon}$ with $\epsilon \rightarrow 0^+$, which leads to a second new description of mana: \emph{it is the rate of divergence of the Renyi-entropy} as we approach the asymptotic Shannon entropy $H(\w)$.
+Alternatively, we can write the divergence of the entropy as $-\epsilon^{-1} \log \sum_{\x} |W_\rho (\x)|^{1+\epsilon}$ with $\epsilon \rightarrow 0^+$, which leads to a second new description of mana: \emph{it is the rate of divergence of the Renyi-entropy} as we approach the limiting Shannon entropy $H(\w)$.
 We also note the recent observation \ddd{[CITE Renyi Entropy and Free Energy by John C.
@@
 Therefore, we might speculate if the presence of magic in Clifford circuits admits a rigorous interpretation in terms of a phase transition signalled by a first-order divergence in the Wigner free energy.
-However since variation in $\alpha$ is no longer smooth ($\alpha$ is restricted to a dense set of rational values) technical obstacles exist and we do not pursue this speculative line here, but just note that other works exist in which computational transitions are considered in relation to phase transitions [Need to cite].
+However since variation in $\alpha$ is no longer smooth ($\alpha$ is restricted to a dense set of rational values) technical obstacles exist and we do not pursue this speculative line here, but just note that other works exist in which computational transitions are considered in relation to phase transitions \ddd{[Need to cite]}.
 

### 2021-06-07 magic_paper.tex
Trialing a new title.
Potentially better title.
Changes made, some rearrangement required

@@
 % Labels and Refs (consistency, cref vs ref, thm vs lem vs prop, ??)
-% Figs check(fig.0, move to app, consistency)
-
-% Notation consistency (R is rate not bound, noise vs error, \ln{} -> \ln, italics, keep \bmx for vectors?)
+% Figs check(fig.0, move to app, consistency, cbars, iffalse)
+
+% Notation consistency (noise vs error, \ln{} -> \ln, italics, Aberg -> {\AA}berg)
 % UK vs US english
@@
 
-\title{General constraints on magic distillation protocols from statistical mechanics}
+\title{Statistical mechanics of Wigner negativity and magic states in quantum computation}
 
@@
 For the case where this reference state is a thermal state at some temperature $T$ our magic distillation bounds are functions of $T$, the noise parameters $\epsilon, \epsilon'$, and the free energy the protocol channel $\E$ injects in.
-In addition a quantity $\phi$ links the computational and physical aspects, and corresponds to the degree to which Wigner negativity in $\rho$ can be assigned a sharp energy via the system Hamiltonian.}
+In addition, a quantity $\phi$ links the computational and physical aspects, and corresponds to the degree to which Wigner negativity in $\rho$ can be assigned a sharp energy via the system Hamiltonian.}
     \label{fig:sketch}
@@
 The phase-point operators form an orthogonal operator basis with respect to the Hilbert-Schmidt inner product, as discussed in~\cref{app:wigner}.
-Therefore, any quantum state $\rho \in \cal{B}(\cal{H}_d)$ can be expressed as a linear combination of them,
-\begin{equation}
-    \rho = \sum_{\bmz \in \cal{P}_d} \W[\bmz]{\rho} A_{\bmz},
-\end{equation}
-where the coefficient vector $\W{\rho}$ is the Wigner distribution of state $\rho$,
+Therefore, any quantum state $\rho \in \cal{B}(\cal{H}_d)$ can be expressed as a linear combination of them, $\rho = \sum_{\bmz \in \cal{P}_d} \W[\bmz]{\rho} A_{\bmz}$, where the coefficient vector $\W{\rho}$ is the Wigner distribution of state $\rho$,
 \begin{equation}\label{eq:wstate}
@@
 More precisely, $W_\rho(\x)$ is a bounded real-valued function on $\P_d$ with the normalisation property $\sum_{\x} W_\rho(\bmx) = 1$ (see~\cref{app:wigner} for details).
-In~\cref{fig:wstate_examples}, we show Wigner distributions of different types of qutrit states.
-
-\begin{figure}[t]
-    \centering
-    \subfigure[][]{%
-    \label{fig:maxmix}%
-    \includegraphics[height=2cm]{figs/maxmixed.pdf}
-    }\hspace{8pt}%
-    \subfigure[][]{%
-    \label{fig:zero}%
-    \includegraphics[height=2cm]{figs/zerostate.pdf}
-    }\\
-    \subfigure[][]{%
-    \label{fig:bound}%
-    \includegraphics[height=2cm]{figs/boundstate.pdf}
-    }\hspace{8pt}%
-    \subfigure[][]{%
-    \label{fig:Strange}%
-    \includegraphics[height=2cm]{figs/Strangestate.pdf}
-    }
-    \caption{\textbf{Qutrit Wigner distributions of varying magic.} 
-    \subref{fig:maxmix} Maximally mixed state $\frac{1}{3}\id$; \subref{fig:zero} Stabilizer zero state $|0\>\<0|$; \subref{fig:bound} A non-stabiliser Wigner-positive state; \subref{fig:Strange} Magic Strange state $\ket{{\rm{S}}} = \frac{1}{\sqrt{2}}(\ket{1} - \ket{2})$, coined in~\cite{cit:veitch2}.
-    }%
-    \label{fig:wstate_examples}
-\end{figure}
 
@@
 
+\nick{Is the following result more distinguished than other results we have in the appendices?}
 \begin{lemma} Let $\w \in \mathbb{R}^n,\w'\in \mathbb{R}^m$ be quasi-distributions, and let $\r \in \mathbb{R}^n, \r' \in \mathbb{R}^m$ be probability distributions with non-zero components.
@@
 
+\iffalse
 \begin{figure}[t]
@@
 \end{figure}
+\fi
 
@@
     Majorisation provides stricter rates than the global mana and max--thauma bounds.
-    Numerical bounds $R_{\rm{opt}}$ obtained by full Lorenz curve comparison for some Strange state purification processes with even number of copies $m,n \leq 30$ highlight that the first elbow constraint can be improved.
+    Numerical bounds $R_{\rm{num}}$ obtained by full Lorenz curve comparison for some Strange state purification processes with even number of copies $m,n \leq 30$ highlight that the first elbow constraint can be improved.
     }
@@
 This motivates defining the following \emph{Wigner divergence} $D_\infty(\rho, \tau) := D_\infty (W_\rho(\x) || W_\tau (\x))$ on all quantum states.
-In Appendix~\ref{app:lcst_technical}, we show that this divergence has the following natural properties that are derived via relative majorization.
+In~\cref{app:lcst_technical}, we show that this divergence has the following natural properties that are derived via relative majorization.
 \begin{theorem} Let $\tau$ be in the interior of $\F$, and define the Wigner divergence $D_\infty(\rho,\tau) := D_\infty(W_\rho(\x) || W_\tau (\x))$.
@@
 Therefore, the statistical mechanical description of stabilizer operations provides a setting in which negative entropy is fully meaningful, and quantifies the fact that magic states are `more ordered' than a perfectly sharp, deterministic classical state $\w = (1,0, \dots , 0)$ with zero entropy.
-We note that prior work has shown that negative conditional entropy \ddd{[CITE: ``The thermodynamic meaning of
-negative entropy'']} arises in the context of quantum correlations, however this is unrelated to the present negative entropy.
+We note that prior work has shown that negative conditional entropy~\cite{rio_thermodynamic_2011} arises in the context of quantum correlations, however this is unrelated to the present negative entropy.
 
@@
 Alternatively, we can write the divergence of the entropy as $-\epsilon^{-1} \log \sum_{\x} |W_\rho (\x)|^{1+\epsilon}$ with $\epsilon \rightarrow 0^+$, which leads to a second new description of mana: \emph{it is the rate of divergence of the Renyi-entropy} as we approach the limiting Shannon entropy $H(\w)$.
-We also note the recent observation \ddd{[CITE Renyi Entropy and Free Energy by John C.
-Baez]}that in standard statistical mechanics that $H_\alpha(\p)$ can be related to the ``$q$--derivative'' of free energy.
+We also note the recent observation~\cite{baez2011renyi} that in standard statistical mechanics that $H_\alpha(\p)$ can be related to the ``$q$--derivative'' of free energy.
 Therefore, we might speculate if the presence of magic in Clifford circuits admits a rigorous interpretation in terms of a phase transition signalled by a first-order divergence in the Wigner free energy.
@@
 
-However, every entropy is best understand as a relative entropy and so we now state the extension to Renyi divergences. \ddd{[Add statements of monotonicity under free ops]}
-
-We can now apply this to obtain new magic bounds. \ddd{[Add]}
+However, every entropy is best understood as a relative entropy and so we now state the extension to Renyi divergences.
+The $\alpha$--Renyi divergence $D_\alpha(\p)$ is defined as
+\begin{equation}
+	D_\alpha(\p|\r) := \frac{1}{\alpha-1} \log \sum_i p_i^\alpha r_i^{1-\alpha},
+\end{equation}
+where $\p$ is a quasi-distribution, $\r$ a probability distribution with positive components and $\alpha$ takes the same values as for $H_\alpha$.
+In~\cref{app:lcst_technical}, we also show that the divergence satisfies the following natural properties for all $\alpha$ for which it is well-defined.
+
+\begin{theorem}\label{thm:Da_props} 
+	Let $\tau$ be a state in the interior of $\F$ and $\alpha = 2a / (2b-1)$ for non-negative integers $a,b$ with $a \geq b$.
+Then, the $\alpha$-Renyi divergence $D_\alpha(W_\rho || W_\tau)$ is well-defined for all states $\rho$, and the following hold:
+\begin{enumerate}
+\item $D_\alpha(W_\rho || W_\tau) \ge 0$ for all quantum states $\rho$.
+\item  $D_\alpha(W_\rho || W_\tau) = 0$ if and only if $\rho =\tau$.
+\item $D_\alpha(W_{\rho^{\otimes n}} || W_{\tau^{\otimes n}}) = n D_\alpha(W_\rho || W_\tau)$ for any $n \in \mathbb{N}$.
+\item $D_\alpha(W_\rho || W_\tau) \geq D_\alpha (W_{\E(\rho)} || W_{\E(\tau)})$ for any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$.
+\end{enumerate}
+\end{theorem}
+
+We can now apply this to obtain new magic bounds.
+\begin{theorem}
+	Consider a general magic state distillation process that converts a magic state $\rho^{\otimes n} \longrightarrow \rho'^{\otimes m}$ as well as an equilibrium state $\tau^{\otimes n} \longrightarrow \tau'^{\otimes m}$
+
+	We have the following family of upper bounds on the distillation rate $R := n'/n$,
+	\begin{equation}
+		R \leq \frac{D_{\alpha}(W_\rho||W_\tau)}{D_{\alpha}(W_{\rho'}||W_{\tau'})} = \frac{F_\alpha(W_\rho) - F_\alpha(W_\tau)}{F'_\alpha(W_{\rho'}) - F'_\alpha(W_{\tau'})},
+	\end{equation}
+	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ and $\beta F_\alpha(W_\rho) := D_\alpha (W_\rho || W_\tau) - \log \Z$ is the $\alpha$--free energy. 
+\end{theorem}
+
+\begin{figure}[t!]
+    \centering
+    \subfigure[][]{%
+    \label{fig:Ra}%
+    \includegraphics[scale=0.4]{figs/Ra_vs_a_eps.pdf}}\\
+    \subfigure[][]{%
+    \label{fig:RaDiff}%
+    \includegraphics[scale=0.4]{figs/RaDiff_vs_a_eps.pdf}}
+    \caption{$R_\alpha$}
+    \label{fig:rate_a_contour}
+\end{figure}
+
 \section{Outlook and open questions}
@@
 \item $D_\infty(\rho^{\otimes 2n}, \tau^{\otimes 2n}) = n D_\infty(\rho^{\otimes 2} ,\tau^{\otimes 2})$ for any $n \in \mathbb{N}$.
-\nick{annoying that it doesn't agree with the simpler property of $D_\alpha$ for finite $\alpha$ in~\cref{thm:Da_props}}
 \item For any quantum state $\rho$, and any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$, we have $D_\infty (\rho , \tau) \ge D_\infty (\E(\rho), \E(\tau))$.
@@
 
-\begin{table}[h]
-  \def\arraystretch{1.5}
-  \centering
-  \begin{tabular}{c|c|c|c||c|c}
-    $w_i$ & $w_{i+1}$ & $\alpha$ & $\frac{w_i^{\alpha-1}}{\alpha-1} \geq \frac{w_{i+1}^{\alpha-1}}{\alpha-1}$ & $\alpha$ & $\frac{w_i^{\alpha-1}}{\alpha-1} \geq \frac{w_{i+1}^{\alpha-1}}{\alpha-1}$ \\[0.5ex]\hline
-    $2$ & $1.5$  & $3$ & $2 > 1.125$ T & $1/3$ & $-0.94 > -1.14$ T \\
-    $2$ & $-1.5$ & $3$ & $2 > 1.125$ T & $1/3$ & $-0.94 > -1.14$ T \\
-    $2$ & $-2.5$ & $3$ & $2 < 3.125$ F & $1/3$ & $-0.94 < -0.81$ F \\[0.5ex]\hline
-    $2/3$ & $1/3$  & $3$ & $0.22 > 0.06$ T & $1/3$ & $-1.97 > -3.12$ T \\
-    $2/3$ & $-1/3$ & $3$ & $0.22 > 0.06$ T & $1/3$ & $-1.97 > -3.12$ T \\
-    $2/3$ & $-4/3$ & $3$ & $0.22 < 0.89$ F & $1/3$ & $-1.97 < -1.24$ F \\[0.5ex]\hline
-    $2$ & $1.5$  & $4$ & $2.67 > 1.125$ T & $2/3$ & $-2.38 > -2.62$ T \\
-    $2$ & $-1.5$ & $4$ & $2.66 > -1.125$ T & $2/3$ & $-2.38 > 2.62$ F \\
-    $2$ & $-2.5$ & $4$ & $2.66 > 5.21$ T & $2/3$ & $-2.38 > 2.21$ F \\
-    $-2$ & $-2.5$ & $4$ & $-2.66 > -5.21$ T & $2/3$ & $2.38 > 2.21$ T \\[0.5ex]\hline
-    $2/3$ & $1/3$  & $4$ & $0.10 > 0.01$ T & $2/3$ & $-3.43 > -4.33$ T \\
-    $2/3$ & $-1/3$ & $4$ & $0.10 > -0.01$ T & $2/3$ & $-3.43 > 4.33$ F \\
-    $2/3$ & $-4/3$ & $4$ & $0.10 > -0.79$ T & $2/3$ & $-3.43 > 2.73$ F \\
-    $-1/3$ & $-2/3$ & $4$ & $-0.01 > -0.10$ T & $2/3$ & $4.33 > 3.43$ T \\
-    $-1/3$ & $-4/3$ & $4$ & $-0.01 > -0.79$ T & $2/3$ & $4.33 > 2.73$ T
-  \end{tabular}
-  \caption{\nick{NUMERICS ON SCHUR-OSTROWSKI CONDITION} The case $\alpha=$ even$/$odd and $\alpha > 1$ works for any combination of $w_i, w_{i+1}$ with $w_i > w_{i+1}$. 
-  All other cases do not work.
-  I put it here cause it's clunky}
-  \label{tab:test}
-\end{table}
-
 \subsection{Well-defined Renyi entropies on quasi-distributions}
-
-\ddd{[ISSUE WITH NOTATION: We can't clash with the quantum Renyi entropies. I think we have to use $H_\alpha(W_\rho)$ is bulky...but hopefully clear.]}
 
@@
 \begin{equation}
-	H_0(W_\rho) = 2\log_2 d = H_\alpha \left( \id/d \right),
+	H_0(W_\rho) = 2\log_2 d = H_\alpha \left( W_{\id/d} \right),
 \end{equation}
 where $d$ is the dimension of $\rho$.
-Inducing any magic state $\rho$ with depolarising noise, $\rho(\epsilon) = (1-\epsilon)\rho + \epsilon \sigma$ results in $H_{\alpha}\left(\rho(\epsilon)\right) \leq H_\alpha(\rho)$ because there exists a free operation $\E \in \O$ that transforms $\rho(\epsilon) = \E(\rho)$ and $H_\alpha$ is Schur-concave.
 
 For $\rho = \rho_{\rm{S}}(\epsilon)$, we get
-\begin{equation}
-	H_{\alpha}\left(\rho_{\rm{S}}(\epsilon)\right) = \frac{1}{1-\alpha}\log_2 \left[ 8\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^\alpha + \left(-\frac{1}{3} + \frac{4}{9}\epsilon \right)^\alpha \right]
-\end{equation}
+\begin{align}
+	&H_{\alpha}\left(W_{\rho_{\rm{S}}(\epsilon)}\right) = \frac{1}{1-\alpha}\log_2 \left[ 8\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^\alpha + \left(-\frac{1}{3} + \frac{4}{9}\epsilon \right)^\alpha \right] \nonumber\\
+	&= \frac{\alpha}{\alpha-1}\log_2 18+ \frac{1}{1-\alpha}\log_2 \left[ 8(3-\epsilon)^\alpha + (6-8\epsilon)^\alpha \right]
+\end{align}
 
@@
     \includegraphics[scale=0.35]{figs/test/H_test.pdf}
-    \caption{Here, the exponent is $\alpha =$ even$/$odd for $0.10 \leq \alpha \leq 0.90$.
-$H_\alpha$ is decreasing in $\epsilon$ (not Schur-conocave for $\alpha < 1$) and increasing in $\alpha$ (clear due to~\cref{thm:H2D}).
+    \caption{Here, the exponent is $\alpha =$ even$/$odd for $0.10 \leq \alpha \leq 0.90$. $H_\alpha$ is decreasing in $\epsilon$ (not Schur-conocave for $\alpha < 1$) and increasing in $\alpha$.
     }
@@
 
-\begin{lemma}
-	Let $\alpha \geq \beta > 1$ where $\alpha, \beta$ are even$/$odd.
-	Then,
-	\begin{equation}
-		H_\alpha(\x) \geq H_\beta(\x) \text{ and } D_\alpha(\x || \r) \leq D_\beta(\x || \r)
-	\end{equation}
-	for any quasi-distribution $\x \in \mathbb{R}^N$ and probability distribution $\r \in \mathbb{R}^N$.
-\end{lemma}
-\begin{proof}
-	For $\alpha \geq \beta > 1$, we have
-	\begin{equation}
-		0 > \frac{1}{1-\alpha} \geq \frac{1}{1-\beta},
-	\end{equation}
-	and $w_i^\alpha = |w_i|^\alpha \leq |w_i|^\beta = w_i^\beta$.
-
-	\nick{how to proceed?}
-
-	For any $\r$ with positive rational components, we have $D_\alpha(\x || \r) \leq D_\beta(\x || \r)$ due to~\cref{thm:H2D}.
-\end{proof}
-
-We can prove additivity of $H_{\alpha}$ on quantum states.
-
-\begin{lemma}\label{H_add}
-	For any quantum states $\rho, \rho'$, we have
-	\begin{equation}
-		H_{\alpha}(\rho \otimes \rho') = H_{\alpha}(\rho) + H_{\alpha}(\rho'),
-	\end{equation}
-	where $\hspace{-1pt}\alpha\hspace{-1pt}$ is such that $\hspace{-1pt}H_\alpha(\sigma)\hspace{-2pt}$ is well-defined for all states $\sigma$.
-\end{lemma}
-\begin{proof}
-	This can be seen directly by the multiplicative property of the Wigner distribution,
-	\begin{align*}
-		H_{\alpha}&(\rho \otimes \rho') = \frac{1}{1-\alpha}\log \sum_{\bmx,\bmx'} \left[W_{\rho}(\bmx)W_{\rho}(\bmx')\right]^{\alpha} \\
-		&= \frac{1}{1-\alpha}\left( \log \sum_{\bmx}W_{\rho}(\bmx)^{\alpha} + \log \sum_{\bmx'}W_{\rho}(\bmx')^{\alpha} \right) \\
-		&= H_{\alpha}(\rho) + H_{\alpha}(\rho').
-	\end{align*}
-\end{proof}
-
 We now make use of known results from majorization theory to establish the Schur-concavity of $H_\alpha$ on Wigner quasi-distributions where $\alpha$ is such that $H_\alpha$ is well-defined. 
@@
 
-Example 1: if $\alpha =$ odd$/$odd, then $f(w)$ is not monotonous because the sign of $f'(w)$ would depend on the sign of $w$. 
-In~\cref{tab:test}, this case fails when $w_i > 0 > -w_i > w_{i+1}$.
-
-Example 2: if $\alpha =$ even$/$odd and $\alpha < 1$, then  $f(w)$ is not monotonous across $0$ because and in fact $\lim_{w\rightarrow 0^+} f(w) = -\infty$, while $\lim_{w\rightarrow 0^-} f(w) = +\infty$.
-In~\cref{tab:test}, this case fails when $w_i > 0 > w_{i+1}$.
+If $\alpha =$ odd$/$odd, then $f(w)$ is not monotonous because the sign of $f'(w)$ would depend on the sign of $w$.
+
+If $\alpha =$ even$/$odd and $\alpha < 1$, then $H_\alpha$ is Schur-convex.
 }
@@
 The set $F := \{2a/(2b-1): a,b \in \mathbb{N} \text{ and } a \geq b\}$ is dense in the rationals $\mathbb{Q}_{>1}$, which in turn are dense in the reals $\mathbb{R}_{>1}$, as any rational $c/d$ with $c>d$ can be approximated by a sequence $f_n := c2^n / (d2^n-1)$ with every element $f_n$ in the set $F$.
-\nick{can turn into lemma}
 
@@
 \begin{equation}
-	D_\alpha(\rho || \tau) := \frac{1}{\alpha - 1} \log_2 \sum_{\bmx} W_{\rho}(\bmx)^\alpha W_{\tau}(\bmx)^{1-\alpha},
+	D_\alpha(W_\rho || W_\tau) := \frac{1}{\alpha - 1} \log_2 \sum_{\bmx} W_{\rho}(\bmx)^\alpha W_{\tau}(\bmx)^{1-\alpha},
 \end{equation}
@@
 	Let $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$. 
-	Then, $D_\alpha$ is Schur-convex, i.e.
-let $\w, \w' \in \mathbb{R}^N$ be quasi-distributions and $\r, \r' \in \mathbb{R}^N$ be probability distributions with positive rational entries given by $r_i = a_i/K$ and $r_i' = a_i'/K$ for positive integers $a_i, a_i'$ and $K = \sum_{i=1}^N a_i = \sum_{i=1}^{N'} a_i'$.
-	Then, we have $D_\alpha(\w || \r) \geq H_\alpha(\w' || \r')$, whenever $(\w, \r) \succ (\w', \r')$.
+	Then, $D_\alpha$ is Schur-convex, i.e. $D_\alpha(\w || \r) \geq D_\alpha(\w' || \r')$, whenever $(\w, \r) \succ (\w', \r')$.
 \end{theorem}
@@
 	\end{equation}
-	which due to~\cref{thm:H2D} is equivalent to
+	which, due to~\cref{thm:H2D}, is equivalent to
 	\begin{equation}
@@
 	Let $\tau$ be a state in the interior of $\F$ and $\alpha = 2a / (2b-1)$ for non-negative integers $a,b$ with $a \geq b$.
-Then, the $\alpha$-Renyi divergence $D_\alpha(\rho, \tau)$ is well-defined for all states $\rho$, and the following hold:
+Then, the $\alpha$-Renyi divergence $D_\alpha(W_\rho || W_\tau)$ is well-defined for all states $\rho$, and the following hold:
 \begin{enumerate}
-\item $D_\alpha(\rho || \tau) \ge 0$ for all quantum states $\rho$.
-\item  $D_\alpha(\rho || \tau) = 0$ if and only if $\rho =\tau$.
-\item $D_\alpha(\rho^{\otimes n} || \tau^{\otimes n}) = n D_\alpha(\rho, \tau)$ for any $n \in \mathbb{N}$.
-\item $D_\alpha(\rho || \tau) \geq D_\alpha (\E(\rho) || \E(\tau))$ for any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$.
+\item $D_\alpha(W_\rho || W_\tau) \ge 0$ for all quantum states $\rho$.
+\item  $D_\alpha(W_\rho || W_\tau) = 0$ if and only if $\rho =\tau$.
+\item $D_\alpha(W_{\rho^{\otimes n}} || W_{\tau^{\otimes n}}) = n D_\alpha(W_\rho || W_\tau)$ for any $n \in \mathbb{N}$.
+\item $D_\alpha(W_\rho || W_\tau) \geq D_\alpha (W_{\E(\rho)} || W_{\E(\tau)})$ for any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$.
 \end{enumerate}
@@
 In general, $W_\rho(\x)$ is a quasi-distribution, but the given form of $\alpha$ ensures that $W_{\rho}(\bmx)^\alpha \geq 0$. 
-Therefore $D_\alpha (\rho || \tau)$ is always well-defined.
-
-1. $D_\alpha$ is Schur-convex and every pair $(\w, \r)$ majorizes $(\r', \r')$, so
-\begin{equation}
-	D_\alpha(\w || \r) \geq D_\alpha(\r' || \r') = \frac{1}{\alpha-1} \log_2 \sum_{i} r_i = 0.
-\end{equation}
-
-2. In the inequality of property 1, equality holds iff $L_{\w|\r}(x) = L_{\r'|\r'}(x) = L_{\r|\r}(x)$ for all $x$ due to~\cref{prop:rmajor} which holds iff $\w = \r$.
+Therefore $D_\alpha (W_\rho || W_\tau)$ is always well-defined.
+
+1. $D_\alpha$ is Schur-convex and every pair $(W_{\rho}, W_{\tau})$ majorizes $(W_{\rho'}, W_{\rho'})$, so
+\begin{align}
+	D_\alpha(W_{\rho} || W_{\tau}) \geq D_\alpha(W_{\rho'} || W_{\rho'}) &= \nonumber\\
+	\frac{1}{\alpha-1} \log_2 \sum_{\bmx} W_{\rho'}(\bmx) &= 0.
+\end{align}
+
+2. In the inequality of property 1, equality holds iff $L_{\rho|\tau}(x) = L_{\rho'|\rho'}(x) = L_{\tau|\tau}(x)$ for all $x$ due to~\cref{prop:rmajor} which holds iff $\rho = \tau$.
 
@@
 \begin{align}
-	&D_\alpha(\rho^{\otimes n} || \tau^{\otimes n}) = \nonumber\\
+	&D_\alpha(W_{\rho^{\otimes n}} || W_{\tau^{\otimes n}}) = \nonumber\\
 	&\frac{1}{\alpha - 1} \log_2 \sum_{\bmx} W_{\rho^{\otimes n}}(\bmx)^\alpha W_{\tau^{\otimes n}}(\bmx)^{1-\alpha} = \nonumber\\
@@
 	&\sum_{i=1}^n \frac{1}{\alpha - 1} \log_2 \sum_{\bmx'} W_{\rho}(\bmx')^\alpha W_{\tau}(\bmx')^{1-\alpha} = \nonumber\\
-	&= n D_{\alpha}(\rho || \tau).
-\end{align}
-
-4. This follows immediately from Schur-convexity of $D_\alpha$.
-\end{proof}
-
-\subsubsection{General entropic bounds}
-
-We first derive the following entropic bounds on magic state transformations for unital processes.
+	&= n D_{\alpha}(W_\rho || W_\tau).
+\end{align}
+
+4. This follows immediately from the Schur-convexity of $D_\alpha$.
+\end{proof}
+
 \begin{theorem}
-	Consider a general magic state distillation process $\rho^{\otimes n} \rightarrow \rho'^{\otimes n'}$	in the unital fragment.
+	Consider a general magic state distillation process that converts a magic state $\rho^{\otimes n} \longrightarrow \rho'^{\otimes m}$ as well as an equilibrium state $\tau^{\otimes n} \longrightarrow \tau'^{\otimes m}$
+
 	We have the following family of upper bounds on the distillation rate $R := n'/n$,
 	\begin{equation}
-		R \leq \frac{D_{\alpha}(\rho||\id/3)}{D_{\alpha}(\rho'||\id/3)},
-	\end{equation}
-	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$.
+		R \leq \frac{D_{\alpha}(W_\rho||W_\tau)}{D_{\alpha}(W_{\rho'}||W_{\tau'})} = \frac{F_\alpha(W_\rho) - F_\alpha(W_\tau)}{F'_\alpha(W_{\rho'}) - F'_\alpha(W_{\tau'})},
+	\end{equation}
+	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ and $\beta F_\alpha(W_\rho) := D_\alpha (W_\rho || W_\tau) - \log \Z$ is the $\alpha$--free energy. 
 \end{theorem}
 \begin{proof}
-	For the given form of $\alpha$, $H_\alpha(\sigma)$ is well-defined adn Schur-concave for all quantum states $\sigma$.
-
-	We first regularise the number of output copies in the state distillation by tensoring in $(n-n')$ copies of the (free) maximally mixed state $\id/3$, so that we instead consider the process
-\begin{equation}
-	\rho^{\otimes n} \rightarrow \rho'^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n - n')}.
-\end{equation}
-Since we have that $W_{\rho^{\otimes n}}(\bmx) \succ_{\id/3} W_{\rho'^{\otimes n'}}(\bmx)$, by Schur-concativity of $H_\alpha$ we obtain
-\begin{equation}
-	H_\alpha \left( \rho^{\otimes n} \right) \leq H_\alpha \left( \rho'^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n - n')} \right).
-\end{equation}
-By additivity of $H_\alpha$, we can rewrite the inequality as
-\begin{equation}
-	n H_\alpha \left( \rho \right) \leq n' H_\alpha \left( \rho' \right) + (n - n') H_\alpha \left( \id/3 \right).
-\end{equation}
-Now, $H_\alpha \left( \id/3 \right)$ is the maximum value of $H_\alpha(\rho)$ for unital processes because every state $\rho$ majorizes $\id/3$, so we can finally re-arrange the inequality to
-\begin{equation}
-	\frac{n'}{n} \leq \frac{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho \right)}{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho' \right)} = \frac{D_{\alpha}(\rho||\id/3)}{D_{\alpha}(\rho'||\id/3)}.
-\end{equation}
-\end{proof}
-
-\begin{theorem}
-	Consider a general magic state distillation process that converts a magic state $\rho^{\otimes n} \longrightarrow \rho'^{\otimes n'}$ as well as an equilibrium state $\tau^{\otimes n} \longrightarrow \tau'^{\otimes n'}$
-
-	We have the following family of upper bounds on the distillation rate $R := n'/n$,
-	\begin{equation}
-		R \leq \frac{D_{\alpha}(\rho||\tau)}{D_{\alpha}(\rho'||\tau')} = \frac{F_\alpha(\rho) - F_\alpha( \tau)}{F'_\alpha(\rho') - F'_\alpha( \tau')},
-	\end{equation}
-	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ and $\beta F_\alpha(\rho) := D_\alpha (\rho || \tau) - \log \Z$ is the $\alpha$--free energy. 
-\end{theorem}
-\begin{proof}
-	For the sake of clarity, we write $\rho_n \coloneqq \rho_S(\epsilon)^{\otimes n}$, $\rho'_{n'} \coloneqq \rho_S(\epsilon')^{\otimes n'}$, $\tau_n \coloneqq \tau^{\otimes n}$ and $\tau'_{n'} \coloneqq \tau'^{\otimes n'}$.
+	For the sake of clarity, we write $\rho_n \coloneqq \rho_S(\epsilon)^{\otimes n}$, $\rho'_m \coloneqq \rho_S(\epsilon')^{\otimes m}$, $\tau_n \coloneqq \tau^{\otimes n}$ and $\tau'_m \coloneqq \tau'^{\otimes m}$.
 
@@
 \begin{equation}	
-	\Big(W_{\rho_n}(\bmx), W_{\tau_n}(\bmx')\Big) \succ \Big(W_{\rho'_{n'}}(\bmx), W_{\tau'_{n'}}(\bmx')\Big)
-\end{equation}	
-or equivalently $\Gamma_{\bma}(W_{\rho_n}(\bmx)) \succ \Gamma_{\bma'}(W_{\rho'_{n'}}(\bmx))$ for all $\bmx$.
+	(W_{\rho_n}, W_{\tau_n}) \succ (W_{\rho'_m}, W_{\tau'_m})
+\end{equation}	
+or equivalently $\Gamma_{\bma}(W_{\rho_n}) \succ \Gamma_{\bma'}(W_{\rho'_m})$.
 
@@
 \begin{equation}
-	H_{\alpha}(\Gamma_{\bma}(W_{\rho_n})) \leq H_{\alpha}(\Gamma_{\bma'}(W_{\rho'_{n'}})),
+	H_{\alpha}(\Gamma_{\bma}(W_{\rho_n})) \leq H_{\alpha}(\Gamma_{\bma'}(W_{\rho'_m})),
 \end{equation}
@@
 \begin{equation}
-	K - D_{\alpha}(W_{\rho_n} || W_{\tau_n}) \leq K - D_{\alpha}(W_{\rho'_{n'}} || W_{\tau'_{n'}}),
+	K - D_{\alpha}(W_{\rho_n} || W_{\tau_n}) \leq K - D_{\alpha}(W_{\rho'_m} || W_{\tau'_m}),
 \end{equation}.
@@
 \begin{equation}
-	K - nD_{\alpha}(W_{\rho} || W_{\tau}) \leq K - n'D_{\alpha}(W_{\rho'} || W_{\tau'}),
+	K - nD_{\alpha}(W_{\rho} || W_{\tau}) \leq K - m D_{\alpha}(W_{\rho'} || W_{\tau'}),
 \end{equation}
@@
 \begin{equation}
-	\frac{n'}{n} \leq \frac{D_{\alpha}(\rho||\tau)}{D_{\alpha}(\rho'||\tau')}.
+	\frac{m}{n} \leq \frac{D_{\alpha}(W_\rho||W_\tau)}{D_{\alpha}(W_{\rho'}||W_{\tau'})}.
 \end{equation}
@@
 We now show the following simple equivalence.
-\begin{theorem} A state $\rho$ has Wigner negativity if and only if $H_\alpha (W_\rho (\x)) < 0$ for some $\alpha >1$.
+\begin{theorem} A state $\rho$ has Wigner negativity if and only if $H_\alpha (W_\rho) < 0$ for some $\alpha >1$.
 \end{theorem}
 The proof of this is as follows.
-\begin{proof} If we have $H_\alpha (W_\rho(\x)) <0 $ for $\alpha >1$ then this implies that $\log \sum_{\x} W_\rho (\x)^\alpha > 1$, however it is known that $H_\alpha$ is always non-negative on probability distributions and therefore $W_\rho(\x)$ must be a strict quasi-distribution with negativity.
+\begin{proof} 
+If we have $H_\alpha (W_\rho) <0 $ for $\alpha >1$ then this implies that $\log \sum_{\x} W_\rho (\x)^\alpha > 1$, however it is known that $H_\alpha$ is always non-negative on probability distributions and therefore $W_\rho(\x)$ must be a strict quasi-distribution with negativity.
 
@@
 \end{equation}
-Since $\frac{1}{1-\alpha}= -\frac{b_n}{a_n} <0$ for any $n$ it follows that $H_\alpha (W_\rho (\x)) = \frac{1}{1-\alpha} \log \sum_{\x} W_\rho (\x)^\alpha  <0 $ at some point in the sequence, which completes the proof.
+Since $\frac{1}{1-\alpha}= -\frac{b_n}{a_n} <0$ for any $n$ it follows that $H_\alpha (W_\rho) = \frac{1}{1-\alpha} \log \sum_{\x} W_\rho (\x)^\alpha  <0 $ at some point in the sequence, which completes the proof.
 \end{proof}

### 2021-06-07 notes/notes.tex
Changes made, some rearrangement required

@@
 holds, given some distillation rate $n'/n$ and input error rate $\epsilon$.
+
+\begin{figure}[t]
+    \centering
+    \subfigure[][]{%
+    \label{fig:maxmix}%
+    \includegraphics[height=2cm]{figs/maxmixed.pdf}
+    }\hspace{8pt}%
+    \subfigure[][]{%
+    \label{fig:zero}%
+    \includegraphics[height=2cm]{figs/zerostate.pdf}
+    }\\
+    \subfigure[][]{%
+    \label{fig:bound}%
+    \includegraphics[height=2cm]{figs/boundstate.pdf}
+    }\hspace{8pt}%
+    \subfigure[][]{%
+    \label{fig:Strange}%
+    \includegraphics[height=2cm]{figs/Strangestate.pdf}
+    }
+    \caption{\textbf{Qutrit Wigner distributions of varying magic.} 
+    \subref{fig:maxmix} Maximally mixed state $\frac{1}{3}\id$; \subref{fig:zero} Stabilizer zero state $|0\>\<0|$; \subref{fig:bound} A non-stabiliser Wigner-positive state; \subref{fig:Strange} Magic Strange state $\ket{{\rm{S}}} = \frac{1}{\sqrt{2}}(\ket{1} - \ket{2})$, coined in~\cite{cit:veitch2}.
+    }%
+    \label{fig:wstate_examples}
+\end{figure}
 

### 2021-06-08 magic_paper.tex
More corrections

@@
     Let $\R = (\F, \O)$ be a theory of magic.
-Then a transformation $\rho \rightarrow \tau$ is possible in $\R$ if and only if the transformation $\rho \rightarrow \tau$ is possible in at least one $\sigma$--fragment of $\R$.
+Then a transformation $\rho_1 \rightarrow \rho_2$ is possible in $\R$ if and only if the transformation $\rho_1 \rightarrow \rho_2$ is possible in at least one $\sigma$--fragment of $\R$.
 \end{theorem}
@@
 \begin{equation}
-	\theta_{\rm{max}}(\rho) \coloneqq \log_2{\min{\{2\hspace{1pt}\sn{V}+1 : V \geq \rho\}}}
+	\theta_{\rm{max}}(\rho) \coloneqq \log{\min{\{2\hspace{1pt}\sn{V}+1 : V \geq \rho\}}}
 \end{equation}
@@
 This does remain well-defined on quasi-distributions, and from the majorization relation also has a clear physical meaning.
-This motivates defining the following \emph{Wigner divergence} $D_\infty(\rho, \tau) := D_\infty (W_\rho(\x) || W_\tau (\x))$ on all quantum states.
+This motivates defining the $\infty$-Renyi \emph{Wigner divergence} $D_\infty (W_\rho || W_\tau)$ on all quantum states.
 In~\cref{app:lcst_technical}, we show that this divergence has the following natural properties that are derived via relative majorization.
-\begin{theorem} Let $\tau$ be in the interior of $\F$, and define the Wigner divergence $D_\infty(\rho,\tau) := D_\infty(W_\rho(\x) || W_\tau (\x))$.
-Then $D_\infty(\rho, \tau)$ is well-defined for all $\rho$, and the following hold:
+\begin{theorem} 
+	Let $\tau$ be in the interior of $\F$, then $D_\infty(W_\rho || W_\tau)$ is well-defined for all $\rho$, and the following hold:
 \begin{enumerate}
-\item $D_\infty(\rho, \tau) \ge 0$ for all quantum states $\rho$.
-\item  $D_\infty(\rho , \tau) = 0$ if and only if $\rho =\tau$.
-\item $D_\infty(\rho^{\otimes 2n}, \tau^{\otimes 2n}) = n D_\infty(\rho^{\otimes 2} ,\tau^{\otimes 2})$ for any $n \in \mathbb{N}$.
-\item For any quantum state $\rho$, and any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$, we have $D_\infty (\rho , \tau) \ge D_\infty (\E(\rho), \E(\tau))$.
+\item $D_\infty(W_\rho || W_\tau) \geq 0$ for all quantum states $\rho$.
+\item  $D_\infty(W_\rho || W_\tau) = 0$ if and only if $\rho =\tau$.
+\item $D_\infty(W_{\rho^{\otimes 2n}} || W_{\tau^{\otimes 2n}}) = n D_\infty(W_{\rho^{\otimes 2}} || W_{\tau^{\otimes 2}})$ for any $n \in \mathbb{N}$.
+\item For any quantum state $\rho$, and any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$, we have $D_\infty (W_\rho || W_\tau) \geq D_\infty (W_{\E(\rho)} || W_{\E(\tau)})$.
 \end{enumerate}
 \end{theorem}
-See Appendix~\ref{app:lcst_technical} for the proof of this.
 
@@
 Therefore, we might speculate if the presence of magic in Clifford circuits admits a rigorous interpretation in terms of a phase transition signalled by a first-order divergence in the Wigner free energy.
-However since variation in $\alpha$ is no longer smooth ($\alpha$ is restricted to a dense set of rational values) technical obstacles exist and we do not pursue this speculative line here, but just note that other works exist in which computational transitions are considered in relation to phase transitions \ddd{[Need to cite]}.
+However since variation in $\alpha$ is no longer smooth ($\alpha$ is restricted to a dense set of rational values) technical obstacles exist and we do not pursue this speculative line here, but just note that other works exist in which computational transitions are considered in relation to phase transitions \ddd{[Need to cite]}\nick{any specific in mind?}.
 
 However, every entropy is best understood as a relative entropy and so we now state the extension to Renyi divergences.
-The $\alpha$--Renyi divergence $D_\alpha(\p)$ is defined as
-\begin{equation}
-	D_\alpha(\p|\r) := \frac{1}{\alpha-1} \log \sum_i p_i^\alpha r_i^{1-\alpha},
-\end{equation}
-where $\p$ is a quasi-distribution, $\r$ a probability distribution with positive components and $\alpha$ takes the same values as for $H_\alpha$.
+We define the $\alpha$--Renyi Wigner divergence $D_\alpha$ as
+\begin{equation}
+	D_\alpha(\w || \r) := \frac{1}{\alpha-1} \log \sum_i w_i^\alpha r_i^{1-\alpha},
+\end{equation}
+where $\w$ can be a quasi-distribution, $\r$ a probability distribution with positive components and $\alpha$ can take the same values as for $H_\alpha$.
 In~\cref{app:lcst_technical}, we also show that the divergence satisfies the following natural properties for all $\alpha$ for which it is well-defined.
@@
 \begin{theorem}\label{thm:Da_props} 
-	Let $\tau$ be a state in the interior of $\F$ and $\alpha = 2a / (2b-1)$ for non-negative integers $a,b$ with $a \geq b$.
-Then, the $\alpha$-Renyi divergence $D_\alpha(W_\rho || W_\tau)$ is well-defined for all states $\rho$, and the following hold:
+	Let $\tau$ be in the interior of $\F$. 
+	If $\alpha = 2a / (2b-1)$ for non-negative integers $a,b$ with $a \geq b$, then the $\alpha$-Renyi divergence $D_\alpha(W_\rho || W_\tau)$ is well-defined for all states $\rho$, and the following hold:
 \begin{enumerate}
@@
     \includegraphics[scale=0.4]{figs/RaDiff_vs_a_eps.pdf}}
-    \caption{$R_\alpha$}
+    \caption{$R_\alpha$ and $R_\alpha - R_{\infty}$ for the Strange state distillation in the unital fragment
+    \nick{Can compare thauma and mana for other magic states now more easily}}
     \label{fig:rate_a_contour}
@@
 \begin{equation}
-	\hspace{-14pt}D_\infty(\rho,\tau) := D_\infty(W_\rho(\x) || W_\tau (\x)) = \log  \max_{\x} \frac{W_\rho(\x)}{W_\tau(\x)},
+	D_\infty(W_\rho || W_\tau) := \log  \max_{\x} \frac{W_\rho(\x)}{W_\tau(\x)},
 \end{equation}
@@
 
-\begin{theorem} Let $\tau$ be in the interior of $\F$, and define $D_\infty(\rho,\tau) := D_\infty(W_\rho(\x) || W_\tau (\x))$.
-Then $D_\infty(\rho, \tau)$ is well-defined for all $\rho$, and the following hold:
+\begin{theorem}
+	Let $\tau$ be in the interior of $\F$, then $D_\infty(W_\rho || W_\tau)$ is well-defined for all $\rho$, and the following hold:
 \begin{enumerate}
-\item $D_\infty(\rho, \tau) \ge 0$ for all quantum states $\rho$.
-\item  $D_\infty(\rho , \tau) = 0$ if and only if $\rho =\tau$.
-\item $D_\infty(\rho^{\otimes 2n}, \tau^{\otimes 2n}) = n D_\infty(\rho^{\otimes 2} ,\tau^{\otimes 2})$ for any $n \in \mathbb{N}$.
-\item For any quantum state $\rho$, and any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$, we have $D_\infty (\rho , \tau) \ge D_\infty (\E(\rho), \E(\tau))$.
+\item $D_\infty(W_\rho || W_\tau) \geq 0$ for all quantum states $\rho$.
+\item  $D_\infty(W_\rho || W_\tau) = 0$ if and only if $\rho =\tau$.
+\item $D_\infty(W_{\rho^{\otimes 2n}} || W_{\tau^{\otimes 2n}}) = n D_\infty(W_{\rho^{\otimes 2}} || W_{\tau^{\otimes 2}})$ for any $n \in \mathbb{N}$.
+\item For any quantum state $\rho$, and any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$, we have $D_\infty (W_\rho || W_\tau) \geq D_\infty (W_{\E(\rho)} || W_{\E(\tau)})$.
 \end{enumerate}
@@
 	Since $\tau$ is in the interior of $\F$, its Wigner function obeys $W_\tau(\x) >0$ for all points $\x$ in the phase space. 
-In general, $W_\rho(\x)$ is a quasi-distribution, however since $\sum_{\x} W_\rho (\x) = 1$ this implies it must have at least one positive component, so $\max_{\x} \frac{W_\rho(\x)}{W_\tau(\x)}>0$.
-Therefore $D_\infty (\rho,\tau)$ is always well-defined.
+In general, $W_\rho(\x)$ is a quasi-distribution, but the given form of $\alpha$ ensures that $W_{\rho}(\bmx)^\alpha \geq 0$. 
+Therefore $D_\infty (W_\rho || W_\tau)$ is always well-defined.
 
@@
 \begin{equation}
-D_\infty(W_\rho(\x) || W_\tau (\x)) =\log  \max_{\x} \frac{W_\rho(\x)}{W_\tau(\x)},
-\end{equation}
-and therefore $2^{D_\infty(\rho,\tau)}$ equals the slope of the Lorenz curve $L_{\rho|\tau}(x)$ at $x=0$.
-Since $L_{\rho|\tau}(x)$ is a concave function passing through $(0,0)$ and $(1,1)$ this implies that $L_{\rho |\tau}(x) \ge x$ for all $x \in [0,1]$, and in particular its slope at $x=0$ is always greater than or equal to $1$, which implies $D_\infty (\rho,\tau) \ge 0$ for all $\rho$.
+	D_\infty(W_\rho || W_\tau) =\log  \max_{\x} \frac{W_\rho}{W_\tau},
+\end{equation}
+so $2^{D_\infty(W_\rho || W_\tau)}$ equals the slope of the Lorenz curve $L_{\rho|\tau}(x)$ at $x=0$.
+Since $L_{\rho|\tau}(x)$ is a concave function passing through $(0,0)$ and $(1,1)$ this implies that $L_{\rho |\tau}(x) \ge x$ for all $x \in [0,1]$, and in particular its slope at $x=0$ is always greater than or equal to $1$, which implies $D_\infty(W_\rho || W_\tau) \geq 0$ for all $\rho$.
 
 2.
-$D_\infty (\rho,\tau) = 0$ implies that $\max_{\x} \frac{W_\rho(\x)}{W_\tau(\x)}=1$ and the initial slope of $L_{\rho|\tau}(x)$ is $1$.
+$D_\infty(W_\rho || W_\tau) = 0$ implies that $\max_{\x} \frac{W_\rho(\x)}{W_\tau(\x)}=1$ and the initial slope of $L_{\rho|\tau}(x)$ is $1$.
 From the concavity of the function this implies that the slope of $L_{\rho|\tau}(x)$ must equal $1$ throughout the interval $[0,1]$ and this, together with the definition of the Lorenz curve, implies that $W_\rho(\x)/W_\tau(\x) = 1$ for all $\x$.
@@
 \end{equation}
-and therefore taking logarithms we have that $D_\infty (\rho^{\otimes 2n}, \tau^{\otimes 2n}) = n D_\infty(\rho^{\otimes 2} ,\tau^{\otimes 2})$ as required.
+and therefore taking logarithms we have that $D_\infty(W_{\rho^{\otimes 2n}} || W_{\tau^{\otimes 2n}}) = n D_\infty(W_{\rho^{\otimes 2}} || W_{\tau^{\otimes 2}})$ as required.
 
@@
 The free operation $\E$ in the Wigner representation corresponds to a stochastic map, which sends $W_\tau(\x)$ to $W_{\E(\tau)}(\x)$, which is another strictly positive probability distribution on the phase space, due to $\E(\tau)$ being in the interior of $\F$.
-Moreover, $(W_\rho(\x), W_\tau(\x) ) \succ (W_{\E(\rho)}(\x) , W_{\E(\tau)}(\x))$.
+Moreover, $(W_\rho, W_\tau ) \succ (W_{\E(\rho)} , W_{\E(\tau)})$.
 As shown in the main text this condition holds if and only if $L_{\rho|\tau}(x) \ge L_{\E(\rho)|\E(\tau)}(x)$ for all $x$.
@@
 \begin{equation}
-	H_0(W_\rho) = 2\log_2 d = H_\alpha \left( W_{\id/d} \right),
+	H_0(W_\rho) = 2\log d = H_\alpha \left( W_{\id/d} \right),
 \end{equation}
@@
 \begin{align}
-	&H_{\alpha}\left(W_{\rho_{\rm{S}}(\epsilon)}\right) = \frac{1}{1-\alpha}\log_2 \left[ 8\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^\alpha + \left(-\frac{1}{3} + \frac{4}{9}\epsilon \right)^\alpha \right] \nonumber\\
-	&= \frac{\alpha}{\alpha-1}\log_2 18+ \frac{1}{1-\alpha}\log_2 \left[ 8(3-\epsilon)^\alpha + (6-8\epsilon)^\alpha \right]
+	&H_{\alpha}\left(W_{\rho_{\rm{S}}(\epsilon)}\right) = \frac{1}{1-\alpha}\log \left[ 8\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^\alpha + \left(-\frac{1}{3} + \frac{4}{9}\epsilon \right)^\alpha \right] \nonumber\\
+	&= \frac{\alpha}{\alpha-1}\log 18+ \frac{1}{1-\alpha}\log \left[ 8(3-\epsilon)^\alpha + (6-8\epsilon)^\alpha \right]
 \end{align}
@@
 
-\nick{This step is the reason why $\alpha =$ odd$/$odd or $\alpha < 1$ do not work.
-
-If $\alpha =$ odd$/$odd, then $f(w)$ is not monotonous because the sign of $f'(w)$ would depend on the sign of $w$.
-
-If $\alpha =$ even$/$odd and $\alpha < 1$, then $H_\alpha$ is Schur-convex.
+\nick{
+If $\alpha =$ odd$/$odd, then $H_\alpha$ is not well-defined for all quasi-probabilities.
+
+If $\alpha =$ even$/$odd and $\alpha < 1$, then $f(w) := \frac{-w^{\alpha-1}}{\alpha-1}$ diverges at $0$ with $\lim_{w\rightarrow 0^-} = -\infty$ and $\lim_{w\rightarrow 0^+} = +\infty$.\\
+Example: If $\alpha = 2/3$, then $f(-2/3) = -3.43$, $f(-1/3) = -4.33$ and $f(+1/3) = +4.33$, so $f(w)$ is nether non-increasing nor non-decreasing.
+In~\cref{fig:Htest}, it looks as if it's Schur-convex though..
 }
@@
 \begin{equation}
-	D_\alpha(W_\rho || W_\tau) := \frac{1}{\alpha - 1} \log_2 \sum_{\bmx} W_{\rho}(\bmx)^\alpha W_{\tau}(\bmx)^{1-\alpha},
+	D_\alpha(W_\rho || W_\tau) := \frac{1}{\alpha - 1} \log \sum_{\bmx} W_{\rho}(\bmx)^\alpha W_{\tau}(\bmx)^{1-\alpha},
 \end{equation}
@@
 	\begin{align}
-		H_\alpha(\Gamma_{\bma}(\w)) &= \frac{1}{1-\alpha} \log_2 \sum_{i=1}^N a_i \left( \frac{w_i}{a_i} \right)^\alpha \nonumber\\
-		&= \frac{1}{1-\alpha} \log_2 \sum_{i=1}^N w_i^{\alpha} a_i^{1-\alpha} \nonumber\\
-		&= \frac{1}{1-\alpha} \log_2 K^{1-\alpha} \sum_{i=1}^N w_i^{\alpha} r_i^{1-\alpha} \nonumber\\
-		&= K + \frac{1}{1-\alpha} \log_2 \sum_{i=1}^N w_i^{\alpha} r_i^{1-\alpha} \nonumber\\
+		H_\alpha(\Gamma_{\bma}(\w)) &= \frac{1}{1-\alpha} \log \sum_{i=1}^N a_i \left( \frac{w_i}{a_i} \right)^\alpha \nonumber\\
+		&= \frac{1}{1-\alpha} \log \sum_{i=1}^N w_i^{\alpha} a_i^{1-\alpha} \nonumber\\
+		&= \frac{1}{1-\alpha} \log K^{1-\alpha} \sum_{i=1}^N w_i^{\alpha} r_i^{1-\alpha} \nonumber\\
+		&= K + \frac{1}{1-\alpha} \log \sum_{i=1}^N w_i^{\alpha} r_i^{1-\alpha} \nonumber\\
 		&= K - D_\alpha(\w ||\r).
@@
 	D_\alpha(W_{\rho} || W_{\tau}) \geq D_\alpha(W_{\rho'} || W_{\rho'}) &= \nonumber\\
-	\frac{1}{\alpha-1} \log_2 \sum_{\bmx} W_{\rho'}(\bmx) &= 0.
+	\frac{1}{\alpha-1} \log \sum_{\bmx} W_{\rho'}(\bmx) &= 0.
 \end{align}
@@
 	&D_\alpha(W_{\rho^{\otimes n}} || W_{\tau^{\otimes n}}) = \nonumber\\
-	&\frac{1}{\alpha - 1} \log_2 \sum_{\bmx} W_{\rho^{\otimes n}}(\bmx)^\alpha W_{\tau^{\otimes n}}(\bmx)^{1-\alpha} = \nonumber\\
-	&\frac{1}{\alpha - 1} \log_2 \sum_{\bmx} \prod_{i=1}^n W_{\rho}(\bmx_i)^\alpha W_{\tau}(\bmx_i)^{1-\alpha} = \nonumber\\
-	&\frac{1}{\alpha - 1} \log_2 \prod_{i=1}^n \sum_{\bmx_i} W_{\rho}(\bmx_i)^\alpha W_{\tau}(\bmx_i)^{1-\alpha} = \nonumber\\
-	&\sum_{i=1}^n \frac{1}{\alpha - 1} \log_2 \sum_{\bmx'} W_{\rho}(\bmx')^\alpha W_{\tau}(\bmx')^{1-\alpha} = \nonumber\\
+	&\frac{1}{\alpha - 1} \log \sum_{\bmx} W_{\rho^{\otimes n}}(\bmx)^\alpha W_{\tau^{\otimes n}}(\bmx)^{1-\alpha} = \nonumber\\
+	&\frac{1}{\alpha - 1} \log \sum_{\bmx} \prod_{i=1}^n W_{\rho}(\bmx_i)^\alpha W_{\tau}(\bmx_i)^{1-\alpha} = \nonumber\\
+	&\frac{1}{\alpha - 1} \log \prod_{i=1}^n \sum_{\bmx_i} W_{\rho}(\bmx_i)^\alpha W_{\tau}(\bmx_i)^{1-\alpha} = \nonumber\\
+	&\sum_{i=1}^n \frac{1}{\alpha - 1} \log \sum_{\bmx'} W_{\rho}(\bmx')^\alpha W_{\tau}(\bmx')^{1-\alpha} = \nonumber\\
 	&= n D_{\alpha}(W_\rho || W_\tau).

### 2021-06-08 magic_paper.tex
Expansion of phase transition speculation. Other polishing.

--- 2021-06-07 magic_paper.tex
@@
 
-This figure includes numerical estimates of the optimal majorization bounds $R_{\rm{opt}}$ obtained by considering the full Lorenz curve, which show that the first elbow constraint can be further improved.
+This figure includes numerical estimates of the optimal majorization bounds $R_{\rm{num}}$ obtained by considering the full Lorenz curve, which show that the first elbow constraint can be further improved.
 \begin{figure}[t]
@@
 In~\cref{app:lcst_technical}, we show that this divergence has the following natural properties that are derived via relative majorization.
-\begin{theorem} Let $\tau$ be in the interior of $\F$, and define the Wigner divergence $D_\infty(\rho,\tau) := D_\infty(W_\rho(\x) || W_\tau (\x))$.
-Then $D_\infty(\rho, \tau)$ is well-defined for all $\rho$, and the following hold:
+\begin{theorem} Let $\tau$ be in the interior of $\F$. Then $D_\infty(W_\rho || W_\tau)$ is well-defined for all $\rho$, and the following hold:
 \begin{enumerate}
-\item $D_\infty(\rho, \tau) \ge 0$ for all quantum states $\rho$.
-\item  $D_\infty(\rho , \tau) = 0$ if and only if $\rho =\tau$.
-\item $D_\infty(\rho^{\otimes 2n}, \tau^{\otimes 2n}) = n D_\infty(\rho^{\otimes 2} ,\tau^{\otimes 2})$ for any $n \in \mathbb{N}$.
-\item For any quantum state $\rho$, and any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$, we have $D_\infty (\rho , \tau) \ge D_\infty (\E(\rho), \E(\tau))$.
+\item $D_\infty(W_\rho || W_\tau) \ge 0$ for all quantum states $\rho$.
+\item  $D_\infty(W_\rho || W_\tau) = 0$ if and only if $\rho =\tau$.
+\item $D_\infty(W_{\rho^{\otimes 2n}}|| W_{\tau^{\otimes 2n}}) = n D_\infty(W_{\rho^{\otimes 2}} ||W_{\tau^{\otimes 2}})$ for any $n \in \mathbb{N}$.
+\item For any quantum state $\rho$, and any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$, we have $D_\infty (W_\rho || W_\tau) \ge D_\infty (W_{\E(\rho)}|| W_{\E(\tau)})$.
 \end{enumerate}
@@
 
-The $\alpha \rightarrow 1$ limit of the Renyi entropy is not well-defined, however the Renyi entropy description shows that this diverges to $-\infty$ due to the Lorenz curve $L_\rho(x)$ no longer being bounded by $1$.
-Alternatively, we can write the divergence of the entropy as $-\epsilon^{-1} \log \sum_{\x} |W_\rho (\x)|^{1+\epsilon}$ with $\epsilon \rightarrow 0^+$, which leads to a second new description of mana: \emph{it is the rate of divergence of the Renyi-entropy} as we approach the limiting Shannon entropy $H(\w)$.
-We also note the recent observation~\cite{baez2011renyi} that in standard statistical mechanics that $H_\alpha(\p)$ can be related to the ``$q$--derivative'' of free energy.
-Therefore, we might speculate if the presence of magic in Clifford circuits admits a rigorous interpretation in terms of a phase transition signalled by a first-order divergence in the Wigner free energy.
+The $\alpha \rightarrow 1$ limit of the Renyi entropy is not well-defined, however the Renyi entropy description shows that this diverges in a well-defined way.
+We can write the divergence of the entropy as
+\begin{equation}
+H_{1-\epsilon}(W_\rho) = -\epsilon^{-1} \log \sum_{\x} |W_\rho (\x)|^{1+\epsilon}
+\end{equation} 
+with $\epsilon \rightarrow 0^+$ through a sequence of rational values $(a-b)/b$.
+However we recall that mana is defined as $\M(\rho) = \log \sum_{\x} |W_\rho(\x)|$, and so we obtain a second new description of mana: \emph{it is the coefficient of divergence of the Wigner Renyi-entropy} as we approach the limiting Shannon entropy $H(\w)$.
+
+We also note that the Renyi entropy can be viewed as a $q$--deformation of the Shannon entropy~\cite{baez2011renyi}, and $H_\alpha(\p)$ can be related to the $q$--derivative of free energy.
+More precisely, it can be shown that
+\begin{equation}
+H_{\frac{T}{x}} = \frac{1}{x-T} ( F(x) - F(T)),
+\end{equation}
+where $F(x)$ is an effect free energy at temperature $x$.
+If we attempt to push this to the present setting, the presence of Wigner negativity would correspond to a divergence in the first derivative of this effective free energy as $x \rightarrow T$.
+One might speculate if the presence of magic in Clifford circuits admits a sensible interpretation in terms of a zeroth-order phase transition.
 However since variation in $\alpha$ is no longer smooth ($\alpha$ is restricted to a dense set of rational values) technical obstacles exist and we do not pursue this speculative line here, but just note that other works exist in which computational transitions are considered in relation to phase transitions \ddd{[Need to cite]}.
@@
 
-We can now apply this to obtain new magic bounds.
+We can now apply this to obtain magic distillation bounds that describe Wigner negativity directly as a form of non-classical free energy.
 \begin{theorem}

### 2021-06-08 magic_paper.tex

--- 2021-06-08 magic_paper.tex
@@
 This does remain well-defined on quasi-distributions, and from the majorization relation also has a clear physical meaning.
-This motivates defining the $\infty$-Renyi \emph{Wigner divergence} $D_\infty (W_\rho || W_\tau)$ on all quantum states.
+
+This motivates defining the following \emph{Wigner divergence} $D_\infty(\rho, \tau) := D_\infty (W_\rho(\x) || W_\tau (\x))$ on all quantum states.
 In~\cref{app:lcst_technical}, we show that this divergence has the following natural properties that are derived via relative majorization.
-\begin{theorem} 
-	Let $\tau$ be in the interior of $\F$, then $D_\infty(W_\rho || W_\tau)$ is well-defined for all $\rho$, and the following hold:
+\begin{theorem} Let $\tau$ be in the interior of $\F$. Then $D_\infty(W_\rho || W_\tau)$ is well-defined for all $\rho$, and the following hold:
 \begin{enumerate}
-\item $D_\infty(W_\rho || W_\tau) \geq 0$ for all quantum states $\rho$.
+\item $D_\infty(W_\rho || W_\tau) \ge 0$ for all quantum states $\rho$.
 \item  $D_\infty(W_\rho || W_\tau) = 0$ if and only if $\rho =\tau$.
-\item $D_\infty(W_{\rho^{\otimes 2n}} || W_{\tau^{\otimes 2n}}) = n D_\infty(W_{\rho^{\otimes 2}} || W_{\tau^{\otimes 2}})$ for any $n \in \mathbb{N}$.
-\item For any quantum state $\rho$, and any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$, we have $D_\infty (W_\rho || W_\tau) \geq D_\infty (W_{\E(\rho)} || W_{\E(\tau)})$.
+\item $D_\infty(W_{\rho^{\otimes 2n}}|| W_{\tau^{\otimes 2n}}) = n D_\infty(W_{\rho^{\otimes 2}} ||W_{\tau^{\otimes 2}})$ for any $n \in \mathbb{N}$.
+\item For any quantum state $\rho$, and any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$, we have $D_\infty (W_\rho || W_\tau) \ge D_\infty (W_{\E(\rho)}|| W_{\E(\tau)})$.
 \end{enumerate}
@@
 
-The $\alpha \rightarrow 1$ limit of the Renyi entropy is not well-defined, however the Renyi entropy description shows that this diverges to $-\infty$ due to the Lorenz curve $L_\rho(x)$ no longer being bounded by $1$.
-Alternatively, we can write the divergence of the entropy as $-\epsilon^{-1} \log \sum_{\x} |W_\rho (\x)|^{1+\epsilon}$ with $\epsilon \rightarrow 0^+$, which leads to a second new description of mana: \emph{it is the rate of divergence of the Renyi-entropy} as we approach the limiting Shannon entropy $H(\w)$.
-We also note the recent observation~\cite{baez2011renyi} that in standard statistical mechanics that $H_\alpha(\p)$ can be related to the ``$q$--derivative'' of free energy.
-Therefore, we might speculate if the presence of magic in Clifford circuits admits a rigorous interpretation in terms of a phase transition signalled by a first-order divergence in the Wigner free energy.
+The $\alpha \rightarrow 1$ limit of the Renyi entropy is not well-defined, however the Renyi entropy description shows that this diverges in a well-defined way.
+We can write the divergence of the entropy as
+\begin{equation}
+H_{1-\epsilon}(W_\rho) = -\epsilon^{-1} \log \sum_{\x} |W_\rho (\x)|^{1+\epsilon}
+\end{equation} 
+with $\epsilon \rightarrow 0^+$ through a sequence of rational values $(a-b)/b$.
+However we recall that mana is defined as $\M(\rho) = \log \sum_{\x} |W_\rho(\x)|$, and so we obtain a second new description of mana: \emph{it is the coefficient of divergence of the Wigner Renyi-entropy} as we approach the limiting Shannon entropy $H(\w)$.
+
+We also note that the Renyi entropy can be viewed as a $q$--deformation of the Shannon entropy~\cite{baez2011renyi}, and $H_\alpha(\p)$ can be related to the $q$--derivative of free energy.
+More precisely, it can be shown that
+\begin{equation}
+H_{\frac{T}{x}} = \frac{1}{x-T} ( F(x) - F(T)),
+\end{equation}
+where $F(x)$ is an effect free energy at temperature $x$.
+If we attempt to push this to the present setting, the presence of Wigner negativity would correspond to a divergence in the first derivative of this effective free energy as $x \rightarrow T$.
+One might speculate if the presence of magic in Clifford circuits admits a sensible interpretation in terms of a zeroth-order phase transition.
 However since variation in $\alpha$ is no longer smooth ($\alpha$ is restricted to a dense set of rational values) technical obstacles exist and we do not pursue this speculative line here, but just note that other works exist in which computational transitions are considered in relation to phase transitions \ddd{[Need to cite]}\nick{any specific in mind?}.
@@
 \end{document}
-
-\end{document}

### 2021-06-08 magic_paper.tex
simplified proof of entropic bound

--- 2021-06-08 magic_paper.tex
@@
 	\begin{equation}
-		R \leq \frac{D_{\alpha}(W_\rho||W_\tau)}{D_{\alpha}(W_{\rho'}||W_{\tau'})} = \frac{F_\alpha(W_\rho) - F_\alpha(W_\tau)}{F'_\alpha(W_{\rho'}) - F'_\alpha(W_{\tau'})},
+		R \leq \frac{D_{\alpha}(W_\rho||W_\tau)}{D_{\alpha}(W_{\rho'}||W_{\tau'})} = \frac{F_\alpha(W_\rho) - F_\alpha(W_\tau)}{F_\alpha(W_{\rho'}) - F_\alpha(W_{\tau'})},
 	\end{equation}
@@
 The proofs for these can be found in~\cite{cit:marshall,ruch_mixing_1978,Renes_2016,Buscemi_2017} and references therein.
+
+We prove the following result connecting majorization to relative majorization.
+\begin{lemma}
+	Let $\w\in \mathbb{R}^N, \w'\in \mathbb{R}^{N'}$ be quasi-distributions and $\r\in \mathbb{R}^N, \r'\in \mathbb{R}^{N'}$ probability distributions with positive rational entries given by $r_i = a_i/K$ and $r_i' = a_i'/K$ for positive integers $a_i, a_i'$ and $K = \sum_{i=1}^N a_i = \sum_{i=1}^{N'} a_i'$.
+Then,
+\begin{equation}
+(\w, \r) \succ (\w', \r') \mbox{ if and only if } \Gamma_{\bma} (\w) \succ \Gamma_{\bma'} (\w'),
+\end{equation}
+where the embedding map $\Gamma_{\bma} :\mathbb{R}^N \rightarrow \mathbb{R}^K$ is given by
+\begin{equation}
+	\Gamma_{\bma}(\x) := \bigoplus_{i=1}^N x_i \eta_{a_i},
+\end{equation}
+with $\eta_{a_i} = (1/a_i, 1/a_i, \dots, 1/a_i)$ the uniform distribution on $a_i$ elements.
+\end{lemma}
+\begin{proof}
+	We first note that the map $\Gamma_{\bma}$ is stochastic and has a well-defined left-inverse $\Gamma^{-1}_{\bma'}: \mathbb{R}^K \rightarrow \mathbb{R}^N$ given by
+\begin{equation}
+	\Gamma^{-1}_{\bma}(\w) = \left( \sum_{i=1}^{a_1} w_i,  \sum_{i = a_1 +1}^{a_1 + a_2} \hspace{-5pt} w_i, \dots , \hspace{-15pt} \sum_{i=a_1 + \dots + a_{N-1}+1}^{K} \hspace{-10pt} w_i \right),
+\end{equation}
+that obeys $(\Gamma^{-1}_{\bma} \circ \Gamma_{\bma}) (\x) = \x$ for all $\x \in \mathbb{R}^N$.
+
+The claim is equivalent to the statement that there exists a \emph{bistochastic map} $B$ sending $\Gamma_{\bma}(\w)$ to $\Gamma_{\bma'}(\w')$ if and only if there exists a stochastic map $A$ sending $\w$ to $\w'$ and $\r$ to $\r'$.
+
+Suppose there is a stochastic map $A$ such that $A\w=\w'$ and $A\r = \r'$. 
+We define $B:\mathbb{R}^K \mapsto \mathbb{R}^K$ by $B := \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1}$ so that it is stochastic as a composition of stochastic maps and it preserves the uniform distribution in $\mathbb{R}^A$, since
+\begin{align}
+	&B(1/K, 1/K, \dots, 1/K) = \big( \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1} \big) \big( \Gamma_{\bma'}(\r) \big) = \nonumber\\
+	&\Gamma_{\bma'} (\r') = (1/K, 1/K, \dots, 1/K),
+\end{align}
+therefore $B$ is bistochastic.
+Finally, $B$ maps the embedded distributions as follows,
+\begin{equation}
+	B \Gamma_{\bma}(\w) = \big( \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1} \big) \big( \Gamma_{\bma}(\w) \big) = \Gamma_{\bma'} (\w').
+\end{equation}
+
+Conversely, suppose a bistochastic map $B$ exists sending $\Gamma_{\bma}(\w)$ to $\Gamma_{\bma'}(\w')$.
+Again, define $A: \mathbb{R}^N \mapsto \mathbb{R}^{N'}$ by $A := \Gamma_{\bma'}^{-1} \circ B \circ \Gamma_{\bma}$ so that it is stochastic as a composition of stochastic maps and $A \w = \big( \Gamma_{\bma'}^{-1} \circ B \circ \Gamma_{\bma} \big) \w = \w'$, as well as $A \r = \r'$.
+\end{proof}
+We note that the vectors $\r, \r'$ with rational components form a dense subset of the positive probability distributions, so we can appeal to the fact that experiments have a finite resolution to ignore technical details regarding the completion to arbitrary real components.
 
@@
 
-We note that we may relate our analysis to the classical single-shot entropies that remain well-defined even in the case of quasi-distributions.
+In this section, we develop the tools that allow the use of entropic functions on quasi-probabilities to retrieve magic distillation bounds.
 
@@
 	&H_{\alpha}\left(W_{\rho_{\rm{S}}(\epsilon)}\right) = \frac{1}{1-\alpha}\log \left[ 8\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^\alpha + \left(-\frac{1}{3} + \frac{4}{9}\epsilon \right)^\alpha \right] \nonumber\\
-	&= \frac{\alpha}{\alpha-1}\log 18+ \frac{1}{1-\alpha}\log \left[ 8(3-\epsilon)^\alpha + (6-8\epsilon)^\alpha \right]
+	&\ddd{= \frac{\alpha}{\alpha-1}\log 18+ \frac{1}{1-\alpha}\log \left[ 8(3-\epsilon)^\alpha + (6-8\epsilon)^\alpha \right]}
 \end{align}
@@
 
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.35]{figs/test/H_test.pdf}
-    \caption{Here, the exponent is $\alpha =$ even$/$odd for $0.10 \leq \alpha \leq 0.90$. $H_\alpha$ is decreasing in $\epsilon$ (not Schur-conocave for $\alpha < 1$) and increasing in $\alpha$.
-    }
-    \label{fig:Htest}
-\end{figure}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.35]{figs/test/D_test.pdf}
-    \caption{Here, the exponent is $\alpha =$ even$/$odd for $0.10 \leq \alpha \leq 0.90$.
-$D_\alpha$ is increasing in $\epsilon$ (not Schur-convex for $\alpha < 1$) and decreasing in $\alpha$ (clear due to~\cref{thm:H2D}).
-    }
-    \label{fig:Dtest}
-\end{figure}
-
 We now make use of known results from majorization theory to establish the Schur-concavity of $H_\alpha$ on Wigner quasi-distributions where $\alpha$ is such that $H_\alpha$ is well-defined. 
@@
 Example: If $\alpha = 2/3$, then $f(-2/3) = -3.43$, $f(-1/3) = -4.33$ and $f(+1/3) = +4.33$, so $f(w)$ is nether non-increasing nor non-decreasing.
-In~\cref{fig:Htest}, it looks as if it's Schur-convex though..
 }
@@
 \end{proof}
-The set $F := \{2a/(2b-1): a,b \in \mathbb{N} \text{ and } a \geq b\}$ is dense in the rationals $\mathbb{Q}_{>1}$, which in turn are dense in the reals $\mathbb{R}_{>1}$, as any rational $c/d$ with $c>d$ can be approximated by a sequence $f_n := c2^n / (d2^n-1)$ with every element $f_n$ in the set $F$.
-
-Now we define the classical $\alpha$-Renyi divergence in terms of the Wigner quasi-distribution of any magic state $\rho$ and the Wigner probability distribution of any equilibrium state $\tau$ as
-\begin{equation}
-	D_\alpha(W_\rho || W_\tau) := \frac{1}{\alpha - 1} \log \sum_{\bmx} W_{\rho}(\bmx)^\alpha W_{\tau}(\bmx)^{1-\alpha},
-\end{equation}
-where $\alpha$ can take values of the form $2a / (2b+1)$, for non-negative integers $a,b$ to ensure that the argument of the logarithm is positive.
+The set $F := \{2a/(2b-1): a,b \in \mathbb{N} \text{ and } a \geq b\}$ is dense in the rationals $\mathbb{Q}_{>1}$, and hence the reals $\mathbb{R}_{>1}$, as any rational $c/d$ with $c>d$ can be approximated by  $c2^n / (d2^n-1) \in F$ for suficiently large $n$.
 
@@
 \subsection{Renyi divergences on quasi-distributions}
-We prove the following result connecting majorization to relative majorization.
-\begin{lemma}
-Let $\w\in \mathbb{R}^N, \w'\in \mathbb{R}^{N'}$ be quasi-distributions and $\r\in \mathbb{R}^N, \r'\in \mathbb{R}^{N'}$ probability distributions with positive rational entries given by $r_i = a_i/K$ and $r_i' = a_i'/K$ for positive integers $a_i, a_i'$ and $K = \sum_{i=1}^N a_i = \sum_{i=1}^{N'} a_i'$.
-Then,
-\begin{equation}
-(\w, \r) \succ (\w', \r') \mbox{ if and only if } \Gamma_{\bma} (\w) \succ \Gamma_{\bma'} (\w'),
-\end{equation}
-where the embedding map $\Gamma_{\bma} :\mathbb{R}^N \rightarrow \mathbb{R}^K$ is given by
-\begin{equation}
-	\Gamma_{\bma}(\x) := \bigoplus_{i=1}^N x_i \eta_{a_i},
-\end{equation}
-with $\eta_{a_i} = (1/a_i, 1/a_i, \dots, 1/a_i)$ the uniform distribution on $a_i$ elements.
-\end{lemma}
-\begin{proof}
-	We first note that the map $\Gamma_{\bma}$ is stochastic and has a well-defined left-inverse $\Gamma^{-1}_{\bma'}: \mathbb{R}^K \rightarrow \mathbb{R}^N$ given by
-\begin{equation}
-	\Gamma^{-1}_{\bma}(\w) = \left( \sum_{i=1}^{a_1} w_i,  \sum_{i = a_1 +1}^{a_1 + a_2} \hspace{-5pt} w_i, \dots , \hspace{-15pt} \sum_{i=a_1 + \dots + a_{N-1}+1}^{K} \hspace{-10pt} w_i \right),
-\end{equation}
-that obeys $(\Gamma^{-1}_{\bma} \circ \Gamma_{\bma}) (\x) = \x$ for all $\x \in \mathbb{R}^N$.
-
-The claim is equivalent to the statement that there exists a \emph{bistochastic map} $B$ sending $\Gamma_{\bma}(\w)$ to $\Gamma_{\bma'}(\w')$ if and only if there exists a stochastic map $A$ sending $\w$ to $\w'$ and $\r$ to $\r'$.
-
-Suppose there is a stochastic map $A$ such that $A\w=\w'$ and $A\r = \r'$. 
-We define $B:\mathbb{R}^K \mapsto \mathbb{R}^K$ by $B := \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1}$ so that it is stochastic as a composition of stochastic maps and it preserves the uniform distribution in $\mathbb{R}^A$, since
-\begin{align}
-	&B(1/K, 1/K, \dots, 1/K) = \big( \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1} \big) \big( \Gamma_{\bma'}(\r) \big) = \nonumber\\
-	&\Gamma_{\bma'} (\r') = (1/K, 1/K, \dots, 1/K),
-\end{align}
-therefore $B$ is bistochastic.
-Finally, $B$ maps the embedded distributions as follows,
-\begin{equation}
-	B \Gamma_{\bma}(\w) = \big( \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1} \big) \big( \Gamma_{\bma}(\w) \big) = \Gamma_{\bma'} (\w').
-\end{equation}
-
-Conversely, suppose a bistochastic map $B$ exists sending $\Gamma_{\bma}(\w)$ to $\Gamma_{\bma'}(\w')$.
-Again, define $A: \mathbb{R}^N \mapsto \mathbb{R}^{N'}$ by $A := \Gamma_{\bma'}^{-1} \circ B \circ \Gamma_{\bma}$ so that it is stochastic as a composition of stochastic maps and $A \w = \big( \Gamma_{\bma'}^{-1} \circ B \circ \Gamma_{\bma} \big) \w = \w'$, as well as $A \r = \r'$.
-\end{proof}
-We note that the vectors $\r, \r'$ with rational components form a dense subset of the positive probability distributions, so we can appeal to the fact that experiments have a finite resolution to ignore technical details regarding the completion to arbitrary real components.
+Now we define the classical $\alpha$-Renyi divergence in terms of the Wigner quasi-distribution of any magic state $\rho$ and the Wigner probability distribution of any equilibrium state $\tau$ as
+\begin{equation}
+	D_\alpha(W_\rho || W_\tau) := \frac{1}{\alpha - 1} \log \sum_{\bmx} W_{\rho}(\bmx)^\alpha W_{\tau}(\bmx)^{1-\alpha},
+\end{equation}
+where $\alpha$ can take values of the form $2a/(2b+1)$, for non-negative integers $a,b$ to ensure once again that the argument of the logarithm is positive.
 
@@
 
+We are now in a position to derive general magic state distillation bounds.
+
 \begin{theorem}
@@
 \begin{proof}
-	For the sake of clarity, we write $\rho_n \coloneqq \rho_S(\epsilon)^{\otimes n}$, $\rho'_m \coloneqq \rho_S(\epsilon')^{\otimes m}$, $\tau_n \coloneqq \tau^{\otimes n}$ and $\tau'_m \coloneqq \tau'^{\otimes m}$.
-
-	We have that 
-\begin{equation}	
-	(W_{\rho_n}, W_{\tau_n}) \succ (W_{\rho'_m}, W_{\tau'_m})
-\end{equation}	
-or equivalently $\Gamma_{\bma}(W_{\rho_n}) \succ \Gamma_{\bma'}(W_{\rho'_m})$.
-
-For the given form of $\alpha$, $H_{\alpha}$ is Schur-concave due to~\cref{thm:HSchur}, so
-\begin{equation}
-	H_{\alpha}(\Gamma_{\bma}(W_{\rho_n})) \leq H_{\alpha}(\Gamma_{\bma'}(W_{\rho'_m})),
-\end{equation}
-and we can use~\cref{thm:H2D} to rewrite the inequality as
-\begin{equation}
-	K - D_{\alpha}(W_{\rho_n} || W_{\tau_n}) \leq K - D_{\alpha}(W_{\rho'_m} || W_{\tau'_m}),
-\end{equation}.
-Due to~\cref{thm:Da_props}, we can rewrite the inequality as
-\begin{equation}
-	K - nD_{\alpha}(W_{\rho} || W_{\tau}) \leq K - m D_{\alpha}(W_{\rho'} || W_{\tau'}),
-\end{equation}
-and rearrange it to reach
+	The bound is a direct consequence of the properties of the $\alpha$--Renyi diveregence, proven in~\cref{thm:Da_props}.
+
+Due to the action of the magic protocol channel, we get
+\begin{equation}	
+	D_\alpha(W_{\rho^{\otimes n}} || W_{\tau^{\otimes n}}) \geq D_\alpha (W_{\rho'^{\otimes m}} || W_{\tau'^{\otimes m}}).\vspace{10pt}
+\end{equation}
+
+We can use the additive property to rewrite this as
+\begin{equation}
+	n D_\alpha(W_\rho || W_\tau) \geq m D_\alpha(W_{\rho'} || W_{\tau'}).
+\end{equation}
+
+Since $\rho' \neq \tau'$, we have $D_\alpha(W_{\rho'} || W_{\tau'}) > 0$, which directly leads to the bound
 \begin{equation}
@@
 \end{theorem}
-The proof of this is as follows.
 \begin{proof} 

### 2021-06-08 magic_paper.tex
added refs and unital bound

@@
 % Labels and Refs (consistency, cref vs ref, thm vs lem vs prop, ??)
-% Figs check(fig.0, move to app, consistency, cbars, iffalse)
-
-% Notation consistency (noise vs error, \ln{} -> \ln, italics, Aberg -> {\AA}berg)
+% Figs check(fig.0, move to app, consistency, cbars, iffalse, axes)
+
+% Notation consistency (noise vs error, \ln{} -> \ln, \ln vs \log vs \log_2, italics & \emph, Aberg -> {\AA}berg, quasi-dist vs quasi-prob dist)
 % UK vs US english
@@
 In~\cref{app:lcst_technical}, we show that this divergence has the following natural properties that are derived via relative majorization.
-\begin{theorem} Let $\tau$ be in the interior of $\F$. Then $D_\infty(W_\rho || W_\tau)$ is well-defined for all $\rho$, and the following hold:
+\begin{theorem}\label{thm:Dinfty} 
+	Let $\tau$ be in the interior of $\F$. Then $D_\infty(W_\rho || W_\tau)$ is well-defined for all $\rho$, and the following hold:
 \begin{enumerate}
@@
 In the Appendices we show the following.
-\begin{theorem} If $\alpha = \frac{2a}{2b-1}$ for integers $a,b \in \mathbb{N}$ and $a\ge b$ then $H_\alpha(\w)$ is well-defined on the set of quasi-distributions $\w$, and moreover if $\w \succ \w'$ for two quasi-distributions $\w, \w'$ then $H_\alpha (\w) \le H_\alpha(\w')$.
+\begin{theorem}\label{thm:HSchur} 
+	If $\alpha = \frac{2a}{2b-1}$ for non-negative integers $a,b$ with $a \geq b$, then $H_\alpha(\w)$ is well-defined on the set of quasi-distributions $\w$, and moreover if $\w \succ \w'$ for two quasi-distributions $\w, \w'$ then $H_\alpha (\w) \leq H_\alpha(\w')$.
 \end{theorem}
@@
 Moreover we can prove the following result, which establishes the equivalence between Wigner negativity and the existence of negative Renyi entropy.
-\begin{theorem} A quantum state $\rho$ has Wigner negativity if and only if $H_\alpha(W_\rho) <0$ for some $\alpha =  \frac{2a}{2b-1}$, with integers $a \ge b$.
+\begin{theorem}\label{thm:Magic}
+	A quantum state $\rho$ has Wigner negativity if and only if $H_\alpha(W_\rho) <0$ for some $\alpha =  \frac{2a}{2b-1}$, with integers $a \ge b$.
 \end{theorem}
@@
 \begin{equation}
-H_{\frac{T}{x}} = \frac{1}{x-T} ( F(x) - F(T)),
-\end{equation}
-where $F(x)$ is an effect free energy at temperature $x$.
+	H_{\frac{T}{x}} = \frac{1}{x-T} (F(x) - F(T)),
+\end{equation}
+\nick{Do you mean $H_{\frac{T}{x}}(\w)$? What is $F(x)$ for a number $x$ ?}
+where $F(x)$ is an effective free energy at temperature $x$.
 If we attempt to push this to the present setting, the presence of Wigner negativity would correspond to a divergence in the first derivative of this effective free energy as $x \rightarrow T$.
 One might speculate if the presence of magic in Clifford circuits admits a sensible interpretation in terms of a zeroth-order phase transition.
-However since variation in $\alpha$ is no longer smooth ($\alpha$ is restricted to a dense set of rational values) technical obstacles exist and we do not pursue this speculative line here, but just note that other works exist in which computational transitions are considered in relation to phase transitions \ddd{[Need to cite]}\nick{any specific in mind?}.
-
-However, every entropy is best understood as a relative entropy and so we now state the extension to Renyi divergences.
+However since variation in $\alpha$ is no longer smooth ($\alpha$ is restricted to a dense set of rational values) technical obstacles exist and we do not pursue this speculative line here, but just note that other works exist in which computational transitions are considered in relation to phase transitions~\cite{arvidsson_2020, halpern_2018}.
+
+Every entropy is best understood as a relative entropy and so we now state the extension to Renyi divergences.
 We define the $\alpha$--Renyi Wigner divergence $D_\alpha$ as
@@
 We can now apply this to obtain magic distillation bounds that describe Wigner negativity directly as a form of non-classical free energy.
-\begin{theorem}
+\begin{theorem}\label{thm:entropic_bounds} 
 	Consider a general magic state distillation process that converts a magic state $\rho^{\otimes n} \longrightarrow \rho'^{\otimes m}$ as well as an equilibrium state $\tau^{\otimes n} \longrightarrow \tau'^{\otimes m}$
@@
 \end{theorem}
+For unital processes, i.e. operations $\E$ such that $\E(\id/d) = \id/d$, the bound reduces to
+\begin{equation}
+	R \leq \frac{2\log d - H_{\alpha}(W_\rho)}{2\log d - H_{\alpha}(W_{\rho'})}.
+\end{equation}
 
@@
 
+\begingroup
+\def\thetheorem{\ref{thm:Dinfty}}
 \begin{theorem}
@@
 \end{theorem}
+\addtocounter{theorem}{-1}
+\endgroup
 \begin{proof}
@@
 
-\begin{theorem}\label{thm:HSchur}
-	Let $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$.
-	Then, $H_\alpha$ is Schur-concave, i.e. for quasi-distributions $\w, \w' \in \mathbb{R}^N$, we have $H_\alpha(\w) \leq H_\alpha(\w')$, whenever $\w \succ \w'$.
+\begingroup
+\def\thetheorem{\ref{thm:HSchur}}
+\begin{theorem}
+	If $\alpha = \frac{2a}{2b-1}$ for non-negative integers $a,b$ with $a \geq b$, then $H_\alpha(\w)$ is well-defined on the set of quasi-distributions $\w$, and moreover if $\w \succ \w'$ for two quasi-distributions $\w, \w'$ then $H_\alpha (\w) \leq H_\alpha(\w')$.
 \end{theorem}
+\addtocounter{theorem}{-1}
+\endgroup
 \begin{proof}
@@
 
-We can check additivity of $H_{\alpha}$ also holds on quasi-distributions. 
+We can check that additivity of $H_{\alpha}$ also holds on quasi-distributions. 
 \begin{lemma}\label{H_add}
@@
 
+We now show the following simple equivalence.
+\begingroup
+\def\thetheorem{\ref{thm:HSchur}}
+\begin{theorem}
+	A quantum state $\rho$ has Wigner negativity if and only if $H_\alpha(W_\rho) < 0$ for some $\alpha =  \frac{2a}{2b-1}$, with integers $a \geq b$.
+\end{theorem}
+\addtocounter{theorem}{-1}
+\endgroup
+\begin{proof} 
+If we have $H_\alpha (W_\rho) <0 $ for $\alpha >1$ then this implies that $\log \sum_{\x} W_\rho (\x)^\alpha > 1$, however it is known that $H_\alpha$ is always non-negative on probability distributions and therefore $W_\rho(\x)$ must be a strict quasi-distribution with negativity.
+
+Conversely, suppose $\rho$ has negativity in its Wigner representation.
+This implies that $\sum_{\x} |W_\rho (\x)| >1$.
+We now consider $\sum_{\x} W_\rho (\x)^{a/b}$ for $a/b >1$ and $a$ even and $b$ odd.
+We have that
+\begin{align}
+\sum_{\x} W_\rho (\x)^{a/b} &= \sum_{\x} |W_\rho (\x)|^{a/b} \nonumber \\
+&= \sum_{\x} |W_\rho (\x)|^{1+ \epsilon},
+\end{align}
+where $\epsilon = a/b - 1 >0$.
+By choosing $a$ and $b$ appropriately we can make $\epsilon$ arbitrarily close to $0$.
+More precisely, there exists a sequence $\epsilon_n=a_n/b_n$ with valid integer pairs $a_n, b_n$ such that
+\begin{equation}
+\sum_{\x} |W_\rho (\x)|^{1+ \epsilon_n} \rightarrow \sum_{\x} |W_\rho (\x)| >1.
+\end{equation}
+Since $\frac{1}{1-\alpha}= -\frac{b_n}{a_n} <0$ for any $n$ it follows that $H_\alpha (W_\rho) = \frac{1}{1-\alpha} \log \sum_{\x} W_\rho (\x)^\alpha  <0 $ at some point in the sequence, which completes the proof.
+\end{proof}
+Therefore Wigner negativity coincides with negativity of a Renyi entropy.
+
 \subsection{Renyi divergences on quasi-distributions}
@@
 
-\begin{theorem}\label{thm:Da_props} 
+\begingroup
+\def\thetheorem{\ref{thm:Da_props}}
+\begin{theorem}
 	Let $\tau$ be a state in the interior of $\F$ and $\alpha = 2a / (2b-1)$ for non-negative integers $a,b$ with $a \geq b$.
@@
 
+\begingroup
+\def\thetheorem{\ref{thm:entropic_bounds}}
 \begin{theorem}
@@
 
-We now show the following simple equivalence.
-\begin{theorem} A state $\rho$ has Wigner negativity if and only if $H_\alpha (W_\rho) < 0$ for some $\alpha >1$.
-\end{theorem}
-\begin{proof} 
-If we have $H_\alpha (W_\rho) <0 $ for $\alpha >1$ then this implies that $\log \sum_{\x} W_\rho (\x)^\alpha > 1$, however it is known that $H_\alpha$ is always non-negative on probability distributions and therefore $W_\rho(\x)$ must be a strict quasi-distribution with negativity.
-
-Conversely, suppose $\rho$ has negativity in its Wigner representation.
-This implies that $\sum_{\x} |W_\rho (\x)| >1$.
-We now consider $\sum_{\x} W_\rho (\x)^{a/b}$ for $a/b >1$ and $a$ even and $b$ odd.
-We have that
-\begin{align}
-\sum_{\x} W_\rho (\x)^{a/b} &= \sum_{\x} |W_\rho (\x)|^{a/b} \nonumber \\
-&= \sum_{\x} |W_\rho (\x)|^{1+ \epsilon},
-\end{align}
-where $\epsilon = a/b - 1 >0$.
-By choosing $a$ and $b$ appropriately we can make $\epsilon$ arbitrarily close to $0$.
-More precisely, there exists a sequence $\epsilon_n=a_n/b_n$ with valid integer pairs $a_n, b_n$ such that
-\begin{equation}
-\sum_{\x} |W_\rho (\x)|^{1+ \epsilon_n} \rightarrow \sum_{\x} |W_\rho (\x)| >1.
-\end{equation}
-Since $\frac{1}{1-\alpha}= -\frac{b_n}{a_n} <0$ for any $n$ it follows that $H_\alpha (W_\rho) = \frac{1}{1-\alpha} \log \sum_{\x} W_\rho (\x)^\alpha  <0 $ at some point in the sequence, which completes the proof.
-\end{proof}
-
-Therefore Wigner negativity coincides with negativity of a Renyi entropy.
-
 \end{document}

### 2021-06-08 magic_paper.tex
Perhaps the final title given. New abstract...still needs polish. Expansion on entropic bounds.

@@
 \begin{abstract}
-\ddd{[To be sharpened]} Magic states are key ingredients in schemes to realise universal fault-tolerant quantum computation.
+Magic states are key ingredients in schemes to realise universal fault-tolerant quantum computation.
 Theories of magic states attempt to quantify this computational element via monotones and determine how these states may be efficiently transformed into useful forms.
-Here we introduce the concept of `fragments', which generalise the concept of magic monotones and has a natural thermodynamic structure based on majorisation.
-From this perspective magic can be viewed as a form of free energy within each fragment and is constrained by relative majorisation relations but now on quasi-probability distributions.
-Notably this approach allows us to incorporate actual physical constraints, for example noise models with particular bias or temperature-dependent features, and study how these constrain general magic distillation protocols.
-In this context we present general temperature-dependent bounds on distillation rates that any theory of magic must respect.
-Significantly, this analysis also presents a thermodynamic context which cannot be analysed via traditional methods based on thermodynamic entropies, due to the presence of negativity, and raises novel questions in the context of statistical mechanics.
+Here we develop a statistical mechanical framework in which Wigner negative magic states provide non-classical free energy that is processed under Clifford circuits.
+While traditional free energy is not defined in the presence of negativity, we show that majorization allows us to both quantify disorder in the Wigner representation and derive magic distillation bounds.
+These upper bounds are shown to be tighter than other bounds, such as those from mana and thauma, and moreover incorporate hardware physics, such as temperature dependence.
+We show that a sub-set of single-shot Renyi entropies remain well-defined on quasi-distributions, are fully meaningful in terms of data processing and can acquire negative values.
+We also show that the mana of a magic state is exactly the coefficient of divergence of Renyi entropies as one approaches the Shannon entropy for Wigner distributions, and discuss how distillation lower bounds could be obtained in this setting.
+This use of majorization for quasi-distributions could find application in other studies of non-classicality, and raises novel questions in the context of classical statistical mechanics.
 \end{abstract}
@@
 
-\title{Statistical mechanics of Wigner negativity and magic states in quantum computation}
+\title{General constraints on magic state protocols from the statistical mechanics of \\Wigner negativity}
 
@@
 \begin{theorem}\label{thm:entropic_bounds} 
-	Consider a general magic state distillation process that converts a magic state $\rho^{\otimes n} \longrightarrow \rho'^{\otimes m}$ as well as an equilibrium state $\tau^{\otimes n} \longrightarrow \tau'^{\otimes m}$
-
-	We have the following family of upper bounds on the distillation rate $R := n'/n$,
-	\begin{equation}
-		R \leq \frac{D_{\alpha}(W_\rho||W_\tau)}{D_{\alpha}(W_{\rho'}||W_{\tau'})} = \frac{F_\alpha(W_\rho) - F_\alpha(W_\tau)}{F_\alpha(W_{\rho'}) - F_\alpha(W_{\tau'})},
-	\end{equation}
-	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ and $\beta F_\alpha(W_\rho) := D_\alpha (W_\rho || W_\tau) - \log \Z$ is the $\alpha$--free energy. 
+	Consider a magic state distillation protocol that converts a magic state $\rho^{\otimes n} \longrightarrow \rho'^{\otimes m}$, which when applied to a reference stabilizer state $\tau^{\otimes n}$ results in $\tau^{\otimes n} \longrightarrow \tau'^{\otimes m}$.
+
+	We have the following family of upper bounds on the magic distillation rate $R := m/n$,
+	\begin{equation}
+		R \leq \frac{F_\alpha(W_\rho) - F_\alpha(W_\tau)}{F_\alpha(W_{\rho'}) - F_\alpha(W_{\tau'})},
+	\end{equation}
+	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ and $\beta F_\alpha(W_\rho) := D_\alpha (W_\rho || W_\tau) - \log \Z$ is the $\alpha$--free energy of the Wigner distribution.
 \end{theorem}
-For unital processes, i.e. operations $\E$ such that $\E(\id/d) = \id/d$, the bound reduces to
+For magic protocols that generate unital maps the above bound reduces to the simpler form
 \begin{equation}
@@
 \end{equation}
-
+In particular for the case of noisy Strange states on qutrits and $\epsilon'=0$, this bound becomes
+\begin{equation}
+	R \leq \frac{2(1-\alpha)\log 3 - \log \left [8(\frac{1}{6} - \frac{\epsilon}{18})^\alpha + (-\frac{1}{3} + \frac{4\epsilon}{9})^\alpha\right ] }{2(1-\alpha)\log 3 + \alpha \log 6 - \log (8 + 2^\alpha )}.
+\end{equation}
+For any $\epsilon$ the upper bound can be numerically minimized over $\alpha$.
 \begin{figure}[t!]

### 2021-06-09 magic_paper.tex
Refs distributed. Polishing...and contraversial change made...

@@
 
-\nick{Bunch of refs:}~\cite{White_2021, Rethinasamy_2020, Blackwell_1953, Sarkar_2020, Gour_2020}
+\ddd{[Title of Gour2020 paper is incorrect in the bibliography]}
 
@@
 These frameworks for magic view magic states as resource states with respect to a natural class of quantum operations that are considered cheap, or free, such as stabilizer operations~\cite{Gour_2019, cit:ahmadi, cit:seddon, Wang_2019}.
+Beyond quantum computing, recent work has also looked at how magic can be used to analyse many-body physics~\cite{Sarkar_2020} and conformal field theories~\cite{White_2021}.
 
@@
 Crucially, we focus on magic states with negativity in their Wigner representation, which is known to be a necessary condition for universality in the state-injection model~\cite{cit:veitch, cit:mari, cit:gottesman, cit:knill, Campbell_2011}.
-Interestingly, taking a statistical mechanical perspective in this context raises a problem, namely it is impossible to define entropies for quasi-distributions.
+However, taking a statistical mechanical perspective in this context raises a problem: the standard Boltzmann entropy is not defined for quasi-distributions.
 We circumvent this obstacle by making use of a more fundamental tool in thermodynamics and information theory -- majorization theory~\cite{cit:marshall, Veinott_1971, Ruch_1976}.
@@
         \includegraphics[scale=0.3]{figs/protocol_diagram.pdf}
-    \caption{\textbf{Magic distillation protocols \& stabilizer reference states.} 
+    \caption{\textbf{Probing magic protocols with reference states.} 
 	A magic protocol (top figure) converts $n$ copies of some noisy magic state $\rho$ with noise parameter $\epsilon$ to $m$ copies of some less noisy state $\rho'$ with $\epsilon' < \epsilon$.
@@
 
-A number of magic theories exist, with the central approach of viewing magic states as computational resource states with respect to a natural class of quantum operations that are considered free~\cite{Gour_2019}.
+A number of magic theories exist, where magic states are computational resource states with respect to a natural class of quantum operations that are considered free~\cite{Gour_2019}.
 One very natural class of free operations are those obtained from Clifford operations, measurements and the ability to discard quantum systems.
-However, there are also other noteworthy candidates~\cite{cit:ahmadi, cit:seddon, Wang_2019}.
+However, there are also other candidates~\cite{cit:ahmadi, cit:seddon, Wang_2019}.
 
@@
 
-\subsection{Stochastic structure of magic protocols}
+\subsection{Stochastic representation of magic protocols}
 \label{sec:struc}
@@
 
-Majorisation is a collection of powerful tools that has recently found many applications in quantum information theory~\cite{Nielsen_1999, cit:cwiklinski, cit:lostaglio2, cit:gour, cit:gour2, Horodecki_2003, Vallejos_2021}.
+Majorisation~\cite{cit:marshall, Blackwell_1953} is a collection of powerful tools that has recently found many applications in quantum information theory~\cite{Nielsen_1999, cit:cwiklinski, cit:lostaglio2, cit:gour, cit:gour2, Horodecki_2003, Vallejos_2021}.
 It describes the disorder of distributions that undergo stochastic transformations.
@@
 
-In fact, we can further generalise to \emph{relative majorization}~\cite{Ruch_1976, ruch_mixing_1978, Renes_2016, Buscemi_2017}, defined as an ordering between pairs of vectors so that 
+In fact, we can further generalise to \emph{relative majorization}~\cite{Blackwell_1953, Ruch_1976, ruch_mixing_1978, Renes_2016, Buscemi_2017, Rethinasamy_2020}, defined as an ordering between pairs of vectors so that
 \begin{equation}
@@
 
-It turns out that relative majorization is equally applicable to \emph{quasi-probability} distributions, and therefore can be applied to the Wigner representation of magic across fragments.
+It turns out that relative majorization is equally applicable to \emph{quasi-probability} distributions, and therefore can be applied to the Wigner representation of magic across different $\R_\sigma$.
 We go into more detail on this in the next section.
@@
 Our analysis applies majorization to magic states at the level of the associated Wigner distributions.
-However, these are in general quasi-probability distributions, so it is important to check how majorization is computed for these cases and what differences quasi-distributions bring over genuine probability distributions.
+However, these are in general quasi-probability distributions, so it is important to check how majorization is computed for these cases and what differences quasi-distributions bring over genuine probability distributions~\cite{arvidsson_2020, halpern_2018}.
 
@@
 In contrast, Lorenz curves for magic states break through the value of $L(x)=1$ due to the presence of negativity in the associated quasi-probability distributions.
-The above family of curves correspond to multiple copies of noisy Strange states $\rho\coloneqq\rho_{\rm{S}}(\epsilon)^{\otimes n}$ (\cref{eq:noisysn}) for $n=2,4,6$ within a particular stabilizer fragment ($\sigma = \id/3$).
+The above family of curves correspond to multiple copies of noisy Strange states $\rho\coloneqq\rho_{\rm{S}}(\epsilon)^{\otimes n}$ (\cref{eq:noisysn}) for $n=2,4,6$ within $\R_{\id/3}$.
 Solid lines represent pure Strange states, while dashed lines represent $\epsilon$-noisy Strange states with depolarising error $\epsilon = 0.1$.
@@
 \newpage
-\section{Magic distillation bounds from majorization}
+\section{Magic distillation bounds with fixed-points}
 \label{sec:frag}
@@
 \begin{definition}\label{def:sigmafrag}
-   Given a theory of magic $\R = (\F, \O)$, the \emph{$\sigma$--fragment of $\R$} is the sub-theory $\R_\sigma = (\F, \O_\sigma)$, in which the free operations are 
+   Given a theory of magic $\R = (\F, \O)$, we define the sub-theory $\R_\sigma = (\F, \O_\sigma)$, in which the free operations are 
    \begin{equation}
@@
 This notion provides a simple way to break up any theory into smaller, more manageable parts.
-Moreover, the union over all fragments returns the parent theory, so we are not discarding any information by breaking up the theory in this way.
+Moreover, the union over all sub-theories returns the parent theory, so we are not discarding any information by breaking up the theory in this way.
 We make this statement precise as follows.
@@
     Let $\R = (\F, \O)$ be a theory of magic.
-Then a transformation $\rho_1 \rightarrow \rho_2$ is possible in $\R$ if and only if the transformation $\rho_1 \rightarrow \rho_2$ is possible in at least one $\sigma$--fragment of $\R$.
+Then a transformation $\rho_1 \rightarrow \rho_2$ is possible in $\R$ if and only if the transformation $\rho_1 \rightarrow \rho_2$ is possible in at least one sub-theory $\R_\sigma$.
 \end{theorem}
@@
 \begin{proof}
-   Suppose the interconversion is possible in a $\sigma$--fragment via some $\E \in \O_\sigma$.
+   Suppose the interconversion is possible in a $\R_\sigma$ via some $\E \in \O_\sigma$.
 But since $\O_\sigma \subseteq \O$ it is also possible in $\R$.
@@
 By the Brouwer Fixed-Point theorem~\cite{cit:brouwer} this mapping must therefore have a fixed point $\sigma \in \F$.
-Therefore, $\E \in \O_\sigma$ and the interconversion is possible in this fragment.
+Therefore, $\E \in \O_\sigma$ and the interconversion is possible in $\R_\sigma$.
 \end{proof}
@@
 A complete set of measures $\{\M_i\}_i$ is such that $\rho \rightarrow \sigma$ if and only if $\M_i(\rho) \ge \M_i(\sigma)$ for all $i$.
-The above set of sub-theories can therefore be viewed as a complete set of ``co-measures'' for the theory, where the parent resource theory's complex pre-order of states is mapped to a simpler pre-order for a particular fragment.
-In the next section we show that this pre-order for a given fragment can always be approximated by a majorization pre-order, and from this we can compute magic distillation bounds.
+The above set of sub-theories can therefore be viewed as a complete set of ``co-measures'' for the theory, where the parent resource theory's complex pre-order of states is mapped to a simpler pre-order for a particular $\R_\sigma$.
+In the next section we show that this pre-order for a given $\R_\sigma$ can always be approximated by a majorization pre-order, and from this we can compute magic distillation bounds.
 
@@
         \includegraphics[scale=0.3]{figs/operations.pdf}
-    \caption{\textbf{Decomposition of a magic theory $\R$ into $\sigma$--fragments.} 
+    \caption{\textbf{Decomposition of a magic theory $\R$ into $\R_\sigma$ bits.} 
 	Examples of magic theories ($\so$: Stabilizer operations, $\Omax$: Completely positive-Wigner-preserving operations, $\rcu$: Random Clifford Unitaries -- subclass of $\so$) are labelled, with other established magic theories also contained within the yellow regions.
@@
 
-\subsection{Majorisation of negative Wigner distributions within $\sigma$--fragments}
+\subsection{Majorisation of negative Wigner distributions with fixed-point structure}
 \label{sec:major_frag}
-
-We consider some $\sigma \in \F$, and its corresponding fragment $\R_\sigma$.
+We can now look at how the simple approach of focussing on fixed-point structures can be used to analyse magic protocols.
+We consider some $\sigma \in \F$, and its corresponding $\R_\sigma$.
 We are interested in the ability to transform many copies of some noisy magic state $\rho$ towards a more pure form of magic.
@@
 
-\subsection{Basic monotones for magic states in a particular fragment}
+\subsection{Basic monotones for magic distillation for a particular $\R_\sigma$}
 \label{sec:monotones_frag}
 
-In this section, we state some generic aspects of Lorenz curves for magic states.
+We state some generic aspects of Lorenz curves for magic states.
 These allow us to interpret previous magic monotones in a new light.
@@
 
-\begin{lemma} Relative majorization in any fragment implies the monotonicity of sum-negativity. 
+\begin{lemma} Relative majorization in any $\R_\sigma$ implies the monotonicity of sum-negativity. 
 \end{lemma}
@@
 \begin{theorem}\label{lem:lcmax}
-	Given a magic state $\rho$, the maximum $L_\star$ of its Lorenz curve $\lc{\rho}{\sigma}(x)$ is independent of the $\sigma$--fragment and equal to $1+\sn{\rho}$.
-Moreover, the majorization constraint is stronger than mana in every fragment.
+	Given a magic state $\rho$, the maximum $L_\star$ of its Lorenz curve $\lc{\rho}{\sigma}(x)$ is independent of the $\R_\sigma$ and equal to $1+\sn{\rho}$.
+Moreover, the majorization constraint is stronger than mana in every $\R_\sigma$.
 \end{theorem}
@@
 Using the Lorenz curve perspective, it is also simple to construct new monotones.
-For example, within a given fragment, the area above the horizontal line $y = 1$ is another magic monotone.
+For example, within a given $\R_\sigma$, the area above the horizontal line $y = 1$ is another magic monotone.
 \begin{lemma}
@@
 \end{proof}
-Note though, in contrast to mana, the area monotone is \emph{specific to the fragment}, and its value will vary as we change $\sigma$.
-Therefore its monotonicity is conditioned on the physics of the fragment and so provides a means to analyse magic distillation only under free operations that leave $\sigma$ invariant.
+Note though, in contrast to mana, the area monotone is \emph{specific to the $\R_\sigma$}, and its value will vary as we change $\sigma$.
+Therefore its monotonicity depends on the physics of the fixed point and so provides a means to analyse magic distillation only under free operations that leave $\sigma$ invariant.
 One can also define an area monotone in the more general setting of relative majorization, where one drops the fixed point emphasis as in Section \ref{sec:stab}, but we do not explore this here.
@@
 
-We now construct magic state distillation bounds within the unital fragment ($\sigma = \I/d$).
-This describes distillation protocols that generate \emph{unital operations}, meaning that $\E(\I/d) = \I/d$, and includes for example all protocols built from Weyl-covariant channels~\cite{cit:gross3}.
-
-Our approach applies to any dimension, but for simplicity we consider qutrit magic states ($d=3$), for which a canonical magic state exists with a particularly simple Wigner distribution.
+We now construct magic state distillation bounds for protocols that generate \emph{unital} channels, meaning that $\E(\I/d) = \I/d$, and includes for example all protocols built from Weyl-covariant channels~\cite{cit:gross3}.
+
+Our approach works for any dimension, but for simplicity we consider qutrit magic states ($d=3$), for which a canonical magic state exists with a particularly simple Wigner distribution.
 This is the Strange state $|S\>$, which is given by
@@
     \includegraphics[scale=0.35]{figs/distill_bounds.pdf}
-    \caption{\textbf{Distillation bounds in the unital fragment.} Distillation bounds obtained by the first elbow majorisation constraint $R$, mana $\M$ and max--thauma $\theta_{\rm{max}}$ are plotted for $\epsilon' = 0$, up to error $\epsilon = 3/7$.
-    Majorisation provides stricter rates than the global mana and max--thauma bounds.
-    Numerical bounds $R_{\rm{num}}$ obtained by full Lorenz curve comparison for some Strange state purification processes with even number of copies $m,n \leq 30$ highlight that the first elbow constraint can be improved.
+    \caption{\textbf{Distillation bounds for unital protocols.} Distillation bounds obtained by the first elbow majorisation constraint $R_\infty$, mana and max--thauma $\theta_{\rm{max}}$ are plotted for $\epsilon' = 0$, up to error $\epsilon = 3/7$.
+Also shown is the bound $R_{10}$ which comes from single-shot entropies, which we discuss in Section~\ref{section:entropies}.
+Numerical bounds $R_{\rm{num}}$ are obtained by using the full set of Lorenz curve constraints.
+Each majorisation constraint provides stricter bounds than the mana and max--thauma bounds for noisy Strange states.
     }
@@
 
-In the next section, we loosen the restriction of working in a fixed fragment, and instead use the full structure of relative majorization to obtain bounds that incorporate energetic aspects of a magic state protocol.
+In the next section, we loosen the restriction of working in a fixed $\R_\sigma$, and instead use full relative majorization to obtain bounds that incorporate energetic aspects of a magic state protocol.
 
@@
 \newpage
-\section{Well-defined \& monotonic  entropies for quasi-distributions}
+\section{Well-defined \& monotonic  entropies for quasi-distributions}\label{section:entropies}
 We have considered Wigner distributions of magic states within a statistical mechanical setting in which it is was argued that magic should be viewed as a non-classical form of free energy.
@@
 One might speculate if the presence of magic in Clifford circuits admits a sensible interpretation in terms of a zeroth-order phase transition.
-However since variation in $\alpha$ is no longer smooth ($\alpha$ is restricted to a dense set of rational values) technical obstacles exist and we do not pursue this speculative line here, but just note that other works exist in which computational transitions are considered in relation to phase transitions~\cite{arvidsson_2020, halpern_2018}.
-
-Every entropy is best understood as a relative entropy and so we now state the extension to Renyi divergences.
+However since variation in $\alpha$ is no longer smooth ($\alpha$ is restricted to a dense set of rational values) technical obstacles exist and we do not pursue this speculative line here, but just note that other works exist in which computational transitions are considered in relation to phase transitions.
+
+Every entropy is best understood as a relative entropy~\cite{Gour_2020} and so we now state the extension to Renyi divergences.
 We define the $\alpha$--Renyi Wigner divergence $D_\alpha$ as
@@
     \includegraphics[scale=0.4]{figs/RaDiff_vs_a_eps.pdf}}
-    \caption{$R_\alpha$ and $R_\alpha - R_{\infty}$ for the Strange state distillation in the unital fragment
+    \caption{$R_\alpha$ and $R_\alpha - R_{\infty}$ for the Strange state distillation for unital protocols
     \nick{Can compare thauma and mana for other magic states now more easily}}
@@
 \section{Acknowledgements}
-We thank Earl Campbell for insightful discussions and comments.
+We thank Earl Campbell for helpful discussions and comments.
 NK is supported by the EPSRC Centre for Doctoral Training in Controlled Quantum Dynamics.
@@
 
-We first prove the following result on the relation between majorization in a particular fragment and mana, which was stated in~\cref{sec:monotones_frag}.
+We first prove the following result on the relation between majorization in a particular sub-theory $\R_\sigma$ and mana, which was stated in~\cref{sec:monotones_frag}.
 \begingroup
@@
 \begin{theorem}
-	Given a magic state $\rho$, the maximum value $L_\star$ attained by the Lorenz curve $\lc{\rho}{\sigma}(x)$ is independent of the $\sigma$--fragment and equal to $1+\sn{\rho}$.
-Moreover, the relative majorization constraint is stronger than mana in every fragment.
+	Given a magic state $\rho$, the maximum value $L_\star$ attained by the Lorenz curve $\lc{\rho}{\sigma}(x)$ is independent of the $\R_\sigma$ and equal to $1+\sn{\rho}$.
+Moreover, the relative majorization constraint is stronger than mana in every $\R_sigma$.
 \end{theorem}
@@
 	\end{equation}
-	and is achieved at $x_{i_\star} \coloneqq \sum_{i=1}^{i_\star} w(\sigma)_i$. The location of this maximum varies from fragment to fragment, but its value is independent of $\sigma$,
+	and is achieved at $x_{i_\star} \coloneqq \sum_{i=1}^{i_\star} w(\sigma)_i$. The location of this maximum varies with $\R_\sigma$, but its value is independent of $\sigma$,
 	\begin{align}
@@
 Since the magic monotone mana is a monotonic function of sum-negativity, $\rm{mana}(\rho) \coloneqq \ln \hspace{1pt}(2\hspace{1pt}\sn{\rho}+1)$, we see that mana corresponds precisely to the peak of the Lorenz curve $L_{\rho|\sigma}(x)$.
-Therefore, mana is one of $d^{2n}$ constraints, so majorization is strictly a stronger constraint in any fragment.
+Therefore, mana is one of $d^{2n}$ constraints, so majorization is strictly a stronger constraint in any $\R_\sigma$.
 \end{proof}
@@
 \end{align}
-In~\cref{app:lcsu_coord}, we will use $\Phi_+$ and $\Phi_-$ to express the elbow coordinates of Lorenz curves in the unital fragment.
+In~\cref{app:lcsu_coord}, we will use $\Phi_+$ and $\Phi_-$ to express the elbow coordinates of Lorenz curves for unital protocols.
 
@@
 
-\subsection{Lorenz curve coordinates in the unital fragment}\label{app:lcsu_coord}
+\subsection{Lorenz curve coordinates for unital protocols}\label{app:lcsu_coord}
 
 The Wigner distribution of the $n$--copy qutrit maximally mixed state $\left(\id/3\right)^{\otimes n}$ is the uniform probability distribution over the phase space, consisting of $9^n$ components equal to $9^{-n}$.
-The Wigner distribution of the 1-copy $\epsilon$--noisy Strange state $\rho_{\rm{S}}(\epsilon)$ in the unital fragment consists of some permutation of a single negative component
+The Wigner distribution of the 1-copy $\epsilon$--noisy Strange state $\rho_{\rm{S}}(\epsilon)$ for unital protocols consists of some permutation of a single negative component
 \begin{equation}
@@
 
-In the unital fragment we need the condition $0 \leq \epsilon < 3/4$, so that the state contains some Wigner negativity ($-v < 0$).
+For unital protocols we need the condition $0 \leq \epsilon < 3/4$, so that the state contains some Wigner negativity ($-v < 0$).
 It is also clear that $v \geq u$ in the interval $0 \leq \epsilon \leq 3/7$, while $u > v$ in the interval $3/7 < \epsilon < 3/4$.
 
-The Wigner distribution of the $n$--copy $\epsilon$--noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ is given by $\W{\rho_{\rm{S}}(\epsilon)^{\otimes n}} = W_{\rho_{\rm{S}}(\epsilon)}^{\otimes n}$ and, using~\cref{lem:ncopycomponents} in the unital fragment, we can associate it with a set $\{(w_i, m_i)\}_{i=0,\dots,n}$ of component-multiplicity pairs, the elements of which are presented in~\cref{tab:lcsu} for all different combinations of physical parameters $n, \epsilon$.
+The Wigner distribution of the $n$--copy $\epsilon$--noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ is given by $\W{\rho_{\rm{S}}(\epsilon)^{\otimes n}} = W_{\rho_{\rm{S}}(\epsilon)}^{\otimes n}$ and, using~\cref{lem:ncopycomponents} for unital protocols, we can associate it with a set $\{(w_i, m_i)\}_{i=0,\dots,n}$ of component-multiplicity pairs, the elements of which are presented in~\cref{tab:lcsu} for all different combinations of physical parameters $n, \epsilon$.
 We split the values of index $i$ into two intervals, defined precisely as
@@
 
-In the unital fragment, the rescaled distribution is simply proportional to the Strange state distribution,
+For unital protocols, the rescaled distribution is simply proportional to the Strange state distribution,
 \begin{equation}
@@
 therefore expressions for the Lorenz curve coordinates follow from summing up the Wigner components in decreasing order.
-As a result, every Strange state Lorenz curve in the unital fragment contains $n$ elbows. In the case of accidental degeneracies among Wigner components, some of these elbows may be straightened out.
+As a result, every Strange state Lorenz curve for a unital protocol contains $n$ elbows. In the case of accidental degeneracies among Wigner components, some of these elbows may be straightened out.
 Including the boundary points $(x_{-1}, L_{-1}) := (0,0)$ and $(x_{n}, L_{n}) := (1,1)$, we label these elbows as 
@@
 
-In~\cref{tab:lcsu_coord_elb_app}, we present the elbow coordinates of the $n$-copy, $\epsilon$--noisy Strange state Lorenz curve in the unital fragment for any combination of physical parameters $n, \epsilon$.
+In~\cref{tab:lcsu_coord_elb_app}, we present the elbow coordinates of the $n$-copy, $\epsilon$--noisy Strange state Lorenz curve for a unital protocol for any combination of physical parameters $n, \epsilon$.
 \begin{table}[h]
@@
   \end{tabular}
-  \caption{Strange state Lorenz curve elbow coordinates in the unital fragment, with $0 \leq i \leq n$. 
+  \caption{Strange state Lorenz curve elbow coordinates for a unital protocol, with $0 \leq i \leq n$. 
   For the LHS cases, the $i$ in the first column labels the elbow coordinate $x_i$ and the second column gives $L_i=L(x_i)$.
@@
 The points defining the Lorenz curve $L_{\rho_n |\tau_n}(x)$ are obtained from sorting the components of $W_{\rho_n |\tau_n}(\x)$ in non-increasing order and then computing the partial sums of $W_{\rho_n |\tau_n}(\pi(\x))$ where $\pi$ is the permutation that realises the sorting.
-However, similar to the unital fragment analysis, we use the slope constraint (\cref{prop:first_elb}) obtained by considering the line segments connecting the origin to the first elbow of both Lorenz curves.
+However, similar to the unital protocol analysis, we use the slope constraint (\cref{prop:first_elb}) obtained by considering the line segments connecting the origin to the first elbow of both Lorenz curves.
 
@@
 
-\subsection{Renyi min-divergence from initial slope}
+\subsection{Renyi min-divergence from Lorenz curves}
 We first demonstrate that the initial slope analysis on the Wigner quasi-distributions makes use of the min-relative divergence. We define 
@@
 	&H_{\alpha}\left(W_{\rho_{\rm{S}}(\epsilon)}\right) = \frac{1}{1-\alpha}\log \left[ 8\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^\alpha + \left(-\frac{1}{3} + \frac{4}{9}\epsilon \right)^\alpha \right] \nonumber\\
-	&\ddd{= \frac{\alpha}{\alpha-1}\log 18+ \frac{1}{1-\alpha}\log \left[ 8(3-\epsilon)^\alpha + (6-8\epsilon)^\alpha \right]}
 \end{align}
@@
     \includegraphics[scale=0.35]{figs/test/H_vs_eps_a.pdf}
-    \caption{\ddd{[TO DO: Set $\epsilon = 0$ and determine region of $\alpha$ such that $H <0$.]} Here, the exponent is $\alpha =$ even$/$odd for $1.10 \leq \alpha \leq 1.50$.
+    \caption{Here, the exponent is $\alpha =$ even$/$odd for $1.10 \leq \alpha \leq 1.50$.
 $H_\alpha$ is increasing in $\alpha$ and $\epsilon$.
 First dashed contour from the right corresponds to $H_\alpha(\rho_{\rm{S}}(\epsilon)) = 0$.
-Specifically, $H_\alpha(\rho_{\rm{S}}(0)) = 0$ has a unique solution, which is the \nick{probably irrational} solution of $3^\alpha - 2^{3-\alpha} = 1$.
+Specifically, $H_\alpha(\rho_{\rm{S}}(0)) = 0$ that implies $6^\alpha - 2^{\alpha} = 8$, with the approximate solution $\alpha \approx 1.31$.
     }

### 2021-06-09 magic_paper.tex
minor canges

--- 2021-06-08 magic_paper.tex
@@
 \input{preamble}
-
-\begin{document}
 % Labels and Refs (consistency, cref vs ref, thm vs lem vs prop, ??)
-% Figs check(fig.0, move to app, consistency, cbars, iffalse, axes)
-
-% Notation consistency (noise vs error, \ln{} -> \ln, \ln vs \log vs \log_2, italics & \emph, Aberg -> {\AA}berg, quasi-dist vs quasi-prob dist)
+% Figs check(consistency, cbars, captions, axes, iffalse)
+% Notation consistency (noise vs error, \ln{} -> \ln, \ln vs \log vs \log_2, italics & \emph, Aberg -> {\AA}berg, quasi-dist vs quasi-prob dist, def elbows)
 % UK vs US english
 % Spacing (figs, sections, paragraphs, eq. numbering, \noindent, QEDs)
+
+\begin{document}
 
@@
     \includegraphics[scale=0.35]{figs/distill_bounds.pdf}
-    \caption{\textbf{Distillation bounds in the unital fragment.} Distillation bounds obtained by the first elbow majorisation constraint $R$, mana $\M$ and max--thauma $\theta_{\rm{max}}$ are plotted for $\epsilon' = 0$, up to error $\epsilon = 3/7$.
+    \caption{\textbf{Distillation bounds in the unital fragment.} Distillation bounds obtained by the first elbow majorisation constraint $R_{\infty}$, the 10-Renyi bound $R_{10}$,o mana $\M$ and max--thauma $\theta_{\rm{max}}$ are plotted for $\epsilon' = 0$, up to error $\epsilon = 3/7$.
     Majorisation provides stricter rates than the global mana and max--thauma bounds.
@@
 \end{theorem}
-For magic protocols that generate unital maps the above bound reduces to the simpler form
+For magic protocols that preserve unital maps, the above bound reduces to the simpler form
 \begin{equation}
@@
 \end{equation}
-For any $\epsilon$ the upper bound can be numerically minimized over $\alpha$.
+The upper bound can be numerically minimized over $\alpha$, for any $\epsilon$.
 \begin{figure}[t!]

### 2021-06-09 magic_paper.tex

--- 2021-06-09 magic_paper.tex
@@
 
-\ddd{[Title of Gour2020 paper is incorrect in the bibliography]}
+\nick{REFs not already cited and that I think are relevant:}
+\begin{enumerate}
+	\item ``Excluding joint probabilities from quantum theory''~\cite{Allahverdyan_2018}
+	\item ``Quantum computation with realistic magic-state factories''~\cite{Ogorman_2017}
+	\item ``Magic-State Distillation in All Prime Dimensions Using Quantum Reed-Muller Codes''~\cite{CampbellAnwar_2012}
+	\item ``Resource optimized quantum architectures for surface code implementations of magic-state distillation''~\cite{holmes_resource_2019}
+	\item ``Quantum advantage in postselected metrology''~\cite{arvidsson_2020}
+	\item ``Quasiprobability behind the out-of-time-ordered correlator''~\cite{halpern_2018}
+	\item ``Quantum Fluctuation Theorems, Contextuality, and Work Quasiprobabilities''~\cite{Lostaglio_2018}
+	\item ``Quasiprobability Distribution for Heat Fluctuations in the Quantum Regime''~\cite{Levy_2020}
+	\item ``A One-Way Quantum Computer''~\cite{cit:raussendorf}
+	\item ``Measurement-based quantum computation on cluster states''~\cite{Raussendorf_2013}
+	\item ``Contextuality as a Resource for Models of Quantum Computation with Qubits''~\cite{Vega_2017}
+	\item ``On the extremal points of the $\Lambda$-polytopes and classical simulation of quantum computation with magic states''~\cite{okay2021extremal}
+\end{enumerate}
 
@@
 Our analysis applies majorization to magic states at the level of the associated Wigner distributions.
-However, these are in general quasi-probability distributions, so it is important to check how majorization is computed for these cases and what differences quasi-distributions bring over genuine probability distributions~\cite{arvidsson_2020, halpern_2018}.
+However, these are in general quasi-probability distributions, so it is important to check how majorization is computed for these cases and what differences quasi-distributions bring over genuine probability distributions \nick{CITE}.
 

### 2021-06-10 magic_paper.tex
distributed refs. Remains to smooth narrative from intro to outlook + decide on figures + eliminate comments

--- 2021-06-09 magic_paper.tex
@@
 
-\ddd{[Title of Gour2020 paper is incorrect in the bibliography]}
-
-The past few years have seen rapid progress towards the goal of a fault-tolerant quantum computer~\cite{Nickerson_2014, Nikahd_2017, chao_2018, lin_pieceable_2020, Lin_2020, Bourassa_2021}.
+The past few years have seen rapid progress towards the goal of a fault-tolerant quantum computer~\cite{cit:raussendorf, Raussendorf_2013, Nickerson_2014, Nikahd_2017, chao_2018, lin_pieceable_2020, Lin_2020, Bourassa_2021}.
 However, many challenges remain and there is increasing need for theory to take into account physical limitations of the hardware involved.
@@
 This can be achieved by injecting in quantum states, called magic states, which promote the Clifford group to universal quantum computing~\cite{cit:bravyi}.
-The obstacle to this is that these states are invariably noisy and so protocols involving stabilizer operations must be employed to purify many copies of the magic states and improve the overall performance of the induced quantum gates.
+The obstacle to this is that these states are invariably noisy and so protocols involving stabilizer operations must be employed to purify many copies of the magic states and improve the overall performance of the induced quantum gates~\cite{cit:bravyi, Jones_2013, Ogorman_2017}.
 A central question then arises about the overhead on purifying many copies of a magic state into less noisy forms.
 
-To address this, concrete distillation protocols have been developed, such as the Bravyi-Haah protocol that provides a quadratic reduction in noise per cycle~\cite{Bravyi2012}.
-Such distillation rates have been improved in more recent works~\cite{Hastings2018, Litinski_2019, Krishna2019, cit:prakash}.
-There is also analysis of magic protocols from the perspective of magic monotones, which provide upper bounds on distillation rates and find application in the analysis of gate synthesis~\cite{Campbell_2017, Howard_2017, Prakash_2018}.
+To address this, concrete distillation protocols have been developed, such as the Bravyi-Haah qubit protocol that provides a quadratic reduction in noise per cycle~\cite{Bravyi2012}.
+Such distillation rates have been improved in more recent works~\cite{Jones_2013, haah2017magic, Hastings2018, Litinski_2019} and protocols for qudits of odd dimension have also been proposed~\cite{Anwar_2012, CampbellAnwar_2012, Dawkins_2015, Krishna2019, cit:prakash}.
+There is also analysis of magic protocols from the perspective of magic monotones, which provide upper bounds on distillation rates and find application in the analysis of gate synthesis~\cite{Campbell_2017, Howard_2017, Prakash_2018, Seddon_2021}.
 These frameworks for magic view magic states as resource states with respect to a natural class of quantum operations that are considered cheap, or free, such as stabilizer operations~\cite{Gour_2019, cit:ahmadi, cit:seddon, Wang_2019}.
-Beyond quantum computing, recent work has also looked at how magic can be used to analyse many-body physics~\cite{Sarkar_2020} and conformal field theories~\cite{White_2021}.
+Beyond quantum computing, recent work has also looked at how magic can be used to analyse many-body physics~\cite{Sarkar_2020} and conformal field theories~\cite{White_2021} as well as how it is connected with contextuality~\cite{Vega_2017, cit:howard2, Zurel_2020, okay2021extremal}.
 
 Recent work towards fault-tolerance has begun to bridge the gap between abstract theory and experiment.
-Extensive work has been done on error mitigation~\cite{Li_2017, Temme_2017, Endo_2018, McClean_2017}, and the incorporation of hardware physics into the theoretical modes~\cite{Kandala_2019, Colless_2018, song2018quantum, Bravyi_2021}.
+Extensive work has been done on error mitigation~\cite{Li_2017, Temme_2017, Endo_2018, McClean_2017}, and the incorporation of hardware physics into the theoretical modes~\cite{holmes_resource_2019, Kandala_2019, Colless_2018, song2018quantum, Bravyi_2021}.
 For example, the XZZX code~\cite{bonilla_ataides_xzzx_2021} is a variant of the surface code that incorporates noise bias explicitly and has been shown to attain the hashing bound of random codes~\cite{Bennett_1996}.
@@
 
-Through this approach we obtain a range of upper bounds for magic distillation rates.
+Through this approach, we obtain a range of upper bounds for magic distillation rates.
 We provide explicit bounds for magic protocols that generate unital channels, as well as bounds that depend on the temperature and Hamiltonian of the system.
@@
 Our analysis applies majorization to magic states at the level of the associated Wigner distributions.
-However, these are in general quasi-probability distributions, so it is important to check how majorization is computed for these cases and what differences quasi-distributions bring over genuine probability distributions~\cite{arvidsson_2020, halpern_2018}.
+However, these are in general quasi-probability distributions, so it is important to check how majorization is computed for these cases and what differences quasi-distributions bring over genuine probability distributions.
 
@@
 
-This motivates defining the following \emph{Wigner divergence} $D_\infty(\rho, \tau) := D_\infty (W_\rho(\x) || W_\tau (\x))$ on all quantum states.
+This motivates defining the following \emph{Wigner divergence} $D_\infty (W_\rho(\x) || W_\tau (\x))$ on all quantum states.
 In~\cref{app:lcst_technical}, we show that this divergence has the following natural properties that are derived via relative majorization.
@@
 \item $D_\infty(W_{\rho^{\otimes 2n}}|| W_{\tau^{\otimes 2n}}) = n D_\infty(W_{\rho^{\otimes 2}} ||W_{\tau^{\otimes 2}})$ for any $n \in \mathbb{N}$.
-\item For any quantum state $\rho$, and any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$, we have $D_\infty (W_\rho || W_\tau) \ge D_\infty (W_{\E(\rho)}|| W_{\E(\tau)})$.
+\item $D_\infty(W_\rho || W_\tau) \geq D_\infty(W_{\E(\rho)} || W_{\E(\tau)})$ for any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$.
 \end{enumerate}
@@
 One might speculate if the presence of magic in Clifford circuits admits a sensible interpretation in terms of a zeroth-order phase transition.
-However since variation in $\alpha$ is no longer smooth ($\alpha$ is restricted to a dense set of rational values) technical obstacles exist and we do not pursue this speculative line here, but just note that other works exist in which computational transitions are considered in relation to phase transitions.
+However since variation in $\alpha$ is no longer smooth ($\alpha$ is restricted to a dense set of rational values) technical obstacles exist and we do not pursue this speculative line here, but just note that other works exist in which computational transitions are considered in relation to phase transitions~\cite{Allahverdyan_2018, arvidsson_2020, halpern_2018, Lostaglio_2018, Levy_2020} \nick{I don't understand this statement, so I just dropped all citations on quasi-distributions here}.
 
 Every entropy is best understood as a relative entropy~\cite{Gour_2020} and so we now state the extension to Renyi divergences.
-We define the $\alpha$--Renyi Wigner divergence $D_\alpha$ as
-\begin{equation}
-	D_\alpha(\w || \r) := \frac{1}{\alpha-1} \log \sum_i w_i^\alpha r_i^{1-\alpha},
-\end{equation}
-where $\w$ can be a quasi-distribution, $\r$ a probability distribution with positive components and $\alpha$ can take the same values as for $H_\alpha$.
+We define the $\alpha$--Renyi Wigner divergence $D_\alpha(\p||\r)$ as
+\begin{equation}
+	D_\alpha(\p || \r) := \frac{1}{\alpha-1} \log \sum_i p_i^\alpha r_i^{1-\alpha},
+\end{equation}
+where $\p$ can be a quasi-distribution, $\r$ a probability distribution with positive components and $\alpha$ can take the same values as for $H_\alpha$.
 In~\cref{app:lcst_technical}, we also show that the divergence satisfies the following natural properties for all $\alpha$ for which it is well-defined.
@@
 	Let $\tau$ be in the interior of $\F$. 
-	If $\alpha = 2a / (2b-1)$ for non-negative integers $a,b$ with $a \geq b$, then the $\alpha$-Renyi divergence $D_\alpha(W_\rho || W_\tau)$ is well-defined for all states $\rho$, and the following hold:
+	If $\alpha = \frac{2a}{2b-1}$ for non-negative integers $a,b$ with $a \geq b$, then the $\alpha$-Renyi divergence $D_\alpha(W_\rho || W_\tau)$ is well-defined for all states $\rho$, and the following hold:
 \begin{enumerate}

### 2021-06-11 magic_paper.tex
Version fit for sending for comments.

@@
 While traditional free energy is not defined in the presence of negativity, we show that majorization allows us to both quantify disorder in the Wigner representation and derive magic distillation bounds.
-These upper bounds are shown to be tighter than other bounds, such as those from mana and thauma, and moreover incorporate hardware physics, such as temperature dependence.
-We show that a sub-set of single-shot Renyi entropies remain well-defined on quasi-distributions, are fully meaningful in terms of data processing and can acquire negative values.
-We also show that the mana of a magic state is exactly the coefficient of divergence of Renyi entropies as one approaches the Shannon entropy for Wigner distributions, and discuss how distillation lower bounds could be obtained in this setting.
+These upper bounds are shown to be tighter than other bounds, such from mana and thauma, and moreover incorporate hardware physics, such as temperature dependence and physical Hamiltonians.
+We also show that a sub-set of single-shot Renyi entropies remain well-defined on quasi-distributions, are fully meaningful in terms of data processing and can acquire negative values.
+We show that the mana of a magic state is the measure of divergence of these Renyi entropies as one approaches the Shannon entropy for Wigner distributions, and discuss how distillation lower bounds could be obtained in this setting.
 This use of majorization for quasi-distributions could find application in other studies of non-classicality, and raises novel questions in the context of classical statistical mechanics.
@@
 
-The past few years have seen rapid progress towards the goal of a fault-tolerant quantum computer~\cite{cit:raussendorf, Raussendorf_2013, Nickerson_2014, Nikahd_2017, chao_2018, lin_pieceable_2020, Lin_2020, Bourassa_2021}.
+There has been rapid progress towards the goal of a fault-tolerant quantum computer~\cite{cit:raussendorf, Raussendorf_2013, Nickerson_2014, Nikahd_2017, chao_2018, lin_pieceable_2020, Lin_2020, Bourassa_2021}.
 However, many challenges remain and there is increasing need for theory to take into account physical limitations of the hardware involved.
@@
 The obstacle to this is that these states are invariably noisy and so protocols involving stabilizer operations must be employed to purify many copies of the magic states and improve the overall performance of the induced quantum gates~\cite{cit:bravyi, Jones_2013, Ogorman_2017}.
-A central question then arises about the overhead on purifying many copies of a magic state into less noisy forms.
+A key question then arises about the overhead on purifying many copies of a magic state into less noisy forms.
 
@@
 
-Recent work towards fault-tolerance has begun to bridge the gap between abstract theory and experiment.
+Recent work towards fault-tolerance is increasingly bridging the gap between abstract theory and experiment.
 Extensive work has been done on error mitigation~\cite{Li_2017, Temme_2017, Endo_2018, McClean_2017}, and the incorporation of hardware physics into the theoretical modes~\cite{holmes_resource_2019, Kandala_2019, Colless_2018, song2018quantum, Bravyi_2021}.
@@
 
-In this work, we develop a framework to analyse magic state distillation protocols where explicit physics of the system is incorporated.
-Distillation bounds are obtained by considering how a given magic state protocol would behave if it were instead applied to a \emph{stabilizer} state that is distinguished by the physics of the system -- for example an equilibrium state at a characteristic temperature, or the maximally mixed state.
-The magic distillation bounds can then be expressed in terms of this distinguished degrees of freedom (e.g.
+In this work, we develop a framework to analyse magic state distillation protocols where explicit physics of the system is incorporated in the distillation bounds.
+This is achieved by considering how a given magic state protocol transforms a \emph{pair} of quantum states -- one being noisy magic state, and the other a stabilizer state that is distinguished by the physics of the system (for example a state at a characteristic temperature, or the maximally mixed state) and acts as a reference state.
+The magic distillation bounds can then be expressed in terms of the physics of the reference state (e.g.
 free energy changes in the case of temperature, or non-unitality in the case of the maximally mixed state).
-Such bounds are therefore of interest in assessing how physical features such as temperature, noise-biases or fixed-point structure associated with restricted gate-sets constrain distillation protocols, and so are of relevance to existing work towards fault-tolerant quantum computing~\cite{Aliferis_2008, Stephens_2013, Li_2015, Babbush_2018, Tuckett_2019, Guillaud_2019, Fowler_2019}.
+Such bounds are therefore of interest in assessing how physical features such as temperature, noise-biases or fixed-point structure associated with restricted gate-sets constrain distillation protocols~\cite{Aliferis_2008, Stephens_2013, Li_2015, Babbush_2018, Tuckett_2019, Guillaud_2019, Fowler_2019}.
 
 The approach we take is most closely aligned with resource theories of magic, however it differs in a few ways.
-Firstly, we obtain distillation upper bounds without the use of monotones, and secondly our distillation bounds are hardware dependent.
-We approach this problem using tools from statistical mechanics and recent work from the overlap of thermodynamics and quantum information theory~\cite{cit:janzing, cit:horodecki2, Brandao_2015, Vinjanampathy_2016, Goold_2016, cit:lostaglio, cit:gour}.
-In particular, we shall view \emph{magic as a form of free energy}, relative to the set of stabilizer states.
-From this perspective, the convex set of stabilizer states behaves as the set of ``equilibrium'' states, and magic corresponds to a form of non-equilibrium free energy that is strictly non-classical.
-
+We obtain distillation upper bounds without the use of monotones, but instead tools from statistical mechanics and recent work from the overlap of thermodynamics and quantum information theory~\cite{cit:janzing, cit:horodecki2, Brandao_2015, Vinjanampathy_2016, Goold_2016, cit:lostaglio, cit:gour}.
 Our analysis relies on the discrete Wigner representation of quantum systems, in which all states and operations can be described on a discrete phase space~\cite{Ferrie_2008, Okay_2021}.
@@
 We circumvent this obstacle by making use of a more fundamental tool in thermodynamics and information theory -- majorization theory~\cite{cit:marshall, Veinott_1971, Ruch_1976}.
-To our knowledge majorization of quasi-distributions has not been considered in quantum physics before, and therefore our analysis is also of interest to the study of non-classicality in quantum systems.
-
-Through this approach, we obtain a range of upper bounds for magic distillation rates.
+To our knowledge majorization of quasi-distributions has not been considered in quantum physics before, and therefore our analysis is also of interest to the study of non-classicality in quantum systems~\cite{Allahverdyan_2018, arvidsson_2020, halpern_2018, Lostaglio_2018, Levy_2020}.
+
+With this approach, we obtain a range of upper bounds for magic distillation rates.
 We provide explicit bounds for magic protocols that generate unital channels, as well as bounds that depend on the temperature and Hamiltonian of the system.
+These bounds are shown to be tighter than other bounds such as from mana and thauma.
 We find that the thermodynamic ordering in the presence of negativity is non-trivial and displays a range of features that, unsurprisingly, do not appear in classical statistical mechanics.
+We show that Wigner negativity in a quantum circuit can be described as a non-classical free energy that is processed under stochastic maps.
+We also show that a subset of single-shot Renyi entropies can be sensibly extended to quasi-distributions, lead to improved distillation bounds, and show that the mana of a quantum state governs the rate of divergence of the Renyi entropies as we approach the (undefined) Shannon entropy.
 Finally, we discuss how our approach could be improved and how it can be exploited to construct explicit lower bounds on distillation that take into account physical structure.
@@
 A number of magic theories exist, where magic states are computational resource states with respect to a natural class of quantum operations that are considered free~\cite{Gour_2019}.
-One very natural class of free operations are those obtained from Clifford operations, measurements and the ability to discard quantum systems.
+One very natural class of free operations are those obtained from Clifford unitaries, Pauli measurements and the ability to discard quantum systems.
 However, there are also other candidates~\cite{cit:ahmadi, cit:seddon, Wang_2019}.
 
-In any theory of magic, a natural route to bounding the distillation rates obtainable is through the concept of a \emph{magic monotone}.
+In any theory of magic, one route to bounding distillation rates is through a \emph{magic monotone}.
 A magic monotone is a real-valued function of any quantum state $\M(\rho)$ that is monotonically non-increasing under the free operations of the magic theory.
-More precisely $\M(\sigma) \le \M(\rho)$ whenever it is possible to convert $\rho$ into $\sigma$ using free operations (e.g.
-Clifford operations).
+More precisely $\M(\sigma) \le \M(\rho)$ whenever it is possible to convert $\rho$ into $\sigma$ using free operations.
 
@@
 where $R\coloneqq \sum_{i=1}^n r_i$ and $\pi$ is the permutation on $n$ objects mapping $\widetilde{\w}$ to $\widetilde{\w}^{\downarrow}$.
-The form of this requires that $\r$ has no zero components, which we shall assume without loss of generality as in any physical situation the rank of a quantum state is not an operationally meaningful quantity.
+The form of this requires that $\r$ has no zero components, which we shall assume without loss of generality as the rank of a quantum state is not operationally meaningful.
 
@@
 
-\nick{Is the following result more distinguished than other results we have in the appendices?}
 \begin{lemma} Let $\w \in \mathbb{R}^n,\w'\in \mathbb{R}^m$ be quasi-distributions, and let $\r \in \mathbb{R}^n, \r' \in \mathbb{R}^m$ be probability distributions with non-zero components.
-Then $(\w, \r) \succ (\w', \r')$ if and only if $L_{\w|\r}(x) \ge L_{\w |\r}(x)$ for all $x \in [0,1]$.
+Then $(\w, \r) \succ (\w', \r')$ if and only if $L_{\w|\r}(x) \ge L_{\w' |\r'}(x)$ for all $x \in [0,1]$.
 \end{lemma}
@@
 
-With all the necessary theory in place, we now turn to magic distillation protocols.
-
-\newpage
+With this theory in place, we now turn to magic distillation protocols.
+
 \section{Magic distillation bounds with fixed-points}
@@
 
-We can now consider how physical constraints that may be hardware specific, affect magic distillation rates.
-These are not a priori encoded in the formulation of the magic theory, and constitute additional physical conditions on top of the underlying resource-theoretic accounting.
-For example, there may be non-trivial thermal noise in the physical set-up or the accessible operations, there might be strong bias in the noise present, or we might be limited in how easily certain gates can be realised.~\cite{Aliferis_2008, Stephens_2013, Li_2015, Babbush_2018, Tuckett_2019, Guillaud_2019, Fowler_2019}.
-
-In~\cref{sec:stab} we shall focus on the energetic costs of a protocol, that are defined due to the specific Hamiltonian that the system possesses.
-However, before that, in this section we encode physical constraints at a more abstract level in terms of the fixed-point structure of  the actual operations that are accessible to us.
+We can now consider how physical constraints affect magic distillation rates.
+In~\cref{sec:stab} we shall focus on the energetic aspects of a protocol, that are defined due to the specific Hamiltonian that the system possesses.
+However, before that, in this section we give a more abstract setting based on the fixed-point structure of  the physical operations accessible to us.
 We show that any magic theory can always be decomposed in terms of `sub-theories' with a particular fixed-point structure.
-This section therefore exploits $\mathbf{d}$--majorization, while in~\cref{sec:stab} we drop the requirement of fixed-points and instead use the full relative majorization relation.
-
- We begin by defining the following kind of sub-theory of any magic theory $\R$.
+This section uses $\mathbf{d}$--majorization, however in~\cref{sec:stab} we drop the requirement of fixed-points and instead use the full relative majorization, before finally giving general entropic constraints in Section~\ref{section:entropies}.
+
+ We begin by defining the following sub-theory of any magic theory $\R$.
 \begin{definition}\label{def:sigmafrag}
@@
 \end{definition}
-This notion provides a simple way to break up any theory into smaller, more manageable parts.
-Moreover, the union over all sub-theories returns the parent theory, so we are not discarding any information by breaking up the theory in this way.
-We make this statement precise as follows.
+This provides a simple way to break up any theory into smaller, more manageable parts, and where the union over all sub-theories returns the parent theory, so we are not discarding any information by breaking up the theory in this way.
+We make this precise as follows.
 \begin{theorem}\label{thm:frag}
@@
 
-\subsection{Basic monotones for magic distillation for a particular $\R_\sigma$}
+\subsection{Basic monotones for magic distillation for a particular $\R_\sigma$ and the relation to mana}
 \label{sec:monotones_frag}
@@
 
-\begin{lemma} Relative majorization in any $\R_\sigma$ implies the monotonicity of sum-negativity. 
+\begin{lemma} Majorization in any $\R_\sigma$ implies the monotonicity of sum-negativity. 
 \end{lemma}
@@
     \caption{\textbf{Distillation bounds for unital protocols.} Distillation bounds obtained by the first elbow majorisation constraint $R_\infty$, mana and max--thauma $\theta_{\rm{max}}$ are plotted for $\epsilon' = 0$, up to error $\epsilon = 3/7$.
-Also shown is the bound $R_{10}$ which comes from single-shot entropies, which we discuss in Section~\ref{section:entropies}.
+Also shown is the bound $R_{10}$ coming from single-shot entropies on the quasi-distributions, which we discuss in Section~\ref{section:entropies}.
 Numerical bounds $R_{\rm{num}}$ are obtained by using the full set of Lorenz curve constraints.
@@
 
-\newpage
 \section{Temperature-dependent bounds for magic state distillation protocols}
@@
 
-We now consider a magic distillation protocol on multiple identical qudits in a noisy magic state $\rho(\epsilon)$, with noise parameter $\epsilon$, sending 
+We can now show how to use majorization to incorporate physics into magic distillation bounds.
+We focus on energetic and entropic aspects of a protocol.
+The way we describe these is by how the protocol would disturb a reference equilibrium state $\tau$ to some different state $\tau'$, if the protocol had been applied to this reference state instead of the actual $n$-copy magic state.
+
+We consider a magic distillation protocol on multiple identical qudits in a noisy magic state $\rho(\epsilon)$, with noise parameter $\epsilon$, sending 
 \begin{equation}
@@
 with $n \gg 1$, $\epsilon' <\epsilon$ and $\E$ denoting the quantum channel induced by the protocol.
-We can now provide distillation bounds that depend on energetic and entropic aspects of the protocol.
-We do this relative to a reference temperature that can be chosen freely.
-The key idea is that the physical measures associated with this protocol are determined by how $\E$ would disturb a reference equilibrium state $\tau$ to some different state $\tau'$, if the protocol had been applied to this reference state instead of the $n$-copy magic state.
-
-More precisely, we assume each qudit has Hamiltonian $H$ and we choose some temperature $T = (k\beta)^{-1}$ where $k$ is Boltzmann's constant and $\beta$ the inverse temperature.
+We also assume each qudit has Hamiltonian $H$ and we choose some temperature $T = (k\beta)^{-1}$ where $k$ is Boltzmann's constant and $\beta$ the inverse temperature.
 The reference equilibrium state of the $n$ qudits is given by
@@
 \end{equation}
-Since we are concerned with magic distillation we may assume that the reference state $\tau$ is not a magic state, so it has a non-negative Wigner distribution, and we shall further assume that it is a full-rank stabilizer state for the qudit.
+We may also assume that the reference state $\tau$ is not a magic state, and has a strictly positive Wigner distribution $W_\tau(\x)$.
 
 A given magic protocol on the $n$ qudits will correspond to a quantum channel $\E$.
-Our analysis associates to this protocol energy/entropy measures by considering how $\E$ transforms this reference equilibrium state.
-We first note that we can assume without loss of generality that $U_\pi\E(X) U_\pi^\dagger = \E(X)$ for all $X$ and any permutation $U_\pi$ of the $m$ output subsystems.
+We also assume for simplicity that $U_\pi\E(X) U_\pi^\dagger = \E(X)$ for all $X$ and any permutation $U_\pi$ of the $m$ output subsystems.
 This is justified because the protocol on the input magic state results in state $\rho(\epsilon')^{\otimes m}$, which is invariant under permutations.
@@
 where $d\mu(x)$ is a probability measure over a set $\{\tau'_x\}$ of single qudit states.
-This makes the setting easier to handle, although we make one more simplifying assumption as explained in the next section.
+This makes the setting easier to handle, although we make one more simplifying assumption on the physics as explained in the next section.
 
 \subsection{Free energy and sub-linear correlations in the thermodynamic limit}
-To simplify our analysis we will make the following physical assumption.
+To keep our analysis simple we make the following physical assumption.
 We assume that in the asymptotic/thermodynamic limit $n,m \rightarrow \infty$ that correlations generated on the reference equilibrium state are negligible.
-This implies that $d\mu(x)$ is peaked on a particular state $\tau'$, and $\E(\tau) = \tau'^{\otimes m}$.
-Physically, this is a natural scenario -- for example, in the context of traditional thermodynamics, it states that the output system is well-described by intrinsic variables that do not scale in $m$, and correlations are sub-linear in $m$.
+This implies that $d\mu(x)$ is peaked on a particular state $\tau'$, and $\E(\tau) \approx \tau'^{\otimes m}$.
+This occurs in the context of traditional thermodynamics, and states that the output system is well-described by intrinsic variables that do not scale in $m$, and correlations are sub-linear in $m$.
 This allows us to compute a free energy per qudit of the output state.
-
 The case of non-trivial correlations in the thermodynamic limit can also be considered, but leads to a more complex analysis within our majorization framework of Wigner distributions.
@@
 
-Our analysis will depend on the energetic properties of the probe state $\tau$ and the output state $\tau'$.
-For the state $\tau = e^{-\beta H}/\Z$, the Helmholtz free energy $F$ is given by
+Our bound turn out to depend on the von Neumann entropy $S(\rho)$ of a state, and the free energy at a particular temperature.
+For a state $\tau = e^{-\beta H}/\Z$, the Helmholtz free energy $F$ is given by
 \begin{equation}
@@
 \end{equation}
-which can be obtained from the internal energy via a Legendre transform~\cite{Pathria_1997}.
+which be obtained from the internal energy via a Legendre transform~\cite{Pathria_1997}.
 
 The protocol transforms the equilibrium as $\tau^{\otimes n} \rightarrow \E(\tau^{\otimes n}) = \tau^{\prime \otimes m}$.
-The protocol does not, on its own, generate magic and so we assume the output state $\tau'$ is also a Wigner-positive state.
+The protocol does not on its own generate magic and so we assume the output state $\tau'$ is also a Wigner-positive state.
 However, this is generally a \emph{non-equilibrium} state for the system.
-Despite this, the distillation bounds that we derive take a particularly simple form if we associate an effective Hamiltonian $H'$ to the output state by considering the change $H \rightarrow H'$ such that equilibrium is restored at the reference temperature $T$.
+Despite this it is useful to associate an effective Hamiltonian $H'$ to the output state by considering the change $H \rightarrow H'$ such that equilibrium is restored at the reference temperature $T$.
 This Hamiltonian is defined by the expression $\tau' = e^{-\beta H'}/\Z'$, and has free energy $F' = -\beta^{-1} \log \Z'$.
@@
 
-We can specify energetic details of a protocol through how much it would disturb some reference equilibrium state.
-The magic state transformation is then considered relative to the equilibrium transformation, and can be recast via the Wigner representation into a relative majorization statement $(\w, \r) \succ (\w', \r')$ where $\w, \w'$ are quasi-distributions corresponding to the magic transformation, while $\r, \r'$ correspond to the transformation of the reference equilibrium state.
-
-This leads to the following magic distillation bound that combines computational measures $\epsilon,\epsilon'$, with terms that depend on the Hamiltonian and reference temperature $T$ of the physical system.
-We state the result for the case of qutrits, but a similar analysis is possible for general qudits.
+The magic state transformation is now considered by how it transforms the pair of quantum states $(\rho^{\otimes n}, \tau^{\otimes n})$.
+This transformation is then constrained by the relative majorization condition $(W_{\rho}, W_\tau) \succ (W_{\rho'}, W_{\tau'})$ that holds due to the protocol being a stochastic map in the Wigner representation.
+
+In Appendix~\ref{thm:free-energy-bound-proof} we analyse the Lorenz curves of this condition and obtain the following magic distillation bound that combines computational measures $\epsilon,\epsilon'$, with terms that depend on the Hamiltonian and reference temperature $T$ of the physical system.
+We state the result for the case of qutrits, but a similar analysis works for general qudits.
 
@@
 The intermediate terms specify how the energy eigenbasis of the system $\{|E_k\>\}$ relates to the computational stabilizer basis $\{|k\>\}$.
-In particular, the term $\phi$ quantifies to what degree a sharp energy value can be ascribed to the negativity in the Wigner representation.
-Its form is similar to $F$, so $\phi$ can informally be viewed as a `magic free energy' term.
+In particular, the term $\phi$ quantifies to what degree a sharp energy value can be associated to the negativity in the Wigner representation.
+Its form is similar to $F$, and so $\phi$ can informally be viewed as a `magic free energy' term.
 
@@
 
-\subsection{Technical aspects of the bound}
+\subsection{Technical aspects and special cases}
 Similar to the unital protocol bounds, the above result is based on only part of the Lorenz curves and so can certainly be tightened with further analysis.
@@
 
-\iffalse
-\begin{figure}[t!]
-    \centering
-    \includegraphics[scale=0.4]{figs/rate_scatter.pdf}
-    \caption{\textbf{Temperature-dependent bounds for magic distillation.}
-  Shown is a contour plot of the bound on $R(\epsilon, \beta)$ for $H = H' = \sum_{k \in \mathbb{Z}_3} k |k\>\<k|$ and $\epsilon' = 0$, where $\beta$ is the inverse temperature and $\epsilon$ the depolarising error of the input magic state.
+%\iffalse
+%\begin{figure}[t!]
+%    \centering
+%    \includegraphics[scale=0.4]{figs/rate_scatter.pdf}
+%    \caption{\textbf{Temperature-dependent bounds for magic distillation.}
+%  Shown is a contour plot of the bound on $R(\epsilon, \beta)$ for $H = H' = \sum_{k \in \mathbb{Z}_3} k |k\>\<k|$ and $\epsilon' = 0$, where $\beta$ is the inverse temperature and $\epsilon$ the depolarising error of the input magic state.
 The relevant data from the spectrum of the qutrit operator $H$ enters in via $\epsilon_\star(\beta)$ and $\beta_\star$.
@@
 \nick{Refer to definitions of starred quantities} The $\beta = 0$ line corresponds to the regime in which the magic protocol corresponds to a unital channel.
-    }
-    \label{fig:rate_contour}
-\end{figure}
-\fi
+%    }
+%    \label{fig:rate_contour}
+%\end{figure}
+%\fi
 
@@
     \label{fig:noCliff}%
-    \includegraphics[scale=0.4]{figs/rate_scatter.pdf}}\\
+    \includegraphics[scale=0.35]{figs/rate_scatter.pdf}}\\
     \subfigure[][]{%
     \label{fig:Cliff}%
-    \includegraphics[scale=0.4]{figs/rate_scatter_cliff.pdf}}
+    \includegraphics[scale=0.35]{figs/rate_scatter_cliff.pdf}}
     \caption{\textbf{Temperature-dependent bounds for magic distillation.} Shown are two contour plots of the bound on $R(\epsilon, \beta)$ for the case $H = H' = \sum_{k \in \mathbb{Z}_3} k \ketbra{k}$ and $\epsilon' = 0$, where $\beta$ is the inverse temperature and $\epsilon$ is the depolarising noise of the input magic state.
@@
 
-\subsection{Distillation bound for special cases}
-
 The simplest special case to consider is where the Hamiltonian $H$ is diagonal in the computational basis, and $H=H'$, implying that the protocol leaves the reference equilibrium state unchanged, hence it corresponds to a Gibbs-preserving map~\cite{faist_2015}.
@@
 In this figure we show both the bounds with Clifford basis changes and without them.
-
 In the more general case, $\Delta F \coloneqq F' - F \ne 0$ and so the protocol, when applied to the reference state, adds/extracts free energy from the system.
 
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.4]{figs/test/R_vs_E1.pdf}
-    \caption{Here, $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$, $H = \rm{diag}(0,E,10)$ and $H' = \rm{diag}(0,E',10)$.
-    }
-    \label{fig:rvse1}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.4]{figs/test/R_vs_E2.pdf}
-    \caption{Here, $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$, $H = \rm{diag}(0,5,E)$ and $H' = \rm{diag}(0,5,E')$.
-    }
-    \label{fig:rvse2}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.4]{figs/test/R_vs_H.pdf}
-    \caption{Here, $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$, $H = {\rm{diag}}(0,1,2)$ and $H' = (1-p-q){\rm{diag}}(0,1,2)+p{\rm{diag}}(1,2,0)+q{\rm{diag}}(2,0,1)$.
-    }
-    \label{fig:rvsh}
-\end{figure}
+%
+%\begin{figure}
+%    \centering
+%    \includegraphics[scale=0.4]{figs/test/R_vs_E1.pdf}
+%    \caption{Here, $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$, $H = \rm{diag}(0,E,10)$ and $H' = \rm{diag}(0,E',10)$.
+%    }
+%    \label{fig:rvse1}
+%\end{figure}
+
+%\begin{figure}
+%    \centering
+%    \includegraphics[scale=0.4]{figs/test/R_vs_E2.pdf}
+%    \caption{Here, $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$, $H = \rm{diag}(0,5,E)$ and $H' = \rm{diag}(0,5,E')$.
+%    }
+%    \label{fig:rvse2}
+%\end{figure}
+
+%\begin{figure}
+%    \centering
+%    \includegraphics[scale=0.4]{figs/test/R_vs_H.pdf}
+%    \caption{Here, $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$, $H = {\rm{diag}}(0,1,2)$ and $H' = (1-p-q){\rm{diag}}(0,1,2)+p{\rm{diag}}(1,2,0)+q{\rm{diag}}(2,0,1)$.
+%    }
+%    \label{fig:rvsh}
+%\end{figure}
 
@@
     \includegraphics[scale=0.4]{figs/test/R_vs_A.pdf}
-    \caption{Here, $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$, $H = A_{\bmo}$ and $H' = (1-p-q)A_{\bmo}+pA_{(1,2)}+q{\rm{diag}}(0,1,2)$.
+    \caption{\textbf{Variation of distillation bounds with Hamiltonian.} We consider $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$, and look at a family of Hamiltonians for the qutrit systems, given by $H = A_{\bmo}$ and $H' = (1-p-q)A_{\bmo}+pA_{(1,2)}+q{\rm{diag}}(0,1,2)$.
     }
@@
 
-\newpage
-\section{Well-defined \& monotonic  entropies for quasi-distributions}\label{section:entropies}
+\section{Extension of single-shot entropies to quasi-distributions}\label{section:entropies}
 We have considered Wigner distributions of magic states within a statistical mechanical setting in which it is was argued that magic should be viewed as a non-classical form of free energy.
-This identification with free energy was done at the level of majorization with respect to stochasticity corresponding to stabilizer operations.
-In this context non-equilibrium states with substantial free energy have Lorenz curves that deviate noticeably from the line $y=x$.
+This identification with free energy was done at the level of majorization constraints that appear due to stabilizer operations being described by stochastic maps in the Wigner representation.
+In this representation, non-equilibrium states with substantial free energy have Lorenz curves that deviate noticeably from the line $y=x$.
 We also found that when considered in a distillation protocol, magic could be linked to thermodynamic free energies in a non-trivial way.
@@
 
-One obstacle to linking with macroscopic, equilibrium free energy is that the Wigner distribution is generally a quasi-distribution and so the entropy $H(\w) = -\sum_i w_i \log w_i$ of the Wigner distribution is not defined off of the set $\F$, let alone being a physically meaningful quantity.
-
-However in this direction, we first note that the analysis for the temperature-dependent bound given by Equation (\ref{eq:rate_bounds_proof}) implicitly makes use of the single-shot Renyi divergence $D_\infty (\p ||\r)$, which is given by
+One obstacle to linking with macroscopic, equilibrium free energy is that the Wigner distribution is generally a quasi-distribution and so the entropy $H(\w) = -\sum_i w_i \log w_i$ of the Wigner distribution is not defined off of the set $\F$, let alone having a physically meaningful interpretation.
+
+However, it turns out that the analysis for the temperature-dependent bound given by Equation (\ref{eq:rate_bounds_proof}) implicitly made use of the single-shot Renyi divergence $D_\infty (\p ||\r)$, which is given by
 \begin{equation}
@@
 \end{equation}
-This does remain well-defined on quasi-distributions, and from the majorization relation also has a clear physical meaning.
-
-This motivates defining the following \emph{Wigner divergence} $D_\infty (W_\rho(\x) || W_\tau (\x))$ on all quantum states.
-In~\cref{app:lcst_technical}, we show that this divergence has the following natural properties that are derived via relative majorization.
+It is clear that this does remain well-defined on quasi-distributions, and from the majorization relation also has a clear physical meaning, and in~\cref{app:lcst_technical}, we show that this divergence has the following properties that are derived via relative majorization.
 \begin{theorem}\label{thm:Dinfty} 
@@
 
-We can now go further, and show that a range of entropies remain both well-defined and meaningful in this setting. The $\alpha$--Renyi entropy $H_\alpha(\p)$ is defined as
+We can go further, and show that a range of Renyi entropies remain both well-defined and meaningful in the Wigner representation. The $\alpha$--Renyi entropy $H_\alpha(\p)$ is defined as
 \begin{equation}
@@
 \end{theorem}
-This therefore provides a meaningful extension of entropies to quasi-distributions.
+This monotonicity provides a meaningful extension of entropies to quasi-distributions, and the allowed values are dense in $\alpha >1$.
 Moreover we can prove the following result, which establishes the equivalence between Wigner negativity and the existence of negative Renyi entropy.
@@
 \end{theorem}
-Therefore, the statistical mechanical description of stabilizer operations provides a setting in which negative entropy is fully meaningful, and quantifies the fact that magic states are `more ordered' than a perfectly sharp, deterministic classical state $\w = (1,0, \dots , 0)$ with zero entropy.
+Therefore, the statistical mechanical description of stabilizer operations provides a setting in which negative entropy is fully meaningful, and quantifies the fact that magic states are more ordered than a perfectly sharp, deterministic classical state $\w = (1,0, \dots , 0)$ with zero entropy.
 We note that prior work has shown that negative conditional entropy~\cite{rio_thermodynamic_2011} arises in the context of quantum correlations, however this is unrelated to the present negative entropy.
@@
 \end{equation} 
-with $\epsilon \rightarrow 0^+$ through a sequence of rational values $(a-b)/b$.
-However we recall that mana is defined as $\M(\rho) = \log \sum_{\x} |W_\rho(\x)|$, and so we obtain a second new description of mana: \emph{it is the coefficient of divergence of the Wigner Renyi-entropy} as we approach the limiting Shannon entropy $H(\w)$.
-
-We also note that the Renyi entropy can be viewed as a $q$--deformation of the Shannon entropy~\cite{baez2011renyi}, and $H_\alpha(\p)$ can be related to the $q$--derivative of free energy.
-More precisely, it can be shown that
-\begin{equation}
-	H_{\frac{T}{x}} = \frac{1}{x-T} (F(x) - F(T)),
-\end{equation}
-\nick{Do you mean $H_{\frac{T}{x}}(\w)$? What is $F(x)$ for a number $x$ ?}
-where $F(x)$ is an effective free energy at temperature $x$.
-If we attempt to push this to the present setting, the presence of Wigner negativity would correspond to a divergence in the first derivative of this effective free energy as $x \rightarrow T$.
-One might speculate if the presence of magic in Clifford circuits admits a sensible interpretation in terms of a zeroth-order phase transition.
-However since variation in $\alpha$ is no longer smooth ($\alpha$ is restricted to a dense set of rational values) technical obstacles exist and we do not pursue this speculative line here, but just note that other works exist in which computational transitions are considered in relation to phase transitions~\cite{Allahverdyan_2018, arvidsson_2020, halpern_2018, Lostaglio_2018, Levy_2020} \nick{I don't understand this statement, so I just dropped all citations on quasi-distributions here}.
-
-Every entropy is best understood as a relative entropy~\cite{Gour_2020} and so we now state the extension to Renyi divergences.
-We define the $\alpha$--Renyi Wigner divergence $D_\alpha(\p||\r)$ as
+with $\epsilon \rightarrow 0^+$ through a sequence of rational values.
+However we recall that mana is defined as $\M(\rho) = \log \sum_{\x} |W_\rho(\x)|$, and so we obtain a second new description of mana:
+\begin{equation}
+\M(\rho) = \lim_{\epsilon \rightarrow 0^+} \epsilon H_{1-\epsilon}(W_\rho).
+\end{equation}
+Therefore, up to a factor $2\pi i$, the mana of a state $\rho$ is the residue of a pole in $H_\alpha(W_\rho)$, and quantifies \emph{the divergence of the Renyi-entropy} as we approach the limiting Shannon entropy $H(W_\rho)$.
+
+We also note that the Renyi entropy can be described as a $q$--deformation of the Shannon entropy~\cite{baez2011renyi}, and $H_\alpha(\p)$ can be related to the $q$--derivative of free energy.
+For this, the Renyi parameter becomes a temperature term $\alpha = \frac{T_0}{T}$ where $T_0$ is a reference temperature and derivatives are considered via the limit $T \rightarrow T_0$.
+Therefore, if we try to push this to the present setting, the presence of Wigner negativity would correspond to a divergence in the first derivative of an effective free energy as $T \rightarrow T_0$.
+We can therefore speculate whether the presence of magic in Clifford circuits admits a sensible interpretation in terms of a zeroth-order phase transition [\ddd{cite}].
+However since variation in $\alpha$ is no longer smooth ($\alpha$ is restricted to a dense set of rational values) technical obstacles exist and we do not pursue this speculative line here, but just note that other works exist in which computational transitions are considered in relation to phase transitions [\ddd{cite}].
+
+Every entropy can be obtained from a relative entropy~\cite{Gour_2020} and so we now state the extensions for Renyi divergences of Wigner distributions.
+The $\alpha$--Renyi divergence $D_\alpha(\p||\r)$ is defined as
 \begin{equation}
@@
 where $\p$ can be a quasi-distribution, $\r$ a probability distribution with positive components and $\alpha$ can take the same values as for $H_\alpha$.
-In~\cref{app:lcst_technical}, we also show that the divergence satisfies the following natural properties for all $\alpha$ for which it is well-defined.
+In~\cref{app:lcst_technical}, we also show that the divergence satisfies the following.
 
@@
 The upper bound can be numerically minimized over $\alpha$, for any $\epsilon$.
-\begin{figure}[t!]
-    \centering
-    \subfigure[][]{%
-    \label{fig:Ra}%
-    \includegraphics[scale=0.4]{figs/Ra_vs_a_eps.pdf}}\\
-    \subfigure[][]{%
-    \label{fig:RaDiff}%
-    \includegraphics[scale=0.4]{figs/RaDiff_vs_a_eps.pdf}}
-    \caption{$R_\alpha$ and $R_\alpha - R_{\infty}$ for the Strange state distillation for unital protocols
-    \nick{Can compare thauma and mana for other magic states now more easily}}
-    \label{fig:rate_a_contour}
-\end{figure}
+%
+%\begin{figure}[t!]
+%    \centering
+%    \subfigure[][]{%
+%    \label{fig:Ra}%
+%    \includegraphics[scale=0.4]{figs/Ra_vs_a_eps.pdf}}\\
+%    \subfigure[][]{%
+%    \label{fig:RaDiff}%
+%    \includegraphics[scale=0.4]{figs/RaDiff_vs_a_eps.pdf}}
+%    \caption{$R_\alpha$ and $R_\alpha - R_{\infty}$ for the Strange state distillation for unital protocols
+%    \nick{Can compare thauma and mana for other magic states now more easily}}
+%    \label{fig:rate_a_contour}
+%\end{figure}
 
@@
 Our bounds exploited relatively simple aspects of the Lorenz curves of the quasi-distributions, so it would be of interest to sharpen these bounds and obtain a better handle on the Lorenz curve structure in the $n\rightarrow \infty$ limit.
-This raises interesting questions in the context of statistical mechanics as we no longer have a notion of typicality and the central limit theorem does not apply.
+It would also be of interest to analyse what features of single-shot entropies can be extended to quasi-distributions in a sensible form [\ddd{cite}].
+This raises interesting questions as we no longer have a notion of typicality and the central limit theorem does not apply.
 That said, for special states such as the Strange state, the asymptotic behaviour is relatively simple, so exact asymptotics for this should be possible.
@@
 Physically, this regime would correspond to a form of thermo-majorization obtained from looking at the action of the Clifford group at a micro-canonical level, and then reducing to a small subsystem~\cite{cit:lostaglio, Pathria_1997}.
-While this might seem like a painful thing to consider, there is motivation for this beyond the aim of simply constructing lower bounds for magic protocols: in the case of statistical mechanics on a phase space this is precisely the situation, albeit in the continuum limit.
+While this seems like a painful thing to consider, there is motivation for this beyond the aim of magic protocols: in the case of statistical mechanics on a phase space this is precisely the situation, albeit in the continuum limit.
 Statistical mechanics of actual systems obey Hamiltonian dynamics and so automatically respect a symplectic form~\cite{Pathria_1997}.
-Therefore, the pre-order of statistical mechanical states with respect to phase space dynamics preserving a Gibbs state must correspond to a symplectic thermo-majorization condition.
+Therefore, the pre-order of statistical mechanical states with respect to phase space dynamics preserving a Gibbs state must correspond to a symplectic majorization condition.
 Of course, technical features arise in the continuum limit when considering distributions on an unbounded phase space, but this could be remedied by either considering a compact phase space (e.g.
 for a particle on a ring) or by first studying the discrete case.
-Such scenarios also arise in the Quantum Hall Effect~\cite{Klitzing_1980}, which is thus another regime where these techniques could be of use.
-
-Lastly, we note that it would be of interest to consider the possibility of applying the approach taken here to other scenarios in which one wishes to distinguish classical from non-classical behaviour based on quasi-probability representations~\cite{Ferrie_2008, barnett_1997}
+Such scenarios also arise in the Quantum Hall Effect~\cite{Klitzing_1980}, which is another regime where these techniques could be of use.
+
+Lastly, we note that it would be of interest to consider the possibility of applying the approach taken here to other scenarios in which one wishes to distinguish classical from non-classical behaviour based on quasi-probability representations~\cite{Ferrie_2008, barnett_1997,Allahverdyan_2018, arvidsson_2020, halpern_2018, Lostaglio_2018, Levy_2020}
 \section{Acknowledgements}
@@
 
-Let each qutrit have a Hamiltonian $H$ with energies $E_0, E_1, E_2$ and stabilizer eigenstates, and define $E_{\rm max} = \max\{E_0, E_1, E_2\}$ and \nick{$E_s$ as the eigenvalue of the Hamiltonian eigenstate whose Wigner distribution overlaps the negative component of $\rho_S(\epsilon)$ in the phase space.}
+Let each qutrit have a Hamiltonian $H$ with energies $E_0, E_1, E_2$ and stabilizer eigenstates, and define $E_{\rm max} = \max\{E_0, E_1, E_2\}$ and $E_s$ as the eigenvalue of the Hamiltonian eigenstate whose Wigner distribution overlaps the negative component of $\rho_S(\epsilon)$ in the phase space.
 Let $T =(k\beta)^{-1}$ be any finite temperature and assume that in the thermodynamic limit ($n,m \gg 1$), the protocol applied to the equilibrium state $\tau^{\otimes n} = (e^{-\beta H}/\Z)^{\otimes n}$ maps $\tau^{\otimes n} \longrightarrow \tau^{\prime \otimes m}$, where we express state $\tau'$ as $\tau' = e^{-\beta H'}/\Z'$ for some Hermitian $H'$.
@@
 
-\nick{Explain why this is not Clifford processing, ensure overlap with negativity is the one suggested}
 The equilibrium state at inverse temperature $\beta$ on a single qutrit is given by $\tau = e^{-\beta H} / \Z$.
@@
     \centering
-    \includegraphics[scale=0.45]{figs/pd_split_thermal.pdf}
+    \includegraphics[scale=0.35]{figs/pd_split_thermal.pdf}
     \caption{\textbf{Qutrit phase space regions for $W_{\rho | \tau}(\x)$.}
@@
     \centering
-    \includegraphics[scale=0.35]{figs/test/H_vs_eps_a.pdf}
+    \includegraphics[scale=0.3]{figs/test/H_vs_eps_a.pdf}
     \caption{Here, the exponent is $\alpha =$ even$/$odd for $1.10 \leq \alpha \leq 1.50$.
@@
     \centering
-    \includegraphics[scale=0.35]{figs/test/D_vs_eps_a.pdf}
-    \caption{Here, the exponent is $\alpha =$ even$/$odd for $1.10 \leq \alpha \leq 1.50$. $D_\alpha$ is decreasing in $\alpha$ and $\epsilon$ (clear due to~\cref{thm:H2D}).
+    \includegraphics[scale=0.3]{figs/test/D_vs_eps_a.pdf}
+    \caption{Here, the exponent is $\alpha =$ even$/$odd for $1.10 \leq \alpha \leq 1.50$. $D_\alpha$ is decreasing in $\alpha$ and $\epsilon$ (\cref{thm:H2D}).
     }
@@
 
-\nick{
-If $\alpha =$ odd$/$odd, then $H_\alpha$ is not well-defined for all quasi-probabilities.
-
-If $\alpha =$ even$/$odd and $\alpha < 1$, then $f(w) := \frac{-w^{\alpha-1}}{\alpha-1}$ diverges at $0$ with $\lim_{w\rightarrow 0^-} = -\infty$ and $\lim_{w\rightarrow 0^+} = +\infty$.\\
-Example: If $\alpha = 2/3$, then $f(-2/3) = -3.43$, $f(-1/3) = -4.33$ and $f(+1/3) = +4.33$, so $f(w)$ is nether non-increasing nor non-decreasing.
-}
-
 Therefore, whenever $w_i \geq w_j$, we have that 
@@
 \end{proof}
-The set $F := \{2a/(2b-1): a,b \in \mathbb{N} \text{ and } a \geq b\}$ is dense in the rationals $\mathbb{Q}_{>1}$, and hence the reals $\mathbb{R}_{>1}$, as any rational $c/d$ with $c>d$ can be approximated by  $c2^n / (d2^n-1) \in F$ for suficiently large $n$.
+We note that if $\alpha =a/b$ with both $a$ and $b$ odd, then $H_\alpha$ is not well-defined for all quasi-probabilities, however if the actual set of quasi-distributions has bounded negativity then $\log \sum_{\x} W_\rho(\x)^\alpha$ can still be obtained for $a$ odd, provided the sum is never negative.
+
+If $\alpha =2a/(2b-1)$ with $\alpha < 1$, then $f(w) := \frac{-w^{\alpha-1}}{\alpha-1}$ is not monotonic.
+For example: If $\alpha = 2/3$, then $f(-2/3) = -3.43$, $f(-1/3) = -4.33$ and $f(+1/3) = +4.33$.
+Finally, we note that the set $F := \{2a/(2b-1): a,b \in \mathbb{N} \text{ and } a \geq b\}$ is dense in the reals $\mathbb{R}_{>1}$, as any rational $c/d$ with $c>d$ can be approximated by  $c2^n / (d2^n-1) \in F$ for suficiently large $n$.
 

### 2021-06-11 magic_paper.tex
minor changes

@@
 
-%\iffalse
-%\begin{figure}[t!]
-%    \centering
-%    \includegraphics[scale=0.4]{figs/rate_scatter.pdf}
-%    \caption{\textbf{Temperature-dependent bounds for magic distillation.}
-%  Shown is a contour plot of the bound on $R(\epsilon, \beta)$ for $H = H' = \sum_{k \in \mathbb{Z}_3} k |k\>\<k|$ and $\epsilon' = 0$, where $\beta$ is the inverse temperature and $\epsilon$ the depolarising error of the input magic state.
+\iffalse
+\begin{figure}[t!]
+    \centering
+    \includegraphics[scale=0.4]{figs/rate_scatter.pdf}
+    \caption{\textbf{Temperature-dependent bounds for magic distillation.}
+  Shown is a contour plot of the bound on $R(\epsilon, \beta)$ for $H = H' = \sum_{k \in \mathbb{Z}_3} k |k\>\<k|$ and $\epsilon' = 0$, where $\beta$ is the inverse temperature and $\epsilon$ the depolarising error of the input magic state.
 The relevant data from the spectrum of the qutrit operator $H$ enters in via $\epsilon_\star(\beta)$ and $\beta_\star$.
@@
 \nick{Refer to definitions of starred quantities} The $\beta = 0$ line corresponds to the regime in which the magic protocol corresponds to a unital channel.
-%    }
-%    \label{fig:rate_contour}
-%\end{figure}
-%\fi
+    }
+    \label{fig:rate_contour}
+\end{figure}
+\fi
 
@@
 with $\epsilon \rightarrow 0^+$ through a sequence of rational values.
-However we recall that mana is defined as $\M(\rho) = \log \sum_{\x} |W_\rho(\x)|$, and so we obtain a second new description of mana:
+We now recall that mana is defined as $\M(\rho) = \log \sum_{\x} |W_\rho(\x)|$, and so we obtain a second new description of mana:
 \begin{equation}
@@
 \end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Details for the derivation of distillation bounds from Lorenz curves}
@@
 The equilibrium state at inverse temperature $\beta$ on a single qutrit is given by $\tau = e^{-\beta H} / \Z$.
-Moreover we have that $\tau$ is a full-rank stabilizer state, where $\beta \geq 0$ and $H = E_0 |\varphi_0\>\<\varphi_0| + E_1 |\varphi_1\>\<\varphi_1| + E_2 |\varphi_2\>\<\varphi_2|$ is an eigendecomposition of $H$.
+Moreover, we have that $\tau$ is a full-rank stabilizer state, where $\beta \geq 0$ and $H = E_0 |\varphi_0\>\<\varphi_0| + E_1 |\varphi_1\>\<\varphi_1| + E_2 |\varphi_2\>\<\varphi_2|$ is an eigendecomposition of $H$.
 The state $\tau$ can now be written as 
@@
 Therefore, $C$ maps $\tau$ to another stabilizer state that is diagonal in the computational basis, and we can assume without loss of generality that $\tau$ is diagonal in $\{|0\>,|1\>, |2\>\}$.
-However, this re-definition of the computational basis means that the location of the negative Wigner component $-v(\epsilon)$ of the Strange state will be permuted on the discrete phase space.
-We denote by $E_s$ the eigenvalue of $H$ where the associated eigenvector has Wigner distribution overlapping the negative component of the magic state $C\rho_S(\epsilon)C^\dagger$.
-This is unique, since the eigenstates form an orthonormal basis.
+However, this re-definition of the computational basis means that the coordinates on the discrete phase space are also permuted, so the negative Wigner component $-v(\epsilon)$ of the Strange state is in a new position.
+We denote by $E_s$ the eigenvalue of $H$ where the associated eigenvector has Wigner distribution overlapping the negative component of the state $C\rho_S(\epsilon)C^\dagger$ in the original phase space, hence also of the state Strange state $\rho_S(\epsilon)$ in the re-defined phase space.
+The eigenvalue $E_s$ is unique, since the eigenstates form an orthonormal basis.
 
@@
 For example: If $\alpha = 2/3$, then $f(-2/3) = -3.43$, $f(-1/3) = -4.33$ and $f(+1/3) = +4.33$.
-Finally, we note that the set $F := \{2a/(2b-1): a,b \in \mathbb{N} \text{ and } a \geq b\}$ is dense in the reals $\mathbb{R}_{>1}$, as any rational $c/d$ with $c>d$ can be approximated by  $c2^n / (d2^n-1) \in F$ for suficiently large $n$.
+Finally, we note that the set $F := \{2a/(2b-1): a,b \in \mathbb{N} \text{ and } a \geq b\}$ is dense in the reals $\mathbb{R}_{>1}$, as any rational $c/d$ with $c>d$ can be approximated by  $c2^n / (d2^n-1) \in F$ for sufficiently large $n$.
 

### 2021-06-16 magic_paper.tex
minor changes

@@
 While traditional free energy is not defined in the presence of negativity, we show that majorization allows us to both quantify disorder in the Wigner representation and derive magic distillation bounds.
-These upper bounds are shown to be tighter than other bounds, such from mana and thauma, and moreover incorporate hardware physics, such as temperature dependence and physical Hamiltonians.
+These upper bounds are shown to be tighter than other bounds, such as mana and thauma, and moreover incorporate hardware physics, such as temperature dependence and physical Hamiltonians.
 We also show that a sub-set of single-shot Renyi entropies remain well-defined on quasi-distributions, are fully meaningful in terms of data processing and can acquire negative values.
@@
 \begin{align*}
-	\bmx \coloneqq (x_1, p_1, x_2, p_2, \dots, x_n, p_n) \in \cal{P}_{d_1} \times \dots \times \cal{P}_{d_n} \eqqcolon  \cal{P}_d,
+	\bmx &\coloneqq (x_1, p_1, x_2, p_2, \dots, x_n, p_n) \in \cal{P}_{d_1} \times \dots \times \cal{P}_{d_n} \eqqcolon  \cal{P}_d, \\
+	&\nick{= (x_1, x_2, \dots, x_n, p_1, p_2, \dots, p_n) ?}
 \end{align*}
@@
     \centering
-    \includegraphics[scale=0.4]{figs/test/R_vs_A.pdf}
+    \includegraphics[scale=0.4]{figs/R_vs_A.pdf}
     \caption{\textbf{Variation of distillation bounds with Hamiltonian.} We consider $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$, and look at a family of Hamiltonians for the qutrit systems, given by $H = A_{\bmo}$ and $H' = (1-p-q)A_{\bmo}+pA_{(1,2)}+q{\rm{diag}}(0,1,2)$.
@@
 
-However, it turns out that the analysis for the temperature-dependent bound given by Equation (\ref{eq:rate_bounds_proof}) implicitly made use of the single-shot Renyi divergence $D_\infty (\p ||\r)$, which is given by
-\begin{equation}
-D_\infty (\p ||\r) = \log \max_i \frac{p_i}{r_i}.
+However, it turns out that the analysis for the temperature-dependent bound given by Equation (\ref{eq:rate_bounds_proof}) implicitly made use of the single-shot Renyi divergence $D_\infty (\p \hspace{1pt}||\hspace{1pt} \r)$, which is given by
+\begin{equation}
+	D_\infty (\p \hspace{1pt}||\hspace{1pt} \r) = \log \max_i \frac{p_i}{r_i}.
 \end{equation}
@@
 \begin{enumerate}
-\item $D_\infty(W_\rho || W_\tau) \ge 0$ for all quantum states $\rho$.
-\item  $D_\infty(W_\rho || W_\tau) = 0$ if and only if $\rho =\tau$.
-\item $D_\infty(W_{\rho^{\otimes 2n}}|| W_{\tau^{\otimes 2n}}) = n D_\infty(W_{\rho^{\otimes 2}} ||W_{\tau^{\otimes 2}})$ for any $n \in \mathbb{N}$.
-\item $D_\infty(W_\rho || W_\tau) \geq D_\infty(W_{\E(\rho)} || W_{\E(\tau)})$ for any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$.
+\item $D_\infty(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) \ge 0$ for all quantum states $\rho$.
+\item  $D_\infty(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) = 0$ if and only if $\rho =\tau$.
+\item $D_\infty(W_{\rho^{\otimes 2n}} \hspace{1pt}||\hspace{1pt} W_{\tau^{\otimes 2n}}) = n D_\infty(W_{\rho^{\otimes 2}} \hspace{1pt}||\hspace{1pt} W_{\tau^{\otimes 2}})$ for any $n \in \mathbb{N}$.
+\item $D_\infty(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) \geq D_\infty(W_{\E(\rho)} \hspace{1pt}||\hspace{1pt} W_{\E(\tau)})$ for any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$.
 \end{enumerate}
@@
 \begin{equation}
-H_{1-\epsilon}(W_\rho) = -\epsilon^{-1} \log \sum_{\x} |W_\rho (\x)|^{1+\epsilon}
+	H_{1+\epsilon}(W_\rho) = -\epsilon^{-1} \log \sum_{\x} |W_\rho (\x)|^{1+\epsilon}
 \end{equation} 
@@
 However since variation in $\alpha$ is no longer smooth ($\alpha$ is restricted to a dense set of rational values) technical obstacles exist and we do not pursue this speculative line here, but just note that other works exist in which computational transitions are considered in relation to phase transitions [\ddd{cite}].
+\nick{Do you know what you want to cite in this paragraph?}
 
@@
 \begin{equation}
-	D_\alpha(\p || \r) := \frac{1}{\alpha-1} \log \sum_i p_i^\alpha r_i^{1-\alpha},
+	D_\alpha(\p \hspace{1pt}||\hspace{1pt} \r) := \frac{1}{\alpha-1} \log \sum_i p_i^\alpha r_i^{1-\alpha},
 \end{equation}
@@
 \begin{enumerate}
-\item $D_\alpha(W_\rho || W_\tau) \ge 0$ for all quantum states $\rho$.
-\item  $D_\alpha(W_\rho || W_\tau) = 0$ if and only if $\rho =\tau$.
-\item $D_\alpha(W_{\rho^{\otimes n}} || W_{\tau^{\otimes n}}) = n D_\alpha(W_\rho || W_\tau)$ for any $n \in \mathbb{N}$.
-\item $D_\alpha(W_\rho || W_\tau) \geq D_\alpha (W_{\E(\rho)} || W_{\E(\tau)})$ for any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$.
+\item $D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) \ge 0$ for all quantum states $\rho$.
+\item  $D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) = 0$ if and only if $\rho =\tau$.
+\item $D_\alpha(W_{\rho^{\otimes n}} \hspace{1pt}||\hspace{1pt} W_{\tau^{\otimes n}}) = n D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)$ for any $n \in \mathbb{N}$.
+\item $D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) \geq D_\alpha (W_{\E(\rho)} \hspace{1pt}||\hspace{1pt} W_{\E(\tau)})$ for any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$.
 \end{enumerate}
@@
 	\end{equation}
-	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ and $\beta F_\alpha(W_\rho) := D_\alpha (W_\rho || W_\tau) - \log \Z$ is the $\alpha$--free energy of the Wigner distribution.
+	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ and $\beta F_\alpha(W_\rho) := D_\alpha (W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) - \log \Z$ is the $\alpha$--free energy of the Wigner distribution.
 \end{theorem}
@@
 Our bounds exploited relatively simple aspects of the Lorenz curves of the quasi-distributions, so it would be of interest to sharpen these bounds and obtain a better handle on the Lorenz curve structure in the $n\rightarrow \infty$ limit.
-It would also be of interest to analyse what features of single-shot entropies can be extended to quasi-distributions in a sensible form [\ddd{cite}].
+It would also be of interest to analyse what features of single-shot entropies can be extended to quasi-distributions in a sensible form [\ddd{cite}] \nick{and here?}.
 This raises interesting questions as we no longer have a notion of typicality and the central limit theorem does not apply.
@@
     \centering
-    \includegraphics[scale=0.3]{figs/test/H_vs_eps_a.pdf}
+    \includegraphics[scale=0.3]{figs/H_vs_eps_a.pdf}
     \caption{Here, the exponent is $\alpha =$ even$/$odd for $1.10 \leq \alpha \leq 1.50$.
@@
     \centering
-    \includegraphics[scale=0.3]{figs/test/D_vs_eps_a.pdf}
+    \includegraphics[scale=0.3]{figs/D_vs_eps_a.pdf}
     \caption{Here, the exponent is $\alpha =$ even$/$odd for $1.10 \leq \alpha \leq 1.50$. $D_\alpha$ is decreasing in $\alpha$ and $\epsilon$ (\cref{thm:H2D}).
@@
 \begin{equation}
-	\frac{\partial H_\alpha}{\partial w_i} = \frac{\alpha}{(\alpha-1)\sum_k{w_k^\alpha}}(-w_i^{\alpha-1}).
+	\frac{\partial H_\alpha}{\partial w_i} = \frac{\alpha}{(\alpha-1)\sum_k{w_k^\alpha}}\left( -w_i^{\alpha-1} \right).
 \end{equation}
@@
 \end{equation}
-We then show that for $\alpha$ in the given form, the function $f(w) = -w^{\alpha - 1}$ is non-increasing.
-To this end, we first note that, for $\alpha > 1$, $f(w)$ has no discontinuities and we then obtain the first derivative
+We then show that for $\alpha$ in the given form, the function $f(w) := -w^{\alpha - 1}$ is non-increasing.
+To this end, we first note that, for $\alpha > 1$, $f(w)$ has no discontinuities and we can obtain the first derivative
 \begin{equation}
@@
 \begin{equation}
-	w^{\frac{2a-4b+2}{2b-1}} = \left(w^{2a-4b+2}\right)^{\frac{1}{2b-1}} = \left(w^{\frac{1}{2b-1}}\right)^{2(a-2b+1)} \geq 0,
+	w^{\frac{2a-4b+2}{2b-1}} = \left(w^{2a-4b+2}\right)^{\frac{1}{2b-1}} = \left(w^{\frac{a-2b+1}{2b-1}}\right)^{2} \geq 0,
 \end{equation}
@@
 \end{proof}
-We note that if $\alpha =a/b$ with both $a$ and $b$ odd, then $H_\alpha$ is not well-defined for all quasi-probabilities, however if the actual set of quasi-distributions has bounded negativity then $\log \sum_{\x} W_\rho(\x)^\alpha$ can still be obtained for $a$ odd, provided the sum is never negative.
+We note that if $\alpha =a/b$ with both $a$ and $b$ odd, then $H_\alpha$ is not well-defined for all quasi-probabilities, however if the actual set of quasi-distributions has a sufficiently bounded negativity, then $\log \sum_{\x} W_\rho(\x)^\alpha$ can still be obtained for $a$ odd, provided the sum is never negative.
 
 If $\alpha =2a/(2b-1)$ with $\alpha < 1$, then $f(w) := \frac{-w^{\alpha-1}}{\alpha-1}$ is not monotonic.
-For example: If $\alpha = 2/3$, then $f(-2/3) = -3.43$, $f(-1/3) = -4.33$ and $f(+1/3) = +4.33$.
+For example, if $\alpha = 2/3$, then $f(-2/6) = -4.33$, $f(-1/6) = -5.45$ and $f(+2/6) = +4.33$.
 Finally, we note that the set $F := \{2a/(2b-1): a,b \in \mathbb{N} \text{ and } a \geq b\}$ is dense in the reals $\mathbb{R}_{>1}$, as any rational $c/d$ with $c>d$ can be approximated by  $c2^n / (d2^n-1) \in F$ for sufficiently large $n$.
@@
 \begin{equation}
-	D_\alpha(W_\rho || W_\tau) := \frac{1}{\alpha - 1} \log \sum_{\bmx} W_{\rho}(\bmx)^\alpha W_{\tau}(\bmx)^{1-\alpha},
+	D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) := \frac{1}{\alpha - 1} \log \sum_{\bmx} W_{\rho}(\bmx)^\alpha W_{\tau}(\bmx)^{1-\alpha},
 \end{equation}
@@
 	\begin{equation}
-		H_\alpha(\Gamma_{\bma}(\w)) = K - D_\alpha(\w ||\r),
+		H_\alpha(\Gamma_{\bma}(\w)) = K - D_\alpha(\w \hspace{1pt}||\hspace{1pt} \r),
 	\end{equation}
@@
 \begin{proof}
-	For the given form of $\alpha$ and positive $r_i,\ i=1,\dots,N$, $D_\alpha(\x ||\r)$ is well-defined for all $\x$.
+	For the given form of $\alpha$ and positive $r_i,\ i=1,\dots,N$, $D_\alpha(\x \hspace{1pt}||\hspace{1pt} \r)$ is well-defined for all $\x$.
 
@@
 	Let $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$. 
-	Then, $D_\alpha$ is Schur-convex, i.e. $D_\alpha(\w || \r) \geq D_\alpha(\w' || \r')$, whenever $(\w, \r) \succ (\w', \r')$.
+	Then, $D_\alpha$ is Schur-convex, i.e. $D_\alpha(\w \hspace{1pt}||\hspace{1pt} \r) \geq D_\alpha(\w' \hspace{1pt}||\hspace{1pt} \r')$, whenever $(\w, \r) \succ (\w', \r')$.
 \end{theorem}
@@
 	\begin{equation}
-		D_\alpha(\w ||\r) \geq D_\alpha(\w' ||\r').
+		D_\alpha(\w \hspace{1pt}||\hspace{1pt} \r) \geq D_\alpha(\w' \hspace{1pt}||\hspace{1pt} \r').
 	\end{equation}
@@
 	Let $\tau$ be a state in the interior of $\F$ and $\alpha = 2a / (2b-1)$ for non-negative integers $a,b$ with $a \geq b$.
-Then, the $\alpha$-Renyi divergence $D_\alpha(W_\rho || W_\tau)$ is well-defined for all states $\rho$, and the following hold:
+Then, the $\alpha$-Renyi divergence $D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)$ is well-defined for all states $\rho$, and the following hold:
 \begin{enumerate}
-\item $D_\alpha(W_\rho || W_\tau) \ge 0$ for all quantum states $\rho$.
-\item  $D_\alpha(W_\rho || W_\tau) = 0$ if and only if $\rho =\tau$.
-\item $D_\alpha(W_{\rho^{\otimes n}} || W_{\tau^{\otimes n}}) = n D_\alpha(W_\rho || W_\tau)$ for any $n \in \mathbb{N}$.
-\item $D_\alpha(W_\rho || W_\tau) \geq D_\alpha (W_{\E(\rho)} || W_{\E(\tau)})$ for any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$.
+\item $D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) \ge 0$ for all quantum states $\rho$.
+\item  $D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) = 0$ if and only if $\rho =\tau$.
+\item $D_\alpha(W_{\rho^{\otimes n}} \hspace{1pt}||\hspace{1pt} W_{\tau^{\otimes n}}) = n D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)$ for any $n \in \mathbb{N}$.
+\item $D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) \geq D_\alpha (W_{\E(\rho)} \hspace{1pt}||\hspace{1pt} W_{\E(\tau)})$ for any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$.
 \end{enumerate}
@@
 \begin{align}
-	D_\alpha(W_{\rho} || W_{\tau}) \geq D_\alpha(W_{\rho'} || W_{\rho'}) &= \nonumber\\
+	D_\alpha(W_{\rho} \hspace{1pt}||\hspace{1pt} W_{\tau}) \geq D_\alpha(W_{\rho'} \hspace{1pt}||\hspace{1pt} W_{\rho'}) &= \nonumber\\
 	\frac{1}{\alpha-1} \log \sum_{\bmx} W_{\rho'}(\bmx) &= 0.
@@
 \begin{align}
-	&D_\alpha(W_{\rho^{\otimes n}} || W_{\tau^{\otimes n}}) = \nonumber\\
+	&D_\alpha(W_{\rho^{\otimes n}} \hspace{1pt}||\hspace{1pt} W_{\tau^{\otimes n}}) = \nonumber\\
 	&\frac{1}{\alpha - 1} \log \sum_{\bmx} W_{\rho^{\otimes n}}(\bmx)^\alpha W_{\tau^{\otimes n}}(\bmx)^{1-\alpha} = \nonumber\\
@@
 	&\sum_{i=1}^n \frac{1}{\alpha - 1} \log \sum_{\bmx'} W_{\rho}(\bmx')^\alpha W_{\tau}(\bmx')^{1-\alpha} = \nonumber\\
-	&= n D_{\alpha}(W_\rho || W_\tau).
+	&= n D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau).
 \end{align}
@@
 	\begin{equation}
-		R \leq \frac{D_{\alpha}(W_\rho||W_\tau)}{D_{\alpha}(W_{\rho'}||W_{\tau'})} = \frac{F_\alpha(W_\rho) - F_\alpha(W_\tau)}{F_\alpha(W_{\rho'}) - F_\alpha(W_{\tau'})},
-	\end{equation}
-	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ and $\beta F_\alpha(W_\rho) := D_\alpha (W_\rho || W_\tau) - \log \Z$ is the $\alpha$--free energy. 
+		R \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{D_{\alpha}(W_{\rho'} \hspace{1pt}||\hspace{1pt} W_{\tau'})} = \frac{F_\alpha(W_\rho) - F_\alpha(W_\tau)}{F_\alpha(W_{\rho'}) - F_\alpha(W_{\tau'})},
+	\end{equation}
+	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ and $\beta F_\alpha(W_\rho) := D_\alpha (W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) - \log \Z$ is the $\alpha$--free energy.
 \end{theorem}
@@
 \begin{equation}	
-	D_\alpha(W_{\rho^{\otimes n}} || W_{\tau^{\otimes n}}) \geq D_\alpha (W_{\rho'^{\otimes m}} || W_{\tau'^{\otimes m}}).\vspace{10pt}
+	D_\alpha(W_{\rho^{\otimes n}} \hspace{1pt}||\hspace{1pt} W_{\tau^{\otimes n}}) \geq D_\alpha (W_{\rho'^{\otimes m}} \hspace{1pt}||\hspace{1pt} W_{\tau'^{\otimes m}}).\vspace{10pt}
 \end{equation}
@@
 \begin{equation}
-	n D_\alpha(W_\rho || W_\tau) \geq m D_\alpha(W_{\rho'} || W_{\tau'}).
-\end{equation}
-
-Since $\rho' \neq \tau'$, we have $D_\alpha(W_{\rho'} || W_{\tau'}) > 0$, which directly leads to the bound
-\begin{equation}
-	\frac{m}{n} \leq \frac{D_{\alpha}(W_\rho||W_\tau)}{D_{\alpha}(W_{\rho'}||W_{\tau'})}.
+	n D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) \geq m D_\alpha(W_{\rho'} \hspace{1pt}||\hspace{1pt} W_{\tau'}).
+\end{equation}
+
+Since $\rho' \neq \tau'$, we have $D_\alpha(W_{\rho'} \hspace{1pt}||\hspace{1pt} W_{\tau'}) > 0$, which directly leads to the bound
+\begin{equation}
+	\frac{m}{n} \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{D_{\alpha}(W_{\rho'} \hspace{1pt}||\hspace{1pt} W_{\tau'})}.
 \end{equation}

### 2021-06-22 magic_paper.tex
Overview of results bit added. Edits throughout in light of comments from people. References to be added still.

@@
 While traditional free energy is not defined in the presence of negativity, we show that majorization allows us to both quantify disorder in the Wigner representation and derive magic distillation bounds.
-These upper bounds are shown to be tighter than other bounds, such as mana and thauma, and moreover incorporate hardware physics, such as temperature dependence and physical Hamiltonians.
-We also show that a sub-set of single-shot Renyi entropies remain well-defined on quasi-distributions, are fully meaningful in terms of data processing and can acquire negative values.
+These upper bounds are shown to be tighter than other bounds, such as from mana and thauma, and can incorporate hardware physics, such as temperature dependence and physical Hamiltonians.
+We also show that a sub-set of single-shot Renyi entropies remain well-defined on quasi-distributions, are fully meaningful in terms of data processing and can acquire negative values that signal magic.
 We show that the mana of a magic state is the measure of divergence of these Renyi entropies as one approaches the Shannon entropy for Wigner distributions, and discuss how distillation lower bounds could be obtained in this setting.
@@
 
-With this approach, we obtain a range of upper bounds for magic distillation rates.
-We provide explicit bounds for magic protocols that generate unital channels, as well as bounds that depend on the temperature and Hamiltonian of the system.
-These bounds are shown to be tighter than other bounds such as from mana and thauma.
-We find that the thermodynamic ordering in the presence of negativity is non-trivial and displays a range of features that, unsurprisingly, do not appear in classical statistical mechanics.
-We show that Wigner negativity in a quantum circuit can be described as a non-classical free energy that is processed under stochastic maps.
-We also show that a subset of single-shot Renyi entropies can be sensibly extended to quasi-distributions, lead to improved distillation bounds, and show that the mana of a quantum state governs the rate of divergence of the Renyi entropies as we approach the (undefined) Shannon entropy.
-Finally, we discuss how our approach could be improved and how it can be exploited to construct explicit lower bounds on distillation that take into account physical structure.
-
+\subsection{Overview of our results}
+We begin by describing how stabilizer operations correspond to stochastic maps on a discrete phase space, and how majorization can be applied to constrain magic state transformations (Section~\ref{sec:ps}).
+We then consider families of magic protocols with increasing complexity.
+The simplest case we consider is for magic protocols that lead to unital channels (Section~\ref{sec:unital}).
+These are a sub-set of protocols that leave invariant some distinguished state or has some equilibrium fixed point (Section~\ref{sec:frag}).
+We then consider protocols that are non-equilibrium processes, but only generate sub-linear correlations that lead to a simple description in the thermodynamic limit (Section~\ref{sec:stab}).
+
+The relations between the sets of protocols considered are as follows:
+\begin{align}
+\mbox{Unital} \subset &\mbox{ local fixed-points} \nonumber\\ 
+& \subset \mbox{ sub-linear correlations} \subset \mbox{ general protocols.} \nonumber
+\end{align}
+
+We provide explicit bounds for magic protocols that generate unital channels (Equation~(\ref{eq:unital-bound})), as well as bounds that incorporate on the temperature and Hamiltonian of the system (Theorem~\ref{thm:free-energy}) and discuss extensions to more general scenarios.
+These bounds are shown to be tighter than other bounds such as those that come from mana and thauma (Section~\ref{sec:monotones_frag} and Figure~\ref{fig:distill_bounds}).
+
+We find that the analysis in the presence of negativity is non-trivial, displays a range of features that do not appear in classical statistical mechanics, and leads to a picture of Wigner negativity in a quantum circuit being described as non-classical free energy that is processed under stochastic dynamics.
+This is demonstrated by Lorenz curves having a non-trivial maximum related to mana (Section~\ref{sec:lc}) and by showing that single-shot entropies for general Wigner quasi-distributions are well-defined, obey data-processing under stabilizer operations and can take on negative values (Section~\ref{section:entropies}).
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[scale=0.35]{figs/distill_bounds.pdf}
+    \caption{\textbf{Magic distillation bounds from majorization of Wigner quasi-distributions.} The above plot shows distillation upper bounds for qutrits obtained from majorisation on unital protocols.
+The constraints are plotted as a function of the depolarizing noise level $\epsilon$ for a noisy Strange state.
+The bound $R_\infty$ follows from a Lorenz curve analysis, while the bound $R_{10}$ comes from single-shot entropies on the Wigner quasi-distributions, as discussed in Section~\ref{section:entropies}.
+Numerical bounds $R_{\rm{num}}$ are obtained by using the full set of majorization constraints.
+The new bounds $R_\infty$, $R_{10}$, $R_{\rm{num}}$ all provide stricter constraints than mana and max--thauma $\theta_{\rm{max}}$ bounds for noisy Strange states.
+    }
+    \label{fig:distill_bounds}
+\end{figure}
+
+We also show that the mana of a quantum state arises as a residue in the $\alpha$--parameter for Renyi entropies, and gives the rate of divergence to $-\infty$ as we approach the Shannon entropy of a Wigner distribution (Equation (\ref{eq:mana-divergence})).
+Finally, in Section~\ref{sec:lower_bounds} we discuss how our approach could be improved and how it can be exploited to construct explicit lower bounds on distillation that take into account physical constraints.
+
+\section{Phase space representations of quantum states}
+\label{sec:ps}
+
+Central to our construction is the representation of any quantum state or quantum operation on a system of dimension $d$ in terms of quasi-probability representations on a discrete phase space~\cite{Ferrie_2008}.
+This construction is a discrete version of Wigner representations in quantum optics~\cite{Wigner_1932, Vourdas_2004}.
+
+Consider a $d$--dimensional quantum system with Hilbert space $\H_d$, and let $\{ |0\>, |1\>, \dots , |d-1\>\}$ denote the standard computational basis, defined over $\mathbb{Z}_d = \{ 0, 1, \dots,d-1 \}$.
+On this space, generalised Pauli matrices $X, Z$ can be defined by their respective roles as shift and phase operators, acting on the basis states as follows,
+\begin{align}
+    X \ket{k} &= \ket{k + 1} \label{eq:xpauli}\\
+	Z \ket{k} &= \omega^k \ket{k}. \label{eq:zpauli}
+\end{align}
+Here $\omega \coloneqq e^{2\pi i/d}$ is the $d$-th root of unity and addition is taken modulo $d$.
+From these we can construct a phase space $\cal{P}_d = \mathbb{Z}_d \times \mathbb{Z}_d$ that provides a complete representation of the quantum system.
+\ddd{[Change $\x$ to $\z$ for phase space points?
+This also distinguishes from the $L_\rho(x)$ use of $x$.
+For multiple phase space points can use $\z_1, \z_2$.]} Given a point $\bmx \coloneqq (x, p)$ we define a displacement operator,
+\begin{equation}\label{eq:ddef}
+    D_{\bmx} \coloneqq \tau^{x p} X^{x} Z^{p},\ 
+\end{equation}
+where the phase factor $\tau \coloneqq -\omega^{1/2}$ ensures unitarity.
+We assume going forward that $d$ is an odd prime~\cite{Appleby_2005}.
+The qubit case $d=2$ is known to have obstacles to using a Wigner representation to quantify magic in terms of negativity \ddd{[Cite early papers highlighting this]}, although recent work \ddd{[Cite Raussendorf PRA 2020 qubit paper!!
+We can't miss such key papers!]} has shown how to extend this to include qubits by enlarging the phase space.
+For a composite system with dimension $d = d_1 \dots d_n$ we can decompose the Hilbert space as $\cal{H}_d = \cal{H}_{d_1} \otimes \dots \otimes \cal{H}_{d_n}$, and then define displacement operators as
+\begin{equation}\label{eq:composited}
+    D_{\bmx} \coloneqq D_{(x_1, p_1)} \otimes \dots \otimes D_{(x_n, p_n)},
+\end{equation}
+where now we have
+\begin{align*}
+	\bmx &\coloneqq (x_1, p_1, x_2, p_2, \dots, x_n, p_n) \in \cal{P}_{d_1} \times \dots \times \cal{P}_{d_n} \eqqcolon  \cal{P}_d,
+\end{align*}
+to denote the phase space point for the composite system. 
+For simplicity going forward, we assume $n$ copies of a $d$--dimensional system $d_1=d_2 = \cdots = d$, and therefore we have that $\x \in \mathbb{Z}_d^{2n}$.
+
+The displacement operators form the Heisenberg-Weyl group~\cite{Folland_1989, Bengtsson_2006} under matrix multiplication modulo phases,
+\begin{equation}\label{eq:gp}
+    {\rm{HW}}_d^n \coloneqq \{ \tau^k D_{\bmx}: k \in \mathbb{Z}_d, \bmx \in \cal{P}_d^n\}.
+\end{equation}
+The Clifford operations $ \cal{C}_d^n $ are then defined as the set of unitaries that normalise the Heisenberg-Weyl group~\cite{Appleby_2005}.
+We may define the pure stabiliser states as those states obtained by acting on $|0\>$ with Clifford unitaries~\cite{cit:gross3} and, finally, the full set of stabilizer states as the convex hull of all pure stabilisers, namely all probabilistic mixtures of states of the form $U|0\>\<0|U^\dagger$ where $U$ is Clifford.
+
+\subsection{Wigner representations for quantum states and quantum operations}\label{sec:wigner}
+
+In order to provide a complete decomposition of arbitrary quantum states and quantum operations we now define a complete basis of Hermitian observables that behaves naturally under the action of the Clifford group.
+At every point $\x \in \P_d$ we define the phase-point operator
+\begin{equation}\label{eq:ax}
+	A_{\bmx} \coloneqq \frac{1}{d} \sum_{\bmz \in \cal{P}_d} \omega^{\eta(\bmx, \bmz)} D_{\bmz}, 
+\end{equation}
+where $\eta(\bmx, \bmz)$ is the symplectic inner product between any two points $\x,\z \in \P_d$, and is given explicitly by
+\begin{equation}
+	\eta(\bmx, \bmz) \coloneqq \bmz^T \begin{pmatrix}
+		0  & \id \\ %\mathbbm{O}_n  & \id_n \\
+		-\id & 0 \\ %-\id_n & \mathbbm{O}_n \\
+	\end{pmatrix} \bmx,
+\end{equation}
+where $0, \id$ denote the $n\times n$ zero and identity matrices.
+
+The phase-point operators form an orthogonal operator basis with respect to the Hilbert-Schmidt inner product, as discussed in~\cref{app:wigner}.
+Therefore, any quantum state $\rho \in \cal{B}(\cal{H}_d)$ can be expressed as a linear combination of them, $\rho = \sum_{\bmz \in \cal{P}_d} \W[\bmz]{\rho} A_{\bmz}$, where the coefficient vector $\W{\rho}$ is the Wigner distribution of state $\rho$,
+\begin{equation}\label{eq:wstate}
+    \W[\bmx]{\rho} \coloneqq \frac{1}{d}\tr[A_{\bmx} \rho].
+\end{equation}
+
+For any quantum state $\rho$, the Wigner distribution $W_\rho(\bmx)$ is readily seen to be a $d^2$-dimensional quasi-probability distribution over $\cal{P}_d$.
+More precisely, $W_\rho(\x)$ is a bounded real-valued function on $\P_d$ with the normalisation property $\sum_{\x} W_\rho(\bmx) = 1$ (see~\cref{app:wigner} for details).
+
+Any quantum operation $\E$ can also admit a Wigner representation.
+If $\E$ maps some quantum system $A$ of dimension $d_A$ to a quantum system $B$ of dimension $d_B$, and $\J(\E)$ is its associated Choi state \ddd{[Cite Watrous book]} then we can define
+\begin{equation}
+W_{\E}(\y |\x) \coloneqq d_A^2 W_{\J(\E)}(\bar{\x} \oplus \y),
+\end{equation}
+where $\bar{x} =(x_1, -p_1, \dots , x_n, -p_n)$ can be viewed as the time-reversed version of $\x$ in the discrete phase space, where momenta are reflected while position coordinates remain unchanged.
+
+\subsection{Magic theories for quantum computation}
+\label{sec:mono}
 \begin{figure}[t]
@@
 \end{figure}
-
-\section{Phase space representations of quantum states}
-\label{sec:ps}
-
-Central to our construction is the representation of any quantum state or quantum operation on a system of dimension $d$ in terms of quasi-probability representations on a discrete phase space~\cite{Ferrie_2008}.
-This construction is a discrete version of Wigner representations in quantum optics~\cite{Wigner_1932, Vourdas_2004}.
-
-Consider a $d$--dimensional quantum system with Hilbert space $\H_d$, and let $\{ |0\>, |1\>, \dots , |d-1\>\}$ denote the standard computational basis, defined over $\mathbb{Z}_d = \{ 0, 1, \dots,d-1 \}$.
-On this space, generalised Pauli matrices $X, Z$ can be defined by their respective roles as shift and phase operators, acting on the basis states as follows,
-\begin{align}
-    X \ket{k} &= \ket{k + 1} \label{eq:xpauli}\\
-	Z \ket{k} &= \omega^k \ket{k}. \label{eq:zpauli}
-\end{align}
-Here $\omega \coloneqq e^{2\pi i/d}$ is the $d$-th root of unity and addition is taken modulo $d$.
-From these we can construct a phase space $\cal{P}_d = \mathbb{Z}_d \times \mathbb{Z}_d$ that provides a complete representation of the quantum system.
-Given a point $\bmx \coloneqq (x, p)$ we define a displacement operator,
-\begin{equation}\label{eq:ddef}
-    D_{\bmx} \coloneqq \tau^{x p} X^{x} Z^{p},\ 
-\end{equation}
-where the phase factor $\tau \coloneqq -\omega^{1/2}$ ensures unitarity.
-We assume going forward that $d$ is an odd prime, however the case $d=2$ can also be handled, but with some additional technical caveats~\cite{Appleby_2005}.
-For a composite system with composite dimension $d = d_1 \dots d_n$ we can decompose the Hilbert space as $\cal{H}_d = \cal{H}_{d_1} \otimes \dots \otimes \cal{H}_{d_n}$, and then define displacement operators as
-\begin{equation}\label{eq:composited}
-    D_{\bmx} \coloneqq D_{(x_1, p_1)} \otimes \dots \otimes D_{(x_n, p_n)},
-\end{equation}
-where now we have
-\begin{align*}
-	\bmx &\coloneqq (x_1, p_1, x_2, p_2, \dots, x_n, p_n) \in \cal{P}_{d_1} \times \dots \times \cal{P}_{d_n} \eqqcolon  \cal{P}_d, \\
-	&\nick{= (x_1, x_2, \dots, x_n, p_1, p_2, \dots, p_n) ?}
-\end{align*}
-to denote the phase space point for the composite system. 
-For simplicity going forward, we assume $n$ copies of a $d$--dimensional system $d_1=d_2 = \cdots = d$, and therefore we have that $\x \in \mathbb{Z}_d^{2n}$.
-
-The displacement operators form the Heisenberg-Weyl group~\cite{Folland_1989, Bengtsson_2006} under matrix multiplication modulo phases,
-\begin{equation}\label{eq:gp}
-    {\rm{HW}}_d^n \coloneqq \{ \tau^k D_{\bmx}: k \in \mathbb{Z}_d, \bmx \in \cal{P}_d^n\}.
-\end{equation}
-The Clifford operations $ \cal{C}_d^n $ are then defined as the set of unitaries that normalise the Heisenberg-Weyl group~\cite{Appleby_2005}.
-We may define the pure stabiliser states as those states obtained by acting on $|0\>$ with Clifford unitaries~\cite{cit:gross3} and, finally, the full set of stabilizer states as the convex hull of all pure stabilisers, namely all probabilistic mixtures of states of the form $U|0\>\<0|U^\dagger$ where $U$ is Clifford.
-
-\subsection{Wigner representations for quantum states and quantum operations}\label{sec:wigner}
-
-In order to provide a complete decomposition of arbitrary quantum states and quantum operations we now define a complete basis of Hermitian observables that behaves naturally under the action of the Clifford group.
-At every point $\x \in \P_d$ we define the phase-point operator
-\begin{equation}\label{eq:ax}
-	A_{\bmx} \coloneqq \frac{1}{d} \sum_{\bmz \in \cal{P}_d} \omega^{\eta(\bmx, \bmz)} D_{\bmz}, 
-\end{equation}
-where $\eta(\bmx, \bmz)$ is the symplectic inner product between any two points $\x,\z \in \P_d$, and is given explicitly by
-\begin{equation}
-	\eta(\bmx, \bmz) \coloneqq \bmz^T \begin{pmatrix}
-		0  & \id \\ %\mathbbm{O}_n  & \id_n \\
-		-\id & 0 \\ %-\id_n & \mathbbm{O}_n \\
-	\end{pmatrix} \bmx,
-\end{equation}
-where $0, \id$ denote the $n\times n$ zero and identity matrices.
-
-The phase-point operators form an orthogonal operator basis with respect to the Hilbert-Schmidt inner product, as discussed in~\cref{app:wigner}.
-Therefore, any quantum state $\rho \in \cal{B}(\cal{H}_d)$ can be expressed as a linear combination of them, $\rho = \sum_{\bmz \in \cal{P}_d} \W[\bmz]{\rho} A_{\bmz}$, where the coefficient vector $\W{\rho}$ is the Wigner distribution of state $\rho$,
-\begin{equation}\label{eq:wstate}
-    \W[\bmx]{\rho} \coloneqq \frac{1}{d}\tr[A_{\bmx} \rho].
-\end{equation}
-
-For any quantum state $\rho$, the Wigner distribution $W_\rho(\bmx)$ is readily seen to be a $d^2$-dimensional quasi-probability distribution over $\cal{P}_d$.
-More precisely, $W_\rho(\x)$ is a bounded real-valued function on $\P_d$ with the normalisation property $\sum_{\x} W_\rho(\bmx) = 1$ (see~\cref{app:wigner} for details).
-
-Any quantum operation $\E$ can also admit a Wigner representation. If $\E$ maps some quantum system $A$ to a quantum system $B$, and $\J(\E)$ is its associated Choi state then we can define
-\begin{equation}
-W_{\E}(\y |\x) \coloneqq d_A^2 W_{\J(\E)}(\bar{\x} \oplus \y),
-\end{equation}
-where $\bar{x} =(x_1, -p_1, \dots , x_n, -p_n)$ can be viewed as the time-reversed version of $\x$ in the discrete phase space, where momenta are reflected while position coordinates remain unchanged.
-
-\subsection{Magic theories for quantum computation}
-\label{sec:mono}
-
 A number of magic theories exist, where magic states are computational resource states with respect to a natural class of quantum operations that are considered free~\cite{Gour_2019}.
@@
 
-Within the Wigner representation, all negatively represented states are magic states, although in general the converse is not true~\cite{cit:campbell}.
+Within the Wigner representation for odd prime dimension, all negatively represented states are magic states, although in general the converse is not true~\cite{cit:veitch}.
 However, it is known that all positively represented states used in Clifford circuits admit an efficient classical description, so it is natural to focus on the negatively represented magic states.
@@
 Since the magic protocol sends free states to free states, $\E$ sends all positively represented quantum state to other positively represented quantum states.
-In such cases, it can be shown~\cite{Wang_2019} that $W_{\E}(\y |\x)$ must form a stochastic matrix.
-In particular, all Clifford operations correspond to stochastic matrices in this Wigner representation.
-
-However, it is important to note that this is not one-to-one.
+In such cases, it can be shown~\cite{Wang_2019} that if $\E$ is a free operation then the associated Wigner representation $W_{\E}(\y |\x)$ must form a stochastic matrix.
+In particular, all stabilizer operations correspond to stochastic matrices in the Wigner representation.
+
+However, it is important to note that this mapping to stochastic maps is not one-to-one.
 Not all stochastic maps on the phase space correspond to valid quantum operations.
-The reason is that the stochastic maps must also respect the symplectic structure of the phase space, which is an additional non-trivial constraint.
-
-In what follows we shall assume that we have a magic theory $\R = (\F, \O)$ in which the free states $\F$ form a closed set and are represented by a non-negative Wigner functions, while the free operations $\O$ are stochastic maps in the Wigner representation.
+The reason is that the maps must also respect the symplectic structure of the phase space, which is an additional non-trivial constraint.
+
+In what follows we shall assume that we have a magic theory $\R = (\F, \O)$ in which the free states $\F$ form a closed set and are represented by non-negative Wigner functions, while the free operations $\O$ are stochastic maps in the Wigner representation.
 To aid our analysis of magic in this phase space setting we shall make use of majorization theory, which we describe in the next section.
@@
 Given a vector $\w$ we define $\w^\downarrow$ to be the re-arrangement of the components of $\w$ into decreasing order.
-Given two $n$--component vectors $\w$ and $\r$, we first define $\widetilde{\w}$, where $\widetilde{w}_i \coloneqq w_i/r_i$, as the vector of component-wise ratios between $\w$ and $\r$.
+Given two $n$--component vectors $\w$ and $\r$, we first define $\widetilde{\w}=(\widetilde{w}_i)$, where $\widetilde{w}_i \coloneqq w_i/r_i$, as the vector of component-wise ratios between $\w$ and $\r$.
 We can now define the \emph{Lorenz curve} of $\w$ relative to $\r$, denoted $L_{\w|\r}(x)$, as the piece-wise linear function that passes through $(0,0)$ and the $n$ points
@@
 However, if $\w$ is a \emph{quasi-probability} distribution with negative values, and $\r$ a regular probability distribution things are different.
-Now the Lorenz curve is no longer monotone increasing, but is a concave function that breaks through the $L_{\w|\r}(x) = 1$ barrier at an interior point and attains some non-trivial maximum $L_\star$ above the value $1$, before decreasing monotonically to $L_{\w|\r}(x)= 1$ at the end-point $x=1$.
+Now the Lorenz curve is no longer monotonically increasing, but is a concave function that breaks through the $L_{\w|\r}(x) = 1$ barrier at an interior point and attains some non-trivial maximum $L_\star$ above the value $1$, before decreasing monotonically to $L_{\w|\r}(x)= 1$ at the end-point $x=1$.
 See~\cref{fig:lcs} for examples of non-monotonic Lorenz curves for quasi-distributions.
@@
 However, relative majorization is usually considered for probability distributions, so we need to verify that the same Lorenz curve conditions apply to quasi-probability distributions before proceeding with our analysis.
-This can be done from first principles, but a simpler way is see that this holds is to reduce to the problem of genuine distributions by first `masking' the negativity in the quasi-probability distribution $\w$ using the reference distribution $\r$ and then applying the conditions for relative majorization.
+This can be done from first principles, but a simpler way to see that this holds is to reduce to the problem of genuine distributions by first `masking' the negativity in the quasi-probability distribution $\w$ using the reference distribution $\r$ and then applying the conditions for relative majorization.
 This negativity masking then gives the following result.
 
-\begin{lemma} Let $\w \in \mathbb{R}^n,\w'\in \mathbb{R}^m$ be quasi-distributions, and let $\r \in \mathbb{R}^n, \r' \in \mathbb{R}^m$ be probability distributions with non-zero components.
+\begin{theorem} Let $\w \in \mathbb{R}^n,\w'\in \mathbb{R}^m$ be quasi-distributions, and let $\r \in \mathbb{R}^n, \r' \in \mathbb{R}^m$ be probability distributions with non-zero components.
 Then $(\w, \r) \succ (\w', \r')$ if and only if $L_{\w|\r}(x) \ge L_{\w' |\r'}(x)$ for all $x \in [0,1]$.
-\end{lemma}
+\end{theorem}
 
@@
 These allow us to interpret previous magic monotones in a new light.
-The first result gives an extremely simple way to see that the sum-negativity of a magic state is a monotone.
-
-\begin{lemma} Majorization in any $\R_\sigma$ implies the monotonicity of sum-negativity. 
-\end{lemma}
+The first result gives an extremely simple way to see that the sum-negativity/mana of a magic state is a monotone~\cite{cit:veitch2}.
+
+\begin{theorem} Majorization in any $\R_\sigma$ implies the monotonicity of sum-negativity. 
+\end{theorem}
 \begin{proof}
@@
 \begin{equation}
-	\W[\bmx]{\rho_{\rm{S}}(\epsilon)} = (1-\epsilon)\W[\bmx]{\rm{S}\>\<\rm{S}|} + \epsilon\W[\bmx]{\frac{1}{3}\id}.
+	\W[\bmx]{\rho_{\rm{S}}(\epsilon)} = (1-\epsilon)\W[\bmx]{|\rm{S}\>\<\rm{S}|} + \epsilon\W[\bmx]{\frac{1}{3}\id}.
 \end{equation}
@@
 
-Due to negativity, the ordering of the components of rescaled Wigner distribution $W_{\rho_n |\sigma_n}(\bmx) \coloneqq W_{\rho_n}(\bmx)/W_{\sigma_n}(\bmx)$, for $\rho_n = \rho_S(\epsilon)^{\otimes n}, \sigma_n = \sigma^{\otimes n}$, depends on whether $-v(\epsilon)$ appears to an even or odd power in the expression of~\cref{eq:wigu}.
+Due to negativity, the ordering of the components of rescaled Wigner distribution $W_{\rho_n |\sigma_n}(\bmx) \coloneqq W_{\rho_n}(\bmx)/W_{\sigma_n}(\bmx)$, for $\rho_n = \rho_S(\epsilon)^{\otimes n}, \sigma_n = \sigma^{\otimes n}$, depends on whether $-v(\epsilon)$ appears to an even or odd power.
 Treating the Wigner distributions as vectors, the component values $w_i$ and associated multiplicities ($m_i$) in the $n$--copy case are found to be
@@
 
-Distillation bounds can be obained from any location of the Lorenz curve, including the region around the peak, by imposing the constraint that the Lorenz curve of the input state never dips below the curve of the output.
+Distillation bounds can be obtained from any location of the Lorenz curve, including the region around the peak, by imposing the constraint that the Lorenz curve of the input state never dips below the curve of the output.
 In particular a compact constraint can be obtained by considering the initial slopes of the two Lorenz curves.
@@
 We find that
-\begin{equation}
-	R(\epsilon, \epsilon') \leq \frac{\ln (3-4\epsilon)}{\ln (3-4\epsilon')}.
-\end{equation}
+\begin{equation}\label{eq:unital-bound}
+	R(\epsilon, \epsilon') \leq R_\infty :=\frac{\ln (3-4\epsilon)}{\ln (3-4\epsilon')}.
+\end{equation}
+The choice of denoting the bound by $R_\infty$ is explained in Section \ref{section:entropies} in relation to single-shot entropies.
 For the limiting case of pure magic states on the output ($\epsilon'=0$), this simplifies to
@@
 This figure includes numerical estimates of the optimal majorization bounds $R_{\rm{num}}$ obtained by considering the full Lorenz curve, which show that the first elbow constraint can be further improved.
-\begin{figure}[t]
-    \centering
-    \includegraphics[scale=0.35]{figs/distill_bounds.pdf}
-    \caption{\textbf{Distillation bounds for unital protocols.} Distillation bounds obtained by the first elbow majorisation constraint $R_\infty$, mana and max--thauma $\theta_{\rm{max}}$ are plotted for $\epsilon' = 0$, up to error $\epsilon = 3/7$.
-Also shown is the bound $R_{10}$ coming from single-shot entropies on the quasi-distributions, which we discuss in Section~\ref{section:entropies}.
-Numerical bounds $R_{\rm{num}}$ are obtained by using the full set of Lorenz curve constraints.
-Each majorisation constraint provides stricter bounds than the mana and max--thauma bounds for noisy Strange states.
-    }
-    \label{fig:distill_bounds}
-\end{figure}
 
@@
 We assume that in the asymptotic/thermodynamic limit $n,m \rightarrow \infty$ that correlations generated on the reference equilibrium state are negligible.
-This implies that $d\mu(x)$ is peaked on a particular state $\tau'$, and $\E(\tau) \approx \tau'^{\otimes m}$.
+This implies that $d\mu(x)$ is peaked on a particular state $\tau'$, and $\E(\tau^{\otimes n}) \approx \tau'^{\otimes m}$.
 This occurs in the context of traditional thermodynamics, and states that the output system is well-described by intrinsic variables that do not scale in $m$, and correlations are sub-linear in $m$.
@@
 
-Our bound turn out to depend on the von Neumann entropy $S(\rho)$ of a state, and the free energy at a particular temperature.
+Our bound turns out to depend on the von Neumann entropy $S(\rho)$ of a state, and the free energy at a particular temperature.
 For a state $\tau = e^{-\beta H}/\Z$, the Helmholtz free energy $F$ is given by
@@
 \end{equation}
-which be obtained from the internal energy via a Legendre transform~\cite{Pathria_1997}.
+which is obtained from the internal energy via a Legendre transform~\cite{Pathria_1997}.
 
@@
     \centering
-    \includegraphics[scale=0.4]{figs/R_vs_A.pdf}
+    \includegraphics[scale=0.35]{figs/R_vs_A.pdf}
     \caption{\textbf{Variation of distillation bounds with Hamiltonian.} We consider $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$, and look at a family of Hamiltonians for the qutrit systems, given by $H = A_{\bmo}$ and $H' = (1-p-q)A_{\bmo}+pA_{(1,2)}+q{\rm{diag}}(0,1,2)$.
@@
 \section{Extension of single-shot entropies to quasi-distributions}\label{section:entropies}
-We have considered Wigner distributions of magic states within a statistical mechanical setting in which it is was argued that magic should be viewed as a non-classical form of free energy.
+We have considered Wigner distributions of magic states within a statistical mechanical setting in which it was argued that magic should be viewed as a non-classical form of free energy.
 This identification with free energy was done at the level of majorization constraints that appear due to stabilizer operations being described by stochastic maps in the Wigner representation.
@@
 \begin{theorem}\label{thm:HSchur} 
-	If $\alpha = \frac{2a}{2b-1}$ for non-negative integers $a,b$ with $a \geq b$, then $H_\alpha(\w)$ is well-defined on the set of quasi-distributions $\w$, and moreover if $\w \succ \w'$ for two quasi-distributions $\w, \w'$ then $H_\alpha (\w) \leq H_\alpha(\w')$.
+	If $\alpha = \frac{2a}{2b-1}$ for non-negative integers $a,b$ with $a \geq b$, then $H_\alpha(\w)$ is well-defined on the set of quasi-distributions, and moreover if $\w \succ \w'$ for two quasi-distributions $\w, \w'$ then $H_\alpha (\w) \leq H_\alpha(\w')$.
 \end{theorem}
@@
 We now recall that mana is defined as $\M(\rho) = \log \sum_{\x} |W_\rho(\x)|$, and so we obtain a second new description of mana:
-\begin{equation}
+\begin{equation}\label{eq:mana-divergence}
 \M(\rho) = \lim_{\epsilon \rightarrow 0^+} \epsilon H_{1-\epsilon}(W_\rho).
 \end{equation}
-Therefore, up to a factor $2\pi i$, the mana of a state $\rho$ is the residue of a pole in $H_\alpha(W_\rho)$, and quantifies \emph{the divergence of the Renyi-entropy} as we approach the limiting Shannon entropy $H(W_\rho)$.
+Therefore, the mana of a state $\rho$ is the residue of a pole in $H_\alpha(W_\rho)$, and quantifies \emph{the divergence of the Renyi-entropy} as we approach the limiting Shannon entropy $H(W_\rho)$.
 
@@
 	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ and $\beta F_\alpha(W_\rho) := D_\alpha (W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) - \log \Z$ is the $\alpha$--free energy of the Wigner distribution.
+\ddd{[$\Z$ needs discussion]}
 \end{theorem}
@@
 
-Lastly, we note that it would be of interest to consider the possibility of applying the approach taken here to other scenarios in which one wishes to distinguish classical from non-classical behaviour based on quasi-probability representations~\cite{Ferrie_2008, barnett_1997,Allahverdyan_2018, arvidsson_2020, halpern_2018, Lostaglio_2018, Levy_2020}
+Lastly, we note that it would be of interest to consider the possibility of applying the approach taken here to other scenarios in which one wishes to distinguish classical from non-classical behaviour based on quasi-probability representations~\cite{Ferrie_2008, barnett_1997,Allahverdyan_2018, arvidsson_2020, halpern_2018, Lostaglio_2018, Levy_2020}.
+
+\vspace{1cm}
 \section{Acknowledgements}
-We thank Earl Campbell for helpful discussions and comments.
+We thank Earl Campbell, Matteo Lostaglio, Philippe Faist and Nicole Yunger Halpern for helpful comments and discussions.
 NK is supported by the EPSRC Centre for Doctoral Training in Controlled Quantum Dynamics.

### 2021-06-22 magic_paper.tex
minor changes

--- 2021-06-16 magic_paper.tex
@@
 While traditional free energy is not defined in the presence of negativity, we show that majorization allows us to both quantify disorder in the Wigner representation and derive magic distillation bounds.
-These upper bounds are shown to be tighter than other bounds, such as mana and thauma, and moreover incorporate hardware physics, such as temperature dependence and physical Hamiltonians.
+These upper bounds are shown to be tighter than other bounds, such as from mana and thauma, and moreover incorporate hardware physics, such as temperature dependence and physical Hamiltonians.
 We also show that a sub-set of single-shot Renyi entropies remain well-defined on quasi-distributions, are fully meaningful in terms of data processing and can acquire negative values.
@@
 In this work, we develop a framework to analyse magic state distillation protocols where explicit physics of the system is incorporated in the distillation bounds.
-This is achieved by considering how a given magic state protocol transforms a \emph{pair} of quantum states -- one being noisy magic state, and the other a stabilizer state that is distinguished by the physics of the system (for example a state at a characteristic temperature, or the maximally mixed state) and acts as a reference state.
+This is achieved by considering how a given magic state protocol transforms a \emph{pair} of quantum states -- one being a noisy magic state, and the other a stabilizer state that is distinguished by the physics of the system (for example a state at a characteristic temperature, or the maximally mixed state) and acts as a reference state.
 The magic distillation bounds can then be expressed in terms of the physics of the reference state (e.g.
@@
 This section uses $\mathbf{d}$--majorization, however in~\cref{sec:stab} we drop the requirement of fixed-points and instead use the full relative majorization, before finally giving general entropic constraints in Section~\ref{section:entropies}.
+\nick{move this to intro}
 

### 2021-06-23 magic_paper.tex

--- 2021-06-22 magic_paper.tex
@@
 \input{preamble}
-% Labels and Refs (consistency, cref vs ref, thm vs lem vs prop, ??)
-% Figs check(consistency, cbars, captions, axes, iffalse)
-% Notation consistency (noise vs error, \ln{} -> \ln, \ln vs \log vs \log_2, italics & \emph, Aberg -> {\AA}berg, quasi-dist vs quasi-prob dist, def elbows)
+% Labels and Refs --- consistency, cref vs ref, thm vs lem vs prop, thm restatements, (??)
+% Notation consistency --- noise vs error, \ln{} -> \ln, \ln vs \log vs \log_2, italics & \emph, Aberg -> {\AA}berg, quasi-dist vs quasi-prob dist, def elbows, cumulant vs cumulative, stabilizer vs free, \p vs \w, W_\rho vs W_\rho(\bmz), \succ_r vs \succ
 % UK vs US english
-% Spacing (figs, sections, paragraphs, eq. numbering, \noindent, QEDs)
+
+% Figs check --- consistency, cbars, captions, axes, iffalse
+% Spacing --- figs, sections, paragraphs, eq. numbering, \noindent, QEDs
 
@@
 Theories of magic states attempt to quantify this computational element via monotones and determine how these states may be efficiently transformed into useful forms.
-Here we develop a statistical mechanical framework in which Wigner negative magic states provide non-classical free energy that is processed under Clifford circuits.
+Here, we develop a statistical mechanical framework based on majorization in which Wigner negative magic states provide non-classical free energy that is processed under Clifford circuits.
 While traditional free energy is not defined in the presence of negativity, we show that majorization allows us to both quantify disorder in the Wigner representation and derive magic distillation bounds.
 These upper bounds are shown to be tighter than other bounds, such as from mana and thauma, and can incorporate hardware physics, such as temperature dependence and physical Hamiltonians.
-We also show that a sub-set of single-shot Renyi entropies remain well-defined on quasi-distributions, are fully meaningful in terms of data processing and can acquire negative values that signal magic.
+We also show that a subset of single-shot Renyi entropies remain well-defined on quasi-distributions, are fully meaningful in terms of data processing and can acquire negative values that signal magic.
 We show that the mana of a magic state is the measure of divergence of these Renyi entropies as one approaches the Shannon entropy for Wigner distributions, and discuss how distillation lower bounds could be obtained in this setting.
@@
 
-There has been rapid progress towards the goal of a fault-tolerant quantum computer~\cite{cit:raussendorf, Raussendorf_2013, Nickerson_2014, Nikahd_2017, chao_2018, lin_pieceable_2020, Lin_2020, Bourassa_2021}.
+There has been rapid progress towards the goal of a fault-tolerant quantum computer~\cite{campbell_roads_2017, cit:raussendorf, Raussendorf_2013, Nickerson_2014, Nikahd_2017, chao_2018, lin_pieceable_2020, Lin_2020, Bourassa_2021}.
 However, many challenges remain and there is increasing need for theory to take into account physical limitations of the hardware involved.
@@
 This can be achieved by injecting in quantum states, called magic states, which promote the Clifford group to universal quantum computing~\cite{cit:bravyi}.
-The obstacle to this is that these states are invariably noisy and so protocols involving stabilizer operations must be employed to purify many copies of the magic states and improve the overall performance of the induced quantum gates~\cite{cit:bravyi, Jones_2013, Ogorman_2017}.
+The obstacle to this is that these states are invariably noisy, so protocols involving stabilizer operations must be employed to purify many copies of the magic states and improve the overall performance of the induced quantum gates~\cite{cit:bravyi, Jones_2013, Ogorman_2017}.
 A key question then arises about the overhead on purifying many copies of a magic state into less noisy forms.
@@
 To address this, concrete distillation protocols have been developed, such as the Bravyi-Haah qubit protocol that provides a quadratic reduction in noise per cycle~\cite{Bravyi2012}.
-Such distillation rates have been improved in more recent works~\cite{Jones_2013, haah2017magic, Hastings2018, Litinski_2019} and protocols for qudits of odd dimension have also been proposed~\cite{Anwar_2012, CampbellAnwar_2012, Dawkins_2015, Krishna2019, cit:prakash}.
+Such distillation rates have been improved in more recent works~\cite{Jones_2013, haah2017magic, Hastings2018, Litinski_2019} and protocols for qudits of odd dimension have also been proposed~\cite{CampbellAnwar_2012, Anwar_2012, Dawkins_2015, Krishna2019, cit:prakash}.
 There is also analysis of magic protocols from the perspective of magic monotones, which provide upper bounds on distillation rates and find application in the analysis of gate synthesis~\cite{Campbell_2017, Howard_2017, Prakash_2018, Seddon_2021}.
@@
 Recent work towards fault-tolerance is increasingly bridging the gap between abstract theory and experiment.
-Extensive work has been done on error mitigation~\cite{Li_2017, Temme_2017, Endo_2018, McClean_2017}, and the incorporation of hardware physics into the theoretical modes~\cite{holmes_resource_2019, Kandala_2019, Colless_2018, song2018quantum, Bravyi_2021}.
+Extensive work has been done on error mitigation~\cite{jones_2012, Li_2017, Temme_2017, Endo_2018, McClean_2017}, and the incorporation of hardware physics into the theoretical modes~\cite{Kandala_2019, holmes_resource_2019, Colless_2018, song2018quantum, Bravyi_2021}.
 For example, the XZZX code~\cite{bonilla_ataides_xzzx_2021} is a variant of the surface code that incorporates noise bias explicitly and has been shown to attain the hashing bound of random codes~\cite{Bennett_1996}.
@@
 In this work, we develop a framework to analyse magic state distillation protocols where explicit physics of the system is incorporated in the distillation bounds.
-This is achieved by considering how a given magic state protocol transforms a \emph{pair} of quantum states -- one being noisy magic state, and the other a stabilizer state that is distinguished by the physics of the system (for example a state at a characteristic temperature, or the maximally mixed state) and acts as a reference state.
+This is achieved by considering how a given magic state protocol transforms a \emph{pair} of quantum states -- one being a noisy magic state, and the other a stabilizer state that is distinguished by the physics of the system (for example a state at a characteristic temperature, or the maximally mixed state) and acts as a reference state.
 The magic distillation bounds can then be expressed in terms of the physics of the reference state (e.g.
 free energy changes in the case of temperature, or non-unitality in the case of the maximally mixed state).
-Such bounds are therefore of interest in assessing how physical features such as temperature, noise-biases or fixed-point structure associated with restricted gate-sets constrain distillation protocols~\cite{Aliferis_2008, Stephens_2013, Li_2015, Babbush_2018, Tuckett_2019, Guillaud_2019, Fowler_2019}.
+Such bounds are therefore of interest in assessing how physical features such as temperature, noise-biases or fixed-point structure associated with restricted gate-sets constrain distillation protocols~\cite{Tuckett_2019, Aliferis_2008, Stephens_2013, Li_2015, Babbush_2018, Guillaud_2019, Fowler_2019}.
 
@@
 We circumvent this obstacle by making use of a more fundamental tool in thermodynamics and information theory -- majorization theory~\cite{cit:marshall, Veinott_1971, Ruch_1976}.
-To our knowledge majorization of quasi-distributions has not been considered in quantum physics before, and therefore our analysis is also of interest to the study of non-classicality in quantum systems~\cite{Allahverdyan_2018, arvidsson_2020, halpern_2018, Lostaglio_2018, Levy_2020}.
+To our knowledge majorization of quasi-distributions has not been considered in quantum physics before, and therefore our analysis is also of interest to the study of non-classicality in quantum systems~\cite{Fine_1982, Allahverdyan_2018, arvidsson_2020, halpern_2018, Lostaglio_2018, Levy_2020}.
 
@@
 The simplest case we consider is for magic protocols that lead to unital channels (Section~\ref{sec:unital}).
-These are a sub-set of protocols that leave invariant some distinguished state or has some equilibrium fixed point (Section~\ref{sec:frag}).
+These are a subset of protocols that leave invariant some distinguished state or have some equilibrium fixed point (Section~\ref{sec:frag}).
 We then consider protocols that are non-equilibrium processes, but only generate sub-linear correlations that lead to a simple description in the thermodynamic limit (Section~\ref{sec:stab}).
@@
 \begin{align}
-\mbox{Unital} \subset &\mbox{ local fixed-points} \nonumber\\ 
-& \subset \mbox{ sub-linear correlations} \subset \mbox{ general protocols.} \nonumber
-\end{align}
-
-We provide explicit bounds for magic protocols that generate unital channels (Equation~(\ref{eq:unital-bound})), as well as bounds that incorporate on the temperature and Hamiltonian of the system (Theorem~\ref{thm:free-energy}) and discuss extensions to more general scenarios.
+\mbox{Unital} &\subset \mbox{ local fixed-points} \nonumber\\ 
+&\subset \mbox{ sub-linear correlations} \subset \mbox{ general protocols.} \nonumber
+\end{align}
+
+We provide explicit bounds for magic protocols that generate unital channels (Equation~(\ref{eq:unital-bound})), as well as bounds that incorporate the temperature and Hamiltonian of the system (Theorem~\ref{thm:free-energy}) and discuss extensions to more general scenarios.
 These bounds are shown to be tighter than other bounds such as those that come from mana and thauma (Section~\ref{sec:monotones_frag} and Figure~\ref{fig:distill_bounds}).
@@
 Here $\omega \coloneqq e^{2\pi i/d}$ is the $d$-th root of unity and addition is taken modulo $d$.
-From these we can construct a phase space $\cal{P}_d = \mathbb{Z}_d \times \mathbb{Z}_d$ that provides a complete representation of the quantum system.
-\ddd{[Change $\x$ to $\z$ for phase space points?
-This also distinguishes from the $L_\rho(x)$ use of $x$.
-For multiple phase space points can use $\z_1, \z_2$.]} Given a point $\bmx \coloneqq (x, p)$ we define a displacement operator,
+From these we can construct a phase space $\cal{P}_d := \mathbb{Z}_d \times \mathbb{Z}_d$ that provides a complete representation of the quantum system.
+Given a point $\bmz \coloneqq (q, p)$ we define a displacement operator,
 \begin{equation}\label{eq:ddef}
-    D_{\bmx} \coloneqq \tau^{x p} X^{x} Z^{p},\ 
+    D_{\bmz} \coloneqq \tau^{q p} X^{q} Z^{p},\ 
 \end{equation}
@@
 We assume going forward that $d$ is an odd prime~\cite{Appleby_2005}.
-The qubit case $d=2$ is known to have obstacles to using a Wigner representation to quantify magic in terms of negativity \ddd{[Cite early papers highlighting this]}, although recent work \ddd{[Cite Raussendorf PRA 2020 qubit paper!!
-We can't miss such key papers!]} has shown how to extend this to include qubits by enlarging the phase space.
+The qubit case $d=2$ is known to have obstacles to using a Wigner representation to quantify magic in terms of negativity~\cite{Mermin_1990, cit:howard2}, although recent work~\cite{Raussendorf_qubits} has shown how to extend this to include qubits by enlarging the phase space.
 For a composite system with dimension $d = d_1 \dots d_n$ we can decompose the Hilbert space as $\cal{H}_d = \cal{H}_{d_1} \otimes \dots \otimes \cal{H}_{d_n}$, and then define displacement operators as
 \begin{equation}\label{eq:composited}
-    D_{\bmx} \coloneqq D_{(x_1, p_1)} \otimes \dots \otimes D_{(x_n, p_n)},
+    D_{\bmz} \coloneqq D_{(q_1, p_1)} \otimes \dots \otimes D_{(q_n, p_n)},
 \end{equation}
@@
 \begin{align*}
-	\bmx &\coloneqq (x_1, p_1, x_2, p_2, \dots, x_n, p_n) \in \cal{P}_{d_1} \times \dots \times \cal{P}_{d_n} \eqqcolon  \cal{P}_d,
+	\bmz &\coloneqq (q_1, \dots, q_n, p_1, \dots, p_n) \in \cal{P}_{d_1} \times \dots \times \cal{P}_{d_n} \eqqcolon  \cal{P}_d,
 \end{align*}
 to denote the phase space point for the composite system. 
-For simplicity going forward, we assume $n$ copies of a $d$--dimensional system $d_1=d_2 = \cdots = d$, and therefore we have that $\x \in \mathbb{Z}_d^{2n}$.
+For simplicity going forward, we assume $n$ copies of a $d$--dimensional system $d_1=d_2 = \cdots = d$, and therefore we have that $\bmz \in \mathbb{Z}_d^{2n}$.
 
@@
 \begin{equation}\label{eq:gp}
-    {\rm{HW}}_d^n \coloneqq \{ \tau^k D_{\bmx}: k \in \mathbb{Z}_d, \bmx \in \cal{P}_d^n\}.
+    {\rm{HW}}_d^n \coloneqq \{ \tau^k D_{\bmz}: k \in \mathbb{Z}_d, \bmz \in \cal{P}_d^n\}.
 \end{equation}
@@
 In order to provide a complete decomposition of arbitrary quantum states and quantum operations we now define a complete basis of Hermitian observables that behaves naturally under the action of the Clifford group.
-At every point $\x \in \P_d$ we define the phase-point operator
+At every point $\bmz \in \P_d$ we define the phase-point operator
 \begin{equation}\label{eq:ax}
-	A_{\bmx} \coloneqq \frac{1}{d} \sum_{\bmz \in \cal{P}_d} \omega^{\eta(\bmx, \bmz)} D_{\bmz}, 
-\end{equation}
-where $\eta(\bmx, \bmz)$ is the symplectic inner product between any two points $\x,\z \in \P_d$, and is given explicitly by
-\begin{equation}
-	\eta(\bmx, \bmz) \coloneqq \bmz^T \begin{pmatrix}
+	A_{\bmz} \coloneqq \frac{1}{d} \sum_{\bmy \in \cal{P}_d} \omega^{\eta(\bmz, \bmy)} D_{\bmy}, 
+\end{equation}
+where $\eta(\bmz, \bmz)$ is the symplectic inner product between any two points $\bmz,\z \in \P_d$, and is given explicitly by
+\begin{equation}
+	\eta(\bmz, \bmy) \coloneqq \bmy^T \begin{pmatrix}
 		0  & \id \\ %\mathbbm{O}_n  & \id_n \\
 		-\id & 0 \\ %-\id_n & \mathbbm{O}_n \\
-	\end{pmatrix} \bmx,
+	\end{pmatrix} \bmz,
 \end{equation}
@@
 \begin{equation}\label{eq:wstate}
-    \W[\bmx]{\rho} \coloneqq \frac{1}{d}\tr[A_{\bmx} \rho].
-\end{equation}
-
-For any quantum state $\rho$, the Wigner distribution $W_\rho(\bmx)$ is readily seen to be a $d^2$-dimensional quasi-probability distribution over $\cal{P}_d$.
-More precisely, $W_\rho(\x)$ is a bounded real-valued function on $\P_d$ with the normalisation property $\sum_{\x} W_\rho(\bmx) = 1$ (see~\cref{app:wigner} for details).
+    \W[\bmz]{\rho} \coloneqq \frac{1}{d}\tr[A_{\bmz} \rho].
+\end{equation}
+
+For any quantum state $\rho$, the Wigner distribution $W_\rho(\bmz)$ is readily seen to be a $d^2$-dimensional quasi-probability distribution over $\cal{P}_d$.
+More precisely, $W_\rho(\bmz)$ is a bounded real-valued function on $\P_d$ with the normalisation property $\sum_{\bmz} W_\rho(\bmz) = 1$ (see~\cref{app:wigner} for details).
 
 Any quantum operation $\E$ can also admit a Wigner representation.
-If $\E$ maps some quantum system $A$ of dimension $d_A$ to a quantum system $B$ of dimension $d_B$, and $\J(\E)$ is its associated Choi state \ddd{[Cite Watrous book]} then we can define
-\begin{equation}
-W_{\E}(\y |\x) \coloneqq d_A^2 W_{\J(\E)}(\bar{\x} \oplus \y),
-\end{equation}
-where $\bar{x} =(x_1, -p_1, \dots , x_n, -p_n)$ can be viewed as the time-reversed version of $\x$ in the discrete phase space, where momenta are reflected while position coordinates remain unchanged.
+If $\E$ maps some quantum system $A$ of dimension $d_A$ to a quantum system $B$ of dimension $d_B$ and $\J(\E)$ is its associated Choi state~\cite{watrous_2018}, then we can define
+\begin{equation}
+W_{\E}(\y |\bmz) \coloneqq d_A^2 W_{\J(\E)}(\bar{\bmz} \oplus \y),
+\end{equation}
+where $\bar{\bmz} = (q_1, \dots, q_n, -p_1, \dots, -p_n)$ can be viewed as the time-reversed version of $\bmz$ in the discrete phase space, where momenta are reflected while position coordinates remain unchanged.
 
@@
 For the case where this reference state is a thermal state at some temperature $T$ our magic distillation bounds are functions of $T$, the noise parameters $\epsilon, \epsilon'$, and the free energy the protocol channel $\E$ injects in.
-In addition, a quantity $\phi$ links the computational and physical aspects, and corresponds to the degree to which Wigner negativity in $\rho$ can be assigned a sharp energy via the system Hamiltonian.}
+In addition, a quantity $\phi$ (Equation~\ref{eq:phi}) links the computational and physical aspects, and corresponds to the degree to which Wigner negativity in $\rho$ can be assigned a sharp energy via the system Hamiltonian.}
     \label{fig:sketch}
@@
 \begin{equation}
-    \sn{\rho} \coloneqq \sum\limits_{\bmx: \W[\bmx]{\rho} < 0} \abs{\W[\bmx]{\rho}}.
+    \sn{\rho} \coloneqq \sum\limits_{\bmz: \W[\bmz]{\rho} < 0} \abs{\W[\bmz]{\rho}}.
 \end{equation}
@@
 \begin{equation}
-    \Fmax \coloneqq \{ \rho: \W[\bmx]{\rho} \geq 0 \text{ for all } \bmx \in \cal{P}_d\}.
+    \Fmax \coloneqq \{ \rho: \W[\bmz]{\rho} \geq 0 \text{ for all } \bmz \in \cal{P}_d\}.
 \end{equation}
@@
 
-Any magic state protocol will correspond to a quantum channel $\E$, and admits a Wigner representation $W_{\E}( \y | \x)$ that can be viewed as a transition matrix mapping phase space points $\x \rightarrow \y$.
+Any magic state protocol will correspond to a quantum channel $\E$, and admits a Wigner representation $W_{\E}( \y | \bmz)$ that can be viewed as a transition matrix mapping phase space points $\bmz \rightarrow \y$.
 The representation obeys the relation
 \begin{equation}
-	W_{\E(\rho)} (\y) = \sum_{\x \in \P_d} W_{\E}( \y | \x) W_\rho(\x),
+	W_{\E(\rho)} (\y) = \sum_{\bmz \in \P_d} W_{\E}( \y | \bmz) W_\rho(\bmz),
 \end{equation}
@@
 Since the magic protocol sends free states to free states, $\E$ sends all positively represented quantum state to other positively represented quantum states.
-In such cases, it can be shown~\cite{Wang_2019} that if $\E$ is a free operation then the associated Wigner representation $W_{\E}(\y |\x)$ must form a stochastic matrix.
+In such cases, it can be shown~\cite{Wang_2019} that if $\E$ is a free operation then the associated Wigner representation $W_{\E}(\y |\bmz)$ must form a stochastic matrix.
 In particular, all stabilizer operations correspond to stochastic matrices in the Wigner representation.
@@
 
-In what follows we shall assume that we have a magic theory $\R = (\F, \O)$ in which the free states $\F$ form a closed set and are represented by non-negative Wigner functions, while the free operations $\O$ are stochastic maps in the Wigner representation.
+In what follows, we shall assume that we have a magic theory $\R = (\F, \O)$ in which the free states $\F$ form a closed set and are represented by non-negative Wigner functions, while the free operations $\O$ are stochastic maps in the Wigner representation.
 To aid our analysis of magic in this phase space setting we shall make use of majorization theory, which we describe in the next section.
@@
 It is readily checked that the original majorization condition between probability distributions corresponds to the case $\r = (1/n, \dots, 1/n)$.
-The pre-order that results from relative majorization is also easily checked and again corresponds to checking a small number of inequalities.
+The pre-order that results from $\bmd$-majorization is also easily checked and again corresponds to checking a small number of inequalities.
 
@@
 It turns out that relative majorization is equally applicable to \emph{quasi-probability} distributions, and therefore can be applied to the Wigner representation of magic across different $\R_\sigma$.
-We go into more detail on this in the next section.
+We discuss this in detail in the next section.
 
@@
 
-\begin{theorem} Let $\w \in \mathbb{R}^n,\w'\in \mathbb{R}^m$ be quasi-distributions, and let $\r \in \mathbb{R}^n, \r' \in \mathbb{R}^m$ be probability distributions with non-zero components.
+\begin{theorem}\label{thm:lcquasi}
+	Let $\w \in \mathbb{R}^n,\w'\in \mathbb{R}^m$ be quasi-distributions, and let $\r \in \mathbb{R}^n, \r' \in \mathbb{R}^m$ be probability distributions with non-zero components.
 Then $(\w, \r) \succ (\w', \r')$ if and only if $L_{\w|\r}(x) \ge L_{\w' |\r'}(x)$ for all $x \in [0,1]$.
 \end{theorem}
-
 \begin{proof}
@@
 
-We can now consider how physical constraints affect magic distillation rates.
-In~\cref{sec:stab} we shall focus on the energetic aspects of a protocol, that are defined due to the specific Hamiltonian that the system possesses.
-However, before that, in this section we give a more abstract setting based on the fixed-point structure of  the physical operations accessible to us.
+We can now consider how physical constraints affect magic distillation rates starting in this section with an abstract setting based on the fixed-point structure of the physical operations accessible to us.
 We show that any magic theory can always be decomposed in terms of `sub-theories' with a particular fixed-point structure.
-This section uses $\mathbf{d}$--majorization, however in~\cref{sec:stab} we drop the requirement of fixed-points and instead use the full relative majorization, before finally giving general entropic constraints in Section~\ref{section:entropies}.
+This allows the use of $\mathbf{d}$--majorization, however in~\cref{sec:stab}, we drop the requirement of fixed-points and instead use the full relative majorization, before finally giving general entropic constraints in Section~\ref{section:entropies}.
 
@@
 We are interested in the ability to transform many copies of some noisy magic state $\rho$ towards a more pure form of magic.
-The state $\rho$ is assumed to have negativity in the Wigner representation, so $W_\rho(\x) < 0$ for some regions of $\x \in \P_d$.
-The state $\sigma$ is assumed to have a Wigner distribution with $W_\sigma(\x) > 0$ for all $\x$ in the phase space\footnote{Any non-full rank state $\sigma$ can be handled as a limiting case in which we first add an infinitesimal fraction of depolarising noise $\epsilon (\id/d)$ and then take $\epsilon \rightarrow 0$ in the end.}.
-
-The free operations within the magic theory $\R$ are represented by stochastic maps, and within $\R_\sigma$ by stochastic maps that leave $W_\sigma(\x)$ invariant.
+The state $\rho$ is assumed to have negativity in the Wigner representation, so $W_\rho(\bmz) < 0$ for some regions of $\bmz \in \P_d$.
+The state $\sigma$ is assumed to have a Wigner distribution with $W_\sigma(\bmz) > 0$ for all $\bmz$ in the phase space\footnote{Any non-full rank state $\sigma$ can be handled as a limiting case in which we first add an infinitesimal fraction of depolarising noise $\epsilon (\id/d)$ and then take $\epsilon \rightarrow 0$ in the end.}.
+
+The free operations within the magic theory $\R$ are represented by stochastic maps, and within $\R_\sigma$ by stochastic maps that leave $W_\sigma(\bmz)$ invariant.
 Therefore, a necessary condition for magic state transformations $\rho_1 \rightarrow \rho_2$ within $\R_\sigma$ will be that
@@
 \begin{proof}
-	The sum-negativity of a magic state $\rho$ can be written as $sn(\rho) =\frac{1}{2} (\sum_{\x} |W_\rho(\x) | - 1)$.
+	The sum-negativity of a magic state $\rho$ can be written as $sn(\rho) =\frac{1}{2} (\sum_{\bmz} |W_\rho(\bmz) | - 1)$.
 We make use of the $L_1$-norm form of relative majorization, (see~\cref{app:major}), which states that $\p \succ_{\r} \q$ if and only if
@@
 in the computational basis.
-Its distribution $W_S(\x)$ has a single negative value of $-1/3$ at $\x =(0,0)$ and the positive value $1/6$ at all other points.
+Its distribution $W_S$ has a single negative value of $-1/3$ at $\bmz =(0,0)$ and the positive value $1/6$ at all other points.
 We define the $\epsilon$--noisy Strange state as
@@
 \begin{equation}
-	\W[\bmx]{\rho_{\rm{S}}(\epsilon)} = (1-\epsilon)\W[\bmx]{|\rm{S}\>\<\rm{S}|} + \epsilon\W[\bmx]{\frac{1}{3}\id}.
+	\W[\bmz]{\rho_{\rm{S}}(\epsilon)} = (1-\epsilon)\W[\bmz]{|\rm{S}\>\<\rm{S}|} + \epsilon\W[\bmz]{\frac{1}{3}\id}.
 \end{equation}
@@
 \end{equation} 
-located at the origin $\bmx = \bmo$ and positive components
+located at the origin $\bmz = \bmo$ and positive components
 \begin{equation}
@@
 \end{equation}
-at the 8 phase space points $\x \ne \mathbf{0}$. We assume that $\epsilon < 3/4$ to ensure the presence of negativity in the Wigner distribution.
+at the 8 phase space points $\bmz \ne \mathbf{0}$. We assume that $\epsilon < 3/4$ to ensure the presence of negativity in the Wigner distribution.
 
@@
 \begin{equation}\label{eq:sudist}
-	\rho_{\rm{S}}(\epsilon)^{\otimes n} \longrightarrow \rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n-n')},
-\end{equation}
-and use them to bound the distillation rate $R(\epsilon, \epsilon') \coloneqq n'/n$.
-
-Due to negativity, the ordering of the components of rescaled Wigner distribution $W_{\rho_n |\sigma_n}(\bmx) \coloneqq W_{\rho_n}(\bmx)/W_{\sigma_n}(\bmx)$, for $\rho_n = \rho_S(\epsilon)^{\otimes n}, \sigma_n = \sigma^{\otimes n}$, depends on whether $-v(\epsilon)$ appears to an even or odd power.
-Treating the Wigner distributions as vectors, the component values $w_i$ and associated multiplicities ($m_i$) in the $n$--copy case are found to be
+	\rho_{\rm{S}}(\epsilon)^{\otimes n} \longrightarrow \rho_{\rm{S}}(\epsilon')^{\otimes n'}, %\otimes \left( \frac{1}{3}\id \right)^{\otimes (n-n')},
+\end{equation}
+and use them to bound the magic distillation rate $R(\epsilon, \epsilon') \coloneqq n'/n$.
+
+Due to negativity, the ordering of the components of rescaled Wigner distribution $W_{\rho_n |\sigma_n}(\bmz) \coloneqq W_{\rho_n}(\bmz)/W_{\sigma_n}(\bmz)$, for $\rho_n = \rho_S(\epsilon)^{\otimes n}, \sigma_n = \sigma^{\otimes n}$, depends on whether $-v(\epsilon)$ appears to an even or odd power.
+Treating the Wigner distributions as vectors, the component values $w_i$ and associated multiplicities $m_i$ in the $n$--copy case are found to be
 \begin{align}
@@
 where index $i$ runs through $0, \dots, n$, and we assume for simplicity that $n$ is even and $\epsilon \leq 3/7$, which implies that $v \geq u$.
-The details of this are provided in~\cref{app:lcsu_technical}.
+All details on the analysis are provided in~\cref{app:lcsu_technical}.
 
@@
 \begin{align}\label{eq:lcsu_max}
-	L_\star &\coloneqq L_{\rho |\sigma} (x_\star) = \sum_{i = 0}^{n/2} m_{2i} w_{2i} \nonumber\\
+	L_\star &\coloneqq L_{\rho_n |\sigma_n} (x_\star) = \sum_{i = 0}^{n/2} m_{2i} w_{2i} \nonumber\\
 	&= \frac{1}{2} + \frac{1}{2}\left(\frac{15 - 8\epsilon}{9}\right)^n > 1,
@@
 
-The first elbow coordinates for $\rho_S(\epsilon)^{\otimes n}$ are given by $(1/9^n, v(\epsilon)^n)$, while for $\rho_S(\epsilon')^{\otimes n'}$ by $(1/9^{n'}, v(\epsilon')^{n'})$, and by considering the slope of the line segment joining this first elbow to the origin we can use~\cref{prop:first_elb} in the Appendices, to bound $R(\epsilon, \epsilon')$.
+The coordinates of the first point after the origin for $\rho_S(\epsilon)^{\otimes n}$ are given by $(1/9^n, v(\epsilon)^n)$, while for $\rho_S(\epsilon')^{\otimes n'}$ by $(1/9^{n'}, v(\epsilon')^{n'})$, and by considering the slope of the line segment joining this point to the origin we can use~\cref{prop:first_elb} in the Appendices, to bound $R(\epsilon, \epsilon')$.
 We find that
@@
 and can be calculated numerically via a semi-definite program.
-For the noisy Strange state, the max--thauma bound coincides with the mana bound, and we find that they are both looser than the majorization bound we derived via the first elbow constraint as shown in~\cref{fig:distill_bounds}.
-
-This figure includes numerical estimates of the optimal majorization bounds $R_{\rm{num}}$ obtained by considering the full Lorenz curve, which show that the first elbow constraint can be further improved.
+For the noisy Strange state, the max--thauma bound coincides with the mana bound, and we find that they are both looser than the majorization bound $R_\infty$ as shown in~\cref{fig:distill_bounds}.
+
+This figure includes numerical estimates of the optimal majorization bounds $R_{\rm{num}}$ obtained by considering the full Lorenz curve, which show that the bound $R_\infty$ can be further improved.
 
@@
 
-We can now show how to use majorization to incorporate physics into magic distillation bounds.
+We can now show how to use relative majorization to incorporate physics into magic distillation bounds.
 We focus on energetic and entropic aspects of a protocol.
@@
 \end{equation}
-We may also assume that the reference state $\tau$ is not a magic state, and has a strictly positive Wigner distribution $W_\tau(\x)$.
+We may also assume that the reference state $\tau$ is not a magic state, and has a strictly positive Wigner distribution $W_\tau(\bmz)$.
 
@@
 where $F$ is the free energy of $\tau$,  and 
-\begin{equation}
+\begin{equation}\label{eq:phi}
 	\phi = -\beta^{-1} \log \zeta
@@
 	\zeta &= \sum_{k\in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}, \nonumber\\
-	\alpha_k &= \<E_k| A_{\x_\star} |E_k\>,
-\end{align}
-and $W_\tau(\x)$ attaining a minimum at $\x=\x_\star$. The primed variables are defined similarly for the output system.
+	\alpha_k &= \<E_k| A_{\bmz_\star} |E_k\>,
+\end{align}
+and $W_\tau(\bmz)$ attaining a minimum at $\bmz=\bmz_\star$. The primed variables are defined similarly for the output system.
 \end{theorem}
@@
 \begin{equation}
-	H_{1+\epsilon}(W_\rho) = -\epsilon^{-1} \log \sum_{\x} |W_\rho (\x)|^{1+\epsilon}
+	H_{1+\epsilon}(W_\rho) = -\epsilon^{-1} \log \sum_{\bmz} |W_\rho (\bmz)|^{1+\epsilon}
 \end{equation} 
 with $\epsilon \rightarrow 0^+$ through a sequence of rational values.
-We now recall that mana is defined as $\M(\rho) = \log \sum_{\x} |W_\rho(\x)|$, and so we obtain a second new description of mana:
+We now recall that mana is defined as $\M(\rho) = \log \sum_{\bmz} |W_\rho(\bmz)|$, and so we obtain a second new description of mana:
 \begin{equation}\label{eq:mana-divergence}
@@
 However since variation in $\alpha$ is no longer smooth ($\alpha$ is restricted to a dense set of rational values) technical obstacles exist and we do not pursue this speculative line here, but just note that other works exist in which computational transitions are considered in relation to phase transitions [\ddd{cite}].
-\nick{Do you know what you want to cite in this paragraph?}
 
@@
 Our bounds exploited relatively simple aspects of the Lorenz curves of the quasi-distributions, so it would be of interest to sharpen these bounds and obtain a better handle on the Lorenz curve structure in the $n\rightarrow \infty$ limit.
-It would also be of interest to analyse what features of single-shot entropies can be extended to quasi-distributions in a sensible form [\ddd{cite}] \nick{and here?}.
+It would also be of interest to analyse what features of single-shot entropies can be extended to quasi-distributions in a sensible form [\ddd{cite}].
 This raises interesting questions as we no longer have a notion of typicality and the central limit theorem does not apply.
@@
 This would correspond to transformations that are \emph{not} unital, but still respect the symplectic structure.
-Physically, this regime would correspond to a form of thermo-majorization obtained from looking at the action of the Clifford group at a micro-canonical level, and then reducing to a small subsystem~\cite{cit:lostaglio, Pathria_1997}.
+Physically, this regime would correspond to a form of thermo-majorization obtained from looking at the action of the Clifford group at a micro-canonical level, and then reducing to a small subsystem~\cite{Pathria_1997}.
 While this seems like a painful thing to consider, there is motivation for this beyond the aim of magic protocols: in the case of statistical mechanics on a phase space this is precisely the situation, albeit in the continuum limit.
-Statistical mechanics of actual systems obey Hamiltonian dynamics and so automatically respect a symplectic form~\cite{Pathria_1997}.
+Statistical mechanics of actual systems obey Hamiltonian dynamics and so automatically respect a symplectic form~\cite{Pathria_1997} \nick{better ref here?}.
 Therefore, the pre-order of statistical mechanical states with respect to phase space dynamics preserving a Gibbs state must correspond to a symplectic majorization condition.
@@
     \begin{enumerate}
-        \item[(i)]\label{en:a1} Hermiticity and unitarity: $A_{\bmx}^\dagger = A_{\bmx} = A_{\bmx}^{-1}$;
-	    \item[(ii)]\label{en:a2} Closure under transposition: $A_{(x, p)}^T = A_{(x, -p)}$;
-	    \item[(iii)]\label{en:a3} Unit trace for odd $d$: $\tr[A_{\bmx}] = 1$;
+        \item[(i)]\label{en:a1} Hermiticity and unitarity: $A_{\bmz}^\dagger = A_{\bmz} = A_{\bmz}^{-1}$;
+	    \item[(ii)]\label{en:a2} Closure under transposition: $A_{(q, p)}^T = A_{(q, -p)}$;
+	    \item[(iii)]\label{en:a3} Unit trace for odd $d$: $\tr[A_{\bmz}] = 1$;
 	    \item[(iv)]\label{en:a4} Completeness relation: $\sum_{\bmz \in \cal{P}_d} A_{\bmz} = d\id$;
-	    \item[(i)]\label{en:a5} Orthogonality: $\tr[A_{\bmx}^\dagger A_{\bm{x'}}] = d \delta_{\bmx,\bm{x'}}$.
+	    \item[(i)]\label{en:a5} Orthogonality: $\tr[A_{\bmz}^\dagger A_{\bmy'}] = d \delta_{\bmz,\bmy'}$.
 	\end{enumerate}
 \end{proposition}
-All properties follow from the definition in~\cref{eq:ax} along with properties of the displacement operator $D_{\bmx}$ and can be found in the literature, e.g.~\cite{cit:veitch,Vourdas_2004,cit:gross3}
+All properties follow from the definition in~\cref{eq:ax} along with properties of the displacement operator $D_{\bmz}$ and can be found in the literature, e.g.~\cite{cit:veitch,Vourdas_2004,cit:gross3}
 
@@
   \begin{enumerate}
-    \item[(i)]\label{en:w1} Real valued: $\W{\rho}(\bmx) \in \mathbb{R}^{d^2}$;
+    \item[(i)]\label{en:w1} Real valued: $\W{\rho}(\bmz) \in \mathbb{R}^{d^2}$;
     \item[(ii)]\label{en:w2} Normalised: $\sum_{\bmz \in \cal{P}_d} \W[\bmz]{\rho}=1$;
-    \item[(iii)]\label{en:w3} Bounded: $\abs{\W[\bmx]{\rho}} \leq \frac{1}{d}$.
+    \item[(iii)]\label{en:w3} Bounded: $\abs{\W[\bmz]{\rho}} \leq \frac{1}{d}$.
     \item[(iv)]\label{en:w4} Additive under mixing: \vspace{2pt}\\
-    $\W[\bmx]{p\rho_1 + (1-p)\rho_2} = p\W[\bmx]{\rho_1} + (1-p)\W[\bmx]{\rho_2}$;
+    $\W[\bmz]{p\rho_1 + (1-p)\rho_2} = p\W[\bmz]{\rho_1} + (1-p)\W[\bmz]{\rho_2}$;
     \item[(v)]\label{en:w5} Multiplicative under tensor products: \vspace{2pt}\\
-    $\W[\bmx_A \oplus \bmx_B]{\rho_A \otimes \rho_B} = \W[\bmx_A]{\rho_A}\W[\bmx_B]{\rho_B}$.
+    $\W[\bmz_A \oplus \bmz_B]{\rho_A \otimes \rho_B} = \W[\bmz_A]{\rho_A}\W[\bmz_B]{\rho_B}$.
 	\end{enumerate}
@@
 Let $\{\lambda_i\}_{i \in \mathbb{Z}_d}$ be the (non-negative) eigenvalues of $\rho$, summing to 1.
-Let $\{\alpha_{\bmx,i}\}_{i \in \mathbb{Z}_d}$ be the eigenvalues of $A_{\bmx}$. For any $\bmx, \alpha_{\bmx,i} \in \{-1, 1\}$, due to the hermiticity and unitarity of the phase-point operators. 
+Let $\{\alpha_{\bmz,i}\}_{i \in \mathbb{Z}_d}$ be the eigenvalues of $A_{\bmz}$. For any $\bmz, \alpha_{\bmz,i} \in \{-1, 1\}$, due to the hermiticity and unitarity of the phase-point operators. 
 Then,
 \begin{align}
-	\abs{W_{\rho}(\bmx)} &= \frac{1}{d}\abs{\tr[A_{\bmx} \rho]} \leq \frac{1}{d} \abs{\sum_i \alpha_{\bmx,i} \lambda_i} \nonumber\\ &\leq \frac{1}{d}\sum_i \lambda_i = \frac{1}{d}.
+	\abs{W_{\rho}(\bmz)} &= \frac{1}{d}\abs{\tr[A_{\bmz} \rho]} \leq \frac{1}{d} \abs{\sum_i \alpha_{\bmz,i} \lambda_i} \nonumber\\ &\leq \frac{1}{d}\sum_i \lambda_i = \frac{1}{d}.
 \end{align}
@@
     \begin{enumerate}
-        \item[(i)]\label{en:wo1} Real-valued: $\W{\E}(\x) \in \mathbb{R}^{d^2} \times \mathbb{R}^{d^2}$;
-        \item[(ii)]\label{en:wo2} Normalised: $\sum_{\bmz \in \cal{P}_{d_B}} \W[\bmz|\bmx]{\E} = 1$ \\ 
-        for any $\bmx \in \cal{P}_{d_A}$;
-        \item[(iii)]\label{en:wo3} Bounded: $\abs{\W[\bmy|\bmx]{\E}} \leq \frac{d_A}{d_B}$;
+        \item[(i)]\label{en:wo1} Real-valued: $\W{\E}(\bmz) \in \mathbb{R}^{d^2} \times \mathbb{R}^{d^2}$;
+        \item[(ii)]\label{en:wo2} Normalised: $\sum_{\bmy \in \cal{P}_{d_B}} \W[\bmz|\bmy]{\E} = 1$ \\ 
+        for any $\bmz \in \cal{P}_{d_A}$;
+        \item[(iii)]\label{en:wo3} Bounded: $\abs{\W[\bmy|\bmz]{\E}} \leq \frac{d_A}{d_B}$;
 	    \item[(iv)]\label{en:wo4} $\W[\bmy]{\E(\rho)} = \sum\limits_{\bmz \in \cal{P}_{d_{A}}} \W[\bmy|\bmz]{\E} \W[\bmz]{\rho}$ for any $\bmy \in \cal{P}_{d_B}$.
@@
 
+Within the context of the Wigner representation, we define the re-scaled quasi-distribution
+\begin{equation}
+	W_{\rho|\tau}(\bmz) := \frac{W_\rho (\bmz) }{ W_\tau(\bmz)},
+\end{equation}
+which is well-defined if $\tau$ is a full-rank stabilizer state.
+
+The following lemma shows that the re-scaled Lorenz curves behave in a natural way under tensor products. 
+\begin{proposition}\label{prop:rescaled_multi}
+	Let $\tau_A, \tau_B$ be full rank stabilizer states on systems $A$ and $B$, and let $\rho_A, \rho_B$ be arbitrary states on $A,B$. Then the rescaled quasi-distribution obeys
+\begin{equation}
+W_{\rho_A \otimes \rho_B | \tau_A \otimes \tau_B}(\bmz_A \oplus \bmz_B) =W_{\rho_A | \tau_A}(\bmz_A) W_{\rho_B | \tau_B}(\bmz_B)
+\end{equation}
+\end{proposition}
+\begin{proof} This follows from the multiplicativity of the Wigner distribution,
+\begin{align}
+W_{\rho_A \otimes \rho_B | \tau_A \otimes \tau_B}(\bmz_A \oplus \bmz_B) &= \frac{W_{\rho_A \otimes \rho_B} (\bmz_A \oplus \bmz_B)}{W_{\tau_A \otimes \tau_B} (\bmz_A \oplus \bmz_B)}\nonumber \\
+ = \frac{W_{\rho_A } (\bmz_A )W_{\rho_B } (\bmz_B )}{W_{\tau_A } (\bmz_A )W_{\tau_B } (\bmz_B )} &= W_{\rho_A | \tau_A}(\bmz_A) W_{\rho_B | \tau_B}(\bmz_B). \nonumber
+\end{align}
+\end{proof}
+
 \section{Properties of relative majorization and Lorenz curves}
@@
 
-The following provides equivalent formulations of relative majorization.
+\subsection{Relative majorization for quasi-distributions}
+\label{app:rel_quasi}
+
+We define a Lorenz curve \emph{elbow} as a point where the slope of the curve changes, in accordance to the use of the term for Lorenz curve of proper probability distributions.
+
+Here, we verify useful majorization properties in the context of quasi-probability distributions, starting from the property that the Lorenz curve is concave.
+\begin{lemma}\label{L-concave} Let $\w$ be a quasi-probability distribution and let $\r$ be a probability distribution with strictly non-zero components.
+Then $L_{\w|\r}(x)$ is a concave function on $[0,1]$.
+\end{lemma}
+\begin{proof} 
+Let $x_\star$ be the point where $L_{\w|\r}(x)$ first attains it maximum.
+Therefore, on $[0,x_\star]$ the function rises monotonically to $L_{\w|\r}(x_\star)$, via the sum of all positive entries of $\w$, taken in decreasing order.
+Likewise on $[x_\star, 1]$, the function decreases monotonically from its maximum via the partial sums of the negative entries of $\w$ in decreasing order.
+Let $f_1(x)$ be equal to $L_{\w|\r}(x)$ on $[0, x_\star]$ and $0$ otherwise.
+Also let $f_2(x)$ be equal to $L_{\w|\r}(x)$ on $[x_\star,1]$ and and $0$ otherwise.
+By inspection both $f_1$ and $f_2$ are concave functions, and $f_1(x) + f_2 (x) = L_{\w|\r}(x)$ for all $x\in [0,1]$.
+However, the sum of two concave functions is also concave and the result follows.
+\end{proof}
+
+The following result is used in~\cref{sec:lc} to prove that the Lorenz curve condition due to relative majorization is true for quasi-distributions.
+\begin{proposition}\label{lemma:Lorenz_linearity}
+	Let $\w$ be a quasi-probability distribution and let $\r$ be a probability distribution with strictly non-zero components. 
+	Then, $L_{a\w + b \r | \r} (x) = a L_{\w |\r}(x) + b x$ for any constants $a > 0$ and $b \in \mathbb{R}$.
+\end{proposition}
+\begin{proof} 
+	The Lorenz curve of $a\w + b \r$ relative to $\r$ passes through $(0,0)$ and the points $(\sum_{i=1}^k{r_{\pi(i)}}, \sum_{i=1}^k(a \w + b \r)_{\pi(i)})$ where $\pi$ is the permutation that puts $(a w_i/r_i + b)$ in non-increasing order.
+Since $a > 0$, the permutation $\pi$ puts  $(w_i/r_i)$ in non-increasing order too.
+We thus have
+\begin{align*}
+&\left( \sum_{i=1}^k r_{\pi(i)}, \sum_{i=1}^k(a \w + b \r)_{\pi(i)} \right) = \\ 
+&\left( \sum_{i=1}^k r_{\pi(i)},a \sum_{i=1}^k  w_{\pi(i)} + b\sum_{i=1}^k r_{\pi(i)} \right) \nonumber,
+\end{align*}
+so the value of the Lorenz curve at each potential elbow point $x_k = \sum_{i=1} ^kr_{\pi(i)}$ is given by
+\begin{align}
+&L_{a \w +b \r|\r} (x_k) = a L_{\w|\r} (x_k) + b L_{\r|\r}(x_k) = \nonumber\\
+&a L_{\w|\r} (x_k) + b x_k,
+\end{align}
+so we have $L_{a\w  + b\r|\r} (x) = a L_{\w |\r}(x) + b x$ for any $x \in [0,1]$ due to linearity.
+\end{proof}
+
+The following provides equivalent formulations of relative majorization on quasi-probabilities.
 
 \begin{proposition}\label{prop:rmajor}
-Given probability distributions $\p, \q$, $\r , \r'$, such that the components of $\r$ and $\r'$ are positive, the following statements are equivalent:
+Given quasi-probability distributions $\w, \w'$, $\r , \r'$, such that the components of $\r$ and $\r'$ are positive, the following statements are equivalent:
   \begin{enumerate}
-    \item[(i)] $\q = A\p$ and $\r' = A\r$ for a stochastic map $A$;
-    \item[(ii)]\label{en:tm3} $\sum\limits_{i=1}^n \abs{p_i - r_i t} \leq \sum\limits_{i=1}^n \abs{q_i - r'_i t}$ for all $t \in \mathbb{R}$;
-    \item[(iii)] $L_{\p|\r}(t) \leq L_{\q|\r'}(t)$ for $t\in [0,1)$ and \vspace{5pt}\\ $L_{\p|\r}(1) = L_{\q|\r'}(1)$.
+    \item[(i)] $\w' = A\w$ and $\r' = A\r$ for a stochastic map $A$;
+    \item[(ii)] $L_{\w|\r}(t) \geq L_{\w'|\r'}(t)$ for $t\in [0,1)$ and \vspace{5pt}\\ $L_{\w|\r}(1) = L_{\w'|\r'}(1)$;
+    \item[(iii)] $\sum\limits_{i=1}^n \abs{w_i - r_i t} \geq \sum\limits_{i=1}^n \abs{w'_i - r'_i t}$ for all $t \in \mathbb{R}$.
   \end{enumerate}
 \end{proposition}
-The proofs for these can be found in~\cite{cit:marshall,ruch_mixing_1978,Renes_2016,Buscemi_2017} and references therein.
+\begin{proof}
+	The proofs for these properties on proper probability distributions can be found in~\cite{cit:marshall,ruch_mixing_1978,Renes_2016,Buscemi_2017} and references therein.
+
+	The equivalence between (i) and (ii) on quasi-distributions was proven in~\cref{thm:lcquasi}.
+
+	The equivalence between (i) and (iii) follows from a similar argument.
+	Namely, let $\epsilon > 0$ be such that $\w(\epsilon) \coloneqq \epsilon \w + (1-\epsilon) \r$ and $\w'(\epsilon) \coloneqq \epsilon \w + (1-\epsilon) \r'$ are genuine probability distributions.
+This is guaranteed by picking a sufficiently small $\epsilon > 0$, since $\r$ has positive components.
+We now have that $(\w , \r) \succ (\w', \r')$ if and only if $(\w(\epsilon) , \r) \succ (\w'(\epsilon), \r')$.
+	Moreover, we have that for all $c \in \mathbb{R}$, $\sum_{i=1}^n \abs{w(\epsilon)_i - r_i c} \geq \sum_{i=1}^n \abs{w'(\epsilon)_i - r'_i c}$, which leads to
+	\begin{align*}
+		\sum\limits_{i=1}^n \abs{w_i - r_i \frac{\epsilon + c - 1}{\epsilon}} \geq \sum\limits_{i=1}^n \abs{w'_i - r'_i \frac{\epsilon + c - 1}{\epsilon}}
+	\end{align*}
+Replacing $t = (\epsilon + c - 1)/\epsilon$, we see that $t$ can attain any real value for some value of $c$, so we retrieve the property on quasi-distributions $\w, \w'$.
+\end{proof}
 
@@
 \begin{equation}
-	\Gamma_{\bma}(\x) := \bigoplus_{i=1}^N x_i \eta_{a_i},
+	\Gamma_{\bma}(\bmz) := \bigoplus_{i=1}^N x_i \eta_{a_i},
 \end{equation}
@@
 \end{equation}
-that obeys $(\Gamma^{-1}_{\bma} \circ \Gamma_{\bma}) (\x) = \x$ for all $\x \in \mathbb{R}^N$.
+that obeys $(\Gamma^{-1}_{\bma} \circ \Gamma_{\bma}) (\bmz) = \bmz$ for all $\bmz \in \mathbb{R}^N$.
 
@@
 
-\subsection{Relative majorization for quasi-distributions}
-\label{app:rel_quasi}
-
-We verify that the Lorenz curve is concave in the context of quasi-distributions.
-\begin{lemma}\label{L-concave} Let $\p$ be a quasi-probability distribution and let $\r$ be a probability distribution with strictly non-zero components.
-Then $L_{\p|\r}(x)$ is a concave function on $[0,1]$.
-\end{lemma}
-\begin{proof} 
-Let $x_\star$ be the point where $L_{\p|\r}(x)$ first attains it maximum.
-Therefore, on $[0,x_\star]$ the function rises monotonically to $L_{\p|\r}(x_\star)$, via the sum of all positive entries of $\p$, taken in decreasing order.
-Likewise on $[x_\star, 1]$, the function decreases monotonically from its maximum via the partial sums of the negative entries of $\p$ in decreasing order.
-Let $f_1(x)$ be equal to $L_{\p|\r}(x)$ on $[0, x_\star]$ and $0$ otherwise.
-Also let $f_2(x)$ be equal to $L_{\p|\r}(x)$ on $[x_\star,1]$ and and $0$ otherwise.
-By inspection both $f_1$ and $f_2$ are concave functions, and $f_1(x) + f_2 (x) = L_{\p|\r}(x)$ for all $x\in [0,1]$.
-However, the sum of two concave functions is also concave and the result follows.
-\end{proof}
-
-The following result is used in~\cref{sec:lc} to prove that the Lorenz curve condition due to relative majorization is true for quasi-distributions.
-\begin{proposition}\label{lemma:Lorenz_linearity}
-	Let $\p$ be a quasi-probability distribution and let $\r$ be a probability distribution with strictly non-zero components. 
-	Then, $L_{a\p + b \r | \r} (x) = a L_{\p |\r}(x) + b x$ for any constants $a > 0$ and $b \in \mathbb{R}$.
-\end{proposition}
-\begin{proof} 
-	The Lorenz curve of $a\p + b \r$ relative to $\r$ passes through $(0,0)$ and the points $(\sum_{i=1}^k{r_{\pi(i)}}, \sum_{i=1}^k(a \p + b \r)_{\pi(i)})$ where $\pi$ is the permutation that puts $(a p_i/r_i + b)$ in non-increasing order.
-Since $a > 0$, the permutation $\pi$ puts  $(p_i/r_i)$ in non-increasing order too.
-We thus have
-\begin{align*}
-&\left( \sum_{i=1}^kr_{\pi(i)}, \sum_{i=1}^k(a \p + b \r)_{\pi(i)} \right) = \\ 
-&\left( \sum_{i=1}^k r_{\pi(i)},a \sum_{i=1}^k  p_{\pi(i)} + b\sum_{i=1}^k r_{\pi(i)} \right) \nonumber,
-\end{align*}
-so the value of the Lorenz curve at each potential elbow point $x_k = \sum_{i=1} ^kr_{\pi(i)}$ is given by
-\begin{align}
-&L_{a \p +b \r|\r} (x_k) = a L_{\p|\r} (x_k) + b L_{\r|\r}(x_k) = \nonumber\\
-&a L_{\p|\r} (x_k) + b x_k,
-\end{align}
-so we have $L_{a\p  + b\r|\r} (x) = a L_{\p |\r}(x) + b x$ for any $x \in [0,1]$ due to linearity.
-\end{proof}
-
-Within the context of the Wigner representation, we define the re-scaled quasi-distribution
-\begin{equation}
-	W_{\rho|\tau}(\x) := \frac{W_\rho (\x) }{ W_\tau(\x)},
-\end{equation}
-which is well-defined if $\tau$ is a full-rank stabilizer state.
-
-The following lemma shows that the re-scaled Lorenz curves behave in a natural way under tensor products. 
-\begin{proposition}\label{prop:rescaled_multi}
-	Let $\tau_A, \tau_B$ be full rank stabilizer states on systems $A$ and $B$, and let $\rho_A, \rho_B$ be arbitrary states on $A,B$. Then the rescaled quasi-distribution obeys
-\begin{equation}
-W_{\rho_A \otimes \rho_B | \tau_A \otimes \tau_B}(\bmx_A \oplus \bmx_B) =W_{\rho_A | \tau_A}(\x_A) W_{\rho_B | \tau_B}(\x_B)
-\end{equation}
-\end{proposition}
-\begin{proof} This follows from the multiplicativity of the Wigner distribution,
-\begin{align}
-W_{\rho_A \otimes \rho_B | \tau_A \otimes \tau_B}(\bmx_A \oplus \bmx_B) &= \frac{W_{\rho_A \otimes \rho_B} (\x_A \oplus \x_B)}{W_{\tau_A \otimes \tau_B} (\x_A \oplus \x_B)}\nonumber \\
- &= \frac{W_{\rho_A } (\x_A )W_{\rho_B } (\x_B )}{W_{\tau_A } (\x_A )W_{\tau_B } (\x_B )}\nonumber \\
-  &= W_{\rho_A | \tau_A}(\x_A) W_{\rho_B | \tau_B}(\x_B). \nonumber
-\end{align}
-\end{proof}
-
 \subsection{Component-multiplicity pairs}
@@
 
-In general, a $1$--copy $d$--dimensional state $\rho$ is described by its $d^2$--dimensional Wigner distribution $\W{\rho}(\bmx)$. 
-The distribution $\W{\rho}(\bmx)$ is defined on the phase space, but it can be convenient to re-express this using vector notation.
+In general, a $1$--copy $d$--dimensional state $\rho$ is described by its $d^2$--dimensional Wigner distribution $\W{\rho}(\bmz)$. 
+The distribution $\W{\rho}(\bmz)$ is defined on the phase space, but it can be convenient to re-express this using vector notation.
 We discuss this in terms of Wigner distributions, but there is nothing to prevent the discussion from applying to rescaled Wigner distributions as well.
 
-To each Wigner distribution $W_\rho(\x)$ we can associate \emph{component-multiplicity} pairs $\{(w_i, m_i)\}$ where the value $w_i$ occurs in the distribution $W_\rho(\x)$ with multiplicity $m_i$.
+To each Wigner distribution $W_\rho(\bmz)$ we can associate \emph{component-multiplicity} pairs $\{(w_i, m_i)\}$ where the value $w_i$ occurs in the distribution $W_\rho(\bmz)$ with multiplicity $m_i$.
 
@@
 \begin{equation}
-W_{\rho_S}(\x) = (-1/3, 1/6,  1/6,  1/6,  1/6,  1/6,  1/6,  1/6,  1/6)
+W_{\rho_S}(\bmz) = (-1/3, 1/6,  1/6,  1/6,  1/6,  1/6,  1/6,  1/6,  1/6)
 \end{equation}
@@
 However, we might also wish more freedom and not require that the different $w_i$ values are all distinct.
-For example, the component-multiplity pairs $\{(-1/3, 1), (1/6, 2), (1/6, 3), (1/6, 3)\}$ also describe $W_{\rho_S}(\x)$.
+For example, the component-multiplity pairs $\{(-1/3, 1), (1/6, 2), (1/6, 3), (1/6, 3)\}$ also describe $W_{\rho_S}(\bmz)$.
 
@@
 \begin{lemma}
-Consider two Wigner distributions $\W{\rho_A}(\x_A), \W{\rho_B}(\x_B)$ with component-multiplicity pairs 
+Consider two Wigner distributions $\W{\rho_A}(\bmz_A), \W{\rho_B}(\bmz_B)$ with component-multiplicity pairs 
 \begin{equation}
@@
 \end{equation}
-respectively. Then, $\{(w_i w_j', m_i m_j')\}$ gives component-multiplicity pairs for $\W{\rho_A \otimes \rho_B}(\x_A \oplus \x_B)$.
+respectively. Then, $\{(w_i w_j', m_i m_j')\}$ gives component-multiplicity pairs for $\W{\rho_A \otimes \rho_B}(\bmz_A \oplus \bmz_B)$.
 \end{lemma}
 \begin{proof}
-	This result is true because all components of $\W{\rho_A \otimes \rho_B}(\x_A \oplus \x_B)$ are of the form $w_i w_j'$ and 
+	This result is true because all components of $\W{\rho_A \otimes \rho_B}(\bmz_A \oplus \bmz_B)$ are of the form $w_i w_j'$ and 
 \begin{equation*}
@@
 where $d_A, d_B$ are the dimensions of $\rho_A, \rho_B$ respectively, and
-so the set $\{(w_i w_j', m_i m_j')\}$ contains exactly the Wigner components of $\W{\rho_A \otimes \rho_B}(\x_A \oplus \x_B)$.
+so the set $\{(w_i w_j', m_i m_j')\}$ contains exactly the Wigner components of $\W{\rho_A \otimes \rho_B}(\bmz_A \oplus \bmz_B)$.
 \end{proof}
@@
 \begin{lemma}\label{lem:ncopycomponents}
-	Suppose $W_\rho(\x)$ has a set of $D$ component-multiplicity pairs $\{(w_i, m_i)\}$.
-Then, $W_{\rho^{\otimes n}} (\x)$ has component-multiplicity pairs $\{(W_{\q}, M_{\q})\}$, with index $\q$ running through all vectors $(q_1, \dots, q_D)$, where $q_1, \dots, q_D$ are non-negative integers that sum to $n$, and
+	Suppose $W_\rho(\bmz)$ has a set of $D$ component-multiplicity pairs $\{(w_i, m_i)\}$.
+Then, $W_{\rho^{\otimes n}} (\bmz)$ has component-multiplicity pairs $\{(W_{\q}, M_{\q})\}$, with index $\q$ running through all vectors $(q_1, \dots, q_D)$, where $q_1, \dots, q_D$ are non-negative integers that sum to $n$, and
 \begin{align}
@@
 \end{equation*}
-Therefore, $\{ (W_{\bmk}, M_{\bmk}) \}_{\bmk \in C_D^1}$ is a complete set of component-multiplicity pairs for $W_\rho(\x)$.
-
-	Assume that $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$ as given in~\cref{eq:M,eq:W} is a complete set of component-multiplicity pairs for the $n$--copy distribution $W_{\rho^{\otimes n}}(\bmx) = W_{\rho}(\bmx)^{\otimes n}$.
-	By construction, the distribution $W_{\rho}(\bmx)^{\otimes (n+1)} = W_{\rho}(\bmx)^{\otimes n} \otimes W_{\rho}(\bmx)$, so it admits the complete set of component multiplicity pairs
+Therefore, $\{ (W_{\bmk}, M_{\bmk}) \}_{\bmk \in C_D^1}$ is a complete set of component-multiplicity pairs for $W_\rho(\bmz)$.
+
+	Assume that $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$ as given in~\cref{eq:M,eq:W} is a complete set of component-multiplicity pairs for the $n$--copy distribution $W_{\rho^{\otimes n}}(\bmz) = W_{\rho}(\bmz)^{\otimes n}$.
+	By construction, the distribution $W_{\rho}(\bmz)^{\otimes (n+1)} = W_{\rho}(\bmz)^{\otimes n} \otimes W_{\rho}(\bmz)$, so it admits the complete set of component multiplicity pairs
 \begin{equation}
@@
 
-	Consider the component sum of the distribution $W_{\rho}(\bmx)^{\otimes (n+1)}$,
+	Consider the component sum of the distribution $W_{\rho}(\bmz)^{\otimes (n+1)}$,
 \begin{align*}
@@
 \end{align*}
-which is the dimension of $W_{\rho}(\bmx)^{\otimes (n+1)}$.
-
-Therefore, $\{ (W_{\bmq}, M_{\bmq}) \}_{\bmq \in C_D^{n+1}}$ contains exactly the components of $W_{\rho}(\bmx)^{\otimes n}$, completing the proof.
+which is the dimension of $W_{\rho}(\bmz)^{\otimes (n+1)}$.
+
+Therefore, $\{ (W_{\bmq}, M_{\bmq}) \}_{\bmq \in C_D^{n+1}}$ contains exactly the components of $W_{\rho}(\bmz)^{\otimes n}$, completing the proof.
 \end{proof}
@@
 \begin{proof}
-	We denote the Wigner distributions of the states single-component vectors $\w(\rho)=W_\rho(x)$ and $ \w(\sigma)=W_\sigma(x)$. Likewise, we write $\w(\rho|\sigma) = W_{\rho|\tau}(\x)$.
+	We denote the Wigner distributions of the states single-component vectors $\w(\rho)=W_\rho(x)$ and $ \w(\sigma)=W_\sigma(x)$. Likewise, we write $\w(\rho|\sigma) = W_{\rho|\tau}(\bmz)$.
 	We choose the component indexing so that $\w(\rho|\sigma)^\downarrow = \w(\rho|\sigma)$ and so the components are sorted in non-increasing order.
@@
 	L_\star &:=	\lc{\rho}{\sigma}(x_{i_\star}) 
-		= \sum\limits_{\bmx: \W[\bmx]{\rho} \geq 0}\hspace{-5pt} \W[\bmx]{\rho} \nonumber \\
+		= \sum\limits_{\bmz: \W[\bmz]{\rho} \geq 0}\hspace{-5pt} \W[\bmz]{\rho} \nonumber \\
 		&= 1 + \sn{\rho}.
@@
 	\zeta &= \sum_{k\in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}, \nonumber\\
-	\alpha_k &= \<E_k| A_{\x_\star} |E_k\>,
-\end{align}
-and $\x_\star = \arg\!\min W_\tau(\x)$. The primed variables are defined similarly for the output system.
+	\alpha_k &= \<E_k| A_{\bmz_\star} |E_k\>,
+\end{align}
+and $\bmz_\star = \arg\!\min W_\tau(\bmz)$. The primed variables are defined similarly for the output system.
 \end{theorem}
@@
 \begin{equation}
-	( W_{\rho_n}(\bmx), W_{\tau_n}(\bmx) ) \succ ( W_{\rho'_m}(\bmx), W_{\tau'_m}(\bmx) ),
+	( W_{\rho_n}(\bmz), W_{\tau_n}(\bmz) ) \succ ( W_{\rho'_m}(\bmz), W_{\tau'_m}(\bmz) ),
 \end{equation}
@@
 
-We now consider the rescaled Wigner distribution $W_{\rho | \tau}(\x) \coloneqq W_\rho(\x)/W_\tau(\x)$, which is well-defined since $\tau$ is full-rank. 
+We now consider the rescaled Wigner distribution $W_{\rho | \tau}(\bmz) \coloneqq W_\rho(\bmz)/W_\tau(\bmz)$, which is well-defined since $\tau$ is full-rank. 
 Due to the multiplicative property of the Wigner distribution, the rescaled distribution is also multiplicative in the sense that
 \begin{equation}
-	W_{\rho \otimes \rho' | \tau \otimes \tau'} (\x_1 \oplus \x_2) = W_{\rho | \tau}(\x_1)W_{\rho' | \tau'}(\x_2),
+	W_{\rho \otimes \rho' | \tau \otimes \tau'} (\bmz_1 \oplus \bmz_2) = W_{\rho | \tau}(\bmz_1)W_{\rho' | \tau'}(\bmz_2),
 \end{equation}
@@
 \begin{align}
-	W_{\rho_n |\tau_n} (\x) &= \prod_{i=1}^n W_{\rho|\tau}(\x_i)\\
-	W_{\rho_n } (\x) &= \prod_{i=1}^n W_\rho(\x_i)
-\end{align}
-where $\x = \oplus_{i=1}^n \x_i \in \mathbb{Z}_3^{2n}$ is the phase space point for the full system in terms of those of the individual subsystems.
-
-The points defining the Lorenz curve $L_{\rho_n |\tau_n}(x)$ are obtained from sorting the components of $W_{\rho_n |\tau_n}(\x)$ in non-increasing order and then computing the partial sums of $W_{\rho_n |\tau_n}(\pi(\x))$ where $\pi$ is the permutation that realises the sorting.
+	W_{\rho_n |\tau_n} (\bmz) &= \prod_{i=1}^n W_{\rho|\tau}(\bmz_i)\\
+	W_{\rho_n } (\bmz) &= \prod_{i=1}^n W_\rho(\bmz_i)
+\end{align}
+where $\bmz = \oplus_{i=1}^n \bmz_i \in \mathbb{Z}_3^{2n}$ is the phase space point for the full system in terms of those of the individual subsystems.
+
+The points defining the Lorenz curve $L_{\rho_n |\tau_n}(x)$ are obtained from sorting the components of $W_{\rho_n |\tau_n}(\bmz)$ in non-increasing order and then computing the partial sums of $W_{\rho_n |\tau_n}(\pi(\bmz))$ where $\pi$ is the permutation that realises the sorting.
 However, similar to the unital protocol analysis, we use the slope constraint (\cref{prop:first_elb}) obtained by considering the line segments connecting the origin to the first elbow of both Lorenz curves.
 
-The Wigner distribution of a single noisy Strange state consists of 1 negative component $W_{\rho}(\mathbf{0}) = -v(\epsilon)$ and 8 positive components $W_{\rho}(\bmx) = u(\epsilon)$ for $\bmx \neq \bmo$.
-The Wigner distribution of the full-rank, stabilizer equilibrium state $\tau$ is $W_{\tau}(\bmx) > 0$ for all $\bmx \in \mathbb{Z}_3^2$.
-
-Assume that the smallest component of the distribution $W_\tau(\x)$ is at $\x=\x_\star$.
+The Wigner distribution of a single noisy Strange state consists of 1 negative component $W_{\rho}(\mathbf{0}) = -v(\epsilon)$ and 8 positive components $W_{\rho}(\bmz) = u(\epsilon)$ for $\bmz \neq \bmo$.
+The Wigner distribution of the full-rank, stabilizer equilibrium state $\tau$ is $W_{\tau}(\bmz) > 0$ for all $\bmz \in \mathbb{Z}_3^2$.
+
+Assume that the smallest component of the distribution $W_\tau(\bmz)$ is at $\bmz=\bmz_\star$.
 Since the magic content of the state is unchanged under a Clifford unitary $C$, we can instead consider the state
 \begin{equation}
-\rho_S(\epsilon) \rightarrow C \rho_S(\epsilon) C^\dagger = D_{\x_\star} \rho_S(\epsilon) D_{\x_\star}^\dagger,
-\end{equation}
-which has its single negative Wigner component $-v(\epsilon)$ at the point $\x_\star$.
+\rho_S(\epsilon) \rightarrow C \rho_S(\epsilon) C^\dagger = D_{\bmz_\star} \rho_S(\epsilon) D_{\bmz_\star}^\dagger,
+\end{equation}
+which has its single negative Wigner component $-v(\epsilon)$ at the point $\bmz_\star$.
 
@@
 \begin{equation}
-	W_{\rho_n|\tau_n} = \left(\frac{-v}{W_{\tau}(\x_\star)}\right)^{i_{\x_\star}} \prod_{\bmx \neq \x_\star} \left(\frac{u}{W_{\tau}(\bmx)}\right)^{i_{\bmx}},
+	W_{\rho_n|\tau_n} = \left(\frac{-v}{W_{\tau}(\bmz_\star)}\right)^{i_{\bmz_\star}} \prod_{\bmz \neq \bmz_\star} \left(\frac{u}{W_{\tau}(\bmz)}\right)^{i_{\bmz}},
 \end{equation}
@@
 \begin{align}
-&0 \leq i_{\bmx} \leq n \mbox{ for all } \bmx \in \mathbb{Z}_3^2, \nonumber \\
-&\sum_{\bmx \in \mathbb{Z}_3^2} i_{\bmx} = n.
+&0 \leq i_{\bmz} \leq n \mbox{ for all } \bmz \in \mathbb{Z}_3^2, \nonumber \\
+&\sum_{\bmz \in \mathbb{Z}_3^2} i_{\bmz} = n.
 \end{align}
 We now compute the largest rescaled component.
-Firstly, note that $n$ is even, so we require that $i_{\x_\star} \in \{0,2,\dots,n\}$ for the component to be positive.
-Then, we have that $v \geq u$ because $\epsilon \leq 3/7$, and we have already ensured that $W_{\tau}(\x_\star) \leq W_{\tau}(\bmx)$ for all $\bmx \in \mathbb{Z}_3^2$.
-Therefore, the largest rescaled component occurs when $i_{\x_{\star}} = n$ and $i_{\x} = 0$ for $\x \neq \x_\star$ and is equal to $(v/W_{\tau}(\x_\star))^n$.
+Firstly, note that $n$ is even, so we require that $i_{\bmz_\star} \in \{0,2,\dots,n\}$ for the component to be positive.
+Then, we have that $v \geq u$ because $\epsilon \leq 3/7$, and we have already ensured that $W_{\tau}(\bmz_\star) \leq W_{\tau}(\bmz)$ for all $\bmz \in \mathbb{Z}_3^2$.
+Therefore, the largest rescaled component occurs when $i_{\bmz_{\star}} = n$ and $i_{\bmz} = 0$ for $\bmz \neq \bmz_\star$ and is equal to $(v/W_{\tau}(\bmz_\star))^n$.
 Accordingly, the coordinates of the first Lorenz curve point after the origin are given by
 \begin{equation}
-	(x_0, L_0) = ((W_{\tau}(\x_\star))^n, v^n)
+	(x_0, L_0) = ((W_{\tau}(\bmz_\star))^n, v^n)
 \end{equation}
@@
 \begin{align}
-	W_{\tau}(\x_\star) &= \frac{1}{3\Z}\tr\left[ A_{\x_\star}e^{-\beta H} \right] \nonumber\\
-	&= \frac{e^{\beta F}}{3} \tr\left[ A_{\x_\star}\sum_{k \in \mathbb{Z}_3} e^{-\beta E_k} |E_k\>\<E_k| \right] \\
+	W_{\tau}(\bmz_\star) &= \frac{1}{3\Z}\tr\left[ A_{\bmz_\star}e^{-\beta H} \right] \nonumber\\
+	&= \frac{e^{\beta F}}{3} \tr\left[ A_{\bmz_\star}\sum_{k \in \mathbb{Z}_3} e^{-\beta E_k} |E_k\>\<E_k| \right] \\
 	&= \frac{e^{\beta F}}{3} \sum_{r \in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}
@@
 \begin{align}
-\alpha_k := \<E_k |A_{\x_\star} |E_k\> \\
+\alpha_k := \<E_k |A_{\bmz_\star} |E_k\> \\
 \zeta :=  \sum_{k \in \mathbb{Z}_3} \alpha_k e^{-\beta E_k},
@@
 \begin{equation}
-	\alpha_k = \<E_k | A_{\bmx_{\star}} |E_k\> = d W_{|E_k\>\<E_k|}(\bmx_{\star})
-\end{equation}
-Since each $|E_k\>\<E_k|$ is a stabilizer state, their Wigner distributions have orthogonal supports in the phase space, so only one of them, say $k = k_{\star}$ contains point $\bmx_{\star}$ in its support.
-Additionally, its distribution is uniform on its support, so $W_{|E_{k_\star}\>\<E_{k_\star}|}(\bmx_{\star}) = 1/d$.
+	\alpha_k = \<E_k | A_{\bmz_{\star}} |E_k\> = d W_{|E_k\>\<E_k|}(\bmz_{\star})
+\end{equation}
+Since each $|E_k\>\<E_k|$ is a stabilizer state, their Wigner distributions have orthogonal supports in the phase space, so only one of them, say $k = k_{\star}$ contains point $\bmz_{\star}$ in its support.
+Additionally, its distribution is uniform on its support, so $W_{|E_{k_\star}\>\<E_{k_\star}|}(\bmz_{\star}) = 1/d$.
 
@@
 \phi &= -\beta^{-1}\ln (\sum_k \alpha_k e^{-\beta E_k}) \nonumber \\
-&=E_{k_{\star}} -kT \ln (d W_{|E_{k_\star}\>\<E_{k_\star}|}(\bmx_{\star})) =E_{k_{\star}}.
+&=E_{k_{\star}} -kT \ln (d W_{|E_{k_\star}\>\<E_{k_\star}|}(\bmz_{\star})) =E_{k_{\star}}.
 \end{align}
@@
 \begin{proof}
-The proof proceeds in the same manner as in~\cref{thm:free-energy-bound-proof} up to the point where we need to evaluate $W_{\rho_n |\tau_n} (\x)$ and $W_{\rho_n}(\x)$ explicitly, beyond which we do not have the freedom of additional Clifford processing.
+The proof proceeds in the same manner as in~\cref{thm:free-energy-bound-proof} up to the point where we need to evaluate $W_{\rho_n |\tau_n} (\bmz)$ and $W_{\rho_n}(\bmz)$ explicitly, beyond which we do not have the freedom of additional Clifford processing.
 
@@
 \begin{align}
-	\W[\bmx]{\tau} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z}W_{|k\>\<k|}(x, p) \nonumber\\
+	\W[\bmz]{\tau} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z}W_{|k\>\<k|}(x, p) \nonumber\\
 	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z} \delta_{x, k} = \frac{e^{-\beta E_x}}{3\Z},
@@
 where $x$ labels one of the three vertical lines in the phase space.
-The rescaled Wigner distribution $W_{\rho|\tau}(\x)$ can now be computed.
+The rescaled Wigner distribution $W_{\rho|\tau}(\bmz)$ can now be computed.
 It has $9$ components, but these come with multiplicities.
@@
     \includegraphics[scale=0.35]{figs/pd_split_thermal.pdf}
-    \caption{\textbf{Qutrit phase space regions for $W_{\rho | \tau}(\x)$.}
+    \caption{\textbf{Qutrit phase space regions for $W_{\rho | \tau}(\bmz)$.}
     Here, the negative component of the magic state overlaps the Wigner distribution of $|0\>$.
@@
 
-We denote by $\w(\rho), \w(\rho|\tau)$ the unique values occurring in $W_\rho(\x), W_{\rho|\tau}(\x)$ respectively and $\bmm$ the vector of associated multiplicities of each value in $W_\rho(\x)$.
+We denote by $\w(\rho), \w(\rho|\tau)$ the unique values occurring in $W_\rho(\bmz), W_{\rho|\tau}(\bmz)$ respectively and $\bmm$ the vector of associated multiplicities of each value in $W_\rho(\bmz)$.
 The component values and multiplicities of the relevant distributions in the four distinct regions are given by
@@
 
-In order to construct the $n$--copy Lorenz curve $L_{\rho_n|\tau_n}(x)$ we need to order the components of the distribution, $w(\rho_{\rm{S}} | \tau)_{ijk}$ in decreasing order, and identify the sequence of indices that give us $W_{\rho_n}(\pi(\x))$.
-
-However, it again suffices to use only the constraint from the first elbow $(x_0, L_0)$ of $L_{\rho_n|\tau_n}(\x)$. We therefore compute the largest component 
+In order to construct the $n$--copy Lorenz curve $L_{\rho_n|\tau_n}(x)$ we need to order the components of the distribution, $w(\rho_{\rm{S}} | \tau)_{ijk}$ in decreasing order, and identify the sequence of indices that give us $W_{\rho_n}(\pi(\bmz))$.
+
+However, it again suffices to use only the constraint from the first elbow $(x_0, L_0)$ of $L_{\rho_n|\tau_n}(\bmz)$. We therefore compute the largest component 
 \begin{equation}
@@
 
-\newpage
 \section{Single-shot entropies on quasi-distributions and magic distillation bounds}
@@
 \begin{equation}
-	D_\infty(W_\rho || W_\tau) := \log  \max_{\x} \frac{W_\rho(\x)}{W_\tau(\x)},
+	D_\infty(W_\rho || W_\tau) := \log  \max_{\bmz} \frac{W_\rho(\bmz)}{W_\tau(\bmz)},
 \end{equation}
@@
 \begin{proof}
-	Since $\tau$ is in the interior of $\F$, its Wigner function obeys $W_\tau(\x) >0$ for all points $\x$ in the phase space. 
-In general, $W_\rho(\x)$ is a quasi-distribution, but the given form of $\alpha$ ensures that $W_{\rho}(\bmx)^\alpha \geq 0$. 
+	Since $\tau$ is in the interior of $\F$, its Wigner function obeys $W_\tau(\bmz) >0$ for all points $\bmz$ in the phase space. 
+In general, $W_\rho(\bmz)$ is a quasi-distribution, but the given form of $\alpha$ ensures that $W_{\rho}(\bmz)^\alpha \geq 0$. 
 Therefore $D_\infty (W_\rho || W_\tau)$ is always well-defined.
@@
 \begin{equation}
-	D_\infty(W_\rho || W_\tau) =\log  \max_{\x} \frac{W_\rho}{W_\tau},
+	D_\infty(W_\rho || W_\tau) =\log  \max_{\bmz} \frac{W_\rho}{W_\tau},
 \end{equation}
@@
 2.
-$D_\infty(W_\rho || W_\tau) = 0$ implies that $\max_{\x} \frac{W_\rho(\x)}{W_\tau(\x)}=1$ and the initial slope of $L_{\rho|\tau}(x)$ is $1$.
-From the concavity of the function this implies that the slope of $L_{\rho|\tau}(x)$ must equal $1$ throughout the interval $[0,1]$ and this, together with the definition of the Lorenz curve, implies that $W_\rho(\x)/W_\tau(\x) = 1$ for all $\x$.
-Since the Wigner representation $\rho \mapsto W_\rho(\x)$ is bijective this implies that $\rho = \tau$ only.
+$D_\infty(W_\rho || W_\tau) = 0$ implies that $\max_{\bmz} \frac{W_\rho(\bmz)}{W_\tau(\bmz)}=1$ and the initial slope of $L_{\rho|\tau}(x)$ is $1$.
+From the concavity of the function this implies that the slope of $L_{\rho|\tau}(x)$ must equal $1$ throughout the interval $[0,1]$ and this, together with the definition of the Lorenz curve, implies that $W_\rho(\bmz)/W_\tau(\bmz) = 1$ for all $\bmz$.
+Since the Wigner representation $\rho \mapsto W_\rho(\bmz)$ is bijective this implies that $\rho = \tau$ only.
 The converse holds by inspection.
@@
 
-If we now let $\w = W_{\rho|\tau}(\x) := W_{\rho}(\x) /W_{\tau}(\x)$ we have
-\begin{equation}
-\max_{\x_1, \x_2, \dots ,\x_{2n}} \prod_{k=1}^{2n} W_{\rho|\tau}(\x_k) = \left( \max_{\x_1, \x_2} W_{\rho|\tau}(\x_1)W_{\rho|\tau}(\x_2) \right)^n
+If we now let $\w = W_{\rho|\tau}(\bmz) := W_{\rho}(\bmz) /W_{\tau}(\bmz)$ we have
+\begin{equation}
+\max_{\bmz_1, \bmz_2, \dots ,\bmz_{2n}} \prod_{k=1}^{2n} W_{\rho|\tau}(\bmz_k) = \left( \max_{\bmz_1, \bmz_2} W_{\rho|\tau}(\bmz_1)W_{\rho|\tau}(\bmz_2) \right)^n
 \end{equation}
@@
 4.
-The free operation $\E$ in the Wigner representation corresponds to a stochastic map, which sends $W_\tau(\x)$ to $W_{\E(\tau)}(\x)$, which is another strictly positive probability distribution on the phase space, due to $\E(\tau)$ being in the interior of $\F$.
+The free operation $\E$ in the Wigner representation corresponds to a stochastic map, which sends $W_\tau(\bmz)$ to $W_{\E(\tau)}(\bmz)$, which is another strictly positive probability distribution on the phase space, due to $\E(\tau)$ being in the interior of $\F$.
 Moreover, $(W_\rho, W_\tau ) \succ (W_{\E(\rho)} , W_{\E(\tau)})$.
@@
 \begin{equation}
-	H_\alpha(W_\rho) := \frac{1}{1-\alpha} \log \sum_{\bmx} W_{\rho}(\bmx)^\alpha,
+	H_\alpha(W_\rho) := \frac{1}{1-\alpha} \log \sum_{\bmz} W_{\rho}(\bmz)^\alpha,
 \end{equation}
@@
 \begin{proof}
-We have $\alpha = \frac{2a}{2b+1} \geq \frac{2b}{2b-1} > 1$ and $\alpha$ is a rational with even numerator and odd denominator, so $\sum_i x_i^\alpha > 0$ and $H_\alpha(\x)$ is well-defined for all quasi-distributions $\x$.
-
-Given a fixed $\alpha$ for which $H_\alpha(\x)$ is well-defined, the function $H_\alpha$ is real-valued, smooth on the interior of $\mathcal{Q}^\downarrow$ and symmetric on any component permutation of $\x$.
+We have $\alpha = \frac{2a}{2b+1} \geq \frac{2b}{2b-1} > 1$ and $\alpha$ is a rational with even numerator and odd denominator, so $\sum_i x_i^\alpha > 0$ and $H_\alpha(\bmz)$ is well-defined for all quasi-distributions $\bmz$.
+
+Given a fixed $\alpha$ for which $H_\alpha(\bmz)$ is well-defined, the function $H_\alpha$ is real-valued, smooth on the interior of $\mathcal{Q}^\downarrow$ and symmetric on any component permutation of $\bmz$.
 
@@
 \end{proof}
-We note that if $\alpha =a/b$ with both $a$ and $b$ odd, then $H_\alpha$ is not well-defined for all quasi-probabilities, however if the actual set of quasi-distributions has a sufficiently bounded negativity, then $\log \sum_{\x} W_\rho(\x)^\alpha$ can still be obtained for $a$ odd, provided the sum is never negative.
+We note that if $\alpha =a/b$ with both $a$ and $b$ odd, then $H_\alpha$ is not well-defined for all quasi-probabilities, however if the actual set of quasi-distributions has a sufficiently bounded negativity, then $\log \sum_{\bmz} W_\rho(\bmz)^\alpha$ can still be obtained for $a$ odd, provided the sum is never negative.
 
@@
 \begin{proof} 
-If we have $H_\alpha (W_\rho) <0 $ for $\alpha >1$ then this implies that $\log \sum_{\x} W_\rho (\x)^\alpha > 1$, however it is known that $H_\alpha$ is always non-negative on probability distributions and therefore $W_\rho(\x)$ must be a strict quasi-distribution with negativity.
+If we have $H_\alpha (W_\rho) <0 $ for $\alpha >1$ then this implies that $\log \sum_{\bmz} W_\rho (\bmz)^\alpha > 1$, however it is known that $H_\alpha$ is always non-negative on probability distributions and therefore $W_\rho(\bmz)$ must be a strict quasi-distribution with negativity.
 
 Conversely, suppose $\rho$ has negativity in its Wigner representation.
-This implies that $\sum_{\x} |W_\rho (\x)| >1$.
-We now consider $\sum_{\x} W_\rho (\x)^{a/b}$ for $a/b >1$ and $a$ even and $b$ odd.
+This implies that $\sum_{\bmz} |W_\rho (\bmz)| >1$.
+We now consider $\sum_{\bmz} W_\rho (\bmz)^{a/b}$ for $a/b >1$ and $a$ even and $b$ odd.
 We have that
 \begin{align}
-\sum_{\x} W_\rho (\x)^{a/b} &= \sum_{\x} |W_\rho (\x)|^{a/b} \nonumber \\
-&= \sum_{\x} |W_\rho (\x)|^{1+ \epsilon},
+\sum_{\bmz} W_\rho (\bmz)^{a/b} &= \sum_{\bmz} |W_\rho (\bmz)|^{a/b} \nonumber \\
+&= \sum_{\bmz} |W_\rho (\bmz)|^{1+ \epsilon},
 \end{align}
@@
 \begin{equation}
-\sum_{\x} |W_\rho (\x)|^{1+ \epsilon_n} \rightarrow \sum_{\x} |W_\rho (\x)| >1.
-\end{equation}
-Since $\frac{1}{1-\alpha}= -\frac{b_n}{a_n} <0$ for any $n$ it follows that $H_\alpha (W_\rho) = \frac{1}{1-\alpha} \log \sum_{\x} W_\rho (\x)^\alpha  <0 $ at some point in the sequence, which completes the proof.
+\sum_{\bmz} |W_\rho (\bmz)|^{1+ \epsilon_n} \rightarrow \sum_{\bmz} |W_\rho (\bmz)| >1.
+\end{equation}
+Since $\frac{1}{1-\alpha}= -\frac{b_n}{a_n} <0$ for any $n$ it follows that $H_\alpha (W_\rho) = \frac{1}{1-\alpha} \log \sum_{\bmz} W_\rho (\bmz)^\alpha  <0 $ at some point in the sequence, which completes the proof.
 \end{proof}
@@
 \begin{equation}
-	D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) := \frac{1}{\alpha - 1} \log \sum_{\bmx} W_{\rho}(\bmx)^\alpha W_{\tau}(\bmx)^{1-\alpha},
+	D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) := \frac{1}{\alpha - 1} \log \sum_{\bmz} W_{\rho}(\bmz)^\alpha W_{\tau}(\bmz)^{1-\alpha},
 \end{equation}
@@
 	\end{equation}
-	where $\alpha = 2c / (2d+1)$ for non-negative integers $c,d$ such that $H_\alpha(\x)$ is well-defined for all $\x$.
+	where $\alpha = 2c / (2d+1)$ for non-negative integers $c,d$ such that $H_\alpha(\bmz)$ is well-defined for all $\bmz$.
 \end{theorem}
 \begin{proof}
-	For the given form of $\alpha$ and positive $r_i,\ i=1,\dots,N$, $D_\alpha(\x \hspace{1pt}||\hspace{1pt} \r)$ is well-defined for all $\x$.
+	For the given form of $\alpha$ and positive $r_i,\ i=1,\dots,N$, $D_\alpha(\bmz \hspace{1pt}||\hspace{1pt} \r)$ is well-defined for all $\bmz$.
 
@@
 \begin{proof}
-	Since $\tau$ is in the interior of $\F$, its Wigner function obeys $W_\tau(\x) >0$ for all points $\x$ in the phase space. 
-In general, $W_\rho(\x)$ is a quasi-distribution, but the given form of $\alpha$ ensures that $W_{\rho}(\bmx)^\alpha \geq 0$. 
+	Since $\tau$ is in the interior of $\F$, its Wigner function obeys $W_\tau(\bmz) >0$ for all points $\bmz$ in the phase space. 
+In general, $W_\rho(\bmz)$ is a quasi-distribution, but the given form of $\alpha$ ensures that $W_{\rho}(\bmz)^\alpha \geq 0$. 
 Therefore $D_\alpha (W_\rho || W_\tau)$ is always well-defined.
@@
 	D_\alpha(W_{\rho} \hspace{1pt}||\hspace{1pt} W_{\tau}) \geq D_\alpha(W_{\rho'} \hspace{1pt}||\hspace{1pt} W_{\rho'}) &= \nonumber\\
-	\frac{1}{\alpha-1} \log \sum_{\bmx} W_{\rho'}(\bmx) &= 0.
+	\frac{1}{\alpha-1} \log \sum_{\bmz} W_{\rho'}(\bmz) &= 0.
 \end{align}
@@
 	&D_\alpha(W_{\rho^{\otimes n}} \hspace{1pt}||\hspace{1pt} W_{\tau^{\otimes n}}) = \nonumber\\
-	&\frac{1}{\alpha - 1} \log \sum_{\bmx} W_{\rho^{\otimes n}}(\bmx)^\alpha W_{\tau^{\otimes n}}(\bmx)^{1-\alpha} = \nonumber\\
-	&\frac{1}{\alpha - 1} \log \sum_{\bmx} \prod_{i=1}^n W_{\rho}(\bmx_i)^\alpha W_{\tau}(\bmx_i)^{1-\alpha} = \nonumber\\
-	&\frac{1}{\alpha - 1} \log \prod_{i=1}^n \sum_{\bmx_i} W_{\rho}(\bmx_i)^\alpha W_{\tau}(\bmx_i)^{1-\alpha} = \nonumber\\
-	&\sum_{i=1}^n \frac{1}{\alpha - 1} \log \sum_{\bmx'} W_{\rho}(\bmx')^\alpha W_{\tau}(\bmx')^{1-\alpha} = \nonumber\\
+	&\frac{1}{\alpha - 1} \log \sum_{\bmz} W_{\rho^{\otimes n}}(\bmz)^\alpha W_{\tau^{\otimes n}}(\bmz)^{1-\alpha} = \nonumber\\
+	&\frac{1}{\alpha - 1} \log \sum_{\bmz} \prod_{i=1}^n W_{\rho}(\bmz_i)^\alpha W_{\tau}(\bmz_i)^{1-\alpha} = \nonumber\\
+	&\frac{1}{\alpha - 1} \log \prod_{i=1}^n \sum_{\bmz_i} W_{\rho}(\bmz_i)^\alpha W_{\tau}(\bmz_i)^{1-\alpha} = \nonumber\\
+	&\sum_{i=1}^n \frac{1}{\alpha - 1} \log \sum_{\bmz'} W_{\rho}(\bmz')^\alpha W_{\tau}(\bmz')^{1-\alpha} = \nonumber\\
 	&= n D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau).

### 2021-06-24 magic_paper.tex
Edits from pdf implemented. Few small things remaining for tomorrow.

@@
 In this work, we develop a framework to analyse magic state distillation protocols where explicit physics of the system is incorporated in the distillation bounds.
-This is achieved by considering how a given magic state protocol transforms a \emph{pair} of quantum states -- one being a noisy magic state, and the other a stabilizer state that is distinguished by the physics of the system (for example a state at a characteristic temperature, or the maximally mixed state) and acts as a reference state.
-The magic distillation bounds can then be expressed in terms of the physics of the reference state (e.g.
-free energy changes in the case of temperature, or non-unitality in the case of the maximally mixed state).
+This is achieved by considering how a given magic state protocol transforms a \emph{pair} of quantum states -- one being a noisy magic state, and the other a stabilizer state that is distinguished by the physics of the system (for example a state at a characteristic temperature, or the maximally mixed state) and acts as a reference state for the protocol.
+The magic distillation bounds can then be expressed in terms of the physics of the reference state (e.g.~free energy changes in the case of temperature).
 Such bounds are therefore of interest in assessing how physical features such as temperature, noise-biases or fixed-point structure associated with restricted gate-sets constrain distillation protocols~\cite{Tuckett_2019, Aliferis_2008, Stephens_2013, Li_2015, Babbush_2018, Guillaud_2019, Fowler_2019}.
 
-The approach we take is most closely aligned with resource theories of magic, however it differs in a few ways.
-We obtain distillation upper bounds without the use of monotones, but instead tools from statistical mechanics and recent work from the overlap of thermodynamics and quantum information theory~\cite{cit:janzing, cit:horodecki2, Brandao_2015, Vinjanampathy_2016, Goold_2016, cit:lostaglio, cit:gour}.
+The approach we take is most closely aligned with resource theories of magic, however it differs in key ways.
+We obtain distillation upper bounds without the use of monotones, but instead use tools from statistical mechanics and recent work in single-shot resource theories~\cite{cit:janzing, cit:horodecki2, Brandao_2015, Vinjanampathy_2016, Goold_2016, cit:lostaglio, cit:gour}.
 Our analysis relies on the discrete Wigner representation of quantum systems, in which all states and operations can be described on a discrete phase space~\cite{Ferrie_2008, Okay_2021}.
@@
 However, taking a statistical mechanical perspective in this context raises a problem: the standard Boltzmann entropy is not defined for quasi-distributions.
-We circumvent this obstacle by making use of a more fundamental tool in thermodynamics and information theory -- majorization theory~\cite{cit:marshall, Veinott_1971, Ruch_1976}.
-To our knowledge majorization of quasi-distributions has not been considered in quantum physics before, and therefore our analysis is also of interest to the study of non-classicality in quantum systems~\cite{Fine_1982, Allahverdyan_2018, arvidsson_2020, halpern_2018, Lostaglio_2018, Levy_2020}.
+We circumvent this obstacle by making use of a more fundamental tool -- majorization theory~\cite{cit:marshall, Veinott_1971, Ruch_1976}.
+To our knowledge majorization of quasi-distributions has not been considered in quantum physics before, and therefore our analysis is also of relevance to other studies of non-classicality in quantum systems~\cite{Fine_1982, Allahverdyan_2018, arvidsson_2020, halpern_2018, Lostaglio_2018, Levy_2020}.
 
@@
 The simplest case we consider is for magic protocols that lead to unital channels (Section~\ref{sec:unital}).
-These are a subset of protocols that leave invariant some distinguished state or have some equilibrium fixed point (Section~\ref{sec:frag}).
-We then consider protocols that are non-equilibrium processes, but only generate sub-linear correlations that lead to a simple description in the thermodynamic limit (Section~\ref{sec:stab}).
+These are a subset of protocols that leave invariant some distinguished state or have some equilibrium fixed-point structure (Section~\ref{sec:frag}).
+We then consider protocols that are non-equilibrium processes, but only generate sub-linear correlations that enable a simple description in the thermodynamic limit (Section~\ref{sec:stab}), before giving entropic analysis that can be applied more generally (Section~\ref{section:entropies}).
 
@@
 We find that the analysis in the presence of negativity is non-trivial, displays a range of features that do not appear in classical statistical mechanics, and leads to a picture of Wigner negativity in a quantum circuit being described as non-classical free energy that is processed under stochastic dynamics.
-This is demonstrated by Lorenz curves having a non-trivial maximum related to mana (Section~\ref{sec:lc}) and by showing that single-shot entropies for general Wigner quasi-distributions are well-defined, obey data-processing under stabilizer operations and can take on negative values (Section~\ref{section:entropies}).
+This is demonstrated by Lorenz curves having a non-trivial maximum that is related to the mana of a state (Section~\ref{sec:lc}), and by showing that single-shot entropies for general Wigner quasi-distributions are well-defined, obey data-processing under stabilizer operations and can take on negative values (Section~\ref{section:entropies}).
 
@@
 
-We also show that the mana of a quantum state arises as a residue in the $\alpha$--parameter for Renyi entropies, and gives the rate of divergence to $-\infty$ as we approach the Shannon entropy of a Wigner distribution (Equation (\ref{eq:mana-divergence})).
-Finally, in Section~\ref{sec:lower_bounds} we discuss how our approach could be improved and how it can be exploited to construct explicit lower bounds on distillation that take into account physical constraints.
+We show that the mana of a quantum state also arises as a residue in the $\alpha$--parameter for Renyi entropies, and gives the rate of divergence to $-\infty$ as we approach the Shannon entropy of a Wigner distribution (Equation (\ref{eq:mana-divergence})).
+Finally, in Section~\ref{sec:lower_bounds} we discuss how our approach could be extended and how it can be exploited to construct explicit lower bounds on distillation that take into account physical constraints.
 
@@
 The qubit case $d=2$ is known to have obstacles to using a Wigner representation to quantify magic in terms of negativity~\cite{Mermin_1990, cit:howard2}, although recent work~\cite{Raussendorf_qubits} has shown how to extend this to include qubits by enlarging the phase space.
-For a composite system with dimension $d = d_1 \dots d_n$ we can decompose the Hilbert space as $\cal{H}_d = \cal{H}_{d_1} \otimes \dots \otimes \cal{H}_{d_n}$, and then define displacement operators as
+For a composite system with dimension $d_{\rm tot} = d_1 \dots d_n$ and Hilbert space $\cal{H}_{d_1} \otimes \dots \otimes \cal{H}_{d_n}$, we define displacement operators as
 \begin{equation}\label{eq:composited}
@@
 \begin{align*}
-	\bmz &\coloneqq (q_1, \dots, q_n, p_1, \dots, p_n) \in \cal{P}_{d_1} \times \dots \times \cal{P}_{d_n} \eqqcolon  \cal{P}_d,
+	\bmz &\coloneqq (q_1, \dots, q_n, p_1, \dots, p_n) \in \cal{P}_{d_1} \times \dots \times \cal{P}_{d_n},
 \end{align*}
@@
 \end{equation}
-The Clifford operations $ \cal{C}_d^n $ are then defined as the set of unitaries that normalise the Heisenberg-Weyl group~\cite{Appleby_2005}.
+The Clifford group $ \cal{C}_d^n $ is then defined as the set of unitaries that normalise the Heisenberg-Weyl group~\cite{Appleby_2005}.
 We may define the pure stabiliser states as those states obtained by acting on $|0\>$ with Clifford unitaries~\cite{cit:gross3} and, finally, the full set of stabilizer states as the convex hull of all pure stabilisers, namely all probabilistic mixtures of states of the form $U|0\>\<0|U^\dagger$ where $U$ is Clifford.
@@
 
-In order to provide a complete decomposition of arbitrary quantum states and quantum operations we now define a complete basis of Hermitian observables that behaves naturally under the action of the Clifford group.
+In order to provide a complete decomposition of arbitrary quantum states and quantum operations we now define a basis of Hermitian observables that transforms covariantly under the action of the Clifford group.
 At every point $\bmz \in \P_d$ we define the phase-point operator
@@
 For any quantum state $\rho$, the Wigner distribution $W_\rho(\bmz)$ is readily seen to be a $d^2$-dimensional quasi-probability distribution over $\cal{P}_d$.
-More precisely, $W_\rho(\bmz)$ is a bounded real-valued function on $\P_d$ with the normalisation property $\sum_{\bmz} W_\rho(\bmz) = 1$ (see~\cref{app:wigner} for details).
-
-Any quantum operation $\E$ can also admit a Wigner representation.
-If $\E$ maps some quantum system $A$ of dimension $d_A$ to a quantum system $B$ of dimension $d_B$ and $\J(\E)$ is its associated Choi state~\cite{watrous_2018}, then we can define
-\begin{equation}
+More precisely, $W_\rho(\bmz)$ is a real-valued function on $\P_d$ with the normalisation property $\sum_{\bmz} W_\rho(\bmz) = 1$ (see~\cref{app:wigner} for details).
+
+Any quantum channel $\E$ also admits a Wigner representation.
+If $\E$ maps some quantum system $A$ of dimension $d_A$ to a quantum system $B$ of dimension $d_B$ and $\J(\E) = \E \otimes id (|\phi^+\> \<\phi^+|)$, with $|\phi^+\> = d_A^{-1/2} \sum_k |kk\>$, is its associated Choi state of the channel~\cite{watrous_2018}, then we can define
+\begin{equation}\label{Wigner-Choi}
 W_{\E}(\y |\bmz) \coloneqq d_A^2 W_{\J(\E)}(\bar{\bmz} \oplus \y),
@@
 In any theory of magic, one route to bounding distillation rates is through a \emph{magic monotone}.
-A magic monotone is a real-valued function of any quantum state $\M(\rho)$ that is monotonically non-increasing under the free operations of the magic theory.
-More precisely $\M(\sigma) \le \M(\rho)$ whenever it is possible to convert $\rho$ into $\sigma$ using free operations.
+A magic monotone is a real-valued function of any quantum state $M(\rho)$ that is monotonically non-increasing under the free operations of the magic theory.
+More precisely $M(\sigma) \le M(\rho)$ whenever it is possible to convert $\rho$ into $\sigma$ using free operations.
 
@@
 \begin{equation}
-    \mana{\rho} \coloneqq \ln (2\hspace{1pt}\sn{\rho}+1),
+    \M(\rho) \coloneqq \log (2\hspace{1pt}\sn{\rho}+1),
 \end{equation}
@@
 \end{equation}
-
-Mana is an additive\footnote{It satisfies the condition $\mana{\rho_1 \otimes \rho_2} = \mana{\rho_1} + \mana{\rho_2}$.} magic monotone, and the fact that it is non-increasing under free operations provides a constraint on magic state interconvertibility.
-
-In this work we shall develop bounds that apply to essentially any reasonable magic theory.
+Using the fact that $W_\rho(\z)$ is a normalised quasi-distribution, we can also write $\M(\rho) = \sum_{\z} |W_\rho(\z)|$.
+
+Mana is an additive magic monotone, and the fact that it is non-increasing under free operations provides a constraint on magic state interconvertibility.
+
+In this work we develop bounds that apply to any reasonable magic theory.
 The central idea is to apply majorization theory to the quasi-probability distributions that arise for magic states.
@@
 However, it is known that all positively represented states used in Clifford circuits admit an efficient classical description, so it is natural to focus on the negatively represented magic states.
-The free states in any magic theory are assumed to lie in the set
-\begin{equation}
-    \Fmax \coloneqq \{ \rho: \W[\bmz]{\rho} \geq 0 \text{ for all } \bmz \in \cal{P}_d\}.
+The free states in any magic theory are required to be a subset of
+\begin{equation}
+    \F \coloneqq \{ \rho: \W[\bmz]{\rho} \geq 0 \text{ for all } \bmz \in \cal{P}_d\}.
 \end{equation}
@@
 the ones that are considered free within the theory.
-The most basic assumption we require on free operations is that they send any free state to another free state, meaning that a resource state cannot be created freely, a common assumption among all magic theories.
-
-Any magic state protocol will correspond to a quantum channel $\E$, and admits a Wigner representation $W_{\E}( \y | \bmz)$ that can be viewed as a transition matrix mapping phase space points $\bmz \rightarrow \y$.
+The most basic assumption we require on free operations is that they send any free state to another free state, meaning that a resource state cannot be created freely.
+
+Any magic state protocol will correspond to a quantum channel $\E$, and so from Equation~(\ref{Wigner-Choi}) admits a Wigner representation $W_{\E}( \y | \bmz)$ that acts as a transition matrix mapping phase space points $\bmz \rightarrow \y$.
 The representation obeys the relation
@@
 
-However, it is important to note that this mapping to stochastic maps is not one-to-one.
+However, note that this mapping to stochastic maps is not one-to-one.
 Not all stochastic maps on the phase space correspond to valid quantum operations.
@@
 
-In what follows, we shall assume that we have a magic theory $\R = (\F, \O)$ in which the free states $\F$ form a closed set and are represented by non-negative Wigner functions, while the free operations $\O$ are stochastic maps in the Wigner representation.
-To aid our analysis of magic in this phase space setting we shall make use of majorization theory, which we describe in the next section.
+In what follows, we shall assume that we have a magic theory $\R = (\F, \O)$ in which the free states $\F$ are represented by non-negative Wigner functions, while the free operations $\O$ are stochastic maps in the Wigner representation.
+Our analysis of magic in this phase space setting makes use of majorization theory, which we describe in the next section.
 
@@
 
-Majorisation~\cite{cit:marshall, Blackwell_1953} is a collection of powerful tools that has recently found many applications in quantum information theory~\cite{Nielsen_1999, cit:cwiklinski, cit:lostaglio2, cit:gour, cit:gour2, Horodecki_2003, Vallejos_2021}.
-It describes the disorder of distributions that undergo stochastic transformations.
-In its simplest form it defines a pre-order on probability distributions.
+Majorisation~\cite{cit:marshall, Blackwell_1953} is a collection of powerful tools that has found many applications in quantum information theory~\cite{Nielsen_1999, cit:cwiklinski, cit:lostaglio2, cit:gour, cit:gour2, Horodecki_2003, Vallejos_2021}.
+It describes the disorder of distributions that undergo stochastic transformations, and in its simplest form defines a pre-order on probability distributions.
 Given two distributions $\p= (p_1, \dots, p_n)$ and $\q = (q_1, \dots, q_n)$ over $n$ outcomes, we say that $\p$ majorises $\q$, denoted $\p \succ \q$, if there exists a bistochastic map $A = (A_{ij})$ such that $A\p = \q$, where bistochastic means that $A_{ij} \geq 0$ and $\sum_i A_{ij} = \sum_j A_{ij} = 1$.
@@
 It is readily checked that the original majorization condition between probability distributions corresponds to the case $\r = (1/n, \dots, 1/n)$.
-The pre-order that results from $\bmd$-majorization is also easily checked and again corresponds to checking a small number of inequalities.
-
-In fact, we can further generalise to \emph{relative majorization}~\cite{Blackwell_1953, Ruch_1976, ruch_mixing_1978, Renes_2016, Buscemi_2017, Rethinasamy_2020}, defined as an ordering between pairs of vectors so that
+The pre-order that results from $\bmd$-majorization is also easily computed and again corresponds to checking a small number of inequalities.
+
+In fact, we can further generalise to \emph{relative majorization}~\cite{Blackwell_1953, Ruch_1976, ruch_mixing_1978, Renes_2016, Buscemi_2017, Rethinasamy_2020}, defined as an ordering between pairs of vectors and write
 \begin{equation}
@@
 \end{equation}
-iff there is a stochastic map $A$ such that $A\r = \r'$ and $A\p = \q$. We retrieve $\bmd$--majorization when $\r = \r'$.
-
-It turns out that relative majorization is equally applicable to \emph{quasi-probability} distributions, and therefore can be applied to the Wigner representation of magic across different $\R_\sigma$.
-We discuss this in detail in the next section.
+if and only if there is a stochastic map $A$ such that $A\r = \r'$ and $A\p = \q$. We retrieve $\bmd$--majorization when $\r = \r'$.
 
@@
 
-Central to the analysis is the notion of a Lorenz curve of a vector $\w \in \mathbb{R}^n$ relative to some other vector $\r \in \mathbb{R}^n$.
+We also make use of the notion of a Lorenz curve of a vector $\w \in \mathbb{R}^n$ relative to some other vector $\r \in \mathbb{R}^n$.
 Given a vector $\w$ we define $\w^\downarrow$ to be the re-arrangement of the components of $\w$ into decreasing order.
@@
 Within quantum theory, the breaking of this barrier is associated with the degree of non-classicality.
-Since majorization provides a measure of order/disorder this is consistent with the intuition that negativity, for example within the context of quantum optics or quantum computing, can provide a greater form of order than is possible within classical theory.
 
@@
 
-However, relative majorization is usually considered for probability distributions, so we need to verify that the same Lorenz curve conditions apply to quasi-probability distributions before proceeding with our analysis.
+Relative majorization is usually considered for probability distributions, so we need to verify that the same Lorenz curve conditions apply to quasi-probability distributions before proceeding with our analysis.
 This can be done from first principles, but a simpler way to see that this holds is to reduce to the problem of genuine distributions by first `masking' the negativity in the quasi-probability distribution $\w$ using the reference distribution $\r$ and then applying the conditions for relative majorization.
@@
 We show that any magic theory can always be decomposed in terms of `sub-theories' with a particular fixed-point structure.
-This allows the use of $\mathbf{d}$--majorization, however in~\cref{sec:stab}, we drop the requirement of fixed-points and instead use the full relative majorization, before finally giving general entropic constraints in Section~\ref{section:entropies}.
+This allows the use of $\mathbf{d}$--majorization, however in~\cref{sec:stab}, we drop the requirement of fixed-points and instead use the full relative majorization, before giving general entropic constraints in Section~\ref{section:entropies}.
 
@@
 \end{definition}
-This provides a simple way to break up any theory into smaller, more manageable parts, and where the union over all sub-theories returns the parent theory, so we are not discarding any information by breaking up the theory in this way.
+This gives a simple way to break up any theory into smaller, more manageable parts, and where the union over all sub-theories returns the parent theory, so we are not discarding any information by breaking up the theory in this way.
 We make this precise as follows.
@@
 \end{proof}
-One can compare with resource monotones, which are also called resource measures.
+We can compare with resource monotones, which are also called resource measures.
 A complete set of measures $\{\M_i\}_i$ is such that $\rho \rightarrow \sigma$ if and only if $\M_i(\rho) \ge \M_i(\sigma)$ for all $i$.
 The above set of sub-theories can therefore be viewed as a complete set of ``co-measures'' for the theory, where the parent resource theory's complex pre-order of states is mapped to a simpler pre-order for a particular $\R_\sigma$.
-In the next section we show that this pre-order for a given $\R_\sigma$ can always be approximated by a majorization pre-order, and from this we can compute magic distillation bounds.
-
-\iffalse
-\begin{figure}[t]
-    \centering
-        \includegraphics[scale=0.3]{figs/operations.pdf}
-    \caption{\textbf{Decomposition of a magic theory $\R$ into $\R_\sigma$ bits.} 
-	Examples of magic theories ($\so$: Stabilizer operations, $\Omax$: Completely positive-Wigner-preserving operations, $\rcu$: Random Clifford Unitaries -- subclass of $\so$) are labelled, with other established magic theories also contained within the yellow regions.
-    We introduce $\sigma$--fragments $\O_\sigma$ defined for all free states $\sigma$ that cover $\Omax$. 
-    Each $\O_\sigma$ is extensible to a set of stochastic maps outside the $\cptp$ operations.
-    Within each $\sigma$--fragment, relative majorisation can be used allowing for a tractable approach towards the study of magic state interconversions.
-    }
-    \label{fig:zoo}
-\end{figure}
-\fi
-
-\subsection{Majorisation of negative Wigner distributions with fixed-point structure}
+In the next section we show that a given $\R_\sigma$ can be approximated by a majorization pre-order, and from this we can compute magic distillation bounds.
+
+\subsection{Majorisation of Wigner distributions with fixed-point structure}
 \label{sec:major_frag}
-We can now look at how the simple approach of focussing on fixed-point structures can be used to analyse magic protocols.
+We now look at how fixed-points give constraints on magic protocols.
 We consider some $\sigma \in \F$, and its corresponding $\R_\sigma$.
@@
 The state $\rho$ is assumed to have negativity in the Wigner representation, so $W_\rho(\bmz) < 0$ for some regions of $\bmz \in \P_d$.
-The state $\sigma$ is assumed to have a Wigner distribution with $W_\sigma(\bmz) > 0$ for all $\bmz$ in the phase space\footnote{Any non-full rank state $\sigma$ can be handled as a limiting case in which we first add an infinitesimal fraction of depolarising noise $\epsilon (\id/d)$ and then take $\epsilon \rightarrow 0$ in the end.}.
+The state $\sigma$ is assumed to have a Wigner distribution with $W_\sigma(\bmz) > 0$ for all $\bmz$ in the phase space\footnote{A non-full rank state $\sigma$ can be handled as a limiting case in which we first add an infinitesimal fraction of depolarising noise $\epsilon (\id/d)$ and then take $\epsilon \rightarrow 0$ in the end.}.
 
@@
 For $n$ copies of a qudit system of dimension $d$ the number of terms in $W_{\rho}$ is $d^{2n}$, so imposing the Lorenz curve condition corresponds to \emph{exponentially} many constraints.
-However,  before computing explicit examples, in the next section we highlight how these majorization constraints relate to other known monotones.
+However,  before computing explicit examples, in the next section we describe how these majorization constraints relate to other known monotones.
 
@@
 
-We state some generic aspects of Lorenz curves for magic states.
-These allow us to interpret previous magic monotones in a new light.
+We state some generic aspects of Lorenz curves for magic states, which allow us to interpret previous magic monotones in a new light.
 The first result gives an extremely simple way to see that the sum-negativity/mana of a magic state is a monotone~\cite{cit:veitch2}.
@@
 Note though, in contrast to mana, the area monotone is \emph{specific to the $\R_\sigma$}, and its value will vary as we change $\sigma$.
-Therefore its monotonicity depends on the physics of the fixed point and so provides a means to analyse magic distillation only under free operations that leave $\sigma$ invariant.
+Therefore its monotonicity depends on the physics of the fixed point and provides a means to analyse magic distillation only under free operations that leave $\sigma$ invariant.
 One can also define an area monotone in the more general setting of relative majorization, where one drops the fixed point emphasis as in Section \ref{sec:stab}, but we do not explore this here.
@@
 
-Our approach works for any dimension, but for simplicity we consider qutrit magic states ($d=3$), for which a canonical magic state exists with a particularly simple Wigner distribution.
+Our approach works for any odd dimension, but for simplicity we consider qutrit magic states ($d=3$), for which a canonical magic state exists with a simple Wigner distribution.
 This is the Strange state $|S\>$, which is given by
@@
 in the computational basis.
-Its distribution $W_S$ has a single negative value of $-1/3$ at $\bmz =(0,0)$ and the positive value $1/6$ at all other points.
+Its distribution $W_{|S\>\<S|}(\z)$ has a single negative value of $-1/3$ at $\bmz =(0,0)$ and the positive value $1/6$ at all other points.
 We define the $\epsilon$--noisy Strange state as
@@
 We now consider purifying $n$ copies of a noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ into a smaller number of copies $n'$ of a less noisy Strange state $\rho_{\rm{S}}(\epsilon')^{\otimes n'}$, with $\epsilon' < \epsilon$ and $n' \leq n$.
-Since we work in the unital fragment, the maximally mixed state is free and we choose to tensor in $n'-n$ auxiliary copies of it to the output.
+The maximally mixed state is a stabilizer state and so free, we choose to tensor in $n'-n$ auxiliary copies of it to the output.
 This simplifies analysis, and does not affect distillation rates as it is easy to see that
@@
 
-Due to negativity, the ordering of the components of rescaled Wigner distribution $W_{\rho_n |\sigma_n}(\bmz) \coloneqq W_{\rho_n}(\bmz)/W_{\sigma_n}(\bmz)$, for $\rho_n = \rho_S(\epsilon)^{\otimes n}, \sigma_n = \sigma^{\otimes n}$, depends on whether $-v(\epsilon)$ appears to an even or odd power.
+Due to negativity, the ordering of the components of rescaled Wigner distribution $W_{\rho_n |\sigma_n}(\bmz) \coloneqq W_{\rho_n}(\bmz)/W_{\sigma_n}(\bmz)$, for $\rho_n = \rho_S(\epsilon)^{\otimes n}$, and $\sigma_n = \sigma^{\otimes n}= (\I/3)^{\otimes n}$, depends on whether $-v(\epsilon)$ appears to an even or odd power.
 Treating the Wigner distributions as vectors, the component values $w_i$ and associated multiplicities $m_i$ in the $n$--copy case are found to be
@@
 Distillation bounds can be obtained from any location of the Lorenz curve, including the region around the peak, by imposing the constraint that the Lorenz curve of the input state never dips below the curve of the output.
-In particular a compact constraint can be obtained by considering the initial slopes of the two Lorenz curves.
+In particular a simple constraint can be obtained by considering the initial slopes of the two Lorenz curves.
 
@@
 \end{equation}
-This can be compared to other known distillation bounds coming from mana and thauma~\cite{Wang_2020}. The mana bound can be directly calculated as
-\begin{equation}
-	R \leq \frac{\mana{\rho_{\rm{S}}(\epsilon)}}{\mana{\rho_{\rm{S}}(0)}} = 1 + \frac{\ln \left(1 - \frac{8}{15}\epsilon \right)}{\ln \frac{5}{3}}.
+We compare this to other known distillation bounds coming from mana and thauma~\cite{Wang_2020}. The mana bound can be directly calculated as
+\begin{equation}
+	R \leq \frac{\M(\rho_{\rm{S}}(\epsilon))}{\M(\rho_{\rm{S}}(0))} = 1 + \frac{\ln \left(1 - \frac{8}{15}\epsilon \right)}{\ln \frac{5}{3}}.
 \end{equation}
@@
 
-In the next section, we loosen the restriction of working in a fixed $\R_\sigma$, and instead use full relative majorization to obtain bounds that incorporate energetic aspects of a magic state protocol.
-
 \section{Temperature-dependent bounds for magic state distillation protocols}
@@
 
-We can now show how to use relative majorization to incorporate physics into magic distillation bounds.
-We focus on energetic and entropic aspects of a protocol.
-The way we describe these is by how the protocol would disturb a reference equilibrium state $\tau$ to some different state $\tau'$, if the protocol had been applied to this reference state instead of the actual $n$-copy magic state.
+We now show how relative majorization can incorporate physics into magic distillation bounds.
+The way we do this is by considering how the protocol would disturb a reference equilibrium state $\tau$ to some different state $\tau'$, if the protocol had been applied to this reference state instead of the actual $n$-copy magic state.
 
@@
 with $n \gg 1$, $\epsilon' <\epsilon$ and $\E$ denoting the quantum channel induced by the protocol.
-We also assume each qudit has Hamiltonian $H$ and we choose some temperature $T = (k\beta)^{-1}$ where $k$ is Boltzmann's constant and $\beta$ the inverse temperature.
+We also assume each qudit has a Hamiltonian $H$ and neglect interaction terms.
+We choose some temperature $T = (k\beta)^{-1}$ where $k$ is Boltzmann's constant and $\beta$ the inverse temperature.
 The reference equilibrium state of the $n$ qudits is given by
@@
 
-This means in particular that $\E(\tau^{\otimes n})$ is a symmetric state on $m$ subsystems, so by the quantum de Finetti theorem~\cite{christandl_2007} we have that for $m \gg 1$
+This means in particular that $\E(\tau^{\otimes n})$ is a symmetric state on $m$ subsystems, so by the quantum de Finetti theorem~\cite{christandl_2007} \ddd{[There is more than one seminal de Finetti paper to cite]} we have that for $m \gg 1$
 \begin{equation}
@@
 where $d\mu(x)$ is a probability measure over a set $\{\tau'_x\}$ of single qudit states.
-This makes the setting easier to handle, although we make one more simplifying assumption on the physics as explained in the next section.
 
@@
 To keep our analysis simple we make the following physical assumption.
-We assume that in the asymptotic/thermodynamic limit $n,m \rightarrow \infty$ that correlations generated on the reference equilibrium state are negligible.
+We assume that in the asymptotic/thermodynamic limit $n,m \rightarrow \infty$ the correlations generated on the reference equilibrium state are negligible.
 This implies that $d\mu(x)$ is peaked on a particular state $\tau'$, and $\E(\tau^{\otimes n}) \approx \tau'^{\otimes m}$.
 This occurs in the context of traditional thermodynamics, and states that the output system is well-described by intrinsic variables that do not scale in $m$, and correlations are sub-linear in $m$.
-This allows us to compute a free energy per qudit of the output state.
+In particular, this allows us to compute a free energy per qudit of the output state.
+
 The case of non-trivial correlations in the thermodynamic limit can also be considered, but leads to a more complex analysis within our majorization framework of Wigner distributions.
 In this direction, we highlight recent work in majorization in which stochastic independence and correlations are analysed.
-In particular, it has been shown that stochastic independence (no correlations) of independent distributions can be viewed as a resource in an extension of catalytic majorization, and leads to a single-shot operational interpretation of the Shannon entropy~\cite{muller_2015, muller_2016, muller_2019}.
-
-Our bound turns out to depend on the von Neumann entropy $S(\rho)$ of a state, and the free energy at a particular temperature.
+In particular, it has been shown~\cite{muller_2015} that stochastic independence (no correlations) of independent distributions can be viewed as a resource in an extension of catalytic majorization, and leads to a single-shot operational interpretation of the Shannon entropy~\cite{muller_2016, muller_2019}.
+
+Our bound depends on the von Neumann entropy $S(\rho)$ of a state, and the free energy at a particular temperature.
 For a state $\tau = e^{-\beta H}/\Z$, the Helmholtz free energy $F$ is given by
@@
 In Appendix~\ref{thm:free-energy-bound-proof} we analyse the Lorenz curves of this condition and obtain the following magic distillation bound that combines computational measures $\epsilon,\epsilon'$, with terms that depend on the Hamiltonian and reference temperature $T$ of the physical system.
-We state the result for the case of qutrits, but a similar analysis works for general qudits.
+We state the result for the case of qutrits, but a similar analysis works for general odd-dimension qudits.
 
@@
 In particular, the term $\phi$ quantifies to what degree a sharp energy value can be associated to the negativity in the Wigner representation.
-Its form is similar to $F$, and so $\phi$ can informally be viewed as a `magic free energy' term.
+Its form is similar to $F$, and so $\phi$ can loosely speaking be viewed as a `magic free energy' term.
 
@@
 We could perform similar analysis for general qudits, and different choices of magic states, for example.
-It might also be of interest to consider other choices of reference states $\tau$ that are more appropriate to the hardware physics, for example for photonic set-ups.
+It might also be of interest to consider other choices of reference states $\tau$ that are more appropriate to the hardware physics, for example for photonic set-ups\ddd{[cite recent PsiQ architecture paper]}.
 
@@
 \section{Extension of single-shot entropies to quasi-distributions}\label{section:entropies}
-We have considered Wigner distributions of magic states within a statistical mechanical setting in which it was argued that magic should be viewed as a non-classical form of free energy.
+We have considered Wigner distributions of magic states within a statistical mechanical setting in which it was argued that magic can be viewed as a non-classical form of free energy.
 This identification with free energy was done at the level of majorization constraints that appear due to stabilizer operations being described by stochastic maps in the Wigner representation.
 In this representation, non-equilibrium states with substantial free energy have Lorenz curves that deviate noticeably from the line $y=x$.
-We also found that when considered in a distillation protocol, magic could be linked to thermodynamic free energies in a non-trivial way.
+We also found that when considered in a distillation protocol, magic could also be linked to physical free energies in a non-trivial way.
 We can therefore ask: is it possible to make a more direct link between magic and free energy or entropy?
@@
 \end{theorem}
-
-We can go further, and show that a range of Renyi entropies remain both well-defined and meaningful in the Wigner representation. The $\alpha$--Renyi entropy $H_\alpha(\p)$ is defined as
+The reason for the power of $2$ in the third property is that the maximization is sensitive to the presence of negativity in the Wigner distribution.
+
+We can go further, and show that in fact a range of Renyi entropies remain both well-defined and meaningful in the Wigner representation. The $\alpha$--Renyi entropy $H_\alpha(\p)$ is defined as
 \begin{equation}
@@
 \end{theorem}
-This monotonicity provides a meaningful extension of entropies to quasi-distributions, and the allowed values are dense in $\alpha >1$.
+This monotonicity provides a meaningful extension of entropies to quasi-distributions, and the allowed values of $\alpha$ are dense in $\alpha >1$.
 Moreover we can prove the following result, which establishes the equivalence between Wigner negativity and the existence of negative Renyi entropy.
@@
 with $\epsilon \rightarrow 0^+$ through a sequence of rational values.
-We now recall that mana is defined as $\M(\rho) = \log \sum_{\bmz} |W_\rho(\bmz)|$, and so we obtain a second new description of mana:
+We now recall that mana can be written as $\M(\rho) = \log \sum_{\bmz} |W_\rho(\bmz)|$, and so we obtain a second new description of mana:
 \begin{equation}\label{eq:mana-divergence}
-\M(\rho) = \lim_{\epsilon \rightarrow 0^+} \epsilon H_{1-\epsilon}(W_\rho).
+\M(\rho) = -\lim_{\epsilon \rightarrow 0^+} \epsilon H_{1-\epsilon}(W_\rho).
 \end{equation}
@@
 
-We also note that the Renyi entropy can be described as a $q$--deformation of the Shannon entropy~\cite{baez2011renyi}, and $H_\alpha(\p)$ can be related to the $q$--derivative of free energy.
+We note that the Renyi entropy can be described as a $q$--deformation of the Shannon entropy~\cite{baez2011renyi}, and $H_\alpha(\p)$ can be related to the $q$--derivative of free energy.
 For this, the Renyi parameter becomes a temperature term $\alpha = \frac{T_0}{T}$ where $T_0$ is a reference temperature and derivatives are considered via the limit $T \rightarrow T_0$.
@@
 We can therefore speculate whether the presence of magic in Clifford circuits admits a sensible interpretation in terms of a zeroth-order phase transition [\ddd{cite}].
-However since variation in $\alpha$ is no longer smooth ($\alpha$ is restricted to a dense set of rational values) technical obstacles exist and we do not pursue this speculative line here, but just note that other works exist in which computational transitions are considered in relation to phase transitions [\ddd{cite}].
-
+However we do not pursue this speculative line here, but just note that other works exist in which computational transitions are considered in relation to phase transitions [\ddd{cite}].
+
+\subsection{Renyi divergences and general distillation bounds}
 Every entropy can be obtained from a relative entropy~\cite{Gour_2020} and so we now state the extensions for Renyi divergences of Wigner distributions.
@@
 \end{theorem}
-For magic protocols that preserve unital maps, the above bound reduces to the simpler form
+\ddd{[Perhaps remove free energy form...and allow $\frac{1}{m} D_\alpha(\rho'_m|| \tau'_m)$ general term with no assumption on correlations. ]}
+
+For magic protocols that give unital maps, the above bound reduces to the simpler form
 \begin{equation}
@@
     \begin{enumerate}
-        \item[(i)]\label{en:wo1} Real-valued: $\W{\E}(\bmz) \in \mathbb{R}^{d^2} \times \mathbb{R}^{d^2}$;
+        \item[(i)]\label{en:wo1} Real-valued: $\W{\E}(\z|\y) \in \mathbb{R}^{d_A^2} \times \mathbb{R}^{d_B^2}$;
         \item[(ii)]\label{en:wo2} Normalised: $\sum_{\bmy \in \cal{P}_{d_B}} \W[\bmz|\bmy]{\E} = 1$ \\ 
@@
 
-We prove the following result connecting majorization to relative majorization.
+We prove the following result connecting majorization to relative majorization~\cite{cit:horodecki2, Brandao_2015,  cit:lostaglio}.
 \begin{lemma}
@@
 Suppose there is a stochastic map $A$ such that $A\w=\w'$ and $A\r = \r'$. 
-We define $B:\mathbb{R}^K \mapsto \mathbb{R}^K$ by $B := \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1}$ so that it is stochastic as a composition of stochastic maps and it preserves the uniform distribution in $\mathbb{R}^A$, since
+We define $B:\mathbb{R}^K \mapsto \mathbb{R}^K$ by $B := \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1}$ so that it is stochastic as a composition of stochastic maps and it preserves the uniform distribution in $\mathbb{R}^K$, since
 \begin{align}
@@
 \end{proof}
-We note that the vectors $\r, \r'$ with rational components form a dense subset of the positive probability distributions, so we can appeal to the fact that experiments have a finite resolution to ignore technical details regarding the completion to arbitrary real components.
-
+We note that the vectors $\r, \r'$ with rational components form a dense subset of the positive probability distributions, do not consider technical fine-print that would not affect actual physical measurements, which always have a finite resolution.
 \subsection{Component-multiplicity pairs}
@@
 	Given a magic state $\rho$, the maximum value $L_\star$ attained by the Lorenz curve $\lc{\rho}{\sigma}(x)$ is independent of the $\R_\sigma$ and equal to $1+\sn{\rho}$.
-Moreover, the relative majorization constraint is stronger than mana in every $\R_sigma$.
+Moreover, the relative majorization constraint is stronger than mana in every $\R_\sigma$.
 \end{theorem}
@@
 
-Since the magic monotone mana is a monotonic function of sum-negativity, $\rm{mana}(\rho) \coloneqq \ln \hspace{1pt}(2\hspace{1pt}\sn{\rho}+1)$, we see that mana corresponds precisely to the peak of the Lorenz curve $L_{\rho|\sigma}(x)$.
-Therefore, mana is one of $d^{2n}$ constraints, so majorization is strictly a stronger constraint in any $\R_\sigma$.
+Since mana is a monotonic function of sum-negativity, $\M(\rho) \coloneqq \log \hspace{1pt}(2\hspace{1pt}\sn{\rho}+1)$, we see that mana determines the peak of the Lorenz curve $L_{\rho|\sigma}(x)$.
+However, mana is one of $d^{2n}$ constraints, so majorization is strictly a stronger constraint in any $\R_\sigma$.
 \end{proof}
@@
 
-\section{Lorenz curves for unital processes}
+\section{General aspects of Lorenz curves for noisy Strange states}
 \label{app:lcsu_technical}
 
+Here we provide background detail as to how the Lorenz curve behaves for a noisy Strange state in the large $n$ limit.
+
 \subsection{Binomial distributions and error bounds}\label{app:phi}
-Consider an experiment consisting of $n$ trials of throwing a $p$--coin, that is a coin with probability $p$ of landing on one side and $1-p$ of landing on the other.
+Consider an experiment consisting of $n$ trials of throwing a coin with probability $p$ of landing on heads and $1-p$ of landing on tails.
 We denote the sums over an even number $m$ of successful trials by $\Phi_+(m; n, p)$ and an odd number $m$ of successful trials by $\Phi_-(m; n, p)$, and they are given by
@@
 
-\section{Details for the derivation of distillation bounds from Lorenz curves}
+\section{Temperature-dependent distillation bounds from relative majorization}
 \label{app:lcst_technical}
 
-\subsection{Free energy dependent magic distillation bounds}\label{free-energy-bound-proof}
-\label{app:main_proof}
 Here we prove our main theorem, which bounds magic distillation rates in terms of free energies.
@@
 \end{align}
-and $\bmz_\star = \arg\!\min W_\tau(\bmz)$. The primed variables are defined similarly for the output system.
+and $W_\tau(\bmz)$ attains a minimum at $\z_\star$. The primed variables are defined similarly for the output system.
 \end{theorem}
@@
 
-If we drop the freedom to transform the magic states via Clifford unitaries, then the final expression for the bounds change and become a little more complex, since the largest component in the rescaled distribution depends on a number of factors.
+If we drop the freedom to pre/post-process the magic states via Clifford unitaries, then the final expression for the bounds change and become a little more complex, since the largest component in the rescaled distribution depends on a number of factors.
 We illustrate this by the following result.
@@
 
-In this section, we develop the tools that allow the use of entropic functions on quasi-probabilities to retrieve magic distillation bounds.
+In this section, we analyse Renyi entropies on quasi-probabilities and use them to get magic distillation bounds.
 
@@
 \begin{equation}
-	D_\infty(W_\rho || W_\tau) =\log  \max_{\bmz} \frac{W_\rho}{W_\tau},
+	D_\infty(W_\rho || W_\tau) =\log  \max_{\bmz} \frac{W_\rho(\z)}{W_\tau(\z)},
 \end{equation}
@@
 $D_\infty(W_\rho || W_\tau) = 0$ implies that $\max_{\bmz} \frac{W_\rho(\bmz)}{W_\tau(\bmz)}=1$ and the initial slope of $L_{\rho|\tau}(x)$ is $1$.
-From the concavity of the function this implies that the slope of $L_{\rho|\tau}(x)$ must equal $1$ throughout the interval $[0,1]$ and this, together with the definition of the Lorenz curve, implies that $W_\rho(\bmz)/W_\tau(\bmz) = 1$ for all $\bmz$.
+From the concavity of the function and the fact that $L_{\rho|\tau}(1)=1$, this implies that the slope of $L_{\rho|\tau}(x)$ must equal $1$ throughout the interval $[0,1]$ and this, together with the definition of the Lorenz curve, implies that $W_\rho(\bmz)/W_\tau(\bmz) = 1$ for all $\bmz$.
 Since the Wigner representation $\rho \mapsto W_\rho(\bmz)$ is bijective this implies that $\rho = \tau$ only.
@@
 \end{equation}
-and if additionally $w_k \geq 0$ for all $k$, then we also have
-\begin{equation}
-	\max_{k_1, k_2, \dots, k_n} \left( w_{k_1}w_{k_2}\cdots w_{k_n} \right) = (\max_k w_k)^n.
+and if additionally $w_k \geq 0$ for all $k$, then we also have for even $n$ that
+\begin{equation}
+	\max_{k_1, k_2, \dots, k_n} \left( w_{k_1}w_{k_2}\cdots w_{k_n} \right) = (\max_k |w_k|)^n.
 \end{equation}
@@
 \end{equation}
-where $\alpha$ can take values of the form $2a / (2b+1)$, for non-negative integers $a,b$ to ensure that the argument of the logarithm is positive.
-Note that for any quantum state $\rho$, $H_1(W_\rho)$ in particular is not well-defined, while for any valid $\alpha$ we have that
-\begin{equation}
-	H_0(W_\rho) = 2\log d = H_\alpha \left( W_{\id/d} \right),
-\end{equation}
-where $d$ is the dimension of $\rho$.
+where $\alpha$ can take values of the form $2a / (2b+1)$, for non-negative integers $a,b$ to ensure that the argument of the logarithm is positive. \ddd{[Need to expand on this]}
 
@@
 \begin{definition} 
-	A continuous, real-valued function $f$ defined on $\mathcal{Q} \subseteq \mathbb{R}^N$ is called Schur-convex on the domain $\mathcal{Q}$ if $\p \prec \q$ on $\mathcal{Q}$ implies that $f(\p) \le f(\q)$.
-A continuous function $f:\mathcal{Q} \rightarrow \mathbb{R}$ is called Schur-concave if $(-f)$ is Schur-convex.
+	A continuous, real-valued function $f$ defined on $\mathcal{D} \subseteq \mathbb{R}^N$ is called Schur-convex on the domain $\mathcal{D}$ if $\p \prec \q$ on $\mathcal{D}$ implies that $f(\p) \le f(\q)$.
+A continuous function $f:\mathcal{D} \rightarrow \mathbb{R}$ is called Schur-concave if $(-f)$ is Schur-convex.
 \end{definition}
@@
 \begin{equation}
-	\mathcal{Q} = \left\{ \w \in \mathbb{R}^N: \sum_{i=1}^N w_i = 1 \right\}.
+	\D=\mathcal{Q}_N = \left\{ \w \in \mathbb{R}^N: \sum_{i=1}^N w_i = 1 \right\}.
 \end{equation}
@@
 \begin{equation}
-	\mathcal{Q}^\downarrow = \{ \w \in \mathcal{Q} : w_1 \ge w_2 \ge \cdots \ge w_N\}.
+	\mathcal{Q}^\downarrow_N = \{ \w \in \mathcal{Q}_N : w_1 \ge w_2 \ge \cdots \ge w_N\}.
 \end{equation}
@@
 We now have that the Schur-Ostrowski theorem~\cite{cit:marshall} provides a characterization of symmetric, Schur-convex and Schur-concave functions on quasi-distributions.
+\ddd{[Needs a bit more expansion]}
 \begin{lemma}
-	Let $f$ be a real-valued continuous function defined on $\mathcal{Q}^\downarrow$ that is continuously differentiable on the interior of $\mathcal{Q}^\downarrow$. 
-Then, $f$ is Schur-convex on $\mathcal{Q}^\downarrow$ if and only if $\partial_k f(\w)$ is decreasing in $k$ for all $\w \in \mathcal{Q}^\downarrow$, namely
+	Let $f$ be a real-valued continuous function defined on $\mathcal{Q}^\downarrow_N$ that is continuously differentiable on the interior of $\mathcal{Q}^\downarrow_N$. 
+Then, $f$ is Schur-convex on $\mathcal{Q}^\downarrow_N$ if and only if $\partial_k f(\w)$ is non-increasing in $k$ for all $\w \in \mathcal{Q}^\downarrow_N$, namely
 \begin{equation}
@@
 \end{equation}
-for all $\w$ in the interior of $\mathcal{Q}^\downarrow$.
+for all $\w$ in the interior of $\mathcal{Q}^\downarrow_N$.
 \end{lemma}
@@
 \begin{theorem}
-	If $\alpha = \frac{2a}{2b-1}$ for non-negative integers $a,b$ with $a \geq b$, then $H_\alpha(\w)$ is well-defined on the set of quasi-distributions $\w$, and moreover if $\w \succ \w'$ for two quasi-distributions $\w, \w'$ then $H_\alpha (\w) \leq H_\alpha(\w')$.
+	If $\alpha = \frac{2a}{2b-1}$ for non-negative integers $a,b$ with $a \geq b$, then $H_\alpha(\w)$ is well-defined on the set of quasi-distributions $\mathcal{Q}_N$, and moreover if $\w \succ \w'$ for two quasi-distributions $\w, \w'\in \mathcal{Q}_N$ then $H_\alpha (\w) \leq H_\alpha(\w')$.
 \end{theorem}
@@
 \begin{proof}
-We have $\alpha = \frac{2a}{2b+1} \geq \frac{2b}{2b-1} > 1$ and $\alpha$ is a rational with even numerator and odd denominator, so $\sum_i x_i^\alpha > 0$ and $H_\alpha(\bmz)$ is well-defined for all quasi-distributions $\bmz$.
-
-Given a fixed $\alpha$ for which $H_\alpha(\bmz)$ is well-defined, the function $H_\alpha$ is real-valued, smooth on the interior of $\mathcal{Q}^\downarrow$ and symmetric on any component permutation of $\bmz$.
+We have $\alpha = \frac{2a}{2b-1} \geq \frac{2b}{2b-1} > 1$ and $\alpha$ is a rational with even numerator and odd denominator, so $\sum_i x_i^\alpha > 0$ and $H_\alpha(\bmz)$ is well-defined for all quasi-distributions $\bmz$.
+
+Given a fixed $\alpha$ for which $H_\alpha(\bmz)$ is well-defined, the function $H_\alpha$ is real-valued, smooth on the interior of $\mathcal{Q}^\downarrow_N$ and symmetric in the components of $\bmz$.
 
@@
 \end{equation}
-We first note that for $\alpha$ in the given form, it is always true that
+We first note that for $\alpha= \frac{2a}{2b-1}$,  with $a\ge b$, it is always true that
 \begin{equation}
@@
 \end{equation}
-We then show that for $\alpha$ in the given form, the function $f(w) := -w^{\alpha - 1}$ is non-increasing.
+We show that for $\alpha$ in the given form, the function $f(w) := -w^{\alpha - 1}$ is non-increasing. \ddd{[Needs improving]}
 To this end, we first note that, for $\alpha > 1$, $f(w)$ has no discontinuities and we can obtain the first derivative
@@
 Finally, we note that the set $F := \{2a/(2b-1): a,b \in \mathbb{N} \text{ and } a \geq b\}$ is dense in the reals $\mathbb{R}_{>1}$, as any rational $c/d$ with $c>d$ can be approximated by  $c2^n / (d2^n-1) \in F$ for sufficiently large $n$.
+\ddd{[Needs edits]}
 
@@
 \begin{lemma}\label{H_add}
-	For any $\w, \w' \in \mathcal{Q}$, we have
+	For any $\w, \w' \in \mathcal{Q}_N$, we have
 	\begin{equation}
@@
 We now consider $\sum_{\bmz} W_\rho (\bmz)^{a/b}$ for $a/b >1$ and $a$ even and $b$ odd.
-We have that
+\ddd{[$a, b \rightarrow 2a, 2b-1$]}We have that
 \begin{align}
@@
 \end{equation}
-where $\alpha$ can take values of the form $2a/(2b+1)$, for non-negative integers $a,b$ to ensure once again that the argument of the logarithm is positive.
+where $\alpha$ can take values of the form $2a/(2b+1)$ \ddd{[2b+1 or 2b-1??]}, for non-negative integers $a,b$ to ensure once again that the argument of the logarithm is positive.
 
@@
 \begin{theorem}\label{thm:H2D}
-	Let $\w\in \mathbb{R}^N$ be a quasi-distribution and $\r \in \mathbb{R}^N$ a probability distribution with positive rational entries given by $r_i = a_i/K$ for positive integers $a_i$ and $K = \sum_{i=1}^N a_i$.
+	Let $\w\in \mathcal{Q}_N$ be a quasi-distribution and $\r \in \mathbb{R}^N$ a probability distribution with positive rational entries given by $r_i = a_i/K$ for positive integers $a_i$ and $K = \sum_{i=1}^N a_i$.
 	Then,
@@
 	\end{equation}
-	where $\alpha = 2c / (2d+1)$ for non-negative integers $c,d$ such that $H_\alpha(\bmz)$ is well-defined for all $\bmz$.
+	where $\alpha = 2a / (2b+1)$ for non-negative integers $a,b$ such that $H_\alpha(\bmz)$ is well-defined for all $\bmz$.
 \end{theorem}
@@
 \end{proof}
+\ddd{[Add in general divergence without product form]}
 

### 2021-06-25 magic_paper.tex
Mainly Appendices edits correcting and expanding.

@@
 Theories of magic states attempt to quantify this computational element via monotones and determine how these states may be efficiently transformed into useful forms.
-Here, we develop a statistical mechanical framework based on majorization in which Wigner negative magic states provide non-classical free energy that is processed under Clifford circuits.
+Here, we develop a statistical mechanical framework based on majorization in which Wigner negative magic states provide non-classical free energy that is processed under Clifford circuits for odd prime qudits.
 While traditional free energy is not defined in the presence of negativity, we show that majorization allows us to both quantify disorder in the Wigner representation and derive magic distillation bounds.
 These upper bounds are shown to be tighter than other bounds, such as from mana and thauma, and can incorporate hardware physics, such as temperature dependence and physical Hamiltonians.
-We also show that a subset of single-shot Renyi entropies remain well-defined on quasi-distributions, are fully meaningful in terms of data processing and can acquire negative values that signal magic.
-We show that the mana of a magic state is the measure of divergence of these Renyi entropies as one approaches the Shannon entropy for Wigner distributions, and discuss how distillation lower bounds could be obtained in this setting.
+We also show that a subset of single-shot R\'{e}nyi entropies remain well-defined on quasi-distributions, are fully meaningful in terms of data processing and can acquire negative values that signal magic.
+We show that the mana of a magic state is the measure of divergence of these R\'{e}nyi entropies as one approaches the Shannon entropy for Wigner distributions, and discuss how distillation lower bounds could be obtained in this setting.
 This use of majorization for quasi-distributions could find application in other studies of non-classicality, and raises novel questions in the context of classical statistical mechanics.
@@
 
-We show that the mana of a quantum state also arises as a residue in the $\alpha$--parameter for Renyi entropies, and gives the rate of divergence to $-\infty$ as we approach the Shannon entropy of a Wigner distribution (Equation (\ref{eq:mana-divergence})).
+We show that the mana of a quantum state also arises as a residue in the $\alpha$--parameter for R\'{e}nyi entropies, and gives the rate of divergence to $-\infty$ as we approach the Shannon entropy of a Wigner distribution (Equation (\ref{eq:mana-divergence})).
 Finally, in Section~\ref{sec:lower_bounds} we discuss how our approach could be extended and how it can be exploited to construct explicit lower bounds on distillation that take into account physical constraints.
@@
 
-However, it turns out that the analysis for the temperature-dependent bound given by Equation (\ref{eq:rate_bounds_proof}) implicitly made use of the single-shot Renyi divergence $D_\infty (\p \hspace{1pt}||\hspace{1pt} \r)$, which is given by
+However, it turns out that the analysis for the temperature-dependent bound given by Equation (\ref{eq:rate_bounds_proof}) implicitly made use of the single-shot R\'{e}nyi divergence $D_\infty (\p \hspace{1pt}||\hspace{1pt} \r)$, which is given by
 \begin{equation}
@@
 
-We can go further, and show that in fact a range of Renyi entropies remain both well-defined and meaningful in the Wigner representation. The $\alpha$--Renyi entropy $H_\alpha(\p)$ is defined as
+We can go further, and show that in fact a range of R\'{e}nyi entropies remain both well-defined and meaningful in the Wigner representation.
+The $\alpha$--R\'{e}nyi entropy $H_\alpha(\p)$ is defined as
 \begin{equation}
@@
 This monotonicity provides a meaningful extension of entropies to quasi-distributions, and the allowed values of $\alpha$ are dense in $\alpha >1$.
-Moreover we can prove the following result, which establishes the equivalence between Wigner negativity and the existence of negative Renyi entropy.
+Moreover we can prove the following result, which establishes the equivalence between Wigner negativity and the existence of negative R\'{e}nyi entropy.
 \begin{theorem}\label{thm:Magic}
@@
 
-The $\alpha \rightarrow 1$ limit of the Renyi entropy is not well-defined, however the Renyi entropy description shows that this diverges in a well-defined way.
+The $\alpha \rightarrow 1$ limit of the R\'{e}nyi entropy is not well-defined, however the R\'{e}nyi entropy description shows that this diverges in a well-defined way.
 We can write the divergence of the entropy as
@@
 \end{equation}
-Therefore, the mana of a state $\rho$ is the residue of a pole in $H_\alpha(W_\rho)$, and quantifies \emph{the divergence of the Renyi-entropy} as we approach the limiting Shannon entropy $H(W_\rho)$.
-
-We note that the Renyi entropy can be described as a $q$--deformation of the Shannon entropy~\cite{baez2011renyi}, and $H_\alpha(\p)$ can be related to the $q$--derivative of free energy.
-For this, the Renyi parameter becomes a temperature term $\alpha = \frac{T_0}{T}$ where $T_0$ is a reference temperature and derivatives are considered via the limit $T \rightarrow T_0$.
+Therefore, the mana of a state $\rho$ is the residue of a pole in $H_\alpha(W_\rho)$, and quantifies \emph{the divergence of the R\'{e}nyi-entropy} as we approach the limiting Shannon entropy $H(W_\rho)$.
+
+We note that the R\'{e}nyi entropy can be described as a $q$--deformation of the Shannon entropy~\cite{baez2011renyi}, and $H_\alpha(\p)$ can be related to the $q$--derivative of free energy.
+For this, the R\'{e}nyi parameter becomes a temperature term $\alpha = \frac{T_0}{T}$ where $T_0$ is a reference temperature and derivatives are considered via the limit $T \rightarrow T_0$.
 Therefore, if we try to push this to the present setting, the presence of Wigner negativity would correspond to a divergence in the first derivative of an effective free energy as $T \rightarrow T_0$.
@@
 
-\subsection{Renyi divergences and general distillation bounds}
-Every entropy can be obtained from a relative entropy~\cite{Gour_2020} and so we now state the extensions for Renyi divergences of Wigner distributions.
-The $\alpha$--Renyi divergence $D_\alpha(\p||\r)$ is defined as
+\subsection{R\'{e}nyi divergences and general distillation bounds}
+Every entropy can be obtained from a relative entropy~\cite{Gour_2020} and so we now state the extensions for R\'{e}nyi divergences of Wigner distributions.
+The $\alpha$--R\'{e}nyi divergence $D_\alpha(\p||\r)$ is defined as
 \begin{equation}
@@
 	Let $\tau$ be in the interior of $\F$. 
-	If $\alpha = \frac{2a}{2b-1}$ for non-negative integers $a,b$ with $a \geq b$, then the $\alpha$-Renyi divergence $D_\alpha(W_\rho || W_\tau)$ is well-defined for all states $\rho$, and the following hold:
+	If $\alpha = \frac{2a}{2b-1}$ for non-negative integers $a,b$ with $a \geq b$, then the $\alpha$-R\'{e}nyi divergence $D_\alpha(W_\rho || W_\tau)$ is well-defined for all states $\rho$, and the following hold:
 \begin{enumerate}
@@
 
-	The equivalence between (i) and (iii) follows from a similar argument.
+	The equivalence between (i) and (iii) follows from a similar argument where we mask negativity with a probability distribution.
 	Namely, let $\epsilon > 0$ be such that $\w(\epsilon) \coloneqq \epsilon \w + (1-\epsilon) \r$ and $\w'(\epsilon) \coloneqq \epsilon \w + (1-\epsilon) \r'$ are genuine probability distributions.
@@
 	\end{align*}
-Replacing $t = (\epsilon + c - 1)/\epsilon$, we see that $t$ can attain any real value for some value of $c$, so we retrieve the property on quasi-distributions $\w, \w'$.
+Replacing $t = (\epsilon + c - 1)/\epsilon$, we see that $t$ can attain any real value for some value of $c$, and so we deduce the required $L_1$ norm condition on quasi-distributions $\w, \w'$.
 \end{proof}
@@
 \begin{proof}
-	We denote the Wigner distributions of the states single-component vectors $\w(\rho)=W_\rho(x)$ and $ \w(\sigma)=W_\sigma(x)$. Likewise, we write $\w(\rho|\sigma) = W_{\rho|\tau}(\bmz)$.
+	We denote the Wigner distributions of the states single-component vectors $\w(\rho)=W_\rho(\z)$ and $ \w(\sigma)=W_\sigma(\z)$. Likewise, we write $\w(\rho|\sigma) = W_{\rho|\tau}(\bmz)$.
 	We choose the component indexing so that $\w(\rho|\sigma)^\downarrow = \w(\rho|\sigma)$ and so the components are sorted in non-increasing order.
@@
 
-In this section, we analyse Renyi entropies on quasi-probabilities and use them to get magic distillation bounds.
-
-\subsection{Renyi min-divergence from Lorenz curves}
+In this section, we analyse R\'{e}nyi entropies on quasi-probabilities and use them to get magic distillation bounds.
+
+\subsection{R\'{e}nyi min-divergence from Lorenz curves}
 We first demonstrate that the initial slope analysis on the Wigner quasi-distributions makes use of the min-relative divergence. We define 
@@
 
-\subsection{Well-defined Renyi entropies on quasi-distributions}
-
-We define the classical $\alpha$-Renyi entropy in terms of the Wigner quasi-distribution of any state $\rho$ as
-\begin{equation}
-	H_\alpha(W_\rho) := \frac{1}{1-\alpha} \log \sum_{\bmz} W_{\rho}(\bmz)^\alpha,
-\end{equation}
-where $\alpha$ can take values of the form $2a / (2b+1)$, for non-negative integers $a,b$ to ensure that the argument of the logarithm is positive. \ddd{[Need to expand on this]}
-
-For $\rho = \rho_{\rm{S}}(\epsilon)$, we get
-\begin{align}
-	&H_{\alpha}\left(W_{\rho_{\rm{S}}(\epsilon)}\right) = \frac{1}{1-\alpha}\log \left[ 8\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^\alpha + \left(-\frac{1}{3} + \frac{4}{9}\epsilon \right)^\alpha \right] \nonumber\\
-\end{align}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.3]{figs/H_vs_eps_a.pdf}
-    \caption{Here, the exponent is $\alpha =$ even$/$odd for $1.10 \leq \alpha \leq 1.50$.
-$H_\alpha$ is increasing in $\alpha$ and $\epsilon$.
-First dashed contour from the right corresponds to $H_\alpha(\rho_{\rm{S}}(\epsilon)) = 0$.
-Specifically, $H_\alpha(\rho_{\rm{S}}(0)) = 0$ that implies $6^\alpha - 2^{\alpha} = 8$, with the approximate solution $\alpha \approx 1.31$.
-    }
-    \label{fig:H}
-\end{figure}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.3]{figs/D_vs_eps_a.pdf}
-    \caption{Here, the exponent is $\alpha =$ even$/$odd for $1.10 \leq \alpha \leq 1.50$. $D_\alpha$ is decreasing in $\alpha$ and $\epsilon$ (\cref{thm:H2D}).
-    }
-    \label{fig:D}
-\end{figure}
-
-We now make use of known results from majorization theory to establish the Schur-concavity of $H_\alpha$ on Wigner quasi-distributions where $\alpha$ is such that $H_\alpha$ is well-defined. 
-We first define the notion of \emph{Schur-convex and Schur-convave functions} on a subset $\D \subseteq \mathbb{R}^N$.
-
+\subsection{Well-defined R\'{e}nyi entropies on quasi-distributions}
+
+We now make use of known results from majorization theory to establish the Schur-concavity of the R\'{e}nyi entropy $H_\alpha$ on Wigner quasi-distributions for a subset of $\alpha$ values.
+We consider the set of all quasi-distributions that is a hyper-plane in $\mathbb{R}^N$ given by
+\begin{equation}
+	\mathcal{Q}_N = \left\{ \w \in \mathbb{R}^N: \sum_{i=1}^N w_i = 1 \right\}.
+\end{equation}
+
+We define the notion of \emph{Schur-convex and Schur-convave functions} on a subset $\D \subseteq \mathbb{R}^N$.
 \begin{definition} 
@@
 \end{definition}
-We can consider the set of all quasi-distributions, which form a hyper-plane and are given by
-\begin{equation}
-	\D=\mathcal{Q}_N = \left\{ \w \in \mathbb{R}^N: \sum_{i=1}^N w_i = 1 \right\}.
-\end{equation}
-For functions that are symmetric, namely $f(\p) = f(\Pi \p)$ for any component permutation $\Pi$, it suffices to restrict to the following region,
-\begin{equation}
-	\mathcal{Q}^\downarrow_N = \{ \w \in \mathcal{Q}_N : w_1 \ge w_2 \ge \cdots \ge w_N\}.
-\end{equation}
-
-We now have that the Schur-Ostrowski theorem~\cite{cit:marshall} provides a characterization of symmetric, Schur-convex and Schur-concave functions on quasi-distributions.
-\ddd{[Needs a bit more expansion]}
+For any subset $\D \subseteq \mathbb{R}^N$ we define
+\begin{equation}
+	\mathcal{D}^\downarrow := \{ \w \in \mathcal{D} : w_1 \ge w_2 \ge \cdots \ge w_N\}.
+\end{equation}
+
+We now have the following fundamental result in majorization theory. \ddd{[Add original papers to cite bit]}
+\begin{theorem}[Schur-Ostrowski theorem~\cite{cit:marshall}] Let $\D\subseteq \mathbb{R}^N$ be a convex set with non-empty interior, and invariant under permutations of vector components.
+Let $f: \D \rightarrow \mathbb{R}$ be a continuously differentiable function on the interior of $\D$ and continuous on the whole of $\D$.
+Then $f$ is Schur-convex on $\D$ if and only if $f$ is a symmetric function on $\D$ and
+\begin{equation}
+	\partial_1 f(\w) \ge \partial_2 f(\w) \ge \cdots \ge \partial_N f(\w),
+\end{equation}
+for all $\w$ in the interior of $\mathcal{D}^\downarrow$.
+\end{theorem}
+Since the set $\mathcal{Q}_N$ of quasi-distributions obey the necessary conditions, we get the following result:
 \begin{lemma}
-	Let $f$ be a real-valued continuous function defined on $\mathcal{Q}^\downarrow_N$ that is continuously differentiable on the interior of $\mathcal{Q}^\downarrow_N$. 
-Then, $f$ is Schur-convex on $\mathcal{Q}^\downarrow_N$ if and only if $\partial_k f(\w)$ is non-increasing in $k$ for all $\w \in \mathcal{Q}^\downarrow_N$, namely
+	Let $f$ be a real-valued continuous function defined on $\mathcal{Q}_N$ that is continuously differentiable on the interior of $\mathcal{Q}_N$. 
+Then, $f$ is Schur-convex on $\mathcal{Q}_N$ if and only if it is a symmetric function and
 \begin{equation}
@@
 \end{equation}
-for all $\w$ in the interior of $\mathcal{Q}^\downarrow_N$.
+for all quasi-distributions $\w$ in the interior of $\mathcal{Q}^\downarrow_N$.
 \end{lemma}
 
-We can use the above to prove that $H_\alpha$ is Schur-concave on quasi-distributions for particular values of $\alpha$.
+The classical $\alpha$-R\'{e}nyi entropy on a probability distribution $\p = (p_i)$ is given by
+\begin{equation}
+	H_\alpha(\p) := \frac{1}{1-\alpha} \log \sum_i p_i^\alpha,
+\end{equation}
+where $\alpha \ge 0$.
+This means the function is well-defined on $\mathcal{Q}_N^+$, namely the set of quasi-distributions with non-negative components.
+We wish to extend the domain to the whole of $\mathcal{Q}_N$, however this requires that $w_i^\alpha$ be a real-number for any $w_i \in \mathbb{R}$.
+
+The exponent function $x \mapsto x^\alpha$ is well-defined and real-valued if $\alpha$ is a rational number of the form $\alpha = r / s$ where $s$ is an odd integer and $r \in \mathbb{N}$.
+However, we also require that $\sum_i w_i^\alpha > 0$ in order for the logarithm to return a real-value.
+To ensure this happens we take $\alpha = r/s$ with $r=2a$ being an even integer and $s=2b-1$ being an odd integer, for some integers $a,b\in  \mathbb{N}$, which implies that the following are all real-valued expressions,
+\begin{equation}
+0 \le w_i^\alpha = w_i^{\frac{2a}{2b-1}} = \left (w_i^{\frac{1}{2b-1}}\right )^{2a} =\left (w_i^{2a}\right )^{\frac{1}{2b-1}} = |w_i|^{\frac{2a}{2b-1}}.
+\end{equation}
+
+We next show that $H_\alpha (\w)$ for $\alpha = 2a/(2b-1)$ is a Schur-concave function on $\mathcal{Q}_N$.
 
@@
 \begin{proof}
-We have $\alpha = \frac{2a}{2b-1} \geq \frac{2b}{2b-1} > 1$ and $\alpha$ is a rational with even numerator and odd denominator, so $\sum_i x_i^\alpha > 0$ and $H_\alpha(\bmz)$ is well-defined for all quasi-distributions $\bmz$.
-
-Given a fixed $\alpha$ for which $H_\alpha(\bmz)$ is well-defined, the function $H_\alpha$ is real-valued, smooth on the interior of $\mathcal{Q}^\downarrow_N$ and symmetric in the components of $\bmz$.
+We have $\alpha = \frac{2a}{2b-1} \geq \frac{2b}{2b-1} > 1$ and $\alpha$ is a rational with even numerator and odd denominator, so $\sum_i w_i^\alpha > 0$ and $H_\alpha(\w)$ is well-defined for all quasi-distributions $\w$.
+
+We also have that $H_\alpha(\w)$ is well-defined, continuous, differentiable on the interior of $\mathcal{Q}_N$ and symmetric in the components of $\w$.
 
@@
 \end{equation}
-We first note that for $\alpha= \frac{2a}{2b-1}$,  with $a\ge b$, it is always true that
+For $\alpha= \frac{2a}{2b-1}$,  with $a\ge b$, we have that
 \begin{equation}
@@
 \end{equation}
-We show that for $\alpha$ in the given form, the function $f(w) := -w^{\alpha - 1}$ is non-increasing. \ddd{[Needs improving]}
-To this end, we first note that, for $\alpha > 1$, $f(w)$ has no discontinuities and we can obtain the first derivative
-\begin{equation}
-	f'(w) = -(\alpha - 1) w^{\alpha-2} = -(\alpha - 1)w^{\frac{2a-4b+2}{2b-1}} \leq 0,
+The first derivative of the function $g(w) := -w^{\alpha - 1}$ is given by
+\begin{equation}
+	g'(w) = -(\alpha - 1) w^{\alpha-2} = -(\alpha - 1)w^{\frac{2a-4b+2}{2b-1}} \leq 0,
 \end{equation}
@@
 \end{equation}
-where each expression is well-defined because the rational exponent has odd denominator.
+and so $g(w)$ is non-increasing in $w$.
 
@@
 \end{equation}
-which leads to
-\begin{equation}
-	\frac{\partial H_\alpha}{\partial w_i} \leq \frac{\partial H_\alpha}{\partial w_j}.
-\end{equation}
-Therefore, $H_\alpha$ is Schur-concave and
+which implies that
+\begin{equation}
+	\frac{\partial H_\alpha}{\partial w_i}(\w) \leq \frac{\partial H_\alpha}{\partial w_j}(\w),
+\end{equation}
+for any $\w$ in the interior of $\mathcal{Q}_N^\downarrow$.
+Therefore, $H_\alpha$ is Schur-concave on $\mathcal{Q}_N$ and
 \begin{equation}
@@
 \end{equation}
-for any quasi-distributions $\w, \w'$ that obey $\w \succ \w'$.
+for any quasi-distributions $\w, \w' \in \mathcal{Q}_N$ that obey $\w \succ \w'$.
 \end{proof}
@@
 If $\alpha =2a/(2b-1)$ with $\alpha < 1$, then $f(w) := \frac{-w^{\alpha-1}}{\alpha-1}$ is not monotonic.
-For example, if $\alpha = 2/3$, then $f(-2/6) = -4.33$, $f(-1/6) = -5.45$ and $f(+2/6) = +4.33$.
-Finally, we note that the set $F := \{2a/(2b-1): a,b \in \mathbb{N} \text{ and } a \geq b\}$ is dense in the reals $\mathbb{R}_{>1}$, as any rational $c/d$ with $c>d$ can be approximated by  $c2^n / (d2^n-1) \in F$ for sufficiently large $n$.
+For example, if $\alpha = 2/3$, then $f(-2/6) = -4.33$, $f(-1/6) = -5.45$ and $f(+2/6) = +4.33$..
 \ddd{[Needs edits]}
 
-We can check that additivity of $H_{\alpha}$ also holds on quasi-distributions. 
+  Finally, we note that the set $F := \{2a/(2b-1): a,b \in \mathbb{N} \text{ and } a \geq b\}$ is dense in the reals $\mathbb{R}_{>1}$, as any rational $c/d$ with $c>d$ can be approximated by  $c2^n / (d2^n-1) \in F$ for sufficiently large $n$
+
+We also have that $H_{\alpha}$ is additive on products of quasi-distributions. 
 \begin{lemma}\label{H_add}
-	For any $\w, \w' \in \mathcal{Q}_N$, we have
+	For any $\w \in \mathcal{Q}_N$ and $\w' \in \mathcal{Q}_{N'}$, we have
 	\begin{equation}
@@
 \begin{proof}
-	That fact that negativity does not affect additivity can be seen directly as follows
 	\begin{align*}
@@
 
-We now show the following simple equivalence.
+Applied to Wigner distributions $W_\rho (\z)$ for a quantum state $\rho$ we have
+\begin{equation}
+	H_\alpha(W_\rho) := \frac{1}{1-\alpha} \log \sum_{\bmz} W_{\rho}(\bmz)^\alpha,
+\end{equation}
+where $\alpha$ can take values of the form $2a / (2b-1)$, for non-negative integers $a,b$. For the noisy Strange state $\rho = \rho_{\rm{S}}(\epsilon)$, this becomes
+\begin{align}
+	H_{\alpha}\left(W_{\rho_{\rm{S}}(\epsilon)}\right) = \frac{1}{1-\alpha}\log \left[ 8\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^\alpha + \left(-\frac{1}{3} + \frac{4}{9}\epsilon \right)^\alpha \right] \nonumber\\
+\end{align}
+\begin{figure}[t!]
+    \centering
+    \includegraphics[scale=0.3]{figs/H_vs_eps_a.pdf}
+    \caption{The R\'{e}nyi entropy $H_\alpha$ is increasing in $\alpha$ and $\epsilon$.
+First dashed contour from the right corresponds to $H_\alpha(\rho_{\rm{S}}(\epsilon)) = 0$.
+Specifically, $H_\alpha(\rho_{\rm{S}}(0)) = 0$ that implies $6^\alpha - 2^{\alpha} = 8$, with the approximate solution $\alpha \approx 1.31$.
+    }
+    \label{fig:H}
+\end{figure}
+We now show the following equivalence between Wigner negativity and negative R\'{e}nyi entropies.
 \begingroup
@@
 \begin{theorem}
-	A quantum state $\rho$ has Wigner negativity if and only if $H_\alpha(W_\rho) < 0$ for some $\alpha =  \frac{2a}{2b-1}$, with integers $a \geq b$.
+	A quantum state $\rho$ has Wigner negativity if and only if $H_\alpha(W_\rho) < 0$ for some $\alpha =  \frac{2a}{2b-1}$, with positive integers $a \geq b$.
 \end{theorem}
@@
 Conversely, suppose $\rho$ has negativity in its Wigner representation.
-This implies that $\sum_{\bmz} |W_\rho (\bmz)| >1$.
-We now consider $\sum_{\bmz} W_\rho (\bmz)^{a/b}$ for $a/b >1$ and $a$ even and $b$ odd.
-\ddd{[$a, b \rightarrow 2a, 2b-1$]}We have that
-\begin{align}
-\sum_{\bmz} W_\rho (\bmz)^{a/b} &= \sum_{\bmz} |W_\rho (\bmz)|^{a/b} \nonumber \\
+This in particular implies that $\sum_{\bmz} |W_\rho (\bmz)| >1$.
+We now consider $\sum_{\bmz} W_\rho (\bmz)^{\frac{2a}{2b-1}}$ for positive integers $a\ge b$.
+We have that
+\begin{align}
+\sum_{\bmz} W_\rho (\bmz)^{\frac{2a}{2b-1}} &= \sum_{\bmz} |W_\rho (\bmz)|^{\frac{2a}{2b-1}} \nonumber \\
 &= \sum_{\bmz} |W_\rho (\bmz)|^{1+ \epsilon},
 \end{align}
-where $\epsilon = a/b - 1 >0$.
-By choosing $a$ and $b$ appropriately we can make $\epsilon$ arbitrarily close to $0$.
-More precisely, there exists a sequence $\epsilon_n=a_n/b_n$ with valid integer pairs $a_n, b_n$ such that
-\begin{equation}
-\sum_{\bmz} |W_\rho (\bmz)|^{1+ \epsilon_n} \rightarrow \sum_{\bmz} |W_\rho (\bmz)| >1.
-\end{equation}
-Since $\frac{1}{1-\alpha}= -\frac{b_n}{a_n} <0$ for any $n$ it follows that $H_\alpha (W_\rho) = \frac{1}{1-\alpha} \log \sum_{\bmz} W_\rho (\bmz)^\alpha  <0 $ at some point in the sequence, which completes the proof.
-\end{proof}
-Therefore Wigner negativity coincides with negativity of a Renyi entropy.
-
-\subsection{Renyi divergences on quasi-distributions}
-Now we define the classical $\alpha$-Renyi divergence in terms of the Wigner quasi-distribution of any magic state $\rho$ and the Wigner probability distribution of any equilibrium state $\tau$ as
+where $\epsilon = \alpha -1=\frac{2a}{2b-1} - 1 >0$.
+By choosing the positive integers $a$ and $b$ sufficiently large we can make $\epsilon$ arbitrarily close to $0$.
+This implies that there exists a sequence $\epsilon_n= \alpha_n-1 =\frac{2a_n}{2b_n-1} - 1$ with integer pairs $a_n, b_n$ such that
+\begin{equation}
+\sum_{\bmz} |W_\rho (\bmz)|^{1+ \epsilon_n} \rightarrow \sum_{\bmz} |W_\rho (\bmz)| >1,
+\end{equation}
+as $n$ increases.
+Since $\frac{1}{1-\alpha_n} <0$ for any $n$ it follows that $H_{\alpha_n} (W_\rho) = \frac{1}{1-\alpha_n} \log \sum_{\bmz} W_\rho (\bmz)^{\alpha_n}  <0 $ at some point in the sequence, which completes the proof.
+\end{proof}
+Therefore Wigner negativity coincides with negativity of a R\'{e}nyi entropy.
+
+\subsection{R\'{e}nyi divergences on quasi-distributions}
+Now we define the classical $\alpha$-R\'{e}nyi divergence in terms of the Wigner quasi-distribution of any magic state $\rho$ and the Wigner probability distribution of any equilibrium state $\tau$ as
 \begin{equation}
@@
 
-We can connect the $\alpha$-Renyi entropy and divergence for quasi-distributions via the following result.
+We can connect the $\alpha$-R\'{e}nyi entropy and divergence for quasi-distributions via the following result.
 
@@
 
-We now establish monotonicity for Renyi relative divergences.
+We now establish monotonicity for R\'{e}nyi relative divergences.
 \begin{theorem}\label{thm:DSchur}
@@
 	Let $\tau$ be a state in the interior of $\F$ and $\alpha = 2a / (2b-1)$ for non-negative integers $a,b$ with $a \geq b$.
-Then, the $\alpha$-Renyi divergence $D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)$ is well-defined for all states $\rho$, and the following hold:
+Then, the $\alpha$-R\'{e}nyi divergence $D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)$ is well-defined for all states $\rho$, and the following hold:
 \begin{enumerate}
@@
 \begin{proof}
-	The bound is a direct consequence of the properties of the $\alpha$--Renyi diveregence, proven in~\cref{thm:Da_props}.
+	The bound is a direct consequence of the properties of the $\alpha$--R\'{e}nyi diveregence, proven in~\cref{thm:Da_props}.
 

### 2021-06-25 magic_paper.tex
minor changes

--- 2021-06-24 magic_paper.tex
@@
 \begin{equation}
-	\theta_{\rm{max}}(\rho) \coloneqq \log{\min{\{2\hspace{1pt}\sn{V}+1 : V \geq \rho\}}}
+	\theta_{\rm{max}}(\rho) \coloneqq \log \min{\{2\hspace{1pt}\sn{V}+1 : V \geq \rho\}}
 \end{equation}
@@
 \begin{equation}
-	F \coloneqq \tr[H \tau] - \beta^{-1}S(\tau) = -\beta^{-1}\log{\Z},
+	F \coloneqq \tr[H \tau] - \beta^{-1}S(\tau) = -\beta^{-1}\log \Z,
 \end{equation}
@@
     \begin{enumerate}
-        \item[(i)]\label{en:wo1} Real-valued: $\W{\E}(\z|\y) \in \mathbb{R}^{d_A^2} \times \mathbb{R}^{d_B^2}$;
+        \item[(i)]\label{en:wo1} Real-valued: $\W{\E}(\bmz|\bmy) \in \mathbb{R}^{d_A^2} \times \mathbb{R}^{d_B^2}$;
         \item[(ii)]\label{en:wo2} Normalised: $\sum_{\bmy \in \cal{P}_{d_B}} \W[\bmz|\bmy]{\E} = 1$ \\ 
         for any $\bmz \in \cal{P}_{d_A}$;
-        \item[(iii)]\label{en:wo3} Bounded: $\abs{\W[\bmy|\bmz]{\E}} \leq \frac{d_A}{d_B}$;
-	    \item[(iv)]\label{en:wo4} $\W[\bmy]{\E(\rho)} = \sum\limits_{\bmz \in \cal{P}_{d_{A}}} \W[\bmy|\bmz]{\E} \W[\bmz]{\rho}$ for any $\bmy \in \cal{P}_{d_B}$.
+        \item[(iii)]\label{en:wo3} Bounded: $\abs{\W[\bmz|\bmy]{\E}} \leq \frac{d_A}{d_B}$;
+	    \item[(iv)]\label{en:wo4} $\W[\bmz]{\E(\rho)} = \sum\limits_{\bmy \in \cal{P}_{d_{A}}} \W[\bmz|\bmy]{\E} \W[\bmy]{\rho}$ for any $\bmz \in \cal{P}_{d_B}$.
     \end{enumerate}
@@
 \end{proof}
-We note that the vectors $\r, \r'$ with rational components form a dense subset of the positive probability distributions, do not consider technical fine-print that would not affect actual physical measurements, which always have a finite resolution.
+We note that the vectors $\r, \r'$ with rational components form a dense subset of the positive probability distributions, and do not consider further technicalities that have no impact on actual physical measurements, which always have a finite resolution.
 \subsection{Component-multiplicity pairs}

### 2021-06-25 magic_paper.tex
Edits done on my side. Refs to be added, and final proofreading before sending off.

--- 2021-06-25 magic_paper.tex
@@
 Theories of magic states attempt to quantify this computational element via monotones and determine how these states may be efficiently transformed into useful forms.
-Here, we develop a statistical mechanical framework based on majorization in which Wigner negative magic states provide non-classical free energy that is processed under Clifford circuits for odd prime qudits.
+Here, we develop a statistical mechanical framework based on majorization in which Wigner negative magic states provide non-classical free energy that is processed under Clifford circuits for qudits of odd prime dimension.
 While traditional free energy is not defined in the presence of negativity, we show that majorization allows us to both quantify disorder in the Wigner representation and derive magic distillation bounds.
@@
 We also show that a subset of single-shot R\'{e}nyi entropies remain well-defined on quasi-distributions, are fully meaningful in terms of data processing and can acquire negative values that signal magic.
-We show that the mana of a magic state is the measure of divergence of these R\'{e}nyi entropies as one approaches the Shannon entropy for Wigner distributions, and discuss how distillation lower bounds could be obtained in this setting.
+We find that the mana of a magic state is the measure of divergence of these R\'{e}nyi entropies as one approaches the Shannon entropy for Wigner distributions, and discuss how distillation lower bounds could be obtained in this setting.
 This use of majorization for quasi-distributions could find application in other studies of non-classicality, and raises novel questions in the context of classical statistical mechanics.
@@
 
-\begin{theorem} Majorization in any $\R_\sigma$ implies the monotonicity of sum-negativity. 
+\begin{theorem} Majorization in any $\R_\sigma$ implies the monotonicity of sum-negativity/mana. 
 \end{theorem}
@@
 If we have a magic state $\rho$ that has negativity in its Wigner representation, then, as discussed, its Lorenz curve over-shoots $1$ and reaches a non-trivial maximum $L_\star$ that depends on the particular state.
-There is an simple relation between $L_\star$ and sum-negativity or mana, which is provided by the following result.
+There is an simple relation between $L_\star$ and sum-negativity/mana, which is provided by the following result.
 \begin{theorem}\label{lem:lcmax}
@@
 \end{equation}
-To extend to quasi-distributions we must ensure the following: (a) the entropy is well-defined on quasi-distributions, and (b) obeys monotonicity under stabilizer/free operations.
-In the Appendices we show the following.
+To extend to quasi-distributions we must ensure the following: (a) the entropy is well-defined on quasi-distributions, and (b) obeys monotonicity under the majorization pre-order.
+In Appendix~\ref{app:single-shot} we prove the following.
 \begin{theorem}\label{thm:HSchur} 
-	If $\alpha = \frac{2a}{2b-1}$ for non-negative integers $a,b$ with $a \geq b$, then $H_\alpha(\w)$ is well-defined on the set of quasi-distributions, and moreover if $\w \succ \w'$ for two quasi-distributions $\w, \w'$ then $H_\alpha (\w) \leq H_\alpha(\w')$.
+	If $\alpha = \frac{2a}{2b-1}$ for positive integers $a,b$ with $a \geq b$, then $H_\alpha(\w)$ is well-defined on the set of quasi-distributions, and moreover if $\w \succ \w'$ for two quasi-distributions $\w, \w'$ then $H_\alpha (\w) \leq H_\alpha(\w')$.
 \end{theorem}
-This monotonicity provides a meaningful extension of entropies to quasi-distributions, and the allowed values of $\alpha$ are dense in $\alpha >1$.
-Moreover we can prove the following result, which establishes the equivalence between Wigner negativity and the existence of negative R\'{e}nyi entropy.
+This monotonicity provides a meaningful extension of entropies to quasi-distributions.
+The unusual form of the $\alpha$ parameter is required so that the entropy function is well-defined and real-valued for all $\w$.
+The allowed values of $\alpha$ are dense in $\alpha >1$, however, while R\'{e}nyi entropies on probabilities can also be used for $0 < \alpha <1$ it turns out that for quasi-probability distributions this parameter regime is no longer monotonic in terms of the majorization pre-order (see Appendix~\ref{app:single-shot} for details).
+
+We can prove the following result, which establishes the equivalence between Wigner negativity and the existence of negative R\'{e}nyi entropy.
 \begin{theorem}\label{thm:Magic}
-	A quantum state $\rho$ has Wigner negativity if and only if $H_\alpha(W_\rho) <0$ for some $\alpha =  \frac{2a}{2b-1}$, with integers $a \ge b$.
+	A quantum state $\rho$ has Wigner negativity if and only if $H_\alpha(W_\rho) <0$ for some $\alpha =  \frac{2a}{2b-1}$, with positive integers $a \ge b$.
 \end{theorem}
@@
 
-The $\alpha \rightarrow 1$ limit of the R\'{e}nyi entropy is not well-defined, however the R\'{e}nyi entropy description shows that this diverges in a well-defined way.
-We can write the divergence of the entropy as
+The $\alpha \rightarrow 1$ limit of the R\'{e}nyi entropy is not well-defined, however it diverges in a well-defined way. We can write the divergence of the entropy as 
 \begin{equation}
@@
 \begin{equation}\label{eq:mana-divergence}
-\M(\rho) = -\lim_{\epsilon \rightarrow 0^+} \epsilon H_{1-\epsilon}(W_\rho).
+\M(\rho) = -\lim_{\epsilon \rightarrow 0^+} \epsilon H_{1+\epsilon}(W_\rho).
 \end{equation}
@@
 
-We note that the R\'{e}nyi entropy can be described as a $q$--deformation of the Shannon entropy~\cite{baez2011renyi}, and $H_\alpha(\p)$ can be related to the $q$--derivative of free energy.
+We also note that the R\'{e}nyi entropy can be described as a $q$--deformation of the Shannon entropy~\cite{baez2011renyi}, and that $H_\alpha(\p)$ can be related to the $q$--derivative of free energy.
 For this, the R\'{e}nyi parameter becomes a temperature term $\alpha = \frac{T_0}{T}$ where $T_0$ is a reference temperature and derivatives are considered via the limit $T \rightarrow T_0$.
 Therefore, if we try to push this to the present setting, the presence of Wigner negativity would correspond to a divergence in the first derivative of an effective free energy as $T \rightarrow T_0$.
-We can therefore speculate whether the presence of magic in Clifford circuits admits a sensible interpretation in terms of a zeroth-order phase transition [\ddd{cite}].
-However we do not pursue this speculative line here, but just note that other works exist in which computational transitions are considered in relation to phase transitions [\ddd{cite}].
+It is interesting to speculate whether the presence of magic in Clifford circuits could admit a sensible interpretation in terms of zeroth-order phase transitions [\ddd{cite}].
 
@@
 Every entropy can be obtained from a relative entropy~\cite{Gour_2020} and so we now state the extensions for R\'{e}nyi divergences of Wigner distributions.
-The $\alpha$--R\'{e}nyi divergence $D_\alpha(\p||\r)$ is defined as
-\begin{equation}
-	D_\alpha(\p \hspace{1pt}||\hspace{1pt} \r) := \frac{1}{\alpha-1} \log \sum_i p_i^\alpha r_i^{1-\alpha},
-\end{equation}
-where $\p$ can be a quasi-distribution, $\r$ a probability distribution with positive components and $\alpha$ can take the same values as for $H_\alpha$.
-In~\cref{app:lcst_technical}, we also show that the divergence satisfies the following.
+The $\alpha$--R\'{e}nyi divergence $D_\alpha(\w||\r)$ is defined as
+\begin{equation}
+	D_\alpha(\w \hspace{1pt}||\hspace{1pt} \r) := \frac{1}{\alpha-1} \log \sum_i w_i^\alpha r_i^{1-\alpha},
+\end{equation}
+where $\w$ can be a quasi-distribution, $\r$ a probability distribution with positive components. In~\cref{app:single-shot}, we also show that the divergence satisfies the following.
 
@@
 	Let $\tau$ be in the interior of $\F$. 
-	If $\alpha = \frac{2a}{2b-1}$ for non-negative integers $a,b$ with $a \geq b$, then the $\alpha$-R\'{e}nyi divergence $D_\alpha(W_\rho || W_\tau)$ is well-defined for all states $\rho$, and the following hold:
+	If $\alpha = \frac{2a}{2b-1}$ for positive integers $a,b$ with $a \geq b$, then the $\alpha$-R\'{e}nyi divergence $D_\alpha(W_\rho || W_\tau)$ is well-defined for all quantum states $\rho$, and the following hold:
 \begin{enumerate}
@@
 
-We can now apply this to obtain magic distillation bounds that describe Wigner negativity directly as a form of non-classical free energy.
-\begin{theorem}\label{thm:entropic_bounds} 
-	Consider a magic state distillation protocol that converts a magic state $\rho^{\otimes n} \longrightarrow \rho'^{\otimes m}$, which when applied to a reference stabilizer state $\tau^{\otimes n}$ results in $\tau^{\otimes n} \longrightarrow \tau'^{\otimes m}$.
-
-	We have the following family of upper bounds on the magic distillation rate $R := m/n$,
-	\begin{equation}
-		R \leq \frac{F_\alpha(W_\rho) - F_\alpha(W_\tau)}{F_\alpha(W_{\rho'}) - F_\alpha(W_{\tau'})},
-	\end{equation}
-	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ and $\beta F_\alpha(W_\rho) := D_\alpha (W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) - \log \Z$ is the $\alpha$--free energy of the Wigner distribution.
-\ddd{[$\Z$ needs discussion]}
+We can now apply this to obtain a family of magic distillation bounds based on R\'{e}nyi divergences.
+\begin{theorem}
+	Consider a general magic state distillation process on prime dimension qudits, that converts a magic state $\rho^{\otimes n} \longrightarrow \E(\rho^{\otimes n})=\rho'^{\otimes m}$and let $\tau$ be any full-rank stabilizer reference state on a qudit.
+Then the distillation rate $R := m/n$ is upper bounded as,
+	\begin{equation}
+		R \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{D^{\rm reg}_\alpha( \rho', \tau')},
+	\end{equation}
+	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ and with the regularized divergence
+	\begin{equation}
+D^{\rm reg}_\alpha( \rho', \tau') = \frac{1}{m} D_\alpha (W_{\rho'^{\otimes m}} || W_{\tau'_m}),
+\end{equation}
+between the output magic state $\rho'^{\otimes m}$ and $\tau'_m = \E(\tau^{\otimes n})$.
 \end{theorem}
-\ddd{[Perhaps remove free energy form...and allow $\frac{1}{m} D_\alpha(\rho'_m|| \tau'_m)$ general term with no assumption on correlations. ]}
-
-For magic protocols that give unital maps, the above bound reduces to the simpler form
-\begin{equation}
-	R \leq \frac{2\log d - H_{\alpha}(W_\rho)}{2\log d - H_{\alpha}(W_{\rho'})}.
+The proof is given in Appendix~\ref{app:single-shot}.
+
+While this bound is abstract in its present form, it does suggest future applications by viewing $D^{\rm reg}_\alpha( \rho', \tau')$ within the context of hypothesis testing, as a measure of distinguishability between $\rho'^{\otimes m}$ and the $m$ qudit state $\tau'_m$.
+However in order to properly link with hypothesis-testing one would have to first extend such results to quasi-distributions.
+
+If correlations in $\tau'_m$ between subsystems can be neglected then we simply get
+\begin{equation}
+D^{\rm reg}_\alpha( \rho', \tau') = D_\alpha (W_{\rho'} || W_{\tau'}),
+\end{equation}
+which gives a generalized version of Theorem \ref{thm:free-energy}.
+
+We can illustrate a simple application of the above bound for magic protocols that give unital maps. In this case it is easy to see that the above bound reduces to the simple form
+\begin{equation}
+	R \leq R_\alpha=\frac{2\log d - H_{\alpha}(W_\rho)}{2\log d - H_{\alpha}(W_{\rho'})}.
 \end{equation}
@@
 \begin{equation}
-	R \leq \frac{2(1-\alpha)\log 3 - \log \left [8(\frac{1}{6} - \frac{\epsilon}{18})^\alpha + (-\frac{1}{3} + \frac{4\epsilon}{9})^\alpha\right ] }{2(1-\alpha)\log 3 + \alpha \log 6 - \log (8 + 2^\alpha )}.
-\end{equation}
-The upper bound can be numerically minimized over $\alpha$, for any $\epsilon$.
+	R \leq R_\alpha=\frac{2(1-\alpha)\log 3 - \log \left [8(\frac{1}{6} - \frac{\epsilon}{18})^\alpha + (-\frac{1}{3} + \frac{4\epsilon}{9})^\alpha\right ] }{2(1-\alpha)\log 3 + \alpha \log 6 - \log (8 + 2^\alpha )}.
+\end{equation}
+This upper bound can be numerically minimized over $\alpha$, for any $\epsilon$.
+The case $R_{10}$ is shown in Figure~\ref{fig:distill_bounds} and numerical evidence shows it is close to the optimal bound from majorization.
 %
@@
 
-\section{Single-shot entropies on quasi-distributions and magic distillation bounds}
+\section{Single-shot entropies on quasi-distributions and magic distillation bounds}\label{app:single-shot}
 
@@
 
-We next show that $H_\alpha (\w)$ for $\alpha = 2a/(2b-1)$ is a Schur-concave function on $\mathcal{Q}_N$.
+We next show that $H_\alpha (\w)$ for $\alpha = 2a/(2b-1)$ is a Schur-concave function on $\mathcal{Q}_N$ provided that $a \ge b$.
 
@@
 \begin{theorem}
-	If $\alpha = \frac{2a}{2b-1}$ for non-negative integers $a,b$ with $a \geq b$, then $H_\alpha(\w)$ is well-defined on the set of quasi-distributions $\mathcal{Q}_N$, and moreover if $\w \succ \w'$ for two quasi-distributions $\w, \w'\in \mathcal{Q}_N$ then $H_\alpha (\w) \leq H_\alpha(\w')$.
+	If $\alpha = \frac{2a}{2b-1}$ for positive integers $a,b$ with $a \geq b$, then $H_\alpha(\w)$ is well-defined on the set of quasi-distributions $\mathcal{Q}_N$, and moreover if $\w \succ \w'$ for two quasi-distributions $\w, \w'\in \mathcal{Q}_N$ then $H_\alpha (\w) \leq H_\alpha(\w')$.
 \end{theorem}
@@
 \end{proof}
-We note that if $\alpha =a/b$ with both $a$ and $b$ odd, then $H_\alpha$ is not well-defined for all quasi-probabilities, however if the actual set of quasi-distributions has a sufficiently bounded negativity, then $\log \sum_{\bmz} W_\rho(\bmz)^\alpha$ can still be obtained for $a$ odd, provided the sum is never negative.
-
-If $\alpha =2a/(2b-1)$ with $\alpha < 1$, then $f(w) := \frac{-w^{\alpha-1}}{\alpha-1}$ is not monotonic.
-For example, if $\alpha = 2/3$, then $f(-2/6) = -4.33$, $f(-1/6) = -5.45$ and $f(+2/6) = +4.33$..
-\ddd{[Needs edits]}
-
-  Finally, we note that the set $F := \{2a/(2b-1): a,b \in \mathbb{N} \text{ and } a \geq b\}$ is dense in the reals $\mathbb{R}_{>1}$, as any rational $c/d$ with $c>d$ can be approximated by  $c2^n / (d2^n-1) \in F$ for sufficiently large $n$
-
-We also have that $H_{\alpha}$ is additive on products of quasi-distributions. 
+While we have integers $a,b$ such that $0 < \alpha=\frac{2a}{2b-1} < 1$ and $H_\alpha(\w)$ is well-defined, it turns out that monotonicity does not hold if we drop the condition $a \ge b$.
+If $\alpha =2a/(2b-1)$ with $\alpha < 1$, then $g(w) := \frac{-w^{\alpha-1}}{\alpha-1}$ is no longer monotonic for all $w \in \mathbb{R}$, and the problem occurs when comparing $w_i < 0$ and $w_j >0$.
+For example the function $g(x) = \frac{1}{x^3}$ is monotone decreasing on $x<0$ and $x>0$ separately, however it is not monotone on the full real-line.
+
+We note that if $\alpha =r/s$ with both $r$ and $s$ odd, then $H_\alpha$ is not well-defined for all quasi-probabilities, however if the actual set of quasi-distributions has a sufficiently bounded levels negativity, then $\log \sum_{\bmz} W_\rho(\bmz)^\alpha$ can still be obtained for $r$ odd, provided the total sum is never negative.
+This occurs for Wigner distributions, where we have $|W_\rho(\z)| \ge 1/d$ for a $d$--dimensional quantum system.
+
+We also note that the set $F := \{2a/(2b-1): a,b \in \mathbb{N} \text{ and } a \geq b\}$ is dense in the reals $\mathbb{R}_{>1}$, as any rational $c/d$ with $c>d$ can be approximated by  $c2^n / (d2^n-1) \in F$ for sufficiently large $n$.
+
+We have that $H_{\alpha}$ is additive on products of quasi-distributions., which we state for completeness.
 \begin{lemma}\label{H_add}
@@
 	\end{equation}
-	where $\alpha = 2a/(2b-1)$ with integers $a\ge b$.
+	where $\alpha = 2a/(2b-1)$ with positive integers $a\ge b$.
 \end{lemma}
@@
 \subsection{R\'{e}nyi divergences on quasi-distributions}
-Now we define the classical $\alpha$-R\'{e}nyi divergence in terms of the Wigner quasi-distribution of any magic state $\rho$ and the Wigner probability distribution of any equilibrium state $\tau$ as
-\begin{equation}
-	D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) := \frac{1}{\alpha - 1} \log \sum_{\bmz} W_{\rho}(\bmz)^\alpha W_{\tau}(\bmz)^{1-\alpha},
-\end{equation}
-where $\alpha$ can take values of the form $2a/(2b+1)$ \ddd{[2b+1 or 2b-1??]}, for non-negative integers $a,b$ to ensure once again that the argument of the logarithm is positive.
-
-We can connect the $\alpha$-R\'{e}nyi entropy and divergence for quasi-distributions via the following result.
-
+We now define the $\alpha$-R\'{e}nyi divergence for a quasi-distribution $\w \in \mathcal{Q}_N$ relative to a full-rank probability distribution $\r\in \mathcal{Q}_N^+$ as
+\begin{equation}
+	D_\alpha(\w||\r) := \frac{1}{\alpha - 1} \log \sum_{i} w_i^\alpha r_i^{1-\alpha},
+\end{equation}
+where $\alpha=2a/(2b-1)$ for positive integers $a \ge b$.
+We now have the following result that relates the R\'{e}nyi divergence to the R\'{e}nyi entropy on a dense subset of probability distributions.
 \begin{theorem}\label{thm:H2D}
-	Let $\w\in \mathcal{Q}_N$ be a quasi-distribution and $\r \in \mathbb{R}^N$ a probability distribution with positive rational entries given by $r_i = a_i/K$ for positive integers $a_i$ and $K = \sum_{i=1}^N a_i$.
+	Let $\w\in \mathcal{Q}_N$ be a quasi-distribution and $\r \in \mathcal{Q}_N^+$ a probability distribution with positive rational entries given by $r_i = a_i/K$ for positive integers $a_i$ and $K = \sum_{i=1}^N a_i$.
 	Then,
@@
 	\end{equation}
-	where $\alpha = 2a / (2b+1)$ for non-negative integers $a,b$ such that $H_\alpha(\bmz)$ is well-defined for all $\bmz$.
+	where $\alpha = 2a / (2b-1)$ for positive integers $a \ge b$.
 \end{theorem}
 \begin{proof}
-	For the given form of $\alpha$ and positive $r_i,\ i=1,\dots,N$, $D_\alpha(\bmz \hspace{1pt}||\hspace{1pt} \r)$ is well-defined for all $\bmz$.
-
-	The expression follows from the definition of $\Gamma_{\bma}$ which gives
+	For the given form of $\alpha$ and positive $r_i,\ i=1,\dots,N$, $D_\alpha(\w || \r)$ is well-defined for all $\w$. From the definition of $\Gamma_{\bma}$ we have
 	\begin{equation}
@@
 \end{proof}
-
-We now establish monotonicity for R\'{e}nyi relative divergences.
+With this we now establish monotonicity for R\'{e}nyi relative divergences.
 \begin{theorem}\label{thm:DSchur}
@@
 \end{proof}
-
+We now specialise to Wigner distributions of quantum states, and quantum operations that map the set of free states $\F$ into itself.
 \begingroup
@@
 \begin{theorem}
-	Let $\tau$ be a state in the interior of $\F$ and $\alpha = 2a / (2b-1)$ for non-negative integers $a,b$ with $a \geq b$.
+	Let $\tau$ be a state in the interior of $\F$ and $\alpha = 2a / (2b-1)$ for positive integers $a,b$ with $a \geq b$.
 Then, the $\alpha$-R\'{e}nyi divergence $D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)$ is well-defined for all states $\rho$, and the following hold:
@@
 	Since $\tau$ is in the interior of $\F$, its Wigner function obeys $W_\tau(\bmz) >0$ for all points $\bmz$ in the phase space. 
-In general, $W_\rho(\bmz)$ is a quasi-distribution, but the given form of $\alpha$ ensures that $W_{\rho}(\bmz)^\alpha \geq 0$. 
-Therefore $D_\alpha (W_\rho || W_\tau)$ is always well-defined.
-
-1. $D_\alpha$ is Schur-convex and every pair $(W_{\rho}, W_{\tau})$ majorizes $(W_{\rho'}, W_{\rho'})$, so
-\begin{align}
-	D_\alpha(W_{\rho} \hspace{1pt}||\hspace{1pt} W_{\tau}) \geq D_\alpha(W_{\rho'} \hspace{1pt}||\hspace{1pt} W_{\rho'}) &= \nonumber\\
-	\frac{1}{\alpha-1} \log \sum_{\bmz} W_{\rho'}(\bmz) &= 0.
-\end{align}
-
-2. In the inequality of property 1, equality holds iff $L_{\rho|\tau}(x) = L_{\rho'|\rho'}(x) = L_{\tau|\tau}(x)$ for all $x$ due to~\cref{prop:rmajor} which holds iff $\rho = \tau$.
+In general, $W_\rho(\bmz)$ is a quasi-distribution, but for $\alpha = 2a/2b-1$ we that $W_{\rho}(\bmz)^\alpha \geq 0$. 
+Therefore $D_\alpha (W_\rho || W_\tau)$ is always well-defined and real-valued.
+
+1. $D_\alpha$ is Schur-convex and every pair $(W_{\rho}, W_{\tau})$ majorizes the pair $(W_{\I/d}, W_{\I/d})$, so
+\begin{align}
+	D_\alpha(W_{\rho} \hspace{1pt}||\hspace{1pt} W_{\tau}) \geq D_\alpha(W_{\I/d} \hspace{1pt}||\hspace{1pt} W_{\I/d}) &= \nonumber\\
+	\frac{1}{\alpha-1} \log \sum_{\bmz} W_{\I/d}(\bmz) &= 0.
+\end{align}
+
+2. In the inequality of property 1, equality holds iff $L_{\rho|\tau}(x) = L_{\I/d|\I/d}(x) = L_{\tau|\tau}(x)$ for all $x\in [0,1]$ due to~\cref{prop:rmajor} which in turn holds iff $\rho = \tau$.
 
@@
 
-4. This follows immediately from the Schur-convexity of $D_\alpha$.
+4.
+This follows immediately from the fact that $(W_\rho, W_\tau) \succ (W_{\E(\rho)}, W_{\E(\tau)})$ for any free quantum channel $\E$ that sends $\tau$ into the interior of $\F$, and the Schur-convexity of $D_\alpha$.
 \end{proof}
@@
 \begin{theorem}
-	Consider a general magic state distillation process that converts a magic state $\rho^{\otimes n} \longrightarrow \rho'^{\otimes m}$ as well as an equilibrium state $\tau^{\otimes n} \longrightarrow \tau'^{\otimes m}$
-
-	We have the following family of upper bounds on the distillation rate $R := n'/n$,
-	\begin{equation}
-		R \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{D_{\alpha}(W_{\rho'} \hspace{1pt}||\hspace{1pt} W_{\tau'})} = \frac{F_\alpha(W_\rho) - F_\alpha(W_\tau)}{F_\alpha(W_{\rho'}) - F_\alpha(W_{\tau'})},
-	\end{equation}
-	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ and $\beta F_\alpha(W_\rho) := D_\alpha (W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) - \log \Z$ is the $\alpha$--free energy.
+	Consider a general magic state distillation process that converts a magic state $\rho^{\otimes n} \longrightarrow \E(\rho^{\otimes n})=\rho'^{\otimes m}$and let $\tau$ be any full-rank stabilizer reference state.
+Then the distillation rate $R := m/n$ is upper bounded as,
+	\begin{equation}
+		R \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{D^{\rm reg}_\alpha( \rho', \tau')},
+	\end{equation}
+	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ with the regularized divergence
+	\begin{equation}
+D^{\rm reg}_\alpha( \rho', \tau') = \frac{1}{m} D_\alpha (W_{\rho\prime_m} || W_{\tau'_m}),
+\end{equation}
+between the output magic state $\rho'^{\otimes m}$ and $\tau'_m = \E(\tau^{\otimes n})$.
 \end{theorem}
@@
 \begin{equation}	
-	D_\alpha(W_{\rho^{\otimes n}} \hspace{1pt}||\hspace{1pt} W_{\tau^{\otimes n}}) \geq D_\alpha (W_{\rho'^{\otimes m}} \hspace{1pt}||\hspace{1pt} W_{\tau'^{\otimes m}}).\vspace{10pt}
-\end{equation}
-
-We can use the additive property to rewrite this as
-\begin{equation}
-	n D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) \geq m D_\alpha(W_{\rho'} \hspace{1pt}||\hspace{1pt} W_{\tau'}).
-\end{equation}
-
-Since $\rho' \neq \tau'$, we have $D_\alpha(W_{\rho'} \hspace{1pt}||\hspace{1pt} W_{\tau'}) > 0$, which directly leads to the bound
-\begin{equation}
-	\frac{m}{n} \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{D_{\alpha}(W_{\rho'} \hspace{1pt}||\hspace{1pt} W_{\tau'})}.
-\end{equation}
-\end{proof}
-\ddd{[Add in general divergence without product form]}
+	D_\alpha(W_{\rho^{\otimes n}} \hspace{1pt}||\hspace{1pt} W_{\tau^{\otimes n}}) \geq D_\alpha (W_{\rho'^{\otimes m}} \hspace{1pt}||\hspace{1pt} W_{\tau'_m}).\vspace{10pt}
+\end{equation}
+
+We can use the additivity to rewrite this as
+\begin{equation}
+	n D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) \geq m \frac{1}{m}D_\alpha(W_{\rho'_m} \hspace{1pt}||\hspace{1pt} W_{\tau'_m}).
+\end{equation}
+
+Since $\rho'^{\otimes m} \neq \tau'_m$, we have $D_\alpha(W_{\rho'_m} \hspace{1pt}||\hspace{1pt} W_{\tau'_m}) > 0$, which directly leads to the bound
+\begin{equation}
+	\frac{m}{n} \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{D^{\rm reg}_\alpha( \rho', \tau')}.
+\end{equation}
+\end{proof}
 

### 2021-06-26 magic_paper.tex
minor changes

@@
 % Labels and Refs --- consistency, cref vs ref, thm vs lem vs prop, thm restatements, (??)
-% Notation consistency --- noise vs error, \ln{} -> \ln, \ln vs \log vs \log_2, italics & \emph, Aberg -> {\AA}berg, quasi-dist vs quasi-prob dist, def elbows, cumulant vs cumulative, stabilizer vs free, \p vs \w, W_\rho vs W_\rho(\bmz), \succ_r vs \succ
+% Notation consistency --- noise vs error, \ln{} -> \ln, \ln vs \log vs \log_2, italics & \emph, Aberg -> {\AA}berg + [110 Knig], quasi-dist vs quasi-prob dist, def elbows, cumulant vs cumulative, stabilizer vs free, \p vs \w, W_\rho vs W_\rho(\bmz), \succ_r vs \succ, Eq.49 minus
 % UK vs US english

### 2021-06-26 magic_paper.tex
fixed refs and comments. David: I left a comment in red for you to revise. Next: check consistency of text throughout and proofread

@@
 \input{preamble}
+
+% Figures
+% Refs
+% Notation
+% Proofreading --- Citations
+% Proofreading --- Main text
+% Proofreading --- Appendices
+
+% Figs check --- consistency (size, font, text size, pads, axes, cbars), captions, folder
+
 % Labels and Refs --- consistency, cref vs ref, thm vs lem vs prop, thm restatements, (??)
-% Notation consistency --- noise vs error, \ln{} -> \ln, \ln vs \log vs \log_2, italics & \emph, Aberg -> {\AA}berg + [110 Knig], quasi-dist vs quasi-prob dist, def elbows, cumulant vs cumulative, stabilizer vs free, \p vs \w, W_\rho vs W_\rho(\bmz), \succ_r vs \succ, Eq.49 minus
+
+% Notation consistency --- noise vs error, \ln{} -> \ln, \ln vs \log vs \log_2, italics & \emph, Aberg -> {\AA}berg + [110 Knig], quasi-dist vs quasi-prob dist, def elbows, cumulant vs cumulative, stabilizer vs free, \p vs \w, W_\rho vs W_\rho(\bmz), \succ_r vs \succ
 % UK vs US english
 
-% Figs check --- consistency, cbars, captions, axes, iffalse
 % Spacing --- figs, sections, paragraphs, eq. numbering, \noindent, QEDs
@@
 These frameworks for magic view magic states as resource states with respect to a natural class of quantum operations that are considered cheap, or free, such as stabilizer operations~\cite{Gour_2019, cit:ahmadi, cit:seddon, Wang_2019}.
-Beyond quantum computing, recent work has also looked at how magic can be used to analyse many-body physics~\cite{Sarkar_2020} and conformal field theories~\cite{White_2021} as well as how it is connected with contextuality~\cite{Vega_2017, cit:howard2, Zurel_2020, okay2021extremal}.
+Beyond quantum computing, recent work has also looked at how magic can be used to analyse many-body physics~\cite{Sarkar_2020} and conformal field theories~\cite{White_2021} as well as how it is connected with contextuality~\cite{Vega_2017, cit:howard2, Zurel_2020, Okay_2021}.
 
@@
 
-This means in particular that $\E(\tau^{\otimes n})$ is a symmetric state on $m$ subsystems, so by the quantum de Finetti theorem~\cite{christandl_2007} \ddd{[There is more than one seminal de Finetti paper to cite]} we have that for $m \gg 1$
+This means in particular that $\E(\tau^{\otimes n})$ is a symmetric state on $m$ subsystems, so by the quantum de Finetti theorem~\cite{hudson_locally_1976, christandl_2007} we have that for $m \gg 1$
 \begin{equation}
@@
 In Appendix \ref{app:lcst_technical}, we give bounds in which one does not include these Clifford changes of basis (see Theorem \ref{thm:no-processing}), and which have a more non-trivial dependency on the parameters.
-
-\iffalse
-\begin{figure}[t!]
-    \centering
-    \includegraphics[scale=0.4]{figs/rate_scatter.pdf}
-    \caption{\textbf{Temperature-dependent bounds for magic distillation.}
-  Shown is a contour plot of the bound on $R(\epsilon, \beta)$ for $H = H' = \sum_{k \in \mathbb{Z}_3} k |k\>\<k|$ and $\epsilon' = 0$, where $\beta$ is the inverse temperature and $\epsilon$ the depolarising error of the input magic state.
-The relevant data from the spectrum of the qutrit operator $H$ enters in via $\epsilon_\star(\beta)$ and $\beta_\star$.
-The vertical dashed line is the `Landauer-like' temperature threshold $\beta_\star$ and the diagonal dashed curve corresponds to the noise threshold $\epsilon_\star(\beta)$ for $\beta \leq \beta_\star$.
-\nick{Refer to definitions of starred quantities} The $\beta = 0$ line corresponds to the regime in which the magic protocol corresponds to a unital channel.
-    }
-    \label{fig:rate_contour}
-\end{figure}
-\fi
 
@@
 We could perform similar analysis for general qudits, and different choices of magic states, for example.
-It might also be of interest to consider other choices of reference states $\tau$ that are more appropriate to the hardware physics, for example for photonic set-ups\ddd{[cite recent PsiQ architecture paper]}.
+It might also be of interest to consider other choices of reference states $\tau$ that are more appropriate to the hardware physics, for example for photonic set-ups~\cite{bombin2021interleaving}.
 
@@
 We note that prior work has shown that negative conditional entropy~\cite{rio_thermodynamic_2011} arises in the context of quantum correlations, however this is unrelated to the present negative entropy.
+\nick{Moreover, recent work~\cite{leone2021renyi} on R\'{e}nyi entropies of magic define the entropies on proper probability distributions related to expectation values of quantum states, hence it is unrelated with the present Wigner negativity setting.}
 
@@
 Therefore, if we try to push this to the present setting, the presence of Wigner negativity would correspond to a divergence in the first derivative of an effective free energy as $T \rightarrow T_0$.
-It is interesting to speculate whether the presence of magic in Clifford circuits could admit a sensible interpretation in terms of zeroth-order phase transitions [\ddd{cite}].
+It is interesting to speculate whether the presence of magic in Clifford circuits could admit a sensible interpretation in terms of zeroth-order phase transitions~\cite{Aharonov_2000, Shiyu_2020, Ippoliti_2021}.
 
@@
 We can now apply this to obtain a family of magic distillation bounds based on R\'{e}nyi divergences.
-\begin{theorem}
+\begin{theorem}\label{thm:entropic_bounds}
 	Consider a general magic state distillation process on prime dimension qudits, that converts a magic state $\rho^{\otimes n} \longrightarrow \E(\rho^{\otimes n})=\rho'^{\otimes m}$and let $\tau$ be any full-rank stabilizer reference state on a qudit.
@@
 	\begin{equation}
-D^{\rm reg}_\alpha( \rho', \tau') = \frac{1}{m} D_\alpha (W_{\rho'^{\otimes m}} || W_{\tau'_m}),
+D^{\rm reg}_\alpha( \rho', \tau') := \frac{1}{m} D_\alpha (W_{\rho'^{\otimes m}} || W_{\tau'_m}),
 \end{equation}
@@
 The case $R_{10}$ is shown in Figure~\ref{fig:distill_bounds} and numerical evidence shows it is close to the optimal bound from majorization.
-%
-%\begin{figure}[t!]
-%    \centering
-%    \subfigure[][]{%
-%    \label{fig:Ra}%
-%    \includegraphics[scale=0.4]{figs/Ra_vs_a_eps.pdf}}\\
-%    \subfigure[][]{%
-%    \label{fig:RaDiff}%
-%    \includegraphics[scale=0.4]{figs/RaDiff_vs_a_eps.pdf}}
-%    \caption{$R_\alpha$ and $R_\alpha - R_{\infty}$ for the Strange state distillation for unital protocols
-%    \nick{Can compare thauma and mana for other magic states now more easily}}
-%    \label{fig:rate_a_contour}
-%\end{figure}
 
@@
 While this seems like a painful thing to consider, there is motivation for this beyond the aim of magic protocols: in the case of statistical mechanics on a phase space this is precisely the situation, albeit in the continuum limit.
-Statistical mechanics of actual systems obey Hamiltonian dynamics and so automatically respect a symplectic form~\cite{Pathria_1997} \nick{better ref here?}.
+Statistical mechanics of actual systems obey Hamiltonian dynamics, thus they automatically respect a symplectic form~\cite{Arnold_2000, Pathria_1997}.
 Therefore, the pre-order of statistical mechanical states with respect to phase space dynamics preserving a Gibbs state must correspond to a symplectic majorization condition.
@@
 
-We now have the following fundamental result in majorization theory. \ddd{[Add original papers to cite bit]}
-\begin{theorem}[Schur-Ostrowski theorem~\cite{cit:marshall}] Let $\D\subseteq \mathbb{R}^N$ be a convex set with non-empty interior, and invariant under permutations of vector components.
+We now have the following fundamental result in majorization theory.
+\begin{theorem}[Schur-Ostrowski theorem~\cite{Schur_1923, Ostrowski_1952, cit:marshall}] Let $\D\subseteq \mathbb{R}^N$ be a convex set with non-empty interior, and invariant under permutations of vector components.
 Let $f: \D \rightarrow \mathbb{R}$ be a continuously differentiable function on the interior of $\D$ and continuous on the whole of $\D$.
@@
 	\begin{equation}
-D^{\rm reg}_\alpha( \rho', \tau') = \frac{1}{m} D_\alpha (W_{\rho\prime_m} || W_{\tau'_m}),
+D^{\rm reg}_\alpha( \rho', \tau') := \frac{1}{m} D_\alpha (W_{\rho\prime_m} || W_{\tau'_m}),
 \end{equation}

### 2021-06-28 magic_paper.tex
red comments to be addressed

@@
     \caption{\textbf{Magic distillation bounds from majorization of Wigner quasi-distributions.} The above plot shows distillation upper bounds for qutrits obtained from majorisation on unital protocols.
-The constraints are plotted as a function of the depolarizing noise level $\epsilon$ for a noisy Strange state.
-The bound $R_\infty$ follows from a Lorenz curve analysis, while the bound $R_{10}$ comes from single-shot entropies on the Wigner quasi-distributions, as discussed in Section~\ref{section:entropies}.
+The constraints are plotted as a function of the depolarizing error $\epsilon$ for a noisy Strange state (Equation~\ref{eq:noisysn}).
+The bound $R_\infty$ follows from a Lorenz curve analysis presented in Section~\ref{sec:unital}, while the bound $R_{10}$ comes from single-shot entropies on the Wigner quasi-distributions, as discussed in Section~\ref{section:entropies}.
 Numerical bounds $R_{\rm{num}}$ are obtained by using the full set of majorization constraints.
-The new bounds $R_\infty$, $R_{10}$, $R_{\rm{num}}$ all provide stricter constraints than mana and max--thauma $\theta_{\rm{max}}$ bounds for noisy Strange states.
+The new bounds $R_\infty$, $R_{10}$, $R_{\rm{num}}$ all provide stricter constraints than mana~\cite{cit:veitch2} and max--thauma $\theta_{\rm{max}}$~\cite{Wang_2020} bounds for noisy Strange states.
     }
@@
 The physics of the protocol can be analysed by considering how it would transform some distinguished reference stabilizer state $\tau^{\otimes n}$ (bottom figure).
-For the case where this reference state is a thermal state at some temperature $T$ our magic distillation bounds are functions of $T$, the noise parameters $\epsilon, \epsilon'$, and the free energy the protocol channel $\E$ injects in.
-In addition, a quantity $\phi$ (Equation~\ref{eq:phi}) links the computational and physical aspects, and corresponds to the degree to which Wigner negativity in $\rho$ can be assigned a sharp energy via the system Hamiltonian.}
+For the case where this reference state is a thermal state at some temperature $T$ our magic distillation bounds are functions of $T$, the error parameters $\epsilon, \epsilon'$, and \nick{the free energies $F, F'$ that the protocol channel $\E$ injects in}.
+In addition, a quantity $\phi$ (Equation~\ref{eq:phi}) links the computational and physical aspects, and corresponds to the degree to which the Wigner negativity of $\rho$ can be assigned a sharp energy via the system Hamiltonian.}
     \label{fig:sketch}
@@
 In contrast, Lorenz curves for magic states break through the value of $L(x)=1$ due to the presence of negativity in the associated quasi-probability distributions.
-The above family of curves correspond to multiple copies of noisy Strange states $\rho\coloneqq\rho_{\rm{S}}(\epsilon)^{\otimes n}$ (\cref{eq:noisysn}) for $n=2,4,6$ within $\R_{\id/3}$.
+The above family of curves correspond to multiple copies of noisy Strange states $\rho\coloneqq\rho_{\rm{S}}(\epsilon)^{\otimes n}$ (Equation~\ref{eq:noisysn}) for $n=2,4,6$ within $\R_{\sigma}$, where $\sigma = \id/3$.
 Solid lines represent pure Strange states, while dashed lines represent $\epsilon$-noisy Strange states with depolarising error $\epsilon = 0.1$.
@@
     \includegraphics[scale=0.35]{figs/rate_scatter_cliff.pdf}}
-    \caption{\textbf{Temperature-dependent bounds for magic distillation.} Shown are two contour plots of the bound on $R(\epsilon, \beta)$ for the case $H = H' = \sum_{k \in \mathbb{Z}_3} k \ketbra{k}$ and $\epsilon' = 0$, where $\beta$ is the inverse temperature and $\epsilon$ is the depolarising noise of the input magic state.
+    \caption{\textbf{Temperature-dependent bounds for magic distillation.} Shown are two contour plots of the bound on $R(\epsilon, \beta)$ for the case $H = H' = \sum_{k \in \mathbb{Z}_3} k \ketbra{k}$ and $\epsilon' = 0$, where $\beta$ is the inverse temperature and $\epsilon$ is the depolarising error of the input magic state.
 The top figure \subref{fig:noCliff} does not use any changes of Clifford basis, and the form of the bound depends on both the noise parameter and temperature.
-The curved dashed line is $\epsilon_\star(\beta)$ is given by Equation \ref{eq:threshold} and $\beta_\star = (kT_\star)^{-1}$ is given by $E_2-\phi = kT_\star \ln 2$.
+The curved dashed line is $\epsilon_\star(\beta)$ and given by Equation~\ref{eq:threshold} and $\beta_\star = (kT_\star)^{-1}$ is given by $E_2-\phi = kT_\star \ln 2$.
 In the bottom figure \subref{fig:Cliff} Clifford processing is used resulting in a smoother bound. In both figures the $\beta = 0$ line correspond to the unital bounds.}
@@
     \includegraphics[scale=0.35]{figs/R_vs_A.pdf}
-    \caption{\textbf{Variation of distillation bounds with Hamiltonian.} We consider $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$, and look at a family of Hamiltonians for the qutrit systems, given by $H = A_{\bmo}$ and $H' = (1-p-q)A_{\bmo}+pA_{(1,2)}+q{\rm{diag}}(0,1,2)$.
+    \caption{\textbf{Variation of distillation bounds with Hamiltonian.} \nick{ We demonstrate non-trivial variation of our bound in Equation~\ref{eq:rate_bounds_proof} with repect to the system Hamiltonian.
+To this end, we fix $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$ and look at a family of Hamiltonians for the qutrit systems, given by $H = A_{\bmo}$ and $H' = (1-p-q)A_{\bmo}+pA_{(1,2)}+q{\rm{diag}}(0,1,2)$ for varying probabilities $p, q$.
+NEED TO DISCUSS VALUE $1.01$}
     }
@@
 \end{theorem}
+\nick{Notation $D^{\rm reg}_\alpha( \rho', \tau')$ is a little clunky.
+What are $\rho'$ and $\tau'$ ?
+Maybe at least use $D^{\rm reg}_\alpha( \rho', \tau'_m)$ as in the presence of correlations marginal state $\tau'$ is not well defined}
 The proof is given in Appendix~\ref{app:single-shot}.
@@
 
-If correlations in $\tau'_m$ between subsystems can be neglected then we simply get
+If correlations in $\tau'_m$ between subsystems can be neglected then \nick{we can write $\tau'_m = \tau'^{\otimes m}$ for some sharp marginal state $\tau'$} and the regularised divergence reduces to
 \begin{equation}
@@
 \begin{align}
-	\W[\bmz]{\tau} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z}W_{|k\>\<k|}(x, p) \nonumber\\
-	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z} \delta_{x, k} = \frac{e^{-\beta E_x}}{3\Z},
+	\W[\bmz]{\tau} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z}W_{|k\>\<k|}(q, p) \nonumber\\
+	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z} \delta_{q, k} = \frac{e^{-\beta E_x}}{3\Z},
 \end{align}
@@
     \centering
-    \includegraphics[scale=0.3]{figs/H_vs_eps_a.pdf}
-    \caption{The R\'{e}nyi entropy $H_\alpha$ is increasing in $\alpha$ and $\epsilon$.
-First dashed contour from the right corresponds to $H_\alpha(\rho_{\rm{S}}(\epsilon)) = 0$.
-Specifically, $H_\alpha(\rho_{\rm{S}}(0)) = 0$ that implies $6^\alpha - 2^{\alpha} = 8$, with the approximate solution $\alpha \approx 1.31$.
+    \includegraphics[scale=0.35]{figs/H_vs_eps_a.pdf}
+    \caption{\textbf{R\'{e}nyi entropy $H_\alpha$ of $\epsilon$-noisy Strange state.} \nick{$H_\alpha$ is increasing in $\alpha$ and $\epsilon$.
+The first dashed contour from the right corresponds to $H_\alpha(\rho_{\rm{S}}(\epsilon)) = 0$.
+In particular, $H_\alpha(\rho_{\rm{S}}(0)) = 0$ corresponds to $\alpha \approx 1.31$.}
     }

### 2021-06-28 magic_paper.tex
Red bits addressed.

@@
 Such distillation rates have been improved in more recent works~\cite{Jones_2013, haah2017magic, Hastings2018, Litinski_2019} and protocols for qudits of odd dimension have also been proposed~\cite{CampbellAnwar_2012, Anwar_2012, Dawkins_2015, Krishna2019, cit:prakash}.
-There is also analysis of magic protocols from the perspective of magic monotones, which provide upper bounds on distillation rates and find application in the analysis of gate synthesis~\cite{Campbell_2017, Howard_2017, Prakash_2018, Seddon_2021}.
+There is also analysis of magic protocols from the perspective of magic monotones, which provide upper bounds on distillation rates and find application in the analysis of gate synthesis~\cite{Campbell_2017, Howard_2017, Prakash_2018, Seddon_2021,leone2021renyi}.
 These frameworks for magic view magic states as resource states with respect to a natural class of quantum operations that are considered cheap, or free, such as stabilizer operations~\cite{Gour_2019, cit:ahmadi, cit:seddon, Wang_2019}.
@@
 The physics of the protocol can be analysed by considering how it would transform some distinguished reference stabilizer state $\tau^{\otimes n}$ (bottom figure).
-For the case where this reference state is a thermal state at some temperature $T$ our magic distillation bounds are functions of $T$, the error parameters $\epsilon, \epsilon'$, and \nick{the free energies $F, F'$ that the protocol channel $\E$ injects in}.
-In addition, a quantity $\phi$ (Equation~\ref{eq:phi}) links the computational and physical aspects, and corresponds to the degree to which the Wigner negativity of $\rho$ can be assigned a sharp energy via the system Hamiltonian.}
+For the case where this reference state is a thermal state at some temperature $T$ our magic distillation bounds are functions of $T$, the noise parameters $\epsilon, \epsilon'$, and free energies $F, F'$.
+In addition, a quantity $\phi$ (Equation~\ref{eq:phi}) relates the computational and energy bases, and corresponds to the degree to which the Wigner negativity of $\rho$ can be given a sharp energy via the system Hamiltonian.}
     \label{fig:sketch}
@@
     \includegraphics[scale=0.35]{figs/R_vs_A.pdf}
-    \caption{\textbf{Variation of distillation bounds with Hamiltonian.} \nick{ We demonstrate non-trivial variation of our bound in Equation~\ref{eq:rate_bounds_proof} with repect to the system Hamiltonian.
-To this end, we fix $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$ and look at a family of Hamiltonians for the qutrit systems, given by $H = A_{\bmo}$ and $H' = (1-p-q)A_{\bmo}+pA_{(1,2)}+q{\rm{diag}}(0,1,2)$ for varying probabilities $p, q$.
-NEED TO DISCUSS VALUE $1.01$}
+    \caption{\textbf{Variation of distillation bounds with Hamiltonian.}  We illustrate variation of the bound in Equation~\ref{eq:rate_bounds_proof} with respect to the system Hamiltonian.
+We fix $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$ and look at a family of Hamiltonians for the qutrit systems, given by $H = A_{\bmo}$ and $H' = (1-p-q)A_{\bmo}+pA_{(1,2)}+q{\rm{diag}}(0,1,2)$ for varying probabilities $p, q$.
     }
@@
 We note that prior work has shown that negative conditional entropy~\cite{rio_thermodynamic_2011} arises in the context of quantum correlations, however this is unrelated to the present negative entropy.
-\nick{Moreover, recent work~\cite{leone2021renyi} on R\'{e}nyi entropies of magic define the entropies on proper probability distributions related to expectation values of quantum states, hence it is unrelated with the present Wigner negativity setting.}
 
@@
 	\begin{equation}
-		R \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{D^{\rm reg}_\alpha( \rho', \tau')},
-	\end{equation}
-	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ and with the regularized divergence
-	\begin{equation}
-D^{\rm reg}_\alpha( \rho', \tau') := \frac{1}{m} D_\alpha (W_{\rho'^{\otimes m}} || W_{\tau'_m}),
+		R \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{\tilde{D}_\alpha( \rho', \tau')},
+	\end{equation}
+	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ and the average divergence
+	\begin{equation}
+\tilde{D}_\alpha( \rho', \tau') := \frac{1}{m} D_\alpha (W_{\rho'^{\otimes m}} || W_{\tau'_m}),
 \end{equation}
@@
 \end{theorem}
-\nick{Notation $D^{\rm reg}_\alpha( \rho', \tau')$ is a little clunky.
-What are $\rho'$ and $\tau'$ ?
-Maybe at least use $D^{\rm reg}_\alpha( \rho', \tau'_m)$ as in the presence of correlations marginal state $\tau'$ is not well defined}
 The proof is given in Appendix~\ref{app:single-shot}.
 
-While this bound is abstract in its present form, it does suggest future applications by viewing $D^{\rm reg}_\alpha( \rho', \tau')$ within the context of hypothesis testing, as a measure of distinguishability between $\rho'^{\otimes m}$ and the $m$ qudit state $\tau'_m$.
+While this bound is abstract in its present form, it does suggest future applications by viewing $\tilde{D}_\alpha( \rho', \tau')$ within the context of hypothesis testing, as a measure of distinguishability between $\rho'^{\otimes m}$ and the $m$ qudit state $\tau'_m$.
 However in order to properly link with hypothesis-testing one would have to first extend such results to quasi-distributions.
 
-If correlations in $\tau'_m$ between subsystems can be neglected then \nick{we can write $\tau'_m = \tau'^{\otimes m}$ for some sharp marginal state $\tau'$} and the regularised divergence reduces to
-\begin{equation}
-D^{\rm reg}_\alpha( \rho', \tau') = D_\alpha (W_{\rho'} || W_{\tau'}),
+If correlations in $\tau'_m$ between subsystems can be neglected then $\tau'_m = \tau'^{\otimes m}$ for some qudit state $\tau'$ we have that
+\begin{equation}
+\tilde{D}_\alpha( \rho', \tau') = D_\alpha (W_{\rho'} || W_{\tau'}),
 \end{equation}
@@
     \includegraphics[scale=0.35]{figs/H_vs_eps_a.pdf}
-    \caption{\textbf{R\'{e}nyi entropy $H_\alpha$ of $\epsilon$-noisy Strange state.} \nick{$H_\alpha$ is increasing in $\alpha$ and $\epsilon$.
+    \caption{\textbf{R\'{e}nyi entropy $H_\alpha$ of $\epsilon$-noisy Strange state.} $H_\alpha$ is increasing in $\alpha$ and $\epsilon$.
 The first dashed contour from the right corresponds to $H_\alpha(\rho_{\rm{S}}(\epsilon)) = 0$.
-In particular, $H_\alpha(\rho_{\rm{S}}(0)) = 0$ corresponds to $\alpha \approx 1.31$.}
+In particular, $H_\alpha(\rho_{\rm{S}}(0)) = 0$ corresponds to $\alpha \approx 1.31$.
     }
@@
 	\begin{equation}
-		R \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{D^{\rm reg}_\alpha( \rho', \tau')},
-	\end{equation}
-	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ with the regularized divergence
-	\begin{equation}
-D^{\rm reg}_\alpha( \rho', \tau') := \frac{1}{m} D_\alpha (W_{\rho\prime_m} || W_{\tau'_m}),
+		R \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{\tilde{D}_\alpha( \rho', \tau')},
+	\end{equation}
+	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ with the average divergence
+	\begin{equation}
+\tilde{D}_\alpha( \rho', \tau') := \frac{1}{m} D_\alpha (W_{\rho\prime_m} || W_{\tau'_m}),
 \end{equation}
@@
 \begin{equation}
-	\frac{m}{n} \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{D^{\rm reg}_\alpha( \rho', \tau')}.
+	\frac{m}{n} \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{\tilde{D}_\alpha( \rho', \tau')}.
 \end{equation}

### 2021-06-28 magic_paper.tex
Potentially my final edits. Refs to be added.

@@
 
-\title{General constraints on magic state protocols from the statistical mechanics of \\Wigner negativity}
+\title{Constraints on magic state protocols from the statistical mechanics of \\Wigner negativity}
 
@@
 These frameworks for magic view magic states as resource states with respect to a natural class of quantum operations that are considered cheap, or free, such as stabilizer operations~\cite{Gour_2019, cit:ahmadi, cit:seddon, Wang_2019}.
-Beyond quantum computing, recent work has also looked at how magic can be used to analyse many-body physics~\cite{Sarkar_2020} and conformal field theories~\cite{White_2021} as well as how it is connected with contextuality~\cite{Vega_2017, cit:howard2, Zurel_2020, Okay_2021}.
-
-Recent work towards fault-tolerance is increasingly bridging the gap between abstract theory and experiment.
-Extensive work has been done on error mitigation~\cite{jones_2012, Li_2017, Temme_2017, Endo_2018, McClean_2017}, and the incorporation of hardware physics into the theoretical modes~\cite{Kandala_2019, holmes_resource_2019, Colless_2018, song2018quantum, Bravyi_2021}.
+Beyond quantum computing, recent work has also looked at how magic can be used to analyse many-body physics~\cite{Sarkar_2020} and conformal field theories~\cite{White_2021} as well its connection to contextuality~\cite{Vega_2017, cit:howard2, Zurel_2020, Okay_2021}.
+
+Work towards fault-tolerance is increasingly bridging the gap between abstract theory and experiment.
+Extensive work is being done on error mitigation~\cite{jones_2012, Li_2017, Temme_2017, Endo_2018, McClean_2017}, and the incorporation of hardware physics into the theoretical models~\cite{Kandala_2019, holmes_resource_2019, Colless_2018, song2018quantum, Bravyi_2021}.
 For example, the XZZX code~\cite{bonilla_ataides_xzzx_2021} is a variant of the surface code that incorporates noise bias explicitly and has been shown to attain the hashing bound of random codes~\cite{Bennett_1996}.
@@
 The magic distillation bounds can then be expressed in terms of the physics of the reference state (e.g.~free energy changes in the case of temperature).
-Such bounds are therefore of interest in assessing how physical features such as temperature, noise-biases or fixed-point structure associated with restricted gate-sets constrain distillation protocols~\cite{Tuckett_2019, Aliferis_2008, Stephens_2013, Li_2015, Babbush_2018, Guillaud_2019, Fowler_2019}.
+Such bounds are of potential interest in assessing how physical features such as temperature, noise-biases or fixed-point structure associated with restricted gate-sets constrain distillation protocols~\cite{Tuckett_2019, Aliferis_2008, Stephens_2013, Li_2015, Babbush_2018, Guillaud_2019, Fowler_2019}.
 
@@
 We circumvent this obstacle by making use of a more fundamental tool -- majorization theory~\cite{cit:marshall, Veinott_1971, Ruch_1976}.
-To our knowledge majorization of quasi-distributions has not been considered in quantum physics before, and therefore our analysis is also of relevance to other studies of non-classicality in quantum systems~\cite{Fine_1982, Allahverdyan_2018, arvidsson_2020, halpern_2018, Lostaglio_2018, Levy_2020}.
+To our knowledge majorization of quasi-distributions has not been considered in quantum physics before, and therefore these methods could find application in other studies of non-classicality in quantum systems~\cite{Fine_1982, Allahverdyan_2018, arvidsson_2020, halpern_2018, Lostaglio_2018, Levy_2020}.
 
@@
 
-We find that the analysis in the presence of negativity is non-trivial, displays a range of features that do not appear in classical statistical mechanics, and leads to a picture of Wigner negativity in a quantum circuit being described as non-classical free energy that is processed under stochastic dynamics.
-This is demonstrated by Lorenz curves having a non-trivial maximum that is related to the mana of a state (Section~\ref{sec:lc}), and by showing that single-shot entropies for general Wigner quasi-distributions are well-defined, obey data-processing under stabilizer operations and can take on negative values (Section~\ref{section:entropies}).
+We find that the analysis in the presence of negativity displays a range of features that do not appear in classical statistical mechanics, and leads to a picture of Wigner negativity in a quantum circuit being described as non-classical free energy that is processed under stochastic dynamics.
+This is demonstrated by non-monotonic Lorenz curves (Section~\ref{sec:lc}), and by single-shot entropies for general Wigner quasi-distributions that are well-defined, obey data-processing under stabilizer operations and can take on negative values (Section~\ref{section:entropies}).
 
@@
 
-We show that the mana of a quantum state also arises as a residue in the $\alpha$--parameter for R\'{e}nyi entropies, and gives the rate of divergence to $-\infty$ as we approach the Shannon entropy of a Wigner distribution (Equation (\ref{eq:mana-divergence})).
-Finally, in Section~\ref{sec:lower_bounds} we discuss how our approach could be extended and how it can be exploited to construct explicit lower bounds on distillation that take into account physical constraints.
+We show that the mana of a quantum state arises as a residue in the $\alpha$--parameter for R\'{e}nyi entropies, and gives the rate of divergence to $-\infty$ as we approach the Shannon entropy of a Wigner distribution (Equation (\ref{eq:mana-divergence})).
+Finally, in Section~\ref{sec:lower_bounds} we discuss how our approach could be extended to construct explicit lower bounds on distillation that take into account physical constraints.
 
@@
 to denote the phase space point for the composite system. 
-For simplicity going forward, we assume $n$ copies of a $d$--dimensional system $d_1=d_2 = \cdots = d$, and therefore we have that $\bmz \in \mathbb{Z}_d^{2n}$.
+For simplicity, we assume $n$ copies of a $d$--dimensional system $d_1=d_2 = \cdots = d$, and therefore we have that $\bmz \in \mathbb{Z}_d^{2n}$.
 
@@
 The Clifford group $ \cal{C}_d^n $ is then defined as the set of unitaries that normalise the Heisenberg-Weyl group~\cite{Appleby_2005}.
-We may define the pure stabiliser states as those states obtained by acting on $|0\>$ with Clifford unitaries~\cite{cit:gross3} and, finally, the full set of stabilizer states as the convex hull of all pure stabilisers, namely all probabilistic mixtures of states of the form $U|0\>\<0|U^\dagger$ where $U$ is Clifford.
+We may define the pure stabilizer states as those states obtained by acting on $|0\>$ with Clifford unitaries~\cite{cit:gross3} and, finally, the full set of stabilizer states as the convex hull of all pure stabilizers, namely all probabilistic mixtures of states of the form $U|0\>\<0|U^\dagger$ where $U$ is Clifford.
 
@@
 \end{equation}
-where $\eta(\bmz, \bmz)$ is the symplectic inner product between any two points $\bmz,\z \in \P_d$, and is given explicitly by
+where $\eta(\bmz, \y)$ is the symplectic inner product between any two points $\bmz,\y \in \P_d$, and is given explicitly by
 \begin{equation}
@@
 The phase-point operators form an orthogonal operator basis with respect to the Hilbert-Schmidt inner product, as discussed in~\cref{app:wigner}.
-Therefore, any quantum state $\rho \in \cal{B}(\cal{H}_d)$ can be expressed as a linear combination of them, $\rho = \sum_{\bmz \in \cal{P}_d} \W[\bmz]{\rho} A_{\bmz}$, where the coefficient vector $\W{\rho}$ is the Wigner distribution of state $\rho$,
+Therefore, any quantum state $\rho$ can be expressed as a linear combination of them, $\rho = \sum_{\bmz \in \cal{P}_d} \W[\bmz]{\rho} A_{\bmz}$, where the coefficients $\W{\rho}(\z)$ give the Wigner distribution of state $\rho$,
 \begin{equation}\label{eq:wstate}
@@
 \end{figure}
-A number of magic theories exist, where magic states are computational resource states with respect to a natural class of quantum operations that are considered free~\cite{Gour_2019}.
-One very natural class of free operations are those obtained from Clifford unitaries, Pauli measurements and the ability to discard quantum systems.
+A number of magic theories exist, where magic states are computational resource states with respect to a class of quantum operations that are considered free~\cite{Gour_2019}.
+One natural class of free operations are those obtained from Clifford unitaries, Pauli measurements and the ability to discard quantum systems.
 However, there are also other candidates~\cite{cit:ahmadi, cit:seddon, Wang_2019}.
@@
 The central idea is to apply majorization theory to the quasi-probability distributions that arise for magic states.
-We begin in the next section by explaining how majorization relates to the free operations in a theory of magic.
+In the next section we explain how majorization relates to the free operations in a theory of magic.
 
@@
 Our focus is on states with negativity, so the particular choice of free states is not critical for our analysis.
-The remaining component that defines any magic theory is the set of allowed quantum operations, i.e.
-the ones that are considered free within the theory.
-The most basic assumption we require on free operations is that they send any free state to another free state, meaning that a resource state cannot be created freely.
+The remaining component that defines any magic theory is the set of free quantum operations.
+The most basic assumption we require on free operations is that they send any free state to another free state.
 
@@
 \end{equation}
-for any $\E$ and $\rho$.
+for any $\rho$.
 Since the magic protocol sends free states to free states, $\E$ sends all positively represented quantum state to other positively represented quantum states.
@@
 Given two distributions $\p= (p_1, \dots, p_n)$ and $\q = (q_1, \dots, q_n)$ over $n$ outcomes, we say that $\p$ majorises $\q$, denoted $\p \succ \q$, if there exists a bistochastic map $A = (A_{ij})$ such that $A\p = \q$, where bistochastic means that $A_{ij} \geq 0$ and $\sum_i A_{ij} = \sum_j A_{ij} = 1$.
-A well-known result~\cite{cit:marshall} tells us that the condition $ \p \succ \q$ over probability distributions is equivalent to $n-1$ inequalities, which can be checked efficiently.
+It can be shown~\cite{cit:marshall} that the condition $ \p \succ \q$ over probability distributions is equivalent to $n-1$ inequalities, which can be checked efficiently.
 
@@
 For a fixed probability distribution $\r = (r_1, \dots, r_n)$ with positive components, we define majorization relative to $\r$ as $\p \succ_{\r} \q$, if and only if there exists a stochastic map $A$ such that $A\r = \r$ and $A \p = \q$.
-In order words, this majorization pre-order coincides with the image of $\p$ under stochastic maps that have $\r$ as a fixed point.
-It is readily checked that the original majorization condition between probability distributions corresponds to the case $\r = (1/n, \dots, 1/n)$.
-The pre-order that results from $\bmd$-majorization is also easily computed and again corresponds to checking a small number of inequalities.
+The original majorization condition between probability distributions corresponds to the case $\r = (1/n, \dots, 1/n)$.
 
@@
 
-With this theory in place, we now turn to magic distillation protocols.
+With this theory in place, we turn to magic distillation protocols.
 
@@
 
-We can now consider how physical constraints affect magic distillation rates starting in this section with an abstract setting based on the fixed-point structure of the physical operations accessible to us.
+We can now consider how majorization constrains magic distillation rates starting in this section with an abstract setting based on the fixed-point structure of the physical operations accessible to us.
 We show that any magic theory can always be decomposed in terms of `sub-theories' with a particular fixed-point structure.
@@
 The above set of sub-theories can therefore be viewed as a complete set of ``co-measures'' for the theory, where the parent resource theory's complex pre-order of states is mapped to a simpler pre-order for a particular $\R_\sigma$.
-In the next section we show that a given $\R_\sigma$ can be approximated by a majorization pre-order, and from this we can compute magic distillation bounds.
+In the next section we show that a given $\R_\sigma$ can be approximated by a majorization pre-order, and from this we compute magic distillation bounds.
 
@@
 \label{sec:major_frag}
-We now look at how fixed-points give constraints on magic protocols.
 We consider some $\sigma \in \F$, and its corresponding $\R_\sigma$.
@@
 For $n$ copies of a qudit system of dimension $d$ the number of terms in $W_{\rho}$ is $d^{2n}$, so imposing the Lorenz curve condition corresponds to \emph{exponentially} many constraints.
-However,  before computing explicit examples, in the next section we describe how these majorization constraints relate to other known monotones.
+Before computing explicit examples, in the next section we describe how these majorization constraints relate to other known monotones.
 
@@
 We state some generic aspects of Lorenz curves for magic states, which allow us to interpret previous magic monotones in a new light.
-The first result gives an extremely simple way to see that the sum-negativity/mana of a magic state is a monotone~\cite{cit:veitch2}.
+The first result gives a simple way to see that the sum-negativity/mana of a magic state is a monotone~\cite{cit:veitch2}.
 
@@
 Therefore its monotonicity depends on the physics of the fixed point and provides a means to analyse magic distillation only under free operations that leave $\sigma$ invariant.
-One can also define an area monotone in the more general setting of relative majorization, where one drops the fixed point emphasis as in Section \ref{sec:stab}, but we do not explore this here.
+One can also define an area monotone in the more general setting of relative majorization, where one drops the fixed point emphasis as in Section \ref{sec:stab}.
 
@@
 
-We now construct magic state distillation bounds for protocols that generate \emph{unital} channels, meaning that $\E(\I/d) = \I/d$, and includes for example all protocols built from Weyl-covariant channels~\cite{cit:gross3}.
+We now construct magic state distillation bounds for protocols that generate \emph{unital} channels, meaning that $\E(\I/d) = \I/d$.
 
@@
 where $\epsilon$ is the depolarizing error parameter.
-One nice feature of this is that any magic state $\rho$ can be processed via Clifford operations~\cite{cit:prakash,cit:prakash2} and put into this canonical form for some $\epsilon \ge 0$.
+Any magic state $\rho$ can be processed via Clifford operations~\cite{cit:prakash,cit:prakash2} and put into this canonical form for some $\epsilon \ge 0$.
 
@@
 
-The coordinates of the first point after the origin for $\rho_S(\epsilon)^{\otimes n}$ are given by $(1/9^n, v(\epsilon)^n)$, while for $\rho_S(\epsilon')^{\otimes n'}$ by $(1/9^{n'}, v(\epsilon')^{n'})$, and by considering the slope of the line segment joining this point to the origin we can use~\cref{prop:first_elb} in the Appendices, to bound $R(\epsilon, \epsilon')$.
+The coordinates of the first point after the origin for $\rho_S(\epsilon)^{\otimes n}$ are given by $(1/9^n, v(\epsilon)^n)$, while for $\rho_S(\epsilon')^{\otimes n'}$ by $(1/9^{n'}, v(\epsilon')^{n'})$, and by considering the slope of the line segment joining this point to the origin we can use~\cref{prop:first_elb} in the appendices, to bound $R(\epsilon, \epsilon')$.
 We find that
@@
 
-We now show how relative majorization can incorporate physics into magic distillation bounds.
+We now show how relative majorization can incorporate the system's Hamiltonian into magic distillation bounds.
 The way we do this is by considering how the protocol would disturb a reference equilibrium state $\tau$ to some different state $\tau'$, if the protocol had been applied to this reference state instead of the actual $n$-copy magic state.
@@
 Thus, we can assume that $\E$ always outputs a symmetric state in general.
-
-This means in particular that $\E(\tau^{\otimes n})$ is a symmetric state on $m$ subsystems, so by the quantum de Finetti theorem~\cite{hudson_locally_1976, christandl_2007} we have that for $m \gg 1$
+This means that $\E(\tau^{\otimes n})$ is a symmetric state on $m$ subsystems, so by the quantum de Finetti theorem~\cite{hudson_locally_1976, christandl_2007} we have that for $m \gg 1$
 \begin{equation}
@@
 This implies that $d\mu(x)$ is peaked on a particular state $\tau'$, and $\E(\tau^{\otimes n}) \approx \tau'^{\otimes m}$.
-This occurs in the context of traditional thermodynamics, and states that the output system is well-described by intrinsic variables that do not scale in $m$, and correlations are sub-linear in $m$.
+This scenario occurs in the context of traditional thermodynamics, and states that the output system is well-described by intrinsic variables that do not scale in $m$, and correlations are sub-linear in $m$.
 In particular, this allows us to compute a free energy per qudit of the output state.
 
-The case of non-trivial correlations in the thermodynamic limit can also be considered, but leads to a more complex analysis within our majorization framework of Wigner distributions.
+Non-trivial correlations in the thermodynamic limit can also be considered, but leads to a more complex analysis within our majorization framework of Wigner distributions.
 In this direction, we highlight recent work in majorization in which stochastic independence and correlations are analysed.
-In particular, it has been shown~\cite{muller_2015} that stochastic independence (no correlations) of independent distributions can be viewed as a resource in an extension of catalytic majorization, and leads to a single-shot operational interpretation of the Shannon entropy~\cite{muller_2016, muller_2019}.
+It has been shown~\cite{muller_2015} that stochastic independence (no correlations) of independent distributions can be viewed as a resource in an extension of catalytic majorization, and leads to a single-shot operational interpretation of the Shannon entropy~\cite{muller_2016, muller_2019}.
 
@@
 
-The magic state transformation is now considered by how it transforms the pair of quantum states $(\rho^{\otimes n}, \tau^{\otimes n})$.
-This transformation is then constrained by the relative majorization condition $(W_{\rho}, W_\tau) \succ (W_{\rho'}, W_{\tau'})$ that holds due to the protocol being a stochastic map in the Wigner representation.
+The magic state protocol is now considered by how it transforms the pair of quantum states $(\rho^{\otimes n}, \tau^{\otimes n})$ and is then constrained by the relative majorization condition $(W_{\rho}, W_\tau) \succ (W_{\rho'}, W_{\tau'})$ that holds due to the protocol being a stochastic map in the Wigner representation.
 
@@
 \end{theorem}
-\noindent The proof of this is provided in~\cref{thm:free-energy-bound-proof}, and follows a similar line as taken for our unital protocol bound.
+\noindent The proof of this is provided in~\cref{thm:free-energy-bound-proof}, and follows a similar line to the unital protocol bound.
 
@@
 We have considered Wigner distributions of magic states within a statistical mechanical setting in which it was argued that magic can be viewed as a non-classical form of free energy.
-This identification with free energy was done at the level of majorization constraints that appear due to stabilizer operations being described by stochastic maps in the Wigner representation.
+This was done at the level of majorization constraints that appear due to stabilizer operations being described by stochastic maps in the Wigner representation.
 In this representation, non-equilibrium states with substantial free energy have Lorenz curves that deviate noticeably from the line $y=x$.
@@
 \begin{theorem}\label{thm:HSchur} 
-	If $\alpha = \frac{2a}{2b-1}$ for positive integers $a,b$ with $a \geq b$, then $H_\alpha(\w)$ is well-defined on the set of quasi-distributions, and moreover if $\w \succ \w'$ for two quasi-distributions $\w, \w'$ then $H_\alpha (\w) \leq H_\alpha(\w')$.
+	If $\alpha = \frac{2a}{2b-1}$ for positive integers $a,b$ with $a \geq b$, then $H_\alpha(\w)$ is well-defined on the set of quasi-distributions, and if $\w \succ \w'$ for two quasi-distributions $\w, \w'$ then $H_\alpha (\w) \leq H_\alpha(\w')$.
 \end{theorem}
@@
 with $\epsilon \rightarrow 0^+$ through a sequence of rational values.
-We now recall that mana can be written as $\M(\rho) = \log \sum_{\bmz} |W_\rho(\bmz)|$, and so we obtain a second new description of mana:
+We recall that mana can be written as $\M(\rho) = \log \sum_{\bmz} |W_\rho(\bmz)|$, and so we obtain a second new perspective on mana:
 \begin{equation}\label{eq:mana-divergence}
@@
 \end{equation}
-Therefore, the mana of a state $\rho$ is the residue of a pole in $H_\alpha(W_\rho)$, and quantifies \emph{the divergence of the R\'{e}nyi-entropy} as we approach the limiting Shannon entropy $H(W_\rho)$.
+Therefore, the mana of a state $\rho$ is the residue of a pole in $H_\alpha(W_\rho)$, and quantifies the divergence of the R\'{e}nyi-entropy as we approach the limiting Shannon entropy $H(W_\rho)$.
 
@@
 Therefore, if we try to push this to the present setting, the presence of Wigner negativity would correspond to a divergence in the first derivative of an effective free energy as $T \rightarrow T_0$.
-It is interesting to speculate whether the presence of magic in Clifford circuits could admit a sensible interpretation in terms of zeroth-order phase transitions~\cite{Aharonov_2000, Shiyu_2020, Ippoliti_2021}.
+It is interesting to speculate whether this non-classicality could be interpreted in terms of a phase transition \ddd{[CITE BOOK]}.
 
@@
 Our bounds exploited relatively simple aspects of the Lorenz curves of the quasi-distributions, so it would be of interest to sharpen these bounds and obtain a better handle on the Lorenz curve structure in the $n\rightarrow \infty$ limit.
-It would also be of interest to analyse what features of single-shot entropies can be extended to quasi-distributions in a sensible form [\ddd{cite}].
+It would also be of interest to analyse what features of single-shot entropies can be extended to quasi-distributions in a sensible form [\ddd{CITE RENNER+TOMAMICHEL}].
 This raises interesting questions as we no longer have a notion of typicality and the central limit theorem does not apply.
@@
 Physically, this regime would correspond to a form of thermo-majorization obtained from looking at the action of the Clifford group at a micro-canonical level, and then reducing to a small subsystem~\cite{Pathria_1997}.
-While this seems like a painful thing to consider, there is motivation for this beyond the aim of magic protocols: in the case of statistical mechanics on a phase space this is precisely the situation, albeit in the continuum limit.
+While this seems like a painful thing to consider, there is motivation for this beyond the aim of magic protocols: in the case of classical statistical mechanics on a phase space this is precisely the situation, albeit in the continuum limit.
 Statistical mechanics of actual systems obey Hamiltonian dynamics, thus they automatically respect a symplectic form~\cite{Arnold_2000, Pathria_1997}.
@@
 Therefore, the largest rescaled component occurs when $i_{\bmz_{\star}} = n$ and $i_{\bmz} = 0$ for $\bmz \neq \bmz_\star$ and is equal to $(v/W_{\tau}(\bmz_\star))^n$.
-Accordingly, the coordinates of the first Lorenz curve point after the origin are given by
+The coordinates of the first Lorenz curve point after the origin are given by
 \begin{equation}
@@
 \end{equation}
-where the eigenstates $\{\ket{\varphi_k}\<\varphi_k|\}$ are pure, orthonormal stabiliser states, which can be represented in terms of generalized Paulis.
+where the eigenstates $\{\ket{\varphi_k}\<\varphi_k|\}$ are pure, orthonormal stabilizer states, which can be represented in terms of generalized Paulis.
 We are free to redefine the computational basis so it coincides with the basis of $H$.
@@
 \end{equation}
+We note that previous work \ddd{[CITE Phys.
+Rev E 62, 4665 (2000)]} has considered the $\alpha=2$ entropy of Wigner distributions, and other work exists that uses the Wehrl entropy, based on the Hussimi function of a quantum state \ddd{[CITE Gnutzmann \& Zyczkowski: R\'{e}nyi-Wehrl entropies as measures of localization in phase space, J.
+Phys.
+A 34 10123]}.
 

### 2021-06-28 magic_paper.tex
midway through refs

--- 2021-06-28 magic_paper.tex
@@
 
-% Figures
+% Aberg -> {\AA}berg
 % Refs
@@
 
-% Figs check --- consistency (size, font, text size, pads, axes, cbars), captions, folder
+%X Figs check --- consistency (size, font, text size, pads, axes, cbars), captions, folder
 
@@
 
-% Notation consistency --- noise vs error, \ln{} -> \ln, \ln vs \log vs \log_2, italics & \emph, Aberg -> {\AA}berg + [110 Knig], quasi-dist vs quasi-prob dist, def elbows, cumulant vs cumulative, stabilizer vs free, \p vs \w, W_\rho vs W_\rho(\bmz), \succ_r vs \succ
+% Notation consistency --- noise vs error, \ln{} -> \ln, \ln vs \log vs \log_2, italics & \emph, quasi-dist vs quasi-prob dist, def elbows, cumulant vs cumulative, stabilizer vs free, \p vs \w, W_\rho vs W_\rho(\bmz), \succ_r vs \succ
 % UK vs US english
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \subsection{Stochastic representation of magic protocols}
@@
 
-This means in particular that $\E(\tau^{\otimes n})$ is a symmetric state on $m$ subsystems, so by the quantum de Finetti theorem~\cite{hudson_locally_1976, christandl_2007} we have that for $m \gg 1$
+This means in particular that $\E(\tau^{\otimes n})$ is a symmetric state on $m$ subsystems, so by the quantum de Finetti theorem~\cite{hudson_locally_1976, christandl_2007, renner_phd} we have that for $m \gg 1$
 \begin{equation}
@@
 
-%
-%\begin{figure}
-%    \centering
-%    \includegraphics[scale=0.4]{figs/test/R_vs_E1.pdf}
-%    \caption{Here, $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$, $H = \rm{diag}(0,E,10)$ and $H' = \rm{diag}(0,E',10)$.
-%    }
-%    \label{fig:rvse1}
-%\end{figure}
-
-%\begin{figure}
-%    \centering
-%    \includegraphics[scale=0.4]{figs/test/R_vs_E2.pdf}
-%    \caption{Here, $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$, $H = \rm{diag}(0,5,E)$ and $H' = \rm{diag}(0,5,E')$.
-%    }
-%    \label{fig:rvse2}
-%\end{figure}
-
-%\begin{figure}
-%    \centering
-%    \includegraphics[scale=0.4]{figs/test/R_vs_H.pdf}
-%    \caption{Here, $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$, $H = {\rm{diag}}(0,1,2)$ and $H' = (1-p-q){\rm{diag}}(0,1,2)+p{\rm{diag}}(1,2,0)+q{\rm{diag}}(2,0,1)$.
-%    }
-%    \label{fig:rvsh}
-%\end{figure}
-
 \begin{figure}
@@
 
-However, it turns out that the analysis for the temperature-dependent bound given by Equation (\ref{eq:rate_bounds_proof}) implicitly made use of the single-shot R\'{e}nyi divergence $D_\infty (\p \hspace{1pt}||\hspace{1pt} \r)$, which is given by
+However, it turns out that the analysis for the temperature-dependent bound given by Equation (\ref{eq:rate_bounds_proof}) implicitly made use of the single-shot R\'{e}nyi divergence~\cite{renyi_1960} $D_\infty (\p \hspace{1pt}||\hspace{1pt} \r)$, which is given by
 \begin{equation}
@@
 We can go further, and show that in fact a range of R\'{e}nyi entropies remain both well-defined and meaningful in the Wigner representation.
-The $\alpha$--R\'{e}nyi entropy $H_\alpha(\p)$ is defined as
+The $\alpha$--R\'{e}nyi entropy $H_\alpha(\p)$ is defined as~\cite{renyi_1960}
 \begin{equation}
@@
 Therefore, if we try to push this to the present setting, the presence of Wigner negativity would correspond to a divergence in the first derivative of an effective free energy as $T \rightarrow T_0$.
-It is interesting to speculate whether the presence of magic in Clifford circuits could admit a sensible interpretation in terms of zeroth-order phase transitions~\cite{Aharonov_2000, Shiyu_2020, Ippoliti_2021}.
+It is interesting to speculate whether the presence of magic in Clifford circuits could admit a sensible interpretation in terms of phase transitions~\cite{domb2000phase}.
 
 \subsection{R\'{e}nyi divergences and general distillation bounds}
-Every entropy can be obtained from a relative entropy~\cite{Gour_2020} and so we now state the extensions for R\'{e}nyi divergences of Wigner distributions.
+Every entropy can be obtained from a relative entropy~\cite{Gour_2020} so we now state the extensions for R\'{e}nyi divergences of Wigner distributions.
 The $\alpha$--R\'{e}nyi divergence $D_\alpha(\w||\r)$ is defined as
@@
 	\begin{equation}
-		R \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{\tilde{D}_\alpha( \rho', \tau')},
+		R \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{\rlap{\raisebox{-0.1ex}{$\widetilde{\phantom{D}}$}}D_\alpha( \rho', \tau')}
 	\end{equation}
@@
 	\begin{equation}
-\tilde{D}_\alpha( \rho', \tau') := \frac{1}{m} D_\alpha (W_{\rho'^{\otimes m}} || W_{\tau'_m}),
+\widetilde{D}_\alpha( \rho', \tau') := \frac{1}{m} D_\alpha (W_{\rho'^{\otimes m}} \hspace{1pt}||\hspace{1pt} W_{\tau'_m}),
 \end{equation}
@@
 
-While this bound is abstract in its present form, it does suggest future applications by viewing $\tilde{D}_\alpha( \rho', \tau')$ within the context of hypothesis testing, as a measure of distinguishability between $\rho'^{\otimes m}$ and the $m$ qudit state $\tau'_m$.
+While this bound is abstract in its present form, it does suggest future applications by viewing $\widetilde{D}_\alpha( \rho', \tau')$ within the context of hypothesis testing~\cite{tomamichel2013}, as a measure of distinguishability between $\rho'^{\otimes m}$ and the $m$ qudit state $\tau'_m$.
 However in order to properly link with hypothesis-testing one would have to first extend such results to quasi-distributions.
@@
 \begin{equation}
-\tilde{D}_\alpha( \rho', \tau') = D_\alpha (W_{\rho'} || W_{\tau'}),
+	\widetilde{D}_\alpha( \rho', \tau') = D_\alpha (W_{\rho'} \hspace{1pt}||\hspace{1pt} W_{\tau'}),
 \end{equation}
@@
 Our bounds exploited relatively simple aspects of the Lorenz curves of the quasi-distributions, so it would be of interest to sharpen these bounds and obtain a better handle on the Lorenz curve structure in the $n\rightarrow \infty$ limit.
-It would also be of interest to analyse what features of single-shot entropies can be extended to quasi-distributions in a sensible form [\ddd{cite}].
+It would also be of interest to analyse what features of single-shot entropies can be extended to quasi-distributions in a sensible form~\cite{renyi_1960, renner_phd, tomamichel2013}.
 This raises interesting questions as we no longer have a notion of typicality and the central limit theorem does not apply.
@@
 \begin{theorem}
-	Consider a general magic state distillation process that converts a magic state $\rho^{\otimes n} \longrightarrow \E(\rho^{\otimes n})=\rho'^{\otimes m}$and let $\tau$ be any full-rank stabilizer reference state.
+	Consider a general magic state distillation process on prime dimension qudits, that converts a magic state $\rho^{\otimes n} \longrightarrow \E(\rho^{\otimes n})=\rho'^{\otimes m}$and let $\tau$ be any full-rank stabilizer reference state on a qudit.
 Then the distillation rate $R := m/n$ is upper bounded as,
 	\begin{equation}
-		R \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{\tilde{D}_\alpha( \rho', \tau')},
-	\end{equation}
-	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ with the average divergence
-	\begin{equation}
-\tilde{D}_\alpha( \rho', \tau') := \frac{1}{m} D_\alpha (W_{\rho\prime_m} || W_{\tau'_m}),
+		R \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{\rlap{\raisebox{-0.1ex}{$\widetilde{\phantom{D}}$}}D_\alpha( \rho', \tau')}
+	\end{equation}
+	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ and the average divergence
+	\begin{equation}
+\widetilde{D}_\alpha( \rho', \tau') := \frac{1}{m} D_\alpha (W_{\rho'^{\otimes m}} \hspace{1pt}||\hspace{1pt} W_{\tau'_m}),
 \end{equation}
@@
 \begin{equation}
-	\frac{m}{n} \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{\tilde{D}_\alpha( \rho', \tau')}.
+	\frac{m}{n} \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{\widetilde{D}_\alpha( \rho', \tau')}.
 \end{equation}

### 2021-06-28 magic_paper.tex

--- 2021-06-28 magic_paper.tex
@@
 
-% Figures
-% Refs
-% Notation
-% Proofreading --- Citations
-% Proofreading --- Main text
+% Proofreading --- Citations (Aberg -> {\AA}berg)
+% Proofreading --- Main text (Spacing)
 % Proofreading --- Appendices
 
-% Figs check --- consistency (size, font, text size, pads, axes, cbars), captions, folder
-
-% Labels and Refs --- consistency, cref vs ref, thm vs lem vs prop, thm restatements, (??)
-
-% Notation consistency --- noise vs error, \ln{} -> \ln, \ln vs \log vs \log_2, italics & \emph, Aberg -> {\AA}berg + [110 Knig], quasi-dist vs quasi-prob dist, def elbows, cumulant vs cumulative, stabilizer vs free, \p vs \w, W_\rho vs W_\rho(\bmz), \succ_r vs \succ
-% UK vs US english
-
 % Spacing --- figs, sections, paragraphs, eq. numbering, \noindent, QEDs
@@
 \begin{abstract}
-Magic states are key ingredients in schemes to realise universal fault-tolerant quantum computation.
+Magic states are key ingredients in schemes to realize universal fault-tolerant quantum computation.
 Theories of magic states attempt to quantify this computational element via monotones and determine how these states may be efficiently transformed into useful forms.
@@
 There has been rapid progress towards the goal of a fault-tolerant quantum computer~\cite{campbell_roads_2017, cit:raussendorf, Raussendorf_2013, Nickerson_2014, Nikahd_2017, chao_2018, lin_pieceable_2020, Lin_2020, Bourassa_2021}.
-However, many challenges remain and there is increasing need for theory to take into account physical limitations of the hardware involved.
+Nevertheless, many challenges remain and there is increasing need for theory to take into account physical limitations of the hardware involved.
 The surface code~\cite{Bravyi_1998, Freedman_2001, Dennis_2002, Raussendorf_2007} is a leading framework for fault-tolerance with very high error thresholds.
 Within this scheme, Clifford unitaries can be implemented in a robust, fault-tolerant way.
-However, due to the Eastin-Knill theorem~\cite{Eastin_2009}, we also know that it is impossible to have a universal set of transversal gates, and although Clifford unitaries can be realised transversally~\cite{Calderbank_1996, Steane_1996}, one needs to find ways around the Eastin-Knill restriction.
+However, due to the Eastin-Knill theorem~\cite{Eastin_2009}, we also know that it is impossible to have a universal set of transversal gates, and although Clifford unitaries can be realized transversally~\cite{Calderbank_1996, Steane_1996}, one needs to find ways around the Eastin-Knill restriction.
 This can be achieved by injecting in quantum states, called magic states, which promote the Clifford group to universal quantum computing~\cite{cit:bravyi}.
@@
 The magic distillation bounds can then be expressed in terms of the physics of the reference state (e.g.~free energy changes in the case of temperature).
-Such bounds are of potential interest in assessing how physical features such as temperature, noise-biases or fixed-point structure associated with restricted gate-sets constrain distillation protocols~\cite{Tuckett_2019, Aliferis_2008, Stephens_2013, Li_2015, Babbush_2018, Guillaud_2019, Fowler_2019}.
-
-The approach we take is most closely aligned with resource theories of magic, however it differs in key ways.
+Such bounds are of potential interest in assessing how physical features such as temperature, noise biases or fixed-point structure associated with restricted gate-sets constrain distillation protocols~\cite{Tuckett_2019, Aliferis_2008, Stephens_2013, Li_2015, Babbush_2018, Guillaud_2019, Fowler_2019}.
+
+The approach we take is most closely aligned with resource theories of magic, although it differs in key ways.
 We obtain distillation upper bounds without the use of monotones, but instead use tools from statistical mechanics and recent work in single-shot resource theories~\cite{cit:janzing, cit:horodecki2, Brandao_2015, Vinjanampathy_2016, Goold_2016, cit:lostaglio, cit:gour}.
@@
 \subsection{Overview of our results}
-We begin by describing how stabilizer operations correspond to stochastic maps on a discrete phase space, and how majorization can be applied to constrain magic state transformations (Section~\ref{sec:ps}).
+We begin by describing how stabilizer operations correspond to stochastic maps on a discrete phase space, and how majorization can be applied to constrain magic state transformations (Sec.~\ref{sec:ps}).
 We then consider families of magic protocols with increasing complexity.
-The simplest case we consider is for magic protocols that lead to unital channels (Section~\ref{sec:unital}).
-These are a subset of protocols that leave invariant some distinguished state or have some equilibrium fixed-point structure (Section~\ref{sec:frag}).
-We then consider protocols that are non-equilibrium processes, but only generate sub-linear correlations that enable a simple description in the thermodynamic limit (Section~\ref{sec:stab}), before giving entropic analysis that can be applied more generally (Section~\ref{section:entropies}).
+The simplest case we consider is for magic protocols that lead to unital channels (Sec.~\ref{sec:unital}).
+These are a subset of protocols that leave invariant some distinguished state or have some equilibrium fixed-point structure (Sec.~\ref{sec:frag}).
+We then consider protocols that are non-equilibrium processes, but only generate sub-linear correlations that enable a simple description in the thermodynamic limit (Sec.~\ref{sec:stab}), before giving entropic analysis that can be applied more generally (Sec.~\ref{section:entropies}).
 
@@
 
-We provide explicit bounds for magic protocols that generate unital channels (Equation~(\ref{eq:unital-bound})), as well as bounds that incorporate the temperature and Hamiltonian of the system (Theorem~\ref{thm:free-energy}) and discuss extensions to more general scenarios.
-These bounds are shown to be tighter than other bounds such as those that come from mana and thauma (Section~\ref{sec:monotones_frag} and Figure~\ref{fig:distill_bounds}).
+We provide explicit bounds for magic protocols that generate unital channels (Eq.~(\ref{eq:unital-bound})), as well as bounds that incorporate the temperature and Hamiltonian of the system (Theorem~\ref{thm:free-energy}) and discuss extensions to more general scenarios.
+These bounds are shown to be tighter than other bounds such as those that come from mana and thauma (Sec.~\ref{sec:monotones_frag} and Fig.~\ref{fig:distill_bounds}).
 
 We find that the analysis in the presence of negativity displays a range of features that do not appear in classical statistical mechanics, and leads to a picture of Wigner negativity in a quantum circuit being described as non-classical free energy that is processed under stochastic dynamics.
-This is demonstrated by non-monotonic Lorenz curves (Section~\ref{sec:lc}), and by single-shot entropies for general Wigner quasi-distributions that are well-defined, obey data-processing under stabilizer operations and can take on negative values (Section~\ref{section:entropies}).
+This is demonstrated by non-monotonic Lorenz curves (Sec.~\ref{sec:lc}), and by single-shot entropies for general Wigner quasi-distributions that are well-defined, obey data-processing under stabilizer operations and can take on negative values (Sec.~\ref{section:entropies}).
 
@@
     \includegraphics[scale=0.35]{figs/distill_bounds.pdf}
-    \caption{\textbf{Magic distillation bounds from majorization of Wigner quasi-distributions.} The above plot shows distillation upper bounds for qutrits obtained from majorisation on unital protocols.
-The constraints are plotted as a function of the depolarizing error $\epsilon$ for a noisy Strange state (Equation~\ref{eq:noisysn}).
-The bound $R_\infty$ follows from a Lorenz curve analysis presented in Section~\ref{sec:unital}, while the bound $R_{10}$ comes from single-shot entropies on the Wigner quasi-distributions, as discussed in Section~\ref{section:entropies}.
+    \caption{\textbf{Magic distillation bounds from majorization of Wigner quasi-distributions.} The above plot shows distillation upper bounds for qutrits obtained from majorization on unital protocols.
+The constraints are plotted as a function of the depolarizing error $\epsilon$ for a noisy Strange state (Eq.~(\ref{eq:noisysn})).
+The bound $R_\infty$ follows from a Lorenz curve analysis presented in Sec.~\ref{sec:unital}, while the bound $R_{10}$ comes from single-shot entropies on the Wigner quasi-distributions, as discussed in Sec.~\ref{section:entropies}.
 Numerical bounds $R_{\rm{num}}$ are obtained by using the full set of majorization constraints.
@@
 
-We show that the mana of a quantum state arises as a residue in the $\alpha$--parameter for R\'{e}nyi entropies, and gives the rate of divergence to $-\infty$ as we approach the Shannon entropy of a Wigner distribution (Equation (\ref{eq:mana-divergence})).
-Finally, in Section~\ref{sec:lower_bounds} we discuss how our approach could be extended to construct explicit lower bounds on distillation that take into account physical constraints.
+We show that the mana of a quantum state arises as a residue in the $\alpha$--parameter for R\'{e}nyi entropies, and gives the rate of divergence to $-\infty$ as we approach the Shannon entropy of a Wigner distribution (Eq.~(\ref{eq:mana-divergence})).
+Finally, in Sec.~\ref{sec:lower_bounds} we discuss how our approach could be extended to construct explicit lower bounds on distillation that take into account physical constraints.
 
@@
 Here $\omega \coloneqq e^{2\pi i/d}$ is the $d$-th root of unity and addition is taken modulo $d$.
-From these we can construct a phase space $\cal{P}_d := \mathbb{Z}_d \times \mathbb{Z}_d$ that provides a complete representation of the quantum system.
+From these we can construct a phase space $\cal{P}_d \coloneqq \mathbb{Z}_d \times \mathbb{Z}_d$ that provides a complete representation of the quantum system.
 Given a point $\bmz \coloneqq (q, p)$ we define a displacement operator,
@@
 
-The phase-point operators form an orthogonal operator basis with respect to the Hilbert-Schmidt inner product, as discussed in~\cref{app:wigner}.
+The phase-point operators form an orthogonal operator basis with respect to the Hilbert-Schmidt inner product, as discussed in Appendix~\ref{app:wigner}.
 Therefore, any quantum state $\rho$ can be expressed as a linear combination of them, $\rho = \sum_{\bmz \in \cal{P}_d} \W[\bmz]{\rho} A_{\bmz}$, where the coefficients $\W{\rho}(\z)$ give the Wigner distribution of state $\rho$,
@@
 
-For any quantum state $\rho$, the Wigner distribution $W_\rho(\bmz)$ is readily seen to be a $d^2$-dimensional quasi-probability distribution over $\cal{P}_d$.
-More precisely, $W_\rho(\bmz)$ is a real-valued function on $\P_d$ with the normalisation property $\sum_{\bmz} W_\rho(\bmz) = 1$ (see~\cref{app:wigner} for details).
+For any quantum state $\rho$, the Wigner distribution $W_\rho(\bmz)$ is readily seen to be a $d^2$-dimensional quasi-distribution over $\cal{P}_d$.
+More precisely, $W_\rho(\bmz)$ is a real-valued function on $\P_d$ with the normalisation property $\sum_{\bmz} W_\rho(\bmz) = 1$ (see Appendix~\ref{app:wigner} for details).
 
@@
     \caption{\textbf{Probing magic protocols with reference states.} 
-	A magic protocol (top figure) converts $n$ copies of some noisy magic state $\rho$ with noise parameter $\epsilon$ to $m$ copies of some less noisy state $\rho'$ with $\epsilon' < \epsilon$.
+	A magic protocol (top figure) converts $n$ copies of some noisy magic state $\rho$ with error parameter $\epsilon$ to $m$ copies of some less noisy state $\rho'$ with $\epsilon' < \epsilon$.
 The physics of the protocol can be analysed by considering how it would transform some distinguished reference stabilizer state $\tau^{\otimes n}$ (bottom figure).
-For the case where this reference state is a thermal state at some temperature $T$ our magic distillation bounds are functions of $T$, the noise parameters $\epsilon, \epsilon'$, and free energies $F, F'$.
-In addition, a quantity $\phi$ (Equation~\ref{eq:phi}) relates the computational and energy bases, and corresponds to the degree to which the Wigner negativity of $\rho$ can be given a sharp energy via the system Hamiltonian.}
+For the case where this reference state is a thermal state at some temperature $T$ our magic distillation bounds are functions of $T$, the error parameters $\epsilon, \epsilon'$, and free energies $F, F'$.
+In addition, a quantity $\phi$ (Eq.~(\ref{eq:phi})) relates the computational and energy bases, and corresponds to the degree to which the Wigner negativity of $\rho$ can be given a sharp energy via the system Hamiltonian.}
     \label{fig:sketch}
@@
 \end{equation}
-Using the fact that $W_\rho(\z)$ is a normalised quasi-distribution, we can also write $\M(\rho) = \sum_{\z} |W_\rho(\z)|$.
+Using the fact that $W_\rho(\z)$ is a normalized quasi-distribution, we can also write $\M(\rho) = \sum_{\z} |W_\rho(\z)|$.
 
@@
 In this work we develop bounds that apply to any reasonable magic theory.
-The central idea is to apply majorization theory to the quasi-probability distributions that arise for magic states.
+The central idea is to apply majorization theory to the quasi-distributions that arise for magic states.
 In the next section we explain how majorization relates to the free operations in a theory of magic.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-Any magic state protocol will correspond to a quantum channel $\E$, and so from Equation~(\ref{Wigner-Choi}) admits a Wigner representation $W_{\E}( \y | \bmz)$ that acts as a transition matrix mapping phase space points $\bmz \rightarrow \y$.
+Any magic state protocol will correspond to a quantum channel $\E$, so from Eq.~(\ref{Wigner-Choi}) it admits a Wigner representation $W_{\E}(\y | \bmz)$ that acts as a transition matrix mapping phase space points $\bmz \rightarrow \y$.
 The representation obeys the relation
@@
 
-However, note that this mapping to stochastic maps is not one-to-one.
+We note that this mapping to stochastic maps is not one-to-one.
 Not all stochastic maps on the phase space correspond to valid quantum operations.
@@
 It describes the disorder of distributions that undergo stochastic transformations, and in its simplest form defines a pre-order on probability distributions.
-Given two distributions $\p= (p_1, \dots, p_n)$ and $\q = (q_1, \dots, q_n)$ over $n$ outcomes, we say that $\p$ majorises $\q$, denoted $\p \succ \q$, if there exists a bistochastic map $A = (A_{ij})$ such that $A\p = \q$, where bistochastic means that $A_{ij} \geq 0$ and $\sum_i A_{ij} = \sum_j A_{ij} = 1$.
+Given two distributions $\p= (p_1, \dots, p_n)$ and $\q = (q_1, \dots, q_n)$ over $n$ outcomes, we say that $\p$ majorizes $\q$, denoted $\p \succ \q$, if there exists a bistochastic map $A = (A_{ij})$ such that $A\p = \q$, where bistochastic means that $A_{ij} \geq 0$ and $\sum_i A_{ij} = \sum_j A_{ij} = 1$.
 It can be shown~\cite{cit:marshall} that the condition $ \p \succ \q$ over probability distributions is equivalent to $n-1$ inequalities, which can be checked efficiently.
@@
 
-In fact, we can further generalise to \emph{relative majorization}~\cite{Blackwell_1953, Ruch_1976, ruch_mixing_1978, Renes_2016, Buscemi_2017, Rethinasamy_2020}, defined as an ordering between pairs of vectors and write
+In fact, we can further generalize to \emph{relative majorization}~\cite{Blackwell_1953, Ruch_1976, ruch_mixing_1978, Renes_2016, Buscemi_2017, Rethinasamy_2020}, defined as an ordering between pairs of vectors and write
 \begin{equation}
@@
 Our analysis applies majorization to magic states at the level of the associated Wigner distributions.
-However, these are in general quasi-probability distributions, so it is important to check how majorization is computed for these cases and what differences quasi-distributions bring over genuine probability distributions.
+Since these are in general quasi-distributions, it is important to check how majorization is computed for these cases and what differences quasi-distributions bring over genuine probability distributions.
 
@@
 Now the Lorenz curve is no longer monotonically increasing, but is a concave function that breaks through the $L_{\w|\r}(x) = 1$ barrier at an interior point and attains some non-trivial maximum $L_\star$ above the value $1$, before decreasing monotonically to $L_{\w|\r}(x)= 1$ at the end-point $x=1$.
-See~\cref{fig:lcs} for examples of non-monotonic Lorenz curves for quasi-distributions.
+See Fig.~\ref{fig:lcs} for examples of non-monotonic Lorenz curves for quasi-distributions.
 Within quantum theory, the breaking of this barrier is associated with the degree of non-classicality.
@@
     \includegraphics[scale=0.35]{figs/lc_strange.pdf}
-    \caption{\textbf{A `heretical' family of Lorenz curves.} Traditionally, Lorenz curves for distributions are monotone increasing cumulant functions that reach a maximum value of $1$.
-In contrast, Lorenz curves for magic states break through the value of $L(x)=1$ due to the presence of negativity in the associated quasi-probability distributions.
-The above family of curves correspond to multiple copies of noisy Strange states $\rho\coloneqq\rho_{\rm{S}}(\epsilon)^{\otimes n}$ (Equation~\ref{eq:noisysn}) for $n=2,4,6$ within $\R_{\sigma}$, where $\sigma = \id/3$.
+    \caption{\textbf{A `heretical' family of Lorenz curves.} Traditionally, Lorenz curves for distributions are monotone increasing cumulative functions that reach a maximum value of $1$.
+In contrast, Lorenz curves for magic states break through the value of $L(x)=1$ due to the presence of negativity in the associated quasi-distributions.
+The above family of curves correspond to multiple copies of noisy Strange states $\rho\coloneqq\rho_{\rm{S}}(\epsilon)^{\otimes n}$ (Eq.~(\ref{eq:noisysn})) for $n=2,4,6$ within $\R_{\sigma}$, where $\sigma = \id/3$.
 Solid lines represent pure Strange states, while dashed lines represent $\epsilon$-noisy Strange states with depolarising error $\epsilon = 0.1$.
@@
 
-Relative majorization is usually considered for probability distributions, so we need to verify that the same Lorenz curve conditions apply to quasi-probability distributions before proceeding with our analysis.
-This can be done from first principles, but a simpler way to see that this holds is to reduce to the problem of genuine distributions by first `masking' the negativity in the quasi-probability distribution $\w$ using the reference distribution $\r$ and then applying the conditions for relative majorization.
+Relative majorization is usually considered for probability distributions, so we need to verify that the same Lorenz curve conditions apply to quasi-distributions before proceeding with our analysis.
+This can be done from first principles, but a simpler way to see that this holds is to reduce to the problem of genuine distributions by first `masking' the negativity in the quasi-distribution $\w$ using the reference distribution $\r$ and then applying the conditions for relative majorization.
 This negativity masking then gives the following result.
@@
 	Let $\w \in \mathbb{R}^n,\w'\in \mathbb{R}^m$ be quasi-distributions, and let $\r \in \mathbb{R}^n, \r' \in \mathbb{R}^m$ be probability distributions with non-zero components.
-Then $(\w, \r) \succ (\w', \r')$ if and only if $L_{\w|\r}(x) \ge L_{\w' |\r'}(x)$ for all $x \in [0,1]$.
+Then, $(\w, \r) \succ (\w', \r')$ if and only if $L_{\w|\r}(x) \ge L_{\w' |\r'}(x)$ for all $x \in [0,1]$.
 \end{theorem}
@@
 A similar result holds for $\w'$ and $\r'$ and we choose $\epsilon$ sufficiently small so that both $\w_\epsilon$ and $\w_\epsilon'$ are probability distributions.
-We now have that $(\w , \r) \succ (\w', \r')$ if and only if $(\w_\epsilon , \r) \succ (\w_\epsilon', \r')$.
+We now have that $(\w, \r) \succ (\w', \r')$ if and only if $(\w_\epsilon , \r) \succ (\w_\epsilon', \r')$.
 This equivalence holds because there exists a stochastic map $A$ such that $A \w = \w'$ and $A \r = \r'$ if and only if
@@
 In terms of a Lorenz curve condition we have that $(\w_\epsilon , \r) \succ (\w_\epsilon', \r')$ if and only if $L_{\w_\epsilon |\r} (x) \ge L_{\w'_\epsilon |\r'} (x)$ for all $x \in [0,1]$. 
-However, as we show in the Appendices (\cref{lemma:Lorenz_linearity}), the Lorenz curve for any quasi-probability distribution obeys the relation
+Additionally, we show in the appendices (Proposition~\ref{Lorenz_linearity}) that the Lorenz curve for any quasi-distribution obeys the relation
 \begin{equation}
@@
 We can now consider how majorization constrains magic distillation rates starting in this section with an abstract setting based on the fixed-point structure of the physical operations accessible to us.
-We show that any magic theory can always be decomposed in terms of `sub-theories' with a particular fixed-point structure.
-This allows the use of $\mathbf{d}$--majorization, however in~\cref{sec:stab}, we drop the requirement of fixed-points and instead use the full relative majorization, before giving general entropic constraints in Section~\ref{section:entropies}.
+We show that any magic theory can always be decomposed in terms of `sub-theories' with a particular fixed-point structure, which allows the use of $\mathbf{d}$--majorization.
+Later, in Sec.~\ref{sec:stab}, we drop the requirement of fixed-points and instead use the full relative majorization, before giving general entropic constraints in Sec.~\ref{section:entropies}.
 
@@
 The free states $\F$ are a closed, bounded set and moreover the image of $\F$ under the map $\E$ is in $\F$.
-By the Brouwer Fixed-Point theorem~\cite{cit:brouwer} this mapping must therefore have a fixed point $\sigma \in \F$.
-Therefore, $\E \in \O_\sigma$ and the interconversion is possible in $\R_\sigma$.
+By the Brouwer fixed-point theorem~\cite{cit:brouwer}, this mapping must therefore have a fixed point $\sigma \in \F$, so $\E \in \O_\sigma$ and the interconversion is possible in $\R_\sigma$.
 \end{proof}
@@
 
-  Note, however, that this is not a single numerical constraint, but a family of constraints.
-For $n$ copies of a qudit system of dimension $d$ the number of terms in $W_{\rho}$ is $d^{2n}$, so imposing the Lorenz curve condition corresponds to \emph{exponentially} many constraints.
+Note that this is not a single numerical constraint, but a family of constraints.
+For $n$ copies of a qudit system of dimension $d$ the number of terms in $W_{\rho}$ is $d^{2n}$, so imposing the Lorenz curve condition corresponds to exponentially many constraints.
 Before computing explicit examples, in the next section we describe how these majorization constraints relate to other known monotones.
@@
 	The sum-negativity of a magic state $\rho$ can be written as $sn(\rho) =\frac{1}{2} (\sum_{\bmz} |W_\rho(\bmz) | - 1)$.
-We make use of the $L_1$-norm form of relative majorization, (see~\cref{app:major}), which states that $\p \succ_{\r} \q$ if and only if
+We make use of the $L_1$-norm form of relative majorization, (see Appendix~\ref{app:major}), which states that $\p \succ_{\r} \q$ if and only if
 	\begin{equation}
@@
 \end{theorem}
-The proof of this is given in~\cref{app:major}.
+The proof of this is given in Appendix~\ref{app:major}.
 Using the Lorenz curve perspective, it is also simple to construct new monotones.
 For example, within a given $\R_\sigma$, the area above the horizontal line $y = 1$ is another magic monotone.
-\begin{lemma}
+\begin{theorem}
 Given a magic state $\rho$ and a free state $\sigma$, let $\A_\sigma(\rho)$ be the area of the region $\{(x, y): 1 \leq y \leq L_{\rho | \sigma}(x)\}$.
 Then $\A_\sigma(\rho)$ is a magic monotone for $\R_\sigma$.
-\end{lemma}
+\end{theorem}
 \begin{proof}
@@
 \end{proof}
-Note though, in contrast to mana, the area monotone is \emph{specific to the $\R_\sigma$}, and its value will vary as we change $\sigma$.
+Note though, in contrast to mana, the area monotone is \emph{specific to $\R_\sigma$}, and its value will vary as we change $\sigma$.
 Therefore its monotonicity depends on the physics of the fixed point and provides a means to analyse magic distillation only under free operations that leave $\sigma$ invariant.
-One can also define an area monotone in the more general setting of relative majorization, where one drops the fixed point emphasis as in Section \ref{sec:stab}.
+One can also define an area monotone in the more general setting of relative majorization, where one drops the fixed point emphasis as in Sec.~\ref{sec:stab}.
 
@@
 
-We now consider purifying $n$ copies of a noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ into a smaller number of copies $n'$ of a less noisy Strange state $\rho_{\rm{S}}(\epsilon')^{\otimes n'}$, with $\epsilon' < \epsilon$ and $n' \leq n$.
-The maximally mixed state is a stabilizer state and so free, we choose to tensor in $n'-n$ auxiliary copies of it to the output.
-This simplifies analysis, and does not affect distillation rates as it is easy to see that
-\begin{equation}
-	L_{\rho |\sigma} (x) = L_{\rho \otimes \sigma |\sigma \otimes \sigma}(x),
-\end{equation}
-for any full-rank $\sigma \in \F$. Therefore, we compute the Lorenz curves for the transformation
+We now consider the problem of purifying $n$ copies of a noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ into a smaller number of copies $n'$ of a less noisy Strange state $\rho_{\rm{S}}(\epsilon')^{\otimes n'}$, with $\epsilon' < \epsilon$ and $n' \leq n$.
+In particular, we compute the Lorenz curves for the transformation
 \begin{equation}\label{eq:sudist}
@@
 
-Due to negativity, the ordering of the components of rescaled Wigner distribution $W_{\rho_n |\sigma_n}(\bmz) \coloneqq W_{\rho_n}(\bmz)/W_{\sigma_n}(\bmz)$, for $\rho_n = \rho_S(\epsilon)^{\otimes n}$, and $\sigma_n = \sigma^{\otimes n}= (\I/3)^{\otimes n}$, depends on whether $-v(\epsilon)$ appears to an even or odd power.
+Due to negativity, the ordering of the components of the rescaled Wigner distribution $W_{\rho_n |\sigma_n}(\bmz) \coloneqq W_{\rho_n}(\bmz)/W_{\sigma_n}(\bmz)$, for $\rho_n = \rho_S(\epsilon)^{\otimes n}$, and $\sigma_n = \sigma^{\otimes n}= (\I/3)^{\otimes n}$, depends on whether $-v(\epsilon)$ is raised to an even or odd power.
 Treating the Wigner distributions as vectors, the component values $w_i$ and associated multiplicities $m_i$ in the $n$--copy case are found to be
@@
 where index $i$ runs through $0, \dots, n$, and we assume for simplicity that $n$ is even and $\epsilon \leq 3/7$, which implies that $v \geq u$.
-All details on the analysis are provided in~\cref{app:lcsu_technical}.
+All details on the analysis are provided in Appendix~\ref{app:lcsu_technical}.
 
@@
 
-The coordinates of the first point after the origin for $\rho_S(\epsilon)^{\otimes n}$ are given by $(1/9^n, v(\epsilon)^n)$, while for $\rho_S(\epsilon')^{\otimes n'}$ by $(1/9^{n'}, v(\epsilon')^{n'})$, and by considering the slope of the line segment joining this point to the origin we can use~\cref{prop:first_elb} in the appendices, to bound $R(\epsilon, \epsilon')$.
+The coordinates of the first point after the origin for $\rho_S(\epsilon)^{\otimes n}$ are given by $(1/9^n, v(\epsilon)^n)$, while for $\rho_S(\epsilon')^{\otimes n'}$ by $(1/9^{n'}, v(\epsilon')^{n'})$, and by considering the slope of the line segment joining this point to the origin we can use Proposition~\ref{prop:first_elb} in the appendices, to bound $R(\epsilon, \epsilon')$.
 We find that
 \begin{equation}\label{eq:unital-bound}
-	R(\epsilon, \epsilon') \leq R_\infty :=\frac{\ln (3-4\epsilon)}{\ln (3-4\epsilon')}.
-\end{equation}
-The choice of denoting the bound by $R_\infty$ is explained in Section \ref{section:entropies} in relation to single-shot entropies.
+	R(\epsilon, \epsilon') \leq R_\infty \coloneqq\frac{\log (3-4\epsilon)}{\log (3-4\epsilon')}.
+\end{equation}
+The choice of denoting the bound by $R_\infty$ is explained in Sec.~\ref{section:entropies} in relation to single-shot entropies.
 For the limiting case of pure magic states on the output ($\epsilon'=0$), this simplifies to
 \begin{equation}
-	R \leq 1 + \frac{\ln (1 - \frac{4}{3} \epsilon)}{\ln 3}.
+	R \leq 1 + \frac{\log (1 - \frac{4}{3} \epsilon)}{\log 3}.
 \end{equation}
@@
 \begin{equation}
-	R \leq \frac{\M(\rho_{\rm{S}}(\epsilon))}{\M(\rho_{\rm{S}}(0))} = 1 + \frac{\ln \left(1 - \frac{8}{15}\epsilon \right)}{\ln \frac{5}{3}}.
+	R \leq \frac{\M(\rho_{\rm{S}}(\epsilon))}{\M(\rho_{\rm{S}}(0))} = 1 + \frac{\log \left(1 - \frac{8}{15}\epsilon \right)}{\log \frac{5}{3}}.
 \end{equation}
@@
 and can be calculated numerically via a semi-definite program.
-For the noisy Strange state, the max--thauma bound coincides with the mana bound, and we find that they are both looser than the majorization bound $R_\infty$ as shown in~\cref{fig:distill_bounds}.
+For the noisy Strange state, the max--thauma bound coincides with the mana bound, and we find that they are both looser than the majorization bound $R_\infty$ as shown in Fig.~\ref{fig:distill_bounds}.
 
@@
 This is justified because the protocol on the input magic state results in state $\rho(\epsilon')^{\otimes m}$, which is invariant under permutations.
-Therefore, we are always allowed to symmetrise the output $\E(X)$ by performing a group average over the permutation group for the output systems without changing the performance of the distillation protocol on $\rho(\epsilon)^{\otimes n}$.
+Therefore, we are always allowed to symmetrize the output $\E(X)$ by performing a group average over the permutation group for the output systems without changing the performance of the distillation protocol on $\rho(\epsilon)^{\otimes n}$.
 Thus, we can assume that $\E$ always outputs a symmetric state in general.
@@
 The protocol transforms the equilibrium as $\tau^{\otimes n} \rightarrow \E(\tau^{\otimes n}) = \tau^{\prime \otimes m}$.
-The protocol does not on its own generate magic and so we assume the output state $\tau'$ is also a Wigner-positive state.
+The protocol does not generate magic on its own, so we assume that the output state $\tau'$ is also a Wigner-positive state.
 However, this is generally a \emph{non-equilibrium} state for the system.
@@
 
-In Appendix~\ref{thm:free-energy-bound-proof} we analyse the Lorenz curves of this condition and obtain the following magic distillation bound that combines computational measures $\epsilon,\epsilon'$, with terms that depend on the Hamiltonian and reference temperature $T$ of the physical system.
+In Appendix~\ref{app:lcst_technical} we analyse the Lorenz curves of this condition and obtain the following magic distillation bound that combines computational measures $\epsilon,\epsilon'$, with terms that depend on the Hamiltonian and reference temperature $T$ of the physical system.
 We state the result for the case of qutrits, but a similar analysis works for general odd-dimension qudits.
@@
 \begin{equation}\label{eq:rate_bounds_proof}
-	R \leq \dfrac{\ln \big( 1-\frac{4}{3}\epsilon \big) + \beta (\phi - F)}{\ln \big( 1-\frac{4}{3}\epsilon' \big) + \beta (\phi' - F')},
+	R \leq \dfrac{\log \big( 1-\frac{4}{3}\epsilon \big) + \beta (\phi - F)}{\log \big( 1-\frac{4}{3}\epsilon' \big) + \beta (\phi' - F')},
 \end{equation}
@@
 \end{theorem}
-\noindent The proof of this is provided in~\cref{thm:free-energy-bound-proof}, and follows a similar line to the unital protocol bound.
+\noindent The proof of this is provided in Appendix~\ref{app:lcst_technical}, and follows a similar line to the unital protocol bound.
 
@@
 Finally, if $H$ has a stabilizer eigenbasis then $\phi = E_i$ for some $i$, independent of the temperature $T$.
-Details of this are provided in Appendix \ref{app:lcst_technical}.
+Details of this are provided in Appendix~\ref{app:lcst_technical}.
 
@@
 Similar to the unital protocol bounds, the above result is based on only part of the Lorenz curves and so can certainly be tightened with further analysis.
-The primary role of the pre/post-processing by Clifford unitaries in~\cref{thm:free-energy} is to simplify the form of the bound, and allow it to be expressed in terms of the free energy per particle in a way that does not depend on the parameters $\epsilon, \epsilon', \beta$ in a complex form.
-In Appendix \ref{app:lcst_technical}, we give bounds in which one does not include these Clifford changes of basis (see Theorem \ref{thm:no-processing}), and which have a more non-trivial dependency on the parameters.
+The primary role of the pre/post-processing by Clifford unitaries in Theorem~\ref{thm:free-energy} is to simplify the form of the bound, and allow it to be expressed in terms of the free energy per particle in a way that does not depend on the parameters $\epsilon, \epsilon', \beta$ in a complex form.
+In Appendix~\ref{app:lcst_technical}, we give bounds in which one does not include these Clifford changes of basis (see Theorem~\ref{thm:no-processing}), and which have a more non-trivial dependency on the parameters.
 
@@
     \centering
-    \subfigure[][]{%
-    \label{fig:noCliff}%
+    \subfigure[][]{
+    \label{fig:noCliff}
     \includegraphics[scale=0.35]{figs/rate_scatter.pdf}}\\
-    \subfigure[][]{%
-    \label{fig:Cliff}%
+    \subfigure[][]{
+    \label{fig:Cliff}
     \includegraphics[scale=0.35]{figs/rate_scatter_cliff.pdf}}
     \caption{\textbf{Temperature-dependent bounds for magic distillation.} Shown are two contour plots of the bound on $R(\epsilon, \beta)$ for the case $H = H' = \sum_{k \in \mathbb{Z}_3} k \ketbra{k}$ and $\epsilon' = 0$, where $\beta$ is the inverse temperature and $\epsilon$ is the depolarising error of the input magic state.
-The top figure \subref{fig:noCliff} does not use any changes of Clifford basis, and the form of the bound depends on both the noise parameter and temperature.
-The curved dashed line is $\epsilon_\star(\beta)$ and given by Equation~\ref{eq:threshold} and $\beta_\star = (kT_\star)^{-1}$ is given by $E_2-\phi = kT_\star \ln 2$.
-In the bottom figure \subref{fig:Cliff} Clifford processing is used resulting in a smoother bound. In both figures the $\beta = 0$ line correspond to the unital bounds.}
+The top figure~\subref{fig:noCliff} does not use any changes of Clifford basis, and the form of the bound depends on both the error parameter and temperature.
+The curved dashed line is $\epsilon_\star(\beta)$ and given by Eq.~(\ref{eq:threshold}) and $\beta_\star = (kT_\star)^{-1}$ is given by $E_2-\phi = kT_\star \ln 2$.
+In the bottom figure~\subref{fig:Cliff} Clifford processing is used resulting in a smoother bound. In both figures the $\beta = 0$ line correspond to the unital bounds.}
     \label{fig:rate_contour}
@@
 
-The assumption that is more non-trivial is that we neglect correlations in the reference state in the thermodynamic limit.
-However for more general scenarios one could make use of variational tools such as the Bogoliubov inequality~\cite{bogolyubov_1966} for approximating the free energy of a system via product states, to obtain similar bounds.
+The assumption which is non-trivial is that we neglect correlations in the reference state in the thermodynamic limit.
+However, for more general scenarios one could make use of variational tools such as the Bogoliubov inequality~\cite{bogolyubov_1966} for approximating the free energy of a system via product states, to obtain similar bounds.
 
 The simplest special case to consider is where the Hamiltonian $H$ is diagonal in the computational basis, and $H=H'$, implying that the protocol leaves the reference equilibrium state unchanged, hence it corresponds to a Gibbs-preserving map~\cite{faist_2015}.
-For the limiting case of $\epsilon' \rightarrow 0$ we obtain~\cref{fig:rate_contour} which is a contour plot of the bound on $R$ as a function of inverse temperature $\beta$ and the depolarising error $\epsilon$ for the noisy input magic states.
+For the limiting case of $\epsilon' \rightarrow 0$ we obtain Fig.~\ref{fig:rate_contour} which is a contour plot of the bound on $R$ as a function of inverse temperature $\beta$ and the depolarising error $\epsilon$ for the noisy input magic states.
 In this figure we show both the bounds with Clifford basis changes and without them.
-In the more general case, $\Delta F \coloneqq F' - F \ne 0$ and so the protocol, when applied to the reference state, adds/extracts free energy from the system.
-
-%
-%\begin{figure}
-%    \centering
-%    \includegraphics[scale=0.4]{figs/test/R_vs_E1.pdf}
-%    \caption{Here, $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$, $H = \rm{diag}(0,E,10)$ and $H' = \rm{diag}(0,E',10)$.
-%    }
-%    \label{fig:rvse1}
-%\end{figure}
-
-%\begin{figure}
-%    \centering
-%    \includegraphics[scale=0.4]{figs/test/R_vs_E2.pdf}
-%    \caption{Here, $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$, $H = \rm{diag}(0,5,E)$ and $H' = \rm{diag}(0,5,E')$.
-%    }
-%    \label{fig:rvse2}
-%\end{figure}
-
-%\begin{figure}
-%    \centering
-%    \includegraphics[scale=0.4]{figs/test/R_vs_H.pdf}
-%    \caption{Here, $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$, $H = {\rm{diag}}(0,1,2)$ and $H' = (1-p-q){\rm{diag}}(0,1,2)+p{\rm{diag}}(1,2,0)+q{\rm{diag}}(2,0,1)$.
-%    }
-%    \label{fig:rvsh}
-%\end{figure}
+In the more general case, $\Delta F \coloneqq F' - F \ne 0$, so the protocol, when applied to the reference state, adds/extracts free energy from the system.
 
@@
     \includegraphics[scale=0.35]{figs/R_vs_A.pdf}
-    \caption{\textbf{Variation of distillation bounds with Hamiltonian.}  We illustrate variation of the bound in Equation~\ref{eq:rate_bounds_proof} with respect to the system Hamiltonian.
+    \caption{\textbf{Variation of distillation bounds with Hamiltonian.}  We illustrate variation of the bound in Eq.~(\ref{eq:rate_bounds_proof}) with respect to the system Hamiltonian.
 We fix $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$ and look at a family of Hamiltonians for the qutrit systems, given by $H = A_{\bmo}$ and $H' = (1-p-q)A_{\bmo}+pA_{(1,2)}+q{\rm{diag}}(0,1,2)$ for varying probabilities $p, q$.
@@
 
-One obstacle to linking with macroscopic, equilibrium free energy is that the Wigner distribution is generally a quasi-distribution and so the entropy $H(\w) = -\sum_i w_i \log w_i$ of the Wigner distribution is not defined off of the set $\F$, let alone having a physically meaningful interpretation.
-
-However, it turns out that the analysis for the temperature-dependent bound given by Equation (\ref{eq:rate_bounds_proof}) implicitly made use of the single-shot R\'{e}nyi divergence $D_\infty (\p \hspace{1pt}||\hspace{1pt} \r)$, which is given by
+One obstacle to linking with macroscopic, equilibrium free energy is that the Wigner distribution is generally a quasi-distribution, so the entropy $H(\w) = -\sum_i w_i \log w_i$ of the Wigner distribution is not defined outside the set $\F$, let alone have a physically meaningful interpretation.
+
+However, it turns out that the analysis for the temperature-dependent bound given by Eq.~(\ref{eq:rate_bounds_proof}) implicitly made use of the single-shot R\'{e}nyi divergence~\cite{renyi_1960} $D_\infty (\p \hspace{1pt}||\hspace{1pt} \r)$, which is given by
 \begin{equation}
@@
 \end{equation}
-It is clear that this does remain well-defined on quasi-distributions, and from the majorization relation also has a clear physical meaning, and in~\cref{app:lcst_technical}, we show that this divergence has the following properties that are derived via relative majorization.
+It is clear that this does remain well-defined on quasi-distributions, and from the majorization relation also has a clear physical meaning, and in Appendix~\ref{app:lcst_technical}, we show that this divergence has the following properties that are derived via relative majorization.
 \begin{theorem}\label{thm:Dinfty} 
@@
 We can go further, and show that in fact a range of R\'{e}nyi entropies remain both well-defined and meaningful in the Wigner representation.
-The $\alpha$--R\'{e}nyi entropy $H_\alpha(\p)$ is defined as
-\begin{equation}
-	H_\alpha(\p) := \frac{1}{1-\alpha} \log \sum_i p_i^\alpha.
+The $\alpha$--R\'{e}nyi entropy $H_\alpha(\p)$ is defined as~\cite{renyi_1960}
+\begin{equation}
+	H_\alpha(\p) \coloneqq \frac{1}{1-\alpha} \log \sum_i p_i^\alpha.
 \end{equation}
@@
 The unusual form of the $\alpha$ parameter is required so that the entropy function is well-defined and real-valued for all $\w$.
-The allowed values of $\alpha$ are dense in $\alpha >1$, however, while R\'{e}nyi entropies on probabilities can also be used for $0 < \alpha <1$ it turns out that for quasi-probability distributions this parameter regime is no longer monotonic in terms of the majorization pre-order (see Appendix~\ref{app:single-shot} for details).
+The allowed values of $\alpha$ are dense in $\alpha >1$, however, while R\'{e}nyi entropies on probabilities can also be used for $0 < \alpha <1$, it turns out that this parameter regime is no longer monotonic in terms of the majorization pre-order for quasi-distributions (see Appendix~\ref{app:single-shot} for details).
 
@@
 Therefore, the statistical mechanical description of stabilizer operations provides a setting in which negative entropy is fully meaningful, and quantifies the fact that magic states are more ordered than a perfectly sharp, deterministic classical state $\w = (1,0, \dots , 0)$ with zero entropy.
-We note that prior work has shown that negative conditional entropy~\cite{rio_thermodynamic_2011} arises in the context of quantum correlations, however this is unrelated to the present negative entropy.
+We note that prior work has shown that negative conditional entropy~\cite{rio_thermodynamic_2011} arises in the context of quantum correlations, but is unrelated to the present negative entropy.
 
@@
 with $\epsilon \rightarrow 0^+$ through a sequence of rational values.
-We recall that mana can be written as $\M(\rho) = \log \sum_{\bmz} |W_\rho(\bmz)|$, and so we obtain a second new perspective on mana:
+We recall that mana can be written as $\M(\rho) = \log \sum_{\bmz} |W_\rho(\bmz)|$, so we obtain a second new perspective on mana:
 \begin{equation}\label{eq:mana-divergence}
@@
 Therefore, if we try to push this to the present setting, the presence of Wigner negativity would correspond to a divergence in the first derivative of an effective free energy as $T \rightarrow T_0$.
-It is interesting to speculate whether this non-classicality could be interpreted in terms of a phase transition \ddd{[CITE BOOK]}.
+It is interesting to speculate whether this non-classicality could be interpreted in terms of a phase transition~\cite{domb2000phase}.
 
 \subsection{R\'{e}nyi divergences and general distillation bounds}
-Every entropy can be obtained from a relative entropy~\cite{Gour_2020} and so we now state the extensions for R\'{e}nyi divergences of Wigner distributions.
-The $\alpha$--R\'{e}nyi divergence $D_\alpha(\w||\r)$ is defined as
-\begin{equation}
-	D_\alpha(\w \hspace{1pt}||\hspace{1pt} \r) := \frac{1}{\alpha-1} \log \sum_i w_i^\alpha r_i^{1-\alpha},
-\end{equation}
-where $\w$ can be a quasi-distribution, $\r$ a probability distribution with positive components. In~\cref{app:single-shot}, we also show that the divergence satisfies the following.
+Every entropy can be obtained from a relative entropy~\cite{Gour_2020} so we now state the extensions for R\'{e}nyi divergences of Wigner distributions.
+The $\alpha$--R\'{e}nyi divergence $D_\alpha(\p||\r)$ is defined as
+\begin{equation}
+	D_\alpha(\p \hspace{1pt}||\hspace{1pt} \r) \coloneqq \frac{1}{\alpha-1} \log \sum_i p_i^\alpha r_i^{1-\alpha},
+\end{equation}
+where $\p$ can be a quasi-distribution and $\r$ a probability distribution with positive components. In Appendix~\ref{app:single-shot}, we also show that the divergence satisfies the following.
 
@@
 	Consider a general magic state distillation process on prime dimension qudits, that converts a magic state $\rho^{\otimes n} \longrightarrow \E(\rho^{\otimes n})=\rho'^{\otimes m}$and let $\tau$ be any full-rank stabilizer reference state on a qudit.
-Then the distillation rate $R := m/n$ is upper bounded as,
-	\begin{equation}
-		R \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{\tilde{D}_\alpha( \rho', \tau')},
+Then the distillation rate $R \coloneqq m/n$ is upper bounded as,
+	\begin{equation}
+		R \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{\rlap{\raisebox{-0.2ex}{$\widetilde{\phantom{D}}$}}D_\alpha( \rho', \tau')}
 	\end{equation}
@@
 	\begin{equation}
-\tilde{D}_\alpha( \rho', \tau') := \frac{1}{m} D_\alpha (W_{\rho'^{\otimes m}} || W_{\tau'_m}),
+\widetilde{D}_\alpha( \rho', \tau') \coloneqq \frac{1}{m} D_\alpha (W_{\rho'^{\otimes m}} \hspace{1pt}||\hspace{1pt} W_{\tau'_m}),
 \end{equation}
@@
 
-While this bound is abstract in its present form, it does suggest future applications by viewing $\tilde{D}_\alpha( \rho', \tau')$ within the context of hypothesis testing, as a measure of distinguishability between $\rho'^{\otimes m}$ and the $m$ qudit state $\tau'_m$.
-However in order to properly link with hypothesis-testing one would have to first extend such results to quasi-distributions.
+While this bound is abstract in its present form, it does suggest future applications by viewing $\widetilde{D}_\alpha( \rho', \tau')$ within the context of hypothesis testing~\cite{tomamichel2013}, as a measure of distinguishability between $\rho'^{\otimes m}$ and the $m$ qudit state $\tau'_m$.
+However, in order to properly link with hypothesis-testing one would have to first extend such results to quasi-distributions.
 
@@
 \begin{equation}
-\tilde{D}_\alpha( \rho', \tau') = D_\alpha (W_{\rho'} || W_{\tau'}),
-\end{equation}
-which gives a generalized version of Theorem \ref{thm:free-energy}.
+	\widetilde{D}_\alpha( \rho', \tau') = D_\alpha (W_{\rho'} \hspace{1pt}||\hspace{1pt} W_{\tau'}),
+\end{equation}
+which gives a generalized version of Theorem~\ref{thm:free-energy}.
 
@@
 This upper bound can be numerically minimized over $\alpha$, for any $\epsilon$.
-The case $R_{10}$ is shown in Figure~\ref{fig:distill_bounds} and numerical evidence shows it is close to the optimal bound from majorization.
+The case $R_{10}$ is shown in Fig.~\ref{fig:distill_bounds} and numerical evidence shows it is close to the optimal bound from majorization.
 
@@
 Our bounds exploited relatively simple aspects of the Lorenz curves of the quasi-distributions, so it would be of interest to sharpen these bounds and obtain a better handle on the Lorenz curve structure in the $n\rightarrow \infty$ limit.
-It would also be of interest to analyse what features of single-shot entropies can be extended to quasi-distributions in a sensible form [\ddd{CITE RENNER+TOMAMICHEL}].
+It would also be of interest to analyse what features of single-shot entropies can be extended to quasi-distributions in a sensible form~\cite{renner_phd, tomamichel2013}.
 This raises interesting questions as we no longer have a notion of typicality and the central limit theorem does not apply.
 That said, for special states such as the Strange state, the asymptotic behaviour is relatively simple, so exact asymptotics for this should be possible.
-In~\cref{app:lcsu_technical} and~\cref{app:lcst_technical} we give additional results that may be of use for later work.
+In Appendix~\ref{app:lcsu_technical} and Appendix~\ref{app:lcst_technical} we give additional results that may be of use for later work.
 
@@
 The Clifford group action on a quantum system corresponds to the action of the affine symplectic group $G=SL(2,\mathbb{Z}_d) \ltimes \mathbb{Z}_d^2$ on the discrete phase space~\cite{cit:gross3, cit:bengtsson}.
-Therefore, any convex mixture of Clifford unitaries will correpond to a convex mixture of these group actions.
-The Hardy-Littlewood theorem~\cite{hardy_1952} tells us that majorization is obtained from convex mixtures of arbitrary permutations, however this has also been generalised to convex mixtures of elements of a general group $G$.
+Therefore, any convex mixture of Clifford unitaries will correspond to a convex mixture of these group actions.
+The Hardy-Littlewood theorem~\cite{hardy_1952} tells us that majorization is obtained from convex mixtures of arbitrary permutations, a result that has also been generalized to convex mixtures of elements of a general group $G$.
 This $G$--majorization has been studied in the classical literature and a range of results are known about it~\cite{giovagnoli_1985, steerneman_1990, eaton_1977}.
@@
 	    \item[(iv)]\label{en:a4} Completeness relation: $\sum_{\bmz \in \cal{P}_d} A_{\bmz} = d\id$;
-	    \item[(i)]\label{en:a5} Orthogonality: $\tr[A_{\bmz}^\dagger A_{\bmy'}] = d \delta_{\bmz,\bmy'}$.
+	    \item[(i)]\label{en:a5} Orthogonality: $\tr[A_{\bmz}^\dagger A_{\bmy}] = d \delta_{\bmz,\bmy}$.
 	\end{enumerate}
 \end{proposition}
-All properties follow from the definition in~\cref{eq:ax} along with properties of the displacement operator $D_{\bmz}$ and can be found in the literature, e.g.~\cite{cit:veitch,Vourdas_2004,cit:gross3}
+All properties follow from the definition in Eq.~(\ref{eq:ax}) along with properties of the displacement operators $D_{\bmz}$ and can be found in the literature, e.g.~\cite{cit:veitch,Vourdas_2004,cit:gross3}
 
@@
     \item[(i)]\label{en:w1} Real valued: $\W{\rho}(\bmz) \in \mathbb{R}^{d^2}$;
-    \item[(ii)]\label{en:w2} Normalised: $\sum_{\bmz \in \cal{P}_d} \W[\bmz]{\rho}=1$;
+    \item[(ii)]\label{en:w2} Normalized: $\sum_{\bmz \in \cal{P}_d} \W[\bmz]{\rho}=1$;
     \item[(iii)]\label{en:w3} Bounded: $\abs{\W[\bmz]{\rho}} \leq \frac{1}{d}$.
@@
         \item[(i)]\label{en:wo1} Real-valued: $\W{\E}(\bmz|\bmy) \in \mathbb{R}^{d_A^2} \times \mathbb{R}^{d_B^2}$;
-        \item[(ii)]\label{en:wo2} Normalised: $\sum_{\bmy \in \cal{P}_{d_B}} \W[\bmz|\bmy]{\E} = 1$ \\ 
+        \item[(ii)]\label{en:wo2} Normalized: $\sum_{\bmy \in \cal{P}_{d_{\scalebox{.9}{$\scriptscriptstyle B$}}}} \W[\bmz|\bmy]{\E} = 1$ \\ 
         for any $\bmz \in \cal{P}_{d_A}$;
@@
 \begin{proof}
-	Proof of all properties are provided in~\cite{Wang_2019} except for property (iii) which is a direct consequence of the definition of $\W{\E}$ and property (iii) in~\cref{thm:wstate}.
-\end{proof}
-
-Within the context of the Wigner representation, we define the re-scaled quasi-distribution
-\begin{equation}
-	W_{\rho|\tau}(\bmz) := \frac{W_\rho (\bmz) }{ W_\tau(\bmz)},
+	Proof of all properties are provided in~\cite{Wang_2019} except for property (iii) which is a direct consequence of the definition of $\W{\E}$ and property (iii) in Proposition~\ref{thm:wstate}.
+\end{proof}
+
+Within the context of the Wigner representation, we define the rescaled quasi-distribution
+\begin{equation}
+	W_{\rho|\tau}(\bmz) \coloneqq \frac{W_\rho (\bmz) }{ W_\tau(\bmz)},
 \end{equation}
@@
 
-The following lemma shows that the re-scaled Lorenz curves behave in a natural way under tensor products. 
+The following result shows that the rescaled Lorenz curves behave in a natural way under tensor products. 
 \begin{proposition}\label{prop:rescaled_multi}
-	Let $\tau_A, \tau_B$ be full rank stabilizer states on systems $A$ and $B$, and let $\rho_A, \rho_B$ be arbitrary states on $A,B$. Then the rescaled quasi-distribution obeys
+	Let $\tau_A, \tau_B$ be full rank stabilizer states on systems $A$ and $B$, and let $\rho_A, \rho_B$ be arbitrary states on $A,B$. Then, the rescaled quasi-distribution obeys
 \begin{equation}
@@
 
-We define a Lorenz curve \emph{elbow} as a point where the slope of the curve changes, in accordance to the use of the term for Lorenz curve of proper probability distributions.
+We define a Lorenz curve \emph{elbow} as a point where the slope of the curve changes, in accordance to the use of the term for Lorenz curves of proper probability distributions.
 
 Here, we verify useful majorization properties in the context of quasi-probability distributions, starting from the property that the Lorenz curve is concave.
-\begin{lemma}\label{L-concave} Let $\w$ be a quasi-probability distribution and let $\r$ be a probability distribution with strictly non-zero components.
-Then $L_{\w|\r}(x)$ is a concave function on $[0,1]$.
-\end{lemma}
+\begin{proposition}\label{L-concave} 
+	Let $\w$ be a quasi-distribution and let $\r$ be a probability distribution with strictly non-zero components. Then $L_{\w|\r}(x)$ is a concave function on $[0,1]$.
+\end{proposition}
 \begin{proof} 
@@
 By inspection both $f_1$ and $f_2$ are concave functions, and $f_1(x) + f_2 (x) = L_{\w|\r}(x)$ for all $x\in [0,1]$.
-However, the sum of two concave functions is also concave and the result follows.
-\end{proof}
-
-The following result is used in~\cref{sec:lc} to prove that the Lorenz curve condition due to relative majorization is true for quasi-distributions.
-\begin{proposition}\label{lemma:Lorenz_linearity}
-	Let $\w$ be a quasi-probability distribution and let $\r$ be a probability distribution with strictly non-zero components. 
+However, the sum of two concave functions is also concave which concludes the proof.
+\end{proof}
+
+The following result is used in Sec.~\ref{sec:lc} to prove that the Lorenz curve condition due to relative majorization is true for quasi-distributions.
+\begin{proposition}\label{Lorenz_linearity}
+	Let $\w$ be a quasi-distribution and let $\r$ be a probability distribution with strictly non-zero components. 
 	Then, $L_{a\w + b \r | \r} (x) = a L_{\w |\r}(x) + b x$ for any constants $a > 0$ and $b \in \mathbb{R}$.
@@
 
-The following provides equivalent formulations of relative majorization on quasi-probabilities.
+The following provides equivalent formulations of relative majorization on quasi-distributions.
 
 \begin{proposition}\label{prop:rmajor}
-Given quasi-probability distributions $\w, \w'$, $\r , \r'$, such that the components of $\r$ and $\r'$ are positive, the following statements are equivalent:
+Given quasi-distributions $\w, \w'$, $\r , \r'$, such that the components of $\r$ and $\r'$ are positive, the following statements are equivalent:
   \begin{enumerate}
@@
 
-	The equivalence between (i) and (ii) on quasi-distributions was proven in~\cref{thm:lcquasi}.
+	The equivalence between (i) and (ii) on quasi-distributions was proven in Theorem~\ref{thm:lcquasi}.
 
@@
 	\end{align*}
-Replacing $t = (\epsilon + c - 1)/\epsilon$, we see that $t$ can attain any real value for some value of $c$, and so we deduce the required $L_1$ norm condition on quasi-distributions $\w, \w'$.
+Replacing $t = (\epsilon + c - 1)/\epsilon$, we see that $t$ can attain any real value for $c \in \mathbb{R}$, so we deduce the required $L_1$--norm condition on quasi-distributions $\w, \w'$.
 \end{proof}
@@
 We prove the following result connecting majorization to relative majorization~\cite{cit:horodecki2, Brandao_2015,  cit:lostaglio}.
-\begin{lemma}
+\begin{proposition}\label{relmaj2maj}
 	Let $\w\in \mathbb{R}^N, \w'\in \mathbb{R}^{N'}$ be quasi-distributions and $\r\in \mathbb{R}^N, \r'\in \mathbb{R}^{N'}$ probability distributions with positive rational entries given by $r_i = a_i/K$ and $r_i' = a_i'/K$ for positive integers $a_i, a_i'$ and $K = \sum_{i=1}^N a_i = \sum_{i=1}^{N'} a_i'$.
@@
 \begin{equation}
-	\Gamma_{\bma}(\bmz) := \bigoplus_{i=1}^N x_i \eta_{a_i},
+	\Gamma_{\bma}(\bmz) \coloneqq \bigoplus_{i=1}^N x_i \eta_{a_i},
 \end{equation}
 with $\eta_{a_i} = (1/a_i, 1/a_i, \dots, 1/a_i)$ the uniform distribution on $a_i$ elements.
-\end{lemma}
+\end{proposition}
 \begin{proof}
@@
 Suppose there is a stochastic map $A$ such that $A\w=\w'$ and $A\r = \r'$. 
-We define $B:\mathbb{R}^K \mapsto \mathbb{R}^K$ by $B := \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1}$ so that it is stochastic as a composition of stochastic maps and it preserves the uniform distribution in $\mathbb{R}^K$, since
+We define $B:\mathbb{R}^K \mapsto \mathbb{R}^K$ by $B \coloneqq \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1}$ so that it is stochastic as a composition of stochastic maps and it preserves the uniform distribution in $\mathbb{R}^K$, since
 \begin{align}
@@
 Conversely, suppose a bistochastic map $B$ exists sending $\Gamma_{\bma}(\w)$ to $\Gamma_{\bma'}(\w')$.
-Again, define $A: \mathbb{R}^N \mapsto \mathbb{R}^{N'}$ by $A := \Gamma_{\bma'}^{-1} \circ B \circ \Gamma_{\bma}$ so that it is stochastic as a composition of stochastic maps and $A \w = \big( \Gamma_{\bma'}^{-1} \circ B \circ \Gamma_{\bma} \big) \w = \w'$, as well as $A \r = \r'$.
+Again, define $A: \mathbb{R}^N \mapsto \mathbb{R}^{N'}$ by $A \coloneqq \Gamma_{\bma'}^{-1} \circ B \circ \Gamma_{\bma}$ so that it is stochastic as a composition of stochastic maps and $A \w = \big( \Gamma_{\bma'}^{-1} \circ B \circ \Gamma_{\bma} \big) \w = \w'$, as well as $A \r = \r'$.
 \end{proof}
 We note that the vectors $\r, \r'$ with rational components form a dense subset of the positive probability distributions, and do not consider further technicalities that have no impact on actual physical measurements, which always have a finite resolution.
+
 \subsection{Component-multiplicity pairs}
@@
 
-In general, a $1$--copy $d$--dimensional state $\rho$ is described by its $d^2$--dimensional Wigner distribution $\W{\rho}(\bmz)$. 
-The distribution $\W{\rho}(\bmz)$ is defined on the phase space, but it can be convenient to re-express this using vector notation.
+In general, a $1$--copy $d$--dimensional state $\rho$ is described by its $d^2$--dimensional Wigner distribution $\W{\rho}$. 
+The distribution $\W{\rho}$ is defined on the phase space, but it can be convenient to re-express this using vector notation.
 We discuss this in terms of Wigner distributions, but there is nothing to prevent the discussion from applying to rescaled Wigner distributions as well.
@@
 
-As an example, for the Strange state $\rho_S := \rho_S(\epsilon=0)$ with
-\begin{equation}
-W_{\rho_S}(\bmz) = (-1/3, 1/6,  1/6,  1/6,  1/6,  1/6,  1/6,  1/6,  1/6)
+As an example, for the Strange state $\rho_S \coloneqq \rho_S(\epsilon=0)$ with
+\begin{equation}
+\hspace{-5pt} W_{\rho_S} = (-1/3, 1/6,  1/6,  1/6,  1/6,  1/6,  1/6,  1/6,  1/6)
 \end{equation}
@@
 However, we might also wish more freedom and not require that the different $w_i$ values are all distinct.
-For example, the component-multiplity pairs $\{(-1/3, 1), (1/6, 2), (1/6, 3), (1/6, 3)\}$ also describe $W_{\rho_S}(\bmz)$.
+For example, the component-multiplity pairs $\{(-1/3, 1), (1/6, 2), (1/6, 3), (1/6, 3)\}$ also describe $W_{\rho_S}$.
 
 This representation is more compact when a Wigner distribution has a lot of multiplicities, and allows for simple handling of multiple copies via the following fact.
-\begin{lemma}
+\begin{proposition}
 Consider two Wigner distributions $\W{\rho_A}(\bmz_A), \W{\rho_B}(\bmz_B)$ with component-multiplicity pairs 
@@
 respectively. Then, $\{(w_i w_j', m_i m_j')\}$ gives component-multiplicity pairs for $\W{\rho_A \otimes \rho_B}(\bmz_A \oplus \bmz_B)$.
-\end{lemma}
+\end{proposition}
 \begin{proof}
@@
 \end{proof}
-The above result also applies when we consider re-scaled Wigner distributions, crucially due to the multiplicativity result shown in~\cref{prop:rescaled_multi}.
+The above result also applies when we consider rescaled Wigner distributions, crucially due to the multiplicativity result shown in Proposition~\ref{prop:rescaled_multi}.
 
@@
 For this, we have the following result, which follows from combinatorics.
-\begin{lemma}\label{lem:ncopycomponents}
-	Suppose $W_\rho(\bmz)$ has a set of $D$ component-multiplicity pairs $\{(w_i, m_i)\}$.
-Then, $W_{\rho^{\otimes n}} (\bmz)$ has component-multiplicity pairs $\{(W_{\q}, M_{\q})\}$, with index $\q$ running through all vectors $(q_1, \dots, q_D)$, where $q_1, \dots, q_D$ are non-negative integers that sum to $n$, and
+\begin{proposition}\label{ncopycomponents}
+	Suppose $W_\rho$ has a set of $D$ component-multiplicity pairs $\{(w_i, m_i)\}$.
+Then, $W_{\rho^{\otimes n}}$ has component-multiplicity pairs $\{(W_{\q}, M_{\q})\}$, with index $\q$ running through all vectors $(q_1, \dots, q_D)$, where $q_1, \dots, q_D$ are non-negative integers that sum to $n$, and
 \begin{align}
@@
 \begin{equation}
-	\binom{n}{q_1,q_2, \dots, q_d} := \frac{n!}{q_1!\dots q_D!}.
-\end{equation}
-\end{lemma}
+	\binom{n}{q_1,q_2, \dots, q_d} \coloneqq \frac{n!}{q_1!\dots q_D!}.
+\end{equation}
+\end{proposition}
 \begin{proof}
@@
 \end{equation*}
-Therefore, $\{ (W_{\bmk}, M_{\bmk}) \}_{\bmk \in C_D^1}$ is a complete set of component-multiplicity pairs for $W_\rho(\bmz)$.
-
-	Assume that $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$ as given in~\cref{eq:M,eq:W} is a complete set of component-multiplicity pairs for the $n$--copy distribution $W_{\rho^{\otimes n}}(\bmz) = W_{\rho}(\bmz)^{\otimes n}$.
-	By construction, the distribution $W_{\rho}(\bmz)^{\otimes (n+1)} = W_{\rho}(\bmz)^{\otimes n} \otimes W_{\rho}(\bmz)$, so it admits the complete set of component multiplicity pairs
+Therefore, $\{ (W_{\bmk}, M_{\bmk}) \}_{\bmk \in C_D^1}$ is a complete set of component-multiplicity pairs for $W_\rho$.
+
+	Assume that $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$ as given in Eqs.~(\ref{eq:W}, \ref{eq:M}) is a complete set of component-multiplicity pairs for the $n$--copy distribution $W_{\rho^{\otimes n}} = W_{\rho}^{\otimes n}$.
+	By construction, the distribution $W_{\rho}^{\otimes (n+1)} = W_{\rho}^{\otimes n} \otimes W_{\rho}$, so it admits the complete set of component multiplicity pairs
 \begin{equation}
@@
 
-	Consider the component sum of the distribution $W_{\rho}(\bmz)^{\otimes (n+1)}$,
+	Consider the component sum of distribution $W_{\rho}^{\otimes (n+1)}$,
 \begin{align*}
@@
 \begin{align*}
-	\sum_{\bmq \in C_D^{n+1}}  \hspace{-6pt} M_{\bmq} =  \hspace{-10pt} \sum_{\bmq \in C_D^{n+1}} \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i} = 
-	\left( \sum_{i=1}^D m_i \right)^{n+1} \hspace{-10pt} = d^{2(n+1)},
+	\sum_{\bmq \in C_D^{n+1}}  \hspace{-6pt} M_{\bmq} &=  \hspace{-10pt} \sum_{\bmq \in C_D^{n+1}} \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i} = \left( \sum_{i=1}^D m_i \right)^{n+1} \hspace{-10pt} \\
+	&= d^{2(n+1)},
 \end{align*}
-which is the dimension of $W_{\rho}(\bmz)^{\otimes (n+1)}$.
-
-Therefore, $\{ (W_{\bmq}, M_{\bmq}) \}_{\bmq \in C_D^{n+1}}$ contains exactly the components of $W_{\rho}(\bmz)^{\otimes n}$, completing the proof.
-\end{proof}
-Once again, the above result applies on re-scaled Wigner distributions as well.
+which is the dimension of $W_{\rho}^{\otimes (n+1)}$.
+
+Therefore, $\{ (W_{\bmq}, M_{\bmq}) \}_{\bmq \in C_D^{n+1}}$ contains exactly the components of $W_{\rho}^{\otimes n}$, completing the proof.
+\end{proof}
+Once again, the above result applies on rescaled Wigner distributions as well.
 
@@
 
-We first prove the following result on the relation between majorization in a particular sub-theory $\R_\sigma$ and mana, which was stated in~\cref{sec:monotones_frag}.
+We first prove the following result on the relation between majorization in a particular sub-theory $\R_\sigma$ and mana, which was stated in Sec.~\ref{sec:monotones_frag}.
 \begingroup
@@
 	We denote the Wigner distributions of the states single-component vectors $\w(\rho)=W_\rho(\z)$ and $ \w(\sigma)=W_\sigma(\z)$. Likewise, we write $\w(\rho|\sigma) = W_{\rho|\tau}(\bmz)$.
-	We choose the component indexing so that $\w(\rho|\sigma)^\downarrow = \w(\rho|\sigma)$ and so the components are sorted in non-increasing order.
+	We choose the component indexing so that $\w(\rho|\sigma)^\downarrow = \w(\rho|\sigma)$, so the components are sorted in non-increasing order.
 
@@
 	\begin{align}
-	L_\star &:=	\lc{\rho}{\sigma}(x_{i_\star}) 
+	L_\star &\coloneqq	\lc{\rho}{\sigma}(x_{i_\star}) 
 		= \sum\limits_{\bmz: \W[\bmz]{\rho} \geq 0}\hspace{-5pt} \W[\bmz]{\rho} \nonumber \\
@@
 We now prove a simple majorization constraint, arising by considering only the part of the Lorenz curves between the origin $(0,0)$ and the first elbow.
-\begin{proposition}\label{prop:first_elb}
+\begin{proposition}[First elbow constraint]\label{prop:first_elb}
 	Consider a magic state process $\rho \longrightarrow \rho'$ with input and output Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\rho'}{\sigma'}(x)$ and denote the coordinates of the first elbow of $L_{\rho|\sigma}(x)$ by $(X_0, L_0)$ and the coordinates of the first elbow of $L_{\rho' |\sigma'}(x)$ by $(X'_0, L'_0)$.
@@
 	Since both these linear segments start at the origin, this condition is equivalent to the slope of the initial segment of the input Lorenz curve being greater than or equal to the slope of the initial segment of the output Lorenz curve.
-	This slope constraint is then equivalent to~\cref{eq:first_elb_bound1}. \end{proof}
-
-The following result, referenced in~\cref{sec:major_frag}, reduces the Lorenz curve condition on the interval $[0,1]$ to a finite set of independent inequalities and can therefore simplify the computation of relative majorization constraints in practical scenarios.
+	This slope constraint is then equivalent to Eq.~(\ref{eq:first_elb_bound1}). \end{proof}
+
+The following result, referenced in Sec.~\ref{sec:major_frag}, reduces the Lorenz curve condition on the interval $[0,1]$ to a finite set of independent inequalities and can therefore simplify the computation of relative majorization constraints in practical scenarios.
 \begin{proposition}\label{thm:elbows}
@@
 \end{align}
-However, since $L_{\rho'|\sigma'}(x)$ is linear between $x_i$ and $x_{i+1}$, the above conditions imply that $L_{\rho|\sigma}(x)$ is not concave, which contradicts~\cref{L-concave}. 
+However, since $L_{\rho'|\sigma'}(x)$ is linear between $x_i$ and $x_{i+1}$, the above conditions imply that $L_{\rho|\sigma}(x)$ is not concave, which contradicts Proposition~\ref{L-concave}.
 Therefore, $L_{\rho|\sigma}(x) \geq L_{\rho'|\sigma'}(x)$ for all $x$ in $[0,1]$.
@@
 \end{align}
-In~\cref{app:lcsu_coord}, we will use $\Phi_+$ and $\Phi_-$ to express the elbow coordinates of Lorenz curves for unital protocols.
+In Appendix~\ref{app:lcsu_coord}, we will use $\Phi_+$ and $\Phi_-$ to express the elbow coordinates of Lorenz curves for unital protocols.
 
@@
 They are symmetric about $p=1/2$ and $q=1/2$, namely $S(p) = S(1-p)$ and $\ent{p}{q} = \ent{1-p}{1-q}$. We also have the entropic bounds
-\begin{lemma}\label{lem:comb_bounds}
+\begin{proposition}\label{comb_bounds}
 	For all $\ell\in [1,n-1]$,
@@
 	\end{align}
-\end{lemma}
+\end{proposition}
 The proof provided in~\cite{cit:ash} proceeds with direct calculation for the edge cases $\ell = 1,2, n-1, n-2$ and use of Stirling's approximation for the remaining cases.
-The bounds in~\cref{lem:comb_bounds} can be directly inserted into the expressions of functions $\Phi_+$ and $\Phi_-$ to derive strict upper and lower bounds.
+The bounds in Proposition~\ref{comb_bounds} can be directly inserted into the expressions of functions $\Phi_+$ and $\Phi_-$ to derive strict upper and lower bounds.
 
@@
 The cumulative function $\Phi$ obeys the following bounds, which are proven in~\cite{cit:ash}.
-\begin{lemma}\label{lem:phi_bounds}
+\begin{proposition}\label{phi_bounds}
 	Given fixed $n>0$ and $p$, $\Phi$ satisfies the following bounds:
@@
 	\end{align*}
-\end{lemma}
+\end{proposition}
 
@@
 
-The Wigner distribution of the $n$--copy $\epsilon$--noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ is given by $\W{\rho_{\rm{S}}(\epsilon)^{\otimes n}} = W_{\rho_{\rm{S}}(\epsilon)}^{\otimes n}$ and, using~\cref{lem:ncopycomponents} for unital protocols, we can associate it with a set $\{(w_i, m_i)\}_{i=0,\dots,n}$ of component-multiplicity pairs, the elements of which are presented in~\cref{tab:lcsu} for all different combinations of physical parameters $n, \epsilon$.
+The Wigner distribution of the $n$--copy $\epsilon$--noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ is given by $\W{\rho_{\rm{S}}(\epsilon)^{\otimes n}} = W_{\rho_{\rm{S}}(\epsilon)}^{\otimes n}$ and, using Proposition~\ref{ncopycomponents} for unital protocols, we can associate it with a set $\{(w_i, m_i)\}_{i=0,\dots,n}$ of component-multiplicity pairs, the elements of which are presented in Table~\ref{tab:lcsu} for all different combinations of physical parameters $n, \epsilon$.
 We split the values of index $i$ into two intervals, defined precisely as
@@
 As a result, every Strange state Lorenz curve for a unital protocol contains $n$ elbows. In the case of accidental degeneracies among Wigner components, some of these elbows may be straightened out.
-Including the boundary points $(x_{-1}, L_{-1}) := (0,0)$ and $(x_{n}, L_{n}) := (1,1)$, we label these elbows as 
+Including the boundary points $(x_{-1}, L_{-1}) \coloneqq (0,0)$ and $(x_{n}, L_{n}) \coloneqq (1,1)$, we label these elbows as 
 \begin{equation*}
@@
 
-In~\cref{tab:lcsu_coord_elb_app}, we present the elbow coordinates of the $n$-copy, $\epsilon$--noisy Strange state Lorenz curve for a unital protocol for any combination of physical parameters $n, \epsilon$.
+In Table~\ref{tab:lcsu_coord_elb_app}, we present the elbow coordinates of the $n$-copy, $\epsilon$--noisy Strange state Lorenz curve for a unital protocol for any combination of physical parameters $n, \epsilon$.
 \begin{table}[h]
@@
   \begin{tabular}{c|c|c|r|r}
-%\multicolumn{2}{c|}{\multirow{2}{*}{Case}} & \multicolumn{1}{c|}{LHS} & \multicolumn{1}{c|}{$x_{i}$} & \multicolumn{1}{c}{$L_{i}$} \\
-%    \multicolumn{2}{c|}{} & \multicolumn{1}{c|}{RHS} & \multicolumn{1}{c|}{$x_{i} - x_{\lfloor n/2 \rfloor}$} & \multicolumn{1}{c}{$L_{i} - L_{\lfloor n/2 \rfloor}$} \\[0.5ex]
 \hline 
@@
 \end{align}
-for $j = 1,\dots,m_{i}$ and $i=0,\dots,n$, where multiplicities $m_i$ are given in~\cref{tab:lcsu}.
+for $j = 1,\dots,m_{i}$ and $i=0,\dots,n$, where multiplicities $m_i$ are given in Table~\ref{tab:lcsu}.
 
@@
 \begin{equation}
-	R \leq \dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (\phi - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (\phi' - F')},
+	R \leq \dfrac{\log \big( 1-\frac{4}{3}\epsilon \big) + \beta (\phi - F)}{\log \big( 1-\frac{4}{3}\epsilon' \big) + \beta (\phi' - F')},
 \end{equation}
@@
 
-\begin{proof}	\label{thm:free-energy-bound-proof}
+\begin{proof}
 	For the sake of clarity, we write $\rho_n \coloneqq \rho_S(\epsilon)^{\otimes n}$, $\rho'_m \coloneqq \rho_S(\epsilon')^{\otimes m}$, $\tau_n \coloneqq \tau^{\otimes m}$ and $\tau'_m \coloneqq \tau'^{\otimes m}$.
@@
 
-The points defining the Lorenz curve $L_{\rho_n |\tau_n}(x)$ are obtained from sorting the components of $W_{\rho_n |\tau_n}(\bmz)$ in non-increasing order and then computing the partial sums of $W_{\rho_n |\tau_n}(\pi(\bmz))$ where $\pi$ is the permutation that realises the sorting.
-However, similar to the unital protocol analysis, we use the slope constraint (\cref{prop:first_elb}) obtained by considering the line segments connecting the origin to the first elbow of both Lorenz curves.
+The points defining the Lorenz curve $L_{\rho_n |\tau_n}(x)$ are obtained from sorting the components of $W_{\rho_n |\tau_n}(\bmz)$ in non-increasing order and then computing the partial sums of $W_{\rho_n |\tau_n}(\pi(\bmz))$ where $\pi$ is the permutation that realizes the sorting.
+However, similar to the unital protocol analysis, we use the slope constraint (Proposition~\ref{prop:first_elb}) obtained by considering the line segments connecting the origin to the first elbow of both Lorenz curves.
 
@@
 
-The rescaled distribution components for this transformed state are given by
-\begin{equation}
-	W_{\rho_n|\tau_n} = \left(\frac{-v}{W_{\tau}(\bmz_\star)}\right)^{i_{\bmz_\star}} \prod_{\bmz \neq \bmz_\star} \left(\frac{u}{W_{\tau}(\bmz)}\right)^{i_{\bmz}},
+The components of the rescaled distribution $W_{\rho_n|\tau_n}$ for this transformed state are given by
+\begin{equation}
+	\left(\frac{-v}{W_{\tau}(\bmz_\star)}\right)^{i_{\bmz_\star}} \prod_{\bmz \neq \bmz_\star} \left(\frac{u}{W_{\tau}(\bmz)}\right)^{i_{\bmz}},
 \end{equation}
@@
 \begin{align}
-\alpha_k := \<E_k |A_{\bmz_\star} |E_k\> \\
-\zeta :=  \sum_{k \in \mathbb{Z}_3} \alpha_k e^{-\beta E_k},
-\end{align}
-and a `magic free energy' term $\phi := -\beta^{-1} \log \zeta$.
+\alpha_k \coloneqq \<E_k |A_{\bmz_\star} |E_k\> \\
+\zeta \coloneqq  \sum_{k \in \mathbb{Z}_3} \alpha_k e^{-\beta E_k},
+\end{align}
+and a `magic free energy' term $\phi \coloneqq -\beta^{-1} \log \zeta$.
 Therefore, the coordinates can be expressed as
@@
 \end{equation}
-The output states obey the same conditions and so we also have the first point coordinates of the output Lorenz curve given by
+The output states obey the same conditions, so we also have the first point coordinates of the output Lorenz curve given by
 \begin{equation}
@@
 If the largest rescaled component of a state is distinct with no multiplicities, then these coordinates correspond to the first elbow of the corresponding Lorenz curve, whereas if it appears multiple times, then the coordinates derived correspond to a point on the interior of the line segment connecting the origin to the first elbow.
-In both cases, the distillation bound remains the same, as is clear by its derivation in~\cref{prop:first_elb}, given by $L_0/x_0 \geq L'_0/x'_0$, leading to
+In both cases, the distillation bound remains the same, as is clear by its derivation in Proposition~\ref{prop:first_elb}, given by $L_0/x_0 \geq L'_0/x'_0$, leading to
 \begin{equation}
@@
 \begin{equation}
-	\frac{m}{n} \leq \dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (\phi - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (\phi' - F')},
+	\frac{m}{n} \leq \dfrac{\log \big( 1-\frac{4}{3}\epsilon \big) + \beta (\phi - F)}{\log \big( 1-\frac{4}{3}\epsilon' \big) + \beta (\phi' - F')},
 \end{equation}
@@
 \begin{align}
-\phi &= -\beta^{-1}\ln (\sum_k \alpha_k e^{-\beta E_k}) \nonumber \\
-&=E_{k_{\star}} -kT \ln (d W_{|E_{k_\star}\>\<E_{k_\star}|}(\bmz_{\star})) =E_{k_{\star}}.
+\phi &= -\beta^{-1}\log (\sum_k \alpha_k e^{-\beta E_k}) \nonumber \\
+&=E_{k_{\star}} \hspace{-2pt}-\hspace{1pt} kT \log (d W_{|E_{k_\star}\>\<E_{k_\star}|}(\bmz_{\star})) =E_{k_{\star}}.
 \end{align}
@@
 	\begin{cases}
-		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F')},\ &\epsilon \leq \epsilon_\star, \epsilon' \leq \epsilon'_\star, \vspace{10pt}\\
-		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F')},\ &\epsilon \leq \epsilon_\star, \epsilon' > \epsilon'_\star, \vspace{10pt}\\
-		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E'_s - F')},\ &\epsilon > \epsilon_\star, \epsilon' \leq \epsilon'_\star, \vspace{10pt}\\
-		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E'_{\rm{max}} - F')},\ &\epsilon > \epsilon_\star, \epsilon' > \epsilon'_\star,
+		\dfrac{\ln \big( 1-\frac{4}{3}\epsilon \big) + \beta (E_s - F)}{\ln \big( 1-\frac{4}{3}\epsilon' \big) + \beta (E'_s - F')},\ &\epsilon \leq \epsilon_\star, \epsilon' \leq \epsilon'_\star, \vspace{10pt}\\
+		\dfrac{\ln \big( 1-\frac{4}{3}\epsilon \big) + \beta (E_s - F)}{\ln \big( \frac{1}{2}-\frac{1}{6}\epsilon' \big) + \beta (E'_{\rm{max}} - F')},\ &\epsilon \leq \epsilon_\star, \epsilon' > \epsilon'_\star, \vspace{10pt}\\
+		\dfrac{\ln \big( \frac{1}{2}-\frac{1}{6}\epsilon \big) + \beta (E_{\rm{max}} - F)}{\ln \big( 1-\frac{4}{3}\epsilon' \big) + \beta (E'_s - F')},\ &\epsilon > \epsilon_\star, \epsilon' \leq \epsilon'_\star, \vspace{10pt}\\
+		\dfrac{\ln\big( \frac{1}{2}-\frac{1}{6}\epsilon \big) + \beta (E_{\rm{max}} - F)}{\ln \big( \frac{1}{2}-\frac{1}{6}\epsilon' \big) + \beta (E'_{\rm{max}} - F')},\ &\epsilon > \epsilon_\star, \epsilon' > \epsilon'_\star,
 	\end{cases}
@@
 \begin{proof}
-The proof proceeds in the same manner as in~\cref{thm:free-energy-bound-proof} up to the point where we need to evaluate $W_{\rho_n |\tau_n} (\bmz)$ and $W_{\rho_n}(\bmz)$ explicitly, beyond which we do not have the freedom of additional Clifford processing.
+The proof proceeds in the same manner as in Theorem~\ref{thm:free-energy} up to the point where we need to evaluate $W_{\rho_n |\tau_n} (\bmz)$ and $W_{\rho_n}(\bmz)$ explicitly, beyond which we do not have the freedom of additional Clifford processing.
 
@@
 Therefore, $C$ maps $\tau$ to another stabilizer state that is diagonal in the computational basis, and we can assume without loss of generality that $\tau$ is diagonal in $\{|0\>,|1\>, |2\>\}$.
-However, this re-definition of the computational basis means that the coordinates on the discrete phase space are also permuted, so the negative Wigner component $-v(\epsilon)$ of the Strange state is in a new position.
+This re-definition of the computational basis means that the coordinates on the discrete phase space are also permuted, so the negative Wigner component $-v(\epsilon)$ of the Strange state is in a new position.
 We denote by $E_s$ the eigenvalue of $H$ where the associated eigenvector has Wigner distribution overlapping the negative component of the state $C\rho_S(\epsilon)C^\dagger$ in the original phase space, hence also of the state Strange state $\rho_S(\epsilon)$ in the re-defined phase space.
@@
 It has $9$ components, but these come with multiplicities.
-In total, there are four distinct values on the phase space, as illustrated in~\cref{fig:pd_split}.
+In total, there are four distinct values on the phase space, as illustrated in Fig.~\ref{fig:pd_split}.
 \begin{figure}[h]
@@
     Here, the negative component of the magic state overlaps the Wigner distribution of $|0\>$.
-The rescaled distribution attains a single value in each of the four regions, proportional to the value depicted in the region, see~\cref{eq:bmw_rescaled}.
+The rescaled distribution attains a single value in each of the four regions, proportional to the value depicted in the region, see Eq.~(\ref{eq:bmw_rescaled}).
     }
@@
 
-We denote by $\w(\rho), \w(\rho|\tau)$ the unique values occurring in $W_\rho(\bmz), W_{\rho|\tau}(\bmz)$ respectively and $\bmm$ the vector of associated multiplicities of each value in $W_\rho(\bmz)$.
-The component values and multiplicities of the relevant distributions in the four distinct regions are given by
-\begin{align}
+We define vectors $\w(\rho), \w(\tau), \w(\rho|\tau)$ based on the values occurring in $W_\rho, W_\tau, W_{\rho|\tau}$ respectively and $\bmm$ as the vector of associated multiplicities of each value in $W_\rho(\bmz)$.
+Specifically, the component values and multiplicities of the relevant distributions in the four distinct regions are given by
+\begin{align}
+		\bmm &\coloneqq (1,2,3,3), \\
 	\w(\rho) &\coloneqq (-v, u, u, u), \\
-		\bmm &\coloneqq (1,2,3,3), \\
 	\w(\tau) &\coloneqq \frac{1}{3\Z} \left( e^{-\beta E_0}, e^{-\beta E_0}, e^{-\beta E_1}, e^{-\beta E_2} \right), \\
-	\w(\rho_{\rm{S}} | \tau) &\coloneqq 3\Z \left( -v e^{\beta E_0}, u e^{\beta E_0}, u e^{\beta E_1}, u e^{\beta E_2} \right). \label{eq:bmw_rescaled}
-\end{align}
-
-Using this notation, the values and multiplicities of the $n$--copy distribution $\bmw(\rho_n |\tau_n)$ are computed in~\cref{lem:ncopycomponents}. The values are given by 
+	\w(\rho | \tau) &\coloneqq 3\Z \left( -v e^{\beta E_0}, u e^{\beta E_0}, u e^{\beta E_1}, u e^{\beta E_2} \right). \label{eq:bmw_rescaled}
+\end{align}
+
+Using this notation, the values and multiplicities of the $n$--copy distribution $\bmw(\rho_n |\tau_n)$ are computed in Proposition~\ref{ncopycomponents}. The values are given by 
 \begin{align}\label{eq:ncopy_w_rescaled}
@@
 
-In order to construct the $n$--copy Lorenz curve $L_{\rho_n|\tau_n}(x)$ we need to order the components of the distribution, $w(\rho_{\rm{S}} | \tau)_{ijk}$ in decreasing order, and identify the sequence of indices that give us $W_{\rho_n}(\pi(\bmz))$.
-
-However, it again suffices to use only the constraint from the first elbow $(x_0, L_0)$ of $L_{\rho_n|\tau_n}(\bmz)$. We therefore compute the largest component 
+In order to construct the $n$--copy Lorenz curve $L_{\rho_n|\tau_n}(x)$ we need to order the components of the distribution, $w(\rho | \tau)_{ijk}$ in decreasing order, and identify the sequence of indices that give us $W_{\rho_n}(\pi(\bmz))$.
+
+However, in order to obtain a non-trivial bound, it again suffices to use the constraint from the first elbow $(x_0, L_0)$ of $L_{\rho_n|\tau_n}(\bmz)$. We therefore compute the largest component 
 \begin{equation}
@@
 
-Given an even value for $\alpha$, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_s}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
+Given an even value for $\alpha$, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_s}$ is fixed, so the expression is maximized by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
 Hence, we have
@@
 such that for the regime $0 \leq \beta \leq \beta_\star$ a threshold error $\epsilon_\star$ exists, and for $\beta > \beta_\star$ no such transition exists, so we choose $\epsilon_\star = 0$. 
-Therefore, the transition value for the noise is given by
+Therefore, the transition value for the error is given by
 \begin{equation}
@@
 \end{equation}
-There are four combinations of coordinates, depending on the noise parameters $\epsilon, \epsilon'$ for the input and output states.
-In each of these combinations, we simply use the first elbow constraint, as described in~\cref{prop:first_elb}, and manipulate the coordinates as in the proof of~\cref{thm:free-energy}, leading to the bounds in the statement of the theorem.
+There are four combinations of coordinates, depending on the error parameters $\epsilon, \epsilon'$ for the input and output states.
+In each of these combinations, we simply use the first elbow constraint, as described in Proposition~\ref{prop:first_elb}, and manipulate the coordinates as in the proof of Theorem~\ref{thm:free-energy}, leading to the bounds in the statement of this theorem.
 \end{proof}
@@
 
-In this section, we analyse R\'{e}nyi entropies on quasi-probabilities and use them to get magic distillation bounds.
+In this section, we analyse R\'{e}nyi entropies on quasi-distributions and use them to get magic distillation bounds.
 
@@
 \begin{equation}
-	D_\infty(W_\rho || W_\tau) := \log  \max_{\bmz} \frac{W_\rho(\bmz)}{W_\tau(\bmz)},
+	D_\infty(W_\rho || W_\tau) \coloneqq \log  \max_{\bmz} \frac{W_\rho(\bmz)}{W_\tau(\bmz)},
 \end{equation}
@@
 
-If we now let $\w = W_{\rho|\tau}(\bmz) := W_{\rho}(\bmz) /W_{\tau}(\bmz)$ we have
+If we now let $\w = W_{\rho|\tau}(\bmz) \coloneqq W_{\rho}(\bmz) /W_{\tau}(\bmz)$ we have
 \begin{equation}
@@
 \begin{equation}
-	\mathcal{D}^\downarrow := \{ \w \in \mathcal{D} : w_1 \ge w_2 \ge \cdots \ge w_N\}.
+	\mathcal{D}^\downarrow \coloneqq \{ \w \in \mathcal{D} : w_1 \ge w_2 \ge \cdots \ge w_N\}.
 \end{equation}
@@
 We now have the following fundamental result in majorization theory.
-\begin{theorem}[Schur-Ostrowski theorem~\cite{Schur_1923, Ostrowski_1952, cit:marshall}] Let $\D\subseteq \mathbb{R}^N$ be a convex set with non-empty interior, and invariant under permutations of vector components.
+\begin{theorem}[Schur-Ostrowski theorem~\cite{Schur_1923, Ostrowski_1952, cit:marshall}] 
+	Let $\D\subseteq \mathbb{R}^N$ be a convex set with non-empty interior, and invariant under permutations of vector components.
 Let $f: \D \rightarrow \mathbb{R}$ be a continuously differentiable function on the interior of $\D$ and continuous on the whole of $\D$.
@@
 Since the set $\mathcal{Q}_N$ of quasi-distributions obey the necessary conditions, we get the following result:
-\begin{lemma}
+\begin{theorem}
 	Let $f$ be a real-valued continuous function defined on $\mathcal{Q}_N$ that is continuously differentiable on the interior of $\mathcal{Q}_N$. 
@@
 for all quasi-distributions $\w$ in the interior of $\mathcal{Q}^\downarrow_N$.
-\end{lemma}
+\end{theorem}
 
@@
 \begin{equation}
-	H_\alpha(\p) := \frac{1}{1-\alpha} \log \sum_i p_i^\alpha,
+	H_\alpha(\p) \coloneqq \frac{1}{1-\alpha} \log \sum_i p_i^\alpha,
 \end{equation}
@@
 This means the function is well-defined on $\mathcal{Q}_N^+$, namely the set of quasi-distributions with non-negative components.
-We wish to extend the domain to the whole of $\mathcal{Q}_N$, however this requires that $w_i^\alpha$ be a real-number for any $w_i \in \mathbb{R}$.
+We wish to extend the domain to the whole of $\mathcal{Q}_N$, but this requires that $w_i^\alpha$ be a real number for any $w_i \in \mathbb{R}$.
 
 The exponent function $x \mapsto x^\alpha$ is well-defined and real-valued if $\alpha$ is a rational number of the form $\alpha = r / s$ where $s$ is an odd integer and $r \in \mathbb{N}$.
-However, we also require that $\sum_i w_i^\alpha > 0$ in order for the logarithm to return a real-value.
-To ensure this happens we take $\alpha = r/s$ with $r=2a$ being an even integer and $s=2b-1$ being an odd integer, for some integers $a,b\in  \mathbb{N}$, which implies that the following are all real-valued expressions,
-\begin{equation}
+However, we also require that $\sum_i w_i^\alpha > 0$ in order for the logarithm to return a real value.
+To ensure this, we restrict to $\alpha = r/s$ with $r=2a$ being an even integer and $s=2b-1$ being an odd integer, for some integers $a,b\in  \mathbb{N}$, which implies that the following are all well-defined, real-valued expressions,
+\begin{equation*}
 	0 \le w_i^\alpha = w_i^{\frac{2a}{2b-1}} = \left (w_i^{\frac{1}{2b-1}}\right )^{2a} =\left (w_i^{2a}\right )^{\frac{1}{2b-1}} = |w_i|^{\frac{2a}{2b-1}}.
-\end{equation}
-We note that previous work \ddd{[CITE Phys.
-Rev E 62, 4665 (2000)]} has considered the $\alpha=2$ entropy of Wigner distributions, and other work exists that uses the Wehrl entropy, based on the Hussimi function of a quantum state \ddd{[CITE Gnutzmann \& Zyczkowski: R\'{e}nyi-Wehrl entropies as measures of localization in phase space, J.
-Phys.
-A 34 10123]}.
+\end{equation*}
+We note that previous work~\cite{Manfredi_2000} has considered the $\alpha=2$ entropy of Wigner distributions, and other work exists that uses the Wehrl entropy, based on the Hussimi function of a quantum state~\cite{Gnutzmann_2001}.
 
@@
 \end{equation}
-The first derivative of the function $g(w) := -w^{\alpha - 1}$ is given by
+The first derivative of the function $g(w) \coloneqq -w^{\alpha - 1}$ is given by
 \begin{equation}
@@
 \begin{equation}
-	w^{\frac{2a-4b+2}{2b-1}} = \left(w^{2a-4b+2}\right)^{\frac{1}{2b-1}} = \left(w^{\frac{a-2b+1}{2b-1}}\right)^{2} \geq 0,
-\end{equation}
-and so $g(w)$ is non-increasing in $w$.
+	w^{\frac{2a-4b+2}{2b-1}} = \left(w^{\frac{a-2b+1}{2b-1}}\right)^{2} \geq 0,
+\end{equation}
+so $g(w)$ is non-increasing in $w$.
 
@@
 \end{equation}
-for any quasi-distributions $\w, \w' \in \mathcal{Q}_N$ that obey $\w \succ \w'$.
+for any quasi-distributions $\w, \w'$ that obey $\w \succ \w'$.
 \end{proof}
 While we have integers $a,b$ such that $0 < \alpha=\frac{2a}{2b-1} < 1$ and $H_\alpha(\w)$ is well-defined, it turns out that monotonicity does not hold if we drop the condition $a \ge b$.
-If $\alpha =2a/(2b-1)$ with $\alpha < 1$, then $g(w) := \frac{-w^{\alpha-1}}{\alpha-1}$ is no longer monotonic for all $w \in \mathbb{R}$, and the problem occurs when comparing $w_i < 0$ and $w_j >0$.
-For example the function $g(x) = \frac{1}{x^3}$ is monotone decreasing on $x<0$ and $x>0$ separately, however it is not monotone on the full real-line.
-
-We note that if $\alpha =r/s$ with both $r$ and $s$ odd, then $H_\alpha$ is not well-defined for all quasi-probabilities, however if the actual set of quasi-distributions has a sufficiently bounded levels negativity, then $\log \sum_{\bmz} W_\rho(\bmz)^\alpha$ can still be obtained for $r$ odd, provided the total sum is never negative.
-This occurs for Wigner distributions, where we have $|W_\rho(\z)| \ge 1/d$ for a $d$--dimensional quantum system.
-
-We also note that the set $F := \{2a/(2b-1): a,b \in \mathbb{N} \text{ and } a \geq b\}$ is dense in the reals $\mathbb{R}_{>1}$, as any rational $c/d$ with $c>d$ can be approximated by  $c2^n / (d2^n-1) \in F$ for sufficiently large $n$.
-
-We have that $H_{\alpha}$ is additive on products of quasi-distributions., which we state for completeness.
-\begin{lemma}\label{H_add}
+If $\alpha =2a/(2b-1)$ with $\alpha < 1$, then $g(w) \coloneqq \frac{-w^{\alpha-1}}{\alpha-1}$ is no longer monotonic for all $w \in \mathbb{R}$, and the problem occurs when comparing $w_i < 0$ and $w_j >0$.
+As an analogy, consider the function $g(x) = \frac{1}{x^3}$ which is monotone decreasing on $x<0$ and $x>0$ separately, however it is not monotone on the full real-line.
+
+We note that if $\alpha =r/s$ with both $r$ and $s$ odd, then $H_\alpha$ is not well-defined for all quasi-distributions, although if the actual set of quasi-distributions has a sufficiently bounded levels negativity, then $\log \sum_{\bmz} W_\rho(\bmz)^\alpha$ can still be obtained for $r$ odd, provided the total sum is never negative.
+This occurs for Wigner distributions, where we have $|W_\rho(\z)| \leq 1/d$ for a $d$--dimensional quantum system.
+
+We also note that the set $F \coloneqq \{2a/(2b-1): a,b \in \mathbb{N} \text{ and } a \geq b\}$ is dense in the reals $\mathbb{R}_{>1}$, as any rational $c/d$ with $c>d$ can be approximated by  $c2^n / (d2^n-1) \in F$ for sufficiently large $n$.
+
+We have that $H_{\alpha}$ is additive on products of quasi-distributions, which we state for completeness.
+\begin{proposition}\label{H_add}
 	For any $\w \in \mathcal{Q}_N$ and $\w' \in \mathcal{Q}_{N'}$, we have
@@
 	where $\alpha = 2a/(2b-1)$ with positive integers $a\ge b$.
-\end{lemma}
+\end{proposition}
 \begin{proof}
@@
 \begin{equation}
-	H_\alpha(W_\rho) := \frac{1}{1-\alpha} \log \sum_{\bmz} W_{\rho}(\bmz)^\alpha,
+	H_\alpha(W_\rho) \coloneqq \frac{1}{1-\alpha} \log \sum_{\bmz} W_{\rho}(\bmz)^\alpha,
 \end{equation}
@@
 \begingroup
-\def\thetheorem{\ref{thm:HSchur}}
+\def\thetheorem{\ref{thm:Magic}}
 \begin{theorem}
@@
 \begin{proof} 
-If we have $H_\alpha (W_\rho) <0 $ for $\alpha >1$ then this implies that $\log \sum_{\bmz} W_\rho (\bmz)^\alpha > 1$, however it is known that $H_\alpha$ is always non-negative on probability distributions and therefore $W_\rho(\bmz)$ must be a strict quasi-distribution with negativity.
+If we have $H_\alpha (W_\rho) <0 $ for $\alpha >1$, then it follows that $\log \sum_{\bmz} W_\rho (\bmz)^\alpha > 1$. 
+However, it is known that $H_\alpha$ is always non-negative on probability distributions, so $W_\rho(\bmz)$ must be a strict quasi-distribution with negativity.
 
@@
 \begin{equation}
-	D_\alpha(\w||\r) := \frac{1}{\alpha - 1} \log \sum_{i} w_i^\alpha r_i^{1-\alpha},
+	D_\alpha(\w||\r) \coloneqq \frac{1}{\alpha - 1} \log \sum_{i} w_i^\alpha r_i^{1-\alpha},
 \end{equation}
@@
 We now have the following result that relates the R\'{e}nyi divergence to the R\'{e}nyi entropy on a dense subset of probability distributions.
-\begin{theorem}\label{thm:H2D}
+\begin{proposition}\label{H2D}
 	Let $\w\in \mathcal{Q}_N$ be a quasi-distribution and $\r \in \mathcal{Q}_N^+$ a probability distribution with positive rational entries given by $r_i = a_i/K$ for positive integers $a_i$ and $K = \sum_{i=1}^N a_i$.
@@
 	where $\alpha = 2a / (2b-1)$ for positive integers $a \ge b$.
-\end{theorem}
+\end{proposition}
 \begin{proof}
@@
 With this we now establish monotonicity for R\'{e}nyi relative divergences.
-\begin{theorem}\label{thm:DSchur}
+\begin{proposition}\label{DSchur}
 	Let $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$. 
 	Then, $D_\alpha$ is Schur-convex, i.e. $D_\alpha(\w \hspace{1pt}||\hspace{1pt} \r) \geq D_\alpha(\w' \hspace{1pt}||\hspace{1pt} \r')$, whenever $(\w, \r) \succ (\w', \r')$.
-\end{theorem}
+\end{proposition}
 \begin{proof}
 	The statement $(\w, \r) \succ (\w', \r')$ is equivalent to $\Gamma_{\bma}(\w) \succ \Gamma_{\bma'}(\w')$.
-	Therefore, due to~\cref{thm:HSchur} we have
+	Therefore, due to Theorem~\ref{thm:HSchur} we have
 	\begin{equation}
@@
 	\end{equation}
-	which, due to~\cref{thm:H2D}, is equivalent to
+	which, due to Proposition~\ref{H2D}, is equivalent to
 	\begin{equation}
@@
 \end{proof}
-We now specialise to Wigner distributions of quantum states, and quantum operations that map the set of free states $\F$ into itself.
+We now specialize to Wigner distributions of quantum states, and quantum operations that map the set of free states $\F$ into itself.
 \begingroup
@@
 
-2. In the inequality of property 1, equality holds iff $L_{\rho|\tau}(x) = L_{\I/d|\I/d}(x) = L_{\tau|\tau}(x)$ for all $x\in [0,1]$ due to~\cref{prop:rmajor} which in turn holds iff $\rho = \tau$.
+2.
+In the inequality of property 1, equality holds iff $L_{\rho|\tau}(x) = L_{\I/d|\I/d}(x) = L_{\tau|\tau}(x)$ for all $x\in [0,1]$ due to Proposition~\ref{prop:rmajor} which in turn holds iff $\rho = \tau$.
 
@@
 \begin{theorem}
-	Consider a general magic state distillation process that converts a magic state $\rho^{\otimes n} \longrightarrow \E(\rho^{\otimes n})=\rho'^{\otimes m}$and let $\tau$ be any full-rank stabilizer reference state.
-Then the distillation rate $R := m/n$ is upper bounded as,
-	\begin{equation}
-		R \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{\tilde{D}_\alpha( \rho', \tau')},
-	\end{equation}
-	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ with the average divergence
-	\begin{equation}
-\tilde{D}_\alpha( \rho', \tau') := \frac{1}{m} D_\alpha (W_{\rho\prime_m} || W_{\tau'_m}),
+	Consider a general magic state distillation process on prime dimension qudits, that converts a magic state $\rho^{\otimes n} \longrightarrow \E(\rho^{\otimes n})=\rho'^{\otimes m}$and let $\tau$ be any full-rank stabilizer reference state on a qudit.
+Then the distillation rate $R \coloneqq m/n$ is upper bounded as,
+	\begin{equation}
+		R \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{\rlap{\raisebox{-0.1ex}{$\widetilde{\phantom{D}}$}}D_\alpha( \rho', \tau')}
+	\end{equation}
+	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ and the average divergence
+	\begin{equation}
+\widetilde{D}_\alpha( \rho', \tau') \coloneqq \frac{1}{m} D_\alpha (W_{\rho'^{\otimes m}} \hspace{1pt}||\hspace{1pt} W_{\tau'_m}),
 \end{equation}
@@
 \begin{proof}
-	The bound is a direct consequence of the properties of the $\alpha$--R\'{e}nyi diveregence, proven in~\cref{thm:Da_props}.
+	The bound is a direct consequence of the properties of the $\alpha$--R\'{e}nyi diveregence, proven in Theorem~\ref{thm:Da_props}.
 

### 2021-06-29 magic_paper.tex
Fixed citations. Only needs final proofreading

@@
 \input{preamble}
-
-% Proofreading --- Citations (Aberg -> {\AA}berg)
-% Proofreading --- Main text (Spacing)
-% Proofreading --- Appendices
-
-% Spacing --- figs, sections, paragraphs, eq. numbering, \noindent, QEDs
 
@@
 The approach we take is most closely aligned with resource theories of magic, although it differs in key ways.
-We obtain distillation upper bounds without the use of monotones, but instead use tools from statistical mechanics and recent work in single-shot resource theories~\cite{cit:janzing, cit:horodecki2, Brandao_2015, Vinjanampathy_2016, Goold_2016, cit:lostaglio, cit:gour}.
+We obtain distillation upper bounds without the use of monotones, but instead use tools from statistical mechanics and recent work in single-shot resource theories~\cite{cit:janzing, cit:horodecki2013, Brandao_2015, Vinjanampathy_2016, Goold_2016, cit:lostaglio, cit:gour}.
 Our analysis relies on the discrete Wigner representation of quantum systems, in which all states and operations can be described on a discrete phase space~\cite{Ferrie_2008, Okay_2021}.
@@
 Moreover, if $\w, \w', \r, \r'$ are all valid probability distributions with neither of $\r,\r'$ having negative components then it can be shown~\cite{ruch_mixing_1978} that
-\begin{equation}
+\begin{equation*}
 (\w, \r) \succ (\w', \r') \mbox{ if and only if } L_{\w |\r}(x) \ge L_{\w' |\r'}(x),
-\end{equation}
+\end{equation*}
 for all $x \in [0,1]$.
@@
 for any $a >0$ and $b \in \mathbb{R}$. This relation implies that
-\begin{align}
+\begin{align*}
 L_{\w_\epsilon |\r} (x) &\ge L_{\w'_\epsilon |\r'} (x) \nonumber \\ 
-&\mbox{ if and only if }& \nonumber \\
+&\mbox{ if and only if }& \\
 \epsilon L_{\w |\r} (x) + (1-\epsilon) x &\ge \epsilon L_{\w' |\r'} (x) + (1-\epsilon) x.
-\end{align}
+\end{align*}
 Finally, the $(1-\epsilon)x$ terms cancel on both sides and we get the required relative majorization conditions that $(\w, \r) \succ (\w', \r')$ if and only if $L_{\w | \r} (x) \ge L_{\w' | \r'}(x)$ for all $x \in [0,1]$, as required.
@@
 \begin{align}
-	\zeta &= \sum_{k\in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}, \nonumber\\
+	\zeta &= \sum_{k\in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}, \\
 	\alpha_k &= \<E_k| A_{\bmz_\star} |E_k\>,
@@
 
-If correlations in $\tau'_m$ between subsystems can be neglected then $\tau'_m = \tau'^{\otimes m}$ for some qudit state $\tau'$ we have that
+If correlations in $\tau'_m$ between subsystems can be neglected, then $\tau'_m = \tau'^{\otimes m}$ for some qudit state $\tau'$ and
 \begin{equation}
@@
 
-We prove the following result connecting majorization to relative majorization~\cite{cit:horodecki2, Brandao_2015,  cit:lostaglio}.
+We prove the following result connecting majorization to relative majorization~\cite{cit:horodecki2013, Brandao_2015,  cit:lostaglio}.
 \begin{proposition}\label{relmaj2maj}
@@
 Suppose on the contrary that $L_{\rho|\sigma}(x)$ dips below $L_{\rho'|\sigma'}(x)$ at some point $x=y$ where $x_i < y < x_{i+1}$ for some $i$. Then this implies
-\begin{align}
-L_{\rho|\sigma}(x_i) &\ge L_{\rho'|\sigma'}(x_i) \nonumber \\
-L_{\rho|\sigma}(y) & <L_{\rho'|\sigma'}(y) \nonumber \\
+\begin{align*}
+L_{\rho|\sigma}(x_i) &\ge L_{\rho'|\sigma'}(x_i) \\
+L_{\rho|\sigma}(y) & <L_{\rho'|\sigma'}(y) \\
 L_{\rho|\sigma}(x_{i+1}) &\ge L_{\rho'|\sigma'}(x_{i+1}).
-\end{align}
+\end{align*}
 However, since $L_{\rho'|\sigma'}(x)$ is linear between $x_i$ and $x_{i+1}$, the above conditions imply that $L_{\rho|\sigma}(x)$ is not concave, which contradicts Proposition~\ref{L-concave}.
@@
 	W_{\tau}(\bmz_\star) &= \frac{1}{3\Z}\tr\left[ A_{\bmz_\star}e^{-\beta H} \right] \nonumber\\
-	&= \frac{e^{\beta F}}{3} \tr\left[ A_{\bmz_\star}\sum_{k \in \mathbb{Z}_3} e^{-\beta E_k} |E_k\>\<E_k| \right] \\
+	&= \frac{e^{\beta F}}{3} \tr\left[ A_{\bmz_\star}\sum_{k \in \mathbb{Z}_3} e^{-\beta E_k} |E_k\>\<E_k| \right] \nonumber\\
 	&= \frac{e^{\beta F}}{3} \sum_{r \in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}
-	= \frac{e^{\beta F}}{3} \zeta \\
+	= \frac{e^{\beta F}}{3} \zeta \nonumber\\
 	&= \frac{e^{\beta (F - \phi)}}{3},
@@
 \begin{proof}
-	\begin{align*}
-		H_{\alpha}(\w \otimes \w') &= \frac{1}{1-\alpha}\log \sum_{i,j'} \left[\w_i \w'_j\right]^{\alpha} \\
-		&= \frac{1}{1-\alpha}\log  \left [ \sum_i\w_i^\alpha \sum_j\w_j^{\prime \alpha} \right ] \\
-				&= \frac{1}{1-\alpha}\log  \left [ \sum_i\w_i^\alpha\right ] + \frac{1}{1-\alpha}\log \left [ \sum_j\w_j^{\prime \alpha} \right ] \\
+	\begin{align}
+		H_{\alpha}(\w \otimes \w') &= \frac{1}{1-\alpha}\log \sum_{i,j'} \left[\w_i \w'_j\right]^{\alpha} \nonumber\\
+		&= \frac{1}{1-\alpha}\log  \left [ \sum_i\w_i^\alpha \sum_j\w_j^{\prime \alpha} \right ] \nonumber\\
+				&= \frac{1}{1-\alpha}\log  \left [ \sum_i\w_i^\alpha\right ] + \frac{1}{1-\alpha}\log \left [ \sum_j\w_j^{\prime \alpha} \right ] \nonumber\\
 		&= H_{\alpha}(\w) + H_{\alpha}(\w').
-	\end{align*}
+	\end{align}
 \end{proof}
@@
 \begin{equation}
-	n D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) \geq m \frac{1}{m}D_\alpha(W_{\rho'_m} \hspace{1pt}||\hspace{1pt} W_{\tau'_m}).
-\end{equation}
-
-Since $\rho'^{\otimes m} \neq \tau'_m$, we have $D_\alpha(W_{\rho'_m} \hspace{1pt}||\hspace{1pt} W_{\tau'_m}) > 0$, which directly leads to the bound
-\begin{equation}
-	\frac{m}{n} \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{\widetilde{D}_\alpha( \rho', \tau')}.
+	n D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) \geq m \frac{1}{m}D_\alpha(W_{\rho'^{\otimes m}} \hspace{1pt}||\hspace{1pt} W_{\tau'_m}).
+\end{equation}
+
+Since $\rho'^{\otimes m} \neq \tau'_m$, we have $D_\alpha(W_{\rho'^{\otimes m}} \hspace{1pt}||\hspace{1pt} W_{\tau'_m}) > 0$, which directly leads to the bound
+\begin{equation}
+	\frac{m}{n} \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{\rlap{\raisebox{-0.1ex}{$\widetilde{\phantom{D}}$}}D_\alpha( \rho', \tau')}.
 \end{equation}

### 2021-06-29 magic_paper.tex
Minor typos/edits.

--- 2021-06-28 magic_paper.tex
@@
 
-We note that this mapping to stochastic maps is not one-to-one.
-Not all stochastic maps on the phase space correspond to valid quantum operations.
+We note however, that not all stochastic maps on the phase space correspond to valid quantum operations.
 The reason is that the maps must also respect the symplectic structure of the phase space, which is an additional non-trivial constraint.
@@
 The value $L_{\w|\r}(x) = 1$ is a global maximum.
-Moreover, if $\w, \w', \r, \r'$ are all valid probability distributions with neither of $\r,\r'$ having negative components then it can be shown~\cite{ruch_mixing_1978} that
+Moreover, if $\w, \w', \r, \r'$ are all valid probability distributions with $\r,\r'$ having positive components then it can be shown~\cite{ruch_mixing_1978} that
 \begin{equation}
@@
 
-\vspace{1cm}
 \section{Acknowledgements}

### 2021-06-29 magic_paper.tex

--- 2021-06-29 magic_paper.tex
@@
 Theories of magic states attempt to quantify this computational element via monotones and determine how these states may be efficiently transformed into useful forms.
-Here, we develop a statistical mechanical framework based on majorization in which Wigner negative magic states provide non-classical free energy that is processed under Clifford circuits for qudits of odd prime dimension.
-While traditional free energy is not defined in the presence of negativity, we show that majorization allows us to both quantify disorder in the Wigner representation and derive magic distillation bounds.
-These upper bounds are shown to be tighter than other bounds, such as from mana and thauma, and can incorporate hardware physics, such as temperature dependence and physical Hamiltonians.
+Here, we develop a statistical mechanical framework based on majorization to describe Wigner negative magic states for qudits of odd prime dimension processed under Clifford circuits.
+We show that majorization allows us to both quantify disorder in the Wigner representation and derive magic distillation bounds.
+These upper bounds are shown to be tighter than other bounds, such as from mana and thauma, and can be used to incorporate hardware physics, such as temperature dependence and system Hamiltonians.
 We also show that a subset of single-shot R\'{e}nyi entropies remain well-defined on quasi-distributions, are fully meaningful in terms of data processing and can acquire negative values that signal magic.
@@
     \centering
-    \includegraphics[scale=0.35]{figs/distill_bounds.pdf}
+    \includegraphics[scale=0.38]{figs/distill_bounds.pdf}
     \caption{\textbf{Magic distillation bounds from majorization of Wigner quasi-distributions.} The above plot shows distillation upper bounds for qutrits obtained from majorization on unital protocols.
@@
 The value $L_{\w|\r}(x) = 1$ is a global maximum.
-Moreover, if $\w, \w', \r, \r'$ are all valid probability distributions with neither of $\r,\r'$ having negative components then it can be shown~\cite{ruch_mixing_1978} that
+Moreover, if $\w, \w', \r, \r'$ are all valid probability distributions with $\r,\r'$ having positive components then it can be shown~\cite{ruch_mixing_1978} that
 \begin{equation*}
@@
 
-Distillation bounds can be obtained from any location of the Lorenz curve, including the region around the peak, by imposing the constraint that the Lorenz curve of the input state never dips below the curve of the output.
-In particular a simple constraint can be obtained by considering the initial slopes of the two Lorenz curves.
-
-The coordinates of the first point after the origin for $\rho_S(\epsilon)^{\otimes n}$ are given by $(1/9^n, v(\epsilon)^n)$, while for $\rho_S(\epsilon')^{\otimes n'}$ by $(1/9^{n'}, v(\epsilon')^{n'})$, and by considering the slope of the line segment joining this point to the origin we can use Proposition~\ref{prop:first_elb} in the appendices, to bound $R(\epsilon, \epsilon')$.
-We find that
+Distillation bounds can be obtained from any part of the Lorenz curve by imposing the constraint that the Lorenz curve of the input state never dips below the curve of the output.
+One simple constraint can be obtained by considering the initial slopes of the two Lorenz curves.
+
+The coordinates of the first point after the origin for $\rho_S(\epsilon)^{\otimes n}$ are given by $(1/9^n, v(\epsilon)^n)$, while for $\rho_S(\epsilon')^{\otimes n'}$ by $(1/9^{n'}, v(\epsilon')^{n'})$, and by requiring that the initial slope for the input state Lorenz curve is larger than that of the output state (Proposition~\ref{prop:first_elb} in the appendices) we find that
 \begin{equation}\label{eq:unital-bound}
@@
 \end{equation}
-We compare this to other known distillation bounds coming from mana and thauma~\cite{Wang_2020}. The mana bound can be directly calculated as
+We compare this to other known distillation bounds coming from mana and thauma. The mana bound can be directly calculated as
 \begin{equation}
@@
 \end{equation}
-The recently introduced max--thauma~\cite{Wang_2020} is defined as
+The max--thauma~\cite{Wang_2020} is defined as
 \begin{equation}
@@
 
-The $\alpha \rightarrow 1$ limit of the R\'{e}nyi entropy is not well-defined, however it diverges in a well-defined way. We can write the divergence of the entropy as 
+The $\alpha \rightarrow 1$ limit of the R\'{e}nyi entropy diverges if negativity is present, however it diverges in a well-defined way. We can write the entropy as 
 \begin{equation}
@@
 \begin{theorem}\label{thm:entropic_bounds}
-	Consider a general magic state distillation process on prime dimension qudits, that converts a magic state $\rho^{\otimes n} \longrightarrow \E(\rho^{\otimes n})=\rho'^{\otimes m}$and let $\tau$ be any full-rank stabilizer reference state on a qudit.
+	Consider a general magic state distillation protocol on odd prime dimension qudits, that converts a magic state $\rho^{\otimes n} \longrightarrow \E(\rho^{\otimes n})=\rho'^{\otimes m}$and let $\tau$ be any full-rank stabilizer reference state on a qudit.
 Then the distillation rate $R \coloneqq m/n$ is upper bounded as,
@@
 \end{equation}
-which gives a generalized version of Theorem~\ref{thm:free-energy}.
-
-We can illustrate a simple application of the above bound for magic protocols that give unital maps. In this case it is easy to see that the above bound reduces to the simple form
+which gives a generalized version of Theorem~\ref{thm:free-energy}, with a term such as $D_\alpha(W_\rho ||W_\tau)$ that behaves essentially as an $\alpha$--free energy difference~\cite{Brandao_2015} in the Wigner representation.
+
+We can illustrate a basic application of the above bound for magic protocols that give unital maps. In this case it is easy to see that the above bound reduces to the simple form
 \begin{equation}
@@
 The topic of $G$--majorization has been extensively studied, but to our knowledge there has not been work on relative $G$--majorization.
-This would correspond to transformations that are \emph{not} unital, but still respect the symplectic structure.
+This would correspond to transformations that are not unital.
 Physically, this regime would correspond to a form of thermo-majorization obtained from looking at the action of the Clifford group at a micro-canonical level, and then reducing to a small subsystem~\cite{Pathria_1997}.
@@
 Therefore, the pre-order of statistical mechanical states with respect to phase space dynamics preserving a Gibbs state must correspond to a symplectic majorization condition.
-Of course, technical features arise in the continuum limit when considering distributions on an unbounded phase space, but this could be remedied by either considering a compact phase space (e.g.
-for a particle on a ring) or by first studying the discrete case.
+Of course, technical features arise in the continuum limit when considering distributions on an unbounded phase space, but this could be remedied by either considering a compact phase space (e.g.~for a particle on a ring) or by first studying the discrete case.
 Such scenarios also arise in the Quantum Hall Effect~\cite{Klitzing_1980}, which is another regime where these techniques could be of use.
@@
 \end{equation}
-and if additionally $w_k \geq 0$ for all $k$, then we also have for even $n$ that
-\begin{equation}
-	\max_{k_1, k_2, \dots, k_n} \left( w_{k_1}w_{k_2}\cdots w_{k_n} \right) = (\max_k |w_k|)^n.
-\end{equation}
-Therefore, for arbitrary $\w \in \mathbb{R}^N$ and $n$, we have
+and if additionally $w_k \geq 0$ for all $k$, then we also have for $2n$ copies that
+\begin{equation}
+	\max_{k_1, k_2, \dots, k_{2n}} \left( w_{k_1}w_{k_2}\cdots w_{k_{2n}} \right) = (\max_k |w_k|)^{2n},
+\end{equation}
+and also,
 \begin{align}
@@
 If $\alpha =2a/(2b-1)$ with $\alpha < 1$, then $g(w) \coloneqq \frac{-w^{\alpha-1}}{\alpha-1}$ is no longer monotonic for all $w \in \mathbb{R}$, and the problem occurs when comparing $w_i < 0$ and $w_j >0$.
-As an analogy, consider the function $g(x) = \frac{1}{x^3}$ which is monotone decreasing on $x<0$ and $x>0$ separately, however it is not monotone on the full real-line.
+As an example of this dependence of monotonicity on the domain of the function, consider the function $g(x) = \frac{1}{x^3}$ which is monotone decreasing on both $x<0$ and $x>0$ separately, however it is not monotone on the full real-line.
 
@@
 	Let $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$.
-	Then, $D_\alpha$ is Schur-convex, i.e. $D_\alpha(\w \hspace{1pt}||\hspace{1pt} \r) \geq D_\alpha(\w' \hspace{1pt}||\hspace{1pt} \r')$, whenever $(\w, \r) \succ (\w', \r')$.
+Let $\w \in \mathcal{Q}_N$, $\w' \in \mathcal{Q}_{N'}$ and $\r \in  \mathcal{Q}^+_N$, $\r' \in \mathcal{Q}^+_{N'}$ with positive rational components $a_i/K$ and $a'_i/K$ respectively.
+	Then $D_\alpha(\w \hspace{1pt}||\hspace{1pt} \r) \geq D_\alpha(\w' \hspace{1pt}||\hspace{1pt} \r')$, whenever $(\w, \r) \succ (\w', \r')$.
 \end{proposition}
@@
 \end{proof}
+Since the rationals are dense in the real numbers we can assume any Wigner distribution considered has rational components without affecting results.
 We now specialize to Wigner distributions of quantum states, and quantum operations that map the set of free states $\F$ into itself.
@@
 \begin{proof}
-	The bound is a direct consequence of the properties of the $\alpha$--R\'{e}nyi diveregence, proven in Theorem~\ref{thm:Da_props}.
+	The bound is a direct consequence of the properties of the $\alpha$--R\'{e}nyi divergence in Theorem~\ref{thm:Da_props}.
 

### 2021-06-29 ms.tex
Version submitted to arXiv

--- 2021-06-29 magic_paper.tex
@@
 Here, we develop a statistical mechanical framework based on majorization to describe Wigner negative magic states for qudits of odd prime dimension processed under Clifford circuits.
-We show that majorization allows us to both quantify disorder in the Wigner representation and derive magic distillation bounds.
-These upper bounds are shown to be tighter than other bounds, such as from mana and thauma, and can be used to incorporate hardware physics, such as temperature dependence and system Hamiltonians.
+We show that majorization allows us to both quantify disorder in the Wigner representation and derive upper bounds for magic distillation.
+These bounds are shown to be tighter than other bounds, such as from mana and thauma, and can be used to incorporate hardware physics, such as temperature dependence and system Hamiltonians.
 We also show that a subset of single-shot R\'{e}nyi entropies remain well-defined on quasi-distributions, are fully meaningful in terms of data processing and can acquire negative values that signal magic.
@@
 Any quantum channel $\E$ also admits a Wigner representation.
-If $\E$ maps some quantum system $A$ of dimension $d_A$ to a quantum system $B$ of dimension $d_B$ and $\J(\E) = \E \otimes id (|\phi^+\> \<\phi^+|)$, with $|\phi^+\> = d_A^{-1/2} \sum_k |kk\>$, is its associated Choi state of the channel~\cite{watrous_2018}, then we can define
+If $\E$ maps some quantum system $A$ of dimension $d_A$ to a quantum system $B$ of dimension $d_B$ and $\J(\E) = (id \otimes \E) (|\phi^+\> \<\phi^+|)$, with $|\phi^+\> = d_A^{-1/2} \sum_k |kk\>$, is its associated Choi state~\cite{watrous_2018}, then we can define
 \begin{equation}\label{Wigner-Choi}
@@
 In the more general case, $\Delta F \coloneqq F' - F \ne 0$, so the protocol, when applied to the reference state, adds/extracts free energy from the system.
+We demonstrate change of the bounds with respect to a varying output Hamiltonian in Fig.~\ref{fig:rvsa}.
 
@@
     \caption{\textbf{Variation of distillation bounds with Hamiltonian.}  We illustrate variation of the bound in Eq.~(\ref{eq:rate_bounds_proof}) with respect to the system Hamiltonian.
-We fix $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$ and look at a family of Hamiltonians for the qutrit systems, given by $H = A_{\bmo}$ and $H' = (1-p-q)A_{\bmo}+pA_{(1,2)}+q{\rm{diag}}(0,1,2)$ for varying probabilities $p, q$.
+We fix $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$ and look at a family of Hamiltonians for the qutrit systems, given by $H = A_{\bmo}$ and $H' = (1-p-q)A_{\bmo}+pA_{(1,2)}+q{\rm{diag}}(0,1,2)$, with varying parameters $p, q$, and where $A_{\bmo}$ and $A_{(1,2)}$ are phase-point operators.
     }
@@
 	\begin{equation}
-		R \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{\rlap{\raisebox{-0.2ex}{$\widetilde{\phantom{D}}$}}D_\alpha( \rho', \tau')}
+		R \leq R_\alpha \coloneqq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{\rlap{\raisebox{-0.2ex}{$\widetilde{\phantom{D}}$}}D_\alpha( \rho', \tau')},
 	\end{equation}
@@
 
-We can also ask if this approach could also provide \emph{lower bounds} for distillation protocols.
+We can also ask if this approach could additionally provide \emph{lower bounds} for distillation protocols.
 In contrast to the upper bounds, it is now essential to include the symplectic constraints on the phase space in the majorization relations.
-The Clifford group action on a quantum system corresponds to the action of the affine symplectic group $G=SL(2,\mathbb{Z}_d) \ltimes \mathbb{Z}_d^2$ on the discrete phase space~\cite{cit:gross3, cit:bengtsson}.
+The Clifford group action on a quantum system corresponds to the action of the affine symplectic group $G=SL(2,\mathbb{Z}_d) \ltimes \mathbb{Z}_d^2$ on the discrete phase space~\cite{Appleby_2005, cit:bengtsson}.
 Therefore, any convex mixture of Clifford unitaries will correspond to a convex mixture of these group actions.
@@
 
-\bibliography{bib}
+%\bibliography{bib}
 %\bibliographystyle{apsrev4-2}
+\input{ms.bbl}
 
@@
 	\W[\bmz]{\tau} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z}W_{|k\>\<k|}(q, p) \nonumber\\
-	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z} \delta_{q, k} = \frac{e^{-\beta E_x}}{3\Z},
+	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z} \delta_{q, k} = \frac{e^{-\beta E_q}}{3\Z},
 \end{align}
@@
     \includegraphics[scale=0.35]{figs/H_vs_eps_a.pdf}
-    \caption{\textbf{R\'{e}nyi entropy $H_\alpha$ of $\epsilon$-noisy Strange state.} $H_\alpha$ is increasing in $\alpha$ and $\epsilon$.
+    \caption{\textbf{R\'{e}nyi entropy $H_\alpha$ of the $\epsilon$-noisy Strange state.} $H_\alpha$ is increasing in $\alpha$ and $\epsilon$.
 The first dashed contour from the right corresponds to $H_\alpha(\rho_{\rm{S}}(\epsilon)) = 0$.
@@
 	\begin{equation}
-		R \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{\rlap{\raisebox{-0.1ex}{$\widetilde{\phantom{D}}$}}D_\alpha( \rho', \tau')}
+		R \leq R_\alpha \coloneqq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{\rlap{\raisebox{-0.2ex}{$\widetilde{\phantom{D}}$}}D_\alpha( \rho', \tau')},
 	\end{equation}

### 2021-07-02 ms.tex
added refs with highlighted comments to be checked

@@
 
-There has been rapid progress towards the goal of a fault-tolerant quantum computer~\cite{campbell_roads_2017, cit:raussendorf, Raussendorf_2013, Nickerson_2014, Nikahd_2017, chao_2018, lin_pieceable_2020, Lin_2020, Bourassa_2021}.
+There has been rapid progress towards the goal of a fault-tolerant quantum computer~\cite{campbell_roads_2017, cit:raussendorf, Raussendorf_2013, Nickerson_2014, Nikahd_2017, chao_2018, lin_pieceable_2020, Lin_2020, chamberland_2020, Bourassa_2021}.
 Nevertheless, many challenges remain and there is increasing need for theory to take into account physical limitations of the hardware involved.
@@
 For example, the XZZX code~\cite{bonilla_ataides_xzzx_2021} is a variant of the surface code that incorporates noise bias explicitly and has been shown to attain the hashing bound of random codes~\cite{Bennett_1996}.
+\nick{There have also been breathroughs in the preparation of high quality magi states with low overhead~\cite{chamberland_very_2020, Chamberland2019faulttolerantmagic}}
 
@@
 
-Central to our construction is the representation of any quantum state or quantum operation on a system of dimension $d$ in terms of quasi-probability representations on a discrete phase space~\cite{Ferrie_2008}.
+Central to our construction is the representation of any quantum state or quantum operation on a system of dimension $d$ in terms of quasi-probability representations on a discrete phase space~\cite{cit:gross3, Ferrie_2008}.
 This construction is a discrete version of Wigner representations in quantum optics~\cite{Wigner_1932, Vourdas_2004}.
@@
 where the phase factor $\tau \coloneqq -\omega^{1/2}$ ensures unitarity.
-We assume going forward that $d$ is an odd prime~\cite{Appleby_2005}.
+We assume going forward that $d$ is an odd prime~\cite{Appleby_2005} \nick{which ensures that the discrete Wigner representation is in fact the only non-contextual quasi-probability representation of odd-dimensional stabilizer theories~\cite{schmid2021noncontextual, schmid2020structure, Schmid_2021}}.
 The qubit case $d=2$ is known to have obstacles to using a Wigner representation to quantify magic in terms of negativity~\cite{Mermin_1990, cit:howard2}, although recent work~\cite{Raussendorf_qubits} has shown how to extend this to include qubits by enlarging the phase space.
@@
 	\begin{equation}
-		R \leq R_\alpha \coloneqq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{\rlap{\raisebox{-0.2ex}{$\widetilde{\phantom{D}}$}}D_\alpha( \rho', \tau')},
+		R \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{\rlap{\raisebox{-0.2ex}{$\widetilde{\phantom{D}}$}}D_\alpha( \rho', \tau')},
 	\end{equation}
@@
 \begin{equation}
-	R \leq R_\alpha=\frac{2\log d - H_{\alpha}(W_\rho)}{2\log d - H_{\alpha}(W_{\rho'})}.
+	R \leq R_\alpha \coloneqq \frac{2\log d - H_{\alpha}(W_\rho)}{2\log d - H_{\alpha}(W_{\rho'})}.
 \end{equation}
@@
 \begin{equation}
-	R \leq R_\alpha=\frac{2(1-\alpha)\log 3 - \log \left [8(\frac{1}{6} - \frac{\epsilon}{18})^\alpha + (-\frac{1}{3} + \frac{4\epsilon}{9})^\alpha\right ] }{2(1-\alpha)\log 3 + \alpha \log 6 - \log (8 + 2^\alpha )}.
+	R \leq R_\alpha = \frac{2(1-\alpha)\log 3 - \log \left [8(\frac{1}{6} - \frac{\epsilon}{18})^\alpha + (-\frac{1}{3} + \frac{4\epsilon}{9})^\alpha\right ] }{2(1-\alpha)\log 3 + \alpha \log 6 - \log (8 + 2^\alpha )}.
 \end{equation}
@@
 
-%\bibliography{bib}
+\bibliography{bib}
 %\bibliographystyle{apsrev4-2}
-\input{ms.bbl}
+%\input{ms.bbl}
 

### 2021-07-05 ms.tex
comments in red

@@
 For example, the XZZX code~\cite{bonilla_ataides_xzzx_2021} is a variant of the surface code that incorporates noise bias explicitly and has been shown to attain the hashing bound of random codes~\cite{Bennett_1996}.
-\nick{There have also been breathroughs in the preparation of high quality magi states with low overhead~\cite{chamberland_very_2020, Chamberland2019faulttolerantmagic}}
+\nick{There have also been breakthroughs in the preparation of high quality magic states with low overhead~\cite{chamberland_very_2020, Chamberland2019faulttolerantmagic}}
 
@@
 We assume going forward that $d$ is an odd prime~\cite{Appleby_2005} \nick{which ensures that the discrete Wigner representation is in fact the only non-contextual quasi-probability representation of odd-dimensional stabilizer theories~\cite{schmid2021noncontextual, schmid2020structure, Schmid_2021}}.
-The qubit case $d=2$ is known to have obstacles to using a Wigner representation to quantify magic in terms of negativity~\cite{Mermin_1990, cit:howard2}, although recent work~\cite{Raussendorf_qubits} has shown how to extend this to include qubits by enlarging the phase space.
+The qubit case $d=2$ is known to have obstacles to using a Wigner representation to quantify magic in terms of negativity~\cite{Mermin_1990, cit:howard2}, although recent work~\cite{Raussendorf_qubits} has shown how to extend the representation to include qubits by enlarging the phase space.
 For a composite system with dimension $d_{\rm tot} = d_1 \dots d_n$ and Hilbert space $\cal{H}_{d_1} \otimes \dots \otimes \cal{H}_{d_n}$, we define displacement operators as
@@
 
-Within the Wigner representation for odd prime dimension, all negatively represented states are magic states, although in general the converse is not true~\cite{cit:veitch}.
-However, it is known that all positively represented states used in Clifford circuits admit an efficient classical description, so it is natural to focus on the negatively represented magic states.
-The free states in any magic theory are required to be a subset of
+Within the Wigner representation for odd prime dimension, \nick{magic states are necessarily negatively represented~\cite{cit:veitch}, while it is also known that all positively represented states used in Clifford circuits admit an efficient classical description~\cite{cit:mari}}.
+Therefore, the free states in any magic theory are required to be a subset of
 \begin{equation}

### 2021-07-06 cover-letter/cover-letter.tex
Cover letter folder added.

\documentclass[11pt]{letter}

%\usepackage{pxfonts}
%\usepackage{color}
%\hyphenation{ma-nu-script}
\usepackage[colorlinks=true,urlcolor=blue, hyperindex,breaklinks=true] {hyperref}

\usepackage{graphicx}
\usepackage[a4paper,left=2cm,right=2cm,bottom=2cm]{geometry}

\usepackage{fancyhdr}
%\usepackage{marvosym}

% nice font.
\renewcommand*\rmdefault{ppl}

\usepackage[table,xcdraw,dvipsnames]{xcolor}
\renewcommand{\cc}[1]{\textcolor{magenta}{#1}}
\newcommand{\mjg}[1]{{\color{NavyBlue}[#1]}}
\newcommand{\ddd}[1]{\textcolor{Blue}{[#1]}}

\pagestyle{empty}

\begin{document}

\hfill\begin{minipage}{6cm}
	\raggedright
	\vspace{-2.5cm}
	{\footnotesize\itshape Matthew Girling}\\
	{\footnotesize\itshape School of Physics and Astronomy}\\
	{\footnotesize\itshape University of Leeds}\\
	{\footnotesize\itshape Leeds, LS2 9JT, United Kingdom}\\
	{\footnotesize\itshape %\MVAt~ 
		\verb|m.j.girling@leeds.ac.uk|}\\
	~\\
		\footnotesize\today
\end{minipage}

\vspace{-3.5cm}
\includegraphics[scale=.40]{leeds-logo.pdf}
\vspace{3.5cm}

\vspace{-1.5cm}
Dear Editors of Physical Review X,

\vspace{.3cm}

Please find enclosed a copy of our manuscript \emph{``Estimation of correlations and non-separability in quantum channels via unitarity benchmarking''}, which we would like to submit for review in Physical Review~X. We believe our work fits naturally into the scope of the journal.

%\ddd{Our manuscript connects analysis of fundamental quantum information theoretic concepts- namely the properties of coherent information flow and correlations in quantum channels, with experimentally estimatable measures of noise in quantum devices. The measures we introduce can be related to foundational elements quantum theory, and provide novel (statements?) of non-classical behaviour. Applied to benchmarking, our measures provide independent information beyond that of existing techniques. In this way, our work links tractable real world methods used in quantum devices with concepts that are of broad interest in the physics community. }

Our results develop connections between fundamental topics in quantum physics and the experimental development of quantum technologies. Moreover, our work pushes core theory of quantum information into experimentally testable regimes.

Famously, quantum states allow for correlations (quantum entanglement) that exceed anything possible in classical physics. Such correlations underlie the complexity of many-body quantum systems, are the focus of foundations research, are central to quantum computing and communications, and are a major focus of high energy physics research. Extensive work has been done on their structure, detection and certification, however far less is known about \emph{dynamical} correlations in quantum physics. For this, the concept of a quantum channel unifies reversible dynamics based on Lagrangians with more general evolutions of quantum systems such as open system dynamics, measurement theory and quantum information processing. Channels therefore constitute fundamental tools, applicable to a broad range of contemporary quantum physics research.

Our work constructs a framework to both quantify and certify correlations in quantum channels. We tackle this problem using methods that have recently been developed in the field of quantum technologies. We develop novel methods to quantify correlations in general quantum channels and prove that, just as with quantum states, there is a separation between ``classical'' correlations and genuinely quantum correlations. We then prove that these quantum correlations obey a fundamental Information-Disturbance trade-off relation that provides a new description of the security of quantum encryption. Finally, we show that the presence of these correlations can be certified in quantum systems, and construct an explicit scheme to do so using existing noisy devices for quantum technologies. Our scheme is both efficient in the number of experimental rounds and robust against imperfections arising due to experimental state preparation and measurement errors.

Our results give a fundamental description of non-classicality in dynamical quantum processes.  This analysis of classical/quantum correlations links to recent work on quantum non-locality and the ``self-testing'' of quantum states, and so may find further application in these areas. The measures and means to estimate correlations are relevant to controlled quantum dynamics and the manipulation of quantum coherence.  Also, to our knowledge, the Information-Disturbance relation constitutes the first such formulation that could be efficiently tested experimentally.  Finally, correlated and cross-talk errors are fundamental obstacles to the construction of a full-scale quantum computer, and our results can be directly applied to the benchmarking of noise in quantum devices. Therefore, our work directly impacts ongoing quantum technology research.

For the above reasons, we believe that our manuscript is of relevance to a wide audience of quantum physicists, and so is suitable for publication in Phys. Rev. X.

\vspace{1cm}
\hspace{8cm}
\begin{minipage}{9cm}
\flushleft
Sincerely Yours,\\

Matthew Girling, Cristina Cirstoiu, David Jennings.
\end{minipage}
\newpage

%\ddd{Popular Summary: Physical Review X requires authors to submit a nontechnical summary that conveys the context, the essential message(s), and the significance of the work to all readers. The summary should be concise (approximately 250 words), readable, objective, and have broad appeal. Please avoid including mathematical expressions.}
%
%\ddd{When writing the Popular Summary, imagine \textbf{how you would explain your work to a junior physics undergrad}: someone familiar with physics fundamentals but likely unfamiliar with your area of research. Step back from the details (expert readers can always read the paper) and focus more on the essence of your work. Depending on the paper, that essence may be a new paradigm, the discovery of some phenomenon, a new technical milestone, or a new methodological capability. The tone can be casual and conversational. Be careful with jargon -- avoid it if possible, but if a technical word or phrase is essential, please make a conscious effort to explain it using plain language.}
%

%
% \ddd{The first paragraph provides the “big picture” context and tells the reader why your investigation is worth doing. The reader should come away knowing what problem you’re trying to solve and the main point of what you found. Keep the wording concise—don’t make the reader wade through lots of background before revealing the central point of the paper. Think of this paragraph as a summary within a summary—a reader could read just this paragraph and have a sense of what you did and why it’s useful.}
% 
% \ddd{The second paragraph fleshes out the most essential details. This is a good place to add extra background and context and to tell the reader how you went about your work and, when appropriate, the new qualitative physical insights you gained from the detailed results. But stay focused on the essentials: The reader doesn’t need to know everything you did, just a “taste” of how you arrived at your results and what your results teach all readers.}
% 
% \ddd{The third paragraph provides the reader with an outlook to the future. In just a sentence or two, tell the reader where you see this research going or what a logical next step might be.}
%

\textbf{[Popular Summary]}

Quantum entanglement was described by Einstein as `spooky action at a distance' and is the uniquely quantum effect where two separated objects hide all their properties in the correlations between them. Remarkably entanglement is also useful: it will power the quantum computers that are currently being built, which promise to revolutionize our modern information age. Our paper looks at quantum correlations in the dynamics of a quantum system, where it is the interactions between particles that are, in a sense, entangled. Such correlations are essential in order for quantum bits to flow through a quantum computer. Our theoretical work both quantifies these correlations and gives means to detect them in existing quantum systems.

Our work predicts that this `dynamical entanglement' should be detectable by virtue of it having stronger dynamical effects than anything possible with classical physics. We also predict that the flow of quantum bits through systems should behave somewhat like an incompressible fluid: quantum bits can stretch and even break into parts but the total `volume' can never increase. In fact, we explain how it is this inability to `expand' quantum bits that makes quantum encryption perfectly secure. Finally, we have devised experimental protocols that could be done to both measure these `volumes' and also detect this dynamical entanglement.

Our work applies to all quantum systems, irrespective of the size or type of the system, and so constitute fundamental results. Moreover, with the concrete protocols we have developed, our predictions should be testable on existing devices, such as IBM or Google's quantum computer. Our results shed new light on how quantum physics differs so fundamentally from classical physics, and provide a novel toolkit of broad relevance to contemporary quantum physics research and the development of quantum technologies.

% -- Tools for studying quantum dynamics (a subset of quantum channel theory).
% }

\end{document}

### 2021-07-07 ms.tex
added karols refs, fixed comments as discussed. Only one red comment that David needs to fix re: uniqueness of Wigner rep

@@
 To address this, concrete distillation protocols have been developed, such as the Bravyi-Haah qubit protocol that provides a quadratic reduction in noise per cycle~\cite{Bravyi2012}.
-Such distillation rates have been improved in more recent works~\cite{Jones_2013, haah2017magic, Hastings2018, Litinski_2019} and protocols for qudits of odd dimension have also been proposed~\cite{CampbellAnwar_2012, Anwar_2012, Dawkins_2015, Krishna2019, cit:prakash}.
+Such distillation rates have been improved in more recent works~\cite{Jones_2013, haah2017magic, Hastings2018, Litinski_2019} and there have been proposals of protocols for qudits of odd dimension~\cite{CampbellAnwar_2012, Anwar_2012, Dawkins_2015, Krishna2019, cit:prakash} as well as of protocols within a full architectural analysis~\cite{chamberland_very_2020, Chamberland2019faulttolerantmagic}.
 There is also analysis of magic protocols from the perspective of magic monotones, which provide upper bounds on distillation rates and find application in the analysis of gate synthesis~\cite{Campbell_2017, Howard_2017, Prakash_2018, Seddon_2021,leone2021renyi}.
 These frameworks for magic view magic states as resource states with respect to a natural class of quantum operations that are considered cheap, or free, such as stabilizer operations~\cite{Gour_2019, cit:ahmadi, cit:seddon, Wang_2019}.
-Beyond quantum computing, recent work has also looked at how magic can be used to analyse many-body physics~\cite{Sarkar_2020} and conformal field theories~\cite{White_2021} as well its connection to contextuality~\cite{Vega_2017, cit:howard2, Zurel_2020, Okay_2021}.
+Beyond quantum computing, recent work has also looked at how magic can be used to analyse many-body physics~\cite{Sarkar_2020} and conformal field theories~\cite{White_2021} as well its connection to contextuality~\cite{Vega_2017, cit:howard2, Zurel_2020, Okay_2021, schmid2020structure, Schmid_2021}.
 
@@
 For example, the XZZX code~\cite{bonilla_ataides_xzzx_2021} is a variant of the surface code that incorporates noise bias explicitly and has been shown to attain the hashing bound of random codes~\cite{Bennett_1996}.
-\nick{There have also been breakthroughs in the preparation of high quality magic states with low overhead~\cite{chamberland_very_2020, Chamberland2019faulttolerantmagic}}
 
@@
 Central to our construction is the representation of any quantum state or quantum operation on a system of dimension $d$ in terms of quasi-probability representations on a discrete phase space~\cite{cit:gross3, Ferrie_2008}.
-This construction is a discrete version of Wigner representations in quantum optics~\cite{Wigner_1932, Vourdas_2004}.
+This construction is a discrete version of Wigner representations in quantum optics~\cite{Wigner_1932, Vourdas_2004, Kenfack_2004}.
 
@@
 where the phase factor $\tau \coloneqq -\omega^{1/2}$ ensures unitarity.
-We assume going forward that $d$ is an odd prime~\cite{Appleby_2005} \nick{which ensures that the discrete Wigner representation is in fact the only non-contextual quasi-probability representation of odd-dimensional stabilizer theories~\cite{schmid2021noncontextual, schmid2020structure, Schmid_2021}}.
+We assume going forward that $d$ is an odd prime~\cite{Appleby_2005}.
 The qubit case $d=2$ is known to have obstacles to using a Wigner representation to quantify magic in terms of negativity~\cite{Mermin_1990, cit:howard2}, although recent work~\cite{Raussendorf_qubits} has shown how to extend the representation to include qubits by enlarging the phase space.
@@
 where $\bar{\bmz} = (q_1, \dots, q_n, -p_1, \dots, -p_n)$ can be viewed as the time-reversed version of $\bmz$ in the discrete phase space, where momenta are reflected while position coordinates remain unchanged.
+
+\nick{We note that the discrete Wigner representation described in this section is in fact the only non-contextual quasi-probability representation of odd-dimensional stabilizer theories~\cite{schmid2021noncontextual}.
+In particular, negativity within the Wigner representation cannot be eliminated by considering a different quasi-probability representation.
+- look at paragraph starting ``In the setting of the full stabilizer subtheory...'' on page 2 of~\cite{schmid2021noncontextual}}
 
@@
 
-Within the Wigner representation for odd prime dimension, \nick{magic states are necessarily negatively represented~\cite{cit:veitch}, while it is also known that all positively represented states used in Clifford circuits admit an efficient classical description~\cite{cit:mari}}.
+Within the Wigner representation for odd prime dimension, it is well-known that all positively represented states used in Clifford circuits admit an efficient classical description~\cite{cit:mari}, so negativity is a necessary resource for universal fault-tolerant quantum computing~\cite{cit:veitch}.
 Therefore, the free states in any magic theory are required to be a subset of
@@
 
-Majorisation~\cite{cit:marshall, Blackwell_1953} is a collection of powerful tools that has found many applications in quantum information theory~\cite{Nielsen_1999, cit:cwiklinski, cit:lostaglio2, cit:gour, cit:gour2, Horodecki_2003, Vallejos_2021}.
+Majorisation~\cite{cit:marshall, Blackwell_1953} is a collection of powerful tools that has found many applications in quantum information theory~\cite{Nielsen_1999, cit:cwiklinski, cit:lostaglio2, cit:gour, cit:gour2, Horodecki_2003, Puchala_2013, Vallejos_2021}.
 It describes the disorder of distributions that undergo stochastic transformations, and in its simplest form defines a pre-order on probability distributions.
@@
 In contrast to the upper bounds, it is now essential to include the symplectic constraints on the phase space in the majorization relations.
-The Clifford group action on a quantum system corresponds to the action of the affine symplectic group $G=SL(2,\mathbb{Z}_d) \ltimes \mathbb{Z}_d^2$ on the discrete phase space~\cite{Appleby_2005, cit:bengtsson}.
+The Clifford group action on a quantum system corresponds to the action of the affine symplectic group $G=SL(2,\mathbb{Z}_d) \ltimes \mathbb{Z}_d^2$ on the discrete phase space~\cite{Appleby_2005, Bengtsson_2006}.
 Therefore, any convex mixture of Clifford unitaries will correspond to a convex mixture of these group actions.

### 2021-07-09 cover-letter/cover-letter.tex
first attempt at cover letter and popular summary. David please also check red comment on manuscript

@@
 \usepackage[table,xcdraw,dvipsnames]{xcolor}
-\renewcommand{\cc}[1]{\textcolor{magenta}{#1}}
-\newcommand{\mjg}[1]{{\color{NavyBlue}[#1]}}
-\newcommand{\ddd}[1]{\textcolor{Blue}{[#1]}}
+\newcommand{\nick}[1]{\textcolor{red}{[#1]}}
+\newcommand{\ddd}[1]{\textcolor{blue}{[#1]}}
 
@@
 	\vspace{-2.5cm}
-	{\footnotesize\itshape Matthew Girling}\\
-	{\footnotesize\itshape School of Physics and Astronomy}\\
-	{\footnotesize\itshape University of Leeds}\\
-	{\footnotesize\itshape Leeds, LS2 9JT, United Kingdom}\\
+	{\footnotesize\itshape Nikolaos Koukoulekidis}\\
+	{\footnotesize\itshape Department of Physics}\\
+	{\footnotesize\itshape Imperial College London}\\
+	{\footnotesize\itshape London SW7 2AZ, UK}\\
 	{\footnotesize\itshape %\MVAt~ 
-		\verb|m.j.girling@leeds.ac.uk|}\\
+		\verb|nk2314@imperial.ac.uk|}\\
 	~\\
@@
 \vspace{-3.5cm}
-\includegraphics[scale=.40]{leeds-logo.pdf}
+\includegraphics[scale=.1]{icllogo.png}
 \vspace{3.5cm}
@@
 \vspace{-1.5cm}
-Dear Editors of Physical Review X,
+Dear Editors of PRX Quantum,
+
+\nick{this is supposed to be a ``100-word concise and compelling argument''. Currently: 203 words}
 
@@
 
-Please find enclosed a copy of our manuscript \emph{``Estimation of correlations and non-separability in quantum channels via unitarity benchmarking''}, which we would like to submit for review in Physical Review~X.
+Please find enclosed a copy of our manuscript \emph{``Constraints on magic state protocols from the statistical mechanics of Wigner negativity''}, which we would like to submit for review in PRX Quantum.
 We believe our work fits naturally into the scope of the journal.
 
-%\ddd{Our manuscript connects analysis of fundamental quantum information theoretic concepts- namely the properties of coherent information flow and correlations in quantum channels, with experimentally estimatable measures of noise in quantum devices.
-The measures we introduce can be related to foundational elements quantum theory, and provide novel (statements?) of non-classical behaviour.
-Applied to benchmarking, our measures provide independent information beyond that of existing techniques.
-In this way, our work links tractable real world methods used in quantum devices with concepts that are of broad interest in the physics community.
-}
+Our work establishes a connection between two fields within quantum information: quantum thermodynamics and quasi-probability representations of quantum physics.
+This allows for important advances in the subfield of magic theory, an increasingly important area of quantum computation.
 
-Our results develop connections between fundamental topics in quantum physics and the experimental development of quantum technologies.
-Moreover, our work pushes core theory of quantum information into experimentally testable regimes.
+Primarily, we develop new techniques that provide analytical bounds on general magic state distillation processes.
+We show that our bounds are tighter than previously defined bounds, and importantly can be expressed in terms of the physical symmetries of the circuit in question.
+We therefore provide novel and powerful constraints on the design of magic protocols.
 
-Famously, quantum states allow for correlations (quantum entanglement) that exceed anything possible in classical physics.
-Such correlations underlie the complexity of many-body quantum systems, are the focus of foundations research, are central to quantum computing and communications, and are a major focus of high energy physics research.
-Extensive work has been done on their structure, detection and certification, however far less is known about \emph{dynamical} correlations in quantum physics.
-For this, the concept of a quantum channel unifies reversible dynamics based on Lagrangians with more general evolutions of quantum systems such as open system dynamics, measurement theory and quantum information processing.
-Channels therefore constitute fundamental tools, applicable to a broad range of contemporary quantum physics research.
-
-Our work constructs a framework to both quantify and certify correlations in quantum channels.
-We tackle this problem using methods that have recently been developed in the field of quantum technologies.
-We develop novel methods to quantify correlations in general quantum channels and prove that, just as with quantum states, there is a separation between ``classical'' correlations and genuinely quantum correlations.
-We then prove that these quantum correlations obey a fundamental Information-Disturbance trade-off relation that provides a new description of the security of quantum encryption.
-Finally, we show that the presence of these correlations can be certified in quantum systems, and construct an explicit scheme to do so using existing noisy devices for quantum technologies.
-Our scheme is both efficient in the number of experimental rounds and robust against imperfections arising due to experimental state preparation and measurement errors.
-
-Our results give a fundamental description of non-classicality in dynamical quantum processes.
-This analysis of classical/quantum correlations links to recent work on quantum non-locality and the ``self-testing'' of quantum states, and so may find further application in these areas.
-The measures and means to estimate correlations are relevant to controlled quantum dynamics and the manipulation of quantum coherence.
-Also, to our knowledge, the Information-Disturbance relation constitutes the first such formulation that could be efficiently tested experimentally.
-Finally, correlated and cross-talk errors are fundamental obstacles to the construction of a full-scale quantum computer, and our results can be directly applied to the benchmarking of noise in quantum devices.
-Therefore, our work directly impacts ongoing quantum technology research.
+The implications of our analysis are also important foundationally.
+We develop a novel theory of statistical mechanics on quasi-distributions and we further construct entropic functions which attain negative values, a property which acts as a fundamental witness of non-classicality.
 
@@
 
-Matthew Girling, Cristina Cirstoiu, David Jennings.
+Nikolaos Koukoulekidis, David Jennings.
 \end{minipage}
@@
 
-%\ddd{Popular Summary: Physical Review X requires authors to submit a nontechnical summary that conveys the context, the essential message(s), and the significance of the work to all readers.
-The summary should be concise (approximately 250 words), readable, objective, and have broad appeal.
-Please avoid including mathematical expressions.}
-%
-%\ddd{When writing the Popular Summary, imagine \textbf{how you would explain your work to a junior physics undergrad}: someone familiar with physics fundamentals but likely unfamiliar with your area of research.
-Step back from the details (expert readers can always read the paper) and focus more on the essence of your work.
-Depending on the paper, that essence may be a new paradigm, the discovery of some phenomenon, a new technical milestone, or a new methodological capability.
-The tone can be casual and conversational.
-Be careful with jargon -- avoid it if possible, but if a technical word or phrase is essential, please make a conscious effort to explain it using plain language.}
-%
+\textbf{Popular Summary}
 
-%
-% \ddd{The first paragraph provides the “big picture” context and tells the reader why your investigation is worth doing.
-The reader should come away knowing what problem you’re trying to solve and the main point of what you found.
-Keep the wording concise—don’t make the reader wade through lots of background before revealing the central point of the paper.
-Think of this paragraph as a summary within a summary—a reader could read just this paragraph and have a sense of what you did and why it’s useful.}
-% 
-% \ddd{The second paragraph fleshes out the most essential details.
-This is a good place to add extra background and context and to tell the reader how you went about your work and, when appropriate, the new qualitative physical insights you gained from the detailed results.
-But stay focused on the essentials: The reader doesn’t need to know everything you did, just a “taste” of how you arrived at your results and what your results teach all readers.}
-% 
-% \ddd{The third paragraph provides the reader with an outlook to the future. In just a sentence or two, tell the reader where you see this research going or what a logical next step might be.}
-%
+\nick{this is supposed to be 250 words long. Currently: 243 words}
 
-\textbf{[Popular Summary]}
+Quantum computers promise astronomical speed-ups for important computational tasks.
+A practically necessary requirement to achieve such speed-ups for useful computational tasks is establishing a framework that ensures fault-tolerance, which is the ability to correct computational errors in the circuit successfully and reliably.
+It is well-known that restricting to this framework, it is impossible to achieve quantum speed-ups, therefore we need to initiate the circuit with some low-noise input state that contains enough resources which can be used by the circuit to perform the desired computational task.
 
-Quantum entanglement was described by Einstein as `spooky action at a distance' and is the uniquely quantum effect where two separated objects hide all their properties in the correlations between them.
-Remarkably entanglement is also useful: it will power the quantum computers that are currently being built, which promise to revolutionize our modern information age.
-Our paper looks at quantum correlations in the dynamics of a quantum system, where it is the interactions between particles that are, in a sense, entangled.
-Such correlations are essential in order for quantum bits to flow through a quantum computer.
-Our theoretical work both quantifies these correlations and gives means to detect them in existing quantum systems.
+Creating this low-noise, highly resourceful state, called a ``magic state'', is a costly process, requiring in principle a quantum process that manipulates many highly noisy copies of the magic state in order to distill one with very low noise.
+Our work addresses the question regarding the highest possible rate of low-noise magic states one could extract, given some copies of highly noisy magic states.
+We provide fundamental bounds on this rate, based on the thermodynamic properties of the quantum process, which constraint the efficiency of any general quantum processes attempting to distill magic.
+As our bounds depend on the thermodynamic properties of the process, they notably provide a way of assessing how physical properties affect the distillation process.
 
-Our work predicts that this `dynamical entanglement' should be detectable by virtue of it having stronger dynamical effects than anything possible with classical physics.
-We also predict that the flow of quantum bits through systems should behave somewhat like an incompressible fluid: quantum bits can stretch and even break into parts but the total `volume' can never increase.
-In fact, we explain how it is this inability to `expand' quantum bits that makes quantum encryption perfectly secure.
-Finally, we have devised experimental protocols that could be done to both measure these `volumes' and also detect this dynamical entanglement.
-
-Our work applies to all quantum systems, irrespective of the size or type of the system, and so constitute fundamental results.
-Moreover, with the concrete protocols we have developed, our predictions should be testable on existing devices, such as IBM or Google's quantum computer.
-Our results shed new light on how quantum physics differs so fundamentally from classical physics, and provide a novel toolkit of broad relevance to contemporary quantum physics research and the development of quantum technologies.
-
-% -- Tools for studying quantum dynamics (a subset of quantum channel theory).
-% }
+On our way to addressing this question, we develop a novel physical framework of thermodynamics, where \nick{microstates of a system can be quasi-probabilistic} and where entropies can attain negative values, which are fully meaningful as indicators of quantum computational speed-ups.
 

### 2021-07-14 cover-letter/cover-letter.tex
Second, better attempt at cover letter and popular summary

@@
 
-\nick{this is supposed to be a ``100-word concise and compelling argument''. Currently: 203 words}
+\nick{this is supposed to be a ``100-word concise and compelling argument''. Currently: 301 words}
 
@@
 
-Our work establishes a connection between two fields within quantum information: quantum thermodynamics and quasi-probability representations of quantum physics.
-This allows for important advances in the subfield of magic theory, an increasingly important area of quantum computation.
+Our work brings together two major fields within quantum information: quantum thermodynamics and quasi-probability representations of quantum physics.
+We combine the two fields in a novel, but natural way leading to the derivation of powerful results which are of interest both in a practical sense to the quantum computing community as well as at a fundamental level to the quantum thermodynamics community.
 
-Primarily, we develop new techniques that provide analytical bounds on general magic state distillation processes.
-We show that our bounds are tighter than previously defined bounds, and importantly can be expressed in terms of the physical symmetries of the circuit in question.
-We therefore provide novel and powerful constraints on the design of magic protocols.
+Primarily, we develop techniques that provide analytical bounds on general magic state distillation processes. 
+Our bounds are tighter than previously defined bounds, and, importantly, they can incorporate and reflect the physical symmetries of the system at question, which can inevitably manifest as some noise bias or temperature threshold of the quantum device.
+We therefore introduce a large family of new and powerful constraints on the design of experimentally implementable magic protocols, which are vital components of fault-tolerant quantum technologies.
+Our work also provides a concrete direction for obtaining lower bounds for magic distillation, \nick{a task which still remains elusive}.
 
-The implications of our analysis are also important foundationally.
-We develop a novel theory of statistical mechanics on quasi-distributions and we further construct entropic functions which attain negative values, a property which acts as a fundamental witness of non-classicality.
+Secondly, the implications of our analysis are also important foundationally, as we develop a novel theory of statistical mechanics on quasi-distributions.
+We develop the first majorization framework which is applicable to quasi-distributions, while providing comprehensive explanations of the unusual features which arise contrasted to common probability distribution settings.
+A prominent example is our construction of entropic functions which attain negative values, hence acting as fundamental witnesses of non-classicality.
 
@@
 
-\nick{this is supposed to be 250 words long. Currently: 243 words}
+\nick{this is supposed to be ``three paragraphs, first should be self-contained summary within summary, second and third more extensive description'', should be at most 250 words long.
+Currently: 264 words}
 
 Quantum computers promise astronomical speed-ups for important computational tasks.
-A practically necessary requirement to achieve such speed-ups for useful computational tasks is establishing a framework that ensures fault-tolerance, which is the ability to correct computational errors in the circuit successfully and reliably.
-It is well-known that restricting to this framework, it is impossible to achieve quantum speed-ups, therefore we need to initiate the circuit with some low-noise input state that contains enough resources which can be used by the circuit to perform the desired computational task.
+A practical requirement to achieve such speed-ups is the ability to correct computational errors during the computation successfully and reliably.
+Having a quantum device with this capability is, however, not sufficient to achieve quantum speed-ups.
+In fact, we need to initiate the computation with some ``magic'' input state which contains enough resources that can be used up during the fault-tolerant steps of the computation by the quantum device.
+We provide novel fundamental bounds on the quantity and quality of the magic input state given the thermodynamic properties of the device.
 
-Creating this low-noise, highly resourceful state, called a ``magic state'', is a costly process, requiring in principle a quantum process that manipulates many highly noisy copies of the magic state in order to distill one with very low noise.
-Our work addresses the question regarding the highest possible rate of low-noise magic states one could extract, given some copies of highly noisy magic states.
-We provide fundamental bounds on this rate, based on the thermodynamic properties of the quantum process, which constraint the efficiency of any general quantum processes attempting to distill magic.
-As our bounds depend on the thermodynamic properties of the process, they notably provide a way of assessing how physical properties affect the distillation process.
+Creating this low-noise, highly resourceful magic state is a costly process, requiring in principle a quantum protocol to distill many highly noisy copies of the desired magic state into a few with very low noise.
+Our bounds restrict the rate at which one can perform this distillation giving the noise levels of the states.
+As our bounds depend on the thermodynamic properties of the process, they notably provide a way of assessing how these properties affect distillation in real implementable protocols, therefore instructing their design.
 
-On our way to addressing this question, we develop a novel physical framework of thermodynamics, where \nick{microstates of a system can be quasi-probabilistic} and where entropies can attain negative values, which are fully meaningful as indicators of quantum computational speed-ups.
+On our way to addressing our main question, we develop a novel physical framework of thermodynamics, where we provide a family of generalised entropies to characterize the disorder of physical quantum processes.
+Our generalised entropies turn out to be quite intriguing, as they can be defined via negative probability representations of the quantum process and can further attain negative values, reversing the direction of the arrow of time.
+The last property acts as an indicator of the quantum computational speed-ups.
 

### 2021-07-16 cover-letter/cover-letter.tex
Cover letter plus summary updated. Minor edits in main text.

--- 2021-07-09 cover-letter/cover-letter.tex
@@
 
-\nick{this is supposed to be a ``100-word concise and compelling argument''. Currently: 203 words}
-
 \vspace{.3cm}
@@
 
-Our work establishes a connection between two fields within quantum information: quantum thermodynamics and quasi-probability representations of quantum physics.
-This allows for important advances in the subfield of magic theory, an increasingly important area of quantum computation.
+A fundamental problem is to understand how quantum physics admits higher degrees of order than possible in classical physics.
+One signature of this non-classical order is the appearance of `negative probabilities' in the Wigner representation of quantum systems.
+However statistical mechanics cannot be directly applied to quantify this order since the Boltzmann entropy is not well-defined when Wigner negativity arises.
+In this work we do two main things: we show how a well-defined statistical mechanics of Wigner negativity can be constructed, and then apply this framework to quantify the order in `magic states', which are the key sources of non-classicality in leading quantum computing models.
 
-Primarily, we develop new techniques that provide analytical bounds on general magic state distillation processes.
-We show that our bounds are tighter than previously defined bounds, and importantly can be expressed in terms of the physical symmetries of the circuit in question.
-We therefore provide novel and powerful constraints on the design of magic protocols.
+It is a major goal to properly understand the processing and `distillation' of magic states for quantum technologies.
+Upper bounds on magic state distillation protocols do exist and are based on abstract information-theoretic measures.
+Our methods outperform existing upper bounds in the literature, and to our knowledge, provide the first general framework to incorporate dependence on hardware physics, such as system Hamiltonians or temperatures.
+As such this approach is relevant to the challenge of designing and building quantum computers.
 
-The implications of our analysis are also important foundationally.
-We develop a novel theory of statistical mechanics on quasi-distributions and we further construct entropic functions which attain negative values, a property which acts as a fundamental witness of non-classicality.
+Our results are also of interest beyond quantum technologies.
+We show that recent research on the thermodynamics of small quantum systems can be extended to Wigner negativity/quasi-distributions.
+To our knowledge, we provide the first application of majorization (a fundamental concept in classical statistics) to quasi-probability distributions, and so open up the possibility of new tools to analyse non-classicality more generally.
+We show that sub-set of classical (R\'{e}nyi) entropies remain meaningful on quasi-distributions and the appearance of negative entropies is a witness of non-classicality in quantum systems.
+Finally, our analysis also raises novel questions relevant to work on classical statistical mechanics.
 
-For the above reasons, we believe that our manuscript is of relevance to a wide audience of quantum physicists, and so is suitable for publication in Phys. Rev. X.
+For the above reasons, we believe that our manuscript is of relevance to a wide audience of quantum physicists, and so is suitable for publication in PRX Quantum.
 
@@
 
-\nick{this is supposed to be 250 words long. Currently: 243 words}
+\ddd{You can use the first paragraph, which is 100 words, for the 100 word summary.
+We can include the cover-letter too, which is not 100 words.
+Find a place to add it in and make it clear e.g.
+in the title, it's a cover letter.
+This way the editor should open it and read it.}
 
-Quantum computers promise astronomical speed-ups for important computational tasks.
-A practically necessary requirement to achieve such speed-ups for useful computational tasks is establishing a framework that ensures fault-tolerance, which is the ability to correct computational errors in the circuit successfully and reliably.
-It is well-known that restricting to this framework, it is impossible to achieve quantum speed-ups, therefore we need to initiate the circuit with some low-noise input state that contains enough resources which can be used by the circuit to perform the desired computational task.
+\nick{this is supposed to be ``three paragraphs, first should be self-contained summary within summary, second and third more extensive description'', should be at most 250 words long.
+Currently: 250 words}
 
-Creating this low-noise, highly resourceful state, called a ``magic state'', is a costly process, requiring in principle a quantum process that manipulates many highly noisy copies of the magic state in order to distill one with very low noise.
-Our work addresses the question regarding the highest possible rate of low-noise magic states one could extract, given some copies of highly noisy magic states.
-We provide fundamental bounds on this rate, based on the thermodynamic properties of the quantum process, which constraint the efficiency of any general quantum processes attempting to distill magic.
-As our bounds depend on the thermodynamic properties of the process, they notably provide a way of assessing how physical properties affect the distillation process.
+A fundamental problem is to understand how quantum physics admits higher degrees of order than classical physics.
+Here we show how quantum-mechanical order can be described in terms of a rigorous statistical mechanics framework in which negative entropies arise.
+We then apply this framework to quantify the order in `magic states' - crucial resources that power quantum computers.
+Our methods outperform existing magic bounds, and provide the first general framework to incorporate dependence on hardware physics, such as system Hamiltonians or temperatures.
+This work is relevant both to quantum technologies and the fundamental challenge of quantifying non-classicality in quantum systems.
 
-On our way to addressing this question, we develop a novel physical framework of thermodynamics, where \nick{microstates of a system can be quasi-probabilistic} and where entropies can attain negative values, which are fully meaningful as indicators of quantum computational speed-ups.
+A signature of non-classical order is the appearance of `negative probabilities' in representations of quantum systems.
+However traditional statistical mechanics cannot be directly applied to negative probabilities.
+We first show how to extend statistical mechanics by using a more fundamental concept of order (`majorization') from statistical theory and then apply this to quantifying the order in magic states.
+
+Quantum computers `burn' magic states as a form of fuel to provide exponential speed-ups for important tasks, such as in computational Chemistry.
+Our results show that this thermodynamic intuition can be made precise and that magic states, in a rigorous sense, carry `negative entropy' that is processed thermodynamically.
+Our methods outperform existing magic bounds in the literature, and to our knowledge, provide the first general framework to incorporate dependence on hardware physics, such as system Hamiltonians or temperatures.
+As such this approach is relevant to the challenge of designing and building quantum computers.
 

### 2021-07-16 ms.tex
Cover letter plus summary updated. Minor edits in main text.

@@
 For example, the XZZX code~\cite{bonilla_ataides_xzzx_2021} is a variant of the surface code that incorporates noise bias explicitly and has been shown to attain the hashing bound of random codes~\cite{Bennett_1996}.
-
 In this work, we develop a framework to analyse magic state distillation protocols where explicit physics of the system is incorporated in the distillation bounds.
@@
 \end{equation}
-
 For any quantum state $\rho$, the Wigner distribution $W_\rho(\bmz)$ is readily seen to be a $d^2$-dimensional quasi-distribution over $\cal{P}_d$.
 More precisely, $W_\rho(\bmz)$ is a real-valued function on $\P_d$ with the normalisation property $\sum_{\bmz} W_\rho(\bmz) = 1$ (see Appendix~\ref{app:wigner} for details).
+Moreover, the above Wigner representation has recently been shown to be the only non-contextual quasi-probability representation of odd-dimensional stabilizer theories for odd prime dimensions~\cite{schmid2021noncontextual}.
 
@@
 where $\bar{\bmz} = (q_1, \dots, q_n, -p_1, \dots, -p_n)$ can be viewed as the time-reversed version of $\bmz$ in the discrete phase space, where momenta are reflected while position coordinates remain unchanged.
-
-\nick{We note that the discrete Wigner representation described in this section is in fact the only non-contextual quasi-probability representation of odd-dimensional stabilizer theories~\cite{schmid2021noncontextual}.
-In particular, negativity within the Wigner representation cannot be eliminated by considering a different quasi-probability representation.
-- look at paragraph starting ``In the setting of the full stabilizer subtheory...'' on page 2 of~\cite{schmid2021noncontextual}}
 
@@
 
-Within the Wigner representation for odd prime dimension, it is well-known that all positively represented states used in Clifford circuits admit an efficient classical description~\cite{cit:mari}, so negativity is a necessary resource for universal fault-tolerant quantum computing~\cite{cit:veitch}.
+Within the Wigner representation for odd prime dimension, it is well-known that all positively represented states used in Clifford circuits admit an efficient classical simulation~\cite{cit:mari}, so negativity is a necessary resource for universal fault-tolerant quantum computing~\cite{cit:veitch}.
 Therefore, the free states in any magic theory are required to be a subset of
@@
 \end{equation}
-To extend to quasi-distributions we must ensure the following: (a) the entropy is well-defined on quasi-distributions, and (b) obeys monotonicity under the majorization pre-order.
+To extend to quasi-distributions we must ensure the following: (a) the entropy is mathematically well-defined on quasi-distributions, and (b) obeys monotonicity under the majorization pre-order.
 In Appendix~\ref{app:single-shot} we prove the following.
@@
 	\end{equation}
-	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ and the average divergence
+	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ and the average divergence per qudit
 	\begin{equation}

### 2021-07-28 cover-letter/Letter to the Editors.tex
changed refs into nature style, changed prxq to npjqi in cover letter

--- 2021-07-16 cover-letter/cover-letter.tex
@@
 One signature of this non-classical order is the appearance of `negative probabilities' in the Wigner representation of quantum systems.
-However statistical mechanics cannot be directly applied to quantify this order since the Boltzmann entropy is not well-defined when Wigner negativity arises.
-In this work we do two main things: we show how a well-defined statistical mechanics of Wigner negativity can be constructed, and then apply this framework to quantify the order in `magic states', which are the key sources of non-classicality in leading quantum computing models.
+However, statistical mechanics cannot be directly applied to quantify this order since the Boltzmann entropy is not well-defined when Wigner negativity arises.
+In this work we do two main things: we construct a well-defined framework of statistical mechanics for Wigner negativity, and then apply it to quantify the order in `magic states', which are the key sources of non-classicality in leading quantum computing models.
 
@@
 Upper bounds on magic state distillation protocols do exist and are based on abstract information-theoretic measures.
-Our methods outperform existing upper bounds in the literature, and to our knowledge, provide the first general framework to incorporate dependence on hardware physics, such as system Hamiltonians or temperatures.
-As such this approach is relevant to the challenge of designing and building quantum computers.
+Our methods outperform existing upper bounds in the literature, and, to our knowledge, provide the first general framework to incorporate dependence on hardware physics, such as system Hamiltonians and temperatures.
+As such, this approach is relevant to the challenge of designing and building quantum computers.
 
 Our results are also of interest beyond quantum technologies.
-We show that recent research on the thermodynamics of small quantum systems can be extended to Wigner negativity/quasi-distributions.
-To our knowledge, we provide the first application of majorization (a fundamental concept in classical statistics) to quasi-probability distributions, and so open up the possibility of new tools to analyse non-classicality more generally.
-We show that sub-set of classical (R\'{e}nyi) entropies remain meaningful on quasi-distributions and the appearance of negative entropies is a witness of non-classicality in quantum systems.
-Finally, our analysis also raises novel questions relevant to work on classical statistical mechanics.
+We show that recent research on the thermodynamics of small quantum systems can be extended to Wigner negativity and quasi-probability distributions.
+To our knowledge, we provide the first application of majorization (a fundamental concept in classical statistics) on quasi-distributions, and so open up the possibility of new tools to analyse non-classicality more generally.
+We show that a sub-set of classical (R\'{e}nyi) entropies remain meaningful on quasi-distributions and that the appearance of negative entropies is a witness of non-classicality in quantum systems.
+Finally, our analysis also raises novel questions relevant to work on statistical mechanics.
 
@@
 \end{minipage}
-\newpage
-
-\textbf{Popular Summary}
-
-\ddd{You can use the first paragraph, which is 100 words, for the 100 word summary.
-We can include the cover-letter too, which is not 100 words.
-Find a place to add it in and make it clear e.g.
-in the title, it's a cover letter.
-This way the editor should open it and read it.}
-
-\nick{this is supposed to be ``three paragraphs, first should be self-contained summary within summary, second and third more extensive description'', should be at most 250 words long.
-Currently: 250 words}
-
-A fundamental problem is to understand how quantum physics admits higher degrees of order than classical physics.
-Here we show how quantum-mechanical order can be described in terms of a rigorous statistical mechanics framework in which negative entropies arise.
-We then apply this framework to quantify the order in `magic states' - crucial resources that power quantum computers.
-Our methods outperform existing magic bounds, and provide the first general framework to incorporate dependence on hardware physics, such as system Hamiltonians or temperatures.
-This work is relevant both to quantum technologies and the fundamental challenge of quantifying non-classicality in quantum systems.
-
-A signature of non-classical order is the appearance of `negative probabilities' in representations of quantum systems.
-However traditional statistical mechanics cannot be directly applied to negative probabilities.
-We first show how to extend statistical mechanics by using a more fundamental concept of order (`majorization') from statistical theory and then apply this to quantifying the order in magic states.
-
-Quantum computers `burn' magic states as a form of fuel to provide exponential speed-ups for important tasks, such as in computational Chemistry.
-Our results show that this thermodynamic intuition can be made precise and that magic states, in a rigorous sense, carry `negative entropy' that is processed thermodynamically.
-Our methods outperform existing magic bounds in the literature, and to our knowledge, provide the first general framework to incorporate dependence on hardware physics, such as system Hamiltonians or temperatures.
-As such this approach is relevant to the challenge of designing and building quantum computers.
 

### 2021-07-29 cover-letter/cover-letter.tex
Rewrote cover letter + fixed refs

--- 2021-07-09 cover-letter/cover-letter.tex
@@
 \vspace{-1.5cm}
-Dear Editors of PRX Quantum,
-
-\nick{this is supposed to be a ``100-word concise and compelling argument''. Currently: 203 words}
+Dear Editors of npj Quantum Information,
 
@@
 
-Please find enclosed a copy of our manuscript \emph{``Constraints on magic state protocols from the statistical mechanics of Wigner negativity''}, which we would like to submit for review in PRX Quantum.
-We believe our work fits naturally into the scope of the journal.
+Please find enclosed a copy of our manuscript \emph{``Constraints on magic state protocols from the statistical mechanics of Wigner negativity''}, which we would like to submit for review in npj Quantum Information.
+Our work provides fundamental restrictions on `magic' protocols, a leading model of fault-tolernat quantum computing, therefore we believe our methods and results are relevant to the audience of the journal.
 
-Our work establishes a connection between two fields within quantum information: quantum thermodynamics and quasi-probability representations of quantum physics.
-This allows for important advances in the subfield of magic theory, an increasingly important area of quantum computation.
+A fundamental problem is to understand how quantum physics admits higher degrees of order than possible in classical physics.
+One signature of this non-classical order is the appearance of `negative probabilities' in the Wigner representation of quantum systems.
+However, statistical mechanics cannot be directly applied to quantify this order since the Boltzmann entropy is not well-defined when Wigner negativity arises.
+In this work, we construct a well-defined framework of statistical mechanics for Wigner negativity, and then apply it to quantify the order in `magic states', which are the key sources of non-classicality in leading quantum computing models.
 
-Primarily, we develop new techniques that provide analytical bounds on general magic state distillation processes.
-We show that our bounds are tighter than previously defined bounds, and importantly can be expressed in terms of the physical symmetries of the circuit in question.
-We therefore provide novel and powerful constraints on the design of magic protocols.
+It is a major goal within the quantum computing community to properly understand the processing and `distillation' of magic states for quantum technologies.
+Several distillation protocols exist, each effectively providing a low bound on the distillation rate of magic states.
+However, upper bounds on distillation protocols express restrictions on our ability to distill magic states.
+Some upper bounds do exist, but they are based on abstract information-theoretic measures.
+Our novel methods of deriving upper bounds via Wigner negativity statistics result in an infinite family of new upper bounds.
+This new family of bounds outperforms existing upper bounds in the literature, and, to our knowledge, provides the first general framework to incorporate dependence on hardware physics.
+In particular, our bounds attain different optimal values depending on the specific quantum computer architectures.
+The architectural properties that dictate this can, for example, be some temperature threshold or noise bias of the device or a fixed-point structure associated with a restriction in the allowed quantum gates.
+As such, this approach is relevant to the challenge of designing and building quantum computers.
 
-The implications of our analysis are also important foundationally.
-We develop a novel theory of statistical mechanics on quasi-distributions and we further construct entropic functions which attain negative values, a property which acts as a fundamental witness of non-classicality.
+Our methods also provide for the first time a clear path towards deriving fundamental lower bounds on magic distillation rates by exploiting the underlying statistical structure of magic states.
+Therefore, it is possible to sharpen current distillation rates, thereby potentially closing the gap between experimentally achievable and theoretically possible distillation rates.
 
-For the above reasons, we believe that our manuscript is of relevance to a wide audience of quantum physicists, and so is suitable for publication in Phys. Rev. X.
+Finally, our results are of interest beyond quantum technologies.
+We show that recent research on the thermodynamics of small quantum systems can be extended to Wigner negativity and quasi-probability distributions.
+As an example, we show that a sub-set of classical (R\'{e}nyi) entropies remain meaningful on quasi-distributions, while they can attain negative values, thus acting as witnesses of non-classicality in quantum systems.
+
+For the above reasons, we believe that our manuscript can communicate significant novel methods, while already providing powerful results within the quantum computing community, and so is suitable for publication in npj Quantum Information.
 
@@
 \end{minipage}
-\newpage
-
-\textbf{Popular Summary}
-
-\nick{this is supposed to be 250 words long. Currently: 243 words}
-
-Quantum computers promise astronomical speed-ups for important computational tasks.
-A practically necessary requirement to achieve such speed-ups for useful computational tasks is establishing a framework that ensures fault-tolerance, which is the ability to correct computational errors in the circuit successfully and reliably.
-It is well-known that restricting to this framework, it is impossible to achieve quantum speed-ups, therefore we need to initiate the circuit with some low-noise input state that contains enough resources which can be used by the circuit to perform the desired computational task.
-
-Creating this low-noise, highly resourceful state, called a ``magic state'', is a costly process, requiring in principle a quantum process that manipulates many highly noisy copies of the magic state in order to distill one with very low noise.
-Our work addresses the question regarding the highest possible rate of low-noise magic states one could extract, given some copies of highly noisy magic states.
-We provide fundamental bounds on this rate, based on the thermodynamic properties of the quantum process, which constraint the efficiency of any general quantum processes attempting to distill magic.
-As our bounds depend on the thermodynamic properties of the process, they notably provide a way of assessing how physical properties affect the distillation process.
-
-On our way to addressing this question, we develop a novel physical framework of thermodynamics, where \nick{microstates of a system can be quasi-probabilistic} and where entropies can attain negative values, which are fully meaningful as indicators of quantum computational speed-ups.
 

### 2021-07-30 cover-letter/cover-letter.tex
Cover letter edited.

@@
 Please find enclosed a copy of our manuscript \emph{``Constraints on magic state protocols from the statistical mechanics of Wigner negativity''}, which we would like to submit for review in npj Quantum Information.
-Our work provides fundamental restrictions on `magic' protocols, a leading model of fault-tolernat quantum computing, therefore we believe our methods and results are relevant to the audience of the journal.
+Our work provides fundamental restrictions on `magic' protocols, a leading model of fault-tolerant quantum computing, that are novel in allowing the inclusion of fundamental hardware physics.
+We believe our methods and results are relevant to the audience of the journal.
 
@@
 Some upper bounds do exist, but they are based on abstract information-theoretic measures.
-Our novel methods of deriving upper bounds via Wigner negativity statistics result in an infinite family of new upper bounds.
+Our novel methods of deriving upper bounds via Wigner negativity statistics result in a family of new upper bounds.
 This new family of bounds outperforms existing upper bounds in the literature, and, to our knowledge, provides the first general framework to incorporate dependence on hardware physics.
@@
 
-Our methods also provide for the first time a clear path towards deriving fundamental lower bounds on magic distillation rates by exploiting the underlying statistical structure of magic states.
+%Our methods also provide for the first time a clear path towards deriving fundamental lower bounds on magic distillation rates by exploiting the underlying statistical structure of magic states.
 Therefore, it is possible to sharpen current distillation rates, thereby potentially closing the gap between experimentally achievable and theoretically possible distillation rates.
 
-Finally, our results are of interest beyond quantum technologies.
+Our results are also of interest to other areas in quantum information science.
 We show that recent research on the thermodynamics of small quantum systems can be extended to Wigner negativity and quasi-probability distributions.
@@
 
-For the above reasons, we believe that our manuscript can communicate significant novel methods, while already providing powerful results within the quantum computing community, and so is suitable for publication in npj Quantum Information.
+For the above reasons, we believe that our manuscript provides significant novel results that connect active areas of research, and so is suitable for publication in npj Quantum Information.
 

### 2021-12-15 npj_revisions/referee_responses.tex
halfway thru revisions

\documentclass[11pt]{letter}

\usepackage[colorlinks=true,urlcolor=blue, hyperindex,breaklinks=true] {hyperref}

\usepackage{graphicx}
\usepackage[a4paper,left=2cm,right=2cm,bottom=2cm]{geometry}
\usepackage{fancyhdr}
\usepackage[table,xcdraw,dvipsnames]{xcolor}

\usepackage{amsmath,amsfonts, amssymb, amsthm}
\usepackage{bm, bbm, physics, mathtools}

\renewcommand*\rmdefault{ppl}

\newcommand{\nick}[1]{\textcolor{red}{[#1]}}
\newcommand{\ddd}[1]{\textcolor{blue}{[#1]}}

\pagestyle{empty}
\input{preamble_mathchars.sty}

\begin{document}

Dear Prof. Sven Rogge,

Thank you for passing on the Reviewers' recommendations.
In this letter, we address the revisions suggested by both Reviewers, by responding to questions raised and describing the resultant changes which can be found highlighted in the current version of the manuscript.\\

\textbf{\large{Response to Reviewer 1}}\\

\textit{In this work, the authors have derived new constraints on the rate of magic state distillation routines for qudits of odd prime dimension, making use of the discrete Wigner function representation. One of the main reasons qudit magic state distillation is of theoretical interest is that it appears possible to develop a powerful resource theory for fault-tolerant quantum computation in odd dimensions, largely due to the discrete Wigner function representation, which only exists for odd-dimensional qudits.}

\textit{Their essential technique is to apply the theory of majorization, which they review in the paper, to the discrete Wigner function, which is a quasi-probability distribution. Essentially one quasi-distribution p can be transformed to another quasi-probability distribution q by a stochastic transformation if and only if p majorizes q (this can be taken as the definition of majorization, but there are other equivalent definitions). One can show that p majorizes q if and only if the Lorenz curve of p is greater than or equal to that of q everywhere. These types of results were previously known for probability distributions, but the authors show that these arguments can also be applied to quasi-probability distributions (assuming the reference distribution is strictly positive).}

\textit{They apply their results to qutrit magic state distillation, mainly for distillation of the qutrit strange state, which is the simplest and most important magic state to consider. The bounds they derive are clearly much stronger than previously known bounds on magic state distillation in the literature, based on mana and thauma. In fact, the monotonicity of mana as a resource follows as a special case of their majorization arguments.}

\textit{They also discuss the case of finite temperature, which shows that their method can be generalized to a variety of situations.}

\textit{They also show that one can define Renyi entropies for quasi-probability distributions, and derive an elegant interpretation of the mana as the residue of a pole quantifying the divergence of the Renyi entropy as it approaches the Shannon entropy.}

\textit{Overall, the results of the paper appear to me to be novel, topical, and mathematically elegant. I also found the paper to be well-written. I therefore strongly recommend it for publication.}

We thank the Reviewer for the positive comments.

\textit{However, I have one suggestion that could be included in a minor revision:}

\textit{The main result of the authors seems to rest on Theorem 1, which in turn relies on the unnumbered result on page 5, after equation (15), which states roughly that “relative majorization holds between pairs of probability distributions holds if the Lorenz curve of one is greater than or equal to the Lorenz curve of the other, for all x.” The authors refer to [103] for a proof of this fact. However, I think it would substantially enhance accessibility and readability if the authors could give a proof of this result within the present paper, perhaps in an appendix.}

We are grateful for suggestion on making our results more accessible.
To this end, we have added a proof of the result in Appendix~B1, relying on the assumption that the result is clear for simple majorization (i.e. when $\r = \r'= (1/N,1/N,\dots,1/N)$) as shown in~[81]. 
In general, we consider statements about simple majorization (presented in Marshall \& Olkin [81]) as well-established in the quantum information community and do not prove them in our paper.
As a side remark, the original proof of this result in the context of relative majorization can be found in [111], not [103].

\textit{A side remark: As I understand, Lorenz curves were initially defined in economics to describe the income distribution of a population. It seems possible for some individuals to lose money during the year, so the distribution of incomes in a population is in general, more analogous to a quasi-probability distribution rather than a probability distribution. So, perhaps some of the basic results of the paper may also be applicable, in principle, to a wider context in economics.}

\nick{David, thoughts on bounding wealth distillation?}\\

\textbf{\large{Response to Reviewer 2}}\\

\textit{A universal gate set for quantum computing is a set of unitary operators such that it can approximate any unitary to arbitrary accuracy. As quantum circuits will employ error correcting codes, we require universal gate set such that gates can be performed fault tolerantly, i.e. can be implemented on qubits encoded in an error correcting code without spreading errors. Sets of universal gates that can be performed on a quantum error correcting code often fall into a natural separation (based on the choice of code). There are gates that are "naturally" fault tolerant, and gates that are difficult to perform in a fault-tolerant manner. In most popular choices of error correcting code to encode qubits, the former corresponds to unitary operators in the Clifford group, and the latter to unitary operator not generated by the Clifford group. These gates outside the orbit of the Clifford group are a central object of study. The closely associated states, sometimes also referred to as magic
states, are notoriously hard to prepare. It is an important question in quantum computation to understand their structure.}

\textit{Authors have made an important fundamental contribution by illuminating the relationship between these states. They have shown that these states obey a partial order based on majorization. Majorization is a partial order on vectors and is often studied when these vectors are normalized probability distributions. A probability distribution p majorizes a distribution q if we can obtain q from p by a permutation or a convex combination of permutations. Majorization is an important way of characterizing other quantities in quantum information, most famously in entanglement transformation under LOCC. However, it is present in other contexts as well such as quantum thermodynamics.}

\textit{The framework authors use is that of a resource theory. This classifies (quantum) operations into easy (free operations) and difficult (resource operations/states). The induced partial order determines whether we can transform one magic state into another and simultaneously leave a particular state fixed. Each magic state defines a "Lorenz curve". To be precise, each magic state is associated with a quasi-probability distribution called the discrete Wigner function discovered by Wootters and later by Gross. By "balancing" potentially negative values of the Wigner function with the Wigner function of some fixed, positive distribution, we can everywhere deal with positive distributions. It is then possible to sensibly define a partial order with respect to transformations under stochastic maps and majorization as commonly defined.}

\textit{Interestingly, previous metrics, such as mana proposed by Veitch et al., can be obtained from this more fundamental quantity. Authors then proceed to show that this realization can be used to upper bound the rate of magic transformation in the context of strange state, a particular magic state for qutrits. They also study limits of magic transformation by providing each qudit with a Hamiltonian and understanding temperature dependent transformations.}

\textit{This is a strong result. However, before accepting for publication, I would like authors to address some comments.
Questions/comments for the authors:}

\textit{1. In section 3C, an upper bound on the rate of distillation for qutrit magic states is presented. However, we do not see an explicit scheme that can actually achieve this bound. Some comments on whether this bound is achievable would be appreciated.}

\nick{ANSWER}

\textit{In the conclusions, short discussion on lower bounds can be lengthened. Does this require explicit error correcting codes for distillation?}

\nick{David, do you want to take this one? -- your previous notes are accessible on GitHub for copy-pasting}

\nick{I haven't added lines on this in the main text}

\textit{2. It was shown by Bengtsson et al. that qudit magic states for prime-dimensional qudits, where the prime p is 1 mod 3, there exist distinct magic states under distinct orbits of the Clifford group. In other words, there exist magic states such that we cannot convert from one to other using only Clifford operations. Can authors reproduce this result using their theory?}

\nick{I haven't had the time to consider this yet. In principle, we would need to find $R_\alpha = 0$ for some $\alpha$ and reference process, given a magic interconversion between Clifford non-equivalent magic states -- seems tough and numerically doesn't look to be the case for the Strange and Norrell states ($d=3$, does not fall under Bengtsson et al's results)}

\textit{3. Perhaps authors have already mentioned this, but Clifford operations can also be supplemented by Pauli measurements and adaptive gates. In the main text, as well as in conclusions (comments about G-majorization) this is not mentioned. Would this lead to distinct/ refined bounds?}

This is a very interesting question from the lens of implementing our results on actual distillation protocols.
According to Jozsa and Van den Nest's work\footnote{Jozsa R and Van den Nest M (2013) Classical simulation complexity of extended Clifford circuits, arXiv:1305.6190}, an $N$-qudit circuit consisting of intermediate measurements and adaptive Clifford gates is always equivalent to an $(N+k)$-qudit circuit ($k \in \mathbb{N}$) consisting of a Clifford gate.
Therefore, our bounds are directly applicable on the equivalent circuit.

In more general scenarios, suppose we project an $n$-copy state $\rho$ with projector $P$, which has success probabilty $p$. This can be written as
\begin{equation}
	\cal{E}(\rho) = p\ \tr_{i=1,\dots,n-1} [P\rho P] \otimes \ketbra{0} + (1-p)\ \tr[(\id-P)\rho] \sigma \otimes \ketbra{1},
\end{equation}
where the last subsystem is labelled $0$ when the projection is successful and 1 when it is not.
Then, $\E$ admits a stochastic Wigner representation and in principle our results can provide bounds on the distillation ratio $\frac{pm}{n}$.
However, one complication arises due to this operational representation of projective measurements, namely that states are no longer product states and the entropic functions are not guaranteed to factor out nicely (Theorem 11 property 3).

\nick{I haven't added lines on this in the main text}

\textit{4. Is it possible that the bounds in a more refined form will depend on the prime dimension of the qudit?}

Yes, this is already clear in Eq.(52) obtained by restricting to unital channels.
\nick{What about more refined, unrestricted bounds? I am not sure this is a well-defined question, as the bounds implicitly depend on the dimension via the states considered. The question seems motivated from the context of real distillation protocols, where the overhead scaling $\gamma$ tends to depend on the dimension e.g. Krishna and Tillich (2019) Towards Low Overhead Magic State Distillation.}

We further note that the numerically optimal bounds presented in Fig.(1), for which we do not have explicit expressions, depend on the numbers of copies $n,m$ and therefore are not constant for a given ratio $m/n$.

\textit{5. In optics, the Wigner function is not the only quasi-probability distribution. Indeed, there are the P and Q distributions and potentially a continuous spectrum of quasiprobability distributions. In the discrete setting the Wigner function occupies a special role because of Gross' work showing that stabilizer states can be represented positively for prime-power dimensions and other useful properties like Clifford covariance. However is it possible that the other distributions offer extra information not captured by the Wigner distribution? Can we use a discrete analogue of the P and Q distributions?}

We particularly welcome this question as it relates to some of the authors' current research.
Firstly, we stress that in odd prime dimensions Gross' Wigner function is the only non-contextual quasi-probability representation of stabilizer theories (see~[101]), and contextuality has been shown to be equivalent to magic (see~[44]), as understood in the resource-theoretic formalism.
Therefore, using different distributions, would in general represent negatively states and channels that are operationally ``free'', while simultaneously representing positively states and operations that are not operationally free, thus shifting the role of our bounds as fundamental bounds on \emph{magic distillation} protocols.

Having noted the above, we are claiming (in upcoming work) that using different distributions offers useful additional information in the context of classical simulability of general quantum circuits.
Indeed, the P and Q quasi-distributions as well as the entire spectrum of s-ordered quasi-distributions introduced by Cahill and Glauber\footnote{Cahill K E and Glauber R J (1969) Ordered expansions in boson amplitude operators, Phys. Rev. 177 1857} find discrete analogues in Ruzzi \textit{et al.}'s work\footnote{Ruzzi M \textit{et al.} (2005) Extended Cahill-Glauber formalism for finite dimensional spaces: I. Fundamentals, J. Phys. A: Math. Gen. 38 6239}.
In our work we come up with different infinite families of quasi-probability representations, but the core idea is the same: the probability outcome of a general quantum circuit can be estimated via Monte Carlo sampling\footnote{Pashayan H (2015) Estimating Outcome Probabilities of Quantum Circuits Using Quasiprobabilities, Phys. Rev. Lett. 115, 070501}, and using different quasi-distributions for representing different circuit components can reduce the sampling overhead.
More specifically, the number of samples required for a probability estimate, which converges well to the actual circuit outcome, scales as a function of the negativities of the distributions that represent the circuit components. Therefore, different quasi-distribution representations can result in greater reduction of the negativity overhead compared to the Wigner representation.

\end{document}

### 2021-12-15 cover_letter/cover-letter.tex
halfway thru revisions

--- 2021-07-30 cover-letter/cover-letter.tex
@@
 Please find enclosed a copy of our manuscript \emph{``Constraints on magic state protocols from the statistical mechanics of Wigner negativity''}, which we would like to submit for review in npj Quantum Information.
-Our work provides fundamental restrictions on `magic' protocols, a leading model of fault-tolerant quantum computing, that are novel in allowing the inclusion of fundamental hardware physics.
+Our work provides fundamental restrictions on `magic' protocols, a leading model of fault-tolerant quantum computing, that are novel in their ability to include experimental hardware limitations.
 We believe our methods and results are relevant to the audience of the journal.
@@
 However, statistical mechanics cannot be directly applied to quantify this order since the Boltzmann entropy is not well-defined when Wigner negativity arises.
-In this work, we construct a well-defined framework of statistical mechanics for Wigner negativity, and then apply it to quantify the order in `magic states', which are the key sources of non-classicality in leading quantum computing models.
+In this work, we construct a well-defined framework of statistical mechanics for Wigner negativity, and then apply it to quantify the order in magic states, which are the key sources of non-classicality in leading quantum computing models.
 
@@
 In particular, our bounds attain different optimal values depending on the specific quantum computer architectures.
-The architectural properties that dictate this can, for example, be some temperature threshold or noise bias of the device or a fixed-point structure associated with a restriction in the allowed quantum gates.
+The architectural properties that dictate optimality can, for example, be some temperature threshold or noise bias of the device or a fixed-point structure associated with a restriction in the allowed quantum gates.
 As such, this approach is relevant to the challenge of designing and building quantum computers.
@@
 
-For the above reasons, we believe that our manuscript provides significant novel results that connect active areas of research, and so is suitable for publication in npj Quantum Information.
+For the above reasons, we believe that our manuscript provides significant novel methods and results that connect active areas of research, and so is suitable for publication in npj Quantum Information.
 

### 2021-12-15 ms.tex
changed refs into nature style, changed prxq to npjqi in cover letter
Rewrote cover letter + fixed refs
halfway thru revisions

@@
 ]{revtex4-1}
+
+%\usepackage[columnwise,switch,displaymath,mathlines]{lineno}
+%\linenumbers
 
@@
 More precisely, $W_\rho(\bmz)$ is a real-valued function on $\P_d$ with the normalisation property $\sum_{\bmz} W_\rho(\bmz) = 1$ (see Appendix~\ref{app:wigner} for details).
-Moreover, the above Wigner representation has recently been shown to be the only non-contextual quasi-probability representation of odd-dimensional stabilizer theories for odd prime dimensions~\cite{schmid2021noncontextual}.
+Moreover, the above Wigner representation has recently been shown to be the only non-contextual quasi-probability representation of stabilizer theories in odd prime dimensions~\cite{schmid2021noncontextual}.
 
@@
 We can now define the \emph{Lorenz curve} of $\w$ relative to $\r$, denoted $L_{\w|\r}(x)$, as the piece-wise linear function that passes through $(0,0)$ and the $n$ points
-\begin{equation}
-\label{eq:lc}
+\begin{equation}\label{eq:lc}
 	(x_k,L_{\w|\r}(x_k)) =\left( \frac{1}{R}\sum_{i=1}^k r_{\pi(i)}, \sum_{i=1}^k w_{\pi(i)} \right),
@@
 The value $L_{\w|\r}(x) = 1$ is a global maximum.
-Moreover, if $\w, \w', \r, \r'$ are all valid probability distributions with $\r,\r'$ having positive components then it can be shown~\cite{ruch_mixing_1978} that
+Moreover, if $\w, \w', \r, \r'$ are all valid probability distributions with $\r,\r'$ having positive components, then
 \begin{equation*}
@@
 for all $x \in [0,1]$. 
-This provides a simple way of computing whether relative majorization holds between pairs of probability distributions.
+\revhigh{This result is shown in~\cite{ruch_mixing_1978} and we reproduce it in Appendix~\ref{app:rel_quasi}.}
+It provides a simple way of computing whether relative majorization holds between pairs of probability distributions.
 
@@
 In terms of a Lorenz curve condition we have that $(\w_\epsilon , \r) \succ (\w_\epsilon', \r')$ if and only if $L_{\w_\epsilon |\r} (x) \ge L_{\w'_\epsilon |\r'} (x)$ for all $x \in [0,1]$. 
-Additionally, we show in the appendices (Proposition~\ref{Lorenz_linearity}) that the Lorenz curve for any quasi-distribution obeys the relation
+Additionally, we show in \revhigh{Appendix~\ref{app:rel_quasi}} that the Lorenz curve for any quasi-distribution obeys the relation
 \begin{equation}
@@
 We can now apply this to obtain a family of magic distillation bounds based on R\'{e}nyi divergences.
+
 \begin{theorem}\label{thm:entropic_bounds}
@@
 In particular for the case of noisy Strange states on qutrits and $\epsilon'=0$, this bound becomes
+
 \begin{equation}
@@
 
-\section{Acknowledgements}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\bibliography{bib}
+\bibliographystyle{naturemag}
+%\bibliography{ms.bbl}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section*{Acknowledgements}
 We thank Earl Campbell, Matteo Lostaglio, Philippe Faist and Nicole Yunger Halpern for helpful comments and discussions.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\bibliography{bib}
-%\bibliographystyle{apsrev4-2}
-%\input{ms.bbl}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Author contributions}
+DJ conceived the theoretical idea. 
+Calculations were performed by NK. 
+Analysis and writing of the manuscript were jointly done by NK and DJ.
+
+\section*{Competing interests}
+The authors declare that there are no competing interests.
+
+\section*{Data availability}
+No datasets were generated or analysed during the current study.
 
@@
 
-We define a Lorenz curve \emph{elbow} as a point where the slope of the curve changes, in accordance to the use of the term for Lorenz curves of proper probability distributions.
-
-Here, we verify useful majorization properties in the context of quasi-probability distributions, starting from the property that the Lorenz curve is concave.
+We prove the following result connecting majorization to relative majorization~\cite{cit:horodecki2013, Brandao_2015,  cit:lostaglio}.
+\begin{proposition}\label{relmaj2maj}
+	Let $\w \in \mathbb{R}^N, \w' \in \mathbb{R}^{N'}$ be quasi-distributions and $\r \in \mathbb{R}^N, \r' \in \mathbb{R}^{N'}$ probability distributions with positive rational entries given by $r_i = a_i/K$ and $r_i' = a_i'/K$ for positive integers $a_i, a_i'$ and $K = \sum_{i=1}^N a_i = \sum_{i=1}^{N'} a_i'$.
+Then,
+\begin{equation}
+(\w, \r) \succ (\w', \r') \mbox{ if and only if } \Gamma_{\bma} (\w) \succ \Gamma_{\bma'} (\w'),
+\end{equation}
+where the embedding map $\Gamma_{\bma} :\mathbb{R}^N \rightarrow \mathbb{R}^K$ is given by
+\begin{equation}
+	\Gamma_{\bma}(\bmz) \coloneqq \bigoplus_{i=1}^N z_i \bmeta_{a_i},
+\end{equation}
+with $\bmeta_{a_i} = (1/a_i, 1/a_i, \dots, 1/a_i)$ the uniform distribution on $a_i$ elements.
+\end{proposition}
+\begin{proof}
+	We first note that the map $\Gamma_{\bma}$ is stochastic and has a well-defined left-inverse $\Gamma^{-1}_{\bma}: \mathbb{R}^K \rightarrow \mathbb{R}^N$ given by
+\begin{equation}
+	\Gamma^{-1}_{\bma}(\x) = \left( \sum_{i=1}^{a_1} x_i,  \sum_{i = a_1 +1}^{a_1 + a_2} \hspace{-5pt} x_i, \dots , \hspace{-15pt} \sum_{i=a_1 + \dots + a_{N-1}+1}^{K} \hspace{-10pt} x_i \right),
+\end{equation}
+that obeys $(\Gamma^{-1}_{\bma} \circ \Gamma_{\bma}) (\bmz) = \bmz$ for all $\bmz \in \mathbb{R}^N$.
+
+The claim is equivalent to the statement that there exists a \emph{bistochastic map} $B$ sending $\Gamma_{\bma}(\w)$ to $\Gamma_{\bma'}(\w')$ if and only if there exists a stochastic map $A$ sending $\w$ to $\w'$ and $\r$ to $\r'$.
+
+Suppose there is a stochastic map $A$ such that $A\w=\w'$ and $A\r = \r'$. 
+We define $B:\mathbb{R}^K \mapsto \mathbb{R}^K$ by $B \coloneqq \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1}$ so that it is stochastic as a composition of stochastic maps and it preserves the uniform distribution in $\mathbb{R}^K$, since
+\begin{align}
+	&B(1/K, 1/K, \dots, 1/K) = \big( \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1} \big) \big( \Gamma_{\bma'}(\r) \big) = \nonumber\\
+	&\Gamma_{\bma'} (\r') = (1/K, 1/K, \dots, 1/K),
+\end{align}
+therefore $B$ is bistochastic.
+Finally, $B$ maps the embedded distributions as follows,
+\begin{equation}
+	B \Gamma_{\bma}(\w) = \big( \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1} \big) \big( \Gamma_{\bma}(\w) \big) = \Gamma_{\bma'} (\w').
+\end{equation}
+
+Conversely, suppose a bistochastic map $B$ exists sending $\Gamma_{\bma}(\w)$ to $\Gamma_{\bma'}(\w')$.
+Again, define $A: \mathbb{R}^N \mapsto \mathbb{R}^{N'}$ by $A \coloneqq \Gamma_{\bma'}^{-1} \circ B \circ \Gamma_{\bma}$ so that it is stochastic as a composition of stochastic maps and $A \w = \big( \Gamma_{\bma'}^{-1} \circ B \circ \Gamma_{\bma} \big) \w = \w'$, as well as $A \r = \r'$.
+\end{proof}
+We note that the vectors $\r, \r'$ with rational components form a dense subset of the positive probability distributions, and do not consider further technicalities that have no impact on actual physical measurements, which always have a finite resolution.
+
+\revhigh{
+Restricting the above result in the context of proper probability distributions, we can immediately prove the Lorenz curve condition for probability distributions.
+We first need to define a Lorenz curve \emph{elbow} as a point where the slope of the curve changes, expressed explicitly in~Eq.~(\ref{eq:lc}) for Lorenz curve $L_{\w | \r}(x)$
+\begin{proposition}\label{thm:lc_equiv_prob}
+    Given probability distributions $\w, \r \in \mathbb{R}^{N}$ and $\w', \r' \in \mathbb{R}^{N'}$ with $\r,\r'$ having positive components, then
+\begin{equation*}
+	(\w, \r) \succ (\w', \r') \mbox{ if and only if } L_{\w |\r}(x) \ge L_{\w' |\r'}(x),
+\end{equation*}
+for all $x \in [0,1]$.
+\end{proposition}
+\begin{proof}
+	In the case of $N=N'$ and $\r = \r' = \bmeta$, where $\bmeta = (1/N,1/N,\dots, 1/N)$ is the uniform distribution on $N$ elements, the statement reduces to the Lorenz curve condition for simple majorization which is proven in~\cite{cit:marshall}.
+
+Borrowing the notation of Proposition~\ref{relmaj2maj}, we can define $\Gamma_{\bma} (\w), \Gamma_{\bma'} (\w')$ and the uniform distribution $\bmeta = (1/K, 1/K, \dots, 1/K)$.
+We can then see that the Lorenz curve of $\w$ relative to $\r$ coincides with the Lorenz curve of $\Gamma_{\bma} (\w)$, i.e.
+\begin{equation}
+	L_{\w | \r}(x) = L_{\Gamma_{\bma} (\w) | \bmeta}(x)\ \mbox{for all } x \in [0,1].
+\end{equation}
+This is clear to see by considering the elbows of $L_{\w | \r}(x)$,
+\begin{equation}
+	(x_k, L_{\w|\r}(x_k)) = \left( \sum_{i=1}^k r_{\pi(i)}, \sum_{i=1}^k w_{\pi(i)} \right),
+\end{equation}
+where permutation $\pi$ sorts $(w_i/r_i)$ in non-increasing order.
+Expressing $\Gamma_{\bma} (\w)$ as
+\begin{equation}
+	\Gamma_{\bma} (\w) = \frac{1}{K} \bigoplus_{i=1}^N \left( \frac{w_i}{r_i}, \dots, \frac{w_i}{r_i} \right),
+\end{equation}
+where $(w_i/r_i, \dots, w_i/r_i)$ has $a_i$ elements, it is clear that permutation $\pi$ sorts $\Gamma_{\bma}(\w)$ in non-increasing order too.
+The elbows of $(y_k, L_{\Gamma_{\bma} (\w) | \bmeta}(y_k))$ then occur at
+\begin{equation}
+	y_k = \sum_{j=1}^{a_{\pi(1)} + \dots + a_{\pi(k)}} \frac{1}{K} = \sum_{i=1}^k \frac{a_{\pi(i)}}{K} = x_k
+\end{equation}
+and take values
+\begin{equation}
+	L_{\Gamma_{\bma} (\w) | \bmeta}(y_k) = \sum_{i=1}^k a_{\pi(i)}\frac{1}{K}\frac{w_{\pi(i)}}{r_{\pi(i)}} = L_{\w|\r}(x_k).
+\end{equation}
+This argument holds for $\w', \r'$ and $\Gamma_{\bma'} (\w')$ too.
+
+Therefore, in the general case of relative majorization, we have
+\begin{align}
+	&(\w, \r) \succ (\w', \r') &\mbox{ iff} \nonumber\\
+	&\Gamma_{\bma} (\w) \succ \Gamma_{\bma'} (\w') &\mbox{ iff} \nonumber\\
+	&L_{\Gamma_{\bma} (\w) | \bmeta}(x) \geq L_{\Gamma_{\bma'} (\w') | \bmeta}(x),\ x \in [0,1] &\mbox{ iff} \nonumber\\
+	&L_{\w | \r}(x) \geq L_{\w' | \r'}(x),\ x \in [0,1],
+\end{align}
+concluding the proof.
+\end{proof}
+}
+
+We now verify useful majorization properties in the context of quasi-probability distributions, starting from the property that the Lorenz curve is concave.
 \begin{proposition}\label{L-concave} 
@@
 
-The following result is used in Sec.~\ref{sec:lc} to prove that the Lorenz curve condition due to relative majorization is true for quasi-distributions.
+The following result is used in Sec.~\ref{sec:lc} to extend the Lorenz curve condition of Proposition~\ref{thm:lc_equiv_prob} into the context of quasi-distributions.
 \begin{proposition}\label{Lorenz_linearity}
@@
 \end{proof}
-
-We prove the following result connecting majorization to relative majorization~\cite{cit:horodecki2013, Brandao_2015,  cit:lostaglio}.
-\begin{proposition}\label{relmaj2maj}
-	Let $\w\in \mathbb{R}^N, \w'\in \mathbb{R}^{N'}$ be quasi-distributions and $\r\in \mathbb{R}^N, \r'\in \mathbb{R}^{N'}$ probability distributions with positive rational entries given by $r_i = a_i/K$ and $r_i' = a_i'/K$ for positive integers $a_i, a_i'$ and $K = \sum_{i=1}^N a_i = \sum_{i=1}^{N'} a_i'$.
-Then,
-\begin{equation}
-(\w, \r) \succ (\w', \r') \mbox{ if and only if } \Gamma_{\bma} (\w) \succ \Gamma_{\bma'} (\w'),
-\end{equation}
-where the embedding map $\Gamma_{\bma} :\mathbb{R}^N \rightarrow \mathbb{R}^K$ is given by
-\begin{equation}
-	\Gamma_{\bma}(\bmz) \coloneqq \bigoplus_{i=1}^N x_i \eta_{a_i},
-\end{equation}
-with $\eta_{a_i} = (1/a_i, 1/a_i, \dots, 1/a_i)$ the uniform distribution on $a_i$ elements.
-\end{proposition}
-\begin{proof}
-	We first note that the map $\Gamma_{\bma}$ is stochastic and has a well-defined left-inverse $\Gamma^{-1}_{\bma'}: \mathbb{R}^K \rightarrow \mathbb{R}^N$ given by
-\begin{equation}
-	\Gamma^{-1}_{\bma}(\w) = \left( \sum_{i=1}^{a_1} w_i,  \sum_{i = a_1 +1}^{a_1 + a_2} \hspace{-5pt} w_i, \dots , \hspace{-15pt} \sum_{i=a_1 + \dots + a_{N-1}+1}^{K} \hspace{-10pt} w_i \right),
-\end{equation}
-that obeys $(\Gamma^{-1}_{\bma} \circ \Gamma_{\bma}) (\bmz) = \bmz$ for all $\bmz \in \mathbb{R}^N$.
-
-The claim is equivalent to the statement that there exists a \emph{bistochastic map} $B$ sending $\Gamma_{\bma}(\w)$ to $\Gamma_{\bma'}(\w')$ if and only if there exists a stochastic map $A$ sending $\w$ to $\w'$ and $\r$ to $\r'$.
-
-Suppose there is a stochastic map $A$ such that $A\w=\w'$ and $A\r = \r'$. 
-We define $B:\mathbb{R}^K \mapsto \mathbb{R}^K$ by $B \coloneqq \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1}$ so that it is stochastic as a composition of stochastic maps and it preserves the uniform distribution in $\mathbb{R}^K$, since
-\begin{align}
-	&B(1/K, 1/K, \dots, 1/K) = \big( \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1} \big) \big( \Gamma_{\bma'}(\r) \big) = \nonumber\\
-	&\Gamma_{\bma'} (\r') = (1/K, 1/K, \dots, 1/K),
-\end{align}
-therefore $B$ is bistochastic.
-Finally, $B$ maps the embedded distributions as follows,
-\begin{equation}
-	B \Gamma_{\bma}(\w) = \big( \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1} \big) \big( \Gamma_{\bma}(\w) \big) = \Gamma_{\bma'} (\w').
-\end{equation}
-
-Conversely, suppose a bistochastic map $B$ exists sending $\Gamma_{\bma}(\w)$ to $\Gamma_{\bma'}(\w')$.
-Again, define $A: \mathbb{R}^N \mapsto \mathbb{R}^{N'}$ by $A \coloneqq \Gamma_{\bma'}^{-1} \circ B \circ \Gamma_{\bma}$ so that it is stochastic as a composition of stochastic maps and $A \w = \big( \Gamma_{\bma'}^{-1} \circ B \circ \Gamma_{\bma} \big) \w = \w'$, as well as $A \r = \r'$.
-\end{proof}
-We note that the vectors $\r, \r'$ with rational components form a dense subset of the positive probability distributions, and do not consider further technicalities that have no impact on actual physical measurements, which always have a finite resolution.
 
@@
 	(x_{i}, L_{i}) = \left( \frac{1}{9^n}\sum_{\ell=0}^i m_{\ell}, \sum_{\ell=0}^i m_{\ell} w_{\ell} \right).
+%\sum_{j: even}^n a^j \binom{n}{j} = \frac{1}{2} [ (1+a)^n + (1-a)^n ]
 \end{equation}
@@
 \end{align}
-%\sum_{j: even}^n a^j \binom{n}{j} = \frac{1}{2} [ (1+a)^n + (1-a)^n ]
 
@@
 The first dashed contour from the right corresponds to $H_\alpha(\rho_{\rm{S}}(\epsilon)) = 0$.
-In particular, $H_\alpha(\rho_{\rm{S}}(0)) = 0$ corresponds to $\alpha \approx 1.31$.
+In particular, $H_\alpha(\rho_{\rm{S}}(0)) = 0$ occurs at $\alpha \approx 1.31$.
     }

### 2021-12-15 qip_extended_abstract/qip_extended_abstract.tex
halfway thru revisions

\documentclass[12pt]{letter}

\usepackage[a4paper,left=2.5cm,right=2.5cm,bottom=2cm]{geometry}
\usepackage{graphicx}

\RequirePackage[fixed]{fontawesome5}
\RequirePackage[scaled=.96,osf]{XCharter}
\linespread{1.1}

\usepackage{color}
\definecolor{slateblue}{rgb}{0.17,0.22,0.64}

\usepackage{hyperref}
\hypersetup{
  colorlinks = true, %Colours links instead of ugly boxes
  urlcolor   = slateblue, %Colour for external hyperlinks
  linkcolor  = blue, %Colour of internal links
  citecolor  = blue %Colour of citations
}

\renewcommand*\rmdefault{ppl} % nice font
\pagestyle{empty}

\begin{document}

\hfill\begin{minipage}{6cm}
	\raggedright
	\vspace{-2.5cm}
	{\footnotesize\itshape Nick Koukoulekidis}\\
	{\footnotesize\itshape (corresponding author)}\\
	{\footnotesize\itshape PhD, Quantum Theory Group}\\
	{\footnotesize\itshape Imperial College London}\\
	{\footnotesize\itshape %\MVAt~ 
		\verb|nk2314@imperial.ac.uk|}\\
	%~\\
	%	\footnotesize\today
\end{minipage}

\vspace{-3.6cm}
\hspace{-0.5cm}\includegraphics[scale=.12]{icllogo.png}
\vspace{1.5cm}

A fundamental problem is to understand how quantum physics admits higher degrees of order than possible in classical physics. 
One signature of this non-classical order is the existence of `negative probabilities' in the Wigner representation of quantum systems. 
In this work, we construct a well-defined framework of statistical mechanics for Wigner negativity, and then apply it to quantify the order in magic states.
Specifically, we provide fundamental restrictions on magic state distillation, a leading model of fault-tolerant quantum computing. 
The restrictions are more powerful than previous approaches and they are novel in their ability to include experimental hardware limitations.

Statistical mechanics cannot be directly applied to quantify order on quasi-probability distributions, since the Shannon entropy is not well-defined when Wigner negativity arises.
In order to establish our statistical framework, we utilise recent research on the thermodynamics of small quantum systems and extend it to Wigner negativity and quasi-probability distributions.
Thermodynamic entropic theories are underlied by majorization orderings between probability distributions that represent the thermodynamic states of a system.
In this sense, majorization is a more fundamental notion than entropy and we show that it is possible to define majorization ordering among quasi-distributions.
We further define a sub-set of classical (R\'{e}nyi) entropies which remain meaningful on quasi-distributions and can attain negative values, acting as witnesses of non-classicality, and specifically magic in the context of Wigner negativity.
Finally, we find that the prominent magic measure of mana naturally arises as the divergence of these R\'{e}nyi entropies as one approaches the Shannon entropy for Wigner distributions, allowing for interpreting magic injection in fault-tolerant schemes as a phase transition.
This use of majorization for quasi-distributions could find application in other studies of non-classicality.

Our framework has a profound impact on the quantification of magic in fault-tolerant schemes, which we now review.
Quantum operations that are robust under errors can be implemented experimentally with high precision, but are not sufficient to achieve quantum speed-ups.
Magic states are key resources injected in fault-tolerant schemes to realize universal quantum computation and contain negativities in their Wigner representation.
They can only be implemented probabilistically within a fault-tolerant framework, hence only injection of noisy magic states is possible.
However, one can perform magic state distillation which aims at converting copies of a noisy magic state into fewer copies of a less noisy, higher quality magic state.
Several distillation protocols exist, each effectively providing a low bound on the optimal achievable distillation rate, i.e. the ratio of final to initial magic state copies. 
On the other hand, upper bounds on distillation protocols express restrictions on our ability to distill magic states. 
Some upper bounds do exist, but they are based on abstract information-theoretic measures, which take into account properties of magic states, but are completely agnostic of the protocol properties.

Our novel statistical framework of Wigner negativity naturally leads to the derivation of an infinite family of entropic upper bounds.
We may encode the physics of a distillation protocol by considering its action on a general reference stabilizer state.
This allows us to impose a majorization ordering between the distribution pairs of the magic and reference stabilizer state, before and after they pass through the protocol, thus obtaining entropic bounds, which encode both the properties of the magic states and of the protocol.
This new family of bounds outperforms existing monotone-based upper bounds, and, to our knowledge, provides the first general framework to incorporate dependence on hardware physics. 
In particular, our bounds attain different optimal values depending on the specific quantum computer architectures. 
The architectural properties that dictate optimality can, for example, be some temperature threshold or noise bias of the device or a fixed-point structure associated with a restriction in the allowed quantum gates. 
We provide explicit demonstrations of how our bounds may depend on the temperature threshold or the Hamiltonian describing the device.
As such, this approach is relevant to the challenge of designing and building quantum computers.

\end{document}

### 2021-12-20 npj_revisions/referee_responses.tex
almost all changes for resubmission done

@@
 \usepackage{amsmath,amsfonts, amssymb, amsthm}
-\usepackage{bm, bbm, physics, mathtools}
+\usepackage{bbm, physics, mathtools}
 
@@
 \newcommand{\ddd}[1]{\textcolor{blue}{[#1]}}
+\newcommand{\revhigh}[1]{{\color{red}#1}}
 
-\pagestyle{empty}
-\input{preamble_mathchars.sty}
+\hypersetup{
+	colorlinks=true,  
+	linkcolor=blue,   
+	citecolor=blue,   
+	urlcolor=blue     
+}
+
+\newcommand{\ent}[2]{S\left( #1 \middle\vert\middle\vert #2 \right)}
+\def\>{\rangle}
+\def\<{\langle}
+
+\def\id{\mathbbm{1}}
+\renewcommand{\tr}{{\rm{tr}}}
+\renewcommand{\det}{{\rm{det}}}
+
+\def\bmeta{\boldsymbol{\eta}}
+\def\bmo{\bm{0}}
+\def\bma{\boldsymbol{a}}
+\let\ring\r
+
+\def\x{\boldsymbol{x}}
+\def\y{\boldsymbol{y}}
+\def\z{\boldsymbol{z}}
+\def\r{\boldsymbol{r}}
+\def\w{\boldsymbol{w}}
+\def\p{\boldsymbol{p}}
+\def\q{\boldsymbol{q}}
+\def\d{\boldsymbol{d}}
+\def\m{\boldsymbol{m}}
+\def\k{\boldsymbol{k}}
+\def\q{\boldsymbol{q}}
+
+\def\A{{\cal A}}
+\def\Z{{\cal Z}}
+\def\H{{\cal H}}
+\def\E{{\cal E}}
+\def\J{{\cal J}}
+\def\R{{\cal R}}
+\def\D{{\cal D}}
+\def\M{{\cal M}}
+\def\F{{\cal F}}
+\renewcommand{\O}{{\cal O}}
+\renewcommand{\P}{{\cal P}}
 
@@
 
-\textit{They also show that one can define Renyi entropies for quasi-probability distributions, and derive an elegant interpretation of the mana as the residue of a pole quantifying the divergence of the Renyi entropy as it approaches the Shannon entropy.}
+\textit{They also show that one can define R\'{e}nyi entropies for quasi-probability distributions, and derive an elegant interpretation of the mana as the residue of a pole quantifying the divergence of the R\'{e}nyi entropy as it approaches the Shannon entropy.}
 
@@
 
-We are grateful for suggestion on making our results more accessible.
-To this end, we have added a proof of the result in Appendix~B1, relying on the assumption that the result is clear for simple majorization (i.e.
-when $\r = \r'= (1/N,1/N,\dots,1/N)$) as shown in~[81].
-In general, we consider statements about simple majorization (presented in Marshall \& Olkin [81]) as well-established in the quantum information community and do not prove them in our paper.
-As a side remark, the original proof of this result in the context of relative majorization can be found in [111], not [103].
+We are grateful for suggestions on making our results more accessible -- we have added a proof of the result in Supplementary Note~2 and a reference to it in the main text.
 
@@
 
-\nick{David, thoughts on bounding wealth distillation?}\\
+This is an interesting idea,  and following the Reviewer's suggestion we have thought about it a little.
+It seems that variants of the Gini coefficient do exist to account for losses,  however the level of technical detail is quite simple.
+The R\'{e}nyi entropies we consider here would certainly give finer information about levels of inequality,  although the physical or statistical interpretations are not so clear to us at present.
+We might expect that the $\alpha \rightarrow 1$ entropy measures the total cumulative losses within a country,  in the same way as mana for magic states relates to the sum negativity.
+
+In traditional majorization this kind of thinking has occurred previously -- for example Robin-Hood transforms that take from the rich and give to the poor.
+Of course in the vein of the present paper,  one could construct a ``resource theory of social inequality'' (although calling this a ``resource'' is highly questionable,  except perhaps for billionaire CEOs) in which socialist policies that redistribute wealth more fairly over a population are the ``free/easy operations'' that transform a country.
+Distillation protocols on multiple countries would then address the question of the degree to which one could form high levels of inequality in one country solely via collective socialist actions on multiple countries.
+However, we do not pursue such social engineering theories any further here.
 
@@
 
-\nick{ANSWER}
+Our current bounds can be viewed as describing purely the constraints on distillation coming from Wigner stochasticity, and the bounds are still far above actual distillation rates one can obtain from explicit schemes.
+We have at least narrowed down the high-level principles that determine the ultimate distillation rates achievable, and our work indicates that to make substantially stronger global statements (as opposed to applications of the theory to specific hardware set-ups) one should probably delve into the affine symplectic group structure on the phase space.
+Since free stabilizer operations correspond to the affine symplectic group which is a strict subgroup of the stochastic group, we do not expect our bounds to be achievable by an explicit distillation scheme.
 
@@
 
-\nick{David, do you want to take this one? -- your previous notes are accessible on GitHub for copy-pasting}
+The proposed route to lower bounds would be separate from the method of explicit distillation rates from error correcting codes.
+Instead the proposal is to leverage the critical additional structure that the Wigner distribution carries,  above and beyond involving stochasticity.
+The upper bounds obtained are upper bounds on distillation rates because the set of stochastic maps is a superset for the actual maps that free operations generate.
+Therefore, one can approach things from the other direction: construct a set of stochastic maps that respect the structure of a subgroup of maps that correspond to free operations and then compute the associated majorization constraints for this restricted set.
+This would then provide lower bounds on what free operations can achieve.
 
-\nick{I haven't added lines on this in the main text}
+The difficulty in obtaining lower bounds lies in the choice of sensible sets of maps. 
+We have briefly explored the stochastic maps one gets from Weyl covariant channels -- these can be shown to be simply represented as convex mixtures of unitary displacements and in fact one can solve the majorization conditions for this class of channels (it is called cyclic majorization in the mathematical literature~[136]).
+The problem is that while Weyl covariant channels are a nice family of channels,  they turn out to be useless for distillation (which can be shown via majorization).
+More non-trivial and useful classes of operations could be analysed but the problem becomes that the majorization conditions may not be solvable in closed form (we flag a class of operations based on finite-reflection groups~[134] -- they are known to have finite conditions for majorization with respect to a discrete group).
+Beyond tidy closed analytics, one can use techniques from semi-definite programming to estimate distillation rates -- which might be an interesting future project to explore.
+
+We have extended our discussion in the main text with some of the above comments.
 
@@
 
-\nick{I haven't had the time to consider this yet.
-In principle, we would need to find $R_\alpha = 0$ for some $\alpha$ and reference process, given a magic interconversion between Clifford non-equivalent magic states -- seems tough and numerically doesn't look to be the case for the Strange and Norrell states ($d=3$, does not fall under Bengtsson et al's results)}
+\nick{ANSWER}
 
@@
 
-This is a very interesting question from the lens of implementing our results on actual distillation protocols.
-According to Jozsa and Van den Nest's work\footnote{Jozsa R and Van den Nest M (2013) Classical simulation complexity of extended Clifford circuits, arXiv:1305.6190}, an $N$-qudit circuit consisting of intermediate measurements and adaptive Clifford gates is always equivalent to an $(N+k)$-qudit circuit ($k \in \mathbb{N}$) consisting of a Clifford gate.
+This is a good point -- these operations still admit representations in terms of positive, stochastic maps and therefore our results cover this regime, and the bounds remain unchanged. 
+For example, according to Jozsa and Van den Nest's work [Jozsa R and Van den Nest M (2013) Classical simulation complexity of extended Clifford circuits, arXiv:1305.6190], intermediate Pauli measurements and adaptive Clifford gates on $N$ qubits can always be substituted by a Clifford gate on $(N+k)$ qudits, with $k \in \mathbb{N}$.
 Therefore, our bounds are directly applicable on the equivalent circuit.
 
-In more general scenarios, suppose we project an $n$-copy state $\rho$ with projector $P$, which has success probabilty $p$. This can be written as
-\begin{equation}
-	\cal{E}(\rho) = p\ \tr_{i=1,\dots,n-1} [P\rho P] \otimes \ketbra{0} + (1-p)\ \tr[(\id-P)\rho] \sigma \otimes \ketbra{1},
-\end{equation}
-where the last subsystem is labelled $0$ when the projection is successful and 1 when it is not.
-Then, $\E$ admits a stochastic Wigner representation and in principle our results can provide bounds on the distillation ratio $\frac{pm}{n}$.
-However, one complication arises due to this operational representation of projective measurements, namely that states are no longer product states and the entropic functions are not guaranteed to factor out nicely (Theorem 11 property 3).
-
-\nick{I haven't added lines on this in the main text}
+We do agree that it is important to better engage the actual classes of operations of interest from a quantum computing perspective, and in recent work we are extending the approach to qubit systems.
+There, it is much more important to be clear on what actual operations are permitted and we better engage such concrete techniques in quantum computing (in particular CSS-code based protocols).
 
@@
 
-Yes, this is already clear in Eq.(52) obtained by restricting to unital channels.
-\nick{What about more refined, unrestricted bounds?
-I am not sure this is a well-defined question, as the bounds implicitly depend on the dimension via the states considered.
-The question seems motivated from the context of real distillation protocols, where the overhead scaling $\gamma$ tends to depend on the dimension e.g.
-Krishna and Tillich (2019) Towards Low Overhead Magic State Distillation.}
+The dimension of the system does arise in the bounds in fairly simple ways (for example see the R\'{e}nyi entropy bounds for unital operations in Eq.(52) of the main text).
+However it does not depend on prime properties of the dimension.
+The only non-trivial dependence on primality is in the original Wigner representation,  with the $p=2$ prime case famously having a more complex structure.
+We might expect that if one consider $G$-majorization for the lower bounds,  one obtains non-trivial features that do depend on the particular prime dimension.
+In this vein,  we note that the symplectic groups for $p=3$ and $p=5$ are finite reflection groups and therefore the associated $G$-majorization for each case is fully solvable in terms of a finite number of conditions.
 
@@
 
-We particularly welcome this question as it relates to some of the authors' current research.
-Firstly, we stress that in odd prime dimensions Gross' Wigner function is the only non-contextual quasi-probability representation of stabilizer theories (see~[101]), and contextuality has been shown to be equivalent to magic (see~[44]), as understood in the resource-theoretic formalism.
-Therefore, using different distributions, would in general represent negatively states and channels that are operationally ``free'', while simultaneously representing positively states and operations that are not operationally free, thus shifting the role of our bounds as fundamental bounds on \emph{magic distillation} protocols.
+We again thank the Reviewer for this nice point.
+In our paper, we first establish results for \emph{arbitrary} quasi-distributions,  and only then specialise to Wigner quasi-distributions.
+The Supplementary Material has general analysis for arbitrary quasi-distributions, which hopefully makes this clear.
 
-Having noted the above, we are claiming (in upcoming work) that using different distributions offers useful additional information in the context of classical simulability of general quantum circuits.
-Indeed, the P and Q quasi-distributions as well as the entire spectrum of s-ordered quasi-distributions introduced by Cahill and Glauber\footnote{Cahill K E and Glauber R J (1969) Ordered expansions in boson amplitude operators, Phys.
-Rev.
-177 1857} find discrete analogues in Ruzzi \textit{et al.}'s work\footnote{Ruzzi M \textit{et al.} (2005) Extended Cahill-Glauber formalism for finite dimensional spaces: I.
-Fundamentals, J.
+The question of whether switching representations provides extra information is a very interesting one,  and it is not obvious to us when this occurs.
+In the context of magic distillation the central thing that must be checked is that the free operations are postively represented as stochastic maps in this new representation -- if they are not,  then the majorization theory cannot be applied.
+However, if the free operations are still positively represented then we can certainly imagine situations in which the majorization bounds can be improved.
+Perhaps the strategy would be to look for a representation that has the largest contrast between free operations and the target magic state: i.e.
+all free operations are positively represented,  but the magic state has very ``large'' negativity in this representation.
+This seems to us an interesting line to explore,  perhaps using the discrete analogues to the $s$--ordered Cahill/Glauber distributions due to Ruzzi \textit{et al.} [Ruzzi M \textit{et al.} (2005),  J.
 Phys.
@@
 Gen.
-38 6239}.
-In our work we come up with different infinite families of quasi-probability representations, but the core idea is the same: the probability outcome of a general quantum circuit can be estimated via Monte Carlo sampling\footnote{Pashayan H (2015) Estimating Outcome Probabilities of Quantum Circuits Using Quasiprobabilities, Phys.
-Rev.
-Lett.
-115, 070501}, and using different quasi-distributions for representing different circuit components can reduce the sampling overhead.
-More specifically, the number of samples required for a probability estimate, which converges well to the actual circuit outcome, scales as a function of the negativities of the distributions that represent the circuit components.
-Therefore, different quasi-distribution representations can result in greater reduction of the negativity overhead compared to the Wigner representation.
+38 6239].
+Or more generally from frame-theory, by perturbing the Wigner frame defined via $\{D_{\x}A_0 D_{\x}^\dagger\}$ to the more general scenario of $\{D_{\x} M D_{\x}^\dagger\}$ where $M$ is an arbitrary trace-one operator that can be tuned to vary the choice of frame,  while still keeping covariance properties.
 

### 2021-12-20 magic_constraints_maintext.tex
almost all changes for resubmission done

--- 2021-07-16 ms.tex
@@
-\documentclass[pra,
-aps,
-twocolumn,
-superscriptaddress,
-groupedaddress,
-nofootinbib,
-reprint
+\documentclass[
+onecolumn,
+superscriptaddress
 ]{revtex4-1}
 
-\input{preamble}
+\usepackage{amsmath,amsfonts, amssymb, amsthm}
+\usepackage{bbm, physics, mathtools}
+\usepackage{graphicx, subfigure}
+\usepackage{enumerate, multirow, makecell}
+\usepackage{xcolor, hyperref}
+
+\newcommand{\revhigh}[1]{{\color{red}#1}}
+\hypersetup{
+	colorlinks=true,  
+	linkcolor=blue,   
+	citecolor=blue,   
+	urlcolor=blue     
+}
+
+\newtheorem{theorem}{Theorem}
+\newtheorem{proposition}[theorem]{Proposition}
+\newtheorem{definition}[theorem]{Definition}
+
+\newcommand{\ent}[2]{S\left( #1 \middle\vert\middle\vert #2 \right)}
+\def\>{\rangle}
+\def\<{\langle}
+
+\def\id{\mathbbm{1}}
+\renewcommand{\tr}{{\rm{tr}}}
+\renewcommand{\det}{{\rm{det}}}
+
+\def\bmeta{\boldsymbol{\eta}}
+\def\bmo{\boldsymbol{0}}
+\def\bma{\boldsymbol{a}}
+\let\ring\r
+
+\def\x{\boldsymbol{x}}
+\def\y{\boldsymbol{y}}
+\def\z{\boldsymbol{z}}
+\def\r{\boldsymbol{r}}
+\def\w{\boldsymbol{w}}
+\def\p{\boldsymbol{p}}
+\def\q{\boldsymbol{q}}
+\def\d{\boldsymbol{d}}
+\def\m{\boldsymbol{m}}
+\def\k{\boldsymbol{k}}
+\def\q{\boldsymbol{q}}
+
+\def\A{{\cal A}}
+\def\Z{{\cal Z}}
+\def\H{{\cal H}}
+\def\E{{\cal E}}
+\def\J{{\cal J}}
+\def\R{{\cal R}}
+\def\D{{\cal D}}
+\def\M{{\cal M}}
+\def\F{{\cal F}}
+\renewcommand{\O}{{\cal O}}
+\renewcommand{\P}{{\cal P}}
 
@@
 We find that the mana of a magic state is the measure of divergence of these R\'{e}nyi entropies as one approaches the Shannon entropy for Wigner distributions, and discuss how distillation lower bounds could be obtained in this setting.
-This use of majorization for quasi-distributions could find application in other studies of non-classicality, and raises novel questions in the context of classical statistical mechanics.
+\revhigh{REMOVE (NO CLAIMS TO NOVELTY): This use of majorization for quasi-distributions could find application in other studies of non-classicality, and raises novel questions in the context of classical statistical mechanics.}
 \end{abstract}
@@
 
-\title{Constraints on magic state protocols from the statistical mechanics of \\Wigner negativity}
+\title{Constraints on magic state protocols from the statistical mechanics of Wigner negativity}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Introduction}
-\label{sec:intro}
+\section*{Introduction}
 
@@
 
-\subsection{Overview of our results}
-We begin by describing how stabilizer operations correspond to stochastic maps on a discrete phase space, and how majorization can be applied to constrain magic state transformations (Sec.~\ref{sec:ps}).
+\subsection*{Overview of our results}
+\revhigh{
+We begin by describing how stabilizer operations correspond to stochastic maps on a discrete phase space, and how majorization can be applied to constrain magic state transformations.
 We then consider families of magic protocols with increasing complexity.
-The simplest case we consider is for magic protocols that lead to unital channels (Sec.~\ref{sec:unital}).
-These are a subset of protocols that leave invariant some distinguished state or have some equilibrium fixed-point structure (Sec.~\ref{sec:frag}).
-We then consider protocols that are non-equilibrium processes, but only generate sub-linear correlations that enable a simple description in the thermodynamic limit (Sec.~\ref{sec:stab}), before giving entropic analysis that can be applied more generally (Sec.~\ref{section:entropies}).
+The simplest case we consider is for magic protocols that lead to unital channels.
+These are a subset of protocols that leave invariant some distinguished state or have some equilibrium fixed-point structure.
+We then consider protocols that are non-equilibrium processes, but only generate sub-linear correlations that enable a simple description in the thermodynamic limit before giving entropic analysis that can be applied generally.}
 
@@
 We provide explicit bounds for magic protocols that generate unital channels (Eq.~(\ref{eq:unital-bound})), as well as bounds that incorporate the temperature and Hamiltonian of the system (Theorem~\ref{thm:free-energy}) and discuss extensions to more general scenarios.
-These bounds are shown to be tighter than other bounds such as those that come from mana and thauma (Sec.~\ref{sec:monotones_frag} and Fig.~\ref{fig:distill_bounds}).
+These bounds are shown to be tighter than other bounds such as those that come from mana and thauma (Fig.~\ref{fig:distill_bounds}).
 
 We find that the analysis in the presence of negativity displays a range of features that do not appear in classical statistical mechanics, and leads to a picture of Wigner negativity in a quantum circuit being described as non-classical free energy that is processed under stochastic dynamics.
-This is demonstrated by non-monotonic Lorenz curves (Sec.~\ref{sec:lc}), and by single-shot entropies for general Wigner quasi-distributions that are well-defined, obey data-processing under stabilizer operations and can take on negative values (Sec.~\ref{section:entropies}).
+This is demonstrated by non-monotonic Lorenz curves (Fig.~\ref{fig:lcs}), and by single-shot entropies for general Wigner quasi-distributions that are well-defined, obey data-processing under stabilizer operations and can take on negative values (Eq.~(\ref{eq:H})).
 
@@
     \centering
-    \includegraphics[scale=0.38]{figs/distill_bounds.pdf}
+    \includegraphics[scale=0.38]{distill_bounds.pdf}
     \caption{\textbf{Magic distillation bounds from majorization of Wigner quasi-distributions.} The above plot shows distillation upper bounds for qutrits obtained from majorization on unital protocols.
 The constraints are plotted as a function of the depolarizing error $\epsilon$ for a noisy Strange state (Eq.~(\ref{eq:noisysn})).
-The bound $R_\infty$ follows from a Lorenz curve analysis presented in Sec.~\ref{sec:unital}, while the bound $R_{10}$ comes from single-shot entropies on the Wigner quasi-distributions, as discussed in Sec.~\ref{section:entropies}.
+\revhigh{The bound $R_\infty$ follows from a Lorenz curve analysis presented before Eq.~(\ref{eq:unital-bound}), while the bound $R_{10}$ comes from single-shot entropies on the Wigner quasi-distributions, as discussed in the derivation of Eq.~(\ref{eq:Ra})}.
 Numerical bounds $R_{\rm{num}}$ are obtained by using the full set of majorization constraints.
@@
 We show that the mana of a quantum state arises as a residue in the $\alpha$--parameter for R\'{e}nyi entropies, and gives the rate of divergence to $-\infty$ as we approach the Shannon entropy of a Wigner distribution (Eq.~(\ref{eq:mana-divergence})).
-Finally, in Sec.~\ref{sec:lower_bounds} we discuss how our approach could be extended to construct explicit lower bounds on distillation that take into account physical constraints.
-
-\section{Phase space representations of quantum states}
-\label{sec:ps}
-
-Central to our construction is the representation of any quantum state or quantum operation on a system of dimension $d$ in terms of quasi-probability representations on a discrete phase space~\cite{cit:gross3, Ferrie_2008}.
+Finally, in the Discussion section, we discuss how our approach could be extended to construct explicit lower bounds on distillation that take into account physical constraints.
+
+\section*{Results}
+
+\revhigh{
+\subsection*{Phase space representation of quantum mechanics}
+}
+
+Central to our construction is the representation of any quantum state or quantum operation on a system of dimension $d$ in terms of quasi-probability representations on a discrete phase space~\cite{Gross2006, Ferrie_2008}.
 This construction is a discrete version of Wigner representations in quantum optics~\cite{Wigner_1932, Vourdas_2004, Kenfack_2004}.
@@
 Here $\omega \coloneqq e^{2\pi i/d}$ is the $d$-th root of unity and addition is taken modulo $d$.
-From these we can construct a phase space $\cal{P}_d \coloneqq \mathbb{Z}_d \times \mathbb{Z}_d$ that provides a complete representation of the quantum system.
-Given a point $\bmz \coloneqq (q, p)$ we define a displacement operator,
+From these we can construct a phase space $\P_d \coloneqq \mathbb{Z}_d \times \mathbb{Z}_d$ that provides a complete representation of the quantum system.
+Given a point $\z \coloneqq (q, p)$ we define a displacement operator,
 \begin{equation}\label{eq:ddef}
-    D_{\bmz} \coloneqq \tau^{q p} X^{q} Z^{p},\ 
+    D_{\z} \coloneqq \tau^{q p} X^{q} Z^{p},\ 
 \end{equation}
@@
 The qubit case $d=2$ is known to have obstacles to using a Wigner representation to quantify magic in terms of negativity~\cite{Mermin_1990, cit:howard2}, although recent work~\cite{Raussendorf_qubits} has shown how to extend the representation to include qubits by enlarging the phase space.
-For a composite system with dimension $d_{\rm tot} = d_1 \dots d_n$ and Hilbert space $\cal{H}_{d_1} \otimes \dots \otimes \cal{H}_{d_n}$, we define displacement operators as
+For a composite system with dimension $d_{\rm tot} = d_1 \dots d_n$ and Hilbert space $\H_{d_1} \otimes \dots \otimes \H_{d_n}$, we define displacement operators as
 \begin{equation}\label{eq:composited}
-    D_{\bmz} \coloneqq D_{(q_1, p_1)} \otimes \dots \otimes D_{(q_n, p_n)},
+    D_{\z} \coloneqq D_{(q_1, p_1)} \otimes \dots \otimes D_{(q_n, p_n)},
 \end{equation}
@@
 \begin{align*}
-	\bmz &\coloneqq (q_1, \dots, q_n, p_1, \dots, p_n) \in \cal{P}_{d_1} \times \dots \times \cal{P}_{d_n},
+	\z &\coloneqq (q_1, \dots, q_n, p_1, \dots, p_n) \in \P_{d_1} \times \dots \times \P_{d_n},
 \end{align*}
 to denote the phase space point for the composite system. 
-For simplicity, we assume $n$ copies of a $d$--dimensional system $d_1=d_2 = \cdots = d$, and therefore we have that $\bmz \in \mathbb{Z}_d^{2n}$.
+For simplicity, we assume $n$ copies of a $d$--dimensional system $d_1=d_2 = \cdots = d$, and therefore we have that $\z \in \mathbb{Z}_d^{2n}$.
 
@@
 \begin{equation}\label{eq:gp}
-    {\rm{HW}}_d^n \coloneqq \{ \tau^k D_{\bmz}: k \in \mathbb{Z}_d, \bmz \in \cal{P}_d^n\}.
-\end{equation}
-The Clifford group $ \cal{C}_d^n $ is then defined as the set of unitaries that normalise the Heisenberg-Weyl group~\cite{Appleby_2005}.
-We may define the pure stabilizer states as those states obtained by acting on $|0\>$ with Clifford unitaries~\cite{cit:gross3} and, finally, the full set of stabilizer states as the convex hull of all pure stabilizers, namely all probabilistic mixtures of states of the form $U|0\>\<0|U^\dagger$ where $U$ is Clifford.
-
-\subsection{Wigner representations for quantum states and quantum operations}\label{sec:wigner}
+    {\rm{HW}}_d^n \coloneqq \{ \tau^k D_{\z}: k \in \mathbb{Z}_d, \z \in \P_d^n\}.
+\end{equation}
+The Clifford group $ {\cal C}_d^n $ is then defined as the set of unitaries that normalise the Heisenberg-Weyl group~\cite{Appleby_2005}.
+We may define the pure stabilizer states as those states obtained by acting on $|0\>$ with Clifford unitaries~\cite{Gross2006} and, finally, the full set of stabilizer states as the convex hull of all pure stabilizers, namely all probabilistic mixtures of states of the form $U|0\>\<0|U^\dagger$ where $U$ is Clifford.
+
+\subsection*{Wigner representation for quantum states and quantum operations}
 
 In order to provide a complete decomposition of arbitrary quantum states and quantum operations we now define a basis of Hermitian observables that transforms covariantly under the action of the Clifford group.
-At every point $\bmz \in \P_d$ we define the phase-point operator
+At every point $\z \in \P_d$ we define the phase-point operator
 \begin{equation}\label{eq:ax}
-	A_{\bmz} \coloneqq \frac{1}{d} \sum_{\bmy \in \cal{P}_d} \omega^{\eta(\bmz, \bmy)} D_{\bmy}, 
-\end{equation}
-where $\eta(\bmz, \y)$ is the symplectic inner product between any two points $\bmz,\y \in \P_d$, and is given explicitly by
-\begin{equation}
-	\eta(\bmz, \bmy) \coloneqq \bmy^T \begin{pmatrix}
-		0  & \id \\ %\mathbbm{O}_n  & \id_n \\
-		-\id & 0 \\ %-\id_n & \mathbbm{O}_n \\
-	\end{pmatrix} \bmz,
+	A_{\z} \coloneqq \frac{1}{d} \sum_{\y \in \P_d} \omega^{\eta(\z, \y)} D_{\y}, 
+\end{equation}
+where $\eta(\z, \y)$ is the symplectic inner product between any two points $\z,\y \in \P_d$, and is given explicitly by
+\begin{equation}
+	\eta(\z, \y) \coloneqq \y^T \begin{pmatrix}
+		0  & \id \\
+		-\id & 0 \\
+	\end{pmatrix} \z,
 \end{equation}
@@
 
-The phase-point operators form an orthogonal operator basis with respect to the Hilbert-Schmidt inner product, as discussed in Appendix~\ref{app:wigner}.
-Therefore, any quantum state $\rho$ can be expressed as a linear combination of them, $\rho = \sum_{\bmz \in \cal{P}_d} \W[\bmz]{\rho} A_{\bmz}$, where the coefficients $\W{\rho}(\z)$ give the Wigner distribution of state $\rho$,
+The phase-point operators form an orthogonal operator basis with respect to the Hilbert-Schmidt inner product, as discussed in Supplementary Note~1.
+Therefore, any quantum state $\rho$ can be expressed as a linear combination of them, $\rho = \sum_{\z \in \P_d} W_\rho(\z) A_{\z}$, where the coefficients $W_\rho(\z)$ give the Wigner distribution of state $\rho$,
 \begin{equation}\label{eq:wstate}
-    \W[\bmz]{\rho} \coloneqq \frac{1}{d}\tr[A_{\bmz} \rho].
-\end{equation}
-For any quantum state $\rho$, the Wigner distribution $W_\rho(\bmz)$ is readily seen to be a $d^2$-dimensional quasi-distribution over $\cal{P}_d$.
-More precisely, $W_\rho(\bmz)$ is a real-valued function on $\P_d$ with the normalisation property $\sum_{\bmz} W_\rho(\bmz) = 1$ (see Appendix~\ref{app:wigner} for details).
-Moreover, the above Wigner representation has recently been shown to be the only non-contextual quasi-probability representation of odd-dimensional stabilizer theories for odd prime dimensions~\cite{schmid2021noncontextual}.
+    W_\rho(\z) \coloneqq \frac{1}{d}\tr[A_{\z} \rho].
+\end{equation}
+For any quantum state $\rho$, the Wigner distribution $W_\rho(\z)$ is readily seen to be a $d^2$-dimensional quasi-distribution over $\P_d$.
+More precisely, $W_\rho(\z)$ is a real-valued function on $\P_d$ with the normalisation property $\sum_{\z} W_\rho(\z) = 1$ (see Supplementary Note~1 for details).
+Moreover, the above Wigner representation has recently been shown to be the only non-contextual quasi-probability representation of stabilizer theories in odd prime dimensions~\cite{schmid2021noncontextual}.
 
@@
 \begin{equation}\label{Wigner-Choi}
-W_{\E}(\y |\bmz) \coloneqq d_A^2 W_{\J(\E)}(\bar{\bmz} \oplus \y),
-\end{equation}
-where $\bar{\bmz} = (q_1, \dots, q_n, -p_1, \dots, -p_n)$ can be viewed as the time-reversed version of $\bmz$ in the discrete phase space, where momenta are reflected while position coordinates remain unchanged.
-
-\subsection{Magic theories for quantum computation}
-\label{sec:mono}
+W_{\E}(\y |\z) \coloneqq d_A^2 W_{\J(\E)}(\bar{\z} \oplus \y),
+\end{equation}
+where $\bar{\z} = (q_1, \dots, q_n, -p_1, \dots, -p_n)$ can be viewed as the time-reversed version of $\z$ in the discrete phase space, where momenta are reflected while position coordinates remain unchanged.
+
+\subsection*{Magic theories for quantum computation}
 \begin{figure}[t]
     \centering
-        \includegraphics[scale=0.3]{figs/protocol_diagram.pdf}
+        \includegraphics[scale=0.3]{protocol_diagram.pdf}
     \caption{\textbf{Probing magic protocols with reference states.} 
@@
 \begin{equation}
-    \M(\rho) \coloneqq \log (2\hspace{1pt}\sn{\rho}+1),
-\end{equation}
-where the \emph{sum-negativity}~\cite{cit:veitch2} is the sum of the negative components in $\W{\rho}$,
-\begin{equation}
-    \sn{\rho} \coloneqq \sum\limits_{\bmz: \W[\bmz]{\rho} < 0} \abs{\W[\bmz]{\rho}}.
+    \M(\rho) \coloneqq \log (2\hspace{1pt}{\rm sn}(\rho)+1),
+\end{equation}
+where the \emph{sum-negativity}~\cite{cit:veitch2} is the sum of the negative components in $W_\rho$,
+\begin{equation}
+    {\rm sn}(\rho) \coloneqq \sum\limits_{\z: W_\rho(\z) < 0} \abs{W_\rho(\z)}.
 \end{equation}
@@
 
-\subsection{Stochastic representation of magic protocols}
-\label{sec:struc}
+\subsection*{Stochastic representation of magic protocols}
 
@@
 \begin{equation}
-    \F \coloneqq \{ \rho: \W[\bmz]{\rho} \geq 0 \text{ for all } \bmz \in \cal{P}_d\}.
+    \F \coloneqq \{ \rho: W_\rho(\z) \geq 0 \text{ for all } \z \in \P_d\}.
 \end{equation}
@@
 
-Any magic state protocol will correspond to a quantum channel $\E$, so from Eq.~(\ref{Wigner-Choi}) it admits a Wigner representation $W_{\E}(\y | \bmz)$ that acts as a transition matrix mapping phase space points $\bmz \rightarrow \y$.
+Any magic state protocol will correspond to a quantum channel $\E$, so from Eq.~(\ref{Wigner-Choi}) it admits a Wigner representation $W_{\E}(\y | \z)$ that acts as a transition matrix mapping phase space points $\z \rightarrow \y$.
 The representation obeys the relation
 \begin{equation}
-	W_{\E(\rho)} (\y) = \sum_{\bmz \in \P_d} W_{\E}( \y | \bmz) W_\rho(\bmz),
+	W_{\E(\rho)} (\y) = \sum_{\z \in \P_d} W_{\E}( \y | \z) W_\rho(\z),
 \end{equation}
@@
 Since the magic protocol sends free states to free states, $\E$ sends all positively represented quantum state to other positively represented quantum states.
-In such cases, it can be shown~\cite{Wang_2019} that if $\E$ is a free operation then the associated Wigner representation $W_{\E}(\y |\bmz)$ must form a stochastic matrix.
+In such cases, it can be shown~\cite{Wang_2019} that if $\E$ is a free operation then the associated Wigner representation $W_{\E}(\y |\z)$ must form a stochastic matrix.
 In particular, all stabilizer operations correspond to stochastic matrices in the Wigner representation.
@@
 
-\subsection{Quantifying disorder without entropies}
-\label{sec:major}
+\subsection*{Quantifying disorder without entropies}
 
@@
 
-There is a natural generalisation, which is called $\bmd$--majorization~\cite{Veinott_1971}, or in the context of thermodynamics, thermo-majorization~\cite{cit:horodecki2013}.
+There is a natural generalisation, which is called $\d$--majorization~\cite{Veinott_1971}, or in the context of thermodynamics, thermo-majorization~\cite{cit:horodecki2013}.
 For a fixed probability distribution $\r = (r_1, \dots, r_n)$ with positive components, we define majorization relative to $\r$ as $\p \succ_{\r} \q$, if and only if there exists a stochastic map $A$ such that $A\r = \r$ and $A \p = \q$.
@@
 \end{equation}
-if and only if there is a stochastic map $A$ such that $A\r = \r'$ and $A\p = \q$. We retrieve $\bmd$--majorization when $\r = \r'$.
-
-\subsection{Quasi-probability majorization and non-monotonic Lorenz curves}
-\label{sec:lc}
+if and only if there is a stochastic map $A$ such that $A\r = \r'$ and $A\p = \q$. We retrieve $\d$--majorization when $\r = \r'$.
+
+\subsection*{Quasi-probability majorization and non-monotonic Lorenz curves}
 
@@
 for all $x \in [0,1]$. 
-This provides a simple way of computing whether relative majorization holds between pairs of probability distributions.
+\revhigh{This result is shown in~\cite{ruch_mixing_1978} and we reproduce it in Supplementary Note~2.}
+It provides a simple way of computing whether relative majorization holds between pairs of probability distributions.
 
@@
     \centering
-    \includegraphics[scale=0.35]{figs/lc_strange.pdf}
+    \includegraphics[scale=0.35]{lc_strange.pdf}
     \caption{\textbf{A `heretical' family of Lorenz curves.} Traditionally, Lorenz curves for distributions are monotone increasing cumulative functions that reach a maximum value of $1$.
@@
 In terms of a Lorenz curve condition we have that $(\w_\epsilon , \r) \succ (\w_\epsilon', \r')$ if and only if $L_{\w_\epsilon |\r} (x) \ge L_{\w'_\epsilon |\r'} (x)$ for all $x \in [0,1]$. 
-Additionally, we show in the appendices (Proposition~\ref{Lorenz_linearity}) that the Lorenz curve for any quasi-distribution obeys the relation
+Additionally, we show in Supplementary Note~2 that the Lorenz curve for any quasi-distribution obeys the relation
 \begin{equation}
@@
 
-\section{Magic distillation bounds with fixed-points}
-\label{sec:frag}
+\subsection*{Magic distillation bounds with fixed-points}
 
 We can now consider how majorization constrains magic distillation rates starting in this section with an abstract setting based on the fixed-point structure of the physical operations accessible to us.
-We show that any magic theory can always be decomposed in terms of `sub-theories' with a particular fixed-point structure, which allows the use of $\mathbf{d}$--majorization.
-Later, in Sec.~\ref{sec:stab}, we drop the requirement of fixed-points and instead use the full relative majorization, before giving general entropic constraints in Sec.~\ref{section:entropies}.
+We show that any magic theory can always be decomposed in terms of `sub-theories' with a particular fixed-point structure, which allows the use of $\d$--majorization.
+\revhigh{Later, we drop the requirement of fixed-points and instead use the full relative majorization, before giving general entropic constraints.}
 
@@
 
-\subsection{Majorisation of Wigner distributions with fixed-point structure}
-\label{sec:major_frag}
+\subsection*{Majorisation of Wigner distributions with fixed-point structure}
+
 We consider some $\sigma \in \F$, and its corresponding $\R_\sigma$.
 We are interested in the ability to transform many copies of some noisy magic state $\rho$ towards a more pure form of magic.
-The state $\rho$ is assumed to have negativity in the Wigner representation, so $W_\rho(\bmz) < 0$ for some regions of $\bmz \in \P_d$.
-The state $\sigma$ is assumed to have a Wigner distribution with $W_\sigma(\bmz) > 0$ for all $\bmz$ in the phase space\footnote{A non-full rank state $\sigma$ can be handled as a limiting case in which we first add an infinitesimal fraction of depolarising noise $\epsilon (\id/d)$ and then take $\epsilon \rightarrow 0$ in the end.}.
-
-The free operations within the magic theory $\R$ are represented by stochastic maps, and within $\R_\sigma$ by stochastic maps that leave $W_\sigma(\bmz)$ invariant.
+The state $\rho$ is assumed to have negativity in the Wigner representation, so $W_\rho(\z) < 0$ for some regions of $\z \in \P_d$.
+The state $\sigma$ is assumed to have a Wigner distribution with $W_\sigma(\z) > 0$ for all $\z$ in the phase space.
+\revhigh{This is justified because a non-full rank state $\sigma$ can be handled as a limiting case in which we first add an infinitesimal fraction of depolarising noise $\epsilon (\id/d)$ and then take $\epsilon \rightarrow 0$.}
+
+The free operations within the magic theory $\R$ are represented by stochastic maps, and within $\R_\sigma$ by stochastic maps that leave $W_\sigma(\z)$ invariant.
 Therefore, a necessary condition for magic state transformations $\rho_1 \rightarrow \rho_2$ within $\R_\sigma$ will be that
@@
 For $n$ copies of a qudit system of dimension $d$ the number of terms in $W_{\rho}$ is $d^{2n}$, so imposing the Lorenz curve condition corresponds to exponentially many constraints.
-Before computing explicit examples, in the next section we describe how these majorization constraints relate to other known monotones.
-
-\subsection{Basic monotones for magic distillation for a particular $\R_\sigma$ and the relation to mana}
-\label{sec:monotones_frag}
-
-We state some generic aspects of Lorenz curves for magic states, which allow us to interpret previous magic monotones in a new light.
+%Before computing explicit examples, in the next section we describe how these majorization constraints relate to other known monotones.
+
+%\subsection*{Basic monotones for magic distillation for a particular $\R_\sigma$ and the relation to mana}
+
+\revhigh{Before computing explicit examples,} we state some generic aspects of Lorenz curves for magic states, which allow us to interpret previous magic monotones in a new light.
 The first result gives a simple way to see that the sum-negativity/mana of a magic state is a monotone~\cite{cit:veitch2}.
@@
 \begin{proof}
-	The sum-negativity of a magic state $\rho$ can be written as $sn(\rho) =\frac{1}{2} (\sum_{\bmz} |W_\rho(\bmz) | - 1)$.
-We make use of the $L_1$-norm form of relative majorization, (see Appendix~\ref{app:major}), which states that $\p \succ_{\r} \q$ if and only if
+	The sum-negativity of a magic state $\rho$ can be written as $sn(\rho) =\frac{1}{2} (\sum_{\z} |W_\rho(\z) | - 1)$.
+We make use of the $L_1$-norm form of relative majorization, (see Supplementary Note~2), which states that $\p \succ_{\r} \q$ if and only if
 	\begin{equation}
@@
 \begin{theorem}\label{lem:lcmax}
-	Given a magic state $\rho$, the maximum $L_\star$ of its Lorenz curve $\lc{\rho}{\sigma}(x)$ is independent of the $\R_\sigma$ and equal to $1+\sn{\rho}$.
+	Given a magic state $\rho$, the maximum $L_\star$ of its Lorenz curve $L_{\rho|\sigma}(x)$ is independent of the $\R_\sigma$ and equal to $1+{\rm sn}(\rho)$.
 Moreover, the majorization constraint is stronger than mana in every $\R_\sigma$.
 \end{theorem}
-The proof of this is given in Appendix~\ref{app:major}.
+The proof of this is given in Supplementary Note~2.
 Using the Lorenz curve perspective, it is also simple to construct new monotones.
@@
 Therefore its monotonicity depends on the physics of the fixed point and provides a means to analyse magic distillation only under free operations that leave $\sigma$ invariant.
-One can also define an area monotone in the more general setting of relative majorization, where one drops the fixed point emphasis as in Sec.~\ref{sec:stab}.
-
-\subsection{Magic distillation bounds for unital protocols}
-\label{sec:unital}
-
-We now construct magic state distillation bounds for protocols that generate \emph{unital} channels, meaning that $\E(\I/d) = \I/d$.
+One can also define an area monotone in the more general setting of relative majorization, where one drops the fixed point emphasis.
+
+\subsection*{Magic distillation bounds for unital protocols}
+
+We now construct magic state distillation bounds for protocols that generate \emph{unital} channels, meaning that $\E(\id/d) = \id/d$.
 
@@
 in the computational basis.
-Its distribution $W_{|S\>\<S|}(\z)$ has a single negative value of $-1/3$ at $\bmz =(0,0)$ and the positive value $1/6$ at all other points.
+Its distribution $W_{|S\>\<S|}(\z)$ has a single negative value of $-1/3$ at $\z =(0,0)$ and the positive value $1/6$ at all other points.
 We define the $\epsilon$--noisy Strange state as
@@
 \begin{equation}
-	\W[\bmz]{\rho_{\rm{S}}(\epsilon)} = (1-\epsilon)\W[\bmz]{|\rm{S}\>\<\rm{S}|} + \epsilon\W[\bmz]{\frac{1}{3}\id}.
+	W_{\rho_{\rm{S}}(\epsilon)}(\z) = (1-\epsilon)W_{|\rm{S}\>\<\rm{S}|}(\z) + \epsilon W_{\frac{1}{3}\id}(\z).
 \end{equation}
@@
 \end{equation} 
-located at the origin $\bmz = \bmo$ and positive components
+located at the origin $\z = \bmo$ and positive components
 \begin{equation}
@@
 \end{equation}
-at the 8 phase space points $\bmz \ne \mathbf{0}$. We assume that $\epsilon < 3/4$ to ensure the presence of negativity in the Wigner distribution.
+at the 8 phase space points $\z \ne \bmo$. We assume that $\epsilon < 3/4$ to ensure the presence of negativity in the Wigner distribution.
 
@@
 \begin{equation}\label{eq:sudist}
-	\rho_{\rm{S}}(\epsilon)^{\otimes n} \longrightarrow \rho_{\rm{S}}(\epsilon')^{\otimes n'}, %\otimes \left( \frac{1}{3}\id \right)^{\otimes (n-n')},
+	\rho_{\rm{S}}(\epsilon)^{\otimes n} \longrightarrow \rho_{\rm{S}}(\epsilon')^{\otimes n'},
 \end{equation}
@@
 
-Due to negativity, the ordering of the components of the rescaled Wigner distribution $W_{\rho_n |\sigma_n}(\bmz) \coloneqq W_{\rho_n}(\bmz)/W_{\sigma_n}(\bmz)$, for $\rho_n = \rho_S(\epsilon)^{\otimes n}$, and $\sigma_n = \sigma^{\otimes n}= (\I/3)^{\otimes n}$, depends on whether $-v(\epsilon)$ is raised to an even or odd power.
+Due to negativity, the ordering of the components of the rescaled Wigner distribution $W_{\rho_n |\sigma_n}(\z) \coloneqq W_{\rho_n}(\z)/W_{\sigma_n}(\z)$, for $\rho_n = \rho_S(\epsilon)^{\otimes n}$, and $\sigma_n = \sigma^{\otimes n}= (\id/3)^{\otimes n}$, depends on whether $-v(\epsilon)$ is raised to an even or odd power.
 Treating the Wigner distributions as vectors, the component values $w_i$ and associated multiplicities $m_i$ in the $n$--copy case are found to be
@@
 where index $i$ runs through $0, \dots, n$, and we assume for simplicity that $n$ is even and $\epsilon \leq 3/7$, which implies that $v \geq u$.
-All details on the analysis are provided in Appendix~\ref{app:lcsu_technical}.
+All details on the analysis are provided in Supplementary Note~3.
 
@@
 
-The coordinates of the first point after the origin for $\rho_S(\epsilon)^{\otimes n}$ are given by $(1/9^n, v(\epsilon)^n)$, while for $\rho_S(\epsilon')^{\otimes n'}$ by $(1/9^{n'}, v(\epsilon')^{n'})$, and by requiring that the initial slope for the input state Lorenz curve is larger than that of the output state (Proposition~\ref{prop:first_elb} in the appendices) we find that
+The coordinates of the first point after the origin for $\rho_S(\epsilon)^{\otimes n}$ are given by $(1/9^n, v(\epsilon)^n)$, while for $\rho_S(\epsilon')^{\otimes n'}$ by $(1/9^{n'}, v(\epsilon')^{n'})$, and by requiring that the initial slope for the input state Lorenz curve is larger than that of the output state (Proposition~12 in Supplementary Note~2) we find that
 \begin{equation}\label{eq:unital-bound}
@@
 \end{equation}
-The choice of denoting the bound by $R_\infty$ is explained in Sec.~\ref{section:entropies} in relation to single-shot entropies.
+The choice of denoting the bound by $R_\infty$ is explained in the derivation of Eq.~(\ref{eq:Ra}) in relation to single-shot entropies.
 For the limiting case of pure magic states on the output ($\epsilon'=0$), this simplifies to
@@
 \begin{equation}
-	\theta_{\rm{max}}(\rho) \coloneqq \log \min{\{2\hspace{1pt}\sn{V}+1 : V \geq \rho\}}
+	\theta_{\rm{max}}(\rho) \coloneqq \log \min{\{2\hspace{1pt}{\rm sn}(V)+1 : V \geq \rho\}}
 \end{equation}
@@
 
-\section{Temperature-dependent bounds for magic state distillation protocols}
-\label{sec:stab}
+\subsection*{Temperature-dependent bounds for magic distillation protocols}
 
@@
 \end{equation}
-We may also assume that the reference state $\tau$ is not a magic state, and has a strictly positive Wigner distribution $W_\tau(\bmz)$.
+We may also assume that the reference state $\tau$ is not a magic state, and has a strictly positive Wigner distribution $W_\tau(\z)$.
 
@@
 
-\subsection{Free energy and sub-linear correlations in the thermodynamic limit}
+\subsection*{Free energy and sub-linear correlations in the thermodynamic limit}
+
 To keep our analysis simple we make the following physical assumption.
@@
 
-\subsection{Temperature-dependent distillation bounds}
+%\subsection*{Temperature-dependent distillation bounds}
 
@@
 
-In Appendix~\ref{app:lcst_technical} we analyse the Lorenz curves of this condition and obtain the following magic distillation bound that combines computational measures $\epsilon,\epsilon'$, with terms that depend on the Hamiltonian and reference temperature $T$ of the physical system.
+In Supplementary Note~4 we analyse the Lorenz curves of this condition and obtain the following magic distillation bound that combines computational measures $\epsilon,\epsilon'$, with terms that depend on the Hamiltonian and reference temperature $T$ of the physical system.
 We state the result for the case of qutrits, but a similar analysis works for general odd-dimension qudits.
@@
 	\zeta &= \sum_{k\in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}, \\
-	\alpha_k &= \<E_k| A_{\bmz_\star} |E_k\>,
+	\alpha_k &= \<E_k| A_{\z_\star} |E_k\>,
 \end{align}
-and $W_\tau(\bmz)$ attaining a minimum at $\bmz=\bmz_\star$. The primed variables are defined similarly for the output system.
+and $W_\tau(\z)$ attaining a minimum at $\z=\z_\star$. The primed variables are defined similarly for the output system.
 \end{theorem}
-\noindent The proof of this is provided in Appendix~\ref{app:lcst_technical}, and follows a similar line to the unital protocol bound.
+\noindent The proof of this is provided in Supplementary Note~4, and follows a similar line to the unital protocol bound.
 
@@
 Finally, if $H$ has a stabilizer eigenbasis then $\phi = E_i$ for some $i$, independent of the temperature $T$.
-Details of this are provided in Appendix~\ref{app:lcst_technical}.
-
-\subsection{Technical aspects and special cases}
+Details of this are provided in Supplementary Note~4.
+
+\revhigh{
+\subsection*{Technical aspects and special cases of free energy bounds}
+}
+
 Similar to the unital protocol bounds, the above result is based on only part of the Lorenz curves and so can certainly be tightened with further analysis.
 The primary role of the pre/post-processing by Clifford unitaries in Theorem~\ref{thm:free-energy} is to simplify the form of the bound, and allow it to be expressed in terms of the free energy per particle in a way that does not depend on the parameters $\epsilon, \epsilon', \beta$ in a complex form.
-In Appendix~\ref{app:lcst_technical}, we give bounds in which one does not include these Clifford changes of basis (see Theorem~\ref{thm:no-processing}), and which have a more non-trivial dependency on the parameters.
+In Supplementary Note~4, we give bounds in which one does not include these Clifford changes of basis, thus having a more non-trivial dependency on the parameters.
 
@@
     \centering
-    \subfigure[][]{
-    \label{fig:noCliff}
-    \includegraphics[scale=0.35]{figs/rate_scatter.pdf}}\\
-    \subfigure[][]{
-    \label{fig:Cliff}
-    \includegraphics[scale=0.35]{figs/rate_scatter_cliff.pdf}}
+    \includegraphics[scale=0.39]{rate_scatter_twopanels.pdf}
     \caption{\textbf{Temperature-dependent bounds for magic distillation.} Shown are two contour plots of the bound on $R(\epsilon, \beta)$ for the case $H = H' = \sum_{k \in \mathbb{Z}_3} k \ketbra{k}$ and $\epsilon' = 0$, where $\beta$ is the inverse temperature and $\epsilon$ is the depolarising error of the input magic state.
-The top figure~\subref{fig:noCliff} does not use any changes of Clifford basis, and the form of the bound depends on both the error parameter and temperature.
-The curved dashed line is $\epsilon_\star(\beta)$ and given by Eq.~(\ref{eq:threshold}) and $\beta_\star = (kT_\star)^{-1}$ is given by $E_2-\phi = kT_\star \ln 2$.
-In the bottom figure~\subref{fig:Cliff} Clifford processing is used resulting in a smoother bound. In both figures the $\beta = 0$ line correspond to the unital bounds.}
+The top figure~(a) does not use any changes of Clifford basis, and the form of the bound depends on both the error parameter and temperature.
+The curved dashed line is $\epsilon_\star(\beta)$ and given by Eq.~(86) in Supplementary Note~4 and $\beta_\star = (kT_\star)^{-1}$ is given by $E_2-\phi = kT_\star \ln 2$.
+In the bottom figure~(b) Clifford processing is used resulting in a smoother bound. In both figures the $\beta = 0$ line correspond to the unital bounds.}
     \label{fig:rate_contour}
@@
     \centering
-    \includegraphics[scale=0.35]{figs/R_vs_A.pdf}
+    \includegraphics[scale=0.35]{R_vs_A.pdf}
     \caption{\textbf{Variation of distillation bounds with Hamiltonian.}  We illustrate variation of the bound in Eq.~(\ref{eq:rate_bounds_proof}) with respect to the system Hamiltonian.
@@
 
-\section{Extension of single-shot entropies to quasi-distributions}\label{section:entropies}
+\subsection*{Extension of single-shot entropies to quasi-distributions}
+
 We have considered Wigner distributions of magic states within a statistical mechanical setting in which it was argued that magic can be viewed as a non-classical form of free energy.
@@
 \end{equation}
-It is clear that this does remain well-defined on quasi-distributions, and from the majorization relation also has a clear physical meaning, and in Appendix~\ref{app:lcst_technical}, we show that this divergence has the following properties that are derived via relative majorization.
+It is clear that this does remain well-defined on quasi-distributions, and from the majorization relation also has a clear physical meaning, and in Supplementary Note~4, we show that this divergence has the following properties that are derived via relative majorization.
 \begin{theorem}\label{thm:Dinfty}
@@
 The $\alpha$--R\'{e}nyi entropy $H_\alpha(\p)$ is defined as~\cite{renyi_1960}
-\begin{equation}
+\begin{equation}\label{eq:H}
 	H_\alpha(\p) \coloneqq \frac{1}{1-\alpha} \log \sum_i p_i^\alpha.
@@
 To extend to quasi-distributions we must ensure the following: (a) the entropy is mathematically well-defined on quasi-distributions, and (b) obeys monotonicity under the majorization pre-order.
-In Appendix~\ref{app:single-shot} we prove the following.
+In Supplementary Note~5 we prove the following.
 \begin{theorem}\label{thm:HSchur} 
@@
 The unusual form of the $\alpha$ parameter is required so that the entropy function is well-defined and real-valued for all $\w$.
-The allowed values of $\alpha$ are dense in $\alpha >1$, however, while R\'{e}nyi entropies on probabilities can also be used for $0 < \alpha <1$, it turns out that this parameter regime is no longer monotonic in terms of the majorization pre-order for quasi-distributions (see Appendix~\ref{app:single-shot} for details).
+The allowed values of $\alpha$ are dense in $\alpha >1$, however, while R\'{e}nyi entropies on probabilities can also be used for $0 < \alpha <1$, it turns out that this parameter regime is no longer monotonic in terms of the majorization pre-order for quasi-distributions (see Supplementary Note~5 for details).
 
@@
 \begin{equation}
-	H_{1+\epsilon}(W_\rho) = -\epsilon^{-1} \log \sum_{\bmz} |W_\rho (\bmz)|^{1+\epsilon}
-\end{equation} 
-with $\epsilon \rightarrow 0^+$ through a sequence of rational values.
-We recall that mana can be written as $\M(\rho) = \log \sum_{\bmz} |W_\rho(\bmz)|$, so we obtain a second new perspective on mana:
+	H_{1+\epsilon}(W_\rho) = -\epsilon^{-1} \log \sum_{\z} |W_\rho (\z)|^{1+\epsilon}
+\end{equation} 
+with $\epsilon \rightarrow 0^+$ through a sequence of rational values. We recall that mana can be written as $\M(\rho) = \log \sum_{\z} |W_\rho(\z)|$, so we obtain a second new perspective on mana:
 \begin{equation}\label{eq:mana-divergence}
@@
 
-\subsection{R\'{e}nyi divergences and general distillation bounds}
+\subsection*{R\'{e}nyi divergences and general distillation bounds}
 Every entropy can be obtained from a relative entropy~\cite{Gour_2020} so we now state the extensions for R\'{e}nyi divergences of Wigner distributions.
 The $\alpha$--R\'{e}nyi divergence $D_\alpha(\p||\r)$ is defined as
-\begin{equation}
+\begin{equation}\label{eq:D}
 	D_\alpha(\p \hspace{1pt}||\hspace{1pt} \r) \coloneqq \frac{1}{\alpha-1} \log \sum_i p_i^\alpha r_i^{1-\alpha},
 \end{equation}
-where $\p$ can be a quasi-distribution and $\r$ a probability distribution with positive components. In Appendix~\ref{app:single-shot}, we also show that the divergence satisfies the following.
+where $\p$ can be a quasi-distribution and $\r$ a probability distribution with positive components. In Supplementary Note~5, we also show that the divergence satisfies the following.
 
@@
 	Let $\tau$ be in the interior of $\F$. 
-	If $\alpha = \frac{2a}{2b-1}$ for positive integers $a,b$ with $a \geq b$, then the $\alpha$-R\'{e}nyi divergence $D_\alpha(W_\rho || W_\tau)$ is well-defined for all quantum states $\rho$, and the following hold:
+	If $\alpha = \frac{2a}{2b-1}$ for positive integers $a,b$ with $a \geq b$, then the $\alpha$-R\'{e}nyi divergence $D_\alpha(W_\rho || W_\tau)$ is well-defined for all states $\rho$, and the following hold:
 \begin{enumerate}
@@
 We can now apply this to obtain a family of magic distillation bounds based on R\'{e}nyi divergences.
+
 \begin{theorem}\label{thm:entropic_bounds}
-	Consider a general magic state distillation protocol on odd prime dimension qudits, that converts a magic state $\rho^{\otimes n} \longrightarrow \E(\rho^{\otimes n})=\rho'^{\otimes m}$and let $\tau$ be any full-rank stabilizer reference state on a qudit.
-Then the distillation rate $R \coloneqq m/n$ is upper bounded as,
+	Consider a general magic state distillation protocol on odd prime dimension qudits, that converts a magic state $\rho^{\otimes n} \longrightarrow \E(\rho^{\otimes n})=\rho'^{\otimes m}$ and let $\tau$ be any full-rank stabilizer reference state on a qudit.
+Then, the distillation rate $R \coloneqq m/n$ is upper bounded as
 	\begin{equation}
@@
 \end{theorem}
-The proof is given in Appendix~\ref{app:single-shot}.
+The proof is given in Supplementary Note~5.
 
@@
 We can illustrate a basic application of the above bound for magic protocols that give unital maps. In this case it is easy to see that the above bound reduces to the simple form
-\begin{equation}
+\begin{equation}\label{eq:Ra}
 	R \leq R_\alpha \coloneqq \frac{2\log d - H_{\alpha}(W_\rho)}{2\log d - H_{\alpha}(W_{\rho'})}.
@@
 
-\section{Outlook and open questions}
-\label{sec:lower_bounds}
+\section*{Discussion}
 
@@
 That said, for special states such as the Strange state, the asymptotic behaviour is relatively simple, so exact asymptotics for this should be possible.
-In Appendix~\ref{app:lcsu_technical} and Appendix~\ref{app:lcst_technical} we give additional results that may be of use for later work.
+In Supplementary Notes~2,~3 and~4 we give additional results that may be of use for later work.
 
@@
 In contrast to the upper bounds, it is now essential to include the symplectic constraints on the phase space in the majorization relations.
-The Clifford group action on a quantum system corresponds to the action of the affine symplectic group $G=SL(2,\mathbb{Z}_d) \ltimes \mathbb{Z}_d^2$ on the discrete phase space~\cite{Appleby_2005, Bengtsson_2006}.
+The Clifford group action on a quantum system corresponds to the action of the affine symplectic group $G \coloneqq SL(2,\mathbb{Z}_d) \ltimes \mathbb{Z}_d^2$ on the discrete phase space~\cite{Appleby_2005, Bengtsson_2006}.
 Therefore, any convex mixture of Clifford unitaries will correspond to a convex mixture of these group actions.
 The Hardy-Littlewood theorem~\cite{hardy_1952} tells us that majorization is obtained from convex mixtures of arbitrary permutations, a result that has also been generalized to convex mixtures of elements of a general group $G$.
-This $G$--majorization has been studied in the classical literature and a range of results are known about it~\cite{giovagnoli_1985, steerneman_1990, eaton_1977}.
-For example, it is known that if $G$ is a finite reflection group then the $G$--majorization pre-order is described by a finite list of conditions~\cite{giovagnoli_1985}, just as is the case for the relative majorization ordering.
+$G$--majorization has been studied in the classical literature and a range of results are known about it~\cite{giovagnoli_1985, steerneman_1990, giovagnoli_cyclic_1996, eaton_1977}.
+\revhigh{One one hand, the sub-group considered may potentially be too simple for distillation to be possible, such as the group corresponding to Weyl covariant channels~\cite{fukuda2006}.
+On the other hand, more non-trivial and useful classes of operations could be analysed but the majorization conditions may not be solvable in closed form.
+However, one can use techniques from semi-definite programming to estimate the distillation rates.
+A nice example occurs when $G$ is a finite reflection group.
+Then, the $G$--majorization pre-order is described by a finite list of conditions~\cite{giovagnoli_1985}, just as is the case for the relative majorization ordering.}
 One route leading to concrete lower bounds on distillation rates is therefore to consider reflection sub-groups of $SL(2,\mathbb{Z}_d) \ltimes \mathbb{Z}_2$, or other simple sub-groups, for which the majorization relation reduces to a finite set of conditions.
@@
 
-\section{Acknowledgements}
+\revhigh{
+\section*{Methods}
+
+In order to derive our results we make use of three broad subfields.
+The first one is the phase space representation of quantum systems as described in the first section of our Results.
+Generally, there are various possible representations~\cite{Ferrie_2008}, but we make use of the distinguished Wigner representation~\cite{Gross2006} for odd-dimensional systems.
+
+We then make use of various forms of majorization to impose a parital order between magic states.
+In hierarchical order from the specific to the general, we make use of: standard majorization~\cite{cit:marshall}, $\d$-majorization~\cite{Veinott_1971} and relative majorization~\cite{Ruch_1976}.
+
+Finally, the classical R\'{e}nyi entropies and divergences~\cite{renyi_1960} emerge naturally from a majorization setting and possess sufficient properties for the derivation of our entropic bounds.
+
+Precise definitions of all the above concepts and explanations of their incorporation to the study of magic distillation are provided in the Results section as the concepts become relevant.
+}
+
+\section*{Data availability}
+No datasets were generated or analysed during the current study.
+
+\section*{Code availability}
+The code used to produce the figures in this work is available from the corresponding author upon reasonable request.
+
+\section*{Acknowledgements}
 We thank Earl Campbell, Matteo Lostaglio, Philippe Faist and Nicole Yunger Halpern for helpful comments and discussions.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\bibliography{bib}
-%\bibliographystyle{apsrev4-2}
-%\input{ms.bbl}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\appendix
-\newpage
-\section{Properties of Wigner representations}
-\label{app:wigner}
-
-In this appendix we present basic properties of the phase-point operators and the Wigner distribution that are used throughout the paper.
-
-\begin{proposition}\label{thm:aproperties}
-    For any dimension $d$, the phase-point operators satisfy:
-    \begin{enumerate}
-        \item[(i)]\label{en:a1} Hermiticity and unitarity: $A_{\bmz}^\dagger = A_{\bmz} = A_{\bmz}^{-1}$;
-	    \item[(ii)]\label{en:a2} Closure under transposition: $A_{(q, p)}^T = A_{(q, -p)}$;
-	    \item[(iii)]\label{en:a3} Unit trace for odd $d$: $\tr[A_{\bmz}] = 1$;
-	    \item[(iv)]\label{en:a4} Completeness relation: $\sum_{\bmz \in \cal{P}_d} A_{\bmz} = d\id$;
-	    \item[(i)]\label{en:a5} Orthogonality: $\tr[A_{\bmz}^\dagger A_{\bmy}] = d \delta_{\bmz,\bmy}$.
-	\end{enumerate}
-\end{proposition}
-All properties follow from the definition in Eq.~(\ref{eq:ax}) along with properties of the displacement operators $D_{\bmz}$ and can be found in the literature, e.g.~\cite{cit:veitch,Vourdas_2004,cit:gross3}
-
-\begin{proposition}\label{thm:wstate}
-  The state Wigner distribution is
-  \begin{enumerate}
-    \item[(i)]\label{en:w1} Real valued: $\W{\rho}(\bmz) \in \mathbb{R}^{d^2}$;
-    \item[(ii)]\label{en:w2} Normalized: $\sum_{\bmz \in \cal{P}_d} \W[\bmz]{\rho}=1$;
-    \item[(iii)]\label{en:w3} Bounded: $\abs{\W[\bmz]{\rho}} \leq \frac{1}{d}$.
-    \item[(iv)]\label{en:w4} Additive under mixing: \vspace{2pt}\\
-    $\W[\bmz]{p\rho_1 + (1-p)\rho_2} = p\W[\bmz]{\rho_1} + (1-p)\W[\bmz]{\rho_2}$;
-    \item[(v)]\label{en:w5} Multiplicative under tensor products: \vspace{2pt}\\
-    $\W[\bmz_A \oplus \bmz_B]{\rho_A \otimes \rho_B} = \W[\bmz_A]{\rho_A}\W[\bmz_B]{\rho_B}$.
-	\end{enumerate}
-\end{proposition}
-\begin{proof}
-	Proof of all properties can be found in the literature~\cite{cit:veitch,Vourdas_2004,cit:gross3,Wang_2019} except for property (iii) which we prove here.
-
-Let $\{\lambda_i\}_{i \in \mathbb{Z}_d}$ be the (non-negative) eigenvalues of $\rho$, summing to 1.
-Let $\{\alpha_{\bmz,i}\}_{i \in \mathbb{Z}_d}$ be the eigenvalues of $A_{\bmz}$. For any $\bmz, \alpha_{\bmz,i} \in \{-1, 1\}$, due to the hermiticity and unitarity of the phase-point operators. 
-Then,
-\begin{align}
-	\abs{W_{\rho}(\bmz)} &= \frac{1}{d}\abs{\tr[A_{\bmz} \rho]} \leq \frac{1}{d} \abs{\sum_i \alpha_{\bmz,i} \lambda_i} \nonumber\\ &\leq \frac{1}{d}\sum_i \lambda_i = \frac{1}{d}.
-\end{align}
-The first inequality follows from Theorem 1 of~\cite{cit:mirsky} for the trace of complex matrices, while the second is the Cauchy-Schwarz inequality.
-\end{proof}
-
-\begin{proposition}
-    \label{thm:wchannel}
-    The Wigner distribution of a quantum channel $\E: \cal{B}(\cal{H}_{d_A}) \rightarrow \cal{B}(\cal{H}_{d_B})$ is
-    \begin{enumerate}
-        \item[(i)]\label{en:wo1} Real-valued: $\W{\E}(\bmz|\bmy) \in \mathbb{R}^{d_A^2} \times \mathbb{R}^{d_B^2}$;
-        \item[(ii)]\label{en:wo2} Normalized: $\sum_{\bmy \in \cal{P}_{d_{\scalebox{.9}{$\scriptscriptstyle B$}}}} \W[\bmz|\bmy]{\E} = 1$ \\ 
-        for any $\bmz \in \cal{P}_{d_A}$;
-        \item[(iii)]\label{en:wo3} Bounded: $\abs{\W[\bmz|\bmy]{\E}} \leq \frac{d_A}{d_B}$;
-	    \item[(iv)]\label{en:wo4} $\W[\bmz]{\E(\rho)} = \sum\limits_{\bmy \in \cal{P}_{d_{A}}} \W[\bmz|\bmy]{\E} \W[\bmy]{\rho}$ for any $\bmz \in \cal{P}_{d_B}$.
-    \end{enumerate}
-\end{proposition}
-\begin{proof}
-	Proof of all properties are provided in~\cite{Wang_2019} except for property (iii) which is a direct consequence of the definition of $\W{\E}$ and property (iii) in Proposition~\ref{thm:wstate}.
-\end{proof}
-
-Within the context of the Wigner representation, we define the rescaled quasi-distribution
-\begin{equation}
-	W_{\rho|\tau}(\bmz) \coloneqq \frac{W_\rho (\bmz) }{ W_\tau(\bmz)},
-\end{equation}
-which is well-defined if $\tau$ is a full-rank stabilizer state.
-
-The following result shows that the rescaled Lorenz curves behave in a natural way under tensor products. 
-\begin{proposition}\label{prop:rescaled_multi}
-	Let $\tau_A, \tau_B$ be full rank stabilizer states on systems $A$ and $B$, and let $\rho_A, \rho_B$ be arbitrary states on $A,B$. Then, the rescaled quasi-distribution obeys
-\begin{equation}
-W_{\rho_A \otimes \rho_B | \tau_A \otimes \tau_B}(\bmz_A \oplus \bmz_B) =W_{\rho_A | \tau_A}(\bmz_A) W_{\rho_B | \tau_B}(\bmz_B)
-\end{equation}
-\end{proposition}
-\begin{proof} This follows from the multiplicativity of the Wigner distribution,
-\begin{align}
-W_{\rho_A \otimes \rho_B | \tau_A \otimes \tau_B}(\bmz_A \oplus \bmz_B) &= \frac{W_{\rho_A \otimes \rho_B} (\bmz_A \oplus \bmz_B)}{W_{\tau_A \otimes \tau_B} (\bmz_A \oplus \bmz_B)}\nonumber \\
- = \frac{W_{\rho_A } (\bmz_A )W_{\rho_B } (\bmz_B )}{W_{\tau_A } (\bmz_A )W_{\tau_B } (\bmz_B )} &= W_{\rho_A | \tau_A}(\bmz_A) W_{\rho_B | \tau_B}(\bmz_B). \nonumber
-\end{align}
-\end{proof}
-
-\section{Properties of relative majorization and Lorenz curves}
-\label{app:major}
-
-\subsection{Relative majorization for quasi-distributions}
-\label{app:rel_quasi}
-
-We define a Lorenz curve \emph{elbow} as a point where the slope of the curve changes, in accordance to the use of the term for Lorenz curves of proper probability distributions.
-
-Here, we verify useful majorization properties in the context of quasi-probability distributions, starting from the property that the Lorenz curve is concave.
-\begin{proposition}\label{L-concave} 
-	Let $\w$ be a quasi-distribution and let $\r$ be a probability distribution with strictly non-zero components. Then $L_{\w|\r}(x)$ is a concave function on $[0,1]$.
-\end{proposition}
-\begin{proof} 
-	Let $x_\star$ be the point where $L_{\w|\r}(x)$ first attains it maximum.
-Therefore, on $[0,x_\star]$ the function rises monotonically to $L_{\w|\r}(x_\star)$, via the sum of all positive entries of $\w$, taken in decreasing order.
-Likewise on $[x_\star, 1]$, the function decreases monotonically from its maximum via the partial sums of the negative entries of $\w$ in decreasing order.
-Let $f_1(x)$ be equal to $L_{\w|\r}(x)$ on $[0, x_\star]$ and $0$ otherwise.
-Also let $f_2(x)$ be equal to $L_{\w|\r}(x)$ on $[x_\star,1]$ and and $0$ otherwise.
-By inspection both $f_1$ and $f_2$ are concave functions, and $f_1(x) + f_2 (x) = L_{\w|\r}(x)$ for all $x\in [0,1]$.
-However, the sum of two concave functions is also concave which concludes the proof.
-\end{proof}
-
-The following result is used in Sec.~\ref{sec:lc} to prove that the Lorenz curve condition due to relative majorization is true for quasi-distributions.
-\begin{proposition}\label{Lorenz_linearity}
-	Let $\w$ be a quasi-distribution and let $\r$ be a probability distribution with strictly non-zero components. 
-	Then, $L_{a\w + b \r | \r} (x) = a L_{\w |\r}(x) + b x$ for any constants $a > 0$ and $b \in \mathbb{R}$.
-\end{proposition}
-\begin{proof} 
-	The Lorenz curve of $a\w + b \r$ relative to $\r$ passes through $(0,0)$ and the points $(\sum_{i=1}^k{r_{\pi(i)}}, \sum_{i=1}^k(a \w + b \r)_{\pi(i)})$ where $\pi$ is the permutation that puts $(a w_i/r_i + b)$ in non-increasing order.
-Since $a > 0$, the permutation $\pi$ puts  $(w_i/r_i)$ in non-increasing order too.
-We thus have
-\begin{align*}
-&\left( \sum_{i=1}^k r_{\pi(i)}, \sum_{i=1}^k(a \w + b \r)_{\pi(i)} \right) = \\ 
-&\left( \sum_{i=1}^k r_{\pi(i)},a \sum_{i=1}^k  w_{\pi(i)} + b\sum_{i=1}^k r_{\pi(i)} \right) \nonumber,
-\end{align*}
-so the value of the Lorenz curve at each potential elbow point $x_k = \sum_{i=1} ^kr_{\pi(i)}$ is given by
-\begin{align}
-&L_{a \w +b \r|\r} (x_k) = a L_{\w|\r} (x_k) + b L_{\r|\r}(x_k) = \nonumber\\
-&a L_{\w|\r} (x_k) + b x_k,
-\end{align}
-so we have $L_{a\w  + b\r|\r} (x) = a L_{\w |\r}(x) + b x$ for any $x \in [0,1]$ due to linearity.
-\end{proof}
-
-The following provides equivalent formulations of relative majorization on quasi-distributions.
-
-\begin{proposition}\label{prop:rmajor}
-Given quasi-distributions $\w, \w'$, $\r , \r'$, such that the components of $\r$ and $\r'$ are positive, the following statements are equivalent:
-  \begin{enumerate}
-    \item[(i)] $\w' = A\w$ and $\r' = A\r$ for a stochastic map $A$;
-    \item[(ii)] $L_{\w|\r}(t) \geq L_{\w'|\r'}(t)$ for $t\in [0,1)$ and \vspace{5pt}\\ $L_{\w|\r}(1) = L_{\w'|\r'}(1)$;
-    \item[(iii)] $\sum\limits_{i=1}^n \abs{w_i - r_i t} \geq \sum\limits_{i=1}^n \abs{w'_i - r'_i t}$ for all $t \in \mathbb{R}$.
-  \end{enumerate}
-\end{proposition}
-\begin{proof}
-	The proofs for these properties on proper probability distributions can be found in~\cite{cit:marshall,ruch_mixing_1978,Renes_2016,Buscemi_2017} and references therein.
-
-	The equivalence between (i) and (ii) on quasi-distributions was proven in Theorem~\ref{thm:lcquasi}.
-
-	The equivalence between (i) and (iii) follows from a similar argument where we mask negativity with a probability distribution.
-	Namely, let $\epsilon > 0$ be such that $\w(\epsilon) \coloneqq \epsilon \w + (1-\epsilon) \r$ and $\w'(\epsilon) \coloneqq \epsilon \w + (1-\epsilon) \r'$ are genuine probability distributions.
-This is guaranteed by picking a sufficiently small $\epsilon > 0$, since $\r$ has positive components.
-We now have that $(\w , \r) \succ (\w', \r')$ if and only if $(\w(\epsilon) , \r) \succ (\w'(\epsilon), \r')$.
-	Moreover, we have that for all $c \in \mathbb{R}$, $\sum_{i=1}^n \abs{w(\epsilon)_i - r_i c} \geq \sum_{i=1}^n \abs{w'(\epsilon)_i - r'_i c}$, which leads to
-	\begin{align*}
-		\sum\limits_{i=1}^n \abs{w_i - r_i \frac{\epsilon + c - 1}{\epsilon}} \geq \sum\limits_{i=1}^n \abs{w'_i - r'_i \frac{\epsilon + c - 1}{\epsilon}}
-	\end{align*}
-Replacing $t = (\epsilon + c - 1)/\epsilon$, we see that $t$ can attain any real value for $c \in \mathbb{R}$, so we deduce the required $L_1$--norm condition on quasi-distributions $\w, \w'$.
-\end{proof}
-
-We prove the following result connecting majorization to relative majorization~\cite{cit:horodecki2013, Brandao_2015,  cit:lostaglio}.
-\begin{proposition}\label{relmaj2maj}
-	Let $\w\in \mathbb{R}^N, \w'\in \mathbb{R}^{N'}$ be quasi-distributions and $\r\in \mathbb{R}^N, \r'\in \mathbb{R}^{N'}$ probability distributions with positive rational entries given by $r_i = a_i/K$ and $r_i' = a_i'/K$ for positive integers $a_i, a_i'$ and $K = \sum_{i=1}^N a_i = \sum_{i=1}^{N'} a_i'$.
-Then,
-\begin{equation}
-(\w, \r) \succ (\w', \r') \mbox{ if and only if } \Gamma_{\bma} (\w) \succ \Gamma_{\bma'} (\w'),
-\end{equation}
-where the embedding map $\Gamma_{\bma} :\mathbb{R}^N \rightarrow \mathbb{R}^K$ is given by
-\begin{equation}
-	\Gamma_{\bma}(\bmz) \coloneqq \bigoplus_{i=1}^N x_i \eta_{a_i},
-\end{equation}
-with $\eta_{a_i} = (1/a_i, 1/a_i, \dots, 1/a_i)$ the uniform distribution on $a_i$ elements.
-\end{proposition}
-\begin{proof}
-	We first note that the map $\Gamma_{\bma}$ is stochastic and has a well-defined left-inverse $\Gamma^{-1}_{\bma'}: \mathbb{R}^K \rightarrow \mathbb{R}^N$ given by
-\begin{equation}
-	\Gamma^{-1}_{\bma}(\w) = \left( \sum_{i=1}^{a_1} w_i,  \sum_{i = a_1 +1}^{a_1 + a_2} \hspace{-5pt} w_i, \dots , \hspace{-15pt} \sum_{i=a_1 + \dots + a_{N-1}+1}^{K} \hspace{-10pt} w_i \right),
-\end{equation}
-that obeys $(\Gamma^{-1}_{\bma} \circ \Gamma_{\bma}) (\bmz) = \bmz$ for all $\bmz \in \mathbb{R}^N$.
-
-The claim is equivalent to the statement that there exists a \emph{bistochastic map} $B$ sending $\Gamma_{\bma}(\w)$ to $\Gamma_{\bma'}(\w')$ if and only if there exists a stochastic map $A$ sending $\w$ to $\w'$ and $\r$ to $\r'$.
-
-Suppose there is a stochastic map $A$ such that $A\w=\w'$ and $A\r = \r'$. 
-We define $B:\mathbb{R}^K \mapsto \mathbb{R}^K$ by $B \coloneqq \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1}$ so that it is stochastic as a composition of stochastic maps and it preserves the uniform distribution in $\mathbb{R}^K$, since
-\begin{align}
-	&B(1/K, 1/K, \dots, 1/K) = \big( \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1} \big) \big( \Gamma_{\bma'}(\r) \big) = \nonumber\\
-	&\Gamma_{\bma'} (\r') = (1/K, 1/K, \dots, 1/K),
-\end{align}
-therefore $B$ is bistochastic.
-Finally, $B$ maps the embedded distributions as follows,
-\begin{equation}
-	B \Gamma_{\bma}(\w) = \big( \Gamma_{\bma'} \circ A \circ \Gamma_{\bma}^{-1} \big) \big( \Gamma_{\bma}(\w) \big) = \Gamma_{\bma'} (\w').
-\end{equation}
-
-Conversely, suppose a bistochastic map $B$ exists sending $\Gamma_{\bma}(\w)$ to $\Gamma_{\bma'}(\w')$.
-Again, define $A: \mathbb{R}^N \mapsto \mathbb{R}^{N'}$ by $A \coloneqq \Gamma_{\bma'}^{-1} \circ B \circ \Gamma_{\bma}$ so that it is stochastic as a composition of stochastic maps and $A \w = \big( \Gamma_{\bma'}^{-1} \circ B \circ \Gamma_{\bma} \big) \w = \w'$, as well as $A \r = \r'$.
-\end{proof}
-We note that the vectors $\r, \r'$ with rational components form a dense subset of the positive probability distributions, and do not consider further technicalities that have no impact on actual physical measurements, which always have a finite resolution.
-
-\subsection{Component-multiplicity pairs}
-\label{app:cmpairs}
-
-In general, a $1$--copy $d$--dimensional state $\rho$ is described by its $d^2$--dimensional Wigner distribution $\W{\rho}$. 
-The distribution $\W{\rho}$ is defined on the phase space, but it can be convenient to re-express this using vector notation.
-We discuss this in terms of Wigner distributions, but there is nothing to prevent the discussion from applying to rescaled Wigner distributions as well.
-
-To each Wigner distribution $W_\rho(\bmz)$ we can associate \emph{component-multiplicity} pairs $\{(w_i, m_i)\}$ where the value $w_i$ occurs in the distribution $W_\rho(\bmz)$ with multiplicity $m_i$.
-
-As an example, for the Strange state $\rho_S \coloneqq \rho_S(\epsilon=0)$ with
-\begin{equation}
-\hspace{-5pt} W_{\rho_S} = (-1/3, 1/6,  1/6,  1/6,  1/6,  1/6,  1/6,  1/6,  1/6)
-\end{equation}
-we have the component-multiplicity pairs: $\{( -1/3, 1), ( 1/6, 8)\}$.
-However, we might also wish more freedom and not require that the different $w_i$ values are all distinct.
-For example, the component-multiplity pairs $\{(-1/3, 1), (1/6, 2), (1/6, 3), (1/6, 3)\}$ also describe $W_{\rho_S}$.
-
-This representation is more compact when a Wigner distribution has a lot of multiplicities, and allows for simple handling of multiple copies via the following fact.
-\begin{proposition}
-Consider two Wigner distributions $\W{\rho_A}(\bmz_A), \W{\rho_B}(\bmz_B)$ with component-multiplicity pairs 
-\begin{equation}
-	\{(w_i, m_i)\} \text{ and } \{(w_j', m_j')\},
-\end{equation}
-respectively. Then, $\{(w_i w_j', m_i m_j')\}$ gives component-multiplicity pairs for $\W{\rho_A \otimes \rho_B}(\bmz_A \oplus \bmz_B)$.
-\end{proposition}
-\begin{proof}
-	This result is true because all components of $\W{\rho_A \otimes \rho_B}(\bmz_A \oplus \bmz_B)$ are of the form $w_i w_j'$ and 
-\begin{equation*}
-	\sum_{i}\sum_{j} m_i m_j' = \sum_{i} m_i \sum_{j} m_j' = d_A^2 d_B^2,
-\end{equation*}
-where $d_A, d_B$ are the dimensions of $\rho_A, \rho_B$ respectively, and
-so the set $\{(w_i w_j', m_i m_j')\}$ contains exactly the Wigner components of $\W{\rho_A \otimes \rho_B}(\bmz_A \oplus \bmz_B)$.
-\end{proof}
-The above result also applies when we consider rescaled Wigner distributions, crucially due to the multiplicativity result shown in Proposition~\ref{prop:rescaled_multi}.
-
-In the case of distillation protocols, we are interested in copies of distributions. 
-For this, we have the following result, which follows from combinatorics.
-\begin{proposition}\label{ncopycomponents}
-	Suppose $W_\rho$ has a set of $D$ component-multiplicity pairs $\{(w_i, m_i)\}$.
-Then, $W_{\rho^{\otimes n}}$ has component-multiplicity pairs $\{(W_{\q}, M_{\q})\}$, with index $\q$ running through all vectors $(q_1, \dots, q_D)$, where $q_1, \dots, q_D$ are non-negative integers that sum to $n$, and
-\begin{align}
-	W_{\q} &= \prod_{i=1}^D w_i^{q_i} \label{eq:W}\\
-	M_{\q} &= \binom{n}{q_1,q_2, \dots, q_d} \prod_{i=1}^D m_i^{q_i}. \label{eq:M}
-\end{align}
-The term outside the product in the expression for $M_{\q}$ is the generalized binomial coefficient,
-\begin{equation}
-	\binom{n}{q_1,q_2, \dots, q_d} \coloneqq \frac{n!}{q_1!\dots q_D!}.
-\end{equation}
-\end{proposition}
-\begin{proof}
-	Denote by $C_D^n \coloneqq \{\bmk\}$ the set of all vectors $\bmk \coloneqq (k_1, \dots, k_D)$ with non-negative integer components that sum to $n$, i.e.
-	\begin{equation*}
-	0 \leq k_1, \dots, k_D \leq n \text{ and } k_1 + \dots + k_D = n.
-	\end{equation*}
-
-	We proceed by induction.	
-	Assume $n = 1$ and let $\bmk_i$ be the vector with its $i$-th component equal to 1 and 0's elsewhere.
-	The set $C_D^1$ consists of all vectors of this form, i.e. 
-\begin{equation*}
-	C_D^1 = \{ \bmk_i \}_{i=1,\dots,D}
-\end{equation*}
-	It is also true by direct calculation that
-\begin{equation*}
-	\left( W_{\bmk_i}, M_{\bmk_i} \right) = (w_i, m_i).
-\end{equation*}
-Therefore, $\{ (W_{\bmk}, M_{\bmk}) \}_{\bmk \in C_D^1}$ is a complete set of component-multiplicity pairs for $W_\rho$.
-
-	Assume that $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$ as given in Eqs.~(\ref{eq:W}, \ref{eq:M}) is a complete set of component-multiplicity pairs for the $n$--copy distribution $W_{\rho^{\otimes n}} = W_{\rho}^{\otimes n}$.
-	By construction, the distribution $W_{\rho}^{\otimes (n+1)} = W_{\rho}^{\otimes n} \otimes W_{\rho}$, so it admits the complete set of component multiplicity pairs
-\begin{equation}
-	\{(W_{\bmk} w_i, M_{\bmk} m_i)\},\ \bmk \in C_D^n \text{ and } i=1,\dots,D.
-\end{equation}
-
-	Consider the component sum of distribution $W_{\rho}^{\otimes (n+1)}$,
-\begin{align*}
-	&\sum_{\bmk \in C_D^n}\sum_{i=1}^D M_{\bmk} m_i W_{\bmk} w_i = \sum_{\bmk \in C_D^n} M_{\bmk}W_{\bmk} \sum_{i=1}^D m_i w_i =\\
-	&\sum_{\bmk \in C_D^n} \frac{n!}{k_1!\dots k_D!} \prod\limits_{i=1}^D {m_i}^{k_i}{w_i}^{k_i} \sum_{i=1}^D m_i w_i =\\
-	&\left( \sum_{i=1}^D m_i w_i \right)^n \left( \sum_{i=1}^D m_i w_i \right) = \left( \sum_{i=1}^D m_i w_i \right)^{n+1} =\\
-	&\sum_{\bmq \in C_D^{n+1}} M_{\bmq}W_{\bmq},
-\end{align*}
-where in the last expression, vectors $\bmq = (q_1, \dots, q_D)$ have non-negative integer components that sum to $(n+1)$ and 
-\begin{align*}
-	M_{\bmq} &= \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i},\\
-	W_{\bmq} &= \prod\limits_{i=1}^D {w_i}^{q_i}.
-\end{align*}
-We have used the multinomial theorem to proceed between lines 2-3 and lines 3-4 of the derivation.
-
-We have achieved a regrouping of the distribution components.
-Every component $W_{\bmq}$ is of the form $W_{\bmk} w_i$ with $q_i = k_i + 1$ and $q_j = k_j$ for $j\neq i$ and 
-\begin{align*}
-	\sum_{\bmq \in C_D^{n+1}}  \hspace{-6pt} M_{\bmq} &=  \hspace{-10pt} \sum_{\bmq \in C_D^{n+1}} \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i} = \left( \sum_{i=1}^D m_i \right)^{n+1} \hspace{-10pt} \\
-	&= d^{2(n+1)},
-\end{align*}
-which is the dimension of $W_{\rho}^{\otimes (n+1)}$.
-
-Therefore, $\{ (W_{\bmq}, M_{\bmq}) \}_{\bmq \in C_D^{n+1}}$ contains exactly the components of $W_{\rho}^{\otimes n}$, completing the proof.
-\end{proof}
-Once again, the above result applies on rescaled Wigner distributions as well.
-
-\subsection{Results on Lorenz curve constraints}
-\label{app:lc_constraints}
-
-We first prove the following result on the relation between majorization in a particular sub-theory $\R_\sigma$ and mana, which was stated in Sec.~\ref{sec:monotones_frag}.
-\begingroup
-\def\thetheorem{\ref{lem:lcmax}}
-\begin{theorem}
-	Given a magic state $\rho$, the maximum value $L_\star$ attained by the Lorenz curve $\lc{\rho}{\sigma}(x)$ is independent of the $\R_\sigma$ and equal to $1+\sn{\rho}$.
-Moreover, the relative majorization constraint is stronger than mana in every $\R_\sigma$.
-\end{theorem}
-\addtocounter{theorem}{-1}
-\endgroup
-\begin{proof}
-	We denote the Wigner distributions of the states single-component vectors $\w(\rho)=W_\rho(\z)$ and $ \w(\sigma)=W_\sigma(\z)$. Likewise, we write $\w(\rho|\sigma) = W_{\rho|\tau}(\bmz)$.
-	We choose the component indexing so that $\w(\rho|\sigma)^\downarrow = \w(\rho|\sigma)$, so the components are sorted in non-increasing order.
-
-Note that all components of $\bmw(\sigma)$ are positive, so $w(\rho|\sigma)_i \geq 0$ if and only if $w(\rho)_i \geq 0$ for any $i=1,\dots,d^2$.
-
-	Let $i_\star$ be the index of the smallest non-negative component of $\w(\rho|\sigma)^\downarrow$.
-	Then, $w(\rho)_i < 0$ if and only if $i > i_\star$, so the maximum of Lorenz curve $\lc{\rho}{\sigma}(x)$ takes the value 
-	\begin{equation}
-		\lc{\rho}{\sigma}(x_{i_\star}) = \sum_{i=1}^{i_\star} w(\rho)_i,
-	\end{equation}
-	and is achieved at $x_{i_\star} \coloneqq \sum_{i=1}^{i_\star} w(\sigma)_i$. The location of this maximum varies with $\R_\sigma$, but its value is independent of $\sigma$,
-	\begin{align}
-	L_\star &\coloneqq	\lc{\rho}{\sigma}(x_{i_\star}) 
-		= \sum\limits_{\bmz: \W[\bmz]{\rho} \geq 0}\hspace{-5pt} \W[\bmz]{\rho} \nonumber \\
-		&= 1 + \sn{\rho}.
-	\end{align}
-
-Since mana is a monotonic function of sum-negativity, $\M(\rho) \coloneqq \log \hspace{1pt}(2\hspace{1pt}\sn{\rho}+1)$, we see that mana determines the peak of the Lorenz curve $L_{\rho|\sigma}(x)$.
-However, mana is one of $d^{2n}$ constraints, so majorization is strictly a stronger constraint in any $\R_\sigma$.
-\end{proof}
-
-We now prove a simple majorization constraint, arising by considering only the part of the Lorenz curves between the origin $(0,0)$ and the first elbow.
-\begin{proposition}[First elbow constraint]\label{prop:first_elb}
-	Consider a magic state process $\rho \longrightarrow \rho'$ with input and output Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\rho'}{\sigma'}(x)$ and denote the coordinates of the first elbow of $L_{\rho|\sigma}(x)$ by $(X_0, L_0)$ and the coordinates of the first elbow of $L_{\rho' |\sigma'}(x)$ by $(X'_0, L'_0)$.
-
-Then, given any coordinates $(x, L)$ and $(x', L')$ on the input and output Lorenz curves respectively, where $0 < x \leq X_0$ and $0 < x' \leq X'_0$, the process is possible only if
-\begin{equation}\label{eq:first_elb_bound1}
-	\frac{L}{x} \geq \frac{L'}{x'}.
-\end{equation}
-\end{proposition}
-\begin{proof} 
-	If the transformation is possible, then $L_{\rho|\sigma}(x) \geq L_{\rho'|\sigma'} (x)$ for all $x$ in $[0,1]$. 
-	Restricting to the initial linear segment of $L_{\rho|\sigma}(x)$ joining $(0,0)$ to $(X_0,L_0)$, we then require that it be above the initial linear segment of $L_{\rho'|\sigma'}(x)$ joining $(0,0)$ to $(X_0', L_0')$.
-	Since both these linear segments start at the origin, this condition is equivalent to the slope of the initial segment of the input Lorenz curve being greater than or equal to the slope of the initial segment of the output Lorenz curve.
-	This slope constraint is then equivalent to Eq.~(\ref{eq:first_elb_bound1}). \end{proof}
-
-The following result, referenced in Sec.~\ref{sec:major_frag}, reduces the Lorenz curve condition on the interval $[0,1]$ to a finite set of independent inequalities and can therefore simplify the computation of relative majorization constraints in practical scenarios.
-\begin{proposition}\label{thm:elbows}
-	Let $\rho, \rho'$ be any two quantum states with Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\rho'}{\sigma'}(x)$, where $\sigma, \sigma'$ are states with positive Wigner distributions.
-Assume that $\lc{\rho'}{\sigma'}(x)$ has $t$ elbows at locations $x_1, \dots, x_t$.
-Then, $\lc{\rho}{\sigma}(x) \geq \lc{\rho'}{\sigma'}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\rho'}{\sigma'}(x_{i})$ for all $i =1,\dots,t$.
-\end{proposition}
-\begin{proof}	
-If $\lc{\rho}{\sigma}(x) \geq \lc{\rho'}{\sigma'}(x)$ for all $x \in [0,1]$, then the condition on the elbows follows trivially.
-
-Conversely, assume $L_{\rho|\sigma}(x_i) \geq L_{\rho'|\sigma'}(x_i)$ for all $i=1,\dots t$. 
-Suppose on the contrary that $L_{\rho|\sigma}(x)$ dips below $L_{\rho'|\sigma'}(x)$ at some point $x=y$ where $x_i < y < x_{i+1}$ for some $i$. Then this implies
-\begin{align*}
-L_{\rho|\sigma}(x_i) &\ge L_{\rho'|\sigma'}(x_i) \\
-L_{\rho|\sigma}(y) & <L_{\rho'|\sigma'}(y) \\
-L_{\rho|\sigma}(x_{i+1}) &\ge L_{\rho'|\sigma'}(x_{i+1}).
-\end{align*}
-However, since $L_{\rho'|\sigma'}(x)$ is linear between $x_i$ and $x_{i+1}$, the above conditions imply that $L_{\rho|\sigma}(x)$ is not concave, which contradicts Proposition~\ref{L-concave}.
-Therefore, $L_{\rho|\sigma}(x) \geq L_{\rho'|\sigma'}(x)$ for all $x$ in $[0,1]$.
-\end{proof}
-
-\section{General aspects of Lorenz curves for noisy Strange states}
-\label{app:lcsu_technical}
-
-Here we provide background detail as to how the Lorenz curve behaves for a noisy Strange state in the large $n$ limit.
-
-\subsection{Binomial distributions and error bounds}\label{app:phi}
-Consider an experiment consisting of $n$ trials of throwing a coin with probability $p$ of landing on heads and $1-p$ of landing on tails.
-We denote the sums over an even number $m$ of successful trials by $\Phi_+(m; n, p)$ and an odd number $m$ of successful trials by $\Phi_-(m; n, p)$, and they are given by
-\begin{align}	
-	\Phi_+(m; n, p) &\coloneqq \sum\limits_{\ell=0}^{m/2} \binom{n}{2\ell} p^{2\ell} (1-p)^{n-2\ell}, \nonumber\\ 
-	&\text{for even integers } m\in[0,n], \label{eq:fp_app} \\
-	\Phi_-(m; n, p) &\coloneqq \sum\limits_{\ell=1}^{(m-1)/2} \binom{n}{2\ell+1} p^{2\ell+1} (1-p)^{n-(2\ell+1)}, \nonumber\\ 
-	&\text{for odd integers }m\in[0,n]. \label{eq:fn_app}
-\end{align}
-In Appendix~\ref{app:lcsu_coord}, we will use $\Phi_+$ and $\Phi_-$ to express the elbow coordinates of Lorenz curves for unital protocols.
-
-We have the Shannon entropy of a $p$--coin and the Shannon relative entropy for a $p$--coin and a $q$--coin given by the expressions
-\begin{align}
-	S(p) &\coloneqq -p\log{p} -(1-p)\log{(1-p)}, \label{eq:ent}\\
-	\ent{p}{q} &\coloneqq p \log{\frac{p}{q}} + (1-p) \log{\frac{1-p}{1-q}}. \label{eq:ent_rel}
-\end{align}
-They are symmetric about $p=1/2$ and $q=1/2$, namely $S(p) = S(1-p)$ and $\ent{p}{q} = \ent{1-p}{1-q}$. We also have the entropic bounds
-\begin{proposition}\label{comb_bounds}
-	For all $\ell\in [1,n-1]$,
-	\begin{align}
-		&\left[ 8\ell\left(1-\frac{\ell}{n}\right) \right]^{-\frac{1}{2}} 2^{n S\left(\frac{\ell}{n}\right)} \leq \binom{n}{\ell} \leq \\
-		&\left[ 2\pi \ell\left(1-\frac{\ell}{n}\right) \right]^{-\frac{1}{2}} 2^{n S\left(\frac{\ell}{n}\right)}.
-	\end{align}
-\end{proposition}
-The proof provided in~\cite{cit:ash} proceeds with direct calculation for the edge cases $\ell = 1,2, n-1, n-2$ and use of Stirling's approximation for the remaining cases.
-The bounds in Proposition~\ref{comb_bounds} can be directly inserted into the expressions of functions $\Phi_+$ and $\Phi_-$ to derive strict upper and lower bounds.
-
-It is also possible to derive more manageable bounds on $\Phi_+, \Phi_-$.
-To this end, we rewrite the functions as
-\begin{equation}
-	\Phi_{\pm}(m; n, a) = \frac{1}{2}(\Phi(m; n, a) \pm (1+a)^{-n} S(m; n, a)),
-\end{equation}
-where $a = p/(1-p)$, and $\Phi$ is the standard cumulative function for the binomial distribution
-\begin{equation}
-	\Phi(m; n, a) = (1+a)^{-n} \sum_{k=0}^m \binom{n}{k} a^k,
-\end{equation}
-and we define the remainder term
-\begin{equation}
-	S(m; n, a) \coloneqq \sum_{k=0}^m \binom{n}{k} (-a)^k.
-\end{equation}
-The cumulative function $\Phi$ obeys the following bounds, which are proven in~\cite{cit:ash}.
-\begin{proposition}\label{phi_bounds}
-	Given fixed $n>0$ and $p$, $\Phi$ satisfies the following bounds:
-	\begin{align*}
-		\begin{split}
-		&\text{1. } \Phi(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m}{n}}{p}}, \\
-		&\hspace{14pt} m\in [1,n-1] \\
-		&\text{2. } \Phi(m; n, p) \geq 1 - 2^{-n\ent{\frac{m+1}{n}}{p}},\ m\in [np+1,n-2] \\
-		&\text{3. } \Phi(m; n, p) \leq 1 - \left[ 8(m+1)\left(1-\frac{m+1}{n}\right) \right]^{-\frac{1}{2}}\times \\
-		&\hspace{14pt} 2^{-n\ent{\frac{m+1}{n}}{p}},\ m\in [0,n-2]
-		\end{split}
-		\\
-		&\text{4. } \Phi(m; n, p) \leq 2^{-n\ent{\frac{m}{n}}{p}},\ m\in [0,np]
-	\end{align*}
-\end{proposition}
-
-We can now put estimates on $S(m; n, a)$, and hence the functions $\Phi_{\pm}$, for different parameter regimes. 
-We can consider the function $f(x) = (1+x)^n$ and note that $S(m; n, a)$ is the $m$'th partial sum of this expansion at the point $x=-a$. The truncated Maclaurin series is given by
-\begin{equation}
-	f(x) = f(0) + x f'(0) + \dots \frac{x^m}{m!}f^{(m)}(0) + R_m(x)
-\end{equation}
-with a remainder term
-\begin{align}
-	R_m (x)&= \int_{0}^x dt f^{(m+1)}(t) \frac{(x-t)^m}{m!} \\
-	&= \frac{x^{m+1}}{(m+1)!} f^{(m+1)}(x_*),
-\end{align}
-where in the second expression, $x_*$ is a point that lies between $0$ and $x$ that comes from the Mean Value Theorem.
-
-Applying this to the function $f(x) = (1+x)^n$ gives
-\begin{equation}
-	(1+x)^n = \sum_{k=0}^m \binom{n}{k} x^k + R_m.
-\end{equation}
-Therefore, if we evaluate at $x=-a$ we obtain
-\begin{equation}
-	S(m; n, a) = (1-a)^n - R_m(-a),
-\end{equation}
-where the remainder term is given by
-\begin{align}
-	R_m(-a) &= \int_0^{-a} dt f^{(m+1)}(t) \frac{(-a-t)^m}{m!} \\
-&= \frac{(-a)^{m+1}}{(m+1)!} f^{(m+1)}(x_*).
-\end{align}
-We can compute the derivative $f^{(m+1)}(x)$ explicitly,
-\begin{equation}
-	f^{(m+1)}(x) = (m+1)!\binom{n}{m+1}(1+x)^{n-m-1}.
-\end{equation}
-Therefore, we have that
-\begin{align}
-	R_m(-a) &= (-1)^{m+1}(m+1)\binom{n}{m+1}\times \nonumber\\
-	&\hspace{12pt} \int_{-a}^0 dt (1+t)^{n-m-1}(a+t)^m \\
-&= \binom{n}{m+1}(-a)^{m+1}(1+x_*)^{n-m-1},
-\end{align}
-where in the latter expression $x_* \in [-a,0]$. 
-The first integral expression can be estimated via the Cauchy-Schwarz or the H{\"o}lder inequality. 
-Therefore, one has an explicit form with an unknown (but bounded) parameter $x_*$, or the integral form.
-
-A very simple estimate, based on $x_*$ lying in the interval $[-a,0]$ gives
-\begin{equation}
-(1-a)^{n-m-1} \leq \frac{R_m(-a)}{\binom{n}{m+1}(-a)^{m+1}} \leq 1,
-\end{equation}
-which in turn leads to the following bounds on $\Phi_+(m; n, a)$:
-\begin{align}
-	\hspace{-2cm}2\Phi_+(m; n, a) \leq\ &\Phi(m; n, a) + (1-a)^n - \frac{(-a)^{m+1}}{m!} \times \nonumber\\
-	 &\binom{n}{m+1} (1-a)^{n-m-1} \text{ and} \\
-	2\Phi_+(m; n, a) \geq\ &\Phi(m; n, a) + (1-a)^n - \frac{(-a)^{m+1}}{m!}  \times \nonumber\\
-	 &\binom{n}{m+1} .
-\end{align}
-Better bounds can be obtained with a finer analysis, and it would be of interest to obtain tighter asymptotic behaviour on $\Phi_{\pm}$ that could in turn be used to improve magic distillation bounds.
-
-\subsection{Lorenz curve coordinates for unital protocols}\label{app:lcsu_coord}
-
-The Wigner distribution of the $n$--copy qutrit maximally mixed state $\left(\id/3\right)^{\otimes n}$ is the uniform probability distribution over the phase space, consisting of $9^n$ components equal to $9^{-n}$.
-The Wigner distribution of the 1-copy $\epsilon$--noisy Strange state $\rho_{\rm{S}}(\epsilon)$ for unital protocols consists of some permutation of a single negative component
-\begin{equation}
-	- v(\epsilon) \coloneqq - \left( \frac{1}{3} -\frac{4}{9}\epsilon \right),
-\end{equation} 
-and $8$ positive components each with value
-\begin{equation}
-	u(\epsilon) \coloneqq \frac{1}{6} -\frac{1}{18}\epsilon.
-\end{equation}
-
-For unital protocols we need the condition $0 \leq \epsilon < 3/4$, so that the state contains some Wigner negativity ($-v < 0$).
-It is also clear that $v \geq u$ in the interval $0 \leq \epsilon \leq 3/7$, while $u > v$ in the interval $3/7 < \epsilon < 3/4$.
-
-The Wigner distribution of the $n$--copy $\epsilon$--noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ is given by $\W{\rho_{\rm{S}}(\epsilon)^{\otimes n}} = W_{\rho_{\rm{S}}(\epsilon)}^{\otimes n}$ and, using Proposition~\ref{ncopycomponents} for unital protocols, we can associate it with a set $\{(w_i, m_i)\}_{i=0,\dots,n}$ of component-multiplicity pairs, the elements of which are presented in Table~\ref{tab:lcsu} for all different combinations of physical parameters $n, \epsilon$.
-We split the values of index $i$ into two intervals, defined precisely as
-\begin{align}
-&\text{LHS: } 0 \leq i \leq \left\lfloor \frac{n}{2} \right\rfloor \text{ and} \\
-&\text{RHS: } \left\lfloor \frac{n}{2} \right\rfloor +1 \leq i \leq n.
-\end{align}
-The labels $\text{LHS}, \text{RHS}$ denote that the components contribute to the left hand side or the right hand side of the Lorenz curve maximum.
-The maximum is included in the $\text{LHS}$ interval.
-\begin{table}[h]
-  \def\arraystretch{1.5}
-  \centering
-  \begin{tabular}{c|c|c|r|r}
-    \multicolumn{3}{c|}{Case} & \multicolumn{1}{c}{$m_{i}$} & \multicolumn{1}{|c}{$w_{i}$} \\[0.5ex]\hline
-    \multirow{4}{*}{\raisebox{-4ex}{\rotatebox[origin=c]{90}{$0\leq \epsilon < \frac{3}{7}$}}} & \hspace{0.8ex}\multirow{2}{*}{\raisebox{-1ex}{\rotatebox[origin=c]{90}{$n$ even}}}\hspace{0.8ex} & LHS & $8^{2i}\binom{n}{2i}$ & $u^{2i}v^{n-2i}$ \\
-    & & RHS & $8^{n-2i}\binom{n}{2i}$ & $-u^{n-2i}v^{2i}$ \\ \cline{2-5}
-    & \multirow{2}{*}{\raisebox{-2ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $8^{2i+1}\binom{n}{2i+1}$ & $u^{2i+1}v^{n-2i-1}$ \\
-    & & RHS & $8^{n-2i-1}\binom{n}{2i+1}$ & $-u^{n-2i-1}v^{2i+1}$ \\ \hline
-    \multirow{4}{*}{\raisebox{-4ex}{\rotatebox[origin=c]{90}{$\frac{3}{7}\leq \epsilon < \frac{3}{4}$}}} & \multirow{2}{*}{\raisebox{-1ex}{\rotatebox[origin=c]{90}{$n$ even}}} & LHS & $8^{n-2i}\binom{n}{2i}$ & $u^{n-2i}v^{2i}$ \\
-    & & RHS & $8^{2i}\binom{n}{2i}$ & $-u^{2i}v^{n-2i}$ \\ \cline{2-5}
-    & \multirow{2}{*}{\raisebox{-2ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $8^{n-2i}\binom{n}{2i}$ & $u^{n-2i}v^{2i}$ \\
-    & & RHS & $8^{2i}\binom{n}{2i}$ & $-u^{2i}v^{n-2i}$ \\ \hline
-  \end{tabular}
-  \caption{Wigner components $w_{i}(n, \epsilon)$ of $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ along with their multiplicities $m_{i}(n, \epsilon)$, with $0 \leq i \leq n$.
-  The expressions change depending on the error $\epsilon$, the parity of the number of copies $n$ and whether the index $i$ is lower or higher than the index of the Lorenz curve maximum (LHS or RHS).
-  The term $2i$ is considered $\hspace{-6pt}\mod{\hspace{-2pt}(n+1)}$, so that $2i\ \hspace{-6pt}\mod{\hspace{-2pt}(n+1)} = 2i - n - 1$ if $i > \left\lfloor n/2 \right\rfloor$.}
-  \label{tab:lcsu}
-\end{table}
-
-For unital protocols, the rescaled distribution is simply proportional to the Strange state distribution,
-\begin{equation}
-	W_{\rho_{\rm{S}}(\epsilon)^{\otimes n}|\left(\id/3\right)^{\otimes n}} = 9^n W_{\rho_{\rm{S}}(\epsilon)^{\otimes n}},
-\end{equation}
-therefore expressions for the Lorenz curve coordinates follow from summing up the Wigner components in decreasing order.
-As a result, every Strange state Lorenz curve for a unital protocol contains $n$ elbows. In the case of accidental degeneracies among Wigner components, some of these elbows may be straightened out.
-Including the boundary points $(x_{-1}, L_{-1}) \coloneqq (0,0)$ and $(x_{n}, L_{n}) \coloneqq (1,1)$, we label these elbows as 
-\begin{equation*}
-\{(x_{i}, L_{i})\}_{i=-1,0,\dots,n},
-\end{equation*}
-where the coordinates are given by
-\begin{equation}
-	(x_{i}, L_{i}) = \left( \frac{1}{9^n}\sum_{\ell=0}^i m_{\ell}, \sum_{\ell=0}^i m_{\ell} w_{\ell} \right).
-\end{equation}
-The Lorenz curve maximum is the $\lfloor n/2 \rfloor$-th elbow and its coordinates are calculated by collecting all the positive Wigner components,
-\begin{align}
-	x_{\lfloor n/2 \rfloor} &= \frac{1}{2}\left(1 + \left(\frac{7}{9}\right)^n\right), \\
-	L_{\lfloor n/2 \rfloor} &= \frac{1}{2}\left (1 + \left(\frac{15 - 8\epsilon}{9}\right)^n \right).
-\end{align}
-%\sum_{j: even}^n a^j \binom{n}{j} = \frac{1}{2} [ (1+a)^n + (1-a)^n ]
-
-In Table~\ref{tab:lcsu_coord_elb_app}, we present the elbow coordinates of the $n$-copy, $\epsilon$--noisy Strange state Lorenz curve for a unital protocol for any combination of physical parameters $n, \epsilon$.
-\begin{table}[h]
-  \def\arraystretch{1.5}
-  \centering
-  \begin{tabular}{c|c|c|r|r}
-\hline 
-    \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$0\leq \epsilon < \frac{3}{7}$}}} & \hspace{0.8ex}\multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ even}}}\hspace{0.8ex} & LHS & $\Phi_+\left(2i;n,\frac{8}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\
-    & & RHS & $\Phi_-\left(2i;n,\frac{1}{9}\right)$ & $- \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-\left(2i;n,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
-    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $\Phi_-\left(2i;n,\frac{8}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_-\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\
-    & & RHS & $\Phi_-\left(2i;n,\frac{1}{9}\right)$ & $- \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-\left(2i;n,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
-    \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$\frac{3}{7}\leq \epsilon < \frac{3}{4}$}}} & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ even}}} & LHS & $\Phi_+\left(2i;n,\frac{1}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+\left(2i;n,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\
-    & & RHS & $\Phi_-\left(2i;n,\frac{8}{9}\right)$ & $- \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
-    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $\Phi_+\left(2i;n,\frac{1}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+\left(2i;n,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\
-    & & RHS & $\Phi_+\left(2i;n,\frac{8}{9}\right)$ & $- \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_+\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
-  \end{tabular}
-  \caption{Strange state Lorenz curve elbow coordinates for a unital protocol, with $0 \leq i \leq n$. 
-  For the LHS cases, the $i$ in the first column labels the elbow coordinate $x_i$ and the second column gives $L_i=L(x_i)$.
-For RHS cases, the $i$ in the first column labels $x_i - x_{\lfloor n/2 \rfloor}$ and the second column gives $L_i - L_{\lfloor n/2 \rfloor}$.
-  The coordinate expressions depend on the error $\epsilon$, the parity of the number of copies $n$ and the location of the elbow relative to the maximum (LHS or RHS).
-  The term $2i$ is considered $\hspace{-6pt}\mod{\hspace{-2pt}(n+1)}$, so that $2i\ \hspace{-6pt}\mod{\hspace{-2pt}(n+1)} = 2i - n - 1$ if $i > \left\lfloor n/2 \right\rfloor$.
-  The point $(x_{-1}, L_{-1}) \coloneqq (0,0)$ is not included in the table.
-  }
-  \label{tab:lcsu_coord_elb_app}
-\end{table}
-
-We can get explicit expressions for all $9^{n}$ points of the Lorenz curve $\lc{\rho_{\rm{S}}(\epsilon)^{\otimes n}}{(\id/3)^{\otimes n}}$, in terms of the elbow coordinates:
-\begin{align}
-    x_{ij} &= \left( 1-\frac{j}{m_{i}} \right) x_{i-1} + \frac{j}{m_{i}} x_{i}, \label{eq:x}\\
-    L_{ij} &= \left( 1-\frac{j}{m_{i}} \right) L_{i-1} + \frac{j}{m_{i}} L_{i} \label{eq:l}
-\end{align}
-for $j = 1,\dots,m_{i}$ and $i=0,\dots,n$, where multiplicities $m_i$ are given in Table~\ref{tab:lcsu}.
-
-One can consider the state 
-\begin{equation*}
-\rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n-n')},
-\end{equation*}
-where tensoring with the maximally mixed state keeps the Lorenz curve unchanged, but increases the resolution of (the uniformly distributed) points.
-The new point coordinates are given by:
-\begin{align}
-    &x_{ijk} = \left( 1-p_{ijk}\right) x_{i-1} + p_{ijk} x_{i} \label{eq:lcsu_xcoord}\\
-    &L_{ijk} = \left( 1-p_{ijk} \right) L_{i-1} + p_{ijk} L_{i}, \label{eq:lcsu_lcoord}\\
-    &\text{where } p_{ijk} = \frac{k + (j-1)9^{n-n'}}{9^{n-n'} m_{i}} \nonumber\\
-    &\text{for } i=0,\dots,n',\ j = 1,\dots,m_{i}(n', \epsilon'),\ k = 1,\dots,9^{n-n'}. \nonumber
-\end{align}
-We can also combine the indices, by introducing a single index
-\begin{equation}
-    I(i,j,k) \coloneqq k + \left[ (j-1) + \sum_{\ell=0}^{i-1} m_{\ell}(n', \epsilon') \right]9^{n-n'},
-\end{equation}
-so that $I=1,2,\dots, 9^{n}$.
-The elbow coordinates correspond to 
-\begin{equation}
-	I(i, m_{i}(n', \epsilon'), 9^{n-n'}) = \sum_{\ell=0}^{i} m_{\ell}(n', \epsilon'),\ i= 0,\dots,n'.
-\end{equation}
-The indexing $I$ is bijective, i.e.
-\begin{equation}
-	(i,j,k) = (i',j',k') \text{ iff } I(i,j,k) = I(i',j',k').
-\end{equation}
-
-\section{Temperature-dependent distillation bounds from relative majorization}
-\label{app:lcst_technical}
-
-Here we prove our main theorem, which bounds magic distillation rates in terms of free energies.
-
-\begingroup
-\def\thetheorem{\ref{thm:free-energy}}
-\begin{theorem}
-	Consider a magic distillation protocol on qutrits that transforms $n$ copies of an $\epsilon$--noisy Strange state into $m$ copies of an $\epsilon'$--noisy Strange state, with depolarising errors $\epsilon' \leq \epsilon \leq 3/7$.
-We also allow pre/post-processing by local Clifford unitaries.
-
-	Let $T =(k\beta)^{-1}$ be any finite temperature for the physical system and let $H= \sum_{k \in \mathbb{Z}_3} E_k |E_k\>\<E_k|$ be the Hamiltonian of each qutrit subsystem in its eigen-decomposition.
-Assume that in the thermodynamic limit ($n,m \gg 1$), the protocol applied to the equilibrium state $\tau^{\otimes n} = (e^{-\beta H}/\Z)^{\otimes n}$ maps $\tau^{\otimes n} \longrightarrow \tau^{\prime \otimes m}$, where we express state $\tau'$ as $\tau' = e^{-\beta H'}/\Z'$ for some Hermitian $H'$.
-
-Then the magic distillation rate $R = m/n$ for the protocol is bounded by the expression
-\begin{equation}
-	R \leq \dfrac{\log \big( 1-\frac{4}{3}\epsilon \big) + \beta (\phi - F)}{\log \big( 1-\frac{4}{3}\epsilon' \big) + \beta (\phi' - F')},
-\end{equation}
-where $F$ is the free energy of $\tau$,  and 
-\begin{equation}
-	\phi = -\beta^{-1} \log \zeta
-\end{equation}
-with $\zeta$ given by the expressions
-\begin{align}
-	\zeta &= \sum_{k\in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}, \nonumber\\
-	\alpha_k &= \<E_k| A_{\bmz_\star} |E_k\>,
-\end{align}
-and $W_\tau(\bmz)$ attains a minimum at $\z_\star$. The primed variables are defined similarly for the output system.
-\end{theorem}
-\addtocounter{theorem}{-1}
-\endgroup
-
-\begin{proof}
-	For the sake of clarity, we write $\rho_n \coloneqq \rho_S(\epsilon)^{\otimes n}$, $\rho'_m \coloneqq \rho_S(\epsilon')^{\otimes m}$, $\tau_n \coloneqq \tau^{\otimes m}$ and $\tau'_m \coloneqq \tau'^{\otimes m}$.
-We also assume, without loss of generality on the asymptotic distillation rate, that $n$ and $m$ are both even.
-
-To establish the distillation bound we consider the distillation protocol that gives $\E( \rho_n) = \rho'_m$ for the magic states. 
-We then consider that the protocol transforms the reference equilibrium state as $\E( \tau_n) = \tau'_m$.
-Since we have a finite temperature we have that $\tau$ and $\tau'$ are full rank stabilizer states and have a strictly positive Wigner distribution.
-The input and output magic states generally have quasi-probability Wigner distributions.
-For any such protocol we therefore have that
-\begin{equation}
-	( W_{\rho_n}(\bmz), W_{\tau_n}(\bmz) ) \succ ( W_{\rho'_m}(\bmz), W_{\tau'_m}(\bmz) ),
-\end{equation}
-or, equivalently, in terms of the relevant Lorenz curves,
-\begin{equation}
-	L_{\rho_n |\tau_n}(x) \ge L_{\rho'_m |\tau'_m}(x) \mbox{ for all } x \in [0,1].
-\end{equation}
-
-We now consider the rescaled Wigner distribution $W_{\rho | \tau}(\bmz) \coloneqq W_\rho(\bmz)/W_\tau(\bmz)$, which is well-defined since $\tau$ is full-rank. 
-Due to the multiplicative property of the Wigner distribution, the rescaled distribution is also multiplicative in the sense that
-\begin{equation}
-	W_{\rho \otimes \rho' | \tau \otimes \tau'} (\bmz_1 \oplus \bmz_2) = W_{\rho | \tau}(\bmz_1)W_{\rho' | \tau'}(\bmz_2),
-\end{equation}
-for any states $\rho, \rho'$ and any full-rank stabilizer states $\tau, \tau'$.
-Therefore, we have that
-\begin{align}
-	W_{\rho_n |\tau_n} (\bmz) &= \prod_{i=1}^n W_{\rho|\tau}(\bmz_i)\\
-	W_{\rho_n } (\bmz) &= \prod_{i=1}^n W_\rho(\bmz_i)
-\end{align}
-where $\bmz = \oplus_{i=1}^n \bmz_i \in \mathbb{Z}_3^{2n}$ is the phase space point for the full system in terms of those of the individual subsystems.
-
-The points defining the Lorenz curve $L_{\rho_n |\tau_n}(x)$ are obtained from sorting the components of $W_{\rho_n |\tau_n}(\bmz)$ in non-increasing order and then computing the partial sums of $W_{\rho_n |\tau_n}(\pi(\bmz))$ where $\pi$ is the permutation that realizes the sorting.
-However, similar to the unital protocol analysis, we use the slope constraint (Proposition~\ref{prop:first_elb}) obtained by considering the line segments connecting the origin to the first elbow of both Lorenz curves.
-
-The Wigner distribution of a single noisy Strange state consists of 1 negative component $W_{\rho}(\mathbf{0}) = -v(\epsilon)$ and 8 positive components $W_{\rho}(\bmz) = u(\epsilon)$ for $\bmz \neq \bmo$.
-The Wigner distribution of the full-rank, stabilizer equilibrium state $\tau$ is $W_{\tau}(\bmz) > 0$ for all $\bmz \in \mathbb{Z}_3^2$.
-
-Assume that the smallest component of the distribution $W_\tau(\bmz)$ is at $\bmz=\bmz_\star$.
-Since the magic content of the state is unchanged under a Clifford unitary $C$, we can instead consider the state
-\begin{equation}
-\rho_S(\epsilon) \rightarrow C \rho_S(\epsilon) C^\dagger = D_{\bmz_\star} \rho_S(\epsilon) D_{\bmz_\star}^\dagger,
-\end{equation}
-which has its single negative Wigner component $-v(\epsilon)$ at the point $\bmz_\star$.
-
-The components of the rescaled distribution $W_{\rho_n|\tau_n}$ for this transformed state are given by
-\begin{equation}
-	\left(\frac{-v}{W_{\tau}(\bmz_\star)}\right)^{i_{\bmz_\star}} \prod_{\bmz \neq \bmz_\star} \left(\frac{u}{W_{\tau}(\bmz)}\right)^{i_{\bmz}},
-\end{equation}
-where the integer indices obey the following conditions:
-\begin{align}
-&0 \leq i_{\bmz} \leq n \mbox{ for all } \bmz \in \mathbb{Z}_3^2, \nonumber \\
-&\sum_{\bmz \in \mathbb{Z}_3^2} i_{\bmz} = n.
-\end{align}
-We now compute the largest rescaled component.
-Firstly, note that $n$ is even, so we require that $i_{\bmz_\star} \in \{0,2,\dots,n\}$ for the component to be positive.
-Then, we have that $v \geq u$ because $\epsilon \leq 3/7$, and we have already ensured that $W_{\tau}(\bmz_\star) \leq W_{\tau}(\bmz)$ for all $\bmz \in \mathbb{Z}_3^2$.
-Therefore, the largest rescaled component occurs when $i_{\bmz_{\star}} = n$ and $i_{\bmz} = 0$ for $\bmz \neq \bmz_\star$ and is equal to $(v/W_{\tau}(\bmz_\star))^n$.
-The coordinates of the first Lorenz curve point after the origin are given by
-\begin{equation}
-	(x_0, L_0) = ((W_{\tau}(\bmz_\star))^n, v^n)
-\end{equation}
-
-Given a Hamiltonian decomposition,
-\begin{equation}
-	H = \sum_{k \in \mathbb{Z}_3} E_k |E_k\>\<E_k|,
-\end{equation}
-we now express the coordinates of the first point in terms of free energy quantities. We expand as follows
-\begin{align}
-	W_{\tau}(\bmz_\star) &= \frac{1}{3\Z}\tr\left[ A_{\bmz_\star}e^{-\beta H} \right] \nonumber\\
-	&= \frac{e^{\beta F}}{3} \tr\left[ A_{\bmz_\star}\sum_{k \in \mathbb{Z}_3} e^{-\beta E_k} |E_k\>\<E_k| \right] \nonumber\\
-	&= \frac{e^{\beta F}}{3} \sum_{r \in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}
-	= \frac{e^{\beta F}}{3} \zeta \nonumber\\
-	&= \frac{e^{\beta (F - \phi)}}{3},
-\end{align}
-where we define
-\begin{align}
-\alpha_k \coloneqq \<E_k |A_{\bmz_\star} |E_k\> \\
-\zeta \coloneqq  \sum_{k \in \mathbb{Z}_3} \alpha_k e^{-\beta E_k},
-\end{align}
-and a `magic free energy' term $\phi \coloneqq -\beta^{-1} \log \zeta$.
-Therefore, the coordinates can be expressed as
-\begin{equation}
-	(x_0, L_0) = \left( \frac{e^{n\beta (F - \phi)}}{3^n}, v(\epsilon)^n \right).
-\end{equation}
-The output states obey the same conditions, so we also have the first point coordinates of the output Lorenz curve given by
-\begin{equation}
-	(x'_0, L'_0) = \left( \frac{e^{m\beta (F' - \phi')}}{3^m}, v(\epsilon')^m \right).
-\end{equation}
-
-If the largest rescaled component of a state is distinct with no multiplicities, then these coordinates correspond to the first elbow of the corresponding Lorenz curve, whereas if it appears multiple times, then the coordinates derived correspond to a point on the interior of the line segment connecting the origin to the first elbow.
-In both cases, the distillation bound remains the same, as is clear by its derivation in Proposition~\ref{prop:first_elb}, given by $L_0/x_0 \geq L'_0/x'_0$, leading to
-\begin{equation}
-	\left( 3v(\epsilon)e^{-\beta (F - \phi)} \right)^{n} = \frac{L_0}{x_0}
-	\geq \frac{L'_0}{x'_0} = \left( 3v(\epsilon')e^{-\beta (F' - \phi')} \right)^{m}.
-\end{equation}
-We note that $3v(\epsilon')e^{-\beta (F' - \phi')} > 1$ always, as $\rho_{\rm{S}}(\epsilon')$ is not a free state, so the initial slope of its Lorenz curve exceeds $1$.
-Taking the natural logarithm on both sides and rearranging gives the bound
-\begin{equation}
-	\frac{m}{n} \leq \dfrac{\log \big( 1-\frac{4}{3}\epsilon \big) + \beta (\phi - F)}{\log \big( 1-\frac{4}{3}\epsilon' \big) + \beta (\phi' - F')},
-\end{equation}
-which completes the proof.
-\end{proof}
-
-The following result shows that if the energy eigenbasis is a stabilizer basis then the above bounds simplify further.
-\begin{proposition} \label{sharp-phi}
-	Let $H$ be a Hamiltonian $H$ with spectrum $\{E_k\}_{k \in \mathbb{Z}_d}$.
-	If $H$ has a stabilizer eigenbasis, then $\phi = E_{k_{\star}}$ for some $k_{\star} \in \mathbb{Z}_d$.
-\end{proposition}
-\begin{proof}
-	We first write $\alpha_k$ as
-\begin{equation}
-	\alpha_k = \<E_k | A_{\bmz_{\star}} |E_k\> = d W_{|E_k\>\<E_k|}(\bmz_{\star})
-\end{equation}
-Since each $|E_k\>\<E_k|$ is a stabilizer state, their Wigner distributions have orthogonal supports in the phase space, so only one of them, say $k = k_{\star}$ contains point $\bmz_{\star}$ in its support.
-Additionally, its distribution is uniform on its support, so $W_{|E_{k_\star}\>\<E_{k_\star}|}(\bmz_{\star}) = 1/d$.
-
-Therefore, only the coefficient $\alpha_{k_{\star}}$ is non-zero and
-\begin{align}
-\phi &= -\beta^{-1}\log (\sum_k \alpha_k e^{-\beta E_k}) \nonumber \\
-&=E_{k_{\star}} \hspace{-2pt}-\hspace{1pt} kT \log (d W_{|E_{k_\star}\>\<E_{k_\star}|}(\bmz_{\star})) =E_{k_{\star}}.
-\end{align}
-
-\end{proof}
-
-\subsection{Dropping pre/post-processing of the magic states}
-\label{app:cliff_processing}
-
-If we drop the freedom to pre/post-process the magic states via Clifford unitaries, then the final expression for the bounds change and become a little more complex, since the largest component in the rescaled distribution depends on a number of factors.
-We illustrate this by the following result.
-
-\begin{theorem}\label{thm:no-processing}
-	Consider a magic distillation protocol on qutrits that transforms
-\begin{equation*}
-	\rho_S(\epsilon)^{\otimes n} \longrightarrow \E(\rho_S(\epsilon)^{\otimes n})=\rho_S(\epsilon')^{\otimes m} 
-\end{equation*}
-with $n, m \gg 1$.
-
-Let each qutrit have a Hamiltonian $H$ with energies $E_0, E_1, E_2$ and stabilizer eigenstates, and define $E_{\rm max} = \max\{E_0, E_1, E_2\}$ and $E_s$ as the eigenvalue of the Hamiltonian eigenstate whose Wigner distribution overlaps the negative component of $\rho_S(\epsilon)$ in the phase space.
-Let $T =(k\beta)^{-1}$ be any finite temperature and assume that in the thermodynamic limit ($n,m \gg 1$), the protocol applied to the equilibrium state $\tau^{\otimes n} = (e^{-\beta H}/\Z)^{\otimes n}$ maps $\tau^{\otimes n} \longrightarrow \tau^{\prime \otimes m}$, where we express state $\tau'$ as $\tau' = e^{-\beta H'}/\Z'$ for some Hermitian $H'$.
-
-Define $\beta_\star = (k T_\star)^{-1}$ through the relation
-\begin{equation}
-	E_{\rm max} - E_s \eqqcolon kT_\star \ln 2,
-\end{equation}
-and define a threshold error,
-\begin{equation}\label{eq:threshold}
-	\epsilon_{\star}(\beta) \coloneqq 
-	\begin{cases}
-		3 - \dfrac{9}{4-2^{\beta/\beta_\star - 1}}, &\text{ for } \beta \leq \beta_\star \\
-		0, &\text{ for } \beta > \beta_\star.
-	\end{cases}
-\end{equation}
-Then, the distillation rate $R = m/n$ of the magic protocol is bounded as:
-\begin{equation}
-	R \leq
-	\begin{cases}
-		\dfrac{\ln \big( 1-\frac{4}{3}\epsilon \big) + \beta (E_s - F)}{\ln \big( 1-\frac{4}{3}\epsilon' \big) + \beta (E'_s - F')},\ &\epsilon \leq \epsilon_\star, \epsilon' \leq \epsilon'_\star, \vspace{10pt}\\
-		\dfrac{\ln \big( 1-\frac{4}{3}\epsilon \big) + \beta (E_s - F)}{\ln \big( \frac{1}{2}-\frac{1}{6}\epsilon' \big) + \beta (E'_{\rm{max}} - F')},\ &\epsilon \leq \epsilon_\star, \epsilon' > \epsilon'_\star, \vspace{10pt}\\
-		\dfrac{\ln \big( \frac{1}{2}-\frac{1}{6}\epsilon \big) + \beta (E_{\rm{max}} - F)}{\ln \big( 1-\frac{4}{3}\epsilon' \big) + \beta (E'_s - F')},\ &\epsilon > \epsilon_\star, \epsilon' \leq \epsilon'_\star, \vspace{10pt}\\
-		\dfrac{\ln\big( \frac{1}{2}-\frac{1}{6}\epsilon \big) + \beta (E_{\rm{max}} - F)}{\ln \big( \frac{1}{2}-\frac{1}{6}\epsilon' \big) + \beta (E'_{\rm{max}} - F')},\ &\epsilon > \epsilon_\star, \epsilon' > \epsilon'_\star,
-	\end{cases}
-\end{equation}
-where $F$ is the free energy of state $\tau$ and all primed quantities are similarly defined for the ouptut system.
-\end{theorem}
-\begin{proof}
-The proof proceeds in the same manner as in Theorem~\ref{thm:free-energy} up to the point where we need to evaluate $W_{\rho_n |\tau_n} (\bmz)$ and $W_{\rho_n}(\bmz)$ explicitly, beyond which we do not have the freedom of additional Clifford processing.
-
-The equilibrium state at inverse temperature $\beta$ on a single qutrit is given by $\tau = e^{-\beta H} / \Z$.
-Moreover, we have that $\tau$ is a full-rank stabilizer state, where $\beta \geq 0$ and $H = E_0 |\varphi_0\>\<\varphi_0| + E_1 |\varphi_1\>\<\varphi_1| + E_2 |\varphi_2\>\<\varphi_2|$ is an eigendecomposition of $H$.
-The state $\tau$ can now be written as 
-\begin{equation}
-	\tau = \frac{e^{-\beta E_0}}{\Z} |\varphi_0\>\<\varphi_0| + \frac{e^{-\beta E_1}}{\Z} |\varphi_1\>\<\varphi_1| + \frac{e^{-\beta E_2}}{\Z} |\varphi_2\>\<\varphi_2|,
-\end{equation}
-where the eigenstates $\{\ket{\varphi_k}\<\varphi_k|\}$ are pure, orthonormal stabilizer states, which can be represented in terms of generalized Paulis.
-We are free to redefine the computational basis so it coincides with the basis of $H$.
-Abstractly, let $C$ be the unitary transforming each $|\varphi_k\>\<\varphi_k|$ to $|k\>\<k|$.
-Since the Clifford group is the normalizer of the Heisenberg-Weyl group, $C$ is a Clifford unitary.
-Therefore, $C$ maps $\tau$ to another stabilizer state that is diagonal in the computational basis, and we can assume without loss of generality that $\tau$ is diagonal in $\{|0\>,|1\>, |2\>\}$.
-This re-definition of the computational basis means that the coordinates on the discrete phase space are also permuted, so the negative Wigner component $-v(\epsilon)$ of the Strange state is in a new position.
-We denote by $E_s$ the eigenvalue of $H$ where the associated eigenvector has Wigner distribution overlapping the negative component of the state $C\rho_S(\epsilon)C^\dagger$ in the original phase space, hence also of the state Strange state $\rho_S(\epsilon)$ in the re-defined phase space.
-The eigenvalue $E_s$ is unique, since the eigenstates form an orthonormal basis.
-
-The Wigner distribution of state $\tau$ is then given by
-\begin{align}
-	\W[\bmz]{\tau} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z}W_{|k\>\<k|}(q, p) \nonumber\\
-	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z} \delta_{q, k} = \frac{e^{-\beta E_q}}{3\Z},
-\end{align}
-where $x$ labels one of the three vertical lines in the phase space.
-The rescaled Wigner distribution $W_{\rho|\tau}(\bmz)$ can now be computed.
-It has $9$ components, but these come with multiplicities.
-In total, there are four distinct values on the phase space, as illustrated in Fig.~\ref{fig:pd_split}.
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.35]{figs/pd_split_thermal.pdf}
-    \caption{\textbf{Qutrit phase space regions for $W_{\rho | \tau}(\bmz)$.}
-    Here, the negative component of the magic state overlaps the Wigner distribution of $|0\>$.
-The rescaled distribution attains a single value in each of the four regions, proportional to the value depicted in the region, see Eq.~(\ref{eq:bmw_rescaled}).
-    }
-    \label{fig:pd_split}
-\end{figure}
-
-We define vectors $\w(\rho), \w(\tau), \w(\rho|\tau)$ based on the values occurring in $W_\rho, W_\tau, W_{\rho|\tau}$ respectively and $\bmm$ as the vector of associated multiplicities of each value in $W_\rho(\bmz)$.
-Specifically, the component values and multiplicities of the relevant distributions in the four distinct regions are given by
-\begin{align}
-		\bmm &\coloneqq (1,2,3,3), \\
-	\w(\rho) &\coloneqq (-v, u, u, u), \\
-	\w(\tau) &\coloneqq \frac{1}{3\Z} \left( e^{-\beta E_0}, e^{-\beta E_0}, e^{-\beta E_1}, e^{-\beta E_2} \right), \\
-	\w(\rho | \tau) &\coloneqq 3\Z \left( -v e^{\beta E_0}, u e^{\beta E_0}, u e^{\beta E_1}, u e^{\beta E_2} \right). \label{eq:bmw_rescaled}
-\end{align}
-
-Using this notation, the values and multiplicities of the $n$--copy distribution $\bmw(\rho_n |\tau_n)$ are computed in Proposition~\ref{ncopycomponents}. The values are given by 
-\begin{align}\label{eq:ncopy_w_rescaled}
-	[\w(\rho_n | \tau_n)]_{ijk} &= (3\Z)^{n} (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )},
-\end{align}
-where the indices $i,j,k$ are non-negative integers that obey the constraint $\alpha \coloneqq i+j+k \leq n$.
-The multiplicity of this above value is $m_{ijk}$ with
-\begin{equation}
-	m_{ijk} = \frac{n!}{i!j!k!(n-\alpha)!} 2^i 3^j 3^k.
-\end{equation}
-The associated components of $\w(\rho_n)$ are given by
-\begin{align}
-	[\w(\rho_n)]_{ijk} &= (-v)^{n-\alpha} u^{\alpha}, \label{eq:ncopy_wrho}\\
-	[\w(\tau)]_{ijk} &= (3\Z)^{-n} e^{-\beta (n-\alpha)E_s} e^{-\beta ( i E_0 + j E_1 + k E_2 )}. \label{eq:ncopy_wsigma}
-\end{align}
-
-In order to construct the $n$--copy Lorenz curve $L_{\rho_n|\tau_n}(x)$ we need to order the components of the distribution, $w(\rho | \tau)_{ijk}$ in decreasing order, and identify the sequence of indices that give us $W_{\rho_n}(\pi(\bmz))$.
-
-However, in order to obtain a non-trivial bound, it again suffices to use the constraint from the first elbow $(x_0, L_0)$ of $L_{\rho_n|\tau_n}(\bmz)$. We therefore compute the largest component 
-\begin{equation}
-	w_{\rm max} \coloneqq \max_{i,j,k} [\w(\rho_n | \tau_n)]_{ijk},
-\end{equation}
-and determine the indices at which this occurs.
-Putting in the values we obtain
-\begin{align}
-	&(3\Z)^{-n}w_{\rm max} = \nonumber\\
-	&\max\limits_{i,j,k}\Big\{ (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \label{eq:max_slope}
-\end{align}
-where $0 \leq i,j,k \leq n$ and $\alpha \coloneqq i+j+k \leq n$.
-Now for $0 \leq \epsilon \leq 3/7$, we have $v \geq u$. Since we assume that $n$ is even, we need the sum $\alpha = i+j+k$ to be even too, so that the expression is positive.
-
-Given an even value for $\alpha$, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_s}$ is fixed, so the expression is maximized by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
-Hence, we have
-\begin{align}
-	&w_{\rm max} = \nonumber\\
-	&(3\Z)^{n} v^n e^{n\beta E_s}\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_s)} \right)^{\alpha} \Big\}}.
-\end{align}
-If the expression $\frac{u(\epsilon)}{v(\epsilon)} e^{\beta (E_{\rm{max}} - E_s)}$ is less than $1$ then the maximum occurs at $\alpha=0$, otherwise it occurs at $\alpha = n$.
-For a fixed state $\tau$, this transition is determined by the value of the depolarising error parameter $\epsilon$ of the noisy magic state.
-The transition occurs at $\epsilon = \epsilon_\star$ where
-\begin{equation}\label{eq:noise_transition}
-	\frac{u(\epsilon_\star)}{v(\epsilon_\star)} e^{\beta (E_{\rm{max}} - E_s)} = \frac{3-\epsilon_\star}{6-8\epsilon_\star} e^{\beta (E_{\rm{max}} - E_s)} = 1.
-\end{equation}
-If $E_{\rm{max}} = E_s$, namely if the state negativity lies in the same phase space region as the highest energy, this threshold is constant in temperature and given by $\epsilon_{\star} = 3/7$.
-However, the condition that $\epsilon_\star \ge 0$ also implies a constraint on the effective temperature of the stabilizer state.
-Specifically, there is a threshold temperature value $\beta_\star$ given by
-\begin{equation}
-	\beta_{\star} \coloneqq \frac{1}{E_{\rm{max}} - E_s} \ln2,
-\end{equation}
-such that for the regime $0 \leq \beta \leq \beta_\star$ a threshold error $\epsilon_\star$ exists, and for $\beta > \beta_\star$ no such transition exists, so we choose $\epsilon_\star = 0$. 
-Therefore, the transition value for the error is given by
-\begin{equation}
-	\epsilon_{\star}(\beta) \coloneqq 
-	\begin{cases}
-		3 - \dfrac{9}{4-2^{\beta/\beta_\star - 1}}, &\text{ for } \beta \leq \beta_\star \\
-		0, &\text{ for } \beta > \beta_\star.
-	\end{cases}
-\end{equation}
-The quantity $w(\rho_{\rm{S}} | \sigma)_{\rm{max}}$ is now given by
-\begin{equation*}
-w_{\rm max} =
-	\begin{cases}
-		(3\Z)^{n} v^n e^{n\beta E_s}, &\mbox{if }\epsilon \leq \epsilon_{\star},\ \hspace{3pt}\rm{(C1)}\\
-		(3\Z)^{n} u^n e^{n\beta E_{\rm{max}}}, &\mbox{if }\epsilon > \epsilon_{\star}.\ \hspace{5pt}\rm{(C2)} 
-	\end{cases}
-\end{equation*}
-Case $\rm{(C1)}$ corresponds to $(i,j,k) = (0,0,0)$, so the multiplicity is $m_{000} = 1$, while
-Case $\rm{(C2)}$ corresponds to
-\begin{equation}
-	(i,j,k) = 
-	\begin{cases}
-	(0,n,0), &\text{if } E_{\rm{max}} = E_1, \\
-	(0,0,n), &\text{if } E_{\rm{max}} = E_2,
-	\end{cases}
-\end{equation}
-so the multiplicity in both cases is $3^n$.
-
-Using that $F = -\beta^{-1} \log \Z$, the first elbow coordinates in the two cases are now given by
-\begin{equation}\label{eq:first_elb_coords}
-	(x_0, L_0) =
-	\begin{cases}
-		\left(\frac{1}{3^n} e^{-n\beta (E_s - F)}, v^n \right), &\epsilon \leq \epsilon_\star \vspace{10pt}\\
-		\left( e^{-n\beta (E_{\rm{max}}-F)}, (3u)^n \right). &\epsilon > \epsilon_\star
-	\end{cases}
-\end{equation}
-
-Similarly, considering the output magic state with respect to state $\sigma'$, the image of equilibrium state $\sigma$ under the magic protocol, we get output Lorenz curve coordinates,
-\begin{equation}\label{eq:transformed_first_elb_coords}
-	(x'_0, L'_0) =
-	\begin{cases}
-		\left(\frac{1}{3^{n'}} e^{-n\beta (E'_s - F')}, v(\epsilon')^{n'} \right), &\epsilon' \leq \epsilon'_\star \vspace{10pt}\\
-		\left( e^{-n'\beta (E'_{\rm{max}}\hspace{-2.5pt}-F')}, (3u(\epsilon'))^{n'} \right), &\epsilon' > \epsilon'_\star
-	\end{cases}
-\end{equation}
-There are four combinations of coordinates, depending on the error parameters $\epsilon, \epsilon'$ for the input and output states.
-In each of these combinations, we simply use the first elbow constraint, as described in Proposition~\ref{prop:first_elb}, and manipulate the coordinates as in the proof of Theorem~\ref{thm:free-energy}, leading to the bounds in the statement of this theorem.
-\end{proof}
-
-\section{Single-shot entropies on quasi-distributions and magic distillation bounds}\label{app:single-shot}
-
-In this section, we analyse R\'{e}nyi entropies on quasi-distributions and use them to get magic distillation bounds.
-
-\subsection{R\'{e}nyi min-divergence from Lorenz curves}
-We first demonstrate that the initial slope analysis on the Wigner quasi-distributions makes use of the min-relative divergence. We define 
-\begin{equation}
-	D_\infty(W_\rho || W_\tau) \coloneqq \log  \max_{\bmz} \frac{W_\rho(\bmz)}{W_\tau(\bmz)},
-\end{equation}
-which is well-defined since both the nominator and denominator in the above expression are strictly positive when $\tau$ is in the interior of $\F$.
-
-\begingroup
-\def\thetheorem{\ref{thm:Dinfty}}
-\begin{theorem}
-	Let $\tau$ be in the interior of $\F$, then $D_\infty(W_\rho || W_\tau)$ is well-defined for all $\rho$, and the following hold:
-\begin{enumerate}
-\item $D_\infty(W_\rho || W_\tau) \geq 0$ for all quantum states $\rho$.
-\item  $D_\infty(W_\rho || W_\tau) = 0$ if and only if $\rho =\tau$.
-\item $D_\infty(W_{\rho^{\otimes 2n}} || W_{\tau^{\otimes 2n}}) = n D_\infty(W_{\rho^{\otimes 2}} || W_{\tau^{\otimes 2}})$ for any $n \in \mathbb{N}$.
-\item For any quantum state $\rho$, and any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$, we have $D_\infty (W_\rho || W_\tau) \geq D_\infty (W_{\E(\rho)} || W_{\E(\tau)})$.
-\end{enumerate}
-\end{theorem}
-\addtocounter{theorem}{-1}
-\endgroup
-\begin{proof}
-	Since $\tau$ is in the interior of $\F$, its Wigner function obeys $W_\tau(\bmz) >0$ for all points $\bmz$ in the phase space. 
-In general, $W_\rho(\bmz)$ is a quasi-distribution, but the given form of $\alpha$ ensures that $W_{\rho}(\bmz)^\alpha \geq 0$. 
-Therefore $D_\infty (W_\rho || W_\tau)$ is always well-defined.
-
-1. We have that 
-\begin{equation}
-	D_\infty(W_\rho || W_\tau) =\log  \max_{\bmz} \frac{W_\rho(\z)}{W_\tau(\z)},
-\end{equation}
-so $2^{D_\infty(W_\rho || W_\tau)}$ equals the slope of the Lorenz curve $L_{\rho|\tau}(x)$ at $x=0$.
-Since $L_{\rho|\tau}(x)$ is a concave function passing through $(0,0)$ and $(1,1)$ this implies that $L_{\rho |\tau}(x) \ge x$ for all $x \in [0,1]$, and in particular its slope at $x=0$ is always greater than or equal to $1$, which implies $D_\infty(W_\rho || W_\tau) \geq 0$ for all $\rho$.
-
-2.
-$D_\infty(W_\rho || W_\tau) = 0$ implies that $\max_{\bmz} \frac{W_\rho(\bmz)}{W_\tau(\bmz)}=1$ and the initial slope of $L_{\rho|\tau}(x)$ is $1$.
-From the concavity of the function and the fact that $L_{\rho|\tau}(1)=1$, this implies that the slope of $L_{\rho|\tau}(x)$ must equal $1$ throughout the interval $[0,1]$ and this, together with the definition of the Lorenz curve, implies that $W_\rho(\bmz)/W_\tau(\bmz) = 1$ for all $\bmz$.
-Since the Wigner representation $\rho \mapsto W_\rho(\bmz)$ is bijective this implies that $\rho = \tau$ only.
-The converse holds by inspection.
-
-3. Given a vector $\w \in \mathbb{R}^N$, it is generally the case that $\max_k w_k \ne \max_k |w_k|$. 
-However, we do have that
-\begin{equation}
-	\max_{k_1,k_2} (w_{k_1} w_{k_2}) = \max_{k_1,k_2} |w_{k_1} w_{k_2}|,
-\end{equation}
-and if additionally $w_k \geq 0$ for all $k$, then we also have for $2n$ copies that
-\begin{equation}
-	\max_{k_1, k_2, \dots, k_{2n}} \left( w_{k_1}w_{k_2}\cdots w_{k_{2n}} \right) = (\max_k |w_k|)^{2n},
-\end{equation}
-and also,
-\begin{align}
-	&\max_{k_1, k_2, \dots, k_{2n}}\left( w_{k_1}w_{k_2}\cdots w_{k_{2n}} \right) = \nonumber\\
-	&\max_{k_1, k_2, \dots, k_{2n}}\left( |w_{k_1}w_{k_2}|\cdots |w_{k_{2n-1}}w_{k_{2n}}| \right) = \nonumber \\
-	&\left( \max_{k_1 ,k_2}\left( w_{k_1} w_{k_2} \right) \right)^n.
-\end{align}
-
-If we now let $\w = W_{\rho|\tau}(\bmz) \coloneqq W_{\rho}(\bmz) /W_{\tau}(\bmz)$ we have
-\begin{equation}
-\max_{\bmz_1, \bmz_2, \dots ,\bmz_{2n}} \prod_{k=1}^{2n} W_{\rho|\tau}(\bmz_k) = \left( \max_{\bmz_1, \bmz_2} W_{\rho|\tau}(\bmz_1)W_{\rho|\tau}(\bmz_2) \right)^n
-\end{equation}
-and therefore taking logarithms we have that $D_\infty(W_{\rho^{\otimes 2n}} || W_{\tau^{\otimes 2n}}) = n D_\infty(W_{\rho^{\otimes 2}} || W_{\tau^{\otimes 2}})$ as required.
-
-4.
-The free operation $\E$ in the Wigner representation corresponds to a stochastic map, which sends $W_\tau(\bmz)$ to $W_{\E(\tau)}(\bmz)$, which is another strictly positive probability distribution on the phase space, due to $\E(\tau)$ being in the interior of $\F$.
-Moreover, $(W_\rho, W_\tau ) \succ (W_{\E(\rho)} , W_{\E(\tau)})$.
-As shown in the main text this condition holds if and only if $L_{\rho|\tau}(x) \ge L_{\E(\rho)|\E(\tau)}(x)$ for all $x$.
-In particular, this implies the slope at the origin of the input curve is never less than the slope at the origin of the output curve, and hence the result follows.
-\end{proof}
-
-\subsection{Well-defined R\'{e}nyi entropies on quasi-distributions}
-
-We now make use of known results from majorization theory to establish the Schur-concavity of the R\'{e}nyi entropy $H_\alpha$ on Wigner quasi-distributions for a subset of $\alpha$ values.
-We consider the set of all quasi-distributions that is a hyper-plane in $\mathbb{R}^N$ given by
-\begin{equation}
-	\mathcal{Q}_N = \left\{ \w \in \mathbb{R}^N: \sum_{i=1}^N w_i = 1 \right\}.
-\end{equation}
-
-We define the notion of \emph{Schur-convex and Schur-convave functions} on a subset $\D \subseteq \mathbb{R}^N$.
-\begin{definition} 
-	A continuous, real-valued function $f$ defined on $\mathcal{D} \subseteq \mathbb{R}^N$ is called Schur-convex on the domain $\mathcal{D}$ if $\p \prec \q$ on $\mathcal{D}$ implies that $f(\p) \le f(\q)$.
-A continuous function $f:\mathcal{D} \rightarrow \mathbb{R}$ is called Schur-concave if $(-f)$ is Schur-convex.
-\end{definition}
-For any subset $\D \subseteq \mathbb{R}^N$ we define
-\begin{equation}
-	\mathcal{D}^\downarrow \coloneqq \{ \w \in \mathcal{D} : w_1 \ge w_2 \ge \cdots \ge w_N\}.
-\end{equation}
-
-We now have the following fundamental result in majorization theory.
-\begin{theorem}[Schur-Ostrowski theorem~\cite{Schur_1923, Ostrowski_1952, cit:marshall}] 
-	Let $\D\subseteq \mathbb{R}^N$ be a convex set with non-empty interior, and invariant under permutations of vector components.
-Let $f: \D \rightarrow \mathbb{R}$ be a continuously differentiable function on the interior of $\D$ and continuous on the whole of $\D$.
-Then $f$ is Schur-convex on $\D$ if and only if $f$ is a symmetric function on $\D$ and
-\begin{equation}
-	\partial_1 f(\w) \ge \partial_2 f(\w) \ge \cdots \ge \partial_N f(\w),
-\end{equation}
-for all $\w$ in the interior of $\mathcal{D}^\downarrow$.
-\end{theorem}
-Since the set $\mathcal{Q}_N$ of quasi-distributions obey the necessary conditions, we get the following result:
-\begin{theorem}
-	Let $f$ be a real-valued continuous function defined on $\mathcal{Q}_N$ that is continuously differentiable on the interior of $\mathcal{Q}_N$. 
-Then, $f$ is Schur-convex on $\mathcal{Q}_N$ if and only if it is a symmetric function and
-\begin{equation}
-	\partial_1 f(\w) \ge \partial_2 f(\w) \ge \cdots \ge \partial_N f(\w),
-\end{equation}
-for all quasi-distributions $\w$ in the interior of $\mathcal{Q}^\downarrow_N$.
-\end{theorem}
-
-The classical $\alpha$-R\'{e}nyi entropy on a probability distribution $\p = (p_i)$ is given by
-\begin{equation}
-	H_\alpha(\p) \coloneqq \frac{1}{1-\alpha} \log \sum_i p_i^\alpha,
-\end{equation}
-where $\alpha \ge 0$.
-This means the function is well-defined on $\mathcal{Q}_N^+$, namely the set of quasi-distributions with non-negative components.
-We wish to extend the domain to the whole of $\mathcal{Q}_N$, but this requires that $w_i^\alpha$ be a real number for any $w_i \in \mathbb{R}$.
-
-The exponent function $x \mapsto x^\alpha$ is well-defined and real-valued if $\alpha$ is a rational number of the form $\alpha = r / s$ where $s$ is an odd integer and $r \in \mathbb{N}$.
-However, we also require that $\sum_i w_i^\alpha > 0$ in order for the logarithm to return a real value.
-To ensure this, we restrict to $\alpha = r/s$ with $r=2a$ being an even integer and $s=2b-1$ being an odd integer, for some integers $a,b\in  \mathbb{N}$, which implies that the following are all well-defined, real-valued expressions,
-\begin{equation*}
-	0 \le w_i^\alpha = w_i^{\frac{2a}{2b-1}} = \left (w_i^{\frac{1}{2b-1}}\right )^{2a} =\left (w_i^{2a}\right )^{\frac{1}{2b-1}} = |w_i|^{\frac{2a}{2b-1}}.
-\end{equation*}
-We note that previous work~\cite{Manfredi_2000} has considered the $\alpha=2$ entropy of Wigner distributions, and other work exists that uses the Wehrl entropy, based on the Hussimi function of a quantum state~\cite{Gnutzmann_2001}.
-
-We next show that $H_\alpha (\w)$ for $\alpha = 2a/(2b-1)$ is a Schur-concave function on $\mathcal{Q}_N$ provided that $a \ge b$.
-
-\begingroup
-\def\thetheorem{\ref{thm:HSchur}}
-\begin{theorem}
-	If $\alpha = \frac{2a}{2b-1}$ for positive integers $a,b$ with $a \geq b$, then $H_\alpha(\w)$ is well-defined on the set of quasi-distributions $\mathcal{Q}_N$, and moreover if $\w \succ \w'$ for two quasi-distributions $\w, \w'\in \mathcal{Q}_N$ then $H_\alpha (\w) \leq H_\alpha(\w')$.
-\end{theorem}
-\addtocounter{theorem}{-1}
-\endgroup
-\begin{proof}
-We have $\alpha = \frac{2a}{2b-1} \geq \frac{2b}{2b-1} > 1$ and $\alpha$ is a rational with even numerator and odd denominator, so $\sum_i w_i^\alpha > 0$ and $H_\alpha(\w)$ is well-defined for all quasi-distributions $\w$.
-
-We also have that $H_\alpha(\w)$ is well-defined, continuous, differentiable on the interior of $\mathcal{Q}_N$ and symmetric in the components of $\w$.
-
-Consider the partial derivatives
-\begin{equation}
-	\frac{\partial H_\alpha}{\partial w_i} = \frac{\alpha}{(\alpha-1)\sum_k{w_k^\alpha}}\left( -w_i^{\alpha-1} \right).
-\end{equation}
-For $\alpha= \frac{2a}{2b-1}$,  with $a\ge b$, we have that
-\begin{equation}
-	\frac{\alpha}{(\alpha-1)\sum_k{w_k^\alpha}} > 0.
-\end{equation}
-The first derivative of the function $g(w) \coloneqq -w^{\alpha - 1}$ is given by
-\begin{equation}
-	g'(w) = -(\alpha - 1) w^{\alpha-2} = -(\alpha - 1)w^{\frac{2a-4b+2}{2b-1}} \leq 0,
-\end{equation}
-because $\alpha > 1$ and
-\begin{equation}
-	w^{\frac{2a-4b+2}{2b-1}} = \left(w^{\frac{a-2b+1}{2b-1}}\right)^{2} \geq 0,
-\end{equation}
-so $g(w)$ is non-increasing in $w$.
-
-Therefore, whenever $w_i \geq w_j$, we have that 
-\begin{equation}
-	-w_i^{\alpha-1} \leq -w_j^{\alpha-1},
-\end{equation}
-which implies that
-\begin{equation}
-	\frac{\partial H_\alpha}{\partial w_i}(\w) \leq \frac{\partial H_\alpha}{\partial w_j}(\w),
-\end{equation}
-for any $\w$ in the interior of $\mathcal{Q}_N^\downarrow$.
-Therefore, $H_\alpha$ is Schur-concave on $\mathcal{Q}_N$ and
-\begin{equation}
-	H_\alpha(\w) \leq H_\alpha(\w'),
-\end{equation}
-for any quasi-distributions $\w, \w'$ that obey $\w \succ \w'$.
-\end{proof}
-While we have integers $a,b$ such that $0 < \alpha=\frac{2a}{2b-1} < 1$ and $H_\alpha(\w)$ is well-defined, it turns out that monotonicity does not hold if we drop the condition $a \ge b$.
-If $\alpha =2a/(2b-1)$ with $\alpha < 1$, then $g(w) \coloneqq \frac{-w^{\alpha-1}}{\alpha-1}$ is no longer monotonic for all $w \in \mathbb{R}$, and the problem occurs when comparing $w_i < 0$ and $w_j >0$.
-As an example of this dependence of monotonicity on the domain of the function, consider the function $g(x) = \frac{1}{x^3}$ which is monotone decreasing on both $x<0$ and $x>0$ separately, however it is not monotone on the full real-line.
-
-We note that if $\alpha =r/s$ with both $r$ and $s$ odd, then $H_\alpha$ is not well-defined for all quasi-distributions, although if the actual set of quasi-distributions has a sufficiently bounded levels negativity, then $\log \sum_{\bmz} W_\rho(\bmz)^\alpha$ can still be obtained for $r$ odd, provided the total sum is never negative.
-This occurs for Wigner distributions, where we have $|W_\rho(\z)| \leq 1/d$ for a $d$--dimensional quantum system.
-
-We also note that the set $F \coloneqq \{2a/(2b-1): a,b \in \mathbb{N} \text{ and } a \geq b\}$ is dense in the reals $\mathbb{R}_{>1}$, as any rational $c/d$ with $c>d$ can be approximated by  $c2^n / (d2^n-1) \in F$ for sufficiently large $n$.
-
-We have that $H_{\alpha}$ is additive on products of quasi-distributions, which we state for completeness.
-\begin{proposition}\label{H_add}
-	For any $\w \in \mathcal{Q}_N$ and $\w' \in \mathcal{Q}_{N'}$, we have
-	\begin{equation}
-		H_{\alpha}(\w\otimes \w') = H_{\alpha}(\w) + H_{\alpha}(\w'),
-	\end{equation}
-	where $\alpha = 2a/(2b-1)$ with positive integers $a\ge b$.
-\end{proposition}
-\begin{proof}
-	\begin{align}
-		H_{\alpha}(\w \otimes \w') &= \frac{1}{1-\alpha}\log \sum_{i,j'} \left[\w_i \w'_j\right]^{\alpha} \nonumber\\
-		&= \frac{1}{1-\alpha}\log  \left [ \sum_i\w_i^\alpha \sum_j\w_j^{\prime \alpha} \right ] \nonumber\\
-				&= \frac{1}{1-\alpha}\log  \left [ \sum_i\w_i^\alpha\right ] + \frac{1}{1-\alpha}\log \left [ \sum_j\w_j^{\prime \alpha} \right ] \nonumber\\
-		&= H_{\alpha}(\w) + H_{\alpha}(\w').
-	\end{align}
-\end{proof}
-
-Applied to Wigner distributions $W_\rho (\z)$ for a quantum state $\rho$ we have
-\begin{equation}
-	H_\alpha(W_\rho) \coloneqq \frac{1}{1-\alpha} \log \sum_{\bmz} W_{\rho}(\bmz)^\alpha,
-\end{equation}
-where $\alpha$ can take values of the form $2a / (2b-1)$, for non-negative integers $a,b$. For the noisy Strange state $\rho = \rho_{\rm{S}}(\epsilon)$, this becomes
-\begin{align}
-	H_{\alpha}\left(W_{\rho_{\rm{S}}(\epsilon)}\right) = \frac{1}{1-\alpha}\log \left[ 8\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^\alpha + \left(-\frac{1}{3} + \frac{4}{9}\epsilon \right)^\alpha \right] \nonumber\\
-\end{align}
-\begin{figure}[t!]
-    \centering
-    \includegraphics[scale=0.35]{figs/H_vs_eps_a.pdf}
-    \caption{\textbf{R\'{e}nyi entropy $H_\alpha$ of the $\epsilon$-noisy Strange state.} $H_\alpha$ is increasing in $\alpha$ and $\epsilon$.
-The first dashed contour from the right corresponds to $H_\alpha(\rho_{\rm{S}}(\epsilon)) = 0$.
-In particular, $H_\alpha(\rho_{\rm{S}}(0)) = 0$ corresponds to $\alpha \approx 1.31$.
-    }
-    \label{fig:H}
-\end{figure}
-We now show the following equivalence between Wigner negativity and negative R\'{e}nyi entropies.
-\begingroup
-\def\thetheorem{\ref{thm:Magic}}
-\begin{theorem}
-	A quantum state $\rho$ has Wigner negativity if and only if $H_\alpha(W_\rho) < 0$ for some $\alpha =  \frac{2a}{2b-1}$, with positive integers $a \geq b$.
-\end{theorem}
-\addtocounter{theorem}{-1}
-\endgroup
-\begin{proof} 
-If we have $H_\alpha (W_\rho) <0 $ for $\alpha >1$, then it follows that $\log \sum_{\bmz} W_\rho (\bmz)^\alpha > 1$. 
-However, it is known that $H_\alpha$ is always non-negative on probability distributions, so $W_\rho(\bmz)$ must be a strict quasi-distribution with negativity.
-
-Conversely, suppose $\rho$ has negativity in its Wigner representation.
-This in particular implies that $\sum_{\bmz} |W_\rho (\bmz)| >1$.
-We now consider $\sum_{\bmz} W_\rho (\bmz)^{\frac{2a}{2b-1}}$ for positive integers $a\ge b$.
-We have that
-\begin{align}
-\sum_{\bmz} W_\rho (\bmz)^{\frac{2a}{2b-1}} &= \sum_{\bmz} |W_\rho (\bmz)|^{\frac{2a}{2b-1}} \nonumber \\
-&= \sum_{\bmz} |W_\rho (\bmz)|^{1+ \epsilon},
-\end{align}
-where $\epsilon = \alpha -1=\frac{2a}{2b-1} - 1 >0$.
-By choosing the positive integers $a$ and $b$ sufficiently large we can make $\epsilon$ arbitrarily close to $0$.
-This implies that there exists a sequence $\epsilon_n= \alpha_n-1 =\frac{2a_n}{2b_n-1} - 1$ with integer pairs $a_n, b_n$ such that
-\begin{equation}
-\sum_{\bmz} |W_\rho (\bmz)|^{1+ \epsilon_n} \rightarrow \sum_{\bmz} |W_\rho (\bmz)| >1,
-\end{equation}
-as $n$ increases.
-Since $\frac{1}{1-\alpha_n} <0$ for any $n$ it follows that $H_{\alpha_n} (W_\rho) = \frac{1}{1-\alpha_n} \log \sum_{\bmz} W_\rho (\bmz)^{\alpha_n}  <0 $ at some point in the sequence, which completes the proof.
-\end{proof}
-Therefore Wigner negativity coincides with negativity of a R\'{e}nyi entropy.
-
-\subsection{R\'{e}nyi divergences on quasi-distributions}
-We now define the $\alpha$-R\'{e}nyi divergence for a quasi-distribution $\w \in \mathcal{Q}_N$ relative to a full-rank probability distribution $\r\in \mathcal{Q}_N^+$ as
-\begin{equation}
-	D_\alpha(\w||\r) \coloneqq \frac{1}{\alpha - 1} \log \sum_{i} w_i^\alpha r_i^{1-\alpha},
-\end{equation}
-where $\alpha=2a/(2b-1)$ for positive integers $a \ge b$.
-We now have the following result that relates the R\'{e}nyi divergence to the R\'{e}nyi entropy on a dense subset of probability distributions.
-\begin{proposition}\label{H2D}
-	Let $\w\in \mathcal{Q}_N$ be a quasi-distribution and $\r \in \mathcal{Q}_N^+$ a probability distribution with positive rational entries given by $r_i = a_i/K$ for positive integers $a_i$ and $K = \sum_{i=1}^N a_i$.
-	Then,
-	\begin{equation}
-		H_\alpha(\Gamma_{\bma}(\w)) = K - D_\alpha(\w \hspace{1pt}||\hspace{1pt} \r),
-	\end{equation}
-	where $\alpha = 2a / (2b-1)$ for positive integers $a \ge b$.
-\end{proposition}
-\begin{proof}
-	For the given form of $\alpha$ and positive $r_i,\ i=1,\dots,N$, $D_\alpha(\w || \r)$ is well-defined for all $\w$. From the definition of $\Gamma_{\bma}$ we have
-	\begin{equation}
-		\Gamma_{\bma}(\w) = \bigoplus_{i=1}^N w_i (1/a_i, 1/a_i, \dots, 1/a_i).
-	\end{equation}
-	This directly leads to
-	\begin{align}
-		H_\alpha(\Gamma_{\bma}(\w)) &= \frac{1}{1-\alpha} \log \sum_{i=1}^N a_i \left( \frac{w_i}{a_i} \right)^\alpha \nonumber\\
-		&= \frac{1}{1-\alpha} \log \sum_{i=1}^N w_i^{\alpha} a_i^{1-\alpha} \nonumber\\
-		&= \frac{1}{1-\alpha} \log K^{1-\alpha} \sum_{i=1}^N w_i^{\alpha} r_i^{1-\alpha} \nonumber\\
-		&= K + \frac{1}{1-\alpha} \log \sum_{i=1}^N w_i^{\alpha} r_i^{1-\alpha} \nonumber\\
-		&= K - D_\alpha(\w ||\r).
-	\end{align}
-\end{proof}
-With this we now establish monotonicity for R\'{e}nyi relative divergences.
-\begin{proposition}\label{DSchur}
-	Let $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$.
-Let $\w \in \mathcal{Q}_N$, $\w' \in \mathcal{Q}_{N'}$ and $\r \in  \mathcal{Q}^+_N$, $\r' \in \mathcal{Q}^+_{N'}$ with positive rational components $a_i/K$ and $a'_i/K$ respectively.
-	Then $D_\alpha(\w \hspace{1pt}||\hspace{1pt} \r) \geq D_\alpha(\w' \hspace{1pt}||\hspace{1pt} \r')$, whenever $(\w, \r) \succ (\w', \r')$.
-\end{proposition}
-\begin{proof}
-	The statement $(\w, \r) \succ (\w', \r')$ is equivalent to $\Gamma_{\bma}(\w) \succ \Gamma_{\bma'}(\w')$.
-	Therefore, due to Theorem~\ref{thm:HSchur} we have
-	\begin{equation}
-		H_\alpha(\Gamma_{\bma}(\w)) \leq H_\alpha(\Gamma_{\bma'}(\w'))
-	\end{equation}
-	which, due to Proposition~\ref{H2D}, is equivalent to
-	\begin{equation}
-		D_\alpha(\w \hspace{1pt}||\hspace{1pt} \r) \geq D_\alpha(\w' \hspace{1pt}||\hspace{1pt} \r').
-	\end{equation}
-\end{proof}
-Since the rationals are dense in the real numbers we can assume any Wigner distribution considered has rational components without affecting results.
-We now specialize to Wigner distributions of quantum states, and quantum operations that map the set of free states $\F$ into itself.
-\begingroup
-\def\thetheorem{\ref{thm:Da_props}}
-\begin{theorem}
-	Let $\tau$ be a state in the interior of $\F$ and $\alpha = 2a / (2b-1)$ for positive integers $a,b$ with $a \geq b$.
-Then, the $\alpha$-R\'{e}nyi divergence $D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)$ is well-defined for all states $\rho$, and the following hold:
-\begin{enumerate}
-\item $D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) \ge 0$ for all quantum states $\rho$.
-\item  $D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) = 0$ if and only if $\rho =\tau$.
-\item $D_\alpha(W_{\rho^{\otimes n}} \hspace{1pt}||\hspace{1pt} W_{\tau^{\otimes n}}) = n D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)$ for any $n \in \mathbb{N}$.
-\item $D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) \geq D_\alpha (W_{\E(\rho)} \hspace{1pt}||\hspace{1pt} W_{\E(\tau)})$ for any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$.
-\end{enumerate}
-\end{theorem}
-\addtocounter{theorem}{-1}
-\endgroup
-\begin{proof}
-	Since $\tau$ is in the interior of $\F$, its Wigner function obeys $W_\tau(\bmz) >0$ for all points $\bmz$ in the phase space. 
-In general, $W_\rho(\bmz)$ is a quasi-distribution, but for $\alpha = 2a/2b-1$ we that $W_{\rho}(\bmz)^\alpha \geq 0$. 
-Therefore $D_\alpha (W_\rho || W_\tau)$ is always well-defined and real-valued.
-
-1. $D_\alpha$ is Schur-convex and every pair $(W_{\rho}, W_{\tau})$ majorizes the pair $(W_{\I/d}, W_{\I/d})$, so
-\begin{align}
-	D_\alpha(W_{\rho} \hspace{1pt}||\hspace{1pt} W_{\tau}) \geq D_\alpha(W_{\I/d} \hspace{1pt}||\hspace{1pt} W_{\I/d}) &= \nonumber\\
-	\frac{1}{\alpha-1} \log \sum_{\bmz} W_{\I/d}(\bmz) &= 0.
-\end{align}
-
-2.
-In the inequality of property 1, equality holds iff $L_{\rho|\tau}(x) = L_{\I/d|\I/d}(x) = L_{\tau|\tau}(x)$ for all $x\in [0,1]$ due to Proposition~\ref{prop:rmajor} which in turn holds iff $\rho = \tau$.
-
-3. This property follows from the multiplicativity of the Wigner distribution.
-In particular,
-\begin{align}
-	&D_\alpha(W_{\rho^{\otimes n}} \hspace{1pt}||\hspace{1pt} W_{\tau^{\otimes n}}) = \nonumber\\
-	&\frac{1}{\alpha - 1} \log \sum_{\bmz} W_{\rho^{\otimes n}}(\bmz)^\alpha W_{\tau^{\otimes n}}(\bmz)^{1-\alpha} = \nonumber\\
-	&\frac{1}{\alpha - 1} \log \sum_{\bmz} \prod_{i=1}^n W_{\rho}(\bmz_i)^\alpha W_{\tau}(\bmz_i)^{1-\alpha} = \nonumber\\
-	&\frac{1}{\alpha - 1} \log \prod_{i=1}^n \sum_{\bmz_i} W_{\rho}(\bmz_i)^\alpha W_{\tau}(\bmz_i)^{1-\alpha} = \nonumber\\
-	&\sum_{i=1}^n \frac{1}{\alpha - 1} \log \sum_{\bmz'} W_{\rho}(\bmz')^\alpha W_{\tau}(\bmz')^{1-\alpha} = \nonumber\\
-	&= n D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau).
-\end{align}
-
-4.
-This follows immediately from the fact that $(W_\rho, W_\tau) \succ (W_{\E(\rho)}, W_{\E(\tau)})$ for any free quantum channel $\E$ that sends $\tau$ into the interior of $\F$, and the Schur-convexity of $D_\alpha$.
-\end{proof}
-
-We are now in a position to derive general magic state distillation bounds.
-
-\begingroup
-\def\thetheorem{\ref{thm:entropic_bounds}}
-\begin{theorem}
-	Consider a general magic state distillation process on prime dimension qudits, that converts a magic state $\rho^{\otimes n} \longrightarrow \E(\rho^{\otimes n})=\rho'^{\otimes m}$and let $\tau$ be any full-rank stabilizer reference state on a qudit.
-Then the distillation rate $R \coloneqq m/n$ is upper bounded as,
-	\begin{equation}
-		R \leq R_\alpha \coloneqq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{\rlap{\raisebox{-0.2ex}{$\widetilde{\phantom{D}}$}}D_\alpha( \rho', \tau')},
-	\end{equation}
-	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ and the average divergence
-	\begin{equation}
-\widetilde{D}_\alpha( \rho', \tau') \coloneqq \frac{1}{m} D_\alpha (W_{\rho'^{\otimes m}} \hspace{1pt}||\hspace{1pt} W_{\tau'_m}),
-\end{equation}
-between the output magic state $\rho'^{\otimes m}$ and $\tau'_m = \E(\tau^{\otimes n})$.
-\end{theorem}
-\addtocounter{theorem}{-1}
-\endgroup
-\begin{proof}
-	The bound is a direct consequence of the properties of the $\alpha$--R\'{e}nyi divergence in Theorem~\ref{thm:Da_props}.
-
-Due to the action of the magic protocol channel, we get
-\begin{equation}	
-	D_\alpha(W_{\rho^{\otimes n}} \hspace{1pt}||\hspace{1pt} W_{\tau^{\otimes n}}) \geq D_\alpha (W_{\rho'^{\otimes m}} \hspace{1pt}||\hspace{1pt} W_{\tau'_m}).\vspace{10pt}
-\end{equation}
-
-We can use the additivity to rewrite this as
-\begin{equation}
-	n D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) \geq m \frac{1}{m}D_\alpha(W_{\rho'^{\otimes m}} \hspace{1pt}||\hspace{1pt} W_{\tau'_m}).
-\end{equation}
-
-Since $\rho'^{\otimes m} \neq \tau'_m$, we have $D_\alpha(W_{\rho'^{\otimes m}} \hspace{1pt}||\hspace{1pt} W_{\tau'_m}) > 0$, which directly leads to the bound
-\begin{equation}
-	\frac{m}{n} \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{\rlap{\raisebox{-0.1ex}{$\widetilde{\phantom{D}}$}}D_\alpha( \rho', \tau')}.
-\end{equation}
-\end{proof}
+\section*{Competing interests}
+The authors declare no competing interests.
+
+\section*{Author contributions}
+DJ conceived the initial idea. 
+Calculations were performed by NK. 
+Analysis and writing of the manuscript were jointly done by NK and DJ.
+
+\section*{References}
+
+\providecommand{\noopsort}[1]{}\providecommand{\singleletter}[1]{#1}
+\begin{thebibliography}{100}
+\expandafter\ifx\csname url\endcsname\relax
+  \def\url#1{\texttt{#1}}\fi
+\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{}\fi
+\providecommand{\bibinfo}[2]{#2}
+\providecommand{\eprint}[2][]{\url{#2}}
+
+\bibitem{campbell_roads_2017}
+\bibinfo{author}{Campbell, E.~T.}, \bibinfo{author}{Terhal, B.~M.} \&
+  \bibinfo{author}{Vuillot, C.}
+\newblock \bibinfo{title}{Roads towards fault-tolerant universal quantum
+  computation}.
+\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{549}},
+  \bibinfo{pages}{172--179} (\bibinfo{year}{2017}).
+\newblock \urlprefix\url{https://www.nature.com/articles/nature23460}.
+
+\bibitem{cit:raussendorf}
+\bibinfo{author}{Raussendorf{ }, R.} \& \bibinfo{author}{Briegel, H.~J.}
+\newblock \bibinfo{title}{A one-way quantum computer}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. Lett.}}
+  \textbf{\bibinfo{volume}{86}}, \bibinfo{pages}{5188--5191}
+  (\bibinfo{year}{2001}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.86.5188}.
+
+\bibitem{Raussendorf_2013}
+\bibinfo{author}{Raussendorf, R.}, \bibinfo{author}{Browne, D.~E.} \&
+  \bibinfo{author}{Briegel, H.~J.}
+\newblock \bibinfo{title}{Measurement-based quantum computation on cluster
+  states}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. A}} \textbf{\bibinfo{volume}{68}},
+  \bibinfo{pages}{022312} (\bibinfo{year}{2003}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.68.022312}.
+
+\bibitem{Nickerson_2014}
+\bibinfo{author}{Nickerson, N.~H.}, \bibinfo{author}{Fitzsimons, J.~F.} \&
+  \bibinfo{author}{Benjamin, S.~C.}
+\newblock \bibinfo{title}{Freely scalable quantum technologies using cells of
+  5-to-50 qubits with very lossy and noisy photonic links}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. X}} \textbf{\bibinfo{volume}{4}},
+  \bibinfo{pages}{041041} (\bibinfo{year}{2014}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevX.4.041041}.
+
+\bibitem{Nikahd_2017}
+\bibinfo{author}{Nikahd, E.}, \bibinfo{author}{Sedighi, M.} \&
+  \bibinfo{author}{Saheb~Zamani, M.}
+\newblock \bibinfo{title}{Nonuniform code concatenation for universal
+  fault-tolerant quantum computing}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. A}} \textbf{\bibinfo{volume}{96}},
+  \bibinfo{pages}{032337} (\bibinfo{year}{2017}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.96.032337}.
+
+\bibitem{chao_2018}
+\bibinfo{author}{Chao, R.} \& \bibinfo{author}{Reichardt, B.~W.}
+\newblock \bibinfo{title}{Fault-tolerant quantum computation with few qubits}.
+\newblock \emph{\bibinfo{journal}{npj Quantum Information}}
+  \textbf{\bibinfo{volume}{4}}, \bibinfo{pages}{1--8} (\bibinfo{year}{2018}).
+\newblock \urlprefix\url{https://www.nature.com/articles/s41534-018-0085-z}.
+
+\bibitem{lin_pieceable_2020}
+\bibinfo{author}{Lin, C.}, \bibinfo{author}{Yang, G.}, \bibinfo{author}{Luo,
+  Q.} \& \bibinfo{author}{Li, X.}
+\newblock \bibinfo{title}{Pieceable fault tolerant conversion between 5-qubit
+  code and 7-{CSS} code}.
+\newblock \emph{\bibinfo{journal}{Quantum Information Processing}}
+  \textbf{\bibinfo{volume}{19}}, \bibinfo{pages}{243} (\bibinfo{year}{2020}).
+\newblock \urlprefix\url{https://doi.org/10.1007/s11128-020-02740-3}.
+
+\bibitem{Lin_2020}
+\bibinfo{author}{Lin, C.} \& \bibinfo{author}{Yang, G.}
+\newblock \bibinfo{title}{Concatenated pieceable fault-tolerant scheme for
+  universal quantum computation}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. A}}
+  \textbf{\bibinfo{volume}{102}}, \bibinfo{pages}{052415}
+  (\bibinfo{year}{2020}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.102.052415}.
+
+\bibitem{chamberland_2020}
+\bibinfo{author}{Chamberland, C.} \emph{et~al.}
+\newblock \bibinfo{title}{Building a fault-tolerant quantum computer using
+  concatenated cat codes} (\bibinfo{year}{2020}).
+\newblock \urlprefix\url{https://arxiv.org/abs/2012.04108}.
+
+\bibitem{Bourassa_2021}
+\bibinfo{author}{Bourassa, J.~E.} \emph{et~al.}
+\newblock \bibinfo{title}{Blueprint for a {S}calable {P}hotonic
+  {F}ault-{T}olerant {Q}uantum {C}omputer}.
+\newblock \emph{\bibinfo{journal}{{Quantum}}} \textbf{\bibinfo{volume}{5}},
+  \bibinfo{pages}{392} (\bibinfo{year}{2021}).
+\newblock \urlprefix\url{https://doi.org/10.22331/q-2021-02-04-392}.
+
+\bibitem{Bravyi_1998}
+\bibinfo{author}{Bravyi, S.~B.} \& \bibinfo{author}{Kitaev, A.~Y.}
+\newblock \bibinfo{title}{Quantum codes on a lattice with boundary}
+  (\bibinfo{year}{1998}).
+\newblock \urlprefix\url{https://arxiv.org/abs/quant-ph/9811052}.
+
+\bibitem{Freedman_2001}
+\bibinfo{author}{Freedman, M.~H.}
+\newblock \bibinfo{title}{Quantum computation and the localization of modular
+  functors}.
+\newblock \emph{\bibinfo{journal}{Foundations of Computational Mathematics}}
+  \textbf{\bibinfo{volume}{1}}, \bibinfo{pages}{183--204}
+  (\bibinfo{year}{2001}).
+\newblock \urlprefix\url{https://doi.org/10.1007/s102080010006}.
+
+\bibitem{Dennis_2002}
+\bibinfo{author}{Dennis, E.}, \bibinfo{author}{Kitaev, A.},
+  \bibinfo{author}{Landahl, A.} \& \bibinfo{author}{Preskill, J.}
+\newblock \bibinfo{title}{Topological quantum memory}.
+\newblock \emph{\bibinfo{journal}{Journal of Mathematical Physics}}
+  \textbf{\bibinfo{volume}{43}}, \bibinfo{pages}{4452--4505}
+  (\bibinfo{year}{2002}).
+\newblock \urlprefix\url{https://aip.scitation.org/doi/10.1063/1.1499754}.
+
+\bibitem{Raussendorf_2007}
+\bibinfo{author}{Raussendorf, R.} \& \bibinfo{author}{Harrington, J.}
+\newblock \bibinfo{title}{Fault-tolerant quantum computation with high
+  threshold in two dimensions}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. Lett.}}
+  \textbf{\bibinfo{volume}{98}}, \bibinfo{pages}{190504}
+  (\bibinfo{year}{2007}).
+\newblock
+  \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.98.190504}.
+
+\bibitem{Eastin_2009}
+\bibinfo{author}{Eastin, B.} \& \bibinfo{author}{Knill, E.}
+\newblock \bibinfo{title}{Restrictions on transversal encoded quantum gate
+  sets}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. Lett.}}
+  \textbf{\bibinfo{volume}{102}}, \bibinfo{pages}{110502}
+  (\bibinfo{year}{2009}).
+\newblock
+  \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.102.110502}.
+
+\bibitem{Calderbank_1996}
+\bibinfo{author}{Calderbank, A.~R.} \& \bibinfo{author}{Shor, P.~W.}
+\newblock \bibinfo{title}{Good quantum error-correcting codes exist}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. A}} \textbf{\bibinfo{volume}{54}},
+  \bibinfo{pages}{1098--1105} (\bibinfo{year}{1996}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.54.1098}.
+
+\bibitem{Steane_1996}
+\bibinfo{author}{Steane, A.}
+\newblock \bibinfo{title}{Multiple-particle interference and quantum error
+  correction}.
+\newblock \emph{\bibinfo{journal}{Proceedings of the Royal Society A:
+  Mathematical, Physical and Engineering Sciences}}
+  \textbf{\bibinfo{volume}{452}}, \bibinfo{pages}{2551--2577}
+  (\bibinfo{year}{1996}).
+\newblock
+  \urlprefix\url{https://royalsocietypublishing.org/doi/abs/10.1098/rspa.1996.0136}.
+
+\bibitem{cit:bravyi}
+\bibinfo{author}{Bravyi{ }, S.} \& \bibinfo{author}{Kitaev, A.}
+\newblock \bibinfo{title}{Universal quantum computation with ideal clifford
+  gates and noisy ancillas}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. A}} \textbf{\bibinfo{volume}{71}},
+  \bibinfo{pages}{022316} (\bibinfo{year}{2005}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.71.022316}.
+
+\bibitem{Jones_2013}
+\bibinfo{author}{Jones, C.}
+\newblock \bibinfo{title}{Multilevel distillation of magic states for quantum
+  computing}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. A}} \textbf{\bibinfo{volume}{87}},
+  \bibinfo{pages}{042305} (\bibinfo{year}{2013}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.87.042305}.
+
+\bibitem{Ogorman_2017}
+\bibinfo{author}{O'Gorman, J.} \& \bibinfo{author}{Campbell, E.~T.}
+\newblock \bibinfo{title}{Quantum computation with realistic magic-state
+  factories}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. A}} \textbf{\bibinfo{volume}{95}},
+  \bibinfo{pages}{032338} (\bibinfo{year}{2017}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.95.032338}.
+
+\bibitem{Bravyi2012}
+\bibinfo{author}{Bravyi, S.} \& \bibinfo{author}{Haah, J.}
+\newblock \bibinfo{title}{Magic-state distillation with low overhead}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. A}} \textbf{\bibinfo{volume}{86}},
+  \bibinfo{pages}{052329} (\bibinfo{year}{2012}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.86.052329}.
+
+\bibitem{haah2017magic}
+\bibinfo{author}{Haah, J.}, \bibinfo{author}{Hastings, M.~B.},
+  \bibinfo{author}{Poulin, D.} \& \bibinfo{author}{Wecker, D.}
+\newblock \bibinfo{title}{Magic state distillation with low space overhead and
+  optimal asymptotic input count}.
+\newblock \emph{\bibinfo{journal}{{Quantum}}} \textbf{\bibinfo{volume}{1}},
+  \bibinfo{pages}{31} (\bibinfo{year}{2017}).
+\newblock \urlprefix\url{https://doi.org/10.22331/q-2017-10-03-31}.
+
+\bibitem{Hastings2018}
+\bibinfo{author}{Hastings, M.~B.} \& \bibinfo{author}{Haah, J.}
+\newblock \bibinfo{title}{Distillation with sublogarithmic overhead}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. Lett.}}
+  \textbf{\bibinfo{volume}{120}}, \bibinfo{pages}{050504}
+  (\bibinfo{year}{2018}).
+\newblock
+  \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.120.050504}.
+
+\bibitem{Litinski_2019}
+\bibinfo{author}{Litinski, D.}
+\newblock \bibinfo{title}{Magic {S}tate {D}istillation: {N}ot as {C}ostly as
+  {Y}ou {T}hink}.
+\newblock \emph{\bibinfo{journal}{{Quantum}}} \textbf{\bibinfo{volume}{3}},
+  \bibinfo{pages}{205} (\bibinfo{year}{2019}).
+\newblock \urlprefix\url{https://doi.org/10.22331/q-2019-12-02-205}.
+
+\bibitem{CampbellAnwar_2012}
+\bibinfo{author}{Campbell, E.~T.}, \bibinfo{author}{Anwar, H.} \&
+  \bibinfo{author}{Browne, D.~E.}
+\newblock \bibinfo{title}{Magic-state distillation in all prime dimensions
+  using quantum reed-muller codes}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. X}} \textbf{\bibinfo{volume}{2}},
+  \bibinfo{pages}{041021} (\bibinfo{year}{2012}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevX.2.041021}.
+
+\bibitem{Anwar_2012}
+\bibinfo{author}{Anwar, H.}, \bibinfo{author}{Campbell, E.~T.} \&
+  \bibinfo{author}{Browne, D.~E.}
+\newblock \bibinfo{title}{Qutrit magic state distillation}.
+\newblock \emph{\bibinfo{journal}{New Journal of Physics}}
+  \textbf{\bibinfo{volume}{14}}, \bibinfo{pages}{063006}
+  (\bibinfo{year}{2012}).
+\newblock \urlprefix\url{https://doi.org/10.1088/1367-2630/14/6/063006}.
+
+\bibitem{Dawkins_2015}
+\bibinfo{author}{Dawkins, H.} \& \bibinfo{author}{Howard, M.}
+\newblock \bibinfo{title}{Qutrit magic state distillation tight in some
+  directions}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. Lett.}}
+  \textbf{\bibinfo{volume}{115}}, \bibinfo{pages}{030501}
+  (\bibinfo{year}{2015}).
+\newblock
+  \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.115.030501}.
+
+\bibitem{Krishna2019}
+\bibinfo{author}{Krishna, A.} \& \bibinfo{author}{Tillich, J.-P.}
+\newblock \bibinfo{title}{Towards low overhead magic state distillation}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. Lett.}}
+  \textbf{\bibinfo{volume}{123}}, \bibinfo{pages}{070507}
+  (\bibinfo{year}{2019}).
+\newblock
+  \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.123.070507}.
+
+\bibitem{cit:prakash}
+\bibinfo{author}{Prakash, S.}
+\newblock \bibinfo{title}{Magic state distillation with the ternary golay
+  code}.
+\newblock \emph{\bibinfo{journal}{Proceedings of the Royal Society A:
+  Mathematical, Physical and Engineering Sciences}}
+  \textbf{\bibinfo{volume}{476}}, \bibinfo{pages}{20200187}
+  (\bibinfo{year}{2020}).
+\newblock
+  \urlprefix\url{https://royalsocietypublishing.org/doi/abs/10.1098/rspa.2020.0187}.
+
+\bibitem{chamberland_very_2020}
+\bibinfo{author}{Chamberland, C.} \& \bibinfo{author}{Noh, K.}
+\newblock \bibinfo{title}{Very low overhead fault-tolerant magic state
+  preparation using redundant ancilla encoding and flag qubits}.
+\newblock \emph{\bibinfo{journal}{npj Quantum Information}}
+  \textbf{\bibinfo{volume}{6}}, \bibinfo{pages}{91} (\bibinfo{year}{2020}).
+\newblock \urlprefix\url{https://doi.org/10.1038/s41534-020-00319-5}.
+
+\bibitem{Chamberland2019faulttolerantmagic}
+\bibinfo{author}{Chamberland, C.} \& \bibinfo{author}{Cross, A.~W.}
+\newblock \bibinfo{title}{Fault-tolerant magic state preparation with flag
+  qubits}.
+\newblock \emph{\bibinfo{journal}{{Quantum}}} \textbf{\bibinfo{volume}{3}},
+  \bibinfo{pages}{143} (\bibinfo{year}{2019}).
+\newblock \urlprefix\url{https://doi.org/10.22331/q-2019-05-20-143}.
+
+\bibitem{Campbell_2017}
+\bibinfo{author}{Campbell, E.~T.} \& \bibinfo{author}{Howard, M.}
+\newblock \bibinfo{title}{Unifying gate synthesis and magic state
+  distillation}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. Lett.}}
+  \textbf{\bibinfo{volume}{118}}, \bibinfo{pages}{060501}
+  (\bibinfo{year}{2017}).
+\newblock
+  \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.118.060501}.
+
+\bibitem{Howard_2017}
+\bibinfo{author}{Campbell, E.~T.} \& \bibinfo{author}{Howard, M.}
+\newblock \bibinfo{title}{Unified framework for magic state distillation and
+  multiqubit gate synthesis with reduced resource cost}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. A}} \textbf{\bibinfo{volume}{95}},
+  \bibinfo{pages}{022316} (\bibinfo{year}{2017}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.95.022316}.
+
+\bibitem{Prakash_2018}
+\bibinfo{author}{Prakash, S.}, \bibinfo{author}{Jain, A.},
+  \bibinfo{author}{Kapur, B.} \& \bibinfo{author}{Seth, S.}
+\newblock \bibinfo{title}{Normal form for single-qutrit clifford+$t$ operators
+  and synthesis of single-qutrit gates}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. A}} \textbf{\bibinfo{volume}{98}},
+  \bibinfo{pages}{032304} (\bibinfo{year}{2018}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.98.032304}.
+
+\bibitem{Seddon_2021}
+\bibinfo{author}{Seddon, J.~R.}, \bibinfo{author}{Regula, B.},
+  \bibinfo{author}{Pashayan, H.}, \bibinfo{author}{Ouyang, Y.} \&
+  \bibinfo{author}{Campbell, E.~T.}
+\newblock \bibinfo{title}{Quantifying quantum speedups: Improved classical
+  simulation from tighter magic monotones}.
+\newblock \emph{\bibinfo{journal}{PRX Quantum}} \textbf{\bibinfo{volume}{2}},
+  \bibinfo{pages}{010345} (\bibinfo{year}{2021}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PRXQuantum.2.010345}.
+
+\bibitem{leone2021renyi}
+\bibinfo{author}{Leone, L.}, \bibinfo{author}{Oliviero, S. F.~E.} \&
+  \bibinfo{author}{Hamma, A.}
+\newblock \bibinfo{title}{R{\'e}nyi entropy of magic} (\bibinfo{year}{2021}).
+\newblock \urlprefix\url{https://arxiv.org/abs/2106.12587}.
+
+\bibitem{Gour_2019}
+\bibinfo{author}{Chitambar, E.} \& \bibinfo{author}{Gour, G.}
+\newblock \bibinfo{title}{Quantum resource theories}.
+\newblock \emph{\bibinfo{journal}{Rev. Mod. Phys.}}
+  \textbf{\bibinfo{volume}{91}}, \bibinfo{pages}{025001}
+  (\bibinfo{year}{2019}).
+\newblock
+  \urlprefix\url{https://link.aps.org/doi/10.1103/RevModPhys.91.025001}.
+
+\bibitem{cit:ahmadi}
+\bibinfo{author}{Ahmadi, M.}, \bibinfo{author}{Dang, H.~B.},
+  \bibinfo{author}{Gour, G.} \& \bibinfo{author}{Sanders, B.~C.}
+\newblock \bibinfo{title}{Quantification and manipulation of magic states}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. A}} \textbf{\bibinfo{volume}{97}},
+  \bibinfo{pages}{062332} (\bibinfo{year}{2018}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.97.062332}.
+
+\bibitem{cit:seddon}
+\bibinfo{author}{Seddon, J.~R.} \& \bibinfo{author}{Campbell, E.~T.}
+\newblock \bibinfo{title}{Quantifying magic for multi-qubit operations}.
+\newblock \emph{\bibinfo{journal}{Proceedings of the Royal Society A:
+  Mathematical, Physical and Engineering Sciences}}
+  \textbf{\bibinfo{volume}{475}}, \bibinfo{pages}{20190251}
+  (\bibinfo{year}{2019}).
+\newblock
+  \urlprefix\url{https://royalsocietypublishing.org/doi/abs/10.1098/rspa.2019.0251}.
+
+\bibitem{Wang_2019}
+\bibinfo{author}{Wang, X.}, \bibinfo{author}{Wilde, M.~M.} \&
+  \bibinfo{author}{Su, Y.}
+\newblock \bibinfo{title}{Quantifying the magic of quantum channels}.
+\newblock \emph{\bibinfo{journal}{New Journal of Physics}}
+  \textbf{\bibinfo{volume}{21}}, \bibinfo{pages}{103002}
+  (\bibinfo{year}{2019}).
+\newblock \urlprefix\url{https://doi.org/10.1088/1367-2630/ab451d}.
+
+\bibitem{Sarkar_2020}
+\bibinfo{author}{Sarkar, S.}, \bibinfo{author}{Mukhopadhyay, C.} \&
+  \bibinfo{author}{Bayat, A.}
+\newblock \bibinfo{title}{Characterization of an operational quantum resource
+  in a critical many-body system}.
+\newblock \emph{\bibinfo{journal}{New Journal of Physics}}
+  \textbf{\bibinfo{volume}{22}}, \bibinfo{pages}{083077}
+  (\bibinfo{year}{2020}).
+\newblock \urlprefix\url{https://doi.org/10.1088/1367-2630/aba919}.
+
+\bibitem{White_2021}
+\bibinfo{author}{White, C.~D.}, \bibinfo{author}{Cao, C.} \&
+  \bibinfo{author}{Swingle, B.}
+\newblock \bibinfo{title}{Conformal field theories are magical}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. B}}
+  \textbf{\bibinfo{volume}{103}}, \bibinfo{pages}{075145}
+  (\bibinfo{year}{2021}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevB.103.075145}.
+
+\bibitem{Vega_2017}
+\bibinfo{author}{Bermejo-Vega, J.}, \bibinfo{author}{Delfosse, N.},
+  \bibinfo{author}{Browne, D.~E.}, \bibinfo{author}{Okay, C.} \&
+  \bibinfo{author}{Raussendorf, R.}
+\newblock \bibinfo{title}{Contextuality as a resource for models of quantum
+  computation with qubits}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. Lett.}}
+  \textbf{\bibinfo{volume}{119}}, \bibinfo{pages}{120505}
+  (\bibinfo{year}{2017}).
+\newblock
+  \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.119.120505}.
+
+\bibitem{cit:howard2}
+\bibinfo{author}{Howard, M.}, \bibinfo{author}{Wallman, J.},
+  \bibinfo{author}{Veitch, V.} \& \bibinfo{author}{Emerson, J.}
+\newblock \bibinfo{title}{Contextuality supplies the ‘magic’ for quantum
+  computation}.
+\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{510}},
+  \bibinfo{pages}{351--355} (\bibinfo{year}{2014}).
+\newblock \urlprefix\url{https://doi.org/10.1038/nature13460}.
+
+\bibitem{Zurel_2020}
+\bibinfo{author}{Zurel, M.}, \bibinfo{author}{Okay, C.} \&
+  \bibinfo{author}{Raussendorf, R.}
+\newblock \bibinfo{title}{Hidden variable model for universal quantum
+  computation with magic states on qubits}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. Lett.}}
+  \textbf{\bibinfo{volume}{125}}, \bibinfo{pages}{260404}
+  (\bibinfo{year}{2020}).
+\newblock
+  \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.125.260404}.
+
+\bibitem{Okay_2021}
+\bibinfo{author}{Okay, C.}, \bibinfo{author}{Zurel, M.} \&
+  \bibinfo{author}{Raussendorf, R.}
+\newblock \bibinfo{title}{On the extremal points of the {$\Lambda$}-polytopes
+  and classical simulation of quantum computation with magic states}
+  (\bibinfo{year}{2021}).
+\newblock \urlprefix\url{https://arxiv.org/abs/2104.05822}.
+
+\bibitem{schmid2020structure}
+\bibinfo{author}{Schmid, D.}, \bibinfo{author}{Selby, J.~H.},
+  \bibinfo{author}{Pusey, M.~F.} \& \bibinfo{author}{Spekkens, R.~W.}
+\newblock \bibinfo{title}{A structure theorem for generalized-noncontextual
+  ontological models} (\bibinfo{year}{2020}).
+\newblock \urlprefix\url{https://arxiv.org/abs/2005.07161}.
+
+\bibitem{Schmid_2021}
+\bibinfo{author}{Schmid, D.}, \bibinfo{author}{Selby, J.~H.},
+  \bibinfo{author}{Wolfe, E.}, \bibinfo{author}{Kunjwal, R.} \&
+  \bibinfo{author}{Spekkens, R.~W.}
+\newblock \bibinfo{title}{Characterization of noncontextuality in the framework
+  of generalized probabilistic theories}.
+\newblock \emph{\bibinfo{journal}{PRX Quantum}} \textbf{\bibinfo{volume}{2}},
+  \bibinfo{pages}{010331} (\bibinfo{year}{2021}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PRXQuantum.2.010331}.
+
+\bibitem{jones_2012}
+\bibinfo{author}{Jones, N.~C.} \emph{et~al.}
+\newblock \bibinfo{title}{Layered architecture for quantum computing}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. X}} \textbf{\bibinfo{volume}{2}},
+  \bibinfo{pages}{031007} (\bibinfo{year}{2012}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevX.2.031007}.
+
+\bibitem{Li_2017}
+\bibinfo{author}{Li, Y.} \& \bibinfo{author}{Benjamin, S.~C.}
+\newblock \bibinfo{title}{Efficient variational quantum simulator incorporating
+  active error minimization}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. X}} \textbf{\bibinfo{volume}{7}},
+  \bibinfo{pages}{021050} (\bibinfo{year}{2017}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevX.7.021050}.
+
+\bibitem{Temme_2017}
+\bibinfo{author}{Temme, K.}, \bibinfo{author}{Bravyi, S.} \&
+  \bibinfo{author}{Gambetta, J.~M.}
+\newblock \bibinfo{title}{Error mitigation for short-depth quantum circuits}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. Lett.}}
+  \textbf{\bibinfo{volume}{119}}, \bibinfo{pages}{180509}
+  (\bibinfo{year}{2017}).
+\newblock
+  \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.119.180509}.
+
+\bibitem{Endo_2018}
+\bibinfo{author}{Endo, S.}, \bibinfo{author}{Benjamin, S.~C.} \&
+  \bibinfo{author}{Li, Y.}
+\newblock \bibinfo{title}{Practical quantum error mitigation for near-future
+  applications}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. X}} \textbf{\bibinfo{volume}{8}},
+  \bibinfo{pages}{031027} (\bibinfo{year}{2018}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevX.8.031027}.
+
+\bibitem{McClean_2017}
+\bibinfo{author}{McClean, J.~R.}, \bibinfo{author}{Kimchi-Schwartz, M.~E.},
+  \bibinfo{author}{Carter, J.} \& \bibinfo{author}{de~Jong, W.~A.}
+\newblock \bibinfo{title}{Hybrid quantum-classical hierarchy for mitigation of
+  decoherence and determination of excited states}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. A}} \textbf{\bibinfo{volume}{95}},
+  \bibinfo{pages}{042308} (\bibinfo{year}{2017}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.95.042308}.
+
+\bibitem{Kandala_2019}
+\bibinfo{author}{Kandala, A.} \emph{et~al.}
+\newblock \bibinfo{title}{Error mitigation extends the computational reach of a
+  noisy quantum processor}.
+\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{567}},
+  \bibinfo{pages}{491--495} (\bibinfo{year}{2019}).
+\newblock \urlprefix\url{https://www.nature.com/articles/s41586-019-1040-7}.
+
+\bibitem{holmes_resource_2019}
+\bibinfo{author}{Holmes, A.} \emph{et~al.}
+\newblock \bibinfo{title}{Resource optimized quantum architectures for surface
+  code implementations of magic-state distillation}.
+\newblock \emph{\bibinfo{journal}{Microprocessors and Microsystems}}
+  \textbf{\bibinfo{volume}{67}}, \bibinfo{pages}{56--70}
+  (\bibinfo{year}{2019}).
+\newblock
+  \urlprefix\url{https://www.sciencedirect.com/science/article/pii/S0141933118303314}.
+
+\bibitem{Colless_2018}
+\bibinfo{author}{Colless, J.~I.} \emph{et~al.}
+\newblock \bibinfo{title}{Computation of molecular spectra on a quantum
+  processor with an error-resilient algorithm}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. X}} \textbf{\bibinfo{volume}{8}},
+  \bibinfo{pages}{011021} (\bibinfo{year}{2018}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevX.8.011021}.
+
+\bibitem{song2018quantum}
+\bibinfo{author}{Song, C.} \emph{et~al.}
+\newblock \bibinfo{title}{Quantum computation with universal error mitigation
+  on superconducting quantum processor} (\bibinfo{year}{2018}).
+\newblock \urlprefix\url{https://arxiv.org/abs/2005.07161}.
+
+\bibitem{Bravyi_2021}
+\bibinfo{author}{Bravyi, S.}, \bibinfo{author}{Sheldon, S.},
+  \bibinfo{author}{Kandala, A.}, \bibinfo{author}{Mckay, D.~C.} \&
+  \bibinfo{author}{Gambetta, J.~M.}
+\newblock \bibinfo{title}{Mitigating measurement errors in multiqubit
+  experiments}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. A}}
+  \textbf{\bibinfo{volume}{103}}, \bibinfo{pages}{042605}
+  (\bibinfo{year}{2021}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.103.042605}.
+
+\bibitem{bonilla_ataides_xzzx_2021}
+\bibinfo{author}{Bonilla~Ataides, J.~P.}, \bibinfo{author}{Tuckett, D.~K.},
+  \bibinfo{author}{Bartlett, S.~D.}, \bibinfo{author}{Flammia, S.~T.} \&
+  \bibinfo{author}{Brown, B.~J.}
+\newblock \bibinfo{title}{The {XZZX} surface code}.
+\newblock \emph{\bibinfo{journal}{Nature Communications}}
+  \textbf{\bibinfo{volume}{12}}, \bibinfo{pages}{2172} (\bibinfo{year}{2021}).
+\newblock \urlprefix\url{https://www.nature.com/articles/s41467-021-22274-1}.
+
+\bibitem{Bennett_1996}
+\bibinfo{author}{Bennett, C.~H.}, \bibinfo{author}{DiVincenzo, D.~P.},
+  \bibinfo{author}{Smolin, J.~A.} \& \bibinfo{author}{Wootters, W.~K.}
+\newblock \bibinfo{title}{Mixed-state entanglement and quantum error
+  correction}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. A}} \textbf{\bibinfo{volume}{54}},
+  \bibinfo{pages}{3824--3851} (\bibinfo{year}{1996}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.54.3824}.
+
+\bibitem{Tuckett_2019}
+\bibinfo{author}{Tuckett, D.~K.} \emph{et~al.}
+\newblock \bibinfo{title}{Tailoring surface codes for highly biased noise}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. X}} \textbf{\bibinfo{volume}{9}},
+  \bibinfo{pages}{041031} (\bibinfo{year}{2019}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevX.9.041031}.
+
+\bibitem{Aliferis_2008}
+\bibinfo{author}{Aliferis, P.} \& \bibinfo{author}{Preskill, J.}
+\newblock \bibinfo{title}{Fault-tolerant quantum computation against biased
+  noise}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. A}} \textbf{\bibinfo{volume}{78}},
+  \bibinfo{pages}{052331} (\bibinfo{year}{2008}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.78.052331}.
+
+\bibitem{Stephens_2013}
+\bibinfo{author}{Stephens, A.~M.}, \bibinfo{author}{Munro, W.~J.} \&
+  \bibinfo{author}{Nemoto, K.}
+\newblock \bibinfo{title}{High-threshold topological quantum error correction
+  against biased noise}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. A}} \textbf{\bibinfo{volume}{88}},
+  \bibinfo{pages}{060301} (\bibinfo{year}{2013}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.88.060301}.
+
+\bibitem{Li_2015}
+\bibinfo{author}{Li, Y.}
+\newblock \bibinfo{title}{A magic state's fidelity can be superior to the
+  operations that created it}.
+\newblock \emph{\bibinfo{journal}{New Journal of Physics}}
+  \textbf{\bibinfo{volume}{17}}, \bibinfo{pages}{023037}
+  (\bibinfo{year}{2015}).
+\newblock \urlprefix\url{https://doi.org/10.1088/1367-2630/17/2/023037}.
+
+\bibitem{Babbush_2018}
+\bibinfo{author}{Babbush, R.} \emph{et~al.}
+\newblock \bibinfo{title}{Encoding electronic spectra in quantum circuits with
+  linear t complexity}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. X}} \textbf{\bibinfo{volume}{8}},
+  \bibinfo{pages}{041015} (\bibinfo{year}{2018}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevX.8.041015}.
+
+\bibitem{Guillaud_2019}
+\bibinfo{author}{Guillaud, J.} \& \bibinfo{author}{Mirrahimi, M.}
+\newblock \bibinfo{title}{Repetition cat qubits for fault-tolerant quantum
+  computation}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. X}} \textbf{\bibinfo{volume}{9}},
+  \bibinfo{pages}{041053} (\bibinfo{year}{2019}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevX.9.041053}.
+
+\bibitem{Fowler_2019}
+\bibinfo{author}{Fowler, A.~G.} \& \bibinfo{author}{Gidney, C.}
+\newblock \bibinfo{title}{Low overhead quantum computation using lattice
+  surgery} (\bibinfo{year}{2019}).
+\newblock \urlprefix\url{https://arxiv.org/abs/1808.06709}.
+
+\bibitem{cit:janzing}
+\bibinfo{author}{Janzing, D.}, \bibinfo{author}{Wocjan, P.},
+  \bibinfo{author}{Zeier, R.}, \bibinfo{author}{Geiss, R.} \&
+  \bibinfo{author}{Beth, T.}
+\newblock \bibinfo{title}{Thermodynamic cost of reliability and low
+  temperatures: Tightening landauer's principle and the second law}.
+\newblock \emph{\bibinfo{journal}{International Journal of Theoretical
+  Physics}} \textbf{\bibinfo{volume}{39}}, \bibinfo{pages}{2717--2753}
+  (\bibinfo{year}{2000}).
+\newblock \urlprefix\url{https://doi.org/10.1023/A:1026422630734}.
+
+\bibitem{cit:horodecki2013}
+\bibinfo{author}{Horodecki, M.} \& \bibinfo{author}{Oppenheim, J.}
+\newblock \bibinfo{title}{Fundamental limitations for quantum and nanoscale
+  thermodynamics}.
+\newblock \emph{\bibinfo{journal}{Nature Communications}}
+  \textbf{\bibinfo{volume}{4}}, \bibinfo{pages}{2059} (\bibinfo{year}{2013}).
+\newblock \urlprefix\url{https://doi.org/10.1038/ncomms3059}.
+
+\bibitem{Brandao_2015}
+\bibinfo{author}{Brand{\~a}o, F.}, \bibinfo{author}{Horodecki, M.},
+  \bibinfo{author}{Ng, N.}, \bibinfo{author}{Oppenheim, J.} \&
+  \bibinfo{author}{Wehner, S.}
+\newblock \bibinfo{title}{The second laws of quantum thermodynamics}.
+\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
+  Sciences}} \textbf{\bibinfo{volume}{112}}, \bibinfo{pages}{3275--3279}
+  (\bibinfo{year}{2015}).
+\newblock \urlprefix\url{https://www.pnas.org/content/112/11/3275}.
+
+\bibitem{Vinjanampathy_2016}
+\bibinfo{author}{Vinjanampathy, S.} \& \bibinfo{author}{Anders, J.}
+\newblock \bibinfo{title}{Quantum thermodynamics}.
+\newblock \emph{\bibinfo{journal}{Contemporary Physics}}
+  \textbf{\bibinfo{volume}{57}}, \bibinfo{pages}{545--579}
+  (\bibinfo{year}{2016}).
+\newblock \urlprefix\url{https://doi.org/10.1080/00107514.2016.1201896}.
+
+\bibitem{Goold_2016}
+\bibinfo{author}{Goold, J.}, \bibinfo{author}{Huber, M.},
+  \bibinfo{author}{Riera, A.}, \bibinfo{author}{del Rio, L.} \&
+  \bibinfo{author}{Skrzypczyk, P.}
+\newblock \bibinfo{title}{The role of quantum information in
+  thermodynamics{\textemdash}a topical review}.
+\newblock \emph{\bibinfo{journal}{Journal of Physics A: Mathematical and
+  Theoretical}} \textbf{\bibinfo{volume}{49}}, \bibinfo{pages}{143001}
+  (\bibinfo{year}{2016}).
+\newblock \urlprefix\url{https://doi.org/10.1088/1751-8113/49/14/143001}.
+
+\bibitem{cit:lostaglio}
+\bibinfo{author}{Lostaglio, M.}
+\newblock \bibinfo{title}{An introductory review of the resource theory
+  approach to thermodynamics}.
+\newblock \emph{\bibinfo{journal}{Reports on Progress in Physics}}
+  \textbf{\bibinfo{volume}{82}}, \bibinfo{pages}{114001}
+  (\bibinfo{year}{2019}).
+\newblock \urlprefix\url{https://doi.org/10.1088/1361-6633/ab46e5}.
+
+\bibitem{cit:gour}
+\bibinfo{author}{Gour, G.}, \bibinfo{author}{Jennings, D.},
+  \bibinfo{author}{Buscemi, F.}, \bibinfo{author}{Duan, R.} \&
+  \bibinfo{author}{Marvian, I.}
+\newblock \bibinfo{title}{Quantum majorization and a complete set of entropic
+  conditions for quantum thermodynamics} \textbf{\bibinfo{volume}{9}},
+  \bibinfo{pages}{5352} (\bibinfo{year}{2018}).
+\newblock \urlprefix\url{https://doi.org/10.1038/s41467-018-06261-7}.
+
+\bibitem{Ferrie_2008}
+\bibinfo{author}{Ferrie, C.} \& \bibinfo{author}{Emerson, J.}
+\newblock \bibinfo{title}{Frame representations of quantum mechanics and the
+  necessity of negativity in quasi-probability representations}.
+\newblock \emph{\bibinfo{journal}{Journal of Physics A: Mathematical and
+  Theoretical}} \textbf{\bibinfo{volume}{41}}, \bibinfo{pages}{352001}
+  (\bibinfo{year}{2008}).
+\newblock \urlprefix\url{https://doi.org/10.1088/1751-8113/41/35/352001}.
+
+\bibitem{cit:veitch}
+\bibinfo{author}{Veitch, V.}, \bibinfo{author}{Ferrie, C.},
+  \bibinfo{author}{Gross, D.} \& \bibinfo{author}{Emerson, J.}
+\newblock \bibinfo{title}{Negative quasi-probability as a resource for quantum
+  computation}.
+\newblock \emph{\bibinfo{journal}{New Journal of Physics}}
+  \textbf{\bibinfo{volume}{14}}, \bibinfo{pages}{113011}
+  (\bibinfo{year}{2012}).
+\newblock \urlprefix\url{https://doi.org/10.1088/1367-2630/14/11/113011}.
+
+\bibitem{cit:mari}
+\bibinfo{author}{Mari{ }, A.} \& \bibinfo{author}{Eisert, J.}
+\newblock \bibinfo{title}{Positive {W}igner functions render classical
+  simulation of quantum computation efficient}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. Lett.}}
+  \textbf{\bibinfo{volume}{109}}, \bibinfo{pages}{230503}
+  (\bibinfo{year}{2012}).
+\newblock
+  \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.109.230503}.
+
+\bibitem{cit:gottesman}
+\bibinfo{author}{{Gottesman}, D.}
+\newblock \emph{\bibinfo{title}{{Stabilizer codes and quantum error
+  correction}}}.
+\newblock Ph.D. thesis, \bibinfo{school}{California Institute of Technology}
+  (\bibinfo{year}{1997}).
+\newblock \urlprefix\url{https://arxiv.org/abs/quant-ph/9705052}.
+
+\bibitem{cit:knill}
+\bibinfo{author}{Knill, E.}
+\newblock \bibinfo{title}{Quantum computing with realistically noisy devices}.
+\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{434}},
+  \bibinfo{pages}{39–44} (\bibinfo{year}{2005}).
+\newblock \urlprefix\url{https://doi.org/10.1038/nature03350}.
+
+\bibitem{Campbell_2011}
+\bibinfo{author}{Campbell, E.~T.}
+\newblock \bibinfo{title}{Catalysis and activation of magic states in
+  fault-tolerant architectures}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. A}} \textbf{\bibinfo{volume}{83}},
+  \bibinfo{pages}{032317} (\bibinfo{year}{2011}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.83.032317}.
+
+\bibitem{cit:marshall}
+\bibinfo{author}{Marshall, A.~W.}, \bibinfo{author}{Olkin, I.} \&
+  \bibinfo{author}{Arnold, B.~C.}
+\newblock \emph{\bibinfo{title}{Inequalities: Theory of Majorization and Its
+  Applications}} (\bibinfo{publisher}{Springer}, \bibinfo{year}{2011}).
+
+\bibitem{Veinott_1971}
+\bibinfo{author}{Veinott, A.~F.}
+\newblock \bibinfo{title}{Least d-majorized network flows with inventory and
+  statistical applications}.
+\newblock \emph{\bibinfo{journal}{Management Science}}
+  \textbf{\bibinfo{volume}{17}}, \bibinfo{pages}{547--567}
+  (\bibinfo{year}{1971}).
+\newblock \urlprefix\url{https://doi.org/10.1287/mnsc.17.9.547}.
+
+\bibitem{Ruch_1976}
+\bibinfo{author}{Ruch, E.} \& \bibinfo{author}{Mead, A.}
+\newblock \bibinfo{title}{The principle of increasing mixing character and some
+  of its consequences}.
+\newblock \emph{\bibinfo{journal}{Theoretica chimica acta}}
+  \textbf{\bibinfo{volume}{41}}, \bibinfo{pages}{95--117}
+  (\bibinfo{year}{1976}).
+\newblock \urlprefix\url{https://doi.org/10.1007/BF01178071}.
+
+\bibitem{Fine_1982}
+\bibinfo{author}{Fine, A.}
+\newblock \bibinfo{title}{Hidden variables, joint probability, and the bell
+  inequalities}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. Lett.}}
+  \textbf{\bibinfo{volume}{48}}, \bibinfo{pages}{291--295}
+  (\bibinfo{year}{1982}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.48.291}.
+
+\bibitem{Allahverdyan_2018}
+\bibinfo{author}{Allahverdyan, A.~E.} \& \bibinfo{author}{Danageozian, A.}
+\newblock \bibinfo{title}{Excluding joint probabilities from quantum theory}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. A}} \textbf{\bibinfo{volume}{97}},
+  \bibinfo{pages}{030102} (\bibinfo{year}{2018}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.97.030102}.
+
+\bibitem{arvidsson_2020}
+\bibinfo{author}{Arvidsson-Shukur, D. R.~M.} \emph{et~al.}
+\newblock \bibinfo{title}{Quantum advantage in postselected metrology}.
+\newblock \emph{\bibinfo{journal}{Nature Communications}}
+  \textbf{\bibinfo{volume}{11}}, \bibinfo{pages}{3775} (\bibinfo{year}{2020}).
+\newblock \urlprefix\url{https://www.nature.com/articles/s41467-020-17559-w}.
+
+\bibitem{halpern_2018}
+\bibinfo{author}{Yunger~Halpern, N.}, \bibinfo{author}{Swingle, B.} \&
+  \bibinfo{author}{Dressel, J.}
+\newblock \bibinfo{title}{Quasiprobability behind the out-of-time-ordered
+  correlator}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. A}} \textbf{\bibinfo{volume}{97}},
+  \bibinfo{pages}{042105} (\bibinfo{year}{2018}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.97.042105}.
+
+\bibitem{Lostaglio_2018}
+\bibinfo{author}{Lostaglio, M.}
+\newblock \bibinfo{title}{Quantum fluctuation theorems, contextuality, and work
+  quasiprobabilities}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. Lett.}}
+  \textbf{\bibinfo{volume}{120}}, \bibinfo{pages}{040602}
+  (\bibinfo{year}{2018}).
+\newblock
+  \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.120.040602}.
+
+\bibitem{Levy_2020}
+\bibinfo{author}{Levy, A.} \& \bibinfo{author}{Lostaglio, M.}
+\newblock \bibinfo{title}{Quasiprobability distribution for heat fluctuations
+  in the quantum regime}.
+\newblock \emph{\bibinfo{journal}{PRX Quantum}} \textbf{\bibinfo{volume}{1}},
+  \bibinfo{pages}{010309} (\bibinfo{year}{2020}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PRXQuantum.1.010309}.
+
+\bibitem{cit:veitch2}
+\bibinfo{author}{Veitch, V.}, \bibinfo{author}{Mousavian, S. A.~H.},
+  \bibinfo{author}{Gottesman, D.} \& \bibinfo{author}{Emerson, J.}
+\newblock \bibinfo{title}{The resource theory of stabilizer quantum
+  computation}.
+\newblock \emph{\bibinfo{journal}{New Journal of Physics}}
+  \textbf{\bibinfo{volume}{16}}, \bibinfo{pages}{013009}
+  (\bibinfo{year}{2014}).
+\newblock \urlprefix\url{https://doi.org/10.1088/F1367-2630/16/1/013009}.
+
+\bibitem{Wang_2020}
+\bibinfo{author}{Wang, X.}, \bibinfo{author}{Wilde, M.~M.} \&
+  \bibinfo{author}{Su, Y.}
+\newblock \bibinfo{title}{Efficiently computable bounds for magic state
+  distillation}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. Lett.}}
+  \textbf{\bibinfo{volume}{124}}, \bibinfo{pages}{090505}
+  (\bibinfo{year}{2020}).
+\newblock
+  \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.124.090505}.
+
+\bibitem{Gross2006}
+\bibinfo{author}{Gross, D.}
+\newblock \bibinfo{title}{Hudson’s theorem for finite-dimensional quantum
+  systems}.
+\newblock \emph{\bibinfo{journal}{Journal of Mathematical Physics}}
+  \textbf{\bibinfo{volume}{47}}, \bibinfo{pages}{122107}
+  (\bibinfo{year}{2006}).
+\newblock \urlprefix\url{https://aip.scitation.org/doi/10.1063/1.2393152}.
+
+\bibitem{Wigner_1932}
+\bibinfo{author}{Wigner, E.}
+\newblock \bibinfo{title}{On the quantum correction for thermodynamic
+  equilibrium}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev.}} \textbf{\bibinfo{volume}{40}},
+  \bibinfo{pages}{749--759} (\bibinfo{year}{1932}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRev.40.749}.
+
+\bibitem{Vourdas_2004}
+\bibinfo{author}{Vourdas, A.}
+\newblock \bibinfo{title}{Quantum systems with finite hilbert space}.
+\newblock \emph{\bibinfo{journal}{Reports on Progress in Physics}}
+  \textbf{\bibinfo{volume}{67}}, \bibinfo{pages}{267--320}
+  (\bibinfo{year}{2004}).
+\newblock \urlprefix\url{https://doi.org/10.1088/0034-4885/67/3/r03}.
+
+\bibitem{Kenfack_2004}
+\bibinfo{author}{Kenfack, A.} \& \bibinfo{author}{{\.{Z}}yczkowski, K.}
+\newblock \bibinfo{title}{Negativity of the {W}igner function as an indicator
+  of non-classicality}.
+\newblock \emph{\bibinfo{journal}{Journal of Optics B: Quantum and
+  Semiclassical Optics}} \textbf{\bibinfo{volume}{6}},
+  \bibinfo{pages}{396--404} (\bibinfo{year}{2004}).
+\newblock \urlprefix\url{https://doi.org/10.1088/1464-4266/6/10/003}.
+
+\bibitem{Appleby_2005}
+\bibinfo{author}{Appleby, D.~M.}
+\newblock \bibinfo{title}{Symmetric informationally complete–positive
+  operator valued measures and the extended clifford group}.
+\newblock \emph{\bibinfo{journal}{Journal of Mathematical Physics}}
+  \textbf{\bibinfo{volume}{46}}, \bibinfo{pages}{052107}
+  (\bibinfo{year}{2005}).
+\newblock \urlprefix\url{https://doi.org/10.1063/1.1896384}.
+
+\bibitem{Mermin_1990}
+\bibinfo{author}{Mermin, N.~D.}
+\newblock \bibinfo{title}{Simple unified form for the major no-hidden-variables
+  theorems}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. Lett.}}
+  \textbf{\bibinfo{volume}{65}}, \bibinfo{pages}{3373--3376}
+  (\bibinfo{year}{1990}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.65.3373}.
+
+\bibitem{Raussendorf_qubits}
+\bibinfo{author}{Raussendorf, R.}, \bibinfo{author}{Bermejo-Vega, J.},
+  \bibinfo{author}{Tyhurst, E.}, \bibinfo{author}{Okay, C.} \&
+  \bibinfo{author}{Zurel, M.}
+\newblock \bibinfo{title}{Phase-space-simulation method for quantum computation
+  with magic states on qubits}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. A}}
+  \textbf{\bibinfo{volume}{101}}, \bibinfo{pages}{012350}
+  (\bibinfo{year}{2020}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.101.012350}.
+
+\bibitem{Folland_1989}
+\bibinfo{author}{Folland, G.~B.}
+\newblock \emph{\bibinfo{title}{Harmonic Analysis in Phase Space}}
+  (\bibinfo{publisher}{Princeton University Press}, \bibinfo{year}{1989}).
+\newblock \urlprefix\url{https://www.jstor.org/stable/j.ctt1b9rzs2}.
+
+\bibitem{Bengtsson_2006}
+\bibinfo{author}{Bengtsson, I.} \& \bibinfo{author}{{\.{Z}}yczkowski, K.}
+\newblock \emph{\bibinfo{title}{Geometry of Quantum States: An Introduction to
+  Quantum Entanglement}} (\bibinfo{publisher}{Cambridge University Press},
+  \bibinfo{year}{2006}).
+
+\bibitem{schmid2021noncontextual}
+\bibinfo{author}{Schmid, D.}, \bibinfo{author}{Du, H.}, \bibinfo{author}{Selby,
+  J.~H.} \& \bibinfo{author}{Pusey, M.~F.}
+\newblock \bibinfo{title}{The only noncontextual model of the stabilizer
+  subtheory is {G}ross's} (\bibinfo{year}{2021}).
+\newblock \urlprefix\url{https://arxiv.org/abs/2101.06263}.
+
+\bibitem{watrous_2018}
+\bibinfo{author}{Watrous, J.}
+\newblock \emph{\bibinfo{title}{The Theory of Quantum Information}}
+  (\bibinfo{publisher}{Cambridge University Press}, \bibinfo{year}{2018}).
+
+\bibitem{Blackwell_1953}
+\bibinfo{author}{Blackwell, D.}
+\newblock \bibinfo{title}{{Equivalent Comparisons of Experiments}}.
+\newblock \emph{\bibinfo{journal}{The Annals of Mathematical Statistics}}
+  \textbf{\bibinfo{volume}{24}}, \bibinfo{pages}{265 -- 272}
+  (\bibinfo{year}{1953}).
+\newblock \urlprefix\url{https://doi.org/10.1214/aoms/1177729032}.
+
+\bibitem{Nielsen_1999}
+\bibinfo{author}{Nielsen, M.~A.}
+\newblock \bibinfo{title}{Conditions for a class of entanglement
+  transformations}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. Lett.}}
+  \textbf{\bibinfo{volume}{83}}, \bibinfo{pages}{436--439}
+  (\bibinfo{year}{1999}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.83.436}.
+
+\bibitem{cit:cwiklinski}
+\bibinfo{author}{\ifmmode \acute{C}\else \'{C}\fi{}wikli\ifmmode~\acute{n}\else
+  \'{n}\fi{}ski, P.}, \bibinfo{author}{Studzi\ifmmode~\acute{n}\else
+  \'{n}\fi{}ski, M.}, \bibinfo{author}{Horodecki, M.} \&
+  \bibinfo{author}{Oppenheim, J.}
+\newblock \bibinfo{title}{Limitations on the evolution of quantum coherences:
+  Towards fully quantum second laws of thermodynamics}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. Lett.}}
+  \textbf{\bibinfo{volume}{115}}, \bibinfo{pages}{210403}
+  (\bibinfo{year}{2015}).
+\newblock
+  \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.115.210403}.
+
+\bibitem{cit:lostaglio2}
+\bibinfo{author}{Lostaglio, M.}, \bibinfo{author}{Jennings, D.} \&
+  \bibinfo{author}{Rudolph, T.}
+\newblock \bibinfo{title}{Description of quantum coherence in thermodynamic
+  processes requires constraints beyond free energy}.
+\newblock \emph{\bibinfo{journal}{Nature Communications}}
+  \textbf{\bibinfo{volume}{6}}, \bibinfo{pages}{6383} (\bibinfo{year}{2015}).
+\newblock \urlprefix\url{https://doi.org/10.1038/ncomms7383}.
+
+\bibitem{cit:gour2}
+\bibinfo{author}{Gour, G.}, \bibinfo{author}{M{\"u}ller, M.~P.},
+  \bibinfo{author}{Narasimhachar, V.}, \bibinfo{author}{Spekkens, R.~W.} \&
+  \bibinfo{author}{Yunger~Halpern, N.}
+\newblock \bibinfo{title}{The resource theory of informational nonequilibrium
+  in thermodynamics}.
+\newblock \emph{\bibinfo{journal}{Physics Reports}}
+  \textbf{\bibinfo{volume}{583}}, \bibinfo{pages}{1--58}
+  (\bibinfo{year}{2015}).
+\newblock \urlprefix\url{https://doi.org/10.1016/j.physrep.2015.04.003}.
+
+\bibitem{Horodecki_2003}
+\bibinfo{author}{Horodecki, M.}, \bibinfo{author}{Horodecki, P.} \&
+  \bibinfo{author}{Oppenheim, J.}
+\newblock \bibinfo{title}{Reversible transformations from pure to mixed states
+  and the unique measure of information}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. A}} \textbf{\bibinfo{volume}{67}},
+  \bibinfo{pages}{062104} (\bibinfo{year}{2003}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.67.062104}.
+
+\bibitem{Puchala_2013}
+\bibinfo{author}{Pucha{\l}a, Z.}, \bibinfo{author}{Rudnicki, {\L}.} \&
+  \bibinfo{author}{{\.{Z}}yczkowski, K.}
+\newblock \bibinfo{title}{Majorization entropic uncertainty relations}.
+\newblock \emph{\bibinfo{journal}{Journal of Physics A: Mathematical and
+  Theoretical}} \textbf{\bibinfo{volume}{46}}, \bibinfo{pages}{272002}
+  (\bibinfo{year}{2013}).
+\newblock \urlprefix\url{https://doi.org/10.1088/1751-8113/46/27/272002}.
+
+\bibitem{Vallejos_2021}
+\bibinfo{author}{Vallejos, R.~O.}, \bibinfo{author}{de~Melo, F.} \&
+  \bibinfo{author}{Carlo, G.~G.}
+\newblock \bibinfo{title}{Principle of majorization: Application to random
+  quantum circuits}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. A}}
+  \textbf{\bibinfo{volume}{104}}, \bibinfo{pages}{012602}
+  (\bibinfo{year}{2021}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.104.012602}.
+
+\bibitem{ruch_mixing_1978}
+\bibinfo{author}{Ruch, E.}, \bibinfo{author}{Schranner, R.} \&
+  \bibinfo{author}{Seligman, T.~H.}
+\newblock \bibinfo{title}{The mixing distance}.
+\newblock \emph{\bibinfo{journal}{The Journal of Chemical Physics}}
+  \textbf{\bibinfo{volume}{69}}, \bibinfo{pages}{386--392}
+  (\bibinfo{year}{1978}).
+\newblock \urlprefix\url{https://aip.scitation.org/doi/10.1063/1.436364}.
+
+\bibitem{Renes_2016}
+\bibinfo{author}{Renes, J.~M.}
+\newblock \bibinfo{title}{Relative submajorization and its use in quantum
+  resource theories}.
+\newblock \emph{\bibinfo{journal}{Journal of Mathematical Physics}}
+  \textbf{\bibinfo{volume}{57}}, \bibinfo{pages}{122202}
+  (\bibinfo{year}{2016}).
+\newblock \urlprefix\url{https://aip.scitation.org/doi/10.1063/1.4972295}.
+
+\bibitem{Buscemi_2017}
+\bibinfo{author}{Buscemi, F.} \& \bibinfo{author}{Gour, G.}
+\newblock \bibinfo{title}{Quantum relative lorenz curves}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. A}} \textbf{\bibinfo{volume}{95}},
+  \bibinfo{pages}{012110} (\bibinfo{year}{2017}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.95.012110}.
+
+\bibitem{Rethinasamy_2020}
+\bibinfo{author}{Rethinasamy, S.} \& \bibinfo{author}{Wilde, M.~M.}
+\newblock \bibinfo{title}{Relative entropy and catalytic relative
+  majorization}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. Research}}
+  \textbf{\bibinfo{volume}{2}}, \bibinfo{pages}{033455} (\bibinfo{year}{2020}).
+\newblock
+  \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevResearch.2.033455}.
+
+\bibitem{cit:brouwer}
+\bibinfo{author}{Brouwer, L. E.~J.}
+\newblock \bibinfo{title}{{\"U}ber abbildung von mannigfaltigkeiten}.
+\newblock \emph{\bibinfo{journal}{Mathematische Annalen}}
+  \textbf{\bibinfo{volume}{71}} (\bibinfo{year}{1911}).
+\newblock \urlprefix\url{https://doi.org/10.1007/BF01456931}.
+
+\bibitem{cit:prakash2}
+\bibinfo{author}{Jain, A.} \& \bibinfo{author}{Prakash, S.}
+\newblock \bibinfo{title}{Qutrit and ququint magic states}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. A}}
+  \textbf{\bibinfo{volume}{102}}, \bibinfo{pages}{042409}
+  (\bibinfo{year}{2020}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.102.042409}.
+
+\bibitem{hudson_locally_1976}
+\bibinfo{author}{Hudson, R.~L.} \& \bibinfo{author}{Moody, G.~R.}
+\newblock \bibinfo{title}{Locally normal symmetric states and an analogue of de
+  finetti's theorem}.
+\newblock \emph{\bibinfo{journal}{Zeitschrift für Wahrscheinlichkeitstheorie
+  und Verwandte Gebiete}} \textbf{\bibinfo{volume}{33}},
+  \bibinfo{pages}{343--351} (\bibinfo{year}{1976}).
+\newblock \urlprefix\url{https://doi.org/10.1007/BF00534784}.
+
+\bibitem{christandl_2007}
+\bibinfo{author}{Christandl, M.}, \bibinfo{author}{König, R.},
+  \bibinfo{author}{Mitchison, G.} \& \bibinfo{author}{Renner, R.}
+\newblock \bibinfo{title}{One-and-a-half quantum de finetti theorems}.
+\newblock \emph{\bibinfo{journal}{Communications in Mathematical Physics}}
+  \textbf{\bibinfo{volume}{273}}, \bibinfo{pages}{473--498}
+  (\bibinfo{year}{2007}).
+\newblock \urlprefix\url{https://doi.org/10.1007/s00220-007-0189-3}.
+
+\bibitem{muller_2015}
+\bibinfo{author}{Lostaglio, M.}, \bibinfo{author}{M\"uller, M.~P.} \&
+  \bibinfo{author}{Pastena, M.}
+\newblock \bibinfo{title}{Stochastic independence as a resource in small-scale
+  thermodynamics}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. Lett.}}
+  \textbf{\bibinfo{volume}{115}}, \bibinfo{pages}{150402}
+  (\bibinfo{year}{2015}).
+\newblock
+  \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.115.150402}.
+
+\bibitem{muller_2016}
+\bibinfo{author}{M{\"u}ller, M.~P.} \& \bibinfo{author}{Pastena, M.}
+\newblock \bibinfo{title}{A generalization of majorization that characterizes
+  shannon entropy}.
+\newblock \emph{\bibinfo{journal}{IEEE Transactions on Information Theory}}
+  \textbf{\bibinfo{volume}{62}}, \bibinfo{pages}{1711--1720}
+  (\bibinfo{year}{2016}).
+\newblock \urlprefix\url{https://ieeexplore.ieee.org/document/7404001}.
+
+\bibitem{muller_2019}
+\bibinfo{author}{Boes, P.}, \bibinfo{author}{Eisert, J.},
+  \bibinfo{author}{Gallego, R.}, \bibinfo{author}{M\"uller, M.~P.} \&
+  \bibinfo{author}{Wilming, H.}
+\newblock \bibinfo{title}{Von neumann entropy from unitarity}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. Lett.}}
+  \textbf{\bibinfo{volume}{122}}, \bibinfo{pages}{210402}
+  (\bibinfo{year}{2019}).
+\newblock
+  \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.122.210402}.
+
+\bibitem{Pathria_1997}
+\bibinfo{author}{Pathria, R.~K.} \& \bibinfo{author}{Beale, P.~D.}
+\newblock \emph{\bibinfo{title}{Statistical Mechanics}}
+  (\bibinfo{publisher}{Elsevier}, \bibinfo{year}{2011}).
+\newblock
+  \urlprefix\url{https://www.sciencedirect.com/book/9780123821881/statistical-mechanics}.
+
+\bibitem{bombin2021interleaving}
+\bibinfo{author}{Bombin, H.} \emph{et~al.}
+\newblock \bibinfo{title}{Interleaving: Modular architectures for
+  fault-tolerant photonic quantum computing} (\bibinfo{year}{2021}).
+\newblock \urlprefix\url{https://arxiv.org/abs/2103.08612}.
+
+\bibitem{bogolyubov_1966}
+\bibinfo{author}{{Bogolubov}, J., N.~N.}
+\newblock \bibinfo{title}{On model dynamical systems in statistical mechanics}.
+\newblock \emph{\bibinfo{journal}{Physica}} \textbf{\bibinfo{volume}{32}},
+  \bibinfo{pages}{933--944} (\bibinfo{year}{1966}).
+\newblock \urlprefix\url{https://doi.org/10.1016/0031-8914(66)90024-3}.
+
+\bibitem{faist_2015}
+\bibinfo{author}{Faist, P.}, \bibinfo{author}{Oppenheim, J.} \&
+  \bibinfo{author}{Renner, R.}
+\newblock \bibinfo{title}{Gibbs-preserving maps outperform thermal operations
+  in the quantum regime}.
+\newblock \emph{\bibinfo{journal}{New Journal of Physics}}
+  \textbf{\bibinfo{volume}{17}}, \bibinfo{pages}{043003}
+  (\bibinfo{year}{2015}).
+\newblock
+  \urlprefix\url{https://iopscience.iop.org/article/10.1088/1367-2630/17/4/043003}.
+
+\bibitem{renyi_1960}
+\bibinfo{author}{R{\'e}nyi, A.}
+\newblock \bibinfo{title}{On measures of entropy and information}.
+\newblock \emph{\bibinfo{journal}{Proceedings of the 4th Berkeley Symposium on
+  Mathematics, Statistics and Probability}} \textbf{\bibinfo{volume}{1}},
+  \bibinfo{pages}{547--561} (\bibinfo{year}{1960}).
+\newblock
+  \urlprefix\url{https://digitalassets.lib.berkeley.edu/math/ucb/text/math_s4_v1_article-27.pdf}.
+
+\bibitem{rio_thermodynamic_2011}
+\bibinfo{author}{Rio, L.~d.},
+  \bibinfo{author}{{$\text{\normalfont\ring{A}}$}berg, J.},
+  \bibinfo{author}{Renner, R.}, \bibinfo{author}{Dahlsten, O.} \&
+  \bibinfo{author}{Vedral, V.}
+\newblock \bibinfo{title}{The thermodynamic meaning of negative entropy}.
+\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{474}},
+  \bibinfo{pages}{61--63} (\bibinfo{year}{2011}).
+\newblock \urlprefix\url{https://www.nature.com/articles/nature10123}.
+
+\bibitem{baez2011renyi}
+\bibinfo{author}{Baez, J.~C.}
+\newblock \bibinfo{title}{R{\'e}nyi entropy and free energy}
+  (\bibinfo{year}{2011}).
+\newblock \urlprefix\url{https://arxiv.org/abs/1102.2098}.
+
+\bibitem{domb2000phase}
+\bibinfo{author}{Domb, C.}
+\newblock \emph{\bibinfo{title}{Phase transitions and critical phenomena}}
+  (\bibinfo{publisher}{Elsevier}, \bibinfo{year}{2000}).
+\newblock
+  \urlprefix\url{https://www.elsevier.com/books/phase-transitions-and-critical-phenomena/domb/978-0-12-220318-3}.
+
+\bibitem{Gour_2020}
+\bibinfo{author}{{Gour}, G.} \& \bibinfo{author}{{Tomamichel}, M.}
+\newblock \bibinfo{title}{Entropy and relative entropy from
+  information-theoretic principles} (\bibinfo{year}{2020}).
+\newblock \urlprefix\url{https://arxiv.org/abs/2006.11164}.
+
+\bibitem{tomamichel2013}
+\bibinfo{author}{Tomamichel, M.}
+\newblock \emph{\bibinfo{title}{A Framework for Non-Asymptotic Quantum
+  Information Theory}}.
+\newblock Ph.D. thesis, \bibinfo{school}{ETH Zurich} (\bibinfo{year}{2012}).
+\newblock \urlprefix\url{https://arxiv.org/abs/1203.2142}.
+
+\bibitem{renner_phd}
+\bibinfo{author}{{Renner}, R.}
+\newblock \emph{\bibinfo{title}{{Security of Quantum Key Distribution}}}.
+\newblock Ph.D. thesis, \bibinfo{school}{Swiss Federal Institute of Technology
+  Zurich} (\bibinfo{year}{2005}).
+\newblock \urlprefix\url{https://arxiv.org/abs/quant-ph/0512258}.
+
+\bibitem{hardy_1952}
+\bibinfo{author}{Hardy, G.} \emph{et~al.}
+\newblock \emph{\bibinfo{title}{Inequalities}} (\bibinfo{publisher}{Cambridge
+  University Press}, \bibinfo{year}{1952}).
+\newblock \urlprefix\url{https://books.google.gr/books?id=t1RCSP8YKt8C}.
+
+\bibitem{giovagnoli_1985}
+\bibinfo{author}{Giovagnoli, A.} \& \bibinfo{author}{Wynn, H.~P.}
+\newblock \bibinfo{title}{G-majorization with applications to matrix
+  orderings}.
+\newblock \emph{\bibinfo{journal}{Linear Algebra and its Applications}}
+  \textbf{\bibinfo{volume}{67}}, \bibinfo{pages}{111--135}
+  (\bibinfo{year}{1985}).
+\newblock
+  \urlprefix\url{https://www.sciencedirect.com/science/article/pii/0024379585901909}.
+
+\bibitem{steerneman_1990}
+\bibinfo{author}{Steerneman, A. G.~M.}
+\newblock \bibinfo{title}{G-majorization, group-induced cone orderings, and
+  reflection groups}.
+\newblock \emph{\bibinfo{journal}{Linear Algebra and its Applications}}
+  \textbf{\bibinfo{volume}{127}}, \bibinfo{pages}{107--119}
+  (\bibinfo{year}{1990}).
+\newblock
+  \urlprefix\url{https://www.sciencedirect.com/science/article/pii/002437959090338D}.
+
+\bibitem{giovagnoli_cyclic_1996}
+\bibinfo{author}{Giovagnoli, A.} \& \bibinfo{author}{Wynn, H.~P.}
+\newblock \bibinfo{title}{Cyclic majorization and smoothing operators}.
+\newblock \emph{\bibinfo{journal}{Linear Algebra and its Applications}}
+  \textbf{\bibinfo{volume}{239}}, \bibinfo{pages}{215--225}
+  (\bibinfo{year}{1996}).
+\newblock
+  \urlprefix\url{https://www.sciencedirect.com/science/article/pii/S0024379596900130}.
+
+\bibitem{eaton_1977}
+\bibinfo{author}{Eaton, M.~L.} \& \bibinfo{author}{Perlman, M.~D.}
+\newblock \bibinfo{title}{{Reflection Groups, Generalized Schur Functions, and
+  the Geometry of Majorization}}.
+\newblock \emph{\bibinfo{journal}{The Annals of Probability}}
+  \textbf{\bibinfo{volume}{5}}, \bibinfo{pages}{829 -- 860}
+  (\bibinfo{year}{1977}).
+\newblock \urlprefix\url{https://doi.org/10.1214/aop/1176995655}.
+
+\bibitem{fukuda2006}
+\bibinfo{author}{Fukuda, M.} \& \bibinfo{author}{Holevo, A.~S.}
+\newblock \bibinfo{title}{On weyl-covariant channels}  (\bibinfo{year}{2006}).
+\newblock \urlprefix\url{http://arxiv.org/abs/quant-ph/0510148}.
+
+\bibitem{Arnold_2000}
+\bibinfo{author}{Arnold, V.~I.}
+\newblock \bibinfo{title}{Symplectic geometry and topology}.
+\newblock \emph{\bibinfo{journal}{Journal of Mathematical Physics}}
+  \textbf{\bibinfo{volume}{41}}, \bibinfo{pages}{3307--3343}
+  (\bibinfo{year}{2000}).
+\newblock \urlprefix\url{https://doi.org/10.1063/1.533315}.
+
+\bibitem{Klitzing_1980}
+\bibinfo{author}{Klitzing, K.~v.}, \bibinfo{author}{Dorda, G.} \&
+  \bibinfo{author}{Pepper, M.}
+\newblock \bibinfo{title}{New method for high-accuracy determination of the
+  fine-structure constant based on quantized hall resistance}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. Lett.}}
+  \textbf{\bibinfo{volume}{45}}, \bibinfo{pages}{494--497}
+  (\bibinfo{year}{1980}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.45.494}.
+
+\bibitem{barnett_1997}
+\bibinfo{author}{Barnett, S.~M.} \& \bibinfo{author}{Radmore, P.~M.}
+\newblock \emph{\bibinfo{title}{Methods in Theoretical Quantum Optics}}.
+\newblock Oxford science publications (\bibinfo{publisher}{Clarendon Press},
+  \bibinfo{year}{1997}).
+\newblock \urlprefix\url{https://books.google.gr/books?id=Hp5z09gPmC8C}.
+
+\end{thebibliography}
 

### 2021-12-20 magic_constraints_supplement.tex
almost all changes for resubmission done

--- 2021-12-15 ms.tex
@@
-\documentclass[pra,
-aps,
+\documentclass[
 twocolumn,
-superscriptaddress,
-groupedaddress,
-nofootinbib,
-reprint
+superscriptaddress
 ]{revtex4-1}
 
-%\usepackage[columnwise,switch,displaymath,mathlines]{lineno}
-%\linenumbers
-
-\input{preamble}
+\usepackage{amsmath,amsfonts, amssymb, amsthm}
+\usepackage{bbm, physics, mathtools}
+\usepackage{graphicx, subfigure}
+\usepackage{enumerate, multirow, makecell}
+\usepackage{xcolor, hyperref}
+
+\newcommand{\revhigh}[1]{{\color{red}#1}}
+\hypersetup{
+	colorlinks=true,  
+	linkcolor=blue,   
+	citecolor=blue,   
+	urlcolor=blue     
+}
+
+\newtheorem{theorem}{Theorem}
+\newtheorem{proposition}[theorem]{Proposition}
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem{innercustomthm}{Theorem}
+\newenvironment{customthm}[1]
+  {\renewcommand\theinnercustomthm{#1}\innercustomthm}
+  {\endinnercustomthm}
+
+\renewcommand{\figurename}{Supplementary Figure}
+\renewcommand{\tablename}{Supplementary Table}
+
+\newcommand{\ent}[2]{S\left( #1 \middle\vert\middle\vert #2 \right)}
+\def\>{\rangle}
+\def\<{\langle}
+
+\def\id{\mathbbm{1}}
+\renewcommand{\tr}{{\rm{tr}}}
+\renewcommand{\det}{{\rm{det}}}
+
+\def\bmeta{\boldsymbol{\eta}}
+\def\bmo{\bm{0}}
+\def\bma{\boldsymbol{a}}
+\let\ring\r
+
+\def\x{\boldsymbol{x}}
+\def\y{\boldsymbol{y}}
+\def\z{\boldsymbol{z}}
+\def\r{\boldsymbol{r}}
+\def\w{\boldsymbol{w}}
+\def\p{\boldsymbol{p}}
+\def\q{\boldsymbol{q}}
+\def\d{\boldsymbol{d}}
+\def\m{\boldsymbol{m}}
+\def\k{\boldsymbol{k}}
+\def\q{\boldsymbol{q}}
+
+\def\A{{\cal A}}
+\def\Z{{\cal Z}}
+\def\H{{\cal H}}
+\def\E{{\cal E}}
+\def\J{{\cal J}}
+\def\R{{\cal R}}
+\def\D{{\cal D}}
+\def\M{{\cal M}}
+\def\F{{\cal F}}
+\renewcommand{\O}{{\cal O}}
+\renewcommand{\P}{{\cal P}}
 
@@
 
-\begin{abstract}
-Magic states are key ingredients in schemes to realize universal fault-tolerant quantum computation.
-Theories of magic states attempt to quantify this computational element via monotones and determine how these states may be efficiently transformed into useful forms.
-Here, we develop a statistical mechanical framework based on majorization to describe Wigner negative magic states for qudits of odd prime dimension processed under Clifford circuits.
-We show that majorization allows us to both quantify disorder in the Wigner representation and derive upper bounds for magic distillation.
-These bounds are shown to be tighter than other bounds, such as from mana and thauma, and can be used to incorporate hardware physics, such as temperature dependence and system Hamiltonians.
-We also show that a subset of single-shot R\'{e}nyi entropies remain well-defined on quasi-distributions, are fully meaningful in terms of data processing and can acquire negative values that signal magic.
-We find that the mana of a magic state is the measure of divergence of these R\'{e}nyi entropies as one approaches the Shannon entropy for Wigner distributions, and discuss how distillation lower bounds could be obtained in this setting.
-This use of majorization for quasi-distributions could find application in other studies of non-classicality, and raises novel questions in the context of classical statistical mechanics.
-\end{abstract}
-
-\preprint{APS/123-QED}
-
-\title{Constraints on magic state protocols from the statistical mechanics of \\Wigner negativity}
-
-\author{Nikolaos Koukoulekidis}
-	\email{nk2314@imperial.ac.uk}
-	\affiliation{Department of Physics, Imperial College London, London SW7 2AZ, UK}
-\author{David Jennings}
-	\affiliation{School of Physics and Astronomy, University of Leeds, Leeds, LS2 9JT, UK}
-	\affiliation{Department of Physics, Imperial College London, London SW7 2AZ, UK}
-
-\date{\today}
-\maketitle
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Introduction}
-\label{sec:intro}
-
-There has been rapid progress towards the goal of a fault-tolerant quantum computer~\cite{campbell_roads_2017, cit:raussendorf, Raussendorf_2013, Nickerson_2014, Nikahd_2017, chao_2018, lin_pieceable_2020, Lin_2020, chamberland_2020, Bourassa_2021}.
-Nevertheless, many challenges remain and there is increasing need for theory to take into account physical limitations of the hardware involved.
-The surface code~\cite{Bravyi_1998, Freedman_2001, Dennis_2002, Raussendorf_2007} is a leading framework for fault-tolerance with very high error thresholds.
-Within this scheme, Clifford unitaries can be implemented in a robust, fault-tolerant way.
-However, due to the Eastin-Knill theorem~\cite{Eastin_2009}, we also know that it is impossible to have a universal set of transversal gates, and although Clifford unitaries can be realized transversally~\cite{Calderbank_1996, Steane_1996}, one needs to find ways around the Eastin-Knill restriction.
-This can be achieved by injecting in quantum states, called magic states, which promote the Clifford group to universal quantum computing~\cite{cit:bravyi}.
-The obstacle to this is that these states are invariably noisy, so protocols involving stabilizer operations must be employed to purify many copies of the magic states and improve the overall performance of the induced quantum gates~\cite{cit:bravyi, Jones_2013, Ogorman_2017}.
-A key question then arises about the overhead on purifying many copies of a magic state into less noisy forms.
-
-To address this, concrete distillation protocols have been developed, such as the Bravyi-Haah qubit protocol that provides a quadratic reduction in noise per cycle~\cite{Bravyi2012}.
-Such distillation rates have been improved in more recent works~\cite{Jones_2013, haah2017magic, Hastings2018, Litinski_2019} and there have been proposals of protocols for qudits of odd dimension~\cite{CampbellAnwar_2012, Anwar_2012, Dawkins_2015, Krishna2019, cit:prakash} as well as of protocols within a full architectural analysis~\cite{chamberland_very_2020, Chamberland2019faulttolerantmagic}.
-There is also analysis of magic protocols from the perspective of magic monotones, which provide upper bounds on distillation rates and find application in the analysis of gate synthesis~\cite{Campbell_2017, Howard_2017, Prakash_2018, Seddon_2021,leone2021renyi}.
-These frameworks for magic view magic states as resource states with respect to a natural class of quantum operations that are considered cheap, or free, such as stabilizer operations~\cite{Gour_2019, cit:ahmadi, cit:seddon, Wang_2019}.
-Beyond quantum computing, recent work has also looked at how magic can be used to analyse many-body physics~\cite{Sarkar_2020} and conformal field theories~\cite{White_2021} as well its connection to contextuality~\cite{Vega_2017, cit:howard2, Zurel_2020, Okay_2021, schmid2020structure, Schmid_2021}.
-
-Work towards fault-tolerance is increasingly bridging the gap between abstract theory and experiment.
-Extensive work is being done on error mitigation~\cite{jones_2012, Li_2017, Temme_2017, Endo_2018, McClean_2017}, and the incorporation of hardware physics into the theoretical models~\cite{Kandala_2019, holmes_resource_2019, Colless_2018, song2018quantum, Bravyi_2021}.
-For example, the XZZX code~\cite{bonilla_ataides_xzzx_2021} is a variant of the surface code that incorporates noise bias explicitly and has been shown to attain the hashing bound of random codes~\cite{Bennett_1996}.
-In this work, we develop a framework to analyse magic state distillation protocols where explicit physics of the system is incorporated in the distillation bounds.
-This is achieved by considering how a given magic state protocol transforms a \emph{pair} of quantum states -- one being a noisy magic state, and the other a stabilizer state that is distinguished by the physics of the system (for example a state at a characteristic temperature, or the maximally mixed state) and acts as a reference state for the protocol.
-The magic distillation bounds can then be expressed in terms of the physics of the reference state (e.g.~free energy changes in the case of temperature).
-Such bounds are of potential interest in assessing how physical features such as temperature, noise biases or fixed-point structure associated with restricted gate-sets constrain distillation protocols~\cite{Tuckett_2019, Aliferis_2008, Stephens_2013, Li_2015, Babbush_2018, Guillaud_2019, Fowler_2019}.
-
-The approach we take is most closely aligned with resource theories of magic, although it differs in key ways.
-We obtain distillation upper bounds without the use of monotones, but instead use tools from statistical mechanics and recent work in single-shot resource theories~\cite{cit:janzing, cit:horodecki2013, Brandao_2015, Vinjanampathy_2016, Goold_2016, cit:lostaglio, cit:gour}.
-Our analysis relies on the discrete Wigner representation of quantum systems, in which all states and operations can be described on a discrete phase space~\cite{Ferrie_2008, Okay_2021}.
-Crucially, we focus on magic states with negativity in their Wigner representation, which is known to be a necessary condition for universality in the state-injection model~\cite{cit:veitch, cit:mari, cit:gottesman, cit:knill, Campbell_2011}.
-However, taking a statistical mechanical perspective in this context raises a problem: the standard Boltzmann entropy is not defined for quasi-distributions.
-We circumvent this obstacle by making use of a more fundamental tool -- majorization theory~\cite{cit:marshall, Veinott_1971, Ruch_1976}.
-To our knowledge majorization of quasi-distributions has not been considered in quantum physics before, and therefore these methods could find application in other studies of non-classicality in quantum systems~\cite{Fine_1982, Allahverdyan_2018, arvidsson_2020, halpern_2018, Lostaglio_2018, Levy_2020}.
-
-\subsection{Overview of our results}
-We begin by describing how stabilizer operations correspond to stochastic maps on a discrete phase space, and how majorization can be applied to constrain magic state transformations (Sec.~\ref{sec:ps}).
-We then consider families of magic protocols with increasing complexity.
-The simplest case we consider is for magic protocols that lead to unital channels (Sec.~\ref{sec:unital}).
-These are a subset of protocols that leave invariant some distinguished state or have some equilibrium fixed-point structure (Sec.~\ref{sec:frag}).
-We then consider protocols that are non-equilibrium processes, but only generate sub-linear correlations that enable a simple description in the thermodynamic limit (Sec.~\ref{sec:stab}), before giving entropic analysis that can be applied more generally (Sec.~\ref{section:entropies}).
-
-The relations between the sets of protocols considered are as follows:
-\begin{align}
-\mbox{Unital} &\subset \mbox{ local fixed-points} \nonumber\\ 
-&\subset \mbox{ sub-linear correlations} \subset \mbox{ general protocols.} \nonumber
-\end{align}
-
-We provide explicit bounds for magic protocols that generate unital channels (Eq.~(\ref{eq:unital-bound})), as well as bounds that incorporate the temperature and Hamiltonian of the system (Theorem~\ref{thm:free-energy}) and discuss extensions to more general scenarios.
-These bounds are shown to be tighter than other bounds such as those that come from mana and thauma (Sec.~\ref{sec:monotones_frag} and Fig.~\ref{fig:distill_bounds}).
-
-We find that the analysis in the presence of negativity displays a range of features that do not appear in classical statistical mechanics, and leads to a picture of Wigner negativity in a quantum circuit being described as non-classical free energy that is processed under stochastic dynamics.
-This is demonstrated by non-monotonic Lorenz curves (Sec.~\ref{sec:lc}), and by single-shot entropies for general Wigner quasi-distributions that are well-defined, obey data-processing under stabilizer operations and can take on negative values (Sec.~\ref{section:entropies}).
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[scale=0.38]{figs/distill_bounds.pdf}
-    \caption{\textbf{Magic distillation bounds from majorization of Wigner quasi-distributions.} The above plot shows distillation upper bounds for qutrits obtained from majorization on unital protocols.
-The constraints are plotted as a function of the depolarizing error $\epsilon$ for a noisy Strange state (Eq.~(\ref{eq:noisysn})).
-The bound $R_\infty$ follows from a Lorenz curve analysis presented in Sec.~\ref{sec:unital}, while the bound $R_{10}$ comes from single-shot entropies on the Wigner quasi-distributions, as discussed in Sec.~\ref{section:entropies}.
-Numerical bounds $R_{\rm{num}}$ are obtained by using the full set of majorization constraints.
-The new bounds $R_\infty$, $R_{10}$, $R_{\rm{num}}$ all provide stricter constraints than mana~\cite{cit:veitch2} and max--thauma $\theta_{\rm{max}}$~\cite{Wang_2020} bounds for noisy Strange states.
-    }
-    \label{fig:distill_bounds}
-\end{figure}
-
-We show that the mana of a quantum state arises as a residue in the $\alpha$--parameter for R\'{e}nyi entropies, and gives the rate of divergence to $-\infty$ as we approach the Shannon entropy of a Wigner distribution (Eq.~(\ref{eq:mana-divergence})).
-Finally, in Sec.~\ref{sec:lower_bounds} we discuss how our approach could be extended to construct explicit lower bounds on distillation that take into account physical constraints.
-
-\section{Phase space representations of quantum states}
-\label{sec:ps}
-
-Central to our construction is the representation of any quantum state or quantum operation on a system of dimension $d$ in terms of quasi-probability representations on a discrete phase space~\cite{cit:gross3, Ferrie_2008}.
-This construction is a discrete version of Wigner representations in quantum optics~\cite{Wigner_1932, Vourdas_2004, Kenfack_2004}.
-
-Consider a $d$--dimensional quantum system with Hilbert space $\H_d$, and let $\{ |0\>, |1\>, \dots , |d-1\>\}$ denote the standard computational basis, defined over $\mathbb{Z}_d = \{ 0, 1, \dots,d-1 \}$.
-On this space, generalised Pauli matrices $X, Z$ can be defined by their respective roles as shift and phase operators, acting on the basis states as follows,
-\begin{align}
-    X \ket{k} &= \ket{k + 1} \label{eq:xpauli}\\
-	Z \ket{k} &= \omega^k \ket{k}. \label{eq:zpauli}
-\end{align}
-Here $\omega \coloneqq e^{2\pi i/d}$ is the $d$-th root of unity and addition is taken modulo $d$.
-From these we can construct a phase space $\cal{P}_d \coloneqq \mathbb{Z}_d \times \mathbb{Z}_d$ that provides a complete representation of the quantum system.
-Given a point $\bmz \coloneqq (q, p)$ we define a displacement operator,
-\begin{equation}\label{eq:ddef}
-    D_{\bmz} \coloneqq \tau^{q p} X^{q} Z^{p},\ 
-\end{equation}
-where the phase factor $\tau \coloneqq -\omega^{1/2}$ ensures unitarity.
-We assume going forward that $d$ is an odd prime~\cite{Appleby_2005}.
-The qubit case $d=2$ is known to have obstacles to using a Wigner representation to quantify magic in terms of negativity~\cite{Mermin_1990, cit:howard2}, although recent work~\cite{Raussendorf_qubits} has shown how to extend the representation to include qubits by enlarging the phase space.
-For a composite system with dimension $d_{\rm tot} = d_1 \dots d_n$ and Hilbert space $\cal{H}_{d_1} \otimes \dots \otimes \cal{H}_{d_n}$, we define displacement operators as
-\begin{equation}\label{eq:composited}
-    D_{\bmz} \coloneqq D_{(q_1, p_1)} \otimes \dots \otimes D_{(q_n, p_n)},
-\end{equation}
-where now we have
-\begin{align*}
-	\bmz &\coloneqq (q_1, \dots, q_n, p_1, \dots, p_n) \in \cal{P}_{d_1} \times \dots \times \cal{P}_{d_n},
-\end{align*}
-to denote the phase space point for the composite system. 
-For simplicity, we assume $n$ copies of a $d$--dimensional system $d_1=d_2 = \cdots = d$, and therefore we have that $\bmz \in \mathbb{Z}_d^{2n}$.
-
-The displacement operators form the Heisenberg-Weyl group~\cite{Folland_1989, Bengtsson_2006} under matrix multiplication modulo phases,
-\begin{equation}\label{eq:gp}
-    {\rm{HW}}_d^n \coloneqq \{ \tau^k D_{\bmz}: k \in \mathbb{Z}_d, \bmz \in \cal{P}_d^n\}.
-\end{equation}
-The Clifford group $ \cal{C}_d^n $ is then defined as the set of unitaries that normalise the Heisenberg-Weyl group~\cite{Appleby_2005}.
-We may define the pure stabilizer states as those states obtained by acting on $|0\>$ with Clifford unitaries~\cite{cit:gross3} and, finally, the full set of stabilizer states as the convex hull of all pure stabilizers, namely all probabilistic mixtures of states of the form $U|0\>\<0|U^\dagger$ where $U$ is Clifford.
-
-\subsection{Wigner representations for quantum states and quantum operations}\label{sec:wigner}
-
-In order to provide a complete decomposition of arbitrary quantum states and quantum operations we now define a basis of Hermitian observables that transforms covariantly under the action of the Clifford group.
-At every point $\bmz \in \P_d$ we define the phase-point operator
-\begin{equation}\label{eq:ax}
-	A_{\bmz} \coloneqq \frac{1}{d} \sum_{\bmy \in \cal{P}_d} \omega^{\eta(\bmz, \bmy)} D_{\bmy}, 
-\end{equation}
-where $\eta(\bmz, \y)$ is the symplectic inner product between any two points $\bmz,\y \in \P_d$, and is given explicitly by
-\begin{equation}
-	\eta(\bmz, \bmy) \coloneqq \bmy^T \begin{pmatrix}
-		0  & \id \\ %\mathbbm{O}_n  & \id_n \\
-		-\id & 0 \\ %-\id_n & \mathbbm{O}_n \\
-	\end{pmatrix} \bmz,
-\end{equation}
-where $0, \id$ denote the $n\times n$ zero and identity matrices.
-
-The phase-point operators form an orthogonal operator basis with respect to the Hilbert-Schmidt inner product, as discussed in Appendix~\ref{app:wigner}.
-Therefore, any quantum state $\rho$ can be expressed as a linear combination of them, $\rho = \sum_{\bmz \in \cal{P}_d} \W[\bmz]{\rho} A_{\bmz}$, where the coefficients $\W{\rho}(\z)$ give the Wigner distribution of state $\rho$,
-\begin{equation}\label{eq:wstate}
-    \W[\bmz]{\rho} \coloneqq \frac{1}{d}\tr[A_{\bmz} \rho].
-\end{equation}
-For any quantum state $\rho$, the Wigner distribution $W_\rho(\bmz)$ is readily seen to be a $d^2$-dimensional quasi-distribution over $\cal{P}_d$.
-More precisely, $W_\rho(\bmz)$ is a real-valued function on $\P_d$ with the normalisation property $\sum_{\bmz} W_\rho(\bmz) = 1$ (see Appendix~\ref{app:wigner} for details).
-Moreover, the above Wigner representation has recently been shown to be the only non-contextual quasi-probability representation of stabilizer theories in odd prime dimensions~\cite{schmid2021noncontextual}.
-
-Any quantum channel $\E$ also admits a Wigner representation.
-If $\E$ maps some quantum system $A$ of dimension $d_A$ to a quantum system $B$ of dimension $d_B$ and $\J(\E) = (id \otimes \E) (|\phi^+\> \<\phi^+|)$, with $|\phi^+\> = d_A^{-1/2} \sum_k |kk\>$, is its associated Choi state~\cite{watrous_2018}, then we can define
-\begin{equation}\label{Wigner-Choi}
-W_{\E}(\y |\bmz) \coloneqq d_A^2 W_{\J(\E)}(\bar{\bmz} \oplus \y),
-\end{equation}
-where $\bar{\bmz} = (q_1, \dots, q_n, -p_1, \dots, -p_n)$ can be viewed as the time-reversed version of $\bmz$ in the discrete phase space, where momenta are reflected while position coordinates remain unchanged.
-
-\subsection{Magic theories for quantum computation}
-\label{sec:mono}
-\begin{figure}[t]
-    \centering
-        \includegraphics[scale=0.3]{figs/protocol_diagram.pdf}
-    \caption{\textbf{Probing magic protocols with reference states.} 
-	A magic protocol (top figure) converts $n$ copies of some noisy magic state $\rho$ with error parameter $\epsilon$ to $m$ copies of some less noisy state $\rho'$ with $\epsilon' < \epsilon$.
-The physics of the protocol can be analysed by considering how it would transform some distinguished reference stabilizer state $\tau^{\otimes n}$ (bottom figure).
-For the case where this reference state is a thermal state at some temperature $T$ our magic distillation bounds are functions of $T$, the error parameters $\epsilon, \epsilon'$, and free energies $F, F'$.
-In addition, a quantity $\phi$ (Eq.~(\ref{eq:phi})) relates the computational and energy bases, and corresponds to the degree to which the Wigner negativity of $\rho$ can be given a sharp energy via the system Hamiltonian.}
-    \label{fig:sketch}
-\end{figure}
-A number of magic theories exist, where magic states are computational resource states with respect to a class of quantum operations that are considered free~\cite{Gour_2019}.
-One natural class of free operations are those obtained from Clifford unitaries, Pauli measurements and the ability to discard quantum systems.
-However, there are also other candidates~\cite{cit:ahmadi, cit:seddon, Wang_2019}.
-
-In any theory of magic, one route to bounding distillation rates is through a \emph{magic monotone}.
-A magic monotone is a real-valued function of any quantum state $M(\rho)$ that is monotonically non-increasing under the free operations of the magic theory.
-More precisely $M(\sigma) \le M(\rho)$ whenever it is possible to convert $\rho$ into $\sigma$ using free operations.
-
-One prominent magic monotone is the \emph{mana} of a state~\cite{cit:veitch2}, defined as
-\begin{equation}
-    \M(\rho) \coloneqq \log (2\hspace{1pt}\sn{\rho}+1),
-\end{equation}
-where the \emph{sum-negativity}~\cite{cit:veitch2} is the sum of the negative components in $\W{\rho}$,
-\begin{equation}
-    \sn{\rho} \coloneqq \sum\limits_{\bmz: \W[\bmz]{\rho} < 0} \abs{\W[\bmz]{\rho}}.
-\end{equation}
-Using the fact that $W_\rho(\z)$ is a normalized quasi-distribution, we can also write $\M(\rho) = \sum_{\z} |W_\rho(\z)|$.
-
-Mana is an additive magic monotone, and the fact that it is non-increasing under free operations provides a constraint on magic state interconvertibility.
-
-In this work we develop bounds that apply to any reasonable magic theory.
-The central idea is to apply majorization theory to the quasi-distributions that arise for magic states.
-In the next section we explain how majorization relates to the free operations in a theory of magic.
-
-\subsection{Stochastic representation of magic protocols}
-\label{sec:struc}
-
-Within the Wigner representation for odd prime dimension, it is well-known that all positively represented states used in Clifford circuits admit an efficient classical simulation~\cite{cit:mari}, so negativity is a necessary resource for universal fault-tolerant quantum computing~\cite{cit:veitch}.
-Therefore, the free states in any magic theory are required to be a subset of
-\begin{equation}
-    \F \coloneqq \{ \rho: \W[\bmz]{\rho} \geq 0 \text{ for all } \bmz \in \cal{P}_d\}.
-\end{equation}
-Our focus is on states with negativity, so the particular choice of free states is not critical for our analysis.
-The remaining component that defines any magic theory is the set of free quantum operations.
-The most basic assumption we require on free operations is that they send any free state to another free state.
-
-Any magic state protocol will correspond to a quantum channel $\E$, so from Eq.~(\ref{Wigner-Choi}) it admits a Wigner representation $W_{\E}(\y | \bmz)$ that acts as a transition matrix mapping phase space points $\bmz \rightarrow \y$.
-The representation obeys the relation
-\begin{equation}
-	W_{\E(\rho)} (\y) = \sum_{\bmz \in \P_d} W_{\E}( \y | \bmz) W_\rho(\bmz),
-\end{equation}
-for any $\rho$.
-Since the magic protocol sends free states to free states, $\E$ sends all positively represented quantum state to other positively represented quantum states.
-In such cases, it can be shown~\cite{Wang_2019} that if $\E$ is a free operation then the associated Wigner representation $W_{\E}(\y |\bmz)$ must form a stochastic matrix.
-In particular, all stabilizer operations correspond to stochastic matrices in the Wigner representation.
-
-We note however, that not all stochastic maps on the phase space correspond to valid quantum operations.
-The reason is that the maps must also respect the symplectic structure of the phase space, which is an additional non-trivial constraint.
-
-In what follows, we shall assume that we have a magic theory $\R = (\F, \O)$ in which the free states $\F$ are represented by non-negative Wigner functions, while the free operations $\O$ are stochastic maps in the Wigner representation.
-Our analysis of magic in this phase space setting makes use of majorization theory, which we describe in the next section.
-
-\subsection{Quantifying disorder without entropies}
-\label{sec:major}
-
-Majorisation~\cite{cit:marshall, Blackwell_1953} is a collection of powerful tools that has found many applications in quantum information theory~\cite{Nielsen_1999, cit:cwiklinski, cit:lostaglio2, cit:gour, cit:gour2, Horodecki_2003, Puchala_2013, Vallejos_2021}.
-It describes the disorder of distributions that undergo stochastic transformations, and in its simplest form defines a pre-order on probability distributions.
-Given two distributions $\p= (p_1, \dots, p_n)$ and $\q = (q_1, \dots, q_n)$ over $n$ outcomes, we say that $\p$ majorizes $\q$, denoted $\p \succ \q$, if there exists a bistochastic map $A = (A_{ij})$ such that $A\p = \q$, where bistochastic means that $A_{ij} \geq 0$ and $\sum_i A_{ij} = \sum_j A_{ij} = 1$.
-It can be shown~\cite{cit:marshall} that the condition $ \p \succ \q$ over probability distributions is equivalent to $n-1$ inequalities, which can be checked efficiently.
-
-There is a natural generalisation, which is called $\bmd$--majorization~\cite{Veinott_1971}, or in the context of thermodynamics, thermo-majorization~\cite{cit:horodecki2013}.
-For a fixed probability distribution $\r = (r_1, \dots, r_n)$ with positive components, we define majorization relative to $\r$ as $\p \succ_{\r} \q$, if and only if there exists a stochastic map $A$ such that $A\r = \r$ and $A \p = \q$.
-The original majorization condition between probability distributions corresponds to the case $\r = (1/n, \dots, 1/n)$.
-
-In fact, we can further generalize to \emph{relative majorization}~\cite{Blackwell_1953, Ruch_1976, ruch_mixing_1978, Renes_2016, Buscemi_2017, Rethinasamy_2020}, defined as an ordering between pairs of vectors and write
-\begin{equation}
-	(\p,\r) \succ (\q, \r')
-\end{equation}
-if and only if there is a stochastic map $A$ such that $A\r = \r'$ and $A\p = \q$. We retrieve $\bmd$--majorization when $\r = \r'$.
-
-\subsection{Quasi-probability majorization and non-monotonic Lorenz curves}
-\label{sec:lc}
-
-Our analysis applies majorization to magic states at the level of the associated Wigner distributions.
-Since these are in general quasi-distributions, it is important to check how majorization is computed for these cases and what differences quasi-distributions bring over genuine probability distributions.
-
-We also make use of the notion of a Lorenz curve of a vector $\w \in \mathbb{R}^n$ relative to some other vector $\r \in \mathbb{R}^n$.
-Given a vector $\w$ we define $\w^\downarrow$ to be the re-arrangement of the components of $\w$ into decreasing order.
-Given two $n$--component vectors $\w$ and $\r$, we first define $\widetilde{\w}=(\widetilde{w}_i)$, where $\widetilde{w}_i \coloneqq w_i/r_i$, as the vector of component-wise ratios between $\w$ and $\r$.
-We can now define the \emph{Lorenz curve} of $\w$ relative to $\r$, denoted $L_{\w|\r}(x)$, as the piece-wise linear function that passes through $(0,0)$ and the $n$ points
-\begin{equation}\label{eq:lc}
-	(x_k,L_{\w|\r}(x_k)) =\left( \frac{1}{R}\sum_{i=1}^k r_{\pi(i)}, \sum_{i=1}^k w_{\pi(i)} \right),
-\end{equation}
-where $R\coloneqq \sum_{i=1}^n r_i$ and $\pi$ is the permutation on $n$ objects mapping $\widetilde{\w}$ to $\widetilde{\w}^{\downarrow}$.
-The form of this requires that $\r$ has no zero components, which we shall assume without loss of generality as the rank of a quantum state is not operationally meaningful.
-
-In the usual case where $\w$ and $\r$ are both probability distributions the Lorenz curve is defined on the interval $[0,1]$, and rises monotonically until it reaches the value $1$ at $x=1$.
-The value $L_{\w|\r}(x) = 1$ is a global maximum.
-Moreover, if $\w, \w', \r, \r'$ are all valid probability distributions with $\r,\r'$ having positive components, then
-\begin{equation*}
-(\w, \r) \succ (\w', \r') \mbox{ if and only if } L_{\w |\r}(x) \ge L_{\w' |\r'}(x),
-\end{equation*}
-for all $x \in [0,1]$. 
-\revhigh{This result is shown in~\cite{ruch_mixing_1978} and we reproduce it in Appendix~\ref{app:rel_quasi}.}
-It provides a simple way of computing whether relative majorization holds between pairs of probability distributions.
-
-However, if $\w$ is a \emph{quasi-probability} distribution with negative values, and $\r$ a regular probability distribution things are different.
-Now the Lorenz curve is no longer monotonically increasing, but is a concave function that breaks through the $L_{\w|\r}(x) = 1$ barrier at an interior point and attains some non-trivial maximum $L_\star$ above the value $1$, before decreasing monotonically to $L_{\w|\r}(x)= 1$ at the end-point $x=1$.
-See Fig.~\ref{fig:lcs} for examples of non-monotonic Lorenz curves for quasi-distributions.
-Within quantum theory, the breaking of this barrier is associated with the degree of non-classicality.
-
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.35]{figs/lc_strange.pdf}
-    \caption{\textbf{A `heretical' family of Lorenz curves.} Traditionally, Lorenz curves for distributions are monotone increasing cumulative functions that reach a maximum value of $1$.
-In contrast, Lorenz curves for magic states break through the value of $L(x)=1$ due to the presence of negativity in the associated quasi-distributions.
-The above family of curves correspond to multiple copies of noisy Strange states $\rho\coloneqq\rho_{\rm{S}}(\epsilon)^{\otimes n}$ (Eq.~(\ref{eq:noisysn})) for $n=2,4,6$ within $\R_{\sigma}$, where $\sigma = \id/3$.
-Solid lines represent pure Strange states, while dashed lines represent $\epsilon$-noisy Strange states with depolarising error $\epsilon = 0.1$.
-    }
-    \label{fig:lcs}
-\end{figure}
-
-Relative majorization is usually considered for probability distributions, so we need to verify that the same Lorenz curve conditions apply to quasi-distributions before proceeding with our analysis.
-This can be done from first principles, but a simpler way to see that this holds is to reduce to the problem of genuine distributions by first `masking' the negativity in the quasi-distribution $\w$ using the reference distribution $\r$ and then applying the conditions for relative majorization.
-This negativity masking then gives the following result.
-
-\begin{theorem}\label{thm:lcquasi}
-	Let $\w \in \mathbb{R}^n,\w'\in \mathbb{R}^m$ be quasi-distributions, and let $\r \in \mathbb{R}^n, \r' \in \mathbb{R}^m$ be probability distributions with non-zero components.
-Then, $(\w, \r) \succ (\w', \r')$ if and only if $L_{\w|\r}(x) \ge L_{\w' |\r'}(x)$ for all $x \in [0,1]$.
-\end{theorem}
-\begin{proof}
-	Since the components of $\r$ are strictly positive, there always exists an $\epsilon >0$ such that $\w_\epsilon \coloneqq \epsilon \w + (1-\epsilon) \r$ is a genuine probability distribution.
-A similar result holds for $\w'$ and $\r'$ and we choose $\epsilon$ sufficiently small so that both $\w_\epsilon$ and $\w_\epsilon'$ are probability distributions.
-We now have that $(\w, \r) \succ (\w', \r')$ if and only if $(\w_\epsilon , \r) \succ (\w_\epsilon', \r')$.
-This equivalence holds because there exists a stochastic map $A$ such that $A \w = \w'$ and $A \r = \r'$ if and only if
-\begin{equation}
-A[\epsilon \w + (1-\epsilon) \r] = \epsilon \w' + (1-\epsilon) \r'\mbox{ and } A\r = \r'.
-\end{equation}
-In terms of a Lorenz curve condition we have that $(\w_\epsilon , \r) \succ (\w_\epsilon', \r')$ if and only if $L_{\w_\epsilon |\r} (x) \ge L_{\w'_\epsilon |\r'} (x)$ for all $x \in [0,1]$. 
-Additionally, we show in \revhigh{Appendix~\ref{app:rel_quasi}} that the Lorenz curve for any quasi-distribution obeys the relation
-\begin{equation}
-L_{a \w + b \r | \r} (x) = a L_{\w|\r} (x) + bx,
-\end{equation}
-for any $a >0$ and $b \in \mathbb{R}$. This relation implies that
-\begin{align*}
-L_{\w_\epsilon |\r} (x) &\ge L_{\w'_\epsilon |\r'} (x) \nonumber \\ 
-&\mbox{ if and only if }& \\
-\epsilon L_{\w |\r} (x) + (1-\epsilon) x &\ge \epsilon L_{\w' |\r'} (x) + (1-\epsilon) x.
-\end{align*}
-Finally, the $(1-\epsilon)x$ terms cancel on both sides and we get the required relative majorization conditions that $(\w, \r) \succ (\w', \r')$ if and only if $L_{\w | \r} (x) \ge L_{\w' | \r'}(x)$ for all $x \in [0,1]$, as required.
-\end{proof}
-
-With this theory in place, we turn to magic distillation protocols.
-
-\section{Magic distillation bounds with fixed-points}
-\label{sec:frag}
-
-We can now consider how majorization constrains magic distillation rates starting in this section with an abstract setting based on the fixed-point structure of the physical operations accessible to us.
-We show that any magic theory can always be decomposed in terms of `sub-theories' with a particular fixed-point structure, which allows the use of $\mathbf{d}$--majorization.
-Later, in Sec.~\ref{sec:stab}, we drop the requirement of fixed-points and instead use the full relative majorization, before giving general entropic constraints in Sec.~\ref{section:entropies}.
-
- We begin by defining the following sub-theory of any magic theory $\R$.
-\begin{definition}\label{def:sigmafrag}
-   Given a theory of magic $\R = (\F, \O)$, we define the sub-theory $\R_\sigma = (\F, \O_\sigma)$, in which the free operations are 
-   \begin{equation}
-        \O_\sigma \coloneqq \{ \E \in \O: \E(\sigma) = \sigma \},
-    \end{equation}
-namely those free operations that leave the distinguished state $\sigma \in \F$ invariant.
-\end{definition}
-This gives a simple way to break up any theory into smaller, more manageable parts, and where the union over all sub-theories returns the parent theory, so we are not discarding any information by breaking up the theory in this way.
-We make this precise as follows.
-\begin{theorem}\label{thm:frag}
-    Let $\R = (\F, \O)$ be a theory of magic.
-Then a transformation $\rho_1 \rightarrow \rho_2$ is possible in $\R$ if and only if the transformation $\rho_1 \rightarrow \rho_2$ is possible in at least one sub-theory $\R_\sigma$.
-\end{theorem}
-The proof of this is straightforward.
-\begin{proof}
-   Suppose the interconversion is possible in a $\R_\sigma$ via some $\E \in \O_\sigma$.
-But since $\O_\sigma \subseteq \O$ it is also possible in $\R$.
-Conversely, suppose the transformation is possible in $\R$ via some $\E$ in $\O$.
-The free states $\F$ are a closed, bounded set and moreover the image of $\F$ under the map $\E$ is in $\F$.
-By the Brouwer fixed-point theorem~\cite{cit:brouwer}, this mapping must therefore have a fixed point $\sigma \in \F$, so $\E \in \O_\sigma$ and the interconversion is possible in $\R_\sigma$.
-\end{proof}
-We can compare with resource monotones, which are also called resource measures.
-A complete set of measures $\{\M_i\}_i$ is such that $\rho \rightarrow \sigma$ if and only if $\M_i(\rho) \ge \M_i(\sigma)$ for all $i$.
-The above set of sub-theories can therefore be viewed as a complete set of ``co-measures'' for the theory, where the parent resource theory's complex pre-order of states is mapped to a simpler pre-order for a particular $\R_\sigma$.
-In the next section we show that a given $\R_\sigma$ can be approximated by a majorization pre-order, and from this we compute magic distillation bounds.
-
-\subsection{Majorisation of Wigner distributions with fixed-point structure}
-\label{sec:major_frag}
-We consider some $\sigma \in \F$, and its corresponding $\R_\sigma$.
-We are interested in the ability to transform many copies of some noisy magic state $\rho$ towards a more pure form of magic.
-The state $\rho$ is assumed to have negativity in the Wigner representation, so $W_\rho(\bmz) < 0$ for some regions of $\bmz \in \P_d$.
-The state $\sigma$ is assumed to have a Wigner distribution with $W_\sigma(\bmz) > 0$ for all $\bmz$ in the phase space\footnote{A non-full rank state $\sigma$ can be handled as a limiting case in which we first add an infinitesimal fraction of depolarising noise $\epsilon (\id/d)$ and then take $\epsilon \rightarrow 0$ in the end.}.
-
-The free operations within the magic theory $\R$ are represented by stochastic maps, and within $\R_\sigma$ by stochastic maps that leave $W_\sigma(\bmz)$ invariant.
-Therefore, a necessary condition for magic state transformations $\rho_1 \rightarrow \rho_2$ within $\R_\sigma$ will be that
-\begin{equation}
-	W_{\rho_1} \succ_{W_{\sigma}} W_{\rho_2},
-\end{equation}
-or put another way, that the quasi-distribution $W_{\rho_1}$ is more ordered than the quasi-distribution $W_{\rho_2}$ relative to $W_\sigma$.
-To simplify notation, we denote by $L_{\rho | \sigma}(x)$ the Lorenz curve $L_{W_{\rho} | W_{\sigma}} (x)$, and therefore have that
-\begin{equation}
-\rho_1 \rightarrow \rho_2 \mbox{ within }\R_\sigma \mbox{ implies } L_{\rho_1 |\sigma} (x) \ge L_{\rho_2 |\sigma} (x),
-\end{equation}
-for all $x \in [0,1]$, which restricts the transformations that are possible.
-
-Note that this is not a single numerical constraint, but a family of constraints.
-For $n$ copies of a qudit system of dimension $d$ the number of terms in $W_{\rho}$ is $d^{2n}$, so imposing the Lorenz curve condition corresponds to exponentially many constraints.
-Before computing explicit examples, in the next section we describe how these majorization constraints relate to other known monotones.
-
-\subsection{Basic monotones for magic distillation for a particular $\R_\sigma$ and the relation to mana}
-\label{sec:monotones_frag}
-
-We state some generic aspects of Lorenz curves for magic states, which allow us to interpret previous magic monotones in a new light.
-The first result gives a simple way to see that the sum-negativity/mana of a magic state is a monotone~\cite{cit:veitch2}.
-
-\begin{theorem} Majorization in any $\R_\sigma$ implies the monotonicity of sum-negativity/mana. 
-\end{theorem}
-\begin{proof}
-	The sum-negativity of a magic state $\rho$ can be written as $sn(\rho) =\frac{1}{2} (\sum_{\bmz} |W_\rho(\bmz) | - 1)$.
-We make use of the $L_1$-norm form of relative majorization, (see Appendix~\ref{app:major}), which states that $\p \succ_{\r} \q$ if and only if
-	\begin{equation}
-\sum_k | p_k - r_k t | \geq \sum_k | q_k - r_k t |,
-\end{equation}
-for all $t\in \mathbb{R}$.
-Choosing $t=0$ we get the single condition that $\sum_k |p_k| \ge |\sum_k |q_k|$, independent of the choice of $\r$.
-Applying this to the Wigner quasi-distributions of two quantum states immediately gives the result.
-\end{proof}
-
-If we have a magic state $\rho$ that has negativity in its Wigner representation, then, as discussed, its Lorenz curve over-shoots $1$ and reaches a non-trivial maximum $L_\star$ that depends on the particular state.
-There is an simple relation between $L_\star$ and sum-negativity/mana, which is provided by the following result.
-\begin{theorem}\label{lem:lcmax}
-	Given a magic state $\rho$, the maximum $L_\star$ of its Lorenz curve $\lc{\rho}{\sigma}(x)$ is independent of the $\R_\sigma$ and equal to $1+\sn{\rho}$.
-Moreover, the majorization constraint is stronger than mana in every $\R_\sigma$.
-\end{theorem}
-The proof of this is given in Appendix~\ref{app:major}.
-Using the Lorenz curve perspective, it is also simple to construct new monotones.
-For example, within a given $\R_\sigma$, the area above the horizontal line $y = 1$ is another magic monotone.
-\begin{theorem}
-Given a magic state $\rho$ and a free state $\sigma$, let $\A_\sigma(\rho)$ be the area of the region $\{(x, y): 1 \leq y \leq L_{\rho | \sigma}(x)\}$.
-Then $\A_\sigma(\rho)$ is a magic monotone for $\R_\sigma$.
-\end{theorem}
-\begin{proof}
-Consider the transformation $\rho_1 \rightarrow \rho_2$ within $\R_\sigma$.
-We have that $L_{\rho_1|\sigma}(x)$ is never below the curve $L_{\rho_2|\sigma}(x)$, and therefore the region above $L=1$ for $\rho_2$ is a subset of the corresponding region for $\rho_1$.
-Thus, $\A_\sigma(\rho_1) \geq \A_\sigma(\rho_2)$, so $\A_\sigma$ is a magic monotone in $\R_\sigma$.
-\end{proof}
-Note though, in contrast to mana, the area monotone is \emph{specific to $\R_\sigma$}, and its value will vary as we change $\sigma$.
-Therefore its monotonicity depends on the physics of the fixed point and provides a means to analyse magic distillation only under free operations that leave $\sigma$ invariant.
-One can also define an area monotone in the more general setting of relative majorization, where one drops the fixed point emphasis as in Sec.~\ref{sec:stab}.
-
-\subsection{Magic distillation bounds for unital protocols}
-\label{sec:unital}
-
-We now construct magic state distillation bounds for protocols that generate \emph{unital} channels, meaning that $\E(\I/d) = \I/d$.
-
-Our approach works for any odd dimension, but for simplicity we consider qutrit magic states ($d=3$), for which a canonical magic state exists with a simple Wigner distribution.
-This is the Strange state $|S\>$, which is given by
-\begin{equation}
-|S\> \coloneqq \frac{1}{\sqrt{2}} (|1\> + |2\>),
-\end{equation}
-in the computational basis.
-Its distribution $W_{|S\>\<S|}(\z)$ has a single negative value of $-1/3$ at $\bmz =(0,0)$ and the positive value $1/6$ at all other points.
-We define the $\epsilon$--noisy Strange state as
-\begin{equation}\label{eq:noisysn}
-    \rho_{\rm{S}}(\epsilon)\coloneqq (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \frac{1}{3}\id,
-\end{equation}
-where $\epsilon$ is the depolarizing error parameter.
-Any magic state $\rho$ can be processed via Clifford operations~\cite{cit:prakash,cit:prakash2} and put into this canonical form for some $\epsilon \ge 0$.
-
-The Wigner distribution of the single-copy, $\epsilon$--noisy Strange state  is given by
-\begin{equation}
-	\W[\bmz]{\rho_{\rm{S}}(\epsilon)} = (1-\epsilon)\W[\bmz]{|\rm{S}\>\<\rm{S}|} + \epsilon\W[\bmz]{\frac{1}{3}\id}.
-\end{equation}
-with a single negative component
-\begin{equation}
-	- v(\epsilon) \coloneqq - \left( \frac{1}{3} -\frac{4}{9}\epsilon \right)
-\end{equation} 
-located at the origin $\bmz = \bmo$ and positive components
-\begin{equation}
-	u(\epsilon) \coloneqq \frac{1}{6} -\frac{1}{18}\epsilon
-\end{equation}
-at the 8 phase space points $\bmz \ne \mathbf{0}$. We assume that $\epsilon < 3/4$ to ensure the presence of negativity in the Wigner distribution.
-
-We now consider the problem of purifying $n$ copies of a noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ into a smaller number of copies $n'$ of a less noisy Strange state $\rho_{\rm{S}}(\epsilon')^{\otimes n'}$, with $\epsilon' < \epsilon$ and $n' \leq n$.
-In particular, we compute the Lorenz curves for the transformation
-\begin{equation}\label{eq:sudist}
-	\rho_{\rm{S}}(\epsilon)^{\otimes n} \longrightarrow \rho_{\rm{S}}(\epsilon')^{\otimes n'}, %\otimes \left( \frac{1}{3}\id \right)^{\otimes (n-n')},
-\end{equation}
-and use them to bound the magic distillation rate $R(\epsilon, \epsilon') \coloneqq n'/n$.
-
-Due to negativity, the ordering of the components of the rescaled Wigner distribution $W_{\rho_n |\sigma_n}(\bmz) \coloneqq W_{\rho_n}(\bmz)/W_{\sigma_n}(\bmz)$, for $\rho_n = \rho_S(\epsilon)^{\otimes n}$, and $\sigma_n = \sigma^{\otimes n}= (\I/3)^{\otimes n}$, depends on whether $-v(\epsilon)$ is raised to an even or odd power.
-Treating the Wigner distributions as vectors, the component values $w_i$ and associated multiplicities $m_i$ in the $n$--copy case are found to be
-\begin{align}
-	m_i &= 8^{i}\binom{n}{i}, \\
-	w_i &= u^{i}(-v)^{n-i}, \label{eq:wigu}
-\end{align}
-where index $i$ runs through $0, \dots, n$, and we assume for simplicity that $n$ is even and $\epsilon \leq 3/7$, which implies that $v \geq u$.
-All details on the analysis are provided in Appendix~\ref{app:lcsu_technical}.
-
-The Lorenz curve $L_{\rho_n|\sigma_n}(x)$ reaches a maximum value of
-\begin{align}\label{eq:lcsu_max}
-	L_\star &\coloneqq L_{\rho_n |\sigma_n} (x_\star) = \sum_{i = 0}^{n/2} m_{2i} w_{2i} \nonumber\\
-	&= \frac{1}{2} + \frac{1}{2}\left(\frac{15 - 8\epsilon}{9}\right)^n > 1,
-\end{align}
-which occurs at $x=x_\star$ given by
-\begin{equation}
-	x_\star = \frac{1}{2} + \frac{1}{2}\left(\frac{7}{9}\right)^n.
-\end{equation}
-
-Distillation bounds can be obtained from any part of the Lorenz curve by imposing the constraint that the Lorenz curve of the input state never dips below the curve of the output.
-One simple constraint can be obtained by considering the initial slopes of the two Lorenz curves.
-
-The coordinates of the first point after the origin for $\rho_S(\epsilon)^{\otimes n}$ are given by $(1/9^n, v(\epsilon)^n)$, while for $\rho_S(\epsilon')^{\otimes n'}$ by $(1/9^{n'}, v(\epsilon')^{n'})$, and by requiring that the initial slope for the input state Lorenz curve is larger than that of the output state (Proposition~\ref{prop:first_elb} in the appendices) we find that
-\begin{equation}\label{eq:unital-bound}
-	R(\epsilon, \epsilon') \leq R_\infty \coloneqq\frac{\log (3-4\epsilon)}{\log (3-4\epsilon')}.
-\end{equation}
-The choice of denoting the bound by $R_\infty$ is explained in Sec.~\ref{section:entropies} in relation to single-shot entropies.
-For the limiting case of pure magic states on the output ($\epsilon'=0$), this simplifies to
-\begin{equation}
-	R \leq 1 + \frac{\log (1 - \frac{4}{3} \epsilon)}{\log 3}.
-\end{equation}
-We compare this to other known distillation bounds coming from mana and thauma. The mana bound can be directly calculated as
-\begin{equation}
-	R \leq \frac{\M(\rho_{\rm{S}}(\epsilon))}{\M(\rho_{\rm{S}}(0))} = 1 + \frac{\log \left(1 - \frac{8}{15}\epsilon \right)}{\log \frac{5}{3}}.
-\end{equation}
-The max--thauma~\cite{Wang_2020} is defined as
-\begin{equation}
-	\theta_{\rm{max}}(\rho) \coloneqq \log \min{\{2\hspace{1pt}\sn{V}+1 : V \geq \rho\}}
-\end{equation}
-and can be calculated numerically via a semi-definite program.
-For the noisy Strange state, the max--thauma bound coincides with the mana bound, and we find that they are both looser than the majorization bound $R_\infty$ as shown in Fig.~\ref{fig:distill_bounds}.
-
-This figure includes numerical estimates of the optimal majorization bounds $R_{\rm{num}}$ obtained by considering the full Lorenz curve, which show that the bound $R_\infty$ can be further improved.
-
-\section{Temperature-dependent bounds for magic state distillation protocols}
-\label{sec:stab}
-
-We now show how relative majorization can incorporate the system's Hamiltonian into magic distillation bounds.
-The way we do this is by considering how the protocol would disturb a reference equilibrium state $\tau$ to some different state $\tau'$, if the protocol had been applied to this reference state instead of the actual $n$-copy magic state.
-
-We consider a magic distillation protocol on multiple identical qudits in a noisy magic state $\rho(\epsilon)$, with noise parameter $\epsilon$, sending 
-\begin{equation}
-\rho(\epsilon)^{\otimes n} \longrightarrow \E(\rho(\epsilon)^{\otimes n}) =\rho(\epsilon')^{\otimes m}
-\end{equation}
-with $n \gg 1$, $\epsilon' <\epsilon$ and $\E$ denoting the quantum channel induced by the protocol.
-We also assume each qudit has a Hamiltonian $H$ and neglect interaction terms.
-We choose some temperature $T = (k\beta)^{-1}$ where $k$ is Boltzmann's constant and $\beta$ the inverse temperature.
-The reference equilibrium state of the $n$ qudits is given by
-\begin{equation}
-\tau^{\otimes n} = \left ( \frac{e^{-\beta H}}{\Z} \right )  ^{\otimes n}.
-\end{equation}
-We may also assume that the reference state $\tau$ is not a magic state, and has a strictly positive Wigner distribution $W_\tau(\bmz)$.
-
-A given magic protocol on the $n$ qudits will correspond to a quantum channel $\E$.
-We also assume for simplicity that $U_\pi\E(X) U_\pi^\dagger = \E(X)$ for all $X$ and any permutation $U_\pi$ of the $m$ output subsystems.
-This is justified because the protocol on the input magic state results in state $\rho(\epsilon')^{\otimes m}$, which is invariant under permutations.
-Therefore, we are always allowed to symmetrize the output $\E(X)$ by performing a group average over the permutation group for the output systems without changing the performance of the distillation protocol on $\rho(\epsilon)^{\otimes n}$.
-Thus, we can assume that $\E$ always outputs a symmetric state in general.
-This means that $\E(\tau^{\otimes n})$ is a symmetric state on $m$ subsystems, so by the quantum de Finetti theorem~\cite{hudson_locally_1976, christandl_2007} we have that for $m \gg 1$
-\begin{equation}
-\E(\tau) \approx \int d\mu(x) \tau_x^{\prime \otimes m},
-\end{equation}
-where $d\mu(x)$ is a probability measure over a set $\{\tau'_x\}$ of single qudit states.
-
-\subsection{Free energy and sub-linear correlations in the thermodynamic limit}
-To keep our analysis simple we make the following physical assumption.
-We assume that in the asymptotic/thermodynamic limit $n,m \rightarrow \infty$ the correlations generated on the reference equilibrium state are negligible.
-This implies that $d\mu(x)$ is peaked on a particular state $\tau'$, and $\E(\tau^{\otimes n}) \approx \tau'^{\otimes m}$.
-This scenario occurs in the context of traditional thermodynamics, and states that the output system is well-described by intrinsic variables that do not scale in $m$, and correlations are sub-linear in $m$.
-In particular, this allows us to compute a free energy per qudit of the output state.
-
-Non-trivial correlations in the thermodynamic limit can also be considered, but leads to a more complex analysis within our majorization framework of Wigner distributions.
-In this direction, we highlight recent work in majorization in which stochastic independence and correlations are analysed.
-It has been shown~\cite{muller_2015} that stochastic independence (no correlations) of independent distributions can be viewed as a resource in an extension of catalytic majorization, and leads to a single-shot operational interpretation of the Shannon entropy~\cite{muller_2016, muller_2019}.
-
-Our bound depends on the von Neumann entropy $S(\rho)$ of a state, and the free energy at a particular temperature.
-For a state $\tau = e^{-\beta H}/\Z$, the Helmholtz free energy $F$ is given by
-\begin{equation}
-	F \coloneqq \tr[H \tau] - \beta^{-1}S(\tau) = -\beta^{-1}\log \Z,
-\end{equation}
-which is obtained from the internal energy via a Legendre transform~\cite{Pathria_1997}.
-
-The protocol transforms the equilibrium as $\tau^{\otimes n} \rightarrow \E(\tau^{\otimes n}) = \tau^{\prime \otimes m}$.
-The protocol does not generate magic on its own, so we assume that the output state $\tau'$ is also a Wigner-positive state.
-However, this is generally a \emph{non-equilibrium} state for the system.
-Despite this it is useful to associate an effective Hamiltonian $H'$ to the output state by considering the change $H \rightarrow H'$ such that equilibrium is restored at the reference temperature $T$.
-This Hamiltonian is defined by the expression $\tau' = e^{-\beta H'}/\Z'$, and has free energy $F' = -\beta^{-1} \log \Z'$.
-
-\subsection{Temperature-dependent distillation bounds}
-
-The magic state protocol is now considered by how it transforms the pair of quantum states $(\rho^{\otimes n}, \tau^{\otimes n})$ and is then constrained by the relative majorization condition $(W_{\rho}, W_\tau) \succ (W_{\rho'}, W_{\tau'})$ that holds due to the protocol being a stochastic map in the Wigner representation.
-
-In Appendix~\ref{app:lcst_technical} we analyse the Lorenz curves of this condition and obtain the following magic distillation bound that combines computational measures $\epsilon,\epsilon'$, with terms that depend on the Hamiltonian and reference temperature $T$ of the physical system.
-We state the result for the case of qutrits, but a similar analysis works for general odd-dimension qudits.
-
-\begin{theorem}\label{thm:free-energy}
-	Consider a magic distillation protocol on qutrits that transforms $n$ copies of an $\epsilon$--noisy Strange state into $m$ copies of an $\epsilon'$--noisy Strange state, with depolarising errors $\epsilon' \leq \epsilon \leq 3/7$.
-We also allow pre/post-processing by local Clifford unitaries.
-
-	Let $T =(k\beta)^{-1}$ be any finite temperature for the physical system and let $H= \sum_{k \in \mathbb{Z}_3} E_k |E_k\>\<E_k|$ be the Hamiltonian of each qutrit subsystem in its eigen-decomposition.
-Assume that in the thermodynamic limit ($n,m \gg 1$), the protocol applied to the equilibrium state $\tau^{\otimes n} = (e^{-\beta H}/\Z)^{\otimes n}$ maps $\tau^{\otimes n} \longrightarrow \tau^{\prime \otimes m}$, where we write $\tau' = e^{-\beta H'}/\Z'$ for some Hermitian $H'$.
-
-Then the asymptotic magic distillation rate $R = m/n$ is bounded as
-\begin{equation}\label{eq:rate_bounds_proof}
-	R \leq \dfrac{\log \big( 1-\frac{4}{3}\epsilon \big) + \beta (\phi - F)}{\log \big( 1-\frac{4}{3}\epsilon' \big) + \beta (\phi' - F')},
-\end{equation}
-where $F$ is the free energy of $\tau$,  and 
-\begin{equation}\label{eq:phi}
-	\phi = -\beta^{-1} \log \zeta
-\end{equation}
-with $\zeta$ given by the expressions
-\begin{align}
-	\zeta &= \sum_{k\in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}, \\
-	\alpha_k &= \<E_k| A_{\bmz_\star} |E_k\>,
-\end{align}
-and $W_\tau(\bmz)$ attaining a minimum at $\bmz=\bmz_\star$. The primed variables are defined similarly for the output system.
-\end{theorem}
-\noindent The proof of this is provided in Appendix~\ref{app:lcst_technical}, and follows a similar line to the unital protocol bound.
-
-The above bound depends on: 
-\begin{itemize}
-\item Quantum computational measures $\epsilon, \epsilon'$,
-\item Thermodynamic quantities $\beta, F, F',$
-\item Intermediate terms $\phi, \phi'$. 
-\end{itemize}
-The intermediate terms specify how the energy eigenbasis of the system $\{|E_k\>\}$ relates to the computational stabilizer basis $\{|k\>\}$.
-In particular, the term $\phi$ quantifies to what degree a sharp energy value can be associated to the negativity in the Wigner representation.
-Its form is similar to $F$, and so $\phi$ can loosely speaking be viewed as a `magic free energy' term.
-
-The coefficients $\alpha_k$ may be negative for some $k$, when the Hamiltonian has non-stabilizer eigenstates, but the quantity $\phi$ is always well-defined, since the function $\zeta$ is always positive for $\tau$ in the interior of $\F$.
-The quantity $\phi$ can diverge if the state $\tau$ acquired zero Wigner components, which occurs for $\tau$ on the boundary of the set of Wigner-positive states, and is not defined outside of $\F$.
-Finally, if $H$ has a stabilizer eigenbasis then $\phi = E_i$ for some $i$, independent of the temperature $T$.
-Details of this are provided in Appendix~\ref{app:lcst_technical}.
-
-\subsection{Technical aspects and special cases}
-Similar to the unital protocol bounds, the above result is based on only part of the Lorenz curves and so can certainly be tightened with further analysis.
-The primary role of the pre/post-processing by Clifford unitaries in Theorem~\ref{thm:free-energy} is to simplify the form of the bound, and allow it to be expressed in terms of the free energy per particle in a way that does not depend on the parameters $\epsilon, \epsilon', \beta$ in a complex form.
-In Appendix~\ref{app:lcst_technical}, we give bounds in which one does not include these Clifford changes of basis (see Theorem~\ref{thm:no-processing}), and which have a more non-trivial dependency on the parameters.
-
-\begin{figure}[t!]
-    \centering
-    \subfigure[][]{
-    \label{fig:noCliff}
-    \includegraphics[scale=0.35]{figs/rate_scatter.pdf}}\\
-    \subfigure[][]{
-    \label{fig:Cliff}
-    \includegraphics[scale=0.35]{figs/rate_scatter_cliff.pdf}}
-    \caption{\textbf{Temperature-dependent bounds for magic distillation.} Shown are two contour plots of the bound on $R(\epsilon, \beta)$ for the case $H = H' = \sum_{k \in \mathbb{Z}_3} k \ketbra{k}$ and $\epsilon' = 0$, where $\beta$ is the inverse temperature and $\epsilon$ is the depolarising error of the input magic state.
-The top figure~\subref{fig:noCliff} does not use any changes of Clifford basis, and the form of the bound depends on both the error parameter and temperature.
-The curved dashed line is $\epsilon_\star(\beta)$ and given by Eq.~(\ref{eq:threshold}) and $\beta_\star = (kT_\star)^{-1}$ is given by $E_2-\phi = kT_\star \ln 2$.
-In the bottom figure~\subref{fig:Cliff} Clifford processing is used resulting in a smoother bound. In both figures the $\beta = 0$ line correspond to the unital bounds.}
-    \label{fig:rate_contour}
-\end{figure}
-
-The analysis makes other simplifying assumptions that could easily be dropped, at the price of more complex expressions.
-We could perform similar analysis for general qudits, and different choices of magic states, for example.
-It might also be of interest to consider other choices of reference states $\tau$ that are more appropriate to the hardware physics, for example for photonic set-ups~\cite{bombin2021interleaving}.
-
-The assumption which is non-trivial is that we neglect correlations in the reference state in the thermodynamic limit.
-However, for more general scenarios one could make use of variational tools such as the Bogoliubov inequality~\cite{bogolyubov_1966} for approximating the free energy of a system via product states, to obtain similar bounds.
-
-The simplest special case to consider is where the Hamiltonian $H$ is diagonal in the computational basis, and $H=H'$, implying that the protocol leaves the reference equilibrium state unchanged, hence it corresponds to a Gibbs-preserving map~\cite{faist_2015}.
-For the limiting case of $\epsilon' \rightarrow 0$ we obtain Fig.~\ref{fig:rate_contour} which is a contour plot of the bound on $R$ as a function of inverse temperature $\beta$ and the depolarising error $\epsilon$ for the noisy input magic states.
-In this figure we show both the bounds with Clifford basis changes and without them.
-In the more general case, $\Delta F \coloneqq F' - F \ne 0$, so the protocol, when applied to the reference state, adds/extracts free energy from the system.
-We demonstrate change of the bounds with respect to a varying output Hamiltonian in Fig.~\ref{fig:rvsa}.
-
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.35]{figs/R_vs_A.pdf}
-    \caption{\textbf{Variation of distillation bounds with Hamiltonian.}  We illustrate variation of the bound in Eq.~(\ref{eq:rate_bounds_proof}) with respect to the system Hamiltonian.
-We fix $(\epsilon, \epsilon', \beta) = (0.1, 0.0, 0.2)$ and look at a family of Hamiltonians for the qutrit systems, given by $H = A_{\bmo}$ and $H' = (1-p-q)A_{\bmo}+pA_{(1,2)}+q{\rm{diag}}(0,1,2)$, with varying parameters $p, q$, and where $A_{\bmo}$ and $A_{(1,2)}$ are phase-point operators.
-    }
-    \label{fig:rvsa}
-\end{figure}
-
-\section{Extension of single-shot entropies to quasi-distributions}\label{section:entropies}
-We have considered Wigner distributions of magic states within a statistical mechanical setting in which it was argued that magic can be viewed as a non-classical form of free energy.
-This was done at the level of majorization constraints that appear due to stabilizer operations being described by stochastic maps in the Wigner representation.
-In this representation, non-equilibrium states with substantial free energy have Lorenz curves that deviate noticeably from the line $y=x$.
-We also found that when considered in a distillation protocol, magic could also be linked to physical free energies in a non-trivial way.
-We can therefore ask: is it possible to make a more direct link between magic and free energy or entropy?
-
-One obstacle to linking with macroscopic, equilibrium free energy is that the Wigner distribution is generally a quasi-distribution, so the entropy $H(\w) = -\sum_i w_i \log w_i$ of the Wigner distribution is not defined outside the set $\F$, let alone have a physically meaningful interpretation.
-
-However, it turns out that the analysis for the temperature-dependent bound given by Eq.~(\ref{eq:rate_bounds_proof}) implicitly made use of the single-shot R\'{e}nyi divergence~\cite{renyi_1960} $D_\infty (\p \hspace{1pt}||\hspace{1pt} \r)$, which is given by
-\begin{equation}
-	D_\infty (\p \hspace{1pt}||\hspace{1pt} \r) = \log \max_i \frac{p_i}{r_i}.
-\end{equation}
-It is clear that this does remain well-defined on quasi-distributions, and from the majorization relation also has a clear physical meaning, and in Appendix~\ref{app:lcst_technical}, we show that this divergence has the following properties that are derived via relative majorization.
-\begin{theorem}\label{thm:Dinfty} 
-	Let $\tau$ be in the interior of $\F$. Then $D_\infty(W_\rho || W_\tau)$ is well-defined for all $\rho$, and the following hold:
-\begin{enumerate}
-\item $D_\infty(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) \ge 0$ for all quantum states $\rho$.
-\item  $D_\infty(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) = 0$ if and only if $\rho =\tau$.
-\item $D_\infty(W_{\rho^{\otimes 2n}} \hspace{1pt}||\hspace{1pt} W_{\tau^{\otimes 2n}}) = n D_\infty(W_{\rho^{\otimes 2}} \hspace{1pt}||\hspace{1pt} W_{\tau^{\otimes 2}})$ for any $n \in \mathbb{N}$.
-\item $D_\infty(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) \geq D_\infty(W_{\E(\rho)} \hspace{1pt}||\hspace{1pt} W_{\E(\tau)})$ for any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$.
-\end{enumerate}
-\end{theorem}
-The reason for the power of $2$ in the third property is that the maximization is sensitive to the presence of negativity in the Wigner distribution.
-
-We can go further, and show that in fact a range of R\'{e}nyi entropies remain both well-defined and meaningful in the Wigner representation.
-The $\alpha$--R\'{e}nyi entropy $H_\alpha(\p)$ is defined as~\cite{renyi_1960}
-\begin{equation}
-	H_\alpha(\p) \coloneqq \frac{1}{1-\alpha} \log \sum_i p_i^\alpha.
-\end{equation}
-To extend to quasi-distributions we must ensure the following: (a) the entropy is mathematically well-defined on quasi-distributions, and (b) obeys monotonicity under the majorization pre-order.
-In Appendix~\ref{app:single-shot} we prove the following.
-\begin{theorem}\label{thm:HSchur} 
-	If $\alpha = \frac{2a}{2b-1}$ for positive integers $a,b$ with $a \geq b$, then $H_\alpha(\w)$ is well-defined on the set of quasi-distributions, and if $\w \succ \w'$ for two quasi-distributions $\w, \w'$ then $H_\alpha (\w) \leq H_\alpha(\w')$.
-\end{theorem}
-This monotonicity provides a meaningful extension of entropies to quasi-distributions.
-The unusual form of the $\alpha$ parameter is required so that the entropy function is well-defined and real-valued for all $\w$.
-The allowed values of $\alpha$ are dense in $\alpha >1$, however, while R\'{e}nyi entropies on probabilities can also be used for $0 < \alpha <1$, it turns out that this parameter regime is no longer monotonic in terms of the majorization pre-order for quasi-distributions (see Appendix~\ref{app:single-shot} for details).
-
-We can prove the following result, which establishes the equivalence between Wigner negativity and the existence of negative R\'{e}nyi entropy.
-\begin{theorem}\label{thm:Magic}
-	A quantum state $\rho$ has Wigner negativity if and only if $H_\alpha(W_\rho) <0$ for some $\alpha = \frac{2a}{2b-1}$, with positive integers $a \ge b$.
-\end{theorem}
-Therefore, the statistical mechanical description of stabilizer operations provides a setting in which negative entropy is fully meaningful, and quantifies the fact that magic states are more ordered than a perfectly sharp, deterministic classical state $\w = (1,0, \dots , 0)$ with zero entropy.
-We note that prior work has shown that negative conditional entropy~\cite{rio_thermodynamic_2011} arises in the context of quantum correlations, but is unrelated to the present negative entropy.
-
-The $\alpha \rightarrow 1$ limit of the R\'{e}nyi entropy diverges if negativity is present, however it diverges in a well-defined way. We can write the entropy as 
-\begin{equation}
-	H_{1+\epsilon}(W_\rho) = -\epsilon^{-1} \log \sum_{\bmz} |W_\rho (\bmz)|^{1+\epsilon}
-\end{equation} 
-with $\epsilon \rightarrow 0^+$ through a sequence of rational values.
-We recall that mana can be written as $\M(\rho) = \log \sum_{\bmz} |W_\rho(\bmz)|$, so we obtain a second new perspective on mana:
-\begin{equation}\label{eq:mana-divergence}
-\M(\rho) = -\lim_{\epsilon \rightarrow 0^+} \epsilon H_{1+\epsilon}(W_\rho).
-\end{equation}
-Therefore, the mana of a state $\rho$ is the residue of a pole in $H_\alpha(W_\rho)$, and quantifies the divergence of the R\'{e}nyi-entropy as we approach the limiting Shannon entropy $H(W_\rho)$.
-
-We also note that the R\'{e}nyi entropy can be described as a $q$--deformation of the Shannon entropy~\cite{baez2011renyi}, and that $H_\alpha(\p)$ can be related to the $q$--derivative of free energy.
-For this, the R\'{e}nyi parameter becomes a temperature term $\alpha = \frac{T_0}{T}$ where $T_0$ is a reference temperature and derivatives are considered via the limit $T \rightarrow T_0$.
-Therefore, if we try to push this to the present setting, the presence of Wigner negativity would correspond to a divergence in the first derivative of an effective free energy as $T \rightarrow T_0$.
-It is interesting to speculate whether this non-classicality could be interpreted in terms of a phase transition~\cite{domb2000phase}.
-
-\subsection{R\'{e}nyi divergences and general distillation bounds}
-Every entropy can be obtained from a relative entropy~\cite{Gour_2020} so we now state the extensions for R\'{e}nyi divergences of Wigner distributions.
-The $\alpha$--R\'{e}nyi divergence $D_\alpha(\p||\r)$ is defined as
-\begin{equation}
-	D_\alpha(\p \hspace{1pt}||\hspace{1pt} \r) \coloneqq \frac{1}{\alpha-1} \log \sum_i p_i^\alpha r_i^{1-\alpha},
-\end{equation}
-where $\p$ can be a quasi-distribution and $\r$ a probability distribution with positive components. In Appendix~\ref{app:single-shot}, we also show that the divergence satisfies the following.
-
-\begin{theorem}\label{thm:Da_props} 
-	Let $\tau$ be in the interior of $\F$. 
-	If $\alpha = \frac{2a}{2b-1}$ for positive integers $a,b$ with $a \geq b$, then the $\alpha$-R\'{e}nyi divergence $D_\alpha(W_\rho || W_\tau)$ is well-defined for all quantum states $\rho$, and the following hold:
-\begin{enumerate}
-\item $D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) \ge 0$ for all quantum states $\rho$.
-\item  $D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) = 0$ if and only if $\rho =\tau$.
-\item $D_\alpha(W_{\rho^{\otimes n}} \hspace{1pt}||\hspace{1pt} W_{\tau^{\otimes n}}) = n D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)$ for any $n \in \mathbb{N}$.
-\item $D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) \geq D_\alpha (W_{\E(\rho)} \hspace{1pt}||\hspace{1pt} W_{\E(\tau)})$ for any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$.
-\end{enumerate}
-\end{theorem}
-
-We can now apply this to obtain a family of magic distillation bounds based on R\'{e}nyi divergences.
-
-\begin{theorem}\label{thm:entropic_bounds}
-	Consider a general magic state distillation protocol on odd prime dimension qudits, that converts a magic state $\rho^{\otimes n} \longrightarrow \E(\rho^{\otimes n})=\rho'^{\otimes m}$and let $\tau$ be any full-rank stabilizer reference state on a qudit.
-Then the distillation rate $R \coloneqq m/n$ is upper bounded as,
-	\begin{equation}
-		R \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{\rlap{\raisebox{-0.2ex}{$\widetilde{\phantom{D}}$}}D_\alpha( \rho', \tau')},
-	\end{equation}
-	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ and the average divergence per qudit
-	\begin{equation}
-\widetilde{D}_\alpha( \rho', \tau') \coloneqq \frac{1}{m} D_\alpha (W_{\rho'^{\otimes m}} \hspace{1pt}||\hspace{1pt} W_{\tau'_m}),
-\end{equation}
-between the output magic state $\rho'^{\otimes m}$ and $\tau'_m = \E(\tau^{\otimes n})$.
-\end{theorem}
-The proof is given in Appendix~\ref{app:single-shot}.
-
-While this bound is abstract in its present form, it does suggest future applications by viewing $\widetilde{D}_\alpha( \rho', \tau')$ within the context of hypothesis testing~\cite{tomamichel2013}, as a measure of distinguishability between $\rho'^{\otimes m}$ and the $m$ qudit state $\tau'_m$.
-However, in order to properly link with hypothesis-testing one would have to first extend such results to quasi-distributions.
-
-If correlations in $\tau'_m$ between subsystems can be neglected, then $\tau'_m = \tau'^{\otimes m}$ for some qudit state $\tau'$ and
-\begin{equation}
-	\widetilde{D}_\alpha( \rho', \tau') = D_\alpha (W_{\rho'} \hspace{1pt}||\hspace{1pt} W_{\tau'}),
-\end{equation}
-which gives a generalized version of Theorem~\ref{thm:free-energy}, with a term such as $D_\alpha(W_\rho ||W_\tau)$ that behaves essentially as an $\alpha$--free energy difference~\cite{Brandao_2015} in the Wigner representation.
-
-We can illustrate a basic application of the above bound for magic protocols that give unital maps. In this case it is easy to see that the above bound reduces to the simple form
-\begin{equation}
-	R \leq R_\alpha \coloneqq \frac{2\log d - H_{\alpha}(W_\rho)}{2\log d - H_{\alpha}(W_{\rho'})}.
-\end{equation}
-In particular for the case of noisy Strange states on qutrits and $\epsilon'=0$, this bound becomes
-
-\begin{equation}
-	R \leq R_\alpha = \frac{2(1-\alpha)\log 3 - \log \left [8(\frac{1}{6} - \frac{\epsilon}{18})^\alpha + (-\frac{1}{3} + \frac{4\epsilon}{9})^\alpha\right ] }{2(1-\alpha)\log 3 + \alpha \log 6 - \log (8 + 2^\alpha )}.
-\end{equation}
-This upper bound can be numerically minimized over $\alpha$, for any $\epsilon$.
-The case $R_{10}$ is shown in Fig.~\ref{fig:distill_bounds} and numerical evidence shows it is close to the optimal bound from majorization.
-
-\section{Outlook and open questions}
-\label{sec:lower_bounds}
-
-We have described how relative majorization can be used to establish upper bounds on magic distillation protocols that take into account additional physics of the system.
-Our bounds exploited relatively simple aspects of the Lorenz curves of the quasi-distributions, so it would be of interest to sharpen these bounds and obtain a better handle on the Lorenz curve structure in the $n\rightarrow \infty$ limit.
-It would also be of interest to analyse what features of single-shot entropies can be extended to quasi-distributions in a sensible form~\cite{renner_phd, tomamichel2013}.
-This raises interesting questions as we no longer have a notion of typicality and the central limit theorem does not apply.
-That said, for special states such as the Strange state, the asymptotic behaviour is relatively simple, so exact asymptotics for this should be possible.
-In Appendix~\ref{app:lcsu_technical} and Appendix~\ref{app:lcst_technical} we give additional results that may be of use for later work.
-
-We can also ask if this approach could additionally provide \emph{lower bounds} for distillation protocols.
-In contrast to the upper bounds, it is now essential to include the symplectic constraints on the phase space in the majorization relations.
-The Clifford group action on a quantum system corresponds to the action of the affine symplectic group $G=SL(2,\mathbb{Z}_d) \ltimes \mathbb{Z}_d^2$ on the discrete phase space~\cite{Appleby_2005, Bengtsson_2006}.
-Therefore, any convex mixture of Clifford unitaries will correspond to a convex mixture of these group actions.
-The Hardy-Littlewood theorem~\cite{hardy_1952} tells us that majorization is obtained from convex mixtures of arbitrary permutations, a result that has also been generalized to convex mixtures of elements of a general group $G$.
-This $G$--majorization has been studied in the classical literature and a range of results are known about it~\cite{giovagnoli_1985, steerneman_1990, eaton_1977}.
-For example, it is known that if $G$ is a finite reflection group then the $G$--majorization pre-order is described by a finite list of conditions~\cite{giovagnoli_1985}, just as is the case for the relative majorization ordering.
-One route leading to concrete lower bounds on distillation rates is therefore to consider reflection sub-groups of $SL(2,\mathbb{Z}_d) \ltimes \mathbb{Z}_2$, or other simple sub-groups, for which the majorization relation reduces to a finite set of conditions.
-
-The topic of $G$--majorization has been extensively studied, but to our knowledge there has not been work on relative $G$--majorization.
-This would correspond to transformations that are not unital.
-Physically, this regime would correspond to a form of thermo-majorization obtained from looking at the action of the Clifford group at a micro-canonical level, and then reducing to a small subsystem~\cite{Pathria_1997}.
-While this seems like a painful thing to consider, there is motivation for this beyond the aim of magic protocols: in the case of classical statistical mechanics on a phase space this is precisely the situation, albeit in the continuum limit.
-Statistical mechanics of actual systems obey Hamiltonian dynamics, thus they automatically respect a symplectic form~\cite{Arnold_2000, Pathria_1997}.
-Therefore, the pre-order of statistical mechanical states with respect to phase space dynamics preserving a Gibbs state must correspond to a symplectic majorization condition.
-Of course, technical features arise in the continuum limit when considering distributions on an unbounded phase space, but this could be remedied by either considering a compact phase space (e.g.~for a particle on a ring) or by first studying the discrete case.
-Such scenarios also arise in the Quantum Hall Effect~\cite{Klitzing_1980}, which is another regime where these techniques could be of use.
-
-Lastly, we note that it would be of interest to consider the possibility of applying the approach taken here to other scenarios in which one wishes to distinguish classical from non-classical behaviour based on quasi-probability representations~\cite{Ferrie_2008, barnett_1997,Allahverdyan_2018, arvidsson_2020, halpern_2018, Lostaglio_2018, Levy_2020}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\bibliography{bib}
-\bibliographystyle{naturemag}
-%\bibliography{ms.bbl}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{Acknowledgements}
-We thank Earl Campbell, Matteo Lostaglio, Philippe Faist and Nicole Yunger Halpern for helpful comments and discussions.
-NK is supported by the EPSRC Centre for Doctoral Training in Controlled Quantum Dynamics.
-DJ is supported by the Royal Society and a University Academic Fellowship.
-
-\section*{Author contributions}
-DJ conceived the theoretical idea. 
-Calculations were performed by NK. 
-Analysis and writing of the manuscript were jointly done by NK and DJ.
-
-\section*{Competing interests}
-The authors declare that there are no competing interests.
-
-\section*{Data availability}
-No datasets were generated or analysed during the current study.
-
-\appendix
-\newpage
-\section{Properties of Wigner representations}
-\label{app:wigner}
-
-In this appendix we present basic properties of the phase-point operators and the Wigner distribution that are used throughout the paper.
+\section*{Supplementary Note 1: Properties of Wigner representations}
+
+Here we present basic properties of the phase-point operators and the Wigner distribution that are used throughout the main text.
 
@@
     \begin{enumerate}
-        \item[(i)]\label{en:a1} Hermiticity and unitarity: $A_{\bmz}^\dagger = A_{\bmz} = A_{\bmz}^{-1}$;
+        \item[(i)]\label{en:a1} Hermiticity and unitarity: $A_{\z}^\dagger = A_{\z} = A_{\z}^{-1}$;
 	    \item[(ii)]\label{en:a2} Closure under transposition: $A_{(q, p)}^T = A_{(q, -p)}$;
-	    \item[(iii)]\label{en:a3} Unit trace for odd $d$: $\tr[A_{\bmz}] = 1$;
-	    \item[(iv)]\label{en:a4} Completeness relation: $\sum_{\bmz \in \cal{P}_d} A_{\bmz} = d\id$;
-	    \item[(i)]\label{en:a5} Orthogonality: $\tr[A_{\bmz}^\dagger A_{\bmy}] = d \delta_{\bmz,\bmy}$.
+	    \item[(iii)]\label{en:a3} Unit trace for odd $d$: $\tr[A_{\z}] = 1$;
+	    \item[(iv)]\label{en:a4} Completeness relation: $\sum_{\z \in \P_d} A_{\z} = d\id$;
+	    \item[(i)]\label{en:a5} Orthogonality: $\tr[A_{\z}^\dagger A_{\y}] = d \delta_{\z,\y}$.
 	\end{enumerate}
 \end{proposition}
-All properties follow from the definition in Eq.~(\ref{eq:ax}) along with properties of the displacement operators $D_{\bmz}$ and can be found in the literature, e.g.~\cite{cit:veitch,Vourdas_2004,cit:gross3}
+All properties follow from the definition in Eq.~(6) in the main text along with properties of the displacement operators $D_{\z}$ and can be found in the literature, e.g.~\cite{cit:veitch,Vourdas_2004,Gross2006}
 
@@
   \begin{enumerate}
-    \item[(i)]\label{en:w1} Real valued: $\W{\rho}(\bmz) \in \mathbb{R}^{d^2}$;
-    \item[(ii)]\label{en:w2} Normalized: $\sum_{\bmz \in \cal{P}_d} \W[\bmz]{\rho}=1$;
-    \item[(iii)]\label{en:w3} Bounded: $\abs{\W[\bmz]{\rho}} \leq \frac{1}{d}$.
+    \item[(i)]\label{en:w1} Real valued: $W_\rho(\z) \in \mathbb{R}^{d^2}$;
+    \item[(ii)]\label{en:w2} Normalized: $\sum_{\z \in \P_d} W_\rho(\z) = 1$;
+    \item[(iii)]\label{en:w3} Bounded: $\abs{W_\rho(\z)} \leq \frac{1}{d}$.
     \item[(iv)]\label{en:w4} Additive under mixing: \vspace{2pt}\\
-    $\W[\bmz]{p\rho_1 + (1-p)\rho_2} = p\W[\bmz]{\rho_1} + (1-p)\W[\bmz]{\rho_2}$;
+    $W_{p\rho_1 + (1-p)\rho_2}(\z) = p W_{\rho_1}(\z) + (1-p) W_{\rho_2}(\z)$;
     \item[(v)]\label{en:w5} Multiplicative under tensor products: \vspace{2pt}\\
-    $\W[\bmz_A \oplus \bmz_B]{\rho_A \otimes \rho_B} = \W[\bmz_A]{\rho_A}\W[\bmz_B]{\rho_B}$.
+    $W_{\rho_A \otimes \rho_B}(\z_A \oplus \z_B) = W_{\rho_A}(\z_A)W_{\rho_B}(\z_B)$.
 	\end{enumerate}
@@
 \begin{proof}
-	Proof of all properties can be found in the literature~\cite{cit:veitch,Vourdas_2004,cit:gross3,Wang_2019} except for property (iii) which we prove here.
+	Proof of all properties can be found in the literature~\cite{cit:veitch,Vourdas_2004,Gross2006,Wang_2019} except for property (iii) which we prove here.
 
 Let $\{\lambda_i\}_{i \in \mathbb{Z}_d}$ be the (non-negative) eigenvalues of $\rho$, summing to 1.
-Let $\{\alpha_{\bmz,i}\}_{i \in \mathbb{Z}_d}$ be the eigenvalues of $A_{\bmz}$. For any $\bmz, \alpha_{\bmz,i} \in \{-1, 1\}$, due to the hermiticity and unitarity of the phase-point operators. 
+Let $\{\alpha_{\z,i}\}_{i \in \mathbb{Z}_d}$ be the eigenvalues of $A_{\z}$. For any $\z, \alpha_{\z,i} \in \{-1, 1\}$, due to the hermiticity and unitarity of the phase-point operators. 
 Then,
 \begin{align}
-	\abs{W_{\rho}(\bmz)} &= \frac{1}{d}\abs{\tr[A_{\bmz} \rho]} \leq \frac{1}{d} \abs{\sum_i \alpha_{\bmz,i} \lambda_i} \nonumber\\ &\leq \frac{1}{d}\sum_i \lambda_i = \frac{1}{d}.
+	\abs{W_{\rho}(\z)} &= \frac{1}{d}\abs{\tr[A_{\z} \rho]} \leq \frac{1}{d} \abs{\sum_i \alpha_{\z,i} \lambda_i} \nonumber\\ &\leq \frac{1}{d}\sum_i \lambda_i = \frac{1}{d}.
 \end{align}
@@
     \label{thm:wchannel}
-    The Wigner distribution of a quantum channel $\E: \cal{B}(\cal{H}_{d_A}) \rightarrow \cal{B}(\cal{H}_{d_B})$ is
+    The Wigner distribution of a quantum channel $\E: {\cal B}(\H_{d_A}) \rightarrow {\cal B}(\H_{d_B})$ is
     \begin{enumerate}
-        \item[(i)]\label{en:wo1} Real-valued: $\W{\E}(\bmz|\bmy) \in \mathbb{R}^{d_A^2} \times \mathbb{R}^{d_B^2}$;
-        \item[(ii)]\label{en:wo2} Normalized: $\sum_{\bmy \in \cal{P}_{d_{\scalebox{.9}{$\scriptscriptstyle B$}}}} \W[\bmz|\bmy]{\E} = 1$ \\ 
-        for any $\bmz \in \cal{P}_{d_A}$;
-        \item[(iii)]\label{en:wo3} Bounded: $\abs{\W[\bmz|\bmy]{\E}} \leq \frac{d_A}{d_B}$;
-	    \item[(iv)]\label{en:wo4} $\W[\bmz]{\E(\rho)} = \sum\limits_{\bmy \in \cal{P}_{d_{A}}} \W[\bmz|\bmy]{\E} \W[\bmy]{\rho}$ for any $\bmz \in \cal{P}_{d_B}$.
+        \item[(i)]\label{en:wo1} Real-valued: $W_{\E}(\z|\y) \in \mathbb{R}^{d_A^2} \times \mathbb{R}^{d_B^2}$;
+        \item[(ii)]\label{en:wo2} Normalized: $\sum_{\y \in \P_{d_{\scalebox{.9}{$\scriptscriptstyle B$}}}} W_{\E}(\z|\y) = 1$ \\ 
+        for any $\z \in \P_{d_A}$;
+        \item[(iii)]\label{en:wo3} Bounded: $\abs{W_{\E}(\z|\y)} \leq \frac{d_A}{d_B}$;
+	    \item[(iv)]\label{en:wo4} $W_{\E(\rho)}(\z) = \sum\limits_{\y \in \P_{d_{A}}} W_{\E}(\z|\y) W_\rho(\y)$ for any $\z \in \P_{d_B}$.
     \end{enumerate}
@@
 \begin{proof}
-	Proof of all properties are provided in~\cite{Wang_2019} except for property (iii) which is a direct consequence of the definition of $\W{\E}$ and property (iii) in Proposition~\ref{thm:wstate}.
+	Proof of all properties are provided in~\cite{Wang_2019} except for property (iii) which is a direct consequence of the definition of $W_{\E}$ and property (iii) in Proposition~\ref{thm:wstate}.
 \end{proof}
@@
 \begin{equation}
-	W_{\rho|\tau}(\bmz) \coloneqq \frac{W_\rho (\bmz) }{ W_\tau(\bmz)},
+	W_{\rho|\tau}(\z) \coloneqq \frac{W_\rho (\z) }{ W_\tau(\z)},
 \end{equation}
@@
 \begin{equation}
-W_{\rho_A \otimes \rho_B | \tau_A \otimes \tau_B}(\bmz_A \oplus \bmz_B) =W_{\rho_A | \tau_A}(\bmz_A) W_{\rho_B | \tau_B}(\bmz_B)
+W_{\rho_A \otimes \rho_B | \tau_A \otimes \tau_B}(\z_A \oplus \z_B) =W_{\rho_A | \tau_A}(\z_A) W_{\rho_B | \tau_B}(\z_B)
 \end{equation}
@@
 \begin{align}
-W_{\rho_A \otimes \rho_B | \tau_A \otimes \tau_B}(\bmz_A \oplus \bmz_B) &= \frac{W_{\rho_A \otimes \rho_B} (\bmz_A \oplus \bmz_B)}{W_{\tau_A \otimes \tau_B} (\bmz_A \oplus \bmz_B)}\nonumber \\
- = \frac{W_{\rho_A } (\bmz_A )W_{\rho_B } (\bmz_B )}{W_{\tau_A } (\bmz_A )W_{\tau_B } (\bmz_B )} &= W_{\rho_A | \tau_A}(\bmz_A) W_{\rho_B | \tau_B}(\bmz_B). \nonumber
-\end{align}
-\end{proof}
-
-\section{Properties of relative majorization and Lorenz curves}
-\label{app:major}
-
-\subsection{Relative majorization for quasi-distributions}
-\label{app:rel_quasi}
+W_{\rho_A \otimes \rho_B | \tau_A \otimes \tau_B}(\z_A \oplus \z_B) &= \frac{W_{\rho_A \otimes \rho_B} (\z_A \oplus \z_B)}{W_{\tau_A \otimes \tau_B} (\z_A \oplus \z_B)}\nonumber \\
+ = \frac{W_{\rho_A } (\z_A )W_{\rho_B } (\z_B )}{W_{\tau_A } (\z_A )W_{\tau_B } (\z_B )} &= W_{\rho_A | \tau_A}(\z_A) W_{\rho_B | \tau_B}(\z_B). \nonumber
+\end{align}
+\end{proof}
+
+\section*{Supplementary Note 2: Properties of relative majorization and Lorenz curves}
+
+\subsection*{Relative majorization for quasi-distributions}
 
@@
 \begin{equation}
-	\Gamma_{\bma}(\bmz) \coloneqq \bigoplus_{i=1}^N z_i \bmeta_{a_i},
+	\Gamma_{\bma}(\z) \coloneqq \bigoplus_{i=1}^N z_i \bmeta_{a_i},
 \end{equation}
@@
 \end{equation}
-that obeys $(\Gamma^{-1}_{\bma} \circ \Gamma_{\bma}) (\bmz) = \bmz$ for all $\bmz \in \mathbb{R}^N$.
+that obeys $(\Gamma^{-1}_{\bma} \circ \Gamma_{\bma}) (\z) = \z$ for all $\z \in \mathbb{R}^N$.
 
@@
 Restricting the above result in the context of proper probability distributions, we can immediately prove the Lorenz curve condition for probability distributions.
-We first need to define a Lorenz curve \emph{elbow} as a point where the slope of the curve changes, expressed explicitly in~Eq.~(\ref{eq:lc}) for Lorenz curve $L_{\w | \r}(x)$
+We first need to define a Lorenz curve \emph{elbow} as a point where the slope of the curve changes, expressed explicitly in Eq.~(15) for Lorenz curve $L_{\w | \r}(x)$
 \begin{proposition}\label{thm:lc_equiv_prob}
@@
 
-The following result is used in Sec.~\ref{sec:lc} to extend the Lorenz curve condition of Proposition~\ref{thm:lc_equiv_prob} into the context of quasi-distributions.
+The following result is used \revhigh{in the main text} to extend the Lorenz curve condition of Proposition~\ref{thm:lc_equiv_prob} into the context of quasi-distributions.
 \begin{proposition}\label{Lorenz_linearity}
@@
 
-	The equivalence between (i) and (ii) on quasi-distributions was proven in Theorem~\ref{thm:lcquasi}.
+	The equivalence between (i) and (ii) on quasi-distributions was proven in Theorem~1 in the main text.
 
@@
 
-\subsection{Component-multiplicity pairs}
-\label{app:cmpairs}
-
-In general, a $1$--copy $d$--dimensional state $\rho$ is described by its $d^2$--dimensional Wigner distribution $\W{\rho}$. 
-The distribution $\W{\rho}$ is defined on the phase space, but it can be convenient to re-express this using vector notation.
+\subsection*{Component-multiplicity pairs}
+
+In general, a $1$--copy $d$--dimensional state $\rho$ is described by its $d^2$--dimensional Wigner distribution $W_\rho$. 
+The distribution $W_\rho$ is defined on the phase space, but it can be convenient to re-express this using vector notation.
 We discuss this in terms of Wigner distributions, but there is nothing to prevent the discussion from applying to rescaled Wigner distributions as well.
 
-To each Wigner distribution $W_\rho(\bmz)$ we can associate \emph{component-multiplicity} pairs $\{(w_i, m_i)\}$ where the value $w_i$ occurs in the distribution $W_\rho(\bmz)$ with multiplicity $m_i$.
+To each Wigner distribution $W_\rho(\z)$ we can associate \emph{component-multiplicity} pairs $\{(w_i, m_i)\}$ where the value $w_i$ occurs in the distribution $W_\rho(\z)$ with multiplicity $m_i$.
 
@@
 \begin{proposition}
-Consider two Wigner distributions $\W{\rho_A}(\bmz_A), \W{\rho_B}(\bmz_B)$ with component-multiplicity pairs 
+Consider two Wigner distributions $W_{\rho_A}(\z_A), W_{\rho_B}(\z_B)$ with component-multiplicity pairs 
 \begin{equation}
@@
 \end{equation}
-respectively. Then, $\{(w_i w_j', m_i m_j')\}$ gives component-multiplicity pairs for $\W{\rho_A \otimes \rho_B}(\bmz_A \oplus \bmz_B)$.
-\end{proposition}
-\begin{proof}
-	This result is true because all components of $\W{\rho_A \otimes \rho_B}(\bmz_A \oplus \bmz_B)$ are of the form $w_i w_j'$ and 
+respectively. Then, $\{(w_i w_j', m_i m_j')\}$ gives component-multiplicity pairs for $W_{\rho_A \otimes \rho_B}(\z_A \oplus \z_B)$.
+\end{proposition}
+\begin{proof}
+	This result is true because all components of $W_{\rho_A \otimes \rho_B}(\z_A \oplus \z_B)$ are of the form $w_i w_j'$ and 
 \begin{equation*}
@@
 where $d_A, d_B$ are the dimensions of $\rho_A, \rho_B$ respectively, and
-so the set $\{(w_i w_j', m_i m_j')\}$ contains exactly the Wigner components of $\W{\rho_A \otimes \rho_B}(\bmz_A \oplus \bmz_B)$.
+so the set $\{(w_i w_j', m_i m_j')\}$ contains exactly the Wigner components of $W_{\rho_A \otimes \rho_B}(\z_A \oplus \z_B)$.
 \end{proof}
@@
 \begin{proof}
-	Denote by $C_D^n \coloneqq \{\bmk\}$ the set of all vectors $\bmk \coloneqq (k_1, \dots, k_D)$ with non-negative integer components that sum to $n$, i.e.
+	Denote by $C_D^n \coloneqq \{\k\}$ the set of all vectors $\k \coloneqq (k_1, \dots, k_D)$ with non-negative integer components that sum to $n$, i.e.
 	\begin{equation*}
@@
 	We proceed by induction.	
-	Assume $n = 1$ and let $\bmk_i$ be the vector with its $i$-th component equal to 1 and 0's elsewhere.
+	Assume $n = 1$ and let $\k_i$ be the vector with its $i$-th component equal to 1 and 0's elsewhere.
 	The set $C_D^1$ consists of all vectors of this form, i.e. 
 \begin{equation*}
-	C_D^1 = \{ \bmk_i \}_{i=1,\dots,D}
+	C_D^1 = \{ \k_i \}_{i=1,\dots,D}
 \end{equation*}
@@
 \begin{equation*}
-	\left( W_{\bmk_i}, M_{\bmk_i} \right) = (w_i, m_i).
+	\left( W_{\k_i}, M_{\k_i} \right) = (w_i, m_i).
 \end{equation*}
-Therefore, $\{ (W_{\bmk}, M_{\bmk}) \}_{\bmk \in C_D^1}$ is a complete set of component-multiplicity pairs for $W_\rho$.
-
-	Assume that $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$ as given in Eqs.~(\ref{eq:W}, \ref{eq:M}) is a complete set of component-multiplicity pairs for the $n$--copy distribution $W_{\rho^{\otimes n}} = W_{\rho}^{\otimes n}$.
+Therefore, $\{ (W_{\k}, M_{\k}) \}_{\k \in C_D^1}$ is a complete set of component-multiplicity pairs for $W_\rho$.
+
+	Assume that $\{(W_{\k}, M_{\k})\}_{\k \in C_D^n}$ as given in Eqs.~(\ref{eq:W}, \ref{eq:M}) is a complete set of component-multiplicity pairs for the $n$--copy distribution $W_{\rho^{\otimes n}} = W_{\rho}^{\otimes n}$.
 	By construction, the distribution $W_{\rho}^{\otimes (n+1)} = W_{\rho}^{\otimes n} \otimes W_{\rho}$, so it admits the complete set of component multiplicity pairs
 \begin{equation}
-	\{(W_{\bmk} w_i, M_{\bmk} m_i)\},\ \bmk \in C_D^n \text{ and } i=1,\dots,D.
+	\{(W_{\k} w_i, M_{\k} m_i)\},\ \k \in C_D^n \text{ and } i=1,\dots,D.
 \end{equation}
@@
 \begin{align*}
-	&\sum_{\bmk \in C_D^n}\sum_{i=1}^D M_{\bmk} m_i W_{\bmk} w_i = \sum_{\bmk \in C_D^n} M_{\bmk}W_{\bmk} \sum_{i=1}^D m_i w_i =\\
-	&\sum_{\bmk \in C_D^n} \frac{n!}{k_1!\dots k_D!} \prod\limits_{i=1}^D {m_i}^{k_i}{w_i}^{k_i} \sum_{i=1}^D m_i w_i =\\
+	&\sum_{\k \in C_D^n}\sum_{i=1}^D M_{\k} m_i W_{\k} w_i = \sum_{\k \in C_D^n} M_{\k}W_{\k} \sum_{i=1}^D m_i w_i =\\
+	&\sum_{\k \in C_D^n} \frac{n!}{k_1!\dots k_D!} \prod\limits_{i=1}^D {m_i}^{k_i}{w_i}^{k_i} \sum_{i=1}^D m_i w_i =\\
 	&\left( \sum_{i=1}^D m_i w_i \right)^n \left( \sum_{i=1}^D m_i w_i \right) = \left( \sum_{i=1}^D m_i w_i \right)^{n+1} =\\
-	&\sum_{\bmq \in C_D^{n+1}} M_{\bmq}W_{\bmq},
+	&\sum_{\q \in C_D^{n+1}} M_{\q}W_{\q},
 \end{align*}
-where in the last expression, vectors $\bmq = (q_1, \dots, q_D)$ have non-negative integer components that sum to $(n+1)$ and 
+where in the last expression, vectors $\q = (q_1, \dots, q_D)$ have non-negative integer components that sum to $(n+1)$ and 
 \begin{align*}
-	M_{\bmq} &= \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i},\\
-	W_{\bmq} &= \prod\limits_{i=1}^D {w_i}^{q_i}.
+	M_{\q} &= \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i},\\
+	W_{\q} &= \prod\limits_{i=1}^D {w_i}^{q_i}.
 \end{align*}
@@
 We have achieved a regrouping of the distribution components.
-Every component $W_{\bmq}$ is of the form $W_{\bmk} w_i$ with $q_i = k_i + 1$ and $q_j = k_j$ for $j\neq i$ and 
+Every component $W_{\q}$ is of the form $W_{\k} w_i$ with $q_i = k_i + 1$ and $q_j = k_j$ for $j\neq i$ and 
 \begin{align*}
-	\sum_{\bmq \in C_D^{n+1}}  \hspace{-6pt} M_{\bmq} &=  \hspace{-10pt} \sum_{\bmq \in C_D^{n+1}} \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i} = \left( \sum_{i=1}^D m_i \right)^{n+1} \hspace{-10pt} \\
+	\sum_{\q \in C_D^{n+1}}  \hspace{-6pt} M_{\q} &=  \hspace{-10pt} \sum_{\q \in C_D^{n+1}} \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i} = \left( \sum_{i=1}^D m_i \right)^{n+1} \hspace{-10pt} \\
 	&= d^{2(n+1)},
@@
 
-Therefore, $\{ (W_{\bmq}, M_{\bmq}) \}_{\bmq \in C_D^{n+1}}$ contains exactly the components of $W_{\rho}^{\otimes n}$, completing the proof.
+Therefore, $\{ (W_{\q}, M_{\q}) \}_{\q \in C_D^{n+1}}$ contains exactly the components of $W_{\rho}^{\otimes n}$, completing the proof.
 \end{proof}
@@
 
-\subsection{Results on Lorenz curve constraints}
-\label{app:lc_constraints}
-
-We first prove the following result on the relation between majorization in a particular sub-theory $\R_\sigma$ and mana, which was stated in Sec.~\ref{sec:monotones_frag}.
-\begingroup
-\def\thetheorem{\ref{lem:lcmax}}
-\begin{theorem}
-	Given a magic state $\rho$, the maximum value $L_\star$ attained by the Lorenz curve $\lc{\rho}{\sigma}(x)$ is independent of the $\R_\sigma$ and equal to $1+\sn{\rho}$.
-Moreover, the relative majorization constraint is stronger than mana in every $\R_\sigma$.
-\end{theorem}
-\addtocounter{theorem}{-1}
-\endgroup
-\begin{proof}
-	We denote the Wigner distributions of the states single-component vectors $\w(\rho)=W_\rho(\z)$ and $ \w(\sigma)=W_\sigma(\z)$. Likewise, we write $\w(\rho|\sigma) = W_{\rho|\tau}(\bmz)$.
+\subsection*{Results on Lorenz curve constraints}
+
+We first prove the following result on the relation between majorization in a particular sub-theory $\R_\sigma$ and mana.
+\begin{customthm}{5}
+	Given a magic state $\rho$, the maximum $L_\star$ of its Lorenz curve $L_{\rho|\sigma}(x)$ is independent of the $\R_\sigma$ and equal to $1+{\rm sn}(\rho)$.
+Moreover, the majorization constraint is stronger than mana in every $\R_\sigma$.
+\end{customthm}
+\begin{proof}
+	We denote the Wigner distributions of the states single-component vectors $\w(\rho)=W_\rho(\z)$ and $ \w(\sigma)=W_\sigma(\z)$. Likewise, we write $\w(\rho|\sigma) = W_{\rho|\tau}(\z)$.
 	We choose the component indexing so that $\w(\rho|\sigma)^\downarrow = \w(\rho|\sigma)$, so the components are sorted in non-increasing order.
 
-Note that all components of $\bmw(\sigma)$ are positive, so $w(\rho|\sigma)_i \geq 0$ if and only if $w(\rho)_i \geq 0$ for any $i=1,\dots,d^2$.
+Note that all components of $\w(\sigma)$ are positive, so $w(\rho|\sigma)_i \geq 0$ if and only if $w(\rho)_i \geq 0$ for any $i=1,\dots,d^2$.
 
 	Let $i_\star$ be the index of the smallest non-negative component of $\w(\rho|\sigma)^\downarrow$.
-	Then, $w(\rho)_i < 0$ if and only if $i > i_\star$, so the maximum of Lorenz curve $\lc{\rho}{\sigma}(x)$ takes the value 
-	\begin{equation}
-		\lc{\rho}{\sigma}(x_{i_\star}) = \sum_{i=1}^{i_\star} w(\rho)_i,
+	Then, $w(\rho)_i < 0$ if and only if $i > i_\star$, so the maximum of Lorenz curve $L_{\rho|\sigma}(x)$ takes the value 
+	\begin{equation}
+		L_{\rho|\sigma}(x_{i_\star}) = \sum_{i=1}^{i_\star} w(\rho)_i,
 	\end{equation}
@@
 	\begin{align}
-	L_\star &\coloneqq	\lc{\rho}{\sigma}(x_{i_\star}) 
-		= \sum\limits_{\bmz: \W[\bmz]{\rho} \geq 0}\hspace{-5pt} \W[\bmz]{\rho} \nonumber \\
-		&= 1 + \sn{\rho}.
-	\end{align}
-
-Since mana is a monotonic function of sum-negativity, $\M(\rho) \coloneqq \log \hspace{1pt}(2\hspace{1pt}\sn{\rho}+1)$, we see that mana determines the peak of the Lorenz curve $L_{\rho|\sigma}(x)$.
+	L_\star &\coloneqq	L_{\rho|\sigma}(x_{i_\star}) 
+		= \sum\limits_{\z: W_{\rho}(\z) \geq 0}\hspace{-5pt} W_{\rho}(\z) \nonumber \\
+		&= 1 + {\rm sn}(\rho).
+	\end{align}
+
+Since mana is a monotonic function of sum-negativity, $\M(\rho) = \log \hspace{1pt}(2\hspace{1pt}{\rm sn}(\rho)+1)$, we see that mana determines the peak of the Lorenz curve $L_{\rho|\sigma}(x)$.
 However, mana is one of $d^{2n}$ constraints, so majorization is strictly a stronger constraint in any $\R_\sigma$.
@@
 \begin{proposition}[First elbow constraint]\label{prop:first_elb}
-	Consider a magic state process $\rho \longrightarrow \rho'$ with input and output Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\rho'}{\sigma'}(x)$ and denote the coordinates of the first elbow of $L_{\rho|\sigma}(x)$ by $(X_0, L_0)$ and the coordinates of the first elbow of $L_{\rho' |\sigma'}(x)$ by $(X'_0, L'_0)$.
+	Consider a magic state process $\rho \longrightarrow \rho'$ with input and output Lorenz curves $L_{\rho|\sigma}(x), L_{\rho'|\sigma'}(x)$ and denote the coordinates of the first elbow of $L_{\rho|\sigma}(x)$ by $(X_0, L_0)$ and the coordinates of the first elbow of $L_{\rho' |\sigma'}(x)$ by $(X'_0, L'_0)$.
 
@@
 
-The following result, referenced in Sec.~\ref{sec:major_frag}, reduces the Lorenz curve condition on the interval $[0,1]$ to a finite set of independent inequalities and can therefore simplify the computation of relative majorization constraints in practical scenarios.
+The following result reduces the Lorenz curve condition on the interval $[0,1]$ to a finite set of independent inequalities and can therefore simplify the computation of relative majorization constraints in practical scenarios.
 \begin{proposition}\label{thm:elbows}
-	Let $\rho, \rho'$ be any two quantum states with Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\rho'}{\sigma'}(x)$, where $\sigma, \sigma'$ are states with positive Wigner distributions.
-Assume that $\lc{\rho'}{\sigma'}(x)$ has $t$ elbows at locations $x_1, \dots, x_t$.
-Then, $\lc{\rho}{\sigma}(x) \geq \lc{\rho'}{\sigma'}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\rho'}{\sigma'}(x_{i})$ for all $i =1,\dots,t$.
-\end{proposition}
-\begin{proof}	
-If $\lc{\rho}{\sigma}(x) \geq \lc{\rho'}{\sigma'}(x)$ for all $x \in [0,1]$, then the condition on the elbows follows trivially.
+	Let $\rho, \rho'$ be any two quantum states with Lorenz curves $L_{\rho|\sigma}(x), L_{\rho'|\sigma'}(x)$, where $\sigma, \sigma'$ are states with positive Wigner distributions.
+Assume that $L_{\rho'|\sigma'}(x)$ has $t$ elbows at locations $x_1, \dots, x_t$.
+Then, $L_{\rho|\sigma}(x) \geq L_{\rho'|\sigma'}(x)$ for all $x \in [0,1]$ iff $L_{\rho|\sigma}(x_{i}) \geq L_{\rho'|\sigma'}(x_{i})$ for all $i =1,\dots,t$.
+\end{proposition}
+\begin{proof}	
+If $L_{\rho|\sigma}(x) \geq L_{\rho'|\sigma'}(x)$ for all $x \in [0,1]$, then the condition on the elbows follows trivially.
 
@@
 
-\section{General aspects of Lorenz curves for noisy Strange states}
-\label{app:lcsu_technical}
+\section*{Supplementary Note 3: General aspects of Lorenz curves for noisy Strange states}
 
@@
 
-\subsection{Binomial distributions and error bounds}\label{app:phi}
+\subsection*{Binomial distributions and error bounds}
 Consider an experiment consisting of $n$ trials of throwing a coin with probability $p$ of landing on heads and $1-p$ of landing on tails.
@@
 \end{align}
-In Appendix~\ref{app:lcsu_coord}, we will use $\Phi_+$ and $\Phi_-$ to express the elbow coordinates of Lorenz curves for unital protocols.
+In the next section we will use $\Phi_+$ and $\Phi_-$ to express the elbow coordinates of Lorenz curves for unital protocols.
 
@@
 
-\subsection{Lorenz curve coordinates for unital protocols}\label{app:lcsu_coord}
+\subsection*{Lorenz curve coordinates for unital protocols}
 
@@
 
-The Wigner distribution of the $n$--copy $\epsilon$--noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ is given by $\W{\rho_{\rm{S}}(\epsilon)^{\otimes n}} = W_{\rho_{\rm{S}}(\epsilon)}^{\otimes n}$ and, using Proposition~\ref{ncopycomponents} for unital protocols, we can associate it with a set $\{(w_i, m_i)\}_{i=0,\dots,n}$ of component-multiplicity pairs, the elements of which are presented in Table~\ref{tab:lcsu} for all different combinations of physical parameters $n, \epsilon$.
+The Wigner distribution of the $n$--copy $\epsilon$--noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ is given by $W_{\rho_{\rm{S}}(\epsilon)^{\otimes n}} = W_{\rho_{\rm{S}}(\epsilon)}^{\otimes n}$ and, using Proposition~\ref{ncopycomponents} for unital protocols, we can associate it with a set $\{(w_i, m_i)\}_{i=0,\dots,n}$ of component-multiplicity pairs, the elements of which are presented in Supplementary Table~\ref{tab:lcsu} for all different combinations of physical parameters $n, \epsilon$.
 We split the values of index $i$ into two intervals, defined precisely as
@@
 	(x_{i}, L_{i}) = \left( \frac{1}{9^n}\sum_{\ell=0}^i m_{\ell}, \sum_{\ell=0}^i m_{\ell} w_{\ell} \right).
-%\sum_{j: even}^n a^j \binom{n}{j} = \frac{1}{2} [ (1+a)^n + (1-a)^n ]
 \end{equation}
@@
 
-In Table~\ref{tab:lcsu_coord_elb_app}, we present the elbow coordinates of the $n$-copy, $\epsilon$--noisy Strange state Lorenz curve for a unital protocol for any combination of physical parameters $n, \epsilon$.
+In Supplementary Table~\ref{tab:lcsu_coord_elb_app}, we present the elbow coordinates of the $n$-copy, $\epsilon$--noisy Strange state Lorenz curve for a unital protocol for any combination of physical parameters $n, \epsilon$.
 \begin{table}[h]
@@
 
-We can get explicit expressions for all $9^{n}$ points of the Lorenz curve $\lc{\rho_{\rm{S}}(\epsilon)^{\otimes n}}{(\id/3)^{\otimes n}}$, in terms of the elbow coordinates:
+We can get explicit expressions for all $9^{n}$ points of the Lorenz curve $L_{\rho_{\rm{S}}(\epsilon)^{\otimes n}|(\id/3)^{\otimes n}}$, in terms of the elbow coordinates:
 \begin{align}
@@
 
-\section{Temperature-dependent distillation bounds from relative majorization}
-\label{app:lcst_technical}
+\section*{Supplementary Note 4: Temperature-dependent distillation bounds from relative majorization}
 
 Here we prove our main theorem, which bounds magic distillation rates in terms of free energies.
-
-\begingroup
-\def\thetheorem{\ref{thm:free-energy}}
-\begin{theorem}
+\begin{customthm}{7}\label{thm:free-energy}
 	Consider a magic distillation protocol on qutrits that transforms $n$ copies of an $\epsilon$--noisy Strange state into $m$ copies of an $\epsilon'$--noisy Strange state, with depolarising errors $\epsilon' \leq \epsilon \leq 3/7$.
@@
 	Let $T =(k\beta)^{-1}$ be any finite temperature for the physical system and let $H= \sum_{k \in \mathbb{Z}_3} E_k |E_k\>\<E_k|$ be the Hamiltonian of each qutrit subsystem in its eigen-decomposition.
-Assume that in the thermodynamic limit ($n,m \gg 1$), the protocol applied to the equilibrium state $\tau^{\otimes n} = (e^{-\beta H}/\Z)^{\otimes n}$ maps $\tau^{\otimes n} \longrightarrow \tau^{\prime \otimes m}$, where we express state $\tau'$ as $\tau' = e^{-\beta H'}/\Z'$ for some Hermitian $H'$.
-
-Then the magic distillation rate $R = m/n$ for the protocol is bounded by the expression
-\begin{equation}
+Assume that in the thermodynamic limit ($n,m \gg 1$), the protocol applied to the equilibrium state $\tau^{\otimes n} = (e^{-\beta H}/\Z)^{\otimes n}$ maps $\tau^{\otimes n} \longrightarrow \tau^{\prime \otimes m}$, where we write $\tau' = e^{-\beta H'}/\Z'$ for some Hermitian $H'$.
+
+Then the asymptotic magic distillation rate $R = m/n$ is bounded as
+\begin{equation}\label{eq:rate_bounds_proof}
 	R \leq \dfrac{\log \big( 1-\frac{4}{3}\epsilon \big) + \beta (\phi - F)}{\log \big( 1-\frac{4}{3}\epsilon' \big) + \beta (\phi' - F')},
@@
 \begin{align}
-	\zeta &= \sum_{k\in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}, \nonumber\\
-	\alpha_k &= \<E_k| A_{\bmz_\star} |E_k\>,
-\end{align}
-and $W_\tau(\bmz)$ attains a minimum at $\z_\star$. The primed variables are defined similarly for the output system.
-\end{theorem}
-\addtocounter{theorem}{-1}
-\endgroup
+	\zeta &= \sum_{k\in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}, \\
+	\alpha_k &= \<E_k| A_{\z_\star} |E_k\>,
+\end{align}
+and $W_\tau(\z)$ attaining a minimum at $\z=\z_\star$. The primed variables are defined similarly for the output system.
+\end{customthm}
 
@@
 \begin{equation}
-	( W_{\rho_n}(\bmz), W_{\tau_n}(\bmz) ) \succ ( W_{\rho'_m}(\bmz), W_{\tau'_m}(\bmz) ),
+	( W_{\rho_n}(\z), W_{\tau_n}(\z) ) \succ ( W_{\rho'_m}(\z), W_{\tau'_m}(\z) ),
 \end{equation}
@@
 
-We now consider the rescaled Wigner distribution $W_{\rho | \tau}(\bmz) \coloneqq W_\rho(\bmz)/W_\tau(\bmz)$, which is well-defined since $\tau$ is full-rank. 
+We now consider the rescaled Wigner distribution $W_{\rho | \tau}(\z) \coloneqq W_\rho(\z)/W_\tau(\z)$, which is well-defined since $\tau$ is full-rank. 
 Due to the multiplicative property of the Wigner distribution, the rescaled distribution is also multiplicative in the sense that
 \begin{equation}
-	W_{\rho \otimes \rho' | \tau \otimes \tau'} (\bmz_1 \oplus \bmz_2) = W_{\rho | \tau}(\bmz_1)W_{\rho' | \tau'}(\bmz_2),
+	W_{\rho \otimes \rho' | \tau \otimes \tau'} (\z_1 \oplus \z_2) = W_{\rho | \tau}(\z_1)W_{\rho' | \tau'}(\z_2),
 \end{equation}
@@
 \begin{align}
-	W_{\rho_n |\tau_n} (\bmz) &= \prod_{i=1}^n W_{\rho|\tau}(\bmz_i)\\
-	W_{\rho_n } (\bmz) &= \prod_{i=1}^n W_\rho(\bmz_i)
-\end{align}
-where $\bmz = \oplus_{i=1}^n \bmz_i \in \mathbb{Z}_3^{2n}$ is the phase space point for the full system in terms of those of the individual subsystems.
-
-The points defining the Lorenz curve $L_{\rho_n |\tau_n}(x)$ are obtained from sorting the components of $W_{\rho_n |\tau_n}(\bmz)$ in non-increasing order and then computing the partial sums of $W_{\rho_n |\tau_n}(\pi(\bmz))$ where $\pi$ is the permutation that realizes the sorting.
+	W_{\rho_n |\tau_n} (\z) &= \prod_{i=1}^n W_{\rho|\tau}(\z_i)\\
+	W_{\rho_n } (\z) &= \prod_{i=1}^n W_\rho(\z_i)
+\end{align}
+where $\z = \oplus_{i=1}^n \z_i \in \mathbb{Z}_3^{2n}$ is the phase space point for the full system in terms of those of the individual subsystems.
+
+The points defining the Lorenz curve $L_{\rho_n |\tau_n}(x)$ are obtained from sorting the components of $W_{\rho_n |\tau_n}(\z)$ in non-increasing order and then computing the partial sums of $W_{\rho_n |\tau_n}(\pi(\z))$ where $\pi$ is the permutation that realizes the sorting.
 However, similar to the unital protocol analysis, we use the slope constraint (Proposition~\ref{prop:first_elb}) obtained by considering the line segments connecting the origin to the first elbow of both Lorenz curves.
 
-The Wigner distribution of a single noisy Strange state consists of 1 negative component $W_{\rho}(\mathbf{0}) = -v(\epsilon)$ and 8 positive components $W_{\rho}(\bmz) = u(\epsilon)$ for $\bmz \neq \bmo$.
-The Wigner distribution of the full-rank, stabilizer equilibrium state $\tau$ is $W_{\tau}(\bmz) > 0$ for all $\bmz \in \mathbb{Z}_3^2$.
-
-Assume that the smallest component of the distribution $W_\tau(\bmz)$ is at $\bmz=\bmz_\star$.
+The Wigner distribution of a single noisy Strange state consists of 1 negative component $W_{\rho}(\mathbf{0}) = -v(\epsilon)$ and 8 positive components $W_{\rho}(\z) = u(\epsilon)$ for $\z \neq \bmo$.
+The Wigner distribution of the full-rank, stabilizer equilibrium state $\tau$ is $W_{\tau}(\z) > 0$ for all $\z \in \mathbb{Z}_3^2$.
+
+Assume that the smallest component of the distribution $W_\tau(\z)$ is at $\z=\z_\star$.
 Since the magic content of the state is unchanged under a Clifford unitary $C$, we can instead consider the state
 \begin{equation}
-\rho_S(\epsilon) \rightarrow C \rho_S(\epsilon) C^\dagger = D_{\bmz_\star} \rho_S(\epsilon) D_{\bmz_\star}^\dagger,
-\end{equation}
-which has its single negative Wigner component $-v(\epsilon)$ at the point $\bmz_\star$.
+\rho_S(\epsilon) \rightarrow C \rho_S(\epsilon) C^\dagger = D_{\z_\star} \rho_S(\epsilon) D_{\z_\star}^\dagger,
+\end{equation}
+which has its single negative Wigner component $-v(\epsilon)$ at the point $\z_\star$.
 
@@
 \begin{equation}
-	\left(\frac{-v}{W_{\tau}(\bmz_\star)}\right)^{i_{\bmz_\star}} \prod_{\bmz \neq \bmz_\star} \left(\frac{u}{W_{\tau}(\bmz)}\right)^{i_{\bmz}},
+	\left(\frac{-v}{W_{\tau}(\z_\star)}\right)^{i_{\z_\star}} \prod_{\z \neq \z_\star} \left(\frac{u}{W_{\tau}(\z)}\right)^{i_{\z}},
 \end{equation}
@@
 \begin{align}
-&0 \leq i_{\bmz} \leq n \mbox{ for all } \bmz \in \mathbb{Z}_3^2, \nonumber \\
-&\sum_{\bmz \in \mathbb{Z}_3^2} i_{\bmz} = n.
+&0 \leq i_{\z} \leq n \mbox{ for all } \z \in \mathbb{Z}_3^2, \nonumber \\
+&\sum_{\z \in \mathbb{Z}_3^2} i_{\z} = n.
 \end{align}
 We now compute the largest rescaled component.
-Firstly, note that $n$ is even, so we require that $i_{\bmz_\star} \in \{0,2,\dots,n\}$ for the component to be positive.
-Then, we have that $v \geq u$ because $\epsilon \leq 3/7$, and we have already ensured that $W_{\tau}(\bmz_\star) \leq W_{\tau}(\bmz)$ for all $\bmz \in \mathbb{Z}_3^2$.
-Therefore, the largest rescaled component occurs when $i_{\bmz_{\star}} = n$ and $i_{\bmz} = 0$ for $\bmz \neq \bmz_\star$ and is equal to $(v/W_{\tau}(\bmz_\star))^n$.
+Firstly, note that $n$ is even, so we require that $i_{\z_\star} \in \{0,2,\dots,n\}$ for the component to be positive.
+Then, we have that $v \geq u$ because $\epsilon \leq 3/7$, and we have already ensured that $W_{\tau}(\z_\star) \leq W_{\tau}(\z)$ for all $\z \in \mathbb{Z}_3^2$.
+Therefore, the largest rescaled component occurs when $i_{\z_{\star}} = n$ and $i_{\z} = 0$ for $\z \neq \z_\star$ and is equal to $(v/W_{\tau}(\z_\star))^n$.
 The coordinates of the first Lorenz curve point after the origin are given by
 \begin{equation}
-	(x_0, L_0) = ((W_{\tau}(\bmz_\star))^n, v^n)
+	(x_0, L_0) = ((W_{\tau}(\z_\star))^n, v^n)
 \end{equation}
@@
 \begin{align}
-	W_{\tau}(\bmz_\star) &= \frac{1}{3\Z}\tr\left[ A_{\bmz_\star}e^{-\beta H} \right] \nonumber\\
-	&= \frac{e^{\beta F}}{3} \tr\left[ A_{\bmz_\star}\sum_{k \in \mathbb{Z}_3} e^{-\beta E_k} |E_k\>\<E_k| \right] \nonumber\\
+	W_{\tau}(\z_\star) &= \frac{1}{3\Z}\tr\left[ A_{\z_\star}e^{-\beta H} \right] \nonumber\\
+	&= \frac{e^{\beta F}}{3} \tr\left[ A_{\z_\star}\sum_{k \in \mathbb{Z}_3} e^{-\beta E_k} |E_k\>\<E_k| \right] \nonumber\\
 	&= \frac{e^{\beta F}}{3} \sum_{r \in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}
@@
 \begin{align}
-\alpha_k \coloneqq \<E_k |A_{\bmz_\star} |E_k\> \\
+\alpha_k \coloneqq \<E_k |A_{\z_\star} |E_k\> \\
 \zeta \coloneqq  \sum_{k \in \mathbb{Z}_3} \alpha_k e^{-\beta E_k},
@@
 \begin{equation}
-	\alpha_k = \<E_k | A_{\bmz_{\star}} |E_k\> = d W_{|E_k\>\<E_k|}(\bmz_{\star})
-\end{equation}
-Since each $|E_k\>\<E_k|$ is a stabilizer state, their Wigner distributions have orthogonal supports in the phase space, so only one of them, say $k = k_{\star}$ contains point $\bmz_{\star}$ in its support.
-Additionally, its distribution is uniform on its support, so $W_{|E_{k_\star}\>\<E_{k_\star}|}(\bmz_{\star}) = 1/d$.
+	\alpha_k = \<E_k | A_{\z_{\star}} |E_k\> = d W_{|E_k\>\<E_k|}(\z_{\star})
+\end{equation}
+Since each $|E_k\>\<E_k|$ is a stabilizer state, their Wigner distributions have orthogonal supports in the phase space, so only one of them, say $k = k_{\star}$ contains point $\z_{\star}$ in its support.
+Additionally, its distribution is uniform on its support, so $W_{|E_{k_\star}\>\<E_{k_\star}|}(\z_{\star}) = 1/d$.
 
@@
 \phi &= -\beta^{-1}\log (\sum_k \alpha_k e^{-\beta E_k}) \nonumber \\
-&=E_{k_{\star}} \hspace{-2pt}-\hspace{1pt} kT \log (d W_{|E_{k_\star}\>\<E_{k_\star}|}(\bmz_{\star})) =E_{k_{\star}}.
-\end{align}
-
-\end{proof}
-
-\subsection{Dropping pre/post-processing of the magic states}
-\label{app:cliff_processing}
+&=E_{k_{\star}} \hspace{-2pt}-\hspace{1pt} kT \log (d W_{|E_{k_\star}\>\<E_{k_\star}|}(\z_{\star})) =E_{k_{\star}}.
+\end{align}
+
+\end{proof}
+
+\subsection*{Dropping pre/post-processing of the magic states}
 
@@
 
-\begin{theorem}\label{thm:no-processing}
+\begin{proposition}\label{prop:no-processing}
 	Consider a magic distillation protocol on qutrits that transforms
@@
 where $F$ is the free energy of state $\tau$ and all primed quantities are similarly defined for the ouptut system.
-\end{theorem}
-\begin{proof}
-The proof proceeds in the same manner as in Theorem~\ref{thm:free-energy} up to the point where we need to evaluate $W_{\rho_n |\tau_n} (\bmz)$ and $W_{\rho_n}(\bmz)$ explicitly, beyond which we do not have the freedom of additional Clifford processing.
+\end{proposition}
+\begin{proof}
+The proof proceeds in the same manner as in Theorem~\ref{thm:free-energy} up to the point where we need to evaluate $W_{\rho_n |\tau_n} (\z)$ and $W_{\rho_n}(\z)$ explicitly, beyond which we do not have the freedom of additional Clifford processing.
 
@@
 \begin{align}
-	\W[\bmz]{\tau} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z}W_{|k\>\<k|}(q, p) \nonumber\\
+	W_{\tau}(\z) &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z}W_{|k\>\<k|}(q, p) \nonumber\\
 	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z} \delta_{q, k} = \frac{e^{-\beta E_q}}{3\Z},
@@
 where $x$ labels one of the three vertical lines in the phase space.
-The rescaled Wigner distribution $W_{\rho|\tau}(\bmz)$ can now be computed.
+The rescaled Wigner distribution $W_{\rho|\tau}(\z)$ can now be computed.
 It has $9$ components, but these come with multiplicities.
-In total, there are four distinct values on the phase space, as illustrated in Fig.~\ref{fig:pd_split}.
+In total, there are four distinct values on the phase space, as illustrated in Supplementary Figure~\ref{fig:pd_split}.
 \begin{figure}[h]
     \centering
-    \includegraphics[scale=0.35]{figs/pd_split_thermal.pdf}
-    \caption{\textbf{Qutrit phase space regions for $W_{\rho | \tau}(\bmz)$.}
+    \includegraphics[scale=0.35]{pd_split_thermal.pdf}
+    \caption{\textbf{Qutrit phase space regions for $W_{\rho | \tau}(\z)$.}
     Here, the negative component of the magic state overlaps the Wigner distribution of $|0\>$.
@@
 
-We define vectors $\w(\rho), \w(\tau), \w(\rho|\tau)$ based on the values occurring in $W_\rho, W_\tau, W_{\rho|\tau}$ respectively and $\bmm$ as the vector of associated multiplicities of each value in $W_\rho(\bmz)$.
+We define vectors $\w(\rho), \w(\tau), \w(\rho|\tau)$ based on the values occurring in $W_\rho, W_\tau, W_{\rho|\tau}$ respectively and $\m$ as the vector of associated multiplicities of each value in $W_\rho(\z)$.
 Specifically, the component values and multiplicities of the relevant distributions in the four distinct regions are given by
 \begin{align}
-		\bmm &\coloneqq (1,2,3,3), \\
+	\m &\coloneqq (1,2,3,3), \\
 	\w(\rho) &\coloneqq (-v, u, u, u), \\
@@
 
-Using this notation, the values and multiplicities of the $n$--copy distribution $\bmw(\rho_n |\tau_n)$ are computed in Proposition~\ref{ncopycomponents}. The values are given by 
+Using this notation, the values and multiplicities of the $n$--copy distribution $\w(\rho_n |\tau_n)$ are computed in Proposition~\ref{ncopycomponents}. The values are given by 
 \begin{align}\label{eq:ncopy_w_rescaled}
@@
 
-In order to construct the $n$--copy Lorenz curve $L_{\rho_n|\tau_n}(x)$ we need to order the components of the distribution, $w(\rho | \tau)_{ijk}$ in decreasing order, and identify the sequence of indices that give us $W_{\rho_n}(\pi(\bmz))$.
-
-However, in order to obtain a non-trivial bound, it again suffices to use the constraint from the first elbow $(x_0, L_0)$ of $L_{\rho_n|\tau_n}(\bmz)$. We therefore compute the largest component 
+In order to construct the $n$--copy Lorenz curve $L_{\rho_n|\tau_n}(x)$ we need to order the components of the distribution, $w(\rho | \tau)_{ijk}$ in decreasing order, and identify the sequence of indices that give us $W_{\rho_n}(\pi(\z))$.
+
+However, in order to obtain a non-trivial bound, it again suffices to use the constraint from the first elbow $(x_0, L_0)$ of $L_{\rho_n|\tau_n}(\z)$. We therefore compute the largest component 
 \begin{equation}
@@
 
-\section{Single-shot entropies on quasi-distributions and magic distillation bounds}\label{app:single-shot}
+\section*{Supplementary Note 5: Single-shot entropies on quasi-distributions and magic distillation bounds}
 
@@
 
-\subsection{R\'{e}nyi min-divergence from Lorenz curves}
+\subsection*{R\'{e}nyi min-divergence from Lorenz curves}
 We first demonstrate that the initial slope analysis on the Wigner quasi-distributions makes use of the min-relative divergence. We define 
 \begin{equation}
-	D_\infty(W_\rho || W_\tau) \coloneqq \log  \max_{\bmz} \frac{W_\rho(\bmz)}{W_\tau(\bmz)},
+	D_\infty(W_\rho || W_\tau) \coloneqq \log  \max_{\z} \frac{W_\rho(\z)}{W_\tau(\z)},
 \end{equation}
@@
 
-\begingroup
-\def\thetheorem{\ref{thm:Dinfty}}
-\begin{theorem}
-	Let $\tau$ be in the interior of $\F$, then $D_\infty(W_\rho || W_\tau)$ is well-defined for all $\rho$, and the following hold:
+\begin{customthm}{8}
+	Let $\tau$ be in the interior of $\F$. Then $D_\infty(W_\rho || W_\tau)$ is well-defined for all $\rho$, and the following hold:
 \begin{enumerate}
-\item $D_\infty(W_\rho || W_\tau) \geq 0$ for all quantum states $\rho$.
-\item  $D_\infty(W_\rho || W_\tau) = 0$ if and only if $\rho =\tau$.
-\item $D_\infty(W_{\rho^{\otimes 2n}} || W_{\tau^{\otimes 2n}}) = n D_\infty(W_{\rho^{\otimes 2}} || W_{\tau^{\otimes 2}})$ for any $n \in \mathbb{N}$.
-\item For any quantum state $\rho$, and any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$, we have $D_\infty (W_\rho || W_\tau) \geq D_\infty (W_{\E(\rho)} || W_{\E(\tau)})$.
+\item $D_\infty(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) \ge 0$ for all quantum states $\rho$.
+\item  $D_\infty(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) = 0$ if and only if $\rho =\tau$.
+\item $D_\infty(W_{\rho^{\otimes 2n}} \hspace{1pt}||\hspace{1pt} W_{\tau^{\otimes 2n}}) = n D_\infty(W_{\rho^{\otimes 2}} \hspace{1pt}||\hspace{1pt} W_{\tau^{\otimes 2}})$ for any $n \in \mathbb{N}$.
+\item $D_\infty(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau) \geq D_\infty(W_{\E(\rho)} \hspace{1pt}||\hspace{1pt} W_{\E(\tau)})$ for any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$.
 \end{enumerate}
-\end{theorem}
-\addtocounter{theorem}{-1}
-\endgroup
-\begin{proof}
-	Since $\tau$ is in the interior of $\F$, its Wigner function obeys $W_\tau(\bmz) >0$ for all points $\bmz$ in the phase space. 
-In general, $W_\rho(\bmz)$ is a quasi-distribution, but the given form of $\alpha$ ensures that $W_{\rho}(\bmz)^\alpha \geq 0$. 
+\end{customthm}
+\begin{proof}
+	Since $\tau$ is in the interior of $\F$, its Wigner function obeys $W_\tau(\z) >0$ for all points $\z$ in the phase space. 
+In general, $W_\rho(\z)$ is a quasi-distribution, but the given form of $\alpha$ ensures that $W_{\rho}(\z)^\alpha \geq 0$. 
 Therefore $D_\infty (W_\rho || W_\tau)$ is always well-defined.
@@
 \begin{equation}
-	D_\infty(W_\rho || W_\tau) =\log  \max_{\bmz} \frac{W_\rho(\z)}{W_\tau(\z)},
+	D_\infty(W_\rho || W_\tau) =\log  \max_{\z} \frac{W_\rho(\z)}{W_\tau(\z)},
 \end{equation}
@@
 2.
-$D_\infty(W_\rho || W_\tau) = 0$ implies that $\max_{\bmz} \frac{W_\rho(\bmz)}{W_\tau(\bmz)}=1$ and the initial slope of $L_{\rho|\tau}(x)$ is $1$.
-From the concavity of the function and the fact that $L_{\rho|\tau}(1)=1$, this implies that the slope of $L_{\rho|\tau}(x)$ must equal $1$ throughout the interval $[0,1]$ and this, together with the definition of the Lorenz curve, implies that $W_\rho(\bmz)/W_\tau(\bmz) = 1$ for all $\bmz$.
-Since the Wigner representation $\rho \mapsto W_\rho(\bmz)$ is bijective this implies that $\rho = \tau$ only.
+$D_\infty(W_\rho || W_\tau) = 0$ implies that $\max_{\z} \frac{W_\rho(\z)}{W_\tau(\z)}=1$ and the initial slope of $L_{\rho|\tau}(x)$ is $1$.
+From the concavity of the function and the fact that $L_{\rho|\tau}(1)=1$, this implies that the slope of $L_{\rho|\tau}(x)$ must equal $1$ throughout the interval $[0,1]$ and this, together with the definition of the Lorenz curve, implies that $W_\rho(\z)/W_\tau(\z) = 1$ for all $\z$.
+Since the Wigner representation $\rho \mapsto W_\rho(\z)$ is bijective this implies that $\rho = \tau$ only.
 The converse holds by inspection.
@@
 
-If we now let $\w = W_{\rho|\tau}(\bmz) \coloneqq W_{\rho}(\bmz) /W_{\tau}(\bmz)$ we have
-\begin{equation}
-\max_{\bmz_1, \bmz_2, \dots ,\bmz_{2n}} \prod_{k=1}^{2n} W_{\rho|\tau}(\bmz_k) = \left( \max_{\bmz_1, \bmz_2} W_{\rho|\tau}(\bmz_1)W_{\rho|\tau}(\bmz_2) \right)^n
+If we now let $\w = W_{\rho|\tau}(\z) \coloneqq W_{\rho}(\z) /W_{\tau}(\z)$ we have
+\begin{equation}
+\max_{\z_1, \z_2, \dots ,\z_{2n}} \prod_{k=1}^{2n} W_{\rho|\tau}(\z_k) = \left( \max_{\z_1, \z_2} W_{\rho|\tau}(\z_1)W_{\rho|\tau}(\z_2) \right)^n
 \end{equation}
@@
 4.
-The free operation $\E$ in the Wigner representation corresponds to a stochastic map, which sends $W_\tau(\bmz)$ to $W_{\E(\tau)}(\bmz)$, which is another strictly positive probability distribution on the phase space, due to $\E(\tau)$ being in the interior of $\F$.
+The free operation $\E$ in the Wigner representation corresponds to a stochastic map, which sends $W_\tau(\z)$ to $W_{\E(\tau)}(\z)$, which is another strictly positive probability distribution on the phase space, due to $\E(\tau)$ being in the interior of $\F$.
 Moreover, $(W_\rho, W_\tau ) \succ (W_{\E(\rho)} , W_{\E(\tau)})$.
@@
 
-\subsection{Well-defined R\'{e}nyi entropies on quasi-distributions}
+\subsection*{Well-defined R\'{e}nyi entropies on quasi-distributions}
 
@@
 We now have the following fundamental result in majorization theory.
-\begin{theorem}[Schur-Ostrowski theorem~\cite{Schur_1923, Ostrowski_1952, cit:marshall}] 
+\begin{proposition}[Schur-Ostrowski theorem~\cite{Schur_1923, Ostrowski_1952, cit:marshall}] 
 	Let $\D\subseteq \mathbb{R}^N$ be a convex set with non-empty interior, and invariant under permutations of vector components.
@@
 for all $\w$ in the interior of $\mathcal{D}^\downarrow$.
-\end{theorem}
+\end{proposition}
 Since the set $\mathcal{Q}_N$ of quasi-distributions obey the necessary conditions, we get the following result:
-\begin{theorem}
+\begin{proposition}
 	Let $f$ be a real-valued continuous function defined on $\mathcal{Q}_N$ that is continuously differentiable on the interior of $\mathcal{Q}_N$. 
@@
 for all quasi-distributions $\w$ in the interior of $\mathcal{Q}^\downarrow_N$.
-\end{theorem}
+\end{proposition}
 
@@
 We next show that $H_\alpha (\w)$ for $\alpha = 2a/(2b-1)$ is a Schur-concave function on $\mathcal{Q}_N$ provided that $a \ge b$.
-
-\begingroup
-\def\thetheorem{\ref{thm:HSchur}}
-\begin{theorem}
+\begin{customthm}{9}\label{thm:HSchur}
 	If $\alpha = \frac{2a}{2b-1}$ for positive integers $a,b$ with $a \geq b$, then $H_\alpha(\w)$ is well-defined on the set of quasi-distributions $\mathcal{Q}_N$, and moreover if $\w \succ \w'$ for two quasi-distributions $\w, \w'\in \mathcal{Q}_N$ then $H_\alpha (\w) \leq H_\alpha(\w')$.
-\end{theorem}
-\addtocounter{theorem}{-1}
-\endgroup
+\end{customthm}
 \begin{proof}
@@
 
-We note that if $\alpha =r/s$ with both $r$ and $s$ odd, then $H_\alpha$ is not well-defined for all quasi-distributions, although if the actual set of quasi-distributions has a sufficiently bounded levels negativity, then $\log \sum_{\bmz} W_\rho(\bmz)^\alpha$ can still be obtained for $r$ odd, provided the total sum is never negative.
+We note that if $\alpha =r/s$ with both $r$ and $s$ odd, then $H_\alpha$ is not well-defined for all quasi-distributions, although if the actual set of quasi-distributions has a sufficiently bounded levels negativity, then $\log \sum_{\z} W_\rho(\z)^\alpha$ can still be obtained for $r$ odd, provided the total sum is never negative.
 This occurs for Wigner distributions, where we have $|W_\rho(\z)| \leq 1/d$ for a $d$--dimensional quantum system.
@@
 \begin{equation}
-	H_\alpha(W_\rho) \coloneqq \frac{1}{1-\alpha} \log \sum_{\bmz} W_{\rho}(\bmz)^\alpha,
+	H_\alpha(W_\rho) \coloneqq \frac{1}{1-\alpha} \log \sum_{\z} W_{\rho}(\z)^\alpha,
 \end{equation}
@@
     \centering
-    \includegraphics[scale=0.35]{figs/H_vs_eps_a.pdf}
+    \includegraphics[scale=0.35]{H_vs_eps_a.pdf}
     \caption{\textbf{R\'{e}nyi entropy $H_\alpha$ of the $\epsilon$-noisy Strange state.} $H_\alpha$ is increasing in $\alpha$ and $\epsilon$.
@@
 We now show the following equivalence between Wigner negativity and negative R\'{e}nyi entropies.
-\begingroup
-\def\thetheorem{\ref{thm:Magic}}
-\begin{theorem}
+\begin{customthm}{10}
 	A quantum state $\rho$ has Wigner negativity if and only if $H_\alpha(W_\rho) < 0$ for some $\alpha =  \frac{2a}{2b-1}$, with positive integers $a \geq b$.
-\end{theorem}
-\addtocounter{theorem}{-1}
-\endgroup
-\begin{proof} 
-If we have $H_\alpha (W_\rho) <0 $ for $\alpha >1$, then it follows that $\log \sum_{\bmz} W_\rho (\bmz)^\alpha > 1$. 
-However, it is known that $H_\alpha$ is always non-negative on probability distributions, so $W_\rho(\bmz)$ must be a strict quasi-distribution with negativity.
+\end{customthm}
+\begin{proof} 
+If we have $H_\alpha (W_\rho) <0 $ for $\alpha >1$, then it follows that $\log \sum_{\z} W_\rho (\z)^\alpha > 1$. 
+However, it is known that $H_\alpha$ is always non-negative on probability distributions, so $W_\rho(\z)$ must be a strict quasi-distribution with negativity.
 
 Conversely, suppose $\rho$ has negativity in its Wigner representation.
-This in particular implies that $\sum_{\bmz} |W_\rho (\bmz)| >1$.
-We now consider $\sum_{\bmz} W_\rho (\bmz)^{\frac{2a}{2b-1}}$ for positive integers $a\ge b$.
+This in particular implies that $\sum_{\z} |W_\rho (\z)| >1$.
+We now consider $\sum_{\z} W_\rho (\z)^{\frac{2a}{2b-1}}$ for positive integers $a\ge b$.
 We have that
 \begin{align}
-\sum_{\bmz} W_\rho (\bmz)^{\frac{2a}{2b-1}} &= \sum_{\bmz} |W_\rho (\bmz)|^{\frac{2a}{2b-1}} \nonumber \\
-&= \sum_{\bmz} |W_\rho (\bmz)|^{1+ \epsilon},
+\sum_{\z} W_\rho (\z)^{\frac{2a}{2b-1}} &= \sum_{\z} |W_\rho (\z)|^{\frac{2a}{2b-1}} \nonumber \\
+&= \sum_{\z} |W_\rho (\z)|^{1+ \epsilon},
 \end{align}
@@
 \begin{equation}
-\sum_{\bmz} |W_\rho (\bmz)|^{1+ \epsilon_n} \rightarrow \sum_{\bmz} |W_\rho (\bmz)| >1,
+\sum_{\z} |W_\rho (\z)|^{1+ \epsilon_n} \rightarrow \sum_{\z} |W_\rho (\z)| >1,
 \end{equation}
 as $n$ increases.
-Since $\frac{1}{1-\alpha_n} <0$ for any $n$ it follows that $H_{\alpha_n} (W_\rho) = \frac{1}{1-\alpha_n} \log \sum_{\bmz} W_\rho (\bmz)^{\alpha_n}  <0 $ at some point in the sequence, which completes the proof.
+Since $\frac{1}{1-\alpha_n} <0$ for any $n$ it follows that $H_{\alpha_n} (W_\rho) = \frac{1}{1-\alpha_n} \log \sum_{\z} W_\rho (\z)^{\alpha_n}  <0 $ at some point in the sequence, which completes the proof.
 \end{proof}
@@
 
-\subsection{R\'{e}nyi divergences on quasi-distributions}
+\subsection*{R\'{e}nyi divergences on quasi-distributions}
 We now define the $\alpha$-R\'{e}nyi divergence for a quasi-distribution $\w \in \mathcal{Q}_N$ relative to a full-rank probability distribution $\r\in \mathcal{Q}_N^+$ as
@@
 We now specialize to Wigner distributions of quantum states, and quantum operations that map the set of free states $\F$ into itself.
-\begingroup
-\def\thetheorem{\ref{thm:Da_props}}
-\begin{theorem}
-	Let $\tau$ be a state in the interior of $\F$ and $\alpha = 2a / (2b-1)$ for positive integers $a,b$ with $a \geq b$.
-Then, the $\alpha$-R\'{e}nyi divergence $D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)$ is well-defined for all states $\rho$, and the following hold:
+\begin{customthm}{11}\label{thm:Da_props}
+	Let $\tau$ be in the interior of $\F$. 
+	If $\alpha = \frac{2a}{2b-1}$ for positive integers $a,b$ with $a \geq b$, then the $\alpha$-R\'{e}nyi divergence $D_\alpha(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)$ is well-defined for all states $\rho$, and the following hold:
 \begin{enumerate}
@@
 \end{enumerate}
-\end{theorem}
-\addtocounter{theorem}{-1}
-\endgroup
-\begin{proof}
-	Since $\tau$ is in the interior of $\F$, its Wigner function obeys $W_\tau(\bmz) >0$ for all points $\bmz$ in the phase space. 
-In general, $W_\rho(\bmz)$ is a quasi-distribution, but for $\alpha = 2a/2b-1$ we that $W_{\rho}(\bmz)^\alpha \geq 0$. 
+\end{customthm}
+\begin{proof}
+	Since $\tau$ is in the interior of $\F$, its Wigner function obeys $W_\tau(\z) >0$ for all points $\z$ in the phase space. 
+In general, $W_\rho(\z)$ is a quasi-distribution, but for $\alpha = 2a/2b-1$ we that $W_{\rho}(\z)^\alpha \geq 0$. 
 Therefore $D_\alpha (W_\rho || W_\tau)$ is always well-defined and real-valued.
 
-1. $D_\alpha$ is Schur-convex and every pair $(W_{\rho}, W_{\tau})$ majorizes the pair $(W_{\I/d}, W_{\I/d})$, so
-\begin{align}
-	D_\alpha(W_{\rho} \hspace{1pt}||\hspace{1pt} W_{\tau}) \geq D_\alpha(W_{\I/d} \hspace{1pt}||\hspace{1pt} W_{\I/d}) &= \nonumber\\
-	\frac{1}{\alpha-1} \log \sum_{\bmz} W_{\I/d}(\bmz) &= 0.
+1. $D_\alpha$ is Schur-convex and every pair $(W_{\rho}, W_{\tau})$ majorizes the pair $(W_{\id/d}, W_{\id/d})$, so
+\begin{align}
+	D_\alpha(W_{\rho} \hspace{1pt}||\hspace{1pt} W_{\tau}) \geq D_\alpha(W_{\id/d} \hspace{1pt}||\hspace{1pt} W_{\id/d}) &= \nonumber\\
+	\frac{1}{\alpha-1} \log \sum_{\z} W_{\id/d}(\z) &= 0.
 \end{align}
@@
 2.
-In the inequality of property 1, equality holds iff $L_{\rho|\tau}(x) = L_{\I/d|\I/d}(x) = L_{\tau|\tau}(x)$ for all $x\in [0,1]$ due to Proposition~\ref{prop:rmajor} which in turn holds iff $\rho = \tau$.
+In the inequality of property 1, equality holds iff $L_{\rho|\tau}(x) = L_{\id/d|\id/d}(x) = L_{\tau|\tau}(x)$ for all $x\in [0,1]$ due to Proposition~\ref{prop:rmajor} which in turn holds iff $\rho = \tau$.
 
@@
 	&D_\alpha(W_{\rho^{\otimes n}} \hspace{1pt}||\hspace{1pt} W_{\tau^{\otimes n}}) = \nonumber\\
-	&\frac{1}{\alpha - 1} \log \sum_{\bmz} W_{\rho^{\otimes n}}(\bmz)^\alpha W_{\tau^{\otimes n}}(\bmz)^{1-\alpha} = \nonumber\\
-	&\frac{1}{\alpha - 1} \log \sum_{\bmz} \prod_{i=1}^n W_{\rho}(\bmz_i)^\alpha W_{\tau}(\bmz_i)^{1-\alpha} = \nonumber\\
-	&\frac{1}{\alpha - 1} \log \prod_{i=1}^n \sum_{\bmz_i} W_{\rho}(\bmz_i)^\alpha W_{\tau}(\bmz_i)^{1-\alpha} = \nonumber\\
-	&\sum_{i=1}^n \frac{1}{\alpha - 1} \log \sum_{\bmz'} W_{\rho}(\bmz')^\alpha W_{\tau}(\bmz')^{1-\alpha} = \nonumber\\
+	&\frac{1}{\alpha - 1} \log \sum_{\z} W_{\rho^{\otimes n}}(\z)^\alpha W_{\tau^{\otimes n}}(\z)^{1-\alpha} = \nonumber\\
+	&\frac{1}{\alpha - 1} \log \sum_{\z} \prod_{i=1}^n W_{\rho}(\z_i)^\alpha W_{\tau}(\z_i)^{1-\alpha} = \nonumber\\
+	&\frac{1}{\alpha - 1} \log \prod_{i=1}^n \sum_{\z_i} W_{\rho}(\z_i)^\alpha W_{\tau}(\z_i)^{1-\alpha} = \nonumber\\
+	&\sum_{i=1}^n \frac{1}{\alpha - 1} \log \sum_{\z'} W_{\rho}(\z')^\alpha W_{\tau}(\z')^{1-\alpha} = \nonumber\\
 	&= n D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau).
@@
 We are now in a position to derive general magic state distillation bounds.
-
-\begingroup
-\def\thetheorem{\ref{thm:entropic_bounds}}
-\begin{theorem}
-	Consider a general magic state distillation process on prime dimension qudits, that converts a magic state $\rho^{\otimes n} \longrightarrow \E(\rho^{\otimes n})=\rho'^{\otimes m}$and let $\tau$ be any full-rank stabilizer reference state on a qudit.
-Then the distillation rate $R \coloneqq m/n$ is upper bounded as,
+\begin{customthm}{12}
+	Consider a general magic state distillation protocol on odd prime dimension qudits, that converts a magic state $\rho^{\otimes n} \longrightarrow \E(\rho^{\otimes n})=\rho'^{\otimes m}$ and let $\tau$ be any full-rank stabilizer reference state on a qudit.
+Then, the distillation rate $R \coloneqq m/n$ is upper bounded as
 	\begin{equation}
@@
 between the output magic state $\rho'^{\otimes m}$ and $\tau'_m = \E(\tau^{\otimes n})$.
-\end{theorem}
-\addtocounter{theorem}{-1}
-\endgroup
+\end{customthm}
 \begin{proof}
@@
 
+\onecolumngrid
+
+\section*{Supplementary References}
+\vspace{-12pt}
+
+\providecommand{\noopsort}[1]{}\providecommand{\singleletter}[1]{#1}
+\begin{thebibliography}{10}
+\expandafter\ifx\csname url\endcsname\relax
+  \def\url#1{\texttt{#1}}\fi
+\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{}\fi
+\providecommand{\bibinfo}[2]{#2}
+\providecommand{\eprint}[2][]{\url{#2}}
+
+\bibitem{cit:veitch}
+\bibinfo{author}{Veitch, V.}, \bibinfo{author}{Ferrie, C.},
+  \bibinfo{author}{Gross, D.} \& \bibinfo{author}{Emerson, J.}
+\newblock \bibinfo{title}{Negative quasi-probability as a resource for quantum
+  computation}.
+\newblock \emph{\bibinfo{journal}{New Journal of Physics}}
+  \textbf{\bibinfo{volume}{14}}, \bibinfo{pages}{113011}
+  (\bibinfo{year}{2012}).
+\newblock \urlprefix\url{https://doi.org/10.1088/1367-2630/14/11/113011}.
+
+\bibitem{Vourdas_2004}
+\bibinfo{author}{Vourdas, A.}
+\newblock \bibinfo{title}{Quantum systems with finite hilbert space}.
+\newblock \emph{\bibinfo{journal}{Reports on Progress in Physics}}
+  \textbf{\bibinfo{volume}{67}}, \bibinfo{pages}{267--320}
+  (\bibinfo{year}{2004}).
+\newblock \urlprefix\url{https://doi.org/10.1088/0034-4885/67/3/r03}.
+
+\bibitem{Gross2006}
+\bibinfo{author}{Gross, D.}
+\newblock \bibinfo{title}{Hudson’s theorem for finite-dimensional quantum
+  systems}.
+\newblock \emph{\bibinfo{journal}{Journal of Mathematical Physics}}
+  \textbf{\bibinfo{volume}{47}}, \bibinfo{pages}{122107}
+  (\bibinfo{year}{2006}).
+\newblock \urlprefix\url{https://aip.scitation.org/doi/10.1063/1.2393152}.
+
+\bibitem{Wang_2019}
+\bibinfo{author}{Wang, X.}, \bibinfo{author}{Wilde, M.~M.} \&
+  \bibinfo{author}{Su, Y.}
+\newblock \bibinfo{title}{Quantifying the magic of quantum channels}.
+\newblock \emph{\bibinfo{journal}{New Journal of Physics}}
+  \textbf{\bibinfo{volume}{21}}, \bibinfo{pages}{103002}
+  (\bibinfo{year}{2019}).
+\newblock \urlprefix\url{https://doi.org/10.1088/1367-2630/ab451d}.
+
+\bibitem{cit:mirsky}
+\bibinfo{author}{Mirsky, L.}
+\newblock \bibinfo{title}{On the trace of matrix products}.
+\newblock \emph{\bibinfo{journal}{Mathematische Nachrichten}}
+  \textbf{\bibinfo{volume}{20}}, \bibinfo{pages}{171--174}
+  (\bibinfo{year}{1959}).
+\newblock
+  \urlprefix\url{https://onlinelibrary.wiley.com/doi/abs/10.1002/mana.19590200306}.
+
+\bibitem{cit:horodecki2013}
+\bibinfo{author}{Horodecki, M.} \& \bibinfo{author}{Oppenheim, J.}
+\newblock \bibinfo{title}{Fundamental limitations for quantum and nanoscale
+  thermodynamics}.
+\newblock \emph{\bibinfo{journal}{Nature Communications}}
+  \textbf{\bibinfo{volume}{4}}, \bibinfo{pages}{2059} (\bibinfo{year}{2013}).
+\newblock \urlprefix\url{https://doi.org/10.1038/ncomms3059}.
+
+\bibitem{Brandao_2015}
+\bibinfo{author}{Brand{\~a}o, F.}, \bibinfo{author}{Horodecki, M.},
+  \bibinfo{author}{Ng, N.}, \bibinfo{author}{Oppenheim, J.} \&
+  \bibinfo{author}{Wehner, S.}
+\newblock \bibinfo{title}{The second laws of quantum thermodynamics}.
+\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
+  Sciences}} \textbf{\bibinfo{volume}{112}}, \bibinfo{pages}{3275--3279}
+  (\bibinfo{year}{2015}).
+\newblock \urlprefix\url{https://www.pnas.org/content/112/11/3275}.
+
+\bibitem{cit:lostaglio}
+\bibinfo{author}{Lostaglio, M.}
+\newblock \bibinfo{title}{An introductory review of the resource theory
+  approach to thermodynamics}.
+\newblock \emph{\bibinfo{journal}{Reports on Progress in Physics}}
+  \textbf{\bibinfo{volume}{82}}, \bibinfo{pages}{114001}
+  (\bibinfo{year}{2019}).
+\newblock \urlprefix\url{https://doi.org/10.1088/1361-6633/ab46e5}.
+
+\bibitem{cit:marshall}
+\bibinfo{author}{Marshall, A.~W.}, \bibinfo{author}{Olkin, I.} \&
+  \bibinfo{author}{Arnold, B.~C.}
+\newblock \emph{\bibinfo{title}{Inequalities: Theory of Majorization and Its
+  Applications}} (\bibinfo{publisher}{Springer}, \bibinfo{year}{2011}).
+
+\bibitem{ruch_mixing_1978}
+\bibinfo{author}{Ruch, E.}, \bibinfo{author}{Schranner, R.} \&
+  \bibinfo{author}{Seligman, T.~H.}
+\newblock \bibinfo{title}{The mixing distance}.
+\newblock \emph{\bibinfo{journal}{The Journal of Chemical Physics}}
+  \textbf{\bibinfo{volume}{69}}, \bibinfo{pages}{386--392}
+  (\bibinfo{year}{1978}).
+\newblock \urlprefix\url{https://aip.scitation.org/doi/10.1063/1.436364}.
+
+\bibitem{Renes_2016}
+\bibinfo{author}{Renes, J.~M.}
+\newblock \bibinfo{title}{Relative submajorization and its use in quantum
+  resource theories}.
+\newblock \emph{\bibinfo{journal}{Journal of Mathematical Physics}}
+  \textbf{\bibinfo{volume}{57}}, \bibinfo{pages}{122202}
+  (\bibinfo{year}{2016}).
+\newblock \urlprefix\url{https://aip.scitation.org/doi/10.1063/1.4972295}.
+
+\bibitem{Buscemi_2017}
+\bibinfo{author}{Buscemi, F.} \& \bibinfo{author}{Gour, G.}
+\newblock \bibinfo{title}{Quantum relative lorenz curves}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. A}} \textbf{\bibinfo{volume}{95}},
+  \bibinfo{pages}{012110} (\bibinfo{year}{2017}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.95.012110}.
+
+\bibitem{cit:ash}
+\bibinfo{author}{Ash, R.}
+\newblock \emph{\bibinfo{title}{Information Theory}} (\bibinfo{publisher}{Dover
+  Publications Inc.}, \bibinfo{year}{1965}).
+\newblock
+  \urlprefix\url{https://www.semanticscholar.org/paper/Information-Theory-Ash/e9f30be9279c6000ce5602370950748cc2c79101}.
+
+\bibitem{Schur_1923}
+\bibinfo{author}{Schur, I.}
+\newblock \bibinfo{title}{{\"U}ber eine klasse von mittelbildungen mit
+  anwendungen auf die determinantentheorie}.
+\newblock \emph{\bibinfo{journal}{Berliner Mathematische Gesellschaft}}
+  \textbf{\bibinfo{volume}{22}}, \bibinfo{pages}{9--20} (\bibinfo{year}{1923}).
+
+\bibitem{Ostrowski_1952}
+\bibinfo{author}{Ostrowski, A.~M.}
+\newblock \bibinfo{title}{Sur quelques applications des fonctions convexes et
+  concaves au sens de i. schur}.
+\newblock \emph{\bibinfo{journal}{Journal de Mathématiques Pures et
+  Appliquées}} \textbf{\bibinfo{volume}{31}}, \bibinfo{pages}{253--292}
+  (\bibinfo{year}{1952}).
+
+\bibitem{Manfredi_2000}
+\bibinfo{author}{Manfredi, G.} \& \bibinfo{author}{Feix, M.~R.}
+\newblock \bibinfo{title}{Entropy and {W}igner functions}.
+\newblock \emph{\bibinfo{journal}{Phys. Rev. E}} \textbf{\bibinfo{volume}{62}},
+  \bibinfo{pages}{4665--4674} (\bibinfo{year}{2000}).
+\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevE.62.4665}.
+
+\bibitem{Gnutzmann_2001}
+\bibinfo{author}{Gnutzmann, S.} \& \bibinfo{author}{{\.{Z}}yczkowski, K.}
+\newblock \bibinfo{title}{R{\'{e}}nyi-wehrl entropies as measures of
+  localization in phase space}.
+\newblock \emph{\bibinfo{journal}{Journal of Physics A: Mathematical and
+  General}} \textbf{\bibinfo{volume}{34}}, \bibinfo{pages}{10123--10139}
+  (\bibinfo{year}{2001}).
+\newblock \urlprefix\url{https://doi.org/10.1088/0305-4470/34/47/317}.
+
+\end{thebibliography}
+
 \end{document}

### 2022-01-04 npj_revisions/referee_responses.tex
revised manuscript

@@
 \usepackage{graphicx}
-\usepackage[a4paper,left=2cm,right=2cm,bottom=2cm]{geometry}
+\usepackage[a4paper,left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
 \usepackage{fancyhdr}
@@
 
-Thank you for passing on the Reviewers' recommendations.
-In this letter, we address the revisions suggested by both Reviewers, by responding to questions raised and describing the resultant changes which can be found highlighted in the current version of the manuscript.\\
+Thank you for passing on the Reviewers' evaluation of our work. We are very glad that both Reviewers had positive opinions on it, and raised thought-provoking questions for future work.
+
+Below we address the comments of both Reviewers, and respond to questions raised.  The revisions we have made are highlighted in the re-submitted version of the manuscript.\\
 
@@
 
-We thank the Reviewer for the positive comments.
+We thank the Reviewer for the positive comments on our work.
 
@@
 
-We are grateful for suggestions on making our results more accessible -- we have added a proof of the result in Supplementary Note~2 and a reference to it in the main text.
+We are very grateful for suggestions on making our results more accessible -- we have added a proof of the result in Supplementary Note~2 and a reference to it in the main text.
 
@@
 In traditional majorization this kind of thinking has occurred previously -- for example Robin-Hood transforms that take from the rich and give to the poor.
-Of course in the vein of the present paper,  one could construct a ``resource theory of social inequality'' (although calling this a ``resource'' is highly questionable,  except perhaps for billionaire CEOs) in which socialist policies that redistribute wealth more fairly over a population are the ``free/easy operations'' that transform a country.
+Of course in the vein of the present paper,  one could construct a ``resource theory of social inequality'' (although calling this a ``resource'' is questionable,  except perhaps for billionaire CEOs) in which socialist policies that redistribute wealth more fairly over a population are the ``free/easy operations'' that transform a country.
 Distillation protocols on multiple countries would then address the question of the degree to which one could form high levels of inequality in one country solely via collective socialist actions on multiple countries.
@@
 
-Our current bounds can be viewed as describing purely the constraints on distillation coming from Wigner stochasticity, and the bounds are still far above actual distillation rates one can obtain from explicit schemes.
-We have at least narrowed down the high-level principles that determine the ultimate distillation rates achievable, and our work indicates that to make substantially stronger global statements (as opposed to applications of the theory to specific hardware set-ups) one should probably delve into the affine symplectic group structure on the phase space.
-Since free stabilizer operations correspond to the affine symplectic group which is a strict subgroup of the stochastic group, we do not expect our bounds to be achievable by an explicit distillation scheme.
+All existing distillation protocols have rates that are very far from any general upper bounds that have been derived e.g.
+via resource monotones.
+While ours improve on prior upper bounds, there still remains a gap between known rates and our bounds.
+Therefore, we do not know if our upper bounds can be achieved, except in trivial scenarios.
+Since our work captures the constraints due to stochasticity in the Wigner representation, the gap between realisable rates and our bounds implies that the (symplectic) phase space structure is crucial in determining what actual rates can be obtained.
 
@@
 The proposed route to lower bounds would be separate from the method of explicit distillation rates from error correcting codes.
-Instead the proposal is to leverage the critical additional structure that the Wigner distribution carries,  above and beyond involving stochasticity.
+Instead, the proposal is to leverage the critical additional structure that the Wigner distribution carries,  above and beyond involving stochasticity.
 The upper bounds obtained are upper bounds on distillation rates because the set of stochastic maps is a superset for the actual maps that free operations generate.
-Therefore, one can approach things from the other direction: construct a set of stochastic maps that respect the structure of a subgroup of maps that correspond to free operations and then compute the associated majorization constraints for this restricted set.
-This would then provide lower bounds on what free operations can achieve.
+Therefore, one can approach rates from the other direction: construct a set of stochastic maps that respect the structure of a subgroup of maps that correspond to free operations and then compute the associated majorization constraints for this restricted set.
+This would provide lower bounds on what free operations can achieve.
 
@@
 
-\nick{ANSWER}
+This is another interesting suggestion.
+We have done initial calculations on this,  and in principle we could reproduce their results, however to do so would require a more detailed analysis.
+Specifically,  we have computed the Lorenz curves for the pairs of states relative to different probability distributions $\mathbf{r}$ on the phase space.
+In all situations considered the Lorenz curves intersect each other which implies the impossibility of interconversion under channels leaving the distribution $\mathbf{r}$ invariant.
+To complete the proof one would have to prove that this occurs for \emph{all} choices of $\mathbf{r}$.
+%In the case of stabilizer \& Clifford circuits, one can consider $\mathbf{r}$ obtained from stabilizer states and in fact pure stabilizer states would suffice. 
+%If one varies over all $\mathbf{r}$ corresponding to the free states of the theory, then the completeness result given in Theorem 3 of the revised manuscript implies the impossibility of the interconversion.
+Varying over all positive $\mathbf{r}$ would in fact imply a stronger result: the impossibility of interconversion under quantum channels with positive Wigner representations.
 
@@
 We do agree that it is important to better engage the actual classes of operations of interest from a quantum computing perspective, and in recent work we are extending the approach to qubit systems.
-There, it is much more important to be clear on what actual operations are permitted and we better engage such concrete techniques in quantum computing (in particular CSS-code based protocols).
+There, it is much more important to be clear on what actual operations are permitted and we engage deeper with such concrete techniques in quantum computing (in particular CSS-code based protocols).
 
@@
 In this vein,  we note that the symplectic groups for $p=3$ and $p=5$ are finite reflection groups and therefore the associated $G$-majorization for each case is fully solvable in terms of a finite number of conditions.
-
-We further note that the numerically optimal bounds presented in Fig.(1), for which we do not have explicit expressions, depend on the numbers of copies $n,m$ and therefore are not constant for a given ratio $m/n$.
 
@@
 However, if the free operations are still positively represented then we can certainly imagine situations in which the majorization bounds can be improved.
-Perhaps the strategy would be to look for a representation that has the largest contrast between free operations and the target magic state: i.e.
+Perhaps a good strategy would be to look for a representation that has the largest contrast between free operations and the target magic state: i.e.
 all free operations are positively represented,  but the magic state has very ``large'' negativity in this representation.

### 2022-01-04 magic_constraints_maintext_numbered.tex
revised manuscript

--- 2021-12-20 magic_constraints_maintext.tex
@@
 
-\newcommand{\revhigh}[1]{{\color{red}#1}}
 \hypersetup{
@@
 }
+
+\usepackage{lineno}
+\linenumbers
 
@@
 We find that the mana of a magic state is the measure of divergence of these R\'{e}nyi entropies as one approaches the Shannon entropy for Wigner distributions, and discuss how distillation lower bounds could be obtained in this setting.
-\revhigh{REMOVE (NO CLAIMS TO NOVELTY): This use of majorization for quasi-distributions could find application in other studies of non-classicality, and raises novel questions in the context of classical statistical mechanics.}
+This use of majorization for quasi-distributions could find application in other studies of non-classicality, and raises non-trivial questions in the context of classical statistical mechanics.
 \end{abstract}
@@
 \subsection*{Overview of our results}
-\revhigh{
 We begin by describing how stabilizer operations correspond to stochastic maps on a discrete phase space, and how majorization can be applied to constrain magic state transformations.
@@
 These are a subset of protocols that leave invariant some distinguished state or have some equilibrium fixed-point structure.
-We then consider protocols that are non-equilibrium processes, but only generate sub-linear correlations that enable a simple description in the thermodynamic limit before giving entropic analysis that can be applied generally.}
+We then consider protocols that are non-equilibrium processes, but only generate sub-linear correlations that enable a simple description in the thermodynamic limit before giving entropic analysis that can be applied generally.
 
 The relations between the sets of protocols considered are as follows:
-\begin{align}
+\begin{linenomath}\begin{align}
 	\mbox{Unital} &\subset \mbox{ local fixed-points} \nonumber\\ 
 &\subset \mbox{ sub-linear correlations} \subset \mbox{ general protocols.} \nonumber
-\end{align}
+\end{align}\end{linenomath}
 
@@
 The constraints are plotted as a function of the depolarizing error $\epsilon$ for a noisy Strange state (Eq.~(\ref{eq:noisysn})).
-\revhigh{The bound $R_\infty$ follows from a Lorenz curve analysis presented before Eq.~(\ref{eq:unital-bound}), while the bound $R_{10}$ comes from single-shot entropies on the Wigner quasi-distributions, as discussed in the derivation of Eq.~(\ref{eq:Ra})}.
+The bound $R_\infty$ follows from a Lorenz curve analysis presented before Eq.~(\ref{eq:unital-bound}), while the bound $R_{10}$ comes from single-shot entropies on the Wigner quasi-distributions, as discussed in the derivation of Eq.~(\ref{eq:Ra}).
 Numerical bounds $R_{\rm{num}}$ are obtained by using the full set of majorization constraints.
@@
 
-\revhigh{
 \subsection*{Phase space representation of quantum mechanics}
-}
 
@@
 On this space, generalised Pauli matrices $X, Z$ can be defined by their respective roles as shift and phase operators, acting on the basis states as follows,
-\begin{align}
+\begin{linenomath}\begin{align}
     X \ket{k} &= \ket{k + 1} \label{eq:xpauli}\\
 	Z \ket{k} &= \omega^k \ket{k}. \label{eq:zpauli}
-\end{align}
+\end{align}\end{linenomath}
 Here $\omega \coloneqq e^{2\pi i/d}$ is the $d$-th root of unity and addition is taken modulo $d$.
@@
 where now we have
-\begin{align*}
+\begin{linenomath}\begin{align*}
 	\z &\coloneqq (q_1, \dots, q_n, p_1, \dots, p_n) \in \P_{d_1} \times \dots \times \P_{d_n},
-\end{align*}
+\end{align*}\end{linenomath}
 to denote the phase space point for the composite system. 
@@
 Moreover, if $\w, \w', \r, \r'$ are all valid probability distributions with $\r,\r'$ having positive components, then
-\begin{equation*}
+\begin{linenomath}\begin{equation*}
 	(\w, \r) \succ (\w', \r') \mbox{ if and only if } L_{\w |\r}(x) \ge L_{\w' |\r'}(x),
-\end{equation*}
+\end{equation*}\end{linenomath}
 for all $x \in [0,1]$. 
-\revhigh{This result is shown in~\cite{ruch_mixing_1978} and we reproduce it in Supplementary Note~2.}
+This result is shown in~\cite{ruch_mixing_1978} and we reproduce it in Supplementary Note~2.
 It provides a simple way of computing whether relative majorization holds between pairs of probability distributions.
@@
 \end{equation}
-for any $a >0$ and $b \in \mathbb{R}$. This relation implies that
-\begin{align*}
-L_{\w_\epsilon |\r} (x) &\ge L_{\w'_\epsilon |\r'} (x) \nonumber \\ 
-&\mbox{ if and only if }& \\
-\epsilon L_{\w |\r} (x) + (1-\epsilon) x &\ge \epsilon L_{\w' |\r'} (x) + (1-\epsilon) x.
-\end{align*}
+for any $a >0$ and $b \in \mathbb{R}$. 
+This relation implies that $L_{\w_\epsilon |\r} (x) \ge L_{\w'_\epsilon |\r'} (x)$ if and only if $\epsilon L_{\w |\r} (x) + (1-\epsilon) x \ge \epsilon L_{\w' |\r'} (x) + (1-\epsilon) x$. 
 Finally, the $(1-\epsilon)x$ terms cancel on both sides and we get the required relative majorization conditions that $(\w, \r) \succ (\w', \r')$ if and only if $L_{\w | \r} (x) \ge L_{\w' | \r'}(x)$ for all $x \in [0,1]$, as required.
@@
 We show that any magic theory can always be decomposed in terms of `sub-theories' with a particular fixed-point structure, which allows the use of $\d$--majorization.
-\revhigh{Later, we drop the requirement of fixed-points and instead use the full relative majorization, before giving general entropic constraints.}
+Later, we drop the requirement of fixed-points and instead use the full relative majorization, before giving general entropic constraints.
 
@@
 \end{theorem}
-The proof of this is straightforward.
+\noindent The proof of this is straightforward.
 \begin{proof}
@@
 The state $\sigma$ is assumed to have a Wigner distribution with $W_\sigma(\z) > 0$ for all $\z$ in the phase space.
-\revhigh{This is justified because a non-full rank state $\sigma$ can be handled as a limiting case in which we first add an infinitesimal fraction of depolarising noise $\epsilon (\id/d)$ and then take $\epsilon \rightarrow 0$.}
+This is justified because a non-full rank state $\sigma$ can be handled as a limiting case in which we first add an infinitesimal fraction of depolarising noise $\epsilon (\id/d)$ and then take $\epsilon \rightarrow 0$.
 
@@
 For $n$ copies of a qudit system of dimension $d$ the number of terms in $W_{\rho}$ is $d^{2n}$, so imposing the Lorenz curve condition corresponds to exponentially many constraints.
-%Before computing explicit examples, in the next section we describe how these majorization constraints relate to other known monotones.
-
-%\subsection*{Basic monotones for magic distillation for a particular $\R_\sigma$ and the relation to mana}
-
-\revhigh{Before computing explicit examples,} we state some generic aspects of Lorenz curves for magic states, which allow us to interpret previous magic monotones in a new light.
+
+Before computing explicit examples, we state some generic aspects of Lorenz curves for magic states, which allow us to interpret previous magic monotones in a new light.
 The first result gives a simple way to see that the sum-negativity/mana of a magic state is a monotone~\cite{cit:veitch2}.
@@
 Treating the Wigner distributions as vectors, the component values $w_i$ and associated multiplicities $m_i$ in the $n$--copy case are found to be
-\begin{align}
+\begin{linenomath}\begin{align}
 	m_i &= 8^{i}\binom{n}{i}, \\
 	w_i &= u^{i}(-v)^{n-i}, \label{eq:wigu}
-\end{align}
+\end{align}\end{linenomath}
 where index $i$ runs through $0, \dots, n$, and we assume for simplicity that $n$ is even and $\epsilon \leq 3/7$, which implies that $v \geq u$.
@@
 The Lorenz curve $L_{\rho_n|\sigma_n}(x)$ reaches a maximum value of
-\begin{align}\label{eq:lcsu_max}
+\begin{linenomath}\begin{align}\label{eq:lcsu_max}
 	L_\star &\coloneqq L_{\rho_n |\sigma_n} (x_\star) = \sum_{i = 0}^{n/2} m_{2i} w_{2i} \nonumber\\
 	&= \frac{1}{2} + \frac{1}{2}\left(\frac{15 - 8\epsilon}{9}\right)^n > 1,
-\end{align}
+\end{align}\end{linenomath}
 which occurs at $x=x_\star$ given by
@@
 This figure includes numerical estimates of the optimal majorization bounds $R_{\rm{num}}$ obtained by considering the full Lorenz curve, which show that the bound $R_\infty$ can be further improved.
+While this is an improvement on prior results,  all known distillation protocols have rates much lower than these upper bounds.
+It remains a major open question to determine what are the best possible rates that can be achieved.
 
@@
 
-%\subsection*{Temperature-dependent distillation bounds}
-
 The magic state protocol is now considered by how it transforms the pair of quantum states $(\rho^{\otimes n}, \tau^{\otimes n})$ and is then constrained by the relative majorization condition $(W_{\rho}, W_\tau) \succ (W_{\rho'}, W_{\tau'})$ that holds due to the protocol being a stochastic map in the Wigner representation.
@@
 with $\zeta$ given by the expressions
-\begin{align}
+\begin{linenomath}\begin{align}
 	\zeta &= \sum_{k\in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}, \\
 	\alpha_k &= \<E_k| A_{\z_\star} |E_k\>,
-\end{align}
+\end{align}\end{linenomath}
 and $W_\tau(\z)$ attaining a minimum at $\z=\z_\star$. The primed variables are defined similarly for the output system.
@@
 
-\revhigh{
 \subsection*{Technical aspects and special cases of free energy bounds}
-}
 
@@
 \end{equation}
-Therefore, the mana of a state $\rho$ is the residue of a pole in $H_\alpha(W_\rho)$, and quantifies the divergence of the R\'{e}nyi-entropy as we approach the limiting Shannon entropy $H(W_\rho)$.
+Therefore, the mana of a state $\rho$ is minus the residue of the pole at $\alpha=1$ for $H_\alpha(W_\rho)$, and quantifies the divergence of the R\'{e}nyi-entropy as we approach the limiting Shannon entropy $H(W_\rho)$.
 
@@
 
-We can also ask if this approach could additionally provide \emph{lower bounds} for distillation protocols.
+Because Theorem \ref{thm:frag}  provides a completeness statement for majorization, we can ask if this approach could additionally provide \emph{lower bounds} for distillation protocols.
 In contrast to the upper bounds, it is now essential to include the symplectic constraints on the phase space in the majorization relations.
+In principle the resultant majorization (and relative majorization) constraints should provide exact specifications on what can be obtained via free operations.
+Interestingly, this route does not require the use of error correcting codes, but instead is built on group-theoretic features of the phase space. 
 The Clifford group action on a quantum system corresponds to the action of the affine symplectic group $G \coloneqq SL(2,\mathbb{Z}_d) \ltimes \mathbb{Z}_d^2$ on the discrete phase space~\cite{Appleby_2005, Bengtsson_2006}.
@@
 $G$--majorization has been studied in the classical literature and a range of results are known about it~\cite{giovagnoli_1985, steerneman_1990, giovagnoli_cyclic_1996, eaton_1977}.
-\revhigh{One one hand, the sub-group considered may potentially be too simple for distillation to be possible, such as the group corresponding to Weyl covariant channels~\cite{fukuda2006}.
-On the other hand, more non-trivial and useful classes of operations could be analysed but the majorization conditions may not be solvable in closed form.
-However, one can use techniques from semi-definite programming to estimate the distillation rates.
-A nice example occurs when $G$ is a finite reflection group.
-Then, the $G$--majorization pre-order is described by a finite list of conditions~\cite{giovagnoli_1985}, just as is the case for the relative majorization ordering.}
-One route leading to concrete lower bounds on distillation rates is therefore to consider reflection sub-groups of $SL(2,\mathbb{Z}_d) \ltimes \mathbb{Z}_2$, or other simple sub-groups, for which the majorization relation reduces to a finite set of conditions.
-
-The topic of $G$--majorization has been extensively studied, but to our knowledge there has not been work on relative $G$--majorization.
+One can therefore consider sub-groups of the affine symplectic group and analyse the resulting majorization/relative majorization that follows from its action on quasi-distributions.
+However if the sub-group considered is too simple then it may lead to trivial distillation rates.
+An example of this is when we restrict to the set of Weyl covariant channels~\cite{fukuda2006}, which are represented by a convex mixture of displacements on the phase space.
+Initial work by the authors have shown that the majorization conditions for Weyl covariant channels can be solved exactly in terms of discrete Fourier transforms, however it is found that the resultant distillation rates are trivial.
+
+One notable structure that could be exploited for $G$--majorization is when $G$ is a finite reflection group.
+For this,  the $G$--majorization pre-order is guaranteed to be described by a finite list of conditions~\cite{giovagnoli_1985}, just as is the case for the relative majorization ordering.
+Therefore one route to concrete lower bounds on distillation rates is to consider stochastic maps obtained by reflection sub-groups of $SL(2,\mathbb{Z}_d) \ltimes \mathbb{Z}_2$, or other simple sub-groups, for which the majorization relation reduces to a finite set of conditions.
+Beyond this, another promising route is to formulate the majorization conditions for a sub-set of operations as a semi-definite program and then attempt to estimate realisable distillation rates by exploiting dualities and appropriate coarse-grainings.
+This approach has recently been applied by one of the authors to estimate the set of quantum states accessible by covariant channels in the resource theory of asymmetry~\cite{alexander2021} where one allows depolarizing noise that is then minimized.
+It would be of interest to see if a similar approach could be followed for magic state distillation.
+
+Beyond magic state distillation, the topic of $G$--majorization has been extensively studied, but to our knowledge there has not been work on relative $G$--majorization.
 This would correspond to transformations that are not unital.
@@
 
-\revhigh{
 \section*{Methods}
@@
 In order to derive our results we make use of three broad subfields.
+
 The first one is the phase space representation of quantum systems as described in the first section of our Results.
@@
 
-We then make use of various forms of majorization to impose a parital order between magic states.
-In hierarchical order from the specific to the general, we make use of: standard majorization~\cite{cit:marshall}, $\d$-majorization~\cite{Veinott_1971} and relative majorization~\cite{Ruch_1976}.
-
-Finally, the classical R\'{e}nyi entropies and divergences~\cite{renyi_1960} emerge naturally from a majorization setting and possess sufficient properties for the derivation of our entropic bounds.
+We then develop a theory of majorization~\cite{cit:marshall,  Veinott_1971, Ruch_1976} for quasi-distributions so as to impose a partial order between magic states.
+
+Finally, we extend the theory of classical R\'{e}nyi entropies and divergences~\cite{renyi_1960} for probability distributions to quasi-distributions and show that they possess sufficient properties for the derivation of our entropic bounds.
 
 Precise definitions of all the above concepts and explanations of their incorporation to the study of magic distillation are provided in the Results section as the concepts become relevant.
-}
 
@@
 
+\bibitem{alexander2021}
+\bibinfo{author}{Alexander, R.}, \bibinfo{author}{Gvirtz-Chen, S.} \&
+  \bibinfo{author}{Jennings, D.}
+\newblock \bibinfo{title}{Infinitesimal reference frames suffice to determine the asymmetry properties of a quantum system}  (\bibinfo{year}{2021}).
+\newblock \urlprefix\url{https://arxiv.org/abs/2107.14181}.
+
 \bibitem{Arnold_2000}

### 2022-01-04 magic_constraints_supplement.tex
revised manuscript

@@
 \revhigh{
-Restricting the above result in the context of proper probability distributions, we can immediately prove the Lorenz curve condition for probability distributions.
-We first need to define a Lorenz curve \emph{elbow} as a point where the slope of the curve changes, expressed explicitly in Eq.~(15) for Lorenz curve $L_{\w | \r}(x)$
+Restricting the above result in the context of proper probability distributions, we can prove the Lorenz curve condition for probability distributions.
+We define a Lorenz curve \emph{elbow} as a point where the slope of the curve changes, expressed explicitly in Eq.~(15) for Lorenz curve $L_{\w | \r}(x)$
 \begin{proposition}\label{thm:lc_equiv_prob}
@@
 \begin{proof}
-	In the case of $N=N'$ and $\r = \r' = \bmeta$, where $\bmeta = (1/N,1/N,\dots, 1/N)$ is the uniform distribution on $N$ elements, the statement reduces to the Lorenz curve condition for simple majorization which is proven in~\cite{cit:marshall}.
-
-Borrowing the notation of Proposition~\ref{relmaj2maj}, we can define $\Gamma_{\bma} (\w), \Gamma_{\bma'} (\w')$ and the uniform distribution $\bmeta = (1/K, 1/K, \dots, 1/K)$.
-We can then see that the Lorenz curve of $\w$ relative to $\r$ coincides with the Lorenz curve of $\Gamma_{\bma} (\w)$, i.e.
-\begin{equation}
-	L_{\w | \r}(x) = L_{\Gamma_{\bma} (\w) | \bmeta}(x)\ \mbox{for all } x \in [0,1].
-\end{equation}
-This is clear to see by considering the elbows of $L_{\w | \r}(x)$,
+	In the case of $N=N'$ and $\r = \r' = \bmeta$, where $\bmeta = (1/N,1/N,\dots, 1/N)$ is the uniform distribution on $N$ elements, the statement reduces to the Lorenz curve condition $L_{\w}(x) \ge L_{\w'}(x)$ for all $x$, for simple majorization which follows immediately from the defining set of inequalities for majorization~\cite{cit:marshall}.
+Namely, the Lorenz curve $L_{\w}(x)$ for $\w$ is obtained from the partial sums of $\w$ sorted in non-increasing order.
+It is also clear from the definition that the Lorenz curve of $\w$ is given by $L_{\w}(x) = L_{\w | \bmeta}(x)$.
+
+To prove the general statement we reduce the relative majorization Lorenz curve condition to standard majorization.
+Using the notation and assumptions of Proposition~\ref{relmaj2maj} for distributions with rational components, we can define $\Gamma_{\bma} (\w), \Gamma_{\bma'} (\w')$ and the uniform distribution $\bmeta = (1/K, 1/K, \dots, 1/K)$.
+
+The key ingredient in the proof is that the Lorenz curve of $\w$ relative to $\r$ coincides with the Lorenz curve of $\Gamma_{\bma} (\w)$, namely
+\begin{equation}
+	L_{\w | \r}(x) = L_{\Gamma_{\bma} (\w) | \bmeta}(x) = L_{
+	\Gamma_{\bma}(\w)}(x) \mbox{ for all } x \in [0,1].
+\end{equation}
+To see this we consider the elbows of $L_{\w | \r}(x)$,
 \begin{equation}
@@
 \end{equation}
-where permutation $\pi$ sorts $(w_i/r_i)$ in non-increasing order.
+where the permutation $\pi$ sorts $(w_i/r_i)$ in non-increasing order.
 Expressing $\Gamma_{\bma} (\w)$ as
@@
 where $(w_i/r_i, \dots, w_i/r_i)$ has $a_i$ elements, it is clear that permutation $\pi$ sorts $\Gamma_{\bma}(\w)$ in non-increasing order too.
-The elbows of $(y_k, L_{\Gamma_{\bma} (\w) | \bmeta}(y_k))$ then occur at
+The Lorenz curve elbows $(y_k, L_{\Gamma_{\bma} (\w) | \bmeta}(y_k))$ occur at
 \begin{equation}
@@
 \end{equation}
-This argument holds for $\w', \r'$ and $\Gamma_{\bma'} (\w')$ too.
-
-Therefore, in the general case of relative majorization, we have
-\begin{align}
-	&(\w, \r) \succ (\w', \r') &\mbox{ iff} \nonumber\\
-	&\Gamma_{\bma} (\w) \succ \Gamma_{\bma'} (\w') &\mbox{ iff} \nonumber\\
-	&L_{\Gamma_{\bma} (\w) | \bmeta}(x) \geq L_{\Gamma_{\bma'} (\w') | \bmeta}(x),\ x \in [0,1] &\mbox{ iff} \nonumber\\
-	&L_{\w | \r}(x) \geq L_{\w' | \r'}(x),\ x \in [0,1],
-\end{align}
-concluding the proof.
+Therefore, the Lorenz curve of the embedded distribution coincides with the Lorenz curve in the relative majorization setting.
+
+Finally, we have $(\w, \r) \succ (\w', \r')$  if and only if $\Gamma_{\bma} (\w) \succ \Gamma_{\bma'} (\w')$, which holds if and only if $L_{\Gamma_{\bma} (\w) | \bmeta}(x) \geq L_{\Gamma_{\bma'} (\w') | \bmeta}(x)$ for all $x \in [0,1]$, which in turn holds if and only if $L_{\w | \r}(x) \geq L_{\w' | \r'}(x),\ x \in [0,1]$,  which concludes the proof.
 \end{proof}

### 2022-02-24 magic_constraints_manuscript.tex
final submission version

--- 2022-01-04 magic_constraints_maintext_numbered.tex
@@
 
-\usepackage{lineno}
-\linenumbers
+%\usepackage{lineno}
+%\linenumbers
 
@@
 \author{David Jennings}
+	\affiliation{Department of Physics, Imperial College London, London SW7 2AZ, UK}
 	\affiliation{School of Physics and Astronomy, University of Leeds, Leeds, LS2 9JT, UK}
-	\affiliation{Department of Physics, Imperial College London, London SW7 2AZ, UK}
 
@@
 In this work, we develop a framework to analyse magic state distillation protocols where explicit physics of the system is incorporated in the distillation bounds.
-This is achieved by considering how a given magic state protocol transforms a \emph{pair} of quantum states -- one being a noisy magic state, and the other a stabilizer state that is distinguished by the physics of the system (for example a state at a characteristic temperature, or the maximally mixed state) and acts as a reference state for the protocol.
+This is achieved by considering how a given magic state protocol transforms a pair of quantum states -- one being a noisy magic state, and the other a stabilizer state that is distinguished by the physics of the system (for example a state at a characteristic temperature, or the maximally mixed state) and acts as a reference state for the protocol.
 The magic distillation bounds can then be expressed in terms of the physics of the reference state (e.g.~free energy changes in the case of temperature).
@@
 We circumvent this obstacle by making use of a more fundamental tool -- majorization theory~\cite{cit:marshall, Veinott_1971, Ruch_1976}.
-To our knowledge majorization of quasi-distributions has not been considered in quantum physics before, and therefore these methods could find application in other studies of non-classicality in quantum systems~\cite{Fine_1982, Allahverdyan_2018, arvidsson_2020, halpern_2018, Lostaglio_2018, Levy_2020}.
-
-\subsection*{Overview of our results}
+To our knowledge majorization of quasi-distributions has not been considered in quantum physics before, and therefore these methods could find application in other studies of non-classicality in quantum systems~\cite{Fine_1982, Allahverdyan_2018, arvidsson_2020, halpern_2018, Lostaglio_2018, Levy_2020}.\\
+
 We begin by describing how stabilizer operations correspond to stochastic maps on a discrete phase space, and how majorization can be applied to constrain magic state transformations.
@@
 The relations between the sets of protocols considered are as follows:
-\begin{linenomath}\begin{align}
+\begin{align}
 	\mbox{Unital} &\subset \mbox{ local fixed-points} \nonumber\\ 
 &\subset \mbox{ sub-linear correlations} \subset \mbox{ general protocols.} \nonumber
-\end{align}\end{linenomath}
+\end{align}
 
@@
 Numerical bounds $R_{\rm{num}}$ are obtained by using the full set of majorization constraints.
-The new bounds $R_\infty$, $R_{10}$, $R_{\rm{num}}$ all provide stricter constraints than mana~\cite{cit:veitch2} and max--thauma $\theta_{\rm{max}}$~\cite{Wang_2020} bounds for noisy Strange states.
+Bounds $R_\infty$, $R_{10}$, $R_{\rm{num}}$ all provide stricter constraints than mana~\cite{cit:veitch2} and max--thauma $\theta_{\rm{max}}$~\cite{Wang_2020} bounds for noisy Strange states.
     }
@@
 On this space, generalised Pauli matrices $X, Z$ can be defined by their respective roles as shift and phase operators, acting on the basis states as follows,
-\begin{linenomath}\begin{align}
+\begin{align}
     X \ket{k} &= \ket{k + 1} \label{eq:xpauli}\\
 	Z \ket{k} &= \omega^k \ket{k}. \label{eq:zpauli}
-\end{align}\end{linenomath}
+\end{align}
 Here $\omega \coloneqq e^{2\pi i/d}$ is the $d$-th root of unity and addition is taken modulo $d$.
@@
 where now we have
-\begin{linenomath}\begin{align*}
+\begin{align*}
 	\z &\coloneqq (q_1, \dots, q_n, p_1, \dots, p_n) \in \P_{d_1} \times \dots \times \P_{d_n},
-\end{align*}\end{linenomath}
+\end{align*}
 to denote the phase space point for the composite system. 
@@
 
-In any theory of magic, one route to bounding distillation rates is through a \emph{magic monotone}.
+In any theory of magic, one route to bounding distillation rates is through a magic monotone.
 A magic monotone is a real-valued function of any quantum state $M(\rho)$ that is monotonically non-increasing under the free operations of the magic theory.
@@
 
-One prominent magic monotone is the \emph{mana} of a state~\cite{cit:veitch2}, defined as
+One prominent magic monotone is the mana of a state~\cite{cit:veitch2}, defined as
 \begin{equation}
@@
 \end{equation}
-where the \emph{sum-negativity}~\cite{cit:veitch2} is the sum of the negative components in $W_\rho$,
+where the sum-negativity~\cite{cit:veitch2} is the sum of the negative components in $W_\rho$,
 \begin{equation}
@@
 
-In fact, we can further generalize to \emph{relative majorization}~\cite{Blackwell_1953, Ruch_1976, ruch_mixing_1978, Renes_2016, Buscemi_2017, Rethinasamy_2020}, defined as an ordering between pairs of vectors and write
+In fact, we can further generalize to relative majorization~\cite{Blackwell_1953, Ruch_1976, ruch_mixing_1978, Renes_2016, Buscemi_2017, Rethinasamy_2020}, defined as an ordering between pairs of vectors and write
 \begin{equation}
@@
 Given two $n$--component vectors $\w$ and $\r$, we first define $\widetilde{\w}=(\widetilde{w}_i)$, where $\widetilde{w}_i \coloneqq w_i/r_i$, as the vector of component-wise ratios between $\w$ and $\r$.
-We can now define the \emph{Lorenz curve} of $\w$ relative to $\r$, denoted $L_{\w|\r}(x)$, as the piece-wise linear function that passes through $(0,0)$ and the $n$ points
+We can now define the Lorenz curve of $\w$ relative to $\r$, denoted $L_{\w|\r}(x)$, as the piece-wise linear function that passes through $(0,0)$ and the $n$ points
 \begin{equation}\label{eq:lc}
@@
 Moreover, if $\w, \w', \r, \r'$ are all valid probability distributions with $\r,\r'$ having positive components, then
-\begin{linenomath}\begin{equation*}
+\begin{equation*}
 	(\w, \r) \succ (\w', \r') \mbox{ if and only if } L_{\w |\r}(x) \ge L_{\w' |\r'}(x),
-\end{equation*}\end{linenomath}
+\end{equation*}
 for all $x \in [0,1]$. 
@@
 
-However, if $\w$ is a \emph{quasi-probability} distribution with negative values, and $\r$ a regular probability distribution things are different.
+However, if $\w$ is a quasi-probability distribution with negative values, and $\r$ a regular probability distribution things are different.
 Now the Lorenz curve is no longer monotonically increasing, but is a concave function that breaks through the $L_{\w|\r}(x) = 1$ barrier at an interior point and attains some non-trivial maximum $L_\star$ above the value $1$, before decreasing monotonically to $L_{\w|\r}(x)= 1$ at the end-point $x=1$.
@@
 
-Before computing explicit examples, we state some generic aspects of Lorenz curves for magic states, which allow us to interpret previous magic monotones in a new light.
+Before computing explicit examples, we state some generic aspects of Lorenz curves for magic states, which allow us to interpret previous magic monotones as features of the curves.
 The first result gives a simple way to see that the sum-negativity/mana of a magic state is a monotone~\cite{cit:veitch2}.
@@
 The proof of this is given in Supplementary Note~2.
-Using the Lorenz curve perspective, it is also simple to construct new monotones.
-For example, within a given $\R_\sigma$, the area above the horizontal line $y = 1$ is another magic monotone.
+Using the Lorenz curve perspective, it is also simple to construct magic monotones.
+For example, within a given $\R_\sigma$, the area above the horizontal line $y = 1$ is a magic monotone.
 \begin{theorem}
@@
 \end{proof}
-Note though, in contrast to mana, the area monotone is \emph{specific to $\R_\sigma$}, and its value will vary as we change $\sigma$.
+Note though, in contrast to mana, the area monotone is specific to $\R_\sigma$, and its value will vary as we change $\sigma$.
 Therefore its monotonicity depends on the physics of the fixed point and provides a means to analyse magic distillation only under free operations that leave $\sigma$ invariant.
@@
 
-We now construct magic state distillation bounds for protocols that generate \emph{unital} channels, meaning that $\E(\id/d) = \id/d$.
+We now construct magic state distillation bounds for protocols that generate unital channels, meaning that $\E(\id/d) = \id/d$.
 
@@
 Treating the Wigner distributions as vectors, the component values $w_i$ and associated multiplicities $m_i$ in the $n$--copy case are found to be
-\begin{linenomath}\begin{align}
+\begin{align}
 	m_i &= 8^{i}\binom{n}{i}, \\
 	w_i &= u^{i}(-v)^{n-i}, \label{eq:wigu}
-\end{align}\end{linenomath}
+\end{align}
 where index $i$ runs through $0, \dots, n$, and we assume for simplicity that $n$ is even and $\epsilon \leq 3/7$, which implies that $v \geq u$.
@@
 The Lorenz curve $L_{\rho_n|\sigma_n}(x)$ reaches a maximum value of
-\begin{linenomath}\begin{align}\label{eq:lcsu_max}
+\begin{align}\label{eq:lcsu_max}
 	L_\star &\coloneqq L_{\rho_n |\sigma_n} (x_\star) = \sum_{i = 0}^{n/2} m_{2i} w_{2i} \nonumber\\
 	&= \frac{1}{2} + \frac{1}{2}\left(\frac{15 - 8\epsilon}{9}\right)^n > 1,
-\end{align}\end{linenomath}
+\end{align}
 which occurs at $x=x_\star$ given by
@@
 The protocol does not generate magic on its own, so we assume that the output state $\tau'$ is also a Wigner-positive state.
-However, this is generally a \emph{non-equilibrium} state for the system.
+However, this is generally a non-equilibrium state for the system.
 Despite this it is useful to associate an effective Hamiltonian $H'$ to the output state by considering the change $H \rightarrow H'$ such that equilibrium is restored at the reference temperature $T$.
@@
 with $\zeta$ given by the expressions
-\begin{linenomath}\begin{align}
+\begin{align}
 	\zeta &= \sum_{k\in \mathbb{Z}_3} \alpha_k e^{-\beta E_k}, \\
 	\alpha_k &= \<E_k| A_{\z_\star} |E_k\>,
-\end{align}\end{linenomath}
+\end{align}
 and $W_\tau(\z)$ attaining a minimum at $\z=\z_\star$. The primed variables are defined similarly for the output system.
@@
 	\item Quantum computational measures $\epsilon, \epsilon'$,
-\item Thermodynamic quantities $\beta, F, F',$
+	\item Thermodynamic quantities $\beta, F, F'$,
 	\item Intermediate terms $\phi, \phi'$. 
@@
 \end{equation} 
-with $\epsilon \rightarrow 0^+$ through a sequence of rational values. We recall that mana can be written as $\M(\rho) = \log \sum_{\z} |W_\rho(\z)|$, so we obtain a second new perspective on mana:
+with $\epsilon \rightarrow 0^+$ through a sequence of rational values. We recall that mana can be written as $\M(\rho) = \log \sum_{\z} |W_\rho(\z)|$, so we obtain a second perspective on mana:
 \begin{equation}\label{eq:mana-divergence}
@@
 
-Because Theorem \ref{thm:frag}  provides a completeness statement for majorization, we can ask if this approach could additionally provide \emph{lower bounds} for distillation protocols.
+Because Theorem \ref{thm:frag}  provides a completeness statement for majorization, we can ask if this approach could additionally provide lower bounds for distillation protocols.
 In contrast to the upper bounds, it is now essential to include the symplectic constraints on the phase space in the majorization relations.
@@
 
+\subsection*{Mathematical methods used for proofs}
+
 In order to derive our results we make use of three broad subfields.
@@
 \section*{Author contributions}
-DJ conceived the initial idea. 
-Calculations were performed by NK. 
+DJ proposed the initial idea. 
+Derivations were done by NK. 
 Analysis and writing of the manuscript were jointly done by NK and DJ.
@@
   \bibinfo{pages}{172--179} (\bibinfo{year}{2017}).
-\newblock \urlprefix\url{https://www.nature.com/articles/nature23460}.
+%\newblock \urlprefix\url{https://www.nature.com/articles/nature23460}.
 
@@
   (\bibinfo{year}{2001}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.86.5188}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.86.5188}.
 
@@
   \bibinfo{pages}{022312} (\bibinfo{year}{2003}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.68.022312}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.68.022312}.
 
@@
   \bibinfo{pages}{041041} (\bibinfo{year}{2014}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevX.4.041041}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevX.4.041041}.
 
@@
   \bibinfo{pages}{032337} (\bibinfo{year}{2017}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.96.032337}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.96.032337}.
 
@@
 \newblock \bibinfo{title}{Fault-tolerant quantum computation with few qubits}.
-\newblock \emph{\bibinfo{journal}{npj Quantum Information}}
+\newblock \emph{\bibinfo{journal}{npj Quantum Inf.}}
   \textbf{\bibinfo{volume}{4}}, \bibinfo{pages}{1--8} (\bibinfo{year}{2018}).
-\newblock \urlprefix\url{https://www.nature.com/articles/s41534-018-0085-z}.
+%\newblock \urlprefix\url{https://www.nature.com/articles/s41534-018-0085-z}.
 
@@
   code and 7-{CSS} code}.
-\newblock \emph{\bibinfo{journal}{Quantum Information Processing}}
+\newblock \emph{\bibinfo{journal}{Quantum Inf. Process.}}
   \textbf{\bibinfo{volume}{19}}, \bibinfo{pages}{243} (\bibinfo{year}{2020}).
-\newblock \urlprefix\url{https://doi.org/10.1007/s11128-020-02740-3}.
+%\newblock \urlprefix\url{https://doi.org/10.1007/s11128-020-02740-3}.
 
@@
   (\bibinfo{year}{2020}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.102.052415}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.102.052415}.
 
@@
   concatenated cat codes} (\bibinfo{year}{2020}).
-\newblock \urlprefix\url{https://arxiv.org/abs/2012.04108}.
+%\newblock \urlprefix\url{https://arxiv.org/abs/2012.04108}.
 
@@
   \bibinfo{pages}{392} (\bibinfo{year}{2021}).
-\newblock \urlprefix\url{https://doi.org/10.22331/q-2021-02-04-392}.
+%\newblock \urlprefix\url{https://doi.org/10.22331/q-2021-02-04-392}.
 
@@
   (\bibinfo{year}{1998}).
-\newblock \urlprefix\url{https://arxiv.org/abs/quant-ph/9811052}.
+%\newblock \urlprefix\url{https://arxiv.org/abs/quant-ph/9811052}.
 
@@
   functors}.
-\newblock \emph{\bibinfo{journal}{Foundations of Computational Mathematics}}
+\newblock \emph{\bibinfo{journal}{Found. Comut. Math.}}
   \textbf{\bibinfo{volume}{1}}, \bibinfo{pages}{183--204}
   (\bibinfo{year}{2001}).
-\newblock \urlprefix\url{https://doi.org/10.1007/s102080010006}.
+%\newblock \urlprefix\url{https://doi.org/10.1007/s102080010006}.
 
@@
 \newblock \bibinfo{title}{Topological quantum memory}.
-\newblock \emph{\bibinfo{journal}{Journal of Mathematical Physics}}
+\newblock \emph{\bibinfo{journal}{J. Math. Phys.}}
   \textbf{\bibinfo{volume}{43}}, \bibinfo{pages}{4452--4505}
   (\bibinfo{year}{2002}).
-\newblock \urlprefix\url{https://aip.scitation.org/doi/10.1063/1.1499754}.
+%\newblock \urlprefix\url{https://aip.scitation.org/doi/10.1063/1.1499754}.
 
@@
   (\bibinfo{year}{2007}).
-\newblock
-  \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.98.190504}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.98.190504}.
 
@@
   (\bibinfo{year}{2009}).
-\newblock
-  \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.102.110502}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.102.110502}.
 
@@
   \bibinfo{pages}{1098--1105} (\bibinfo{year}{1996}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.54.1098}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.54.1098}.
 
@@
   correction}.
-\newblock \emph{\bibinfo{journal}{Proceedings of the Royal Society A:
-  Mathematical, Physical and Engineering Sciences}}
+\newblock \emph{\bibinfo{journal}{Proc. Math. Phys. Eng. Sci.}}
   \textbf{\bibinfo{volume}{452}}, \bibinfo{pages}{2551--2577}
   (\bibinfo{year}{1996}).
-\newblock
-  \urlprefix\url{https://royalsocietypublishing.org/doi/abs/10.1098/rspa.1996.0136}.
+%\newblock \urlprefix\url{https://royalsocietypublishing.org/doi/abs/10.1098/rspa.1996.0136}.
 
@@
   \bibinfo{pages}{022316} (\bibinfo{year}{2005}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.71.022316}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.71.022316}.
 
@@
   \bibinfo{pages}{042305} (\bibinfo{year}{2013}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.87.042305}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.87.042305}.
 
@@
   \bibinfo{pages}{032338} (\bibinfo{year}{2017}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.95.032338}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.95.032338}.
 
@@
   \bibinfo{pages}{052329} (\bibinfo{year}{2012}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.86.052329}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.86.052329}.
 
@@
   \bibinfo{pages}{31} (\bibinfo{year}{2017}).
-\newblock \urlprefix\url{https://doi.org/10.22331/q-2017-10-03-31}.
+%\newblock \urlprefix\url{https://doi.org/10.22331/q-2017-10-03-31}.
 
@@
   (\bibinfo{year}{2018}).
-\newblock
-  \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.120.050504}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.120.050504}.
 
@@
   \bibinfo{pages}{205} (\bibinfo{year}{2019}).
-\newblock \urlprefix\url{https://doi.org/10.22331/q-2019-12-02-205}.
+%\newblock \urlprefix\url{https://doi.org/10.22331/q-2019-12-02-205}.
 
@@
   \bibinfo{pages}{041021} (\bibinfo{year}{2012}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevX.2.041021}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevX.2.041021}.
 
@@
 \newblock \bibinfo{title}{Qutrit magic state distillation}.
-\newblock \emph{\bibinfo{journal}{New Journal of Physics}}
+\newblock \emph{\bibinfo{journal}{New J. Phys.}}
   \textbf{\bibinfo{volume}{14}}, \bibinfo{pages}{063006}
   (\bibinfo{year}{2012}).
-\newblock \urlprefix\url{https://doi.org/10.1088/1367-2630/14/6/063006}.
+%\newblock \urlprefix\url{https://doi.org/10.1088/1367-2630/14/6/063006}.
 
@@
   (\bibinfo{year}{2015}).
-\newblock
-  \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.115.030501}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.115.030501}.
 
@@
   (\bibinfo{year}{2019}).
-\newblock
-  \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.123.070507}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.123.070507}.
 
@@
   code}.
-\newblock \emph{\bibinfo{journal}{Proceedings of the Royal Society A:
-  Mathematical, Physical and Engineering Sciences}}
+\newblock \emph{\bibinfo{journal}{Proc. Math. Phys. Eng. Sci.}}
   \textbf{\bibinfo{volume}{476}}, \bibinfo{pages}{20200187}
   (\bibinfo{year}{2020}).
-\newblock
-  \urlprefix\url{https://royalsocietypublishing.org/doi/abs/10.1098/rspa.2020.0187}.
+%\newblock \urlprefix\url{https://royalsocietypublishing.org/doi/abs/10.1098/rspa.2020.0187}.
 
@@
   preparation using redundant ancilla encoding and flag qubits}.
-\newblock \emph{\bibinfo{journal}{npj Quantum Information}}
+\newblock \emph{\bibinfo{journal}{npj Quantum Inf.}}
   \textbf{\bibinfo{volume}{6}}, \bibinfo{pages}{91} (\bibinfo{year}{2020}).
-\newblock \urlprefix\url{https://doi.org/10.1038/s41534-020-00319-5}.
+%\newblock \urlprefix\url{https://doi.org/10.1038/s41534-020-00319-5}.
 
@@
   \bibinfo{pages}{143} (\bibinfo{year}{2019}).
-\newblock \urlprefix\url{https://doi.org/10.22331/q-2019-05-20-143}.
+%\newblock \urlprefix\url{https://doi.org/10.22331/q-2019-05-20-143}.
 
@@
   (\bibinfo{year}{2017}).
-\newblock
-  \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.118.060501}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.118.060501}.
 
@@
   \bibinfo{pages}{022316} (\bibinfo{year}{2017}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.95.022316}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.95.022316}.
 
@@
   \bibinfo{pages}{032304} (\bibinfo{year}{2018}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.98.032304}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.98.032304}.
 
@@
   \bibinfo{pages}{010345} (\bibinfo{year}{2021}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PRXQuantum.2.010345}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PRXQuantum.2.010345}.
 
@@
 \newblock \bibinfo{title}{R{\'e}nyi entropy of magic} (\bibinfo{year}{2021}).
-\newblock \urlprefix\url{https://arxiv.org/abs/2106.12587}.
+%\newblock \urlprefix\url{https://arxiv.org/abs/2106.12587}.
 
@@
   (\bibinfo{year}{2019}).
-\newblock
-  \urlprefix\url{https://link.aps.org/doi/10.1103/RevModPhys.91.025001}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/RevModPhys.91.025001}.
 
@@
   \bibinfo{pages}{062332} (\bibinfo{year}{2018}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.97.062332}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.97.062332}.
 
@@
 \newblock \bibinfo{title}{Quantifying magic for multi-qubit operations}.
-\newblock \emph{\bibinfo{journal}{Proceedings of the Royal Society A:
-  Mathematical, Physical and Engineering Sciences}}
+\newblock \emph{\bibinfo{journal}{Proc. Math. Phys. Eng. Sci.}}
   \textbf{\bibinfo{volume}{475}}, \bibinfo{pages}{20190251}
   (\bibinfo{year}{2019}).
-\newblock
-  \urlprefix\url{https://royalsocietypublishing.org/doi/abs/10.1098/rspa.2019.0251}.
+%\newblock \urlprefix\url{https://royalsocietypublishing.org/doi/abs/10.1098/rspa.2019.0251}.
 
@@
 \newblock \bibinfo{title}{Quantifying the magic of quantum channels}.
-\newblock \emph{\bibinfo{journal}{New Journal of Physics}}
+\newblock \emph{\bibinfo{journal}{New J. Phys.}}
   \textbf{\bibinfo{volume}{21}}, \bibinfo{pages}{103002}
   (\bibinfo{year}{2019}).
-\newblock \urlprefix\url{https://doi.org/10.1088/1367-2630/ab451d}.
+%\newblock \urlprefix\url{https://doi.org/10.1088/1367-2630/ab451d}.
 
@@
   in a critical many-body system}.
-\newblock \emph{\bibinfo{journal}{New Journal of Physics}}
+\newblock \emph{\bibinfo{journal}{New J. Phys.}}
   \textbf{\bibinfo{volume}{22}}, \bibinfo{pages}{083077}
   (\bibinfo{year}{2020}).
-\newblock \urlprefix\url{https://doi.org/10.1088/1367-2630/aba919}.
+%\newblock \urlprefix\url{https://doi.org/10.1088/1367-2630/aba919}.
 
@@
   (\bibinfo{year}{2021}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevB.103.075145}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevB.103.075145}.
 
@@
   (\bibinfo{year}{2017}).
-\newblock
-  \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.119.120505}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.119.120505}.
 
@@
   \bibinfo{pages}{351--355} (\bibinfo{year}{2014}).
-\newblock \urlprefix\url{https://doi.org/10.1038/nature13460}.
+%\newblock \urlprefix\url{https://doi.org/10.1038/nature13460}.
 
@@
   (\bibinfo{year}{2020}).
-\newblock
-  \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.125.260404}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.125.260404}.
 
@@
   (\bibinfo{year}{2021}).
-\newblock \urlprefix\url{https://arxiv.org/abs/2104.05822}.
+%\newblock \urlprefix\url{https://arxiv.org/abs/2104.05822}.
 
@@
   ontological models} (\bibinfo{year}{2020}).
-\newblock \urlprefix\url{https://arxiv.org/abs/2005.07161}.
+%\newblock \urlprefix\url{https://arxiv.org/abs/2005.07161}.
 
@@
   \bibinfo{pages}{010331} (\bibinfo{year}{2021}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PRXQuantum.2.010331}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PRXQuantum.2.010331}.
 
@@
   \bibinfo{pages}{031007} (\bibinfo{year}{2012}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevX.2.031007}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevX.2.031007}.
 
@@
   \bibinfo{pages}{021050} (\bibinfo{year}{2017}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevX.7.021050}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevX.7.021050}.
 
@@
   (\bibinfo{year}{2017}).
-\newblock
-  \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.119.180509}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.119.180509}.
 
@@
   \bibinfo{pages}{031027} (\bibinfo{year}{2018}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevX.8.031027}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevX.8.031027}.
 
@@
   \bibinfo{pages}{042308} (\bibinfo{year}{2017}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.95.042308}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.95.042308}.
 
@@
   \bibinfo{pages}{491--495} (\bibinfo{year}{2019}).
-\newblock \urlprefix\url{https://www.nature.com/articles/s41586-019-1040-7}.
+%\newblock \urlprefix\url{https://www.nature.com/articles/s41586-019-1040-7}.
 
@@
   code implementations of magic-state distillation}.
-\newblock \emph{\bibinfo{journal}{Microprocessors and Microsystems}}
+\newblock \emph{\bibinfo{journal}{Microprocess. Microsyst.}}
   \textbf{\bibinfo{volume}{67}}, \bibinfo{pages}{56--70}
   (\bibinfo{year}{2019}).
-\newblock
-  \urlprefix\url{https://www.sciencedirect.com/science/article/pii/S0141933118303314}.
+%\newblock \urlprefix\url{https://www.sciencedirect.com/science/article/pii/S0141933118303314}.
 
@@
   \bibinfo{pages}{011021} (\bibinfo{year}{2018}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevX.8.011021}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevX.8.011021}.
 
@@
   on superconducting quantum processor} (\bibinfo{year}{2018}).
-\newblock \urlprefix\url{https://arxiv.org/abs/2005.07161}.
+%\newblock \urlprefix\url{https://arxiv.org/abs/2005.07161}.
 
@@
   (\bibinfo{year}{2021}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.103.042605}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.103.042605}.
 
@@
 \newblock \bibinfo{title}{The {XZZX} surface code}.
-\newblock \emph{\bibinfo{journal}{Nature Communications}}
+\newblock \emph{\bibinfo{journal}{Nat. Commun.}}
   \textbf{\bibinfo{volume}{12}}, \bibinfo{pages}{2172} (\bibinfo{year}{2021}).
-\newblock \urlprefix\url{https://www.nature.com/articles/s41467-021-22274-1}.
+%\newblock \urlprefix\url{https://www.nature.com/articles/s41467-021-22274-1}.
 
@@
   \bibinfo{pages}{3824--3851} (\bibinfo{year}{1996}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.54.3824}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.54.3824}.
 
@@
   \bibinfo{pages}{041031} (\bibinfo{year}{2019}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevX.9.041031}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevX.9.041031}.
 
@@
   \bibinfo{pages}{052331} (\bibinfo{year}{2008}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.78.052331}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.78.052331}.
 
@@
   \bibinfo{pages}{060301} (\bibinfo{year}{2013}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.88.060301}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.88.060301}.
 
@@
   operations that created it}.
-\newblock \emph{\bibinfo{journal}{New Journal of Physics}}
+\newblock \emph{\bibinfo{journal}{New J. Phys.}}
   \textbf{\bibinfo{volume}{17}}, \bibinfo{pages}{023037}
   (\bibinfo{year}{2015}).
-\newblock \urlprefix\url{https://doi.org/10.1088/1367-2630/17/2/023037}.
+%\newblock \urlprefix\url{https://doi.org/10.1088/1367-2630/17/2/023037}.
 
@@
   \bibinfo{pages}{041015} (\bibinfo{year}{2018}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevX.8.041015}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevX.8.041015}.
 
@@
   \bibinfo{pages}{041053} (\bibinfo{year}{2019}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevX.9.041053}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevX.9.041053}.
 
@@
   surgery} (\bibinfo{year}{2019}).
-\newblock \urlprefix\url{https://arxiv.org/abs/1808.06709}.
+%\newblock \urlprefix\url{https://arxiv.org/abs/1808.06709}.
 
@@
   temperatures: Tightening landauer's principle and the second law}.
-\newblock \emph{\bibinfo{journal}{International Journal of Theoretical
-  Physics}} \textbf{\bibinfo{volume}{39}}, \bibinfo{pages}{2717--2753}
+\newblock \emph{\bibinfo{journal}{Int. J. Theor. Phys.}} \textbf{\bibinfo{volume}{39}}, \bibinfo{pages}{2717--2753}
   (\bibinfo{year}{2000}).
-\newblock \urlprefix\url{https://doi.org/10.1023/A:1026422630734}.
+%\newblock \urlprefix\url{https://doi.org/10.1023/A:1026422630734}.
 
@@
   thermodynamics}.
-\newblock \emph{\bibinfo{journal}{Nature Communications}}
+\newblock \emph{\bibinfo{journal}{Nat. Commun.}}
   \textbf{\bibinfo{volume}{4}}, \bibinfo{pages}{2059} (\bibinfo{year}{2013}).
-\newblock \urlprefix\url{https://doi.org/10.1038/ncomms3059}.
+%\newblock \urlprefix\url{https://doi.org/10.1038/ncomms3059}.
 
@@
 \newblock \bibinfo{title}{The second laws of quantum thermodynamics}.
-\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
-  Sciences}} \textbf{\bibinfo{volume}{112}}, \bibinfo{pages}{3275--3279}
+\newblock \emph{\bibinfo{journal}{PNAS}} \textbf{\bibinfo{volume}{112}}, \bibinfo{pages}{3275--3279}
   (\bibinfo{year}{2015}).
-\newblock \urlprefix\url{https://www.pnas.org/content/112/11/3275}.
+%\newblock \urlprefix\url{https://www.pnas.org/content/112/11/3275}.
 
@@
 \newblock \bibinfo{title}{Quantum thermodynamics}.
-\newblock \emph{\bibinfo{journal}{Contemporary Physics}}
+\newblock \emph{\bibinfo{journal}{Contemp. Phys.}}
   \textbf{\bibinfo{volume}{57}}, \bibinfo{pages}{545--579}
   (\bibinfo{year}{2016}).
-\newblock \urlprefix\url{https://doi.org/10.1080/00107514.2016.1201896}.
+%\newblock \urlprefix\url{https://doi.org/10.1080/00107514.2016.1201896}.
 
@@
   thermodynamics{\textemdash}a topical review}.
-\newblock \emph{\bibinfo{journal}{Journal of Physics A: Mathematical and
-  Theoretical}} \textbf{\bibinfo{volume}{49}}, \bibinfo{pages}{143001}
+\newblock \emph{\bibinfo{journal}{J. Phys. A Math.}} \textbf{\bibinfo{volume}{49}}, \bibinfo{pages}{143001}
   (\bibinfo{year}{2016}).
-\newblock \urlprefix\url{https://doi.org/10.1088/1751-8113/49/14/143001}.
+%\newblock \urlprefix\url{https://doi.org/10.1088/1751-8113/49/14/143001}.
 
@@
   (\bibinfo{year}{2019}).
-\newblock \urlprefix\url{https://doi.org/10.1088/1361-6633/ab46e5}.
+%\newblock \urlprefix\url{https://doi.org/10.1088/1361-6633/ab46e5}.
 
@@
   \bibinfo{pages}{5352} (\bibinfo{year}{2018}).
-\newblock \urlprefix\url{https://doi.org/10.1038/s41467-018-06261-7}.
+%\newblock \urlprefix\url{https://doi.org/10.1038/s41467-018-06261-7}.
 
@@
   necessity of negativity in quasi-probability representations}.
-\newblock \emph{\bibinfo{journal}{Journal of Physics A: Mathematical and
-  Theoretical}} \textbf{\bibinfo{volume}{41}}, \bibinfo{pages}{352001}
+\newblock \emph{\bibinfo{journal}{J. Phys. A Math.}} \textbf{\bibinfo{volume}{41}}, \bibinfo{pages}{352001}
   (\bibinfo{year}{2008}).
-\newblock \urlprefix\url{https://doi.org/10.1088/1751-8113/41/35/352001}.
+%\newblock \urlprefix\url{https://doi.org/10.1088/1751-8113/41/35/352001}.
 
@@
   computation}.
-\newblock \emph{\bibinfo{journal}{New Journal of Physics}}
+\newblock \emph{\bibinfo{journal}{New J. Phys.}}
   \textbf{\bibinfo{volume}{14}}, \bibinfo{pages}{113011}
   (\bibinfo{year}{2012}).
-\newblock \urlprefix\url{https://doi.org/10.1088/1367-2630/14/11/113011}.
+%\newblock \urlprefix\url{https://doi.org/10.1088/1367-2630/14/11/113011}.
 
@@
   (\bibinfo{year}{2012}).
-\newblock
-  \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.109.230503}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.109.230503}.
 
@@
 \bibinfo{author}{{Gottesman}, D.}
-\newblock \emph{\bibinfo{title}{{Stabilizer codes and quantum error
-  correction}}}.
+\newblock \bibinfo{title}{{Stabilizer codes and quantum error
+  correction}}.
 \newblock Ph.D. thesis, \bibinfo{school}{California Institute of Technology}
   (\bibinfo{year}{1997}).
-\newblock \urlprefix\url{https://arxiv.org/abs/quant-ph/9705052}.
+%\newblock \urlprefix\url{https://arxiv.org/abs/quant-ph/9705052}.
 
@@
   \bibinfo{pages}{39–44} (\bibinfo{year}{2005}).
-\newblock \urlprefix\url{https://doi.org/10.1038/nature03350}.
+%\newblock \urlprefix\url{https://doi.org/10.1038/nature03350}.
 
@@
   \bibinfo{pages}{032317} (\bibinfo{year}{2011}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.83.032317}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.83.032317}.
 
@@
   \bibinfo{author}{Arnold, B.~C.}
-\newblock \emph{\bibinfo{title}{Inequalities: Theory of Majorization and Its
+\newblock {\bibinfo{title}{Inequalities: Theory of Majorization and Its
   Applications}} (\bibinfo{publisher}{Springer}, \bibinfo{year}{2011}).
@@
   (\bibinfo{year}{1971}).
-\newblock \urlprefix\url{https://doi.org/10.1287/mnsc.17.9.547}.
+%\newblock \urlprefix\url{https://doi.org/10.1287/mnsc.17.9.547}.
 
@@
   (\bibinfo{year}{1976}).
-\newblock \urlprefix\url{https://doi.org/10.1007/BF01178071}.
+%\newblock \urlprefix\url{https://doi.org/10.1007/BF01178071}.
 
@@
   (\bibinfo{year}{1982}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.48.291}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.48.291}.
 
@@
   \bibinfo{pages}{030102} (\bibinfo{year}{2018}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.97.030102}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.97.030102}.
 
@@
 \newblock \bibinfo{title}{Quantum advantage in postselected metrology}.
-\newblock \emph{\bibinfo{journal}{Nature Communications}}
+\newblock \emph{\bibinfo{journal}{Nat. Commun.}}
   \textbf{\bibinfo{volume}{11}}, \bibinfo{pages}{3775} (\bibinfo{year}{2020}).
-\newblock \urlprefix\url{https://www.nature.com/articles/s41467-020-17559-w}.
+%\newblock \urlprefix\url{https://www.nature.com/articles/s41467-020-17559-w}.
 
@@
   \bibinfo{pages}{042105} (\bibinfo{year}{2018}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.97.042105}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.97.042105}.
 
@@
   (\bibinfo{year}{2018}).
-\newblock
-  \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.120.040602}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.120.040602}.
 
@@
   \bibinfo{pages}{010309} (\bibinfo{year}{2020}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PRXQuantum.1.010309}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PRXQuantum.1.010309}.
 
@@
   computation}.
-\newblock \emph{\bibinfo{journal}{New Journal of Physics}}
+\newblock \emph{\bibinfo{journal}{New J. Phys.}}
   \textbf{\bibinfo{volume}{16}}, \bibinfo{pages}{013009}
   (\bibinfo{year}{2014}).
-\newblock \urlprefix\url{https://doi.org/10.1088/F1367-2630/16/1/013009}.
+%\newblock \urlprefix\url{https://doi.org/10.1088/1367-2630/16/1/013009}.
 
@@
   (\bibinfo{year}{2020}).
-\newblock
-  \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.124.090505}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.124.090505}.
 
@@
   systems}.
-\newblock \emph{\bibinfo{journal}{Journal of Mathematical Physics}}
+\newblock \emph{\bibinfo{journal}{J. Math. Phys.}}
   \textbf{\bibinfo{volume}{47}}, \bibinfo{pages}{122107}
   (\bibinfo{year}{2006}).
-\newblock \urlprefix\url{https://aip.scitation.org/doi/10.1063/1.2393152}.
+%\newblock \urlprefix\url{https://aip.scitation.org/doi/10.1063/1.2393152}.
 
@@
   \bibinfo{pages}{749--759} (\bibinfo{year}{1932}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRev.40.749}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRev.40.749}.
 
@@
   (\bibinfo{year}{2004}).
-\newblock \urlprefix\url{https://doi.org/10.1088/0034-4885/67/3/r03}.
+%\newblock \urlprefix\url{https://doi.org/10.1088/0034-4885/67/3/r03}.
 
@@
   of non-classicality}.
-\newblock \emph{\bibinfo{journal}{Journal of Optics B: Quantum and
-  Semiclassical Optics}} \textbf{\bibinfo{volume}{6}},
+\newblock \emph{\bibinfo{journal}{J. opt. B, Quantum semiclass. opt.}} \textbf{\bibinfo{volume}{6}},
   \bibinfo{pages}{396--404} (\bibinfo{year}{2004}).
-\newblock \urlprefix\url{https://doi.org/10.1088/1464-4266/6/10/003}.
+%\newblock \urlprefix\url{https://doi.org/10.1088/1464-4266/6/10/003}.
 
@@
   operator valued measures and the extended clifford group}.
-\newblock \emph{\bibinfo{journal}{Journal of Mathematical Physics}}
+\newblock \emph{\bibinfo{journal}{J. Math. Phys.}}
   \textbf{\bibinfo{volume}{46}}, \bibinfo{pages}{052107}
   (\bibinfo{year}{2005}).
-\newblock \urlprefix\url{https://doi.org/10.1063/1.1896384}.
+%\newblock \urlprefix\url{https://doi.org/10.1063/1.1896384}.
 
@@
   (\bibinfo{year}{1990}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.65.3373}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.65.3373}.
 
@@
   (\bibinfo{year}{2020}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.101.012350}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.101.012350}.
 
@@
 \bibinfo{author}{Folland, G.~B.}
-\newblock \emph{\bibinfo{title}{Harmonic Analysis in Phase Space}}
+\newblock {\bibinfo{title}{Harmonic Analysis in Phase Space}}
   (\bibinfo{publisher}{Princeton University Press}, \bibinfo{year}{1989}).
-\newblock \urlprefix\url{https://www.jstor.org/stable/j.ctt1b9rzs2}.
+%\newblock \urlprefix\url{https://www.jstor.org/stable/j.ctt1b9rzs2}.
 
@@
 \bibinfo{author}{Bengtsson, I.} \& \bibinfo{author}{{\.{Z}}yczkowski, K.}
-\newblock \emph{\bibinfo{title}{Geometry of Quantum States: An Introduction to
+\newblock {\bibinfo{title}{Geometry of Quantum States: An Introduction to
   Quantum Entanglement}} (\bibinfo{publisher}{Cambridge University Press},
@@
   subtheory is {G}ross's} (\bibinfo{year}{2021}).
-\newblock \urlprefix\url{https://arxiv.org/abs/2101.06263}.
+%\newblock \urlprefix\url{https://arxiv.org/abs/2101.06263}.
 
@@
 \bibinfo{author}{Watrous, J.}
-\newblock \emph{\bibinfo{title}{The Theory of Quantum Information}}
+\newblock {\bibinfo{title}{The Theory of Quantum Information}}
   (\bibinfo{publisher}{Cambridge University Press}, \bibinfo{year}{2018}).
@@
   (\bibinfo{year}{1953}).
-\newblock \urlprefix\url{https://doi.org/10.1214/aoms/1177729032}.
+%\newblock \urlprefix\url{https://doi.org/10.1214/aoms/1177729032}.
 
@@
   (\bibinfo{year}{1999}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.83.436}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.83.436}.
 
@@
   (\bibinfo{year}{2015}).
-\newblock
-  \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.115.210403}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.115.210403}.
 
@@
   processes requires constraints beyond free energy}.
-\newblock \emph{\bibinfo{journal}{Nature Communications}}
+\newblock \emph{\bibinfo{journal}{Nat. Commun.}}
   \textbf{\bibinfo{volume}{6}}, \bibinfo{pages}{6383} (\bibinfo{year}{2015}).
-\newblock \urlprefix\url{https://doi.org/10.1038/ncomms7383}.
+%\newblock \urlprefix\url{https://doi.org/10.1038/ncomms7383}.
 
@@
   (\bibinfo{year}{2015}).
-\newblock \urlprefix\url{https://doi.org/10.1016/j.physrep.2015.04.003}.
+%\newblock \urlprefix\url{https://doi.org/10.1016/j.physrep.2015.04.003}.
 
@@
   \bibinfo{pages}{062104} (\bibinfo{year}{2003}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.67.062104}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.67.062104}.
 
@@
 \newblock \bibinfo{title}{Majorization entropic uncertainty relations}.
-\newblock \emph{\bibinfo{journal}{Journal of Physics A: Mathematical and
-  Theoretical}} \textbf{\bibinfo{volume}{46}}, \bibinfo{pages}{272002}
+\newblock \emph{\bibinfo{journal}{J. Phys. A Math.}} \textbf{\bibinfo{volume}{46}}, \bibinfo{pages}{272002}
   (\bibinfo{year}{2013}).
-\newblock \urlprefix\url{https://doi.org/10.1088/1751-8113/46/27/272002}.
+%\newblock \urlprefix\url{https://doi.org/10.1088/1751-8113/46/27/272002}.
 
@@
   (\bibinfo{year}{2021}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.104.012602}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.104.012602}.
 
@@
 \newblock \bibinfo{title}{The mixing distance}.
-\newblock \emph{\bibinfo{journal}{The Journal of Chemical Physics}}
+\newblock \emph{\bibinfo{journal}{J. Chem. Phys.}}
   \textbf{\bibinfo{volume}{69}}, \bibinfo{pages}{386--392}
   (\bibinfo{year}{1978}).
-\newblock \urlprefix\url{https://aip.scitation.org/doi/10.1063/1.436364}.
+%\newblock \urlprefix\url{https://aip.scitation.org/doi/10.1063/1.436364}.
 
@@
   resource theories}.
-\newblock \emph{\bibinfo{journal}{Journal of Mathematical Physics}}
+\newblock \emph{\bibinfo{journal}{J. Math. Phys.}}
   \textbf{\bibinfo{volume}{57}}, \bibinfo{pages}{122202}
   (\bibinfo{year}{2016}).
-\newblock \urlprefix\url{https://aip.scitation.org/doi/10.1063/1.4972295}.
+%\newblock \urlprefix\url{https://aip.scitation.org/doi/10.1063/1.4972295}.
 
@@
   \bibinfo{pages}{012110} (\bibinfo{year}{2017}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.95.012110}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.95.012110}.
 
@@
   \textbf{\bibinfo{volume}{2}}, \bibinfo{pages}{033455} (\bibinfo{year}{2020}).
-\newblock
-  \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevResearch.2.033455}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevResearch.2.033455}.
 
@@
   \textbf{\bibinfo{volume}{71}} (\bibinfo{year}{1911}).
-\newblock \urlprefix\url{https://doi.org/10.1007/BF01456931}.
+%\newblock \urlprefix\url{https://doi.org/10.1007/BF01456931}.
 
@@
   (\bibinfo{year}{2020}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.102.042409}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevA.102.042409}.
 
@@
   \bibinfo{pages}{343--351} (\bibinfo{year}{1976}).
-\newblock \urlprefix\url{https://doi.org/10.1007/BF00534784}.
+%\newblock \urlprefix\url{https://doi.org/10.1007/BF00534784}.
 
@@
 \newblock \bibinfo{title}{One-and-a-half quantum de finetti theorems}.
-\newblock \emph{\bibinfo{journal}{Communications in Mathematical Physics}}
+\newblock \emph{\bibinfo{journal}{Commun. Math. Phys.}}
   \textbf{\bibinfo{volume}{273}}, \bibinfo{pages}{473--498}
   (\bibinfo{year}{2007}).
-\newblock \urlprefix\url{https://doi.org/10.1007/s00220-007-0189-3}.
+%\newblock \urlprefix\url{https://doi.org/10.1007/s00220-007-0189-3}.
 
@@
   (\bibinfo{year}{2015}).
-\newblock
-  \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.115.150402}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.115.150402}.
 
@@
   shannon entropy}.
-\newblock \emph{\bibinfo{journal}{IEEE Transactions on Information Theory}}
+\newblock \emph{\bibinfo{journal}{IEEE Trans. Inf. Theory}}
   \textbf{\bibinfo{volume}{62}}, \bibinfo{pages}{1711--1720}
   (\bibinfo{year}{2016}).
-\newblock \urlprefix\url{https://ieeexplore.ieee.org/document/7404001}.
+%\newblock \urlprefix\url{https://ieeexplore.ieee.org/document/7404001}.
 
@@
   (\bibinfo{year}{2019}).
-\newblock
-  \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.122.210402}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.122.210402}.
 
@@
 \bibinfo{author}{Pathria, R.~K.} \& \bibinfo{author}{Beale, P.~D.}
-\newblock \emph{\bibinfo{title}{Statistical Mechanics}}
+\newblock {\bibinfo{title}{Statistical Mechanics}}
   (\bibinfo{publisher}{Elsevier}, \bibinfo{year}{2011}).
-\newblock
-  \urlprefix\url{https://www.sciencedirect.com/book/9780123821881/statistical-mechanics}.
+%\newblock \urlprefix\url{https://www.sciencedirect.com/book/9780123821881/statistical-mechanics}.
 
@@
   fault-tolerant photonic quantum computing} (\bibinfo{year}{2021}).
-\newblock \urlprefix\url{https://arxiv.org/abs/2103.08612}.
+%\newblock \urlprefix\url{https://arxiv.org/abs/2103.08612}.
 
@@
   \bibinfo{pages}{933--944} (\bibinfo{year}{1966}).
-\newblock \urlprefix\url{https://doi.org/10.1016/0031-8914(66)90024-3}.
+%\newblock \urlprefix\url{https://doi.org/10.1016/0031-8914(66)90024-3}.
 
@@
   in the quantum regime}.
-\newblock \emph{\bibinfo{journal}{New Journal of Physics}}
+\newblock \emph{\bibinfo{journal}{New J. Phys.}}
   \textbf{\bibinfo{volume}{17}}, \bibinfo{pages}{043003}
   (\bibinfo{year}{2015}).
-\newblock
-  \urlprefix\url{https://iopscience.iop.org/article/10.1088/1367-2630/17/4/043003}.
+%\newblock \urlprefix\url{https://iopscience.iop.org/article/10.1088/1367-2630/17/4/043003}.
 
@@
   \bibinfo{pages}{547--561} (\bibinfo{year}{1960}).
-\newblock
-  \urlprefix\url{https://digitalassets.lib.berkeley.edu/math/ucb/text/math_s4_v1_article-27.pdf}.
+%\newblock \urlprefix\url{https://digitalassets.lib.berkeley.edu/math/ucb/text/math_s4_v1_article-27.pdf}.
 
@@
   \bibinfo{pages}{61--63} (\bibinfo{year}{2011}).
-\newblock \urlprefix\url{https://www.nature.com/articles/nature10123}.
+%\newblock \urlprefix\url{https://www.nature.com/articles/nature10123}.
 
@@
   (\bibinfo{year}{2011}).
-\newblock \urlprefix\url{https://arxiv.org/abs/1102.2098}.
+%\newblock \urlprefix\url{https://arxiv.org/abs/1102.2098}.
 
@@
 \bibinfo{author}{Domb, C.}
-\newblock \emph{\bibinfo{title}{Phase transitions and critical phenomena}}
+\newblock {\bibinfo{title}{Phase transitions and critical phenomena}}
   (\bibinfo{publisher}{Elsevier}, \bibinfo{year}{2000}).
-\newblock
-  \urlprefix\url{https://www.elsevier.com/books/phase-transitions-and-critical-phenomena/domb/978-0-12-220318-3}.
+%\newblock \urlprefix\url{https://www.elsevier.com/books/phase-transitions-and-critical-phenomena/domb/978-0-12-220318-3}.
 
@@
 \bibinfo{author}{{Gour}, G.} \& \bibinfo{author}{{Tomamichel}, M.}
-\newblock \bibinfo{title}{Entropy and relative entropy from
-  information-theoretic principles} (\bibinfo{year}{2020}).
-\newblock \urlprefix\url{https://arxiv.org/abs/2006.11164}.
+\newblock \bibinfo{title}{Entropy and relative entropy from information-theoretic principles}.
+\newblock \emph{\bibinfo{journal}{IEEE Trans. Inf. Theory}} \textbf{\bibinfo{volume}{67}},
+  \bibinfo{pages}{6313-–6327} (\bibinfo{year}{2021}).
+%\newblock \urlprefix\url{http://dx.doi.org/10.1109/TIT.2021.3078337}.
 
@@
 \bibinfo{author}{Tomamichel, M.}
-\newblock \emph{\bibinfo{title}{A Framework for Non-Asymptotic Quantum
+\newblock {\bibinfo{title}{A Framework for Non-Asymptotic Quantum
   Information Theory}}.
 \newblock Ph.D. thesis, \bibinfo{school}{ETH Zurich} (\bibinfo{year}{2012}).
-\newblock \urlprefix\url{https://arxiv.org/abs/1203.2142}.
+%\newblock \urlprefix\url{https://arxiv.org/abs/1203.2142}.
 
@@
 \bibinfo{author}{{Renner}, R.}
-\newblock \emph{\bibinfo{title}{{Security of Quantum Key Distribution}}}.
+\newblock {\bibinfo{title}{{Security of Quantum Key Distribution}}}.
 \newblock Ph.D. thesis, \bibinfo{school}{Swiss Federal Institute of Technology
   Zurich} (\bibinfo{year}{2005}).
-\newblock \urlprefix\url{https://arxiv.org/abs/quant-ph/0512258}.
+%\newblock \urlprefix\url{https://arxiv.org/abs/quant-ph/0512258}.
 
@@
 \bibinfo{author}{Hardy, G.} \emph{et~al.}
-\newblock \emph{\bibinfo{title}{Inequalities}} (\bibinfo{publisher}{Cambridge
+\newblock {\bibinfo{title}{Inequalities}} (\bibinfo{publisher}{Cambridge
   University Press}, \bibinfo{year}{1952}).
-\newblock \urlprefix\url{https://books.google.gr/books?id=t1RCSP8YKt8C}.
+%\newblock \urlprefix\url{https://books.google.gr/books?id=t1RCSP8YKt8C}.
 
@@
   orderings}.
-\newblock \emph{\bibinfo{journal}{Linear Algebra and its Applications}}
+\newblock \emph{\bibinfo{journal}{Linear Algebra Appl.}}
   \textbf{\bibinfo{volume}{67}}, \bibinfo{pages}{111--135}
   (\bibinfo{year}{1985}).
-\newblock
-  \urlprefix\url{https://www.sciencedirect.com/science/article/pii/0024379585901909}.
+%\newblock \urlprefix\url{https://www.sciencedirect.com/science/article/pii/0024379585901909}.
 
@@
   reflection groups}.
-\newblock \emph{\bibinfo{journal}{Linear Algebra and its Applications}}
+\newblock \emph{\bibinfo{journal}{Linear Algebra Appl.}}
   \textbf{\bibinfo{volume}{127}}, \bibinfo{pages}{107--119}
   (\bibinfo{year}{1990}).
-\newblock
-  \urlprefix\url{https://www.sciencedirect.com/science/article/pii/002437959090338D}.
+%\newblock \urlprefix\url{https://www.sciencedirect.com/science/article/pii/002437959090338D}.
 
@@
 \newblock \bibinfo{title}{Cyclic majorization and smoothing operators}.
-\newblock \emph{\bibinfo{journal}{Linear Algebra and its Applications}}
+\newblock \emph{\bibinfo{journal}{Linear Algebra Appl.}}
   \textbf{\bibinfo{volume}{239}}, \bibinfo{pages}{215--225}
   (\bibinfo{year}{1996}).
-\newblock
-  \urlprefix\url{https://www.sciencedirect.com/science/article/pii/S0024379596900130}.
+%\newblock \urlprefix\url{https://www.sciencedirect.com/science/article/pii/S0024379596900130}.
 
@@
   (\bibinfo{year}{1977}).
-\newblock \urlprefix\url{https://doi.org/10.1214/aop/1176995655}.
+%\newblock \urlprefix\url{https://doi.org/10.1214/aop/1176995655}.
 
@@
 \newblock \bibinfo{title}{On weyl-covariant channels}  (\bibinfo{year}{2006}).
-\newblock \urlprefix\url{http://arxiv.org/abs/quant-ph/0510148}.
+%\newblock \urlprefix\url{http://arxiv.org/abs/quant-ph/0510148}.
 
@@
 \newblock \bibinfo{title}{Infinitesimal reference frames suffice to determine the asymmetry properties of a quantum system}  (\bibinfo{year}{2021}).
-\newblock \urlprefix\url{https://arxiv.org/abs/2107.14181}.
+%\newblock \urlprefix\url{https://arxiv.org/abs/2107.14181}.
 
@@
 \newblock \bibinfo{title}{Symplectic geometry and topology}.
-\newblock \emph{\bibinfo{journal}{Journal of Mathematical Physics}}
+\newblock \emph{\bibinfo{journal}{J. Math. Phys.}}
   \textbf{\bibinfo{volume}{41}}, \bibinfo{pages}{3307--3343}
   (\bibinfo{year}{2000}).
-\newblock \urlprefix\url{https://doi.org/10.1063/1.533315}.
+%\newblock \urlprefix\url{https://doi.org/10.1063/1.533315}.
 
@@
   (\bibinfo{year}{1980}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.45.494}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevLett.45.494}.
 
@@
 \bibinfo{author}{Barnett, S.~M.} \& \bibinfo{author}{Radmore, P.~M.}
-\newblock \emph{\bibinfo{title}{Methods in Theoretical Quantum Optics}}.
+\newblock \bibinfo{title}{Methods in Theoretical Quantum Optics}.
 \newblock Oxford science publications (\bibinfo{publisher}{Clarendon Press},
   \bibinfo{year}{1997}).
-\newblock \urlprefix\url{https://books.google.gr/books?id=Hp5z09gPmC8C}.
+%\newblock \urlprefix\url{https://books.google.gr/books?id=Hp5z09gPmC8C}.
 

### 2022-02-24 npj_revisions/manuscript files/magic_constraints_maintext.tex
final submission version

--- 2021-12-20 magic_constraints_maintext.tex
@@
 For $n$ copies of a qudit system of dimension $d$ the number of terms in $W_{\rho}$ is $d^{2n}$, so imposing the Lorenz curve condition corresponds to exponentially many constraints.
-%Before computing explicit examples, in the next section we describe how these majorization constraints relate to other known monotones.
-
-%\subsection*{Basic monotones for magic distillation for a particular $\R_\sigma$ and the relation to mana}
 
@@
 This figure includes numerical estimates of the optimal majorization bounds $R_{\rm{num}}$ obtained by considering the full Lorenz curve, which show that the bound $R_\infty$ can be further improved.
+\revhigh{While this is an improvement on prior results,  all known distillation protocols have rates much lower than these upper bounds.
+It remains a major open question to determine what are the best possible rates that can be achieved.}
 
@@
 This Hamiltonian is defined by the expression $\tau' = e^{-\beta H'}/\Z'$, and has free energy $F' = -\beta^{-1} \log \Z'$.
-
-%\subsection*{Temperature-dependent distillation bounds}
 
@@
 \end{equation}
-Therefore, the mana of a state $\rho$ is the residue of a pole in $H_\alpha(W_\rho)$, and quantifies the divergence of the R\'{e}nyi-entropy as we approach the limiting Shannon entropy $H(W_\rho)$.
+Therefore, the mana of a state $\rho$ is minus the residue of the pole at $\alpha=1$ for $H_\alpha(W_\rho)$, and quantifies the divergence of the R\'{e}nyi entropy as we approach the limiting Shannon entropy $H(W_\rho)$.
 
@@
 
-We can also ask if this approach could additionally provide \emph{lower bounds} for distillation protocols.
+Because Theorem \ref{thm:frag}  provides a completeness statement for majorization, we can ask if this approach could additionally provide \emph{lower bounds} for distillation protocols.
 In contrast to the upper bounds, it is now essential to include the symplectic constraints on the phase space in the majorization relations.
-The Clifford group action on a quantum system corresponds to the action of the affine symplectic group $G \coloneqq SL(2,\mathbb{Z}_d) \ltimes \mathbb{Z}_d^2$ on the discrete phase space~\cite{Appleby_2005, Bengtsson_2006}.
+\revhigh{In principle the resultant majorization (and relative majorization) constraints should provide exact specifications on what can be obtained via free operations.
+Interestingly, this route does not require the use of error correcting codes, but instead is built on group-theoretic features of the phase space.
+} The Clifford group action on a quantum system corresponds to the action of the affine symplectic group $G \coloneqq SL(2,\mathbb{Z}_d) \ltimes \mathbb{Z}_d^2$ on the discrete phase space~\cite{Appleby_2005, Bengtsson_2006}.
 Therefore, any convex mixture of Clifford unitaries will correspond to a convex mixture of these group actions.
@@
 $G$--majorization has been studied in the classical literature and a range of results are known about it~\cite{giovagnoli_1985, steerneman_1990, giovagnoli_cyclic_1996, eaton_1977}.
-\revhigh{One one hand, the sub-group considered may potentially be too simple for distillation to be possible, such as the group corresponding to Weyl covariant channels~\cite{fukuda2006}.
-On the other hand, more non-trivial and useful classes of operations could be analysed but the majorization conditions may not be solvable in closed form.
-However, one can use techniques from semi-definite programming to estimate the distillation rates.
-A nice example occurs when $G$ is a finite reflection group.
-Then, the $G$--majorization pre-order is described by a finite list of conditions~\cite{giovagnoli_1985}, just as is the case for the relative majorization ordering.}
-One route leading to concrete lower bounds on distillation rates is therefore to consider reflection sub-groups of $SL(2,\mathbb{Z}_d) \ltimes \mathbb{Z}_2$, or other simple sub-groups, for which the majorization relation reduces to a finite set of conditions.
-
-The topic of $G$--majorization has been extensively studied, but to our knowledge there has not been work on relative $G$--majorization.
+\revhigh{One can therefore consider sub-groups of the affine symplectic group and analyse the resulting majorization/relative majorization that follows from its action on quasi-distributions.
+However if the sub-group considered is too simple then it may lead to trivial distillation rates.
+An example of this is when we restrict to the set of Weyl covariant channels~\cite{fukuda2006}, which are represented by a convex mixture of displacements on the phase space.
+Initial work by the authors have shown that the majorization conditions for Weyl covariant channels can be solved exactly in terms of discrete Fourier transforms, however it is found that the resultant distillation rates are trivial.
+
+One notable structure that could be exploited for $G$--majorization is when $G$ is a finite reflection group.
+For this,  the $G$--majorization pre-order is guaranteed to be described by a finite list of conditions~\cite{giovagnoli_1985}, just as is the case for the relative majorization ordering.} Therefore one route to concrete lower bounds on distillation rates is to consider stochastic maps obtained by reflection sub-groups of $SL(2,\mathbb{Z}_d) \ltimes \mathbb{Z}_2$, or other simple sub-groups, for which the majorization relation reduces to a finite set of conditions.
+\revhigh{Beyond this, another promising route is to formulate the majorization conditions for a sub-set of operations as a semi-definite program and then attempt to estimate realisable distillation rates by exploiting dualities and appropriate coarse-grainings.
+This approach has recently been applied by one of the authors to estimate the set of quantum states accessible by covariant channels in the resource theory of asymmetry~\cite{alexander2021} where one allows depolarizing noise that is then minimized.
+It would be of interest to see if a similar approach could be followed for magic state distillation.}
+
+Beyond magic state distillation, the topic of $G$--majorization has been extensively studied, but to our knowledge there has not been work on relative $G$--majorization.
 This would correspond to transformations that are not unital.
@@
 
-We then make use of various forms of majorization to impose a parital order between magic states.
-In hierarchical order from the specific to the general, we make use of: standard majorization~\cite{cit:marshall}, $\d$-majorization~\cite{Veinott_1971} and relative majorization~\cite{Ruch_1976}.
-
-Finally, the classical R\'{e}nyi entropies and divergences~\cite{renyi_1960} emerge naturally from a majorization setting and possess sufficient properties for the derivation of our entropic bounds.
+We then develop a theory of majorization~\cite{cit:marshall,  Veinott_1971, Ruch_1976} for quasi-distributions so as to impose a partial order between magic states.
+
+Finally, we extend the theory of classical R\'{e}nyi entropies and divergences~\cite{renyi_1960} for probability distributions to quasi-distributions and show that they possess sufficient properties for the derivation of our entropic bounds.
 
@@
   (\bibinfo{year}{2014}).
-\newblock \urlprefix\url{https://doi.org/10.1088/F1367-2630/16/1/013009}.
+\newblock \urlprefix\url{https://doi.org/10.1088/1367-2630/16/1/013009}.
 

### 2022-02-24 npj_revisions/manuscript files/magic_constraints_supplement.tex
final submission version

--- 2022-01-04 magic_constraints_supplement.tex
@@
 
-\newcommand{\revhigh}[1]{{\color{red}#1}}
+\def\bibsection{\vspace{45pt}}
+
+%\newcommand{\revhigh}[1]{{\color{red}#1}}
 \hypersetup{
@@
 
-The claim is equivalent to the statement that there exists a \emph{bistochastic map} $B$ sending $\Gamma_{\bma}(\w)$ to $\Gamma_{\bma'}(\w')$ if and only if there exists a stochastic map $A$ sending $\w$ to $\w'$ and $\r$ to $\r'$.
+The claim is equivalent to the statement that there exists a bistochastic map $B$ sending $\Gamma_{\bma}(\w)$ to $\Gamma_{\bma'}(\w')$ if and only if there exists a stochastic map $A$ sending $\w$ to $\w'$ and $\r$ to $\r'$.
 
@@
 
-\revhigh{
 Restricting the above result in the context of proper probability distributions, we can prove the Lorenz curve condition for probability distributions.
-We define a Lorenz curve \emph{elbow} as a point where the slope of the curve changes, expressed explicitly in Eq.~(15) for Lorenz curve $L_{\w | \r}(x)$
+We define a Lorenz curve elbow as a point where the slope of the curve changes, expressed explicitly in Eq.~(15) for Lorenz curve $L_{\w | \r}(x)$
 \begin{proposition}\label{thm:lc_equiv_prob}
@@
 \end{proof}
-}
 
@@
 
-The following result is used \revhigh{in the main text} to extend the Lorenz curve condition of Proposition~\ref{thm:lc_equiv_prob} into the context of quasi-distributions.
+The following result is used in the main text to extend the Lorenz curve condition of Proposition~\ref{thm:lc_equiv_prob} into the context of quasi-distributions.
 \begin{proposition}\label{Lorenz_linearity}
@@
 
-To each Wigner distribution $W_\rho(\z)$ we can associate \emph{component-multiplicity} pairs $\{(w_i, m_i)\}$ where the value $w_i$ occurs in the distribution $W_\rho(\z)$ with multiplicity $m_i$.
+To each Wigner distribution $W_\rho(\z)$ we can associate component-multiplicity pairs $\{(w_i, m_i)\}$ where the value $w_i$ occurs in the distribution $W_\rho(\z)$ with multiplicity $m_i$.
 
@@
 
-We define the notion of \emph{Schur-convex and Schur-convave functions} on a subset $\D \subseteq \mathbb{R}^N$.
+We define the notion of Schur-convex and Schur-convave functions on a subset $\D \subseteq \mathbb{R}^N$.
 \begin{definition} 
@@
 	\begin{align}
-		H_{\alpha}(\w \otimes \w') &= \frac{1}{1-\alpha}\log \sum_{i,j'} \left[\w_i \w'_j\right]^{\alpha} \nonumber\\
+		H_{\alpha}(\w \otimes \w') &= \frac{1}{1-\alpha}\log \sum_{i,j} \left[\w_i \w'_j\right]^{\alpha} \nonumber\\
 		&= \frac{1}{1-\alpha}\log  \left [ \sum_i\w_i^\alpha \sum_j\w_j^{\prime \alpha} \right ] \nonumber\\
@@
     \caption{\textbf{R\'{e}nyi entropy $H_\alpha$ of the $\epsilon$-noisy Strange state.} $H_\alpha$ is increasing in $\alpha$ and $\epsilon$.
-The first dashed contour from the right corresponds to $H_\alpha(\rho_{\rm{S}}(\epsilon)) = 0$.
-In particular, $H_\alpha(\rho_{\rm{S}}(0)) = 0$ occurs at $\alpha \approx 1.31$.
+The rightmost dashed contour line corresponds to $H_\alpha(W_{\rho_{\rm{S}}(\epsilon)}) = 0$.
+In particular, $H_\alpha(W_{\rho_{\rm{S}}(0)}) = 0$ occurs at $\alpha \approx 1.31$.
     }
@@
 
+\vspace{10pt}
 \section*{Supplementary References}
-\vspace{-12pt}
+\vspace{-50pt}
 
@@
 \newblock \bibinfo{title}{Quantum systems with finite hilbert space}.
-\newblock \emph{\bibinfo{journal}{Reports on Progress in Physics}}
+\newblock \emph{\bibinfo{journal}{Rep. Prog. Phys.}}
   \textbf{\bibinfo{volume}{67}}, \bibinfo{pages}{267--320}
   (\bibinfo{year}{2004}).
-\newblock \urlprefix\url{https://doi.org/10.1088/0034-4885/67/3/r03}.
+%\newblock \urlprefix\url{https://doi.org/10.1088/0034-4885/67/3/r03}.
 
@@
   (\bibinfo{year}{1959}).
-\newblock
-  \urlprefix\url{https://onlinelibrary.wiley.com/doi/abs/10.1002/mana.19590200306}.
+%\newblock \urlprefix\url{https://onlinelibrary.wiley.com/doi/abs/10.1002/mana.19590200306}.
 
@@
   approach to thermodynamics}.
-\newblock \emph{\bibinfo{journal}{Reports on Progress in Physics}}
+\newblock \emph{\bibinfo{journal}{Rep. Prog. Phys.}}
   \textbf{\bibinfo{volume}{82}}, \bibinfo{pages}{114001}
   (\bibinfo{year}{2019}).
-\newblock \urlprefix\url{https://doi.org/10.1088/1361-6633/ab46e5}.
+%\newblock \urlprefix\url{https://doi.org/10.1088/1361-6633/ab46e5}.
 
@@
 \bibinfo{author}{Ash, R.}
-\newblock \emph{\bibinfo{title}{Information Theory}} (\bibinfo{publisher}{Dover
-  Publications Inc.}, \bibinfo{year}{1965}).
-\newblock
-  \urlprefix\url{https://www.semanticscholar.org/paper/Information-Theory-Ash/e9f30be9279c6000ce5602370950748cc2c79101}.
+\newblock \emph{\bibinfo{title}{Information Theory}} (\bibinfo{publisher}{Dover Publications Inc.}, \bibinfo{year}{1965}).
+%\newblock \urlprefix\url{https://www.semanticscholar.org/paper/Information-Theory-Ash/e9f30be9279c6000ce5602370950748cc2c79101}.
 
@@
   \bibinfo{pages}{4665--4674} (\bibinfo{year}{2000}).
-\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevE.62.4665}.
+%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevE.62.4665}.
 
@@
   localization in phase space}.
-\newblock \emph{\bibinfo{journal}{Journal of Physics A: Mathematical and
-  General}} \textbf{\bibinfo{volume}{34}}, \bibinfo{pages}{10123--10139}
+\newblock \emph{\bibinfo{journal}{J. Phys. A Math.}} \textbf{\bibinfo{volume}{34}}, \bibinfo{pages}{10123--10139}
   (\bibinfo{year}{2001}).
-\newblock \urlprefix\url{https://doi.org/10.1088/0305-4470/34/47/317}.
+%\newblock \urlprefix\url{https://doi.org/10.1088/0305-4470/34/47/317}.
 
